\chapter{A Concrete Naming Certificate for $\BoundedVariationUp$}
\label{ch:concrete-instances-boundedvariation-namecert}
\origin{human}

The $\BoundedVariationUp$ interface names the finite partition-variation packet used by real-analysis consumers of $\RealUp$ data. It follows the Jordan bounded-variation surface treated in Rudin, \emph{Principles of Mathematical Analysis}, and Folland, \emph{Real Analysis}, but expresses every read as a finite partition ledger over regular rational names, dyadic observations, endpoint transports, and package provenance. The packet does not introduce a completed function space, a supremum over all partitions, a variation measure, or a host real-valued function quotient.

Its dependency list is $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and interval-partition rows supplied by $\RationalIntervalUp$ or $\NestedIntervalUp$ when such endpoints are available.

The finite partition-variation ledger consumes the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational stream surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the dyadic observation rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}.

\begin{definition}[BoundedVariation carrier]
\label{def:bounded-variation-carrier}
A $\BoundedVariationUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
B=(I,\Pi,X,D,V,R,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $I$ is the rational or nested interval row on which the variation packet is read;
\item $\Pi$ is a finite ordered interval-partition ledger with displayed endpoint rows and common-refinement rows;
\item $X$ records the $\RealUp$ endpoint values or their $\RegSeqRatUp$ regular-name representatives at the partition points;
\item $D$ records the $\DyadicRatCoreUp$ observation rows used to compare endpoint differences on each partition edge;
\item $V$ is the finite dyadic variation-sum ledger attached to the displayed partition;
\item $R$ records common-refinement comparison rows for transported partitions and endpoint reads;
\item $H$, $C$, $P$, and $N$ are respectively the visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\BoundedVariationUp}$ provenance rows.
\end{enumerate}
The classifier compares accepted packets only through common refinements of $\Pi$, transported endpoint values, dyadic variation-sum ledgers, endpoint-difference comparisons, and the displayed provenance rows.
\end{definition}

\begin{theorem}[BoundedVariation NameCert obligations]
\label{thm:bounded-variation-namecert-obligations}
Every accepted $\BoundedVariationUp$ packet with carrier \autoref{def:bounded-variation-carrier} carries the following naming-certificate obligations:
\begin{enumerate}
\item carrier habitation by a constant $\RealUp$ or $\RegSeqRatUp$ endpoint row, with zero dyadic variation sum on every displayed finite partition;
\item classifier comparison by common refinement of the finite partition ledgers and componentwise endpoint transport;
\item dyadic variation-sum exactness for each displayed partition edge, read through $\DyadicRatCoreUp$ observations and $\RegSeqRatUp$ endpoint comparisons;
\item carrier transport under displayed $\hsame$ and $\Cont$ routes for interval rows, partitions, endpoint names, dyadic observations, variation sums, and refinement rows;
\item boundary exclusion of completed function spaces, variation measures, host supremum principles, quotient functions, and hidden partitions.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.BoundedVariationUp.BoundedVariationCarrier\_namecert\_obligations}
\begin{proof}
For habitation, take a constant real-name or regular-rational endpoint row. Every edge of a displayed finite partition has equal endpoint reads, so the dyadic edge differences and their finite sum are the zero variation ledger.

Classifier comparison is by common refinement. Refine two displayed partition ledgers to a shared finite ledger, transport the endpoint rows componentwise, and compare the dyadic edge observations along that shared list.

Variation-sum exactness is read edge by edge from the carrier. The $\DyadicRatCoreUp$ observations give the displayed endpoint-difference rows, and the finite sum row $V$ records exactly those edge rows and no unlisted partition.

Transport uses the stored $\hsame$ and $\Cont$ coordinates. Moving the interval, partition, endpoint, dyadic, sum, and refinement rows along those routes repacks the same finite packet with the same local $\NameCert$ provenance.

The boundary exclusion follows because the carrier has no coordinate for a completed function space, variation measure, host supremum over all partitions, quotient of functions, or hidden partition family.
\end{proof}

\begin{theorem}[BoundedVariation variation-ledger exactness]
\label{thm:bounded-variation-variation-ledger-exactness}
For every accepted $\BoundedVariationUp$ packet and every displayed finite partition row $\Pi$, the public variation read factors through the interval row, the ordered endpoint ledger, the $\RealUp$ or $\RegSeqRatUp$ endpoint names, the $\DyadicRatCoreUp$ edge-difference observations, and the finite dyadic variation-sum row $V$. A common-refinement read transports the same edge data and repacks the same finite sum ledger.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedVariationUp.BoundedVariationCarrier\_variation\_ledger\_exactness}
\begin{proof}
Start from the displayed partition row $\Pi$. Its ordered endpoint ledger gives the only edges whose variation contribution may be read by the packet.

For each edge, read the two endpoint names through $X$ and the dyadic comparison row through $D$. The regular-name and real-seal data are therefore consumed before the finite variation sum is formed.

The row $V$ stores the finite sum of exactly those displayed edge observations. When a common refinement is supplied by $R$, the endpoint transports and dyadic edge rows are repacked along the refinement ledger, so the public read remains a finite partition-sum read.
\end{proof}

\begin{theorem}[BoundedVariation common-refinement classifier exactness]
\label{thm:bounded-variation-common-refinement-classifier-exactness}
Let $B$ and $B'$ be accepted $\BoundedVariationUp$ packets with carrier coordinates as in \autoref{def:bounded-variation-carrier}. The local $\BoundedVariationUp$ classifier identifies $B$ and $B'$ if and only if there is a displayed common finite refinement whose interval row, transported endpoint $\RealUp$ or $\RegSeqRatUp$ names, $\DyadicRatCoreUp$ edge observations, finite variation-sum ledger, and $\Pkg$ and $\NameCert$ provenance rows compare componentwise by the visible $\hsame$ and $\Cont$ routes stored in the two packets.
\end{theorem}
\begin{proof}
Unfold the carrier of \autoref{def:bounded-variation-carrier}. The classifier has no hidden coordinate beyond the interval row, finite partition ledger, endpoint names, dyadic edge observations, variation-sum ledger, common-refinement rows, and displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

For the forward direction, project the classifier witness to its common-refinement rows. Apply \autoref{thm:bounded-variation-variation-ledger-exactness} to both packets on that refinement. Both public variation reads therefore factor through the same displayed endpoint ledger, dyadic edge observations, and finite variation-sum row, with the endpoint and provenance coordinates transported by the recorded $\hsame$ and $\Cont$ routes.

For the reverse direction, start from the displayed common finite refinement and its componentwise comparisons. Repack the transported interval, endpoint, edge-observation, variation-sum, $\Pkg$, and $\NameCert$ rows into the local classifier data. Since the exactness theorem accounts for every public variation read through that finite ledger, no further comparison data are required.
\end{proof}
\leanchecked{BEDC.Derived.BoundedVariationUp.BoundedVariationCarrier\_common\_refinement\_classifier\_exactness}

\begin{theorem}[BoundedVariation carrier transport]
\label{thm:bounded-variation-carrier-transport}
Let $B$ and $B'$ be accepted $\BoundedVariationUp$ packets. If their interval rows, finite partition ledgers, endpoint-name rows, dyadic observation rows, variation-sum ledgers, and common-refinement rows are transported componentwise by displayed $\hsame$ routes and read through the corresponding $\Cont$ routes, then the local classifier identifies the same bounded-variation packet on every common finite refinement.
\end{theorem}
\begin{proof}
Unfold the classifier of \autoref{def:bounded-variation-carrier}. It compares only the interval row, partition ledger, endpoint names, dyadic observations, finite variation sums, refinement rows, and provenance.

Move each of those coordinates along the displayed $\hsame$ routes. The $\Cont$ routes preserve the read order from an interval request to a partition, then to endpoint names, edge observations, and the finite sum row.

Apply \autoref{thm:bounded-variation-variation-ledger-exactness} on the common refinement. The transported endpoint and dyadic rows repack the same finite variation ledger, leaving no extra classifier coordinate on which the packets could differ.
\end{proof}
\leanchecked{BEDC.Derived.BoundedVariationUp.BoundedVariationCarrier\_transport}

\begin{theorem}[BoundedVariation no-escape boundary]
\label{thm:bounded-variation-no-escape-boundary}
The $\BoundedVariationUp$ public boundary exports only finite interval-partition rows, transported endpoint names, dyadic edge-difference observations, common-refinement ledgers, finite variation sums, and visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. It exports no completed function-space carrier, variation measure, supremum over all partitions, quotient of real-valued functions, or hidden partition family.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedVariationUp.BoundedVariationCarrier\_public\_rows\_zero\_head\_absurd}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:bounded-variation-carrier}. The only analysis-facing data are the displayed interval row, the finite partition ledger, endpoint names, dyadic observations, the finite sum row, and common-refinement rows.

The exactness theorem \autoref{thm:bounded-variation-variation-ledger-exactness} shows that every public variation read factors through those rows. The transport theorem \autoref{thm:bounded-variation-carrier-transport} shows that moving the packet preserves the same finite ledger.

No coordinate names a completed function space, variation measure, host supremum over all partitions, quotient function, or hidden partition family. Hence none of those objects is exported by the public boundary.
\end{proof}

\begin{theorem}[BoundedVariation partition scope binding]
\label{thm:bounded-variation-partition-scope-binding}
The carrier, NameCert obligation surface, and variation-ledger exactness rows of \autoref{def:bounded-variation-carrier}, \autoref{thm:bounded-variation-namecert-obligations}, and \autoref{thm:bounded-variation-variation-ledger-exactness} bind the finite partition-variation packet to $\DyadicRatCoreUp$, $\NestedIntervalUp$, $\RationalIntervalUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The bound is a finite partition-sum scope: every variation read passes through the displayed interval row, partition ledger, endpoint rows, dyadic edge observations, finite variation sum, and local provenance before it can be consumed by a bounded-variation classifier.
\end{theorem}
\begin{proof}
Start with the carrier in \autoref{def:bounded-variation-carrier}. It names the interval row, finite partition ledger, endpoint rows, dyadic observations, finite variation sum, common-refinement rows, and provenance rows.

Apply \autoref{thm:bounded-variation-namecert-obligations}. The local certificate records habitation, classifier comparison, variation-sum exactness, carrier transport, and boundary exclusion for those same coordinates.

Finally use \autoref{thm:bounded-variation-variation-ledger-exactness}. Each public variation read factors through a displayed finite partition and its dyadic edge ledger, so the partition-sum scope is exactly the listed dependency stack.
\end{proof}

\begin{theorem}[BoundedVariation refinement ledger scope]
\label{thm:bounded-variation-refinement-ledger-scope}
The common-refinement classifier exactness row of \autoref{thm:bounded-variation-common-refinement-classifier-exactness}, together with the variation-ledger exactness row of \autoref{thm:bounded-variation-variation-ledger-exactness}, gives the scoped refinement ledger for $\BoundedVariationUp$. Accepted packets compare only by a displayed common finite refinement whose interval, endpoint, dyadic observation, finite sum, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are visible over $\DyadicRatCoreUp$, $\NestedIntervalUp$, $\RationalIntervalUp$, $\RealUp$, $\RegSeqRatUp$, and $\StreamNameUp$.

No classifier comparison in this scope uses a hidden partition family, host supremum, variation measure, quotient function, or completed function-space carrier.
\end{theorem}
\begin{proof}
Project the classifier through \autoref{thm:bounded-variation-common-refinement-classifier-exactness}. The comparison data are a displayed common finite refinement with componentwise endpoint, dyadic, finite-sum, package, and naming rows.

Use \autoref{thm:bounded-variation-variation-ledger-exactness} on that refinement. Both public variation reads are finite sums over the displayed edge observations and transported endpoint rows.

Thus the refinement ledger is already the classifier scope. Since the carrier has no hidden partition family or host supremum coordinate, no additional comparison object can enter.
\end{proof}

\begin{theorem}[BoundedVariation finite Jordan-split scope]
\label{thm:bounded-variation-jordan-finite-split-scope}
For an accepted $\BoundedVariationUp$ packet, a displayed finite partition may be split into positive-edge and negative-edge dyadic variation ledgers using only the listed endpoint rows. The split reads the $\RealUp$ or $\RegSeqRatUp$ endpoint names, the $\DyadicRatCoreUp$ endpoint-difference observations, the finite partition ledger, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\BoundedVariationUp}$ provenance.

This is only a finite displayed partition split. It does not assert Jordan decomposition, a variation measure, a host supremum over all partitions, or a completed function-space object.
\end{theorem}
\begin{proof}
Project the finite partition ledger and endpoint rows from the carrier. Each edge already carries two endpoint reads and a displayed dyadic difference observation.

Split the finite list of edge observations by the sign recorded in the $\DyadicRatCoreUp$ row. The positive-edge and negative-edge ledgers are therefore subledgers of the displayed partition, transported by the same $\hsame$ and $\Cont$ routes as the original variation sum.

Repack the two ledgers with the existing package and naming provenance. Since the construction uses only the displayed finite partition, it does not create a Jordan decomposition or a measure-valued object.
\end{proof}

\begin{theorem}[BoundedVariation refinement additivity scope]
\label{thm:bounded-variation-refinement-additivity-scope}
For two accepted $\BoundedVariationUp$ packets compared on a displayed common finite refinement, the variation read is additive over the refinement blocks in the finite dyadic ledger. Each block sum uses only $\RealUp$ or $\RegSeqRatUp$ endpoint rows, $\DyadicRatCoreUp$ edge observations, the common-refinement row, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\BoundedVariationUp}$ provenance.

The additivity claim is restricted to the displayed common refinement and exports no supremum principle, variation measure, hidden partition family, quotient function, or completed function space.
\end{theorem}
\begin{proof}
Start with the refinement ledger scope. It supplies one displayed common finite refinement whose endpoint and dyadic edge rows are visible to both packets.

Use variation-ledger exactness on each block of that common refinement. The finite dyadic sum for a block is obtained by summing exactly the edge observations in that block, with endpoint transports carried by the displayed $\hsame$ and $\Cont$ rows.

Concatenate the finite block sums inside the same common-refinement ledger. The package and naming rows remain unchanged, and the statement never ranges over all partitions or any completed function object.
\end{proof}

\begin{theorem}[BoundedVariation partition-concatenation ledger]
\label{thm:bounded-variation-partition-concatenation-ledger}
Let $L_0$ and $L_1$ be displayed $\BoundedVariationUp$ partition ledgers in the sense of \autoref{def:bounded-variation-partition-ledger}. Suppose the final endpoint row of $L_0$ and the initial endpoint row of $L_1$ are related by a displayed transported endpoint row over the same $\RealUp$ or $\RegSeqRatUp$ name, with matching $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\BoundedVariationUp}$ provenance. Then the concatenated ordered partition row is again a displayed $\BoundedVariationUp$ partition ledger, and its finite dyadic variation-sum row is the concatenation of the visible edge-observation sums of $L_0$ and $L_1$.

This ledger composition is restricted to the displayed finite partitions and their transported shared endpoint. It does not assert Jordan decomposition, variation measures, host suprema, quotient function equality, completed function spaces, or any hidden partition family.
\end{theorem}
\begin{proof}
Project $L_0$ and $L_1$ through \autoref{def:bounded-variation-partition-ledger}. Each ledger exposes an interval row, an ordered finite partition, adjacent-edge rows, endpoint-name rows, dyadic edge observations, a finite variation sum, refinement rows, transport, continuation, package provenance, and local naming data.

Use the transported shared endpoint to identify the terminal endpoint row of $L_0$ with the initial endpoint row of $L_1$ inside the displayed $\hsame$ and $\Cont$ surface. This supplies the only splice row needed to concatenate the two ordered partition ledgers without adding an unrecorded endpoint.

Apply \autoref{thm:bounded-variation-refinement-additivity-scope} to read the two edge lists as finite dyadic blocks, and apply \autoref{thm:bounded-variation-endpoint-transport-scope} to keep the shared endpoint and the adjacent edge observations on the displayed dependency stack. The concatenated variation row is therefore the finite concatenation of the two visible edge-observation sums.

Finally use \autoref{thm:bounded-variation-no-escape-boundary}. The construction has used only displayed partition, endpoint, dyadic, transport, continuation, package, and naming rows, so the resulting ledger cannot export a host supremum, variation measure, quotient function, completed function-space carrier, or hidden partition family.
\end{proof}

\begin{theorem}[BoundedVariation endpoint transport scope]
\label{thm:bounded-variation-endpoint-transport-scope}
The carrier transport and no-escape boundary rows of \autoref{thm:bounded-variation-carrier-transport} and \autoref{thm:bounded-variation-no-escape-boundary} give the endpoint transport scope for $\BoundedVariationUp$. Endpoint reads may move only along displayed $\hsame$ and $\Cont$ routes for the interval row, finite partition ledger, $\RealUp$ or $\RegSeqRatUp$ endpoint names, $\StreamNameUp$ read schedule, $\DyadicRatCoreUp$ observations, finite variation ledger, $\BHist$, $\Pkg$, and $\NameCert$ provenance.

The endpoint transport scope exports no completed function space, variation measure, host supremum over all partitions, quotient real-valued function, or hidden partition row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bounded-variation-carrier-transport}. It moves interval rows, finite partition ledgers, endpoint-name rows, dyadic observation rows, variation-sum ledgers, and common-refinement rows componentwise through displayed transport and continuation routes.

Then use \autoref{thm:bounded-variation-no-escape-boundary}. The public boundary exports only the finite partition rows, transported endpoints, dyadic edge observations, common refinements, finite sums, and visible provenance.

The two rows together give the endpoint transport scope. Every endpoint read remains attached to the displayed dependency stack, and no absent host object is exported.
\end{proof}

\begin{definition}[BoundedVariation partition ledger]
\label{def:bounded-variation-partition-ledger}
A $\BoundedVariationUp$ partition ledger is a finite $\BHist$ packet
$$
L=(I,\Pi,E,X,D,V,R,H,C,P,N)
$$
whose rows refine the carrier of \autoref{def:bounded-variation-carrier} for a
single displayed interval read:
\begin{enumerate}
\item $I$ is the displayed rational or nested interval row;
\item $\Pi$ is a finite ordered partition of $I$ with endpoint order and edge rows;
\item $E$ is the finite edge ledger induced by adjacent endpoints of $\Pi$;
\item $X$ records the endpoint $\RealUp$ rows or their $\RegSeqRatUp$ regular-name representatives;
\item $D$ records the $\DyadicRatCoreUp$ edge observations used to compare adjacent endpoint values;
\item $V$ is the finite dyadic variation sum over exactly the edge observations in $D$;
\item $R$ records refinement rows comparing $\Pi$ with displayed finer partitions and their transported edge ledgers;
\item $H$ records the componentwise $\hsame$ transports for interval, partition, endpoint, edge-observation, finite-sum, refinement, package, and naming rows;
\item $C$ records the displayed $\Cont$ routes from an interval request to endpoints, dyadic edge reads, finite variation sums, refinement comparison, and consumer exposure;
\item $P$ and $N$ are the $\Pkg$ provenance and local $\NameCert_{\BoundedVariationUp}$ rows.
\end{enumerate}
The ledger has no coordinate for a host supremum over all partitions, a
completed function space, a variation measure, a quotient of real-valued
functions, or a hidden partition family.
\end{definition}

\begin{theorem}[BoundedVariation partition refinement monotonicity]
\label{thm:bounded-variation-partition-refinement-monotonicity}
Let $L=(I,\Pi,E,X,D,V,R,H,C,P,N)$ be a
$\BoundedVariationUp$ partition ledger in the sense of
\autoref{def:bounded-variation-partition-ledger}. If $\Pi'$ is a displayed
finite refinement of $\Pi$ whose endpoint, edge-observation, and finite-sum
rows are recorded in $R$, then the variation read on $\Pi'$ is obtained by
repacking the same finite edge-observation ledger through $H$ and $C$. The
refinement comparison therefore cannot introduce a host supremum over all
partitions or any unrecorded variation object.
\end{theorem}
\begin{proof}
Project the ledger $L$. The only partition rows available to a consumer are the
displayed partition $\Pi$ and the displayed refinement rows stored in $R$.

Read the refinement edge by edge. Each refined edge obtains its endpoint names
from $X$ and its dyadic observation from $D$ after the transports recorded in
$H$ and the continuation routes recorded in $C$.

The finite sum row for the refinement is therefore a repacking of visible edge
observations. Since the packet has no row ranging over all partitions and no
measure-valued coordinate, the refinement read is monotone only inside the
displayed finite ledger surface.
\end{proof}

\begin{theorem}[BoundedVariation Cauchy consumer boundary]
\label{thm:bounded-variation-cauchy-consumer-boundary}
Every $\RegSeqRatUp$ or $\RealUp$ consumer of a $\BoundedVariationUp$ packet may
read bounded variation only through finite partition ledgers of
\autoref{def:bounded-variation-partition-ledger}. Such a consumer receives
endpoint regular-name or real-name rows, $\DyadicRatCoreUp$ edge observations,
displayed refinement rows, $\hsame$ transports, $\Cont$ routes, $\Pkg$
provenance, and local $\NameCert$ data; it receives no host supremum, variation
measure, completed function-space carrier, quotient function, or hidden
partition family.
\end{theorem}
\begin{proof}
Start from a consumer request. The carrier of
\autoref{def:bounded-variation-carrier} and the ledger of
\autoref{def:bounded-variation-partition-ledger} expose only interval,
partition, endpoint, dyadic observation, finite-sum, refinement, transport,
route, provenance, and naming rows.

If the consumer is a $\RegSeqRatUp$ consumer, it reads endpoint data through the
regular-name rows in $X$ before any dyadic edge observation is formed. If the
consumer is a $\RealUp$ consumer, it reads the same endpoint positions through
the displayed real-name rows and then through the dyadic observation rows.

Apply the refinement monotonicity row
\autoref{thm:bounded-variation-partition-refinement-monotonicity}. Refinement
access remains finite and displayed, so the consumer boundary is exhausted by
partition ledgers and dyadic observations rather than by any absent host
supremum or completed function object.
\end{proof}
\leanchecked{BEDC.Derived.BoundedVariationUp.BoundedVariationCauchyConsumerBoundary}

\begin{theorem}[BoundedVariation real dependency scope]
\label{thm:bounded-variation-real-dependency-scope}
Every endpoint-variation read consumed from a $\BoundedVariationUp$ packet reads $\RealUp$ endpoint rows through \autoref{ch:concrete-instances-real-namecert}, $\RegSeqRatUp$ regular-name rows through \autoref{ch:concrete-instances-regseqrat-namecert}, $\StreamNameUp$ read windows through \autoref{ch:concrete-instances-streamname-namecert}, and $\DyadicRatCoreUp$ edge observations through \autoref{ch:concrete-instances-dyadicratcore-namecert}. The $\BoundedVariationUp$ packet only packages those sibling rows into a finite interval-partition ledger with visible transport, continuation, package, and naming provenance.
\end{theorem}
\begin{proof}
Start from the carrier of \autoref{def:bounded-variation-carrier}. Its endpoint coordinate $X$ stores only $\RealUp$ endpoint values or $\RegSeqRatUp$ regular-name representatives, while $D$ stores the $\DyadicRatCoreUp$ observations attached to partition edges.

Use the partition ledger of \autoref{def:bounded-variation-partition-ledger}. A consumer reaches endpoints by first selecting a displayed finite partition and then reading the endpoint rows, stream windows, dyadic edge rows, and finite variation-sum row through the recorded routes.

Finally apply \autoref{thm:bounded-variation-cauchy-consumer-boundary}. Every $\RegSeqRatUp$ or $\RealUp$ consumer is exhausted by those ledger rows, so the dependency scope is exactly the cited RealUp, RegSeqRatUp, StreamNameUp, and DyadicRatCoreUp sibling surface together with the local $\BoundedVariationUp$ provenance.
\end{proof}

\closureat{BoundedVariationUp}{seedStr}
\closureat{BoundedVariationUp}{obligationStr}
\closureat{BoundedVariationUp}{scopedStr}

\begin{closurestatus}{\BoundedVariationUp}
  \constructivestory{A $\BoundedVariationUp$ packet is generated from an interval row, a finite ordered partition ledger, $\RealUp$ or $\RegSeqRatUp$ endpoint names, $\DyadicRatCoreUp$ edge observations, a finite dyadic variation-sum row, common-refinement rows, displayed transport, continuation, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{thm:bounded-variation-partition-scope-binding}, \autoref{thm:bounded-variation-refinement-ledger-scope}, \autoref{thm:bounded-variation-endpoint-transport-scope}, and \autoref{thm:bounded-variation-real-dependency-scope} bind finite partition variation, common-refinement comparison, endpoint transport, dyadic variation-sum ledger, sibling dependency scope, and no-escape boundary to the displayed $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ scope.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close completed function spaces, variation measures, host suprema over all partitions, quotient real-valued functions, hidden partition families, Jordan decomposition, or bridge checking.}
  \upgradepath{Public closure requires a public finite-variation consumer theorem over the same displayed partition and endpoint transport surface.}
\end{closurestatus}
