\chapter{A Concrete Naming Certificate for $\GaloisGroupUp$}
\label{ch:concrete-instances-galoisgroup-namecert}

The Galois-group interface $\GaloisGroupUp$ packages the group of field automorphisms of a Galois extension fixing the base field pointwise. It depends on $\NameCert_{\GaloisExtUp}$ (\autoref{ch:concrete-instances-galoisext-namecert}) and $\NameCert_{\GroupUp}$ (\autoref{ch:concrete-instances-group-namecert}).

\section{Carrier definition}
\label{sec:galoisgroup-carrier}

\begin{definition}[GaloisGroupUp BHist automorphism-action packet]
\label{def:galoisgroup-bhist-automorphism-action-packet}
A $\GaloisGroupUp$ automorphism-action packet is a finite $\mathsf{BHist}$
tuple $(E,G,b,a,m,i,c,\rho,\lambda)$ over two consumed dependency packets. The
row $E$ is a $\NameCert_{\GaloisExtUp}$ packet, read through its public
extension carrier, normality, separability, classifier, exactness, and ledger
surface. The row $G$ is a $\NameCert_{\GroupUp}$ packet, read through its
operation, unit, inverse, associativity, congruence, and inverse-law surface.

The row $b$ is the fixed-base row. It records, for each displayed base-field
endpoint of $E$, that the automorphism endpoint leaves that base endpoint in
the same $\hsame$ class. The row $a$ is the automorphism-action row: source
and target extension endpoints are finite $\mathsf{BHist}$ endpoints from
$E$, and the action is carried only by $\mathsf{Cont}$ rows and the displayed
classifier of $E$. The unit row is read from the $\GroupUp$ unit endpoint of
$G$ and the GaloisExtUp identity classifier of $E$. The row $m$ is the
composition row, aligning the $\GroupUp$ multiplication operation of $G$ with
composition of the displayed automorphism-action rows. The row $i$ is the
inverse row, aligning the $\GroupUp$ inverse operation of $G$ with inverse
automorphism-action rows.

The row $c$ is the classifier row. It compares automorphism packets by
$\hsame$ on their finite extension endpoints, fixed-base rows, action rows,
composition rows, and inverse rows, without requiring equality of host fields,
ambient function spaces, or quotient representatives. The row $\rho$ is the
$\mathsf{Pkg}$ provenance row assigning every displayed face to either the
Galois-extension packet $E$, the group packet $G$, or the Galois-group
automorphism surface. The finite ledger $\lambda$ is the $\mathsf{Cont}$ list
containing exactly the dependency rows, fixed-base rows, identity rows, action
rows, composition rows, inverse rows, classifier rows, provenance rows, and
exactness rows consumed by the public $\NameCert_{\GaloisGroupUp}$ interface.
\end{definition}

\section{The certificate}
\label{sec:galoisgroup-certificate}

\begin{theorem}[GaloisGroupUp fixed-base carrier obligation]
\label{thm:galoisgroup-fixed-base-carrier-obligation}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, carrier
acceptance for $\NameCert_{\GaloisGroupUp}$ is exactly acceptance of
fixed-base automorphism rows whose extension endpoints are read from the
public $\NameCert_{\GaloisExtUp}$ surface of $E$ and whose operation endpoints
are read from the $\NameCert_{\GroupUp}$ surface of $G$. No carrier clause
asks for equality of host fields, ambient endomorphism sets, or uncarried
base-field elements.
\end{theorem}
\begin{proof}
Project the packet to $E$ and $G$. The Galois-extension public boundary of
\autoref{thm:galoisext-public-obligation-boundary} supplies the extension
carrier, classifier, exactness, normality, separability, and finite ledger
rows. The group certificate supplies the operation surface, inverse surface,
congruence rows, and inverse-law rows through the $\GroupUp$ public packet.

For the forward direction, carrier acceptance exposes a fixed-base
automorphism row. Reading the row through
\autoref{def:galoisgroup-bhist-automorphism-action-packet} projects each
extension endpoint to $E$, each multiplication or inverse endpoint to $G$, and
each fixed-base comparison to an $\hsame$ row in the finite ledger
$\lambda$. Thus the accepted carrier is only a displayed BEDC row family over
the two consumed packets.

For the reverse direction, start with fixed-base automorphism rows whose
endpoints are already read from $E$ and $G$ with the stated ledger and package
provenance. Repack those rows as $b$ and $a$, attach the classifier row $c$,
and retain the same $\mathsf{Pkg}$ row $\rho$ and $\mathsf{Cont}$ ledger
$\lambda$. This constructs the carrier face of
$\NameCert_{\GaloisGroupUp}$ without adding any host-field equality clause.
\end{proof}
\leanchecked{BEDC.Derived.GaloisGroupUp.GaloisGroupAutomorphismActionPacket\_fixed\_base\_carrier\_obligation}

\begin{theorem}[GaloisGroupUp fixed-base classifier]
\label{thm:galoisgroup-fixed-base-classifier}
For two accepted automorphism-action packets
$(E,G,b,a,m,i,c,\rho,\lambda)$ and
$(E',G',b',a',m',i',c',\rho',\lambda')$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the fixed-base
automorphism classifier is the conjunction of the inherited
$\NameCert_{\GaloisExtUp}$ classifier on the extension packets, the inherited
$\NameCert_{\GroupUp}$ classifier on the operation packets, and the $\hsame$
comparisons of the displayed fixed-base, action, composition, and inverse
rows. In particular, two rows are classified only through the dependency
surfaces and endpoint comparison inside the finite automorphism-action packet.
\end{theorem}
\begin{proof}
Project each accepted automorphism-action packet to its $E$ and $G$ rows.
\autoref{thm:galoisext-public-obligation-boundary} says that the available
extension information is precisely the carrier, normality, separability,
classifier, stability, ledger, and exactness surface of the extension packet.
The group certificate supplies only the operation, unit, inverse, congruence,
and inverse-law rows exposed by its public packet.

Now inspect the automorphism-specific rows. The fixed-base, action,
composition, and inverse rows are all finite $\mathsf{BHist}$ rows inside
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. Their comparisons
are therefore exactly the restricted $\hsame$ rows recorded in the finite
ledger $\lambda$ and its counterpart.

Combining the projected dependency classifiers with these row comparisons
gives the stated classifier. Reflexive, symmetric, and transitive uses are
inherited from the dependency classifiers and from the structural $\hsame$
laws, and repacking those rows returns an accepted fixed-base
automorphism-action packet.
\end{proof}

\begin{theorem}[GaloisGroupUp composition closure]
\label{thm:galoisgroup-composition-closure}
Let $x$ and $y$ be accepted fixed-base automorphism-action rows of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. If the target
endpoint of $x$ is $\hsame$-classified with the source endpoint of $y$, and
the packet contains a displayed $\Cont$ row composing their automorphism
ledgers, then the composed row is again accepted by the $\GaloisGroupUp$
automorphism-action packet. Its fixed-base witness is obtained by composing
the two fixed-base witness rows and transporting the middle endpoint through
$\hsame$.
\end{theorem}
\leanchecked{BEDC.Derived.GaloisGroupUp.GaloisGroupAutomorphismActionPacket\_composition\_closure}
\begin{proof}
Read the two accepted rows through the same packet shape. Each supplies a
$\GaloisExtUp$ projection, a $\GroupUp$ projection, a displayed
automorphism-action row, endpoint rows, a fixed-base row, classifier rows, and
$\Pkg$ provenance through
\autoref{def:galoisgroup-bhist-automorphism-action-packet}.

The displayed $\Cont$ row concatenates the two automorphism ledgers. The
middle endpoint comparison supplies the transport needed to align the target
of $x$ with the source of $y$, so the concatenated ledger has the source
endpoint of $x$ and the target endpoint of $y$.

For the fixed-base face, compose the two fixed-base witness rows. Since each
row fixes the base endpoint pointwise inside the inherited GaloisExtUp
surface, the composite fixes the same base endpoint after transporting the
middle row by $\hsame$.

Finally, repack the dependency projections, composed display, endpoints,
fixed-base witness, $\Cont$ ledger, classifier rows, and $\Pkg$ provenance.
The result is one of the finite packets accepted by the carrier, so
composition is closed.
\end{proof}

\begin{theorem}[GaloisGroupUp inverse closure]
\label{thm:galoisgroup-inverse-closure}
Every accepted automorphism-action row of
\autoref{def:galoisgroup-bhist-automorphism-action-packet} exposes an inverse
row through the $\GroupUp$ dependency surface. The inverse row reverses the
displayed source and target endpoints, carries the inverse automorphism ledger
supplied by $\NameCert_{\GroupUp}$, preserves the same fixed-base endpoint up
to $\hsame$, and is accepted by the same $\GaloisGroupUp$ packet.
\end{theorem}
\begin{proof}
Unpack the accepted automorphism-action row into its source GaloisExtUp
packet, GroupUp packet, displayed action row, endpoints, fixed-base witness,
classifier rows, composition ledger, inverse row, and $\Pkg$ provenance.

Use the $\NameCert_{\GroupUp}$ dependency cited in
\autoref{ch:concrete-instances-group-namecert}. Its inverse surface supplies
the inverse operation row together with the left-unit and right-unit
classification rows for the automorphism ledger. These rows reverse the
displayed source and target endpoints.

The fixed-base witness is stable under this reversal because the original row
fixes the base endpoint and the inverse ledger is classified with the identity
row on that endpoint by the GroupUp inverse laws. Transport the displayed
base comparison by $\hsame$ to obtain the fixed-base row for the inverse.

Repack the reversed endpoints, inverse ledger, fixed-base witness, inherited
dependency projections, classifier rows, and $\Pkg$ provenance. This is again
a finite packet of the form required by
\autoref{def:galoisgroup-bhist-automorphism-action-packet}.
\end{proof}

\begin{theorem}[GaloisGroupUp unit automorphism row]
\label{thm:galoisgroup-unit-automorphism-row}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the unit row
inherited from the $\NameCert_{\GroupUp}$ dependency $G$ repacks as the
fixed-base identity automorphism row on every endpoint accepted by the public
$\NameCert_{\GaloisExtUp}$ boundary of $E$. The resulting row is classified by
the same $\GaloisGroupUp$ classifier as the displayed identity action, and its
ledger uses only the unit, operation, congruence, and endpoint rows already
carried by $G$, $E$, and $\lambda$.
\end{theorem}
\begin{proof}
Project the packet by
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. The
Galois-extension side is the public boundary of
\autoref{thm:galoisext-public-obligation-boundary}, so every endpoint under
discussion is an accepted extension endpoint with classifier, exactness, and
finite ledger rows in $E$.

On the group side, read the operation, unit, associativity, congruence, and
two-sided inverse-law surface from the $\NameCert_{\GroupUp}$ packet named in
\autoref{ch:concrete-instances-group-namecert}. The unit operation endpoint is
therefore already a carried row of $G$.

Repack that unit endpoint as the identity automorphism-action row. Its
fixed-base face is the identity comparison on each base endpoint of $E$, and
the same endpoint is transported through the $\hsame$ rows in $\lambda$.
\autoref{thm:galoisgroup-composition-closure} supplies compatibility with the
composition row, while \autoref{thm:galoisgroup-inverse-closure} supplies the
inverse-facing row needed by the same packet.

The resulting finite tuple has exactly the rows required by
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. Hence the inherited
GroupUp unit row is the GaloisGroupUp fixed-base identity automorphism row.
\end{proof}

\begin{theorem}[GaloisGroupUp composition associativity row]
\label{thm:galoisgroup-composition-associativity-row}
Let $x$, $y$, and $z$ be accepted fixed-base automorphism-action rows of an
automorphism-action packet
$(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. Suppose the target
endpoint of $x$ is $\hsame$-classified with the source endpoint of $y$, the
target endpoint of $y$ is $\hsame$-classified with the source endpoint of $z$,
and the two finite $\mathsf{Cont}$ parenthesizations
$(z\circ y)\circ x$ and $z\circ(y\circ x)$ are both displayed by the composition
row $m$. Then the two parenthesized rows are classified by the inherited
$\GroupUp$ associativity row, transported along the endpoint $\hsame$ rows from
the public $\NameCert_{\GaloisExtUp}$ boundary of $E$.
\end{theorem}
\begin{proof}
Project $x$, $y$, and $z$ through
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. The GaloisExtUp
public boundary of \autoref{thm:galoisext-public-obligation-boundary} supplies
the accepted source, middle, and target endpoints together with the classifier
rows that identify the two displayed middle endpoints.

Apply \autoref{thm:galoisgroup-composition-closure} first to $x$ and $y$, then
to the resulting row and $z$. This constructs the finite $\mathsf{Cont}$ row for
$(z\circ y)\circ x$ with the required fixed-base witness and provenance.

Apply \autoref{thm:galoisgroup-composition-closure} in the other order, first
to $y$ and $z$ and then to $x$ with the result. This constructs the finite
$\mathsf{Cont}$ row for $z\circ(y\circ x)$ over the same outer endpoints.

The $\NameCert_{\GroupUp}$ dependency $G$ supplies the operation, unit,
associativity, congruence, and two-sided inverse-law surface named in
\autoref{ch:concrete-instances-group-namecert}. Its associativity row
classifies the two operation parenthesizations in $G$, and the endpoint
$\hsame$ rows from $E$ transport that classification to the displayed
automorphism-action rows.

Repacking the transported classifier, the two composition ledgers, the
fixed-base witnesses, and the $\Pkg$ provenance gives the claimed
GaloisGroupUp classifier row.
\end{proof}

\begin{theorem}[GaloisGroupUp inverse cancellation rows]
\label{thm:galoisgroup-inverse-cancellation-rows}
For every accepted fixed-base automorphism-action row $x$ of an
automorphism-action packet
$(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, let $x^{-1}$ be the
inverse row supplied by \autoref{thm:galoisgroup-inverse-closure}. The composed
rows $x^{-1}\circ x$ and $x\circ x^{-1}$ are accepted by
\autoref{thm:galoisgroup-composition-closure} and are classified with the unit
automorphism row of \autoref{thm:galoisgroup-unit-automorphism-row} by the
inherited left and right inverse laws of the $\NameCert_{\GroupUp}$ dependency,
with endpoint transport through the public $\NameCert_{\GaloisExtUp}$ boundary.
\end{theorem}
\begin{proof}
Start with the accepted row $x$ and unpack it using
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. The endpoint rows,
fixed-base row, classifier row, inverse row, provenance row, and finite ledger
all live in the same packet, while
\autoref{thm:galoisext-public-obligation-boundary} supplies the public
GaloisExtUp classifier rows needed for endpoint transport.

Use \autoref{thm:galoisgroup-inverse-closure} to obtain the accepted inverse
row $x^{-1}$. Its source and target are the reversed endpoints of $x$, and its
fixed-base witness is transported by the same $\hsame$ comparisons on the base
endpoint.

Apply \autoref{thm:galoisgroup-composition-closure} to $x$ followed by
$x^{-1}$, and again to $x^{-1}$ followed by $x$. These applications produce the
two finite composition ledgers and preserve the fixed-base witness on both
sides.

The $\NameCert_{\GroupUp}$ packet $G$ supplies the operation, unit, congruence,
associativity, and two-sided inverse-law rows from the GroupUp surface named in
\autoref{ch:concrete-instances-group-namecert}. The right inverse law classifies
$x\circ x^{-1}$ with the unit row, and the left inverse law classifies
$x^{-1}\circ x$ with the unit row.

Finally, \autoref{thm:galoisgroup-unit-automorphism-row} identifies that unit
row with the fixed-base identity automorphism row over $E$. Repacking the two
inverse-law classifications with the endpoint $\hsame$ transports and the
ledger $\lambda$ gives the two claimed GaloisGroupUp cancellation rows.
\end{proof}

\begin{theorem}[GaloisGroupUp identity row closure]
\label{thm:galoisgroup-identity-row-closure}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the $\GroupUp$
unit row of $G$, read through the GaloisExtUp identity classifier of $E$ and
the fixed-base row $b$, is an accepted $\GaloisGroupUp$ automorphism-action row.
It fixes every displayed base endpoint by $\hsame$, carries only rows listed in
$\lambda$, and uses no equality of host fields or ambient automorphism sets.
\end{theorem}
\begin{proof}
Project the packet to its consumed rows $E$ and $G$. The Galois-extension
projection supplies the displayed extension endpoints, the identity classifier,
and the exactness rows on the public extension surface. The group projection
supplies the unit endpoint, the unit classifier rows, and the provenance needed
to read the unit as a finite $\mathsf{BHist}$ row.

Now combine those projections with the fixed-base row $b$. For each displayed
base endpoint, the identity classifier leaves the endpoint in its original
$\hsame$ class, and $b$ records that this comparison is part of the finite
automorphism ledger. Thus the unit action fixes every displayed base endpoint.

Finally, repack the base row, identity action row, classifier row $c$,
provenance row $\rho$, and the same finite ledger $\lambda$. The resulting row
has the packet shape required by
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, so it is accepted
by the public $\NameCert_{\GaloisGroupUp}$ carrier.
\end{proof}

\begin{theorem}[GaloisGroupUp composition classifier congruence]
\label{thm:galoisgroup-composition-classifier-congruence}
Let $x,x',y,y'$ be accepted fixed-base automorphism-action rows in an
automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. Suppose $x$ is
classified with $x'$, $y$ is classified with $y'$, the target endpoint of $x$
is classified with the source endpoint of $y$, and the target endpoint of
$x'$ is classified with the source endpoint of $y'$. Then the composite of
$x$ with $y$ is classified with the composite of $x'$ with $y'$. The
classification uses only inherited GaloisExtUp classifier transport,
$\GroupUp$ operation congruence, $\hsame$, $\Cont$, and $\mathsf{Pkg}$
provenance from the packet.
\end{theorem}
\begin{proof}
First transport the extension faces. The GaloisExtUp classifier of $E$
transports source, middle, and target endpoints across the displayed
$\hsame$ rows, and the $\Cont$ rows in $\lambda$ record the two compatible
composition ledgers.

Next transport the fixed-base faces. Since $x$ is classified with $x'$ and
$y$ is classified with $y'$, their fixed-base witnesses compare by the
classifier row $c$. The middle endpoint comparisons align the two ways of
reading the shared extension endpoint, so the composed fixed-base witness is
again compared by $\hsame$.

Apply the $\GroupUp$ operation congruence from $G$ to the operation endpoints
underlying the two composites. The $\mathsf{Pkg}$ row $\rho$ identifies these
operation endpoints as dependency rows from $G$, while the acted-on extension
endpoints remain dependency rows from $E$.

Repack the transported source, middle, target, fixed-base, operation, and
ledger rows as the composed classifier row. This gives classifier-equivalent
composites without introducing any host automorphism equality.
\end{proof}

\begin{theorem}[GaloisGroupUp automorphism ledger exactness]
\label{thm:galoisgroup-automorphism-ledger-exactness}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the public ledger
$\lambda$ hides exactly the dependency rows, fixed-base rows, identity rows,
action rows, composition rows, inverse rows, classifier rows, provenance rows,
and exactness rows exposed by the $\GaloisGroupUp$ automorphism surface. Every
public consumer of the packet factors through those rows and does not require
host automorphism equality, equality of ambient function spaces, or equality of
uncarried quotient representatives.
\end{theorem}
\begin{proof}
Project the packet coordinates. The rows $E$ and $G$ give the dependency
surfaces, $b$ gives the fixed-base surface, the unit endpoint of $G$ with the
identity classifier of $E$ gives the identity surface, $m$ gives composition,
$i$ gives inverse, $c$ gives classifier comparison, and $\rho$ gives
provenance. The exactness rows are precisely the exactness rows already named
by the dependency packets and the automorphism-action surface.

These projected rows account for every public operation used by a
$\NameCert_{\GaloisGroupUp}$ consumer. Carrier acceptance uses the dependency
and fixed-base rows; identity uses the unit and identity-classifier rows;
composition and inverse use $m$ and $i$; classifier transport uses $c$ together
with $\hsame$ and $\Cont$; provenance uses $\rho$.

Conversely, start from exactly those finite rows and their $\mathsf{Pkg}$
assignments. Repacking them as $E$, $G$, $b$, $a$, $m$, $i$, $c$, $\rho$, and
$\lambda$ reconstructs the public automorphism-action packet. Since no
coordinate contains host automorphism equality, no consumer can depend on such
an equality through the public ledger.
\end{proof}

\begin{theorem}[GaloisGroupUp identity automorphism row]
\label{thm:galoisgroup-identity-automorphism-row}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the unit row of
the $\NameCert_{\GroupUp}$ surface of $G$, together with the classifier and
endpoint rows of the $\NameCert_{\GaloisExtUp}$ surface of $E$, determines an
accepted fixed-base identity automorphism row on every displayed extension
endpoint. The row is a finite $\mathsf{BHist}$ row whose action ledger is a
$\mathsf{Cont}$ identity readback, whose fixed-base witness is repacked through
$\hsame$, and whose $\mathsf{Pkg}$ provenance remains the pair of dependency
packets $E$ and $G$.
\end{theorem}
\begin{proof}
Project the packet to its Galois-extension row $E$ and group row $G$. The
$\NameCert_{\GroupUp}$ dependency supplies the unit endpoint and the group unit
surface, while $\NameCert_{\GaloisExtUp}$ supplies the displayed extension
endpoints, classifier rows, exactness rows, and finite endpoint ledger.

Choose one displayed extension endpoint of $E$. The identity action keeps that
source and target endpoint in the same $\hsame$ class, so its action face is a
finite $\mathsf{BHist}$ row read by the singleton $\mathsf{Cont}$ ledger for the
endpoint. The fixed-base face is the same base endpoint comparison already
recorded by the GaloisExtUp classifier.

Repack the unit endpoint from $G$, the identity action row over $E$, the
fixed-base $\hsame$ witness, the classifier row $c$, the provenance row
$\rho$, and the ledger $\lambda$. This is exactly one accepted fixed-base
automorphism-action row of the packet, with no ambient automorphism equality
added.
\end{proof}

\begin{theorem}[GaloisGroupUp composition associativity ledger]
\label{thm:galoisgroup-composition-associativity-ledger}
Let $x$, $y$, and $z$ be accepted fixed-base automorphism-action rows of
\autoref{def:galoisgroup-bhist-automorphism-action-packet} whose displayed
source and target endpoints are composable by $\hsame$ comparisons in the
$\NameCert_{\GaloisExtUp}$ packet $E$. The two parenthesized finite
$\mathsf{Cont}$ composition ledgers, first composing $x$ with $y$ and then with
$z$, or first composing $y$ with $z$ and then with $x$, classify the same final
extension endpoint. The comparison is the inherited associativity row of
$\NameCert_{\GroupUp}$ transported through the GaloisExtUp endpoint classifier,
with the same $\mathsf{BHist}$ rows and $\mathsf{Pkg}$ provenance.
\end{theorem}
\begin{proof}
Read $x$, $y$, and $z$ through the common packet. Each row exposes a
$\mathsf{BHist}$ source endpoint, target endpoint, fixed-base witness, action
ledger, classifier row, and $\mathsf{Pkg}$ provenance, while the composability
assumptions give the two middle $\hsame$ transports inside $E$.

Form the two finite $\mathsf{Cont}$ ledgers. On the group side, the
$\NameCert_{\GroupUp}$ associativity row identifies the two parenthesized
operation rows. On the extension side, the $\NameCert_{\GaloisExtUp}$
classifier transports the intermediate endpoints so both ledgers have the same
source endpoint from $x$ and the same target endpoint from $z$.

The fixed-base witnesses compose along the same endpoint transports, so both
parenthesized rows keep every displayed base endpoint in its original
$\hsame$ class. Repacking the common endpoints, the reassociated ledger, the
classifier row, and the unchanged provenance row $\rho$ gives a single
GaloisGroupUp classifier comparison between the two ledgers.
\end{proof}

\begin{theorem}[GaloisGroupUp unit action laws]
\label{thm:galoisgroup-unit-action-laws}
For every accepted fixed-base automorphism-action row $x$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, composing $x$ on
the left or on the right with the identity row of
\autoref{thm:galoisgroup-identity-automorphism-row} classifies back to $x$.
Both unit compositions are finite $\mathsf{BHist}$ rows: their
$\mathsf{Cont}$ ledgers use the left and right unit rows of
$\NameCert_{\GroupUp}$, their endpoint transports use the
$\NameCert_{\GaloisExtUp}$ classifier, their fixed-base witnesses are carried
by $\hsame$, and their $\mathsf{Pkg}$ provenance is unchanged.
\end{theorem}
\begin{proof}
Start with the accepted row $x$ and project its dependency data. The identity
row supplied by \autoref{thm:galoisgroup-identity-automorphism-row} has the
same displayed endpoint system from $E$ and the unit endpoint from $G$, so it
can be composed with $x$ on either side whenever the finite endpoint ledgers
match by $\hsame$.

For the left composition, use the left unit law in the
$\NameCert_{\GroupUp}$ surface and transport the acted-on endpoint through the
$\NameCert_{\GaloisExtUp}$ classifier. For the right composition, use the right
unit law and the same endpoint classifier. In both cases the resulting
$\mathsf{Cont}$ ledger is classified with the original action ledger of $x$.

It remains to check the fixed-base face. The fixed-base carrier obligation of
\autoref{thm:galoisgroup-fixed-base-carrier-obligation} says this face is only
the displayed base endpoint plus its $\hsame$ comparison, and the identity row
preserves that comparison. Repacking the original row $x$, the unit law
transport, and the same $\mathsf{Pkg}$ provenance gives the two stated unit
classifications.
\end{proof}

\begin{theorem}[GaloisGroupUp composition and inverse obligation]
\label{thm:galoisgroup-composition-and-inverse-obligation}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the composition
row $m$ and inverse row $i$ remain in the same Galois-group classifier exactly
when their displayed endpoints are transported by finite $\mathsf{Cont}$ rows,
$\hsame$ comparisons, and $\mathsf{Pkg}$ provenance from the Galois-extension
packet $E$ and the group-operation packet $G$.
\end{theorem}
\begin{proof}
First isolate the composition row. The operation endpoint in $m$ is the
$\GroupUp$ multiplication row, while the acted-on endpoints are extension
histories from $E$. Group congruence transports the multiplication endpoint,
and the Galois-extension classifier transports the acted-on endpoints. The
ledger $\lambda$ records both transports as finite $\mathsf{Cont}$ rows.

Next isolate the inverse row. The inverse endpoint in $i$ is the $\GroupUp$
inverse row, and the inverse action endpoints are again displayed extension
histories from $E$. The inverse congruence and inverse laws from the group
surface keep the operation in the same classifier, while the fixed-base row
$b$ keeps the base endpoints in their original $\hsame$ classes.

Combining the two rows gives the stated equivalence. If composition and
inverse endpoints are transported by $\mathsf{Cont}$, $\hsame$, and
$\mathsf{Pkg}$, then $m$ and $i$ repack into the classifier row $c$.
Conversely, projecting $c$ exposes precisely those finite transports and no
additional ambient automorphism equality.
\end{proof}

\begin{theorem}[GaloisGroupUp identity action row]
\label{thm:galoisgroup-identity-action-row}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the unit row of the
group packet $G$ gives a displayed identity automorphism-action row on every
extension endpoint carried by $E$. This row fixes every displayed base-field
endpoint by $\hsame$ and is accepted by the same finite
$\GaloisGroupUp$ automorphism-action packet using only $\mathsf{BHist}$,
$\mathsf{Cont}$, $\mathsf{Pkg}$, and the inherited
$\GaloisExtUp$ classifier.
\end{theorem}
\begin{proof}
Unpack the automorphism-action packet. By
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the only available
dependency data are the Galois-extension packet $E$, the group packet $G$, the
fixed-base row $b$, the action row $a$, the composition row $m$, the inverse row
$i$, the classifier row $c$, the package row $\rho$, and the finite ledger
$\lambda$.

The public Galois-extension boundary of
\autoref{thm:galoisext-public-obligation-boundary} supplies the extension
endpoints and their classifier rows. The fixed-base carrier obligation of
\autoref{thm:galoisgroup-fixed-base-carrier-obligation} supplies the
$\hsame$ base-field comparison for a displayed automorphism row over those
endpoints.

Read the unit endpoint from the $\GroupUp$ dependency packet $G$. Its displayed
unit ledger acts as the identity action on each extension endpoint, and the
fixed-base row transports the base endpoint back to its original $\hsame$ class.
The composition and inverse controls of
\autoref{thm:galoisgroup-composition-closure},
\autoref{thm:galoisgroup-inverse-closure}, and
\autoref{thm:galoisgroup-composition-and-inverse-obligation} ensure that this
unit row lies in the same accepted automorphism-action classifier as the rows
already carried by the packet.

Repack the dependency projections, unit action ledger, fixed-base witness,
classifier row, $\mathsf{Cont}$ readbacks, and shared $\mathsf{Pkg}$
provenance. The result is a finite accepted row of the original packet, so the
identity action is public without exporting a host automorphism function.
\end{proof}

\begin{theorem}[GaloisGroupUp associative composition row]
\label{thm:galoisgroup-associative-composition-row}
For three composable accepted automorphism-action rows in an
automorphism-action packet of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the left-associated
and right-associated composite ledgers are classified by the same
$\GaloisGroupUp$ row. The comparison is obtained from the $\GroupUp$
associativity row together with the middle-endpoint $\hsame$ transports exposed
by the $\GaloisExtUp$ surface.
\end{theorem}
\begin{proof}
Unpack the three accepted action rows through
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. Each row has
extension endpoints from $E$, group-operation endpoints from $G$, fixed-base
witnesses, classifier entries, $\mathsf{Cont}$ ledger entries, and the shared
$\mathsf{Pkg}$ provenance row.

The endpoint alignments come from the Galois-extension public boundary
\autoref{thm:galoisext-public-obligation-boundary}. Those classifier rows
transport the first middle endpoint to the second source endpoint and the second
middle endpoint to the third source endpoint inside the finite ledger
$\lambda$.

Apply the composition closure of
\autoref{thm:galoisgroup-composition-closure} twice, once to form the
left-associated ledger and once to form the right-associated ledger. The group
packet $G$ contributes the $\GroupUp$ associativity row, and
\autoref{thm:galoisgroup-composition-and-inverse-obligation} identifies the two
composition ledgers through the same finite $\mathsf{Cont}$ and $\hsame$
transports.

The inverse closure of \autoref{thm:galoisgroup-inverse-closure} supplies the
same accepted classifier controls for the operation endpoints that appear in
the association comparison. Repack the two associated ledgers, their fixed-base
witnesses, the dependency projections, and the shared package row. The repacked
classifier proves that associativity is an action-ledger row of the original
finite packet.
\end{proof}

\begin{theorem}[GaloisGroupUp action ledger exactness]
\label{thm:galoisgroup-action-ledger-exactness}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the public action
ledger is exactly the fixed-base row, identity row, composition row, inverse
row, classifier row, dependency projections to $E$ and $G$, finite
$\mathsf{Cont}$ readbacks, and shared $\mathsf{Pkg}$ provenance. No host
automorphism function space, quotient of automorphisms, or uncarried equality
of field presentations is exported.
\end{theorem}
\begin{proof}
Project the packet along
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. The projection
exposes only $E$, $G$, $b$, $a$, $m$, $i$, $c$, $\rho$, and $\lambda$ together
with the dependency rows recorded inside the two consumed NameCert packets.

The Galois-extension public boundary
\autoref{thm:galoisext-public-obligation-boundary} accounts for all extension
carrier, classifier, exactness, and ledger rows from $E$. The fixed-base carrier
obligation \autoref{thm:galoisgroup-fixed-base-carrier-obligation} accounts for
the base-fixing face of the action ledger.

The identity row is the unit action row supplied above. The composition and
inverse faces are exactly the rows controlled by
\autoref{thm:galoisgroup-composition-closure},
\autoref{thm:galoisgroup-inverse-closure}, and
\autoref{thm:galoisgroup-composition-and-inverse-obligation}. These references
exhaust the accepted action, association, and reversal data available in the
finite packet.

Conversely, every listed row is a displayed packet row or a dependency
projection already carried by $\lambda$ and tagged by $\rho$. Repacking those
rows gives the same public $\GaloisGroupUp$ automorphism-action packet, so the
ledger is exact and has no additional ambient automorphism object behind it.
\end{proof}

\begin{theorem}[GaloisGroupUp public NameCert obligation boundary]
\label{thm:galoisgroup-public-namecert-obligation-boundary}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the public
$\NameCert_{\GaloisGroupUp}$ obligation surface is exactly the following
finite row family: the Galois-extension dependency packet $E$, the group
dependency packet $G$, the fixed-base row $b$, the automorphism-action row
$a$, the identity row read from the unit of $G$, the composition row $m$, the
inverse row $i$, the classifier row $c$, the $\mathsf{Pkg}$ provenance row
$\rho$, the finite $\mathsf{Cont}$ ledger $\lambda$, and the exactness rows
named by those packets. This is the public
obligation boundary consumed by downstream Galois and representation-facing
chapters.
\end{theorem}
\leanchecked{BEDC.Derived.GaloisGroupUp.GaloisGroupAutomorphismActionPacket\_semantic\_name\_certificate}
\begin{proof}
Project the packet to its dependency surfaces. The Galois-extension side is
the public boundary of
\autoref{thm:galoisext-public-obligation-boundary}; the group side is the
operation and inverse surface named by the $\GroupUp$ certificate. These two
dependency projections account for the extension carrier, group operation,
classifier, stability, ledger, and exactness rows available to the
Galois-group packet.

The fixed-base carrier obligation is supplied by
\autoref{thm:galoisgroup-fixed-base-carrier-obligation}. The identity row is
supplied by \autoref{thm:galoisgroup-identity-row-closure}; classifier-stable
composition is supplied by
\autoref{thm:galoisgroup-composition-classifier-congruence}; and the
composition and inverse obligation is supplied by
\autoref{thm:galoisgroup-composition-and-inverse-obligation}. Therefore every
public row is a projection of $E$, $G$, $b$, $a$, the identity row, $m$, $i$,
$c$, $\rho$, or $\lambda$.

Conversely, each listed row is either a coordinate of
\autoref{def:galoisgroup-bhist-automorphism-action-packet} or a projected row
read from those coordinates. Repacking those rows gives the carrier, identity,
operation, inverse, classifier, provenance, ledger, and exactness surface needed
by downstream Galois and representation-facing uses, so no hidden host
automorphism datum is part of the public boundary.
\end{proof}
