\chapter{A Concrete Naming Certificate for $\SqueezeRealUp$}
\label{ch:concrete-instances-squeezereal-namecert}
\origin{human}

The $\SqueezeRealUp$ interface names the finite dyadic sandwich packet used when a constructive squeeze argument is consumed by $\RealUp$ and completion-facing certificates. The mathematical squeeze theorem is usually stated as a convergence principle for a middle sequence bounded between two convergent endpoints; BEDC records only the visible finite certificate: lower and upper $\RegularCauchyNameUp$ rows, a middle $\RegularCauchyNameUp$ row, a shared $\DyadicTailBoundUp$ tolerance row, sandwich ledgers, a $\RealUp$ seal row, package provenance, and a local $\NameCert$ row.

The packet is not a quotient of streams, not an ambient equality of host reals, and not a choice-selected limit. It is a finite ledger surface over $\DyadicTailBoundUp$, $\RegularCauchyNameUp$, $\RegSeqRatUp$, $\RealUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

\begin{definition}[SqueezeReal finite sandwich carrier]
\label{def:squeeze-real-carrier}
A $\SqueezeRealUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
Q=(l,x,u,\epsilon,L,U,S,E,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $l$ is the lower $\RegularCauchyNameUp$ row, read through its $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\StreamNameUp$ observation surface;
\item $x$ is the middle $\RegularCauchyNameUp$ row whose real-facing seal is to be exposed only through the sandwich packet;
\item $u$ is the upper $\RegularCauchyNameUp$ row, read through the same kind of regular rational observation surface as $l$;
\item $\epsilon$ is the shared $\DyadicTailBoundUp$ tolerance row consumed by all three regular names;
\item $L$ is the lower sandwich ledger certifying the displayed finite comparisons $l \le x$ at every requested dyadic window;
\item $U$ is the upper sandwich ledger certifying the displayed finite comparisons $x \le u$ and the width bound $u-l \le \epsilon$ at the same requested dyadic windows;
\item $S$ is the shared $\RealUp$ seal row, exposed only after the lower and upper ledgers have consumed the shared tolerance row;
\item $E$ stores componentwise $\hsame$ transports for the three regular-name rows, the tolerance row, both sandwich ledgers, the seal row, provenance, and the local naming row;
\item $P$ is the $\Pkg$ provenance naming the consumed $\DyadicTailBoundUp$, $\RegularCauchyNameUp$, $\RegSeqRatUp$, $\RealUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\mathsf{BHist}$, $\hsame$, and $\Cont$ rows;
\item $N$ is the local $\NameCert_{\SqueezeRealUp}$ row.
\end{enumerate}
The carrier has no coordinate for a completed host real, quotient stream equality, a selected limiting value, or an external completeness theorem.
\end{definition}
\leanchecked{BEDC.Derived.SqueezeRealUp.SqueezeRealTasteGate\_single\_carrier\_alignment}

\begin{definition}[SqueezeReal packet classifier]
\label{def:squeeze-real-classifier}
Two accepted $\SqueezeRealUp$ carriers are classified as the same finite sandwich packet exactly when their displayed rows compare componentwise. The lower, middle, and upper $\RegularCauchyNameUp$ rows agree through their scheduled $\RegSeqRatUp$ and $\StreamNameUp$ observations, the shared $\DyadicTailBoundUp$ rows agree as the same tolerance request, the lower and upper sandwich ledgers transport through the displayed $\hsame$ rows, and the $\RealUp$ seal, $\Pkg$ provenance, and local $\NameCert$ rows name the same packet.

The classifier has no generator for quotienting regular names, identifying host reals, selecting a limit, or replacing the two sandwich ledgers by a single ambient order proof.
\end{definition}

\begin{theorem}[SqueezeReal NameCert obligations]
\label{thm:squeeze-real-namecert-obligations}
The carrier of \autoref{def:squeeze-real-carrier} satisfies the local $\NameCert_{\SqueezeRealUp}$ obligation surface. Its five obligation rows are:
\begin{enumerate}
\item carrier habitation by any displayed triple of regular dyadic rows whose lower and upper ledgers use the same tolerance request;
\item classifier transport by the componentwise classifier of \autoref{def:squeeze-real-classifier};
\item lower and upper sandwich ledger stability under the displayed $\hsame$ and $\Cont$ routes;
\item dyadic tail exhaustion, saying that every precision read factors through the shared $\DyadicTailBoundUp$ row before any seal read;
\item $\RealUp$ seal boundary, saying that the public real-facing read exposes only the middle regular name after both sandwich ledgers have been consumed.
\end{enumerate}
\end{theorem}
\begin{proof}
For habitation, take the displayed regular-name rows $l$, $x$, and $u$ together with a single tolerance row $\epsilon$. The packet is accepted only when $L$ and $U$ name the finite comparisons over that same tolerance request, so the carrier is a concrete $\mathsf{BHist}$ tuple.

For classifier transport, use \autoref{def:squeeze-real-classifier}. Each regular-name row is transported through its scheduled rational observations, the tolerance row is transported as a shared request, and both sandwich ledgers are repacked with the transported provenance.

For ledger stability and tail exhaustion, inspect any consumer read. A lower or upper comparison read must project $L$ or $U$, and both ledgers cite $\epsilon$ before exposing a dyadic endpoint comparison. Thus the two bounding rows cannot be separated from the shared dyadic tail request.

For the seal boundary, project $S$ only after the previous rows have been read. Since no coordinate of $Q$ is a quotient stream, host real equality, selected limit, or completeness datum, the local $\NameCert_{\SqueezeRealUp}$ surface is exactly the displayed finite sandwich packet.
\end{proof}

\begin{theorem}[SqueezeReal sandwich exactness]
\label{thm:squeeze-real-sandwich-exactness}
Every accepted $\SqueezeRealUp$ packet consumes the same $\DyadicTailBoundUp$ tolerance row and both bounding ledgers before exposing the $\RealUp$ seal. Concretely, a read of $S$ must factor through the rows $\epsilon$, $L$, and $U$, where $L$ certifies the lower comparisons $l \le x$ and $U$ certifies both the upper comparisons $x \le u$ and the finite width bounds $u-l \le \epsilon$ for the scheduled dyadic windows.

Consequently a $\RealUp$ or completion-facing consumer receives a finite sandwich certificate for the middle regular name, not a host-real equality proof and not a selected limiting object.
\end{theorem}
\leanchecked{BEDC.Derived.SqueezeRealUp.SqueezeRealCarrier\_sandwich\_exactness}
\begin{proof}
Start with an accepted packet $Q=(l,x,u,\epsilon,L,U,S,E,P,N)$. By \autoref{def:squeeze-real-carrier}, the only tolerance coordinate in the carrier is $\epsilon$, and both ledgers are declared over the same requested dyadic windows.

Read the lower ledger $L$. It supplies exactly the finite comparisons from the lower regular row to the middle regular row at the scheduled windows; no seal row is projected by this read.

Read the upper ledger $U$. It supplies the finite comparisons from the middle regular row to the upper regular row and the displayed width bounds against the same tolerance row $\epsilon$.

Only after these two reads may the consumer project $S$. Coordinate exhaustion shows that the exposed seal is the shared $\RealUp$ row named by the packet, and the consumer has not acquired quotient stream equality, host real equality, a selected limit, or a separate completeness principle.
\end{proof}

\begin{theorem}[SqueezeReal RealUp boundary]
\label{thm:squeeze-real-realup-boundary}
When a $\RealUp$, $\RegSeqRatUp$, or completion consumer cites an accepted $\SqueezeRealUp$ packet, the citation can use only the lower regular-name row, middle regular-name row, upper regular-name row, shared dyadic tolerance row, lower sandwich ledger, upper sandwich-and-width ledger, displayed transports, package provenance, and local naming row of \autoref{def:squeeze-real-carrier}. The citation cannot infer a quotient of presentations, a host real equality, a selected limit, an ambient order-completeness theorem, or a standard bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.SqueezeRealUp.SqueezeRealCarrier\_realup\_boundary}
\begin{proof}
Factor the consumer citation through the local $\NameCert_{\SqueezeRealUp}$ surface of \autoref{thm:squeeze-real-namecert-obligations}. The visible packet supplies three regular-name rows, one shared tolerance row, two sandwich ledgers, transports, continuations, provenance, and the local naming row.

Apply the exactness statement of \autoref{thm:squeeze-real-sandwich-exactness}. Any real-facing read must consume the tolerance row and both bounding ledgers before the seal row is visible.

None of the displayed coordinates is a quotient stream, host real equality, selected limiting value, order-completeness theorem, or standard bridge. The real-facing boundary is therefore the finite dyadic sandwich surface and nothing stronger.
\end{proof}

\begin{theorem}[SqueezeReal transport stability]
\label{thm:squeeze-real-transport-stability}
Let $Q=(l,x,u,\epsilon,L,U,S,E,P,N)$ be an accepted $\SqueezeRealUp$ packet. Componentwise $\hsame$ transport of the lower, middle, and upper $\RegularCauchyNameUp$ rows, the shared $\DyadicTailBoundUp$ row, both sandwich ledgers, the $\RealUp$ seal row, the $\Pkg$ provenance row, and the local $\NameCert_{\SqueezeRealUp}$ row preserves the carrier of \autoref{def:squeeze-real-carrier} and the classifier of \autoref{def:squeeze-real-classifier}. The transported packet is still classified only by the displayed regular-name observations, the single tolerance request, the two transported ledgers, the seal row, provenance, and local naming data.
\end{theorem}
\leanchecked{BEDC.Derived.SqueezeRealUp.SqueezeRealCarrier\_transport\_stability}
\begin{proof}
Project the carrier coordinates from \autoref{def:squeeze-real-carrier}. Each transported row named in the statement is already a visible coordinate of $Q$, and the transport ledger $E$ records the componentwise $\hsame$ routes for exactly those coordinates.

The carrier is preserved by repacking the transported lower, middle, and upper regular-name rows with the transported tolerance row, the transported lower and upper ledgers, the transported seal, provenance, and local naming row. No additional coordinate is available in the displayed $\mathsf{BHist}$ packet.

The classifier is preserved by \autoref{def:squeeze-real-classifier}. Classification compares the same rows componentwise after transport: scheduled regular-name observations, the shared tolerance request, both sandwich ledgers, the $\RealUp$ seal, the $\Pkg$ row, and the local $\NameCert$ row.
\end{proof}

\begin{theorem}[SqueezeReal dyadic tail exhaustion]
\label{thm:squeeze-real-dyadic-tail-exhaustion}
Every precision read of the real-facing seal in an accepted $\SqueezeRealUp$ packet factors first through the shared $\DyadicTailBoundUp$ tolerance row and then through both sandwich ledgers before any $\RealUp$ seal read. Thus a consumer can reach $S$ only by the finite route $\epsilon,L,U,S$ inside the displayed $\mathsf{BHist}$ packet.
\end{theorem}
\begin{proof}
Begin with a precision request addressed to the real-facing row. The carrier of \autoref{def:squeeze-real-carrier} stores only one dyadic tolerance coordinate, namely $\epsilon$, so every such request has a unique tolerance row to consume.

Next read the sandwich ledgers. The lower ledger $L$ records the finite lower comparisons against the middle regular name, and the upper ledger $U$ records the finite upper comparisons and width bounds against the same tolerance request. These two ledger reads account for the sandwich data available to the request.

Only after those rows have been consumed can the seal coordinate $S$ be projected. This is exactly the route isolated in \autoref{thm:squeeze-real-sandwich-exactness}, so the precision read has no remaining access to quotient regular names, host equality, selected limits, or ambient completeness.
\end{proof}

\begin{theorem}[SqueezeReal shared tail ledger determinacy]
\label{thm:squeeze-real-shared-tail-ledger-determinacy}
Let $Q=(l,x,u,\epsilon,L,U,S,E,P,N)$ be an accepted $\SqueezeRealUp$ packet. If two precision reads use the same lower, middle, and upper $\RegularCauchyNameUp$ rows $l$, $x$, and $u$, and the same shared $\DyadicTailBoundUp$ tolerance row $\epsilon$, then their lower ledger, upper ledger, width-bound surface, and $\RealUp$ seal-facing route agree at the classifier-facing packet level. The agreement is only the finite packet agreement of \autoref{def:squeeze-real-classifier}; it does not identify host real values, quotient regular names, selected limits, or an ambient completeness proof.
\end{theorem}
\leanchecked{BEDC.Derived.SqueezeRealUp.SqueezeRealCarrier\_shared\_tail\_ledger\_determinacy}
\begin{proof}
Project the accepted carrier of \autoref{def:squeeze-real-carrier}. The rows $l$, $x$, $u$, and $\epsilon$ are the only inputs from which a precision read can obtain the three regular-name surfaces and the shared dyadic tail request.

Apply the sandwich exactness and dyadic-tail exhaustion rows, \autoref{thm:squeeze-real-sandwich-exactness} and \autoref{thm:squeeze-real-dyadic-tail-exhaustion}. They force each read to consume the same tolerance row before reading $L$, $U$, the width-bound data inside $U$, and then the seal-facing route $S$.

If a read is carried through displayed transport before comparison, use \autoref{thm:squeeze-real-transport-stability}. The transported packet preserves the lower, middle, upper, tolerance, ledger, seal, package, and local naming rows that the classifier can inspect.

The classifier of \autoref{def:squeeze-real-classifier} now compares the same visible rows componentwise. By the real-facing boundary of \autoref{thm:squeeze-real-realup-boundary}, there is no additional coordinate from which the two reads could obtain a different host equality, quotient representative, selected limit, or order-completeness route.
\end{proof}

\begin{theorem}[SqueezeReal completion consumer package]
\label{thm:squeeze-real-completion-consumer-package}
The carrier and classifier of \autoref{def:squeeze-real-carrier} and \autoref{def:squeeze-real-classifier}, together with the $\NameCert_{\SqueezeRealUp}$ obligations of \autoref{thm:squeeze-real-namecert-obligations}, sandwich exactness of \autoref{thm:squeeze-real-sandwich-exactness}, real-facing boundary of \autoref{thm:squeeze-real-realup-boundary}, transport stability of \autoref{thm:squeeze-real-transport-stability}, dyadic-tail exhaustion of \autoref{thm:squeeze-real-dyadic-tail-exhaustion}, and shared tail ledger determinacy of \autoref{thm:squeeze-real-shared-tail-ledger-determinacy}, form the finite completion-facing packet consumed by $\RegSeqRatUp$, $\RealUp$, and completion certificates. The packet excludes quotient regular names, host equality, selected limits, and ambient order completeness.
\end{theorem}
\begin{proof}
Assemble the carrier and classifier rows first. They identify the finite $\mathsf{BHist}$ tuple and the componentwise equality route over the three regular-name rows, the shared tolerance request, both ledgers, the seal, provenance, and local naming data.

Add the naming-certificate obligations and sandwich exactness. These rows show that carrier habitation, classifier transport, ledger stability, tail exhaustion, and seal boundary are all witnessed inside the displayed packet, and that the seal can be read only through $\epsilon$, $L$, and $U$.

Finally add transport stability, dyadic-tail exhaustion, and shared tail ledger determinacy. The resulting package is stable under the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and supplies exactly the finite consumer surface needed by $\RegSeqRatUp$, $\RealUp$, and completion certificates. Since all rows have been exhausted, no quotient regular name, host equality, selected limit, or ambient order-completeness coordinate is present.
\end{proof}

\begin{theorem}[SqueezeReal scoped dependency packet]
\label{thm:squeeze-real-scoped-dependency-packet}
For an accepted $\SqueezeRealUp$ packet $Q=(l,x,u,\epsilon,L,U,S,E,P,N)$, the carrier row, classifier row, sandwich exactness row, transport-stability row, and dyadic-tail exhaustion row factor through exactly the displayed dependencies
$$
\DyadicTailBoundUp,\quad \RegularCauchyNameUp,\quad \RegSeqRatUp,\quad \RealUp,\quad \mathsf{BHist},\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert .
$$
The packet has no further dependency coordinate for quotient regular-name equality, host real equality, selected limits, or ambient order completeness.
\end{theorem}
\begin{proof}
Read the carrier and classifier of \autoref{def:squeeze-real-carrier} and \autoref{def:squeeze-real-classifier}. They expose only the three regular-name rows, the shared dyadic tail row, both sandwich ledgers, the real seal, transport data, continuation routes, package provenance, and local naming row.

The naming obligations of \autoref{thm:squeeze-real-namecert-obligations} identify those same rows as the local $\NameCert_{\SqueezeRealUp}$ surface. Sandwich exactness in \autoref{thm:squeeze-real-sandwich-exactness} and dyadic-tail exhaustion in \autoref{thm:squeeze-real-dyadic-tail-exhaustion} consume the shared tolerance row before any ledger or seal read is exported.

Transport stability in \autoref{thm:squeeze-real-transport-stability} preserves precisely the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates. The completion consumer package of \autoref{thm:squeeze-real-completion-consumer-package} then repacks the rows for $\RegSeqRatUp$ and $\RealUp$ without adding a coordinate outside the listed dependencies.
\end{proof}

\begin{theorem}[SqueezeReal shared-tail real-seal factorization]
\label{thm:squeeze-real-shared-tail-real-seal-factorization}
Every $\RealUp$ seal read exported by an accepted $\SqueezeRealUp$ packet factors through the shared $\DyadicTailBoundUp$ row together with both sandwich ledgers. In particular, the lower and upper ledger reads are forced to consume the same tail request before the seal row $S$ can be read by a $\RegSeqRatUp$, $\RealUp$, or completion-facing consumer.
\end{theorem}
\begin{proof}
Start from the real-facing boundary of \autoref{thm:squeeze-real-realup-boundary}. It states that a seal-facing consumer can see only the regular-name rows, the shared tolerance row, both ledger rows, the displayed transport and continuation data, provenance, and the local naming row.

Apply sandwich exactness from \autoref{thm:squeeze-real-sandwich-exactness}. The lower and upper ledger reads are tied to the same middle regular-name row and to the same width-bound route, so neither side can supply an independent seal coordinate.

Use dyadic-tail exhaustion from \autoref{thm:squeeze-real-dyadic-tail-exhaustion} and shared tail ledger determinacy from \autoref{thm:squeeze-real-shared-tail-ledger-determinacy}. These rows force every precision read to pass through $\epsilon$ before reading $L$, $U$, and $S$, and transport stability preserves that factorization under the displayed classifier route.
\end{proof}

\begin{theorem}[SqueezeReal completion handoff scope]
\label{thm:squeeze-real-completion-handoff-scope}
The scoped completion-facing handoff for $\SqueezeRealUp$ is exactly the packet assembled from the scoped dependency packet of \autoref{thm:squeeze-real-scoped-dependency-packet}, the shared-tail seal factorization of \autoref{thm:squeeze-real-shared-tail-real-seal-factorization}, and the completion consumer package of \autoref{thm:squeeze-real-completion-consumer-package}. It exports the finite dyadic sandwich handoff to $\RegSeqRatUp$, $\RealUp$, and completion certificates, while excluding quotient regular names, host real equality, selected limits, and ambient order completeness.
\end{theorem}
\begin{proof}
First assemble the dependency surface. The carrier, classifier, local naming obligations, transport stability, and dyadic-tail exhaustion rows give the finite $\mathsf{BHist}$ packet over $\DyadicTailBoundUp$, $\RegularCauchyNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next attach the seal factorization. The shared tolerance row and both sandwich ledgers determine every $\RealUp$ seal read, so the completion-facing consumer cannot replace the finite ledger by a host equality or a selected limit.

Finally use \autoref{thm:squeeze-real-completion-consumer-package}. It repacks the dependency and seal rows as the completion-facing handoff, and the boundary rows already rule out every coordinate not displayed in the accepted $\SqueezeRealUp$ carrier.
\end{proof}

\begin{theorem}[SqueezeReal scoped tail ledger package]
\label{thm:squeeze-real-scoped-tail-ledger-package}
The carrier and classifier of \autoref{def:squeeze-real-carrier} and \autoref{def:squeeze-real-classifier}, the sandwich exactness of \autoref{thm:squeeze-real-sandwich-exactness}, the dyadic-tail exhaustion of \autoref{thm:squeeze-real-dyadic-tail-exhaustion}, the shared-tail determinacy of \autoref{thm:squeeze-real-shared-tail-ledger-determinacy}, the completion consumer package of \autoref{thm:squeeze-real-completion-consumer-package}, the scoped dependency packet of \autoref{thm:squeeze-real-scoped-dependency-packet}, the shared-tail real-seal factorization of \autoref{thm:squeeze-real-shared-tail-real-seal-factorization}, and the completion handoff of \autoref{thm:squeeze-real-completion-handoff-scope} assemble one scoped finite ledger over
$$
\DyadicTailBoundUp,\quad \RegularCauchyNameUp,\quad \RegSeqRatUp,\quad \RealUp,\quad \mathsf{BHist},\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Every $\RegSeqRatUp$, $\RealUp$, or completion-facing read of the packet is exhausted by this ledger and cannot introduce quotient regular-name equality, host real equality, selected limits, or ambient order completeness.
\end{theorem}
\begin{proof}
First collect the local packet rows. The carrier and classifier identify the finite sandwich tuple, and sandwich exactness forces every seal-facing read through the shared tolerance row and the two displayed ledgers.

Next bind the tail ledger. Dyadic-tail exhaustion and shared-tail determinacy show that all precision reads use the same $\DyadicTailBoundUp$ request before consuming $L$, $U$, and $S$.

Finally assemble the completion-facing scope. The completion consumer package, scoped dependency packet, shared-tail real-seal factorization, and completion handoff repack the same rows over $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Since those rows are the entire displayed packet, no unlisted completion or host-real coordinate remains.
\end{proof}

\begin{theorem}[SqueezeReal public interval seal export]
\label{thm:squeeze-real-public-interval-seal-export}
An accepted $\SqueezeRealUp$ packet whose lower, middle, and upper rows satisfy the $\RegularCauchyNameUp$ carrier clauses, whose tolerance is the shared $\DyadicTailBoundUp$ row, and whose sandwich exactness, $\RealUp$ boundary, transport stability, and scoped tail ledger package are displayed, exports a public $\RealUp$ interval-seal certificate for the middle row. The certificate is the finite package over the lower and upper ledgers, the middle regular name, the shared tail request, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\SqueezeRealUp}$; it does not assert host real equality, select a limit, or appeal to ambient order completeness.
\end{theorem}
\begin{proof}
Start from the three $\RegularCauchyNameUp$ rows and the shared $\DyadicTailBoundUp$ request. Sandwich exactness ties the middle row to the lower and upper ledgers, while dyadic-tail exhaustion makes the shared request the common precision source for both sides.

Apply the $\RealUp$ boundary and transport stability rows. They keep the interval read on the displayed sandwich ledgers, componentwise $\hsame$ transports, continuation routes, package provenance, and local naming row.

Before exposing the public interval seal, read the finite sandwich carrier through \autoref{ch:concrete-instances-locatedinterval-namecert}: its endpoint-cell refinement and interval-containment route supply the located interval ledger consumed by the lower and upper rows.

The shared-tail real-seal factorization then places the middle seal after the shared tolerance and both ledger reads. Repack this route with the scoped tail ledger package to obtain the public interval-seal certificate for the middle row, with no host real equality or selected limit available as an additional coordinate.
\end{proof}

\closureat{SqueezeRealUp}{seedStr}
\closureat{SqueezeRealUp}{obligationStr}
\closureat{SqueezeRealUp}{scopedStr}
\closureat{SqueezeRealUp}{publicStr}

\begin{closurestatus}{\SqueezeRealUp}
  \constructivestory{A $\SqueezeRealUp$ packet is generated from lower, middle, and upper $\RegularCauchyNameUp$ rows, a shared $\DyadicTailBoundUp$ tolerance row, two finite sandwich ledgers, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, a $\RealUp$ seal row, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{def:squeeze-real-carrier}, \autoref{def:squeeze-real-classifier}, \autoref{thm:squeeze-real-namecert-obligations}, \autoref{thm:squeeze-real-sandwich-exactness}, \autoref{thm:squeeze-real-realup-boundary}, \autoref{thm:squeeze-real-transport-stability}, \autoref{thm:squeeze-real-dyadic-tail-exhaustion}, \autoref{thm:squeeze-real-shared-tail-ledger-determinacy}, \autoref{thm:squeeze-real-completion-consumer-package}, \autoref{thm:squeeze-real-scoped-dependency-packet}, \autoref{thm:squeeze-real-shared-tail-real-seal-factorization}, \autoref{thm:squeeze-real-completion-handoff-scope}, \autoref{thm:squeeze-real-scoped-tail-ledger-package}, and \autoref{thm:squeeze-real-public-interval-seal-export} bind the finite shared-tail ledger and export the public interval-seal certificate route.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.SqueezeRealUp.SqueezeRealCarrier\_sandwich\_exactness}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not claim quotient equality of regular names, host real equality, a selected limit, ambient order completeness, or a standard bridge.}
  \upgradepath{Bridge closure requires a standard-facing route for the public interval-seal certificate.}
\end{closurestatus}
