\chapter{A Concrete Naming Certificate for $\CauchyConvergenceModulusUp$}
\label{ch:concrete-instances-cauchy-convergence-modulus-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\CauchyConvergenceModulusUp$ packet records the finite convergence-modulus surface needed by the L10 Real and Completion route. It sits between the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the sequence-limit handoff of \autoref{ch:concrete-instances-real-sequence-limit-namecert}, and the regular-completion seed of \autoref{ch:concrete-instances-regular-cauchy-completion-universal-namecert}. The packet names a convergence schedule as certificate data before any completion-facing consumer may speak about a tail limit.

\begin{definition}[Cauchy convergence modulus carrier]
\label{def:cauchy-convergence-modulus-carrier}
A $\CauchyConvergenceModulusUp$ carrier is a finite $\BHist$ packet
$$
K=(S,D,T,W,Q,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the sequence-source row whose entries are read as the common source for the convergence claim.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger naming the requested dyadic radii.
\item $T$ is the tail-index schedule assigning each tolerance row in $D$ a finite threshold.
\item $W$ is the $\StreamNameUp$ finite tail-window family selected by $T$.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the displayed tail windows and dyadic tolerances.
\item $L$ is the $\RealSequenceLimitUp$ handoff row reached only after $S,D,T,W,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source, tolerance, tail schedule, windows, readback, limit handoff, continuation, provenance, and local naming rows.
\item $C$ records the displayed $\Cont$ replay from each tolerance request through $S,D,T,W,Q,L,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealSequenceLimitUp$, $\RegularCauchyCompletionUniversalUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyConvergenceModulusUp}$ row.
\end{enumerate}
The carrier has no coordinate for $\RealUp$ completeness, quotient limits, host sequence convergence, host real equality, countable choice, trichotomy, selected representatives, or an unbounded tail read.
\end{definition}

\begin{theorem}[Cauchy convergence modulus NameCert obligations]
\label{thm:cauchy-convergence-modulus-namecert-obligations}
The seed $\NameCert_{\CauchyConvergenceModulusUp}$ surface for \autoref{def:cauchy-convergence-modulus-carrier} consists exactly of carrier exposure for $K$, sequence-source exposure through $S$, dyadic tolerance exposure through $D$, tail-index exposure through $T$, finite StreamName window exposure through $W$, regular rational readback through $Q$, RealSequenceLimit handoff through $L$, componentwise transport through $H$, displayed continuation replay through $C$, package provenance through $P$, and local naming through $N$. Every accepted convergence request is classified only by the displayed tolerance row, the finite tail threshold, and the corresponding finite tail windows.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyConvergenceModulusUp.CauchyConvergenceModulusNamecertObligations}
\begin{proof}
Project the carrier tuple $K=(S,D,T,W,Q,L,H,C,P,N)$. Each analytic coordinate is a displayed finite row, and the final coordinate names the same tuple as the local $\NameCert_{\CauchyConvergenceModulusUp}$ surface.

Read the rows in the convergence order. A tolerance request first consumes the source row $S$ and dyadic ledger $D$, then the tail schedule $T$, then the finite tail windows $W$, and only then the regular readback $Q$ and sequence-limit handoff $L$.

The structural rows add no hidden convergence principle. They transport, replay, source, and name the displayed route, while the excluded objects have no coordinate in the carrier. Hence the listed rows exhaust the seed obligation surface.
\end{proof}

\begin{theorem}[Cauchy convergence modulus tail-window cofinality]
\label{thm:cauchy-convergence-modulus-tail-window-cofinality}
For every accepted $\CauchyConvergenceModulusUp$ packet $K=(S,D,T,W,Q,L,H,C,P,N)$ and every displayed dyadic tolerance request, the completion-facing read factors through the cofinal finite route
$$
S\longmapsto D\longmapsto T\longmapsto W\longmapsto Q\longmapsto L\longmapsto(H,C,P,N).
$$
Every later use by $\RegularCauchyCompletionUniversalUp$ must read the same displayed tail-index schedule and the same finite windows before it reaches the $\RealSequenceLimitUp$ handoff. The consumer receives no $\RealUp$ completeness theorem, quotient limit, host sequence convergence, host real equality, countable-choice row, trichotomy row, selected representative, or detached completion datum.
\end{theorem}
\begin{proof}
Start with \autoref{thm:cauchy-convergence-modulus-namecert-obligations}. It places the dyadic tolerance row $D$ before the tail-index schedule $T$ and places $T$ before the finite StreamName windows $W$.

The regular readback is then forced through the same finite tail window. The row $Q$ is read only after $S,D,T,W$ are displayed, so no quotient limit, host convergence predicate, or selected representative can substitute for the scheduled tail comparison.

Finally read the handoff coordinate. The row $L$ is reached after $Q$, and the rows $H,C,P,N$ only preserve and name that route. Thus every completion-facing consumer factors through the displayed cofinal tail-window route.
\end{proof}

\begin{theorem}[Cauchy convergence modulus tail-window exactness]
\label{thm:cauchy-convergence-modulus-tail-window-exactness}
For every accepted $\CauchyConvergenceModulusUp$ packet $K=(S,D,T,W,Q,L,H,C,P,N)$ and every displayed dyadic tolerance request in $D$, the request reaches exactly the tail schedule $T$ and the finite $\StreamNameUp$ windows $W$ before any $\RegSeqRatUp$ readback row $Q$ is inspected. No consumer may replace that schedule by an unbounded tail, a detached modulus, a host convergence predicate, a quotient limit, or a selected representative.
\end{theorem}
\begin{proof}
Project the carrier definition. The tolerance ledger $D$ is the only source of displayed precision requests, and the next analytic row in the packet is the tail-index schedule $T$.

Use the NameCert obligations and tail-window cofinality. They force each admitted request to pass from $D$ through $T$ and then through the finite window family $W$ before the regular rational readback $Q$ is available.

Apply the ledger refusal clause. Since the refused host, quotient, selected, and unbounded-tail objects have no carrier row or provenance edge, the displayed schedule and its finite windows are the exact pre-readback route.
\end{proof}

\begin{theorem}[Cauchy convergence modulus limit-readback exhaustion]
\label{thm:cauchy-convergence-modulus-limit-readback-exhaustion}
Every $\RealSequenceLimitUp$ or $\RegularCauchyCompletionUniversalUp$ consumer of an accepted $\CauchyConvergenceModulusUp$ packet receives only the rows
$$
S,D,T,W,Q,L,H,C,P,N.
$$
The consumer may read the source, tolerance ledger, tail schedule, finite windows, RegSeqRat readback, limit handoff, componentwise transport, displayed continuation replay, package provenance, and local NameCert row, but it receives no additional completion datum, host convergence predicate, quotient stream, selected representative, countable-choice selector, trichotomy row, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start from the carrier and NameCert obligation theorem. Together they expose exactly the ten displayed rows and make the limit handoff $L$ downstream of $S,D,T,W,Q$.

Tail-window cofinality and tail-window exactness identify the consumer route. A $\RealSequenceLimitUp$ or $\RegularCauchyCompletionUniversalUp$ read must pass through the same scheduled finite windows and the same regular readback before it can inspect $L$ or any structural row.

Finally use ledger refusal. The packet has no row for an independent completion object, host convergence, quotient streams, selected representatives, choice, trichotomy, or ambient completeness, so the listed rows exhaust the consumer-visible readback.
\end{proof}

\begin{theorem}[Cauchy convergence modulus carrier transport]
\label{thm:cauchy-convergence-modulus-carrier-transport}
Let $K=(S,D,T,W,Q,L,H,C,P,N)$ be an accepted $\CauchyConvergenceModulusUp$ packet, and let
$$
K'=(S',D',T',W',Q',L',H',C',P',N')
$$
be a second displayed ten-row packet. If the transport row supplies componentwise $\hsame$ comparisons from $S,D,T,W,Q,L,H,C,P,N$ to $S',D',T',W',Q',L',H',C',P',N'$ in the listed order, then $K'$ is accepted by the same $\NameCert_{\CauchyConvergenceModulusUp}$ surface. The transported packet exposes the same convergence-modulus route through sequence source, dyadic tolerance ledger, tail-index schedule, finite StreamName windows, RegSeqRat readback, RealSequenceLimit handoff, replay, provenance, and local name.
\end{theorem}
\begin{proof}
Project the accepted packet $K$ and read the carrier rows in the displayed order. The source, tolerance, schedule, window, readback, and handoff coordinates are finite rows, so componentwise $\hsame$ transport sends each exposed coordinate to the corresponding coordinate of $K'$.

Next read the structural rows. The transported row $H'$ records the same componentwise comparisons, $C'$ replays the displayed route, $P'$ keeps the same sibling provenance over \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-real-sequence-limit-namecert}, and \autoref{ch:concrete-instances-regular-cauchy-completion-universal-namecert}, and $N'$ names the transported tuple locally.

The NameCert surface therefore accepts $K'$ without opening any coordinate outside the ten displayed rows.
\end{proof}

\begin{theorem}[Cauchy convergence modulus classifier stability]
\label{thm:cauchy-convergence-modulus-classifier-stability}
Let $K=(S,D,T,W,Q,L,H,C,P,N)$ and $K'=(S',D',T',W',Q',L',H',C',P',N')$ be accepted $\CauchyConvergenceModulusUp$ packets. If the displayed source row, dyadic tolerance ledger, tail-index schedule, finite StreamName windows, RegSeqRat readback, and RealSequenceLimit handoff agree componentwise through the packet's $\hsame$ rows, then every completion-facing consumer sees the same finite convergence classifier from $K$ and $K'$. In particular, the consumer can distinguish packets only by the displayed route
$$
S,D,T,W,Q,L
$$
together with its transport, continuation replay, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Begin with the tail-window cofinality theorem. Any completion-facing read must pass through $S,D,T,W,Q,L$ before it reaches the structural rows, and the hypotheses identify those analytic rows componentwise.

Use carrier transport for the structural part. The rows $H,C,P,N$ and $H',C',P',N'$ preserve, replay, source, and name the same finite route, with the sibling anchors supplying only the displayed tolerance, window, readback, limit-handoff, and completion-facing surfaces.

Thus the classifier available to a completion consumer is determined by the shared finite rows. No ambient completion, quotient limit, host convergence predicate, or selected representative can refine the comparison.
\end{proof}

\begin{theorem}[Cauchy convergence modulus ledger refusal]
\label{thm:cauchy-convergence-modulus-ledger-refusal}
Every consumer of an accepted $\CauchyConvergenceModulusUp$ packet factors through the displayed rows $S,D,T,W,Q,L,H,C,P,N$. The packet refuses reads of $\RealUp$ completeness, quotient limits, host convergence, host real equality, countable choice, trichotomy, selected representatives, and any unbounded tail datum.
\end{theorem}
\begin{proof}
Read the carrier definition and the NameCert obligation theorem together. They expose exactly the ten displayed rows and classify tolerance requests by the sequence source, dyadic ledger, scheduled finite tail threshold, StreamName windows, RegSeqRat readback, and RealSequenceLimit handoff.

The cofinality theorem forces later completion-facing uses through the same finite route. Carrier transport and classifier stability show that replacing the packet by a componentwise transported packet does not create a new consumer-visible coordinate.

Therefore every permitted consumer read is already a read of $S,D,T,W,Q,L,H,C,P,N$. The listed host, choice, quotient, representative, and unbounded-tail objects have no carrier row, continuation replay, provenance edge, or local name in the packet.
\end{proof}

\begin{definition}[Cauchy convergence modulus Real-seal surface]
\label{def:cauchy-convergence-modulus-real-seal-surface}
For an accepted $\CauchyConvergenceModulusUp$ packet, the Real-seal surface is the displayed boundary
$$
(D,T,W,Q,L,E,H,C,P,N)
$$
where $D$ is the dyadic tolerance ledger, $T$ is the tail-index schedule, $W$ is the finite $\StreamNameUp$ tail-window family, $Q$ is the $\RegSeqRatUp$ readback row, $L$ is the $\RealSequenceLimitUp$ handoff, $E$ is the completion-facing seal read by $\RegularCauchyCompletionUniversalUp$, and $H,C,P,N$ carry transport, replay, provenance, and local naming. The surface is read only after the sequence source row of \autoref{def:cauchy-convergence-modulus-carrier} has exposed the same tolerance request.
\end{definition}

\begin{theorem}[Cauchy convergence modulus completion readiness]
\label{thm:cauchy-convergence-modulus-completion-readiness}
Every accepted $\CauchyConvergenceModulusUp$ packet exposes a completion-ready route from dyadic tolerance to regular Cauchy seal:
$$
D\longmapsto T\longmapsto W\longmapsto Q\longmapsto L\longmapsto E\longmapsto(H,C,P,N).
$$
The route is available to $\RealSequenceLimitUp$ and $\RegularCauchyCompletionUniversalUp$ consumers only through the displayed Real-seal surface of \autoref{def:cauchy-convergence-modulus-real-seal-surface}; it exports no host convergence predicate, quotient limit, selected representative, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with the carrier and NameCert obligation theorems. They place the dyadic tolerance row before the tail-index schedule and finite StreamName windows, then route the resulting readback through $\RegSeqRatUp$ and $\RealSequenceLimitUp$.

Apply tail-window cofinality. Any completion-facing consumer must replay the same finite windows before it can read the regular rational row $Q$ or the limit handoff $L$.

Finally use classifier stability and ledger refusal. Transport preserves the displayed route, and the refused host, quotient, choice, representative, and ambient-completion objects have no row in the Real-seal surface. The remaining visible boundary is exactly the completion-ready route displayed above.
\end{proof}

\begin{theorem}[Cauchy convergence modulus regular-Cauchy handoff]
\label{thm:cauchy-convergence-modulus-regular-cauchy-handoff}
Every $\RegularCauchyCompletionUniversalUp$ consumer of an accepted $\CauchyConvergenceModulusUp$ packet must read the Real-seal surface
$$
(D,T,W,Q,L,E,H,C,P,N)
$$
before it can treat the packet as a regular-Cauchy completion input. In particular, the consumer must pass through the dyadic tolerance ledger, the tail-index schedule, the finite StreamName windows, the RegSeqRat readback row, and the RealSequenceLimit handoff before it reaches the completion-facing seal $E$.
\end{theorem}
\begin{proof}
Use completion readiness to put every completion-facing read on the displayed route from $D$ through $E$. The route includes exactly the tolerance, schedule, window, readback, and handoff rows needed by the regular-Cauchy consumer.

The carrier-transport theorem keeps the route stable under componentwise $\hsame$ replacement. The classifier-stability theorem then shows that two packets with the same displayed rows present the same regular-Cauchy handoff to a completion consumer.

The ledger-refusal theorem excludes the alternate routes. A consumer cannot bypass $D,T,W,Q,L$ by appealing to host convergence, quotient limits, selected representatives, or ambient completeness, because those objects are absent from the packet.
\end{proof}

\begin{theorem}[Cauchy convergence modulus uniform threshold handoff]
\label{thm:cauchy-convergence-modulus-uniform-threshold-handoff}
Every $\RegularCauchyCompletionUniversalUp$ or $\RealSequenceLimitUp$ consumer of an accepted $\CauchyConvergenceModulusUp$ packet that receives a displayed tolerance request must use the same threshold row $T$ for all tail windows $W$ associated to that request before it can read the $\RegSeqRatUp$ row $Q$, the $\RealSequenceLimitUp$ handoff $L$, or the completion-facing seal $E$.

The handoff is the finite route
$$
D\longmapsto T\longmapsto W\longmapsto Q\longmapsto L\longmapsto E
$$
inside the carrier and Real-seal surface. It exports no quotient limit, selected representative, countable-choice selector, ambient $\RealUp$ completeness theorem, or detached completion datum.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-convergence-modulus-carrier}. The tolerance ledger $D$ is followed by the single displayed tail-index schedule $T$, and the finite window family $W$ is read only after that threshold row is exposed.

Apply tail-window cofinality. It forces every completion-facing use of the displayed tolerance request through the same scheduled tail windows before any regular rational readback is available.

Use completion readiness and the regular-Cauchy handoff for the downstream boundary. They place $Q$, then $L$, then the completion-facing seal $E$ after the same threshold and window rows.

The carrier and Real-seal surface contain no quotient limit, selected representative, countable-choice selector, ambient completeness theorem, or detached completion coordinate. Therefore the threshold handoff is uniform across all tail windows associated to the displayed request.
\end{proof}

\begin{theorem}[Cauchy convergence modulus uniform tail grid]
\label{thm:cauchy-convergence-modulus-uniform-tail-grid}
Let $K=(S,D,T,W,Q,L,H,C,P,N)$ be an accepted $\CauchyConvergenceModulusUp$ packet, and suppose a displayed dyadic grid refinement is attached to the tolerance row $D$, the tail schedule $T$, and the finite tail-window family $W$. Then every $\RealSequenceLimitUp$ and $\RegularCauchyCompletionUniversalUp$ consumer of $K$ must route the requested read through the same finite tail grid before reading the $\RegSeqRatUp$ row $Q$, the $\RealSequenceLimitUp$ handoff $L$, or the completion-facing seal $E$.

The finite grid route is
$$
D\longmapsto T\longmapsto W\longmapsto Q\longmapsto L\longmapsto E
$$
inside the carrier and Real-seal surface. It exports no quotient stream, selected representative, countable-choice schedule, ambient $\RealUp$ completeness row, detached completion datum, or alternate tail grid.
\end{theorem}
\begin{proof}
Project the carrier and apply the uniform threshold handoff. The tolerance row $D$ selects the tail schedule $T$, and the displayed grid refinement is read only through the finite tail-window family $W$ attached to that schedule.

Use tail-window cofinality and tail-schedule totality. They force each accepted Real-sequence or regular-completion request to pass through the same scheduled finite windows before any $\RegSeqRatUp$ readback can be inspected.

Completion readiness then places $Q$, $L$, and the completion-facing seal $E$ downstream of that grid. Scoped support and ledger refusal exclude quotient streams, selected representatives, countable-choice schedules, ambient completeness rows, and alternate tail grids, so the displayed finite route is the only consumer-visible path.
\end{proof}

\begin{theorem}[Cauchy convergence modulus Bishop criterion handoff]
\label{thm:cauchy-convergence-modulus-bishop-criterion-handoff}
Every $\BishopCompletionCriterionUp$ consumer of an accepted $\CauchyConvergenceModulusUp$ packet must read only the displayed route
$$
S\longmapsto D\longmapsto T\longmapsto W\longmapsto Q\longmapsto L\longmapsto H\longmapsto C\longmapsto P\longmapsto N.
$$
The handoff is anchored in the $\BHist$ carrier of \autoref{def:cauchy-convergence-modulus-carrier}, the $\StreamNameUp$ window row, the $\RegSeqRatUp$ readback row, the $\DyadicRatCoreUp$ tolerance ledger, the $\RealSequenceLimitUp$ handoff, and the $\RegularCauchyCompletionUniversalUp$ completion boundary. It uses the NameCert obligations of \autoref{thm:cauchy-convergence-modulus-namecert-obligations}, tail-window cofinality of \autoref{thm:cauchy-convergence-modulus-tail-window-cofinality}, completion readiness of \autoref{thm:cauchy-convergence-modulus-completion-readiness}, and regular-Cauchy handoff of \autoref{thm:cauchy-convergence-modulus-regular-cauchy-handoff}; it exposes no quotient stream, selected representative, host convergence predicate, countable-choice selector, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Project the accepted carrier. The displayed rows $S,D,T,W,Q,L,H,C,P,N$ are the only analytic and structural coordinates available to the completion criterion.

Use the NameCert obligations and tail-window cofinality. They place the dyadic tolerance ledger, tail-index schedule, finite windows, and regular readback before any sequence-limit or completion-facing consumer can read the packet.

Completion readiness and the regular-Cauchy handoff identify the boundary seen by $\BishopCompletionCriterionUp$. The consumer therefore receives exactly the displayed route, while the refused quotient, selected, host, choice, and ambient-completion objects remain outside the carrier.
\end{proof}

\begin{theorem}[Cauchy convergence modulus root-unblock tail route]
\label{thm:cauchy-convergence-modulus-root-unblock-tail-route}
For every accepted $\CauchyConvergenceModulusUp$ packet $K=(S,D,T,W,Q,L,H,C,P,N)$, every downstream root-unblock request for a regular tail comparison must read the route
$$
S\longmapsto D\longmapsto T\longmapsto W\longmapsto Q\longmapsto L\longmapsto H\longmapsto C\longmapsto P\longmapsto N
$$
before any completion-facing row is consumed. The route exposes the $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, $\RealSequenceLimitUp$ handoff, and structural rows, and it exports no quotient stream, selected representative, host convergence predicate, countable-choice selector, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-convergence-modulus-carrier}. The source row $S$, tolerance ledger $D$, tail schedule $T$, finite windows $W$, regular readback $Q$, and limit handoff $L$ are displayed in the accepted packet.

Apply tail-window cofinality and tail-schedule totality. They force each regular tail request to pass through the scheduled $\StreamNameUp$ windows after the $\DyadicRatCoreUp$ tolerance row and before the $\RegSeqRatUp$ readback.

Use the Bishop criterion handoff to identify the same route for downstream consumers. The structural rows $H,C,P,N$ preserve the route, while the refused host, quotient, selected, choice, and ambient-completeness objects have no carrier row.
\end{proof}

\begin{theorem}[Cauchy convergence modulus RealSeries consumer handoff]
\label{thm:cauchy-convergence-modulus-realseries-consumer-handoff}
Every $\RealSeriesUp$ consumer of an accepted $\CauchyConvergenceModulusUp$ packet must obtain its convergence-modulus read through
$$
S,D,T,W,Q,L,H,C,P,N.
$$
The consumer first reads the $\StreamNameUp$ source windows and $\DyadicRatCoreUp$ tolerance ledger, then the tail-index schedule and $\RegSeqRatUp$ readback, then the $\RealSequenceLimitUp$ handoff and structural rows. It receives no host series convergence theorem, quotient sum, selected limiting value, countable-choice schedule, trichotomy row, or ambient completeness witness.
\end{theorem}
\begin{proof}
Begin with the Bishop criterion handoff. It already places completion-facing consumers on the finite route through $S,D,T,W,Q,L,H,C,P,N$.

Read the $\RealSeriesUp$ consumer as a series-facing use of the same regular tail data. The only available convergence evidence is the displayed $\DyadicRatCoreUp$ request, the scheduled $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback, and the $\RealSequenceLimitUp$ handoff.

Completion readiness and the Real-seal nonescape theorem exclude external series convergence data. Thus the $\RealSeriesUp$ consumer receives exactly the finite convergence-modulus packet and no host sum or selected limit.
\end{proof}

\begin{theorem}[Cauchy convergence modulus regular completion unblock]
\label{thm:cauchy-convergence-modulus-regular-completion-unblock}
For every $\RegularCauchyCompletionUniversalUp$ consumer of an accepted $\CauchyConvergenceModulusUp$ packet, the regular-completion unblock surface is exhausted by the displayed rows
$$
S,D,T,W,Q,L,H,C,P,N.
$$
The unblock first consumes the $\DyadicRatCoreUp$ tolerance ledger and $\StreamNameUp$ finite windows, then repacks the read as $\RegSeqRatUp$ data, then reaches the $\RealSequenceLimitUp$ handoff and the completion boundary. No quotient completion object, selected representative, host equality test, countable-choice selector, trichotomy split, or ambient $\RealUp$ completeness theorem is supplied.
\end{theorem}
\begin{proof}
Use completion readiness and the regular-Cauchy handoff. They place $\RegularCauchyCompletionUniversalUp$ consumers on the route from the tolerance ledger through scheduled windows, regular readback, and the sequence-limit handoff.

Apply the root-unblock tail route above. The same $S,D,T,W,Q,L$ rows are available before any completion boundary is consumed, and $H,C,P,N$ keep transport, replay, provenance, and naming attached to the packet.

Finally apply ledger refusal and Real-seal nonescape. Since the refused completion, selected, host, choice, trichotomy, and ambient-completeness objects have no displayed row, the regular-completion unblock is exactly the finite route named in the statement.
\end{proof}

\begin{theorem}[Cauchy convergence modulus threshold totality]
\label{thm:cauchy-convergence-modulus-threshold-totality}
For every accepted $\CauchyConvergenceModulusUp$ packet $K=(S,D,T,W,Q,L,H,C,P,N)$, every displayed completion-facing tolerance request has a threshold row inside the same packet. After the source row $S$ and dyadic tolerance ledger $D$ are read, the permitted route must pass through
$$
T\longmapsto W\longmapsto Q\longmapsto L\longmapsto H\longmapsto C\longmapsto P\longmapsto N
$$
before any $\RegularCauchyCompletionUniversalUp$ or $\RealSeriesUp$ consumer can inspect a completion boundary. No host convergence predicate, quotient limit, selected representative, countable-choice selector, or ambient completeness row supplies an alternate threshold.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-convergence-modulus-carrier}. The rows $S,D,T,W,Q,L,H,C,P,N$ are the only displayed coordinates, and $T$ is positioned between the tolerance ledger and finite-window readback.

Apply tail-window cofinality. Every accepted dyadic request that leaves $D$ enters the scheduled finite window row $W$ through the threshold row $T$, so the threshold is total for the packet's displayed requests.

Use ledger refusal and non-escape. Because the carrier has no host convergence predicate, quotient boundary, selected representative, choice schedule, or ambient completeness coordinate, no second threshold source can be consumed by downstream completion or series readers.
\end{proof}

\begin{theorem}[Cauchy convergence modulus RealSeries budget lock]
\label{thm:cauchy-convergence-modulus-real-series-budget-lock}
For every accepted $\CauchyConvergenceModulusUp$ packet $K=(S,D,T,W,Q,L,H,C,P,N)$, any $\RealSeriesUp$ budget read is locked to the finite route
$$
S,D,T,W,Q,L,H,C,P,N.
$$
The series-facing consumer may spend only the displayed dyadic tolerance ledger, scheduled tail threshold, finite StreamName windows, RegSeqRat readback, RealSequenceLimit handoff, transport, replay, provenance, and local naming rows. It receives no hidden series convergence theorem, quotient sum, selected limit, countable-choice budget, or ambient $\RealUp$ completeness resource.
\end{theorem}
\begin{proof}
Begin with the regular-completion unblock route and the RealSeries consumer handoff. Both place the series-facing read on the same finite carrier coordinates before any Real-facing seal can be consumed.

Threshold totality fixes the budget source. Once $D$ has been read, the row $T$ determines the finite windows $W$ available to $Q$ and $L$, and the structural rows $H,C,P,N$ can replay only that route.

Finally apply ledger refusal. The packet stores no hidden convergence theorem, quotient sum, selected limit, choice budget, or ambient completeness resource, so the RealSeries budget is locked to the displayed rows.
\end{proof}

\begin{theorem}[Cauchy convergence modulus completion-boundary exactness]
\label{thm:cauchy-convergence-modulus-completion-boundary-exactness}
For every accepted $\CauchyConvergenceModulusUp$ packet $K=(S,D,T,W,Q,L,H,C,P,N)$, the completion boundary exported to $\RegularCauchyCompletionUniversalUp$ is exact only along the displayed route
$$
S,D,T,W,Q,L,H,C,P,N.
$$
The boundary may read the source, tolerance, threshold, finite windows, regular readback, limit handoff, componentwise transport, displayed continuation replay, package provenance, and local NameCert rows, but it may not import a quotient completion object, selected representative, host equality test, countable-choice selector, trichotomy split, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Project the carrier and apply the regular-completion unblock theorem. It already exhausts the boundary surface by $S,D,T,W,Q,L,H,C,P,N$.

Use threshold totality and the RealSeries budget lock as compatibility checks. They show that both completion-facing and series-facing consumers reuse the same threshold, finite-window, readback, and handoff rows rather than creating a second boundary.

The refusal ledger closes the exactness claim. Since quotient completion objects, selected representatives, host equality tests, choice selectors, trichotomy splits, and ambient completeness theorems have no row in $K$, the exported completion boundary is exactly the displayed finite route.
\end{proof}

\begin{theorem}[Cauchy convergence modulus tail schedule totality]
\label{thm:cauchy-convergence-modulus-tail-schedule-totality}
For every accepted $\CauchyConvergenceModulusUp$ packet and every $\BishopCompletionCriterionUp$ or $\RegularCauchyCompletionUniversalUp$ consumer, the tail-index schedule $T$ is total for the displayed finite-window route. After the source row $S$ and dyadic tolerance ledger $D$ are read, every permitted completion-facing request must pass through $T,W,Q,L,H,C,P,N$ in the same $\BHist$ packet, with no alternate tail schedule, quotient stream equality, selected limit, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Start from the carrier and NameCert obligation surfaces. They expose $T$ as the named tail-index schedule between the tolerance ledger $D$ and the finite window row $W$.

Tail-window cofinality supplies the totality witness for displayed requests: each accepted dyadic tolerance request is routed through a scheduled finite window before $Q$ and $L$ are available. The carrier-transport theorem preserves that row under componentwise $\hsame$ replacement.

Finally apply classifier stability and ledger refusal. Since no other tail schedule or completion coordinate is present in the packet, every Bishop-completion-facing request consumes the displayed $T,W,Q,L,H,C,P,N$ route.
\end{proof}

\begin{theorem}[Cauchy convergence modulus regular completion readiness]
\label{thm:cauchy-convergence-modulus-regular-completion-readiness}
An accepted $\CauchyConvergenceModulusUp$ packet is ready for current L10 regular-completion consumers exactly through the finite route
$$
S,D,T,W,Q,L,H,C,P,N.
$$
The readiness claim is anchored in $\BHist$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealSequenceLimitUp$, and $\RegularCauchyCompletionUniversalUp$ data, and every $\BishopCompletionCriterionUp$ consumer must use the displayed route rather than a quotient-stream boundary, selected host limit, host equality test, countable-choice selector, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Use completion readiness to put Real-sequence and regular-completion reads on the route from $D$ through $T,W,Q,L$ and the structural rows. The source row $S$ supplies the displayed sequence input for that route.

The Bishop criterion handoff theorem then identifies the same route as the only surface available to $\BishopCompletionCriterionUp$ consumers. Tail-schedule totality prevents a consumer from replacing the displayed schedule with an unbounded or hidden tail.

The remaining exclusions follow from classifier stability and ledger refusal. The packet is therefore completion-ready only as finite BEDC certificate data over the displayed rows.
\end{proof}

\begin{theorem}[Cauchy convergence modulus real-sequence-limit consumer]
\label{thm:cauchy-convergence-modulus-real-sequence-limit-consumer}
Every $\RealSequenceLimitUp$ consumer of an accepted $\CauchyConvergenceModulusUp$ packet must read the displayed $\BHist$ carrier route
$$
S,D,T,W,Q,L,H,C,P,N
$$
before it can consume the limit handoff row $L$. The consumer receives the $\DyadicRatCoreUp$ tolerance ledger, the finite $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row, but it receives no $\RealUp$ completeness theorem, selected limit, host convergence predicate, countable-choice selector, or quotient representative.
\end{theorem}
\begin{proof}
Project the carrier route of \autoref{def:cauchy-convergence-modulus-carrier}. The limit consumer can reach $L$ only after the source, tolerance, schedule, window, and regular readback rows have been displayed.

Use \autoref{thm:cauchy-convergence-modulus-tail-window-cofinality} to make the route cofinal for every displayed tolerance request. The finite window row $W$ and regular readback row $Q$ cannot be skipped, because they are the route through which the tolerance ledger $D$ becomes a sequence-limit handoff.

Finally use classifier stability and ledger refusal. The structural rows $H,C,P,N$ preserve the displayed packet, while the excluded host and choice objects have no row in the $\BHist$ carrier. Thus the $\RealSequenceLimitUp$ consumer receives exactly the displayed finite convergence-modulus data.
\end{proof}

\begin{theorem}[Cauchy convergence modulus completion-threshold exhaustion]
\label{thm:cauchy-convergence-modulus-completion-threshold-exhaustion}
For every accepted $\CauchyConvergenceModulusUp$ packet, the completion threshold exposed to a $\RegularCauchyCompletionUniversalUp$ or $\RealUp$-facing consumer is exhausted by the finite rows $D,T,W,Q,L$ together with $H,C,P,N$. Once the dyadic tolerance row $D$ has selected a tail-index row $T$, every permitted completion read must pass through the finite $\StreamNameUp$ window family $W$, the $\RegSeqRatUp$ readback $Q$, and the $\RealSequenceLimitUp$ handoff $L$.
\end{theorem}
\begin{proof}
Begin with the regular-Cauchy handoff theorem. It places completion consumers on the route from the dyadic tolerance ledger through the tail-index schedule, finite windows, regular readback, and limit handoff.

Apply completion readiness to identify the Real-seal surface. The seal row is reached only after the displayed threshold and window rows have been read, and its structural support is limited to $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

The carrier contains no further threshold coordinate. Hence the displayed tail-index row and its finite window family exhaust the completion threshold available to Real and completion consumers.
\end{proof}

\begin{theorem}[Cauchy convergence modulus Real seal nonescape]
\label{thm:cauchy-convergence-modulus-real-seal-nonescape}
Every $\RealUp$ seal read exported by an accepted $\CauchyConvergenceModulusUp$ packet factors through the displayed $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealSequenceLimitUp$ rows and through the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The seal exports no ambient real completeness theorem, quotient limit, host sequence convergence, host real equality, countable choice, trichotomy, selected representative, or unbounded tail read.
\end{theorem}
\begin{proof}
Read the Real-seal surface of \autoref{def:cauchy-convergence-modulus-real-seal-surface}. The seal is attached to the same dyadic tolerance ledger, tail-index schedule, finite windows, regular readback, and sequence-limit handoff as the carrier route.

Use \autoref{thm:cauchy-convergence-modulus-completion-threshold-exhaustion}. It says that no completion-facing threshold remains beyond $D,T,W,Q,L$ and the structural rows, so a Real-facing consumer cannot replace the displayed route by an unbounded host tail.

Use \autoref{thm:cauchy-convergence-modulus-ledger-refusal} for the excluded objects. Since the packet has no row for real completeness, quotient limits, host equality, countable choice, trichotomy, selected representatives, or unbounded tail data, the exported $\RealUp$ seal cannot escape the finite convergence-modulus route.
\end{proof}

\begin{theorem}[Cauchy convergence modulus scoped support]
\label{thm:cauchy-convergence-modulus-scoped-support}
For every accepted $\CauchyConvergenceModulusUp$ packet, the scoped support is exactly the sequence-source row $S$, the $\DyadicRatCoreUp$ tolerance ledger $D$, the tail-index schedule $T$, the finite $\StreamNameUp$ windows $W$, the $\RegSeqRatUp$ readback row $Q$, the $\RealSequenceLimitUp$ handoff $L$, the $\RegularCauchyCompletionUniversalUp$ consumer boundary, and the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows $H,C,P,N$. No quotient limit, selected tail, host convergence predicate, host real equality, countable choice, trichotomy, ambient $\RealUp$ completeness theorem, or unbounded tail read lies in the packet scope.
\end{theorem}
\begin{proof}
Project the carrier and NameCert obligations. The packet exposes $S,D,T,W,Q,L,H,C,P,N$, and the local NameCert obligations require every admitted convergence-modulus read to pass through those displayed rows.

Use tail-window cofinality and carrier transport next. Cofinality routes each dyadic tolerance request through the tail-index schedule and finite StreamName windows, while transport preserves the same route under componentwise $\hsame$ replacement.

Completion readiness, the regular-Cauchy handoff, and the Real-seal nonescape theorem identify the consumer boundary. They place $\RealSequenceLimitUp$, $\RegularCauchyCompletionUniversalUp$, and $\RealUp$ consumers on the same finite path and exclude all host, quotient, selected, choice, trichotomy, ambient-completeness, and unbounded-tail rows from the scoped support.
\end{proof}

\falsifiablePrediction{An accepted $\CauchyConvergenceModulusUp$ consumer that reaches a $\RealSequenceLimitUp$ handoff without the displayed sequence source, dyadic tolerance ledger, tail-index schedule, finite StreamName windows, and RegSeqRat readback refutes the carrier surface.}

\independenceWitness{dyadicratcore, streamname, regseqrat, realsequencelimit, regularcauchycompletionuniversal: no listed sibling supplies the whole ten-row packet $K=(S,D,T,W,Q,L,H,C,P,N)$, because each sibling contributes only a tolerance, window, readback, limit, or completion-facing surface while this chapter binds all five analytic faces with transport, replay, provenance, and local naming.}

\begin{closurestatus}{\CauchyConvergenceModulusUp}
  \constructivestory{A $\CauchyConvergenceModulusUp$ packet is generated from a sequence-source row, dyadic tolerance ledger, tail-index schedule, finite StreamName windows, RegSeqRat readback, RealSequenceLimit handoff, componentwise hsame transports, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:cauchy-convergence-modulus-carrier}, \autoref{thm:cauchy-convergence-modulus-namecert-obligations}, \autoref{thm:cauchy-convergence-modulus-tail-window-cofinality}, \autoref{thm:cauchy-convergence-modulus-tail-window-exactness}, \autoref{thm:cauchy-convergence-modulus-limit-readback-exhaustion}, \autoref{thm:cauchy-convergence-modulus-carrier-transport}, \autoref{thm:cauchy-convergence-modulus-classifier-stability}, \autoref{thm:cauchy-convergence-modulus-ledger-refusal}, \autoref{def:cauchy-convergence-modulus-real-seal-surface}, \autoref{thm:cauchy-convergence-modulus-completion-readiness}, \autoref{thm:cauchy-convergence-modulus-regular-cauchy-handoff}, \autoref{thm:cauchy-convergence-modulus-uniform-threshold-handoff}, \autoref{thm:cauchy-convergence-modulus-uniform-tail-grid}, \autoref{thm:cauchy-convergence-modulus-bishop-criterion-handoff}, \autoref{thm:cauchy-convergence-modulus-tail-schedule-totality}, \autoref{thm:cauchy-convergence-modulus-regular-completion-readiness}, \autoref{thm:cauchy-convergence-modulus-real-sequence-limit-consumer}, \autoref{thm:cauchy-convergence-modulus-completion-threshold-exhaustion}, \autoref{thm:cauchy-convergence-modulus-real-seal-nonescape}, and \autoref{thm:cauchy-convergence-modulus-scoped-support} bind the constructive convergence-modulus route over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealSequenceLimitUp$, $\RegularCauchyCompletionUniversalUp$, and $\RealUp$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.CauchyConvergenceModulusUp.CauchyConvergenceModulusNamecertObligations}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim $\RealUp$ completeness, quotient limits, host sequence convergence, host real equality, countable choice, trichotomy, selected representatives, ambient completion, or a Lean theorem.}
  \upgradepath{A formal route can encode the ten-row carrier and prove the NameCert, cofinality, transport, classifier-stability, and ledger-refusal obligations.}
\end{closurestatus}
