\chapter{A Concrete Naming Certificate for $\DyadicIntervalCoverUp$}
\label{ch:concrete-instances-dyadic-interval-cover-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\DyadicIntervalCoverUp$ packet records a finite dyadic interval-cover surface for the open Real and Completion route. It sits between the dyadic arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the visible Real seal of \autoref{ch:concrete-instances-real-namecert}, and the finite interval-net surface of \autoref{ch:concrete-instances-bishop-interval-compact-namecert}. The packet names cover data that can be inspected through finitely many rows; it does not assert an open-cover compactness theorem or any host completion principle.

\begin{definition}[DyadicIntervalCover carrier]
\label{def:dyadic-interval-cover-carrier}
A $\DyadicIntervalCoverUp$ carrier is a finite $\BHist$ packet
$$
I=(L,U,M,R,V,W,Q,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ and $U$ are finite rows of lower and upper dyadic endpoints, each endpoint read through the $\DyadicRatCoreUp$ arithmetic surface.
\item $M$ is the mesh-index row that records the dyadic scale at which endpoint comparisons and interval-membership tests are performed.
\item $R$ is the radius ledger assigning a displayed dyadic tolerance to every interval row and every inspected regular-name window.
\item $V$ is the finite cover-membership row: each listed mesh cell carries the index of a displayed dyadic interval whose lower and upper endpoint rows contain that cell at the tolerance named by $R$.
\item $W$ is the $\StreamNameUp$ finite-window row used by the consumer real names that are tested against the cover.
\item $Q$ is the $\RegSeqRatUp$ readback row that translates the windows $W$ into regular rational approximants at the mesh scale $M$.
\item $A$ is the visible $\RealUp$ seal row reached through the same window and readback data.
\item $H$ stores the componentwise $\hsame$ transports for endpoints, mesh indices, radius rows, cover-membership rows, windows, readbacks, Real seals, continuation, provenance, and local naming rows.
\item $C$ stores the displayed $\Cont$ replay from dyadic endpoints to mesh cells, from mesh cells to cover-membership rows, from windows to regular readback, and from regular readback to the visible Real seal.
\item $P$ is the $\Pkg$ provenance over $\DyadicIntervalCoverUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BishopIntervalCompactUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\DyadicIntervalCoverUp}$ row.
\end{enumerate}
The accepted carrier stores only the finite cover surface just displayed. It carries no open-cover compactness principle, no Heine--Borel theorem, no sequential compactness selector, no selected limit, no quotient real equality, no host real equality test, no countable-choice functional, and no ambient $\RealUp$ completeness coordinate.
\end{definition}

\begin{theorem}[DyadicIntervalCover NameCert obligations]
\label{thm:dyadic-interval-cover-namecert-obligations}
For an accepted packet $I=(L,U,M,R,V,W,Q,A,H,C,P,N)$, the local $\NameCert_{\DyadicIntervalCoverUp}$ obligations are exhausted by the finite endpoint, mesh, radius, membership, window, readback, seal, transport, continuation, and provenance rows of \autoref{def:dyadic-interval-cover-carrier}. In particular, every obligation can be checked by finite projection from the displayed $\BHist$ packet and by replay of $H$, $C$, and $P$; no obligation may call on open-cover compactness, Heine--Borel compactness, sequential compactness, selected limits, quotient real equality, host real equality, countable choice, or Real completeness.
\end{theorem}
\begin{proof}
Project the carrier row by row. The endpoint and mesh obligations read only $L,U,M,R,V$ and the dyadic arithmetic certified by the $\DyadicRatCoreUp$ sibling chapter. The real-name obligations read only the finite windows $W$, the regular-rational readback $Q$, and the visible seal $A$, hence they factor through the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ sibling surfaces.

The remaining obligations are structural. The $\hsame$ row $H$ transports equal displayed coordinates, the $\Cont$ row $C$ replays the permitted reads, and the provenance row $P$ records exactly the finite BEDC surfaces used by the packet, including the comparison with the $\BishopIntervalCompactUp$ finite-net interface. Since the carrier has no row for an open-cover selector, a host limit, a quotient equality, a choice functional, or a completeness principle, none of those principles can appear in a local NameCert obligation.
\end{proof}

\begin{theorem}[Regular-sequence finite-window exhaustion]
\label{thm:dyadic-interval-cover-regular-sequence-window-exhaustion}
Let $I=(L,U,M,R,V,W,Q,A,H,C,P,N)$ be an accepted $\DyadicIntervalCoverUp$ packet. Any consumer that asks whether a regular real name represented by the displayed $\StreamNameUp$ windows $W$ and $\RegSeqRatUp$ readback $Q$ meets the cover named by $L,U,M,R,V$ is exhausted by a finite window computation: it reads the mesh index $M$, the radius ledger $R$, the regular approximants in $Q$, the finite membership rows $V$, and the visible $\RealUp$ seal $A$. No later tail of the regular sequence and no ambient equality of real names contributes to the cover decision.
\end{theorem}
\begin{proof}
Begin with the window and readback coordinates. The $\StreamNameUp$ row supplies exactly the finite windows available to the consumer, and the $\RegSeqRatUp$ row turns those windows into rational approximants at the mesh scale named by $M$ and the radii named by $R$.

Next inspect the cover surface. The finite row $V$ contains the whole list of membership witnesses for the dyadic endpoint rows $L$ and $U$, so a consumer can only compare the displayed approximants with this finite list. The continuation row $C$ has no replay path beyond those rows, and the Real seal $A$ records only the visible endpoint reached through the same finite readback.

Thus the decision surface is exhausted by $M,R,Q,V,A$ together with the displayed transports in $H$. A later regular-sequence tail, quotient equality of real names, host equality, countable choice, selected limits, and Real completeness are absent from the packet, so they cannot affect the finite-window cover read.
\end{proof}

\begin{theorem}[DyadicIntervalCover finite-window carrier]
\label{thm:dyadicintervalcover-finite-window-carrier}
Every accepted $\DyadicIntervalCoverUp$ packet exposes only finite interval-window rows over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. For a carrier
$$
I=(L,U,M,R,V,W,Q,A,H,C,P,N),
$$
the endpoint rows $L,U$, mesh row $M$, radius ledger $R$, membership row $V$, window row $W$, readback row $Q$, and seal row $A$ form the whole displayed cover surface before the local $\NameCert_{\DyadicIntervalCoverUp}$ row is exported.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-interval-cover-carrier}. The endpoint, mesh, radius, and membership rows are finite dyadic interval-window data, and the only Real-facing rows are the displayed StreamName windows, RegSeqRat readback, and terminal Real seal.

Apply \autoref{thm:dyadic-interval-cover-regular-sequence-window-exhaustion}. It forces every regular-name cover read through $M,R,Q,V,A$ together with the finite window row $W$ before any cover decision is consumed. The L10 sibling dependencies are exactly the dyadic arithmetic of $\DyadicRatCoreUp$, the finite observation surface of $\StreamNameUp$, the regular-rational readback of $\RegSeqRatUp$, and the visible seal of $\RealUp$.

Since the carrier contains no row beyond $L,U,M,R,V,W,Q,A,H,C,P,N$, the finite-window surface is exhausted by those rows.
\end{proof}

\begin{theorem}[DyadicIntervalCover refinement stability]
\label{thm:dyadicintervalcover-refinement-stability}
Let
$$
I=(L,U,M,R,V,W,Q,A,H,C,P,N)
$$
and
$$
I'=(L',U',M',R',V',W',Q',A',H',C',P',N')
$$
be accepted $\DyadicIntervalCoverUp$ packets. If a displayed refinement carries componentwise $\hsame$ data from the endpoint, mesh, radius, membership, window, readback, and seal rows of $I$ to the corresponding rows of $I'$, and the replay rows display the same $\Cont$ route through those transported coordinates, then the refined cover preserves the same finite interval-window route over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.
\end{theorem}
\begin{proof}
Project both carriers. The rows available to the refinement are precisely the finite endpoint rows, mesh rows, radius ledgers, membership rows, finite windows, regular readbacks, Real seals, and structural rows listed in \autoref{def:dyadic-interval-cover-carrier}.

Apply \autoref{thm:dyadic-interval-cover-regular-sequence-window-exhaustion} to $I$ and $I'$. The cover read in each packet is exhausted by the displayed mesh, radius, readback, membership, and seal rows. Componentwise $\hsame$ in $H,H'$ identifies those rows as packet data, and the displayed $\Cont$ replay in $C,C'$ preserves the route through the same L10 siblings.

Thus refinement changes only the displayed finite interval rows and their transported membership witnesses. It does not create an open-cover compactness row, a selected subcover, a host equality test, a quotient stream, a choice functional, or a Real-completeness witness.
\end{proof}

\begin{theorem}[DyadicIntervalCover ledger exactness]
\label{thm:dyadicintervalcover-ledger-exactness}
The $\DyadicIntervalCoverUp$ cover ledger is exact for the displayed finite windows. In an accepted carrier
$$
I=(L,U,M,R,V,W,Q,A,H,C,P,N),
$$
the radius ledger $R$ and membership row $V$ account for exactly the dyadic endpoint comparisons and regular-name windows read through $L,U,M,W,Q,A$. The ledger exports no open-cover compactness theorem, selected subcover, host real equality, quotient stream, countable choice, or Real completeness.
\end{theorem}
\begin{proof}
Project the displayed carrier. The ledger row $R$ supplies the tolerance data for endpoint comparisons and for each inspected regular-name window, while $V$ records the finite membership witnesses at that tolerance.

Use \autoref{thm:dyadic-interval-cover-regular-sequence-window-exhaustion}. Every cover decision reads only $M,R,Q,V,A$ after the StreamName window $W$ has been opened, so the ledger has no hidden tail coordinate beyond the finite rows.

The sibling dependencies are the dyadic arithmetic surface $\DyadicRatCoreUp$, the window surface $\StreamNameUp$, the readback surface $\RegSeqRatUp$, and the terminal seal $\RealUp$. Since none of those rows supplies open-cover compactness, a selected subcover, host equality, quotient equality, choice, or completeness, the accepted ledger cannot export any such principle.
\end{proof}

\begin{theorem}[DyadicIntervalCover membership transport]
\label{thm:dyadic-interval-cover-membership-transport}
Let $I=(L,U,M,R,V,W,Q,A,H,C,P,N)$ be an accepted $\DyadicIntervalCoverUp$ packet. Every cover-membership read through the row $V$ is transported only by the componentwise $\hsame$ row $H$ and the displayed $\Cont$ replay row $C$ over the endpoint rows $L,U$, mesh row $M$, radius ledger $R$, readback row $Q$, and membership row $V$. In particular, membership transport exports no host interval equality, selected subcover, quotient real equality, countable choice, or Real completeness row.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-interval-cover-carrier}. The membership row $V$ is displayed together with endpoint rows $L,U$, mesh row $M$, radius ledger $R$, window row $W$, readback row $Q$, and seal row $A$.

Use \autoref{thm:dyadic-interval-cover-namecert-obligations}. The local NameCert obligations make $H$ the componentwise transport row and $C$ the replay route for endpoint, mesh, radius, membership, window, readback, and seal data.

Finally apply \autoref{thm:dyadicintervalcover-refinement-stability}. Refinement preserves the finite interval-window route only through the transported rows, so a transported membership read cannot acquire host interval equality, selected subcover data, quotient equality, countable choice, or Real completeness.
\end{proof}

\begin{theorem}[DyadicIntervalCover seal nonescape]
\label{thm:dyadic-interval-cover-seal-nonescape}
Let $I=(L,U,M,R,V,W,Q,A,H,C,P,N)$ be an accepted $\DyadicIntervalCoverUp$ packet. Every $\RealUp$ seal read through $A$ factors through the finite window row $W$ and regular readback row $Q$ before it reaches the cover rows $L,U,M,R,V$ and the structural rows $H,C,P,N$. The seal exports no open-cover compactness, host equality, quotient stream, selected limit, countable choice, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Start with \autoref{thm:dyadic-interval-cover-regular-sequence-window-exhaustion}. It forces any regular-name cover read to inspect the finite windows $W$, readback row $Q$, mesh row $M$, radius ledger $R$, membership row $V$, and visible Real seal $A$.

Use \autoref{thm:dyadicintervalcover-finite-window-carrier} to identify the whole cover surface. The rows $L,U,M,R,V,W,Q,A$ are the displayed interval-window data before the local $\NameCert_{\DyadicIntervalCoverUp}$ row can be exported.

The structural rows $H,C,P,N$ preserve only that displayed route. Since the carrier of \autoref{def:dyadic-interval-cover-carrier} contains no coordinate for open-cover compactness, host equality, quotient streams, selected limits, countable choice, or Real completeness, the seal cannot export any such data.
\end{proof}

\begin{theorem}[DyadicIntervalCover regular-window ledger]
\label{thm:dyadic-interval-cover-regular-window-ledger}
For every accepted $\DyadicIntervalCoverUp$ carrier $I=(L,U,M,R,V,W,Q,A,H,C,P,N)$, the regular-window ledger is exactly the finite accounting of $W,Q,R$ against the mesh and membership rows $M,V$. Each regular-name window opened by $W$ is read back through $Q$, assigned its displayed radius by $R$, and compared with the finite membership row $V$ at the mesh named by $M$; no hidden tail ledger or ambient equality source contributes to the accounting.
\end{theorem}
\begin{proof}
Project the carrier and read the rows $W,Q,R,M,V$. The window row $W$ supplies the finite observations, the readback row $Q$ turns them into regular rational approximants, the radius ledger $R$ supplies the displayed tolerance, and $M,V$ give the mesh and membership rows that consume those approximants.

Apply \autoref{thm:dyadic-interval-cover-regular-sequence-window-exhaustion}. It says every cover decision is exhausted by the displayed finite window computation and has no later regular-sequence tail or ambient real-name equality input.

Now use \autoref{thm:dyadicintervalcover-ledger-exactness}. The existing ledger theorem identifies $R$ and $V$ as the exact accounting rows for the dyadic endpoint comparisons and regular-name windows. Therefore the regular-window accounting is exactly $W,Q,R$ against $M,V$, with no hidden tail ledger, host equality, quotient equality, choice, selected limit, or completeness row.
\end{proof}

\begin{closurestatus}{\DyadicIntervalCoverUp}
  \constructivestory{A $\DyadicIntervalCoverUp$ packet is generated from dyadic lower and upper endpoint rows, a mesh index, a radius ledger, finite cover-membership rows, StreamName windows, RegSeqRat readbacks, a Real seal, componentwise transport, displayed continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-interval-cover-carrier}, \autoref{thm:dyadic-interval-cover-namecert-obligations}, and \autoref{thm:dyadic-interval-cover-regular-sequence-window-exhaustion} bind the finite dyadic interval-cover seed over the Real and Completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, Heine--Borel compactness, sequential compactness, selected limits, quotient real equality, host real equality, countable choice, Real completeness, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, finite membership transport, regular-window exhaustion, seal nonescape, and ledger exactness for the displayed packet.}
\end{closurestatus}
