\chapter{A Concrete Naming Certificate for $\BoundedRealLowerCutUp$}
\label{ch:concrete-instances-bounded-real-lower-cut-namecert}
\origin{human}

Following Bishop and Bridges, bounded real lower-cut data are read as finite rational observations attached to a $\RealUp$ seal and an Archimedean bound, not as a host supremum or completed cut quotient. The packet consumes the real-name boundary of \autoref{ch:concrete-instances-real-namecert}, the located lower-cut discipline of \autoref{ch:concrete-instances-locatedcut-namecert}, the explicit rational-bound surface of \autoref{ch:concrete-instances-archimedeanreal-namecert}, and the nonconvergent observation boundary of \autoref{ch:concrete-instances-speckersequence-namecert}. It is a constructive observation surface for bounded names rather than a Dedekind-real construction.

\begin{definition}[BoundedRealLowerCut carrier]
\label{def:bounded-real-lower-cut-carrier}
A $\BoundedRealLowerCutUp$ carrier is a finite $\BHist$ packet
$$
L=(R,A,D,S,O,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUp$ seal row whose lower observations are being exposed.
\item $A$ is the $\ArchimedeanRealUp$ rational-bound row attached to the same displayed real name.
\item $D$ is the $\DyadicRatCoreUp$ comparison row used to read rational lower observations at finite precision.
\item $S$ is the $\StreamNameUp$ finite-window schedule that names which observations of $R$ are inspected.
\item $O$ is the lower-observation ledger: each row records a rational candidate, its dyadic comparison budget, the finite window it reads, and the evidence that the candidate lies below the sealed name as far as the displayed packet can observe.
\item $B$ is the boundedness ledger tying every lower-observation row in $O$ to the Archimedean bound row $A$.
\item $H$ records the componentwise $\hsame$ transports for $R,A,D,S,O,B$ and the structural rows.
\item $C$ records the displayed $\Cont$ routes by which consumers replay the Real seal, Archimedean bound, dyadic comparison, window schedule, observation ledger, and boundedness ledger.
\item $P$ is the $\Pkg$ provenance over $\BoundedRealLowerCutUp$, $\RealUp$, $\LocatedCutUp$, $\ArchimedeanRealUp$, $\SpeckerSequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BoundedRealLowerCutUp}$ row.
\end{enumerate}
The carrier stores no host supremum, no Dedekind real construction, no trichotomy branch, no quotient real equality, no selected limit, and no ambient completeness coordinate for $\RealUp$.
\end{definition}

\begin{theorem}[BoundedRealLowerCut NameCert obligations]
\label{thm:bounded-real-lower-cut-namecert-obligations}
For an accepted $\BoundedRealLowerCutUp$ carrier $L=(R,A,D,S,O,B,H,C,P,N)$, the local $\NameCert_{\BoundedRealLowerCutUp}$ surface consists of five finite obligation rows:
\begin{enumerate}
\item carrier formation for the $\RealUp$ seal, $\ArchimedeanRealUp$ bound, $\DyadicRatCoreUp$ comparison row, $\StreamNameUp$ finite-window schedule, lower-observation ledger, boundedness ledger, transports, continuations, provenance, and local naming data;
\item classifier stability, stating that replacement of the displayed rows through $H$ and replay through $C$ preserves the same bounded lower-cut observation packet;
\item lower-observation exactness, stating that each row of $O$ is read from the same Real seal $R$ through the finite windows $S$ and dyadic comparison budget $D$;
\item boundedness handoff, stating that the Archimedean row $A$ bounds every lower-observation row recorded in $O$ through the finite ledger $B$;
\item seal non-escape, stating that no consumer reaches a supremum, Dedekind cut quotient, trichotomy branch, quotient real equality, selected limit, or $\RealUp$ completeness principle from the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier formation is the displayed tuple of \autoref{def:bounded-real-lower-cut-carrier}. It contains exactly one Real seal row, one Archimedean bound row, one dyadic comparison row, one finite-window schedule, one lower-observation ledger, one boundedness ledger, and the structural transport, continuation, provenance, and naming rows.

Classifier stability is componentwise over $H$ and $C$. A classified replacement may transport the displayed rows and replay their consumers, but it cannot introduce a second Real seal, a second bound, a hidden quotient of cuts, or an external completeness witness.

Lower-observation exactness is the role of $O$. Each observation row records the rational candidate, the dyadic comparison budget, and the finite window through which the same seal $R$ is inspected. The packet therefore exposes the lower-cut face only as observed finite data.

The boundedness handoff is supplied by $A$ and $B$. The Archimedean row gives the explicit rational-bound surface, and the ledger $B$ ties every accepted lower observation to that surface without selecting a least upper bound or a supremum.

Seal non-escape follows from the row inventory. The provenance row mentions the sibling $\LocatedCutUp$ and $\SpeckerSequenceUp$ boundaries only as observation disciplines; no row carries a Dedekind construction, trichotomy branch, quotient equality, selected limit, or ambient $\RealUp$ completeness coordinate.
\end{proof}

\begin{theorem}[BoundedRealLowerCut L10 handoff]
\label{thm:bounded-real-lower-cut-l10-handoff}
Every Real-and-Completion consumer of an accepted $\BoundedRealLowerCutUp$ packet factors through the displayed $\RealUp$ seal $R$, the $\ArchimedeanRealUp$ bound $A$, the $\DyadicRatCoreUp$ comparison row $D$, the $\StreamNameUp$ finite windows $S$, the lower-observation ledger $O$, the boundedness ledger $B$, the transport row $H$, the continuation row $C$, the provenance row $P$, and the local $\NameCert_{\BoundedRealLowerCutUp}$ row $N$ before using the bounded lower-cut surface.
\end{theorem}
\begin{proof}
Project the accepted carrier. The Real-facing coordinate is $R$, and every lower-cut read is mediated by $D,S,O$ while every boundedness read is mediated by $A$ and $B$.

Next replay the sibling route. The $\RealUp$ chapter supplies the seal boundary, $\LocatedCutUp$ supplies the finite lower-cut observation discipline, $\ArchimedeanRealUp$ supplies the rational-bound surface, and $\SpeckerSequenceUp$ marks the refusal to turn bounded observations into a general convergence or completeness principle.

Finally use $H,C,P,N$ to close the handoff route. These rows record the only permitted transports, continuations, provenance, and local naming evidence, so an L10 consumer cannot bypass the finite observation surface by reading a host supremum, a Dedekind real, trichotomy, quotient real equality, selected limits, or Real completeness.
\end{proof}

\begin{closurestatus}{\BoundedRealLowerCutUp}
  \constructivestory{A $\BoundedRealLowerCutUp$ packet is generated from a displayed $\RealUp$ seal, an $\ArchimedeanRealUp$ bound row, a $\DyadicRatCoreUp$ comparison row, a $\StreamNameUp$ window schedule, a lower-observation ledger, a boundedness ledger, componentwise $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bounded-real-lower-cut-carrier}, \autoref{thm:bounded-real-lower-cut-namecert-obligations}, and \autoref{thm:bounded-real-lower-cut-l10-handoff} bind the finite bounded lower-cut observation surface for Real-and-Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a host supremum, a Dedekind real construction, trichotomy, quotient real equality, selected limits, $\RealUp$ completeness, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier formation, classifier stability, lower-observation exactness, boundedness handoff, and seal non-escape for the displayed packet.}
\end{closurestatus}
