\chapter{A Concrete Naming Certificate for $\RegularLocatedCauchyRealUp$}
\label{ch:concrete-instances-regular-located-cauchy-real-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\RegularLocatedCauchyRealUp$ packet records the boundary where a regular rational Cauchy name, an explicit convergence modulus, and finite locatedness evidence are all visible before the $\RealUp$ seal is read. It sits over the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the endpoint and radius ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the located enclosure surface of \autoref{ch:concrete-instances-locatedreal-namecert}, and the explicit rate rows of \autoref{ch:concrete-instances-modulusofconvergence-namecert}. The certificate keeps convergence and location as finite rows rather than hiding them inside a later BishopReal or compact-interval consumer.

\begin{definition}[Regular located Cauchy real carrier]
\label{def:regular-located-cauchy-real-carrier}
A $\RegularLocatedCauchyRealUp$ carrier is a finite $\BHist$ packet
$$
R=(S,Q,D,M,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ window family naming the finite observation windows used by the packet.
\item $Q$ is the $\RegSeqRatUp$ source row whose regular rational entries are read only on the windows in $S$.
\item $D$ is the $\DyadicRatCoreUp$ endpoint and radius ledger recording the rational centers, dyadic radii, and interval comparisons attached to those windows.
\item $M$ is the $\ModulusOfConvergenceUp$ rate row assigning each requested tolerance a finite threshold over the displayed windows.
\item $L$ is the $\LocatedRealUp$ enclosure row recording the finite interval-location evidence attached to the same source, endpoint, radius, and threshold rows.
\item $E$ is the terminal $\RealUp$ seal row reached only after the stream, regular-source, dyadic-ledger, modulus, and located-enclosure rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the stream windows, regular rational source, dyadic endpoint and radius ledger, convergence-modulus row, located enclosure, Real seal, continuation, provenance, and local naming rows.
\item $C$ records the displayed $\Cont$ replay from each precision and location request through $S,Q,D,M,L,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\ModulusOfConvergenceUp$, $\LocatedRealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularLocatedCauchyRealUp}$ row.
\end{enumerate}
The carrier has no coordinate for Dedekind construction of $\RealUp$, quotient equality, trichotomy, open-cover compactness, countable choice, completed metric-space points, or an unbounded stream read.
\end{definition}

\begin{theorem}[Regular located Cauchy real NameCert obligations]
\label{thm:regular-located-cauchy-real-namecert-obligations}
The seed $\NameCert_{\RegularLocatedCauchyRealUp}$ surface for \autoref{def:regular-located-cauchy-real-carrier} consists exactly of carrier exposure for $R$, finite-window exposure through $S$, regular rational source exposure through $Q$, endpoint and radius exposure through $D$, convergence-rate exposure through $M$, located-enclosure exposure through $L$, terminal $\RealUp$ seal exposure through $E$, componentwise transport through $H$, displayed continuation replay through $C$, package provenance through $P$, and local naming through $N$. Each accepted request is classified only by the displayed StreamName window, the RegSeqRat source row, the dyadic endpoint and radius ledger, the convergence threshold, and the located enclosure row.
\end{theorem}
\leanchecked{BEDC.Derived.RegularLocatedCauchyRealUp.TasteGate.RegularLocatedCauchyRealTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier tuple $R=(S,Q,D,M,L,E,H,C,P,N)$. Each analytic coordinate is a displayed finite row, and the final coordinate names the same tuple as the local $\NameCert_{\RegularLocatedCauchyRealUp}$ surface.

Read the rows in their dependency order. A request first consumes the stream window $S$ and regular rational source $Q$, then the dyadic endpoint and radius ledger $D$, then the convergence threshold row $M$, and only then the located enclosure $L$ and terminal Real seal $E$.

The structural rows add no hidden analytic object. They transport, replay, source, and name the displayed route, while the excluded objects have no coordinate in the carrier. Hence the listed rows exhaust the seed obligation surface.
\end{proof}

\begin{theorem}[Regular located Cauchy real RealUp seal route]
\label{thm:regular-located-cauchy-real-realup-seal-route}
For every accepted $\RegularLocatedCauchyRealUp$ packet $R=(S,Q,D,M,L,E,H,C,P,N)$ and every displayed precision request, the Real-facing read factors through the finite route
$$
S\longmapsto Q\longmapsto D\longmapsto M\longmapsto L\longmapsto E\longmapsto(H,C,P,N).
$$
No consumer can read the terminal $\RealUp$ seal from $R$ without also reading the same StreamName window family, RegSeqRat source row, DyadicRatCore endpoint and radius ledger, ModulusOfConvergence rate row, and LocatedReal enclosure row.
\end{theorem}
\begin{proof}
Start with \autoref{thm:regular-located-cauchy-real-namecert-obligations}. It places the finite window row $S$ before the regular source row $Q$ and places the dyadic ledger $D$ before the convergence modulus $M$ and located enclosure $L$.

The Real seal is therefore not an independent coordinate. The row $E$ is reached after $S,Q,D,M,L$ are displayed, so a consumer omitting any of those rows has not followed the carrier route.

Finally read the structural rows. The rows $H,C,P,N$ preserve, replay, source, and name the same route; they do not add a second route to $\RealUp$. Thus the terminal seal factors through the displayed finite certificate path.
\end{proof}

\begin{theorem}[Regular located Cauchy real modulus-location factorization]
\label{thm:regular-located-cauchy-real-modulus-location-factorization}
For every accepted $\RegularLocatedCauchyRealUp$ packet $R=(S,Q,D,M,L,E,H,C,P,N)$, every locatedness read factors through the common finite data
$$
S,\quad Q,\quad D,\quad M
$$
before it reaches $L$, and every convergence-modulus read uses the same $S,Q,D$ rows before it reaches $M$. Hence the modulus and locatedness surfaces share the StreamName windows, RegSeqRat source, and DyadicRatCore endpoint and radius ledger rather than presenting two unrelated certificates.
\end{theorem}
\begin{proof}
Use the carrier definition. The row $M$ is a rate row over the windows, source, endpoints, and radii already named by $S,Q,D$; the row $L$ is a located enclosure over the same displayed source and dyadic ledger, with the rate row fixing the relevant tail threshold.

Now compare the two reads. The convergence side stops at $M$ after $S,Q,D$, while the locatedness side continues through $M$ to $L$ on the same finite rows.

The componentwise $\hsame$ and $\Cont$ rows preserve that shared route, and the $\Pkg$ and local $\NameCert$ rows name it. Thus any accepted consumer sees one factored certificate surface, not a separated modulus certificate and a separated location certificate.
\end{proof}

\falsifiablePrediction{An accepted $\RegularLocatedCauchyRealUp$ consumer that reaches a $\RealUp$ seal or a locatedness enclosure without the displayed $\StreamNameUp$ windows, $\RegSeqRatUp$ source, $\DyadicRatCoreUp$ endpoint and radius ledger, and $\ModulusOfConvergenceUp$ rate row refutes the carrier surface.}

\independenceWitness{streamname, regseqrat, dyadicratcore, real, locatedreal, modulusofconvergence: no listed sibling supplies the whole ten-row packet $R=(S,Q,D,M,L,E,H,C,P,N)$, because each sibling contributes only a window, regular-source, dyadic-ledger, Real-seal, located-enclosure, or rate surface while this chapter binds all six analytic faces with transport, replay, provenance, and local naming.}

\closureat{RegularLocatedCauchyRealUp}{obligationStr}[BEDC.Derived.RegularLocatedCauchyRealUp.TasteGate.RegularLocatedCauchyRealTasteGate\_single\_carrier\_alignment]
\begin{closurestatus}{\RegularLocatedCauchyRealUp}
  \constructivestory{A $\RegularLocatedCauchyRealUp$ packet is generated from finite $\StreamNameUp$ windows, a $\RegSeqRatUp$ source row, a $\DyadicRatCoreUp$ endpoint and radius ledger, a $\ModulusOfConvergenceUp$ rate row, a $\LocatedRealUp$ enclosure row, a terminal $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:regular-located-cauchy-real-carrier}, \autoref{thm:regular-located-cauchy-real-namecert-obligations}, \autoref{thm:regular-located-cauchy-real-realup-seal-route}, and \autoref{thm:regular-located-cauchy-real-modulus-location-factorization} seed the regular located Cauchy real-name boundary over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\ModulusOfConvergenceUp$, $\LocatedRealUp$, and $\RealUp$.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RegularLocatedCauchyRealUp.TasteGate.RegularLocatedCauchyRealTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Dedekind construction of $\RealUp$, quotient equality, trichotomy, open-cover compactness, countable choice, completeness, or completed metric-space points.}
  \upgradepath{Scoped closure requires binding the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\ModulusOfConvergenceUp$, $\LocatedRealUp$, and $\RealUp$ dependency scope as the public route for every accepted regular located Cauchy real-name read.}
\end{closurestatus}
