\chapter{A Concrete Naming Certificate for $\StolzCesaroUp$}
\label{ch:concrete-instances-stolz-cesaro-namecert}
\origin{human}

Following Stolz and Cesaro, and in the Bishop--Bridges style of constructive convergence, the $\StolzCesaroUp$ packet records the finite certificate surface for a quotient-tail convergence argument before it reaches a Real-completion consumer. It sits over the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic estimate ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the convergence schedule surface of \autoref{ch:concrete-instances-cauchy-convergence-modulus-namecert}, the monotone source discipline of \autoref{ch:concrete-instances-monotone-subsequence-namecert}, and the real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names the displayed finite route used by the convergence certificate; it does not import a host theorem about all real sequences.

\begin{definition}[Stolz-Cesaro finite convergence carrier]
\label{def:stolz-cesaro-carrier}
A $\StolzCesaroUp$ carrier is a finite $\BHist$ packet
$$
Z=(A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the finite $\StreamNameUp$ window family for the numerator sequence rows inspected by the packet.
\item $B$ is the finite $\StreamNameUp$ window family for the denominator sequence rows inspected by the same tail schedule.
\item $\Delta A$ is the numerator difference row, recording the displayed differences used by the ratio classifier.
\item $\Delta B$ is the positive denominator step row, recording the displayed denominator steps and their positivity evidence.
\item $D$ is the $\DyadicRatCoreUp$ ratio-difference ledger for the inspected step quotients and requested tolerances.
\item $T$ is the finite tail-window schedule deciding which inspected windows are admitted for each dyadic tolerance.
\item $Q$ is the $\RegSeqRatUp$ handoff row reached from $A,B,\Delta A,\Delta B,D,T$.
\item $E$ is the $\RealUp$ seal-facing row reached only after the finite stream, difference, dyadic, schedule, and regular-rational rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the two stream families, difference rows, positivity row, dyadic ledger, schedule, regular-rational handoff, Real seal-facing row, continuation, provenance, and local naming rows.
\item $C$ records the displayed $\Cont$ replay from each quotient-tail request through $A,B,\Delta A,\Delta B,D,T,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\StolzCesaroUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyConvergenceModulusUp$, $\MonotoneSubsequenceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\StolzCesaroUp}$ row.
\end{enumerate}
The carrier has no coordinate for host limits, quotient streams, choice-selected subsequences, ambient completeness, real-closed field reasoning, or an unbounded sequence oracle.
\end{definition}

\begin{theorem}[Stolz-Cesaro NameCert obligation sketch]
\label{thm:stolz-cesaro-namecert-obligation-sketch}
The seed $\NameCert_{\StolzCesaroUp}$ surface for \autoref{def:stolz-cesaro-carrier} consists of the following five obligation rows:
\begin{enumerate}
\item carrier admission: the accepted object is exactly the displayed packet $Z=(A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N)$;
\item denominator-step positivity: every admitted quotient-tail request reads the positive denominator step row $\Delta B$ before any ratio-difference row is classified;
\item ratio-difference classifier transport: the dyadic ratio-difference ledger $D$ is stable under the componentwise $\hsame$ transport $H$ and the displayed $\Cont$ replay $C$;
\item Cauchy-convergence handoff: the tail-window schedule $T$ and dyadic ledger $D$ supply the finite route consumed by the $\CauchyConvergenceModulusUp$-style handoff before $Q$ is read;
\item non-escape: no accepted consumer obtains a host limit, quotient stream, choice-selected subsequence, ambient completeness witness, or detached real-seal row outside $A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N$.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.StolzCesaroUp.StolzCesaroTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier tuple $Z=(A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N)$. Carrier admission is exactly the assertion that the local $\NameCert_{\StolzCesaroUp}$ row names this displayed finite packet.

The denominator side is read before the ratio classifier. The row $\Delta B$ supplies the positive difference evidence used to admit a quotient-tail request, and the dyadic row $D$ records only the ratio-difference estimates over the displayed numerator and denominator step rows.

Now transport the classifier. The componentwise $\hsame$ row $H$ and continuation replay $C$ preserve the same stream windows, difference rows, positivity row, and dyadic ledger, so the classifier cannot move to a hidden quotient stream or host equality source.

Finally read the completion-facing handoff. The schedule $T$ and ledger $D$ feed the regular-rational row $Q$, and the Real seal-facing row $E$ is reached only after that finite handoff has been displayed. The excluded objects have no coordinate in $Z$, so the five listed rows exhaust the seed obligation surface.
\end{proof}

\begin{theorem}[Stolz-Cesaro finite tail handoff]
\label{thm:stolz-cesaro-finite-tail-handoff}
For every accepted $\StolzCesaroUp$ packet $Z=(A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N)$ and every displayed quotient-tail request, the Real-completion-facing read factors through the finite route
$$
A,B\longmapsto \Delta A,\Delta B\longmapsto D\longmapsto T\longmapsto Q\longmapsto E\longmapsto(H,C,P,N).
$$
No consumer can read the $\RegSeqRatUp$ handoff or the $\RealUp$ seal-facing row without also reading the displayed stream windows, numerator difference row, positive denominator step row, dyadic ratio-difference ledger, and finite tail-window schedule.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:stolz-cesaro-namecert-obligation-sketch}. Its carrier-admission and positivity rows place $A,B,\Delta A,\Delta B$ before any ratio-difference classifier can be used.

The classifier then passes through the dyadic and schedule rows. The row $D$ records the finite ratio-difference estimates, while $T$ records which tail windows are admitted for the requested tolerance.

The completion-facing rows are downstream of that finite route. The regular-rational handoff $Q$ and Real seal-facing row $E$ are reached only after the scheduled dyadic estimate surface is displayed, and $H,C,P,N$ preserve and name that same route. Hence the read cannot escape into host limits, quotient streams, choice-selected subsequences, or ambient completeness.
\end{proof}

\begin{definition}[Stolz-Cesaro finite-difference subcarrier]
\label{def:stolz-cesaro-finite-difference-carrier}
The finite-difference subcarrier of an accepted $\StolzCesaroUp$ packet is the displayed six-row packet
$$
Z_{\Delta}=(A,B,\Delta A,\Delta B,D,T)
$$
cut out of \autoref{def:stolz-cesaro-carrier}. Its rows expose only the numerator $\StreamNameUp$ windows, denominator $\StreamNameUp$ windows, displayed numerator differences, positive denominator-step differences, $\DyadicRatCoreUp$ quotient-estimate ledger, and finite tail schedules. The subcarrier carries no $\RegSeqRatUp$ handoff row, no $\RealUp$ seal-facing row, no host limit, no quotient stream, and no ambient completeness witness.
\end{definition}

\begin{theorem}[Stolz-Cesaro finite-difference NameCert obligations]
\label{thm:stolz-cesaro-namecert-obligations}
For every accepted $\StolzCesaroUp$ packet $Z=(A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N)$, the subcarrier $Z_{\Delta}=(A,B,\Delta A,\Delta B,D,T)$ of \autoref{def:stolz-cesaro-finite-difference-carrier} carries the complete finite $\NameCert_{\StolzCesaroUp}$ surface consumed before any completion-facing route is exposed:
\begin{enumerate}
\item carrier admission identifies $Z_{\Delta}$ as the only finite-difference source admitted from the ambient packet $Z$;
\item denominator positivity is read from $\Delta B$ before any quotient estimate in $D$ is classified;
\item dyadic ratio transport in $D$ is stable under the componentwise $\hsame$ row $H$;
\item the finite schedule $T$ names the inspected tail windows used by every tolerance request;
\item the $\RegSeqRatUp$ handoff $Q$ may be read only after $A,B,\Delta A,\Delta B,D,T$ have all been displayed;
\item the $\RealUp$ seal-facing row $E$ is a terminal readback from $Q$ and cannot expose a separate real-completion witness;
\item $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and the local naming row $N$ preserve the same displayed subcarrier route.
\end{enumerate}
\end{theorem}
\begin{proof}
Start from the carrier admission in \autoref{thm:stolz-cesaro-namecert-obligation-sketch}. Projection to the six displayed coordinates gives the finite-difference packet $Z_{\Delta}$, and the excluded coordinates show that no host quotient stream or completion witness is part of this subcarrier.

The denominator and ratio rows are then forced locally. The positive denominator-step evidence lives in $\Delta B$, while $D$ records dyadic quotient estimates over the displayed numerator and denominator windows, so every ratio read factors through the $\StreamNameUp$ and $\DyadicRatCoreUp$ surfaces already named in the packet.

Next apply \autoref{thm:stolz-cesaro-finite-tail-handoff}. It places the finite schedule $T$ before the regular-rational handoff $Q$, and places the Real seal-facing row $E$ after $Q$.

Finally replay the structural rows. The componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert_{\StolzCesaroUp}$ row $N$ preserve the same $A,B,\Delta A,\Delta B,D,T$ route through the sibling surfaces $\RegSeqRatUp$, $\CauchyConvergenceModulusUp$, $\MonotoneSubsequenceUp$, and $\RealUp$.
\end{proof}

\begin{theorem}[Stolz-Cesaro Cauchy tail handoff]
\label{thm:stolz-cesaro-cauchy-tail-handoff}
Every completion-facing read from an accepted $\StolzCesaroUp$ packet factors through the finite-difference subcarrier
$$
Z_{\Delta}=(A,B,\Delta A,\Delta B,D,T)
$$
before any $\RegSeqRatUp$ handoff or $\RealUp$ seal-facing row is exposed. Equivalently, a read of $Q$ or $E$ is accepted only as the continuation of the displayed route from $\StreamNameUp$ windows through $\DyadicRatCoreUp$ quotient estimates and the $\CauchyConvergenceModulusUp$ tail schedule; it is rejected when it bypasses $A$, $B$, $\Delta A$, $\Delta B$, $D$, or $T$.
\end{theorem}
\begin{proof}
Use \autoref{thm:stolz-cesaro-finite-tail-handoff} to order the completion-facing route. That theorem already places $A,B,\Delta A,\Delta B,D,T$ before $Q$ and $E$.

Now identify this ordered prefix with \autoref{def:stolz-cesaro-finite-difference-carrier}. The prefix is exactly $Z_{\Delta}$, so the Cauchy-modulus read has no access to a separate numerator stream, denominator stream, denominator positivity proof, quotient estimate ledger, or tail schedule.

It remains to account for stability under accepted replay. By \autoref{thm:stolz-cesaro-namecert-obligations}, $\hsame$, $\Cont$, $\Pkg$, and local naming preserve the same finite-difference route, while the sibling $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyConvergenceModulusUp$, $\MonotoneSubsequenceUp$, and $\RealUp$ surfaces supply only their displayed rows. Thus every accepted completion-facing read is mediated by $Z_{\Delta}$ before $Q$ or $E$ becomes visible.
\end{proof}

\begin{theorem}[Stolz-Cesaro RegSeqRat handoff]\label{thm:stolz-cesaro-regseqrat-handoff}
For every accepted $\StolzCesaroUp$ packet $Z=(A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N)$, an accepted read of the row $Q$ is exactly the $\RegSeqRatUp$ handoff induced by the finite-difference subcarrier
$$
Z_{\Delta}=(A,B,\Delta A,\Delta B,D,T).
$$
Conversely, any accepted finite-difference packet exposing $Z_{\Delta}$ together with the displayed transport $H$, replay $C$, provenance $P$, and local name $N$ repacks as the same $Q$ handoff, and cannot supply a host limit, quotient stream, choice-selected subsequence, ambient completeness witness, or detached $\RealUp$ seal.
\end{theorem}
\begin{proof}
Start with an accepted read of $Q$. By \autoref{thm:stolz-cesaro-cauchy-tail-handoff}, that read is admitted only after the displayed route through $A,B,\Delta A,\Delta B,D,T$ has been exposed, so the source of $Q$ is the finite-difference subcarrier $Z_{\Delta}$.

The exact obligation surface is supplied by \autoref{thm:stolz-cesaro-namecert-obligations}. It identifies carrier admission, denominator positivity, dyadic ratio transport, the tail schedule, $\Cont$ replay, $\Pkg$ provenance, and local naming as the rows that preserve the finite-difference route before $Q$ is read.

For the converse, begin with an accepted finite-difference packet exposing $Z_{\Delta}$ and the structural rows $H,C,P,N$. The same obligation theorem preserves the route under displayed transport and replay, while \autoref{thm:stolz-cesaro-cauchy-tail-handoff} places the $\RegSeqRatUp$ row immediately after that route and before any $\RealUp$ seal-facing row.

Thus the repacked packet reaches exactly the same $Q$ handoff. The excluded host limit, quotient stream, choice-selected subsequence, ambient-completeness, and detached-seal objects have no coordinate in $Z_{\Delta}$ or in the structural rows that name and replay it.
\end{proof}

\falsifiablePrediction{An accepted $\StolzCesaroUp$ consumer that reaches a $\RegSeqRatUp$ handoff or $\RealUp$ seal-facing row without the displayed numerator windows, denominator windows, numerator differences, positive denominator steps, dyadic ratio-difference ledger, and finite tail-window schedule refutes the carrier surface.}

\independenceWitness{streamname, regseqrat, dyadicratcore, cauchyconvergencemodulus, monotonesubsequence, real: no listed sibling supplies the whole twelve-row packet $Z=(A,B,\Delta A,\Delta B,D,T,Q,E,H,C,P,N)$, because each sibling contributes only a stream, regular-rational, dyadic, convergence-schedule, monotone-source, or real-seal surface while this chapter binds the quotient-tail certificate with transport, replay, provenance, and local naming.}

\begin{closurestatus}{\StolzCesaroUp}
  \constructivestory{A $\StolzCesaroUp$ packet is generated from finite numerator and denominator stream windows, numerator difference rows, positive denominator step rows, dyadic ratio-difference estimates, finite tail-window schedules, a RegSeqRat handoff, a Real seal-facing row, componentwise hsame transports, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:stolz-cesaro-carrier}, \autoref{thm:stolz-cesaro-namecert-obligation-sketch}, and \autoref{thm:stolz-cesaro-finite-tail-handoff} seed the finite quotient-tail convergence certificate over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyConvergenceModulusUp$, $\MonotoneSubsequenceUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim the full classical Stolz-Cesaro theorem as an imported real-analysis principle, host limits, quotient streams, choice-selected subsequences, ambient completeness, or a Lean theorem.}
  \upgradepath{A formal route can encode the twelve-row carrier and prove the NameCert obligation sketch and finite tail handoff theorem.}
\end{closurestatus}
