\chapter{A Concrete Naming Certificate for $\RegularCauchyReciprocalUp$}
\label{ch:concrete-instances-regular-cauchy-reciprocal-namecert}
\origin{human}

Bishop and Bridges-style constructive reciprocal data begin from a regular Cauchy rational name together with a displayed apartness window that keeps the inspected tail away from zero. The $\RegularCauchyReciprocalUp$ packet names the finite interface needed to read that reciprocal surface. It refines the budget-only surface of \autoref{ch:concrete-instances-cauchyinversebudget-namecert} by binding the $\RegSeqRatUp$ source of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic endpoint and radius arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert} into one local NameCert carrier. The chapter records only the finite reciprocal-read surface; it does not construct a total reciprocal operation on $\RealUp$.

\begin{definition}[Regular Cauchy reciprocal carrier]
\label{def:regular-cauchy-reciprocal-carrier}
A $\RegularCauchyReciprocalUp$ carrier is a finite $\BHist$ packet
$$
R=(Q,A,M,W,D,B,T,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the accepted $\RegSeqRatUp$ source row whose regular rational entries are being inspected.
\item $A$ is the apartness-window row displaying a rational lower bound that keeps the inspected tail of $Q$ away from zero.
\item $M$ is the finite modulus row selecting the precision at which the reciprocal read is requested.
\item $W$ is the finite $\StreamNameUp$ window opened from $Q$ under $A$ and $M$.
\item $D$ is the $\DyadicRatCoreUp$ endpoint, radius, and comparison ledger read from $W$.
\item $B$ is the sibling $\CauchyInverseBudgetUp$ row that records the reciprocal-window budget over the same $Q,A,M,W,D$ rows.
\item $T$ is the regular rational readback row naming the reciprocal candidate as a $\RegSeqRatUp$ surface.
\item $E$ is the terminal $\RealUp$ seal row reached only after the displayed source, apartness, modulus, window, dyadic, budget, and readback rows have been consumed.
\item $H$ records componentwise $\hsame$ transport for $Q,A,M,W,D,B,T,E,C,P,N$.
\item $C$ records the displayed $\Cont$ replay for source inspection, apartness exposure, finite-window selection, dyadic reciprocal arithmetic, budget handoff, regular readback, and Real seal handoff.
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\CauchyInverseBudgetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyReciprocalUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through the displayed rows $Q,A,M,W,D,B,T,E,H,C,P,N$.
\end{definition}

\begin{theorem}[Regular Cauchy reciprocal apartness window]
\label{thm:regular-cauchy-reciprocal-apartness-window}
Every accepted $\RegularCauchyReciprocalUp$ carrier exposes the apartness row $A$ before any reciprocal dyadic row $D$, budget row $B$, regular readback row $T$, or $\RealUp$ seal row $E$ can be consumed. A route that omits $A$ remains a boundary attempt and cannot export a reciprocal candidate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-reciprocal-carrier}. The source-side rows are $Q,A,M,W$, and the reciprocal-facing rows begin only after the apartness and modulus rows have selected a finite window.

The dyadic ledger $D$ reads endpoint, radius, and comparison data from $W$. Since the reciprocal denominator is controlled by the displayed lower bound in $A$, the dyadic reciprocal row has no carrier route that bypasses $A$.

The budget row $B$, readback row $T$, and seal row $E$ are downstream of that dyadic row. Therefore omitting $A$ leaves no displayed route from the source to a reciprocal candidate; the local classifier records such a route as boundary evidence.
\end{proof}

\begin{theorem}[Regular Cauchy reciprocal readback route]
\label{thm:regular-cauchy-reciprocal-readback-route}
For every accepted $\RegularCauchyReciprocalUp$ carrier $R=(Q,A,M,W,D,B,T,E,H,C,P,N)$, the reciprocal readback row $T$ factors through
$$
Q\longmapsto A\longmapsto M\longmapsto W\longmapsto D\longmapsto B\longmapsto T.
$$
The terminal $\RealUp$ seal $E$ is reached only after this finite route has been displayed.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyReciprocalUp.TasteGate.RegularCauchyReciprocalTasteGate\_single\_carrier\_alignment}
\begin{proof}
Begin with the apartness-window theorem. It places $A$ before any dyadic reciprocal arithmetic, so the route to $T$ cannot start from $Q$ alone.

Next open the finite window row $W$ by using the modulus row $M$. The dyadic ledger $D$ is a read of that window, and the sibling budget row $B$ is the same reciprocal-window discipline named by \autoref{ch:concrete-instances-cauchyinversebudget-namecert}.

Finally project $T$ and then $E$ from the carrier. The readback row names the reciprocal candidate as regular rational data, while the seal row is terminal and adds no second route around the displayed finite chain.
\end{proof}

\begin{theorem}[Regular Cauchy reciprocal NameCert obligations]
\label{thm:regular-cauchy-reciprocal-namecert-obligations}
The seed $\NameCert_{\RegularCauchyReciprocalUp}$ surface consists exactly of carrier exposure for $R=(Q,A,M,W,D,B,T,E,H,C,P,N)$, apartness-window exposure through $A$, finite-window exposure through $W$, dyadic reciprocal arithmetic through $D$, sibling budget exposure through $B$, regular readback through $T$, terminal $\RealUp$ sealing through $E$, componentwise transport through $H$, displayed continuation replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier exposure is \autoref{def:regular-cauchy-reciprocal-carrier}. It supplies the full row list and states that the classifier reads only those rows.

The analytic route is given by \autoref{thm:regular-cauchy-reciprocal-apartness-window} and \autoref{thm:regular-cauchy-reciprocal-readback-route}. Together they force every reciprocal read to pass through the source, apartness, modulus, finite window, dyadic arithmetic, and sibling budget rows before reaching $T$ and $E$.

The structural rows $H,C,P,N$ transport, replay, source, and name the same finite packet. Since none of these rows contains a total reciprocal, quotient stream equality, selected limit, trichotomy decision, or ambient completeness principle, the displayed obligations exhaust the local NameCert surface.
\end{proof}

\falsifiablePrediction{An accepted $\RegularCauchyReciprocalUp$ consumer that reaches a reciprocal readback row or a $\RealUp$ seal without the displayed $\RegSeqRatUp$ source, apartness row, finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, and $\CauchyInverseBudgetUp$ row refutes the carrier surface.}

\independenceWitness{regseqrat, streamname, dyadicratcore, cauchyinversebudget, real: no listed sibling supplies the whole twelve-row packet $R=(Q,A,M,W,D,B,T,E,H,C,P,N)$, because each sibling contributes only a regular source, finite window, dyadic ledger, reciprocal budget, or Real seal while this chapter binds all five analytic faces with transport, replay, provenance, and local naming.}

\begin{closurestatus}{\RegularCauchyReciprocalUp}
  \constructivestory{A $\RegularCauchyReciprocalUp$ packet is generated from a $\RegSeqRatUp$ source, an apartness-window row, a finite modulus row, a $\StreamNameUp$ window, a $\DyadicRatCoreUp$ ledger, a $\CauchyInverseBudgetUp$ budget row, a reciprocal readback row, a terminal $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-reciprocal-carrier}, \autoref{thm:regular-cauchy-reciprocal-apartness-window}, \autoref{thm:regular-cauchy-reciprocal-readback-route}, and \autoref{thm:regular-cauchy-reciprocal-namecert-obligations} seed the reciprocal NameCert boundary for regular Cauchy names over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\CauchyInverseBudgetUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a total reciprocal, trichotomy, quotient stream equality, selected limits, ambient real completeness, or a Lean theorem.}
  \upgradepath{A formal route can encode the twelve-row carrier and prove the apartness-window, readback-route, and NameCert-obligation theorems.}
\end{closurestatus}
