\chapter{A Concrete Naming Certificate for $\StolzCesaroUp$}
\label{ch:concrete-instances-stolz-cesaro-namecert}
\origin{human}

Following classical presentations of the Stolz--Cesaro theorem in sequence theory, the $\StolzCesaroUp$ packet records the finite ratio-difference comparison route as constructive BEDC NameCert data. It sits after the sequence naming surface of \autoref{ch:concrete-instances-seq-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The packet compares numerator differences against strictly growing denominator differences through displayed windows; it does not import host limits, quotient streams, trichotomy, or ambient completeness.

\begin{definition}[Stolz-Cesaro carrier]
\label{def:stolz-cesaro-carrier}
A $\StolzCesaroUp$ carrier is a finite $\BHist$ packet
$$
J=(A,B,\Delta A,\Delta B,G,W,Q,L,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the numerator sequence row, displayed only through the finite inspected windows selected for the packet.
\item $B$ is the denominator sequence row, displayed through the same inspected index schedule and carrying no host sequence equality coordinate.
\item $\Delta A$ is the finite numerator-difference row, listing the observed differences $A_{k+1}-A_k$ on the scheduled adjacent pairs.
\item $\Delta B$ is the finite denominator-difference row, listing the observed positive differences $B_{k+1}-B_k$ on the same adjacent pairs.
\item $G$ is the strict-growth ledger for the denominator row: every scheduled $\Delta B$ entry is a displayed positive rational readback, and the cumulative denominator windows are increasing on the inspected tail.
\item $W$ is the finite ratio-window schedule, recording the adjacent pairs and tolerances used to inspect the ratios $\Delta A/\Delta B$.
\item $Q$ is the $\RegSeqRatUp$ readback row for the scheduled ratio windows and their dyadic tolerances.
\item $L$ is the displayed candidate ratio-limit $\RealUp$ row, read only through its finite $\StreamNameUp$ windows and $\RegSeqRatUp$ observations.
\item $R$ is the terminal $\RealUp$ seal for the quotient sequence comparison, consumed only after the $W,Q,L$ route has been displayed.
\item $H$ stores componentwise $\hsame$ transport for the numerator rows, denominator rows, difference rows, strict-growth ledger, ratio windows, regular rational readbacks, real seals, continuation routes, provenance, and local naming.
\item $C$ stores displayed $\Cont$ replay from sequence rows to adjacent differences, from positive denominator differences to ratio windows, from ratio windows to regular rational readback, and from the ratio-limit row to the terminal real seal.
\item $P$ is the $\Pkg$ provenance over $\StolzCesaroUp$, $\SeqUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and the local ratio-difference classifier.
\item $N$ is the local $\NameCert_{\StolzCesaroUp}$ row.
\end{enumerate}
The carrier classifier reads only
$$
A,B,\Delta A,\Delta B,G,W,Q,L,R,H,C,P,N.
$$
It has no coordinate for host sequence limits, quotient stream equality, trichotomy, ambient completeness, countable choice, or an uninspected infinite ratio object.
\end{definition}

\begin{theorem}[Stolz-Cesaro NameCert obligations]
\label{thm:stolz-cesaro-namecert-obligations}
For every accepted $\StolzCesaroUp$ carrier $J=(A,B,\Delta A,\Delta B,G,W,Q,L,R,H,C,P,N)$, the local $\NameCert_{\StolzCesaroUp}$ surface consists exactly of five finite rows: carrier admission, strict denominator-growth admission, finite ratio-window classification, componentwise transport and continuation replay, and package provenance with real-seal non-escape for the displayed rows of \autoref{def:stolz-cesaro-carrier}.
\end{theorem}
\begin{proof}
Carrier admission is the tuple of \autoref{def:stolz-cesaro-carrier}. The numerator and denominator sequence rows are not read as host functions; the packet exposes only the scheduled windows and adjacent-pair differences named by $A,B,\Delta A,\Delta B$.

Strict denominator-growth admission is the row $G$. It certifies that the scheduled denominator differences in $\Delta B$ are positive rational readbacks, so each displayed ratio window has a denominator side accepted before the quotient comparison is formed.

Finite ratio-window classification is the row $W$ together with the $\RegSeqRatUp$ readback row $Q$ and the candidate ratio-limit row $L$. The classifier never ranges over an ambient infinite stream; it reads only the adjacent pairs and tolerances listed in the packet.

Transport and replay are exactly the rows $H$ and $C$. They preserve the same numerator, denominator, difference, growth, window, readback, and real-seal coordinates under componentwise $\hsame$ and displayed $\Cont$ routes.

Finally, $P$ records package provenance and $N$ records the local naming row. Since the real seal $R$ is consumed only after the finite $W,Q,L$ route is present, the certificate cannot export host sequence limits, quotient stream equality, trichotomy, ambient completeness, countable choice, or an uninspected infinite ratio object.
\end{proof}

\begin{theorem}[Stolz-Cesaro RealUp handoff]
\label{thm:stolz-cesaro-real-handoff}
For every accepted $\StolzCesaroUp$ carrier, a displayed convergence read of the ratio-difference windows hands off to $\RealUp$ only through
$$
A,B\longmapsto \Delta A,\Delta B,G\longmapsto W\longmapsto Q\longmapsto L\longmapsto R,
$$
together with $H,C,P,N$. Thus the BEDC packet supplies a constructive RealUp comparison route for the Stolz--Cesaro conclusion without importing a host limit theorem or an ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with the sequence rows $A$ and $B$. The continuation row $C$ exposes adjacent-pair differences $\Delta A$ and $\Delta B$ only at the scheduled indices, so the route starts from finite sequence data rather than from a host sequence object.

The strict-growth ledger $G$ is read before ratio formation. Its positive denominator-difference entries make the scheduled quotient windows legitimate finite observations, and those observations are exactly the windows listed by $W$.

The regular rational readback row $Q$ classifies the scheduled quotient observations against the displayed candidate row $L$. This is the constructive comparison step: each tolerance check is a finite $\RegSeqRatUp$ readback, not a statement about a quotient stream in the meta-theory.

The terminal seal $R$ is reached only after $Q$ and $L$ have been displayed. Componentwise transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$ preserve that order, so the handoff to $\RealUp$ remains inside the packet.
\end{proof}

\falsifiablePrediction{Every $\StolzCesaroUp$ RealUp handoff factors through finite numerator and denominator difference rows, a strict positive denominator-difference ledger, ratio-window scheduling, RegSeqRat readback, a displayed ratio-limit row, and the terminal RealUp seal carried by the packet.}

\independenceWitness{seq, regseqrat, real: $\StolzCesaroUp$ is not bijective to any listed sibling because it jointly carries numerator sequence rows, denominator sequence rows, adjacent difference rows, strict denominator-growth data, finite ratio windows, regular rational readback, a candidate ratio-limit row, a terminal real seal, transport, continuation, provenance, and local naming.}

\closureat{StolzCesaroUp}{seedStr}

\begin{closurestatus}{\StolzCesaroUp}
  \constructivestory{A $\StolzCesaroUp$ packet is generated from numerator and denominator sequence rows, adjacent difference rows, strict positive denominator-difference data, finite ratio-window scheduling, RegSeqRat readback, a displayed ratio-limit RealUp row, a terminal RealUp seal, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:stolz-cesaro-carrier}, \autoref{thm:stolz-cesaro-namecert-obligations}, and \autoref{thm:stolz-cesaro-real-handoff} seed the finite Stolz-Cesaro ratio-difference certificate and its constructive RealUp handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, host sequence limits, quotient stream equality, trichotomy, ambient completeness, countable choice, or an uninspected infinite ratio object.}
  \upgradepath{Obligation closure requires checked carrier admission, strict denominator-growth admission, finite ratio-window classification, componentwise transport and continuation replay, package provenance, and RealUp seal non-escape for BEDC.Derived.StolzCesaroUp.}
\end{closurestatus}
