\chapter{CompactLocatedSubcover NameCert Construction}
\label{ch:concrete-instances-compact-located-subcover-namecert}
\origin{human}

Following Bishop and Bridges, the $\CompactLocatedSubcoverUp$ packet records finite located subcover extraction as displayed BEDC data: a finite family of named located balls is already present, each member has a positive radius row, and the certificate extracts the finite bundle and lower-radius ledger read by compact and uniform consumers. The chapter treats the object as a located finite extraction surface, not as open-cover compactness. It sits between the finite-net compact packets of \autoref{ch:concrete-instances-compact-namecert} and \autoref{ch:concrete-instances-compactmetric-namecert}, the finite positive-radius ledger of \autoref{ch:concrete-instances-finite-lebesgue-number-namecert}, and the downstream modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}.

\begin{definition}[Compact located subcover carrier]
\label{def:compact-located-subcover-carrier}
A $\CompactLocatedSubcoverUp$ carrier is a finite $\BHist$ packet
$$
S=(B,C,R,U,V,L,H,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is a finite $\mathsf{ProbeBundle}$ spine naming the located cover candidates inspected by the packet;
\item $C$ is the center-history ledger assigning to every bundled probe a center $\BHist$ row readable through the compact or compact-metric source;
\item $R$ is the positive $\DyadicRatCoreUp$ radius ledger attached to the bundled candidates;
\item $U$ is the positive $\RationalBallUp$ radius readback for the same centers and dyadic radii;
\item $V$ is the coverage row stating that every compact-source history accepted by the packet is covered by one bundled located ball;
\item $L$ is the lower-radius fold over the finite bundle, producing one positive radius ledger below every displayed radius in $R$ and $U$;
\item $H$ records componentwise $\hsame$ transport for bundle, center, dyadic-radius, rational-ball, coverage, and lower-fold rows;
\item $Q$ records the displayed $\Cont$ routes by which compact, compact-metric, finite-Lebesgue-number, and uniform-modulus consumers inspect the packet;
\item $P$ is the $\Pkg$ provenance over $\CompactLocatedSubcoverUp$, $\CompactUp$, $\CompactMetricUp$, $\FiniteLebesgueNumberUp$, $\UniformModulusUp$, $\DyadicRatCoreUp$, $\RationalBallUp$, $\mathsf{ProbeBundle}$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\CompactLocatedSubcoverUp}$ row.
\end{enumerate}
The carrier exports only the displayed finite located subcover extraction route. It has no coordinate for an arbitrary open family, an ambient compactness theorem, a selected open-cover subfamily, quotient real equality, countable choice, or an external modulus selector.
\end{definition}

\begin{theorem}[CompactLocatedSubcover NameCert obligations]
\label{thm:compact-located-subcover-namecert-obligations}
For an accepted $\CompactLocatedSubcoverUp$ carrier $S=(B,C,R,U,V,L,H,Q,P,N)$, the local $\NameCert_{\CompactLocatedSubcoverUp}$ surface consists of five finite rows: carrier admission for the tuple of \autoref{def:compact-located-subcover-carrier}; located-ball source rows over $B,C,R,U$; coverage rows over $V$; lower-radius fold rows over $L$; and downstream transport, replay, provenance, and naming rows over $H,Q,P,N$.

These five rows are exactly the finite located extraction packet read by compact and compact-metric consumers. No consumer can replace them by open-cover compactness, a host subcover selector, a hidden radius minimum, or a detached analytic compactness principle.
\end{theorem}
\begin{proof}
Carrier admission fixes the finite packet and the only rows the classifier may inspect. The bundle and center rows are the displayed located candidates, while the dyadic and rational-ball rows give the positive radii attached to those candidates.

The coverage coordinate $V$ is the finite located subcover assertion. It is already indexed by the $\mathsf{ProbeBundle}$ spine $B$, so a consumer reads a bundled cover row rather than selecting a subfamily from an arbitrary cover.

The fold coordinate $L$ supplies the lower-radius ledger. Since it folds only over the displayed finite bundle and is transported only by $H$, it cannot read a host minimum or an external choice operator.

Finally the rows $Q,P,N$ replay, source, and name the same packet for compact, compact-metric, finite-Lebesgue-number, and uniform-modulus consumers. Thus the five finite rows are the whole local obligation surface.
\end{proof}

\begin{theorem}[CompactLocatedSubcover uniform-modulus handoff]
\label{thm:compact-located-subcover-uniform-modulus-handoff}
Every $\UniformModulusUp$ or $\FiniteLebesgueNumberUp$ consumer of an accepted $\CompactLocatedSubcoverUp$ carrier receives the same finite packet
$$
B,C,R,U,V,L,H,Q,P,N.
$$
The rows $V$ and $L$ respectively supply the located coverage surface and the positive lower-radius ledger. They hand forward to \autoref{ch:concrete-instances-finite-lebesgue-number-namecert} and \autoref{ch:concrete-instances-uniformmodulus-namecert} as finite BEDC rows, not as open-cover compactness, selected subcover choice, or an external modulus.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-located-subcover-carrier}. The compact source contributes only the finite bundle $B$, center ledger $C$, dyadic radius ledger $R$, rational-ball readback $U$, and coverage row $V$.

Read the lower-radius fold $L$ over that same finite bundle. The fold provides one positive radius row below the displayed located-ball radii, which is the radius shape expected by finite-Lebesgue-number and uniform-modulus consumers.

Transport the resulting located coverage and radius rows through $H$, then replay them through $Q$ with provenance and local naming supplied by $P$ and $N$. Because every downstream read is forced through these rows, the handoff cannot invoke arbitrary open covers, chosen subcovers, host minima, countable choice, or detached real-completion data.
\end{proof}

\closureat{CompactLocatedSubcoverUp}{seedStr}

\begin{closurestatus}{\CompactLocatedSubcoverUp}
  \constructivestory{A $\CompactLocatedSubcoverUp$ packet is generated from a finite ProbeBundle of located cover candidates, center histories, positive DyadicRatCore and RationalBall radius rows, coverage rows, a finite lower-radius fold, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-located-subcover-carrier}, \autoref{thm:compact-located-subcover-namecert-obligations}, and \autoref{thm:compact-located-subcover-uniform-modulus-handoff} bind the finite located subcover extraction packet and its radius handoff to finite-Lebesgue-number and uniform-modulus consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, arbitrary cover selection, host compactness, host minima, quotient real equality, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located-ball coverage rows, positive-radius readback, lower-radius fold exactness, and uniform-consumer handoff for BEDC.Derived.CompactLocatedSubcoverUp.}
\end{closurestatus}
