\chapter{A Concrete Naming Certificate for $\LocatedInfimumUp$}
\label{ch:concrete-instances-locatedinfimum-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\LocatedInfimumUp$ packet records greatest-lower-bound data by finite lower-bound ledgers and upper-approximation rows, before any ambient completeness principle for $\RealUp$ is available. It is the lower-bound companion to the $\LocatedSupremumUp$ certificate of \autoref{ch:concrete-instances-locatedsupremum-namecert} and consumes the bounded-family source supplied by \autoref{ch:concrete-instances-boundedrealfamily-namecert}. The carrier therefore gives later interval and bounded-family arguments a finite NameCert target for infimum-shaped reasoning while keeping quotient real equality, trichotomy, countable choice, and host completeness outside the packet.

\begin{definition}[LocatedInfimum carrier]
\label{def:located-infimum-carrier}
A $\LocatedInfimumUp$ carrier is a finite $\BHist$ packet
$$
I=(F,L,G,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the bounded real family row, read through the finite index-window, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and common-bound ledgers of $\BoundedRealFamilyUp$.
\item $L$ is the lower-bound ledger. It records the inspected lower-bound claims and the finite comparison rows that certify each requested member of $F$ above the proposed lower surface.
\item $G$ is the greatest-lower-approximation ledger. For each precision request in the displayed window, it stores a finite family-side witness above the proposed lower surface and below every displayed stronger lower-bound candidate at that precision.
\item $W$ is the $\StreamNameUp$ precision-window row that fixes the finite observations of the family, lower-bound ledger, and greatest-lower-approximation ledger in scope.
\item $R$ is the $\RegSeqRatUp$ handoff row that repacks the windowed observations as regular rational readback data.
\item $E$ is the $\RealUp$ seal row reached only through $F,L,G,W,R$.
\item $H$ records componentwise $\hsame$ transports for the family row, lower-bound ledger, greatest-lower-approximation ledger, precision window, regular handoff, real seal, continuation replay, provenance, and local naming row.
\item $C$ records displayed $\Cont$ routes that replay lower-bound reads, greatest-lower-approximation reads, classifier transport, regular-rational handoff, and real-seal readback.
\item $P$ is the $\Pkg$ provenance over $\LocatedInfimumUp$, $\LocatedSupremumUp$, $\BoundedRealFamilyUp$, $\BishopRealComparisonUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\LocatedInfimumUp}$ row.
\end{enumerate}
The accepted carrier stores no Dedekind cut completion, no arbitrary infimum operator, no quotient real equality test, no trichotomy oracle, no countable-choice functional, and no host-completeness coordinate.
\end{definition}

\begin{theorem}[LocatedInfimum lower-bound obligation]
\label{thm:located-infimum-lower-bound-obligation}
For an accepted packet $I=(F,L,G,W,R,E,H,C,P,N)$, every lower-bound read exposed by the local $\NameCert_{\LocatedInfimumUp}$ row factors through the bounded-family row $F$, the lower-bound ledger $L$, the precision window $W$, the regular-rational handoff $R$, and the $\RealUp$ seal $E$, together with the transport, continuation, provenance, and local naming rows. No lower-bound obligation may invoke Dedekind completeness, an arbitrary infimum operator, quotient real equality, trichotomy, countable choice, or host completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The only family source is $F$, and the only lower-bound source is $L$, so a lower-bound consumer must first inspect the bounded-family row and then one of the displayed comparison entries of $L$.

The precision window $W$ determines which finite observations are admitted. The handoff row $R$ repacks those observations as regular rational data, and the seal $E$ is reached only after this route has been replayed.

The structural rows cannot enlarge the obligation surface. The transports in $H$, continuations in $C$, provenance in $P$, and name row $N$ preserve the displayed route, but none carries a Dedekind completion, arbitrary infimum operator, quotient equality test, trichotomy oracle, countable-choice functional, or host-completeness field.
\end{proof}

\begin{theorem}[LocatedInfimum greatest-lower-bound obligation]
\label{thm:located-infimum-greatest-lower-bound-obligation}
For an accepted packet $I=(F,L,G,W,R,E,H,C,P,N)$, the greatest-lower-bound obligation is exactly the finite demand that each precision row of $W$ receives a displayed witness in $G$ whose readback lies above the proposed lower surface and blocks every displayed stronger lower-bound candidate at that precision. The obligation is local to $F,L,G,W,R,E,H,C,P,N$ and does not assert a global infimum for arbitrary real families.
\end{theorem}
\begin{proof}
Fix a precision row in $W$. By definition of the carrier, $G$ is the only ledger that can answer greatest-lower-approximation requests at that precision.

Read the corresponding $G$ entry. It supplies a finite family-side witness, and the route through $R$ and $E$ gives the regular-rational and real-name readback for the same displayed observation.

The comparison is therefore local: the witness is checked against the lower surface and against the stronger lower-bound candidates that are actually present in the window. Since the packet has no coordinate for arbitrary families or an ambient completeness principle, the row proves only the displayed finite greatest-lower-bound obligation.
\end{proof}

\begin{theorem}[LocatedInfimum classifier stability]
\label{thm:located-infimum-classifier-stability}
Let $I=(F,L,G,W,R,E,H,C,P,N)$ be an accepted $\LocatedInfimumUp$ packet. Replacing any displayed component along the corresponding $\hsame$ transport in $H$ preserves lower-bound reads, greatest-lower-approximation reads, $\RegSeqRatUp$ handoff, $\RealUp$ seal access, continuation replay, provenance, and the local $\NameCert_{\LocatedInfimumUp}$ classifier. Thus the classifier is stable under componentwise BEDC transport.
\end{theorem}
\begin{proof}
Use the transport ledger $H$ component by component. The family row, lower-bound ledger, greatest-lower-approximation ledger, precision window, regular handoff, real seal, continuation row, provenance row, and name row each have their own displayed $\hsame$ transport.

Transport the lower-bound route first. The route still starts at $F$, reads $L$ inside the same window $W$, passes through $R$, and reaches $E$.

Transport the greatest-lower-approximation route next. The row $G$ is moved with the same precision window and the same handoff and seal rows, so the finite witness relation seen by the classifier is unchanged.

Finally replay $C$ and $P$ after transport. They can only replay and source the transported rows, so the local classifier has no new field through which to distinguish transported copies beyond the displayed $\hsame$ data.
\end{proof}

\begin{theorem}[LocatedInfimum ledger exactness]
\label{thm:located-infimum-ledger-exactness}
Every Real-facing observation exported by an accepted $\LocatedInfimumUp$ packet is obtained from one of the displayed rows $F,L,G,W,R,E,H,C,P,N$. In particular, lower-bound, greatest-lower-approximation, handoff, and seal observations are exhausted by the ledger rows, and the packet exports no hidden Dedekind-completeness, arbitrary-infimum, quotient-equality, trichotomy, countable-choice, or host-completeness witness.
\end{theorem}
\begin{proof}
Begin with a Real-facing observation. The carrier contains only one real seal row, namely $E$, and the definition makes $E$ reachable only after the bounded-family row, lower-bound ledger, greatest-lower-approximation ledger, precision window, and regular handoff have been displayed.

Inspect the possible observation classes. Lower-bound reads come from $L$, greatest-lower-approximation reads come from $G$, window restrictions come from $W$, and regular rational readback comes from $R$.

The remaining rows are structural. They transport, replay, source, or name the same finite rows, and therefore cannot create an unlisted completion principle or choice principle. Hence every exported observation is ledger-exact for $F,L,G,W,R,E,H,C,P,N$.
\end{proof}

\begin{closurestatus}{\LocatedInfimumUp}
  \constructivestory{A $\LocatedInfimumUp$ packet is generated from a bounded real family row, a lower-bound ledger, a greatest-lower-approximation ledger, a StreamName precision window, a RegSeqRat handoff, a RealUp seal, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-infimum-carrier}, \autoref{thm:located-infimum-lower-bound-obligation}, \autoref{thm:located-infimum-greatest-lower-bound-obligation}, \autoref{thm:located-infimum-classifier-stability}, and \autoref{thm:located-infimum-ledger-exactness} bind the finite lower-bound and greatest-lower-approximation seed over the L10 Real and Completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Dedekind completeness, arbitrary infima, quotient real equality, trichotomy, countable choice, host completeness, or a standard bridge.}
  \upgradepath{Formal verification can encode carrier admission, lower-bound readback, greatest-lower-approximation witnessing, classifier stability, ledger exactness, handoff stability, and real-seal factorization for BEDC.Derived.LocatedInfimumUp.}
\end{closurestatus}
