\chapter{A Concrete Naming Certificate for $\SeparatedMetricCompletionUp$}
\label{ch:concrete-instances-separated-metric-completion-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis and Bourbaki general topology, the $\SeparatedMetricCompletionUp$ packet isolates the equality-facing boundary where completion names are compared only after their zero-distance classifier has been displayed. It sits between the completion handoff of \autoref{ch:concrete-instances-cauchy-completion-adjunction-namecert} and the located completion boundary of \autoref{ch:concrete-instances-bishoplocatedcompletionboundary-namecert}, while reusing the regular Cauchy equality surface of \autoref{ch:concrete-instances-regularcauchyequivalence-namecert} and the null-tail classifier of \autoref{ch:concrete-instances-nullsequence-namecert}. The chapter records a separated classifier boundary, not a quotient completion, selected limit, ambient completeness theorem, or host-level equality principle.

\begin{definition}[Separated metric completion carrier]
\label{def:separated-metric-completion-carrier}
A $\SeparatedMetricCompletionUp$ carrier is a finite $\BHist$ packet
$$
S=(M,C,Q,Z,R,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source metric and Cauchy-observation row, including the finite distance windows and Cauchy rows accepted before the completion seal is read.
\item $C$ is the completion handoff row from the source Cauchy data into the completion surface displayed by $\CauchyCompletionAdjunctionUp$.
\item $Q$ is the equality-facing completion-name row. It exposes compared completion names only as rows awaiting a classifier, not as quotient classes or selected limits.
\item $Z$ is the zero-distance classifier row, displayed either as $\RegularCauchyEquivalenceUp$ evidence between regular Cauchy representatives or as $\NullSequenceUp$ evidence for the difference-tail route.
\item $R$ is the $\RealUp$ seal row read after $Z$, with no direct equality read from the seal before the classifier has been exposed.
\item $H$ records the componentwise $\hsame$ transport for $M,C,Q,Z,R$ and the matching $\Cont$ replay for any consumer that reads a completion name.
\item $T$ is the separation transport row asserting that equality-facing consumers may transport along $Q$ only through the displayed classifier $Z$ before reaching $R$.
\item $P$ is the $\Pkg$ provenance over $\MetricUp$, $\CauchyCompletionAdjunctionUp$, $\BishopLocatedCompletionBoundaryUp$, $\RegularCauchyEquivalenceUp$, $\NullSequenceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SeparatedMetricCompletionUp}$ row.
\end{enumerate}
The carrier contains no quotient-completion constructor, no chosen limit operator, no ambient complete metric space, no countable-choice selector, and no equality of host functions.
\end{definition}

\begin{theorem}[SeparatedMetricCompletion NameCert obligations]
\label{thm:separated-metric-completion-namecert-obligations}
The seed $\NameCert_{\SeparatedMetricCompletionUp}$ surface for \autoref{def:separated-metric-completion-carrier} consists exactly of five finite obligation groups:
\begin{enumerate}
\item carrier exposure: an accepted object exposes only the packet $S=(M,C,Q,Z,R,H,T,P,N)$ and its listed rows;
\item classifier exposure: every equality-facing comparison of completion names must expose the classifier row $Z$ as $\RegularCauchyEquivalenceUp$ or $\NullSequenceUp$ evidence;
\item completion handoff: the source metric and Cauchy data in $M$ reach equality-facing completion names only through the handoff row $C$;
\item zero-distance separation: the consumer-facing equality row $Q$ may be transported to the $\RealUp$ seal $R$ only along the separation transport row $T$ after $Z$ has been displayed;
\item Real-seal nonescape: any public read that reaches $R$ remains inside the $\MetricUp$, $\CauchyCompletionAdjunctionUp$, $\BishopLocatedCompletionBoundaryUp$, $\RegularCauchyEquivalenceUp$, $\NullSequenceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows named by $P$.
\end{enumerate}
Thus the packet binds the separated completion boundary without adding quotient completions, selected limits, ambient completeness, countable choice, or host-level function equality.
\end{theorem}
\begin{proof}
Carrier exposure is projection from the tuple in \autoref{def:separated-metric-completion-carrier}. The rows $M,C,Q,Z,R,H,T,P,N$ are the only named coordinates, so an accepted object has no further completion, quotient, selection, or ambient completeness field to expose.

Classifier exposure follows from the role of $Z$. The equality-facing row $Q$ names compared completion entries, but the only displayed comparison evidence is the regular Cauchy equivalence route or the null-sequence route carried by $Z$.

Completion handoff is read before separation. Source metric and Cauchy rows enter through $M$, pass to completion-facing names through $C$, and only then appear at $Q$ as objects whose comparison still awaits a displayed zero-distance classifier.

For zero-distance separation, the transport row $T$ is the sole bridge from $Q$ through $Z$ to $R$. Consequently a consumer cannot read the $\RealUp$ seal as equality evidence until the corresponding $\RegularCauchyEquivalenceUp$ or $\NullSequenceUp$ row has been displayed.

Real-seal nonescape is the provenance statement. The row $P$ lists the allowed dependencies and contains no quotient completion, selected limit, ambient complete metric space, countable-choice selector, or host-level function equality coordinate. The five groups therefore exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[SeparatedMetricCompletion zero-distance classifier]
\label{thm:separated-metric-completion-zero-distance-classifier}
Let $S=(M,C,Q,Z,R,H,T,P,N)$ be a $\SeparatedMetricCompletionUp$ carrier. Any equality-facing completion consumer certified by $S$ compares completion names only through the displayed $\RegularCauchyEquivalenceUp$ or $\NullSequenceUp$ evidence in $Z$ before reading the $\RealUp$ seal $R$. In particular, if a consumer reaches $R$, its comparison route already factors through the zero-distance classifier named by $Z$ and the separation transport row $T$.
\end{theorem}
\begin{proof}
The consumer can read completion names only through the equality-facing row $Q$. By \autoref{thm:separated-metric-completion-namecert-obligations}, $Q$ has no direct route to the $\RealUp$ seal; it must expose the classifier row $Z$ and then travel along $T$.

The row $Z$ has exactly the two allowed classifier shapes: $\RegularCauchyEquivalenceUp$ evidence for regular Cauchy representatives and $\NullSequenceUp$ evidence for the difference-tail route. Hence every certified equality-facing read that reaches $R$ has already passed through one of these displayed zero-distance witnesses.
\end{proof}

\begin{closurestatus}{\SeparatedMetricCompletionUp}
  \constructivestory{A $\SeparatedMetricCompletionUp$ packet is generated from source metric and Cauchy rows, a completion handoff row, equality-facing completion names, a zero-distance classifier, a Real seal, componentwise hsame transport, Cont replay, separation transport, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:separated-metric-completion-carrier}, \autoref{thm:separated-metric-completion-namecert-obligations}, and \autoref{thm:separated-metric-completion-zero-distance-classifier} bind the separated classifier boundary for L10 completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient completions, selected limits, ambient completeness, countable choice, host-level function equality, or bridge checking.}
  \upgradepath{A formal route can encode the nine-row carrier and prove carrier exposure, classifier exposure, completion handoff, zero-distance separation, Real-seal nonescape, and equality-facing consumer factorization through the displayed classifier.}
\end{closurestatus}
