\chapter{A Concrete Naming Certificate for $\RegularCauchyRatioTestUp$}
\label{ch:concrete-instances-regular-cauchy-ratio-test-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\RegularCauchyRatioTestUp$ packet records the finite ratio-bound test that turns a displayed geometric tail estimate into a regular Cauchy source row before the Real-facing route is consumed. It sits over the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the comparison handoff of \autoref{ch:concrete-instances-regular-cauchy-comparison-test-namecert}, and the partial-sum ledger of \autoref{ch:concrete-instances-series-namecert}. The packet is a constructive ratio test for regular Cauchy tails; it is not a quotient of streams, a selected infinite tail, a host real norm, countable choice, or an ambient completeness theorem.

\begin{definition}[Regular Cauchy ratio test carrier]
\label{def:regular-cauchy-ratio-test-carrier}
A $\RegularCauchyRatioTestUp$ carrier is a finite $\BHist$ packet
$$
T=(A,R,M,W,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the source row for the series or tail family whose consecutive finite terms are inspected.
\item $R$ is the ratio-bound row, displaying a dyadic bound strictly inside the unit tolerance scale together with the index after which the bound is claimed.
\item $M$ is the modulus row assigning each displayed precision request a finite threshold beyond the ratio-bound index.
\item $W$ is the finite $\StreamNameUp$ window family on which the source row, ratio-bound row, modulus row, and downstream partial-sum rows are read.
\item $D$ is the dyadic domination ledger that unfolds the finite geometric tail estimate from the ratio row and records the comparison majorant consumed by $\RegularCauchyComparisonTestUp$.
\item $H$ records componentwise $\hsame$ transport for the source row, ratio-bound row, modulus, finite windows, dyadic domination ledger, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a precision request through $R$ and $M$ to the windows in $W$, then through $D$ to the comparison-test handoff and the downstream $\RegSeqRatUp$ row.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyRatioTestUp$, $\SeriesUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyComparisonTestUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyRatioTestUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these displayed rows. It has no coordinate for quotient stream equality, an infinite product or power object, a hidden tail selector, a host real absolute value, a selected completed limit, countable choice, or ambient completeness.
\end{definition}

\begin{theorem}[Regular Cauchy ratio test NameCert obligations]
\label{thm:regular-cauchy-ratio-test-namecert-obligations}
For every accepted $\RegularCauchyRatioTestUp$ carrier $T=(A,R,M,W,D,H,C,P,N)$, the local $\NameCert_{\RegularCauchyRatioTestUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed nine-row packet;
\item source exposure for $A$ on the finite windows in $W$;
\item ratio-bound exposure for $R$, including the displayed dyadic bound and the displayed entry index of the tail;
\item modulus readback for $M$, stating that every inspected precision request receives a finite threshold beyond the ratio-bound index;
\item dyadic geometric domination in $D$, producing the finite majorant tail consumed by $\RegularCauchyComparisonTestUp$;
\item transport stability for the source, ratio-bound, modulus, window, and domination rows along the componentwise $\hsame$ rows in $H$;
\item continuation replay, provenance, and local naming for exactly the route recorded by $C,P,N$.
\end{enumerate}
These obligations are finite-row obligations over the sibling surfaces of \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regular-cauchy-comparison-test-namecert}, and \autoref{ch:concrete-instances-series-namecert}.
\end{theorem}
\begin{proof}
Project the carrier $T=(A,R,M,W,D,H,C,P,N)$. The projection exposes exactly the source row, ratio-bound row, modulus row, finite window family, dyadic domination ledger, transport rows, continuation replay, provenance, and local naming row.

For a displayed precision request, read the ratio-bound row $R$ and the modulus row $M$. The ratio row supplies the dyadic bound and the entry index for the tail, while the modulus row supplies a finite threshold beyond that index. Thus the relevant part of the source is inspected only through the windows recorded in $W$.

The dyadic ledger $D$ unfolds the finite geometric domination calculation. Because every factor and tolerance scale is displayed in $D$, the comparison majorant sent to $\RegularCauchyComparisonTestUp$ is a finite row rather than an appeal to an external infinite estimate.

Finally apply the structural rows. The componentwise $\hsame$ entries in $H$ preserve the ratio-bound, threshold, window, and domination data together, while $C,P,N$ only replay, source, and name the displayed route. No omitted coordinate remains from which an additional NameCert obligation could be read.
\end{proof}

\begin{theorem}[Regular Cauchy ratio test comparison handoff]
\label{thm:regular-cauchy-ratio-test-comparison-handoff}
Every accepted $\RegularCauchyRatioTestUp$ carrier hands a regular Cauchy tail to $\RegularCauchyComparisonTestUp$ only through the finite route
$$
A,R,M\longmapsto W,D\longmapsto H,C,P,N.
$$
Consequently a $\RegSeqRatUp$ or $\RealUp$ consumer can use the ratio test only after reading the displayed $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ domination ledger, the ratio-bound row, and the comparison-test handoff row that binds the source to a regular Cauchy majorant.
\end{theorem}
\begin{proof}
Begin with an accepted carrier and fix a displayed precision request. The rows $R$ and $M$ determine a finite threshold beyond the tail entry index, and $W$ is the only family of source windows admitted for that request.

Read the finite domination ledger. The row $D$ expands the ratio-bound data into a dyadic geometric tail estimate on the selected windows and presents that estimate in the same finite comparison format used by $\RegularCauchyComparisonTestUp$.

Transport preserves the handoff. The componentwise $\hsame$ rows in $H$ carry the source row, ratio-bound row, threshold, selected window, and domination certificate together, so a transported carrier cannot alter the comparison-test input while retaining the same displayed packet.

The remaining rows are bookkeeping for the public route. The $\Cont$ replay in $C$, the provenance row $P$, and the local naming row $N$ send the comparison handoff to $\RegSeqRatUp$ and then to Real-facing consumers only through the named sibling rows.
\end{proof}

\begin{theorem}[Regular Cauchy ratio test nonescape]
\label{thm:regular-cauchy-ratio-test-nonescape}
An accepted $\RegularCauchyRatioTestUp$ carrier cannot expose a regular Cauchy conclusion through any route that omits one of $R$, $M$, $W$, or $D$. In particular, the carrier surface rejects any consumer that claims the ratio-test conclusion from the source row $A$ alone, from a host real ratio, from an unrecorded infinite tail estimate, or from ambient completeness.
\end{theorem}
\begin{proof}
Suppose a consumer reads a regular Cauchy conclusion from an accepted carrier. By the NameCert obligation surface of \autoref{thm:regular-cauchy-ratio-test-namecert-obligations}, the only conclusion row exported by the carrier is obtained after reading the ratio-bound row $R$, the modulus row $M$, the finite windows $W$, and the dyadic domination ledger $D$.

If any one of these rows is omitted, the displayed route no longer contains the data needed to form the comparison-test input: without $R$ there is no ratio bound, without $M$ there is no finite threshold, without $W$ there is no admitted source window, and without $D$ there is no dyadic majorant ledger.

The structural rows cannot repair the omission. Transport in $H$ preserves displayed data, and $C,P,N$ replay, source, and name only the displayed route. Therefore any conclusion obtained from a host real ratio, an unrecorded infinite tail estimate, or ambient completeness lies outside the accepted $\RegularCauchyRatioTestUp$ classifier.
\end{proof}

\falsifiablePrediction{An accepted $\RegularCauchyRatioTestUp$ consumer that reads a $\RegSeqRatUp$ or $\RealUp$ conclusion without the displayed ratio-bound row, modulus row, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ domination ledger, and $\RegularCauchyComparisonTestUp$ handoff refutes the carrier surface.}

\independenceWitness{series, regseqrat, streamname, dyadicratcore, regular-cauchy-comparison-test: no listed sibling supplies the whole nine-row packet $T=(A,R,M,W,D,H,C,P,N)$, because each sibling contributes only a source, partial-sum, window, dyadic-ledger, or comparison face while this chapter binds the ratio-bound tail route with transport, replay, provenance, and local naming.}

\closureat{RegularCauchyRatioTestUp}{seedStr}

\begin{closurestatus}{\RegularCauchyRatioTestUp}
  \constructivestory{A $\RegularCauchyRatioTestUp$ packet is generated from a source row, a displayed dyadic ratio-bound row, an explicit modulus row, finite $\StreamNameUp$ windows, dyadic geometric domination rows, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-ratio-test-carrier}, \autoref{thm:regular-cauchy-ratio-test-namecert-obligations}, \autoref{thm:regular-cauchy-ratio-test-comparison-handoff}, and \autoref{thm:regular-cauchy-ratio-test-nonescape} seed the finite ratio-test boundary over $\SeriesUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegularCauchyComparisonTestUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient stream equality, selected completed limits, host real ratios, countable choice, RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the nine-row carrier and prove the finite NameCert obligation surface, comparison handoff theorem, and nonescape theorem.}
\end{closurestatus}
