\chapter{A Concrete Naming Certificate for $\CauchyCondensationUp$}
\label{ch:concrete-instances-cauchycondensation-namecert}
\origin{human}

Following Cauchy and Bishop--Bridges constructive analysis, the $\CauchyCondensationUp$ packet records the dyadic-block test for a monotone nonnegative series as finite BEDC data before any completion-facing consumer may read a real seal. Its source and tail rows are the series surface of \autoref{ch:concrete-instances-series-namecert}; its comparison budget sits beside \autoref{ch:concrete-instances-fastconvergentseries-namecert}; its regular rational readback is the handoff surface of \autoref{ch:concrete-instances-regseqrat-namecert}; and its terminal seal is the $\RealUp$ boundary of \autoref{ch:concrete-instances-real-namecert}. The packet is a constructive condensation certificate; it is not an ambient summability principle, a quotient of infinite series, a selected sum, host real equality, countable choice, trichotomy on arbitrary summands, or RealUp completeness.

\begin{definition}[Cauchy condensation carrier]
\label{def:cauchy-condensation-carrier}
A $\CauchyCondensationUp$ carrier is a finite $\BHist$ packet
$$
K=(S,W,B,L,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the monotone nonnegative $\SeriesUp$ summand source, read only through finite windows and partial-sum rows.
\item $W$ is the summand-window ledger, recording the finite intervals on which monotonicity and nonnegativity are inspected.
\item $B$ is the dyadic block schedule, listing the powers of two, block endpoints, and block lengths consumed by the condensation test.
\item $L$ is the block-sum ledger, storing the original finite block sums and the condensed dyadic terms $2^n a_{2^n}$ over the same schedule.
\item $T$ is the tail-bound row, packaging displayed tolerances, dyadic thresholds, and the domination inequalities that compare original tails with condensed block tails.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the block-sum and tail-bound ledgers.
\item $E$ is the $\RealUp$ seal row attached to the regular rational readback.
\item $H$ records componentwise $\hsame$ transports for the source, windows, schedule, block sums, tail bounds, regular readback, real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ routes from each finite precision request through $W,B,L,T$ to the readback row $R$ and the seal row $E$.
\item $P$ is the $\Pkg$ provenance over $\CauchyCondensationUp$, $\SeriesUp$, $\FastConvergentSeriesUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCondensationUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these eleven rows. It has no coordinate for an infinite choice of blocks, a quotient series equality, a host limit, a selected completed real, a trichotomy oracle, or an ambient completeness theorem.
\end{definition}
\leanchecked{BEDC.Derived.CauchyCondensationUp.CauchyCondensationTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cauchy condensation NameCert obligations]
\label{thm:cauchy-condensation-namecert-obligations}
For every accepted $\CauchyCondensationUp$ carrier $K=(S,W,B,L,T,R,E,H,C,P,N)$, the local $\NameCert_{\CauchyCondensationUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed eleven-row packet;
\item monotone nonnegative source exposure for $S$ through finite $\SeriesUp$ summand and partial-sum windows;
\item window compatibility for $W$, stating that every inspected monotonicity and nonnegativity claim is tied to displayed summand rows;
\item dyadic schedule admission for $B$, with powers of two, endpoints, and block lengths available as finite ledger entries;
\item block-sum formation for $L$, relating each original finite block sum to the condensed term on the same schedule;
\item tail-bound compatibility for $T$, routing finite block domination into the comparison budget consumed by $\FastConvergentSeriesUp$;
\item $\RegSeqRatUp$ readback and $\RealUp$ seal exposure for $R$ and $E$;
\item transport stability, continuation replay, provenance, and local naming for exactly the displayed route recorded by $H,C,P,N$.
\end{enumerate}
No other analytic or choice-theoretic obligation is part of the local certificate.
\end{theorem}
\begin{proof}
Project the accepted packet $K=(S,W,B,L,T,R,E,H,C,P,N)$. The projection exposes exactly the monotone source, finite windows, dyadic schedule, block-sum ledger, tail-bound row, regular readback, real seal, transport rows, continuation replay, provenance, and local naming row.

Read a finite tail request through $W$ and $B$. The schedule selects finitely many dyadic blocks, and the ledger $L$ stores both the original block sums and the condensed terms on those same indices.

The monotone nonnegative source row $S$ is used only through displayed summand windows. The tail-bound row $T$ then turns the finite block comparisons into the comparison budget consumed by the fast-convergent-series surface, so the argument never appeals to an infinite choice of block representatives.

Finally use the structural rows. The componentwise transports in $H$ preserve the displayed data, and $C,P,N$ only replay, source, and name that route. Since the carrier has no further coordinate, the listed obligations exhaust the local $\NameCert_{\CauchyCondensationUp}$ surface.
\end{proof}

\begin{theorem}[Cauchy condensation dyadic-block handoff]
\label{thm:cauchy-condensation-dyadic-block-handoff}
Every accepted $\CauchyCondensationUp$ carrier sends a monotone nonnegative series tail to a completion-facing comparison route only through the finite dyadic-block handoff
$$
S,W,B,L \longmapsto T \longmapsto R,E,H,C,P,N.
$$
Thus a downstream consumer can read the condensation comparison only after reading the displayed summand windows, dyadic block schedule, block-sum ledger, tail-bound row, and $\RegSeqRatUp$ readback.
\end{theorem}
\begin{proof}
Begin with an accepted carrier and a displayed tail request. The window ledger $W$ identifies the finite summand rows to inspect, while the dyadic schedule $B$ fixes the block endpoints and powers of two.

Read the source row $S$ through those windows. The block ledger $L$ records the corresponding original block sums together with the condensed terms $2^n a_{2^n}$, so every comparison is attached to the displayed schedule.

Now apply the tail-bound row $T$. It packages the finite domination inequalities and tolerance thresholds that route the block comparison into the regular rational readback. No consumer can reach $R$ without the data supplied by $S,W,B,L,T$.

Transport and replay preserve this route componentwise. The rows $H,C,P,N$ therefore attach the handoff to the local certificate without creating an alternate path through host summability, selected sums, or completion.
\end{proof}

\begin{theorem}[Cauchy condensation Real-seal nonescape]
\label{thm:cauchy-condensation-real-seal-nonescape}
For every accepted $\CauchyCondensationUp$ carrier, any $\RealUp$ seal-facing read factors through the $\RegSeqRatUp$ handoff row $R$ produced from the finite dyadic-block route. The seal row $E$ receives the monotone source, summand windows, dyadic schedule, block-sum ledger, tail bounds, componentwise transports, continuation replay, provenance, and local naming rows, but it receives no quotient series equality, selected infinite sum, countable choice, trichotomy premise, host real equality, or RealUp completeness theorem.
\end{theorem}
\begin{proof}
Project the seal-facing rows $R$ and $E$ from the accepted carrier. The regular handoff $R$ is downstream of the tail-bound row $T$, and $T$ is downstream of the displayed summand windows, dyadic schedule, and block-sum ledger.

Apply \autoref{thm:cauchy-condensation-dyadic-block-handoff}. It identifies the only route from a monotone nonnegative tail to the readback row as the finite path through $S,W,B,L,T$ and the structural rows attached to the same packet.

Read the seal row $E$. Its analytic input is exactly $R$, together with $H,C,P,N$. Since the carrier has no coordinate for quotient series equality, a selected sum, countable choice, trichotomy outside the displayed windows, host real equality, or RealUp completeness, the seal-facing read cannot export any of those objects.
\end{proof}

\falsifiablePrediction{An accepted $\CauchyCondensationUp$ consumer that reaches a $\RealUp$ seal without reading the displayed summand windows, dyadic block schedule, block-sum ledger, tail-bound row, and $\RegSeqRatUp$ handoff refutes the carrier surface.}

\independenceWitness{series, fastconvergentseries, regseqrat, real: no listed sibling supplies the whole eleven-row packet $K=(S,W,B,L,T,R,E,H,C,P,N)$, because each sibling contributes only a source, comparison budget, regular readback, or seal face while this chapter binds all four faces with dyadic block scheduling, block-sum ledgers, tail bounds, transports, replay, provenance, and local naming.}

\closureat{$\CauchyCondensationUp$}{seedStr}

\begin{closurestatus}{\CauchyCondensationUp}
  \constructivestory{A $\CauchyCondensationUp$ packet is generated from a monotone nonnegative $\SeriesUp$ source, finite summand windows, a dyadic block schedule, block-sum ledgers, tail-bound rows, a $\RegSeqRatUp$ readback, a $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-condensation-carrier}, \autoref{thm:cauchy-condensation-namecert-obligations}, \autoref{thm:cauchy-condensation-dyadic-block-handoff}, and \autoref{thm:cauchy-condensation-real-seal-nonescape} seed the finite dyadic-block condensation boundary over $\SeriesUp$, $\FastConvergentSeriesUp$, $\RegSeqRatUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim ambient summability, quotient series equality, selected sums, countable choice, trichotomy, host real equality, RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the eleven-row carrier and prove the finite NameCert obligation surface, dyadic-block handoff theorem, and Real-seal nonescape theorem.}
\end{closurestatus}
