\chapter{A Concrete Naming Certificate for $\CantorSpaceUp$}
\label{ch:concrete-instances-cantorspace-namecert}
\origin{human}

Following Brouwer and Bishop--Bridges constructive analysis, the
$\CantorSpaceUp$ packet records the traditional Boolean sequence space as
finite prefix data over the L10 countable-name substrate. It consumes the
two-endpoint discipline of \autoref{ch:concrete-instances-bool-namecert}, the
finite window schedule of \autoref{ch:concrete-instances-streamname-namecert},
and the finite-data spine discipline of
\autoref{ch:concrete-instances-list-namecert}. The carrier is a displayed
$\BHist$ packet of $\BoolUp$ observations over unary $\StreamNameUp$ windows;
it is not a quotient of infinite streams, a host function space
$\NatUp \to \BoolUp$, a completed infinite product, a choice-selected branch,
or an open-cover compactness theorem.

\begin{definition}[CantorSpace carrier]
\label{def:cantor-space-carrier}
A $\CantorSpaceUp$ carrier is a finite $\BHist$ packet
$$
C=(S,W,B,L,E,H,K,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $S$ is the unary $\StreamNameUp$ schedule row whose entries are the
finite positions currently requested by the consumer;
\item $W$ is the finite prefix-window row, recording the initial segment and
any explicitly named subwindow inside that segment;
\item $B$ is the $\BoolUp$ observation ledger, assigning displayed Boolean
rows to the positions of $W$;
\item $L$ is the $\ListUp$ prefix-spine row that keeps the observed Boolean
entries as finite ordered data;
\item $E$ is the endpoint-exclusion row saying that every public bit is read
through the $\BoolUp$ two-row surface rather than through a hidden host
Boolean;
\item $H$ is the componentwise $\hsame$ transport row for $S,W,B,L,E$;
\item $K$ is the displayed $\Cont$ replay row for already accepted prefix
windows and Boolean rows;
\item $P$ is the $\Pkg$ provenance over $\CantorSpaceUp$, $\StreamNameUp$,
$\BoolUp$, $\ListUp$, $\BHist$, $\hsame$, $\Cont$, and the local naming row;
\item $N$ is the local $\NameCert_{\CantorSpaceUp}$ row.
\end{enumerate}
The carrier contains no quotient stream, no host-level function equality, no
completed infinite product, no branch chosen by countable choice, and no
compactness principle.
\end{definition}

\begin{definition}[CantorSpace classifier]
\label{def:cantor-space-classifier}
Two accepted $\CantorSpaceUp$ carriers
$$
C=(S,W,B,L,E,H,K,P,N)
\quad\hbox{and}\quad
C'=(S',W',B',L',E',H',K',P',N')
$$
are classified as the same at the local surface exactly when their
$\StreamNameUp$ schedules request the same finite prefix window and the
$\BoolUp$ observations agree componentwise on that common window. The
comparison is mediated by the $\ListUp$ spine rows, transported by $H,H'$, and
replayed only through $K,K'$. No classifier clause compares host functions,
quotient streams, or all infinite coordinates at once.
\end{definition}

\begin{theorem}[CantorSpace NameCert obligation surface]
\label{thm:cantor-space-namecert-obligation-surface}
The local $\NameCert_{\CantorSpaceUp}$ surface of
\autoref{def:cantor-space-carrier} consists of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet
$C=(S,W,B,L,E,H,K,P,N)$;
\item classifier transport for common finite-prefix $\BoolUp$ equality under
the same $\StreamNameUp$ schedule;
\item prefix stability, requiring every shorter requested window inside $W$ to
reuse the matching visible Boolean rows already recorded in $B$ and $L$;
\item continuation compatibility, requiring every replayed read to pass
through $H,K,P,N$ before it reaches a downstream L10 consumer;
\item non-escape, excluding quotient streams, host function equality,
completed infinite products, choice-selected branches, and compactness claims.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.CantorSpaceUp.CantorSpaceCarrier\_namecert\_obligation\_surface}
\begin{proof}
Carrier admission is projection of the nine displayed coordinates in
\autoref{def:cantor-space-carrier}. The schedule, prefix window, Boolean
ledger, and list spine rows are finite $\BHist$ data.

Classifier transport uses \autoref{def:cantor-space-classifier}. Once the
common $\StreamNameUp$ window is fixed, equality is read only as
componentwise $\BoolUp$ agreement along the displayed $\ListUp$ spine and is
then transported by $H$.

Prefix stability follows because a shorter requested window is a subrow of the
same displayed prefix row $W$. Its Boolean entries are already present in $B$
and in the ordered spine $L$, so $\Cont$ may replay them without adding an
infinite stream coordinate.

The non-escape clause is inspection of the carrier and classifier. The packet
has rows for finite schedules, finite Boolean observations, transport,
continuation, provenance, and the local $\NameCert$ row, and has no coordinate
for quotient streams, host functions, infinite products, selected branches, or
compactness witnesses.
\end{proof}

\begin{theorem}[CantorSpace finite-prefix cylinder stability]
\label{thm:cantor-space-finite-prefix-cylinder-stability}
Let $C=(S,W,B,L,E,H,K,P,N)$ be an accepted $\CantorSpaceUp$ carrier. Any
finite cylinder read determined by a prefix subwindow of $W$ factors through
the same $\StreamNameUp$ schedule row $S$, the same $\BoolUp$ observation
ledger $B$, the same $\ListUp$ spine $L$, and the same $H,K,P,N$ transport,
continuation, provenance, and local naming rows. The cylinder read exports no
extra infinite tail, no quotient-stream equality, no host function
extensionality, and no compactness argument.
\end{theorem}
\leanchecked{BEDC.Derived.CantorSpaceUp.CantorSpaceCarrier\_finite\_prefix\_cylinder\_stability}
\begin{proof}
Choose a prefix subwindow of $W$. Since $W$ is a finite row of the accepted
carrier, the requested positions are already part of the displayed
$\StreamNameUp$ schedule $S$.

The Boolean values on that subwindow are precisely the corresponding entries
of $B$, ordered by the finite $\ListUp$ spine $L$. Transport by $H$ preserves
the componentwise rows, and $\Cont$ replay through $K$ reuses only those rows.

Thus every cylinder read is exhausted by $S,W,B,L,H,K,P,N$. The excluded
objects are not coordinates of the carrier, so the read cannot produce an
infinite tail, quotient equality, host-function extensionality, or compactness
data.
\end{proof}

\begin{theorem}[CantorSpace prefix projection stability]
\label{thm:cantor-space-prefix-projection-stability}
Let $K=(S,W,B,L,E,H,K_0,P,N)$ be an accepted $\CantorSpaceUp$ carrier. Any restriction of a public read to a shorter finite prefix is again a read through the displayed rows $S,W,B,L,E,H,K_0,P,N$: the schedule row $S$ and window row $W$ choose the visible positions, the $\BoolUp$ row $B$ supplies endpoint values, and the $\ListUp$ spine $L$ records the prefix order. The projection contains no host infinite stream, no quotient equality of functions, no branch choice, and no compactness principle.
\end{theorem}
\begin{proof}
Start with the accepted carrier and project its finite prefix spine. The shorter prefix is obtained by reading an initial segment of $L$ and the corresponding entries of $S$ and $W$.

For each retained position, the endpoint value is still read from $B$. Componentwise transport by $H$ and replay through $K_0$ preserve only the retained rows, while $P$ and $N$ keep the same provenance and local certificate.

Thus prefix projection is closed inside the displayed carrier. Since no coordinate names an infinite stream, a quotient-function equality, a branch selector, or compactness data, none of those objects can appear in the projected read.
\end{proof}
\leanchecked{BEDC.Derived.CantorSpaceUp.CantorSpaceCarrier\_prefix\_projection\_stability}

\begin{theorem}[CantorSpace prefix cylinder no-confusion]
\label{thm:cantorspace-prefix-cylinder-no-confusion}
Let $K=(S,W,B,L,E,H,K_0,P,N)$ and $K'=(S',W',B',L',E',H',K'_0,P',N')$ be
accepted $\CantorSpaceUp$ carriers whose finite cylinder reads are projected to
the same certified unary index window. If the displayed $\ListUp$ prefix
readbacks first disagree at a certified unary index $i$ and the corresponding
$\BoolUp$ rows in $B$ and $B'$ have separated tags at $i$, then the two
$\StreamNameUp$ carrier reads are not classifier-equal on that finite window.
The conclusion is only the finite-window failure of classifier equality for the
displayed prefixes; it is not an inequality of ambient infinite sequences.
\end{theorem}
\begin{proof}
Project both carrier reads to the common finite window using
\autoref{thm:cantor-space-prefix-projection-stability}. The projected data are
exactly the visible schedule rows, the two finite $\ListUp$ prefix spines, and
the corresponding $\BoolUp$ ledger entries.

At the first certified unary index $i$ where the prefix readbacks disagree,
$\ListUp$ readback identifies the two compared positions as the same finite
slot. The separated $\BoolUp$ tags at that slot cannot be transported into the
same componentwise observation row.

StreamName pointwise classifier stability therefore blocks equality on the
projected window: any classifier equality for the two carrier reads would have
to identify the two Boolean rows at $i$. This contradicts the displayed
tag separation, so no classifier-equality certificate exists on the finite
window.
\end{proof}

\begin{theorem}[CantorSpace Bool cylinder endpoint determinacy]
\label{thm:cantor-space-bool-cylinder-endpoint-determinacy}
For an accepted $\CantorSpaceUp$ carrier $K=(S,W,B,L,E,H,K_0,P,N)$, each cylinder endpoint visible to a downstream consumer is determined by the finite $\BoolUp$ ledger $B$ along the positions ordered by $L$. If two consumer reads inspect the same prefix coordinates through $S,W,L$ and transport by the same $H,K_0,P,N$ rows, then their endpoint rows agree exactly as displayed by $B$; no endpoint is chosen from an ambient infinite product.
\end{theorem}
\begin{proof}
Read the shared prefix coordinates from $S,W,L$. These rows specify which positions are visible and in which finite order they are consumed.

The endpoint value at each visible position is then the corresponding row of $B$. If two reads use the same visible coordinates and the same transport and replay data, they reach the same finite Bool ledger entries.

The structural rows $H,K_0,P,N$ preserve this ledger route. There is no carrier coordinate for an infinite product endpoint, a choice-selected branch, or a host stream function, so endpoint determinacy is the finite determinacy of $B$ over $L$.
\end{proof}

\begin{theorem}[CantorSpace StreamName prefix consumer exhaustion]
\label{thm:cantor-space-streamname-prefix-consumer-exhaustion}
Every $\StreamNameUp$ or $\ListUp$ consumer of an accepted $\CantorSpaceUp$ carrier factors through the finite rows $S,W,B,L,E,H,K_0,P,N$. The consumer may restrict, transport, and replay a displayed prefix cylinder, but after the rows $S,W,B,L,E,H,K_0,P,N$ are exhausted it has no further route to an infinite stream tail, a quotient of branches, a fan-theorem compactness object, or countable-choice data.
\end{theorem}
\begin{proof}
Project the consumer read through the $\StreamNameUp$ rows $S,W$ and the $\ListUp$ row $L$. These rows are the only coordinates that expose positions and prefix order.

The Bool observations are then consumed through $B$, with any endpoint and cylinder data carried by $E$. Transport and continuation replay remain componentwise through $H$ and $K_0$.

Once $P$ and $N$ record provenance and local naming, every carrier coordinate has been inspected. The consumer is therefore exhausted by the displayed finite packet and cannot continue to an unlisted stream tail, quotient branch, compactness object, or choice schedule.
\end{proof}
\leanchecked{BEDC.Derived.CantorSpaceUp.CantorSpaceCarrier\_streamname\_prefix\_consumer\_exhaustion}

\begin{theorem}[CantorSpace StreamName-Bool scope]
\label{thm:cantor-space-streamname-bool-scope}
Every public read exported by an accepted $\CantorSpaceUp$ carrier reaches the
L10 countable-name substrate only through the finite route
$$
\StreamNameUp,\ \BoolUp,\ \ListUp,\ \NameCert_{\CantorSpaceUp}.
$$
The route binds the schedule, Boolean endpoint rows, finite prefix spine, and
local certificate before any downstream consumer may inspect the packet. It
does not claim Real completeness, quotient stream completeness, open-cover
compactness, fan-theorem compactness, or choice of an infinite branch.
\end{theorem}
\leanchecked{BEDC.Derived.CantorSpaceUp.CantorSpaceStreamNameBoolScope}
\begin{proof}
Project a public consumer read from the accepted carrier. The requested
positions are first visible in the $\StreamNameUp$ schedule row $S$ and prefix
row $W$.

Each visible value is then read through the $\BoolUp$ ledger $B$ and ordered by
the $\ListUp$ spine $L$. The rows $H$ and $K$ only transport and replay that
finite data, while $P$ and $N$ record the provenance and local certificate.

Therefore the public route is exactly the displayed finite route through
$\StreamNameUp$, $\BoolUp$, $\ListUp$, and
$\NameCert_{\CantorSpaceUp}$. No coordinate in the packet supplies Real
completeness, stream quotient completeness, open-cover compactness,
fan-theorem compactness, or a choice-selected infinite branch.
\end{proof}

\begin{closurestatus}{\CantorSpaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cantor-space-carrier}, \autoref{def:cantor-space-classifier}, \autoref{thm:cantor-space-namecert-obligation-surface}, \autoref{thm:cantor-space-finite-prefix-cylinder-stability}, and \autoref{thm:cantor-space-streamname-bool-scope} seed the finite Bool-valued StreamName packet for Cantor-space prefix cylinders.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{The chapter does not close quotient streams, host function equality, completed infinite products, Real completeness, choice-selected branches, open-cover compactness, fan-theorem compactness, or a standard bridge.}
  \upgradepath{The next step is obligationClosure: carrier admission, classifier transport, finite-prefix cylinder stability, StreamName-Bool routing, and non-escape must be discharged as local rows.}
  \constructivestory{The construction starts from finite unary StreamName windows, records Bool observations along a List prefix spine, and exposes only displayed hsame, Cont, Pkg, and local NameCert rows to downstream L10 consumers.}
\end{closurestatus}
