\chapter{A Concrete Naming Certificate for $\RealSequenceLimitLawsUp$}
\label{ch:concrete-instances-real-sequence-limit-laws-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the
$\RealSequenceLimitLawsUp$ packet records the finite algebra used when two
displayed $\RealUp$ sequence limits are combined by a standard arithmetic
operation. It sits over the $\StreamNameUp$ windows of
\autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$
readback rows of \autoref{ch:concrete-instances-regseqrat-namecert}, the
$\DyadicRatCoreUp$ tolerance ledger of
\autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal
$\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, and the
sandwich route of \autoref{ch:concrete-instances-squeezereal-namecert}. The
certificate keeps limit arithmetic as displayed finite route data, not as
quotient stream equality, a selected host limit, trichotomy, or ambient
completeness.

\begin{definition}[Real sequence limit laws carrier]
\label{def:real-sequence-limit-laws-carrier}
A $\RealSequenceLimitLawsUp$ carrier is a finite $\BHist$ packet
$$
L=(X,Y,S_X,S_Y,R_X,R_Y,D,E_X,E_Y,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are two $\RealUp$ sequence source routes whose terms are read
only through finite observation windows.
\item $S_X$ and $S_Y$ are the $\StreamNameUp$ window rows opened for the two
sources at the requested precision scale.
\item $R_X$ and $R_Y$ are the $\RegSeqRatUp$ readback rows attached to those
windows.
\item $D$ is the $\DyadicRatCoreUp$ error ledger recording the two source
budgets, the operation budget, and the output tolerance request.
\item $E_X$ and $E_Y$ are the two limit-seal rows that certify the displayed
source routes before any arithmetic read is public.
\item $O$ is the operation row, recording whether the read is sum, difference,
product under a displayed bound, scalar multiple, or squeeze-mediated
comparison, together with its required dyadic error estimate.
\item $H$ stores componentwise $\hsame$ transport for the two sources, their
windows, readbacks, limit seals, dyadic ledger, and operation row.
\item $C$ stores displayed $\Cont$ replay for opening windows, reading regular
rational approximants, consuming dyadic error rows, invoking the operation
row, and exposing the output seal route.
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\RegSeqRatUp$,
$\DyadicRatCoreUp$, $\RealUp$, $\SqueezeRealUp$, $\BHist$, $\hsame$, $\Cont$,
and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RealSequenceLimitLawsUp}$ row.
\end{enumerate}
The carrier contains no quotient stream, no host equality of real sequences,
no selected limit value, no trichotomy row, and no ambient completeness
principle.
\end{definition}

\begin{theorem}[Real sequence limit laws NameCert obligations]
\label{thm:real-sequence-limit-laws-namecert-obligations}
The local $\NameCert_{\RealSequenceLimitLawsUp}$ surface for
\autoref{def:real-sequence-limit-laws-carrier} consists of five finite
obligation rows:
\begin{enumerate}
\item carrier admission for the displayed packet
$L=(X,Y,S_X,S_Y,R_X,R_Y,D,E_X,E_Y,O,H,C,P,N)$;
\item classifier stability under componentwise $\hsame$ transport and
displayed $\Cont$ replay of the two source routes, window rows, readback rows,
limit seals, dyadic ledger, and operation row;
\item operation-row exactness, requiring the output tolerance read to be the
dyadic estimate stored in $D$ and cited by $O$;
\item seal handoff, requiring every public limit-law read to pass through
$E_X$, $E_Y$, $O$, and the displayed transport, replay, provenance, and local
naming rows before any $\RealUp$ output seal is exposed;
\item non-escape, stating that quotient stream equality, selected host limits,
trichotomy, host real-sequence equality, and ambient completeness are absent
from the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from
\autoref{def:real-sequence-limit-laws-carrier}. The two source routes, two
window rows, two readback rows, dyadic ledger, two limit seals, operation row,
transport, replay, provenance, and local name are explicit coordinates of
$L$.

Classifier stability is componentwise. The stored $H$ and $C$ rows transport
and replay exactly the coordinates named by the carrier, so a classified read
cannot detach an operation row from its two source seals or from the dyadic
error ledger.

Operation-row exactness is the role of $D$ and $O$. The dyadic ledger records
the input and output tolerances, while $O$ declares which arithmetic or
squeeze-mediated operation consumes those estimates.

The seal handoff then forces a public limit-law consumer to read $E_X$ and
$E_Y$ before it invokes $O$. Since the carrier has no coordinate for quotient
stream equality, selected host limits, trichotomy, host sequence equality, or
ambient completeness, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Real sequence limit laws RealUp handoff]
\label{thm:real-sequence-limit-laws-realup-handoff}
Every public limit-law read exported by an accepted
$\RealSequenceLimitLawsUp$ carrier factors through the displayed
$\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of
\autoref{def:real-sequence-limit-laws-carrier}. The handoff exports no
quotient stream equality, selected host limit, trichotomy, host equality of
real sequences, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with a public limit-law consumer and project the accepted carrier. The
consumer first receives the two source routes $X,Y$ through the finite windows
$S_X,S_Y$ and the regular rational readbacks $R_X,R_Y$.

The dyadic error ledger $D$ is then read at the same precision scale. It is the
only tolerance coordinate listed in the carrier, and the operation row $O$
must cite it before an output route can be exposed.

The two limit-seal rows $E_X,E_Y$ bind the source routes to the terminal
$\RealUp$ surface, while $H,C,P,N$ provide the componentwise transport, replay,
provenance, and local naming route. These rows are exactly the public handoff
surface. No further coordinate remains from which a consumer could read a
quotient stream equality, a selected host limit, trichotomy, host sequence
equality, or ambient completeness.
\end{proof}

\begin{theorem}[Real sequence limit laws dyadic operation exhaustion]
\label{thm:real-sequence-limit-laws-dyadic-operation-exhaustion}
Every accepted operation row $O$ in a $\RealSequenceLimitLawsUp$ carrier
$$
L=(X,Y,S_X,S_Y,R_X,R_Y,D,E_X,E_Y,O,H,C,P,N)
$$
must cite the displayed $\DyadicRatCoreUp$ ledger $D$ for its input budgets, operation budget, and output tolerance request. After $D,O,E_X,E_Y,H,C,P,N$ are fixed, no quotient stream equality, selected host limit, trichotomy row, host sequence equality, or ambient completeness principle can alter the public limit-law read.
\end{theorem}
\begin{proof}
Project the accepted carrier. The operation row $O$ and the dyadic ledger $D$ are the only coordinates that describe arithmetic error accounting for the two displayed source routes.

Apply operation-row exactness from \autoref{thm:real-sequence-limit-laws-namecert-obligations}. The row $O$ must consume the tolerance data stored in $D$, including the two input budgets, the operation budget, and the output tolerance request.

Apply the RealUp handoff theorem \autoref{thm:real-sequence-limit-laws-realup-handoff}. Once the two source seals $E_X,E_Y$ and the structural rows $H,C,P,N$ are fixed with $D$ and $O$, the public limit-law read is already routed through the displayed finite packet.

The carrier has no coordinate for quotient stream equality, selected host limits, trichotomy, host sequence equality, or ambient completeness. Hence none of those objects can revise the dyadic operation read.
\end{proof}

\begin{closurestatus}{\RealSequenceLimitLawsUp}
  \constructivestory{A $\RealSequenceLimitLawsUp$ packet is generated from two $\RealUp$ sequence source routes, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, a $\DyadicRatCoreUp$ error ledger, two limit-seal rows, an operation row, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-sequence-limit-laws-carrier}, \autoref{thm:real-sequence-limit-laws-namecert-obligations}, \autoref{thm:real-sequence-limit-laws-realup-handoff}, and \autoref{thm:real-sequence-limit-laws-dyadic-operation-exhaustion} seed the finite constructive limit-law packet over StreamName, RegSeqRat, DyadicRatCore, RealUp, and SqueezeReal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient stream equality, selected host limits, trichotomy, host equality of real sequences, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, operation-row exactness, seal handoff, and non-escape for the same finite limit-law packet.}
\end{closurestatus}
