\chapter{A Concrete Naming Certificate for $\DyadicDensityRealUp$}
\label{ch:concrete-instances-dyadic-density-real-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the
$\DyadicDensityRealUp$ packet records the finite dyadic witness surface used
when a displayed real-name interval must expose a dyadic point at a displayed
radius. It sits over the $\DyadicRatCoreUp$ tolerance ledger of
\autoref{ch:concrete-instances-dyadicratcore-namecert}, the constant dyadic
real-name route of \autoref{ch:concrete-instances-dyadicembedding-namecert},
the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the
regular rational readbacks of
\autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal
$\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The
certificate names density as finite BEDC route data, not as quotient streams,
selected host limits, host real equality, trichotomy, or ambient completeness.

\begin{definition}[DyadicDensityReal carrier]
\label{def:dyadic-density-real-carrier}
A $\DyadicDensityRealUp$ carrier is a finite $\BHist$ packet
$$
W=(L,U,D,\rho,S_L,S_U,R_L,R_U,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ and $U$ are the lower and upper $\RealUp$ endpoint seal rows for the
displayed interval, read only as Real-facing name data.
\item $D$ is the $\DyadicRatCoreUp$ source row naming the candidate dyadic
rational witness and its comparison scales.
\item $\rho$ is the dyadic radius row recording the requested positive window
and the two endpoint tolerances used by the witness read.
\item $S_L$ and $S_U$ are the $\StreamNameUp$ finite observation windows
opened for the two endpoint names at the scales requested by $\rho$.
\item $R_L$ and $R_U$ are the $\RegSeqRatUp$ readback rows attached to those
two finite windows.
\item $E$ is the $\DyadicEmbeddingUp$ handoff row sending the dyadic source
named by $D$ into the same real-name surface as the two endpoint seals.
\item $H$ stores componentwise $\hsame$ transport for the endpoint seals,
dyadic source row, radius row, stream windows, regular readbacks, embedding
handoff, continuations, provenance, and local naming.
\item $C$ stores displayed $\Cont$ routes for opening endpoint windows, reading
the regular rational rows, consuming the dyadic source and radius rows,
invoking the embedding handoff, and exposing the dyadic witness to the
$\RealUp$ interval consumer.
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$,
$\DyadicEmbeddingUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$,
$\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicDensityRealUp}$ row.
\end{enumerate}
The carrier contains no quotient stream, selected host limit, host real
equality, trichotomy row, or ambient completeness principle.
\end{definition}

\begin{theorem}[DyadicDensityReal NameCert obligations]
\label{thm:dyadic-density-real-namecert-obligations}
For every accepted $\DyadicDensityRealUp$ carrier
$W=(L,U,D,\rho,S_L,S_U,R_L,R_U,E,H,C,P,N)$, the local
$\NameCert_{\DyadicDensityRealUp}$ surface consists of five finite obligation
rows:
\begin{enumerate}
\item carrier admission for the displayed endpoint, dyadic, window, readback,
handoff, transport, continuation, provenance, and local naming rows;
\item endpoint-window compatibility, stating that $S_L,S_U,R_L,R_U$ are read
from the same displayed radius row $\rho$ and the same endpoint seals $L,U$;
\item dyadic-source exactness, stating that the exported witness is the
$\DyadicRatCoreUp$ source named by $D$ at the radius and comparison scales
recorded in $\rho$;
\item embedding handoff, stating that the only Real-facing route for the
dyadic witness is the $\DyadicEmbeddingUp$ row $E$ followed by the displayed
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ reads;
\item non-escape, stating that quotient streams, selected host limits, host
real equality, trichotomy, and ambient completeness are absent from the
carrier.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-density-real-carrier}. The two
endpoint seals, dyadic source, radius row, two window rows, two readback rows,
embedding handoff, transports, continuations, provenance, and local name are
exactly the coordinates available to the classifier.

Endpoint-window compatibility follows from the shared radius row. Both
$S_L,S_U$ and their readbacks $R_L,R_U$ are listed as windows opened at the
scales requested by $\rho$, so a classified interval read cannot use an
endpoint window detached from the displayed tolerance request.

Dyadic-source exactness and embedding handoff are the same finite route read
from opposite sides. The row $D$ supplies the dyadic rational witness, while
$E$ is the only coordinate that embeds that source into the Real-facing naming
surface.

The non-escape row is inspection of the packet. Since the carrier has no
coordinate for quotient streams, selected host limits, host real equality,
trichotomy, or ambient completeness, the five rows exhaust the local
NameCert surface.
\end{proof}

\begin{theorem}[DyadicDensityReal witness route]
\label{thm:dyadic-density-real-witness-route}
Every exported dyadic witness of an accepted $\DyadicDensityRealUp$ carrier
factors through the displayed route
$$
\DyadicRatCoreUp \longrightarrow \DyadicEmbeddingUp \longrightarrow
\StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \RealUp
$$
together with the carrier's componentwise $\hsame$ transports, displayed
$\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. The route exports
no quotient stream, selected host limit, host real equality, trichotomy row, or
ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with an exported dyadic witness and project the accepted carrier. The
only dyadic source coordinate is $D$, so the witness begins as the
$\DyadicRatCoreUp$ row named by the packet.

The witness then crosses the embedding handoff. The row $E$ is the sole
$\DyadicEmbeddingUp$ coordinate, and the continuation routes $C$ expose it
only after the endpoint windows and readbacks attached to $\rho$ have been
displayed.

Finally the Real-facing consumer reads the same finite surface through
$S_L,S_U,R_L,R_U$ and the endpoint seals $L,U$. Componentwise transport $H$,
provenance $P$, and the local naming row $N$ preserve that route as a single
packet over the displayed primitives.

No other carrier coordinate can export a witness. Hence every public dyadic
density read factors through the stated
$\DyadicRatCoreUp \to \DyadicEmbeddingUp \to \StreamNameUp \to
\RegSeqRatUp \to \RealUp$ route and cannot obtain any of the excluded host or
quotient data.
\end{proof}

\begin{closurestatus}{\DyadicDensityRealUp}
  \constructivestory{A $\DyadicDensityRealUp$ packet is generated from lower and upper Real endpoint seals, a DyadicRatCore source row, a dyadic radius row, finite StreamName windows, RegSeqRat readbacks, a DyadicEmbedding handoff, componentwise hsame transports, displayed Cont routes, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-density-real-carrier}, \autoref{thm:dyadic-density-real-namecert-obligations}, and \autoref{thm:dyadic-density-real-witness-route} seed the finite dyadic-density packet over DyadicRatCore, DyadicEmbedding, StreamName, RegSeqRat, and RealUp rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient stream equality, selected host limits, host real equality, trichotomy, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, endpoint-window compatibility, dyadic-source exactness, embedding handoff, and non-escape for the same finite dyadic-density packet.}
\end{closurestatus}
