\chapter{A Concrete Naming Certificate for $\LocatedOpenUp$}
\label{ch:concrete-instances-locatedopen-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\LocatedOpenUp$
packet records a neighbourhood interface whose evidence is located in finite
real and cut data before any topological consumer reads it. It sits over the
located cut surface of \autoref{ch:concrete-instances-locatedcut-namecert}, the
located real enclosure of \autoref{ch:concrete-instances-locatedreal-namecert},
the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert},
the regular rational readback of
\autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal
of \autoref{ch:concrete-instances-real-namecert}, and the completion-facing
filter route of \autoref{ch:concrete-instances-cauchyfilter-namecert}. The
chapter names only a finite L10 neighbourhood packet: it does not identify
opens with quotient subsets of host reals and does not invoke open-cover
compactness.

\begin{definition}[LocatedOpen carrier]
\label{def:located-open-carrier}
A $\LocatedOpenUp$ carrier is a finite $\BHist$ packet
$$
O=(L,R,S,Q,W,E,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the $\LocatedCutUp$ source row exposing the finite lower and upper
cut comparisons used by the local membership read.
\item $R$ is the $\LocatedRealUp$ enclosure row tying the same comparisons to a
located real presentation.
\item $S$ is the $\StreamNameUp$ window family recording the inspected stream
positions and replayable requests.
\item $Q$ is the $\RegSeqRatUp$ regular rational readback attached to those
windows.
\item $W$ is the displayed located-membership window row. For each inspected
candidate it records a finite interval-entry witness or a positive dyadic
radius witness around the candidate.
\item $E$ is the $\RealUp$ seal row reached only after the located cut, located
real, stream, regular rational, and membership-window rows have been displayed.
\item $T$ is the local classifier transport row moving $L,R,S,Q,W,E$ to a
common finite comparison surface.
\item $H$ records componentwise $\hsame$ transport for the cut, real, stream,
regular rational, membership-window, Real-seal, classifier, continuation,
provenance, and local naming rows.
\item $C$ records the displayed $\Cont$ replay from a neighbourhood request
through the inspected windows, radius or interval-entry evidence, readback rows,
Real seal, and classifier transport.
\item $P$ is the $\Pkg$ provenance over $\LocatedOpenUp$, $\LocatedCutUp$,
$\LocatedRealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$,
$\CauchyFilterUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedOpenUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed finite
windows and transports. It has no coordinate for quotient subsets of reals,
host real equality, a choice-selected neighbourhood, arbitrary-union
completion, open-cover compactness, or a proof that $\RealUp$ is complete.
\end{definition}

\begin{theorem}[LocatedOpen window stability]
\label{thm:located-open-window-stability}
For every accepted $\LocatedOpenUp$ packet
$O=(L,R,S,Q,W,E,T,H,C,P,N)$, the located-membership windows in $W$ are stable
under the componentwise $\hsame$ transports recorded in $H$. In particular, a
transported consumer reads the same finite interval-entry witnesses and
positive dyadic radius witnesses after $L,R,S,Q,W,E$ have been moved to the
common comparison surface named by $T$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-open-carrier}. The only
membership evidence available to a consumer is the row $W$, and each entry of
$W$ is already displayed as a finite interval-entry witness or a positive
dyadic radius witness.

Apply the transport row $H$ componentwise. The located cut, located real,
stream, regular rational, membership-window, and Real-seal rows are moved
together to the comparison surface named by $T$, so the transported packet
contains the same window indices and the same radius or interval-entry
witnesses.

Finally replay the continuation row $C$. Replay follows the transported
windows and readbacks; it does not introduce an ambient subset, a host equality
test, a selected neighbourhood, or an arbitrary union. Thus the located
membership surface is stable exactly over the displayed finite windows.
\end{proof}

\begin{theorem}[LocatedOpen Real consumer route]
\label{thm:located-open-realup-consumer-route}
Every $\RealUp$-facing consumer of an accepted $\LocatedOpenUp$ packet factors
through
$$
\LocatedCutUp,\quad \LocatedRealUp,\quad \StreamNameUp,\quad
\RegSeqRatUp,\quad \RealUp,\quad \CauchyFilterUp,\quad
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert .
$$
Concretely, the consumer first reads the located cut and located real rows,
then the finite stream and regular rational readbacks, then the displayed
located-membership windows, and only then the terminal $\RealUp$ seal and
filter-facing continuation route.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$-facing read of the seal row $E$. The carrier stores $E$
after the located cut row $L$, located real row $R$, stream window row $S$,
regular rational readback row $Q$, and located-membership window row $W$.
Therefore no consumer can reach the seal without first exposing these finite
rows.

The completion-facing part is only a route. The provenance row names
$\CauchyFilterUp$ so that a filtered consumer can replay the finite
neighbourhood request through $C$, but the packet supplies no completeness
field and no arbitrary-union constructor.

Attach $T,H,P,N$ to the same route. Classifier transport, componentwise
$\hsame$, package provenance, and local naming keep the consumer inside the
listed rows. Since the carrier has no coordinate for quotient subsets, host
real equality, selected neighbourhoods, open-cover compactness, or
$\RealUp$ completeness, no such datum can be recovered from the read.
\end{proof}

\begin{closurestatus}{\LocatedOpenUp}
  \constructivestory{A $\LocatedOpenUp$ packet is generated from located cut rows, located real enclosure rows, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, displayed membership windows with positive dyadic radius or interval-entry witnesses, a terminal $\RealUp$ seal, classifier transport, componentwise $\hsame$ rows, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-open-carrier}, \autoref{thm:located-open-window-stability}, and \autoref{thm:located-open-realup-consumer-route} seed the finite L10 located-neighbourhood interface over located real and cut data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim general topology, open-cover compactness, Heine--Borel, arbitrary-union completion, quotient subsets of reals, host real equality, choice-selected neighbourhoods, or $\RealUp$ completeness.}
  \upgradepath{A formal route can encode BEDC.Derived.LocatedOpenUp.LocatedOpenCarrier and prove window stability, Real-facing consumer routing, classifier transport, provenance, and local NameCert exactness.}
\end{closurestatus}
