\chapter{A Concrete Naming Certificate for $\CauchyModulusOfContinuityUp$}
\label{ch:concrete-instances-cauchymodulusofcontinuity-namecert}
\origin{human}

Following Bishop and Bridges' constructive-analysis use of explicit moduli,
the $\CauchyModulusOfContinuityUp$ packet records pointwise continuity data for
Cauchy names as a visible finite schedule rather than as a host continuity
predicate. It sits between the explicit Cauchy schedule surface of
\autoref{ch:concrete-instances-cauchymodulus-namecert}, the finite
Cauchy-name transformer of
\autoref{ch:concrete-instances-cauchycontinuousmap-namecert}, the regular
rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the
terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and
the compact uniform consumer boundary of
\autoref{ch:concrete-instances-uniformmodulus-namecert}. The pointwise packet
records the threshold route for one displayed source Cauchy name and its
target tolerances; it is not compactness, a uniform modulus over all inputs,
or a host function equality principle.

\begin{definition}[Cauchy modulus of continuity carrier]
\label{def:cauchy-modulus-of-continuity-carrier}
A $\CauchyModulusOfContinuityUp$ carrier is a finite $\BHist$ packet
$$
K=(S,T,\mu,F,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\StreamNameUp$ window surface whose finite rational
observations are inspected before a target tolerance is answered.
\item $T$ is the target $\StreamNameUp$ window surface promised by the
pointwise Cauchy-name transformer.
\item $\mu$ is the $\CauchyModulusUp$ threshold schedule assigned to each
requested target tolerance, including the finite source-window bound that the
consumer must inspect.
\item $F$ is the $\CauchyContinuousMapUp$ transformer row that consumes
$S,\mu$ and produces the displayed target windows $T$.
\item $R$ stores the $\RegSeqRatUp$ readbacks for the source and target
windows, with the target readback reached only through $F$ and $\mu$.
\item $E$ is the $\RealUp$ seal row reached from the target
$\RegSeqRatUp$ readback after the displayed schedule has been replayed.
\item $H$ records componentwise $\hsame$ transport for $S,T,\mu,F,R,E$ and
for the continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a target tolerance request
through the threshold schedule $\mu$, the source window $S$, the transformer
row $F$, the target window $T$, the regular readbacks $R$, and the seal row
$E$.
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\CauchyModulusUp$,
$\CauchyContinuousMapUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$,
$\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyModulusOfContinuityUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only by transporting these displayed
rows to a common finite source-window, target-window, threshold, transformer,
readback, and seal surface. It has no coordinate for quotient streams, host
function equality, selected limits, compactness, a uniform modulus, or ambient
completeness.
\end{definition}

\begin{theorem}[Cauchy modulus of continuity NameCert obligations]
\label{thm:cauchy-modulus-of-continuity-namecert-obligations}
For every accepted $\CauchyModulusOfContinuityUp$ carrier
$K=(S,T,\mu,F,R,E,H,C,P,N)$, the local
$\NameCert_{\CauchyModulusOfContinuityUp}$ surface consists exactly of five
obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source windows, target windows,
threshold schedule, transformer row, regular readbacks, seal row, transport,
continuation, provenance, and local name;
\item classifier transport to a common $\StreamNameUp$, $\CauchyModulusUp$,
$\CauchyContinuousMapUp$, $\RegSeqRatUp$, and $\RealUp$ finite surface;
\item stability of $S,T,\mu,F,R,E$ under the componentwise $\hsame$ rows
recorded in $H$;
\item exactness of $\mu$ as the only threshold route read by the
$\CauchyContinuousMapUp$ consumer;
\item $\Cont$ replay, $\Pkg$ provenance, $\RealUp$ seal factorization, and
local NameCert rows for exactly the displayed packet.
\end{enumerate}
No NameCert obligation is stored outside those five rows.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:cauchy-modulus-of-continuity-carrier}. The projection exposes
exactly the source windows, target windows, threshold schedule, transformer
row, regular readbacks, real seal, transport rows, continuation rows,
provenance row, and local name.

Classifier transport is componentwise. The rows in $H$ move the source and
target windows, the threshold schedule, the transformer row, the readbacks,
and the seal row to the same displayed finite surface.

The threshold exactness row is exhausted by $\mu$. The transformer row $F$
reads a target tolerance by first reading the schedule $\mu$, then inspecting
the named source windows $S$, and then producing the target windows $T$.

Finally replay $C$ and attach $P,N$. These rows route, source, and name the
already displayed packet; they do not introduce quotient streams, host
function equality, selected limits, compactness, a uniform modulus, or ambient
completeness. Hence the five listed rows exhaust the local naming obligations.
\end{proof}

\begin{theorem}[CauchyContinuousMap threshold handoff]
\label{thm:cauchy-modulus-of-continuity-cauchy-handoff}
For every accepted $\CauchyModulusOfContinuityUp$ carrier
$K=(S,T,\mu,F,R,E,H,C,P,N)$, the displayed schedule $\mu$ is the only
threshold route used by a $\CauchyContinuousMapUp$ consumer. Any read of the
target window $T$ must pass through the source window $S$, the schedule $\mu$,
the transformer row $F$, the $\RegSeqRatUp$ readbacks $R$, and the displayed
$\Cont$, $\Pkg$, and local $\NameCert$ rows.
\end{theorem}
\begin{proof}
Start with a target tolerance request. Carrier admission exposes the schedule
$\mu$ before the transformer row $F$ can be consumed.

Replay the displayed continuation row $C$. The route sends the tolerance
request to $\mu$, obtains the finite source-window threshold, reads the
corresponding source observations in $S$, and then lets $F$ produce the target
windows $T$.

The readback row $R$ is reached only after that transformer route. Transport
through $H$ preserves the same order of dependencies, and $P,N$ merely record
provenance and local naming.

Since the carrier contains no second threshold coordinate, no quotient stream,
and no host function row, a $\CauchyContinuousMapUp$ consumer has no alternate
route by which to obtain $T$.
\end{proof}

\begin{theorem}[Cauchy modulus of continuity Real consumer boundary]
\label{thm:cauchy-modulus-of-continuity-real-consumer-boundary}
For every accepted $\CauchyModulusOfContinuityUp$ carrier
$K=(S,T,\mu,F,R,E,H,C,P,N)$, every $\RealUp$ consumer factors through the
displayed $\RegSeqRatUp$ readbacks $R$ and the $\RealUp$ seal row $E$. The
consumer surface exposes only the source and target windows, the schedule
$\mu$, the transformer row $F$, the readbacks $R$, the seal $E$, and the
recorded $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows; it exposes no
quotient stream, host function equality, selected limit, or ambient
completeness.
\end{theorem}
\begin{proof}
Read the carrier inventory. The only real-facing coordinate is $E$, and it is
listed as the seal row reached from the target $\RegSeqRatUp$ readback.

Use the handoff theorem
\autoref{thm:cauchy-modulus-of-continuity-cauchy-handoff}. It shows that the
target readback has already passed through $S,\mu,F$, and $T$ before $R$ can
be consumed by a real-facing route.

Replay the seal route through $C$ and transport it through $H$. The package
row $P$ and the local name $N$ certify that the same displayed finite rows
source the read.

Thus every $\RealUp$ consumer factors through $R$ and $E$. The packet has no
coordinate from which to read a quotient stream, host function equality,
selected limit, or ambient completeness principle.
\end{proof}

\closureat{CauchyModulusOfContinuityUp}{seedStr}

\begin{closurestatus}{\CauchyModulusOfContinuityUp}
  \constructivestory{A $\CauchyModulusOfContinuityUp$ packet is generated from source and target $\StreamNameUp$ windows, a $\CauchyModulusUp$ threshold schedule for each requested target tolerance, a $\CauchyContinuousMapUp$ transformer row, $\RegSeqRatUp$ readbacks, a $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-modulus-of-continuity-carrier}, \autoref{thm:cauchy-modulus-of-continuity-namecert-obligations}, \autoref{thm:cauchy-modulus-of-continuity-cauchy-handoff}, and \autoref{thm:cauchy-modulus-of-continuity-real-consumer-boundary} bind the pointwise Cauchy-name continuity schedule and Real-consumer boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close uniform continuity, compactness, quotient stream equality, host function equality, selected limits, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, threshold-route exactness, Real-consumer factorization, and TasteGate nontriviality with field faithfulness for $S,T,\mu,F,R,E,H,C,P,N$.}
\end{closurestatus}
