\chapter{A Concrete Naming Certificate for $\PolishSpaceUp$}
\label{ch:concrete-instances-polishspace-namecert}
\origin{human}

Following Alexandrov and Urysohn, a Polish space is treated here as a complete
separable metric object whose admissible data are displayed by finite naming
routes rather than by ambient set-theoretic selection. The
$\PolishSpaceUp$ packet synthesizes the metric carrier of
\autoref{ch:concrete-instances-metric-namecert}, the completion handoff of
\autoref{ch:concrete-instances-completemetric-namecert}, the countable dense
surface of \autoref{ch:concrete-instances-separablemetric-namecert}, the
finite stream-window interface of
\autoref{ch:concrete-instances-streamname-namecert}, and the regular rational
readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}. Its
role is to expose the L10 complete-separable metric synthesis node without
claiming choice-selected dense points, quotient equality, open-cover
compactness, or a host-level completion principle.

\begin{definition}[Polish-space carrier]
\label{def:polish-space-carrier}
A $\PolishSpaceUp$ carrier is a finite $\BHist$ packet
$$
P=(M,K,D,S,R,W,H,C,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricSpaceUp$ row containing the admitted point-history
carrier, metric readbacks, distance classifier, and local metric
$\NameCert$.
\item $K$ is the $\CompleteMetricUp$ handoff row; it records the displayed
Cauchy-window and limit-seal route over the same metric carrier.
\item $D$ is the $\SeparableMetricUp$ row; it stores the countable dense
schedule as public finite name data, not as a choice function over arbitrary
balls.
\item $S$ is the $\StreamNameUp$ schedule that enumerates the inspected dense
names and the Cauchy-window requests made by downstream consumers.
\item $R$ is the $\RegSeqRatUp$ readback row used to observe finite rational
windows on the scheduled dense names and Cauchy approximants.
\item $W$ is the finite observation ledger joining requested tolerances,
stream positions, regular rational windows, metric-radius checks, and
completion handoff rows.
\item $H$ records componentwise $\hsame$ transport for $M,K,D,S,R,W$ and for
the local certificate rows.
\item $C$ records the displayed $\Cont$ routes from a metric-radius request to
the dense schedule, from a Cauchy-window request to the completion handoff,
and from either request to the regular rational readback.
\item $G$ is the $\Pkg$ provenance over $\MetricSpaceUp$,
$\CompleteMetricUp$, $\SeparableMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$,
$\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PolishSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only by transporting these displayed
rows to a common metric, complete-metric, separable-metric, stream-name, and
regular-readback surface. It has no coordinate for selected dense points,
quotient equality of completions, arbitrary open covers, or ambient host
sets.
\end{definition}

\begin{theorem}[Polish-space NameCert obligations]
\label{thm:polish-space-namecert-obligations}
For every accepted $\PolishSpaceUp$ carrier
$P=(M,K,D,S,R,W,H,C,G,N)$, the local $\NameCert_{\PolishSpaceUp}$ surface
consists exactly of six obligation rows:
\begin{enumerate}
\item carrier admission for the displayed metric, complete-metric,
separable-metric, stream-name, regular-readback, observation-ledger,
transport, continuation, provenance, and local-name rows;
\item classifier transport to a common $\MetricSpaceUp$ surface before either
the complete-metric or separable-metric row is consumed;
\item stability of the completion handoff $K$ and the countable dense schedule
$D$ under the componentwise $\hsame$ transports recorded in $H$;
\item exactness of the observation ledger $W$ as the only source of metric
radius checks, Cauchy windows, dense-name inspections, and regular rational
readbacks;
\item $\Cont$ replay from radius or Cauchy-window requests through $S,R,W$ to
the corresponding metric, completion, or dense-schedule row;
\item $\Pkg$ provenance and local $\NameCert$ naming for exactly the displayed
packet.
\end{enumerate}
No NameCert obligation is stored outside these six rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:polish-space-carrier}. The projection
exposes the metric row, complete-metric handoff, separable-metric dense
schedule, stream schedule, regular rational readback, observation ledger,
transport rows, continuation rows, provenance row, and local name.

The classifier route begins at the metric surface. The rows in $H$ transport
$M,K,D,S,R,W$ together, so the completion handoff and dense schedule are never
compared over different metric carriers.

The observation exactness row is exhausted by $W$. A metric-radius request, a
Cauchy-window request, and a dense-name inspection all read their finite
stream positions and regular rational observations through this ledger.

Finally replay $C$ and attach $G,N$. These rows route, source, and name the
already displayed packet; they do not introduce selected dense points,
quotient completion equality, arbitrary open covers, or ambient host sets.
Hence the six listed rows exhaust the local Polish-space naming obligations.
\end{proof}

\begin{theorem}[Polish-space StreamName dense handoff]
\label{thm:polish-space-streamname-countable-dense-handoff}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. Every
consumer that reads the countable dense surface must factor through the
displayed $\StreamNameUp$ schedule $S$, the finite observation ledger $W$, and
the $\RegSeqRatUp$ readback row $R$ before using the $\SeparableMetricUp$ row
$D$ or the $\CompleteMetricUp$ handoff $K$. Consequently the packet exports a
countable dense handoff by finite names and regular rational windows, not by a
choice-selected dense subset or a quotient-completion representative.
\end{theorem}
\begin{proof}
Start with a consumer of the dense surface. Carrier admission exposes $D$
only as a separable-metric row over the metric carrier $M$ and the stream
schedule $S$.

Read the requested dense-name index through $S$ and the finite ledger $W$.
The regular rational observation used by the consumer is then obtained through
$R$, so the handoff has a visible finite window before the dense row is
consumed.

If the same consumer also requests a completion read, the route passes through
$K$ after the same metric surface and observation ledger have been fixed.
The transports in $H$ keep the dense schedule, completion handoff, and metric
classifier on one admitted surface.

The remaining rows $C,G,N$ only replay, source, and name this finite route.
Since the carrier has no row for a choice-selected dense subset or a quotient
completion representative, the dense handoff can export only the displayed
stream-name and regular-readback data.
\end{proof}

\begin{theorem}[Polish-space observation-ledger exhaustion]
\label{thm:polish-space-observation-ledger-exhaustion}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. Every
$\MetricSpaceUp$, $\CompleteMetricUp$, $\SeparableMetricUp$, $\StreamNameUp$,
and $\RegSeqRatUp$ consumer read from $P$ factors through the finite
observation ledger $W$ together with the componentwise $\hsame$ rows $H$, the
displayed $\Cont$ replay rows $C$, the $\Pkg$ provenance row $G$, and the local
$\NameCert$ row $N$. In particular, dense-schedule reads and completion reads
cannot bypass $W$: the rows $D$ and $K$ are consumable only after the finite
stream windows in $S$ and regular rational readbacks in $R$ have been displayed
inside the observation ledger.
\end{theorem}
\begin{proof}
Project the accepted carrier as $P=(M,K,D,S,R,W,H,C,G,N)$. The projection
exposes the metric row, complete-metric handoff, separable-metric dense
schedule, stream-name schedule, regular rational readback, observation ledger,
transport, replay, provenance, and local naming rows.

Apply \autoref{thm:polish-space-namecert-obligations}. Its exactness row
identifies $W$ as the only source of metric-radius checks, Cauchy-window
requests, dense-name inspections, and regular rational readbacks.

A dense-schedule consumer reaches $D$ only through an index displayed by $S$
and an observation recorded in $W$. A completion consumer reaches $K$ only
after its Cauchy-window request has been recorded in the same ledger. In both
cases the inspected value is read back through $R$ before the metric,
completion, or separability row is consumed.

The remaining rows $H,C,G,N$ transport, replay, source, and name this finite
route. Since the carrier has no coordinate outside the displayed ledger route,
no consumer of $M,K,D,S,$ or $R$ can bypass $W$.
\end{proof}

\begin{theorem}[Polish-space root obligation package]
\label{thm:polish-space-root-obligation-package}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. Before any complete-separable metric synthesis is consumed, $P$ exposes exactly the $\MetricSpaceUp$ row $M$, the $\CompleteMetricUp$ row $K$, the $\SeparableMetricUp$ row $D$, the $\StreamNameUp$ row $S$, and the $\RegSeqRatUp$ row $R$, together with the finite observation ledger $W$, componentwise $\hsame$ transports $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $G$, and local $\NameCert$ row $N$.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:polish-space-carrier}. Its displayed rows are precisely the metric, complete, separable, stream, regular-readback, observation-ledger, transport, replay, provenance, and local naming rows.

Use \autoref{thm:polish-space-namecert-obligations} to read those rows as the local NameCert obligation package. It binds metric admission, completion handoff, dense schedule, stream windows, regular rational readback, and ledger exactness in one finite surface.

Finally apply \autoref{thm:polish-space-observation-ledger-exhaustion}. The root obligation package has no route around $W,H,C,G,N$, so every complete-separable consumer first sees exactly the five displayed analytic rows and their finite support.
\end{proof}

\begin{theorem}[Polish-space completion observation triad]
\label{thm:polish-space-completion-observation-triad}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. The complete-metric handoff $K$ and the separable dense schedule $D$ are both consumable only after the finite $\StreamNameUp$ observation ledger $S$, the $\RegSeqRatUp$ readback row $R$, and the support ledger $W$ have been displayed over the same metric row $M$. Thus every complete-separable consumer reads the triad
$$
S,R,W
$$
before either $K$ or $D$, and the packet exports no selected dense points, quotient completion equality, countable-choice schedule, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:polish-space-root-obligation-package}. It displays $M,K,D,S,R,W,H,C,G,N$ before the complete-separable synthesis can be consumed.

Apply \autoref{thm:polish-space-observation-ledger-exhaustion}. Dense-schedule reads and completion reads are both routed through $W$, and their finite windows and rational observations are supplied by $S$ and $R$.

The componentwise transport $H$ keeps $K$ and $D$ over the same metric row $M$, while $C,G,N$ replay, source, and name the route. Since no carrier coordinate stores selected dense points, quotient completion equality, a countable-choice schedule, or ambient $\RealUp$ completeness, none of those objects can be exported.
\end{proof}

\begin{theorem}[Polish-space complete-metric source lock]
\label{thm:polish-space-complete-metric-source-lock}
For an accepted $\PolishSpaceUp$ packet $P=(M,K,D,S,R,W,H,C,G,N)$, every read of the complete-metric handoff $K$ is locked to the source metric row $M$ after the finite observation rows $S,R,W$ have been displayed. The handoff may use the dense schedule $D$ only through the same observation route, and it cannot replace that route by quotient completion equality, selected dense representatives, countable choice, or completeness of an ambient $\RealUp$ object.
\end{theorem}
\begin{proof}
Project $P$ through \autoref{def:polish-space-carrier}. The row $K$ is a $\CompleteMetricUp$ handoff over the metric carrier $M$, not an independent completion object.

Use \autoref{thm:polish-space-namecert-obligations}. The classifier transport row fixes the common metric surface before $K$ or $D$ is read, and the exactness row identifies $W$ as the only source of Cauchy-window requests and regular rational readbacks.

Now apply \autoref{thm:polish-space-completion-observation-triad}. The rows $S$ and $R$ display the finite observations on which the handoff depends. Therefore a complete-metric consumer receives $K$ only as a source-locked finite route over $M$, with no additional quotient, selector, choice, or ambient-completeness coordinate.
\end{proof}

\begin{theorem}[Polish-space separable dense schedule handoff]
\label{thm:polish-space-separable-dense-schedule-handoff}
For an accepted $\PolishSpaceUp$ packet $P=(M,K,D,S,R,W,H,C,G,N)$, every read of the separable dense schedule $D$ is handed off only after the finite $\StreamNameUp$ schedule $S$, the $\RegSeqRatUp$ readback row $R$, and the observation ledger $W$ have been displayed. The dense schedule is therefore a finite NameCert route over $M$ and $K$, not a choice-selected dense subset, countable-choice enumeration, quotient-completion representative, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with a consumer of $D$. By \autoref{thm:polish-space-streamname-countable-dense-handoff}, the consumer must read the displayed stream schedule $S$, ledger $W$, and regular readback $R$ before using the separable-metric row.

The root obligation package fixes the surrounding rows $M,K,H,C,G,N$. Transport through $H$ keeps the dense schedule on the same metric carrier as the complete-metric handoff, and replay through $C$ records the finite request route.

Finally invoke \autoref{thm:polish-space-completion-observation-triad}. Since the carrier has no row for selected dense points, countable choice, quotient completion representatives, or ambient $\RealUp$ completeness, the only exported dense-schedule handoff is the displayed finite NameCert route.
\end{proof}

\begin{theorem}[Polish-space complete separable synthesis]
\label{thm:polish-space-complete-separable-synthesis}
Every accepted $\PolishSpaceUp$ packet synthesizes a $\CompleteSeparableMetricUp$ read over the same metric carrier named by $M$. The synthesis consumes the $\CompleteMetricUp$ handoff $K$, the $\SeparableMetricUp$ dense schedule $D$, the finite $\StreamNameUp$ windows $S$, the $\RegSeqRatUp$ readback $R$, and the ledger route $W,H,C,G,N$; it exports no selected dense points, quotient completion equality, countable-choice schedule, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the root obligation package of \autoref{thm:polish-space-root-obligation-package}. The metric row $M$ is fixed before both completion and separability are read, so the synthesis is over one displayed metric carrier.

The completion side is supplied by $K$, and the separability side is supplied by $D$. The dense schedule can be inspected only through $S$, while regular rational observations pass through $R$ after their finite windows have been displayed.

The ledger exhaustion theorem, \autoref{thm:polish-space-observation-ledger-exhaustion}, keeps both sides inside $W,H,C,G,N$. Since the carrier contains no selected dense-point row, quotient-completion equality, countable-choice coordinate, or ambient real-completeness row, the resulting complete separable metric read is exactly the finite synthesis surface named above.
\end{proof}

\begin{theorem}[Polish-space complete separable non-escape]
\label{thm:polish-space-complete-separable-nonescape}
Every $\CompleteSeparableMetricUp$ consumer of an accepted $\PolishSpaceUp$ packet factors through the finite route
$$
M,K,D,S,R,W,H,C,G,N.
$$
The route is forced by \autoref{thm:polish-space-namecert-obligations}, exhausted by \autoref{thm:polish-space-observation-ledger-exhaustion}, and repacked by \autoref{thm:polish-space-complete-separable-synthesis}. Hence the synthesis exports no selected dense points, quotient completion equality, countable-choice schedule, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a $\CompleteSeparableMetricUp$ consumer of an accepted packet. By \autoref{thm:polish-space-namecert-obligations}, the packet presents only the metric carrier $M$, completion handoff $K$, separable schedule $D$, stream windows $S$, regular readback $R$, and support rows $W,H,C,G,N$.

Use \autoref{thm:polish-space-observation-ledger-exhaustion}. It forces dense-schedule reads and completion reads through the observation ledger $W$, componentwise transport $H$, displayed replay $C$, provenance $G$, and local name $N$ before the consumer can use the complete or separable side.

Finally apply \autoref{thm:polish-space-complete-separable-synthesis}. The synthesis repacks the same rows as a complete-separable metric read over $M$. Since none of those rows stores selected dense points, quotient completion equality, a countable-choice schedule, open-cover compactness, or ambient $\RealUp$ completeness, no such datum can be exported by the consumer.
\end{proof}

\begin{theorem}[Polish-space L10 consumer boundary]
\label{thm:polish-space-l10-consumer-boundary}
An L10 consumer of an accepted $\PolishSpaceUp$ packet may import only the finite boundary consisting of $\MetricSpaceUp$, $\CompleteMetricUp$, $\SeparableMetricUp$, $\CompleteSeparableMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, the observation ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows. The boundary excludes selected dense points, quotient completion equality, countable choice, open-cover compactness, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the packet through \autoref{thm:polish-space-root-obligation-package}. This gives the finite L10 rows $M,K,D,S,R$ and the support rows $W,H,C,G,N$ before any downstream consumer can inspect the packet.

Use \autoref{thm:polish-space-complete-separable-synthesis}. It repacks the completion and separability sides as a $\CompleteSeparableMetricUp$ read over the same metric carrier while preserving the stream windows, regular readback, and ledger route.

The exclusion list follows from the carrier and ledger exactness. None of the displayed rows supplies a selected dense point, quotient-completion equality, countable-choice schedule, open-cover compactness principle, or ambient $\RealUp$ completeness datum, so an L10 consumer cannot cite any of those objects through $\PolishSpaceUp$.
\end{proof}

\begin{theorem}[Polish-space completion dense schedule obligation]
\label{thm:polish-space-completion-dense-schedule-obligation}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. Every completion-facing dense-schedule obligation exported from $P$ factors through the $\MetricSpaceUp$ row $M$, the $\CompleteMetricUp$ handoff $K$, the $\SeparableMetricUp$ schedule $D$, the $\StreamNameUp$ windows $S$, the $\RegSeqRatUp$ readback row $R$, the observation ledger $W$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $G$, and the local $\NameCert$ row $N$.

The obligation is exactly the finite route certified by \autoref{thm:polish-space-namecert-obligations}, constrained by \autoref{thm:polish-space-observation-ledger-exhaustion}, synthesized by \autoref{thm:polish-space-complete-separable-synthesis}, and bounded at L10 by \autoref{thm:polish-space-l10-consumer-boundary}. It exposes no choice-selected dense point, quotient completion, countable-choice schedule, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:polish-space-carrier}. The displayed analytic rows are precisely $M,K,D,S,R$, and the support rows are $W,H,C,G,N$.

Apply \autoref{thm:polish-space-namecert-obligations} to read those rows as local NameCert obligations. The exactness clause makes $W$ the only route for metric-radius checks, Cauchy windows, dense-name inspections, and regular rational readbacks.

Use \autoref{thm:polish-space-observation-ledger-exhaustion} and \autoref{thm:polish-space-complete-separable-synthesis}. They force the completion side and dense side through the same finite stream and readback route before the complete-separable metric synthesis can be consumed.

Finally apply \autoref{thm:polish-space-l10-consumer-boundary}. Since the boundary contains no coordinate for selected dense points, quotient completions, countable choice, open-cover compactness, or ambient real completeness, the exported obligation is exactly the displayed finite route.
\end{proof}

\begin{theorem}[Polish-space metric readback stability]
\label{thm:polish-space-metric-readback-stability}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. Suppose a downstream consumer transports the metric row, completion handoff, dense schedule, stream windows, regular rational readback, and ledger rows along the componentwise $\hsame$ data recorded in $H$ and replays the same request through the displayed $\Cont$ routes in $C$. Then the transported packet preserves the same $\MetricSpaceUp$ readback boundary for $M$, the same $\CompleteMetricUp$ and $\SeparableMetricUp$ handoff surface for $K,D$, and the same $\StreamNameUp$ and $\RegSeqRatUp$ finite observations through $S,R,W,G,N$.

Thus metric readback stability is a finite NameCert property of $P$ and not a quotient-completion equality, selected dense representative, countable-choice enumeration, or host-level equality of metric spaces.
\end{theorem}
\begin{proof}
Begin with the carrier projection and the componentwise transport row $H$. The row transports $M,K,D,S,R,W$ together with the local certificate data, so a metric readback cannot move independently from the completion or dense-schedule rows.

Apply \autoref{thm:polish-space-namecert-obligations}. Its classifier-transport and stability clauses require $K$ and $D$ to remain over the transported metric surface before either row is consumed.

Next use \autoref{thm:polish-space-observation-ledger-exhaustion}. Every finite observation read by the transported consumer still passes through $S,R,W$, and the replay row $C$ records the same request route.

The L10 boundary theorem, \autoref{thm:polish-space-l10-consumer-boundary}, supplies the exclusion list. Because no accepted packet coordinate stores quotient completion equality, selected dense representatives, countable-choice enumerations, or host-level metric equality, the stability claim is only the displayed finite transport-and-replay property.
\end{proof}

\begin{theorem}[Polish-space L10 root unblock package]
\label{thm:polish-space-l10-root-unblock-package}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. The L10 root obligation package exported by $P$ consists of the completion-dense schedule route of \autoref{thm:polish-space-completion-dense-schedule-obligation}, the metric readback stability route of \autoref{thm:polish-space-metric-readback-stability}, the finite observation exhaustion of \autoref{thm:polish-space-observation-ledger-exhaustion}, the complete-separable synthesis of \autoref{thm:polish-space-complete-separable-synthesis}, and the consumer boundary of \autoref{thm:polish-space-l10-consumer-boundary}.

Consequently every downstream complete-separable metric chapter may import only $\MetricSpaceUp$, $\CompleteMetricUp$, $\SeparableMetricUp$, $\CompleteSeparableMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows through the displayed tuple $P=(M,K,D,S,R,W,H,C,G,N)$. The package does not supply choice-selected dense points, quotient completions, countable-choice schedules, host equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First assemble the finite route. The completion-dense schedule obligation displays $M,K,D,S,R,W,H,C,G,N$ before any dense or complete read leaves the chapter boundary.

Next apply metric readback stability. It shows that transported consumers still read the same metric, completion, dense-schedule, stream, regular-readback, ledger, replay, provenance, and naming rows.

The observation-ledger and complete-separable synthesis theorems then repack this route as a $\CompleteSeparableMetricUp$ surface over the metric row $M$. This is the only synthesis route available to an L10 consumer.

Finally invoke the consumer boundary theorem. It permits the listed BEDC rows and refuses selected dense points, quotient completions, countable choice, host equality, open-cover compactness, and ambient real completeness, so the root unblock package is exactly the displayed finite package.
\end{proof}

\falsifiablePrediction{An accepted $\PolishSpaceUp$ consumer that reaches a
$\SeparableMetricUp$, $\CompleteMetricUp$, or $\MetricSpaceUp$ row without
reading the displayed $\StreamNameUp$ schedule, finite observation ledger,
$\RegSeqRatUp$ readback, componentwise $\hsame$ transports, $\Cont$ routes,
$\Pkg$ provenance, and local $\NameCert$ row refutes the carrier surface.}

\independenceWitness{metric, completemetric, separablemetric, streamname,
regseqrat: no listed sibling supplies the whole Polish packet
$P=(M,K,D,S,R,W,H,C,G,N)$, because each sibling contributes only the distance
carrier, completion handoff, dense schedule, stream schedule, or rational
readback while this chapter binds the complete-separable metric synthesis
route with transport, replay, provenance, and local naming.}

\closureat{PolishSpaceUp}{seedStr}

\begin{closurestatus}{\PolishSpaceUp}
  \constructivestory{A $\PolishSpaceUp$ packet is generated from a $\MetricSpaceUp$ carrier, a $\CompleteMetricUp$ handoff, a $\SeparableMetricUp$ countable dense schedule, $\StreamNameUp$ finite windows, $\RegSeqRatUp$ regular rational readbacks, an observation ledger, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:polish-space-carrier}, \autoref{thm:polish-space-namecert-obligations}, \autoref{thm:polish-space-streamname-countable-dense-handoff}, and \autoref{thm:polish-space-observation-ledger-exhaustion} seed the L10 complete-separable metric synthesis route over $\MetricSpaceUp$, $\CompleteMetricUp$, $\SeparableMetricUp$, $\StreamNameUp$, and $\RegSeqRatUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim choice-selected dense points, quotient completion equality, arbitrary open-cover compactness, host set equality, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the displayed carrier and prove the finite NameCert obligation surface and stream-name dense handoff.}
\end{closurestatus}
