\chapter{A Concrete Naming Certificate for $\NormedRealLineUp$}
\label{ch:concrete-instances-normed-real-line-namecert}
\origin{human}

Following Bishop and Bridges' constructive normed-space analysis, the $\NormedRealLineUp$ packet records the real line as a normed object only through the regular Cauchy absolute-value route. It binds the real seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic observation core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the absolute-value packet of \autoref{ch:concrete-instances-regularcauchyabs-namecert}, and the metric interface of \autoref{ch:concrete-instances-metric-namecert}. The certificate names the RealUp line equipped with that displayed norm route; it does not assert RealUp completeness, trichotomy, quotient equality of names, or a host norm function.

\begin{definition}[Normed real line carrier]
\label{def:normed-real-line-carrier}
A $\NormedRealLineUp$ carrier is a finite $\BHist$ packet
$$
L=(R,S,D,A,M,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $R$ is the $\RealUp$ seal row for the underlying real-line object.
\item $S$ is the $\RegSeqRatUp$ source and readback row through which the real seal is observed by regular rational names.
\item $D$ is the joined $\StreamNameUp$ and $\DyadicRatCoreUp$ observation ledger recording the finite windows and dyadic endpoints read from $S$.
\item $A$ is the $\RegularCauchyAbsUp$ norm row, applied only to the displayed regular Cauchy name and its dyadic observations.
\item $M$ is the $\MetricSpaceUp$ distance-and-norm interface that reads the distance of the real line through the same absolute-value handoff.
\item $H$ records componentwise $\hsame$ transport for $R,S,D,A,M$ and for the structural rows.
\item $C$ records the displayed $\Cont$ routes from real-seal requests to regular windows, from those windows to dyadic observations, from the observations to the absolute-value row, and from that row to the metric interface.
\item $P$ records $\Pkg$ provenance over $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyAbsUp$, $\MetricSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NormedRealLineUp}$ row.
\end{enumerate}
The carrier contains no coordinate for a selected host real, quotient equality of real names, trichotomy, a host norm function, or a completeness principle for $\RealUp$.
\end{definition}

\begin{theorem}[Normed real line NameCert obligations]
\label{thm:normed-real-line-namecert-obligations}
For every accepted $\NormedRealLineUp$ carrier $L=(R,S,D,A,M,H,C,P,N)$, the local $\NameCert_{\NormedRealLineUp}$ surface consists exactly of carrier admission for the displayed real seal, regular rational source and readback, stream and dyadic observation ledger, regular Cauchy absolute-value norm row, metric distance-and-norm interface, componentwise transport, continuation replay, package provenance, and local naming row. No obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:normed-real-line-carrier}. The projection exposes the real seal $R$, the regular rational source and readback $S$, the observation ledger $D$, the absolute-value norm row $A$, the metric interface $M$, and the structural rows $H,C,P,N$.

The analytic obligation is the norm route. The row $A$ is already the displayed $\RegularCauchyAbsUp$ handoff over $S$ and $D$, so the certificate reads norm data only after the stream windows and dyadic endpoints have been displayed.

The metric obligation is then a consumer of the same handoff. The row $M$ receives its distance-and-norm interface through $A$, and the rows $H,C,P,N$ transport, replay, source, and name that finite route without adding a host norm function, quotient equality, trichotomy, or completeness.
\end{proof}

\begin{theorem}[Normed real line regular Cauchy norm handoff]
\label{thm:normed-real-line-regular-cauchy-norm-handoff}
Every norm-facing consumer of an accepted $\NormedRealLineUp$ carrier $L=(R,S,D,A,M,H,C,P,N)$ reaches the norm row only through the route
$$
R \longrightarrow S \longrightarrow D \longrightarrow A \longrightarrow M .
$$
Thus the exported norm route is the $\RegularCauchyAbsUp$ handoff over displayed $\StreamNameUp$ windows and $\DyadicRatCoreUp$ observations, not a separate host-level norm operation.
\end{theorem}
\begin{proof}
Begin with a norm-facing consumer. Carrier admission gives a single real seal row $R$ and a single regular rational source and readback row $S$ through which $R$ is observed.

Read the finite observations next. The observation ledger $D$ joins the $\StreamNameUp$ windows and $\DyadicRatCoreUp$ endpoint rows for the same regular name, so the absolute-value row cannot be reached without first displaying those windows and endpoints.

Apply the $\RegularCauchyAbsUp$ row $A$ to the displayed observations. The metric interface $M$ is downstream of $A$, and the continuation rows in $C$ record this order for every consumer route. Hence the norm handoff is exactly the displayed regular Cauchy absolute-value route.
\end{proof}

\begin{theorem}[Normed real line non-escape boundary]
\label{thm:normed-real-line-non-escape}
No accepted $\NormedRealLineUp$ packet exports data outside the tuple $R,S,D,A,M,H,C,P,N$. In particular, the packet cannot be used to recover RealUp completeness, real trichotomy, quotient equality of names, a selected host real, or a host norm function.
\end{theorem}
\begin{proof}
Inspect the carrier in \autoref{def:normed-real-line-carrier}. Its only analytic data are the real seal, the regular rational source and readback, the stream and dyadic observations, the regular Cauchy absolute-value row, and the metric interface.

Use \autoref{thm:normed-real-line-namecert-obligations} to exhaust the local certificate. Every named obligation is a projection of those rows or a transport, continuation, provenance, or naming route for those rows.

Finally combine this exhaustion with \autoref{thm:normed-real-line-regular-cauchy-norm-handoff}. Any norm-facing or metric-facing consumer must pass through $R,S,D,A,M,H,C,P,N$, so no unlisted completeness, trichotomy, quotient, selected-real, or host-norm object can be extracted.
\end{proof}

\begin{closurestatus}{\NormedRealLineUp}
  \constructivestory{A $\NormedRealLineUp$ packet is generated from a RealUp seal row, a RegSeqRat source and readback row, StreamName and DyadicRatCore observations, a RegularCauchyAbs norm row, a MetricSpace distance-and-norm interface, componentwise transport, continuation replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:normed-real-line-carrier}, \autoref{thm:normed-real-line-namecert-obligations}, \autoref{thm:normed-real-line-regular-cauchy-norm-handoff}, and \autoref{thm:normed-real-line-non-escape} seed the finite normed real-line route through $\RegularCauchyAbsUp$ and $\MetricSpaceUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, RealUp completeness, trichotomy, quotient equality of real names, selected host reals, host norm functions, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, regular Cauchy norm handoff, metric-interface routing, transport stability, provenance, and non-escape for the same finite packet.}
\end{closurestatus}
