\chapter{A Concrete Naming Certificate for $\MetricClosedBallUp$}
\label{ch:concrete-instances-metricclosedball-namecert}
\origin{human}

Following Kelley and Bishop--Bridges, the $\MetricClosedBallUp$ packet records center-radius closed balls as finite BEDC NameCert rows. It sits beside the open-ball carrier of \autoref{ch:concrete-instances-metricball-namecert}, but its membership row is read through non-strict ordered-real comparison over MetricDistanceWitness, Real/Rat order, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows rather than through an ambient closed subset.

\begin{definition}[MetricClosedBall carrier]
\label{def:metric-closed-ball-carrier}
A $\MetricClosedBallUp$ carrier is a finite $\BHist$ packet
$$
Q=(X,d,c,r,\rho,m,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\MetricSpaceUp$ carrier row with its point classifier and metric source data.
\item $d$ is the $\mathsf{MetricDistanceWitness}$ row read from $X$ and valued in the $\RealUp$ distance surface.
\item $c$ is the center row, classified as a point of the carrier named by $X$.
\item $r$ is a $\RatUp$ or $\RealUp$ radius row, according to the chosen radius ledger.
\item $\rho$ is the radius order ledger for $r$, recording nonnegativity and, when the packet is handed to an open-ball consumer, the separate positive-radius comparison needed by $\MetricBallUp$.
\item $m$ is the closed-membership and distance-comparison row. For a displayed point $x$, it records the comparison $d(c,x)\leq_{\mathsf R}r$ and names this comparison as the $\mathsf{MetricClosedBall}_d(c,r,\rho)$ membership read.
\item $H$ records the $\hsame$ transports for the carrier, distance witness, center, radius, radius order ledger, and closed-membership comparison row.
\item $C$ records the $\Cont$ routes that replay distance evaluation, non-strict radius comparison, closed-membership transport, and boundary handoff to open-ball rows when a strict comparison is separately supplied.
\item $P$ is the $\Pkg$ provenance over $\MetricClosedBallUp$, $\MetricBallUp$, $\MetricSpaceUp$, $\RealUp$, $\RealAlgOrderUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\MetricClosedBallUp}$ row.
\end{enumerate}
The accepted carrier contains no ambient powerset coordinate, no topology-closure predicate, no quotient equality test on points or radii, no compactness witness, and no generated-open field.
\end{definition}
\leanchecked{BEDC.Derived.MetricClosedBallUp.MetricClosedBallTasteGate\_single\_carrier\_alignment}

\begin{theorem}[MetricClosedBall NameCert obligations]
\label{thm:metric-closed-ball-namecert-obligations}
For an accepted packet $Q=(X,d,c,r,\rho,m,H,C,P,N)$, the local $\NameCert_{\MetricClosedBallUp}$ obligation surface consists exactly of carrier admission, classifier transport, radius nonnegativity stability, positive-radius stability for strict-boundary handoff when that handoff is requested, closed-membership transport, boundary comparison with $\MetricBallUp$, and ledger non-escape for the displayed rows $X,d,c,r,\rho,m,H,C,P,N$.
\end{theorem}
\begin{proof}
Carrier admission reads $X$ as the metric carrier and $d$ as the distance witness over that carrier. The center row $c$ and radius row $r$ are admitted only relative to those source rows, while $\rho$ supplies the displayed ordered-real radius ledger.

Classifier transport is supplied by $H$. Transporting the carrier, distance witness, center, radius, and radius ledger moves the comparison data in $m$ to the transported copy without introducing a second point classifier or a second radius equality test.

Closed-membership transport is the non-strict distance-comparison part of the same ledger. The row $m$ names the predicate $d(c,x)\leq_{\mathsf R}r$, while $C$ replays the route from distance evaluation to ordered-real comparison.

Boundary comparison with $\MetricBallUp$ is conditional on a strict comparison row. When an open-ball consumer supplies the positive-radius and strict-membership data required by \autoref{def:metric-ball-carrier}, the route passes through $\MetricBallUp$; otherwise the closed-ball packet exports only its non-strict comparison row.

Ledger non-escape follows by inspecting the carrier. Every exported read is one of $X,d,c,r,\rho,m,H,C,P,N$, so no ambient subset, topology closure, quotient equality test, compactness witness, or generated-open field can be recovered from the packet.
\end{proof}
\leanchecked{BEDC.Derived.MetricClosedBallUp.MetricClosedBallCarrier\_namecert\_obligations}

\begin{theorem}[MetricClosedBall boundary handoff]
\label{thm:metric-closed-ball-metricball-boundary-handoff}
Every open-ball consumer of a center-radius strict comparison passes through $\MetricBallUp$, while every closed-ball consumer of $Q=(X,d,c,r,\rho,m,H,C,P,N)$ can read only the non-strict comparison row $d(c,x)\leq_{\mathsf R}r$ together with its transports and replay routes. The $\MetricClosedBallUp$ packet therefore does not recover ambient subsets, quotient point equality, compactness, or topology closure.
\end{theorem}
\begin{proof}
Start with the accepted closed-ball carrier of \autoref{def:metric-closed-ball-carrier}. Its membership coordinate is $m$, and $m$ records only the non-strict comparison $d(c,x)\leq_{\mathsf R}r$.

If a downstream consumer asks for a strict center-radius ball, the required predicate is not $m$. It is the open comparison row used by \autoref{def:metric-ball-carrier}, so the request factors through the $\MetricBallUp$ packet and its positive-radius ledger.

If the downstream consumer remains closed-ball facing, the only exported comparison is the non-strict row transported by $H$ and replayed by $C$. Package provenance $P$ and the local naming row $N$ identify this as the $\MetricClosedBallUp$ surface, not as a topology closure or compactness object.

Thus the handoff is exact at the boundary: strict consumers use $\MetricBallUp$, and closed consumers receive no coordinate from which to reconstruct an ambient subset, quotient point equality, compactness proof, or generated topology closure.
\end{proof}
\leanchecked{BEDC.Derived.MetricClosedBallUp.MetricClosedBallCarrier\_metricball\_boundary\_handoff}

\begin{theorem}[MetricClosedBall carrier obligations]
\label{thm:metricclosedball-carrier-obligations}
For an accepted $\MetricClosedBallUp$ packet $Q=(X,d,c,r,\rho,m,H,C,P,N)$, carrier admission is exactly the simultaneous admission of the $\MetricSpaceUp$ row $X$, the $\mathsf{MetricDistanceWitness}$ row $d$, the center row $c$, the radius row $r$, the nonnegative radius ledger $\rho$, the closed-membership comparison row $m$, and the support rows $H,C,P,N$. The packet exports no ambient closed subset, topology-closure predicate, compactness witness, quotient point equality, quotient radius equality, or generated-open field.
\end{theorem}
\begin{proof}
Read the carrier tuple of \autoref{def:metric-closed-ball-carrier}. The rows $X,d,c,r,\rho,m$ are the only mathematical rows admitted before the structural rows appear.

The support rows do not add a second carrier. The row $H$ transports those displayed coordinates, $C$ replays their distance and comparison route, $P$ records the named provenance, and $N$ gives the local certificate name.

Since no tuple coordinate stores an ambient subset, closure predicate, compactness object, quotient equality test, or generated-open field, none of those objects can be projected from an accepted packet.
\end{proof}

\begin{theorem}[MetricClosedBall radius classifier stability]
\label{thm:metricclosedball-radius-classifier-stability}
Let $Q=(X,d,c,r,\rho,m,H,C,P,N)$ and $Q'=(X',d',c',r',\rho',m',H',C',P',N')$ be accepted $\MetricClosedBallUp$ packets whose carrier, distance, center, radius, and radius-ledger rows are paired by the displayed componentwise $\hsame$ data in $H$ and $H'$. Then the closed-membership classifier transported by $H$ and replayed by $C$ carries the non-strict comparison row $d(c,x)\leq_{\mathsf R}r$ to the corresponding row $d'(c',x')\leq_{\mathsf R}r'$. The transport preserves the radius nonnegativity ledger and the optional positive-radius handoff data used by $\MetricBallUp$.
\end{theorem}
\begin{proof}
Start from the displayed $\hsame$ rows. They pair the metric carrier, distance witness, center, radius, and radius ledger componentwise, so the radius classifier is not transported by a host equality of reals or by a quotient radius comparison.

Now replay the closed-membership route. The row $C$ reads distance evaluation first and then the non-strict ordered-real comparison in $m$, so transporting $d,c,r,\rho$ transports the comparison row itself.

For strict-boundary consumers, the positive-radius data remain a separate part of $\rho$. Thus the same transport preserves the closed non-strict classifier and, when present, the positive-radius handoff required before the request can pass to $\MetricBallUp$.
\end{proof}
\leanchecked{BEDC.Derived.MetricClosedBallUp.MetricClosedBallCarrier\_radius\_classifier\_stability}

\begin{theorem}[MetricClosedBall RealAlgOrder boundary]
\label{thm:metricclosedball-realalgorder-boundary}
Every $\RealAlgOrderUp$ boundary read made by an accepted $\MetricClosedBallUp$ packet factors through the displayed distance witness $d$, the $\RealUp$ or $\RatUp$ radius row $r$, the radius ledger $\rho$, and the closed-membership comparison row $m$. If a downstream consumer asks for a strict boundary comparison, the route first passes through the $\MetricBallUp$ handoff of \autoref{thm:metric-closed-ball-metricball-boundary-handoff}; otherwise it remains the non-strict RealAlgOrder comparison $d(c,x)\leq_{\mathsf R}r$ carried by $m$.
\end{theorem}
\begin{proof}
Inspect the comparison coordinates of $Q$. The distance side is the $\RealUp$-valued witness row $d$, the radius side is $r$, and the admissible radius facts are exactly those recorded in $\rho$.

The non-strict order read is $m$. It routes the displayed distance value and displayed radius through the RealAlgOrder or Rat-order rows named by $P$, then returns the membership classifier $d(c,x)\leq_{\mathsf R}r$.

If a strict comparison is requested, the packet must use the separate positive-radius and strict-membership data described in \autoref{thm:metric-closed-ball-metricball-boundary-handoff}. That request therefore factors through $\MetricBallUp$ and does not create a second closed-ball boundary.

Thus every RealAlgOrder-facing read is either the displayed non-strict comparison row $m$ or the explicit $\MetricBallUp$ strict-boundary handoff. No host closed subset, topology closure, quotient point equality, compactness witness, or generated-open field is exported.
\end{proof}
\leanchecked{BEDC.Derived.MetricClosedBallUp.MetricClosedBallCarrier\_realalgorder\_boundary}

\begin{theorem}[MetricClosedBall boundary classifier transport]
\label{thm:metricclosedball-boundary-classifier-transport}
Let $Q=(X,d,c,r,\rho,m,H,C,P,N)$ and $Q'=(X',d',c',r',\rho',m',H',C',P',N')$ be accepted $\MetricClosedBallUp$ packets whose carrier, distance, center, radius, and radius-ledger rows are classified componentwise by the displayed $\hsame$ data. Then the boundary row $m$ carrying $d(c,x)\leq_{\mathsf R}r$ transports through $H$ and replays through $C$ to the boundary row $m'$ carrying $d'(c',x')\leq_{\mathsf R}r'$. The transport introduces no topology closure, compactness witness, quotient point equality, or ambient subset data.
\end{theorem}
\begin{proof}
Project the two packets. The only rows that can affect the closed boundary classifier are the metric carrier, distance witness, center, radius, radius ledger, membership row, and their transport and continuation data.

Use the classifier definition from \autoref{def:metric-closed-ball-carrier}. The row $m$ is precisely the non-strict comparison $d(c,x)\leq_{\mathsf R}r$, and the corresponding row in $Q'$ is $m'$.

Apply radius classifier stability from \autoref{thm:metricclosedball-radius-classifier-stability}. The componentwise $\hsame$ data preserve the radius ledger and the comparison row under transport.

Finally replay the RealAlgOrder boundary route of \autoref{thm:metricclosedball-realalgorder-boundary}. Since the carrier inventory has no topology-closure, compactness, quotient-point, or ambient-subset coordinate, the transported classifier remains exactly the displayed closed-boundary row.
\end{proof}
\leanchecked{BEDC.Derived.MetricClosedBallUp.MetricClosedBallCarrier\_boundary\_classifier\_transport}

\closureat{MetricClosedBallUp}{obligationStr}

\begin{closurestatus}{\MetricClosedBallUp}
  \constructivestory{A $\MetricClosedBallUp$ packet is generated from a MetricSpace carrier row, a MetricDistanceWitness row, a center row, a RatUp or RealUp radius row, a nonnegative radius ledger with optional positive-radius handoff data, a closed-membership comparison row, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:metric-closed-ball-carrier}, \autoref{thm:metric-closed-ball-namecert-obligations}, \autoref{thm:metric-closed-ball-metricball-boundary-handoff}, \autoref{thm:metricclosedball-carrier-obligations}, \autoref{thm:metricclosedball-radius-classifier-stability}, \autoref{thm:metricclosedball-realalgorder-boundary}, and \autoref{thm:metricclosedball-boundary-classifier-transport} bind the finite non-strict center-radius ball obligation surface and its strict-boundary handoff to $\MetricBallUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim compactness, full metric topology, topology closure, quotient equality for metric points or radii, ambient subsets, Lean verification, or bridge checking.}
  \upgradepath{Formal verification can encode carrier admission, closed-membership transport, radius nonnegativity stability, strict-boundary handoff, and ledger non-escape for BEDC.Derived.MetricClosedBallUp.}
\end{closurestatus}
