\chapter{A Concrete Naming Certificate for $\RegularCauchyTailEstimateUp$}
\label{ch:concrete-instances-regularcauchytailestimate-namecert}
\origin{human}

Following Bishop and Bridges' constructive-analysis treatment of regular
Cauchy names, the $\RegularCauchyTailEstimateUp$ packet records explicit
finite tail-estimate data before a $\RealUp$ seal is consumed. It sits between
the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert},
the finite window surface of \autoref{ch:concrete-instances-streamname-namecert},
the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert},
the real seal of \autoref{ch:concrete-instances-real-namecert}, and the
modulus-facing route of \autoref{ch:concrete-instances-realcauchymodulus-namecert}.
The packet names the finite rows a consumer must inspect for a requested tail
tolerance; it is not a quotient stream, a selected limit, a host real equality
principle, or an ambient completeness theorem.

\begin{definition}[Regular Cauchy tail estimate carrier]
\label{def:regular-cauchy-tail-estimate-carrier}
A $\RegularCauchyTailEstimateUp$ carrier is a finite $\BHist$ packet
$$
T=(M,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the modulus-threshold row. For each requested tail tolerance it
records the finite index after which the regular Cauchy estimate is allowed to
be read.
\item $W$ is the $\StreamNameUp$ window row whose finite observations are
inspected at and beyond the threshold stored in $M$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row naming the dyadic error
budget used by the tail estimate.
\item $R$ is the $\RegSeqRatUp$ readback row reached from the window $W$ under
the threshold and tolerance rows $M,D$.
\item $E$ is the $\RealUp$ seal row that may be consumed only after the
threshold, window, tolerance, and regular readback rows have been replayed.
\item $H$ records componentwise $\hsame$ transport for $M,W,D,R,E$ and for the
continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tolerance request through
$M$, $W$, $D$, $R$, and then $E$.
\item $P$ is the $\Pkg$ provenance over $\RealCauchyModulusUp$,
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$,
$\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyTailEstimateUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only by transporting the displayed
modulus threshold, finite window, dyadic tolerance, regular readback, real seal,
continuation, provenance, and local naming rows to a common finite surface. It
has no coordinate for quotient streams, host real equality, selected limits,
choice, trichotomy, open-cover compactness, or ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyTailEstimateUp.RegularCauchyTailEstimateTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy tail estimate NameCert obligations]
\label{thm:regular-cauchy-tail-estimate-namecert-obligations}
For every accepted $\RegularCauchyTailEstimateUp$ carrier
$T=(M,W,D,R,E,H,C,P,N)$, the local
$\NameCert_{\RegularCauchyTailEstimateUp}$ surface consists exactly of five
obligation rows:
\begin{enumerate}
\item carrier admission for the displayed modulus threshold, finite
$\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance, $\RegSeqRatUp$ readback,
$\RealUp$ seal, transport, continuation, provenance, and local name;
\item classifier transport to a common $\RealCauchyModulusUp$,
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ finite
surface;
\item stability of $M,W,D,R,E$ under the componentwise $\hsame$ rows recorded
in $H$;
\item seal-route exactness requiring every real-facing read to pass through
$M,W,D,R,E$ in that order;
\item refusal rows excluding quotient streams, host real equality, choice,
trichotomy, selected limits, open-cover compactness, and ambient completeness.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:regular-cauchy-tail-estimate-carrier}. The projection exposes
exactly the modulus threshold, finite window, dyadic tolerance, regular
readback, real seal, transport rows, continuation row, provenance row, and
local naming row.

Classifier transport is componentwise. The rows in $H$ move the five
mathematical coordinates $M,W,D,R,E$ and the administrative coordinates
$C,P,N$ to the same finite comparison surface.

Seal-route exactness is read from the displayed continuation row. A tail
tolerance request first reaches the threshold row $M$, then the finite window
$W$, then the dyadic tolerance row $D$, then the regular readback $R$, and only
then the real seal $E$.

The refusal rows are exhausted by the carrier inventory. Since the packet has
no coordinate for quotient stream equality, host real equality, choice,
trichotomy, selected limits, open-cover compactness, or completeness, no local
NameCert obligation can export those data.
\end{proof}

\begin{theorem}[Regular Cauchy tail estimate Real seal route]
\label{thm:regular-cauchy-tail-estimate-real-seal-route}
For every accepted $\RegularCauchyTailEstimateUp$ carrier
$T=(M,W,D,R,E,H,C,P,N)$, every $\RealUp$ seal consumer of $E$ factors through
the modulus threshold $M$, the finite $\StreamNameUp$ window $W$, the
$\DyadicRatCoreUp$ tolerance row $D$, the $\RegSeqRatUp$ readback $R$, and the
$\RealUp$ seal row $E$ before it can inspect the transport, continuation,
provenance, and local naming rows $H,C,P,N$. No consumer route can bypass
$M,W,D,R,E$ or read a quotient stream, a selected host limit, host real
equality, choice, trichotomy, open-cover compactness, or ambient completeness.
\end{theorem}
\begin{proof}
Start with a real-facing consumer of $E$. Carrier admission lists $E$ only as
the seal row reached from the regular readback coordinate $R$.

Replay the continuation row $C$. Its route sends a tolerance request first to
the threshold row $M$, uses $M$ to choose the finite window reads in $W$, checks
the dyadic tolerance row $D$, and then reaches the regular readback $R$.

Transport through $H$ preserves this order of displayed dependencies. The
package row $P$ and local name $N$ record provenance and naming for the same
finite packet; they do not add a second seal coordinate.

Thus every $\RealUp$ seal consumer factors through $M,W,D,R,E$ before
$H,C,P,N$. The carrier contains no coordinate from which a bypass route could
obtain quotient streams, selected limits, host equality, choice, trichotomy,
open-cover compactness, or completeness.
\end{proof}

\closureat{RegularCauchyTailEstimateUp}{seedStr}

\begin{closurestatus}{\RegularCauchyTailEstimateUp}
  \constructivestory{A $\RegularCauchyTailEstimateUp$ packet is generated from a $\RealCauchyModulusUp$ threshold row, a finite $\StreamNameUp$ window, a $\DyadicRatCoreUp$ tolerance row, a $\RegSeqRatUp$ readback, a $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-tail-estimate-carrier}, \autoref{thm:regular-cauchy-tail-estimate-namecert-obligations}, and \autoref{thm:regular-cauchy-tail-estimate-real-seal-route} bind the finite tail-estimate carrier, local NameCert obligations, and real-seal factorization route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient streams, host real equality, choice, trichotomy, selected limits, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, stability, Real-seal route exactness, refusal rows, and TasteGate nontriviality with field faithfulness for $M,W,D,R,E,H,C,P,N$.}
\end{closurestatus}
