\chapter{A Concrete Naming Certificate for $\RingOfIntegersUp$}
\label{ch:concrete-instances-ringofintegers-namecert}

The ring-of-integers interface $\RingOfIntegersUp$ packages the integral closure of $\IntUp$ inside a number-field carrier. It depends on $\NameCert_{\NumFieldUp}$ (\autoref{ch:concrete-instances-numfield-namecert}) and $\NameCert_{\IntUp}$ (\autoref{ch:concrete-instances-int-namecert}).

\section{Carrier definition}
\label{sec:ringofintegers-carrier}

\begin{definition}[RingOfIntegers Dedekind-source carrier]\label{def:ringofintegers-dedekind-source-carrier}
A $\RingOfIntegersUp$ Dedekind-source carrier is a finite displayed
$\mathsf{BHist}$ packet
$$
\mathcal O=(\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho)
$$
over $\NameCert_{\NumFieldUp}$ and $\NameCert_{\IntUp}$. The row
$\mathcal N$ is the accepted number-field carrier row, and $\mathcal Z$ is the
accepted embedded integer row read through $\NameCert_{\IntUp}$ inside the same
field-operation boundary. The row $\eta$ records the displayed embedding
provenance from the integer source into the number-field source.

The finite ledger $E$ lists integral-equation rows over the visible field
addition, multiplication, zero, one, and negation operations supplied by
$\mathcal N$, with coefficients read from $\mathcal Z$. The classifier row
$\kappa$ records the $\hsame$ transports for the number-field carrier, embedded
integer rows, field-operation endpoints, and every equation row in $E$. The row
$\tau$ is the finite $\Cont$ provenance tying the equation ledger to the two
dependency certificates, and $\rho$ is the shared $\Pkg$ provenance. No host
quotient of algebraic integers, host polynomial equality, or ambient choice of a
number-field model is a field of the carrier.
\end{definition}

\section{The certificate}
\label{sec:ringofintegers-certificate}

\begin{theorem}[RingOfIntegers integral-closure obligation surface]\label{thm:ringofintegers-integral-closure-obligation-surface}
The $\RingOfIntegersUp$ root obligation surface consists of the
Dedekind-source carrier of
\autoref{def:ringofintegers-dedekind-source-carrier}, its classifier
$\kappa$, the finite integral-equation ledger $E$, the transport rows for
$\mathcal N$, $\mathcal Z$, $\eta$, and $E$, and the no-host-quotient ledger
recording that integral closure is read only from displayed $\mathsf{BHist}$,
$\hsame$, $\Cont$, and $\Pkg$ data. These rows form the root
$\NameCert_{\RingOfIntegersUp}$ obligation surface over
$\NameCert_{\NumFieldUp}$ and $\NameCert_{\IntUp}$.

Every accepted root row projects to the number-field carrier row, the embedded
integer row, the integral-equation ledger, classifier transport, continuation
provenance, and package provenance listed above. Conversely, any finite row
family with exactly these fields repacks as a $\RingOfIntegersUp$ obligation
surface.
\end{theorem}
\begin{proof}
Read the two dependency certificates first. The $\NumFieldUp$ certificate
supplies the visible field carrier and operation endpoints used by
$\mathcal N$, while the $\IntUp$ certificate supplies the embedded integer row
and the coefficient rows used by $\mathcal Z$ and $\eta$.

Project the carrier of
\autoref{def:ringofintegers-dedekind-source-carrier}. Its visible fields are
precisely $\mathcal N$, $\mathcal Z$, $\eta$, the integral-equation ledger
$E$, the classifier row $\kappa$, the continuation row $\tau$, and the package
row $\rho$. The no-host-quotient clause in the definition excludes any additional
ambient quotient or host polynomial-equality witness.

It remains to check the equation ledger. Induct over the finite ledger $E$. The
empty ledger contributes no integral equation and leaves only the dependency,
classifier, continuation, and package rows. In the cons step, the head equation
is projected to its displayed field-operation endpoints and integer-coefficient
rows, while the induction hypothesis projects the tail ledger.

The same induction gives the reverse packaging. Given the listed rows, rebuild
the empty ledger immediately, and in the cons case attach the displayed head
equation to the carrier already rebuilt for the tail. The transport rows for
$\mathcal N$, $\mathcal Z$, $\eta$, and $E$ supply exactly the classifier
stability required by $\kappa$.

Collecting these fields yields the stated $\NameCert_{\RingOfIntegersUp}$
obligation surface. Since every field has been projected from, or repacked into,
the displayed finite packet, the surface has no hidden host quotient or detached
integral-closure carrier.
\end{proof}

\begin{theorem}[RingOfIntegers dependency projection boundary]
\label{thm:ringofintegers-dependency-projection-boundary}
Every accepted $\RingOfIntegersUp$ Dedekind-source carrier
$$
\mathcal O=(\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho)
$$
projects exactly to the $\NumFieldUp$ carrier and operation rows carried by
$\mathcal N$, the embedded $\IntUp$ rows carried by $\mathcal Z$ and $\eta$,
the displayed $\Cont$ provenance $\tau$, the $\hsame$ classifier row $\kappa$,
and the $\Pkg$ provenance $\rho$. The dependency projection has no host
polynomial-equality row, host integral-closure carrier, or quotient carrier.
\end{theorem}
\leanchecked{BEDC.Derived.RingOfIntegersUp.RingOfIntegersDedekindSourceCarrier\_dependency\_projection\_boundary}
\begin{proof}
Unpack the carrier of
\autoref{def:ringofintegers-dedekind-source-carrier}. Its dependency fields are
precisely the number-field row $\mathcal N$, embedded integer row
$\mathcal Z$, embedding provenance $\eta$, classifier $\kappa$, continuation
row $\tau$, and package row $\rho$.

Apply \autoref{thm:ringofintegers-integral-closure-obligation-surface}. The
obligation surface projects accepted rows to those displayed dependency rows
and to the finite equation ledger $E$, with no hidden host carrier.

Finally drop the equation entries and retain only the rows that describe the
dependency boundary. Because the carrier definition has no field for host
polynomial equality, a quotient carrier, or a detached integral-closure object,
the projection is exhausted by the listed $\NumFieldUp$, $\IntUp$, $\Cont$,
$\hsame$, and $\Pkg$ rows.
\end{proof}

\begin{theorem}[RingOfIntegers equation-ledger transport closure]
\label{thm:ringofintegers-equation-ledger-transport-closure}
For an accepted $\RingOfIntegersUp$ Dedekind-source carrier
$$
\mathcal O=(\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho),
$$
transport the finite integral-equation ledger $E$ by the displayed classifier
row $\kappa$. The transported ledger, together with the same
$\NumFieldUp$ carrier row, embedded $\IntUp$ rows, $\Cont$ provenance, and
$\Pkg$ provenance, repacks as the same accepted
$\RingOfIntegersUp$ obligation surface. No host polynomial-equality row,
quotient carrier, or detached integral-closure carrier is introduced by the
transport.
\end{theorem}
\leanchecked{BEDC.Derived.RingOfIntegersUp.RingOfIntegersDedekindSourceCarrier\_equation\_ledger\_transport\_closure}
\begin{proof}
Unpack \autoref{def:ringofintegers-dedekind-source-carrier}. The classifier row
$\kappa$ contains the $\hsame$ transports for the number-field carrier, embedded
integer rows, field-operation endpoints, and every integral-equation row in
$E$.

Induct over the finite ledger $E$, following the ledger argument in
\autoref{thm:ringofintegers-integral-closure-obligation-surface}. In the empty
case, transport preserves only the dependency, classifier, continuation, and
package rows, so the obligation surface repacks immediately.

In the cons case, the head equation is transported through the displayed
field-operation endpoints and integer-coefficient rows recorded by $\kappa$.
The induction hypothesis transports the tail ledger and repacks it over the
same $\mathcal N$, $\mathcal Z$, $\eta$, $\tau$, and $\rho$ rows.

Attach the transported head equation to the transported tail and repack through
the obligation surface. Since every transported equation row remains a row of
the displayed finite ledger and the carrier has no host polynomial-equality or
quotient field, the accepted surface is unchanged.
\end{proof}

\begin{theorem}[RingOfIntegers root classifier transport]
\label{thm:ringofintegers-root-classifier-transport}
For a $\RingOfIntegersUp$ Dedekind-source carrier
$$
\mathcal O=(\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho),
$$
the root classifier transports exactly the displayed packet fields
$\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho$ along $\hsame$. A transported
accepted row has the same number-field source row, embedded integer row,
embedding-provenance row, finite integral-equation ledger, classifier row,
$\Cont$ provenance row, and $\Pkg$ provenance row. No host integral-closure
carrier, quotient object, or detached polynomial-equality row is transported.
\end{theorem}
\begin{proof}
Project the carrier through
\autoref{def:ringofintegers-dedekind-source-carrier}. Its named fields are
exactly $\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho$, and the classifier row
$\kappa$ records the allowed $\hsame$ transports for these fields.

Apply the obligation surface of
\autoref{thm:ringofintegers-integral-closure-obligation-surface}. It says that
accepted root rows project only to the number-field source, embedded integer
source, embedding provenance, integral-equation ledger, classifier transport,
continuation provenance, and package provenance.

Repack the transported projections with the same finite ledger and provenance
rows. Since neither the carrier definition nor the obligation surface has a
field for a host integral-closure carrier, quotient object, or detached
polynomial-equality row, transport is exhausted by the displayed packet
fields.
\end{proof}
\leanchecked{BEDC.Derived.RingOfIntegersUp.RingOfIntegersDedekindSourceCarrier\_classifier\_transport}

\begin{theorem}[RingOfIntegers integral-equation ledger exhaustion]
\label{thm:ringofintegers-integral-equation-ledger-exhaustion}
Every integral-equation read accepted by a $\RingOfIntegersUp$ root surface is
one of the finite ledger rows in $E$ of the Dedekind-source carrier
$\mathcal O=(\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho)$. Conversely, every
row of $E$, together with its $\hsame$ classifier entry in $\kappa$, its finite
$\Cont$ provenance in $\tau$, and the shared $\Pkg$ row $\rho$, repacks as an
accepted integral-equation read of the same root surface.
\end{theorem}
\begin{proof}
Induct on the finite ledger $E$. In the empty case, the carrier still exposes
the dependency rows, classifier row, continuation row, and package row, but it
exposes no integral-equation read.

In the cons case, project the head equation to its displayed field-operation
endpoints and integer-coefficient rows. The classifier component of $\kappa$
and the continuation component of $\tau$ are the only rows that bind this head
equation to the root packet.

Apply the induction hypothesis to the tail ledger. It exhausts all remaining
integral-equation reads through the same $\mathcal N,\mathcal Z,\eta$ source
rows and the same shared package provenance.

The reverse direction uses the same induction. The empty ledger repacks
immediately, and the cons step attaches the displayed head equation before
repacking the tail. Thus the accepted equation reads are exactly the finite
rows of $E$, with no host integral-closure or quotient source.
\end{proof}
\begin{theorem}[RingOfIntegers DirichletUnit source readback]
\label{thm:ringofintegers-dirichletunit-source-readback}
A downstream $\DirichletUnitUp$ consumer reading from
$\RingOfIntegersUp$ may read only the embedded integer row $\mathcal Z$, the
integral-equation ledger $E$, the classifier row $\kappa$, the finite $\Cont$
provenance row $\tau$, and the shared $\Pkg$ provenance row $\rho$ carried by
the accepted Dedekind-source packet
$\mathcal O=(\mathcal N,\mathcal Z,\eta,E,\kappa,\tau,\rho)$. The consumer may
also retain the number-field source row $\mathcal N$ and embedding provenance
$\eta$ as dependency scope, but it receives no host integral-closure carrier,
quotient object, or analytic unit datum from $\RingOfIntegersUp$.
\end{theorem}
\begin{proof}
Project the $\RingOfIntegersUp$ source through
\autoref{thm:ringofintegers-integral-closure-obligation-surface}. The
dependency rows available to any consumer are the number-field row, embedded
integer row, embedding provenance, integral-equation ledger, classifier,
continuation provenance, and package provenance.

Use \autoref{thm:ringofintegers-root-classifier-transport} to identify the
transported classifier data. A $\DirichletUnitUp$ reader may compare accepted
integer and equation rows only through the displayed $\hsame$ entries of
$\kappa$.

Use \autoref{thm:ringofintegers-integral-equation-ledger-exhaustion} to exhaust
the equation side. Every equation read is a member of $E$ and is tied to the
same finite continuation and package rows.

Therefore the downstream readback surface is exactly the embedded integer,
equation-ledger, classifier, $\Cont$, and $\Pkg$ rows, with $\mathcal N$ and
$\eta$ serving only as dependency scope. No additional host integral-closure,
quotient, or analytic unit row is available to the consumer.
\end{proof}

\begin{theorem}[RingOfIntegers scoped dependency package]
\label{thm:ringofintegers-scoped-dependency-package}
The $\RingOfIntegersUp$ carrier, integral-equation ledger, dependency
projection, classifier transport, ledger exhaustion, and $\DirichletUnitUp$
readback rows of this chapter are exhausted by the scoped primitive package
consisting of $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$,
$\NameCert_{\NumFieldUp}$, and $\NameCert_{\IntUp}$.

No public read of the chapter uses a host integral-closure predicate, quotient
integer object, analytic unit datum, or extra dependency beyond those primitive
rows and the displayed source certificates.
\end{theorem}
\begin{proof}
First use
\autoref{thm:ringofintegers-integral-closure-obligation-surface}. It lists the
carrier and integral-equation ledger rows available to the chapter and ties
them to the number-field and integer source certificates.

Next apply \autoref{thm:ringofintegers-dependency-projection-boundary} and
\autoref{thm:ringofintegers-root-classifier-transport}. These identify the
dependency projection and classifier transport as rows over $\mathsf{BHist}$,
$\hsame$, $\Cont$, $\Pkg$, $\NameCert_{\NumFieldUp}$, and
$\NameCert_{\IntUp}$.

Finally use
\autoref{thm:ringofintegers-integral-equation-ledger-exhaustion} together with
\autoref{thm:ringofintegers-dirichletunit-source-readback}. The ledger
exhaustion and downstream readback clauses show that every consumer row is one
of the displayed primitive rows, so the obligation surface is a scoped
dependency package.
\end{proof}

\begin{theorem}[RingOfIntegers scoped BHist source binding]
\label{thm:ringofintegers-scoped-bhist-source-binding}
The Dedekind-source carrier, dependency projection boundary,
equation-ledger transport closure, root classifier transport, integral-equation
ledger exhaustion, and $\DirichletUnitUp$ source readback bind the
$\RingOfIntegersUp$ obligation surface entirely to $\mathsf{BHist}$, $\hsame$,
$\Cont$, $\NameCert_{\NumFieldUp}$, $\NameCert_{\IntUp}$, and $\Pkg$ rows.

No host polynomial equality, quotient object, detached integral-closure
carrier, analytic unit datum, or standard bridge row is in scope for this
binding.
\end{theorem}
\begin{proof}
First project the carrier and obligation rows through
\autoref{def:ringofintegers-dedekind-source-carrier} and
\autoref{thm:ringofintegers-integral-closure-obligation-surface}. These two
blocks identify the accepted surface with the displayed number-field source,
embedded integer source, integral-equation ledger, classifier, continuation,
and package provenance.

Next bind the dependency and transport faces. Apply
\autoref{thm:ringofintegers-dependency-projection-boundary},
\autoref{thm:ringofintegers-equation-ledger-transport-closure}, and
\autoref{thm:ringofintegers-root-classifier-transport}. They restrict all
dependency projections, equation transport, and root classifier movement to
the same $\mathsf{BHist}$, $\hsame$, $\Cont$,
$\NameCert_{\NumFieldUp}$, $\NameCert_{\IntUp}$, and $\Pkg$ rows.

Finally use
\autoref{thm:ringofintegers-integral-equation-ledger-exhaustion} and
\autoref{thm:ringofintegers-dirichletunit-source-readback}. The equation
ledger is exhausted by the finite displayed rows, and the downstream
$\DirichletUnitUp$ readback receives only the embedded integer, equation
ledger, classifier, continuation, package, and dependency-scope rows already
listed.

Repacking these projections gives the scoped source binding. Since none of the
cited blocks exports a field for host polynomial equality, a quotient object,
a detached integral-closure carrier, an analytic unit datum, or a standard
bridge, those rows are outside the $\RingOfIntegersUp$ obligation surface.
\end{proof}

\closureat{RingOfIntegersUp}{scopedStr}
\begin{closurestatus}{\RingOfIntegersUp}
  \constructivestory{}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The scoped dependency package binds the Dedekind-source carrier, integral-equation ledger, dependency projection, classifier transport, ledger exhaustion, and DirichletUnit readback rows to $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert_{\NumFieldUp}$, and $\NameCert_{\IntUp}$.}
  \formalstatus{\unformalizedV}
  \leantarget{}
  \bridgestatus{none}
  \notclaimed{It does not close full algebraic-integer theory, class-group structure, analytic units, or standard bridge rows.}
  \upgradepath{Public closure requires an exported $\NameCert_{\RingOfIntegersUp}$ public surface with integral readback, endpoint exactness, and standard bridge boundary.}
\end{closurestatus}
