\chapter{A Concrete Naming Certificate for $\BishopCompletionComparisonUp$}
\label{ch:concrete-instances-bishopcompletioncomparison-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\BishopCompletionComparisonUp$ packet compares the displayed regular located Cauchy route with the completion-facing real-name seal as finite BEDC data. It sits after the regular located Cauchy surface of \autoref{ch:concrete-instances-regular-located-cauchy-real-namecert}, the boundary packet of \autoref{ch:concrete-instances-bishoplocatedcompletionboundary-namecert}, the located-limit route of \autoref{ch:concrete-instances-locatedlimit-namecert}, the located-real enclosure of \autoref{ch:concrete-instances-locatedreal-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the stream-window source of \autoref{ch:concrete-instances-streamname-namecert}, and the dyadic arithmetic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The chapter records the finite comparison route from regular located Cauchy data to the $\RealUp$ seal; it does not assert that $\RealUp$ is complete.

\begin{definition}[BishopCompletionComparison carrier]
\label{def:bishop-completion-comparison-carrier}
A $\BishopCompletionComparisonUp$ carrier is a finite $\BHist$ packet
$$
C=(R,B,L,E,T,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RegularLocatedCauchyRealUp$ source row, including its visible $\RegSeqRatUp$ regular rational source, $\StreamNameUp$ finite-window route, and $\DyadicRatCoreUp$ tolerance ledger.
\item $B$ is the $\BishopLocatedCompletionBoundaryUp$ boundary row attached to the same regular located Cauchy source.
\item $L$ is the $\LocatedLimitUp$ route read from the displayed boundary and regular located source rows.
\item $E$ is the $\LocatedRealUp$ enclosure row exposed before the terminal real-name seal is inspected.
\item $T$ is the terminal $\RealUp$ seal row reached only after $R,B,L,E$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the regular located source, boundary route, located-limit route, located-real enclosure, real seal, replay rows, provenance, and local naming row.
\item $K$ records the displayed $\Cont$ replay from $R$ to $B$, from $B$ to $L$, from $L$ to $E$, and from $E$ to $T$.
\item $P$ is the $\Pkg$ provenance over $\BishopCompletionComparisonUp$, $\RegularLocatedCauchyRealUp$, $\BishopLocatedCompletionBoundaryUp$, $\LocatedLimitUp$, $\LocatedRealUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopCompletionComparisonUp}$ row.
\end{enumerate}
The carrier has no coordinate for $\RealUp$ completeness, quotient equality of Cauchy names, real trichotomy, countable choice, open-cover compactness, or a host-selected limit.
\end{definition}

\begin{theorem}[BishopCompletionComparison NameCert obligations]
\label{thm:bishop-completion-comparison-namecert-obligations}
For the carrier of \autoref{def:bishop-completion-comparison-carrier}, the local $\NameCert_{\BishopCompletionComparisonUp}$ surface consists exactly of carrier admission for $C=(R,B,L,E,T,H,K,P,N)$, regular located source exposure through $R$, boundary-route exposure through $B$, located-limit exposure through $L$, located-real enclosure exposure through $E$, terminal $\RealUp$ seal exposure through $T$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $K$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is tuple projection from the displayed packet $C$. The rows expose the regular located Cauchy source, Bishop boundary route, located-limit route, located-real enclosure, terminal real seal, transport, replay, provenance, and local name.

The analytic obligations are exactly the rows $R,B,L,E,T$. The source row $R$ carries the $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$ data used by the regular located Cauchy surface; the boundary row $B$ keeps the same source visible before the located-limit and located-real rows are read.

The structural obligations are exactly $H,K,P,N$. They transport the same rows, replay the same finite route, record provenance for the named packets, and bind the local certificate without adding any coordinate outside the carrier.
\end{proof}

\begin{theorem}[BishopCompletionComparison regular located route]
\label{thm:bishop-completion-comparison-regular-located-route}
Every accepted $\BishopCompletionComparisonUp$ packet $C=(R,B,L,E,T,H,K,P,N)$ routes a completion-facing read through
$$
R\longmapsto B\longmapsto L\longmapsto E\longmapsto T .
$$
The row $R$ supplies the $\RegularLocatedCauchyRealUp$ source, including the displayed $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$ rows; $B$ supplies the $\BishopLocatedCompletionBoundaryUp$ comparison boundary; $L$ and $E$ supply the $\LocatedLimitUp$ and $\LocatedRealUp$ rows before the terminal $\RealUp$ seal is read.
\end{theorem}
\begin{proof}
Project the accepted carrier. The only source row for regular located Cauchy data is $R$, and its regular rational, stream-window, and dyadic tolerance coordinates are present only as part of that row.

Now read the completion-facing side. The replay row $K$ places $B$ after $R$, then places $L$ and $E$ before the terminal seal $T$. Thus every such read factors through the displayed boundary and locatedness route.

Transport and provenance preserve the same factorization. The rows $H$ and $P$ identify the transported route as the same finite comparison packet, while $N$ names the local surface for downstream consumers.
\end{proof}

\begin{theorem}[BishopCompletionComparison seal non-escape]
\label{thm:bishop-completion-comparison-seal-nonescape}
No accepted $\BishopCompletionComparisonUp$ carrier exports data outside the tuple $R,B,L,E,T,H,K,P,N$. In particular, a $\RealUp$ consumer of the terminal seal cannot recover $\RealUp$ completeness, quotient equality of Cauchy names, real trichotomy, countable choice, open-cover compactness, or a host-selected limit from the packet.
\end{theorem}
\begin{proof}
Inspect the carrier of \autoref{def:bishop-completion-comparison-carrier}. Its only analytic rows are the regular located source, boundary route, located-limit route, located-real enclosure, and terminal real seal.

Apply \autoref{thm:bishop-completion-comparison-namecert-obligations}. Every local obligation is a projection of those rows or a structural transport, replay, provenance, or naming obligation for those rows.

Finally apply \autoref{thm:bishop-completion-comparison-regular-located-route}. Any terminal seal read first passes through $R,B,L,E$, so the finite comparison route is exhausted before the $\RealUp$ seal is reached. Since none of the excluded principles is a carrier coordinate, none can be exported by the packet.
\end{proof}

\closureat{BishopCompletionComparisonUp}{seedStr}

\begin{closurestatus}{\BishopCompletionComparisonUp}
  \constructivestory{A $\BishopCompletionComparisonUp$ packet is generated from a regular located Cauchy source row, a Bishop located completion boundary row, a located-limit row, a located-real enclosure row, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-completion-comparison-carrier}, \autoref{thm:bishop-completion-comparison-namecert-obligations}, \autoref{thm:bishop-completion-comparison-regular-located-route}, and \autoref{thm:bishop-completion-comparison-seal-nonescape} seed the finite comparison route from $\RegularLocatedCauchyRealUp$ and $\BishopLocatedCompletionBoundaryUp$ to the terminal $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim $\RealUp$ completeness, quotient equality of Cauchy names, real trichotomy, countable choice, open-cover compactness, host-selected limits, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, regular located source exposure, boundary-route factorization, located-limit and located-real exposure, terminal seal non-escape, transport stability, replay, provenance, and local naming for the same finite packet.}
\end{closurestatus}
