\chapter{A Concrete Naming Certificate for $\MetricCompletionUp$}
\label{ch:concrete-instances-metriccompletion-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, and Kelley-style metric completion, the $\MetricCompletionUp$ packet records the L10 metric-completion interface as finite Cauchy-filter or Cauchy-net evidence over a displayed metric source. It sits between the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the directed-net surface of \autoref{ch:concrete-instances-cauchynet-namecert}, the separated-limit uniqueness surface of \autoref{ch:concrete-instances-separatedmetric-namecert}, and the uniform-completion boundary of \autoref{ch:concrete-instances-uniformcompletion-namecert}. The packet gives later complete-metric and real-completion consumers a named landing surface without quotienting Cauchy names, selecting representatives, assuming an ambient complete space, invoking open-cover compactness, using countable choice, or asserting completeness of $\RealUp$.

\begin{definition}[MetricCompletion carrier]
\label{def:metric-completion-carrier}
A $\MetricCompletionUp$ carrier is a finite $\BHist$ packet
$$
M=(X,F,D,R,S,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the $\MetricUp$ source row, including its point classifier, metric-distance witness surface, and displayed finite observation histories.
\item $F$ is either a $\CauchyFilterUp$ cofinal packet or an empty marker when the completion route is presented by directed nets.
\item $D$ is either a $\CauchyNetUp$ directed-window packet or an empty marker when the completion route is presented by Cauchy filters.
\item $R$ is the finite $\RegSeqRatUp$ or $\RealUp$ readback row used when a completion-facing consumer asks for numerical tolerance data.
\item $S$ is the $\SeparatedMetricUp$ uniqueness row, used only to identify two displayed limit readings through zero-distance classifier evidence.
\item $H$ records componentwise $\hsame$ transport for the source metric, cofinal Cauchy packet, finite numerical readback, separatedness row, replay row, package row, and local naming row.
\item $C$ records the displayed $\Cont$ route replaying metric admission, Cauchy cofinality, readback extraction, separated-limit comparison, and completion handoff.
\item $P$ is the $\Pkg$ provenance over $\MetricUp$, $\CauchyFilterUp$, $\CauchyNetUp$, $\RegSeqRatUp$, $\RealUp$, $\SeparatedMetricUp$, $\UniformCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\MetricCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, an ambient complete metric space, open-cover compactness, countable choice, or completeness of $\RealUp$.
\end{definition}
\leanchecked{BEDC.Derived.MetricCompletionUp.TasteGate.MetricCompletionTasteGate\_single\_carrier\_alignment}

\begin{definition}[MetricCompletion classifier]
\label{def:metric-completion-classifier}
The classifier of an accepted $\MetricCompletionUp$ packet relates two completion-facing reads precisely when their source metric row is the same displayed $X$, their cofinal Cauchy evidence is read from the same $F$ or $D$ branch, their finite $\RegSeqRatUp$ or $\RealUp$ tolerance rows agree after the componentwise $\hsame$ transport $H$, and the separatedness row $S$ identifies any two displayed limit readings through the zero-distance route already available in $\SeparatedMetricUp$.

Equivalently, the classifier is the finite replay path
$$
X,(F\ \hbox{or}\ D),R,S,H,C,P,N .
$$
It is not a quotient of Cauchy names, not a choice of canonical representatives, and not a claim that a host metric space is complete.
\end{definition}

\begin{theorem}[MetricCompletion NameCert obligations]
\label{thm:metric-completion-namecert-obligations}
For an accepted $\MetricCompletionUp$ carrier $M=(X,F,D,R,S,H,C,P,N)$, the local $\NameCert_{\MetricCompletionUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed $\MetricUp$ source, $\CauchyFilterUp$ or $\CauchyNetUp$ cofinal packet, finite $\RegSeqRatUp$ or $\RealUp$ readback, $\SeparatedMetricUp$ uniqueness row, componentwise transport, continuation replay, provenance row, and local naming row;
\item cofinal evidence selection, requiring each completion-facing read to pass through exactly one visible branch, either $F$ or $D$;
\item finite readback compatibility, requiring numerical tolerance requests to factor through $R$ before any completion handoff is consumed;
\item separated-limit uniqueness, requiring equality of two displayed limit readings to pass through the zero-distance classifier route stored in $S$;
\item ledger non-escape, stating that no quotient completion, selected representative, ambient complete metric space, open-cover compactness principle, countable-choice schedule, or $\RealUp$ completeness theorem is exported by the packet.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.MetricCompletionUp.NameCertObligations.MetricCompletionCarrier\_semantic\_name\_certificate}
\begin{proof}
Carrier admission is projection from \autoref{def:metric-completion-carrier}. The tuple lists the source metric row, the two possible Cauchy-evidence branches, the finite numerical readback, the separatedness row, and the structural support rows.

Cofinal evidence selection is local because the accepted carrier records the chosen branch in $F$ or $D$. A filter-presented route consumes the $\CauchyFilterUp$ row before any completion handoff, while a net-presented route consumes the $\CauchyNetUp$ directed-window row in the same position.

Finite readback compatibility is the role of $R$. Every tolerance-facing consumer reads the displayed $\RegSeqRatUp$ or $\RealUp$ data before it can compare completion endpoints.

Separated-limit uniqueness is supplied by $S$ and replayed by $C$ after transport by $H$. The provenance row $P$ and local naming row $N$ record that no further coordinate is available, so the excluded quotient, choice, compactness, ambient completeness, and real-completeness principles cannot be read from the certificate.
\end{proof}

\begin{theorem}[MetricCompletion Cauchy-filter handoff]
\label{thm:metric-completion-cauchy-filter-handoff}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet whose cofinal evidence is presented by the $\CauchyFilterUp$ branch $F$. Then every completion-facing consumer of $M$ factors first through the source metric row $X$, then through the displayed Cauchy-filter row $F$, then through the finite readback row $R$ when numerical tolerance data are requested, and only then through the separatedness row $S$ for comparison of displayed limit readings.

The handoff is therefore the finite route
$$
X\longmapsto F\longmapsto R\longmapsto S\longmapsto H,C,P,N ,
$$
not a quotient completion, not a selected representative, not an ambient complete metric space, and not an appeal to countable choice or $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.MetricCompletionUp.NameCertObligations.MetricCompletionCarrier\_filter\_branch\_handoff}
\begin{proof}
Project the accepted packet and choose the filter branch. The first row available to a completion consumer is the metric source $X$, so point admission and distance evidence are read before any completion-facing operation.

The next row is $F$. It is already a $\CauchyFilterUp$ finite-filterbase and late-window packet, so cofinality is consumed as displayed filter evidence rather than as a selected Cauchy representative.

When the consumer asks for tolerance data, the route passes through $R$. The replay row $C$ then carries the same source, filter, and readback rows to $S$, where separated-limit comparison is performed only through the local zero-distance classifier route.

The remaining rows $H,P,N$ transport and name the same finite packet. Since the route has no coordinate for quotient equality, selected representatives, ambient completeness, countable choice, or $\RealUp$ completeness, none of those principles is exported by the handoff.
\end{proof}

\begin{theorem}[MetricCompletion separated limit uniqueness]
\label{thm:metric-completion-separated-limit-uniqueness}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet, and suppose two completion-facing reads of the same source metric packet use the same displayed cofinal branch $F$ or $D$ and the same finite readback row $R$ after transport by $H$. If the separatedness row $S$ displays zero distance between the two resulting limit readings, then the $\MetricCompletionUp$ classifier identifies the two reads.

This identification is internal to the displayed $\MetricUp$, $\CauchyFilterUp$ or $\CauchyNetUp$, $\RegSeqRatUp$ or $\RealUp$, and $\SeparatedMetricUp$ rows. It is not host equality, not equality of quotient classes, and not a selected-limit principle.
\end{theorem}
\begin{proof}
Read the two completion-facing paths through the common source metric row $X$. The shared cofinal branch, either $F$ or $D$, keeps both paths on the same displayed Cauchy evidence.

Transport by $H$ aligns the finite readback row $R$ for the two paths. The replay row $C$ then presents the two limit readings to the separatedness row $S$.

By the meaning of $S$, zero distance between the two displayed limit readings yields classifier equivalence inside the underlying metric carrier. The definition of \autoref{def:metric-completion-classifier} uses exactly this route as the comparison criterion.

No quotient class, host equality, selected representative, ambient completeness row, countable-choice schedule, or $\RealUp$ completeness theorem appears among the fields of $M$, so the uniqueness conclusion remains a local classifier identification.
\end{proof}

\begin{theorem}[MetricCompletion Cauchy-net handoff]
\label{thm:metric-completion-cauchy-net-handoff}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet whose cofinal evidence is presented by the $\CauchyNetUp$ branch $D$. Then every completion-facing consumer of $M$ factors first through the source metric row $X$, then through the displayed directed Cauchy-net row $D$, then through the finite readback row $R$ when numerical tolerance data are requested, and only then through the separatedness row $S$ for comparison of displayed limit readings.

The handoff is therefore the finite route
$$
X\longmapsto D\longmapsto R\longmapsto S\longmapsto H,C,P,N ,
$$
not a quotient completion, not a selected representative, not an ambient complete metric space, and not an appeal to countable choice or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted packet and choose the net branch. The source metric row $X$ supplies the displayed point classifier, metric-distance witness surface, and finite observation histories before any completion-facing read is available.

The next row is $D$. It is already the $\CauchyNetUp$ directed-window packet, so cofinality is consumed as visible net evidence rather than as a chosen representative of a completion class.

When a consumer requests tolerance data, the route passes through $R$. The replay row $C$ then carries the same source, net, and readback rows to $S$, where separated-limit comparison is performed through the local zero-distance classifier route.

The rows $H,P,N$ transport, package, and name the same finite packet. Since none of the carrier coordinates is a quotient-completion equality, a selected limit, a countable-choice schedule, an ambient completeness witness, or a $\RealUp$ completeness theorem, the net handoff exports none of those principles.
\end{proof}

\begin{theorem}[MetricCompletion filter-net branch determinacy]
\label{thm:metric-completion-filter-net-branch-determinacy}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. Every completion-facing read of $M$ uses exactly one visible cofinal branch, either the $\CauchyFilterUp$ row $F$ or the $\CauchyNetUp$ row $D$. A downstream read cannot mix filter evidence and net evidence unless an additional branch-conversion row is added, and no such row occurs in the carrier of \autoref{def:metric-completion-carrier}.
\end{theorem}
\leanchecked{BEDC.Derived.MetricCompletionUp.BranchDeterminacy.MetricCompletion\_filter\_net\_branch\_determinacy}
\begin{proof}
The classifier of \autoref{def:metric-completion-classifier} reads the cofinal evidence from the single displayed branch recorded in the packet, written there as $F$ or $D$. Thus the accepted route selects one branch before the finite readback row $R$ and separatedness row $S$ are inspected.

In the filter case, every downstream comparison factors through the row $F$ named in the finite route. In the net case, the corresponding route factors through $D$ in the same position.

A mixed read would require a new row relating the filter and net evidence before $R$ and $S$ could be shared as one classifier path. The carrier has no coordinate for such a row, so the classifier route cannot manufacture it downstream.
\end{proof}

\begin{theorem}[MetricCompletion finite-readback ledger non-escape]
\label{thm:metric-completion-finite-readback-ledger-nonescape}
For an accepted $\MetricCompletionUp$ carrier $M=(X,F,D,R,S,H,C,P,N)$, every tolerance read, readback request, and limit-comparison read exported by $M$ is exhausted by the rows
$$
X,F,D,R,S,H,C,P,N .
$$
Consequently the packet cannot introduce quotient classes, host equality, selected limits, open-cover compactness, countable choice, or completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Tolerance-facing reads pass through the finite readback row $R$ after the source metric row $X$ and the chosen cofinal branch $F$ or $D$ have been displayed. The componentwise transport row $H$ and replay row $C$ preserve that same route.

Limit-comparison reads then pass through $S$. The separatedness row supplies only local zero-distance classifier evidence, so it compares displayed limit readings without changing the carrier into a host equality or quotient equality.

The provenance row $P$ and local naming row $N$ close the ledger at exactly the listed rows. Since no remaining coordinate names quotient classes, selected limits, open-cover compactness, countable choice, host equality, ambient completeness, or $\RealUp$ completeness, none of those data can escape from the finite readback ledger.
\end{proof}
\leanchecked{BEDC.Derived.MetricCompletionUp.ReadbackLedger.MetricCompletion\_finite\_readback\_ledger\_nonescape}

\begin{theorem}[MetricCompletion branch coverage]
\label{thm:metric-completion-branch-coverage}
Let
$$
M=(X,F,D,R,S,H,C,P,N)
$$
be an accepted $\MetricCompletionUp$ packet. Every completion-facing read of $M$ uses either the $\CauchyFilterUp$ branch $F$ or the $\CauchyNetUp$ branch $D$ before any finite readback, separated-limit comparison, or completion handoff is inspected. A consumer that has not chosen one of these displayed branches has no route to $R$, $S$, $H$, $C$, $P$, or $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-carrier}. The only cofinal evidence fields are $F$ and $D$, and the classifier of \autoref{def:metric-completion-classifier} reads completion data through one of those fields before it reaches the readback row.

The existing handoff theorems identify the two possible routes. In the filter case, \autoref{thm:metric-completion-cauchy-filter-handoff} forces the path through $F$ before $R$ and $S$ are read. In the net case, \autoref{thm:metric-completion-cauchy-net-handoff} forces the same position to be occupied by $D$.

The remaining rows are structural. Transport, replay, provenance, and local naming preserve the chosen branch; they do not create a third Cauchy-evidence coordinate. Hence branch coverage is exactly the displayed filter-or-net dichotomy.
\end{proof}

\begin{theorem}[MetricCompletion filter-net compatibility]
\label{thm:metric-completion-filter-net-compatibility}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. Any consumer comparing filter and net presentations of the same completion-facing read must pass through the same source $\MetricUp$ row $X$, the same finite readback row $R$, the same $\SeparatedMetricUp$ row $S$, the componentwise $\hsame$ transport row $H$, the displayed $\Cont$ replay row $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert_{\MetricCompletionUp}$ row $N$. The comparison cannot be made by quotienting the two Cauchy presentations or by selecting a representative common limit.
\end{theorem}
\begin{proof}
Start with the branch coverage of \autoref{thm:metric-completion-branch-coverage}. A filter presentation and a net presentation are readable only as the two visible cofinal branches of the same carrier, so any comparison between them must keep the source row $X$ fixed.

Finite numerical data are then compared through $R$. The finite-readback ledger non-escape theorem, \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, prevents a consumer from replacing this row by an external tolerance oracle or a quotient-class read.

Separated comparison is performed at $S$. The separated-limit uniqueness theorem, \autoref{thm:metric-completion-separated-limit-uniqueness}, supplies only local zero-distance classifier evidence, and $H,C,P,N$ preserve and name that same route.

Since no carrier coordinate stores quotient equality or a selected representative, the filter-net comparison is exhausted by the listed rows.
\end{proof}

\begin{theorem}[MetricCompletion filter-net branch exhaustion]
\label{thm:metric-completion-filter-net-branch-exhaustion}
For an accepted $\MetricCompletionUp$ carrier $M=(X,F,D,R,S,H,C,P,N)$, every completion-facing consumer reads exactly one of the displayed Cauchy evidence branches before readback: either the $\CauchyFilterUp$ branch $F$ or the $\CauchyNetUp$ branch $D$. The remaining rows $R,S,H,C,P,N$ can transport, replay, compare, package, and name the selected route, but they cannot introduce a third completion evidence route.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-carrier}. The only Cauchy evidence rows in the accepted tuple are $F$ and $D$, and the classifier of \autoref{def:metric-completion-classifier} reads one of them before the finite readback row $R$ is available.

Use the NameCert obligations together with branch determinacy and compatibility, \autoref{thm:metric-completion-namecert-obligations}, \autoref{thm:metric-completion-filter-net-branch-determinacy}, and \autoref{thm:metric-completion-filter-net-compatibility}. These keep the selected branch attached to the same source metric, readback row, separatedness comparison, transport, replay, provenance, and local naming route.

It remains to exclude a hidden third route. The finite-readback ledger non-escape theorem, \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, rules out quotient completions, selected representatives, ambient complete spaces, countable choice, and $\RealUp$ completeness. Since $R,S,H,C,P,N$ are structural or readback rows downstream of the chosen branch, they cannot supply independent Cauchy evidence.
\end{proof}

\begin{theorem}[MetricCompletion UniformCompletion handoff]
\label{thm:metric-completion-uniform-completion-handoff}
Every $\UniformCompletionUp$ consumer of an accepted $\MetricCompletionUp$ packet reads the packet only through the displayed $\CauchyFilterUp$ or $\CauchyNetUp$ evidence, the finite $\RegSeqRatUp$ or $\RealUp$ readback row, the $\SeparatedMetricUp$ uniqueness row, componentwise transport, replay, provenance, and local naming. The handoff provides no quotient row, no selected representative row, no host equality row, and no $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Use \autoref{thm:metric-completion-branch-coverage} to select the visible Cauchy-evidence branch. The $\UniformCompletionUp$ consumer therefore begins with the same filter or net route already displayed by the metric-completion packet.

Next the consumer reads finite tolerance information through $R$. This is the only $\RegSeqRatUp$ or $\RealUp$ readback coordinate in the carrier, so every numerical request remains attached to the same source metric and branch evidence.

Finally the consumer reaches $S,H,C,P,N$. The separatedness row supplies local uniqueness, while the structural rows transport, replay, source, and name the same finite packet.

The excluded completion principles are absent from \autoref{def:metric-completion-carrier} and are barred again by \autoref{thm:metric-completion-finite-readback-ledger-nonescape}. The uniform-completion handoff therefore exports exactly the displayed finite evidence and no quotient or selected-representative data.
\end{proof}

\begin{theorem}[MetricCompletion obligation branch readback]
\label{thm:metric-completion-obligation-branch-readback}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$, every finite readback exported by the metric-completion surface first chooses one displayed cofinal branch, either the $\CauchyFilterUp$ branch $F$ or the $\CauchyNetUp$ branch $D$. Only after that branch is fixed may a consumer read the finite $\RegSeqRatUp$ or $\RealUp$ tolerance row $R$.
\end{theorem}
\begin{proof}
Use \autoref{thm:metric-completion-branch-coverage}. It states that every completion-facing read chooses one of the visible Cauchy-evidence branches before any finite readback, separated comparison, or completion handoff is inspected.

The carrier of \autoref{def:metric-completion-carrier} has only one readback coordinate $R$. Thus a $\RegSeqRatUp$ or $\RealUp$ tolerance read can occur only after the selected filter or net branch has been displayed.

The filter-net compatibility theorem, \autoref{thm:metric-completion-filter-net-compatibility}, keeps $R,H,C,P,N$ attached to the same source metric and branch route. The finite-readback non-escape theorem, \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, excludes quotient classes, selected limits, countable choice, and $\RealUp$ completeness from the readback path.
\end{proof}

\begin{theorem}[MetricCompletion obligation separated comparison]
\label{thm:metric-completion-obligation-separated-comparison}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. Any two displayed completion reads of $M$ compare only through the $\SeparatedMetricUp$ zero-distance classifier row $S$ together with the componentwise $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route. They are not compared by host equality, quotient equality, or a selected representative of a completion class.
\end{theorem}
\begin{proof}
Start from the classifier of \autoref{def:metric-completion-classifier}. It identifies completion-facing reads only when the source metric, selected Cauchy branch, readback row, separatedness row, and structural routes agree componentwise.

Apply \autoref{thm:metric-completion-separated-limit-uniqueness}. The zero-distance evidence in $S$ is the only comparison row that can identify two displayed limit readings.

The carrier and finite-readback non-escape theorem rule out host equality, quotient equality, selected representatives, ambient completeness, and countable choice. Therefore every accepted comparison remains a local $\SeparatedMetricUp$ classifier comparison transported through $H,C,P,N$.
\end{proof}

\begin{theorem}[MetricCompletion regular-Cauchy readback]
\label{thm:metric-completion-regular-cauchy-readback}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. Any completion consumer that reaches a $\RegSeqRatUp$ or $\RealUp$ tolerance row first chooses one visible Cauchy evidence branch, either the $\CauchyFilterUp$ row $F$ or the $\CauchyNetUp$ row $D$. Only after that branch choice may the consumer read $R$, and every such readback is replayed through $H,C,P,N$ over the same metric source $X$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-carrier}. The only Cauchy evidence rows are $F$ and $D$, and the only numerical readback row is $R$.

Apply the branch coverage and branch determinacy theorems, \autoref{thm:metric-completion-branch-coverage} and \autoref{thm:metric-completion-filter-net-branch-determinacy}. Together they force every completion-facing read to select exactly one displayed branch before the finite readback row can be inspected.

Now apply the obligation branch-readback theorem \autoref{thm:metric-completion-obligation-branch-readback}. It places the $\RegSeqRatUp$ or $\RealUp$ tolerance row after the selected filter or net evidence.

The support rows do not alter the branch. The componentwise transport, replay, provenance, and local naming rows $H,C,P,N$ preserve the same source metric, selected Cauchy evidence, and readback row. Thus no consumer reaches $R$ before a visible branch choice.
\end{proof}

\begin{theorem}[MetricCompletion separated-branch readback]
\label{thm:metric-completion-separated-branch-readback}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. Every completion consumer that reaches separated comparison first reads the selected $\CauchyFilterUp$ branch $F$ or $\CauchyNetUp$ branch $D$, then the finite readback row $R$, and only then the $\SeparatedMetricUp$ row $S$. The separated comparison is therefore a branch-indexed local zero-distance classifier route, not host equality, quotient equality, selected representative equality, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the regular-Cauchy readback theorem above. It fixes the route to $R$ as a route through exactly one displayed Cauchy evidence branch over the source metric row $X$.

Apply \autoref{thm:metric-completion-obligation-separated-comparison}. It states that any comparison of displayed completion reads uses the separatedness row $S$ together with the componentwise transport, continuation, provenance, and naming route.

The separated-limit uniqueness theorem, \autoref{thm:metric-completion-separated-limit-uniqueness}, identifies the content of $S$ as local zero-distance classifier evidence. This comparison is downstream of the selected branch and readback rows, not an independent completion equality.

Finally use \autoref{thm:metric-completion-finite-readback-ledger-nonescape}. Quotient equality, host equality, selected representatives, ambient complete spaces, countable choice, and $\RealUp$ completeness are absent from the carrier, so separated comparison cannot be reached through any route other than the displayed branch, readback, and $S,H,C,P,N$ rows.
\end{proof}

\begin{theorem}[MetricCompletion obligation uniform handoff]
\label{thm:metric-completion-obligation-uniform-handoff}
Every $\UniformCompletionUp$ consumer of an accepted $\MetricCompletionUp$ packet sees exactly the same displayed branch, finite readback row, separatedness row, componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ route as the metric-completion packet itself. The handoff adds no quotient completion row, no branch conversion row, no selected limit, and no independent uniform-completion classifier.
\end{theorem}
\begin{proof}
Use \autoref{thm:metric-completion-uniform-completion-handoff}. The uniform consumer reads the displayed $\CauchyFilterUp$ or $\CauchyNetUp$ evidence, $R$, $S$, and the structural rows $H,C,P,N$.

The branch-readback obligation above fixes that the same branch precedes the same readback row. The separated-comparison obligation fixes that any comparison available to the uniform consumer is still routed through $S$ rather than through host or quotient equality.

Finally \autoref{thm:metric-completion-filter-net-compatibility} and \autoref{thm:metric-completion-finite-readback-ledger-nonescape} keep the handoff on the same source metric, readback, separatedness, transport, replay, provenance, and naming route. No additional uniform-completion data is introduced by the handoff.
\end{proof}

\begin{theorem}[MetricCompletion branch-conversion refusal]
\label{thm:metric-completion-branch-conversion-refusal}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. Any completion-facing read that uses data from both the $\CauchyFilterUp$ branch $F$ and the $\CauchyNetUp$ branch $D$ must display a branch-conversion row between those two branches. Since the carrier of \autoref{def:metric-completion-carrier} contains no such row, no accepted read of $M$ may mix filter evidence and net evidence as one completion route.
\end{theorem}
\begin{proof}
Apply \autoref{thm:metric-completion-filter-net-branch-determinacy}. The accepted packet selects the visible branch before a read reaches the readback row $R$ or the separatedness row $S$.

Now apply \autoref{thm:metric-completion-branch-coverage}. A consumer that reads $F$ follows the filter handoff, while a consumer that reads $D$ follows the net handoff. To combine the two as one route, the consumer would need an additional row witnessing conversion from one displayed branch to the other.

The carrier inventory in \autoref{def:metric-completion-carrier} lists only $X,F,D,R,S,H,C,P,N$. The structural rows transport, replay, source, and name the selected route; they do not add a conversion coordinate. Hence a mixed read has no projection from the accepted packet.
\end{proof}

\begin{theorem}[MetricCompletion uniform-seal factorization]
\label{thm:metric-completion-uniform-seal-factorization}
Every $\UniformCompletionUp$ consumer of an accepted $\MetricCompletionUp$ packet factors through the selected $\CauchyFilterUp$ branch $F$ or $\CauchyNetUp$ branch $D$, the finite readback row $R$, the $\SeparatedMetricUp$ row $S$, the componentwise $\hsame$ row $H$, the displayed $\Cont$ replay row $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert_{\MetricCompletionUp}$ row $N$. No uniform-facing seal is available outside that selected branch and structural route.
\end{theorem}
\begin{proof}
Start with \autoref{thm:metric-completion-obligation-uniform-handoff}. It gives the uniform consumer exactly the branch, readback, separatedness, transport, replay, provenance, and naming rows of the metric-completion packet.

Use \autoref{thm:metric-completion-obligation-branch-readback} to place $R$ after the selected Cauchy-evidence branch. Then use \autoref{thm:metric-completion-obligation-separated-comparison} to place every comparison through $S$ and the structural rows $H,C,P,N$.

The branch-conversion refusal above prevents the uniform consumer from combining $F$ and $D$ through an absent conversion row. Thus the uniform seal factors through one selected branch together with $R,S,H,C,P,N$.
\end{proof}

\begin{theorem}[MetricCompletion completion-consumer totality]
\label{thm:metric-completion-completion-consumer-totality}
Every current completion-facing consumer of an accepted $\MetricCompletionUp$ packet receives only the rows listed in the carrier
$$
X,F,D,R,S,H,C,P,N .
$$
It receives no quotient-completion class, selected representative, countable-choice schedule, branch-conversion coordinate, open-cover compactness row, or $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-carrier}. The finite packet lists the metric source, two alternative Cauchy-evidence rows, one readback row, one separatedness row, and the transport, replay, provenance, and naming rows.

The obligation theorems above exhaust the possible consumer routes. Branch readback fixes how $R$ is reached; separated comparison fixes how $S$ is used; uniform handoff and uniform-seal factorization fix the completion-facing handoff; branch-conversion refusal rejects mixed branches without an explicit row.

Finally apply \autoref{thm:metric-completion-finite-readback-ledger-nonescape}. The excluded quotient, representative, countable-choice, compactness, and ambient-completeness principles have no coordinate in the accepted tuple and cannot be recovered by the structural rows.
\end{proof}

\begin{theorem}[MetricCompletion carrier admission]
\label{thm:metric-completion-carrier-admission}
For an accepted $\MetricCompletionUp$ packet, carrier admission is exactly projection of the finite rows
$$
X,F,D,R,S,H,C,P,N .
$$
The admitted rows are the displayed $\MetricUp$ source $X$, the $\CauchyFilterUp$ branch $F$ or $\CauchyNetUp$ branch $D$, the finite $\RegSeqRatUp$ or $\RealUp$ readback row $R$, the $\SeparatedMetricUp$ comparison row $S$, the componentwise $\hsame$ transport row $H$, the displayed $\Cont$ replay row $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert_{\MetricCompletionUp}$ row $N$. No carrier admission judgment for this packet has a coordinate for quotient completion equality, selected representatives, host equality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-carrier}. Its displayed tuple is exactly $M=(X,F,D,R,S,H,C,P,N)$.

The row inventory is already separated by the NameCert obligations of \autoref{thm:metric-completion-namecert-obligations}. The branch coverage theorem, \autoref{thm:metric-completion-branch-coverage}, forces completion-facing reads to choose $F$ or $D$ before $R$ and $S$ can be inspected.

The finite-readback ledger non-escape theorem, \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, closes the negative side. Since every exported tolerance read, comparison read, and handoff read is exhausted by the displayed tuple, no excluded completion principle can be admitted as an additional carrier coordinate.
\end{proof}

\begin{theorem}[MetricCompletion classifier stability]
\label{thm:metric-completion-classifier-stability}
Let $M=(X,F,D,R,S,H,C,P,N)$ and $M'=(X',F',D',R',S',H',C',P',N')$ be accepted $\MetricCompletionUp$ packets whose displayed rows are related componentwise by the $\hsame$ transport rows and replayed by the corresponding $\Cont$ rows. Then the $\MetricCompletionUp$ classifier preserves branch choice, finite readback, separated comparison, and completion handoff along that componentwise route.

In particular, a classified replacement cannot change a filter branch into an unrelated net branch, replace $R$ by an external tolerance oracle, compare endpoints outside $S$, or introduce a new $\UniformCompletionUp$ handoff row.
\end{theorem}
\begin{proof}
Start with the classifier of \autoref{def:metric-completion-classifier}. It reads the source metric, the chosen Cauchy branch, the finite readback row, the separatedness row, and the support rows as one displayed route.

Apply branch determinacy and branch coverage, \autoref{thm:metric-completion-filter-net-branch-determinacy} and \autoref{thm:metric-completion-branch-coverage}. These results keep the branch position fixed as either $F$ or $D$ before any downstream read reaches $R$ or $S$.

Next apply \autoref{thm:metric-completion-obligation-branch-readback} and \autoref{thm:metric-completion-obligation-separated-comparison}. The first keeps tolerance evidence at the transported readback row, and the second keeps endpoint comparison at the transported separatedness row.

Finally use \autoref{thm:metric-completion-obligation-uniform-handoff}. The $\UniformCompletionUp$ consumer sees the same displayed branch, readback, separatedness, transport, replay, provenance, and naming rows, so classifier transport preserves the handoff rather than adding an independent completion surface.
\end{proof}

\begin{definition}[MetricCompletion branch-interface scope]
\label{def:metriccompletion-branch-interface-scope}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$, the branch-interface rows are the displayed source metric row $X$, exactly one Cauchy-evidence branch $F$ or $D$, the finite $\RegSeqRatUp$ or $\RealUp$ readback row $R$, the $\SeparatedMetricUp$ comparison row $S$, the componentwise $\hsame$ transport row $H$, the displayed $\Cont$ replay row $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert_{\MetricCompletionUp}$ row $N$. This scope is a row boundary: it names what filter and net consumers may read, and it does not add carrier/classifier transport beyond the accepted packet.
\end{definition}

\begin{theorem}[MetricCompletion filter-branch scope]
\label{thm:metriccompletion-filter-branch-scope}
On the filter branch of an accepted $\MetricCompletionUp$ packet, every completion-facing read consumes the rows in the order
$$
\MetricUp,\ \CauchyFilterUp,\ \RegSeqRatUp\hbox{ or }\RealUp,\ \SeparatedMetricUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Equivalently, in the carrier notation it reads $X$, then $F$, then $R$, then $S$, and finally $H,C,P,N$. It has no route to a net branch, quotient completion row, selected representative, countable-choice schedule, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Start with the branch-interface scope of \autoref{def:metriccompletion-branch-interface-scope}. The filter case selects the displayed row $F$ after the source metric row $X$.

Apply the branch-readback and separated-comparison obligations, \autoref{thm:metric-completion-obligation-branch-readback} and \autoref{thm:metric-completion-obligation-separated-comparison}. These place $R$ after the chosen filter branch and place comparison at $S$ together with $H,C,P,N$.

Finally use the filter handoff and finite-readback ledger non-escape theorems, \autoref{thm:metric-completion-cauchy-filter-handoff} and \autoref{thm:metric-completion-finite-readback-ledger-nonescape}. The selected route remains $X,F,R,S,H,C,P,N$, and no absent completion principle is introduced downstream.
\end{proof}

\begin{theorem}[MetricCompletion net-branch scope]
\label{thm:metriccompletion-net-branch-scope}
On the net branch of an accepted $\MetricCompletionUp$ packet, every completion-facing read consumes the rows in the order
$$
\MetricUp,\ \CauchyNetUp,\ \RegSeqRatUp\hbox{ or }\RealUp,\ \SeparatedMetricUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Equivalently, in the carrier notation it reads $X$, then $D$, then $R$, then $S$, and finally $H,C,P,N$. It has no route to a filter branch, quotient completion row, selected representative, countable-choice schedule, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Start with the branch-interface scope of \autoref{def:metriccompletion-branch-interface-scope}. The net case selects the displayed row $D$ after the source metric row $X$.

Apply the branch-readback and separated-comparison obligations, \autoref{thm:metric-completion-obligation-branch-readback} and \autoref{thm:metric-completion-obligation-separated-comparison}. These place $R$ after the chosen net branch and place comparison at $S$ together with $H,C,P,N$.

Finally use the net handoff and finite-readback ledger non-escape theorems, \autoref{thm:metric-completion-cauchy-net-handoff} and \autoref{thm:metric-completion-finite-readback-ledger-nonescape}. The selected route remains $X,D,R,S,H,C,P,N$, and no absent completion principle is introduced downstream.
\end{proof}

\begin{theorem}[MetricCompletion Cauchy-evidence handoff]
\label{thm:metric-completion-cauchy-evidence-handoff}
Every completion-facing consumer of an accepted $\MetricCompletionUp$ packet reaches separated comparison only after the exact Cauchy-evidence handoff
$$
X \longmapsto (F\ \hbox{or}\ D) \longmapsto R \longmapsto S .
$$
On the filter branch this is the $\CauchyFilterUp$ route of \autoref{thm:metric-completion-cauchy-filter-handoff}; on the net branch this is the $\CauchyNetUp$ route of \autoref{thm:metric-completion-cauchy-net-handoff}. The row $R$ is the finite $\RegSeqRatUp$ or $\RealUp$ readback used before separated comparison, and the structural rows $H,C,P,N$ only transport, replay, source, and name the same route.
\end{theorem}
\begin{proof}
Use \autoref{thm:metric-completion-branch-coverage}. A consumer that has not chosen the filter branch $F$ or the net branch $D$ has no route to readback, separated comparison, or completion handoff.

In the filter case, apply \autoref{thm:metric-completion-cauchy-filter-handoff}. The route is $X$ to $F$, then to $R$, then to $S$, with the support rows preserving the same displayed evidence.

In the net case, apply \autoref{thm:metric-completion-cauchy-net-handoff}. The route is $X$ to $D$, then to $R$, then to $S$, again with only the support rows available downstream.

The finite-readback ledger non-escape theorem and the UniformCompletion handoff theorem, \autoref{thm:metric-completion-finite-readback-ledger-nonescape} and \autoref{thm:metric-completion-uniform-completion-handoff}, prevent the consumer from replacing this sequence by quotient completion data, selected representatives, host equality, countable choice, or ambient completeness.
\end{proof}

\begin{theorem}[Metric completion Cauchy-filter/net seal]
\label{thm:metriccompletion-cauchy-filter-net-seal}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. Every accepted completion-facing seal exposes either $\CauchyFilterUp$ evidence through $F$ or $\CauchyNetUp$ evidence through $D$ over the same displayed metric source $X$, and then reads the finite tolerance row $R$, separatedness row $S$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. The seal does not quotient Cauchy names, select a representative completion point, or replace $X$ by an ambient metric source.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-carrier}. The only metric source is $X$, and the only Cauchy evidence rows are the filter branch $F$ and the net branch $D$.

Use branch coverage and branch determinacy, \autoref{thm:metric-completion-branch-coverage} and \autoref{thm:metric-completion-filter-net-branch-determinacy}. These force every completion-facing seal to choose the displayed filter branch or the displayed net branch before any read reaches $R$ or $S$.

The local handoff theorems then identify the two allowed routes. Apply \autoref{thm:metric-completion-cauchy-filter-handoff} in the filter case and \autoref{thm:metric-completion-cauchy-net-handoff} in the net case.

Finally use \autoref{thm:metric-completion-finite-readback-ledger-nonescape} and \autoref{thm:metric-completion-branch-conversion-refusal}. The structural rows $H,C,P,N$ preserve and name the same selected route, while quotient names, representative selection, and ambient metric replacement have no carrier coordinate.
\end{proof}

\begin{theorem}[Metric completion separated-limit uniqueness boundary]
\label{thm:metriccompletion-separated-limit-uniqueness}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$, separatedness is the only uniqueness route exported to completion-facing consumers. Any identification of two displayed completion reads must pass through the $\SeparatedMetricUp$ row $S$ together with $H,C,P,N$, and no representative choice, quotient equality, host equality, or selected limit is exported by the packet.
\end{theorem}
\begin{proof}
Start from the classifier of \autoref{def:metric-completion-classifier}. It identifies reads only through the displayed metric source, selected Cauchy branch, finite readback, separatedness row, and structural rows.

Apply \autoref{thm:metric-completion-separated-limit-uniqueness}. The zero-distance evidence stored in $S$ is the route by which two displayed completion readings may be identified.

The comparison cannot move to host equality or quotient equality. The finite-readback ledger non-escape theorem, \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, excludes quotient classes, selected limits, representative choice, countable choice, and ambient completeness from the exported rows.

Thus uniqueness remains a local separatedness boundary: $S$ supplies the comparison, and $H,C,P,N$ transport, replay, source, and name that same comparison without adding any representative selector.
\end{proof}

\begin{theorem}[Metric completion uniform-completion handoff]
\label{thm:metriccompletion-uniform-completion-handoff}
Every $\UniformCompletionUp$ consumer of an accepted $\MetricCompletionUp$ packet consumes only the displayed metric source, the selected $\CauchyFilterUp$ or $\CauchyNetUp$ row, the finite readback row, separatedness row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows. In the carrier notation this is exactly
$$
X,(F\ \hbox{or}\ D),R,S,H,C,P,N .
$$
The handoff exports no quotient completion row, branch-conversion row, representative choice, host equality row, or independent uniform-completion classifier.
\end{theorem}
\begin{proof}
Use \autoref{thm:metric-completion-uniform-completion-handoff}. It states that a uniform-completion consumer reads the same Cauchy evidence, finite readback, separatedness, transport, replay, provenance, and naming rows as the metric-completion packet.

Next apply \autoref{thm:metric-completion-obligation-branch-readback}. This places the selected branch before $R$, so the uniform consumer cannot obtain tolerance data without first using the displayed filter or net evidence over $X$.

Apply \autoref{thm:metric-completion-obligation-separated-comparison} and \autoref{thm:metric-completion-uniform-seal-factorization}. They keep any comparison through $S,H,C,P,N$ and factor the seal through one selected branch.

The refusal and non-escape boundaries complete the handoff. By \autoref{thm:metric-completion-branch-conversion-refusal} and \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, no absent branch-conversion row, quotient row, representative selector, host equality row, or independent uniform-completion classifier can be recovered downstream.
\end{proof}

\begin{theorem}[MetricCompletion Cauchy-filter carrier admission]
\label{thm:metriccompletion-cauchyfilter-carrier-admission}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ carrier whose completion route uses the $\CauchyFilterUp$ branch. Then carrier admission for the filter route is exactly the displayed row chain
$$
\MetricUp\longmapsto\CauchyFilterUp\longmapsto R\longmapsto\SeparatedMetricUp\longmapsto\UniformCompletionUp ,
$$
where $R$ is the finite $\RegSeqRatUp$ or $\RealUp$ readback row named in \autoref{def:metric-completion-carrier}. The admission route has no coordinate for $\CauchyNetUp$ conversion, quotient completion, selected representatives, selected limits, host equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier row by row. The filter-presented route reads the metric source $X$ first and then the displayed $\CauchyFilterUp$ row $F$; the net row $D$ remains an empty marker for this branch.

The numerical request is admitted only through $R$. Thus $\RegSeqRatUp$ windows or $\RealUp$ seal data are read as finite rows attached to the filter branch, not as selected limit representatives.

Separated comparison and uniform-completion handoff then use $S$ and the existing replay surface $C$. Since the tuple has no further coordinate, the excluded net conversion, quotient, selector, host-equality, choice, and ambient-completeness data cannot be part of filter carrier admission.
\end{proof}

\begin{theorem}[MetricCompletion Cauchy-filter limit factorization]
\label{thm:metriccompletion-cauchyfilter-limit-factorization}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$ with displayed $\CauchyFilterUp$ branch $F$, every completion-facing limit read factors through $X,F,R,S,H,C,P,N$ before any $\UniformCompletionUp$ consumer may inspect it. If a $\CauchyNetUp$ branch is also named elsewhere in the ambient theory, it is not read by this factorization unless it appears as the selected branch of the same packet.
\end{theorem}
\begin{proof}
Start with the completion-facing request. The replay row $C$ sends the request to the metric source $X$, then to the filter evidence $F$, and then to the finite readback row $R$.

The limit comparison is not selected externally. It is checked through the separatedness row $S$, which supplies only zero-distance classifier evidence over the displayed source metric and the chosen Cauchy-filter branch.

The final handoff to a uniform-completion consumer is therefore a repacking of the same rows under $H,P,N$. A separately named $\CauchyNetUp$ route is outside this branch unless it is the selected row of the packet, so no branch conversion or selected limit can be inferred.
\end{proof}

\begin{theorem}[MetricCompletion Real-seal nonescape]
\label{thm:metriccompletion-real-seal-nonescape}
Every $\RealUp$ read exported by an accepted $\MetricCompletionUp$ packet factors through the displayed finite readback row $R$ after the selected $\CauchyFilterUp$ or $\CauchyNetUp$ branch and before the $\SeparatedMetricUp$ comparison row. Consequently a downstream $\UniformCompletionUp$ or L10 real-completion consumer cannot recover $\RealUp$ completeness, quotient stream equality, selected representatives, selected limits, countable choice, host equality, or ambient complete metric space data from the packet.
\end{theorem}
\begin{proof}
Inspect the carrier definition. The only numerical coordinate is $R$, and $R$ is explicitly the finite $\RegSeqRatUp$ or $\RealUp$ readback row used after a selected Cauchy branch.

The separatedness row $S$ can compare displayed limit readings only after that finite readback has been opened. It supplies zero-distance classifier evidence, not a proof that the host real line is complete.

Uniform-completion and L10 real-completion consumers then replay the same route through $H,C,P,N$. Since quotient streams, representatives, selected limits, countable-choice schedules, host equality rows, and ambient complete metric spaces are absent from the tuple, the Real-seal read cannot escape to any of them.
\end{proof}

\begin{theorem}[MetricCompletion root carrier obligation]
\label{thm:metriccompletion-root-obligation-carrier}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet. The root carrier projection of $M$ is exhausted by the displayed route
$$
\MetricUp\longmapsto (F:\CauchyFilterUp)\ \text{or}\ (D:\CauchyNetUp)\longmapsto R\longmapsto \SeparatedMetricUp\longmapsto H,C,P,N ,
$$
where $R$ is the finite $\RegSeqRatUp$ or $\RealUp$ readback row attached to the selected branch. Thus every root consumer of $M$ must expose the metric source $X$, one selected Cauchy branch, the finite readback row $R$, the separated comparison row $S$, and the structural rows $H,C,P,N$ before it can read any completion-facing endpoint.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:metric-completion-carrier}. Its visible analytic source is $X$, and the only Cauchy evidence available to a consumer is the displayed filter row $F$ or the displayed net row $D$.

Use branch coverage from \autoref{thm:metric-completion-branch-coverage}. The packet selects one branch for the requested read, and the filter-net compatibility theorem \autoref{thm:metric-completion-filter-net-compatibility} allows only the recorded compatibility rows to mediate between the two presentations.

The numerical endpoint then passes through $R$ and the separated comparison row $S$. The finite readback compatibility of \autoref{thm:metric-completion-finite-readback-ledger-nonescape} keeps the $\RegSeqRatUp$ or $\RealUp$ row attached to the selected branch.

Finally the transport, replay, provenance, and naming fields $H,C,P,N$ repack the same carrier. Since there is no additional coordinate, a root consumer cannot read quotient completions, selected representatives, choice schedules, open-cover compactness, or ambient $\RealUp$ completeness from carrier admission.
\end{proof}

\begin{theorem}[MetricCompletion root classifier obligation]
\label{thm:metriccompletion-root-obligation-classifier}
Let $M=(X,F,D,R,S,H,C,P,N)$ and $M'=(X',F',D',R',S',H',C',P',N')$ be accepted $\MetricCompletionUp$ packets. If $X,F,D,R,S,H,C,P,N$ and $X',F',D',R',S',H',C',P',N'$ are related componentwise by the displayed $\hsame$ rows and the replay rows $\Cont$ transport the same selected Cauchy branch, then the root classifier for $\MetricCompletionUp$ is stable between $M$ and $M'$. The stability claim is only this componentwise replay; it does not identify quotient completions, selected representatives, host equality, open-cover compactness, or ambient complete metric spaces.
\end{theorem}
\begin{proof}
Begin with the classifier of \autoref{def:metric-completion-classifier}. It compares packets by reading the metric source, the selected Cauchy branch, the finite readback, the separated comparison, and the structural rows.

Apply carrier projection from \autoref{thm:metriccompletion-root-obligation-carrier}. Componentwise $\hsame$ transport moves each visible row of $M$ to the matching visible row of $M'$ without changing the order in which the branch and readback rows are inspected.

The replay hypothesis supplies the $\Cont$ part of the comparison. It ensures that a request routed through $F$ or $D$ in one packet is routed through the matching branch in the other packet, using only the compatibility rows already displayed by the packets.

Thus the classifier is stable under the stated componentwise transport and replay. The proof has not introduced a quotient completion, representative selector, host equality row, open-cover compactness proof, or ambient complete metric space; those objects remain outside the classifier surface.
\end{proof}

\begin{theorem}[MetricCompletion root ledger nonescape]
\label{thm:metriccompletion-root-obligation-ledger}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$, every root ledger read factors through the selected Cauchy branch, the finite readback row $R$, and the separated comparison row $S$. Consequently the packet exports no quotient completion ledger, selected representative ledger, choice ledger, open-cover compactness ledger, ambient complete-metric ledger, or $\RealUp$ completeness ledger.
\end{theorem}
\begin{proof}
Use the finite readback ledger nonescape theorem \autoref{thm:metric-completion-finite-readback-ledger-nonescape}. It places every numerical ledger entry after the selected Cauchy branch and before the downstream separated or uniform-completion read.

Next use separated-limit uniqueness, \autoref{thm:metric-completion-separated-limit-uniqueness} and \autoref{thm:metriccompletion-separated-limit-uniqueness}. These results identify displayed zero-distance comparisons through $S$; they do not create a selected host representative.

The uniform handoff theorem \autoref{thm:metric-completion-uniform-completion-handoff} then exports only the same branch, readback, separatedness, transport, replay, provenance, and naming rows. Downstream consumers therefore see the ledger already present in $M$.

Since quotient completions, representative selectors, countable-choice schedules, open-cover compactness, ambient complete metric spaces, and $\RealUp$ completeness are absent from the carrier tuple, no root ledger read can escape to those objects.
\end{proof}

\begin{theorem}[MetricCompletion root carrier witness obligation]
\label{thm:metriccompletion-root-obligation-carrier-witness}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$ and any $\BHist$-anchored root carrier request, the displayed witness is the finite row sequence consisting of the metric source $X$, the selected Cauchy branch, the finite readback row $R$, the separatedness row $S$, and the structural rows $H,C,P,N$. If the selected branch is the filter route, the witness reads $F$ before $R$; if it is the net route, the witness reads $D$ before $R$. No root carrier witness may consume a completion endpoint before this same route has exposed $R,S,H,C,P,N$.
\end{theorem}
\begin{proof}
Start with carrier projection from \autoref{thm:metriccompletion-root-obligation-carrier}. It already exhausts the accepted packet by $X$, one chosen Cauchy branch, $R,S,H,C,P,N$.

Use branch coverage from \autoref{thm:metric-completion-branch-coverage}. The request selects exactly the displayed filter row $F$ or the displayed net row $D$ for the root read, so the witness cannot mix the two routes.

Finally apply finite-readback nonescape, \autoref{thm:metric-completion-finite-readback-ledger-nonescape}. The readback row $R$ remains downstream of the selected branch and upstream of separatedness and structural replay, giving the required $\BHist$-anchored witness form.
\end{proof}

\begin{theorem}[MetricCompletion root classifier witness obligation]
\label{thm:metriccompletion-root-obligation-classifier-witness}
Let $M=(X,F,D,R,S,H,C,P,N)$ and $M'=(X',F',D',R',S',H',C',P',N')$ be accepted $\MetricCompletionUp$ packets. A $\BHist$-anchored root classifier witness between them consists of componentwise $\hsame$ rows for the metric source, the selected Cauchy branch, the finite readback row $R$, the separatedness row $S$, and the structural rows $H,C,P,N$, together with replay evidence that the same selected branch is read on both sides. Thus the classifier witness is branch-specific and cannot be replaced by quotient completion equality, selected representatives, or host metric equality.
\end{theorem}
\begin{proof}
Begin with the root classifier obligation, \autoref{thm:metriccompletion-root-obligation-classifier}. It states classifier stability using componentwise transport and replay for the displayed rows of the two packets.

The branch-specific part is supplied by branch coverage and filter-net compatibility. The selected Cauchy route is fixed before $R$ is read, and compatibility can only mediate through recorded rows of the accepted packets.

The witness is therefore the finite transport data for the selected route plus $R,S,H,C,P,N$. Since the cited classifier theorem never introduces a quotient completion, representative selector, or host metric equality, the witness has no coordinate for those objects.
\end{proof}

\begin{theorem}[MetricCompletion root ledger witness obligation]
\label{thm:metriccompletion-root-obligation-ledger-witness}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$, every $\BHist$-anchored root ledger witness is the displayed ledger route through the selected Cauchy branch, the finite readback row $R$, the separatedness row $S$, and the structural rows $H,C,P,N$. The witness records whether the selected branch is $F$ or $D$, records the finite readback row $R$ attached to that branch, and records the separatedness row $S$ before any uniform-completion or Real-facing consumer may use the ledger.
\end{theorem}
\begin{proof}
Use the root ledger nonescape theorem \autoref{thm:metriccompletion-root-obligation-ledger}. It places every root ledger read behind the selected branch, $R$, and $S$.

Refine the ledger route by finite-readback nonescape. The row $R$ is not an ambient endpoint; it is the finite $\RegSeqRatUp$ or $\RealUp$ readback attached to the displayed Cauchy branch.

Finally use carrier projection and branch coverage to repack the same rows as a witness. The structural rows $H,C,P,N$ transport, replay, source, and name this ledger, while no additional coordinate supplies quotient completion ledgers, selected representatives, choice schedules, or ambient completeness.
\end{proof}

\begin{theorem}[MetricCompletion source-separated scope]
\label{thm:metriccompletion-source-separated-scope}
Let $M=(X,F,D,R,S,H,C,P,N)$ be an accepted $\MetricCompletionUp$ packet that reaches a completion-facing consumer. The consumer first exposes the $\MetricUp$ source row $X$, exactly one cofinal Cauchy branch, either the $\CauchyFilterUp$ row $F$ or the $\CauchyNetUp$ row $D$, the finite $\RegSeqRatUp$ or $\RealUp$ readback row $R$, the $\SeparatedMetricUp$ zero-distance uniqueness row $S$, and then the $\UniformCompletionUp$ handoff through $H,C,P,N$. Thus the source-separated scope of the packet is exactly the displayed route
$$
\MetricUp\longmapsto(\CauchyFilterUp\ \text{or}\ \CauchyNetUp)\longmapsto(\RegSeqRatUp\ \text{or}\ \RealUp)\longmapsto\SeparatedMetricUp\longmapsto\UniformCompletionUp .
$$
This scope excludes quotient completion equality, selected representatives, countable choice, ambient completeness, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:metric-completion-carrier}. Its visible source is the metric row $X$, and its only completion evidence rows are the displayed filter row $F$ and net row $D$.

The NameCert obligation theorem, \autoref{thm:metric-completion-namecert-obligations}, keeps every accepted packet on the same carrier, classifier, stability, transport, replay, provenance, and naming surface. Branch coverage from \autoref{thm:metric-completion-branch-coverage} then forces a completion-facing consumer to choose exactly one of the two cofinal Cauchy routes before reading numerical data.

The finite readback ledger nonescape theorem, \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, places the $\RegSeqRatUp$ or $\RealUp$ row after that selected branch and before any separated or uniform-completion read. The root obligation ledger, \autoref{thm:metriccompletion-root-obligation-ledger}, repacks this same order at the root level.

It remains only to mark the boundary. Since the carrier has no quotient-equality coordinate, representative selector, choice schedule, ambient complete-space row, or $\RealUp$ completeness row, those principles cannot be opened by a completion-facing consumer. The consumer therefore reaches $\UniformCompletionUp$ only through $X$, the selected branch, $R$, $S$, and the structural rows $H,C,P,N$.
\end{proof}

\begin{theorem}[MetricCompletion scoped dependency package]\label{thm:metriccompletion-scoped-dependency-package}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$, the scoped proof surface is bound by the existing carrier, classifier, Cauchy-filter handoff, Cauchy-net handoff, finite readback, separated-limit uniqueness, uniform-completion handoff, and root obligation rows. More precisely, every completion-facing consumer factors through the displayed route over $\MetricUp$, $\CauchyFilterUp$, $\CauchyNetUp$, $\RegSeqRatUp$ or $\RealUp$ readback, $\SeparatedMetricUp$, $\UniformCompletionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, and through no quotient completion, selected representative, ambient complete metric space, open-cover compactness, countable-choice schedule, or host equality row.
\end{theorem}
\begin{proof}
Carrier and classifier scope come from \autoref{def:metric-completion-carrier}, \autoref{def:metric-completion-classifier}, and \autoref{thm:metric-completion-namecert-obligations}. These fix the visible rows $X,F,D,R,S,H,C,P,N$ and require all local naming reads to pass through the same finite packet.

The Cauchy branch surface is then supplied by \autoref{thm:metric-completion-cauchy-filter-handoff}, \autoref{thm:metriccompletion-cauchy-filter-net-seal}, \autoref{thm:metric-completion-cauchy-net-handoff}, \autoref{thm:metric-completion-filter-net-branch-determinacy}, \autoref{thm:metric-completion-branch-coverage}, and \autoref{thm:metric-completion-filter-net-compatibility}. Together these rows bind the filter and net presentations to the displayed branch evidence and prevent an unrecorded Cauchy presentation from entering the packet.

The endpoint and separation surface is supplied by \autoref{thm:metric-completion-finite-readback-ledger-nonescape}, \autoref{thm:metric-completion-separated-limit-uniqueness}, and \autoref{thm:metriccompletion-separated-limit-uniqueness}. These theorems place every $\RegSeqRatUp$ or $\RealUp$ readback behind the selected branch and keep zero-distance uniqueness inside the displayed $\SeparatedMetricUp$ row.

Finally, \autoref{thm:metric-completion-uniform-completion-handoff}, \autoref{thm:metriccompletion-uniform-completion-handoff}, \autoref{thm:metriccompletion-root-obligation-carrier}, \autoref{thm:metriccompletion-root-obligation-classifier}, \autoref{thm:metriccompletion-root-obligation-ledger}, and \autoref{thm:metriccompletion-source-separated-scope} repack the same data as the root and uniform-completion boundary. Since each cited row is a projection or replay of the displayed carrier, the scoped package contains exactly the named BEDC objects and none of the excluded ambient or choice principles.
\end{proof}

\begin{definition}[MetricCompletion scoped readback scope]
\label{def:metric-completion-scoped-readback-scope}
For an accepted $\MetricCompletionUp$ packet $M=(X,F,D,R,S,H,C,P,N)$, the scoped readback scope is the displayed route
$$
\MetricUp \longmapsto (\CauchyFilterUp\ \text{or}\ \CauchyNetUp) \longmapsto (\RegSeqRatUp\ \text{or}\ \RealUp) \longmapsto \SeparatedMetricUp \longmapsto \UniformCompletionUp
$$
together with the carrier rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ that transport, replay, source, and name that route. A read belongs to this scope exactly when it exposes the same metric source row $X$, exactly one of the Cauchy branch rows $F$ or $D$, the corresponding readback row $R$, the separatedness row $S$, and the uniform-completion handoff through $H,C,P,N$.
\end{definition}

\begin{theorem}[MetricCompletion uniform source lock]
\label{thm:metric-completion-uniform-source-lock}
Every $\UniformCompletionUp$ consumer of an accepted $\MetricCompletionUp$ packet must keep the same displayed $\MetricUp$ source row and the same chosen Cauchy branch. If the consumer reads through the $\CauchyFilterUp$ branch, all later finite readback, separatedness, transport, replay, provenance, and naming rows are read over $X,F,R,S,H,C,P,N$; if it reads through the $\CauchyNetUp$ branch, the corresponding rows are read over $X,D,R,S,H,C,P,N$. No uniform-completion read may switch between the two branches or replace $X$ by an ambient metric source.
\end{theorem}
\begin{proof}
Start with \autoref{def:metric-completion-scoped-readback-scope}. A scoped read is admitted only after the displayed $\MetricUp$ row $X$ and exactly one Cauchy branch have been opened.

The branch is fixed by the existing coverage and compatibility rows. Theorems \autoref{thm:metric-completion-branch-coverage}, \autoref{thm:metric-completion-filter-net-compatibility}, and \autoref{thm:metriccompletion-source-separated-scope} place finite readback after the selected branch and before separatedness or uniform completion.

Finally apply \autoref{thm:metriccompletion-scoped-dependency-package}. Its package route carries the same $X,F,D,R,S,H,C,P,N$ rows through transport and replay, so a uniform-completion consumer has no coordinate from which to substitute a new metric source or cross from the chosen filter route to the net route.
\end{proof}

\begin{theorem}[MetricCompletion no ambient completion scope]
\label{thm:metric-completion-no-ambient-completion-scope}
No scoped read of an accepted $\MetricCompletionUp$ packet can introduce a quotient completion, selected representative, ambient complete metric space, open-cover compactness row, countable-choice schedule, or $\RealUp$ completeness theorem. Every completion-facing read is already exhausted by the scoped readback route of \autoref{def:metric-completion-scoped-readback-scope} and the source lock of \autoref{thm:metric-completion-uniform-source-lock}.
\end{theorem}
\begin{proof}
Inspect the carrier of \autoref{def:metric-completion-carrier}. Its visible coordinates are the metric source, filter branch, net branch, readback row, separatedness row, transport, continuation, provenance, and local name.

The scoped readback definition repacks exactly those coordinates as the route through $\MetricUp$, a chosen Cauchy branch, finite readback, $\SeparatedMetricUp$, and $\UniformCompletionUp$. The source-lock theorem then prevents a consumer from replacing the displayed source or changing branches after the read has begun.

The excluded objects are not fields of the carrier and are not introduced by the cited package rows. Therefore quotient completions, representatives, ambient complete spaces, open-cover compactness, countable-choice data, and $\RealUp$ completeness remain outside the scoped MetricCompletion surface.
\end{proof}

\begin{closurestatus}{\MetricCompletionUp}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:metric-completion-carrier}, \autoref{def:metric-completion-classifier}, \autoref{thm:metric-completion-namecert-obligations}, \autoref{thm:metriccompletion-scoped-dependency-package}, \autoref{def:metric-completion-scoped-readback-scope}, \autoref{thm:metric-completion-uniform-source-lock}, and \autoref{thm:metric-completion-no-ambient-completion-scope} bind the finite L10 metric-completion interface to the displayed Metric source, chosen Cauchy branch, readback, separatedness, uniform-completion, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, ambient complete metric spaces, open-cover compactness, countable choice, or $\RealUp$ completeness.}
  \upgradepath{Public closure requires a public MetricCompletion export surface and checked Lean carrier alignment for the scoped readback package.}
  \constructivestory{The construction starts from a displayed metric source, routes cofinal evidence through CauchyFilter or CauchyNet rows, reads finite RegSeqRat or Real tolerance data when requested, and uses SeparatedMetric uniqueness only as a local zero-distance classifier route.}
\end{closurestatus}
\closureat{MetricCompletionUp}{scopedStr}[BEDC.Derived.MetricCompletionUp.TasteGate.MetricCompletionTasteGate\_single\_carrier\_alignment]
