\chapter{A Concrete Naming Certificate for $\SequentiallyCompleteMetricUp$}
\label{ch:concrete-instances-sequentiallycompletemetric-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis and Kelley-style metric completion, the $\SequentiallyCompleteMetricUp$ packet records the L10 sequence-completeness interface as finite Cauchy-sequence data over a displayed metric source. It sits between the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the limit-witness boundary of \autoref{ch:concrete-instances-completemetric-namecert}, and the completion route of \autoref{ch:concrete-instances-metriccompletion-namecert}. The packet gives later real-completion consumers a traditional sequence-completeness bridge without quotienting Cauchy names, selecting representatives, using countable choice, invoking open-cover compactness, assuming ambient completeness, or asserting that $\RealUp$ is complete.

\begin{definition}[SequentiallyCompleteMetric carrier]
\label{def:sequentially-complete-metric-carrier}
A $\SequentiallyCompleteMetricUp$ carrier is a finite $\BHist$ packet
$$
Q=(X,S,M,L,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\MetricUp$ source row, including the admitted point classifier, distance witness surface, and finite metric observation histories.
\item $S$ is the regular Cauchy sequence row, read through $\StreamNameUp$ windows and $\RegSeqRatUp$ rational readbacks over the same metric source.
\item $M$ is the displayed modulus row assigning each positive tolerance request a finite late-index threshold.
\item $L$ is the displayed limit row, carried as an admitted point history of $X$ before any completion-facing consumer can read it.
\item $D$ is the distance-bound ledger whose rows display, for every requested tolerance and every sufficiently late sequence window, the metric-distance witness from the sequence value to $L$ and the rational comparison below that tolerance.
\item $H$ records componentwise $\hsame$ transport for the metric source, Cauchy-sequence rows, modulus, displayed limit, distance-bound ledger, replay row, provenance row, and local naming row.
\item $C$ records the displayed $\Cont$ replay from source metric admission to stream-window reads, regular rational readbacks, modulus thresholds, late-distance bounds, and the $\CompleteMetricUp$ limit-witness handoff.
\item $P$ is the $\Pkg$ provenance over $\SequentiallyCompleteMetricUp$, $\MetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\CompleteMetricUp$, $\MetricCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\SequentiallyCompleteMetricUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, countable choice, open-cover compactness, ambient completeness, or completeness of $\RealUp$.
\end{definition}

\begin{theorem}[SequentiallyCompleteMetric NameCert obligations]
\label{thm:sequentially-complete-metric-namecert-obligations}
For an accepted $\SequentiallyCompleteMetricUp$ carrier $Q=(X,S,M,L,D,H,C,P,N)$, the local $\NameCert_{\SequentiallyCompleteMetricUp}$ surface consists exactly of five obligations:
\begin{enumerate}
\item carrier admission for the displayed metric source, regular Cauchy sequence row, modulus, displayed limit, late-distance ledger, componentwise transport, continuation replay, provenance, and local naming;
\item classifier stability, requiring any accepted replacement of $Q$ to transport $X,S,M,L,D$ componentwise by $H$ before the local classifier identifies the two packets;
\item sequence convergence, requiring each tolerance request to read a threshold from $M$ and then a late-distance row from $D$ witnessing convergence of the displayed sequence $S$ to the displayed limit $L$ inside $X$;
\item $\CompleteMetricUp$ handoff, requiring the same rows $S,M,L,D$ to supply the limit-witness surface consumed by \autoref{ch:concrete-instances-completemetric-namecert};
\item ledger non-escape, stating that no quotient completion, selected representative, countable-choice schedule, open-cover compactness principle, ambient-completeness witness, or $\RealUp$ completeness theorem is exported by the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:sequentially-complete-metric-carrier}. The tuple exposes the metric source, sequence row, modulus, limit row, distance-bound ledger, transport, replay, provenance, and local name as visible rows.

Classifier stability is componentwise. A comparison of two accepted packets first transports the metric source, stream windows, regular rational readbacks, modulus thresholds, displayed limits, and distance-bound rows by $H$; only after that transport can the local classifier identify the two packets.

Sequence convergence is the content of $M$ and $D$. For each tolerance request, the modulus row supplies a late threshold, and the distance-bound ledger supplies the metric-distance witness from every displayed late sequence value to $L$ together with the rational comparison below the requested tolerance.

The complete-metric handoff consumes the same convergence rows rather than a second completion object. The replay row $C$ presents $S,M,L,D$ to the $\CompleteMetricUp$ limit-witness boundary, while $P$ and $N$ record that the route is sourced and named by the same finite packet.

The rows of $Q$ are exhausted by this route. Since none of them stores quotient equality, a selected representative, a countable-choice schedule, an open-cover compactness principle, an ambient complete space, or a $\RealUp$ completeness theorem, the ledger non-escape clause follows.
\end{proof}

\begin{theorem}[SequentiallyCompleteMetric complete-metric handoff]
\label{thm:sequentially-complete-metric-complete-metric-handoff}
Let $Q=(X,S,M,L,D,H,C,P,N)$ be an accepted $\SequentiallyCompleteMetricUp$ packet. If the source metric $X$, the stream rows $S$, the modulus row $M$, the displayed limit $L$, and all late-distance bounds $D$ are displayed, then $Q$ supplies the $\CompleteMetricUp$ limit-witness surface for that regular Cauchy sequence over $X$.

The handoff is the finite route
$$
X\longmapsto S\longmapsto M\longmapsto L\longmapsto D\longmapsto H,C,P,N .
$$
It exports sequence completeness only as a displayed limit-witness packet for the given regular Cauchy data, not as quotient completion, representative selection, countable choice, open-cover compactness, ambient completeness, or completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Start with the accepted carrier and project the metric source $X$. The point classifier and metric-distance witnesses used by the handoff are read from this source row, so the limit-witness surface is over the same metric carrier.

Next read the sequence and modulus rows. The row $S$ supplies the finite stream windows and regular rational readbacks of the Cauchy sequence, while $M$ supplies the threshold requested by each tolerance.

Now read the proposed limit and late-distance ledger. The row $L$ is already an admitted point history of $X$, and $D$ records the metric-distance witness from each sufficiently late displayed sequence value to $L$ together with the required rational comparison.

Finally replay the route through $C$ and attach $H,P,N$. These rows transport, source, and name exactly the data required by the $\CompleteMetricUp$ limit-witness boundary of \autoref{def:completemetric-limit-witness}. Because the route has no further coordinate, the handoff cannot export quotient completion, selected representatives, countable choice, open-cover compactness, ambient completeness, or $\RealUp$ completeness.
\end{proof}

\begin{closurestatus}{\SequentiallyCompleteMetricUp}
  \constructivestory{A $\SequentiallyCompleteMetricUp$ packet is generated from a displayed $\MetricUp$ source, a regular Cauchy sequence read through $\StreamNameUp$ and $\RegSeqRatUp$ rows, a modulus, a displayed limit point, late-distance bound rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sequentially-complete-metric-carrier}, \autoref{thm:sequentially-complete-metric-namecert-obligations}, and \autoref{thm:sequentially-complete-metric-complete-metric-handoff} seed the finite sequence-completeness bridge from regular Cauchy data to the $\CompleteMetricUp$ limit-witness surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected representatives, countable choice, open-cover compactness, ambient completeness, or any assertion that $\RealUp$ is complete.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, sequence convergence, complete-metric handoff, and ledger non-escape for the same packet.}
\end{closurestatus}
