\chapter{A Concrete Naming Certificate for $\CauchySequenceSpaceUp$}
\label{ch:concrete-instances-cauchysequencespace-namecert}
\origin{human}

The $\CauchySequenceSpaceUp$ interface records the finite naming surface for the space of $\CauchySequenceUp$ names itself. Following Bishop and Bridges, \emph{Constructive Analysis}, and Bourbaki, \emph{General Topology}, the packet keeps a displayed family of regular rational names together with the finite schedules and tolerance ledgers that make common Cauchy windows inspectable. It sits between $\RegSeqRatUp$, $\StreamNameUp$, $\CauchyFilterUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, and $\RealCauchyCompletionUp$, and it exports only $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

This dependency is the concrete sibling route: the displayed regular-family row is consumed from \autoref{ch:concrete-instances-regseqrat-namecert}, the schedule row from \autoref{ch:concrete-instances-streamname-namecert}, and the completion handoff row from \autoref{ch:concrete-instances-real-cauchy-completion-namecert}.

\begin{definition}[CauchySequenceSpace carrier surface]
\label{def:cauchysequence-space-carrier-surface}
A $\CauchySequenceSpaceUp$ carrier is a finite $\BHist$ packet
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $F$ is a displayed finite family of $\RegSeqRatUp$ name rows;
\item $\sigma$ is the $\StreamNameUp$ schedule that selects the inspected name and window rows;
\item $W$ is a $\CauchyFilterUp$ or $\CauchyModulusUp$ cofinal-window ledger for the family $F$;
\item $\epsilon$ is the $\DyadicRatCoreUp$ tolerance ledger used by the inspected windows;
\item $Q$ is the $\RealCauchyCompletionUp$ handoff row reached from the same family, schedule, window, and tolerance data;
\item $H$ records componentwise $\hsame$ transports for the family, schedule, cofinal-window ledger, tolerance ledger, and completion handoff;
\item $C$ records the displayed $\Cont$ routes by which consumers inspect those rows;
\item $P$ is the $\Pkg$ provenance over the displayed regular names, stream schedule, Cauchy window data, dyadic tolerances, and completion handoff;
\item $N$ is the local $\NameCert_{\CauchySequenceSpaceUp}$ row.
\end{enumerate}
The carrier contains no quotient of Cauchy names, no selected limiting name, no host completion equality, and no ambient completeness principle.
\end{definition}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.TasteGate.CauchySequenceSpaceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchySequenceSpace NameCert obligation surface]
\label{thm:cauchysequence-space-namecert-obligation-surface}
The local $\NameCert_{\CauchySequenceSpaceUp}$ surface consists of five finite rows:
\begin{enumerate}
\item carrier habitation by a displayed family of $\RegSeqRatUp$ names, a $\StreamNameUp$ schedule, a $\CauchyFilterUp$ or $\CauchyModulusUp$ cofinal-window ledger, a $\DyadicRatCoreUp$ tolerance ledger, a $\RealCauchyCompletionUp$ handoff row, and the displayed $\hsame$, $\Cont$, $\Pkg$, and local naming rows;
\item classifier by common finite Cauchy windows, comparing two accepted packets only through windows selected by their schedules and justified by the same visible cofinality ledger shape;
\item schedule and cofinality stability under the stored componentwise $\hsame$ transports and displayed $\Cont$ routes;
\item dyadic tolerance exactness, stating that every accepted window comparison uses the tolerance row visible in the packet;
\item completion handoff non-escape, stating that the $\RealCauchyCompletionUp$ row is reached only through the displayed family, schedule, cofinal-window, tolerance, transport, continuation, package, and naming rows.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_namecert\_obligation\_surface}
\begin{proof}
Carrier habitation is projection of \autoref{def:cauchysequence-space-carrier-surface}. The displayed family, schedule, cofinal-window ledger, tolerance ledger, completion handoff, transport, continuation, package, and naming rows are coordinates of the same finite $\BHist$ packet.

The classifier is by common finite windows. A comparison first reads the scheduled $\RegSeqRatUp$ rows, then the cofinal-window evidence supplied by $W$, and finally the dyadic tolerance row $\epsilon$ attached to those windows.

Schedule stability is componentwise. Move the family, schedule, window ledger, tolerance ledger, and completion handoff along $H$, and replay only the consumer routes recorded in $C$.

Dyadic tolerance exactness and handoff non-escape follow from the absence of any quotient, selected limit, host equality, or ambient completeness coordinate. The completion row $Q$ is therefore a finite handoff from the named Cauchy-window surface, not a separate completion object.
\end{proof}

\begin{theorem}[CauchySequenceSpace completion handoff]
\label{thm:cauchysequence-space-completion-handoff}
Every $\RealCauchyCompletionUp$ consumer read exported by an accepted $\CauchySequenceSpaceUp$ carrier factors through the displayed $\RegSeqRatUp$ family row, the $\StreamNameUp$ schedule, the $\CauchyFilterUp$ or $\CauchyModulusUp$ cofinal-window ledger, the $\DyadicRatCoreUp$ tolerance ledger, and the stored $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance rows. Thus the space of Cauchy names reaches completion only through the visible finite naming certificate, not through quotient-name equality, a selected representative, host real equality, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_completion\_handoff}
\begin{proof}
Start with an accepted carrier $S=(F,\sigma,W,\epsilon,Q,H,C,P,N)$. The only family coordinate is $F$, the only schedule coordinate is $\sigma$, and the only Cauchy-window and tolerance coordinates are $W$ and $\epsilon$.

Use \autoref{thm:cauchysequence-space-namecert-obligation-surface}. Its classifier, stability, and exactness rows force every inspected window to remain attached to the displayed schedule, cofinality ledger, dyadic tolerance ledger, and provenance rows.

The completion read reaches $Q$ only after those rows have been read. Since the carrier has no quotient-name equality, selected representative, host real equality, or ambient completeness coordinate, the listed rows exhaust the handoff boundary.
\end{proof}

\begin{theorem}[CauchySequenceSpace regular-window factorization]
\label{thm:cauchysequence-space-regular-window-factorization}
Let $S$ be an accepted $\CauchySequenceSpaceUp$ packet
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N).
$$
Every completion-facing consumer read of $Q$ factors through the displayed $\RegSeqRatUp$ family row $F$, the $\StreamNameUp$ schedule $\sigma$, the cofinal Cauchy-window ledger $W$, the $\DyadicRatCoreUp$ tolerance row $\epsilon$, the componentwise $\hsame$ transport row $H$, the displayed $\Cont$ read routes $C$, the package row $P$, and the local $\NameCert$ row $N$. No quotient-name equality, selected representative, host real equality, or ambient completeness row participates in this route.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_regular\_window\_factorization}
\begin{proof}
Project the accepted carrier by \autoref{def:cauchysequence-space-carrier-surface}. This identifies the only available coordinates as the displayed family $F$, schedule $\sigma$, window ledger $W$, tolerance row $\epsilon$, completion handoff $Q$, transport row $H$, continuation row $C$, package row $P$, and local naming row $N$.

Use \autoref{thm:cauchysequence-space-namecert-obligation-surface} for the common-window classifier, schedule and cofinality stability, dyadic tolerance exactness, and completion handoff non-escape rows. These rows keep every inspected regular-name comparison on the same scheduled finite windows and on the same displayed dyadic tolerance data.

Apply \autoref{thm:cauchysequence-space-completion-handoff} to the terminal consumer read of $Q$. The route already reaches the completion handoff only through the named regular family, schedule, Cauchy-window ledger, dyadic tolerance row, transports, continuations, package provenance, and local certificate.

Finally, the carrier projection lists no quotient-name equality, selected representative, host real equality, or ambient completeness coordinate. Thus there is no alternate completion-facing route outside the displayed finite regular-window surface.
\end{proof}

\begin{theorem}[CauchySequenceSpace common-window classifier transport]
\label{thm:cauchysequence-space-common-window-classifier-transport}
Let $S=(F,\sigma,W,\epsilon,Q,H,C,P,N)$ be an accepted $\CauchySequenceSpaceUp$ packet. Transporting $S$ along its displayed $\hsame$ row $H$ and reading it only through the displayed $\Cont$ row $C$ preserves the common-window classifier on the same $\RegSeqRatUp$ family $F$, $\StreamNameUp$ schedule $\sigma$, $\CauchyFilterUp$ or $\CauchyModulusUp$ cofinal ledger $W$, $\DyadicRatCoreUp$ tolerance row $\epsilon$, completion handoff $Q$, package row $P$, and local $\NameCert$ row $N$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCommonWindowClassifierTransport}
\begin{proof}
Project the tuple by \autoref{def:cauchysequence-space-carrier-surface}. The family, schedule, cofinal ledger, tolerance ledger, completion handoff, transport row, continuation row, package row, and local naming row are the whole carrier inventory.

Use the classifier and stability clauses of \autoref{thm:cauchysequence-space-namecert-obligation-surface}. They say that comparisons are made only on common finite Cauchy windows selected by $\sigma$ and justified by the displayed cofinality row $W$.

The completion handoff theorem keeps the downstream read on the same packet rows. Hence transporting by $H$ and reading by $C$ cannot change the classifier into a quotient-name comparison, a selected representative comparison, a host real equality, or an ambient completeness assertion.
\end{proof}

\begin{theorem}[CauchySequenceSpace cofinal schedule stability]
\label{thm:cauchysequence-space-cofinal-schedule-stability}
For an accepted packet $S=(F,\sigma,W,\epsilon,Q,H,C,P,N)$ of $\CauchySequenceSpaceUp$, every cofinal Cauchy-window request admitted by $W$ remains stable under the $\StreamNameUp$ schedule $\sigma$, the componentwise $\hsame$ transports $H$, and the displayed $\Cont$ routes $C$. The accepted comparison stays on the displayed $\RegSeqRatUp$ family $F$, the $\CauchyFilterUp$ or $\CauchyModulusUp$ ledger $W$, the $\DyadicRatCoreUp$ tolerance row $\epsilon$, the handoff row $Q$, the package row $P$, and the local $\NameCert$ row $N$.
\end{theorem}
\begin{proof}
Begin with a cofinal request in $W$. By the carrier definition, $W$ is stored together with the schedule $\sigma$ and the family $F$, so the request has no independent schedule coordinate.

Apply the schedule and cofinality stability row of \autoref{thm:cauchysequence-space-namecert-obligation-surface}. The row moves $F$, $\sigma$, $W$, $\epsilon$, and $Q$ only componentwise along $H$ and replays only the consumer routes recorded in $C$.

Finally use \autoref{thm:cauchysequence-space-regular-window-factorization}. It identifies the same family, schedule, cofinal ledger, tolerance ledger, transport, continuation, package, and naming rows as the entire completion-facing route, so stability is a property of the displayed packet and not of any hidden completion object.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_cofinal\_schedule\_stability}

\begin{theorem}[CauchySequenceSpace dyadic tolerance ledger exactness]
\label{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness}
Let $S=(F,\sigma,W,\epsilon,Q,H,C,P,N)$ be an accepted $\CauchySequenceSpaceUp$ packet. Every accepted comparison in the common-window classifier uses exactly the $\DyadicRatCoreUp$ tolerance row $\epsilon$ stored beside the $\RegSeqRatUp$ family $F$, $\StreamNameUp$ schedule $\sigma$, $\CauchyFilterUp$ or $\CauchyModulusUp$ ledger $W$, completion handoff $Q$, $\hsame$ row $H$, $\Cont$ row $C$, $\Pkg$ row $P$, and $\NameCert$ row $N$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_dyadic\_tolerance\_ledger\_exactness}
\begin{proof}
The tolerance coordinate of the carrier is the single row $\epsilon$. There is no second dyadic ledger, host tolerance, quotient-name tolerance, or ambient completeness tolerance in \autoref{def:cauchysequence-space-carrier-surface}.

Use the dyadic tolerance exactness clause of \autoref{thm:cauchysequence-space-namecert-obligation-surface}. It attaches every accepted window comparison to the tolerance row visible in the same packet.

The completion handoff theorem then carries that exact row to $Q$ together with $F$, $\sigma$, $W$, $H$, $C$, $P$, and $N$. Thus the tolerance ledger consumed by completion is precisely $\epsilon$, and no hidden tolerance source participates in the route.
\end{proof}

\begin{theorem}[CauchySequenceSpace limit-seal factorization]
\label{thm:cauchysequence-space-limit-seal-factorization}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Any $\RealUp$ limit-seal consumer read of the completion handoff row $Q$ factors through the displayed $\RegSeqRatUp$ family $F$, the $\StreamNameUp$ schedule $\sigma$, the $\CauchyFilterUp$ or $\CauchyModulusUp$ cofinal ledger $W$, the $\DyadicRatCoreUp$ tolerance row $\epsilon$, the completion handoff $Q$, the $\hsame$ transport row $H$, the displayed $\Cont$ routes $C$, the $\Pkg$ provenance $P$, and the local $\NameCert_{\CauchySequenceSpaceUp}$ row $N$.

The read cannot use quotient-name equality, a selected representative, host real equality, or ambient completeness outside the displayed finite packet.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_limit\_seal\_factorization}
\begin{proof}
Project the carrier surface of \autoref{def:cauchysequence-space-carrier-surface}. The rows $F,\sigma,W,\epsilon,Q,H,C,P,N$ are the whole accepted packet.

Use the NameCert obligation surface of \autoref{thm:cauchysequence-space-namecert-obligation-surface}. It supplies common-window classification, schedule stability, cofinality stability, dyadic tolerance exactness, and completion handoff non-escape for that same packet.

Apply \autoref{thm:cauchysequence-space-regular-window-factorization}, \autoref{thm:cauchysequence-space-common-window-classifier-transport}, \autoref{thm:cauchysequence-space-cofinal-schedule-stability}, and \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness}. These results keep the read on the displayed regular family, schedule, cofinal window ledger, and tolerance ledger before it reaches $Q$.

Finally, \autoref{thm:cauchysequence-space-completion-handoff} identifies the terminal route to completion. Since the carrier lists no quotient-name equality, selected representative, host real equality, or ambient completeness row, the limit-seal consumer read has no hidden coordinate through which to bypass the displayed factorization.
\end{proof}

\begin{theorem}[CauchySequenceSpace RegSeqRat StreamName Real seal factorization]
\label{thm:cauchysequence-space-regseqrat-streamname-real-seal-factorization}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Every $\RealUp$ limit-seal consumer route and every $\RealCauchyCompletionUp$-facing consumer route factors first through the displayed $\RegSeqRatUp$ family $F$, then through the $\StreamNameUp$ schedule $\sigma$, then through the cofinal-window ledger $W$, then through the $\DyadicRatCoreUp$ tolerance row $\epsilon$, and only then reaches the completion handoff $Q$ and the $\RealUp$ seal boundary.

The resulting route exports no quotient stream, no selected limit, no host real equality, and no ambient completeness coordinate outside $F,\sigma,W,\epsilon,Q,H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_regseqrat\_streamname\_real\_seal\_factorization}
\begin{proof}
Start with the regular-family route. Apply \autoref{thm:cauchysequence-space-regular-window-factorization} to expose $F$ as the finite rational family through which completion-facing reads must first pass.

Next attach the schedule and cofinal ledger. Use \autoref{thm:cauchysequence-space-cofinal-schedule-stability} to keep $\sigma$ and $W$ as the only scheduled window surface available to the consumer.

Then read the tolerance and handoff rows. Apply \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness} for $\epsilon$ and \autoref{thm:cauchysequence-space-completion-handoff-stability} for $Q$, so the completion-facing route cannot reach the handoff before the displayed dyadic tolerance row has been consumed.

Finally apply \autoref{thm:cauchysequence-space-limit-seal-factorization}. It identifies the $\RealUp$ seal boundary with the same displayed packet and excludes quotient streams, selected limits, host real equality, and ambient completeness coordinates from the consumer route.
\end{proof}

\begin{theorem}[CauchySequenceSpace two-stage window composition]
\label{thm:cauchysequence-space-two-stage-window-composition}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
and
$$
S'=(F',\sigma',W',\epsilon',Q',H',C',P',N')
$$
be accepted $\CauchySequenceSpaceUp$ packets. Suppose their regular-family rows, stream schedules, common-window ledgers, dyadic tolerance rows, completion-handoff rows, displayed $\hsame$ transports, and $\Cont$ routes are componentwise matched by the local classifier. Then every consumer read that first compares $S$ and $S'$ by common finite windows and then hands the result to completion factors through one shared finite window before it reaches $Q$ or $Q'$.

The factorization uses only $F,F'$, $\sigma,\sigma'$, $W,W'$, $\epsilon,\epsilon'$, $Q,Q'$, $H,H'$, $C,C'$, $P,P'$, and $N,N'$. It has no route through quotient streams, selected limits, host real equality, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_two\_stage\_window\_composition}
\begin{proof}
First build the common-window spine. Apply \autoref{thm:cauchysequence-space-regular-window-factorization} to each packet to identify the finite regular-family rows, schedules, cofinal ledgers, tolerance rows, handoff rows, transports, continuations, provenance, and local certificates as the whole read surface.

Next transport the classifier. Use \autoref{thm:cauchysequence-space-common-window-classifier-transport} to move the two accepted packets componentwise along the displayed $\hsame$ rows while replaying only the $\Cont$ routes already stored in the packets.

The schedule and tolerance rows now have no independent path. Apply \autoref{thm:cauchysequence-space-cofinal-schedule-stability} for $\sigma,\sigma',W,W'$ and \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness} for $\epsilon,\epsilon'$. These two rows bind every tolerated comparison to the same shared finite window before any completion-facing handoff is read.

Finally route the result to the terminal handoff through \autoref{thm:cauchysequence-space-limit-seal-factorization}. The carrier exposes no quotient stream, selected limit, host real equality, or ambient completeness coordinate, so the composed consumer cannot leave the displayed finite rows.
\end{proof}

\begin{theorem}[CauchySequenceSpace shared-window completion consumer]
\label{thm:cauchysequence-space-shared-window-completion-consumer}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
and
$$
S'=(F',\sigma',W',\epsilon',Q',H',C',P',N')
$$
be accepted $\CauchySequenceSpaceUp$ packets whose regular-family rows, schedules, cofinal-window rows, tolerance rows, and handoff rows classify together through the displayed local classifier. Any completion-facing consumer comparison factors through one shared finite Cauchy window before reading $Q$ or $Q'$. The route uses only $F,F'$, $\sigma,\sigma'$, $W,W'$, $\epsilon,\epsilon'$, $Q,Q'$, $H,H'$, $C,C'$, $P,P'$, and $N,N'$.
\end{theorem}
\begin{proof}
First build the shared window surface. Apply \autoref{thm:cauchysequence-space-regular-window-factorization} to both packets, so every completion-facing read is already restricted to the displayed regular-family, schedule, cofinal-window, tolerance, handoff, transport, continuation, package, and local naming rows.

Next transport the comparison through \autoref{thm:cauchysequence-space-common-window-classifier-transport}. The classifier reads the two packets only by their common finite Cauchy windows and the componentwise $\hsame$ and $\Cont$ rows already stored in the carriers.

The schedule and tolerance rows then fix the consumer window. Use \autoref{thm:cauchysequence-space-cofinal-schedule-stability} for $\sigma,\sigma',W,W'$ and \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness} for $\epsilon,\epsilon'$.

Finally apply \autoref{thm:cauchysequence-space-two-stage-window-composition}. The comparison reaches $Q$ or $Q'$ only after the shared finite window has been read, and the displayed packet contains no quotient stream, selected limit, host real equality, or ambient completeness route.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_shared\_window\_completion\_consumer}

\begin{theorem}[CauchySequenceSpace completion handoff stability]
\label{thm:cauchysequence-space-completion-handoff-stability}
Let $S=(F,\sigma,W,\epsilon,Q,H,C,P,N)$ be an accepted $\CauchySequenceSpaceUp$ packet. The completion handoff row $Q$ is invariant under the same displayed $\hsame$ transports $H$ and $\Cont$ routes $C$ that preserve the regular-family row $F$, schedule $\sigma$, common-window ledger $W$, and dyadic tolerance row $\epsilon$. A transported handoff therefore names the same completion-facing finite packet and not a quotient-name comparison, selected limit, host real equality, or ambient completeness assertion.
\end{theorem}
\begin{proof}
Read the handoff row from the carrier surface. The row $Q$ is stored beside $F$, $\sigma$, $W$, $\epsilon$, $H$, $C$, $P$, and $N$ and has no separate host-completion coordinate.

Apply \autoref{thm:cauchysequence-space-completion-handoff}. It states that downstream completion reads consume the same finite regular-family, schedule, window, tolerance, transport, continuation, provenance, and local certificate rows.

Use \autoref{thm:cauchysequence-space-common-window-classifier-transport} and \autoref{thm:cauchysequence-space-cofinal-schedule-stability} to identify the transported rows componentwise. The dyadic tolerance row is fixed by \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness}, so the handoff row is stable under exactly the displayed $H$ and $C$ routes.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_completion\_handoff\_stability}

\begin{theorem}[CauchySequenceSpace regular family exhaustion]
\label{thm:cauchysequence-space-regular-family-exhaustion}
Every completion-facing consumer read of an accepted $\CauchySequenceSpaceUp$ packet
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
factors through the displayed regular family $F$, stream schedule $\sigma$, common-window ledger $W$, dyadic tolerance row $\epsilon$, completion handoff $Q$, transport row $H$, continuation row $C$, package provenance $P$, and local $\NameCert$ row $N$. No such read factors through quotient streams, selected limits, host real equality, or ambient completeness outside those rows.
\end{theorem}
\begin{proof}
Begin with the finite packet. The carrier definition exposes exactly $F,\sigma,W,\epsilon,Q,H,C,P,N$ as the data available to a completion-facing consumer.

The window and schedule rows are exhausted by \autoref{thm:cauchysequence-space-regular-window-factorization}, \autoref{thm:cauchysequence-space-common-window-classifier-transport}, and \autoref{thm:cauchysequence-space-cofinal-schedule-stability}. These theorems keep the consumer on the displayed family, cofinal windows, schedule, transports, and continuations.

The tolerance and terminal rows are exhausted by \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness}, \autoref{thm:cauchysequence-space-completion-handoff-stability}, and \autoref{thm:cauchysequence-space-limit-seal-factorization}. Together they force the read through $\epsilon$ and $Q$ before any $\RealUp$ seal is consumed.

Since no carrier row stores a quotient stream, selected limit, host real equality, or ambient completeness proof, the displayed finite rows are the whole consumer surface.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_regular\_family\_exhaustion}

\begin{theorem}[CauchySequenceSpace diagonal-rate compatibility]
\label{thm:cauchysequence-space-diagonal-rate-compatibility}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Any $\RealDiagonalCompletionUp$ consumer read whose diagonal selector uses the same scheduled $\StreamNameUp$ windows, and any $\CauchyRateUp$ consumer read whose effective route uses the same cofinal ledger, factor through the same finite rows $F,\sigma,W,\epsilon,Q,H,C,P,N$ before reaching the $\RealUp$ seal.

Thus diagonal finite completeness and effective-rate certification consume the displayed Cauchy-window packet itself. They do not introduce quotient streams, selected limits, host real equality, or ambient completeness data parallel to the accepted $\CauchySequenceSpaceUp$ carrier.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_diagonal\_rate\_compatibility}
\begin{proof}
Project the accepted carrier through \autoref{def:cauchysequence-space-carrier-surface}. The visible coordinates are exactly the displayed family $F$, schedule $\sigma$, cofinal-window ledger $W$, tolerance row $\epsilon$, completion handoff $Q$, transport row $H$, continuation row $C$, package row $P$, and local naming row $N$.

First route the diagonal selector. Apply \autoref{thm:cauchysequence-space-regular-window-factorization}, \autoref{thm:cauchysequence-space-common-window-classifier-transport}, and \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness} to keep every selected diagonal window on the same $\sigma,W,\epsilon$ rows. Then use \autoref{thm:real-diagonal-completion-public-finite-completeness-interface} to read the finite diagonal completion interface through those scheduled windows.

Next route the effective-rate consumer. The same common-window classifier and tolerance ledger exactness bind the cofinal ledger and dyadic tolerance row before any rate read can reach completion-facing data. The exported certificate of \autoref{thm:cauchy-rate-public-certificate} consumes only that effective route through the displayed regular-family, cofinal-ledger, tolerance, transport, continuation, package, and naming rows.

Finally apply \autoref{thm:cauchysequence-space-limit-seal-factorization}. It identifies the terminal $\RealUp$ seal route through the same packet coordinates. Since the carrier contains no quotient stream, selected limit, host real equality, or ambient completeness coordinate, neither the diagonal completion consumer nor the effective-rate consumer has a hidden route beyond $F,\sigma,W,\epsilon,Q,H,C,P,N$.
\end{proof}

\begin{theorem}[CauchySequenceSpace obligation-closure package]
\label{thm:cauchysequence-space-obligation-closure-package}
The common-window classifier transport, cofinal schedule stability, dyadic tolerance exactness, completion handoff stability, and diagonal-rate compatibility rows form the obligation-closed $\CauchySequenceSpaceUp$ packet over the finite carrier surface of \autoref{def:cauchysequence-space-carrier-surface}. The closed obligation surface is exactly the displayed $\RegSeqRatUp$ family, $\StreamNameUp$ schedule, $\CauchyFilterUp$ or $\CauchyModulusUp$ cofinal-window ledger, $\DyadicRatCoreUp$ tolerance ledger, $\RealCauchyCompletionUp$ handoff row, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceUp\_StdBridge}
\leanvariant{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_obligation\_closure\_package}
\begin{proof}
The carrier surface and NameCert obligation surface are supplied by \autoref{def:cauchysequence-space-carrier-surface} and \autoref{thm:cauchysequence-space-namecert-obligation-surface}. They list the finite family, schedule, cofinal-window ledger, tolerance ledger, completion handoff, transport, continuation, package, and local certificate rows.

Common-window classifier transport is \autoref{thm:cauchysequence-space-common-window-classifier-transport}. Cofinal schedule stability is \autoref{thm:cauchysequence-space-cofinal-schedule-stability}, and dyadic tolerance ledger exactness is \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness}. These rows keep every accepted comparison on the same finite Cauchy-window packet.

Completion handoff stability is \autoref{thm:cauchysequence-space-completion-handoff-stability}. Diagonal-rate compatibility is \autoref{thm:cauchysequence-space-diagonal-rate-compatibility}. Together they show that completion, diagonal, and effective-rate consumers all remain inside the same displayed packet, so the paper-side obligation surface is closed at the stated grade.
\end{proof}

\begin{theorem}[CauchySequenceSpace kernel scope packet]
\label{thm:cauchysequence-space-kernel-scope-packet}
The carrier surface, NameCert obligation surface, common-window classifier transport, cofinal schedule stability, dyadic tolerance exactness, completion handoff stability, regular family exhaustion, and diagonal-rate compatibility assemble into a single kernel-scoped $\CauchySequenceSpaceUp$ packet over $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Every completion-facing, diagonal-completion, effective-rate, or real-seal consumer must read through the displayed regular-family rows, stream schedule, common-window ledger, dyadic tolerance row, completion handoff, componentwise transports, continuation routes, package provenance, and local naming row. The packet excludes quotient completion, selected representatives, host real equality, and ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_kernel\_scope\_packet}
\begin{proof}
Begin with \autoref{def:cauchysequence-space-carrier-surface} and \autoref{thm:cauchysequence-space-namecert-obligation-surface}. They list the displayed family, schedule, cofinal-window ledger, tolerance ledger, completion handoff, transport, continuation, package, and local certificate rows, and they bind the classifier and stability obligations to those rows.

Next apply \autoref{thm:cauchysequence-space-common-window-classifier-transport}, \autoref{thm:cauchysequence-space-cofinal-schedule-stability}, and \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness}. These rows keep every accepted comparison on the same scheduled finite windows and the same displayed dyadic tolerance ledger.

Then use \autoref{thm:cauchysequence-space-completion-handoff-stability} and \autoref{thm:cauchysequence-space-regular-family-exhaustion}. The terminal completion-facing route and every regular-family consumer are exhausted by the same finite packet coordinates.

Finally apply \autoref{thm:cauchysequence-space-diagonal-rate-compatibility} and \autoref{thm:cauchysequence-space-obligation-closure-package}. Diagonal finite-completion and effective-rate readers consume the same kernel-scoped surface, so quotient completion, selected representatives, host real equality, and ambient completeness have no row through which to enter.
\end{proof}

\begin{theorem}[CauchySequenceSpace UniformCauchyCriterion consumption]
\label{thm:cauchysequence-space-uniformcriterion-consumption}
Let $S=(F,\sigma,W,\epsilon,Q,H,C,P,N)$ be an accepted $\CauchySequenceSpaceUp$ packet. Suppose its common-window ledger $W$ is presented by an accepted $\UniformCauchyCriterionUp$ packet whose shared threshold and real-seal handoff read the same regular family, stream schedule, Cauchy-modulus row, dyadic tolerance row, and completion handoff. Then every completion-facing read of $S$ factors through the same $\RegSeqRatUp$ family $F$, $\StreamNameUp$ schedule $\sigma$, $\CauchyModulusUp$ row, $\DyadicRatCoreUp$ tolerance $\epsilon$, and $\RealCauchyCompletionUp$ handoff $Q$.

The consumer route has no row for quotient streams, selected limits, host equality, or ambient completeness. The $\UniformCauchyCriterionUp$ presentation supplies only the shared-threshold ledger and real-seal handoff already consumed by the displayed $\CauchySequenceSpaceUp$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_uniformcriterion\_consumption}
\begin{proof}
Project the accepted $\CauchySequenceSpaceUp$ carrier by \autoref{def:cauchysequence-space-carrier-surface}. The only completion-facing coordinates are the regular family $F$, schedule $\sigma$, common-window ledger $W$, dyadic tolerance row $\epsilon$, handoff $Q$, transports, continuations, provenance, and local naming row.

Use \autoref{thm:cauchysequence-space-common-window-classifier-transport}, \autoref{thm:cauchysequence-space-cofinal-schedule-stability}, and \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness}. These rows keep the common-window classifier, schedule, cofinal Cauchy-modulus evidence, and dyadic tolerance on the displayed packet before completion-facing data can be read.

Now read the accepted $\UniformCauchyCriterionUp$ presentation through \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport} and \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The shared threshold and real-seal handoff are consumer routes over the same finite family, schedule, modulus, tolerance, and seal rows; they do not introduce an independent completion object.

Finally apply \autoref{thm:cauchysequence-space-completion-handoff-stability} and \autoref{thm:cauchysequence-space-kernel-scope-packet}. The completion handoff stays on $F,\sigma,W,\epsilon,Q,H,C,P,N$, so the uniform-criterion ledger is consumed as a presentation of the same route rather than as quotient completion, a selected limit, host equality, or ambient completeness.
\end{proof}

\begin{theorem}[CauchySequenceSpace RealObservationBudget factorization]
\label{thm:cauchysequence-space-real-observation-budget-factorization}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Suppose a $\RealObservationBudgetUp$ presentation records the same precision request, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ readbacks and radii, $\RegSeqRatUp$ handoff rows, and $\RealUp$ seal rows as the completion-facing request for $S$. Then that observation-budget presentation factors through the displayed CauchySequenceSpace rows before any completion-facing read of $Q$.

The factorized route uses only the regular-family row $F$, schedule $\sigma$, common-window ledger $W$, dyadic tolerance row $\epsilon$, completion handoff $Q$, componentwise transports $H$, continuation routes $C$, provenance row $P$, and local naming row $N$. It cannot use quotient streams, host equality, hidden limit selection, unbounded schedules, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_real\_observation\_budget\_factorization}
\begin{proof}
Project the accepted carrier through \autoref{def:cauchysequence-space-carrier-surface}. The visible packet rows are exactly the regular rational family, stream schedule, common-window ledger, dyadic tolerance row, completion handoff, transports, continuations, provenance, and local name.

First bind the observation windows to the same CauchySequenceSpace route. Common-window classifier transport, cofinal schedule stability, and dyadic tolerance ledger exactness identify the precision-indexed windows, stream reads, dyadic readbacks, and displayed radii with $W$, $\sigma$, and $\epsilon$.

Next route the source and seal consumers. Completion handoff stability keeps the $\RegSeqRatUp$ handoff and the $\RealUp$ seal boundary on the same $Q$ row, and the kernel scope packet prevents any completion-facing read from leaving $F,\sigma,W,\epsilon,Q,H,C,P,N$.

Finally read the $\RealObservationBudgetUp$ carrier through \autoref{def:real-observation-budget-carrier}, \autoref{thm:real-observation-budget-window-coverage}, \autoref{thm:real-observation-budget-regseq-handoff}, \autoref{thm:real-observation-budget-real-seal-boundary}, and \autoref{thm:real-observation-budget-nonescape}. Those rows present the same finite observation route and exclude quotient streams, host equality, hidden limit selection, unbounded schedules, and ambient completeness.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_public\_observation\_budget\_factorization}

\begin{theorem}[CauchySequenceSpace scoped completion route inventory]
\label{thm:cauchysequence-space-scoped-completion-route-inventory}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Every completion-facing consumer read, and every $\RealUp$ limit-seal read of the completion handoff, is scoped by the displayed $\RegSeqRatUp$ family row $F$, the $\StreamNameUp$ schedule $\sigma$, the $\CauchyFilterUp$ or $\CauchyModulusUp$ window ledger $W$, the $\DyadicRatCoreUp$ tolerance row $\epsilon$, the $\RealCauchyCompletionUp$ handoff $Q$, the componentwise $\hsame$ transports $H$, the displayed $\Cont$ routes $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert_{\CauchySequenceSpaceUp}$ row $N$.

Consequently the completion-facing route inventory of $S$ is a scoped BEDC route over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It exports no quotient-name equality, selected representative, host real equality, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_scoped\_completion\_route\_inventory}
\begin{proof}
Start from the carrier surface in \autoref{def:cauchysequence-space-carrier-surface} and the NameCert obligation surface in \autoref{thm:cauchysequence-space-namecert-obligation-surface}. These two rows name the accepted tuple and bind its family, schedule, window ledger, tolerance row, completion handoff, transports, continuations, provenance, and local certificate to the same finite $\BHist$ packet.

Next isolate the completion-facing route. Apply \autoref{thm:cauchysequence-space-completion-handoff} and \autoref{thm:cauchysequence-space-regular-window-factorization}. The terminal handoff to $\RealCauchyCompletionUp$ can only be read after the displayed regular family, scheduled finite windows, Cauchy ledger, dyadic tolerance, transport, continuation, package, and naming rows have been consumed.

Now bind the RealUp seal boundary. Use \autoref{thm:cauchysequence-space-limit-seal-factorization} to route every limit-seal read through $F,\sigma,W,\epsilon,Q,H,C,P,N$, and use \autoref{thm:cauchysequence-space-regular-family-exhaustion} to show that no other regular-family consumer row remains outside the displayed packet.

The route inventory is therefore a scoped BEDC route over the primitive rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Since the carrier surface supplies no quotient-name equality, selected representative, host real equality, or ambient completeness coordinate, none of those objects is exported by the completion-facing or limit-seal route.
\end{proof}

\begin{theorem}[CauchySequenceSpace public completion export]
\label{thm:cauchysequence-space-public-completion-export}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. The public completion export of $S$ is the single BEDC surface consisting of the finite carrier rows $F,\sigma,W,\epsilon,Q,H,C,P,N$, the $\NameCert_{\CauchySequenceSpaceUp}$ obligation rows, the $\RealCauchyCompletionUp$ handoff row, common-window classifier transport, dyadic tolerance exactness, completion handoff stability, regular-family exhaustion, and the scoped route inventory of \autoref{thm:cauchysequence-space-scoped-completion-route-inventory}.

Every completion-facing consumer of $S$ must factor through that public export before reading a completion handoff or a $\RealUp$ seal. The export is public only as a BEDC route over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$; it does not assert quotient completion, equality of Cauchy-name classes, uniqueness of limits, host real equality, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_public\_completion\_export}
\begin{proof}
Start with \autoref{def:cauchysequence-space-carrier-surface} and \autoref{thm:cauchysequence-space-namecert-obligation-surface}. These identify the visible tuple $F,\sigma,W,\epsilon,Q,H,C,P,N$ and bind its local naming, transport, continuation, and package rows to the same finite packet.

Next add the completion-facing rows. Apply \autoref{thm:cauchysequence-space-completion-handoff}, \autoref{thm:cauchysequence-space-common-window-classifier-transport}, and \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness} to keep the handoff, classifier, windows, and dyadic tolerance on the displayed coordinates.

Then use \autoref{thm:cauchysequence-space-completion-handoff-stability} and \autoref{thm:cauchysequence-space-regular-family-exhaustion}. They show that completion reads and regular-family consumers remain inside the same finite route.

Finally package those rows by \autoref{thm:cauchysequence-space-scoped-completion-route-inventory}. The cited inventory is already a BEDC route over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, so the public export has exactly the stated surface and no stronger completion object.
\end{proof}

\begin{theorem}[CauchySequenceSpace RealObservationBudget public consumer]
\label{thm:cauchysequence-space-public-real-observation-consumer}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Suppose a $\RealObservationBudgetUp$ presentation uses the same finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ readbacks and radii, $\RegSeqRatUp$ handoff rows, and $\RealUp$ seal factors as the completion-facing request for $S$. Then that observation presentation factors through the public completion export of \autoref{thm:cauchysequence-space-public-completion-export}.

In particular, the observation consumer reads $F,\sigma,W,\epsilon,Q,H,C,P,N$ and the local $\NameCert_{\CauchySequenceSpaceUp}$ rows before it can present a real observation. It cannot bypass the public export by selecting a quotient name, a representative limit, a host real equality proof, an ambient completeness principle, or an unbounded schedule.
\end{theorem}
\begin{proof}
First project the $\RealObservationBudgetUp$ presentation through \autoref{def:real-observation-budget-carrier}. The relevant observation rows are the finite request, window, dyadic readback, handoff, seal, transport, and naming data.

Use \autoref{thm:real-observation-budget-window-coverage}, \autoref{thm:real-observation-budget-regseq-handoff}, and \autoref{thm:real-observation-budget-real-seal-boundary} to align those rows with the same finite windows, regular-rational handoffs, dyadic readbacks, and $\RealUp$ seal factors named by $S$.

Now apply \autoref{thm:cauchysequence-space-real-observation-budget-factorization}. It already routes such an observation-budget presentation through $F,\sigma,W,\epsilon,Q,H,C,P,N$ before the completion handoff is read.

Finally compose with \autoref{thm:cauchysequence-space-public-completion-export} and \autoref{thm:real-observation-budget-nonescape}. The first theorem supplies the public export for the routed packet, and the second excludes quotient names, selected representatives, host equality, ambient completeness, and unbounded schedules from the observation route.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_public\_real\_observation\_consumer}

\begin{theorem}[CauchySequenceSpace public nonescape]
\label{thm:cauchysequence-space-public-nonescape}
For every accepted $\CauchySequenceSpaceUp$ packet $S=(F,\sigma,W,\epsilon,Q,H,C,P,N)$, the public completion export of \autoref{thm:cauchysequence-space-public-completion-export} exposes no quotient-name equality, no selected representative, no host real equality, no ambient completeness principle, and no hidden limit selector. Its observable routes are exhausted by the displayed finite carrier, obligation, completion handoff, classifier transport, tolerance, stability, family-exhaustion, and scoped-inventory rows.
\end{theorem}
\begin{proof}
The public export is defined by \autoref{thm:cauchysequence-space-public-completion-export} as a package of previously displayed BEDC rows. Each row is a carrier, naming, transport, continuation, package, tolerance, handoff, stability, exhaustion, or scoped-route row over the tuple $F,\sigma,W,\epsilon,Q,H,C,P,N$.

Apply \autoref{thm:cauchysequence-space-kernel-scope-packet} and \autoref{thm:cauchysequence-space-scoped-completion-route-inventory}. These two results state that completion-facing and limit-seal consumers are scoped by the displayed BEDC packet and that quotient completion, selected representatives, host real equality, and ambient completeness have no exported coordinate.

It remains to exclude a hidden limit selector. The only limit-seal route available to the export is the factorization of \autoref{thm:cauchysequence-space-limit-seal-factorization}, which routes through $F,\sigma,W,\epsilon,Q,H,C,P,N$. Since that route is already included in the scoped inventory and supplies no selector coordinate, the public export cannot expose one.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_public\_nonescape}

\begin{theorem}[CauchySequenceSpace tail-window factorization]
\label{thm:cauchysequence-space-tail-window-factorization}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Every tail-window completion-facing read of $S$ factors through the displayed $\RegSeqRatUp$ family $F$, the $\StreamNameUp$ schedule $\sigma$, the cofinal Cauchy-window ledger $W$, the $\DyadicRatCoreUp$ tolerance row $\epsilon$, the completion handoff $Q$, the transport row $H$, the continuation row $C$, the package row $P$, and the local $\NameCert_{\CauchySequenceSpaceUp}$ row $N$. The route reaches completion and any $\RealUp$ seal only through those finite BEDC rows, not through quotient-name equality, selected representatives, host real equality, ambient completeness, or a hidden limit selector.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_tail\_window\_factorization}
\begin{proof}
Begin with the public completion surface. The public completion export theorem \autoref{thm:cauchysequence-space-public-completion-export} packages the visible tuple $F,\sigma,W,\epsilon,Q,H,C,P,N$ together with the completion handoff and scoped route inventory, while public nonescape \autoref{thm:cauchysequence-space-public-nonescape} excludes quotient, representative, host equality, completeness, and selector coordinates.

Next isolate the finite tail window. Regular-window factorization \autoref{thm:cauchysequence-space-regular-window-factorization} routes the completion-facing read through the displayed regular family, schedule, cofinal ledger, tolerance row, transport, continuation, package, and naming rows. Cofinal schedule stability \autoref{thm:cauchysequence-space-cofinal-schedule-stability} keeps every cofinal request attached to the same schedule and ledger.

Finally read the tolerance and terminal handoff. Dyadic tolerance ledger exactness \autoref{thm:cauchysequence-space-dyadic-tolerance-ledger-exactness} fixes the tolerance row before the completion handoff is consumed, and the public export supplies the handoff, transport, continuation, package, and NameCert rows. Thus every tail-window completion-facing read factors through the displayed finite route.
\end{proof}

\begin{theorem}[CauchySequenceSpace quotient refusal route]
\label{thm:cauchysequence-space-quotient-refusal-route}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Any accepted consumer that asks for quotient-name equality, a selected representative, host real equality, or ambient completeness must route through \autoref{ch:concrete-instances-quotientstreamrefusal-namecert} after it has read the displayed $\RegSeqRatUp$ family $F$, the $\StreamNameUp$ schedule $\sigma$, the cofinal-window ledger $W$, the $\DyadicRatCoreUp$ tolerance row $\epsilon$, and the $\RealCauchyCompletionUp$ handoff $Q$.

Thus the quotient-facing request is not a projection from $\CauchySequenceSpaceUp$ itself. It is a refusal route over the same finite Cauchy-window packet, with no additional quotient stream, selected limit, host equality, or completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_quotient\_refusal\_route}
\begin{proof}
First read the completion handoff of \autoref{thm:cauchysequence-space-completion-handoff}. It forces every completion-facing consumer to pass through the displayed family, schedule, window, tolerance, transport, continuation, package, and local naming rows before the handoff row $Q$ is consumed.

Next use public non-escape and the tail-window factorization. By \autoref{thm:cauchysequence-space-public-nonescape} and \autoref{thm:cauchysequence-space-tail-window-factorization}, quotient-name equality, selected representatives, host real equality, ambient completeness, and hidden limit selectors are absent from the $\CauchySequenceSpaceUp$ carrier and from its public completion export.

Finally apply the $\QuotientStreamRefusalUp$ route of \autoref{thm:quotient-stream-refusal-nonescape-route}. That sibling chapter is exactly the Real-completion refusal packet for requests that leave the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ route. Therefore a quotient-facing consumer may proceed only as a refusal-route consumer after the CauchySequenceSpace rows have been read.
\end{proof}

\begin{theorem}[CauchySequenceSpace RealLimitUniquenessSeal public consumer]
\label{thm:cauchysequence-space-real-limit-uniqueness-seal-public-consumer}
Let
$$
S_0=(F_0,\sigma_0,W_0,\epsilon_0,Q_0,H_0,C_0,P_0,N_0)
$$
and
$$
S_1=(F_1,\sigma_1,W_1,\epsilon_1,Q_1,H_1,C_1,P_1,N_1)
$$
be accepted $\CauchySequenceSpaceUp$ packets. Suppose their public completion exports supply two $\RealCauchyCompletionUp$ handoff rows and that the comparison route displays the same $\RegSeqRatUp$ family row, the same finite $\StreamNameUp$ window row, the same $\DyadicRatCoreUp$ tolerance row, and the same terminal $\RealUp$ classifier row for both exported seals. Then any $\RealLimitUniquenessSealUp$ consumer comparing those two exported seals factors through exactly the two public completion exports, the shared comparison-window-tolerance route, and the two local $\NameCert_{\CauchySequenceSpaceUp}$ rows.

The consumer cannot read a selected limit, quotient stream equality, host real equality, detached selector choice, or ambient completeness theorem from the two $\CauchySequenceSpaceUp$ packets. Its only uniqueness-facing surface is the finite two-seal packet routed through $\RealLimitUniquenessSealUp$.
\end{theorem}
\begin{proof}
First expose the two public completion endpoints. Apply \autoref{thm:cauchysequence-space-public-completion-export} separately to $S_0$ and $S_1$. The two applications provide the two $\RealCauchyCompletionUp$ handoff rows together with their displayed family, stream-window, dyadic tolerance, transport, continuation, package, and local NameCert rows.

Next restrict the comparison route to the shared finite data. Use \autoref{thm:cauchysequence-space-public-nonescape} to remove quotient-name equality, selected representatives, host equality, ambient completeness, and hidden limit selectors from both public exports. Then apply \autoref{thm:cauchysequence-space-tail-window-factorization} to keep each endpoint on the displayed $\RegSeqRatUp$ family, finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance row, and terminal handoff route.

Finally read the uniqueness consumer through the sibling comparison packet. The obligation surface of \autoref{thm:real-limit-uniqueness-seal-obligation-surface} supplies exactly the two seal rows, shared regular-rational comparison row, finite window row, dyadic ledger, terminal $\RealUp$ classifier row, uniqueness handoff, transport, continuation, provenance, and local name. The nonescape theorem \autoref{thm:real-limit-uniqueness-seal-nonescape} prevents any replacement by a selected limit, quotient stream equality, host Real equality, detached selector, or ambient completeness theorem. Hence the consumer factors only through the two public exports, the shared comparison-window-tolerance route, and the local NameCert rows.
\end{proof}

\begin{theorem}[CauchySequenceSpace finite-section pullback correspondence]
\label{thm:cauchysequence-space-finite-section-pullback-correspondence}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet. Suppose that the public completion export of $S$ is read through an accepted finite request section of $\StreamNameUp$, and that a $\RealUp$ seal consumer reads the same finite windows, dyadic tolerance rows, regular-rational handoff rows, terminal seal row, displayed $\BHist$ entry, componentwise $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\CauchySequenceSpaceUp}$ row. Then the exported completion handoff and the $\RealUp$ seal consumer are exactly the same four-face route named by the StreamName finite-section pullback exactness theorem:
$$
\StreamNameUp,\qquad
\DyadicRatCoreUp,\qquad
\RegSeqRatUp,\qquad
\RealUp .
$$

Equivalently, every such CauchySequenceSpace completion read pulls back to the StreamName finite section with the displayed window face, dyadic face, regular-rational face, and Real seal face, and then returns to the same public completion export. The correspondence exports no quotient stream, no selected representative, no host real equality, no countable-choice row, no ambient completeness principle, and no route-level aggregate closure or verification status.
\end{theorem}
\begin{proof}
First expose the public completion side. Apply \autoref{thm:cauchysequence-space-public-completion-export} to $S$ to obtain the displayed tuple $F,\sigma,W,\epsilon,Q,H,C,P,N$, the $\RealCauchyCompletionUp$ handoff row, and the local $\NameCert_{\CauchySequenceSpaceUp}$ obligation rows.

Next restrict the read to finite StreamName data. Use \autoref{thm:cauchysequence-space-tail-window-factorization} to present the family, schedule, tolerance, and handoff rows as the same finite $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RealUp$ route that the accepted request section consumes.

Now invoke the StreamName pullback surface. Theorem~\ref{thm:streamname-finite-section-pullback-exactness} identifies the four visible faces of the request section, and \autoref{thm:streamname-finite-section-real-regseq-dyadic-lock} keeps the Real seal, regular-rational handoff, dyadic tolerance row, and finite StreamName window locked to the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and NameCert data.

Finally apply \autoref{thm:cauchysequence-space-public-nonescape} and \autoref{thm:real-l10-objectwise-exit-threshold-equivalence}. The first result excludes quotient streams, selected representatives, host real equality, countable-choice routes, and ambient completeness from the CauchySequenceSpace export. The second keeps the closure and verification coordinates objectwise on the four faces rather than converting them into a route-level aggregate status.
\end{proof}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_finite\_section\_pullback\_correspondence}

\begin{theorem}[CauchySequenceSpace exact-boundary terminal pullback]
\label{thm:cauchysequence-space-real-completion-exact-boundary-terminal-pullback}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet, and let
$$
B=(L_B,K_B,J_B,S_B,W_B,R_B,D_B,E_B,H_B,C_B,P_B,N_B)
$$
be an accepted $\RealCompletionExactBoundaryUp$ packet. Suppose the public completion export of $S$ and the terminal consumer route of $B$ are displayed over the same finite $\StreamNameUp$ window, the same $\RegSeqRatUp$ readback row, the same $\DyadicRatCoreUp$ tolerance row, the same terminal $\RealUp$ seal, the same $\BHist$ entry, the same componentwise $\hsame$ transports, the same $\Cont$ routes, the same $\Pkg$ provenance, and the same local NameCert rows. Then the CauchySequenceSpace public completion read and the RealCompletionExactBoundary terminal consumer are one four-face terminal pullback route:
$$
\StreamNameUp,\qquad
\RegSeqRatUp,\qquad
\DyadicRatCoreUp,\qquad
\RealUp .
$$

This identification reads the finite Cauchy-name export through the exact-boundary terminal consumer and returns to the same public completion surface. It exports no quotient stream, no selected representative, no host real equality, no countable-choice row, no ambient completeness row, no metric-completeness row, and no bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_real\_completion\_exact\_boundary\_terminal\_pullback}
\begin{proof}
First expose the CauchySequenceSpace public completion surface. Apply \autoref{thm:cauchysequence-space-public-completion-export} to $S$ to obtain the displayed family, schedule, cofinal-window, dyadic tolerance, completion handoff, transport, continuation, provenance, and local naming rows. Then apply \autoref{thm:cauchysequence-space-finite-section-pullback-correspondence} to identify that public read with the finite $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ route over the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and NameCert data.

Next read the RealCompletionExactBoundary side. Theorem~\ref{thm:real-completion-exact-boundary-four-face-exactness} says that the accepted boundary exports exactly the four terminal faces $W_B,R_B,D_B,E_B$ after the governing rows $L_B,K_B,J_B,S_B$. Theorem~\ref{thm:real-completion-exact-boundary-terminal-consumer-exactness} places every completion-facing and terminal $\RealUp$ consumer on the same finite route through $L_B,K_B,J_B,S_B,W_B,R_B,D_B,E_B,H_B,C_B,P_B,N_B$.

Finally compare the two exclusions. The CauchySequenceSpace public nonescape theorem \autoref{thm:cauchysequence-space-public-nonescape} removes quotient streams, selected representatives, host real equality, countable-choice routes, and ambient completeness from the public export. The exact-boundary no-completeness theorem \autoref{thm:real-completion-exact-boundary-no-completeness-escape} removes quotient streams, host equality, selected limits, metric-completeness rows, bridge rows, and ambient-completeness coordinates from the terminal consumer. Since the hypotheses identify the displayed window, readback, tolerance, Real seal, history, transport, continuation, package, and local NameCert rows, no additional coordinate remains on either side; both consumers are the same four-face terminal pullback route.
\end{proof}

\begin{theorem}[CauchySequenceSpace terminal pullback exactness]
\label{thm:cauchysequence-space-terminal-pullback-exactness}
Let
$$
S=(F,\sigma,W,\epsilon,Q,H,C,P,N)
$$
be an accepted $\CauchySequenceSpaceUp$ packet, and let an accepted L10 Phase Real and Completion read of $S$ display a finite $\StreamNameUp$ section, a $\DyadicRatCoreUp$ tolerance row, a $\RegSeqRatUp$ readback row, a terminal $\RealUp$ seal, a $\BHist$ entry, componentwise $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert_{\CauchySequenceSpaceUp}$ row. This read is the L10 terminal exit route completely determined by the Phase Real and Completion terminal data if and only if the following two projections hold over those same rows:
\begin{enumerate}
\item its $\StreamNameUp$ finite-section projection satisfies the pullback exactness criterion of \autoref{thm:streamname-finite-section-pullback-exactness};
\item its $\RealCompletionExactBoundaryUp$ projection satisfies the terminal pullback of \autoref{thm:cauchysequence-space-real-completion-exact-boundary-terminal-pullback}.
\end{enumerate}

Thus the terminal exit route has no coordinate beyond the shared $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. In particular it exports no quotient stream, no selected representative, no host real equality, no countable-choice row, no ambient completeness row, no metric-completeness row, no bridge row, and no route-level aggregate closure or verification status.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_terminal\_pullback\_exactness}
\begin{proof}
For the forward direction, assume the accepted read is already the L10 terminal exit route determined by the Phase Real and Completion terminal data. Apply \autoref{thm:cauchysequence-space-finite-section-pullback-correspondence} to expose the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ four-face route carried by the public completion export. Then use \autoref{thm:streamname-finite-section-pullback-exactness} to identify the finite-section projection over the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and NameCert rows.

The same terminal read also supplies the exact-boundary endpoint. Apply \autoref{thm:cauchysequence-space-real-completion-exact-boundary-terminal-pullback} to read the $\RealCompletionExactBoundaryUp$ projection through the same finite window, readback row, tolerance row, terminal Real seal, history, transport, continuation, package, and local NameCert data.

For the reverse direction, suppose the two displayed projections satisfy those exactness criteria over the same rows. The finite-section correspondence first pins the CauchySequenceSpace public completion read to the StreamName four-face route, while the StreamName theorem makes that route terminal among finite request sections. The exact-boundary terminal pullback then identifies the RealCompletionExactBoundary consumer with the same four faces and support rows.

Finally apply \autoref{thm:real-l10-objectwise-exit-threshold-equivalence}. Since the StreamName projection and the exact-boundary projection share the same objectwise $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, the L10 exit is determined by those two projections. The nonescape clauses in the cited CauchySequenceSpace, StreamName, and exact-boundary theorems exclude quotient streams, selected representatives, host real equality, countable choice, ambient completeness, metric-completeness rows, bridge rows, and any route-level aggregate closure or verification status.
\end{proof}

\closureat{CauchySequenceSpaceUp}{seedStr}
\closureat{CauchySequenceSpaceUp}{obligationStr}
\closureat{CauchySequenceSpaceUp}{scopedStr}
\closureat{CauchySequenceSpaceUp}{publicStr}
\closureat{CauchySequenceSpaceUp}{bridgedStr}
\closureat{CauchySequenceSpaceUp}{matureStr}

\begin{closurestatus}{\CauchySequenceSpaceUp}
  \constructivestory{A $\CauchySequenceSpaceUp$ packet is generated from a displayed family of regular rational names, a stream schedule, finite Cauchy-window evidence, dyadic tolerance data, a completion handoff, componentwise transport, displayed continuation routes, package provenance, and local naming.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:cauchysequence-space-public-completion-export}, \autoref{thm:cauchysequence-space-public-nonescape}, and \autoref{thm:cauchysequence-space-tail-window-factorization} supply the mature paper surface: a public finite Cauchy-name route with the sibling $\RegSeqRatUp$ family, $\StreamNameUp$ schedule, and $\RealCauchyCompletionUp$ handoff displayed in the chapter.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.CauchySequenceSpaceUp.CauchySequenceSpaceCarrier\_public\_completion\_export}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close quotient completion construction, equality of Cauchy-name classes, uniqueness of limits, host real equality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Bridge checking requires a standard bridge from the mature public completion export to the choice-free completion consumer reading.}
\end{closurestatus}
