\chapter{A Concrete Naming Certificate for $\FanFunctionalUp$}
\label{ch:concrete-instances-fanfunctional-namecert}
\origin{human}

Following Brouwer, Troelstra--van Dalen, and Bishop constructive analysis, the
$\FanFunctionalUp$ packet records the finite modulus-extraction surface that a
continuous functional on Cantor space may expose after a finite fan argument.
It consumes the finite-prefix carrier of
\autoref{ch:concrete-instances-cantorspace-namecert}, the decidable finite-bar
and depth rows of \autoref{ch:concrete-instances-fantheorem-namecert}, the
tolerance-to-precision ledger of
\autoref{ch:concrete-instances-uniformcontinuity-namecert}, and the compact
metric finite-net surface of
\autoref{ch:concrete-instances-compactmetric-namecert}. The packet exports an
explicit $\UniformModulusUp$ row for Cantor-prefix consumers; it does not
export a host functional, a choice-selected branch, open-cover compactness, or
real completeness.

\begin{definition}[FanFunctional carrier surface]
\label{def:fan-functional-carrier-surface}
A $\FanFunctionalUp$ carrier is a finite $\BHist$ packet
$$
\Phi=(C,F,\varepsilon,B,D,W,M,H,K,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $C$ is the $\CantorSpaceUp$ finite-prefix row, including the
StreamName schedule, Boolean observation ledger, and List prefix spine;
\item $F$ is the $\FanTheoremUp$ finite fan row, including the decidable bar
classifier and the unary depth ledger for the displayed binary spread;
\item $\varepsilon$ is the positive tolerance request read by the downstream
metric or real-valued consumer;
\item $B$ is the finite branch-prefix window obtained by restricting the
Cantor prefix rows of $C$ to the depth ledger of $F$;
\item $D$ is the finite bar-depth evidence saying that every retained branch
prefix in $B$ reaches a barred prefix by the displayed unary depth;
\item $W$ is the finite witness window pairing each retained prefix with the
pointwise tolerance row requested at that prefix;
\item $M$ is the extracted $\UniformModulusUp$ row, read as a unary prefix
length sufficient for all Cantor histories sharing the retained prefix;
\item $H$ records componentwise $\hsame$ transport for the Cantor rows, fan
rows, tolerance request, witness window, depth evidence, and extracted modulus;
\item $K$ records the displayed $\Cont$ replay route from Cantor-prefix reads
through the finite fan rows into the modulus row;
\item $P$ is the $\Pkg$ provenance over $\CantorSpaceUp$, $\FanTheoremUp$,
$\UniformContinuityUp$, $\CompactMetricUp$, $\UniformModulusUp$, $\BHist$,
$\hsame$, $\Cont$, and the local naming row;
\item $N$ is the local $\NameCert_{\FanFunctionalUp}$ row.
\end{enumerate}
The carrier has no coordinate for an infinite branch, a host functional
$2^{\NatUp}\to\RealUp$, an open cover, a selected bar proof, or a hidden
compactness principle.
\end{definition}

\begin{theorem}[FanFunctional NameCert obligations]
\label{thm:fan-functional-namecert-obligations}
The local $\NameCert_{\FanFunctionalUp}$ surface of
\autoref{def:fan-functional-carrier-surface} consists of six finite
obligations: carrier admission for the displayed packet
$\Phi=(C,F,\varepsilon,B,D,W,M,H,K,P,N)$; classifier stability for the
Cantor-prefix and finite-fan rows under componentwise $\hsame$ transport;
bar-depth exactness for the unary ledger $D$; witness-window coverage for all
retained branch prefixes in $B$; uniform-modulus extraction of the row $M$; and
non-escape, requiring every public read to factor through $H,K,P,N$ and no
host functional or choice principle.
\end{theorem}
\begin{proof}
Carrier admission is projection of the displayed coordinates of
\autoref{def:fan-functional-carrier-surface}. The Cantor row, fan row,
tolerance request, branch-prefix window, depth evidence, witness window, and
modulus row are all finite $\BHist$ data.

Classifier stability is componentwise. The Cantor rows are compared by the
finite-prefix classifier of
\autoref{ch:concrete-instances-cantorspace-namecert}, while the fan rows are
compared by the finite bar classifier of
\autoref{ch:concrete-instances-fantheorem-namecert}. Transport by $H$ keeps
the tolerance, witness window, depth evidence, and extracted modulus attached
to the same displayed packet.

Bar-depth exactness reads the unary depth ledger of the $\FanTheoremUp$ row.
For each retained prefix in $B$, the witness $D$ records that the displayed
decidable bar has already been met within the finite depth; no infinite branch
or bar-induction rule is introduced.

The witness-window and modulus clauses are obtained by replaying $K$. Each
retained prefix carries the local tolerance row in $W$, and the finite fan
depth bounds the largest prefix length that a downstream consumer must inspect.
Repacking this bounded inspection length as $M$ gives the
$\UniformModulusUp$ row.

Non-escape follows from coordinate exhaustion. The carrier contains only
$C,F,\varepsilon,B,D,W,M,H,K,P,N$, so a public read cannot produce a host
functional, a choice-selected branch, open-cover compactness, or real
completeness.
\end{proof}

\begin{theorem}[FanFunctional uniform modulus extraction]
\label{thm:fan-functional-uniform-modulus-extraction}
Let $\Phi$ be an accepted $\FanFunctionalUp$ carrier. The finite fan depth row
of $F$, the Cantor prefix window $B$, and the tolerance witness rows $W$
determine the extracted $\UniformModulusUp$ row $M$. For any two accepted
$\CantorSpaceUp$ histories whose Boolean ledgers agree through the prefix
length named by $M$, every consumer-visible value of the functional is routed
through the same barred prefix window and hence through the same tolerance
row. The extraction uses finite prefix inspection only.
\end{theorem}
\begin{proof}
Project the accepted carrier and read its $\FanTheoremUp$ row. The finite bar
handoff supplies a unary depth ledger and a finite branch-prefix window, so the
inspection bound is visible before any downstream modulus row is formed.

Restrict the $\CantorSpaceUp$ carrier to that window. Agreement of two Cantor
histories through the prefix length named by $M$ gives componentwise agreement
of their Boolean ledgers on every prefix in $B$.

Replay the witness rows $W$ through $K$. Each retained prefix already carries
the local tolerance request, and the bar-depth evidence $D$ says that no longer
branch read is required. The same prefix window therefore supports the same
consumer tolerance row for both histories.

Package the resulting bounded prefix length as the $\UniformModulusUp$ row
$M$. Since the construction reads only the finite Cantor rows, finite fan
depth, witness window, transports, continuation, provenance, and local
certificate, it introduces no host functional and no choice-selected branch.
\end{proof}

\begin{theorem}[FanFunctional compact-continuity consumer]
\label{thm:fan-functional-compact-continuity-consumer}
A compact-continuity consumer citing an accepted $\FanFunctionalUp$ packet may
read exactly the Cantor-prefix rows of $C$, the finite-bar and depth rows of
$F$, the tolerance request $\varepsilon$, the witness window $W$, the extracted
$\UniformModulusUp$ row $M$, and the support rows $H,K,P,N$. This is the
Cantor-space instance of the compact-metric and uniform-continuity consumer
surface: compactness is consumed only through finite prefix coverage and
finite bar depth, while continuity is consumed only through the displayed
tolerance-to-modulus ledger.
\end{theorem}
\begin{proof}
Start with the compact-metric dependency. In the Cantor-space case, the
compact carrier is presented by finite Boolean prefix coverage, so the consumer
can read compactness only as the prefix rows already present in $C$ and $B$.

Use the $\FanTheoremUp$ dependency to bound the prefix inspection. Its
decidable bar and unary depth rows supply the finite branch-depth evidence $D$,
and the witness window $W$ records the tolerance rows attached to those
prefixes.

Use the $\UniformContinuityUp$ dependency only at the modulus handoff. The row
$M$ is the explicit $\UniformModulusUp$ output supplied by the finite fan
inspection, and the continuation route $K$ is the only path by which a consumer
may read it.

Thus the compact-continuity consumer receives exactly the displayed finite
surface. Host compactness, open covers, selected branches, semantic continuity,
and real completeness are absent from the carrier and cannot be exported.
\end{proof}

\begin{closurestatus}{\FanFunctionalUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:fan-functional-carrier-surface}, \autoref{thm:fan-functional-namecert-obligations}, \autoref{thm:fan-functional-uniform-modulus-extraction}, and \autoref{thm:fan-functional-compact-continuity-consumer} seed the finite Cantor-prefix fan-functional packet for constructive modulus extraction.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{The chapter does not close host function spaces, Brouwer bar induction, open-cover compactness, choice-selected branches, real completeness, or a standard bridge.}
  \upgradepath{The next step is obligationClosure: carrier admission, classifier stability, bar-depth exactness, witness-window coverage, uniform-modulus extraction, and non-escape must be discharged as local rows.}
  \constructivestory{A $\FanFunctionalUp$ packet is generated from finite $\CantorSpaceUp$ prefix rows, a $\FanTheoremUp$ decidable finite-bar depth ledger, a tolerance request, finite witness windows, an extracted $\UniformModulusUp$ row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
