\chapter{A Concrete Naming Certificate for $\MooreSmithConvergenceUp$}
\label{ch:concrete-instances-mooresmithconvergence-namecert}
\origin{human}

Following Kelley and Bourbaki, the $\MooreSmithConvergenceUp$ packet records ordinary Moore--Smith convergence as a finite directed-net observation surface. It sits between the directed Cauchy evidence of \autoref{ch:concrete-instances-cauchynet-namecert} and the boundary consumers in \autoref{ch:concrete-instances-uniformcompletion-namecert} and \autoref{ch:concrete-instances-metriccompletion-namecert}: the packet names convergence toward a displayed completion boundary without turning the directed net into a quotient object, a chosen limit point, or an ambient completeness theorem.

\begin{definition}[Moore--Smith convergence carrier]
\label{def:moore-smith-convergence-carrier}
A $\MooreSmithConvergenceUp$ carrier is a finite directed-net $\BHist$ packet
$$
M=(D,V,U,C,B,R,L,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the finite directed index-window ledger, naming the inspected indices, the tail windows, and the common upper-window witnesses used by the packet.
\item $V$ is the net-value window, exposing the finitely displayed values of the Moore--Smith net on the addresses recorded by $D$.
\item $U$ is the $\UniformSpaceUp$ entourage row, recording the displayed entourages used to test convergence at the inspected boundary.
\item $C$ is the $\CauchyNetUp$ tail row, stating that the same finite directed windows support the Cauchy side of the net evidence.
\item $B$ is the boundary row, read either through $\UniformCompletionUp$ or through $\MetricCompletionUp$, naming the displayed completion boundary to which the net is tested.
\item $R$ is the $\RegSeqRatUp$ readback row for the finite rational coordinates exposed by the inspected net values and boundary reads.
\item $L$ is the $\RealUp$ readback row reached from the regular rational row when a real-facing consumer asks for a displayed boundary coordinate.
\item $H$ records componentwise $\hsame$ transport for $D,V,U,C,B,R,L$ and the structural support rows.
\item $K$ records the displayed $\Cont$ replay from directed windows through net values, entourages, Cauchy tail evidence, completion boundary reads, regular rational readbacks, and real readbacks.
\item $P$ is the $\Pkg$ provenance over $\MooreSmithConvergenceUp$, $\CauchyNetUp$, $\UniformSpaceUp$, $\UniformCompletionUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MooreSmithConvergenceUp}$ row.
\end{enumerate}
The carrier exports only this finite convergence-to-boundary packet. It contains no quotient of nets, no selected Moore--Smith limit, no global completeness assertion, no cofinal choice function, and no host-level equality of completion points.
\end{definition}

\begin{theorem}[Moore--Smith convergence NameCert obligations]
\label{thm:moore-smith-convergence-namecert-obligations}
The local $\NameCert_{\MooreSmithConvergenceUp}$ surface for \autoref{def:moore-smith-convergence-carrier} consists of six finite obligations:
\begin{enumerate}
\item carrier admission for the displayed directed-net packet $M$;
\item directed-tail coverage, stating that every displayed entourage request is routed to a tail window recorded in $D$;
\item net-value exposure, stating that the values used in the convergence test are exactly the displayed coordinates of $V$;
\item Cauchy compatibility, stating that the same directed windows feed the $\CauchyNetUp$ tail row $C$;
\item completion-boundary exposure, stating that boundary reads pass through $B$ before any $\RegSeqRatUp$ or $\RealUp$ readback is exported;
\item ledger non-escape, stating that a consumer request without a displayed tail witness or boundary row is recorded outside the packet rather than exported as convergence data.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from the tuple in \autoref{def:moore-smith-convergence-carrier}. The directed ledger, net-value window, entourage row, Cauchy tail row, completion boundary row, readback rows, transports, continuations, provenance, and local name are visible coordinates of one finite $\BHist$ packet.

Directed-tail coverage is read from $D$ together with the entourage row $U$. A convergence request can use only the inspected entourages whose tail witnesses have been displayed in the directed ledger.

Net-value exposure is then forced through $V$. The continuation row $K$ replays every accepted request from the directed window to the displayed net values before it reaches either the Cauchy tail row or the completion boundary row.

Cauchy compatibility follows because $C$ is carried in the same packet and is indexed by the same displayed directed windows. The transport row $H$ preserves those coordinates componentwise and does not add a cofinal choice function or a quotient relation on nets.

The boundary row $B$ is the only route to $\UniformCompletionUp$ or $\MetricCompletionUp$. Consequently the downstream readback rows $R$ and $L$ expose only boundary data already certified by the directed-window, entourage, and Cauchy-tail rows. If a request lacks one of these displayed witnesses, no coordinate of $M$ can export it, giving ledger non-escape.
\end{proof}
\leanchecked{BEDC.Derived.MooreSmithConvergenceUp.MooreSmithConvergencePacket\_namecert\_obligations}

\begin{theorem}[Moore--Smith convergence uniform handoff]
\label{thm:moore-smith-convergence-uniform-handoff}
Let $M=(D,V,U,C,B,R,L,H,K,P,N)$ be an accepted $\MooreSmithConvergenceUp$ carrier. Every $\UniformSpaceUp$ consumer of $M$ reads convergence evidence through the finite route
$$
D \longmapsto U \longmapsto V \longmapsto C \longmapsto B .
$$
Thus the uniform handoff exposes displayed entourages, directed tail witnesses, net values, Cauchy tail compatibility, and the completion boundary row, but it does not export a selected limit point, a quotient net, an ambient completeness theorem, or a cofinal choice operator.
\end{theorem}
\begin{proof}
Start with a uniform-facing consumer. The only entourage coordinate in the carrier is $U$, and $U$ is attached to the finite directed ledger $D$.

The continuation row $K$ sends each displayed entourage request through the net-value window $V$. The same replay then reaches the $\CauchyNetUp$ tail row $C$, so the uniform convergence read cannot separate from the finite directed-tail evidence.

The boundary row $B$ occurs after those rows in the displayed packet. The package row $P$ and local name row $N$ record the same route, while $H$ transports the listed coordinates componentwise.

Since no coordinate names a selected limit point, quotient net, ambient completeness theorem, or cofinal choice operator, the exported uniform evidence is exactly the displayed finite route.
\end{proof}
\leanchecked{BEDC.Derived.MooreSmithConvergenceUp.MooreSmithConvergencePacket\_uniform\_handoff}

\begin{theorem}[Moore--Smith convergence completion boundary]
\label{thm:moore-smith-convergence-completion-boundary}
For an accepted $\MooreSmithConvergenceUp$ carrier $M=(D,V,U,C,B,R,L,H,K,P,N)$, every $\UniformCompletionUp$ or $\MetricCompletionUp$ read exported by $B$ is downstream of the directed index-window ledger, the net-value window, the entourage row, and the $\CauchyNetUp$ tail row. The subsequent $\RegSeqRatUp$ and $\RealUp$ readbacks $R$ and $L$ therefore expose only finite boundary data certified by the same Moore--Smith convergence packet.
\end{theorem}
\begin{proof}
Project the boundary-facing coordinates of \autoref{def:moore-smith-convergence-carrier}. The boundary row $B$ is included with the same directed ledger $D$, net-value window $V$, entourage row $U$, and Cauchy tail row $C$.

The continuation row $K$ records the order in which boundary reads are replayed. A completion-boundary consumer therefore reaches $B$ only after the directed window, value, entourage, and Cauchy-tail evidence has been displayed.

The readback rows $R$ and $L$ are later than $B$. They expose regular rational and real-facing coordinates read from the displayed boundary row, not from an independent completion object.

The carrier omits selected completion points, quotient nets, global completeness, and host-level equality of boundary points. Hence the completion boundary exported by $M$ is exactly the finite Moore--Smith convergence boundary named by the same packet.
\end{proof}
\leanchecked{BEDC.Derived.MooreSmithConvergenceUp.MooreSmithConvergencePacket\_completion\_boundary}

\begin{theorem}[Moore--Smith convergence boundary scope]
\label{thm:moore-smith-convergence-boundary-scope}
For every accepted $\MooreSmithConvergenceUp$ packet $M=(D,V,U,C,B,R,L,H,K,P,N)$, a route reaches $\UniformCompletionUp$ or $\MetricCompletionUp$ only after the directed index-window ledger $D$, the net-value window $V$, the entourage row $U$, and the $\CauchyNetUp$ tail row $C$ have been displayed. The $\RegSeqRatUp$ and $\RealUp$ readbacks $R,L$ are downstream of the same boundary row $B$, so no completion-facing consumer can bypass the directed-net boundary ledger.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:moore-smith-convergence-carrier}. The only completion-facing coordinate is $B$, and it is carried with the directed ledger $D$, net-value window $V$, uniform entourage row $U$, and Cauchy-tail row $C$.

Apply \autoref{thm:moore-smith-convergence-uniform-handoff} to force uniform-facing reads through the directed window, entourage, value, and tail rows. Then apply \autoref{thm:moore-smith-convergence-completion-boundary} to place every $\UniformCompletionUp$ or $\MetricCompletionUp$ read at $B$ and every $\RegSeqRatUp$ or $\RealUp$ readback after $B$.

The remaining rows $H,K,P,N$ only transport, replay, source, and name this displayed boundary route. Because the carrier has no coordinate for quotient nets, selected limits, global completeness, or cofinal choice, ledger nonescape records those requests outside the accepted packet.
\end{proof}

\begin{theorem}[Moore--Smith convergence obligation exhaustion]
\label{thm:moore-smith-convergence-obligation-exhaustion}
For every accepted $\MooreSmithConvergenceUp$ carrier $M=(D,V,U,C,B,R,L,H,K,P,N)$, every consumer-visible convergence read is exhausted by the displayed rows
$$
D,V,U,C,B,R,L,H,K,P,N .
$$
The rows are, respectively, the directed index window, value window, uniform entourage, $\CauchyNetUp$ tail, completion boundary, $\RegSeqRatUp$ readback, $\RealUp$ readback, componentwise transport, replay, provenance, and local $\NameCert$. Quotient nets, selected limits, cofinal choice, and ambient completeness have no coordinate in the accepted packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:moore-smith-convergence-carrier}. The tuple exposes exactly the directed index window $D$, value window $V$, uniform entourage row $U$, Cauchy tail row $C$, completion boundary row $B$, readback rows $R$ and $L$, transport row $H$, replay row $K$, provenance row $P$, and local name row $N$.

Apply the NameCert obligations of \autoref{thm:moore-smith-convergence-namecert-obligations}. They account for carrier admission, directed-tail coverage, net-value exposure, Cauchy compatibility, completion-boundary exposure, and ledger non-escape using only those projected rows.

Next apply the uniform handoff of \autoref{thm:moore-smith-convergence-uniform-handoff}. It forces every uniform-facing convergence read through $D$, $U$, $V$, $C$, and $B$ before any boundary information is available.

Finally apply the completion boundary theorem \autoref{thm:moore-smith-convergence-completion-boundary}. It places the $\RegSeqRatUp$ and $\RealUp$ readbacks downstream of $B$ and prevents them from reading an independent completion object.

The excluded data have no projected coordinate. There is no row for a quotient net, selected limit, cofinal choice operator, or ambient completeness theorem, so ledger non-escape records such requests outside the packet rather than exporting them as convergence evidence.
\end{proof}

\closureat{MooreSmithConvergenceUp}{seedStr}

\begin{closurestatus}{\MooreSmithConvergenceUp}
  \constructivestory{A $\MooreSmithConvergenceUp$ packet is generated from a finite directed index-window ledger, a net-value window, a $\UniformSpaceUp$ entourage row, a $\CauchyNetUp$ tail row, a $\UniformCompletionUp$ or $\MetricCompletionUp$ boundary row, $\RegSeqRatUp$ and $\RealUp$ readbacks, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:moore-smith-convergence-carrier}, \autoref{thm:moore-smith-convergence-namecert-obligations}, \autoref{thm:moore-smith-convergence-uniform-handoff}, and \autoref{thm:moore-smith-convergence-completion-boundary} seed the finite directed-net convergence surface between Cauchy-net evidence and completion-boundary consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient nets, selected limits, global completeness, cofinal choice, host equality of completion points, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, directed-tail coverage, net-value exposure, Cauchy compatibility, completion-boundary exposure, readback nonescape, provenance, and ledger exhaustion for the same finite packet.}
\end{closurestatus}
