\chapter{A Concrete Naming Certificate for $\RegularCauchyMinUp$}
\label{ch:concrete-instances-regularcauchymin-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyMinUp$ packet reads the pointwise minimum of two regular Cauchy real names by a finite selector over displayed rational windows. The certificate sits beside the maximum and absolute-value surfaces of \autoref{ch:concrete-instances-regularcauchymax-namecert} and \autoref{ch:concrete-instances-regularcauchyabs-namecert}, uses the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and seals only through the terminal $\RealUp$ boundary of \autoref{ch:concrete-instances-real-namecert}. It does not compare completed reals by host trichotomy, quotient streams, selected limits, or ambient completeness.

\begin{definition}[RegularCauchyMin carrier]
\label{def:regular-cauchy-min-carrier}
A $\RegularCauchyMinUp$ carrier is a finite $\BHist$ packet
$$
M=(A,B,W,D_A,D_B,J,S,R,E,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $A$ and $B$ are the two source $\RegSeqRatUp$ regular rational Cauchy name rows.
\item $W$ is the shared $\StreamNameUp$ window schedule used to observe both sources at the same finite precision requests.
\item $D_A$ and $D_B$ are the displayed $\DyadicRatCoreUp$ endpoint-and-tolerance rows read from the shared window schedule for the two sources.
\item $J$ is the comparison-selector row whose finite alternatives are $A \preceq_W B$ and $B \preceq_W A$ on the displayed dyadic window data.
\item $S$ is the resulting $\RegSeqRatUp$ selector row: in the first alternative it replays the $A$ windows, and in the second alternative it replays the $B$ windows.
\item $R$ is the $\RegSeqRatUp$ readback row assembled from the selected windows and the displayed tolerance ledger.
\item $E$ is the $\RealUp$ seal row reached only after the readback row $R$ has been exposed.
\item $H$ records componentwise $\hsame$ transport for the two sources, the shared window, dyadic observations, selector row, selected regular row, readback, seal, provenance, and local name.
\item $C$ records the displayed $\Cont$ routes from the sources to the shared windows and dyadic rows, through the selector row, through the selected regular row, and onward to the readback and real seal.
\item $P$ records $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyMaxUp$, $\RegularCauchyAbsUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyMinUp}$ row.
\end{enumerate}
The carrier has no coordinate for host trichotomy on completed real names, quotient stream equality, selected limits, or a $\RealUp$ completeness principle.
\end{definition}

\begin{theorem}[RegularCauchyMin NameCert obligations]
\label{thm:regular-cauchy-min-namecert-obligations}
The local $\NameCert_{\RegularCauchyMinUp}$ surface for \autoref{def:regular-cauchy-min-carrier} consists exactly of two-source $\RegSeqRatUp$ admission, shared $\StreamNameUp$ window exposure, $\DyadicRatCoreUp$ tolerance observations, the displayed comparison-selector row, the selected $\RegSeqRatUp$ row, the $\RegSeqRatUp$ readback, the $\RealUp$ seal boundary, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row.
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed packet $M$. The coordinates expose the two source regular names, their shared stream window, their dyadic endpoint-and-tolerance rows, the selector row, the selected regular row, the readback, the real seal, and the structural rows.

The operation obligation is finite because the only branch point is the displayed row $J$. In the $A \preceq_W B$ alternative, the selected row $S$ replays the $A$ windows and their tolerance ledger; in the $B \preceq_W A$ alternative, it replays the $B$ windows and their tolerance ledger.

The sibling operation surfaces provide the algebraic checks used by consumers that prefer an identity route. The $\RegularCauchyMaxUp$ and $\RegularCauchyAbsUp$ certificates already expose finite window transport for lattice-facing regular Cauchy operations, so the minimum packet can route compatibility checks through the same displayed-window, tolerance-ledger, readback, and seal surfaces without importing host order on completed reals.

The rows $H,C,P,N$ transport, replay, source, and name this same finite route. No clause asks for trichotomy, quotient stream equality, a selected limiting real, or ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyMin selector ledger exactness]
\label{thm:regular-cauchy-min-selector-ledger}
For every accepted $\RegularCauchyMinUp$ carrier $M=(A,B,W,D_A,D_B,J,S,R,E,H,C,P,N)$, every selector-facing consumer factors through exactly one of the two displayed selector alternatives in $J$. In the $A \preceq_W B$ case the selected regular row $S$ is the finite replay of $A$ on $W,D_A$; in the $B \preceq_W A$ case $S$ is the finite replay of $B$ on $W,D_B$. No further comparison data are exported.
\end{theorem}
\begin{proof}
Begin with a selector-facing consumer of the accepted packet. The carrier gives it only the two source rows, the shared window, the two dyadic observation ledgers, and the displayed selector row.

Case-split on $J$. In the $A \preceq_W B$ branch, the continuation route in $C$ points from $A,W,D_A$ to the selected row $S$, and the transport row $H$ preserves that same selected replay componentwise. Thus the readback data downstream of $S$ are exactly the $A$ window data recorded in the packet.

In the $B \preceq_W A$ branch, the same argument uses $B,W,D_B$. The selected row $S$ is then the finite replay of the second source and its displayed tolerance ledger.

There is no third branch and no hidden comparison coordinate in \autoref{def:regular-cauchy-min-carrier}. Hence the selector ledger is exhausted by the two displayed alternatives and exports no host trichotomy, quotient stream equality, selected limit, or completeness witness.
\end{proof}

\begin{theorem}[RegularCauchyMin RealAlgOrder handoff]
\label{thm:regular-cauchy-min-realalgorder-handoff}
Every $\RealAlgOrderUp$-facing use of an accepted $\RegularCauchyMinUp$ carrier reaches the minimum row through the finite route
$$
(A,B,W,D_A,D_B)
\longrightarrow
J
\longrightarrow
S
\longrightarrow
R
\longrightarrow
E .
$$
The handoff is therefore a regular Cauchy selector ledger over shared windows and dyadic tolerance observations, not a host-order comparison of completed real names.
\end{theorem}
\begin{proof}
Start with a $\RealAlgOrderUp$-facing consumer. The only real-facing endpoint in the carrier is the seal row $E$, and $E$ is downstream of the readback row $R$.

By \autoref{thm:regular-cauchy-min-selector-ledger}, the readback row $R$ is downstream of a selected regular row $S$ obtained by case-splitting only on the displayed selector row $J$. Each selector branch uses the same shared window schedule and one of the two displayed dyadic tolerance ledgers.

The handoff to order-facing consumers is therefore the listed finite route. Compatibility with existing lattice surfaces can be checked against the sibling $\RegularCauchyMaxUp$ and $\RegularCauchyAbsUp$ routes, but the minimum packet itself does not expose host trichotomy, quotient stream equality, selected limits, or ambient completeness.
\end{proof}

\begin{closurestatus}{\RegularCauchyMinUp}
  \constructivestory{A $\RegularCauchyMinUp$ packet is generated from two RegSeqRat source rows, a shared StreamName window schedule, DyadicRatCore endpoint-and-tolerance observations, a comparison-selector row, a selected RegSeqRat row, a RegSeqRat readback row, a RealUp seal row, componentwise transport, continuation replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-min-carrier}, \autoref{thm:regular-cauchy-min-namecert-obligations}, \autoref{thm:regular-cauchy-min-selector-ledger}, and \autoref{thm:regular-cauchy-min-realalgorder-handoff} seed the finite pointwise minimum route over shared regular Cauchy windows, selector ledgers, readback, and RealUp sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, host trichotomy on completed real names, quotient stream equality, selected limits, ambient completeness, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, selector ledger exactness, RealAlgOrder handoff, transport stability, provenance, and non-escape for the same finite packet.}
\end{closurestatus}
