\chapter{A Concrete Naming Certificate for $\CantorSetUp$}
\label{ch:concrete-instances-cantorset-namecert}
\origin{human}

Following Cantor and Bishop--Bridges constructive analysis, the $\CantorSetUp$ packet records the middle-third closed subset of the real line as finite ternary-prefix and deleted-middle interval data. It is a real-set certificate downstream of the nested interval discipline of \autoref{ch:concrete-instances-nestedinterval-namecert}, the dyadic endpoint surface of \autoref{ch:concrete-instances-dyadicinterval-namecert}, and the $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The carrier names only finite prefixes, finite gap ledgers, nested interval rows, and real-seal routing; it does not import open-cover compactness, host powersets, quotient real equality, or a completed infinite intersection.

\begin{definition}[Cantor set carrier]
\label{def:cantor-set-carrier}
A $\CantorSetUp$ carrier is a finite $\BHist$ packet
$$
C=(T,G,I,D,R,E,H,K,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $T$ is the ternary-prefix ledger, a finite word over the left and right retained thirds, together with its generation depth.
\item $G$ is the deleted-middle interval ledger, listing the middle-third gaps excluded at the displayed depths.
\item $I$ is the retained nested-interval row whose endpoints are determined by $T$ and whose containment route is read through the $\NestedIntervalUp$ surface.
\item $D$ is the auxiliary $\DyadicIntervalUp$ or rational endpoint ledger used to expose the retained interval endpoints to finite consumers.
\item $R$ is the $\RegSeqRatUp$ handoff row for a real-name readback compatible with the retained interval chain.
\item $E$ is the $\RealUp$ seal row reached only after the ternary prefix, deleted-gap ledger, retained interval row, endpoint ledger, and regular-rational handoff have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the ternary prefix, gap ledger, interval row, endpoint ledger, handoff row, real seal, continuation replay, provenance, and local naming row.
\item $K$ stores displayed $\Cont$ replay from prefix requests to gap checks, from gap checks to retained intervals, and from retained intervals to $R$ and $E$.
\item $P$ is the $\Pkg$ provenance over $\CantorSetUp$, $\NestedIntervalUp$, $\DyadicIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CantorSetUp}$ row.
\end{enumerate}
The classifier accepts a packet only when the displayed prefix $T$ selects retained thirds, the ledger $G$ contains exactly the finite deleted-middle gaps inspected at those depths, the interval row $I$ avoids those gaps, and every real-facing read factors through $R,E,H,K,P,N$. It has no coordinate for a host subset of $\RealUp$, open-cover compactness, quotient real equality, selected infinite branch, or ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.CantorSetUp.CantorSetTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cantor set NameCert obligations]
\label{thm:cantor-set-namecert-obligations}
For an accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, the local $\NameCert_{\CantorSetUp}$ obligations are exactly carrier admission, finite ternary-prefix classification, deleted-middle gap exclusion, nested-interval containment, endpoint-ledger compatibility, $\RealUp$ seal handoff, and non-escape. These obligations are discharged by the displayed route
$$
T\longmapsto G\longmapsto I\longmapsto D\longmapsto R\longmapsto E
$$
together with $H,K,P,N$.
\end{theorem}
\begin{proof}
Carrier admission projects the finite tuple of \autoref{def:cantor-set-carrier}. The prefix classifier reads $T$ as a finite retained-third word and therefore inspects only finitely many ternary branch decisions.

The deleted-middle exclusion row $G$ is the only place where removed middle-third intervals are named. The retained interval row $I$ must pass through the $\NestedIntervalUp$ containment surface, so every accepted prefix determines a retained nested interval before any real-facing row is read.

Endpoint compatibility is checked by $D$. This ledger exposes the same retained interval endpoints to dyadic or rational interval consumers and prevents a later consumer from replacing the ternary interval by an unrelated host interval.

Finally, $R$ and $E$ are downstream readback and seal rows. The transport, continuation, provenance, and naming rows $H,K,P,N$ preserve the same finite route, and no carrier coordinate supplies open-cover compactness, host powersets, quotient real equality, a selected infinite branch, or ambient real completeness.
\end{proof}

\begin{theorem}[Cantor set finite-prefix induction]
\label{thm:cantor-set-finite-prefix-induction}
For every accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, retained-third prefixes are generated only by finite induction over the displayed ternary-prefix ledger $T$. No membership-facing read may replace this finite induction with a selected infinite branch, a host powerset element, quotient real equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cantor-set-carrier}. The row $T$ is a finite word over retained left and right thirds together with its displayed generation depth, so its generation rule is finite ledger induction rather than branch selection.

Use \autoref{thm:cantor-set-namecert-obligations}. Its finite ternary-prefix classification is the first obligation read by the local $\NameCert_{\CantorSetUp}$ surface, before deleted-gap exclusion, nested-interval containment, endpoint compatibility, or Real seal handoff.

The structural rows preserve this induction route. Componentwise $\hsame$ transport in $H$ and displayed $\Cont$ replay in $K$ move only the finite prefix ledger named by $T$, while $P$ and $N$ record the same finite provenance and local naming. Since no carrier coordinate stores a selected infinite branch or host powerset, every retained-prefix read is generated by the displayed finite induction.
\end{proof}

\begin{theorem}[Cantor set deleted-gap ledger exhaustion]
\label{thm:cantor-set-deleted-gap-ledger-exhaustion}
For every accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, every deleted-middle exclusion read factors through the displayed route
$$
G\longmapsto I\longmapsto D
$$
before any regular-rational handoff $R$ or $\RealUp$ seal $E$ is consumed. Thus the exclusion surface is exhausted by the finite gap ledger, retained interval row, and endpoint ledger, not by open-cover compactness, host powersets, quotient real equality, selected infinite branches, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the deleted-middle coordinate in \autoref{def:cantor-set-carrier}. The row $G$ is the only carrier row where removed middle-third gaps are named, and the accepted classifier requires the retained interval row $I$ to avoid exactly the displayed gap entries at the inspected depths.

Next read the endpoint ledger $D$. It exposes the retained interval endpoints determined by $T$ and checked against $G$, so an exclusion read cannot pass directly from a gap name to $R$ or $E$ without first traversing $I$ and $D$.

Finally apply \autoref{thm:cantor-set-namecert-obligations}. Deleted-middle gap exclusion, nested-interval containment, and endpoint-ledger compatibility all precede Real seal handoff. The rows $H,K,P,N$ transport, replay, package, and name this same exhausted route, and no excluded host-level coordinate is available.
\end{proof}

\begin{theorem}[Cantor set Real membership handoff]
\label{thm:cantor-set-real-membership-handoff}
Every Real-facing membership consumer of an accepted $\CantorSetUp$ carrier receives only the route
$$
T,G,I,D,R,E,H,K,P,N .
$$
In particular, the handoff to a $\RealUp$ membership surface cannot bypass the ternary-prefix ledger, deleted-gap ledger, retained interval row, endpoint ledger, regular-rational readback, seal, transport, continuation replay, provenance, or local $\NameCert$ row.
\end{theorem}
\begin{proof}
Start from the Real seal coordinate $E$ in \autoref{def:cantor-set-carrier}. It is downstream of the finite prefix row $T$, the deleted-gap ledger $G$, the retained nested interval row $I$, the endpoint ledger $D$, and the regular-rational handoff $R$.

Use \autoref{thm:cantor-set-namecert-obligations} to identify the local obligation order. The membership-facing read reaches the Real seal only after carrier admission, prefix classification, gap exclusion, nested-interval containment, endpoint compatibility, and seal handoff have all been read on the same packet.

The same route is stable under $\hsame$ and $\Cont$. Rows $H$ and $K$ preserve the componentwise transport and replay, while $P$ and $N$ bind the package provenance and local name. Therefore a Real-facing membership consumer receives precisely $T,G,I,D,R,E,H,K,P,N$ and no open-cover compactness, host powerset, quotient real equality, selected branch, or ambient completeness claim.
\end{proof}

\begin{theorem}[Cantor set prefix-gap separation]
\label{thm:cantor-set-prefix-gap-separation}
For every accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, a retained-prefix read from $T$ excludes each displayed deleted-middle gap row in $G$ before any $\RealUp$ seal is consumed. The exclusion is witnessed inside the route
$$
T \longmapsto G \longmapsto I \longmapsto D
$$
through the retained $\NestedIntervalUp$ row and the endpoint ledger, and it has no access to host powersets, quotient real equality, selected infinite branches, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cantor-set-carrier}. The prefix ledger $T$ names only retained left and right thirds, while the deleted-middle ledger $G$ is the unique row where excluded middle-third intervals are displayed.

The retained interval row $I$ is read before the endpoint row $D$ and before the Real seal $E$. Thus a prefix request must first compare its retained interval with the displayed gap ledger, using the same $\NestedIntervalUp$ containment route and the same dyadic or rational endpoint ledger.

The structural rows $H,K,P,N$ preserve this route under $\hsame$ transport and $\Cont$ replay. Since the carrier has no host powerset, quotient real equality, selected branch, compactness, or completeness coordinate, a retained-prefix read can exclude only the displayed gap rows before it reaches the seal.
\end{proof}

\begin{theorem}[Cantor set ternary-prefix classifier]
\label{thm:cantor-set-ternary-prefix-classifier}
For every accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, a finite prefix read is classified only by the retained left-third and right-third symbols recorded in $T$ before any deleted-gap ledger or $\RealUp$ row is read. The classifier therefore exposes a finite ternary-retention surface and not a host powerset, quotient real equality, selected infinite branch, compactness theorem, or ambient completeness principle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cantor-set-carrier}. The prefix coordinate $T$ is the only row that records retained left and right thirds, while the deleted-gap row $G$ and Real seal $E$ are downstream rows.

Use \autoref{thm:cantor-set-namecert-obligations}. Its finite ternary-prefix classification row is read before deleted-middle exclusion, nested-interval containment, endpoint compatibility, and Real seal handoff.

Finally apply \autoref{thm:cantor-set-prefix-gap-separation} and \autoref{thm:cantor-set-real-seal-nonescape}. They keep every gap and Real-facing read behind the displayed route from $T$ through $G,I,D,R,E$, so the prefix classifier cannot supply any excluded host-level principle.
\end{proof}

\begin{theorem}[Cantor set nested-interval handoff]
\label{thm:cantor-set-nested-interval-handoff}
For every accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, the retained prefix ledger $T$ and deleted-gap ledger $G$ hand the consumer to the retained $\NestedIntervalUp$ row $I$ before any endpoint readback through $D,R,E$ is available. The handoff is a finite row route and not a selected infinite branch, quotient real equality, open-cover compactness theorem, or ambient $\RealUp$ completeness argument.
\end{theorem}
\begin{proof}
Start from the retained-prefix and gap rows in \autoref{def:cantor-set-carrier}. The row $I$ is defined as the retained nested-interval row whose endpoints are determined by $T$ and whose avoided gaps are the displayed entries of $G$.

Apply \autoref{thm:cantor-set-prefix-gap-separation}. It forces the consumer to compare the retained prefix with the deleted-middle ledger before the endpoint row $D$ and before the Real seal $E$.

Use \autoref{thm:cantor-set-namecert-obligations} for the remaining handoff. Nested-interval containment precedes endpoint-ledger compatibility and regular-rational readback, so $D,R,E$ can only read the retained interval already named by $I$.
\end{proof}

\begin{theorem}[Cantor set Real-seal membership boundary]
\label{thm:cantor-set-real-seal-membership-boundary}
For every accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, every membership-facing $\RealUp$ seal is downstream of $T,G,I,D,R,E,H,K,P,N$. It cannot supply a host powerset, quotient real equality, selected infinite branch, compactness theorem, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cantor-set-real-seal-nonescape}. It states that every Real-facing read factors through $T,G,I,D,R,E$ and the structural rows $H,K,P,N$.

Use \autoref{thm:cantor-set-namecert-obligations}. The same rows cover carrier admission, prefix classification, gap exclusion, nested-interval containment, endpoint compatibility, Real seal handoff, and non-escape.

Finally apply \autoref{thm:cantor-set-prefix-gap-separation}. Since the carrier has no coordinate outside the displayed finite rows, the membership-facing seal cannot become a host powerset, quotient equality, selected branch, compactness, or completeness object.
\end{proof}

\begin{theorem}[Cantor set downstream membership consumer]
\label{thm:cantor-set-downstream-membership-consumer}
Any downstream Real-facing closed-set or interval-membership consumer of an accepted $\CantorSetUp$ packet must read the ternary-prefix ledger $T$, the deleted-gap ledger $G$, the retained $\NestedIntervalUp$ row $I$, the endpoint ledger $D$, the $\RegSeqRatUp$ handoff $R$, and the $\RealUp$ seal $E$ before treating the packet as membership data. In particular, a locator-facing consumer such as \autoref{ch:concrete-instances-real-locator-namecert} receives only this displayed finite route and not a host powerset, quotient real equality, selected infinite branch, compactness theorem, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Begin with the Real-seal membership boundary of \autoref{thm:cantor-set-real-seal-membership-boundary}. It places every membership-facing Real seal downstream of the displayed rows $T,G,I,D,R,E,H,K,P,N$.

Next use the nested-interval handoff, \autoref{thm:cantor-set-nested-interval-handoff}. The retained interval row $I$ is available only after the prefix and gap ledgers have been read, and the endpoint ledger $D$ is downstream of that retained interval route.

Finally apply Real seal nonescape, \autoref{thm:cantor-set-real-seal-nonescape}. It forces each Real-facing read through $T,G,I,D,R,E$ with the same transport, replay, provenance, and local naming rows. Hence any downstream closed-set, interval-membership, or locator-facing consumer receives exactly the finite membership route and none of the excluded host-level data.
\end{proof}

\begin{theorem}[Cantor set Real seal nonescape]
\label{thm:cantor-set-real-seal-nonescape}
For every accepted $\CantorSetUp$ carrier $C=(T,G,I,D,R,E,H,K,P,N)$, every $\RealUp$-facing read factors through the finite route
$$
T \longmapsto G \longmapsto I \longmapsto D \longmapsto R \longmapsto E
$$
with the same transport, replay, provenance, and local name rows $H,K,P,N$. No Real-facing consumer can bypass the retained-prefix ledger, deleted-gap ledger, nested interval row, endpoint ledger, regular-rational handoff, or local NameCert surface.
\end{theorem}
\begin{proof}
Start from a Real-facing read. By \autoref{def:cantor-set-carrier}, the seal coordinate $E$ is downstream of the ternary prefix, gap ledger, retained interval, endpoint ledger, and regular-rational handoff.

Use \autoref{thm:cantor-set-namecert-obligations}. Its deleted-middle exclusion, nested-interval containment, endpoint compatibility, and Real seal handoff rows require the consumer to traverse $T,G,I,D,R$ before $E$ is visible.

Finally read the structural coordinates. The rows $H,K,P,N$ preserve and name the same finite route, and there is no coordinate from which a consumer could construct a bypassing seal, host subset equality, selected infinite branch, or ambient completeness proof.
\end{proof}

\begin{theorem}[Cantor set endpoint-ledger stability]
\label{thm:cantor-set-endpoint-ledger-stability}
Let $C=(T,G,I,D,R,E,H,K,P,N)$ and $C'=(T',G',I',D',R',E',H',K',P',N')$ be accepted $\CantorSetUp$ carriers whose prefix, gap, retained-interval, regular-rational, seal, provenance, and local naming rows are related by the componentwise $\hsame$ transports stored in $H$ and $H'$, and whose displayed continuations replay the same retained-prefix requests through $K$ and $K'$. If the endpoint ledger $D$ is admitted for $C$, then the transported endpoint ledger $D'$ is admitted for $C'$ and determines the same retained endpoint route for Real-facing reads.
\end{theorem}
\begin{proof}
Project the endpoint row. In an accepted carrier, $D$ is not a free interval datum; it is read after the retained prefix $T$, the displayed deleted-gap ledger $G$, and the retained $\NestedIntervalUp$ row $I$.

Apply the componentwise $\hsame$ transport rows. They carry the prefix, gap, retained interval, endpoint, regular handoff, seal, provenance, and local name rows together, so the endpoint ledger cannot be transported without preserving the retained interval route that generated it.

Now use the displayed $\Cont$ replay rows. The same prefix requests replay through the same gap checks and retained interval rows before the endpoint ledger is consumed. Therefore $D'$ is admitted exactly when it continues the transported retained route, and it determines the same endpoint path for the downstream $\RegSeqRatUp$ and $\RealUp$ reads.
\end{proof}

\falsifiablePrediction{Every accepted $\CantorSetUp$ real-facing read factors through the displayed ternary-prefix ledger, deleted-middle interval ledger, retained nested-interval row, endpoint ledger, regular-rational handoff, and $\RealUp$ seal before the set membership surface is consumed.}

\independenceWitness{nestedinterval, dyadicinterval, regseqrat, real, cantorspace: $\CantorSetUp$ is not bijective to any listed sibling because it jointly carries a ternary retained-prefix ledger, deleted-middle gap ledger, retained nested interval row, endpoint compatibility row, regular-rational handoff, real seal, transport, continuation replay, provenance, and local naming.}

\closureat{CantorSetUp}{seedStr}

\begin{closurestatus}{\CantorSetUp}
  \constructivestory{A $\CantorSetUp$ packet is generated from a finite ternary retained-prefix ledger, a deleted-middle gap ledger, a retained NestedInterval row, a DyadicInterval or rational endpoint ledger, a RegSeqRat handoff, a RealUp seal, componentwise transport, continuation replay, provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cantor-set-carrier} and \autoref{thm:cantor-set-namecert-obligations} seed the finite closed-set carrier for the middle-third Cantor subset through retained prefixes, deleted gaps, nested intervals, endpoint rows, and the $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close located compactness, open-cover compactness, host powerset equality, quotient real equality, selected infinite branches, ambient $\RealUp$ completeness, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, prefix classification, gap exclusion, nested-interval containment, endpoint-ledger compatibility, real-seal handoff, and non-escape for BEDC.Derived.CantorSetUp.}
\end{closurestatus}
