\chapter{A Concrete Naming Certificate for $\ClosedGraphTheoremUp$}
\label{ch:concrete-instances-closed-graph-theorem-namecert}
\origin{human}

Following the Banach closed graph theorem tradition in Banach and Bourbaki-style functional analysis, the $\ClosedGraphTheoremUp$ packet records the finite BEDC certificate for reading a graph-closed linear or structured map as a locally bounded route between complete normed or complete-metric presentations. The packet is anchored in the Banach carrier of \autoref{ch:concrete-instances-banach-namecert}, the complete-metric surface of \autoref{ch:concrete-instances-completemetric-namecert}, the metric observation rows of \autoref{ch:concrete-instances-metric-namecert}, and the bounded-map comparison interface of \autoref{ch:concrete-instances-lipschitzmap-namecert}. Its finite real-facing names pass through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}, so the certificate exposes only displayed graph closure, transported Cauchy control, and local boundedness rows rather than host graph equality, quotient function spaces, choice-selected limits, or ambient completeness.

\begin{definition}[ClosedGraphTheorem carrier]
\label{def:closed-graph-theorem-carrier}
A $\ClosedGraphTheoremUp$ carrier is a finite $\BHist$ packet
$$
G=(X,Y,T,\Gamma,C_M,S,R,E,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the source $\BanachUp$ or $\CompleteMetricUp$ row, including the displayed metric observations through the $\MetricUp$ surface used to read Cauchy input windows.
\item $Y$ is the target $\BanachUp$ or $\CompleteMetricUp$ row, including the displayed metric observations through the $\MetricUp$ surface used to read Cauchy output windows.
\item $T$ is the map row, read as a finite graph or action table whose bounded-map comparisons may be inspected through the $\LipschitzMapUp$ interface when a modulus or local bound is displayed.
\item $\Gamma$ is the graph row, consisting of finite source--target observation pairs and the graph-membership witnesses by which a consumer reads that $y$ is the displayed image of $x$.
\item $C_M$ is the closed-graph witness row, recording the paired Cauchy-route test: source windows converge in $X$, output windows converge in $Y$, graph rows persist along the paired route, and the target limit row is accepted as the graph value.
\item $S$ is the $\StreamNameUp$ schedule row selecting finite source, target, graph, and modulus windows for each inspection.
\item $R$ is the $\RegSeqRatUp$ readback row supplying regular rational distance and bound observations for the scheduled metric windows.
\item $E$ is the $\RealUp$ seal row through which numeric distance, bound, and convergence reads are consumed.
\item $H$ records componentwise $\hsame$ transport for source, target, map, graph, closed-graph, schedule, readback, seal, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from source and target admission through stream scheduling, regular rational readback, graph inspection, closed-graph transfer, bound extraction, and real-seal handoff.
\item $P$ is the $\Pkg$ provenance over $\ClosedGraphTheoremUp$, $\BanachUp$, $\CompleteMetricUp$, $\MetricUp$, $\LipschitzMapUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\ClosedGraphTheoremUp}$ row.
\end{enumerate}
The carrier has no coordinate for the open mapping theorem, bounded inverse theorem, host graph equality, quotient function spaces, choice-selected limits, or ambient completeness beyond the source and target completeness rows explicitly displayed in $X$ and $Y$.
\end{definition}

\begin{theorem}[ClosedGraphTheorem NameCert obligations]
\label{thm:closed-graph-theorem-namecert-obligations}
For an accepted $\ClosedGraphTheoremUp$ carrier $G=(X,Y,T,\Gamma,C_M,S,R,E,H,C,P,N)$, the local $\NameCert_{\ClosedGraphTheoremUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the source complete row, target complete row, map row, graph row, closed-graph witness, stream schedule, regular rational readback, real seal, transport, replay, provenance, and local naming rows;
\item source and target completeness routing, requiring every Cauchy input and Cauchy output inspection to pass through the $\BanachUp$ or $\CompleteMetricUp$ rows in $X$ and $Y$ and their displayed $\MetricUp$ observations;
\item graph-membership exactness, requiring every accepted graph read to be a finite row of $\Gamma$ over the scheduled source and target windows;
\item closed-graph transfer, requiring the paired limit route in $C_M$ to preserve $\Gamma$ along the same stream schedule and regular rational readback;
\item bounded-route extraction, requiring any local boundedness or Lipschitz-facing consumer to read through $T$, $\Gamma$, $C_M$, $S$, $R$, and $E$ rather than through an ambient function-space theorem;
\item classifier stability, requiring transported packets with the same displayed rows to be identified by the carried $\hsame$ data and replayed by the same $\Cont$ route;
\item ledger non-escape, stating that no open mapping theorem, bounded inverse theorem, host graph equality, quotient function space, choice-selected limit, or ambient-completeness principle is exported by the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:closed-graph-theorem-carrier}. The listed rows are exactly the source, target, map, graph, closed-graph, schedule, readback, real-seal, transport, replay, provenance, and local name data available to a consumer.

The completeness routing is inherited only as displayed source and target rows. The source side is read through \autoref{ch:concrete-instances-banach-namecert} or \autoref{ch:concrete-instances-completemetric-namecert}, and the target side is read through the same complete-metric vocabulary; the metric observations used by both sides are those of \autoref{ch:concrete-instances-metric-namecert}.

Graph-membership exactness is the role of $\Gamma$. A graph consumer cannot infer equality of host functions; it reads finite source--target observation pairs, and those pairs are scheduled by $S$ and measured through $R$ and $E$ using the naming route of \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

Closed-graph transfer is then the finite witness row $C_M$. It records the paired Cauchy route, the persistence of graph rows along that route, and the accepted target limit row. When a bounded-map consumer is present, the read is compared through the interface of \autoref{ch:concrete-instances-lipschitzmap-namecert}, but the packet exports only the displayed route and not an external open-mapping or inverse theorem.

Finally $H$ and $C$ transport and replay the same fields, while $P$ and $N$ package the local certificate. Since the carrier fields are exhausted by $X,Y,T,\Gamma,C_M,S,R,E,H,C,P,N$, the excluded principles have no row from which a consumer could read them.
\end{proof}

\begin{theorem}[ClosedGraphTheorem graph-closure route]
\label{thm:closed-graph-theorem-graph-closure-route}
Let $G=(X,Y,T,\Gamma,C_M,S,R,E,H,C,P,N)$ be an accepted $\ClosedGraphTheoremUp$ carrier. Every graph-closure read exported by $G$ factors through the displayed route
$$
X,Y,T,\Gamma,S,R,E,C_M,H,C,P,N .
$$
Thus a convergent source schedule and a convergent target schedule identify a graph value only after their finite graph rows have been replayed through $C_M$ and sealed through the StreamName, RegSeqRat, and Real rows; the route does not assert host graph equality or equality inside a quotient function space.
\end{theorem}
\begin{proof}
Begin with the source and target Cauchy inspections. The rows $X$ and $Y$ expose the complete Banach or complete-metric data, and their metric windows are the observations read by the route rather than ambient points.

The map and graph information is then read through $T$ and $\Gamma$. The schedule $S$ selects the finite source, target, and graph windows; the regular readback $R$ and real seal $E$ measure the requested distances and bounds.

The closed-graph witness $C_M$ is the only row that turns the paired Cauchy route into a graph-value read. It requires the graph rows to persist along the same schedule and accepts the target limit row as a displayed graph value.

Transport by $H$ and replay by $C$ preserve the same route after classifier movement, and $P,N$ record its provenance and local certificate. Because no quotient function-space coordinate or host graph equality coordinate is present, the graph-closure read is exactly the displayed finite route.
\end{proof}

\begin{theorem}[ClosedGraphTheorem non-escape boundary]
\label{thm:closed-graph-theorem-nonescape-boundary}
For every accepted $\ClosedGraphTheoremUp$ carrier $G=(X,Y,T,\Gamma,C_M,S,R,E,H,C,P,N)$, any boundedness, continuity-facing, or graph-facing conclusion exported by the packet is confined to the rows displayed in $G$. In particular, the packet does not export the open mapping theorem, the bounded inverse theorem, host graph equality, quotient function spaces, choice-selected limits, or ambient completeness beyond the source and target rows $X$ and $Y$.
\end{theorem}
\begin{proof}
Read an exported conclusion from the carrier. A graph-facing read must use $\Gamma$ and $C_M$; a boundedness or continuity-facing read must use $T$ together with the same graph, schedule, readback, and seal rows.

The source and target completeness information is limited to $X$ and $Y$. These rows may expose the Banach or complete-metric certificate and the associated metric observations, but they do not add any global function-space carrier.

The numeric side is likewise finite. Stream windows come from $S$, regular rational observations from $R$, and real-facing distance or bound reads from $E$.

All remaining movement is componentwise transport by $H$, continuation replay by $C$, and package bookkeeping by $P,N$. Since no excluded principle is a coordinate of $G$, no accepted consumer can obtain one from the $\ClosedGraphTheoremUp$ packet.
\end{proof}

\begin{closurestatus}{\ClosedGraphTheoremUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:closed-graph-theorem-carrier}, \autoref{thm:closed-graph-theorem-namecert-obligations}, \autoref{thm:closed-graph-theorem-graph-closure-route}, and \autoref{thm:closed-graph-theorem-nonescape-boundary} seed the finite closed-graph certificate over displayed complete source and target rows, graph witnesses, StreamName schedules, RegSeqRat readbacks, and Real seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close the open mapping theorem, bounded inverse theorem, host graph equality, quotient function spaces, choice-selected limits, or ambient completeness beyond the displayed source and target rows.}
  \upgradepath{Obligation closure requires checked carrier admission, graph-membership exactness, closed-graph transfer, bounded-route extraction, classifier stability, and ledger non-escape for the same packet.}
  \constructivestory{The construction starts from displayed complete source and target rows, schedules finite graph observations, seals distance and bound reads through RegSeqRat and Real data, and exports only the local graph-closure route recorded by hsame and Cont ledgers.}
\end{closurestatus}
