\chapter{A Concrete Naming Certificate for $\LowerSemicontinuousUp$}
\label{ch:concrete-instances-lowersemicontinuous-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, lower semicontinuity is
read through lower bounds and finite epigraph witnesses rather than through a
host topology. The $\LowerSemicontinuousUp$ packet records that interface over
the lower-real surface of \autoref{ch:concrete-instances-lowerreal-namecert},
the upper-real comparison boundary of
\autoref{ch:concrete-instances-upperreal-namecert}, the located readbacks of
\autoref{ch:concrete-instances-locatedreal-namecert}, the modulus-bearing
map rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the
scheduled stream windows of \autoref{ch:concrete-instances-streamname-namecert},
the regular rational source rows of
\autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name
seal of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[LowerSemicontinuous carrier]
\label{def:lower-semicontinuous-carrier}
A $\LowerSemicontinuousUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
L=(X,F,E,W,R,O,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the source carrier row whose accepted points are read through
  displayed $\mathsf{BHist}$ histories and their classifier transport;
\item $F$ is the function graph or map row, read through the
  $\ContinuousMapUp$ pointwise carrier only when such a map surface is present;
\item $E$ is the lower-real epigraph ledger, consisting of finite rows
  $(x,q)$ saying that the value at the displayed source point admits the
  rational lower bound $q$ at the inspected window;
\item $W$ is the $\StreamNameUp$ schedule row selecting finite source and
  value windows for each epigraph inspection;
\item $R$ is the $\RegSeqRatUp$ readback row giving the regular rational
  value windows used by $E$;
\item $O$ is the $\LowerRealUp$, $\UpperRealUp$, and $\LocatedRealUp$
  comparison ledger used to read lower windows, upper exclusions, located
  endpoint checks, and finite lower-bound refinements;
\item $H$ records componentwise $\hsame$ transport for source histories,
  graph rows, lower-real epigraph rows, stream windows, regular readbacks,
  comparison ledgers, provenance rows, and local naming rows;
\item $C$ records displayed $\Cont$ replay from source admission through
  window selection, regular rational readback, lower-real epigraph inspection,
  located readback, and real-seal handoff;
\item $P$ is the $\Pkg$ provenance over $\LowerSemicontinuousUp$,
  $\LowerRealUp$, $\UpperRealUp$, $\LocatedRealUp$, $\ContinuousMapUp$,
  $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$,
  $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\LowerSemicontinuousUp}$ row.
\end{enumerate}
The classifier relates two accepted packets exactly when their source rows,
finite epigraph windows, regular rational readbacks, lower-real comparisons,
located readbacks, $\RealUp$ seal rows, and provenance rows transport
componentwise along $H$ and replay through the same displayed routes in $C$.
No host topology, open-set lattice, quotient real equality, semantic limit
operator, or completeness principle is a carrier coordinate.
\end{definition}
\leanchecked{BEDC.Derived.LowerSemicontinuousUp.LowerSemicontinuousTasteGate\_single\_carrier\_alignment}

\begin{theorem}[LowerSemicontinuous NameCert obligation surface]
\label{thm:lower-semicontinuous-namecert-obligation-surface}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, the local
$\NameCert_{\LowerSemicontinuousUp}$ surface consists exactly of six
obligations:
\begin{enumerate}
\item carrier admission for the displayed source, graph, epigraph, schedule,
  readback, comparison, transport, replay, provenance, and local naming rows;
\item epigraph-window exactness, requiring every lower-bound read to appear
  as a finite $(x,q)$ row in $E$ after the schedule in $W$ and readback in
  $R$ have been replayed;
\item lower-real classifier stability, requiring lower refinements and
  rational-bound comparisons to be transported through the $\LowerRealUp$
  rows in $O$;
\item located readback compatibility, requiring every inspected source or
  value window to pass through the $\LocatedRealUp$ rows before a real-facing
  consumer can read it;
\item $\hsame$ and $\Cont$ replay, requiring all source, graph, epigraph,
  readback, comparison, and seal rows to move together under the displayed
  transport and continuation ledgers;
\item provenance and non-escape, stating that the package exports only the
  named finite rows and no host topology, quotient equality, semantic limit,
  open-cover compactness, countable choice, or $\RealUp$ completeness
  principle.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from
\autoref{def:lower-semicontinuous-carrier}. The packet lists exactly the
source row, graph row, epigraph ledger, finite schedule, regular readback,
comparison ledger, transport ledger, replay ledger, provenance row, and local
name.

Epigraph-window exactness is read from $E$ only after the requested source
window has passed through $W$ and the value readback through $R$. Thus a
lower-bound claim is not an external predicate; it is a displayed finite row
over the inspected source and rational bound.

Lower-real classifier stability is the role of $O$ together with $H$. The
lower-real comparisons, upper-side exclusions, and located endpoint checks
move componentwise by $\hsame$, and the continuation row $C$ records the same
inspection route after transport.

Located readback compatibility follows because every real-facing window is
read through the $\LocatedRealUp$ rows before the terminal $\RealUp$ seal is
available. The readback is therefore a finite stream and regular-rational
route, not a host limit operation.

Finally, $P$ and $N$ package those rows as the local certificate. Since the
carrier has no coordinate for the excluded principles, no consumer can obtain
them from the $\LowerSemicontinuousUp$ NameCert surface.
\end{proof}

\begin{theorem}[LowerSemicontinuous epigraph window exactness]
\label{thm:lowersemicontinuous-epigraph-window-exactness}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, every lower-bound or epigraph read exposed by
$E$ is exact only along the finite window route
$$
W \longrightarrow R \longrightarrow E .
$$
A consumer must first select the displayed source window in $W$, then read the
regular rational value data in $R$, and only then inspect the epigraph row
$E$. The row $E$ cannot be read as a host lower-set predicate, a semantic
liminf assertion, quotient real equality, selected limits, countable choice,
or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier coordinates from
\autoref{def:lower-semicontinuous-carrier}. The epigraph row is one displayed
coordinate of $L$, and the only finite schedule for inspecting it is $W$.

Apply \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. Its
epigraph-window obligation places every lower-bound read after a scheduled
window and a regular rational readback.

The route is therefore $W,R,E$ inside the same $\BHist$ packet. Since the
carrier contains no coordinate for the excluded host principles, the epigraph
read cannot detach from that route.
\end{proof}

\begin{theorem}[LowerSemicontinuous located epigraph transport]
\label{thm:lower-semicontinuous-located-epigraph-transport}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, the located lower-real and upper-real comparison
rows recorded in $O$ transport the displayed epigraph row $E$ through $H$ and
$C$. A lower-bound read that has passed through $W,R,E,O$ remains the same
BEDC row after componentwise $\hsame$ transport and displayed continuation
replay; it cannot become a host lower-set predicate, a semantic liminf
assertion, quotient equality, selected endpoints, countable choice, or ambient
completeness.
\end{theorem}
\begin{proof}
Start with the epigraph route of
\autoref{thm:lowersemicontinuous-epigraph-window-exactness}. It places every
lower-bound read on $W,R,E$ before the located comparison ledger can be used.

The row $O$ then supplies the lower-real, upper-real, and located comparison
data for that same displayed epigraph row. These comparisons are packet rows,
not external topological predicates.

Transport and replay are componentwise. The row $H$ moves $E$ and $O$ by
$\hsame$, and $C$ replays the same finite inspection route, so the transported
read is still the displayed $W,R,E,O$ route.
\end{proof}

\begin{theorem}[LowerSemicontinuous regular readback nonescape]
\label{thm:lower-semicontinuous-regular-readback-nonescape}
Every lower-bound read from an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$ factors through
$$
W,R,E,O,H,C,P,N .
$$
The readback route uses finite windows, regular-rational values, the epigraph
row, located comparison rows, transport, replay, provenance, and local naming;
it has no coordinate for host liminf, quotient equality, selected limits,
countable choice, compactness, or ambient completeness.
\end{theorem}
\begin{proof}
The scheduled window row $W$ fixes the inspected source window, and the
regular-rational row $R$ supplies the displayed value readback. By
\autoref{thm:lowersemicontinuous-epigraph-window-exactness}, the epigraph row
$E$ is readable only after those two rows are present.

Apply \autoref{thm:lower-semicontinuous-located-epigraph-transport}. The
located comparison ledger $O$ and structural rows $H,C$ keep the lower-bound
read on the displayed epigraph route under transport and replay.

Finally $P$ and $N$ source and name the same packet. Since no listed carrier
row stores a host liminf operator, quotient equality, selected limit, choice
schedule, compactness principle, or completeness theorem, the readback cannot
escape the displayed route.
\end{proof}

\begin{theorem}[LowerSemicontinuous Real seal boundary]
\label{thm:lower-semicontinuous-real-seal-boundary}
Any $\RealUp$-facing consumer of an accepted $\LowerSemicontinuousUp$ packet
may read the terminal seal only after the $\LowerRealUp$, $\UpperRealUp$,
$\LocatedRealUp$, $\StreamNameUp$, and $\RegSeqRatUp$ rows have been displayed
through $E,O,W,R,H,C,P,N$. The Real-facing boundary therefore records a
finite lower-semicontinuity certificate rather than host topology, semantic
liminf data, quotient real equality, selected representatives, countable
choice, compactness, or ambient completeness.
\end{theorem}
\begin{proof}
Use the NameCert obligation surface of
\autoref{thm:lower-semicontinuous-namecert-obligation-surface}. It requires
source windows, graph data, epigraph rows, finite schedules, regular readback,
located comparison rows, transport, replay, provenance, and local naming.

The lower-real and upper-real rows are displayed inside $E$ and $O$, while
$W$ and $R$ supply the StreamName and RegSeqRat route used to inspect them.
The located comparison surface cannot be skipped because
\autoref{thm:lower-semicontinuous-located-epigraph-transport} keeps the
epigraph row tied to $O,H,C$.

Now apply
\autoref{thm:lower-semicontinuous-regular-readback-nonescape}. It forces every
lower-bound read through $W,R,E,O,H,C,P,N$, so a Real-facing consumer reaches
the terminal seal only after the displayed lower, upper, located, stream, and
regular rows are visible.
\end{proof}

\begin{theorem}[LowerSemicontinuous located readback compatibility]
\label{thm:lowersemicontinuous-located-readback-compatibility}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, every $\RealUp$-facing output read must pass
through the located comparison ledger $O$ before the terminal real seal is
available. Thus source windows, regular rational value rows, lower-real
epigraph data, and upper-side comparison rows may be exported to a real-facing
consumer only along
$$
X,F,W,R,E,O,H,C,P,N .
$$
The output cannot bypass $O$ by invoking host real equality, selected endpoint
representatives, semantic limits, countable choice, open-cover compactness, or
completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Start with a real-facing consumer of $L$. The source, graph, schedule,
readback, and epigraph coordinates are displayed as $X,F,W,R,E$, but none of
them alone supplies a located readback.

Use \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. The
located-readback obligation requires the route to pass through $O$ before a
real-facing output can be read.

Transport and replay then use only $H$ and $C$, and the resulting route is
packaged and named by $P$ and $N$. No additional host coordinate is present,
so the real-facing output remains the stated finite BEDC route.
\end{proof}

\begin{theorem}[LowerSemicontinuous transport replay exactness]
\label{thm:lowersemicontinuous-transport-replay-exactness}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, componentwise $\hsame$ transport and displayed
$\Cont$ replay preserve exactly the rows
$$
X,F,E,W,R,O,H,C,P,N .
$$
They do not add a host topology row, an open-set lattice, quotient equality,
semantic limit data, selected witnesses, countable choice, open-cover
compactness, or ambient completeness. Every transported lower-semicontinuity
read is therefore the same finite carrier route with the same local
$\NameCert_{\LowerSemicontinuousUp}$ row.
\end{theorem}
\begin{proof}
Read the transport and replay ledgers from the carrier. The $H$ row records
componentwise $\hsame$ only for the displayed coordinates, while $C$ records
continuation replay only for the same inspection routes.

Apply \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. Its
replay obligation lists the source, graph, epigraph, readback, comparison,
seal, provenance, and naming rows as the complete transport surface.

It remains to identify what cannot appear after replay. Because
$L=(X,F,E,W,R,O,H,C,P,N)$ has no coordinate for the excluded host principles,
$H$ and $C$ can only preserve the displayed rows and cannot introduce a new
semantic route.
\end{proof}

\begin{theorem}[LowerSemicontinuous NameCert basis obligations]
\label{thm:lowersemicontinuous-namecert-obligation-basis}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, every root-unblock obligation that exposes
lower-real epigraph data to a downstream consumer is a finite row of the same
packet. The basis consists of the $\LowerRealUp$ epigraph ledger $E$, the
$\StreamNameUp$ schedule $W$, the $\RegSeqRatUp$ readback $R$, the
$UpperRealUp$ and $\LocatedRealUp$ comparison rows in $O$, the terminal
$\RealUp$ seal boundary, $\BHist$ histories, $\hsame$ transport, $\Cont$
replay, $\Pkg$ provenance, and the local $\NameCert$ row.

No basis obligation is discharged by host topology, a semantic liminf
operator, quotient real equality, selected limits, countable choice, or
ambient completeness. Epigraph and comparison rows are finite carrier data
rather than host-theoretic evidence.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:lower-semicontinuous-carrier}. The only
epigraph data available to a consumer is the finite ledger $E$, and the only
inspection route to it is through the scheduled windows $W$ and regular
rational readbacks $R$.

The comparison row $O$ records lower-real, upper-real, and located-real
readbacks before the terminal $\RealUp$ seal is exposed. Thus every
root-unblock read remains inside the displayed carrier coordinates.

The structural rows $H,C,P,N$ transport, replay, package, and name the same
finite route. Since the excluded host principles are absent from
$L=(X,F,E,W,R,O,H,C,P,N)$, they cannot serve as basis obligations.
\end{proof}

\begin{theorem}[LowerSemicontinuous Real seal nonescape]
\label{thm:lowersemicontinuous-real-seal-nonescape}
Let $L=(X,F,E,W,R,O,H,C,P,N)$ be an accepted
$\LowerSemicontinuousUp$ carrier. Any $\RealUp$ readback from $L$ must pass
through the $\LowerRealUp$ epigraph row $E$, the $\StreamNameUp$ schedule
$W$, the $\RegSeqRatUp$ readback $R$, the $\UpperRealUp$ and
$\LocatedRealUp$ comparisons in $O$, the $\BHist$ history rows, $\hsame$
transport, $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row.

The $\RealUp$ seal is therefore a finite carrier boundary. It is not a route
to host topology, a semantic limit, quotient real equality, selected limits,
countable choice, open-cover compactness, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$-facing consumer of $L$. By
\autoref{def:lower-semicontinuous-carrier}, the consumer can inspect only the
displayed source, graph, epigraph, schedule, readback, comparison, transport,
replay, provenance, and naming rows.

Apply \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. Its
non-escape obligation places the terminal real seal downstream from
epigraph-window exactness, lower-real classifier stability, located readback
compatibility, and replay.

Hence a real readback cannot detach from $E,W,R,O,H,C,P,N$. The excluded
principles have no coordinate in the carrier and no continuation row that
could introduce them.
\end{proof}

\begin{theorem}[LowerSemicontinuous UpperReal handoff]
\label{thm:lowersemicontinuous-upperreal-handoff}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, every $\UpperRealUp$ comparison handed to a
downstream lower-semicontinuity consumer is read from the same comparison
ledger $O$ that also records the $\LowerRealUp$, $\LocatedRealUp$, and
$\RealUp$ readbacks. The handoff preserves the $\StreamNameUp$ schedule,
$\RegSeqRatUp$ value windows, $\BHist$ histories, $\hsame$ transport, $\Cont$
replay, $\Pkg$ provenance, and local $\NameCert$ naming of the carrier.

Thus upper-side comparison is finite BEDC data paired with lower-real
epigraph rows. It is not an ambient order-completeness principle, a host
topology assertion, a semantic upper envelope, quotient real equality, a
selected limit, countable choice, or completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Read the comparison ledger from
\autoref{def:lower-semicontinuous-carrier}. The row $O$ is the only carrier
coordinate that contains upper-real comparison data, and it is tied to the
same lower-real and located-real checks used by epigraph reads.

The schedule and readback rows $W$ and $R$ determine which finite value
windows the comparison may inspect. Transport through $H$ and replay through
$C$ preserve those windows together with the epigraph and comparison rows.

The provenance and local name rows $P,N$ certify this as a
$\LowerSemicontinuousUp$ handoff. Since the carrier has no coordinate for the
excluded host principles, the $\UpperRealUp$ consumer receives only the
finite comparison surface stated above.
\end{proof}

\begin{theorem}[Lower-real epigraph route]
\label{thm:lower-semicontinuous-lowerreal-epigraph-route}
Every lower-real or real-seal consumer of an accepted
$\LowerSemicontinuousUp$ carrier factors through the finite epigraph route
$$
X,F,W,R,E,O,H,C,P,N .
$$
The consumer may inspect scheduled source windows, regular rational value
readbacks, displayed lower-bound rows, lower-real refinements, located
endpoint checks, componentwise transports, continuation replay, provenance,
and local naming rows. It cannot bypass the epigraph ledger to read host
topological openness, quotient real equality, a semantic liminf operator,
countable choice, open-cover compactness, or completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Start from a real-facing consumer of the packet. The source row $X$ and graph
row $F$ are visible only through the finite schedule $W$, so every value
inspection begins with a displayed source window rather than an ambient
neighbourhood.

The regular rational readback row $R$ then supplies the finite value window.
The epigraph ledger $E$ records the lower-bound row $(x,q)$ attached to that
same inspection, and the comparison ledger $O$ checks lower-real refinements,
upper-side exclusions, and located endpoint compatibility.

Transport and replay are exhausted by $H$ and $C$. They move the source,
graph, readback, epigraph, comparison, and seal rows together, so the route
remains the same after classifier transport.

The package and local name rows $P,N$ record exactly this route for consumers.
Since the excluded host principles are absent from the route and absent from
the carrier coordinates, the lower-real epigraph handoff exposes only the
finite BEDC rows stated above.
\end{proof}

\begin{theorem}[LowerSemicontinuous located readback stability]
\label{thm:lower-semicontinuous-located-readback-stability}
Let $L=(X,F,E,W,R,O,H,C,P,N)$ be an accepted
$\LowerSemicontinuousUp$ carrier. Every epigraph-window comparison accepted by
$E$ and transported by $H$ preserves the $\LocatedRealUp$ endpoint checks in
$O$ before any $\RealUp$-facing consumer can read the transported lower bound.
Equivalently, a consumer that receives a transported row $(x,q)$ must pass
through the same scheduled window in $W$, the same regular rational readback in
$R$, and the located endpoint ledger in $O$ before the terminal real-seal route
is available.
\end{theorem}
\begin{proof}
Project the carrier rows from \autoref{def:lower-semicontinuous-carrier}. The
only accepted lower-bound comparisons are the finite epigraph rows in $E$, and
the only transport available for those rows is the componentwise $\hsame$
ledger $H$.

Apply \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route}. Its route
places $W$ and $R$ before $E$, and places the lower-real, upper-real, and
located-real comparison ledger $O$ before any terminal $\RealUp$ seal can be
read.

Thus the transported comparison cannot expose a bound by itself. The located
endpoint checks in $O$ remain on the route after transport, and $C$ replays the
same scheduled inspection for every Real-facing consumer.
\end{proof}

\begin{theorem}[LowerSemicontinuous Real seal nonescape]
\label{thm:lower-semicontinuous-real-seal-nonescape}
An accepted $\LowerSemicontinuousUp$ packet exports $\RealUp$-facing data only
through the displayed rows
$$
E,W,R,O,H,C,P,N .
$$
In particular, the packet cannot expose host topology, a semantic liminf
operator, quotient real equality, a selected limit, countable choice,
open-cover compactness, or ambient completeness as a route to the terminal
real seal.
\end{theorem}
\begin{proof}
Read the export surface from \autoref{def:lower-semicontinuous-carrier}. The
terminal real-facing route is represented by epigraph rows, scheduled windows,
regular rational readbacks, comparison rows, componentwise transport,
continuation replay, package provenance, and the local name.

Apply \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route}. The theorem
states that every lower-real or real-seal consumer factors through the finite
epigraph route and cannot bypass it to host topological openness, quotient
real equality, semantic liminf data, countable choice, open-cover compactness,
or completeness of $\RealUp$.

The listed excluded principles are not carrier coordinates and are not
introduced by $H$ or $C$. Therefore the $\RealUp$ seal row remains a finite
BEDC export through $E,W,R,O,H,C,P,N$ rather than a host-theoretic escape.
\end{proof}

\begin{theorem}[LowerSemicontinuous Baire-one source handoff]
\label{thm:lower-semicontinuous-baireone-source-handoff}
Let $L=(X,F,E,W,R,O,H,C,P,N)$ be an accepted
$\LowerSemicontinuousUp$ carrier. Any $\BaireOneFunctionUp$ source read that
uses $L$ as its lower-semicontinuous boundary must first pass through the
$\ContinuousMapUp$ graph row $F$, the $\StreamNameUp$ schedule row $W$, the
$\RegSeqRatUp$ readback row $R$, the epigraph ledger $E$, and the comparison
ledger $O$ before the structural rows $H,C,P,N$ may hand the read to a
$\RealUp$-facing consumer. The handoff supplies finite epigraph data only; it
does not supply a host pointwise limit, quotient equality of functions, a
selected approximating sequence, or semantic topology.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:lower-semicontinuous-carrier}. The only
map-facing coordinate is $F$, and it is tied to the scheduled windows $W$ and
regular rational readbacks $R$ before a lower-bound row can be inspected.

Apply \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. Its
epigraph-window exactness and located readback clauses force the
$\BaireOneFunctionUp$ source handoff through $E,W,R,O$ rather than through an
ambient pointwise-limit predicate.

Finally use \autoref{thm:lower-semicontinuous-real-seal-nonescape}. The
structural rows $H,C,P,N$ replay and name the same finite route before the
$\RealUp$ seal is visible, so no selected approximating sequence, quotient
function equality, or host topology is exported.
\end{proof}

\begin{theorem}[LowerSemicontinuous Real and regular-rational scope]
\label{thm:lower-semicontinuous-real-regseqrat-scope}
For an accepted $\LowerSemicontinuousUp$ carrier
$L=(X,F,E,W,R,O,H,C,P,N)$, the $\RegSeqRatUp$ and $\RealUp$ scope is exactly the
route that reads a finite schedule from $W$, regular rational value data from
$R$, lower-bound evidence from $E$, comparison data from $O$, and then the
transport, replay, provenance, and local name rows $H,C,P,N$. Thus a
$\RegSeqRatUp$ or $\RealUp$ consumer receives the epigraph-ledger route, not a
semantic liminf operation, quotient real equality, selected limit, countable
choice, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the root carrier route. The rows $W$ and $R$ determine the finite
windows and regular rational values that can be read before any lower-bound
claim is visible.

Use \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route}. It places the
epigraph ledger $E$ and comparison ledger $O$ downstream of the schedule and
readback rows, and upstream of any real-facing seal.

Now apply \autoref{thm:lower-semicontinuous-located-readback-stability} and
\autoref{thm:lower-semicontinuous-real-seal-nonescape}. Transport and replay
preserve the same route, while the seal theorem excludes liminf semantics,
quotient equality, selected limits, countable choice, and ambient completeness
from the $\RegSeqRatUp$ and $\RealUp$ scope.
\end{proof}

\begin{theorem}[LowerSemicontinuous epigraph-ledger refusal]
\label{thm:lower-semicontinuous-epigraph-ledger-refusal}
No accepted $\LowerSemicontinuousUp$ packet lets a consumer read
$\BaireOneFunctionUp$, $\ContinuousMapUp$, $\StreamNameUp$, $\RegSeqRatUp$, or
$\RealUp$ data while bypassing the epigraph rows $E,W,R,O,H,C,P,N$. A purported
consumer that reaches a Baire-one source handoff, a continuous-map graph row, a
regular rational readback, or a terminal real seal without those rows is refused
by the local NameCert obligation surface.
\end{theorem}
\begin{proof}
Read the purported consumer against the carrier. The graph row $F$ has no
standalone export path: every lower-semicontinuous read proceeds through
scheduled windows, regular rational readbacks, epigraph rows, and comparison
rows.

Apply \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. Carrier
admission, epigraph-window exactness, located readback compatibility, replay,
provenance, and non-escape are all obligations on the same packet.

Finally combine the Baire-one handoff and the Real--regular-rational scope
theorems above. They identify the only visible source and seal routes with
$E,W,R,O,H,C,P,N$, so any route omitting one of those rows has no accepted
NameCert read.
\end{proof}

\begin{definition}[LowerSemicontinuous root carrier]
\label{def:lowersemicontinuous-root-carrier}
The root packet for $\LowerSemicontinuousUp$ is the accepted finite carrier
$$
L_{\mathrm{root}}=(X,F,E,W,R,O,H,C,P,N)
$$
of \autoref{def:lower-semicontinuous-carrier}, read with $X$ as the displayed
source row, $F$ as the graph row, $E$ as the lower-real epigraph ledger, $W$ as
the stream schedule, $R$ as the regular rational readback row, $O$ as the
lower-real, upper-real, located-real, and real-seal comparison ledger, $H$ as
componentwise transport, $C$ as displayed replay, $P$ as provenance, and $N$ as
the local NameCert row. A root consumer may inspect only these rows and the
routes certified by \autoref{thm:lower-semicontinuous-namecert-obligation-surface};
it receives no separate topology carrier, semantic liminf operation, quotient
real equality, selected limit, countable choice, open-cover compactness, or
ambient completeness principle.
\end{definition}

\begin{theorem}[LowerSemicontinuous real handoff]
\label{thm:lowersemicontinuous-real-handoff}
Every $\RealUp$-facing read of the root packet
$L_{\mathrm{root}}=(X,F,E,W,R,O,H,C,P,N)$ factors through the displayed
$\StreamNameUp$, $\RegSeqRatUp$, $\LowerRealUp$, $\LocatedRealUp$, and
$\RealUp$ rows. Concretely, a consumer first reads a stream window from $W$,
then a regular rational value row from $R$, then a lower-real epigraph witness
from $E$, then the located comparison data in $O$, and only then the terminal
real-seal route recorded by $O,H,C,P,N$.
\end{theorem}
\begin{proof}
The root packet is the carrier of
\autoref{def:lowersemicontinuous-root-carrier}, so a consumer can start only
from the rows $X,F,E,W,R,O,H,C,P,N$.

Apply \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. Its
obligation surface places carrier admission, epigraph-window exactness,
lower-real classifier stability, located readback compatibility, transport
replay, provenance, and non-escape on the same local NameCert route.

Apply \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route}. That route
orders the read through scheduled windows, regular rational readbacks,
displayed lower-bound rows, lower-real refinements, located endpoint checks,
transport, replay, provenance, and local naming.

Finally apply
\autoref{thm:lower-semicontinuous-located-readback-stability} and
\autoref{thm:lower-semicontinuous-real-seal-nonescape}. They keep the located
readback before the terminal real seal and exclude every host route not present
in the finite packet.
\end{proof}

\begin{theorem}[LowerSemicontinuous open-sublevel route]
\label{thm:lowersemicontinuous-open-sublevel-route}
Every sublevel or open-window read of the root packet
$L_{\mathrm{root}}=(X,F,E,W,R,O,H,C,P,N)$ is a displayed epigraph route through
$E,W,R,O,H,C,P,N$. It is not a read of host topological openness: the only
available witness is a finite lower-bound row transported through the
$\LowerRealUp$ and $\LocatedRealUp$ comparison ledgers and replayed by the same
continuation route.
\end{theorem}
\begin{proof}
Start with a sublevel or open-window consumer of the root packet. By
\autoref{def:lowersemicontinuous-root-carrier}, the packet has no coordinate
for a topology carrier or open-set lattice, so the consumer must read one of
the displayed finite rows.

Use \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route}. The theorem
identifies the lower-real route as
$$
X,F,W,R,E,O,H,C,P,N .
$$
Thus an open-window read can only mean that a scheduled source window and a
regular rational value row have reached a displayed epigraph witness in $E$.

The located readback stability theorem keeps the comparison in $O$ on the same
route after transport. The real-seal nonescape theorem then prevents the
consumer from replacing that displayed epigraph route by host topology,
semantic liminf data, quotient real equality, choice, compactness, or ambient
completeness.
\end{proof}

\begin{definition}[LowerSemicontinuous closed-superlevel carrier]
\label{def:lowersemicontinuous-closed-superlevel-carrier}
A closed-superlevel row for the root packet
$L_{\mathrm{root}}=(X,F,E,W,R,O,H,C,P,N)$ is a finite $\BHist$ packet
$$
S=(q,E_q,O_q,B_q,H_q,C_q,P_q,N_q)
$$
where $q$ is the rational threshold being tested, $E_q$ is the lower-real
epigraph window read from $E$ at threshold $q$, $O_q$ is the $\RealUp$-seal and
$\LocatedRealUp$ comparison route attached to the same threshold, $B_q$ is the
$\BHist$ evidence that the complement of the displayed sublevel window remains
stable under the shown $\hsame$ and $\Cont$ transports, and $H_q,C_q,P_q,N_q$
transport, replay, source, and name the same threshold row. The row records a
constructive complement boundary for the finite lower-real window; it does not
assert classical topological closedness of a host superlevel set.
\end{definition}

\begin{theorem}[LowerSemicontinuous closed-superlevel stability]
\label{thm:lowersemicontinuous-closed-superlevel-stability}
For every accepted closed-superlevel row
$$
S=(q,E_q,O_q,B_q,H_q,C_q,P_q,N_q)
$$
attached to $L_{\mathrm{root}}$, transport by the displayed $\hsame$ rows and
replay by the displayed $\Cont$ route preserves the finite superlevel
complement boundary determined by $q$. Equivalently, a consumer that avoids the
open-sublevel window at threshold $q$ may keep that avoidance only through the
lower-real epigraph row $E_q$, the located readback route $O_q$, the $\RealUp$
seal data, and the stability evidence $B_q$; it cannot replace them by host
closedness, semantic liminf data, quotient real equality, countable choice,
open-cover compactness, or ambient completeness.
\end{theorem}
\begin{proof}
Project the closed-superlevel carrier. Its threshold is the displayed rational
$q$, and all boundary information is stored in $E_q,O_q,B_q,H_q,C_q,P_q,N_q$.
There is no coordinate for a host topological closed set.

Apply \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route}. The
threshold row $E_q$ is read only through the lower-real epigraph window
attached to the original root packet, after the scheduled source windows and
regular rational value rows have been displayed.

Use \autoref{thm:lower-semicontinuous-located-readback-stability}. The located
comparison row $O_q$ remains on the same route under the componentwise
$\hsame$ transport and the displayed $\Cont$ replay. Hence the complement of
the open-sublevel window is carried by $B_q$ as finite transport evidence, not
as a detached topological predicate.

Finally apply \autoref{thm:lowersemicontinuous-open-sublevel-route} together
with \autoref{thm:lower-semicontinuous-real-seal-nonescape}. The open-sublevel
route identifies the boundary being avoided, and the real-seal nonescape row
prevents the consumer from substituting classical closedness, semantic liminf
data, quotient real equality, countable choice, compactness, or ambient
completeness for the displayed finite boundary.
\end{proof}

\begin{theorem}[LowerSemicontinuous Baire-window factorization]
\label{thm:lowersemicontinuous-baire-window-factorization}
Every Baire-one or lower-real consumer of an accepted $\LowerSemicontinuousUp$ packet $L=(X,F,E,W,R,O,H,C,P,N)$ factors its finite request through the route
$$
W \longmapsto R \longmapsto E \longmapsto O
$$
before any $\RealUp$-facing seal is read. The consumer cannot replace that route by host topology, semantic liminf data, quotient equality, selected limits, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier rows from \autoref{def:lower-semicontinuous-carrier}. The finite request first chooses the inspected windows in $W$, then reads regular rational data from $R$, then reaches the lower-real epigraph ledger $E$, and only then enters the located comparison row $O$.

Use epigraph exactness and located readback compatibility, \autoref{thm:lowersemicontinuous-epigraph-window-exactness} and \autoref{thm:lowersemicontinuous-located-readback-compatibility}. These theorems keep lower-bound reads and real-facing comparison data on the displayed route rather than on a host liminf or topology predicate.

Finally apply closed-superlevel stability from \autoref{thm:lowersemicontinuous-closed-superlevel-stability}. The open-sublevel and closed-superlevel boundary reads remain finite BEDC rows, so a Baire-one or lower-real consumer receives exactly the $W,R,E,O$ factorization before any terminal seal is available.
\end{proof}

\begin{theorem}[LowerSemicontinuous kernel scope]
\label{thm:lowersemicontinuous-kernel-scope}
Every lower-semicontinuous epigraph, located-readback, or Real-seal consumer of an accepted $\LowerSemicontinuousUp$ packet must route through the visible $\BHist$, $\StreamNameUp$, $\RegSeqRatUp$, $\LowerRealUp$, $\UpperRealUp$, $\LocatedRealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the carrier. The route may read epigraph windows, open-sublevel boundaries, closed-superlevel stability, transport replay, and Real handoff data, but it cannot replace those rows by host topology, semantic liminf data, quotient real equality, countable choice, compactness, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the NameCert obligation surface of \autoref{thm:lower-semicontinuous-namecert-obligation-surface}. It lists the finite source, graph, epigraph, window, readback, located comparison, transport, replay, provenance, and local naming rows that any consumer must expose.

Apply epigraph exactness and the epigraph-window route, \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route} and \autoref{thm:lowersemicontinuous-open-sublevel-route}. These results keep lower-real and sublevel reads inside the displayed $\BHist$, $\StreamNameUp$, $\RegSeqRatUp$, $\LowerRealUp$, and $\UpperRealUp$ rows.

Next use located-readback stability and transport replay. The theorems \autoref{thm:lower-semicontinuous-located-readback-stability} and \autoref{thm:lowersemicontinuous-transport-replay-exactness} keep the $\LocatedRealUp$, $\hsame$, and $\Cont$ rows visible when a comparison is moved or replayed.

Finally apply the Real handoff and nonescape statements, \autoref{thm:lowersemicontinuous-real-handoff} and \autoref{thm:lower-semicontinuous-real-seal-nonescape}. They force every Real-facing read through the same $\Pkg$ and $\NameCert$ rows and exclude host topology, semantic liminf data, quotient real equality, countable choice, compactness, and ambient completeness.
\end{proof}

\begin{closurestatus}{\LowerSemicontinuousUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lower-semicontinuous-carrier}, \autoref{thm:lower-semicontinuous-namecert-obligation-surface}, and \autoref{thm:lower-semicontinuous-lowerreal-epigraph-route} seed the finite lower-semicontinuity certificate over lower-real epigraph windows, located readbacks, stream schedules, regular rational value rows, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{The chapter does not close host topological openness, semantic liminf operators, quotient real equality, countable choice, open-cover compactness, or completeness of $\RealUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, epigraph-window exactness, lower-real classifier stability, located readback compatibility, transport replay, provenance, and real-seal non-escape for the same packet.}
  \constructivestory{The construction starts from finite source windows, reads regular rational value rows, records lower-real epigraph witnesses, transports them through hsame and Cont ledgers, checks located readbacks, and hands the accepted route to Real-facing consumers without importing host topology.}
\end{closurestatus}
