\chapter{A Concrete Naming Certificate for $\DedekindUp$}
\label{ch:concrete-instances-dedekind-namecert}
\origin{human}

The Dedekind-domain interface $\DedekindUp$ packages an integrally closed Noetherian commutative domain in which every nonzero prime ideal is maximal. It depends on $\NameCert_{\CommRingUp}$ (\autoref{ch:concrete-instances-commring-namecert}) and $\NameCert_{\IdealUp}$ (\autoref{ch:concrete-instances-ideal-namecert}).

\section{Carrier definition}
\label{sec:dedekind-carrier}

\begin{theorem}[Dedekind source obligation]\label{thm:dedekind-source-obligation}
A $\DedekindUp$ source consists of a shared $\mathsf{BHist}$ carrier and classifier equipped with the cited $\NameCert_{\CommRingUp}$ and $\NameCert_{\IdealUp}$ surfaces. The commutative-ring certificate fixes the visible ring package, and the ideal certificate is read over the same carrier and classifier rather than over a second ambient presentation.
\end{theorem}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_shared\_source\_obligation}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_source\_obligation}
\begin{proof}
Unpack the seed boundary for $\DedekindUp$: the seed already names the $\CommRingUp$ source and the $\IdealUp$ source as required inputs. The roadmap ten-field template then asks first for a carrier and classifier surface before any domain law can be read.

Those two inputs must therefore share the same $\mathsf{BHist}$ carrier and the same classifier transport. The proof records only this interface shape: it does not assert that the Dedekind certificate fields have been constructed.
\end{proof}

\begin{theorem}[Dedekind domain-law obligation]\label{thm:dedekind-domain-law-obligation}
For the shared $\DedekindUp$ classifier, the domain-specific rows are integrally closedness, Noetherianity, and the assertion that every nonzero prime ideal is maximal. Each row is a certificate field over the shared classifier, with its own witness and stability requirement.
\end{theorem}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_domain\_law\_obligation}
\begin{proof}
The seed closure lists the integrally closed row, the Noetherian row, and the nonzero-prime-maximal row as the precise domain obligations. The roadmap ten-field template turns each listed row into visible data: a field, a witness, and classifier stability.

Since the carrier and ideal classifier have already been fixed by the source obligation, the three domain laws cannot be supplied as detached host properties. They must be read as certificate rows over that same BEDC classifier.
\end{proof}

\begin{theorem}[Dedekind Noetherian source factorization]\label{thm:dedekind-noetherian-source-factorization}
For any accepted $\DedekindUp$ packet, the Noetherian witness row of \autoref{thm:dedekind-domain-law-obligation} factors through the $\NoetherianRingUp$ carrier of \autoref{def:noetherian-ring-carrier} over the same $\CommRingUp$ and $\IdealUp$ classifier. The integrally closed row and the nonzero-prime-maximal row remain Dedekind-specific rows over that shared classifier.
\end{theorem}
\begin{proof}
Project the $\DedekindUp$ source obligation from \autoref{thm:dedekind-source-obligation}. It fixes the commutative-ring source and the ideal source before the domain-law rows are read, so the Noetherian row has the same ambient carrier and classifier required by the $\NoetherianRingUp$ carrier.

Apply \autoref{thm:noetherian-ring-namecert-obligations} to read the Noetherian witness as finite ideal-chain stabilization data over those two source rows. The $\DedekindUp$ packet therefore consumes the reusable $\NoetherianRingUp$ surface rather than treating Noetherianity as an isolated internal row.

The remaining two domain-law rows are not absorbed by $\NoetherianRingUp$. Integrally closedness and nonzero-prime-maximality are projected from \autoref{thm:dedekind-domain-law-obligation} and stay attached to the Dedekind classifier as the Dedekind-specific part of the packet.
\end{proof}

\begin{theorem}[Dedekind classifier ledger obligation]\label{thm:dedekind-classifier-ledger-obligation}
Classifier transport and the $\DedekindUp$ ledger expose exactly the commutative-ring source, the ideal source, the integrally closed witness, the Noetherian witness, and the nonzero-prime-maximal witness. The ledger exposes no quotient data, no classical-choice data, and no $\StdBridge$ data.
\end{theorem}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_classifier\_ledger\_obligation}
\begin{proof}
Unpack the exact-ledger boundary in the seed closure. Its upgrade path names the commutative-ring source, ideal source, three domain-law witnesses, classifier transport, and ledger boundary as the full local inventory.

The roadmap ten-field template then separates local certificate data from quotient, classical, and standard-bridge comparisons. The theorem therefore fixes the exposed ledger shape without claiming a completed $\NameCert_{\DedekindUp}$.
\end{proof}

\section{The certificate}
\label{sec:dedekind-certificate}

\begin{theorem}[Dedekind scoped certificate packet]\label{thm:dedekind-scoped-certificate-packet}
The scoped $\DedekindUp$ certificate packet consists exactly of the shared $\mathsf{BHist}$ carrier and classifier, the cited $\NameCert_{\CommRingUp}$ and $\NameCert_{\IdealUp}$ surfaces, the integrally closed row, the Noetherian row, the nonzero-prime-maximal row, classifier transport, and the exact $\DedekindUp$ ledger boundary. This packet is scoped over the existing NameCert, CommRing, and Ideal primitives, and it contains no quotient presentation, no classical-choice datum, and no completed public $\NameCert_{\DedekindUp}$ surface.
\end{theorem}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_scoped\_certificate\_packet}
\begin{proof}
Apply \autoref{thm:dedekind-source-obligation} to fix the shared $\mathsf{BHist}$ carrier, the classifier, and the two cited source surfaces. Apply \autoref{thm:dedekind-domain-law-obligation} to read integrally closedness, Noetherianity, and nonzero-prime-maximality as rows over that same classifier.

Apply \autoref{thm:dedekind-classifier-ledger-obligation} to identify the classifier transport and exact ledger boundary. Unpacking the roadmap ten-field template then packages these rows as the scoped local certificate inventory.

The scoped packet itself is not yet the exported public certificate surface for $\NameCert_{\DedekindUp}$. It is the local inventory from which that surface is assembled, and it does not pass through quotient representatives or classical choice.
\end{proof}

\begin{theorem}[Dedekind certificate stability rows]\label{thm:dedekind-certificate-stability-rows}
Over the shared $\mathsf{BHist}$ carrier and classifier fixed by \autoref{thm:dedekind-source-obligation}, the integrally closed row, the Noetherian row, and the nonzero-prime-maximal row of \autoref{thm:dedekind-domain-law-obligation} are classifier-stable $\DedekindUp$ certificate rows. Each row is transported only along the same classifier used by the $\NameCert_{\CommRingUp}$ and $\NameCert_{\IdealUp}$ source surfaces, so no row is read over a detached carrier or a second classifier.
\end{theorem}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_certificate\_stability\_rows}
\begin{proof}
Begin with the shared carrier and classifier supplied by \autoref{thm:dedekind-source-obligation}. That theorem fixes the $\mathsf{BHist}$ presentation before any domain-law row is interpreted.

Apply \autoref{thm:dedekind-domain-law-obligation} to identify the three domain rows as certificate fields over that same classifier. Their witnesses are therefore stability data for the displayed $\DedekindUp$ packet, not external predicates attached after the carrier has been chosen.

The conclusion is classifier stability row by row: integrally closedness, Noetherianity, and nonzero-prime-maximality all move only through the classifier already shared by the commutative-ring and ideal source surfaces.
\end{proof}

\begin{theorem}[Dedekind exact ledger public surface]\label{thm:dedekind-exact-ledger-public-surface}
The public $\DedekindUp$ ledger exposes exactly the $\CommRingUp$ source, the $\IdealUp$ source, the integrally closed witness, the Noetherian witness, the nonzero-prime-maximal witness, classifier transport, and the exact $\DedekindUp$ ledger boundary. It exposes no quotient data, no classical-choice data, and no $\StdBridge$ data.
\end{theorem}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_exact\_ledger\_public\_surface}
\begin{proof}
Apply \autoref{thm:dedekind-classifier-ledger-obligation}. Its ledger boundary names the commutative-ring source, the ideal source, the three domain witnesses, and classifier transport as the visible inventory.

Exactness is read negatively as well as positively. The same ledger theorem excludes quotient representatives, classical-choice witnesses, and $\StdBridge$ fields from the $\DedekindUp$ certificate surface.

Thus the public ledger has exactly the displayed rows: every named row is exposed, and every excluded kind of host or bridge data remains outside the surface.
\end{proof}

\begin{theorem}[Dedekind public NameCert surface]\label{thm:dedekind-public-namecert-surface}
The public $\NameCert_{\DedekindUp}$ surface over the concrete $\mathsf{BHist}$ carrier and the same classifier is assembled from \autoref{thm:dedekind-source-obligation}, \autoref{thm:dedekind-domain-law-obligation}, \autoref{thm:dedekind-classifier-ledger-obligation}, \autoref{thm:dedekind-certificate-stability-rows}, and \autoref{thm:dedekind-exact-ledger-public-surface}. Its exported rows are exactly the shared $\CommRingUp$ and $\IdealUp$ source surfaces, the three classifier-stable domain witnesses, classifier transport, and the exact ledger boundary.
\end{theorem}
\leanchecked{BEDC.Derived.DedekindUp.DedekindSingleton\_public\_namecert\_surface}
\begin{proof}
First fix the public carrier data. Apply \autoref{thm:dedekind-source-obligation} to obtain the concrete $\mathsf{BHist}$ carrier, the common classifier, and the two source surfaces.

Next fix the domain content. Apply \autoref{thm:dedekind-domain-law-obligation} and \autoref{thm:dedekind-certificate-stability-rows} to read integrally closedness, Noetherianity, and nonzero-prime-maximality as classifier-stable certificate rows over that same carrier.

Finally apply \autoref{thm:dedekind-classifier-ledger-obligation} and \autoref{thm:dedekind-exact-ledger-public-surface}. These identify the transport and exact ledger rows, exclude quotient, classical-choice, and $\StdBridge$ data, and repack the displayed inventory as the public $\NameCert_{\DedekindUp}$ surface.
\end{proof}

\closureat{DedekindUp}{matureStr}[BEDC.Derived.DedekindUp.DedekindSingleton\_public\_namecert\_surface]

\begin{closurestatus}{\DedekindUp}
  \constructivestory{A Dedekind domain is carried by a shared $\mathsf{BHist}$ source where the $\CommRingUp$ surface and the $\IdealUp$ surface use the same carrier and classifier before the domain-law rows are attached. The carrier accepts exactly that shared commutative-ring and ideal source together with the integrally closed, Noetherian, and nonzero-prime-maximal witness rows, while quotient presentations, classical-choice data, and standard-bridge fields are absent from the packet. Two accepted presentations classify together only through the same classifier used by the CommRing and Ideal source surfaces, and each of the three domain-law rows must be stable under that classifier. The source specification is the paired CommRing and Ideal dependency surface, the pattern specification is the three visible domain-law witnesses over that surface, and the ledger exposes exactly those sources, witnesses, classifier-transport rows, and exact boundary rows. The five naming-certificate obligations are arranged by the public surface: the shared carrier gives an inhabitant, $\hsame$ and the inherited classifier rows give reflexivity, symmetry, and transitivity, and classifier stability repacks any transported domain-law witness inside the same accepted carrier. A history $h$ lies in the signature GAP of a $\DedekindUp$ token $p$ when the source accepts $h$, the signature relation pairs it to an answer Dedekind packet and evidence ledger, and token introduction names that answer as $p$; concretely, the CommRing source, Ideal source, integrally closed row, Noetherian row, prime-maximal row, transport rows, and ledger boundary must all be the displayed rows for $h$. The chapter registers this construction as $\DedekindUp$ without adding a quotient construction, a classical-choice presentation, a standard bridge, or a separate verification target.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The paper-side scope is the public $\NameCert_{\DedekindUp}$ surface in \autoref{thm:dedekind-public-namecert-surface}, grounded by the shared-source row, the three domain-law rows, classifier stability, classifier transport, and the exact ledger boundary.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.DedekindUp.DedekindSingleton\_public\_namecert\_surface}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a Lean verification target, standard bridge, quotient construction, or classical-choice presentation.}
  \upgradepath{No further paper theory-axis upgrade is recorded for this chapter; bridge verification remains a separate axis.}
\end{closurestatus}
