\chapter{A Concrete Naming Certificate for $\IsometryExtensionUp$}
\label{ch:concrete-instances-isometryextension-namecert}
\origin{human}

Following Bishop and Bridges constructive completion and the standard extension theorem for isometries on dense subspaces, the $\IsometryExtensionUp$ packet records the finite BEDC surface by which a dense isometric embedding extends across an L10 completion route. It sits after the dense completion entry of \autoref{ch:concrete-instances-completionembedding-namecert}, the displayed distance-reflection route of \autoref{ch:concrete-instances-isometric-embedding-namecert}, the extension-and-uniqueness surface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, and the unit boundary of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}. The packet also fixes the finite name route through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}; it is a named obligation surface, not a quotient-completion construction.

\begin{definition}[IsometryExtension carrier]
\label{def:isometry-extension-carrier}
An $\IsometryExtensionUp$ carrier is a finite $\BHist$ packet
$$
E=(X,Y,J,I,U,W,R,S,A,L,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source metric row together with the dense source reads admitted by the $\CompletionEmbeddingUp$ packet.
\item $Y$ is the target completion-facing metric row whose target reads are reached through displayed completion evidence.
\item $J$ is the dense completion embedding row, read through $\CompletionEmbeddingUp$ rather than through a host inclusion map.
\item $I$ is the distance-preserving graph row supplied by $\IsometricEmbeddingUp$.
\item $U$ is the $\CompletionUniversalPropertyUp$ extension-and-uniqueness row attached to the same dense source and target route.
\item $W$ is the $\CauchyCompletionUnitUp$ unit row that admits source points into the completion-facing surface.
\item $R$ is the $\RegSeqRatUp$ regular rational Cauchy name row used by the source completion read.
\item $S$ is the $\StreamNameUp$ finite window row used to inspect the displayed regular Cauchy name.
\item $A$ is the $\RealUp$ distance and seal row reached after the stream-window and regular-rational rows have been read.
\item $L$ records componentwise $\hsame$ transport for the source, target, dense embedding, isometry, universal-property, unit, stream, regular-rational, and real-seal rows.
\item $C$ records displayed $\Cont$ replay through $X,Y,J,I,U,W,R,S,A,L$.
\item $P$ is the $\Pkg$ provenance over $\CompletionEmbeddingUp$, $\IsometricEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\CauchyCompletionUnitUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\IsometryExtensionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, countable choice, open-cover compactness, or completeness of $\RealUp$.
\end{definition}

\begin{theorem}[IsometryExtension NameCert obligations]
\label{thm:isometry-extension-namecert-obligations}
For an accepted $\IsometryExtensionUp$ carrier $E=(X,Y,J,I,U,W,R,S,A,L,C,P,N)$, the local $\NameCert_{\IsometryExtensionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed source, target, dense embedding, isometry, universal-property, unit, stream-window, regular-rational, real-seal, transport, continuation, provenance, and local naming rows;
\item dense-source compatibility, requiring every extension read to enter through $J$ and the unit row $W$ before any target completion-facing row is consumed;
\item isometric distance preservation, requiring each source-distance read to pass through $I$ and then through the $\RealUp$ row $A$;
\item universal-property extension, requiring the extension candidate and its uniqueness ledger to be read only through $U$ over the same dense isometric route;
\item finite-name handoff, requiring stream windows $S$ and regular rational names $R$ to be displayed before the real-seal row $A$ is consumed;
\item ledger non-escape, stating that $L,C,P,N$ expose no quotient completion equality, selected representatives, countable choice, open-cover compactness, or completeness of $\RealUp$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:isometry-extension-carrier}. The tuple lists exactly the source and target rows, dense embedding row, isometry row, universal-property row, unit row, finite-name rows, real-seal row, and structural BEDC rows available to the certificate.

Dense-source compatibility is read from $J$ and $W$. The completion embedding supplies the dense source image, and the unit row is the only admission route from a displayed source point into the completion-facing surface.

Distance preservation is then forced by $I$ and $A$. The isometry row records the distance-reflection route, while the real-seal row records the terminal distance observation after the source stream and regular-rational names have been displayed.

The universal-property obligation is local to $U$. Since $U$ is attached to the same $J,I,W,R,S,A$ route, extension existence and uniqueness can be read only as a ledger over those displayed rows.

Finally inspect $L,C,P,N$. Transport is componentwise, replay follows the displayed route, and provenance names only the listed sibling packets. Hence the excluded quotient, representative-choice, countability, compactness, and real-completeness principles have no row from which a consumer could read them.
\end{proof}

\begin{theorem}[IsometryExtension completion handoff]
\label{thm:isometry-extension-completion-handoff}
Every completion-facing consumer of an accepted $\IsometryExtensionUp$ carrier factors through the displayed route
$$
X,J,W\longmapsto R,S\longmapsto I,A\longmapsto U\longmapsto Y .
$$
Thus the extension reaches the target completion-facing row only after the dense completion embedding, unit admission, finite stream and regular-rational name rows, real-distance seal, and universal-property extension ledger have been replayed inside the same packet.
\end{theorem}
\begin{proof}
Begin with the source side. The source metric row $X$ reaches a completion-facing read only through the dense embedding row $J$ and the unit row $W$, so no detached source completion point is exposed.

Next read the finite name route. The regular rational row $R$ and stream-window row $S$ display the source Cauchy evidence before any real-distance seal is available.

Apply the isometry route through $I$ and $A$. The distance-preserving graph transports the displayed source evidence to the target side, and the real-seal row records the resulting distance observation.

The universal-property row $U$ then supplies the extension and uniqueness ledger for the same dense isometric route. Only after this ledger is displayed can a consumer read the target row $Y$ as the completion-facing endpoint of the extension.

The structural rows $L,C,P,N$ preserve the same ordered route and add no quotient completion equality, selected representative, countable-choice schedule, open-cover compactness, or completeness of $\RealUp$.
\end{proof}

\begin{theorem}[IsometryExtension Real seal boundary]
\label{thm:isometry-extension-real-seal-boundary}
For every accepted $\IsometryExtensionUp$ carrier $E=(X,Y,J,I,U,W,R,S,A,L,C,P,N)$, each $\RealUp$ seal-facing read exported by the extension is determined by the displayed chain
$$
J,W,R,S,I,A,U .
$$
The seal cannot be read as a quotient-completion equality, a selected representative, a countable-choice selection, an open-cover compactness witness, or a proof of completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Project the carrier and isolate the real-seal coordinate $A$. It appears only after the dense embedding row $J$, unit row $W$, regular-rational row $R$, stream-window row $S$, and isometry row $I$ have been displayed.

Use the completion handoff of \autoref{thm:isometry-extension-completion-handoff}. Any completion-facing consumer reaches the target side by replaying the same $J,W,R,S,I,A,U$ route before reading $Y$.

The universal-property row $U$ keeps the extension ledger attached to that real-seal route. A second seal, a selected representative, or a quotient equality would require a carrier coordinate outside the displayed chain.

No such coordinate exists in $E$. Transport, continuation, provenance, and local naming preserve the listed rows componentwise, so every $\RealUp$ read remains bounded by $J,W,R,S,I,A,U,L,C,P,N$.
\end{proof}

\begin{closurestatus}{\IsometryExtensionUp}
  \constructivestory{An $\IsometryExtensionUp$ packet is generated from source and target metric rows, a CompletionEmbedding row, an IsometricEmbedding row, a CompletionUniversalProperty row, a CauchyCompletionUnit row, StreamName and RegSeqRat finite-name rows, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:isometry-extension-carrier}, \autoref{thm:isometry-extension-namecert-obligations}, \autoref{thm:isometry-extension-completion-handoff}, and \autoref{thm:isometry-extension-real-seal-boundary} seed the finite isometry-extension surface for L10 completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, countable choice, open-cover compactness, or completeness of $\RealUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-source compatibility, isometric distance preservation, universal-property extension, finite-name handoff, Real-seal boundary, and ledger non-escape for BEDC.Derived.IsometryExtensionUp.}
\end{closurestatus}
