\chapter{A Concrete Naming Certificate for $\CompletionDensityUp$}
\label{ch:concrete-instances-completion-density-namecert}
\origin{human}

Following Bishop and Bridges, the $\CompletionDensityUp$ packet records the finite density surface by which source names remain visible inside the regular Cauchy completion route. It sits between the embedding packet of \autoref{ch:concrete-instances-completionembedding-namecert}, the regular dense embedding of \autoref{ch:concrete-instances-regular-cauchy-dense-embedding-namecert}, the regular rational name surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the dense image of displayed source names before any completion-facing consumer can treat the route as a completed real object; it is not a quotient completion, a selected limit, a countable-choice construction, a host real equality principle, or an ambient completeness assertion.

\begin{definition}[CompletionDensity carrier]
\label{def:completion-density-carrier}
A $\CompletionDensityUp$ carrier is a finite $\BHist$ packet
$$
D=(S,W,R,T,E,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source-name row whose entries are to remain dense after entering the completion route;
\item $W$ is the $\StreamNameUp$ finite-window row through which the source names are inspected;
\item $R$ is the $\RegSeqRatUp$ readback row attached to the displayed windows;
\item $T$ is the $\DyadicRatCoreUp$ tolerance ledger that controls the finite density test;
\item $E$ is the $\CompletionEmbeddingUp$ row that carries the source names into the completion-facing surface;
\item $Q$ is the accepted $\RegularCauchyDenseEmbeddingUp$ row witnessing that every regular Cauchy density request reads the image through $S,W,R,T,E$ before reaching the $\RealUp$ seal;
\item $H$ records componentwise $\hsame$ transport for the source row, windows, readbacks, dyadic ledger, embedding row, dense-image row, continuation row, provenance row, and local naming row;
\item $C$ records displayed $\Cont$ replay from a source-name request through finite windows, regular readback, dyadic tolerance, completion embedding, dense-image verification, and real-seal handoff;
\item $P$ is the $\Pkg$ provenance over $\CompletionDensityUp$, $\CompletionEmbeddingUp$, $\RegularCauchyDenseEmbeddingUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CompletionDensityUp}$ row.
\end{enumerate}
The carrier has no coordinate for a quotient completion, a selected representative limit, countable choice, host real equality, ambient completeness, or an external dense subset.
\end{definition}

\begin{theorem}[CompletionDensity NameCert obligations]
\label{thm:completion-density-namecert-obligations}
For an accepted $\CompletionDensityUp$ carrier $D=(S,W,R,T,E,Q,H,C,P,N)$, the local $\NameCert_{\CompletionDensityUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed source names, finite stream windows, regular rational readbacks, dyadic tolerance ledger, completion embedding row, regular Cauchy dense-image row, transports, replay route, provenance, and local naming row;
\item source-image exactness, requiring every dense-image claim to start from the row $S$ and to inspect it only through $W,R,T$;
\item embedding compatibility, requiring the row $E$ to be the only completion-facing handoff of those source names;
\item dense-image stability, requiring the accepted row $Q$ to remain attached to $S,W,R,T,E$ under the componentwise $\hsame$ row $H$ and displayed $\Cont$ replay $C$;
\item provenance exhaustion, requiring $P$ and $N$ to name only the displayed route and to export no quotient completion, selected limit, countable-choice selector, host real equality, ambient completeness row, or detached dense subset.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:completion-density-carrier}. The tuple displays the source row, window row, regular readback, tolerance ledger, completion embedding, dense-image row, transports, replay, provenance, and local name.

Source-image exactness is forced by the order of the displayed rows. A density request first reads $S$, then inspects the source name through $W$, obtains regular rational readback through $R$, and consults the dyadic ledger $T$ before the completion embedding row $E$ is available.

Dense-image stability is the role of $Q,H,C$. The accepted regular Cauchy dense embedding row $Q$ is transported only componentwise by $H$ and replayed only along the continuation route $C$, so no second dense-image witness or detached subset can enter the certificate.

Finally, $P$ and $N$ package and name the same finite route. Since the carrier lists no quotient completion, selected limit, countable-choice selector, host real equality, ambient completeness, or external dense subset coordinate, those data cannot be exported by the local NameCert surface.
\end{proof}

\begin{theorem}[CompletionDensity regular Cauchy dense image]
\label{thm:completion-density-regular-cauchy-dense-image}
Let $D=(S,W,R,T,E,Q,H,C,P,N)$ be an accepted $\CompletionDensityUp$ packet. Every regular Cauchy density read of the source image factors through the finite route
$$
S,W,R,T,E,Q,H,C,P,N .
$$
In particular, a $\RegularCauchyDenseEmbeddingUp$ consumer can read the dense image only after the source names, stream windows, regular rational readbacks, dyadic tolerance ledger, and completion embedding row have been displayed. The read cannot substitute a quotient completion, a selected host limit, a countable-choice schedule, host real equality, ambient completeness, or an external dense subset.
\end{theorem}
\begin{proof}
Start with a regular Cauchy dense-image consumer. The carrier gives the consumer only the tuple rows of \autoref{def:completion-density-carrier}.

The consumer reaches the dense-image row $Q$ after the source route $S,W,R,T$ and the embedding row $E$ have been displayed. Thus every density read is downstream of the same finite source-name and tolerance route.

Transport and replay preserve this route through $H$ and $C$, while $P$ and $N$ record it as provenance and local naming data. Since no quotient, selected host limit, countable-choice schedule, host equality, ambient completeness, or external dense subset appears in the tuple, the dense image is exhausted by the stated finite packet.
\end{proof}

\begin{theorem}[CompletionDensity Real handoff]
\label{thm:completion-density-real-handoff}
For an accepted $\CompletionDensityUp$ carrier $D=(S,W,R,T,E,Q,H,C,P,N)$, every $\RealUp$-facing completion read that uses the dense image first consumes the displayed route
$$
\StreamNameUp(W),\quad \RegSeqRatUp(R),\quad \DyadicRatCoreUp(T),\quad \CompletionEmbeddingUp(E),\quad \RegularCauchyDenseEmbeddingUp(Q).
$$
The terminal real-name seal therefore receives only a dense image generated from source names already carried by $S$ and replayed through $H,C,P,N$. It receives no quotient completion, selected limit, countable choice, host real equality, ambient completeness, or independent real equality witness.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$-facing completion read. The packet exposes no terminal real coordinate except through the dense-image row $Q$ and the structural rows $H,C,P,N$.

The row $Q$ is downstream of the completion embedding row $E$, and $E$ is downstream of the source-name route $S,W,R,T$. Hence the real-facing consumer must first read the StreamName window, RegSeqRat readback, DyadicRatCore tolerance ledger, completion embedding, and regular Cauchy dense-image row displayed in the statement.

The remaining rows only transport, replay, package, and name that route. Because the carrier has no quotient-completion coordinate, selected limit, countable choice, host real equality, ambient completeness row, or independent real equality witness, the Real handoff is exactly the displayed finite density route.
\end{proof}

\closureat{CompletionDensityUp}{seedStr}

\begin{closurestatus}{\CompletionDensityUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:completion-density-carrier}, \autoref{thm:completion-density-namecert-obligations}, \autoref{thm:completion-density-regular-cauchy-dense-image}, and \autoref{thm:completion-density-real-handoff} seed the dense source-image surface between CompletionEmbedding, RegularCauchyDenseEmbedding, RegSeqRat, StreamName, DyadicRatCore, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected limits, countable choice, host real equality, ambient completeness, independent real equality witnesses, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, source-image exactness, embedding compatibility, dense-image stability, Real handoff, and provenance exhaustion for BEDC.Derived.CompletionDensityUp.}
  \constructivestory{A $\CompletionDensityUp$ packet is generated from source names, StreamName finite windows, RegSeqRat readbacks, a DyadicRatCore tolerance ledger, a CompletionEmbedding row, an accepted RegularCauchyDenseEmbedding row, componentwise hsame transports, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
