\chapter{A Concrete Naming Certificate for $\RealApartnessCompletionUp$}
\label{ch:concrete-instances-realapartnesscompletion-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RealApartnessCompletionUp$ packet records the separated completion boundary for $\RealUp$ names when apartness evidence is the visible equality discriminator. It reads the apartness surface of \autoref{ch:concrete-instances-apartnessreal-namecert}, the Hausdorff separation boundary of \autoref{ch:concrete-instances-hausdorffcompletion-namecert}, the constructive completion route of \autoref{ch:concrete-instances-constructive-metric-completion-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names the displayed boundary between regular Cauchy completion data and apartness-separated real reads; it does not assert completeness of $\RealUp$ or import quotient equality, selected limits, countable choice, trichotomy, or host real equality.

\begin{definition}[RealApartnessCompletion carrier]
\label{def:real-apartness-completion-carrier}
A $\RealApartnessCompletionUp$ carrier is a finite $\BHist$ packet
$$
A=(X,Q,M,S,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\ApartnessRealUp$ source row, exposing apartness evidence for the real-name boundary under inspection.
\item $Q$ is the $\HausdorffCompletionUp$ separation row attached to the same source read.
\item $M$ is the $\ConstructiveMetricCompletionUp$ completion-route row through which the separated completion request is replayed.
\item $S$ is the $\StreamNameUp$ finite-window schedule used by the completion read.
\item $R$ is the $\RegSeqRatUp$ regular rational readback extracted from those stream windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare the readback rows at the requested precision.
\item $E$ is the $\RealUp$ seal reached only after the apartness, separation, completion, window, readback, and tolerance rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the apartness row, separation row, completion route, window schedule, readback row, tolerance ledger, real seal, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from apartness inspection through Hausdorff separation, constructive completion, stream windows, regular readback, dyadic tolerance, and then the real seal.
\item $P$ is the $\Pkg$ provenance over $\RealApartnessCompletionUp$, $\ApartnessRealUp$, $\HausdorffCompletionUp$, $\ConstructiveMetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealApartnessCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completions, host real equality, selected limits, countable choice, trichotomy, or ambient completeness of $\RealUp$.
\end{definition}
\leanchecked{BEDC.Derived.RealApartnessCompletionUp.RealApartnessCompletionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RealApartnessCompletion obligation surface]
\label{thm:real-apartness-completion-obligation-surface}
For every accepted $\RealApartnessCompletionUp$ carrier $A=(X,Q,M,S,R,D,E,H,C,P,N)$, the local $\NameCert_{\RealApartnessCompletionUp}$ surface consists exactly of the following five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed apartness, Hausdorff separation, constructive completion, stream-window, regular readback, dyadic tolerance, Real seal, transport, replay, provenance, and local naming rows;
\item separated-source exactness, requiring the $\ApartnessRealUp$ row $X$ and $\HausdorffCompletionUp$ row $Q$ to be read before any completion-facing consumer can inspect $M$;
\item regular readback discipline, requiring every completion observation to pass through $S$, $R$, and $D$ before the $\RealUp$ seal $E$ is available;
\item componentwise stability, requiring $H$ and $C$ to transport and replay only the displayed rows $X,Q,M,S,R,D,E,P,N$;
\item ledger exhaustion, requiring the packet to export no quotient completion, host real equality, selected limit, countable-choice schedule, trichotomy row, or ambient $\RealUp$ completeness principle.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-apartness-completion-carrier}. The tuple displays exactly the apartness row, Hausdorff separation row, constructive completion route, stream windows, regular rational readback, dyadic tolerance ledger, Real seal, transport, replay, provenance, and local name.

Separated-source exactness is forced by the order of the visible route. The completion row $M$ is named only after the apartness row $X$ and the Hausdorff separation row $Q$ have been displayed, so a consumer cannot read completion data before seeing the separated source surface.

The regular readback discipline is the role of $S,R,D,E$. The seal row $E$ is downstream of the finite windows $S$, regular readback $R$, and dyadic tolerance ledger $D$, which keeps each Real-facing observation attached to the displayed regular-Cauchy route.

Componentwise stability and ledger exhaustion follow from $H,C,P,N$. These rows transport, replay, package, and name only the displayed packet, so they cannot add quotient completions, host real equality, selected limits, countable choice, trichotomy, or ambient completeness.
\end{proof}

\begin{theorem}[RealApartnessCompletion non-escape boundary]
\label{thm:real-apartness-completion-nonescape}
Let $A=(X,Q,M,S,R,D,E,H,C,P,N)$ be an accepted $\RealApartnessCompletionUp$ packet. Every separated completion read of $A$ factors through the finite route
$$
X,Q,M,S,R,D \longmapsto E \longmapsto H,C,P,N .
$$
Thus the boundary can expose apartness-separated real-name evidence only through the displayed $\ApartnessRealUp$, $\HausdorffCompletionUp$, $\ConstructiveMetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It excludes quotient completions, host real equality, selected limits, countable choice, trichotomy, and ambient Real completeness.
\end{theorem}
\begin{proof}
Begin with an accepted separated completion read. Carrier admission gives a single visible route from the apartness source $X$ and Hausdorff separation row $Q$ into the constructive completion row $M$.

Replay the observation path through the finite windows. The stream schedule $S$, regular rational readback $R$, and dyadic tolerance ledger $D$ must be displayed before the Real seal $E$ can be read.

Finally transport and package the same route through $H,C,P,N$. Since no other coordinate occurs in the carrier or obligation surface, the read cannot escape to quotient completions, host real equality, selected limits, countable choice, trichotomy, or ambient Real completeness.
\end{proof}

\closureat{RealApartnessCompletionUp}{seedStr}

\begin{closurestatus}{\RealApartnessCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-apartness-completion-carrier}, \autoref{thm:real-apartness-completion-obligation-surface}, and \autoref{thm:real-apartness-completion-nonescape} seed the separated apartness-completion boundary over ApartnessReal, HausdorffCompletion, ConstructiveMetricCompletion, StreamName, RegSeqRat, DyadicRatCore, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, host real equality, selected limits, countable choice, trichotomy, ambient $\RealUp$ completeness, or Lean verification.}
  \upgradepath{Obligation closure requires carrier admission, separated-source exactness, regular readback discipline, componentwise stability, and ledger exhaustion proofs for BEDC.Derived.RealApartnessCompletionUp.}
  \constructivestory{A $\RealApartnessCompletionUp$ packet is generated from an ApartnessReal source row, a HausdorffCompletion separation row, a ConstructiveMetricCompletion route, StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
