\chapter{A Concrete Naming Certificate for $\LimitPointUp$}
\label{ch:concrete-instances-limitpoint-namecert}
\origin{human}

Following Bishop and Bridges, the $\LimitPointUp$ packet records a constructive cluster-point and accumulation-point surface for real sequences by finite neighborhoods and cofinal subsequence windows. It reads finite windows from \autoref{ch:concrete-instances-streamname-namecert}, dyadic neighborhood radii from \autoref{ch:concrete-instances-dyadicratcore-namecert}, regular rational readback from \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the bounded source surface of \autoref{ch:concrete-instances-boundedrealsequence-namecert}, and the subsequence compactness route of \autoref{ch:concrete-instances-bolzanoweierstrass-namecert}. The packet gives downstream compactness arguments a BEDC-native cluster-point interface; it is not host completeness, quotient equality of streams, open-cover compactness, or a choice-selected subsequence.

\begin{definition}[LimitPoint carrier]
\label{def:limitpoint-carrier}
A $\LimitPointUp$ carrier is a finite $\BHist$ packet
$$
L=(S,W,D,Q,\Phi,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source real sequence row, including the $\BoundedRealSequenceUp$ source data when the packet is supplied from a bounded sequence and the sequence observations consumed by cluster-point readers.
\item $W$ is the finite $\StreamNameUp$ window row. It records the source windows and the selected cofinal windows inspected at the displayed precision requests.
\item $D$ is the $\DyadicRatCoreUp$ neighborhood-radius row containing the positive dyadic radii, comparison cells, and finite inclusion tests used to read a neighborhood of the proposed cluster point.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the selected windows and dyadic radius ledger before any real seal is exposed.
\item $\Phi$ is the cofinal subsequence witness row. It stores only the inspected monotone selector cells, later-index comparisons, and cofinal threshold witnesses needed by the finite windows in $W$.
\item $E$ is the $\RealUp$ cluster seal row reached only after $S,W,D,Q,\Phi$ have been replayed.
\item $H$ records componentwise $\hsame$ transport for the source sequence, StreamName windows, DyadicRatCore radii, RegSeqRat readback, cofinal subsequence witness, Real cluster seal, continuation row, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay from a neighborhood request through the source sequence, finite windows, dyadic radius ledger, cofinal subsequence witness, regular rational readback, and then the Real cluster seal.
\item $P$ is the $\Pkg$ provenance over $\LimitPointUp$, $\BoundedRealSequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BolzanoWeierstrassUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LimitPointUp}$ row naming the displayed packet and its permitted consumer reads.
\end{enumerate}
The classifier compares accepted packets only through these rows and their transported replay paths. It has no coordinate for host real completeness, quotient streams, open covers, arbitrary choice of subsequences, or a least cluster-point selector.
\end{definition}

\begin{theorem}[LimitPoint NameCert obligations]
\label{thm:limitpoint-namecert-obligations}
For every accepted $\LimitPointUp$ carrier $L=(S,W,D,Q,\Phi,E,H,C,P,N)$, the local $\NameCert_{\LimitPointUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the source real sequence, finite StreamName windows, DyadicRatCore neighborhood radii, RegSeqRat readback, cofinal subsequence witness, Real cluster seal, transport, continuation replay, provenance, and local naming row;
\item neighborhood coverage, requiring every cluster-point request to consume a displayed dyadic radius in $D$ and a finite selected window in $W$ before it reads the regular rational row $Q$;
\item cofinal-window persistence, requiring the selected windows in $W$ to travel through the cofinal witness row $\Phi$ with displayed monotone and later-index evidence;
\item Real seal routing, requiring the cluster seal row $E$ to be reached only after $S,W,D,\Phi,Q$ have been displayed;
\item ledger non-escape, excluding host completeness, quotient stream equality, open-cover compactness, arbitrary choice-selected subsequences, and least cluster-point selection.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:limitpoint-carrier}. The projection exposes exactly the source sequence, finite window, dyadic radius, regular readback, cofinal witness, Real seal, transport, continuation, provenance, and local naming rows.

The neighborhood coverage row is read through $W$ and $D$. A cluster-point request first fixes the inspected finite source and selected windows, then reads the positive dyadic radius and comparison cells attached to that request, and only then reaches the regular rational row $Q$.

The cofinal-window row $\Phi$ controls the selected windows. It supplies the inspected monotone selector cells, later-index comparisons, and cofinal threshold witnesses, so the selected windows cannot be replaced by an arbitrary host subsequence.

Finally, the seal row $E$ sits downstream of $S,W,D,\Phi,Q$, while $H,C,P,N$ preserve and name the same route. Since none of these rows carries host completeness, quotient stream equality, open-cover compactness, arbitrary choice of subsequences, or a least cluster-point selector, the five listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[LimitPoint Bolzano--Weierstrass handoff]
\label{thm:limitpoint-bolzano-weierstrass-handoff}
Every $\BolzanoWeierstrassUp$ cluster consumer supplied by a $\BoundedRealSequenceUp$ source and the regular-subsequence route of \autoref{ch:concrete-instances-regular-cauchy-subsequence-namecert} factors through an accepted $\LimitPointUp$ packet. In the notation of \autoref{def:limitpoint-carrier}, the consumer reads the finite route
$$
S,W,D,\Phi \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Thus the Bolzano--Weierstrass cluster row can be consumed as a LimitPoint surface over $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, without importing host completeness, quotient streams, open-cover compactness, or a choice-selected subsequence.
\end{theorem}
\begin{proof}
Start with the bounded source row. The $\BoundedRealSequenceUp$ packet of \autoref{ch:concrete-instances-boundedrealsequence-namecert} supplies the source sequence surface consumed by the $\BolzanoWeierstrassUp$ carrier.

Use the Bolzano--Weierstrass route of \autoref{ch:concrete-instances-bolzanoweierstrass-namecert}. Its cluster consumer first reads finite interval and sequence data, then passes through the regular-subsequence route, the $\RegSeqRatUp$ readback, and the terminal $\RealUp$ cluster seal.

Repack that same downstream surface as $S,W,D,\Phi,Q,E$. The source sequence becomes $S$, the inspected source and selected windows become $W$, the neighborhood mesh radii become $D$, the regular-subsequence evidence becomes $\Phi$, the regular rational handoff becomes $Q$, and the real cluster row becomes $E$.

The structural rows $H,C,P,N$ then transport, replay, source, and name this finite route as a $\LimitPointUp$ packet. Since the original Bolzano--Weierstrass consumer exposes no host completeness, quotient stream equality, open-cover compactness, or arbitrary subsequence choice, the factored LimitPoint packet exposes none.
\end{proof}

\closureat{LimitPointUp}{seedStr}

\begin{closurestatus}{\LimitPointUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:limitpoint-carrier}, \autoref{thm:limitpoint-namecert-obligations}, and \autoref{thm:limitpoint-bolzano-weierstrass-handoff} seed the finite cluster-point interface from real-sequence windows through cofinal subsequence evidence, dyadic neighborhoods, regular rational readback, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, host completeness, quotient stream equality, open-cover compactness, arbitrary choice-selected subsequences, or least cluster-point selection.}
  \upgradepath{Obligation closure requires checked carrier admission, neighborhood coverage, cofinal-window persistence, Real seal routing, ledger non-escape, and Bolzano--Weierstrass handoff for the same packet.}
  \constructivestory{A $\LimitPointUp$ packet is generated from a source real sequence, finite StreamName windows, DyadicRatCore neighborhood radii, RegSeqRat readback, a cofinal subsequence witness, a RealUp cluster seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
