\chapter{A Concrete Naming Certificate for $\PrincipalCauchyFilterUp$}
\label{ch:concrete-instances-principal-cauchy-filter-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\PrincipalCauchyFilterUp$ packet names the finite point-generated Cauchy-filter boundary used by Phase Real and Completion before a generic $\CauchyFilterUp$ surface is consumed. It starts from a displayed $\RegSeqRatUp$ point name, reads the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, uses the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, saturates into the finite filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, and leaves the downstream seal of \autoref{ch:concrete-instances-real-namecert} behind that route. The packet is a point-generated filter certificate, not a quotient filter, not a selected limit, not host real equality, and not ambient completeness.

\begin{definition}[PrincipalCauchyFilter carrier]
\label{def:principal-cauchy-filter-carrier}
A $\PrincipalCauchyFilterUp$ carrier is a finite $\BHist$ packet
$$
K=(X,S,R,D,G,F,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the point-name row whose observations generate the principal Cauchy filter.
\item $S$ is the $\StreamNameUp$ finite-window schedule through which the point-name row is inspected.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row attached to the same windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare observations at the requested filter scale.
\item $G$ is the principal-generator row. For each displayed precision request it names the finite tail neighbourhood generated by $X,S,R,D$.
\item $F$ is the $\CauchyFilterUp$ saturation row obtained from the generator row $G$ by closing only the finite directed-refinement obligations recorded in the packet.
\item $A$ is the downstream $\RealUp$ seal row reached only after $X,S,R,D,G,F$ have been consumed.
\item $H$ records componentwise $\hsame$ transport for the point name, stream schedule, regular readback, dyadic tolerance ledger, generator row, saturated filter row, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a filter request back through the principal generator and then through the stream, regular rational, dyadic tolerance, and seal rows.
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyFilterUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PrincipalCauchyFilterUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient filters, selected limits, countable-choice selectors, host real equality, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[PrincipalCauchyFilter NameCert obligations]
\label{thm:principal-cauchy-filter-namecert-obligations}
For every accepted $\PrincipalCauchyFilterUp$ carrier $K=(X,S,R,D,G,F,A,H,C,P,N)$, the local $\NameCert_{\PrincipalCauchyFilterUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the point-name row, stream schedule, regular rational readback, dyadic tolerance ledger, principal generator, saturated Cauchy filter, Real seal, transport, continuation, provenance, and local naming row;
\item point generation, requiring every displayed filter neighbourhood in $G$ to be generated from the same $X,S,R,D$ rows;
\item saturation discipline, requiring the $\CauchyFilterUp$ row $F$ to consume the finite generator row $G$ before any completion-facing read can use a generic Cauchy-filter surface;
\item seal nonescape, requiring the $\RealUp$ row $A$ to remain downstream of $X,S,R,D,G,F$;
\item ledger refusal, excluding quotient filters, selected limits, countable-choice selectors, host real equality, and ambient completeness.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:principal-cauchy-filter-carrier}. The projection exposes exactly the point-name row, stream schedule, regular readback, dyadic tolerance ledger, principal generator, saturated filter row, Real seal, and structural rows $H,C,P,N$.

Point generation is forced by the row inventory. The generator row $G$ has no independent source; each of its displayed neighbourhoods reads the same point observation through $S$, the same regular rational readback through $R$, and the same dyadic tolerance ledger through $D$.

Saturation discipline is then internal to $F$. A completion-facing consumer reaches the generic $\CauchyFilterUp$ surface only after $G$ has been consumed, so the packet cannot exchange the principal generator for an arbitrary quotient filter.

Finally, the seal row $A$ is downstream of the same route. Transport by $H$ preserves each coordinate, while $C$, $P$, and $N$ replay and name only that finite route; hence no selected limit, countable-choice selector, host real equality, or ambient completeness coordinate remains available.
\end{proof}

\begin{theorem}[PrincipalCauchyFilter RegSeqRat handoff]
\label{thm:principal-cauchy-filter-regseqrat-handoff}
Let $K=(X,S,R,D,G,F,A,H,C,P,N)$ be an accepted $\PrincipalCauchyFilterUp$ carrier. Every completion-facing read that starts from the regular rational point name factors through the finite route
$$
X,S,R,D \longmapsto G \longmapsto F \longmapsto A \longmapsto H,C,P,N .
$$
Thus the $\RegSeqRatUp$ row reaches the generic $\CauchyFilterUp$ saturation surface only through the principal generator row, and the downstream $\RealUp$ seal remains after that saturation handoff.
\end{theorem}
\begin{proof}
Begin with a completion-facing consumer of the accepted packet. Carrier admission gives access to the saturated filter row $F$ and the seal row $A$, but only as rows downstream of the point-name route $X,S,R,D,G$.

Replay the continuation row $C$. The request first reads the stream schedule $S$, then the regular rational readback $R$, then the dyadic tolerance ledger $D$ attached to the same point-name row $X$.

Only after those rows have been consumed can the principal generator $G$ be saturated into the $\CauchyFilterUp$ row $F$. The seal row $A$ and the structural rows $H,C,P,N$ record the same dependency order, which proves the stated factorization.
\end{proof}

\begin{theorem}[PrincipalCauchyFilter ledger non-escape]
\label{thm:principal-cauchy-filter-ledger-non-escape}
For every accepted $\PrincipalCauchyFilterUp$ carrier $K=(X,S,R,D,G,F,A,H,C,P,N)$, every exported filter or Real-facing read remains inside the finite ledger
$$
X,S,R,D,G,F,A,H,C,P,N .
$$
It cannot produce a quotient filter, a selected limit, a countable-choice selector, host real equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project an exported read from the carrier. By \autoref{def:principal-cauchy-filter-carrier}, the read has access only to the eleven displayed coordinates and their componentwise transport and continuation rows.

Apply \autoref{thm:principal-cauchy-filter-namecert-obligations}. Point generation keeps the read inside $X,S,R,D,G$; saturation discipline moves it through $F$; seal nonescape moves it through $A$; and the structural rows $H,C,P,N$ record only the same route.

Every excluded principle is absent from this ledger. Quotient filters, selected limits, countable-choice selectors, host real equality, and ambient $\RealUp$ completeness have no carrier coordinate, no replay edge, and no provenance row in the packet, so the exported read cannot leave the displayed finite surface.
\end{proof}

\begin{closurestatus}{\PrincipalCauchyFilterUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:principal-cauchy-filter-carrier}, \autoref{thm:principal-cauchy-filter-namecert-obligations}, \autoref{thm:principal-cauchy-filter-regseqrat-handoff}, and \autoref{thm:principal-cauchy-filter-ledger-non-escape} seed the finite point-generated Cauchy-filter boundary between regular rational names, generic Cauchy-filter evidence, and the downstream $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, selected limits, countable-choice selectors, host real equality, ambient $\RealUp$ completeness, or Lean verification.}
  \upgradepath{Obligation closure requires carrier admission, point generation, CauchyFilter saturation handoff, RegSeqRat readback, Real seal factorization, and ledger refusal for the same packet.}
  \constructivestory{A $\PrincipalCauchyFilterUp$ packet is generated from a point-name row, StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a principal-generator row, a CauchyFilter saturation row, a RealUp seal, componentwise transport, continuation replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
