\chapter{A Concrete Naming Certificate for $\CauchyShiftUp$}
\label{ch:concrete-instances-cauchyshift-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\CauchyShiftUp$ packet records the finite certified route by which a regular Cauchy name may ignore an initial finite prefix and still present the same tail-facing regularity surface to a downstream $\RealUp$ seal. It sits beside the schedule-changing packet of \autoref{ch:concrete-instances-cauchy-reindexing-namecert}, reads the explicit modulus discipline of \autoref{ch:concrete-instances-cauchymodulus-namecert}, and consumes the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The chapter names a finite tail shift of a regular Cauchy name, not quotient stream equality, not a selected limit, not countable choice, not host real equality, and not ambient completeness of $\RealUp$.

\begin{definition}[CauchyShift carrier]
\label{def:cauchy-shift-carrier-surface}
A $\CauchyShiftUp$ carrier is a finite $\BHist$ packet
$$
K=(S,T,k,M,D,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\StreamNameUp$ schedule row whose finite observation windows are available before the shift is requested.
\item $T$ is the shifted $\StreamNameUp$ schedule row whose $n$th displayed request is routed to the source request $n+k$.
\item $k$ is the finite unary shift-length row, recording the displayed prefix length and no unbounded selector.
\item $M$ is the $\CauchyModulusUp$ tail row that certifies every post-shift precision request by replaying the corresponding source-tail modulus request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used to compare the source and shifted observations at the finite budgets named by $k$ and $M$.
\item $R$ is the $\RegSeqRatUp$ readback row showing that the shifted schedule remains a regular rational name after the tail route has been replayed.
\item $A$ is the $\RealUp$ seal row reached only after $S,T,k,M,D,R$ have been consumed.
\item $H$ records componentwise $\hsame$ transport for the source schedule, shifted schedule, shift length, modulus row, dyadic tolerance row, regularity row, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a shifted-window request through the finite shift length, back to the source schedule, then forward through the modulus row, dyadic tolerance, regular readback, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\CauchyModulusUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyShiftUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient streams, selected limits, countable-choice tail selection, host real equality, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[CauchyShift NameCert obligations]
\label{thm:cauchy-shift-namecert-obligations}
For every accepted $\CauchyShiftUp$ carrier $K=(S,T,k,M,D,R,A,H,C,P,N)$, the local $\NameCert_{\CauchyShiftUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the source schedule, shifted schedule, finite shift length, Cauchy modulus row, dyadic tolerance row, regularity row, Real seal, transport, continuation, provenance, and local naming row;
\item shift admissibility, requiring every shifted-window read in $T$ to replay through the displayed finite unary shift $k$ before it can consult the source schedule $S$;
\item tail-modulus discipline, requiring $M$ to be consumed before a post-shift observation can be treated as a regular Cauchy tail observation;
\item tolerance and readback preservation, requiring $D$ and $R$ to certify the finite regular rational readback after the shifted route has been replayed;
\item seal nonescape, requiring the $\RealUp$ row $A$ to remain downstream of $S,T,k,M,D,R$;
\item ledger refusal, excluding quotient streams, selected limits, countable-choice tail selectors, host real equality, and ambient $\RealUp$ completeness.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-shift-carrier-surface}. The projection exposes exactly the source schedule, shifted schedule, finite shift length, Cauchy modulus row, dyadic tolerance row, regularity row, Real seal, and structural rows $H,C,P,N$.

Shift admissibility is forced by the continuation row $C$. A shifted-window request reaches $T$ only by replaying the displayed unary shift length $k$ back to the source schedule $S$, so the packet has no independent tail stream coordinate.

The modulus row $M$ is then the only row that permits the shifted request to be treated as a Cauchy-tail request. The dyadic tolerance row $D$ and regularity row $R$ sit downstream of that tail route, so tolerance preservation and regular readback cannot be exported before the finite shift discipline has been consumed.

Finally, the seal row $A$ is downstream of the same route. Transport by $H$ preserves each listed coordinate, while $P$ and $N$ package only that finite route; hence no quotient stream, selected limit, countable-choice tail selector, host real equality, or ambient completeness coordinate remains available.
\end{proof}

\begin{theorem}[CauchyShift regularity transport]
\label{thm:cauchy-shift-regularity-transport}
Let $K=(S,T,k,M,D,R,A,H,C,P,N)$ be an accepted $\CauchyShiftUp$ carrier. Every displayed $\RegSeqRatUp$ regularity read on the shifted schedule $T$ factors through the finite route
$$
S,k,M,D \longmapsto T \longmapsto R .
$$
Thus finite-prefix shift preserves the displayed regularity surface through the Cauchy modulus row and the dyadic tolerance row before any downstream consumer can read $R$ as a regular rational name.
\end{theorem}
\begin{proof}
Begin with a shifted regularity read. Carrier admission gives access to the $\RegSeqRatUp$ row $R$, but only as the row downstream of the shifted schedule $T$, finite shift length $k$, modulus row $M$, and dyadic tolerance row $D$.

Replay the continuation row $C$. The shifted request is translated by the finite unary length $k$ into the source schedule $S$. The modulus row $M$ then supplies the displayed tail budget for that source request, and the dyadic tolerance row $D$ records the finite comparison at the requested scale.

Once those rows have been consumed, $T$ has exactly the displayed tail observations licensed by $S,k,M,D$. The regular readback row $R$ therefore transports regularity along the finite shift route, with $H$ preserving the same dependency order and $P,N$ naming only that packet.
\end{proof}

\begin{theorem}[CauchyShift Real seal boundary]
\label{thm:cauchy-shift-real-seal-boundary}
Let $K=(S,T,k,M,D,R,A,H,C,P,N)$ be an accepted $\CauchyShiftUp$ carrier. Every $\RealUp$-facing read of the shifted name factors through the finite route
$$
S,T,k,M,D,R \longmapsto A \longmapsto H,C,P,N .
$$
The shifted name reaches the seal only after the source schedule, shifted schedule, finite shift length, Cauchy modulus row, dyadic tolerance row, and $\RegSeqRatUp$ readback have been displayed. The route contains no quotient stream equality, selected limit, countable-choice tail selector, host real equality, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with a Real-facing consumer of the packet. Carrier admission gives access to the seal row $A$, but only as a row downstream of $S,T,k,M,D,R$.

Replay the continuation row $C$. The request first reads the shifted schedule $T$ as a finite-prefix shift of the source schedule $S$, then consumes the shift length $k$ and the Cauchy modulus row $M$ that make the tail request admissible.

After those rows have been consumed, the dyadic tolerance row $D$ and regularity row $R$ provide the finite readback accepted by the Real seal. The transport, provenance, and local naming rows record the same dependency order, so the packet exports no direct route through quotient streams, selected limits, countable-choice tail selection, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[CauchyShift reindexing selector handoff]
\label{thm:cauchy-shift-reindexing-selector-handoff}
Let $K=(S,T,k,M,D,R,A,H,C,P,N)$ be an accepted $\CauchyShiftUp$ carrier. Any $\RealUp$-facing read of $K$ that is also consumed by a $\CauchyReindexingUp$ route or by a $\RealCauchyModulusSelectorUp$ route factors through the ordered handoff
$$
S,k,M,D \longmapsto T \longmapsto R \longmapsto \RegularCauchyModulusRealizationUp \longmapsto \RealCauchyModulusSelectorUp \longmapsto A
$$
with the structural rows $H,C,P,N$ preserving that order. Thus the shifted name may be reindexed, realized as a regular Cauchy modulus surface, selected by the Real Cauchy modulus selector, and then sealed at $A$, but it exports no quotient stream, selected limit, countable-choice tail selector, host real equality, detached modulus selector, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:cauchy-shift-regularity-transport}. Every shifted regularity read first consumes the source schedule, finite shift length, Cauchy modulus row, and dyadic tolerance row before it can read the shifted schedule $T$ and the regular rational row $R$.

The downstream reindexing side is the route recorded in \autoref{ch:concrete-instances-cauchy-reindexing-namecert}. A consumer that asks for a $\CauchyReindexingUp$ read therefore receives only the displayed regular readback produced by the shift packet; it does not obtain a second stream coordinate or an independent equality of streams.

The modulus-selection side is the route recorded in \autoref{ch:concrete-instances-regular-cauchy-modulus-realization-namecert} and \autoref{ch:concrete-instances-realcauchymodulusselector-namecert}. The regular Cauchy modulus realization reads the finite $M,S,D,R$-style window as a displayed regular surface, and the Real Cauchy modulus selector then chooses only the threshold, finite window, tolerance, readback, and seal rows already displayed by that route.

Finally apply \autoref{thm:cauchy-shift-real-seal-boundary}. The seal row $A$ remains downstream of the shifted route and of the structural rows $H,C,P,N$. Since neither this carrier nor the cited sibling routes contain quotient streams, selected limits, countable-choice tail selectors, host real equality, detached modulus selectors, or ambient $\RealUp$ completeness, the composite handoff cannot export any of those principles.
\end{proof}

\begin{closurestatus}{\CauchyShiftUp}
  \constructivestory{A $\CauchyShiftUp$ packet is generated from a source StreamName schedule, a shifted StreamName schedule, a finite unary shift length, a CauchyModulus tail row, a DyadicRatCore tolerance row, a RegSeqRat readback row, a RealUp seal, componentwise transport, continuation replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-shift-carrier-surface}, \autoref{thm:cauchy-shift-namecert-obligations}, \autoref{thm:cauchy-shift-regularity-transport}, \autoref{thm:cauchy-shift-real-seal-boundary}, and \autoref{thm:cauchy-shift-reindexing-selector-handoff} seed the finite tail-shift route from regular Cauchy names through reindexing, regular modulus realization, selector handoff, and the downstream $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable-choice tail selectors, host real equality, ambient $\RealUp$ completeness, or Lean verification.}
  \upgradepath{Obligation closure requires carrier admission, regularity transport, Real seal boundary, and ledger refusal proofs for the same finite tail-shift packet.}
\end{closurestatus}
