\chapter{A Concrete Naming Certificate for $\RealCauchyCriterionUp$}
\label{ch:concrete-instances-real-cauchy-criterion-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\RealCauchyCriterionUp$ packet records the finite criterion by which a displayed sequence of Real names is admitted as Cauchy data before any completion-facing consumer reads a terminal Real seal. It sits between the finite-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the Real seal boundary of \autoref{ch:concrete-instances-real-namecert}, and the exact completion boundary of \autoref{ch:concrete-instances-real-completion-exact-boundary-namecert}. The packet is a Real-sequence Cauchy readiness certificate, not a quotient stream, selected limit, host real equality, trichotomy, countable-choice source, or ambient Real completeness principle.

\begin{definition}[Real Cauchy criterion carrier]
\label{def:real-cauchy-criterion-carrier}
A $\RealCauchyCriterionUp$ carrier is a finite $\BHist$ packet
$$
K=(S,W,Q,D,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\RealUp$ sequence-source row, exposing the finite list of Real-name entries and precision requests inspected by the criterion.
\item $W$ is the family of $\StreamNameUp$ finite windows selected for the inspected source entries and late-pair requests.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained only through the windows in $W$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance-test ledger recording the rational radii, late-pair comparisons, and dyadic triangle-budget cells used by the Cauchy test.
\item $L$ is the Cauchy-test ledger tying each accepted precision request to a displayed late-pair window, regular readback, and dyadic tolerance comparison.
\item $E$ is the $\RealUp$ seal row reached only after $S,W,Q,D,L$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the sequence source, windows, regular readback, dyadic tolerance ledger, Cauchy-test ledger, Real seal, continuation row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a precision request through the sequence source, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance test, Cauchy-test ledger, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\RealCauchyCriterionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\RealCompletionExactBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealCauchyCriterionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,W,Q,D,L,E,H,C,P,N$. It has no coordinate for quotient stream equality, a selected limit, countable choice, host real equality, trichotomy, detached Real completeness, or an ambient completion theorem.
\end{definition}

\begin{theorem}[Real Cauchy criterion NameCert obligations]
\label{thm:real-cauchy-criterion-namecert-obligations}
For an accepted $\RealCauchyCriterionUp$ carrier $K=(S,W,Q,D,L,E,H,C,P,N)$, the local $\NameCert_{\RealCauchyCriterionUp}$ surface consists exactly of the following five finite obligations:
\begin{enumerate}
\item carrier admission for the Real sequence source, finite StreamName windows, RegSeqRat readback, DyadicRatCore tolerance ledger, Cauchy-test ledger, Real seal, transport, replay, provenance, and local naming row;
\item window-readback compatibility, requiring every regular rational read in $Q$ to be obtained from a displayed window in $W$ attached to the source row $S$;
\item dyadic Cauchy-test exactness, requiring $D$ and $L$ to record the requested tolerance, late-pair budget, and triangle cells before the criterion may expose the seal row $E$;
\item transport and replay stability, requiring componentwise $\hsame$ transport $H$ and displayed $\Cont$ replay $C$ to preserve the same ordered route $S,W,Q,D,L,E$;
\item provenance exhaustion, requiring $P$ and $N$ to name only this displayed route and to export no quotient streams, selected limits, countable-choice selector, host real equality, trichotomy, detached Real completeness, or ambient completion principle.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-cauchy-criterion-carrier}. The packet displays the Real sequence source, selected StreamName windows, regular rational readback, dyadic tolerance ledger, Cauchy-test ledger, terminal seal row, and the structural rows $H,C,P,N$.

Window-readback compatibility is read from the order of $W$ and $Q$. The readback row $Q$ appears only after the selected finite windows $W$, and those windows are attached to the source row $S$ rather than to an unbounded host stream.

Dyadic exactness is the role of $D$ and $L$. The tolerance row $D$ stores the rational radii and comparison cells, while the ledger $L$ records which late-pair request has been tested before the Real seal $E$ is available.

Transport and replay are structural. Componentwise $\hsame$ in $H$ preserves the displayed rows, and $\Cont$ replay in $C$ repeats the route from the precision request through $S,W,Q,D,L,E$.

Finally, provenance is exhausted by $P$ and $N$. Since the carrier has no row for quotient stream equality, selected limits, countable choice, host real equality, trichotomy, detached Real completeness, or ambient completion, the local NameCert surface cannot export any such object.
\end{proof}

\begin{theorem}[Real Cauchy criterion regular readback route]
\label{thm:real-cauchy-criterion-regular-readback-route}
Every accepted $\RealCauchyCriterionUp$ read factors through the displayed route
$$
\StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \DyadicRatCoreUp \longmapsto \RealUp
$$
together with the Real sequence source, Cauchy-test ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, local $\NameCert_{\RealCauchyCriterionUp}$ row, and the $\RealCompletionExactBoundaryUp$ sibling boundary. The route cannot expose quotient streams, selected limits, countable choice, host real equality, trichotomy, or ambient Real completeness.
\end{theorem}
\begin{proof}
Begin with an accepted read of the criterion packet. Carrier projection gives the sequence source $S$ and the selected finite windows $W$ before any regular rational readback is available.

The readback row $Q$ is downstream of $W$. Thus each accepted read first passes through the $\StreamNameUp$ window discipline and then through the $\RegSeqRatUp$ regular rational surface attached to that same displayed window.

The dyadic Cauchy test is downstream of the readback. The rows $D$ and $L$ record the requested tolerance, late-pair budget, and comparison cells before the terminal $\RealUp$ seal $E$ may be consumed.

The exact-boundary sibling is read only as provenance discipline. The row $P$ names $\RealCompletionExactBoundaryUp$ to keep the Real-completion faces aligned, but it contributes no selected limit, quotient equality, or independent completeness witness.

The exclusions follow from the carrier inventory. Since quotient streams, selected limits, countable choice, host real equality, trichotomy, and ambient Real completeness are not rows of $K$, no accepted read through $H,C,P,N$ can expose them.
\end{proof}

\begin{theorem}[Real Cauchy criterion seal factorization]
\label{thm:real-cauchy-criterion-seal-factorization}
For every accepted $\RealCauchyCriterionUp$ packet
$$
K=(S,W,Q,D,L,E,H,C,P,N),
$$
the terminal $\RealUp$ seal row $E$ is reachable only through the ordered finite route $S,W,Q,D,L,E,H,C,P,N$. Along this route $W$ supplies the $\StreamNameUp$ windows, $Q$ supplies the $\RegSeqRatUp$ readback, and $D,L$ supply the dyadic Cauchy-test ledger. No quotient stream, selected limit, countable choice, host equality, trichotomy, or ambient completeness row can bypass $E$.
\end{theorem}
\begin{proof}
Project the carrier using \autoref{def:real-cauchy-criterion-carrier}. The projection displays the ordered rows $S,W,Q,D,L,E,H,C,P,N$, with the terminal Real seal placed after the finite windows, regular readback, dyadic tolerance data, and Cauchy-test ledger.

\autoref{thm:real-cauchy-criterion-namecert-obligations} identifies the five-row certificate surface governing carrier admission, window-readback compatibility, dyadic exactness, transport and replay stability, and provenance exhaustion. In particular, the seal row $E$ is not an independent input; it is admitted only after the $S,W,Q,D,L$ route has been recorded.

\autoref{thm:real-cauchy-criterion-regular-readback-route} supplies the StreamName--RegSeqRat--DyadicRatCore readback path. Combining that route with the carrier projection shows that every completion-facing use of $E$ factors through the same finite Cauchy-test ledger.

The excluded objects are absent from the carrier inventory and from the NameCert surface. Therefore quotient stream equality, selected limits, countable choice, host equality, trichotomy, and ambient completeness cannot supply an alternate row reaching the terminal $\RealUp$ seal.
\end{proof}

\closureat{RealCauchyCriterionUp}{seedStr}

\begin{closurestatus}{\RealCauchyCriterionUp}
  \constructivestory{A $\RealCauchyCriterionUp$ packet is generated from a RealUp sequence source, StreamName finite windows, a RegSeqRat readback row, a DyadicRatCore tolerance-test ledger, a Cauchy-test ledger, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-cauchy-criterion-carrier}, \autoref{thm:real-cauchy-criterion-namecert-obligations}, \autoref{thm:real-cauchy-criterion-regular-readback-route}, and \autoref{thm:real-cauchy-criterion-seal-factorization} seed the Real-specific Cauchy criterion route through StreamName, RegSeqRat, DyadicRatCore, Real, and RealCompletionExactBoundary faces.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, host real equality, trichotomy, ambient Real completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, window-readback compatibility, dyadic Cauchy-test exactness, transport stability, replay stability, regular readback factorization, Real seal factorization, and provenance exhaustion for BEDC.Derived.RealCauchyCriterionUp.}
\end{closurestatus}
