\chapter{A Concrete Naming Certificate for $\HausdorffMetricUp$}
\label{ch:concrete-instances-hausdorffmetric-namecert}
\origin{human}

Following Hausdorff and Kelley, and in the constructive metric style of Bishop--Bridges, the $\HausdorffMetricUp$ packet records the finite distance ledger by which two displayed compact or located subset rows are compared inside one metric source. It sits between the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the compact finite-net surface of \autoref{ch:concrete-instances-compactmetric-namecert}, the located-subset boundary of \autoref{ch:concrete-instances-locatedset-namecert}, the ball ledger of \autoref{ch:concrete-instances-metricball-namecert}, and the terminal distance seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite Hausdorff-distance interface; it does not introduce a host hyperspace, quotient subset equality, selected suprema, open-cover compactness, or Gromov-Hausdorff comparison.

\begin{definition}[Hausdorff metric carrier]
\label{def:hausdorff-metric-carrier}
A $\HausdorffMetricUp$ carrier is a finite $\BHist$ packet
$$
K=(X,A,B,d_A,d_B,h,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the shared $\MetricUp$ source row, including the accepted point histories, distance classifier, metric-ball ledger, and componentwise transport data available to both subset rows.
\item $A$ and $B$ are compact or located subset rows over $X$. Each row exposes only its displayed membership, finite-net, located-distance, and ball-incidence ledgers, as supplied by the $\CompactMetricUp$, $\LocatedSetUp$, and $\MetricBallUp$ sibling packets.
\item $d_A$ is the directed $\RealUp$ distance ledger from $A$ toward $B$: for every displayed finite request from $A$ it records the inspected source point, the matching finite window or located-distance row in $B$, the rational tolerance bound, and the resulting real-distance seal.
\item $d_B$ is the directed $\RealUp$ distance ledger from $B$ toward $A$, with the same displayed fields in the reverse direction.
\item $h$ is the symmetric maximum packaging row. It packages the two directed ledgers by a finite dyadic or rational maximum certificate before a $\RealUp$ seal is exposed as the Hausdorff tolerance read.
\item $H$ records componentwise $\hsame$ transport for $X,A,B,d_A,d_B,h$ and for the structural provenance rows.
\item $C$ records the displayed $\Cont$ routes through the shared metric source, both subset rows, both directed ledgers, the symmetric maximum packaging row, and the terminal distance seal.
\item $P$ is the $\Pkg$ provenance over $\HausdorffMetricUp$, $\MetricUp$, $\CompactMetricUp$, $\LocatedSetUp$, $\MetricBallUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HausdorffMetricUp}$ row naming the permitted reads from the packet.
\end{enumerate}
The carrier has no coordinate for a host powerset, quotient subset equality, a selected supremum, an open cover, an ambient hyperspace, or Gromov-Hausdorff data.
\end{definition}

\begin{theorem}[HausdorffMetric NameCert obligations]
\label{thm:hausdorff-metric-namecert-obligations}
For every accepted $\HausdorffMetricUp$ carrier
$$
K=(X,A,B,d_A,d_B,h,H,C,P,N),
$$
the local $\NameCert_{\HausdorffMetricUp}$ surface consists exactly of five obligation rows:
\begin{enumerate}
\item carrier admission for the shared $\MetricUp$ row, the two compact or located subset rows, the two directed $\RealUp$ distance ledgers, the symmetric maximum row, the transport ledger, the continuation routes, the provenance row, and the local naming row;
\item classifier transport, requiring any replacement of $A$ or $B$ to move componentwise along the stored $\hsame$ rows and replay only the displayed $\Cont$ routes over the same metric source;
\item directed-distance stability, requiring $d_A$ and $d_B$ to preserve their inspected point, finite-net or located-distance witness, metric-ball incidence, rational tolerance, and $\RealUp$ seal fields under refinement of the displayed subset rows;
\item symmetric max packaging, requiring the public Hausdorff tolerance read to pass through $h$ after both directed ledgers have been displayed;
\item ledger non-escape, excluding host subsets, quotient subset equality, selected suprema, open-cover compactness, ambient hyperspace completeness, and Gromov-Hausdorff comparison.
\end{enumerate}
No Hausdorff-distance obligation is stored outside these displayed rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:hausdorff-metric-carrier}. The packet lists the shared metric source, the two compact or located subset rows, the two directed distance ledgers, the maximum packaging row, transport, continuation, provenance, and local naming.

Classifier transport is componentwise. A replacement of either subset row first follows the stored $\hsame$ rows, then replays the displayed $\Cont$ routes through the same metric source and the same ball and real-distance ledgers.

Directed-distance stability is read separately from $d_A$ and $d_B$. Each directed ledger stores the inspected source point, the finite-net or located-distance witness on the opposite side, the metric-ball incidence row, the rational tolerance bound, and the $\RealUp$ seal, so a refinement may tighten the visible witness while retaining the same route shape.

The symmetric read is available only after both directed ledgers have been displayed. The row $h$ packages those two directed reads by a finite maximum certificate and exposes that packaged value as the Hausdorff tolerance.

Finally, $P$ and $N$ name only the rows displayed in the carrier. Since none of those rows contains a host subset, quotient subset equality, selected supremum, open-cover compactness, ambient hyperspace completeness, or Gromov-Hausdorff comparison, the NameCert surface cannot export such data.
\end{proof}

\begin{theorem}[HausdorffMetric finite-net stability]
\label{thm:hausdorff-metric-finite-net-stability}
Let
$$
K=(X,A,B,d_A,d_B,h,H,C,P,N)
$$
be an accepted $\HausdorffMetricUp$ carrier. If the compact or located subset rows $A$ and $B$ are replaced by displayed finite-net refinements over the same metric source $X$, then the transported carrier preserves the Hausdorff tolerance ledger displayed by $d_A,d_B,h,H,C,P,N$. The refinement may expose smaller finite windows, sharper located-distance witnesses, and tighter metric-ball incidences, but it does not introduce host subsets, quotient points, selected suprema, open-cover compactness, ambient hyperspace completeness, or Gromov-Hausdorff data.
\end{theorem}
\begin{proof}
Start with the accepted carrier and project the rows from \autoref{def:hausdorff-metric-carrier}. The shared metric source $X$ remains fixed, so the finite-net refinements of $A$ and $B$ are read as subset-row refinements over the same distance classifier and ball ledger.

Apply the classifier-transport and directed-distance rows of \autoref{thm:hausdorff-metric-namecert-obligations}. They move the refined subset rows along $H$, replay the route through $C$, and keep each directed ledger attached to its inspected point, opposite-side witness, ball incidence, rational tolerance, and $\RealUp$ seal.

The row $h$ then packages the transported directed ledgers in the same symmetric maximum format. Thus the public Hausdorff tolerance read remains a read of $d_A,d_B,h,H,C,P,N$, with only the displayed finite witnesses refined.

The non-escape row rules out all additional sources. A finite-net refinement has no coordinate from which to obtain host subsets, quotient points, selected suprema, open-cover compactness, ambient hyperspace completeness, or Gromov-Hausdorff data, so the transported carrier preserves the displayed Hausdorff ledger.
\end{proof}

\begin{closurestatus}{\HausdorffMetricUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hausdorff-metric-carrier}, \autoref{thm:hausdorff-metric-namecert-obligations}, and \autoref{thm:hausdorff-metric-finite-net-stability} seed the finite Hausdorff-distance interface over one metric source, two compact or located subset rows, directed distance ledgers, symmetric maximum packaging, and displayed provenance.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim ambient hyperspace completeness, quotient subset equality, Gromov-Hausdorff distance, open-cover compactness, selected suprema, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, directed-distance stability, symmetric max packaging, finite-net stability, and ledger non-escape for the same packet.}
  \constructivestory{A $\HausdorffMetricUp$ packet is generated from one metric source, two compact or located subset rows, two directed RealUp distance ledgers, a symmetric maximum row, componentwise transport, continuation replay, provenance, and a local NameCert row.}
\end{closurestatus}
