\chapter{A Concrete Naming Certificate for $\ClosedBoundedIntervalUp$}
\label{ch:concrete-instances-closedboundedinterval-namecert}
\origin{human}

Following Bishop and Bridges, the $\ClosedBoundedIntervalUp$ packet records a displayed closed bounded real interval as finite BEDC rows rather than as an ambient set of host reals. It consumes the located endpoint discipline of \autoref{ch:concrete-instances-locatedinterval-namecert}, supplies the base carrier read by the finite net route of \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}, and fixes the interval object consumed by the uniform-modulus chapter \autoref{ch:concrete-instances-closed-bounded-interval-uniform-modulus-namecert}. The packet is a finite certificate for lower and upper located endpoints, endpoint order, rational and dyadic containment ledgers, StreamName windows, RegSeqRat readbacks, RealUp sealing, transport, replay, provenance, and local naming. It is not an open-cover compactness theorem, quotient equality of reals, trichotomy, a selected point of the interval, or an ambient completeness principle.

\begin{definition}[Closed bounded interval carrier]
\label{def:closed-bounded-interval-carrier}
A $\ClosedBoundedIntervalUp$ carrier is a finite $\BHist$ packet
$$
I=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the lower located endpoint row, read through the located real and interval-endpoint surface of $\LocatedIntervalUp$;
\item $U$ is the upper located endpoint row, read through the same located endpoint surface;
\item $O$ is the endpoint-order row saying that the lower endpoint is admitted no later than the upper endpoint in every displayed containment read;
\item $Q$ is the rational containment ledger, recording finite rational tests that enter the closed interval through the endpoint rows and $O$;
\item $D$ is the dyadic containment ledger, refining the rational tests by finite dyadic cells and dyadic endpoint comparisons;
\item $S$ is the $\StreamNameUp$ window row used to inspect the endpoint names and containment tests at finite precision;
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same endpoint, rational-containment, and dyadic-containment windows;
\item $E$ is the $\RealUp$ seal row reached only after $L,U,O,Q,D,S,R$ have been displayed;
\item $H$ records componentwise $\hsame$ transports for the lower endpoint, upper endpoint, endpoint order, containment ledgers, windows, readbacks, and Real seal;
\item $C$ records displayed $\Cont$ replay from located endpoints through containment tests, StreamName windows, RegSeqRat readbacks, and RealUp sealing;
\item $P$ is the $\Pkg$ provenance over $\ClosedBoundedIntervalUp$, $\LocatedIntervalUp$, $\RationalIntervalUp$, $\DyadicIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ClosedBoundedIntervalUp}$ row.
\end{enumerate}
The carrier exports no open cover, hidden selector for a point in the interval, quotient real equality, trichotomy row, or completeness datum. Its public object is the finite endpoint-and-containment packet $I$.
\end{definition}
\leanchecked{BEDC.Derived.ClosedBoundedIntervalUp.ClosedBoundedIntervalTasteGate\_single\_carrier\_alignment}

\begin{definition}[Closed bounded interval classifier]
\label{def:closed-bounded-interval-classifier}
Two accepted $\ClosedBoundedIntervalUp$ carriers
$$
I=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
and
$$
I'=(L',U',O',Q',D',S',R',E',H',C',P',N')
$$
are classified together exactly when the displayed $\hsame$ rows transport $L$ to $L'$, $U$ to $U'$, $O$ to $O'$, $Q$ to $Q'$, $D$ to $D'$, $S$ to $S'$, $R$ to $R'$, and $E$ to $E'$, and the displayed $\Cont$ rows replay the same endpoint-to-containment-to-seal route on both packets. The classifier has no coordinate for host-level set equality, order trichotomy, quotient equality of real names, or a choice of representatives for endpoint streams.
\end{definition}

\begin{theorem}[Closed bounded interval NameCert obligations]
\label{thm:closed-bounded-interval-namecert-obligations}
For the carrier of \autoref{def:closed-bounded-interval-carrier}, the local $\NameCert_{\ClosedBoundedIntervalUp}$ surface consists exactly of carrier admission for $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$; endpoint admission for $L$ and $U$ through $\LocatedIntervalUp$; endpoint-order admission through $O$; rational and dyadic containment admission through $Q$ and $D$; StreamName and RegSeqRat readback through $S$ and $R$; RealUp sealing through $E$; classifier preservation under the componentwise $\hsame$ rows of $H$; displayed $\Cont$ replay through $C$; provenance through $P$; and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_semantic\_name\_certificate}
\begin{proof}
Project the carrier. Its endpoint rows $L$ and $U$, order row $O$, containment ledgers $Q$ and $D$, window row $S$, readback row $R$, seal row $E$, transport row $H$, replay row $C$, provenance row $P$, and local name $N$ are visible coordinates of one finite packet.

Endpoint and containment admission are read before the Real seal. The rational and dyadic ledgers are attached to the same lower and upper located endpoints and to the same endpoint-order row, so a containment consumer cannot replace the packet by a host interval or by an unrecorded order decision.

The structural rows close the naming surface. The componentwise $\hsame$ transports and displayed $\Cont$ routes preserve exactly the rows listed in the carrier, and the $\Pkg$ and $\NameCert$ rows name that finite route without adding any hidden selector, quotient equality, trichotomy, or completeness datum.
\end{proof}

\begin{theorem}[Closed bounded interval root obligation spine]
\label{thm:closed-bounded-interval-root-obligation-spine}
Every downstream $\ClosedBoundedIntervalUp$ consumer must read three root obligations through the existing carrier rows: endpoint-order exposure through $L,U,O$, containment-ledger exposure through $Q,D$, and $\StreamNameUp/\RegSeqRatUp/\RealUp$ seal handoff through $S,R,E$. These obligations are transported only by $H$, replayed only by $C$, recorded only by $P$, and named only by $N$.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_root\_obligation\_spine}
\begin{proof}
Project the carrier and classifier. The carrier of \autoref{def:closed-bounded-interval-carrier} supplies the endpoint, containment, schedule, readback, seal, transport, replay, provenance, and local naming rows, while \autoref{def:closed-bounded-interval-classifier} preserves those rows componentwise.

Apply the NameCert obligations of \autoref{thm:closed-bounded-interval-namecert-obligations}. They expose endpoint order through $O$, containment through $Q,D$, and the StreamName, RegSeqRat, and Real seal handoff through $S,R,E$.

The source nonescape and finite-net source theorems then keep interval-net, compactness-facing, and uniform-modulus consumers on the same root spine. Thus the downstream route cannot replace the endpoint order, containment ledger, or seal handoff by a host interval, selected subcover, quotient equality, or ambient completeness row.
\end{proof}

\begin{theorem}[Closed bounded interval carrier gate]
\label{thm:closedboundedinterval-carrier-gate}
Every accepted consumer route for a $\ClosedBoundedIntervalUp$ packet must display the carrier rows
$$
L,U,O,Q,D,S,R,E,H,C,P,N
$$
before it can read interval-net or compactness rows. In particular, an interval-net, nested-window, located-cover, compactness-facing, or uniform-modulus consumer cannot bypass lower endpoint, upper endpoint, endpoint order, rational containment, dyadic containment, StreamName window, RegSeqRat readback, Real seal, componentwise transport, displayed replay, provenance, or local naming.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_carrier\_gate}
\begin{proof}
Project the carrier of \autoref{def:closed-bounded-interval-carrier}. The rows $L,U,O,Q,D,S,R,E,H,C,P,N$ are the whole finite source surface of the closed bounded interval packet.

Apply the NameCert obligation theorem. Theorem~\ref{thm:closed-bounded-interval-namecert-obligations} lists exactly those rows as the local $\NameCert_{\ClosedBoundedIntervalUp}$ surface, so a consumer has no independent route into interval-net or compactness data.

Use the source-window and nonescape theorems. The source window of \autoref{def:closed-bounded-interval-source-window}, source transport of \autoref{thm:closed-bounded-interval-source-transport}, and source nonescape of \autoref{thm:closed-bounded-interval-source-nonescape} keep every downstream consumer behind the same displayed carrier gate.
\end{proof}

\begin{theorem}[Closed bounded interval dyadic-net ledger]
\label{thm:closedboundedinterval-dyadic-net-ledger}
Dyadic containment subledgers are the only finite-net source for $\ClosedBoundedIntervalUp$ consumers. Any finite-net read exported from an accepted packet must pass through the dyadic containment row $D$, together with the endpoint rows $L,U$, endpoint-order row $O$, rational containment row $Q$, StreamName window $S$, RegSeqRat readback $R$, Real seal $E$, and structural rows $H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_dyadic\_net\_ledger}
\begin{proof}
Start with the carrier and classifier. The carrier of \autoref{def:closed-bounded-interval-carrier} contains exactly one dyadic containment coordinate $D$, and the classifier of \autoref{def:closed-bounded-interval-classifier} transports that coordinate componentwise with the endpoint, rational-containment, StreamName, RegSeqRat, and Real-seal rows.

Apply the source-window route. The source window of \autoref{def:closed-bounded-interval-source-window} reads dyadic containment through the same endpoint-source packet before any interval-net or compactness consumer opens its own rows.

Finally apply finite-net source and source nonescape. Theorem~\ref{thm:closed-bounded-interval-finite-net-source} makes $D$ part of the required finite-net source, and \autoref{thm:closed-bounded-interval-source-nonescape} excludes any alternate host interval, open-cover, or choice-selected net source.
\end{proof}

\begin{theorem}[Closed bounded interval endpoint transport]
\label{thm:closedboundedinterval-endpoint-transport}
Classifier transport of a $\ClosedBoundedIntervalUp$ carrier is determined by componentwise $\hsame$ transport of lower endpoint, upper endpoint, endpoint order, rational containment, dyadic containment, StreamName window, RegSeqRat readback, and Real seal. The transported interval-net and compactness-facing routes are then replayed only through the displayed $\Cont$, provenance, and local naming rows of the same packet.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_endpoint\_transport}
\begin{proof}
Project two classified carriers through \autoref{def:closed-bounded-interval-classifier}. The classifier compares $L,U,O,Q,D,S,R,E$ only through the componentwise $\hsame$ rows stored in $H$.

Use source transport. Theorem~\ref{thm:closed-bounded-interval-source-transport} states that endpoint source windows move by exactly those componentwise rows before any interval-net or compactness consumer reads them.

The replay step is fixed by the carrier. The displayed $\Cont$ row $C$, provenance row $P$, and local naming row $N$ preserve the same transported endpoint route, and \autoref{thm:closed-bounded-interval-source-nonescape} prevents the transported consumer from importing host interval equality, quotient real equality, trichotomy, or ambient completeness.
\end{proof}

\begin{definition}[Closed bounded interval root source ledger]
\label{def:closed-bounded-interval-root-source-ledger}
For an accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$, the root source ledger is the finite $\BHist$ row
$$
\Lambda_I=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
read before any interval-net, compactness-facing, located-cover, nested-window, or uniform-modulus consumer opens a downstream row. The ledger records lower endpoint, upper endpoint, endpoint order, rational containment, dyadic containment, stream schedule, regular rational readback, Real seal, componentwise transport, displayed replay, provenance, and local naming as one source surface.
\end{definition}

\begin{theorem}[Closed bounded interval endpoint-containment route]
\label{thm:closed-bounded-interval-endpoint-containment-route}
Every containment consumer of an accepted $\ClosedBoundedIntervalUp$ carrier must pass through the endpoint and containment prefix
$$
L,U,O,Q,D
$$
of \autoref{def:closed-bounded-interval-root-source-ledger} before any finite-net, located-cover, nested-window, compactness, or uniform-modulus row is available. In particular, no downstream consumer can read a finite-net or compactness row while bypassing the lower endpoint, upper endpoint, endpoint-order row, rational containment ledger, or dyadic containment ledger of the root source packet.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_endpoint\_containment\_route}
\begin{proof}
Project the carrier and the root source ledger. By \autoref{def:closed-bounded-interval-carrier} and \autoref{def:closed-bounded-interval-root-source-ledger}, the endpoint rows $L,U$, order row $O$, and containment ledgers $Q,D$ are the first displayed source rows of the packet.

Apply the NameCert obligation theorem. The obligations of \autoref{thm:closed-bounded-interval-namecert-obligations} admit endpoint rows, endpoint order, and rational and dyadic containment before StreamName, RegSeqRat, Real sealing, transport, replay, provenance, or local naming can be consumed.

Finally use the source-window route. The source window of \autoref{def:closed-bounded-interval-source-window} and source transport of \autoref{thm:closed-bounded-interval-source-transport} keep the same prefix upstream of every interval-net or compactness-facing read, so no downstream row can bypass $L,U,O,Q,D$.
\end{proof}

\begin{theorem}[Closed bounded interval Real-seal root handoff]
\label{thm:closed-bounded-interval-real-seal-root-handoff}
For every accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$, the $\RealUp$ seal row $E$ is downstream of the $\StreamNameUp$ schedule $S$ and $\RegSeqRatUp$ readback row $R$, which themselves are downstream of the endpoint and containment prefix $L,U,O,Q,D$. The root handoff exports no selected point, quotient equality, trichotomy row, selected subcover, or ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedBoundedIntervalUp.ClosedBoundedIntervalPacket\_real\_seal\_root\_handoff}
\begin{proof}
Start with the root source ledger. It records the route $L,U,O,Q,D,S,R,E,H,C,P,N$ as one finite $\BHist$ source surface, so the seal row is not available before the schedule and readback rows are displayed.

Use the existing source-window theorem. By \autoref{def:closed-bounded-interval-source-window}, the $\StreamNameUp$ row $S$, $\RegSeqRatUp$ row $R$, and $\RealUp$ seal $E$ are read from the same endpoint-source packet after the endpoint and containment rows.

The non-escape conclusion follows from \autoref{thm:closed-bounded-interval-source-nonescape}. Since the carrier and source route contain no selected point, quotient equality, trichotomy row, selected subcover, or ambient completeness coordinate, the Real-seal handoff cannot export any of them.
\end{proof}

\input{parts/concrete_instances/closedboundedinterval/root_source_obligations}

\begin{definition}[Closed bounded interval source window]
\label{def:closed-bounded-interval-source-window}
For an accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$, the source window is the finite $\BHist$ row
$$
\Omega_I=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
read as the endpoint-source packet before any interval-net, compactness, or uniform-modulus consumer opens its own rows. The lower and upper endpoint rows $L,U$ are read through $\LocatedIntervalUp$, the dyadic containment ledger $D$ is read through $\DyadicIntervalUp$, the finite observation schedule $S$ is read through $\StreamNameUp$, the regular rational readback $R$ is read through $\RegSeqRatUp$, and the terminal endpoint seal $E$ is read through $\RealUp$. The rows $H,C,P,N$ record the componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\ClosedBoundedIntervalUp}$ naming for the same endpoint-source route.
\end{definition}

\begin{theorem}[Closed bounded interval source transport]
\label{thm:closed-bounded-interval-source-transport}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ and $I'=(L',U',O',Q',D',S',R',E',H',C',P',N')$ be accepted $\ClosedBoundedIntervalUp$ carriers classified together by \autoref{def:closed-bounded-interval-classifier}. Any endpoint source window transported from $I$ to $I'$ carries $L,U,O,Q,D,S,R,E$ through the componentwise $\hsame$ rows of $H$ and then replays the same route through the displayed $\Cont$ rows of $C$ before any interval-net or compactness consumer reads it.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_source\_transport}
\begin{proof}
Project the two carriers and the classifier. The rows $L,U,O,Q,D,S,R,E$ and $L',U',O',Q',D',S',R',E'$ are the endpoint, containment, window, readback, and Real-seal coordinates being compared.

Use the source window of \autoref{def:closed-bounded-interval-source-window}. It lists the same rows as a $\BHist$ endpoint-source packet, so transport of the source window is exactly componentwise transport of lower endpoint, upper endpoint, order, rational containment, dyadic containment, $\StreamNameUp$ schedule, $\RegSeqRatUp$ readback, and $\RealUp$ seal rows.

The replay step is downstream. The displayed $\Cont$ rows in $C$ carry the transported endpoint-source route to consumers only after the $\hsame$ transport has preserved every listed coordinate. Thus an interval-net, compactness, or uniform-modulus consumer cannot read a transported source window before the endpoint rows have passed through $H$ and $C$.
\end{proof}

\begin{theorem}[Closed bounded interval source nonescape]
\label{thm:closed-bounded-interval-source-nonescape}
Every interval-net, nested-window, located-cover, compactness-facing, or uniform-modulus consumer of an accepted $\ClosedBoundedIntervalUp$ source window factors through
$$
L,U,O,Q,D,S,R,E,H,C,P,N .
$$
In particular, the consumer first reads the $\BHist$ endpoint-source rows, the $\LocatedIntervalUp$ endpoint route, the $\DyadicIntervalUp$ containment ledger, the $\StreamNameUp$ schedule, the $\RegSeqRatUp$ readback, and the $\RealUp$ seal before it reads any downstream interval-net or compactness rows. The source window cannot expose a host interval set, open-cover compactness, selected point, selected subcover, quotient real equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_source\_nonescape}
\begin{proof}
Start from the source window. By \autoref{def:closed-bounded-interval-source-window}, every endpoint-source read is one of $L,U,O,Q,D,S,R,E,H,C,P,N$.

Next apply source transport. Theorem~\ref{thm:closed-bounded-interval-source-transport} forces transported endpoint-source reads through the $\hsame$ and $\Cont$ rows before any downstream consumer can inspect them.

Finally compare with the existing finite-cover, dyadic-net, located-cover, and compactness handoffs in this chapter. Each of those consumers reads the closed bounded interval through the displayed endpoint, containment, schedule, readback, seal, transport, replay, provenance, and local naming rows. Since none of those rows is a host interval set, open cover, selected point, quotient equality, trichotomy decision, choice selector, or ambient completeness theorem, the source window has no route to any excluded object.
\end{proof}

\begin{definition}[Closed bounded interval finite-cover window]
\label{def:closed-bounded-interval-finite-cover-window}
For an accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ as in \autoref{def:closed-bounded-interval-carrier}, a finite-cover window is a finite $\BHist$ row
$$
W_I=(S_0,R_0,Q_0,D_0,E_0)
$$
whose $\StreamNameUp$ coordinate $S_0$ is a subwindow of the carried row $S$, whose $\RegSeqRatUp$ coordinate $R_0$ is read through $R$, whose rational and dyadic containment ledgers $Q_0,D_0$ are subledgers of $Q,D$, and whose endpoint seal $E_0$ is reached through the same $\RealUp$ row $E$. The window is admissible only when its lower-endpoint, upper-endpoint, endpoint-order, rational-containment, dyadic-containment, readback, and seal reads are all classifier-preserved by the carrier rows $H$ and $C$ of \autoref{def:closed-bounded-interval-classifier}.
\end{definition}

\begin{theorem}[Closed bounded interval finite-net source]
\label{thm:closed-bounded-interval-finite-net-source}
Every finite-net consumer of an accepted $\ClosedBoundedIntervalUp$ carrier
$$
I=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
must read the lower endpoint $L$, upper endpoint $U$, endpoint-order row $O$, rational containment ledger $Q$, and dyadic containment ledger $D$ before any net row is available. The $\StreamNameUp$ window $S$, $\RegSeqRatUp$ readback $R$, and $\RealUp$ seal $E$ are downstream of the same endpoint and containment route, with $H,C,P,N$ preserving the route under transport, replay, provenance, and local naming.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_finite\_net\_source}
\begin{proof}
Start with the carrier of \autoref{def:closed-bounded-interval-carrier}. Its finite-net source coordinates are the lower endpoint, upper endpoint, endpoint order, rational containment, and dyadic containment rows $L,U,O,Q,D$.

Apply the classifier and source-window definitions. The classifier of \autoref{def:closed-bounded-interval-classifier} preserves these rows componentwise, while \autoref{def:closed-bounded-interval-source-window} reads them before any downstream interval-net, compactness, or uniform-modulus consumer opens its own rows.

Finally use source nonescape, \autoref{thm:closed-bounded-interval-source-nonescape}. It forces every interval-net read through $L,U,O,Q,D,S,R,E,H,C,P,N$, so the endpoint and containment rows are the required source before any finite-net row can be consumed.
\end{proof}

\begin{theorem}[Closed bounded interval RegSeqRat window]
\label{thm:closed-bounded-interval-regseqrat-window}
For accepted $\ClosedBoundedIntervalUp$ carriers
$$
I=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
and
$$
I'=(L',U',O',Q',D',S',R',E',H',C',P',N')
$$
classified together, each finite-cover window preserves its $\StreamNameUp$ and $\RegSeqRatUp$ readback rows under componentwise $\hsame$ transport. In particular, every transported window carries $S,R$ to $S',R'$ only after $L,U,O,Q,D$ have been transported to $L',U',O',Q',D'$ and replayed through the displayed $\Cont$ rows.
\end{theorem}
\begin{proof}
Project the two carriers and the classifier of \autoref{def:closed-bounded-interval-classifier}. The classifier compares endpoint, containment, window, readback, and seal rows only by componentwise $\hsame$ transport and displayed replay.

Use the finite-cover window of \autoref{def:closed-bounded-interval-finite-cover-window}. Its $S_0$ and $R_0$ rows are subwindow and readback rows of the carried $S$ and $R$, while $Q_0,D_0,E_0$ remain attached to the same endpoint and containment route.

Now apply source transport, \autoref{thm:closed-bounded-interval-source-transport}. It transports the endpoint and containment rows before the StreamName and RegSeqRat rows are available to consumers. Hence a transported finite-cover window preserves the $S,R$ readback route under the same componentwise transport and replay.
\end{proof}
\leanchecked{BEDC.Derived.ClosedboundedintervalUp.ClosedBoundedIntervalPacket\_regseqrat\_window}

\begin{theorem}[Closed bounded interval Real seal nonescape]
\label{thm:closed-bounded-interval-real-seal-nonescape}
For an accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$, the $\RealUp$ seal row $E$ exports only the endpoint route displayed by $L,U,O,Q,D,S,R,H,C,P,N$. It exports no open-cover compactness, selected point, selected subcover, quotient equality of Real names, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the carrier and source window. The seal row $E$ is reached only after the endpoint rows $L,U$, endpoint order $O$, rational and dyadic containment ledgers $Q,D$, StreamName window $S$, and RegSeqRat readback $R$ have been displayed.

Apply source nonescape and finite-cover nonescape. Theorems~\ref{thm:closed-bounded-interval-source-nonescape} and \ref{thm:closed-bounded-interval-finite-cover-nonescape} keep every consumer route inside the displayed endpoint, containment, window, readback, seal, transport, replay, provenance, and local naming rows.

The excluded objects have no carrier coordinate and no replay edge. Since $H,C,P,N$ only transport, replay, source, and name the same finite route, the Real seal cannot export open-cover compactness, selected points or subcovers, quotient equality, trichotomy, countable choice, or ambient Real completeness.
\end{proof}

\begin{theorem}[Closed bounded interval finite-cover nonescape]
\label{thm:closed-bounded-interval-finite-cover-nonescape}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ be an accepted $\ClosedBoundedIntervalUp$ carrier, and let $W_I=(S_0,R_0,Q_0,D_0,E_0)$ be a finite-cover window in the sense of \autoref{def:closed-bounded-interval-finite-cover-window}. Every finite-cover read exported to an interval-net, nested-window, or uniform-modulus consumer factors through
$$
L,U,O,Q_0,D_0,S_0,R_0,E_0,H,C,P,N .
$$
Consequently the read cannot escape to a host open cover, a selected subcover, quotient real equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the finite-cover window. By definition, $S_0$ and $R_0$ are read through the carried $\StreamNameUp$ and $\RegSeqRatUp$ rows, while $Q_0$ and $D_0$ are subledgers of the rational and dyadic containment rows attached to the same endpoints.

The endpoint route is fixed before the cover window is visible. The rows $L,U,O$ must be displayed before $Q_0,D_0,S_0,R_0$ can be read, and the terminal seal $E_0$ is reached only through the carried $\RealUp$ row $E$.

The structural rows close the nonescape claim. Since $H$ and $C$ preserve exactly the carrier and window rows named above, and since $P,N$ only source and name that route, no exported finite-cover read contains a host open cover, selected subcover, quotient real equality, trichotomy, choice selector, or ambient completeness datum.
\end{proof}

\begin{theorem}[Closed bounded interval finite-net compactness obligations]
\label{thm:closed-bounded-interval-finite-net-compactness-obligations}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ be an accepted $\ClosedBoundedIntervalUp$ carrier, and let $W_I=(S_0,R_0,Q_0,D_0,E_0)$ be a finite-cover window in the sense of \autoref{def:closed-bounded-interval-finite-cover-window}. Any finite-net compactness consumer must expose the endpoint rows $L,U,O$, the rational and dyadic containment rows $Q,D$, the $\StreamNameUp$ and $\RegSeqRatUp$ rows $S,R$, the $\RealUp$ seal $E$, and the transport, replay, provenance, and local naming rows $H,C,P,N$ before it may read mesh centers, finite cover refinements, or interval compactness ledgers.

Consequently such a consumer factors through \autoref{def:closed-bounded-interval-carrier}, \autoref{def:closed-bounded-interval-finite-cover-window}, \autoref{thm:closed-bounded-interval-source-nonescape}, and \autoref{thm:closed-bounded-interval-net-handoff}. It does not export open-cover compactness, selected subcovers, countable choice, quotient real equality, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier and finite-cover window. The carrier exposes only $L,U,O,Q,D,S,R,E,H,C,P,N$, while the window exposes $S_0,R_0,Q_0,D_0,E_0$ as subwindow, readback, containment, dyadic, and seal rows attached to the same endpoint route.

Apply source nonescape. Theorem~\ref{thm:closed-bounded-interval-source-nonescape} keeps every interval-net or compactness-facing read downstream of the displayed endpoint, containment, window, readback, Real-seal, transport, replay, provenance, and local naming rows.

Apply the net handoff. Theorem~\ref{thm:closed-bounded-interval-net-handoff} allows a net consumer to add mesh-specific cells, centers, and coverage data only after the base interval route has been displayed. Hence finite cover refinements and compactness ledgers remain downstream of $L,U,O,Q,D,S,R,E,H,C,P,N$.

The excluded compactness principles have no coordinate in either displayed packet. Since neither the carrier nor the window stores an open cover, selected subcover, choice selector, quotient-real equality, trichotomy decision, or ambient completeness datum, the finite-net compactness consumer cannot read any of them from this obligation surface.
\end{proof}

\begin{theorem}[Closed bounded interval located endpoint readback]
\label{thm:closed-bounded-interval-located-endpoint-readback}
For an accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$, every endpoint-facing $\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ readback of the lower or upper endpoint factors through the displayed route
$$
L,U,O \longmapsto S,R \longmapsto E \longmapsto H,C,P,N .
$$
The readback therefore preserves the endpoint-order row and the rational and dyadic containment ledgers of \autoref{def:closed-bounded-interval-carrier}; it does not replace the endpoints by host reals or by quotient representatives.
\end{theorem}
\begin{proof}
Start with an endpoint-facing request. The carrier exposes lower and upper endpoint data only as $L$ and $U$, and the order row $O$ is carried before any rational, dyadic, stream, or regular-readback inspection.

The finite readback rows are next. The $\StreamNameUp$ windows in $S$ and the $\RegSeqRatUp$ rows in $R$ inspect the displayed endpoint names and containment ledgers, and the $\RealUp$ seal $E$ is downstream of those finite windows.

Finally apply the classifier of \autoref{def:closed-bounded-interval-classifier}. Its componentwise $\hsame$ rows and displayed $\Cont$ replay preserve the same endpoint, order, containment, window, readback, and seal coordinates, so the readback cannot be reinterpreted as a host-real endpoint or as a quotient representative outside the accepted packet.
\end{proof}

\begin{theorem}[Closed bounded interval endpoint-order transport]
\label{thm:closed-bounded-interval-endpoint-order-transport}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ and $I'=(L',U',O',Q',D',S',R',E',H',C',P',N')$ be accepted $\ClosedBoundedIntervalUp$ carriers classified together by \autoref{def:closed-bounded-interval-classifier}. Every containment read transported from $I$ to $I'$ carries the endpoint-order row $O$ to $O'$ before it transports the rational ledger $Q$ to $Q'$ or the dyadic ledger $D$ to $D'$. Consequently no consumer can preserve containment while dropping endpoint order or replacing it by a host-level comparison.
\end{theorem}
\begin{proof}
Start from the classifier. It classifies accepted carriers only by componentwise $\hsame$ transport and replay of the same endpoint-to-containment-to-seal route.

The endpoint-order coordinate is upstream of both containment ledgers. A transported rational or dyadic containment read therefore has already transported $L,U,O$ to $L',U',O'$ before it reaches $Q',D'$.

The replay rows preserve the same order. Since neither the carrier nor the classifier contains a host comparison, trichotomy row, quotient-real equality witness, or alternate endpoint selector, the transported containment read cannot drop $O'$ or replace it by data outside the accepted packet.
\end{proof}

\begin{theorem}[Closed bounded interval net handoff]
\label{thm:closed-bounded-interval-net-handoff}
Every $\ClosedBoundedIntervalNetUp$ or $\ClosedBoundedIntervalUniformModulusUp$ consumer of an accepted $\ClosedBoundedIntervalUp$ carrier reads the base interval through the finite route
$$
L,U,O,Q,D,S,R,E,H,C,P,N.
$$
The interval-net chapter \autoref{ch:concrete-instances-closedboundedintervalnet-namecert} may add mesh scales, cells, centers, and coverage rows only after the base endpoint and containment route has been displayed. The uniform-modulus chapter \autoref{ch:concrete-instances-closed-bounded-interval-uniform-modulus-namecert} may read Heine--Cantor interval data only through that base route and its downstream finite-cover ledgers.
\end{theorem}
\begin{proof}
Read the base carrier first. The route $L,U,O,Q,D,S,R,E,H,C,P,N$ exposes lower and upper located endpoints, endpoint order, rational and dyadic containment, finite windows, readbacks, Real sealing, transport, replay, provenance, and local naming.

The interval-net handoff then appends its mesh-specific rows. Its finite cells, dyadic refinements, centers, and coverage ledger are downstream of the displayed endpoint and containment rows, so the net packet cannot treat the mesh as the interval object itself.

The uniform-modulus handoff is later still. It reads compactness and modulus data through finite cover and Lebesgue-number ledgers, while the source interval remains the accepted $\ClosedBoundedIntervalUp$ route. Thus no consumer receives an open cover, selected subcover, quotient real equality, host interval set, or ambient completeness row in place of the base carrier.
\end{proof}

\begin{theorem}[Closed bounded interval nested compactness handoff]
\label{thm:closed-bounded-interval-nested-compactness-handoff}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ be an accepted $\ClosedBoundedIntervalUp$ carrier, and let a finite prefix of a nested-interval display be read inside the same closed bounded interval. The accepted packet supplies the endpoint-order row $O$, the rational and dyadic containment ledgers $Q,D$, the $\StreamNameUp$ window row $S$, the $\RegSeqRatUp$ readback row $R$, and the $\RealUp$ seal row $E$ required by the finite-window $\NestedIntervalCompactnessUp$ route. The handoff is therefore a row-level bridge from the closed bounded interval carrier to the nested-window consumer of \autoref{thm:nested-interval-compactness-real-seal-boundary}; it does not export open-cover compactness, selected endpoints, quotient real equality, trichotomy, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the accepted $\ClosedBoundedIntervalUp$ carrier. By \autoref{thm:closed-bounded-interval-endpoint-order-transport}, any transported containment read keeps the endpoint-order row upstream of the rational and dyadic ledgers.

Apply \autoref{thm:closed-bounded-interval-net-handoff}. The finite consumer receives the base interval only through the displayed route $L,U,O,Q,D,S,R,E,H,C,P,N$, so a nested prefix displayed inside that interval must inherit the same endpoint, containment, window, readback, and seal rows.

The nested-window side then reads exactly the finite route isolated by \autoref{thm:nested-interval-compactness-real-seal-boundary}. Since neither source packet contains an open cover, endpoint selector, quotient-real equality, trichotomy decision, countable-choice selector, or ambient completeness datum, the handoff cannot add any such row.
\end{proof}

\begin{theorem}[Closed bounded interval Cantor intersection handoff]
\label{thm:closed-bounded-interval-cantor-intersection-handoff}
Let a decreasing finite-window family of accepted $\ClosedBoundedIntervalUp$ packets be consumed by $\CantorIntersectionUp$. The consumer may read the family only through endpoint rows, endpoint-order transport, rational and dyadic containment ledgers, $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, $\RealUp$ seals, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ rows of the accepted packets.

The handoff supplies the finite nested-window data needed by the Cantor-intersection route. It does not export open-cover compactness, a choice-selected point, quotient real equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with endpoint-order transport. The endpoint classifier stability route keeps lower endpoints, upper endpoints, and order rows upstream of every containment read in the decreasing family.

Use the finite-net source and RegSeqRat window theorems. They place rational containment ledgers, dyadic containment ledgers, $\StreamNameUp$ windows, and $\RegSeqRatUp$ readbacks inside the displayed finite packet before any nested-family consumer can inspect the windows.

The Real seal nonescape theorem then keeps each endpoint and containment read behind the same $\RealUp$ seal row. Thus the Cantor-facing consumer receives sealed finite windows, not quotient real representatives or an ambient completeness theorem.

Finally apply the nested compactness handoff \autoref{thm:closed-bounded-interval-nested-compactness-handoff}. It already routes nested-window compactness through the accepted closed bounded interval packet, so the Cantor-intersection handoff is exactly the same finite endpoint, containment, window, readback, seal, transport, replay, provenance, and local-name surface.
\end{proof}

\begin{theorem}[Closed bounded interval dyadic-net obligations]
\label{thm:closed-bounded-interval-dyadic-net-obligations}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ be an accepted $\ClosedBoundedIntervalUp$ carrier. Every $\DyadicIntervalUp$ net or $\LocatedIntervalUp$ refinement read attached to $I$ must display the endpoint rows $L,U$, the endpoint-order row $O$, the rational and dyadic containment ledgers $Q,D$, and the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ readback route $S,R,E$ before the local $\NameCert_{\ClosedBoundedIntervalUp}$ row is consumed. The dyadic-net obligations are therefore rows of the same $\BHist$ packet and not an open-cover compactness principle, a selected mesh point, quotient real equality, trichotomy, or countable choice.
\end{theorem}
\begin{proof}
Project the accepted carrier. Its endpoint, order, rational containment, dyadic containment, finite-window, regular readback, and Real seal rows are already displayed as $L,U,O,Q,D,S,R,E$.

A dyadic-net consumer may refine the interval only through the dyadic ledger $D$ and the rational containment ledger $Q$ over the same located endpoints. The rows $S,R,E$ then read those finite tests through StreamName, RegSeqRat, and Real-facing windows without replacing the interval by a host set.

Transport and replay preserve the same route. Since $H,C,P,N$ only carry componentwise $\hsame$, displayed $\Cont$, provenance, and local naming for the listed rows, no dyadic-net read can add an open cover, selected mesh point, quotient equality, trichotomy decision, choice schedule, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[Closed bounded interval containment-ledger obligations]
\label{thm:closed-bounded-interval-containment-ledger-obligations}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ be an accepted $\ClosedBoundedIntervalUp$ carrier. Every containment-ledger obligation for $I$ is a $\BHist$ obligation over the displayed endpoint rows $L,U$, endpoint-order row $O$, rational and dyadic containment rows $Q,D$, componentwise $\hsame$ row $H$, displayed $\Cont$ replay row $C$, $\Pkg$ provenance row $P$, and local $\NameCert_{\ClosedBoundedIntervalUp}$ row $N$. The ledger must preserve endpoint order before rational or dyadic containment is exported, and it cannot read host interval sets, quotient real equality, trichotomy, selected points, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:closed-bounded-interval-carrier} and the classifier of \autoref{def:closed-bounded-interval-classifier}. The displayed endpoint rows, order row, containment ledgers, transport, replay, provenance, and local name are exactly $L,U,O,Q,D,H,C,P,N$.

Apply source nonescape, finite-cover nonescape, and endpoint-order transport. Theorems~\ref{thm:closed-bounded-interval-source-nonescape}, \ref{thm:closed-bounded-interval-finite-cover-nonescape}, and \ref{thm:closed-bounded-interval-endpoint-order-transport} force every containment read to keep $O$ upstream of $Q$ and $D$ and to pass through the displayed $\hsame$ and $\Cont$ rows.

Finally use the dyadic-net obligations of \autoref{thm:closed-bounded-interval-dyadic-net-obligations}. They place every dyadic or located refinement inside the same $\BHist$ packet, while $P$ and $N$ only source and name that route. Thus no excluded host object is introduced by the containment ledger.
\end{proof}

\begin{theorem}[Closed bounded interval finite-window transport obligations]
\label{thm:closed-bounded-interval-finite-window-transport-obligations}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ and $I'=(L',U',O',Q',D',S',R',E',H',C',P',N')$ be accepted $\ClosedBoundedIntervalUp$ carriers classified together. Every finite-window transport obligation from $I$ to $I'$ is a $\BHist$ transport obligation that carries $S,R,E$ to $S',R',E'$ only after $L,U,O,Q,D$ have been transported to $L',U',O',Q',D'$ through the displayed $\hsame$ row $H$ and replayed by the displayed $\Cont$ row $C$. The transported window remains sourced by $\Pkg$ provenance and named by $\NameCert$, not by host equality of intervals or selected representatives.
\end{theorem}
\begin{proof}
Start with source transport. Theorem~\ref{thm:closed-bounded-interval-source-transport} says that a transported source window carries lower endpoint, upper endpoint, endpoint order, containment, window, readback, and seal rows componentwise before any downstream consumer reads them.

Use located endpoint readback and finite-cover nonescape. Theorems~\ref{thm:closed-bounded-interval-located-endpoint-readback} and \ref{thm:closed-bounded-interval-finite-cover-nonescape} identify $S,R,E$ as downstream finite windows over the same endpoint and containment route, so their transport cannot be separated from $L,U,O,Q,D$.

The nested compactness handoff and dyadic-net obligations preserve the same route for later consumers. Theorems~\ref{thm:closed-bounded-interval-nested-compactness-handoff} and \ref{thm:closed-bounded-interval-dyadic-net-obligations} keep the finite-window rows inside the displayed $\BHist$ packet, with $P,N$ recording provenance and local naming only.
\end{proof}

\begin{theorem}[Closed bounded interval consumer nonescape obligations]
\label{thm:closed-bounded-interval-consumer-nonescape-obligations}
Every interval-net, located-cover, nested-compactness, finite-window, or uniform-modulus consumer of an accepted $\ClosedBoundedIntervalUp$ carrier factors its $\BHist$ read through
$$
L,U,O,Q,D,S,R,E,H,C,P,N .
$$
The consumer therefore sees $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\ClosedBoundedIntervalUp}$ naming for the displayed carrier rows before it sees any downstream conclusion. It cannot escape to open-cover compactness, selected subcovers, selected points, quotient real equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First project the carrier and source nonescape route. The carrier definition and \autoref{thm:closed-bounded-interval-source-nonescape} expose only $L,U,O,Q,D,S,R,E,H,C,P,N$ to endpoint-source consumers.

Next compose the finite-cover, located-cover, endpoint-order, and dyadic-net obligations. Theorems~\ref{thm:closed-bounded-interval-finite-cover-nonescape}, \ref{thm:closed-bounded-interval-located-cover-handoff}, \ref{thm:closed-bounded-interval-endpoint-order-transport}, and \ref{thm:closed-bounded-interval-dyadic-net-obligations} keep every net or cover read downstream of the same displayed endpoint, containment, window, readback, and seal rows.

Finally apply nested compactness and compactness consumer boundary. Theorems~\ref{thm:closed-bounded-interval-nested-compactness-handoff} and \ref{thm:closed-bounded-interval-compactness-consumer-boundary} show that later compactness-facing consumers inherit the same finite packet. Since the packet contains no open-cover compactness theorem, selected object, quotient equality, trichotomy decision, countable-choice row, or ambient completeness row, the consumer obligations are nonescaping.
\end{proof}

\begin{theorem}[Closed bounded interval located-cover handoff]
\label{thm:closed-bounded-interval-located-cover-handoff}
Every located-cover consumer of an accepted $\ClosedBoundedIntervalUp$ carrier factors through the displayed route
$$
L,U,O,Q,D,S,R,E,H,C,P,N
$$
before reading any $\NestedIntervalCompactnessUp$ or compactness-facing row. The $\LocatedIntervalUp$ and $\RationalIntervalUp$ data supply finite containment tests, the $\DyadicIntervalUp$ ledger supplies the mesh boundary, and the $\RealUp$ readback remains downstream of the same displayed packet.
\end{theorem}
\begin{proof}
Start with the located endpoint surface. The rows $L,U,O$ must be visible before a located-cover row can decide which rational or dyadic containment tests are being inspected.

The cover handoff then reads $Q,D,S,R,E$. Rational and dyadic ledgers provide finite containment data, while StreamName and RegSeqRat windows carry those tests to the Real seal without choosing a subcover or a point of the interval.

Finally use $H,C,P,N$. These structural rows replay and name exactly the displayed route, so a compactness-facing consumer receives a located-cover handoff over the accepted packet and not an open-cover theorem, quotient real equality, trichotomy, countable choice, or ambient completeness.
\end{proof}

\begin{theorem}[Closed bounded interval located-cover source totality]
\label{thm:closed-bounded-interval-located-cover-source-totality}
Any located-cover consumer of an accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ must read the endpoint rows $L,U,O$, containment ledgers $Q,D$, $\StreamNameUp$ row $S$, $\RegSeqRatUp$ readback $R$, $\RealUp$ seal $E$, and structural rows $H,C,P,N$ before consuming a $\LocatedIntervalCoverUp$ row. The located-cover source is therefore the full displayed endpoint-and-containment packet, not a parameter echo of the cover consumer.
\end{theorem}
\begin{proof}
Project the carrier and the source window. The carrier of \autoref{def:closed-bounded-interval-carrier} lists $L,U,O,Q,D,S,R,E,H,C,P,N$, while \autoref{def:closed-bounded-interval-source-window} reads the same rows as the endpoint-source packet.

Apply source nonescape and finite-net source. Theorems~\ref{thm:closed-bounded-interval-source-nonescape} and \ref{thm:closed-bounded-interval-finite-net-source} force every interval-net, located-cover, or compactness-facing read through the endpoint rows, containment ledgers, observation schedule, readback, and seal before any downstream cover row is available.

Finally use the located-cover handoff. Theorem~\ref{thm:closed-bounded-interval-located-cover-handoff} keeps the cover consumer on the same displayed route, with $H,C,P,N$ preserving replay, provenance, and local naming. Thus a $\LocatedIntervalCoverUp$ row can only be consumed after the full source package has been exposed.
\end{proof}

\begin{theorem}[Closed bounded interval compactness consumer boundary]
\label{thm:closed-bounded-interval-compactness-consumer-boundary}
Any $\NestedIntervalCompactnessUp$ consumer, finite-net compactness consumer, or Real-completion consumer that reads an accepted $\ClosedBoundedIntervalUp$ packet must keep the endpoint rows, dyadic-net rows, located-cover rows, and nested compactness rows displayed before any compactness conclusion is consumed. Thus every such consumer factors through the carrier route of \autoref{def:closed-bounded-interval-carrier}, the dyadic-net obligations of \autoref{thm:closed-bounded-interval-dyadic-net-obligations}, the located-cover handoff of \autoref{thm:closed-bounded-interval-located-cover-handoff}, and the nested compactness handoff of \autoref{thm:closed-bounded-interval-nested-compactness-handoff}.
\end{theorem}
\begin{proof}
First read the source carrier. The endpoint, order, containment, window, readback, seal, transport, replay, provenance, and naming rows of $I$ are the only rows a consumer can project from $\ClosedBoundedIntervalUp$.

Next apply the dyadic-net and located-cover handoffs. They force finite mesh and cover consumers to pass through $Q,D,S,R,E$ over the same $L,U,O$ endpoint route.

Finally pass to nested compactness. The nested-window consumer reads the same displayed interval data before it uses any compactness-facing row, so the boundary excludes open-cover compactness, selected subcovers, selected endpoints, quotient real equality, trichotomy, countable choice, and ambient completeness as hidden inputs.
\end{proof}

\begin{theorem}[Closed bounded interval endpoint classifier stability]
\label{thm:closed-bounded-interval-endpoint-classifier-stability}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ and $I'=(L',U',O',Q',D',S',R',E',H',C',P',N')$ be accepted $\ClosedBoundedIntervalUp$ carriers classified together. Any classifier-preserved endpoint read from $I$ to $I'$ keeps the lower endpoint row $L$, upper endpoint row $U$, and endpoint-order row $O$ upstream of the rational containment ledger $Q$, dyadic containment ledger $D$, $\StreamNameUp$ window $S$, $\RegSeqRatUp$ readback $R$, $\RealUp$ seal $E$, componentwise $\hsame$ row $H$, displayed $\Cont$ replay row $C$, $\Pkg$ provenance row $P$, and local $\NameCert_{\ClosedBoundedIntervalUp}$ row $N$.
\end{theorem}
\begin{proof}
Start with the classifier of \autoref{def:closed-bounded-interval-classifier}. It classifies two carriers only by transporting $L,U,O,Q,D,S,R,E$ componentwise and replaying the same endpoint-to-containment-to-seal route through the displayed $\Cont$ rows.

The endpoint rows are therefore the source of the route. The finite-net source theorem and endpoint-order transport theorem, \autoref{thm:closed-bounded-interval-finite-net-source} and \autoref{thm:closed-bounded-interval-endpoint-order-transport}, place $L,U,O$ before any rational, dyadic, window, readback, or seal row can be consumed.

Finally read the structural rows. The rows $H,C,P,N$ transport, replay, source, and name exactly that displayed route, so classifier preservation cannot expose $Q,D,S,R,E,H,C,P,N$ before the endpoint classifier has already preserved $L,U,O$.
\end{proof}

\begin{theorem}[Closed bounded interval dyadic containment totality]
\label{thm:closed-bounded-interval-dyadic-containment-totality}
Every rational or dyadic containment consumer of an accepted $\ClosedBoundedIntervalUp$ carrier factors through the rational containment ledger $Q$ and dyadic containment ledger $D$ over the displayed $\LocatedIntervalUp$, $\RationalIntervalUp$, $\DyadicIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route. Thus containment totality for this packet is a finite ledger-totality obligation over $L,U,O,Q,D,S,R,E,H,C,P,N$, not a host interval set, an open-cover principle, a selected point, quotient real equality, trichotomy, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the containment surface of the carrier. The rows $Q$ and $D$ are the only rational and dyadic containment ledgers, and by \autoref{def:closed-bounded-interval-carrier} they are attached to the lower endpoint, upper endpoint, and endpoint-order rows $L,U,O$.

Next use the located-cover handoff and dyadic-net obligations. Theorems~\ref{thm:closed-bounded-interval-located-cover-handoff} and \ref{thm:closed-bounded-interval-dyadic-net-obligations} force every located or dyadic refinement through $\LocatedIntervalUp$, $\RationalIntervalUp$, $\DyadicIntervalUp$, $Q$, and $D$ before any compactness-facing read.

The readback route is finite as well. The $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows $S,R,E$ inspect the same containment windows, while $H,C,P,N$ preserve and name the route. Hence every containment consumer is accounted for by the displayed ledger route and no excluded host object is introduced.
\end{proof}

\begin{theorem}[Closed bounded interval compact-uniform source package]
\label{thm:closed-bounded-interval-compact-uniform-source-package}
For every accepted $\ClosedBoundedIntervalUp$ carrier, the finite-net source, located-cover handoff, nested-compactness handoff, and compactness-consumer boundary assemble a compact-uniform source package
$$
L,U,O,Q,D,S,R,E,H,C,P,N
$$
for closed bounded interval nets and uniform-modulus consumers. The package records endpoint classifier stability, rational and dyadic containment totality, finite-window readback, Real sealing, transport, replay, provenance, and local naming before any net, nested-window, compactness-facing, or uniform-modulus conclusion is consumed.
\end{theorem}
\begin{proof}
First build the finite source package. The finite-net source theorem and endpoint classifier stability identify $L,U,O$ as the stable endpoint classifier rows and place $Q,D$ downstream as the rational and dyadic containment ledgers.

Next attach the cover and compactness routes. The located-cover handoff, nested-compactness handoff, and compactness-consumer boundary, \autoref{thm:closed-bounded-interval-located-cover-handoff}, \autoref{thm:closed-bounded-interval-nested-compactness-handoff}, and \autoref{thm:closed-bounded-interval-compactness-consumer-boundary}, keep every finite-net, located-cover, and nested-window consumer inside the same displayed packet.

Finally add the uniform readback surface. The dyadic containment totality theorem supplies $Q,D,S,R,E$ as the ledger and readback route, and $H,C,P,N$ preserve, replay, source, and name it. Therefore closed bounded interval nets and uniform-modulus consumers receive a single compact-uniform source package without open-cover compactness, selected subcovers, selected points, quotient real equality, trichotomy, countable choice, or ambient completeness as hidden inputs.
\end{proof}

\falsifiablePrediction{Every interval-net or uniform-modulus read of a ClosedBoundedIntervalUp packet factors through displayed lower and upper located endpoints, endpoint order, rational and dyadic containment ledgers, StreamName windows, RegSeqRat readback, and a RealUp seal.}

\independenceWitness{locatedinterval, closedboundedintervalnet, closedboundedintervaluniformmodulus, real: $\ClosedBoundedIntervalUp$ is not bijective to any listed sibling because it jointly carries lower and upper located endpoints, endpoint order, rational and dyadic containment ledgers, finite readback windows, a RealUp seal, transport, replay, provenance, and local naming.}

\begin{definition}[Closed bounded interval constructive source]
\label{def:closed-bounded-interval-constructive-source}
A constructive source for a $\ClosedBoundedIntervalUp$ packet is a finite $\BHist$ source
$$
J=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
where $L$ and $U$ are located endpoint rows, $O$ records the endpoint order, $Q$ and $D$ record rational and dyadic containment ledgers, $S$ is the $\StreamNameUp$ finite-window row, $R$ is the $\RegSeqRatUp$ readback row, $E$ is the $\RealUp$ seal row, $H$ is the componentwise $\hsame$ transport row, $C$ is the displayed $\Cont$ replay row, $P$ is the $\Pkg$ provenance row, and $N$ is the local $\NameCert_{\ClosedBoundedIntervalUp}$ row. The source has no coordinate for open-cover compactness, selected subcovers, selected points, quotient real equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Closed bounded interval constructive carrier]
\label{thm:closed-bounded-interval-constructive-carrier}
Every constructive source $J=(L,U,O,Q,D,S,R,E,H,C,P,N)$ for $\ClosedBoundedIntervalUp$ exposes exactly the root carrier rows of \autoref{def:closed-bounded-interval-carrier}: located lower endpoint, located upper endpoint, endpoint order, rational containment, dyadic containment, StreamName window, RegSeqRat readback, Real seal, componentwise transport, displayed replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the source of \autoref{def:closed-bounded-interval-constructive-source}. Its coordinates are precisely the rows $L,U,O,Q,D,S,R,E,H,C,P,N$.

Compare with the carrier definition. The root carrier of \autoref{def:closed-bounded-interval-carrier} has the same endpoint, containment, finite-window, readback, seal, transport, replay, provenance, and naming rows, and no additional coordinate is available to a carrier projection.

The excluded host objects are absent from the source and from the carrier. Therefore the constructive source exposes exactly the root carrier rows and cannot extend them by compactness, choice, quotient equality, trichotomy, or ambient completeness data.
\end{proof}

\begin{theorem}[Closed bounded interval constructive handoff]
\label{thm:closed-bounded-interval-constructive-handoff}
Every net, nested-window, finite-cover, located-cover, and uniform-modulus consumer of a $\ClosedBoundedIntervalUp$ constructive source factors through
$$
L,U,O,Q,D,S,R,E,H,C,P,N.
$$
The factorization first reads located endpoints and endpoint order, then rational and dyadic containment, then finite windows, RegSeqRat readback, the Real seal, transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Begin with the root carrier route. By \autoref{thm:closed-bounded-interval-constructive-carrier}, any consumer of the constructive source can project only $L,U,O,Q,D,S,R,E,H,C,P,N$.

Net and finite-cover consumers use the containment ledgers. The finite-net source, consumer nonescape obligations, dyadic containment totality, and located-cover handoff force such reads through $L,U,O,Q,D$ before they reach $S,R,E$.

Nested-window and uniform-modulus consumers use the same readback route. The nested compactness handoff and compact-uniform source package keep $S,R,E,H,C,P,N$ attached to the endpoint and containment rows, so these consumers cannot bypass the displayed source.
\end{proof}

\begin{definition}[Closed bounded interval Cauchy modulus window]
\label{def:closed-bounded-interval-cauchy-modulus-window}
A Cauchy-modulus window for a $\ClosedBoundedIntervalUp$ constructive source is the finite subpacket
$$
W_{\mathsf{mod}}=(L,U,O,D,S,R,E,M)
$$
where $L$ and $U$ are the located endpoint rows, $O$ is the endpoint-order row, $D$ is the dyadic containment and tolerance ledger, $S$ is the $\StreamNameUp$ finite-window row, $R$ is the $\RegSeqRatUp$ readback row, $E$ is the terminal $\RealUp$ seal row, and $M$ is the $\RealCauchyModulusUp$ consumer slot. The window exposes endpoint order, dyadic containment, finite StreamName windows, RegSeqRat readback, and the RealCauchyModulus-facing slot before any compactness, net, or uniform-modulus consumer may inspect the interval packet.
\end{definition}

\begin{theorem}[Closed bounded interval modulus window transport]
\label{thm:closed-bounded-interval-modulus-window-transport}
Every classifier transport of a $\ClosedBoundedIntervalUp$ constructive source preserves the Cauchy-modulus window $W_{\mathsf{mod}}=(L,U,O,D,S,R,E,M)$ componentwise. In particular, the transported packet keeps the same endpoint-order row, dyadic containment ledger, finite $\StreamNameUp$ window row, $\RegSeqRatUp$ readback row, terminal $\RealUp$ seal row, and $\RealCauchyModulusUp$ consumer slot.
\end{theorem}
\begin{proof}
Project the source of \autoref{def:closed-bounded-interval-constructive-source}. The rows $L,U,O,D,S,R,E$ are already displayed as part of the constructive source, and \autoref{def:closed-bounded-interval-cauchy-modulus-window} only repackages them with the modulus consumer slot $M$.

Apply endpoint classifier stability to $L,U,O$. The transport cannot alter the lower endpoint, upper endpoint, or endpoint-order route before the containment rows are read.

Apply dyadic containment totality and the compact-uniform source package to $D,S,R,E$. These results keep the dyadic ledger attached to the same finite StreamName window, RegSeqRat readback, and Real seal.

Finally route the preserved rows to the $\RealCauchyModulusUp$ surface of \autoref{ch:concrete-instances-realcauchymodulus-namecert}. Since the modulus slot reads only $D,S,R,E$ and the endpoint-order rows already transported above, it is preserved componentwise as part of the same finite window.
\end{proof}

\begin{theorem}[Closed bounded interval RealCauchyModulus handoff]
\label{thm:closed-bounded-interval-real-cauchy-modulus-handoff}
Every $\RealCauchyModulusUp$ consumer of an accepted $\ClosedBoundedIntervalUp$ constructive source receives its precision data through the finite route
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp
$$
after reading the endpoint order and containment rows $L,U,O,D$. The handoff supplies the modulus consumer with dyadic tolerance data, finite observation windows, regular rational readback, and the Real seal, but not open-cover compactness, selected subcovers, quotient real equality, trichotomy, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start from the window of \autoref{def:closed-bounded-interval-cauchy-modulus-window}. The endpoint rows $L,U$ and the order row $O$ are read before the dyadic ledger $D$, so the consumer receives a bounded interval request rather than a detached Real name.

The dyadic row $D$ supplies the tolerance and containment data through \autoref{ch:concrete-instances-dyadicratcore-namecert}. The StreamName and RegSeqRat rows $S,R$ then provide the finite observation window and regular rational readback through \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-regseqrat-namecert}.

The terminal seal $E$ is read only after that route reaches \autoref{ch:concrete-instances-real-namecert}. The $\RealCauchyModulusUp$ consumer of \autoref{ch:concrete-instances-realcauchymodulus-namecert} therefore receives the displayed tolerance, window, readback, and seal data without gaining any excluded compactness or choice principle.
\end{proof}

\begin{theorem}[Closed bounded interval Cauchy modulus nonescape]
\label{thm:closed-bounded-interval-cauchy-modulus-nonescape}
No $\RealCauchyModulusUp$ read admitted by a $\ClosedBoundedIntervalUp$ Cauchy-modulus window can bypass endpoint order, dyadic containment, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, and the terminal $\RealUp$ seal. Equivalently, every accepted modulus read factors through $L,U,O,D,S,R,E,M$ and cannot introduce open-cover compactness, selected points, quotient real equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:closed-bounded-interval-real-cauchy-modulus-handoff}. It fixes the RealCauchyModulus-facing route through endpoint order, dyadic tolerance and containment, finite StreamName windows, RegSeqRat readback, and the Real seal.

The nonescape claim follows from the carrier inventory. Neither \autoref{def:closed-bounded-interval-carrier} nor \autoref{def:closed-bounded-interval-cauchy-modulus-window} contains a coordinate for open-cover compactness, selected points, quotient real equality, trichotomy, countable choice, or ambient Real completeness.

Transport and replay rows do not add analytic data. They only preserve the displayed route already used by \autoref{ch:concrete-instances-realcauchymodulus-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. Hence every accepted modulus read remains inside $L,U,O,D,S,R,E,M$.
\end{proof}

\begin{definition}[Closed bounded interval density ledger]
\label{def:closed-bounded-interval-density-ledger}
For an accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$, the root density ledger is the finite $\BHist$ packet
$$
\Delta_I=(L,U,O,Q,D,S,R,E,H,C,P,N)
$$
read as the source for dyadic mesh cells and interval-net consumers. The rows $L,U,O$ fix the endpoint route, $Q$ records rational containment tests, $D$ records finite dyadic mesh cells and dyadic containment comparisons, $S$ records the $\StreamNameUp$ finite windows, $R$ records the $\RegSeqRatUp$ readbacks, $E$ records the $\RealUp$ endpoint seals, and $H,C,P,N$ record transport, replay, provenance, and local naming for the same endpoint-and-containment surface.
\end{definition}

\begin{theorem}[Closed bounded interval density readback]
\label{thm:closed-bounded-interval-density-readback}
Every density or interval-net readback admitted by an accepted $\ClosedBoundedIntervalUp$ carrier factors through the root density ledger
$$
L,U,O,Q,D,S,R,E,H,C,P,N .
$$
In particular, dyadic mesh cells and rational containment tests are read after the endpoint route $L,U,O$, the finite observation windows and regular rational readbacks are read after $Q,D$, and the endpoint seals are read through the terminal $\RealUp$ row $E$ with transport, replay, provenance, and local naming carried by $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the density ledger. Its coordinates are exactly the endpoint rows, rational and dyadic containment rows, finite windows, regular rational readbacks, endpoint seals, and structural rows already present in the carrier.

Apply the existing source and compact-uniform package theorems. The finite-net source theorem places $L,U,O,Q,D$ before any mesh consumer, while the compact-uniform source package keeps $S,R,E,H,C,P,N$ attached to the same endpoint-and-containment route.

Thus density readback cannot start from a free mesh. It must pass through $L,U,O,Q,D,S,R,E,H,C,P,N$, so every downstream interval-net or uniform-modulus consumer receives dyadic density data only as a readback of the root endpoint ledger.
\end{proof}

\begin{theorem}[Closed bounded interval net-unblock package]
\label{thm:closed-bounded-interval-net-unblock-package}
Every $\ClosedBoundedIntervalNetUp$, finite-cover, nested-window, and uniform-modulus consumer of an accepted $\ClosedBoundedIntervalUp$ carrier must obtain its interval source from \autoref{def:closed-bounded-interval-density-ledger}. No such consumer can bypass the root endpoint-and-containment package
$$
L,U,O,Q,D,S,R,E,H,C,P,N
$$
or replace it by a host interval set, an open-cover compactness object, selected subcover, selected point, quotient real equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the density readback theorem. It identifies $L,U,O,Q,D,S,R,E,H,C,P,N$ as the complete source route for dyadic mesh cells, rational containment tests, StreamName windows, RegSeqRat readbacks, and Real endpoint seals.

Now compare the downstream consumers. Closed bounded interval nets, finite-cover windows, nested-window compactness, and uniform-modulus handoffs all use the same endpoint rows, containment rows, windows, readbacks, and seals before adding their own consumer rows.

The non-bypass claim follows from the carrier inventory. Since the root density ledger contains no host interval set, open-cover compactness object, selected subcover, selected point, quotient equality, trichotomy decision, choice selector, or ambient completeness datum, no downstream consumer can obtain one without leaving the displayed $\ClosedBoundedIntervalUp$ package.
\end{proof}

\begin{theorem}[Closed bounded interval source obligation package]
\label{thm:closed-bounded-interval-source-obligation-package}
For every accepted $\ClosedBoundedIntervalUp$ carrier $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$, the source-obligation surface for downstream L10 consumers is exactly the endpoint route $L,U,O$, the rational and dyadic containment rows $Q,D$, the finite observation and regular readback rows $S,R$, the terminal $\RealUp$ seal $E$, and the structural rows $H,C,P,N$. This package includes endpoint containment, endpoint order, finite-net source admission, and Real-seal handoff before any interval-net, nested-window, or completion consumer may read the interval.
\end{theorem}
\begin{proof}
Project the carrier rows. The endpoint-containment and endpoint-order results already identify $L,U,O,Q$ as the only accepted lower-bound, upper-bound, order, and rational containment surface.

Apply the finite-net source and net-unblock package theorems. They force every mesh, finite-window, and downstream interval-net read through $D,S,R$ before the consumer adds its own rows.

The Real-seal handoff keeps $E$ after the displayed endpoint and readback rows, while $H,C,P,N$ only transport, replay, source, and name that same package. Hence the listed rows are the complete source-obligation surface.
\end{proof}

\begin{theorem}[Closed bounded interval source cover boundary]
\label{thm:closed-bounded-interval-source-cover-boundary}
Every finite-cover, compactness, interval-net, nested-window, and uniform-modulus consumer of an accepted $\ClosedBoundedIntervalUp$ packet must enter through the source-obligation package
$$
L,U,O,Q,D,S,R,E,H,C,P,N.
$$
Such a consumer may refine the displayed finite source by its own cover or net rows, but it cannot replace the source by a host interval set, open-cover compactness principle, selected subcover, selected point, quotient real equality, trichotomy, countable-choice schedule, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start from the finite-net source theorem and the net-unblock package. Together they make the density ledger the only admitted source for dyadic cells, rational containment tests, finite observation windows, regular readbacks, and endpoint seals.

Finite-cover and compactness consumers add rows after that source has been displayed. They may inspect $D,S,R,E$ through the same replay row $C$, but they do not receive a separate open-cover object or a selector coordinate.

The exclusion follows from the carrier inventory and the endpoint-containment boundary. Since $I$ contains only $L,U,O,Q,D,S,R,E,H,C,P,N$, every accepted cover boundary remains a finite BEDC source route rather than host compactness data.
\end{proof}

\begin{theorem}[Closed bounded interval source readback stability]
\label{thm:closed-bounded-interval-source-readback-stability}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ be an accepted $\ClosedBoundedIntervalUp$ carrier. Any $\RegSeqRatUp$ or $\RealUp$ readback used by a downstream interval consumer is stable under the displayed componentwise $\hsame$ row $H$ and the displayed $\Cont$ replay row $C$: transporting the source rows by $H$ and replaying them by $C$ preserves the same finite endpoint, containment, dyadic, StreamName, RegSeqRat, and Real-seal route.
\end{theorem}
\begin{proof}
Read the RegSeqRat and Real handoff rows through the density ledger. The rows $S,R,E$ are reached only after the endpoint route $L,U,O$, containment rows $Q,D$, and finite source windows have been displayed.

Use the componentwise transport row $H$. It preserves lower and upper endpoint rows, order, containment ledgers, dyadic cells, StreamName windows, RegSeqRat readbacks, and the terminal Real seal as components of the same packet.

Use the replay row $C$ for downstream consumers. Since $C$ replays the same displayed route and $P,N$ only source and name it, the readback cannot drift into quotient real equality, selected representatives, trichotomy, choice, or ambient $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Closed bounded interval root consumer obligations]
\label{thm:closed-bounded-interval-root-consumer-obligations}
Every net, uniform-modulus, located-cover, nested-window, or compactness-facing consumer of an accepted $\ClosedBoundedIntervalUp$ carrier must first expose the same lower endpoint, upper endpoint, endpoint-order, rational containment, dyadic containment, StreamName window, RegSeqRat readback, Real seal, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows. The consumer may add its own downstream rows only after this root package has been displayed; it cannot replace the root by quotient real equality, trichotomy, selected points, selected subcovers, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from the source-obligation package. It identifies $L,U,O,Q,D,S,R,E,H,C,P,N$ as the finite endpoint, containment, window, readback, seal, transport, replay, provenance, and local naming surface for downstream interval reads.

Apply the source cover boundary. It forces cover, compactness, interval-net, nested-window, and uniform-modulus consumers to enter through that source package before adding their own cover or net rows.

Finally use source readback stability. The RegSeqRat and Real rows remain attached to the same componentwise $\hsame$ transport and $\Cont$ replay route, so no consumer can detach the root package into quotient equality, trichotomy, selected interval points, selected subcovers, or an ambient completeness assertion.
\end{proof}

\begin{theorem}[Closed bounded interval root net readiness]
\label{thm:closed-bounded-interval-root-net-readiness}
Every $\ClosedBoundedIntervalNetUp$ consumer of an accepted $\ClosedBoundedIntervalUp$ carrier must receive the endpoint rows $L,U,O$, the containment ledgers $Q,D$, the $\StreamNameUp$ row $S$, the $\RegSeqRatUp$ row $R$, the $\RealUp$ seal $E$, and the structural rows $H,C,P,N$ before reading mesh centers, coverage rows, or net refinements.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:closed-bounded-interval-carrier} and the classifier of \autoref{def:closed-bounded-interval-classifier}. The endpoint rows are $L,U,O$, containment is recorded by $Q,D$, finite windows and rational readback by $S,R$, and the terminal seal by $E$.

Apply the source nonescape and finite-cover nonescape boundaries already established for the chapter. They keep every interval source read inside the displayed carrier rows and refuse host interval sets, selected points, quotient real equality, trichotomy, and ambient completeness.

The finite-net consumer can therefore add mesh centers and coverage rows only after the source package has been displayed. The replay and provenance rows $H,C,P,N$ carry exactly that source into the consumer, so net readiness is the endpoint-and-containment package rather than an independent mesh object.
\end{proof}

\begin{theorem}[Closed bounded interval carrier-classifier scope]
\label{thm:closed-bounded-interval-carrier-classifier-scope}
Let $I=(L,U,O,Q,D,S,R,E,H,C,P,N)$ be an accepted $\ClosedBoundedIntervalUp$ carrier. Every downstream read of the lower endpoint, upper endpoint, endpoint-order row, dyadic containment ledger, StreamName window, RegSeqRat readback, RealUp seal, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows routes through the carrier of \autoref{def:closed-bounded-interval-carrier} and the classifier of \autoref{def:closed-bounded-interval-classifier}. No consumer may replace that pair by quotient real equality, trichotomy, selected interval points, selected subcovers, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:closed-bounded-interval-namecert-obligations}. It identifies the lower endpoint, upper endpoint, endpoint-order, rational containment, dyadic containment, window, readback, seal, transport, replay, provenance, and local naming rows as the local obligation surface of the accepted packet.

Apply \autoref{thm:closed-bounded-interval-endpoint-order-transport}. The endpoint rows and their order are preserved only by the displayed componentwise transport and classifier comparison, so the lower and upper endpoints cannot be reclassified through host real equality or trichotomy.

Use \autoref{thm:closed-bounded-interval-net-handoff} and \autoref{thm:closed-bounded-interval-nested-compactness-handoff}. Net, cover, and nested compactness consumers receive the same endpoint, containment, StreamName, RegSeqRat, Real-seal, transport, replay, provenance, and local naming rows before adding their own downstream data.

Thus every accepted read is scoped by the carrier/classifier pair of \autoref{def:closed-bounded-interval-carrier} and \autoref{def:closed-bounded-interval-classifier}. Since neither definition contains a coordinate for the refused host data, no downstream consumer can add such a coordinate while preserving the displayed route.
\end{proof}
\closureat{ClosedBoundedIntervalUp}{seedStr}

\begin{closurestatus}{\ClosedBoundedIntervalUp}
  \constructivestory{A $\ClosedBoundedIntervalUp$ packet is generated from lower and upper located endpoint rows, an endpoint-order row, rational and dyadic containment ledgers, StreamName windows, RegSeqRat readbacks, a RealUp seal, hsame transports, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:closed-bounded-interval-carrier}, \autoref{def:closed-bounded-interval-classifier}, \autoref{thm:closed-bounded-interval-namecert-obligations}, \autoref{thm:closed-bounded-interval-endpoint-order-transport}, \autoref{thm:closed-bounded-interval-net-handoff}, and \autoref{thm:closed-bounded-interval-nested-compactness-handoff} bind the finite base carrier for closed bounded intervals before net, uniform-modulus, and nested-window compactness consumers add their own rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, open-cover compactness, quotient real equality, trichotomy, selected points of the interval, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier preservation, endpoint-order transport, and net-handoff nonescape for BEDC.Derived.ClosedBoundedIntervalUp.}
\end{closurestatus}
