\chapter{A Concrete Naming Certificate for $\PositiveRealUp$}
\label{ch:concrete-instances-positivereal-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\PositiveRealUp$
packet names a positive real not by a host order predicate but by displayed
apartness-from-zero evidence over the finite real-name substrate. It sits at
the L10 boundary between the sealed $\RealUp$ name surface of
\autoref{ch:concrete-instances-real-namecert}, the located interval route of
\autoref{ch:concrete-instances-locatedreal-namecert}, the positive separation
rows of \autoref{ch:concrete-instances-apartnessreal-namecert}, and the
located-apartness handoff of
\autoref{ch:concrete-instances-located-apartness-namecert}.

\section{Carrier and positivity packet}
\label{sec:positivereal-carrier}

\begin{definition}[PositiveReal carrier]
\label{def:positivereal-carrier}
A $\PositiveRealUp$ carrier is a finite packet
$(R,A,D,W,Q,H,C,P,N)$ with the following displayed rows:
\begin{enumerate}
\item $R$, a sealed $\RealUp$ row for the real-name presentation being
classified;
\item $A$, a positive apartness-to-zero row, read as an
$\ApartnessRealUp$ finite-window separation packet whose left endpoint is the
zero real-name row and whose right endpoint is $R$;
\item $D$, a positive $\DyadicRatCoreUp$ radius ledger for the separation
radius used by $A$;
\item $W$, a finite $\StreamNameUp$ observation window shared by the zero row
and $R$;
\item $Q$, a $\RegSeqRatUp$ readback row exposing the scheduled rational
observations of $R$ on $W$;
\item $H$, the componentwise $\hsame$ transport rows for the real seal,
apartness row, radius ledger, window, and readback;
\item $C$, the displayed $\Cont$ replay routes keeping the finite observations
attached to the transported carrier;
\item $P$, the $\mathsf{Pkg}$ provenance rows for the real seal, dyadic
radius, stream window, regular-rational readback, and apartness ledger;
\item $N$, the local $\NameCert$ row binding these eight rows as one
positive-real certificate.
\end{enumerate}
The carrier accepts only this finite positivity packet. It contains no
trichotomy coordinate, no host real order predicate, no quotient stream
equality, no selected limit, and no ambient completeness principle.
\end{definition}
\leanchecked{BEDC.Derived.PositiveRealUp.PositiveRealTasteGate\_single\_carrier\_alignment}

\section{NameCert obligations}
\label{sec:positivereal-namecert-obligations}

\begin{theorem}[PositiveReal NameCert obligations]
\label{thm:positivereal-namecert-obligations}
The local $\NameCert_{\PositiveRealUp}$ surface for the carrier of
\autoref{def:positivereal-carrier} consists of six finite obligations:
\begin{enumerate}
\item carrier admission: the displayed rows $(R,A,D,W,Q,H,C,P,N)$ are present
in the same finite $\mathsf{BHist}$ packet;
\item classifier transport: accepted carriers compare only by componentwise
transport of the real seal row, apartness row, positive radius ledger, finite
window, readback, replay, provenance, and local certificate rows;
\item positive-radius exactness: the radius consumed by the apartness-to-zero
row is exactly the positive $\DyadicRatCoreUp$ row $D$ displayed by the
carrier;
\item apartness handoff: every positivity read factors through the
$\ApartnessRealUp$ and $\LocatedApartnessUp$ finite-window rows named in $A$;
\item real-seal non-escape: the real component is exported only through the
sealed $\RealUp$ row $R$ and the $\RegSeqRatUp$ readback $Q$;
\item ledger exhaustion: downstream metric or order consumers can read only
the nine displayed carrier rows and their componentwise transport routes.
\end{enumerate}
These obligations certify positivity as finite apartness-from-zero evidence.
They do not certify a classical positive cone, a total order, trichotomy of
constructive reals, quotient equality of streams, selected limits, or ambient
real completeness.
\end{theorem}
\leanchecked{BEDC.Derived.PositiveRealUp.PositiveRealNameCert\_obligations}
\begin{proof}
Project the carrier of \autoref{def:positivereal-carrier}. The projection
exposes exactly the sealed real row, apartness-to-zero row, positive dyadic
radius, finite observation window, regular-rational readback, transport,
replay, provenance, and local certificate rows.

Classifier transport is then componentwise. The $\hsame$ and $\Cont$ rows move
the real seal, apartness packet, radius ledger, stream window, readback, and
provenance together, so the transported packet has the same visible carrier
shape.

Positive-radius exactness follows by reading $D$ as the only dyadic radius row
available to the apartness coordinate $A$. The apartness handoff is therefore
the finite-window separation route already displayed by the
$\ApartnessRealUp$ and $\LocatedApartnessUp$ packets.

The real-seal boundary is negative. Since $R$ and $Q$ are the only real-name
coordinates, no consumer can leave the sealed $\RealUp$ or $\RegSeqRatUp$
surface. The listed rows exhaust the packet, so no trichotomy, host order,
quotient stream equality, selected limit, or ambient completeness datum can be
exported.
\end{proof}

\begin{theorem}[PositiveReal apartness handoff]
\label{thm:positivereal-apartness-handoff}
Every accepted $\PositiveRealUp$ read factors through the displayed
$\ApartnessRealUp$ or $\LocatedApartnessUp$ separation row, the positive
$\DyadicRatCoreUp$ radius row, the finite $\StreamNameUp$ observation window,
and the $\RegSeqRatUp$ readback row of
\autoref{def:positivereal-carrier}. Consequently a downstream real-order,
metric, or algebraic consumer receives positivity only as finite
apartness-from-zero evidence with visible $\hsame$, $\Cont$, $\mathsf{Pkg}$,
and $\NameCert$ provenance.

No such read supplies trichotomy, host order, quotient stream equality,
selected limits, or ambient completeness for $\RealUp$.
\end{theorem}
\begin{proof}
Start with an accepted carrier and project its apartness coordinate $A$. By
\autoref{def:positivereal-carrier}, $A$ is already an apartness-to-zero
finite-window row whose positive radius is displayed by $D$ and whose window is
displayed by $W$.

Read the same packet through the surrounding L10 siblings. The real-name
endpoint is sealed by $R$, the scheduled rational observations are exposed by
$Q$, and the located-apartness route repacks the positive gap as the finite
separation ledger consumed by $A$.

Transport preserves only these rows. The $\hsame$, $\Cont$, $\mathsf{Pkg}$,
and $\NameCert$ coordinates move the real seal, apartness packet, dyadic
radius, finite window, and readback componentwise, so every transported read
still factors through the displayed apartness and radius surfaces.

The carrier has no coordinate for an order decision, quotient representative,
chosen limit, or completeness witness. Therefore every downstream consumer is
confined to the finite apartness-from-zero evidence stated above.
\end{proof}
\leanchecked{BEDC.Derived.PositiveRealUp.PositiveRealCarrier\_apartness\_handoff}

\begin{theorem}[PositiveReal RegSeqRat window positivity scope]
\label{thm:positivereal-regseqrat-window-positivity-scope}
Every accepted $\PositiveRealUp$ packet $(R,A,D,W,Q,H,C,P,N)$ exposes positivity reads only through the finite $\StreamNameUp$ windows $W$ and the $\RegSeqRatUp$ readback row $Q$ attached to the sealed $\RealUp$ row $R$. The apartness coordinate $A$ may consume the positive $\DyadicRatCoreUp$ radius $D$ only after those window and readback rows are displayed, and every transported read remains confined to the same $R,A,D,W,Q,H,C,P,N$ carrier surface.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:positivereal-carrier}. The real endpoint is $R$, the apartness-to-zero evidence is $A$, the positive radius is $D$, and the only observation route is the pair $W,Q$.

Use the obligation surface of \autoref{thm:positivereal-namecert-obligations}. Its real-seal non-escape and apartness handoff rows require each positivity read to pass through the displayed window and readback rows before the apartness evidence is exported.

Apply \autoref{thm:positivereal-apartness-handoff}. The handoff keeps $A$ tied to the finite $\StreamNameUp$ window $W$, the $\RegSeqRatUp$ readback $Q$, and the dyadic radius $D$.

Transport is componentwise through $H$ and replayed through $C$, with $P,N$ recording provenance and local naming. Hence the positivity scope never leaves the displayed $R,A,D,W,Q,H,C,P,N$ packet.
\end{proof}

\begin{theorem}[PositiveReal apartness radius transport]
\label{thm:positivereal-apartness-radius-transport}
For every accepted $\PositiveRealUp$ carrier $(R,A,D,W,Q,H,C,P,N)$, the positive $\DyadicRatCoreUp$ radius row $D$ transported by $H$ and replayed by $C$ is the same radius read by the apartness-to-zero row $A$. A downstream consumer may move this radius only together with the sealed real row $R$, the stream window $W$, the regular readback $Q$, the provenance row $P$, and the local name $N$.
\end{theorem}
\begin{proof}
Read $D$ from the carrier definition. It is the unique positive dyadic radius ledger assigned to the apartness coordinate $A$, so a radius consumer has no second radius row to inspect.

Invoke \autoref{thm:positivereal-namecert-obligations}. Positive-radius exactness identifies the radius consumed by $A$ with the displayed $D$ row, while classifier transport moves the real seal, apartness row, radius ledger, window, readback, replay, provenance, and local certificate componentwise.

The apartness handoff of \autoref{thm:positivereal-apartness-handoff} supplies the consumer boundary. It lets downstream order, metric, or algebraic reads use only the finite apartness-from-zero evidence carried by $A,D,W,Q$.

Therefore $H$ and $C$ transport the positive radius as part of the whole $R,A,D,W,Q,H,C,P,N$ packet. The transported radius is not a host real selector, a trichotomy branch, a quotient representative, or a completeness witness.
\end{proof}

\begin{theorem}[PositiveReal RealAlgOrder consumer boundary]
\label{thm:positivereal-realalgorder-consumer-boundary}
Every $\RealAlgOrderUp$ or metric consumer of an accepted $\PositiveRealUp$ carrier $(R,A,D,W,Q,H,C,P,N)$ receives only apartness-from-zero evidence: the sealed real row $R$, the apartness row $A$, the positive radius ledger $D$, the finite window $W$, the readback $Q$, and the support rows $H,C,P,N$. Such a consumer receives no trichotomy, host order predicate, quotient stream equality, selected limit, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with the accepted carrier and project its finite rows. The only order-facing data are the apartness row $A$ and the positive dyadic radius $D$ attached to the sealed real row $R$.

The NameCert obligations of \autoref{thm:positivereal-namecert-obligations} force real-seal non-escape and ledger exhaustion. Thus any consumer reads $R$ through $W,Q$, reads positivity through $A,D$, and reads stability only through $H,C,P,N$.

Use \autoref{thm:positivereal-apartness-handoff} to identify the exported evidence. The handoff is apartness-from-zero evidence with visible transport, replay, provenance, and local naming.

Since no carrier coordinate stores trichotomy, a host order predicate, quotient stream equality, a selected limit, or real completeness, $\RealAlgOrderUp$ and metric consumers cannot receive any such principle from the packet.
\end{proof}

\begin{theorem}[PositiveReal multiplicative radius transport]
\label{thm:positivereal-multiplicative-radius-transport}
Let two accepted $\PositiveRealUp$ packets expose positive dyadic radius rows
through the same finite $\StreamNameUp$ and $\RegSeqRatUp$ observation window.
Then the product-facing positivity read transports through the displayed
$\DyadicRatCoreUp$ radius ledgers, the componentwise $\hsame$ rows, the
$\Cont$ replay routes, the $\mathsf{Pkg}$ provenance rows, and the local
$\NameCert$ rows of the two packets. The transported read cannot use
trichotomy, host order, quotient stream equality, selected limits, or
$\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.PositiveRealUp.PositiveRealCarrier\_multiplicative\_radius\_transport}
\begin{proof}
Project the two accepted carriers of \autoref{def:positivereal-carrier}. Each
projection exposes a sealed real row, an apartness-to-zero row, a positive
dyadic radius, a finite stream window, a regular-rational readback, transport,
replay, provenance, and a local certificate row.

Read the common observation window componentwise. The apartness-to-zero rows
use their displayed positive dyadic radii, and the shared
$\StreamNameUp$/$\RegSeqRatUp$ window keeps the product-facing read attached to
the same finite schedule of rational observations.

Transport the two packets through the visible $\hsame$ and $\Cont$ rows. These
rows preserve the radius ledgers, windows, readbacks, and provenance entries as
finite data, so the product consumer receives only the displayed
apartness-radius evidence.

The carrier definition supplies no trichotomy coordinate, host order predicate,
quotient stream equality, selected limit, or completeness witness. Hence the
product-facing positivity read cannot draw on any evidence outside the two
finite PositiveReal packets.
\end{proof}

\begin{theorem}[PositiveReal product-radius window compatibility]
\label{thm:positivereal-product-radius-window-compatibility}
Two accepted $\PositiveRealUp$ packets used by a product-facing
$\RealAlgOrderUp$ or metric consumer may combine their positive
$\DyadicRatCoreUp$ radius rows only after both packets expose compatible
$\StreamNameUp$ windows and $\RegSeqRatUp$ readbacks. The product-radius read is
then transported through the same $R,A,D,W,Q,H,C,P,N$ carrier rows for each
packet, with the radius ledgers, windows, readbacks, replay routes, provenance,
and local names kept componentwise.

No product-facing consumer may infer radius compatibility from a host real
order predicate, quotient stream equality, selected limits, or ambient
$\RealUp$ completeness.
\end{theorem}
\begin{proof}
First use \autoref{thm:positivereal-regseqrat-window-positivity-scope}. It
forces each positivity read to pass through the displayed $\StreamNameUp$ window
$W$ and the $\RegSeqRatUp$ readback row $Q$ before the apartness radius is
available to a downstream consumer.

Next apply \autoref{thm:positivereal-apartness-radius-transport}. The positive
dyadic radius row $D$ is the same row consumed by the apartness-to-zero packet
$A$, and it is moved only with $R,W,Q,H,C,P,N$.

Finally invoke \autoref{thm:positivereal-multiplicative-radius-transport}. Its
product-facing route combines two positive radius reads only through shared
finite observation data and componentwise transport. Therefore a
$\RealAlgOrderUp$ or metric consumer may reuse the product radius exactly when
the two packets display compatible stream windows and regular readbacks, and no
stronger real-order or completeness datum is exported.
\end{proof}

\begin{theorem}[PositiveReal dyadic radius lower bound]
\label{thm:positive-real-dyadic-radius-lower-bound}
Every accepted $\PositiveRealUp$ packet whose positivity is read through the
$\RealUp$ apartness row exposes a finite $\DyadicRatCoreUp$ radius row below
the positive witness. The row is transported through the displayed
$\RegSeqRatUp$ readback and $\StreamNameUp$ observation windows, and it is
available to $\MetricBallUp$ and $\RealAlgOrderUp$ consumers as finite
apartness-radius evidence without trichotomy, a host real selector, quotient
stream equality, selected limits, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:positivereal-carrier}. Its
apartness coordinate $A$ is read over the sealed real row $R$, and its dyadic
radius ledger $D$ is already displayed before any downstream order or metric
consumer can inspect the packet.

Use the apartness handoff of \autoref{thm:positivereal-apartness-handoff}. The
handoff keeps the positive witness attached to the same finite
$\StreamNameUp$ window and the same $\RegSeqRatUp$ readback row, so $D$ is read
as a lower-radius row beneath that witness rather than as a host real choice.

Transport follows the multiplicative radius route of
\autoref{thm:positivereal-multiplicative-radius-transport}. The $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows preserve the dyadic radius ledger,
the finite observation window, and the regular-rational readback componentwise.

Thus a $\MetricBallUp$ or $\RealAlgOrderUp$ consumer receives exactly the
displayed dyadic lower-radius row. Since the carrier contains no trichotomy,
selector, quotient equality, selected limit, or completeness coordinate, no
stronger real-order principle is exported.
\end{proof}

\closureat{PositiveRealUp}{seedStr}

\begin{closurestatus}{\PositiveRealUp}
  \constructivestory{A $\PositiveRealUp$ packet is generated from a sealed real-name row, an apartness-to-zero row, one positive dyadic radius ledger, one finite observation window, one regular-rational readback, transport, replay, provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:positivereal-carrier}, \autoref{thm:positivereal-namecert-obligations}, and \autoref{thm:positivereal-apartness-handoff} name the seed carrier, obligation surface, and finite apartness-from-zero handoff for positive real packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim trichotomy of constructive reals, total order, quotient stream equality, selected limits, ambient real completeness, or a standard bridge.}
  \upgradepath{To reach obligationClosure, the carrier, six obligation rows, and apartness handoff must be checked as finite BEDC packet obligations.}
\end{closurestatus}
