\chapter{RegularCauchyInterleaving NameCert Construction}
\label{ch:concrete-instances-regularcauchyinterleaving-namecert}
\origin{human}

The $\RegularCauchyInterleavingUp$ interface isolates the standard alternating construction for two regular Cauchy names. In the constructive-analysis reading of Bishop and Bridges, \emph{Constructive Analysis}, the interleaving is not a quotient of two completed real values; it is a finite certificate that records which regular Cauchy observation is read at each unary selector step, how the two schedules share a modulus ledger, and where the resulting $\RealUp$ seal can be consumed.

\begin{definition}[Regular Cauchy interleaving source]
\label{def:regular-cauchy-interleaving-source}
A $\RegularCauchyInterleavingUp$ source packet is a finite $\mathsf{BHist}$ row
$$
I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $A$ and $B$ are the two $\RegSeqRatUp$ regular Cauchy names whose point rows may be inspected;
\item $S_A$ and $S_B$ are the two $\StreamNameUp$ schedules that expose the finite observation windows for $A$ and $B$;
\item $\sigma$ is the alternating unary selector row, with even selector rows reading from $A$ and odd selector rows reading from $B$;
\item $M$ is the combined modulus ledger, recording the common precision budget and the component budget used on each selected side;
\item $E_A$ and $E_B$ are the $\RealUp$ seal readbacks attached to the two source names;
\item $E$ is the interleaved $\RealUp$ seal row reached only through the selected source readback and the common modulus ledger;
\item $H$ stores the componentwise $\hsame$ transports for the two regular names, both schedules, the selector, the combined modulus ledger, and all three seal rows;
\item $C$ stores the displayed $\Cont$ routes for selecting a source side, reading its scheduled window, checking the combined modulus row, and exposing the interleaved seal;
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\RatUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RegularCauchyInterleavingUp}$ row.
\end{enumerate}
The packet has no coordinate for a quotient real, a selected host limit, or an equality principle beyond the displayed $\hsame$ and $\Cont$ rows.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.TasteGate.RegularCauchyInterleavingTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy interleaving classifier]
\label{thm:regular-cauchy-interleaving-classifier}
Two accepted $\RegularCauchyInterleavingUp$ source packets classify together exactly when their two $\RegSeqRatUp$ source names, two $\StreamNameUp$ schedules, alternating selector rows, combined modulus ledgers, source $\RealUp$ readbacks, interleaved $\RealUp$ seal rows, package provenance, and local naming rows are transported componentwise by the displayed $\hsame$ comparisons and read through the displayed $\Cont$ routes. The classifier compares the selected finite window on the even side with the transported even-side window, and the selected finite window on the odd side with the transported odd-side window, always under the same combined modulus ledger.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_classifier\_transport}
\begin{proof}
Project the two accepted source packets. Their carrier rows expose only the two regular names, the two stream schedules, the selector, the modulus ledger, the seal readbacks, and the displayed transport and continuation rows.

For an even selector row, the classifier reads the scheduled window from the first $\RegSeqRatUp$ name through $S_A$, then checks the corresponding component of $M$. For an odd selector row, it performs the same finite read through $S_B$ and the second component of $M$.

The rows $H$ and $C$ record exactly the transports and consumer routes used by these reads. Repacking the transported side-specific read with $P$ and $N$ gives the same classifier surface for the interleaved seal $E$, and no quotient real or host-limit comparison is available.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving NameCert obligations]
\label{thm:regular-cauchy-interleaving-namecert-obligations}
The local $\NameCert_{\RegularCauchyInterleavingUp}$ surface for the source packet of \autoref{def:regular-cauchy-interleaving-source} consists of five finite rows:
\begin{enumerate}
\item carrier admission: the accepted object is the displayed $\mathsf{BHist}$ packet $I$;
\item classifier equivalence: classification is the finite even-and-odd window comparison of \autoref{thm:regular-cauchy-interleaving-classifier};
\item $\hsame$ transport: the two source names, two schedules, selector, combined modulus ledger, and seal rows are preserved componentwise by the stored transport rows;
\item combined modulus exactness: each interleaved precision request is discharged by the displayed common budget and the component budget selected by $\sigma$;
\item $\RealUp$ seal non-escape: the interleaved seal $E$ can be consumed only after the selected $\RegSeqRatUp$ readback, its $\StreamNameUp$ schedule row, and the combined modulus ledger have been displayed.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_namecert\_obligations}
\begin{proof}
Carrier admission is the projection of the finite packet $I$. The source rows $A$, $B$, $S_A$, $S_B$, $\sigma$, $M$, $E_A$, $E_B$, and $E$ are stored coordinates, while $H$, $C$, $P$, and $N$ record transport, continuation, package, and local naming provenance.

Classifier equivalence is \autoref{thm:regular-cauchy-interleaving-classifier}. Its even and odd cases use the same packet rows and differ only in which source schedule the selector chooses.

The $\hsame$ row transports each displayed coordinate componentwise, and the $\Cont$ row records the consumer route through the selected schedule and modulus ledger. The combined modulus row is exact because a request is answered by the common budget together with the component budget named by $\sigma$.

Finally, the real-facing coordinate $E$ is downstream of the selected regular readback and not an independent host real. Since the packet has no field for quotient equality, selected limits, or ambient completeness, the seal cannot escape the displayed interleaving certificate.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving carrier admission]
\label{thm:regular-cauchy-interleaving-carrier-admission}
Let
$$
I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)
$$
be a displayed packet satisfying the $\RegSeqRatUp$ rows for $A$ and $B$, the $\StreamNameUp$ rows for $S_A$ and $S_B$, the alternating selector row $\sigma$, the combined modulus ledger $M$, the three $\RealUp$ seal rows $E_A$, $E_B$, and $E$, the displayed $\hsame$ and $\Cont$ rows, the $\Pkg$ provenance row, and the local $\NameCert_{\RegularCauchyInterleavingUp}$ row. Then $I$ is an accepted $\RegularCauchyInterleavingUp$ carrier.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_carrier\_admission}
\begin{proof}
Project the displayed coordinates of $I$. The first two coordinates give the required regular Cauchy names, the next two give their finite stream schedules, and the selector and modulus coordinates give the alternating read policy and its common budget ledger.

The seal coordinates $E_A$, $E_B$, and $E$ are already part of the same finite history row. The rows $H$ and $C$ supply the componentwise transport and consumer routes, while $P$ and $N$ supply the package provenance and local naming certificate.

Repack these projected rows in the order of \autoref{def:regular-cauchy-interleaving-source}. The definition has no further carrier field, so the displayed packet is exactly an admitted carrier.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving selector parity exactness]
\label{thm:regular-cauchy-interleaving-selector-parity-exactness}
For every accepted $\RegularCauchyInterleavingUp$ source packet $I$, each even selector read factors through the first regular name $A$, the schedule $S_A$, and the first component of the combined modulus ledger $M$, while each odd selector read factors through the second regular name $B$, the schedule $S_B$, and the second component of $M$. Componentwise $\hsame$ transports and the displayed $\Cont$ routes preserve this even-side and odd-side partition.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_selector\_parity\_exactness}
\begin{proof}
Unpack $I$ as in \autoref{def:regular-cauchy-interleaving-source}. The selector coordinate $\sigma$ is displayed as alternating, so an even selector row exposes the first source side and an odd selector row exposes the second source side.

In the even case, \autoref{thm:regular-cauchy-interleaving-classifier} reads the finite window through $A$ and $S_A$ and checks the corresponding first component of $M$. In the odd case, the same classifier reads through $B$ and $S_B$ and checks the second component of $M$.

The stored row $H$ transports the selector, both schedules, both regular names, and the combined modulus ledger componentwise. The stored row $C$ only routes consumers through the selected schedule and the selected ledger component, so transport preserves the parity partition rather than mixing the two source sides.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving swap symmetry boundary]
\label{thm:regular-cauchy-interleaving-swap-symmetry-boundary}
Let $I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)$ be an accepted $\RegularCauchyInterleavingUp$ source packet. Exchanging the two $\RegSeqRatUp$ source names $A,B$, exchanging the two schedules $S_A,S_B$, and replacing the alternating selector $\sigma$ by its opposite selector preserves the same public $\RealUp$ seal boundary through the displayed $\hsame$ transports, $\Cont$ routes, combined modulus ledger, $\Pkg$ provenance, and local $\NameCert$ row. The boundary is only the finite selector-swapped interleaving surface; it does not assert quotient real equality, selected host limits, ambient completeness, or access to a third schedule.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regular-cauchy-interleaving-selector-parity-exactness}. The forward selector sends even reads through $A,S_A$ and the first component of $M$, and odd reads through $B,S_B$ and the second component.

After the source and schedule exchange, the opposite selector sends its odd reads through the transported $A,S_A$ route and its even reads through the transported $B,S_B$ route. Thus the two presentations inspect the same two finite windows with only the selector parity exchanged.

Use \autoref{thm:regular-cauchy-interleaving-combined-modulus-exactness} to keep each selected read attached to the same component of $M$. Then use \autoref{thm:regular-cauchy-interleaving-schedule-window-coverage} to rule out any route through a schedule other than $S_A$ or $S_B$.

Finally apply \autoref{thm:regular-cauchy-interleaving-real-seal-non-escape}. The real-facing seal can be consumed only after the selected source row, selected schedule, combined ledger, displayed transport, displayed continuation route, package provenance, and local name have been read. Since the carrier has no quotient-real, host-limit, ambient-completeness, or third-schedule coordinate, the swapped presentation preserves exactly the public seal boundary and nothing stronger.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving selector transport determinacy]
\label{thm:regular-cauchy-interleaving-selector-transport-determinacy}
For classified accepted $\RegularCauchyInterleavingUp$ packets, transported selector rows preserve the even and odd routes. Every even transported read factors through the transported $A$-side schedule and the first component of the combined modulus ledger, and every odd transported read factors through the transported $B$-side schedule and the second component. No transported read can switch sides or use a third schedule.
\end{theorem}
\begin{proof}
Project the classifier statement of \autoref{thm:regular-cauchy-interleaving-classifier}. It compares the two source names, the two schedules, the selector row, and the combined modulus ledger componentwise through the displayed $\hsame$ and $\Cont$ data.

Apply \autoref{thm:regular-cauchy-interleaving-selector-parity-exactness} before transport. Even reads are routed through $A$, $S_A$, and the first component of $M$, while odd reads are routed through $B$, $S_B$, and the second component.

Apply the same parity exactness after the $\hsame$ transport. The transported selector still exposes the transported even side through the transported $A$-schedule and the transported odd side through the transported $B$-schedule.

Use \autoref{thm:regular-cauchy-interleaving-combined-modulus-exactness} to keep the selected ledger component fixed. Then use \autoref{thm:regular-cauchy-interleaving-schedule-window-coverage} to rule out unscheduled routes: the carrier has only the two transported schedules, so there is no coordinate from which a third schedule or side switch could be read.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_selector\_transport\_determinacy}

\begin{theorem}[Regular Cauchy interleaving RealUp seal non-escape]
\label{thm:regular-cauchy-interleaving-real-seal-non-escape}
Let $I$ be an accepted $\RegularCauchyInterleavingUp$ source packet with interleaved seal $E$. Any $\RealUp$ consumer of $E$ must pass through the selected $\RegSeqRatUp$ readback, the selected $\StreamNameUp$ schedule, the combined modulus ledger, the displayed $\hsame$ transport and $\Cont$ route, and the package and naming rows $P$ and $N$. No consumer of $E$ can read quotient real equality, a host limit, or ambient completeness from the packet.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_real\_seal\_non\_escape}
\begin{proof}
Carrier admission exposes only the fields listed in \autoref{def:regular-cauchy-interleaving-source}. Thus the real-facing row $E$ is not a standalone real object; it is a coordinate in the same finite packet as the two regular names, their schedules, the selector, and the ledger.

\autoref{thm:regular-cauchy-interleaving-selector-parity-exactness} identifies the required readback path for each selector parity. The even route passes through $A$, $S_A$, and the first component of $M$, while the odd route passes through $B$, $S_B$, and the second component of $M$.

The NameCert obligations then attach the displayed $\hsame$ transport, $\Cont$ consumer route, package provenance, and local naming row to that selected path. Since the carrier definition contains no quotient-equality coordinate, no host-limit coordinate, and no ambient-completeness coordinate, a $\RealUp$ consumer has no route out of the displayed certificate.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving combined modulus exactness]
\label{thm:regular-cauchy-interleaving-combined-modulus-exactness}
Let
$$
I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)
$$
be an accepted $\RegularCauchyInterleavingUp$ packet. Every precision request for the interleaved $\RealUp$ seal first reads the selector row $\sigma$, then reads the selected schedule $S_A$ or $S_B$, and then checks the matching component of the combined modulus ledger $M$. Even requests use the $A$ component of $M$, odd requests use the $B$ component of $M$, and no request can consume $E$ without one of these displayed ledger routes.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_combined\_modulus\_exactness}
\begin{proof}
Unpack the packet by \autoref{def:regular-cauchy-interleaving-source}. The selector row, both schedules, the combined modulus ledger, and the interleaved seal are stored coordinates of the same finite $\mathsf{BHist}$ row.

For an even selector read, \autoref{thm:regular-cauchy-interleaving-selector-parity-exactness} routes the request through $A$, $S_A$, and the first component of $M$. For an odd selector read, the same theorem routes the request through $B$, $S_B$, and the second component of $M$.

The $\Cont$ row records this order before the seal row $E$ is exposed. The $\hsame$, $\Pkg$, and $\NameCert$ rows are attached to the same route, so the precision request has no separate path to a selected real limit, quotient equality, or ambient completeness.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving schedule window coverage]
\label{thm:regular-cauchy-interleaving-schedule-window-coverage}
For an accepted packet $I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)$, the even and odd schedule windows exhaust the consumer reads of the interleaving. Every displayed consumer read is either an even read through $S_A$ and the $A$ side of $M$, or an odd read through $S_B$ and the $B$ side of $M$. There is no third schedule window and no unscheduled read of the interleaved seal.
\end{theorem}
\begin{proof}
Inspect the source packet. Its only schedule coordinates are $S_A$ and $S_B$, and its only side-selector coordinate is the alternating row $\sigma$.

The even case is the route through the first schedule. It reads the $A$ source row, the $S_A$ window, and the first component of the combined modulus ledger.

The odd case is the route through the second schedule. It reads the $B$ source row, the $S_B$ window, and the second component of the combined modulus ledger.

These two cases exhaust the selector row. Since the carrier has no coordinate for any further schedule, any consumer of $E$ must pass through one of the two displayed windows.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_schedule\_window\_coverage}

\begin{theorem}[Regular Cauchy interleaving obligation closure package]
\label{thm:regular-cauchy-interleaving-obligation-closure-package}
The rows of an accepted packet $I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)$ assemble the obligation surface for $\RegularCauchyInterleavingUp$ over $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The surface consists exactly of carrier admission, componentwise classifier transport, combined modulus exactness, schedule window coverage, and $\RealUp$ seal non-escape.
\end{theorem}
\begin{proof}
Carrier admission is \autoref{thm:regular-cauchy-interleaving-carrier-admission}. Componentwise classifier transport is \autoref{thm:regular-cauchy-interleaving-classifier}, with the parity partition supplied by \autoref{thm:regular-cauchy-interleaving-selector-parity-exactness}.

The combined modulus obligation is \autoref{thm:regular-cauchy-interleaving-combined-modulus-exactness}. The coverage obligation is \autoref{thm:regular-cauchy-interleaving-schedule-window-coverage}. The seal boundary is \autoref{thm:regular-cauchy-interleaving-real-seal-non-escape}.

These rows are all read from the same finite packet through the displayed transport, continuation, package, and naming coordinates. Therefore the chapter supplies the obligation surface, while leaving quotient equality, selected host limits, ambient completeness, and bridge checking outside the claim.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_obligation\_closure\_package}

\begin{theorem}[Regular Cauchy interleaving scoped kernel route]
\label{thm:regular-cauchy-interleaving-scoped-kernel-route}
Every accepted packet from \autoref{def:regular-cauchy-interleaving-source} factors its carrier admission, classifier transport, selector parity, combined modulus, schedule-window coverage, and $\RealUp$ seal non-escape through exactly the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\RatUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. No part of the accepted carrier is routed through quotient equality of reals, selected host limits, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the classifier of \autoref{thm:regular-cauchy-interleaving-classifier}. It reads only the two regular names, the two stream schedules, the alternating selector, the combined modulus ledger, the real seal rows, and the displayed transport and continuation coordinates.

The NameCert surface of \autoref{thm:regular-cauchy-interleaving-namecert-obligations} supplies the carrier row, classifier row, transport row, exactness row, and seal-boundary row. The carrier admission theorem then repacks those coordinates as the finite $\mathsf{BHist}$ packet of the source definition.

Selector parity is exact by \autoref{thm:regular-cauchy-interleaving-selector-parity-exactness}. Combined modulus exactness is \autoref{thm:regular-cauchy-interleaving-combined-modulus-exactness}, and schedule coverage is \autoref{thm:regular-cauchy-interleaving-schedule-window-coverage}. These three statements bind every consumer read to one of the two displayed schedules and to the matching component of the ledger.

Finally, \autoref{thm:regular-cauchy-interleaving-real-seal-non-escape} keeps the $\RealUp$ seal downstream of the selected regular readback, selected schedule, combined modulus row, $\hsame$ transport, $\Cont$ route, package row, and naming row. Together with \autoref{thm:regular-cauchy-interleaving-obligation-closure-package}, this exhausts the scoped kernel route and leaves no carrier coordinate for quotient equality, host limits, or ambient completeness.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving public real seal export]
\label{thm:regular-cauchy-interleaving-public-real-seal-export}
The public $\RegularCauchyInterleavingUp$ export of an accepted packet $I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)$ is exactly the finite $\RealUp$ seal boundary obtained from the two $\RegSeqRatUp$ source names $A,B$, the two $\StreamNameUp$ schedules $S_A,S_B$, the alternating selector $\sigma$, the combined modulus ledger $M$, the source seals $E_A,E_B$, the interleaved seal row $E$, the displayed $\hsame$ transports $H$, the $\Cont$ routes $C$, the $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$. Every public $\RealUp$ consumer factors through this displayed packet and receives no quotient real equality, selected host limit, ambient completeness principle, or third schedule.
\end{theorem}
\begin{proof}
Carrier admission is supplied by \autoref{thm:regular-cauchy-interleaving-carrier-admission}. The admitted row is the finite $\mathsf{BHist}$ packet of \autoref{def:regular-cauchy-interleaving-source}, so the public boundary has no carrier beyond the two source names, two schedules, selector, ledger, seals, transport rows, continuation rows, package row, and naming row.

Classifier transport is \autoref{thm:regular-cauchy-interleaving-classifier}. Selector parity exactness is \autoref{thm:regular-cauchy-interleaving-selector-parity-exactness}, combined modulus exactness is \autoref{thm:regular-cauchy-interleaving-combined-modulus-exactness}, and schedule-window coverage is \autoref{thm:regular-cauchy-interleaving-schedule-window-coverage}. These rows force every consumer read to use either the $A,S_A$ side with the first component of $M$ or the $B,S_B$ side with the second component of $M$.

The seal boundary is \autoref{thm:regular-cauchy-interleaving-real-seal-non-escape}. The obligation closure package of \autoref{thm:regular-cauchy-interleaving-obligation-closure-package} gathers the same rows, and \autoref{thm:regular-cauchy-interleaving-scoped-kernel-route} binds them to the displayed kernel route.

Repack these rows as the public export packet. Since the repacked packet exposes only the displayed $\RealUp$ seal boundary, a public consumer obtains the named seal interface and none of quotient equality, a selected host limit, ambient completeness, or a third schedule.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_public\_real\_seal\_export}

\begin{theorem}[Regular Cauchy interleaving bridge readback scope]
\label{thm:regular-cauchy-interleaving-bridge-readback-scope}
Any bridge readback from the public $\RealUp$ seal export of an accepted $\RegularCauchyInterleavingUp$ packet $I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)$ factors through the two $\RegSeqRatUp$ source names $A,B$, the two $\StreamNameUp$ schedules $S_A,S_B$, the alternating selector $\sigma$, the combined modulus ledger $M$, the source seal rows $E_A,E_B$, the interleaved seal row $E$, componentwise $\hsame$ transports $H$, $\Cont$ routes $C$, $\Pkg$ provenance $P$, and the local $\NameCert_{\RegularCauchyInterleavingUp}$ row $N$. The bridge readback has no route to a quotient real, selected host limit, ambient completeness principle, or third schedule beyond this displayed public seal surface.
\end{theorem}
\begin{proof}
Carrier admission is \autoref{thm:regular-cauchy-interleaving-carrier-admission}. It gives the finite packet rows that any bridge readback must start from: the two source names, their schedules, the selector, the modulus ledger, the three seal rows, transports, routes, provenance, and local naming row.

Selector parity exactness from \autoref{thm:regular-cauchy-interleaving-selector-parity-exactness} determines which source side is read. Combined modulus exactness from \autoref{thm:regular-cauchy-interleaving-combined-modulus-exactness} supplies the matching ledger component, and schedule-window coverage from \autoref{thm:regular-cauchy-interleaving-schedule-window-coverage} rules out a third schedule.

The seal boundary is controlled by \autoref{thm:regular-cauchy-interleaving-real-seal-non-escape}. The scoped kernel route of \autoref{thm:regular-cauchy-interleaving-scoped-kernel-route} then binds the same rows to the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route.

Finally apply the public Real seal export, \autoref{thm:regular-cauchy-interleaving-public-real-seal-export}. A bridge readback that begins from that public export can only read back the rows exported there, so it factors through $A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N$ and cannot access quotient equality, selected host limits, ambient completeness, or an unlisted schedule.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_bridge\_readback\_scope}

\begin{theorem}[Regular Cauchy interleaving finite-tail consumer boundary]
\label{thm:regular-cauchy-interleaving-finite-tail-consumer-boundary}
Every downstream consumer that reads the interleaved $\RealUp$ seal of an accepted $\RegularCauchyInterleavingUp$ packet through a finite-tail or diagonal-limit route must factor through one of the two displayed $\StreamNameUp$ schedules, the matching $\RegSeqRatUp$ source row, the combined modulus ledger, and the local $\NameCert$ row before it can consume a $\FiniteTailDiagonalSealUp$-style witness. The route is the sibling surface of \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regularcauchyname-namecert}, and \autoref{ch:concrete-instances-finitetaildiagonalseal-namecert}.
\end{theorem}
\begin{proof}
Use selector parity exactness. An even read is routed through $A,S_A$ and the first component of $M$, while an odd read is routed through $B,S_B$ and the second component.

Apply combined modulus exactness and schedule-window coverage. Together they make the selected schedule, matching regular source row, and selected modulus component the only finite window route into the interleaved seal.

Use the Real seal non-escape theorem and the bridge readback scope. They keep every seal-facing consumer downstream of the displayed $\hsame$ transports, $\Cont$ routes, package row, and local $\NameCert$ row.

The finite-tail handoff therefore has no coordinate for quotient reals, host limits, ambient completeness, or a third schedule. Any $\FiniteTailDiagonalSealUp$-style witness consumed downstream must use the displayed finite-window route.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving window-seal symmetry]
\label{thm:regular-cauchy-interleaving-window-seal-symmetry}
For an accepted $\RegularCauchyInterleavingUp$ packet $I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)$, the two parity branches preserve the same public $\RealUp$ seal surface. The even branch through $A,S_A$ and the odd branch through $B,S_B$ are distinguished only by selector parity and the selected component of the combined modulus ledger; after selector transport, schedule-window coverage, and real-seal non-escape, both branches expose the same interleaved seal row $E$ and no additional public seal coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyInterleavingUp.RegularCauchyInterleavingPacket\_window\_seal\_symmetry}
\begin{proof}
Use selector parity exactness to split any consumer read into the even branch and the odd branch. The even branch selects the $A,S_A$ side and the first ledger component, while the odd branch selects the $B,S_B$ side and the second ledger component.

Apply classifier transport and combined modulus exactness on each branch. These rows determine the selected source row and the matching modulus component before any public seal read occurs.

Schedule-window coverage rules out a third schedule and forces both parity branches through the two displayed $\StreamNameUp$ windows. The bridge readback scope keeps the same $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows attached to the selected read.

Finally apply real-seal non-escape and the public Real seal export. Both branches terminate at the same interleaved seal row $E$, so the branch distinction is internal to the finite-window route and does not create a second public $\RealUp$ seal surface.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving finite-tail budget route]
\label{thm:regular-cauchy-interleaving-finite-tail-budget-route}
Every finite-tail diagonal consumer of the interleaved $\RealUp$ seal of an accepted packet $I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)$ factors through the two displayed $\StreamNameUp$ schedules $S_A,S_B$, the matching $\RegSeqRatUp$ source rows $A,B$, the combined modulus ledger $M$, the downstream $\FiniteTailDiagonalSealUp$ witness surface, and the local $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. No finite-tail budget read bypasses this route through quotient equality, selected host limits, ambient completeness, or an unlisted schedule.
\end{theorem}
\begin{proof}
Begin with the finite-tail consumer boundary. It already places any diagonal-limit or finite-tail consumer downstream of a selected schedule, a matching regular source row, the combined modulus ledger, and the local naming row.

Use selector parity exactness and schedule-window coverage to identify the only two possible schedule windows. The selected window is $S_A$ for an even read and $S_B$ for an odd read, with no further schedule coordinate in the packet.

Combined modulus exactness supplies the budget component attached to that selected window. Carrier admission supplies the finite $\mathsf{BHist}$ packet, and the scoped kernel route keeps the selected read attached to the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

The sibling chapters \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regularcauchyname-namecert}, and \autoref{ch:concrete-instances-finitetaildiagonalseal-namecert} provide the schedule, regular-source, and finite-tail witness surfaces named by the boundary. Therefore every finite-tail budget read factors through the displayed route and has no bypass through the excluded public objects.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving public bridge readiness]
\label{thm:regular-cauchy-interleaving-public-bridge-readiness}
The obligation closure package, scoped kernel route, public real seal export, bridge readback scope, finite-tail consumer boundary, window-seal symmetry, and finite-tail budget route assemble the public bridge surface for $\RegularCauchyInterleavingUp$. A bridge-facing consumer of an accepted packet can read the two $\RegSeqRatUp$ source names, the two $\StreamNameUp$ schedules, selector parity, the combined modulus ledger, source and interleaved $\RealUp$ seal rows, $\mathsf{BHist}$ support, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, local $\NameCert$ row, and the downstream finite-tail witness route; it cannot read quotient real equality, selected host limits, ambient completeness, or a third schedule.
\end{theorem}
\begin{proof}
The obligation closure package gives the carrier, classifier, combined modulus, schedule coverage, and seal-boundary rows. The scoped kernel route binds these rows to the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\RatUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

The public Real seal export exposes the seal row visible to outside consumers, and the bridge readback scope describes exactly which packet rows a bridge-facing readback can inspect. The finite-tail consumer boundary then places diagonal consumers downstream of the same selected schedule and budget route.

Window-seal symmetry shows that the even and odd branches preserve one public seal surface rather than two branch-specific exports. The finite-tail budget route supplies the budget and witness path needed by downstream finite-tail consumers.

Combining these rows yields the public bridge surface for $\RegularCauchyInterleavingUp$. Since every component in the assembled surface is one of the displayed packet rows or one of the named sibling surfaces, the route has no coordinate for quotient equality of reals, selected host limits, ambient completeness, or any schedule beyond $S_A$ and $S_B$.
\end{proof}

\begin{theorem}[Regular Cauchy interleaving RegSeqRat Real consumer factorization]
\label{thm:regular-cauchy-interleaving-regseqrat-real-consumer-factorization}
Let
$$
I=(A,B,S_A,S_B,\sigma,M,E_A,E_B,E,H,C,P,N)
$$
be an accepted $\RegularCauchyInterleavingUp$ packet. Every $\RegSeqRatUp$, $\CauchySequenceSpaceUp$, or terminal $\RealUp$ consumer of the interleaved seal factors through the selected parity branch, then through the selected $\StreamNameUp$ schedule, the matching $\RegSeqRatUp$ source row, the corresponding component of $M$, and finally through $E,H,C,P,N$. The factorization exports no quotient stream, selected host limit, host real equality, ambient completeness principle, or third schedule.
\end{theorem}
\begin{proof}
Use selector parity exactness to split the consumer read. The even branch is routed through $A$ and $S_A$, while the odd branch is routed through $B$ and $S_B$.

Apply combined modulus exactness on the selected branch. The even route reads the first component of $M$, the odd route reads the second component of $M$, and the selected ledger component is fixed before any $\RegSeqRatUp$, $\CauchySequenceSpaceUp$, or terminal $\RealUp$ consumer can inspect the interleaved seal.

Schedule-window coverage rules out an unscheduled route. Thus the selected $\StreamNameUp$ window and the matching $\RegSeqRatUp$ source row are the only finite-name entry points for the consumer.

Finally apply real-seal non-escape and the public Real seal export. These rows keep the consumer downstream of the interleaved seal $E$, the displayed $\hsame$ transports $H$, the $\Cont$ routes $C$, package provenance $P$, and the local naming row $N$, while leaving quotient streams, selected host limits, host real equality, ambient completeness, and any third schedule outside the exported route.
\end{proof}

\closureat{RegularCauchyInterleavingUp}{seedStr}
\closureat{RegularCauchyInterleavingUp}{obligationStr}
\closureat{RegularCauchyInterleavingUp}{scopedStr}
\closureat{RegularCauchyInterleavingUp}{publicStr}

\begin{closurestatus}{\RegularCauchyInterleavingUp}
  \constructivestory{A $\RegularCauchyInterleavingUp$ packet is generated from two $\RegSeqRatUp$ regular names, their $\StreamNameUp$ schedules, an alternating unary selector, a combined modulus ledger, source $\RealUp$ readbacks, an interleaved $\RealUp$ seal row, displayed $\hsame$ and $\Cont$ rows, package provenance, and a local naming row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{thm:regular-cauchy-interleaving-public-real-seal-export} gives the public $\RealUp$ seal export over the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\RatUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient equality of reals, selected host limits, ambient completeness, diagonal-completion uniqueness, or bridge checking.}
  \upgradepath{Bridge closure requires a checked bridge theorem over the public seal export and the acceptance-bridge schema.}
\end{closurestatus}
