\chapter{A Concrete Naming Certificate for $\EllipticCurveUp$}
\label{ch:concrete-instances-ellipticcurve-namecert}

The elliptic-curve interface $\EllipticCurveUp$ packages a smooth projective genus-one curve over a field carrier together with a chosen base point. It depends on $\NameCert_{\ProjectiveVarUp}$ (\autoref{ch:concrete-instances-projectivevar-namecert}) and $\NameCert_{\FieldUp}$ (\autoref{ch:concrete-instances-field-namecert}).

\section{Carrier definition}
\label{sec:ellipticcurve-carrier}

\begin{definition}[Elliptic-curve BHist carrier packet]
\label{def:ellipticcurve-bhist-carrier-packet}
An $\EllipticCurveUp$ carrier is a $\mathsf{BHist}$ packet
$$
\mathcal{E}=(\mathcal{F},\mathcal{P},a_1,a_2,a_3,a_4,a_6,\gamma,\sigma,o,\lambda_F,\lambda_P,\rho)
$$
where $\mathcal{F}$ is a source $\NameCert_{\FieldUp}$ row, $\mathcal{P}$ is a source $\NameCert_{\ProjectiveVarUp}$ row over the same field row, $a_1,a_2,a_3,a_4,a_6:\mathsf{BHist}$ are field-coefficient rows, $\gamma:\mathsf{BHist}$ is the homogeneous cubic and projective-incidence row, $\sigma:\mathsf{BHist}$ is the smooth genus-one boundary row, $o:\mathsf{BHist}$ is the chosen base-point row, $\lambda_F$ and $\lambda_P$ are the field and projective classifier rows witnessed through $\hsame$, and $\rho$ records the $\mathsf{Pkg}$ provenance of the two source certificates and the displayed rows.

The accepted endpoint is exactly the displayed history packet. It contains no ambient curve equality, no external point set, and no host discriminant predicate; all coefficient, incidence, smoothness, base-point, classifier, continuation, and provenance data are rows of $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$.
\end{definition}
\leandef{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket}

\section{The certificate}
\label{sec:ellipticcurve-certificate}

\begin{theorem}[Elliptic-curve field source obligation]
\label{thm:ellipticcurve-field-source-obligation}
In every carrier packet of \autoref{def:ellipticcurve-bhist-carrier-packet}, the coefficient rows $a_1,a_2,a_3,a_4,a_6$, the field operation rows used to form the Weierstrass cubic, and the nonzero-discriminant row are projected from the $\NameCert_{\FieldUp}$ dependency. The $\EllipticCurveUp$ boundary may read these rows only as $\mathsf{BHist}$ data with the $\mathsf{Pkg}$ provenance inherited from $\mathcal{F}$.
\end{theorem}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_field\_source\_obligation}
\begin{proof}
Project the carrier packet to its $\mathcal{F}$ component and to the five displayed coefficient rows. The FieldUp certificate supplies the addition, multiplication, negation, unit, and nonzero rows needed to interpret the coefficients and the discriminant expression.

The Weierstrass cubic row is then formed by reading those operations through the same $\mathsf{BHist}$ ledger. The discriminant row is not a host-side assertion about a curve; it is the nonzero field row reached through the projected FieldUp source.

Repack the coefficient rows, operation rows, and nonzero-discriminant row with the original $\mathsf{Pkg}$ provenance. This gives the exact field-source part of the elliptic-curve certificate surface.
\end{proof}

\begin{theorem}[Elliptic-curve projective genus-one obligation]
\label{thm:ellipticcurve-projective-genus-one-obligation}
In every carrier packet of \autoref{def:ellipticcurve-bhist-carrier-packet}, the projective equation row, projective-incidence row, smoothness row, and genus-one boundary row are carried by the $\NameCert_{\ProjectiveVarUp}$ dependency as BEDC rows. They are not imported as host curves, external schemes, or ambient geometric equalities.
\end{theorem}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_projective\_genus\_one\_obligation}
\begin{proof}
Project the packet to its $\mathcal{P}$ component and to the homogeneous cubic row $\gamma$. The ProjectiveVarUp source supplies the projective carrier, homogeneous zero-locus, incidence, classifier, and ledger rows needed to read $\gamma$ as a projective BEDC row.

Next project the smooth genus-one boundary row $\sigma$. Its smoothness and genus-one readings are attached to the same projective package, so the row is routed through the ProjectiveVarUp carrier and exactness surface rather than through an external curve object.

Repacking $\mathcal{P}$, $\gamma$, and $\sigma$ records the projective equation, incidence, smoothness, and genus-one data as the projective dependency portion of the $\EllipticCurveUp$ carrier.
\end{proof}

\begin{theorem}[Elliptic-curve base-point stability obligation]
\label{thm:ellipticcurve-basepoint-stability-obligation}
The chosen base-point row $o$ in \autoref{def:ellipticcurve-bhist-carrier-packet} is stable under the inherited projective classifier and the inherited field classifier. If the field source is transported by $\lambda_F$ and the projective source is transported by $\lambda_P$, the transported packet carries a base-point row connected to $o$ by $\hsame$ and accepted by the same $\Cont$ provenance surface.
\end{theorem}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_basepoint\_stability\_obligation}
\begin{proof}
Start with the base-point row $o$ and the projective classifier row $\lambda_P$. Projective transport preserves the projective incidence row, so the image of $o$ remains accepted by the transported projective carrier.

Use the field classifier row $\lambda_F$ to transport the coordinate and coefficient readings used by the base-point incidence test. The same FieldUp source rows supply the operation and nonzero data needed after transport.

The continuation row records that the transported endpoint is read through the same base-point provenance route. Repack the transported field source, projective source, incidence row, and base-point row to obtain the stable $\EllipticCurveUp$ packet.
\end{proof}

\begin{theorem}[Elliptic-curve classifier transport obligation]
\label{thm:ellipticcurve-classifier-transport-obligation}
Classified replacement of the field source and the projective source transports the whole carrier packet of \autoref{def:ellipticcurve-bhist-carrier-packet}. Componentwise $\hsame$ transports the coefficient, cubic, smoothness, genus-one, and base-point rows, while the displayed $\Cont$ rows preserve their acceptance and the $\mathsf{Pkg}$ row preserves their provenance.
\end{theorem}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_classifier\_transport\_obligation}
\begin{proof}
Project a classifier witness into its field part $\lambda_F$ and projective part $\lambda_P$. The field part transports the coefficient and operation rows; the projective part transports the homogeneous cubic, incidence, smoothness, and genus-one rows.

Apply componentwise $\hsame$ to the displayed $\mathsf{BHist}$ entries. Each transported entry is accepted through its original $\Cont$ row after replacing the source endpoint by the classified endpoint.

Finally carry the provenance row $\rho$ along the same componentwise route. Repacking the transported entries gives the full replacement carrier packet, with no additional quotient or host equality inserted at the boundary.
\end{proof}

\begin{theorem}[Base-point readback obligation]\label{thm:ellipticcurve-basepoint-readback-obligation}
For every $\EllipticCurveUp$ carrier packet of \autoref{def:ellipticcurve-bhist-carrier-packet}, the base-point row $o$ is readable as a point row of the carried $\ProjectiveVarUp$ surface. If $o\hsame o'$ and the $\ProjectiveVarUp$ classifier transports the point row from $o$ to $o'$, then replacing $o$ by $o'$ gives a carrier packet with the same coefficient, cubic, smooth genus-one, field, classifier, and $\mathsf{Pkg}$ provenance rows.
\end{theorem}
\begin{proof}
Project the $\ProjectiveVarUp$ source certificate $\mathcal{P}$ from the carrier packet. Its point readback clause supplies the carrier row containing $o$, and the incidence ledger records that $o$ lies on the displayed cubic row $\gamma$.

Apply the $\hsame$ transport hypothesis to the point row. The $\ProjectiveVarUp$ classifier transports incidence along this row, so the replacement point $o'$ remains attached to the same projective carrier and the same cubic row.

The remaining rows are unchanged projections of the original packet. Repacking them with $o'$ yields the transported $\EllipticCurveUp$ packet, and no field coefficient, smooth genus-one boundary, classifier, or provenance row is altered.
\end{proof}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_basepoint\_readback\_obligation}

\begin{theorem}[Smooth projective carrier obligation]\label{thm:ellipticcurve-smooth-projective-carrier-obligation}
An accepted $\EllipticCurveUp$ carrier is accepted only through the $\ProjectiveVarUp$ projective-carrier, incidence, smoothness, genus-one, and point rows together with the $\FieldUp$ scalar rows for the displayed equation coefficients. In particular, smoothness and genus-one status are certificate rows over the carried projective variety and field source, not host-level assertions about an unrecorded curve.
\end{theorem}
\begin{proof}
Unpack an accepted carrier packet. The projective carrier and incidence rows are projections of $\mathcal{P}$, while the coefficient and scalar rows used by $\gamma$ are projections of $\mathcal{F}$.

The smooth genus-one boundary row $\sigma$ is then checked against those same projections. Its scope is the displayed projective carrier over the displayed field coefficients, so there is no separate ambient curve object to validate.

Finally attach the base-point row by \autoref{thm:ellipticcurve-basepoint-readback-obligation}. The accepted carrier is therefore exactly the smooth genus-one projective carrier with the named base point and the named field dependency rows.
\end{proof}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_smooth\_projective\_carrier\_obligation}

\begin{theorem}[Field dependency ledger obligation]\label{thm:ellipticcurve-field-dependency-ledger-obligation}
All coefficient and scalar comparisons in an $\EllipticCurveUp$ carrier packet descend through the $\FieldUp$ classifier and the $\mathsf{Pkg}$ provenance ledger. If two packets have $\hsame$-transported equation rows and the $\FieldUp$ source certificate classifies their coefficient rows as the same scalar data, then every scalar comparison used by the projective incidence, smoothness, genus-one, and base-point clauses is transported by the same finite ledger.
\end{theorem}
\begin{proof}
Read the coefficient rows $a_1,a_2,a_3,a_4,a_6$ from the carrier packet of \autoref{def:ellipticcurve-bhist-carrier-packet}. Those rows are not interpreted directly; they are projected through the $\NameCert_{\FieldUp}$ source certificate $\mathcal{F}$.

Use the $\FieldUp$ classifier to transport each scalar comparison along the displayed $\hsame$ relation on coefficient and cubic rows. The finite $\mathsf{Pkg}$ provenance row records the order in which these transported scalar rows feed the projective incidence, smooth genus-one, and base-point checks.

Repack the transported scalar rows with the unchanged projective certificate rows. The result is the same dependency ledger for the elliptic-curve packet, now read over the transported coefficient and cubic rows.
\end{proof}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_field\_dependency\_ledger\_obligation}

\begin{theorem}[EllipticCurveUp NameCert exactness obligation]\label{thm:ellipticcurve-namecert-exactness-obligation}
The public $\NameCert_{\EllipticCurveUp}$ obligation surface consists exactly of the carrier packet of \autoref{def:ellipticcurve-bhist-carrier-packet}, the field-source rows of \autoref{thm:ellipticcurve-field-source-obligation}, the projective genus-one rows of \autoref{thm:ellipticcurve-projective-genus-one-obligation}, the base-point stability row of \autoref{thm:ellipticcurve-basepoint-stability-obligation}, the classifier transport row of \autoref{thm:ellipticcurve-classifier-transport-obligation}, the base-point readback of \autoref{thm:ellipticcurve-basepoint-readback-obligation}, the smooth projective validation of \autoref{thm:ellipticcurve-smooth-projective-carrier-obligation}, the field dependency transport of \autoref{thm:ellipticcurve-field-dependency-ledger-obligation}, and the ledger exactness asserting that no row outside $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, $\NameCert_{\FieldUp}$, and $\NameCert_{\ProjectiveVarUp}$ is exported.
\end{theorem}
\begin{proof}
Soundness is obtained by projecting a public elliptic-curve certificate to its listed packet rows. The carrier definition supplies the field source, projective-variety source, equation, smoothness, genus-one, base-point, and provenance rows.

Completeness goes in the reverse direction. Given exactly those rows with the field-source, projective genus-one, base-point, classifier, readback, smooth projective, and field dependency clauses, assemble the tuple of \autoref{def:ellipticcurve-bhist-carrier-packet} and read it as the public $\EllipticCurveUp$ surface.

The exclusion clause follows from the same projection list. Since every accepted row is one of the displayed $\mathsf{BHist}$ rows or one of the two source $\NameCert$ projections, the certificate exports no unrecorded host curve, no external equation equality, and no standard bridge row.
\end{proof}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_semantic\_name\_certificate}

\begin{theorem}[Elliptic-curve Weierstrass coefficient ledger]
\label{thm:ellipticcurve-weierstrass-coefficient-ledger}
In the carrier packet of \autoref{def:ellipticcurve-bhist-carrier-packet}, the five coefficient rows $a_1,a_2,a_3,a_4,a_6$ and every scalar operation used by the displayed Weierstrass cubic are projected through the $\FieldUp$ source certificate and the $\mathsf{Pkg}$ ledger. The cubic row is therefore a BEDC row over the inherited field source, not a host polynomial equality.
\end{theorem}
\begin{proof}
Project the packet to its field source $\mathcal{F}$ and to the coefficient rows $a_1,a_2,a_3,a_4,a_6$. The field source obligation of \autoref{thm:ellipticcurve-field-source-obligation} supplies the addition, multiplication, negation, unit, and nonzero rows used by the cubic.

Next read the provenance component $\rho$ of the packet. It records that the coefficient and scalar-operation rows enter the cubic through the same $\mathsf{Pkg}$ ledger as the $\FieldUp$ source.

Repacking these projections gives the coefficient ledger. Since every scalar row comes from $\mathcal{F}$ and $\rho$, there is no unrecorded host polynomial equality in the certificate surface.
\end{proof}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_weierstrass\_coefficient\_ledger}

\begin{theorem}[Elliptic-curve base-point incidence exactness]
\label{thm:ellipticcurve-basepoint-incidence-exactness}
Base-point acceptance in an $\EllipticCurveUp$ carrier packet is exactly projective point carriage plus incidence with the displayed cubic under the inherited $\ProjectiveVarUp$ classifier. Replacing it by an ambient point-set membership predicate or by host curve equality changes the certificate surface.
\end{theorem}
\begin{proof}
Project the packet to its projective source $\mathcal{P}$, cubic row $\gamma$, and base-point row $o$. The projective genus-one obligation of \autoref{thm:ellipticcurve-projective-genus-one-obligation} supplies the projective carrier and incidence rows attached to $\gamma$.

Use \autoref{thm:ellipticcurve-basepoint-readback-obligation} to read $o$ as a point row of the carried projective surface. The base-point stability row of \autoref{thm:ellipticcurve-basepoint-stability-obligation} transports that reading through the inherited projective classifier.

The exactness obligation of \autoref{thm:ellipticcurve-namecert-exactness-obligation} excludes rows outside the displayed packet and its two source certificates. Thus base-point acceptance is precisely carriage plus incidence with $\gamma$ under the inherited classifier.
\end{proof}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_basepoint\_incidence\_exactness}

\begin{theorem}[Elliptic-curve field-projective source compatibility]
\label{thm:ellipticcurve-field-projective-source-compatibility}
Transporting the $\FieldUp$ source and the $\ProjectiveVarUp$ source together transports the Weierstrass cubic, smooth genus-one row, and base-point row of an $\EllipticCurveUp$ packet. The transported packet adds no host curve equality and no external comparison between projective models.
\end{theorem}
\begin{proof}
Project the classifier transport witnesses $\lambda_F$ and $\lambda_P$ from the carrier packet. The classifier transport obligation of \autoref{thm:ellipticcurve-classifier-transport-obligation} applies $\lambda_F$ to the coefficient and scalar rows and applies $\lambda_P$ to the cubic, incidence, smoothness, genus-one, and base-point rows.

The field dependency ledger of \autoref{thm:ellipticcurve-field-dependency-ledger-obligation} keeps every scalar comparison on the $\FieldUp$ side. The base-point stability row of \autoref{thm:ellipticcurve-basepoint-stability-obligation} keeps point acceptance on the $\ProjectiveVarUp$ side.

Repack the transported field source, projective source, cubic, smooth genus-one row, base-point row, classifier rows, and provenance row. The result is a transported $\EllipticCurveUp$ packet whose compatibility is witnessed entirely by the two source certificates and their BEDC rows.
\end{proof}
\leanchecked{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_field\_projective\_source\_compatibility}

\closureat{EllipticCurveUp}{publicStr}[BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_semantic\_name\_certificate]
\closureat{EllipticCurveUp}{bridgedStr}[BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_semantic\_name\_certificate]
\closureat{EllipticCurveUp}{matureStr}[BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_semantic\_name\_certificate]

\begin{closurestatus}{\EllipticCurveUp}
  \constructivestory{An elliptic curve is generated as a $\mathsf{BHist}$ packet containing a $\FieldUp$ source row, a $\ProjectiveVarUp$ source row over the same field, five field-coefficient rows, a homogeneous cubic and incidence row, a smooth genus-one boundary row, a chosen base-point row, classifier transports for the two sources, and $\mathsf{Pkg}$ provenance. The carrier accepts exactly packets with those coefficient, cubic, smoothness, genus-one, base-point, field, projective, continuation, and provenance rows; it excludes an ambient curve object, host discriminant predicate, external point set, group law, Weierstrass standard bridge, and equality between curve models. Two accepted packets classify together when the inherited field classifier transports coefficient and scalar-operation rows, the inherited projective classifier transports the cubic, incidence, smoothness, genus-one, and base-point rows, and componentwise $\hsame$ plus $\Cont$ keeps each row accepted. The source specification is this field-projective carrier packet, the pattern records field-source obligations, projective genus-one obligations, base-point stability, classifier transport, smooth projective validation, and field dependency ledgers, while the ledger keeps the raw coefficient rows, cubic row, base point, source classifiers, and provenance visible. The five naming-certificate obligations hold because an accepted packet inhabits the carrier, the inherited field and projective classifiers provide reflexivity, symmetry, and transitivity, and the classifier transport theorem repacks every transported coefficient, incidence, and base-point row as another accepted packet. A history $h$ lies in the signature gap of an $\EllipticCurveUp$ token $p$ when the source domain accepts this packet, the signature relation pairs it with an answer packet and evidence ledger, and token introduction names that answer as $p$; unfolded, the field row, projective row, Weierstrass coefficients, cubic incidence, smooth genus-one row, and base point of $h$ are the rows encoded by $p$. The chapter registers this smooth projective genus-one packet under $\EllipticCurveUp$; it introduces no elliptic-curve group operation, no external Weierstrass bridge, and no independent curve-equality primitive.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The semantic certificate is the public exported $\EllipticCurveUp$ carrier packet over the inherited $\FieldUp$ and $\ProjectiveVarUp$ sources, with the displayed coefficient, cubic, base-point, transport, classifier, and provenance rows.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.EllipticCurveUp.EllipticCurveCarrierPacket\_semantic\_name\_certificate}
  \bridgestatus{none}
  \notclaimed{The chapter does not close an elliptic-curve group law, a standard Weierstrass bridge, or external equality between curve models.}
  \upgradepath{No further paper-side theory grade remains for the field-projective genus-one packet; remaining work is an optional standard bridge and downstream consumers.}
\end{closurestatus}

\begin{definition}[Elliptic-curve Weierstrass admission profile]
\label{def:ellipticcurve-weierstrass-admission-profile}
A Weierstrass admission profile for the public $\EllipticCurveUp$ surface is a finite row family
$$
W=(\mathcal{F},\mathcal{P},a_1,a_2,a_3,a_4,a_6,\gamma,\sigma,o,\lambda_F,\lambda_P,\rho)
$$
with the following boundary readings. The row $\mathcal{F}$ is a $\NameCert_{\FieldUp}$ source row; the five rows $a_1,a_2,a_3,a_4,a_6:\BHist$ and the scalar operations used in the Weierstrass cubic are read through that field source; $\mathcal{P}$ is a $\NameCert_{\ProjectiveVarUp}$ source row over the same field row; $\gamma:\BHist$ is the homogeneous cubic incidence row over the five displayed coefficients; $\sigma:\BHist$ is the smooth genus-one boundary row over that projective cubic; $o:\BHist$ is the chosen base-point incidence row; $\lambda_F$ and $\lambda_P$ are the inherited field and projective classifier transport rows; and $\rho$ is the $\Pkg$ provenance row naming exactly these source, coefficient, cubic, smoothness, base-point, and transport entries.

The profile has no coordinate for an elliptic-curve group operation, no coordinate for equality with an external curve model, and no coordinate for host-level equality between a standard Weierstrass presentation and a projective carrier. Such data may be discussed only after a separate row is supplied outside this admission profile.
\end{definition}

\begin{theorem}[Elliptic-curve Weierstrass bridge boundary]
\label{thm:ellipticcurve-weierstrass-bridge-boundary}
Let $W$ be a Weierstrass admission profile as in \autoref{def:ellipticcurve-weierstrass-admission-profile}. If every standard-presentation datum in $W$ is admitted only through the $\FieldUp$ source row, the $\ProjectiveVarUp$ source row, the five coefficient rows, the cubic incidence row, the smooth genus-one row, the base-point row, the two classifier transport rows, and the $\Pkg$ provenance row listed in \autoref{def:ellipticcurve-bhist-carrier-packet}, then $W$ repacks as the same public $\EllipticCurveUp$ carrier packet. Projecting the public $\NameCert_{\EllipticCurveUp}$ surface recovers exactly those rows, and exports no elliptic-curve group law, no external curve equality, and no equality between a host Weierstrass model and the carried projective model.
\end{theorem}
\begin{proof}
Start with the field side of the profile. By \autoref{thm:ellipticcurve-field-source-obligation}, the five coefficient rows and the scalar operation rows used by the cubic are readable only through the $\NameCert_{\FieldUp}$ source $\mathcal{F}$. By \autoref{thm:ellipticcurve-weierstrass-coefficient-ledger}, their contribution to the Weierstrass equation is the displayed cubic row $\gamma$ together with its $\Pkg$ provenance, not a host polynomial equality.

Project the geometric side next. By \autoref{thm:ellipticcurve-projective-genus-one-obligation}, the cubic incidence row $\gamma$ and the smooth genus-one row $\sigma$ are carried by the $\NameCert_{\ProjectiveVarUp}$ dependency as BEDC rows. By \autoref{thm:ellipticcurve-smooth-projective-carrier-obligation}, smoothness and genus-one status are checked against the same field and projective projections, so the profile does not introduce a second curve object.

For the chosen point, \autoref{thm:ellipticcurve-basepoint-incidence-exactness} identifies base-point acceptance with projective point carriage plus incidence with $\gamma$ under the inherited projective classifier. The base-point row therefore repacks with $\mathcal{P}$, $\gamma$, and $\sigma$ as the same point coordinate $o$ of the public packet; it is not an external point-set membership predicate.

Now apply the two transport rows. The classifier transport obligation of \autoref{thm:ellipticcurve-classifier-transport-obligation} transports coefficients, cubic, smoothness, genus-one, and base-point rows componentwise through $\lambda_F$, $\lambda_P$, $\hsame$, and $\Cont$. The field-projective compatibility theorem, \autoref{thm:ellipticcurve-field-projective-source-compatibility}, says that this simultaneous transport still repacks as an $\EllipticCurveUp$ packet and adds no host comparison between projective models.

It remains to identify the public export. By \autoref{thm:ellipticcurve-namecert-exactness-obligation}, the public $\NameCert_{\EllipticCurveUp}$ surface consists exactly of the carrier packet, the field-source rows, the projective genus-one rows, the base-point rows, the classifier transport rows, and the ledger exactness over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert_{\FieldUp}$, and $\NameCert_{\ProjectiveVarUp}$. These are precisely the coordinates of $W$. Hence projecting the public surface recovers the same tuple, while any group law row, host curve-equality row, or external Weierstrass-to-projective equality row would require a coordinate absent from both \autoref{def:ellipticcurve-weierstrass-admission-profile} and \autoref{def:ellipticcurve-bhist-carrier-packet}.
\end{proof}
