\chapter{A Concrete Naming Certificate for $\CompleteOrderedRealUp$}
\label{ch:concrete-instances-completeorderedreal-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and Bourbaki's ordered-field language, the $\CompleteOrderedRealUp$ packet records the finite interface where $\RealUp$ names are read together with constructive ordered-field data and located least-upper-bound data. It sits over the ordered-field surface of \autoref{ch:concrete-instances-archimedeanorderedfield-namecert}, the located-supremum boundary of \autoref{ch:concrete-instances-locatedsupremum-namecert}, and the inhabited bounded-family completion surface of \autoref{ch:concrete-instances-dedekind-complete-real-namecert}. The packet is a BEDC NameCert interface for consumers that need these rows in one visible route; it is not a construction of all reals, not a quotient carrier, and not a classical completeness principle.

\begin{definition}[CompleteOrderedReal carrier]
\label{def:complete-ordered-real-carrier}
A $\CompleteOrderedRealUp$ carrier is a finite $\BHist$ tuple
$$
K=(R,A,S,D,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the family of $\RealUp$ endpoint and witness rows read by the packet.
\item $A$ is the $\ArchimedeanOrderedFieldUp$ row supplying displayed addition, negation, multiplication, order, rational-bound, and Archimedean comparison data over the rows of $R$.
\item $S$ is the $\LocatedSupremumUp$ row supplying the upper-bound and lower-approximation faces for located bounded windows over $R$.
\item $D$ is the $\DedekindCompleteRealUp$ row tying inhabited bounded $\RealUp$ family windows to the located-supremum witness and terminal real-seal readback.
\item $W$ is the local compatibility ledger recording which real endpoints, order comparisons, bounded-family observations, and supremum precision requests are being inspected.
\item $H$ records componentwise $\hsame$ transports for the real rows, ordered-field row, located-supremum row, completion row, compatibility ledger, continuation routes, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay from real-name inspection through ordered-field comparison, located-supremum witnessing, completion handoff, and local compatibility.
\item $P$ is the $\Pkg$ provenance over $\CompleteOrderedRealUp$, $\RealUp$, $\ArchimedeanOrderedFieldUp$, $\LocatedSupremumUp$, $\DedekindCompleteRealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CompleteOrderedRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only by replaying $R,A,S,D,W,H,C,P,N$. The carrier has no coordinate for a Dedekind-cut construction of $\RealUp$, arbitrary subset completeness, trichotomy, quotient reals, countable choice, host real equality, or bridge checking.
\end{definition}

\begin{theorem}[CompleteOrderedReal NameCert obligations]
\label{thm:complete-ordered-real-namecert-obligations}
For every accepted $\CompleteOrderedRealUp$ carrier $K=(R,A,S,D,W,H,C,P,N)$, the local $\NameCert_{\CompleteOrderedRealUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed real endpoint and witness rows, ordered-field row, located-supremum row, completion row, compatibility ledger, transports, continuations, provenance, and local naming row;
\item ordered-field compatibility, requiring every operation, order, rational-bound, and Archimedean comparison read to pass through $A$ over the same real rows listed in $R$ and $W$;
\item located-supremum compatibility, requiring every upper-bound and lower-approximation read to pass through $S$ and the bounded-family handoff in $D$ at a precision listed in $W$;
\item transport and replay stability, requiring $H$ and $C$ to preserve the route $R,A,S,D,W$ componentwise;
\item ledger exhaustion, requiring $P$ and $N$ to export no Dedekind-cut construction, arbitrary subset completeness, trichotomy, quotient real, countable-choice selector, host real equality, or bridge-checked standard object.
\end{enumerate}
No local obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:complete-ordered-real-carrier}. The accepted packet exposes exactly the real rows, ordered-field row, located-supremum row, completion row, compatibility ledger, transport row, replay row, provenance row, and local naming row.

Ordered-field compatibility is inherited through the displayed row $A$. Its operation, order, rational-bound, and Archimedean comparison reads are available only over the real rows recorded in $R$ and selected by the local ledger $W$.

Located-supremum compatibility is inherited through the displayed rows $S$ and $D$. The row $S$ supplies the upper-bound and lower-approximation faces, while $D$ records the inhabited bounded-family handoff that reaches the terminal $\RealUp$ seal.

Transport and replay are structural. Componentwise $\hsame$ in $H$ preserves each displayed coordinate, and $\Cont$ replay in $C$ repeats the route $R,A,S,D,W$ for every accepted request.

Finally, provenance is exhausted by $P$ and $N$. Since the excluded principles are not coordinates of $K$, the local $\NameCert_{\CompleteOrderedRealUp}$ surface cannot export them.
\end{proof}

\begin{theorem}[CompleteOrderedReal Archimedean order route]
\label{thm:complete-ordered-real-archimedean-order-route}
Every order-facing read exported by an accepted $\CompleteOrderedRealUp$ carrier factors through
$$
R \longmapsto A \longmapsto W \longmapsto H,C,P,N .
$$
Thus the packet presents constructive ordered-field behavior only through the existing $\ArchimedeanOrderedFieldUp$ surface over displayed $\RealUp$ rows. It does not identify those rows with quotient reals, host real equality, trichotomy, a complete host ordered field, or a bridge-checked standard object.
\end{theorem}
\begin{proof}
Start with an order-facing consumer of $K$. The only row carrying ordered-field operations and comparisons is $A$, and the row $A$ is indexed by the displayed real rows in $R$.

The compatibility ledger $W$ selects the particular endpoints, operation reads, rational-bound checks, and Archimedean comparisons in scope. No order read can bypass $W$, because the local carrier does not expose an independent host ordered-field coordinate.

The structural rows $H,C,P,N$ then transport, replay, source, and name this route. Since quotient reals, host real equality, trichotomy, complete host ordered fields, and bridge-checked standard objects are absent from the carrier, the route exports none of them.
\end{proof}

\begin{theorem}[CompleteOrderedReal located-supremum boundary]
\label{thm:complete-ordered-real-located-supremum-boundary}
Every supremum-facing read exported by an accepted $\CompleteOrderedRealUp$ carrier factors through
$$
R \longmapsto W \longmapsto S \longmapsto D \longmapsto H,C,P,N .
$$
The read supplies only the displayed located upper-bound and lower-approximation boundary for the named inhabited bounded family window. It does not supply a Dedekind-cut construction of $\RealUp$, arbitrary subset completeness, trichotomy, quotient reals, countable choice, host real equality, or bridge checking.
\end{theorem}
\begin{proof}
Begin with a supremum-facing request. The local ledger $W$ fixes the family observations, bounds, and precision request currently under inspection over the real rows $R$.

The row $S$ is then the only located-supremum coordinate. It supplies the upper-bound face and the lower-approximation face for the precision listed in $W$.

The row $D$ is the only completion-facing handoff. It ties the located-supremum read to the inhabited bounded-family route and terminal $\RealUp$ seal without adding a separate arbitrary subset classifier.

Finally, $H,C,P,N$ transport, replay, source, and name exactly this displayed route. The excluded completeness and classical-order principles have no carrier coordinate, so they cannot be read from the packet.
\end{proof}

\begin{closurestatus}{\CompleteOrderedRealUp}
  \constructivestory{A $\CompleteOrderedRealUp$ packet is generated from displayed $\RealUp$ endpoint and witness rows, an $\ArchimedeanOrderedFieldUp$ ordered-field row, a $\LocatedSupremumUp$ least-upper-bound row, a $\DedekindCompleteRealUp$ inhabited bounded-family handoff, a compatibility ledger, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:complete-ordered-real-carrier}, \autoref{thm:complete-ordered-real-namecert-obligations}, \autoref{thm:complete-ordered-real-archimedean-order-route}, and \autoref{thm:complete-ordered-real-located-supremum-boundary} seed the finite ordered-field and located-supremum interface for displayed $\RealUp$ data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Dedekind-cut construction, arbitrary subset completeness, trichotomy, quotient reals, countable choice, bridge checking, host real equality, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, ordered-field compatibility, located-supremum compatibility, transport stability, replay stability, and ledger exhaustion for BEDC.Derived.CompleteOrderedRealUp.}
\end{closurestatus}
