\chapter{A Concrete Naming Certificate for $\CauchyLocalizationUp$}
\label{ch:concrete-instances-cauchy-localization-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, the $\CauchyLocalizationUp$ packet records the finite-window point at which a regular rational Cauchy source is inspected only as far as a requested tolerance requires, then sealed into the Real route without exporting a quotient stream or a selected limit. It sits between the dyadic arithmetic surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the effective threshold discipline of \autoref{ch:concrete-instances-cauchyrate-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter isolates the Cauchy localization row consumed by Real and Completion arguments as finite $\BHist$ data, not as ambient completeness, countable choice, host real equality, or quotient equality of streams.

\begin{definition}[Cauchy localization carrier]
\label{def:cauchy-localization-carrier}
A $\CauchyLocalizationUp$ carrier is a finite $\BHist$ packet
$$
K=(W,R,D,T,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\StreamNameUp$ window row naming exactly the finite source positions inspected for the requested tolerance.
\item $R$ is the $\RegSeqRatUp$ source row whose regular rational readback supplies the values visible through $W$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the rational radius, dyadic comparison cells, and arithmetic budget attached to the request.
\item $T$ is the $\CauchyRateUp$ threshold row selecting the displayed late index after which the window is sufficient for the tolerance in $D$.
\item $L$ is the localized request window, pairing the request precision with the subwindow of $W$ certified by $T$ and read through $R$.
\item $E$ is the $\RealUp$ seal row reached only after $W,R,D,T,L$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the StreamName window, RegSeqRat source, DyadicRatCore tolerance ledger, CauchyRate threshold, localized request window, Real seal, continuation row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a precision request through $D$, $T$, $W$, $L$, $R$, and finally to the seal row $E$.
\item $P$ is the $\Pkg$ provenance over $\CauchyLocalizationUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyRateUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyLocalizationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,R,D,T,L,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, host real equality, countable choice, detached Real completeness, or an ambient completion theorem.
\end{definition}

\begin{theorem}[Cauchy localization NameCert obligations]
\label{thm:cauchy-localization-namecert-obligations}
For an accepted $\CauchyLocalizationUp$ carrier $K=(W,R,D,T,L,E,H,C,P,N)$, the local $\NameCert_{\CauchyLocalizationUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the finite StreamName window, RegSeqRat source row, DyadicRatCore tolerance ledger, CauchyRate threshold, localized request window, Real seal, transport, replay, provenance, and local naming row;
\item classifier stability, requiring accepted packets to be compared componentwise only through $W,R,D,T,L,E,H,C,P,N$;
\item threshold exactness, requiring $T$ to bind the request tolerance in $D$ to a displayed late index before any localized window is exposed;
\item window extraction, requiring $L$ to expose only the finite subwindow of $W$ certified by $T$ and read through the same source row $R$;
\item RegSeqRat handoff, requiring all rational readback for the localized window to pass through $R$ rather than through a host stream;
\item Real seal non-escape, requiring every Real-facing read to pass through $W,R,D,T,L$ before it reaches $E$;
\item transport, requiring componentwise $\hsame$ in $H$ to preserve the displayed row order;
\item replay, requiring displayed $\Cont$ in $C$ to repeat the same precision-to-window-to-seal route;
\item provenance, requiring $P$ to name only the sibling surfaces displayed in the carrier;
\item naming, requiring $N$ to certify exactly the local $\CauchyLocalizationUp$ route and no hidden quotient, selected limit, host equality, countable-choice, or ambient-completeness row.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-localization-carrier}. The packet displays the window, source, tolerance, threshold, localized request, seal, transport, replay, provenance, and naming rows as the full local inventory.

Classifier stability follows because the classifier is rowwise. Every accepted comparison is made through $W,R,D,T,L,E,H,C,P,N$, and no further classifier coordinate is present.

Threshold exactness and window extraction are the analytic core of the packet. The dyadic tolerance row $D$ states the requested radius, the CauchyRate row $T$ supplies the late threshold for that radius, and the localized row $L$ exposes only the finite part of $W$ certified by that threshold.

The RegSeqRat handoff and Real seal boundary are ordered by the carrier. The rational readback is read through $R$ at the displayed window, and the seal row $E$ is downstream of $W,R,D,T,L$.

Transport, replay, provenance, and naming are structural. The rows $H$ and $C$ preserve and replay the same displayed route, while $P$ and $N$ package only that route. Since the carrier contains no hidden quotient, selected limit, host equality, countable-choice, or ambient-completeness row, none can be exported by the local certificate.
\end{proof}

\begin{theorem}[Cauchy localization window extraction]
\label{thm:cauchy-localization-window-extraction}
Every accepted $\CauchyLocalizationUp$ packet exposes a finite Cauchy window sufficient for the requested tolerance. More precisely, if $K=(W,R,D,T,L,E,H,C,P,N)$ is accepted, then the request row in $D$ and the threshold row $T$ determine a finite localized window $L$ whose entries are read through the $\StreamNameUp$ window $W$ and the $\RegSeqRatUp$ source $R$ before any $\RealUp$ seal read reaches $E$. The packet cannot export quotient stream equality, selected limits, host real equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with an accepted packet and project its displayed rows. The tolerance ledger $D$ fixes the requested radius, while the threshold row $T$ supplies the finite late boundary attached to that radius.

Use the localized request row $L$. It is downstream of $D$ and $T$, so it may expose only the portion of the StreamName window $W$ needed for the certified late-bound request. The RegSeqRat source row $R$ supplies the rational observations for exactly that displayed window.

The Real seal row $E$ is reached only after $W,R,D,T,L$ have been consumed. The structural rows $H,C,P,N$ preserve, replay, and name this same route, so the packet has no export path for quotient stream equality, selected limits, host real equality, countable choice, or ambient completeness.
\end{proof}

\begin{closurestatus}{\CauchyLocalizationUp}
  \constructivestory{A $\CauchyLocalizationUp$ packet is generated from a StreamName finite window, RegSeqRat source row, DyadicRatCore tolerance ledger, CauchyRate threshold, localized request window, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-localization-carrier}, \autoref{thm:cauchy-localization-namecert-obligations}, and \autoref{thm:cauchy-localization-window-extraction} seed the finite Cauchy localization route between Cauchy-rate data and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, host real equality, countable choice, ambient completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, threshold exactness, window extraction, RegSeqRat handoff, Real seal non-escape, transport, replay, provenance, and naming targets for BEDC.Derived.CauchyLocalizationUp.}
\end{closurestatus}
