\chapter{A Concrete Naming Certificate for $\KleeneTreeUp$}
\label{ch:concrete-instances-kleene-tree-namecert}
\origin{human}

Following Kleene and Troelstra--van Dalen on computable trees and constructive fan boundaries, the $\KleeneTreeUp$ packet records a finite prefix-tree boundary object for L10 Real and Completion consumers. It sits between the finite fan evidence of \autoref{ch:concrete-instances-fantheorem-namecert}, the Cantor and Baire prefix surfaces of \autoref{ch:concrete-instances-cantorspace-namecert} and \autoref{ch:concrete-instances-bairespace-namecert}, the stream-window route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet exposes only finite prefix rows, decidable-node rows, finite witness windows, and a no-computable-path boundary ledger; it is not a bar-induction principle, not an open-cover compactness theorem, not a choice-selected path object, and not a completeness assertion for $\RealUp$.

\begin{definition}[KleeneTree carrier]
\label{def:kleene-tree-carrier}
A $\KleeneTreeUp$ carrier is a finite $\BHist$ packet
$$
K=(T,D,B,W,F,A,S,R,Q,E,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $T$ is the displayed prefix-tree row. Its entries are finite Boolean words closed under displayed prefix restriction, read through the $\CantorSpaceUp$ and $\BaireSpaceUp$ prefix surfaces.
\item $D$ is the decidable-node ledger. For every displayed word queried by the packet, $D$ records the finite yes-or-no membership row used to decide whether that word lies in $T$.
\item $B$ is the no-computable-path boundary row. It records only finite refutation windows for the computable path candidates named by the packet; it does not store a global proof over all host functions.
\item $W$ is the finite witness-window table. Each entry names the prefix length and finite obstruction row through which a candidate stream is refused.
\item $F$ is the $\FanTheoremUp$ handoff row, used only as a finite fan-depth or decidable-bar boundary witness when a consumer asks for a bounded prefix read.
\item $A$ is the $\CantorSpaceUp$ and $\BaireSpaceUp$ prefix-space handoff row, keeping Boolean-prefix and natural-prefix observations separate before any stream consumer is reached.
\item $S$ is the $\StreamNameUp$ window route through which finite observations of candidate paths are scheduled.
\item $R$ is the $\RegSeqRatUp$ handoff row used by Real and Completion consumers that translate a displayed prefix obstruction into a regular-rational readback request.
\item $Q$ is the $\DyadicRatCoreUp$ tolerance ledger attached to those readback requests.
\item $E$ is the downstream $\RealUp$ seal route, available only after the prefix tree, decidable ledger, witness windows, stream schedule, regular readback, and dyadic tolerance rows have been consumed.
\item $H$ records componentwise $\hsame$ transport for the prefix tree, decidable-node ledger, no-path boundary, witness windows, fan handoff, space handoff, stream schedule, readback, tolerance, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite path-candidate request through $S$, into the prefix rows $T,D,W$, across the boundary row $B$, and onward to $R,Q,E$ only when a Real or Completion consumer asks for that route.
\item $P$ is the $\Pkg$ provenance over $\KleeneTreeUp$, $\FanTheoremUp$, $\CantorSpaceUp$, $\BaireSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\KleeneTreeUp}$ row.
\end{enumerate}
The carrier has no coordinate for Brouwer bar induction, a choice-selected infinite path, open-cover compactness, quotient stream equality, a global enumeration of all computable streams, or $\RealUp$ completeness.
\end{definition}

\begin{theorem}[KleeneTree NameCert obligations]
\label{thm:kleene-tree-namecert-obligations}
For every accepted $\KleeneTreeUp$ carrier $K=(T,D,B,W,F,A,S,R,Q,E,H,C,P,N)$, the local $\NameCert_{\KleeneTreeUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed prefix tree, decidable-node ledger, no-computable-path boundary row, witness-window table, fan handoff, Cantor and Baire prefix-space handoff, stream schedule, regular readback, dyadic tolerance ledger, Real seal, transport, continuation, provenance, and local naming rows;
\item prefix closure and decidability, requiring every inspected node and every displayed prefix of that node to be classified through $T$ and $D$;
\item finite witness-window exactness, requiring each computable-path candidate named by the packet to meet a displayed obstruction row in $W$ before the no-path boundary row $B$ may be read;
\item fan-boundary routing, requiring every bounded fan or bar-shaped read to pass through the finite $\FanTheoremUp$ row $F$ and the prefix-space handoff $A$ rather than through an ambient compactness theorem;
\item Real and Completion handoff, requiring every downstream consumer to pass through $S,R,Q,E$ after the prefix and boundary rows have already been displayed;
\item non-escape, excluding Brouwer bar induction, choice-selected paths, open-cover compactness, quotient stream equality, global computable-stream enumeration, and $\RealUp$ completeness.
\end{enumerate}
No NameCert obligation is stored outside these displayed rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:kleene-tree-carrier}. The tuple exposes exactly the prefix tree, decidable-node ledger, no-path boundary, witness windows, fan and space handoffs, stream route, regular readback, dyadic tolerance, Real seal, and structural rows.

Prefix closure and decidability are local to $T$ and $D$. A consumer can inspect only words already named in the finite packet, and every displayed prefix of such a word is read through the same ledger. Thus the tree surface is a finite prefix object rather than a host tree quantified over all streams.

The no-computable-path row is reached only through $W$ and $B$. Each candidate stream named by the packet supplies a finite prefix window, and $W$ records the obstruction window before $B$ reports the boundary read. This proves only the displayed refusal route; it does not import a choice-selected path or a global enumeration principle.

Fan-boundary reads then pass through $F$ and $A$. The $\FanTheoremUp$ row contributes only finite depth or decidable-bar data, while the Cantor and Baire handoff keeps the prefix-space observations explicit. No Brouwer bar induction or open-cover compactness row is present in the carrier.

Finally the Real and Completion route is downstream of $S,R,Q,E$. A consumer may translate a prefix obstruction into stream windows, regular rational readback, dyadic tolerances, and a terminal real seal, but it cannot bypass the displayed rows to obtain quotient stream equality or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[KleeneTree fan boundary]
\label{thm:kleene-tree-fan-boundary}
Let $K=(T,D,B,W,F,A,S,R,Q,E,H,C,P,N)$ be an accepted $\KleeneTreeUp$ carrier. Every Real or Completion consumer read from $K$ factors through the displayed finite route
$$
T,D,W,B,F,A,S,R,Q,E,H,C,P,N .
$$
In particular, the consumer sees only finite prefix rows, decidable-node rows, finite witness windows, the FanTheorem and Cantor or Baire handoff rows, stream windows, regular-rational readback, dyadic tolerances, and the terminal Real seal. It cannot read Brouwer bar induction, a choice-selected path, open-cover compactness, quotient stream equality, or $\RealUp$ completeness from the packet.
\end{theorem}
\begin{proof}
Start with a Real or Completion consumer. The consumer receives the carrier only as the accepted finite packet of \autoref{def:kleene-tree-carrier}, so the first available data are the prefix tree row $T$, the decidable-node ledger $D$, the witness windows $W$, and the boundary row $B$.

The fan boundary is then routed through $F$ and $A$. Those rows expose finite fan-depth and prefix-space data; they do not contain a bar-induction rule, an open-cover compactness proof, or an infinite-path selector.

Only after those rows have been consumed can the request reach $S,R,Q,E$. The stream, regular-rational, dyadic, and Real-seal rows are downstream translations of the same finite obstruction route, not independent completeness witnesses.

Transport, continuation replay, provenance, and local naming are exhausted by $H,C,P,N$. Since the carrier fields contain no Brouwer bar-induction coordinate, no choice-selected path coordinate, no open-cover compactness coordinate, no quotient stream equality coordinate, and no $\RealUp$ completeness coordinate, none of those principles can be exported by the fan-boundary read.
\end{proof}

\begin{closurestatus}{\KleeneTreeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:kleene-tree-carrier}, \autoref{thm:kleene-tree-namecert-obligations}, and \autoref{thm:kleene-tree-fan-boundary} seed the finite Kleene-tree boundary over prefix-tree, decidable-node, no-computable-path, witness-window, fan, Cantor, Baire, StreamName, RegSeqRat, DyadicRatCore, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Brouwer bar induction, choice-selected paths, open-cover compactness, quotient stream equality, global computable-stream enumeration, RealUp completeness, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, prefix closure and decidability, finite witness-window exactness, fan-boundary routing, Real and Completion handoff, and non-escape for the same finite packet.}
  \constructivestory{A $\KleeneTreeUp$ packet is generated from a finite prefix tree, decidable-node ledger, no-computable-path boundary row, finite witness windows, FanTheorem handoff, CantorSpace and BaireSpace prefix handoffs, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance ledger, RealUp seal route, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
