\chapter{A Concrete Naming Certificate for $\RegularCauchyTailFilterUp$}
\label{ch:concrete-instances-regular-cauchy-tail-filter-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis and the Bourbaki--Kelley filter terminology, the $\RegularCauchyTailFilterUp$ packet records the finite route by which the cofinite Frechet tail filter of a regular Cauchy source is read through Cauchy-filter basis rows, saturated Cauchy-filter evidence, stream windows, dyadic tolerances, regular rational readback, and the terminal $\RealUp$ seal. It refines the cofinite-tail filter surface of \autoref{ch:concrete-instances-frechetfilter-namecert}, the basis generator of \autoref{ch:concrete-instances-cauchy-filter-basis-namecert}, the saturation row of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the filter-to-regular route of \autoref{ch:concrete-instances-regularcauchyfilter-namecert}, the finite-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational interface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the Real naming boundary of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite tail-filter specialization; it is not a quotient filter, not a selected limit, not host real equality, not countable choice, and not an ambient completeness principle.

\begin{definition}[Regular Cauchy tail filter carrier]
\label{def:regular-cauchy-tail-filter-carrier}
A $\RegularCauchyTailFilterUp$ carrier is a finite $\BHist$ packet
$$
T=(F,B,Q,S,D,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\FrechetFilterUp$ cofinite-tail neighbourhood row, carrying the displayed tail threshold and finite-complement checks through which the regular Cauchy source is inspected.
\item $B$ is the $\CauchyFilterBasisUp$ generator row built from the same tail neighbourhoods, finite stream windows, regular readbacks, and dyadic tolerance requests.
\item $Q$ is the $\CauchyFilterUp$ saturation row that consumes $B$ before any filter-facing or Real-facing consumer can inspect the packet.
\item $S$ is the $\StreamNameUp$ finite-window row whose late observations are admitted only after the Frechet tail row and basis row have been replayed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row attached to those late windows and to the Cauchy-filter basis inclusions.
\item $R$ is the $\RegSeqRatUp$ readback row produced from $S,D$ after the saturated Cauchy-filter route $F,B,Q$ has been displayed.
\item $A$ is the terminal $\RealUp$ seal row reached only after $F,B,Q,S,D,R$ have been replayed.
\item $H$ records componentwise $\hsame$ transport for the Frechet tail row, basis row, saturation row, stream windows, dyadic tolerances, readback, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tail-filter request through the Frechet tail neighbourhoods, CauchyFilterBasis generator, CauchyFilter saturation, StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, and then the Real seal.
\item $P$ is the $\Pkg$ provenance over $\FrechetFilterUp$, $\CauchyFilterBasisUp$, $\CauchyFilterUp$, $\RegularCauchyFilterUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyTailFilterUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient filters, selected limits, host real equality, countable-choice tail selectors, quotient Cauchy names, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Regular Cauchy tail filter NameCert obligations]
\label{thm:regular-cauchy-tail-filter-namecert-obligations}
For every accepted $\RegularCauchyTailFilterUp$ carrier $T=(F,B,Q,S,D,R,A,H,C,P,N)$, the local $\NameCert_{\RegularCauchyTailFilterUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the Frechet tail row, CauchyFilterBasis generator, CauchyFilter saturation row, StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, Real seal, transport, continuation, provenance, and local naming row;
\item tail-neighbourhood exposure, requiring every accepted read to consume $F$ before a stream window or basis element is inspected;
\item basis generation and saturation exactness, requiring $B$ to be generated from the displayed tail windows and $Q$ to consume that basis before any downstream filter route is exported;
\item regular readback order, requiring $S$ and $D$ to be replayed before the $\RegSeqRatUp$ row $R$ is available;
\item Real seal boundary, requiring $A$ to remain downstream of $F,B,Q,S,D,R$ and refusing quotient filters, selected limits, host real equality, countable choice, quotient Cauchy names, and ambient completeness.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-tail-filter-carrier}. The visible rows are exactly $F,B,Q,S,D,R,A,H,C,P,N$.

The tail-neighbourhood obligation is forced by the replay row $C$. A request first consumes the cofinite-tail row $F$, then uses the same late-tail data to form the displayed basis row $B$.

Saturation exactness is the role of $Q$. Since $Q$ is downstream of $B$, every filter-facing consumer receives the generated Cauchy-filter surface rather than a detached quotient filter.

The regular readback and Real boundary are then fixed by row order. The stream windows $S$ and dyadic tolerances $D$ feed the readback row $R$, and the seal row $A$ is available only after $R$ and the structural rows have been replayed. The excluded quotient, selector, host-equality, choice, and completeness objects are absent from the carrier, so the displayed rows exhaust the local obligation surface.
\end{proof}

\begin{theorem}[Regular Cauchy tail filter Real seal boundary]
\label{thm:regular-cauchy-tail-filter-real-seal-boundary}
Let $T=(F,B,Q,S,D,R,A,H,C,P,N)$ be an accepted $\RegularCauchyTailFilterUp$ carrier. Every $\RealUp$-facing or completion-facing consumer of $T$ factors through the finite route
$$
F \longmapsto B \longmapsto Q \longmapsto S,D \longmapsto R \longmapsto A \longmapsto H,C,P,N .
$$
Thus the consumer reads the Frechet tail neighbourhoods, generated Cauchy-filter basis, saturated Cauchy filter, finite stream windows, dyadic tolerances, and regular rational readback before reaching the Real seal. The exported surface contains no quotient filter, selected limit, host real equality, countable-choice selector, quotient Cauchy name, or ambient completeness assertion.
\end{theorem}
\begin{proof}
Start with a Real-facing or completion-facing consumer. Carrier admission exposes the seal row $A$, but only as a row downstream of the tail, basis, saturation, window, tolerance, and readback rows.

Replay the continuation row $C$. The route first reads $F$, generates $B$, saturates through $Q$, and then inspects the finite windows $S$ with their dyadic ledger $D$.

The next public row is the regular rational readback $R$. Only after $R$ has been replayed can the consumer read $A$.

Transport through $H$ and provenance through $P,N$ preserve the same route. Since the carrier contains no quotient-filter coordinate, selected limit, host real equality, countable-choice selector, quotient Cauchy name, or completeness witness, no Real-facing read can export one.
\end{proof}

\begin{theorem}[Regular Cauchy tail filter Real seal handoff]
\label{thm:regular-cauchy-tail-filter-real-seal-handoff}
Let $T=(F,B,Q,S,D,R,A,H,C,P,N)$ be an accepted $\RegularCauchyTailFilterUp$ carrier. Any $\DyadicTailBallUp$ or $\RealCauchyCriterionUp$ consumer using $T$ must read the finite route
$$
\FrechetFilterUp \longmapsto \CauchyFilterBasisUp \longmapsto \CauchyFilterUp \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
in that order before exporting a Real-seal-facing conclusion.

The handoff is consumed by the downstream dyadic tail-ball route of \autoref{ch:concrete-instances-dyadic-tail-ball-namecert} and by the Real Cauchy criterion route of \autoref{ch:concrete-instances-real-cauchy-criterion-namecert}. It cannot bypass through quotient stream equality, selected limits, countable choice, host real equality, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-tail-filter-carrier}. The rows $F,B,Q,S,D,R,A$ expose the Frechet tail filter, CauchyFilterBasis generator, CauchyFilter saturation, StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, and terminal Real seal.

Apply \autoref{thm:regular-cauchy-tail-filter-real-seal-boundary}. It forces every Real-facing or completion-facing consumer to read $F$, then $B$, then $Q$, then $S,D$, then $R$, and only then $A$.

The $\DyadicTailBallUp$ consumer reads this same tail route before its dyadic ball containment row, while the $\RealCauchyCriterionUp$ consumer reads the same stream, readback, dyadic tolerance, and Real-seal surface before exposing its criterion row.

Since quotient stream equality, selected limits, countable choice, host real equality, trichotomy, and ambient completeness are absent from the carrier, neither downstream consumer can replace the displayed tail-filter route by one of those objects.
\end{proof}

\begin{theorem}[Regular Cauchy tail filter Bishop completion handoff]
\label{thm:regular-cauchy-tail-filter-bishop-completion-handoff}
Let $T=(F,B,Q,S,D,R,A,H,C,P,N)$ be an accepted $\RegularCauchyTailFilterUp$ carrier. Any $\BishopRegularCauchyCompletionUp$ consumer that reads the tail-filter route must factor its request through
$$
F \longmapsto B \longmapsto Q \longmapsto S,D \longmapsto R \longmapsto A
$$
before invoking the Bishop completion carrier rows of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}. The handoff consumes the displayed $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and terminal $\RealUp$ surface already exposed by $T$, then presents only the L10 completion rows governed by \autoref{thm:bishop-regular-cauchy-completion-regularity-envelope} and \autoref{thm:bishop-regular-cauchy-completion-nonescape-exactness}. It exports no quotient stream, selected limit, host real equality, countable-choice selector, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-tail-filter-carrier}. A completion-facing read has access only to the rows $F,B,Q,S,D,R,A,H,C,P,N$, with $F$ supplying tail exposure, $B$ supplying the generated Cauchy-filter basis, and $Q$ supplying saturation.

Apply \autoref{thm:regular-cauchy-tail-filter-namecert-obligations}. Tail exposure forces the consumer to read $F$ before any stream window is inspected, while basis generation and saturation exactness force the route through $B$ and $Q$ before any filter-facing surface is available.

Apply \autoref{thm:regular-cauchy-tail-filter-real-seal-boundary}. The only ordered Real-facing route then continues through the finite $\StreamNameUp$ windows $S$, the $\DyadicRatCoreUp$ tolerance row $D$, the $\RegSeqRatUp$ readback row $R$, and the terminal $\RealUp$ seal $A$.

The Bishop completion chapter can therefore receive the tail-filter data only as the displayed L10 rows. Its regularity envelope in \autoref{thm:bishop-regular-cauchy-completion-regularity-envelope} reads the finite stream, regular sequence, dyadic tolerance, common-tail, and Real-seal rows, while \autoref{thm:bishop-regular-cauchy-completion-nonescape-exactness} prevents escape to quotient streams, selected limits, host real equality, countable choice, or ambient completeness.
\end{proof}

\begin{closurestatus}{\RegularCauchyTailFilterUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-tail-filter-carrier}, \autoref{thm:regular-cauchy-tail-filter-namecert-obligations}, and \autoref{thm:regular-cauchy-tail-filter-real-seal-boundary} seed the finite route from Frechet tail neighbourhoods through CauchyFilterBasis generation, CauchyFilter saturation, StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, and the downstream Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, selected limits, host real equality, countable-choice tail selectors, quotient Cauchy names, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tail-neighbourhood exposure, basis generation, CauchyFilter saturation exactness, RegSeqRat readback order, Real seal boundary, and ledger refusal proofs for the same packet.}
  \constructivestory{A $\RegularCauchyTailFilterUp$ packet is generated from a FrechetFilter tail row, a CauchyFilterBasis generator, a CauchyFilter saturation row, StreamName windows, a DyadicRatCore tolerance ledger, a RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
