\chapter{A Concrete Naming Certificate for $\DirectedSetUp$}
\label{ch:concrete-instances-directedset-namecert}
\origin{human}

Following Moore--Smith and Kelley directed sets, and the Bishop--Bridges use of finite constructive evidence in analysis, the $\DirectedSetUp$ packet names the directed-index substrate consumed by net-based BEDC chapters. It sits upstream of the directed-window surface of \autoref{ch:concrete-instances-cauchynet-namecert}, the limit boundary of \autoref{ch:concrete-instances-cauchynetlimit-namecert}, and the convergence packet of \autoref{ch:concrete-instances-mooresmithconvergence-namecert}. The packet records finite preorder and upper-window data; it is not a quotient of indices, not a global cofinal-choice operator, and not a host-level order-completeness principle.

\begin{definition}[DirectedSet carrier]
\label{def:directed-set-carrier}
A $\DirectedSetUp$ carrier is a finite $\BHist$ packet
$$
D=(I,\preceq,W,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite index row naming the inspected directed addresses.
\item $\preceq$ is the comparison row, recording the displayed preorder comparisons among the inspected addresses.
\item $W$ is the finite window row, naming each finite subfamily of inspected addresses requested by a downstream net consumer.
\item $U$ is the upper-window witness row, assigning to every displayed window in $W$ a named address in $I$ that is above every address in that window according to $\preceq$.
\item $H$ records componentwise $\hsame$ transport for the index, comparison, window, upper-witness, continuation, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay from a downstream finite-window request through $W$, $\preceq$, and $U$.
\item $P$ is the $\Pkg$ provenance over $\DirectedSetUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, together with the downstream consumers $\CauchyNetUp$, $\CauchyNetLimitUp$, and $\MooreSmithConvergenceUp$.
\item $N$ is the local $\NameCert_{\DirectedSetUp}$ row.
\end{enumerate}
The carrier exports only this finite directed-index packet. It contains no total order extension, no selected cofinal sequence, no quotient on indices, and no infinite choice principle.
\end{definition}
\leanchecked{BEDC.Derived.DirectedSetUp.DirectedSetCarrier\_fields\_faithful}

\begin{theorem}[DirectedSet NameCert obligations]
\label{thm:directed-set-namecert-obligations}
For every accepted $\DirectedSetUp$ carrier $D=(I,\preceq,W,U,H,C,P,N)$, the local $\NameCert_{\DirectedSetUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed index, comparison, window, upper-witness, transport, continuation, provenance, and naming rows;
\item preorder readability, stating that every comparison exported to a consumer is one of the displayed $\preceq$ rows on addresses in $I$;
\item finite-window coverage, stating that every requested finite index family is first named in $W$;
\item upper-window witnessing, stating that every displayed window has a named witness in $U$ above each of its addresses by the displayed comparison row;
\item transport and continuation stability, stating that $H$ and $C$ preserve the same finite window and witness data under $\hsame$ replay;
\item ledger non-escape, excluding cofinal choice functions, quotient index objects, total-order completions, and infinite upper-bound selection.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:directed-set-carrier}. The finite index row, comparison row, displayed windows, upper-window witnesses, transports, continuations, provenance, and local naming row are visible coordinates of one $\BHist$ packet.

Preorder readability and finite-window coverage are forced by the row order. A consumer can read an address only through $I$, a comparison only through $\preceq$, and a finite request only after that request has been named in $W$.

The upper-window obligation is the defining role of $U$. For each displayed window, $U$ supplies a named address and the comparison row supplies the finite list of relations showing that the address lies above every member of the window.

Transport and continuation stability use the structural rows $H$ and $C$. They replay the same displayed windows, comparisons, and upper-witness entries, so they do not add a cofinal selector or an unrecorded index relation.

Finally, the package and naming rows name exactly the displayed finite packet. Since no coordinate stores a quotient of indices, a total-order completion, a selected cofinal sequence, or an infinite choice function, any request for such data remains outside the local ledger.
\end{proof}
\leanchecked{BEDC.Derived.DirectedSetUp.DirectedSetTasteGate\_single\_carrier\_alignment}

\begin{theorem}[DirectedSet CauchyNet index handoff]
\label{thm:directed-set-cauchynet-index-handoff}
Let $D=(I,\preceq,W,U,H,C,P,N)$ be an accepted $\DirectedSetUp$ carrier. Any $\CauchyNetUp$ or $\CauchyNetLimitUp$ packet that reads its directed-window ledger from $D$ receives index data only through the finite route
$$
I,\preceq,W,U \longmapsto H,C,P,N .
$$
Thus the Cauchy-net carrier of \autoref{def:cauchy-net-carrier} and the limit carrier of \autoref{def:cauchy-net-limit-carrier} may share the same displayed directed-index substrate without adding quotient nets, selected limits, cofinal choice, or ambient completeness.
\end{theorem}
\begin{proof}
Start with a downstream Cauchy-net request. The directed addresses available to the consumer are the entries of $I$, and the comparisons available to the consumer are the displayed rows of $\preceq$.

The finite request is then named in $W$. The witness row $U$ supplies the common upper-window address needed by the $\CauchyNetUp$ directed-window ledger, and the same witness row can be replayed before the $\CauchyNetLimitUp$ seal handoff is read.

The structural rows $H$ and $C$ transport and replay this route componentwise. The provenance and local naming rows record that the exported data is the finite directed-index packet, not a quotient net, selected host limit, cofinal-choice selector, or completeness assertion.
\end{proof}
\leanchecked{BEDC.Derived.DirectedSetUp.DirectedSet\_cauchynet\_index\_handoff\_certificate}

\begin{theorem}[DirectedSet finite upper-window stability]
\label{thm:directed-set-finite-upper-window-stability}
Let $D=(I,\preceq,W,U,H,C,P,N)$ be an accepted $\DirectedSetUp$ carrier, and let $\Omega$ be a retained finite subledger of $I$ whose displayed windows in $W_{\Omega}$ keep their named upper witnesses in $\Omega$. Then
$$
D_{\Omega}=(I_{\Omega},\preceq_{\Omega},W_{\Omega},U_{\Omega},H_{\Omega},C_{\Omega},P_{\Omega},N_{\Omega})
$$
is an accepted $\DirectedSetUp$ carrier for the retained windows. Every $\MooreSmithConvergenceUp$ or $\CauchyNetUp$ consumer of $D_{\Omega}$ therefore reads the same finite upper-window witnesses, restricted to $\Omega$.
\end{theorem}
\begin{proof}
Restrict the index row to $I_{\Omega}$ and the comparison row to $\preceq_{\Omega}$. The hypothesis on retained windows says that every window kept in $W_{\Omega}$ still has its upper witness inside the retained index row.

The witness row $U_{\Omega}$ is the corresponding restriction of $U$. For each retained window, the required comparison entries are exactly the entries of $\preceq_{\Omega}$ that already certified the witness in the original carrier.

The transport, continuation, provenance, and naming rows restrict componentwise to $H_{\Omega}$, $C_{\Omega}$, $P_{\Omega}$, and $N_{\Omega}$. Their endpoints are among the retained rows, so replay cannot leave the finite subledger.

Apply the obligation surface of \autoref{thm:directed-set-namecert-obligations}. Carrier admission is the displayed restricted tuple; preorder readability, finite-window coverage, upper-window witnessing, and structural stability are inherited by restriction. Ledger non-escape remains valid because no retained coordinate stores quotient indices, cofinal choice, total-order completion, or infinite upper-bound selection.
\end{proof}
\leanchecked{BEDC.Derived.DirectedSetUp.DirectedSetPacket\_finite\_upper\_window\_stability}

\begin{theorem}[DirectedSet carrier obligation]
\label{thm:directedset-carrier-obligation}
For every accepted $\DirectedSetUp$ carrier $D=(I,\preceq,W,U,H,C,P,N)$, the carrier obligation is the visible finite row family consisting of the index row $I$, the displayed preorder comparison row $\preceq$, the finite-window row $W$, and the upper-window witness row $U$, together with structural rows $H,C,P,N$. No carrier obligation may be discharged by quotient indices, a total-order completion, cofinal choice, or infinite upper-bound selection.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:directed-set-carrier}. The rows $I,\preceq,W,U,H,C,P,N$ are exactly the displayed coordinates of the accepted packet.

Apply the NameCert obligation theorem \autoref{thm:directed-set-namecert-obligations}. Its carrier admission, preorder readability, finite-window coverage, and upper-window witnessing clauses identify the same visible rows.

The non-escape clause excludes the forbidden objects. Since none of them appears as a carrier coordinate, no downstream consumer can use one to discharge the carrier obligation.
\end{proof}

\begin{theorem}[DirectedSet preorder stability obligation]
\label{thm:directedset-preorder-stability-obligation}
Let $D=(I,\preceq,W,U,H,C,P,N)$ be an accepted $\DirectedSetUp$ carrier. Every displayed preorder comparison exported from $D$ remains stable under the componentwise $\hsame$ transport row $H$ and the displayed $\Cont$ replay row $C$. The stable comparison is still a row of $\preceq$ on addresses from $I$, not a host preorder, quotient relation, total-order completion, or hidden comparison outside the packet.
\end{theorem}
\begin{proof}
Read the comparison row through \autoref{def:directed-set-carrier}. The only preorder comparisons available to a consumer are the displayed entries of $\preceq$ between addresses named by $I$.

Use the transport and continuation stability clause of \autoref{thm:directed-set-namecert-obligations}. It requires $H$ and $C$ to preserve the same finite windows, comparisons, and upper-witness data under replay.

The CauchyNet handoff theorem \autoref{thm:directed-set-cauchynet-index-handoff} then sends net consumers through the same row family. Thus a transported or replayed comparison cannot be replaced by a quotient relation, a host preorder, or a total-order completion.
\end{proof}
\leanchecked{BEDC.Derived.DirectedSetUp.DirectedSetCarrier\_preorder\_stability\_obligation}

\begin{theorem}[DirectedSet cofinal merge obligation]
\label{thm:directedset-cofinal-merge-obligation}
Let $D=(I,\preceq,W,U,H,C,P,N)$ be an accepted $\DirectedSetUp$ carrier, and let two retained finite windows in $W$ have displayed upper witnesses named by $U$. The cofinal merge obligation for their union is discharged only by naming that union as a finite window in $W$ and reading its displayed upper witness through $U$. The resulting merge remains a finite-window witness and is not a cofinal sequence, infinite upper-bound selector, quotient index, or choice function.
\end{theorem}
\begin{proof}
Begin with the two retained windows. By \autoref{thm:directed-set-namecert-obligations}, each window is first named in $W$ and each upper witness is read through $U$ using displayed comparisons from $\preceq$.

For the merged request, use the same finite-window coverage clause on the union window. Once that union is displayed in $W$, the upper-window witnessing clause supplies its named upper witness in $U$.

Apply finite upper-window stability, \autoref{thm:directed-set-finite-upper-window-stability}, to retained subledgers. It keeps the merged witness inside the same finite route and prevents the merge from becoming a cofinal sequence, quotient index, infinite selector, or choice function.
\end{proof}
\leanchecked{BEDC.Derived.DirectedSetUp.DirectedSetCarrier\_cofinal\_merge\_obligation}

\begin{theorem}[DirectedSet upper-window exhaustion]
\label{thm:directed-set-upper-window-exhaustion}
Let $D=(I,\preceq,W,U,H,C,P,N)$ be an accepted $\DirectedSetUp$ carrier. Any $\CauchyNetUp$, $\CauchyNetLimitUp$, or $\MooreSmithConvergenceUp$ consumer that reads a finite directed-window request from $D$ factors through the displayed rows
$$
I,\preceq,W,U,H,C,P,N .
$$
The consumer therefore cannot obtain a cofinal sequence, quotient index, total-order completion, infinite upper-bound selector, or choice function from the directed-window read.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:directed-set-carrier}. The only index addresses are the entries of $I$, the only comparisons are the displayed rows of $\preceq$, and the only finite requests are the windows named in $W$.

Apply \autoref{thm:directed-set-namecert-obligations}. Its finite-window coverage and upper-window witnessing clauses force every accepted request to read its witness through $U$, while its transport and continuation clauses route every replay through $H$ and $C$.

Now use \autoref{thm:directed-set-cauchynet-index-handoff} for $\CauchyNetUp$ and $\CauchyNetLimitUp$ consumers, and \autoref{thm:directed-set-finite-upper-window-stability} for retained Moore--Smith windows. These results identify the same finite upper-window route after restriction or handoff.

Finally, $P$ and $N$ source and name only that route. Since the carrier and the cited obligations contain no row for a cofinal sequence, quotient index, total-order completion, infinite upper-bound selector, or choice function, no downstream consumer can extract one from the finite directed-window request.
\end{proof}

\begin{theorem}[DirectedSet obligation closure package]
\label{thm:directed-set-obligation-closure-package}
The accepted $\DirectedSetUp$ carrier
$$
D=(I,\preceq,W,U,H,C,P,N)
$$
supports an obligationClosure package whose finite boundary consists of carrier admission for the displayed rows, preorder readability through $\preceq$, finite-window coverage through $W$, upper-window witnessing through $U$, transport and $\Cont$ replay through $H,C$, retained-subledger stability, and non-escape from cofinal selectors, quotient indices, total-order completions, infinite upper-bound selection, and choice functions. Every $\CauchyNetUp$, $\CauchyNetLimitUp$, and $\MooreSmithConvergenceUp$ consumer of the package reads only this finite directed-window substrate.
\end{theorem}
\begin{proof}
Begin with the carrier definition, \autoref{def:directed-set-carrier}. It supplies the finite index row, comparison row, finite-window row, upper-witness row, transport row, continuation row, provenance row, and local naming row.

Apply the NameCert obligations of \autoref{thm:directed-set-namecert-obligations}. Carrier admission, preorder readability, finite-window coverage, upper-window witnessing, transport replay, continuation replay, and ledger non-escape are exactly the displayed obligations.

Use the CauchyNet index handoff, \autoref{thm:directed-set-cauchynet-index-handoff}, to identify how $\CauchyNetUp$ and $\CauchyNetLimitUp$ consumers read the same route through $I,\preceq,W,U,H,C,P,N$.

Use finite upper-window stability and upper-window exhaustion, \autoref{thm:directed-set-finite-upper-window-stability} and \autoref{thm:directed-set-upper-window-exhaustion}. These keep retained subledgers inside the same finite route and show that Moore--Smith and Cauchy-net consumers cannot extract cofinal selectors, quotient indices, total-order completions, infinite upper-bound selection, or choice functions.
\end{proof}

\closureat{DirectedSetUp}{scopedStr}

\begin{closurestatus}{\DirectedSetUp}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:directed-set-carrier}, the NameCert obligations, CauchyNet handoff, finite-window stability, \autoref{thm:directed-set-upper-window-exhaustion}, and \autoref{thm:directed-set-obligation-closure-package} bind the scoped BEDC primitive boundary for the finite directed-index substrate consumed by Cauchy-net, Cauchy-net-limit, and Moore--Smith convergence packets.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.DirectedSetUp.DirectedSetCarrier\_fields\_faithful}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient index objects, selected cofinal sequences, total-order completions, infinite choice principles, Lean verification, or bridge checking.}
  \upgradepath{Public closure requires bridge-ready standard-schema rows and public consumer determinacy for the same directed-index packet.}
  \constructivestory{A $\DirectedSetUp$ packet is generated from a finite index row, displayed preorder comparisons, finite requested windows, common upper-window witnesses, componentwise $\hsame$ transports, displayed $\Cont$ replay, package provenance, and a local $\NameCert$ row.}
\end{closurestatus}
