\chapter{A Concrete Naming Certificate for $\CauchyCompletionMinimalityUp$}
\label{ch:concrete-instances-cauchycompletionminimality-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, and the Bourbaki and Kelley treatments of metric completion, the $\CauchyCompletionMinimalityUp$ packet records the minimality boundary for Cauchy completion through existing BEDC finite rows. It reads the finite completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the dense isometric embedding surface of \autoref{ch:concrete-instances-completionembedding-namecert}, the extension and uniqueness interface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the uniformly continuous extension handoff of \autoref{ch:concrete-instances-uniform-continuous-extension-namecert}, and the Bishop-style constructive route of \autoref{ch:concrete-instances-constructive-metric-completion-namecert}. The packet names the least completion-facing service boundary visible to later consumers: source metric data, dense embedding, universal extension, separated uniqueness, transport, provenance, and local naming.

\begin{definition}[CauchyCompletionMinimality carrier]
\label{def:cauchy-completion-minimality-carrier}
A $\CauchyCompletionMinimalityUp$ carrier is a finite $\BHist$ packet
$$
M=(X,C,E,U,F,S,H,R,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the source metric row together with the located source evidence used by the completion route.
\item $C$ is the displayed $\MetricCompletionUp$ or $\ConstructiveMetricCompletionUp$ completion row over the same source histories.
\item $E$ is the dense $\CompletionEmbeddingUp$ row, including source-image coverage and distance reflection.
\item $U$ is the $\CompletionUniversalPropertyUp$ row that supplies the extension and uniqueness surface for completion-facing consumers.
\item $F$ is the $\UniformContinuousExtensionUp$ row that hands uniformly continuous dense-source maps to the completed packet.
\item $S$ is the separated uniqueness row comparing two displayed completion reads only through zero-distance classifier evidence.
\item $H$ records componentwise $\hsame$ transport for the source, completion, embedding, universal-property, extension, separatedness, replay, provenance, and local naming rows.
\item $R$ records the displayed $\Cont$ replay through $X,C,E,U,F,S,H,P,N$, in the order in which a consumer may read the packet.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionUp$, $\ConstructiveMetricCompletionUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\UniformContinuousExtensionUp$, $\SeparatedMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CauchyCompletionMinimalityUp}$ row naming this packet and no larger completion principle.
\end{enumerate}
The carrier has no coordinate for quotient completions, selected representatives, host equality, countable choice, open-cover compactness, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[CauchyCompletionMinimality NameCert obligations]
\label{thm:cauchy-completion-minimality-namecert-obligations}
For an accepted $\CauchyCompletionMinimalityUp$ carrier $M=(X,C,E,U,F,S,H,R,P,N)$, the local $\NameCert_{\CauchyCompletionMinimalityUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the source metric and located source row, displayed completion row, dense embedding row, universal-property row, uniformly continuous extension row, separated uniqueness row, componentwise transport, continuation replay, provenance, and local naming row;
\item dense-image coverage, requiring every completion-facing source approximation to pass through the embedding row $E$ after the completion row $C$ has been displayed;
\item universal factorization, requiring every completion-facing consumer to read the universal-property row $U$ and extension handoff $F$ before it can export a completed value;
\item separated uniqueness, requiring any comparison of two completed reads to pass through $S$ and the componentwise transport ledger $H$;
\item ledger non-escape, stating that $R,P,N$ expose no quotient completion, selected representative, host equality, countable-choice schedule, open-cover compactness principle, or ambient $\RealUp$ completeness theorem.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-minimality-carrier}. The tuple displays exactly the source, completion, embedding, universal-property, extension, separatedness, transport, replay, provenance, and naming rows.

Dense-image coverage is read from $E$ after $C$. The completion row gives the target-facing packet, and the embedding row supplies the source-image route through which every admitted approximation reaches that packet.

Universal factorization is the role of $U$ and $F$. The universal-property row supplies extension and uniqueness data, while the uniformly continuous extension row records the finite handoff used by dense-source consumers.

Separated uniqueness is local to $S$ and transported by $H$. The replay row $R$ orders the same route, and the provenance rows $P,N$ list no additional coordinate. Hence the excluded quotient, representative-selection, host-equality, choice, compactness, and ambient real-completeness principles cannot be read from the certificate.
\end{proof}

\begin{theorem}[CauchyCompletionMinimality universal factorization]
\label{thm:cauchy-completion-minimality-universal-factorization}
Let $M=(X,C,E,U,F,S,H,R,P,N)$ be an accepted $\CauchyCompletionMinimalityUp$ carrier. Any completion-facing consumer sharing the same source metric $X$, dense embedding $E$, and separated target boundary $S$ factors through the route
$$
X\longmapsto E\longmapsto U\longmapsto F\longmapsto S\longmapsto(H,R,P,N).
$$
The factorization exports no quotient completion, selected representative, host equality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Start from the shared source metric row $X$. A completion-facing consumer cannot reach a completed read until the dense embedding row $E$ has displayed the source image used by that read.

The universal row $U$ is consumed next. It is the finite extension and uniqueness surface through which the consumer obtains a completion-facing map rather than a detached host-space operation.

The uniformly continuous handoff $F$ then records the carried extension route. Its source and target sides are still the same rows displayed by $X$, $E$, and $U$.

Finally the separated row $S$ compares any two resulting target reads, while $H,R,P,N$ transport, replay, source, and name the same finite packet. Because none of the listed rows contains a quotient completion, selected representative, host equality, countable-choice schedule, open-cover compactness principle, or ambient $\RealUp$ completeness theorem, the factorization is minimal in exactly the displayed BEDC coordinates.
\end{proof}

\begin{closurestatus}{\CauchyCompletionMinimalityUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-minimality-carrier}, \autoref{thm:cauchy-completion-minimality-namecert-obligations}, and \autoref{thm:cauchy-completion-minimality-universal-factorization} seed the finite minimal Cauchy-completion service boundary over source metrics, displayed completion rows, dense embeddings, universal extension, uniformly continuous handoff, and separated uniqueness.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, host equality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-image coverage, universal factorization, separated uniqueness, replay exactness, and ledger non-escape for BEDC.Derived.CauchyCompletionMinimalityUp.}
  \constructivestory{A $\CauchyCompletionMinimalityUp$ packet is generated from a source metric with located source evidence, a displayed completion row, a dense completion embedding, a universal-property row, a uniformly continuous extension handoff, separated uniqueness, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
