\chapter{A Concrete Naming Certificate for $\CauchyConvolutionUp$}
\label{ch:concrete-instances-cauchyconvolution-namecert}
\origin{human}

The $\CauchyConvolutionUp$ packet records the finite Cauchy-product surface that sits between fast-series convolution ledgers and the regular rational real-name route. Following Bishop--Bridges constructive analysis, it keeps displayed source series, finite convolution windows, dyadic tail budgets, $\RegSeqRatUp$ handoff rows, $\RealUp$ seal rows, transport data, continuation routes, package provenance, and local naming provenance as finite certificate data. It does not claim host real multiplication, quotient equality of streams, selected infinite sums, or ambient real completeness.

\begin{definition}[CauchyConvolution carrier]
\label{def:cauchy-convolution-carrier}
A $\CauchyConvolutionUp$ carrier is a finite $\BHist$ packet
$$
Q=(F,G,K,A,D,R,E,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $F$ and $G$ are two accepted $\FastConvergentSeriesUp$ source rows, including their displayed summand windows, fast tail schedules, regular rational readbacks, $\RealUp$ seal-facing rows, $\hsame$ transports, $\Cont$ routes, package provenance, and local certificate rows;
\item $K$ is the finite convolution ledger whose inspected coefficient at index $n$ is the displayed finite sum $\sum_{0 \leq i \leq n} a_i b_{n-i}$ over the source summand rows;
\item $A$ is the finite product-prefix ledger that reads only the displayed convolution coefficients in $K$;
\item $D$ is the $\DyadicTailBoundUp$ budget ledger, including the source tail budgets, the finite source-window bounds, and the pasted product-tail budget consumed by the convolution row;
\item $R$ is the $\RegSeqRatUp$ handoff row obtained from $A$ and $D$;
\item $E$ is the $\RealUp$ seal row attached to that regular rational handoff;
\item $H$ records the componentwise $\hsame$ transports for source rows, convolution ledgers, dyadic tail budgets, regular handoffs, and seal-facing rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read the source packets, finite convolution ledger, dyadic tail ledger, regular handoff, and real seal;
\item $P$ is the $\Pkg$ provenance over $\FastConvergentSeriesUp$, $\FastSeriesProductUp$, $\DyadicTailBoundUp$, $\RegSeqRatUp$, $\RealUp$, and the finite rational arithmetic rows used by the convolution;
\item $N$ is the local $\NameCert_{\CauchyConvolutionUp}$ provenance row.
\end{enumerate}
The carrier is finite Cauchy-product data. It exports no host product of real numbers, no quotient stream, no selected infinite sum, and no real-completeness principle.
\end{definition}

\begin{theorem}[CauchyConvolution NameCert obligations]
\label{thm:cauchy-convolution-namecert-obligations}
Every accepted $\CauchyConvolutionUp$ packet with carrier \autoref{def:cauchy-convolution-carrier} carries five local naming obligations:
\begin{enumerate}
\item carrier habitation by zero-product data, where both accepted source rows may be the displayed zero fast series, the convolution ledger is the zero finite ledger, the dyadic budget is the zero pasted budget, and the handoff and seal rows are the corresponding regular rational zero rows;
\item componentwise classifier laws over the two $\FastConvergentSeriesUp$ source rows, finite convolution ledger, dyadic tail ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row;
\item finite convolution ledger exactness, requiring each inspected coefficient row in $K$ to be the finite displayed sum $\sum_{0 \leq i \leq n} a_i b_{n-i}$;
\item dyadic tail-bound handoff, requiring the source fast-tail schedules and finite source-window bounds to feed the $\DyadicTailBoundUp$ ledger $D$ and then the $\RegSeqRatUp$ row $R$;
\item $\RealUp$ seal non-escape, requiring every real-facing read to pass through the regular rational handoff and the displayed finite provenance rows.
\end{enumerate}
These obligations are the complete local certificate surface for the finite Cauchy-product route.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyConvolutionUp.CauchyConvolutionPacket\_semantic\_name\_certificate}
\leanchecked{BEDC.Derived.CauchyConvolutionUp.CauchyConvolutionCarrier\_namecert\_obligations}
\begin{proof}
Carrier habitation is witnessed by the displayed zero source rows. Their finite convolution coefficients are zero, the product-prefix ledger is zero, and the dyadic tail budget is the zero budget. Repacking those rows gives the zero regular rational handoff and its real-seal-facing row.

The classifier obligations are componentwise projections of \autoref{def:cauchy-convolution-carrier}. A permitted comparison reads only the two source packets, $K$, $A$, $D$, $R$, $E$, and the transport, continuation, package, and local naming rows.

The exactness obligation is local to the finite convolution ledger: at each inspected index $n$, the row records the finite sum over $0 \leq i \leq n$. The dyadic handoff obligation then reads the source tail schedules and finite source-window bounds into $D$, so $R$ is reached through displayed tail-budget data rather than a host summation theorem.

Finally, the seal row $E$ is attached only after the regular rational handoff has been displayed. Since the carrier has no coordinate for quotient streams, selected infinite sums, host multiplication, or completeness, every real-facing read remains inside the finite certificate packet.
\end{proof}

\begin{theorem}[CauchyConvolution carrier admission]
\label{thm:cauchy-convolution-carrier-admission}
An accepted $\CauchyConvolutionUp$ carrier is admitted as the finite $\BHist$ packet
$$
Q=(F,G,K,A,D,R,E,H,C,P,N)
$$
of \autoref{def:cauchy-convolution-carrier}. Admission projects the two $\FastConvergentSeriesUp$ source rows $F,G$, the finite convolution ledger $K$, the product-prefix ledger $A$, the $\DyadicTailBoundUp$ budget ledger $D$, the $\RegSeqRatUp$ handoff row $R$, the $\RealUp$ seal row $E$, and the transport, continuation, package, and local naming rows $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The coordinates $F,G,K,A,D,R,E,H,C,P,N$ are all rows of one finite packet, so the local $\NameCert_{\CauchyConvolutionUp}$ carrier is inhabited by those projections.

The construction does not add a host product, a quotient stream, a selected infinite sum, or a completeness witness. Those objects are absent from the carrier, so admission remains a finite Cauchy-product packet over the displayed BEDC rows.
\end{proof}

\begin{theorem}[CauchyConvolution tail-budget compatibility]
\label{thm:cauchy-convolution-tail-budget-compatibility}
For every accepted $\CauchyConvolutionUp$ carrier $Q=(F,G,K,A,D,R,E,H,C,P,N)$, the source fast-tail schedules and finite source-window bounds in $F$ and $G$, together with the product-prefix rows in $A$ over the inspected coefficients of $K$, determine exactly the $\DyadicTailBoundUp$ ledger $D$ consumed by the $\RegSeqRatUp$ handoff row $R$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyConvolutionUp.CauchyConvolutionTailBudgetCompatibility}
\begin{proof}
Read the two source packets $F$ and $G$. Their fast-tail schedules and finite source-window bounds are part of the displayed source rows, so they can be transported only through the componentwise rows in $H$ and consumed only through the routes in $C$.

Next read the finite convolution ledger $K$ and the product-prefix ledger $A$. The prefix rows inspect only finitely many Cauchy-product coefficients, and $D$ records the pasted dyadic tail budget built from those finite inspections and the two source tail schedules.

The handoff row $R$ consumes that same ledger $D$. Hence compatibility is a row-projection statement about $F,G,K,A,D,R,H,C,P,N$, with no appeal to host real multiplication or equality of quotient streams.
\end{proof}

\begin{theorem}[CauchyConvolution Real seal factorization boundary]
\label{thm:cauchy-convolution-real-seal-factorization-boundary}
Every $\RealUp$ seal read from an accepted $\CauchyConvolutionUp$ carrier factors through the regular handoff row $R$ and the finite Cauchy-product provenance consisting of $F,G,K,A,D,H,C,P,N$. The seal boundary does not expose host real multiplication, quotient stream equality, a selected infinite convolution sum, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the seal row $E$. By the carrier shape, $E$ is attached to the regular handoff $R$ and has no independent route to an external real-valued multiplication operation.

Use \autoref{thm:cauchy-convolution-tail-budget-compatibility} to identify the evidence consumed by $R$. It is the finite product-prefix ledger $A$ over $K$ together with the dyadic budget $D$ assembled from the displayed source rows $F$ and $G$.

The remaining rows $H,C,P,N$ preserve transport, consumer access, package provenance, and local naming. Therefore the real-facing seal factors through the finite Cauchy-product packet and cannot export any object outside that packet.
\end{proof}

\begin{theorem}[CauchyConvolution finite tail ledger]
\label{thm:cauchy-convolution-finite-tail-ledger}
For every accepted $\CauchyConvolutionUp$ carrier
$$
Q=(F,G,K,A,D,R,E,H,C,P,N),
$$
the finite convolution ledger $K$, product-prefix ledger $A$, and $\DyadicTailBoundUp$ ledger $D$ determine the displayed product-tail comparison consumed by $R$. The comparison uses only source fast-tail schedules, finite source-window bounds, inspected convolution coefficients, componentwise $\hsame$ transports, and displayed $\Cont$ routes.
\end{theorem}
\begin{proof}
Project the two $\FastConvergentSeriesUp$ source rows from $F$ and $G$. Their fast tail schedules and finite source-window bounds are already displayed rows of the carrier.

The convolution ledger $K$ supplies only finite coefficients, and the product-prefix ledger $A$ reads those coefficients over finite inspected windows. The dyadic ledger $D$ pastes the source tail schedules with the finite source-window bounds to obtain the product-tail budget at the requested precision.

Transport along $H$ and read along $C$ preserve exactly these displayed rows. Thus the comparison consumed by $R$ is a finite tail ledger over $\DyadicTailBoundUp$, not an appeal to a host Cauchy product or an infinite convolution object.
\end{proof}

\begin{theorem}[CauchyConvolution Real seal handoff]
\label{thm:cauchy-convolution-real-seal-handoff}
Every $\RealUp$ seal exported by an accepted $\CauchyConvolutionUp$ packet factors through the $\RegSeqRatUp$ handoff row $R$, whose regularity evidence is supplied by the finite product-prefix ledger $A$ and the $\DyadicTailBoundUp$ ledger $D$ over the finite convolution row $K$. The seal route is therefore confined to $\FastConvergentSeriesUp$, $\FastSeriesProductUp$, $\DyadicTailBoundUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Start from the seal coordinate $E$ of the accepted carrier. By the carrier definition, $E$ is attached to the same regular rational handoff row $R$ and has no independent route to a host real object.

Apply \autoref{thm:cauchy-convolution-finite-tail-ledger}. It identifies the regularity evidence for $R$ with the finite product-prefix ledger $A$ and dyadic tail budget $D$, both built over the inspected convolution coefficients in $K$ and the displayed source rows $F$ and $G$.

The remaining coordinates $H$, $C$, $P$, and $N$ record transport, continuation, package provenance, and local naming. They preserve the displayed route but do not add quotient streams, selected sums, host real multiplication, or completeness. Hence every exported seal read factors through the finite Cauchy-convolution packet alone.
\end{proof}

\begin{definition}[CauchyConvolution obligation surface]
\label{def:cauchy-convolution-obligation-surface}
For an accepted $\CauchyConvolutionUp$ packet
$$
Q=(F,G,K,A,D,R,E,H,C,P,N),
$$
the obligation surface consists of source-series admission, finite convolution coefficient ledger, dyadic tail-budget compatibility, $\RegSeqRatUp$ handoff, and $\RealUp$ seal non-escape. The surface is confined to $\FastConvergentSeriesUp$, $\FastSeriesProductUp$, $\DyadicTailBoundUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{definition}

\begin{theorem}[CauchyConvolution obligation ledger exactness]
\label{thm:cauchy-convolution-obligation-ledger-exactness}
For every accepted $\CauchyConvolutionUp$ packet $Q=(F,G,K,A,D,R,E,H,C,P,N)$, the source-series, finite coefficient, and dyadic tail-budget obligations of \autoref{def:cauchy-convolution-obligation-surface} are witnessed by the concrete rows $F,G,K,A,D,H,C,P,N$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:cauchy-convolution-carrier-admission}. It admits the source series rows, finite convolution row, product-prefix ledger, dyadic tail-budget row, and provenance rows as one finite carrier.

Apply \autoref{thm:cauchy-convolution-tail-budget-compatibility}. This binds the source fast-tail schedules and finite source-window bounds to the dyadic tail budget consumed by the regular handoff.

Finally apply \autoref{thm:cauchy-convolution-finite-tail-ledger}. The convolution coefficient ledger remains finite and tied to $K,A,D$ before the handoff row $R$ is read.
\end{proof}

\begin{theorem}[CauchyConvolution obligation real handoff package]
\label{thm:cauchy-convolution-obligation-real-handoff-package}
For every accepted $\CauchyConvolutionUp$ packet $Q=(F,G,K,A,D,R,E,H,C,P,N)$, the $\RegSeqRatUp$ handoff and $\RealUp$ seal non-escape obligations of \autoref{def:cauchy-convolution-obligation-surface} are exactly the displayed route through $R,E,H,C,P,N$ together with the finite convolution ledger $F,G,K,A,D$.
\end{theorem}
\begin{proof}
Use \autoref{thm:cauchy-convolution-real-seal-factorization-boundary}. It factors the real-facing route through the regular rational handoff row and the finite convolution ledger.

Then use \autoref{thm:cauchy-convolution-real-seal-handoff}. It identifies the exported seal as a read of $R$ supported by $A$ and $D$ over $K$, with source rows $F$ and $G$ retained as finite provenance.

The transport, continuation, package, and naming rows preserve that route and do not introduce host real multiplication, quotient equality, selected infinite summation, or completeness.
\end{proof}

\closureat{CauchyConvolutionUp}{seedStr}

\begin{closurestatus}{\CauchyConvolutionUp}
  \constructivestory{A $\CauchyConvolutionUp$ packet is generated from two accepted $\FastConvergentSeriesUp$ source rows, a finite convolution ledger, finite product-prefix rows, dyadic tail-budget rows, a $\RegSeqRatUp$ handoff, a $\RealUp$ seal row, componentwise transport, continuation readback, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope registers the carrier, the five local naming obligations, the finite convolution tail ledger, and the regular-rational-to-$\RealUp$ seal route for Cauchy-product data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host real multiplication, quotient equality of streams, selected infinite sums, uniqueness of products, real completeness, or bridge checking.}
  \upgradepath{Scoped closure requires Lean targets for the carrier, convolution ledger exactness, dyadic tail handoff, regular rational handoff, and real seal non-escape rows.}
\end{closurestatus}
