\chapter{A Concrete Naming Certificate for $\SeparatedCompletionUp$}
\label{ch:concrete-instances-separatedcompletion-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, and Kelley-style separated uniform reasoning, the $\SeparatedCompletionUp$ packet records the finite NameCert boundary at which a metric-completion route becomes separated without becoming a quotient completion. It consumes the metric-completion surface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the dense embedding route of \autoref{ch:concrete-instances-completionembedding-namecert}, the extension-and-uniqueness surface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the zero-distance classifier of \autoref{ch:concrete-instances-separatedmetric-namecert}, the Hausdorff boundary of \autoref{ch:concrete-instances-hausdorffcompletion-namecert}, and the regular-Cauchy separated route of \autoref{ch:concrete-instances-regular-cauchy-completion-separated-namecert}. The L10 spine supplying finite names is the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route of \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

The packet is a general separated-completion interface. It exposes source metric rows, dense embedding rows, completion handoff rows, separated classifier rows, uniqueness-boundary rows, transport rows, continuation replay, package provenance, and local naming. It exports no quotient completion, no selected representative, no host equality of completed points, no countable-choice schedule, no ambient $\RealUp$ completeness theorem, and no hidden complete metric space.

\begin{definition}[SeparatedCompletion carrier]
\label{def:separated-completion-carrier}
A $\SeparatedCompletionUp$ carrier is a finite $\BHist$ packet
$$
S=(M,D,C,Z,U,H,R,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source metric row together with the $\MetricCompletionUp$ admission boundary for completion-facing reads.
\item $D$ is the dense $\CompletionEmbeddingUp$ row, recording how source observations enter the completion interface before any separated comparison is public.
\item $C$ is the completion handoff row, read through the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ L10 naming spine.
\item $Z$ is the $\SeparatedMetricUp$ classifier row that compares displayed completion readings by zero-distance evidence rather than by host equality.
\item $U$ is the uniqueness boundary, supplied by the $\CompletionUniversalPropertyUp$, $\HausdorffCompletionUp$, and $\RegularCauchyCompletionSeparatedUp$ rows over the same source, dense embedding, completion handoff, and separated classifier.
\item $H$ records componentwise $\hsame$ transport for $M,D,C,Z,U$ and for the local structural rows.
\item $R$ records displayed $\Cont$ replay from source metric observations through dense embedding, completion handoff, separated classification, and uniqueness boundary.
\item $T$ is the local transport ledger that states that hsame transport and Cont replay preserve the same ordered completion route.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, $\HausdorffCompletionUp$, $\RegularCauchyCompletionSeparatedUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SeparatedCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient Cauchy classes, selected completion representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or an external complete metric space.
\end{definition}

\begin{theorem}[SeparatedCompletion NameCert obligations]
\label{thm:separated-completion-namecert-obligations}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, the local $\NameCert_{\SeparatedCompletionUp}$ surface consists exactly of these finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, hsame transport, Cont replay, package provenance, and local naming rows;
\item dense-source compatibility, requiring every completion-facing consumer to read $M$ and $D$ before the handoff row $C$;
\item separated-classifier exactness, requiring every comparison of completion readings to pass through $Z$ after $C$ has been displayed;
\item uniqueness-boundary exactness, requiring every asserted uniqueness read to be exhausted by $U$ over the same $M,D,C,Z$ route;
\item transport replay, requiring $H,R,T$ to preserve the ordered route under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item ledger non-escape, excluding quotient completions, selected representatives, host equality, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:separated-completion-carrier}. The tuple displays the source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, structural transport rows, provenance, and local naming.

Dense-source compatibility is the first dependency order. The rows $M$ and $D$ must be present before $C$ can expose any completion-facing read, so no consumer can replace the dense embedding by a selected representative or external completion point.

Separated-classifier exactness is isolated in $Z$. Once $C$ has been displayed, comparison of completion readings is admitted only through the zero-distance classifier row, not through host equality of completed points.

The uniqueness boundary is the row $U$. It is read over the same $M,D,C,Z$ route and is therefore a local ledger comparison, not a quotient-completion uniqueness theorem outside the packet.

Finally, $H,R,T,P,N$ record transport, replay, route preservation, provenance, and local naming for exactly those rows. Since the carrier has no quotient, representative, choice, ambient-completeness, host-equality, or external-complete-space coordinate, the listed obligations exhaust the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.SeparatedCompletionUp.SeparatedCompletionCarrier\_semantic\_name\_certificate}

\begin{theorem}[SeparatedCompletion dense factorization]
\label{thm:separated-completion-dense-factorization}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every completion-facing consumer read factors through the finite dense route
$$
M,D\longmapsto C\longmapsto Z\longmapsto U\longmapsto H,R,T,P,N .
$$
Thus source metric data enter the separated-completion boundary only through the displayed metric-completion and dense-embedding rows before any separated classifier or uniqueness boundary can be consumed.
\end{theorem}
\begin{proof}
Begin with an accepted consumer read. Carrier admission gives the rows $M,D,C,Z,U,H,R,T,P,N$ and no other completion coordinate.

The source part is $M,D$. The metric-completion row admits the request, and the dense embedding row carries source observations into the completion-facing interface.

The handoff row $C$ is read only after that source part is fixed. Its L10 route is the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ naming spine, so the consumer cannot replace it by a quotient stream or selected host limit.

The separated classifier $Z$ and uniqueness boundary $U$ are downstream of the same handoff. Transport, replay, provenance, and local naming in $H,R,T,P,N$ preserve this route and add no external completion object.
\end{proof}

\begin{theorem}[SeparatedCompletion uniqueness boundary]
\label{thm:separated-completion-uniqueness-boundary}
For accepted packets
$$
S=(M,D,C,Z,U,H,R,T,P,N)
\quad\text{and}\quad
S'=(M,D,C,Z,U',H',R',T',P,N')
$$
over the same source metric row, dense embedding, completion handoff, separated classifier, and package provenance, every comparison between their completion-facing exports is exhausted by the uniqueness rows $U,U'$ together with the displayed transport and replay rows $H,R,T$ and $H',R',T'$.
\end{theorem}
\begin{proof}
The shared coordinates $M,D,C,Z,P$ fix the metric-completion source, the dense embedding route, the completion handoff, the separated classifier, and the provenance surface for both packets.

The remaining comparison data are $U,H,R,T,N$ and $U',H',R',T',N'$. The uniqueness rows compare completion-facing presentations over the same shared route, while the transport and replay rows display the permitted movements of that route.

No further field remains from which a consumer could read quotient-completion equality, a selected representative, host equality, countable choice, ambient $\RealUp$ completeness, or a hidden complete metric space. The uniqueness judgement is therefore exactly the displayed local boundary.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy-equivalence source]
\label{thm:separatedcompletion-cauchy-equivalence-source}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every comparison between separated-completion exports first reads the $\RegularCauchyCompletionSeparatedUp$ and $\CauchySequenceEquivalenceUp$ source rows carried by $M,D,C$ before the separated classifier row $Z$ is available. The comparison route is therefore sourced in displayed Cauchy-equivalence data over the same source metric and dense embedding, not in quotient completions, selected representatives, host equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a comparison read of an accepted packet. Carrier admission exposes $M,D,C,Z,U,H,R,T,P,N$ and no other completion coordinate.

The source of the read is the $M,D,C$ route. The metric row and dense embedding row fix the source side, while the completion handoff records the regular-Cauchy separated completion and Cauchy-sequence equivalence data consumed by the comparison.

Only after that source route is displayed may $Z$ classify separated completion readings. Since the carrier has no quotient-completion, selected-representative, host-equality, choice, Real-completeness, or hidden-complete-space coordinate, no comparison can bypass the displayed Cauchy-equivalence source.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy reflector obligation]
\label{thm:separatedcompletion-cauchy-reflector-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every Cauchy-reflector read exposed by $S$ first displays the $\CauchyCompletionReflectorUp$ route and the dense embedding route inside the $M,D,C$ rows, then reads the separated comparison row $Z$. The obligation is a $\BHist$ and $\NameCert$ row route through $M,D,C,Z,H,R,T,P,N$, not parameter transport over an external completion object.
\end{theorem}
\begin{proof}
Start from \autoref{thm:separatedcompletion-cauchy-equivalence-source}. It places every comparison behind the displayed Cauchy-equivalence and regular separated-completion source rows carried by $M,D,C$.

The reflector read is therefore not a free-standing map. Its source side is the displayed CauchyCompletionReflector row, while the dense embedding row $D$ records the admission route into the completion handoff $C$.

Only after those rows are visible can $Z$ compare separated completion readings. The structural rows $H,R,T,P,N$ transport, replay, source, and locally name the same route, so the Cauchy reflector obligation is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[SeparatedCompletion Real seal nonescape]
\label{thm:separatedcompletion-real-seal-nonescape}
Every $\RealUp$ seal read accepted by a $\SeparatedCompletionUp$ carrier remains downstream of the displayed $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$ rows carried through $M,D,C$. The seal may be consumed by the separated classifier $Z$ and uniqueness boundary $U$, but it cannot expose host real equality, ambient $\RealUp$ completeness, quotient completion equality, selected representatives, or countable choice.
\end{theorem}
\begin{proof}
Read the source route $M,D,C$ first. These rows carry the metric-completion source, dense embedding, regular rational readback, finite stream windows, and dyadic tolerance evidence before any separated comparison is inspected.

The $\RealUp$ seal is reached only after that finite route. It records terminal readback data for the displayed completion route rather than an ambient completeness theorem.

Now apply the separated classifier and uniqueness rows $Z,U$. They consume the seal downstream of the same packet, while $H,R,T,P,N$ merely transport, replay, source, and name the route. Since no excluded real or completion principle is a carrier coordinate, the seal cannot escape the displayed rows.
\end{proof}

\begin{theorem}[SeparatedCompletion universal route exhaustion]
\label{thm:separatedcompletion-universal-route-exhaustion}
For every accepted $\SeparatedCompletionUp$ carrier, the universal completion route is exhausted by the displayed rows
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The route exports dense-source admission, Cauchy-equivalence sourcing, separated comparison, uniqueness boundary, transport, replay, provenance, and local naming, but it exports no quotient completion, selected representative, host equality, countable choice, ambient $\RealUp$ completeness, or additional universal completion principle outside the carrier.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. Its displayed rows are exactly the source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, provenance, and local naming rows.

Use dense factorization and the Cauchy-equivalence source theorem. They place the universal read behind $M,D,C$ before $Z$ or $U$ can be inspected.

The separated comparison and uniqueness rows then account for the completion-facing universal property available to consumers. No further coordinate remains for quotient completion, representative selection, host equality, choice, or ambient completeness.

Finally $H,R,T,P,N$ preserve the same row list. Thus the displayed carrier exhausts the universal route and exports no completion principle beyond the finite packet.
\end{proof}

\begin{theorem}[SeparatedCompletion zero-distance factorization]
\label{thm:separatedcompletion-zero-distance-factorization}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. The separated classifier route factors through the $\MetricCompletionUp$, $\SeparatedMetricUp$, $\RegSeqRatUp$, and $\RealUp$ zero-distance evidence displayed by $M,C,Z$. Thus a separated-completion equality read is a finite zero-distance handoff through the local packet, not a quotient completion, a selected representative, host equality, countable choice, or an ambient $\RealUp$ completeness assertion.
\end{theorem}
\begin{proof}
Read the route in order. The row $M$ supplies the metric-completion admission boundary, and $C$ supplies the finite L10 handoff through regular rational readback toward the Real-facing seal.

The row $Z$ then reads that handoff as $\SeparatedMetricUp$ zero-distance evidence. Its classifier compares displayed completion readings by zero distance after the $\RegSeqRatUp$ and $\RealUp$ rows have been reached through $C$.

Transport, replay, provenance, and local naming in $H,R,T,P,N$ preserve the same factorization. No field remains for quotient completion equality, selected representatives, host equality, countable choice, or ambient Real completeness.
\end{proof}

\begin{theorem}[SeparatedCompletion limit-uniqueness export]
\label{thm:separatedcompletion-limit-uniqueness-export}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, the public limit-uniqueness export is exactly the local boundary $U$ over the already displayed $M,D,C,Z$ route. The export contains no separate uniqueness principle over quotient completions, selected representatives, host equality, countable choice, ambient $\RealUp$ completeness, or hidden complete metric spaces.
\end{theorem}
\begin{proof}
Carrier admission makes $U$ the only uniqueness-boundary row in the packet. Its hypotheses and conclusion are read over the same source metric, dense embedding, completion handoff, and separated classifier rows $M,D,C,Z$.

The transport and replay rows $H,R,T$ can move this boundary componentwise, but they do not create a second uniqueness coordinate. The package and local naming rows $P,N$ record the same source list.

Therefore every public uniqueness export is the local $U$ boundary over $M,D,C,Z$. The excluded quotient, representative, host-equality, choice, Real-completeness, and hidden-complete-space objects are absent from the carrier and cannot be exported.
\end{proof}

\begin{theorem}[SeparatedCompletion dense uniqueness interface]
\label{thm:separatedcompletion-dense-uniqueness-interface}
Let
$$
S=(M,D,C,Z,U,H,R,T,P,N)
\quad\text{and}\quad
S'=(M,D,C,Z,U',H',R',T',P,N')
$$
be accepted $\SeparatedCompletionUp$ carriers with the same dense-source route $M,D,C$ and the same zero-distance separated classifier $Z$. Then any completion-facing comparison between their exports exposes the same limit-uniqueness boundary through $U,U'$ together with the displayed transport and replay rows. It exports no quotient representative, no selected completion point, no host equality of completed points, no countable-choice schedule, and no ambient $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Use the dense factorization of \autoref{thm:separated-completion-dense-factorization}. Every completion-facing read of either packet first passes through the shared source metric, dense embedding, and completion handoff rows $M,D,C$.

Use the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}. Since the separated classifier row $Z$ is also shared, the comparison is read as zero-distance evidence over the same finite route rather than as host equality of completed points.

Apply the limit-uniqueness export of \autoref{thm:separatedcompletion-limit-uniqueness-export} to both packets. The only remaining uniqueness data are $U,U'$ and the displayed transport and replay rows $H,R,T$ and $H',R',T'$. The carrier has no quotient representative, selected completion point, choice schedule, or ambient completeness coordinate, so the dense uniqueness interface exports exactly that local boundary.
\end{proof}

\begin{theorem}[SeparatedCompletion source-comparison exhaustion]
\label{thm:separatedcompletion-source-comparison-exhaustion}
Let
$$
S=(M,D,C,Z,U,H,R,T,P,N)
\quad\text{and}\quad
S'=(M,D,C,Z,U',H',R',T',P,N')
$$
be accepted $\SeparatedCompletionUp$ carriers over the same source metric row, dense embedding, completion handoff, separated classifier, and provenance surface. Every accepted comparison between their separated-completion exports is exhausted by the shared $M,D,C,Z$ source route, by the uniqueness rows $U,U'$, and by the displayed transport and replay rows $H,R,T$ and $H',R',T'$. The comparison exports no quotient completion, selected representative, host equality of completed points, countable-choice schedule, ambient $\RealUp$ completeness theorem, or hidden complete metric space.
\end{theorem}
\begin{proof}
First use the dense factorization of \autoref{thm:separated-completion-dense-factorization}. It sends every completion-facing read through the shared source metric row $M$, dense embedding row $D$, and completion handoff row $C$ before any separated classifier or uniqueness boundary is consumed.

Next use the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}. The shared classifier $Z$ reads the comparison as zero-distance evidence over the same finite route, so the comparison cannot be replaced by host equality of completed points.

Now apply the limit-uniqueness export of \autoref{thm:separatedcompletion-limit-uniqueness-export} to both packets. The only remaining comparison rows are $U,U'$ together with the displayed transport and replay ledgers.

Finally attach the Cauchy-equivalence source theorem, \autoref{thm:separatedcompletion-cauchy-equivalence-source}. It keeps the comparison sourced in the displayed Cauchy-equivalence and dense-completion data carried by $M,D,C$. Since the carriers contain no excluded completion coordinate, the listed rows exhaust the accepted comparison surface.
\end{proof}

\begin{theorem}[SeparatedCompletion non-escape]
\label{thm:separated-completion-nonescape}
Every accepted $\SeparatedCompletionUp$ carrier exports only the rows
$$
M,D,C,Z,U,H,R,T,P,N
$$
of \autoref{def:separated-completion-carrier}. No consumer of the packet can obtain a quotient completion, selected representative, host equality of completed points, countable-choice schedule, ambient $\RealUp$ completeness theorem, or hidden complete metric space.
\end{theorem}
\begin{proof}
The NameCert obligations of \autoref{thm:separated-completion-namecert-obligations} enumerate the carrier, dense-source, separated-classifier, uniqueness-boundary, transport-replay, and refusal rows available to the packet.

The dense factorization of \autoref{thm:separated-completion-dense-factorization} covers every completion-facing consumer read. Such a read must traverse $M,D,C,Z,U,H,R,T,P,N$ and cannot bypass the finite route through a host completion object.

The uniqueness boundary of \autoref{thm:separated-completion-uniqueness-boundary} covers every comparison between completion-facing exports. Since the carrier has no additional coordinate beyond the displayed rows, none of the excluded quotient, representative, host-equality, choice, Real-completeness, or hidden-complete-space objects can be projected from an accepted packet.
\end{proof}

\begin{theorem}[SeparatedCompletion choice-free source route]
\label{thm:separatedcompletion-choice-free-source-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every accepted source-to-uniqueness read exposes the source metric row $M$, dense embedding row $D$, completion handoff row $C$, and separated classifier row $Z$ before any uniqueness row $U$ is available. The route is carried by displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and cannot expose choice data, quotient completion data, selected representatives, or host equality of completed points.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:separated-completion-carrier}. Its displayed rows are $M,D,C,Z,U,H,R,T,P,N$, so the source metric, dense embedding, completion handoff, and separated classifier are present before the uniqueness boundary can be projected.

Apply the dense factorization theorem, \autoref{thm:separated-completion-dense-factorization}. It fixes the order $M,D\mapsto C\mapsto Z\mapsto U$ for completion-facing reads.

Apply the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization} and the source-comparison exhaustion theorem, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. These results keep the comparison in displayed Cauchy and zero-distance data rather than in quotient or host equality data.

The structural support rows are exactly $H,R,T,P,N$: componentwise $\hsame$ transport, displayed $\Cont$ replay, route preservation, $\Pkg$ provenance, and local $\NameCert$ admission. Since the carrier contains no choice, quotient completion, selected-representative, or host-equality coordinate, the source route is choice-free.
\end{proof}

\begin{theorem}[SeparatedCompletion regular-Cauchy source route]
\label{thm:separatedcompletion-regular-cauchy-source-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every regular-Cauchy source read used by the separated-completion boundary factors through the displayed source metric row $M$, dense embedding row $D$, completion handoff row $C$, and separated classifier row $Z$ before the uniqueness row $U$ and the structural rows $H,R,T,P,N$ are consumed. The route may use the dense factorization of \autoref{thm:separated-completion-dense-factorization}, the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}, and the source-comparison exhaustion of \autoref{thm:separatedcompletion-source-comparison-exhaustion}, but it cannot add quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or hidden complete metric spaces.
\end{theorem}
\begin{proof}
Start with carrier admission. The visible rows are exactly $M,D,C,Z,U,H,R,T,P,N$, so any regular-Cauchy source read must begin inside the displayed carrier inventory.

Apply dense factorization, \autoref{thm:separated-completion-dense-factorization}. It fixes $M,D$ as the source prefix and $C$ as the completion handoff reached from that prefix.

Apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The separated classifier row $Z$ reads equality through zero-distance evidence over the same handoff, not through host equality of completed points.

Finally use source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It leaves only $U,H,R,T,P,N$ as the downstream uniqueness, transport, replay, route, provenance, and naming rows, and the excluded completion and choice objects have no coordinate in the carrier.
\end{proof}

\begin{theorem}[SeparatedCompletion Hausdorff uniqueness route]
\label{thm:separatedcompletion-hausdorff-uniqueness-route}
For accepted $\SeparatedCompletionUp$ carriers over displayed rows $M,D,C,Z,U,H,R,T,P,N$, every Hausdorff-style uniqueness read is exhausted by the dense source route $M,D,C$, the zero-distance separated classifier $Z$, the uniqueness boundary $U$, and the transport, replay, route, provenance, and local naming rows $H,R,T,P,N$. The read is a local separated-completion boundary over the theorems \autoref{thm:separated-completion-dense-factorization}, \autoref{thm:separatedcompletion-zero-distance-factorization}, and \autoref{thm:separatedcompletion-source-comparison-exhaustion}; it is not a quotient completion, a selected representative, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or a hidden complete metric space.
\end{theorem}
\begin{proof}
Read the dense source route first. By \autoref{thm:separated-completion-dense-factorization}, a uniqueness consumer must pass through $M,D,C$ before reaching any separated classifier or uniqueness row.

Read the separated classifier next. By \autoref{thm:separatedcompletion-zero-distance-factorization}, $Z$ supplies the zero-distance route that replaces host equality inside the accepted packet.

The Hausdorff-style uniqueness boundary is then the local row $U$ together with the structural rows $H,R,T,P,N$. These rows transport, replay, preserve, source, and name the same displayed route.

Source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, closes the comparison surface. Since quotient completions, selected representatives, host equality, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces are absent from $M,D,C,Z,U,H,R,T,P,N$, they cannot enter the uniqueness read.
\end{proof}

\begin{theorem}[SeparatedCompletion metric-completion handoff]
\label{thm:separatedcompletion-metric-completion-handoff}
Every metric-completion handoff exported by an accepted $\SeparatedCompletionUp$ carrier factors through the displayed rows
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The handoff uses the dense route of \autoref{thm:separated-completion-dense-factorization}, the zero-distance route of \autoref{thm:separatedcompletion-zero-distance-factorization}, and the exhausted comparison surface of \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It exports no quotient completion, selected representative, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or hidden complete metric space.
\end{theorem}
\begin{proof}
Project the accepted carrier. The metric-completion source row $M$, dense embedding row $D$, and completion handoff row $C$ form the only displayed metric-completion prefix.

Use \autoref{thm:separated-completion-dense-factorization}. It sends every completion-facing handoff through $M,D,C$ before any separated or uniqueness boundary is available.

Use \autoref{thm:separatedcompletion-zero-distance-factorization}. The row $Z$ is the separated comparison route available after the completion handoff, and it is finite zero-distance evidence rather than host equality.

Use \autoref{thm:separatedcompletion-source-comparison-exhaustion}. The remaining rows $U,H,R,T,P,N$ exhaust the uniqueness, transport, replay, route, provenance, and naming surface. Because the carrier has no quotient-completion, selected-representative, host-equality, choice, Real-completeness, or hidden-complete-space coordinate, the metric-completion handoff exports only the displayed finite route.
\end{proof}

\begin{theorem}[SeparatedCompletion filtered limit boundary]
\label{thm:separatedcompletion-filtered-limit-boundary}
For an accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, every filtered limit-boundary read is exhausted by the Cauchy-equivalence source rows displayed by $M,D,C$, the zero-distance separated classifier row $Z$, the local uniqueness row $U$, and the transport and replay rows $H,R,T$. It exports no additional limit selector, quotient class, host equality, countable-choice schedule, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Read the source side first. The Cauchy-equivalence source theorem, \autoref{thm:separatedcompletion-cauchy-equivalence-source}, places every comparison over the displayed $M,D,C$ route.

Read the classifier next. The zero-distance factorization theorem, \autoref{thm:separatedcompletion-zero-distance-factorization}, makes $Z$ the only separated comparison row available after the completion handoff.

Read the boundary row. The limit-uniqueness export theorem, \autoref{thm:separatedcompletion-limit-uniqueness-export}, identifies $U$ as the public uniqueness boundary over the same $M,D,C,Z$ route.

Finally apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It includes the displayed $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows and excludes any extra selector, quotient class, host equality, choice schedule, or ambient Real-completeness coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion completion-reflector handoff]
\label{thm:separatedcompletion-completion-reflector-handoff}
Every handoff from an accepted $\SeparatedCompletionUp$ carrier to $\CauchyCompletionReflectorUp$ or $\CompletionUniversalPropertyUp$ factors through the same finite source route
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The handoff may use the source metric, dense factorization, zero-distance factorization, limit-uniqueness export, source-comparison exhaustion, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row, but it cannot add a quotient completion, selected representative, host equality, countable choice, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project the accepted carrier and apply dense factorization from \autoref{thm:separated-completion-dense-factorization}. The handoff begins with $M,D,C$, so both reflector-facing and universal-property-facing reads share the same source metric, dense embedding, and completion handoff.

Apply the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}. The separated classifier $Z$ is the only comparison route available before any uniqueness boundary is read.

Apply the limit-uniqueness export of \autoref{thm:separatedcompletion-limit-uniqueness-export} and the source-comparison exhaustion theorem, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. Together they identify $U$ and the transport and replay rows $H,R,T$ as the complete handoff boundary.

The provenance and local naming rows $P,N$ attach the boundary to $\Pkg$ and $\NameCert$ data. Because the carrier contains no quotient-completion, selected-representative, host-equality, choice, or ambient-completeness coordinate, a $\CauchyCompletionReflectorUp$ or $\CompletionUniversalPropertyUp$ consumer receives only the displayed finite route.
\end{proof}

\begin{theorem}[SeparatedCompletion dense replay scope]
\label{thm:separatedcompletion-dense-replay-scope}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, every completion-facing read exposes the source metric row $M$, dense embedding row $D$, and completion handoff row $C$ before the separated classifier $Z$, uniqueness boundary $U$, transport row $H$, replay row $R$, route ledger $T$, provenance row $P$, or local naming row $N$ is consumed. Thus dense replay is a finite $M,D,C$ prefix over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data, not a selected representative or quotient-completion read.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:separated-completion-carrier}. The rows $M,D,C$ are the only source metric, dense embedding, and completion handoff coordinates.

Apply dense factorization, \autoref{thm:separated-completion-dense-factorization}. It places every completion-facing consumer read on the route $M,D\mapsto C$ before the separated classifier and uniqueness boundary are available.

Then use the choice-free source route, \autoref{thm:separatedcompletion-choice-free-source-route}. The structural rows $H,R,T,P,N$ preserve the same ordered route and do not introduce a choice coordinate, quotient completion, selected representative, or host equality of completed points.
\end{proof}

\begin{theorem}[SeparatedCompletion separated classifier scope]
\label{thm:separatedcompletion-separated-classifier-scope}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, zero-distance classification through $Z$ is the only separated equality route after the dense completion handoff $M,D,C$ has been displayed. Any completion-facing equality read that bypasses $Z$ leaves the $\NameCert_{\SeparatedCompletionUp}$ surface and cannot be recovered from $U,H,R,T,P,N$ alone.
\end{theorem}
\begin{proof}
Read the dense prefix first. By \autoref{thm:separatedcompletion-dense-replay-scope}, a completion-facing equality read has already exposed $M,D,C$ before it reaches any separated comparison row.

Now apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The classifier row $Z$ reads equality as displayed zero-distance evidence over the $\MetricCompletionUp$, $\SeparatedMetricUp$, $\RegSeqRatUp$, and $\RealUp$ route, rather than as host equality or quotient completion equality.

Finally apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. The uniqueness, transport, replay, provenance, and naming rows preserve a comparison once $Z$ is present, but none of them supplies an alternate separated equality route.
\end{proof}

\begin{theorem}[SeparatedCompletion obligation closure package]
\label{thm:separatedcompletion-obligation-closure-package}
The accepted $\SeparatedCompletionUp$ carrier
$$
S=(M,D,C,Z,U,H,R,T,P,N)
$$
supports an obligationClosure package whose finite boundary is exactly dense factorization, zero-distance factorization, source-comparison exhaustion, the choice-free source route, the filtered limit boundary, and the completion-reflector handoff. The package closes the paper-side obligation surface over the displayed rows and refuses quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces.
\end{theorem}
\begin{proof}
Build the source prefix from dense factorization, \autoref{thm:separated-completion-dense-factorization}, and dense replay scope, \autoref{thm:separatedcompletion-dense-replay-scope}. These results force every completion-facing read through $M,D,C$.

Build the classifier boundary from zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, and separated classifier scope, \autoref{thm:separatedcompletion-separated-classifier-scope}. They make $Z$ the only separated equality route after the dense completion handoff.

Add the comparison and source routes from \autoref{thm:separatedcompletion-source-comparison-exhaustion} and \autoref{thm:separatedcompletion-choice-free-source-route}. These theorems keep all comparison data in displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally attach the filtered limit boundary, \autoref{thm:separatedcompletion-filtered-limit-boundary}, and the completion-reflector handoff, \autoref{thm:separatedcompletion-completion-reflector-handoff}. The resulting package contains no coordinate for quotient completions, selected representatives, host equality, countable choice, ambient Real completeness, or hidden complete metric spaces, so the obligation surface is closed at the paper level.
\end{proof}

\begin{theorem}[SeparatedCompletion carrier admission root obligation]
\label{thm:separated-completion-carrier-admission-root-obligation}
Every accepted $\SeparatedCompletionUp$ carrier exposes only the displayed $\CauchySequenceEquivalenceUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\HausdorffCompletionUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ rows before its local $\NameCert_{\SeparatedCompletionUp}$ row is read. The admission surface contains no additional completion point, quotient class, selected representative, host equality of completed points, countable-choice schedule, or hidden complete metric space.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. The source, dense-embedding, completion handoff, separated classifier, and uniqueness rows are exactly $M,D,C,Z,U$.

Read these rows through the existing source route. The Cauchy-equivalence source theorem, \autoref{thm:separatedcompletion-cauchy-equivalence-source}, and the dense factorization theorem, \autoref{thm:separated-completion-dense-factorization}, place the admission boundary over $\CauchySequenceEquivalenceUp$, $\CompletionEmbeddingUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ data.

Then attach the uniqueness boundary from \autoref{thm:separated-completion-uniqueness-boundary}. It adds only the displayed $\CompletionUniversalPropertyUp$ and $\HausdorffCompletionUp$ rows over the same finite route. Since $H,R,T,P,N$ merely transport, replay, preserve, source, and name the displayed rows, the excluded completion objects have no carrier coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion classifier stability root obligation]
\label{thm:separated-completion-classifier-stability-root-obligation}
For any accepted $\SeparatedCompletionUp$ carriers over componentwise $\hsame$-transported $M,D,C,Z,U,H,R,T,P,N$ rows, the separated classifier exposed by $Z$ is preserved by the displayed transport and replay rows. This stability cannot introduce quotient-completion equality, selected representatives, host equality of completed points, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the transported carrier rows. Componentwise $\hsame$ transport acts on the displayed source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, replay, provenance, and local naming rows named by the carrier.

Apply separated classifier scope, \autoref{thm:separatedcompletion-separated-classifier-scope}. After the dense completion handoff, $Z$ is the only separated equality route available to a completion-facing read.

Finally apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It keeps transported comparisons inside $M,D,C,Z,U,H,R,T,P,N$. Because the transported packet has no quotient-completion or host-equality coordinate, classifier stability cannot create one.
\end{proof}

\begin{theorem}[SeparatedCompletion Real seal root obligation]
\label{thm:separated-completion-real-seal-root-obligation}
Any Real-facing seal read exported by an accepted $\SeparatedCompletionUp$ carrier factors through displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\MetricCompletionUp$ rows before the separated completion handoff is consumed. The seal read is therefore a finite BEDC route through $M,D,C,Z,U,H,R,T,P,N$, not an ambient $\RealUp$ completeness principle or a chosen completion representative.
\end{theorem}
\begin{proof}
Read the dense prefix first. By \autoref{thm:separatedcompletion-dense-replay-scope}, every completion-facing read exposes $M,D,C$ before any separated classifier, uniqueness boundary, or local naming row is available.

The opening carrier route identifies this prefix with the L10 spine through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, together with the $\MetricCompletionUp$ handoff. The Real-facing seal is therefore downstream from finite stream windows and regular rational readback.

Now apply the choice-free source route, \autoref{thm:separatedcompletion-choice-free-source-route}, and the completion-reflector handoff, \autoref{thm:separatedcompletion-completion-reflector-handoff}. They keep the separated completion handoff in displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and exclude ambient Real completeness, selected representatives, quotient completions, host equality, and countable choice.
\end{proof}

\begin{theorem}[SeparatedCompletion root obligation package]
\label{thm:separated-completion-root-obligation-package}
For every accepted $\SeparatedCompletionUp$ carrier, the carrier-admission, classifier-stability, and Real-seal root obligations of \autoref{thm:separated-completion-carrier-admission-root-obligation}, \autoref{thm:separated-completion-classifier-stability-root-obligation}, and \autoref{thm:separated-completion-real-seal-root-obligation} jointly exhaust the finite $\NameCert_{\SeparatedCompletionUp}$ surface over $\CauchyCompletionReflectorUp$, $\CompletionEmbeddingUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\RealUp$, and $\StreamNameUp$ rows. Thus every downstream completion consumer receives only displayed source admission, separated classifier stability, Real-seal readback, componentwise transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
The carrier-admission root obligation identifies the finite row inventory available to the accepted carrier. It confines every completion-facing read to the displayed source, dense embedding, completion handoff, separated classifier, uniqueness, transport, replay, provenance, and local naming rows.

The classifier-stability root obligation then fixes the separated equality surface. Transport and replay preserve the classifier row inside that same finite inventory, so no extra quotient representative or host equality coordinate appears after the carrier is admitted.

The Real-seal root obligation closes the remaining completion-to-Real route through the StreamName, RegSeqRat, DyadicRatCore, and MetricCompletion rows. Together the three obligations cover the root surface exposed to CauchyCompletionReflector, CompletionEmbedding, MetricCompletion, RegSeqRat, Real, and StreamName consumers, and none of them introduces quotient representatives, host equality, countable choice, or an ambient completeness coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion filterbase admission]
\label{thm:separated-completion-filterbase-admission}
For every accepted $\SeparatedCompletionUp$ carrier
$$
S=(M,D,C,Z,U,H,R,T,P,N),
$$
any filterbase-facing admission read factors through the same finite source route as \autoref{thm:separated-completion-root-obligation-package}. The $\CauchyCompletionReflectorUp$ and $\MetricCompletionUp$ rows receive the source metric $M$, dense embedding $D$, completion handoff $C$, separated classifier $Z$, $\RegSeqRatUp$ and $\StreamNameUp$ windows, terminal $\RealUp$ seal, and structural rows $H,R,T,P,N$ before a filterbase consumer may inspect completion data. Thus filterbase admission is a $\BHist$ and $\NameCert$ route, not a quotient completion, selected representative, host equality, countable-choice selector, or ambient complete-space coordinate.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $M,D,C$ admit the source metric, dense embedding, and completion handoff before any filterbase-facing consumer can read completion data.

The separated classifier row $Z$ and uniqueness boundary $U$ keep the filterbase comparison inside the same displayed separated route. Apply \autoref{thm:separated-completion-classifier-stability-root-obligation} to see that transport and replay cannot add a host equality coordinate.

Finally read the completion-facing spine. The $\CauchyCompletionReflectorUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ rows are delivered through $H,R,T,P,N$, so the filterbase admission has no access to quotient completions, selected representatives, countable choice, or an ambient complete-space object.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy-equivalence routing]
\label{thm:separated-completion-cauchy-equivalence-routing}
For every accepted $\SeparatedCompletionUp$ carrier, each Cauchy-equivalence read sent to $\RegSeqRatUp$, $\StreamNameUp$, $\MetricCompletionUp$, or $\RealUp$ factors through the separated classifier and the Cauchy source rows before the terminal Real seal is exposed. In symbols, the public Cauchy-equivalence route is
$$
M,D,C,Z,U \longmapsto \RegSeqRatUp,\StreamNameUp,\MetricCompletionUp,\RealUp \longmapsto H,R,T,P,N .
$$
The route exports only displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and does not export quotient stream equality, host equality of completed points, selected limits, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:separatedcompletion-cauchy-equivalence-source}. It places every Cauchy-equivalence read behind the displayed Cauchy source and separated-completion rows, so the comparison is not a free-standing quotient relation.

Next apply \autoref{thm:separatedcompletion-zero-distance-factorization} and \autoref{thm:separatedcompletion-limit-uniqueness-export}. These theorems route zero-distance and uniqueness reads through $Z$ and $U$ before the regular-rational and stream windows can be consumed.

The Real-facing boundary is then supplied by \autoref{thm:separated-completion-real-seal-root-obligation}. The structural rows preserve and replay the same path through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, so no quotient stream equality, host equality, selected limit, choice principle, or ambient completeness coordinate is available.
\end{proof}

\begin{theorem}[SeparatedCompletion completion-reflector nonescape]
\label{thm:separated-completion-completion-reflector-nonescape}
Every $\CauchyCompletionReflectorUp$ or $\MetricCompletionUp$ consumer of an accepted $\SeparatedCompletionUp$ carrier remains inside the finite route
$$
M,D,C,Z,U,H,R,T,P,N
$$
together with the displayed $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ handoff rows. The reflector may read the source metric, dense embedding, separated classifier, uniqueness boundary, transport, replay, provenance, and local naming, but it may not import quotient completions, selected representatives, host equality, countable choice, hidden complete metric spaces, or an ambient real-completeness theorem.
\end{theorem}
\begin{proof}
Read the reflector handoff through \autoref{thm:separatedcompletion-completion-reflector-handoff}. It already places the completion-reflector consumer downstream of the source metric, dense embedding, completion handoff, separated classifier, and Real-facing L10 spine.

The root package of \autoref{thm:separated-completion-root-obligation-package} exhausts the carrier-admission, classifier-stability, and Real-seal obligations. Hence the reflector consumer can inspect only the rows listed there and the transport, replay, provenance, and naming rows $H,R,T,P,N$.

Nonescape follows from absence of coordinates. Quotient completions, selected representatives, host equality, countable choice, hidden complete metric spaces, and ambient real completeness are not fields of the carrier and cannot be produced by $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, or local $\NameCert$ naming.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy-reflector triangle]
\label{thm:separatedcompletion-cauchy-reflector-triangle}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier whose source route receives $\CauchyCompletionReflectorUp$, $\CompletionUniversalPropertyUp$, $\RegularCauchyCompletionSeparatedUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows. Every endpoint-uniqueness read sent toward a Real-facing completion seal factors through the separated classifier row $Z$ before it can be consumed by the reflector or universal-property rows. The triangle
$$
\CauchyCompletionReflectorUp
\longmapsto
\SeparatedCompletionUp
\longmapsto
\CompletionUniversalPropertyUp
$$
therefore commutes at the displayed $\NameCert$ surface through $M,D,C,Z,U,H,R,T,P,N$, and exports no quotient completion, selected representative, host equality of completed points, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The dense source rows $M,D,C$ are read first, so the reflector-facing route starts from the same finite metric, dense embedding, and completion handoff as the rest of the chapter.

Apply \autoref{thm:separated-completion-dense-factorization} and \autoref{thm:separated-completion-uniqueness-boundary}. They place endpoint uniqueness downstream of the dense factorization and force the uniqueness boundary to read the separated classifier row $Z$ rather than a host equality coordinate.

Now apply \autoref{thm:separatedcompletion-completion-reflector-handoff}. The CauchyCompletionReflector and CompletionUniversalProperty consumers receive the same route through $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyCompletionSeparatedUp$, and the terminal $\RealUp$ seal.

The transport, route-preservation, provenance, and local naming rows $H,R,T,P,N$ preserve this factorization. Because the carrier contains no quotient-completion, selected-representative, host-equality, choice, or ambient-completeness coordinate, the only available triangle is the displayed separated-classifier route.
\end{proof}

\begin{theorem}[SeparatedCompletion root-consumer unblock package]
\label{thm:separatedcompletion-root-consumer-unblock-package}
Every downstream Real or Completion consumer of an accepted $\SeparatedCompletionUp$ carrier must factor through the carrier-admission root obligation, classifier-stability root obligation, Real-seal root obligation, root obligation package, and Cauchy-reflector triangle before reading any completion-facing output. Equivalently, any consumer route over $S=(M,D,C,Z,U,H,R,T,P,N)$ must display the finite root surface
$$
M,D,C,Z,U,H,R,T,P,N
$$
together with the carrier-admission, classifier-stability, Real-seal, root-package, and reflector-triangle witnesses. The package exports no quotient completion, selected representative, host equality of completed points, countable choice, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Project the accepted carrier into the rows $M,D,C,Z,U,H,R,T,P,N$. The source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, route preservation, replay, provenance, and local naming rows are therefore the only displayed input surface available to downstream consumers.

Apply \autoref{thm:separated-completion-root-obligation-package}. It combines the carrier-admission root obligation, classifier-stability root obligation, and Real-seal root obligation, so the source, classifier, and seal sides of the accepted packet are exhausted before a completion-facing output can be read.

Next apply \autoref{thm:separatedcompletion-cauchy-reflector-triangle}. The reflector and universal-property routes commute only through the separated classifier row and the same finite L10 source spine, so endpoint-uniqueness reads cannot bypass the root package.

The remaining structural rows $H,R,T,P,N$ preserve, replay, source, and name that route. Since no quotient completion, selected representative, host equality, countable-choice schedule, or ambient Real-completeness coordinate appears among the carrier rows, the displayed package is the required unblock surface for all downstream Real and Completion consumers.
\end{proof}

\begin{theorem}[SeparatedCompletion dense limit route]
\label{thm:separatedcompletion-dense-limit-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every accepted limit-facing read must pass through the displayed $\MetricCompletionUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, $\HausdorffCompletionUp$, $\RegularCauchyCompletionSeparatedUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows before the uniqueness row $U$ is public. The route exposes dense source data, zero-distance classification, regular-Cauchy separated completion, and the Real-facing L10 spine, and it exports no quotient completion, selected limit representative, host equality of completed points, countable-choice schedule, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Read the dense source prefix first. Dense factorization, \autoref{thm:separated-completion-dense-factorization}, and dense replay scope, \autoref{thm:separatedcompletion-dense-replay-scope}, force every completion-facing read through $M,D,C$ before any separated classifier or uniqueness row is available.

Read the classifier and limit boundary next. Zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, makes $Z$ the separated equality route, and limit-uniqueness export, \autoref{thm:separatedcompletion-limit-uniqueness-export}, makes $U$ the public uniqueness row over $M,D,C,Z$.

Now attach source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, and nonescape, \autoref{thm:separated-completion-nonescape}. These results keep the source route inside the displayed MetricCompletion, CompletionEmbedding, CompletionUniversalProperty, SeparatedMetric, HausdorffCompletion, RegularCauchyCompletionSeparated, DyadicRatCore, StreamName, RegSeqRat, and Real rows. Since none of the excluded objects is a carrier coordinate, the dense limit route reaches uniqueness only through the displayed packet.
\end{proof}

\begin{theorem}[SeparatedCompletion choice-free limit transport]
\label{thm:separatedcompletion-choice-free-limit-transport}
For accepted $\SeparatedCompletionUp$ carriers whose source, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, route, provenance, and local naming rows are matched componentwise by $\hsame$ and replayed by $\Cont$, the transported packet preserves the same dense source, zero-distance classifier, and uniqueness boundary. This preservation uses no countable choice, quotient completion, selected representative, host equality of completed points, hidden complete metric space, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project the two carriers and read their transported rows componentwise. The $\hsame$ rows act only on $M,D,C,Z,U,H,R,T,P,N$, and the $\Cont$ rows replay the same displayed path.

Apply dense factorization, \autoref{thm:separated-completion-dense-factorization}, to both packets. The dense source remains the $M,D,C$ route after transport, because no additional source coordinate is present.

Apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, and limit-uniqueness export, \autoref{thm:separatedcompletion-limit-uniqueness-export}. They identify $Z$ as the classifier and $U$ as the uniqueness boundary before any downstream completion consumer can read the transported packet.

Finally use source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, together with nonescape, \autoref{thm:separated-completion-nonescape}. The structural rows preserve the dense source, zero-distance classifier, and uniqueness boundary, while the excluded choice, quotient, representative, host-equality, hidden-space, and ambient-completeness objects remain absent from the carrier.
\end{proof}

\begin{theorem}[SeparatedCompletion completion uniqueness package]
\label{thm:separatedcompletion-completion-uniqueness-package}
Every downstream $\MetricCompletionUp$ or $\HausdorffCompletionUp$ consumer of an accepted $\SeparatedCompletionUp$ carrier receives uniqueness only as the displayed row $U$ over $M,D,C,Z$ together with the structural rows $H,R,T,P,N$. The package may use the dense limit route of \autoref{thm:separatedcompletion-dense-limit-route} and the choice-free transport route of \autoref{thm:separatedcompletion-choice-free-limit-transport}, but it cannot export quotient completion equality, a selected representative, host equality of completed points, countable choice, a hidden complete metric space, or an ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with the dense route. By \autoref{thm:separatedcompletion-dense-limit-route}, a MetricCompletion or HausdorffCompletion consumer sees $M,D,C$ before the separated classifier $Z$ and uniqueness row $U$ are public.

Read uniqueness through the local row $U$. The limit-uniqueness export theorem, \autoref{thm:separatedcompletion-limit-uniqueness-export}, identifies that row as the whole uniqueness boundary over $M,D,C,Z$.

Transport and replay are then handled by \autoref{thm:separatedcompletion-choice-free-limit-transport}. The rows $H,R,T,P,N$ preserve, replay, source, and name the same boundary for downstream consumers.

Apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, and nonescape, \autoref{thm:separated-completion-nonescape}, to close the package. Since the carrier contains no quotient completion equality, selected representative, host equality, choice schedule, hidden complete metric space, or ambient completeness coordinate, the displayed $U$ row over $M,D,C,Z,H,R,T,P,N$ is the only uniqueness package available.
\end{proof}

\begin{closurestatus}{\SeparatedCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:separated-completion-carrier}, \autoref{thm:separated-completion-namecert-obligations}, \autoref{thm:separated-completion-dense-factorization}, \autoref{thm:separated-completion-uniqueness-boundary}, \autoref{thm:separatedcompletion-cauchy-equivalence-source}, \autoref{thm:separatedcompletion-zero-distance-factorization}, \autoref{thm:separatedcompletion-limit-uniqueness-export}, \autoref{thm:separatedcompletion-dense-uniqueness-interface}, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, and \autoref{thm:separated-completion-nonescape} seed the general separated-completion interface over finite source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, hidden complete metric spaces, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-source compatibility, separated-classifier exactness, uniqueness-boundary exactness, transport replay, and non-escape for BEDC.Derived.SeparatedCompletionUp.}
  \constructivestory{A $\SeparatedCompletionUp$ packet is generated from a source metric row, a dense CompletionEmbedding row, a completion handoff through the DyadicRatCore-StreamName-RegSeqRat-Real L10 spine, a SeparatedMetric classifier, a CompletionUniversalProperty-HausdorffCompletion-RegularCauchyCompletionSeparated uniqueness boundary, componentwise hsame transport, Cont replay, route-preservation ledger, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
