\chapter{A Concrete Naming Certificate for $\PseudometricUp$}
\label{ch:concrete-instances-pseudometric-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\PseudometricUp$ packet records the pre-separated distance surface used by the constructive metric and completion route. It sits before the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the separated reflection of \autoref{ch:concrete-instances-separatedmetric-namecert}, the located-distance interface of \autoref{ch:concrete-instances-locatedmetric-namecert}, and the completion boundary of \autoref{ch:concrete-instances-completion-namecert}. The packet reads dyadic tolerance rows from \autoref{ch:concrete-instances-dyadicratcore-namecert}, finite windows from \autoref{ch:concrete-instances-streamname-namecert}, regular rational readback from \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal distance seal of \autoref{ch:concrete-instances-real-namecert}. Its purpose is to expose distance-zero evidence as finite NameCert data before any consumer turns that evidence into point identity.

\begin{definition}[Pseudometric carrier]
\label{def:pseudometric-carrier}
A $\PseudometricUp$ carrier is a finite $\BHist$ packet
$$
P=(X,M,D,S,R,E,Z,H,C,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the point carrier row. It records the admitted point names and their classifier, but it does not quotient points by zero distance.
\item $M$ is the displayed distance witness. It names the finite comparison surface used to request a distance between two admitted point rows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and triangle ledger. It records dyadic bounds, reflexive zero requests, symmetry swaps, and triangle estimates as displayed comparison rows.
\item $S$ is the $\StreamNameUp$ finite-window row controlling which point-name and distance-name windows may be inspected.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the distance witness, giving regular rational approximants for requested windows.
\item $E$ is the $\RealUp$ distance seal. It is reachable only after $S,R,D$ have displayed the finite readback and tolerance evidence.
\item $Z$ is the zero-distance boundary row. It records that zero distance is a boundary condition on the distance ledger, not an identification of point rows.
\item $H$ records componentwise $\hsame$ transport for the point carrier, distance witness, dyadic ledger, stream windows, regular readback, Real seal, zero-distance boundary, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a consumer request through point admission, stream windows, regular readback, dyadic tolerance and triangle rows, Real distance sealing, and the zero-distance boundary.
\item $N$ is both the $\Pkg$ provenance over the listed BEDC dependencies and the local $\NameCert_{\PseudometricUp}$ row.
\end{enumerate}
The carrier has no coordinate for host equality of points, quotient completion, selected limits, countable choice, trichotomy, open-cover compactness, or a separated reflection.
\end{definition}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricTasteGate\_single\_carrier\_alignment}

\begin{definition}[Pseudometric source carrier]
\label{def:pseudometric-source-carrier}
A $\PseudometricUp$ source carrier is a finite $\BHist$ packet
$$
P_s=(X,M,D,S,R,E,Z,H,C,N)
$$
as in \autoref{def:pseudometric-carrier}, with the additional source-side reading convention that $D$ records metric-like distance rows while permitting zero distance between classifier-distinct point rows of $X$. The rows $S,R,E$ expose the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ readback of each requested distance, while $Z$ records zero-distance evidence as a boundary row. Thus $P_s$ is a source for separated reflection and completion consumers without identifying point names, quotienting the carrier, or importing ambient separated completion.
\end{definition}

\begin{theorem}[Pseudometric source obligation surface]
\label{thm:pseudometric-namecert-obligation-surface}
For every accepted $\PseudometricUp$ source carrier $P_s=(X,M,D,S,R,E,Z,H,C,N)$, the NameCert obligation surface is the conjunction of source carrier admission, dyadic distance readback through $\DyadicRatCoreUp$, finite-window exposure through $\StreamNameUp$, regular rational readback through $\RegSeqRatUp$, terminal distance sealing through $\RealUp$, zero-distance non-identification through $Z$, componentwise transport through $H$, replay through $C$, and local naming through $N$. The surface explicitly refuses quotient equality, host equality, and any ambient $\SeparatedMetricUp$ or $\CompletionUp$ object not routed through these displayed rows.
\end{theorem}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_namecert\_obligation\_surface}
\begin{proof}
Start with the source carrier of \autoref{def:pseudometric-source-carrier}. The tuple contains the point carrier, distance witness, dyadic ledger, finite stream windows, regular rational readback, Real seal, zero-distance row, transport, replay, and local naming row.

The distance side is read in order. A consumer may request a distance through $M$, but the observable data pass through $\DyadicRatCoreUp$ in $D$, the $\StreamNameUp$ windows in $S$, the $\RegSeqRatUp$ readback in $R$, and only then the $\RealUp$ seal in $E$.

The zero-distance side is deliberately separate from identity. The row $Z$ records the boundary condition, while $X$ retains classifier-distinct point rows and $H,C,N$ merely transport, replay, and name the displayed packet.

Therefore a separated metric or completion consumer receives only this source surface. Quotient equality, host equality, and ambient separated completion are absent unless a later $\SeparatedMetricUp$ or $\CompletionUp$ packet adds its own rows.
\end{proof}

\begin{theorem}[Pseudometric separated completion readback]
\label{thm:pseudometric-separated-completion-readback}
Every read from a $\PseudometricUp$ source carrier into a $\SeparatedMetricUp$ or $\CompletionUp$ route factors through
$$
X,M,D,S,R,E,Z,H,C,N .
$$
The $\SeparatedMetricUp$ route may consume $Z$ as zero-distance evidence only after the $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ distance rows have been displayed, and the $\CompletionUp$ route receives the same pre-separated source rows without quotient equality, host equality, selected representatives, selected limits, or ambient separated completion.
\end{theorem}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_zero\_distance\_boundary\_obligation}
\begin{proof}
Project the accepted source carrier. The only distance-read route is $M,D,S,R,E$, with $D$ supplying dyadic tolerance and triangle rows, $S$ supplying finite windows, $R$ supplying regular rational readback, and $E$ supplying the Real distance seal.

For the separated route, $Z$ is read after that distance route as evidence of zero distance. It is not an equality constructor for point rows in $X$, so the separated packet must add its own reflection rows before point identity is available.

For the completion route, the consumer reads the same pre-separated source rows and the structural rows $H,C,N$. Since the carrier has no quotient, representative, limit selector, host equality, or ambient separated-completion coordinate, those objects cannot be exported from the pseudometric source.
\end{proof}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_separated\_completion\_readback}

\begin{theorem}[Pseudometric separated-reflection factorization]
\label{thm:pseudometric-separated-reflection-factorization}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ source carrier. Any $\SeparatedMetricUp$ or $\CompletionUp$ consumer that reads zero-distance evidence from $P$ must first factor through the displayed rows
$$
X,M,D,S,R,E,Z,H,C,N .
$$
Only a later separated-reflection packet may turn the zero-distance boundary row $Z$ into point-identity data; the pseudometric source itself exports no quotient equality, host equality, selected representative, selected limit, or ambient separated completion.
\end{theorem}
\begin{proof}
Project the source carrier of \autoref{def:pseudometric-source-carrier}. The only available rows are the point carrier, distance witness, dyadic tolerance and triangle ledger, finite windows, regular readback, Real seal, zero-distance boundary, transport, replay, and local naming rows.

Apply \autoref{thm:pseudometric-separated-completion-readback}. It forces both separated-metric and completion-facing reads through $X,M,D,S,R,E,Z,H,C,N$ before either consumer can inspect zero-distance evidence.

Use the zero-distance non-identification row. The row $Z$ records boundary evidence on the displayed distance ledger, while point rows remain in $X$ and are transported only by $H$ and replayed only by $C$.

Finally apply the carrier exclusions. Since no quotient equality, host equality, selected representative, selected limit, or ambient separated-completion coordinate occurs in the source packet, identity data can appear only after a later separated-reflection packet supplies its own rows.
\end{proof}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_separated\_reflection\_factorization}

\begin{theorem}[Pseudometric zero-distance scope]
\label{thm:pseudometric-zero-distance-scope}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ source carrier. Zero-distance evidence in $P$ remains scoped to the displayed boundary row $Z$ until a $\SeparatedMetricUp$ consumer supplies its own reflection rows. $\CompletionUp$ and $\LocatedMetricUp$ consumers may consume the distance witness, dyadic ledger, finite windows, regular readback, Real seal, transport, and replay rows, but they cannot turn $Z$ into host equality, quotient equality, or selected representatives.
\end{theorem}
\begin{proof}
Read the source carrier through \autoref{def:pseudometric-source-carrier}. The row $Z$ is part of the displayed pseudometric packet, while point admission remains in $X$ and distance readback remains in $M,D,S,R,E$.

Apply \autoref{thm:pseudometric-separated-completion-readback}. Completion-facing and separated-facing reads must factor through the displayed rows before zero-distance evidence is inspected, and the completion route receives no quotient equality, host equality, selected representative, selected limit, or ambient separated-completion coordinate.

Apply \autoref{thm:pseudometric-separated-reflection-factorization}. The only route that may interpret zero distance as identity is a later separated-reflection packet with its own rows.

Thus a $\CompletionUp$ or $\LocatedMetricUp$ consumer may use the distance and readback data exposed by $M,D,S,R,E,H,C,N$, but $Z$ remains a scoped boundary row. Host equality, quotient equality, and selected representatives are absent until supplied by a distinct $\SeparatedMetricUp$ reflection surface.
\end{proof}

\begin{theorem}[Pseudometric NameCert obligations]
\label{thm:pseudometric-namecert-obligations}
For every accepted $\PseudometricUp$ carrier $P=(X,M,D,S,R,E,Z,H,C,N)$, the local $\NameCert_{\PseudometricUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the point carrier, displayed distance witness, dyadic tolerance and triangle ledger, StreamName windows, RegSeqRat readback, Real distance seal, zero-distance boundary, transport, continuation, provenance, and local naming rows;
\item distance readback, requiring every exported distance request to pass through $S,R,D$ before the Real seal $E$ is read;
\item reflexive, symmetric, and triangle stability, requiring zero self-distance, symmetry transport, and triangle estimates to be displayed as rows of $D$ rather than imported as host metric laws;
\item classifier transport, requiring point and distance classifiers to move only by the componentwise $\hsame$ row $H$ and replay row $C$;
\item zero-distance non-identification, requiring the row $Z$ to record zero distance without equating the two point rows;
\item ledger non-escape, excluding quotient completion, host equality, selected limits, countable-choice selectors, trichotomy, open-cover compactness, and any separated reflection not routed through $\SeparatedMetricUp$.
\end{enumerate}
No pseudometric NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. The tuple lists exactly the point carrier, distance witness, dyadic ledger, stream windows, regular readback, Real seal, zero-distance boundary, transport, continuation, provenance, and local naming rows.

Distance readback follows the replay order in $C$. A consumer first reads the point names and finite stream windows, then the regular rational readback $R$ and dyadic tolerance ledger $D$, and only then reaches the Real seal $E$.

Reflexive, symmetric, and triangle stability are ledger rows. The packet stores self-distance, symmetry, and triangle estimates inside $D$, so no host-level metric law can enter as a detached premise.

Classifier transport is componentwise. The row $H$ transports exactly the displayed coordinates, while $C$ replays them in the same order for consumers.

The zero-distance row $Z$ is separate from point identity. Since $X$ keeps point admission and $Z$ keeps the boundary condition, the certificate exposes zero-distance evidence without identifying the point rows.

The remaining exclusions are immediate from the carrier coordinates. No quotient completion, host equality, selected limit, countable-choice selector, trichotomy, open-cover compactness, or separated reflection appears in $P$, so the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Pseudometric separated reflection handoff]
\label{thm:pseudometric-separated-reflection-handoff}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Any consumer that wants point identity from zero distance must pass through the separated reflection boundary named by $\SeparatedMetricUp$. Consumers for $\CompletionUp$ and $\LocatedMetricUp$ receive only the displayed pseudometric rows $X,M,D,S,R,E,Z,H,C,N$; they receive no quotient completion, host equality, selected limit, countable-choice selector, trichotomy, or open-cover compactness from the pseudometric packet itself.
\end{theorem}
\begin{proof}
Start with a consumer of $P$. Carrier admission exposes the point carrier and distance rows, but the zero-distance row $Z$ is only a boundary row on the displayed distance ledger.

If the consumer asks for point identity, the request is not answered inside $P$. The only named route from zero distance to point identity is the separated reflection interface of $\SeparatedMetricUp$.

Completion and located-distance consumers follow a different boundary. They may read the displayed point, distance, tolerance, stream, readback, Real seal, zero-distance, transport, replay, provenance, and local naming rows, but those rows do not identify points.

Because quotient completion, host equality, selected limits, countable-choice selectors, trichotomy, and open-cover compactness are absent from the carrier, no such datum can be exported along the completion or located-metric route.
\end{proof}

\begin{theorem}[Pseudometric zero-distance completion route]
\label{thm:pseudometric-zero-distance-completion-route}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every zero-distance or completion-facing consumer must read the rows in the order
$$
X\longmapsto M\longmapsto D\longmapsto S\longmapsto R\longmapsto E\longmapsto Z\longmapsto H\longmapsto C\longmapsto N .
$$
The only point-identity boundary available from the zero-distance row is the later $\SeparatedMetricUp$ reflection route of \autoref{thm:pseudometric-separated-reflection-handoff}; the pseudometric packet itself exports no quotient equality, host point equality, selected representative, or ambient separated completion.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. The point admission row $X$ is read before the distance witness $M$, the dyadic tolerance and triangle ledger $D$, the finite stream windows $S$, and the regular-rational readback $R$.

Use \autoref{thm:pseudometric-namecert-obligations}. It binds the terminal Real seal $E$, zero-distance boundary $Z$, componentwise transport $H$, replay $C$, and local naming row $N$ to that same displayed distance route.

Now apply \autoref{thm:pseudometric-separated-reflection-handoff}. A consumer may turn zero-distance evidence into point identity only after reading the separated metric boundary; the pseudometric carrier does not identify the source rows in $X$.

The exclusions follow from the displayed coordinate list. Since no coordinate stores quotient equality, host point equality, selected representatives, or ambient separated completion, a completion-facing consumer receives only the ordered finite route above.
\end{proof}

\begin{theorem}[Pseudometric quotient reflection route]
\label{thm:pseudometric-quotient-reflection-route}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every consumer that tries to turn zero-distance evidence from $P$ into point identity must factor first through the displayed $\SeparatedMetricUp$ reflection boundary and then through the existing $\MetricUp$ and $\CompletionUp$ consumers. The route preserves the rows $X,M,D,S,R,E,Z,H,C,N$ and exports no quotient completion, host equality, selected limit, countable choice, trichotomy, or open-cover compactness from the pseudometric packet itself.
\end{theorem}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_quotient\_reflection\_route}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. Zero-distance evidence is stored in $Z$ after the distance route through $S,R,D,E$, while point admission remains in $X$.

Apply \autoref{thm:pseudometric-separated-reflection-handoff}. It forces any request for point identity from zero distance through the separated reflection boundary named by $\SeparatedMetricUp$ before metric or completion consumers can read the result.

Use \autoref{thm:pseudometric-zero-distance-boundary-obligation}. The zero-distance read is a boundary ledger read through $Z,H,C,N$, so it preserves the displayed pseudometric rows rather than identifying points inside $P$.

Finally apply \autoref{thm:pseudometric-completion-nonescape-obligation}. Completion-facing consumers receive only $X,M,D,S,R,E,Z,H,C,N$ unless a later separated-metric boundary supplies stronger identity data, and the excluded quotient, choice, trichotomy, compactness, and host-equality objects are absent from the packet.
\end{proof}

\begin{theorem}[Pseudometric zero-distance boundary obligation]
\label{thm:pseudometric-zero-distance-boundary-obligation}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every read that treats zero distance as available evidence must pass through the displayed rows $Z,H,C,N$ after the distance request has been routed through $S,R,D,E$. The row $Z$ records a boundary condition on the displayed distance ledger, $H$ records componentwise $\hsame$ transport, $C$ records replay through the same rows, and $N$ records the local $\NameCert$ provenance. No such read identifies point rows in $X$ or exports host equality from zero distance.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. The zero-distance coordinate is $Z$, while point admission remains in $X$ and the distance route is displayed by $M,D,S,R,E$.

The replay row $C$ forces a consumer to read stream windows, regular rational readback, the dyadic distance ledger, and the Real distance seal before reaching $Z$. The transport row $H$ then moves only the displayed coordinates componentwise, and $N$ names the local certificate row for the same packet.

Apply \autoref{thm:pseudometric-separated-reflection-handoff}. It states that point identity from zero distance is not answered inside the pseudometric packet. Therefore $Z,H,C,N$ expose zero-distance evidence as a boundary ledger and do not identify point rows in $X$.
\end{proof}

\begin{theorem}[Pseudometric triangle ledger obligation]
\label{thm:pseudometric-triangle-ledger-obligation}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Symmetry reads and triangle-estimate reads are ledger rows of $D$. Each such read is routed through the $\DyadicRatCoreUp$ tolerance ledger, the $\StreamNameUp$ finite windows, the $\RegSeqRatUp$ readback row, and the terminal $\RealUp$ distance seal before the transport, replay, provenance, and local naming rows are consumed. The packet provides no detached host symmetry law and no ambient metric triangle axiom outside this displayed ledger route.
\end{theorem}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_triangle\_ledger\_obligation}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. The row $D$ is explicitly the tolerance and triangle ledger, and the rows $S,R,E$ are the only displayed route from finite windows and regular rational readback to the Real distance seal.

For a symmetry request, $C$ replays the admitted point rows through $S,R,D,E$ before any structural row is read. The symmetry datum is therefore a row of $D$, transported by $H$ only after the same displayed distance route has been consumed.

For a triangle request, the same ledger row $D$ supplies the dyadic estimates. The consumer then reaches $E$ through $S$ and $R$, and only afterward can read $H,C,N$ as transport, replay, provenance, and naming rows.

Apply \autoref{thm:pseudometric-separated-reflection-handoff}. Since separated identity and completion consumers receive only the displayed pseudometric rows, neither symmetry nor triangle data can enter as a detached host law.
\end{proof}

\begin{theorem}[Pseudometric completion nonescape obligation]
\label{thm:pseudometric-completion-nonescape-obligation}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every $\CompletionUp$ or $\LocatedMetricUp$ consumer receives only the displayed point carrier, distance witness, dyadic ledger, stream windows, regular rational readback, Real distance seal, zero-distance boundary, componentwise transport, continuation replay, provenance, and local naming rows of $P$. The handoff exports no quotient completion, selected representative, trichotomy split, open-cover compactness datum, or separated point identity except through the named $\SeparatedMetricUp$ boundary.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. Its coordinates are exactly $X,M,D,S,R,E,Z,H,C,N$, with no coordinate for a quotient completion, selected representative, trichotomy split, open-cover compactness datum, or separated point identity.

The completion-facing consumer can read distances only through $S,R,D,E$ and can read zero-distance evidence only through $Z,H,C,N$. These are displayed pseudometric rows, not quotient-completion constructors or selectors.

The located-metric consumer receives the same surface. Its distance readbacks are routed through the dyadic, stream, regular rational, and Real rows, while the remaining structural information is componentwise transport, replay, provenance, and local naming.

Apply \autoref{thm:pseudometric-separated-reflection-handoff}. Any conversion from zero distance to point identity is forced through $\SeparatedMetricUp$, so the pseudometric packet itself cannot export separated identity or any of the listed non-displayed principles.
\end{proof}

\begin{theorem}[Pseudometric distance readback obligation]
\label{thm:pseudometric-distance-readback-obligation}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every consumer read of a distance witness must pass through the finite route $S,R,D,E$ before any consumer may read the zero-distance boundary, componentwise transport, replay, provenance, or local naming rows $Z,H,C,N$. The route exposes stream windows, regular rational readback, the dyadic tolerance and triangle ledger, and the terminal $\RealUp$ seal as displayed rows of \autoref{def:pseudometric-carrier}; it exports no detached host distance or ambient metric law.
\end{theorem}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_distance\_readback\_obligation}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. The distance witness is named by $M$, while the observable distance readback is routed through the stream window $S$, regular rational row $R$, dyadic ledger $D$, and Real seal $E$.

Apply \autoref{thm:pseudometric-namecert-obligations}. It lists distance readback as a local obligation requiring every exported distance request to pass through $S,R,D$ before $E$ is read.

The structural rows $Z,H,C,N$ occur after the displayed distance route. Thus a consumer cannot read zero-distance evidence, componentwise transport, replay, provenance, or the local name before the finite distance route has been displayed.

Finally use \autoref{thm:pseudometric-triangle-ledger-obligation}. Symmetry and triangle estimates are rows of $D$, so the readback route does not import a detached host distance or ambient metric law.
\end{proof}

\begin{theorem}[Pseudometric classifier transport obligation]
\label{thm:pseudometric-classifier-transport-obligation}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Point classifiers and distance classifiers transport only componentwise through the $\hsame$ row $H$ and are replayed for consumers only through the displayed $\Cont$ row $C$. The transport reads no quotient completion, selected representative, separated point identity, host equality, or detached metric classifier outside the rows of \autoref{def:pseudometric-carrier}.
\end{theorem}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_classifier\_transport\_obligation}
\begin{proof}
Start from the carrier definition. The row $H$ is the only componentwise transport row for point admission, distance witness, dyadic ledger, stream windows, regular readback, Real seal, zero-distance boundary, continuation, provenance, and local naming.

Apply \autoref{thm:pseudometric-namecert-obligations}. Its classifier-transport clause requires point and distance classifiers to move only by $H$ and replay row $C$.

The replay row $C$ preserves the same order as the displayed distance route. It replays point admission, stream windows, regular readback, dyadic tolerance and triangle rows, Real sealing, and zero-distance boundary evidence before provenance and local naming are consumed.

Apply \autoref{thm:pseudometric-separated-reflection-handoff}. Any conversion of zero distance into separated identity lies outside $P$ and must pass through $\SeparatedMetricUp$, so transport inside $P$ cannot smuggle in quotient completion, selected representatives, host equality, or a detached metric classifier.
\end{proof}

\begin{theorem}[Pseudometric ledger nonescape obligation]
\label{thm:pseudometric-ledger-nonescape-obligation}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Quotient completion, host equality, selected limits, countable choice, trichotomy, open-cover compactness, and separated identity are absent from the pseudometric ledger unless a consumer routes the separated-identity request through $\SeparatedMetricUp$. The only ledger rows available to completion and located-metric consumers are the displayed coordinates $X,M,D,S,R,E,Z,H,C,N$.
\end{theorem}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_ledger\_nonescape\_obligation}
\begin{proof}
Project \autoref{def:pseudometric-carrier}. The tuple contains the point carrier, displayed distance witness, dyadic ledger, stream windows, regular readback, Real seal, zero-distance boundary, transport, replay, provenance, and local naming rows, and it contains no coordinate for the excluded objects.

Apply \autoref{thm:pseudometric-completion-nonescape-obligation}. Completion and located-metric consumers receive only the displayed pseudometric rows and no quotient completion, selected representative, trichotomy split, open-cover compactness datum, or separated point identity except through $\SeparatedMetricUp$.

Apply \autoref{thm:pseudometric-triangle-ledger-obligation}. The metric-law surface is confined to the dyadic ledger $D$ and the route through $S,R,E$, so host equality, countable choice, and ambient metric principles cannot enter through the distance side.

Finally apply \autoref{thm:pseudometric-separated-reflection-handoff}. The only named route from zero distance to point identity is the separated reflection boundary, so separated identity is absent from the pseudometric ledger itself.
\end{proof}

\begin{theorem}[Pseudometric distance source obligation]
\label{thm:pseudometric-distance-source}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. The displayed distance row $M$ is the only source from which a consumer may request pseudometric distance data. Every such request is routed through the finite $\BHist$ rows $S,R,D,E$ and is then accounted for by $\hsame$ transport $H$, $\Cont$ replay $C$, provenance, and the local $\NameCert$ row $N$. No consumer receives a detached host distance or an ambient metric law outside this displayed route.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. The distance witness is the row $M$, while finite windows, regular rational readback, dyadic ledger data, and the Real seal are displayed by $S,R,D,E$.

Apply \autoref{thm:pseudometric-distance-readback-obligation}. It forces every exported distance request through $S,R,D,E$ before the structural rows are read.

The transport and replay rows are then $H$ and $C$, and the local naming row is $N$. Since the carrier has no further distance coordinate, a consumer cannot obtain a detached host distance or ambient metric law from the pseudometric packet.
\end{proof}
\leanchecked{BEDC.Derived.PseudometricUp.PseudometricCarrier\_distance\_source}

\begin{theorem}[Pseudometric kernel route obligation]
\label{thm:pseudometric-kernel-route}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Zero-distance reads and triangle-estimate reads remain kernel ledger reads until a consumer explicitly routes separated point identity through $\SeparatedMetricUp$ and real-valued distance sealing through $\RealUp$. The packet therefore exposes $Z$ and $D$ as displayed evidence rows, not as quotient completion, host equality, or separatedness.
\end{theorem}
\begin{proof}
For zero-distance reads, use \autoref{thm:pseudometric-zero-distance-boundary-obligation}. It routes the read through $S,R,D,E$ and then through $Z,H,C,N$, while leaving point rows in $X$ unidentified.

For triangle-estimate reads, use \autoref{thm:pseudometric-triangle-ledger-obligation}. It keeps symmetry and triangle evidence inside the dyadic ledger $D$ and routes those estimates through the same StreamName, RegSeqRat, and Real rows.

Finally apply \autoref{thm:pseudometric-separated-reflection-handoff}. Point identity from zero distance is not answered inside $P$ and must pass through $\SeparatedMetricUp$, so neither $Z$ nor $D$ can export quotient completion, host equality, or separatedness.
\end{proof}

\begin{theorem}[Pseudometric dependency-ready package]
\label{thm:pseudometric-deps-ready-package}
The $\PseudometricUp$ chapter is dependency-ready for separated-completion and represented-space consumers at the level of displayed rows: it supplies the point carrier $X$, distance witness $M$, dyadic tolerance and triangle ledger $D$, StreamName windows $S$, RegSeqRat readback $R$, Real distance seal $E$, zero-distance boundary $Z$, componentwise transport $H$, replay $C$, provenance, and local naming $N$. This package does not claim separatedness, quotient completion, selected representatives, or completion uniqueness.
\end{theorem}
\begin{proof}
Combine the carrier of \autoref{def:pseudometric-carrier} with the obligations of \autoref{thm:pseudometric-namecert-obligations}. Together they expose the point carrier, distance witness, dyadic ledger, stream windows, regular readback, Real seal, zero-distance boundary, transport, replay, provenance, and local naming rows.

Apply \autoref{thm:pseudometric-distance-source}. It makes the displayed distance row the only source for distance requests and routes every such request through the finite BEDC rows.

Apply \autoref{thm:pseudometric-kernel-route}. It keeps zero-distance and triangle evidence in the displayed ledger until the separated reflection and Real sealing dependencies are read.

The exclusions follow from \autoref{thm:pseudometric-completion-nonescape-obligation}. The packet has no coordinate for separatedness, quotient completion, selected representatives, or completion uniqueness, so downstream consumers receive a dependency-ready surface without those stronger claims.
\end{proof}

\begin{theorem}[Pseudometric dependency unblock surface]
\label{thm:pseudometric-dependency-unblock-surface}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. The rows $X,M,D,S,R,E,Z,H,C,N$ are enough for dependency readiness of separated-completion and located-metric consumers: every such consumer can read point admission, distance source, dyadic tolerance and triangle evidence, finite windows, regular-rational readback, the Real distance seal, zero-distance boundary data, componentwise transport, replay, provenance, and local naming without receiving separated identity, quotient completion, selected representatives, or completion uniqueness.
\end{theorem}
\begin{proof}
First project \autoref{def:pseudometric-carrier}. It displays exactly $X,M,D,S,R,E,Z,H,C,N$ as the point, distance, tolerance, window, readback, Real-seal, zero-distance, transport, replay, provenance, and naming surface.

Apply \autoref{thm:pseudometric-deps-ready-package}. That theorem identifies the same rows as the dependency-ready package available to separated-completion and represented-space consumers.

Finally apply \autoref{thm:pseudometric-completion-nonescape-obligation}. It excludes separatedness, quotient completion, selected representatives, and completion uniqueness from the exported packet unless a later consumer routes a stronger claim through its own named boundary.
\end{proof}

\begin{theorem}[Pseudometric separated-reflection kernel saturation]
\label{thm:pseudometric-separated-reflection-kernel-saturation}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. The zero-distance kernel available to a separated-reflection consumer is saturated by the displayed route
$$
M,D,S,R,E,Z,H,C,N.
$$
That is, every accepted zero-distance read must pass through the distance source, dyadic tolerance and triangle ledger, finite windows, regular-rational readback, Real seal, zero-distance boundary, componentwise $\hsame$ transport, replay, and local naming rows before any $\SeparatedMetricUp$ consumer may inspect it; no quotient equality, host point identity, selected representative, or ambient separated metric row is supplied by $\PseudometricUp$.
\end{theorem}
\begin{proof}
Start with \autoref{thm:pseudometric-dependency-unblock-surface}. It identifies the rows available to separated-completion and located-metric consumers and excludes separated identity and quotient completion from the packet itself.

Apply \autoref{thm:pseudometric-separated-reflection-handoff}. A consumer that wants point identity from zero distance must pass through the later $\SeparatedMetricUp$ boundary after the zero-distance row has been read.

Use \autoref{thm:pseudometric-zero-distance-completion-route}. The zero-distance route is already forced through $M,D,S,R,E,Z,H,C,N$, so the displayed rows saturate the kernel evidence available before separated reflection.
\end{proof}

\begin{theorem}[Pseudometric zero-distance classifier stability]
\label{thm:pseudometric-zero-distance-classifier-stability}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. If two zero-distance reads are transported by the packet's componentwise $\hsame$ row $H$ and replayed by $C$, then their classifier-visible content remains the same displayed boundary route $M,D,S,R,E,Z,H,C,N$. The classifier may preserve the zero-distance evidence as a row of $Z$, but it cannot convert that evidence into point identity until a $\SeparatedMetricUp$ boundary is read.
\end{theorem}
\begin{proof}
Project the classifier transport obligation through \autoref{thm:pseudometric-classifier-transport-obligation}. The only transport rows available to point and distance classifiers are the displayed $\hsame$ row $H$ and replay row $C$.

Now use \autoref{thm:pseudometric-zero-distance-boundary-obligation}. Zero-distance evidence is a boundary row tied to the distance route through $S,R,D,E$ and then to $Z,H,C,N$.

Finally apply \autoref{thm:pseudometric-separated-reflection-kernel-saturation}. Since the saturated route contains no point-identity coordinate, classifier stability preserves the finite zero-distance row without adding separated equality.
\end{proof}

\begin{theorem}[Pseudometric completion universal handoff]
\label{thm:pseudometric-completion-universal-handoff}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every completion-facing consumer receives $P$ through the universal pre-separated handoff consisting of the displayed rows $X,M,D,S,R,E,Z,H,C,N$, followed only by the external $\SeparatedMetricUp$ and $\CompletionUp$ rows supplied by that consumer. The handoff carries zero-distance and distance-readback evidence, but it does not create completion points, identify quotient classes, select limits, or assert host equality inside $\PseudometricUp$.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:pseudometric-deps-ready-package}. It packages the point carrier, distance witness, dyadic ledger, StreamName windows, RegSeqRat readback, Real seal, zero-distance boundary, transport, replay, provenance, and local naming rows as the dependency-ready surface.

Use \autoref{thm:pseudometric-zero-distance-classifier-stability}. The zero-distance row remains stable under the displayed classifier transport, so completion consumers receive a coherent pre-separated source rather than a quotient construction.

Apply \autoref{thm:pseudometric-separated-completion-source}. Separated identity and completion points enter only through later $\SeparatedMetricUp$ and $\CompletionUp$ boundaries. The pseudometric packet therefore provides the universal handoff route without supplying selected limits, quotient classes, or host point equality.
\end{proof}

\begin{theorem}[Pseudometric separated-completion source]
\label{thm:pseudometric-separated-completion-source}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Any separated-completion consumer that treats zero distance as point identity must route that identity claim through $\SeparatedMetricUp$ after reading the displayed zero-distance boundary $Z$. The pseudometric packet itself supplies only the pre-separated source rows $X,M,D,S,R,E,Z,H,C,N$ and exports no host equality, quotient completion class, selected representative, or separated completion point.
\end{theorem}
\begin{proof}
Start with \autoref{thm:pseudometric-zero-distance-boundary-obligation}. It makes zero-distance evidence a read of $Z,H,C,N$ after the distance route has passed through $S,R,D,E$.

Next use \autoref{thm:pseudometric-separated-reflection-handoff}. It states that point identity from zero distance is not answered inside the pseudometric packet and must pass through the separated reflection boundary named by $\SeparatedMetricUp$.

The completion-side exclusions then follow from \autoref{thm:pseudometric-completion-nonescape-obligation}. Since host equality, quotient completion classes, selected representatives, and separated completion points are absent from the carrier, the separated-completion consumer receives only the displayed pre-separated source rows.
\end{proof}

\begin{theorem}[Pseudometric separated-reflection source]
\label{thm:pseudometric-separated-reflection-source}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every $\SeparatedReflectionUp$ consumer receives the source only through the displayed rows of \autoref{def:pseudometric-carrier}: point admission $X$, distance witness $M$, dyadic tolerance and triangle ledger $D$, StreamName windows $S$, RegSeqRat readback $R$, Real seal $E$, zero-distance boundary $Z$, componentwise transport $H$, replay $C$, provenance, and local naming $N$. In particular, the consumer may use zero-distance evidence only through \autoref{thm:pseudometric-zero-distance-boundary-obligation} and \autoref{thm:pseudometric-separated-reflection-handoff}; it receives no point identity, quotient class, selected representative, or host equality before $\SeparatedMetricUp$ supplies a stronger boundary.
\end{theorem}
\begin{proof}
Project the carrier rows from \autoref{def:pseudometric-carrier}. They are exactly $X,M,D,S,R,E,Z,H,C,N$, so a separated-reflection consumer has no other coordinate to inspect.

Apply \autoref{thm:pseudometric-zero-distance-boundary-obligation}. It keeps zero-distance evidence in the displayed $Z,H,C,N$ route after the distance read has passed through $S,R,D,E$.

Finally use \autoref{thm:pseudometric-separated-reflection-handoff} and \autoref{thm:pseudometric-completion-nonescape-obligation}. The first theorem forces any identity request through $\SeparatedMetricUp$, and the second excludes quotient classes, selected representatives, and host equality from the pseudometric packet.
\end{proof}

\begin{theorem}[Pseudometric pre-separated completion source]
\label{thm:pseudometric-preseparated-completion-source}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. A completion consumer that has not yet read a $\SeparatedMetricUp$ or $\CompletionUp$ boundary can use $P$ only as a pre-separated source: it may read the displayed distance, tolerance, finite-window, regular-rational, Real-seal, zero-distance, transport, replay, provenance, and naming rows, but it cannot read separated completion points, completion uniqueness, quotient completion, selected limits, host equality, or ambient $\RealUp$ completeness from $P$.
\end{theorem}
\begin{proof}
The pre-separated source is the carrier of \autoref{def:pseudometric-carrier}. Its displayed rows provide distance witnesses, tolerance and triangle ledgers, finite windows, regular-rational readback, Real sealing, zero-distance boundary data, transport, replay, provenance, and local naming.

Use \autoref{thm:pseudometric-separated-reflection-handoff}. Any move from zero distance to point identity is outside $P$ until the separated metric boundary is read.

Use \autoref{thm:pseudometric-completion-nonescape-obligation}. Completion uniqueness, quotient completion, selected limits, host equality, and ambient $\RealUp$ completeness are absent from the packet, so a completion consumer must wait for $\CompletionUp$ or a later named completion boundary to supply them.
\end{proof}

\begin{theorem}[Pseudometric located-metric source exhaustion]
\label{thm:pseudometric-located-metric-source-exhaustion}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every located-metric consumer of $P$ exhausts the available source data by reading the displayed distance source $M$, dyadic tolerance and triangle ledger $D$, StreamName windows $S$, RegSeqRat readback $R$, Real seal $E$, zero-distance boundary $Z$, and structural rows $H,C,N$. After these rows are read, no further located-metric structure remains in $P$; stronger separatedness, completion, host-equality, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness claims must come from $\SeparatedMetricUp$, $\CompletionUp$, or another named consumer boundary.
\end{theorem}
\begin{proof}
Begin with \autoref{def:pseudometric-carrier}. The only located-metric-facing coordinates are the displayed distance source, tolerance and triangle ledger, finite windows, regular-rational readback, Real seal, zero-distance boundary, and structural rows.

Apply \autoref{thm:pseudometric-zero-distance-boundary-obligation}. It identifies the zero-distance part of this surface as boundary evidence rather than separated identity.

Then apply \autoref{thm:pseudometric-separated-reflection-handoff} and \autoref{thm:pseudometric-completion-nonescape-obligation}. They force stronger separated or completion claims outside the pseudometric packet and leave the listed rows as the exhausted located-metric source surface.
\end{proof}

\begin{theorem}[Pseudometric located-metric readiness]
\label{thm:pseudometric-located-metric-readiness}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every located-metric consumer of $P$ reads only the displayed distance source $M$, the dyadic tolerance ledger $D$, the finite window row $S$, the regular-rational readback $R$, the terminal $\RealUp$ distance seal $E$, and the structural rows $H,C,N$. It receives no detached host distance, ambient metric law, trichotomy split, open-cover compactness datum, quotient completion, or separated point identity from the pseudometric packet.
\end{theorem}
\begin{proof}
Apply \autoref{thm:pseudometric-distance-source}. It names $M$ as the only source for pseudometric distance requests and routes every such request through $S,R,D,E$ before the structural rows are read.

Use \autoref{thm:pseudometric-distance-readback-obligation}. The readback route exposes finite windows, regular rational readback, dyadic tolerance and triangle data, and the terminal $\RealUp$ seal as displayed rows rather than as detached host distance data.

Finally apply \autoref{thm:pseudometric-ledger-nonescape-obligation}. The located-metric consumer receives only the displayed ledger rows and cannot extract ambient metric laws, trichotomy, open-cover compactness, quotient completion, or separated point identity from the pseudometric packet.
\end{proof}

\begin{theorem}[Pseudometric finite-window distance route]
\label{thm:pseudometric-finite-window-distance-route}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every finite distance read exported by $P$ is routed through the carrier row $X$, the displayed distance source $M$, the dyadic tolerance and triangle ledger $D$, the finite-window row $S$, the regular-rational readback row $R$, the terminal $\RealUp$ seal $E$, the zero-distance boundary $Z$, and the structural rows $H,C,N$. The route is exactly the distance-readback surface of \autoref{thm:pseudometric-distance-readback-obligation} together with the triangle-ledger control of \autoref{thm:pseudometric-triangle-ledger-obligation}, and it does not expose a detached host distance, separated point identity, quotient completion, selected limit, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with the carrier projection of \autoref{def:pseudometric-carrier}. The accepted packet gives the rows $X,M,D,S,R,E,Z,H,C,N$ and no additional distance coordinate.

Apply \autoref{thm:pseudometric-distance-readback-obligation}. A distance request must pass through the finite windows $S$, the regular-rational readback $R$, the dyadic ledger $D$, and the terminal seal $E$ before the structural rows can package the read.

Apply \autoref{thm:pseudometric-triangle-ledger-obligation}. The same ledger row $D$ is the only triangle-facing control row, so finite-window distance reads and triangle comparisons share the displayed tolerance route rather than splitting into a host metric law.

Finally use \autoref{thm:pseudometric-completion-nonescape-obligation}. Completion, selected-limit, host-equality, and ambient-completeness claims are outside the pseudometric packet, while $Z$ remains only the zero-distance boundary available for later separated reflection.
\end{proof}

\begin{theorem}[Pseudometric zero-distance separated-reflection exactness]
\label{thm:pseudometric-zero-distance-separated-reflection-exactness}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. The zero-distance row $Z$ is the exact boundary offered to separated-reflection consumers: it can be transported with $H$, replayed through $C$, packaged by the local naming row $N$, and compared with the distance-readback route $M,D,S,R,E$, but it becomes separated point identity only after the consumer reads the $\SeparatedMetricUp$ boundary named in \autoref{thm:pseudometric-separated-reflection-handoff}. The packet therefore exposes zero-distance evidence without quotient completion, selected limits, host equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the rows of $P$. The zero-distance row $Z$ is present beside the distance source $M$, tolerance ledger $D$, finite windows $S$, regular readback $R$, and Real seal $E$.

Use \autoref{thm:pseudometric-distance-readback-obligation} to align $Z$ with the displayed distance route. The row can be inspected only against the same finite-window and dyadic readback surface that supplies distance evidence.

Now apply \autoref{thm:pseudometric-separated-reflection-handoff}. That theorem places separated point identity beyond the pseudometric packet, at the later separated metric boundary, so $Z$ is exact as boundary evidence and not as identity in $X$.

The non-escape clause follows from \autoref{thm:pseudometric-completion-nonescape-obligation}. Rows $H,C,N$ preserve and name the boundary route, but no row stores quotient completion, selected limits, host equality, countable choice, or ambient completeness.
\end{proof}

\begin{theorem}[Pseudometric triangle separated-reflection compatibility]
\label{thm:pseudometric-triangle-separated-reflection-compatibility}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. The triangle information carried by $D$ is compatible with separated reflection exactly along the displayed route $M,D,S,R,E,Z,H,C,N$: triangle comparisons are read through the same finite-window and regular-rational distance surface as zero-distance evidence, and any separated identity conclusion must pass through \autoref{thm:pseudometric-separated-reflection-handoff}. The compatibility claim uses the distance-readback obligation, triangle-ledger obligation, and completion non-escape boundary, and it does not add an ambient metric law, quotient completion, selected limit, host equality, trichotomy split, or open-cover compactness datum.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:pseudometric-triangle-ledger-obligation}. It identifies the triangle-facing content of $P$ with the dyadic ledger row $D$, not with an external metric law.

Apply \autoref{thm:pseudometric-distance-readback-obligation}. The triangle comparison and the zero-distance comparison both read the finite windows $S$, regular-rational readback $R$, dyadic tolerance row $D$, and terminal Real seal $E$.

Use \autoref{thm:pseudometric-separated-reflection-handoff} for the separated boundary. If a consumer turns zero-distance evidence into point identity, that step is performed by the separated metric route, not by the pseudometric carrier itself.

Finally invoke \autoref{thm:pseudometric-completion-nonescape-obligation}. The same structural rows $H,C,N$ preserve the displayed compatibility route while refusing quotient completion, selected limits, host equality, trichotomy, open-cover compactness, and ambient Real completeness.
\end{proof}

\begin{theorem}[Pseudometric zero-distance source reflection]
\label{thm:pseudometric-zero-distance-source-reflection}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Every accepted zero-distance read from $Z$ factors through the displayed $\DyadicRatCoreUp$ tolerance and triangle ledger $D$, the $\StreamNameUp$ finite windows $S$, the $\RegSeqRatUp$ readback row $R$, the terminal $\RealUp$ seal $E$, the separated-reflection boundary of \autoref{thm:pseudometric-zero-distance-separated-reflection-exactness}, and the completion source route of \autoref{thm:pseudometric-preseparated-completion-source} before any $\MetricUp$ consumer may read it as identity-like evidence. The source reflection is transported only by $H$, replayed only by $C$, and packaged only by the local $\Pkg$ and $\NameCert$ rows; it does not assert quotient identity, separated metric equality, host equality, selected limits, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:pseudometric-zero-distance-separated-reflection-exactness}. It identifies $Z$ as exact boundary evidence and places separated point identity beyond the pseudometric packet.

Use \autoref{thm:pseudometric-triangle-separated-reflection-compatibility}. The zero-distance read and the triangle comparison share the displayed route through $D,S,R,E,Z,H,C,N$, so the source reflection remains tied to dyadic tolerance, finite windows, regular readback, and the Real seal.

Apply \autoref{thm:pseudometric-preseparated-completion-source}. Completion-facing consumers must first read the same pre-separated source rows before any metric or separated completion route can consume the evidence.

Finally project the structural rows. The $\BHist$ packet, $H$, $C$, local $\Pkg$, and $\NameCert$ rows carry the source reflection, while the carrier has no coordinate for quotient identity, separated metric equality, host equality, selected limits, countable choice, or ambient completeness.
\end{proof}

\begin{theorem}[Pseudometric kernel source carrier]
\label{thm:pseudometric-kernel-source-carrier}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. The concrete source carrier available to every root-unblock consumer is exactly the finite $\BHist$ carrier row $X$ together with the displayed distance source $M$, dyadic tolerance and triangle ledger $D$, finite $\StreamNameUp$ windows $S$, regular-rational readback $R$, terminal $\RealUp$ seal $E$, zero-distance boundary $Z$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, package provenance, and local $\NameCert$ row $N$. No consumer may replace this source by a host point set, quotient carrier, separated reflection, selected completion point, or ambient metric object.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:pseudometric-carrier}. The tuple displays exactly the rows $X,M,D,S,R,E,Z,H,C,N$, so the source carrier is a finite BEDC packet rather than an external set of points.

Apply \autoref{thm:pseudometric-zero-distance-source-reflection}. It routes every zero-distance source read through the dyadic ledger, stream windows, regular readback, Real seal, and structural rows before any metric-like consumer can inspect it.

Use \autoref{thm:pseudometric-completion-nonescape-obligation}. The excluded host point set, quotient carrier, selected completion point, separated reflection, and ambient metric object are absent from the carrier inventory, so the displayed rows exhaust the root-unblock source.
\end{proof}

\begin{theorem}[Pseudometric classifier stability]
\label{thm:pseudometric-classifier-stability}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. Classifier transport for point rows and zero-distance rows is stable exactly along the displayed $\hsame$ and $\Cont$ route $H,C$: if two accepted reads share the same finite $\BHist$ carrier row $X$ and the same transported zero-distance boundary $Z$, then any classifier comparison offered to a $\MetricUp$, $\SeparatedMetricUp$, or completion-facing consumer must pass through $M,D,S,R,E,Z,H,C,N$. The comparison may cite the zero-distance row, but it cannot identify point names until the separated-reflection handoff is displayed.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:pseudometric-classifier-transport-obligation}. It confines point and distance classifier transport to the componentwise $\hsame$ row $H$ and the displayed replay row $C$.

Next read the zero-distance route through \autoref{thm:pseudometric-zero-distance-separated-reflection-exactness}. The row $Z$ is boundary evidence aligned with $M,D,S,R,E$, not an equality row for point names in $X$.

Finally apply \autoref{thm:pseudometric-separated-reflection-handoff}. A separated identity conclusion belongs to the later separated metric boundary. Thus classifier stability is available to consumers as a transported finite row, while point identification remains outside the pseudometric packet.
\end{proof}

\begin{theorem}[Pseudometric separated quotient handoff]
\label{thm:pseudometric-separated-quotient-handoff}
Let $P=(X,M,D,S,R,E,Z,H,C,N)$ be an accepted $\PseudometricUp$ packet. The separated quotient handoff ledger offered by $P$ is the displayed route from $X$ through $M,D,S,R,E,Z,H,C,N$ to the separated-reflection boundary of \autoref{thm:pseudometric-separated-reflection-handoff} and the completion source of \autoref{thm:pseudometric-preseparated-completion-source}. The handoff supplies source rows for later separated reflection and completion consumers, but it does not form quotient classes, choose representatives, assert host equality, or close separated point identity inside $\PseudometricUp$.
\end{theorem}
\begin{proof}
Start with \autoref{thm:pseudometric-kernel-source-carrier}. It fixes the source carrier as the displayed finite packet $X,M,D,S,R,E,Z,H,C,N$.

Use \autoref{thm:pseudometric-classifier-stability}. Classifier comparisons and zero-distance boundary rows are transported only through $H$ and replayed only through $C$, so the handoff is a ledger route rather than a quotient construction.

Now apply \autoref{thm:pseudometric-separated-reflection-handoff} and \autoref{thm:pseudometric-preseparated-completion-source}. These theorems route separated reflection and completion consumers through the displayed source rows while keeping quotient classes, selected representatives, host equality, and separated point identity outside the pseudometric packet.
\end{proof}

\begin{closurestatus}{\PseudometricUp}
  \constructivestory{A $\PseudometricUp$ packet is generated from point carrier rows, displayed distance witnesses, DyadicRatCore tolerance and triangle ledgers, StreamName windows, RegSeqRat readback, a Real distance seal, a zero-distance boundary row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:pseudometric-carrier}, \autoref{thm:pseudometric-namecert-obligations}, \autoref{thm:pseudometric-distance-readback-obligation}, \autoref{thm:pseudometric-triangle-ledger-obligation}, \autoref{thm:pseudometric-classifier-transport-obligation}, and \autoref{thm:pseudometric-completion-nonescape-obligation} expose the obligation surface for the pre-separated distance interface before separated reflection or completion consumers read it.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close separated point identity, quotient completion, host equality, selected limits, countable choice, trichotomy, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, distance readback, reflexive and symmetric and triangle stability, classifier transport, zero-distance non-identification, and ledger refusal for BEDC.Derived.PseudometricUp.}
\end{closurestatus}
