\chapter{A Concrete Naming Certificate for $\RegularCauchyCofinalRateUp$}
\label{ch:concrete-instances-regular-cauchy-cofinal-rate-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RegularCauchyCofinalRateUp$ packet records the finite cofinal-rate surface used when a regular rational stream must answer every later precision request through an explicit late-window route. It sits between the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the effective threshold surface of \autoref{ch:concrete-instances-cauchyrate-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet records a displayed cofinal-rate row and its finite handoff to the Real boundary; it is not a quotient of streams, a selected real value, a host metric limit, countable choice, or ambient completeness of $\RealUp$.

\begin{definition}[Regular Cauchy cofinal-rate carrier]
\label{def:regular-cauchy-cofinal-rate-carrier}
A $\RegularCauchyCofinalRateUp$ carrier is a finite $\BHist$ packet
$$
G=(R,K,W,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RegSeqRatUp$ source row whose regular rational approximants are the only numeric data read by the packet.
\item $K$ is the cofinal rate row, read through the $\CauchyRateUp$ surface and assigning to each displayed dyadic tolerance a late stream stage sufficient for all later windows.
\item $W$ is the $\StreamNameUp$ finite-window row reached at and beyond the stage named by $K$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger through which every requested radius is named before the cofinal row is inspected.
\item $Q$ is the RegSeqRat readback row, exposing the regular rational comparison certified by $R,W,D,K$.
\item $E$ is the $\RealUp$ seal row, available only after the source, rate, window, tolerance, and readback rows have been replayed.
\item $H$ records componentwise $\hsame$ transport for the RegSeqRat source, cofinal rate, StreamName windows, DyadicRatCore ledger, readback, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a precision request through dyadic tolerance naming, cofinal-rate lookup, stream-window extraction, regular rational readback, and Real seal handoff.
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\CauchyRateUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyCofinalRateUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $R,K,W,D,Q,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, host real equality, trichotomy, countable-choice schedules, or ambient Real completeness.
\end{definition}

\begin{theorem}[Regular Cauchy cofinal-rate NameCert obligations]
\label{thm:regular-cauchy-cofinal-rate-namecert-obligations}
For every accepted $\RegularCauchyCofinalRateUp$ carrier $G=(R,K,W,D,Q,E,H,C,P,N)$, the local $\NameCert_{\RegularCauchyCofinalRateUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the RegSeqRat source, cofinal rate, StreamName windows, DyadicRatCore tolerance ledger, RegSeqRat readback, Real seal, transport, continuation, provenance, and local naming row;
\item tolerance-first routing, requiring each precision request to enter through $D$ before the cofinal stage in $K$ is read;
\item cofinal window exactness, requiring $K$ to name a late stage after which $W$ supplies every finite stream window consumed by the readback row;
\item readback stability, requiring $Q,H,C$ to preserve the regular rational comparison under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item Real seal handoff, requiring $E$ to be downstream of $R,K,W,D,Q$ and to expose no quotient stream, selected limit, host equality, trichotomy, countable-choice selector, or ambient completeness principle.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-cofinal-rate-carrier}. The projection exposes exactly the RegSeqRat source row, cofinal rate row, StreamName window row, DyadicRatCore ledger, readback row, Real seal, and structural rows $H,C,P,N$.

Tolerance-first routing follows from the order recorded by $C$. A precision request must name its radius through $D$ before the cofinal rate row $K$ can select the late stage.

The selected stage then controls the visible stream data. The window row $W$ supplies only finite StreamName observations at and beyond the stage named by $K$, and the readback row $Q$ consumes those observations with the source row $R$.

Transport and replay cannot add further obligations. The rows $H$ and $C$ preserve the displayed route, while $P$ and $N$ name the same finite packet.

Since quotient streams, selected limits, host equality, trichotomy, choice schedules, and ambient completeness data are absent from the carrier, the Real seal row $E$ has no path to export them.
\end{proof}

\begin{theorem}[Regular Cauchy cofinal-rate downstream route]
\label{thm:regular-cauchy-cofinal-rate-downstream-route}
Let $G=(R,K,W,D,Q,E,H,C,P,N)$ be an accepted $\RegularCauchyCofinalRateUp$ carrier. Every downstream consumer of the readback row factors through the finite route
$$
D \longmapsto K \longmapsto W \longmapsto R \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Consequently the consumer receives a dyadic tolerance name and a cofinal late-stage witness before it can read any regular rational comparison or Real seal.
\end{theorem}
\begin{proof}
Begin with a downstream consumer of the readback row. Carrier admission exposes $Q$ only as a row in the displayed packet, not as an independent comparison principle.

Replay the continuation row $C$. The replay first names the requested tolerance by $D$ and then reads the cofinal rate row $K$ for the late stage attached to that tolerance.

The StreamName row $W$ is available only after the cofinal stage is fixed. The RegSeqRat source row $R$ is then read through those finite windows, and the readback row $Q$ records the resulting regular rational comparison.

The Real seal row $E$ and structural rows $H,C,P,N$ are downstream of the same route. Thus no consumer reaches $Q$ or $E$ without first receiving the dyadic tolerance name and cofinal late-stage witness.
\end{proof}

\begin{theorem}[Regular Cauchy cofinal-rate Real seal handoff]
\label{thm:regular-cauchy-cofinal-rate-real-seal-handoff}
Let $G=(R,K,W,D,Q,E,H,C,P,N)$ be an accepted $\RegularCauchyCofinalRateUp$ carrier. Every $\RealUp$-facing read of $G$ reaches the seal row $E$ only after replaying the RegSeqRat source, cofinal rate, StreamName windows, DyadicRatCore tolerance ledger, and RegSeqRat readback rows. The exported surface contains no quotient stream, selected limit, host real equality, trichotomy, countable-choice selector, or ambient Real completeness assertion.
\end{theorem}
\begin{proof}
The Real seal row $E$ is part of the carrier, but its accessibility is ordered by the continuation row $C$. A Real-facing read must therefore replay the tolerance ledger $D$, the cofinal rate row $K$, the finite window row $W$, the source row $R$, and the readback row $Q$ before the seal is available.

Componentwise transport through $H$ preserves the same row inventory. It can identify accepted packets along displayed $\hsame$ coordinates, but it cannot introduce a quotient stream, selected limit, host equality, trichotomy, choice schedule, or completeness theorem.

The provenance and local naming rows $P,N$ certify the same finite packet. Hence the Real seal is a downstream handoff surface for regular Cauchy cofinal-rate data, not an appeal to ambient Real completeness.
\end{proof}

\closureat{RegularCauchyCofinalRateUp}{seedStr}

\begin{closurestatus}{\RegularCauchyCofinalRateUp}
  \constructivestory{A $\RegularCauchyCofinalRateUp$ packet is generated from a RegSeqRat source row, cofinal CauchyRate row, finite StreamName windows, DyadicRatCore tolerance ledger, RegSeqRat readback row, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-cofinal-rate-carrier}, \autoref{thm:regular-cauchy-cofinal-rate-namecert-obligations}, \autoref{thm:regular-cauchy-cofinal-rate-downstream-route}, and \autoref{thm:regular-cauchy-cofinal-rate-real-seal-handoff} seed the finite cofinal-rate route from dyadic tolerance requests through StreamName windows, RegSeqRat readback, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, host real equality, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tolerance-first routing, cofinal window exactness, readback stability, Real seal handoff, and ledger refusal proofs for BEDC.Derived.RegularCauchyCofinalRateUp.}
\end{closurestatus}
