\chapter{A Concrete Naming Certificate for $\LipschitzMapUp$}
\label{ch:concrete-instances-lipschitzmap-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, a metric
Lipschitz map is useful only when its bound is carried as explicit data. The
$\LipschitzMapUp$ interface records that data as a finite BEDC packet: source
and target $\MetricSpaceUp$ rows, a $\RealUp$-valued rational Lipschitz-bound
ledger, a $\ContinuousMapUp$ graph row, a $\UniformModulusUp$ row induced by the
bound, componentwise $\hsame$ transports, visible $\Cont$ routes, $\Pkg$
provenance, and a local $\NameCert$ row. The packet is a connector for
$\UniformModulusUp$, $\PicardContractionUp$, $\BanachFixedPointUp$, and
$\ContinuousMapUp$ consumers; it is not a Banach fixed-point theorem, a
completeness claim, differentiability data, or host function extensionality.

The sibling dependency route is explicit. A $\LipschitzMapUp$ packet consumes
the source and target metric rows from \autoref{ch:concrete-instances-metric-namecert},
the graph row from \autoref{ch:concrete-instances-continuousmap-namecert}, and
the induced modulus row from \autoref{ch:concrete-instances-uniformmodulus-namecert}.
Its bound ledger is read through the $\RealUp$ surface of
\autoref{ch:concrete-instances-real-namecert}. The fixed-point consumers in
\autoref{ch:concrete-instances-picardcontraction-namecert} and
\autoref{ch:concrete-instances-banach-fixed-point-namecert} read the same bound
ledger as their contraction witness surface, so the Lipschitz packet is the
bound-carrying connector between metric, continuity, modulus, real-bound, and
fixed-point certificates.

\begin{definition}[LipschitzMap carrier]
\label{def:lipschitz-map-carrier}
A $\LipschitzMapUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $X$ is the source $\MetricSpaceUp$ row;
\item $Y$ is the target $\MetricSpaceUp$ row;
\item $B$ is a rational Lipschitz-bound ledger, read as a $\RealUp$-valued
nonnegative bound row for target distances;
\item $G$ is the $\ContinuousMapUp$ graph row for the carried map;
\item $M$ is the $\UniformModulusUp$ modulus row induced by the displayed bound
ledger;
\item $H$ records componentwise $\hsame$ transports for source points, target
points, distance rows, the bound ledger, graph rows, and modulus rows;
\item $C$ records the $\Cont$ routes by which consumers read source distances,
target distances, the Lipschitz-bound comparison, the graph row, and the
uniform-modulus row;
\item $P$ records $\Pkg$ provenance for $\MetricSpaceUp$, $\RealUp$,
$\ContinuousMapUp$, $\UniformModulusUp$, $\PicardContractionUp$, $\mathsf{BHist}$,
$\hsame$, $\Cont$, and $\NameCert$ dependency rows;
\item $N$ is the local $\NameCert_{\LipschitzMapUp}$ provenance row.
\end{enumerate}
The carrier accepts exactly those packets whose displayed graph reads and
metric-distance rows are bounded by the ledger $B$ and whose modulus row $M$ is
the finite uniform-modulus route induced by that same bound.
\end{definition}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_semantic\_carrier\_package}

\begin{definition}[LipschitzMap classifier]
\label{def:lipschitz-map-classifier}
For accepted $\LipschitzMapUp$ carriers
$$
L=(X,Y,B,G,M,H,C,P,N)
\quad\text{and}\quad
L'=(X',Y',B',G',M',H',C',P',N'),
$$
the classifier compares source and target metric-space rows, rational
bound-ledger rows, graph rows, induced uniform-modulus rows, transport rows,
continuation routes, package provenance, and local certificate rows
componentwise through the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
surface.

It does not compare host functions extensionally, form a quotient of maps,
choose representatives, assert completeness of either metric space, or infer
differentiability.
\end{definition}
\leandef{BEDC.Derived.LipschitzMapUp.LipschitzMapClassifier}

\begin{theorem}[LipschitzMap NameCert obligations]
\label{thm:lipschitz-map-namecert-obligations}
The local $\NameCert_{\LipschitzMapUp}$ seed surface consists of five finite
obligations:
\begin{enumerate}
\item carrier: the packet of \autoref{def:lipschitz-map-carrier};
\item classifier: the componentwise comparison of
\autoref{def:lipschitz-map-classifier};
\item stability: $\hsame$ and $\Cont$ transport preserve the source and target
metric rows, bound ledger, graph row, and induced modulus row;
\item exactness: every target-distance read factors through the source-distance
read, the displayed rational bound ledger, and the graph row;
\item ledger policy: $\Pkg$ and $\NameCert$ expose only the listed metric,
real-bound, continuous-map, uniform-modulus, transport, and continuation rows.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_namecert\_obligation\_certificate}
\begin{proof}
Project the carrier. The source and target metric rows, rational bound ledger,
graph row, induced modulus row, transport rows, continuation routes, package
provenance, and local certificate row are exactly the visible coordinates.

The classifier is componentwise by definition, so stability is obtained by
moving each displayed coordinate through the stored $\hsame$ rows and then
following the stored $\Cont$ routes. This preserves the order from source
distance to graph read to target distance and bound comparison.

Exactness follows because the target-distance row has no source except the
graph row applied to source points and the bound ledger read against the
source-distance row. The package and local certificate rows list no host
function equality, completeness principle, differentiability datum, or chosen
representative, so the ledger policy is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[LipschitzMap composition boundary]
\label{thm:lipschitz-map-composition-boundary}
Let $L$ and $L'$ be accepted $\LipschitzMapUp$ carriers whose target
$\MetricSpaceUp$ row of $L$ is classifier-compatible with the source
$\MetricSpaceUp$ row of $L'$. The composite consumer route is bounded by the
displayed product of the two rational Lipschitz ledgers, reads the composite
graph through the two $\ContinuousMapUp$ rows, and induces the composite
$\UniformModulusUp$ row through the two visible modulus routes.

The boundary is a finite consumer boundary: it does not assert completeness,
fixed points, differentiability, or host-level equality of composite functions.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_composition\_boundary}
\begin{proof}
Read the first carrier through its source metric row, graph row, target metric
row, and rational bound ledger. The target row is classifier-compatible with the
source row of the second carrier, so the intermediate metric observation is a
visible carried row rather than a host equality.

Read the second carrier through its graph row and bound ledger. The target
distance of the second read is bounded by the second ledger applied to the
intermediate distance, while the intermediate distance is bounded by the first
ledger applied to the original source distance.

Repack the two bound reads as the displayed product ledger and route the graph
reads through the two $\ContinuousMapUp$ rows. The induced modulus route is the
sequential use of the two $\UniformModulusUp$ rows, and the exclusions follow
because neither carrier contains completeness, fixed-point, differentiability,
or host function-extensionality coordinates.
\end{proof}

\begin{theorem}[LipschitzMap ledger nonescape]
\label{thm:lipschitz-map-ledger-nonescape}
Every $\UniformModulusUp$, $\PicardContractionUp$, $\BanachFixedPointUp$, or
$\ContinuousMapUp$ consumer of an accepted $\LipschitzMapUp$ carrier factors
through the displayed source and target $\MetricSpaceUp$ rows, rational
$\RealUp$ bound ledger, $\ContinuousMapUp$ graph row, $\UniformModulusUp$ row,
componentwise $\hsame$ transports, visible $\Cont$ routes, $\Pkg$ provenance,
and local $\NameCert$ row.

No consumer can obtain a Banach fixed-point conclusion, completeness witness,
differentiability row, quotient of maps, selected representative, or host
function extensionality from the Lipschitz ledger alone.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_uniform\_modulus\_boundary}
\begin{proof}
Use the obligation surface of
\autoref{thm:lipschitz-map-namecert-obligations}. It lists the carrier,
classifier, stability, exactness, and ledger rows available to every local
certificate consumer.

For a $\UniformModulusUp$ consumer, read the modulus row $M$ induced by the
bound ledger $B$. For $\ContinuousMapUp$ consumers, read the graph row $G$ and
the same transport routes. For $\PicardContractionUp$ and
$\BanachFixedPointUp$ consumers, the only available contraction-relevant datum
is the rational bound ledger together with the metric rows and graph route.

Thus every consumer route stays inside the displayed finite packet. The
excluded conclusions require coordinates not present in
\autoref{def:lipschitz-map-carrier}, so they cannot escape from the local
ledger.
\end{proof}

\begin{theorem}[LipschitzMap complete-metric regular seal boundary]
\label{thm:lipschitzmap-completemetric-regular-seal-boundary}
For an accepted $\LipschitzMapUp$ packet
$$
L=(X,Y,B,G,M,H,C,P,N),
$$
any $\CompleteMetricUp$, $\RegSeqRatUp$, or $\RealUp$ consumer of the
Lipschitz graph and bound must factor through the displayed source
$\MetricSpaceUp$ row $X$, target $\MetricSpaceUp$ row $Y$, rational
$\RealUp$ bound ledger $B$, $\ContinuousMapUp$ graph row $G$, induced
$\UniformModulusUp$ row $M$, componentwise $\hsame$ transports $H$,
displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert$
row $N$.

The handoff exports no Banach fixed point, completed orbit, host function
equality, quotient map, selected limit, or ambient completeness row. The
downstream seal surfaces are the complete-metric row of
\autoref{ch:concrete-instances-completemetric-namecert}, the regular-rational
source row of \autoref{ch:concrete-instances-regseqrat-namecert}, and the
real-name seal row of \autoref{ch:concrete-instances-real-namecert}.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_completemetric\_regular\_seal\_boundary}
\begin{proof}
Start with \autoref{thm:lipschitz-map-namecert-obligations}. It exposes
exactly the carrier rows $X,Y,B,G,M,H,C,P,N$ together with the local
classifier, stability, exactness, and ledger obligations.

Apply \autoref{thm:lipschitz-map-ledger-nonescape}. Every listed consumer of
the Lipschitz graph and bound remains inside the displayed source metric,
target metric, rational bound, graph, modulus, transport, continuation,
package, and naming rows. Thus a completion-facing read cannot obtain an
ambient completeness coordinate or a selected point from the Lipschitz packet.

Use \autoref{thm:lipschitz-map-uniform-modulus-consumer-handoff} for the
modulus route. The induced row $M$ is read from $X$, $G$, and $B$ through the
same transport and package surface, so the route toward regular-rational and
real seal consumers is the carried modulus route rather than a host function
equality or quotient map.

The sibling chapters
\autoref{ch:concrete-instances-completemetric-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert}, and
\autoref{ch:concrete-instances-real-namecert} supply only the downstream seal
surfaces. Since none of those surfaces is a coordinate of $L$, the
LipschitzMap packet contributes only the displayed graph-and-bound ledger to
their consumer routes.
\end{proof}

\begin{theorem}[LipschitzMap uniform-modulus consumer handoff]
\label{thm:lipschitz-map-uniform-modulus-consumer-handoff}
Every $\UniformModulusUp$ consumer of an accepted $\LipschitzMapUp$ carrier
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
reads the modulus row only through the source $\MetricSpaceUp$ distance row
$X$, the $\ContinuousMapUp$ graph row $G$, the rational $\RealUp$ bound ledger
$B$, displayed $\hsame$ and $\Cont$ transport, $\Pkg$ provenance, and the local
$\NameCert$ row $N$. The handoff exposes the same induced modulus row $M$ and
does not export host function extensionality, a quotient of maps, a selected
representative, or a target-space principle outside the carried Lipschitz
packet.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_uniform\_modulus\_consumer\_handoff}
\begin{proof}
Start with the obligation surface of
\autoref{thm:lipschitz-map-namecert-obligations}. It binds the carrier,
classifier, stability, exactness, and ledger policy for the rows
$X,Y,B,G,M,H,C,P,N$.

Apply ledger nonescape from \autoref{thm:lipschitz-map-ledger-nonescape}. A
$\UniformModulusUp$ consumer is one of the listed consumers, so its read stays
inside the displayed metric rows, graph row, bound ledger, induced modulus row,
transport, continuation, provenance, and naming data.

Finally apply bound transport from \autoref{thm:lipschitz-map-bound-transport}.
Transport preserves the accepted Lipschitz packet and keeps $M$ tied to the
same bound ledger $B$. The consumer therefore receives the uniform-modulus data
only through the carried source distance, graph, rational bound, and visible
certificate rows.
\end{proof}

\begin{theorem}[LipschitzMap public modulus export]
\label{thm:lipschitz-map-public-modulus-export}
For an accepted $\LipschitzMapUp$ packet
$$
L=(X,Y,B,G,M,H,C,P,N),
$$
the public $\UniformModulusUp$ row exported to any consumer is exactly $M$. It is induced from the rational $\RealUp$ bound ledger $B$ through the graph row $G$ and the source $\MetricSpaceUp$ row $X$. No consumer may replace $M$ by a host function modulus, a quotient of maps, or a target-space completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_public\_modulus\_export}
\begin{proof}
First read the packet rows from \autoref{thm:lipschitz-map-namecert-obligations}. The accepted carrier exposes $X,Y,B,G,M,H,C,P,N$ as the complete Lipschitz naming surface.

Next apply bound transport from \autoref{thm:lipschitz-map-bound-transport}. The rational ledger $B$, graph row $G$, and induced modulus row $M$ are transported as displayed rows of the same packet, so a consumer cannot detach the modulus from its source metric and graph evidence.

Finally use \autoref{thm:lipschitz-map-uniform-modulus-consumer-handoff}. The handoff routes every $\UniformModulusUp$ read through $X,G,B,M,H,C,P,N$, hence the public row exported to the consumer is the carried row $M$ and no host modulus, map quotient, or completeness principle is available.
\end{proof}

\begin{theorem}[LipschitzMap bound transport]
\label{thm:lipschitz-map-bound-transport}
Let
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
be an accepted $\LipschitzMapUp$ carrier. Any displayed $\hsame$ and $\Cont$
transport of the source $\MetricSpaceUp$ row $X$, target $\MetricSpaceUp$ row
$Y$, graph row $G$, rational $\RealUp$ bound ledger $B$, and induced
$\UniformModulusUp$ row $M$ preserves the accepted Lipschitz packet. The
transported packet has the same finite consumer surface: source-distance reads
still enter through $X$, target-distance reads still exit through $Y$, graph
reads still pass through $G$, and every modulus read is routed through the row
$M$ induced by the ledger $B$.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_bound\_transport}
\begin{proof}
Project the carrier coordinates. The transport row $H$ already lists the
componentwise $\hsame$ moves for source points, target points, metric-distance
rows, bound ledger entries, graph rows, and modulus rows.

Follow the stored $\Cont$ routes in $C$ after each componentwise move. The
source-distance route is transported first, the graph route is then read over
the transported source and target rows, and the rational bound comparison is
read from the transported ledger $B$.

The induced modulus row has no separate origin: it is the $\UniformModulusUp$
route generated from the same displayed bound ledger. Repack the transported
coordinates with the original $\Pkg$ provenance $P$ and local $\NameCert$ row
$N$. No representative choice or host function equality is used.
\end{proof}

\begin{theorem}[LipschitzMap target-distance exactness]
\label{thm:lipschitz-map-target-distance-exactness}
For an accepted $\LipschitzMapUp$ carrier
$$
L=(X,Y,B,G,M,H,C,P,N),
$$
every target-distance read factors through the displayed source-distance read
in $X$, the $\ContinuousMapUp$ graph row $G$, and the rational $\RealUp$ bound
ledger $B$. In particular, a consumer cannot read a target metric comparison
from a hidden target-space principle, a quotient of maps, or an external
function-extensionality assertion; the only exact route is the carried BEDC
route
$$
\begin{gathered}
\text{source distance in } X,\\
\text{graph read through } G,\\
\text{bound comparison through } B,\\
\text{target distance in } Y.
\end{gathered}
$$
\end{theorem}
\begin{proof}
Read the target-distance coordinate from the carrier. By the classifier of
\autoref{def:lipschitz-map-classifier}, target metric rows are compared only
componentwise through the displayed $\hsame$ and $\Cont$ surface.

The graph coordinate $G$ supplies the only route from source points to target
points. The rational ledger $B$ supplies the only nonnegative bound row for the
target-distance comparison, and the source metric row $X$ supplies the only
source-distance input to that comparison.

Thus every target-distance read is obtained by composing those visible routes.
The package row $P$ and local certificate row $N$ mention no completeness
principle, quotient equality, representative selector, or host extensionality
datum, so there is no second exactness route to project.
\end{proof}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_target\_distance\_exactness}

\begin{theorem}[LipschitzMap contraction-threshold handoff]
\label{thm:lipschitz-map-contraction-threshold-handoff}
Let
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
be an accepted $\LipschitzMapUp$ carrier. If the rational bound ledger $B$ is
read through the displayed $\RealUp$ order as strictly below the unit
threshold, then every $\PicardContractionUp$ or $\BanachFixedPointUp$ consumer
may use only the carried source $\MetricSpaceUp$ row $X$, target
$\MetricSpaceUp$ row $Y$, $\ContinuousMapUp$ graph row $G$,
$\UniformModulusUp$ row $M$, displayed $\hsame$ and $\Cont$ routes, $\Pkg$
provenance, and local $\NameCert$ row $N$.

The handoff records contraction-threshold data for downstream packets, but it
does not assert fixed points, completeness of $X$ or $Y$, a quotient of maps,
host function extensionality, or a selected representative.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_contraction\_threshold\_handoff}
\begin{proof}
Start with target-distance exactness from
\autoref{thm:lipschitz-map-target-distance-exactness}. It fixes the only
target-distance route as the path from the source distance in $X$ through the
graph row $G$, bound ledger $B$, and target row $Y$.

Use bound transport from \autoref{thm:lipschitz-map-bound-transport}. The
strict subunit read of $B$ is preserved by the displayed $\hsame$ and $\Cont$
movement, so the threshold datum remains attached to the same finite carrier.

Now apply the uniform-modulus consumer handoff of
\autoref{thm:lipschitz-map-uniform-modulus-consumer-handoff}. The modulus row
$M$ is read only through $X,G,B$ and the local certificate rows, so a
contraction consumer receives no independent analytic input.

Finally apply ledger nonescape from
\autoref{thm:lipschitz-map-ledger-nonescape}. $\PicardContractionUp$ and
$\BanachFixedPointUp$ are listed consumers, and the packet contains no
completeness, fixed-point, quotient, selector, or host-extensionality
coordinate. The contraction-threshold handoff is therefore exactly the
displayed finite route.
\end{proof}

\begin{theorem}[LipschitzMap contraction-threshold factorization]
\label{thm:lipschitz-map-contraction-threshold-factorization}
Let
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
be an accepted $\LipschitzMapUp$ carrier. If the bound ledger $B$ is read as
strictly below the unit threshold and a downstream fixed-point consumer supplies
the required $\CompleteMetricUp$, $\PicardContractionUp$, or
$\BanachFixedPointUp$ carrier row, then the consumer route factors through
exactly
$$
X,Y,B,G,M,H,C,P,N
$$
plus that displayed completeness or contraction row. The route cannot read
fixed points, completeness, quotient-map equality, selected representatives, or
host function extensionality from the $\LipschitzMapUp$ packet itself.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_contraction\_threshold\_factorization}
\begin{proof}
Start with target-distance exactness from
\autoref{thm:lipschitz-map-target-distance-exactness}. Every target-distance
comparison used by the downstream consumer is routed through the source metric
row $X$, graph row $G$, bound ledger $B$, and target metric row $Y$.

Use bound transport from \autoref{thm:lipschitz-map-bound-transport} together
with the uniform-modulus handoff of
\autoref{thm:lipschitz-map-uniform-modulus-consumer-handoff}. These results
keep the subunit threshold read attached to the displayed carrier and expose
the modulus row $M$ only through $X,G,B,H,C,P,N$.

Apply the contraction-threshold handoff of
\autoref{thm:lipschitz-map-contraction-threshold-handoff}. A
$\PicardContractionUp$ or $\BanachFixedPointUp$ consumer may therefore import
only the displayed Lipschitz packet together with its own completeness or
contraction row.

Finally apply ledger nonescape from
\autoref{thm:lipschitz-map-ledger-nonescape}. The $\LipschitzMapUp$ packet has
no coordinate for a fixed point, a completeness witness, quotient-map equality,
a selected representative, or host function extensionality, so those data must
come from the downstream carrier rather than from $L$.
\end{proof}

\begin{theorem}[LipschitzMap composite-bound routing]
\label{thm:lipschitz-map-composite-bound-routing}
Let $L$ and $L'$ be accepted $\LipschitzMapUp$ carriers with compatible
intermediate metric rows as in
\autoref{thm:lipschitz-map-composition-boundary}. The composite consumer path
is routed only through the displayed product of the two rational $\RealUp$
bound ledgers and the sequential $\UniformModulusUp$ route induced by the two
carried modulus rows. The composite boundary exposes no alternative consumer
path for the bound, graph, or modulus data.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_composite\_bound\_routing}
\begin{proof}
Project the two carriers. The first carrier supplies the source metric row,
first graph row, first bound ledger, and first induced modulus route. The
second carrier supplies the intermediate-compatible source row, second graph
row, second bound ledger, and second induced modulus route.

Use the compatibility of the intermediate metric rows to pass the first target
distance into the second source-distance input through the displayed
classifier surface. This is a carried $\hsame$ and $\Cont$ passage, not an
identification of host maps.

Now multiply the two rational ledgers as the composite bound ledger and route
the modulus read sequentially through the two $\UniformModulusUp$ rows. Since
the packet contains no other bound or modulus coordinate, every composite
consumer must use this product-ledger route.
\end{proof}

\begin{theorem}[LipschitzMap identity carrier boundary]
\label{thm:lipschitz-map-identity-carrier-boundary}
Let $X$ be a transported $\MetricSpaceUp$ row and let
$$
L=(X,X,B_{\mathsf{id}},G_{\mathsf{id}},M_{\mathsf{id}},H,C,P,N)
$$
be the packet whose source and target metric rows are the same transported row, whose graph row $G_{\mathsf{id}}$ is the identity graph over $X$, whose rational bound ledger $B_{\mathsf{id}}$ is the unit $\RealUp$ row, and whose modulus row $M_{\mathsf{id}}$ is the identity $\UniformModulusUp$ route. Then $L$ forms an accepted $\LipschitzMapUp$ consumer boundary over the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and it exposes no host function extensionality or selected representative.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_identity\_carrier\_boundary}
\begin{proof}
Project the carrier shape of \autoref{def:lipschitz-map-carrier}. With the same $\MetricSpaceUp$ row in the source and target coordinates, the identity graph row supplies the carried $\ContinuousMapUp$ route from each source point history to the same target point history.

Use target-distance exactness from \autoref{thm:lipschitz-map-target-distance-exactness}. For the identity graph, every target-distance read is the same transported source-distance read, so the unit rational ledger $B_{\mathsf{id}}$ binds the target comparison to the original source metric row.

The identity $\UniformModulusUp$ route $M_{\mathsf{id}}$ is then the modulus induced by that unit bound. Bound transport from \autoref{thm:lipschitz-map-bound-transport} keeps $B_{\mathsf{id}}$, $G_{\mathsf{id}}$, and $M_{\mathsf{id}}$ attached to the same transported row through $H$ and $C$.

Finally apply ledger nonescape from \autoref{thm:lipschitz-map-ledger-nonescape}. The packet contains only the displayed metric row, identity graph, unit bound ledger, identity modulus route, transports, continuations, provenance, and local certificate, so it cannot export host function extensionality or a selected representative.
\end{proof}

\begin{theorem}[LipschitzMap obligation closure package]
\label{thm:lipschitz-map-obligation-closure-package}
The $\LipschitzMapUp$ obligation surface is exhausted by the carrier of
\autoref{def:lipschitz-map-carrier}, the classifier of
\autoref{def:lipschitz-map-classifier}, bound transport
\autoref{thm:lipschitz-map-bound-transport}, target-distance exactness
\autoref{thm:lipschitz-map-target-distance-exactness}, composite-bound routing
\autoref{thm:lipschitz-map-composite-bound-routing}, and ledger nonescape
\autoref{thm:lipschitz-map-ledger-nonescape}. These rows form a finite
$\BHist$ package over $\hsame$, $\Cont$, $\Pkg$, $\NameCert$,
$\MetricSpaceUp$, $\RealUp$, $\ContinuousMapUp$, and $\UniformModulusUp$.
\end{theorem}
\begin{proof}
Collect the carrier and classifier rows first. They name exactly the finite
coordinates and the componentwise comparison surface available to a local
$\NameCert_{\LipschitzMapUp}$ consumer.

Add the three transport and routing obligations. Bound transport preserves the
accepted packet under displayed $\hsame$ and $\Cont$ movement. Target-distance
exactness fixes the unique target-distance read route. Composite-bound routing
fixes the product ledger and sequential modulus route for composed consumers.

Finally apply ledger nonescape. It states that $\UniformModulusUp$,
$\PicardContractionUp$, $\BanachFixedPointUp$, and $\ContinuousMapUp$
consumers factor through the displayed rows and do not acquire hidden
completeness, differentiability, quotient, representative-selection, or host
extensionality data. Repacking these named clauses gives precisely the
obligation closure package.
\end{proof}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_obligation\_closure\_package}

\begin{theorem}[LipschitzMap bound dependency lock]
\label{thm:lipschitz-map-bound-dependency-lock}
Let
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
be an accepted $\LipschitzMapUp$ carrier. Every $\UniformModulusUp$, $\PicardContractionUp$, $\BanachFixedPointUp$, or $\ContinuousMapUp$ consumer of $L$ must read the rational $\RealUp$ bound ledger $B$ together with the source and target $\MetricSpaceUp$ rows $X,Y$, the graph row $G$, and the induced modulus row $M$. No such consumer may detach $B$ into a fixed-point theorem, completeness theorem, differentiability claim, quotient-map claim, or host-extensionality claim.
\end{theorem}
\begin{proof}
Start with target-distance exactness. It binds each target-distance read to the source and target metric rows $X,Y$, the graph row $G$, and the rational bound ledger $B$ through the displayed carrier route.

Use bound transport to keep $B$ attached to the same graph and modulus data under $\hsame$ and $\Cont$ movement. The ledger is transported only as part of the accepted packet, not as an independent real-number fact.

Now apply the consumer handoffs. Uniform-modulus consumers read the induced row $M$ from $B,X,Y,G$, contraction-threshold consumers read the same bound through the displayed threshold route, and composite-bound routing preserves the bound only through the product-ledger route for compatible Lipschitz packets.

Finally apply ledger nonescape. Since the carrier contains no row for completeness, differentiability, quotient-map equality, selected representatives, or host function extensionality, every listed consumer remains locked to $X,Y,B,G,M,H,C,P,N$ and cannot detach $B$ into one of those stronger claims.
\end{proof}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_bound\_dependency\_lock}

\begin{theorem}[LipschitzMap common-bound completion route]
\label{thm:lipschitz-map-common-bound-completion-route}
Let
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
be an accepted $\LipschitzMapUp$ carrier. Every completion-facing consumer that reads the graph row $G$, the rational Lipschitz-bound ledger $B$, a $\RegSeqRatUp$ source row, and a $\RealUp$ seal must factor through one shared bound ledger together with the source and target $\MetricSpaceUp$ rows $X,Y$, the $\ContinuousMapUp$ graph row $G$, and the $\UniformModulusUp$ row $M$ before reaching the $\RegSeqRatUp$ and $\RealUp$ seal boundary. This route does not supply ambient completeness, selected limits, quotient-map equality, host function extensionality, or differentiability.
\end{theorem}
\leanchecked{BEDC.Derived.LipschitzMapUp.LipschitzMapCarrier\_common\_bound\_completion\_route}
\begin{proof}
Start from the local $\NameCert_{\LipschitzMapUp}$ obligations. They make the accepted packet read exactly the displayed source metric row, target metric row, rational bound ledger, continuous graph row, induced modulus row, transports, continuations, provenance, and local naming certificate.

Apply ledger nonescape and the uniform-modulus handoff. The rational bound $B$ can be used by a consumer only through the displayed Lipschitz packet, so the modulus row $M$ remains tied to the same $X,Y,B,G$ ledger rather than becoming an ambient regularity fact.

Next use the complete-metric regular seal boundary. The completion-facing $\RegSeqRatUp$ source row and $\RealUp$ seal are read only after the shared Lipschitz ledger has passed through the sibling $\MetricSpaceUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ rows.

Finally apply \autoref{thm:lipschitz-map-bound-dependency-lock}. It excludes detaching the common bound into completeness, selected limits, quotient-map equality, host function extensionality, or differentiability, and leaves the displayed $\MetricSpaceUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\RegSeqRatUp$, and $\RealUp$ rows as the only available completion route.
\end{proof}

\begin{theorem}[LipschitzMap separated-completion nonescape]
\label{thm:lipschitz-map-separated-completion-nonescape}
Let
$$
L=(X,Y,B,G,M,H,C,P,N)
$$
be an accepted $\LipschitzMapUp$ carrier. Every completion-facing consumer routed through $\CompleteMetricUp$, $\SeparatedMetricUp$, $\RealUp$, $\RegSeqRatUp$, and $\UniformModulusUp$ must read the rational Lipschitz-bound ledger $B$ and the separated zero-distance route before any completion identity claim is exposed. The consumer receives only the common-bound completion route, target-distance exactness, contraction-threshold factorization, and the public zero-distance route of $\SeparatedMetricUp$; it receives no ambient completeness theorem, selected limit, quotient completion equality, host function extensionality, differentiability, or detached real equality.
\end{theorem}
\begin{proof}
Start from \autoref{thm:lipschitz-map-common-bound-completion-route}. It places the graph row $G$, rational bound ledger $B$, source and target metric rows $X,Y$, induced modulus row $M$, $\RegSeqRatUp$ source row, and $\RealUp$ seal on one shared completion-facing route.

Apply target-distance exactness and the contraction threshold factorization. The target-distance read is tied to $X,Y,B,G$, while contraction-facing consumers may use the bound only through the displayed threshold route and induced modulus row.

Finally use the public separated-metric zero-distance route of \autoref{thm:separatedmetric-public-identity-export}. A completion identity claim can be exposed only after the separated zero-distance classifier has been read, so the Lipschitz packet cannot bypass $B$ or replace the separated route by quotient completion equality, selected limits, or host equality.
\end{proof}

\closureat{LipschitzMapUp}{seedStr}
\closureat{LipschitzMapUp}{obligationStr}

\begin{closurestatus}{\LipschitzMapUp}
  \constructivestory{A $\LipschitzMapUp$ packet is generated from source and target $\MetricSpaceUp$ rows, a rational $\RealUp$ Lipschitz-bound ledger, a $\ContinuousMapUp$ graph row, a $\UniformModulusUp$ modulus row induced by the bound, componentwise $\hsame$ transports, visible $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:lipschitz-map-carrier}, \autoref{def:lipschitz-map-classifier}, \autoref{thm:lipschitz-map-namecert-obligations}, \autoref{thm:lipschitz-map-bound-transport}, \autoref{thm:lipschitz-map-target-distance-exactness}, \autoref{thm:lipschitz-map-composite-bound-routing}, and \autoref{thm:lipschitz-map-obligation-closure-package} bind the carrier, classifier, NameCert obligations, bound transport, target-distance exactness, composite-bound routing, and obligation surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Banach fixed point, completeness of the metric spaces, differentiability, quotient equality of maps, selected representatives, host function extensionality, or bridge checking.}
  \upgradepath{Scoped closure requires routing $\MetricSpaceUp$, $\RealUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows through the displayed bound, graph, modulus, transport, continuation, provenance, and local naming surface.}
\end{closurestatus}
