\chapter{A Concrete Naming Certificate for $\RegularCauchyUniformityUp$}
\label{ch:concrete-instances-regularcauchyuniformity-namecert}
\origin{human}

Following Bourbaki and Kelley on uniform spaces and Bishop--Bridges regular Cauchy names, the $\RegularCauchyUniformityUp$ packet names the dyadic-entourage uniformity on regular rational Cauchy names as finite BEDC rows. It reads the dyadic arithmetic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the ambient uniform-space interface of \autoref{ch:concrete-instances-uniformspace-namecert}, and the completion-facing route of \autoref{ch:concrete-instances-metriccompletion-namecert}. The packet is the finite dyadic-entourage surface used by Real and completion consumers; it is not quotient stream equality, not a selected limit, not host real equality, not countable choice, not open-cover compactness, and not Real completeness.

\begin{definition}[Regular Cauchy uniformity carrier]
\label{def:regular-cauchy-uniformity-carrier}
A $\RegularCauchyUniformityUp$ carrier is a finite $\BHist$ packet
$$
U=(R,W,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RegSeqRatUp$ regular rational name row read only through finite $\StreamNameUp$ windows.
\item $W$ is the finite window row recording the inspected stream prefix and the later common refinements admitted for the same regular Cauchy name.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row naming the dyadic radius used by the entourage request.
\item $E$ is the dyadic-entourage row, asserting that two displayed regular rational windows are within the tolerance named by $D$ at the inspected stage.
\item $H$ records componentwise $\hsame$ transport for the regular rational name, window, dyadic tolerance, entourage row, continuation row, provenance row, and local naming row.
\item $C$ records the displayed $\Cont$ replay from a regular Cauchy request through finite windows, dyadic tolerance naming, entourage admission, and the downstream Real or completion handoff.
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\UniformSpaceUp$, $\MetricCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyUniformityUp}$ row.
\end{enumerate}
The carrier predicate is exactly the assertion that these eight rows form one finite dyadic-entourage uniformity packet. It contains no coordinate for quotient stream equality, selected limits, host real equality, countable choice, open-cover compactness, or Real completeness.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyUniformityUp.TasteGate.RegularCauchyUniformityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy uniformity NameCert obligations]
\label{thm:regular-cauchy-uniformity-namecert-obligations}
For every accepted $\RegularCauchyUniformityUp$ carrier $U=(R,W,D,E,H,C,P,N)$, the local $\NameCert_{\RegularCauchyUniformityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the regular rational name, finite window, dyadic tolerance, entourage, transport, continuation, provenance, and local naming rows;
\item dyadic entourage admission, requiring $E$ to be read only after the window row $W$ and tolerance row $D$ have been displayed;
\item window reindexing, requiring later common finite $\StreamNameUp$ refinements to preserve the same regular rational source row $R$;
\item Real seal handoff, requiring every $\RealUp$ consumer to enter through the displayed route $R,W,D,E,H,C,P,N$;
\item transport, requiring $H$ to identify only the listed rows componentwise under $\hsame$;
\item replay, requiring $C$ to reproduce the same finite path before any downstream uniform-space or completion read;
\item provenance, requiring $P$ to name only the displayed RegSeqRat, StreamName, DyadicRatCore, Real, UniformSpace, and MetricCompletion dependencies;
\item non-escape, excluding quotient stream equality, selected limits, host real equality, countable choice, open-cover compactness, Real completeness, and any hidden host uniformity.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-uniformity-carrier}. The projection exposes exactly the regular rational name row, finite window row, dyadic tolerance row, entourage row, transport row, continuation row, provenance row, and local naming row.

Dyadic entourage admission is the row $E$ downstream of $W$ and $D$. Since $D$ is the only tolerance coordinate and $W$ is the only finite observation coordinate, the entourage cannot be read before both rows are displayed.

Window reindexing is recorded by the same $W$ row and transported by $H$. A later common refinement changes only the inspected finite prefix, while the source row $R$ and dyadic tolerance row $D$ remain the rows named by the packet.

The Real and completion handoff is ordered by $C$. Any downstream consumer must replay $R,W,D,E$ before reaching the structural rows $H,C,P,N$, so the consumer sees a finite dyadic-entourage route rather than a host uniformity.

The exclusions follow from the carrier inventory. There is no row for quotient stream equality, selected limits, host real equality, countable choice, open-cover compactness, Real completeness, or any hidden uniformity outside the displayed packet.
\end{proof}

\begin{theorem}[Regular Cauchy uniformity dyadic entourage stability]
\label{thm:regular-cauchy-uniformity-dyadic-entourage-stability}
Let $U=(R,W,D,E,H,C,P,N)$ be an accepted $\RegularCauchyUniformityUp$ carrier. If two finite $\StreamNameUp$ windows are common refinements of the window row $W$ and keep the same $\RegSeqRatUp$ source row $R$, then the dyadic-entourage row $E$ remains the displayed entourage row for both refinements after componentwise $\hsame$ transport. In particular, common finite refinements preserve the same dyadic tolerance row $D$ and do not create a second uniformity route.
\end{theorem}
\begin{proof}
Start with the accepted carrier and the two common finite refinements of $W$. The carrier has only one source row $R$ and only one dyadic tolerance row $D$, so both refinements are read as later windows for the same regular rational name and the same tolerance request.

Use the transport row $H$ componentwise. It identifies the original window data and the refined window data only along the displayed regular rational, dyadic tolerance, and entourage rows.

Replay $C$ after transport. The replay reaches the same entourage row $E$ from each refined window, because no second tolerance coordinate, quotient stream coordinate, or host uniformity coordinate is present in the carrier.

Thus the dyadic-entourage row is stable under the common finite refinements, and the packet continues to expose a single finite route through $R,W,D,E,H,C,P,N$.
\end{proof}

\begin{theorem}[Regular Cauchy uniformity common-refinement transitivity]
\label{thm:regular-cauchy-uniformity-common-refinement-transitivity}
Let $U=(R,W,D,E,H,C,P,N)$ be an accepted $\RegularCauchyUniformityUp$ carrier. For any displayed finite chain of $\StreamNameUp$ common refinements
$$
W=W_0 \leadsto W_1 \leadsto \cdots \leadsto W_k
$$
starting at the window row $W$, if every step keeps the same $\RegSeqRatUp$ source row $R$ and the same $\DyadicRatCoreUp$ tolerance row $D$, then the terminal window $W_k$ carries the same dyadic-entourage row $E$. Every $\RealUp$ or $\MetricCompletionUp$ consumer of $W_k$ still factors through the finite route
$$
R \longmapsto W \longmapsto D \longmapsto E \longmapsto H,C,P,N .
$$
The chain introduces no quotient stream equality, selected limit, host real equality, countable choice, open-cover compactness, or Real completeness.
\end{theorem}
\begin{proof}
Induct on the displayed finite refinement chain. In the base case the terminal window is $W$ itself, so the carrier projection of \autoref{def:regular-cauchy-uniformity-carrier} supplies the source row $R$, tolerance row $D$, dyadic-entourage row $E$, and the replay route through $H,C,P,N$.

For the step, assume the current terminal window has already retained the same rows $R,D,E$. Apply \autoref{thm:regular-cauchy-uniformity-dyadic-entourage-stability} to the next common finite refinement. The hypothesis that the refinement keeps $R$ and $D$ makes the theorem applicable, and its conclusion preserves $E$ as the displayed dyadic-entourage row.

Finally apply \autoref{thm:regular-cauchy-uniformity-real-seal-handoff} to the terminal window. The consumer route remains the finite route through $R,W,D,E,H,C,P,N$, so the induction never creates quotient stream equality, a selected limit, host real equality, countable choice, open-cover compactness, Real completeness, or any host uniformity coordinate.
\end{proof}

\begin{theorem}[Regular Cauchy uniformity Real seal handoff]
\label{thm:regular-cauchy-uniformity-real-seal-handoff}
Every $\RealUp$ or $\MetricCompletionUp$ consumer of an accepted $\RegularCauchyUniformityUp$ carrier sees the uniformity only through the finite route
$$
R \longmapsto W \longmapsto D \longmapsto E \longmapsto H,C,P,N .
$$
Consequently the consumer receives a dyadic-entourage service for regular rational Cauchy names, not quotient stream equality, not a selected limit, not host real equality, not countable choice, not open-cover compactness, and not Real completeness.
\end{theorem}
\begin{proof}
Let $U=(R,W,D,E,H,C,P,N)$ be accepted. The only regular Cauchy source available to a downstream consumer is $R$, and the only observation surface attached to it is the finite window row $W$.

The tolerance request then passes through $D$, and the uniformity read is the dyadic-entourage row $E$. No Real or completion consumer can bypass those rows, because $C$ records the replay order and $H$ transports only the displayed coordinates.

The provenance and local naming rows $P,N$ package the same route for $\RealUp$, $\UniformSpaceUp$, and $\MetricCompletionUp$ consumers. They do not add quotient stream equality, a selected limit, host real equality, countable choice, open-cover compactness, Real completeness, or a host uniformity coordinate.
\end{proof}

\begin{theorem}[Regular Cauchy uniformity scoped obligation package]
\label{thm:regular-cauchy-uniformity-scoped-obligation-package}
The carrier of \autoref{def:regular-cauchy-uniformity-carrier}, the NameCert obligations of \autoref{thm:regular-cauchy-uniformity-namecert-obligations}, dyadic-entourage stability of \autoref{thm:regular-cauchy-uniformity-dyadic-entourage-stability}, common-refinement transitivity of \autoref{thm:regular-cauchy-uniformity-common-refinement-transitivity}, and the Real seal handoff of \autoref{thm:regular-cauchy-uniformity-real-seal-handoff} form the complete $\RegularCauchyUniformityUp$ obligation package over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\UniformSpaceUp$, $\MetricCompletionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The package excludes quotient stream equality, selected limits, host real equality, countable choice, open-cover compactness, Real completeness, and hidden host uniformity.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-uniformity-carrier}. Its rows are exactly the regular rational source, finite stream window, dyadic tolerance, dyadic entourage, componentwise transport, continuation replay, provenance, and local naming rows.

Apply \autoref{thm:regular-cauchy-uniformity-namecert-obligations} to read those rows as the local $\NameCert_{\RegularCauchyUniformityUp}$ surface. The obligation rows include carrier admission, dyadic entourage admission, window reindexing, Real seal handoff, transport, replay, provenance, and non-escape.

Next apply \autoref{thm:regular-cauchy-uniformity-dyadic-entourage-stability} and \autoref{thm:regular-cauchy-uniformity-common-refinement-transitivity}. These two results compose the finite window route under common refinements while preserving the same source row, tolerance row, and entourage row.

Finally apply \autoref{thm:regular-cauchy-uniformity-real-seal-handoff}. Every $\RealUp$ or $\MetricCompletionUp$ consumer still reaches the packet through the displayed finite route, so the listed BEDC rows exhaust the obligation surface and none of the excluded host-side data is introduced.
\end{proof}

\closureat{RegularCauchyUniformityUp}{seedStr}
\closureat{RegularCauchyUniformityUp}{obligationStr}

\begin{closurestatus}{\RegularCauchyUniformityUp}
  \constructivestory{A $\RegularCauchyUniformityUp$ packet is generated from a regular rational name row, a finite StreamName window row, a DyadicRatCore tolerance row, a dyadic-entourage row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:regular-cauchy-uniformity-carrier}, \autoref{thm:regular-cauchy-uniformity-namecert-obligations}, \autoref{thm:regular-cauchy-uniformity-dyadic-entourage-stability}, \autoref{thm:regular-cauchy-uniformity-common-refinement-transitivity}, \autoref{thm:regular-cauchy-uniformity-real-seal-handoff}, and \autoref{thm:regular-cauchy-uniformity-scoped-obligation-package} close the finite dyadic-entourage obligation surface for RegSeqRat, StreamName, DyadicRatCore, Real, UniformSpace, and MetricCompletion consumers.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RegularCauchyUniformityUp.TasteGate.RegularCauchyUniformityTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, host real equality, countable choice, open-cover compactness, Real completeness, or a public standard bridge.}
  \upgradepath{Scoped closure requires a public consumer boundary and bridge-checked standard interface for the displayed $\RegularCauchyUniformityUp$ dyadic-entourage route.}
\end{closurestatus}
