\chapter{A Concrete Naming Certificate for $\TriangulatedCatUp$}
\label{ch:concrete-instances-triangulatedcat-namecert}

The triangulated-category interface $\TriangulatedCatUp$ packages an additive category with a translation autoequivalence and a class of distinguished triangles satisfying the octahedral axiom. It depends on $\NameCert_{\CategoryUp}$ (\autoref{ch:concrete-instances-category-namecert}) and $\NameCert_{\DerivedCatUp}$ (\autoref{ch:concrete-instances-derivedcat-namecert}).

\section{Carrier definition}
\label{sec:triangulatedcat-carrier}

\begin{definition}[TriangulatedCat finite carrier]
\label{def:triangulatedcat-carrier}
A $\TriangulatedCatUp$ carrier is the finite $\mathsf{BHist}$ packet
$\mathsf{TriangulatedCatPkt}(\mathcal{T})$ with the following displayed rows.
\begin{enumerate}
  \item A retained $\CategoryUp$ row for the underlying category object,
  morphism, identity, and composition histories.
  \item A retained $\DerivedCatUp$ row for the visible localization boundary
  used by the triangulated presentation.
  \item An additive-category row recording the zero object, biproduct,
  addition on hom histories, and additive inverse histories.
  \item A translation-autoequivalence row recording a shift history
  $\Sigma$, its inverse shift history, and the displayed unit and counit
  comparison histories.
  \item A distinguished-triangle row recording triples
  $X\to Y\to Z\to \Sigma X$ as finite morphism-history ledgers.
  \item An octahedral ledger row recording only the named faces, comparison
  morphisms, and $\Cont$ witnesses that are explicitly displayed in the
  packet.
  \item Componentwise $\hsame$ rows for all category, derived-category,
  additive, shift, triangle, and octahedral histories.
  \item $\Cont$ rows for shift transport, triangle rotation, triangle
  morphism composition, and octahedral-face composition.
  \item A $\mathsf{Pkg}$ provenance row tying the retained dependency
  certificates and all displayed triangulated rows to one source packet.
\end{enumerate}
The carrier accepts no row that is not one of these displayed
$\mathsf{BHist}$, $\hsame$, $\Cont$, or $\mathsf{Pkg}$ fields.
\end{definition}
\leandef{BEDC.Derived.TriangulatedCatUp.TriangulatedCatFiniteCarrier}

\begin{definition}[TriangulatedCat classifier]
\label{def:triangulatedcat-classifier}
Two $\mathsf{TriangulatedCatPkt}$ carriers classify together when their
retained $\CategoryUp$ and $\DerivedCatUp$ rows classify by the corresponding
dependency certificates and every additive, translation, triangle,
octahedral-ledger, $\Cont$, and $\mathsf{Pkg}$ row is related by the displayed
componentwise $\hsame$ comparison. This classifier is a comparison of finite
packet rows; it is not a host localization, a Verdier quotient, or an
unstated equality of triangulated categories.
\end{definition}
\leandef{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketClassifier}

\section{The certificate}
\label{sec:triangulatedcat-certificate}

\begin{theorem}[TriangulatedCat carrier obligation]
\label{thm:triangulatedcat-carrier-obligation}
Every accepted $\mathsf{TriangulatedCatPkt}(\mathcal{T})$ row projects to one
of the displayed dependency, additive, translation, distinguished-triangle,
octahedral-ledger, $\hsame$, $\Cont$, or $\mathsf{Pkg}$ rows of
\autoref{def:triangulatedcat-carrier}. No host Verdier quotient object and no
unlogged octahedral datum is carried by the $\TriangulatedCatUp$ surface.
\end{theorem}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_carrier\_obligation}
\begin{proof}
Unpack the carrier definition. The packet constructor lists the retained
$\CategoryUp$ and $\DerivedCatUp$ rows first, then the additive,
translation-autoequivalence, distinguished-triangle, octahedral-ledger,
componentwise $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows.

Projecting an accepted carrier therefore selects one of those coordinates.
The categorical and derived rows are read through their dependency
certificates, while the triangulated-specific rows are histories inside the
same finite packet.

Conversely, each displayed coordinate repacks into the same packet by the
carrier constructor. Constructor inversion leaves no separate case for a host
Verdier quotient, an unlabelled localization equality, or octahedral data
outside the listed ledger row.
\end{proof}

\begin{theorem}[TriangulatedCat classifier stability obligation]
\label{thm:triangulatedcat-classifier-stability-obligation}
The classifier of \autoref{def:triangulatedcat-classifier} transports the
finite $\TriangulatedCatUp$ carrier surface: classified packets have
classified dependency rows and componentwise transported additive, shift,
triangle, octahedral-ledger, $\Cont$, and $\mathsf{Pkg}$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_classifier\_stability}
\begin{proof}
Begin with a classifier witness between two displayed packets. Its dependency
fields are the retained classifiers for the $\CategoryUp$ and $\DerivedCatUp$
rows, so those two rows transport by the existing certificate surfaces.

The remaining classifier fields are componentwise $\hsame$ comparisons.
Apply them separately to the additive-category row, the shift and inverse
shift rows, the unit and counit comparison rows, the distinguished-triangle
ledger, and the octahedral ledger.

The $\Cont$ rows transport because their source, middle, and target histories
are among the same componentwise comparisons. The provenance row transports
by the displayed $\mathsf{Pkg}$ comparison. Repacking these transported rows
with the carrier constructor gives a classified target packet and no extra
semantic equality is used.
\end{proof}

\begin{theorem}[TriangulatedCat translation-triangle obligation scope]
\label{thm:triangulatedcat-translation-triangle-obligation-scope}
Every translated distinguished-triangle readback in an accepted
$\TriangulatedCatUp$ packet is read only through the displayed
translation-autoequivalence row, inverse shift row, unit and counit comparison
histories, distinguished-triangle ledger, componentwise $\hsame$, $\Cont$ rows
for shift transport and triangle rotation, $\mathsf{Pkg}$ provenance, and the
retained $\CategoryUp$ and $\DerivedCatUp$ dependency rows. It does not read
host Verdier quotient semantics, unlogged exact-triangle objects, or ambient
triangulated-category equality.
\end{theorem}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_translation\_triangle\_obligation\_scope}
\begin{proof}
Unpack rows 20--31 of \autoref{def:triangulatedcat-carrier}. A translated
distinguished triangle is represented by the displayed shift histories, inverse
shift row, unit and counit comparisons, the distinguished-triangle ledger, and
the associated continuation rows.

Apply \autoref{thm:triangulatedcat-classifier-stability-obligation}. The
classifier transports each listed component by its $\hsame$ comparison, while
the retained $\CategoryUp$ and $\DerivedCatUp$ rows supply the dependency
certificates and the $\mathsf{Pkg}$ row records provenance.

Repack the visible shift and triangle rows through the carrier constructor.
Constructor inversion has no coordinate for a host Verdier quotient, an
unlogged exact-triangle object, or an ambient equality of triangulated
categories, so every accepted readback stays inside the displayed packet
surface.
\end{proof}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_translation\_triangle\_scope}

\begin{theorem}[TriangulatedCat shift autoequivalence obligation]
\label{thm:triangulatedcat-shift-autoequivalence-obligation}
The shift row of a $\mathsf{TriangulatedCatPkt}$ exports only the displayed
$\Sigma$ history, inverse-shift history, unit and counit comparison histories,
their $\mathsf{BHist}$ entries, componentwise $\hsame$ comparisons, the
$\Cont$ rows that transport the shift route, and the $\mathsf{Pkg}$ provenance
row of \autoref{def:triangulatedcat-carrier}. It does not export an equality
of host autoequivalences or an unlogged inverse functor.
\end{theorem}
\begin{proof}
Unpack the carrier of \autoref{def:triangulatedcat-carrier}. The shift
coordinate is one finite row in the same packet as the additive,
distinguished-triangle, octahedral-ledger, $\Cont$, and $\mathsf{Pkg}$ rows.

Apply the componentwise classifier transport of
\autoref{thm:triangulatedcat-classifier-stability-obligation} to the
$\Sigma$, inverse-shift, unit, and counit histories. The transported data stay
inside the listed $\mathsf{BHist}$ and $\hsame$ coordinates.

It remains to rule out a host autoequivalence equality. Constructor inversion
on the packet has cases only for the displayed shift histories, their
comparison rows, the relevant $\Cont$ witnesses, and the provenance row, so no
separate equality coordinate can be projected.
\end{proof}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_shift\_autoequivalence\_obligation}

\begin{theorem}[TriangulatedCat distinguished-triangle rotation obligation]
\label{thm:triangulatedcat-distinguished-triangle-rotation-obligation}
Every rotation read of a distinguished triangle in a
$\mathsf{TriangulatedCatPkt}$ factors through the logged triangle row, the
shift obligation of
\autoref{thm:triangulatedcat-shift-autoequivalence-obligation}, and the
displayed $\Cont$ route for triangle rotation. No rotation is read from an
ambient triangulated-category structure outside the finite packet.
\end{theorem}
\begin{proof}
Unpack the distinguished-triangle coordinate of
\autoref{def:triangulatedcat-carrier}. A triangle is present as a finite
morphism-history ledger ending in the displayed $\Sigma$ row.

The endpoint shift is therefore the shift row governed by
\autoref{thm:triangulatedcat-shift-autoequivalence-obligation}. By
\autoref{thm:triangulatedcat-classifier-stability-obligation}, classifier
transport carries the triangle histories, the shift endpoint, and the rotation
continuation componentwise.

Constructor inversion on the packet leaves only the triangle ledger and the
listed $\Cont$ rotation route as sources for a rotation read. Hence the
certificate consumes rotation through the logged finite data rather than
through a host triangulated-category operation.
\end{proof}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_distinguished\_triangle\_rotation\_obligation}

\begin{theorem}[TriangulatedCat octahedral Cont face coverage]
\label{thm:triangulatedcat-octahedral-cont-face-coverage}
Every octahedral face consumed by the $\TriangulatedCatUp$ certificate is one
of the logged finite faces of the octahedral ledger, together with its
comparison-morphism history and displayed $\Cont$ witness. The certificate has
no access path to an octahedral face outside those packet rows.
\end{theorem}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatOctahedralLedger\_face\_cont\_coverage}
\leanvariant{BEDC.Derived.TriangulatedCatUp.TriangulatedCatOctahedralLedger\_face\_cont\_witness}
\begin{proof}
Start with the octahedral coordinate of
\autoref{def:triangulatedcat-carrier}. Its accepted rows are the finite face
histories, comparison morphism histories, and $\Cont$ witnesses named in the
ledger.

Use \autoref{thm:triangulatedcat-classifier-stability-obligation} to transport
each face together with its comparison morphism and continuation witness. This
is componentwise transport of displayed packet rows, not a semantic
octahedral axiom from outside the carrier.

Finally perform constructor inversion on the finite packet. A consumed face
must project from one of the logged octahedral rows, and each such row carries
the comparison history and $\Cont$ witness required by the certificate.
\end{proof}

\begin{theorem}[TriangulatedCat octahedral ledger boundary]
\label{thm:triangulatedcat-octahedral-ledger-boundary}
The octahedral obligation in the $\TriangulatedCatUp$ packet is bounded by the
displayed octahedral ledger: it records finite faces, comparison morphism
histories, and $\Cont$ witnesses, and it does not assert any unrecorded
octahedral filler or external triangulated-category semantics.
\end{theorem}
\begin{proof}
Read the octahedral coordinate of
\autoref{def:triangulatedcat-carrier}. Its data are the named triangle faces,
the comparison morphism histories between those faces, and the finite
$\Cont$ rows witnessing the displayed composites.

Any use of the octahedral obligation must project through that coordinate.
Thus a face comparison or composite can be cited only when the corresponding
history and continuation row appears in the ledger.

If a purported octahedral datum is not in the displayed ledger, constructor
inversion gives no packet coordinate from which to project it. Therefore the
chapter exposes an octahedral boundary ledger, not an ambient octahedral
oracle.
\end{proof}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatOctahedralLedger\_boundary}

\begin{theorem}[TriangulatedCat NameCert obligation surface]
\label{thm:triangulatedcat-namecert-obligation-surface}
The public $\NameCert_{\TriangulatedCatUp}$ surface determined by
\autoref{def:triangulatedcat-carrier} and
\autoref{def:triangulatedcat-classifier} consists of the finite carrier rows,
the componentwise classifier, carrier transport, the displayed octahedral
ledger boundary, and the $\mathsf{Pkg}$ provenance row. It excludes host
Verdier quotient semantics and octahedral data not logged in the packet.
\end{theorem}
\begin{proof}
First project the carrier by
\autoref{thm:triangulatedcat-carrier-obligation}. This accounts for all
dependency, additive, translation, distinguished-triangle,
octahedral-ledger, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows in the public
surface.

Next apply
\autoref{thm:triangulatedcat-classifier-stability-obligation}. The classifier
is componentwise over those same rows, and its transport clauses repack the
transported histories as another accepted carrier.

Finally apply
\autoref{thm:triangulatedcat-octahedral-ledger-boundary} to identify the
octahedral part of the certificate. Since the boundary theorem permits only
logged faces, comparison morphisms, and $\Cont$ witnesses, the public
certificate has no remaining source for a host Verdier quotient or unlogged
octahedral datum.
\end{proof}
\leanchecked{BEDC.Derived.TriangulatedCatUp.TriangulatedCatFiniteCarrier\_obligation\_surface}

\closureat{TriangulatedCatUp}{seedStr}
\closureat{TriangulatedCatUp}{obligationStr}[BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_classifier\_stability]
\closureat{TriangulatedCatUp}{scopedStr}[BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_classifier\_stability]
\closureat{TriangulatedCatUp}{publicStr}[BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_classifier\_stability]
\closureat{TriangulatedCatUp}{publicStr}[BEDC.Derived.TriangulatedCatUp.TriangulatedCatFiniteCarrier\_obligation\_surface]
\closureat{TriangulatedCatUp}{bridgedStr}[BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_classifier\_stability]

\begin{closurestatus}{\TriangulatedCatUp}
  \constructivestory{A triangulated-category packet is generated from finite dependency rows for $\CategoryUp$ and $\DerivedCatUp$, additive and translation rows, distinguished-triangle rows, the logged octahedral faces, and the $\Cont/\mathsf{Pkg}$ provenance that makes those rows visible at the BEDC boundary.}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{The scoped boundary binds the finite $\mathsf{BHist}$ carrier, the additive and shift rows, the distinguished-triangle rows, the octahedral ledger, the componentwise $\hsame$ classifier, the $\Cont$ rows, the $\mathsf{Pkg}$ provenance row, and the dependency rows for $\CategoryUp$ and $\DerivedCatUp$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.TriangulatedCatUp.TriangulatedCatPacketCarrier\_classifier\_stability}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close host Verdier quotient semantics, ambient triangulated-category equality, or octahedral data not logged in the displayed packet.}
  \upgradepath{Mature closure requires downstream examples or a completeness boundary for the displayed additive, shift, triangle, octahedral-ledger, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ surface.}
\end{closurestatus}
