\chapter{A Concrete Naming Certificate for $\MonoidalCatUp$}
\label{ch:concrete-instances-monoidalcat-namecert}
\origin{human}

The monoidal-category interface $\MonoidalCatUp$ packages a category with a tensor-product bifunctor, unit object, and coherent associator and unitor isomorphisms. It depends on $\NameCert_{\CategoryUp}$ (\autoref{ch:concrete-instances-category-namecert}).

\section{Carrier definition}
\label{sec:monoidalcat-carrier}

\section{The certificate}
\label{sec:monoidalcat-certificate}

\begin{definition}[MonoidalCat singleton tensor instance]
\label{def:monoidalcat-singleton-tensor-instance}
The singleton $\mathsf{BHist}$ monoidal-category instance uses the unary-continuation category of \autoref{thm:category-unary-continuation-stability-law-package} as its underlying $\CategoryUp$ carrier. Its objects are carried unary histories, its displayed hom rows are $\mathsf{CategoryHomCarrier}(a,b,f)$ rows, and its tensor is continuation append:
$$
a\otimes b := \mathsf{append}(a,b),\qquad
f\otimes g := \mathsf{append}(f,g).
$$
The unit object is $\emp$. The associator row from $(x\otimes y)\otimes z$ to $x\otimes(y\otimes z)$ and the left and right unitor rows from $\emp\otimes x$ and $x\otimes\emp$ to $x$ are the $\hsame$ witnesses supplied by continuation associativity and the empty-continuation unit laws on the displayed $\mathsf{BHist}$ rows.
\end{definition}
\leandef{BEDC.Derived.MonoidalCatUp.MonoidalCatSingletonTensor}

\begin{theorem}[MonoidalCat singleton tensor carrier]
\label{thm:monoidalcat-singleton-tensor-carrier}
In the singleton tensor instance of \autoref{def:monoidalcat-singleton-tensor-instance}, tensoring carried unary objects remains a carried unary object. If
$$
\mathsf{CategoryHomCarrier}(a,b,f)
$$
and
$$
\mathsf{CategoryHomCarrier}(c,d,g)
$$
are displayed hom histories, then the tensor hom history $\mathsf{append}(f,g)$ is carried by the same unary-continuation hom surface from $\mathsf{append}(a,c)$ to $\mathsf{append}(b,d)$.
\end{theorem}
\leanchecked{BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_tensor\_carrier}
\begin{proof}
Unary object closure is the ordinary append closure for unary $\mathsf{BHist}$ rows.

For hom rows, first use the endpoint stability law package of \autoref{cor:category-hom-carrier-stability-law-package} to read both displayed morphisms as continuation tails over their endpoints. Then apply \autoref{thm:category-hom-carrier-comp-closed} to the compatible tail rows after appending the source and target endpoints.

The resulting composite row has exactly the source $\mathsf{append}(a,c)$, target $\mathsf{append}(b,d)$, and displayed morphism $\mathsf{append}(f,g)$ required by the tensor carrier surface.
\end{proof}

\begin{theorem}[MonoidalCat singleton tensor preserves identity homs]
\label{thm:monoidalcat-singleton-tensor-identity-hom}
In the singleton tensor instance of \autoref{def:monoidalcat-singleton-tensor-instance}, let $a$ and $b$ be carried unary objects. The tensor of the identity hom histories $\emp:a\to a$ and $\emp:b\to b$ is classified as the identity hom on $a\otimes b$. Concretely, $\mathsf{append}(\emp,\emp)$ is $\hsame$ to $\emp$, and the row gives
$$
\mathsf{CategoryHomCarrier}(\mathsf{append}(a,b),\mathsf{append}(a,b),\emp).
$$
\end{theorem}
\leanchecked{BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_tensor\_identity\_hom}
\begin{proof}
The identity rows for $a$ and $b$ are the empty continuation rows supplied by \autoref{thm:category-unary-continuation-stability-law-package}. Unary append closure gives the tensor object $\mathsf{append}(a,b)$ as a carried unary object.

Tensoring the two displayed identity histories gives $\mathsf{append}(\emp,\emp)$. The empty-continuation unit laws of \autoref{thm:concrete-history-monoid-laws} identify this displayed history with $\emp$ by $\hsame$.

Transport the identity row on $\mathsf{append}(a,b)$ along that $\hsame$ classifier row. The resulting displayed hom carrier is exactly $\mathsf{CategoryHomCarrier}(\mathsf{append}(a,b),\mathsf{append}(a,b),\emp)$, so the tensor preserves identity hom histories on the concrete singleton carrier.
\end{proof}

\begin{theorem}[MonoidalCat singleton associator and unitors]
\label{thm:monoidalcat-singleton-associator-unitors}
For carried unary histories $x$, $y$, and $z$ in the singleton tensor instance, the displayed histories $(x\otimes y)\otimes z$ and $x\otimes(y\otimes z)$ are related by $\hsame$. The displayed histories $\emp\otimes x$ and $x\otimes\emp$ are each related to $x$ by $\hsame$ on the same concrete $\mathsf{BHist}$ carrier.
\end{theorem}
\begin{proof}
The associator row is continuation associativity applied to the three visible tails $x$, $y$, and $z$. Both bracketings reduce to the same iterated continuation history, so the classifier row is the corresponding $\hsame$ witness.

For the left unitor, use the left empty-continuation law to identify $\mathsf{append}(\emp,x)$ with $x$. For the right unitor, use the right empty-continuation law to identify $\mathsf{append}(x,\emp)$ with $x$.

The category continuation-morphism tail theorems transport these three $\hsame$ rows through the displayed hom carrier, so the associator and both unitors live on the concrete unary-continuation category rather than on an external categorical carrier.
\end{proof}
\leanchecked{BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_associator\_unitors}

\begin{theorem}[MonoidalCat singleton coherence laws]
\label{thm:monoidalcat-singleton-coherence-laws}
In the singleton tensor instance, the pentagon and triangle diagrams commute under the morphism classifier. For any carried unary histories appearing in either diagram, the two displayed paths have $\hsame$-equal classifier rows because both paths reduce to the same iterated $\ContR$ tail.
\end{theorem}
\begin{proof}
For the pentagon, expand each edge into the associator row of \autoref{thm:monoidalcat-singleton-associator-unitors}. The two boundary paths are the two standard ways to reassociate a fourfold continuation tail, and the category fourfold associativity witness \autoref{thm:category-hom-carrier-fourfold-assoc-witness} identifies their displayed histories by $\hsame$.

For the triangle, expand the associator and the two unitor rows. The left path and the right path both normalize to the same twofold continuation tail after applying the empty-continuation unit laws.

Finally compose the classifier rows by transitivity of $\hsame$. The displayed hom carrier is preserved along the comparison by the category stability law package, so the commuting diagrams are certified inside the BEDC morphism classifier.
\end{proof}
\leanchecked{BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_coherence\_laws}

\begin{theorem}[MonoidalCat NameCert obligation surface]
\label{thm:monoidalcat-namecert-obligation-surface}
The singleton tensor instance assembles the following paper-side $\NameCert_{\MonoidalCatUp}$ obligation surface:
\begin{enumerate}
  \item Traditional target: a monoidal category.
  \item BEDC source: $\CategoryUp$, $\ContR$, $\hsame$, and $\mathsf{CategoryHomCarrier}$.
  \item Carrier: unary $\mathsf{BHist}$ objects and continuation hom histories.
  \item Classifier: $\hsame$ on displayed object and hom histories.
  \item Stability: tensor carrier closure, identity-hom preservation, composition preservation, associator rows, unitor rows, pentagon coherence, and triangle coherence.
  \item Ledger: tensor tails and the two coherence-path ledgers.
  \item Core theorem list: \autoref{thm:monoidalcat-singleton-tensor-carrier}, \autoref{thm:monoidalcat-singleton-tensor-identity-hom}, \autoref{thm:monoidalcat-singleton-tensor-preserves-composition}, \autoref{thm:monoidalcat-singleton-associator-unitors}, \autoref{thm:monoidalcat-singleton-coherence-laws}, and \autoref{thm:category-unary-continuation-stability-law-package}.
  \item Exactness: classifier equality of the displayed coherence paths.
  \item Standard bridge: absent.
  \item Status: paper-side obligation surface.
\end{enumerate}
\end{theorem}
\begin{proof}
The carrier and classifier fields are supplied by the unary-continuation category and its $\mathsf{CategoryHomCarrier}$ rows. The tensor field is the append operation in \autoref{def:monoidalcat-singleton-tensor-instance}.

The stability fields are discharged by \autoref{thm:monoidalcat-singleton-tensor-carrier}, \autoref{thm:monoidalcat-singleton-tensor-identity-hom}, \autoref{thm:monoidalcat-singleton-tensor-preserves-composition}, and \autoref{thm:monoidalcat-singleton-associator-unitors}. The coherence fields are discharged by \autoref{thm:monoidalcat-singleton-coherence-laws}.

The ledger records only the displayed continuation tails and the two coherence paths. Exactness is the statement that the two paths in each coherence diagram are equal under $\hsame$, and no standard external monoidal-category bridge is asserted here.
\end{proof}
\leanchecked{BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_semantic\_name\_certificate}

\begin{theorem}[MonoidalCat singleton tensor preserves composition]
\label{thm:monoidalcat-singleton-tensor-preserves-composition}
In the singleton tensor instance of \autoref{def:monoidalcat-singleton-tensor-instance}, suppose
$$
\mathsf{CategoryHomCarrier}(a_0,a_1,f),\quad
\mathsf{CategoryHomCarrier}(a_1,a_2,f'),\quad
\mathsf{CategoryHomCarrier}(c_0,c_1,g),\quad
\mathsf{CategoryHomCarrier}(c_1,c_2,g')
$$
are two composable pairs of displayed hom rows. Then the tensor composite and the tensor of component composites are both displayed hom rows from $\mathsf{append}(a_0,c_0)$ to $\mathsf{append}(a_2,c_2)$, and their morphism classifiers agree:
$$
\begin{gathered}
\mathsf{CategoryHomCarrier}
  (\mathsf{append}(a_0,c_0),\mathsf{append}(a_2,c_2),
   \mathsf{append}(\mathsf{append}(f,g),\mathsf{append}(f',g'))),\\
\mathsf{CategoryHomCarrier}
  (\mathsf{append}(a_0,c_0),\mathsf{append}(a_2,c_2),
   \mathsf{append}(\mathsf{append}(f,f'),\mathsf{append}(g,g'))),\\
\HSame(\mathsf{append}(\mathsf{append}(f,g),\mathsf{append}(f',g')),
       \mathsf{append}(\mathsf{append}(f,f'),\mathsf{append}(g,g'))).
\end{gathered}
$$
Equivalently, $(f\otimes g)$ followed by $(f'\otimes g')$ is classifier-equal to $(f'\circ f)\otimes(g'\circ g)$ in the concrete singleton $\MonoidalCatUp$ certificate.
\end{theorem}
\leanchecked{BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_tensor\_preserves\_composition}
\begin{proof}
By \autoref{thm:monoidalcat-singleton-tensor-carrier}, the tensor rows $\mathsf{append}(f,g)$ and $\mathsf{append}(f',g')$ are hom-carriers from $\mathsf{append}(a_0,c_0)$ to $\mathsf{append}(a_1,c_1)$ and from $\mathsf{append}(a_1,c_1)$ to $\mathsf{append}(a_2,c_2)$. Applying \autoref{thm:category-hom-carrier-comp-closed} to these two tensor rows gives the first displayed carrier.

Applying \autoref{thm:category-hom-carrier-comp-closed} to the pair $f,f'$ gives the component composite $\mathsf{append}(f,f')$ from $a_0$ to $a_2$, and applying it to $g,g'$ gives $\mathsf{append}(g,g')$ from $c_0$ to $c_2$. A second use of \autoref{thm:monoidalcat-singleton-tensor-carrier} gives the second displayed carrier.

It remains to compare the displayed morphism histories. The four input hom-carrier rows expose unary membership of $f$, $f'$, $g$, and $g'$. Hence \autoref{thm:unary-commutativity-refined}, applied to the canonical append continuations for $g$ followed by $f'$ and for $f'$ followed by $g$, gives
$$
\HSame(\mathsf{append}(g,f'),\mathsf{append}(f',g)).
$$
Repeated use of \autoref{thm:continuation-associativity} identifies the tensor composite with
$$
\mathsf{append}(f,\mathsf{append}(\mathsf{append}(g,f'),g'))
$$
and identifies the tensor of component composites with
$$
\mathsf{append}(f,\mathsf{append}(\mathsf{append}(f',g),g')).
$$
The reverse direction of \autoref{thm:append-hsame-common-context-cancel}, with common left context $f$ and common right context $g'$, transports the middle comparison into the two displayed fourfold histories. Transitivity of $\HSame$ with the two associativity comparisons gives the required classifier equality.
\end{proof}

\begin{theorem}[MonoidalCat singleton standard bridge]
\label{thm:monoidalcat-singleton-standard-bridge}
The singleton continuation tensor package of \autoref{def:monoidalcat-singleton-tensor-instance}, together with the tensor carrier row of \autoref{thm:monoidalcat-singleton-tensor-carrier}, the associator and unitor rows of \autoref{thm:monoidalcat-singleton-associator-unitors}, the coherence rows of \autoref{thm:monoidalcat-singleton-coherence-laws}, the semantic certificate of \autoref{thm:monoidalcat-namecert-obligation-surface}, and the tensor composition row of \autoref{thm:monoidalcat-singleton-tensor-preserves-composition}, determines the standard bridge rows for $\MonoidalCatUp$ on the singleton BEDC surface.

The bridge reads objects as unary-history rows, morphisms as displayed unary-history hom rows, tensor as $\Cont$ append, the unit as $\emp$, and equality as $\hsame$. It exports exactly this singleton continuation package and no non-singleton monoidal category, host bifunctor, external object carrier, or ambient categorical coherence data.
\end{theorem}
\begin{proof}
The carrier theorem supplies the object and morphism rows: carried unary histories remain carried after tensor append, and displayed hom histories tensor by appending their $\Cont$ tails.

The associator and unitor theorem supplies the structural comparison rows. The coherence theorem identifies the pentagon and triangle boundary paths by $\hsame$, so the bridge has the standard coherence entries required for the singleton tensor surface.

The semantic certificate records the visible $\NameCert_{\MonoidalCatUp}$ carrier, classifier, stability, ledger, and exactness rows. The tensor-preserves-composition theorem supplies the bifunctorial composition row on the same displayed histories, while the identity-hom theorem supplies the identity row.

Thus every bridge entry is a row already present in the singleton continuation package: objects and morphisms are unary-history rows, tensor is $\Cont$ append, unit is $\emp$, and equality is $\hsame$. Because no carrier coordinate names non-singleton objects or a host bifunctor, the bridge exports none of that data.
\end{proof}
\leanchecked{BEDC.Derived.MonoidalCatUp.MonoidalCatUp\_StdBridge}

\begin{theorem}[MonoidalCat singleton tensor consumer coverage]
\label{thm:monoidalcat-singleton-tensor-consumer-coverage}
Every consumer read of the singleton tensor bridge of
\autoref{thm:monoidalcat-singleton-standard-bridge} is one of the unary object
rows, unary hom rows, $\Cont$ tensor rows, $\emp$ unit rows, $\hsame$
associator, unitor, and coherence rows, identity-hom rows,
composition-preservation rows, or the semantic $\NameCert$ ledger already
listed for $\MonoidalCatUp$.

The covered surface exports exactly the singleton continuation tensor package
and no non-singleton object carrier, host bifunctor, external coherence object,
or ambient monoidal-category structure.
\end{theorem}
\begin{proof}
Use \autoref{thm:monoidalcat-singleton-tensor-carrier} for the unary object and
hom rows and for tensor as continuation append. The identity-hom reads are the
rows of \autoref{thm:monoidalcat-singleton-tensor-identity-hom}.

Use \autoref{thm:monoidalcat-singleton-associator-unitors} and
\autoref{thm:monoidalcat-singleton-coherence-laws} for the associator, unitor,
pentagon, and triangle rows. These rows are $\hsame$ comparisons over the same
unary-history surface.

Use \autoref{thm:monoidalcat-singleton-tensor-preserves-composition} for the
composition-preservation readers and
\autoref{thm:monoidalcat-namecert-obligation-surface} for the semantic
certificate ledger. The standard bridge of
\autoref{thm:monoidalcat-singleton-standard-bridge} collects exactly these
rows, so the listed families exhaust all consumer reads.
\end{proof}

\closureat{MonoidalCatUp}{scopedStr}[BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_semantic\_name\_certificate]
\closureat{MonoidalCatUp}{publicStr}[BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_semantic\_name\_certificate]
\closureat{MonoidalCatUp}{bridgedStr}[BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_semantic\_name\_certificate]
\closureat{MonoidalCatUp}{matureStr}[BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_semantic\_name\_certificate]

\begin{closurestatus}{\MonoidalCatUp}
  \constructivestory{A monoidal category at this seed level is the unary-continuation category with tensor given by appending the underlying histories: carried unary objects tensor to $\mathsf{append}(a,b)$, carried hom histories tensor to $\mathsf{append}(f,g)$, and the unit object is $\emp$. The carrier therefore accepts only the singleton tensor instance whose objects and morphisms are already admitted by the $\CategoryUp$ continuation surface, while non-singleton monoidal categories and host bifunctor data remain outside the seed. Two displayed tensor rows are classified by the same history-equality used for the category object and hom rows; associator and unitor comparisons are the $\hsame$ witnesses supplied by continuation associativity and the empty-continuation laws, not an imported coherence theorem. The source is $\CategoryUp$ over unary histories, the pattern records tensor closure, identity-hom preservation, composition preservation, associator, unitors, pentagon, and triangle rows, and the ledger keeps the tensor tails and the two coherence-path ledgers visible. Because $\emp$ is carried, unary histories are closed under append, and $\hsame$ is an equivalence transported through the hom carrier, the five name-certificate obligations are obtained by the same componentwise carrier witness, reflexive/symmetric/transitive classifier, and closure under classified tensor representatives. A row $h$ lies in the signature gap of a $\MonoidalCatUp$ token $p$ when the source-domain accepts the unary category and tensor ledgers, the signature relation pairs the singleton tensor package with an answer package and evidence ledger, and the token-introduction relation names that answer as $p$; concretely, $p$ encodes the continuation tensor together with its associator, unitor, and coherence rows. The chapter registers this singleton continuation tensor under the name $\MonoidalCatUp$ with a paper-side standard bridge whose rows are precisely unary objects, unary hom histories, $\Cont$ append tensor, $\emp$ unit, and $\hsame$ equality; it does not register a general monoidal-category carrier.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The mature surface is the singleton standard bridge for $\MonoidalCatUp$: tensor carrier, identity-hom, tensor-composition, associator, unitor, coherence, semantic certificate, and singleton bridge rows over the CategoryUp continuation surface and the kernel $\Cont$ and $\hsame$ dependencies used by those rows.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.MonoidalCatUp.MonoidalCatSingleton\_semantic\_name\_certificate}
  \bridgestatus{bridgeChecked}
  \notclaimed{This chapter does not close an external standard model, host bifunctor data, or non-singleton monoidal categories.}
  \upgradepath{No further formal-axis upgrade is pending for the checked singleton continuation-tensor bridge.}
\end{closurestatus}
