\chapter{A Concrete Naming Certificate for $\RegularLimitUniquenessUp$}
\label{ch:concrete-instances-regular-limit-uniqueness-namecert}
\origin{human}

The $\RegularLimitUniquenessUp$ interface records the separated uniqueness side of regular-Cauchy completion. In the Bishop--Bridges constructive-analysis presentation, a completed real is read through finite regular-name windows and explicit moduli; uniqueness is therefore a visible separated-seal certificate over two accepted completion candidates, not a quotient of streams or a selected host limit.

The packet compares two diagonal completion candidates only after their regular rational readbacks from \autoref{ch:concrete-instances-regseqrat-namecert} pass through the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the diagonal route of \autoref{ch:concrete-instances-real-diagonal-completion-namecert}, the shared family surface of \autoref{ch:concrete-instances-regularcauchyfamily-namecert}, the separated boundary of \autoref{ch:concrete-instances-hausdorffcompletion-namecert}, and the $\RealUp$ seal rows of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[RegularLimitUniqueness carrier]
\label{def:regular-limit-uniqueness-carrier}
A $\RegularLimitUniquenessUp$ carrier is a finite $\BHist$ packet
$$
U=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $F$ is the shared $\RegularCauchyFamilyUp$ input row;
\item $D_0$ and $D_1$ are two $\RealDiagonalCompletionUp$ candidate limit rows for the same $F$;
\item $\mu$ is the shared $\CauchyModulusUp$ threshold row controlling the tail windows compared by both candidates;
\item $R_0$ and $R_1$ are the $\RegSeqRatUp$ readback rows exposed by the two diagonal candidates at the threshold selected by $\mu$;
\item $E_0$ and $E_1$ are the two $\RealUp$ seal rows reached from those readbacks;
\item $S$ is the separated comparison row, read through the $\HausdorffCompletionUp$ boundary, stating that $E_0$ and $E_1$ classify at the same separated real seal;
\item $H$ records the displayed $\hsame$ transports tying $F$, $\mu$, the two diagonal rows, the two readbacks, the two seals, and the separated comparison together;
\item $C$ records the displayed $\Cont$ routes through the shared family, threshold row, diagonal candidates, readback rows, real seals, and separated comparison;
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyFamilyUp$, $\CauchyModulusUp$, $\RealDiagonalCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\HausdorffCompletionUp$, $\RealUp$, $\BHist$, $\hsame$, and $\Cont$;
\item $N$ is the local $\NameCert_{\RegularLimitUniquenessUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient streams, a chosen host limit, host real equality, or choice. Its public data are exactly the displayed finite rows above.
\end{definition}

\begin{theorem}[RegularLimitUniqueness NameCert obligations]
\label{thm:regular-limit-uniqueness-namecert-obligations}
The local $\NameCert_{\RegularLimitUniquenessUp}$ surface has five finite obligations:
\begin{enumerate}
\item habitation by a displayed diagonal candidate pair over the carrier of \autoref{def:regular-limit-uniqueness-carrier};
\item classifier laws obtained by componentwise $\hsame$ transport of the shared family, threshold row, diagonal candidates, readbacks, real seals, separated comparison, continuation routes, package provenance, and local naming row;
\item carrier transport through the displayed routes from $\RegularCauchyFamilyUp$ to $\RealDiagonalCompletionUp$, then through $\RegSeqRatUp$ and $\StreamNameUp$ readbacks to the two $\RealUp$ seals;
\item exactness through the separated $\RealUp$ classifier row $S$, so the two accepted candidates are compared only at the displayed separated seal;
\item ledger non-escape excluding quotient streams, selected host limits, host real equality, and choice.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_namecert\_obligations}
\begin{proof}
Carrier habitation is projection of \autoref{def:regular-limit-uniqueness-carrier}. The shared family row, the two diagonal candidates, the common threshold, the two readbacks, the two seals, the separated comparison, transport rows, continuation routes, package provenance, and local certificate are finite coordinates of the same $\BHist$ packet.

Classifier stability is componentwise. Transport the shared $\RegularCauchyFamilyUp$ and $\CauchyModulusUp$ rows first, then move the two $\RealDiagonalCompletionUp$ rows and their $\RegSeqRatUp$ readbacks along the displayed $\hsame$ rows while replaying the corresponding $\Cont$ routes.

Exactness is the separated-seal step. The only row that compares the two completion candidates after readback is $S$, and $S$ is a displayed $\RealUp$ classifier row read through the $\HausdorffCompletionUp$ boundary.

The non-escape clauses follow from the carrier list. No coordinate contains a quotient of regular streams, a selected host limit, host real equality, or a choice principle, so the local certificate can export only the listed BEDC rows.
\end{proof}

\begin{theorem}[RegularLimitUniqueness separated limit certificate]
\label{thm:regular-limit-uniqueness-separated-limit-certificate}
Let $U$ be an accepted $\RegularLimitUniquenessUp$ carrier. Suppose two accepted $\RealDiagonalCompletionUp$ candidates in $U$ read the same $\RegularCauchyFamilyUp$ input through the shared $\CauchyModulusUp$ threshold and reach the same separated boundary row $S$. Then their $\RegSeqRatUp$ readbacks classify through the same $\RealUp$ seal: the two candidate limits are identified exactly by the displayed separated $\RealUp$ classifier row, with visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

The certificate exports no quotient stream comparison, selected host limit, host real equality, ambient completeness principle, or choice.
\end{theorem}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_separated\_limit\_certificate}
\begin{proof}
Project $U$ as in \autoref{def:regular-limit-uniqueness-carrier}. Both candidates point to the same $\RegularCauchyFamilyUp$ row $F$ and the same $\CauchyModulusUp$ threshold $\mu$, so their readback routes begin at one displayed regular-Cauchy input surface.

Read each candidate through its diagonal row. The two $\RealDiagonalCompletionUp$ coordinates expose the corresponding $\RegSeqRatUp$ readbacks and $\StreamNameUp$ windows, and the stored $\hsame$ and $\Cont$ rows keep those reads attached to the shared family and threshold.

Now use the separated comparison row $S$. It is the only accepted comparison between $E_0$ and $E_1$, and it lives at the $\RealUp$ seal boundary through the $\HausdorffCompletionUp$ separated surface.

Repacking this route gives the stated certificate. Since the carrier contains no quotient, selected host limit, host real equality, ambient completeness, or choice coordinate, the equality claim is precisely the displayed separated classifier claim and nothing stronger.
\end{proof}

\begin{theorem}[RegularLimitUniqueness classifier determinacy]
\label{thm:regular-limit-uniqueness-classifier-determinacy}
Let $U$ and $U'$ be accepted $\RegularLimitUniquenessUp$ carriers whose displayed $\hsame$ and $\Cont$ rows classify the shared $\RegularCauchyFamilyUp$ input, the shared $\CauchyModulusUp$ threshold, the two $\RealDiagonalCompletionUp$ candidates, their $\RegSeqRatUp$ readbacks, their $\RealUp$ seals, and their separated comparison rows. Then the two carriers determine the same separated limit route: every classified candidate pair reaches the corresponding $\RealUp$ seals through the displayed separated comparison row and through no additional host equality or chosen limit.
\end{theorem}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_classifier\_determinacy}
\begin{proof}
Project both carriers using \autoref{def:regular-limit-uniqueness-carrier}. The family row, threshold row, diagonal candidate rows, readback rows, seal rows, separated comparison rows, transport rows, continuation rows, package rows, and local certificates are all visible coordinates.

Apply the classifier obligations of \autoref{thm:regular-limit-uniqueness-namecert-obligations}. Componentwise transport moves the shared family and threshold first, then moves each diagonal candidate, readback, seal, and separated comparison row along the displayed routes.

Now apply \autoref{thm:regular-limit-uniqueness-separated-limit-certificate} to either classified carrier. The separated comparison row is the only route that identifies the two candidate seals, so classification determines the same separated limit route without adding host equality, a quotient stream, or a selected limit.
\end{proof}

\begin{theorem}[RegularLimitUniqueness completion consumer boundary]
\label{thm:regular-limit-uniqueness-completion-consumer-boundary}
Every completion consumer that reads a $\RegularLimitUniquenessUp$ packet can inspect only the displayed $\RegSeqRatUp$ readback rows, $\RealDiagonalCompletionUp$ candidate rows, $\RealUp$ seal rows, shared family and threshold rows, separated comparison row, and the recorded $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. The packet exports no quotient completion object, selected host limit, host real equality, ambient completeness principle, or choice witness.
\end{theorem}
\begin{proof}
Read the carrier inventory. The completion-facing coordinates are the two $\RealDiagonalCompletionUp$ candidates and their $\RegSeqRatUp$ readbacks over the shared family and threshold, followed by the two $\RealUp$ seal rows and the separated comparison row.

The separated-limit certificate of \autoref{thm:regular-limit-uniqueness-separated-limit-certificate} consumes exactly those rows. It compares the candidate seals only after their readbacks have passed through the displayed diagonal and stream-name routes.

The non-exported objects are absent from the carrier. Since no coordinate contains a quotient completion, selected host limit, host real equality, ambient completeness theorem, or choice witness, no completion consumer can obtain one from the packet.
\end{proof}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_completion\_consumer\_boundary}

\begin{theorem}[RegularLimitUniqueness separated transport]
\label{thm:regular-limit-uniqueness-separated-transport}
Separatedness in a $\RegularLimitUniquenessUp$ carrier transports through the displayed $\hsame$ and $\Cont$ rows. If the separated comparison row $S$ identifies the two $\RealUp$ seals reached from one accepted carrier, then any classified carrier carries the transported separated comparison for the transported seals, without introducing host-level equality or a quotient of regular streams.
\end{theorem}
\begin{proof}
Begin with the separated comparison row $S$ in an accepted carrier. By \autoref{thm:regular-limit-uniqueness-separated-limit-certificate}, $S$ sits after the shared family, threshold, diagonal candidates, regular readbacks, and two real seal rows.

Transport each upstream coordinate through the displayed $\hsame$ rows and replay the corresponding $\Cont$ routes. The classifier obligations of \autoref{thm:regular-limit-uniqueness-namecert-obligations} keep the separated comparison attached to the transported seals and to the same package and local certificate rows.

The transported statement is again a separated $\RealUp$ classifier claim. It does not become a host equality statement, and it does not require a quotient of the regular-stream readbacks.
\end{proof}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_separated\_transport}

\begin{theorem}[RegularLimitUniqueness obligation closure package]
\label{thm:regular-limit-uniqueness-obligation-closure-package}
The $\RegularLimitUniquenessUp$ packet of \autoref{def:regular-limit-uniqueness-carrier}, together with the local $\NameCert_{\RegularLimitUniquenessUp}$ obligations of \autoref{thm:regular-limit-uniqueness-namecert-obligations}, the separated-limit certificate of \autoref{thm:regular-limit-uniqueness-separated-limit-certificate}, classifier determinacy of \autoref{thm:regular-limit-uniqueness-classifier-determinacy}, the completion consumer boundary of \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary}, and separated transport of \autoref{thm:regular-limit-uniqueness-separated-transport}, presents the five displayed obligation rows required by the regular-limit uniqueness surface:
\begin{enumerate}
\item carrier habitation for the finite row
$$
U=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N);
$$
\item classifier transport along the recorded $\hsame$ rows and replayed $\Cont$ routes for $F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N$;
\item readback-to-seal exactness from each $\RealDiagonalCompletionUp$ candidate through its displayed $\RegSeqRatUp$ and $\StreamNameUp$ readback into the corresponding $\RealUp$ seal;
\item separated comparison exactness through the single displayed row $S$ at the $\HausdorffCompletionUp$ boundary;
\item ledger non-escape for quotient streams, selected host limits, host real equality, ambient completeness, and choice witnesses.
\end{enumerate}
These rows are sufficient as the paper-side obligation package for later scoped closure of the same regular-limit uniqueness claim.
\end{theorem}
\begin{proof}
The carrier habitation row is the finite packet displayed in \autoref{def:regular-limit-uniqueness-carrier}. The first NameCert obligation of \autoref{thm:regular-limit-uniqueness-namecert-obligations} supplies the accepted carrier instance over that packet.

Classifier transport is the second and third obligation row of \autoref{thm:regular-limit-uniqueness-namecert-obligations}, refined by \autoref{thm:regular-limit-uniqueness-classifier-determinacy} and \autoref{thm:regular-limit-uniqueness-separated-transport}. These results keep the family, threshold, diagonal candidates, readbacks, real seals, separated comparison, package row, and local naming row attached to the same displayed $\BHist$ surface.

Readback-to-seal exactness follows from \autoref{thm:regular-limit-uniqueness-separated-limit-certificate}. Each diagonal candidate is read through its $\RegSeqRatUp$ and $\StreamNameUp$ rows before it reaches a $\RealUp$ seal, so the certificate never compares unsealed host objects.

Separated comparison exactness is the role of $S$. The comparison occurs only at the separated $\RealUp$ classifier row, read through the $\HausdorffCompletionUp$ boundary.

Ledger non-escape is the completion-facing boundary of \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary}. Every consumer route is a route through the listed BEDC rows, so the packet exports no quotient stream, selected host limit, host equality, ambient completeness theorem, or choice witness.
\end{proof}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_obligation\_closure\_package}

\begin{theorem}[RegularLimitUniqueness readback seal exactness]
\label{thm:regular-limit-uniqueness-readback-seal-exactness}
Let $U=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N)$ be an accepted $\RegularLimitUniquenessUp$ carrier. If $D_0$ and $D_1$ are two diagonal completion candidates over the same regular family row $F$ and threshold row $\mu$, then the packet can identify the candidates only through the displayed $\RegSeqRatUp$ readbacks $R_0,R_1$ and the separated $\RealUp$ seal row $S$ comparing $E_0$ and $E_1$.

No identification route in the packet bypasses $R_0,R_1,E_0,E_1,S$, and no route factors through host real equality, a selected host limit, a quotient stream, ambient completeness, or choice.
\end{theorem}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_readback\_seal\_exactness}
\begin{proof}
Project the accepted carrier. The two candidates share the same $F$ and $\mu$ coordinates, and their readback rows are explicitly $R_0$ and $R_1$.

The diagonal rows expose only the displayed regular-rational readbacks before reaching real seals. The $\hsame$ and $\Cont$ coordinates keep those readbacks tied to the same family and threshold, but they do not add a separate equality object.

The separated comparison row is $S$. By \autoref{thm:regular-limit-uniqueness-separated-limit-certificate}, candidate identification occurs after the readbacks reach $E_0$ and $E_1$, and the comparison is exactly the separated $\RealUp$ classifier row.

The exclusion statement follows from the ledger boundary in \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary}. The omitted host and quotient objects are not coordinates of $U$.
\end{proof}

\begin{theorem}[RegularLimitUniqueness dyadic-window separation pullback]
\label{thm:regular-limit-uniqueness-dyadic-window-separation-pullback}
Let $U=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N)$ be an accepted $\RegularLimitUniquenessUp$ packet. Suppose the two candidate routes share the $\StreamNameUp$ finite-window rows, the $\RegSeqRatUp$ readback rows, the $\DyadicRatCoreUp$ observation ledger read by those windows, and the $\HausdorffCompletionUp$ separated comparison row whose endpoint is the $\RealUp$ seal comparison $S$.

Then every completion consumer reaches the same $\RealUp$ seal comparison through that finite pullback surface. The consumer route is forced through $R_0,R_1,E_0,E_1,S$ and through the shared $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of $U$; it cannot be replaced by quotient streams, selected host limits, host real equality, ambient completeness, or choice.
\end{theorem}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_dyadic\_window\_separation\_pullback}
\begin{proof}
First apply \autoref{thm:regular-limit-uniqueness-readback-seal-exactness}. The accepted packet identifies the two diagonal candidates only after the displayed readbacks $R_0,R_1$ reach the seal rows $E_0,E_1$ and the separated comparison row $S$.

Next apply \autoref{thm:regular-limit-uniqueness-shared-family-scope}. The common family row $F$, threshold row $\mu$, both diagonal candidates, and their transport, continuation, package, and naming rows remain inside the same $\RegularLimitUniquenessUp$ packet.

The finite pullback is supplied by \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback} and \autoref{thm:streamname-regseqrat-real-dyadic-pullback-seal-determinacy}. The shared $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, $\DyadicRatCoreUp$ ledger, and $\RealUp$ seal rows determine one finite surface for downstream seal comparison.

Finally use the completion consumer boundary from \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary}. Since every consumer has already been routed through the displayed finite surface, no quotient stream, selected host limit, host equality, ambient completeness row, or choice witness can enter the uniqueness comparison.
\end{proof}

\begin{theorem}[RegularLimitUniqueness seal-selector pullback]
\label{thm:regular-limit-uniqueness-seal-selector-pullback}
Let $U=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N)$ be an accepted $\RegularLimitUniquenessUp$ packet. Suppose the two candidate routes share the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ readback rows, the $\RealDiagonalCompletionUp$ candidate rows, the $\DiagonalLimitUp$ completion-seal factorization row, the $\HausdorffCompletionUp$ separated row, and the $\RealUp$ seal comparison row $S$.

Then every uniqueness consumer factors through the single finite selector-pullback surface
$$
F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N.
$$
The surface is obtained by first routing the comparison through the dyadic-window separation pullback, then through the checked $\DiagonalLimitUp$ completion-seal factorization, and finally through the $\RegularLimitUniquenessUp$ completion-consumer boundary. It exports no quotient stream, selected host limit, host real equality, ambient completeness principle, or choice witness.
\end{theorem}
\begin{proof}
Project the accepted packet $U$. Its carrier exposes exactly the shared family row, the two diagonal completion candidates, the threshold row, the readback rows, the two seal rows, the separated comparison row $S$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

Apply \autoref{thm:regular-limit-uniqueness-dyadic-window-separation-pullback}. This routes each uniqueness consumer through the common $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, $\DyadicRatCoreUp$ ledger, and separated $\RealUp$ comparison row before any completion-facing comparison is exposed.

Next compose that finite window route with \autoref{thm:diagonallimit-completion-seal-factorization}. The checked $\DiagonalLimitUp$ factorization makes the $\RealUp$ seal read pass through the $\RealDiagonalCompletionUp$ packet and the displayed $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$ rows, so the selector route is the same finite pullback surface rather than an independent host-limit route.

Finally use \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary}. Since the consumer boundary lists only the displayed carrier, transport, continuation, package, and naming rows, the composed selector-pullback route cannot import quotient streams, selected host limits, host real equality, ambient completeness, or choice.
\end{proof}

\begin{theorem}[RegularLimitUniqueness choice-free ledger exhaustion]
\label{thm:regular-limit-uniqueness-choice-free-ledger-exhaustion}
Every completion consumer route exported by an accepted $\RegularLimitUniquenessUp$ packet is exhausted by
$$
F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N,
$$
by the ambient $\BHist$ packet structure, by $\hsame$ transport, by $\Cont$ continuation, by $\Pkg$ provenance, and by the local $\NameCert_{\RegularLimitUniquenessUp}$ row. The packet contains no quotient stream, selected host limit, host equality, ambient completeness principle, or choice witness.
\end{theorem}
\begin{proof}
Inspect the carrier in \autoref{def:regular-limit-uniqueness-carrier}. Its named coordinates are exactly the displayed family, candidate, threshold, readback, seal, comparison, transport, continuation, package, and local certificate rows.

The consumer boundary theorem \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary} says that a completion consumer can inspect only those rows and their $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. The separated transport theorem \autoref{thm:regular-limit-uniqueness-separated-transport} keeps the same inventory after classifier movement.

Therefore every exported route is already listed in the carrier ledger. Since quotient streams, selected host limits, host equality, ambient completeness, and choice are not listed coordinates, no consumer route can recover them from the packet.
\end{proof}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_choice\_free\_ledger\_exhaustion}

\begin{theorem}[RegularLimitUniqueness shared family scope]
\label{thm:regular-limit-uniqueness-shared-family-scope}
The carrier and classifier rows of \autoref{def:regular-limit-uniqueness-carrier}, \autoref{thm:regular-limit-uniqueness-namecert-obligations}, and \autoref{thm:regular-limit-uniqueness-classifier-determinacy} form the shared-family scope for $\RegularLimitUniquenessUp$. This scope binds the common $\RegularCauchyFamilyUp$ input, the two $\RealDiagonalCompletionUp$ candidate rows, their $\RegSeqRatUp$ and $\StreamNameUp$ readbacks, the two $\RealUp$ seal rows, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance into one finite uniqueness packet.

The scope exports the family comparison needed by the L10 dependency stack without adding a quotient of streams, a selected host limit, host real equality, or choice.
\end{theorem}
\begin{proof}
Start with the carrier inventory of \autoref{def:regular-limit-uniqueness-carrier}. Its coordinates contain the shared family row, both diagonal candidates, both readbacks, both real seals, and the displayed transport, continuation, package, and naming rows.

Apply the local naming obligations of \autoref{thm:regular-limit-uniqueness-namecert-obligations}. They identify habitation, classifier transport, carrier transport, separated exactness, and ledger non-escape as rows of that same finite packet.

Finally use \autoref{thm:regular-limit-uniqueness-classifier-determinacy}. Classification cannot move the two candidates outside the shared family surface, so the listed rows are the complete shared-family scope for the regular-limit uniqueness consumer.
\end{proof}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_shared\_family\_scope}

\begin{theorem}[RegularLimitUniqueness separated comparison scope]
\label{thm:regular-limit-uniqueness-separated-comparison-scope}
The separated comparison rows of \autoref{thm:regular-limit-uniqueness-separated-limit-certificate}, \autoref{thm:regular-limit-uniqueness-separated-transport}, and \autoref{thm:regular-limit-uniqueness-readback-seal-exactness} bind the uniqueness comparison to the concrete route
$$
\RegularCauchyFamilyUp \longrightarrow \RealDiagonalCompletionUp \longrightarrow \RegSeqRatUp,\StreamNameUp \longrightarrow \RealUp
$$
with displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. Thus the separated seal comparison is scoped exactly by the two readbacks, the two real seals, and the row $S$; it has no bypass through host equality or an unrecorded completion object.
\end{theorem}
\begin{proof}
First read the two completion candidates through \autoref{thm:regular-limit-uniqueness-separated-limit-certificate}. The certificate forces both candidates to share the same family and threshold before their readbacks reach the two real seals.

Next apply \autoref{thm:regular-limit-uniqueness-readback-seal-exactness}. It makes $R_0,R_1,E_0,E_1,S$ the only identification route available inside the packet.

The transport step is supplied by \autoref{thm:regular-limit-uniqueness-separated-transport}. Transport preserves the separated comparison as a $\RealUp$ classifier row, so the displayed route is the entire separated comparison scope.
\end{proof}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_separated\_comparison\_scope}

\begin{theorem}[RegularLimitUniqueness ledger non-escape scope]
\label{thm:regular-limit-uniqueness-ledger-non-escape-scope}
The completion consumer boundary of \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary}, the obligation package of \autoref{thm:regular-limit-uniqueness-obligation-closure-package}, and the ledger exhaustion row of \autoref{thm:regular-limit-uniqueness-choice-free-ledger-exhaustion} give the ledger non-escape scope for $\RegularLimitUniquenessUp$. Every exported uniqueness route is a route through $\RegularCauchyFamilyUp$, $\RealDiagonalCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

No exported row leaves this scope for quotient stream equality, selected host limits, host real equality, ambient completeness, or choice.
\end{theorem}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_ledger\_non\_escape\_scope}
\begin{proof}
Use \autoref{thm:regular-limit-uniqueness-completion-consumer-boundary} to identify the rows visible to a completion consumer. The boundary lists only the family, candidate, readback, seal, separated comparison, transport, continuation, package, and naming data.

Apply \autoref{thm:regular-limit-uniqueness-obligation-closure-package}. It repacks those visible rows as carrier habitation, classifier transport, readback-to-seal exactness, separated comparison exactness, and ledger non-escape.

Finally apply \autoref{thm:regular-limit-uniqueness-choice-free-ledger-exhaustion}. Since every exported route is already exhausted by the displayed coordinates, no unlisted host or quotient object can enter the scoped uniqueness packet.
\end{proof}

\begin{theorem}[RegularLimitUniqueness scoped handoff]
\label{thm:regular-limit-uniqueness-scoped-handoff}
The shared-family scope of \autoref{thm:regular-limit-uniqueness-shared-family-scope}, the separated-comparison scope of \autoref{thm:regular-limit-uniqueness-separated-comparison-scope}, and the ledger non-escape scope of \autoref{thm:regular-limit-uniqueness-ledger-non-escape-scope} jointly bind every $\RegularLimitUniquenessUp$ consumer route to $\RegularCauchyFamilyUp$, $\RealDiagonalCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Within this scoped handoff, no consumer may replace the displayed rows by a quotient stream, selected host limit, host equality, ambient completeness principle, or choice witness.
\end{theorem}
\leanchecked{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_scoped\_handoff}
\begin{proof}
Begin with the shared-family scope. It fixes the common $\RegularCauchyFamilyUp$ input, both $\RealDiagonalCompletionUp$ candidates, their $\RegSeqRatUp$ and $\StreamNameUp$ readbacks, the two $\RealUp$ seal rows, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

Next use the separated-comparison scope. It binds the uniqueness comparison to the route from the shared family through diagonal completion and regular-rational readback into the two real seals, with the row $S$ as the only separated comparison.

Finally apply the ledger non-escape scope together with the NameCert obligation package of \autoref{thm:regular-limit-uniqueness-namecert-obligations}. The non-escape row excludes quotient streams, selected host limits, host equality, ambient completeness, and choice, so the three scoped rows hand off exactly the displayed consumer surface and nothing outside it.
\end{proof}

\begin{theorem}[RegularLimitUniqueness public completion export]
\label{thm:regular-limit-uniqueness-public-completion-export}
The carrier of \autoref{def:regular-limit-uniqueness-carrier}, the NameCert obligations of \autoref{thm:regular-limit-uniqueness-namecert-obligations}, the separated-limit certificate of \autoref{thm:regular-limit-uniqueness-separated-limit-certificate}, classifier determinacy from \autoref{thm:regular-limit-uniqueness-classifier-determinacy}, readback seal exactness from \autoref{thm:regular-limit-uniqueness-readback-seal-exactness}, the shared-family scope of \autoref{thm:regular-limit-uniqueness-shared-family-scope}, the separated-comparison scope of \autoref{thm:regular-limit-uniqueness-separated-comparison-scope}, the scoped handoff of \autoref{thm:regular-limit-uniqueness-scoped-handoff}, and the ledger non-escape row of \autoref{thm:regular-limit-uniqueness-ledger-non-escape-scope} assemble a single public completion-consumer export for two diagonal completion candidates over one regular-Cauchy family.

The exported route is exactly
$$
\RegularCauchyFamilyUp \longrightarrow \RealDiagonalCompletionUp \longrightarrow \RegSeqRatUp,\StreamNameUp \longrightarrow \RealUp
$$
through the separated row $S$. It exports no quotient stream comparison, selected host limit, host equality, ambient completeness principle, or choice witness.
\end{theorem}
\begin{proof}
Start from the carrier and NameCert obligation package. They provide the shared family row, the two diagonal completion candidates, the shared threshold, the two readbacks, the two real seals, the separated row $S$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

Next apply the separated-limit certificate, classifier determinacy, and readback seal exactness. These rows identify the only equality-facing comparison as the path from the two diagonal candidates through their $\RegSeqRatUp$ and $\StreamNameUp$ readbacks into the two $\RealUp$ seals, with $S$ as the separated comparison row.

Finally use the shared-family scope, separated-comparison scope, scoped handoff, and ledger non-escape scope. Together they make the route public for completion consumers while excluding quotient streams, selected host limits, host equality, ambient completeness, and choice from the exported surface.
\end{proof}

\begin{theorem}[RegularLimitUniqueness consumer determinacy]
\label{thm:regular-limit-uniqueness-consumer-determinacy}
Let
$$
A=(F,D0,D1,\mu,R0,R1,E0,E1,S,H,C,P,N)
$$
be an accepted $\RegularLimitUniquenessUp$ packet. Any two completion consumers that read the public completion export of \autoref{thm:regular-limit-uniqueness-public-completion-export} determine the same separated $\RealUp$ seal comparison through the displayed row $S$. No such consumer can distinguish the two reads through quotient stream equality, selected host limits, host real equality, ambient completeness, or choice.
\end{theorem}
\begin{proof}
Begin with classifier determinacy and readback seal exactness. These results identify the comparison route from the shared family $F$ through the two diagonal completion rows $D0,D1$, the readback rows $R0,R1$, the seal rows $E0,E1$, and the separated row $S$.

Next apply the scoped handoff and the public completion export. They make that route the public completion-consumer surface for the displayed packet, so both consumers read the same separated comparison row rather than independent host data.

Finally use the ledger non-escape scope. It excludes quotient stream equality, selected host limits, host real equality, ambient completeness, and choice from the exported route, leaving $S$ as the unique separated $\RealUp$ seal comparison available to either consumer.
\end{proof}

\begin{theorem}[RegularLimitUniqueness bridge handoff]
\label{thm:regular-limit-uniqueness-bridge-handoff}
Every bridge consumer comparing two diagonal completion candidates over the same $\RegularCauchyFamilyUp$ input in a $\RegularLimitUniquenessUp$ packet must factor through the displayed rows
$$
F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N.
$$
The handoff uses the public completion export of \autoref{thm:regular-limit-uniqueness-public-completion-export} and the consumer determinacy of \autoref{thm:regular-limit-uniqueness-consumer-determinacy}: the comparison is read from the shared family $F$ through the two diagonal candidates $D_0,D_1$, their regular-rational readbacks $R_0,R_1$, the two real seal rows $E_0,E_1$, and the separated comparison row $S$, with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

No bridge consumer may import quotient completion, selected host limits, host real equality, ambient completeness, or choice into this handoff. Those objects are outside the carrier ledger and outside the exported completion-consumer surface.
\end{theorem}
\begin{proof}
Compose the checked local rows. The NameCert obligations give carrier habitation, classifier transport, readback routing, separated exactness, and ledger non-escape for the finite packet of \autoref{def:regular-limit-uniqueness-carrier}.

Next use the separated-limit certificate, classifier determinacy, and readback-seal exactness. They force every comparison of the two diagonal candidates to pass through $R_0,R_1,E_0,E_1,S$ after the shared family and threshold rows have been fixed.

The public completion export then exposes exactly this route to bridge consumers, and consumer determinacy makes two reads of that export agree at the same separated $\RealUp$ comparison row $S$.

Finally apply ledger non-escape. Since quotient completion, selected host limits, host real equality, ambient completeness, and choice are not carrier coordinates and are not exported rows, the bridge handoff is precisely the displayed BEDC route.
\end{proof}

\begin{theorem}[RegularLimitUniqueness mature consumer route]
\label{thm:regular-limit-uniqueness-mature-consumer-route}
Let
$$
A=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N)
$$
be an accepted $\RegularLimitUniquenessUp$ packet whose rows display one shared $\RegularCauchyFamilyUp$ route, two $\RealDiagonalCompletionUp$ candidates, readback-to-seal rows through $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$, a separated comparison row $S$, componentwise transports, $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row. Then $A$ gives a mature consumer route
$$
\RegularCauchyFamilyUp \longrightarrow \RealDiagonalCompletionUp \longrightarrow \RegSeqRatUp,\StreamNameUp \longrightarrow \RealUp.
$$
No consumer of this packet can replace that route by quotient completion, selected host limits, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the bridge handoff of \autoref{thm:regular-limit-uniqueness-bridge-handoff}. It forces every comparison consumer for the two diagonal candidates to factor through the displayed rows $F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N$.

The public completion export of \autoref{thm:regular-limit-uniqueness-public-completion-export} supplies the downstream route from the shared family through the two diagonal completion candidates and their readbacks into the two Real seals. Consumer determinacy from \autoref{thm:regular-limit-uniqueness-consumer-determinacy} makes any two reads of that exported route agree at the same separated comparison row $S$.

Finally combine readback-seal exactness with the non-escape rows recorded in the bridge handoff. Since quotient completion, selected host limits, host real equality, and ambient completeness are outside the finite carrier and outside the exported completion-consumer surface, the displayed route is the mature consumer route for this packet.
\end{proof}

\begin{theorem}[RegularLimitUniqueness L10 terminal handoff]
\label{thm:regular-limit-uniqueness-l10-terminal-handoff}
Let
$$
A=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N)
$$
be an accepted $\RegularLimitUniquenessUp$ packet whose public route is read by a current Phase Real and Completion terminal consumer. If that consumer uses the mature route of \autoref{thm:regular-limit-uniqueness-mature-consumer-route}, then its visible terminal boundary factors through exactly the finite four-face L10 packet
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp.
$$
The $\RegularLimitUniquenessUp$ rows are used only as the separated-comparison consumer of this boundary: they read the shared family, the two diagonal completion candidates, the regular-rational readbacks, the two Real seal rows, and the separated comparison row $S$ through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

The handoff exports no quotient completion, selected host limit, host real equality, countable-choice selector, ambient completeness principle, metric-completeness row, or standard bridge row.
\end{theorem}
\begin{proof}
First expose the local completion consumer. Apply \autoref{thm:regular-limit-uniqueness-bridge-handoff} and \autoref{thm:regular-limit-uniqueness-mature-consumer-route}. The accepted packet can be read by downstream consumers only through the displayed route from the shared $\RegularCauchyFamilyUp$ family, through the two $\RealDiagonalCompletionUp$ candidates and their $\RegSeqRatUp$ and $\StreamNameUp$ readbacks, into the two $\RealUp$ seal rows and the separated comparison row $S$.

Next attach the current terminal boundary. By \autoref{thm:streamname-regseqrat-realup-lattice-budget-cover}, every StreamName, RegSeqRat, and Real budget cover used by the Phase Real and Completion surface is confined to the four sibling rows $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, with only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Now apply \autoref{thm:real-l10-four-face-exactness}. The current terminal $\RealUp$ read is accepted exactly when its visible rows factor through the finite four-face packet in the statement, and the converse read adds no further visible coordinate.

Finally use \autoref{thm:real-l10-terminal-pullback-uniqueness}. Since the mature $\RegularLimitUniquenessUp$ consumer reaches the terminal read through the same four faces and the same displayed coordinates, the consumer boundary is the unique terminal pullback over that packet. The exclusion clauses follow from the inventories in the cited handoff, budget-cover, exactness, and uniqueness theorems: quotient completion, selected host limits, host real equality, countable choice, ambient completeness, metric-completeness rows, and standard bridge rows have no coordinate in the resulting handoff.
\end{proof}

\begin{theorem}[Separated Real-seal finality]
\label{thm:regular-limit-uniqueness-separated-real-seal-finality}
Let
$$
A=(F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N)
$$
be an accepted $\RegularLimitUniquenessUp$ packet whose comparison row $S$ is read as a separated $\RegSeqRatUp$ and $\RealUp$ comparison inside a $\CompleteMetricUp$ consumer. Suppose the consumer route has passed through the readback seal rows $R_0,R_1,E_0,E_1$, the dyadic-window separation of the $\DyadicRatCoreUp$ boundary, the seal-selector pullback into $\RealUp$, the choice-free ledger exhaustion of the displayed route, and the L10 terminal handoff of \autoref{thm:regular-limit-uniqueness-l10-terminal-handoff}.

Then every accepted limit read of $A$ is final up to the displayed Real classifier: any later read that preserves the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows must factor through the same separated $S$ row and hence through the same $\RealUp$ classifier surface. The finality route is finite:
$$
\DyadicRatCoreUp \to \RegSeqRatUp \to \RealUp \to \CompleteMetricUp,
$$
with $\RegularLimitUniquenessUp$ contributing only the shared family, readback-to-seal, separated comparison, transport, continuation, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Start from the terminal handoff in \autoref{thm:regular-limit-uniqueness-l10-terminal-handoff}. It has already confined the visible Real and completion boundary to the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route, with no quotient completion, selected host limit, host real equality, countable-choice selector, ambient completeness principle, or standard bridge row.

Use the public completion export and consumer determinacy theorems to identify the only comparison row available to a downstream reader. The shared family, the two diagonal completion candidates, the regular-rational readbacks, and the two Real seal rows are all read through $F,D_0,D_1,\mu,R_0,R_1,E_0,E_1,S,H,C,P,N$, so a $\CompleteMetricUp$ consumer cannot acquire an additional limit coordinate outside $S$.

Now apply the separated-comparison part of the carrier. The $\RegSeqRatUp$ and $\RealUp$ seal reads are already tied to the dyadic-window boundary and seal-selector pullback, while $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ preserve exactly the displayed rows. Thus any accepted later read that keeps the packet accepted must return to the same Real classifier surface.

The choice-free ledger exhaustion supplies the non-escape step. Since no selected subsequence, quotient class, host equality, Real completeness principle, or hidden metric-completeness witness is a coordinate of $A$, the displayed classifier is the final public limit read for this separated Real-seal route.
\end{proof}

\begin{theorem}[Classifier route non-escape]
\label{thm:regular-limit-uniqueness-classifier-choice-free-nonescape}
No accepted $\RegularLimitUniquenessUp$ consumer may replace the classifier-finality route of \autoref{thm:regular-limit-uniqueness-separated-real-seal-finality} by host equality, a selected subsequence choice, quotient classes, or a Real completeness principle. Any consumer that claims uniqueness for the two limit reads must exhibit the same finite route through $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\CompleteMetricUp$, the separated comparison row $S$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Read the carrier inventory from \autoref{thm:regular-limit-uniqueness-bridge-handoff} and \autoref{thm:regular-limit-uniqueness-mature-consumer-route}. These theorems place the shared family, diagonal completions, readbacks, seals, separated comparison, transport, continuation, provenance, and naming rows on the visible route.

Next use \autoref{thm:regular-limit-uniqueness-l10-terminal-handoff}. The Real-facing boundary has only the finite four-face route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$; the $\CompleteMetricUp$ reader can use that route only after it passes through the same separated comparison and support rows.

Finally apply \autoref{thm:regular-limit-uniqueness-separated-real-seal-finality}. Finality is a statement about the displayed Real classifier surface, not about an ambient equality proof. Host equality, selected subsequence choice, quotient classes, and Real completeness have no carrier row, no transport row, no continuation row, no provenance row, and no local NameCert row in $A$, so replacing the route with one of them leaves the accepted packet.
\end{proof}

\closureat{RegularLimitUniquenessUp}{seedStr}
\closureat{RegularLimitUniquenessUp}{obligationStr}
\closureat{RegularLimitUniquenessUp}{scopedStr}
\closureat{RegularLimitUniquenessUp}{publicStr}
\closureat{RegularLimitUniquenessUp}{bridgedStr}
\closureat{RegularLimitUniquenessUp}{matureStr}

\begin{closurestatus}{\RegularLimitUniquenessUp}
  \constructivestory{A $\RegularLimitUniquenessUp$ packet is generated from one regular-Cauchy family, two diagonal completion candidates, a shared Cauchy threshold, two regular-rational readbacks, two real seal rows, one separated comparison row, displayed transport and continuation rows, package provenance, and local naming.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:regular-limit-uniqueness-bridge-handoff}, together with the public completion export and consumer determinacy theorems, records the carrier, classifier transport, shared-family route, readback-to-seal exactness, separated comparison exactness, ledger non-escape rows, and bridge-consumer handoff for two regular-Cauchy completion candidates over the same displayed input and boundary.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.RegularLimitUniquenessUp.RegularLimitUniquenessCarrier\_namecert\_obligations}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close quotient completion construction, selected host limits, host real equality, ambient completeness, bridge checking, or a Lean implementation.}
  \upgradepath{The theory axis is mature for the displayed route from $\RegularCauchyFamilyUp$ through $\RealDiagonalCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$; the remaining verification work is auditClean and bridgeChecked certification.}
\end{closurestatus}
