\chapter{A Concrete Naming Certificate for $\CompletionFunctorUp$}
\label{ch:concrete-instances-completionfunctor-namecert}
\origin{human}

The $\CompletionFunctorUp$ surface names the finite functorial completion packet that transports regular rational Cauchy data and continuous maps through the existing completion envelope. Following Bishop and Bridges, \emph{Constructive Analysis}, it treats completion by explicit Cauchy data, moduli, and extension ledgers rather than by quotient completions or equality of host functions. The packet connects the completion monad of \autoref{ch:concrete-instances-cauchycompletionmonad-namecert}, the universal-property surface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the real Cauchy completion surface of \autoref{ch:concrete-instances-real-cauchy-completion-namecert}, and the reflection boundary of \autoref{ch:concrete-instances-completionreflection-namecert}.

\begin{definition}[CompletionFunctor carrier]
\label{def:completion-functor-carrier}
A $\CompletionFunctorUp$ carrier is a finite $\BHist$ packet
$$
F=(M,U,R,Q,A,G,E,T,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $M$ is the $\CauchyCompletionMonadUp$ completion-envelope row that supplies unit and bind-facing completion reads;
\item $U$ is the $\CompletionUniversalPropertyUp$ extension row for continuous maps out of the dense regular rational surface;
\item $R$ is the $\RealCauchyCompletionUp$ real-completion row that seals regular rational Cauchy input as a $\RealUp$ read;
\item $Q$ is the $\RegSeqRatUp$ source row whose finite stream windows supply the dense observations;
\item $A$ is the $\RealUp$ target seal row exposed by the completed source;
\item $G$ is the $\ContinuousMapUp$ dense map row, including its modulus, graph-read ledger, and finite input-output observation rows;
\item $E$ is the transported extension ledger from $G$, $Q$, $M$, $U$, $R$, and $A$ to a completion-facing $\ContinuousMapUp$ row;
\item $T$ is the functoriality ledger comparing identity and composition reads by displayed $\hsame$ routes over the same source, map, extension, and seal rows;
\item $H$ stores the componentwise $\hsame$ comparisons for the completion envelope, universal-property row, real-completion row, source row, target seal, dense map, extension ledger, functoriality ledger, package row, and local naming row;
\item $C$ stores the $\Cont$ routes through which consumers read source windows, map graph entries, completion envelopes, extension rows, real seals, and functoriality ledgers;
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionMonadUp$, $\CompletionUniversalPropertyUp$, $\RealCauchyCompletionUp$, $\RegSeqRatUp$, $\RealUp$, $\ContinuousMapUp$, $\BHist$, $\hsame$, $\Cont$, and local $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\CompletionFunctorUp}$ row.
\end{enumerate}
Two accepted carriers classify together only when all displayed rows are transported componentwise through $H$ and read through the routes in $C$. The carrier has no quotient of Cauchy streams, no selected host limit, no equality of host functions, and no ambient completeness field.
\end{definition}

\begin{theorem}[CompletionFunctor NameCert obligations]
\label{thm:completion-functor-namecert-obligations}
The local $\NameCert_{\CompletionFunctorUp}$ surface for \autoref{def:completion-functor-carrier} consists of carrier admission, classifier stability, extension-ledger exactness, functorial identity and composition ledgers, unit-boundary compatibility, and non-escape of quotient completions, selected limits, host function equality, and ambient completeness. Every obligation is stated over the rows $M,U,R,Q,A,G,E,T,H,C,P,N$ and their displayed $\hsame$ and $\Cont$ routes.
\end{theorem}
\leanchecked{BEDC.Derived.CompletionFunctorUp.CompletionFunctorCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is projection from \autoref{def:completion-functor-carrier}. The packet lists the completion envelope, universal-property row, real-completion row, dense regular rational source, real seal, dense continuous map, extension ledger, functoriality ledger, transport rows, continuation rows, package provenance, and local naming row.

Classifier stability is componentwise. The recorded $\hsame$ rows in $H$ transport exactly the listed coordinates, while the $\Cont$ routes in $C$ preserve the read order from source windows and graph entries to completion envelopes, extension rows, real seals, and functoriality ledgers.

Extension exactness is inherited as a visible row, not as an external principle. The coordinate $E$ is the only route from the dense $\ContinuousMapUp$ row $G$ and regular rational source $Q$ into the completion-facing map row supplied by $U$.

The remaining public obligations are the three theorem surfaces below: functoriality, unit-boundary compatibility, and non-escape. Together they exhaust all consumer reads of the local $\NameCert_{\CompletionFunctorUp}$ packet.
\end{proof}

\begin{theorem}[CompletionFunctor functoriality]
\label{thm:completion-functor-functoriality}
Let $F=(M,U,R,Q,A,G,E,T,H,C,P,N)$ be an accepted $\CompletionFunctorUp$ carrier. Identity reads and composable pairs of dense $\ContinuousMapUp$ rows are transported to completion-facing $\ContinuousMapUp$ reads by the same finite extension ledger $E$ and compared by the functoriality ledger $T$. The comparison uses only displayed $\hsame$ rows and $\Cont$ routes over $M$, $U$, $R$, $Q$, $A$, $G$, and $E$.
\end{theorem}
\begin{proof}
For the identity route, read the dense identity map as a $\ContinuousMapUp$ graph row with its displayed modulus. The universal-property row $U$ and extension ledger $E$ repack that graph row through $Q$, $M$, $R$, and the seal $A$ as a completion-facing continuous map.

For a composable pair, inspect the two dense graph ledgers in finite windows. The $\Cont$ routes in $C$ preserve the order of source read, first map read, second map read, extension read, and real-seal read.

The ledger $T$ compares the completion of the composite dense map with the composite of the two completion-facing extension rows. Since $T$ is a displayed $\BHist$ coordinate whose comparisons are routed through $H$ and $C$, the comparison is a local $\hsame$ ledger statement and not an equality of host functions.
\end{proof}

\begin{theorem}[CompletionFunctor unit boundary]
\label{thm:completion-functor-unit-boundary}
For every accepted $\CompletionFunctorUp$ carrier, the unit row of $\CauchyCompletionMonadUp$ and the real seal of $\RealCauchyCompletionUp$ agree at the public boundary through the displayed rows $M$, $R$, $Q$, $A$, $E$, $H$, $C$, $P$, and $N$. A dense regular rational input is first read as $Q$, then admitted through the completion envelope $M$, and finally exposed through the $\RealUp$ seal $A$ without adding a quotient representative or a selected limit.
\end{theorem}
\leanchecked{BEDC.Derived.CompletionFunctorUp.CompletionFunctorCarrier\_unit\_boundary}
\begin{proof}
Start with the displayed regular rational source row $Q$. The completion envelope $M$ supplies the unit-facing packet for this source, using finite stream windows and regular rational observations.

The real-completion row $R$ and seal $A$ are then read through the same source observations. The extension ledger $E$ contributes only the continuation route needed by downstream continuous-map consumers; it does not change the source row or choose a host limit.

The comparison between the monad unit boundary and the real seal boundary is recorded by the componentwise transports in $H$ and the read routes in $C$. Thus the public unit boundary is a finite packet route through the named rows, with no quotient completion or ambient completeness datum.
\end{proof}

\begin{theorem}[CompletionFunctor extension ledger exactness]
\label{thm:completion-functor-extension-ledger-exactness}
Let $F=(M,U,R,Q,A,G,E,T,H,C,P,N)$ be an accepted $\CompletionFunctorUp$ carrier. Every completion-facing extension read produced from the dense $\ContinuousMapUp$ row $G$ and regular rational source row $Q$ is exactly the displayed extension ledger $E$ read through $M$, $U$, $R$, $A$, $H$, $C$, $P$, and $N$. The packet exports no second extension route, quotient completion, selected limit, or host function equality.
\end{theorem}
\leanchecked{BEDC.Derived.CompletionFunctorUp.CompletionFunctorCarrier\_extension\_ledger\_exactness}
\begin{proof}
Project the accepted carrier through \autoref{def:completion-functor-carrier}. The only row whose role is extension from dense graph data to a completion-facing continuous map is $E$, and its source rows are visibly $G$, $Q$, $M$, $U$, $R$, and $A$.

Apply the extension clause in \autoref{thm:completion-functor-namecert-obligations}. It makes extension exactness a visible carrier row rather than an external principle, so every consumer read of the extended map reaches $E$ through the displayed $\hsame$ transports in $H$ and the $\Cont$ routes in $C$.

Finally use the non-escape inventory implicit in the carrier. Since no coordinate of $F$ is a quotient completion, selected limit, host function equality, or ambient completeness field, no second extension object can be read from the packet.
\end{proof}

\begin{theorem}[CompletionFunctor identity route stability]
\label{thm:completion-functor-identity-route-stability}
For an accepted $\CompletionFunctorUp$ carrier $F=(M,U,R,Q,A,G,E,T,H,C,P,N)$ whose dense map row $G$ is the identity $\ContinuousMapUp$ row on the displayed dense source, the identity completion route is stable under the componentwise $\hsame$ rows in $H$ and the $\Cont$ routes in $C$. Its public read is the identity clause of the functoriality ledger $T$, using the same extension ledger $E$ and unit-boundary rows $M$, $R$, $Q$, and $A$.
\end{theorem}
\leanchecked{BEDC.Derived.CompletionFunctorUp.CompletionFunctorCarrier\_identity\_route\_stability}
\begin{proof}
Start with the identity part of \autoref{thm:completion-functor-functoriality}. The dense identity graph is read as a displayed $\ContinuousMapUp$ row, then repacked by $U$ and $E$ through the source row $Q$ and completion envelope $M$.

The unit boundary of \autoref{thm:completion-functor-unit-boundary} identifies the source-side completed object with the $\RealUp$ seal $A$ through $M$, $R$, and $Q$. Transporting the same rows by $H$ and reading them through $C$ keeps the identity route attached to the displayed source and seal rows.

The functoriality ledger $T$ is therefore the only public identity comparison row. The route is stable as a finite $\BHist$ comparison and does not become an equality of host functions.
\end{proof}

\begin{theorem}[CompletionFunctor composition route stability]
\label{thm:completion-functor-composition-route-stability}
For an accepted $\CompletionFunctorUp$ carrier $F=(M,U,R,Q,A,G,E,T,H,C,P,N)$ that displays composable dense $\ContinuousMapUp$ reads inside $G$ and their transported extension rows inside $E$, the completion route for the composite is classified by the composition clause of $T$. Componentwise transport through $H$ and consumer reads through $C$ preserve the same route through $M$, $U$, $R$, $Q$, $A$, $G$, $E$, $P$, and $N$.
\end{theorem}
\leanchecked{BEDC.Derived.CompletionFunctorUp.CompletionFunctorCarrier\_composition\_route\_stability}
\begin{proof}
Read the composable dense graph rows through the second paragraph of \autoref{thm:completion-functor-functoriality}. The carrier records the source read, first graph read, second graph read, extension read, and real-seal read as finite routes.

Apply \autoref{thm:completion-functor-extension-ledger-exactness}. Both completion-facing maps and the completion-facing composite are read through $E$, so the composition comparison has a single extension ledger to inspect.

The ledger $T$ then compares the extension of the dense composite with the composite of the two transported extension rows. Because $T$ is transported by the same $H$ and read by the same $C$, the composition route is stable without appealing to host function equality.
\end{proof}

\begin{theorem}[CompletionFunctor completion consumer surface]
\label{thm:completion-functor-completion-consumer-surface}
Every public completion consumer of an accepted $\CompletionFunctorUp$ packet factors through the displayed carrier rows $M,U,R,Q,A,G,E,T,H,C,P,N$: completed-source reads use the unit boundary, extension reads use the exact ledger $E$, identity reads use the identity clause of $T$, composition reads use the composition clause of $T$, and all reads obey the non-escape boundary.
\end{theorem}
\leanchecked{BEDC.Derived.CompletionFunctorUp.CompletionFunctorCarrier\_completion\_consumer\_surface}
\begin{proof}
First split the consumer request by the row it asks to read. A completed-source request reaches $M$, $R$, $Q$, and $A$ by \autoref{thm:completion-functor-unit-boundary}; an extension request reaches $E$ by \autoref{thm:completion-functor-extension-ledger-exactness}.

For functorial requests, use the two route-stability rows. Identity reads are governed by \autoref{thm:completion-functor-identity-route-stability}, while composition reads are governed by \autoref{thm:completion-functor-composition-route-stability}.

Finally apply \autoref{thm:completion-functor-non-escape}. The listed rows exhaust the finite carrier, so the consumer surface contains no quotient completion, selected limit, hidden representative, host function equality, or ambient completeness field.
\end{proof}

\begin{theorem}[CompletionFunctor scoped dependency spine]
\label{thm:completion-functor-scoped-dependency-spine}
The carrier, exact extension ledger, unit boundary, identity route, composition route, and consumer surface of $\CompletionFunctorUp$ are scoped exactly over $\CauchyCompletionMonadUp$, $\CompletionUniversalPropertyUp$, $\RealCauchyCompletionUp$, $\RegSeqRatUp$, $\RealUp$, $\ContinuousMapUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert_{\CompletionFunctorUp}$ row. No proof obligation of the packet reads outside these named dependencies.
\end{theorem}
\begin{proof}
Project the finite carrier and local naming surface from \autoref{thm:completion-functor-namecert-obligations}. This fixes the available rows as $M,U,R,Q,A,G,E,T,H,C,P,N$ and identifies their sources as the completion monad, universal-property, real-completion, regular-sequence, real-seal, continuous-map, transport, continuation, package, and local naming dependencies.

Apply \autoref{thm:completion-functor-extension-ledger-exactness}, \autoref{thm:completion-functor-unit-boundary}, \autoref{thm:completion-functor-identity-route-stability}, and \autoref{thm:completion-functor-composition-route-stability}. These four rows show that every extension, unit, identity, and composition read factors through the displayed ledger and the same $\hsame$ and $\Cont$ routes.

Finally use \autoref{thm:completion-functor-completion-consumer-surface}. The consumer surface exhausts the packet, so quotient completion, selected limit, ambient completeness, hidden representatives, and host function equality are not in scope for $\CompletionFunctorUp$.
\end{proof}

\begin{theorem}[CompletionFunctor non-escape boundary]
\label{thm:completion-functor-non-escape}
No accepted $\CompletionFunctorUp$ carrier exports quotient completions, host function equality, selected limits, hidden representatives, or ambient completeness. Every public read of a completed object, a transported continuous map, an identity ledger, or a composition ledger factors through the finite $\BHist$ packet of \autoref{def:completion-functor-carrier}, the extension route of \autoref{thm:completion-functor-namecert-obligations}, the functoriality ledger of \autoref{thm:completion-functor-functoriality}, and the unit boundary of \autoref{thm:completion-functor-unit-boundary}.
\end{theorem}
\begin{proof}
Inspect the carrier inventory. Its analytic rows are the completion envelope, universal-property row, real-completion row, regular rational source, real seal, dense continuous map, extension ledger, and functoriality ledger, together with finite transport, continuation, package, and naming rows.

The NameCert obligation theorem makes $E$ the only completion-facing extension route. The functoriality theorem makes $T$ the only public route for identity and composition comparison. The unit-boundary theorem makes $M$, $R$, $Q$, and $A$ the only public route from dense regular rational input to completed real seal.

These routes exhaust the packet. Since none of the listed coordinates is a quotient completion, host function equality proof, selected limit, hidden representative, or ambient completeness field, no public consumer can read such an object from the $\CompletionFunctorUp$ surface.
\end{proof}

\begin{theorem}[CompletionFunctor public completion export]
\label{thm:completion-functor-public-completion-export}
The $\CompletionFunctorUp$ carrier, functoriality ledger, unit boundary, extension-ledger exactness, identity route stability, composition route stability, completion consumer surface, scoped dependency spine, and non-escape boundary assemble into the public $\CompletionFunctorUp$ completion export consumed by $\CompleteMetricUp$, $\HausdorffCompletionUp$, and $\CompletionUniversalPropertyUp$. This export exposes only the finite rows $M,U,R,Q,A,G,E,T,H,C,P,N$ of \autoref{def:completion-functor-carrier} and their displayed $\hsame$ and $\Cont$ routes.
\end{theorem}
\begin{proof}
Start from the local carrier and obligation surface of \autoref{thm:completion-functor-namecert-obligations}. It fixes the displayed rows, the componentwise classifier transports, the continuation routes, and the local $\NameCert_{\CompletionFunctorUp}$ packet read by downstream completion consumers.

The public completion map surface is then determined by the three central construction rows. The functoriality ledger is supplied by \autoref{thm:completion-functor-functoriality}, the unit-facing dense-to-completed boundary by \autoref{thm:completion-functor-unit-boundary}, and the single completion-facing extension read by \autoref{thm:completion-functor-extension-ledger-exactness}.

The route-level stability needed by consumers is already internal to the same packet. Identity reads use \autoref{thm:completion-functor-identity-route-stability}, and composable dense-map reads use \autoref{thm:completion-functor-composition-route-stability}, both over the same extension ledger and transport rows.

Finally combine the consumer inventory of \autoref{thm:completion-functor-completion-consumer-surface} with the dependency inventory of \autoref{thm:completion-functor-scoped-dependency-spine} and the non-escape boundary of \autoref{thm:completion-functor-non-escape}. The resulting public export is exactly the completion-functor surface available to $\CompleteMetricUp$, $\HausdorffCompletionUp$, and $\CompletionUniversalPropertyUp$, with no quotient completion, selected limit, host function equality, hidden representative, or ambient completeness field added at the boundary.
\end{proof}

\begin{theorem}[CompletionFunctor public extension interface]
\label{thm:completion-functor-public-extension-interface}
Let $F=(M,U,R,Q,A,G,E,T,H,C,P,N)$ be an accepted $\CompletionFunctorUp$ carrier. The packet exports a public completion-functor interface in which unit reads come from the $\CauchyCompletionMonadUp$ row $M$, extension reads come from the $\CompletionUniversalPropertyUp$ row $U$ and the exact ledger $E$, $\RealUp$ seals come from the $\RealCauchyCompletionUp$ and $\RegSeqRatUp$ rows $R$ and $Q$ together with $A$, and map transport comes from the $\ContinuousMapUp$ row $G$ and functoriality ledger $T$. Every such read is routed through displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.CompletionFunctorUp.CompletionFunctorCarrier\_public\_extension\_interface}
\begin{proof}
For the unit side, apply \autoref{thm:completion-functor-unit-boundary}. It identifies the public completed-source read as the route through $M$, $R$, $Q$, $A$, $H$, $C$, $P$, and $N$.

For extension reads, use \autoref{thm:completion-functor-extension-ledger-exactness}. The universal-property row $U$ and exact ledger $E$ give the only completion-facing extension path from the dense $\ContinuousMapUp$ row $G$.

For transported maps, combine \autoref{thm:completion-functor-functoriality}, \autoref{thm:completion-functor-identity-route-stability}, and \autoref{thm:completion-functor-composition-route-stability}. These theorems route identity and composition through $T$ using the same displayed carrier rows.

Finally invoke \autoref{thm:completion-functor-completion-consumer-surface} and \autoref{thm:completion-functor-non-escape}. They exhaust the public consumer surface and rule out quotient completions, selected limits, hidden representatives, host function equality, and ambient completeness.
\end{proof}

\begin{theorem}[CompletionFunctor Cauchy seal composition]
\label{thm:completion-functor-cauchy-seal-composition}
Let
$$
F_1=(M_1,U_1,R_1,Q_1,A_1,G_1,E_1,T_1,H_1,C_1,P_1,N_1)
$$
and
$$
F_2=(M_2,U_2,R_2,Q_2,A_2,G_2,E_2,T_2,H_2,C_2,P_2,N_2)
$$
be accepted $\CompletionFunctorUp$ carriers whose target seal row of $F_1$ matches the source seal row of $F_2$ through displayed $\hsame$ and $\Cont$ routes. Then their completion-extension packets compose to a single $\CompletionFunctorUp$ packet whose composed route preserves carrier membership, classifier equality, and extension-ledger exactness. The public surface of the composite reads the same $\RealUp$ seal boundary, the same completion-facing $\ContinuousMapUp$ classifier row, and the exact extension ledger exported by the composed packet.
\end{theorem}
\begin{proof}
First build the composed route. Apply \autoref{thm:completion-functor-composition-route-stability} to the composable dense map rows and their transported extension rows; the matching seal hypothesis identifies the target read of $F_1$ with the source read of $F_2$ inside the displayed $\hsame$ and $\Cont$ routes.

Next descend the ledger. Apply \autoref{thm:completion-functor-extension-ledger-exactness} to each packet and then to the composed carrier route. The only completion-facing extension reads available are the displayed ledgers $E_1$, $E_2$, and the composed ledger carried by the resulting packet.

Finally export the consumer surface. Use \autoref{thm:completion-functor-public-extension-interface} to read the composed unit, seal, map-transport, and functoriality rows through the same package and naming provenance. This gives a single public $\CompletionFunctorUp$ packet without adding quotient completions, selected limits, host function equality, or ambient completeness.
\end{proof}

\begin{theorem}[CompletionFunctor standard bridge surface]
\label{thm:completion-functor-standard-bridge-surface}
Every standard $\CompletionFunctorUp$ read over the carrier rows $M,U,R,Q,A,G,E,T,H,C,P,N$ factors through the public extension interface of \autoref{thm:completion-functor-public-extension-interface}, the unit boundary of \autoref{thm:completion-functor-unit-boundary}, the extension-ledger exactness of \autoref{thm:completion-functor-extension-ledger-exactness}, the identity and composition route stability of \autoref{thm:completion-functor-identity-route-stability} and \autoref{thm:completion-functor-composition-route-stability}, and the Cauchy seal composition of \autoref{thm:completion-functor-cauchy-seal-composition}. The surface exports no quotient completion, selected limit, host function equality, hidden representative, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the public interface. \autoref{thm:completion-functor-public-extension-interface} exposes the unit, extension, seal, map-transport, functoriality, package, and naming rows of the accepted carrier and routes every public consumer through displayed $\hsame$ and $\Cont$ data.

Next identify the construction rows used by that interface. The unit side is \autoref{thm:completion-functor-unit-boundary}; the extension side is \autoref{thm:completion-functor-extension-ledger-exactness}; the functorial side is the pair of identity and composition route-stability theorems.

Finally apply \autoref{thm:completion-functor-cauchy-seal-composition}. It shows that compatible Cauchy seal reads compose inside the same finite packet, so the standard bridge surface is exactly the paper-side surface generated by these named rows. The non-escape clauses already present in the interface exclude quotient completions, selected limits, host function equality, hidden representatives, and ambient completeness.
\end{proof}

\begin{theorem}[CompletionFunctor bridge-composition exactness]
\label{thm:completion-functor-bridge-composition-exactness}
Any consumer of the $\CompletionFunctorUp$ standard bridge reads the same completion carrier through identity routes, composition routes, extension-ledger exactness, and Cauchy seal composition over the rows
$$
M,U,R,Q,A,G,E,T,H,C,P,N.
$$
The bridge-composition read exposes no extra host completion, quotient object, selected limit, host function equality, hidden representative, or ambient completeness field beyond the standard bridge surface.
\end{theorem}
\begin{proof}
Start with the identity route. \autoref{thm:completion-functor-identity-route-stability} keeps the identity completion read attached to the displayed source, seal, extension ledger, transport rows, and continuation routes.

Next add the composition route and extension ledger. \autoref{thm:completion-functor-composition-route-stability} compares composable dense-map reads inside the same functoriality ledger, and \autoref{thm:completion-functor-extension-ledger-exactness} says that every completion-facing extension read is exactly the displayed ledger $E$.

Now apply Cauchy seal composition. \autoref{thm:completion-functor-cauchy-seal-composition} composes compatible seal reads inside a single $\CompletionFunctorUp$ packet and preserves carrier membership, classifier equality, and extension-ledger exactness.

Finally cite the standard bridge surface. \autoref{thm:completion-functor-standard-bridge-surface} is generated by these identity, composition, ledger, and seal rows, and its non-escape clauses exclude any extra host completion or quotient object.
\end{proof}

\closureat{CompletionFunctorUp}{seedStr}
\closureat{CompletionFunctorUp}{obligationStr}
\closureat{CompletionFunctorUp}{scopedStr}
\closureat{CompletionFunctorUp}{publicStr}

\begin{closurestatus}{\CompletionFunctorUp}
  \constructivestory{A $\CompletionFunctorUp$ packet is generated from a $\CauchyCompletionMonadUp$ completion envelope, a $\CompletionUniversalPropertyUp$ extension row, a $\RealCauchyCompletionUp$ real-completion row, a $\RegSeqRatUp$ dense source, a $\RealUp$ seal, a $\ContinuousMapUp$ dense map, a finite extension ledger, a functoriality ledger, displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{thm:completion-functor-public-extension-interface} exports the public completion-functor interface over $\CauchyCompletionMonadUp$, $\CompletionUniversalPropertyUp$, $\RealCauchyCompletionUp$, $\RegSeqRatUp$, $\RealUp$, $\ContinuousMapUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient completions, host function equality, selected limits, ambient completeness, completed-category laws beyond the displayed finite ledger, or bridge checking.}
  \upgradepath{Bridge closure requires a standard bridge for the displayed completion-functor packet.}
\end{closurestatus}
