\chapter{A Concrete Naming Certificate for $\IndependenceUp$}
\label{ch:concrete-instances-independence-namecert}

The independence interface $\IndependenceUp$ packages the property that the joint distribution of a finite family of random variables factors as the product of marginals. It depends on $\NameCert_{\RandomVarUp}$ (\autoref{ch:concrete-instances-randomvar-namecert}) and $\NameCert_{\DistributionUp}$ (\autoref{ch:concrete-instances-distribution-namecert}).

\section{Carrier definition}
\label{sec:independence-carrier}

\begin{definition}[Finite-family carrier for IndependenceUp]
\label{def:independence-finite-family-carrier}
A finite-family carrier for $\IndependenceUp$ consists of a carried $\ProbSpaceUp$ source $S$, a finite $\FinSetUp$ index carrier $I$, and for every $i\in I$ a carried $\RandomVarUp$ map
$$
X_i:S\to T_i.
$$
For each $i$, the carrier includes the displayed $\DistributionUp$ marginal endpoint $\mu_i$ obtained as the pushforward of $X_i$, together with a displayed joint $\DistributionUp$ endpoint $\mu_X^J$ for the tuple map into the finite product target $\prod_{i\in I}T_i$.

The readback ledger assigns to every finite family of measurable target events $B=(B_i)_{i\in I}$ a product-cylinder event $\operatorname{Cyl}_X(B)$ in the joint target and records the source-event readback
$$
s\in X^{-1}(\operatorname{Cyl}_X(B))
\Longleftrightarrow
\forall i\in I.\;X_i(s)\in B_i.
$$
Thus the carrier exposes exactly the source, finite index spine, random-variable spine, marginal distribution spine, joint distribution endpoint, and product-cylinder readback needed for the finite factorisation row.
\end{definition}

\begin{definition}[Finite factorisation classifier for IndependenceUp]
\label{def:independence-factorisation-classifier}
Let $R_X$ and $R_Y$ be two finite-family rows of \autoref{def:independence-finite-family-carrier}. An $\IndependenceUp$ factorisation classifier from $R_X$ to $R_Y$ consists of the following compatible comparisons:
\begin{enumerate}
\item a $\ProbSpaceUp$ classifier identifying the carried sources;
\item a $\FinSetUp$ classifier identifying the finite index carriers and transporting the finite-position spine;
\item for every matched index, a $\RandomVarUp$ classifier between the corresponding carried random-variable maps;
\item for every matched index and measurable target event, a $\DistributionUp$ classifier between the corresponding marginal endpoints;
\item compatibility of the two product-cylinder readbacks under the source, index, and random-variable classifiers;
\item $\RealUp$ classifier agreement between the two marginal product folds and between the two joint-cylinder endpoints for every transported measurable event family.
\end{enumerate}
The classifier holds when these comparisons compose to the displayed endpoint condition
$$
\mu_X^J(\operatorname{Cyl}_X(B))\sim_R\Pi_R(\mathsf{MargSp}_X(B))
\Longleftrightarrow
\mu_Y^J(\operatorname{Cyl}_Y(B'))\sim_R\Pi_R(\mathsf{MargSp}_Y(B'))
$$
for each event family $B$ and its transported family $B'$.
\end{definition}

\section{The certificate}
\label{sec:independence-certificate}

\begin{definition}[Finite factorisation row for IndependenceUp]
\label{def:independence-finite-factorisation-row}
Let $S$ be a carried $\ProbSpaceUp$ source, let $I$ be a finite index carrier supplied by a $\FinSetUp$ certificate, and let
$$
X_i:S\to T_i\qquad (i\in I)
$$
be a finite family of carried $\RandomVarUp$ maps as in \autoref{sec:randomvar-carrier}. For each $i$, write $\mu_i$ for the $\DistributionUp$ pushforward measure of $X_i$ as in \autoref{sec:distribution-carrier}, and write $\mu_X^J$ for the displayed joint $\DistributionUp$ endpoint of the tuple family. A finite factorisation row for $\IndependenceUp$ consists of the following data:
\begin{enumerate}
\item for every finite family of measurable target events $B=(B_i)_{i\in I}$, a product-cylinder event $\operatorname{Cyl}_X(B)$ in the joint target, read by
$$
s\in X^{-1}(\operatorname{Cyl}_X(B))
\Longleftrightarrow
\forall i\in I.\;X_i(s)\in B_i;
$$
\item a finite $\RealUp$ product fold $\Pi_R$ on the marginal-value spine
$$
\mathsf{MargSp}_X(B)(i):=\mu_i(B_i),
$$
using the multiplication and classifier rows of the $\RealUp$ commutative ring surface of \autoref{def:ring-stability-certificate} and \autoref{def:commring-stability-certificate};
\item the joint-distribution factorisation row
$$
\mu_X^J(\operatorname{Cyl}_X(B))\sim_R\Pi_R(\mathsf{MargSp}_X(B))
$$
for every such measurable event family $B$, where $\sim_R$ is the $\RealUp$ classifier of \autoref{def:real-classifier-specification}.
\end{enumerate}
This is the concrete paper-side factorisation surface carried by $\IndependenceUp$ in \autoref{sec:independence-carrier} and \autoref{sec:independence-certificate}.
\end{definition}
\leandef{BEDC.Derived.IndependenceUp.IndependenceFiniteFactorizationRow}

\begin{theorem}[Independence obligation stability under certified transport]
\label{thm:independence-obligation-stability-transport}
Let $R_X$ and $R_Y$ be finite-family carriers for $\IndependenceUp$ as in \autoref{def:independence-finite-family-carrier}. Suppose they are related by the classifier of \autoref{def:independence-factorisation-classifier}, using the $\RandomVarUp$, $\DistributionUp$, $\FinSetUp$, $\PermutationUp$, and $\RealUp$ classifier rows named there. If $R_X$ carries the finite factorisation row of \autoref{def:independence-finite-factorisation-row}, then $R_Y$ carries the corresponding finite factorisation row for every transported measurable event family.
\end{theorem}
\begin{proof}
Fix a measurable event family $B'$ for $R_Y$ and choose its transported source family $B$ along the $\FinSetUp$ and $\RandomVarUp$ classifier data. The product-cylinder compatibility in \autoref{def:independence-factorisation-classifier} identifies the two source-event readbacks, so the $\DistributionUp$ rows compare the two joint-cylinder endpoints.

The marginal clauses of the same classifier compare each marginal endpoint in the transported spine. The finite-position comparison and, when the presentation order changes, the $\PermutationUp$ row reduce the product comparison to \autoref{lem:realup-finite-product-permutation-readback}.

Apply the factorisation row for $R_X$ to $B$. The joint-endpoint comparison, the transported marginal-product comparison, and transitivity of the $\RealUp$ classifier give the factorisation row for $R_Y$ at $B'$. Since $B'$ was arbitrary, stability holds for the whole finite family.
\end{proof}

\begin{theorem}[Independence obligation ledger exactness]
\label{thm:independence-obligation-ledger-exactness}
For a finite-family carrier $R_X$ of \autoref{def:independence-finite-family-carrier}, the $\IndependenceUp$ ledger exposes exactly four rows: the product-cylinder readback, the marginal distribution spine, the finite $\RealUp$ product fold, and the joint distribution endpoint. The ledger is exact precisely when, for every finite measurable event family $B$, the displayed factorisation row
$$
\mu_X^J(\operatorname{Cyl}_X(B))\sim_R\Pi_R(\mathsf{MargSp}_X(B))
$$
holds with the cylinder, spine, fold, and endpoint supplied by those four rows.
\end{theorem}
\begin{proof}
The carrier definition lists the only data read by the factorisation judgment: source membership in the cylinder, the marginal endpoint attached to each index, the finite product of those endpoints, and the joint endpoint of the tuple map. No additional event, source witness, or hidden distribution endpoint is read by \autoref{def:independence-finite-factorisation-row}.

If the ledger is exact, evaluating it at $B$ returns those four entries, and the final entry is classified with the product fold by the recorded factorisation row. This gives the displayed equation for every measurable event family.

Conversely, assume the displayed equation holds for every $B$ using the four ledger rows. Then every value consumed by the independence judgment is one of the exposed rows, and the judgment is true exactly when the displayed equation is true. Hence the ledger is exact for the finite-family factorisation surface.
\end{proof}
\leanchecked{BEDC.Derived.IndependenceUp.IndependenceFiniteFactorizationRow\_ledger\_exactness}

\begin{theorem}[Independence obligation certificate packet]
\label{thm:independence-obligation-certificate-packet}
The data consisting of the carrier of \autoref{def:independence-finite-family-carrier}, the classifier of \autoref{def:independence-factorisation-classifier}, the stability theorem of \autoref{thm:independence-obligation-stability-transport}, and the ledger exactness theorem of \autoref{thm:independence-obligation-ledger-exactness} form the finite-family $\IndependenceUp$ obligation packet. This packet fixes the paper-side obligations for closing $\NameCert_{\IndependenceUp}$ on finite families of carried random variables over a carried $\ProbSpaceUp$ source.
\end{theorem}
\begin{proof}
The carrier supplies the source, finite index, random-variable spine, marginal endpoints, joint endpoint, and cylinder readback. The classifier states exactly when two such rows have the same finite-family independence content after certified transport.

The stability theorem records that the factorisation judgment is preserved by the named classifiers. The ledger exactness theorem records that no field outside the cylinder readback, marginal spine, product fold, and joint endpoint is used by the judgment.

Together these rows are the required carrier, classifier, stability, ledger, and exactness faces of the finite-family naming certificate. Therefore they assemble into the $\IndependenceUp$ obligation packet for the stated finite scope.
\end{proof}

\begin{theorem}[Independence scoped primitive boundary]
\label{thm:independence-scoped-primitive-boundary}
The finite-family $\IndependenceUp$ certificate surface is scoped by exactly the displayed $\NameCert$ rows for $\ProbSpaceUp$, $\FinSetUp$, $\RandomVarUp$, $\DistributionUp$, $\PermutationUp$, and $\RealUp$, together with the BEDC kernel carriers and classifiers $BHist$, $hsame$, and $Cont$, the product-cylinder readback, finite product fold, joint endpoint, and marginal spine of \autoref{def:independence-finite-factorisation-row}. It consumes no conditional-expectation row, martingale row, sigma-completion row, host equality row, host function equality row, or standard probability-space bridge row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:independence-obligation-certificate-packet}. The packet assembles the finite-family carrier, classifier, stability, ledger, and exactness faces from the displayed source, index, random-variable, distribution, permutation, and real rows.

The generated transport scope is the one stated in \autoref{thm:independence-classifier-stability-obligation}. Its generators are certified finite reindexing, readable-preimage transport, distribution endpoint transport, and finite-product classifier transport; each is supplied by the displayed $\NameCert$ rows and the kernel classifiers $BHist$, $hsame$, and $Cont$.

The exact ledger boundary is the one stated in \autoref{thm:independence-ledger-exactness-obligation}. It reads only the product-cylinder readback, marginal distribution spine, finite $\RealUp$ product fold, and joint distribution endpoint of \autoref{def:independence-finite-factorisation-row}.

The nontrivial finite-family stability faces are exactly the checked rows \autoref{lem:realup-finite-product-permutation-readback}, \autoref{thm:independence-finite-reindexing-invariance}, and \autoref{thm:independence-measurable-image-bridge}. Those rows cover permutation readback, finite reindexing, and measurable-image transport, so no conditional-expectation, martingale, sigma-completion, host equality, host function equality, or standard bridge row remains in the scoped boundary.
\end{proof}

\begin{theorem}[Independence carrier obligation]
\label{thm:independence-carrier-obligation}
The carrier for $\IndependenceUp$ is exactly the finite-family package consisting of one carried $\ProbSpaceUp$ source $S$, a certified $\FinSetUp$ index carrier $I$, carried $\RandomVarUp$ maps $X_i:S\to T_i$ for $i\in I$, their $\DistributionUp$ marginal endpoints $\mu_i$, the displayed joint $\DistributionUp$ endpoint $\mu_X^J$, and the finite factorisation row of \autoref{def:independence-finite-factorisation-row}. No further carrier datum is part of the $\IndependenceUp$ surface.
\end{theorem}
\begin{proof}
Unpack the finite factorisation row. Its inputs name one source probability-space carrier, one finite index carrier, and one carried random-variable map at each finite index. The row then records exactly the marginal pushforward endpoint for each map and the joint pushforward endpoint for the tuple family.

The remaining fields of \autoref{def:independence-finite-factorisation-row} are certificate rows over those endpoints: product-cylinder readback, finite $\RealUp$ product fold, and the joint-distribution factorisation comparison. Each field is typed over the same displayed source, index, random-variable, marginal, and joint endpoints. Thus the carrier is closed by these finite data, and there is no separate conditional, completed, or standard-space carrier to add.
\end{proof}

\begin{theorem}[Independence classifier and stability obligation]
\label{thm:independence-classifier-stability-obligation}
The classifier comparison for $\IndependenceUp$ is generated by certified index reindexing, readable-preimage transport for carried $\RandomVarUp$ maps, $\DistributionUp$ endpoint transport along the displayed pushforward rows, and finite-product classifier transport over $\RealUp$. Under these generators, the finite factorisation row is stable under certified finite reindexing and under measurable-image transport of a binary pair.
\end{theorem}
\begin{proof}
The classifier generators are the comparison rows already present in the input certificates. A certified reindexing compares index positions by the $\FinSetUp$ and $\PermutationUp$ rows. A readable-preimage transport compares target events through the $\RandomVarUp$ readback clauses. The $\DistributionUp$ pushforward row transports the resulting event comparison to marginal and joint endpoints, and the $\RealUp$ classifier transports the finite product fold.

For the finite-family face, apply \autoref{thm:independence-finite-reindexing-invariance}. It uses the certified inverse position map, product-cylinder readback, the original factorisation row, and \autoref{lem:realup-finite-product-permutation-readback} to rebuild the same factorisation comparison after reindexing.

For the binary measurable-image face, apply \autoref{thm:independence-measurable-image-bridge}. It reads preimages through the displayed maps, transports the marginal and joint distribution endpoints, and then composes the original binary factorisation comparison with $\RealUp$ classifier transitivity. These two stability faces exhibit the generated classifier comparison for the independence certificate.
\end{proof}

\begin{theorem}[Independence ledger and exactness obligation]
\label{thm:independence-ledger-exactness-obligation}
The exact ledger exported by $\IndependenceUp$ consists only of the source probability-space row, finite index evidence, random-variable preimage rows, distribution pushforward rows, product-cylinder readback, and finite $\RealUp$ product-fold provenance. It exports no conditional expectation, martingale, sigma-algebra completion, or standard probability-space bridge.
\end{theorem}
\begin{proof}
Read the ledger entries from \autoref{def:independence-finite-factorisation-row}. The source row supplies the carried probability space, the finite index evidence supplies the allowed family positions, and the random-variable rows supply readable preimages for the events used in each product cylinder.

The distribution rows supply only the marginal and joint pushforward endpoints attached to those same readable events. The product-cylinder readback records the equivalence between membership in the tuple cylinder and membership in every displayed component event. The $\RealUp$ product-fold provenance records how marginal values are multiplied and compared by the real classifier.

Exactness follows because the factorisation equation mentions only these exported rows:
$$
\mu_X^J(\operatorname{Cyl}_X(B))\sim_R\Pi_R(\mathsf{MargSp}_X(B)).
$$
Neither the statement nor the construction calls for conditional expectation, martingale filtrations, sigma-algebra completion, or a standard probability-space bridge. The ledger is therefore exact for the finite-family independence surface and silent about those additional probability-theoretic structures.
\end{proof}

\begin{lemma}[Finite RealUp product fold is invariant under certified reindexing]
\label{lem:realup-finite-product-permutation-readback}
Let $xs$ and $ys$ be finite spines of carried $\RealUp$ endpoints, and let
$$
\rho:\mathsf{Pos}(xs)\cong\mathsf{Pos}(ys)
$$
be a certified finite-position bijection in the sense of \autoref{def:finset-classifier-preserving-enumeration-permutation}. If each matched pair satisfies
$$
\mathsf{entry}_{xs}(i)\sim_R\mathsf{entry}_{ys}(\rho(i)),
$$
then the finite product fold $\Pi_R$ satisfies
$$
\Pi_R(xs)\sim_R\Pi_R(ys).
$$
\end{lemma}
\leanchecked{BEDC.Derived.IndependenceUp.IndependenceFiniteProduct\_reindexing\_readback}
\begin{proof}
Induct on the target spine $ys$. If $ys$ is empty, the certified inverse position map forces $\mathsf{Pos}(xs)$ to be empty as well. Both product folds are the multiplicative unit endpoint, so the $\RealUp$ classifier reflexivity row gives the claim.

In the cons case, write the head of $ys$ as $b$ and its tail as $t$. Let $i_0:=\rho^{-1}(\operatorname{head})$ be the source position matched with the target head. Removing $i_0$ from the source position spine and removing the head from $ys$ leaves a certified finite-position bijection between the residual source spine and $t$; this is the same inverse-map data used in \autoref{lem:finset-enum-position-bijection-inversion}, restricted away from the matched pair.

By the induction hypothesis, the product of the residual source spine is classified with $\Pi_R(t)$. The matched-pair hypothesis gives
$$
\mathsf{entry}_{xs}(i_0)\sim_R b.
$$
Multiplication congruence from \autoref{def:ring-stability-certificate} transports these two comparisons to the product of the selected head and the residual product. It remains only to compare the original source fold with the fold in which the selected occurrence $i_0$ is placed first. A finite sequence of adjacent swaps moves $i_0$ to the head of the source spine; each adjacent swap is justified by multiplicative commutativity from \autoref{def:commring-stability-certificate}, multiplicative associativity from \autoref{def:ring-stability-certificate}, and classifier transitivity. Hence the original source product is classified with $\mathsf{entry}_{xs}(i_0)\cdot_R\Pi_R(\text{residual})$, while the target product is classified with $b\cdot_R\Pi_R(t)$. The preceding congruence and transitivity give
$$
\Pi_R(xs)\sim_R\Pi_R(ys).
$$
\end{proof}

\begin{theorem}[Independence finite reindexing invariance]
\label{thm:independence-finite-reindexing-invariance}
Let $I$ be a finite $\FinSetUp$ index carrier, let $\pi:I\cong I$ be a $\PermutationUp$ certified bijection as in \autoref{sec:permutation-carrier}, and let $(X_i)_{i\in I}$ be a finite family of carried $\RandomVarUp$ maps over one carried $\ProbSpaceUp$ source. Suppose the family carries the finite factorisation row of \autoref{def:independence-finite-factorisation-row}. Define the reindexed family and marginals by
$$
X_i^{\pi}:=X_{\pi(i)},\qquad \mu_i^{\pi}:=\mu_{\pi(i)}.
$$
For every reindexed measurable event family $B=(B_i)_{i\in I}$, define the pulled-back original event family
$$
C_j:=B_{\pi^{-1}(j)}.
$$
Let the reindexed joint $\DistributionUp$ endpoint be read through the same product-cylinder ledger, so that the cylinder for $X^{\pi}$ at $B$ is classified with the cylinder for $X$ at $C$. Then the reindexed family also carries the finite $\IndependenceUp$ factorisation row:
$$
\mu_{X^{\pi}}^J(\operatorname{Cyl}_{X^{\pi}}(B))
\sim_R
\Pi_R(\mathsf{MargSp}_{X^{\pi}}(B)).
$$
\end{theorem}
\leanchecked{BEDC.Derived.IndependenceUp.IndependenceFiniteReindexing\_invariance}
\begin{proof}
Fix a measurable reindexed event family $B=(B_i)_{i\in I}$ and put $C_j:=B_{\pi^{-1}(j)}$. Since $\pi$ is a certified bijection, every target index $j$ has the unique source index $\pi^{-1}(j)$ and every source index $i$ is sent to $\pi(i)$. For each carried sample point $s$, the cylinder readbacks give
$$
s\in X^{-1}_{\pi}(\operatorname{Cyl}_{X^{\pi}}(B))
\Longleftrightarrow
\forall i\in I.\;X_{\pi(i)}(s)\in B_i
\Longleftrightarrow
\forall j\in I.\;X_j(s)\in B_{\pi^{-1}(j)}
\Longleftrightarrow
s\in X^{-1}(\operatorname{Cyl}_{X}(C)).
$$
Thus the reindexed cylinder and the original cylinder have the same displayed source-event readback. The $\DistributionUp$ pushforward row of \autoref{sec:distribution-certificate}, read through the event transport of \autoref{thm:semantic-namecert-pattern-ledger-transport}, gives
$$
\mu_{X^{\pi}}^J(\operatorname{Cyl}_{X^{\pi}}(B))
\sim_R
\mu_X^J(\operatorname{Cyl}_{X}(C)).
$$

Apply the original $\IndependenceUp$ factorisation row from \autoref{def:independence-finite-factorisation-row} to the event family $C$. This yields
$$
\mu_X^J(\operatorname{Cyl}_{X}(C))
\sim_R
\Pi_R(\mathsf{MargSp}_{X}(C)).
$$

It remains to compare the two marginal products. The original marginal spine at a position $j$ has entry
$$
\mathsf{MargSp}_{X}(C)(j)=\mu_j(C_j)=\mu_j(B_{\pi^{-1}(j)}),
$$
while the reindexed marginal spine at $i$ has entry
$$
\mathsf{MargSp}_{X^{\pi}}(B)(i)=\mu_i^{\pi}(B_i)=\mu_{\pi(i)}(B_i).
$$
Using the inverse certified bijection $j\mapsto\pi^{-1}(j)$ from \autoref{lem:finset-enum-position-bijection-inversion}, the entry at $j$ in the original spine is matched with the entry at $\pi^{-1}(j)$ in the reindexed spine, and these two entries are the same marginal endpoint. Classifier reflexivity gives the matched-entry comparison. Therefore \autoref{lem:realup-finite-product-permutation-readback} gives
$$
\Pi_R(\mathsf{MargSp}_{X}(C))
\sim_R
\Pi_R(\mathsf{MargSp}_{X^{\pi}}(B)).
$$

Transitivity of the $\RealUp$ classifier from \autoref{def:real-classifier-specification} composes the reindexed joint comparison, the original factorisation row, and the finite-product reindexing comparison. Hence
$$
\mu_{X^{\pi}}^J(\operatorname{Cyl}_{X^{\pi}}(B))
\sim_R
\Pi_R(\mathsf{MargSp}_{X^{\pi}}(B)).
$$
Since $B$ was arbitrary, the reindexed family carries the stated finite $\IndependenceUp$ factorisation row.
\end{proof}

\begin{theorem}[Independence\textsuperscript{$\uparrow$} measurable-image bridge for two variables]
\label{thm:independence-measurable-image-bridge}
Let $S$ be a carried $\ProbSpaceUp$ source.
Let
$$
X:S\to T,
Y:S\to U
$$
be carried $\RandomVarUp$ maps as in \autoref{sec:randomvar-carrier}, and suppose the pair $(X,Y)$ carries the binary finite factorisation row of $\IndependenceUp$ from \autoref{def:independence-finite-factorisation-row}.
Let
$$
f:T\to T',\qquad g:U\to U'$$
be carried $\RandomVarUp$ maps satisfying the readable preimage row of \autoref{sec:randomvar-certificate}.
Assume for every target-measurable $C_0\in\mathcal A_{T'}$ and $C_1\in\mathcal A_{U'}$ that the pullbacks
$$
A_0:=f^{-1}(C_0)\in\mathcal A_T,\qquad
A_1:=g^{-1}(C_1)\in\mathcal A_U
$$
are readable and satisfy
$$
t\in A_0\Longleftrightarrow f(t)\in C_0,
\qquad
u\in A_1\Longleftrightarrow g(\nu)\in C_1.
$$
Define the compositions
$$
H:=f\circ X,\qquad K:=g\circ Y
$$
and write $\mu_H,\mu_K,\mu_{H,K}^J$ for their pushforwards.

Fix measurable $C_0\in\mathcal A_{T'}$ and $C_1\in\mathcal A_{U'}$.
For every carried source point $s$ the readable preimage clauses give
$$
s\in H^{-1}(C_0)\Longleftrightarrow X(s)\in A_0,
\qquad
s\in K^{-1}(C_1)\Longleftrightarrow Y(s)\in A_1,
$$
and hence
$$
s\in \operatorname{Cyl}_{(H,K)}(C_0,C_1)
\Longleftrightarrow
\operatorname{Cyl}_{(X,Y)}(A_0,A_1).
$$
Applying the distribution pushforward row of \autoref{sec:distribution-certificate} to the two displayed cylinder events gives
$$
\mu_{H,K}^J\bigl(\operatorname{Cyl}_{(H,K)}(C_0,C_1)\bigr)\sim_R
\mu_{(X,Y)}^J\bigl(\operatorname{Cyl}_{(X,Y)}(A_0,A_1)\bigr),
$$
$$
\mu_H(C_0)\sim_R\mu_X(A_0),\qquad
\mu_K(C_1)\sim_R\mu_Y(A_1).
$$
The factorisation row of $(X,Y)$ from \autoref{def:independence-finite-factorisation-row} yields
$$
\mu_{(X,Y)}^J\bigl(\operatorname{Cyl}_{(X,Y)}(A_0,A_1)\bigr)\sim_R
\mu_X(A_0)\cdot_R\mu_Y(A_1).
$$
Transitivity of $\sim_R$ then gives
$$
\mu_{H,K}^J\bigl(\operatorname{Cyl}_{(H,K)}(C_0,C_1)\bigr)
\sim_R
\mu_H(C_0)\cdot_R\mu_K(C_1).
$$
Since $C_0,C_1$ were arbitrary measurable events, this is exactly the binary finite factorisation equation for the pair $(H,K)$. Therefore $f\circ X$ is independent of $g\circ Y$ under $\IndependenceUp$.
\end{theorem}
\leanchecked{BEDC.Derived.IndependenceUp.IndependenceBinaryFactorization\_measurable\_image\_bridge}

\begin{theorem}[Independence public NameCert export]
\label{thm:independence-public-namecert-export}
The finite-family carrier, factorisation classifier, stability transport, ledger exactness, finite reindexing row, and measurable-image bridge assemble the public reusable $\NameCert_{\IndependenceUp}$ export for the finite-family scope. Its carrier and classifier are the rows of \autoref{thm:independence-obligation-certificate-packet}; its primitive boundary is the scoped surface of \autoref{thm:independence-scoped-primitive-boundary}; its finite-product and reindexing stability are supplied by \autoref{lem:realup-finite-product-permutation-readback} and \autoref{thm:independence-finite-reindexing-invariance}; and its binary measurable-image transport is the bridge of \autoref{thm:independence-measurable-image-bridge}. This public export is reusable by downstream finite-family probability chapters without adding conditional-expectation, martingale, sigma-completion, host equality, host function equality, or standard bridge rows.
\end{theorem}
\begin{proof}
Apply \autoref{thm:independence-obligation-certificate-packet}. It supplies the finite-family carrier, factorisation classifier, stability transport, ledger exactness, and certificate packet for carried random-variable families over the displayed $\ProbSpaceUp$ source.

Apply \autoref{thm:independence-scoped-primitive-boundary} to fix the visible primitive boundary. The boundary identifies the exact $\ProbSpaceUp$, $\FinSetUp$, $\RandomVarUp$, $\DistributionUp$, $\PermutationUp$, $\RealUp$, BHist-readable cylinder, and product-fold rows consumed by the packet, and it excludes the probability-theoretic rows outside the finite-family surface.

For reusable finite-family stability, apply \autoref{lem:realup-finite-product-permutation-readback} and \autoref{thm:independence-finite-reindexing-invariance}. These rows make the product fold and the factorisation comparison invariant under certified finite reindexing.

Finally apply \autoref{thm:independence-measurable-image-bridge}. It gives the binary measurable-image transport row over the same factorisation classifier. Collecting these rows produces the public $\NameCert_{\IndependenceUp}$ export for the stated finite-family scope.
\end{proof}

\closureat{IndependenceUp}{bridgedStr}[BEDC.Derived.IndependenceUp.IndependenceBinaryFactorization\_measurable\_image\_bridge]

\begin{closurestatus}{\IndependenceUp}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{The scoped finite-family carrier, factorisation classifier, stability transport, ledger exactness, finite reindexing, and measurable-image bridge are bound over the displayed $\RandomVarUp$, $\DistributionUp$, $\FinSetUp$, $\PermutationUp$, $\RealUp$, BHist-readable cylinder, and product-fold rows.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.IndependenceUp.IndependenceBinaryFactorization\_measurable\_image\_bridge}
  \bridgestatus{paperBridge}
  \notclaimed{Full probability theory, sigma-algebra completion, conditional expectation, martingales, and standard bridge data are not claimed here.}
  \upgradepath{Mature closure requires downstream examples or cross-chapter consumption of the finite-family measurable-image bridge.}
\end{closurestatus}
