\chapter{A Concrete Naming Certificate for $\MarkovChainUp$}
\label{ch:concrete-instances-markovchain-namecert}

The Markov-chain interface $\MarkovChainUp$ packages a sequence of random variables in which the conditional distribution of each step depends only on the previous step. It depends on $\NameCert_{\RandomVarUp}$ (\autoref{ch:concrete-instances-randomvar-namecert}) and $\NameCert_{\DistributionUp}$ (\autoref{ch:concrete-instances-distribution-namecert}).

\section{Carrier definition}
\label{sec:markovchain-carrier}

\begin{definition}[MarkovChain BHist transition carrier]
\label{def:markovchain-bhist-transition-carrier}
A $\MarkovChainUp$ carrier is a finite $\mathsf{BHist}$ transition-row packet over a source $\ProbSpaceUp$ carrier. It consists of a unary time ledger, carried $\RandomVarUp$ rows $X_n:S\to E$ for each displayed time row, $\DistributionUp$ rows for the laws of those random variables, transition rows $K_n(e,-)$ whose endpoints are probability distributions on the next-state event family, and the visible $\hsame/\Cont/\Pkg$ provenance tying each transition row to the adjacent pair $X_n,X_{n+1}$.

The packet is accepted only when the $\Cont$ ledger records that the next-step distribution read for $X_{n+1}$ is sourced from the current-state endpoint of $X_n$ and the displayed transition row $K_n$. The carrier contains no host stochastic-process object, no filtration, no conditional-expectation primitive, and no standard Markov-kernel bridge; those may be named only by later certificates that consume this finite transition ledger.
\end{definition}
\leandef{BEDC.Derived.MarkovChainUp.MarkovChainBHistTransitionCarrier}

\begin{theorem}[MarkovChain kernel classifier stability]
\label{thm:markovchain-kernel-classifier-stability}
Let two $\MarkovChainUp$ transition packets have the same displayed unary time ledger. Suppose their $\ProbSpaceUp$ sources, $\RandomVarUp$ rows, $\DistributionUp$ law rows, and transition rows are related componentwise by $\hsame$, and suppose the transition $\Cont$ ledgers and $\Pkg$ provenance rows are transported along those comparisons. Then the transported rows form an accepted $\MarkovChainUp$ carrier, and the transition classifier has the same current-state to next-law shape.
\end{theorem}
\leanchecked{BEDC.Derived.MarkovChainUp.MarkovChainKernelClassifier\_stability}
\begin{proof}
Use the classifier field of the roadmap ten-field template. The source rows are the $\ProbSpaceUp$ carrier, the displayed $\RandomVarUp$ sequence, and the $\DistributionUp$ law rows; the carrier row is the finite $\mathsf{BHist}$ packet of \autoref{def:markovchain-bhist-transition-carrier}.

Transport each source row through the displayed $\hsame$ comparison. The $\RandomVarUp$ rows keep their domain in the same probability-space packet, and the $\DistributionUp$ rows keep the law endpoints attached to the transported random-variable rows.

Finally transport the transition $\Cont$ ledger and $\Pkg$ provenance. Since acceptance asks only that the next-step law be read through the adjacent carried rows and the displayed transition row, the transported packet satisfies the same carrier predicate without importing a host stochastic-process equality.
\end{proof}
\begin{theorem}[MarkovChain transition ledger exactness]
\label{thm:markovchain-transition-ledger-exactness}
For every accepted $\MarkovChainUp$ carrier, the transition ledger exposes exactly the $\mathsf{BHist}$ rows for the $\ProbSpaceUp$ source, the displayed $\RandomVarUp$ rows, the corresponding $\DistributionUp$ law rows, the transition rows $K_n$, the continuation row from the random-variable and transition rows, the provenance row from the probability-space and law rows, the endpoint row from provenance and transition-continuation rows, and the package provenance. It does not expose a host Markov process, a filtration, a conditional-expectation row, or a standard kernel bridge.
\end{theorem}
\leanchecked{BEDC.Derived.MarkovChainUp.MarkovChainTransitionPacket\_ledger\_exactness}
\begin{proof}
Inspect the carrier definition. Its accepted rows are precisely the source probability-space row, the displayed random-variable rows, the displayed distribution rows, the transition rows, and the provenance entries that bind adjacent time steps.

The ledger field of the ten-field template is the finite $\Cont$ display explaining how the transition-continuation row is read from the displayed random-variable row and $K_n$, how the provenance row is read from the probability-space and law rows, and how the endpoint is read from the provenance and transition-continuation rows. Projecting the ledger therefore returns only those named rows and their package provenance.

No constructor in the carrier produces a filtration, a conditional-expectation object, or a host stochastic-process carrier. Hence none of those external stochastic objects is exported by the transition ledger.
\end{proof}
\leanchecked{BEDC.Derived.MarkovChainUp.MarkovChainBHistTransitionCarrier\_transition\_ledger\_exactness}

\begin{theorem}[MarkovChain probability-random-variable source boundary]
\label{thm:markovchain-probspace-randomvar-source-boundary}
The $\MarkovChainUp$ source boundary is the joint BEDC packet consisting of the underlying $\ProbSpaceUp$ event-and-measure rows, the time-indexed $\RandomVarUp$ measurable-preimage rows, and the $\DistributionUp$ pushforward rows for the laws of the displayed random variables. Every transition row in an accepted carrier must read its source event through that packet, and no transition row may replace it with an external probability space, external random variable, or host distribution object.
\end{theorem}
\begin{proof}
Project the source field of the ten-field template. The probability-space source is the displayed $\ProbSpaceUp$ packet, and every random-variable row is carried over that same source packet.

Next project the law rows through $\DistributionUp$. Each law endpoint is a pushforward row for the corresponding $\RandomVarUp$ map, so the row remains inside the BEDC source boundary.

The transition row may consume those source, random-variable, and law rows through $\Cont$ and $\Pkg$ provenance only. This gives the stated boundary and excludes host probability spaces, host random variables, and host distribution objects.
\end{proof}
\leanchecked{BEDC.Derived.MarkovChainUp.MarkovChainBHistTransitionCarrier\_probspace\_randomvar\_source\_boundary}

\begin{theorem}[MarkovChain NameCert obligation surface]
\label{thm:markovchain-namecert-obligation-surface}
The local $\NameCert_{\MarkovChainUp}$ obligation surface is the transition carrier of \autoref{def:markovchain-bhist-transition-carrier}, the componentwise kernel classifier of \autoref{thm:markovchain-kernel-classifier-stability}, the transition ledger exactness row of \autoref{thm:markovchain-transition-ledger-exactness}, and the probability-random-variable source boundary of \autoref{thm:markovchain-probspace-randomvar-source-boundary}. The surface names only $\mathsf{BHist}$ rows, $\hsame$ comparisons, $\Cont$ transition displays, and $\Pkg$ provenance over $\ProbSpaceUp$, $\RandomVarUp$, and $\DistributionUp$ dependency certificates.
\end{theorem}
\leanchecked{BEDC.Derived.MarkovChainUp.MarkovChainTransitionCarrier\_semantic\_name\_certificate}
\begin{proof}
Assemble the obligation surface by the roadmap ten-field template. The traditional target is a discrete-time Markov chain; the BEDC source is the probability-space, random-variable, and distribution dependency packet; the carrier is the finite transition packet.

The classifier and stability fields are supplied by \autoref{thm:markovchain-kernel-classifier-stability}. The ledger and exactness fields are supplied by \autoref{thm:markovchain-transition-ledger-exactness}.

The source-boundary field is \autoref{thm:markovchain-probspace-randomvar-source-boundary}. Together these rows give the named $\NameCert_{\MarkovChainUp}$ obligation surface while keeping host stochastic-process structure outside the certificate.
\end{proof}

\begin{theorem}[MarkovChain scoped kernel dependency package]
\label{thm:markovchain-scoped-kernel-dependency-package}
The $\NameCert_{\MarkovChainUp}$ obligation surface of \autoref{thm:markovchain-namecert-obligation-surface} is scoped exactly by the $\ProbSpaceUp$, $\RandomVarUp$, and $\DistributionUp$ dependency certificates, the finite unary time ledger, the transition rows $K_n$, $\mathsf{BHist}$ rows, $\hsame$ comparisons, $\Cont$ displays, and $\mathsf{Pkg}$ provenance. No filtration, conditional-expectation primitive, host stochastic process, or standard Markov kernel is read by this scoped package.
\end{theorem}
\leanchecked{BEDC.Derived.MarkovChainUp.MarkovChainKernelClassifier\_endpoint\_confluence}
\begin{proof}
Project the carrier row from \autoref{def:markovchain-bhist-transition-carrier}. Its constructors expose only the source probability-space packet, the carried random-variable rows, the law rows, the unary time ledger, transition rows, and the displayed provenance.

Next use \autoref{thm:markovchain-kernel-classifier-stability} and \autoref{thm:markovchain-transition-ledger-exactness}. These identify the classifier transport and ledger reads with componentwise $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows over the same finite packet.

Finally apply \autoref{thm:markovchain-probspace-randomvar-source-boundary} together with \autoref{thm:markovchain-namecert-obligation-surface}. The dependency rows consumed by those projections are exactly the $\ProbSpaceUp$, $\RandomVarUp$, and $\DistributionUp$ certificates and the finite transition ledger, so the excluded stochastic-process, filtration, conditional-expectation, and standard-kernel objects remain outside the scoped package.
\end{proof}

\begin{theorem}[MarkovChain transition-packet scope]
\label{thm:markovchain-transition-packet-scope}
The paper scope of $\mathsf{MarkovChainTransitionPacket}$ is the finite
$\mathsf{BHist}$ packet consisting of
$\mathsf{ProbSpacePublicEventPacket}$ source rows,
$\mathsf{DistributionPushforwardSourceSpec}$ law rows,
$\mathsf{RandomVarTotalReadbackCertificate}$ current-to-next readback rows,
$\Cont$ provenance rows, $\hsame$ transport rows, and the visible
$\mathsf{BHist}$ time, current-state, next-state, transition, provenance, and
ledger endpoints. It introduces no host stochastic-process carrier, filtration,
conditional-expectation primitive, or standard Markov-kernel object.
\end{theorem}
\begin{proof}
Unfold the transition-packet rows. The source field is the public probability
event packet, the law field is the distribution pushforward source
specification, and the readback field is the random-variable total readback
certificate.

The remaining rows are the two displayed $\Cont$ ledgers: one from the current
state and transition row to the provenance endpoint, and one from that
provenance endpoint and law row to the ledger endpoint. The only transport
allowed across the packet is componentwise $\hsame$ on those displayed
$\mathsf{BHist}$ rows, so the external stochastic objects listed above are not
part of the scope.
\end{proof}

\begin{theorem}[MarkovChain Lean target surface]
\label{thm:markovchain-lean-target-surface}
The checked
$\mathsf{MarkovChainTransitionPacket\_kernel\_classifier\_stability}$ theorem
states that componentwise $\hsame$ transport of the source, time, current,
next, law, and transition rows, together with transported $\Cont$ provenance
and ledger rows, preserves the $\mathsf{MarkovChainTransitionPacket}$ carrier
and returns $\hsame$ comparisons for the provenance and ledger endpoints.
\end{theorem}
\leanchecked{BEDC.Derived.MarkovChainUp.MarkovChainTransitionPacket\_kernel\_classifier\_stability}
\begin{proof}
Read the checked theorem as the transition-packet classifier transport row.
The inputs are precisely the rows isolated in
\autoref{thm:markovchain-transition-packet-scope}.

The theorem transports the probability source, unary time row,
random-variable current and next endpoints, law row, and transition row by
$\hsame$. It then rebuilds the two $\Cont$ ledgers at the transported
endpoints, producing both the transported carrier packet and the displayed
provenance and ledger endpoint comparisons.
\end{proof}

\begin{theorem}[MarkovChain scoped obligation package]
\label{thm:markovchain-scoped-obligation-package}
The transition-packet stability theorem of
\autoref{thm:markovchain-lean-target-surface} supplies the scoped
carrier/classifier transport row for $\MarkovChainUp$. Ledger exactness and the
assembled $\NameCert_{\MarkovChainUp}$ remain paper obligations until their
corresponding rows are separately formalized.
\end{theorem}
\begin{proof}
Combine \autoref{thm:markovchain-transition-packet-scope} with
\autoref{thm:markovchain-lean-target-surface}. The former fixes the visible
carrier rows, and the latter proves that the classifier transport preserves
that packet.

The remaining fields of the local name certificate are not consequences of the
transport theorem alone. They require the ledger exactness row and the final
assembly of the $\NameCert_{\MarkovChainUp}$ surface, so they stay as stated
paper obligations.
\end{proof}

\section{The certificate}
\label{sec:markovchain-certificate}

\closureat{MarkovChainUp}{obligationStr}

\begin{closurestatus}{\MarkovChainUp}
  \constructivestory{A Markov-chain packet is generated from a displayed $\ProbSpaceUp$ source, a unary time ledger, carried $\RandomVarUp$ rows, $\DistributionUp$ law rows, transition rows, $\Cont$ displays, $\hsame$ transport, and $\mathsf{Pkg}$ provenance. The carrier accepts only finite transition ledgers whose next-law rows are sourced from the adjacent carried random-variable rows, so host stochastic-process objects, filtrations, conditional-expectation primitives, and standard kernel bridges remain outside the certificate.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{The obligation surface is exactly the $\mathsf{BHist}$ transition carrier, kernel classifier stability, transition ledger exactness, and probability-random-variable source boundary over $\ProbSpaceUp$, $\RandomVarUp$, $\DistributionUp$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{No host stochastic-process carrier, filtration, conditional-expectation construction, stationary law, martingale property, or standard kernel bridge is claimed.}
  \upgradepath{The next grade requires separate Lean rows for ledger exactness, source boundary, and assembled NameCert obligation surface beyond the checked transition-packet carrier/classifier transport theorem.}
\end{closurestatus}

\begin{definition}[MarkovChain finite-prefix restriction]
\label{def:markovchain-finite-prefix-restriction}
Let $P$ be a displayed $\MarkovChainUp$ transition packet over a unary time ledger with transition-time rows $0,\ldots,n+k-1$ and endpoint rows $0,\ldots,n+k$. The finite-prefix restriction $P_{\le n}$ is the subpacket obtained by keeping the same $\ProbSpaceUp$ source, the endpoint rows $X_0,\ldots,X_n$, the $\DistributionUp$ law rows read by the first $n$ transitions, the transition rows $K_0,\ldots,K_{n-1}$, and exactly the $\hsame/\Cont/\Pkg$ provenance entries whose adjacent endpoints both lie in $X_0,\ldots,X_n$.

No row with transition index at least $n$ is copied into $P_{\le n}$, and no row is reindexed except by the evident inclusion of the prefix ledger into the original unary ledger.
\end{definition}

\begin{theorem}[MarkovChain finite-prefix restriction carrier]
\label{thm:markovchain-finite-prefix-restriction-carrier}
Let $P$ be an accepted $\MarkovChainUp$ transition packet in the sense of \autoref{def:markovchain-bhist-transition-carrier}. Suppose its unary time ledger has length $n+k$, with endpoint rows $X_0,\ldots,X_{n+k}$ and transition rows $K_0,\ldots,K_{n+k-1}$. Then the finite-prefix restriction $P_{\le n}$ of \autoref{def:markovchain-finite-prefix-restriction}, consisting of the same $\ProbSpaceUp$ source, the first $n+1$ displayed $\RandomVarUp$ endpoint rows, the first $n$ next-law $\DistributionUp$ rows, the first $n$ transition rows, and the inherited adjacent $\hsame/\Cont/\Pkg$ provenance, is again an accepted $\MarkovChainUp$ carrier.
\end{theorem}
\begin{proof}
The carrier predicate of \autoref{def:markovchain-bhist-transition-carrier} is local along adjacent transition rows. It asks for a finite unary time ledger, carried $\RandomVarUp$ endpoint rows on that ledger, the displayed $\DistributionUp$ law rows read by the transition rows, and for each adjacent pair $X_i,X_{i+1}$ a $\Cont$ ledger and $\Pkg$ provenance row recording that the next-step distribution for $X_{i+1}$ is sourced from the current-state endpoint of $X_i$ through the displayed transition row $K_i$.

The prefix ledger $0,\ldots,n$ is finite because it is obtained by induction on the first $n$ successors of the original unary ledger. Its endpoint rows $X_0,\ldots,X_n$ are carried $\RandomVarUp$ rows because each is one of the carried endpoint rows of $P$. The retained next-law rows are $\DistributionUp$ rows for the same reason: each retained law row is one of the law rows already accepted in the original packet and is attached to the same adjacent transition where it is read.

It remains only to check the transition obligations. Fix a prefix transition index $i<n$. Since the original packet has length $n+k$, the same index also satisfies $i<n+k$. Acceptance of $P$ therefore supplies the transition row $K_i$ together with the displayed $\Cont$ ledger witnessing that the next-law row for $X_{i+1}$ is read from the current-state endpoint of $X_i$ through $K_i$, and the corresponding $\Pkg$ provenance. Both endpoints $X_i$ and $X_{i+1}$ lie in the retained endpoint list, and $K_i$ lies among the retained transition rows, so this exact $\Cont/\Pkg$ entry is a well-formed adjacent transition entry of $P_{\le n}$.

Every transition obligation of $P_{\le n}$ is obtained in this way from a unique transition obligation of $P$, and the restriction introduces no additional transition row whose source, target, law, or provenance would need a separate witness. The source-boundary statement of \autoref{thm:markovchain-probspace-randomvar-source-boundary} also remains unchanged, because the restricted packet keeps the same $\ProbSpaceUp$ source and only discards later rows. Thus all fields required by the MarkovChain transition carrier predicate are present in the restricted finite packet, so $P_{\le n}$ is an accepted $\MarkovChainUp$ carrier.
\end{proof}

\begin{theorem}[MarkovChain transition-packet concatenation closure]
\label{thm:markovchain-transition-packet-concatenation-closure}
Let $P_1$ be an accepted $\MarkovChainUp$ transition packet of length $n$ over a unary time ledger $T_1$, with displayed random-variable rows
$$
X_0,X_1,\ldots,X_n
$$
source law rows $\mu^X_0,\mu^X_1,\ldots,\mu^X_n$, transition rows $K^X_0,\ldots,K^X_{n-1}$, and transition provenance ledgers accepted by \autoref{def:markovchain-bhist-transition-carrier}. Let $P_2$ be an accepted $\MarkovChainUp$ transition packet of length $m$ over a unary time ledger $T_2$, over the same displayed $\ProbSpaceUp$ source, with displayed random-variable rows
$$
Y_0,Y_1,\ldots,Y_m
$$
source law rows $\mu^Y_0,\mu^Y_1,\ldots,\mu^Y_m$, transition rows $K^Y_0,\ldots,K^Y_{m-1}$, and accepted transition provenance ledgers. Suppose the shared endpoint is displayed by a $\RandomVarUp$ classifier row
$$
\hsame(X_n,Y_0)
$$
over that same $\ProbSpaceUp$ source, and let the induced $\DistributionUp$ law comparison identify the endpoint law rows $\mu^X_n$ and $\mu^Y_0$. If the unary ledgers are displayed with a concatenation row
$$
\Cont(T_1,T_2,T_{12})
$$
so that $T_{12}$ is the unary ledger of length $n+m$, then the end-to-end displayed packet $P_{12}$ is an accepted $\MarkovChainUp$ transition packet over $T_{12}$. Its random-variable row at time $i$ is $X_i$ for $0\leq i\leq n$ and $Y_j$ for $i=n+j$ with $1\leq j\leq m$; its transition rows are $K^X_i$ for $0\leq i<n$ and the shifted rows $K^Y_j$ for $0\leq j<m$, with the first shifted row read across the splice comparison $\hsame(X_n,Y_0)$.
\end{theorem}
\begin{proof}
Unpack the accepted carrier condition in \autoref{def:markovchain-bhist-transition-carrier}. The first packet supplies the common $\ProbSpaceUp$ source, the random-variable rows $X_i$, the law rows $\mu^X_i$, the transition rows $K^X_i$, and for every $0\leq i<n$ a displayed $\Cont/\Pkg$ provenance ledger certifying that the next-step law for $X_{i+1}$ is read from the current-state endpoint of $X_i$ through $K^X_i$. The second packet supplies the same kind of data for $Y_j$, $\mu^Y_j$, and $K^Y_j$ for $0\leq j<m$ over the same probability source.

Define the displayed concatenated row sequence by
$$
Z_i:=X_i\quad(0\leq i\leq n),
\qquad
Z_{n+j}:=Y_j\quad(1\leq j\leq m).
$$
Define its law rows by
$$
\lambda_i:=\mu^X_i\quad(0\leq i\leq n),
\qquad
\lambda_{n+j}:=\mu^Y_j\quad(1\leq j\leq m).
$$
The endpoint law at the splice is well-defined on the displayed carrier because the hypothesis $\hsame(X_n,Y_0)$ is a $\RandomVarUp$ comparison over the shared $\ProbSpaceUp$ source, and the pushforward classifier of \autoref{def:distribution-pushforward-classifier} transports the law row of $Y_0$ to the law row already carried by $X_n$.

The transition rows of $P_{12}$ are the visible list
$$
K^X_0,\ldots,K^X_{n-1},K^Y_0,\ldots,K^Y_{m-1}.
$$
For indices $i<n$, the required adjacent provenance row from $Z_i$ to $Z_{i+1}$ is exactly the accepted provenance row of $P_1$. For indices $i=n+j$ with $1\leq j<m$, the required adjacent provenance row from $Z_{n+j}=Y_j$ to $Z_{n+j+1}=Y_{j+1}$ is exactly the accepted provenance row of $P_2$.

It remains to check the splice transition, the row using $K^Y_0$ from time $n$ to time $n+1$. In $P_2$, acceptance says that the next-step law for $Y_1$ is read from the current-state endpoint $Y_0$ through $K^Y_0$, with its displayed $\Cont/\Pkg$ provenance. Transport the current-state endpoint and its law row along
$$
\hsame(X_n,Y_0).
$$
By \autoref{thm:markovchain-kernel-classifier-stability}, this componentwise transport preserves acceptance of the transition row and preserves the current-state to next-law classifier shape. Therefore the transported splice row reads the same next-step law $\mu^Y_1$ from the concatenated current row $Z_n=X_n$ through $K^Y_0$.

The time ledger is finite and unary because $T_1$ and $T_2$ are unary and the displayed continuation row $\Cont(T_1,T_2,T_{12})$ is the finite BEDC concatenation of those two ledgers. The transition provenance ledgers concatenate in the same order: rows internal to $P_1$ and $P_2$ are inherited, and the single boundary row is the transported splice row just constructed. The carrier definition asks for no host stochastic process, filtration, conditional expectation, or standard kernel bridge; it asks only for these displayed random-variable rows, law rows, transition rows, and $\hsame/\Cont/\Pkg$ provenance. Hence the assembled packet satisfies the accepted $\MarkovChainUp$ carrier predicate over the unary ledger $T_{12}$ of length $n+m$.
\end{proof}

\begin{definition}[MarkovChain finite-suffix restriction]
\label{def:markovchain-finite-suffix-restriction}
Let $P$ be a displayed $\MarkovChainUp$ transition packet over a unary time ledger with transition-time rows $0,\ldots,n+k-1$ and endpoint rows $0,\ldots,n+k$. The finite-suffix restriction $P_{\ge n}^{k}$ is the packet obtained by keeping the same $\ProbSpaceUp$ source, replacing the initial endpoint by the boundary row $X_n$, retaining the endpoint rows
$$
X_n,X_{n+1},\ldots,X_{n+k},
$$
retaining the law rows read at those endpoints, retaining the transition rows
$$
K_n,K_{n+1},\ldots,K_{n+k-1},
$$
and retaining exactly the $\hsame/\Cont/\Pkg$ provenance entries whose adjacent endpoints both lie in that displayed suffix.

The suffix ledger is the unary ledger of length $k$ whose endpoint row $j$ is read as the original endpoint row $n+j$ and whose transition row $j<k$ is read as the original transition row $n+j$. No transition row before $n$ is copied into $P_{\ge n}^{k}$.
\end{definition}

\begin{theorem}[MarkovChain finite-suffix restriction carrier]
\label{thm:markovchain-finite-suffix-restriction-carrier}
Let $P$ be an accepted $\MarkovChainUp$ transition packet in the sense of \autoref{def:markovchain-bhist-transition-carrier}. Suppose its unary time ledger has length $n+k$, with endpoint rows $X_0,\ldots,X_{n+k}$ and transition rows $K_0,\ldots,K_{n+k-1}$. Then the finite-suffix restriction $P_{\ge n}^{k}$ of \autoref{def:markovchain-finite-suffix-restriction}, consisting of the same $\ProbSpaceUp$ source, the displayed endpoint rows $X_n,\ldots,X_{n+k}$, the corresponding $\DistributionUp$ law rows, the transition rows $K_n,\ldots,K_{n+k-1}$, and the inherited adjacent $\hsame/\Cont/\Pkg$ provenance, is again an accepted $\MarkovChainUp$ carrier.
\end{theorem}
\begin{proof}
The carrier predicate of \autoref{def:markovchain-bhist-transition-carrier} is local along adjacent transition rows. It requires a finite unary ledger, carried $\RandomVarUp$ endpoint rows, law rows supplied by $\DistributionUp$, transition rows, and for each adjacent pair a displayed $\Cont$ ledger and $\Pkg$ provenance row witnessing that the next-step distribution is read from the current-state endpoint through the displayed transition row.

The suffix ledger is finite because it is the displayed block of $k$ successive transitions beginning at the boundary endpoint $X_n$. Its endpoint row $j$ is $X_{n+j}$ for $0\leq j\leq k$, and its transition row $j<k$ is $K_{n+j}$. Each such endpoint and transition row is already a row of the accepted packet $P$, so the restricted packet obtains its $\RandomVarUp$ and transition data by projection from $P$ rather than by introducing any outside stochastic-process object.

The boundary condition at the first suffix time is the only place where a prefix argument does not directly apply. In $P_{\ge n}^{k}$ the initial row is $X_n$, not $X_0$. This causes no additional obligation: the MarkovChain carrier does not require a distinguished initial law supplied by the original start row. It requires only that every displayed transition row have its adjacent source and target endpoints and its next-law row. For the first suffix transition, acceptance of $P$ at the original index $n$ supplies exactly the row
$$
X_n \xrightarrow{K_n} X_{n+1}
$$
with the displayed $\Cont/\Pkg$ provenance saying that the next-step law of $X_{n+1}$ is read from the current-state endpoint of $X_n$ through $K_n$. Thus the suffix packet has the required first adjacent transition ledger.

For any remaining suffix transition $j<k$, the corresponding original index is $n+j<n+k$. Acceptance of $P$ supplies the transition row $K_{n+j}$, the adjacent endpoints $X_{n+j}$ and $X_{n+j+1}$, the law row for the target endpoint, and the provenance witnessing the same current-state to next-law read. These are precisely the rows displayed at suffix positions $j$ and $j+1$, so the original provenance is well-typed after the suffix reindexing.

Every transition obligation of $P_{\ge n}^{k}$ is obtained from exactly one transition obligation of $P$ with index between $n$ and $n+k-1$, and the suffix construction creates no additional transition. The source boundary of \autoref{thm:markovchain-probspace-randomvar-source-boundary} is preserved because the restricted packet keeps the same $\ProbSpaceUp$ source and only discards rows outside the suffix. Hence all rows required by the accepted $\MarkovChainUp$ transition carrier predicate are present in $P_{\ge n}^{k}$.
\end{proof}
