\chapter{A Concrete Naming Certificate for $\TaylorModelUp$}
\label{ch:concrete-instances-taylormodel-namecert}
\origin{human}

The $\TaylorModelUp$ packet names the finite Taylor-jet enclosure method used in Berz-style and Makino--Berz validated numerics, but it records only finite BEDC rows. A packet exposes a center observation, dyadic jet coefficients, an interval or dyadic-ball remainder, an interval-arithmetic ledger, a real-name evaluation route, a validated readback certificate, package provenance, and a local naming row. It does not import host Taylor series semantics, analytic convergence, selected real limits, or quotient real equality.

The carrier consumes the interval-operation ledger of \autoref{ch:concrete-instances-intervalarithmetic-namecert}, the dyadic-ball remainder surface of \autoref{ch:concrete-instances-dyadicball-namecert}, the validated readback certificate of \autoref{ch:concrete-instances-validatednumerics-namecert}, and the NewtonIteration provenance route of \autoref{ch:concrete-instances-newtoniteration-namecert}. These sibling rows are the horizontal dependency lattice for the center, jet, remainder, operation, readback, and provenance coordinates below.

\begin{definition}[TaylorModel BHist carrier]
\label{def:taylormodel-bhist-carrier}
A $\TaylorModelUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
T=(c,J,R,I,E,V,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $c$ is a center $\RealUp$ finite observation row;
\item $J$ is a finite jet ledger of dyadic coefficient histories, with every coefficient read through $\DyadicRatCoreUp$ and finite $\StreamNameUp$ windows;
\item $R$ is an $\IntervalArithmeticUp$ interval row or $\DyadicBallUp$ remainder enclosure attached to the same precision window;
\item $I$ is the $\IntervalArithmeticUp$ operation ledger recording each polynomial, interval, and remainder operation used by the enclosure;
\item $E$ is the $\RealUp$ and $\RegSeqRatUp$ finite-window evaluation route through which consumers read the center, coefficient, and remainder rows;
\item $V$ is the $\ValidatedNumericsUp$ readback certificate asserting that the displayed route returns an enclosure row rather than a selected host value;
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\IntervalArithmeticUp$, $\DyadicBallUp$, $\ValidatedNumericsUp$, and $\NewtonIterationUp$;
\item $N$ is the local $\NameCert_{\TaylorModelUp}$ row.
\end{enumerate}
Two accepted carriers are classified together only when the center row, finite jet ledger, remainder enclosure, interval-operation ledger, evaluation route, readback certificate, package row, and local naming row are transported componentwise by the displayed $\hsame$ comparisons and $\Cont$ routes.
\end{definition}
\leandef{BEDC.Derived.TaylorModelUp.TaylorModelCarrier}

\begin{theorem}[TaylorModel NameCert obligation surface]
\label{thm:taylormodel-namecert-obligation-surface}
The local $\NameCert_{\TaylorModelUp}$ surface for the carrier of \autoref{def:taylormodel-bhist-carrier} consists of five rows:
\begin{enumerate}
\item carrier habitation by the finite packet $T=(c,J,R,I,E,V,P,N)$;
\item classifier stability under componentwise $\hsame$ comparisons and displayed $\Cont$ routes for $c,J,R,I,E,V,P,N$;
\item finite-jet transport through the $\DyadicRatCoreUp$ coefficient histories and their $\StreamNameUp$ windows;
\item interval-remainder soundness through the $\IntervalArithmeticUp$ ledger and the displayed $R$ enclosure;
\item non-escape from host Taylor series, analytic convergence, selected real limits, and quotient real equality.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.TaylorModelUp.TaylorModelJetLedger\_finite\_transport}
\begin{proof}
Carrier habitation is projection from \autoref{def:taylormodel-bhist-carrier}. The center, finite jet, remainder, ledger, evaluation, readback, package, and local certificate rows are visible coordinates of one finite packet.

Classifier stability is componentwise. The accepted classifier may replace a displayed row only by a recorded $\hsame$ comparison or by a $\Cont$ route that reads the same row inside the same packet.

The remaining rows are the coefficient transport, interval-remainder enclosure, and non-escape boundary stated below. Together they describe exactly what the local naming certificate must expose to a consumer of the finite Taylor-jet enclosure.
\end{proof}

\begin{theorem}[TaylorModel finite-jet transport]
\label{thm:taylormodel-finite-jet-transport}
For every accepted $\TaylorModelUp$ carrier $T=(c,J,R,I,E,V,P,N)$, every consumer-visible coefficient read factors through the finite jet ledger $J$, its displayed $\DyadicRatCoreUp$ coefficient histories, the finite $\StreamNameUp$ windows used to inspect them, the evaluation route $E$, and the componentwise $\hsame$ and $\Cont$ rows recorded by the packet classifier.
\end{theorem}
\leanchecked{BEDC.Derived.TaylorModelUp.TaylorModelFiniteJet\_transport}
\begin{proof}
Project the packet to its jet coordinate $J$. Since $J$ is finite, each coefficient requested by a consumer is one of the displayed dyadic coefficient histories rather than a term of an ambient infinite series.

The consumer reaches a coefficient through the $\StreamNameUp$ window named in $J$ and through the evaluation route $E$. Transport along accepted classifiers preserves those two displayed rows by the stored $\hsame$ comparisons and $\Cont$ routes.

Thus the coefficient read remains inside the finite jet ledger and cannot appeal to a host Taylor series or to an unbounded coefficient family.
\end{proof}

\begin{theorem}[TaylorModel interval-remainder soundness]
\label{thm:taylormodel-interval-remainder-soundness}
Every enclosure exported by an accepted $\TaylorModelUp$ carrier is bounded by the displayed remainder row $R$ and the $\IntervalArithmeticUp$ operation ledger $I$. The bound is read through the same center row $c$, finite jet ledger $J$, evaluation route $E$, and validated readback certificate $V$, and it exports no external analytic convergence theorem.
\end{theorem}
\leanchecked{BEDC.Derived.TaylorModelUp.TaylorModelCarrier\_interval\_remainder\_soundness}
\begin{proof}
Start with an exported enclosure read. The read first identifies the center row $c$ and the finite jet ledger $J$ used by the polynomial part of the packet.

The remainder coordinate $R$ is then read through the interval or dyadic-ball enclosure named by the packet. The operation ledger $I$ records the finite interval-arithmetic route by which polynomial and remainder rows are combined.

The validated readback row $V$ certifies that the consumer receives the displayed enclosure. Since every operation has already passed through $I$ and $R$, soundness is a statement about those finite rows and not about analytic convergence in a host real model.
\end{proof}

\begin{theorem}[TaylorModel validated consumer boundary]
\label{thm:taylormodel-validated-consumer-boundary}
Every $\ValidatedNumericsUp$ consumer of an accepted $\TaylorModelUp$ packet receives only the displayed center row, finite jet ledger, remainder enclosure, interval-operation ledger, $\RealUp$ and $\RegSeqRatUp$ evaluation route, readback certificate, package provenance, and local naming row. The consumer receives no host Taylor series object, no selected real limit, and no quotient real equality witness.
\end{theorem}
\leanchecked{BEDC.Derived.TaylorModelUp.TaylorModelCarrier\_validated\_consumer\_boundary}
\begin{proof}
Read the carrier coordinates of \autoref{def:taylormodel-bhist-carrier}. The rows available to a validated-numerics consumer are exactly $c,J,R,I,E,V,P,N$.

Apply \autoref{thm:taylormodel-finite-jet-transport} to every coefficient request and \autoref{thm:taylormodel-interval-remainder-soundness} to every enclosure request. These two routes account for all numeric information exposed by the packet.

No remaining coordinate names a host Taylor series, an analytic radius of convergence, a selected real limit, or quotient equality of real names. The consumer boundary is therefore the finite readback surface alone.
\end{proof}

\begin{theorem}[TaylorModel seed public package]
\label{thm:taylormodel-seed-public-package}
The carrier of \autoref{def:taylormodel-bhist-carrier}, the NameCert surface of \autoref{thm:taylormodel-namecert-obligation-surface}, the finite-jet transport of \autoref{thm:taylormodel-finite-jet-transport}, the interval-remainder soundness of \autoref{thm:taylormodel-interval-remainder-soundness}, and the validated consumer boundary of \autoref{thm:taylormodel-validated-consumer-boundary} assemble the seed $\TaylorModelUp$ public package over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\IntervalArithmeticUp$, $\DyadicBallUp$, $\ValidatedNumericsUp$, and $\NewtonIterationUp$.
\end{theorem}
\leanchecked{BEDC.Derived.TaylorModelUp.TaylorModelCarrier\_seed\_public\_package}
\begin{proof}
Project the finite packet
$$
T=(c,J,R,I,E,V,P,N).
$$
The carrier and NameCert surface expose the rows required for a local naming certificate.

The finite-jet theorem accounts for coefficient transport, and the interval-remainder theorem accounts for enclosure soundness through the displayed operation ledger. The validated consumer theorem then fixes the downstream boundary of every readback.

The package provenance $P$ names exactly the dependency rows listed in the theorem statement. Hence the seed package is a finite BEDC naming certificate for Taylor-model enclosures, with no analytic object outside the displayed packet.
\end{proof}

\closureat{TaylorModelUp}{seedStr}

\begin{closurestatus}{\TaylorModelUp}
  \constructivestory{A $\TaylorModelUp$ packet is generated from a center $\RealUp$ observation row, a finite dyadic jet ledger, an interval or dyadic-ball remainder enclosure, an $\IntervalArithmeticUp$ operation ledger, a $\RealUp$ and $\RegSeqRatUp$ evaluation route, a $\ValidatedNumericsUp$ readback certificate, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite carrier, five-row NameCert obligation surface, coefficient transport, interval-remainder soundness, validated consumer boundary, and dependency package for finite Taylor-jet enclosures.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host Taylor series semantics, analytic convergence, selected real limits, quotient real equality, public Taylor-model algebra, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier habitation, classifier stability under $\hsame$ and $\Cont$, finite-jet transport, interval-remainder soundness, and non-escape for the same packet rows.}
\end{closurestatus}

\begin{definition}[TaylorModel displayed finite-jet subwindow]
\label{def:taylormodel-displayed-finite-jet-subwindow}
Let $T=(c,J,R,I,E,V,P,N)$ be an accepted $\TaylorModelUp$ carrier in the sense of \autoref{def:taylormodel-bhist-carrier}. A displayed finite-jet subwindow $J'\preceq_J J$ is a finite prefix or finite contiguous subledger of $J$ equipped with the following retained rows:
\begin{enumerate}
\item every coefficient history displayed in $J'$ is one of the $\DyadicRatCoreUp$ coefficient histories displayed in $J$;
\item the $\StreamNameUp$ window attached to a retained coefficient is the same displayed window as in $J$, or a displayed smaller finite window reached by a $\Cont$ route already present in the packet;
\item the restricted evaluation row $E\vert_{J'}$ contains exactly the coefficient-read routes of $E$ whose coefficient selector lies in $J'$;
\item the restricted readback row $V\vert_{J'}$ validates only the finite reads routed through $E\vert_{J'}$;
\item the restricted provenance and local name rows $P\vert_{J'}$ and $N\vert_{J'}$ name the same dependency certificates as $P$ and $N$, but only for the retained coefficient selectors and their windows.
\end{enumerate}
The projected TaylorModel read surface over $J'$ is the finite packet
$$
T\vert_{J'}=(c,J',R\vert_{J'},I\vert_{J'},E\vert_{J'},V\vert_{J'},P\vert_{J'},N\vert_{J'}),
$$
where $R\vert_{J'}$ and $I\vert_{J'}$ are the remainder and interval-operation rows read only at the retained coefficient selectors. The notation records a displayed packet restriction; it is not a quotient of Taylor series and it does not introduce an ambient coefficient family.
\end{definition}

\begin{proposition}[TaylorModel finite-jet prefix restriction]
\label{prop:taylormodel-finite-jet-prefix-restriction}
Let $T=(c,J,R,I,E,V,P,N)$ be an accepted $\TaylorModelUp$ carrier, and let $J'\preceq_J J$ be a displayed finite-jet subwindow as in \autoref{def:taylormodel-displayed-finite-jet-subwindow}. Suppose every consumer-visible coefficient request under consideration has its coefficient selector in $J'$ and that its $\StreamNameUp$ window is one of the retained windows of $J'$. Then the projected packet $T\vert_{J'}$ is an accepted finite $\TaylorModelUp$ read surface for those consumers. Moreover, every such consumer-visible coefficient read factors through $J'$, $E\vert_{J'}$, and the retained $\StreamNameUp$ window, and no coefficient row in $J\setminus J'$ is accessed.
\end{proposition}
\leanchecked{BEDC.Derived.TaylorModelUp.TaylorModelCarrier\_finite\_jet\_prefix\_restriction}
\begin{proof}
Project the accepted carrier through \autoref{def:taylormodel-bhist-carrier}. The jet coordinate $J$ is a finite ledger of displayed $\DyadicRatCoreUp$ coefficient histories, and the only public coefficient-read routes are the finite $\StreamNameUp$ windows and the evaluation route $E$ attached to those histories.

By \autoref{def:taylormodel-displayed-finite-jet-subwindow}, the subwindow $J'$ retains only coefficient histories already displayed in $J$. Hence every coefficient row in $J'$ is still a valid dyadic coefficient history, and every retained window is either the same finite window as in $J$ or a smaller finite window reached by a displayed $\Cont$ route. Since a finite prefix or finite contiguous subledger of a finite ledger is finite, $J'$ is again a finite coefficient ledger.

Restrict the evaluation and readback rows to the retained selectors. The row $E\vert_{J'}$ contains exactly the routes by which the selected coefficients are read, and $V\vert_{J'}$ validates exactly those finite routes as readback rows. The restricted provenance and local naming rows keep the same dependency certificates named by the original packet, now indexed only by the retained selectors. Thus the projected packet has the same kind of visible coordinates as the TaylorModel carrier, but with its coefficient surface replaced by the displayed finite subwindow.

Apply \autoref{thm:taylormodel-finite-jet-transport} to a consumer-visible coefficient request for $T$. The original factorization passes through $J$, the coefficient history selected there, the attached $\StreamNameUp$ window, the evaluation route $E$, and the componentwise $\hsame$ and $\Cont$ rows recorded by the packet classifier. The hypothesis says that the selector for this request lies in $J'$ and that the attached window is retained in $J'$. Therefore the same factorization factors through $J'$ and $E\vert_{J'}$ after replacing each unrestricted row by its retained projection.

No discarded coefficient is needed in this read. A row in $J\setminus J'$ has no selector in the restricted consumer surface, no route in $E\vert_{J'}$, and no validation entry in $V\vert_{J'}$. The interval and remainder rows used by the projected surface are likewise the restricted rows $I\vert_{J'}$ and $R\vert_{J'}$, so a retained coefficient read cannot obtain an outside coefficient indirectly through the operation ledger.

Finally apply \autoref{thm:taylormodel-validated-consumer-boundary}. A validated consumer receives only the displayed center row, finite jet ledger, remainder enclosure, interval-operation ledger, evaluation route, readback certificate, package provenance, and local naming row. For the projected surface these rows are exactly $c$, $J'$, $R\vert_{J'}$, $I\vert_{J'}$, $E\vert_{J'}$, $V\vert_{J'}$, $P\vert_{J'}$, and $N\vert_{J'}$. Thus the projected packet is an accepted finite TaylorModel read surface for the stated consumers, and every visible coefficient read is exhausted by the retained finite jet subwindow.
\end{proof}
