\chapter{A Concrete Naming Certificate for $\FibonacciInverseLimitUp$}
\label{ch:concrete-instances-fibonacci-inverse-limit-namecert}
\origin{human}

The $\FibonacciInverseLimitUp$ interface is a BEDC-native finite certificate surface.

The $\FibonacciInverseLimitUp$ interface names the finite-prefix surface of a projective Fibonacci-modulus tower. It records compatible prefixes over already displayed BEDC packets and does not import external rings, quotient completion, choice, topology, Haar measure, compactness, or an external profinite-ring theorem.

\begin{definition}[Fibonacci inverse-limit carrier]
\label{def:fibonacci-inverse-limit-carrier}
A $\FibonacciInverseLimitUp$ carrier is a finite compatible prefix packet
$$
Q=(G,F,W,R,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $G$ is a finite $\GoldenMeanShiftUp$ admissibility ledger for the inspected prefix windows;
\item $F$ is a finite $\FibonacciCubeUp$ modulus-coordinate ledger for the same windows;
\item $W$ is the $\StreamNameUp$ window schedule selecting exactly the displayed prefix packets;
\item $R$ records the finite projection rows between adjacent Fibonacci-modulus windows and their compatibility witnesses;
\item $H$ records componentwise $\hsame$ transports for the golden-mean rows, cube rows, stream-window rows, and projection rows inside $\mathsf{BHist}$;
\item $C$ records the displayed $\Cont$ routes by which consumers read a smaller prefix from a larger recorded prefix;
\item $P$ is the $\Pkg$ provenance over $\GoldenMeanShiftUp$, $\FibonacciCubeUp$, $\StreamNameUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and the local naming row;
\item $N$ is the local $\NameCert_{\FibonacciInverseLimitUp}$ row.
\end{enumerate}
The carrier contains only finite prefix packets and their displayed projection routes. It contains no completed topological carrier, no quotient of streams, no selected infinite point, no Haar measure row, and no external profinite-ring theorem.
\end{definition}

\begin{theorem}[Fibonacci inverse-limit NameCert obligations]
\label{thm:fibonacci-inverse-limit-namecert-obligations}
Every accepted $\FibonacciInverseLimitUp$ packet with carrier \autoref{def:fibonacci-inverse-limit-carrier} carries exactly the following local naming-certificate obligations:
\begin{enumerate}
\item carrier habitation by the empty compatible prefix packet with empty $\GoldenMeanShiftUp$, $\FibonacciCubeUp$, $\StreamNameUp$, and projection rows;
\item prefix classifier transport along the componentwise $\hsame$ rows for $G$, $F$, $W$, $R$, $H$, $C$, $P$, and $N$;
\item projection compatibility for every displayed finite route from a larger Fibonacci-modulus prefix to a smaller prefix;
\item finite-prefix exhaustion: every public finite read of the inverse-limit surface factors through some row already selected by $W$ and $R$;
\item ledger non-escape: downstream consumers can read only $G$, $F$, $W$, $R$, $H$, $C$, $P$, and $N$.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.FibonacciInverseLimitUp.FibonacciInverseLimitPacket\_namecert\_obligation\_surface}
\begin{proof}
Carrier habitation uses the empty prefix window. The empty $\GoldenMeanShiftUp$ and $\FibonacciCubeUp$ rows, the empty $\StreamNameUp$ schedule, and the empty projection ledger form a finite $\mathsf{BHist}$ packet with identity transport and local naming evidence.

Classifier transport is componentwise. Moving a prefix row by $\hsame$ also moves its golden-mean admissibility row, Fibonacci-cube modulus row, selected stream window, and projection witness through the matching entries of $H$.

Projection compatibility is the content of the route ledger $R$ and the consumer routes $C$. A smaller prefix is obtained only by following a displayed route from a larger recorded prefix, so no hidden tower map is available.

Finite-prefix exhaustion follows from the selected window schedule $W$. A public read must first choose a recorded window and then read through the corresponding projection row in $R$.

The non-escape clause is a coordinate inspection of \autoref{def:fibonacci-inverse-limit-carrier}. Since the carrier has no coordinate for topology, quotient completion, Haar measure, a selected infinite point, or an external profinite-ring theorem, none of those objects can be exported by its local certificate.
\end{proof}

\begin{theorem}[Fibonacci inverse-limit prefix projection exactness]
\label{thm:fibonacci-inverse-limit-prefix-projection-exactness}
Let $Q=(G,F,W,R,H,C,P,N)$ be an accepted $\FibonacciInverseLimitUp$ carrier. For every displayed pair of Fibonacci-modulus prefix windows in $W$, each consumer read of the smaller window factors through the unique recorded projection row in $R$, then through the transported $\GoldenMeanShiftUp$ and $\FibonacciCubeUp$ rows named by $G$ and $F$. Thus a finite prefix is exact relative to the recorded tower data and is not reconstructed from an unrecorded infinite point.
\end{theorem}
\begin{proof}
Begin with a consumer read of a smaller prefix. The schedule $W$ selects the requested finite window before any coordinate can be inspected.

The projection ledger $R$ then supplies the displayed route from the larger recorded prefix to the smaller one. The route is stabilized by the matching $\hsame$ entries in $H$ and by the $\Cont$ read in $C$.

Finally, the golden-mean and Fibonacci-cube rows $G$ and $F$ verify that the projected row remains inside the finite admissibility and modulus surfaces. No step asks for a completed inverse-limit point or a quotient of compatible streams.
\end{proof}

\begin{theorem}[Fibonacci inverse-limit ledger non-escape]
\label{thm:fibonacci-inverse-limit-ledger-non-escape}
The public boundary of an accepted $\FibonacciInverseLimitUp$ packet exports only finite $\GoldenMeanShiftUp$ admissibility rows, finite $\FibonacciCubeUp$ modulus rows, selected $\StreamNameUp$ windows, projection-compatibility rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ evidence. It exports no compactness theorem, no topology of the inverse limit, no Haar measure, no quotient completion, no choice-selected infinite point, and no external profinite-ring theorem.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:fibonacci-inverse-limit-carrier}. The rows $G$, $F$, $W$, $R$, $H$, $C$, $P$, and $N$ exhaust the public packet.

By \autoref{thm:fibonacci-inverse-limit-prefix-projection-exactness}, every finite consumer read reaches a selected window and a displayed projection row before it reaches a prefix value. This keeps all reads inside finite prefix data.

Therefore the packet can serve as a concrete BEDC naming certificate for finite inverse-limit projections, but it does not export compactness, inverse-limit topology, Haar measure, quotient completion, choice, or an external profinite-ring theorem.
\end{proof}

\begin{theorem}[Fibonacci inverse-limit window-extension exhaustion]
\label{thm:fibonacci-inverse-limit-window-extension-exhaustion}
Let $Q=(G,F,W,R,H,C,P,N)$ be an accepted $\FibonacciInverseLimitUp$ carrier. Extending its finite prefix window adds only named larger-window rows to $W$ and recorded projection rows to $R$. Every read of an older prefix either factors through the older selected window already present in $W$, or through a newly recorded larger window followed by the displayed projection row in $R$ back to the older prefix. In both cases the provenance rows $G,F,W,H,C,P,N$ remain the same public coordinates of the packet, and no completed inverse-limit point, quotient stream, selected infinite prefix, topology, Haar measure, or external profinite-ring theorem is imported.
\end{theorem}
\begin{proof}
Inspect the carrier tuple $Q=(G,F,W,R,H,C,P,N)$. A window extension can add rows only to the finite window schedule $W$ and the projection ledger $R$; the admissibility rows, modulus rows, transports, continuations, provenance, and local certificate remain the displayed coordinates of the same packet.

For an older-prefix read, apply \autoref{thm:fibonacci-inverse-limit-prefix-projection-exactness}. If the read uses the old selected window, it is already exact over the old $W$ and $R$ rows. If it uses a larger recorded window, exactness forces the read through the recorded projection row in $R$ before it reaches the older prefix.

The ledger non-escape theorem \autoref{thm:fibonacci-inverse-limit-ledger-non-escape} excludes any hidden source for the older prefix. Thus the extension exhausts public reads by named larger-window rows and recorded projections, with $G,F,W,H,C,P,N$ preserved as the visible provenance surface.
\end{proof}

\closureat{FibonacciInverseLimitUp}{seedStr}

\begin{closurestatus}{\FibonacciInverseLimitUp}
  \constructivestory{A $\FibonacciInverseLimitUp$ packet is generated from finite $\GoldenMeanShiftUp$ admissibility rows, finite $\FibonacciCubeUp$ modulus rows, selected $\StreamNameUp$ windows, projection-compatibility rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope registers finite compatible prefix packets, prefix projection exactness, and ledger non-escape for Fibonacci-modulus projection surfaces.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not claim compactness, topology of the inverse limit, Haar measure, quotient completion, choice-selected infinite points, external imports, or external profinite-ring theorems.}
  \upgradepath{Obligation closure requires formal carrier encoding, prefix classifier transport, projection compatibility, finite-prefix exhaustion, and ledger non-escape under \texttt{BEDC.Derived.FibonacciInverseLimitUp}.}
\end{closurestatus}
