\chapter{A Concrete Naming Certificate for $\DyadicRoundingUp$}
\label{ch:concrete-instances-dyadicrounding-namecert}
\origin{human}

The $\DyadicRoundingUp$ interface names the finite dyadic-grid enclosure used on the constructive real path. Following Bishop and Bridges, \emph{Constructive Analysis}, it records an adjacent dyadic cell around a regular rational or $\RealUp$ read at a displayed unary precision, without invoking a quotient real, selected limit, trichotomy, or host rounding function. The adjacent endpoint rows consume the dyadic arithmetic surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the handoff row is read by the $\RealUp$ boundary of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[DyadicRounding carrier]
\label{def:dyadic-rounding-carrier}
A $\DyadicRoundingUp$ carrier is a finite $\BHist$ packet
$$
D=(x,n,a,b,I,E,L,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $x$ is the source read, either a $\RealUp$ seal route or a $\RegSeqRatUp$ regular rational readback already present on the constructive real path;
\item $n$ is the $\UnaryHistory$ precision request that fixes the dyadic grid scale;
\item $a$ and $b$ are adjacent $\DyadicRatCoreUp$ grid endpoints at precision $n$;
\item $I$ is the $\RationalIntervalUp$ containment row witnessing that the inspected rational approximation of $x$ lies inside the interval with endpoints $a$ and $b$;
\item $E$ is the $\FiniteErrorBudgetUp$ tolerance row that bounds the readback error at the same precision;
\item $L$ stores the componentwise $\hsame$ transports for the source read, unary precision, dyadic endpoint rows, interval containment row, and error-budget row;
\item $C$ stores the $\Cont$ routes for reading the source, inspecting the dyadic grid, transporting containment, and exposing the tolerance ledger;
\item $P$ is the $\Pkg$ provenance over $\RealUp$, $\RegSeqRatUp$, $\UnaryHistory$, $\DyadicRatCoreUp$, $\RationalIntervalUp$, $\FiniteErrorBudgetUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\DyadicRoundingUp}$ row.
\end{enumerate}
The carrier is a finite rounding certificate. It stores no completed real representative, no limiting point, no order trichotomy branch, and no host rounding operation.
\end{definition}

\begin{theorem}[DyadicRounding NameCert obligations]
\label{thm:dyadic-rounding-namecert-obligations}
The local $\NameCert_{\DyadicRoundingUp}$ surface for the carrier of \autoref{def:dyadic-rounding-carrier} consists of five finite obligations:
\begin{enumerate}
\item carrier admission: the accepted object is exactly the displayed packet $D$ with source read, unary precision, adjacent dyadic endpoints, interval containment, finite tolerance ledger, transport rows, continuation rows, package provenance, and local naming data;
\item classifier transport: classified source reads transport the same precision request, adjacent endpoint pair, containment row, error-budget row, and provenance rows componentwise through $L$ and $C$;
\item grid adjacency: $a$ and $b$ are the displayed adjacent $\DyadicRatCoreUp$ endpoints at precision $n$;
\item ledger exactness: every tolerance consumed by the containment read is the displayed $\FiniteErrorBudgetUp$ row $E$;
\item real handoff: every $\DyadicApproximationUp$, $\FiniteErrorBudgetUp$, or $\RealUp$ consumer first reads $x,n,a,b,I,E,L,C,P,N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dyadic-rounding-carrier}. The source row, precision request, endpoint pair, containment row, tolerance row, transport routes, continuation routes, package row, and local naming row are all visible coordinates of $D$.

Classifier transport is componentwise. A transported $\RealUp$ seal route or $\RegSeqRatUp$ readback carries the same unary precision, the same adjacent dyadic endpoint rows, and the same interval and budget ledgers through $L$ and $C$.

The grid and ledger clauses are finite projections. Since the carrier records only the endpoint rows $a,b$, the containment row $I$, and the tolerance row $E$, downstream consumers have no coordinate from which to obtain a quotient real, selected limit, trichotomy split, or host rounding function.
\end{proof}

\begin{theorem}[DyadicRounding grid sandwich]
\label{thm:dyadic-rounding-grid-sandwich}
For every accepted $\DyadicRoundingUp$ carrier $D=(x,n,a,b,I,E,L,C,P,N)$, the source read $x$ is exposed to dyadic-grid consumers only through the displayed sandwich by the adjacent $\DyadicRatCoreUp$ endpoints $a$ and $b$ at precision $n$, together with the $\RationalIntervalUp$ containment row $I$ and the $\FiniteErrorBudgetUp$ tolerance row $E$.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicRoundingUp.DyadicRoundingPacket\_grid\_sandwich}
\begin{proof}
Project the accepted carrier. The precision coordinate $n$ fixes the grid scale, and the endpoint coordinates $a$ and $b$ are the only dyadic grid rows available at that scale.

Read containment through $I$. This row places the inspected rational approximation of $x$ inside the displayed interval bounded by $a$ and $b$.

Finally read the tolerance through $E$. The finite error budget is the only permitted widening of the containment row, so the consumer receives the sandwich data $a,I,b,E$ rather than any ambient rounded value or host real comparison.
\end{proof}

\begin{theorem}[DyadicRounding ledger exactness]
\label{thm:dyadic-rounding-ledger-exactness}
Every tolerance, containment, and endpoint read exported by an accepted $\DyadicRoundingUp$ carrier is exhausted by the rows $n,a,b,I,E,L,C,P,N$ of \autoref{def:dyadic-rounding-carrier}. No downstream read may replace these rows by an external modulus, completed-real equality, selected limit, trichotomy decision, or host rounding operation.
\end{theorem}
\begin{proof}
Start with any exported dyadic rounding read. The NameCert obligation surface routes it through the precision request, adjacent endpoint rows, interval containment row, and finite error-budget row.

The transport and continuation rows $L$ and $C$ move only those displayed coordinates. They do not add analytic data beyond the source read and the finite ledgers already recorded in the packet.

Inspecting the carrier inventory completes the exactness claim. Since no coordinate stores an external modulus, completed-real equality, selected limit, trichotomy decision, or host rounding operation, no consumer can read one from the packet.
\end{proof}

\begin{theorem}[DyadicRounding RealUp handoff]
\label{thm:dyadic-rounding-realup-handoff}
Every $\RealUp$-facing handoff from an accepted $\DyadicRoundingUp$ carrier factors through the source row $x$, the unary precision $n$, the adjacent $\DyadicRatCoreUp$ endpoint pair $a,b$, the $\RationalIntervalUp$ containment row $I$, the $\FiniteErrorBudgetUp$ tolerance row $E$, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. The handoff exposes no quotient real, selected limit, trichotomy branch, or host rounding function.
\end{theorem}
\begin{proof}
First read the source coordinate $x$. If it is already a $\RealUp$ seal route, the handoff remains on that route; if it is a $\RegSeqRatUp$ readback, the regular rational row is inspected only at the displayed precision $n$.

Next apply the grid sandwich theorem. The handoff passes through $a,b,I,E$, so every real-facing approximation is the finite dyadic enclosure with its recorded budget.

Finally apply ledger exactness. The remaining coordinates are provenance and transport rows, not analytic choice data, so the $\RealUp$ consumer receives exactly the finite rounding packet and nothing outside it.
\end{proof}

\begin{theorem}[DyadicRounding transport stability]
\label{thm:dyadic-rounding-transport-stability}
Let $D=(x,n,a,b,I,E,L,C,P,N)$ be an accepted $\DyadicRoundingUp$ carrier. If each displayed coordinate is transported componentwise along the $\hsame$ rows stored in $L$ and then read along the $\Cont$ routes stored in $C$, the resulting packet is accepted by the same $\NameCert_{\DyadicRoundingUp}$ surface and preserves the source read $x$, unary precision $n$, adjacent endpoints $a,b$, containment row $I$, finite budget row $E$, transport ledger $L$, continuation ledger $C$, package provenance $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Start from the carrier inventory in \autoref{def:dyadic-rounding-carrier}. The only movable data are the displayed source read, unary precision, endpoint pair, containment row, finite budget row, and provenance rows.

Apply \autoref{thm:dyadic-rounding-grid-sandwich} after transport. The same transported precision row still selects the adjacent endpoint pair, and the same containment and budget rows provide the finite sandwich.

Apply \autoref{thm:dyadic-rounding-ledger-exactness} and \autoref{thm:dyadic-rounding-realup-handoff}. The transported packet exposes no extra rounding operation or real comparison, so the original NameCert obligations are preserved componentwise.
\end{proof}

\begin{theorem}[DyadicRounding finite-grid coverage]
\label{thm:dyadic-rounding-finite-grid-coverage}
Every accepted $\RealUp$ or $\RegSeqRatUp$ read at unary precision $n$ from a $\DyadicRoundingUp$ carrier is covered by the displayed adjacent $\DyadicRatCoreUp$ endpoints $a,b$ together with the $\RationalIntervalUp$ containment row $I$ and the $\FiniteErrorBudgetUp$ row $E$ of \autoref{def:dyadic-rounding-carrier}. No accepted read at that precision can require a dyadic endpoint, interval witness, or tolerance ledger outside the displayed packet.
\end{theorem}
\begin{proof}
First use \autoref{thm:dyadic-rounding-grid-sandwich}. It places the source read at precision $n$ between the adjacent dyadic endpoints $a$ and $b$ through the containment row $I$.

Next use \autoref{thm:dyadic-rounding-ledger-exactness}. The only widening of that interval read is the finite budget row $E$, and every tolerance consumed by the read is exhausted by the displayed ledger.

Finally apply \autoref{thm:dyadic-rounding-realup-handoff}. A $\RealUp$ read and a $\RegSeqRatUp$ read both pass through the same finite enclosure data before any downstream consumer sees them, so the displayed grid covers every accepted read at precision $n$.
\end{proof}

\begin{theorem}[DyadicRounding carrier scope]
\label{thm:dyadic-rounding-carrier-scope}
The carrier of \autoref{def:dyadic-rounding-carrier} has no coordinate for order trichotomy, host rounding, quotient reals, or selected limits. Its complete analytic surface is the finite grid sandwich of \autoref{thm:dyadic-rounding-grid-sandwich}, the ledger exactness boundary of \autoref{thm:dyadic-rounding-ledger-exactness}, and the $\RealUp$ handoff of \autoref{thm:dyadic-rounding-realup-handoff}.
\end{theorem}
\begin{proof}
Inspect the packet $D=(x,n,a,b,I,E,L,C,P,N)$ from \autoref{def:dyadic-rounding-carrier}. Each coordinate is a finite source, precision, dyadic endpoint, interval, budget, transport, continuation, package, or naming row.

The grid sandwich and ledger exactness theorems identify all analytic data available to consumers: adjacent endpoints, containment, and a finite error budget at the displayed precision.

The $\RealUp$ handoff theorem then accounts for the real-facing route. Since the carrier inventory contains no further coordinate, trichotomy, host rounding, quotient-real data, and selected limits are outside the scoped surface.
\end{proof}

\closureat{DyadicRoundingUp}{seedStr}[BEDC.Derived.DyadicRoundingUp.DyadicRoundingPacket\_grid\_sandwich]
\closureat{DyadicRoundingUp}{obligationStr}[BEDC.Derived.DyadicRoundingUp.DyadicRoundingPacket\_grid\_sandwich]
\closureat{DyadicRoundingUp}{scopedStr}[BEDC.Derived.DyadicRoundingUp.DyadicRoundingPacket\_grid\_sandwich]

\begin{closurestatus}{\DyadicRoundingUp}
  \constructivestory{A $\DyadicRoundingUp$ packet is generated from a displayed source read, unary precision request, adjacent dyadic endpoint rows, interval containment, finite error budget, componentwise transports, continuation routes, package provenance, and a local naming row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:dyadic-rounding-carrier}, \autoref{thm:dyadic-rounding-namecert-obligations}, \autoref{thm:dyadic-rounding-grid-sandwich}, \autoref{thm:dyadic-rounding-ledger-exactness}, and \autoref{thm:dyadic-rounding-realup-handoff} bind the source read, unary precision, dyadic endpoints, interval containment, finite error budget, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the displayed rounding packet.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.DyadicRoundingUp.DyadicRoundingPacket\_grid\_sandwich}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient reals, selected limits, trichotomy of host order, host rounding operations, or a public standard bridge.}
  \upgradepath{The next paper grade is a public export theorem for the finite dyadic rounding packet.}
\end{closurestatus}
