\chapter{A Concrete Naming Certificate for $\IsometricEmbeddingUp$}
\label{ch:concrete-instances-isometric-embedding-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, and the metric-space treatment in Kreyszig, \emph{Introductory Functional Analysis}, the $\IsometricEmbeddingUp$ interface records a distance-preserving injection only as a finite BEDC certificate. It is a completion-boundary object for $\RealUp$, $\CompletionReflectionUp$, and $\HausdorffCompletionUp$: downstream consumers see displayed metric and distance rows, not a host function equality or a quotient map.

\begin{definition}[IsometricEmbedding carrier]
\label{def:isometric-embedding-carrier}
An $\IsometricEmbeddingUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the source $\MetricSpaceUp$ carrier and classifier row;
\item $Y$ is the target $\MetricSpaceUp$ carrier and classifier row;
\item $F$ is the graph row displaying the embedding as a finite BEDC relation from source observations to target observations;
\item $D_X$ is the source $\mathsf{MetricDistanceWitness}$ row for displayed source endpoints;
\item $D_Y$ is the target $\mathsf{MetricDistanceWitness}$ row for the displayed target endpoints selected by $F$;
\item $R$ is the $\RealUp$ distance-reflection row comparing the real-distance read from $D_X$ with the real-distance read from $D_Y$;
\item $T$ stores the componentwise $\hsame$ transports for $X$, $Y$, $F$, $D_X$, $D_Y$, and $R$;
\item $Q$ stores the $\Cont$ routes for source reads, graph reads, target reads, and real-distance reflection reads;
\item $P$ is the $\Pkg$ provenance over $\MetricSpaceUp$, $\RealUp$, $\mathsf{MetricDistanceWitness}$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\IsometricEmbeddingUp}$ row.
\end{enumerate}
The carrier contains no quotient map, no host function object, no selected representative of a completion class, and no external completion theorem.
\end{definition}
\leandef{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier}

\begin{definition}[IsometricEmbedding classifier]
\label{def:isometric-embedding-classifier}
For accepted $\IsometricEmbeddingUp$ carriers $I$ and $I'$, the classifier $\mathsf{IsometricEmbeddingClassifier}(I,I')$ compares the packet rows componentwise. The source and target rows compare through their $\MetricSpaceUp$ classifiers, the graph rows compare through the displayed relation row, the two distance-witness rows compare through their $\RealUp$ distance observations, and the distance-reflection row compares only after the same source and target distance reads have been transported.

The classifier has no component for host-level function equality, quotient-map equality, selected representatives, or ambient completion principles. Its entire comparison surface is the displayed $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ data.
\end{definition}
\leandef{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingClassifier}

\begin{theorem}[IsometricEmbedding NameCert obligations]
\label{thm:isometric-embedding-namecert-obligations}
The local $\NameCert_{\IsometricEmbeddingUp}$ surface for the carrier of \autoref{def:isometric-embedding-carrier} consists of five finite rows:
\begin{enumerate}
\item carrier admission by the displayed packet $I$;
\item classifier transport by the componentwise comparison surface of \autoref{def:isometric-embedding-classifier};
\item distance preservation from the source $\mathsf{MetricDistanceWitness}$ row $D_X$ to the target $\mathsf{MetricDistanceWitness}$ row $D_Y$ through the $\RealUp$ reflection row $R$;
\item reflection into separated completion-facing consumers through the displayed $\MetricSpaceUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item non-escape from quotient maps, host functions, selected representatives, and external completion theorems.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is projection of the finite packet. The source metric row, target metric row, graph row, two distance-witness rows, real-distance reflection row, transport rows, continuation rows, package provenance, and local naming row are all visible coordinates.

Classifier transport is componentwise. The source and target classifiers move the endpoint rows, the graph row moves the displayed embedding relation, and the distance-witness rows move only along the transported endpoint data.

Distance preservation is then read from $R$. Since $R$ is paired with $D_X$ and $D_Y$ in the carrier, the target distance read cannot be separated from the source distance read that generated it.

The separated completion-facing row consumes the same displayed metric and real-distance data. The package and naming rows record that every downstream read remains inside this surface, so no quotient map, host function, selected representative, or external completion theorem is exported.
\end{proof}

\begin{theorem}[IsometricEmbedding distance reflection]
\label{thm:isometric-embedding-distance-reflection}
Let $I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)$ be an accepted $\IsometricEmbeddingUp$ carrier. Any source metric-distance read exposed by $D_X$ reflects through the graph row $F$ into the target metric-distance read exposed by $D_Y$, and the comparison of those distances is made only through the displayed $\RealUp$ row $R$ together with the stored $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_distance\_reflection}
\begin{proof}
Project the accepted carrier. The source distance read is stored in $D_X$, and the only target endpoint route attached to it is the displayed graph row $F$.

Read the target distance through $D_Y$. The transport row $T$ keeps the source endpoint, graph endpoint, and target endpoint data aligned, while $Q$ records the continuation route by which the target distance is consumed.

Finally read the real-distance comparison through $R$. The carrier has no separate host function or quotient-map coordinate, so the reflected target distance is the displayed $\RealUp$ comparison attached to $D_X$ and $D_Y$.
\end{proof}

\begin{theorem}[IsometricEmbedding completion boundary]
\label{thm:isometric-embedding-completion-boundary}
Every $\CompletionReflectionUp$ or $\HausdorffCompletionUp$ consumer of an accepted $\IsometricEmbeddingUp$ carrier may use the embedding only through the displayed source and target $\MetricSpaceUp$ rows, the source and target $\mathsf{MetricDistanceWitness}$ rows, the $\RealUp$ distance-reflection row, and the stored $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. No completion-facing consumer receives a quotient map, host function equality, selected representative, or external completion theorem from the packet.
\end{theorem}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_completion\_boundary}
\begin{proof}
Start with a completion-facing consumer. Its metric input must read either the source row $X$, the target row $Y$, or the graph row $F$, because those are the only carrier coordinates exposing the embedding.

The distance input is then forced through $D_X$, $D_Y$, and $R$. By \autoref{thm:isometric-embedding-distance-reflection}, this is exactly the displayed source-to-target real-distance reflection route.

Apply the non-escape row of \autoref{thm:isometric-embedding-namecert-obligations}. The packet inventory is exhausted by metric, real-distance, transport, continuation, package, and naming rows, so completion and separated-completion consumers cannot obtain non-displayed quotient, function, representative, or completion-theorem data.
\end{proof}

\begin{theorem}[IsometricEmbedding carrier admission]
\label{thm:isometric-embedding-carrier-admission}
Let
$$
I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)
$$
be an accepted $\IsometricEmbeddingUp$ packet. The carrier admitted by the local $\NameCert_{\IsometricEmbeddingUp}$ surface is exactly the displayed $\mathsf{BHist}$ packet with source and target $\MetricSpaceUp$ rows, graph row, source and target distance witnesses, $\RealUp$ distance-reflection row, componentwise $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local naming row. No admitted carrier field is a host function, quotient map, completion representative, or external completion theorem.
\end{theorem}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.TasteGate.IsometricEmbeddingTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier definition \autoref{def:isometric-embedding-carrier}. Its ten coordinates are the complete visible inventory of the accepted packet.

Read the carrier-admission row of \autoref{thm:isometric-embedding-namecert-obligations}. That row admits the packet by those coordinates and by no separate analytic object, because the package and local certificate only certify the displayed $\mathsf{BHist}$ surface.

The excluded objects have no coordinate in $I$. Therefore the admitted carrier is precisely the metric, graph, distance, reflection, transport, route, provenance, and naming packet.
\end{proof}

\begin{theorem}[IsometricEmbedding classifier transport]
\label{thm:isometric-embedding-classifier-transport}
For accepted packets $I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)$ and $I'=(X',Y',F',D'_X,D'_Y,R',T',Q',P',N')$, any classifier comparison between $I$ and $I'$ is componentwise: source and target rows are compared by their $\MetricSpaceUp$ classifiers, graph rows by the displayed relation row, distance witnesses by their endpoint and $\RealUp$ distance observations, and reflection rows only after the same transported source and target distance reads have been displayed.
\end{theorem}
\begin{proof}
Start from the classifier definition \autoref{def:isometric-embedding-classifier}. It gives no global equality test for the packet and no host function equality; each visible row is compared at its own BEDC surface.

Transport the source and target rows through the corresponding components of $T$ and $T'$. The graph rows then compare the displayed source observations with the displayed target observations, and the distance-witness rows compare only the endpoint data selected by those transported graph rows.

Finally read the reflection rows $R$ and $R'$. Since the classifier waits for the source and target distance observations before comparing the $\RealUp$ reflection data, classifier preservation is componentwise and remains inside the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.
\end{proof}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_classifier\_transport}

\begin{theorem}[IsometricEmbedding separated consumer route]
\label{thm:isometric-embedding-separated-consumer-route}
Every separated completion-facing consumer of an accepted $\IsometricEmbeddingUp$ packet $I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)$ factors through the displayed metric rows $X,Y$, the graph row $F$, the distance witnesses $D_X,D_Y$, the $\RealUp$ reflection row $R$, and the provenance rows $T,Q,P,N$. The consumer receives a distance-preserving route, not a quotient map, host function equality, selected representative, or ambient completion principle.
\end{theorem}
\begin{proof}
Project the consumer route from \autoref{thm:isometric-embedding-completion-boundary}. A completion-facing read can access the embedding only by reading the metric and graph rows of the accepted packet.

Apply \autoref{thm:isometric-embedding-distance-reflection}. The distance data then pass from $D_X$ through the graph row to $D_Y$, and the comparison is consumed only through the $\RealUp$ reflection row $R$.

The package rows $T,Q,P,N$ record transport, continuation, provenance, and local naming for this same finite packet. Since no excluded completion object occurs in the carrier, the separated consumer route is exactly the displayed metric-distance route.
\end{proof}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_separated\_consumer\_route}

\begin{theorem}[IsometricEmbedding distance preservation obligation]
\label{thm:isometric-embedding-distance-preservation-obligation}
Let
$$
I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)
$$
be an accepted $\IsometricEmbeddingUp$ packet. The distance-preservation obligation says that every displayed source-distance read in $D_X$ is transported along the graph row $F$ to the displayed target-distance read in $D_Y$, and the equality of the two distance observations is read only through the $\RealUp$ row $R$ and the provenance rows $T,Q,P,N$.
\end{theorem}
\begin{proof}
Project the carrier and classifier surfaces of \autoref{def:isometric-embedding-carrier} and \autoref{def:isometric-embedding-classifier}. They bind the source metric row $X$, target metric row $Y$, graph row $F$, distance witnesses $D_X,D_Y$, and real-distance row $R$ as one finite packet.

Apply the NameCert obligations of \autoref{thm:isometric-embedding-namecert-obligations}. The distance-preservation row is the clause that pairs the source distance witness with the target distance witness through $R$.

Finally use distance reflection. Since no host function or quotient map is exported, the preservation claim is exactly the displayed source-to-target real-distance comparison.
\end{proof}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_distance\_preservation\_obligation}

\begin{theorem}[IsometricEmbedding completion reflection handoff]
\label{thm:isometric-embedding-completion-reflection-handoff}
Every $\CompletionReflectionUp$ consumer of an accepted $\IsometricEmbeddingUp$ packet $I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)$ receives its embedding input through the displayed metric rows $X,Y$, graph row $F$, distance witnesses $D_X,D_Y$, real-distance reflection row $R$, and provenance rows $T,Q,P,N$. The handoff supplies a separated completion-facing route, not a quotient map, host function equality, selected representative, or ambient completion theorem.
\end{theorem}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_completion\_reflection\_handoff}
\begin{proof}
Begin with the completion boundary theorem \autoref{thm:isometric-embedding-completion-boundary}. It restricts every completion-facing consumer to the metric, graph, distance, reflection, transport, route, package, and naming rows of the accepted packet.

Use classifier transport to keep these rows componentwise under the displayed $\hsame$ and $\Cont$ routes. The NameCert obligations then identify the same rows as the local certificate surface.

The separated consumer route theorem supplies the final handoff: downstream consumers obtain a distance-preserving route through the displayed packet and receive no completion object outside it.
\end{proof}

\begin{theorem}[IsometricEmbedding Hausdorff separation boundary]
\label{thm:isometric-embedding-hausdorff-separation-boundary}
Every $\HausdorffCompletionUp$ consumer of an accepted $\IsometricEmbeddingUp$ packet can use separatedness only through the displayed rows
$$
X,Y,F,D_X,D_Y,R,T,Q,P,N.
$$
The packet may certify the finite distance-reflection route needed by a separated consumer, but it does not identify completion classes, choose representatives, export quotient maps, or assert an external Hausdorff-completion theorem.
\end{theorem}
\begin{proof}
Read the packet through the carrier definition. The only rows visible to a Hausdorff separatedness consumer are the source and target metric rows, the graph row, the two distance witnesses, the real-distance reflection row, and the transport and provenance rows.

Apply the distance-preservation obligation and the separated consumer route. Together they give the finite route from source distance data to target distance data and then to the separated completion-facing consumer.

The completion boundary theorem supplies the non-escape boundary. Because the carrier has no quotient map, selected representative, or ambient completion theorem, separatedness remains a consumer boundary over the displayed distance route.
\end{proof}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_hausdorff\_separation\_boundary}

\begin{theorem}[IsometricEmbedding real-distance route determinacy]
\label{thm:isometric-embedding-real-distance-route-determinacy}
For every accepted $\IsometricEmbeddingUp$ packet $I=(X,Y,F,D_X,D_Y,R,T,Q,P,N)$, each source-target distance comparison routes through exactly the displayed metric rows $X,Y$, graph row $F$, distance witnesses $D_X,D_Y$, real-distance row $R$, transport rows $T$, continuation route $Q$, package provenance $P$, and local $\NameCert_{\IsometricEmbeddingUp}$ row $N$. The route exports no host function equality, quotient completion class, or selected representative.
\end{theorem}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_real\_distance\_route\_determinacy}
\begin{proof}
Start with carrier admission. The admitted packet is precisely the displayed $\mathsf{BHist}$ surface with source and target metric rows, graph row, distance witnesses, real-distance reflection, transport, continuation, package provenance, and local naming.

Apply classifier transport and the distance preservation obligation. Classifier transport keeps packet comparison componentwise, while distance preservation identifies the only source-to-target distance comparison as the passage from $D_X$ through $F$ to $D_Y$ and then to the $\RealUp$ row $R$.

Use the separated consumer route together with the Hausdorff separation boundary. A separated or Hausdorff completion-facing consumer receives only the finite distance route $X,Y,F,D_X,D_Y,R,T,Q,P,N$ and no quotient map, host function equality, selected representative, completion class, or ambient completion theorem.

Therefore the real-distance route is determined by the displayed BEDC rows. Any downstream completion or Hausdorff consumer must cite those rows rather than an external isometry object.
\end{proof}

\begin{theorem}[IsometricEmbedding sibling completion lattice]
\label{thm:isometric-embedding-sibling-completion-lattice}
The $\IsometricEmbeddingUp$ packet is read in the concrete-instance lattice after the metric and real-distance witnesses of \autoref{ch:concrete-instances-metric-namecert} and \autoref{ch:concrete-instances-real-namecert}, and before completion-facing consumers in \autoref{ch:concrete-instances-completionreflection-namecert} and \autoref{ch:concrete-instances-hausdorffcompletion-namecert}. Its carrier consumes $\MetricSpaceUp$ endpoint rows and $\RealUp$ distance rows, then exposes only the displayed completion-facing route $X,Y,F,D_X,D_Y,R,T,Q,P,N$.
\end{theorem}
\begin{proof}
Start with the carrier and distance-preservation obligation. The source and target rows $X,Y$ are metric rows, while $D_X,D_Y$ and $R$ place their distance comparison in the $\RealUp$ surface.

Apply real-distance route determinacy. It fixes the only source-target comparison route as $X,Y,F,D_X,D_Y,R,T,Q,P,N$, so downstream readers do not receive a host isometry object or a quotient map.

The completion reflection handoff and Hausdorff separation boundary identify the consumers that read this packet. Therefore $\IsometricEmbeddingUp$ sits between the sibling metric and real chapters and the completion-facing chapters as a finite dependency lattice over displayed distance data.
\end{proof}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_sibling\_completion\_lattice}

\begin{theorem}[IsometricEmbedding distance-route reflection lock]
\label{thm:isometric-embedding-distance-route-reflection-lock}
Every separated or completion-facing consumer comparing source and target distances in an accepted $\IsometricEmbeddingUp$ packet must route through the displayed metric rows $X,Y$, graph row $F$, distance witnesses $D_X,D_Y$, $\RealUp$ reflection row $R$, transport row $T$, continuation row $Q$, package provenance $P$, and local $\NameCert$ row $N$. The route cannot be replaced by host function equality, a quotient map, a selected representative, or an ambient completion theorem.
\end{theorem}
\begin{proof}
Start with carrier admission and classifier transport. \autoref{thm:isometric-embedding-carrier-admission} exposes exactly $X,Y,F,D_X,D_Y,R,T,Q,P,N$, and \autoref{thm:isometric-embedding-classifier-transport} keeps comparisons componentwise on those rows.

Apply the distance-preservation obligation. \autoref{thm:isometric-embedding-distance-preservation-obligation} identifies the distance comparison as the displayed passage from the source witness $D_X$ through the graph row $F$ to the target witness $D_Y$ and then to the $\RealUp$ reflection row $R$.

Now use the separated and completion-facing boundaries. \autoref{thm:isometric-embedding-separated-consumer-route}, \autoref{thm:isometric-embedding-completion-boundary}, and \autoref{thm:isometric-embedding-hausdorff-separation-boundary} confine separated and completion-facing consumers to the same finite packet.

Finally invoke real-distance route determinacy. \autoref{thm:isometric-embedding-real-distance-route-determinacy} rules out host function equality, quotient completion classes, selected representatives, quotient maps, and ambient completion theorems as substitutes for the displayed BEDC route.
\end{proof}
\leanchecked{BEDC.Derived.IsometricEmbeddingUp.IsometricEmbeddingCarrier\_distance\_route\_reflection\_lock}

\closureat{IsometricEmbeddingUp}{seedStr}

\begin{closurestatus}{\IsometricEmbeddingUp}
  \constructivestory{An $\IsometricEmbeddingUp$ packet is generated from source and target $\MetricSpaceUp$ rows, a displayed graph row, source and target $\mathsf{MetricDistanceWitness}$ rows, a $\RealUp$ distance-reflection row, componentwise transport, continuation, package provenance, and local naming data.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite carrier, componentwise classifier, five-row naming-certificate surface, distance reflection, and completion-facing non-escape boundary for displayed isometric embeddings.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host-level isometry theorems, quotient maps, selected representatives, ambient completion existence, extension uniqueness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, distance preservation, separated completion-facing reflection, and non-escape for the same packet.}
\end{closurestatus}
