\chapter{A Concrete Naming Certificate for $\SobolevUp$}
\label{ch:concrete-instances-sobolev-namecert}
\origin{human}

The $\SobolevUp$ interface records the finite naming surface for a Sobolev-style weak-derivative packet. Classical references such as Evans, \emph{Partial Differential Equations}, and Adams--Fournier, \emph{Sobolev Spaces}, describe the surrounding analytic theory. BEDC records only the finite certificate surface needed by later PDE, variational, compact-embedding, and functional-analysis consumers: a displayed domain row, metric or complete-metric base row, normed or Hilbert codomain row, integrability magnitude row, weak-gradient test row, package provenance, and local naming evidence.

The packet consumes the $\RealUp$ domain surface of \autoref{ch:concrete-instances-real-namecert}, the metric or complete-metric base through \autoref{ch:concrete-instances-metric-namecert} or \autoref{ch:concrete-instances-completemetric-namecert}, and the weak-gradient magnitude route through the $\IntegralUp$ and $\DerivativeUp$ sibling certificates of \autoref{ch:concrete-instances-integral-namecert} and \autoref{ch:concrete-instances-derivative-namecert}. These dependencies are read as finite carrier rows and ledger routes, not as a host Sobolev space or completed function quotient.

The packet is not distribution theory, not Lebesgue completion, not quotient equality of functions, and not a completed function space. It is a finite $\mathsf{BHist}$ carrier whose accepted observations are compared by displayed rows and $\hsame$ routes.

\begin{definition}[Sobolev BHist carrier]
\label{def:sobolev-bhist-carrier}
A $\SobolevUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
S=(D,M,V,L,G,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $D$ is the $\RealUp$ domain row naming the scalar observation surface on which the weak tests are read;
\item $M$ is a $\MetricSpaceUp$ or $\CompleteMetricUp$ base row naming the ambient finite metric information used by the domain consumer;
\item $V$ is a $\NormUp$ or $\HilbertUp$ codomain row naming the magnitude target for function and weak-gradient observations;
\item $L$ is the $\IntegralUp$ magnitude row recording the finite integrability ledger for the displayed function and weak-gradient reads;
\item $G$ is the $\DerivativeUp$ weak-gradient test row, displayed as the finite list of test-observation routes and their recorded weak-derivative responses;
\item $H$ stores the componentwise $\hsame$ routes for the domain, base, codomain, integrability, weak-gradient, provenance, and local naming rows;
\item $C$ stores the displayed $\Cont$ routes by which a consumer reads the domain row, metric base row, codomain norm row, integrability ledger, and weak-gradient test ledger;
\item $P$ is the $\Pkg$ provenance over $\RealUp$, $\MetricSpaceUp$ or $\CompleteMetricUp$, $\NormUp$ or $\HilbertUp$, $\IntegralUp$, $\DerivativeUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\SobolevUp}$ evidence.
\end{enumerate}
The carrier has no coordinate for a host function space, a distributional dual, a quotient by almost-everywhere equality, a completed Lebesgue measure space, or a choice-selected representative.
\end{definition}

\begin{definition}[Sobolev classifier]
\label{def:sobolev-classifier}
Two accepted $\SobolevUp$ carriers are classified as the same weak-derivative certificate exactly when their visible domain, base, codomain, magnitude, weak-gradient, provenance, and naming rows compare componentwise through the stored $\hsame$ routes. The classifier compares the $\RealUp$ domain row, the $\MetricSpaceUp$ or $\CompleteMetricUp$ base row, the $\NormUp$ or $\HilbertUp$ codomain row, the $\IntegralUp$ magnitude row, the $\DerivativeUp$ weak-gradient test row, the $\Pkg$ row, and the local $\NameCert$ row.

The classifier does not compare host functions, ambient distributions, completed $L^p$ classes, quotient representatives, or equality in a background Sobolev space.
\end{definition}

\begin{theorem}[Sobolev NameCert obligation surface]
\label{thm:sobolev-namecert-obligation-surface}
The local $\NameCert_{\SobolevUp}$ obligation surface for the carrier of \autoref{def:sobolev-bhist-carrier} consists of five finite rows:
\begin{enumerate}
\item carrier habitation by the zero weak-gradient packet, with a displayed $\RealUp$ domain row, metric base row, codomain norm row, zero $\IntegralUp$ magnitude row, zero $\DerivativeUp$ weak-gradient test row, package provenance, and local naming evidence;
\item classifier reflexivity, symmetry, and transitivity by the componentwise classifier of \autoref{def:sobolev-classifier};
\item carrier transport under the classifier, preserving the same visible domain, metric base, codomain, integrability, weak-gradient, provenance, and naming rows up to $\hsame$;
\item ledger exactness for weak-derivative observations, requiring every accepted derivative read to factor through the displayed $G$ row and the magnitude ledger $L$;
\item completion-boundary non-escape, preventing any consumer from reading distribution theory, Lebesgue completion, quotient equality, or a host Sobolev space from the finite carrier.
\end{enumerate}
\end{theorem}
\begin{proof}
For habitation, use the displayed zero weak-gradient test row. The domain, metric base, codomain, zero magnitude, provenance, and local naming coordinates are all finite carrier rows, so no ambient function space is needed.

For classifier stability, compare accepted carriers by the rows named in \autoref{def:sobolev-classifier}. Reflexivity, symmetry, and transitivity are inherited componentwise from the displayed $\hsame$ routes and are repacked into the same finite carrier shape.

For transport and exactness, inspect any downstream read. It can project only $D$, $M$, $V$, $L$, $G$, $H$, $C$, $P$, or $N$, and the weak-derivative read is the displayed route through $G$ with its magnitude entry in $L$. Coordinate exhaustion gives the non-escape boundary.
\end{proof}
\leanchecked{BEDC.Derived.SobolevUp.SobolevCarrier\_namecert\_obligation\_surface}

\begin{theorem}[Sobolev weak-derivative ledger]
\label{thm:sobolev-weak-derivative-ledger}
Every accepted weak-derivative observation exported by a $\SobolevUp$ carrier factors through the finite route
$$
D \longmapsto M \longmapsto V \longmapsto L \longmapsto G.
$$
The route first fixes the displayed $\RealUp$ domain row and metric base, then reads the $\NormUp$ or $\HilbertUp$ codomain row, then records the $\IntegralUp$ magnitude ledger before exposing the $\DerivativeUp$ weak-gradient test row. It exports no distributional dual object, no completed $L^p$ class, no quotient representative, and no host equality of functions.
\end{theorem}
\begin{proof}
Start with a consumer request for a weak-derivative observation. Carrier projection forces the request to identify the domain row $D$ and the metric or complete-metric base row $M$ before any derivative data can be read.

The codomain and magnitude rows are then read through $V$ and $L$. These rows specify the finite normed target and the accepted integrability ledger for the observation, not an ambient measure completion.

Only after that route reaches $G$ does the weak-gradient test row become visible. Since $H$, $C$, $P$, and $N$ record transport, continuation, provenance, and local naming without adding analytic coordinates, the exported observation is exactly the finite ledger described above.
\end{proof}
\leanchecked{BEDC.Derived.SobolevUp.SobolevCarrier\_weak\_derivative\_ledger}

\begin{theorem}[Sobolev completion boundary]
\label{thm:sobolev-completion-boundary}
A $\RealUp$, $\IntegralUp$, $\DerivativeUp$, $\HilbertUp$, functional-analysis, PDE, variational, or compact-embedding consumer citing an accepted $\SobolevUp$ packet receives only the displayed carrier rows of \autoref{def:sobolev-bhist-carrier}, the classifier of \autoref{def:sobolev-classifier}, the five obligation rows of \autoref{thm:sobolev-namecert-obligation-surface}, and the weak-derivative ledger of \autoref{thm:sobolev-weak-derivative-ledger}. The citation cannot assert full distribution theory, Lebesgue completion, quotient equality of functions, density of smooth functions, compact embedding, trace theory, or a completed Sobolev space.
\end{theorem}
\begin{proof}
Factor the consumer citation through the local $\NameCert_{\SobolevUp}$ surface. The available data are the finite rows $D,M,V,L,G,H,C,P,N$ and the classifier routes between accepted packets.

Apply the weak-derivative ledger theorem to any derivative-facing read. It fixes the route through the displayed domain, base, codomain, magnitude, and weak-gradient rows before the observation is exported.

The excluded analytic objects are not coordinates of the packet and are not produced by the classifier or continuation rows. Therefore downstream consumers may use the finite weak-derivative certificate surface, but they cannot read any stronger completion, quotient, density, compactness, or trace result from this chapter.
\end{proof}
\leanchecked{BEDC.Derived.SobolevUp.SobolevCarrier\_completion\_boundary}

\begin{theorem}[Sobolev weak-derivative root-unblock package]
\label{thm:sobolev-weak-derivative-root-unblock-package}
Every accepted $\SobolevUp$ packet $S=(D,M,V,L,G,H,C,P,N)$ exports a finite root package combining carrier admission, classifier stability, weak-derivative ledger exactness, metric or complete-metric boundary data, $\IntegralUp$ and $\DerivativeUp$ handoff, and the terminal $\RealUp$ seal nonescape. Any downstream analysis consumer must read this package through the displayed weak-gradient magnitude route
$$
D \longmapsto M \longmapsto V \longmapsto L \longmapsto G
$$
before reaching completion-facing rows.

The package supplies no distributional dual object, Lebesgue completion, quotient equality of functions, density theorem, compact embedding theorem, trace theorem, or completed Sobolev space.
\end{theorem}
\begin{proof}
Project the carrier and classifier surfaces. The carrier rows $D,M,V,L,G,H,C,P,N$ are the complete visible inventory, and the classifier compares them componentwise through the stored $\hsame$ routes.

Apply the NameCert obligation surface. Carrier habitation, classifier stability, carrier transport, weak-derivative ledger exactness, and completion-boundary non-escape are already recorded as finite rows over the same packet.

Use the weak-derivative ledger theorem to identify the route used by every derivative-facing read. The read passes from the $\RealUp$ domain row through the metric or complete-metric base, the normed or Hilbert codomain row, the $\IntegralUp$ magnitude ledger, and only then the $\DerivativeUp$ weak-gradient test row.

Finally apply the completion boundary theorem. It confines downstream PDE, variational, functional-analysis, compact-embedding, and completion-facing consumers to the displayed carrier, classifier, obligation, and ledger rows. Coordinate exhaustion then gives the Real seal nonescape and rules out all stronger analytic objects listed in the statement.
\end{proof}

\begin{theorem}[Sobolev weak-derivative carrier transport]
\label{thm:sobolev-weak-derivative-carrier-transport}
Let $S=(D,M,V,L,G,H,C,P,N)$ and $S'=(D',M',V',L',G',H',C',P',N')$ be accepted $\SobolevUp$ packets whose domain, base, codomain, magnitude, weak-gradient, provenance, and local naming rows are connected by the componentwise $\hsame$ entries recorded in $H$ and $H'$. Any weak-derivative consumer transported from $S$ to $S'$ must carry the same $\BHist$ route
$$
D \longmapsto M \longmapsto V \longmapsto L \longmapsto G
$$
to
$$
D' \longmapsto M' \longmapsto V' \longmapsto L' \longmapsto G'
$$
through the displayed $\Cont$ replay rows. The transport preserves the carrier, classifier, weak-derivative ledger, completion-boundary rows, $\Pkg$ provenance, and local $\NameCert$ evidence, and it supplies no distributional dual, quotient function class, completed measure carrier, compact embedding object, or trace row.
\end{theorem}
\begin{proof}
Begin with the classifier of \autoref{def:sobolev-classifier}. It compares accepted packets only through the visible rows $D,M,V,L,G,P,N$ and the componentwise $\hsame$ transport stored in $H$.

Next replay the consumer route through $C$ and $C'$. Since every weak-derivative read is forced by \autoref{thm:sobolev-weak-derivative-ledger} to pass through the displayed domain, base, codomain, magnitude, and weak-gradient rows, transport replaces each row by its classified mate and keeps the same finite route.

Finally use the completion boundary theorem. The excluded analytic objects are absent from both carrier inventories, so transport across the classifier cannot create them.
\end{proof}

\begin{theorem}[Sobolev classifier locality]
\label{thm:sobolev-classifier-locality}
The $\SobolevUp$ classifier is local to the rows displayed by the carrier of \autoref{def:sobolev-bhist-carrier}. A downstream consumer may decide sameness of accepted weak-derivative packets only by reading the $\BHist$ rows $D,M,V,L,G$, the $\hsame$ transport row $H$, the $\Cont$ replay row $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert$ row $N$. It cannot appeal to host function equality, equality in a quotient of measurable functions, distributional equality outside the displayed weak-gradient tests, ambient Hilbert completion, compact embedding, trace data, or density of smooth approximants.
\end{theorem}
\begin{proof}
Read the classifier definition. Its comparison surface is componentwise and mentions only the displayed domain, base, codomain, magnitude, weak-gradient, provenance, and naming rows.

Apply carrier transport. Any consumer trying to move a classified packet must replay the same $\Cont$ route through the same finite weak-derivative ledger, so the classifier remains local to the carrier inventory.

The nonlocal analytic objects listed in the statement are not coordinates of $S$. Coordinate exhaustion therefore blocks them from acting as classifier inputs or classifier witnesses.
\end{proof}

\begin{theorem}[Sobolev root-unblock certificate]
\label{thm:sobolev-root-unblock-certificate}
Every accepted $\SobolevUp$ packet exports a root-unblock certificate consisting exactly of the carrier row, local classifier, weak-derivative ledger, carrier transport row, classifier-locality row, completion-boundary row, $\Pkg$ provenance, and local $\NameCert$ evidence. Any Hilbert, metric, integral, derivative, PDE, variational, or compactness-facing consumer must first pass through these finite $\BHist$, $\hsame$, and $\Cont$ rows before reading the weak-gradient data. The certificate supplies no completed Sobolev space, no distributional dual, no quotient function equality, no selected representative, no density theorem, no compact embedding theorem, and no trace theorem.
\end{theorem}
\begin{proof}
Project the accepted packet. The carrier exposes exactly $D,M,V,L,G,H,C,P,N$, and the NameCert obligation surface records habitation, classifier stability, transport, ledger exactness, and completion-boundary nonescape.

Use the weak-derivative ledger and carrier transport rows. They force every derivative-facing read to traverse the displayed domain, base, codomain, magnitude, and weak-gradient route, then preserve that route under componentwise $\hsame$ comparison.

Use classifier locality for downstream consumers. Hilbert, metric, integral, derivative, PDE, variational, and compactness-facing reads can cite only the local classifier and the replayed route, not a host analytic object outside the packet.

The completion boundary then removes the remaining escape routes. Since the excluded spaces, quotients, representatives, density results, compact embeddings, and traces are not carrier coordinates, the root-unblock certificate is exhausted by the displayed finite rows.
\end{proof}

\begin{theorem}[Sobolev integral and derivative handoff]
\label{thm:sobolev-integral-derivative-handoff}
Every $\IntegralUp$, $\DerivativeUp$, $\HilbertUp$, $\MetricSpaceUp$, $\CompleteMetricUp$, PDE, or variational consumer of an accepted $\SobolevUp$ packet must traverse the displayed route
$$
D \longmapsto M \longmapsto V \longmapsto L \longmapsto G \longmapsto H,C,P,N .
$$
Thus weak-derivative data are consumed only through the finite integral and derivative ledgers. The handoff supplies no distribution theory, Lebesgue completion, quotient equality of functions, compact embedding theorem, trace row, selected representative, or completed Sobolev space.
\end{theorem}
\begin{proof}
Project the carrier rows of \autoref{def:sobolev-bhist-carrier}. The only analytic-facing coordinates are the domain row $D$, the metric or complete-metric base row $M$, the codomain row $V$, the integral magnitude ledger $L$, and the weak-gradient test row $G$.

Apply the weak-derivative ledger theorem. It places every derivative-facing observation on the route from $D$ through $M,V,L$ and then to $G$, so the integral and derivative consumers read the same finite ledger rather than an ambient function space.

Use the root-unblock certificate to carry the route to Hilbert, metric, complete-metric, PDE, and variational consumers. The transport, replay, provenance, and local naming rows $H,C,P,N$ preserve the displayed route without adding analytic coordinates.

Finally apply the completion boundary. The excluded distribution, completion, quotient, compactness, trace, representative, and completed-space objects are absent from the carrier inventory, so the handoff is exhausted by the finite route displayed above.
\end{proof}

\begin{theorem}[Sobolev BHist carrier scope]
\label{thm:sobolev-bhist-carrier-scope}
Every accepted $\SobolevUp$ read is scoped by the finite $\BHist$ carrier rows
$$
D,M,V,L,G,H,C,P,N
$$
of \autoref{def:sobolev-bhist-carrier}. A consumer may reach $\RealUp$, $\MetricSpaceUp$ or $\CompleteMetricUp$, $\NormUp$ or $\HilbertUp$, $\IntegralUp$, and $\DerivativeUp$ only through those displayed rows, their componentwise $\hsame$ transports, their $\Cont$ replay route, the $\Pkg$ provenance row, and the local $\NameCert$ evidence.
\end{theorem}
\begin{proof}
Project the accepted carrier. The carrier definition lists exactly the domain row $D$, metric or complete-metric base $M$, codomain row $V$, magnitude ledger $L$, weak-gradient row $G$, and structural rows $H,C,P,N$.

Apply the classifier locality and carrier transport rows. They compare and move accepted packets only through the same displayed coordinates, with $\hsame$ and $\Cont$ preserving the route rather than adding a host analytic object.

Finally inspect a downstream analysis read. Since every readable sibling is named in $P$ and replayed through $C$, the $\RealUp$, metric, complete-metric, norm, Hilbert, integral, and derivative surfaces can appear only as the finite rows already present in the $\BHist$ packet.
\end{proof}

\begin{theorem}[Sobolev derivative norm ledger]
\label{thm:sobolev-derivative-norm-ledger}
Every derivative-facing $\SobolevUp$ consumer first reads the $\DerivativeUp$ weak-gradient row $G$ and the $\IntegralUp$ magnitude row $L$ through the displayed codomain row $V$. If $V$ is Hilbert-facing, the same route reads $\HilbertUp$ only through the finite $\NormUp$ magnitude interface carried by $V$ before the $\NameCert_{\SobolevUp}$ row is exposed. Thus derivative magnitude, norm control, $\hsame$ transport, $\Cont$ replay, and $\Pkg$ provenance are one finite ledger, not a quotient Sobolev norm or a completed Hilbert-space argument.
\end{theorem}
\begin{proof}
Begin with the integral and derivative handoff. It forces the consumer route through $D,M,V,L,G$ before the structural rows are read.

The codomain row $V$ is therefore fixed before $L$ and $G$ are interpreted. The $\IntegralUp$ magnitude ledger reads weak-gradient size through $L$, and the $\DerivativeUp$ row reads the corresponding weak-gradient tests through $G$.

If the codomain is Hilbert-facing, the Hilbert row remains the displayed codomain surface inside $V$. The route supplies norm data only by the finite norm interface already named there, and the later rows $H,C,P,N$ merely transport, replay, source, and name the same derivative-norm ledger.
\end{proof}

\begin{theorem}[Sobolev Hilbert completion descent]
\label{thm:sobolev-hilbert-completion-descent}
Any $\HilbertUp$, $\MetricSpaceUp$, $\CompleteMetricUp$, PDE, variational, or completion-facing consumer of a $\SobolevUp$ packet descends to the carrier rows of \autoref{thm:sobolev-bhist-carrier-scope} before it may cite weak-derivative data. The descent route passes through the displayed $\RealUp$ domain row, the metric or complete-metric base row, the codomain norm or Hilbert row, the $\IntegralUp$ magnitude ledger, the $\DerivativeUp$ weak-gradient row, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence. It supplies no completed Sobolev space, distributional dual, quotient function equality, density theorem, compact embedding, trace row, or selected representative.
\end{theorem}
\begin{proof}
Start with a Hilbert-facing or completion-facing consumer. The BHist carrier scope theorem forces the read to land on the displayed finite inventory $D,M,V,L,G,H,C,P,N$.

Use the derivative norm ledger. It identifies the analytic handoff as a route from the codomain row $V$ through the integral magnitude row $L$ and derivative row $G$, with Hilbert information restricted to the finite norm-facing surface in $V$.

The completion boundary then applies to the same route. The structural rows record transport, replay, provenance, and local naming only, so no completed Sobolev space, distributional dual, quotient function equality, density, compactness, trace, or selected representative can be read by descent.
\end{proof}

\closureat{SobolevUp}{seedStr}

\begin{closurestatus}{\SobolevUp}
  \constructivestory{A $\SobolevUp$ packet is generated from a displayed $\RealUp$ domain row, a metric or complete-metric base row, a normed or Hilbert codomain row, an $\IntegralUp$ magnitude ledger, a $\DerivativeUp$ weak-gradient test row, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite carrier, classifier, NameCert obligation surface, weak-derivative ledger, and completion boundary for a concrete weak-derivative certificate.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close distribution theory, Lebesgue completion, quotient equality of functions, density of smooth functions, compact embedding, trace theory, or completed Sobolev spaces.}
  \upgradepath{Obligation closure requires checked carrier habitation, classifier stability, carrier transport, weak-derivative ledger exactness, and completion-boundary non-escape for the same finite packet.}
\end{closurestatus}
