\chapter{A Concrete Naming Certificate for $\DyadicCoverUp$}
\label{ch:concrete-instances-dyadiccover-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, finite covers over
located real data are useful when the finite list, the dyadic mesh, and the
coverage witnesses are carried as explicit data. The $\DyadicCoverUp$
interface packages this information as a finite BEDC certificate for Real and
Completion consumers. It depends on $\DyadicRatCoreUp$, $\DyadicMeshUp$,
$\RationalIntervalUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$,
$\RealUp$, and $\FiniteWindowEnvelopeUp$, and it does not invoke open-cover
compactness, excluded middle, or a choice of subcover from an arbitrary family.

\begin{definition}[DyadicCover carrier]
\label{def:dyadic-cover-carrier}
A $\DyadicCoverUp$ carrier is a finite $\BHist$ packet
$$
D=(K,R,I,Q,W,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $K$ is the finite list of dyadic centers, each read through a
$\DyadicRatCoreUp$ row;
\item $R$ is the finite list of dyadic radii, each routed through a
$\RationalBallUp$ row with rational nonnegative radius data;
\item $I$ is the finite list of rational interval cells, each routed through a
$\RationalIntervalUp$ row and attached to the corresponding center-radius
entry;
\item $Q$ records the $\DyadicMeshUp$ mesh level and the finite refinement rows
between adjacent mesh levels;
\item $W$ is the displayed $\FiniteWindowEnvelopeUp$ window whose points are
covered by the interval cells;
\item $H$ records the $\hsame$ transports for centers, radii, interval cells,
mesh rows, window bounds, stream-name reads, regular-rational sequence reads,
and real rows;
\item $C$ records the $\Cont$ routes by which consumers read center membership,
radius bounds, interval containment, mesh refinement, coverage witnesses, and
total-bounded handoff rows;
\item $P$ records $\Pkg$ provenance for $\DyadicRatCoreUp$, $\DyadicMeshUp$,
$\RationalIntervalUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$,
$\RealUp$, $\FiniteWindowEnvelopeUp$, $\BHist$, $\hsame$, $\Cont$, and
$\NameCert$ dependency rows;
\item $N$ is the local $\NameCert_{\DyadicCoverUp}$ provenance row.
\end{enumerate}
The carrier accepts exactly those packets whose finite cell list covers the
displayed finite window and whose refinement rows keep every later mesh cell
inside a named earlier interval or rational ball.
\end{definition}
\leandef{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket}

\begin{theorem}[DyadicCover NameCert obligations]
\label{thm:dyadic-cover-namecert-obligations}
The local $\NameCert_{\DyadicCoverUp}$ seed surface consists of five finite
obligations:
\begin{enumerate}
\item carrier: the packet of \autoref{def:dyadic-cover-carrier};
\item classifier: componentwise comparison of centers, radii, interval cells,
mesh rows, finite-window witnesses, transport rows, continuation routes,
package provenance, and local certificate rows;
\item refinement stability: displayed $\hsame$ and $\Cont$ transport preserves
the dyadic center list, rational radii, interval cells, mesh refinement rows,
and coverage witnesses;
\item coverage exactness: every covered real read factors through a
$\StreamNameUp$ row, a $\RegSeqRatUp$ approximation row, a $\RealUp$ row, and a
finite interval or ball cell in the displayed window;
\item ledger policy: $\Pkg$ and $\NameCert$ expose only the listed dyadic,
rational, real, finite-window, transport, and continuation rows.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_namecert\_obligations}
\begin{proof}
Project the carrier. The finite center list, radius list, interval-cell list,
mesh rows, window witnesses, transport rows, continuation routes, package
provenance, and local certificate row are exactly the visible coordinates.

The classifier is componentwise over these rows. Transport stability follows
by moving each coordinate through the stored $\hsame$ rows and then reading it
through the corresponding $\Cont$ route.

Coverage exactness follows from the explicit witness attached to each point in
the displayed finite window: the witness names the stream read, regular
rational approximation, real row, and interval or ball cell used for that
point. The package and certificate rows contain no arbitrary open family or
subcover selector, so the ledger policy is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[DyadicCover finite refinement]
\label{thm:dyadic-cover-finite-refinement}
Let $D$ be an accepted $\DyadicCoverUp$ carrier and let $Q'$ be a displayed
later $\DyadicMeshUp$ refinement row of its mesh coordinate $Q$. The refined
packet is obtained by replacing each old cell with the finite list of named
dyadic subcells routed by $Q'$, transporting the corresponding rational
interval and rational ball rows through $\hsame$, and retaining the same
$\FiniteWindowEnvelopeUp$ coverage witnesses after refinement.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_finite\_refinement}
\begin{proof}
Read the mesh coordinate $Q$ and the displayed refinement row $Q'$. Each old
dyadic cell has a finite named list of subcells, so the refined center, radius,
and interval lists are built by finite list replacement.

Transport each subcell's rational interval and rational ball rows through the
stored $\hsame$ entries, then read the containment route through $\Cont$. The
finite-window coordinate $W$ is unchanged, while each old coverage witness now
points to the named refined subcell contained in the old cell.

Repack the refined rows with the same $\Pkg$ provenance and local
$\NameCert_{\DyadicCoverUp}$ row. No infinite cover or selected subcover is
introduced, because every operation is over the displayed finite mesh lists.
\end{proof}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_finite\_refinement\_transport}

\begin{theorem}[DyadicCover total-bounded handoff]
\label{thm:dyadic-cover-total-bounded-handoff}
Every total-bounded or compact-metric consumer of an accepted
$\DyadicCoverUp$ carrier factors through the displayed finite list of dyadic
centers, rational radii, rational interval cells, $\DyadicMeshUp$ refinement
rows, $\FiniteWindowEnvelopeUp$ coverage witnesses, and the $\Cont$ routes
that read $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ data into those cells.
The handoff is a finite packet handoff, not an appeal to open-cover compactness.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_total\_bounded\_handoff\_export}
\begin{proof}
Project the carrier and choose a consumer route. The only data addressed to
total-bounded consumers are the finite center list, radius list, interval-cell
list, mesh refinement rows, and coverage witnesses over the displayed window.

Follow the real-data read route. A covered point is read through its
$\StreamNameUp$ and $\RegSeqRatUp$ rows into a $\RealUp$ row, then into the
named rational interval or rational ball cell supplied by the coverage
witness.

Thus the consumer receives exactly a finite cover packet with explicit mesh
and radius data. Since the carrier contains no arbitrary indexed open family,
no compactness principle and no choice of subcover can be projected from it.
\end{proof}

\begin{theorem}[DyadicCover ledger nonescape]
\label{thm:dyadic-cover-ledger-nonescape}
Every $\RealUp$, $\FiniteWindowEnvelopeUp$, total-bounded, or completion
consumer of an accepted $\DyadicCoverUp$ carrier factors through the displayed
finite dyadic centers, dyadic radii, rational interval cells, mesh refinement
rows, coverage witnesses, $\hsame$ transports, $\Cont$ routes, $\Pkg$
provenance, and local $\NameCert$ row.

No consumer can obtain open-cover compactness, a choice function for arbitrary
covers, a completeness theorem, a quotient of names, or host-level real
extensionality from the $\DyadicCoverUp$ ledger alone.
\end{theorem}
\begin{proof}
Use the obligation surface of
\autoref{thm:dyadic-cover-namecert-obligations}. It lists the carrier,
classifier, refinement stability, coverage exactness, and ledger rows
available to every local certificate consumer.

For a $\RealUp$ or $\FiniteWindowEnvelopeUp$ consumer, read the stream,
regular-rational, real, and finite-window rows that are already displayed in
the carrier. For a total-bounded or completion consumer, read the finite center
and radius lists together with the mesh refinement and coverage routes.

All of these routes stay inside the finite $\BHist$ packet. The excluded
conclusions require coordinates not present in
\autoref{def:dyadic-cover-carrier}, so they cannot escape from the local
ledger.
\end{proof}

\begin{theorem}[DyadicCover window-cell incidence]
\label{thm:dyadic-cover-window-cell-incidence}
Let $D=(K,R,I,Q,W,H,C,P,N)$ be an accepted $\DyadicCoverUp$ carrier, where
$K$ is the finite dyadic center list, $R$ is the finite rational-radius list,
$I$ is the finite rational-interval cell list, $Q$ records the named real-data
rows, and $W$ is the displayed finite-window coordinate. Every point covered
inside $W$ by the accepted packet factors through one listed dyadic center, one
rational radius, one rational interval cell, one $\StreamNameUp$ row, one
$\RegSeqRatUp$ row, one $\RealUp$ row, and the displayed $\Cont$ route from
the corresponding stream and regular-rational name into that real and cell
incidence record.
\end{theorem}
\begin{proof}
Project the tuple $D=(K,R,I,Q,W,H,C,P,N)$. The coverage coordinate of the
carrier is indexed by the displayed finite window $W$, so a covered point
comes with a coverage witness rather than with an arbitrary open-family
membership assertion.

Read that witness through the carrier definition. It names a dyadic center
from $K$, a rational radius from $R$, and a rational interval cell from $I$,
and it also names the stream, regular-rational, and real rows in $Q$ used to
place the point in the cell.

Finally follow the stored $\Cont$ route. The route is part of the accepted
packet, so the incidence surface consumed downstream is exactly the finite
window-cell record listed in the carrier.
\end{proof}

\begin{theorem}[DyadicCover refinement witness exhaustion]
\label{thm:dyadic-cover-refinement-witness-exhaustion}
Every later mesh-refinement witness for an accepted $\DyadicCoverUp$ packet is
exhausted by finitely replacing old listed cells by named dyadic subcells whose
center, radius, interval, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are
already recorded in the packet ledger. Such a witness cannot introduce an
arbitrary open family, an external indexed cover, or a selector for subcovers.
\end{theorem}
\begin{proof}
Start with \autoref{thm:dyadic-cover-finite-refinement}. It decomposes a mesh
refinement into finite replacement of the old rational interval cells by named
subcells, preserving the displayed finite-window coordinate and the local read
routes.

Use \autoref{thm:dyadic-cover-ledger-nonescape} on the refined packet. The
ledger exposes only the finite center, radius, interval, mesh, coverage,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows recorded in the carrier.

Therefore the refinement witness is exhausted by those finite replacements.
The excluded open-family and subcover-selector data have no coordinate in the
accepted packet and cannot be projected from the ledger.
\end{proof}

\begin{theorem}[DyadicCover total-bounded radius ledger]
\label{thm:dyadic-cover-total-bounded-radius-ledger}
Every total-bounded consumer of an accepted $\DyadicCoverUp$ packet reads
exactly the finite center list, rational-radius list, rational-interval list,
mesh-refinement rows, and finite-window coverage witnesses displayed by the
carrier, with the radius data routed through the corresponding
$\RationalBallUp$ rows before the consumer receives a bounded-radius cover
packet.
\end{theorem}
\begin{proof}
Use \autoref{thm:dyadic-cover-total-bounded-handoff}. It identifies the
consumer-facing data as the finite center list, rational radii, interval
cells, mesh-refinement rows, coverage witnesses, and read routes into the real
and finite-window coordinates.

Then apply \autoref{thm:dyadic-cover-ledger-nonescape} to the same packet. The
radius coordinates available to the consumer are the displayed rational-radius
rows and their $\RationalBallUp$ routing; no external metric ball family or
choice of cover can be read from the ledger.

Thus the total-bounded handoff is a bounded-radius ledger over the listed
finite rows, not a compactness principle or a host-level open-cover argument.
\end{proof}

\begin{theorem}[DyadicCover finite-window obligation triad]
\label{thm:dyadic-cover-finite-window-obligation-triad}
For every accepted $\DyadicCoverUp$ packet
$$
D=(K,R,I,Q,W,H,C,P,N),
$$
the finite dyadic center-radius rows $(K,R)$, the mesh-refinement row $Q$, and
the $\FiniteWindowEnvelopeUp$ coverage row $W$ jointly form the finite-window
obligation surface. This surface includes the routed $\RationalIntervalUp$ and
$\RationalBallUp$ cell rows, the $\StreamNameUp$, $\RegSeqRatUp$, and
$\RealUp$ consumer reads, the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ rows, and no arbitrary open-cover family, subcover selector,
metric-completeness claim, or quotient equality of names.
\end{theorem}
\begin{proof}
Project the packet through \autoref{def:dyadic-cover-carrier}. The center list
$K$, radius list $R$, interval-cell list $I$, mesh row $Q$, and finite-window
row $W$ are the only coordinates from which coverage data can be read.

Apply \autoref{thm:dyadic-cover-namecert-obligations} to bind the local
certificate rows and \autoref{thm:dyadic-cover-window-cell-incidence} to bind
each finite-window point to one displayed center, radius, interval cell,
stream-name row, regular-rational row, real row, and continuation route.

Finally use \autoref{thm:dyadic-cover-ledger-nonescape}. It exhausts consumer
access by the displayed finite carrier rows, so the center-radius data, mesh
row, and finite-window coverage row form exactly the obligation triad named in
the statement.
\end{proof}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_finite\_window\_obligation\_triad}

\begin{theorem}[DyadicCover mesh-refinement carrier transport]
\label{thm:dyadic-cover-mesh-refinement-carrier-transport}
Let $D=(K,R,I,Q,W,H,C,P,N)$ be an accepted $\DyadicCoverUp$ carrier, and let
$Q'$ be a displayed later $\DyadicMeshUp$ refinement row of $Q$. Transporting
$D$ along $Q'$ through the stored $\hsame$ and $\Cont$ rows preserves the finite
center list, rational-radius list, interval-cell ledger, finite-window
coverage witnesses, package provenance, and local $\NameCert$ row as one
accepted carrier surface. The transported packet is a mesh refinement of the
same finite-window cover, not a cover chosen from an arbitrary host family.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:dyadic-cover-finite-refinement}. It replaces each old
cell by a finite named list of dyadic subcells routed by $Q'$, while retaining
the same finite-window coordinate $W$ and local read routes.

Next apply \autoref{thm:dyadic-cover-refinement-witness-exhaustion}. The
refinement witness is exhausted by the displayed center, radius, interval,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so transport has no route to an
external indexed cover.

The incidence and radius rows remain attached to the transported cells by
\autoref{thm:dyadic-cover-window-cell-incidence} and
\autoref{thm:dyadic-cover-total-bounded-radius-ledger}. Repacking these rows
gives the transported carrier surface and preserves the stated non-escape
boundary.
\end{proof}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_mesh\_refinement\_carrier\_transport}

\begin{theorem}[DyadicCover finite-window envelope factorization]
\label{thm:dyadic-cover-finite-window-envelope-factorization}
Every $\FiniteWindowEnvelopeUp$, $\RegSeqRatUp$, $\RealUp$, total-bounded, or
completion-facing read of an accepted $\DyadicCoverUp$ packet factors through
the finite-window route
$$
W \longmapsto Q \longmapsto I \longmapsto (K,R) \longmapsto H,C,P,N.
$$
The route first fixes the displayed envelope window, then reads the dyadic mesh
and refinement rows, then chooses one listed rational interval or rational ball
cell with its dyadic center and radius, and finally transports the read through
the recorded BEDC provenance. It does not assert open-cover compactness,
ambient completeness, quotient equality of real names, or a host-level
subcover choice.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_finite\_window\_envelope\_factorization}
\begin{proof}
Start from a finite-window or real-facing consumer read. By
\autoref{thm:dyadic-cover-window-cell-incidence}, any point inside $W$ is read
through one displayed stream-name row, regular-rational row, real row, and one
listed interval or ball cell.

Apply \autoref{thm:dyadic-cover-mesh-refinement-carrier-transport}. Mesh
transport keeps that cell inside the same carrier surface after finite
refinement, and \autoref{thm:dyadic-cover-refinement-witness-exhaustion}
exhausts the witness by the listed finite rows.

Finally attach the total-bounded side through
\autoref{thm:dyadic-cover-total-bounded-handoff} and
\autoref{thm:dyadic-cover-total-bounded-radius-ledger}. These rows factor
bounded-cover consumers through the same centers, radii, interval cells, mesh,
window, transport, package, and naming rows. The finite-window envelope route
therefore accounts for every listed consumer without any excluded host
principle.
\end{proof}

\begin{theorem}[DyadicCover finite-window mesh incidence package]
\label{thm:dyadic-cover-finite-window-mesh-incidence-package}
Let
$$
D=(K,R,I,Q,W,H,C,P,N)
$$
be an accepted $\DyadicCoverUp$ packet. Every accepted coverage request for a
point in the displayed finite window factors through exactly one listed
dyadic center in $K$, one rational radius in $R$, one rational interval cell in
$I$, one mesh row in $Q$, one $\StreamNameUp$ row, one $\RegSeqRatUp$ row, one
$\RealUp$ row, and the displayed $\Cont$ route that relates those rows inside
the local $\BHist$, $\Pkg$, and $\NameCert$ ledger.
\end{theorem}
\begin{proof}
First unpack the packet with
\autoref{thm:dyadic-cover-namecert-obligations}. This fixes the carrier
coordinates, the local classifier, and the named transport and read routes
available to a coverage consumer.

Next use \autoref{thm:dyadic-cover-window-cell-incidence}. The covered point
is read from the finite-window coordinate $W$, so its incidence witness is one
listed center, radius, interval cell, stream-name row, regular-rational row,
real row, and continuation route.

Finally apply \autoref{thm:dyadic-cover-ledger-nonescape}. Since the ledger
has no coordinate for an external cover or selector, the displayed incidence
witness is the whole consumer-facing package for the finite window and mesh
surface.
\end{proof}

\begin{theorem}[DyadicCover refined-window total-bounded package]
\label{thm:dyadic-cover-refined-window-total-bounded-package}
Every mesh-refined total-bounded consumer of an accepted $\DyadicCoverUp$
packet receives only the refined finite dyadic center list, rational radius
list, rational interval cell list, and the transported finite-window coverage
witnesses already carried by the packet. The consumer receives these rows
through the same $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance, and it
receives no open-cover compactness principle, arbitrary subcover choice, or
external metric-ball family.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicCoverUp.DyadicCoverPacket\_refined\_window\_total\_bounded\_package}
\begin{proof}
Start with \autoref{thm:dyadic-cover-finite-refinement}. It replaces cells by
a finite list of named dyadic subcells and transports the finite-window
witnesses along the displayed mesh refinement row.

Then use \autoref{thm:dyadic-cover-refinement-witness-exhaustion}. This
exhausts the refined witness by the packet's center, radius, cell, transport,
continuation, package, and naming rows, so no new cover family appears during
refinement.

Attach the total-bounded read by
\autoref{thm:dyadic-cover-total-bounded-handoff} and
\autoref{thm:dyadic-cover-total-bounded-radius-ledger}. The bounded-radius
consumer therefore sees the transported finite window package and the refined
finite lists, with the non-escape boundary supplied by
\autoref{thm:dyadic-cover-ledger-nonescape}.
\end{proof}

\begin{theorem}[DyadicCover Real envelope coverage exactness]
\label{thm:dyadic-cover-real-envelope-coverage-exactness}
Every $\RealUp$ or $\FiniteWindowEnvelopeUp$ coverage consumer of an accepted
$\DyadicCoverUp$ packet factors through the same finite envelope rows: the
displayed finite window, mesh-refined rational interval cells, dyadic centers,
rational radii, stream-name rows, regular-rational rows, real rows,
$\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local
$\NameCert$ certificate. Such a consumer cannot read open-cover compactness,
arbitrary subcover choice, quotient real equality, or host real extensionality
from the packet.
\end{theorem}
\begin{proof}
Begin with the finite-window incidence package from
\autoref{thm:dyadic-cover-finite-window-mesh-incidence-package}. It gives the
unique listed center, radius, interval cell, mesh row, stream row,
regular-rational row, real row, and continuation route for each accepted
coverage request.

Now transport along refinements using
\autoref{thm:dyadic-cover-refined-window-total-bounded-package}. The refined
packet keeps the same finite envelope surface and presents only transported
finite-window witnesses to downstream coverage consumers.

Finally combine \autoref{thm:dyadic-cover-total-bounded-handoff} with
\autoref{thm:dyadic-cover-ledger-nonescape}. These theorems bind the
Real-facing and finite-envelope reads to the displayed rows and exclude
compactness, arbitrary subcovers, quotient equality of reals, and host real
extensionality.
\end{proof}

\begin{theorem}[DyadicCover finite-subcover exhaustion]
\label{thm:dyadic-cover-finite-subcover-exhaustion}
Any downstream total-bounded or Real-envelope consumer of an accepted
$\DyadicCoverUp$ packet can only read the displayed finite center list,
dyadic radius rows, rational interval cells, mesh-refinement rows,
finite-window envelope, $\hsame$ transports, $\Cont$ routes, $\Pkg$
provenance, and local $\NameCert$ row. In particular, the consumer receives a
finite subcover already present in the packet and cannot replace it by an
ambient open-cover family, an arbitrary subcover choice, quotient equality of
real names, or host real extensionality.
\end{theorem}
\begin{proof}
First apply finite refinement. The displayed center, radius, interval, and
mesh rows are refined only by the finite dyadic subcells recorded in the
packet, so every downstream cover read starts from the same finite list.

Next use refinement witness exhaustion. It identifies each refined witness
with the packet's own center, radius, cell, transport, continuation, package,
and naming rows, leaving no independent cover-family coordinate.

Now attach the refined-window total-bounded package. The total-bounded
consumer therefore receives the transported finite window and the same
bounded-radius ledger rather than a separate compactness principle.

Finally use Real envelope coverage exactness. It repacks the finite-window
and total-bounded rows for $\RealUp$ and $\FiniteWindowEnvelopeUp$ consumers,
so the displayed finite subcover exhausts the exported coverage surface.
\end{proof}

\begin{theorem}[DyadicCover scoped package]
\label{thm:dyadic-cover-scoped-package}
The local obligation surface of $\DyadicCoverUp$ assembles into a scoped
package over $\DyadicRatCoreUp$, $\DyadicMeshUp$, $\RationalIntervalUp$,
$\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$,
$\FiniteWindowEnvelopeUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$. The scope is exactly the carrier, naming, finite-window triad,
mesh transport, finite-window envelope factorization, refined total-bounded
handoff, and Real envelope exactness supplied by
\autoref{thm:dyadic-cover-namecert-obligations},
\autoref{thm:dyadic-cover-finite-window-obligation-triad},
\autoref{thm:dyadic-cover-mesh-refinement-carrier-transport},
\autoref{thm:dyadic-cover-finite-window-envelope-factorization},
\autoref{thm:dyadic-cover-refined-window-total-bounded-package}, and
\autoref{thm:dyadic-cover-real-envelope-coverage-exactness}.
\end{theorem}
\begin{proof}
First project an accepted $\DyadicCoverUp$ packet to its displayed carrier
coordinates. The NameCert obligation theorem fixes the finite center,
radius, interval, mesh, finite-window, history, continuation, package, and
name rows that may be read from the packet.

Next apply the finite-window obligation triad and mesh-refinement carrier
transport theorems. They bind the finite window to the dyadic mesh and carry
the same rows across displayed refinements, so the scoped package has one
transport surface rather than separate host-side choices.

Now use finite-window envelope factorization and the refined-window
total-bounded package. These results route every finite-window,
total-bounded, and completion-facing read through the packet's own center,
radius, interval, mesh, envelope, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
rows.

Finally the Real envelope coverage exactness theorem repacks the same finite
packet for $\RealUp$ and $\FiniteWindowEnvelopeUp$ consumers. The assembled
package is therefore scoped to the listed BEDC objects, with no open-cover
compactness, arbitrary subcover choice, quotient equality of names, or host
real extensionality added.
\end{proof}

\begin{theorem}[DyadicCover public total-bounded export]
\label{thm:dyadic-cover-public-total-bounded-export}
Every public total-bounded or Real-envelope consumer of an accepted $\DyadicCoverUp$ packet receives exactly the finite center list, rational radius list, interval cells, mesh refinement rows, finite-window envelope coverage, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row assembled in \autoref{thm:dyadic-cover-scoped-package}. The export factors through \autoref{thm:dyadic-cover-finite-window-envelope-factorization}, \autoref{thm:dyadic-cover-refined-window-total-bounded-package}, and \autoref{thm:dyadic-cover-real-envelope-coverage-exactness}; it exports no open-cover compactness, arbitrary subcover choice, metric completeness, quotient equality of names, or host real extensionality.
\end{theorem}
\begin{proof}
Start with \autoref{thm:dyadic-cover-scoped-package}. It assembles the carrier, naming, mesh, finite-window envelope, refined total-bounded, and Real envelope rows into one scoped package.

Apply \autoref{thm:dyadic-cover-finite-window-envelope-factorization}. This identifies the coverage surface as the displayed finite envelope over the packet's own center list, radius list, interval cells, mesh rows, transports, routes, package provenance, and local name row.

Next use \autoref{thm:dyadic-cover-refined-window-total-bounded-package}. A total-bounded consumer therefore reads only the refined finite window and the same bounded-radius ledger, not an arbitrary subcover selection.

Finally apply \autoref{thm:dyadic-cover-real-envelope-coverage-exactness}. It repacks those same finite coverage rows for Real-envelope consumers, so the public export carries no open-cover compactness, metric completeness, quotient equality of names, or host real extensionality.
\end{proof}

\closureat{DyadicCoverUp}{seedStr}
\closureat{DyadicCoverUp}{obligationStr}
\closureat{DyadicCoverUp}{scopedStr}
\closureat{DyadicCoverUp}{publicStr}

\begin{closurestatus}{\DyadicCoverUp}
  \constructivestory{A $\DyadicCoverUp$ packet is generated from finite dyadic centers, dyadic radii, rational interval cells, mesh refinement rows, coverage witnesses for a displayed finite window, $\hsame$ transports, $\Cont$ read routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{The public surface is the finite carrier, naming, mesh transport, finite-window envelope, refined total-bounded, Real envelope package, and downstream total-bounded export of \autoref{thm:dyadic-cover-scoped-package} and \autoref{thm:dyadic-cover-public-total-bounded-export} over $\DyadicRatCoreUp$, $\DyadicMeshUp$, $\RationalIntervalUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\FiniteWindowEnvelopeUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close open-cover compactness, arbitrary subcover choice, metric completeness, compact-metric equivalence, quotient equality of real names, host real extensionality, or bridge checking.}
  \upgradepath{The next paper grade requires the standard bridge with bridge-surface fields and no-host-leak discipline.}
\end{closurestatus}
