\chapter{A Concrete Naming Certificate for $\CollisionKernelSpectrumUp$}
\label{ch:concrete-instances-collisionkernelspectrum-namecert}
\origin{human}

The $\CollisionKernelSpectrumUp$ packet is a BEDC-native finite certificate surface. It records a finite golden-mean fold moment ledger with a collision-kernel matrix and a spectral-shadow row, linking the finite-window surfaces of $\GoldenMeanShiftUp$, $\FibonacciCubeUp$, and $\FoldMomentKernelUp$ without importing external linear algebra or an ambient spectral theorem.

\begin{definition}[Collision kernel spectrum carrier]
\label{def:collision-kernel-spectrum-carrier}
A $\CollisionKernelSpectrumUp$ carrier is a finite $\BHist$ packet
$$
C=(G,F,V,I,K,S,H,T,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $G$ is the finite golden-mean window row, displaying binary words accepted by the $\GoldenMeanShiftUp$ no-adjacent-one ledger;
\item $F$ is the fold-source row, recording the corresponding $\FibonacciCubeUp$ finite path row and the fold map into visible fibers;
\item $V$ is the visible fiber-multiplicity row, listing the finite fibers and their displayed cardinal ledgers;
\item $I$ is the finite moment-index row used by $\FoldMomentKernelUp$ to read the selected fold moments;
\item $K$ is the collision-kernel matrix row whose entries count displayed pair collisions between fiber rows inside the finite window;
\item $S$ is the spectral-shadow row, a finite ledger of row sums, diagonal weights, and moment shadows read from $K$;
\item $H$ is the adjacency-moment handoff row from the golden-mean and Fibonacci-cube ledgers to the fold-moment rows;
\item $T$ stores the componentwise $\hsame$ and $\Cont$ routes for $G,F,V,I,K,S,H$;
\item $P$ is the $\Pkg$ provenance naming $\GoldenMeanShiftUp$, $\FibonacciCubeUp$, $\FoldMomentKernelUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ source rows;
\item $N$ is the local $\NameCert_{\CollisionKernelSpectrumUp}$ provenance row.
\end{enumerate}
The classifier compares two carriers only by the displayed finite rows $G,F,V,I,K,S,H,T,P,N$. No coordinate contains an infinite spectrum, an external matrix space, a Perron eigenvector, or an imported external object.
\end{definition}

\begin{theorem}[Collision kernel spectrum NameCert obligations]
\label{thm:collision-kernel-spectrum-namecert-obligations}
The local $\NameCert_{\CollisionKernelSpectrumUp}$ surface consists of five obligations:
\begin{enumerate}
\item carrier admission for the finite packet of \autoref{def:collision-kernel-spectrum-carrier};
\item classifier laws by componentwise $\hsame$ on golden-mean windows, fold-source rows, fiber multiplicities, moment indices, kernel entries, spectral shadows, handoff rows, transports, package provenance, and the local certificate row;
\item finite-window kernel exactness: every entry of $K$ is read from displayed collisions between rows of $V$ over the finite $G,F,I$ ledger;
\item spectral-shadow exactness: every row of $S$ is a finite row-sum, diagonal, or selected moment shadow of $K$;
\item non-escape: accepted carriers export no infinite spectrum, no host linear algebra, no choice of eigenbasis, and no external import.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is the displayed tuple $C=(G,F,V,I,K,S,H,T,P,N)$. Each coordinate is a finite $\BHist$ row or a finite route between such rows.

For the classifier laws, compare the coordinates componentwise after the stored $\hsame$ and $\Cont$ routes. The local certificate row has no access to any datum beyond $G,F,V,I,K,S,H,T,P,N$, so reflexive, symmetric, and transitive reads are inherited coordinate by coordinate.

Kernel exactness is finite ledger inspection. A matrix entry of $K$ is accepted only when the relevant pair of visible fiber rows in $V$ is displayed over the same golden-mean window, fold-source row, and moment-index row.

Spectral-shadow exactness then projects $S$. Its row sums, diagonal weights, and selected moment shadows are computed from the displayed entries of $K$ and the same handoff row $H$.

Non-escape follows from the carrier definition. Since no coordinate names an infinite spectrum, host matrix space, chosen eigenbasis, or external artifact, a downstream $\NameCert$ consumer can cite only the finite rows and their recorded routes.
\end{proof}

\begin{theorem}[Collision kernel spectrum finite-window spectral shadow]
\label{thm:collision-kernel-spectrum-finite-window-spectral-shadow}
For every accepted $\CollisionKernelSpectrumUp$ carrier, the spectral-shadow row $S$ is determined by the finite golden-mean window $G$, the fold-source row $F$, the visible fiber-multiplicity row $V$, the moment-index row $I$, and the collision-kernel matrix row $K$. Two accepted carriers with matching $G,F,V,I,K$ rows therefore have matching spectral-shadow rows after the displayed $\hsame$ and $\Cont$ routes.
\end{theorem}
\leanchecked{BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_finite\_window\_spectral\_shadow}
\begin{proof}
Project the carrier and read $S$ through the spectral-shadow exactness obligation. Each row of $S$ is a row-sum, diagonal weight, or selected moment shadow of the displayed kernel entries in $K$.

The kernel entries are themselves read from finite collisions between fiber rows in $V$ over the same golden-mean window $G$, fold-source row $F$, and moment-index row $I$. Thus matching $G,F,V,I,K$ rows transport the same finite calculations.

The stored routes in $T$ and the provenance in $P,N$ carry these componentwise readings between accepted packets. No external spectral theorem is needed because the shadow is only the finite ledger projected from $K$.
\end{proof}

\begin{theorem}[Collision kernel spectrum ledger non-escape]
\label{thm:collision-kernel-spectrum-ledger-non-escape}
Every exported route from an accepted $\CollisionKernelSpectrumUp$ packet factors through the finite golden-mean window row, fold-source row, fiber-multiplicity row, moment-index row, collision-kernel matrix row, spectral-shadow row, adjacency-moment handoff row, componentwise transport row, package provenance, and local $\NameCert$ row. The packet exports no infinite shift space, no ambient graph theory, no host spectral measure, no selected eigenvector, and no external theorem.
\end{theorem}
\leanchecked{BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_ledger\_non\_escape}
\begin{proof}
Take an exported consumer route and project the carrier of \autoref{def:collision-kernel-spectrum-carrier}. The only coordinates available are $G,F,V,I,K,S,H,T,P,N$.

The NameCert obligations account for carrier formation, classifier transport, finite-window kernel exactness, spectral-shadow exactness, and non-escape. Each of these obligations refers to a displayed finite row of the same packet.

Therefore every export factors through the listed finite coordinates. Since the carrier definition has no further coordinate, it cannot supply an infinite shift object, ambient graph theorem, host spectral measure, selected eigenvector, or imported external result.
\end{proof}

\begin{theorem}[Collision kernel spectrum adjacency-moment handoff]
\label{thm:collision-kernel-spectrum-adjacency-moment-handoff}
The handoff row $H$ sends each accepted golden-mean adjacency ledger in $G$ through the finite $\FibonacciCubeUp$ fold-source row $F$ to the moment-index rows used by $\FoldMomentKernelUp$. Consequently every collision-kernel entry in $K$ is indexed by a displayed finite adjacency path, a visible fiber row, and a finite moment index from the same carrier.
\end{theorem}
\begin{proof}
Project $H$ from the carrier. Its source is the golden-mean no-adjacent-one ledger $G$, and its intermediate row is the finite Fibonacci-cube fold source $F$.

The visible fiber row $V$ records which fold fibers are present over that source, while $I$ records the finite moments read by $\FoldMomentKernelUp$. The handoff row ties these three displays to the same finite window.

Thus an entry of $K$ cannot be indexed independently of the adjacency and moment ledgers. It is accepted only as a collision count between displayed fibers over $G,F,V,I$, transported by $T$ and recorded by $P,N$.
\end{proof}
\leanchecked{BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_adjacency\_moment\_handoff}

\begin{theorem}[Collision kernel spectrum window restriction]
\label{thm:collision-kernel-spectrum-window-restriction}
Let $C=(G,F,V,I,K,S,H,T,P,N)$ be an accepted $\CollisionKernelSpectrumUp$ carrier, and let $G'$ be a displayed golden-mean finite window obtained by restricting $G$ to a smaller no-adjacent-one row already visible through the $G,F,V,I$ ledger. The restricted packet formed by projecting $F,V,I,K,S$ to that smaller window is again accepted, and its kernel entries and spectral-shadow rows are exactly the corresponding displayed rows of the original packet.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:collision-kernel-spectrum-carrier}. The finite-window data are displayed in $G$, while $F,V,I$ record the fold-source, visible fibers, and moment indices read over that window.

Restricting to $G'$ deletes no external datum; it only selects already displayed rows from $G,F,V,I$. The collision entries in $K$ over the smaller window are therefore the same finite pair-collision rows, read after the same componentwise transport through $T$.

The spectral-shadow row $S$ is a ledger of row sums, diagonal weights, and moment shadows of $K$. Projecting $S$ along the restricted kernel rows preserves exactly those displayed finite calculations, with provenance still recorded by $P,N$.
\end{proof}
\leanchecked{BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_window\_restriction}

\begin{theorem}[Collision kernel spectrum fiber-row symmetry]
\label{thm:collision-kernel-spectrum-fiber-row-symmetry}
In an accepted $\CollisionKernelSpectrumUp$ carrier, the collision count attached to two displayed visible fiber rows is unchanged when the two fiber rows are exchanged, provided the same finite golden-mean window, fold-source row, and moment-index row are retained. The transported entry remains a row of the same collision-kernel matrix $K$ and feeds the same spectral-shadow index in $S$.
\end{theorem}
\begin{proof}
Read the relevant kernel entry from $K$. By the NameCert obligations, such an entry is accepted only as a finite collision count between two displayed fiber rows in $V$ over the same $G,F,I$ ledger.

Swapping the two visible fiber rows changes only the order in which the finite pair is inspected. The componentwise $\hsame$ and $\Cont$ routes in $T$ carry the exchanged pair back to the same finite carrier surface.

The moment index is not changed by this exchange. Hence the resulting count is the same displayed kernel row, and the spectral-shadow row $S$ reads it at the same finite moment index.
\end{proof}

\begin{theorem}[Collision kernel spectrum moment-index projection]
\label{thm:collision-kernel-spectrum-moment-index-projection}
Every exported spectral-shadow row of an accepted $\CollisionKernelSpectrumUp$ carrier factors through a finite moment-index row $I$. In particular, the export can mention only the displayed rows $G,F,V,I,K,S,H,T,P,N$ and cannot cite an infinite spectrum, a host matrix space, an eigenbasis, or ambient linear algebra.
\end{theorem}
\begin{proof}
Start from an exported spectral-shadow route and project the carrier. The only spectral-shadow coordinate is $S$, and each row of $S$ is displayed as a row sum, diagonal weight, or selected moment shadow of entries in $K$.

The entries of $K$ are indexed over the same finite ledger $G,F,V,I$. The moment information available to the export is therefore precisely the finite row $I$, transported through $T$ and recorded with the handoff and provenance rows $H,P,N$.

No carrier coordinate names an infinite spectrum, a host matrix space, an eigenbasis, or ambient linear algebra. Thus every exported spectral-shadow row factors through $I$ and the listed finite packet rows.
\end{proof}
\leanchecked{BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_moment\_index\_projection}

\begin{theorem}[Collision kernel spectrum kernel-entry source lock]
\label{thm:collision-kernel-spectrum-kernel-entry-source-lock}
Every collision-kernel entry displayed in the row $K$ of an accepted $\CollisionKernelSpectrumUp$ carrier is sourced only from the golden-mean window $G$, the $\FibonacciCubeUp$ fold-source row $F$, the visible fiber row $V$, the moment-index row $I$, and the componentwise $\hsame$ and $\Cont$ routes recorded in $T$. No entry of $K$ can be read from an infinite shift space, an ambient graph adjacency object, a host matrix entry, an outside theorem, or an external formalization object outside the displayed packet.
\end{theorem}
\begin{proof}
Project the carrier $C=(G,F,V,I,K,S,H,T,P,N)$ and focus on one displayed entry of $K$. By \autoref{thm:collision-kernel-spectrum-adjacency-moment-handoff}, the entry is indexed by a finite adjacency path, a visible fiber row, and a finite moment index from the same carrier.

The golden-mean window and the fold-source row supply the allowed source coordinates. The visible fiber row supplies the two finite rows being compared, and the moment-index row supplies the selected read position.

The only transport allowed between these coordinates is the componentwise $\hsame$ and $\Cont$ data stored in $T$. Since the carrier has no further coordinate for an infinite shift space, host matrix entry, ambient adjacency theorem, outside theorem object, or external formalization object, every accepted kernel entry is locked to the displayed finite source rows.
\end{proof}

\begin{theorem}[Collision kernel spectrum shadow classifier stability]
\label{thm:collision-kernel-spectrum-shadow-classifier-stability}
If two accepted $\CollisionKernelSpectrumUp$ carriers are classified equal by the displayed componentwise classifier on $G,F,V,I,K,H,T,P,N$, then their spectral-shadow rows $S$ match after the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ routes. The classifier therefore transports spectral-shadow rows without invoking a host spectral measure, selected eigenvector, or ambient spectral theorem.
\end{theorem}
\begin{proof}
Begin with the componentwise classifier. It identifies the visible finite rows $G,F,V,I,K,H,T,P,N$ through the stored $\hsame$ and $\Cont$ routes and records the same package provenance and local naming rows.

Apply \autoref{thm:collision-kernel-spectrum-finite-window-spectral-shadow}. The row $S$ is determined by the finite rows $G,F,V,I,K$, so matching those rows forces the same row sums, diagonal weights, and selected moment shadows.

The remaining coordinates $H,T,P,N$ carry the handoff, transport, package, and local certificate data needed to read this equality as a $\BHist$ route. Thus spectral-shadow stability is a finite classifier fact and has no dependency on host spectral structure.
\end{proof}

\begin{theorem}[Collision kernel spectrum downstream readback package]
\label{thm:collision-kernel-spectrum-downstream-readback-package}
Every downstream consumer of an accepted $\CollisionKernelSpectrumUp$ spectrum packet factors through the finite tuple
$$
(G,F,V,I,K,S,H,T,P,N).
$$
Such a consumer can read the displayed golden-mean window, fold-source row, fiber row, moment-index row, kernel row, spectral-shadow row, adjacency-moment handoff, componentwise transport, package provenance, and local naming row, but cannot read an infinite shift space, host spectral measure, selected eigenvector, host linear-algebra object, outside theorem object, or external formalization object.
\end{theorem}
\begin{proof}
First apply \autoref{thm:collision-kernel-spectrum-ledger-non-escape}. Every exported route from the packet already factors through the listed finite coordinates.

Next apply \autoref{thm:collision-kernel-spectrum-kernel-entry-source-lock}. Any consumer that reads $K$ can only recover entries sourced from $G,F,V,I$ and transported through $T$.

Finally apply \autoref{thm:collision-kernel-spectrum-adjacency-moment-handoff}. The adjacency, fold, and moment reads are tied to the same carrier, while $S,H,P,N$ record the finite shadow, handoff, package, and naming rows. Since none of these coordinates contains an infinite shift space, host spectral measure, selected eigenvector, host linear-algebra object, outside or imported theorem object, or external formalization object, the downstream readback package is exactly the displayed tuple.
\end{proof}

\closureat{CollisionKernelSpectrumUp}{seedStr}
\closureat{CollisionKernelSpectrumUp}{obligationStr}[BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_namecert\_obligations]
\closureat{CollisionKernelSpectrumUp}{scopedStr}

\begin{closurestatus}{\CollisionKernelSpectrumUp}
  \constructivestory{A $\CollisionKernelSpectrumUp$ packet is generated from finite golden-mean windows, Fibonacci-cube fold-source rows, visible fiber multiplicities, finite moment indices, collision-kernel matrix rows, spectral shadows, handoff rows, componentwise transports, package provenance, and local naming.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The scoped surface records the finite carrier, local NameCert obligations, finite-window spectral shadow, ledger non-escape, adjacency-moment handoff, smaller-window restriction, fiber-row symmetry, moment-index projection, source lock, classifier stability, and downstream readback rows for collision-kernel spectrum packets.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.CollisionKernelSpectrumUp.CollisionKernelSpectrumCarrier\_namecert\_obligations}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close infinite spectra, host linear algebra, Perron eigenvectors, spectral measures, external imports, or a standard bridge.}
  \upgradepath{Public closure requires a single exported $\CollisionKernelSpectrumUp$ public certificate over the scoped spectrum packet.}
\end{closurestatus}
