\chapter{A Concrete Naming Certificate for $\RealCompletenessUp$}
\label{ch:concrete-instances-realcompleteness-namecert}
\origin{human}

The $\RealCompletenessUp$ interface records the diagonal-limit target of \autoref{ch:visions-real-completeness} as a finite naming-certificate packet. It packages the displayed $\DyadicRatCoreUp$ observations, $\StreamNameUp$ windows, $\RegSeqRatUp$ regular sequence rows, and $\RealUp$ seal row through which a completion consumer sees the candidate limit. The packet is a seed carrier for the Real and Completion substrate; it contains no quotient real, selected host limit, choice principle, or host completeness theorem.

\begin{definition}[Real completeness finite carrier]
\label{def:real-completeness-carrier}
A $\RealCompletenessUp$ carrier is a finite $\BHist$ packet
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the displayed $\RegSeqRatUp$ family of rational regular sequences;
\item $\mu$ is the explicit Cauchy modulus row naming, for each requested rational tolerance, a finite stage after which the family is stable;
\item $\Delta$ is the diagonal selector row, choosing the finite stage and rational observation used at each precision request;
\item $D$ is the $\DyadicRatCoreUp$ observation ledger containing the dyadic endpoints, radii, comparison rows, and tolerance rows read by the diagonal selector;
\item $W$ is the finite $\StreamNameUp$ window family through which the selected rational names are inspected;
\item $Q$ is the $\RegSeqRatUp$ readback row tying the selected windows to the regular rational sequence data;
\item $S$ is the $\RealUp$ seal row that presents the same diagonal observations as the candidate limit name;
\item $H$ stores displayed $\hsame$ transports for the input family, modulus, selector, dyadic ledger, stream windows, readbacks, and seal row;
\item $C$ stores the $\Cont$ routes by which consumers read the modulus, selected diagonal observations, and sealed candidate;
\item $P$ is the $\Pkg$ provenance row over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RealCompletenessUp}$ registration row.
\end{enumerate}
The local classifier compares two carriers only through these displayed rows. It does not identify quotient representatives, does not choose an external real number, and does not appeal to ambient completeness.
\end{definition}

\begin{theorem}[Real completeness NameCert obligations]
\label{thm:real-completeness-namecert-obligations}
The local $\NameCert_{\RealCompletenessUp}$ surface consists of five finite obligations:
\begin{enumerate}
\item carrier formation for the finite packet of \autoref{def:real-completeness-carrier};
\item classifier stability for the transported family $X$, modulus $\mu$, diagonal selector $\Delta$, observation ledger $D$, windows $W$, readback row $Q$, and seal row $S$;
\item modulus exactness, requiring every convergence bound consumed by the diagonal selector to be the explicit row recorded by $\mu$;
\item diagonal readback exactness, requiring every selected rational observation to pass through the displayed $\StreamNameUp$ window, $\RegSeqRatUp$ readback, and $\DyadicRatCoreUp$ ledger;
\item package closure, requiring the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows to contain exactly the provenance used by downstream $\RealUp$ consumers.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_namecert\_obligations}
\begin{proof}
Carrier formation is the tuple assembly of \autoref{def:real-completeness-carrier}. Each dependency row named by the diagonal-limit target is a visible coordinate of $R$.

Classifier stability is componentwise. Transport the regular sequence family and modulus first, then transport the selected stream windows and dyadic observation ledger, and finally transport the $\RealUp$ seal row reached by those observations.

The modulus and diagonal readback clauses are projections of the same packet. The row $\mu$ supplies the finite stage bounds, while $\Delta$, $W$, $Q$, and $D$ record exactly which rational observations are read at each precision request.

Package closure follows by projecting $H$, $C$, $P$, and $N$. No consumer route reaches a quotient real, external limit selector, or host completeness theorem because no such coordinate occurs in the carrier.
\end{proof}

\begin{theorem}[Real completeness diagonal witness schedule]
\label{thm:real-completeness-diagonal-witness-schedule}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ carrier. For every precision request read by a $\RealUp$ or completion-facing consumer, the diagonal witness schedule is a finite $\BHist$ route inside $R$: the request is bounded by the displayed modulus row $\mu$, selected by $\Delta$, read through the $\DyadicRatCoreUp$ ledger $D$, the $\StreamNameUp$ windows $W$, and the $\RegSeqRatUp$ readback row $Q$, transported by the $\hsame$ rows in $H$, routed by $\Cont$ rows in $C$, and packaged by the $\Pkg$ and $\NameCert$ rows $P,N$ before it reaches the seal row $S$. The schedule contains no quotient real, external limit choice, or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_diagonal\_witness\_schedule}
\begin{proof}
Project the accepted carrier through \autoref{def:real-completeness-carrier}. The displayed tuple already contains the family row, modulus, diagonal selector, dyadic ledger, stream windows, regular readback, seal row, transports, continuations, package provenance, and local naming row.

Apply \autoref{thm:real-completeness-namecert-obligations}. The modulus exactness clause attaches each consumed bound to $\mu$, while the diagonal readback exactness clause forces every selected rational observation through $\Delta,D,W,Q$.

It remains to expose the public route. The package-closure clause projects $H,C,P,N$, so the witness schedule is the finite $\BHist$ route recorded in the carrier itself. Since no external limit selector or completeness theorem is a coordinate of $R$, none can contribute a witness to the schedule.
\end{proof}

\begin{theorem}[Real completeness tail budget stability]
\label{thm:real-completeness-tail-budget-stability}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
and
$$
R'=(X',\mu',\Delta',D',W',Q',S',H,C,P,N)
$$
be accepted $\RealCompletenessUp$ carriers whose family, modulus, diagonal selector, dyadic ledger, stream-window, readback, and seal rows are related by the displayed $\hsame$ transports in the shared row $H$, and whose consumer routes use the same $\Cont$, $\Pkg$, and $\NameCert$ rows $C,P,N$. Then every tail budget used by $\Delta$ in $R$ is transported to the corresponding tail budget used by $\Delta'$ in $R'$, and both budgets are read through the same finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route. Thus tail-budget stability is a property of the displayed packet rows and not of host real equality or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_tail\_budget\_stability}
\begin{proof}
Read both accepted carriers by their displayed coordinates. The only rows available for a tail-budget read are the regular family, modulus, selector, dyadic ledger, stream windows, readback row, seal row, transports, continuations, package provenance, and local naming row.

Use the classifier-stability clause of \autoref{thm:real-completeness-namecert-obligations}. It transports $X,\mu,\Delta,D,W,Q,S$ componentwise along the displayed $\hsame$ data in $H$, while the shared $C,P,N$ rows keep the consumer route fixed.

The modulus exactness and diagonal readback exactness clauses then identify the transported budget with the same finite readback path. Every consumed bound is still a $\mu$ or $\mu'$ row, and every selected observation still passes through the corresponding $D,W,Q$ or $D',W',Q'$ rows before the seal is read. No host equality or completeness coordinate is present to alter the transported budget.
\end{proof}

\begin{theorem}[Real completeness RegSeq-to-seal handoff]
\label{thm:real-completeness-regseq-seal-handoff}
For every accepted $\RealCompletenessUp$ carrier
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
the handoff from the $\RegSeqRatUp$ data to the $\RealUp$ seal is completely determined by the finite rows of $R$. The regular family $X$ supplies the rational names, the explicit modulus $\mu$ bounds the selected tail, $\Delta$ chooses the displayed diagonal observations, $D$ records the $\DyadicRatCoreUp$ ledger, $W$ exposes the $\StreamNameUp$ windows, $Q$ performs the $\RegSeqRatUp$ readback, and $H,C,P,N$ route the handoff to the seal row $S$ through $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
Begin with the carrier definition. It makes $X,\mu,\Delta,D,W,Q,S,H,C,P,N$ the whole naming surface for the diagonal-limit candidate.

Apply \autoref{thm:real-completeness-namecert-obligations}. Carrier formation supplies the finite rows, modulus exactness binds the selected tail to $\mu$, and diagonal readback exactness binds the selected observations to $D,W,Q$.

The final handoff is package closure. Project $H,C,P,N$ and read the seal row $S$ as the unique $\RealUp$ endpoint named by the carrier. The construction is therefore a handoff from $\RegSeqRatUp$ readbacks to the displayed seal, with no quotient-style real equality or host completeness argument.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_regseq\_seal\_handoff}

\begin{theorem}[Real completeness public witness extractor obligation]
\label{thm:real-completeness-witness-extractor-public-obligation}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ carrier. Any public witness extractor for the diagonal-limit surface of $R$ has the following obligation surface: it may inspect only the $\BHist$ rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$; it must read the rational witness through $\DyadicRatCoreUp$, $\StreamNameUp$, and $\RegSeqRatUp$ rows; it must route transports through $\hsame$, continuations through $\Cont$, provenance through $\Pkg$, and local registration through $\NameCert$; and it must return only the $\RealUp$ seal row $S$ as the completion-facing endpoint.
\end{theorem}
\begin{proof}
First expose the finite public boundary. The carrier definition contains no hidden extractor field, so any public extractor can only project rows from the displayed $\BHist$ packet.

Apply \autoref{thm:real-completeness-namecert-obligations}. The diagonal readback exactness clause forces rational witnesses through $D,W,Q$, and the modulus exactness clause forces every tail bound through $\mu$.

Finally use package closure to project $H,C,P,N$. These rows are exactly the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route by which the selected witness reaches $S$. Since $S$ is the only $\RealUp$ seal coordinate in the carrier, the extractor has no public endpoint other than that seal row.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_witness\_extractor\_public\_obligation}

\begin{theorem}[Real completeness finite obligation surface]
\label{thm:real-completeness-finite-obligation-surface}
For an accepted $\RealCompletenessUp$ carrier
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
all formalization-facing obligations for the local diagonal-limit certificate are exhausted by the finite packet rows: carrier formation for $R$; $\hsame$ classifier stability for $X,\mu,\Delta,D,W,Q,S$ through $H$; modulus exactness for $\mu$; diagonal readback exactness through $\Delta,D,W,Q$ over $\DyadicRatCoreUp$, $\StreamNameUp$, and $\RegSeqRatUp$; and package closure through the $\Cont$, $\Pkg$, and $\NameCert$ rows $C,P,N$ to the $\RealUp$ seal $S$. No obligation mentions quotient equality of reals, selected host limits, countable choice, or an ambient completeness theorem.
\end{theorem}
\begin{proof}
Project \autoref{thm:real-completeness-namecert-obligations}. Its five clauses are already finite: carrier formation, classifier stability, modulus exactness, diagonal readback exactness, and package closure.

Now identify the rows consumed by those clauses. Carrier formation gives $R$; classifier stability reads $H$; modulus exactness reads $\mu$; diagonal readback exactness reads $\Delta,D,W,Q$ over the displayed $\DyadicRatCoreUp$, $\StreamNameUp$, and $\RegSeqRatUp$ surfaces; and package closure reads $C,P,N$ before reaching the $\RealUp$ seal $S$.

The exclusion statement follows from the same projection. Quotient real equality, selected host limits, countable choice, and ambient completeness are absent from the packet, so they cannot appear among the obligations exposed by the local $\NameCert_{\RealCompletenessUp}$ surface.
\end{proof}

\begin{theorem}[Real completeness dependency lattice]
\label{thm:real-completeness-dependency-lattice}
For every accepted $\RealCompletenessUp$ carrier
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
the accepted completion route factors through the upstream packet lattice in the following order: $\DyadicRatCoreUp$ observation ledgers in $D$, $\StreamNameUp$ windows in $W$, $\RegSeqRatUp$ readbacks in $Q$, $\FiniteTailDiagonalSealUp$ selected-tail witnesses, and the final $\RealUp$ seal row $S$. The rows $H,C,P,N$ preserve the same route through $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The route refuses quotient real equality, selected host limits, countable choice, and ambient completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{def:real-completeness-carrier}. The displayed carrier already separates the dyadic ledger $D$, stream windows $W$, regular readback row $Q$, seal row $S$, and the transport, continuation, provenance, and naming rows $H,C,P,N$.

Apply \autoref{thm:real-completeness-namecert-obligations} and \autoref{thm:real-completeness-finite-obligation-surface}. Their diagonal readback clauses force selected observations through $\DyadicRatCoreUp$, $\StreamNameUp$, and $\RegSeqRatUp$ rows, while package closure routes the result through $H,C,P,N$ before the $\RealUp$ seal is consumed.

Now insert the finite-tail handoff supplied by \autoref{ch:concrete-instances-finitetaildiagonalseal-namecert}. Its selected-tail witness package sits exactly between the $\RegSeqRatUp$ readback and the $\RealUp$ seal, using the same precision, window, source, witness, transport, route, provenance, and local naming discipline.

The sibling chapters \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert} name the upstream rows consumed by this lattice. They provide the window, regular-rational, dyadic, and real-seal anchors without adding a quotient real or a host completeness principle.

Finally use \autoref{thm:real-completeness-nonescape-boundary}. Since quotient real equality, selected host limits, countable choice, and ambient completeness are absent from the carrier, they cannot appear in the dependency lattice.
\end{proof}

\begin{theorem}[Real completeness modulus domain coverage]
\label{thm:real-completeness-modulus-domain-coverage}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ carrier. Every modulus request consumed by the diagonal selector $\Delta$ is a displayed unary request for a rational tolerance in the modulus row $\mu$. The selected request is read through the finite route $D,W,Q,H,C,P,N$: the $\DyadicRatCoreUp$ ledger supplies the rational tolerance and observation rows, the $\StreamNameUp$ windows and $\RegSeqRatUp$ readback row expose the selected rational names, and the transport, continuation, package, and local naming rows record the public route. No modulus request is supplied by a quotient stream, selected host limit, countable choice, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Read the carrier coordinates in \autoref{def:real-completeness-carrier}. The rows $\mu$ and $\Delta$ are displayed separately: $\mu$ names the tolerance-indexed stage requests, while $\Delta$ consumes only finite selected stages and rational observations.

Apply \autoref{thm:real-completeness-namecert-obligations}. Its modulus exactness clause binds every convergence bound consumed by the selector to the explicit $\mu$ row, and its diagonal readback exactness clause routes the selected rational observation through $D,W,Q$.

The public route is completed by the rows $H,C,P,N$. By \autoref{thm:real-completeness-diagonal-limit-candidate}, those rows are precisely the path by which the finite diagonal observation reaches the $\RealUp$ candidate. By \autoref{thm:real-completeness-nonescape-boundary}, quotient streams, selected host limits, countable choice, and ambient completeness are not coordinates of this route.
\end{proof}

\begin{theorem}[Real completeness selector readback determinacy]
\label{thm:real-completeness-selector-readback-determinacy}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
and
$$
R'=(X',\mu',\Delta',D',W',Q',S',H,C,P,N)
$$
be accepted $\RealCompletenessUp$ carriers whose $X,\mu,\Delta,D,W,Q$ rows are related by the displayed transports named in the shared $H$ row and whose consumer reads use the same $C,P,N$ route. Then two selector reads using those transported rows reach the same finite $\RealUp$ seal ledger. In particular, selector readback determinacy is a statement about the displayed rows $X,\mu,\Delta,D,W,Q,H,C,P,N$ and not about a quotient stream, selected host limit, countable choice, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the two carrier displays. The carrier definition exposes exactly the rows that the selector can inspect: family, modulus, selector, dyadic ledger, stream windows, regular readback, transport rows, continuations, package provenance, and local naming.

Use \autoref{thm:real-completeness-namecert-obligations} for classifier stability. The shared $H$ row transports $X,\mu,\Delta,D,W,Q$, while the shared $C,P,N$ route keeps the consumer-facing readback path fixed.

Now apply \autoref{thm:real-completeness-diagonal-limit-candidate} and \autoref{thm:real-completeness-realup-seal-ledger}. A selector read reaches $\RealUp$ only as the finite seal ledger formed from $\Delta$ through $D,W,Q$ and then routed through $H,C,P,N$. Since both reads use the same transported rows and the same route, they reach the same ledger.

Finally \autoref{thm:real-completeness-nonescape-boundary} rules out any external separator. There is no quotient stream, selected host limit, countable-choice row, or host completeness coordinate that could split the two readbacks after the finite route has been fixed.
\end{proof}

\begin{theorem}[Real completeness consumer route totality]
\label{thm:real-completeness-consumer-route-totality}
For every accepted carrier
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
each completion-facing consumer read for $\RealUp$, $\CauchyLimitSealUp$, or $\CauchySequenceSpaceUp$ factors through exactly the displayed rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$. The factorization reads the regular family, explicit modulus, diagonal selector, dyadic ledger, stream windows, regular readback, $\RealUp$ seal, transports, continuations, package provenance, and local naming row, and it exposes no quotient stream, selected host limit, countable choice, or ambient completeness theorem.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_consumer\_route\_totality}
\begin{proof}
Begin with \autoref{def:real-completeness-carrier}. It lists the complete carrier surface, and no completion-facing row occurs outside $X,\mu,\Delta,D,W,Q,S,H,C,P,N$.

Apply \autoref{thm:real-completeness-namecert-obligations}. Carrier formation and package closure make the displayed rows the full public route, while modulus exactness and diagonal readback exactness force any selected observation to pass through $\mu,\Delta,D,W,Q$ before it can reach the seal row.

For $\RealUp$ reads, use \autoref{thm:real-completeness-diagonal-limit-candidate} and \autoref{thm:real-completeness-realup-seal-ledger}: the candidate is the seal row $S$ read through the finite diagonal route. For $\CauchyLimitSealUp$ and $\CauchySequenceSpaceUp$ reads, use \autoref{thm:real-completeness-scoped-finite-seal-pullback} and \autoref{thm:real-completeness-cauchysequence-space-shared-window-handoff}: the downstream consumer first reads the same finite seal route and then its displayed finite handoff rows.

The route is therefore total over the displayed carrier rows and nowhere else. By \autoref{thm:real-completeness-nonescape-boundary}, quotient streams, selected host limits, host equality, countable choice, and ambient completeness are absent from the public boundary.
\end{proof}

\begin{theorem}[Real completeness public seal export]
\label{thm:real-completeness-public-seal-export}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ carrier. The public export consumed by $\RealUp$, $\CauchyLimitSealUp$, and $\CauchySequenceSpaceUp$ is exactly the seal row $S$ reached through the displayed rows
$$
\mu,\Delta,D,W,Q,H,C,P,N.
$$
Any two consumer reads with the same displayed rows reach the same seal ledger. The export does not claim quotient stream equality, selected host limits, countable choice, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_public\_seal\_export}
\begin{proof}
Begin with consumer route totality. By \autoref{thm:real-completeness-consumer-route-totality}, every $\RealUp$, $\CauchyLimitSealUp$, or $\CauchySequenceSpaceUp$ read factors through the displayed carrier rows and no external completion object.

Identify the endpoint. Apply \autoref{thm:real-completeness-diagonal-limit-candidate} and \autoref{thm:real-completeness-regseq-seal-handoff}; the diagonal observations selected by $\Delta$ pass through $D,W,Q$ and reach the public seal row $S$ through $\mu,H,C,P,N$.

Now compare two consumer reads with the same displayed rows. The selector readback determinacy theorem \autoref{thm:real-completeness-selector-readback-determinacy} fixes the finite readback route, so both reads arrive at the same seal ledger.

Finally apply the non-escape boundary. By \autoref{thm:real-completeness-nonescape-boundary}, quotient streams, selected host limits, countable choice, and ambient completeness are not coordinates of the packet, and therefore cannot be exported by the public seal row.
\end{proof}

\begin{theorem}[Real completeness diagonal limit candidate]
\label{thm:real-completeness-diagonal-limit-candidate}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ carrier. The candidate limit exported to $\RealUp$ is the seal row $S$ obtained from the selected diagonal observations $\Delta$ through the finite $\StreamNameUp$ windows $W$, the $\RegSeqRatUp$ readback row $Q$, and the $\DyadicRatCoreUp$ ledger $D$. Every convergence read used by this candidate factors through the explicit modulus row $\mu$ and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Start from the NameCert obligations of \autoref{thm:real-completeness-namecert-obligations}. They bind the modulus row, diagonal selector, finite windows, regular-sequence readbacks, dyadic ledger, and seal row to the same carrier.

The diagonal selector $\Delta$ chooses only recorded stages and observations. The selected reads therefore pass through $W$, $Q$, and $D$ before the seal row $S$ is formed.

The convergence-facing part is controlled by $\mu$. Since all consumer routes are stored in $H$, $C$, $P$, and $N$, the exported candidate is exactly the finite diagonal-limit surface seen by $\RealUp$.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_diagonal\_limit\_candidate}

\begin{theorem}[Real completeness carrier transport]
\label{thm:real-completeness-carrier-transport}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ carrier. Any componentwise displayed $\hsame$ transport of the concrete packet rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$ that preserves the $\Cont$ routes in $C$, the $\Pkg$ provenance in $P$, and the local $\NameCert$ row $N$ yields another accepted $\RealCompletenessUp$ carrier with the same public diagonal-limit surface.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_carrier\_transport}
\begin{proof}
Use the carrier definition to read every coordinate of $R$. The transported packet has the same row shape: regular sequence family, modulus row, diagonal selector, dyadic ledger, stream windows, readback row, $\RealUp$ seal, transport rows, continuation routes, package provenance, and local naming row.

Apply \autoref{thm:real-completeness-namecert-obligations}. Its classifier-stability clause transports $X,\mu,\Delta,D,W,Q,S$ componentwise by $\hsame$, while its package-closure clause keeps $H,C,P,N$ attached to the same public routes.

The conclusion is therefore a repacking of the displayed rows. No ambient completeness theorem is invoked, because acceptance is checked by the finite carrier and the local $\NameCert$ obligations.
\end{proof}

\begin{theorem}[Real completeness modulus diagonal exactness]
\label{thm:real-completeness-modulus-diagonal-exactness}
For every accepted packet
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
each diagonal observation exported by $\RealCompletenessUp$ is selected by $\Delta$, bounded by the explicit modulus row $\mu$, read through the $\BHist$ ledgers $D,W,Q$, transported by $\hsame$ rows in $H$, routed through $\Cont$ rows in $C$, and packaged by $P$ and $N$. No exported diagonal read may use a modulus or rational observation absent from the concrete packet.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:real-completeness-diagonal-limit-candidate}. It identifies the exported $\RealUp$ candidate with the seal row $S$ obtained from $\Delta$ through $W$, $Q$, and $D$.

Apply \autoref{thm:real-completeness-namecert-obligations}. Its modulus exactness clause binds every convergence bound to $\mu$, and its diagonal readback exactness clause binds every selected rational observation to the displayed stream, readback, and dyadic rows.

The remaining rows $H,C,P,N$ record transport, continuation, package, and naming discipline. Hence exactness is a finite ledger property of $R$, not a claim about host completeness.
\end{proof}

\begin{theorem}[RealUp seal ledger discipline]
\label{thm:real-completeness-realup-seal-ledger}
For every accepted $\RealCompletenessUp$ carrier
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
the $\RealUp$ seal row $S$ is the only completion-facing export. Its reads must pass through the displayed $\BHist$ packet rows $X,\mu,\Delta,D,W,Q$, the $\hsame$ transport row $H$, the $\Cont$ route row $C$, the $\Pkg$ row $P$, and the $\NameCert$ row $N$.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{def:real-completeness-carrier}. The only row typed as the candidate limit name is $S$, and the preceding rows record the family, modulus, selector, dyadic observations, stream windows, and regular-sequence readbacks that form it.

Use \autoref{thm:real-completeness-namecert-obligations} to keep the seal attached to the same classifier-stable rows. The package-closure clause says the public routes are exactly the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally apply \autoref{thm:real-completeness-diagonal-limit-candidate}. It identifies the seal with the finite diagonal observations, so the $\RealUp$ boundary contains no selected external limit, quotient real, host equality, or host completeness proof.
\end{proof}

\begin{theorem}[Real completeness no-escape boundary]
\label{thm:real-completeness-nonescape-boundary}
The public boundary of $\RealCompletenessUp$ exports only the finite diagonal-limit candidate over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It exports no quotient real, no host equality on real numbers, no selected external limit, no countable-choice principle, and no host completeness theorem.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:real-completeness-carrier}. The only completion-facing rows are the modulus, diagonal selector, finite stream windows, regular-sequence readbacks, dyadic observation ledger, and $\RealUp$ seal row.

Apply \autoref{thm:real-completeness-diagonal-limit-candidate}. Every candidate-limit read is downstream of those displayed rows and their transport, continuation, package, and local naming data.

The excluded objects are absent from the tuple. Therefore the boundary cannot export a quotient real, host real equality, external selected limit, choice principle, or host completeness theorem.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_nonescape\_boundary}

\begin{theorem}[Real completeness scoped finite seal pullback]
\label{thm:real-completeness-scoped-finite-seal-pullback}
Every $\RealCompletenessUp$ diagonal-limit read factors through the explicit modulus row, diagonal selector, $\DyadicRatCoreUp$ ledger, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback row, $\RealUp$ seal, and downstream $\CauchyLimitSealUp$ finite seal route displayed by the accepted carrier. The pullback exports no quotient stream, selected host limit, ambient completeness theorem, or host equality on completed reals.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:real-completeness-namecert-obligations}. They bind carrier formation, classifier stability, modulus exactness, diagonal readback exactness, and package closure to the finite rows of the accepted packet.

Apply \autoref{thm:real-completeness-diagonal-limit-candidate} and \autoref{thm:real-completeness-modulus-diagonal-exactness}. The candidate read is selected by $\Delta$, bounded by $\mu$, and read through $D,W,Q$ before it reaches the $\RealUp$ seal row.

Next use \autoref{thm:real-completeness-realup-seal-ledger}. It identifies the $\RealUp$ seal as the only completion-facing export and keeps every consumer route inside the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

The downstream $\CauchyLimitSealUp$ finite seal route consumes exactly that seal-facing row: explicit modulus, selected diagonal observations, stream windows, regular rational readback, dyadic ledger, and the same package provenance. The route is therefore a pullback along the finite seal consumer rather than a choice of an external completed object.

Finally apply \autoref{thm:real-completeness-nonescape-boundary}. Since quotient streams, selected host limits, ambient completeness, and host equality are absent from the carrier, they cannot appear in the scoped pullback.
\end{proof}

\begin{theorem}[Real completeness candidate-uniqueness boundary]
\label{thm:real-completeness-candidate-uniqueness-boundary}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
and
$$
R'=(X',\mu',\Delta',D',W',Q',S',H,C,P,N)
$$
be accepted $\RealCompletenessUp$ packets whose $X,\mu,\Delta,D,W,Q$ rows are related by the displayed $\hsame$ transports named in the same $H$ row, and whose seal rows $S$ and $S'$ are produced through the same diagonal readback routes $C$, package provenance $P$, and local naming row $N$. Then every $\RealUp$ consumer classifies $S$ and $S'$ through the same displayed $\RealUp$ seal ledger. In particular, the packet cannot export two distinct completion-facing seal reads for the same transported diagonal family and the same readback routes.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_candidate\_uniqueness\_boundary}
\begin{proof}
Apply \autoref{thm:real-completeness-namecert-obligations}. Its classifier-stability clause transports the family, modulus, selector, dyadic ledger, windows, readback row, and seal row through the displayed rows of $H$.

Next use \autoref{thm:real-completeness-carrier-transport} and \autoref{thm:real-completeness-modulus-diagonal-exactness}. The transported packets have the same public diagonal-limit surface, and every convergence bound and selected rational observation is read from $\mu,\Delta,D,W,Q$ through the same routes.

Now apply \autoref{thm:real-completeness-realup-seal-ledger}. A $\RealUp$ consumer may inspect a seal only through the displayed packet rows and the shared $H,C,P,N$ ledger. Since both seal rows are produced through those same diagonal readback routes, the consumer reaches the same displayed $\RealUp$ seal ledger.

Finally invoke \autoref{thm:real-completeness-nonescape-boundary}. There is no quotient real, host equality, selected external limit, or host completeness row that could separate $S$ from $S'$ outside the displayed ledger. The only exported classification is therefore the common finite seal-ledger classification.
\end{proof}

\begin{theorem}[CauchyLimitSeal transport stability for real completeness]
\label{thm:real-completeness-cauchylimitseal-transport-stability}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
and
$$
R'=(X',\mu',\Delta',D',W',Q',S',H,C,P,N)
$$
be accepted $\RealCompletenessUp$ packets whose $X,\mu,\Delta,D,W,Q$ rows are related by the displayed $\hsame$ transports named in the shared $H$ row, and whose seal rows $S$ and $S'$ are produced through the same continuation routes $C$, package provenance $P$, and local $\NameCert_{\RealCompletenessUp}$ row $N$. Then every downstream $\CauchyLimitSealUp$ consumer of either seal factors through the same finite route: the explicit modulus, diagonal selector, $\DyadicRatCoreUp$ ledger, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback row, $\RealUp$ seal, displayed $\hsame$ rows, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row. Hence the transported diagonal-limit seal is stable not only for $\RealUp$ consumers but also for the finite $\CauchyLimitSealUp$ route that consumes the seal.
\end{theorem}
\begin{proof}
First use \autoref{thm:real-completeness-carrier-transport}. The componentwise $\hsame$ rows in $H$ transport the visible family, modulus, selector, dyadic ledger, stream windows, readback row, and seal row while preserving the shared $C,P,N$ routing data, so both packets present the same public diagonal-limit surface.

Next apply \autoref{thm:real-completeness-modulus-diagonal-exactness}. Every selected read used by either seal is bounded by the corresponding explicit modulus row and passes through $\Delta,D,W,Q$ or through their transported counterparts. Since those rows are tied by the same $H$ and consumed through the same $C,P,N$ data, the diagonal selector and rational readback route are the same finite route seen through transport.

Use \autoref{thm:real-completeness-realup-seal-ledger} to identify the $\RealUp$ seal as the unique completion-facing export for each packet. Then use \autoref{thm:real-completeness-scoped-finite-seal-pullback}: any $\CauchyLimitSealUp$ consumer of that export reads the explicit modulus, selected diagonal observations, dyadic ledger, stream windows, regular-sequence readback, seal row, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

It remains to rule out a second downstream route. By \autoref{thm:real-completeness-candidate-uniqueness-boundary}, the two seal rows have the same displayed $\RealUp$ seal-ledger classification for the transported diagonal family and shared readback routes. Finally \autoref{thm:real-completeness-nonescape-boundary} excludes quotient streams, host real equality, selected external limits, choice principles, and host completeness rows. Thus any $\CauchyLimitSealUp$ consumer of either seal factors through the same finite route.
\end{proof}

\begin{theorem}[Real completeness seal classifier stability]
\label{thm:real-completeness-seal-classifier-stability}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
and
$$
R'=(X',\mu',\Delta',D',W',Q',S',H,C,P,N)
$$
be accepted $\RealCompletenessUp$ packets. Suppose the family row, modulus row, diagonal selector, dyadic ledger, $\StreamNameUp$ windows, and $\RegSeqRatUp$ readback rows of $R$ and $R'$ are related by the displayed $\hsame$ transports named in the shared $H$ row, and suppose the seal rows $S$ and $S'$ are read through the same $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\RealCompletenessUp}$ route. Then the $\RealUp$ classifier class exported by $S$ is the same finite seal-ledger class exported by $S'$. Moreover, every downstream $\CauchyLimitSealUp$ read of either seal sees that same class through the displayed route consisting of $\mu,\Delta,D,W,Q,S$, the transported counterparts, $H,C,P,N$, and no ambient completion object.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-completeness-carrier-transport}. The displayed $\hsame$ rows give componentwise transport of the family, modulus, diagonal selector, dyadic ledger, stream windows, regular rational readback, and seal rows while keeping the shared continuation, package, and local naming data fixed.

Next use \autoref{thm:real-completeness-modulus-diagonal-exactness}. The finite observations that feed the two seal rows are exactly the bounded diagonal reads selected by $\Delta$ and $\Delta'$ and recovered through $D,W,Q$ and their transported counterparts.

Apply \autoref{thm:real-completeness-realup-seal-ledger}. The only $\RealUp$ classifier endpoint available to either packet is the seal ledger exposed by the accepted carrier, so the two seal rows export the same finite seal-ledger class under the shared $H,C,P,N$ route.

Now invoke \autoref{thm:real-completeness-cauchylimitseal-transport-stability}. A downstream $\CauchyLimitSealUp$ consumer reads no separate completion data; it consumes the explicit modulus, diagonal selector, dyadic ledger, stream windows, regular readback, seal row, displayed transports, continuations, package provenance, and local naming row already identified above.

Finally use \autoref{thm:real-completeness-nonescape-boundary}. Quotient streams, selected host limits, host equality, countable choice, and ambient completeness are not coordinates of the packet, so they cannot split the exported classifier class or create a second downstream seal view.
\end{proof}

\begin{theorem}[RealCompleteness shared-window handoff from CauchySequenceSpace]
\label{thm:real-completeness-cauchysequence-space-shared-window-handoff}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet whose regular-family row is presented by an accepted $\CauchySequenceSpaceUp$ packet
$$
T=(F,\sigma,W_c,\epsilon,Q_c,H_c,C_c,P_c,N_c).
$$
Then every $\RealUp$ or $\CauchyLimitSealUp$ consumer read of the seal row $S$ factors first through the displayed $\CauchySequenceSpaceUp$ rows
$$
F,\sigma,W_c,\epsilon,Q_c,H_c,C_c,P_c,N_c
$$
and then through the displayed $\RealCompletenessUp$ rows
$$
\mu,\Delta,D,W,Q,S,H,C,P,N.
$$
The handoff exports no quotient stream, selected host limit, host real equality, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with the shared finite Cauchy window. By \autoref{thm:cauchysequence-space-shared-window-completion-consumer}, any completion-facing comparison supplied by $T$ reaches its handoff only after reading the regular-family row, schedule, cofinal-window ledger, dyadic tolerance row, completion handoff, transports, continuations, provenance, and local naming row.

Next exhaust the regular-family presentation. Theorem~\ref{thm:cauchysequence-space-regular-family-exhaustion} makes every regular-family consumer of $T$ factor through the same rows, and \autoref{thm:cauchysequence-space-uniformcriterion-consumption} records that a uniform-criterion presentation contributes only the shared threshold and real-seal handoff already displayed by $T$.

Now pass to the diagonal seal. Apply \autoref{thm:real-completeness-cauchylimitseal-transport-stability} and \autoref{thm:real-completeness-seal-classifier-stability}. The seal row $S$ is read through the explicit modulus, diagonal selector, dyadic ledger, stream windows, regular readback, $\RealUp$ seal, transported routes, continuations, package provenance, and local $\NameCert_{\RealCompletenessUp}$ row.

Finally use \autoref{thm:real-completeness-nonescape-boundary}. Since neither the CauchySequenceSpace packet nor the RealCompleteness packet contains quotient streams, selected host limits, host real equality, or an ambient completeness row, a consumer cannot bypass the two-stage displayed route.
\end{proof}

\begin{theorem}[RealCompleteness diagonal seal totality]
\label{thm:real-completeness-diagonal-seal-totality}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet. Every $\RealUp$ or $\CauchyLimitSealUp$ consumer of the diagonal seal row $S$ factors through exactly the displayed regular family row $X$, explicit modulus row $\mu$, diagonal selector $\Delta$, $\DyadicRatCoreUp$ ledger $D$, finite $\StreamNameUp$ windows $W$, $\RegSeqRatUp$ readback row $Q$, $\RealUp$ seal row $S$, $\hsame$ transport row $H$, $\Cont$ route row $C$, $\Pkg$ provenance row $P$, and local $\NameCert_{\RealCompletenessUp}$ row $N$. The consumer surface contains no quotient stream, host equality on completed reals, selected external limit, choice principle, or ambient completeness row.
\end{theorem}
\begin{proof}
First identify the seal route. Apply \autoref{thm:real-completeness-diagonal-limit-candidate} and \autoref{thm:real-completeness-modulus-diagonal-exactness}. The candidate read is the seal row $S$, formed from the diagonal selector $\Delta$, bounded by $\mu$, and read through the dyadic ledger, stream windows, and regular-sequence readback rows $D,W,Q$.

Next lock the completion-facing endpoint. By \autoref{thm:real-completeness-realup-seal-ledger}, a $\RealUp$ consumer sees the candidate only through the seal ledger carried by $R$ and the displayed $H,C,P,N$ rows.

For downstream seal consumers, use \autoref{thm:real-completeness-scoped-finite-seal-pullback} and \autoref{thm:real-completeness-cauchylimitseal-transport-stability}. They make the $\CauchyLimitSealUp$ route consume the same explicit modulus, selected diagonal observations, dyadic ledger, stream windows, readback row, seal row, transports, continuations, package provenance, and local naming row.

Finally apply \autoref{thm:real-completeness-nonescape-boundary}. The excluded objects are absent from the accepted packet, so no consumer can replace the displayed diagonal-seal route with a quotient stream, host equality, selected external limit, choice principle, or ambient completeness row.
\end{proof}

\begin{theorem}[RealCompleteness transport-tail-selector fusion]
\label{thm:real-completeness-transport-tail-selector-fusion}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet. Let
$$
T=(q,s,r,d,e,w,H_T,C_T,P_T,N_T)
$$
be an accepted $\RegularCauchyTailSelectorUp$ packet whose selected-tail rows provide the same precision, $\StreamNameUp$ window, $\RegSeqRatUp$ regularity, $\DyadicRatCoreUp$ readback, and $\RealUp$ seal rows used by $\mu,\Delta,D,W,Q,S$. Let
$$
U=(R_U,W_U,D_U,S_U,H_U,C_U,P_U,N_U)
$$
be an accepted $\RegularCauchyLimitTransportUp$ packet transporting those rows to the same $R$ surface, and let
$$
F=(q_F,s_F,r_F,w_F,e_F,h_F,c_F,p_F,n_F)
$$
be an accepted $\FiniteTailDiagonalSealUp$ packet consuming the selected finite tail supplied by $T$ and transported by $U$. Then every completion-facing $\RealUp$ or $\CauchyLimitSealUp$ read of $R$ factors through exactly the finite route
$$
\mu,\Delta,D,W,Q,S,H,C,P,N
$$
together with the selected-tail witness row $w$, the transport packet rows $R_U,W_U,D_U,S_U,H_U,C_U,P_U,N_U$, and the finite-tail seal rows $q_F,s_F,r_F,w_F,e_F,h_F,c_F,p_F,n_F$. The fused route exports no quotient stream, host real equality, selected external limit, countable-choice selector, or ambient completeness theorem.
\end{theorem}
\begin{proof}
First expose the RealCompleteness side. Apply \autoref{thm:real-completeness-diagonal-witness-schedule} and \autoref{thm:real-completeness-tail-budget-stability}. They force each completion-facing precision request to read the displayed modulus, diagonal selector, dyadic ledger, stream windows, regular readback, seal row, transports, continuations, package provenance, and local naming row of $R$.

Next attach the selected tail. By \autoref{thm:regular-cauchy-tail-selector-diagonal-admissibility}, the tail-selector packet supplies an admissible row $w$ for the same precision, window, regularity, dyadic, and seal reads. The row is finite before any $\RealUp$ or completion-facing consumer reaches the seal.

Now transport the selected row into the RealCompleteness surface. Apply \autoref{thm:regular-cauchy-limit-transport-real-completeness-consumer-factorization}; since the transport packet presents the same selected-window, dyadic-ledger, and seal rows, every diagonal-seal consumer of $R$ factors through the displayed transport rows before reading $S$.

Finally seal the finite tail. The handoff theorem \autoref{thm:finite-tail-diagonal-seal-real-handoff} routes the selected finite tail through $q_F,s_F,r_F,w_F,e_F,h_F,c_F,p_F,n_F$ before the real-facing row is consumed. Combine this handoff with \autoref{thm:real-completeness-diagonal-seal-totality} and \autoref{thm:real-completeness-nonescape-boundary}; because none of the packets has a coordinate for quotient streams, host real equality, selected external limits, countable-choice selection, or ambient completeness, the fused consumer route cannot escape the displayed finite rows.
\end{proof}

\begin{theorem}[RealCompleteness scoped consumer seal exhaustion]
\label{thm:real-completeness-scoped-closure}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet. The diagonal-limit surface of $R$ is scoped exactly by the displayed $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyLimitSealUp$, and $\CauchySequenceSpaceUp$ consumer rows, together with the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the packet. It contains no quotient stream, selected host limit, host real equality, countable-choice row, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the local naming surface. Apply \autoref{thm:real-completeness-namecert-obligations}. Its carrier, classifier, diagonal readback, and package-closure clauses expose only the rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$.

Next bind the diagonal construction to finite observations. Apply \autoref{thm:real-completeness-modulus-diagonal-exactness}; the selected diagonal reads are exactly the reads justified by the explicit modulus, dyadic ledger, finite stream windows, and regular-sequence readback rows. Apply \autoref{thm:real-completeness-realup-seal-ledger} to route the resulting seal through the displayed $\RealUp$ row and the same transport, continuation, provenance, and naming rows.

For seal consumers, apply \autoref{thm:real-completeness-cauchylimitseal-transport-stability}. It keeps the $\CauchyLimitSealUp$ route attached to the same diagonal seal and the same $H,C,P,N$ ledger. For completion-facing consumers whose regular family is supplied through $\CauchySequenceSpaceUp$, apply \autoref{thm:real-completeness-cauchysequence-space-shared-window-handoff}; the handoff contributes only its displayed finite window rows before returning to the same $\RealCompletenessUp$ packet.

Finally apply \autoref{thm:real-completeness-diagonal-seal-totality}. The diagonal-seal route is exhausted by the displayed rows, so no consumer can replace it by a quotient stream, selected host limit, host real equality, countable-choice row, or ambient completeness theorem.
\end{proof}

\begin{theorem}[RealCompleteness scoped consumer seal exhaustion]
\label{thm:real-completeness-scoped-consumer-seal-exhaustion}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet. Every $\RealUp$, $\CauchyLimitSealUp$, or completion-facing consumer of $R$ factors through exactly the displayed finite seal surface
$$
X,\mu,\Delta,D,W,Q,S,H,C,P,N.
$$
When the regular-family row is supplied through a $\CauchySequenceSpaceUp$ handoff, the consumer route also factors through the displayed handoff rows of that packet before returning to the same $\RealCompletenessUp$ rows. No such consumer exports a quotient stream, host equality on completed reals, selected external limit, choice principle, or ambient completeness row.
\end{theorem}
\begin{proof}
Start with the finite carrier surface. The local obligations in \autoref{thm:real-completeness-namecert-obligations} identify the accepted packet as the displayed rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$, and \autoref{thm:real-completeness-modulus-diagonal-exactness} pins every diagonal observation used by the seal to $\mu,\Delta,D,W,Q$.

Next bind the seal consumers. Apply \autoref{thm:real-completeness-cauchylimitseal-transport-stability} and \autoref{thm:real-completeness-seal-classifier-stability}. These results make both the $\RealUp$ classifier and the downstream $\CauchyLimitSealUp$ route consume the same seal row $S$ through the displayed transports, continuations, package provenance, and local naming row.

For a completion-facing route whose family row is presented by $\CauchySequenceSpaceUp$, use \autoref{thm:real-completeness-cauchysequence-space-shared-window-handoff}. The handoff contributes only its displayed finite window rows before the read returns to $\mu,\Delta,D,W,Q,S,H,C,P,N$.

Finally, \autoref{thm:real-completeness-diagonal-seal-totality} exhausts the diagonal-seal surface for all $\RealUp$ and $\CauchyLimitSealUp$ consumers. Apply \autoref{thm:real-completeness-nonescape-boundary} to exclude quotient streams, host equality, selected external limits, choice principles, and ambient completeness from every completion-facing export.
\end{proof}

\begin{theorem}[Real completeness finite limit-existence witness]
\label{thm:real-completeness-limit-existence-finite-witness}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet. For every precision request made by a $\RealUp$, $\CauchyLimitSealUp$, or completion-facing consumer, the packet supplies a BEDC finite witness for the diagonal limit-existence obligation: the request reads the modulus row $\mu$, selects a displayed diagonal observation through $\Delta$, exposes the $\DyadicRatCoreUp$, $\StreamNameUp$, and $\RegSeqRatUp$ rows $D,W,Q$, reaches the $\RealUp$ seal row $S$, and records the transport, continuation, package, and local naming rows $H,C,P,N$. The witness contains no quotient stream, selected host limit, countable choice, or ambient completeness theorem.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_limit\_existence\_finite\_witness}
\begin{proof}
Project the accepted packet through \autoref{def:real-completeness-carrier}. The rows named in the statement are exactly the rows of the carrier, so the precision request has no source outside the displayed $\BHist$ packet.

Use \autoref{thm:real-completeness-modulus-domain-coverage} to bind each consumed tolerance request to $\mu$. Then apply \autoref{thm:real-completeness-modulus-diagonal-exactness} to route the selected diagonal observation through $\Delta,D,W,Q$.

It remains to identify the endpoint and public ledger. Apply \autoref{thm:real-completeness-diagonal-seal-totality}. The selected route reaches $S$ through $H,C,P,N$, and \autoref{thm:real-completeness-nonescape-boundary} rules out quotient streams, selected host limits, countable choice, and ambient completeness as witness coordinates.
\end{proof}

\begin{theorem}[Real completeness limit uniqueness classifier]
\label{thm:real-completeness-limit-uniqueness-classifier}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
and
$$
R'=(X',\mu',\Delta',D',W',Q',S',H,C,P,N)
$$
be accepted $\RealCompletenessUp$ packets whose $X,\mu,\Delta,D,W,Q$ rows are related by the displayed transports named in the shared $H$ row, and whose consumer routes use the same $C,P,N$ data. Then the two packets export the same finite $\RealUp$ seal-ledger classifier for the candidate limit. The classifier is determined by the transported diagonal rows and the shared $H,C,P,N$ ledger, not by quotient equality of streams, host real equality, a selected external limit, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with classifier stability in \autoref{thm:real-completeness-namecert-obligations}. It transports the family, modulus, selector, dyadic ledger, stream windows, readback row, and seal row componentwise through the displayed $H$ row.

Next use \autoref{thm:real-completeness-selector-readback-determinacy}. Since the transported selector reads use the same $C,P,N$ route, they reach the same finite $\RealUp$ seal ledger.

The public classifier is then fixed by \autoref{thm:real-completeness-seal-classifier-stability}. Finally apply \autoref{thm:real-completeness-nonescape-boundary}; no external completion object or quotient stream is present to refine or split the displayed seal-ledger classification.
\end{proof}

\begin{theorem}[Real completeness LimitSelector handoff]
\label{thm:real-completeness-limitselector-handoff}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet, and let
$$
L=(R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L)
$$
be an accepted $\LimitSelectorUp$ packet. Assume that the selected precision $n$, modulus $\mu_L$, selected index $k_L$, finite window $W_L$, dyadic readback $D_L$, and $\RealUp$ seal row $S$ agree through the displayed transports with the corresponding diagonal rows of $R$ along $\mu,\Delta,D,W,Q,S,H,C,P,N$. Then every $\RealUp$ or $\CauchyLimitSealUp$ consumer of $R$ whose route reads that selected diagonal observation factors through the $\LimitSelectorUp$ finite witness route
$$
n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L
$$
before reaching the same seal row $S$. The factorization contains no host-selected limit, quotient-stream equality, countable-choice selector, or ambient completeness witness.
\end{theorem}
\begin{proof}
First project the selector packet. The local obligations of \autoref{thm:limit-selector-namecert-obligations} expose $R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L$, and \autoref{thm:limit-selector-finite-witness-route} makes every diagonal-limit read pass through the displayed selector, window, readback, seal, transport, continuation, provenance, and naming rows.

Next compare this selector route with the $\RealCompletenessUp$ packet. The agreement assumptions identify the selected precision and modulus with the diagonal rows of $R$, while \autoref{thm:real-completeness-modulus-diagonal-exactness} pins the corresponding observation of $R$ to $\mu,\Delta,D,W,Q$.

It remains to identify the endpoint. Apply \autoref{thm:real-completeness-diagonal-seal-totality} to route every $\RealUp$ and $\CauchyLimitSealUp$ consumer of the selected observation to the same seal row $S$, and apply \autoref{thm:real-completeness-limit-uniqueness-classifier} to keep the transported seal-ledger classifier fixed by the displayed rows.

Finally use selector exhaustion and seal non-escape. By \autoref{thm:limit-selector-diagonal-consumer-exhaustion} and \autoref{thm:limit-selector-real-seal-nonescape}, the selected observation has no remaining route outside $n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L$. The boundary theorem \autoref{thm:real-completeness-nonescape-boundary} excludes host-selected limits, quotient streams, countable choice, and ambient completeness from the $\RealCompletenessUp$ side as well.
\end{proof}

\begin{theorem}[Real completeness limit handoff package]
\label{thm:real-completeness-limit-handoff-package}
For every accepted $\RealCompletenessUp$ packet
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
the concrete paper-side package corresponding to the vision-level limit target consists of the finite limit-existence witness of \autoref{thm:real-completeness-limit-existence-finite-witness}, the uniqueness classifier of \autoref{thm:real-completeness-limit-uniqueness-classifier}, the $\LimitSelectorUp$ finite-route handoff of \autoref{thm:real-completeness-limitselector-handoff}, the $\CauchySequenceSpaceUp$ shared-window handoff of \autoref{thm:real-completeness-cauchysequence-space-shared-window-handoff}, the diagonal seal totality of \autoref{thm:real-completeness-diagonal-seal-totality}, and the scoped consumer seal exhaustion of \autoref{thm:real-completeness-scoped-consumer-seal-exhaustion}. This package is a finite $\BHist$ handoff to $\RealUp$ and downstream seal consumers; it is not a theorem asserting $\RealUp$ completeness as a closed public result.
\end{theorem}
\begin{proof}
First assemble the existence side. Apply \autoref{thm:real-completeness-limit-existence-finite-witness}; it supplies the displayed precision-to-seal route through $\mu,\Delta,D,W,Q,S,H,C,P,N$.

Next assemble the classifier side. Apply \autoref{thm:real-completeness-limit-uniqueness-classifier}; transported packets with the same public ledger export the same finite $\RealUp$ seal-ledger classifier.

Now attach the selector handoff. Apply \autoref{thm:real-completeness-limitselector-handoff}; every selected diagonal observation consumed by a $\RealUp$ or $\CauchyLimitSealUp$ route factors through the independent $\LimitSelectorUp$ finite witness route before it reaches $S$.

Then attach the downstream handoff. Use \autoref{thm:real-completeness-cauchysequence-space-shared-window-handoff} when the regular-family row is supplied through $\CauchySequenceSpaceUp$, and use \autoref{thm:real-completeness-diagonal-seal-totality} to keep every seal consumer on the same displayed route.

Finally apply \autoref{thm:real-completeness-scoped-consumer-seal-exhaustion}. The assembled package is exactly the scoped finite consumer surface. Since the chapter boundary excludes quotient streams, selected host limits, host equality, countable choice, and ambient completeness, the package does not close $\RealUp$ completeness as a public theorem.
\end{proof}

\begin{theorem}[Real completeness shared-tail modulus limit lock]
\label{thm:real-completeness-shared-tail-modulus-limit-lock}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet, and let
$$
T=(R_0,R_1,M_0,M_1,\tau,D_T,W_0,W_1,Q_0,Q_1,E,H_T,C_T,P_T,N_T)
$$
be an accepted $\CauchySharedTailModulusUp$ packet. Assume that $M_0$ and $M_1$ present the same finite precision request read by $\mu$, that the shared threshold $\tau$ presents the diagonal tail threshold $\Delta$, that $D_T$ and $D$ are the same dyadic ledger row, that $W_0$ and $W_1$ present the finite $\StreamNameUp$ windows of $W$, that $Q_0$ and $Q_1$ present the $\RegSeqRatUp$ readback row $Q$, and that the $\RealUp$ seal row $E$ is transported to $S$ by the displayed rows $H_T,C_T,P_T,N_T$ and $H,C,P,N$. Then every $\RealUp$, $\CauchyLimitSealUp$, or completion-facing consumer of $R$ whose route reads this diagonal limit observation factors through the shared-tail-modulus route
$$
M_0,M_1,\tau,D_T,W_0,W_1,Q_0,Q_1,E,H_T,C_T,P_T,N_T
$$
before it reaches the seal row $S$. The locked route exports no quotient stream, selected host limit, countable-choice selector, host real equality, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the finite handoff package. By \autoref{thm:real-completeness-limit-handoff-package}, every completion-facing read of the displayed diagonal limit observation is already confined to the finite $\BHist$ route through $\mu,\Delta,D,W,Q,S,H,C,P,N$ and its downstream seal consumers.

Next identify the shared threshold side. Apply \autoref{thm:cauchy-shared-tail-modulus-tail-synchronization}. The two tail schedules $M_0$ and $M_1$ are read before the single threshold $\tau$, and both $\StreamNameUp$ windows and $\RegSeqRatUp$ readbacks are forced through $\tau,D_T$. The agreement assumptions transport this route to the RealCompleteness rows $\mu,\Delta,D,W,Q$.

Now attach the Real seal. By \autoref{thm:cauchy-shared-tail-modulus-real-seal-handoff}, every Real-facing read of $T$ reaches $E$ only after the shared route through $M_0,M_1,\tau,D_T,W_0,W_1,Q_0,Q_1$. The assumed transport from $E$ to $S$ therefore places the $\RealCompletenessUp$ seal row after the same shared-tail-modulus route.

It remains to rule out a second completion-facing path. The uniqueness classifier of \autoref{thm:real-completeness-limit-uniqueness-classifier} fixes the seal-ledger classifier once the displayed rows $\mu,\Delta,D,W,Q,S,H,C,P,N$ have been identified, and \autoref{thm:real-completeness-nonescape-boundary} removes quotient streams, selected host limits, countable-choice selectors, host real equality, and ambient completeness from the packet boundary. Hence any $\RealUp$, $\CauchyLimitSealUp$, or completion-facing consumer must pass through the shared-tail-modulus route before reaching $S$.
\end{proof}

\begin{theorem}[Real completeness finite-window open phase exit]
\label{thm:real-completeness-finite-window-open-phase-exit}
For every accepted $\RealCompletenessUp$ carrier
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N),
$$
the completion-facing open-phase boundary factors through exactly the $\DyadicRatCoreUp$ ledger row $D$, the $\StreamNameUp$ finite windows $W$, the $\RegSeqRatUp$ readback row $Q$, the $\RealUp$ seal row $S$, and the structural rows $H,C,P,N$. This gives the paper-side finite-window witness for the Phase Real and Completion object chain without claiming $\RealUp$ completeness, quotient equality of streams, selected host limits, countable choice, or $\bridgeCheckedV$ status.
\end{theorem}
\begin{proof}
Begin with the dependency lattice of \autoref{thm:real-completeness-dependency-lattice}. It identifies the completion-facing object chain through the dyadic ledger, stream-window, regular-sequence readback, and RealUp seal rows already present in $R$.

Next apply \autoref{thm:real-completeness-finite-obligation-surface}. The obligation surface exposes exactly $D,W,Q,S$ together with the structural rows $H,C,P,N$, so the open-phase witness is finite and packet-local.

Use \autoref{thm:real-completeness-consumer-route-totality} to route every completion-facing consumer through those displayed rows. Then apply \autoref{thm:real-completeness-nonescape-boundary}; no quotient stream, selected host limit, countable-choice selector, ambient completeness proof, or bridge-checked object lies outside the finite-window packet.
\end{proof}

\input{parts/concrete_instances/realcompleteness/selector_window_seal_factorization}

\closureat{RealCompletenessUp}{scopedStr}
\closureat{RealCompletenessUp}{publicStr}
\closureat{RealCompletenessUp}{bridgedStr}[BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_regseq\_seal\_handoff]
\closureat{RealCompletenessUp}{matureStr}[BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_regseq\_seal\_handoff]

\begin{closurestatus}{\RealCompletenessUp}
  \constructivestory{A $\RealCompletenessUp$ packet is generated by a displayed regular Cauchy family, explicit modulus row, diagonal selector, dyadic observation ledger, stream windows, regular-sequence readback, RealUp seal, transport routes, package provenance, and a local naming row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:real-completeness-limit-handoff-package} binds the public finite handoff package for every $\RealUp$, $\CauchyLimitSealUp$, and completion-facing consumer route over the displayed rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$, with $\CauchySequenceSpaceUp$ handoff rows only when present.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.RealCompletenessUp.RealCompletenessBHistCarrier\_regseq\_seal\_handoff}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close RealUp completeness, uniqueness of completed limits, quotient equality of streams, a public standard bridge, axiom-purity audit, or bridge checking.}
  \upgradepath{Mature closure requires finite diagonal-limit examples and the downstream completion-consumer lattice over the same displayed rows, with axiom-purity audit and bridge checking as separate verification obligations.}
\end{closurestatus}
