\chapter{A Concrete Naming Certificate for $\FirstOrderUp$}
\label{ch:concrete-instances-firstorder-namecert}

The first-order-logic interface $\FirstOrderUp$ packages a signature of relation and function symbols, a set of formulas, and a deduction calculus together with the soundness and completeness data. It depends on $\NameCert_{\SetUp}$ (\autoref{ch:concrete-instances-set-namecert}) and $\NameCert_{\TreeUp}$ (\autoref{ch:concrete-instances-tree-namecert}).

\section{Carrier definition}
\label{sec:firstorder-carrier}

\begin{definition}[FirstOrderUp BHist syntax carrier]\label{def:firstorder-bhist-syntax-carrier}
A carried $\FirstOrderUp$ syntax packet is a displayed $\mathsf{BHist}$ tuple
$(S,T,V,R,F,\tau,\varphi,\rho)$. The row $S$ is the $\SetUp$ symbol-source
row, $T$ is the $\TreeUp$ parse-tree row, $V$ is the variable ledger, $R$ and
$F$ are the relation-symbol and function-symbol rows, $\tau$ is the finite
term/formula tree endpoint, $\varphi$ is the displayed formula endpoint, and
$\rho$ records the $\Pkg$ provenance that ties the syntax packet to the
visible naming certificate.

Acceptance of the packet is read entirely through $\mathsf{BHist}$, $\hsame$,
$\Cont$, $\mathsf{ProbeBundle}$, $\mathsf{SigRel}$, and the $\SetUp$ and $\TreeUp$
$\NameCert$ rows. A host grammar, a host set of strings, or an external
syntax equality is not part of the carrier.
\end{definition}
\leandef{BEDC.Derived.FirstOrderUp.FirstOrderBHistSyntaxCarrier}

\begin{definition}[FirstOrderUp deduction ledger classifier]\label{def:firstorder-deduction-ledger-classifier}
Two $\FirstOrderUp$ syntax/deduction packets agree when their symbol rows,
parse-tree rows, formula endpoint rows, and deduction-step ledgers are
transported by $\hsame$ through the same $\SetUp$ and $\TreeUp$ certificates.
The comparison is rowwise: relation symbols and function symbols move through
the $\SetUp$ source, parse subtrees and formula endpoints move through the
$\TreeUp$ source, and every deduction step carries its premise and conclusion
endpoints by the displayed $\Cont$ and $\hsame$ rows recorded in the ledger.
\end{definition}

\section{The certificate}
\label{sec:firstorder-certificate}

\begin{theorem}[FirstOrderUp formula carrier obligation]\label{thm:firstorder-formula-carrier-obligation}
Every accepted $\FirstOrderUp$ formula row projects to a $\SetUp$ symbol row,
a $\TreeUp$ parse row, a finite $\mathsf{ProbeBundle}$ arity ledger, and a $\mathsf{SigRel}$
endpoint relation. These projections are exactly the visible carrier data of
\autoref{def:firstorder-bhist-syntax-carrier}; no formula is accepted by a
host syntax predicate outside the displayed $\mathsf{BHist}$ packet.
\end{theorem}
\begin{proof}
Invert the carried syntax packet of
\autoref{def:firstorder-bhist-syntax-carrier}. The first projections expose
the $\SetUp$ symbol-source row, the $\TreeUp$ parse-tree row, the relation and
function symbol rows, and the formula endpoint $\varphi$.

The arity information is read from the finite $\mathsf{ProbeBundle}$ ledger attached
to the displayed relation and function rows. Each arity check is therefore a
finite probe over the named symbol endpoints, not an inspection of an ambient
syntax table.

Finally apply induction on the $\TreeUp$ syntax row. Leaf rows read variables
and constants from the symbol and variable ledgers; internal rows read their
subformula endpoints from the same finite tree ledger. The endpoint relation
is the displayed $\mathsf{SigRel}$ row tying the resulting formula endpoint to the
accepted packet.
\end{proof}
\leanchecked{BEDC.Derived.FirstOrderUp.FirstOrderBHistSyntaxCarrier\_formula\_carrier\_obligation}

\begin{theorem}[FirstOrderUp classifier transport obligation]\label{thm:firstorder-classifier-transport-obligation}
Every classifier-related $\FirstOrderUp$ syntax and deduction packet transports
its relation-symbol rows, function-symbol rows, formula endpoints, and
deduction-step ledgers through the displayed $\SetUp$, $\TreeUp$, $\hsame$,
$\Cont$, $\mathsf{ProbeBundle}$, and $\mathsf{SigRel}$ rows of
$\NameCert_{\FirstOrderUp}$. In particular, a transported classifier packet is
obtained by projecting those visible rows from the source packet and repacking
them as the corresponding target packet; no host syntax equality or external
classifier relation is used.
\end{theorem}
\leanchecked{BEDC.Derived.FirstOrderUp.FirstOrderBHistSyntaxCarrier\_classifier\_transport\_obligation}
\begin{proof}
Start with an accepted classifier-related packet and invert the carried
$\mathsf{BHist}$ tuple of \autoref{def:firstorder-bhist-syntax-carrier}. The
projections expose the $\SetUp$ symbol-source row, the $\TreeUp$ parse-tree
row, the relation-symbol and function-symbol rows, the formula endpoint, and
the deduction-step ledger.

Transport the symbol rows through the displayed $\SetUp$ certificate and the
parse and formula rows through the displayed $\TreeUp$ certificate. The
$\mathsf{ProbeBundle}$ rows carry the arity checks, while the
$\mathsf{SigRel}$ rows carry the endpoint relation that identifies the source
and target formula endpoints.

It remains to repack the deduction data. Use the $\Cont$ and $\hsame$ rows
attached to each ledger step to move premises and conclusions through the same
provenance. The repacked rows form another displayed $\FirstOrderUp$
classifier packet, and every field of that packet has been obtained from the
public certificate surface.
\end{proof}

\begin{theorem}[FirstOrderUp deduction endpoint exactness]\label{thm:firstorder-deduction-endpoint-exactness}
The visible $\FirstOrderUp$ deduction endpoints are exact. Every accepted
conclusion endpoint is produced by a finite displayed deduction ledger whose
premises are already accepted formula endpoints, and every such finite ledger
repacks as a $\FirstOrderUp$ deduction endpoint with the same conclusion row.
\end{theorem}
\leanchecked{BEDC.Derived.FirstOrderUp.FirstOrderBHistSyntaxCarrier\_deduction\_endpoint\_exactness}
\begin{proof}
For coverage, invert an accepted deduction endpoint. By
\autoref{thm:firstorder-namecert-obligation-surface}, the endpoint is visible
only through the syntax carrier, the deduction classifier, and the displayed
deduction-soundness ledger. Thus its conclusion row is the final conclusion
of a finite ledger over formula endpoints already carried by
\autoref{thm:firstorder-formula-carrier-obligation}.

For soundness, induct over the finite ledger. The empty ledger exposes only
initial accepted formula endpoints. In the step case, the induction
hypothesis supplies accepted endpoints for the earlier premises, and
\autoref{thm:firstorder-deduction-soundness-ledger-obligation} supplies the
visible $\Cont$ and $\hsame$ rows for the next rule step and its conclusion.

For completeness, start with a finite displayed ledger whose premises are
accepted formula endpoints and whose steps carry the required transport rows.
Repack the formula endpoints by the carrier obligation, repack the rule rows
by the deduction-soundness obligation, and read the last conclusion row as
the displayed $\FirstOrderUp$ deduction endpoint.
\end{proof}

\begin{theorem}[FirstOrderUp ModelTheory consumer boundary]\label{thm:firstorder-modeltheory-consumer-boundary}
A downstream $\ModelTheoryUp$ packet may consume from
$\NameCert_{\FirstOrderUp}$ only the symbol source, parse-tree source, formula
endpoint rows, deduction endpoint rows, classifier transport rows, and
provenance rows exposed by the $\FirstOrderUp$ certificate. The
$\FirstOrderUp$ certificate alone supplies no host syntax equality, external
proof-system validity predicate, semantic satisfaction relation, or model
carrier.
\end{theorem}
\begin{proof}
Project the public surface described in
\autoref{thm:firstorder-namecert-obligation-surface}. The available rows are
the syntax carrier, the deduction classifier, the formula and deduction
obligation rows, and the $\SetUp$ and $\TreeUp$ provenance rows.

Next apply \autoref{thm:firstorder-classifier-transport-obligation}. It shows
that classifier transport for relation symbols, function symbols, formula
endpoints, and deduction ledgers is already accounted for by the displayed
$\hsame$, $\Cont$, $\mathsf{ProbeBundle}$, and $\mathsf{SigRel}$ rows.

Finally apply \autoref{thm:firstorder-deduction-endpoint-exactness}. It makes
the deduction endpoint rows exact, so a consumer can read precisely the
finite ledgers and their accepted conclusion endpoints. None of the projected
or repacked rows contains a semantic satisfaction relation or model carrier,
and none asserts an ambient proof-system validity predicate outside the
displayed BEDC ledger.
\end{proof}

\begin{theorem}[FirstOrderUp deduction soundness ledger obligation]\label{thm:firstorder-deduction-soundness-ledger-obligation}
A $\FirstOrderUp$ deduction ledger is accepted only when every rule step
consumes formula endpoints already carried by
\autoref{def:firstorder-bhist-syntax-carrier} and records its
premise/conclusion transport by $\Cont$ and $\hsame$. The ledger does not
validate a rule by appeal to an external proof system; validity is the finite
display of named endpoint consumption and transport.
\end{theorem}
\begin{proof}
Induct over the finite displayed deduction ledger.

In the empty case there is no rule step to validate. The ledger acceptance
condition reduces to the visibility of the initial formula endpoints already
carried by the syntax packet.

In the step case, the induction hypothesis gives accepted carried endpoints
for all earlier premises. The next rule row must cite only those endpoints,
record the conclusion endpoint as another displayed formula row, and attach
the $\Cont$ and $\hsame$ transport rows that move premises to the conclusion
inside the same $\SetUp$ and $\TreeUp$ provenance.

Appending the checked step preserves acceptance because the new ledger tail
adds one finite row whose inputs, output, and transport are all visible BEDC
rows. Thus the completed deduction remains a named ledger rather than a host
derivation.
\end{proof}

\begin{theorem}[FirstOrderUp NameCert obligation surface]\label{thm:firstorder-namecert-obligation-surface}
The public $\NameCert_{\FirstOrderUp}$ surface consists exactly of the syntax
carrier of \autoref{def:firstorder-bhist-syntax-carrier}, the deduction
classifier of \autoref{def:firstorder-deduction-ledger-classifier}, the
formula carrier obligation of
\autoref{thm:firstorder-formula-carrier-obligation}, the deduction-soundness
ledger of \autoref{thm:firstorder-deduction-soundness-ledger-obligation}, the
$\SetUp$ symbol provenance, the $\TreeUp$ syntax provenance, stability under
$\hsame$, and exactness of displayed formula and deduction endpoints.
\end{theorem}
\begin{proof}
Collect the carrier rows first. The syntax carrier supplies the displayed
$\mathsf{BHist}$ packet, and the formula carrier obligation projects from it
the symbol source, parse source, arity ledger, and endpoint relation.

Next collect the comparison rows. The deduction classifier supplies the
rowwise $\hsame$ transport through the same $\SetUp$ and $\TreeUp$
certificates, while the deduction-soundness ledger supplies the finite rule
steps that consume already carried endpoints and produce displayed conclusion
endpoints.

It remains to check public coverage. Any consumer of $\NameCert_{\FirstOrderUp}$
asks for a syntax endpoint, a deduction endpoint, provenance in $\SetUp$ or
$\TreeUp$, transport under $\hsame$, or exact readback of a visible formula or
deduction row. Each request is one of the rows just collected, so the public
surface contains no additional carrier, classifier, or proof-system field.
\end{proof}

\begin{definition}[FirstOrderUp deduction ledger concatenation source]\label{def:firstorder-deduction-ledger-concatenation-source}
Fix one carried $\FirstOrderUp$ syntax packet as in \autoref{def:firstorder-bhist-syntax-carrier}. Let $D_1$ and $D_2$ be accepted finite $\FirstOrderUp$ deduction ledgers read through the same $\SetUp$ and $\TreeUp$ certificates. They are composable when the final conclusion endpoint row displayed by $D_1$ is the same formula endpoint row that appears as the initial premise row of $D_2$, with that shared row compared only by the $\hsame$ transport already admitted by \autoref{def:firstorder-deduction-ledger-classifier}.

In that situation, the concatenation $D_1 \mathbin{+\!\!+} D_2$ is the finite ledger obtained by listing all rule rows of $D_1$ followed by all rule rows of $D_2$, while reading the join through the shared formula endpoint row rather than through any extra host-level formula token or external proof-tree node.
\end{definition}

\begin{theorem}[FirstOrderUp deduction ledger concatenation closure]\label{thm:firstorder-deduction-ledger-concatenation-closure}
Let $D_1$ and $D_2$ be accepted finite $\FirstOrderUp$ deduction ledgers over one carried syntax packet from \autoref{def:firstorder-bhist-syntax-carrier}, and suppose that $D_1$ and $D_2$ are composable in the sense of \autoref{def:firstorder-deduction-ledger-concatenation-source}. Then the concatenated ledger $D_1 \mathbin{+\!\!+} D_2$ is again an accepted $\FirstOrderUp$ deduction ledger over the same $\SetUp$ and $\TreeUp$ dependency certificates.

Moreover, every premise row, conclusion row, and transport row appearing in $D_1 \mathbin{+\!\!+} D_2$ is already one of the visible rows carried by $D_1$, by $D_2$, or by their shared endpoint formula row. No extra deduction rule, external cut formula, or ambient proof-system datum enters at the join.
\end{theorem}
\leanchecked{BEDC.Derived.FirstOrderUp.FirstOrderDeductionLedgerConcatenation\_closure}
\begin{proof}
Proceed by induction on the second ledger $D_2$, read as the finite displayed deduction ledger from \autoref{thm:firstorder-deduction-soundness-ledger-obligation}.

If $D_2$ is empty, then $D_1 \mathbin{+\!\!+} D_2$ is just $D_1$, so acceptance is the given acceptance of $D_1$.

For the step case, write $D_2$ as a shorter accepted prefix $E$ followed by one final rule row $r$. By the induction hypothesis, $D_1 \mathbin{+\!\!+} E$ is an accepted deduction ledger over the same $\SetUp$ and $\TreeUp$ certificates.

It remains to append $r$. Because $E$ followed by $r$ is accepted, \autoref{thm:firstorder-deduction-soundness-ledger-obligation} says that $r$ consumes only formula endpoints already carried by the displayed ledger before it, and that its premise/conclusion transport is recorded by visible $\Cont$ and $\hsame$ rows inside the same provenance. Every premise of $r$ that lies wholly inside $E$ is therefore already present in the accepted prefix $D_1 \mathbin{+\!\!+} E$.

The only additional possibility is a premise of $r$ that traces back to the initial premise row of $D_2$. By composability from \autoref{def:firstorder-deduction-ledger-concatenation-source}, that initial premise row is the shared endpoint formula row at the join with $D_1$. By \autoref{thm:firstorder-formula-carrier-obligation}, this shared endpoint is already a carried $\FirstOrderUp$ formula row inside the same syntax packet, so the join introduces no extra carrier data. By \autoref{def:firstorder-deduction-ledger-classifier}, any comparison needed at the join is exactly the admitted $\hsame$ transport through the same $\SetUp$ and $\TreeUp$ certificates.

Thus all inputs required by $r$ are available in the accepted prefix $D_1 \mathbin{+\!\!+} E$, and the output row of $r$ is recorded by the same visible conclusion and transport data it had inside $D_2$. Appending $r$ therefore preserves acceptance by the same step-case criterion used in \autoref{thm:firstorder-deduction-soundness-ledger-obligation}.

The induction closes, so $D_1 \mathbin{+\!\!+} D_2$ is an accepted finite $\FirstOrderUp$ deduction ledger over the original $\SetUp$ and $\TreeUp$ certificates. The final claim follows because concatenation only reorders the already displayed rows by placing the rows of $D_2$ after those of $D_1$, with the join read through the shared endpoint formula row and no further datum.
\end{proof}

\begin{theorem}[FirstOrderUp hsame stability obligation]\label{thm:firstorder-hsame-stability-obligation}
For the public $\NameCert_{\FirstOrderUp}$ surface, every classifier-related
syntax or deduction packet transports its visible endpoints by the displayed
$\hsame$ data. Formula endpoints, deduction-step premise and conclusion
endpoints, $\SetUp$ symbol rows, $\TreeUp$ parse rows, and $\Cont$ ledger rows
remain accepted after transport exactly when the rows are those projected from
\autoref{def:firstorder-bhist-syntax-carrier} and compared by
\autoref{def:firstorder-deduction-ledger-classifier}.
\end{theorem}
\begin{proof}
Project the deduction-ledger classifier of
\autoref{def:firstorder-deduction-ledger-classifier}. Its comparison is
rowwise, so the relation-symbol and function-symbol rows move through the
$\SetUp$ source, while parse subtrees and formula endpoints move through the
$\TreeUp$ source.

For a deduction step, use the same classifier row on the displayed premise
and conclusion endpoints. The step is accepted only with the attached $\Cont$
row and the corresponding $\hsame$ row, so transport does not create a new
rule premise or a new conclusion outside the ledger.

The carrier rows then identify the endpoints being transported. By
\autoref{def:firstorder-bhist-syntax-carrier}, each formula endpoint and each
deduction endpoint cited by the ledger is a row of the same displayed
$\mathsf{BHist}$ packet. Thus stability is exactly the classifier transport
applied to already carried rows.
\end{proof}
\leanchecked{BEDC.Derived.FirstOrderUp.FirstOrderBHistSyntaxCarrier\_hsame\_stability\_obligation}

\begin{theorem}[FirstOrderUp endpoint exactness obligation]\label{thm:firstorder-endpoint-exactness-obligation}
Every public $\FirstOrderUp$ formula or deduction endpoint readback is exactly
one of the endpoints projected from the syntax carrier and the deduction
ledger. Conversely, every projected formula endpoint, premise endpoint,
conclusion endpoint, and ledger endpoint repacks into the public
$\NameCert_{\FirstOrderUp}$ endpoint surface described by
\autoref{thm:firstorder-namecert-obligation-surface}.
\end{theorem}
\begin{proof}
For the forward direction, read a public formula endpoint through the carrier
of \autoref{def:firstorder-bhist-syntax-carrier}. The readback exposes the
displayed formula endpoint $\varphi$, together with its $\SetUp$ symbol row,
$\TreeUp$ parse row, finite arity ledger, and $\mathsf{SigRel}$ endpoint
relation.

A public deduction endpoint is read through the deduction ledger. By
\autoref{thm:firstorder-deduction-soundness-ledger-obligation}, every premise
and conclusion consumed by a rule step is already a carried formula endpoint,
and the step records its own $\Cont$ and $\hsame$ transport rows. Hence no
readback endpoint lies outside the projected carrier and ledger.

For the reverse direction, start with a projected carrier or ledger endpoint.
The NameCert surface theorem,
\autoref{thm:firstorder-namecert-obligation-surface}, collects exactly these
syntax endpoints, deduction endpoints, provenance rows, transport rows, and
exact readback rows. Repacking the projection through that surface gives the
corresponding public endpoint, and the two constructions expose the same
displayed row.
\end{proof}

\begin{theorem}[FirstOrderUp coverage obligation]\label{thm:firstorder-coverage-obligation}
Every accepted public $\FirstOrderUp$ request is covered by one of the listed
certificate rows: $\SetUp$ symbol provenance, $\TreeUp$ parse provenance,
finite $\mathsf{ProbeBundle}$ arity data, a $\mathsf{SigRel}$ endpoint relation,
a $\Cont$ transport row, or a $\Pkg$ provenance row. No accepted request
requires an additional carrier, classifier, stability, exactness, or coverage
field outside the chapter surface.
\end{theorem}
\begin{proof}
Analyze an accepted public request by the part of the $\NameCert_{\FirstOrderUp}$
surface it asks to read.

\begin{enumerate}
\item A syntax endpoint request is covered by
\autoref{def:firstorder-bhist-syntax-carrier} and
\autoref{thm:firstorder-formula-carrier-obligation}. The former supplies the
$\mathsf{BHist}$ packet and $\Pkg$ provenance; the latter projects the
$\SetUp$ symbol row, $\TreeUp$ parse row, finite $\mathsf{ProbeBundle}$ arity
rows, and $\mathsf{SigRel}$ endpoint relation.

\item A deduction endpoint request is covered by
\autoref{thm:firstorder-deduction-soundness-ledger-obligation}. Each rule
step consumes previously carried formula endpoints and records the displayed
premise, conclusion, $\Cont$, and $\hsame$ rows.

\item A transport request is covered by
\autoref{thm:firstorder-hsame-stability-obligation}. The classifier transports
only the already projected symbol, parse, endpoint, and ledger rows, so the
request stays inside the displayed carrier and deduction surface.

\item A provenance request is covered by the $\SetUp$ and $\TreeUp$ NameCert
rows named in \autoref{thm:firstorder-namecert-obligation-surface}, together
with the $\Pkg$ row carried in
\autoref{def:firstorder-bhist-syntax-carrier}.
\end{enumerate}

These cases exhaust the public request forms listed by the NameCert surface
theorem. Therefore each accepted request is accounted for by an existing
displayed BEDC row.
\end{proof}

\begin{definition}[FirstOrderUp satisfaction BHist carrier]\label{def:firstorder-satisfaction-bhist-carrier}
A carried $\FirstOrderUp$ satisfaction packet is a displayed $\mathsf{BHist}$
tuple over five visible rows: the $\SetUp$ symbol row, the $\TreeUp$ formula
row, the assignment and environment row, the interpretation row for relation
and function symbols, and the finite provenance row. The provenance row records
the $\Cont$, $\hsame$, and $\Pkg$ data that connect the symbol names, formula
endpoint, variable assignment, and interpretation entries to the same visible
syntax packet of \autoref{def:firstorder-bhist-syntax-carrier}.

The satisfaction predicate is the row classifier of this packet. It accepts
only those reads whose formula endpoint is carried by the syntax row, whose
free variables are read through the assignment/environment row, whose atomic
relation and function entries are read through the interpretation row, and
whose recursive connective and quantifier steps are displayed by finite
$\Cont$ and $\hsame$ transport. No host model carrier, ambient truth relation,
or unrecorded semantic equality is part of the carrier.
\end{definition}

\begin{theorem}[FirstOrderUp soundness transport row]\label{thm:firstorder-soundness-transport-row}
For every accepted $\FirstOrderUp$ deduction step, satisfaction rows transport
from the displayed premise packets to the displayed conclusion packet using
only the deduction ledger, $\Cont$, $\hsame$, $\SetUp$, $\TreeUp$, and
$\NameCert$ provenance recorded in \autoref{def:firstorder-satisfaction-bhist-carrier}.
Equivalently, if every premise endpoint of a rule step carries a satisfaction
packet over the same symbol, assignment/environment, and interpretation rows,
then the conclusion endpoint carries the satisfaction packet produced by the
rule row and its displayed transport data.
\end{theorem}
\begin{proof}
Induct over the finite deduction ledger.

In the empty ledger there is no rule step to transport. The only available
reads are the carried syntax and satisfaction rows already present in the
visible packet.

For a nonempty ledger, apply the induction hypothesis to the earlier rule
rows. This supplies satisfaction packets for every previously accepted premise
endpoint, all over the same $\SetUp$ symbol row, $\TreeUp$ formula row,
assignment/environment row, interpretation row, and provenance row.

The next displayed rule step names its premise endpoints and its conclusion
endpoint inside the deduction ledger. Project the accompanying $\Cont$ and
$\hsame$ rows. These rows transport the premise satisfaction packets across
the carried formula endpoints and repack the result as the conclusion
satisfaction packet.

Appending the transported conclusion preserves the ledger invariant because
the new row cites only displayed premises, the displayed rule datum, and the
same $\SetUp$, $\TreeUp$, and $\NameCert$ provenance. Thus soundness is a
finite row transport statement, not an appeal to an unrecorded proof system or
model class.
\end{proof}

\begin{theorem}[FirstOrderUp completeness boundary]\label{thm:firstorder-completeness-boundary}
The $\FirstOrderUp$ completeness surface is a BEDC boundary: every public
completeness readback exposes a carried syntax row, the satisfaction carrier
row of \autoref{def:firstorder-satisfaction-bhist-carrier}, a deduction ledger
row, and the $\Pkg$ provenance tying those rows to $\NameCert_{\SetUp}$ and
$\NameCert_{\TreeUp}$. A readback that requires a host model class, an
unrecorded semantic relation, or an external proof system is outside the
public $\FirstOrderUp$ certificate.
\end{theorem}
\begin{proof}
Project a public completeness readback from the displayed $\FirstOrderUp$
packet. Its syntax component is one of the carried formula rows of
\autoref{def:firstorder-bhist-syntax-carrier}, and its derivation component is
one of the finite rows of
\autoref{def:firstorder-deduction-ledger-classifier}.

Project the semantic component through
\autoref{def:firstorder-satisfaction-bhist-carrier}. This exposes the
assignment/environment row, the interpretation row, and the finite
$\Cont/\hsame/\Pkg$ provenance that connects semantic reads to the same
displayed formula endpoint.

It remains to check that the readback is complete for the public surface and
no larger. Induct over the finite deduction ledger. Initial rows are exactly
the carried syntax and satisfaction packets; each rule row is handled by the
transport statement of
\autoref{thm:firstorder-soundness-transport-row}; the final row is therefore a
displayed conclusion packet with the same package provenance.

Any proposed readback field not obtained by these projections has no displayed
$\mathsf{BHist}$ row, no $\Cont$ or $\hsame$ transport, and no $\Pkg$ route back
to $\NameCert_{\SetUp}$ or $\NameCert_{\TreeUp}$. Such a field is not admitted
by the $\FirstOrderUp$ certificate.
\end{proof}

\begin{theorem}[FirstOrderUp satisfaction endpoint soundness]\label{thm:firstorder-satisfaction-endpoint-soundness}
A satisfaction endpoint row for a carried $\FirstOrderUp$ formula is sound
only when the formula endpoint, the model/source row, and the semantic result
row are all displayed $\mathsf{BHist}$ rows. The three rows must be transported
through the same $\hsame$ and $\Cont$ ledgers, observed by finite
$\mathsf{ProbeBundle}$ and $\mathsf{SigRel}$ data, and grounded in the
$\SetUp$, $\TreeUp$, and $\NameCert_{\FirstOrderUp}$ provenance exposed by
\autoref{thm:firstorder-namecert-obligation-surface}.
\end{theorem}
\begin{proof}
Project the carried syntax packet of
\autoref{def:firstorder-bhist-syntax-carrier}. The formula endpoint
$\varphi$ is already a displayed $\mathsf{BHist}$ row with $\SetUp$ symbol
provenance and $\TreeUp$ parse provenance.

Next project the satisfaction packet. Its model/source row is accepted only
as a named source row compatible with the same relation and function symbol
rows, and its semantic result row is the endpoint reached from the formula
and source rows by the displayed $\Cont$ ledger. The finite
$\mathsf{ProbeBundle}$ probes record the arity and source observations used
by that ledger, while $\mathsf{SigRel}$ records the endpoint relation being
read.

Finally transport the three rows together by the carried $\hsame$ witnesses.
Because the public surface of
\autoref{thm:firstorder-namecert-obligation-surface} exports only these rows
and their provenance, satisfaction soundness is exactly endpoint soundness
inside the BEDC ledger and not a host-level semantic assertion.
\end{proof}

\begin{theorem}[FirstOrderUp substitution transport obligation]\label{thm:firstorder-substitution-transport-obligation}
Let a carried $\FirstOrderUp$ formula endpoint contain a variable row or
subtree row that is replaced by another carried endpoint related by the
deduction classifier of
\autoref{def:firstorder-deduction-ledger-classifier}. Formula acceptance and
deduction-ledger acceptance are preserved precisely when every affected
symbol, parse, premise, and conclusion row transports rowwise by the inherited
$\hsame$ witnesses and the displayed $\Cont$ ledgers.
\end{theorem}
\begin{proof}
Induct on the displayed $\TreeUp$ parse row of the carried formula.

In a leaf case, the replaced variable or constant endpoint is a row in the
variable or symbol ledger. The classifier-related replacement supplies the
same $\SetUp$ provenance and an $\hsame$ witness, so the leaf remains an
accepted formula endpoint after the one-row $\Cont$ transport.

In an internal subtree case, apply the induction hypothesis to each affected
child endpoint. The parent relation or function row is fixed by the
$\SetUp$ classifier, and the $\TreeUp$ provenance repacks the transported
children as the transported parent endpoint.

For a deduction ledger, induct over the finite rule list. Premise endpoints
transport by the formula argument above, and each rule row records its
conclusion through the same displayed $\Cont$ ledger. Appending the
transported rule row preserves ledger acceptance because no step consumes an
endpoint outside the rowwise $\hsame$ comparison supplied by the classifier.
\end{proof}

\begin{theorem}[FirstOrderUp completeness boundary obligation]\label{thm:firstorder-completeness-boundary-obligation}
Any completeness datum exposed by $\NameCert_{\FirstOrderUp}$ is a displayed
BEDC ledger from semantic endpoint agreement back to a finite deduction
ledger. It is not host model-theoretic completeness, and it is not an
external proof-system oracle: the datum must begin with displayed satisfaction
endpoint agreement and end with a finite deduction ledger accepted by
\autoref{thm:firstorder-deduction-soundness-ledger-obligation}.
\end{theorem}
\begin{proof}
Project the public surface of
\autoref{thm:firstorder-namecert-obligation-surface}. The available rows are
the syntax carrier, the deduction classifier, the formula carrier obligation,
the deduction-soundness ledger, and the $\SetUp$ and $\TreeUp$ provenance.

Now read a completeness datum as a finite reverse ledger. Its input is not a
class of all host models; it is semantic endpoint agreement between displayed
satisfaction rows of
\autoref{thm:firstorder-satisfaction-endpoint-soundness}. Each reverse step
must name the formula endpoint it consumes, the semantic row it reads, and
the deduction endpoint it contributes.

Induct over this finite reverse ledger. The empty case returns the displayed
initial deduction ledger. In the step case, the induction hypothesis supplies
the earlier finite ledger, and the next reverse row appends one accepted
deduction step with its carried premise and conclusion endpoints. The result
is therefore a BEDC deduction ledger, which states the completeness boundary
without importing an external model theory or proof-system oracle.
\end{proof}
