\chapter{A Concrete Naming Certificate for $\DoCalculusUp$}
\label{ch:concrete-instances-do-calculus-namecert}
\origin{human}

Following Pearl, \emph{Causality}, 2009, the intervention calculus used here is
recorded as a finite certificate surface rather than as an external semantic
oracle. The $\DoCalculusUp$ packet keeps the intervention ledger, observed
variable rows, adjustment-set witnesses, distribution rows, conditional
independence certificates, and conditional-expectation handoff rows visible as
BEDC data. It does not claim a host probability space, a full structural causal
model, graphical completeness of do-calculus, or a selected counterfactual
semantics.

The finite intervention ledger consumes already certified probability-facing
rows rather than creating a host causal model. Its probability-space export
surface is the one isolated by
\autoref{ch:concrete-instances-probspace-namecert}; its conditional
independence certificates are read through
\autoref{ch:concrete-instances-independence-namecert}; its displayed
distribution handoff is the surface of
\autoref{ch:concrete-instances-distribution-namecert}; and its
conditional-expectation row is routed through
\autoref{ch:concrete-instances-condexp-namecert}. Thus $\DoCalculusUp$ only
packages finite intervention reads through those certified probability-facing
rows.

\begin{definition}[DoCalculus carrier]
\label{def:do-calculus-carrier}
A $\DoCalculusUp$ carrier is a finite $\BHist$ packet
$$
D=(I,V,A,M,R,J,E,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $I$ is the finite intervention ledger, whose rows name the intervened
variables, the displayed intervention marks, and the finite order in which the
intervention rows are read;
\item $V$ is the finite observed-variable row, listing the outcome, treatment,
covariate, and auxiliary observation names that are visible to the certificate;
\item $A$ is the adjustment-set ledger, containing only finite rows that name
which observed variables are admitted as adjustment coordinates for the
displayed query;
\item $M$ records the intervention-modified distribution rows, including the
pre-intervention observational row, the post-intervention row, and the finite
conditioning rows exposed to consumers;
\item $R$ records conditional-independence certificates used by the intervention
ledger and the adjustment-set ledger;
\item $J$ is the conditional-expectation handoff row, whose input is the
displayed adjusted distribution row and whose output is the query-facing
expectation row;
\item $E$ records the probability-facing export row consumed by downstream
probability chapters;
\item $H$ records the componentwise $\hsame$ transports for intervention rows,
observed-variable rows, adjustment ledgers, distribution rows, independence
certificates, conditional-expectation rows, and probability exports;
\item $C$ records the displayed $\Cont$ routes by which consumers read
intervention admission, adjustment-set membership, independence certificates,
distribution handoffs, and conditional-expectation exports;
\item $P$ records $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, finite
variable rows, finite ledger rows, probability handoff rows, and local naming
rows;
\item $N$ is the local $\NameCert_{\DoCalculusUp}$ provenance row.
\end{enumerate}
The carrier accepts exactly finite intervention-ledger packets whose consumers
can read every causal query through the displayed adjustment, independence,
distribution, and expectation rows.
\end{definition}

\begin{theorem}[DoCalculus NameCert obligation surface]
\label{thm:do-calculus-namecert-obligation-surface}
Every accepted $\DoCalculusUp$ packet with carrier
\autoref{def:do-calculus-carrier} carries five local naming obligations:
\begin{enumerate}
\item carrier admission: the tuple $D=(I,V,A,M,R,J,E,H,C,P,N)$ is admitted as
one finite $\BHist$ packet;
\item classifier transport: componentwise $\hsame$ and $\Cont$ transport
preserves the intervention, observed-variable, adjustment, distribution,
independence, expectation, package, and naming rows;
\item adjustment ledger exactness: the adjustment row $A$ lists exactly the
observed coordinates allowed to mediate the displayed intervention query;
\item intervention non-escape: every consumer-visible intervention read passes
through $I,V,A,M,R,H,C,P,N$ and cannot project an unlisted intervention, hidden
counterfactual, or host causal model;
\item probability handoff: every probability-facing read passes through the
conditional-expectation row $J$ and the export row $E$ after the finite
adjustment and independence rows have been displayed.
\end{enumerate}
These five rows are the complete local $\NameCert_{\DoCalculusUp}$ surface for
the finite intervention calculus packet.
\end{theorem}
\begin{proof}
Project the accepted carrier. Its coordinates are the finite rows
$I,V,A,M,R,J,E,H,C,P,N$, so carrier admission is just the displayed $\BHist$
packet.

For classifier transport, move each coordinate through its stored $\hsame$ row
and then read it through the corresponding $\Cont$ route. Because the carrier is
componentwise, no transported row can introduce a variable, intervention,
distribution, or handoff coordinate not already listed in the tuple.

Adjustment exactness is read from $A$: it names only observed variables from
$V$, and the distribution rows in $M$ consume exactly those names for the
displayed query. The intervention non-escape clause follows because every
intervention-facing route has to pass through $I$ and the same finite ledger
rows before a consumer can read it.

Finally, probability-facing data are exported only through $J$ and $E$. The
conditional-independence certificates in $R$ and the adjustment ledger $A$ are
therefore visible before the expectation handoff is consumed, which keeps the
handoff finite and internal to the packet.
\end{proof}

\begin{theorem}[DoCalculus adjustment ledger exactness]
\label{thm:do-calculus-adjustment-ledger}
For every accepted $\DoCalculusUp$ packet $D=(I,V,A,M,R,J,E,H,C,P,N)$, the
adjustment-set ledger $A$ is exhausted by the finite observed-variable rows in
$V$ and by the conditional-independence certificates in $R$ that justify their
use for the displayed intervention query. No variable outside $V$ and no
unstored independence assertion can be read as part of the adjustment set.
\end{theorem}
\begin{proof}
Read the observed-variable coordinate $V$. It gives the finite list of
outcome, treatment, covariate, and auxiliary observation names available to the
packet.

Next read the adjustment ledger $A$. Each adjustment entry is indexed by one of
those observed names and points to an independence certificate in $R$ used by
the displayed query.

Thus the adjustment surface is exhausted by $V,A,R,H,C,P,N$. A hidden variable
or unstored independence assertion would require a coordinate absent from
\autoref{def:do-calculus-carrier}, so it cannot be projected from the accepted
packet.
\end{proof}

\begin{theorem}[DoCalculus intervention non-escape]
\label{thm:do-calculus-intervention-non-escape}
Every intervention-facing consumer of an accepted $\DoCalculusUp$ packet
$D=(I,V,A,M,R,J,E,H,C,P,N)$ factors through the intervention ledger $I$, the
observed-variable row $V$, the adjustment ledger $A$, the distribution rows
$M$, the independence certificates $R$, the transport rows $H$, the
continuation routes $C$, the package provenance $P$, and the local
$\NameCert$ row $N$. Such a consumer cannot obtain a hidden intervention, an
unlisted causal graph, a counterfactual selector, or a host structural causal
model from the packet.
\end{theorem}
\begin{proof}
Use the carrier definition to inspect an intervention read. The read begins at
the finite ledger $I$, and each intervention mark is paired with visible
observed-variable data in $V$.

The route then passes through the adjustment ledger, the modified distribution
rows, and the named independence certificates. Transport and consumer access
are only the displayed $H$ and $C$ rows, with provenance kept in $P$ and $N$.

The excluded objects have no coordinate in the carrier. Since consumer routes
are finite projections from the displayed packet, none of those objects can
escape through an intervention-facing read.
\end{proof}

\begin{theorem}[DoCalculus probability handoff]
\label{thm:do-calculus-probability-handoff}
Every probability-facing read from an accepted $\DoCalculusUp$ packet factors
through the adjusted distribution rows $M$, the conditional-independence
certificates $R$, the conditional-expectation handoff row $J$, and the export
row $E$. The handoff is a finite certificate route into probability chapters,
not a claim of host measure theory, graphical completeness, or selected
counterfactual semantics.
\end{theorem}
\begin{proof}
Project the distribution coordinate $M$ and the independence coordinate $R$.
They display the observational, post-intervention, and conditioning rows
available to the query together with the finite certificates that justify the
adjustment route.

Read the conditional-expectation handoff $J$. Its input is the adjusted
distribution row already exposed by $M$ and $R$, and its output is the
probability-facing row later exported by $E$.

Therefore the probability chapter receives only the finite handoff packet
$M,R,J,E,H,C,P,N$. No ambient probability space, completeness theorem for
do-calculus, or counterfactual selector is supplied by this route.
\end{proof}
