\chapter{A Concrete Naming Certificate for \(\AbGroupUp\)}
\label{ch:concrete-instances-abgroup-namecert}

The abelian group interface \(\AbGroupUp\) extends \autoref{ch:concrete-instances-group-namecert} with the commutativity field \(a \cdot b = b \cdot a\) under the carrier's classifier. It is the abelian specialization of the group certificate; the integer additive group from \autoref{ch:concrete-instances-int-namecert} is the canonical concrete instance.

\section{Carrier definition}

\begin{definition}[AbGroup carrier]
\label{def:abgroup-carrier}
Use a group setup extended with commutativity of the binary operation.
\end{definition}

\section{The certificate}

\begin{definition}[AbGroup source specification]
\label{def:abgroup-source-specification}
The source is a certified group carrier plus a commutativity field.
\end{definition}

\begin{definition}[AbGroup pattern specification]
\label{def:abgroup-pattern-specification}
The pattern is group expression formation under an operation whose operands may be exchanged by certificate law.
\end{definition}

\begin{definition}[AbGroup classifier specification]
\label{def:abgroup-classifier-specification}
The classifier is the group carrier classifier.
\end{definition}

\begin{definition}[AbGroup stability certificate]
\label{def:abgroup-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item all group stability fields
  \item commutativity under classifier
  \item compatibility of commutativity with inverse and multiplication congruence
\end{enumerate}
\end{definition}

\begin{theorem}[AbGroup left-right multiplication swap]
\label{thm:abgroup-mul-left-right-swap}
For BEDC histories equipped with an associative multiplication, commutativity,
and multiplication congruence under \(\hsame\), the expression
\(a\cdot(b\cdot c)\) is internally the same as \(b\cdot(a\cdot c)\).
\end{theorem}
\begin{proof}
Reassociate \(a\cdot(b\cdot c)\) to \((a\cdot b)\cdot c\), transport the
left factor across commutativity, and reassociate \((b\cdot a)\cdot c\) back to
\(b\cdot(a\cdot c)\).
\end{proof}
\leanchecked{BEDC.Derived.AbGroupUp.abgroup\_mul\_left\_right\_swap}

\begin{definition}[AbGroup ledger policy]
\label{def:abgroup-ledger-policy}
Record group expression provenance and the commutativity law when used.
\end{definition}

\begin{definition}[\(\AbGroupUp\) certificate obligations]
\label{def:abgroup-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\AbGroupUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\AbGroupUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.
