\chapter{A Concrete Naming Certificate for $\RamseyUp$}
\label{ch:concrete-instances-ramsey-namecert}

The Ramsey-theory interface $\RamseyUp$ packages, for every finite colouring of the $r$-element subsets of a sufficiently large finite set, a monochromatic subset of bounded size. It depends on $\NameCert_{\FinSetUp}$ (\autoref{ch:concrete-instances-finset-namecert}) and $\NameCert_{\GraphUp}$ (\autoref{ch:concrete-instances-graph-namecert}).

\section{Carrier definition}
\label{sec:ramsey-carrier}

\begin{definition}[Ramsey monochrome witness carrier]
\label{def:ramsey-monochrome-witness-carrier}
The Ramsey monochrome witness carrier is the finite $\mathsf{BHist}$ packet
whose readable rows are the $\FinSetUp$ vertex spine, the displayed subset
spine, the colour endpoint rows indexed by that subset spine, the chosen
witness subset row, the component $\hsame$ transports, the finite $\Cont$
lookup routes from displayed subsets to colour endpoints, and the shared
$\Pkg$ provenance for the packet. The carrier accepts a downstream witness
only when each row is read through these finite packet coordinates and through
the dependency certificates $\NameCert_{\FinSetUp}$ and
$\NameCert_{\GraphUp}$ where those projections are requested.
\end{definition}

\section{The certificate}
\label{sec:ramsey-certificate}

\begin{theorem}[Ramsey colouring carrier obligation]
\label{thm:ramsey-colouring-carrier-obligation}
A carried $\RamseyUp$ colouring row over a displayed $\FinSetUp$ source is a
finite $\mathsf{BHist}$ packet consisting of the certified finite vertex
spine, the certified $r$-subset spine read through $\NameCert_{\FinSetUp}$,
one colour endpoint row for each displayed subset, finite $\Cont$ routes tying
the subset rows to their colour endpoints, and shared $\Pkg$ provenance for
the table. The carrier accepts only these finite colouring rows.

The carrier does not read a host finite-set enumeration, a host function from
subsets to colours, or an ambient combinatorial universe. All subset and colour
reads pass through the displayed $\mathsf{BHist}$ rows and the finite ledger.
\end{theorem}
\leanchecked{BEDC.Derived.RamseyUp.RamseyColouringCarrier\_obligation\_surface}
\begin{proof}
Project the $\RamseyUp$ row to the finite vertex spine supplied by
$\NameCert_{\FinSetUp}$ and to the displayed subset spine built over it. The
colour table is then a finite family of endpoint rows indexed by that subset
spine, with each lookup routed by a visible $\Cont$ row and packaged by the
same $\Pkg$ provenance.

Since the packet has no coordinate for a host enumeration or a host colouring
function, a consumer can only read the listed $\mathsf{BHist}$ rows. Repacking
those rows gives the stated carrier surface.
\end{proof}

\begin{theorem}[Ramsey monochrome classifier stability]
\label{thm:ramsey-monochrome-classifier-stability}
Let $\mathcal C$ and $\mathcal C'$ be carried $\RamseyUp$ colouring rows over
the same displayed $\FinSetUp$ source. If their vertex spines, subset spines,
colour endpoint rows, finite $\Cont$ routes, and $\Pkg$ provenance are related
componentwise by $\hsame$, then the monochrome-subset classifier transports
from $\mathcal C$ to $\mathcal C'$. In particular, any displayed witness subset
whose $r$-subsets have one colour in $\mathcal C$ is carried to a displayed
witness subset with the same classified colour in $\mathcal C'$.
\end{theorem}
\leanchecked{BEDC.Derived.RamseyUp.RamseyColouringCarrier\_classifier\_stability}
\begin{proof}
Begin with the subset witness. The $\FinSetUp$ classifier transports the
finite vertex entries and the displayed subset spine, so every $r$-subset read
from the witness in $\mathcal C$ has a corresponding transported row in
$\mathcal C'$.

Next transport the colour endpoints along the displayed $\hsame$ rows. The
finite $\Cont$ routes preserve which table entry is read by each subset, and
the shared $\Pkg$ provenance keeps the transported reads inside the same
colouring packet.

The monochrome condition is pointwise equality through the colour classifier
on the transported endpoint rows. Thus all transported $r$-subsets retain the
same classified colour, and the witness subset remains monochrome without
choosing a host subset representative.
\end{proof}

\begin{theorem}[Ramsey monochrome witness scope]
\label{thm:ramsey-monochrome-witness-scope}
Every monochrome witness consumed downstream from the $\RamseyUp$ surface is
read only through the carrier of
\autoref{def:ramsey-monochrome-witness-carrier}, together with the
$\NameCert_{\FinSetUp}$ and $\NameCert_{\GraphUp}$ projections already exposed
by the displayed packet. No downstream clause reads a host subset iterator, a
host colouring function, or an ambient graph object outside those packet rows.
\end{theorem}
\begin{proof}
First project the witness to the finite packet of
\autoref{def:ramsey-monochrome-witness-carrier}. This gives the vertex spine,
subset spine, colour endpoint rows, chosen witness subset, component
$\hsame$ transports, finite lookup routes, and shared provenance as explicit
$\mathsf{BHist}$ rows.

Next apply \autoref{thm:ramsey-colouring-carrier-obligation}. It identifies
the accepted colouring surface with the same finite packet, so every colour
read used by the witness is routed through a displayed $\Cont$ lookup rather
than through a host colouring function.

The witness classifier is stable under the transported rows by
\autoref{thm:ramsey-monochrome-classifier-stability}. The finite ledger
exactness theorem then says that the readable rows are exactly the displayed
carrier, lookup, transport, and provenance rows, with any finset or graph
consumer receiving only the corresponding $\NameCert_{\FinSetUp}$ or
$\NameCert_{\GraphUp}$ projection.

Thus the downstream witness has no remaining coordinate from which a host
subset iterator, host colouring function, or ambient graph object could be
read.
\end{proof}

\begin{theorem}[Ramsey finite ledger exactness]
\label{thm:ramsey-finite-ledger-exactness}
For every accepted $\RamseyUp$ colouring row, the readable ledger consists
exactly of the $\FinSetUp$ vertex spine, the finite $r$-subset spine, the
colour endpoint table, the displayed monochrome witness subset rows, the
component $\hsame$ transports, the finite $\Cont$ lookup routes, and the
shared $\Pkg$ provenance. It exposes no host finite-set enumeration, host
subset iterator, off-ledger colour function, or graph object beyond the
displayed dependency rows.
\end{theorem}
\leanchecked{BEDC.Derived.RamseyUp.RamseyColouringCarrier\_finite\_ledger\_exactness}
\begin{proof}
Use \autoref{thm:ramsey-colouring-carrier-obligation} to reduce any consumer
read to the carrier packet. Each listed ledger row is a coordinate of that
packet or a finite lookup route attached to it.

For the reverse containment, inspect the carrier surface: every vertex,
subset, colour, witness, transport, lookup, and provenance row appears in the
finite ledger. The packet has no constructor for host enumeration, host subset
iteration, or off-ledger colouring functions.

If a graph consumer is present, it can only receive the dependency rows already
certified by $\NameCert_{\GraphUp}$ and the displayed finite ledger. No extra
graph object is generated by the Ramsey ledger itself.
\end{proof}

\begin{theorem}[Ramsey NameCert obligation assembly]
\label{thm:ramsey-namecert-obligation-assembly}
The public $\NameCert_{\RamseyUp}$ obligation surface is assembled from the
finite colouring carrier of
\autoref{thm:ramsey-colouring-carrier-obligation}, the monochrome-subset
classifier stability of
\autoref{thm:ramsey-monochrome-classifier-stability}, the ledger exactness of
\autoref{thm:ramsey-finite-ledger-exactness}, and the dependency certificates
$\NameCert_{\FinSetUp}$ and $\NameCert_{\GraphUp}$ when graph-shaped consumers
read the same finite rows. The assembled surface binds carrier, classifier,
stability, exactness, and source coverage over $\mathsf{BHist}$, $\hsame$,
$\Cont$, and $\Pkg$.

No clause of the assembled surface treats host finite-set enumeration, host
function equality, or an ambient graph object as a primitive.
\end{theorem}
\begin{proof}
Use the carried colouring row as the source predicate. Its finite vertex
spine, subset spine, colour table, lookup routes, and provenance are exactly
the carrier rows isolated in
\autoref{thm:ramsey-colouring-carrier-obligation}.

Use the monochrome-subset classifier as the comparison predicate. Stability
under transported vertex, subset, colour, route, and provenance rows is
precisely \autoref{thm:ramsey-monochrome-classifier-stability}.

The exactness and source-coverage clauses are supplied by
\autoref{thm:ramsey-finite-ledger-exactness}. The $\FinSetUp$ dependency
accounts for all finite spines, and the $\GraphUp$ dependency is only a
consumer boundary for graph-shaped readings of those rows, so the assembled
certificate remains a finite $\mathsf{BHist}$ ledger.
\end{proof}

\begin{theorem}[Ramsey downstream boundary]
\label{thm:ramsey-downstream-boundary}
Every graph, finset, or combinatorial consumer of the $\RamseyUp$ surface reads
only the assembled $\NameCert_{\RamseyUp}$ rows of
\autoref{thm:ramsey-namecert-obligation-assembly}: the displayed
$\FinSetUp$ vertex spine, the finite subset spine, the colour endpoint table,
the monochrome witness rows, the $\hsame$ transports, the finite $\Cont$
lookup routes, and the shared $\Pkg$ provenance. A consumer may project these
rows into $\NameCert_{\GraphUp}$ or $\NameCert_{\FinSetUp}$ interfaces, but it
cannot read a host finite-set enumeration, host subset iterator, host colouring
function, or graph equality primitive from $\RamseyUp$ itself.
\end{theorem}
\begin{proof}
First reduce the consumer read to the assembled certificate surface by
\autoref{thm:ramsey-namecert-obligation-assembly}. This fixes the carrier,
classifier, stability, ledger, and source-coverage rows over the finite
$\mathsf{BHist}$ packet.

For a finset consumer, project the vertex and subset spines through
$\NameCert_{\FinSetUp}$. The projection preserves the displayed $\hsame$
transports and finite lookup routes, and it does not expose a host
enumeration.

For a graph-shaped consumer, use $\NameCert_{\GraphUp}$ only on rows already
present in the finite ledger. The graph interface receives carried vertex,
edge, or incidence rows as projections, while the Ramsey table and witness
remain the same $\Cont$-routed finite packet.

Thus every downstream boundary is a projection of the public Ramsey ledger,
not an additional primitive surface.
\end{proof}
