\chapter{A Concrete Naming Certificate for $\RegularCauchyProductUp$}
\label{ch:concrete-instances-regularcauchyproduct-namecert}
\origin{human}

The $\RegularCauchyProductUp$ interface names the finite pointwise Cauchy-product surface for two regular rational Cauchy names. Bishop-Bridges constructive real arithmetic uses Cauchy products to make multiplication of regular real names visible. BEDC records the finite packet version: two regular source rows, aligned stream windows, dyadic endpoint multiplication, a product-error ledger, regular rational readback, componentwise transport, continuation routes, package provenance, and a local naming row.

The packet sits beside $\RegularCauchySumUp$ and $\RegularCauchyDifferenceUp$. It is not a completed-real multiplication law, not a quotient of Cauchy streams, not a selected host limit, and not an ambient completeness theorem.

\begin{definition}[RegularCauchyProduct carrier]
\label{def:regular-cauchy-product-carrier}
A $\RegularCauchyProductUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
M=(A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two $\RegSeqRatUp$ source rows whose scheduled rational observations are multiplied pointwise;
\item $W_A$ and $W_B$ are aligned $\StreamNameUp$ windows for a shared precision request and a shared unary observation index;
\item $D_A$ and $D_B$ are the $\DyadicRatCoreUp$ endpoint rows read from those windows;
\item $D$ is the displayed $\DyadicRatCoreUp$ multiplication row obtained from the common-exponent product window for $D_A \cdot D_B$;
\item $E$ is the finite $\FiniteErrorBudgetUp$ product ledger recording the two input tolerances, endpoint magnitude bounds, cross-error terms, and the output tolerance assigned to $D$;
\item $R$ is the $\RegSeqRatUp$ readback row whose scheduled point row is $D$ with the tolerance budget recorded by $E$;
\item $H$ stores componentwise $\hsame$ transports for both source names, both stream windows, the three dyadic endpoint rows, the product-error ledger, and the readback row;
\item $C$ stores the displayed $\Cont$ routes for reading the two input windows, forming the dyadic endpoint multiplication row, checking the product budget, and exposing the readback;
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\FiniteErrorBudgetUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RegularCauchyProductUp}$ row.
\end{enumerate}
The carrier is a finite multiplication certificate for regular Cauchy names. It stores no quotient stream, no selected limit, no host real equality, and no ambient completeness object.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RegularCauchyProduct NameCert obligations]
\label{thm:regular-cauchy-product-namecert-obligations}
The local $\NameCert_{\RegularCauchyProductUp}$ surface for the carrier of \autoref{def:regular-cauchy-product-carrier} consists of five finite obligations:
\begin{enumerate}
\item carrier admission: the accepted object is the displayed $\mathsf{BHist}$ packet $M$ with two $\RegSeqRatUp$ sources, aligned $\StreamNameUp$ windows, dyadic endpoint rows, a product-error ledger, transport rows, continuation rows, provenance, and local naming data;
\item classifier transport: classification transports the two source rows, the aligned windows, the endpoint multiplication row, the finite product-error ledger, and the readback row componentwise through the stored $\hsame$ and $\Cont$ rows;
\item stability: replacing either source by a classified regular name preserves the aligned window and recomputes the same kind of displayed dyadic multiplication row;
\item ledger exactness: the output tolerance row is the finite product-error budget recorded in $E$, including the two input tolerances and the displayed endpoint magnitude bounds;
\item downstream handoff: every $\RegSeqRatUp$ or $\RealUp$ consumer of the product first reads $R$ together with $A$, $B$, $W_A$, $W_B$, $D_A$, $D_B$, $D$, $E$, $H$, $C$, $P$, and $N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from the tuple in \autoref{def:regular-cauchy-product-carrier}. Each source row, window row, endpoint row, budget row, transport route, continuation route, provenance row, and local naming row is an explicit coordinate of $M$.

Classifier transport is componentwise. The two $\RegSeqRatUp$ source rows transport their scheduled rational observations, the $\StreamNameUp$ rows transport the aligned window reads, and the $\DyadicRatCoreUp$ rows transport the endpoint multiplication calculation at the common exponent.

The budget row is finite. It records the two input tolerances, the endpoint magnitude bounds used in the product estimate, the cross-error terms, and the output tolerance before the product readback is exposed. The downstream handoff is then the readback row $R$, and no omitted coordinate can add quotient streams, selected limits, host real equality, or ambient completeness.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_namecert\_obligations}

\begin{theorem}[RegularCauchyProduct window budget]
\label{thm:regular-cauchy-product-window-budget}
Given accepted $\RegSeqRatUp$ source rows $A$ and $B$ in a $\RegularCauchyProductUp$ packet and a shared precision request, the aligned $\StreamNameUp$ windows $W_A$ and $W_B$ display dyadic endpoint rows $D_A$ and $D_B$. The packet displays a $\DyadicRatCoreUp$ row $D$ for $D_A \cdot D_B$ and a finite ledger $E$ whose output tolerance is the recorded product-error budget for the two source tolerances and endpoint magnitude bounds.
\end{theorem}
\begin{proof}
Read the shared precision request through the two stream windows. Since $W_A$ and $W_B$ are aligned coordinates of the same packet, they expose the two endpoint rows at the same requested observation index.

Apply the displayed common-exponent multiplication row of $\DyadicRatCoreUp$ to $D_A$ and $D_B$. The result is the endpoint row $D$, still inside the carrier.

Finally read the finite budget ledger $E$. Its entries record the two input tolerances, the visible endpoint bounds, and the product-error terms assigned to the output request. This proves the window budget without invoking any completed real, quotient stream, or hidden limit.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_window\_budget}

\begin{theorem}[RegularCauchyProduct RegSeqRat handoff]
\label{thm:regular-cauchy-product-regseqrat-handoff}
The budgeted pointwise-product windows of \autoref{thm:regular-cauchy-product-window-budget} repack as the $\RegSeqRatUp$ readback row $R$ of \autoref{def:regular-cauchy-product-carrier}. A consumer of $R$ reads only the aligned input windows, the dyadic endpoint multiplication row, the finite product-error ledger, the displayed $\hsame$ transports, the $\Cont$ routes, the $\Pkg$ provenance, and the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Start with the finite window budget. For each requested precision, the packet exposes the two source endpoint rows, the dyadic product endpoint, and the product-error row that bounds the output tolerance.

Repack those displayed rows as a regular rational sequence readback. The point row of $R$ is $D$, and the regularity evidence visible to the consumer is the product ledger $E$ routed through the same aligned windows.

The transport and continuation rows are inherited from the carrier. Since the repacking uses only coordinates already listed in \autoref{def:regular-cauchy-product-carrier}, it introduces no host sequence quotient, selected limit, or completed-real multiplication object.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_regseqrat\_handoff}

\begin{theorem}[RegularCauchyProduct RealUp seal boundary]
\label{thm:regular-cauchy-product-real-seal-boundary}
Any $\RealUp$ consumer of an accepted $\RegularCauchyProductUp$ packet reads only the $\RegSeqRatUp$ readback row $R$ together with the visible provenance of the two source names, aligned windows, dyadic endpoint multiplication row, finite product-error ledger, $\hsame$ transports, $\Cont$ routes, $\Pkg$ row, and local $\NameCert_{\RegularCauchyProductUp}$ row.
\end{theorem}
\begin{proof}
Factor the real-facing read through the regular readback. By \autoref{thm:regular-cauchy-product-regseqrat-handoff}, $R$ is already the repacking of the budgeted pointwise-product windows.

The remaining consumer-visible data are exactly the provenance rows attached to that repacking: the two source names, aligned schedules, dyadic product endpoints, product-error ledger, transports, continuations, package row, and local naming row.

The carrier has no independent $\RealUp$ equality field and no completion witness outside the readback. Therefore the real seal can consume only the displayed regular readback and its visible provenance.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_real\_seal\_boundary}

\begin{theorem}[RegularCauchyProduct source-window transport]
\label{thm:regular-cauchy-product-source-window-transport}
For an accepted $\RegularCauchyProductUp$ packet $M=(A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N)$, classifier transport preserves the two $\RegSeqRatUp$ source rows $A,B$ and the aligned $\StreamNameUp$ windows $W_A,W_B$ through the displayed $\hsame$ and $\Cont$ routes. Consequently any transported packet reads the same two regular sources and the same aligned source windows before forming the dyadic product row.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_source\_window\_transport}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-product-carrier}. The two source rows and the two aligned stream windows are explicit coordinates of the same finite packet.

Apply the classifier-transport obligation of \autoref{thm:regular-cauchy-product-namecert-obligations}. It transports the source rows and aligned windows componentwise through the stored $\hsame$ and $\Cont$ rows.

The product endpoint rows $D_A,D_B,D$ are downstream of these transported windows. Since the transport first fixes $A,B,W_A,W_B$, the dyadic product row can only be read after the same two source rows and the same aligned window positions have been displayed.
\end{proof}

\begin{theorem}[RegularCauchyProduct error-budget exactness]
\label{thm:regular-cauchy-product-error-budget-exactness}
For an accepted $\RegularCauchyProductUp$ packet, the output tolerance assigned to the readback row $R$ is exactly the finite product-error ledger $E$ computed from the two input tolerances, the endpoint magnitude bounds for $D_A$ and $D_B$, and the cross-error terms recorded in the packet. No additional tolerance rule is read from a quotient stream, a selected limit, or a completed real multiplication object.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_error\_budget\_exactness}
\begin{proof}
Use the window budget theorem \autoref{thm:regular-cauchy-product-window-budget}. It displays $D_A$ and $D_B$ from the aligned source windows and forms the dyadic endpoint product row $D$.

Read the ledger row $E$. By the NameCert obligations, $E$ records the two input tolerances, the endpoint magnitude bounds, the cross-error terms, and the output tolerance before $R$ is exposed.

Apply the $\RegSeqRatUp$ handoff of \autoref{thm:regular-cauchy-product-regseqrat-handoff}. The readback row $R$ is repacked from $D$ with the tolerance budget already recorded in $E$, so the output tolerance is exactly that finite ledger and nothing outside the displayed packet.
\end{proof}

\begin{theorem}[RegularCauchyProduct downstream source lock]
\label{thm:regular-cauchy-product-downstream-source-lock}
Every downstream $\RegSeqRatUp$ or $\RealUp$ consumer of an accepted $\RegularCauchyProductUp$ packet factors through
$$
(A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N).
$$
Such a consumer can read the two source rows, aligned windows, dyadic endpoint rows, finite product-error ledger, regular readback, transport rows, continuation routes, package provenance, and local naming row, but cannot read quotient streams, selected limits, host real equality, or completed real multiplication.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_downstream\_source\_lock}
\begin{proof}
Start with the regular handoff. By \autoref{thm:regular-cauchy-product-regseqrat-handoff}, every $\RegSeqRatUp$ readback factors through the aligned input windows, dyadic endpoint multiplication row, finite product-error ledger, transports, continuations, package row, and local naming row.

Use \autoref{thm:regular-cauchy-product-source-window-transport} to lock the source rows. The aligned windows available to any transported consumer are still the windows attached to $A$ and $B$.

Finally apply the RealUp seal boundary of \autoref{thm:regular-cauchy-product-real-seal-boundary}. A real-facing consumer reads only the regular readback and its visible provenance, so neither a quotient stream nor a selected limit nor host real equality nor completed multiplication can enter downstream.
\end{proof}

\begin{theorem}[RegularCauchyProduct public export certificate]
\label{thm:regular-cauchy-product-public-export-certificate}
The carrier, local $\NameCert$ obligations, window budget, $\RegSeqRatUp$ handoff, $\RealUp$ seal boundary, source-window transport, error-budget exactness, and downstream source lock assemble into one public $\RegularCauchyProductUp$ export packet. Its exported rows are exactly
$$
A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N.
$$
The packet exports no quotient stream, selected limit, host real equality, ambient completeness witness, or completed-real multiplication law.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_public\_export\_certificate}
\begin{proof}
Start with the displayed carrier of \autoref{def:regular-cauchy-product-carrier}. It supplies exactly the two regular source rows, two aligned source-window rows, dyadic endpoint rows, product row, finite error ledger, regular readback, transports, continuations, provenance, and local name.

Add the local acceptance and budget rows. The $\NameCert$ obligations of \autoref{thm:regular-cauchy-product-namecert-obligations} bind the accepted packet, while \autoref{thm:regular-cauchy-product-window-budget} computes the endpoint and product rows from the aligned windows.

Next expose the two consumer boundaries. The $\RegSeqRatUp$ handoff is supplied by \autoref{thm:regular-cauchy-product-regseqrat-handoff}, and the $\RealUp$ seal boundary is supplied by \autoref{thm:regular-cauchy-product-real-seal-boundary}.

Finally use \autoref{thm:regular-cauchy-product-source-window-transport}, \autoref{thm:regular-cauchy-product-error-budget-exactness}, and \autoref{thm:regular-cauchy-product-downstream-source-lock}. These results keep every downstream read on the displayed source windows and finite error ledger, and they exclude quotient streams, selected limits, host real equality, ambient completeness, and completed-real multiplication from the public export.
\end{proof}

\begin{theorem}[RegularCauchyProduct real algebra boundary]
\label{thm:regular-cauchy-product-real-algebra-boundary}
Every downstream $\RealUp$ algebra consumer of an accepted $\RegularCauchyProductUp$ packet
$$
M=(A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N)
$$
must read the source-window rows $A,B,W_A,W_B$, the finite error-budget ledger $E$, the $\RegSeqRatUp$ handoff row $R$, the $\DyadicRatCoreUp$ observations $D_A,D_B,D$, the $\RealUp$ seal boundary, the displayed $\hsame$ transports $H$, the finite $\Cont$ routes $C$, the $\Pkg$ provenance $P$, and the local $\NameCert_{\RegularCauchyProductUp}$ row $N$. It receives no quotient stream, host multiplication over completed reals, selected limit, ambient completeness, or unlisted algebra law.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_real\_algebra\_boundary}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:regular-cauchy-product-namecert-obligations}. They admit only the displayed packet $M$ and force every accepted read through the two source rows, aligned windows, endpoint rows, product ledger, transports, routes, provenance, and local name.

Apply the window budget theorem \autoref{thm:regular-cauchy-product-window-budget}. It builds the dyadic product row from the two source windows and records the product tolerance in the finite ledger $E$ before any downstream algebra consumer sees the readback.

Next use the $\RegSeqRatUp$ handoff \autoref{thm:regular-cauchy-product-regseqrat-handoff} together with the $\RealUp$ seal boundary \autoref{thm:regular-cauchy-product-real-seal-boundary}. The real-facing route is the regular readback $R$ with its visible product provenance, not a host multiplication operation over completed reals.

Finally combine error-budget exactness, downstream source lock, and the public export certificate. These results exhaust the consumer-visible rows and exclude quotient streams, selected limits, ambient completeness, host real equality, completed-real multiplication, and unlisted algebra laws from the product boundary.
\end{proof}

\begin{theorem}[RegularCauchyProduct bounded-source handoff]
\label{thm:regular-cauchy-product-bounded-source-handoff}
Let
$$
M=(A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N)
$$
be an accepted $\RegularCauchyProductUp$ packet. If the two source windows
$W_A$ and $W_B$ expose dyadic endpoint magnitude bounds in the finite
product-error ledger $E$, then every $\RegSeqRatUp$ readback of the product
factors through $W_A,W_B$, the dyadic product row $D$, and the same ledger row
$E$. No readback may replace those bounded windows by a quotient stream,
selected limit, host real equality, ambient completeness, or completed-real
multiplication law.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_bounded\_source\_handoff}
\begin{proof}
Start with \autoref{thm:regular-cauchy-product-window-budget}. The product
row $D$ is computed from the displayed source windows and the dyadic endpoint
rows, and the product tolerance is recorded in the finite ledger $E$.

Use \autoref{thm:regular-cauchy-product-source-window-transport}. Transported
consumers still see the windows attached to the source rows $A$ and $B$, so
the endpoint magnitude bounds remain the bounds supplied by $W_A$ and $W_B$.

Apply \autoref{thm:regular-cauchy-product-error-budget-exactness}. The error
budget exposed to a readback is exactly the displayed product ledger, with no
additional completed-real algebra coordinate.

Finally use \autoref{thm:regular-cauchy-product-downstream-source-lock}. Any
downstream $\RegSeqRatUp$ handoff must keep the same source windows, dyadic
product row, and ledger row $E$, which gives the stated bounded-source
factorization.
\end{proof}

\begin{theorem}[RegularCauchyProduct real seal product budget]
\label{thm:regular-cauchy-product-real-seal-product-budget}
Every $\RealUp$ algebra consumer of the product seal in an accepted
$\RegularCauchyProductUp$ packet receives the finite product-budget row $E$
before the $\RegSeqRatUp$ handoff row $R$. The consumer cannot replace this
budget by completed-real multiplication, quotient stream equality, selected
limits, ambient completeness, host real equality, or any unlisted algebra law.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_real\_seal\_product\_budget}
\begin{proof}
First apply \autoref{thm:regular-cauchy-product-real-seal-boundary}. The
real-facing endpoint is read through the visible product provenance and
regular readback route, not through completed-real multiplication.

Next use \autoref{thm:regular-cauchy-product-real-algebra-boundary}. A
$\RealUp$ algebra consumer must read the finite error ledger $E$, the
$\RegSeqRatUp$ handoff $R$, the dyadic product row, transports, continuations,
provenance, and local name.

The public export certificate
\autoref{thm:regular-cauchy-product-public-export-certificate} supplies the
same row order at the public surface. The packet contains the product ledger
and readback row, but no quotient stream, selected limit, ambient
completeness, or host real equality.

Finally invoke
\autoref{thm:regular-cauchy-product-bounded-source-handoff}. Since every
readback factors through the bounded source windows, dyadic product row, and
ledger $E$, the real seal consumer receives the finite product budget before
it can consume the regular rational handoff.
\end{proof}

\begin{theorem}[RegularCauchyProduct window comparison]
\label{thm:regular-cauchy-product-window-comparison}
Let $M$ be an accepted $\RegularCauchyProductUp$ packet, let $S$ be an accepted $\RegularCauchySumUp$ packet, and let $Q$ be an accepted $\RegularCauchyDifferenceUp$ packet. Suppose the three packets share the same two $\RegSeqRatUp$ source rows $A,B$ and the same aligned $\StreamNameUp$ source windows $W_A,W_B$. Then every product consumer must first read the common finite boundary
$$
(A,B,W_A,W_B)
$$
before diverging to the product-error ledger $E$ of $M$, while the sum and difference consumers diverge from that same boundary to their own finite arithmetic ledgers. The conclusion is a comparison of finite-window routes; it is not a completed-real algebra law.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_window\_comparison}
\begin{proof}
Start with the product carrier of \autoref{def:regular-cauchy-product-carrier}. Its first four rows are the two regular source rows and the two aligned source-window rows, so any product read must expose $A,B,W_A,W_B$ before it reaches dyadic endpoint multiplication or the product ledger.

Use the source-window transport theorem \autoref{thm:regular-cauchy-product-source-window-transport}. Transport preserves the same source rows and aligned windows through the displayed $\hsame$ and $\Cont$ routes, so the shared boundary remains the first visible route segment for every transported product consumer.

Now apply the real algebra boundary and product-budget results, \autoref{thm:regular-cauchy-product-real-algebra-boundary} and \autoref{thm:regular-cauchy-product-real-seal-product-budget}. They force the product route to diverge from the shared source-window boundary into the finite product-error ledger $E$ before the $\RegSeqRatUp$ handoff and $\RealUp$ seal are consumed.

Finally compare the sibling surfaces \autoref{ch:concrete-instances-regularcauchysum-namecert} and \autoref{ch:concrete-instances-regularcauchydifference-namecert}. Their accepted packets read the same kind of finite source-window boundary for the same two source rows, but their next arithmetic coordinates are the finite sum and difference ledgers rather than $E$. Thus the comparison is a route comparison over shared windows and sibling ledgers, with no quotient stream, selected limit, host real equality, ambient completeness, or field multiplication law.
\end{proof}

\begin{theorem}[RegularCauchyProduct coordinate regularity]
\label{thm:regular-cauchy-product-coordinate-regularity}
For every accepted $\RegularCauchyProductUp$ packet
$$
M=(A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N),
$$
the readback row $R$ is regular by finite coordinates alone. Each requested product endpoint row $D$ is obtained from the aligned $\StreamNameUp$ windows $W_A,W_B$, and the ledger $E$ records the two source tolerances, the endpoint magnitude bounds for $D_A,D_B$, and the cross-error terms needed for the output tolerance. Thus the regularity of $R$ is witnessed by the carrier coordinates, the local $\NameCert$ obligations, the window budget, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal boundary, source-window transport, error-budget exactness, and downstream source lock, with no appeal to a quotient stream, selected limit, host real equality, ambient completeness, or completed-real multiplication.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_coordinate\_regularity}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-product-carrier}. The coordinates $A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N$ include the two regular sources, the aligned windows, the dyadic endpoint rows, the product row, and the finite budget ledger.

Use the local $\NameCert$ obligations and the window budget theorem, \autoref{thm:regular-cauchy-product-namecert-obligations} and \autoref{thm:regular-cauchy-product-window-budget}. They force each requested product endpoint to be read from the aligned $\StreamNameUp$ windows and place the two source tolerances, endpoint bounds, and cross-error terms in $E$.

Apply the $\RegSeqRatUp$ handoff and the $\RealUp$ seal boundary, \autoref{thm:regular-cauchy-product-regseqrat-handoff} and \autoref{thm:regular-cauchy-product-real-seal-boundary}. The row $R$ is the regular rational readback of these finite product windows, while the real-facing boundary exposes only the same finite provenance.

Finally use source-window transport, error-budget exactness, and downstream source lock. These keep every transported consumer on the displayed windows and ledger, so the regularity witness for $R$ is the finite product-coordinate route itself.
\end{proof}

\begin{theorem}[RegularCauchyProduct classifier stability]
\label{thm:regular-cauchy-product-classifier-stability}
Let
$$
M=(A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N)
$$
be an accepted $\RegularCauchyProductUp$ packet. Classifier transport of either source row preserves the aligned source windows, the dyadic endpoint product row, the finite error ledger, and the readback route through the stored $\hsame$ and $\Cont$ coordinates. Consequently replacing $A$ or $B$ by a classified regular source does not change the finite product boundary read by $R$; it only replays the carrier, $\NameCert$ obligations, window budget, $\RegSeqRatUp$ handoff, $\RealUp$ seal boundary, source-window transport, error-budget exactness, and downstream source lock along the displayed transport rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_classifier\_stability}
\begin{proof}
Start from the classifier-transport clause in \autoref{thm:regular-cauchy-product-namecert-obligations}. It transports the two source rows, aligned windows, endpoint rows, finite product-error ledger, and readback row componentwise through the stored $\hsame$ and $\Cont$ coordinates.

Use \autoref{thm:regular-cauchy-product-source-window-transport}. Transported packets still display the same source-window boundary $A,B,W_A,W_B$ before any dyadic endpoint product row can be consumed.

Next apply the window budget and error-budget exactness results. The product row $D$ and ledger $E$ remain the rows obtained from the transported aligned windows, and the output tolerance is still exactly the displayed product ledger.

Finally combine the $\RegSeqRatUp$ handoff, $\RealUp$ seal boundary, and downstream source lock. They force the transported readback to consume the same finite product boundary, so classifier stability is a stability claim about the displayed coordinates rather than a completed-real algebra law.
\end{proof}

\begin{theorem}[RegularCauchyProduct RealUp pair seal]
\label{thm:regular-cauchy-product-real-pair-seal}
Every $\RealUp$ consumer of a product pair sealed by an accepted $\RegularCauchyProductUp$ packet can read only the two source regular names $A,B$, the regular readback row $R$, and the finite product provenance carried by $W_A,W_B,D_A,D_B,D,E,H,C,P,N$. The seal exposes the carrier, $\NameCert$ obligations, window budget, $\RegSeqRatUp$ handoff, $\RealUp$ seal boundary, source-window transport, error-budget exactness, and downstream source lock, but it does not expose host real multiplication, a quotient stream, a selected limit, an ambient completeness witness, or any extra algebra law.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyProductUp.RegularCauchyProductCarrier\_real\_pair\_seal}
\begin{proof}
Begin with the carrier and local $\NameCert$ obligations. The accepted packet contains exactly the two source rows, aligned windows, dyadic endpoint rows, product ledger, readback, transports, continuations, package provenance, and local name.

Apply the window budget and $\RegSeqRatUp$ handoff. They show that the product readback $R$ is assembled from the finite endpoint rows and product-error ledger, so the consumer reads a regular rational product route rather than a completed-real multiplication operation.

Use the $\RealUp$ seal boundary together with source-window transport. The real-facing consumer sees the same two source names and aligned windows after transport, and no additional real-valued coordinate is introduced.

Finally invoke error-budget exactness and downstream source lock. They exhaust the visible product provenance and rule out quotient streams, selected limits, host real equality, ambient completeness witnesses, host multiplication, and unlisted algebra laws at the pair seal.
\end{proof}

\closureat{RegularCauchyProductUp}{seedStr}
\closureat{RegularCauchyProductUp}{obligationStr}
\closureat{RegularCauchyProductUp}{scopedStr}
\closureat{RegularCauchyProductUp}{publicStr}

\begin{closurestatus}{\RegularCauchyProductUp}
  \constructivestory{A $\RegularCauchyProductUp$ packet is generated from two $\RegSeqRatUp$ source rows, aligned $\StreamNameUp$ windows, $\DyadicRatCoreUp$ endpoint multiplication rows, a finite $\FiniteErrorBudgetUp$ product ledger, displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, a $\RegSeqRatUp$ readback row, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{The scoped public surface records the finite carrier, local naming obligations, shared-window product budget, regular readback handoff, real-seal boundary, source-window transport, error-budget exactness, downstream source lock, and public export certificate for pointwise products of regular Cauchy names.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient equality of streams, selected limits, host real equality, ambient completeness, real-field multiplication laws, or bridge checking.}
  \upgradepath{Bridge closure requires a standard bridge from the public regular-Cauchy product boundary to downstream real-algebra consumer interfaces.}
\end{closurestatus}
