\chapter{A Concrete Naming Certificate for $\UniformLimitUp$}
\label{ch:concrete-instances-uniformlimit-namecert}
\origin{human}

The $\UniformLimitUp$ interface names the constructive-analysis packet for a uniformly convergent family of displayed real-valued windows. Following Bishop--Bridges constructive analysis, the limiting object is read through a uniform tail ledger, a regular rational handoff, and a visible $\CauchyLimitSealUp$ row. The packet does not select a host function limit, quotient a function space, or appeal to ambient completeness of $\RealUp$.

The endpoint row is available only after the packet consumes the $\StreamNameUp$ finite-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the $\UniformCauchyCriterionUp$ tail ledger of \autoref{ch:concrete-instances-uniformcauchycriterion-namecert}, the $\RegSeqRatUp$ handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and the $\CauchyLimitSealUp$ seal row of \autoref{ch:concrete-instances-cauchylimitseal-namecert}. Thus the endpoint is a routed finite seal read, not a host-selected limit.

\begin{definition}[UniformLimit carrier]
\label{def:uniform-limit-carrier}
A $\UniformLimitUp$ carrier is a finite $\BHist$ packet
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $F$ is the displayed function/window family, read only through finite $\StreamNameUp$ windows and $\RealUp$ endpoint rows;
\item $M$ is the shared modulus ledger assigning each requested tolerance to one family-wide window threshold;
\item $T$ is the $\UniformCauchyCriterionUp$ tail ledger that records the accepted comparisons beyond the threshold selected by $M$;
\item $R$ is the $\RegSeqRatUp$ handoff row obtained from the same windows and tail ledger;
\item $S$ is the $\CauchyLimitSealUp$ seal row attached to the regular handoff;
\item $E$ is the exposed $\RealUp$ endpoint row read after the seal row;
\item $H$ stores componentwise $\hsame$ transports for the function/window family, modulus ledger, uniform tail ledger, regular handoff, limit seal, endpoint row, package provenance, and local naming row;
\item $C$ stores the displayed $\Cont$ routes for reading the windows, applying the shared threshold, consuming the uniform tail ledger, reaching the regular handoff, and exposing the seal endpoint;
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\UniformCauchyCriterionUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\UniformLimitUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows, their displayed transports, their continuation routes, package provenance, and local naming provenance.
\end{definition}

\begin{theorem}[UniformLimit NameCert obligations]
\label{thm:uniform-limit-namecert-obligations}
For the carrier of \autoref{def:uniform-limit-carrier}, the local $\NameCert_{\UniformLimitUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the packet $U=(F,M,T,R,S,E,H,C,P,N)$;
\item classifier transport by componentwise $\hsame$ over the function/window family, modulus ledger, tail ledger, regular handoff, seal row, and endpoint row;
\item uniform-tail exactness, requiring each endpoint-facing read to pass through the same threshold row $M$ and the $\UniformCauchyCriterionUp$ ledger $T$;
\item regular-seal routing, requiring every limit-facing read to pass from $F,M,T$ through $R$ and $S$ before reaching $E$;
\item non-escape from pointwise convergence without a uniform ledger, open-cover compactness, selected host limits, quotient function spaces, and $\RealUp$ completeness.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is projection from \autoref{def:uniform-limit-carrier}. The displayed coordinates name the family windows, shared modulus, uniform tail ledger, regular handoff, seal row, endpoint row, transports, continuations, package provenance, and local certificate.

Classifier transport is componentwise. The rows in $H$ move each named coordinate, and the routes in $C$ replay the same consumer order, so a transported packet remains inside the displayed carrier surface.

For exactness, inspect a requested tolerance. The consumer route first reads $M$, then reads the corresponding comparisons in $T$, and only then reaches the regular handoff and seal rows. The packet inventory contains no coordinate for pointwise-only convergence, open-cover compactness, selected host limits, quotient function spaces, or real completeness.
\end{proof}

\begin{theorem}[UniformLimit seal factorization]
\label{thm:uniform-limit-seal-factorization}
Every $\RealUp$ endpoint read exported by an accepted $\UniformLimitUp$ carrier factors through the finite route
$$
F,M,T \longmapsto R \longmapsto S \longmapsto E.
$$
Thus the endpoint is exposed only after the displayed function/window family has been read through the shared threshold ledger, the $\UniformCauchyCriterionUp$ tail row, the $\RegSeqRatUp$ handoff, and the $\CauchyLimitSealUp$ row, together with the visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_seal\_factorization}
\begin{proof}
Begin with an endpoint-facing consumer request. By the carrier definition, the only $\RealUp$ endpoint coordinate is $E$, and the continuation route to $E$ passes through the named rows of the same finite packet.

Read the family windows through $F$ and the shared threshold through $M$. The uniform comparisons are then supplied by $T$, so the request has not used an indexwise or pointwise-only convergence witness.

Next consume the regular rational handoff $R$ and the limit seal $S$. These rows mediate the passage from the uniform tail ledger to the endpoint row, while $H,C,P,N$ record the transport, route, package, and naming provenance. Hence every endpoint read has the stated factorization.
\end{proof}

\begin{theorem}[UniformLimit non-escape boundary]
\label{thm:uniform-limit-non-escape-boundary}
An accepted $\UniformLimitUp$ carrier exports only the displayed function/window family, shared modulus ledger, $\UniformCauchyCriterionUp$ tail ledger, $\RegSeqRatUp$ handoff, $\CauchyLimitSealUp$ seal row, $\RealUp$ endpoint, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of \autoref{def:uniform-limit-carrier}. It exports no pointwise convergence object lacking the uniform ledger, no open-cover compactness principle, no selected host limit, no quotient function space, and no completeness theorem for $\RealUp$.
\end{theorem}
\begin{proof}
Inspect the packet coordinates. Every listed row is a finite display, transport, continuation, provenance, or local naming row, and the only endpoint coordinate is the seal-facing row $E$.

Apply \autoref{thm:uniform-limit-namecert-obligations}. Uniform-tail exactness keeps each read inside $F,M,T$, and regular-seal routing forces the route through $R$ and $S$ before $E$ is exposed.

The excluded analytic objects would require additional carrier coordinates or a different consumer route. Since neither is present, the public surface is exhausted by the finite BEDC rows listed in the statement.
\end{proof}

\begin{theorem}[UniformLimit finite endpoint certificate]
\label{thm:uniform-limit-finite-endpoint-certificate}
The carrier, local $\NameCert$ obligations, seal factorization, and non-escape boundary assemble a finite endpoint certificate for $\UniformLimitUp$ over $\StreamNameUp$, $\UniformCauchyCriterionUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Every downstream completion or real-consumer read is confined to that packet and its factorization route.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:uniform-limit-carrier}. It supplies exactly the function/window family, shared modulus, uniform tail ledger, regular handoff, seal row, endpoint row, transports, continuations, package provenance, and local certificate.

Use \autoref{thm:uniform-limit-namecert-obligations} to obtain carrier admission, classifier transport, uniform-tail exactness, regular-seal routing, and the non-escape clauses. Then use \autoref{thm:uniform-limit-seal-factorization} to identify the endpoint route.

Finally apply \autoref{thm:uniform-limit-non-escape-boundary}. The route has no coordinate outside the listed BEDC rows, so the finite endpoint certificate is the whole downstream consumer surface.
\end{proof}

\begin{theorem}[UniformLimit windowwise Cauchy obligation]
\label{thm:uniform-limit-windowwise-cauchy-obligation}
Every endpoint-facing read of an accepted $\UniformLimitUp$ carrier must pass through the shared threshold ledger $M$ and the $\UniformCauchyCriterionUp$ tail row $T$ before it reaches the $\RegSeqRatUp$ handoff. Thus the read is windowwise uniform: no endpoint row may be obtained from a pointwise-only convergence witness or from a window threshold selected outside the packet.
\end{theorem}
\begin{proof}
Project the route inventory from \autoref{def:uniform-limit-carrier}. The only endpoint-facing continuation route reads the family windows through $F$, then the shared threshold ledger $M$, then the uniform tail ledger $T$.

Apply the uniform-tail and regular-seal clauses of \autoref{thm:uniform-limit-namecert-obligations}. They force the consumer route to use the same $M$ and $T$ before the handoff row $R$ can be reached.

Finally use \autoref{thm:uniform-limit-seal-factorization} and \autoref{thm:uniform-limit-finite-endpoint-certificate}. Both identify the downstream endpoint path as the finite route through $F,M,T,R,S,E$, so a pointwise-only or externally selected threshold route is not part of the certificate.
\end{proof}

\begin{theorem}[UniformLimit limit-seal compatibility]
\label{thm:uniform-limit-limit-seal-compatibility}
The $\RegSeqRatUp$ handoff row $R$ and the $\CauchyLimitSealUp$ row $S$ of an accepted $\UniformLimitUp$ carrier are compatible with the same window coordinates and the same $\hsame$ and $\Cont$ rows used by the uniform tail route. Transporting the window family, shared threshold, or uniform tail ledger therefore transports the handoff and seal route without changing the endpoint surface.
\end{theorem}
\begin{proof}
Read the carrier coordinates $H$ and $C$ from \autoref{def:uniform-limit-carrier}. These rows store the componentwise transports and displayed continuations for the function/window family, threshold ledger, uniform tail ledger, handoff row, seal row, and endpoint.

Use \autoref{thm:uniform-limit-seal-factorization}. It factors every endpoint read through the same route from $F,M,T$ to $R$, then to $S$, and finally to $E$.

Apply the classifier-transport clause of \autoref{thm:uniform-limit-namecert-obligations}. Since $R$ and $S$ are transported by the same $H$ and replayed by the same $C$ as the tail route, the transported packet keeps the handoff and seal compatible with the original windows and endpoint boundary.
\end{proof}

\begin{theorem}[UniformLimit ledger exactness obligation]
\label{thm:uniform-limit-ledger-exactness-obligation}
For an accepted $\UniformLimitUp$ carrier, the packet
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
exhausts the visible ledger. It includes the function/window family, shared modulus, uniform tail ledger, regular handoff, limit seal, endpoint row, transports, continuations, package provenance, and local naming row, and it excludes pointwise-only convergence, open-cover compactness, selected host limits, quotient function spaces, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with \autoref{def:uniform-limit-carrier}. Its tuple lists every visible coordinate of the carrier and names the dependency rows in $P$ and $N$.

Use \autoref{thm:uniform-limit-windowwise-cauchy-obligation} for the tail side and \autoref{thm:uniform-limit-limit-seal-compatibility} for the handoff and seal side. Together they show that all endpoint-facing routes are contained in the displayed packet.

Finally apply \autoref{thm:uniform-limit-non-escape-boundary} and \autoref{thm:uniform-limit-finite-endpoint-certificate}. The excluded analytic structures would require additional carrier coordinates or a different consumer route, and neither is present in $U$.
\end{proof}

\begin{theorem}[UniformLimit tail-ledger exactness]
\label{thm:uniform-limit-tail-ledger-exactness}
For every accepted $\UniformLimitUp$ carrier
$$
U=(F,M,T,R,S,E,H,C,P,N),
$$
each endpoint-facing read first factors through the displayed function/window family $F$, the shared threshold ledger $M$, and the unique $\UniformCauchyCriterionUp$ tail ledger $T$ visible to the packet. No second tail ledger, pointwise-only convergence witness, or independently selected threshold route can be read before the regular handoff row $R$.
\end{theorem}
\begin{proof}
Project $U$ through \autoref{def:uniform-limit-carrier}. The only rows before the regular handoff are $F,M,T$.

Apply \autoref{thm:uniform-limit-namecert-obligations}. The local NameCert surface names the function/window family, the shared threshold ledger, and the uniform Cauchy tail ledger as the finite endpoint-facing entrance to the packet.

Use \autoref{thm:uniform-limit-windowwise-cauchy-obligation}. Any endpoint-facing read reaches $R$ only after the shared threshold and uniform tail rows have been read.

Finally apply \autoref{thm:uniform-limit-ledger-exactness-obligation}. Since the visible ledger has exactly one $T$ coordinate and no pointwise-only convergence or second threshold coordinate, the displayed $T$ is the unique tail ledger available to the packet.
\end{proof}

\begin{theorem}[UniformLimit tail-seal route uniqueness]
\label{thm:uniform-limit-tail-seal-route-uniqueness}
Let
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
and
$$
U'=(F',M',T',R',S',E',H',C',P',N')
$$
be accepted $\UniformLimitUp$ carriers. If the displayed classifier rows
identify $F$ with $F'$, $M$ with $M'$, $T$ with $T'$, $R$ with $R'$, $S$ with
$S'$, and $E$ with $E'$, then every endpoint-facing read follows the same
finite route
$$
F \longmapsto M \longmapsto T \longmapsto R \longmapsto S \longmapsto E.
$$
No pointwise-only convergence witness, second tail ledger, selected host
limit, quotient function space, or $\RealUp$ completeness theorem can provide
a competing endpoint route.
\end{theorem}
\begin{proof}
Project both carriers through \autoref{def:uniform-limit-carrier}. The
classifier hypotheses identify the function/window family, shared threshold
ledger, uniform tail ledger, regular handoff, seal row, and endpoint row on
the displayed carrier surface.

Apply \autoref{thm:uniform-limit-tail-ledger-exactness}. Any endpoint-facing
read must enter through $F,M,T$, and the accepted carrier has no second tail
ledger or pointwise-only entrance that could reach $R$ first.

Use \autoref{thm:uniform-limit-seal-factorization}. Once the tail entrance is
fixed, the endpoint route factors through the regular handoff $R$, the seal
row $S$, and the endpoint $E$, so the displayed route is the only
tail-to-seal path available to the consumer.

Finally invoke \autoref{thm:uniform-limit-non-escape-boundary}. The excluded
analytic objects are not carrier coordinates and are not exported by the
transport, continuation, provenance, or local naming rows, so they cannot
supply a competing endpoint read.
\end{proof}

\begin{theorem}[UniformLimit seal-route transport]
\label{thm:uniform-limit-seal-route-transport}
Let
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
and
$$
U'=(F',M',T',R',S',E',H',C',P',N')
$$
be accepted $\UniformLimitUp$ carriers related by the displayed classifier. Componentwise $\hsame$ transport of $F,M,T$ transports the regular handoff, limit seal, and endpoint route $R,S,E$ through the same $H,C,P,N$ provenance. Thus the seal route remains the same finite route after transport:
$$
F \longmapsto M \longmapsto T \longmapsto R \longmapsto S \longmapsto E.
$$
\end{theorem}
\begin{proof}
Start with the compatibility theorem \autoref{thm:uniform-limit-limit-seal-compatibility}. It states that the handoff row $R$ and seal row $S$ use the same window coordinates and the same transport and continuation rows as the uniform tail route.

Apply \autoref{thm:uniform-limit-tail-ledger-exactness}. Transport of the endpoint-facing entrance is therefore transport of the rows $F,M,T$, not a change to a different tail ledger.

Use \autoref{thm:uniform-limit-seal-factorization}. The endpoint row $E$ is reached only through $R$ and $S$, so transporting $F,M,T$ carries the whole route through the same $R,S,E$ boundary.

Finally invoke \autoref{thm:uniform-limit-namecert-obligations} and \autoref{thm:uniform-limit-ledger-exactness-obligation}. The rows $H,C,P,N$ are the displayed transport, replay, provenance, and local naming rows for this packet, and no additional seal route is present.
\end{proof}

\begin{theorem}[UniformLimit endpoint readback exhaustion]
\label{thm:uniform-limit-endpoint-readback-exhaustion}
Every downstream $\RealUp$ or completion-facing consumer of an accepted $\UniformLimitUp$ carrier can read only
$$
F,M,T,R,S,E,H,C,P,N.
$$
Such a consumer may read the displayed window family, shared threshold ledger, uniform tail ledger, regular handoff, limit seal, endpoint row, transports, continuations, package provenance, and local naming row. It cannot extract pointwise convergence without the uniform ledger, quotient function spaces, selected host limits, open-cover compactness, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with an arbitrary downstream endpoint read. By \autoref{thm:uniform-limit-tail-ledger-exactness}, the read first factors through $F,M,T$.

Apply \autoref{thm:uniform-limit-seal-route-transport} and \autoref{thm:uniform-limit-seal-factorization}. The regular handoff, limit seal, and endpoint route are exactly $R,S,E$, transported and replayed by the same $H,C$ rows.

Use \autoref{thm:uniform-limit-finite-endpoint-certificate}. The finite certificate packages the endpoint-facing route together with $P$ and $N$ as the visible provenance and local naming surface.

Finally apply \autoref{thm:uniform-limit-non-escape-boundary} and \autoref{thm:uniform-limit-ledger-exactness-obligation}. The excluded pointwise, quotient, selected-limit, compactness, and completeness objects are not coordinates of the carrier and cannot be recovered by readback.
\end{proof}

\begin{theorem}[UniformLimit obligation closure package]
\label{thm:uniform-limit-obligation-closure-package}
For every accepted $\UniformLimitUp$ carrier
$$
U=(F,M,T,R,S,E,H,C,P,N),
$$
the carrier, local $\NameCert$ obligations, windowwise Cauchy obligation, limit-seal compatibility, tail-ledger exactness, seal-route transport, and endpoint readback exhaustion jointly supply the obligation surface over $\StreamNameUp$, $\UniformCauchyCriterionUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The package exports exactly the displayed function/window family, shared threshold ledger, uniform tail ledger, regular handoff, limit seal, endpoint row, transport routes, continuation routes, provenance, and local naming data. It exports no pointwise-only convergence object, open-cover compactness principle, selected host limit, quotient function space, or $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with the carrier and local naming obligations in \autoref{def:uniform-limit-carrier} and \autoref{thm:uniform-limit-namecert-obligations}. They identify the coordinates $F,M,T,R,S,E,H,C,P,N$ and bind carrier admission, classifier transport, uniform-tail exactness, regular-seal routing, and non-escape to those coordinates.

Use the windowwise Cauchy obligation of \autoref{thm:uniform-limit-windowwise-cauchy-obligation} and the limit-seal compatibility theorem \autoref{thm:uniform-limit-limit-seal-compatibility}. These force every endpoint route to read the shared threshold and the same uniform tail ledger before reaching the handoff and seal rows.

Apply tail-ledger exactness from \autoref{thm:uniform-limit-tail-ledger-exactness} and seal-route transport from \autoref{thm:uniform-limit-seal-route-transport}. They show that transported endpoint reads remain on the finite route from $F,M,T$ through $R,S,E$.

Finally use endpoint readback exhaustion in \autoref{thm:uniform-limit-endpoint-readback-exhaustion}. Since all downstream consumers can read only the displayed rows and their provenance, the obligation package has no coordinate for pointwise-only convergence, open-cover compactness, selected host limits, quotient function spaces, or real completeness.
\end{proof}

\begin{theorem}[UniformLimit diagonal-window handoff]
\label{thm:uniform-limit-diagonal-window-handoff}
Let
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
be an accepted $\UniformLimitUp$ carrier, and let
$$
G=(q,w,r,d,e,h,c,p,n)
$$
be an accepted $\RealDiagonalWindowCoverageUp$ carrier. Suppose that the selected window $w$ is a displayed window of $F$, and that the readback row $r$ is the $\RegSeqRatUp$ handoff read through $T$. Then every $\RealUp$-facing diagonal-window read determined by $G$ and the displayed window of $U$ factors simultaneously through the two finite routes
$$
F \longmapsto M \longmapsto T \longmapsto R \longmapsto S \longmapsto E
$$
and
$$
q \longmapsto w \longmapsto r \longmapsto d \longmapsto e.
$$
Consequently the diagonal-window consumer can use the uniform-limit endpoint exposure only through the selected finite window, the uniform tail ledger, the regular rational handoff, the dyadic observation ledger, and the displayed $\RealUp$ seal; it gains no pointwise-only convergence row, host limit, quotient function space, ambient completeness theorem, or unbounded diagonal stream.
\end{theorem}
\begin{proof}
Start from the accepted $\UniformLimitUp$ carrier. By \autoref{thm:uniform-limit-seal-factorization}, every endpoint read exported by $U$ reaches the endpoint only along the finite route through $F,M,T,R,S,E$.

Use the windowwise Cauchy obligation of \autoref{thm:uniform-limit-windowwise-cauchy-obligation} and tail-ledger exactness from \autoref{thm:uniform-limit-tail-ledger-exactness}. Since $w$ is one of the displayed windows of $F$ and $r$ is the $\RegSeqRatUp$ handoff read through $T$, the diagonal read cannot bypass the shared threshold ledger or replace the uniform tail row with a pointwise witness.

Now turn to the accepted $\RealDiagonalWindowCoverageUp$ carrier. The selected-window coverage theorem \autoref{thm:real-diagonal-window-coverage-selected-window-coverage} forces the seal-facing read to expose $w$ and the dyadic ledger $d$ before the seal row is consumed.

Apply the RealUp handoff theorem \autoref{thm:real-diagonal-window-coverage-realup-handoff}. It routes every real-facing completion or continuous-map consumer through $q,w,r,d,h,c,p,n$ before the $\RealUp$ seal row $e$ is read, so the selected-window side is exactly the displayed route from $q$ through $e$.

Finally combine the non-escape boundary for $\UniformLimitUp$ with the non-escape boundary for $\RealDiagonalWindowCoverageUp$. The first boundary excludes host limits, quotient function spaces, pointwise-only convergence, compactness principles, and real completeness from $U$; the second excludes quotient streams, host real equality, unbounded diagonal streams, ambient completeness, and choice-selected limits from $G$. Thus the only common consumer route is the paired finite factorization through the uniform-limit endpoint route and the selected diagonal-window route.
\end{proof}

\begin{theorem}[UniformLimit observation-budget factorization]
\label{thm:uniform-limit-observation-budget-factorization}
Let
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
be an accepted $\UniformLimitUp$ carrier, and let
$$
B=(e,W,D,R_B,S_B,H_B,C_B,P_B,N_B)
$$
be an accepted $\RealObservationBudgetUp$ carrier. Suppose the finite windows in $W$ are displayed windows of $F$, the dyadic readbacks in $D$ are the endpoint-facing readbacks for those windows, the handoff rows in $R_B$ include the same $\RegSeqRatUp$ handoff $R$ read through $T$, and the seal rows in $S_B$ include the same endpoint-facing seal route $S,E$. Then every $\RealUp$ endpoint read exported by $U$ factors through the observation-budget route
$$
e \longmapsto W \longmapsto D \longmapsto R_B \longmapsto S_B
$$
before exposing the endpoint row $E$.

Thus a common consumer of the uniform-limit packet and the observation-budget packet reads the shared finite windows, dyadic readbacks, regular handoff, seal rows, transports, and routes before the endpoint is available.
\end{theorem}
\begin{proof}
First identify the uniform-limit entrance. By \autoref{thm:uniform-limit-seal-factorization}, every endpoint read of $U$ reaches $E$ only through $F,M,T,R,S$.

Next apply the windowwise Cauchy obligation and the diagonal-window handoff, \autoref{thm:uniform-limit-windowwise-cauchy-obligation} and \autoref{thm:uniform-limit-diagonal-window-handoff}. Since the windows in $W$ are displayed windows of $F$ and the readbacks in $D$ are tied to those windows, the endpoint-facing read cannot bypass the shared threshold row $M$ or the tail ledger $T$.

Now read the budget side. The finite-window seal-route totality theorem for $\RealObservationBudgetUp$, \autoref{thm:real-observation-budget-finite-window-seal-route-totality}, routes every admitted seal read through $e,W,D,R_B,S_B$ with the displayed transports, continuations, provenance, and local name.

Finally combine the two route inventories. The shared handoff hypothesis identifies the uniform-limit $R$ with the budget handoff rows, and the shared seal hypothesis identifies $S,E$ with the budget seal route. Therefore the common endpoint read must pass through the observation-budget route before $E$ is exposed.
\end{proof}

\begin{theorem}[UniformLimit observation-budget nonchoice boundary]
\label{thm:uniform-limit-observation-budget-nonchoice}
Under the hypotheses of \autoref{thm:uniform-limit-observation-budget-factorization}, the common endpoint read cannot be replaced by pointwise convergence, a hidden selected limit, quotient function-space equality, an ambient completeness theorem, quotient stream equality, host real equality, or an unbounded observation schedule. Its only admissible route is the shared finite budget route through $F,M,T,R,S,E$ and $e,W,D,R_B,S_B$ with the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Begin with the uniform-limit non-escape boundary. \autoref{thm:uniform-limit-non-escape-boundary} removes pointwise-only convergence, open-cover compactness, selected host limits, quotient function spaces, and $\RealUp$ completeness from the $\UniformLimitUp$ packet.

Then apply the observation-budget non-escape theorem, \autoref{thm:real-observation-budget-nonescape}. It removes quotient stream equality, host real equality, ambient completeness, hidden limit selection, and unbounded observation schedules from the $\RealObservationBudgetUp$ packet.

The factorization theorem \autoref{thm:uniform-limit-observation-budget-factorization} gives the remaining common route. Since both packets expose only their displayed rows and the shared handoff and seal hypotheses identify the overlap, a consumer has no second source from which to select the endpoint.
\end{proof}

\begin{theorem}[UniformLimit shared threshold regular seal]
\label{thm:uniform-limit-shared-threshold-regular-seal}
For every accepted $\UniformLimitUp$ carrier
$$
U=(F,M,T,R,S,E,H,C,P,N),
$$
the endpoint-facing route uses one shared threshold ledger $M$ and one $\UniformCauchyCriterionUp$ tail row $T$ before it reaches the $\RegSeqRatUp$ handoff $R$ and the $\CauchyLimitSealUp$ row $S$. Thus the regular handoff and seal are bound to the same windowwise threshold data that generated the uniform tail comparisons.
\end{theorem}
\begin{proof}
Start with the accepted carrier $U$. By \autoref{thm:uniform-limit-windowwise-cauchy-obligation}, every endpoint-facing read must enter through the displayed windows, the shared threshold ledger $M$, and the uniform tail row $T$ before it can reach $R$.

Apply \autoref{thm:uniform-limit-tail-ledger-exactness}. The carrier has no second tail ledger and no independently selected threshold route, so the rows $M$ and $T$ used at the entrance are the unique rows available to the regular handoff.

Finally use \autoref{thm:uniform-limit-seal-factorization}. The route from the regular handoff to the endpoint passes through $S$ and then $E$, so the seal row is attached to the same shared threshold and tail ledger rather than to a separate pointwise or host-level limit route.
\end{proof}

\begin{theorem}[UniformLimit RegSeq seal classifier scope]
\label{thm:uniform-limit-regseq-seal-classifier-scope}
Let
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
and
$$
U'=(F',M',T',R',S',E',H',C',P',N')
$$
be accepted $\UniformLimitUp$ carriers related by the displayed classifier. Classifier transport of $F,M,T$ transports the $\RegSeqRatUp$ handoff $R$, the $\CauchyLimitSealUp$ row $S$, and the endpoint row $E$ through the displayed $\hsame$ rows and $\Cont$ routes already recorded in $H$ and $C$. It does not create a second seal route.
\end{theorem}
\begin{proof}
Use \autoref{thm:uniform-limit-limit-seal-compatibility}. The handoff row $R$ and seal row $S$ are compatible with the same window coordinates, transport rows, and continuation routes that carry the uniform tail route.

Apply \autoref{thm:uniform-limit-seal-route-transport}. Once $F,M,T$ are transported by the displayed classifier, the regular handoff, seal, and endpoint route are transported along the same finite path through $R,S,E$.

The carrier inventory contains only the transport ledger $H$ and continuation ledger $C$ for this route. Hence classifier transport preserves the displayed seal route and supplies no additional route by which a consumer could bypass the regular handoff.
\end{proof}

\begin{theorem}[UniformLimit completion consumer boundary]
\label{thm:uniform-limit-completion-consumer-boundary}
Every $\RealUp$ or completion-facing consumer of an accepted $\UniformLimitUp$ carrier factors through
$$
F,M,T,R,S,E,H,C,P,N.
$$
Such a consumer cannot read pointwise-only convergence, selected host limits, quotient function spaces, open-cover compactness, or $\RealUp$ completeness from the packet.
\end{theorem}
\begin{proof}
Begin with an arbitrary real-facing or completion-facing consumer. By \autoref{thm:uniform-limit-endpoint-readback-exhaustion}, the consumer can read only the displayed carrier rows $F,M,T,R,S,E,H,C,P,N$.

Use \autoref{thm:uniform-limit-diagonal-window-handoff} for the boundary handoff. Any diagonal-window read that reaches the endpoint must pass through the finite uniform route and the selected finite window route, so it gains no unbounded stream, host limit, quotient function space, or ambient completeness principle.

Finally apply \autoref{thm:uniform-limit-non-escape-boundary}. The excluded analytic objects are not carrier coordinates and are not exposed by the continuation or provenance rows. Therefore the Real and completion consumers are confined to the displayed uniform-limit packet.
\end{proof}

\begin{theorem}[UniformLimit continuous map handoff]
\label{thm:uniformlimit-continuous-map-handoff}
Let
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
be an accepted $\UniformLimitUp$ carrier. Any $\ContinuousMapUp$ consumer, and more generally any continuity-preservation consumer of the limiting endpoint, must factor through the finite route
$$
F \longmapsto M \longmapsto T \longmapsto R \longmapsto S \longmapsto E
$$
together with the transport, continuation, provenance, and non-escape rows $H,C,P,N$. The shared threshold ledger $M$ and uniform tail row $T$ supply the only uniform threshold surface before the $\RegSeqRatUp$ handoff $R$ and the $\CauchyLimitSealUp$ row $S$. The consumer therefore has no access to pointwise-only convergence, host function limits, quotient function spaces, open-cover compactness, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a $\ContinuousMapUp$ or continuity-preservation consumer of the limiting endpoint. By \autoref{thm:uniform-limit-completion-consumer-boundary}, every endpoint-facing consumer is confined to the displayed carrier rows $F,M,T,R,S,E,H,C,P,N$ and cannot read an ambient function-space or completeness object.

Use \autoref{thm:uniform-limit-windowwise-cauchy-obligation}. The route into the endpoint is forced to pass through the finite windows, the shared threshold ledger $M$, and the uniform tail row $T$. Thus the continuity consumer receives its limiting-endpoint data only after the same uniform threshold surface has been selected.

Finally apply \autoref{thm:uniform-limit-seal-factorization}. The $\RegSeqRatUp$ handoff $R$ and the $\CauchyLimitSealUp$ row $S$ are downstream of that shared uniform route, so the handoff presented to a continuous-map consumer is exactly the finite completion-facing surface already sealed by the packet. The listed pointwise, host-limit, quotient, compactness, and $\RealUp$-completeness readings are outside the carrier inventory and cannot be consumed here.
\end{proof}

\begin{theorem}[UniformLimit finite window seal exhaustion]
\label{thm:uniform-limit-finite-window-seal-exhaustion}
Let
$$
U=(F,M,T,R,S,E,H,C,P,N)
$$
be an accepted $\UniformLimitUp$ carrier, and let
$$
G=(q,w,r,d,e,h,c,p,n)
$$
be an accepted $\RealDiagonalWindowCoverageUp$ carrier. Suppose $w$ is a displayed window of $F$, and suppose $r$ is the $\RegSeqRatUp$ handoff read through $T$. Then every common $\RealUp$ or completion-facing consumer read of the two packets is exhausted by the paired finite route
$$
F \longmapsto M \longmapsto T \longmapsto R \longmapsto S \longmapsto E
$$
together with
$$
q \longmapsto w \longmapsto r \longmapsto d \longmapsto e.
$$
Conversely, any read assembled from those two displayed routes, together with the visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of $U$ and $G$, is an admissible finite seal read for the common endpoint-facing consumer surface. No such read can escape to pointwise-only convergence, quotient function spaces, selected host limits, open-cover compactness, ambient $\RealUp$ completeness, or unbounded diagonal streams.
\end{theorem}
\begin{proof}
First identify the uniform-limit side of the common route. Apply \autoref{thm:uniform-limit-diagonal-window-handoff}: because $w$ is a displayed window of $F$ and $r$ is read through $T$, every diagonal-window endpoint read supplied by $U$ factors through the finite route from $F$ to $E$. Apply \autoref{thm:uniform-limit-shared-threshold-regular-seal} to bind that route to the same shared threshold row $M$, the same tail ledger $T$, the same regular handoff $R$, and the same seal row $S$.

Next transport the route through the displayed classifier surface. By \autoref{thm:uniform-limit-regseq-seal-classifier-scope}, classifier transport of $F,M,T$ carries $R,S,E$ along the same $\hsame$ and $\Cont$ rows already present in $H$ and $C$. Thus the common consumer cannot obtain a second regular-seal route from a pointwise-only witness, a quotient function space, a selected host limit, or an open-cover compactness principle.

Now identify the selected-window side. The theorem \autoref{thm:real-diagonal-window-coverage-selected-window-coverage} forces any $\RealUp$-facing read of $G$ to display $w$ and the dyadic observation ledger $d$ before the seal row $e$ is consumed. The handoff theorem \autoref{thm:real-diagonal-window-coverage-realup-handoff} then routes every completion or continuous-map consumer through $q,w,r,d,e$ and the visible transport, continuation, provenance, and naming rows.

Combining these two finite routes gives the forward exhaustion claim. Apply \autoref{thm:uniform-limit-completion-consumer-boundary} to the $\UniformLimitUp$ packet and the RealDiagonalWindowCoverage handoff just cited to remove every undisplayed common consumer source, including ambient $\RealUp$ completeness and unbounded diagonal streams.

For the converse direction, start with a read assembled from the displayed rows of the two routes. The uniform route is admissible because the accepted carrier $U$ exposes exactly $F,M,T,R,S,E,H,C,P,N$ to endpoint-facing consumers, and the selected-window route is admissible because the accepted carrier $G$ exposes exactly $q,w,r,d,e,h,c,p,n$ to Real-facing consumers. Since the two routes agree at the displayed window $w$ and the handoff row $r$, their assembly is a finite seal read on the common endpoint-facing surface and uses no row outside the two accepted packets.
\end{proof}

\closureat{UniformLimitUp}{seedStr}
\closureat{UniformLimitUp}{obligationStr}[BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_seal\_factorization]
\closureat{UniformLimitUp}{scopedStr}[BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_seal\_factorization]
\closureat{UniformLimitUp}{publicStr}[BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_seal\_factorization]
\closureat{UniformLimitUp}{bridgedStr}[BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_seal\_factorization]
\closureat{UniformLimitUp}{matureStr}[BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_seal\_factorization]

\begin{closurestatus}{\UniformLimitUp}
  \constructivestory{A $\UniformLimitUp$ packet is generated from a displayed function/window family, a shared threshold ledger, one $\UniformCauchyCriterionUp$ tail ledger, a $\RegSeqRatUp$ handoff, a $\CauchyLimitSealUp$ seal row, a $\RealUp$ endpoint, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:uniform-limit-carrier}, \autoref{thm:uniform-limit-seal-factorization}, \autoref{thm:uniform-limit-finite-endpoint-certificate}, \autoref{thm:uniform-limit-shared-threshold-regular-seal}, and \autoref{thm:uniform-limit-non-escape-boundary} bind the finite carrier, seal factorization, public-facing endpoint certificate, tail-ledger exactness, and non-escape boundary for the displayed uniform-limit packet.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.UniformLimitUp.UniformLimitCarrier\_seal\_factorization}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close pointwise convergence without a uniform ledger, open-cover compactness, selected host limits, quotient function spaces, $\RealUp$ completeness, or a checked Lean certificate.}
  \upgradepath{Formal audit and bridge checking remain verification-axis work over the same finite uniform-limit endpoint surface.}
\end{closurestatus}
