\chapter{A Concrete Naming Certificate for $\CStarAlgUp$}
\label{ch:concrete-instances-cstaralgebra-namecert}

The C*-algebra interface $\CStarAlgUp$ packages a Banach algebra with an involution satisfying $\|a^* a\| = \|a\|^2$. It depends on $\NameCert_{\BanachUp}$ (\autoref{ch:concrete-instances-banach-namecert}) and $\NameCert_{\RingUp}$ (\autoref{ch:concrete-instances-ring-namecert}), and is the substrate for noncommutative topology and operator-theoretic spectra.

\section{Carrier definition}
\label{sec:cstaralgebra-carrier}

\begin{definition}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} BHist carrier]
\label{def:cstaralgebra-bhist-carrier}
Fix a $\NameCert_{\BanachUp}$ row $B$ and a $\NameCert_{\RingUp}$ row $R$ over the same $\mathsf{BHist}$ source. A $\CStarAlgUp$ carrier row is the predicate on a history $h:\mathsf{BHist}$ asserting that $h$ carries exactly the following certificate-visible data: the Banach carrier row from $B$, the RingUp multiplication row from $R$, an involution row $s:\mathsf{BHist}$ on the same carried endpoints, a norm-square compatibility row for $s$ and the multiplication row, the $\hsame$ transport rows for the carrier, multiplication, involution, and norm-square witnesses, and the $\Pkg$ provenance rows naming $B$ and $R$.
\end{definition}
\leandef{BEDC.Derived.CStarAlgUp.CstaralgebraBHistCarrier}

The predicate of \autoref{def:cstaralgebra-bhist-carrier} treats multiplication, involution, norm, and provenance as BEDC rows. It does not expose an ambient host $*$-algebra object or a quotient of algebra presentations.

\section{The certificate}
\label{sec:cstaralgebra-certificate}

\begin{definition}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} certificate surface]
\label{def:cstaralgebra-certificate-surface}
The $\NameCert_{\CStarAlgUp}$ certificate surface consists of the carrier predicate of \autoref{def:cstaralgebra-bhist-carrier}, the classifier inherited from the common $\hsame$ transport of the BanachUp and RingUp rows, the involution transport row, the norm-square compatibility transport row, the $\Cont$ ledger recording multiplication and involution observations, and the $\Pkg$ provenance naming $\NameCert_{\BanachUp}$ and $\NameCert_{\RingUp}$ as the only dependencies.
\end{definition}

\begin{theorem}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} NameCert obligation surface]
\label{thm:cstaralgebra-namecert-obligation-surface}
The surface of \autoref{def:cstaralgebra-certificate-surface} is a complete paper-side obligation surface for $\NameCert_{\CStarAlgUp}$. Every accepted $\CStarAlgUp$ row is read from a $\mathsf{BHist}$ carrier row, a BanachUp source row, a RingUp multiplication row, an involution row, a norm-square compatibility row, the corresponding $\hsame$ and $\Cont$ transport rows, and the $\Pkg$ provenance rows for the two dependency certificates.
\end{theorem}
\leanchecked{BEDC.Derived.CstaralgebraUp.CstaralgebraNameCert\_obligation\_surface}
\begin{proof}
Project an accepted carrier witness through \autoref{def:cstaralgebra-bhist-carrier}. The projection exposes the Banach row, the RingUp multiplication row, the involution row, the norm-square row, the transport rows, and the dependency provenance.

The classifier is then forced by the same $\hsame$ transport rows. Banach transport moves the norm carrier, RingUp transport moves multiplication, and the involution and norm-square rows are retained only when their displayed histories transport along the same carrier comparison.

Repack these projections as the certificate surface of \autoref{def:cstaralgebra-certificate-surface}. No further row is available to the repacking step, so the listed rows are the whole obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.CStarAlgUp.CStarAlgCertificateSurface\_namecert\_obligation}
\leanvariant{BEDC.Derived.CStarAlgUp.CStarAlgBHistCarrier\_namecert\_obligation\_surface}

\begin{theorem}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} Gelfand and von Neumann consumer boundary]
\label{thm:cstaralgebra-gelfand-vonneumann-consumer-boundary}
Any $\GelfandDualityUp$ or $\VonNeumannAlgUp$ consumer citing $\NameCert_{\CStarAlgUp}$ may consume only the $\mathsf{BHist}$ carrier, the BanachUp carrier and norm rows, the RingUp multiplication row, the involution row, the norm-square compatibility row, the $\hsame$ and $\Cont$ transport rows, and the $\Pkg$ provenance rows displayed in \autoref{def:cstaralgebra-certificate-surface}. It may not infer a spectrum, weak-operator closure, representation on a Hilbert space, or commutative Gelfand transform from the root $\CStarAlgUp$ surface alone.
\end{theorem}
\begin{proof}
Read the dependency citation through \autoref{thm:cstaralgebra-namecert-obligation-surface}. The citation yields only the certificate rows projected there, so a downstream consumer receives the carried Banach, RingUp, involution, norm-square, transport, ledger, and provenance data.

For $\GelfandDualityUp$, a spectrum and a commutative transform require rows not present in the $\CStarAlgUp$ root surface. For $\VonNeumannAlgUp$, weak-operator closure and Hilbert-space representation data also require rows not present in that surface.

Thus both consumers share the same BEDC source boundary: they may cite the $\CStarAlgUp$ certificate rows, while their own chapters must supply any spectrum, closure, representation, or transform rows they use.
\end{proof}
\leanchecked{BEDC.Derived.CStarAlgUp.CStarAlgCertificateSurface\_gelfand\_vonneumann\_consumer\_boundary}

\begin{theorem}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} unital-commutative source boundary]
\label{thm:cstaralgebra-unital-commutative-source-boundary}
A $\GelfandDualityUp$ consumer may treat a $\CStarAlgUp$ row as a unital
commutative source only when the displayed $\mathsf{BHist}$ surface supplies,
in addition to the root certificate, a unit row, multiplication row,
commutativity classifier row, involution row, norm-square row, $\hsame$
transport, $\Cont$ ledger, and $\mathsf{Pkg}$ provenance over the same
BanachUp and RingUp dependency rows. The root $\CStarAlgUp$ certificate alone
does not export the Gelfand transform, the spectrum row, or a compact
Hausdorff carrier.
\end{theorem}
\leanchecked{BEDC.Derived.CstaralgebraUp.CstaralgebraBHistCarrier\_unital\_commutative\_source\_boundary}
\begin{proof}
Unfold \autoref{def:cstaralgebra-bhist-carrier}. The root carrier exposes the
Banach row, RingUp multiplication row, involution row, norm-square row,
transport rows, and dependency provenance.

Unfold \autoref{def:cstaralgebra-certificate-surface}. Its public classifier
and ledger are the displayed $\hsame$, $\Cont$, and $\Pkg$ rows over those
carrier components; unit and commutativity data must therefore be supplied as
visible rows of the consumer surface when $\GelfandDualityUp$ asks for a
unital commutative source.

Finally apply
\autoref{thm:cstaralgebra-gelfand-vonneumann-consumer-boundary}. That boundary
rules out hidden spectrum data and hidden transform rows, so the
$\GelfandDualityUp$ source read is limited to the displayed unital,
commutative, involutive, norm-square, transport, ledger, and provenance rows.
\end{proof}

\begin{theorem}[No host star-algebra primitive in \texorpdfstring{$\CStarAlgUp$}{CStarAlgUp}]
\label{thm:cstaralgebra-no-host-star-algebra-primitive}
The $\CStarAlgUp$ obligation surface does not include a host $*$-algebra primitive. Equality and transport for $\CStarAlgUp$ are mediated only by $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert_{\BanachUp}$, and $\NameCert_{\RingUp}$ together with the displayed involution and norm-square rows.
\end{theorem}
\begin{proof}
Unfold the carrier predicate of \autoref{def:cstaralgebra-bhist-carrier}. Its only source rows are the BanachUp and RingUp certificate rows, the involution row, the norm-square row, the transport rows, and the provenance rows.

Unfold the certificate surface of \autoref{def:cstaralgebra-certificate-surface}. The surface records classifier and ledger data by $\hsame$, $\Cont$, and $\Pkg$; it never adds an ambient equality predicate for host $*$-algebras.

Therefore replacing the displayed rows by a host $*$-algebra primitive would change the carrier. The BEDC object is precisely the row package described above.
\end{proof}

\begin{theorem}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} Banach--Ring source boundary]
\label{thm:cstaralgebra-banach-ring-source-boundary}
Every public source read of a $\CStarAlgUp$ certificate factors through the
displayed BanachUp carrier row, the RingUp multiplication row, the involution
row, the norm-square compatibility row, the $\hsame$ transports for those rows,
the finite $\Cont$ ledger, and the $\Pkg$ provenance naming the BanachUp and
RingUp dependency certificates. No source read exports a host $*$-algebra
equality, an ambient Banach-ring object, or spectrum data.
\end{theorem}
\begin{proof}
Project the source read through
\autoref{def:cstaralgebra-bhist-carrier}. The carrier predicate lists exactly
the Banach row, RingUp multiplication row, involution row, norm-square row,
transport rows, and dependency provenance.

Next read the certificate surface of
\autoref{def:cstaralgebra-certificate-surface}. Its public ledger is the
$\Cont$ route recording multiplication and involution observations together
with the same $\hsame$ and $\Pkg$ rows.

Finally apply
\autoref{thm:cstaralgebra-no-host-star-algebra-primitive}. Since the surface has
no slot for host $*$-algebra equality, ambient Banach-ring structure, spectrum,
or transform data, a public source read must factor through the displayed BEDC
rows alone.
\end{proof}

\begin{theorem}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} classifier stability]
\label{thm:cstaralgebra-classifier-stability}
Componentwise $\hsame$ transport of the BanachUp carrier row, the RingUp
multiplication row, the involution row, the norm-square compatibility row, the
$\Cont$ ledger, and the $\Pkg$ provenance preserves the $\CStarAlgUp$
classifier and the carrier predicate of \autoref{def:cstaralgebra-bhist-carrier}.
The transported certificate remains a $\CStarAlgUp$ row precisely because each
displayed component is transported inside the certificate surface.
\end{theorem}
\begin{proof}
Unfold the carrier predicate in
\autoref{def:cstaralgebra-bhist-carrier}. A transported carrier is accepted when
the Banach, multiplication, involution, norm-square, and provenance rows are all
transported along their displayed $\hsame$ witnesses.

Unfold \autoref{def:cstaralgebra-certificate-surface}. Its classifier is
inherited from those same componentwise transports, while the ledger rows are
read only through $\Cont$ and the dependency provenance remains the displayed
$\Pkg$ row.

Thus the transported packet satisfies the same carrier predicate and the same
certificate classifier. No host star-algebra equality or spectrum datum is
introduced, because neither appears among the transported rows.
\end{proof}

\begin{theorem}[\texorpdfstring{$\CStarAlgUp$}{CStarAlgUp} ledger exactness]
\label{thm:cstaralgebra-ledger-exactness}
The public $\CStarAlgUp$ ledger is exhausted by the multiplication row, the
involution row, the norm-square compatibility row, the $\hsame$ transport rows,
the finite $\Cont$ readbacks, and the $\Pkg$ provenance rows for
$\NameCert_{\BanachUp}$ and $\NameCert_{\RingUp}$. Every downstream
$\GelfandDualityUp$ or $\VonNeumannAlgUp$ citation of $\CStarAlgUp$ reads one of
those ledger rows, and every listed row is part of the certificate surface.
\end{theorem}
\begin{proof}
Start from the certificate surface in
\autoref{def:cstaralgebra-certificate-surface}. Its ledger records
multiplication and involution observations, norm-square compatibility,
componentwise transport, finite readback, and dependency provenance.

For downstream consumption, apply
\autoref{thm:cstaralgebra-gelfand-vonneumann-consumer-boundary}. The consumer
boundary exposes exactly the same carrier, source, transport, ledger, and
provenance rows to $\GelfandDualityUp$ and $\VonNeumannAlgUp$.

The reverse inclusion is by projection from
\autoref{def:cstaralgebra-bhist-carrier}: each listed ledger row is a field of
the displayed carrier or certificate surface. Spectrum data, weak-operator
closure, Hilbert-space representations, and host star-algebra equality are
therefore outside the public ledger.
\end{proof}

\closureat{CStarAlgUp}{seedStr}[BEDC.Derived.CStarAlgUp.CStarAlgCertificateSurface\_namecert\_obligation]

\begin{closurestatus}{\CStarAlgUp}
  \constructivestory{}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope binds the $\BanachUp$ and $\RingUp$ dependency rows, the involution row, norm-square compatibility, componentwise $\hsame$, finite $\Cont$ readback, and $\Pkg$ provenance of the $\CStarAlgUp$ certificate surface.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.CStarAlgUp.CStarAlgCertificateSurface\_namecert\_obligation}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a spectrum, weak-operator closure, Hilbert-space representation, host star-algebra equality, or standard bridge.}
  \upgradepath{Obligation closure requires the full classifier-stability, ledger-exactness, source-boundary, and downstream-consumer inventory for the displayed certificate surface.}
\end{closurestatus}
