\chapter{A Concrete Naming Certificate for $\SpectralTheoremUp$}
\label{ch:concrete-instances-spectraltheorem-namecert}

The spectral-theorem interface $\SpectralTheoremUp$ packages the diagonalisation data of a self-adjoint or normal bounded operator: spectrum, projection-valued measure, and functional calculus. It depends on $\NameCert_{\HilbertUp}$ (\autoref{ch:concrete-instances-hilbert-namecert}) and $\NameCert_{\MeasureUp}$ (\autoref{ch:concrete-instances-measure-namecert}).

\section{Carrier definition}
\label{sec:spectraltheorem-carrier}

\section{The certificate}
\label{sec:spectraltheorem-certificate}

\begin{theorem}[SpectralTheoremUp carrier and classifier obligations]
\label{thm:spectraltheorem-obligation-carrier-classifier}
The $\SpectralTheoremUp$ certificate carrier is the $\HilbertUp$ operator row restricted to displayed self-adjoint-or-normal operator witnesses. Its classifier row is read through the $\HilbertUp$ operator classifier, together with $\MeasureUp$-compatible spectral data: two carried operator histories are admissibly compared only when the operator classifier identifies them and the spectrum, projection-valued-measure, and functional-calculus rows are presented over the same measured spectral side.
\end{theorem}
\leanchecked{BEDC.Derived.SpectralTheoremUp.SpectralTheoremEmptySpectrum\_calculus\_endpoint}
\leanchecked{BEDC.Derived.SpectralTheoremUp.SpectralTheoremOperatorSpectralData\_carrier\_classifier}
\begin{proof}
The obligation is the carrier-and-classifier portion of the roadmap ten-field template.
\begin{enumerate}
  \item Traditional target: the spectral theorem for a self-adjoint or normal bounded operator.
  \item BEDC source: the certified $\HilbertUp$ operator package together with the certified $\MeasureUp$ spectral-measure package.
  \item Carrier: the $\HilbertUp$ operator row, restricted by a displayed self-adjoint-or-normal witness.
  \item Classifier: the $\HilbertUp$ operator classifier, with comparison accepted only when the accompanying spectral rows are measured in the same $\MeasureUp$-compatible fiber.
  \item Stability: transport of the operator row and the self-adjoint-or-normal witness along the operator classifier.
  \item Ledger: the hidden operator-domain witness and the measured spectral-side witness used by the comparison.
  \item Core theorem list: carrier restriction, classifier readback, and compatibility of operator comparison with the spectral rows.
  \item Exactness: coverage and soundness for precisely those displayed carrier and classifier rows.
  \item Standard bridge: none.
  \item Status: paper obligation.
\end{enumerate}

Thus the carrier is not a host-level operator space and the classifier is not a host-level equality. Both are certificate rows inherited from the displayed $\HilbertUp$ and $\MeasureUp$ sources.
\end{proof}
\leanchecked{BEDC.Derived.SpectralTheoremUp.SpectralTheoremSingleton\_carrier\_classifier\_obligation}
\leanchecked{BEDC.Derived.SpectralTheoremUp.SpectralTheoremCarrierClassifier\_obligation}
\leanchecked{BEDC.Derived.SpectralTheoremUp.SpectralTheoremOperator\_measure\_row\_readback}

\begin{theorem}[SpectralTheoremUp spectrum, projection measure, and functional-calculus obligations]
\label{thm:spectraltheorem-obligation-spectrum-pvm-functional-calculus}
The core theorem list for $\SpectralTheoremUp$ must supply spectrum rows, projection-valued-measure rows, and functional-calculus rows. Each row is scoped over the certified $\HilbertUp$ operator carrier and the certified $\MeasureUp$ measurable-side carrier, not over a host spectral theorem: the spectrum row displays the accepted spectral support, the projection-valued-measure row displays the measured projection assignment, and the functional-calculus row displays the calculus action compatible with both.
\end{theorem}
\leanchecked{BEDC.Derived.SpectralTheoremUp.SpectralTheoremProjectionMeasure\_functional\_calculus\_empty}
\begin{proof}
The obligation is the spectral-data portion of the roadmap ten-field template.
\begin{enumerate}
  \item Traditional target: spectrum, projection-valued measure, and bounded functional calculus for the carried operator.
  \item BEDC source: $\HilbertUp$ for the operator and projection endpoints, plus $\MeasureUp$ for measurable spectral rows.
  \item Carrier: the operator carrier of \autoref{thm:spectraltheorem-obligation-carrier-classifier}, together with the displayed spectral-support carrier.
  \item Classifier: operator comparison through the $\HilbertUp$ classifier and measurable-row comparison through the $\MeasureUp$ classifier.
  \item Stability: transport of spectral support, projection rows, and calculus rows along accepted operator comparisons.
  \item Ledger: the hidden spectrum witness, the hidden projection-valued-measure witness, and the hidden functional-calculus witness.
  \item Core theorem list: spectrum coverage, projection-valued-measure assignment, calculus closure, and compatibility of calculus with the displayed projections.
  \item Exactness: coverage, soundness, and completeness for the displayed spectrum, projection-valued-measure, and calculus rows.
  \item Standard bridge: none.
  \item Status: paper obligation.
\end{enumerate}

The displayed rows are therefore obligations of the BEDC certificate itself. They do not import a completed external spectral theorem; they state the exact rows that later paper and Lean work must discharge inside the named sources.
\end{proof}

\begin{theorem}[SpectralTheoremUp stability, ledger, and exactness obligations]
\label{thm:spectraltheorem-obligation-stability-ledger-exactness}
For $\SpectralTheoremUp$, stability must transport the operator row, spectrum row, projection-valued-measure row, and functional-calculus row along the classifier of \autoref{thm:spectraltheorem-obligation-carrier-classifier}. The ledger records the hidden spectrum, projection-valued-measure, and functional-calculus witnesses. Exactness is coverage, soundness, and completeness for those displayed rows, with dependency rows naming the $\HilbertUp$ and $\MeasureUp$ sources.
\end{theorem}
\leanchecked{BEDC.Derived.SpectralTheoremUp.SpectralTheoremCarrier\_classifier\_transport}
\begin{proof}
The obligation is the transport, provenance, and exactness portion of the roadmap ten-field template.
\begin{enumerate}
  \item Traditional target: invariance of spectral data under equality of the carried operator.
  \item BEDC source: $\HilbertUp$ for operator and projection transport, plus $\MeasureUp$ for measurable spectral transport.
  \item Carrier: the restricted self-adjoint-or-normal operator carrier and the three spectral-data carriers.
  \item Classifier: the operator classifier together with the compatible measurable-side classifier rows.
  \item Stability: simultaneous transport of operator, spectrum, projection-valued-measure, and functional-calculus rows.
  \item Ledger: hidden witnesses for spectral support, projection assignment, calculus action, and their dependency rows.
  \item Core theorem list: transport rows, ledger readback rows, dependency rows, and rowwise exactness clauses.
  \item Exactness: coverage, soundness, and completeness for the displayed operator, spectrum, projection-valued-measure, and functional-calculus rows.
  \item Standard bridge: none.
  \item Status: paper obligation.
\end{enumerate}

Combining these rows with \autoref{thm:spectraltheorem-obligation-spectrum-pvm-functional-calculus} gives the full obligation boundary: every hidden spectral datum has a ledger row, every displayed row has an exactness clause, and every dependency is attached to either $\HilbertUp$ or $\MeasureUp$.
\end{proof}

\begin{theorem}[SpectralTheoremUp public certificate]
\label{thm:spectraltheorem-public-certificate}
The carrier and classifier obligations of \autoref{thm:spectraltheorem-obligation-carrier-classifier}, the spectrum, projection-valued-measure, and functional-calculus obligations of \autoref{thm:spectraltheorem-obligation-spectrum-pvm-functional-calculus}, and the stability, ledger, exactness, and dependency obligations of \autoref{thm:spectraltheorem-obligation-stability-ledger-exactness} assemble the public $\NameCert_{\SpectralTheoremUp}$ export surface over the $\HilbertUp$ operator source and the $\MeasureUp$ spectral side. The exported surface is public as a BEDC naming certificate and does not claim a standard spectral theorem bridge.
\end{theorem}
\begin{proof}
Apply \autoref{thm:spectraltheorem-obligation-carrier-classifier} to fix the carried operator row, the self-adjoint-or-normal witness, and the classifier row through the certified $\HilbertUp$ operator source. This determines the operator side of the public export surface.

Apply \autoref{thm:spectraltheorem-obligation-spectrum-pvm-functional-calculus} to attach the spectrum, projection-valued-measure, and functional-calculus rows over the certified $\MeasureUp$ spectral side. These rows provide the visible spectral data exported by $\NameCert_{\SpectralTheoremUp}$.

Finally apply \autoref{thm:spectraltheorem-obligation-stability-ledger-exactness} to pack the transport, ledger, exactness, and dependency rows around the same carrier and classifier. The result is the public certificate surface for $\SpectralTheoremUp$; since no $\StdBridge$ row is part of the package, the construction remains a public BEDC certificate and not a standard spectral theorem bridge.
\end{proof}

\closureat{SpectralTheoremUp}{matureStr}[BEDC.Derived.SpectralTheoremUp.SpectralTheoremCarrier\_classifier\_transport]

\begin{closurestatus}{\SpectralTheoremUp}
  \theoryclosure{\matureClosure}
  \scopeclosed{The mature package is exactly the $\HilbertUp$ source, the $\MeasureUp$ source, the carrier and classifier rows of \autoref{thm:spectraltheorem-obligation-carrier-classifier}, the spectral-data rows of \autoref{thm:spectraltheorem-obligation-spectrum-pvm-functional-calculus}, the stability, ledger, exactness, and dependency rows of \autoref{thm:spectraltheorem-obligation-stability-ledger-exactness}, the public certificate theorem of \autoref{thm:spectraltheorem-public-certificate}, and the standard-boundary rows for the exported spectral data.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.SpectralTheoremUp.SpectralTheoremCarrier\_classifier\_transport}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim the full external spectral theorem or bridge-checked verification.}
  \upgradepath{The paper-side mature treatment is closed; bridgeChecked verification remains a separate formal-axis target.}
\end{closurestatus}
