\chapter{A Concrete Naming Certificate for $\ContinuationTraceUp$}
\label{ch:concrete-instances-continuationtrace-namecert}
\origin{human}

The $\ContinuationTraceUp$ packet gives the computation-as-continuation reading of \autoref{ch:visions-computation-as-continuation} a concrete finite carrier. It treats a displayed small-step computation as a $\mathsf{BHist}$ trace: each row records a source history, a mark-and-tail route, a target history, the $\hsame$ transports needed to compare displayed histories, the $\Cont$ route that witnesses the step, package provenance, and a local naming row. The packet does not introduce a host evaluator, a host termination predicate, quotient behaviour, or big-step semantic object.

The same trace packet supplies the step-ledger surface consumed by the unary-continuation categorical reading in \autoref{ch:concrete-instances-unary-continuation-category-namecert}: source and target rows together with $\Cont$ tails become the hom-carrier data, while the trace ledger records the finite route support.

\begin{definition}[ContinuationTrace carrier]
\label{def:continuation-trace-carrier}
A $\ContinuationTraceUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
T=(S,M,R,Q,H,C,P,N)
$$
whose displayed coordinates are as follows:
\begin{enumerate}
\item $S$ is the source-history row being inspected by the small-step read;
\item $M$ is the mark row and displayed tail route by which the step is named;
\item $R$ is the target-history row reached by the displayed route;
\item $Q$ is the finite trace ledger containing the ordered source, mark, tail, and target reads for each displayed step row;
\item $H$ is the componentwise $\hsame$ transport row comparing source histories, tail histories, and target histories across accepted trace packets;
\item $C$ is the $\Cont$ route witnessing that the displayed tail carries the source row to the target row;
\item $P$ is the $\Pkg$ provenance over $\mathsf{BHist}$, $\mathsf{BMark}$, $\hsame$, $\Cont$, and the continuation-reading dependencies;
\item $N$ is the local $\NameCert_{\ContinuationTraceUp}$ row.
\end{enumerate}
Two accepted traces classify together only when the source histories, mark-and-tail route, target histories, finite trace ledger, $\hsame$ transport, $\Cont$ route, package row, and local certificate row are transported componentwise by the displayed rows.
\end{definition}
\leandef{BEDC.Derived.ContinuationTraceUp.ContinuationTraceCarrier}

\begin{theorem}[ContinuationTrace NameCert obligations]
\label{thm:continuation-trace-namecert-obligations}
The local $\NameCert_{\ContinuationTraceUp}$ surface consists of five finite rows:
\begin{enumerate}
\item carrier: an accepted trace is exactly the finite packet of \autoref{def:continuation-trace-carrier};
\item classifier: two accepted traces compare only by componentwise $\hsame$ transport of $S$, $M$, $R$, $Q$, $H$, $C$, $P$, and $N$;
\item step readback: every displayed small-step row is read from the $\Cont$ route $C$ together with the mark-and-tail coordinate $M$ and the source and target rows $S$ and $R$;
\item non-escape: the trace exports no host function, host termination object, quotient behaviour, or big-step semantic value;
\item public export: the packet handed to later formalization is the same finite $\mathsf{BHist}$ trace carrier with its classifier, readback, non-escape, and provenance rows.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationTraceUp.ContinuationTraceCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is the finite packaging operation of \autoref{def:continuation-trace-carrier}. Every coordinate in the accepted object is one of the displayed trace rows.

Classifier stability is componentwise. A transport of accepted traces may compare source histories, target histories, route rows, and provenance rows, but it can only do so through the listed $\hsame$ and $\Cont$ fields.

The final three rows are supplied by the readback, non-escape, and public export theorems below. Together they account for every consumer-facing trace read and keep the packet inside the BEDC history, mark, sameness, continuation, package, and naming primitives.
\end{proof}

\begin{theorem}[ContinuationTrace small-step readback]
\label{thm:continuation-trace-small-step-readback}
Let $T=(S,M,R,Q,H,C,P,N)$ be an accepted $\ContinuationTraceUp$ carrier. Every displayed small-step transition read from $T$ factors through the source-history row $S$, the mark-and-tail row $M$, the target-history row $R$, the finite trace ledger $Q$, and the $\Cont$ route $C$. Conversely, any displayed $\Cont$ tail in $C$ whose source, mark, tail, and target rows are listed in $Q$ is read back as a step of the same trace classifier.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationTraceUp.ContinuationTraceCarrier\_small\_step\_readback}
\begin{proof}
Project the accepted trace through \autoref{def:continuation-trace-carrier}. A step read has no coordinates available except the source row, the mark-and-tail row, the target row, the trace ledger, and the displayed continuation route.

For the forward direction, inspect the row of $Q$ named by the consumer. It records the same source, mark, tail, and target rows, and the route coordinate $C$ supplies the displayed $\Cont$ witness that the tail carries the source to the target.

For the reverse direction, begin with such a displayed $\Cont$ tail in $C$. Since its source, mark, tail, and target rows are listed in $Q$, the classifier of the carrier reads it through the same local packet and returns the corresponding trace step. The transport row $H$ accounts only for $\hsame$ comparisons among displayed histories and does not alter the trace boundary.
\end{proof}

\begin{theorem}[ContinuationTrace non-escape boundary]
\label{thm:continuation-trace-non-escape-boundary}
An accepted $\ContinuationTraceUp$ packet exposes no host function graph, host termination predicate, quotient behaviour relation, selected evaluator, or big-step semantic object. Its visible computational content is exactly the finite source, mark-and-tail, target, trace-ledger, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of \autoref{def:continuation-trace-carrier}.
\end{theorem}
\begin{proof}
Read the carrier coordinates. None of $S$, $M$, $R$, $Q$, $H$, $C$, $P$, or $N$ is a host function, a host termination object, a quotient of behaviours, or a big-step value.

The only operational row is $C$, and it is a BEDC continuation route. By \autoref{thm:continuation-trace-small-step-readback}, consumer-facing steps are recovered from that route together with the finite trace ledger $Q$ and the displayed source, mark, and target rows.

Thus every exported computation read remains in the finite continuation trace packet. There is no coordinate through which a host evaluator, host termination principle, quotient behaviour, or big-step semantics can enter the public surface.
\end{proof}

\begin{theorem}[ContinuationTrace public export]
\label{thm:continuation-trace-public-export}
The public $\ContinuationTraceUp$ export surface is the finite carrier of \autoref{def:continuation-trace-carrier} together with the five NameCert rows of \autoref{thm:continuation-trace-namecert-obligations}, the readback equivalence of \autoref{thm:continuation-trace-small-step-readback}, and the boundary statement of \autoref{thm:continuation-trace-non-escape-boundary}. This is the canonical finite packet for future Lean formalization of continuation traces.
\end{theorem}
\begin{proof}
The carrier exposes exactly the rows $S,M,R,Q,H,C,P,N$. The NameCert theorem identifies the accepted carrier, its classifier, the step readback row, non-escape, and the public export obligation over those rows.

The readback theorem accounts for the computation-facing use: displayed small-step reads are precisely reads through the source, mark-and-tail, target, trace ledger, and continuation route. The non-escape theorem accounts for the boundary by excluding host functions, host termination, quotient behaviours, selected evaluators, and big-step semantic objects.

Repacking these clauses gives the public finite certificate. Since every clause points back to the same displayed carrier coordinates, the export is a concrete BEDC packet and not an external operational semantics.
\end{proof}

\begin{theorem}[ContinuationTrace obligation closure package]
\label{thm:continuation-trace-obligation-closure-package}
The carrier, NameCert obligations, small-step readback, non-escape boundary, and public export of \autoref{def:continuation-trace-carrier}, \autoref{thm:continuation-trace-namecert-obligations}, \autoref{thm:continuation-trace-small-step-readback}, \autoref{thm:continuation-trace-non-escape-boundary}, and \autoref{thm:continuation-trace-public-export} assemble the finite $\ContinuationTraceUp$ obligation package over $\BHist$, $\BMark$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The package exposes source histories, mark-and-tail rows, target histories, trace ledgers, transports, continuation routes, provenance, and the local naming row as the whole public surface.
\end{theorem}
\begin{proof}
The carrier theorem supplies the finite trace packet. The NameCert obligations bind admission, classifier comparison, step readback, non-escape, and public export to the displayed coordinates $S,M,R,Q,H,C,P,N$.

The small-step readback theorem accounts for every computation-facing row by reading it through the source history, mark-and-tail route, target history, trace ledger, and continuation route. The non-escape boundary prevents the same read from acquiring a host evaluator, host termination predicate, quotient behaviour, selected evaluator, or big-step semantic object.

The public export theorem repacks those rows as the visible trace interface. Because all five cited results refer back to the same carrier coordinates, they form one finite $\ContinuationTraceUp$ obligation package over the BEDC history, mark, sameness, continuation, package, and naming primitives.
\end{proof}

\begin{theorem}[ContinuationTrace concatenation readback]
\label{thm:continuation-trace-concatenation-readback}
Let
$$
T_0=(S_0,M_0,R_0,Q_0,H_0,C_0,P_0,N_0)
\quad\text{and}\quad
T_1=(S_1,M_1,R_1,Q_1,H_1,C_1,P_1,N_1)
$$
be accepted $\ContinuationTraceUp$ packets. If the target row $R_0$ of $T_0$ and the source row $S_1$ of $T_1$ are matched by a displayed $\hsame$ row, then their concatenation is a finite trace packet whose step reads factor through exactly one of the two source ledgers $Q_0$ or $Q_1$, with the boundary comparison supplied by that displayed $\hsame$ row.

The public concatenated packet is still over $\BHist$, $\BMark$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It exports no host evaluator, host termination predicate, quotient behaviour, or big-step semantic object.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationTraceUp.ContinuationTraceCarrier\_concatenation\_readback}
\begin{proof}
Project both accepted packets through \autoref{def:continuation-trace-carrier}. The only rows available for a step read in the first packet are $S_0,M_0,R_0,Q_0,H_0,C_0,P_0,N_0$, and the only rows available in the second packet are $S_1,M_1,R_1,Q_1,H_1,C_1,P_1,N_1$.

Use \autoref{thm:continuation-trace-small-step-readback} separately on the two packets. A step read before the boundary is read from $Q_0$ together with $C_0$, while a step read after the boundary is read from $Q_1$ together with $C_1$.

The displayed $\hsame$ match between $R_0$ and $S_1$ supplies only the boundary comparison. By \autoref{thm:continuation-trace-non-escape-boundary}, that comparison cannot introduce a host evaluator, host termination predicate, quotient behaviour, selected evaluator, or big-step semantic object.

Finally apply \autoref{thm:continuation-trace-public-export} and \autoref{thm:continuation-trace-obligation-closure-package}. Repacking the two finite ledgers with the boundary $\hsame$ row keeps the concatenated public packet inside $\BHist$, $\BMark$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, and every step read is accounted for by exactly one source ledger.
\end{proof}

\begin{theorem}[ContinuationTrace endpoint ledger exhaustion]
\label{thm:continuation-trace-endpoint-ledger-exhaustion}
Let $T=(S,M,R,Q,H,C,P,N)$ be an accepted $\ContinuationTraceUp$ packet. Every endpoint-facing source or target read of $T$ is exhausted by the displayed rows $S,M,R,Q,H,C,P,N$: the endpoint read is listed in the finite trace ledger $Q$ and replayed by the continuation route $C$ from the displayed source side to the displayed target side.

No endpoint read of $T$ is supplied by a host evaluator, a host termination predicate, a quotient behaviour, a selected evaluator, or a big-step semantic object.
\end{theorem}
\begin{proof}
Project $T$ through \autoref{def:continuation-trace-carrier}. The endpoint-facing coordinates are the source row $S$, mark-and-tail row $M$, target row $R$, finite ledger $Q$, transport row $H$, continuation route $C$, provenance row $P$, and local naming row $N$.

Apply \autoref{thm:continuation-trace-small-step-readback}. A displayed endpoint read is a small-step read only when its source, mark, tail, and target rows are listed in $Q$ and its route is supplied by $C$.

Apply \autoref{thm:continuation-trace-non-escape-boundary} and \autoref{thm:continuation-trace-public-export}. These two results exclude host evaluators, host termination, quotient behaviours, selected evaluators, and big-step semantic objects from the public packet, so the endpoint read is exhausted by the concrete trace rows already displayed.
\end{proof}

\begin{theorem}[ContinuationTrace boundary hsame pullback]
\label{thm:continuation-trace-boundary-hsame-pullback}
Let
$$
T_0=(S_0,M_0,R_0,Q_0,H_0,C_0,P_0,N_0)
\quad\text{and}\quad
T_1=(S_1,M_1,R_1,Q_1,H_1,C_1,P_1,N_1)
$$
be accepted $\ContinuationTraceUp$ packets. A displayed boundary comparison $R_0\hsame S_1$ pulls back only through the transport rows $H_0,H_1$ and the displayed ledgers $Q_0,Q_1$. It adds no new step row and no extra endpoint outside the two accepted trace packets.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationTraceUp.ContinuationTraceCarrier\_boundary\_hsame\_pullback}
\begin{proof}
Project both packets through \autoref{def:continuation-trace-carrier}. The boundary comparison has access to $R_0$ from the first packet and $S_1$ from the second packet, while its admissible transport data is recorded by $H_0$ and $H_1$.

Use \autoref{thm:continuation-trace-small-step-readback} on each side. Step rows before the boundary are read from $Q_0$ and $C_0$, and step rows after the boundary are read from $Q_1$ and $C_1$.

Now apply \autoref{thm:continuation-trace-concatenation-readback}. The displayed $R_0\hsame S_1$ row supplies the boundary comparison between the two ledgers rather than a third ledger row. By \autoref{thm:continuation-trace-non-escape-boundary}, the comparison cannot import an external endpoint or host-level computation.
\end{proof}

\begin{theorem}[ContinuationTrace route support totality]
\label{thm:continuation-trace-route-support-totality}
For accepted packets
$$
T_0=(S_0,M_0,R_0,Q_0,H_0,C_0,P_0,N_0)
\quad\text{and}\quad
T_1=(S_1,M_1,R_1,Q_1,H_1,C_1,P_1,N_1),
$$
every consumer route of their concatenated $\ContinuationTraceUp$ packet factors through exactly one of the source ledgers $Q_0$ or $Q_1$, together with the displayed boundary row $R_0\hsame S_1$. The full route remains a route over $\BHist$, $\BMark$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
Begin with the two accepted carriers of \autoref{def:continuation-trace-carrier}. Their route support is displayed by the two finite ledgers $Q_0,Q_1$, the continuation rows $C_0,C_1$, the transport rows $H_0,H_1$, provenance, and local naming.

Apply \autoref{thm:continuation-trace-small-step-readback} separately to the two packets. A consumer route whose read lies before the boundary is supported by $Q_0$, and a consumer route whose read lies after the boundary is supported by $Q_1$.

Apply \autoref{thm:continuation-trace-concatenation-readback} and the boundary pullback of \autoref{thm:continuation-trace-boundary-hsame-pullback}. The displayed $R_0\hsame S_1$ row is the only boundary support, so the concatenated route has no third source ledger.

Finally use \autoref{thm:continuation-trace-public-export}. The public packet is still the finite BEDC trace packet, hence the complete route support is over $\BHist$, $\BMark$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{proof}

\begin{theorem}[ContinuationTrace route composition determinacy]
\label{thm:continuation-trace-route-composition-determinacy}
For accepted packets
$$
T_0=(S_0,M_0,R_0,Q_0,H_0,C_0,P_0,N_0),\quad
T_1=(S_1,M_1,R_1,Q_1,H_1,C_1,P_1,N_1),\quad
T_2=(S_2,M_2,R_2,Q_2,H_2,C_2,P_2,N_2),
$$
suppose the displayed boundary rows match $R_0\hsame S_1$ and $R_1\hsame S_2$. Then every consumer route of the two-step concatenated $\ContinuationTraceUp$ packet factors through exactly one source ledger among $Q_0,Q_1,Q_2$ together with the two displayed boundary rows. The selected source ledger and the resulting public route are independent of whether the first boundary $R_0\hsame S_1$ or the second boundary $R_1\hsame S_2$ is assembled first.

The composed packet still exports no host evaluator, host termination predicate, quotient behaviour, or big-step semantic object.
\end{theorem}
\begin{proof}
Apply \autoref{thm:continuation-trace-concatenation-readback} to the pair $(T_0,T_1)$ and then to the resulting packet with $T_2$. The first assembly contributes exactly the ledgers $Q_0,Q_1$ and the boundary row $R_0\hsame S_1$; the second assembly contributes $Q_2$ and the boundary row $R_1\hsame S_2$.

Apply the same readback in the other order, first to $(T_1,T_2)$ and then to $T_0$ with that packet. The visible route inventory is again $Q_0,Q_1,Q_2$ plus the two displayed boundary rows.

Use \autoref{thm:continuation-trace-boundary-hsame-pullback} for each boundary. Each $\hsame$ row pulls back only to the adjacent trace ledgers and does not add a third boundary source or an external endpoint.

Finally apply \autoref{thm:continuation-trace-route-support-totality} on the assembled finite packet. Every consumer route chooses exactly one of the three source ledgers, while the two boundary rows only glue adjacent endpoints. The non-escape boundary remains the one already stated for continuation traces, so host evaluators, termination predicates, quotient behaviours, and big-step semantics stay outside the public route.
\end{proof}

\closureat{ContinuationTraceUp}{seedStr}

\begin{closurestatus}{\ContinuationTraceUp}
  \constructivestory{A $\ContinuationTraceUp$ packet is generated from finite source-history rows, mark-and-tail route rows, target-history rows, trace ledgers, displayed $\hsame$ transports, $\Cont$ routes, package provenance, and a local naming row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The chapter specifies the finite continuation-trace carrier, its NameCert obligations, small-step readback, non-escape boundary, and public export over displayed BEDC rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean formalization, bridge checking, host evaluator semantics, host termination, quotient behaviours, or big-step semantics.}
  \upgradepath{Scoped closure requires a Lean carrier and checked readback theorem for the finite $\ContinuationTraceUp$ trace packet.}
\end{closurestatus}
