\chapter{A Concrete Naming Certificate for $\StreamLimitReflectionUp$}
\label{ch:concrete-instances-streamlimitreflection-namecert}
\origin{human}

The $\StreamLimitReflectionUp$ interface records the reflection-limit boundary in the countable-name layer. It packages a finite observation schedule for regular rational names, the RealUp seal row available at the same finite site, and a structural code row for the internal $\mathrm{CIC}^{*}$ copy, while keeping runtime execution and truth classification outside the packet.

The reflection packet consumes \autoref{ch:concrete-instances-streamname-namecert} for scheduled finite windows, \autoref{ch:concrete-instances-regseqrat-namecert} for regular rational readback, and \autoref{ch:concrete-instances-real-namecert} for the finite $\RealUp$ seal. These are substantive carrier rows of the packet; runtime execution, truth classification, quotient streams, selected limits, and host real equality remain outside the packet.

\begin{definition}[StreamLimitReflection carrier]
\label{def:stream-limit-reflection-carrier}
A $\StreamLimitReflectionUp$ carrier is a finite $\BHist$ packet
$$
Q=(S,R,E,K,T,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ observation schedule, listing the finite countable-name window queried by the packet;
\item $R$ is the $\RegSeqRatUp$ regularity row read over that schedule;
\item $E$ is the $\RealUp$ seal row attached to the finite regular-name readback;
\item $K$ is an internal $\mathrm{CIC}^{*}$ structural-code row for formation, recursor, and certificate syntax visible at this site;
\item $T$ records runtime-boundary and truth-boundary ledger entries, separating structural codes from an executing checker and from an internal truth classifier;
\item $H$ stores the componentwise $\hsame$ routes for $S,R,E,K,T$;
\item $C$ stores the displayed $\Cont$ routes for reading the schedule, regularity row, RealUp seal, structural-code row, and boundary ledger;
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\StreamLimitReflectionUp}$ row.
\end{enumerate}
The carrier exports finite structural observations and explicit non-closure ledgers. It stores no internal runtime, no truth predicate, no quotient stream, no selected limit, and no host real equality.
\end{definition}

\begin{theorem}[StreamLimitReflection NameCert obligations]
\label{thm:stream-limit-reflection-namecert-obligations}
The local $\NameCert_{\StreamLimitReflectionUp}$ surface for the carrier of \autoref{def:stream-limit-reflection-carrier} consists of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $Q=(S,R,E,K,T,H,C,P,N)$;
\item classifier transport by componentwise $\hsame$ and $\Cont$ on the stream schedule, regularity row, RealUp seal, structural-code row, boundary ledger, package row, and local naming row;
\item countable-name handoff from $S$ to the regular rational readback $R$ and the RealUp seal $E$;
\item structural-code separation, which reads $K$ only as $\mathrm{CIC}^{*}$ formation and recursor syntax, not as an executing checker;
\item boundary non-escape, which forces runtime and truth claims to pass through the ledger $T$ rather than through a hidden object-language predicate.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is tuple projection. The rows $S,R,E,K,T,H,C,P,N$ are all displayed coordinates of the same finite $\BHist$ packet.

Classifier transport is componentwise. The stored $\hsame$ routes compare the schedule, regularity, seal, structural-code, ledger, package, and local naming rows, while the $\Cont$ routes record the allowed reads among those rows.

The countable-name handoff is then finite. The observation schedule $S$ exposes the requested stream window, $R$ records the regular rational row over that window, and $E$ records the RealUp seal that can be named from the same readback.

The structural row $K$ is only syntax for the internal copy. The ledger $T$ records that no coordinate executes that syntax and no coordinate classifies BEDC truth. Thus the certificate exports structural finite observations and explicit non-closure ledgers, not a runtime, truth predicate, quotient stream, selected limit, or host real equality.
\end{proof}

\begin{theorem}[StreamLimitReflection runtime boundary]
\label{thm:stream-limit-reflection-runtime-boundary}
Every runtime-facing consumer of an accepted $\StreamLimitReflectionUp$ carrier factors through $S,R,E,K,T,H,C,P,N$. It may read the structural $\mathrm{CIC}^{*}$ code row and the boundary ledger, but it cannot obtain an internal evaluator, checker, execution semantics, quotient stream, selected limit, or host real equality from the packet.
\end{theorem}
\begin{proof}
Project the accepted carrier. The only row that mentions the host calculus is $K$, and that row is structural syntax: formation, recursor, and certificate-code data.

The boundary ledger $T$ records that execution of such syntax is not a coordinate of the carrier. The transport rows $H$ and $C$ can move and read only the displayed finite rows, so they cannot create an evaluator or checker.

The regular-name rows do not change this boundary. They expose the countable schedule, regular rational readback, and RealUp seal, but none of these rows contains a quotient stream, selected limit, host equality test, or runtime semantics. Hence every runtime-facing read remains outside the finite packet.
\end{proof}

\begin{theorem}[StreamLimitReflection truth non-closure]
\label{thm:stream-limit-reflection-truth-nonclosure}
Every truth-facing consumer of an accepted $\StreamLimitReflectionUp$ carrier reads the structural code row $K$ and the truth-boundary entries of $T$ only as finite ledger data. The packet does not define a BEDC truth predicate for the represented $\mathrm{CIC}^{*}$ sentences and does not turn the RealUp seal $E$ into host real equality or completed-limit selection.
\end{theorem}
\begin{proof}
Begin with the structural-code row. By \autoref{def:stream-limit-reflection-carrier}, $K$ names formation, recursor, and certificate syntax for the internal copy, not a truth classifier over that syntax.

Next read the truth-boundary entries of $T$. They mark truth-total classification as external to the packet, so a consumer may cite the boundary but cannot convert it into an object-language truth predicate.

Finally inspect the countable-name side. The RealUp seal $E$ is attached to the finite regular-name readback $R$ over schedule $S$. It seals the displayed name site only; it supplies neither host real equality nor a selected completed limit. Therefore truth-facing exports remain finite ledger exports.
\end{proof}
