\chapter{A Concrete Naming Certificate for $\FactorUp$}
\label{ch:concrete-instances-factor-namecert}

The factor interface $\FactorUp$ packages a von Neumann algebra with trivial centre, classified into types $\mathrm{I}$, $\mathrm{II}_1$, $\mathrm{II}_\infty$, $\mathrm{III}$. It depends on $\NameCert_{\VonNeumannAlgUp}$ (\autoref{ch:concrete-instances-vonneumannalgebra-namecert}).

\section{Carrier definition}
\label{sec:factor-carrier}

\begin{definition}[Factor BHist source packet]
\label{def:factor-bhist-source-packet}
A $\FactorUp$ source packet is a $\mathsf{BHist}$ row carrying a
$\VonNeumannAlgUp$ dependency row, a displayed centre row, a trivial-centre
witness, and a factor-type classifier row with value in
$\mathrm{I}$, $\mathrm{II}_1$, $\mathrm{II}_\infty$, or $\mathrm{III}$. The
carrier accepts exactly those packets whose algebra component is accepted by
$\NameCert_{\VonNeumannAlgUp}$, whose centre witness is transported by the
same $\hsame$ evidence, and whose type row is recorded in the visible ledger.
\end{definition}

\begin{theorem}[Factor carrier trivial-centre obligation]
\label{thm:factor-carrier-trivial-centre-obligation}
Every accepted $\FactorUp$ carrier row projects to a
$\VonNeumannAlgUp$ carrier row together with a centre witness whose only
visible carrier is the scalar endpoint of the source algebra. Conversely, a
$\VonNeumannAlgUp$ carrier row, a displayed centre row, and a trivial-centre
witness transported through the same $\hsame$ comparison repack as a
$\FactorUp$ carrier row. No host equality of algebras or ambient Hilbert-space
realization is read by this obligation.
\end{theorem}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_trivial\_centre\_obligation}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_carrier\_trivial\_centre\_obligation}
\begin{proof}
Project the dependency row from the source packet of
\autoref{def:factor-bhist-source-packet}. The $\NameCert_{\VonNeumannAlgUp}$
row supplies the algebra carrier and the classifier used to compare its
visible history.

The trivial-centre field is then read as a displayed witness over that same
history. Transport along $\hsame$ preserves the centre row because the packet
stores the centre witness beside the algebra dependency rather than as a host
property.

For the converse direction, place the algebra dependency, centre row, and
trivial-centre witness into the packet constructor and apply $\Cont$ to the
shared history comparison. The result is exactly the factor carrier surface.
\end{proof}

\begin{theorem}[Factor type classifier stability obligation]
\label{thm:factor-type-classifier-stability-obligation}
The factor-type classifier row of a $\FactorUp$ packet is stable under
accepted $\hsame$ replacement of the underlying $\VonNeumannAlgUp$ history.
If two source packets compare through the algebra classifier, the transported
trivial-centre witnesses determine the same displayed type row among
$\mathrm{I}$, $\mathrm{II}_1$, $\mathrm{II}_\infty$, and $\mathrm{III}$.
\end{theorem}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_type\_classifier\_stability\_obligation}
\begin{proof}
Start with the algebra comparison supplied by
$\NameCert_{\VonNeumannAlgUp}$. It transports the carrier, operation, and
classifier rows of the source von Neumann algebra through the accepted
$\hsame$ evidence.

The factor packet keeps the type classifier in the same ledger as the
trivial-centre witness. Therefore the transported centre witness is read
before the type row is compared, so the classification cannot change without
leaving the displayed packet.

Repacking the transported algebra row, centre witness, and type row gives the
same $\FactorUp$ classifier surface for the target packet.
\end{proof}

\begin{theorem}[Factor ledger exactness obligation]
\label{thm:factor-ledger-exactness-obligation}
The $\FactorUp$ ledger consists exactly of the
$\NameCert_{\VonNeumannAlgUp}$ dependency row, the $\mathsf{BHist}$ algebra
carrier row, the centre row, the trivial-centre witness row, the factor-type
classifier row, and their $\hsame$ and $\Cont$ transport evidence. Coverage,
soundness, and completeness hold for precisely those rows; spectral
decomposition theorems, representation theorems, measure-class data, and
standard bridge rows are excluded.
\end{theorem}
\begin{proof}
Coverage projects an accepted packet into its visible ledger entries: the
von Neumann algebra dependency, the algebra carrier, the centre row, the
trivial-centre witness, the factor-type row, and the transport witnesses.

Soundness reads those entries back through the packet constructor. The
dependency certificate justifies the algebra component, while $\hsame$ and
$\Cont$ carry the centre and type rows across the accepted history comparison.

Completeness follows because the packet has no ledger coordinate for spectral
decomposition, representation, measure class, or bridge data. Any accepted row
therefore exposes exactly the listed entries and no larger analytic surface.
\end{proof}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_ledger\_exactness\_obligation}

\begin{theorem}[Factor root threshold unblock surface]
\label{thm:factor-root-threshold-unblock-surface}
The rows of \autoref{def:factor-bhist-source-packet},
\autoref{thm:factor-carrier-trivial-centre-obligation},
\autoref{thm:factor-type-classifier-stability-obligation}, and
\autoref{thm:factor-ledger-exactness-obligation} form the dependency-ready
surface for $\FactorUp$. A downstream certificate may consume the
$\mathsf{BHist}$ carrier, $\NameCert_{\VonNeumannAlgUp}$ dependency,
trivial-centre witness, factor-type classifier, and exact ledger exclusions,
but it must supply any standard bridge or analytic classification theorem
separately.
\end{theorem}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_root\_threshold\_unblock\_surface}
\begin{proof}
The definition fixes the source packet and names every row that can enter the
factor certificate. The carrier obligation recovers the algebra dependency
and the trivial-centre witness from any accepted packet.

The stability obligation gives the classifier transport needed by downstream
NameCert rows. The ledger exactness obligation then closes the readback by
excluding every row outside the displayed packet.

Combining these three obligations gives a concrete finite-history interface
over $\mathsf{BHist}$ rather than an empty chapter shell. Later bridges may
attach to this surface, but they are not part of the factor packet itself.
\end{proof}

\section{The certificate}
\label{sec:factor-certificate}

\begin{theorem}[Factor type row no-confusion]
\label{thm:factor-type-row-no-confusion}
An accepted $\FactorUp$ packet cannot expose two distinct visible factor-type
rows under the same transported trivial-centre witness. If the packet carries a
$\NameCert_{\VonNeumannAlgUp}$ dependency, a $\mathsf{BHist}$ algebra carrier,
a centre row, a trivial-centre witness transported by the displayed $\hsame$
evidence, and visible type rows $T$ and $T'$, then the certificate ledger
identifies $T$ and $T'$ as the same row among $\mathrm{I}$, $\mathrm{II}_1$,
$\mathrm{II}_\infty$, and $\mathrm{III}$.
\end{theorem}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_type\_row\_no\_confusion}
\begin{proof}
Project the accepted packet through
\autoref{thm:factor-carrier-trivial-centre-obligation}. The projection gives one
von Neumann algebra dependency and one transported trivial-centre witness over
the displayed centre row.

Now read the type coordinates through
\autoref{thm:factor-type-classifier-stability-obligation}. The classifier row is
stored in the same ledger as the transported centre witness, so two visible type
rows under that witness must be compared by the same $\hsame$ evidence.

Finally apply \autoref{thm:factor-ledger-exactness-obligation}. Since the ledger
has exactly one factor-type coordinate and no hidden representation or spectral
coordinate, the two displayed type rows are the same certificate row.
\end{proof}

\begin{theorem}[Factor centre ledger transport determinacy]
\label{thm:factor-center-ledger-transport-determinacy}
For a $\FactorUp$ packet, $\hsame$ transport of the
$\NameCert_{\VonNeumannAlgUp}$ dependency, the $\mathsf{BHist}$ algebra carrier,
the centre row, the trivial-centre witness, and the $\Cont$ provenance
determines the transported $\FactorUp$ centre ledger. No additional
representation row, spectral row, or ambient Hilbert-space equality can change
the transported ledger.
\end{theorem}
\begin{proof}
Start from the dependency row named by
\autoref{def:factor-bhist-source-packet}. Its $\NameCert_{\VonNeumannAlgUp}$
component transports the algebra carrier through the displayed $\hsame$ evidence.

Transport the centre row and the trivial-centre witness along the same history
comparison. The $\Cont$ provenance records that these rows move together as one
factor packet rather than as independent host data.

The ledger exactness theorem
\autoref{thm:factor-ledger-exactness-obligation} then leaves no further centre
coordinate to choose. The transported dependency, carrier, centre,
trivial-centre witness, and $\Cont$ provenance therefore determine the
transported centre ledger.
\end{proof}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_centre\_ledger\_transport\_determinacy}

\begin{theorem}[Factor VonNeumann dependency consumer boundary]
\label{thm:factor-vonneumann-dependency-consumer-boundary}
Every downstream consumer of the $\FactorUp$ certificate may read only the
$\NameCert_{\VonNeumannAlgUp}$ dependency, the $\mathsf{BHist}$ algebra carrier,
the centre row, the trivial-centre witness, the factor-type classifier, and the
$\hsame/\Cont$ ledger. It may not read representation data, spectral
decomposition data, measure-class data, ambient Hilbert-space equality, or any
row not displayed by the factor source packet.
\end{theorem}
\begin{proof}
The source packet of \autoref{def:factor-bhist-source-packet} lists the complete
visible input surface: dependency, carrier, centre, trivial-centre witness, type
classifier, and transport provenance.

Apply \autoref{thm:factor-ledger-exactness-obligation} to the consumer read. The
coverage direction supplies exactly those visible rows, while soundness and
completeness repack only rows of the same listed kinds.

The excluded analytic data have no coordinate in the packet and no entry in the
ledger. Hence a consumer that remains inside the $\FactorUp$ certificate can read
the displayed dependency and centre surface, but cannot inspect representation
or spectral information.
\end{proof}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_vonneumann\_dependency\_consumer\_boundary}

\begin{theorem}[FactorUp public NameCert export]
\label{thm:factor-public-namecert-export}
The source packet of \autoref{def:factor-bhist-source-packet}, the
trivial-centre carrier obligation of
\autoref{thm:factor-carrier-trivial-centre-obligation}, the classifier
stability obligation of
\autoref{thm:factor-type-classifier-stability-obligation}, the ledger
exactness obligation of \autoref{thm:factor-ledger-exactness-obligation}, and
the root threshold surface of \autoref{thm:factor-root-threshold-unblock-surface}
together export the public $\NameCert_{\FactorUp}$ surface.

Consumers of this certificate may read only the
$\NameCert_{\VonNeumannAlgUp}$ dependency row, the centre row, the
trivial-centre witness, the factor-type classifier, the $\hsame/\Cont$
transport rows, and the ledger exclusions listed by the packet. Representation
theory, spectral decomposition, measure-class data, and standard bridge rows
remain outside the certificate.
\end{theorem}
\begin{proof}
The source packet fixes the only rows available to $\FactorUp$: a
$\VonNeumannAlgUp$ dependency, a displayed centre row, a trivial-centre
witness, a factor-type classifier, and the shared transport ledger.

Apply the trivial-centre carrier obligation to project an accepted packet to
the von Neumann algebra carrier and its scalar-centre witness. Apply the
classifier stability obligation to transport the displayed factor type along
the same $\hsame$ comparison.

The ledger exactness obligation then says that the visible rows are exactly the
dependency, centre, trivial-centre, classifier, $\hsame$, and $\Cont$ entries.
The root threshold surface packages these rows for downstream consumers, so the
public $\NameCert_{\FactorUp}$ surface contains precisely those entries and no
representation-theoretic, spectral, measure-class, or bridge datum.
\end{proof}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_public\_namecert\_export}

\begin{theorem}[FactorUp public bridge boundary]
\label{thm:factor-public-bridge-boundary}
The public $\NameCert_{\FactorUp}$ surface is exactly the BEDC-side boundary
available to any later standard bridge packet. It exposes the
$\NameCert_{\VonNeumannAlgUp}$ dependency, the centre row, the trivial-centre
witness, the factor-type classifier, the $\hsame/\Cont$ transport rows, and the
ledger exclusions.

It exposes no representation data, spectral decomposition, measure-class data,
ambient Hilbert-space equality, or bridge row unless those data are supplied by
a separate bridge packet.
\end{theorem}
\begin{proof}
Apply \autoref{thm:factor-public-namecert-export}. The exported public surface
already packages the von Neumann algebra dependency, centre row,
trivial-centre witness, classifier, transport provenance, and ledger
exclusions.

Next apply \autoref{thm:factor-vonneumann-dependency-consumer-boundary} to any
consumer that reads the certificate as the input face of a standard bridge. The
consumer boundary permits exactly the displayed dependency and centre surface
and blocks representation, spectral, measure-class, and Hilbert-space equality
data.

Finally apply \autoref{thm:factor-ledger-exactness-obligation}. Ledger
exactness says that no additional public row is available inside the
$\FactorUp$ source packet. Hence bridge data can enter only through a separate
bridge packet, not through the public $\NameCert_{\FactorUp}$ surface itself.
\end{proof}
\leanchecked{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_public\_bridge\_boundary}

\closureat{FactorUp}{scopedStr}[BEDC.Derived.FactorUp.FactorBHistSourcePacket\_public\_bridge\_boundary]
\closureat{FactorUp}{publicStr}[BEDC.Derived.FactorUp.FactorBHistSourcePacket\_public\_namecert\_export]
\closureat{FactorUp}{bridgedStr}[BEDC.Derived.FactorUp.FactorBHistSourcePacket\_public\_bridge\_boundary]

\begin{closurestatus}{\FactorUp}
  \constructivestory{A $\FactorUp$ row is built as a finite $\mathsf{BHist}$ packet whose visible coordinates are the $\NameCert_{\VonNeumannAlgUp}$ dependency, the algebra carrier, the centre row, the transported trivial-centre witness, the factor-type classifier, and the shared $\hsame/\Cont$ ledger. The carrier theorem reads the dependency and trivial-centre witness directly from that packet, while the surrounding certificate theorems record classifier stability, ledger exactness, consumer boundaries, and the public bridge-facing surface.}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{The public surface is the listed $\mathsf{BHist}$ source packet, trivial-centre carrier, classifier, $\VonNeumannAlgUp$ consumer rows, exported public $\NameCert_{\FactorUp}$ certificate, and the cited Lean target.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.FactorUp.FactorBHistSourcePacket\_public\_bridge\_boundary}
  \bridgestatus{paperBridge}
  \notclaimed{This chapter does not close spectral decomposition, representation theorems, measure-class data, or standard bridge rows.}
  \upgradepath{Mature closure requires finite consumer examples for the displayed $\FactorUp$ bridge surface.}
\end{closurestatus}
