\begin{theorem}[QuantumStateUp observable state boundary]
\label{thm:quantumstate-observable-state-boundary}
An $\ObservableUp$ expectation row may read a $\QuantumStateUp$ $\mathsf{BHist}$
packet only through the Hilbert source row $\mathcal{H}$, the projective
endpoint row $p$, the global-phase classifier $\phi$, the norm ledger $n$, and
the package provenance $\rho$ exposed by
\autoref{thm:quantumstate-projective-consumer-boundary}, together with the
observable endpoint, self-adjoint witness, spectral-data row, and expectation
row displayed by $\ObservableUp$. It may not replace the certified state input
by host vector equality, a raw quotient representative, or an expectation row
whose Hilbert source is not the shared $\mathcal{H}$ endpoint.
\end{theorem}
\begin{proof}
Project the accepted quantum-state packet through
\autoref{thm:quantumstate-projective-consumer-boundary}. The only state-side
rows visible to a downstream consumer are $\mathcal{H}$, $p$, $\phi$, $n$, and
$\rho$.

Now apply the expectation boundary of
\autoref{thm:observable-quantumstate-expectation-boundary}. The observable
packet contributes its operator endpoint, self-adjoint witness, spectral-data
row, and expectation row, and that theorem requires the expectation input to be
compatible with the same Hilbert source.

Combining the two projections gives the displayed boundary. Any host vector
equality, quotient representative, or Hilbert-mismatched expectation row would
have to enter through a field not present in one of the two cited packet
surfaces, so it is not readable by the consumer.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix boundary]
\label{thm:quantumstate-densitymatrix-boundary}
A $\QuantumStateUp$ $\mathsf{BHist}$ packet does not itself supply a
$\DensityMatrixUp$ row. A density-matrix consumer of a pure projective state
must add, as separate displayed rows, trace-class membership, positivity,
trace-one evidence, and any rank-one projection bridge that turns the
projective endpoint into a positive trace-class trace-one operator. These rows
are not part of the Hilbert source, projective endpoint, phase classifier, norm
ledger, or provenance exposed by
\autoref{thm:quantumstate-projective-consumer-boundary}.
\end{theorem}
\begin{proof}
Read the quantum-state packet fields from
\autoref{thm:quantumstate-projective-consumer-boundary}. They certify the
Hilbert source, projective endpoint, phase classifier, norm ledger, and package
provenance, but no field has the form of a trace-class operator on the Hilbert
carrier.

Compare this with the density carrier obligation of
\autoref{thm:densitymatrix-carrier-obligation}. A $\DensityMatrixUp$ endpoint is
accepted only when trace-class membership, positivity, and trace-one evidence
are all displayed over the Hilbert carrier.

Therefore a pure-state-to-density-matrix use must introduce the trace-class,
positivity, trace-one, and rank-one projection bridge rows at the consumer site.
The quantum-state packet can supply the named source and projective endpoint
for such a bridge, but it does not supply the density row itself.
\end{proof}

\begin{theorem}[QuantumStateUp quantum-channel input boundary]
\label{thm:quantumstate-channel-input-boundary}
A $\QuantumChannelUp$ consumer may use a $\QuantumStateUp$ packet as an input
only after a displayed $\DensityMatrixUp$-compatible input row has been supplied
for the same Hilbert source. Channel image closure can then read the
$\DensityMatrixUp$ row and the CPTP carrier of the channel, but it cannot read
host vector equality, a raw pure-state quotient, or a direct channel action on
the projective endpoint.
\end{theorem}
\begin{proof}
First apply \autoref{thm:quantumstate-densitymatrix-boundary}. The
quantum-state packet alone has no density-matrix row, so a channel input must
pass through a separately displayed trace-class, positivity, trace-one, and
rank-one projection bridge package.

Next use the CPTP carrier of \autoref{def:quantumchannel-cptp-carrier}. Its
source type is the trace-class carrier over the input Hilbert space, and its
density-state action is stated over $\DensityMatrixUp$ inputs rather than over
projective representatives.

Finally apply the density-matrix image lemma
\autoref{lem:quantumchannel-densitymatrix-image}. Once the compatible density
row is present, the channel image closure reads exactly that row and the CPTP
channel rows. The excluded host equality, quotient representative, and direct
projective action are outside the displayed density and channel carrier
surfaces.
\end{proof}

\begin{theorem}[ObservableUp expectation-row boundary]
\label{thm:quantumstate-observable-expectation-row-boundary}
When $\ObservableUp$ forms expectation or eigenvalue rows from a
$\QuantumStateUp$ source, it may read only the Hilbert source row
$\mathcal{H}$, the projective endpoint row $p$, the global-phase classifier
$\phi$, the norm ledger $n$, and the provenance row $\rho$ of
\autoref{def:quantumstate-bhist-carrier}. The observable consumer may combine
those rows with its own observable certificate, but it receives no
density-matrix row, measurement row, channel row, spectral row, quotient
object, or host Hilbert-vector equality from $\QuantumStateUp$ itself.
\end{theorem}
\begin{proof}
Unpack the carrier packet
$\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho)$
of \autoref{def:quantumstate-bhist-carrier}. The rows available to an
observable construction are the Hilbert source row, the projected endpoint, the
phase classifier, the norm ledger, and the provenance row.

Apply the Hilbert source boundary of
\autoref{thm:quantumstate-hilbert-source-boundary} to locate all vector,
norm, and inner-product inputs inside $\mathcal{H}$ and $\lambda_H$. Apply
\autoref{thm:quantumstate-projective-phase-classifier} and
\autoref{thm:quantumstate-global-phase-stability} to replace any phase choice
by the projective endpoint classifier.

The public surface theorem,
\autoref{thm:quantumstate-namecert-obligation-surface}, identifies the
complete exported row list. Expectation and eigenvalue rows therefore require a
separate $\ObservableUp$ certificate for observable, measurement, or spectral
data. Since none of those rows occurs in $\mathcal{Q}$, and since quotient and
host-vector equalities are excluded by the classifier boundary, the displayed
rows are the whole $\QuantumStateUp$ input boundary for this consumer.
\end{proof}

\begin{theorem}[DensityMatrixUp rank-one row boundary]
\label{thm:quantumstate-density-matrix-row-boundary}
When $\DensityMatrixUp$ forms a rank-one projector row from a
$\QuantumStateUp$ source, it may read only the projective endpoint row $p$ and
the norm-one ledger $n$, together with the provenance row $\rho$ that records
their common packet. The density-matrix consumer may not read a host quotient,
an ambient vector equality, a measurement row, a channel row, a spectral row,
or any density-matrix row unless that row is supplied by its own downstream
certificate.
\end{theorem}
\begin{proof}
Unpack \autoref{def:quantumstate-bhist-carrier}. The rank-one projector input
is not a new field of $\mathcal{Q}$; the packet exposes only the projective
endpoint $p$, the norm-one ledger $n$, the inherited classifiers, and the
provenance row $\rho$.

Use \autoref{thm:quantumstate-hilbert-source-boundary} to read $n$ through the
Hilbert source row rather than through an ambient vector equality. Use
\autoref{thm:quantumstate-projective-phase-classifier} to read $p$ through the
projective endpoint classifier, and use
\autoref{thm:quantumstate-global-phase-stability} to ensure that replacing a
unit-vector representative by a certified phase-equivalent representative does
not change the exposed projector input.

Finally apply
\autoref{thm:quantumstate-namecert-obligation-surface}. Its exactness clause
contains no density-matrix, measurement, channel, or spectral row, and it
contains no quotient object or host-vector equality. Thus any matrix row,
operator row, or spectral decomposition must come from the
$\DensityMatrixUp$ certificate itself, while $\QuantumStateUp$ contributes
only the projective endpoint, norm ledger, and provenance needed to form the
rank-one boundary.
\end{proof}

\begin{theorem}[QuantumChannelUp pure-state input boundary]
\label{thm:quantumstate-channel-pure-state-input-boundary}
When $\QuantumChannelUp$ consumes pure-state input or output rows from a
$\QuantumStateUp$ source, it may use the exported $\QuantumStateUp$ classifier
and provenance only: the Hilbert source row $\mathcal{H}$, the projective
endpoint row $p$, the global-phase classifier $\phi$, the norm ledger $n$, and
the provenance row $\rho$. Channel action, density-matrix data, measurement
data, spectral data, quotient objects, and host Hilbert-vector equalities must
be supplied by the channel-side certificate rather than by
$\QuantumStateUp$.
\end{theorem}
\begin{proof}
Unpack the packet of \autoref{def:quantumstate-bhist-carrier}. A pure-state
input or output row can name the state only through the Hilbert source row,
the projective endpoint, the phase classifier, the norm ledger, and the
provenance row.

Apply \autoref{thm:quantumstate-hilbert-source-boundary} to keep vector and
norm data inside the consumed Hilbert certificate. Apply
\autoref{thm:quantumstate-projective-phase-classifier} to expose equality of
pure states only through the projective/global-phase classifier, and apply
\autoref{thm:quantumstate-global-phase-stability} to transport that classifier
across certified presentations.

The public obligation surface of
\autoref{thm:quantumstate-namecert-obligation-surface} is exact. It exports no
channel map, no density-matrix row, no measurement row, no spectral row, and
no quotient or host-vector equality. Therefore $\QuantumChannelUp$ may attach
its channel certificate to the exported classifier and provenance, but all
channel action and output certification remains a downstream obligation.
\end{proof}
