\chapter{A Concrete Naming Certificate for $\QuantumStateUp$}
\label{ch:concrete-instances-quantumstate-namecert}

The quantum-state interface $\QuantumStateUp$ packages a unit vector in a Hilbert space carrier together with the equivalence under global phase. It depends on $\NameCert_{\HilbertUp}$ (\autoref{ch:concrete-instances-hilbert-namecert}) and $\NameCert_{\ProjectiveSpaceUp}$ (\autoref{ch:concrete-instances-projectivespace-namecert}).

\section{Carrier definition}
\label{sec:quantumstate-carrier}

\begin{definition}[QuantumStateUp BHist carrier]
\label{def:quantumstate-bhist-carrier}
A $\QuantumStateUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho).
$$
The row $\mathcal{H}$ is a consumed $\NameCert_{\HilbertUp}$ row. The row
$\mathcal{P}$ is a consumed $\NameCert_{\ProjectiveSpaceUp}$ row over the
displayed projective line determined by $\mathcal{H}$. The endpoint $v$ is the
unit-vector row projected from $\mathcal{H}$, $n$ is the norm-one ledger row,
$\phi$ is the global-phase row, and $p$ is the projective-line endpoint row
projected from $\mathcal{P}$.

The rows $\lambda_H$ and $\lambda_P$ are the inherited Hilbert and projective
classifier rows, respectively. The row $\rho$ is the $\mathsf{Pkg}$ provenance
record witnessing that the two consumed certificates and all displayed endpoint
rows belong to the same finite packet. No carrier datum outside
$\mathcal{H}$, $\mathcal{P}$, $v$, $n$, $\phi$, $p$, $\lambda_H$, $\lambda_P$,
and $\rho$ is part of the public $\QuantumStateUp$ row.
\end{definition}

\section{The certificate}
\label{sec:quantumstate-certificate}

\begin{theorem}[QuantumStateUp Hilbert source boundary]
\label{thm:quantumstate-hilbert-source-boundary}
For every carrier packet $\mathcal{Q}$ of
\autoref{def:quantumstate-bhist-carrier}, all vector, norm, and inner-product
rows used by the $\QuantumStateUp$ interface are projected from the consumed
$\NameCert_{\HilbertUp}$ row $\mathcal{H}$. In particular, the visible vector
endpoint $v$, the norm-one ledger $n$, and every inner-product row used to test
unit length are read through $\mathcal{H}$ and the inherited classifier
$\lambda_H$, not through an ambient Hilbert-space carrier.
\end{theorem}
\begin{proof}
The traditional target is a Hilbert-space unit vector carrying the usual norm
and inner-product data. The BEDC source is the consumed
$\NameCert_{\HilbertUp}$ row $\mathcal{H}$, and the carrier choice is the finite
packet $\mathcal{Q}$ of \autoref{def:quantumstate-bhist-carrier}.

Unpack the definition of $\mathcal{Q}$. The only fields naming Hilbert-side
data are $\mathcal{H}$, $v$, $n$, and $\lambda_H$, together with the provenance
row $\rho$. Thus the classifier choice is the inherited Hilbert classifier
$\lambda_H$, stability is $\hsame$ transport through that classifier, and the
ledger is the norm-one row $n$.

The core theorem list for this boundary consists of the visible endpoint
projection, the norm-one ledger projection, and the inner-product projection.
Exactness says that every Hilbert-side row visible to $\QuantumStateUp$ is one
of those projected rows. There is no standard bridge supplied here, and the
status is a paper obligation for the $\NameCert_{\QuantumStateUp}$ Hilbert
source boundary.
\end{proof}

\begin{theorem}[QuantumStateUp projective phase classifier]
\label{thm:quantumstate-projective-phase-classifier}
The classified $\QuantumStateUp$ rows are exactly the Hilbert unit-vector rows
$v$ whose projective endpoints $p$ are related by the global-phase row $\phi$
and the $\ProjectiveSpaceUp$ classifier $\lambda_P$. Equivalently, two carrier
packets
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho)
$$
and
$$
\mathcal{Q}'=(\mathcal{H}',\mathcal{P}',v',n',\phi',p',\lambda'_H,\lambda'_P,\rho')
$$
classify the same quantum state precisely when the Hilbert endpoint rows are
unit-vector rows and the projective endpoints are identified by the displayed
global-phase/projective-space classifier rows. The classifier records no host
vector equality, no independent Hilbert-space quotient, and no primitive
quotient object beyond the projective scaling classifier supplied by
$\mathcal{P}$.
\end{theorem}
\begin{proof}
The traditional target is equality of pure quantum states modulo global phase.
The BEDC source is the pair of consumed certificates
$\NameCert_{\HilbertUp}$ and $\NameCert_{\ProjectiveSpaceUp}$. The carrier
choice is the packet $\mathcal{Q}$, while the classifier choice is the pair
formed by the global-phase row $\phi$ and the projective classifier
$\lambda_P$.

For the forward reading, a classified $\QuantumStateUp$ row first exposes a
Hilbert endpoint $v$ and its norm-one ledger $n$ through
\autoref{thm:quantumstate-hilbert-source-boundary}. It then exposes the
projective endpoint $p$ through $\mathcal{P}$. The row $\phi$ records the
allowed phase change, and $\lambda_P$ records the projective classifier that
accepts the resulting endpoint comparison.

For the reverse reading, a Hilbert unit-vector endpoint with a norm-one ledger
and a projective endpoint accepted by $\phi$ and $\lambda_P$ supplies all fields
of \autoref{def:quantumstate-bhist-carrier}. Stability is componentwise
$\hsame$ transport through $\lambda_H$ and $\lambda_P$, the ledger is $n$
together with the phase row $\phi$, and exactness says that no host quotient is
read. The core theorem list is this classifier row together with the Hilbert
source boundary. The standard bridge is absent, and the status is a paper
obligation for the $\NameCert_{\QuantumStateUp}$ classifier.
\end{proof}

\begin{theorem}[QuantumStateUp global phase stability]
\label{thm:quantumstate-global-phase-stability}
Let $\mathcal{Q}$ and $\mathcal{Q}'$ be two carrier packets of
\autoref{def:quantumstate-bhist-carrier}. If the Hilbert rows
$\mathcal{H},v,n,\lambda_H$ and the projective rows
$\mathcal{P},p,\lambda_P$ are transported componentwise by $\hsame$, then the
global-phase classifier row is preserved and the norm-one ledger remains a
valid $\QuantumStateUp$ ledger row. Thus $\hsame$ transport of the consumed
Hilbert and projective certificates preserves the phase classifier and the
norm-one condition.
\end{theorem}
\begin{proof}
The traditional target is invariance of a pure state under change of certified
presentation. The BEDC source is the pair of source certificates
$\mathcal{H}$ and $\mathcal{P}$, the carrier choice is the packet
$\mathcal{Q}$, and the classifier choice is $\lambda_H$, $\lambda_P$, and the
phase row $\phi$.

Transport the Hilbert side first. The $\hsame$ witnesses for
$\mathcal{H}$, $v$, $n$, and $\lambda_H$ move the unit-vector endpoint and the
norm-one ledger through the Hilbert classifier without opening any host vector
equality.

Transport the projective side next. The $\hsame$ witnesses for
$\mathcal{P}$, $p$, and $\lambda_P$ move the projective endpoint and its
classifier row. The phase row $\phi$ is preserved because its source and target
endpoints are exactly the transported Hilbert and projective endpoints.

The ledger consists of the norm-one row, the phase row, and the provenance
row. The core theorem list is the Hilbert source boundary, the projective phase
classifier, and this transport row. Exactness says that every preserved row is
one of the displayed packet fields. No standard bridge is supplied, and the
status is a paper obligation for $\NameCert_{\QuantumStateUp}$ stability.
\end{proof}

\begin{theorem}[QuantumStateUp public obligation surface]
\label{thm:quantumstate-namecert-obligation-surface}
The public $\NameCert_{\QuantumStateUp}$ surface consists exactly of the
carrier packet of \autoref{def:quantumstate-bhist-carrier}, the projective
phase classifier of \autoref{thm:quantumstate-projective-phase-classifier}, the
stability row of \autoref{thm:quantumstate-global-phase-stability}, the
norm-one ledger, the projective exactness predicate, and the hidden
global-phase rows needed to witness the endpoint comparison. These rows form
the carrier, classifier, stability, ledger, exactness, and hidden
global-phase obligations exported by $\QuantumStateUp$. The surface contains
no density-matrix row, measurement row, channel row, or spectral row.
\end{theorem}
\begin{proof}
The traditional target is the pure-state naming certificate. The BEDC source
is the pair $\NameCert_{\HilbertUp}$ and $\NameCert_{\ProjectiveSpaceUp}$, and
the carrier choice is the displayed packet $\mathcal{Q}$. The classifier choice
is the global-phase/projective classifier, while stability is
\autoref{thm:quantumstate-global-phase-stability}.

The ledger is finite: it contains the norm-one row $n$, the phase row $\phi$,
the two inherited classifier rows $\lambda_H$ and $\lambda_P$, and the
provenance row $\rho$. The core theorem list is the Hilbert source boundary,
the projective phase classifier, and the global-phase stability row.

Exactness says that every public $\QuantumStateUp$ row is assembled from those
fields and that every hidden phase row is used only to classify projective
endpoints. The named dependency certificates expose no density-matrix,
measurement, channel, or spectral row at this site. The standard bridge field
is empty. The status is a paper obligation for the $\NameCert_{\QuantumStateUp}$
public surface.
\end{proof}

\begin{theorem}[QuantumStateUp projective consumer boundary]
\label{thm:quantumstate-projective-consumer-boundary}
Downstream $\ObservableUp$, $\DensityMatrixUp$, and $\QuantumChannelUp$
consumers of $\NameCert_{\QuantumStateUp}$ may read only the Hilbert source row
$\mathcal{H}$, the projective endpoint row $p$, the global-phase classifier
$\phi$, the norm ledger $n$, and the package provenance $\rho$. They may not
read a host Hilbert-vector equality, a quotient object, or any equality outside
the Hilbert and projective classifiers exported by
\autoref{thm:quantumstate-namecert-obligation-surface}.
\end{theorem}
\begin{proof}
The traditional target is the pure-state input boundary for observable,
density-matrix, and quantum-channel constructions. The BEDC source is the
public $\NameCert_{\QuantumStateUp}$ surface, the carrier choice is the packet
$\mathcal{Q}$, and the classifier choice is the pair of inherited classifiers
plus the phase row.

Read the exported rows of
\autoref{thm:quantumstate-namecert-obligation-surface}. A consumer receives the
Hilbert source row, the projective endpoint row, the phase classifier, the
norm-one ledger, and the provenance row. These are the only fields that carry
forward from the certificate.

It remains to exclude stronger inputs. Host vector equality is not a field of
\autoref{def:quantumstate-bhist-carrier}; quotient equality is replaced by the
projective classifier; and hidden phase witnesses are readable only through
the classifier row that uses them. Thus stability, ledger, exactness, and the
core theorem list are inherited from the public surface. No standard bridge is
present, and the status is a paper obligation for the downstream consumer
boundary.
\end{proof}

\begin{theorem}[QuantumStateUp provenance row exactness]
\label{thm:quantumstate-provenance-row-exactness}
For every carrier packet
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho)
$$
of \autoref{def:quantumstate-bhist-carrier}, the provenance row $\rho$
partitions the public rows of $\mathcal{Q}$ exactly into the consumed
$\NameCert_{\HilbertUp}$ packet $\mathcal{H}$, the consumed
$\NameCert_{\ProjectiveSpaceUp}$ packet $\mathcal{P}$, the displayed
norm row $n$, phase row $\phi$, projective endpoint row $p$, Hilbert
endpoint row $v$, and inherited classifier rows $\lambda_H,\lambda_P$.
No observable row, density-matrix row, channel row, spectral row,
host-vector-equality row, or quotient row belongs to the public
$\mathsf{BHist}$ packet witnessed by $\rho$.
\end{theorem}
\begin{proof}
Use the carrier display in \autoref{def:quantumstate-bhist-carrier} as the
row inventory. The packet has the two consumed $\NameCert$ rows
$\mathcal{H}$ and $\mathcal{P}$, the endpoint and ledger rows
$v,n,\phi,p$, the inherited classifiers $\lambda_H,\lambda_P$, and the
provenance row $\rho$. The row $\rho$ is therefore the $\mathsf{Pkg}$
record tying exactly those rows into one finite $\mathsf{BHist}$ packet.

The Hilbert portion is supplied by
\autoref{thm:quantumstate-namecert-obligation-surface}: it exposes the
carrier, classifier, stability, ledger, exactness, and hidden phase rows
but no downstream observable object. The projective portion is supplied by
\autoref{thm:quantumstate-projective-phase-classifier}: it reads phase
classification through $\phi$ and $\lambda_P$, not through a host quotient.

Finally apply the consumer boundary in
\autoref{thm:quantumstate-projective-consumer-boundary}. A downstream row
may inspect only the named Hilbert, projective, phase, norm, and provenance
fields. Together with the global-phase stability theorem
\autoref{thm:quantumstate-global-phase-stability}, this proves that
$\rho$ is exact for the displayed $\NameCert$ package and excludes every
observable, density-matrix, channel, spectral, host-vector-equality, and
quotient row from the public surface.
\end{proof}

\begin{theorem}[QuantumStateUp phase ledger exhaustion]
\label{thm:quantumstate-phase-ledger-exhaustion}
Every hidden row used to classify two $\QuantumStateUp$ carrier packets is
one of the displayed phase row $\phi$, inherited Hilbert classifier
$\lambda_H$, inherited projective classifier $\lambda_P$, norm-one ledger
$n$, endpoint $\hsame$ transport row, or provenance row $\rho$ from the
carrier of \autoref{def:quantumstate-bhist-carrier}. Conversely, those
rows reconstruct exactly the projective phase classifier of
\autoref{thm:quantumstate-projective-phase-classifier} inside the consumed
$\NameCert_{\HilbertUp}$ and $\NameCert_{\ProjectiveSpaceUp}$ packets.
\end{theorem}
\begin{proof}
Start from two displayed packets
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho)
$$
and
$$
\mathcal{Q}'=(\mathcal{H}',\mathcal{P}',v',n',\phi',p',\lambda'_H,\lambda'_P,\rho').
$$
The carrier definition lists the only rows available to the classifier.
Thus a hidden classifier row must be read from the phase row, one of the
inherited classifiers, the norm ledger, the endpoint $\hsame$ transport
data, or the $\mathsf{Pkg}$ provenance record.

For exhaustion, use \autoref{thm:quantumstate-namecert-obligation-surface}
to identify the public $\NameCert_{\QuantumStateUp}$ obligations and
\autoref{thm:quantumstate-projective-consumer-boundary} to rule out
consumer access to a stronger equality. The stability row in
\autoref{thm:quantumstate-global-phase-stability} accounts for every
endpoint transport through $\hsame$, while the provenance exactness of
\autoref{thm:quantumstate-provenance-row-exactness} keeps those transports
inside the same finite $\mathsf{BHist}$ package.

For reconstruction, read the Hilbert endpoint through $\lambda_H$, read the
norm ledger through $n$, and read the projective endpoint comparison through
$\phi$ and $\lambda_P$. These are precisely the inputs named by
\autoref{thm:quantumstate-projective-phase-classifier}; repacking them with
$\rho$ recovers the same projective phase classifier and adds no hidden
row beyond the displayed ledger.
\end{proof}

\begin{theorem}[QuantumStateUp consumer readback completeness]
\label{thm:quantumstate-consumer-readback-completeness}
Every downstream $\ObservableUp$, $\DensityMatrixUp$, and
$\QuantumChannelUp$ consumer row reading $\NameCert_{\QuantumStateUp}$
factors through the five public fields named in
\autoref{thm:quantumstate-projective-consumer-boundary}: the Hilbert source
row $\mathcal{H}$, projective endpoint row $p$, global-phase classifier
$\phi$, norm ledger $n$, and package provenance $\rho$. Conversely, any
consumer depending only on those five fields is stable under
\autoref{thm:quantumstate-global-phase-stability}.
\end{theorem}
\begin{proof}
The forward direction is a readback claim. By
\autoref{def:quantumstate-bhist-carrier}, a consumer begins with a finite
$\mathsf{BHist}$ packet carried by $\mathsf{Pkg}$ provenance. By
\autoref{thm:quantumstate-namecert-obligation-surface}, the public
$\NameCert_{\QuantumStateUp}$ surface supplies the carrier, classifier,
stability, ledger, exactness, and hidden phase obligations, but it supplies
no observable, density-matrix, channel, or spectral row.

Apply \autoref{thm:quantumstate-projective-consumer-boundary}. The rows
that remain readable by $\ObservableUp$, $\DensityMatrixUp$, and
$\QuantumChannelUp$ consumers are exactly $\mathcal{H}$, $p$, $\phi$, $n$,
and $\rho$. The projective classifier theorem
\autoref{thm:quantumstate-projective-phase-classifier} explains how the
endpoint and phase comparison behind those five fields is classified
without exposing host vector equality or a quotient primitive.

For the converse direction, suppose a consumer depends only on
$\mathcal{H}$, $p$, $\phi$, $n$, and $\rho$. Transport the Hilbert and
projective source data by the $\hsame$ rows governed by $\lambda_H$ and
$\lambda_P$. The global-phase stability theorem
\autoref{thm:quantumstate-global-phase-stability} preserves the phase row
and norm ledger, and \autoref{thm:quantumstate-provenance-row-exactness}
preserves the finite package boundary. Therefore the consumer readback is
unchanged under certified global-phase transport.
\end{proof}

\begin{theorem}[QuantumStateUp observable expectation input exactness]
\label{thm:quantumstate-observable-expectation-input-exactness}
An $\ObservableUp$ expectation consumer that receives
$\NameCert_{\QuantumStateUp}$ may read exactly the state rows
$\mathcal{H}$, $v$, $n$, $p$, $\phi$, $\lambda_H$, $\lambda_P$, and $\rho$
from the carrier packet of \autoref{def:quantumstate-bhist-carrier}. The
expectation input is the $\mathsf{BHist}$ endpoint $v$ scoped by the
Hilbert row $\mathcal{H}$, the norm-one ledger $n$, the projective endpoint
$p$, the global-phase row $\phi$, the inherited classifier rows
$\lambda_H$ and $\lambda_P$, and the $\mathsf{Pkg}$ provenance row $\rho$.
It may not read an observable spectrum row, measurement-result row,
host-level vector equality, or state data outside the displayed
$\NameCert_{\QuantumStateUp}$ classifier.
\end{theorem}
\begin{proof}
Unpack the carrier packet of \autoref{def:quantumstate-bhist-carrier}. The
rows available to any consumer are the two source certificates, the Hilbert
endpoint, the norm-one ledger, the phase and projective endpoint data, the
two inherited classifiers, and the finite provenance package. The observable
expectation site uses the state side of this packet, so its state input is
the listed eight rows
$$
\mathcal{H},v,n,p,\phi,\lambda_H,\lambda_P,\rho.
$$

The classifier is fixed by
\autoref{thm:quantumstate-projective-phase-classifier}. Thus $v$ is not read
as a raw host vector: it is read as a Hilbert $\mathsf{BHist}$ endpoint
whose admissible comparisons pass through $\lambda_H$, $\phi$, and
$\lambda_P$. The stability available to the expectation consumer is exactly
\autoref{thm:quantumstate-global-phase-stability}, so changing certified
presentations transports the same input rows by $\hsame$ rather than by a
host quotient.

Exactness follows from
\autoref{thm:quantumstate-namecert-obligation-surface} together with
\autoref{thm:quantumstate-projective-consumer-boundary}. The public surface
contains no spectral, measurement, density-matrix, or channel row, and the
consumer boundary forbids equality outside the Hilbert and projective
classifiers. Therefore the observable expectation input is precisely the
displayed $\mathsf{BHist}$ and $\mathsf{Pkg}$ row family.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix pure ray readback]
\label{thm:quantumstate-densitymatrix-pure-ray-readback}
A $\DensityMatrixUp$ pure-state consumer reading
$\NameCert_{\QuantumStateUp}$ may recover only the projective ray endpoint
$p$ together with the Hilbert source row $\mathcal{H}$, the endpoint row
$v$, the norm-one ledger $n$, the global-phase row $\phi$, the inherited
classifiers $\lambda_H,\lambda_P$, and the provenance row $\rho$. Its
readback is a certified pure ray in $\mathsf{BHist}/\hsame$ terms, not a
host vector quotient and not an already supplied density-matrix row.
\end{theorem}
\begin{proof}
Start with the carrier packet
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho).
$$
The pure-density consumer needs a ray source and a unit ledger. These are
already the projective endpoint $p$ and the norm-one Hilbert ledger $n$,
with $v$ serving only as the certified Hilbert endpoint from which the ray
row is projected.

Apply \autoref{thm:quantumstate-projective-phase-classifier} to identify the
ray comparison used by the consumer. The global-phase row $\phi$ and the
projective classifier $\lambda_P$ determine sameness of pure rays, while
$\lambda_H$ scopes the Hilbert endpoint and norm ledger. Apply
\autoref{thm:quantumstate-global-phase-stability} to transport this
readback along $\hsame$ without changing the rows that the consumer may
inspect.

The exclusion is the constructive content. By
\autoref{thm:quantumstate-namecert-obligation-surface}, no density-matrix row
is exported by $\NameCert_{\QuantumStateUp}$. By
\autoref{thm:quantumstate-projective-consumer-boundary}, no host vector
quotient or equality outside the displayed classifiers is available. Thus a
pure-state density-matrix consumer can build its downstream row only from
the certified ray endpoint, the norm-one Hilbert ledger, and the same
$\mathsf{Pkg}$ provenance record.
\end{proof}

\begin{theorem}[QuantumStateUp channel consumer input boundary]
\label{thm:quantumstate-channel-consumer-input-boundary}
A $\QuantumChannelUp$ state-input consumer of
$\NameCert_{\QuantumStateUp}$ is stable under the same
global-phase/projective classifier as $\QuantumStateUp$. Its input rows are
limited to $\mathcal{H}$, $v$, $n$, $p$, $\phi$, $\lambda_H$, $\lambda_P$,
and $\rho$ from the carrier packet; it carries no independent channel row,
no density-matrix row, and no classifier other than the inherited
$\mathsf{BHist}$, $\hsame$, $\mathsf{Pkg}$, and $\NameCert$ data already
exported by the state certificate.
\end{theorem}
\begin{proof}
Unpack \autoref{def:quantumstate-bhist-carrier} and read the state input as
a finite $\mathsf{BHist}$ package. The endpoint supplied to a channel is
$v$ together with its norm-one ledger $n$, its projective endpoint $p$, the
phase row $\phi$, the inherited classifiers $\lambda_H,\lambda_P$, and the
provenance row $\rho$ tying these rows to the consumed source certificates.

The classifier for this input is not chosen by the channel consumer. It is
the classifier of \autoref{thm:quantumstate-projective-phase-classifier}:
Hilbert endpoint transport is scoped by $\lambda_H$, and ray transport is
scoped by $\phi$ and $\lambda_P$. The stability required by the channel
input is exactly \autoref{thm:quantumstate-global-phase-stability}, which
keeps the same finite row family under componentwise $\hsame$ transport.

Finally apply \autoref{thm:quantumstate-namecert-obligation-surface} and
\autoref{thm:quantumstate-projective-consumer-boundary}. The public surface
exports no channel datum and no density-matrix datum, while the consumer
boundary forbids a separate quotient or host equality. Repacking the
displayed rows therefore gives the whole channel state-input boundary in
$\mathsf{BHist}/\hsame/\mathsf{Pkg}/\NameCert$ terms.
\end{proof}
