\chapter{A Concrete Naming Certificate for $\TypeClassifierMembershipUp$}
\label{ch:concrete-instances-typeclassifiermembership-namecert}
\origin{human}

The $\TypeClassifierMembershipUp$ surface realizes type checking as a finite classifier-membership packet over displayed BEDC histories. It records a term row, a judgment ledger, an $\Ext$ membership row, a $\Cont$ reduction row, and local naming provenance, so type membership and subject-reduction reads remain inside $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data.

\begin{definition}[TypeClassifierMembership carrier]
\label{def:type-classifier-membership-carrier}
A $\TypeClassifierMembershipUp$ carrier is a finite $\BHist$ packet
$$
X=(T,J,E,R,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $T$ is the displayed term row whose finite syntax window is being checked;
\item $J$ is the finite judgment ledger recording the available typing judgments and their dependency order;
\item $E$ is the $\Ext$ membership row saying that the displayed term row is admitted by the local classifier;
\item $R$ is the $\Cont$ reduction row recording the typed continuation steps whose source and target terms are visible in the packet;
\item $H$ records the componentwise $\hsame$ transports for term rows, judgment ledgers, membership rows, reduction rows, dependency packages, and local provenance;
\item $C$ records the $\Cont$ read routes for accessing the judgment ledger, the $\Ext$ membership row, the typed reduction row, and the subject-reduction boundary;
\item $P$ packages the dependencies on $\Ext$, $\Cont$, the judgment ledger, the surrounding $\NameCert$ rows, and the BEDC carrier rows used by the local checker;
\item $N$ is the local $\NameCert_{\TypeClassifierMembershipUp}$ provenance row.
\end{enumerate}
The carrier contains no host type-theory semantics, no semantic equality of terms, no global normalization theorem, and no undecidable classifier outside the finite membership and reduction rows.
\end{definition}

\begin{definition}[TypeClassifierMembership classifier]
\label{def:type-classifier-membership-classifier}
For accepted $\TypeClassifierMembershipUp$ carriers $X$ and $X'$, the classifier compares the judgment ledgers, $\Ext$ membership rows, and $\Cont$ reduction rows componentwise under the displayed $\hsame$ transports in $H$ and the read routes in $C$. A comparison may inspect the term row $T$, the dependency package $P$, and the local provenance row $N$ only as named carrier coordinates.

The classifier does not compare host typing derivations, semantic equality of terms, erased representatives, or any unrecorded conversion relation.
\end{definition}

\begin{theorem}[TypeClassifierMembership NameCert obligations]
\label{thm:type-classifier-membership-namecert-obligations}
The local $\NameCert_{\TypeClassifierMembershipUp}$ surface for \autoref{def:type-classifier-membership-carrier} consists of five obligations:
\begin{enumerate}
\item carrier admission for the finite packet $X=(T,J,E,R,H,C,P,N)$;
\item classifier stability for the judgment, $\Ext$, and reduction rows under the displayed $\hsame$ and $\Cont$ routes;
\item $\Ext$ stability, saying that a transported accepted judgment ledger preserves the membership row $E$;
\item subject-reduction boundary, saying that a visible reduction row $R$ whose source is admitted by $E$ can read only the displayed target membership row;
\item non-escape from host type theory, semantic equality of terms, undecidable conversion, unrecorded normalization, or any classifier not named by $J$, $E$, $R$, $H$, $C$, $P$, and $N$.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.TypeClassifierMembershipUp.TypeClassifierMembershipPacket\_namecert\_obligations}
\begin{proof}
Carrier admission is the finite packet of \autoref{def:type-classifier-membership-carrier}. Its coordinates display the term row, judgment ledger, membership row, reduction row, transport rows, continuation routes, dependency package, and local certificate row.

Classifier stability follows from \autoref{def:type-classifier-membership-classifier}. The only comparisons are componentwise reads of the judgment, $\Ext$, and reduction rows through $H$ and $C$.

$\Ext$ stability and subject reduction are boundary reads, not external semantic principles. The row $E$ is the visible membership witness, and $R$ is the visible typed reduction route whose target membership can only be obtained through the recorded subject-reduction boundary.

The non-escape clause is the carrier inventory. Since no coordinate names host typing semantics, semantic equality, undecidable conversion, or a hidden normalization oracle, no consumer can read those objects from the local $\NameCert_{\TypeClassifierMembershipUp}$ surface.
\end{proof}

\begin{theorem}[TypeClassifierMembership subject-reduction boundary]
\label{thm:type-classifier-membership-subject-reduction-boundary}
Let $X=(T,J,E,R,H,C,P,N)$ be an accepted $\TypeClassifierMembershipUp$ carrier. Every public subject-reduction read starts from the displayed term row $T$, the judgment ledger $J$, the source membership row $E$, and the reduction row $R$, then reaches the target membership boundary only through the recorded $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ routes. It does not appeal to host reduction semantics, global normalization, or semantic equality of terms.
\end{theorem}
\leanchecked{BEDC.Derived.TypeClassifierMembershipUp.TypeClassifierMembershipPacket\_subject\_reduction\_boundary}
\begin{proof}
Project the accepted carrier. The only source of type membership is $E$, and the only source of reduction information is $R$.

Use classifier stability from \autoref{def:type-classifier-membership-classifier}. Transport can move the judgment, membership, and reduction rows only along the displayed $\hsame$ routes, and consumer access is mediated by $C$.

Finally apply the obligation surface of \autoref{thm:type-classifier-membership-namecert-obligations}. Its subject-reduction boundary repacks the visible source membership and reduction rows into the target membership read, so host reduction semantics and semantic equality never enter the packet.
\end{proof}

\begin{theorem}[TypeClassifierMembership non-escape]
\label{thm:type-classifier-membership-non-escape}
No accepted $\TypeClassifierMembershipUp$ carrier exports a host type checker, an undecidable semantic equality oracle, a hidden conversion relation, an erased representative of a typing derivation, or an ambient normalization theorem. Every public type-checking read factors through the finite judgment ledger $J$, the $\Ext$ membership row $E$, the $\Cont$ reduction row $R$, displayed $\hsame$ transport, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row of \autoref{def:type-classifier-membership-carrier}.
\end{theorem}
\leanchecked{BEDC.Derived.TypeClassifierMembershipUp.TypeClassifierMembershipPacket\_non\_escape}
\begin{proof}
Inspect the carrier inventory. The public rows are exactly $T,J,E,R,H,C,P,N$, with $J$ recording the finite judgments, $E$ recording classifier membership, and $R$ recording typed reduction.

Apply \autoref{thm:type-classifier-membership-subject-reduction-boundary} for reduction-facing consumers and \autoref{def:type-classifier-membership-classifier} for classifier-facing consumers. Both routes pass through the same displayed transport and continuation rows.

Since no coordinate of the packet names a host type checker, semantic equality oracle, hidden conversion relation, erased derivation representative, or ambient normalization theorem, those objects cannot be exported by the $\TypeClassifierMembershipUp$ surface.
\end{proof}

\begin{theorem}[TypeClassifierMembership Ext membership stability]
\label{thm:type-classifier-membership-ext-membership-stability}
Let $X=(T,J,E,R,H,C,P,N)$ be an accepted $\TypeClassifierMembershipUp$ carrier. Any transported accepted judgment ledger for $X$ preserves the displayed $\Ext$ membership row $E$ through the componentwise $\hsame$ transport row $H$ and the $\Cont$ read routes $C$. The transported read does not replace $E$ by host typing semantics, semantic equality of terms, undecidable conversion, or an unrecorded membership predicate.
\end{theorem}
\leanchecked{BEDC.Derived.TypeClassifierMembershipUp.TypeClassifierMembershipPacket\_ext\_membership\_stability}
\begin{proof}
Start from the carrier of \autoref{def:type-classifier-membership-carrier}. Its judgment and membership information is displayed only by the rows $J$ and $E$, and the only transport and read coordinates are $H$ and $C$.

Apply the classifier description in \autoref{def:type-classifier-membership-classifier}. Classifier comparisons of the judgment ledger and $\Ext$ row are componentwise reads through those displayed routes, so a transported accepted ledger still reads the same membership coordinate $E$.

The obligation surface in \autoref{thm:type-classifier-membership-namecert-obligations} records this as $\Ext$ stability. Since no carrier coordinate names host typing semantics or an unrecorded predicate, the transported ledger cannot substitute any external membership witness for $E$.
\end{proof}

\begin{theorem}[TypeClassifierMembership reduction target coverage]
\label{thm:type-classifier-membership-reduction-target-coverage}
Let $X=(T,J,E,R,H,C,P,N)$ be an accepted $\TypeClassifierMembershipUp$ carrier. Every typed $\Cont$ reduction target membership read is covered by the displayed rows $T,J,E,R,H,C,P,N$. In particular, the target membership is reached from the finite judgment ledger, the visible $\Ext$ membership row, the reduction row, componentwise transport, continuation routes, dependency package, and local naming row, not from host reduction semantics or hidden normalization.
\end{theorem}
\begin{proof}
Project the accepted carrier. The reduction source and target are visible only through $T,J,E,R$, while $H$ and $C$ provide the recorded transport and continuation access to those rows.

Apply \autoref{thm:type-classifier-membership-subject-reduction-boundary}. It sends each public subject-reduction read from the source membership and visible reduction row to the target membership boundary through the same $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ routes.

The non-escape theorem \autoref{thm:type-classifier-membership-non-escape} excludes host reduction semantics, hidden conversion, erased derivations, and ambient normalization from the exported surface. Thus every typed reduction target membership read is covered by the packet rows $T,J,E,R,H,C,P,N$.
\end{proof}

\begin{theorem}[TypeClassifierMembership obligation closure package]
\label{thm:type-classifier-membership-obligation-closure-package}
Every accepted $\TypeClassifierMembershipUp$ packet carries the obligation package consisting of carrier admission, classifier stability, $\Ext$ membership stability, subject-reduction boundary coverage, reduction target coverage, and public non-escape. The package is witnessed by the carrier and classifier surfaces together with the finite rows $T,J,E,R,H,C,P,N$, and it uses no host type semantics, semantic equality of terms, hidden conversion relation, global normalization theorem, or unrecorded classifier.
\end{theorem}
\begin{proof}
Carrier admission is supplied by \autoref{def:type-classifier-membership-carrier}. Classifier stability is supplied by \autoref{def:type-classifier-membership-classifier}, which limits comparison to the displayed judgment, membership, and reduction rows under $H$ and $C$.

For membership preservation, apply \autoref{thm:type-classifier-membership-ext-membership-stability}. For the subject-reduction boundary, apply \autoref{thm:type-classifier-membership-subject-reduction-boundary}. For target coverage, apply \autoref{thm:type-classifier-membership-reduction-target-coverage}.

It remains to close the public boundary. Apply \autoref{thm:type-classifier-membership-non-escape}; the packet exports only $T,J,E,R,H,C,P,N$ and no host type checker, semantic equality oracle, hidden conversion relation, erased derivation representative, or ambient normalization theorem.
\end{proof}
\leanchecked{BEDC.Derived.TypeClassifierMembershipUp.TypeClassifierMembershipPacket\_obligation\_closure\_package}

\closureat{TypeClassifierMembershipUp}{seedStr}
\closureat{TypeClassifierMembershipUp}{obligationStr}

\begin{closurestatus}{\TypeClassifierMembershipUp}
  \constructivestory{A $\TypeClassifierMembershipUp$ packet is generated from a displayed term row, finite judgment ledger, $\Ext$ membership row, typed $\Cont$ reduction row, componentwise $\hsame$ transports, continuation routes, dependency package, and local $\NameCert$ provenance row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:type-classifier-membership-carrier}, \autoref{def:type-classifier-membership-classifier}, \autoref{thm:type-classifier-membership-namecert-obligations}, \autoref{thm:type-classifier-membership-subject-reduction-boundary}, and \autoref{thm:type-classifier-membership-non-escape} bind the finite type-classifier membership packet, its local classifier, its obligation surface, its subject-reduction boundary, and its non-escape theorem.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host type semantics, semantic equality of terms, global normalization, Lean verification, or bridge checking.}
  \upgradepath{Scoped closure requires checked carrier admission, classifier stability, subject-reduction boundary, target coverage, and public non-escape for the same finite type-classifier membership packet.}
\end{closurestatus}
