\chapter{A Concrete Naming Certificate for $\ObserverHistIdentityUp$}
\label{ch:concrete-instances-observerhistidentity-namecert}
\origin{ai}

The $\ObserverHistIdentityUp$ interface packages the finite observation surface behind observer-history identity. It names the point at which $\Hist$ rows, $\hsame$ transport, $\Cont$ routes, probe and signature observations, no-subject ledgers, package provenance, and a local naming row form one BEDC-native certificate without adding an observer-substance coordinate.

The no-subject side of this carrier is supplied by \autoref{ch:concrete-instances-observersubjectboundary-namecert}, whose finite observation boundary is consumed before the $H,O,L,C,P,N$ rows are read as an identity packet.

\begin{definition}[Observer-Hist identity carrier]\label{def:observer-hist-identity-carrier}
An $\ObserverHistIdentityUp$ carrier is a finite $\BHist$ packet
$$
Q=(H,O,L,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $H$ is the observed $\Hist$ pair, or a unary $\Hist$ row when the consumer inspects one observer-history trace at a time;
\item $O$ lists the finite mark observations, displayed $\Cont$ observations, $\mathsf{ProbeBundle}$ reads, $\mathsf{SigRel}$ reads, and classifier observations available to the consumer;
\item $L$ stores the componentwise $\hsame$ transports for the observed $\Hist$ rows, observation rows, continuation routes, package provenance, and local name;
\item $C$ stores the displayed $\Cont$ routes by which observations are read from the packet;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\mathsf{ProbeBundle}$, $\mathsf{SigRel}$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ObserverHistIdentityUp}$ row.
\end{enumerate}
The classifier compares observer-history packets only by their displayed history rows, transported observations, routes, provenance, and local name. The carrier has no coordinate for an internal truth predicate, observer-substance type, quotient identity, or host equality of observers.
\end{definition}

\begin{theorem}[Observer-Hist identity NameCert obligations]\label{thm:observer-hist-identity-namecert-obligations}
The local $\NameCert_{\ObserverHistIdentityUp}$ surface for the carrier of \autoref{def:observer-hist-identity-carrier} consists exactly of five obligations:
\begin{enumerate}
\item carrier admission for the finite packet $Q=(H,O,L,C,P,N)$;
\item classifier transport by componentwise $\hsame$ over the displayed $\Hist$ and observation rows;
\item observation-ledger exactness for mark, $\Cont$, $\mathsf{ProbeBundle}$, $\mathsf{SigRel}$, and classifier reads;
\item no-subject non-escape, asserting that no consumer route introduces a subject coordinate outside $\Hist$;
\item consumer-surface factorization through $H,O,L,C,P,N$.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.ObserverHistIdentityUp.ObserverHistIdentityTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:observer-hist-identity-carrier}. The finite packet already displays the history row, observation ledger, transport row, continuation row, provenance row, and local naming row.

Classifier transport is componentwise. The row $L$ moves the displayed $\Hist$ observations to the common $\hsame$ surface, and the row $C$ supplies the only permitted observation routes.

Observation exactness and no-subject non-escape follow by inventory of the packet. Since no coordinate stores an internal truth predicate, observer-substance type, quotient identity, or host equality of observers, every consumer read is exhausted by the five displayed obligation rows.
\end{proof}

\begin{theorem}[Observer-Hist identity transport stability]\label{thm:observer-hist-identity-transport-stability}
Let $Q=(H,O,L,C,P,N)$ be an accepted $\ObserverHistIdentityUp$ carrier. If each displayed history and observation coordinate is transported componentwise by the $\hsame$ rows stored in $L$ and then read along the $\Cont$ routes stored in $C$, the resulting packet is accepted by the same $\NameCert_{\ObserverHistIdentityUp}$ surface and preserves the displayed observation ledger, package provenance, and local naming row.
\end{theorem}
\leanchecked{BEDC.Derived.ObserverHistIdentityUp.ObserverHistoryIdentityPacket\_transport\_stability}
\begin{proof}
Project the accepted packet to its six displayed rows. The movable coordinates are exactly the $\Hist$ rows, observation rows, continuation routes, provenance, and local name.

Use $L$ to transport each displayed coordinate componentwise to the common $\hsame$ surface. The routes in $C$ then read the transported mark, continuation, probe, signature, and classifier observations.

No extra coordinate is available after transport. Thus the transported packet is accepted by the same NameCert surface and preserves the displayed ledger, provenance, and local naming data.
\end{proof}

\begin{theorem}[Observer-Hist identity ledger exactness]\label{thm:observer-hist-identity-ledger-exactness}
Every observation exported by an accepted $\ObserverHistIdentityUp$ carrier is one of the displayed rows in $O$ and is read through $L,C,P,N$. No exported observation can be replaced by an internal truth predicate, quotient observer identity, host equality of observers, or subject parameter outside $\Hist$.
\end{theorem}
\begin{proof}
Start with an exported observation. By carrier admission, the observation must be listed in $O$ as a mark, continuation, probe-bundle, signature-relation, or classifier read.

The transport row $L$ and continuation row $C$ account for movement and readback of that listed observation. The rows $P$ and $N$ record provenance and local naming only.

The carrier inventory contains no truth, quotient, host-equality, or subject coordinate. Hence every exported observation is exactly a displayed ledger entry read through the finite certificate rows.
\end{proof}

\begin{theorem}[Observer-Hist identity no-subject boundary]\label{thm:observer-hist-identity-no-subject-boundary}
Every consumer of an accepted $\ObserverHistIdentityUp$ carrier may inspect observer-history identity only through $\Hist$, $\hsame$, $\Cont$, $\mathsf{ProbeBundle}$, $\mathsf{SigRel}$, $\Pkg$, and $\NameCert$ rows displayed in $H,O,L,C,P,N$. The consumer obtains no observer-substance type, no host equality of observers, and no quotient identity outside those rows.
\end{theorem}
\begin{proof}
Let a consumer route be given. Project the carrier to $H,O,L,C,P,N$ and read the displayed observation ledger.

All observer-facing data are $\Hist$ rows and their licensed observations. The $\hsame$ row supplies identity transport, while $\Cont$, $\mathsf{ProbeBundle}$, and $\mathsf{SigRel}$ supply the finite observation routes.

Since $P$ and $N$ only record package provenance and local naming, there is no remaining coordinate from which a separate observer-substance, host equality, or quotient identity could be read.
\end{proof}

\begin{theorem}[Observer-Hist identity consumer surface]\label{thm:observer-hist-identity-consumer-surface}
Every consumer route out of an accepted $\ObserverHistIdentityUp$ carrier factors through the ordered rows
$$
H,O,L,C,P,N.
$$
In particular, the consumer first reads the displayed $\Hist$ and observation rows, then uses only componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert_{\ObserverHistIdentityUp}$ row.
\end{theorem}
\leanchecked{BEDC.Derived.ObserverHistIdentityUp.ObserverHistIdentityPacket\_consumer\_surface}
\begin{proof}
Project the accepted carrier to the ordered tuple of \autoref{def:observer-hist-identity-carrier}. The tuple lists every row that can be inspected by a consumer.

The observation-ledger exactness theorem \autoref{thm:observer-hist-identity-ledger-exactness} forces all exported observations through $O,L,C,P,N$. The no-subject boundary theorem \autoref{thm:observer-hist-identity-no-subject-boundary} excludes any route through a subject coordinate outside $\Hist$.

Therefore every consumer route factors through $H,O,L,C,P,N$, and the finite packet is the whole public surface of the certificate.
\end{proof}

\begin{theorem}[Observer-Hist identity scoped consumer interface]\label{thm:observer-hist-identity-scoped-consumer-interface}
Any downstream observer-facing consumer of an accepted $\ObserverHistIdentityUp$ carrier must read observer identity through the displayed packet
$$
H,O,L,C,P,N,
$$
through the no-subject boundary supplied by \autoref{ch:concrete-instances-observersubjectboundary-namecert}, and through the kernel rows $\BHist$, $\hsame$, $\Cont$, $\mathsf{ProbeBundle}$, $\mathsf{SigRel}$, $\Pkg$, and $\NameCert$. No such consumer may introduce observer-substance, host equality, quotient identity, or an internal truth predicate.
\end{theorem}
\begin{proof}
Project the accepted carrier to $H,O,L,C,P,N$. The carrier definition lists the observed history rows, observation ledger, componentwise transports, continuation routes, provenance, and local name as the whole packet.

Apply ledger exactness and the consumer surface theorem. Observation reads factor through $O,L,C,P,N$, and every downstream route factors through the ordered packet $H,O,L,C,P,N$.

Apply the no-subject boundary and the sibling no-subject source cited in the introduction. Together they rule out a subject coordinate outside $\Hist$ and force observer-facing identity reads to remain on the displayed $\BHist$, $\hsame$, $\Cont$, $\mathsf{ProbeBundle}$, $\mathsf{SigRel}$, $\Pkg$, and $\NameCert$ rows.

The packet therefore has no coordinate from which observer-substance, host equality, quotient identity, or an internal truth predicate could be introduced.
\end{proof}

\closureat{ObserverHistIdentityUp}{seedStr}
\closureat{ObserverHistIdentityUp}{obligationStr}
\closureat{ObserverHistIdentityUp}{scopedStr}[BEDC.Derived.ObserverHistIdentityUp.taste\_gate]
\closureat{ObserverHistIdentityUp}{publicStr}[BEDC.Derived.ObserverHistIdentityUp.ObserverHistIdentityPacket\_consumer\_surface]

\begin{closurestatus}{\ObserverHistIdentityUp}
  \constructivestory{An $\ObserverHistIdentityUp$ packet is generated from displayed $\Hist$ rows, mark and continuation observations, $\mathsf{ProbeBundle}$ and $\mathsf{SigRel}$ reads, classifier observations, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{def:observer-hist-identity-carrier}, \autoref{thm:observer-hist-identity-namecert-obligations}, \autoref{thm:observer-hist-identity-transport-stability}, \autoref{thm:observer-hist-identity-ledger-exactness}, \autoref{thm:observer-hist-identity-no-subject-boundary}, and \autoref{thm:observer-hist-identity-consumer-surface} with \leanchecked{BEDC.Derived.ObserverHistIdentityUp.taste\_gate} bind the carrier admission, classifier transport, observation-ledger exactness, no-subject boundary, and consumer factorization rows for the finite observer-history packet.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.ObserverHistIdentityUp.ObserverHistIdentityPacket\_consumer\_surface}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close an internal truth predicate, observer-substance type, quotient identity, host equality of observers, or a public standard bridge.}
  \upgradepath{Bridged closure requires a standard bridge for the same observer-history consumer surface.}
\end{closurestatus}
