\chapter{A Concrete Naming Certificate for $\KernelCategoryUp$}
\label{ch:concrete-instances-kernel-category-namecert}
\origin{human}

The $\KernelCategoryUp$ packet is the finite naming-certificate surface for
the unary-continuation categorical reading of $\BHist$. It presents objects,
displayed homs, identities, composition routes, endpoint transport, package
provenance, and local naming as rows of the BEDC kernel rather than as a host
category object.

The packet consumes the unary-continuation category surface of \autoref{ch:concrete-instances-unary-continuation-category-namecert} and refines the finite-kernel category packet of \autoref{ch:concrete-instances-finitekernelcategory-namecert}. Its hom row specializes those sibling carriers to $\mathsf{CategoryHomCarrier}$ over $\BHist$ and $\Cont$, so kernel-category reads inherit the displayed object, hom, identity, composition, and endpoint-transport rows before the local naming certificate is applied.

\begin{definition}[KernelCategory NameCert carrier]
\label{def:kernel-category-namecert-carrier}
A $\KernelCategoryUp$ NameCert carrier is a finite $\mathsf{BHist}$ packet
$$
K=(O,H,I,C,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the object row, accepting exactly unary $\mathsf{BHist}$ objects;
\item $H$ is the displayed hom row, where an arrow from $a$ to $b$ with tail
$f$ is accepted by $\mathsf{CategoryHomCarrier}(a,b,f)$;
\item $I$ is the identity row, storing the empty-tail continuation route for
each accepted object;
\item $C$ is the composition route row, storing displayed $\Cont$ routes that
compose accepted hom tails and return the resulting
$\mathsf{CategoryHomCarrier}$ row;
\item $T$ is the endpoint $\hsame$ transport row for objects and displayed hom
tails;
\item $P$ is the $\Pkg$ provenance row over $\BHist$, $\Cont$, $\hsame$,
$\mathsf{CategoryHomCarrier}$, and $\CategoryUp$;
\item $N$ is the local $\NameCert_{\KernelCategoryUp}$ row naming the carrier,
classifier, identity, composition, transport, and non-escape clauses.
\end{enumerate}
Thus the carrier is a kernel-facing categorical packet: all accepted objects,
arrows, equalities, identities, composites, and dependency names are visible
BEDC rows.
\end{definition}

\begin{theorem}[KernelCategory NameCert obligations]
\label{thm:kernel-category-namecert-obligations}
The local $\NameCert_{\KernelCategoryUp}$ obligation surface for the carrier
of \autoref{def:kernel-category-namecert-carrier} consists of five rows:
\begin{enumerate}
\item carrier admission by the finite packet $K=(O,H,I,C,T,P,N)$;
\item hom classifier transport through componentwise $\hsame$ on endpoints
and displayed hom tails;
\item identity route stability through the empty-tail continuation row stored
in $I$;
\item composition route stability through the displayed $\Cont$ route stored
in $C$ and the resulting $\mathsf{CategoryHomCarrier}$ row;
\item non-escape from host category equality, external standard-category
semantics, morphism types outside $\mathsf{BHist}$, and hidden categorical
structure not named by $P$ and $N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is immediate from the coordinates of
\autoref{def:kernel-category-namecert-carrier}. The object, hom, identity,
composition, transport, package, and local naming rows are all finite
$\mathsf{BHist}$ data.

For hom classifier transport, unpack the displayed hom row
$\mathsf{CategoryHomCarrier}(a,b,f)$. Endpoint and hom-tail comparison is
componentwise in $\hsame$, so transported endpoints and transported tails
remain inside the same carrier coordinates.

Identity stability reads the row $I$. The empty-tail continuation route is
stored only for accepted object rows, and its transported form is again read
through $T$ and the same local naming ledger.

Composition stability reads the row $C$. Given accepted displayed hom rows and
a displayed $\Cont$ composition route, the resulting composite is repacked as
the carrier's displayed $\mathsf{CategoryHomCarrier}$ row, with provenance kept
in $P$ and $N$.

The non-escape clause follows by inspection. No coordinate of $K$ is a host
category equality, an external standard-category semantic object, or a hidden
morphism type, so every public read remains within the named BEDC rows.
\end{proof}
\leanchecked{BEDC.Derived.KernelCategoryUp.KernelCategoryCarrier\_certificate\_surface}

\begin{theorem}[KernelCategory Cont-hom exactness]
\label{thm:kernel-category-cont-hom-exactness}
Every public hom read of an accepted $\KernelCategoryUp$ carrier factors
exactly through the displayed continuation route:
$$
O \longmapsto H \longmapsto C \longmapsto T \longmapsto P \longmapsto N.
$$
For endpoints $a,b$ and displayed tail $f$, the public hom classifier is the
row $\mathsf{CategoryHomCarrier}(a,b,f)$ together with its $\Cont$ route and
endpoint $\hsame$ transport. Conversely, any identity or composite route
accepted by $I$ or $C$ returns to a displayed hom row in $H$. The exactness
surface exports no host category equality, external associativity theorem, or
standard-category morphism object outside the kernel packet.
\end{theorem}
\begin{proof}
Start with a public hom read. By the carrier definition, the read must first
select accepted object endpoints from $O$ and then a displayed hom row from
$H$, whose classifier is $\mathsf{CategoryHomCarrier}(a,b,f)$.

Next read the continuation route. Identity reads pass through $I$, while
binary composite reads pass through $C$ and the displayed $\Cont$ route for
the two hom tails. Endpoint and tail movement is then transported only through
$T$.

It remains to check readback. Each identity or composite route named by $I$ or
$C$ is stored precisely so that it returns to the displayed hom row $H$, with
$P$ and $N$ recording the dependency and local naming provenance.

Since the route never leaves these coordinates, there is no place to export
host category equality, external standard-category semantics, or a morphism
object not already represented by a $\mathsf{BHist}$ history.
\end{proof}
