\chapter{A Concrete Naming Certificate for \(\CommRingUp\)}
\label{ch:concrete-instances-commring-namecert}

The commutative ring interface \(\CommRingUp\) extends \autoref{ch:concrete-instances-ring-namecert} with the commutativity field \(a \cdot b = b \cdot a\) for the multiplicative operation under the carrier's classifier. The integer ring from \autoref{ch:concrete-instances-int-namecert} is the canonical concrete instance.

\section{Carrier definition}

\begin{definition}[CommRing carrier]
\label{def:commring-carrier}
Use a ring setup extended with commutativity of multiplication.
\end{definition}

\section{The certificate}

\begin{definition}[CommRing source specification]
\label{def:commring-source-specification}
The source is a certified ring carrier plus multiplicative commutativity.
\end{definition}

\begin{definition}[CommRing pattern specification]
\label{def:commring-pattern-specification}
The pattern is ring expression formation where multiplication may be exchanged by the commutativity field.
\end{definition}

\begin{definition}[CommRing classifier specification]
\label{def:commring-classifier-specification}
The classifier is the ring carrier classifier.
\end{definition}

\begin{definition}[CommRing stability certificate]
\label{def:commring-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item all ring stability fields
  \item multiplicative commutativity
  \item compatibility of multiplication commutativity with ring congruence
\end{enumerate}
\end{definition}

\begin{theorem}[CommRing right distributivity from left distributivity]
\label{thm:commring-right-distrib-from-left}
For BEDC history addition and multiplication, multiplicative commutativity,
additive congruence, and left distributivity imply right distributivity:
$$
(x+y)\cdot z \hsame x\cdot z + y\cdot z .
$$
\end{theorem}
\begin{proof}
Commute \((x+y)\cdot z\) to \(z\cdot(x+y)\). Apply left distributivity, then
use additive congruence with multiplicative commutativity on both summands.
\end{proof}
\leanchecked{BEDC.Derived.CommRingUp.commring\_right\_distrib\_from\_left}

\begin{theorem}[CommRing left distributivity from right distributivity]
\label{thm:commring-left-distrib-from-right}
For BEDC history addition and multiplication, multiplicative commutativity,
additive congruence, and right distributivity imply left distributivity:
$$
x\cdot(y+z)\hsame x\cdot y + x\cdot z .
$$
\end{theorem}
\begin{proof}
Commute $x\cdot(y+z)$ to $(y+z)\cdot x$. Apply right distributivity, then
use additive congruence with multiplicative commutativity on both summands.
\end{proof}
\leanchecked{BEDC.Derived.CommRingUp.commring\_left\_distrib\_from\_right}

\begin{theorem}[CommRing square of a sum expansion]
\label{thm:commring-square-add-expand}
For BEDC history addition and multiplication, multiplicative commutativity,
additive congruence, and both distributive laws imply
$$
(a+b)\cdot(a+b)\hsame (a\cdot a+a\cdot b)+(a\cdot b+b\cdot b).
$$
\end{theorem}
\begin{proof}
Apply right distributivity to the outer product. Apply left distributivity to
both exposed factors, then use additive congruence and multiplicative
commutativity to replace \(b\cdot a\) by \(a\cdot b\).
\end{proof}
\leanchecked{BEDC.Derived.CommRingUp.commring\_square\_add\_expand}

\begin{definition}[CommRing ledger policy]
\label{def:commring-ledger-policy}
Record ring expression provenance and the multiplicative commutativity law when used.
\end{definition}

\begin{definition}[\(\CommRingUp\) certificate obligations]
\label{def:commring-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\CommRingUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\CommRingUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.
