\begin{definition}[CommRing ledger policy]
\label{def:commring-ledger-policy}
Record ring expression provenance and the multiplicative commutativity law when used.
\end{definition}

\begin{definition}[\(\CommRingUp\) certificate obligations]
\label{def:commring-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\CommRingUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\CommRingUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{proposition}[CommRing forgets to Ring certificate]
\label{prop:commring-forgets-ring-certificate}
Let \(R\) carry a \(\CommRingUp(R)\) certificate. If the multiplicative
commutativity field and its compatibility data are ignored, the retained
carrier, source, pattern, classifier, stability, and ledger fields form a
\(\RingUp(R)\) certificate. The carrier operations \(0\), \(1\), \(+\),
\(-\), \(\cdot\), and the classifier are unchanged.
\end{proposition}
\begin{proof}
By \autoref{def:commring-carrier}, a \(\CommRingUp\) carrier is a ring setup
together with multiplication commutativity. The underlying carrier,
classifier, addition, zero, additive inverse, multiplication, and one are
therefore already the data listed in \autoref{def:ring-carrier}.

By \autoref{def:commring-source-specification}, the source is a certified ring
carrier plus multiplicative commutativity. Ignoring the commutativity field
leaves exactly the ring source from \autoref{def:ring-source-specification}.
By \autoref{def:commring-classifier-specification}, the classifier is the ring
carrier classifier, so it is the classifier of
\autoref{def:ring-classifier-specification} with no replacement.

By \autoref{def:commring-pattern-specification}, the commutative-ring pattern
is ring expression formation together with the permission to exchange
multiplication operands by the commutativity field. Removing only that exchange
permission leaves the ring expression formation of
\autoref{def:ring-pattern-specification}.

By \autoref{def:commring-stability-certificate}, the stability certificate
contains all ring stability fields, multiplicative commutativity, and the
compatibility data for that commutativity field. The first component is the
entire list of ring stability fields in \autoref{def:ring-stability-certificate};
the latter two components are not obligations for \(\RingUp\). The ledger left
after suppressing entries justified solely by commutativity is the shared
carrier ledger and operation tree of \autoref{def:ring-ledger-policy}, matching
the ring part of \autoref{def:commring-ledger-policy}.

The remaining carrier, source, pattern, classifier, stability, and ledger data
are exactly the obligations named in \autoref{def:ring-certificate-obligations}.
Since every retained operation and the classifier are copied from the original
\(\CommRingUp(R)\) certificate, the resulting \(\RingUp(R)\) source package has
the same carrier operations and classifier.
\end{proof}
