\chapter{A Concrete Naming Certificate for $\StatManifoldUp$}
\label{ch:concrete-instances-statmanifold-namecert}

The statistical-manifold interface $\StatManifoldUp$ packages a parameter-space manifold whose points label probability distributions, equipped with the Fisher information metric and dual affine connections. It depends on $\NameCert_{\ManifoldUp}$ (\autoref{ch:concrete-instances-manifold-namecert}) and $\NameCert_{\FisherInfoUp}$ (\autoref{ch:concrete-instances-fisherinfo-namecert}).

\section{Carrier definition}
\label{sec:statmanifold-carrier}

\begin{theorem}[StatManifoldUp carrier classifier obligation]
\label{thm:statmanifold-carrier-classifier-obligation}
A carried $\StatManifoldUp$ packet is a $\mathsf{BHist}$ row tuple
$$
(\mathcal{M},\mathcal{I},\theta,p,g,\nabla,\nabla^\ast,\rho,\lambda).
$$
Here $\mathcal{M}$ is the displayed $\NameCert_{\ManifoldUp}$ parameter
carrier, $\mathcal{I}$ is the displayed $\NameCert_{\FisherInfoUp}$ score and
metric packet, $\theta$ and $p$ are parameter and distribution-endpoint rows,
$g$ is the Fisher metric row consumed from $\mathcal{I}$, $\nabla$ and
$\nabla^\ast$ are the dual affine connection ledger rows, $\rho$ is the shared
$\mathsf{Pkg}$ provenance, and $\lambda$ is the finite $\Cont$ ledger joining
these displayed rows. The classifier is the componentwise $\hsame$ transport
that preserves the $\ManifoldUp$ carrier row, the $\FisherInfoUp$ metric row,
both connection ledgers, and the shared provenance.
\end{theorem}
\leanchecked{BEDC.Derived.StatManifoldUp.StatManifoldCarrier\_classifier\_transport}
\begin{proof}
Unpack the displayed tuple as a finite list of $\mathsf{BHist}$ rows. The
parameter carrier is not an abstract transported manifold; it is the concrete
$\NameCert_{\ManifoldUp}$ source row $\mathcal{M}$.

Read the Fisher metric coordinate through $\mathcal{I}$. The dependency
chapter \autoref{ch:concrete-instances-fisherinfo-namecert} supplies the
score, expectation, metric-component, and provenance rows, so $g$ is accepted
only as the FisherInfoUp metric endpoint.

Finally inspect the classifier. Each coordinate moves by the visible
$\hsame$ comparison and the finite $\Cont$ route already stored in
$\lambda$. Repacking the transported coordinates gives another accepted tuple
with the same dependency sources and the same public row inventory.
\end{proof}

\begin{theorem}[StatManifoldUp FisherInfo and Manifold source scope]
\label{thm:statmanifold-fisher-manifold-source-scope}
Every accepted $\StatManifoldUp$ packet projects exactly two dependency
sources: the parameter carrier $\mathcal{M}$ from $\NameCert_{\ManifoldUp}$
and the Fisher metric packet $\mathcal{I}$ from
$\NameCert_{\FisherInfoUp}$. The parameter point row $\theta$, distribution
endpoint row $p$, and Fisher metric row $g$ are read through these two
dependency certificates, not through a host smooth manifold, ambient
probability family, or external metric tensor.
\end{theorem}
\begin{proof}
Project the first two coordinates of the packet. The row $\mathcal{M}$ is the
only carrier for parameter-space chart and tangent information, and
\autoref{ch:concrete-instances-manifold-namecert} is the only source chapter
used for that carrier.

Project the Fisher-information coordinate $\mathcal{I}$. By
\autoref{ch:concrete-instances-fisherinfo-namecert}, the metric component is a
displayed expectation endpoint over the distribution family, so $g$ is
inherited as a $\mathsf{BHist}$ metric row.

The remaining parameter and distribution rows are ledger coordinates tied to
these two sources by $\rho$ and $\lambda$. Since no coordinate of the tuple
names a host manifold, probability family, or metric tensor, those objects are
not exported by the source scope.
\end{proof}

\begin{theorem}[StatManifoldUp ledger exactness]
\label{thm:statmanifold-ledger-exactness}
The public ledger of a $\StatManifoldUp$ packet consists exactly of the
parameter carrier row $\mathcal{M}$, the Fisher packet $\mathcal{I}$, the
parameter and distribution endpoint rows $\theta,p$, the Fisher metric row
$g$, the dual affine connection rows $\nabla,\nabla^\ast$, the shared
$\mathsf{Pkg}$ row $\rho$, and the finite $\Cont$ ledger $\lambda$. No
coordinate-level Christoffel symbol, density formula, or ambient affine
connection object is available outside this list.
\end{theorem}
\leanchecked{BEDC.Derived.StatManifoldUp.StatManifoldBHistPacket\_ledger\_exactness}
\leanchecked{BEDC.Derived.StatManifoldUp.StatManifoldCarrierPacket\_ledger\_exactness}
\begin{proof}
Inspect the coordinates displayed in
\autoref{thm:statmanifold-carrier-classifier-obligation}. They already list
the complete accepted packet, including both dependency certificates, the
metric row, the two connection rows, and the shared provenance.

The connection data are ledger rows rather than host formulas. They can be
transported only along the carried $\Cont$ route and compared only by
$\hsame$ against the same dependency sources.

Conversely, every public readback from the packet must project one of the
listed rows. Repacking these projections gives exactly the same finite ledger,
so there is no hidden coordinate connection or analytic density primitive to
read.
\end{proof}
\leanchecked{BEDC.Derived.StatManifoldUp.StatManifoldDependencyLedgerPacket\_public\_projection}

\begin{theorem}[StatManifoldUp NameCert obligation surface]
\label{thm:statmanifold-namecert-obligation-surface}
The $\NameCert_{\StatManifoldUp}$ obligation surface is generated by the
carrier-classifier row of
\autoref{thm:statmanifold-carrier-classifier-obligation}, the dependency
source scope of
\autoref{thm:statmanifold-fisher-manifold-source-scope}, and the ledger
exactness row of \autoref{thm:statmanifold-ledger-exactness}. Its carrier
witness is the displayed packet, its classifier obligations are reflexivity,
symmetry, and transitivity of the componentwise $\hsame$ row, and its
stability obligation is preservation of the same packet shape under the
finite $\Cont$ transports recorded by $\lambda$.
\end{theorem}
\leanchecked{BEDC.Derived.StatManifoldUp.StatManifoldPacket\_namecert\_obligation\_surface}
\begin{proof}
Use the carrier theorem to obtain the displayed packet and its classifier.
The carrier witness is the packet itself; the classifier relation is the
componentwise $\hsame$ relation over the visible coordinates.

Reflexivity, symmetry, and transitivity are inherited coordinate by
coordinate from $\hsame$ while the dependency rows remain those of
$\NameCert_{\ManifoldUp}$ and $\NameCert_{\FisherInfoUp}$. The shared
$\mathsf{Pkg}$ row ensures that the transported coordinates still belong to
the same certificate packet.

Apply the ledger exactness theorem to close the public surface. It says that
no extra carrier or classifier field can be read outside the tuple, so the
displayed packet supplies the whole NameCert obligation surface.
\end{proof}

\begin{theorem}[StatManifoldUp downstream consumption boundary]
\label{thm:statmanifold-downstream-consumption-boundary}
Any downstream consumer of $\StatManifoldUp$ can read only the
$\mathsf{BHist}$ parameter carrier, Fisher metric, dual affine connection,
provenance, and finite continuation rows enumerated in
\autoref{thm:statmanifold-ledger-exactness}. In particular, consumers such as
information-geometric curvature, statistical geodesic, or divergence
interfaces must factor their inputs through the displayed $\NameCert$ rows
and cannot demand an external smooth model or analytic probability space.
\end{theorem}
\leanchecked{BEDC.Derived.StatManifoldUp.StatManifoldCarrier\_downstream\_consumption\_endpoint\_transport}
\begin{proof}
Start from an accepted consumer readback. By the NameCert obligation surface,
the readback first factors through the carried packet and the componentwise
classifier of
\autoref{thm:statmanifold-carrier-classifier-obligation}.

Apply the source-scope theorem. It restricts all manifold and metric inputs to
the two dependency certificates $\NameCert_{\ManifoldUp}$ and
$\NameCert_{\FisherInfoUp}$.

Apply ledger exactness. The remaining consumable rows are precisely
$\theta,p,g,\nabla,\nabla^\ast,\rho,\lambda$ together with the two dependency
packets, so every downstream interface must consume those rows and no others.
\end{proof}

\section{The certificate}
\label{sec:statmanifold-certificate}

\begin{theorem}[StatManifoldUp public certificate export]
\label{thm:statmanifold-public-certificate-export}
The carrier-classifier obligation of
\autoref{thm:statmanifold-carrier-classifier-obligation}, the
FisherInfo/Manifold source scope of
\autoref{thm:statmanifold-fisher-manifold-source-scope}, the ledger
exactness row of \autoref{thm:statmanifold-ledger-exactness}, the
$\NameCert_{\StatManifoldUp}$ obligation surface of
\autoref{thm:statmanifold-namecert-obligation-surface}, and the downstream
consumption boundary of
\autoref{thm:statmanifold-downstream-consumption-boundary} together export
the public $\NameCert_{\StatManifoldUp}$ surface. The exported rows are
exactly the $\mathsf{BHist}$ parameter carrier, Fisher metric packet, dual
affine connection ledgers, $\mathsf{Pkg}$ provenance, and finite $\Cont$
ledger, with no host manifold or analytic probability primitive.
\end{theorem}
\begin{proof}
First project the carrier-classifier obligation and the source-scope row. They
identify the public packet as the displayed parameter carrier from
$\NameCert_{\ManifoldUp}$ and the Fisher metric packet from
$\NameCert_{\FisherInfoUp}$.

Next apply ledger exactness. It says that the remaining public rows are the
parameter endpoint, distribution endpoint, Fisher metric, dual affine
connection ledgers, shared provenance, and finite continuation ledger, with no
extra coordinate-level analytic data.

Finally use the NameCert obligation surface and the downstream consumption
boundary. These two rows repack the displayed carrier, classifier, stability,
ledger, and consumer-facing rows as the public $\NameCert_{\StatManifoldUp}$
surface, and they exclude any host manifold or analytic probability primitive
outside the listed $\mathsf{BHist}$ packet.
\end{proof}

\closureat{StatManifoldUp}{seedStr}[BEDC.Derived.StatManifoldUp.StatManifoldPacket\_namecert\_obligation\_surface]

\begin{closurestatus}{\StatManifoldUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope names the $\ManifoldUp$ and $\FisherInfoUp$ source rows, parameter and distribution endpoints, Fisher metric, dual affine connection rows, $\mathsf{Pkg}$ provenance, and finite $\Cont$ ledger of the displayed statistical-manifold packet.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.StatManifoldUp.StatManifoldPacket\_namecert\_obligation\_surface}
  \bridgestatus{none}
  \constructivestory{The statistical-manifold packet is carried by a finite $\mathsf{BHist}$ ledger whose source rows come from $\ManifoldUp$ and $\FisherInfoUp$, whose visible rows expose parameter and distribution endpoints, Fisher metric data, dual affine connection data, package provenance, and continuation evidence, and whose classifier transports only those displayed rows through $\hsame$ and $\Cont$.}
  \notclaimed{This chapter does not close host manifolds, analytic probability primitives, coordinate Christoffel symbols, or standard bridges.}
  \upgradepath{Obligation closure requires the carrier, source-scope, ledger, NameCert, downstream, and public-export rows to be enumerated as one obligation surface.}
\end{closurestatus}
