\chapter{A Concrete Naming Certificate for $\WitnessedRefutationUp$}
\label{ch:concrete-instances-witnessedrefutation-namecert}
\origin{ai}

The $\WitnessedRefutationUp$ surface packages the permitted contradiction boundary as finite NameCert data. It records the source history whose claim is being rejected, the continuation packet that turns an attempted witness into a displayed bottom row, the transported refutation ledger, and the local naming certificate that keeps the whole argument inside $\BHist$, $\Cont$, $\hsame$, and $\NameCert$. The packet does not prove an unwitnessed existence statement, does not eliminate double negation for an undecided classifier, and does not branch on excluded middle for certificate-level predicates.

\begin{definition}[Witnessed refutation carrier]
\label{def:witnessed-refutation-carrier}
A $\WitnessedRefutationUp$ carrier is a finite $\BHist$ packet
$$
W=(h,A,R,b,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $h$ is the source $\Hist$ row at which the rejected claim is read;
\item $A$ is the attempted-witness packet, recording only the visible BEDC evidence whose use is being refuted;
\item $R$ is the continuation/refutation packet, a finite list of $\Cont$ rows that sends each admitted attempted witness for $A$ at $h$ to the bottom row;
\item $b$ is the produced bottom witness, displayed as the terminal absurdity row reached by the continuation packet;
\item $H$ records the componentwise $\hsame$ transports for the source history, attempted-witness packet, refutation packet, bottom row, package provenance, and local naming row;
\item $C$ records the $\Cont$ routes that read the source history, expose the attempted witness, execute the refutation packet, and return the bottom row to the ledger;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\Hist$, $\Cont$, $\hsame$, explicit bottom witnesses, and the surrounding certificate rows;
\item $N$ is the local $\NameCert_{\WitnessedRefutationUp}$ ledger.
\end{enumerate}
The carrier is exactly this finite packet. It has no coordinate for unwitnessed excluded middle, double-negation elimination on an undecided proposition, proof by contradiction into an existential conclusion, or a predicate over the carrier of all naming certificates.
\end{definition}
\leanchecked{BEDC.Derived.WitnessedRefutationUp.WitnessedRefutationTasteGate\_single\_carrier\_alignment}

\begin{definition}[Witnessed refutation classifier]
\label{def:witnessed-refutation-classifier}
The $\WitnessedRefutationUp$ classifier compares two accepted packets only by transported displayed witnesses. It relates
$$
W=(h,A,R,b,H,C,P,N)
$$
and
$$
W'=(h',A',R',b',H',C',P',N')
$$
when the source histories, attempted-witness packets, continuation/refutation packets, produced bottom witnesses, transport ledgers, continuation routes, package provenance, and local naming rows are connected by the recorded componentwise $\hsame$ rows and by the displayed $\Cont$ routes. Thus classifier transport carries exactly the same refutation evidence from $W$ to $W'$: the source $\Hist$ row, the attempted witness, the continuation packet, and the produced bottom witness.
\end{definition}

\begin{theorem}[WitnessedRefutation NameCert obligations]
\label{thm:witnessed-refutation-namecert-obligations}
The local $\NameCert_{\WitnessedRefutationUp}$ surface has five finite obligations:
\begin{enumerate}
\item carrier exposure: every accepted object exposes the tuple $W=(h,A,R,b,H,C,P,N)$ of \autoref{def:witnessed-refutation-carrier};
\item classifier stability: classifier-related packets transport the source row, attempted-witness packet, refutation packet, bottom witness, provenance, and local naming row by the displayed $\hsame$ data;
\item $\Cont$-locality: the refutation route uses only the continuation rows recorded in $R$ and $C$;
\item ledger witness accountability: every produced bottom row $b$ is reached from a displayed attempted witness through the recorded route, and no bottom row is accepted without that route;
\item separation from unwitnessed schemas: the packet exports no excluded-middle branch, no double-negation eliminator for an undecided classifier, and no proof-by-contradiction rule whose conclusion is an existential witness.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is projection from the finite tuple of \autoref{def:witnessed-refutation-carrier}. Each coordinate is a displayed $\BHist$ row or a finite ledger row named by the tuple.

Classifier stability is exactly \autoref{def:witnessed-refutation-classifier}. The comparison transports the same source history, attempted-witness packet, refutation packet, bottom witness, provenance, and naming row, and has no hidden coordinate to compare.

$\Cont$-locality follows by inspecting $R$ and $C$. The route from an attempted witness to $b$ is a finite continuation chain recorded in those coordinates.

Ledger witness accountability follows because $b$ is a coordinate only together with the route that produces it. A consumer projecting $b$ must also project the source, attempted witness, and continuation packet that account for it.

Finally, separation from unwitnessed schemas is immediate from the carrier inventory. None of the coordinates names an excluded-middle branch over certificates, an undecided double-negation eliminator, or an existential witness produced without its constructor.
\end{proof}

\begin{theorem}[Witnessed refutation separation from forbidden schemas]
\label{thm:witnessed-refutation-forbidden-schema-separation}
Every consumer read of an accepted $\WitnessedRefutationUp$ packet factors through the displayed source history, attempted-witness packet, continuation/refutation packet, and produced bottom witness. Consequently the packet realizes only the permitted rule ``a displayed witness of $A$ leads by displayed $\Cont$ rows to $\bot$, hence $A$ is refuted at this certificate surface'' and cannot be read as any of the forbidden contradiction schemas of \autoref{def:reasoning-forbidden-pattern}.
\end{theorem}
\begin{proof}
Project the accepted packet as $W=(h,A,R,b,H,C,P,N)$. Any consumer read is one of these displayed coordinates or a component transported through $H$ and exposed through $C$.

The only negative conclusion available from the packet is the function that sends an admitted attempted witness for $A$ at $h$ through the recorded continuation packet $R$ to the displayed bottom witness $b$. This is the permitted refutation shape of \autoref{def:reasoning-permitted-pattern}.

The three forbidden shapes require data absent from the packet: a constructor for an existential obtained from $\neg\forall\neg$, a double-negation eliminator for an undecided classifier, or a certificate-indexed excluded-middle branch. Since the carrier and classifier expose none of these coordinates, no consumer can extract them from $\WitnessedRefutationUp$.
\end{proof}

\begin{theorem}[Witnessed refutation concretizes the contradiction boundary]
\label{thm:witnessed-refutation-vision-concretization}
The $\WitnessedRefutationUp$ certificate realizes the proof-discipline boundary of \autoref{ch:visions-reasoning-by-contradiction-boundary}: permitted refutations are represented as explicit $\Hist$-level evidence carried through $\Cont$ and $\hsame$, while the unwitnessed contradiction schemas remain outside the NameCert surface.
\end{theorem}
\begin{proof}
The permitted side is the packet $W=(h,A,R,b,H,C,P,N)$. Its source history, attempted-witness row, continuation/refutation packet, and produced bottom witness are all explicit BEDC rows, and the classifier transports them only by $\hsame$ and displayed $\Cont$ routes.

The boundary side is \autoref{thm:witnessed-refutation-forbidden-schema-separation}. Since the carrier has no coordinate for certificate-level excluded middle, undecided double-negation elimination, or existential-by-contradiction, the packet cannot close the meta loop described in the vision chapter.

Thus the certificate is a concrete NameCert realization of the permitted contradiction boundary: refutation is admitted exactly when its bottom witness and route are displayed in the ledger.
\end{proof}

\begin{theorem}[Witnessed refutation carrier admission obligation]
\label{thm:witnessed-refutation-carrier-admission-obligation}
For an accepted $\WitnessedRefutationUp$ packet, carrier admission is exactly the finite tuple
$$
W=(h,A,R,b,H,C,P,N)
$$
of \autoref{def:witnessed-refutation-carrier}. The admitted rows are the source $\Hist$ row $h$, attempted-witness packet $A$, displayed continuation/refutation packet $R$, produced bottom witness $b$, componentwise $\hsame$ ledger $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert_{\WitnessedRefutationUp}$ row $N$. The AI single-carrier evidence is the checked TasteGate alignment marker attached to \autoref{def:witnessed-refutation-carrier}, so no second carrier coordinate is available.
\end{theorem}
\begin{proof}
Project the accepted packet to the tuple of \autoref{def:witnessed-refutation-carrier}. Each admitted coordinate is named in that tuple and is read as a displayed $\BHist$ row or a finite ledger row.

The TasteGate alignment fixes the AI surface to this one carrier inventory. Since the inventory contains only $h,A,R,b,H,C,P,N$, a consumer cannot admit a hidden witness source, an extra bottom row, or a second naming carrier.

Thus carrier admission is exhausted by the concrete packet rows, with no route to excluded middle or to an unwitnessed contradiction schema.
\end{proof}

\begin{theorem}[Witnessed refutation route transport obligation]
\label{thm:witnessed-refutation-refuter-route-transport-obligation}
Classifier transport for $\WitnessedRefutationUp$ carries the displayed refuter route only through the rows of \autoref{def:witnessed-refutation-carrier}. If
$$
W=(h,A,R,b,H,C,P,N)
$$
and
$$
W'=(h',A',R',b',H',C',P',N')
$$
are classifier-related accepted packets, then the source history, attempted-witness packet, continuation/refutation packet, produced bottom row, provenance, and local naming row are transported by the stored $\hsame$ data and replayed through the displayed $\Cont$ routes. No transport step may replace the refuter route by a non-displayed proof by contradiction.
\end{theorem}
\begin{proof}
Start with the classifier of \autoref{def:witnessed-refutation-classifier}. It relates two packets by componentwise transport of the same source row, attempted-witness packet, refutation packet, bottom witness, provenance, and naming row.

Read the refuter route through $R$ and $C$. The continuation rows execute the attempted witness route to the bottom witness, while $H$ transports the named coordinates between classified packets.

Because the classifier has no coordinate beyond the displayed tuple, the transported route remains a $\Cont$ route over the same finite ledger. It cannot be replaced by an excluded-middle branch, a double-negation eliminator, or an existential conclusion without a witness row.
\end{proof}

\begin{theorem}[Witnessed refutation bottom-ledger non-escape obligation]
\label{thm:witnessed-refutation-bottom-ledger-nonescape-obligation}
Every bottom-ledger read of an accepted $\WitnessedRefutationUp$ packet factors through the source row $h$, attempted-witness packet $A$, continuation/refutation packet $R$, produced bottom witness $b$, $\hsame$ ledger $H$, $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$. Consequently the packet exports no excluded-middle branch, no double-negation eliminator for an undecided classifier, and no unwitnessed contradiction schema outside the displayed bottom route.
\end{theorem}
\begin{proof}
Read the bottom row from the carrier. The coordinate $b$ is stored only with the source row, attempted-witness packet, refutation packet, transport ledger, continuation routes, provenance, and local naming row.

Apply the forbidden-schema separation theorem. It already identifies the only negative conclusion available from the packet as the displayed route sending an admitted attempted witness through $R$ to $b$.

The bottom ledger therefore has no escape row. A consumer may project the witnessed refutation route, but it cannot extract certificate-level excluded middle, undecided double-negation elimination, or an existential-by-contradiction rule.
\end{proof}

\begin{theorem}[Witnessed refutation RefutationWitness dependency boundary]
\label{thm:witnessed-refutation-refutationwitness-dependency-boundary}
Every accepted $\WitnessedRefutationUp$ packet consumes the same assumption-to-bottom route shape exposed by \autoref{ch:concrete-instances-refutationwitness-namecert}. The witnessed packet adds the attempted-witness row $A$ and TasteGate single-carrier alignment for $W=(h,A,R,b,H,C,P,N)$, but its bottom-ledger non-escape row is the witnessed form of the $\RefutationWitnessUp$ route replay surface: a displayed assumption is carried through recorded $\Cont$ rows to bottom, with no excluded-middle branch, undecided double-negation eliminator, or unwitnessed contradiction schema.
\end{theorem}
\begin{proof}
Read the sibling route first. \autoref{ch:concrete-instances-refutationwitness-namecert} exposes the constructive assumption-to-bottom surface as a finite route from an admitted assumption through displayed continuation rows to a bottom witness.

Project the witnessed packet. Its carrier adds the attempted-witness row $A$ to the source history, refuter route, bottom ledger, transport, continuation, provenance, and local naming rows, and the checked TasteGate alignment attached to \autoref{def:witnessed-refutation-carrier} fixes those rows as one carrier surface.

Apply \autoref{thm:witnessed-refutation-bottom-ledger-nonescape-obligation}. The bottom read still factors through the displayed source, attempted witness, continuation/refutation packet, bottom row, transport, continuation, provenance, and naming rows. Thus the dependency is substantive: the witnessed bottom-ledger row is the RefutationWitness route replay boundary with the attempted witness and single-carrier alignment made explicit.
\end{proof}

\closureat{WitnessedRefutationUp}{seedStr}
\closureat{WitnessedRefutationUp}{obligationStr}
\closureat{WitnessedRefutationUp}{scopedStr}[BEDC.Derived.WitnessedRefutationUp.taste\_gate]

\begin{closurestatus}{\WitnessedRefutationUp}
  \constructivestory{A $\WitnessedRefutationUp$ packet is generated from a source $\Hist$ row, an attempted-witness packet, a displayed $\Cont$ refutation route, the produced bottom witness, componentwise $\hsame$ transports, $\Pkg$ provenance, and a local $\NameCert$ ledger.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:witnessed-refutation-carrier}, \autoref{def:witnessed-refutation-classifier}, \autoref{thm:witnessed-refutation-namecert-obligations}, \autoref{thm:witnessed-refutation-carrier-admission-obligation}, \autoref{thm:witnessed-refutation-refuter-route-transport-obligation}, \autoref{thm:witnessed-refutation-bottom-ledger-nonescape-obligation}, \autoref{thm:witnessed-refutation-forbidden-schema-separation}, and \autoref{thm:witnessed-refutation-vision-concretization} bind the finite carrier, displayed classifier, carrier admission, refuter-route transport, bottom-ledger non-escape, and separation from unwitnessed contradiction schemas.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.WitnessedRefutationUp.WitnessedRefutationTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \leanchecked{BEDC.Derived.WitnessedRefutationUp.taste\_gate}
  \notclaimed{This chapter does not close bridge status, excluded-middle branch, undecided double-negation eliminator, existential-by-contradiction rule, or predicate over the carrier of all naming certificates.}
  \upgradepath{Scoped closure requires a public consumer boundary for the witnessed refutation route together with bridge-grade non-escape.}
\end{closurestatus}
