\chapter{A Concrete Naming Certificate for $\RussellBoundaryUp$}
\label{ch:concrete-instances-russellboundary-namecert}
\origin{human}

The $\RussellBoundaryUp$ surface turns the Russell problem boundary of \autoref{ch:visions-russell-problem-boundary} into a finite NameCert packet. It records relation-first observation rows, description-expansion obligations, contextual class readings, stratification bridges, witnessed-descent routes, componentwise transports, package provenance, and a local naming ledger. The packet does not add a class ontology, a reducibility principle, a quotient over certificates, a host choice selector, or an identity between strata. The witnessed-descent row $W$ is consumed as a public residue ledger in the same sense as \autoref{ch:concrete-instances-inscription-gap-ledger-namecert}, while $\RussellBoundaryUp$ keeps the stratification and contextual-class boundary separate from the inscription residue packet.

The packet also consumes the $\NameCertMorphismUp$ sibling route of \autoref{ch:concrete-instances-namecertmorphism-namecert}. Relation-first rows and witnessed-descent ledgers are read as morphism-preserving certificate boundaries, not as a standalone class ontology.

\begin{definition}[RussellBoundary carrier]
\label{def:russell-boundary-carrier}
A $\RussellBoundaryUp$ carrier is a finite $\BHist$ packet
$$
R=(S,O,D,K,L,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source-expression row whose apparent object grammar is being inspected;
\item $O$ is the relation-first observation row, recording the BEDC relation that licenses the public name before any object-like reading is consumed;
\item $D$ is the description-expansion row, listing the existence, uniqueness or stability, and ledger obligations attached to the definite-description use of $S$;
\item $K$ is the contextual-class row, reading class-like grammar through the finite classifier context that admits it;
\item $L$ is the stratification row, recording the source stratum, target stratum, and displayed bridge through which any level passage is consumed;
\item $W$ is the witnessed-descent row, a finite list of certificate routes required before an upward name may be read downward by a consumer;
\item $H$ records componentwise $\hsame$ transports for $S,O,D,K,L,W$, package rows, and the local naming row;
\item $C$ records the displayed $\Cont$ routes that expose the source expression, replay the relation, unfold the description, read the classifier context, consume the bridge, and check the descent witnesses;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\Hist$, $\Cont$, $\hsame$, $\msame$, bridge rows, and the surrounding certificate rows;
\item $N$ is the local $\NameCert_{\RussellBoundaryUp}$ ledger.
\end{enumerate}
The carrier is exactly this finite packet. It has no coordinate for a class object beyond its contextual classifier row, no primitive denoting description, no reducibility-style stratum collapse, no host quotient over certificate rows, and no choice selector for unlisted descent witnesses.
\end{definition}

\begin{theorem}[RussellBoundary fivefold obligations]
\label{thm:russell-boundary-fivefold-obligations}
The local $\NameCert_{\RussellBoundaryUp}$ surface binds five obligations: relation-first licensing through $O$, description expansion through $D$, contextual class reading through $K$, stratification by the displayed bridge row $L$, and witnessed descent through the route ledger $W$.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:russell-boundary-carrier}. The rows $S,O,D,K,L,W,H,C,P,N$ are the only displayed data admitted by the packet.

Relation-first licensing is the row $O$. A consumer reads the public name through the relation recorded there, and the continuation routes in $C$ replay that relation before any object-like use is available.

Description expansion is the row $D$. It displays the obligations attached to the description rather than treating the description as a primitive denoting term.

Contextual class reading is the row $K$. Class-like grammar is consumed only through the finite classifier context recorded in that row.

Stratification and witnessed descent are the rows $L$ and $W$. The bridge row records the level passage, while the descent ledger records the finite certificate routes required for downward use. Together with $H,P,N$, these rows form the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.RussellBoundaryUp.RussellBoundaryCarrier\_fivefold\_obligations}

\begin{theorem}[RussellBoundary NameCert noncollapse]
\label{thm:russell-boundary-namecert-noncollapse}
Every accepted $\RussellBoundaryUp$ packet keeps source expressions, contextual classifier rows, bridge rows, and witnessed-descent rows as distinct displayed coordinates. Hence the packet cannot be read as an identity between a class expression and a class object, between a description and a primitive denotation, or between source and target strata.
\end{theorem}
\begin{proof}
Project an accepted carrier as $R=(S,O,D,K,L,W,H,C,P,N)$. The source expression, relation row, description row, contextual-class row, stratum bridge, and descent ledger occupy separate coordinates.

The classifier context cannot collapse into a class object, because the only class-like coordinate is $K$, and $K$ is read through the continuation routes and transports recorded in $C$ and $H$. No coordinate stores an object obtained by forgetting that context.

The description row cannot collapse into primitive denotation, because $D$ records obligations rather than a bare selected object. A consumer of the description must also consume the displayed rows that account for existence, stability, and ledger use.

The source and target strata cannot collapse, because $L$ records the bridge as a bridge row. The packet exposes a consumable passage between strata, not an equality of the strata themselves.
\end{proof}
\leanchecked{BEDC.Derived.RussellBoundaryUp.RussellBoundaryCarrier\_namecert\_noncollapse}

\begin{theorem}[RussellBoundary witnessed-descent ledger]
\label{thm:russell-boundary-witnessed-descent-ledger}
Any downward consumer read of a $\RussellBoundaryUp$ upward name factors through the witnessed-descent row $W$ and the displayed $\Cont$ routes in $C$. Therefore the packet admits downward use only when the relevant certificate route is present in the finite ledger.
\end{theorem}
\begin{proof}
Let a consumer attempt a downward read of an accepted packet. The only descent coordinate in \autoref{def:russell-boundary-carrier} is $W$, and the only executable routes available to the packet are the displayed continuation rows in $C$.

If the read is admitted, it must project a route from $W$ and replay it through $C$. The componentwise transports in $H$ ensure that the source expression, relation row, description row, contextual classifier, and bridge row are the same displayed data after transport.

If no such route is present in $W$, the carrier has no substitute coordinate from which to manufacture a witness. The packet has no host choice selector, no class-level truth branch, and no quotient that can identify an absent witness with a present one. Thus downward use is ledger-bounded.
\end{proof}
\leanchecked{BEDC.Derived.RussellBoundaryUp.RussellBoundaryCarrier\_witnessed\_descent\_ledger}

\begin{theorem}[RussellBoundary public certificate]
\label{thm:russell-boundary-public-certificate}
The carrier, fivefold obligations, noncollapse boundary, and witnessed-descent ledger assemble a public $\RussellBoundaryUp$ certificate for relation-first, description-expansion, contextual-class, stratification, and witnessed-descent discipline over finite BEDC rows.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:russell-boundary-carrier}. It fixes the finite source, relation, description, contextual classifier, bridge, descent, transport, continuation, package, and naming rows.

Apply \autoref{thm:russell-boundary-fivefold-obligations}. It identifies the five public obligations by their rows $O,D,K,L,W$.

Use \autoref{thm:russell-boundary-namecert-noncollapse} for the boundary side: the packet does not identify class grammar with a class object, description grammar with primitive denotation, or bridge consumption with stratum equality.

Use \autoref{thm:russell-boundary-witnessed-descent-ledger} for the consumer side: downward use is admitted only through recorded certificate routes.

These clauses expose a public certificate surface. It is public because every consumer-facing use is one of the displayed rows or a route through those rows, and it is a Russell boundary because the five restrictions of \autoref{sec:russell-problem-inherited} are enforced by the NameCert packet rather than by an external ontology.
\end{proof}
\leanchecked{BEDC.Derived.RussellBoundaryUp.RussellBoundaryCarrier\_public\_certificate}

\closureat{RussellBoundaryUp}{seedStr}

\begin{closurestatus}{\RussellBoundaryUp}
  \constructivestory{A $\RussellBoundaryUp$ packet is generated from a source-expression row, a relation-first observation row, a description-expansion obligation row, a contextual-class row, a stratification bridge row, a witnessed-descent ledger, componentwise transports, displayed continuation routes, package provenance, and a local naming ledger.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:russell-boundary-carrier}, \autoref{thm:russell-boundary-fivefold-obligations}, \autoref{thm:russell-boundary-namecert-noncollapse}, \autoref{thm:russell-boundary-witnessed-descent-ledger}, and \autoref{thm:russell-boundary-public-certificate} bind the finite carrier, five public obligations, noncollapse boundary, descent ledger, and public certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close a Lean implementation, bridge checking, class ontology, reducibility principle, quotient over certificates, host choice selector, or identity between strata.}
  \upgradepath{Obligation closure requires Lean encoding of the carrier and checked theorems for the fivefold obligations, noncollapse boundary, witnessed-descent ledger, and public certificate.}
\end{closurestatus}
