\chapter{A Concrete Naming Certificate for $\PersistentHomUp$}
\label{ch:concrete-instances-persistenthom-namecert}

The persistent-homology interface $\PersistentHomUp$ packages the bigraded module of homology groups of a filtered simplicial complex together with the persistence-diagram / barcode summary. It depends on $\NameCert_{\HomologyUp}$ (\autoref{ch:concrete-instances-homology-namecert}) and $\NameCert_{\SimplicialComplexUp}$ (\autoref{ch:concrete-instances-simplicialcomplex-namecert}).

\section{Carrier definition}
\label{sec:persistenthom-carrier}

\begin{theorem}[PersistentHomUp carrier obligation surface]
\label{thm:persistenthom-carrier-obligation-surface}
An accepted $\PersistentHomUp$ row is a finite $\mathsf{BHist}$ filtration
packet over a displayed $\SimplicialComplexUp$ carrier together with
$\HomologyUp$ rows for the filtration stages. Its visible data consist of the
finite index spine, the simplicial-complex packet at each index, the boundary
maps between adjacent stages, the homology rows read from those complexes, the
persistence maps induced by the boundary ledger, and the $\Pkg$ provenance row
binding all of these entries into one named packet.
\end{theorem}
\begin{proof}
Inspect the accepted $\mathsf{BHist}$ packet. The carrier row contains only the
finite filtration spine, the stagewise $\SimplicialComplexUp$ packets, the
$\HomologyUp$ readback rows, the displayed persistence-map routes, and their
common provenance.

Each projected row is already a BEDC history component rather than an ambient
topological object. The finite spine supplies the index boundary, the
simplicial-complex rows supply the face carriers at each stage, and the
homology rows supply the cycle-boundary readbacks.

Repacking these projections gives exactly the carrier obligation surface: a
finite filtration packet whose accepted rows are the displayed histories and no
additional geometric realization, chain-complex library, or barcode object.
\end{proof}
\leanchecked{BEDC.Derived.PersistentHomUp.PersistentHomFiltrationCarrier\_obligation\_surface}

\begin{theorem}[PersistentHomUp filtration classifier stability]
\label{thm:persistenthom-filtration-classifier-stability}
If two accepted $\PersistentHomUp$ packets are related by the displayed
classifier, then transport along their $\hsame$ rows and $\Cont$ routes
preserves the finite filtration-index rows, the stagewise
$\SimplicialComplexUp$ rows, the $\HomologyUp$ readback rows, the persistence
maps between stages, and the shared $\Pkg$ provenance.
\end{theorem}
\begin{proof}
Unpack the classifier as componentwise history comparison. Its index component
is an $\hsame$ row on the finite filtration spine, so transported endpoints keep
the same displayed index boundary.

For each carried index, the classifier also contains the transported
$\SimplicialComplexUp$ and $\HomologyUp$ rows. Their source certificates remain
the same named rows after transport because the classifier stores the endpoint
histories rather than replacing them by external complexes.

Finally, inspect the $\Cont$ routes and $\Pkg$ row. The route entries identify
the persistence maps between the transported stage rows, while the provenance
entry is carried unchanged as the common package witness. These projections are
precisely the advertised stability clauses.
\end{proof}
\leanchecked{BEDC.Derived.PersistentHomUp.PersistentHomFiltrationCarrier\_classifier\_stability}

\begin{theorem}[PersistentHomUp simplicial homology source boundary]
\label{thm:persistenthom-simplicial-homology-source-boundary}
A downstream consumer of an accepted $\PersistentHomUp$ row may read only the
source certificates for the displayed $\SimplicialComplexUp$ stages, the source
certificates for the displayed $\HomologyUp$ rows, and the finite filtration
ledger showing how those rows are ordered and connected. It cannot read an
unstated complex, an unstated boundary quotient, or a barcode row outside the
displayed ledger.
\end{theorem}
\begin{proof}
Project the consumer interface from the accepted carrier. The only named source
certificates in the packet are the $\NameCert_{\SimplicialComplexUp}$ rows for
the stages and the $\NameCert_{\HomologyUp}$ rows for the associated homology
readbacks.

The filtration ledger supplies the order relation on the finite index spine and
the $\Cont$ routes connecting adjacent stages. Therefore every consumer-visible
map is traced through a displayed history row and its package provenance.

Any row not listed in those projections has no constructor in the accepted
packet. It is therefore outside the source boundary for the
$\PersistentHomUp$ interface.
\end{proof}
\leanchecked{BEDC.Derived.PersistentHomUp.PersistentHomFiltrationCarrier\_source\_boundary}

\begin{theorem}[PersistentHomUp filtration ledger exactness]
\label{thm:persistenthom-filtration-ledger-exactness}
The filtration ledger of an accepted $\PersistentHomUp$ row exposes exactly the
finite filtration indices, the boundary maps between adjacent stages, the
$\HomologyUp$ rows computed from the displayed $\SimplicialComplexUp$ stages,
the barcode summary rows read from those persistence maps, the $\Cont$ routes
that witness stage transport, and the $\Pkg$ provenance that binds the packet.
\end{theorem}
\begin{proof}
Read the ledger by constructor inspection. Its index entries are the finite
filtration spine, and its stage entries are the displayed simplicial-complex
and homology histories attached to those indices.

The boundary-map and persistence-map rows are exactly the $\Cont$ entries whose
endpoints are adjacent stage histories. The barcode summary rows are ledger
summaries of those same routes, so they do not introduce a separate external
barcode carrier.

The remaining displayed row is the $\Pkg$ provenance. Combining these
projections gives both directions of exactness: every listed component is
visible in the ledger, and every ledger component is one of the listed rows.
\end{proof}
\leanchecked{BEDC.Derived.PersistentHomUp.PersistentHomFiltrationCarrier\_ledger\_exactness}

\begin{theorem}[PersistentHomUp local NameCert surface]
\label{thm:persistenthom-local-namecert-surface}
The local $\NameCert$ obligation surface for $\PersistentHomUp$ is assembled
from the finite filtration carrier, the filtration-classifier stability row,
the simplicial and homology source boundary, and the filtration-ledger
exactness row. Thus a local persistent-homology name certificate records a
carried $\mathsf{BHist}$ packet, classifier transport by $\hsame$ and $\Cont$,
source readback through $\SimplicialComplexUp$ and $\HomologyUp$, and package
provenance through $\Pkg$.
\end{theorem}
\begin{proof}
Use \autoref{thm:persistenthom-carrier-obligation-surface} for the carried
packet. It supplies the finite filtration spine, stage rows, homology rows,
persistence maps, and package provenance.

Use \autoref{thm:persistenthom-filtration-classifier-stability} for classifier
transport and \autoref{thm:persistenthom-simplicial-homology-source-boundary}
for the consumer-visible source rows. These two projections give the
$\hsame$ and $\Cont$ movement required by the local certificate.

Use \autoref{thm:persistenthom-filtration-ledger-exactness} for the ledger
field. Repacking the carrier, classifier, source, ledger, and provenance rows
into the $\NameCert$ template gives the local obligation surface and does not
assert a separate Lean theorem or standard bridge.
\end{proof}
\leanchecked{BEDC.Derived.PersistentHomUp.PersistentHomFiltrationCarrier\_local\_namecert\_surface}

\section{The certificate}
\label{sec:persistenthom-certificate}
