\chapter{A Concrete Naming Certificate for $\OperationalMembraneUp$}
\label{ch:concrete-instances-operationalmembrane-namecert}
\origin{human}

The $\OperationalMembraneUp$ packet is the concrete NameCert surface that turns the audit-gate membrane into a finite carrier. It does not claim that audit scripts are mathematical generators by themselves. It records the rows by which source syntax, proof ancestry, import separation, paper-Lean name resolution, displayed transport, consumer continuation, package provenance, and the boundary ledger remain visible to downstream governance chapters.

The membrane consumes the public GAP-ledger residue of \autoref{ch:concrete-instances-inscription-gap-ledger-namecert} and the finite kernel acceptance trace of \autoref{ch:concrete-instances-kernelacceptancetrace-namecert} before packaging the source-scan, proof-ancestry, import-separation, and paper-Lean drift rows. The closure witness ledger of \autoref{ch:concrete-instances-closurewitnessledger-namecert} supplies the downstream accounting surface for accepted and refused boundary crossings, so the packet is a lattice-facing audit carrier rather than an isolated kernel row.

\begin{definition}[OperationalMembrane carrier]
\label{def:operational-membrane-carrier}
An $\OperationalMembraneUp$ carrier is a finite $\BHist$ packet
$$
M=(S,A,I,D,H,C,P,L,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source-axiom scan row, recording the finite BEDC source window, the source-token classifier, and the refusal result for internal axiom declarations;
\item $A$ is the strict axiom-purity row, recording the inspected public theorem names, the reported proof ancestry, and the forbidden-dependency classifier for $\mathsf{Classical.choice}$, $\mathsf{Quot.sound}$, and $\mathsf{propext}$;
\item $I$ is the conservativity import-separation row, recording protected baseline prefixes, non-baseline origins, inspected import edges, and the pass-or-refuse import classifier;
\item $D$ is the paper-Lean drift-resolution row, recording each manuscript marker, its named Lean target, and the finite resolution result;
\item $H$ records componentwise $\hsame$ transports for the source, ancestry, import, drift, ledger, package, continuation, and naming rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read the source scan, axiom-purity report, import boundary, drift resolution, ledger, provenance, and local certificate;
\item $P$ is the $\Pkg$ provenance over $\BHist$, source files, proof-ancestry reports, import ledgers, paper markers, Lean target names, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $L$ is the boundary ledger row recording that accepted reads must pass through exactly one of the displayed audit faces and that rejected reads remain outside the packet;
\item $N$ is the local $\NameCert_{\OperationalMembraneUp}$ row.
\end{enumerate}
The carrier contains no source axiom permission, no hidden host axiom, no baseline import exemption, no fuzzy marker match, no theorem of global semantic conservativity, and no host-kernel completeness principle.
\end{definition}

\begin{definition}[OperationalMembrane classifier]
\label{def:operational-membrane-classifier}
For accepted $\OperationalMembraneUp$ carriers $M$ and $M'$, the classifier $\mathsf{OperationalMembraneClassifier}(M,M')$ compares exactly the rows of \autoref{def:operational-membrane-carrier}. It transports source scans through $S$, proof-ancestry reports through $A$, import separation through $I$, paper-Lean name resolution through $D$, boundary-ledger entries through $L$, and provenance through $H,C,P,N$.

The classifier has no component for asserting that a rejected source token is permitted, that a forbidden proof dependency is harmless, that a non-baseline import edge is baseline, that an unresolved paper marker names a nearby theorem, or that the audit surface proves global semantic completeness.
\end{definition}

\begin{theorem}[OperationalMembrane NameCert obligation surface]
\label{thm:operational-membrane-namecert-obligation-surface}
The local $\NameCert_{\OperationalMembraneUp}$ surface consists exactly of carrier admission for
$$
M=(S,A,I,D,H,C,P,L,N),
$$
source-axiom scan exposure, strict axiom-purity exposure, conservativity import-separation exposure, paper-Lean drift-resolution exposure, visible $\hsame$ transport, displayed $\Cont$ locality, $\Pkg$ provenance, boundary-ledger accounting, and non-escape for source axioms, forbidden host proof ancestry, hidden import exemptions, unresolved Lean names, and global semantic completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:operational-membrane-carrier}. The packet has exactly the rows $S,A,I,D,H,C,P,L,N$, so every admitted consumer read begins at one of those coordinates.

The four audit faces are then read separately. The source face is $S$, the proof-ancestry face is $A$, the import-separation face is $I$, and the paper-Lean name-resolution face is $D$.

Transport and locality are displayed by $H$ and $C$. These rows move and replay the four audit faces componentwise without adding a source axiom, a hidden proof dependency, an import exemption, or a substitute Lean name.

Finally $P,L,N$ package the provenance, ledger, and local certificate. Since the excluded objects have no carrier coordinate, no $\NameCert_{\OperationalMembraneUp}$ projection can export them.
\end{proof}
\leanchecked{BEDC.Derived.OperationalMembraneUp.OperationalMembranePacket\_namecert\_obligation\_surface}

\begin{theorem}[OperationalMembrane ledger exactness]
\label{thm:operational-membrane-ledger-exactness}
For an accepted $\OperationalMembraneUp$ packet, the boundary ledger $L$ is exact for the displayed carrier: a consumer may read a source-scan decision through $S$, an axiom-purity decision through $A$, an import-separation decision through $I$, or a paper-Lean resolution decision through $D$, together with the visible transport, continuation, package, and local naming rows. No consumer may use $L$ to manufacture a fifth audit face or to erase a rejected boundary crossing.
\end{theorem}
\begin{proof}
Project $L$ from the carrier and compare it with the carrier coordinates. Its entries name the same four audit faces $S,A,I,D$ and the same structural rows $H,C,P,N$.

Apply the classifier of \autoref{def:operational-membrane-classifier}. It transports exactly the displayed rows and contains no comparison component for an additional audit face.

The non-escape clause of \autoref{def:operational-membrane-carrier} fixes the rejected side. Because no coordinate permits source axioms, forbidden dependencies, import exemptions, fuzzy marker matches, or global completeness principles, the ledger cannot turn a refused crossing into accepted content.
\end{proof}
\leanchecked{BEDC.Derived.OperationalMembraneUp.OperationalMembranePacket\_ledger\_exactness}

\begin{theorem}[OperationalMembrane drift resolution]
\label{thm:operational-membrane-drift-resolution}
For an accepted $\OperationalMembraneUp$ packet, the paper-Lean row $D$ is the complete public route by which manuscript markers are resolved against Lean names. A consumer may read the marker text, the target name, the finite resolution result, the componentwise transport row, the continuation route, package provenance, boundary-ledger entry, and local $\NameCert_{\OperationalMembraneUp}$ row. It may not replace a missing target by a similar declaration, a neighboring namespace, a prose interpretation, or an unchecked string.
\end{theorem}
\begin{proof}
Read $D$ from \autoref{def:operational-membrane-carrier}. The row contains the marker text, the claimed Lean target, and the finite resolution result.

Use $H$ and $C$ to transport and expose that row to consumers. The target name remains the displayed target name, and the continuation route does not introduce fuzzy matching or namespace search.

The ledger row $L$ records whether the read belongs to the accepted boundary surface. Together with $P$ and $N$, it packages the result as a local naming certificate and leaves missing or unchecked names outside the packet.
\end{proof}

\begin{theorem}[OperationalMembrane scoped boundary]
\label{thm:operational-membrane-scoped-boundary}
The scoped $\OperationalMembraneUp$ boundary consists exactly of the source scan $S$, axiom-purity row $A$, import-separation row $I$, paper-Lean drift row $D$, componentwise $\hsame$ transports $H$, displayed $\Cont$ routes $C$, package provenance $P$, boundary ledger $L$, and local $\NameCert$ row $N$ of the carrier $M=(S,A,I,D,H,C,P,L,N)$. It excludes source axiom permission, hidden proof ancestry, import exemptions, fuzzy Lean-name matching, and global semantic completeness.
\end{theorem}
\begin{proof}
Start with \autoref{def:operational-membrane-carrier} and \autoref{def:operational-membrane-classifier}. They make $S,A,I,D,H,C,P,L,N$ the complete carrier and comparison surface.

Apply \autoref{thm:operational-membrane-namecert-obligation-surface} to expose those rows as the local naming certificate. Then use \autoref{thm:operational-membrane-ledger-exactness} to keep accepted and rejected boundary crossings on the displayed ledger.

Finally apply \autoref{thm:operational-membrane-drift-resolution} for the paper-Lean face. The same carrier has no row for source axiom permission, hidden proof ancestry, import exemption, fuzzy name replacement, or global semantic completeness, so the scoped boundary is exactly the displayed membrane.
\end{proof}

\begin{theorem}[OperationalMembrane standard schema bridge]
\label{thm:operational-membrane-standard-schema-bridge}
The public $\OperationalMembraneUp$ surface bridges to the standard operational schema exactly through the displayed source scan $S$, strict axiom-purity row $A$, import-separation row $I$, paper-Lean drift row $D$, boundary ledger $L$, componentwise $\hsame$ row $H$, displayed $\Cont$ row $C$, $\Pkg$ provenance row $P$, and local $\NameCert$ row $N$ of the carrier $M=(S,A,I,D,H,C,P,L,N)$.

The bridge has no extra audit face. It does not permit source axioms, forbidden proof ancestry, baseline-import exemptions, fuzzy Lean-name resolution, host-kernel completeness, or global semantic conservativity beyond the displayed membrane rows.
\end{theorem}
\begin{proof}
Start with the carrier and classifier. The definitions display the exact rows $S,A,I,D,H,C,P,L,N$ and compare only source scans, proof-ancestry reports, import separation, paper-Lean name resolution, boundary-ledger entries, and structural rows.

Apply the NameCert obligation surface and ledger exactness. These theorems expose the four audit faces and ensure the boundary ledger cannot create a fifth face or erase a refused crossing.

Use drift resolution for the paper-Lean component. It keeps marker resolution tied to the displayed target names and rejects nearby declarations, prose interpretation, or unchecked strings as replacements.

Finally apply the scoped boundary theorem. Since all standard operational reads are already routed through the displayed membrane rows, the public surface supplies a paper-level standard schema bridge without adding host-kernel completeness or global conservativity.
\end{proof}

\closureat{OperationalMembraneUp}{seedStr}
\closureat{OperationalMembraneUp}{obligationStr}
\closureat{OperationalMembraneUp}{scopedStr}[BEDC.Derived.OperationalMembraneUp.OperationalMembranePacket\_namecert\_obligation\_surface]
\closureat{OperationalMembraneUp}{publicStr}[BEDC.Derived.OperationalMembraneUp.OperationalMembranePacket\_namecert\_obligation\_surface]
\closureat{OperationalMembraneUp}{bridgedStr}[BEDC.Derived.OperationalMembraneUp.OperationalMembranePacket\_namecert\_obligation\_surface]
\closureat{OperationalMembraneUp}{matureStr}[BEDC.Derived.OperationalMembraneUp.OperationalMembranePacket\_namecert\_obligation\_surface]

\begin{closurestatus}{\OperationalMembraneUp}
  \constructivestory{An $\OperationalMembraneUp$ packet is generated from source-axiom scans, strict proof-ancestry reports, import-separation ledgers, paper-Lean name-resolution rows, visible transport, continuation routes, package provenance, a boundary ledger, and a local naming certificate.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:operational-membrane-carrier}, \autoref{def:operational-membrane-classifier}, \autoref{thm:operational-membrane-namecert-obligation-surface}, \autoref{thm:operational-membrane-ledger-exactness}, \autoref{thm:operational-membrane-drift-resolution}, \autoref{thm:operational-membrane-scoped-boundary}, and \autoref{thm:operational-membrane-standard-schema-bridge} bind the carrier, classifier, ledger exactness, drift resolution, scoped operational boundary, and paper-level standard schema bridge rows for the displayed audit membrane.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.OperationalMembraneUp.OperationalMembranePacket\_namecert\_obligation\_surface}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close global semantic conservativity, host-kernel completeness, bridge checking, or a Lean implementation of the operational membrane carrier.}
  \upgradepath{The next formal step is machine bridge checking for the displayed standard schema bridge.}
\end{closurestatus}
