\chapter{A Concrete Naming Certificate for $\InducedRepUp$}
\label{ch:concrete-instances-inducedrep-namecert}

The induced-representation interface $\InducedRepUp$ packages, for a subgroup inclusion, the induction and restriction functors between representation categories together with Frobenius reciprocity. It depends on $\NameCert_{\SubgroupUp}$ (\autoref{ch:concrete-instances-subgroup-namecert}) and $\NameCert_{\RepresentationRingUp}$ (\autoref{ch:concrete-instances-representationring-namecert}).

\section{Carrier definition}
\label{sec:inducedrep-carrier}

\begin{definition}[InducedRepUp BHist carrier packet]
\label{def:inducedrep-bhist-carrier}
An $\InducedRepUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
\mathcal{I}=(S,R,i,r,F,\eta,\epsilon,\rho,\lambda).
$$
The row $S$ is the consumed $\NameCert_{\SubgroupUp}$ packet naming the
subgroup inclusion. The row $R$ is the consumed
$\NameCert_{\RepresentationRingUp}$ packet naming the source and target
representation-ring rows. The rows $i$ and $r$ are the displayed induction
and restriction endpoints, each scoped by $S$ for the subgroup inclusion and
by $R$ for the representation-ring source and target rows. The row $F$ is the
finite Frobenius reciprocity ledger whose entries compare the displayed
induction and restriction endpoints without exporting a host adjunction.

The rows $\eta$ and $\epsilon$ are the Frobenius unit and counit rows in the
same finite ledger. The row $\rho$ is the $\mathsf{Pkg}$ provenance packet
recording exactly the consumed package rows from $S$ and $R$ together with
the package rows attached to $i$, $r$, $F$, $\eta$, and $\epsilon$. The finite
row $\lambda$ is the $\Cont$ ledger containing exactly the consumed SubgroupUp
rows, consumed RepresentationRingUp rows, induction and restriction endpoint
rows, Frobenius rows, provenance rows, and public continuation rows exposed
by the packet.
\end{definition}

\begin{definition}[InducedRepUp induction--restriction packet]
\label{def:inducedrep-induction-restriction-packet}
An $\InducedRepUp$ induction--restriction packet is a finite
$\mathsf{BHist}$ packet
$$
\mathcal{P}_{\InducedRepUp}=(S_{\leq},R_{\mathrm{rep}},I_{\uparrow},
R_{\downarrow},\Phi,H_{\leq},H_{\mathrm{rep}},H_{\uparrow},H_{\downarrow},
C_{\mathrm{src}},C_{\mathrm{fr}},\Pi).
$$
The row $S_{\leq}$ is the consumed subgroup-inclusion row supplied by
$\NameCert_{\SubgroupUp}$. The row $R_{\mathrm{rep}}$ is the consumed
representation-ring row supplied by $\NameCert_{\RepresentationRingUp}$.
The rows $I_{\uparrow}$ and $R_{\downarrow}$ are the displayed induction and
restriction rows over that same subgroup source and representation-ring
source.

The row $\Phi$ is the finite Frobenius comparison row. It compares the
displayed $I_{\uparrow}$ and $R_{\downarrow}$ rows as BEDC data and does not
export a host adjunction. The classifier rows
$H_{\leq},H_{\mathrm{rep}},H_{\uparrow},H_{\downarrow}$ are the corresponding
$\hsame$ rows for subgroup inclusion, representation-ring transport,
induction transport, and restriction transport. The ledgers
$C_{\mathrm{src}}$ and $C_{\mathrm{fr}}$ are finite $\Cont$ ledgers for the
source-certificate rows and the Frobenius comparison rows. The row $\Pi$ is
the $\mathsf{Pkg}$ provenance row recording exactly the consumed
$\NameCert_{\SubgroupUp}$ package, the consumed
$\NameCert_{\RepresentationRingUp}$ package, and the displayed induction,
restriction, classifier, Frobenius, and continuation rows.
\end{definition}

\begin{definition}[InducedRepUp restriction-induction classifier]
\label{def:inducedrep-restriction-induction-classifier}
For two carrier packets
$$
\mathcal{I}=(S,R,i,r,F,\eta,\epsilon,\rho,\lambda)
\qquad\text{and}\qquad
\mathcal{I}'=(S',R',i',r',F',\eta',\epsilon',\rho',\lambda'),
$$
the restriction-induction classifier
$\mathcal{I}\sim_{\InducedRepUp}^{\mathrm{ri}}\mathcal{I}'$ is the finite
componentwise transport datum consisting of:
\begin{enumerate}
  \item an $\hsame$ transport row between the consumed
  $\NameCert_{\SubgroupUp}$ packets $S$ and $S'$;
  \item an $\hsame$ transport row between the consumed
  $\NameCert_{\RepresentationRingUp}$ packets $R$ and $R'$;
  \item entrywise $\hsame$ transport of the subgroup-inclusion rows read from
  $S$ and the representation-ring rows read from $R$;
  \item $\hsame$ transport rows between the induction endpoints $i$ and $i'$
  and between the restriction endpoints $r$ and $r'$;
  \item entrywise $\hsame$ transport of the Frobenius ledger rows
  $F,\eta,\epsilon$ to $F',\eta',\epsilon'$;
  \item an $\hsame$ transport row between the provenance packets $\rho$ and
  $\rho'$;
  \item a finite $\Cont$ ledger comparison between $\lambda$ and $\lambda'$,
  entry by entry.
\end{enumerate}
This classifier transports only displayed BEDC rows: subgroup inclusion rows,
representation-ring rows, induction and restriction endpoints, Frobenius
unit and counit rows, provenance, and continuation entries. It explicitly
does not require equality of host induction functors, host restriction
functors, representation categories, or adjunction data outside the finite
packet.
\end{definition}

\section{The certificate}
\label{sec:inducedrep-certificate}

\begin{theorem}[InducedRepUp subgroup source boundary]
\label{thm:inducedrep-subgroup-source-boundary}
For every $\InducedRepUp$ packet of
\autoref{def:inducedrep-induction-restriction-packet}, the subgroup source
visible to downstream consumers is exactly the finite $\mathsf{BHist}$ row
$S_{\leq}$ consumed from $\NameCert_{\SubgroupUp}$, together with its
$\hsame$ classifier row $H_{\leq}$, its $\Cont$ entries inside
$C_{\mathrm{src}}$, and its $\mathsf{Pkg}$ provenance inside $\Pi$. No
additional subgroup object, ambient group, inclusion witness, or host
restriction datum is part of the public source boundary.
\end{theorem}
\begin{proof}
The traditional target is the subgroup inclusion along which induction and
restriction are displayed. The BEDC source is not an ambient group object but
the consumed $\NameCert_{\SubgroupUp}$ row $S_{\leq}$ in the packet.

Project the carrier. The only subgroup-source row in
$\mathcal{P}_{\InducedRepUp}$ is $S_{\leq}$, and the matching classifier
entry is $H_{\leq}$. Stability is therefore componentwise $\hsame$ transport
through $H_{\leq}$ together with the source continuation entries recorded in
$C_{\mathrm{src}}$.

The ledger and exactness clauses are read from $\Pi$ and $C_{\mathrm{src}}$.
Every exported subgroup-source entry occurs in those rows, and every such
entry is named by the packet. Since no $\StdBridge$ row is carried, the
standard bridge is absent at this boundary.
\end{proof}

\begin{theorem}[InducedRepUp representation-ring action boundary]
\label{thm:inducedrep-representation-ring-action-boundary}
For every $\InducedRepUp$ packet of
\autoref{def:inducedrep-induction-restriction-packet}, the
representation-ring action visible at the induction and restriction
interface is exactly the finite $\mathsf{BHist}$ row $R_{\mathrm{rep}}$
consumed from $\NameCert_{\RepresentationRingUp}$, the displayed rows
$I_{\uparrow}$ and $R_{\downarrow}$, the $\hsame$ classifier rows
$H_{\mathrm{rep}},H_{\uparrow},H_{\downarrow}$, the continuation rows in
$C_{\mathrm{src}}$ and $C_{\mathrm{fr}}$, and the $\mathsf{Pkg}$ provenance
row $\Pi$.
\end{theorem}
\begin{proof}
The traditional target is an action of representation rings on induction and
restriction. The BEDC source is the consumed
$\NameCert_{\RepresentationRingUp}$ row $R_{\mathrm{rep}}$, and the carrier
exposes only the two displayed action endpoints $I_{\uparrow}$ and
$R_{\downarrow}$.

Classifier stability is componentwise. The row $H_{\mathrm{rep}}$ transports
the representation-ring source, while $H_{\uparrow}$ and $H_{\downarrow}$
transport the displayed induction and restriction rows. The $\Cont$ ledgers
record the public continuation entries attached to those rows and to the
Frobenius comparison.

Exactness is obtained by checking the provenance row $\Pi$. Any action row
available to a consumer must be one of
$R_{\mathrm{rep}},I_{\uparrow},R_{\downarrow}$ or a continuation entry named
by the displayed ledgers. No host representation category, functor equality,
or standard bridge is exported.
\end{proof}

\begin{theorem}[InducedRepUp Frobenius reciprocity classifier]
\label{thm:inducedrep-frobenius-reciprocity-classifier}
The Frobenius reciprocity data of an $\InducedRepUp$ packet is classified by
the finite comparison row $\Phi$, the endpoint classifier rows
$H_{\uparrow}$ and $H_{\downarrow}$, the source classifier rows $H_{\leq}$
and $H_{\mathrm{rep}}$, the $\Cont$ ledger $C_{\mathrm{fr}}$, and the
$\mathsf{Pkg}$ provenance row $\Pi$. Thus $\hsame$ equivalence of Frobenius
rows is a BEDC comparison between displayed induction and restriction rows,
not equality of a host adjunction.
\end{theorem}
\begin{proof}
The traditional target is Frobenius reciprocity for induction and
restriction. The BEDC carrier names this target by the row $\Phi$, whose
endpoints are the displayed rows $I_{\uparrow}$ and $R_{\downarrow}$ over the
source rows $S_{\leq}$ and $R_{\mathrm{rep}}$.

The classifier is the tuple of $\hsame$ rows. Source transport uses
$H_{\leq}$ and $H_{\mathrm{rep}}$; endpoint transport uses $H_{\uparrow}$ and
$H_{\downarrow}$. Stability of the Frobenius comparison is the finite
$\Cont$ transport recorded in $C_{\mathrm{fr}}$.

The ledger clause is exactly the combination of $C_{\mathrm{fr}}$ and
$\Pi$. Exactness follows because every Frobenius entry consumed by the public
interface is named by $\Phi$ or by that ledger. The packet carries no
$\StdBridge$ row, so the standard bridge is absent and the classifier remains
inside $\mathsf{BHist}$.
\end{proof}

\begin{theorem}[InducedRepUp public obligation surface]
\label{thm:inducedrep-public-obligation-surface}
The public $\NameCert_{\InducedRepUp}$ obligation surface consists of the
$\mathsf{BHist}$ packet of
\autoref{def:inducedrep-induction-restriction-packet}, the consumed
$\NameCert_{\SubgroupUp}$ and $\NameCert_{\RepresentationRingUp}$ rows, the
displayed induction and restriction rows, the Frobenius comparison row, all
listed $\hsame$ classifier rows, the $\Cont$ ledgers
$C_{\mathrm{src}}$ and $C_{\mathrm{fr}}$, and the $\mathsf{Pkg}$ provenance
row $\Pi$. No obligation outside those displayed rows is public.
\end{theorem}
\begin{proof}
The traditional target is the public certificate for an induced
representation interface. The BEDC source is the pair of consumed
certificates $\NameCert_{\SubgroupUp}$ and
$\NameCert_{\RepresentationRingUp}$, read through $S_{\leq}$ and
$R_{\mathrm{rep}}$.

The carrier is the finite packet
$\mathcal{P}_{\InducedRepUp}$. Its classifier rows are
$H_{\leq},H_{\mathrm{rep}},H_{\uparrow},H_{\downarrow}$, and stability is the
corresponding componentwise $\hsame$ transport together with the two finite
$\Cont$ ledgers.

The ledger and exactness conditions are public precisely because they are
recorded in $C_{\mathrm{src}}$, $C_{\mathrm{fr}}$, and $\Pi$. Every row in the
surface is a projection of the packet, and every projection repacks into the
same surface. With no $\StdBridge$ row present, the standard bridge is absent.
\end{proof}

\begin{theorem}[InducedRepUp consumer boundary]
\label{thm:inducedrep-consumer-boundary}
An $\InducedRepUp$ consumer may inspect exactly the source rows
$S_{\leq}$ and $R_{\mathrm{rep}}$, the displayed induction and restriction
rows $I_{\uparrow}$ and $R_{\downarrow}$, the Frobenius row $\Phi$, the
$\hsame$ classifier rows $H_{\leq},H_{\mathrm{rep}},H_{\uparrow},
H_{\downarrow}$, the $\Cont$ ledgers $C_{\mathrm{src}}$ and
$C_{\mathrm{fr}}$, and the $\mathsf{Pkg}$ row $\Pi$. Any use of
$\NameCert_{\SubgroupUp}$ or $\NameCert_{\RepresentationRingUp}$ by that
consumer factors through those rows.
\end{theorem}
\begin{proof}
The traditional target is a downstream use of induction, restriction, and
Frobenius reciprocity. The BEDC source data are the two consumed
certificates, and the carrier presents them only through $S_{\leq}$ and
$R_{\mathrm{rep}}$.

For classifier stability, the consumer must use the displayed $\hsame$ rows.
Subgroup and representation-ring requests pass through $H_{\leq}$ and
$H_{\mathrm{rep}}$; induction and restriction requests pass through
$H_{\uparrow}$ and $H_{\downarrow}$; Frobenius requests pass through
$\Phi$ and $C_{\mathrm{fr}}$.

The ledger is finite and explicit: $C_{\mathrm{src}}$, $C_{\mathrm{fr}}$,
and $\Pi$ list exactly what the consumer may read. Exactness is the converse
projection from those listed rows back to the carrier. No host carrier,
external representation category, adjunction object, or standard bridge is
available beyond that boundary.
\end{proof}

\begin{theorem}[InducedRepUp Frobenius ledger boundary]
\label{thm:inducedrep-frobenius-ledger-boundary}
Every Frobenius row exported by an $\InducedRepUp$ carrier of
\autoref{def:inducedrep-bhist-carrier} is one of the displayed finite rows
$F,\eta,\epsilon,\lambda$. Its endpoints are the displayed induction row $i$
and restriction row $r$, scoped through the consumed
$\NameCert_{\SubgroupUp}$ and $\NameCert_{\RepresentationRingUp}$ packets.
No host adjunction, host functor equality, naturality square, or external
representation category is exported at the Frobenius boundary.
\end{theorem}
\leanchecked{BEDC.Derived.InducedRepUp.InducedRepFrobeniusLedger\_boundary}
\begin{proof}
Project an accepted packet to
$\mathcal{I}=(S,R,i,r,F,\eta,\epsilon,\rho,\lambda)$. The carrier definition
lists the Frobenius part as the finite ledger $F$ together with the unit row
$\eta$, the counit row $\epsilon$, and the public continuation entries in
$\lambda$.

The displayed endpoints of those rows are $i$ and $r$. Their subgroup source
is read through $S$, and their representation-ring source and target rows are
read through $R$. The source certificates are precisely the SubgroupUp and
RepresentationRingUp $\NameCert$ rows cited in the packet.

Exactness is the reverse projection. A row outside
$F,\eta,\epsilon,\lambda$ is not a Frobenius row of the carrier, and a row
outside $S,R,i,r,\rho$ supplies no public endpoint or provenance for that
Frobenius display. Thus the Frobenius boundary is exactly the finite ledger
shown in the packet.
\end{proof}

\begin{theorem}[InducedRepUp NameCert obligation surface]
\label{thm:inducedrep-namecert-obligation-surface}
The $\NameCert_{\InducedRepUp}$ obligation surface is the package consisting
of the carrier packet of \autoref{def:inducedrep-bhist-carrier}, the
restriction-induction classifier of
\autoref{def:inducedrep-restriction-induction-classifier}, the Frobenius
ledger boundary of \autoref{thm:inducedrep-frobenius-ledger-boundary},
componentwise $\hsame$ and $\Cont$ stability for each displayed row, exactness
of the finite provenance and continuation ledgers, and no standard bridge.
The surface exports no row outside the carrier, classifier, and provenance
ledger.
\end{theorem}
\begin{proof}
Start with the carrier and classifier. The carrier supplies the finite row
family $S,R,i,r,F,\eta,\epsilon,\rho,\lambda$, while the classifier supplies
componentwise $\hsame$ transport for the consumed certificates, subgroup
inclusion rows, representation-ring rows, induction and restriction endpoints,
Frobenius rows, provenance packet, and continuation ledger.

The ten-field reading is therefore fixed. The traditional target is the
restriction-induction interface with Frobenius reciprocity; the BEDC sources
are $\NameCert_{\SubgroupUp}$ and $\NameCert_{\RepresentationRingUp}$; the
carrier is the displayed finite $\mathsf{BHist}$ packet; the classifier is
the restricted componentwise relation; stability is the listed $\hsame$ and
$\Cont$ transport; the ledger is $\lambda$ together with the Frobenius rows;
the core theorem list is this surface and the Frobenius ledger boundary;
exactness is projection from the displayed rows; the standard bridge is none;
and the status is a paper-side obligation surface for
$\NameCert_{\InducedRepUp}$.

For stability, transport each component of a packet along the corresponding
classifier row. The SubgroupUp source certificate transports the subgroup
inclusion rows, the RepresentationRingUp source certificate transports the
representation-ring rows, and the endpoint and Frobenius rows are transported
by their displayed $\hsame$ comparisons and the finite $\Cont$ comparison.

Exactness follows because every exported row is named in the carrier,
classifier, or provenance ledger. Conversely, each named row repacks into the
obligation surface by the displayed packet, so no additional host functor,
host category, adjunction, character table, or bridge row is part of the
certificate.
\end{proof}

\begin{theorem}[InducedRepUp Subgroup and RepresentationRing consumer boundary]
\label{thm:inducedrep-subgroup-representationring-consumer-boundary}
An $\InducedRepUp$ consumer of the source certificates may read exactly the
SubgroupUp rows exposed by $\NameCert_{\SubgroupUp}$ and the
representation-ring rows exposed by $\NameCert_{\RepresentationRingUp}$,
together with the induction, restriction, Frobenius, provenance, and
continuation rows displayed in \autoref{def:inducedrep-bhist-carrier}. It may
not read a subgroup carrier, representation ring, functor, category, or
Frobenius adjunction row unless that row is present in the carrier,
classifier, or provenance ledger of the $\InducedRepUp$ packet.
\end{theorem}
\begin{proof}
Project the consumer request through the carrier packet. A SubgroupUp request
lands in $S$, and a RepresentationRingUp request lands in $R$. The source
certificates named by those two rows supply their own public carrier,
classifier, stability, exactness, and ledger boundaries.

Next project the $\InducedRepUp$-specific request. The induction endpoint is
$i$, the restriction endpoint is $r$, the Frobenius rows are
$F,\eta,\epsilon$, the provenance packet is $\rho$, and the continuation
ledger is $\lambda$. Transport between two such consumer surfaces is exactly
the componentwise $\hsame$ and $\Cont$ transport listed in the
restriction-induction classifier.

There are no remaining exported rows. Any row not found in the two source
certificates or in $i,r,F,\eta,\epsilon,\rho,\lambda$ is outside the consumer
boundary, so the downstream interface receives a concrete BEDC packet rather
than equality of host-level induction and restriction constructions.
\end{proof}

\begin{definition}[InducedRepUp stability obligation packet]
\label{def:inducedrep-stability-obligation-packet}
For carrier packets
$$
\mathcal{I}=(S,R,i,r,F,\eta,\epsilon,\rho,\lambda)
\qquad\text{and}\qquad
\mathcal{I}'=(S',R',i',r',F',\eta',\epsilon',\rho',\lambda'),
$$
the $\InducedRepUp$ stability obligation packet is the finite datum
consisting of the two displayed carriers, the componentwise $\hsame$ rows
from the restriction-induction classifier of
\autoref{def:inducedrep-restriction-induction-classifier}, and the finite
$\Cont$ comparison ledger from $\lambda$ to $\lambda'$. Its fields are:
\begin{enumerate}
  \item $\hsame$ rows for the consumed certificate rows $S$ and $R$;
  \item $\hsame$ rows for the induction and restriction endpoints $i$ and
  $r$;
  \item entrywise $\hsame$ rows for the Frobenius display
  $F,\eta,\epsilon$;
  \item an $\hsame$ row for the provenance packet $\rho$;
  \item the finite $\Cont$ comparison ledger relating the source,
  endpoint, Frobenius, provenance, and public continuation entries recorded
  by $\lambda$.
\end{enumerate}
The packet has no field for equality of host categories, host induction
functors, host restriction functors, functorial naturality, or adjunction
objects outside the displayed $\mathsf{BHist}$ rows.
\end{definition}

\begin{theorem}[InducedRepUp classifier stability]
\label{thm:inducedrep-classifier-stability}
The restriction-induction classifier of
\autoref{def:inducedrep-restriction-induction-classifier} transports every
carrier component of \autoref{def:inducedrep-bhist-carrier}. For any two
packets $\mathcal{I}$ and $\mathcal{I}'$ related by that classifier, the
transport repacks as the stability obligation packet of
\autoref{def:inducedrep-stability-obligation-packet} and preserves the
public $\NameCert_{\InducedRepUp}$ obligation surface of
\autoref{thm:inducedrep-namecert-obligation-surface}.
\end{theorem}
\begin{proof}
Project the two carriers as
$\mathcal{I}=(S,R,i,r,F,\eta,\epsilon,\rho,\lambda)$ and
$\mathcal{I}'=(S',R',i',r',F',\eta',\epsilon',\rho',\lambda')$. The
classifier is already componentwise: it gives the $\hsame$ rows for the
consumed SubgroupUp and RepresentationRingUp packets, the displayed
subgroup and representation-ring rows read from them, the induction and
restriction endpoints, the Frobenius rows, and the provenance packet.

It remains to repack the continuation part. The same classifier includes
the finite $\Cont$ comparison between $\lambda$ and $\lambda'$, entry by
entry, so the source, endpoint, Frobenius, provenance, and public
continuation reads are transported inside the displayed ledger.

The obligation surface in
\autoref{thm:inducedrep-namecert-obligation-surface} asks for no more data
than those projected rows. Repacking the projected $\hsame$ rows and the
finite $\Cont$ comparison gives the stability obligation packet, and the
surface is preserved because no host category, functor equality, adjunction
row, or bridge row is part of the transported data.
\end{proof}

\begin{theorem}[InducedRepUp continuation ledger closure]
\label{thm:inducedrep-cont-ledger-closure}
The source reads, induction and restriction endpoint reads, Frobenius reads,
provenance reads, and public continuation reads of an $\InducedRepUp$
carrier close under finite $\Cont$ composition inside the ledger
$\lambda$ of \autoref{def:inducedrep-bhist-carrier}. Consequently every
finite continuation needed by the obligation surface is again a row recorded
by $\lambda$.
\end{theorem}
\begin{proof}
Project the carrier to the finite packet
$\mathcal{I}=(S,R,i,r,F,\eta,\epsilon,\rho,\lambda)$. By definition,
$\lambda$ contains the consumed SubgroupUp rows, consumed
RepresentationRingUp rows, induction and restriction endpoint rows,
Frobenius rows, provenance rows, and public continuation rows exposed by the
packet.

Now compose only rows already listed in $\lambda$. A source read followed by
an endpoint read, an endpoint read followed by a Frobenius read, or a
Frobenius read followed by a public continuation read is still a finite
read through the same displayed ledger, because the ledger is the complete
$\Cont$ record for the carrier.

Thus the closure statement is a projection-and-repacking argument. The
projection chooses the listed rows of $\lambda$, and the repacking records
their finite composite as another continuation row of the same public
ledger. Nothing in the argument introduces a host functor, host category,
or adjunction object outside the carrier.
\end{proof}

\begin{theorem}[InducedRepUp package provenance exactness]
\label{thm:inducedrep-pkg-provenance-exactness}
Every row exported by the $\InducedRepUp$ package provenance surface is
exactly one of the rows recorded by $\rho$ or $\lambda$ in
\autoref{def:inducedrep-bhist-carrier}: the consumed SubgroupUp rows, the
consumed RepresentationRingUp rows, the induction row, the restriction row,
and the Frobenius rows $F,\eta,\epsilon$. No host category, host functor
equality, or adjunction row is exported by the provenance surface.
\end{theorem}
\begin{proof}
Project the package row $\rho$. Its definition records precisely the
consumed package rows from $S$ and $R$ together with the package rows
attached to $i$, $r$, $F$, $\eta$, and $\epsilon$. These are exactly the
SubgroupUp, RepresentationRingUp, induction, restriction, and Frobenius
rows named in the theorem.

Project the continuation ledger $\lambda$ next. It records the corresponding
public reads: source rows, endpoint rows, Frobenius rows, provenance rows,
and public continuation rows. Therefore every public continuation witness
for a provenance row is already present in the same finite carrier.

For the converse, take any row recorded by $\rho$ or $\lambda$ with one of
the listed roles. The carrier definition repacks it as part of the
$\InducedRepUp$ public provenance surface, and the consumer boundary of
\autoref{thm:inducedrep-subgroup-representationring-consumer-boundary}
excludes every row not so recorded. Hence no host category, equality of
induction or restriction functors, or Frobenius adjunction row is exported.
\end{proof}

\begin{theorem}[InducedRepUp source-Frobenius exact consumption]
\label{thm:inducedrep-source-frobenius-exact-consumption}
A downstream row consumed from an $\InducedRepUp$ packet is visible exactly
when it is one of the following finite public rows: a SubgroupUp source row
exposed through $S$, a RepresentationRingUp source row exposed through $R$,
an induction or restriction endpoint row, one of the Frobenius rows
$F,\eta,\epsilon$, or a provenance and continuation row recorded by $\rho$ or
$\lambda$. No host subgroup object, host representation category, host
functor equality, or Frobenius adjunction object is visible outside this
finite source--Frobenius ledger.
\end{theorem}
\begin{proof}
Project a consumed row through the carrier packet
$\mathcal{I}=(S,R,i,r,F,\eta,\epsilon,\rho,\lambda)$. The source rows are
exactly the SubgroupUp and RepresentationRingUp rows allowed by
\autoref{thm:inducedrep-subgroup-representationring-consumer-boundary}; the
endpoint rows are the displayed induction and restriction rows $i$ and $r$.

Project the Frobenius part next. By
\autoref{thm:inducedrep-frobenius-ledger-boundary}, every Frobenius read is
one of $F,\eta,\epsilon$ and has endpoints in the displayed induction and
restriction rows. By \autoref{thm:inducedrep-cont-ledger-closure}, any finite
continuation needed to consume those rows remains inside $\lambda$.

The provenance projection is fixed by
\autoref{thm:inducedrep-pkg-provenance-exactness}: every public provenance
row is recorded by $\rho$ or by the corresponding public continuation row in
$\lambda$. Therefore any downstream row consumed from the packet is on the
listed source, endpoint, Frobenius, provenance, or continuation surface.

Conversely, take any row on that finite list. The source rows repack through
the consumer boundary, the endpoint and Frobenius rows repack through the
Frobenius ledger boundary, and the provenance and continuation rows repack
through $\rho$ and $\lambda$. The four cited boundaries together reconstruct
the same $\InducedRepUp$ public packet, so every listed row is visible to the
consumer and no outside host-level datum is added.
\end{proof}
