\chapter{A Concrete Naming Certificate for $\VermaModuleUp$}
\label{ch:concrete-instances-vermamodule-namecert}

The Verma-module interface $\VermaModuleUp$ packages, for a semisimple Lie algebra and a highest weight, the universal highest-weight module obtained by inducing from a Borel subalgebra. It depends on $\NameCert_{\LieAlgebraUp}$ (\autoref{ch:concrete-instances-liealgebra-namecert}) and $\NameCert_{\RootSystemUp}$ (\autoref{ch:concrete-instances-rootsystem-namecert}).

\section{Carrier definition}
\label{sec:vermamodule-carrier}

\begin{theorem}[Verma-module finite carrier obligation]
\label{thm:vermamodule-carrier-obligation}
A $\VermaModuleUp$ packet is a finite $\mathsf{BHist}$ row package containing a
displayed $\LieAlgebraUp$ source row, $\RootSystemUp$ positive-root rows, a
highest-weight row, Borel action rows, induced-module generator rows, and
$\mathsf{Pkg}$ provenance naming the displayed Lie-algebra and root-system
sources. The packet contains no host quotient module, no selected PBW basis,
and no ambient category of modules beyond these finite rows.
\end{theorem}
\leanchecked{BEDC.Derived.VermaModuleUp.VermaModuleFiniteCarrier\_obligation\_surface}
\begin{proof}
Unpack the packet as a finite BEDC history. The Lie-algebra source, positive
root data, highest weight, Borel action, induced generator, and provenance
coordinates are the displayed rows of that history package.

Each consumer-visible coordinate is obtained by projecting one of those rows or
transporting it along the displayed $\hsame$ and $\Cont$ data. Since the packet
has no coordinate for a host quotient module or selected basis, neither object
is introduced by the carrier obligation.
\end{proof}

\section{The certificate}
\label{sec:vermamodule-certificate}

\begin{theorem}[Verma-module highest-weight ledger]
\label{thm:vermamodule-highest-weight-ledger}
Every accepted $\VermaModuleUp$ packet exposes exactly the highest-weight row,
lowering-operator rows from the displayed positive-root data, Borel action
rows, $\hsame$ comparison rows, $\Cont$ provenance rows, and $\mathsf{Pkg}$
dependency rows consumed by downstream representation certificates. It exports
no quotient by a maximal submodule, no irreducible-module classifier, and no
chosen basis for weight spaces.
\end{theorem}
\begin{proof}
Project an accepted packet to the rows named in
\autoref{thm:vermamodule-carrier-obligation}. The highest-weight coordinate,
lowering-operator coordinates, Borel action, transport, continuation, and
package provenance are all finite $\mathsf{BHist}$ entries.

Downstream representation certificates can only read through those finite
entries. Componentwise transport preserves the highest-weight and action rows,
and continuation rows record the finite lowering operations already present in
the packet.

The carrier contains no row for a maximal-submodule quotient, irreducibility
classifier, or basis choice. The accepted ledger therefore exhausts exactly the
displayed highest-weight surface.
\end{proof}

\begin{theorem}[Verma-module NameCert obligation surface]
\label{thm:vermamodule-namecert-obligation-surface}
The carrier obligation of \autoref{thm:vermamodule-carrier-obligation}, the
componentwise classifier transport over the displayed highest-weight and action
rows, the highest-weight ledger of
\autoref{thm:vermamodule-highest-weight-ledger}, and the source dependencies on
$\NameCert_{\LieAlgebraUp}$ and $\NameCert_{\RootSystemUp}$ provide the local
$\NameCert_{\VermaModuleUp}$ obligation surface. The surface is entirely
$\mathsf{BHist}$-anchored and does not introduce a host quotient module or a
choice of basis.
\end{theorem}
\begin{proof}
Begin with the finite carrier obligation. It supplies the source rows,
positive-root rows, highest-weight row, Borel action rows, induced-generator
rows, and package provenance needed for the local naming surface.

Transport the displayed classifier componentwise along $\hsame$. The
highest-weight and action rows move through the same finite coordinates, while
the $\Cont$ rows record only the lowering operations already carried by the
packet.

Finally apply the highest-weight ledger to identify the exact downstream
readback surface. Together with the displayed $\LieAlgebraUp$ and
$\RootSystemUp$ provenance, these rows provide the local
$\NameCert_{\VermaModuleUp}$ obligation surface without adding a quotient
module, irreducible classifier, or basis choice.
\end{proof}
