\chapter{A Concrete Naming Certificate for $\UnaryDirectionBridgeUp$}
\label{ch:concrete-instances-unarydirectionbridge-namecert}
\origin{human}

The $\UnaryDirectionBridgeUp$ interface packages the finite bridge by which the unary $\NatUp$ spine and the zero-spine $\AxisNatUp$ surface can be compared without identifying their kernel carriers. Its local certificate records the two source rows, the bridge witness, the one-point kernel intersection, standard-boundary interpretation, ledger policy, and public naming row. The packet is a comparison certificate over displayed BEDC rows; it is not a kernel equality between $\NatUp$ and $\AxisNatUp$.

The dependency anchors are $\NatUp$, $\AxisNatUp$, $\AddUp$, $\AxisAddUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and the Lean-side bridge object $\mathsf{UnaryDirectionBridge}$.

\begin{definition}[UnaryDirectionBridge NameCert carrier]
\label{def:unary-direction-bridge-namecert-carrier}
A $\UnaryDirectionBridgeUp$ carrier is a finite $\BHist$ packet
$$
U=(N,A,B,K,S,L,H,C,P,M)
$$
with the following visible rows:
\begin{enumerate}
\item $N$ is the $\NatUp$ unary-spine source row, read through the $\mathsf{Unary}$ predicate over $\Eone$ histories;
\item $A$ is the $\AxisNatUp$ zero-spine source row, read through the $\mathsf{ZeroSpine}$ predicate over $\Ezero$ histories;
\item $B$ is the local bridge row naming $\mathsf{UnaryDirectionBridge}$ and its two displayed source carriers;
\item $K$ is the kernel-distinctness ledger asserting that the unary and zero-spine carriers intersect only at $\emp$;
\item $S$ is the standard-boundary row, matching nonempty unary histories with nonempty zero-spine histories by length and preserving the $\AddUp/\AxisAddUp$ consumer route at the standard boundary;
\item $L$ is the ledger policy row, recording that bridge reads must cite $N,A,B,K,S$ before exporting any comparison;
\item $H$ stores componentwise $\hsame$ transports for the two source rows, bridge row, kernel-distinctness witness, standard-boundary row, ledger policy row, and local naming row;
\item $C$ stores displayed $\Cont$ routes for unary inspection, zero-spine inspection, bridge comparison, standard-boundary readback, ledger audit, and NameCert comparison;
\item $P$ is the $\Pkg$ provenance row naming $\NatUp$, $\AxisNatUp$, $\AddUp$, $\AxisAddUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and $\mathsf{UnaryDirectionBridge}$;
\item $M$ is the local $\NameCert_{\UnaryDirectionBridgeUp}$ row.
\end{enumerate}
The classifier compares accepted bridge packets only after transporting these rows componentwise. It has no coordinate for a kernel equality between $\NatUp$ and $\AxisNatUp$, no quotient identifying unary and zero-spine histories, and no host-level natural-number equality beyond the displayed standard-boundary row.
\end{definition}

\begin{theorem}[UnaryDirectionBridge kernel-distinct obligations]
\label{thm:unary-direction-bridge-kernel-distinct-obligations}
The local $\NameCert_{\UnaryDirectionBridgeUp}$ obligation surface must expose the $\NatUp$ unary source row $N$, the $\AxisNatUp$ zero-spine source row $A$, the bridge row $B$, and the kernel-distinctness ledger $K$. Every accepted bridge comparison first reads the two source classifiers, then cites $K$ to rule out a kernel-level carrier collapse except at $\emp$.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_kernel\_distinct\_obligations}
\begin{proof}
Project the carrier of \autoref{def:unary-direction-bridge-namecert-carrier}. The source rows $N$ and $A$ are separate coordinates, so a comparison cannot begin from a single shared carrier.

The bridge row $B$ names the comparison object, while $K$ records the only permitted kernel intersection. Reading $K$ before the standard-boundary row forces the comparison to treat unary and zero-spine histories as distinct BEDC predicates.

The transport rows $H$ and continuation routes $C$ preserve this separation for downstream consumers. Since the carrier contains no equality coordinate identifying $N$ and $A$, the obligations close exactly as a kernel-distinct bridge surface.
\end{proof}

\begin{theorem}[UnaryDirectionBridge standard boundary]
\label{thm:unary-direction-bridge-standard-boundary}
For an accepted $\UnaryDirectionBridgeUp$ carrier $U=(N,A,B,K,S,L,H,C,P,M)$, the public standard boundary is the displayed row $S$: nonempty unary histories are matched with nonempty zero-spine histories by the same finite length, and the $\AddUp/\AxisAddUp$ consumer route is read only after the source rows and the kernel-distinctness ledger have been transported through $H$ and $C$.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_standard\_boundary\_readout}
\begin{proof}
Begin with an accepted bridge packet and project the standard-boundary row $S$. Its inputs are the two already displayed source rows, not an ambient natural-number object.

The row $K$ is read before $S$, so the boundary comparison is licensed only after the paper has recorded the one-point kernel intersection. The transports in $H$ and the routes in $C$ then carry the unary and zero-spine rows to the same public comparison site.

The additive consumers $\AddUp$ and $\AxisAddUp$ are reached through this transported boundary. Because no carrier coordinate identifies the two source predicates, the standard boundary is a public interpretation row rather than a kernel collapse.
\end{proof}

\begin{theorem}[UnaryDirectionBridge ledger policy]
\label{thm:unary-direction-bridge-ledger-policy}
Every consumer-facing route out of an accepted $\UnaryDirectionBridgeUp$ packet factors through the displayed rows $N,A,B,K,S,L,H,C,P,M$. The ledger policy row $L$ rejects any route that compares $\NatUp$ and $\AxisNatUp$ by host equality, by quotienting histories, or by skipping the kernel-distinctness witness.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_ledger\_policy}
\begin{proof}
Take any consumer-facing route and inspect the finite packet. The available source, bridge, kernel, standard-boundary, policy, transport, continuation, provenance, and naming rows are exactly $N,A,B,K,S,L,H,C,P,M$.

The policy row $L$ orders the read: source rows first, bridge row second, kernel-distinctness ledger third, and standard-boundary comparison only after those rows are present. The continuation routes in $C$ expose no alternate branch.

Thus the route is exhausted by the displayed ledger. Since the carrier has no coordinate for host equality or quotient identification of histories, neither can be exported by a bridge consumer.
\end{proof}

\begin{theorem}[UnaryDirectionBridge NameCert surface]
\label{thm:unary-direction-bridge-namecert-surface}
The $\NameCert_{\UnaryDirectionBridgeUp}$ surface is the finite bridge packet of \autoref{def:unary-direction-bridge-namecert-carrier} together with the kernel-distinctness obligations of \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}, the standard boundary of \autoref{thm:unary-direction-bridge-standard-boundary}, and the ledger policy of \autoref{thm:unary-direction-bridge-ledger-policy}. It realizes the unary-direction bridge as a NameCert packet while keeping $\NatUp$ and $\AxisNatUp$ distinct inside the kernel.
\end{theorem}
\begin{proof}
Assemble the carrier rows $N,A,B,K,S,L,H,C,P,M$. These rows provide the two source certificates, the bridge object, kernel-distinctness witness, standard-boundary readback, policy ledger, transports, routes, provenance, and local name.

Apply \autoref{thm:unary-direction-bridge-kernel-distinct-obligations} to bind the two source rows before any comparison. Apply \autoref{thm:unary-direction-bridge-standard-boundary} to expose the length-preserving public boundary. Apply \autoref{thm:unary-direction-bridge-ledger-policy} to rule out routes that bypass the displayed rows.

Repacking these rows gives the local $\NameCert$ surface. The packet therefore realizes the bridge at the paper-certificate level and leaves the kernel carriers separate.
\end{proof}

\begin{theorem}[UnaryDirectionBridge source obligation inventory]
\label{thm:unary-direction-bridge-source-obligation-inventory}
Every accepted $\UnaryDirectionBridgeUp$ packet exposes exactly the source rows needed before any bridge comparison: the $\NatUp$ unary-spine row $N$, the $\AxisNatUp$ zero-spine row $A$, the $\AddUp$ and $\AxisAddUp$ standard-boundary consumer rows read through $S$, the carrier history row $\BHist$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ routes through $C$, package provenance through $P$, and the local $\NameCert$ row $M$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:unary-direction-bridge-namecert-carrier}. The source coordinates are $N$ and $A$, while $S$ is the only displayed row through which $\AddUp/\AxisAddUp$ consumers may read the public boundary.

Use \autoref{thm:unary-direction-bridge-kernel-distinct-obligations} to keep the source rows separate before the boundary is inspected. Then use \autoref{thm:unary-direction-bridge-standard-boundary} and \autoref{thm:unary-direction-bridge-ledger-policy} to account for the boundary, route, and policy rows.

Finally, \autoref{thm:unary-direction-bridge-namecert-surface} repacks the same inventory as the local certificate. Since the carrier has no further coordinate, the listed rows exhaust the source obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_source\_obligation\_inventory}

\begin{theorem}[UnaryDirectionBridge kernel-boundary obligation]
\label{thm:unary-direction-bridge-kernel-boundary-obligation}
Any $\UnaryDirectionBridgeUp$ read that reaches the standard-boundary row $S$ must first pass through the kernel-distinctness ledger $K$. Thus a consumer cannot interpret the displayed $\AddUp/\AxisAddUp$ boundary until the unary $\NatUp$ row, the zero-spine $\AxisNatUp$ row, and the one-point kernel-intersection policy have been recorded in the same packet.
\end{theorem}
\begin{proof}
Start from the kernel-distinctness obligations. By \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}, the rows $N,A,B,K$ are read before any comparison is exported.

The standard boundary of \autoref{thm:unary-direction-bridge-standard-boundary} is therefore downstream of $K$. It reads nonempty unary and zero-spine histories through the displayed boundary, but it does not identify the two kernel carriers.

The ledger policy of \autoref{thm:unary-direction-bridge-ledger-policy} rules out a route that skips $K$. Repacking through \autoref{thm:unary-direction-bridge-namecert-surface} gives the required boundary obligation for every accepted packet.
\end{proof}

\begin{theorem}[UnaryDirectionBridge standard handoff obligation]
\label{thm:unary-direction-bridge-standard-handoff-obligation}
$\AddUp/\AxisAddUp$ consumers of an accepted $\UnaryDirectionBridgeUp$ packet read only the displayed standard-boundary row $S$, the componentwise transport rows $H$, the continuation routes $C$, package provenance $P$, the local $\NameCert$ row $M$, and the source and ledger rows required by $N,A,B,K,L$. They receive no host natural-number equality, quotient of histories, or carrier identity between $\NatUp$ and $\AxisNatUp$.
\end{theorem}
\begin{proof}
First expose the public boundary. \autoref{thm:unary-direction-bridge-standard-boundary} places every $\AddUp/\AxisAddUp$ handoff on $S$ after the source rows and the kernel ledger have been transported.

Next apply the ledger policy. \autoref{thm:unary-direction-bridge-ledger-policy} requires the route to cite $N,A,B,K,S,L,H,C,P,M$ before it can export a comparison to additive consumers.

Finally use the NameCert surface. \autoref{thm:unary-direction-bridge-namecert-surface} packages exactly those rows and keeps $\NatUp$ and $\AxisNatUp$ distinct inside the kernel, so the standard handoff cannot export host equality, quotient identification, or carrier identity.
\end{proof}

\begin{theorem}[UnaryDirectionBridge AxisAdd handoff obligations]
\label{thm:unary-direction-bridge-axisadd-handoff-obligations}
Every $\AddUp/\AxisAddUp$ consumer using the standard-boundary handoff of an
accepted $\UnaryDirectionBridgeUp$ packet must first read the rows
$N,A,B,K,S,L,H,C,P,M$. The handoff is licensed only after the source rows,
bridge row, kernel-distinctness ledger, standard-boundary row, policy row,
transport row, continuation row, provenance row, and local $\NameCert$ row are
all present.
\end{theorem}
\begin{proof}
Start from the carrier of
\autoref{def:unary-direction-bridge-namecert-carrier}. Its displayed rows are
exactly $N,A,B,K,S,L,H,C,P,M$, so a consumer route has no additional coordinate
from which to read a boundary.

Apply \autoref{thm:unary-direction-bridge-kernel-distinct-obligations} before
the public boundary is used. This binds the source rows and the
kernel-distinctness ledger.

Apply \autoref{thm:unary-direction-bridge-standard-boundary} and then
\autoref{thm:unary-direction-bridge-ledger-policy}. The first theorem supplies
the length-preserving handoff row, and the second requires the policy and route
rows before export.

Finally, use \autoref{thm:unary-direction-bridge-namecert-surface} to repack
the read rows as the local certificate. Thus $\AddUp/\AxisAddUp$ consumers reach
the handoff only through the displayed packet.
\end{proof}

\begin{theorem}[UnaryDirectionBridge empty-intersection readback]
\label{thm:unary-direction-bridge-empty-intersection-readback}
For an accepted $\UnaryDirectionBridgeUp$ packet, the only kernel intersection
exposed by the bridge is the empty-history row named by $K$. No consumer-facing
readback from $B$, $S$, $L$, $H$, $C$, $P$, or $M$ exports a second intersection
between the $\NatUp$ unary source row and the $\AxisNatUp$ zero-spine source row.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_empty\_intersection\_readback}
\begin{proof}
Read the kernel-distinctness obligations. By
\autoref{thm:unary-direction-bridge-kernel-distinct-obligations}, the bridge
must cite $K$ before it compares the source rows.

The standard-boundary theorem \autoref{thm:unary-direction-bridge-standard-boundary}
then interprets nonempty rows only at the public boundary. It does not insert a
kernel equality between the two predicates.

The ledger-policy theorem \autoref{thm:unary-direction-bridge-ledger-policy}
rules out host equality, quotienting, and routes that skip $K$. Together with
\autoref{thm:unary-direction-bridge-namecert-surface}, this leaves the
empty-history row named by $K$ as the sole exposed kernel intersection.
\end{proof}

\begin{theorem}[UnaryDirectionBridge consumer normal form]
\label{thm:unary-direction-bridge-consumer-normal-form}
Every consumer route out of an accepted $\UnaryDirectionBridgeUp$ packet
normalizes to the source rows $N,A$, the bridge row $B$, the kernel-distinctness
ledger $K$, the standard-boundary row $S$, and the local $\NameCert$ row $M$,
with transport, continuation, provenance, and policy reads occurring only as
displayed rows of the same packet. No normalized route contains quotient
identification or host-level natural-number equality.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_consumer\_normal\_form}
\begin{proof}
Inspect the carrier rows given by
\autoref{def:unary-direction-bridge-namecert-carrier}. A consumer can mention
only the displayed source, bridge, kernel, standard-boundary, policy, transport,
route, provenance, and naming rows.

Apply \autoref{thm:unary-direction-bridge-ledger-policy}. It orders every
consumer-facing route through the source rows, the bridge row, the
kernel-distinctness ledger, and the standard-boundary row.

Apply \autoref{thm:unary-direction-bridge-standard-boundary} for the public
handoff and \autoref{thm:unary-direction-bridge-namecert-surface} for the local
name. The resulting normal form is therefore $N,A,B,K,S,M$ with $L,H,C,P$ as
the displayed support rows, and it has no quotient or host natural-number
equality coordinate.
\end{proof}

\begin{theorem}[UnaryDirectionBridge carrier admission]
\label{thm:unary-direction-bridge-carrier-admission}
For the finite packet $U=(N,A,B,K,S,L,H,C,P,M)$ over $\NatUp$, $\AxisNatUp$, $\AddUp$, $\AxisAddUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, admission to the $\UnaryDirectionBridgeUp$ surface is exactly admission of the ten displayed rows of \autoref{def:unary-direction-bridge-namecert-carrier}. The admitted packet exposes the unary source row, zero-spine source row, bridge row, kernel-distinctness ledger, standard-boundary row, ledger policy, componentwise transports, continuation routes, package provenance, and local naming row, and it exposes no additional carrier coordinate.
\end{theorem}
\begin{proof}
Start with the carrier description of \autoref{def:unary-direction-bridge-namecert-carrier}. It lists $N,A,B,K,S,L,H,C,P,M$ as the complete finite packet over the named source, bridge, history, transport, continuation, package, and naming surfaces.

Apply the kernel-distinct obligations of \autoref{thm:unary-direction-bridge-kernel-distinct-obligations} and the standard boundary of \autoref{thm:unary-direction-bridge-standard-boundary}. These identify the source rows, the bridge row, the kernel ledger, and the public boundary as displayed rows of the same packet.

Use the ledger policy of \autoref{thm:unary-direction-bridge-ledger-policy}, the NameCert surface of \autoref{thm:unary-direction-bridge-namecert-surface}, and the AxisAdd handoff of \autoref{thm:unary-direction-bridge-axisadd-handoff-obligations}. Together they force every admitted read through the packet rows and leave no extra carrier coordinate.

Finally, the empty-intersection readback of \autoref{thm:unary-direction-bridge-empty-intersection-readback} and the consumer normal form of \autoref{thm:unary-direction-bridge-consumer-normal-form} exclude host equality, quotient identification, and a second kernel carrier. Thus admission is exactly the finite ledger packet.
\end{proof}

\begin{theorem}[UnaryDirectionBridge classifier stability]
\label{thm:unary-direction-bridge-classifier-stability}
For an accepted $\UnaryDirectionBridgeUp$ packet $U=(N,A,B,K,S,L,H,C,P,M)$, componentwise $\hsame$ transport by the stored row $H$ preserves the unary source classifier, the zero-spine source classifier, the bridge classifier, the kernel-distinctness ledger, the standard-boundary route, the ledger policy, the continuation routes, the package provenance, and the local $\NameCert$ row. After transport, the packet still presents the same kernel-distinctness ledger and the same standard-boundary route.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_classifier\_stability}
\begin{proof}
Project $H$ from the carrier of \autoref{def:unary-direction-bridge-namecert-carrier}. By construction it stores componentwise transports for the two source rows, bridge row, kernel-distinctness witness, standard-boundary row, ledger policy row, and local naming row.

Apply \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}. Since $K$ remains a transported row rather than an equality coordinate, the transported classifiers cannot collapse the $\NatUp$ and $\AxisNatUp$ carriers.

Use \autoref{thm:unary-direction-bridge-standard-boundary} and \autoref{thm:unary-direction-bridge-axisadd-handoff-obligations} for the boundary route. The transported standard-boundary row is the only route available to $\AddUp/\AxisAddUp$ consumers.

The ledger policy, NameCert surface, empty-intersection readback, and consumer normal form of \autoref{thm:unary-direction-bridge-ledger-policy}, \autoref{thm:unary-direction-bridge-namecert-surface}, \autoref{thm:unary-direction-bridge-empty-intersection-readback}, and \autoref{thm:unary-direction-bridge-consumer-normal-form} then keep every classifier read inside the displayed packet. Hence componentwise transport preserves both the kernel-distinctness ledger and the standard-boundary route.
\end{proof}

\begin{theorem}[UnaryDirectionBridge ledger exactness]
\label{thm:unary-direction-bridge-ledger-exactness}
Every consumer route out of an accepted $\UnaryDirectionBridgeUp$ packet is exhausted by $N,A,B,K,S,L,H,C,P,M$. There is no consumer route through host equality of natural numbers, no quotient identification of histories, and no collapse of the $\NatUp$ unary carrier with the $\AxisNatUp$ zero-spine carrier.
\end{theorem}
\begin{proof}
Begin with the finite carrier in \autoref{def:unary-direction-bridge-namecert-carrier}. Its rows are exactly $N,A,B,K,S,L,H,C,P,M$, so any consumer route must be assembled from these rows.

Apply the kernel-distinct obligations and standard boundary from \autoref{thm:unary-direction-bridge-kernel-distinct-obligations} and \autoref{thm:unary-direction-bridge-standard-boundary}. They require the source rows and $K$ before any public boundary read.

Next use the ledger policy, NameCert surface, and AxisAdd handoff of \autoref{thm:unary-direction-bridge-ledger-policy}, \autoref{thm:unary-direction-bridge-namecert-surface}, and \autoref{thm:unary-direction-bridge-axisadd-handoff-obligations}. These force consumer access through the displayed ledger and then through the local naming row.

Finally apply the empty-intersection readback of \autoref{thm:unary-direction-bridge-empty-intersection-readback} and the consumer normal form of \autoref{thm:unary-direction-bridge-consumer-normal-form}. They rule out any second intersection, quotient route, or host equality coordinate, so the displayed finite ledger is exact.
\end{proof}

\begin{theorem}[UnaryDirectionBridge source-classifier transport]
\label{thm:unary-direction-bridge-source-classifier-transport}
For an accepted $\UnaryDirectionBridgeUp$ carrier $U=(N,A,B,K,S,L,H,C,P,M)$, componentwise $\hsame$ transport of $N,A,B,K,S,L,H,C,P,M$ preserves the separate $\NatUp$ unary source classifier and the $\AxisNatUp$ zero-spine source classifier. The transported packet keeps the two source classifiers as distinct rows and does not collapse them into a kernel equality.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_source\_classifier\_transport}
\begin{proof}
Project the carrier of \autoref{def:unary-direction-bridge-namecert-carrier}. Rows $N$ and $A$ are separate source rows, while $H$ supplies componentwise transport for those rows together with the bridge, ledger, route, provenance, and local name.

Apply \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}. The kernel-distinctness row $K$ must be read before any comparison, so transport cannot replace the two classifiers by a shared kernel carrier.

Use \autoref{thm:unary-direction-bridge-empty-intersection-readback} to keep the empty-history row as the only exposed kernel intersection. Thus the transported source classifiers remain the unary $\NatUp$ row and the zero-spine $\AxisNatUp$ row separately.
\end{proof}

\begin{theorem}[UnaryDirectionBridge additive consumer exactness]
\label{thm:unary-direction-bridge-additive-consumer-exactness}
Every $\AddUp/\AxisAddUp$ consumer of an accepted $\UnaryDirectionBridgeUp$ carrier reads the standard-boundary row only after the source rows, bridge row, kernel-distinctness ledger, ledger policy, transports, routes, provenance, and local $\NameCert$ row are present. The consumer receives the rows $N,A,B,K,S,L,H,C,P,M$ in that order of dependence and receives no kernel equality between $\NatUp$ and $\AxisNatUp$.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_additive\_consumer\_exactness}
\begin{proof}
Start with the consumer normal form of \autoref{thm:unary-direction-bridge-consumer-normal-form}. It limits every consumer route to the source rows, bridge row, kernel-distinctness ledger, standard-boundary row, local name, and the displayed support rows.

Apply \autoref{thm:unary-direction-bridge-axisadd-handoff-obligations}. This requires $N,A,B,K,S,L,H,C,P,M$ to be present before the $\AddUp/\AxisAddUp$ handoff is licensed.

The standard-boundary theorem \autoref{thm:unary-direction-bridge-standard-boundary} supplies the public boundary only after those rows have been transported. The ledger policy of \autoref{thm:unary-direction-bridge-ledger-policy} rules out any consumer route that skips the source rows or exports a host equality.
\end{proof}

\begin{theorem}[UnaryDirectionBridge NameCert obligation closure]
\label{thm:unary-direction-bridge-namecert-obligation-closure}
The carrier, kernel-distinctness obligations, standard boundary, ledger policy, consumer normal form, source-classifier transport, and additive consumer exactness assemble the local $\NameCert_{\UnaryDirectionBridgeUp}$ obligation closure for $U=(N,A,B,K,S,L,H,C,P,M)$. The closure keeps the unary and zero-spine kernels distinct while presenting the finite bridge packet required by downstream additive consumers.
\end{theorem}
\begin{proof}
The carrier of \autoref{def:unary-direction-bridge-namecert-carrier} supplies the finite packet. The kernel-distinctness obligations, standard boundary, ledger policy, and NameCert surface of \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}, \autoref{thm:unary-direction-bridge-standard-boundary}, \autoref{thm:unary-direction-bridge-ledger-policy}, and \autoref{thm:unary-direction-bridge-namecert-surface} bind the basic certificate rows.

Add the handoff obligations and empty-intersection readback from \autoref{thm:unary-direction-bridge-axisadd-handoff-obligations} and \autoref{thm:unary-direction-bridge-empty-intersection-readback}. These keep additive consumers on the displayed standard boundary and prevent a second kernel intersection from appearing.

Finally apply \autoref{thm:unary-direction-bridge-consumer-normal-form}, \autoref{thm:unary-direction-bridge-source-classifier-transport}, and \autoref{thm:unary-direction-bridge-additive-consumer-exactness}. The resulting local NameCert obligation closure is exactly the displayed bridge packet, with no asserted kernel equality.
\end{proof}

\begin{theorem}[UnaryDirectionBridge scoped source bindings]
\label{thm:unary-direction-bridge-scoped-source-bindings}
For an accepted $\UnaryDirectionBridgeUp$ carrier $U=(N,A,B,K,S,L,H,C,P,M)$, the rows $N,A,B,K,S,L,H,C,P,M$ bind the bridge packet to $\NatUp$, $\AxisNatUp$, $\AddUp$, $\AxisAddUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The binding is scoped to the displayed carrier rows: $N$ and $A$ are the two source classifiers, $B,K,S,L$ are the bridge, kernel-distinctness, boundary, and policy rows, $H$ and $C$ are the transport and continuation rows, $P$ is the package provenance row, and $M$ is the local naming row.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:unary-direction-bridge-namecert-carrier}. The row list already names the two source surfaces, the bridge object, the kernel ledger, the boundary, the policy, the transport, the route, the package row, and the local $\NameCert$ row.

Apply \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}. This keeps $N$ and $A$ as separate source classifiers and forces every comparison to cite $K$ before a public boundary is read.

Use \autoref{thm:unary-direction-bridge-standard-boundary} for the $S$ row and \autoref{thm:unary-direction-bridge-ledger-policy} for the $L$ row. The transport and route rows $H,C$ carry these displayed rows without creating a host equality or quotient coordinate.

Finally apply \autoref{thm:unary-direction-bridge-namecert-surface}. The provenance row $P$ and local name $M$ therefore bind the packet to the listed BEDC dependencies as scoped rows of the same finite carrier.
\end{proof}

\begin{theorem}[UnaryDirectionBridge additive route scope]
\label{thm:unary-direction-bridge-additive-route-scope}
Every $\AddUp/\AxisAddUp$ handoff route out of an accepted $\UnaryDirectionBridgeUp$ packet factors through $K,S,H,C,P,M$ together with the source rows $N,A$ and the bridge row $B$. Such a route cannot use host equality of natural numbers, quotient identification of histories, or a second kernel carrier for the unary and zero-spine sources.
\end{theorem}
\begin{proof}
Start with the additive consumer exactness of \autoref{thm:unary-direction-bridge-additive-consumer-exactness}. It says that an $\AddUp/\AxisAddUp$ consumer receives the displayed source, bridge, kernel, policy, transport, route, provenance, and local naming rows before the boundary is used.

Apply the source-classifier transport theorem \autoref{thm:unary-direction-bridge-source-classifier-transport}. The transported packet still has separate $\NatUp$ and $\AxisNatUp$ source rows, so the additive route cannot be reinterpreted as a single kernel carrier.

Use the empty-intersection readback of \autoref{thm:unary-direction-bridge-empty-intersection-readback} and the consumer normal form of \autoref{thm:unary-direction-bridge-consumer-normal-form}. These exclude a second kernel intersection, quotient identification, and host equality from the normalized route.

The remaining route is therefore exactly the displayed additive handoff through $K,S,H,C,P,M$, with $N,A,B$ supplying the source and bridge context.
\end{proof}

\begin{theorem}[UnaryDirectionBridge scoped NameCert package]
\label{thm:unary-direction-bridge-namecert-scoped-package}
The scoped source bindings of \autoref{thm:unary-direction-bridge-scoped-source-bindings}, the additive route scope of \autoref{thm:unary-direction-bridge-additive-route-scope}, and the obligation closure of \autoref{thm:unary-direction-bridge-namecert-obligation-closure} assemble the scoped $\NameCert_{\UnaryDirectionBridgeUp}$ package. The package exposes the carrier rows, the obligation closure, the scoped BEDC dependency bindings, and the additive handoff route, while preserving the separation of $\NatUp$ and $\AxisNatUp$ inside the kernel.
\end{theorem}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_namecert\_scoped\_package}
\begin{proof}
Begin with \autoref{thm:unary-direction-bridge-namecert-obligation-closure}. It supplies the local closure of the carrier, kernel-distinctness obligations, standard boundary, ledger policy, consumer normal form, source-classifier transport, and additive consumer exactness.

Apply \autoref{thm:unary-direction-bridge-scoped-source-bindings}. This binds the same finite packet to $\NatUp$, $\AxisNatUp$, $\AddUp$, $\AxisAddUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ through displayed carrier rows.

Apply \autoref{thm:unary-direction-bridge-additive-route-scope}. The additive route is then confined to the scoped bridge packet and cannot pass through host equality, quotient identification, or a second kernel carrier.

Repacking these rows gives the scoped local $\NameCert$ package for $\UnaryDirectionBridgeUp$. Its public commitment is the displayed BEDC bridge packet, not an identification of the two source kernels.
\end{proof}

\begin{theorem}[UnaryDirectionBridge kernel-axis composition]
\label{thm:unary-direction-bridge-kernel-axis-composition}
For an accepted $\UnaryDirectionBridgeUp$ carrier $U=(N,A,B,K,S,L,H,C,P,M)$, the kernel-distinct obligations, standard boundary, and $\AxisAddUp$ handoff assemble one $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route from the unary direction row $N$ to the additive consumer row. The route reads $A,B,K,S,L,H,C,P,M$ as displayed support and never identifies the unary and zero-spine classifiers as one kernel carrier.
\end{theorem}
\begin{proof}
Project the carrier and begin with the kernel-distinct obligations of \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}. They force the route to read the $\NatUp$ row $N$, the $\AxisNatUp$ row $A$, the bridge row $B$, and the kernel ledger $K$ before any additive handoff is considered.

Next apply the standard boundary of \autoref{thm:unary-direction-bridge-standard-boundary}. The boundary row $S$ is reached only after the source rows and $K$ have been transported through $H$ and replayed through $C$.

Finally use \autoref{thm:unary-direction-bridge-axisadd-handoff-obligations} and \autoref{thm:unary-direction-bridge-additive-consumer-exactness}. These results place the $\AxisAddUp$ consumer behind the same displayed packet and repack the route through $L,P,M$ as policy, provenance, and local naming data. The resulting composition is a projection-and-route composition, not a carrier equivalence.
\end{proof}

\begin{theorem}[UnaryDirectionBridge bidirectional readback]
\label{thm:unary-direction-bridge-bidirectional-readback}
For accepted left and right direction reads of a $\UnaryDirectionBridgeUp$ packet, if their displayed $\hsame$ rows and $\Cont$ rows agree, then both reads transport to the same empty-intersection readback surface. The common surface is the $K$-licensed intersection row together with the standard boundary and local NameCert rows, not an equivalence between the source classifiers.
\end{theorem}
\begin{proof}
Start with the two direction reads and project their carrier rows. Agreement of the displayed $\hsame$ and $\Cont$ rows means both reads use the same transport $H$ and the same route family $C$.

Apply \autoref{thm:unary-direction-bridge-empty-intersection-readback}. The only kernel intersection exposed by either read is the empty-history row licensed by $K$.

Use \autoref{thm:unary-direction-bridge-source-classifier-transport} to keep the unary and zero-spine classifiers separate after transport. Then apply \autoref{thm:unary-direction-bridge-standard-boundary} and \autoref{thm:unary-direction-bridge-namecert-surface} to place both reads on the same public boundary and local certificate surface.

Thus the left and right reads agree at the empty-intersection readback surface while preserving the source-classifier separation.
\end{proof}

\begin{theorem}[UnaryDirectionBridge downstream seal]
\label{thm:unary-direction-bridge-downstream-seal}
Every downstream $\AxisAddUp$ or $\AxisZeckendorfCannotClaimUp$ consumer reads an accepted $\UnaryDirectionBridgeUp$ packet only through the carrier, kernel-distinct classifier rows, ledger policy, source-classifier transport, and additive consumer exactness rows. The downstream seal exports the bridge as the displayed packet $U=(N,A,B,K,S,L,H,C,P,M)$ and exports no quotient identification, host natural-number equality, or carrier equivalence between $\NatUp$ and $\AxisNatUp$.
\end{theorem}
\begin{proof}
Begin with carrier admission and ledger policy, \autoref{thm:unary-direction-bridge-carrier-admission} and \autoref{thm:unary-direction-bridge-ledger-policy}. They restrict every downstream read to the ten displayed rows and order the read through the source, bridge, kernel, boundary, policy, transport, route, provenance, and naming data.

For the classifier side, apply \autoref{thm:unary-direction-bridge-kernel-distinct-obligations}, \autoref{thm:unary-direction-bridge-classifier-stability}, and \autoref{thm:unary-direction-bridge-source-classifier-transport}. These keep $N$ and $A$ as separate source classifiers under componentwise transport.

For the consumer side, use \autoref{thm:unary-direction-bridge-additive-consumer-exactness} and \autoref{thm:unary-direction-bridge-kernel-axis-composition}. The $\AxisAddUp$ route and any $\AxisZeckendorfCannotClaimUp$ consumer that depends on it can therefore read only the displayed bridge packet.

The empty-intersection readback excludes any second kernel overlap, and the consumer normal form excludes host equality and quotient identification. Hence the downstream seal is the packet route itself, not a carrier/classifier equivalence transport.
\end{proof}

\begin{theorem}[UnaryDirectionBridge scoped source anchors]
\label{thm:unary-direction-bridge-scope-source-anchors}
Every accepted $\UnaryDirectionBridgeUp$ packet $U=(N,A,B,K,S,L,H,C,P,M)$ binds the $\NatUp$ unary source, the $\AxisNatUp$ zero-spine source, the kernel-distinctness ledger, and the standard-boundary row to the displayed support
$$
\BHist,\hsame,\Cont,\Pkg,\NameCert.
$$
The binding is a source-route obligation: $N$ and $A$ remain separate source classifiers, $K$ records their kernel separation, $S$ is the only standard-boundary row, and $L,H,C,P,M$ are the ledger, transport, continuation, provenance, and local certificate rows through which downstream consumers read the packet.
\end{theorem}
\begin{proof}
Start with the carrier and carrier admission results, \autoref{def:unary-direction-bridge-namecert-carrier} and \autoref{thm:unary-direction-bridge-carrier-admission}. They make $N,A,B,K,S,L,H,C,P,M$ the complete admitted packet surface and place the source rows, bridge row, ledger row, boundary row, transport rows, route row, package row, and local name in one carrier.

Apply the kernel-distinct obligations and standard boundary, \autoref{thm:unary-direction-bridge-kernel-distinct-obligations} and \autoref{thm:unary-direction-bridge-standard-boundary}. These force every source comparison to read $K$ before $S$ and prevent the unary and zero-spine source classifiers from being merged.

Use the ledger policy, classifier stability, and ledger exactness of \autoref{thm:unary-direction-bridge-ledger-policy}, \autoref{thm:unary-direction-bridge-classifier-stability}, and \autoref{thm:unary-direction-bridge-ledger-exactness}. The only stable transport route is the displayed $H,C,P,M$ route, so every accepted source read is anchored to the listed BEDC support.

Finally apply the obligation closure of \autoref{thm:unary-direction-bridge-namecert-obligation-closure}. It repacks these rows as the local $\NameCert_{\UnaryDirectionBridgeUp}$ obligation surface, with no additional kernel equality or host natural-number route.
\end{proof}

\begin{theorem}[UnaryDirectionBridge scoped additive route]
\label{thm:unary-direction-bridge-scope-additive-route}
Every $\AddUp/\AxisAddUp$ consumer route out of an accepted $\UnaryDirectionBridgeUp$ packet factors through the scoped source anchors of \autoref{thm:unary-direction-bridge-scope-source-anchors} before reaching the standard boundary. Thus the additive route receives the unary source, zero-spine source, bridge row, kernel-distinctness ledger, ledger policy, componentwise $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row before any standard-boundary read.
\end{theorem}
\begin{proof}
First apply the scoped source anchors. They bind $N,A,B,K,S,L,H,C,P,M$ to the finite BEDC support and make $K$ available before the standard-boundary row is consumed.

Next use the additive consumer exactness and additive route scope, \autoref{thm:unary-direction-bridge-additive-consumer-exactness} and \autoref{thm:unary-direction-bridge-additive-route-scope}. These results identify the $\AddUp/\AxisAddUp$ route as a consumer of the displayed packet, not as a separate operation over host equality or quotient histories.

The carrier admission theorem and ledger policy keep the route inside the admitted rows. The standard-boundary theorem then places $S$ after the source and kernel-distinctness anchors, while classifier stability transports the same route through $H,C,P,M$.

Finally the obligation closure repacks the route as a downstream obligation of the same local certificate. The consumer therefore reaches the boundary only through the scoped source anchors and the displayed bridge packet.
\end{proof}

\begin{theorem}[UnaryDirectionBridge scoped NameCert transport]
\label{thm:unary-direction-bridge-scope-namecert-transport}
Componentwise $\hsame$ transport of an accepted $\UnaryDirectionBridgeUp$ packet preserves the scoped bridge packet of \autoref{thm:unary-direction-bridge-scope-source-anchors} and the additive route of \autoref{thm:unary-direction-bridge-scope-additive-route}. The transported packet cannot collapse the $\NatUp$ unary source classifier and the $\AxisNatUp$ zero-spine source classifier into one kernel row.
\end{theorem}
\begin{proof}
Begin with classifier stability and source-classifier transport, \autoref{thm:unary-direction-bridge-classifier-stability} and \autoref{thm:unary-direction-bridge-source-classifier-transport}. They state that componentwise transport preserves the source rows, bridge row, kernel ledger, standard-boundary row, route rows, package provenance, and local naming row.

Apply the scoped source anchors to the transported packet. The anchors still require $N$ and $A$ as separate source classifiers and still require $K$ before any comparison reaches $S$.

Use ledger exactness, ledger policy, and the standard boundary. These exclude host natural-number equality, quotient identification of histories, and any second kernel carrier as sources for the transported route.

Finally combine the scoped additive route with the obligation closure. The resulting transported $\NameCert_{\UnaryDirectionBridgeUp}$ packet is the same finite bridge surface over $\BHist,\hsame,\Cont,\Pkg,\NameCert$, so transport preserves the route without identifying the two source classifiers.
\end{proof}

\begin{theorem}[UnaryDirectionBridge standard-boundary consumer factorization]
\label{thm:unary-direction-bridge-standard-boundary-consumer-factorization}
Every $\AddUp$ or $\AxisAddUp$ consumer of the standard boundary of an accepted $\UnaryDirectionBridgeUp$ packet
$$
U=(N,A,B,K,S,L,H,C,P,M)
$$
factors through the displayed unary source row $N$, zero-spine source row $A$, bridge row $B$, kernel-distinctness ledger $K$, standard-boundary row $S$, ledger policy $L$, componentwise transports $H$, continuation routes $C$, package provenance $P$, and local name $M$. The consumer receives no carrier equivalence between $\NatUp$ and $\AxisNatUp$, no host natural-number equality, and no quotient identification of histories.
\end{theorem}
\begin{proof}
Start from carrier admission and the standard-boundary theorem. They make $S$ a row of the accepted packet and place it after the source rows, bridge row, and kernel-distinctness ledger.

Apply the scoped source anchors. They require $N,A,B,K,S,L,H,C,P,M$ before any boundary consumer can read the packet, and they keep the unary and zero-spine source classifiers separate.

Now use the scoped additive route and additive consumer exactness. These route every $\AddUp/\AxisAddUp$ read through the displayed bridge packet rather than through a host-side equality or a quotient transport.

Finally apply scoped NameCert transport. Componentwise transport preserves the same packet surface, so any standard-boundary consumer factors through the displayed rows and through no alternate carrier/classifier equivalence.
\end{proof}
\leanchecked{BEDC.Derived.UnaryDirectionBridgeUp.UnaryDirectionBridgeCarrier\_standard\_boundary\_consumer\_factorization}

\begin{theorem}[UnaryDirectionBridge AxisZeckendorf ledger gate]
\label{thm:unary-direction-bridge-axiszeckendorf-ledger-gate}
Any $\AxisZeckendorfCannotClaimUp$ consumer of an accepted $\UnaryDirectionBridgeUp$ packet must read the kernel-distinctness ledger $K$ and the additive route through $N,A,B,S,L,H,C,P,M$ before it can see the bridge as a downstream obstruction. In particular, the consumer cannot bypass the ledger by identifying the $\NatUp$ unary source classifier with the $\AxisNatUp$ zero-spine source classifier.
\end{theorem}
\begin{proof}
Project the accepted packet. The carrier and kernel-distinct obligations expose $K$ as the row that separates the unary and zero-spine source classifiers.

Use the ledger policy and ledger exactness. They make $K$ and $L$ mandatory for downstream reads and exclude host equality, quotient identification, or a second kernel carrier as substitute evidence.

Apply additive consumer exactness, kernel-axis composition, and the downstream seal. These results route $\AxisZeckendorfCannotClaimUp$ consumers through the additive bridge packet before the obstruction row is visible.

Therefore the bridge can be consumed only after the kernel-distinctness ledger and additive route have been read from the same displayed packet.
\end{proof}

\begin{theorem}[UnaryDirectionBridge root-unblock readback package]
\label{thm:unary-direction-bridge-root-unblock-readback-package}
The accepted $\UnaryDirectionBridgeUp$ packet $U=(N,A,B,K,S,L,H,C,P,M)$ forms a root-unblock readback package for downstream $\AddUp$, $\AxisAddUp$, and $\AxisZeckendorfCannotClaimUp$ consumers. The package consists exactly of carrier admission, kernel-distinct classifier rows, ledger exactness, the standard-boundary consumer factorization of \autoref{thm:unary-direction-bridge-standard-boundary-consumer-factorization}, the AxisZeckendorf ledger gate of \autoref{thm:unary-direction-bridge-axiszeckendorf-ledger-gate}, scoped NameCert transport, and the downstream seal.
\end{theorem}
\begin{proof}
Begin with carrier admission. It fixes the readback packet as the ten displayed rows $N,A,B,K,S,L,H,C,P,M$.

Add the kernel-distinct obligations and ledger exactness. These make the source classifiers separate at the kernel row and make the ledger the public witness for that separation.

Use standard-boundary consumer factorization to bind $\AddUp/\AxisAddUp$ consumers to the same packet. Use the AxisZeckendorf ledger gate to ensure that obstruction-facing consumers read the ledger and additive route before the bridge can be consumed.

Finally combine scoped NameCert transport with the downstream seal. The assembled package exports the bridge as the displayed finite readback surface and does not export carrier equivalence transport, host natural-number equality, or quotient identification.
\end{proof}

\closureat{UnaryDirectionBridgeUp}{seedStr}
\closureat{UnaryDirectionBridgeUp}{obligationStr}
\closureat{UnaryDirectionBridgeUp}{scopedStr}

\begin{closurestatus}{\UnaryDirectionBridgeUp}
  \constructivestory{A $\UnaryDirectionBridgeUp$ packet is generated by a $\NatUp$ unary source row, an $\AxisNatUp$ zero-spine source row, the displayed bridge object, kernel-distinctness witness, standard-boundary row, ledger policy, $\hsame$ transports, $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The scoped surface binds the carrier, obligation closure, scoped source rows for $\NatUp$, $\AxisNatUp$, $\AddUp$, $\AxisAddUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, the additive route scope, and the local scoped NameCert package for the unary-direction bridge packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not identify $\NatUp$ and $\AxisNatUp$ inside the kernel, close the full standard-model isomorphism, or provide Lean verification for the NameCert packet.}
  \upgradepath{Public closure requires a verified public-object surface for the unary-direction bridge package and its downstream additive consumers.}
\end{closurestatus}
