\chapter{A Concrete Naming Certificate for \(\VecSpaceUp\)}
\label{ch:concrete-instances-vecspace-namecert}

The vector space interface \(\VecSpaceUp\) is the specialization of \autoref{ch:concrete-instances-module-namecert} to the case where the scalar ring satisfies \autoref{ch:concrete-instances-field-namecert}. No new fields are required beyond the module ones; the change is the strengthened scalar source. The \(n\)-fold rational tuple space (an iterated product over \(\RatUp\)) is the canonical concrete instance.

\section{Carrier definition}

\begin{definition}[VecSpace carrier]
\label{def:vecspace-carrier}
Use a module setup whose scalar source is a certified field.
\end{definition}

\section{Concrete singleton history vector space instance}
\label{sec:vecspace-concrete-singleton-history-instance}

\begin{definition}[Concrete singleton empty-history vector space instance]
\label{def:singleton-empty-history-vecspace-instance}
Let the scalar carrier and vector carrier both be the singleton history source
$A_{\emp}$ of Definition~\ref{def:singleton-empty-history-module-instance}.
Define the shared classifier
$$
\rho_{\emp}(h,k):=
A_{\emp}(h)\land A_{\emp}(k)\land\hsame(h,k).
$$
Use the scalar addition, scalar negation, scalar multiplication, scalar zero,
scalar one, nonzero predicate, and proof-indexed scalar inverse from
Definition~\ref{def:singleton-empty-history-field-schema-instance}. Use the
vector addition, vector negation, vector zero, and scalar action from
Definition~\ref{def:singleton-empty-history-module-instance}, with
$$
\mathsf{smul}(r,m):=\emp.
$$
The certificate fit has ten fields:
\begin{enumerate}
  \item Traditional target: the one-element vector space over the one-element
  proof-indexed field.
  \item BEDC source: $\mathsf{BHist}$.
  \item Carrier choice: $A_{\emp}$ for both scalars and vectors.
  \item Classifier choice: $\rho_{\emp}$.
  \item Stability obligations: the singleton field laws together with the
  singleton module laws and the vacuous nonzero-indexed scalar inverse
  reasoning.
  \item Ledger: singleton scalar, vector, and action provenance.
  \item Core theorem list: Theorem~\ref{thm:singleton-empty-history-vecspace-laws}.
  \item Exactness predicate: singleton endpoint classification.
  \item Standard bridge: the terminal one-object vector space.
  \item Status: $\mathsf{ProofTarget}$.
\end{enumerate}
\end{definition}

\begin{theorem}[Singleton empty-history vector space laws]
\label{thm:singleton-empty-history-vecspace-laws}
The tuple
$$
(A_{\emp},\rho_{\emp},\mathsf{add},0,\mathsf{neg},
\mathsf{mul},1,\mathsf{smul},\mathsf{NonZero}_{\bot},\mathsf{inv})
$$
satisfies the $\VecSpaceUp$ schema over the concrete $\mathsf{BHist}$
singleton carrier:
scalar $\FieldUp$ laws, additive module laws, scalar-action closure,
scalar-action congruence, scalar associativity, distributivity over vector
addition, distributivity over scalar addition, scalar unit law, and
inverse-enabled scalar reasoning for explicitly nonzero scalars.
\end{theorem}
\begin{proof}
The module part is exactly the singleton empty-history module package of
Theorem~\ref{thm:module-singleton-scalar-action-laws}. It supplies closure,
the additive abelian-group laws, scalar-action congruence, scalar
associativity, both distributivity laws, and the scalar unit law for the same
$A_{\emp}$ carrier and $\rho_{\emp}$ classifier.

The scalar field part is exactly the singleton empty-history field schema of
Theorem~\ref{thm:singleton-empty-history-field-schema-laws}. It supplies the
scalar commutative-ring laws together with the proof-indexed nonzero transport,
inverse closure, inverse congruence, and inverse laws. The certificate
packaging is the one recorded in
Theorem~\ref{thm:singleton-empty-history-field-schema-certificate}.

It remains only to check that the two packages share the displayed scalar
source. Both use the constant empty-history scalar operations on
$A_{\emp}$, the same classifier $\rho_{\emp}$, and the same scalar unit. Hence
their scalar ring fragments coincide as the scalar side of the vector-space
schema.

For scalar congruence and each scalar-action law, every endpoint reduces to
$\emp$. The required classifier witness is assembled from
$A_{\emp}(\emp)$ and $\hsame(\emp,\emp)$.

For inverse-enabled scalar reasoning, every such clause begins with a witness
$p:\mathsf{NonZero}_{\bot}(h)$. Theorem~\ref{thm:field-singleton-nonzero-absurd}
identifies the singleton nonzero predicate as contradictory at the only
possible endpoint. Since
$\mathsf{NonZero}_{\bot}(h)$ is $\bot$, eliminating $p$ closes the clause over
the empty witness domain. No classical nonzero test or further endpoint datum
is needed.
\end{proof}
\leanchecked{BEDC.Derived.VecSpaceUp.singleton\_empty\_history\_vecspace\_laws}

\begin{theorem}[Singleton empty-history vector space endpoint collapse]
\label{thm:singleton-empty-history-vecspace-endpoint-collapse}
With the notation of
Definition~\ref{def:singleton-empty-history-vecspace-instance}, let
$r,s:\mathsf{BHist}$ be scalar endpoints and $m,n:\mathsf{BHist}$ be vector
endpoints carried by $A_{\emp}$. Then the concrete singleton tuple has the
following endpoint classifications:
\begin{enumerate}
  \item For any $x,y:\mathsf{BHist}$, if $A_{\emp}(x)$ and $A_{\emp}(y)$,
  then $\rho_{\emp}(x,y)$.
  \item $A_{\emp}(\mathsf{smul}(r,m))$ and
  $\rho_{\emp}(\mathsf{smul}(r,m),\emp)$.
  \item The vector endpoints $\mathsf{add}(m,n)$, $\mathsf{neg}(m)$, and
  the vector zero are all carried by $A_{\emp}$ and classified with $\emp$.
  \item The scalar endpoints $0$, $1$, and $\mathsf{mul}(r,s)$ are all
  carried by $A_{\emp}$ and classified with $\emp$.
  \item For any witness $p:\mathsf{NonZero}_{\bot}(r)$, the inverse endpoint
  $\mathsf{inv}(r,p)$ is carried by $A_{\emp}$ and classified with $\emp$.
\end{enumerate}
\end{theorem}
\begin{proof}
Apply Theorem~\ref{thm:module-singleton-scalar-action-laws} to the carried
scalar and vector inputs. Its closure and congruence clauses cover the
additive vector endpoints and the scalar-action endpoint for the same
$A_{\emp}$ carrier and $\rho_{\emp}$ classifier.

Apply Theorem~\ref{thm:singleton-empty-history-field-schema-laws} to the
scalar side. It supplies closure for scalar zero, scalar one, scalar
multiplication, and the proof-indexed inverse clauses over the same singleton
source.

Unfold the concrete operations in
Definition~\ref{def:singleton-empty-history-vecspace-instance}. The displayed
scalar action is definitionally $\emp$, and the imported singleton vector and
scalar operations reduce to the singleton endpoint as recorded by the module
and field law packages.

For any two carried endpoints $x$ and $y$, unfold
$\rho_{\emp}(x,y)$. The carrier components are the two assumptions
$A_{\emp}(x)$ and $A_{\emp}(y)$, and the singleton endpoint witnesses for
$x$ and $y$ compose to give the required $\hsame(x,y)$ component.

Each operation endpoint already reduces to $\emp$ or is closed by the cited
law package at the singleton endpoint. Pair the relevant
$A_{\emp}(\emp)$ witness with reflexivity $\hsame(\emp,\emp)$ to obtain the
displayed classifier witness against $\emp$.

For the inverse-indexed clause, assume
$p:\mathsf{NonZero}_{\bot}(r)$. Since $A_{\emp}(r)$ holds,
Theorem~\ref{thm:field-singleton-nonzero-absurd} eliminates the nonzero
witness at the only possible endpoint. From that contradiction, the carried
and classified inverse conclusion follows over the empty witness domain.
\end{proof}

\leanchecked{BEDC.Derived.VecSpaceUp.VecSpaceSingletonEmptyHistory\_laws}

\begin{theorem}[VecSpace singleton scalar action inverse law]
\label{thm:vecspace-singleton-scalar-action-inverse-law}
For the concrete singleton $\VecSpaceUp$ instance, let
$p:\mathsf{FieldSingletonNonZero}(r)$ be an explicit scalar inverse witness and
let $m:\mathsf{BHist}$ satisfy $A_{\emp}(m)$. Then
$\mathsf{smul}(r,m)$ is classified with $\emp$, and applying the proof-indexed
inverse scalar to that result is classified with the original vector endpoint
$m$.
\end{theorem}
\begin{proof}
The scalar action is the constant empty-history action, so
$\mathsf{smul}(r,m)\hsame\emp$ by reflexivity. Applying the inverse scalar
again has the same empty-history endpoint. The first classifier package uses
$A_{\emp}(\emp)$ on both sides. The second uses $A_{\emp}(\emp)$ on the action
side and the assumed singleton-carrier witness for $m$ on the readback side;
symmetry of that witness gives $\emp\hsame m$.
\end{proof}
\leanchecked{BEDC.Derived.VecSpaceUp.VecSpaceSingleton\_scalar\_action\_inverse\_law}

The $\VecSpaceUp$ schema is instantiated by this concrete $\mathsf{BHist}$
carrier and scalar action, so Lean formalization can target BHist-anchored
vector-space laws in $\mathsf{BEDC.Derived.VecSpaceUp}$.

\begin{theorem}[Singleton empty-history vector space semantic certificate]
\label{thm:singleton-empty-history-vecspace-semantic-certificate}
The tuple from
Definition~\ref{def:singleton-empty-history-vecspace-instance}, together with
the law package of Theorem~\ref{thm:singleton-empty-history-vecspace-laws},
supplies the concrete paper-side semantic certificate for the terminal
$\VecSpaceUp$ over the singleton $\FieldUp$ and singleton $\ModuleUp$ carriers.
Its certificate target is the following ten-field template:
\begin{enumerate}
  \item Traditional target: the terminal vector space.
  \item BEDC source: $\mathsf{BHist}$.
  \item Carrier: $A_{\emp}$.
  \item Classifier: $\rho_{\emp}$.
  \item Stability: the singleton field and module law packages together with
  nonzero-witness elimination.
  \item Ledger: singleton scalar, vector, and action provenance.
  \item Core theorem:
  Theorem~\ref{thm:singleton-empty-history-vecspace-laws}.
  \item Exactness: singleton endpoint classification.
  \item Standard bridge: the terminal vector space.
  \item Status: $\mathsf{ProofTarget}$.
\end{enumerate}
\end{theorem}
\begin{proof}
The scalar component is supplied by
Theorem~\ref{thm:singleton-empty-history-field-schema-laws}, and its
paper-side packaging is recorded by
Theorem~\ref{thm:singleton-empty-history-field-schema-certificate}. These give
the singleton $\FieldUp$ source, the shared $A_{\emp}$ carrier, and the
classifier $\rho_{\emp}$ used by the displayed tuple.

The vector component is supplied by
Theorem~\ref{thm:module-singleton-scalar-action-laws}. It gives the singleton
$\ModuleUp$ additive laws, scalar-action closure, scalar-action congruence,
associativity, both distributivity laws, and the scalar unit law over the same
empty-history endpoint.

The remaining inverse-indexed clauses are vacuous in the singleton field
source. By Theorem~\ref{thm:field-singleton-nonzero-absurd}, any witness of
$\mathsf{NonZero}_{\bot}(h)$ is impossible at the only endpoint, so each
nonzero-indexed scalar obligation is closed by elimination.

Thus the tuple already carries the scalar, vector, classifier, ledger,
exactness, bridge, and status data listed in the ten-field template, with
Theorem~\ref{thm:singleton-empty-history-vecspace-laws} as its core theorem.
\end{proof}
\leanchecked{BEDC.Derived.VecSpaceUp.VecSpaceSingleton\_semanticNameCert}

\section{The certificate}

\begin{definition}[VecSpace source specification]
\label{def:vecspace-source-specification}
The source is \(\FieldUp(F)\) together with a certified \(F\)-module carrier.
\end{definition}

\begin{definition}[VecSpace pattern specification]
\label{def:vecspace-pattern-specification}
The pattern is exactly module expression formation over field scalars.
\end{definition}

\begin{definition}[VecSpace classifier specification]
\label{def:vecspace-classifier-specification}
The classifier is the module carrier classifier, with scalar congruence inherited from the field.
\end{definition}

\begin{definition}[VecSpace stability certificate]
\label{def:vecspace-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item all module stability fields
  \item all scalar field stability fields
  \item inverse-enabled scalar reasoning for apart-from-zero scalars
\end{enumerate}
\end{definition}

\begin{definition}[VecSpace ledger policy]
\label{def:vecspace-ledger-policy}
Record module ledgers plus the field ledger for scalar operations.
\end{definition}

\begin{definition}[\(\VecSpaceUp\) certificate obligations]
\label{def:vecspace-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\VecSpaceUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\VecSpaceUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:vecspace-zero-axiom-note}
Inverses use field apartness witnesses rather than LEM-based nonzero tests.
\end{remark}
