\chapter{A Concrete Naming Certificate for $\ModularFormUp$}
\label{ch:concrete-instances-modularform-namecert}

The modular-form interface $\ModularFormUp$ packages a holomorphic function on the upper half plane invariant under a congruence subgroup of $SL_2(\mathbb{Z})$ up to a fixed weight factor. It depends on $\NameCert_{\HolomorphicUp}$ (\autoref{ch:concrete-instances-holomorphic-namecert}) and $\NameCert_{\AutomorphicUp}$ (\autoref{ch:concrete-instances-automorphic-namecert}).

\section{Carrier definition}
\label{sec:modularform-carrier}

\begin{definition}[Modular-form q-expansion carrier]
\label{def:modularform-bhist-qexpansion-carrier}
Fix a $\NameCert_{\HolomorphicUp}$ source row and a $\NameCert_{\AutomorphicUp}$ source row for the same displayed weight and congruence-subgroup context. A $\ModularFormUp$ carrier row is the finite $\mathsf{BHist}$ ledger consisting of the holomorphic source answer row, the automorphic transformation answer row, a finite q-expansion coefficient observation row, and the $\Cont$ witnesses that place the coefficient observations under both sources.

The carrier records finite q-expansion and transformation data only. It does not assert analytic continuation, dimension formulas, Hecke operators, cusp expansions at every cusp, or a host space of modular forms.
\end{definition}
\leandef{BEDC.Derived.ModularFormUp.ModularFormQExpansionCarrier}

\begin{definition}[Modular-form congruence classifier]
\label{def:modularform-congruence-classifier}
Two rows of \autoref{def:modularform-bhist-qexpansion-carrier} are classified as the same $\ModularFormUp$ observation exactly when their holomorphic source rows are transported by $\NameCert_{\HolomorphicUp}$, their automorphic transformation rows are transported by $\NameCert_{\AutomorphicUp}$, and their visible finite q-expansion coefficient packages are matched by $\hsame$, $\Cont$, and $\Pkg$.

The classifier is generated by source transport, finite coefficient package transport, and congruence-subgroup transformation transport. It contains no generator for analytic continuation, dimension counting, or Hecke stability.
\end{definition}

\section{The certificate}
\label{sec:modularform-certificate}

\begin{theorem}[Modular-form holomorphic source scope]
\label{thm:modularform-holomorphic-source-scope}
Every $\ModularFormUp$ carrier row contains one $\NameCert_{\HolomorphicUp}$ source row, one $\NameCert_{\AutomorphicUp}$ transformation source row, and finite q-expansion coefficient answer histories attached to those sources by $\Cont$ and $\Pkg$ witnesses.
\end{theorem}
\leanchecked{BEDC.Derived.ModularFormUp.ModularFormQExpansionCarrier\_holomorphic\_source\_scope}
\begin{proof}
Invert \autoref{def:modularform-bhist-qexpansion-carrier}. The holomorphic source and automorphic source are explicit fields, while the coefficient data are finite answer rows recorded under those fields.

The classifier of \autoref{def:modularform-congruence-classifier} can change representatives only through the two source certificates and the displayed finite coefficient package witnesses. Thus the source scope is exactly the holomorphic row, the automorphic row, and the finite q-expansion ledger.
\end{proof}

\begin{theorem}[Modular-form automorphic transport stability]
\label{thm:modularform-automorphic-transport-stability}
If two $\ModularFormUp$ rows are classified by \autoref{def:modularform-congruence-classifier}, then transporting the automorphic transformation row through $\NameCert_{\AutomorphicUp}$ and transporting any visible q-expansion coefficient row through $\hsame$, $\Cont$, or $\Pkg$ preserves the classified carrier row.
\end{theorem}
\leanchecked{BEDC.Derived.ModularFormUp.ModularFormAutomorphicTransport\_stability}
\begin{proof}
Transport the automorphic source first. The $\NameCert_{\AutomorphicUp}$ classifier supplies the new transformation answer row, and the carrier retains the same displayed weight and congruence-subgroup context.

For the coefficient row, use the stored $\hsame$ endpoint comparison and the $\Pkg$ package comparison, with $\Cont$ placing the transported coefficient back under the holomorphic and automorphic source rows. Since the coefficient list is finite, concatenating these transports yields a classifier witness for the whole row.
\end{proof}

\begin{theorem}[Modular-form NameCert obligation surface]
\label{thm:modularform-namecert-obligation-surface}
The $\ModularFormUp$ chapter exports a NameCert obligation surface consisting of the finite q-expansion carrier, the congruence classifier, the holomorphic and automorphic source rows, and ledger exactness for the displayed coefficient and transformation observations.
\end{theorem}
\leanchecked{BEDC.Derived.ModularFormUp.ModularFormQExpansionCarrier\_semantic\_name\_certificate}
\begin{proof}
Assemble the surface from a carried row and a classifier witness. The carried row supplies the holomorphic source, the automorphic source, and the finite q-expansion observations; the classifier supplies only source transport, coefficient transport, and transformation transport.

Ledger exactness follows by inverting those constructors. Every accepted field is a source row, a coefficient answer, a transformation answer, or a named $\hsame$, $\Cont$, or $\Pkg$ witness. Therefore the obligation surface stays within finite BEDC data and makes no analytic-continuation, dimension-formula, or Hecke-theoretic claim.
\end{proof}
\leanchecked{BEDC.Derived.ModularFormUp.ModularFormQExpansionCarrier\_namecert\_obligation\_surface}

\closureat{ModularFormUp}{seedStr}[BEDC.Derived.ModularFormUp.ModularFormAutomorphicTransport\_stability]
\closureat{ModularFormUp}{obligationStr}[BEDC.Derived.ModularFormUp.ModularFormQExpansionCarrier\_namecert\_obligation\_surface]
\closureat{ModularFormUp}{scopedStr}[BEDC.Derived.ModularFormUp.ModularFormAutomorphicTransport\_stability]
\closureat{ModularFormUp}{publicStr}[BEDC.Derived.ModularFormUp.ModularFormQExpansionCarrier\_namecert\_obligation\_surface]

\begin{closurestatus}{\ModularFormUp}
  \theoryclosure{\publicClosure}
  \scopeclosed{The obligation surface records the finite q-expansion carrier of \autoref{def:modularform-bhist-qexpansion-carrier}, the congruence classifier of \autoref{def:modularform-congruence-classifier}, the $\HolomorphicUp$ and $\AutomorphicUp$ source rows, and the $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\Pkg$ rows exposed by \autoref{thm:modularform-namecert-obligation-surface}.}
  \constructivestory{A modular-form packet consumes one $\HolomorphicUp$ source row and one $\AutomorphicUp$ source row over the same displayed weight and congruence-subgroup context, then attaches a finite q-expansion coefficient ledger through $\Cont$, $\Pkg$, and $\hsame$ rows.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.ModularFormUp.ModularFormAutomorphicTransport\_stability}
  \bridgestatus{none}
  \notclaimed{This obligation boundary does not close analytic continuation, dimension formulas, Hecke operators, all-cusp expansions, or a host modular-form space.}
  \upgradepath{The next paper-grade step is a bridge boundary for the public q-expansion and automorphic-source package.}
\end{closurestatus}

\begin{theorem}[Modular-form empty coefficient classifier]
\label{thm:modularform-empty-coefficient-classifier}
Let $R$ and $R'$ be two $\ModularFormUp$ carrier rows of \autoref{def:modularform-bhist-qexpansion-carrier} over the same displayed weight and congruence-subgroup context. Suppose that both rows use the same $\NameCert_{\HolomorphicUp}$ source row $H$, the same $\NameCert_{\AutomorphicUp}$ source row $A$, and the visible q-expansion coefficient observation row is $\emp$ in both carriers. Then $R$ and $R'$ are classified as the same $\ModularFormUp$ observation by the modular-form congruence classifier of \autoref{def:modularform-congruence-classifier}.
\end{theorem}
\leanchecked{BEDC.Derived.ModularFormUp.ModularFormQExpansionCarrier\_empty\_coefficient\_classifier}
\begin{proof}
Unpack the two carrier rows by \autoref{def:modularform-bhist-qexpansion-carrier}. Their source part is the common pair $(H,A)$, so the holomorphic source component is transported by the reflexive classifier row of $\NameCert_{\HolomorphicUp}$ and the automorphic component is transported by the reflexive classifier row of $\NameCert_{\AutomorphicUp}$. The displayed weight and congruence-subgroup context is also common, so no context replacement is required.

It remains only to compare the finite q-expansion coefficient ledger. Both visible coefficient rows are $\emp$. The empty history supplies the endpoint comparison $\emp\hsame\emp$, and the right-unit continuation rows place the empty coefficient observation under the already shared holomorphic and automorphic source rows:
$$
\Cont(H,\emp,H)
\qquad\text{and}\qquad
\Cont(A,\emp,A).
$$
The finite coefficient package therefore has no nonempty coefficient entry to match. Its package comparison is the empty package comparison, with the displayed $\hsame$ and $\Cont$ witnesses as its whole ledger.

The generators listed in \autoref{def:modularform-congruence-classifier} are exactly source transport, finite coefficient package transport, and congruence-subgroup transformation transport. Applying the two reflexive source transports, the empty coefficient package comparison, and the shared automorphic transformation context gives a classifier witness from $R$ to $R'$. Since no generator for analytic continuation, dimension counting, Hecke stability, or all-cusp data participates in that classifier, the conclusion is confined to the two empty-coefficient carrier rows.
\end{proof}
