\chapter{A Concrete Naming Certificate for $\AuthorizedRecursorUp$}
\label{ch:concrete-instances-authorizedrecursor-namecert}
\origin{human}

The $\AuthorizedRecursorUp$ interface records legal eliminator calls as finite naming packets. Its role is not to add a recursor beyond CIC. It names the BEDC surface already present when the kernel accepts an inductive constructor signature, checks a motive, checks one branch package for that signature, and emits an output whose computation cannot escape the displayed constructor spine.

The recursor packet consumes the accepted constructor-signature boundary of \autoref{ch:concrete-instances-kernelinductiveacceptance-namecert}, where constructor signature acceptance supplies $\Sigma$, and exports its generated output through the generator seal of \autoref{ch:concrete-instances-generatorinductionseal-namecert} or the ledger of \autoref{ch:concrete-instances-inductionclosureledger-namecert}, where generator-induction sealing supplies the downstream non-escape route for $O$.

\begin{definition}[AuthorizedRecursor carrier]
\label{def:authorized-recursor-carrier}
An $\AuthorizedRecursorUp$ carrier is a finite $\BHist$ packet
$$
R=(I,\Sigma,M,B,O,A,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $I$ is the inductive-family name whose kernel-accepted constructor signature is being consumed;
\item $\Sigma$ is the finite constructor-signature row listing the accepted constructors and their recursive argument positions;
\item $M$ is the motive row checked over the closed carrier generated by $\Sigma$;
\item $B$ is the branch-package row, with one displayed branch for each constructor in $\Sigma$;
\item $O$ is the output row produced by the legal eliminator call over the selected input object;
\item $A$ is the authorization ledger stating that the recursor call uses exactly the accepted signature, motive, branches, and structural recursive subcalls;
\item $H$ stores displayed $\hsame$ transports for the signature, motive, branch package, output row, authorization ledger, and local naming row;
\item $C$ stores the finite $\Cont$ routes by which consumers read signature rows, motive rows, branch rows, output rows, and rejected non-structural attempts;
\item $P$ is the $\Pkg$ provenance over the inductive declaration, constructor signature, motive, branch package, output row, $\hsame$ transports, $\Cont$ routes, and audit ledger;
\item $N$ is the local $\NameCert_{\AuthorizedRecursorUp}$ row.
\end{enumerate}
The carrier exports only these displayed rows. It contains no extra induction principle, no branch outside $\Sigma$, no negative self-use hidden behind the motive, and no recursive call whose descent is not recorded in $A$.
\end{definition}

\begin{theorem}[AuthorizedRecursor NameCert obligations]
\label{thm:authorized-recursor-namecert-obligations}
The local $\NameCert_{\AuthorizedRecursorUp}$ surface for \autoref{def:authorized-recursor-carrier} consists of five finite obligations: carrier admission for $R$; constructor-signature exactness for $\Sigma$; motive-and-branch coverage for $M$ and $B$; authorization-ledger exactness for $A$; and non-escape of negative self-use, missing branches, unrecorded recursion, quotient equality, selected witnesses, and ambient classical principles.
\end{theorem}
\begin{proof}
Carrier admission is projection of the displayed packet $R$. The inductive name, signature row, motive row, branch package, output row, authorization ledger, transports, routes, provenance, and local certificate are all explicit coordinates.

Signature exactness and coverage are read from $\Sigma$, $M$, and $B$. Since $B$ has one branch row for each constructor row in $\Sigma$, every legal eliminator case is paid for by a visible branch and no additional branch is exported.

The authorization and boundary clauses are read from $A$ and $P$. A recursive subcall is admitted only when $A$ records its structural descent through the constructor spine; every missing branch, negative self-use, unrecorded recursion, quotient equality, selected witness, or classical principle has no carrier coordinate and is therefore recorded only as a boundary attempt.
\end{proof}

\begin{theorem}[AuthorizedRecursor generator ledger exactness]
\label{thm:authorized-recursor-generator-ledger-exactness}
Every consumer read of an accepted $\AuthorizedRecursorUp$ packet factors through the displayed rows $I,\Sigma,M,B,O,A,H,C,P,N$. The generator ledger is exact: a read of the recursor output $O$ determines the constructor signature row $\Sigma$, the motive row $M$, the branch-package row $B$, and the authorization row $A$ used to produce it, and no consumer can replace them by a different hidden eliminator call.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:authorized-recursor-carrier}. The output row $O$ is stored together with the signature, motive, branch package, and authorization ledger that generated it.

Transport through $H$ preserves those same rows, and continuation through $C$ exposes them as the only legal consumer routes. Thus a consumer that reads $O$ also reads the finite provenance of the eliminator call.

If a consumer asks for a different signature, motive, branch package, or recursive-call ledger, the packet has no coordinate that can supply it. The request is outside the displayed route and cannot be exported as a generated recursor output.
\end{proof}

\begin{theorem}[AuthorizedRecursor non-escape boundary]
\label{thm:authorized-recursor-non-escape-boundary}
An accepted $\AuthorizedRecursorUp$ packet does not export any object obtained from a constructor outside $\Sigma$, a branch not listed in $B$, a motive not named by $M$, a recursive call not justified by $A$, or an external principle such as quotient soundness, propositional extensionality, choice, or ambient classical completeness.
\end{theorem}
\begin{proof}
The constructor boundary is finite. Every admissible constructor read is one of the rows listed in $\Sigma$, and every admissible branch read is the corresponding row in $B$.

The motive and recursion boundaries are also finite. The motive row $M$ is the only motive exported by the packet, and the authorization ledger $A$ is the only place where recursive subcalls can be justified.

The provenance row $P$ records the absence of external principles. Since none of quotient soundness, propositional extensionality, choice, or ambient completeness is a coordinate of $R$, no downstream route can receive such a principle from this certificate.
\end{proof}

\begin{theorem}[AuthorizedRecursor downstream handoff]
\label{thm:authorized-recursor-downstream-handoff}
Every downstream BEDC consumer of an $\AuthorizedRecursorUp$ output receives a finite handoff packet consisting of the output row $O$, its constructor-signature row $\Sigma$, motive row $M$, branch-package row $B$, authorization ledger $A$, transport row $H$, continuation route $C$, package row $P$, and local naming row $N$. The handoff is sufficient for later TasteGate or kernel-recursion certificates to inspect the legal eliminator call without reopening the host declaration.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedRecursorUp.AuthorizedRecursorTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the handoff rows from the carrier $R$. The output row is not transmitted alone; it is transmitted with the exact signature, motive, branch, authorization, transport, route, package, and naming rows that make the eliminator call visible.

TasteGate-style consumers inspect the same finite rows to decide whether the call stays inside the accepted constructor signature. Kernel-recursion consumers inspect the authorization ledger to replay the structural descent boundary.

No downstream consumer needs a fresh host-side induction principle. The handoff carries the already named BEDC certificate surface, so later packets can consume the recursor output through finite NameCert rows.
\end{proof}

\closureat{AuthorizedRecursorUp}{seedStr}

\begin{closurestatus}{\AuthorizedRecursorUp}
  \constructivestory{An $\AuthorizedRecursorUp$ packet is generated from an inductive-family name, accepted constructor-signature row, checked motive row, branch package, output row, authorization ledger, displayed $\hsame$ transports, finite $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the carrier, five NameCert obligations, generator-ledger exactness, non-escape boundary, and downstream handoff for legal eliminator calls.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean kernel soundness, all inductive-family positivity checks, all termination checking, TasteGate verification, kernel-recursion bridge checking, or any external classical principle.}
  \upgradepath{Obligation closure requires a checked finite carrier, signature coverage theorem, motive-and-branch ledger theorem, structural recursion ledger theorem, and downstream handoff theorem for the same packet.}
\end{closurestatus}
