\chapter{A Concrete Naming Certificate for $\ClebschGordanUp$}
\label{ch:concrete-instances-clebschgordan-namecert}

The Clebsch-Gordan interface $\ClebschGordanUp$ packages, for a pair of irreducible representations of a compact Lie group, the decomposition of their tensor product into irreducibles together with the explicit coupling coefficients. It depends on $\NameCert_{\LieGroupUp}$ (\autoref{ch:concrete-instances-liegroup-namecert}) and $\NameCert_{\TensorProductUp}$ (\autoref{ch:concrete-instances-tensorproduct-namecert}).

\section{Carrier definition}
\label{sec:clebschgordan-carrier}

\section{The certificate}
\label{sec:clebschgordan-certificate}

\begin{definition}[ClebschGordanUp BHist coupling packet]
\label{def:clebschgordan-bhist-coupling-packet}
A $\ClebschGordanUp$ coupling packet is a finite $\mathsf{BHist}$ tuple
$$
\mathcal{C}=(G,T,R,V_{1},V_{2},\tau,D,\Gamma,\theta,P,\lambda).
$$
The rows $G$, $T$, and $R$ are consumed certificates
$\NameCert_{\LieGroupUp}$, $\NameCert_{\TensorProductUp}$, and
$\NameCert_{\RepresentationRingUp}$. The rows $V_{1}$ and $V_{2}$ are the two
irreducible source-representation histories, each read through $G$ and $R$.
The row $\tau$ is the tensor-product endpoint history for
$V_{1}\otimes V_{2}$ read through $T$.

The finite decomposition ledger $D$ lists irreducible output histories
$W_{j}$ with multiplicity histories $m_{j}$ and representation-ring
summand rows in $R$. The coefficient ledger $\Gamma$ lists the displayed
coupling-coefficient histories $\gamma_{a,b}^{j,q}$ that relate source basis
histories for $V_{1}$ and $V_{2}$ to output basis histories for each
$W_{j}$ and multiplicity slot $q$. The row $\theta$ is the componentwise
$\hsame$ transport datum for $G,T,R,V_{1},V_{2},\tau,D,\Gamma$.

The row $P$ is the $\mathsf{Pkg}$ provenance recording exactly the consumed
LieGroupUp, TensorProductUp, RepresentationRingUp, decomposition, and
coefficient rows. The finite ledger $\lambda$ is the $\Cont$ route containing
only those displayed rows and their endpoint readbacks.
\end{definition}

\begin{theorem}[ClebschGordanUp carrier source obligation]
\label{thm:clebschgordan-carrier-source-obligation}
Every public carrier row of a $\ClebschGordanUp$ coupling packet is one of the
displayed rows of
\autoref{def:clebschgordan-bhist-coupling-packet}. In particular, the two
irreducible source rows are read only through
$\NameCert_{\LieGroupUp}$ and $\NameCert_{\RepresentationRingUp}$, and the
tensor endpoint is read only through $\NameCert_{\TensorProductUp}$ together
with those two source rows.
\end{theorem}
\leanchecked{BEDC.Derived.ClebschGordanUp.ClebschGordanCouplingPacket\_carrier\_source\_obligation}
\begin{proof}
Project an accepted packet to the tuple
$\mathcal{C}=(G,T,R,V_{1},V_{2},\tau,D,\Gamma,\theta,P,\lambda)$. The carrier
definition lists all public rows in that tuple, so no additional carrier row
can be read by a downstream consumer.

The two source rows $V_{1}$ and $V_{2}$ carry their group action through $G$
and their representation-ring membership through $R$. The tensor endpoint
$\tau$ is then the row supplied by $T$ on those same two source histories.

Repacking these projections gives the carrier obligation: source
irreducibles, tensor endpoint, decomposition entries, coefficients,
transport, provenance, and continuation are all $\mathsf{BHist}$ rows of the
same displayed packet.
\end{proof}

\begin{theorem}[ClebschGordanUp classifier transport obligation]
\label{thm:clebschgordan-classifier-transport-obligation}
Let $\mathcal{C}$ and $\mathcal{C}'$ be two
\autoref{def:clebschgordan-bhist-coupling-packet} packets. A public
$\ClebschGordanUp$ classifier row from $\mathcal{C}$ to $\mathcal{C}'$ is the
componentwise $\hsame$ transport of the consumed
$\NameCert_{\LieGroupUp}$, $\NameCert_{\TensorProductUp}$, and
$\NameCert_{\RepresentationRingUp}$ rows, the two irreducible source rows, the
tensor endpoint row, the finite decomposition ledger, the coefficient
histories, the $\mathsf{Pkg}$ provenance row, and the finite $\Cont$ ledger.
\end{theorem}
\leanchecked{BEDC.Derived.ClebschGordanUp.ClebschGordanCouplingPacket\_classifier\_transport\_obligation}
\begin{proof}
Unpack the transport row $\theta$ in the source packet and the corresponding
row $\theta'$ in the target packet. Their displayed fields compare the three
consumed certificates, the two source irreducibles, and the tensor endpoint
by $\hsame$.

The same componentwise comparison transports the decomposition ledger $D$:
each output irreducible history, multiplicity history, and
representation-ring summand row is matched with its transported target row.
The coefficient ledger $\Gamma$ is transported entry by entry over the same
source and output histories.

Finally compare $P$ and $\lambda$ by the displayed provenance and continuation
rows. These projections exhaust the public classifier, so no host equality of
representations, basis vectors, or coefficient arrays is available outside
the packet.
\end{proof}

\begin{theorem}[ClebschGordanUp ledger exactness obligation]
\label{thm:clebschgordan-ledger-exactness-obligation}
The exact ledger of a $\ClebschGordanUp$ coupling packet consists precisely
of the tensor endpoint $\tau$, the finite decomposition ledger $D$, the
coefficient-history ledger $\Gamma$, the componentwise $\hsame$ transport
$\theta$, the provenance packet $P$, and the finite $\Cont$ route $\lambda$.
Every accepted coupling read projects to these rows, and every family of
these rows repacks as the public coupling ledger.
\end{theorem}
\leanchecked{BEDC.Derived.ClebschGordanUp.ClebschGordanCouplingPacket\_ledger\_exactness\_obligation}
\begin{proof}
For the projection direction, take an accepted coupling read and inspect its
public packet. The tensor product endpoint is the row $\tau$, the finite list
of irreducible summands and multiplicities is $D$, and the coupling
coefficients are the histories in $\Gamma$.

The transport, provenance, and continuation fields are then the displayed
rows $\theta$, $P$, and $\lambda$. Because the packet definition contains no
other public field, the projection cannot expose a host decomposition theorem
or an unrecorded coefficient table.

For the reverse direction, start with rows of exactly these six forms over
the same consumed $G,T,R,V_{1},V_{2}$ source data. Insert them into the tuple
of \autoref{def:clebschgordan-bhist-coupling-packet}. The resulting tuple is
the public ledger, so exactness is projection followed by this repacking.
\end{proof}

\begin{theorem}[ClebschGordanUp source NameCert boundary]
\label{thm:clebschgordan-source-namecert-boundary}
The source boundary of a $\ClebschGordanUp$ coupling packet is exactly the
triple of consumed certificates
$\NameCert_{\LieGroupUp}$, $\NameCert_{\TensorProductUp}$, and
$\NameCert_{\RepresentationRingUp}$ together with the two irreducible source
rows and their tensor endpoint. It does not export a separate compact-group
carrier, representation category, basis convention, or ambient Hilbert-space
object.
\end{theorem}
\begin{proof}
Project the dependency rows $G,T,R$ from the packet. The irreducible source
histories $V_{1}$ and $V_{2}$ are scoped by $G$ and $R$, while the tensor row
$\tau$ is scoped by $T$ and those same two source histories.

The decomposition ledger and coefficient histories are downstream rows over
this source boundary. They refer back to $G,T,R,V_{1},V_{2},\tau$ through
$\mathsf{Pkg}$ provenance and through the displayed $\Cont$ route.

Since no other source row occurs in the tuple, any consumer requesting a
Clebsch-Gordan source can receive only those certificates and histories.
Thus the boundary is a BEDC source boundary, not a hidden representation
theory environment.
\end{proof}

\begin{theorem}[ClebschGordanUp consumer readback boundary]
\label{thm:clebschgordan-consumer-readback-boundary}
Every downstream consumer of a $\ClebschGordanUp$ coupling packet reads only
the two irreducible source histories, the tensor endpoint, the finite
decomposition ledger, the coefficient histories, the componentwise $\hsame$
transport rows, the $\mathsf{Pkg}$ provenance, and the finite $\Cont$
readback route of
\autoref{def:clebschgordan-bhist-coupling-packet}. If two packets agree on
those rows by the public classifier, then every such consumer has the same
readback.
\end{theorem}
\begin{proof}
Let a consumer be invariant under the displayed rows named in the statement.
Project both packets to their source histories, tensor endpoint,
decomposition ledger, coefficient histories, transport rows, provenance, and
continuation route.

The public classifier supplies componentwise $\hsame$ comparisons for those
projections. The consumer therefore sees the same source inputs, the same
tensor endpoint, the same finite decomposition entries, and the same
coefficient histories after transport.

By the ledger exactness obligation of
\autoref{thm:clebschgordan-ledger-exactness-obligation}, there is no further
public row that could affect the consumer. Repacking the transported
projections gives identical readback at the consumer boundary.
\end{proof}

\begin{theorem}[ClebschGordanUp coefficient slot determinacy]
\label{thm:clebschgordan-coefficient-slot-determinacy}
Let two accepted reads of coefficient histories in the coefficient ledger
$\Gamma$ of a $\ClebschGordanUp$ coupling packet have the same transported
source rows $V_{1}$ and $V_{2}$, the same tensor endpoint $\tau$, the same
output irreducible row $W_{j}$, the same multiplicity history $m_{j}$, and
the same source and output basis-index histories. Then the public classifier
identifies the two coefficient rows by the componentwise $\hsame$ transport
field of the coupling packet of
\autoref{def:clebschgordan-bhist-coupling-packet}.

Equivalently, a displayed coefficient history accepted in $\Gamma$ belongs to
a unique public slot determined by
$(V_{1},V_{2},\tau,W_{j},m_{j})$ together with its basis-index histories; no
second public coefficient table can be read at that same slot.
\end{theorem}
\begin{proof}
Project the two accepted coefficient reads through
\autoref{def:clebschgordan-bhist-coupling-packet}. Each read is a row of the
same displayed coefficient ledger $\Gamma$, so its source rows, tensor
endpoint, output row, multiplicity row, and basis-index histories are among
the packet fields.

Use the classifier transport obligation of
\autoref{thm:clebschgordan-classifier-transport-obligation}. Under the shared
slot hypotheses, the public classifier compares the two coefficient rows by
the componentwise $\hsame$ entry assigned to $\Gamma$ in the transport row
$\theta$.

It remains to exclude a second public coefficient source for that slot. Apply
the ledger exactness obligation of
\autoref{thm:clebschgordan-ledger-exactness-obligation}: every accepted
coefficient read is projected from $\Gamma$, and the packet has no additional
coefficient table. Thus the transported $\Gamma$ entry is the unique public
coefficient row at the displayed slot.
\end{proof}
