\chapter{A Concrete Naming Certificate for $\KernelAcceptanceAuditWitnessUp$}
\label{ch:concrete-instances-kernelacceptanceauditwitness-namecert}
\origin{human}

The $\KernelAcceptanceAuditWitnessUp$ surface turns a Lean acceptance event into a finite \NameCert{} packet. It does not certify the kernel from inside BEDC. It records the generated candidate, the accepted declaration, the environment ledger, the axiom-query boundary, the build replay route, transport, continuation, provenance, and local naming row that make the acceptance event available to audit consumers.

The witness packet consumes the finite audit-gate rows of \autoref{ch:concrete-instances-auditgateboundary-namecert}: source-token refusal, axiom-purity dependency report, paper-Lean target audit, origin and import conservativity ledger, and GAP boundary rows. The $\KernelAcceptanceAuditWitnessUp$ packet specializes that sibling gate surface to a single Lean acceptance event by adding generated-term, kernel-candidate, accepted-declaration, environment-ledger, query, replay, transport, continuation, provenance, and local $\NameCert{}$ rows.

\begin{definition}[KernelAcceptanceAuditWitness carrier]
\label{def:kernel-acceptance-audit-witness-carrier}
A $\KernelAcceptanceAuditWitnessUp$ carrier is a finite $\BHist$ packet
$$
W=(G,K,A,L,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the generated-term row naming the elaborated proof term, definition body, inductive declaration, or recursor use submitted to the Lean kernel;
\item $K$ is the kernel-candidate row, pairing $G$ with its claimed type, universe data, binder context, recursion account, or constructor signature as applicable;
\item $A$ is the accepted-declaration row, present only when the candidate has been accepted under the current Lean environment;
\item $L$ is the environment-ledger row recording the accepted name and the module position at which the declaration is entered;
\item $Q$ is the axiom-query row naming the transitive dependency query surface used by the strict purity audit;
\item $R$ is the build-replay row naming the project replay that reconstructs the same acceptance event from the Lean sources;
\item $H$ records componentwise $\hsame$ transport for the generated term, candidate, accepted declaration, ledger row, axiom query, replay row, provenance, and local naming row;
\item $C$ records the displayed $\Cont$ routes through which consumers read kernel acceptance, inspect the ledger position, ask the axiom query, and replay the build route;
\item $P$ is the $\Pkg$ provenance over $\BHist$, generated terms, kernel candidates, accepted declarations, environment ledgers, axiom-query rows, build-replay rows, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\KernelAcceptanceAuditWitnessUp}$ row.
\end{enumerate}
The carrier exports no row that proves the Lean kernel correct, no row that turns a weak theorem statement into a stronger paper claim, and no row that hides a dependency outside the axiom-query boundary.
\end{definition}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_terminal\_row\_semantic\_certificate}

\begin{theorem}[KernelAcceptanceAuditWitness NameCert obligations]
\label{thm:kernel-acceptance-audit-witness-namecert-obligations}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the local $\NameCert_{\KernelAcceptanceAuditWitnessUp}$ surface consists exactly of the generated-term row $G$, kernel-candidate row $K$, accepted-declaration row $A$, environment-ledger row $L$, axiom-query row $Q$, build-replay row $R$, componentwise $\hsame$ transport $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local naming row $N$. Any audit consumer of $N$ must read acceptance through the finite packet $W$ and may not replace it by prose confidence, an external certificate, or an unrecorded dependency route.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_namecert\_obligations}
\begin{proof}
Start with the carrier in \autoref{def:kernel-acceptance-audit-witness-carrier}. The displayed coordinates expose the candidate-generating side, the kernel acceptance side, the environment ledger, the axiom-query surface, and the replay route in one finite $\BHist$ packet.

The transport and continuation rows then bind how the packet is read. The $\hsame$ row preserves each named coordinate componentwise, while the $\Cont$ row gives only the displayed routes from generated term to candidate, accepted declaration, ledger entry, axiom query, and replay.

Finally the provenance and local naming rows package the same finite data as a $\NameCert_{\KernelAcceptanceAuditWitnessUp}$ surface. Since no additional coordinate is present, a consumer has no place from which to import prose confidence, an external certificate, or an unrecorded dependency route.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness ledger non-escape]
\label{thm:kernel-acceptance-audit-witness-ledger-non-escape}
For every accepted carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the accepted declaration row $A$ reaches downstream consumers only through the environment-ledger row $L$, the axiom-query row $Q$, the build-replay row $R$, and the local $\NameCert$ row $N$. Thus a checked BEDC marker may consume kernel acceptance as a ledgered declaration with a replayable source and queryable dependency surface, but it cannot read acceptance as a certificate for the kernel's own correctness or for any paper-side claim not stated by the accepted declaration.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_ledger\_non\_escape}
\begin{proof}
Project the accepted declaration row $A$ from the carrier. Its only ledger-facing coordinate is $L$, so downstream reads of the accepted name pass through the environment row rather than through an informal description of the term.

Next read the dependency side through $Q$ and the replay side through $R$. These rows bind the transitive dependency query and the source replay that reconstructs the acceptance event from the project ledger.

The local naming row $N$ packages $A,L,Q,R$ together with $G,K,H,C,P$. Because the carrier contains no row for kernel correctness or for unstated paper meaning, ledgered acceptance cannot escape into either claim.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness axiom-query boundary]
\label{thm:kernel-acceptance-audit-witness-axiom-query-boundary}
For every accepted carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the axiom-query row $Q$ is the only boundary through which an audit consumer may classify the transitive dependency ancestry of the accepted declaration. The build-replay row $R$ reconstructs the local acceptance event, while $Q$ classifies whether the resulting ledgered declaration imports a forbidden dependency. No consumer may infer dependency cleanliness from the generated-term row $G$, the candidate row $K$, the accepted-declaration row $A$, or the local naming row $N$ alone.
\end{theorem}
\begin{proof}
The generated term, candidate, accepted declaration, and name rows identify what was submitted, accepted, ledgered, and named. These rows do not enumerate the transitive ancestry of the proof object or definition body.

The build-replay row $R$ reconstructs the acceptance event from sources, but replay alone records that the declaration is accepted in the current environment. The dependency classification is a separate audit read.

That separate read is $Q$. Since the carrier designates $Q$ as the axiom-query row and provides no second ancestry coordinate, any cleanliness conclusion must pass through $Q$ rather than through the local name, the generated term, or the acceptance stamp by itself.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_axiom\_query\_boundary}

\begin{definition}[KernelAcceptanceAuditWitness terminal accepted row]
\label{def:kernel-acceptance-audit-witness-terminal-row}
For an accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the terminal accepted-row surface is the finite read endpoint
$$
A,L,Q,R,N.
$$
It records the accepted declaration, its environment ledger entry, the axiom-query boundary, the build-replay route, and the local naming row. It contains no coordinate for kernel correctness, host runtime correctness, or a paper claim stronger than the accepted declaration.
\end{definition}
\leandef{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessTerminalRow}

\begin{theorem}[KernelAcceptanceAuditWitness route determinacy]
\label{thm:kernel-acceptance-audit-witness-route-determinacy}
For every accepted carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the replay route from the generated row $G$ to the accepted row $A$ and the axiom-query route from $A$ to $Q$ are determined by the displayed continuation coordinate $C$. Any two audit reads that agree on $C$ and on the packet rows $G,K,A,L,Q,R,H,P,N$ reach the same replay row $R$ and the same axiom-query row $Q$.
\end{theorem}
\begin{proof}
Read the carrier coordinates first. The generated row, kernel candidate, accepted declaration, ledger row, axiom-query row, replay row, transport row, provenance row, and local name are fixed as the packet $W$.

The only displayed continuation coordinate is $C$. Thus a replay consumer and an axiom-query consumer have no second route field from which to choose a different path through the same packet.

If two audit reads agree on $C$ and on the displayed rows, their replay endpoints and axiom-query endpoints are the fixed rows $R$ and $Q$. Route determinacy is therefore read directly from the finite packet.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_route\_determinacy}

\begin{theorem}[KernelAcceptanceAuditWitness replay and query non-escape]
\label{thm:kernel-acceptance-audit-witness-nonescape}
For every accepted carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
every downstream replay or axiom-query consumer factors through the terminal accepted-row surface $A,L,Q,R,N$ together with the displayed route row $C$. No such consumer can extract kernel correctness, compiler correctness, runtime correctness, dependency cleanliness without $Q$, replay success without $R$, or an unstated paper claim from the finite packet.
\end{theorem}
\begin{proof}
Start with the terminal accepted-row surface of \autoref{def:kernel-acceptance-audit-witness-terminal-row}. It exposes only $A,L,Q,R,N$, so accepted-declaration access terminates at the ledger, query, replay, and naming rows.

Use route determinacy from \autoref{thm:kernel-acceptance-audit-witness-route-determinacy}. Replay and axiom-query reads are routed by $C$ to the displayed rows $R$ and $Q$ rather than to an implicit source of correctness.

Finally inspect the missing coordinates of the carrier. Since $W$ has no row for kernel correctness, compiler correctness, runtime correctness, hidden dependency cleanliness, or stronger paper meaning, replay and query consumers cannot escape beyond the finite audit packet.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_replay\_query\_nonescape}

\begin{theorem}[KernelAcceptanceAuditWitness public obligation surface]
\label{thm:kernel-acceptance-audit-witness-obligation-surface}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the public obligation surface consists exactly of the accepted declaration row $A$, environment-ledger row $L$, axiom-query row $Q$, build-replay row $R$, componentwise $\hsame$ transports $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$, together with the generated and candidate rows $G,K$ needed to replay the acceptance event. Consumers cannot read kernel correctness, compiler correctness, runtime correctness, dependency cleanliness without $Q$, replay success without $R$, or stronger paper meaning from this packet.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_public\_obligation\_surface}
\begin{proof}
First expose the finite packet by \autoref{thm:kernel-acceptance-audit-witness-namecert-obligations}. It identifies the generated row, candidate row, accepted declaration, ledger row, axiom-query row, replay row, transport row, continuation row, provenance row, and local name as the entire NameCert surface.

Next isolate the accepted endpoint. The terminal row of \autoref{def:kernel-acceptance-audit-witness-terminal-row} gives $A,L,Q,R,N$, while \autoref{thm:kernel-acceptance-audit-witness-ledger-non-escape} prevents that endpoint from becoming a certificate of kernel correctness or a stronger paper claim.

Finally combine the query and route controls. The axiom-query boundary of \autoref{thm:kernel-acceptance-audit-witness-axiom-query-boundary} forces dependency classification through $Q$, route determinacy from \autoref{thm:kernel-acceptance-audit-witness-route-determinacy} fixes the replay and query endpoints through $C$, and replay/query non-escape from \autoref{thm:kernel-acceptance-audit-witness-nonescape} excludes compiler correctness, runtime correctness, hidden dependency cleanliness, and stronger paper meaning.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness source gate]
\label{thm:kernel-acceptance-audit-witness-source-gate}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
an accepted source row may enter the audit witness only through the generated-term row $G$, the kernel-candidate row $K$, the accepted-declaration row $A$, and the environment-ledger row $L$. The source gate is therefore the displayed route from source replay to kernel candidate to accepted declaration to ledger entry; it is not host equality, proof text, runtime evidence, or an unledgered source artifact.
\end{theorem}
\begin{proof}
Start with the carrier and NameCert obligations. The only entry coordinates for source-facing data are the generated row $G$, candidate row $K$, accepted declaration $A$, and ledger row $L$.

Use ledger non-escape. It forces downstream reads of $A$ through $L,Q,R,N$, so a source-facing acceptance row cannot bypass the environment ledger or the replay and query boundaries.

Finally apply route determinacy. The route row $C$ fixes the passage from generation to candidate, acceptance, ledger, replay, and query, while replay/query non-escape excludes host equality, proof text, runtime evidence, and unledgered source artifacts.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_source\_gate}

\begin{theorem}[KernelAcceptanceAuditWitness query-ledger totality]
\label{thm:kernel-acceptance-audit-witness-query-ledger-totality}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
every axiom query made by an audit consumer is accounted for by the ledgered query route $A,L,Q,R,C,N$. A consumer may replay the accepted declaration through $R$ and classify its transitive dependency ancestry through $Q$, but it cannot obtain dependency cleanliness from $G,K,A,L,H,P,N$ without that query row.
\end{theorem}
\begin{proof}
Read the axiom-query boundary first. It makes $Q$ the only coordinate that classifies the transitive dependency ancestry of the accepted declaration.

Next combine the terminal accepted-row surface with route determinacy. The rows $A,L,Q,R,N$ give the accepted declaration, ledger entry, query boundary, replay route, and local name, while $C$ fixes the route by which the query is reached.

Finally use the public obligation surface. It includes all finite rows of the packet but still withholds dependency cleanliness unless $Q$ is read, so every axiom query is accounted for by the displayed query ledger.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_query\_ledger\_totality}

\begin{theorem}[KernelAcceptanceAuditWitness source-query route exhaustion]
\label{thm:kernel-acceptance-audit-witness-source-query-route-exhaustion}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
every public source-facing audit route from the generated row $G$ to dependency classification passes through the kernel-candidate row $K$, accepted-declaration row $A$, environment-ledger row $L$, build-replay row $R$, axiom-query row $Q$, displayed continuation row $C$, and local $\NameCert$ row $N$ in that order of displayed obligations. No audit consumer may infer kernel correctness, replay success, or dependency cleanliness from $G,K,A,L,H,P,N$ without the replay row $R$ and the query row $Q$.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_source\_query\_route\_exhaustion}
\begin{proof}
Start with the carrier definition. It lists exactly the rows $G,K,A,L,Q,R,H,C,P,N$, so a public source-facing route has no coordinate outside the generated row, kernel candidate, accepted declaration, ledger row, query boundary, replay row, transport, continuation, provenance, and local name.

Apply the source gate to the entry side. Source-facing material can enter the witness only through $G,K,A,L$, which fixes the passage from generated row to kernel candidate, accepted declaration, and environment ledger before any dependency classification is read.

Use query-ledger totality for the audit side. Every query is accounted for by the ledgered route through $A,L,Q,R,C,N$, while the displayed obligations require the build replay row $R$ and axiom-query row $Q$ before the route can be consumed by $C$ and named by $N$.

Finally apply replay/query non-escape. The finite packet exports no row for kernel correctness, replay success without $R$, or dependency cleanliness without $Q$, so the source-to-query route is exhausted by the displayed rows and cannot be replaced by $G,K,A,L,H,P,N$ alone.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness standard bridge preconditions]
\label{thm:kernel-acceptance-audit-witness-standard-bridge-preconditions}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
a standard bridge request for this audit witness must display the generated-term row $G$, kernel-candidate row $K$, accepted-declaration row $A$, environment-ledger row $L$, axiom-query row $Q$, build-replay row $R$, componentwise transport row $H$, displayed continuation row $C$, provenance row $P$, and local naming row $N$. These are the bridge preconditions for a public replay/query handoff over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\KernelAcceptanceAuditWitnessUp}$.

The bridge request may not replace any of these rows by an accepted-name string, prose confidence, host runtime behavior, kernel-correctness claim, hidden dependency classification, or unledgered replay artifact.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_standard\_bridge\_preconditions}
\begin{proof}
Start with the carrier in \autoref{def:kernel-acceptance-audit-witness-carrier}. It lists exactly the generated term, candidate, accepted declaration, environment ledger, axiom query, build replay, transport, continuation, provenance, and local name as the finite packet rows.

Apply the NameCert obligation surface of \autoref{thm:kernel-acceptance-audit-witness-namecert-obligations}. The local naming row packages precisely those coordinates, so a bridge request that consumes the NameCert must display the same rows rather than a smaller accepted-name surface.

Use the axiom-query boundary and route determinacy, \autoref{thm:kernel-acceptance-audit-witness-axiom-query-boundary} and \autoref{thm:kernel-acceptance-audit-witness-route-determinacy}. They force dependency classification through $Q$ and route replay/query access through $C$ to the displayed $R$ and $Q$ endpoints.

Finally combine query-ledger totality and source-query route exhaustion, \autoref{thm:kernel-acceptance-audit-witness-query-ledger-totality} and \autoref{thm:kernel-acceptance-audit-witness-source-query-route-exhaustion}. These results account for every bridge-facing source-to-query read by the ledgered packet $G,K,A,L,Q,R,H,C,P,N$, leaving no hidden row from which a standard bridge request could infer acceptance, replay, dependency cleanliness, or local naming.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness bridge query replay boundary]
\label{thm:kernel-acceptance-audit-witness-bridge-query-replay-boundary}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the bridge-facing read of $A$ cannot infer dependency cleanliness without the axiom-query row $Q$ and cannot infer replay success without the build-replay row $R$. The continuation row $C$, ledger row $L$, provenance row $P$, and local name $N$ may route, ledger, package, and name the read, but they do not substitute for $Q$ or $R$.

Thus the public bridge boundary separates dependency classification from build replay while keeping both rows inside the same finite $\KernelAcceptanceAuditWitnessUp$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_bridge\_query\_replay\_boundary}
\begin{proof}
First apply the axiom-query boundary, \autoref{thm:kernel-acceptance-audit-witness-axiom-query-boundary}. It makes $Q$ the only coordinate through which a bridge-facing consumer may classify the accepted declaration's transitive dependency ancestry.

Next apply route determinacy, \autoref{thm:kernel-acceptance-audit-witness-route-determinacy}. The displayed continuation row $C$ fixes the replay endpoint $R$ and the query endpoint $Q$, but it does not turn either endpoint into the other.

Use query-ledger totality and source-query route exhaustion, \autoref{thm:kernel-acceptance-audit-witness-query-ledger-totality} and \autoref{thm:kernel-acceptance-audit-witness-source-query-route-exhaustion}. Together they account for every source-facing bridge read through $G,K,A,L,Q,R,C,N$ and require the query and replay rows before dependency and replay conclusions can be consumed.

Finally inspect the carrier rows through \autoref{def:kernel-acceptance-audit-witness-carrier}. The remaining rows $H,P,N$ transport, package, and name the finite packet, but none of them is an axiom query or build replay. The bridge boundary therefore permits no dependency cleanliness without $Q$ and no replay success without $R$.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness query replay interface]
\label{thm:kernel-acceptance-audit-witness-query-replay-interface}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
a public audit read of the accepted declaration $A$ reaches replay evidence
only through the build-replay row $R$ and dependency classification only
through the axiom-query row $Q$. The pair is routed by the displayed
continuation row $C$, ledgered by the environment row $L$, packaged by
$\mathsf{Pkg}$ provenance $P$, and named by the local $\NameCert$ row $N$.
Neither row can substitute for the other: replay through $R$ is not dependency
classification, and query classification through $Q$ is not build replay.

The interface exports no kernel correctness, compiler correctness, runtime
correctness, hidden dependency cleanliness, or paper meaning stronger than the
accepted declaration and its displayed audit rows.
\end{theorem}
\begin{proof}
Start with \autoref{thm:kernel-acceptance-audit-witness-axiom-query-boundary}.
It makes $Q$ the only coordinate through which a consumer classifies the
transitive dependency ancestry of the accepted declaration, while replay
through $R$ only reconstructs the local acceptance event.

Apply \autoref{thm:kernel-acceptance-audit-witness-route-determinacy}. The
displayed continuation row $C$ fixes both the replay endpoint and the query
endpoint for reads of $A$, so no second route can exchange their roles.

Use \autoref{thm:kernel-acceptance-audit-witness-query-ledger-totality}. The
query side is accounted for by the ledgered route $A,L,Q,R,C,N$, with
dependency cleanliness unavailable unless the query row $Q$ is read.

Finally invoke \autoref{thm:kernel-acceptance-audit-witness-build-replay-coverage}.
The replay side is covered by $R,L,C,Q,N$ as a replayed and ledgered acceptance
event. Combining the two rows gives the public interface: $R$ supplies replay,
$Q$ supplies dependency classification, and $L,C,P,N$ ledger, route, package,
and name the pair without adding kernel correctness, compiler correctness,
runtime correctness, hidden dependency cleanliness, or stronger paper meaning.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_query\_replay\_interface}

\begin{theorem}[KernelAcceptanceAuditWitness acceptance boundary]
\label{thm:kernel-acceptance-audit-witness-acceptance-boundary}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
kernel acceptance records that the declaration row $A$ has entered the environment ledger $L$ with replay route $R$ and axiom-query boundary $Q$. It does not promote host equality, proof text, generated prose, runtime behavior, compiler correctness, or a stronger BEDC theorem into evidence beyond the accepted declaration and its displayed audit rows.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_acceptance\_boundary}
\begin{proof}
Begin with the public obligation surface. It exposes the accepted declaration, environment ledger, axiom-query row, build replay, transports, continuations, provenance, local name, and the generated and candidate rows needed for replay.

Use the source gate theorem above to restrict how source-facing material reaches acceptance. The only admitted route passes through $G,K,A,L$ and then through the displayed replay and query coordinates.

Apply replay/query non-escape and the axiom-query boundary. Replay success is read through $R$, dependency classification through $Q$, and the carrier contains no coordinate for host equality, proof text, generated prose, runtime behavior, compiler correctness, or stronger BEDC evidence.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness build replay coverage]
\label{thm:kernel-acceptance-audit-witness-build-replay-coverage}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
each accepted declaration row consumed by the witness is covered by the displayed build-replay row $R$, environment ledger $L$, route row $C$, query row $Q$, and local name row $N$. Thus an audit consumer may read acceptance only as the replayed and ledgered declaration $A$ with its query boundary and local $\NameCert$ packaging, not as an unledgered kernel event or an external proof of correctness.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_build\_replay\_coverage}
\begin{proof}
Start with the carrier and terminal accepted-row surface. The carrier displays $G,K,A,L,Q,R,H,C,P,N$, while the terminal surface isolates $A,L,Q,R,N$ as the endpoint available to acceptance consumers.

Apply route determinacy to the replay and query routes. The displayed continuation row $C$ fixes the replay endpoint $R$ and query endpoint $Q$ for the accepted row $A$, so another route cannot be substituted after the declaration has been accepted.

Finally use replay/query non-escape. Since replay success is read through $R$, dependency classification through $Q$, ledger position through $L$, and local naming through $N$, the accepted declaration is covered exactly by the displayed rows and cannot be read as an unledgered kernel event or an external correctness certificate.
\end{proof}

\begin{theorem}[KernelAcceptanceAuditWitness public bridge boundary]
\label{thm:kernel-acceptance-audit-witness-public-bridge-boundary}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
any public bridge consumer of $W$ may read only the accepted declaration row $A$, environment ledger $L$, axiom-query row $Q$, build-replay row $R$, displayed route row $C$, package provenance $P$, and local $\NameCert$ row $N$, together with the transport row $H$ as the componentwise equality data already displayed by the packet. Such a consumer cannot infer kernel correctness, compiler correctness, host runtime correctness, dependency cleanliness without $Q$, or any paper claim stronger than the accepted declaration $A$.
\end{theorem}
\begin{proof}
Start with the axiom-query boundary. It makes $Q$ the only displayed row that classifies transitive dependency ancestry, so a public bridge consumer cannot turn $A,L,H,C,P,N$ into dependency cleanliness without reading $Q$.

Next use build replay coverage. The accepted declaration is covered by $R,L,C,Q,N$, so the bridge-facing read of acceptance remains the replayed and ledgered row $A$ rather than an unledgered kernel event or an external correctness certificate.

Apply dependency-query exhaustion for the cleanliness side. It rules out reads of dependency cleanliness through the generated row, kernel candidate, accepted declaration, ledger, transport, provenance, or local name when the query boundary is absent.

Finally combine replay/query non-escape with the marker-consumer boundary. Replay and query consumers factor through $A,L,Q,R,C,N$, while marker consumers see only the accepted declaration, replay, query, ledger, local name, and route rows. The public bridge boundary therefore exposes the finite audit packet but does not export kernel correctness, compiler correctness, host runtime correctness, hidden dependency cleanliness, or a strengthened paper claim beyond $A$.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_public\_bridge\_boundary}

\begin{theorem}[KernelAcceptanceAuditWitness dependency-query exhaustion]
\label{thm:kernel-acceptance-audit-witness-dependency-query-exhaustion}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
dependency cleanliness can be read only through the axiom-query row $Q$. It cannot be inferred from the generated row $G$, kernel-candidate row $K$, accepted-declaration row $A$, environment ledger $L$, transport row $H$, provenance row $P$, or local name row $N$ without the displayed query boundary.
\end{theorem}
\begin{proof}
Use the axiom-query boundary first. It makes $Q$ the only row that classifies the transitive dependency ancestry of the accepted declaration.

Next apply query-ledger totality. Every audit query is accounted for by the ledgered route $A,L,Q,R,C,N$, so a cleanliness read must pass through the displayed query row rather than through a neighboring carrier coordinate.

The public obligation surface then lists all rows available to the consumer and still withholds dependency cleanliness unless $Q$ is read. Therefore $G,K,A,L,H,P,N$ can identify, ledger, transport, package, and name the declaration, but none of them can replace the axiom query.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_dependency\_query\_exhaustion}

\begin{theorem}[KernelAcceptanceAuditWitness marker consumer boundary]
\label{thm:kernel-acceptance-audit-witness-marker-consumer-boundary}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
a paper checked-marker consumer may consume only the accepted declaration row $A$, build-replay row $R$, axiom-query row $Q$, environment-ledger row $L$, and local $\NameCert$ row $N$, together with the displayed route $C$ that connects them. Such a marker consumer may not read kernel correctness, a stronger paper theorem, compiler correctness, runtime behavior, or dependency cleanliness outside $Q$.
\end{theorem}
\begin{proof}
Begin with ledger non-escape and the acceptance boundary. They make acceptance available as the ledgered declaration $A$ with $L,Q,R,N$, while excluding kernel correctness, compiler correctness, runtime behavior, and stronger paper meaning.

Use dependency-query exhaustion for the dependency side. Cleanliness is available only through $Q$, so a marker cannot infer it from the generated term, candidate, accepted row, ledger row, transport, provenance, or name by itself.

Finally combine build replay coverage with route determinacy. The replay row $R$, query row $Q$, ledger row $L$, local name $N$, and route row $C$ form the consumer boundary for the paper marker. Since no stronger coordinate is present in the carrier, the marker consumes the accepted declaration rather than a strengthened theorem.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_marker\_consumer\_boundary}

\begin{theorem}[KernelAcceptanceAuditWitness public export]
\label{thm:kernel-acceptance-audit-witness-public-export}
For every accepted $\KernelAcceptanceAuditWitnessUp$ carrier
$$
W=(G,K,A,L,Q,R,H,C,P,N),
$$
the public audit interface exported by $W$ is exactly the finite packet consisting of the carrier, the source gate, query-ledger totality, build replay coverage, dependency-query exhaustion, and the marker-consumer boundary. A downstream audit consumer may therefore read the acceptance event only through $A,L,Q,R,C,N$ together with the displayed provenance and transport rows $P,H$; it may not replace that interface by kernel correctness, compiler correctness, generated prose, host runtime behavior, or a stronger theorem than the accepted declaration.
\end{theorem}
\begin{proof}
First read the carrier and source gate. The carrier displays $G,K,A,L,Q,R,H,C,P,N$, and the source gate restricts source-facing material to the route through the generated term, kernel candidate, accepted row, ledger, replay, query, transport, continuation, provenance, and local name rows.

Next combine query-ledger totality with build replay coverage. These results force every accepted-row audit query to pass through $A,L,Q,R,C,N$ and keep replay success on the displayed replay row $R$ rather than on an unledgered kernel event.

Finally apply dependency-query exhaustion and the marker-consumer boundary. Cleanliness is readable only through $Q$, while marker consumers see only the accepted declaration, replay row, query row, ledger row, local name row, and their displayed route. The exported interface is therefore public as an audit object, but it contains no coordinate for kernel correctness, compiler correctness, generated prose, host runtime behavior, or theorem strengthening beyond $A$.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_public\_export}

\begin{theorem}[KernelAcceptanceAuditWitness accepted-row consumer boundary]
\label{thm:kernel-acceptance-audit-witness-accepted-row-consumer-boundary}
Every downstream consumer of an accepted $\KernelAcceptanceAuditWitnessUp$ row factors first through the terminal accepted row $A$ and the query ledger $Q$ before it may read package provenance $P$ or the local $\NameCert$ row $N$. Thus provenance identifies how the already ledgered accepted row is packaged, but it cannot supply dependency cleanliness, replay success, or acceptance by itself.
\end{theorem}
\begin{proof}
Start from the terminal accepted-row surface and the acceptance boundary. They expose $A$ together with $L,Q,R,N$ as the consumer endpoint and prevent a downstream read from treating provenance or naming as acceptance.

Use dependency-query exhaustion for the query side. Any cleanliness read must pass through $Q$, so provenance cannot replace the axiom-query row even when it packages the same accepted declaration.

Now apply build replay coverage and the marker-consumer boundary. Replay success is read through $R$, marker consumption is bounded by $A,L,Q,R,C,N$, and $P$ only packages the ledgered accepted row. Therefore an accepted-row consumer reaches provenance and local naming only after the terminal row and query ledger have already been fixed.
\end{proof}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_accepted\_row\_consumer\_boundary}

\begin{theorem}[KernelAcceptanceAuditWitness formal-axis separation]
\label{thm:kernel-acceptance-audit-witness-formal-axis-separation}
The public paper export in \autoref{thm:kernel-acceptance-audit-witness-public-export} is a paper-axis audit interface for the finite $\KernelAcceptanceAuditWitnessUp$ packet. It does not assert a Lean verification result, does not introduce a Lean marker, and leaves the chapter's formal status at $\unformalizedV$ until an independent Lean target verifies the corresponding carrier, ledger, replay, query, transport, provenance, and naming obligations.
\end{theorem}
\leanchecked{BEDC.Derived.KernelAcceptanceAuditWitnessUp.KernelAcceptanceAuditWitnessCarrier\_formal\_axis\_separation}
\begin{proof}
Inspect the exported rows. The public interface is built from the paper-side carrier and the finite audit route $A,L,Q,R,C,N$ with $H$ and $P$ as displayed support rows.

The theorem adds no Lean-side verification marker and cites no Lean declaration as its verifier. Hence it records the paper closure of the audit interface only.

The closure block therefore keeps the formal status at $\unformalizedV$ while raising the theory axis to the public audit surface. Formal verification remains a separate obligation for the Lean-side pipeline.
\end{proof}

\closureat{KernelAcceptanceAuditWitnessUp}{seedStr}
\closureat{KernelAcceptanceAuditWitnessUp}{obligationStr}
\closureat{KernelAcceptanceAuditWitnessUp}{scopedStr}
\closureat{KernelAcceptanceAuditWitnessUp}{publicStr}

\begin{closurestatus}{\KernelAcceptanceAuditWitnessUp}
  \constructivestory{A $\KernelAcceptanceAuditWitnessUp$ packet is generated from an elaborated term, kernel candidate, accepted declaration, environment ledger, axiom-query row, build-replay row, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{def:kernel-acceptance-audit-witness-carrier}, \autoref{thm:kernel-acceptance-audit-witness-namecert-obligations}, \autoref{thm:kernel-acceptance-audit-witness-ledger-non-escape}, \autoref{thm:kernel-acceptance-audit-witness-axiom-query-boundary}, \autoref{def:kernel-acceptance-audit-witness-terminal-row}, \autoref{thm:kernel-acceptance-audit-witness-route-determinacy}, \autoref{thm:kernel-acceptance-audit-witness-nonescape}, \autoref{thm:kernel-acceptance-audit-witness-obligation-surface}, \autoref{thm:kernel-acceptance-audit-witness-source-gate}, \autoref{thm:kernel-acceptance-audit-witness-query-ledger-totality}, \autoref{thm:kernel-acceptance-audit-witness-source-query-route-exhaustion}, \autoref{thm:kernel-acceptance-audit-witness-acceptance-boundary}, \autoref{thm:kernel-acceptance-audit-witness-build-replay-coverage}, \autoref{thm:kernel-acceptance-audit-witness-public-bridge-boundary}, \autoref{thm:kernel-acceptance-audit-witness-dependency-query-exhaustion}, \autoref{thm:kernel-acceptance-audit-witness-marker-consumer-boundary}, \autoref{thm:kernel-acceptance-audit-witness-public-export}, \autoref{thm:kernel-acceptance-audit-witness-accepted-row-consumer-boundary}, and \autoref{thm:kernel-acceptance-audit-witness-formal-axis-separation} bind the finite audit-witness carrier, local naming surface, terminal accepted-row endpoint, ledger route, replay route, deterministic query route, dependency-query boundary, public obligation surface, source gate, query-ledger totality, source-query route exhaustion, acceptance boundary, build replay coverage, public bridge boundary, dependency-query exhaustion, marker consumer boundary, public export, accepted-row consumer boundary, and verification-axis separation.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean verification, kernel correctness, host runtime correctness, compiler correctness, theorem-content strengthening beyond the accepted declaration, or a public standard bridge.}
  \upgradepath{Bridged closure requires a standard bridge target for the public accepted-row audit interface, while formal verification of carrier, ledger replay, axiom-query readback, transport, provenance, and local naming rows remains separate.}
\end{closurestatus}
