\chapter{A Concrete Naming Certificate for $\ClosedTermSubstitutionUp$}
\label{ch:concrete-instances-closedtermsubstitution-namecert}
\origin{ai}

The $\ClosedTermSubstitutionUp$ surface packages the MetaCIC boundary law for substitution as finite NameCert data. It records the term row, the closedness boundary, the substituting value, the shift and substitution witnesses, componentwise transport, continuation reads, provenance, and the local naming row that prevents a substitution payload from becoming an unregistered free variable.

The displayed boundary rows are consumed from \autoref{ch:concrete-instances-closedtermsubstitutionboundary-namecert}. The $\ClosedTermSubstitutionUp$ surface specializes that finite boundary to the inert value-payload route $Q=(T,d,V,S,H,C,P,N)$, without adding subject reduction, evaluator correctness, host CIC truth, or an unregistered variable source.

The packet is the local closed-term substitution surface consumed by \autoref{ch:concrete-instances-closedtermsubstitutionboundary-namecert} and by the compiler-facing schedule of \autoref{ch:concrete-instances-closedtermsubstitutioncompiler-namecert}. The dependency is the displayed term row, closedness boundary, substitution and shift witness row, $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ ledger, not semantic evaluator correctness or subject reduction.

\begin{definition}[Closed-term substitution carrier]
\label{def:closed-term-substitution-carrier}
A $\ClosedTermSubstitutionUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,d,V,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the MetaCIC term row, carrying a closed generator tree for the inspected term;
\item $d$ is the boundary row, recording the local de Bruijn depth at which closedness is certified;
\item $V$ is the substituting value row, displayed as payload data but not consumed by the closed term at boundary $d$;
\item $S$ is the substitution and shift witness row, containing the boundary equations for $\mathsf{substitute}(d,V,T)$ and $\mathsf{shift}(d,1,T)$ on the classified slice;
\item $H$ records componentwise $\hsame$ transports for $T,d,V,S$, package provenance, and the local naming row;
\item $C$ records the $\Cont$ read routes that expose the term, boundary, value, witness row, and returned term equality;
\item $P$ is the $\Pkg$ provenance over the MetaCIC term generator, $\mathsf{ClosedAt}$ classifier, substitution and shift generators, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ClosedTermSubstitutionUp}$ row.
\end{enumerate}
The carrier is exactly this finite packet. It contains no open-term subject-reduction theorem, no semantic evaluator correctness proof, no host CIC truth predicate, no future binder budget, and no unregistered free-variable source.
\end{definition}
\leanchecked{BEDC.Derived.ClosedTermSubstitutionUp.ClosedTermSubstitutionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Closed-term substitution boundary inertness]
\label{thm:closed-term-substitution-boundary-inertness}
For an accepted $\ClosedTermSubstitutionUp$ carrier $Q=(T,d,V,S,H,C,P,N)$, every substitution read at the displayed boundary is inert on the classified term row. The witness row $S$ records the boundary equation
$$
\begin{aligned}
  \mathsf{ClosedAt}(d,T)
  &\Rightarrow
  \mathsf{substitute}(d,V,T)=T
\end{aligned}
$$
and the companion shift equation at the same boundary. The value row $V$ remains displayed payload data; it is not projected as a consumed variable of $T$.
\end{theorem}
\begin{proof}
Project the term, boundary, and witness rows of the carrier. The classifier row says that every free de Bruijn index visible in $T$ lies below $d$.

The substitution generator can change a variable only at the displayed boundary, or adjust a variable above that boundary. Both branches require an index at or beyond $d$, and the closedness witness excludes such an index inside $T$.

The compound cases are transported componentwise through $H$ and replayed by the read routes in $C$. Thus the only public output of the substitution read is the equality stored in $S$, while $V$ remains a displayed but unconsumed payload row.
\end{proof}

\begin{theorem}[Closed-term substitution NameCert obligations]
\label{thm:closed-term-substitution-namecert-obligations}
The local $\NameCert_{\ClosedTermSubstitutionUp}$ surface consists of carrier admission for $Q=(T,d,V,S,H,C,P,N)$, term-row exposure, boundary-row exposure, value-row display without consumption, substitution and shift witness accountability, componentwise $\hsame$ stability, displayed $\Cont$ read locality, $\Pkg$ provenance, and non-escape for open-term subject reduction, semantic evaluator correctness, host truth, future binder budgets, and unregistered free variables.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:closed-term-substitution-carrier}. The packet exposes exactly the MetaCIC term row, boundary row, value row, witness row, transport rows, continuation routes, provenance, and local naming row.

Boundary accountability follows from \autoref{thm:closed-term-substitution-boundary-inertness}. The substitution and shift witnesses are read from $S$, and the continuation routes in $C$ expose those witnesses without adding a further generator.

Finally inspect the excluded objects. None appears as a carrier coordinate, and the transport row $H$ preserves only the displayed coordinates. Therefore a consumer of $\ClosedTermSubstitutionUp$ cannot extract an open-term theorem, evaluator semantics, host truth predicate, future binder budget, or unregistered free variable from this packet.
\end{proof}

\begin{theorem}[Closed-term substitution closure-preservation provenance]
\label{thm:closed-term-substitution-closure-preservation-provenance}
Every $\ClosedTermSubstitutionUp$ boundary-inert read consumed by closure-preservation or beta-substitution routes remains the displayed packet
$$
Q=(T,d,V,S,H,C,P,N).
$$
Downstream closure-preservation consumers may cite this substitution surface only through the provenance rows of \autoref{ch:concrete-instances-closurepreservationtrace-namecert}, \autoref{ch:concrete-instances-betasubstitutionpreservation-namecert}, and \autoref{ch:concrete-instances-subjectreduction-namecert}. Those consumers add closure-preservation and typing-route context, but they do not add an open-term theorem, evaluator semantics, host truth predicate, or free-variable source to the closed substitution packet.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:closed-term-substitution-carrier}. It exposes only $T,d,V,S,H,C,P,N$ as the term, boundary, value, witness, transport, route, provenance, and local naming rows.

Apply \autoref{thm:closed-term-substitution-boundary-inertness} and \autoref{thm:closed-term-substitution-namecert-obligations}. The inertness theorem keeps the substitution read at the displayed boundary, and the NameCert obligations keep every public read inside the same packet.

The sibling closure-preservation, beta-substitution, and subject-reduction chapters consume this packet through their own provenance rows. Their additional rows record closure-preservation and typing-route context downstream; they do not enlarge $Q$ with open-term semantics, evaluator truth, host truth, or a new free-variable source.
\end{proof}

\begin{theorem}[Closed substitution source boundary]
\label{thm:closed-substitution-source-boundary}
Every accepted $\ClosedTermSubstitutionUp$ carrier $Q=(T,d,V,S,H,C,P,N)$ exposes only the displayed MetaCIC term row, the closedness boundary row, the value payload row, the substitution and shift witness row, the $\hsame$ transport row, the $\Cont$ read routes, the $\Pkg$ provenance row, and the local $\NameCert_{\ClosedTermSubstitutionUp}$ row. No other source row is public from this carrier.
\end{theorem}
\begin{proof}
Project $Q$ through \autoref{def:closed-term-substitution-carrier}. The eight coordinates are exactly the displayed term, boundary, value, witness, transport, route, provenance, and naming rows.

The source boundary is the one imported from \autoref{ch:concrete-instances-closedtermsubstitutionboundary-namecert}. That chapter supplies the boundary law consumed here, while this carrier only specializes the law to the inert value-payload route.

The excluded sources are therefore absent by coordinate inspection. An accepted read may expose $T,d,V,S,H,C,P,N$, but it has no coordinate from which to extract an open-term theorem, evaluator semantics, host truth predicate, future binder budget, or unregistered variable source.
\end{proof}

\begin{theorem}[Closed substitution ledger exhaustion]
\label{thm:closed-substitution-substitution-ledger-exhaustion}
Every public substitution read from an accepted $\ClosedTermSubstitutionUp$ carrier factors through $S$, $H$, $C$, and $P$. Consequently the ledger records exactly boundary inertness together with substitution and shift witness accountability, and no further substitution authority is exported.
\end{theorem}
\begin{proof}
Apply \autoref{thm:closed-term-substitution-boundary-inertness}. The only boundary equation made public for substitution is the equation stored in the witness row $S$, together with the companion shift equation at the same boundary.

Apply \autoref{thm:closed-term-substitution-namecert-obligations}. Public access to the witness row is routed through the displayed continuation row $C$, stabilized through the componentwise $\hsame$ row $H$, and sourced through the package provenance row $P$.

Thus a substitution consumer exhausts the ledger by reading $S$, transporting through $H$, following $C$, and citing $P$. No additional row remains from which to read a second substitution law, a semantic evaluator claim, or a host-level truth predicate.
\end{proof}

\begin{theorem}[Closed substitution binder-scope nonescape]
\label{thm:closed-substitution-binder-scope-nonescape}
For every accepted $\ClosedTermSubstitutionUp$ carrier $Q=(T,d,V,S,H,C,P,N)$, binder depth, value payload, and continuation reads cannot export open-term subject reduction, evaluator correctness, host CIC truth, or an unregistered variable source.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. The boundary coordinate $d$ records only the local de Bruijn depth at which closedness is certified, and the value coordinate $V$ is displayed payload data rather than a consumed variable of $T$.

The continuation coordinate $C$ records routes that expose the term, boundary, value, witness row, and returned term equality. By \autoref{thm:closed-term-substitution-namecert-obligations}, those routes do not add a further generator.

The non-escape clauses stated in the carrier and NameCert rows exclude open-term subject reduction, evaluator correctness, host CIC truth, future binder budgets, and unregistered free variables. Since none of those objects is a coordinate of $Q$, the binder scope and payload reads cannot export them.
\end{proof}

\closureat{ClosedTermSubstitutionUp}{scopedStr}[BEDC.Derived.ClosedTermSubstitutionUp.ClosedTermSubstitutionTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\ClosedTermSubstitutionUp}
  \constructivestory{A $\ClosedTermSubstitutionUp$ packet is generated from a MetaCIC term row, a closedness boundary row, a displayed substitution value, substitution and shift witness rows, componentwise transports, continuation routes, package provenance, and local naming.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:closed-term-substitution-carrier}, \autoref{thm:closed-term-substitution-boundary-inertness}, \autoref{thm:closed-term-substitution-namecert-obligations}, \autoref{thm:closed-substitution-source-boundary}, \autoref{thm:closed-substitution-substitution-ledger-exhaustion}, \autoref{thm:closed-substitution-binder-scope-nonescape}, and \leanchecked{BEDC.Derived.ClosedTermSubstitutionUp.taste\_gate} bind the carrier, boundary inertness, NameCert obligations, source boundary, ledger exhaustion, binder-scope nonescape, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ to the scoped packet surface.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.ClosedTermSubstitutionUp.ClosedTermSubstitutionTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close open-term subject reduction, semantic evaluator correctness, host CIC truth, future binder allocation, or a complete self-compilation theorem.}
  \upgradepath{Public closure next requires a reusable closed-substitution export package.}
\end{closurestatus}
