\chapter{A Concrete Naming Certificate for $\CriticalLineWitnessUp$}
\label{ch:concrete-instances-criticallinewitness-namecert}
\origin{human}

The $\CriticalLineWitnessUp$ interface records the finite packet a constructive Riemann Hypothesis witness would expose after a zero has already been supplied in the critical strip. It does not prove $\mathsf{RH}$ and does not produce a zero. It only names the BEDC-native surface of the witness type in \autoref{thm:rh-witness-modulus} and the restriction type in \autoref{thm:rh-witness-critical-line-restriction}.

\begin{definition}[Critical-line witness carrier]
\label{def:critical-line-witness-carrier}
A $\CriticalLineWitnessUp$ carrier is a finite $\BHist$ packet
$$
W=(Z,S,M,R,Q,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $Z$ is the supplied $\ZetaZerosUp$ zero row, displaying the zero history and its zero-classifier witness;
\item $S$ is the supplied $\CritStripUp$ critical-strip row for the same complex history, displaying the left and right strip comparisons;
\item $M$ is the on-critical-line modulus row, sending each depth $n:\NatUp$ to an inspected rational depth at which the real-part representative is within $2^{-n}$ of $1/2$;
\item $R$ is the $\RealUp$ real-part row consumed by the modulus;
\item $Q$ is the $\RatUp$ comparison ledger containing the half-line rational row, dyadic tolerance row, and strict comparison row used by $M$;
\item $H$ records componentwise $\hsame$ transports for the zero row, critical-strip row, real-part row, rational comparison ledger, and modulus row;
\item $C$ records the displayed $\Cont$ routes through which consumers inspect those rows;
\item $P$ is the $\Pkg$ provenance over $\ZetaZerosUp$, $\CritStripUp$, $\RealUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, and the supplied analytic certificates;
\item $N$ is the local $\NameCert_{\CriticalLineWitnessUp}$ row.
\end{enumerate}
The carrier exposes a witness packet for a supplied zero-in-strip input. It contains no proof that every zero in the critical strip has such a packet, no zero-producing search, no host complex equality, no quotient real equality, no selected representative of a Cauchy class, and no appeal to ambient analytic completeness.
\end{definition}

\begin{theorem}[Critical-line witness NameCert obligations]
\label{thm:critical-line-witness-namecert-obligations}
The local $\NameCert_{\CriticalLineWitnessUp}$ surface consists exactly of five finite rows:
\begin{enumerate}
\item carrier admission for the displayed packet of \autoref{def:critical-line-witness-carrier};
\item zero-strip compatibility, stating that the $\ZetaZerosUp$ row $Z$ and $\CritStripUp$ row $S$ name the same supplied complex history through displayed $\hsame$ transport;
\item modulus discipline, stating that every depth request is answered by the on-critical-line modulus row $M$ using only the real-part row $R$ and rational comparison ledger $Q$;
\item non-escape discipline, stating that consumers reach the critical-line conclusion only through $Z,S,M,R,Q,H,C,P,N$;
\item ledger exactness, stating that the public witness surface is exhausted by the displayed zero, strip, modulus, comparison, transport, continuation, package, and local naming rows.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_modulus\_route\_closure}
\begin{proof}
Carrier admission is projection of the finite packet in \autoref{def:critical-line-witness-carrier}. The packet lists the supplied zero row, critical-strip row, modulus row, real-part row, rational comparison ledger, transports, continuations, package provenance, and local naming row.

Zero-strip compatibility uses the componentwise $\hsame$ rows in $H$ to bind $Z$ and $S$ to the same supplied complex history. No host complex equality is read, and no independent zero search is introduced.

Modulus discipline is the row $M$. A depth request $n$ is routed to the inspected real-part representative in $R$ and to the dyadic comparison rows in $Q$, yielding the critical-line approximation at that depth.

The non-escape and ledger rows then use $C$, $P$, and $N$. Since the packet has no quotient, representative-selection, host-equality, or analytic-completeness coordinate, every public witness read is exhausted by the displayed finite rows.
\end{proof}

\begin{theorem}[Critical-line witness zero-strip compatibility]
\label{thm:critical-line-witness-strip-zero-compatibility}
For an accepted $\CriticalLineWitnessUp$ carrier
$$
W=(Z,S,M,R,Q,H,C,P,N),
$$
the supplied $\ZetaZerosUp$ row $Z$ and supplied $\CritStripUp$ row $S$ are tied to the same complex history by displayed $\hsame$ transport in $H$. A public witness read may therefore consume $Z$ as the zero row and $S$ as the strip row for the same supplied history, but it cannot replace that displayed transport by host complex equality or by a new zero-producing search.
\end{theorem}
\begin{proof}
Project the carrier and inspect the transport coordinate $H$. Its zero-strip component is the only row that connects the zero row $Z$ and the critical-strip row $S$.

The row is an $\hsame$ transport between the displayed complex histories already carried by $Z$ and $S$. It moves the supplied history across the two public rows without introducing a separate complex equality principle.

Since the carrier contains no search coordinate and no host equality coordinate, the compatibility read is exhausted by the displayed zero row, strip row, and transport row.
\end{proof}

\begin{theorem}[Critical-line witness real-part modulus stability]
\label{thm:critical-line-witness-realpart-modulus-stability}
For an accepted $\CriticalLineWitnessUp$ carrier
$$
W=(Z,S,M,R,Q,H,C,P,N),
$$
transported depth requests preserve the alignment between the $\RealUp$ real-part row $R$ and the on-line modulus row $M$. At each depth $n:\NatUp$, the answer $M(n)$ is read against the transported $R$ row and the comparison ledger $Q$, so the public critical-line modulus remains attached to the same supplied zero-in-strip history.
\end{theorem}
\begin{proof}
Start with a depth request $n:\NatUp$. The carrier exposes only the modulus coordinate $M$ as the answer row for such a request.

The real-part row used by that answer is $R$. Transport through $H$ keeps the displayed real-part history aligned with the zero and strip rows, and continuation through $C$ only routes this already displayed data.

The rational comparison needed to read the modulus is then supplied by $Q$. Thus every transported request still reads the same $R$ row through $M$ and $Q$, with no selected Cauchy representative or ambient analytic completeness principle.
\end{proof}

\begin{theorem}[Critical-line witness rational comparison ledger exactness]
\label{thm:critical-line-witness-rat-comparison-ledger-exactness}
For an accepted $\CriticalLineWitnessUp$ carrier
$$
W=(Z,S,M,R,Q,H,C,P,N),
$$
the $\RatUp$ comparison ledger $Q$ is exactly the finite collection of the half-line row, the dyadic tolerance row, and the strict comparison row used by the modulus coordinate $M$. Every public rational comparison read of the witness packet factors through those three rows and cannot appeal to an external real-order decision, quotient equality, or hidden numeric oracle.
\end{theorem}
\begin{proof}
Inspect the comparison ledger coordinate $Q$. By carrier admission, $Q$ exposes the half-line row, the dyadic tolerance row, and the strict comparison row used by the modulus.

The modulus coordinate $M$ consumes exactly those rational rows when answering a depth request. The half-line row supplies the target $1/2$, the dyadic tolerance row supplies the inspected $2^{-n}$ bound, and the strict comparison row supplies the visible inequality read.

No other rational comparison coordinate is present in $W$. Therefore the public comparison ledger is exact and has no route to an external real-order decision, quotient equality, or hidden oracle.
\end{proof}

\begin{theorem}[Critical-line witness modulus row]
\label{thm:critical-line-witness-modulus-row}
For an accepted $\CriticalLineWitnessUp$ carrier
$$
W=(Z,S,M,R,Q,H,C,P,N),
$$
each request $n:\NatUp$ is answered by the displayed modulus coordinate $M(n)$ and the $\RatUp$ comparison ledger $Q$. The resulting read states that the rational representative of the $\RealUp$ real-part row $R$ at the inspected depth lies within the dyadic tolerance $2^{-n}$ of the half-line row $1/2$.
\end{theorem}
\begin{proof}
Project the carrier and inspect the modulus coordinate. The only field that answers a depth request is $M$, and its target is the inspected real-part representative carried by $R$.

The rational comparison is then read from $Q$. The half-line row, dyadic tolerance row, and strict comparison row are all visible coordinates of the same packet, so the read remains at the $\RatUp$ level.

Transport through $H$ and continuation through $C$ preserve exactly these rows. The package and local naming fields $P,N$ record provenance and membership, but they add no analytic proof of $\mathsf{RH}$ and no off-ledger equality principle.
\end{proof}

\begin{theorem}[Critical-line witness non-escape boundary]
\label{thm:critical-line-witness-nonescape-boundary}
Every public critical-line read exported by an accepted $\CriticalLineWitnessUp$ carrier factors through $Z,S,M,R,Q,H,C,P,N$. It cannot read a host complex equality, quotient real equality, selected Cauchy representative, zero-producing search, global zero-set classifier, or ambient analytic completeness principle.
\end{theorem}
\begin{proof}
Start with the carrier inventory. The packet contains exactly the supplied zero row, critical-strip row, modulus row, real-part row, rational comparison ledger, transport rows, continuation rows, package provenance, and local naming row.

The critical-line conclusion is consumed through the modulus row and rational comparison ledger. The zero and strip rows provide the supplied input context, while $H$ and $C$ provide only displayed transport and route data.

None of the excluded objects appears as a coordinate of the carrier. Therefore a public read has no route by which host equality, quotient equality, representative selection, zero search, global zero-set classification, or ambient completeness can enter the witness packet.
\end{proof}

\begin{theorem}[Critical-line witness ledger exactness]
\label{thm:critical-line-witness-ledger-exactness}
The public $\CriticalLineWitnessUp$ ledger of an accepted carrier is exactly the finite packet
$$
Z,S,M,R,Q,H,C,P,N.
$$
It exposes a BEDC-native witness that a supplied $\ZetaZerosUp$ row in a supplied $\CritStripUp$ row carries an on-critical-line modulus over $\RealUp$ and $\RatUp$, and it exposes no proof that all non-trivial zeros admit such a packet.
\end{theorem}
\begin{proof}
Read the public ledger by projecting the carrier. The rows $Z$ and $S$ provide the supplied zero-in-strip input, and $M,R,Q$ provide the critical-line modulus and its rational comparison surface.

The rows $H$ and $C$ account for the only permitted movement of the displayed data, while $P$ and $N$ record package provenance and local naming. These rows do not add a quantifier over all zeros and do not create a zero.

Consequently the ledger is exact: every exported witness coordinate is one of $Z,S,M,R,Q,H,C,P,N$, and every coordinate in that tuple has a public role in the witness packet.
\end{proof}

\begin{theorem}[Critical-line witness zero-row source scope]
\label{thm:critical-line-witness-zero-row-scope}
An accepted $\CriticalLineWitnessUp$ packet consumes only the supplied zero row, critical-strip row, modulus route, real-part row, rational comparison ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ evidence:
$$
Z,S,M,R,Q,H,C,P,N.
$$
This finite zero-row source scope exports no proof of $\mathsf{RH}$, zero construction, global zero-set classifier, analytic continuation, host equality, quotient representative, or analytic completeness principle.
\end{theorem}
\begin{proof}
Begin with the carrier and NameCert obligation surface. The accepted packet exposes exactly the supplied zero row $Z$, strip row $S$, modulus row $M$, real-part row $R$, comparison ledger $Q$, transports $H$, continuations $C$, provenance $P$, and local naming row $N$.

Use \autoref{thm:critical-line-witness-strip-zero-compatibility} and \autoref{thm:critical-line-witness-realpart-modulus-stability} to keep the witness attached to the displayed zero-in-strip source and its inspected real-part route. The modulus row is therefore a finite witness row, not a construction of zeros or a classification of all zero rows.

Apply \autoref{thm:critical-line-witness-rat-comparison-ledger-exactness} and \autoref{thm:critical-line-witness-nonescape-boundary}. They account for the half-line comparison and exclude host equality, quotient representatives, analytic continuation, and ambient completeness from the packet surface.

Finally invoke \autoref{thm:critical-line-witness-ledger-exactness}. It identifies the public ledger with $Z,S,M,R,Q,H,C,P,N$, so every accepted read is sourced by the finite zero-row packet and no global $\mathsf{RH}$-facing conclusion is exported.
\end{proof}

\closureat{CriticalLineWitnessUp}{seedStr}

\begin{closurestatus}{\CriticalLineWitnessUp}
  \constructivestory{A $\CriticalLineWitnessUp$ packet is generated from a supplied zeta-zero row, a supplied critical-strip row, an on-critical-line modulus row, a real-part row, rational half-line and dyadic comparison rows, displayed transports, continuation routes, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite carrier and witness-ledger surface for supplied zero-in-strip inputs over $\ZetaZerosUp$, $\CritStripUp$, $\RealUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not prove $\mathsf{RH}$, produce zeros, close the global zero-set classifier, construct analytic continuation, assert host equality, select quotient representatives, or invoke ambient analytic completeness.}
  \upgradepath{Obligation closure requires checking carrier admission, zero-strip compatibility, modulus discipline, non-escape, and ledger exactness for the displayed rows.}
\end{closurestatus}
