\chapter{A Concrete Naming Certificate for $\KnotUp$}
\label{ch:concrete-instances-knot-namecert}

The knot interface $\KnotUp$ packages a diagrammatic BEDC surface whose traditional reading is a closed one-dimensional source carried through an ambient deformation ledger. It depends on $\NameCert_{\SOneUp}$ (\autoref{ch:concrete-instances-s1-namecert}) and $\NameCert_{\HomotopyUp}$ (\autoref{ch:concrete-instances-homotopy-namecert}); those dependencies supply the endpoint rows and deformation rows, while the knot certificate records only finite $\mathsf{BHist}$, $\mathsf{Cont}$, $\hsame$, and $\mathsf{Pkg}$ data.

\section{Carrier definition}
\label{sec:knot-carrier}

\begin{definition}[KnotUp diagram BHist carrier]
\label{def:knot-diagram-bhist-carrier}
A $\KnotUp$ diagram packet is a finite carried tuple
$$
\mathcal{K}=(\mathcal{S},\mathcal{A},d,r,h,e_0,e_1,\rho,\lambda)
$$
whose rows are all BEDC rows. The source row $\mathcal{S}$ is a consumed
$\NameCert_{\SOneUp}$ packet, read only through its exposed source carrier,
component classifier, endpoint readback, and ledger surface. The ambient row
$\mathcal{A}$ is the target row in which the diagram lives; it is a
$\mathsf{BHist}$ endpoint family classified by the same package provenance as
the deformation rows and not by an external host embedding.

The diagram row $d$ is a finite crossing ledger. Each crossing entry is a
$\mathsf{BHist}$ face whose incident source endpoints are read from
$\mathcal{S}$ and whose over-under comparison is a displayed $\hsame$ or
$\mathsf{Cont}$ row. The row $r$ is the Reidemeister trace: a finite
$\mathsf{Cont}$ list whose entries are exactly the local crossing changes,
endpoint-preserving moves, and package-provenance updates used to pass from
one diagram ledger to the next. The row $h$ is the consumed
$\HomotopyUp$ deformation row, read as an ambient-deformation history
compatible with the same endpoints and with the same finite trace.

The endpoint rows $e_0$ and $e_1$ expose the initial and final embedded-source
interfaces as $\mathsf{BHist}$ rows over $\mathcal{S}$ and $\mathcal{A}$. The
row $\rho$ records the $\mathsf{Pkg}$ provenance of the source certificate,
ambient target row, diagram ledger, Reidemeister trace, and HomotopyUp
deformation row. The finite ledger $\lambda$ is the $\mathsf{Cont}$ display
containing precisely those source, ambient, crossing, move-trace, deformation,
endpoint, classifier, provenance, and exactness rows accepted by the public
$\NameCert_{\KnotUp}$ carrier.
\end{definition}

\begin{definition}[KnotUp Reidemeister ledger classifier]
\label{def:knot-reidemeister-ledger-classifier}
Two $\KnotUp$ diagram packets
$\mathcal{K}=(\mathcal{S},\mathcal{A},d,r,h,e_0,e_1,\rho,\lambda)$ and
$\mathcal{K}'=(\mathcal{S}',\mathcal{A}',d',r',h',e'_0,e'_1,\rho',\lambda')$
are related by the $\KnotUp$ Reidemeister ledger classifier when the following
finite rows are supplied:
\begin{enumerate}
  \item the $\SOneUp$ source packets $\mathcal{S}$ and $\mathcal{S}'$ are
  transported by the $\hsame$ classifier of $\NameCert_{\SOneUp}$;
  \item the crossing ledgers $d$ and $d'$ are matched entrywise by $\hsame$
  on their incident source endpoint rows and by $\mathsf{Cont}$ transport on
  their over-under comparison rows;
  \item the Reidemeister traces $r$ and $r'$ are related by a finite
  $\mathsf{Cont}$ refinement whose entries are again Reidemeister trace rows,
  not external diagram equivalences;
  \item the HomotopyUp deformation rows $h$ and $h'$ are related by the
  ambient-deformation classifier exposed by $\NameCert_{\HomotopyUp}$;
  \item the endpoint rows $e_0,e_1,e'_0,e'_1$ and the provenance rows
  $\rho,\rho'$ remain in the same $\mathsf{Pkg}$ scope, and the resulting
  ledgers $\lambda,\lambda'$ list exactly the transported source, diagram,
  deformation, endpoint, and provenance faces.
\end{enumerate}
This classifier is componentwise on the visible BEDC rows. It does not
identify packets by equality of host embeddings, by a quotient of knots, or by
treating ambient isotopy as an undecomposed primitive.
\end{definition}

\section{The certificate}
\label{sec:knot-certificate}

\begin{theorem}[KnotUp SOne source boundary]
\label{thm:knot-sone-source-boundary}
For a $\KnotUp$ diagram packet $\mathcal{K}$ of
\autoref{def:knot-diagram-bhist-carrier}, the public source boundary exposed
to $\NameCert_{\KnotUp}$ is exactly the $\SOneUp$ source carrier row
$\mathcal{S}$, its component classifier rows, the endpoint rows $e_0$ and
$e_1$, and the package-provenance row $\rho$ linking those endpoints to the
ambient target row. No carrier clause may read an unclassified source point,
an external circle object, or a host-level embedding in place of these rows.
\end{theorem}
\leanchecked{BEDC.Derived.KnotUp.KnotDiagramPacket\_sone\_source\_boundary}
\begin{proof}
Project $\mathcal{K}$ to its source field $\mathcal{S}$. The source
certificate is already a $\NameCert_{\SOneUp}$ packet, so its carrier,
component classifier, endpoint readback, and ledger rows are exactly the rows
available to the knot packet.

Next project the endpoint fields $e_0$ and $e_1$. By
\autoref{def:knot-diagram-bhist-carrier}, each endpoint row is a
$\mathsf{BHist}$ interface over the source packet and ambient target row, and
the provenance field $\rho$ records that these endpoints are part of the same
$\mathsf{Pkg}$ package.

Conversely, given precisely those source, endpoint, and provenance rows,
place them in the displayed fields of $\mathcal{K}$ and leave the diagram,
trace, deformation, and ledger rows to the remaining certificate clauses. This
reconstructs the public source boundary without adding any host source object.
\end{proof}

\begin{theorem}[KnotUp Homotopy ledger boundary]
\label{thm:knot-homotopy-ledger-boundary}
For a $\KnotUp$ diagram packet $\mathcal{K}$ of
\autoref{def:knot-diagram-bhist-carrier}, the HomotopyUp and Reidemeister
rows exposed to $\NameCert_{\KnotUp}$ are exactly the crossing ledger $d$, the
Reidemeister trace $r$, the HomotopyUp deformation row $h$, and the finite
$\mathsf{Cont}$ ledger $\lambda$. If two packets are related by the classifier
of \autoref{def:knot-reidemeister-ledger-classifier}, these four rows are
stable under the displayed $\hsame$ and $\mathsf{Cont}$ transports.
\end{theorem}
\leanchecked{BEDC.Derived.KnotUp.KnotDiagramPacket\_homotopy\_ledger\_boundary}
\begin{proof}
First read the crossing ledger $d$. Its entries name only incident
$\SOneUp$ endpoint rows, over-under comparison rows, and finite
$\mathsf{BHist}$ faces. Transporting the source endpoints by $\hsame$ therefore
transports every crossing entry componentwise.

Now read the Reidemeister trace $r$ and the deformation row $h$. The trace is
a finite $\mathsf{Cont}$ list of local moves, while $h$ is the corresponding
$\HomotopyUp$ deformation row. The classifier requires these rows to be
matched by finite trace refinement and by the $\NameCert_{\HomotopyUp}$
ambient-deformation classifier.

Finally inspect $\lambda$. It contains exactly the source, crossing,
Reidemeister, deformation, endpoint, provenance, and exactness faces. Since
each listed face is transported by the classifier clauses above, the ledger is
stable under the same $\hsame$ and $\mathsf{Cont}$ transports. Projecting a
classifier witness gives no additional ambient relation beyond these rows.
\end{proof}

\begin{theorem}[KnotUp public NameCert obligation surface]
\label{thm:knot-namecert-obligation-surface}
For a $\KnotUp$ diagram packet $\mathcal{K}$ of
\autoref{def:knot-diagram-bhist-carrier}, the public
$\NameCert_{\KnotUp}$ obligation surface is exactly the following finite row
family: the $\SOneUp$ source packet $\mathcal{S}$, the ambient target row
$\mathcal{A}$, the crossing ledger $d$, the Reidemeister trace $r$, the
$\HomotopyUp$ deformation row $h$, the endpoint rows $e_0$ and $e_1$, the
$\mathsf{Pkg}$ provenance row $\rho$, the finite $\mathsf{Cont}$ ledger
$\lambda$, the classifier of
\autoref{def:knot-reidemeister-ledger-classifier}, the source boundary of
\autoref{thm:knot-sone-source-boundary}, and the Homotopy ledger boundary of
\autoref{thm:knot-homotopy-ledger-boundary}. These rows supply the carrier,
classifier, stability, ledger, and exactness fields consumed by downstream
knot-facing chapters.
\end{theorem}
\leanchecked{BEDC.Derived.KnotUp.KnotDiagramPacket\_namecert\_obligation\_surface}
\begin{proof}
Project the packet to the fields listed in
\autoref{def:knot-diagram-bhist-carrier}. The source boundary theorem supplies
the exact $\SOneUp$ rows and endpoint package provenance. The Homotopy ledger
boundary theorem supplies the exact crossing, Reidemeister, deformation, and
continuation rows together with their classifier stability.

The classifier field is the relation of
\autoref{def:knot-reidemeister-ledger-classifier}. Its clauses transport the
source, diagram, trace, deformation, endpoint, provenance, and ledger rows
componentwise, so it is the stability surface required by the public
$\NameCert_{\KnotUp}$ package.

Conversely, every row named in the obligation surface is a field of
$\mathcal{K}$ or a projection theorem for those fields. Repacking them gives
the carrier, classifier, stability, ledger, and exactness surface visible to
downstream consumers. No additional host embedding, external knot quotient, or
undecomposed ambient-isotopy witness is part of the public interface.
\end{proof}

\begin{theorem}[KnotUp projection stability obligation]\label{thm:knot-projection-stability-obligation}
Every carried knot projection row over $\mathsf{BHist}$ is stable under $\hsame$ transport of the displayed $\SOneUp$ source row and the ambient $\HomotopyUp$ row. The transported row has the same visible knot packet, and its hidden projection data are carried only through the $\Cont$ ledger and the two cited NameCert source rows.
\end{theorem}
\leanchecked{BEDC.Derived.KnotUp.KnotDiagramPacket\_projection\_stability\_obligation}

\begin{proof}
Read the carried projection row as a $\mathsf{BHist}$ packet whose visible boundary consists of the $\SOneUp$ source row, the ambient $\HomotopyUp$ row, and the finite projection ledger. The BEDC source field is therefore $\NameCert_{\SOneUp}$ together with $\NameCert_{\HomotopyUp}$; the carrier field is the projection packet; the classifier field is the row displayed by the packet; and the stability field is the given $\hsame$ transport.

Transport first along the $\SOneUp$ source row and then along the ambient $\HomotopyUp$ row. The $\Cont$ ledger carries exactly the hidden projection witnesses, so no additional diagram equality or ambient quotient is introduced.

The ledger field is the transported finite projection ledger, the core theorem list is this stability row together with the two dependency rows, and exactness says that the accepted packet is precisely the transported packet. The standard bridge field is none, and the status field is a paper obligation for $\NameCert_{\KnotUp}$.
\end{proof}

\begin{theorem}[KnotUp Reidemeister-move classifier obligation]\label{thm:knot-reidemeister-move-classifier-obligation}
The $\KnotUp$ classifier is generated by finite $\mathsf{ProbeBundle}$ ledgers for Reidemeister I, II, and III moves, together with endpoint $\hsame$ transport. Reflexive, symmetric, and transitive classifier rows are supplied respectively by the empty move ledger, the reversed move ledger, and concatenation of finite move ledgers.
\end{theorem}

\begin{proof}
The BEDC source field is the projection carrier from \autoref{thm:knot-projection-stability-obligation} with endpoints classified by $\NameCert_{\SOneUp}$ and ambient rows classified by $\NameCert_{\HomotopyUp}$. The carrier field is a finite move ledger whose entries are tagged Reidemeister I, Reidemeister II, or Reidemeister III probes inside $\mathsf{ProbeBundle}$.

For the classifier field, accept a row exactly when such a finite ledger connects the two visible projection endpoints after endpoint $\hsame$ transport. Stability follows by transporting the endpoints first and then reusing the same tagged move probes over the transported boundary.

The ledger field records the tagged move list. The core theorem list consists of the empty-ledger row, the reverse-ledger row, and the concatenation row, giving reflexivity, symmetry, and transitivity of the classifier. Exactness states that every accepted classifier row has one of these finite ledger presentations; the standard bridge field is none, and the status field is a paper obligation.
\end{proof}

\begin{theorem}[KnotUp empty Reidemeister ledger reflexivity]\label{thm:knot-reidemeister-empty-ledger-reflexivity}
For every $\KnotUp$ diagram packet, the empty finite $\mathsf{ProbeBundle}$ Reidemeister ledger over its displayed $\SOneUp$ endpoints and ambient $\HomotopyUp$ row supplies the $\KnotUp$ classifier row from the packet to itself.
\end{theorem}

\begin{proof}
Project the packet to its visible boundary: the two $\SOneUp$ endpoint rows, the ambient $\HomotopyUp$ row, the packet provenance in $\Pkg$, and the hidden diagram data carried by $\Cont$. These are exactly the endpoint fields read by the classifier obligation of \autoref{thm:knot-reidemeister-move-classifier-obligation}.

Choose the empty $\mathsf{ProbeBundle}$ ledger. It has the same starting and ending endpoint boundary, so the endpoint $\hsame$ transport is the identity row and no hidden move witness is introduced.

Applying \autoref{thm:knot-reidemeister-move-classifier-obligation} to this boundary and empty ledger gives the accepted classifier row from the displayed packet back to itself. The ledger exactness surface is the empty presentation named in \autoref{thm:knot-ambient-isotopy-ledger-exactness}.
\end{proof}

\begin{theorem}[KnotUp reversed Reidemeister ledger symmetry]\label{thm:knot-reidemeister-reversal-ledger-symmetry}
If a finite $\mathsf{ProbeBundle}$ Reidemeister ledger over the displayed $\SOneUp$ endpoints and ambient $\HomotopyUp$ row supplies an accepted $\KnotUp$ classifier row from one diagram packet to another, then the reversed finite ledger supplies the opposite classifier row over the same visible endpoint data and the same $\Pkg$ scope.
\end{theorem}

\begin{proof}
Start with the accepted classifier row and read it through \autoref{thm:knot-reidemeister-move-classifier-obligation}. The row exposes a finite tagged Reidemeister ledger, endpoint $\hsame$ transport, the shared $\SOneUp$ endpoint source rows, and the ambient $\HomotopyUp$ row.

Reverse the finite ledger by reversing the order of its $\mathsf{ProbeBundle}$ entries and replacing each Reidemeister probe with the same move read in the opposite direction. The endpoints are unchanged as visible BEDC rows: the former target boundary becomes the source boundary, the former source boundary becomes the target boundary, and the $\Pkg$ provenance remains the same package scope.

The reversed ledger is therefore a finite presentation over the same visible endpoints. Applying \autoref{thm:knot-reidemeister-move-classifier-obligation} again gives the opposite classifier row, and \autoref{thm:knot-ambient-isotopy-ledger-exactness} records that no extra ambient-isotopy witness is admitted beyond that finite reversal.
\end{proof}

\begin{theorem}[KnotUp concatenated Reidemeister ledger transitivity]\label{thm:knot-reidemeister-concat-ledger-transitivity}
If one accepted $\KnotUp$ classifier row is carried by a finite Reidemeister ledger from a first diagram packet to a middle packet, and a second accepted row is carried by a finite Reidemeister ledger from that middle packet to a third packet, then the concatenated $\mathsf{ProbeBundle}$ ledger supplies a classifier row from the first packet to the third.
\end{theorem}

\begin{proof}
Read the two accepted rows through \autoref{thm:knot-reidemeister-move-classifier-obligation}. The first row supplies a finite ledger from the first boundary to the middle boundary, and the second supplies a finite ledger from the middle boundary to the third boundary.

Use the $\Cont$ and $\Pkg$ provenance of the middle packet to identify the two displayed middle boundaries as the same BEDC boundary data. The shared $\SOneUp$ endpoint rows and the shared ambient $\HomotopyUp$ row give the endpoint compatibility needed before the ledgers can be joined.

Append the two finite $\mathsf{ProbeBundle}$ ledgers. The appended ledger starts at the first packet boundary, passes through the shared middle boundary, and ends at the third packet boundary, while preserving every tagged Reidemeister probe already accepted in the two input rows.

Applying \autoref{thm:knot-reidemeister-move-classifier-obligation} to the appended ledger gives the composite classifier row. Exactness is inherited from \autoref{thm:knot-ambient-isotopy-ledger-exactness}: the accepted composite row is represented precisely by the concatenated finite Reidemeister ledger over the displayed endpoints.
\end{proof}

\begin{theorem}[KnotUp Homotopy source obligation]\label{thm:knot-homotopy-source-obligation}
Every ambient-isotopy row consumed by the $\KnotUp$ certificate factors through the displayed $\NameCert_{\HomotopyUp}$ source, and it consumes only endpoints supplied by the $\SOneUp$ carrier boundary.
\end{theorem}

\begin{proof}
The BEDC source field is the pair of source certificates $\NameCert_{\SOneUp}$ and $\NameCert_{\HomotopyUp}$. The carrier field is the knot packet whose source boundary exposes the circle endpoints and whose ambient boundary exposes the homotopy row.

Factor the ambient row through $\NameCert_{\HomotopyUp}$ before it is used by any Reidemeister ledger. The endpoint checks are then read from the $\SOneUp$ carrier boundary, so the homotopy row cannot introduce a new endpoint source or an untracked ambient endpoint.

The classifier and stability fields are inherited from the factorized homotopy row and the endpoint $\hsame$ transport. The ledger field records only the homotopy source witness and the endpoint boundary witnesses; exactness says that these are the only inputs consumed by the ambient-isotopy row. The standard bridge field is none, and the status field is a paper obligation.
\end{proof}

\begin{theorem}[KnotUp SOne boundary ledger]\label{thm:knot-sone-boundary-ledger}
Every diagram endpoint, arc endpoint, and crossing endpoint used by a $\KnotUp$ packet has an $\SOneUp$ boundary source. The boundary ledger records the hidden projection and crossing data while exposing only the $\SOneUp$ endpoint rows and the ambient $\HomotopyUp$ row.
\end{theorem}

\begin{proof}
The BEDC source field is the displayed $\SOneUp$ boundary together with the ambient $\HomotopyUp$ boundary. The carrier field is the knot packet with diagram endpoints, arc endpoints, crossing endpoints, hidden projection data, and hidden crossing data.

For each endpoint kind, choose its boundary witness from the $\SOneUp$ carrier row. The classifier field then reads endpoint compatibility through those source witnesses, while the stability field transports them by $\hsame$ and leaves hidden projection and crossing witnesses inside the finite ledger.

The ledger field is the list of endpoint witnesses plus the hidden projection and crossing records. The core theorem list is the diagram-endpoint, arc-endpoint, and crossing-endpoint boundary rows. Exactness states that no endpoint used by the packet is outside the $\SOneUp$ source boundary; the standard bridge field is none, and the status field is a paper obligation.
\end{proof}

\begin{theorem}[KnotUp ambient-isotopy ledger exactness]\label{thm:knot-ambient-isotopy-ledger-exactness}
If two knot packets are related by the $\KnotUp$ classifier, then they have compatible visible $\SOneUp$ endpoints and compatible visible $\HomotopyUp$ endpoints, and a finite Reidemeister ledger over those same visible endpoints supplies the accepted classifier row.
\end{theorem}

\begin{proof}
The BEDC source field is the pair of endpoint sources from $\NameCert_{\SOneUp}$ and $\NameCert_{\HomotopyUp}$. The carrier field is the two knot packets together with their displayed boundaries, and the classifier field is the accepted finite Reidemeister ledger from \autoref{thm:knot-reidemeister-move-classifier-obligation}.

Project the accepted classifier row to its endpoint boundary. The $\SOneUp$ projection gives compatible circle endpoints, and the $\HomotopyUp$ projection gives compatible ambient endpoints; both projections use the same visible endpoints as the finite Reidemeister ledger.

The stability field is endpoint $\hsame$ transport, and the ledger field is the shared finite Reidemeister ledger. The core theorem list is projection stability, the Reidemeister classifier, homotopy source factorization, and the $\SOneUp$ boundary ledger. Exactness says that the accepted classifier row contains exactly those visible endpoints and that ledger; the standard bridge field is none, and the status field is a paper obligation.
\end{proof}

\begin{theorem}[KnotUp endpoint source exhaustion]\label{thm:knot-endpoint-source-exhaustion}
For every $\KnotUp$ diagram packet $\mathcal{K}$ of
\autoref{def:knot-diagram-bhist-carrier}, every endpoint row appearing as a
diagram endpoint, arc endpoint, crossing endpoint, or Reidemeister-move
endpoint factors through the displayed $\SOneUp$ source row and the ambient
$\HomotopyUp$ row. The public packet has no host embedding endpoint source
and no undecomposed ambient-isotopy endpoint source outside those two rows.
\end{theorem}

\begin{proof}
Project $\mathcal{K}$ to its source field $\mathcal{S}$, ambient field
$\mathcal{A}$, endpoint rows $e_0,e_1$, Reidemeister trace $r$, HomotopyUp
row $h$, provenance row $\rho$, and finite ledger $\lambda$ as displayed in
\autoref{def:knot-diagram-bhist-carrier}. These projections are the only
places where endpoint data enter the packet.

For diagram endpoints, arc endpoints, and crossing endpoints, apply
\autoref{thm:knot-sone-boundary-ledger}. It supplies an $\SOneUp$ boundary
source for each endpoint kind and leaves hidden projection or crossing data
inside the finite ledger rather than in a separate source object.

For endpoints consumed by Reidemeister moves, first read the finite
$\mathsf{ProbeBundle}$ move ledger from
\autoref{thm:knot-reidemeister-move-classifier-obligation}. Then apply
\autoref{thm:knot-homotopy-source-obligation} to the ambient row used by that
ledger. The ambient row factors through $\NameCert_{\HomotopyUp}$ and consumes
only endpoints already supplied by the $\SOneUp$ carrier boundary.

Thus each endpoint row factors through the displayed $\SOneUp$ and
$\HomotopyUp$ sources, with package provenance recorded by $\rho$ and with
all remaining witnesses carried by $\lambda$. No host embedding source or
primitive ambient-isotopy source remains available to the public packet.
\end{proof}
\leanchecked{BEDC.Derived.KnotUp.KnotDiagramPacket\_endpoint\_source\_exhaustion}

\begin{theorem}[KnotUp Reidemeister ledger composition closure]\label{thm:knot-reidemeister-ledger-composition-closure}
Let two accepted finite $\mathsf{ProbeBundle}$ Reidemeister ledgers over
$\KnotUp$ packets have matching visible endpoint rows after the endpoint
$\hsame$ transports required by
\autoref{def:knot-reidemeister-ledger-classifier}. Their
$\mathsf{Cont}$ concatenation is again an accepted $\KnotUp$ classifier
ledger over the same public source and ambient rows, and the empty ledger is
the unit accepted classifier row.
\end{theorem}

\begin{proof}
Apply \autoref{thm:knot-reidemeister-move-classifier-obligation} to the first
accepted ledger. It presents the classifier row as a finite
$\mathsf{ProbeBundle}$ list whose entries are Reidemeister I, II, or III moves
together with endpoint $\hsame$ transport.

Apply the same theorem to the second accepted ledger. The hypothesis that the
visible endpoints match supplies the endpoint transport needed to place the
second list after the first one without changing the displayed $\SOneUp$ and
$\HomotopyUp$ boundary rows.

Concatenate the two finite lists by the $\mathsf{Cont}$ ledger operation.
Each entry is still one of the accepted Reidemeister probe rows, and the
middle endpoint is discharged by the supplied $\hsame$ transport. Therefore
\autoref{def:knot-reidemeister-ledger-classifier} accepts the concatenated
ledger as a classifier row.

For the unit, take the empty finite $\mathsf{ProbeBundle}$ list. The empty
ledger has the same visible endpoints on both sides and is the reflexive row
named by \autoref{thm:knot-reidemeister-move-classifier-obligation}, so it is
accepted and acts as the $\mathsf{Cont}$ unit.
\end{proof}

\begin{theorem}[KnotUp classifier ledger completeness]\label{thm:knot-classifier-ledger-completeness}
Every accepted $\KnotUp$ classifier row is exactly a finite ledger generated
by endpoint $\hsame$ transport and Reidemeister I, II, and III
$\mathsf{ProbeBundle}$ rows. Its source and ambient endpoints are the visible
endpoints of \autoref{thm:knot-ambient-isotopy-ledger-exactness}, and every
finite ledger with those generators repacks as an accepted classifier row of
\autoref{def:knot-reidemeister-ledger-classifier}.
\end{theorem}

\begin{proof}
For the forward direction, start from an accepted classifier row. Project it
through \autoref{thm:knot-ambient-isotopy-ledger-exactness}; the result has
compatible visible $\SOneUp$ endpoints, compatible visible $\HomotopyUp$
endpoints, and a finite Reidemeister ledger over those same endpoints.

Next apply \autoref{thm:knot-reidemeister-move-classifier-obligation}. The
accepted ledger is generated by endpoint $\hsame$ transport and
Reidemeister I, II, and III $\mathsf{ProbeBundle}$ rows. The exhaustion result
\autoref{thm:knot-endpoint-source-exhaustion} identifies the endpoint sources
with the displayed $\SOneUp$ and $\HomotopyUp$ rows.

For the reverse direction, assume such a finite generated ledger over the
visible source and ambient endpoints. Place the endpoint transports, move
probes, provenance row, and continuation ledger into the clauses of
\autoref{def:knot-reidemeister-ledger-classifier}.

The classifier definition accepts exactly those component rows, so the
repacked finite ledger is an accepted $\KnotUp$ classifier row. This gives
both directions and leaves no additional quotient or ambient-isotopy
primitive in the classifier surface.
\end{proof}

\begin{theorem}[KnotUp NameCert field coverage]\label{thm:knot-namecert-field-coverage}
The public $\NameCert_{\KnotUp}$ carrier, classifier, stability, ledger, and
exactness fields are covered by
\autoref{def:knot-diagram-bhist-carrier},
\autoref{def:knot-reidemeister-ledger-classifier},
\autoref{thm:knot-sone-source-boundary},
\autoref{thm:knot-homotopy-ledger-boundary},
\autoref{thm:knot-namecert-obligation-surface},
\autoref{thm:knot-projection-stability-obligation},
\autoref{thm:knot-reidemeister-move-classifier-obligation},
\autoref{thm:knot-homotopy-source-obligation},
\autoref{thm:knot-sone-boundary-ledger},
\autoref{thm:knot-ambient-isotopy-ledger-exactness},
\autoref{thm:knot-endpoint-source-exhaustion},
\autoref{thm:knot-reidemeister-ledger-composition-closure}, and
\autoref{thm:knot-classifier-ledger-completeness}. Downstream consumers may
cite these rows without assuming a knot quotient, host embedding equality, or
external ambient-isotopy primitive.
\end{theorem}

\begin{proof}
Enumerate the public certificate surface in the ten-field roadmap form. The
BEDC source field is the pair of consumed $\NameCert_{\SOneUp}$ and
$\NameCert_{\HomotopyUp}$ packets; the carrier field is
\autoref{def:knot-diagram-bhist-carrier}; and the classifier field is
\autoref{def:knot-reidemeister-ledger-classifier}.

The stability field is supplied by
\autoref{thm:knot-projection-stability-obligation} and by the endpoint
$\hsame$ transport in
\autoref{thm:knot-reidemeister-move-classifier-obligation}. The ledger field
is the finite $\mathsf{Cont}$ and $\mathsf{ProbeBundle}$ surface identified by
\autoref{thm:knot-homotopy-ledger-boundary},
\autoref{thm:knot-reidemeister-ledger-composition-closure}, and
\autoref{thm:knot-classifier-ledger-completeness}.

The source-boundary and endpoint-coverage fields are
\autoref{thm:knot-sone-source-boundary},
\autoref{thm:knot-homotopy-source-obligation},
\autoref{thm:knot-sone-boundary-ledger}, and
\autoref{thm:knot-endpoint-source-exhaustion}. The exactness field is
\autoref{thm:knot-ambient-isotopy-ledger-exactness} together with the
classifier completeness theorem. The standard bridge field is none, and the
status field is the public paper surface described by
\autoref{thm:knot-namecert-obligation-surface}.

Every item in the roadmap is therefore a displayed BEDC row or a theorem
about those displayed rows. Repacking those rows gives the public
$\NameCert_{\KnotUp}$ coverage surface and supplies downstream knot-facing
work with citations that do not import a knot quotient, host embedding
equality, or external ambient-isotopy primitive.
\end{proof}

\begin{definition}[KnotUp downstream consumer boundary packet]\label{def:knot-consumer-boundary-packet}
For an accepted $\KnotUp$ diagram packet $\mathcal{K}$ of
\autoref{def:knot-diagram-bhist-carrier}, its downstream consumer boundary
packet is the finite BEDC row family
$$
\mathsf{KnotConsumer}(\mathcal{K})
$$
consisting of the projected $\SOneUp$ source packet $\mathcal{S}$ and its
endpoint rows, the ambient $\HomotopyUp$ target and deformation rows, the two
endpoint $\mathsf{BHist}$ rows, the finite Reidemeister
$\mathsf{ProbeBundle}$ ledger, the finite $\mathsf{Cont}$ continuation
ledger, and the $\mathsf{Pkg}$ provenance row linking all of these rows in the
same package scope. The packet exposes only these rows and the public
classifier surface of \autoref{def:knot-reidemeister-ledger-classifier}.
\end{definition}

\begin{theorem}[KnotUp consumer boundary extraction]\label{thm:knot-consumer-boundary-extraction}
Every accepted $\KnotUp$ diagram packet projects to exactly the downstream
consumer boundary packet of
\autoref{def:knot-consumer-boundary-packet}. The projection contains the
visible $\SOneUp$ source rows, ambient $\HomotopyUp$ rows, endpoint family,
finite Reidemeister $\mathsf{ProbeBundle}$ ledger, finite $\mathsf{Cont}$
ledger, and $\mathsf{Pkg}$ provenance, and it contains no additional host
embedding equality, knot quotient, or undecomposed ambient-isotopy primitive.
\end{theorem}

\begin{proof}
Start with an accepted diagram packet $\mathcal{K}$ and project its carrier
fields through \autoref{def:knot-diagram-bhist-carrier}. This gives the
displayed source packet, ambient packet, endpoint rows, crossing ledger,
Reidemeister trace, deformation row, continuation ledger, and provenance row.

The certificate field coverage theorem
\autoref{thm:knot-namecert-field-coverage} identifies these same carrier and
classifier fields as the public $\NameCert_{\KnotUp}$ surface. The source and
ambient boundary theorems then place the visible source and deformation rows
in the same finite row family.

Repack the projected rows in the order named by
\autoref{def:knot-consumer-boundary-packet}. Since every listed component is a
carrier field or a field-coverage projection, the extracted family is exactly
the consumer boundary packet and no hidden host datum is available to add.
\end{proof}

\begin{theorem}[KnotUp consumer classifier determinacy]\label{thm:knot-consumer-classifier-determinacy}
If two accepted $\KnotUp$ classifier rows have the same downstream consumer
boundary packet, then they have the same public classifier surface. In
particular, their visible endpoint transports agree by $\hsame$, and their
Reidemeister and continuation ledgers agree as the finite ledger surface
specified by \autoref{thm:knot-classifier-ledger-completeness}.
\end{theorem}

\begin{proof}
Assume two accepted classifier rows share the same consumer boundary packet.
The shared packet identifies the projected $\SOneUp$ endpoint family and the
ambient $\HomotopyUp$ rows, so the endpoint transports used by the classifier
are the same $\hsame$ rows.

Apply \autoref{thm:knot-classifier-ledger-completeness} to each classifier
row. Both rows decompose into finite ledgers generated by endpoint $\hsame$
transport and Reidemeister I, II, and III $\mathsf{ProbeBundle}$ rows over the
visible endpoints supplied by the shared packet.

The shared $\mathsf{ProbeBundle}$ and $\mathsf{Cont}$ ledgers therefore give
the same generator list and the same package provenance. Repacking those
generators through \autoref{def:knot-reidemeister-ledger-classifier} yields
the same public classifier surface for both accepted rows.
\end{proof}

\begin{theorem}[KnotUp consumer continuation composition]\label{thm:knot-consumer-cont-composition}
Composable downstream consumer boundary packets compose by concatenating their
finite $\mathsf{Cont}$ continuation ledgers and their finite Reidemeister
$\mathsf{ProbeBundle}$ ledgers. The composed packet preserves the endpoint
source exhaustion of \autoref{thm:knot-endpoint-source-exhaustion} and remains
accepted by the classifier composition theorem
\autoref{thm:knot-reidemeister-ledger-composition-closure}.
\end{theorem}

\begin{proof}
Take two consumer boundary packets whose target endpoint family of the first
matches the source endpoint family of the second. The shared middle endpoint
is one of the projected $\SOneUp$ and $\HomotopyUp$ rows named by the packets,
so \autoref{thm:knot-endpoint-source-exhaustion} supplies the same source
identification on both sides.

Concatenate the two finite $\mathsf{Cont}$ ledgers and concatenate the two
finite Reidemeister $\mathsf{ProbeBundle}$ ledgers. The package provenance
rows are composable because both packets expose the same middle endpoint and
ambient scope.

Finally apply
\autoref{thm:knot-reidemeister-ledger-composition-closure}. It accepts exactly
this concatenated ledger as a classifier row, while the endpoint-source
exhaustion theorem keeps the visible source rows fixed at the composed
boundary. Repacking the rows gives the composed consumer boundary packet.
\end{proof}

\closureat{KnotUp}{seedStr}[BEDC.Derived.KnotUp.KnotDiagramPacket\_namecert\_obligation\_surface]

\begin{closurestatus}{\KnotUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope covers the $\SOneUp$ source packet, ambient target row, Reidemeister trace, $\HomotopyUp$ deformation row, endpoint rows, $\Pkg$ provenance, and finite $\Cont$ ledger of the displayed knot packet.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.KnotUp.KnotDiagramPacket\_namecert\_obligation\_surface}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient-isotopy quotients, host knot types, or general knot invariants beyond the displayed finite certificate rows.}
  \upgradepath{Obligation closure requires a complete enumeration of the Reidemeister, endpoint, deformation, classifier, and downstream consumer rows.}
\end{closurestatus}
