\chapter{A Concrete Naming Certificate for $\JonesPolynomialUp$}
\label{ch:concrete-instances-jonespolynomial-namecert}

The Jones-polynomial interface $\JonesPolynomialUp$ packages the Laurent polynomial knot invariant in $\mathbb{Z}[t^{1/2}, t^{-1/2}]$ defined by the skein relation. It depends on $\NameCert_{\KnotUp}$ (\autoref{ch:concrete-instances-knot-namecert}) and $\NameCert_{\PolynomialUp}$ (\autoref{ch:concrete-instances-polynomial-namecert}).

\section{Carrier definition}
\label{sec:jonespolynomial-carrier}

\section{The certificate}
\label{sec:jonespolynomial-certificate}

\begin{definition}[JonesPolynomial skein ledger packet]
\label{def:jonespolynomial-skein-ledger-packet}
A $\JonesPolynomialUp$ skein ledger packet is a finite BEDC row family
$$
\mathcal{J}=(\mathcal{K},\mathcal{K}_+,\mathcal{K}_-,\mathcal{K}_0,J,\sigma,\rho,\lambda)
$$
with the following visible fields.
\begin{enumerate}
  \item $\mathcal{K}$ is an accepted $\KnotUp$ diagram packet of
  \autoref{def:knot-diagram-bhist-carrier}; it is the diagram row whose
  polynomial endpoint is being named.
  \item $\mathcal{K}_+$, $\mathcal{K}_-$, and $\mathcal{K}_0$ are accepted
  $\KnotUp$ diagram packets over the same displayed $\SOneUp$ source,
  ambient $\HomotopyUp$ row, endpoint family, and $\Pkg$ scope, except for
  one local skein window tagged respectively as the positive crossing,
  negative crossing, and oriented smoothing boundary row.
  \item $J$ is a Laurent-polynomial endpoint row whose underlying normalized
  finite coefficient row is accepted by $\NameCert_{\PolynomialUp}$ through
  \autoref{def:polynomial-carrier},
  \autoref{def:polynomial-classifier-specification}, and
  \autoref{def:polynomial-certificate-obligations}. The Laurent bookkeeping is
  carried as displayed endpoint data and is not read as host polynomial
  equality.
  \item $\sigma$ is a finite $\Bundle$-indexed skein ledger. Each entry names
  one local skein face, the three $\KnotUp$ boundary rows
  $\mathcal{K}_+,\mathcal{K}_-,\mathcal{K}_0$, the endpoint row $J$, the
  polynomial classifier rows consumed at that face, and the $\KnotUp$
  classifier rows showing that Reidemeister transport of the surrounding
  diagram commutes with reading the same local face.
  \item $\rho$ records the shared $\Pkg$ provenance of the four knot packets,
  the polynomial endpoint, and the finite skein ledger. The continuation
  ledger $\lambda$ lists exactly the $\Cont$, $\hsame$, $\Bundle$,
  polynomial-classifier, knot-classifier, and exactness rows accepted by the
  public $\JonesPolynomialUp$ surface.
\end{enumerate}
The packet exports only these rows. It does not export a host knot quotient,
external diagram equality, or a complete Jones-polynomial invariant beyond the
supplied finite skein ledger.
\end{definition}

\begin{definition}[JonesPolynomial skein ledger classifier]
\label{def:jonespolynomial-skein-ledger-classifier}
Two packets
$\mathcal{J}=(\mathcal{K},\mathcal{K}_+,\mathcal{K}_-,\mathcal{K}_0,J,\sigma,\rho,\lambda)$
and
$\mathcal{J}'=(\mathcal{K}',\mathcal{K}'_+,\mathcal{K}'_-,\mathcal{K}'_0,J',\sigma',\rho',\lambda')$
of \autoref{def:jonespolynomial-skein-ledger-packet} are related by
$\mathsf{JonesSkeinCls}$ when the following finite rows are supplied.
\begin{enumerate}
  \item The main diagram rows $\mathcal{K}$ and $\mathcal{K}'$ are related by
  the $\KnotUp$ Reidemeister ledger classifier of
  \autoref{def:knot-reidemeister-ledger-classifier}.
  \item The three skein boundary pairs
  $(\mathcal{K}_+,\mathcal{K}'_+)$, $(\mathcal{K}_-,\mathcal{K}'_-)$, and
  $(\mathcal{K}_0,\mathcal{K}'_0)$ are related by the same $\KnotUp$
  classifier surface, with matching local-window tags and the same transported
  endpoint rows.
  \item The polynomial endpoints $J$ and $J'$ are related by the normalized
  structural classifier of $\NameCert_{\PolynomialUp}$ from
  \autoref{def:polynomial-classifier-specification}, with stability read
  through \autoref{def:polynomial-stability-certificate}.
  \item The ledgers $\sigma$ and $\sigma'$ are matched by finite $\Bundle$
  induction: empty skein ledgers compare, and a cons step compares the
  displayed local skein face after applying the four $\KnotUp$ transports and
  the $\PolynomialUp$ endpoint classifier row.
  \item The provenance rows $\rho,\rho'$ and continuation ledgers
  $\lambda,\lambda'$ list exactly the transported rows above and no further
  host-level witness.
\end{enumerate}
\end{definition}

\begin{lemma}[JonesPolynomial skein ledger Reidemeister transport]
\label{lem:jonespolynomial-skein-ledger-reidemeister-transport}
Let $\mathcal{J}$ be a $\JonesPolynomialUp$ skein ledger packet. Transport
$\mathcal{K}$ and the three boundary rows
$\mathcal{K}_+,\mathcal{K}_-,\mathcal{K}_0$ by accepted finite $\KnotUp$
Reidemeister ledgers whose displayed endpoint transports preserve the local
skein window. Transport the endpoint $J$ by an accepted $\PolynomialUp$
classifier row. Then the transported rows repack as a $\JonesPolynomialUp$
skein ledger packet $\mathcal{J}'$, and
$\mathsf{JonesSkeinCls}(\mathcal{J},\mathcal{J}')$ holds.
\end{lemma}
\begin{proof}
Project the four knot rows of $\mathcal{J}$ to downstream consumer boundary
packets by \autoref{thm:knot-consumer-boundary-extraction}. Each projection
contains exactly the displayed $\SOneUp$ source rows, ambient $\HomotopyUp$
rows, finite Reidemeister $\Bundle$ ledger, finite $\Cont$ ledger, and
$\Pkg$ provenance.

Apply \autoref{thm:knot-reidemeister-ledger-composition-closure} to compose
any Reidemeister transport already present in the packet with the supplied
transport ledgers. Then apply \autoref{thm:knot-classifier-ledger-completeness}
to read the result again as a finite ledger generated by endpoint $\hsame$
transport and Reidemeister move rows. The hypothesis that the local skein
window is preserved identifies the positive, negative, and smoothing tags after
transport, so every skein face in $\sigma$ has a transported face over the
same displayed boundary pattern.

The polynomial endpoint transport is accepted by the normalized structural
classifier of \autoref{def:polynomial-classifier-specification}; the stability
rows of \autoref{def:polynomial-stability-certificate} keep the endpoint
inside the $\PolynomialUp$ carrier. Induct over the finite $\Bundle$ ledger
$\sigma$. The empty ledger transports to the empty ledger. In the cons case,
the head face is transported by the four knot classifier rows and the
polynomial endpoint classifier row, while the induction hypothesis transports
the remaining finite ledger.

Collecting the transported skein faces gives a finite ledger $\sigma'$. The
transported provenance and continuation rows give $\rho'$ and $\lambda'$.
These fields satisfy the clauses of
\autoref{def:jonespolynomial-skein-ledger-packet}, and the same construction
is exactly the classifier relation of
\autoref{def:jonespolynomial-skein-ledger-classifier}.
\end{proof}

\begin{theorem}[JonesPolynomial skein ledger obligation surface]
\label{thm:jonespolynomial-skein-ledger-obligation-surface}
Let $\mathcal{J}$ be a $\JonesPolynomialUp$ skein ledger packet of
\autoref{def:jonespolynomial-skein-ledger-packet}. Assume its finite skein
ledger is compatible with Reidemeister transport in the sense of
\autoref{lem:jonespolynomial-skein-ledger-reidemeister-transport}. Then the
finite row family consisting of the main $\KnotUp$ diagram row, the three
skein-related $\KnotUp$ boundary rows, the $\PolynomialUp$ Laurent-polynomial
endpoint row, the finite $\Bundle$ skein ledger, the shared $\Pkg$ provenance,
the finite $\Cont$ continuation ledger, and the classifier
$\mathsf{JonesSkeinCls}$ forms an accepted carrier/classifier surface for
$\NameCert_{\JonesPolynomialUp}$ over those rows.

The exactness boundary of this surface is the displayed packet itself: every
accepted $\JonesPolynomialUp$ row projects to those listed fields, and every
listed field repacks into the same packet. No full Jones-polynomial invariant,
unknot normalization, global skein recursion, host polynomial quotient, or
external ambient-isotopy primitive is part of this obligation surface.
\end{theorem}
\begin{proof}
Start with the packet fields displayed in
\autoref{def:jonespolynomial-skein-ledger-packet}. The main diagram row and
the three skein boundary rows are accepted $\KnotUp$ packets, so
\autoref{thm:knot-consumer-boundary-extraction} exposes their public boundary
packets and \autoref{thm:knot-consumer-classifier-determinacy} fixes the
classifier surface read by any downstream consumer.

The endpoint $J$ is accepted by the polynomial carrier and classifier rows of
\autoref{def:polynomial-carrier},
\autoref{def:polynomial-classifier-specification}, and
\autoref{def:polynomial-certificate-obligations}. Thus the polynomial side of
the surface is a normalized finite coefficient endpoint carried by
$\NameCert_{\PolynomialUp}$, with the Laurent tags retained only as displayed
endpoint data.

The finite skein ledger $\sigma$ ties these two sides together. Each ledger
entry reads the same three $\KnotUp$ boundary rows, the same polynomial
endpoint row, and the same package provenance. By the Reidemeister transport
lemma, transporting the diagram and boundary rows through accepted $\KnotUp$
classifier ledgers transports the corresponding skein face and keeps the
polynomial endpoint inside the $\PolynomialUp$ classifier. Hence the surface
has a stable classifier, namely
\autoref{def:jonespolynomial-skein-ledger-classifier}.

For exactness, project an accepted surface row to its knot fields, polynomial
endpoint field, skein ledger, provenance row, and continuation ledger. These
are precisely the fields of
\autoref{def:jonespolynomial-skein-ledger-packet}. Conversely, given those
fields, the definition repacks them as a $\JonesPolynomialUp$ skein ledger
packet, and the classifier definition supplies the accepted comparison rows.
The public carrier/classifier surface is therefore exactly the supplied finite
skein-ledger row family and contains no additional invariant or bridge row.
\end{proof}

\begin{theorem}[JonesPolynomial skein endpoint classifier exhaustion]
\label{thm:jonespolynomial-skein-endpoint-classifier-exhaustion}
Every accepted $\mathsf{JonesSkeinCls}$ witness between skein ledger packets
$\mathcal{J}$ and $\mathcal{J}'$ projects exactly to the main $\KnotUp$ row, the
three skein-boundary $\KnotUp$ rows, the $\PolynomialUp$ endpoint classifier
row, the finite $\Bundle$ skein ledger, the shared $\Pkg$ provenance, and the
finite $\Cont$ continuation ledger displayed in
\autoref{def:jonespolynomial-skein-ledger-classifier}. Conversely, any finite
row family with precisely those fields repacks as the same
$\mathsf{JonesSkeinCls}$ witness.

Thus endpoint readback for $\JonesPolynomialUp$ is exhausted by generated
classifier data: the endpoint comparison reads the listed knot, polynomial,
ledger, provenance, and continuation rows, not host Laurent-polynomial equality
or a knot quotient.
\end{theorem}
\begin{proof}
Project an accepted classifier witness by the constructor clauses of
\autoref{def:jonespolynomial-skein-ledger-classifier}. The first four clauses
give the main $\KnotUp$ row, the three skein-boundary $\KnotUp$ rows, the
$\PolynomialUp$ endpoint classifier row, and the finite $\Bundle$ ledger
comparison.

For the ledger component, induct over the finite $\Bundle$ skein ledger. The
empty ledger projects to the empty displayed row family. In the cons step, the
head face projects to its four knot classifier rows and its polynomial endpoint
classifier row, while the induction hypothesis projects the tail ledger.

Apply
\autoref{lem:jonespolynomial-skein-ledger-reidemeister-transport} at each head
face to keep Reidemeister transport inside the same local skein window. The
polynomial classifier specification from
\autoref{def:polynomial-classifier-specification} keeps the Laurent endpoint
readback inside $\NameCert_{\PolynomialUp}$.

The final classifier clauses project the shared $\Pkg$ provenance and finite
$\Cont$ continuation ledger. These are exactly the rows listed in the theorem
statement, and no further host witness is present in the classifier definition.

Conversely, given the listed rows, rebuild the witness by the same constructor
clauses. The finite $\Bundle$ ledger is rebuilt by the empty and cons cases just
used in projection, the knot rows are accepted by their displayed
$\KnotUp$ classifier clauses, and the polynomial endpoint row is accepted by the
polynomial classifier specification. Repacking these fields gives precisely an
accepted $\mathsf{JonesSkeinCls}$ witness.
\end{proof}

\begin{theorem}[JonesPolynomial local skein-window composition]
\label{thm:jonespolynomial-local-skein-window-composition}
Let $\mathcal{J}_1$ and $\mathcal{J}_2$ be finite $\JonesPolynomialUp$ skein
ledger packets over $\mathsf{BHist}$ as in
\autoref{def:jonespolynomial-skein-ledger-packet}. Suppose the terminal local
skein-window row of $\mathcal{J}_1$ and the initial local skein-window row of
$\mathcal{J}_2$ are the same displayed $\KnotUp$ boundary row under $\hsame$,
and suppose the adjacent Laurent endpoints carry compatible $\PolynomialUp$
endpoint classifier rows. Then the finite $\Bundle$ skein ledgers of
$\mathcal{J}_1$ and $\mathcal{J}_2$ concatenate to a finite $\JonesPolynomialUp$
skein ledger packet whose classifier projects exactly to the two original
classifiers, the shared $\KnotUp$ boundary row, the compatible $\PolynomialUp$
endpoint row, the inherited $\Cont$ ledgers, and the shared $\Pkg$ provenance.

The composed packet is a local finite-window construction. It introduces no
host Laurent-polynomial equality, no knot quotient, and no global invariant row
beyond the displayed $\mathsf{BHist}$, $\mathsf{Bundle}$, $\hsame$, $\Cont$,
$\Pkg$, $\KnotUp$, and $\PolynomialUp$ data.
\end{theorem}
\begin{proof}
Unpack the two packets by
\autoref{def:jonespolynomial-skein-ledger-packet}. Each packet supplies four
visible $\KnotUp$ rows, one $\PolynomialUp$ endpoint row, a finite
$\Bundle$ skein ledger, a $\Pkg$ provenance row, and a finite $\Cont$
continuation ledger.

Concatenate the two finite $\Bundle$ skein ledgers at the shared boundary face.
The hypothesis identifies that face as the same displayed $\KnotUp$ local-window
row under $\hsame$, and the compatible $\PolynomialUp$ endpoint classifier row
gives the polynomial endpoint comparison needed at the join.

Apply
\autoref{lem:jonespolynomial-skein-ledger-reidemeister-transport} to the shared
boundary face. The Reidemeister transport stays inside the same local skein
window, so the concatenated ledger still has the positive, negative, and
smoothing boundary rows required by
\autoref{def:jonespolynomial-skein-ledger-packet}.

The provenance rows and continuation ledgers concatenate as finite $\Pkg$ and
$\Cont$ rows over the same public source certificates. Repacking these fields
therefore gives a $\JonesPolynomialUp$ skein ledger packet.

Finally apply
\autoref{thm:jonespolynomial-skein-endpoint-classifier-exhaustion}. The
classifier of the composed packet projects exactly to the two original
classifier surfaces plus the shared boundary row and the compatible polynomial
endpoint row. Since endpoint exhaustion lists no host polynomial equality or
knot quotient, the composition does not introduce either one.
\end{proof}

\begin{theorem}[JonesPolynomial public NameCert obligation surface]
\label{thm:jonespolynomial-namecert-obligation-surface}
The public $\NameCert_{\JonesPolynomialUp}$ obligation surface consists exactly
of the skein ledger packet, skein classifier, Reidemeister transport row,
$\PolynomialUp$ endpoint classifier, $\KnotUp$ boundary rows, finite $\Bundle$
skein ledger, $\Cont$ ledger, and shared $\Pkg$ provenance displayed in this
section. It exports no full ambient-isotopy quotient, no host
Laurent-polynomial equality, and no complete-knot-invariant claim.
\end{theorem}
\begin{proof}
Start with the packet of
\autoref{def:jonespolynomial-skein-ledger-packet}. Its fields already list the
main knot diagram, the three skein boundary diagrams, the polynomial endpoint,
the finite skein ledger, the continuation ledger, and the shared provenance
row.

The classifier is
\autoref{def:jonespolynomial-skein-ledger-classifier}. It supplies the accepted
comparison rows for the knot faces, the polynomial endpoint, the ledger, and
the provenance component. The Reidemeister stability needed by that classifier
is exactly \autoref{lem:jonespolynomial-skein-ledger-reidemeister-transport}.

Apply
\autoref{thm:jonespolynomial-skein-ledger-obligation-surface}. That theorem
packages the displayed packet and classifier into the accepted finite
carrier/classifier surface for $\NameCert_{\JonesPolynomialUp}$ over the knot,
polynomial, bundle, continuation, and provenance rows.

Finally read the roadmap ten-field template field by field. Each required
public field is one of the rows just named, and every row in the public surface
projects back to the same packet. Hence the public NameCert obligation surface
is exactly the displayed skein-ledger construction, with no additional quotient,
host-polynomial equality, or invariant row.
\end{proof}

\begin{theorem}[JonesPolynomial skein classifier determinacy]
\label{thm:jonespolynomial-skein-classifier-determinacy}
Fix a $\JonesPolynomialUp$ skein ledger packet whose main $\KnotUp$ diagram row,
three skein boundary rows, $\PolynomialUp$ endpoint classifier row, finite
skein $\Bundle$, finite $\Cont$ ledger, and $\Pkg$ provenance are displayed as in
\autoref{def:jonespolynomial-skein-ledger-packet}. Then any accepted
$\mathsf{JonesSkeinCls}$ witness over those fixed rows determines the same
displayed $\JonesPolynomialUp$ endpoint row by $\hsame$ and $\Cont$ transport.
The determinacy is internal to the skein classifier surface and asserts no host
Laurent-polynomial equality, knot quotient, or complete invariant.
\end{theorem}
\begin{proof}
Start with two accepted $\mathsf{JonesSkeinCls}$ witnesses over the fixed packet
rows. The packet fixes the main knot diagram, positive crossing, negative
crossing, smoothing boundary rows, the polynomial endpoint row, the finite
skein bundle, the continuation ledger, and the provenance row.

Apply \autoref{lem:jonespolynomial-skein-ledger-reidemeister-transport}. The
Reidemeister row transports only the displayed $\KnotUp$ local-window boundary,
so both classifier witnesses read the same boundary diagrams through $\hsame$.

Next use \autoref{thm:jonespolynomial-skein-endpoint-classifier-exhaustion}. It
projects each accepted classifier witness exactly to the fixed knot rows, the
fixed polynomial endpoint classifier, the finite skein ledger, the $\Cont$
ledger, and the $\Pkg$ provenance.

Apply \autoref{thm:jonespolynomial-local-skein-window-composition} to the fixed
local window. The composition theorem keeps the skein bundle and the polynomial
endpoint comparison at the same displayed boundary, so the two classifier
readings cannot produce distinct displayed endpoint rows.

Finally cite \autoref{thm:jonespolynomial-namecert-obligation-surface}. The
public surface contains exactly these packet and classifier rows. Repacking the
exhausted rows therefore gives one $\JonesPolynomialUp$ endpoint row determined
by $\hsame$ and $\Cont$ transport.
\end{proof}

\begin{theorem}[JonesPolynomial skein boundary no-confusion]
\label{thm:jonespolynomial-skein-boundary-no-confusion}
Fix a $\mathsf{JonesSkeinCls}$ packet as in
\autoref{def:jonespolynomial-skein-ledger-packet}. An accepted classifier
witness cannot interchange the positive-crossing boundary row, the
negative-crossing boundary row, and the smoothing boundary row unless the
displayed local-window tag and the corresponding finite $\Bundle$ ledger row
are the same packet entry. The separation is internal to the skein ledger and
does not assert any host knot quotient or Laurent-polynomial equality.
\end{theorem}
\begin{proof}
Unpack the packet of
\autoref{def:jonespolynomial-skein-ledger-packet}. Its skein boundary fields
are three displayed local-window rows, each paired with its own tag and its own
position in the finite skein $\Bundle$ ledger.

Proceed by closed finite $\Bundle$ induction over the skein ledger. In the base
case there is no ledger row available, so no accepted classifier witness can
manufacture a boundary tag from outside the packet.

For the induction step, inspect the head ledger row. If the displayed tag is
the positive-crossing tag, the classifier reads the positive boundary entry and
the remaining bundle is handled by the induction hypothesis. The negative and
smoothing tag cases are identical, with their own displayed boundary entries.

Apply
\autoref{thm:jonespolynomial-skein-endpoint-classifier-exhaustion}. Every
accepted witness projects back to the fixed knot rows, the finite skein ledger,
the $\Cont$ ledger, and the $\Pkg$ provenance. Thus an attempted interchange
would require changing either the displayed local-window tag or the ledger row
selected by that tag.

The tag fields in
\autoref{def:jonespolynomial-skein-ledger-packet} are distinct packet
coordinates. Hence two boundary rows can be identified by an accepted witness
only when the displayed tag and the finite $\Bundle$ ledger row already agree
as the same coordinate of the fixed packet. No quotient of host knots and no
Laurent-polynomial equality is used.
\end{proof}

\begin{closurestatus}{\JonesPolynomialUp}
  \constructivestory{}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope is the finite skein ledger over $\mathsf{BHist}$, $\Cont$, $\hsame$, $\mathsf{Pkg}$, $\NameCert_{\KnotUp}$, $\NameCert_{\PolynomialUp}$, and $\NameCert_{\SOneUp}$ displayed by the carrier, classifier, transport, exhaustion, determinacy, and no-confusion blocks in this chapter.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a full Jones invariant, a quotient of diagrams, Reidemeister-complete standard model, standard bridge, or Lean verification target.}
  \upgradepath{Obligation closure requires a finite package for the skein classifier surface, including carrier, classifier, endpoint, exactness, ledger, and consumer rows.}
\end{closurestatus}
