\chapter{A Concrete Naming Certificate for $\TasteGateAdmissionUp$}
\label{ch:concrete-instances-tastegateadmission-namecert}
\origin{ai}

The $\TasteGateAdmissionUp$ packet is the concrete NameCert surface for admitting an AI-origin chapter into the BEDC horizon. It packages the candidate chapter identity, origin row, naming surface, chapter taste gate, event-flow witness, ground-compiler theorem references, transport rows, continuation routes, package provenance, and refusal ledger into one finite audit object.

\begin{definition}[TasteGateAdmission carrier]
\label{def:tastegate-admission-carrier}
A $\TasteGateAdmissionUp$ carrier is a finite $\BHist$ packet
$$
A=(X,O,N,T,E,R,H,C,P,G)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the candidate chapter identity row, recording the chapter label, local carrier name, and the paper site whose admission is being requested;
\item $O$ is the origin row, recording that the candidate enters through the AI-origin track rather than through inherited human-curated consensus;
\item $N$ is the visible $\NameCert$ surface proposed for the candidate chapter, including its carrier, classifier, pattern, ledger, and non-escape rows;
\item $T$ is the $\ChapterTasteGate$ witness row, recording the conservativity, no-hidden-input, round-trip, and layer-separation obligations exposed by the candidate;
\item $E$ is the event-flow witness row, displaying the finite $\GroundCompiler$ event-flow image from which the candidate tokens are read;
\item $R$ records the ground-compiler theorem references used by the witness, including the no-hidden-input, round-trip, and source-channel separation routes available to the admission check;
\item $H$ stores componentwise $\hsame$ transports for $X,O,N,T,E,R,C,P,G$;
\item $C$ records the displayed $\Cont$ routes by which the admission check reads the NameCert surface, the taste-gate witness, the event-flow witness, and the compiler reference row;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\NameCert$, $\ChapterTasteGate$, $\GroundCompiler$, event-flow witnesses, ground-compiler theorem references, $\hsame$, $\Cont$, and local naming;
\item $G$ is the GAP refusal ledger, recording failed admission attempts whose NameCert row, taste-gate row, event-flow row, compiler-reference row, transport row, continuation row, or provenance row is absent.
\end{enumerate}
The carrier has no coordinate for hidden prompt state, an oracle classifier, an unrecorded compiler theorem, host-side chapter approval, or a prose-only admission decision.
\end{definition}
\leanchecked{BEDC.Derived.TasteGateAdmissionUp.TasteGateAdmissionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[TasteGateAdmission NameCert obligations]
\label{thm:tastegate-admission-namecert-obligations}
For every accepted $\TasteGateAdmissionUp$ carrier
$$
A=(X,O,N,T,E,R,H,C,P,G),
$$
the local $\NameCert_{\TasteGateAdmissionUp}$ surface consists exactly of carrier admission for $A$, candidate identity through $X$, AI-origin exposure through $O$, candidate NameCert exposure through $N$, $\ChapterTasteGate$ exposure through $T$, event-flow exposure through $E$, ground-compiler reference exposure through $R$, componentwise transport through $H$, replay and admission routes through $C$, package provenance through $P$, and refused-case accounting through $G$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:tastegate-admission-carrier}. The packet exposes exactly the chapter identity, origin, NameCert surface, taste-gate witness, event-flow witness, compiler references, transport, continuation, provenance, and refusal rows.

The candidate and origin obligations are the rows $X$ and $O$. They identify the paper site being admitted and record that the admission is evaluated through the AI-origin track.

The naming and taste-gate obligations are the rows $N$ and $T$. A downstream reader can inspect the candidate's local NameCert surface and its four taste-gate obligations without importing a second chapter object outside the packet.

The compiler-facing obligations are the rows $E$ and $R$. They record the event-flow witness and the ground-compiler theorem references that make the taste-gate rows auditable.

Finally $H,C,P,G$ preserve the same admission object under transport, replay, provenance, and refused-case accounting. Since every admissible read is routed through those rows, the packet supplies the whole local $\NameCert_{\TasteGateAdmissionUp}$ surface and no hidden approval channel.
\end{proof}

\begin{theorem}[TasteGateAdmission ground compiler witnesses]
\label{thm:tastegate-admission-ground-compiler-witnesses}
In every accepted $\TasteGateAdmissionUp$ carrier, the $\ChapterTasteGate$ witness row $T$ is read only together with the event-flow row $E$ and the ground-compiler reference row $R$. Thus no-hidden-input, round-trip, and layer-separation claims are admitted only through displayed finite event-flow evidence and named compiler theorem references, not through an unrecorded semantic judgment about the candidate chapter.
\end{theorem}
\begin{proof}
Start from the carrier of \autoref{def:tastegate-admission-carrier}. The only taste-gate coordinate is $T$, and its compiler-facing evidence is displayed in $E$ and $R$.

The no-hidden-input and round-trip reads pass through $E$ before they can be consumed. The row $E$ is the finite event-flow witness, so the admission check sees the displayed compiler image rather than an external account of the candidate's tokens.

The layer-separation and compiler-reference reads pass through $R$. This row records the named ground-compiler theorem references used by the chapter-level witness.

Transport and replay are then carried by $H$ and $C$, with package provenance in $P$. These rows preserve the same witness surface and do not add an unrecorded compiler theorem or host-side approval step.
\end{proof}

\begin{theorem}[TasteGateAdmission non-escape]
\label{thm:tastegate-admission-non-escape}
Every accepted $\TasteGateAdmissionUp$ admission route factors through the finite rows
$$
(X,O,N,T,E,R,H,C,P,G).
$$
The route may export that the candidate chapter has an AI-origin admission packet with a displayed NameCert surface, $\ChapterTasteGate$ witness, ground-compiler witness, audit route, transport route, package provenance, GAP refusal ledger, and local naming data. It cannot export hidden prompt state, oracle approval, unlisted compiler facts, selected host semantics, or a chapter object not named by the packet.
\end{theorem}
\begin{proof}
Project an accepted admission route through the carrier. The route has access only to the ten displayed rows $X,O,N,T,E,R,H,C,P,G$.

Use \autoref{thm:tastegate-admission-namecert-obligations} to account for local naming, candidate identity, origin, taste-gate inspection, compiler evidence, replay, provenance, and refused-case accounting.

Use \autoref{thm:tastegate-admission-ground-compiler-witnesses} for the compiler-facing part. It keeps every taste-gate read attached to the finite event-flow witness and named compiler-reference rows.

Since the carrier has no coordinate for hidden prompt state, oracle approval, unlisted compiler facts, selected host semantics, or an unnamed chapter object, no exported admission route can supply one.
\end{proof}

\closureat{TasteGateAdmissionUp}{seedStr}

\begin{closurestatus}{\TasteGateAdmissionUp}
  \constructivestory{A $\TasteGateAdmissionUp$ packet is generated from a candidate chapter identity row, AI-origin row, candidate NameCert surface, ChapterTasteGate witness, event-flow witness, ground-compiler reference row, componentwise transport, continuation routes, package provenance, and GAP refusal ledger.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:tastegate-admission-carrier}, \autoref{thm:tastegate-admission-namecert-obligations}, \autoref{thm:tastegate-admission-ground-compiler-witnesses}, and \autoref{thm:tastegate-admission-non-escape} bind the seed carrier, local NameCert surface, ground-compiler witness rows, and non-escape boundary for AI-origin TasteGate admission.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove the candidate chapter's mathematical content, certify arbitrary host semantics, close bridge checking, or provide Lean verification for the admission packet.}
  \upgradepath{Obligation closure requires checked carrier, NameCert-surface, ground-compiler-witness, refusal-ledger, and non-escape theorems for the same finite admission packet.}
\end{closurestatus}
