\chapter{A Concrete Naming Certificate for $\GeneratorInductionSealUp$}
\label{ch:concrete-instances-generatorinductionseal-namecert}
\origin{ai}

The $\GeneratorInductionSealUp$ surface names the generator-internal induction packet that remains inside an authorized generator while recording every attempted passage to free-floating induction as $\Gap$ residue. It combines the authorized generator row, the continuation witness row required by the generator-closure classifier, the closure classifier row itself, the residue ledger, transport rows, continuation routes, package provenance, and local naming into one finite certificate.

\begin{definition}[Generator induction seal carrier]
\label{def:generator-induction-seal-carrier}
A $\GeneratorInductionSealUp$ carrier is a finite $\BHist$ packet
$$
S=(G,W,K,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the authorized generator row whose constructor-list provenance supplies the only internal induction authority;
\item $W$ is the continuation witness row carried by every accepted generator-internal continuation;
\item $K$ is the closure classifier row that checks whether a continuation remains inside the closure of $G$ with the witness $W$;
\item $R$ is the $\Gap$ ledger row recording every requested passage from the displayed generator-internal route to an unscoped induction claim;
\item $H$ records componentwise $\hsame$ transports for $G,W,K,R$, package provenance, and the local naming row;
\item $C$ records the displayed $\Cont$ routes for reading the generator row, replaying the witness-carrying continuation, consulting the closure classifier, emitting residue, and exporting the local packet;
\item $P$ is the $\Pkg$ provenance over $\BHist$, authorized generator rows, continuation witnesses, closure classifier rows, $\Gap$ ledger rows, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\GeneratorInductionSealUp}$ row.
\end{enumerate}
The carrier contains no induction rule over unnamed objects, no erased residue, and no route that turns a continuation lacking $W$ into a continuation of $G$.
\end{definition}
\leanchecked{BEDC.Derived.GeneratorInductionSealUp.GeneratorInductionSealTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Generator induction seal NameCert obligations]
\label{thm:generator-induction-seal-namecert-obligations}
For the carrier of \autoref{def:generator-induction-seal-carrier}, the local $\NameCert_{\GeneratorInductionSealUp}$ surface consists exactly of carrier admission for
$$
S=(G,W,K,R,H,C,P,N),
$$
authorized-generator exposure, continuation-witness preservation, closure-classifier lookup, $\Gap$ residue retention, componentwise $\hsame$ stability, displayed $\Cont$ replay, $\Pkg$ provenance, and NameCert export for the same finite packet.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:generator-induction-seal-carrier}. The packet exposes only the eight displayed rows $G,W,K,R,H,C,P,N$.

Generator authority is read from $G$, witness-carrying continuation from $W$, and closure classification from $K$. These rows determine which induction routes remain internal to the authorized generator.

Residue, transport, replay, and provenance are confined by $R,H,C,P$. The local row $N$ exports only this packet as a naming certificate, so no projection can add a hidden universal induction principle.
\end{proof}

\begin{theorem}[Generator induction seal continuation witness]
\label{thm:generator-induction-seal-continuation-witness}
Every continuation accepted by a $\GeneratorInductionSealUp$ packet carries the displayed witness row $W$ and is checked by the closure classifier row $K$ against the authorized generator row $G$. A continuation that cannot replay $W$ through the displayed $\Cont$ route is not a continuation of this seal.
\end{theorem}
\begin{proof}
Read the proposed continuation through $C$. If it is accepted, the route reaches $G$, replays $W$, and consults $K$ before the local certificate row is exported.

The transport row $H$ preserves the same generator, witness, classifier, residue, package, and naming coordinates. Thus a transported accepted continuation still carries the displayed witness.

If the route cannot replay $W$, no carrier coordinate classifies it as a continuation of $G$. It is therefore outside the seal rather than an induction step of the packet.
\end{proof}

\begin{theorem}[Generator induction seal GAP non-escape]
\label{thm:generator-induction-seal-gap-non-escape}
Whenever a requested continuation is not classified by $K$ as a witness-carrying continuation of the authorized generator row $G$, the $\GeneratorInductionSealUp$ packet records the request only as $\Gap$ residue in $R$. The residue may be transported, replayed as a refusal, packaged, and named, but it cannot become an internal induction theorem.
\end{theorem}
\begin{proof}
Inspect the classifier row $K$. If the request is not accepted as a continuation of $G$ carrying $W$, the only coordinate that records it is the residue row $R$.

Transport through $H$ preserves residue as residue. Replay through $C$ can expose the refusal and package it through $P$, while $N$ names the same boundary.

The carrier has no conversion row from residue to induction authority. Therefore the $\Gap$ ledger cannot export an internal induction theorem or a free-floating closure principle.
\end{proof}

\begin{theorem}[Generator induction seal public package]
\label{thm:generator-induction-seal-public-package}
The public export of a $\GeneratorInductionSealUp$ packet is exactly the finite NameCert packet over the authorized generator row $G$, continuation witness row $W$, closure classifier row $K$, $\Gap$ ledger row $R$, componentwise $\hsame$ transports, displayed $\Cont$ routes, and $\Pkg$ provenance. A consumer can recover generator authority, witness status, classifier status, and residue location, but no induction object beyond those rows.
\end{theorem}
\begin{proof}
Start with the carrier tuple $S=(G,W,K,R,H,C,P,N)$. The export row $N$ names this tuple and no larger surface.

A consumer recovers generator authority from $G$, witness status from $W$, classifier status from $K$, and residue location from $R$. The same consumer uses $H$ for componentwise transport, $C$ for replay, and $P$ for provenance.

These rows exhaust the public package. Since $S$ has no coordinate for an unnamed induction principle, hidden eliminator, or erased residue, the NameCert packet cannot export such content.
\end{proof}

\closureat{GeneratorInductionSealUp}{seedStr}

\begin{closurestatus}{\GeneratorInductionSealUp}
  \constructivestory{A $\GeneratorInductionSealUp$ packet is generated from an authorized generator row, a continuation witness row, a closure classifier row, a $\Gap$ ledger row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:generator-induction-seal-carrier}, \autoref{thm:generator-induction-seal-namecert-obligations}, \autoref{thm:generator-induction-seal-continuation-witness}, \autoref{thm:generator-induction-seal-gap-non-escape}, and \autoref{thm:generator-induction-seal-public-package} bind the finite carrier, witness-carrying continuation route, classifier boundary, residue ledger, and NameCert export.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, induction over unnamed objects, erased GAP residue, or continuations outside the displayed generator witness.}
  \upgradepath{Obligation closure requires a checked carrier and finite theorems for witness preservation, classifier stability, residue non-escape, provenance, and NameCert export.}
\end{closurestatus}
