\chapter{A Concrete Naming Certificate for $\ZCarryUp$}
\label{ch:concrete-instances-zcarry-namecert}
\origin{ai}

The $\ZCarryUp$ interface packages the displayed Zeckendorf carry row
$\mathtt{word\_011}\to\mathtt{word\_100}$ as a finite BEDC naming surface. The
packet records the carry generator, the source non-normality witness, the target
normality witness, the non-$\hsame$ boundary, transport rows, continuation
routes, package provenance, and the local naming row. It licenses the carry as a
classifier and gives no route to treating the two histories as kernel-equal.

\begin{definition}[ZCarry finite carry packet]
\label{def:zcarry-finite-carry-packet}
A $\ZCarryUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
Z=(h,k,G,N_h,N_k,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $h$ is the source history row $\mathtt{word\_011}$;
\item $k$ is the target history row $\mathtt{word\_100}$;
\item $G$ is the generated carry row $\mathsf{ZCarry}(h,k)$;
\item $N_h$ is the source ledger row witnessing $\neg\mathsf{ZNormal}(h)$;
\item $N_k$ is the target ledger row witnessing $\mathsf{ZNormal}(k)$;
\item $H$ records the non-$\hsame$ boundary $\neg\hsame(h,k)$ together with the componentwise $\hsame$ transports that preserve the displayed rows separately;
\item $C$ records the displayed $\Cont$ routes for source inspection, target inspection, carry readback, normality readback, non-$\hsame$ readback, and NameCert comparison;
\item $P$ is the $\Pkg$ provenance row naming $\ZeckendorfNormalUp$, $\ZCarryUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and the generated carry row;
\item $N$ is the local $\NameCert_{\ZCarryUp}$ row.
\end{enumerate}
The local classifier compares accepted packets only by the displayed rows
$h,k,G,N_h,N_k,H,C,P,N$. No coordinate identifies $h$ and $k$, quotienting
histories or replacing the carry classifier by $\hsame$.
\end{definition}
\leandef{BEDC.Derived.ZCarryUp.ZCarryFiniteCarryPacket}

\begin{theorem}[ZCarry finite NameCert obligations]
\label{thm:zcarry-finite-namecert-obligations}
The local $\NameCert_{\ZCarryUp}$ obligation surface consists exactly of carrier
admission by \autoref{def:zcarry-finite-carry-packet}, the generated carry row
$G$, the source non-normal row $N_h$, the target normal row $N_k$, the
non-$\hsame$ boundary row $H$, the displayed $\Cont$ routes $C$, the $\Pkg$
provenance row $P$, and the local naming row $N$.
\end{theorem}
\begin{proof}
Project the finite packet. Each row required by the carry certificate appears as
a coordinate before any consumer can read the classifier.

The generator row $G$ fixes the only displayed carry window. The two normality
rows record the source and target sides of that window, while $H$ records that
the window is not an $\hsame$ identification.

The routes $C$, provenance row $P$, and local naming row $N$ then repack the
same finite surface as a $\NameCert_{\ZCarryUp}$ obligation surface. Since the
carrier has no equality or quotient coordinate, no further object can be
exported by the certificate.
\end{proof}
\leanchecked{BEDC.Derived.ZCarryUp.ZCarryFiniteCarryPacket\_obligation\_surface}

\begin{theorem}[ZCarry carry-not-hsame boundary]
\label{thm:zcarry-carry-not-hsame-boundary}
For every accepted $\ZCarryUp$ packet $Z=(h,k,G,N_h,N_k,H,C,P,N)$, the carry row
$G$ is stable only as a classifier row. Its ledger includes $\neg\hsame(h,k)$,
so the displayed carry from $\mathtt{word\_011}$ to $\mathtt{word\_100}$ cannot
be consumed as history-sameness.
\end{theorem}
\begin{proof}
Read the generated carry row $G$. By the Zeckendorf carry theorem
\autoref{thm:zcarry-not-hsame}, every instance of $\mathsf{ZCarry}(h,k)$ carries
the boundary $\neg\hsame(h,k)$.

The packet stores this boundary in $H$ and routes it through $C$. Therefore a
consumer can transport the carry classifier only together with the recorded
non-$\hsame$ witness, so the carry row cannot become a kernel equality.
\end{proof}

\begin{theorem}[ZCarry normal-target ledger]
\label{thm:zcarry-normal-target-ledger}
For every accepted $\ZCarryUp$ packet $Z=(h,k,G,N_h,N_k,H,C,P,N)$, the target
history is normal and the source history is non-normal. The target row is
$\mathtt{word\_100}$ with $N_k:\mathsf{ZNormal}(k)$, while the source row is
$\mathtt{word\_011}$ with $N_h:\neg\mathsf{ZNormal}(h)$.
\end{theorem}
\begin{proof}
The generator row $G$ identifies the displayed carry window. Applying
\autoref{thm:zcarry-target-normal} reads the target normality witness, and
applying \autoref{thm:zcarry-source-not-normal} reads the source non-normality
witness.

The packet stores those two reads as $N_k$ and $N_h$. Transport through $H$ and
$C$ preserves the target and source ledgers as separate rows, so normality can be
reported only with the same displayed source-target orientation.
\end{proof}
\leanchecked{BEDC.Derived.ZCarryUp.TasteGate.ZCarryNormalTargetLedger}

\begin{theorem}[ZCarry Zeckendorf normal sibling dependency]
\label{thm:zcarry-zeckendorf-normal-sibling-dependency}
For every accepted $\ZCarryUp$ packet $Z=(h,k,G,N_h,N_k,H,C,P,N)$, the source non-normal row $N_h$ and target normal row $N_k$ are read through the Zeckendorf normal-form sibling surface of \autoref{ch:concrete-instances-zeckendorf-normal-namecert} before the local carry packet assembles its $\NameCert_{\ZCarryUp}$ boundary. The $\ZCarryUp$ packet supplies the generated carry classifier, the non-$\hsame$ ledger, and the local transport, continuation, provenance, and naming rows; it does not duplicate the sibling normal-word evidence.
\end{theorem}
\begin{proof}
Project the accepted packet as $h,k,G,N_h,N_k,H,C,P,N$. The two normality rows are separate fields of the local carrier, while $G$ and $H$ record the carry classifier and the non-$\hsame$ boundary.

Apply \autoref{thm:zcarry-normal-target-ledger}. It reads $N_k$ as the target normal row and $N_h$ as the source non-normal row with the displayed source-target orientation.

The normal-word evidence used by those rows is supplied through the sibling chapter \autoref{ch:concrete-instances-zeckendorf-normal-namecert}. The local packet then contributes $H,C,P,N$ and the generated carry row $G$, so the NameCert boundary consumes the sibling normal-form surface without replacing it.
\end{proof}

\begin{theorem}[ZCarry NameCert assembly]
\label{thm:zcarry-namecert-assembly}
The carrier of \autoref{def:zcarry-finite-carry-packet}, the obligation surface
of \autoref{thm:zcarry-finite-namecert-obligations}, the non-$\hsame$ boundary
of \autoref{thm:zcarry-carry-not-hsame-boundary}, and the normal-target ledger
of \autoref{thm:zcarry-normal-target-ledger} assemble the concrete
$\NameCert_{\ZCarryUp}$ packet for the displayed Zeckendorf carry classifier.
\end{theorem}
\begin{proof}
Bind the carrier rows $h,k,G,N_h,N_k,H,C,P,N$. These rows expose the source,
target, generator, normality witnesses, non-$\hsame$ boundary, transport routes,
provenance, and local name.

Apply the finite obligation theorem to identify the public certificate surface.
Apply the carry-not-$\hsame$ boundary theorem to keep the classifier separate
from history-sameness. Apply the normal-target ledger theorem to retain the
target-normal and source-non-normal rows.

Repacking these rows gives the local naming certificate. The assembly is exactly
the concrete packet recorded by the Lean-side object
$\mathsf{zCarry\_namecert}$.
\end{proof}
\leanchecked{BEDC.Derived.AxisZeckendorf.Carry.zCarry\_namecert}

\begin{corollary}[ZCarry licensed classifier boundary]
\label{cor:zcarry-licensed-classifier-boundary}
The $\ZCarryUp$ interface is licensed by the finite packet of
\autoref{thm:zcarry-namecert-assembly}. Any downstream use of the displayed
carry must cite the generated carry row, the normality ledgers, the non-$\hsame$
boundary, the displayed $\Cont$ routes, the $\Pkg$ provenance, and the local
$\NameCert$ row; it may not read the carry as $\hsame$ or as a primitive kernel
rewrite.
\end{corollary}
\begin{proof}
Use the assembled $\NameCert_{\ZCarryUp}$ packet. Its public rows are exactly
the carrier coordinates and obligation rows named above.

The non-$\hsame$ boundary is part of the exported ledger. Hence a consumer that
uses the carry classifier also receives the evidence preventing a kernel-equality
reading, and no primitive rewrite row is available in the packet.
\end{proof}

\closureat{ZCarryUp}{scopedStr}[BEDC.Derived.AxisZeckendorf.Carry.zCarry\_namecert]
\closureat{ZCarryUp}{publicStr}[BEDC.Derived.AxisZeckendorf.Carry.zCarry\_namecert]
\closureat{ZCarryUp}{bridgedStr}[BEDC.Derived.AxisZeckendorf.Carry.zCarry\_namecert]
\closureat{ZCarryUp}{matureStr}[BEDC.Derived.AxisZeckendorf.Carry.zCarry\_namecert]

\begin{closurestatus}{\ZCarryUp}
  \constructivestory{A $\ZCarryUp$ packet is generated from the displayed Zeckendorf carry row, source non-normal ledger, target normal ledger, non-$\hsame$ boundary, componentwise transports, displayed continuation routes, package provenance, and a local NameCert row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The checked $\mathsf{zCarry\_namecert}$ assembly of \autoref{thm:zcarry-namecert-assembly} and the licensed boundary of \autoref{cor:zcarry-licensed-classifier-boundary} bind the public $\ZCarryUp$ classifier boundary to the bridge-readable package rows $G,N_h,N_k,H,C,P,N$ for the displayed Zeckendorf carry.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.AxisZeckendorf.Carry.zCarry\_namecert}
  \bridgestatus{none}
  \notclaimed{This chapter does not identify the source and target histories by $\hsame$, does not install quotient rewriting, and does not close arbitrary Zeckendorf carry generation.}
  \upgradepath{No further theory-axis upgrade is claimed here; remaining work is bridge checking for the same displayed generated-carry, normality, non-$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet.}
\end{closurestatus}
