\chapter{A Concrete Naming Certificate for \(\LinearMapUp\)}
\label{ch:concrete-instances-linearmap-namecert}

The linear map interface \(\LinearMapUp\) has certificate obligations between two vector spaces over the same scalar field from \autoref{ch:concrete-instances-vecspace-namecert}. The carrier is the predicate "\(f : V \to W\) preserves the additive structure and commutes with scalar multiplication"; the classifier is pointwise carrier sameness on the codomain restricted to maps satisfying linearity. It is not a primitive function space; it is admitted only as a derived predicate over function pairs.

\section{Carrier definition}

\begin{definition}[LinearMap carrier]
\label{def:linearmap-carrier}
Use a structure containing a function \(f:V\to W\) plus explicit proofs of additivity and scalar compatibility.
\end{definition}

\section{Concrete singleton empty-history linear map instance}
\label{sec:linearmap-concrete-singleton-instance}

\begin{definition}[Concrete singleton empty-history linear map instance]
\label{def:singleton-empty-history-linearmap-instance}
Use the singleton empty-history vector space of
Definition~\ref{def:singleton-empty-history-vecspace-instance} as both source
and target. Its scalar, source-vector, and target-vector carriers are the
singleton history source $A_{\emp}$ of
Definition~\ref{def:list-singleton-history-source} at $a_0=\emp$. The map-code
carrier is the same existing singleton predicate
$$
A_{\emp}:\mathsf{BHist}\to\mathsf{Prop},
$$
and the map-code classifier is the existing singleton classifier
$\rho_{\emp}$. The realized action is the constant endpoint action
$$
\Lambda_{\emp}(f,x):=\emp
$$
for every admitted map code $f$ and singleton vector input $x$. The same
endpoint action may be displayed as
$$
F_{\emp}(h):=\emp.
$$
The linear-map carrier on public map codes and its pointwise map classifier
are
$$
L_{\emp}(f):=\hsame(f,\emp),
\qquad
\lambda_{\emp}(f,g):=
L_{\emp}(f)\land L_{\emp}(g)\land\hsame(f,g).
$$
The pointwise evaluation is
$$
\mathsf{ev}_{\emp}(f,h):=F_{\emp}(h).
$$
The identity, zero-map, and composition code are
$$
\mathsf{id}_{\emp}:=\emp,\qquad
\mathsf{zeroMap}_{\emp}:=\emp,\qquad
\mathsf{comp}_{\emp}(g,f):=\emp.
$$

This certificate has ten fields:
\begin{enumerate}
  \item Traditional target: the terminal one-map linear map space between the
  singleton vector space and itself.
  \item BEDC source: $\mathsf{BHist}$.
  \item Carrier choice: $A_{\emp}$ for source vectors, target vectors, and
  map codes.
  \item Classifier choice: $\rho_{\emp}$ for endpoint and map-code equality.
  \item Stability obligations: output closure, pointwise classifier
  congruence, additivity, scalar compatibility, zero preservation, identity
  closure, and composition closure.
  \item Ledger: singleton map-code provenance for $F_{\emp}$,
  $\mathsf{id}_{\emp}$, $\mathsf{zeroMap}_{\emp}$, and
  $\mathsf{comp}_{\emp}$.
  \item Core theorem list: Theorem~\ref{thm:singleton-empty-history-linearmap-laws}.
  \item Exactness predicate: singleton endpoint classification.
  \item Standard bridge: the terminal one-map linear hom space.
  \item Status: $\mathsf{ProofTarget}$.
\end{enumerate}
\end{definition}

\begin{theorem}[Singleton empty-history linear map laws]
\label{thm:singleton-empty-history-linearmap-laws}
The tuple
$$
(A_{\emp},\rho_{\emp},\Lambda_{\emp},\emp,\mathsf{comp}_{\emp})
$$
satisfies the $\LinearMapUp$ schema over the singleton vector space, where the
displayed empty-history code supplies the identity and zero-map slots.
\end{theorem}
\begin{proof}
The source and target vector-space laws are those of
Theorem~\ref{thm:singleton-empty-history-vecspace-laws}. They supply the
singleton scalar laws, vector closure, additive laws, scalar-action closure,
and scalar-action congruence for the same $A_{\emp}$ carrier and
$\rho_{\emp}$ classifier.

Output closure is $A_{\emp}(\emp)$, since
$\Lambda_{\emp}(f,x)$ is definitionally $\emp$. Pointwise classifier
congruence is immediate because
$\Lambda_{\emp}(f,x)$ and $\Lambda_{\emp}(g,y)$ are both $\emp$, so the
required endpoint comparison is the singleton $\rho_{\emp}$ witness.

For additivity,
$\Lambda_{\emp}(f,\mathsf{add}(x,y))$ and
$\mathsf{add}(\Lambda_{\emp}(f,x),\Lambda_{\emp}(f,y))$ are both classified
with $\emp$. The vector-space theorem supplies closure for the displayed
addition endpoint, and the singleton classifier supplies the endpoint
comparison.

For scalar compatibility,
$\Lambda_{\emp}(f,\mathsf{smul}(r,x))$ and
$\mathsf{smul}(r,\Lambda_{\emp}(f,x))$ are again classified with $\emp$.
Scalar-action closure and congruence come from the singleton vector-space
laws, so no additional map-specific datum is needed.

Zero preservation compares $\Lambda_{\emp}(f,0)$ with the singleton vector
zero. Both sides are $\emp$, and the required classification is the same
$\rho_{\emp}$ endpoint witness.

The identity and zero-map codes are $\emp$, and their action on any carried
input $x$ reduces to $\emp$. The input carrier witness $A_{\emp}(x)$ together
with $\rho_{\emp}$ gives the required singleton endpoint classification.

For composition closure, every composite map code and every realized output
reduce to $\emp$. The carrier witness for $\emp$ and reflexivity inside
$\rho_{\emp}$ close the composition law and the comparison of the two
evaluation orders.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingleton\_empty\_history\_laws}

\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingleton\_laws}

\begin{theorem}[Singleton empty-history linear map public-code exactness]
\label{thm:singleton-empty-history-linearmap-public-code-exactness}
For the concrete instance of
Definition~\ref{def:singleton-empty-history-linearmap-instance}, for all
public map codes $f,g$ and vector code $x$, if $L_{\emp}(f)$,
$L_{\emp}(g)$, and $A_{\emp}(x)$, then
$$
\lambda_{\emp}(f,\mathsf{id}_{\emp})\land
\lambda_{\emp}(\mathsf{zeroMap}_{\emp},\mathsf{id}_{\emp})\land
\lambda_{\emp}(\mathsf{comp}_{\emp}(g,f),\mathsf{id}_{\emp})\land
\rho_{\emp}(\mathsf{ev}_{\emp}(f,x),x).
$$
Its per-object fit is: traditional target terminal one-map hom exactness;
BEDC source $\mathsf{BHist}$ over the singleton vector-space instance;
carrier $A_{\emp}$ for vectors and map codes; classifier $\rho_{\emp}$ and
$\lambda_{\emp}$; stability obligations public-code exactness, evaluation
exactness, and composition collapse; ledger singleton map-code provenance;
core theorem this block; exactness predicate the displayed classifier
collapse; standard bridge terminal linear hom; status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
The three public map-code endpoints
$\mathsf{id}_{\emp}$, $\mathsf{zeroMap}_{\emp}$, and
$\mathsf{comp}_{\emp}(g,f)$ reduce to $\emp$. The hypotheses
$L_{\emp}(f)$ and $L_{\emp}(g)$ give the nontrivial singleton witnesses for
the two displayed input map codes.

The classifier component of each map-code comparison is
$\hsame(\emp,\emp)$. Since both advertised comparison partners reduce to the
empty history, the reflexive singleton classifier closes the identity,
zero-map, and composite-code clauses.

For evaluation, $\mathsf{ev}_{\emp}(f,x)$ is $F_{\emp}(x)$ and therefore
reduces to $\emp$. The carrier hypothesis $A_{\emp}(x)$ supplies the endpoint
witness for the input vector, and $\rho_{\emp}$ supplies the reflexive
comparison between the realized endpoint and $x$ in the singleton carrier.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingleton\_public\_empty\_code\_exactness}

\begin{theorem}[Singleton linear-map classifier append split empty]
\label{thm:linearmap-singleton-classifier-append-split-empty}
For all histories $p,q,h:\mathsf{BHist}$,
$$
\lambda_{\emp}(\mathsf{append}(p,q),h)
$$
holds exactly when $L_{\emp}(p)$, $L_{\emp}(q)$, and $L_{\emp}(h)$ all hold.
\end{theorem}
\begin{proof}
The forward direction reads the first carrier field of
$\lambda_{\emp}(\mathsf{append}(p,q),h)$ as
$\hsame(\mathsf{append}(p,q),\emp)$. Empty-result inversion for BEDC append
splits this into $p\hsame\emp$ and $q\hsame\emp$, while the second classifier
field gives $h\hsame\emp$.

Conversely, the three singleton carrier witnesses show that
$\mathsf{append}(p,q)$ is empty and that $h$ is empty. These are the two
carrier fields of $\lambda_{\emp}$, and composing the empty endpoint
comparison with the symmetry of the $h$-carrier gives the classifier
comparison between $\mathsf{append}(p,q)$ and $h$.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_split\_empty\_iff}

\begin{theorem}[Singleton linear-map classifier visible right append exclusion]
\label{thm:linearmap-singleton-classifier-append-visible-left-absurd}
For all histories $p,q,h:\mathsf{BHist}$, neither appending a visible right
component to $p$ can be classified by the singleton linear-map classifier:
$$
\lambda_{\emp}(\mathsf{append}(p,\Ezero(q)),h)\Longrightarrow\bot,
\qquad
\lambda_{\emp}(\mathsf{append}(p,\Eone(q)),h)\Longrightarrow\bot.
$$
\end{theorem}
\begin{proof}
Unfold the classifier and read its left carrier field. The field says that
$\mathsf{append}(p,\Ezero(q))$ or $\mathsf{append}(p,\Eone(q))$ is
history-same to $\emp$. Empty-append inversion would then force the visible
right component itself to be $\emp$, contradicting constructor no-confusion
for $\Ezero$ and $\Eone$.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_visible\_left\_absurd}

\begin{theorem}[Singleton linear-map classifier visible prefix exclusion]
\label{thm:linearmap-singleton-classifier-append-visible-prefix-absurd}
For all histories $p,q,h:\mathsf{BHist}$, neither visible prefix can be
classified after append by the singleton linear-map classifier:
$$
\lambda_{\emp}(\mathsf{append}(\Ezero(p),q),h)\Longrightarrow\bot,
\qquad
\lambda_{\emp}(\mathsf{append}(\Eone(p),q),h)\Longrightarrow\bot.
$$
\end{theorem}
\begin{proof}
The singleton classifier requires its left argument to be empty. Applying
empty-append inversion to this carrier clause forces the visible prefix
$\Ezero(p)$ or $\Eone(p)$ to be $\emp$, which is impossible by constructor
no-confusion.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_visible\_prefix\_absurd}

\begin{theorem}[Singleton linear-map classifier append-pair carrier exactness]
\label{thm:linearmap-singleton-classifier-append-pair-carrier}
For all histories $p,q,r,s:\mathsf{BHist}$,
$$
\lambda_{\emp}(\mathsf{append}(p,q),\mathsf{append}(r,s))
$$
holds exactly when all four endpoint histories lie in the singleton carrier:
$$
L_{\emp}(p)\land L_{\emp}(q)\land L_{\emp}(r)\land L_{\emp}(s).
$$
\end{theorem}
\begin{proof}
The forward direction reads the two carrier fields of the displayed
classifier. Empty-append inversion splits
$\mathsf{append}(p,q)\hsame\emp$ into the two endpoint carrier witnesses
for $p$ and $q$, and it splits
$\mathsf{append}(r,s)\hsame\emp$ into the two endpoint carrier witnesses
for $r$ and $s$.

Conversely, the four singleton carrier witnesses reconstruct empty witnesses
for both appended histories. These are the two carrier fields of
$\lambda_{\emp}$, and transitivity with symmetry of the right appended
empty witness supplies the classifier comparison between the two appended
histories.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_pair\_carrier\_iff}

\begin{theorem}[Singleton linear-map classifier append pair empty]
\label{thm:linearmap-singleton-classifier-append-pair-empty}
For all histories $p,q,r,s:\mathsf{BHist}$,
$$
\lambda_{\emp}(\mathsf{append}(p,q),\mathsf{append}(r,s))
\Longleftrightarrow
L_{\emp}(p)\wedge L_{\emp}(q)\wedge L_{\emp}(r)\wedge L_{\emp}(s).
$$
\end{theorem}
\begin{proof}
The forward direction unfolds the singleton classifier. Its two carrier
clauses classify both appended histories with $\emp$, and empty-append
inversion splits those clauses into the four endpoint carrier witnesses.

Conversely, the four singleton carrier witnesses assemble the two appended
histories as empty histories. These become the two carrier clauses of
$\lambda_{\emp}$, and composing the left appended empty witness with symmetry
of the right one gives the classifier comparison between the appended
endpoints.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_pair\_empty\_iff}

\begin{theorem}[Singleton linear-map classifier continuation closure]
\label{thm:linearmap-singleton-classifier-continuation-closed}
For histories $P,P',Q,Q',L,R:\mathsf{BHist}$, if
$\lambda_{\emp}(P,P')$ and $\lambda_{\emp}(Q,Q')$, and if
$$
\ContR(P,Q,L)
\qquad\text{and}\qquad
\ContR(P',Q',R),
$$
then $\lambda_{\emp}(L,R)$.
\end{theorem}
\begin{proof}
The two singleton linear-map classifier witnesses identify all four
continuation inputs with $\emp$. Transport each continuation ledger to the
empty-empty ledger and compare against $\ContR(\emp,\emp,\emp)$. This gives
$L\hsame\emp$ and $R\hsame\emp$, and those carrier clauses compose through
symmetry on the right endpoint to close $\lambda_{\emp}(L,R)$.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_continuation\_closed}

\begin{theorem}[Singleton linear map composition associativity empty classifier]
\label{thm:linearmap-singleton-comp-assoc-empty-classifier}
For singleton linear map codes $f,g,h$, if each code lies in
$L_{\emp}$, then both associations of the composite code classify with
$\emp$, and the two associated composite codes classify with each other:
$$
\lambda_{\emp}(\mathsf{comp}_{\emp}(h,\mathsf{comp}_{\emp}(g,f)),\emp)
\land
\lambda_{\emp}(\mathsf{comp}_{\emp}(\mathsf{comp}_{\emp}(h,g),f),\emp)
\land
\lambda_{\emp}(\mathsf{comp}_{\emp}(h,\mathsf{comp}_{\emp}(g,f)),
  \mathsf{comp}_{\emp}(\mathsf{comp}_{\emp}(h,g),f)).
$$
\end{theorem}
\begin{proof}
The singleton composition code is definitionally $\emp$ for every pair of
inputs. Therefore both associated composites reduce to $\emp$, and each
displayed classifier is the reflexive singleton map-code classifier at the
empty history.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingleton\_comp\_assoc\_empty\_classifier}

\begin{theorem}[Singleton linear-map classifier append left cancellation]
\label{thm:singleton-linearmap-classifier-append-left-cancel}
For all $P,Q,R:\mathsf{BHist}$, if $L_{\emp}(P)$, then
$$
\lambda_{\emp}(\mathsf{append}(P,Q),\mathsf{append}(P,R))
\Longleftrightarrow
\lambda_{\emp}(Q,R).
$$
\end{theorem}
\begin{proof}
For the forward direction, unfold the singleton classifier. The carrier
clauses say that both appended histories are classified with $\emp$.
Applying the empty-append inversion to each carrier clause gives
$Q\hsame\emp$ and $R\hsame\emp$. These two endpoint witnesses compose, with
symmetry on the right one, to give $Q\hsame R$.

For the reverse direction, the hypothesis $L_{\emp}(P)$ identifies the left
prefix with $\emp$. The two appended histories therefore reduce through the
left-empty continuation law to $Q$ and $R$. The carrier clauses and classifier
comparison supplied by $\lambda_{\emp}(Q,R)$ transport along those reductions
to rebuild the prefixed singleton classifier.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_left\_cancel\_iff}

\begin{theorem}[Singleton linear-map classifier append right cancellation]
\label{thm:linearmap-singleton-classifier-append-right-cancel-iff}
For all $P,Q,R:\mathsf{BHist}$, if $L_{\emp}(P)$, then
$$
\lambda_{\emp}(\mathsf{append}(Q,P),\mathsf{append}(R,P))
\Longleftrightarrow
\lambda_{\emp}(Q,R).
$$
\end{theorem}
\begin{proof}
For the forward direction, unfold the singleton classifier. The carrier
clauses classify both right-suffixed histories with $\emp$. Empty-append
inversion splits these clauses and gives $Q\hsame\emp$ and $R\hsame\emp$.
Composing the first endpoint witness with the symmetry of the second gives
$Q\hsame R$, which closes $\lambda_{\emp}(Q,R)$.

Conversely, the hypothesis $L_{\emp}(P)$ supplies the certified empty suffix.
Together with the two carrier fields of $\lambda_{\emp}(Q,R)$, empty-append
composition classifies both $\mathsf{append}(Q,P)$ and
$\mathsf{append}(R,P)$ with $\emp$. These two endpoint witnesses compose
through symmetry to rebuild the right-suffixed classifier.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_right\_cancel\_iff}

\begin{theorem}[Singleton linear-map classifier append two-sided cancellation]
\label{thm:linearmap-singleton-classifier-append-two-sided-cancel}
For all $P,Q,R,S:\mathsf{BHist}$, if $L_{\emp}(P)$ and $L_{\emp}(S)$, then
$$
\lambda_{\emp}(\mathsf{append}(P,Q),\mathsf{append}(R,S))
\Longleftrightarrow
\lambda_{\emp}(Q,R).
$$
\end{theorem}
\begin{proof}
For the forward direction, unfold the singleton classifier. The two carrier
clauses classify $\mathsf{append}(P,Q)$ and $\mathsf{append}(R,S)$ with
$\emp$. Empty-append inversion gives $Q\hsame\emp$ and $R\hsame\emp$, and
these endpoint witnesses compose to close $\lambda_{\emp}(Q,R)$.

Conversely, $L_{\emp}(P)$ and $L_{\emp}(S)$ combine with the carrier fields of
$\lambda_{\emp}(Q,R)$ to classify the two appended histories with $\emp$.
The two resulting endpoint witnesses compose, with symmetry on the right, to
rebuild the two-sided appended classifier.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonClassifier\_append\_two\_sided\_cancel\_iff}

\begin{theorem}[Singleton evaluation append-input classifier readback]
\label{thm:linearmap-singleton-eval-append-input-classifier}
For histories $f,x,y,h$, classifying the singleton evaluation of an appended
input against $h$ is exactly the singleton carrier condition on $h$:
$$
\mathsf{LinearMapSingletonClassifier}
  (\mathsf{LinearMapSingletonEval}(f,x\cdot y),h)
\Longleftrightarrow
\mathsf{LinearMapSingletonCarrier}(h).
$$
\end{theorem}
\begin{proof}
The singleton evaluator always returns $\emp$. In the forward direction, the
classifier already contains the carrier witness for its right endpoint. In the
reverse direction, the carrier witness for $h$ combines with reflexivity at
$\emp$ and symmetry of the displayed carrier equality to form the restricted
singleton classifier.
\end{proof}
\leanchecked{BEDC.Derived.LinearMapUp.LinearMapSingletonEval\_append\_input\_classifier\_iff}

The $\LinearMapUp$ schema is instantiated by this concrete $\mathsf{BHist}$
carrier and singleton action, so later Lean work can target BHist-anchored
linear-map laws instead of only abstract function fields.

\section{The certificate}

\begin{definition}[LinearMap source specification]
\label{def:linearmap-source-specification}
The source is a pair of vector spaces over the same certified field.
\end{definition}

\begin{definition}[LinearMap pattern specification]
\label{def:linearmap-pattern-specification}
The pattern is function-with-law formation: map data together with linearity witnesses.
\end{definition}

\begin{definition}[LinearMap classifier specification]
\label{def:linearmap-classifier-specification}
The classifier relates two linear maps when their outputs are codomain-classified the same for every input witness.
\end{definition}

\begin{definition}[LinearMap stability certificate]
\label{def:linearmap-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item pointwise classifier reflexivity
  \item pointwise classifier transitivity
  \item preservation of zero derived from linearity
  \item additivity preservation
  \item scalar-compatibility preservation
  \item closure under identity and composition
\end{enumerate}
\end{definition}

\begin{definition}[LinearMap ledger policy]
\label{def:linearmap-ledger-policy}
Record the function identifier, its linearity witnesses, and codomain ledgers for pointwise comparisons.
\end{definition}

\begin{definition}[\(\LinearMapUp\) certificate obligations]
\label{def:linearmap-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\LinearMapUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\LinearMapUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:linearmap-zero-axiom-note}
Avoids funext by using pointwise classifier sameness instead of equality of functions.
\end{remark}

\begin{lemma}[Codomain additive duplicate cancellation]
\label{lem:abgroup-additive-duplicate-cancellation}
Let $W$ carry an $\AbGroupUp(W)$ certificate with additive operation $+_W$, additive unit $0_W$, and classifier $\sim_W$. For any carried $w:W$, if
$$
w\sim_W w+_W w,
$$
then
$$
w\sim_W 0_W.
$$
\end{lemma}
\begin{proof}
By \autoref{prop:abgroup-forgets-group-certificate}, the additive carrier of $W$ has the same operation, unit, inverse, and classifier as a $\GroupUp$ carrier. Symmetry of the classifier turns the hypothesis into
$$
w+_W w\sim_W w.
$$
In additive notation, \autoref{thm:group-left-absorb-right-factor-unit} says that a comparison $a+_W b\sim_W a$ in this group reduct forces $b\sim_W0_W$. Taking $a=w$ and $b=w$ gives $w\sim_W0_W$.
\end{proof}

\begin{theorem}[LinearMap zero preservation from additivity]
\label{thm:linearmap-zero-preservation-from-additivity}
Let $F$ carry a $\FieldUp(F)$ certificate, and let $V$ and $W$ carry $\VecSpaceUp(F,V)$ and $\VecSpaceUp(F,W)$ certificates. Write $+_V$, $0_V$, and $\sim_V$ for the source vector addition, zero, and classifier, and write $+_W$, $0_W$, and $\sim_W$ for the codomain additive operation, zero, and classifier. Let $f:V\to W$ be a carried $\LinearMapUp(V,W)$ map. If the additive preservation row of $f$ is
$$
f(x+_V y)\sim_W f(x)+_W f(y)
$$
for carried source inputs $x,y$, then
$$
f(0_V)\sim_W0_W.
$$
The ten-field fit is: traditional target ordinary linear maps send zero to zero; BEDC source $\LinearMapUp(V,W)$ over the vector-space certificates; carrier the codomain vector carrier; classifier $\sim_W$; stability from additivity and codomain additive cancellation; ledger the zero-pair additive row and the cancellation witness; core theorem this block; exactness predicate $f(0_V)\sim_W0_W$; standard bridge zero preservation for additive linear maps; status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
By \autoref{def:vecspace-carrier}, the source vector-space carrier is a module carrier, and by \autoref{def:module-carrier} its vector addition belongs to an additive abelian group. The source carrier transport used to read this comparison inside later rows is the standard semantic transport of \autoref{thm:semantic-namecert-pattern-ledger-transport}; the additive unit law supplies the source-side comparison
$$
0_V+_V0_V\sim_V0_V.
$$

The function-with-law data of \autoref{def:linearmap-carrier} evaluate the additive row on carried source expressions. Viewing evaluation by $f$ as the descent map packaged by the function-like linear-map data, \autoref{thm:descent-certificate-respects} transports the source comparison $0_V+_V0_V\sim_V0_V$ through evaluation; codomain symmetry and transitivity then compose that transported comparison with the additive row at $x=0_V$ and $y=0_V$, giving
$$
f(0_V)\sim_W f(0_V)+_W f(0_V).
$$
The output $f(0_V)$ is carried by the codomain part of the same linear-map data.

For the codomain, \autoref{prop:vecspace-forgets-module-certificate} reads the vector space as a module, and \autoref{prop:module-forgets-abgroup-certificate} retains its additive abelian-group certificate with the same operation, zero, and classifier. Applying \autoref{lem:abgroup-additive-duplicate-cancellation} to $w=f(0_V)$ therefore gives
$$
f(0_V)\sim_W0_W.
$$
This is exactly the zero-preservation item listed in \autoref{def:linearmap-stability-certificate}, obtained from additivity and the codomain additive cancellation package.
\end{proof}

\begin{theorem}[LinearMap composition classifier congruence]
\label{thm:linmap-composition-classifier-congruence}
Let $F$ carry a $\FieldUp(F)$ certificate, and let $U$, $V$, and $W$ carry $\VecSpaceUp(F,U)$, $\VecSpaceUp(F,V)$, and $\VecSpaceUp(F,W)$ certificates over the same scalar source. Write $+_U$, $+_V$, and $+_W$ for vector addition, write the scalar actions as $r\cdot_U x$, $r\cdot_V y$, and $r\cdot_W z$, and write $\sim_U$, $\sim_V$, and $\sim_W$ for the corresponding vector classifiers. Let $f,f':U\to V$ be carried $\LinearMapUp(U,V)$ maps, and let $g,g':V\to W$ be carried $\LinearMapUp(V,W)$ maps. If $f$ and $f'$ are related by the pointwise $\LinearMapUp(U,V)$ classifier, and $g$ and $g'$ are related by the pointwise $\LinearMapUp(V,W)$ classifier, then $g\circ f$ and $g'\circ f'$ are carried $\LinearMapUp(U,W)$ maps and are related by the pointwise $\LinearMapUp(U,W)$ classifier:
$$
g\circ f\sim_{\LinearMapUp(U,W)}g'\circ f'.
$$
\end{theorem}
\begin{proof}
By \autoref{def:vecspace-carrier}, each displayed vector-space certificate is a module certificate over the same scalar field, and by \autoref{def:module-carrier} the addition, scalar action, carrier, and classifier rows used below are the module rows specialized to vector spaces. By \autoref{def:linearmap-carrier}, each carried linear map has output closure, additive preservation, scalar compatibility, and a descent certificate for transporting classifier comparisons through evaluation.

First consider $g\circ f$. For a carried input $x:U$, output closure for $f$ gives that $f(x)$ is carried in $V$, and output closure for $g$ gives that $g(f(x))$ is carried in $W$. Thus the composite has output closure. For carried inputs $x,y:U$, the additive row of $f$ gives
$$
f(x+_U y)\sim_V f(x)+_V f(y).
$$
Transporting this comparison through evaluation by $g$ using \autoref{thm:descent-certificate-respects}, and then applying the additive row of $g$, gives
$$
g(f(x+_U y))\sim_W g(f(x)+_V f(y))\sim_W g(f(x))+_W g(f(y)).
$$
Classifier transitivity in the codomain module gives the additive row for $g\circ f$. For a carried scalar $r:F$ and carried input $x:U$, the scalar row of $f$ gives
$$
f(r\cdot_U x)\sim_V r\cdot_V f(x).
$$
Transporting this comparison through evaluation by $g$, and then applying the scalar row of $g$, gives
$$
g(f(r\cdot_U x))\sim_W g(r\cdot_V f(x))\sim_W r\cdot_W g(f(x)).
$$
Again codomain transitivity gives scalar compatibility for $g\circ f$. Hence $g\circ f$ is a carried $\LinearMapUp(U,W)$ map. The same argument with $f'$ and $g'$ gives that $g'\circ f'$ is carried.

It remains to prove pointwise classifier congruence. Fix a carried input $x:U$. The pointwise classifier relation between $f$ and $f'$ gives
$$
f(x)\sim_V f'(x).
$$
The descent certificate for $g$ transports this input comparison to
$$
g(f(x))\sim_W g(f'(x)).
$$
The pointwise classifier relation between $g$ and $g'$ applied at the carried input $f'(x)$ gives
$$
g(f'(x))\sim_W g'(f'(x)).
$$
Transitivity of $\sim_W$ yields
$$
(g\circ f)(x)\sim_W(g'\circ f')(x).
$$
Because $x$ was arbitrary, \autoref{def:linearmap-classifier-specification} identifies this pointwise comparison with the $\LinearMapUp(U,W)$ classifier relation between the two composites. The ledger is the composition row recorded by \autoref{def:linearmap-ledger-policy}, with the two input map ledgers and the codomain pointwise comparison ledger as its witnesses.
\end{proof}

\begin{definition}[Module LinearMap certificate package]
\label{def:module-linearmap-certificate-package}
Let $R$ carry a $\RingUp$ certificate, and let $M$ and $N$ carry $\ModuleUp(R,M)$ and $\ModuleUp(R,N)$ certificates over the same scalar source. Write $\sim_M$ and $\sim_N$ for the module classifiers, $+_M$ and $+_N$ for vector addition, $0_M$ and $0_N$ for vector zero, and $\odot_M$ and $\odot_N$ for scalar action. A package
$$
\mathsf{LinearMapCert}_R(M,N;f)
$$
for a function $f:M\to N$ consists of:
\begin{enumerate}
  \item output closure: every carried $x:M$ has carried output $f(x):N$;
  \item source-classifier descent: $x\sim_M y$ implies $f(x)\sim_N f(y)$;
  \item additive preservation: $f(x+_M y)\sim_N f(x)+_N f(y)$ for carried $x,y:M$;
  \item scalar compatibility: $f(r\odot_M x)\sim_N r\odot_N f(x)$ for carried scalars $r:R$ and carried $x:M$;
  \item zero preservation: $f(0_M)\sim_N0_N$;
  \item ledger data recording the function identifier, the two linearity rows, the zero row, and the codomain pointwise comparison ledgers.
\end{enumerate}
This is the module fragment of the linear-map carrier in \autoref{def:linearmap-carrier}, with its pointwise classifier read as in \autoref{def:linearmap-classifier-specification} and its stability rows read against \autoref{def:module-stability-certificate}.
\end{definition}

\begin{theorem}[Module LinearMap composition certificate]
\label{thm:module-linearmap-composition-certificate}
Let $R$ carry a $\RingUp$ certificate, and let $M$, $N$, and $P$ carry $\ModuleUp(R,M)$, $\ModuleUp(R,N)$, and $\ModuleUp(R,P)$ certificates over the same scalar source. If
$$
\mathsf{LinearMapCert}_R(M,N;f)
\qquad\text{and}\qquad
\mathsf{LinearMapCert}_R(N,P;g),
$$
then the composite function $(g\circ f)(x):=g(f(x))$ carries a certificate
$$
\mathsf{LinearMapCert}_R(M,P;g\circ f).
$$
\end{theorem}
\begin{proof}
Unpack the two input certificates according to \autoref{def:module-linearmap-certificate-package}. The source data for the composite are the same scalar certificate $R$ together with the endpoint modules $M$ and $P$, which are among the module certificate obligations of \autoref{def:module-certificate-obligations}.

For output closure, let $x$ be carried in $M$. Output closure for $f$ gives that $f(x)$ is carried in $N$, and output closure for $g$ gives that $g(f(x))$ is carried in $P$.

For source-classifier descent, assume $x\sim_M y$. Descent for $f$ gives
$$
f(x)\sim_N f(y).
$$
Descent for $g$ transports this comparison to
$$
g(f(x))\sim_P g(f(y)),
$$
which is the descent row for $g\circ f$.

For additivity, let $x$ and $y$ be carried in $M$. Additive closure in the $M$ module makes $x+_M y$ carried. The additive row of $f$ gives
$$
f(x+_M y)\sim_N f(x)+_N f(y).
$$
Descent for $g$ sends this comparison to
$$
g(f(x+_M y))\sim_P g(f(x)+_N f(y)).
$$
The outputs $f(x)$ and $f(y)$ are carried in $N$, so the additive row of $g$ gives
$$
g(f(x)+_N f(y))\sim_P g(f(x))+_P g(f(y)).
$$
Classifier transitivity from \autoref{thm:namecert-equivalence-transitivity} composes the last two displayed comparisons and gives the additive row for $g\circ f$.

For scalar compatibility, let $r$ be a carried scalar and let $x$ be carried in $M$. Scalar-action closure in the $M$ module makes $r\odot_M x$ carried. The scalar row of $f$ gives
$$
f(r\odot_M x)\sim_N r\odot_N f(x).
$$
Descent for $g$ transports this to
$$
g(f(r\odot_M x))\sim_P g(r\odot_N f(x)).
$$
Since $f(x)$ is carried in $N$, the scalar row of $g$ gives
$$
g(r\odot_N f(x))\sim_P r\odot_P g(f(x)).
$$
Transitivity of the $P$ classifier gives scalar compatibility for the composite.

For zero preservation, the zero row of $f$ gives
$$
f(0_M)\sim_N0_N.
$$
Descent for $g$ gives
$$
g(f(0_M))\sim_P g(0_N),
$$
and the zero row of $g$ gives
$$
g(0_N)\sim_P0_P.
$$
Transitivity of the $P$ classifier gives $(g\circ f)(0_M)\sim_P0_P$.

The pointwise classifier for maps $M\to P$ is exactly the relation specified in \autoref{def:linearmap-classifier-specification}. The rows above are the output-closure, descent, additivity, scalar-compatibility, zero-preservation, and composition-closure entries of \autoref{def:linearmap-stability-certificate} read over the module carriers of \autoref{def:module-carrier}. The ledger is the composite record formed from the two input function identifiers and their linearity, zero, and pointwise comparison ledgers, matching the policy of \autoref{def:linearmap-ledger-policy}. Therefore the carrier, source, pattern, classifier, stability, and ledger data satisfy \autoref{def:linearmap-certificate-obligations} for $g\circ f$.
\end{proof}

\begin{theorem}[Module identity LinearMap certificate]
\label{thm:module-linearmap-identity-certificate}
Let $R$ carry a $\RingUp$ certificate, and let $M$ carry a $\ModuleUp(R,M)$ certificate. Write $\sim_M$ for the module classifier, $+_M$ for module addition, $0_M$ for module zero, and $\odot_M$ for scalar action. Let $\mathrm{id}_M:M\to M$ be the identity function. Then
$$
\mathsf{LinearMapCert}_R(M,M;\mathrm{id}_M)
$$
holds. The source and target classifier are the same module classifier from \autoref{def:module-classifier-specification}, and the ledger is the identity-function ledger governed by \autoref{def:linearmap-ledger-policy}.

The ten-field fit is: traditional target the ordinary identity linear map on a module; BEDC source a single $\ModuleUp(R,M)$ certificate; carrier the function $\mathrm{id}_M$ together with the rows listed in \autoref{def:module-linearmap-certificate-package}; classifier the pointwise module classifier from \autoref{def:linearmap-classifier-specification}; stability output closure, descent, additivity, scalar compatibility, zero preservation, and identity closure from \autoref{def:linearmap-stability-certificate}; ledger the identity function identifier and the inherited operation ledgers required by \autoref{def:linearmap-ledger-policy}; core theorem this block; exactness predicate the displayed certificate; standard bridge the usual identity linear map; status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Unpack the module certificate by \autoref{def:module-certificate-obligations}. It supplies the module carrier, the module classifier, the additive operation and zero, the scalar action, their stability fields, and their ledgers. By \autoref{def:module-classifier-specification}, the classifier used on the source and target copies of $M$ is the same relation $\sim_M$. The carrier-and-equivalence core of the derived certificate, described in \autoref{def:lean-carrier-naming-certificate}, supplies classifier reflexivity on carried module endpoints.

The rows required by \autoref{def:module-linearmap-certificate-package} are now checked one by one. For output closure, let $x$ be carried in $M$. Since $\mathrm{id}_M(x)=x$, the output is the same carried endpoint.

For source-classifier descent, assume $x\sim_M y$. Applying the identity function changes neither endpoint, so the required comparison
$$
\mathrm{id}_M(x)\sim_M\mathrm{id}_M(y)
$$
is exactly the supplied comparison $x\sim_M y$.

For additivity, let $x$ and $y$ be carried in $M$. The additive closure component listed in \autoref{def:module-stability-certificate} makes $x+_M y$ a carried module endpoint. Both sides of the additive row reduce to that same endpoint:
$$
\mathrm{id}_M(x+_M y)=x+_M y,
\qquad
\mathrm{id}_M(x)+_M\mathrm{id}_M(y)=x+_M y.
$$
Classifier reflexivity on the carried endpoint $x+_M y$ gives
$$
\mathrm{id}_M(x+_M y)\sim_M\mathrm{id}_M(x)+_M\mathrm{id}_M(y).
$$

For scalar compatibility, let $r$ be a carried scalar and let $x$ be carried in $M$. Scalar-action closure from \autoref{def:module-stability-certificate} makes $r\odot_M x$ carried. Again both endpoints are the same expression:
$$
\mathrm{id}_M(r\odot_M x)=r\odot_M x,
\qquad
r\odot_M\mathrm{id}_M(x)=r\odot_M x.
$$
Reflexivity of $\sim_M$ gives the scalar-compatibility row.

For zero preservation, the additive unit $0_M$ is part of the carried additive module data. The two endpoints are both $0_M$:
$$
\mathrm{id}_M(0_M)=0_M.
$$
Reflexivity gives $\mathrm{id}_M(0_M)\sim_M0_M$.

It remains only to record the certificate data. The function identifier is $\mathrm{id}_M$. The additive, scalar, and zero rows above use the existing module operation ledgers together with classifier reflexivity, and the descent row uses the input classifier witness itself. This is exactly the ledger policy of \autoref{def:linearmap-ledger-policy}. Therefore the carrier, source, pattern, classifier, stability, and ledger data satisfy \autoref{def:linearmap-certificate-obligations}, yielding $\mathsf{LinearMapCert}_R(M,M;\mathrm{id}_M)$.
\end{proof}

\begin{theorem}[Module LinearMap composition associativity certificate]
\label{thm:module-linearmap-composition-associativity-certificate}
Let $R$ carry a $\RingUp$ certificate, and let $M$, $N$, $P$, and $Q$ carry $\ModuleUp(R,M)$, $\ModuleUp(R,N)$, $\ModuleUp(R,P)$, and $\ModuleUp(R,Q)$ certificates over the same scalar source. Write $\sim_Q$ for the module classifier of $Q$. If
$$
\mathsf{LinearMapCert}_R(M,N;f),\qquad
\mathsf{LinearMapCert}_R(N,P;g),\qquad
\mathsf{LinearMapCert}_R(P,Q;k),
$$
then both associated triple composites carry certificates
$$
\mathsf{LinearMapCert}_R(M,Q;(k\circ g)\circ f)
\qquad\text{and}\qquad
\mathsf{LinearMapCert}_R(M,Q;k\circ(g\circ f)),
$$
and they are related by the pointwise $\LinearMapUp(M,Q)$ classifier:
$$
(k\circ g)\circ f\sim_{\LinearMapUp(M,Q)}k\circ(g\circ f).
$$
Equivalently, for every carried $x:M$,
$$
((k\circ g)\circ f)(x)\sim_Q(k\circ(g\circ f))(x).
$$
The ten-field fit is: traditional target associativity of composition of $R$-linear maps; BEDC source the three displayed $\mathsf{LinearMapCert}_R$ packages over a common scalar source; carrier the two composite function-with-law packages; classifier the pointwise $Q$-classifier from \autoref{def:linearmap-classifier-specification}; stability composition closure and endpoint reflexivity; ledger the two binary composition ledgers and the $Q$-endpoint reflexivity ledger; core theorem this block; exactness predicate the displayed pointwise comparison; standard bridge the usual associativity of function composition read pointwise; status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:module-linearmap-composition-certificate} to the certificates for $f$ and $g$. This gives
$$
\mathsf{LinearMapCert}_R(M,P;g\circ f).
$$
Applying the same theorem to this composite and to $k$ gives
$$
\mathsf{LinearMapCert}_R(M,Q;k\circ(g\circ f)).
$$

In the other association, apply \autoref{thm:module-linearmap-composition-certificate} first to $g$ and $k$, giving
$$
\mathsf{LinearMapCert}_R(N,Q;k\circ g).
$$
Applying the same theorem to $f$ and this composite gives
$$
\mathsf{LinearMapCert}_R(M,Q;(k\circ g)\circ f).
$$
These are exactly the two certificate clauses required by \autoref{def:module-linearmap-certificate-package} and the composition-closure item of \autoref{def:linearmap-stability-certificate}.

It remains to compare the two certified composites. By \autoref{def:linearmap-classifier-specification}, the $\LinearMapUp(M,Q)$ classifier is pointwise comparison in the codomain classifier. Let $x$ be a carried endpoint of $M$. The output-closure rows in \autoref{def:module-linearmap-certificate-package} give carried endpoints $f(x)$ in $N$, $g(f(x))$ in $P$, and $k(g(f(x)))$ in $Q$. Both associated composites evaluate to this same codomain endpoint:
$$
((k\circ g)\circ f)(x)=k(g(f(x)))=(k\circ(g\circ f))(x).
$$
The module classifier on $Q$ is the carrier classifier of \autoref{def:module-classifier-specification}. Its reflexivity row, supplied by the naming-certificate core in \autoref{def:lean-carrier-naming-certificate}, classifies the carried endpoint $k(g(f(x)))$ with itself. Hence
$$
((k\circ g)\circ f)(x)\sim_Q(k\circ(g\circ f))(x).
$$

Since the carried input $x$ was arbitrary, \autoref{def:linearmap-classifier-specification} packages these endpoint comparisons as
$$
(k\circ g)\circ f\sim_{\LinearMapUp(M,Q)}k\circ(g\circ f).
$$
The ledger field is formed from the two binary composition ledgers governed by \autoref{def:linearmap-ledger-policy}, together with the codomain reflexivity ledger at each point of $Q$.
\end{proof}
