\chapter{A Concrete Naming Certificate for $\PontryaginDualityUp$}
\label{ch:concrete-instances-pontryaginduality-namecert}

The Pontryagin-duality interface $\PontryaginDualityUp$ packages the contravariant self-equivalence on locally compact abelian groups via the Hom-into-circle functor, with the double-dual canonical isomorphism. It depends on $\NameCert_{\TopGroupUp}$ (\autoref{ch:concrete-instances-topgroup-namecert}) and $\NameCert_{\AbGroupUp}$ (\autoref{ch:concrete-instances-abgroup-namecert}), and bridges harmonic-analytic and group-theoretic certificates through the same character classifier.

\section{Carrier definition}
\label{sec:pontryaginduality-carrier}

\begin{definition}[Pontryagin-duality character carrier]
\label{def:pontryaginduality-character-carrier}
A $\PontryaginDualityUp$ carrier is a finite $\mathsf{BHist}$
character-ledger packet over $\NameCert_{\TopGroupUp}$ and
$\NameCert_{\AbGroupUp}$, together with a circle-valued target row read through
$\SOneUp$-style component data. Its rows are the displayed topological-group
source row, the displayed abelian-group operation row, finite character rows
from the shared source to the circle target, pointwise product and inverse
rows for those characters, $\hsame$ comparisons between corresponding source,
target, and character rows, $\Cont$ provenance explaining how each character
row is read from the displayed source and circle rows, and $\mathsf{Pkg}$ rows
naming the two dependency certificates and the circle component packet.

The carrier records only the BEDC character ledger. It does not include Haar
measure, Fourier inversion, local compactness theorems, a completed dual group
topology, or a full duality equivalence.
\end{definition}

\section{The certificate}
\label{sec:pontryaginduality-certificate}

\begin{theorem}[Pontryagin-duality character carrier obligation]
\label{thm:pontryaginduality-character-carrier-obligation}
Every accepted $\PontryaginDualityUp$ packet is read from the character carrier
of \autoref{def:pontryaginduality-character-carrier}: the
$\TopGroupUp/\AbGroupUp$ source rows, the circle-valued target row, the finite
character rows, the pointwise product and inverse rows, the displayed
$\hsame$ comparisons, the $\Cont$ provenance, and the $\mathsf{Pkg}$ source
rows. No additional analytic or host duality object is exposed.
\end{theorem}
\leanchecked{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_obligation}
\leanvariant{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_source\_boundary}
\begin{proof}
Project an accepted packet to the finite character ledger. The carrier
definition lists exactly the source, target, character, algebraic operation,
comparison, continuation, and package rows available to a consumer.

Constructor inspection gives the converse readback boundary: every row named
in the theorem is a coordinate of the finite $\mathsf{BHist}$ carrier, and the
carrier has no coordinate for Haar measure, Fourier inversion, local
compactness theorems, or a completed duality object.
\end{proof}

\begin{theorem}[Pontryagin-duality character classifier stability]
\label{thm:pontryaginduality-character-classifier-stability}
Let $P$ and $P'$ be accepted $\PontryaginDualityUp$ character-ledger packets.
If their displayed $\TopGroupUp$ rows, $\AbGroupUp$ rows, circle-valued target
rows, character rows, pointwise product and inverse rows, $\Cont$ provenance,
and $\mathsf{Pkg}$ source rows are related componentwise by $\hsame$, then the
transported rows form another accepted character carrier with the same visible
classifier surface.
\end{theorem}
\leanchecked{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_stability}
\begin{proof}
Transport first the dependency rows from $\NameCert_{\TopGroupUp}$ and
$\NameCert_{\AbGroupUp}$ and the circle target row. This preserves the finite
source and target boundary through displayed $\hsame$ witnesses.

Next transport each character row and its pointwise product and inverse rows.
The operations are carrier rows in the same finite ledger, so their readback is
preserved by projection along the transported row positions.

Finally transport the $\Cont$ and $\mathsf{Pkg}$ rows. The acceptance
predicate only asks that characters be read through those visible provenance
rows from the displayed source and circle target, so the transported packet is
accepted again.
\end{proof}

\begin{theorem}[Pontryagin-duality dual ledger exactness]
\label{thm:pontryaginduality-dual-ledger-exactness}
The dual ledger exported by an accepted $\PontryaginDualityUp$ packet consists
exactly of finite character rows into the circle-valued target, their
pointwise product and inverse rows, the displayed source and target
comparisons, and the visible $\Cont/\mathsf{Pkg}$ provenance. It exports no
Haar integration row, Fourier transform row, local compactness theorem, or
double-dual equivalence.
\end{theorem}
\leanchecked{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_visible\_dual\_ledger\_boundary}
\leanchecked{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_dual\_ledger\_rows}
\begin{proof}
Use \autoref{thm:pontryaginduality-character-carrier-obligation} to reduce
readback to carrier projection. Every listed dual-ledger row is a coordinate of
the finite packet.

For exactness, inspect the constructors of the packet. They generate character
rows and their pointwise algebraic rows, together with source, target,
comparison, continuation, and package provenance. They do not generate an
analytic measure row, transform row, compactness theorem row, or equivalence
row.
\end{proof}

\begin{theorem}[Pontryagin-duality source boundary]
\label{thm:pontryaginduality-source-boundary}
The dependency boundary of $\PontryaginDualityUp$ is exactly the displayed
$\NameCert_{\TopGroupUp}$ source row, the displayed
$\NameCert_{\AbGroupUp}$ algebraic row, and the circle-valued target component
read in the style of $\SOneUp$. Every accepted character row is sourced through
that boundary by visible $\Cont$ provenance and packaged by $\mathsf{Pkg}$.
\end{theorem}
\leanchecked{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_dependency\_source\_boundary}
\begin{proof}
Read the source rows from
\autoref{def:pontryaginduality-character-carrier}. The carrier names only the
topological-group source, the abelian-group operation surface, and the circle
target packet as external dependency data.

Each character row is accepted only when the displayed $\Cont$ row connects it
to that boundary and the $\mathsf{Pkg}$ row records the same source package.
There is no constructor that sources a character from a host locally compact
abelian group object or an external harmonic-analysis structure.
\end{proof}

\begin{theorem}[Pontryagin-duality NameCert obligation surface]
\label{thm:pontryaginduality-namecert-obligation-surface}
The local $\NameCert_{\PontryaginDualityUp}$ obligation surface consists of
the character carrier of
\autoref{def:pontryaginduality-character-carrier}, carrier readback from
\autoref{thm:pontryaginduality-character-carrier-obligation}, classifier
stability from
\autoref{thm:pontryaginduality-character-classifier-stability}, dual-ledger
exactness from \autoref{thm:pontryaginduality-dual-ledger-exactness}, and the
dependency-source boundary of
\autoref{thm:pontryaginduality-source-boundary}.
\end{theorem}
\begin{proof}
Use the character carrier as the source predicate and its displayed
$\hsame$ rows as the classifier surface. Carrier readback supplies the visible
packet rows, and classifier stability shows that this surface is preserved by
componentwise transport.

Use dual-ledger exactness to identify the complete exported dual character
ledger. Use the source-boundary theorem to bind every character row to the
displayed $\TopGroupUp$, $\AbGroupUp$, and circle target rows.

These clauses assemble the finite local NameCert surface. The assembly is
deliberately limited to the BEDC packet and therefore excludes Haar measure,
Fourier inversion, local compactness theorems, and a full Pontryagin-duality
equivalence.
\end{proof}
\leanchecked{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_namecert\_obligation\_surface}

\begin{theorem}[Pontryagin-duality public character export]
\label{thm:pontryaginduality-public-character-export}
The scoped carrier, classifier-stability, dual-ledger exactness,
source-boundary, and $\NameCert$ obligation-surface rows assemble the public
$\NameCert_{\PontryaginDualityUp}$ export for downstream consumers. The export
exposes only the displayed character rows, target-circle rows, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ provenance.

It exposes no locally compact group theorem, Haar measure, biduality
isomorphism, or host dual group.
\end{theorem}
\begin{proof}
Apply \autoref{def:pontryaginduality-character-carrier} and
\autoref{thm:pontryaginduality-character-carrier-obligation}. These identify
the character carrier and the displayed character rows available for readback.

Next apply \autoref{thm:pontryaginduality-character-classifier-stability} and
\autoref{thm:pontryaginduality-dual-ledger-exactness}. They transport the
classifier surface and exhaust the dual character ledger by the displayed
$\hsame$, $\Cont$, and $\Pkg$ rows.

Finally use \autoref{thm:pontryaginduality-source-boundary} and
\autoref{thm:pontryaginduality-namecert-obligation-surface}. The source rows
and local $\NameCert$ packet repack exactly the target-circle and provenance
fields already named above, leaving no constructor for Haar measure, biduality,
locally compact group theorems, or a host dual group.
\end{proof}

\closureat{PontryaginDualityUp}{seedStr}[BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_stability]
\closureat{PontryaginDualityUp}{obligationStr}[BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_namecert\_obligation\_surface]
\closureat{PontryaginDualityUp}{scopedStr}[BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_namecert\_obligation\_surface]
\begin{closurestatus}{\PontryaginDualityUp}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The scoped boundary binds the $\TopGroupUp$ source row, $\AbGroupUp$ source row, $\SOneUp$-style circle target, finite character rows, pointwise product and inverse rows, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.PontryaginDualityUp.PontryaginDualityCharacterCarrier\_namecert\_obligation\_surface}
  \bridgestatus{none}
  \constructivestory{A finite character packet is assembled from the displayed topological-group and abelian-group rows, a circle-valued target row, finite character rows, transport witnesses, and one provenance packet; every accepted read remains inside that ledger.}
  \notclaimed{This chapter does not claim Haar measure, Fourier inversion, completed dual topology, or double-dual equivalence.}
  \upgradepath{Public closure next exposes the scoped character-ledger boundary as a stable downstream export.}
\end{closurestatus}
