\chapter{A Concrete Naming Certificate for $\TannakaKreinUp$}
\label{ch:concrete-instances-tannakakrein-namecert}

The Tannaka-Krein interface $\TannakaKreinUp$ packages the reconstruction of a compact group from its tensor category of finite-dimensional representations together with a fibre functor to vector spaces. It depends on $\NameCert_{\LieGroupUp}$ (\autoref{ch:concrete-instances-liegroup-namecert}) and $\NameCert_{\MonoidalCatUp}$ (\autoref{ch:concrete-instances-monoidalcat-namecert}), and bridges representation theory and category theory through the same fibre-functor classifier.

\section{Carrier definition}
\label{sec:tannakakrein-carrier}

\begin{definition}[Tannaka-Krein fibre-functor carrier]
\label{def:tannakakrein-fiber-functor-carrier}
A $\TannakaKreinUp$ carrier is a finite $\mathsf{BHist}$ reconstruction
packet over the displayed dependency rows
$\NameCert_{\LieGroupUp}$ and $\NameCert_{\MonoidalCatUp}$. Its visible rows
are the Lie-group source certificate, the monoidal-category source
certificate, a fibre-functor row from representation-object histories into
vector-space histories, representation-object rows in the monoidal source,
the tensor-unit comparison row, tensor-product comparison rows, $\hsame$
witnesses comparing transported group, category, functor, unit, product, and
reconstruction-ledger endpoints, $\Cont$ provenance for the displayed reads,
and $\Pkg$ provenance naming the two source certificates and the
fibre-functor ledger.

The carrier records only this BEDC reconstruction packet. It does not include
Haar measure, analytic compactness, an external compact-group equality, or a
full Tannaka duality theorem.
\end{definition}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_dependency\_endpoint\_readback}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_endpoint\_expanded\_boundary}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_endpoint\_deterministic}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_reconstruction\_provenance\_endpoint\_confluence}

\begin{definition}[Tannaka-Krein monoidal classifier]
\label{def:tannakakrein-monoidal-classifier}
Two $\TannakaKreinUp$ reconstruction packets are identified by the local
monoidal classifier exactly when the displayed $\hsame$ transport relates
their Lie-group rows, monoidal-category rows, fibre-functor rows,
representation-object rows, tensor-unit comparison rows, tensor-product
comparison rows, reconstruction-ledger rows, $\Cont$ provenance rows, and
$\Pkg$ source rows componentwise.

No further equality of compact groups, representation categories, vector
spaces, or analytic reconstruction objects is part of the classifier.
\end{definition}
\leandef{BEDC.Derived.TannakaKreinUp.TannakaKreinMonoidalClassifier}

\section{The certificate}
\label{sec:tannakakrein-certificate}

\begin{theorem}[Tannaka-Krein source boundary]
\label{thm:tannakakrein-liegroup-monoidalcat-source-boundary}
Every downstream consumer of a $\TannakaKreinUp$ packet may read only the
displayed $\NameCert_{\LieGroupUp}$ source certificate, the displayed
$\NameCert_{\MonoidalCatUp}$ source certificate, and the fibre-functor ledger
of \autoref{def:tannakakrein-fiber-functor-carrier}. In particular, the
consumer receives no Haar-measure row, no analytic compactness row, and no
host compact-group object beyond those visible histories.
\end{theorem}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_source\_boundary}
\begin{proof}
Project the packet to the carrier rows. The carrier definition lists the
Lie-group source, monoidal-category source, fibre-functor row,
representation-object rows, tensor-unit and tensor-product comparison rows,
continuation rows, and package provenance.

The consumer boundary is therefore the displayed dependency pair together
with the fibre-functor reconstruction ledger. There is no carrier coordinate
for Haar measure, analytic compactness, or a host compact-group equality, so
those objects cannot be read from the packet.
\end{proof}

\begin{theorem}[Tannaka-Krein fibre-functor classifier stability]
\label{thm:tannakakrein-fiber-functor-classifier-stability}
If two accepted $\TannakaKreinUp$ packets are related by the monoidal
classifier of \autoref{def:tannakakrein-monoidal-classifier}, then transport
along the displayed $\hsame$ rows preserves the carrier, the fibre-functor
row, the representation-object rows, the tensor-unit comparison row, the
tensor-product comparison rows, the reconstruction ledger, and the
$\Cont/\Pkg$ provenance rows.
\end{theorem}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_classifier\_stability}
\begin{proof}
Transport the dependency rows first. The classifier supplies componentwise
$\hsame$ witnesses for the $\NameCert_{\LieGroupUp}$ row and the
$\NameCert_{\MonoidalCatUp}$ row, so the source boundary remains inside the
same displayed pair of certificates.

Next transport the fibre-functor row, representation-object rows, tensor-unit
comparison, tensor-product comparisons, and reconstruction-ledger row. These
are exactly the remaining carrier coordinates, and each is related by a
displayed $\hsame$ witness.

Finally transport the $\Cont$ and $\Pkg$ rows. Since acceptance asks only for
the visible carrier rows and their provenance, the transported packet is again
an accepted carrier with the same tensor comparison surface.
\end{proof}

\begin{theorem}[Tannaka-Krein reconstruction ledger exactness]
\label{thm:tannakakrein-reconstruction-ledger-exactness}
The reconstructed group token exported by a $\TannakaKreinUp$ packet is
determined by the displayed fibre-functor row, representation-object rows,
tensor-unit comparison row, tensor-product comparison rows, reconstruction
ledger, $\Cont$ provenance, and $\Pkg$ source rows. It is not determined by,
and does not expose, host compact-group equality or a full analytic
Tannaka-duality equivalence.
\end{theorem}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_reconstruction\_ledger\_exactness}
\begin{proof}
Unfold the carrier rows. The reconstruction token is read from the same finite
$\mathsf{BHist}$ packet that records the fibre functor, its representation
objects, the tensor-unit comparison, tensor-product comparisons, continuation
routes, and package provenance.

The exactness claim is componentwise: changing any visible reconstruction row
changes the packet boundary, while componentwise $\hsame$ transport of those
rows preserves the token by
\autoref{thm:tannakakrein-fiber-functor-classifier-stability}.

The carrier has no coordinate for host compact-group equality and no row for
full Tannaka duality. Hence the exported token is determined by the displayed
ledger rather than by an external analytic reconstruction theorem.
\end{proof}

\begin{theorem}[Tannaka-Krein NameCert obligation surface]
\label{thm:tannakakrein-namecert-obligation-surface}
The local $\NameCert_{\TannakaKreinUp}$ obligation surface consists of the
carrier of \autoref{def:tannakakrein-fiber-functor-carrier}, the monoidal
classifier of \autoref{def:tannakakrein-monoidal-classifier}, classifier
stability from
\autoref{thm:tannakakrein-fiber-functor-classifier-stability}, the source
boundary from
\autoref{thm:tannakakrein-liegroup-monoidalcat-source-boundary}, and
reconstruction-ledger exactness from
\autoref{thm:tannakakrein-reconstruction-ledger-exactness}.
\end{theorem}
\leanchecked{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_semantic\_name\_certificate}
\begin{proof}
Use the carrier as the accepted-packet predicate and the monoidal classifier
as the visible $\hsame$ comparison relation. The carrier supplies exactly the
Lie-group source row, monoidal-category source row, fibre-functor row,
representation-object rows, tensor comparison rows, continuation rows, and
package provenance.

Classifier stability shows that the carrier and tensor comparison rows are
preserved under componentwise transport. The source-boundary theorem limits
all consumer reads to the two dependency certificates and the displayed
fibre-functor ledger.

Reconstruction-ledger exactness identifies the exported group token with the
visible ledger. The assembled obligation surface is therefore constructive
and finite, using only $\Cont$, $\Pkg$, $\NameCert$, $\LieGroupUp$, and
$\MonoidalCatUp$ rows, while excluding Haar measure, analytic compactness, and
full Tannaka duality.
\end{proof}

\closureat{TannakaKreinUp}{scopedStr}[BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_semantic\_name\_certificate]
\closureat{TannakaKreinUp}{publicStr}[BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_semantic\_name\_certificate]
\begin{closurestatus}{\TannakaKreinUp}
  \theoryclosure{\publicClosure}
  \scopeclosed{The public surface binds the $\LieGroupUp$ source rows, $\MonoidalCatUp$ tensor rows, fibre-functor rows, representation rows, unit and tensor-product rows, reconstruction ledger, $\hsame$ classifier transport, $\Cont$ reconstruction routes, and $\mathsf{Pkg}$ provenance into one finite dependency packet.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.TannakaKreinUp.TannakaKreinFiberFunctorCarrier\_semantic\_name\_certificate}
  \bridgestatus{none}
  \constructivestory{A $\TannakaKreinUp$ packet is assembled from the two source certificates, the fibre-functor row, representation-object rows, tensor-unit and tensor-product comparison rows, reconstruction ledger endpoints, and visible provenance rows; consumers read only this finite reconstruction surface.}
  \notclaimed{This chapter does not claim Haar measure, analytic compactness, host compact-group equality, or full Tannaka duality.}
  \upgradepath{The next paper-side step is a bridge theorem connecting the public reconstruction export to the standard Tannaka-Krein schema.}
\end{closurestatus}
