\chapter{A Concrete Naming Certificate for $\AxisZeckendorfCannotClaimUp$}
\label{ch:concrete-instances-axiszeckendorfcannotclaim-namecert}

This chapter packages the AxisZeckendorf non-claim surface as a finite $\NameCert$ packet. Its carrier records checked negative theorem rows, horizon refusal rows, displayed transport, continuation routes, package provenance, and a local naming row; it does not add an arithmetic interpretation of the carry classifier.

\begin{definition}[AxisZeckendorf cannot-claim registry packet]
\label{def:axis-zeckendorf-cannot-claim-registry-packet}
An $\AxisZeckendorfCannotClaimUp$ registry packet is a finite $\BHist$ tuple
$$
R=(a,b,c,d,e,f,g,h,p,n)
$$
with the following visible coordinates:
\begin{enumerate}
\item $a$ is the negative theorem row for $\mathtt{word\_011}$ and $\mathtt{word\_100}$, citing the non-$\HSame$ separation of \autoref{thm:cannot-claim-011-is-infinity};
\item $b$ is the carry-not-$\HSame$ row, citing \autoref{thm:cannot-claim-carry-is-hsame};
\item $c$ is the non-normality row for $\mathtt{word\_011}$, citing \autoref{thm:cannot-claim-011-is-normal};
\item $d$ is the boundary-zero-spine exclusion row, citing \autoref{thm:cannot-claim-boundary-01-in-zerospine};
\item $e$ is the horizon refusal row for $\FullAxisUp$ as $\RealUp$, citing \autoref{thm:cannot-claim-fullAxis-is-real-horizon};
\item $f$ is the horizon refusal row for $\AxisNatUp$ as $\NatUp$, citing \autoref{thm:cannot-claim-axisNat-replaces-natUp-horizon};
\item $g$ is the horizon refusal row for primitive dimension lift, citing \autoref{thm:cannot-claim-dimLift-primitive-horizon};
\item $h$ is the componentwise $\hsame$ and $\Cont$ route ledger by which consumers inspect exactly the rows $a,b,c,d,e,f,g$;
\item $p$ is the $\Pkg$ provenance over $\BHist$, $\HSame$, $\ZCarryUp$, $\ZeckendorfNormalUp$, $\AxisNatUp$, $\FullAxisUp$, $\DimLiftUp$, $\RealUp$, and $\NameCert$;
\item $n$ is the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row.
\end{enumerate}
The packet has no coordinate for a Real completion, a natural-number replacement, a geometric dimension, a kernel rewrite, a quotient of histories, or a host arithmetic equality.
\end{definition}

\begin{theorem}[AxisZeckendorf cannot-claim public boundary]
\label{thm:axis-zeckendorf-cannot-claim-public-boundary}
Every public read of an accepted $\AxisZeckendorfCannotClaimUp$ registry packet $R=(a,b,c,d,e,f,g,h,p,n)$ factors through the displayed rows $a,b,c,d,e,f,g,h,p,n$. The packet cannot export RealUp completion data, NatUp replacement data, DimLift primitive data, quotient data, or kernel rewrite data.
\end{theorem}
\begin{proof}
Project the displayed $\BHist$ packet in \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}. Its public inventory is exactly the seven refusal rows, the route ledger, the package row, and the local naming row.

The existing non-escape theorem for the registry states that public reads cannot leave that inventory. The carrier itself contains no row for RealUp completion, NatUp replacement, primitive dimension lift, quotient formation, or kernel rewriting.

Thus every public read is a read of $a,b,c,d,e,f,g,h,p,n$, and every excluded positive structure remains outside the exported surface.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim refusal ledger row]
\label{thm:axis-zeckendorf-cannot-claim-refusal-ledger-row}
Every accepted refusal read of an $\AxisZeckendorfCannotClaimUp$ registry packet is determined by exactly one of the seven refusal rows $a,b,c,d,e,f,g$ before the route row $h$, provenance row $p$, or local naming row $n$ is consumed.
\end{theorem}
\begin{proof}
The carrier lists the refusal rows first: $a,b,c,d$ are theorem-level refusals and $e,f,g$ are horizon refusals. These rows are the only coordinates that state refusal content.

The route row $h$ can transport an already selected refusal row, and the rows $p,n$ can record package provenance and local naming. None of $h,p,n$ is itself a refusal source.

The existing refusal transport and non-escape statements keep this selection inside the displayed packet. Therefore an accepted refusal read has exactly one source among $a,b,c,d,e,f,g$ before any route or provenance row is read.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim downstream unblock]
\label{thm:axis-zeckendorf-cannot-claim-downstream-unblock}
Downstream $\AxisNatUp$, $\FullAxisUp$, $\ZCarryUp$, $\ZeckendorfNormalUp$, $\DimLiftUp$, and Real-horizon consumers of an accepted $\AxisZeckendorfCannotClaimUp$ packet may cite only the finite refusal ledger $a,b,c,d,e,f,g,h,p,n$. They receive no positive AxisNat bridge, FullAxis bridge, carry-equality bridge, normal-form bridge, primitive dimension bridge, or RealUp bridge from this registry.
\end{theorem}
\begin{proof}
Start with the public boundary. It confines every downstream read to the displayed finite registry rows and excludes the positive structures that would be needed for bridge data.

Next use the refusal ledger row. A downstream consumer first selects one refusal source among $a,b,c,d,e,f,g$ and then may route or record that selected row through $h,p,n$.

The existing refusal transport theorem keeps the selected row as a refusal under componentwise $\hsame$ and $\Cont$ movement. Hence the downstream consumer can cite the cannot-claim ledger, but it cannot obtain a positive bridge for the listed AxisNat, FullAxis, carry, normal-form, dimension, or Real horizon surfaces.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim registry obligations]
\label{thm:axis-zeckendorf-cannot-claim-registry-obligations}
The local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ surface for the carrier of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet} consists exactly of four finite obligation families:
\begin{enumerate}
\item negative theorem coverage for $\mathtt{word\_011}$ versus $\mathtt{word\_100}$, carry-not-$\HSame$, $\mathtt{word\_011}$ non-normality, and boundary-zero-spine exclusion;
\item horizon refusal coverage for $\FullAxisUp$ as $\RealUp$, $\AxisNatUp$ as $\NatUp$, and primitive dimension lift;
\item componentwise transport and continuation routing for every visible refusal row;
\item ledger exactness through the displayed $\Pkg$ provenance and local $\NameCert$ row.
\end{enumerate}
\end{theorem}
\begin{proof}
The negative theorem rows are precisely $a,b,c,d$ in the registry packet. Each row names an already stated AxisZeckendorf refusal and therefore supplies a finite citation target rather than a new classifier.

The horizon refusal rows are $e,f,g$. They expose only the three named non-claims: no $\FullAxisUp$ field or completion route is read as $\RealUp$, no $\AxisNatUp$ carrier is read as $\NatUp$, and no $\DimLiftUp$ seed is read as a primitive geometric dimension.

Transport and continuation routing are carried by $h$. Since the route ledger is componentwise, it can move a displayed refusal row to an equivalent registry presentation without turning a refusal into a positive bridge.

Finally, $p$ and $n$ record the package and local name boundary. Every public read of the registry passes through the seven refusal rows and these provenance coordinates, so the obligation surface is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[AxisZeckendorf source row coverage]
\label{thm:axis-zeckendorf-cannot-claim-source-row-coverage}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the source rows $a,b,c,d,e,f,g$ exactly cover the checked refusal surface: $a,b,c,d$ are the four negative theorem rows, and $e,f,g$ are the three horizon refusal rows. No source row outside $a,b,c,d,e,f,g$ is available in the carrier.
\end{theorem}
\begin{proof}
Read the carrier definition coordinate by coordinate. Rows $a,b,c,d$ are respectively the $\mathtt{word\_011}$--$\mathtt{word\_100}$ non-$\HSame$ row, the carry-not-$\HSame$ row, the $\mathtt{word\_011}$ non-normality row, and the boundary-zero-spine exclusion row.

Rows $e,f,g$ are respectively the $\FullAxisUp$-as-$\RealUp$ refusal, the $\AxisNatUp$-as-$\NatUp$ refusal, and the primitive dimension-lift refusal. These are precisely the two coverage families named in \autoref{thm:axis-zeckendorf-cannot-claim-registry-obligations}.

The remaining carrier coordinates are $h,p,n$. They provide route, package, and local naming data, not source refusal rows. Hence the seven displayed source rows exhaust the refusal surface of the concrete registry packet.
\end{proof}

\begin{theorem}[AxisZeckendorf refusal transport]
\label{thm:axis-zeckendorf-cannot-claim-refusal-transport}
Let $r$ be any public transport accepted by an $\AxisZeckendorfCannotClaimUp$ registry packet for one of the refusal rows $a,b,c,d,e,f,g$ of $R=(a,b,c,d,e,f,g,h,p,n)$. Then $r$ factors through the componentwise $\hsame$ relation and the displayed $\Cont$ route recorded in row $h$; it cannot pass through a parameter-equivalence transport external to the carrier.
\end{theorem}
\begin{proof}
By \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, row $h$ is the only transport and continuation coordinate of the packet. It is stated componentwise over exactly the visible refusal rows $a,b,c,d,e,f,g$.

Apply the transport family in \autoref{thm:axis-zeckendorf-cannot-claim-registry-obligations}. That theorem identifies componentwise transport and continuation routing as one of the four finite obligation families of the local $\NameCert$ surface.

Since no other transport coordinate appears in $R$, an accepted public movement of a refusal row must use the $\hsame$ and $\Cont$ route displayed by $h$. The packet therefore supplies no external equivalence route that could turn a refusal row into a positive bridge.
\end{proof}

\begin{theorem}[AxisZeckendorf ledger exactness]
\label{thm:axis-zeckendorf-cannot-claim-ledger-exactness}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the provenance rows $p$ and $n$ exhaust the public $\Pkg$ and $\NameCert_{\AxisZeckendorfCannotClaimUp}$ ledger. Consequently the packet cannot export RealUp operations, NatUp replacement, primitive dimension, quotient of histories, kernel rewrite, or standard-model bridge data.
\end{theorem}
\begin{proof}
The carrier definition assigns $p$ to the displayed $\Pkg$ provenance and $n$ to the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row. There is no second package row, no second naming row, and no hidden coordinate in the tuple $R$.

The ledger exactness family in \autoref{thm:axis-zeckendorf-cannot-claim-registry-obligations} reads exactly these two provenance coordinates together with the refusal rows and the route row $h$. Thus every public ledger read has to pass through $p$ or $n$ after the visible refusal surface has been selected.

RealUp operations, NatUp replacement, primitive dimension, quotient formation, kernel rewriting, and standard-model bridge data would each require a positive coordinate outside this ledger. Because the carrier lists no such coordinate, the provenance rows are exact and cannot export any of those structures.
\end{proof}

\begin{theorem}[AxisZeckendorf negative theorem surface]
\label{thm:axis-zeckendorf-cannot-claim-negative-theorem-surface}
Every theorem-level refusal exported by an accepted $\AxisZeckendorfCannotClaimUp$ packet is one of the four negative rows $a,b,c,d$: the $\mathtt{word\_011}$--$\mathtt{word\_100}$ non-$\HSame$ row, the carry-not-$\HSame$ row, the $\mathtt{word\_011}$ non-normality row, or the boundary-zero-spine exclusion row.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}. The only theorem-level refusal rows are $a,b,c,d$.

The route ledger $h$ transports these rows componentwise. It does not introduce a fifth negative theorem, because it has no theorem coordinate apart from the transported row it is carrying.

The package and local naming rows $p,n$ record provenance only. Thus a consumer cannot extract a further theorem-level refusal from the registry beyond the four displayed rows.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim non-escape]
\label{thm:axis-zeckendorf-cannot-claim-non-escape}
Every public read exported by an accepted $\AxisZeckendorfCannotClaimUp$ packet factors through $a,b,c,d,e,f,g,h,p,n$. In particular, the registry cannot be used to construct an $\HSame(\mathtt{word\_011},\mathtt{word\_100})$ witness, a RealUp structure on $\FullAxisUp$, an identification of $\AxisNatUp$ with $\NatUp$, a primitive dimension for $\DimLiftUp$, or a kernel rewrite rule.
\end{theorem}
\begin{proof}
Begin with the registry inventory. The packet contains exactly four negative theorem rows, three horizon refusal rows, the componentwise transport and continuation ledger, package provenance, and a local naming row.

The negative reads factor through $a,b,c,d$, and the horizon reads factor through $e,f,g$. The only admissible movement of those reads is the componentwise $\hsame$ and $\Cont$ routing recorded by $h$.

The package row $p$ and local name row $n$ do not add mathematical structure; they record where the displayed rows come from. Since none of the excluded objects appears as a coordinate, no public consumer can extract a positive bridge, equality, dimension, or rewrite from the registry packet.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim consumer horizon exhaustion]
\label{thm:axis-zeckendorf-cannot-claim-consumer-horizon-exhaustion}
Any downstream consumer of an accepted $\AxisZeckendorfCannotClaimUp$ registry packet can read only the negative theorem rows $a,b,c,d$, the horizon refusal rows $e,f,g$, the transport and route ledger $h$, the provenance row $p$, and the local $\NameCert$ row $n$. Consequently the packet cannot supply a $\RealUp$ completion, a $\NatUp$ replacement, a primitive dimension-lift operation, a kernel rewrite, a quotient of histories, or a standard-model bridge.
\end{theorem}
\begin{proof}
Start with the registry packet of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}. Its displayed rows are exactly $a,b,c,d,e,f,g,h,p,n$.

The theorem-level consumer reads are exhausted by \autoref{thm:axis-zeckendorf-cannot-claim-negative-theorem-surface}: they are precisely the negative rows $a,b,c,d$.

The remaining horizon reads are the refusal rows $e,f,g$, transported and routed through $h$ and recorded through $p,n$. By \autoref{thm:axis-zeckendorf-cannot-claim-non-escape}, this public surface cannot export any coordinate beyond the registry inventory.

Since a $\RealUp$ completion, $\NatUp$ replacement, primitive dimension-lift operation, kernel rewrite, quotient, or standard-model bridge would require a positive coordinate not present in the registry, no downstream consumer can derive one from the packet.
\end{proof}

\begin{theorem}[AxisZeckendorf refusal row determinacy]
\label{thm:axis-zeckendorf-cannot-claim-refusal-row-determinacy}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, every accepted refusal read is determined by exactly one displayed source row among $a,b,c,d,e,f,g$. The rows $a,b,c,d$ determine theorem-level refusals, the rows $e,f,g$ determine horizon refusals, and no accepted refusal read is determined by $h,p$, or $n$.
\end{theorem}
\begin{proof}
The packet definition displays the seven refusal coordinates before any route or provenance coordinate. By \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, $a,b,c,d$ are the negative theorem rows and $e,f,g$ are the horizon refusal rows.

The obligation statement in \autoref{thm:axis-zeckendorf-cannot-claim-registry-obligations} separates these two refusal families from the transport and ledger families. Thus an accepted refusal read first selects one of the displayed source rows, not a route row or a provenance row.

The non-escape theorem \autoref{thm:axis-zeckendorf-cannot-claim-non-escape} and the consumer exhaustion theorem \autoref{thm:axis-zeckendorf-cannot-claim-consumer-horizon-exhaustion} leave no public read outside $a,b,c,d,e,f,g,h,p,n$. Since $h$ only routes and $p,n$ only record provenance, the selected refusal source is unique among $a,b,c,d,e,f,g$.
\end{proof}

\begin{theorem}[AxisZeckendorf transport non-promotion]
\label{thm:axis-zeckendorf-cannot-claim-transport-nonpromotion}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the componentwise $\hsame$ and $\Cont$ ledger $h$ transports refusal rows only as refusal rows. It does not promote any transported row into an $\HSame$ witness, a $\RealUp$ completion, a $\NatUp$ replacement, a primitive dimension, a quotient, or a kernel rewrite.
\end{theorem}
\begin{proof}
The packet definition assigns the only transport and continuation coordinate to $h$. That coordinate is componentwise over the displayed refusal rows, so its source and target data are still rows drawn from $a,b,c,d,e,f,g$.

The routing family in \autoref{thm:axis-zeckendorf-cannot-claim-registry-obligations} records transport and continuation as an obligation on visible refusals. It does not add a positive equality, completion, replacement, dimension, quotient, or rewrite coordinate.

Apply the non-escape boundary of \autoref{thm:axis-zeckendorf-cannot-claim-non-escape}. Any public read exported by the packet factors through the displayed registry rows, and none of the promoted structures appears in that inventory.

Finally, \autoref{thm:axis-zeckendorf-cannot-claim-consumer-horizon-exhaustion} says downstream consumers can read the ledger $h$ only together with the refusal and provenance rows. Therefore componentwise $\hsame$ and $\Cont$ transport preserves the refusal status instead of converting it into a positive BEDC structure.
\end{proof}

\begin{theorem}[AxisZeckendorf provenance exhaustion]
\label{thm:axis-zeckendorf-cannot-claim-provenance-exhaustion}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the provenance row $p$ and the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row $n$ exhaust the public provenance of the registry. They add no new mathematical coordinate beyond the seven refusal rows and the route ledger $h$.
\end{theorem}
\begin{proof}
The registry packet definition names $p$ as the displayed $\Pkg$ provenance row and $n$ as the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row. No further provenance coordinate occurs in $R$.

The ledger exactness family in \autoref{thm:axis-zeckendorf-cannot-claim-registry-obligations} binds the public ledger to the displayed package provenance and local naming row. The provenance read is therefore exhausted by $p$ and $n$ after the refusal row and route row have been selected.

By \autoref{thm:axis-zeckendorf-cannot-claim-non-escape}, the packet cannot export a positive bridge, equality, dimension, quotient, or rewrite outside the registry inventory. By \autoref{thm:axis-zeckendorf-cannot-claim-consumer-horizon-exhaustion}, a downstream consumer has no additional public coordinate to inspect.

Thus $p$ and $n$ close the public provenance surface of the registry and do not contribute another mathematical coordinate.
\end{proof}

\begin{theorem}[AxisZeckendorf refusal kernel scope]
\label{thm:axis-zeckendorf-refusal-kernel-scope}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the seven refusal rows $a,b,c,d,e,f,g$ are scoped over the displayed $\BHist$, $\hsame$, and $\Cont$ registry rows. Every accepted refusal read is determined inside that registry surface and cannot be promoted to a positive arithmetic, RealUp, NatUp, dimension, quotient, or kernel-rewrite claim.
\end{theorem}
\begin{proof}
Read the carrier definition. The rows $a,b,c,d$ are the negative theorem rows, the rows $e,f,g$ are the horizon refusal rows, and the row $h$ is the componentwise transport and continuation route ledger for those rows.

Apply \autoref{thm:axis-zeckendorf-cannot-claim-refusal-row-determinacy}. It assigns each accepted refusal read to exactly one displayed source row among $a,b,c,d,e,f,g$ before any route or provenance row is consumed.

Use \autoref{thm:axis-zeckendorf-cannot-claim-transport-nonpromotion}. The $\hsame$ and $\Cont$ ledger transports refusal rows only as refusal rows, so the registry cannot turn them into a positive bridge, equality, completion, replacement, dimension, quotient, or rewrite coordinate.
\end{proof}

\begin{theorem}[AxisZeckendorf registry classifier scope]
\label{thm:axis-zeckendorf-registry-classifier-scope}
Classifier reads of an accepted $\AxisZeckendorfCannotClaimUp$ registry packet are determined by the displayed rows $a,b,c,d,e,f,g,h,p,n$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}. They are not determined by host arithmetic, a RealUp interpretation of $\FullAxisUp$, a NatUp interpretation of $\AxisNatUp$, or a primitive interpretation of the dimension-lift row.
\end{theorem}
\begin{proof}
The carrier definition gives the classifier only the seven refusal rows, the route ledger, package provenance, and local naming row. No host arithmetic interpretation, RealUp completion, NatUp replacement, or primitive dimension coordinate is present.

Apply \autoref{thm:axis-zeckendorf-cannot-claim-refusal-row-determinacy}. It shows that an accepted refusal read selects a source row from $a,b,c,d,e,f,g$, not an external arithmetic or semantic interpretation.

Then use \autoref{thm:axis-zeckendorf-cannot-claim-transport-nonpromotion}. Transport through $h$ preserves refusal status under the displayed $\hsame$ and $\Cont$ rows and cannot turn the selected registry row into any of the excluded positive structures.
\end{proof}

\begin{theorem}[AxisZeckendorf ledger route scope]
\label{thm:axis-zeckendorf-ledger-route-scope}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the $\Pkg$ row $p$ and local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row $n$ exhaust the consumer ledger route after the refusal source and componentwise route ledger have been selected. Thus every consumer access to the cannot-claim registry factors through the displayed refusal rows, $h$, $p$, and $n$.
\end{theorem}
\begin{proof}
Start with the displayed registry packet. It lists the refusal source rows $a,b,c,d,e,f,g$, the componentwise route ledger $h$, the package row $p$, and the local naming row $n$.

Use \autoref{thm:axis-zeckendorf-cannot-claim-refusal-row-determinacy} to choose the refusal row inspected by the consumer. Use \autoref{thm:axis-zeckendorf-cannot-claim-transport-nonpromotion} to route that row only through the displayed $\hsame$ and $\Cont$ ledger $h$.

Finally apply \autoref{thm:axis-zeckendorf-cannot-claim-provenance-exhaustion}. The rows $p$ and $n$ close the public provenance after the refusal and route rows have been selected, and no second package, naming, bridge, quotient, dimension, completion, replacement, or rewrite route is available.
\end{proof}

\begin{theorem}[AxisZeckendorf negative row scope]
\label{thm:axis-zeckendorf-cannot-claim-negative-row-scope}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the four negative theorem rows $a,b,c,d$ are scoped exactly over the displayed $\BHist$, $\HSame$, and $\Cont$ route surface. They are not promoted to positive equality, quotient, dimension, completion, replacement, or kernel-rewrite data.
\end{theorem}
\begin{proof}
The packet definition displays $a,b,c,d$ as the four theorem-level refusal rows before the horizon, route, provenance, and naming coordinates. The registry obligations assign their NameCert role to that visible refusal surface.

Apply refusal-row determinacy to separate $a,b,c,d$ from the horizon rows and from $h,p,n$. Transport non-promotion then fixes the $\BHist$, $\HSame$, and $\Cont$ route surface as transport of refusals only, and non-escape prevents any promoted positive structure from entering the scope.
\end{proof}

\begin{theorem}[AxisZeckendorf horizon refusal scope]
\label{thm:axis-zeckendorf-cannot-claim-horizon-refusal-scope}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the horizon refusal rows $e,f,g$ scope exactly the refusal of $\RealUp$ completion, $\NatUp$ replacement, and primitive dimension lift. They add no positive completion row, no Nat replacement carrier, and no primitive-dimension witness.
\end{theorem}
\begin{proof}
The packet definition names $e,f,g$ as the three horizon refusal rows. The registry-obligation and consumer-horizon-exhaustion theorems keep those rows in the public refusal inventory rather than in a positive construction inventory.

Refusal-row determinacy identifies each horizon read with one of $e,f,g$. Transport non-promotion and provenance exhaustion then show that $h,p,n$ can only route and record these refusals, while non-escape rules out the corresponding positive $\RealUp$, $\NatUp$, and primitive-dimension objects.
\end{proof}

\begin{theorem}[AxisZeckendorf FullAxis Real refusal boundary]
\label{thm:axis-zeckendorf-fullaxis-real-refusal-boundary}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, every consumer that reads the FullAxis-as-Real horizon row $e$ receives only the displayed $\BHist$ refusal row $e$, its componentwise $\hsame$ and $\Cont$ route through $h$, the $\Pkg$ provenance row $p$, and the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row $n$. The read supplies no promoted $\RealUp$ completion for $\FullAxisUp$ and no hidden real-valued axis reconstruction.
\end{theorem}
\begin{proof}
The carrier definition places $e$ among the three horizon refusal rows, and \autoref{thm:axis-zeckendorf-cannot-claim-horizon-refusal-scope} identifies it with the refusal of a $\RealUp$ completion read for the full axis surface.

Apply refusal-row determinacy to lock the consumer read to the displayed row $e$. Apply transport non-promotion to the componentwise route $h$: the $\hsame$ and $\Cont$ data can only carry the same refusal row, not a positive completion object.

Finally use provenance exhaustion. The rows $p$ and $n$ record the package and local name after the refusal source has already been selected, and non-escape excludes every second route to a real-valued axis carrier. Thus the consumer receives the finite refusal package and no promoted $\RealUp$ completion.
\end{proof}

\begin{theorem}[AxisZeckendorf AxisNat Nat refusal boundary]
\label{thm:axis-zeckendorf-axisnat-nat-refusal-boundary}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, every consumer that reads the AxisNat-as-Nat horizon row $f$ receives only the displayed $\BHist$ refusal row $f$, its componentwise $\hsame$ and $\Cont$ route through $h$, the $\Pkg$ provenance row $p$, and the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row $n$. The read supplies no promoted $\NatUp$ replacement for $\AxisNatUp$ and no hidden natural-number carrier.
\end{theorem}
\begin{proof}
The carrier definition lists $f$ as the AxisNat-as-Nat horizon refusal row, while \autoref{thm:axis-zeckendorf-cannot-claim-horizon-refusal-scope} fixes the row as a refusal rather than a positive $\NatUp$ replacement.

Refusal-row determinacy assigns the accepted consumer read to $f$ before any route, package, or naming coordinate is consumed. Transport non-promotion then keeps the $h$ route inside the same refusal status; the displayed $\hsame$ and $\Cont$ data do not create a natural-number carrier.

Provenance exhaustion and non-escape close the boundary. The rows $p,n$ only record the accepted cannot-claim package, and the registry has no second coordinate from which a $\NatUp$ replacement for $\AxisNatUp$ can be read.
\end{proof}

\begin{theorem}[AxisZeckendorf dimension-lift primitive refusal boundary]
\label{thm:axis-zeckendorf-dimlift-primitive-refusal-boundary}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, every consumer that reads the primitive dimension-lift horizon row $g$ receives only the displayed $\BHist$ refusal row $g$, its componentwise $\hsame$ and $\Cont$ route through $h$, the $\Pkg$ provenance row $p$, and the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row $n$. The read supplies no primitive dimension witness and no promoted dimension-lift carrier.
\end{theorem}
\begin{proof}
The carrier definition displays $g$ as the primitive dimension-lift refusal row, and \autoref{thm:axis-zeckendorf-cannot-claim-horizon-refusal-scope} keeps that row inside the horizon-refusal surface.

Use refusal-row determinacy to identify $g$ as the unique source of the accepted read. The componentwise route $h$ is governed by transport non-promotion, so its $\hsame$ and $\Cont$ data can replay the refusal but cannot construct a primitive dimension witness.

The package and naming rows are exhausted by $p$ and $n$. Together with non-escape, this leaves the consumer with the finite refusal row and its recorded route, provenance, and name, and with no promoted dimension-lift object.
\end{proof}

\begin{theorem}[AxisZeckendorf audit-gate consumption]
\label{thm:axis-zeckendorf-cannot-claim-audit-gate-consumption}
Any audit-gate consumer of an accepted $\AxisZeckendorfCannotClaimUp$ registry packet
$$
R=(a,b,c,d,e,f,g,h,p,n)
$$
must read refusal rows through $a,b,c,d,e,f,g$ and the route, provenance, and naming rows $h,p,n$. The consumer cannot turn the registry into $\RealUp$ completion data, $\NatUp$ replacement data, primitive dimension data, a quotient, a kernel rewrite, or standard-model bridge data.
\end{theorem}
\begin{proof}
Begin with refusal-row determinacy. It assigns every accepted refusal read to one displayed source row among $a,b,c,d,e,f,g$ before any route or provenance row is consumed.

Apply transport non-promotion to the audit route. The componentwise $\hsame$ and $\Cont$ ledger $h$ transports refusal rows only as refusal rows, so it cannot promote the selected source into a positive completion, replacement, dimension, quotient, or rewrite coordinate.

Finally use provenance exhaustion together with negative-row and horizon-refusal scope. The rows $p,n$ record the refusal route without adding mathematical data, and the scoped refusal theorems exclude the corresponding positive structures. Thus an audit-gate consumer receives only the displayed cannot-claim registry.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim audit-gate boundary]
\label{thm:axis-zeckendorf-cannot-claim-audit-gate-boundary}
Every audit consumer of an accepted $\AxisZeckendorfCannotClaimUp$ registry packet $R=(a,b,c,d,e,f,g,h,p,n)$ factors through the seven refusal rows $a,b,c,d,e,f,g$ together with the route, provenance, and local naming rows $h,p,n$. Such a consumer cannot read $\RealUp$, $\NatUp$, primitive dimension, quotient, kernel rewrite, or standard bridge data from the packet.
\end{theorem}
\begin{proof}
Start with audit-gate consumption. It confines every audit-facing read to the selected refusal source and to the displayed rows $h,p,n$.

Use non-escape and transport non-promotion for the boundary. The registry has no coordinate for RealUp completion, NatUp replacement, primitive dimension, quotient, kernel rewrite, or standard bridge data, and the route row $h$ transports only refusal rows.

Finally apply provenance exhaustion and consumer horizon exhaustion. The rows $p,n$ record package and local naming data without adding a mathematical coordinate, and every downstream audit read remains inside the displayed registry packet.
\end{proof}

\begin{definition}[AxisZeckendorf cannot-claim route-provenance triad]
\label{def:axis-zeckendorf-cannot-claim-route-provenance-triad}
After a selected refusal source $x\in\{a,b,c,d,e,f,g\}$ in the carrier $R=(a,b,c,d,e,f,g,h,p,n)$, the route-provenance triad is
$$
(h,p,n),
$$
where $h$ is the componentwise $\hsame$ and $\Cont$ route for the selected refusal row, $p$ is the $\Pkg$ provenance row for the cannot-claim registry, and $n$ is the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row. The triad is read only after the refusal source has been chosen, and it is not itself a new refusal source.
\end{definition}

\begin{theorem}[AxisZeckendorf route-provenance triad obligations]
\label{thm:axis-zeckendorf-cannot-claim-route-provenance-triad-obligations}
For the carrier $R=(a,b,c,d,e,f,g,h,p,n)$ and the triad $(h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-route-provenance-triad}, the local obligation surface consists of carrier admission, transport through the displayed $\hsame$ and $\Cont$ route, ledger exactness through $p,n$, non-promotion of every selected refusal source, and exhaustion of all audit and downstream consumers by the selected source row together with the triad.
\end{theorem}
\begin{proof}
Carrier admission is the registry packet of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}. The selected refusal source is one of $a,b,c,d,e,f,g$, and the triad supplies only the displayed route, provenance, and local naming rows.

Transport and non-promotion come from \autoref{thm:axis-zeckendorf-cannot-claim-transport-nonpromotion}. The row $h$ may carry the selected refusal through $\hsame$ and $\Cont$, but it cannot promote the refusal into a positive equality, completion, replacement, dimension, quotient, rewrite, or bridge.

Ledger exactness is supplied by \autoref{thm:axis-zeckendorf-cannot-claim-provenance-exhaustion}. The rows $p,n$ exhaust the package and local naming surface, so the triad has no hidden ledger coordinate.

Finally apply \autoref{thm:axis-zeckendorf-cannot-claim-consumer-horizon-exhaustion} and the audit-gate boundary of \autoref{thm:axis-zeckendorf-cannot-claim-audit-gate-boundary}. Every public consumer first chooses a refusal row and then reads only the triad, which proves consumer exhaustion without adding any forbidden positive structure.
\end{proof}

\begin{theorem}[AxisZeckendorf negative refusal coverage]
\label{thm:axis-zeckendorf-cannot-claim-negative-refusal-coverage}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the negative refusal coverage consumed by the $\AxisZeckendorfCannotClaimUp$ obligation package is exactly the four rows $a,b,c,d$. These rows cover the non-$\HSame$ separation of $\mathtt{word\_011}$ and $\mathtt{word\_100}$, the carry-not-$\HSame$ refusal, the $\mathtt{word\_011}$ non-normality refusal, and the boundary-zero-spine refusal, and they do not promote to a positive equality, quotient, completion, dimension, replacement, or kernel-rewrite row.
\end{theorem}
\begin{proof}
Start with the carrier definition. The packet lists $a,b,c,d$ as the four negative theorem rows before the horizon, route, package, and local naming coordinates.

Use refusal-row determinacy and negative-row scope. \autoref{thm:axis-zeckendorf-cannot-claim-refusal-row-determinacy} selects one source row among $a,b,c,d,e,f,g$ for every accepted refusal read, while \autoref{thm:axis-zeckendorf-cannot-claim-negative-row-scope} identifies the theorem-level source family as exactly $a,b,c,d$.

Finally apply transport non-promotion and audit-gate consumption. The route row $h$ may carry these refusals through $\hsame$ and $\Cont$, but \autoref{thm:axis-zeckendorf-cannot-claim-transport-nonpromotion} and \autoref{thm:axis-zeckendorf-cannot-claim-audit-gate-consumption} prevent that route from becoming a positive BEDC object.
\end{proof}

\begin{theorem}[AxisZeckendorf horizon refusal coverage]
\label{thm:axis-zeckendorf-cannot-claim-horizon-refusal-coverage}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the horizon refusal coverage consumed by the $\AxisZeckendorfCannotClaimUp$ obligation package is exactly the three rows $e,f,g$. These rows cover the refusal of $\FullAxisUp$ as $\RealUp$, the refusal of $\AxisNatUp$ as $\NatUp$, and the refusal of primitive dimension lift, with no hidden positive carrier behind the horizon.
\end{theorem}
\begin{proof}
Read the horizon coordinates from the carrier definition. Rows $e,f,g$ are the only rows named for the three horizon-facing non-claims.

Apply horizon-refusal scope and refusal-row determinacy. \autoref{thm:axis-zeckendorf-cannot-claim-horizon-refusal-scope} fixes $e,f,g$ as the $\RealUp$, $\NatUp$, and primitive-dimension refusal surface, and \autoref{thm:axis-zeckendorf-cannot-claim-refusal-row-determinacy} keeps each accepted horizon read on one displayed source row.

Use transport non-promotion, provenance exhaustion, and audit-gate consumption for the public route. The rows $h,p,n$ can route and record the selected horizon refusal, but they cannot promote it to a completion, replacement, dimension, quotient, rewrite, or standard bridge.
\end{proof}

\begin{theorem}[AxisZeckendorf ledger consumer exactness]
\label{thm:axis-zeckendorf-cannot-claim-ledger-consumer-exactness}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, every public consumer of the cannot-claim ledger routes through $h,p,n$ after selecting one refusal source among $a,b,c,d,e,f,g$. The row $h$ supplies the componentwise $\hsame$ and $\Cont$ route, the row $p$ supplies the displayed $\Pkg$ provenance, and the row $n$ supplies the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ record.
\end{theorem}
\begin{proof}
Begin with the source choice. Refusal-row determinacy selects one row among $a,b,c,d,e,f,g$ before any ledger coordinate is consumed.

Next route the selected row through $h$. Transport non-promotion says that the componentwise $\hsame$ and $\Cont$ ledger carries the same refusal status and cannot create a positive equality, completion, replacement, dimension, quotient, or rewrite.

Finally read the provenance and local name through $p,n$. Provenance exhaustion identifies these rows as the whole public package and naming surface, and audit-gate consumption confines every consumer of the registry to the selected refusal row together with $h,p,n$.
\end{proof}

\begin{theorem}[AxisZeckendorf root-unblock package]
\label{thm:axis-zeckendorf-cannot-claim-root-unblock-package}
The $\AxisZeckendorfCannotClaimUp$ root-unblock package is the finite $\NameCert$ obligation surface obtained by combining negative refusal coverage on $a,b,c,d$, horizon refusal coverage on $e,f,g$, and ledger consumer exactness through $h,p,n$. This surface is over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\ZCarryUp$, $\ZeckendorfNormalUp$, $\AxisNatUp$, $\FullAxisUp$, $\DimLiftUp$, $\RealUp$, and $\NatUp$, and it exports no Real completion, Nat replacement, primitive dimension, quotient, kernel rewrite, or standard bridge.
\end{theorem}
\begin{proof}
First assemble the refusal sources. \autoref{thm:axis-zeckendorf-cannot-claim-negative-refusal-coverage} supplies the four negative rows $a,b,c,d$, and \autoref{thm:axis-zeckendorf-cannot-claim-horizon-refusal-coverage} supplies the three horizon rows $e,f,g$.

Next attach the public ledger. \autoref{thm:axis-zeckendorf-cannot-claim-ledger-consumer-exactness} routes every consumer through $h,p,n$, so the selected refusal row is carried only by displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ evidence.

Finally use audit-gate consumption and the existing scope boundaries. Negative-row scope, horizon-refusal scope, transport non-promotion, and provenance exhaustion keep the package on the cannot-claim surface over $\ZCarryUp$, $\ZeckendorfNormalUp$, $\AxisNatUp$, $\FullAxisUp$, $\DimLiftUp$, $\RealUp$, and $\NatUp$ without adding any promoted BEDC object.
\end{proof}

\begin{theorem}[AxisZeckendorf ledger route scope]
\label{thm:axis-zeckendorf-cannot-claim-ledger-route-scope}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the rows $h,p,n$ are the only public transport, package, and $\NameCert$ route for all consumers of the registry. Every public consumer must read refusal data through the componentwise $\hsame$ and $\Cont$ ledger $h$, the $\Pkg$ provenance row $p$, and the local naming row $n$.
\end{theorem}
\begin{proof}
The carrier definition assigns route data to $h$, package provenance to $p$, and local naming to $n$. The registry obligations bind these rows to the same finite refusal inventory $a,b,c,d,e,f,g$.

Consumer-horizon exhaustion and provenance exhaustion leave no second transport, package, or naming coordinate for a public read. Together with non-escape and transport non-promotion, this forces every consumer route through $h,p,n$ without adding a positive bridge, quotient, dimension, completion, replacement, or rewrite row.
\end{proof}

\begin{theorem}[AxisZeckendorf refusal source lock]
\label{thm:axis-zeckendorf-cannot-claim-source-lock}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, every accepted refusal reader first locks onto exactly one source row among $a,b,c,d,e,f,g$ before it consumes the route ledger $h$, the provenance row $p$, or the local naming row $n$.
\end{theorem}
\begin{proof}
Carrier projection gives the only refusal source inventory: the negative theorem rows $a,b,c,d$ and the horizon refusal rows $e,f,g$. The route and provenance coordinates are listed only after that refusal source surface has been displayed.

Apply refusal-row determinacy. It assigns each accepted refusal read to one displayed source row among $a,b,c,d,e,f,g$, and it excludes $h,p,n$ as refusal sources.

Transport non-promotion then fixes the role of $h$: it may route the selected refusal through componentwise $\hsame$ and $\Cont$ data, but it cannot choose a new source row or turn the selected source into a positive BEDC object. Provenance exhaustion fixes $p,n$ as recording rows only, so the lock onto the unique source row precedes every route or provenance read.
\end{proof}

\begin{theorem}[AxisZeckendorf refusal reader totality]
\label{thm:axis-zeckendorf-cannot-claim-refusal-reader-totality}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$, the displayed refusal families $a,b,c,d$ and $e,f,g$ cover all public refusal reads exported by an accepted $\AxisZeckendorfCannotClaimUp$ packet. No public refusal reader can be sourced by $h,p,n$ or by data outside the carrier.
\end{theorem}
\begin{proof}
The registry carrier exposes exactly two refusal families. Rows $a,b,c,d$ are theorem-level refusals, and rows $e,f,g$ are horizon refusals.

Negative theorem surface covers all theorem-level refusal reads, while consumer-horizon exhaustion covers the remaining horizon-facing reads. Together they leave only transport through $h$ and recording through $p,n$ after a refusal source has already been selected.

Refusal-row determinacy rules out $h,p,n$ as source rows. Non-escape rules out every external source: the packet contains no RealUp completion, NatUp replacement, primitive dimension, quotient, host arithmetic, or kernel-rewrite coordinate from which another refusal reader could be drawn.
\end{proof}

\begin{theorem}[AxisZeckendorf gap ledger exhaustion]
\label{thm:axis-zeckendorf-cannot-claim-gap-ledger-exhaustion}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$, the rows $h,p,n$ exhaust all GAP-facing route and provenance reads of the cannot-claim registry. These rows cannot promote any refusal source to $\RealUp$, $\NatUp$, primitive dimension, quotient, or kernel-rewrite data.
\end{theorem}
\begin{proof}
Ledger route scope identifies $h,p,n$ as the only public transport, package, and local naming route after a refusal source has been selected. Provenance exhaustion shows that $p$ and $n$ add no mathematical coordinate beyond the seven refusal rows and the route ledger $h$.

Transport non-promotion gives the decisive boundary for the route row. The componentwise $\hsame$ and $\Cont$ ledger transports refusal rows only as refusal rows, so it cannot create a positive $\RealUp$ completion, $\NatUp$ replacement, primitive dimension, quotient, or rewrite object.

Finally, consumer-horizon exhaustion and non-escape close the public route surface. Any GAP-facing consumer reads only the displayed refusal rows together with $h,p,n$, and none of those rows carries the promoted structures named in the statement.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim dependency interface]
\label{thm:axis-zeckendorf-cannot-claim-dependency-interface}
Every admitted $\AxisZeckendorfCannotClaimUp$ packet records its dependency-facing rows for $\AxisNatUp$, $\ZCarryUp$, $\ZeckendorfNormalUp$, $\DimLiftUp$, $\FullAxisUp$, $\NatUp$, and $\RealUp$ as visible $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$ data. The $\hsame$ route row preserves those dependency rows componentwise, and no consumer may read one of the seven dependencies through an unrecorded carrier, package, or naming witness.
\end{theorem}
\begin{proof}
Start with the carrier $R=(a,b,c,d,e,f,g,h,p,n)$. The negative theorem rows and horizon refusal rows list the dependency-facing surface before any public route is exposed, while the rows $h,p,n$ give the componentwise $\hsame$ and $\Cont$ route, package provenance, and local $\NameCert$ records.

The registry obligations and source-row coverage identify the seven visible rows that a consumer may cite for $\AxisNatUp$, $\ZCarryUp$, $\ZeckendorfNormalUp$, $\DimLiftUp$, $\FullAxisUp$, $\NatUp$, and $\RealUp$. Refusal transport then keeps those rows inside the same $\BHist$ packet; it does not replace them by host arithmetic, a primitive dimension, a completion object, or a kernel rewrite.

Ledger exactness and gap ledger exhaustion close the interface. Since the source lock, refusal reader totality, and negative theorem surface have already exhausted the accepted reads, every dependency-facing consumer must pass through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and cannot appeal to a second carrier.
\end{proof}

\begin{theorem}[AxisNat and ZCarry refusal rows do not promote]
\label{thm:axis-zeckendorf-cannot-claim-axisnat-zcarry-refusal}
In every admitted $\AxisZeckendorfCannotClaimUp$ packet, the $\AxisNatUp$ and $\ZCarryUp$ readbacks may feed the refusal ledger, but they cannot be converted into a $\FullAxisUp$ carrier row or a $\RealUp$ carrier row without an explicit $\NameCert$ witness for that promoted carrier. The available data remain the displayed $\BHist$ refusal rows, componentwise $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local cannot-claim $\NameCert$ row.
\end{theorem}
\begin{proof}
Read the $\AxisNatUp$ and $\ZCarryUp$ rows through the dependency interface. Their role is refusal-facing: source-row coverage and the negative theorem surface place them among the rows that explain why the cannot-claim packet has no positive axis reconstruction.

Apply refusal transport and ledger exactness. The $\hsame$ and $\Cont$ route can replay the same refusal row inside the accepted $\BHist$ packet, and $p,n$ can package and name that refusal. None of these operations introduces a $\NameCert_{\FullAxisUp}$ or $\NameCert_{\RealUp}$ witness.

Finally use the source lock, refusal reader totality, and gap ledger exhaustion. They force every public read through the displayed refusal inventory and exclude an external $\FullAxisUp$ or $\RealUp$ carrier row. Thus AxisNat and ZCarry readbacks remain ledger data unless a separate promoted $\NameCert$ witness is supplied.
\end{proof}

\begin{theorem}[Real readback non-promotion]
\label{thm:axis-zeckendorf-cannot-claim-real-readback-nonpromotion}
Every $\RealUp$-facing consumer of an admitted $\AxisZeckendorfCannotClaimUp$ packet receives only the recorded refusal and readback package. It reads the visible $\BHist$ rows, the componentwise $\hsame$ and $\Cont$ ledger, the $\Pkg$ provenance row, and the local $\NameCert$ row; it does not receive a real-valued axis reconstruction or a hidden completion carrier.
\end{theorem}
\begin{proof}
The carrier and registry obligations expose the $\RealUp$-facing entry only as part of the refusal surface. Source-row coverage and the negative theorem surface identify the row as a readback boundary, not as a real-valued axis carrier.

Refusal transport carries that boundary through $h$. The componentwise $\hsame$ and $\Cont$ data preserve the same refusal record, while $p$ and $n$ package and name the same cannot-claim packet.

Gap ledger exhaustion gives the final non-promotion step. A $\RealUp$ consumer can inspect the recorded refusal package, but the packet has no row for a $\RealUp$ completion, host real arithmetic, or reconstructed axis value. The source lock and refusal reader totality leave no second read path from which such a carrier could be obtained.
\end{proof}

\begin{theorem}[AxisZeckendorf root-unblock refusal package]
\label{thm:axis-zeckendorf-root-unblock-refusal-package}
For the concrete carrier $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the rows $a,b,c,d,e,f,g$ package the refusal source consumed by downstream unary-direction and axis-carry certificates. The rows $h,p,n$ supply the only accepted route, package provenance, and local $\NameCert$ data for that downstream read.
\end{theorem}
\begin{proof}
Read the carrier inventory. The negative refusal rows $a,b,c,d$ are fixed by negative refusal coverage, and the horizon refusal rows $e,f,g$ are fixed by horizon refusal coverage.

Use root-unblock package. It combines those two refusal families with ledger consumer exactness through $h,p,n$, so downstream certificates receive a finite refusal source rather than a positive arithmetic carrier.

Transport non-promotion and provenance exhaustion give the boundary. The route row $h$ may replay the selected refusal, while $p,n$ record provenance and local naming, but none of the three rows creates a promoted object for unary-direction or axis-carry consumers.
\end{proof}

\begin{theorem}[AxisZeckendorf root-unblock downstream boundary]
\label{thm:axis-zeckendorf-root-unblock-downstream-boundary}
Any downstream consumer of the $\AxisZeckendorfCannotClaimUp$ root-unblock package may read only the refusal rows $a,b,c,d,e,f,g$ together with the route, provenance, and local naming rows $h,p,n$. It may cite the package as a refusal source for unary-direction and axis-carry work, but it may not inspect host arithmetic, a hidden carrier, or any row outside the displayed registry.
\end{theorem}
\begin{proof}
Begin with consumer-horizon exhaustion and refusal reader totality. Together they cover every accepted public refusal read by the displayed refusal rows $a,b,c,d,e,f,g$.

Next use ledger consumer exactness and gap ledger exhaustion. After a refusal source has been selected, the only public route and provenance rows are $h,p,n$.

The downstream restriction follows from transport non-promotion. Since $h$ carries refusal rows only as refusal rows and $p,n$ add no mathematical coordinate, unary-direction and axis-carry consumers cannot obtain a hidden carrier, host arithmetic interpretation, quotient, completion, replacement, dimension, or rewrite from the package.
\end{proof}

\begin{theorem}[AxisZeckendorf downstream route refusal]
\label{thm:axis-zeckendorf-cannot-claim-downstream-route-refusal}
Any $\UnaryDirectionBridgeUp$ consumer of an accepted $\AxisZeckendorfCannotClaimUp$ packet may read the cannot-claim source only through the seven refusal rows $a,b,c,d,e,f,g$ and the route and provenance rows $h,p,n$ already exposed by the registry. The consumer route of \autoref{ch:concrete-instances-unarydirectionbridge-namecert} may cite these rows as a downstream refusal source, but it cannot read a positive direction bridge, host arithmetic carrier, $\RealUp$ completion, $\NatUp$ replacement, primitive dimension, quotient, or kernel rewrite from the packet.
\end{theorem}
\begin{proof}
Start with the consumer horizon exhaustion theorem. \autoref{thm:axis-zeckendorf-cannot-claim-consumer-horizon-exhaustion} says that every downstream consumer is confined to the displayed refusal rows $a,b,c,d,e,f,g$ together with the route, provenance, and local naming rows $h,p,n$.

Next use the root-unblock downstream boundary of \autoref{thm:axis-zeckendorf-root-unblock-downstream-boundary}. It identifies the downstream package as a refusal source for later unary-direction and axis-carry work, not as a hidden positive carrier.

Finally apply ledger consumer exactness and transport non-promotion. The $\UnaryDirectionBridgeUp$ consumer named by \autoref{ch:concrete-instances-unarydirectionbridge-namecert} can replay the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, but no row in the registry promotes a refusal into the positive structures excluded in the statement.
\end{proof}

\begin{theorem}[AxisZeckendorf root-unblock ledger non-escape]
\label{thm:axis-zeckendorf-root-unblock-ledger-nonescape}
The downstream $\AxisZeckendorfCannotClaimUp$ root-unblock ledger cannot yield a positive $\RealUp$ row, a positive $\NatUp$ row, a primitive $\DimLiftUp$ row, a quotient row, or a kernel rewrite row. Every such requested read is routed back to the refusal source $a,b,c,d,e,f,g$ and the ledger rows $h,p,n$.
\end{theorem}
\begin{proof}
Start from the existing non-escape theorem. It excludes RealUp operations, NatUp replacement, primitive dimension, quotient of histories, kernel rewrite, and standard-model bridge data from the accepted registry packet.

Apply refusal-row determinacy. Any accepted downstream refusal read first selects one row among $a,b,c,d,e,f,g$, so the requested positive object cannot be sourced by $h,p,n$.

Then apply transport non-promotion. The componentwise $\hsame$ and $\Cont$ ledger $h$ preserves the selected row as a refusal and cannot promote it to a positive RealUp, NatUp, DimLiftUp, quotient, or rewrite row.

Finally use provenance exhaustion. The rows $p,n$ close the public package and naming route without adding another mathematical coordinate, so the downstream ledger has no escape path beyond the displayed refusal package.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim root obligation surface]
\label{thm:axis-zeckendorf-cannot-claim-root-obligation-surface}
For the displayed $\BHist$ registry packet $R=(a,b,c,d,e,f,g,h,p,n)$ of \autoref{def:axis-zeckendorf-cannot-claim-registry-packet}, the root obligation surface consists exactly of the four negative theorem rows $a,b,c,d$, the three horizon refusal rows $e,f,g$, the $\hsame$ transport and $\Cont$ route ledger $h$, the $\Pkg$ provenance row $p$, and the local $\NameCert_{\AxisZeckendorfCannotClaimUp}$ row $n$. Each accepted root read must expose the refusal row it consumes, its transport through $h$, its route through $h$, its provenance in $p$, and its local naming in $n$.
\end{theorem}
\begin{proof}
Begin with refusal coverage. Negative refusal coverage accounts for $a,b,c,d$, and horizon refusal coverage accounts for $e,f,g$.

Use the root-unblock package to combine those rows with the downstream route surface. It identifies the registry as a finite refusal source whose public reads are carried by the displayed $\BHist$ packet rather than by host arithmetic.

Finally apply ledger non-escape. The rows $h,p,n$ transport, route, package, and name the refusal surface, but they add no positive $\RealUp$, $\NatUp$, $\DimLiftUp$, quotient, or kernel-rewrite coordinate. Hence the root obligation surface is exactly the displayed registry packet.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim downstream blocker scope]
\label{thm:axis-zeckendorf-cannot-claim-downstream-blocker-scope}
Every downstream blocker that cites $\AxisZeckendorfCannotClaimUp$ must factor through the displayed registry packet $R=(a,b,c,d,e,f,g,h,p,n)$. It may consume a NameCert refusal row, transport it by the componentwise $\hsame$ data in $h$, follow the displayed $\Cont$ route in $h$, and cite the $\Pkg$ provenance $p$ and local name $n$; it may not replace those rows by a positive arithmetic construction, a hidden carrier, a host equality, or a stronger axis reconstruction.
\end{theorem}
\begin{proof}
First use consumer horizon exhaustion. It says that every downstream consumer is confined to the refusal rows $a,b,c,d,e,f,g$ together with the route, provenance, and local naming rows.

Next use the root-unblock downstream boundary. That theorem identifies the consumer-facing role of the packet as a refusal source for unary-direction and axis-carry work, not as a promoted arithmetic carrier.

The ledger non-escape theorem supplies the blocker scope. Since the registry cannot yield a positive $\RealUp$ row, $\NatUp$ row, primitive dimension row, quotient row, or kernel rewrite row, every downstream blocker remains a read of the displayed NameCert refusal rows and their $h,p,n$ support.
\end{proof}

\begin{theorem}[AxisZeckendorf cannot-claim formalization handoff]
\label{thm:axis-zeckendorf-cannot-claim-formalization-handoff}
The future formalization target for $\AxisZeckendorfCannotClaimUp$ is the finite registry handoff for $R=(a,b,c,d,e,f,g,h,p,n)$: refusal coverage for $a,b,c,d,e,f,g$, $\hsame$ transport and $\Cont$ route preservation through $h$, $\Pkg$ provenance through $p$, local $\NameCert$ naming through $n$, and non-escape from all requested positive $\FullAxisUp$, $\RealUp$, $\AxisNatUp$, $\NatUp$, $\DimLiftUp$, quotient, and kernel-rewrite rows. The handoff is a negative registry theorem, not a positive Zeckendorf or axis construction.
\end{theorem}
\begin{proof}
Assemble the proof surface from the existing registry theorems. Refusal coverage supplies the seven negative rows, and refusal reader totality says that accepted reads choose from those rows.

Transport and route preservation are supplied by ledger consumer exactness and transport non-promotion. They keep the selected row inside the same $\BHist$, $\hsame$, and $\Cont$ registry route, while $p,n$ record provenance and local naming.

The final formalization boundary is given by consumer horizon exhaustion and root-unblock ledger non-escape. Together they rule out every listed positive structure and leave the future Lean handoff as the finite cannot-claim registry rather than an arithmetic construction.
\end{proof}

\closureat{AxisZeckendorfCannotClaimUp}{seedStr}
\closureat{AxisZeckendorfCannotClaimUp}{obligationStr}
\closureat{AxisZeckendorfCannotClaimUp}{scopedStr}

\begin{closurestatus}{\AxisZeckendorfCannotClaimUp}
  \constructivestory{An $\AxisZeckendorfCannotClaimUp$ packet records four checked negative theorem rows, three horizon refusal rows, componentwise $\hsame$ and $\Cont$ routing, $\Pkg$ provenance, and a local $\NameCert$ row, while exporting no RealUp, NatUp replacement, dimension, quotient, or kernel-rewrite coordinate.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The scoped registry records the finite carrier, four negative theorem rows, three horizon refusal rows, componentwise transport, ledger exactness, non-escape, consumer exhaustion, determinacy, transport non-promotion, provenance exhaustion, negative-row scope, horizon-refusal scope, and ledger-route scope for the AxisZeckendorf cannot-claim packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not prove a Lean implementation, a standard bridge, RealUp completeness for FullAxisUp, AxisNatUp equality with NatUp, primitive dimension lift, host arithmetic equality, or kernel rewriting.}
  \upgradepath{Obligation closure requires checking the carrier, classifier routing, refusal-row coverage, consumer horizon exhaustion, and ledger exactness for the displayed registry packet.}
\end{closurestatus}
