\chapter{A Concrete Naming Certificate for $\FiniteTailDiagonalSealUp$}
\label{ch:concrete-instances-finitetaildiagonalseal-namecert}
\origin{human}

The $\FiniteTailDiagonalSealUp$ packet records the finite handoff from a selected regular-Cauchy tail window to a $\RealUp$ seal. It is the concrete NameCert surface used when a diagonal-limit consumer asks for a rational precision request, a StreamName window, a RegSeqRat row, and the selected finite-tail witness that justifies the real-facing read.

\begin{definition}[Finite-tail diagonal seal carrier]
\label{def:finite-tail-diagonal-seal-carrier}
A $\FiniteTailDiagonalSealUp$ carrier is a finite $\BHist$ packet
$$
D=(q,s,r,w,e,h,c,p,n)
$$
with the following visible coordinates:
\begin{enumerate}
\item $q$ is the rational precision request, read through the displayed $\RatUp$ and $\DyadicRatCoreUp$ tolerance rows;
\item $s$ is the $\StreamNameUp$ window selecting the finite diagonal observation interval;
\item $r$ is the $\RegSeqRatUp$ row whose regularity ledger supplies the source observations;
\item $w$ is the selected finite-tail witness, displaying the bounded tail segment that answers $q$ inside the window $s$;
\item $e$ is the $\RealUp$ seal row reached only after $q,s,r,w$ have been exposed;
\item $h$ records componentwise $\hsame$ transports for the precision request, StreamName window, RegSeqRat row, finite-tail witness, and real-seal row;
\item $c$ records the displayed $\Cont$ routes by which consumers inspect the rows;
\item $p$ is the $\Pkg$ provenance over $\RatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\FiniteWindowEnvelopeUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and selected-tail evidence;
\item $n$ is the local $\NameCert_{\FiniteTailDiagonalSealUp}$ row.
\end{enumerate}
The carrier contains no quotient stream, no host real equality, no unbounded diagonal object, no ambient completeness theorem, and no selected limit outside the finite witness row $w$.
\end{definition}

\begin{theorem}[Finite-tail diagonal seal NameCert obligations]
\label{thm:finite-tail-diagonal-seal-namecert-obligations}
The local $\NameCert_{\FiniteTailDiagonalSealUp}$ surface consists exactly of carrier admission for $D=(q,s,r,w,e,h,c,p,n)$, precision routing through $q$, finite-window routing through $s$, regular-Cauchy source routing through $r$, selected-tail witness exactness through $w$, $\RealUp$ seal handoff through $e$, componentwise $\hsame$ transport through $h$, displayed $\Cont$ route replay through $c$, package provenance through $p$, and local naming through $n$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-tail-diagonal-seal-carrier}. The rows $q,s,r,w,e,h,c,p,n$ display the precision request, finite window, regular rational source, selected tail witness, real seal, transports, routes, package provenance, and local naming evidence.

The precision and source obligations are read before the seal. A consumer first reads $q$, then the selected StreamName window $s$, and then the RegSeqRat row $r$ whose regularity ledger supplies the observations inside that window.

The selected witness obligation is the row $w$. It gives the finite tail segment that answers the request and prevents the handoff from appealing to an unbounded diagonal stream or an existential limit choice.

Finally the rows $h,c,p,n$ account for transport, route replay, provenance, and local naming. Since the carrier has no quotient-stream coordinate, no host real equality coordinate, and no ambient-completeness coordinate, the obligation surface is exhausted by the displayed rows.
\end{proof}

\begin{theorem}[Finite-tail diagonal seal window factorization]
\label{thm:finite-tail-diagonal-seal-window-factorization}
For an accepted $\FiniteTailDiagonalSealUp$ carrier $D=(q,s,r,w,e,h,c,p,n)$, every finite-tail read factors through the StreamName window $s$ and the selected witness row $w$ before any $\RealUp$ seal row is consumed. The factorization may use the regular-Cauchy source row $r$, the precision row $q$, the componentwise transports $h$, and the displayed routes $c$, but it has no route through a quotient stream, an infinite diagonal object, or a host real equality.
\end{theorem}
\begin{proof}
Read the finite-window coordinates from the carrier. The only window coordinate is $s$, and the only selected tail coordinate is $w$.

Use the NameCert obligations of \autoref{thm:finite-tail-diagonal-seal-namecert-obligations}. They force precision routing through $q$, source routing through $r$, and selected-tail witness exactness through $w$ before the real-facing row $e$ is reached.

Transport and route replay are then confined to $h$ and $c$. The package and local certificate rows $p,n$ record that this is a finite packet, so the factorization has no coordinate for quotient streams, infinite diagonal data, or host real equality.
\end{proof}

\begin{theorem}[Finite-tail diagonal seal window lock]
\label{thm:finite-tail-diagonal-seal-window-lock}
For an accepted $\FiniteTailDiagonalSealUp$ carrier $D=(q,s,r,w,e,h,c,p,n)$, the selected finite-tail witness row $w$ is readable only under the selected $\StreamNameUp$ window row $s$ and the $\RegSeqRatUp$ source row $r$. Any $\RealUp$ seal handoff through $e$ preserves that same window lock through the componentwise transports $h$, the displayed routes $c$, the package provenance $p$, and the local $\NameCert$ row $n$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteTailDiagonalSealUp.FiniteTailDiagonalSealCarrier\_window\_lock}
\begin{proof}
Project the carrier of \autoref{def:finite-tail-diagonal-seal-carrier}. The row $w$ is listed only as the selected finite-tail witness for the window $s$ and the regular-rational source row $r$.

Apply the NameCert obligation theorem. It routes finite-window exposure through $s$, regular-Cauchy source exposure through $r$, and selected-tail witness exactness through $w$ before the seal row $e$ can be consumed.

Use the window factorization theorem to keep every finite-tail read under the same $s,r,w$ boundary. The transports $h$, routes $c$, provenance $p$, and local name $n$ replay that displayed boundary rather than selecting a second window.

Finally apply the non-escape boundary. Since the packet has no quotient stream, unbounded diagonal, host equality, ambient completeness, or external limit coordinate, a Real handoff through $e$ cannot release $w$ from the selected window and source rows.
\end{proof}

\begin{theorem}[Finite-tail diagonal seal Real handoff]
\label{thm:finite-tail-diagonal-seal-real-handoff}
Every $\RealUp$ consumer of an accepted $\FiniteTailDiagonalSealUp$ carrier receives the seal row $e$ only through the displayed chain
$$
q,s,r,w,h,c,p,n.
$$
Thus the real-facing handoff consumes a rational precision request, a finite StreamName window, a RegSeqRat source row, a selected finite-tail witness, componentwise transport, route replay, package provenance, and local naming. It does not consume host real equality, quotient-name equality, an ambient completeness principle, or a selected limit outside the finite witness.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteTailDiagonalSealUp.FiniteTailDiagonalSealCarrier\_real\_handoff}
\begin{proof}
Start with the carrier row $e$. It is a $\RealUp$ seal coordinate inside the same finite packet as $q,s,r,w,h,c,p,n$.

Apply the window factorization theorem. The seal-facing read must pass through the precision, window, source, and witness rows before it reaches $e$.

The rows $h$ and $c$ then replay the displayed transport and continuation data, while $p$ and $n$ provide provenance and local naming. Because the carrier lists no host equality, quotient equality, ambient completeness, or external limit coordinate, the real-facing handoff is exactly the displayed chain.
\end{proof}

\begin{theorem}[Finite-tail diagonal seal non-escape]
\label{thm:finite-tail-diagonal-seal-non-escape}
Every downstream consumer of an accepted $\FiniteTailDiagonalSealUp$ packet factors through the finite rows
$$
q,s,r,w,e,h,c,p,n.
$$
The consumer may read the rational precision request, selected StreamName window, RegSeqRat source, finite-tail witness, $\RealUp$ seal, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row, and it cannot read quotient streams, host real equality, unbounded diagonal streams, ambient completeness, or a choice-selected limit.
\end{theorem}
\begin{proof}
Project the accepted carrier and the NameCert obligation surface. The rows $q,s,r,w,e,h,c,p,n$ are the complete displayed packet.

Use the window factorization theorem for all finite-tail observations. It routes tail reads through $s$ and $w$ with the source and precision rows visible.

Use the Real handoff theorem for real-facing consumers. It routes seal reads through $q,s,r,w,h,c,p,n$ before $e$ is consumed.

Since the carrier has no remaining coordinate beyond the displayed rows, no downstream consumer can extract quotient-stream data, host real equality, unbounded diagonal data, ambient completeness, or a choice-selected limit from the packet.
\end{proof}

\begin{theorem}[Finite-tail diagonal seal selected-tail exactness]
\label{thm:finite-tail-diagonal-seal-selected-tail-exactness}
For an accepted $\FiniteTailDiagonalSealUp$ carrier
$$
D=(q,s,r,w,e,h,c,p,n),
$$
the selected-tail witness row $w$ is exact for the displayed $\StreamNameUp$ window $s$. A consumer may read $w$ only as the finite tail segment selected under $s$ from the $\RegSeqRatUp$ source row $r$ for the rational precision request $q$. The witness is not a quotient stream, an unbounded diagonal stream, a host real equality, or a selected limit outside the finite packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteTailDiagonalSealUp.FiniteTailDiagonalSealCarrier\_selected\_tail\_exactness}
\begin{proof}
Project the carrier rows. The only selected-tail coordinate is $w$, and the carrier names it relative to the window row $s$, source row $r$, and precision request $q$.

Use the NameCert obligations and window lock. They force finite-window routing through $s$, source routing through $r$, and selected-tail witness exposure through $w$ before the seal row $e$ can be consumed.

Apply non-escape for the negative boundary. Since no quotient stream, unbounded diagonal stream, host equality, ambient completeness, or selected limit is present as a carrier coordinate, $w$ is exact only as the displayed finite witness.
\end{proof}

\begin{theorem}[Finite-tail diagonal seal RegSeqRat source coverage]
\label{thm:finite-tail-diagonal-seal-regseq-source-coverage}
For an accepted $\FiniteTailDiagonalSealUp$ carrier
$$
D=(q,s,r,w,e,h,c,p,n),
$$
the row $r$ is the only $\RegSeqRatUp$ source route into the selected finite-tail witness and the $\RealUp$ seal. Every seal-facing read passes through the precision row $q$, the window row $s$, the source row $r$, and the selected witness row $w$ before reaching $e$, with transport, continuation, provenance, and local naming recorded by $h,c,p,n$.
\end{theorem}
\begin{proof}
Start with the source coordinate of the carrier. The packet lists one $\RegSeqRatUp$ row, namely $r$, and no second regular-rational source route.

Apply window factorization and window lock. The selected finite-tail read is confined to $s,r,w$, while the precision request $q$ fixes the finite observation demand answered by that tail.

Use the Real handoff theorem for the seal-facing step. It routes the consumer through $q,s,r,w,h,c,p,n$ before $e$ is consumed, so $r$ is the only source route available to the seal.
\end{proof}

\begin{theorem}[Finite-tail diagonal seal obligation package]
\label{thm:finite-tail-diagonal-seal-obligation-package}
The $\FiniteTailDiagonalSealUp$ obligation package over
$$
D=(q,s,r,w,e,h,c,p,n)
$$
consists exactly of precision routing through $q$, selected window routing through $s$, $\RegSeqRatUp$ source coverage through $r$, selected-tail witness exactness through $w$, $\RealUp$ seal handoff through $e$, componentwise transport through $h$, displayed route replay through $c$, provenance through $p$, and the local $\NameCert$ row $n$. This package has no quotient-stream, host-real-equality, hidden-limit, or ambient-completeness input.
\end{theorem}
\begin{proof}
First assemble the displayed carrier rows. The carrier definition and NameCert obligation theorem give the precision, window, source, witness, seal, transport, route, provenance, and local naming coordinates.

Next add the source and witness controls. Selected-tail exactness binds $w$ to the finite window $s$ and source $r$, while RegSeqRat source coverage makes $r$ the only source route into the witness and seal.

Finally apply Real handoff and non-escape. Real handoff places the seal row $e$ downstream of the displayed finite chain, and non-escape rules out quotient streams, host real equality, unbounded diagonal streams, ambient completeness, and selected limits as additional inputs.
\end{proof}
\leanchecked{BEDC.Derived.FiniteTailDiagonalSealUp.FiniteTailDiagonalSealCarrier\_obligation\_package}

\begin{theorem}[FiniteTailDiagonalSeal obligation closure]
\label{thm:finitetaildiagonalseal-obligation-closure}
For an accepted $\FiniteTailDiagonalSealUp$ carrier $D=(q,s,r,w,e,h,c,p,n)$, the obligation surface closes over the same finite packet: carrier admission, precision routing, window routing, witness exactness, seal handoff, transport, route replay, provenance, and local naming are all read through $q,s,r,w,e,h,c,p,n$. The closure route is the one consumed by \autoref{ch:concrete-instances-realcompleteness-namecert}, and its upstream rows are the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows displayed in the carrier.
\end{theorem}
\begin{proof}
Assemble the carrier and local NameCert rows from \autoref{def:finite-tail-diagonal-seal-carrier} and \autoref{thm:finite-tail-diagonal-seal-namecert-obligations}. These rows provide carrier admission, precision routing, finite-window routing, source routing, selected-tail witness exactness, seal handoff, transport, route replay, provenance, and naming.

Use the exactness theorems to fix the route. \autoref{thm:finite-tail-diagonal-seal-window-factorization}, \autoref{thm:finite-tail-diagonal-seal-window-lock}, \autoref{thm:finite-tail-diagonal-seal-selected-tail-exactness}, and \autoref{thm:finite-tail-diagonal-seal-regseq-source-coverage} keep every witness read inside the selected $\StreamNameUp$ window, the $\RegSeqRatUp$ source row, and the precision route supplied through the $\DyadicRatCoreUp$ tolerance rows.

Finally apply the handoff and boundary theorems. \autoref{thm:finite-tail-diagonal-seal-real-handoff} sends the selected witness to the $\RealUp$ seal row, while \autoref{thm:finite-tail-diagonal-seal-non-escape} blocks quotient streams, host real equality, unbounded diagonal data, ambient completeness, and choice-selected limits.
\end{proof}

\begin{theorem}[FiniteTailDiagonalSeal RealCompleteness route]
\label{thm:finitetaildiagonalseal-realcompleteness-route}
The route from $\FiniteTailDiagonalSealUp$ to \autoref{ch:concrete-instances-realcompleteness-namecert} passes through the same finite-tail seal rows $q,s,r,w,e,h,c,p,n$. A RealCompleteness consumer may read the selected $\StreamNameUp$ window, the $\RegSeqRatUp$ source row, the $\DyadicRatCoreUp$ precision route, and the $\RealUp$ seal row, but it has no route through quotient streams, ambient completeness, host real equality, or an unbounded diagonal object.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finitetaildiagonalseal-obligation-closure}. It makes the finite-tail seal packet the entire obligation route available to downstream consumers.

Read the RealCompleteness side through \autoref{ch:concrete-instances-realcompleteness-namecert}. Its finite diagonal-limit packet consumes StreamName windows, RegSeqRat readbacks, DyadicRatCore ledgers, and the final RealUp seal row, which are exactly the rows exposed by $s,r,q,e$ together with the selected witness $w$.

The route is preserved by $h,c,p,n$. Componentwise transport, continuation replay, provenance, and local naming keep the consumer on the same finite seal route.

Apply \autoref{thm:finite-tail-diagonal-seal-non-escape} for the negative boundary. Since the finite packet lacks quotient streams, ambient completeness, host equality, and unbounded diagonal data, the RealCompleteness route cannot acquire them.
\end{proof}

\begin{theorem}[FiniteTailDiagonalSeal window obligation package]
\label{thm:finitetaildiagonalseal-window-obligation-package}
The window-specific obligation package inside an accepted $\FiniteTailDiagonalSealUp$ carrier isolates three rows: the $\StreamNameUp$ window row $s$, the $\RegSeqRatUp$ source row $r$, and the selected finite-tail witness row $w$. Every precision request from the $\DyadicRatCoreUp$ side reaches the $\RealUp$ seal row $e$ only after these three rows have been read and transported through $h,c,p,n$.
\end{theorem}
\begin{proof}
Project the window, source, and witness rows from the carrier. The displayed packet contains one selected window row $s$, one regular-rational source route $r$, and one selected finite-tail witness $w$.

Use \autoref{thm:finite-tail-diagonal-seal-window-lock} and \autoref{thm:finite-tail-diagonal-seal-selected-tail-exactness}. Together they make $w$ readable only under $s$ and $r$, with the precision request supplied by $q$.

Then use \autoref{thm:finite-tail-diagonal-seal-real-handoff}. The seal row $e$ is downstream of $q,s,r,w$ and remains routed by $h,c,p,n$.

The non-escape theorem supplies the boundary: no quotient stream, host real equality, hidden limit, or ambient completeness row can enter the window package.
\end{proof}

\closureat{FiniteTailDiagonalSealUp}{seedStr}
\closureat{FiniteTailDiagonalSealUp}{obligationStr}
\closureat{FiniteTailDiagonalSealUp}{scopedStr}
\closureat{FiniteTailDiagonalSealUp}{publicStr}[BEDC.Derived.FiniteTailDiagonalSealUp.FiniteTailDiagonalSealCarrier\_obligation\_package]
\closureat{FiniteTailDiagonalSealUp}{bridgedStr}[BEDC.Derived.FiniteTailDiagonalSealUp.FiniteTailDiagonalSealCarrier\_obligation\_package]

\begin{closurestatus}{\FiniteTailDiagonalSealUp}
  \constructivestory{A $\FiniteTailDiagonalSealUp$ packet is generated from a rational precision request, selected $\StreamNameUp$ window, $\RegSeqRatUp$ source row, selected finite-tail witness, $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{\autoref{def:finite-tail-diagonal-seal-carrier}, \autoref{thm:finite-tail-diagonal-seal-obligation-package}, and \autoref{thm:finitetaildiagonalseal-realcompleteness-route} bind the public finite-tail seal surface over the obligation package and the RealCompleteness route.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.FiniteTailDiagonalSealUp.FiniteTailDiagonalSealCarrier\_obligation\_package}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient streams, host real equality, unbounded diagonal streams, ambient completeness, selected limits, or bridge checking.}
  \upgradepath{Bridge closure requires a standard bridge from the public finite-tail packet to the standard choice-free finite-tail seal reading.}
\end{closurestatus}
