\chapter{A Concrete Naming Certificate for $\NoetherSymmetryUp$}
\label{ch:concrete-instances-noethersymmetry-namecert}

The Noether-symmetry interface $\NoetherSymmetryUp$ packages the bijection between continuous symmetries of a Lagrangian and conserved currents along solutions of the Euler-Lagrange equations. It depends on $\NameCert_{\LieAlgebraUp}$ (\autoref{ch:concrete-instances-liealgebra-namecert}) and $\NameCert_{\PdeUp}$ (\autoref{ch:concrete-instances-pde-namecert}), and bridges algebraic and analytic certificates through the same conservation-law ledger.

\section{Carrier definition}
\label{sec:noethersymmetry-carrier}

\begin{definition}[Noether-symmetry conservation-ledger carrier]
\label{def:noethersymmetry-conservation-ledger-carrier}
A $\NoetherSymmetryUp$ conservation-ledger carrier is a finite
$\mathsf{BHist}$ row containing a $\NameCert_{\LieAlgebraUp}$ infinitesimal
symmetry source, a $\NameCert_{\PdeUp}$ Euler-Lagrange source, a displayed
current history, and named $\hsame$, $\Cont$, and $\Pkg$ witnesses placing the
current under both sources. The carrier also records the finite source-domain
token that says the Lie-algebra row acts on the same displayed field history
whose Euler-Lagrange equation is carried by the PDE row.

The carrier is only this finite certificate surface. It does not assert a
global Noether bijection, smooth variational calculus, an analytic action
functional, or a standard model of conservation laws.
\end{definition}

\begin{definition}[Noether-symmetry current classifier]
\label{def:noethersymmetry-current-classifier}
Two rows of \autoref{def:noethersymmetry-conservation-ledger-carrier} are
classified as the same $\NoetherSymmetryUp$ observation when their
$\LieAlgebraUp$ infinitesimal-symmetry sources are transported by
$\NameCert_{\LieAlgebraUp}$, their $\PdeUp$ Euler-Lagrange sources are
transported by $\NameCert_{\PdeUp}$, and their displayed current histories and
dependency ledgers are matched by $\hsame$, $\Cont$, and $\Pkg$.

The classifier is generated by source transport and finite current-ledger
transport. It has no generator for equality of smooth fields, integration by
parts in a host calculus, or a bijective correspondence between all
symmetries and all conserved currents.
\end{definition}
\leandef{BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryCurrentClassifier}

\section{The certificate}
\label{sec:noethersymmetry-certificate}

\begin{theorem}[Noether-symmetry Lie-PDE source boundary]
\label{thm:noethersymmetry-lie-pde-source-boundary}
Every row of
\autoref{def:noethersymmetry-conservation-ledger-carrier} exposes a finite
$\LieAlgebraUp$ infinitesimal-symmetry source, a finite $\PdeUp$
Euler-Lagrange source, and the displayed current row attached to their shared
field-history boundary by $\Cont$ and $\Pkg$ witnesses.
\end{theorem}
\leanchecked{BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_source\_boundary}
\begin{proof}
Invert the carrier definition. The Lie-algebra source, the PDE source, the
current history, and the source-domain token are explicit fields of the
finite $\mathsf{BHist}$ row.

The only boundary comparisons available in the carrier are the named
$\hsame$, $\Cont$, and $\Pkg$ witnesses. Therefore the shared field-history
boundary is read from those finite rows, not from a smooth variational model
or from global conservation-law semantics.
\end{proof}
\leanchecked{BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_lie\_pde\_source\_boundary}

\begin{theorem}[Noether-symmetry conservation-ledger stability]
\label{thm:noethersymmetry-conservation-ledger-stability}
If two $\NoetherSymmetryUp$ rows are classified by
\autoref{def:noethersymmetry-current-classifier}, then transport of the
$\LieAlgebraUp$ infinitesimal-symmetry source, transport of the $\PdeUp$
Euler-Lagrange source, and transport of the displayed current through
$\hsame$, $\Cont$, and $\Pkg$ preserve the same conservation-ledger carrier.
\end{theorem}
\leanchecked{BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_stability}
\begin{proof}
Transport the two source rows first. The $\NameCert_{\LieAlgebraUp}$ and
$\NameCert_{\PdeUp}$ classifiers supply transported source histories while
keeping the displayed field-history boundary visible in the finite ledger.

Then transport the current row and its dependency witnesses through
$\hsame$, $\Cont$, and $\Pkg$. These are exactly the generators listed in
\autoref{def:noethersymmetry-current-classifier}, so the transported packet is
again a row of
\autoref{def:noethersymmetry-conservation-ledger-carrier}.
\end{proof}

\begin{theorem}[Noether-symmetry NameCert obligation surface]
\label{thm:noethersymmetry-namecert-obligation-surface}
The $\NoetherSymmetryUp$ chapter exports a NameCert obligation surface
consisting of the conservation-ledger carrier of
\autoref{def:noethersymmetry-conservation-ledger-carrier}, the current
classifier of \autoref{def:noethersymmetry-current-classifier}, the finite
$\LieAlgebraUp$ infinitesimal-symmetry source, the finite $\PdeUp$
Euler-Lagrange source, the displayed conservation-current row, and the
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and NameCert rows that connect
those fields.

The surface does not claim a global Noether bijection, smooth variational
calculus, equality in a standard analytical model, or completeness of all
conserved currents.
\end{theorem}
\leanchecked{BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_namecert\_obligation\_surface}
\begin{proof}
Assemble the surface from one carried row and one classifier witness. The
carried row supplies the Lie-algebra source, PDE source, current history,
source-domain token, and dependency ledger; the classifier supplies only
source transport and finite current-ledger transport.

Conversely, every exported row appears in one of those fields or in the
transport witnesses named by the classifier. Thus a downstream chapter may
consume the finite $\mathsf{BHist}$ and NameCert obligation surface, but it
cannot read off a global Noether correspondence or an analytic variational
calculus from this certificate alone.
\end{proof}

\begin{theorem}[Noether-symmetry finite-current public export]
\label{thm:noethersymmetry-finite-current-public-export}
The accepted finite conservation-current package for $\NoetherSymmetryUp$
exports exactly the $\mathsf{BHist}$ conservation-ledger carrier of
\autoref{def:noethersymmetry-conservation-ledger-carrier}, the current
classifier of \autoref{def:noethersymmetry-current-classifier}, the
Lie-PDE source boundary of
\autoref{thm:noethersymmetry-lie-pde-source-boundary}, the stability row of
\autoref{thm:noethersymmetry-conservation-ledger-stability}, and the
$\NameCert$ obligation surface of
\autoref{thm:noethersymmetry-namecert-obligation-surface}.

The exported public row exposes only $\Cont$, $\hsame$, $\Pkg$,
$\NameCert$, the finite Lie source, the finite PDE field row, and the
conservation-current ledger. It does not expose variational calculus,
analytic PDE regularity, smooth manifold data, or a standard Noether
theorem.
\end{theorem}
\leanchecked{BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_public\_export}
\begin{proof}
Project the five displayed rows. The carrier projection gives the finite
$\mathsf{BHist}$ conservation ledger, the classifier projection gives the
current comparison rule, and the source-boundary projection gives the
finite Lie source together with the finite PDE field row.

Next use the stability theorem to keep the projected carrier fixed under
the allowed $\hsame$, $\Cont$, and $\Pkg$ transports. Use the obligation
surface theorem to retain exactly the $\NameCert$ rows and dependency
ledgers already named by the package.

Repack these projections as the public consumer boundary. Since every
component of the repacked boundary is one of the five projected rows, and
since no projected row contains variational calculus, analytic PDE
regularity, smooth manifold data, or a standard Noether theorem, the public
export has precisely the stated finite-current surface.
\end{proof}

\begin{theorem}[Noether-symmetry mature finite-current boundary]
\label{thm:noethersymmetry-mature-finite-current-boundary}
The mature package boundary for $\NoetherSymmetryUp$ is exhausted by the
conservation-ledger carrier, current classifier, Lie-PDE source boundary,
stability row, NameCert obligation surface, and finite-current public export.
Every consumer reads only the finite Lie source, finite PDE field row,
conservation-current ledger, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows
already displayed by that surface.
\end{theorem}
\begin{proof}
Project the conservation-ledger carrier and current classifier. These rows
provide the finite current packet and the finite comparison rule used by every
accepted $\NoetherSymmetryUp$ read.

Apply the Lie-PDE source boundary and the stability row. They keep the Lie
source, PDE field row, conservation-current row, $\hsame$ transport,
$\Cont$ route, and $\Pkg$ provenance inside the same finite package boundary.

Use the NameCert obligation surface and the finite-current public export to
repack those projections as the consumer-facing package. The public export
already lists the exact rows available to consumers, so the mature boundary
adds no independent coordinate.

The boundary explicitly excludes a global Noether correspondence, smooth
variational calculus, analytic PDE regularity, smooth manifold data, and a
standard Noether theorem. Those structures are not read from the finite
current package.
\end{proof}

\closureat{NoetherSymmetryUp}{obligationStr}[BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_namecert\_obligation\_surface]
\closureat{NoetherSymmetryUp}{scopedStr}[BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_namecert\_obligation\_surface]
\closureat{NoetherSymmetryUp}{publicStr}[BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_public\_export]
\closureat{NoetherSymmetryUp}{bridgedStr}[BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_public\_export]
\closureat{NoetherSymmetryUp}{matureStr}[BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_public\_export]

\begin{closurestatus}{\NoetherSymmetryUp}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:noethersymmetry-finite-current-public-export} is the public boundary over the finite Lie source, PDE field row, conservation-current ledger, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.NoetherSymmetryUp.NoetherSymmetryConservationLedgerCarrier\_public\_export}
  \bridgestatus{none}
  \constructivestory{A finite conservation-ledger packet is assembled from the displayed Lie-algebra row, PDE row, current classifier row, transport witnesses, and one provenance packet; accepted consumers read only those finite current rows.}
  \notclaimed{This chapter does not claim a full Noether theorem, variational calculus, analytic PDE regularity, smooth manifold data, or standard bridge.}
  \upgradepath{The paper axis is mature; further progress is Lean and bridge verification for the same finite-current package boundary.}
\end{closurestatus}
