\chapter{A Concrete Naming Certificate for $\DeformQuantizationUp$}
\label{ch:concrete-instances-deformquantization-namecert}

The deformation-quantization interface $\DeformQuantizationUp$ packages the formal star product $\star_\hbar$ on a Poisson manifold whose first-order term is the Poisson bracket (Kontsevich formality). It depends on $\NameCert_{\SymplecticUp}$ (\autoref{ch:concrete-instances-symplectic-namecert}) and $\NameCert_{\HopfAlgUp}$ (\autoref{ch:concrete-instances-hopfalg-namecert}), and bridges Poisson and noncommutative certificates through the same formal-deformation classifier.

\section{Carrier definition}
\label{sec:deformquantization-carrier}

\section{The certificate}
\label{sec:deformquantization-certificate}

\begin{definition}[DeformQuantization first-order star-product ledger]
\label{def:deformquantization-first-order-star-product-ledger}
Fix a $\SymplecticUp$ obligation boundary $\Sigma$ as in \autoref{def:symplectic-obligation-boundary}. Fix a $\HopfAlgUp$ row $H=(a,t,s,u,e)$ whose carrier and classifier are read through \autoref{def:hopfalg-bhist-bialgebra-carrier} and \autoref{def:hopfalg-antipode-ledger-classifier}. A first-order star-product ledger for $\DeformQuantizationUp$ over $(\Sigma,H)$ is a displayed $\mathsf{BHist}$ row
$$
\mathsf{DQStarLedger}_{\Sigma,H}(\mu_\hbar,\mu_0,\mu_1,\mu_1^{\mathrm{op}},\kappa,\pi,\Lambda_\star)
$$
with the following fields.
\begin{enumerate}
  \item The row $\mu_\hbar$ is a formal-product row whose multiplication provenance is read through the $\HopfAlgUp$ multiplication and tensor rows of $H$.
  \item The row $\mu_0$ is the degree-zero product endpoint of $\mu_\hbar$ and is classified with the ordinary commutative product row on the function algebra over the carrier exposed by $\Sigma$.
  \item The rows $\mu_1$ and $\mu_1^{\mathrm{op}}$ are the degree-one coefficient endpoints of $\mu_\hbar$ and of the opposite formal product.
  \item The row $\kappa$ is the degree-one commutator endpoint, displayed by the continuation row
$$
\Cont(\mu_1,\mu_1^{\mathrm{op}},\kappa).
$$
  \item The row $\pi$ is the Poisson-bracket obligation row attached by the $\DeformQuantizationUp$ packet to the same symplectic boundary $\Sigma$.
  \item The formal-deformation classifier attached to $\Lambda_\star$ contains the bracket exactness comparison
$$
\hsame(\kappa,\pi),
$$
and its coverage and soundness clauses say that every bracket read of the formal-deformation classifier factors through $\pi$ and every accepted degree-one commutator endpoint factors through $\kappa$ before this comparison is applied.
\end{enumerate}
\end{definition}

\begin{theorem}[DeformQuantization first-order bracket ledger]
\label{thm:deformquantization-first-order-bracket-ledger}
Let $\Sigma$ be a $\SymplecticUp$ obligation boundary and let $H=(a,t,s,u,e)$ be a $\HopfAlgUp$ formal-product row as in \autoref{def:deformquantization-first-order-star-product-ledger}. Let $Q$ be a $\DeformQuantizationUp$ packet over $(\Sigma,H)$ containing the visible ledger row
$$
\mathsf{DQStarLedger}_{\Sigma,H}(\mu_\hbar,\mu_0,\mu_1,\mu_1^{\mathrm{op}},\kappa,\pi,\Lambda_\star).
$$
If $\mu_0$ is read as the degree-zero product endpoint of the star product and $\kappa$ is read as the degree-one commutator endpoint, then the formal-deformation classifier of $Q$ reads the same degree-one endpoint as the displayed Poisson-bracket obligation row:
$$
\mathsf{PoissonBracketOb}_{\Sigma,H}(\pi)\land\hsame(\kappa,\pi).
$$
Thus the bracket endpoint belongs to the $\DeformQuantizationUp$ ledger over the supplied $\SymplecticUp$ boundary and $\HopfAlgUp$ formal-product row, not to the $\SymplecticUp$ boundary alone.
\end{theorem}
\leanchecked{BEDC.Derived.DeformQuantizationUp.DeformQuantizationStarLedger\_first\_order\_bracket}
\begin{proof}
Unpack \autoref{def:deformquantization-first-order-star-product-ledger}. The $\HopfAlgUp$ side supplies the formal product substrate through the multiplication and tensor provenance rows recorded in \autoref{thm:hopfalg-namecert-obligation-surface}. This places $\mu_\hbar$ inside the same ledger spine as the degree-zero endpoint $\mu_0$ and the two degree-one coefficient endpoints $\mu_1$ and $\mu_1^{\mathrm{op}}$.

The commutator endpoint is not an additional classifier choice. It is the row $\kappa$ displayed by the continuation face
$$
\Cont(\mu_1,\mu_1^{\mathrm{op}},\kappa)
$$
inside the same star-product ledger. The degree-zero clause records that the zeroth coefficient is the ordinary product endpoint, while the degree-one clause records that the first antisymmetric endpoint is $\kappa$.

The Poisson-bracket clause of the ledger then supplies the row $\pi$ and the exactness comparison
$$
\hsame(\kappa,\pi).
$$
By the coverage clause, any bracket read made by the formal-deformation classifier factors through this displayed $\pi$ row. By the soundness clause, the accepted degree-one commutator read factors through $\kappa$ before it is compared with $\pi$. Therefore the endpoint read from the degree-one commutator is classified with the displayed Poisson-bracket obligation row, giving
$$
\mathsf{PoissonBracketOb}_{\Sigma,H}(\pi)\land\hsame(\kappa,\pi).
$$

The separation from the symplectic dependency is exactly the consumer frontier of \autoref{thm:symplecticup-hamiltonian-poisson-consumer-frontier}: the $\SymplecticUp$ boundary supplies carrier, two-form, closedness, nondegeneracy, pairing, and transport rows, but it does not by itself export a Poisson bracket. The bracket endpoint used here is supplied only after the $\DeformQuantizationUp$ packet adds the first-order star-product ledger over the Hopf formal-product row.
\end{proof}

\begin{theorem}[DeformQuantization star-ledger carrier obligation]
\label{thm:deformquantization-star-ledger-carrier-obligation}
Let $\Sigma$ be a $\SymplecticUp$ obligation boundary and let $H=(a,t,s,u,e)$ be a $\HopfAlgUp$ row satisfying \autoref{def:hopfalg-bhist-bialgebra-carrier} and \autoref{def:hopfalg-antipode-ledger-classifier}. A $\DeformQuantizationUp$ packet $Q$ over $(\Sigma,H)$ has its first-order carrier exactly when it exposes a displayed row
$$
\mathsf{DQStarLedger}_{\Sigma,H}(\mu_\hbar,\mu_0,\mu_1,\mu_1^{\mathrm{op}},\kappa,\pi,\Lambda_\star)
$$
of \autoref{def:deformquantization-first-order-star-product-ledger} whose formal product provenance is the $\Pkg$ row read from the multiplication and tensor faces of $H$, whose commutator face is the continuation row $\Cont(\mu_1,\mu_1^{\mathrm{op}},\kappa)$, and whose carrier comparisons are the displayed $\hsame$ rows of the packet. Thus no separate carrier for $Q$ is admitted beyond the $\mathsf{BHist}$ ledger row, the $\Cont$ face, the $\hsame$ comparisons, and the $\Pkg$ provenance supplied by $\Sigma$ and $H$.
\end{theorem}
\begin{proof}
Project the $\HopfAlgUp$ side first. By \autoref{thm:hopfalg-namecert-obligation-surface}, the row $H$ supplies the carrier, classifier, tensor-row stability, multiplication and comultiplication provenance through $\Cont$, and the antipode ledger rows. The formal-product provenance of $\mu_\hbar$ is therefore the same $\Pkg$ row read from those multiplication and tensor faces.

Next project the $\SymplecticUp$ boundary. The consumer frontier of \autoref{thm:symplecticup-hamiltonian-poisson-consumer-frontier} supplies the carrier boundary and transport surface needed by a Poisson consumer, while withholding any independent bracket export. Hence the deformation packet must attach its bracket-facing carrier through the displayed star ledger rather than through a hidden symplectic row.

Finally repack the projections into \autoref{def:deformquantization-first-order-star-product-ledger}. The row $\mu_\hbar$ carries the formal product, $\mu_0,\mu_1,\mu_1^{\mathrm{op}}$ are its coefficient endpoints, $\kappa$ is displayed by $\Cont(\mu_1,\mu_1^{\mathrm{op}},\kappa)$, and the packet comparisons are the recorded $\hsame$ rows. These fields are exactly the advertised $\mathsf{BHist}$ carrier for $Q$, so any accepted first-order carrier read is covered by that row and by no additional carrier datum.
\end{proof}

\begin{theorem}[DeformQuantization bracket classifier obligation]
\label{thm:deformquantization-bracket-classifier-obligation}
Let $Q$ and $Q'$ be $\DeformQuantizationUp$ packets over transported rows $(\Sigma,H)$ and $(\Sigma',H')$, with displayed star-product ledger rows
$$
\mathsf{DQStarLedger}_{\Sigma,H}(\mu_\hbar,\mu_0,\mu_1,\mu_1^{\mathrm{op}},\kappa,\pi,\Lambda_\star)
$$
and
$$
\mathsf{DQStarLedger}_{\Sigma',H'}(\mu'_\hbar,\mu'_0,\mu'_1,(\mu'_1)^{\mathrm{op}},\kappa',\pi',\Lambda'_\star).
$$
If the $\SymplecticUp$ and $\HopfAlgUp$ carrier-classifier rows transport $\Sigma$ to $\Sigma'$ and $H$ to $H'$, then the $\DeformQuantizationUp$ classifier transports the degree-zero product endpoint, the two first-order coefficient endpoints, the commutator endpoint, and the Poisson-bracket comparison row:
$$
\hsame(\mu_0,\mu'_0)\land\hsame(\mu_1,\mu'_1)\land\hsame(\mu_1^{\mathrm{op}},(\mu'_1)^{\mathrm{op}})\land\hsame(\kappa,\kappa')\land\hsame(\pi,\pi').
$$
\end{theorem}
\begin{proof}
Begin with the transported $\HopfAlgUp$ row. The classifier surface in \autoref{thm:hopfalg-namecert-obligation-surface} carries the multiplication and tensor provenance rows through the transport from $H$ to $H'$, so the formal-product row $\mu_\hbar$ and the transported row $\mu'_\hbar$ have the same $\Pkg$ provenance for the product spine.

The endpoint clauses are then read directly from the two displayed star ledgers. The degree-zero endpoint is transported as the ordinary product endpoint over the transported symplectic carrier. The two first-order coefficient endpoints are transported as coefficient faces of the same formal-product spine.

It remains to transport the bracket-facing rows. The continuation faces
$$
\Cont(\mu_1,\mu_1^{\mathrm{op}},\kappa)
$$
and
$$
\Cont(\mu'_1,(\mu'_1)^{\mathrm{op}},\kappa')
$$
identify the commutator endpoints after the two coefficient endpoints have been transported. The consumer frontier of \autoref{thm:symplecticup-hamiltonian-poisson-consumer-frontier} supplies the transported Poisson consumer boundary, and the ledger exactness clause records the corresponding $\hsame(\pi,\pi')$ comparison. Repacking these five transported rows gives the displayed classifier obligation.
\end{proof}

\begin{theorem}[DeformQuantization first-order ledger exactness obligation]
\label{thm:deformquantization-first-order-ledger-exactness-obligation}
For every $\DeformQuantizationUp$ packet $Q$ over $(\Sigma,H)$ with displayed ledger
$$
\mathsf{DQStarLedger}_{\Sigma,H}(\mu_\hbar,\mu_0,\mu_1,\mu_1^{\mathrm{op}},\kappa,\pi,\Lambda_\star),
$$
every accepted first-order bracket readback of $Q$ is covered by the ledger row of \autoref{def:deformquantization-first-order-star-product-ledger} and is sound for the checked bracket statement of \autoref{thm:deformquantization-first-order-bracket-ledger}. Equivalently, an accepted readback factors through the degree-one commutator endpoint $\kappa$, the Poisson-bracket obligation row $\pi$, and the exactness comparison $\hsame(\kappa,\pi)$ before it is reported as a $\DeformQuantizationUp$ bracket endpoint.
\end{theorem}
\begin{proof}
Coverage is the first projection. Unpack \autoref{def:deformquantization-first-order-star-product-ledger}: the formal-deformation classifier attached to $\Lambda_\star$ records that every bracket read factors through the displayed row $\pi$, and every accepted degree-one commutator endpoint factors through $\kappa$.

Soundness is the second projection. The checked ledger theorem \autoref{thm:deformquantization-first-order-bracket-ledger} identifies the endpoint read from the degree-one commutator with the displayed Poisson-bracket obligation row by the comparison
$$
\mathsf{PoissonBracketOb}_{\Sigma,H}(\pi)\land\hsame(\kappa,\pi).
$$

The Hopf provenance and the symplectic frontier rule out the two possible escapes. By \autoref{thm:hopfalg-namecert-obligation-surface}, the formal product and its coefficient endpoints are read through the $\Pkg$ and $\Cont$ faces supplied by $H$. By \autoref{thm:symplecticup-hamiltonian-poisson-consumer-frontier}, $\Sigma$ supplies the consumer boundary but does not export an independent Poisson bracket. Therefore every accepted first-order readback is both covered by the displayed ledger row and sound for the checked bracket exactness statement.
\end{proof}

\begin{definition}[DeformQuantization formal-deformation obligation inventory]
\label{def:deformquantization-formal-deformation-obligation-inventory}
For a $\DeformQuantizationUp$ packet $Q$ over a $\SymplecticUp$ boundary $\Sigma$ and a $\HopfAlgUp$ row $H$, the formal-deformation obligation inventory is the finite list of public rows consisting of the carrier row of \autoref{thm:deformquantization-star-ledger-carrier-obligation}, the bracket classifier row of \autoref{thm:deformquantization-bracket-classifier-obligation}, the $\Cont$ and $\hsame$ stability rows for the coefficient and commutator endpoints, the first-order ledger row of \autoref{def:deformquantization-first-order-star-product-ledger}, the exactness row of \autoref{thm:deformquantization-first-order-ledger-exactness-obligation}, and the public certificate rows that expose these data through $\Pkg$ provenance. The inventory permits reads from $\NameCert_{\SymplecticUp}$, $\NameCert_{\HopfAlgUp}$, $\Cont$, $\hsame$, $\mathsf{BHist}$, and $\Pkg$ only.
\end{definition}

\begin{theorem}[DeformQuantization scoped primitive inventory]
\label{thm:deformquantization-scoped-primitive-inventory}
Every accepted first-order obligation row of the $\DeformQuantizationUp$ inventory of \autoref{def:deformquantization-formal-deformation-obligation-inventory} factors through exactly the displayed $\SymplecticUp$ boundary $\Sigma$, the $\HopfAlgUp$ formal-product row $H$, the coefficient and commutator faces carried by $\Cont$, the endpoint comparisons carried by $\hsame$, the first-order $\mathsf{BHist}$ ledger row, and the $\Pkg$ provenance of that inventory. Conversely, those rows repack into the public first-order obligation surface of $\NameCert_{\DeformQuantizationUp}$, with no additional bracket source, analytic convergence witness, or formality datum.
\end{theorem}
\begin{proof}
For the carrier part, apply \autoref{thm:deformquantization-star-ledger-carrier-obligation}. It identifies the accepted first-order carrier with the displayed $\mathsf{BHist}$ ledger, the $\Cont$ commutator face, the packet $\hsame$ comparisons, and the $\Pkg$ provenance supplied by the $\SymplecticUp$ and $\HopfAlgUp$ dependencies.

For classifier movement, apply \autoref{thm:deformquantization-bracket-classifier-obligation}. Transport of the degree-zero product endpoint, the two first-order coefficient endpoints, the commutator endpoint, and the Poisson-bracket row is componentwise over the transported $\Sigma$ and $H$ rows.

For readback exactness, apply \autoref{thm:deformquantization-first-order-ledger-exactness-obligation}. It forces every accepted first-order bracket read through the degree-one commutator endpoint $\kappa$, the Poisson-bracket obligation row $\pi$, and the comparison $\hsame(\kappa,\pi)$ before the public endpoint is reported.

The remaining source check is \autoref{thm:deformquantization-source-boundary-obligation}. It rules out any source outside $\Sigma$, $H$, $\Cont$, $\hsame$, $\mathsf{BHist}$, and $\Pkg$. Repacking these projections through \autoref{thm:deformquantization-public-certificate-obligation-surface} gives the public first-order obligation surface and no larger primitive boundary.
\end{proof}

\begin{theorem}[DeformQuantization source-boundary obligation]
\label{thm:deformquantization-source-boundary-obligation}
Every source read accepted by the inventory of \autoref{def:deformquantization-formal-deformation-obligation-inventory} factors through the supplied $\SymplecticUp$ boundary $\Sigma$ and the supplied $\HopfAlgUp$ formal-product row $H$. In particular, a bracket-facing read reaches the public packet only through the symplectic consumer boundary, the Hopf formal-product provenance, the coefficient continuation rows, and the first-order exactness comparison of \autoref{thm:deformquantization-first-order-ledger-exactness-obligation}.
\end{theorem}
\begin{proof}
Project the read into the finite inventory. The carrier case is exactly \autoref{thm:deformquantization-star-ledger-carrier-obligation}: it exposes the star-product carrier through the displayed $\mathsf{BHist}$ ledger, the Hopf $\Pkg$ provenance, the $\Cont$ face, and the packet $\hsame$ comparisons.

The classifier and stability cases use \autoref{thm:deformquantization-bracket-classifier-obligation}. Transport of the degree-zero endpoint, first-order coefficient endpoints, commutator endpoint, and Poisson comparison is therefore controlled by the transported $\SymplecticUp$ and $\HopfAlgUp$ rows, not by an independent deformation source.

For the bracket readback, apply \autoref{thm:deformquantization-first-order-ledger-exactness-obligation}. It factors the read through $\kappa$, $\pi$, and $\hsame(\kappa,\pi)$ after the Hopf formal-product row has supplied the coefficient spine and after the symplectic boundary has supplied only the Poisson consumer frontier. Thus every source read is bounded by the two supplied dependencies and the named BEDC transport rows.
\end{proof}

\begin{theorem}[DeformQuantization public certificate obligation surface]
\label{thm:deformquantization-public-certificate-obligation-surface}
The inventory of \autoref{def:deformquantization-formal-deformation-obligation-inventory}, together with the source-boundary factorization of \autoref{thm:deformquantization-source-boundary-obligation}, forms the public $\NameCert_{\DeformQuantizationUp}$ obligation surface at first order. The surface contains carrier, classifier, stability, ledger, exactness, and public certificate rows over $\SymplecticUp$, $\HopfAlgUp$, $\Cont$, $\hsame$, $\mathsf{BHist}$, and $\Pkg$, and it does not claim Kontsevich formality, analytic convergence, or a full star-product construction beyond the displayed first-order ledger.
\end{theorem}
\begin{proof}
Assemble the carrier and classifier fields first. The carrier field is supplied by \autoref{thm:deformquantization-star-ledger-carrier-obligation}; the classifier and transported endpoint fields are supplied by \autoref{thm:deformquantization-bracket-classifier-obligation}.

Next add stability and exactness. The stability rows are the displayed $\Cont$ and $\hsame$ fields in the ledger, and the exactness row is \autoref{thm:deformquantization-first-order-ledger-exactness-obligation}. These rows cover the first-order commutator endpoint and its comparison with the Poisson-bracket obligation row.

Finally apply \autoref{thm:deformquantization-source-boundary-obligation}. It ensures that every public read is sourced by $\Sigma$, $H$, and the named BEDC rows in the inventory. Repacking those fields gives the stated public obligation surface while leaving full formality and convergence outside the certificate.
\end{proof}

\closureat{DeformQuantizationUp}{scopedStr}[BEDC.Derived.DeformQuantizationUp.DeformQuantizationStarLedger\_first\_order\_bracket]

\begin{closurestatus}{\DeformQuantizationUp}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The obligation scope is exactly the carrier row, bracket classifier, coefficient and commutator stability rows, first-order ledger, exactness row, source-boundary factorization, and public certificate rows over $\SymplecticUp$, $\HopfAlgUp$, $\Cont$, $\hsame$, $\mathsf{BHist}$, and $\Pkg$.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.DeformQuantizationUp.DeformQuantizationStarLedger\_first\_order\_bracket}
  \bridgestatus{none}
  \notclaimed{This seed does not claim Kontsevich formality, full deformation quantization, analytic convergence, a standard bridge, or closure beyond the displayed first-order ledger.}
  \upgradepath{Public closure requires a single exported public certificate theorem for downstream bridge consumers.}
\end{closurestatus}
