\chapter{ObserverFilterUp NameCert construction}
\label{ch:concrete-instances-observer-filter-namecert}
\origin{human}

The $\ObserverFilterUp$ surface packages observer-history identity as a finite selection of $\BHist$ rows together with a ledger for everything the observer does not export. It is a reusable filter carrier: an observer may retain a finite subhistory for downstream naming, while the omitted rows remain visible as a boundary ledger rather than disappearing into host equality, quotient identity, or an unrecorded subject parameter.

The filter consumes observer-history identity through \autoref{ch:concrete-instances-observerhistoryidentity-namecert} and hands selected rows to the StreamName surface of \autoref{ch:concrete-instances-streamname-namecert}; the omitted-row ledger remains a boundary certificate rather than stream data.

\begin{definition}[ObserverFilter BHist carrier]
\label{def:observer-filter-bhist-carrier}
An $\ObserverFilterUp$ carrier is a finite $\BHist$ packet
$$
F=(H,S,O,R,L,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $H$ is the source observer-history row;
\item $S$ is the finite selected subhistory row, listing exactly the $\BHist$ entries retained for public observation;
\item $O$ is the omitted-row ledger, listing every source row not selected into $S$ together with its local boundary reason;
\item $R$ records the componentwise $\hsame$ transports between source rows, selected rows, omitted rows, downstream stream-name rows, continuation routes, package provenance, and the local name;
\item $L$ is the observer ledger tying each retained or omitted row to its source position, observer decision, and local naming boundary;
\item $C$ records the displayed $\Cont$ routes by which a consumer reads the source history, retained subhistory, omitted ledger, and downstream handoff rows;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\ObserverHistoryIdentityUp$, $\StreamNameUp$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ObserverFilterUp}$ row.
\end{enumerate}
The classifier for $F$ compares only the retained row $S$, omitted-row ledger $O$, transport row $R$, observer ledger $L$, continuation row $C$, provenance row $P$, and local name row $N$. The carrier has no coordinate for host equality of histories, quotient streams, hidden observer state, or an unledgered deletion.
\end{definition}

\begin{theorem}[ObserverFilter NameCert obligations]
\label{thm:observer-filter-namecert-obligations}
For the carrier of \autoref{def:observer-filter-bhist-carrier}, the local $\NameCert_{\ObserverFilterUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the packet $F=(H,S,O,R,L,C,P,N)$;
\item classifier transport by the componentwise $\hsame$ rows in $R$;
\item observer-ledger exactness for retained and omitted $\BHist$ rows;
\item downstream handoff through the displayed $\Cont$ routes and $\StreamNameUp$ provenance;
\item non-escape from host equality of histories, quotient streams, hidden observer state, and unledgered deletion.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:observer-filter-bhist-carrier}. The packet displays the source history, selected subhistory, omitted-row ledger, transports, observer ledger, continuation routes, provenance, and local naming row before any classifier read is available.

Classifier transport is componentwise. The row $R$ moves selected and omitted rows to the common $\hsame$ surface, and $C$ supplies the only read routes through which those transported rows can be consumed.

The remaining obligations follow by finite-row cases on whether a source row is selected into $S$ or recorded in $O$. The selected case is named by the observer ledger $L$ and may be handed to downstream consumers; the omitted case is also named by $L$ and stops at the boundary reason recorded in $O$.

No further coordinate is present in the carrier. Thus host history equality, quotient stream equality, hidden observer state, and deletion without a ledger row cannot be exported by the local $\NameCert_{\ObserverFilterUp}$ surface.
\end{proof}

\begin{theorem}[ObserverFilter identity stability]
\label{thm:observer-filter-identity-stability}
Let $F=(H,S,O,R,L,C,P,N)$ and $F'=(H',S',O',R',L',C',P',N')$ be accepted $\ObserverFilterUp$ carriers. If their source rows, selected rows, omitted ledgers, observer ledgers, continuation routes, package rows, and local names are related componentwise by the displayed $\hsame$ transports, then the two carriers determine the same observer-filter identity judgment. The judgment is computed only from the retained subhistory and omitted-row boundary ledger.
\end{theorem}
\begin{proof}
Project both carriers to their displayed rows. The comparison data are exactly $H,S,O,R,L,C,P,N$ and $H',S',O',R',L',C',P',N'$.

Use the $\hsame$ rows in $R$ and $R'$ to transport corresponding selected rows and omitted rows to a common observer-history surface. The routes in $C$ and $C'$ replay the same source, selection, omission, provenance, and local-name reads after transport.

Now inspect each finite source row. A retained row is compared through the matching entry of $S$ and $S'$, while an omitted row is compared through the matching boundary entry of $O$ and $O'$. These two cases exhaust the source ledger.

Therefore the classifier has the same retained public rows and the same omitted boundary rows on both sides. No host equality, quotient identity, or hidden observer-state coordinate is available to distinguish the transported packets.
\end{proof}

\begin{theorem}[ObserverFilter StreamName handoff]
\label{thm:observer-filter-streamname-handoff}
Every $\StreamNameUp$ consumer of an accepted $\ObserverFilterUp$ carrier reads only the selected subhistory row $S$, its observer-ledger entries in $L$, the componentwise $\hsame$ transports in $R$, the displayed $\Cont$ routes in $C$, the package provenance $P$, and the local naming row $N$. Omitted rows in $O$ may certify the boundary of the handoff, but they do not become stream-name data.
\end{theorem}
\begin{proof}
Start with a consumer route from the accepted filter into $\StreamNameUp$. Carrier projection exposes the finite selected row $S$ as the only row permitted to supply stream-name entries.

The route must then pass through $L$, $R$, and $C$. The observer ledger names the retained entries, the transport row moves them by $\hsame$, and the continuation row records the read order used by the downstream stream-name surface.

The omitted ledger $O$ is still visible, but only as a boundary witness. Its entries certify which source rows were not exported; they supply no selected stream-name row and no replacement stream value.

Thus the handoff to $\StreamNameUp$ is exactly the displayed selected-subhistory route through $S,L,R,C,P,N$, with $O$ serving as the finite non-export boundary.
\end{proof}

\begin{theorem}[ObserverFilter ObserverHistoryIdentity factorization]
\label{thm:observer-filter-observer-history-factorization}
Every accepted $\ObserverFilterUp$ carrier factors its public identity claim through $\ObserverHistoryIdentityUp$: the source observer history $H$, selected subhistory $S$, omitted-row ledger $O$, $\hsame$ transports $R$, observer ledger $L$, continuation routes $C$, provenance $P$, and local name $N$ provide exactly the observer-history identity surface seen by downstream consumers.
\end{theorem}
\begin{proof}
Read the accepted filter as a finite observer-history packet. The source row $H$ is the displayed history, $S$ and $O$ divide its rows into retained public observations and recorded boundary observations, and $L$ records the local decision for each row.

The rows $R$ and $C$ supply the transport and read routes required by $\ObserverHistoryIdentityUp$. They identify how selected rows and omitted rows are compared without adding a subject coordinate outside the displayed $\BHist$ data.

Package provenance and local naming are carried by $P$ and $N$. Repacking $H,S,O,R,L,C,P,N$ along these roles gives the observer-history identity surface and uses no further identity principle.
\end{proof}

\begin{theorem}[ObserverFilter ledger exactness]
\label{thm:observer-filter-ledger-exactness}
For every accepted $\ObserverFilterUp$ carrier, each source $\BHist$ row is accounted for exactly once as either a selected row in $S$ or an omitted boundary row in $O$, and every consumer-facing read factors through the corresponding entry of $L$, $R$, $C$, $P$, and $N$. No row may be silently discarded, duplicated into both surfaces, or exported outside the displayed ledger.
\end{theorem}
\begin{proof}
Induct over the finite source history $H$. The empty source row has empty selected and omitted ledgers, so the claim is immediate by carrier projection.

For a cons row, inspect the filter-row decision recorded in $L$. In the selected case the new row is placed in $S$, transported by $R$, and made readable only along a route in $C$ with provenance in $P$ and local naming in $N$.

In the omitted case the new row is placed in $O$ with its boundary reason, transported by $R$, and made readable only as an omission witness along the displayed route in $C$.

The induction hypothesis accounts for the preceding source rows. The two filter-row cases are disjoint and exhaustive, so the full source history is partitioned by $S$ and $O$, and every consumer read passes through the displayed ledger rows.
\end{proof}

\begin{theorem}[ObserverFilter selected-row totality]
\label{thm:observer-filter-selected-row-totality}
For every accepted $\ObserverFilterUp$ carrier $F=(H,S,O,R,L,C,P,N)$, every selected $\BHist$ row exported by the filter is witnessed by a source position in $H$, a selected-row entry in $S$, an observer-ledger entry in $L$, and a consumer route through $R,C,P,N$. No selected row can be supplied by hidden observer state, quotient identity, or a source outside the finite carrier of \autoref{def:observer-filter-bhist-carrier}.
\end{theorem}
\begin{proof}
Project the accepted carrier $F=(H,S,O,R,L,C,P,N)$ through \autoref{def:observer-filter-bhist-carrier}. The only public selected-row coordinates are $H,S,L,R,C,P,N$.

Apply ledger exactness from \autoref{thm:observer-filter-ledger-exactness}. A selected row is one of the two exhaustive cases of the finite source ledger, so it must be paired with its source position in $H$ and its retained entry in $S$.

The consumer read then factors through $R,C,P,N$. Since the carrier contains no hidden observer-state row and no quotient identity coordinate, the selected row has no alternate source.
\end{proof}

\begin{theorem}[ObserverFilter omitted-row boundary exhaustion]
\label{thm:observer-filter-omitted-row-boundary-exhaustion}
For every accepted $\ObserverFilterUp$ carrier $F=(H,S,O,R,L,C,P,N)$, every source $\BHist$ row not selected into $S$ appears in the omitted-row ledger $O$ with its observer-ledger entry in $L$ and its boundary read through $R,C,P,N$. Thus omission exhausts the non-selected part of $H$ and admits no unledgered deletion.
\end{theorem}
\begin{proof}
Read the source history through \autoref{def:observer-filter-bhist-carrier}. Each row of $H$ is compared against the finite selected and omitted surfaces $S$ and $O$.

Use \autoref{thm:observer-filter-ledger-exactness}. Its two cases are selected and omitted, and the selected case is already represented in $S$; therefore every remaining source row must land in $O$ with its corresponding ledger entry in $L$.

The boundary read is routed by $R,C,P,N$. Because the omitted case is an explicit carrier row, deleting a non-selected source row without an omitted-ledger entry is outside the accepted $\ObserverFilterUp$ surface.
\end{proof}

\begin{theorem}[ObserverFilter StreamName selected-subhistory non-escape]
\label{thm:observer-filter-streamname-selected-subhistory-nonescape}
For every accepted $\ObserverFilterUp$ carrier $F=(H,S,O,R,L,C,P,N)$, the $\StreamNameUp$ handoff is exactly the selected subhistory $S$ with its source ledger $L$, componentwise transports $R$, displayed routes $C$, package provenance $P$, and local name $N$. Omitted rows in $O$ remain boundary witnesses and cannot become stream-name data, hidden observer state, or quotient history identity.
\end{theorem}
\begin{proof}
Start from the handoff theorem \autoref{thm:observer-filter-streamname-handoff}. It identifies $S,L,R,C,P,N$ as the only stream-facing rows supplied by the filter.

Apply \autoref{thm:observer-filter-ledger-exactness} to the same carrier. The finite source rows of $H$ are exhausted by the selected surface $S$ and the omitted boundary $O$, so every stream-name read is already accounted for by the selected side of the partition.

The omitted side remains visible only as $O$. Since neither \autoref{def:observer-filter-bhist-carrier} nor the handoff theorem carries hidden observer state or quotient history identity, no omitted row can escape into the selected subhistory route.
\end{proof}

\closureat{ObserverFilterUp}{seedStr}
\closureat{ObserverFilterUp}{obligationStr}
\closureat{ObserverFilterUp}{scopedStr}

\begin{closurestatus}{\ObserverFilterUp}
  \constructivestory{An $\ObserverFilterUp$ packet is generated from a source BHist row, selected subhistory row, omitted-row ledger, componentwise hsame transports, observer ledger, displayed Cont routes, package provenance, and local NameCert row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:observer-filter-bhist-carrier}, \autoref{thm:observer-filter-namecert-obligations}, \autoref{thm:observer-filter-identity-stability}, \autoref{thm:observer-filter-streamname-handoff}, \autoref{thm:observer-filter-observer-history-factorization}, and \autoref{thm:observer-filter-ledger-exactness} specify the BHist filter carrier, selected and omitted ledgers, hsame transport, Cont route, Pkg provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close hidden observer state, quotient identity, unledgered deletion, Lean verification, or bridge checking for $\ObserverFilterUp$.}
  \upgradepath{Scoped closure requires binding the selected and omitted ledger, hsame transport, Cont routes, StreamName handoff, and ObserverHistoryIdentity factorization to explicit BEDC primitives.}
\end{closurestatus}
