\chapter{A Concrete Naming Certificate for $\ContourIntegralOperationUp$}
\label{ch:concrete-instances-contourintegraloperation-namecert}
\origin{human}

The $\ContourIntegralOperationUp$ interface turns the contour-integral operation surface of \autoref{ch:concrete-instances-contour-integral} into a concrete finite NameCert packet. Its traditional target is contour integration of a holomorphic input along a piecewise-linear contour, with value in $\ComplexUp$. Its BEDC sources are $\HolomorphicUp$, $\ContinuousFunctionUp$, $\ComplexUp$, $\mathsf{PLContour}$, and the surrounding $\NameCert$ rows.

\begin{definition}[Contour integral operation carrier]
\label{def:contour-integral-operation-carrier}
A $\ContourIntegralOperationUp$ carrier is a finite $\BHist$ packet
$$
Q=(D,F,\Gamma,V,A,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\ComplexUp$ domain row on which the input is read;
\item $F$ is the $\HolomorphicUp$ input row over $D$ together with the $\ContinuousFunctionUp$ boundary-read row used along the contour;
\item $\Gamma$ is the $\mathsf{PLContour}$ row, including endpoints, subdivision data, and the contour classifier;
\item $V$ is the output $\ComplexUp$ value row;
\item $A$ is the contour-integral operation row, read as the certificate-visible predicate $\mathsf{ContInt}(F,\Gamma,V)$;
\item $L$ is the contour-law ledger, listing existence, uniqueness, linearity, concatenation, reversal, reparameterization, and exactness coverage rows;
\item $H$ stores componentwise $\hsame$ transports for $D,F,\Gamma,V,A,L$;
\item $C$ stores the finite $\Cont$ routes by which consumers read the input, contour, value, law ledger, transport rows, package provenance, and local naming row;
\item $P$ is the $\Pkg$ provenance over the same finite operation packet;
\item $N$ is the local $\NameCert_{\ContourIntegralOperationUp}$ row.
\end{enumerate}
The classifier of the packet compares outputs only through the displayed $\hsame$-stable $\ComplexUp$ value row, and it compares inputs only through the classifier-aware $\HolomorphicUp$, $\ContinuousFunctionUp$, and $\mathsf{PLContour}$ rows.
\end{definition}

\begin{theorem}[Contour integral operation NameCert obligations]
\label{thm:contour-integral-operation-namecert-obligations}
The local $\NameCert_{\ContourIntegralOperationUp}$ surface for \autoref{def:contour-integral-operation-carrier} consists exactly of carrier admission for $Q$; classifier-aware input stability for $D,F,\Gamma$; $\hsame$-stable output transport for $V$; contour-integral operation admission for $A$; contour-law ledger exposure for $L$; finite $\Cont$ routes $C$; $\Pkg$ provenance $P$; and local naming exactness for $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection of the finite tuple $Q$. The displayed coordinates name the traditional contour-integral inputs, the output value, the operation predicate, and the law ledger before any consumer can read the certificate.

Input stability is componentwise. The holomorphic and continuous-function rows are transported through the classifiers of $\HolomorphicUp$ and $\ContinuousFunctionUp$, while the contour row is transported through the endpoint and subdivision classifier of $\mathsf{PLContour}$.

The output row $V$ is read only through the $\ComplexUp$ classifier and the stored $\hsame$ rows in $H$. The operation row $A$ is therefore stable under the same transported input and output rows.

Finally, $L,C,P,N$ do not add analytic content. They expose the contour laws, read routes, package provenance, and local naming row for the same finite operation packet.
\end{proof}

\begin{theorem}[Contour integral operation contour-laws ledger]
\label{thm:contour-integral-operation-contour-laws-ledger}
For an accepted $\ContourIntegralOperationUp$ carrier $Q=(D,F,\Gamma,V,A,L,H,C,P,N)$, the ledger $L$ accounts for exactly the following operation-certificate coverage: existence of the contour integral, uniqueness of the $\ComplexUp$ value up to the displayed classifier, linearity in the holomorphic input, concatenation of compatible $\mathsf{PLContour}$ rows, reversal of orientation, reparameterization by a displayed contour transport, and exactness of every exported contour-integral fact through $D,F,\Gamma,V,A,H,C,P,N$.

No law in $L$ exports a host integral, quotient of contours, selected representative, hidden branch, or analytic fact outside the displayed BEDC rows.
\end{theorem}
\begin{proof}
First read the operation row $A$ through the carrier. Its inputs are the displayed holomorphic and continuous-function rows together with the displayed $\mathsf{PLContour}$ row, and its output is the displayed $\ComplexUp$ value row.

The existence and uniqueness entries in $L$ certify that this operation row has a value and that any competing value is compared only by the $\ComplexUp$ classifier and the stored $\hsame$ transport. Thus exactness begins at the output row $V$, not at a host integral.

The linearity, concatenation, reversal, and reparameterization entries are ledger rows over the same packet. Each one consumes the classifier-aware input rows and the contour transport rows named by $H$ and $C$.

Since every read route passes through $C$ and every provenance read through $P,N$, an exported contour-integral fact can only cite the displayed packet. Quotient contours, selected representatives, hidden branches, and external analytic facts have no carrier coordinate and no ledger route.
\end{proof}

\closureat{ContourIntegralOperationUp}{seedStr}

\begin{closurestatus}{\ContourIntegralOperationUp}
  \constructivestory{A $\ContourIntegralOperationUp$ packet is generated from a $\ComplexUp$ domain row, $\HolomorphicUp$ and $\ContinuousFunctionUp$ input rows, a $\mathsf{PLContour}$ row, an output $\ComplexUp$ value row, a contour-integral operation row, contour-law ledgers, componentwise $\hsame$ transports, finite $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:contour-integral-operation-carrier}, \autoref{thm:contour-integral-operation-namecert-obligations}, and \autoref{thm:contour-integral-operation-contour-laws-ledger} bind the finite operation carrier, local NameCert obligation surface, classifier-aware stability, and contour-law ledger for the contour-integral operation packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a Lean theorem, a global Cauchy theory, quotient-contour equality, host integral semantics, analytic continuation, or any RH zero-location consequence.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, contour transport, holomorphic input transport, and contour-law ledger exactness for the same finite operation packet.}
\end{closurestatus}
