\chapter{A Concrete Naming Certificate for $\FiniteWitnessedRefutationUp$}
\label{ch:concrete-instances-finitewitnessedrefutation-namecert}
\origin{human}

The $\FiniteWitnessedRefutationUp$ interface records a causal-commitment failure as a finite contrary-record packet. It turns the causality reading of \autoref{sec:hard-problems-causality} into a concrete naming surface: an observed regularity ledger, a forward-binding $\Gap$ commitment, a contrary record, and the GAP non-escape ledger through which downstream consumers may inspect the failure. The finite contrary-record row specializes the witness-row discipline of \autoref{ch:concrete-instances-witnessedrefutation-namecert} and is consumed by bounded-search refutation through \autoref{ch:concrete-instances-boundedsearchrefutation-namecert} as a finite branch surface.

\begin{definition}[Finite witnessed refutation carrier]
\label{def:finite-witnessed-refutation-carrier}
A $\FiniteWitnessedRefutationUp$ carrier is a finite $\BHist$ packet
$$
F=(R,G,K,V,D,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $R$ is the finite observed-regularity ledger that supported the causal commitment;
\item $G$ is the $\Gap$-tagged forward-binding commitment asserting that the recorded regularity persists beyond the currently observed history;
\item $K$ is the finite commitment key naming the prediction, tolerance, domain cell, and record shape against which a contrary record is checked;
\item $V$ is the contrary-record witness, displayed as a finite observation row whose classifier conflicts with the commitment key;
\item $D$ is the decision ledger recording the local comparison between $K$ and $V$;
\item $H$ stores the displayed $\hsame$ transports for the regularity ledger, commitment row, commitment key, contrary witness, and decision ledger;
\item $C$ stores the $\Cont$ routes by which consumers inspect the support record, commitment, witness, and decision row;
\item $P$ is the $\Pkg$ provenance row over $\BHist$, $\hsame$, $\Cont$, $\Gap$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\FiniteWitnessedRefutationUp}$ registration row.
\end{enumerate}
The local classifier compares two carriers only through these rows. It does not decide universal causality, does not choose a host law, and does not erase the $\Gap$ commitment; it records that the named finite witness conflicts with the named finite commitment key.
\end{definition}
\leanchecked{BEDC.Derived.FiniteWitnessedRefutationUp.FiniteWitnessedRefutationCarrier\_single\_carrier\_alignment}

\begin{theorem}[Finite witnessed refutation NameCert obligations]
\label{thm:finite-witnessed-refutation-namecert-obligations}
The local $\NameCert_{\FiniteWitnessedRefutationUp}$ surface consists of five finite obligations:
\begin{enumerate}
\item carrier formation for the finite packet of \autoref{def:finite-witnessed-refutation-carrier};
\item classifier stability for the transported support ledger $R$, commitment row $G$, key $K$, contrary witness $V$, and decision ledger $D$;
\item witness exactness, requiring the contrary record consumed by the refutation to be exactly the displayed row $V$;
\item decision exactness, requiring the conflict claim to be read only through the comparison row $D$ between $K$ and $V$;
\item package closure, requiring the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows to contain exactly the provenance used by downstream causal-commitment consumers.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWitnessedRefutationUp.FiniteWitnessedRefutationCarrier\_namecert\_obligations}
\begin{proof}
Carrier formation is the tuple assembly of \autoref{def:finite-witnessed-refutation-carrier}. The support ledger, commitment, key, contrary witness, decision row, transport rows, continuation routes, package provenance, and naming row are all visible coordinates of $F$.

Classifier stability is componentwise. Transport the support ledger and commitment first, then transport the key and contrary witness, and finally transport the decision ledger that compares them.

Witness exactness and decision exactness are projections of the same finite packet. A consumer may cite a refutation only by reading $V$ against $K$ through $D$.

Package closure follows by projecting $H$, $C$, $P$, and $N$. No host causal law, all-future causal closure, or external failure oracle occurs as a coordinate of the carrier.
\end{proof}

\begin{theorem}[Finite witnessed refutation ledger exactness]
\label{thm:finite-witnessed-refutation-ledger-exactness}
For every accepted packet
$$
F=(R,G,K,V,D,H,C,P,N),
$$
the public refutation read is exactly the finite route from the support ledger $R$ and forward-binding commitment $G$ to the key $K$, contrary witness $V$, and comparison ledger $D$, transported by $H$, routed by $C$, packaged by $P$, and named by $N$. No refutation read may use a witness, comparison, or support record absent from the packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWitnessedRefutationUp.FiniteWitnessedRefutationLedgerExactness}
\begin{proof}
Begin with \autoref{thm:finite-witnessed-refutation-namecert-obligations}. Its witness exactness clause binds every contrary record to $V$, and its decision exactness clause binds the conflict claim to $D$.

The support side is also finite. The rows $R$ and $G$ state which observed regularity and which forward-binding $\Gap$ commitment are under inspection, while $K$ states the finite prediction cell tested by $V$.

The remaining rows $H,C,P,N$ carry transport, continuation, provenance, and local naming. Hence the refutation route is exactly the displayed finite ledger, not a hidden appeal to an ambient theory of causation.
\end{proof}

\begin{theorem}[Finite witnessed refutation non-escape]
\label{thm:finite-witnessed-refutation-non-escape}
The public boundary of $\FiniteWitnessedRefutationUp$ exports only the finite contrary-record packet over $\BHist$, $\Gap$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It exports no host causal law, no global falsification principle, no all-future causal closure, no external observation selector, and no erasure of the original $\Gap$ commitment.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWitnessedRefutationUp.FiniteWitnessedRefutationCarrier\_non\_escape}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:finite-witnessed-refutation-carrier}. The only failure-facing rows are the support ledger, commitment row, key, contrary witness, and decision ledger.

Apply \autoref{thm:finite-witnessed-refutation-ledger-exactness}. Every public refutation read passes through those rows and their displayed transport, continuation, package, and naming data.

The excluded objects are absent from the tuple. The packet therefore records a finite witnessed conflict with a causal commitment, while the wider question of universal causal closure remains outside the exported boundary.
\end{proof}

\begin{theorem}[Finite witnessed refutation public packet]
\label{thm:finite-witnessed-refutation-public-packet}
An accepted $\FiniteWitnessedRefutationUp$ packet is a public causal-commitment failure surface for downstream BEDC consumers. Such a consumer may inspect the supporting observations, the forward-binding $\Gap$ row, the commitment key, the contrary witness, and the decision ledger, but every read must factor through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed by the carrier.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWitnessedRefutationUp.FiniteWitnessedRefutationCarrier\_public\_packet}
\begin{proof}
Use \autoref{thm:finite-witnessed-refutation-namecert-obligations} to obtain the carrier, stability, witness, decision, and package clauses. These clauses identify the rows available to a public consumer.

Next apply \autoref{thm:finite-witnessed-refutation-ledger-exactness}. It forces the refutation read through $R,G,K,V,D,H,C,P,N$ and rules out any absent witness or comparison row.

Finally apply \autoref{thm:finite-witnessed-refutation-non-escape}. Since the carrier has no coordinate for a host law, global falsification principle, external observation selector, or erased $\Gap$, the exported object is exactly the finite public packet.
\end{proof}

\begin{theorem}[Finite witnessed refutation Gap boundary crosslink]
\label{thm:finite-witnessed-refutation-gap-boundary-crosslink}
For an accepted $\FiniteWitnessedRefutationUp$ packet
$$
F=(R,G,K,V,D,H,C,P,N),
$$
the forward-binding $\Gap$ row $G$ and the refusal/non-escape reading of the refutation are governed by the common boundary of \autoref{ch:concrete-instances-gapclosureboundary-namecert}. The finite witnessed refutation supplies the contrary record $V$ and decision ledger $D$, while $\GapClosureBoundaryUp$ supplies the rule that unsupported closure requests route to refusal rather than to internal universal closure.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWitnessedRefutationUp.FiniteWitnessedRefutationCarrier\_gap\_boundary\_crosslink}
\begin{proof}
Project the finite refutation carrier. The rows $R,G,K,V,D,H,C,P,N$ display the support ledger, forward-binding $\Gap$ commitment, commitment key, contrary witness, decision ledger, transport, continuation, provenance, and local name.

Apply the public packet theorem above. It lets downstream consumers inspect $R,G,K,V,D$ only through the same structural rows $H,C,P,N$ and does not erase the original $\Gap$ commitment.

Now use the GapClosureBoundary source and refusal surface of \autoref{thm:gap-closure-boundary-namecert-obligations} and \autoref{thm:gap-closure-boundary-refusal-nonescape}. That common carrier routes unsupported attempts to turn a $\Gap$ request into internal closure to the refusal ledger, so the finite witnessed refutation remains a contrary-record packet rather than a universal closure principle.
\end{proof}

\closureat{FiniteWitnessedRefutationUp}{obligationStr}

\begin{closurestatus}{\FiniteWitnessedRefutationUp}
  \constructivestory{A $\FiniteWitnessedRefutationUp$ packet is generated from a finite support ledger, a forward-binding $\Gap$ row, a commitment key, a contrary witness, a decision ledger, displayed transports, continuation routes, provenance, and local naming.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{The obligation scope records the carrier, local $\NameCert$ obligations, ledger exactness, non-escape, public packet, and Gap boundary crosslink for the finite contrary-record surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close universal causality, global falsification, all-future causal closure, host-law selection, bridge checking, or Lean verification.}
  \upgradepath{Scoped closure requires a checked consumer boundary showing that all downstream refutation reads remain inside the finite carrier, local $\NameCert$ obligations, ledger exactness, non-escape, public packet, and Gap boundary crosslink.}
\end{closurestatus}
