\chapter{A Concrete Naming Certificate for $\ExternalityGateUp$}
\label{ch:concrete-instances-externalitygate-namecert}
\origin{ai}

The $\ExternalityGateUp$ interface is the concrete gate attached to the
name-to-gate correspondence of \autoref{prin:apophatic-naming-name-to-gate}. It
turns a named externality into a finite NameCert packet: a socket-name row, a
gate-question row, a classifier for visible use, a refusal ledger, an audit
readback route, transport and continuation rows, package provenance, and a
local naming certificate. The packet makes the gate question inspectable
without turning the requested external supply into an internal BEDC object.

The packet consumes the apophatic-name row of \autoref{ch:concrete-instances-apophaticname-namecert} and the socket-ledger row of \autoref{ch:concrete-instances-apophaticsocket-namecert} before it exposes the gate question, visible-use classifier, refusal ledger, audit readback, transports, routes, provenance, and local NameCert row.

\begin{definition}[ExternalityGate carrier]
\label{def:externality-gate-carrier}
An $\ExternalityGateUp$ carrier is a finite $\BHist$ packet
$$
E=(A,Q,U,R,D,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $A$ is the apophatic-name row naming the externality;
\item $Q$ is the gate-question row determined by that name;
\item $U$ is the visible-use classifier row distinguishing cited socket use
from hidden internalization;
\item $R$ is the refusal ledger for requests that would make the externality
available as an internal generator, theorem, axiom, quotient, or host datum;
\item $D$ is the audit readback row exposing the name, gate question, visible-use
classifier, and refusal outcome to downstream checks;
\item $H$ records componentwise $\hsame$ transports for name, gate question,
classifier, refusal, readback, provenance, and local certificate rows;
\item $C$ records the $\Cont$ routes by which consumers read the gate question,
classifier, refusal ledger, and audit readback;
\item $P$ records $\Pkg$ provenance over $\ApophaticNameUp$,
$\ApophaticSocketUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ExternalityGateUp}$ row.
\end{enumerate}
The carrier contains no coordinate for the requested external supply itself.
\end{definition}
\leanchecked{BEDC.Derived.ExternalityGateUp.ExternalityGateTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ExternalityGate name-to-gate obligations]
\label{thm:externality-gate-name-to-gate-obligations}
For every accepted $\ExternalityGateUp$ carrier
$$
E=(A,Q,U,R,D,H,C,P,N),
$$
the apophatic-name row $A$ determines the gate-question row $Q$ as the public
question by which hidden internalization is tested. The local
$\NameCert_{\ExternalityGateUp}$ surface consists of carrier admission, name
readback, gate-question readback, visible-use classification, refusal-ledger
exhaustion, audit readback, componentwise transport, continuation routing,
package provenance, and the local naming row.
\end{theorem}
\begin{proof}
Project the carrier. The tuple lists the name row $A$, gate-question row $Q$,
visible-use classifier $U$, refusal ledger $R$, audit readback $D$, transport
rows, continuation routes, provenance, and local certificate.

The name-to-gate obligation is the dependency from $A$ to $Q$. A consumer that
cites the externality must pass through the gate question before it can be
classified as visible use by $U$ or refused by $R$.

The remaining obligations are the ordinary NameCert routing obligations. The
readback row $D$ exposes exactly the name, question, classifier, and refusal
outcome, while $H,C,P,N$ preserve and name those rows without adding an
internal supply coordinate.
\end{proof}

\begin{theorem}[ExternalityGate non-internalization]
\label{thm:externality-gate-non-internalization}
Every accepted $\ExternalityGateUp$ packet keeps the externality named by $A$
outside the generated substrate. A downstream consumer may cite $A$, ask the
gate question $Q$, receive the visible-use classification $U$, read the refusal
ledger $R$, and replay the audit readback $D$, but it cannot extract an
internal generator, theorem, axiom, quotient representative, host datum, or
unrecorded supply from the packet.
\end{theorem}
\begin{proof}
Begin with the carrier inventory of
\autoref{def:externality-gate-carrier}. The requested external supply is not a
coordinate of $E$; only its name, gate question, classifier, refusal ledger,
and audit readback are present.

Apply the name-to-gate obligations. Any consumer route must pass through $Q$,
then through either the visible-use classifier $U$ or the refusal ledger $R$.

The transport and continuation rows preserve the same finite surface. Since no
route in $C$ targets an internal supply coordinate, no downstream read can
convert the named externality into generated substrate content.
\end{proof}

\begin{theorem}[ExternalityGate NameCert surface]
\label{thm:externality-gate-namecert-surface}
The public $\NameCert_{\ExternalityGateUp}$ surface is exhausted by the
apophatic-name row $A$, gate-question row $Q$, visible-use classifier $U$,
refusal ledger $R$, audit readback row $D$, componentwise $\hsame$ transport,
displayed $\Cont$ routes, $\Pkg$ provenance, and local certificate row $N$.
It has no second surface for anonymous external dependence, unmarked proof
input, hidden setup fields, or host-side recognition content.
\end{theorem}
\begin{proof}
Use the NameCert obligations of
\autoref{thm:externality-gate-name-to-gate-obligations}. They list every row
available to the local certificate.

The non-internalization theorem then removes any possible extra source for the
named externality. What remains is exactly the finite public surface
$A,Q,U,R,D,H,C,P,N$.

Thus any consumer that claims an externality gate must cite the displayed rows.
A route through anonymous dependence or hidden host recognition has no row to
project and is refused by the ledger.
\end{proof}

\begin{theorem}[ExternalityGate audit readback]
\label{thm:externality-gate-audit-readback}
For an accepted $\ExternalityGateUp$ packet, the audit readback row $D$ reports
exactly four visible facts: the apophatic name $A$, the gate question $Q$, the
visible-use classifier result $U$, and the refusal-ledger outcome $R$. The
readback is stable under the displayed $\hsame$ and $\Cont$ routes and exposes
no internal supply object beyond those four rows.
\end{theorem}
\begin{proof}
Project the audit readback row $D$ from the carrier. By definition, it is
attached to $A,Q,U,R$ and not to a hidden external supply coordinate.

Use the componentwise transport rows in $H$ and replay routes in $C$. They move
the name, gate question, classifier, refusal ledger, and readback together, so
the audit report remains stable under displayed transport.

Finally apply the NameCert surface theorem. Since the certificate surface is
exhausted by the listed rows, the audit readback cannot expose any additional
internal object.
\end{proof}

\closureat{ExternalityGateUp}{seedStr}

\begin{closurestatus}{\ExternalityGateUp}
  \constructivestory{An $\ExternalityGateUp$ packet is generated from an apophatic-name row, a gate-question row, a visible-use classifier, a refusal ledger, an audit readback row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:externality-gate-carrier}, \autoref{thm:externality-gate-name-to-gate-obligations}, \autoref{thm:externality-gate-non-internalization}, \autoref{thm:externality-gate-namecert-surface}, and \autoref{thm:externality-gate-audit-readback} bind the finite name-to-gate carrier, refusal ledger, audit readback, and non-internalization surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close the requested external supply, host recognition content, hidden setup fields, quotient representatives, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, name-to-gate routing, refusal-ledger exhaustion, NameCert surface exactness, and audit-readback stability for the same finite packet.}
\end{closurestatus}
