\chapter{A Concrete Naming Certificate for $\RealDiagonalWindowCoverageUp$}
\label{ch:concrete-instances-realdiagonalwindowcoverage-namecert}
\origin{human}

The $\RealDiagonalWindowCoverageUp$ interface records the finite selected-window route used when Real completeness arguments pass from a precision request to a visible diagonal observation and then to a $\RealUp$ seal. It sits over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, and it exposes only the rows needed by the diagonal-window consumer.

This packet consumes the finite-window schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic observation ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the seal boundary of \autoref{ch:concrete-instances-real-namecert} before exposing its diagonal-window coverage row.

\begin{definition}[Real diagonal-window coverage carrier]
\label{def:real-diagonal-window-coverage-carrier}
A $\RealDiagonalWindowCoverageUp$ carrier is a finite $\BHist$ packet
$$
G=(q,w,r,d,e,h,c,p,n)
$$
with the following visible coordinates:
\begin{enumerate}
\item $q$ is the rational precision request, read through the displayed $\RatUp$ and $\DyadicRatCoreUp$ tolerance rows;
\item $w$ is the selected $\StreamNameUp$ window that exposes the finite diagonal observation interval requested by $q$;
\item $r$ is the $\RegSeqRatUp$ readback row naming the rational observation selected by $w$;
\item $d$ is the $\DyadicRatCoreUp$ observation ledger recording the endpoint, radius, comparison, and precision rows used by the readback;
\item $e$ is the $\RealUp$ seal row reached only after $q,w,r,d$ have been exposed;
\item $h$ stores componentwise $\hsame$ transports for the precision request, selected window, readback row, dyadic ledger, seal row, provenance, and local name;
\item $c$ stores the displayed $\Cont$ routes from $q$ to $w$, from $w$ to $r$, from $r$ to $d$, and from $d$ to the seal row $e$;
\item $p$ is the $\Pkg$ provenance over $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $n$ is the local $\NameCert_{\RealDiagonalWindowCoverageUp}$ row.
\end{enumerate}
The carrier contains no quotient stream, no host real equality, no unbounded diagonal stream, no ambient completeness theorem, and no selected limit outside the displayed seal row.
\end{definition}

\begin{definition}[Real diagonal-window coverage classifier]
\label{def:real-diagonal-window-coverage-classifier}
For accepted carriers
$$
G=(q,w,r,d,e,h,c,p,n)
\quad\text{and}\quad
G'=(q',w',r',d',e',h',c',p',n'),
$$
the classifier $\mathsf{RealDiagonalWindowCoverageClassifier}(G,G')$ compares only the displayed precision request, selected $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ observation ledger, $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row. It never compares host streams extensionally and never identifies completed reals by quotient equality.
\end{definition}

\begin{theorem}[Real diagonal-window coverage NameCert obligations]
\label{thm:real-diagonal-window-coverage-namecert-obligations}
The local $\NameCert_{\RealDiagonalWindowCoverageUp}$ surface for \autoref{def:real-diagonal-window-coverage-carrier} consists exactly of carrier admission for $G$, precision-request exposure through $q$, selected-window coverage through $w$, $\RegSeqRatUp$ readback through $r$, dyadic observation-ledger exactness through $d$, $\RealUp$ seal handoff through $e$, componentwise $\hsame$ transport through $h$, displayed $\Cont$ route replay through $c$, $\Pkg$ provenance through $p$, and local naming through $n$.
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed packet $G$. The rows $q,w,r,d,e,h,c,p,n$ list the precision request, selected window, regular rational readback, dyadic observation ledger, real seal, transports, routes, package provenance, and local name.

The selected-window obligation is finite. A consumer reads $q$ first, then uses $w$ to inspect the requested diagonal interval, and then reads the rational observation through $r$ and the dyadic ledger through $d$.

The remaining rows account for transport, route replay, provenance, and naming. Since no coordinate records quotient streams, host real equality, an unbounded diagonal stream, ambient completeness, or a selected external limit, the local $\NameCert$ obligation surface is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[Real diagonal-window coverage carrier admission]
\label{thm:real-diagonal-window-coverage-carrier-admission}
An accepted $\RealDiagonalWindowCoverageUp$ packet exposes exactly the carrier rows
$$
q,w,r,d,e,h,c,p,n.
$$
These rows are, respectively, the precision request, selected $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ observation ledger, $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\begin{proof}
Read \autoref{def:real-diagonal-window-coverage-carrier}. Carrier admission is projection from the displayed tuple $G=(q,w,r,d,e,h,c,p,n)$.

Apply the NameCert obligations of \autoref{thm:real-diagonal-window-coverage-namecert-obligations}. They name each coordinate as part of the local certificate surface and provide no additional row beyond the displayed tuple.

The carrier definition excludes quotient streams, host real equality, unbounded diagonal streams, ambient completeness, and selected external limits, so the accepted packet exposes exactly the nine listed rows.
\end{proof}
\leanchecked{BEDC.Derived.RealDiagonalWindowCoverageUp.RealDiagonalWindowCoverageCarrier\_carrier\_admission}

\begin{theorem}[Real diagonal-window coverage classifier stability]
\label{thm:real-diagonal-window-coverage-classifier-stability}
For accepted $\RealDiagonalWindowCoverageUp$ packets, classifier comparison is stable under componentwise $\hsame$ transport of the precision request, selected $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ observation ledger, $\RealUp$ seal row, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\begin{proof}
Unfold the classifier in \autoref{def:real-diagonal-window-coverage-classifier}. Its comparison fields are exactly the displayed precision request, window, readback, dyadic ledger, seal row, transports, routes, provenance, and local name.

Use the $h$ coordinate of the carrier to transport each component. The same rows are the rows exposed by carrier admission, so no comparison field is lost or replaced during transport.

The RealUp handoff theorem keeps seal-facing comparisons on the displayed route through $q,w,r,d,h,c,p,n$. Hence classifier stability never appeals to host stream equality, quotient equality of completed reals, or an undisplayed completeness principle.
\end{proof}

\begin{theorem}[Real diagonal-window coverage selected-window coverage]
\label{thm:real-diagonal-window-coverage-selected-window-coverage}
Every $\RealUp$-facing read of an accepted $\RealDiagonalWindowCoverageUp$ packet reaches the seal row $e$ only after the selected $\StreamNameUp$ window $w$ and the $\DyadicRatCoreUp$ observation ledger $d$ have been displayed.
\end{theorem}
\begin{proof}
Start from the carrier definition. The $\RealUp$ seal row $e$ is listed after the precision request $q$, selected window $w$, $\RegSeqRatUp$ readback $r$, and dyadic ledger $d$.

Apply \autoref{thm:real-diagonal-window-coverage-namecert-obligations}. The selected-window and dyadic observation-ledger obligations are part of the local certificate surface before any seal-facing consumer is exported.

Now use \autoref{thm:real-diagonal-window-coverage-realup-handoff}. It routes every $\RealUp$ completion or continuous-map consumer through the displayed selected-window and dyadic-ledger rows before the seal row is read.
\end{proof}

\begin{theorem}[Real diagonal-window coverage RealUp handoff]
\label{thm:real-diagonal-window-coverage-realup-handoff}
Every $\RealUp$ completion or continuous-map consumer of an accepted $\RealDiagonalWindowCoverageUp$ carrier receives the seal row $e$ only through the displayed route
$$
q,w,r,d,h,c,p,n.
$$
Thus the handoff consumes a rational precision request, a selected $\StreamNameUp$ window, a $\RegSeqRatUp$ readback row, a $\DyadicRatCoreUp$ observation ledger, componentwise transport, route replay, package provenance, and local naming before the $\RealUp$ seal is read.
\end{theorem}
\leanchecked{BEDC.Derived.RealDiagonalWindowCoverageUp.RealDiagonalWindowCoverageCarrier\_realup\_handoff}
\begin{proof}
Start with the carrier row $e$. It is the only $\RealUp$ seal coordinate in the finite packet.

Apply the NameCert obligations. They force a seal-facing read to pass through the precision request $q$, the selected window $w$, the readback row $r$, and the dyadic ledger $d$ before the seal is consumed.

The rows $h$ and $c$ replay the displayed transport and continuation data, while $p$ and $n$ provide provenance and local naming. Because the carrier lists no host equality, quotient equality, ambient completeness, or external limit coordinate, the real-facing handoff is exactly the displayed route.
\end{proof}

\begin{theorem}[Real diagonal-window coverage non-escape]
\label{thm:real-diagonal-window-coverage-nonescape}
Every downstream consumer of an accepted $\RealDiagonalWindowCoverageUp$ packet factors through the finite rows
$$
q,w,r,d,e,h,c,p,n.
$$
The consumer may read the rational precision request, selected $\StreamNameUp$ window, $\RegSeqRatUp$ source observation, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row, and it cannot read quotient streams, host real equality, unbounded diagonal streams, ambient completeness, or a choice-selected limit.
\end{theorem}
\begin{proof}
Project the accepted carrier and the local NameCert surface. The rows $q,w,r,d,e,h,c,p,n$ are the complete displayed packet.

Use the classifier of \autoref{def:real-diagonal-window-coverage-classifier}. It compares only those rows under the stored transport and route data, so a transported consumer remains on the same finite window-read route.

Use the RealUp handoff theorem for seal-facing consumers. It routes every completion or continuous-map read through $q,w,r,d,h,c,p,n$ before $e$ is consumed.

Since the carrier has no remaining coordinate beyond the displayed rows, no downstream consumer can extract quotient-stream data, host real equality, unbounded diagonal data, ambient completeness, or a choice-selected limit from the packet.
\end{proof}

\begin{theorem}[Real diagonal-window tail-meet triangle handoff]
\label{thm:real-diagonal-window-coverage-tail-meet-triangle-handoff}
Let $G=(q,w,r,d,e,h,c,p,n)$ be an accepted $\RealDiagonalWindowCoverageUp$ packet. Suppose its selected window row $w$ is supplied by an accepted $\RegularCauchyTailMeetUp$ shared-threshold packet, and suppose its dyadic observation ledger $d$ is supplied by an accepted $\RegularCauchyTriangleBoundUp$ three-leg estimate. Then every $\RealUp$ seal-facing consumer of $G$ factors through the finite route
$$
q \to w \to r \to d \to e
$$
together with the tail-meet shared threshold, the triangle-bound tolerance ledger, componentwise $\hsame$ rows, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ rows of the three packets.

The handoff exports no quotient stream, selected limit, host real equality, ambient completeness principle, or hidden tail oracle.
\end{theorem}
\begin{proof}
Begin with the RealUp handoff of \autoref{thm:real-diagonal-window-coverage-realup-handoff}. It forces every seal-facing read of $G$ through the displayed precision request, selected window, readback row, dyadic ledger, transport rows, continuation routes, provenance, and local name before $e$ is consumed.

Next read the selected window through the shared tail packet. Apply \autoref{thm:regular-cauchy-tail-meet-obligation-closure-package}; its shared-threshold surface supplies the paired regular-Cauchy tails, source schedules, source modulus rows, threshold ledger, comparison row, transports, continuations, provenance, and local tail-meet name.

Now read the dyadic observation ledger through the triangle-bound packet. Apply \autoref{thm:regular-cauchy-triangle-bound-phase-handoff} for the three-leg estimate and \autoref{thm:regular-cauchy-triangle-bound-nonescape} for its consumer boundary.

Composing the displayed $\Cont$ routes gives the route $q \to w \to r \to d \to e$. Each leg is already guarded by componentwise $\hsame$, $\Pkg$ provenance, and a local $\NameCert$ row, and the cited non-escape boundaries leave no coordinate for quotient streams, selected limits, host real equality, ambient completeness, or a hidden tail oracle.
\end{proof}

\begin{theorem}[Real diagonal-window coverage kernel scope]
\label{thm:real-diagonal-window-coverage-kernel-scope}
The carrier, classifier, local $\NameCert_{\RealDiagonalWindowCoverageUp}$ obligations, selected-window coverage, $\RealUp$ handoff, non-escape boundary, and tail-meet triangle handoff for an accepted $\RealDiagonalWindowCoverageUp$ packet are all routed through exactly the displayed $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. No step in this kernel scope adds a quotient-stream coordinate, host real equality, unbounded diagonal stream, selected limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start from \autoref{def:real-diagonal-window-coverage-carrier} and \autoref{def:real-diagonal-window-coverage-classifier}. They display the packet $G=(q,w,r,d,e,h,c,p,n)$ and restrict classifier comparison to the same precision request, selected window, readback row, dyadic ledger, seal row, transports, continuations, provenance, and local name.

Apply \autoref{thm:real-diagonal-window-coverage-namecert-obligations} for the local certificate surface. The selected-window coverage theorem then forces every seal-facing read to display $w$ and $d$ before the $\RealUp$ row $e$ is consumed.

Use \autoref{thm:real-diagonal-window-coverage-realup-handoff} and \autoref{thm:real-diagonal-window-coverage-nonescape}. They keep completion and downstream consumers on the finite route through $q,w,r,d,e,h,c,p,n$ and exclude every undisplayed real or stream coordinate.

Finally, \autoref{thm:real-diagonal-window-coverage-tail-meet-triangle-handoff} composes this route with the cited $\RegularCauchyTailMeetUp$ and $\RegularCauchyTriangleBoundUp$ packets. Those packets are consumed through their displayed threshold and estimate rows, so the full kernel dependency scope is precisely the listed BEDC rows.
\end{proof}

\begin{theorem}[Real diagonal-window coverage selected-window source lock]
\label{thm:real-diagonal-window-coverage-selected-window-source-lock}
For an accepted $\RealDiagonalWindowCoverageUp$ packet $G=(q,w,r,d,e,h,c,p,n)$, the selected window $w$ and dyadic ledger $d$ determine the only source-lock route from the rational precision request $q$ to the $\RegSeqRatUp$ readback row $r$ and the $\RealUp$ seal row $e$. The source lock has no quotient stream, host equality, unbounded diagonal stream, selected limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:real-diagonal-window-coverage-carrier}. The route from $q$ to $r$ passes through the selected $\StreamNameUp$ window $w$, and the route from $r$ to $e$ passes through the $\DyadicRatCoreUp$ ledger $d$.

Apply \autoref{thm:real-diagonal-window-coverage-namecert-obligations} to identify the certificate rows that expose $w$, $r$, $d$, and $e$. Then apply \autoref{thm:real-diagonal-window-coverage-selected-window-coverage}, which prevents a $\RealUp$-facing read from reaching $e$ before the selected window and dyadic ledger have been displayed.

The handoff theorem \autoref{thm:real-diagonal-window-coverage-realup-handoff} supplies the same route for completion and continuous-map consumers. The non-escape theorem \autoref{thm:real-diagonal-window-coverage-nonescape} removes every other source coordinate, so $w$ and $d$ are the only source-lock route to $r$ and $e$.
\end{proof}

\begin{theorem}[Real diagonal-window coverage tail-meet triangle scope]
\label{thm:real-diagonal-window-coverage-tail-meet-triangle-scope}
The tail-meet and triangle-bound handoff cited by \autoref{thm:real-diagonal-window-coverage-tail-meet-triangle-handoff} consumes only the $\RegularCauchyTailMeetUp$ shared-threshold packet, the $\RegularCauchyTriangleBoundUp$ estimate packet, and the local $\RealDiagonalWindowCoverageUp$ route
$$
q,w,r,d,e,h,c,p,n.
$$
It exports no extra source stream, no selected limit, no host equality, no ambient completeness row, and no hidden tail oracle.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:real-diagonal-window-coverage-tail-meet-triangle-handoff}. Its hypotheses name exactly one accepted selected-window packet from $\RegularCauchyTailMeetUp$ and one accepted dyadic-ledger packet from $\RegularCauchyTriangleBoundUp$.

The local $\RealDiagonalWindowCoverageUp$ contribution is fixed by \autoref{def:real-diagonal-window-coverage-carrier} and \autoref{thm:real-diagonal-window-coverage-namecert-obligations}. These give only the rows $q,w,r,d,e,h,c,p,n$ and the corresponding local certificate surface.

The $\RealUp$ handoff and non-escape theorems keep the seal-facing consumer on the displayed route through those rows. Therefore the tail-meet and triangle-bound packets are consumed as threshold and estimate witnesses for $w$ and $d$, not as a new stream, limit, host-equality, completeness, or tail-oracle coordinate.
\end{proof}

\closureat{RealDiagonalWindowCoverageUp}{seedStr}
\closureat{RealDiagonalWindowCoverageUp}{obligationStr}
\closureat{RealDiagonalWindowCoverageUp}{scopedStr}
\closureat{RealDiagonalWindowCoverageUp}{scopedStr}[BEDC.Derived.RealDiagonalWindowCoverageUp.RealDiagonalWindowCoverageCarrier\_realup\_handoff]
\closureat{RealDiagonalWindowCoverageUp}{publicStr}
\closureat{RealDiagonalWindowCoverageUp}{bridgedStr}[BEDC.Derived.RealDiagonalWindowCoverageUp.RealDiagonalWindowCoverageCarrier\_realup\_handoff]
\closureat{RealDiagonalWindowCoverageUp}{matureStr}[BEDC.Derived.RealDiagonalWindowCoverageUp.RealDiagonalWindowCoverageCarrier\_realup\_handoff]

\begin{closurestatus}{\RealDiagonalWindowCoverageUp}
  \constructivestory{A $\RealDiagonalWindowCoverageUp$ packet is generated from a rational precision request, a selected $\StreamNameUp$ window, a $\RegSeqRatUp$ readback row, a $\DyadicRatCoreUp$ observation ledger, a $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:real-diagonal-window-coverage-carrier}, \autoref{def:real-diagonal-window-coverage-classifier}, \autoref{thm:real-diagonal-window-coverage-namecert-obligations}, \autoref{thm:real-diagonal-window-coverage-selected-window-coverage}, \autoref{thm:real-diagonal-window-coverage-realup-handoff}, \autoref{thm:real-diagonal-window-coverage-nonescape}, \autoref{thm:real-diagonal-window-coverage-tail-meet-triangle-handoff}, \autoref{thm:real-diagonal-window-coverage-kernel-scope}, \autoref{thm:real-diagonal-window-coverage-selected-window-source-lock}, and \autoref{thm:real-diagonal-window-coverage-tail-meet-triangle-scope} bind the finite selected-window route from precision request through $\StreamNameUp$ and $\RegSeqRatUp$ readback to $\DyadicRatCoreUp$ observations, the $\RealUp$ seal, the selected-window source lock, and the tail-meet triangle scope for downstream consumers.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.RealDiagonalWindowCoverageUp.RealDiagonalWindowCoverageCarrier\_realup\_handoff}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close RealUp completeness, uniqueness of completed limits, quotient equality of streams, host real equality, continuous-map theorems, Lean verification, or bridge checking.}
  \upgradepath{Bridge checking requires a checked standard bridge for the selected-window $\RealUp$ seal handoff.}
\end{closurestatus}
