\chapter{A Concrete Naming Certificate for $\ContourIntegralSocketUp$}
\label{ch:concrete-instances-contourintegralsocket-namecert}
\origin{human}

The $\ContourIntegralSocketUp$ interface turns the contour-integral operation surface of \autoref{ch:concrete-instances-contour-integral} into a finite BEDC operation socket. It names piecewise-linear contour rows, holomorphic input rows, Riemann-sum modulus rows, complex output rows, componentwise transport, continuation routes, package provenance, and a local naming ledger for consumers that need contour integration without a host complex-analysis oracle.

\begin{definition}[Contour-integral socket carrier]
\label{def:contour-integral-socket-carrier}
A $\ContourIntegralSocketUp$ carrier is a finite $\BHist$ packet
$$
S=(G,F,M,I,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the $\mathsf{PLContour}$ row, including endpoints, segment list, concatenation boundary, reversal boundary, and reparameterization witness rows;
\item $F$ is the $\HolomorphicUp$ input row on a displayed $\ComplexUp$ neighbourhood of the contour image;
\item $M$ is the Riemann-sum modulus row, carrying tagged-partition refinement data and the convergence modulus used to read the integral;
\item $I$ is the $\ComplexUp$ output row naming the contour-integral value;
\item $L$ is the operation-law ledger for linearity, concatenation, reversal, reparameterization, Cauchy triangle, polygon subdivision, and Cauchy integral formula rows;
\item $H$ stores componentwise $\hsame$ transports for $G,F,M,I,L$ and for the local naming rows;
\item $C$ stores the finite $\Cont$ routes by which analytic-continuation and Cauchy-operation consumers read the contour, input, modulus, output, operation ledger, package provenance, and local naming row;
\item $P$ is the $\Pkg$ provenance over the same finite operation-socket packet;
\item $N$ is the local $\NameCert_{\ContourIntegralSocketUp}$ ledger.
\end{enumerate}
The carrier exposes only this finite socket. It contains no host contour-integral function, no quotient path space, no use of $\mathsf{Classical.choice}$, and no undisplayed completeness principle.
\end{definition}

\begin{theorem}[Contour-integral socket NameCert obligations]
\label{thm:contour-integral-socket-namecert-obligations}
The local $\NameCert_{\ContourIntegralSocketUp}$ surface for \autoref{def:contour-integral-socket-carrier} consists of five finite rows: carrier admission for $S$; classifier stability for the $\mathsf{PLContour}$ row, the $\HolomorphicUp$ input row, the Riemann-sum modulus row, the $\ComplexUp$ output row, and the operation ledger; operation-law ledger exactness for $L$; $\Pkg$ provenance over $G,F,M,I,L,H,C$; and local naming exactness for $N$.
\end{theorem}
\leanchecked{BEDC.Derived.ContourIntegralSocketUp.ContourIntegralSocketSemanticNameCert}
\begin{proof}
Carrier admission is projection of the tuple $S$. Each contour, input, modulus, output, ledger, transport, continuation, package, and local naming coordinate is a displayed row of one finite $\BHist$ packet.

Classifier stability is componentwise. Transport of $G$ preserves the piecewise-linear contour data, transport of $F$ preserves the holomorphic input row over the transported neighbourhood, transport of $M$ preserves the Riemann-sum modulus, and transport of $I$ preserves the complex output row.

The package and naming rows repack those same coordinates. Since the carrier definition lists no host contour-integral function, quotient path space, choice principle, or completeness oracle, the obligation surface is exactly the five displayed rows.
\end{proof}

\begin{theorem}[Contour-integral socket transport]
\label{thm:contour-integral-socket-transport}
Let $S=(G,F,M,I,L,H,C,P,N)$ be an accepted $\ContourIntegralSocketUp$ carrier. Any componentwise $\hsame$ transport of the contour row, holomorphic input row, Riemann-sum modulus row, and complex output row preserves carrier admission, the finite $\Cont$ read routes, the operation-law ledger, $\Pkg$ provenance, and the local $\NameCert$ ledger.
\end{theorem}
\leanchecked{BEDC.Derived.ContourIntegralSocketUp.ContourIntegralSocketCarrier\_transport}
\leanvariant{BEDC.Derived.ContourIntegralSocketUp.ContourIntegralSocketCarrier\_component\_transport\_closure}
\begin{proof}
Begin with the transport row $H$. It stores the componentwise $\hsame$ comparisons for the contour, holomorphic input, modulus, output, ledger, and local naming rows.

The continuation routes in $C$ read only those transported coordinates. Therefore a consumer that follows a route before transport reaches the corresponding transported coordinate after transport.

The package and local naming rows are attached to the same finite packet. Repacking through $H$ preserves admission, provenance, and the local certificate without exposing any host equality beyond the displayed $\hsame$ rows.
\end{proof}

\begin{theorem}[Contour-integral socket ledger exactness]
\label{thm:contour-integral-socket-ledger-exactness}
For an accepted $\ContourIntegralSocketUp$ carrier $S=(G,F,M,I,L,H,C,P,N)$, every exported contour-integral operation law factors through the ledger row $L$ and one of the displayed rows $G,F,M,I,H,C,P,N$. The ledger entries are exactly the linearity, concatenation, reversal, reparameterization, Cauchy-triangle, polygon-subdivision, and Cauchy-integral-formula rows named by the contour-integral operation surface.
\end{theorem}
\begin{proof}
Read an exported operation-law request through the finite routes in $C$. If the request asks for contour shape, holomorphic input data, modulus evidence, output value, transport, package, or local naming, the corresponding coordinate of $S$ supplies it.

If the request asks for an operation law, the only classifier-visible destination is the ledger row $L$. Its entries are the displayed operation laws listed in the carrier definition.

Thus every exported law is accounted for by a row of the packet, and no additional analytic theorem, quotient-path equation, or host integral identity can enter the socket.
\end{proof}

\begin{theorem}[Contour-integral socket non-escape]
\label{thm:contour-integral-socket-non-escape}
An accepted $\ContourIntegralSocketUp$ carrier exports no host complex-analysis theorem, no quotient path equality, no $\mathsf{Classical.choice}$ witness, and no hidden completeness object. A consumer request outside the displayed contour, holomorphic input, modulus, output, operation-ledger, transport, continuation, package, and local naming rows is recorded as outside the socket boundary and is not returned as a contour-integral fact.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. The packet contains the displayed rows $G,F,M,I,L,H,C,P,N$ and no further analytic carrier.

The continuation routes in $C$ can only land in those rows. A request for a host complex-analysis theorem, quotient path equality, choice witness, or undisplayed completeness object has no coordinate to read.

The local naming ledger therefore records such a request as outside the operation socket. It does not manufacture a contour-integral fact or an additional $\ComplexUp$ output row.
\end{proof}

\begin{theorem}[Contour-integral socket handoff]
\label{thm:contour-integral-socket-handoff}
Every analytic-continuation or Cauchy-operation consumer of an accepted $\ContourIntegralSocketUp$ carrier factors its read through the finite packet $S=(G,F,M,I,L,H,C,P,N)$. Analytic-continuation consumers receive the holomorphic input, contour-domain, transport, and output rows; Cauchy-operation consumers receive the Cauchy-triangle, polygon-subdivision, and Cauchy-integral-formula rows of $L$ together with the same provenance and local naming rows.
\end{theorem}
\begin{proof}
For an analytic-continuation consumer, follow the routes in $C$ to the holomorphic input row $F$, the contour-domain information in $G$, the output row $I$, and the transports in $H$. These rows supply the finite handoff surface.

For a Cauchy-operation consumer, follow the routes in $C$ to the operation ledger $L$. The Cauchy-triangle, polygon-subdivision, and Cauchy-integral-formula entries are ledger rows attached to the same contour and holomorphic input data.

Both consumers then read $\Pkg$ provenance and local naming through $P$ and $N$. The handoff is therefore bounded by the displayed socket packet and does not expose any standalone host contour-integral operation.
\end{proof}

\closureat{ContourIntegralSocketUp}{seedStr}

\begin{closurestatus}{\ContourIntegralSocketUp}
  \constructivestory{A $\ContourIntegralSocketUp$ packet is generated from a $\mathsf{PLContour}$ row, a $\HolomorphicUp$ input row, a Riemann-sum modulus row, a $\ComplexUp$ output row, operation-law ledger rows, componentwise $\hsame$ transports, finite $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ ledger.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:contour-integral-socket-carrier}, \autoref{thm:contour-integral-socket-namecert-obligations}, \autoref{thm:contour-integral-socket-transport}, \autoref{thm:contour-integral-socket-ledger-exactness}, \autoref{thm:contour-integral-socket-non-escape}, and \autoref{thm:contour-integral-socket-handoff} define the finite operation socket, transport rows, operation-law ledger exactness, non-escape boundary, and downstream handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a host contour-integral function, quotient path spaces, global complex analysis, RH zero-location consequences, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, operation-law ledger exactness, package provenance, non-escape, and consumer handoff rows for the same finite socket packet.}
\end{closurestatus}
