\chapter{A Concrete Naming Certificate for \(\PolynomialUp\)}
\label{ch:concrete-instances-polynomial-namecert}

The polynomial interface \(\PolynomialUp\) has certificate obligations over a scalar ring from \autoref{ch:concrete-instances-ring-namecert} as finite coefficient sequences from \autoref{ch:concrete-instances-list-namecert}, normalized to remove trailing zeros so that the highest-index entry is nonzero (or the sequence is empty for the zero polynomial). The classifier is structural sameness on the normalized representative. Polynomial addition and multiplication are derived operations governed by the ring's certificate fields.

\section{Carrier definition}

\begin{definition}[Polynomial carrier]
\label{def:polynomial-carrier}
Use finite coefficient lists over a scalar ring, normalized by removing trailing zero coefficients.
\end{definition}

\section{The certificate}

\begin{definition}[Polynomial source specification]
\label{def:polynomial-source-specification}
The source is \(\ListUp(R)\) over a certified scalar ring \(\RingUp(R)\), restricted to normalized lists.
\end{definition}

\begin{definition}[Polynomial pattern specification]
\label{def:polynomial-pattern-specification}
The pattern is finite coefficient-sequence generation followed by canonical trimming.
\end{definition}

\begin{definition}[Polynomial classifier specification]
\label{def:polynomial-classifier-specification}
The classifier is structural list sameness on normalized coefficient lists.
\end{definition}

\begin{definition}[Polynomial stability certificate]
\label{def:polynomial-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item normalization removes trailing zeros
  \item normalization is idempotent
  \item zero polynomial represented by empty list
  \item structural reflexivity and transitivity
  \item addition and multiplication closure after normalization
\end{enumerate}
\end{definition}

\begin{definition}[Polynomial ledger policy]
\label{def:polynomial-ledger-policy}
Record the original coefficient list and its normalized representative.
\end{definition}

\begin{definition}[\(\PolynomialUp\) certificate obligations]
\label{def:polynomial-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\PolynomialUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\PolynomialUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:polynomial-zero-axiom-note}
Replaces quotienting by trailing-zero equivalence with normalization.
\end{remark}

\begin{theorem}[Finite additive fold congruence for coefficient lists]
\label{thm:finite-additive-fold-congruence-coefficient-lists}
Let \(R\) be a scalar carrier with classifier \(\sim_R\), zero \(0_R\), and addition \(+\). Assume \(0_R\sim_R0_R\) and the additive congruence field
\[
a\sim_R a' \;\text{and}\; b\sim_R b'
\quad\Longrightarrow\quad
(a+b)\sim_R(a'+b')
\]
for all scalar endpoints. These are among the additive ring fields retained in \autoref{def:ring-stability-certificate}; when the scalar source is presented by the commutative-ring certificate, \autoref{prop:commring-forgets-ring-certificate} keeps these additive fields unchanged.

Let \(\mathsf{fold}_{+}\) be the finite recursive coefficient fold on finite coefficient spines, satisfying
\[
\mathsf{fold}_{+}(\mathsf{nil})=0_R,
\qquad
\mathsf{fold}_{+}(\mathsf{cons}(a,xs'))=a+\mathsf{fold}_{+}(xs').
\]
For finite coefficient spines \(xs,ys:\mathsf{ListCarrier}(R)\), if their same-length pointwise scalar comparison is represented by the structural classifier witness
\[
\mathsf{ListClassifierSpec}(\sim_R,xs,ys)
\]
from \autoref{def:list-classifier-specification}, then
\[
\mathsf{fold}_{+}(xs)\sim_R\mathsf{fold}_{+}(ys).
\]
\end{theorem}
\begin{proof}
Induct on the structural classifier witness. By \autoref{thm:list-classifier-case-exactness}, the nil case is the nil-nil constructor and the cons case is the cons-cons constructor; mixed nil-cons shapes have no classifier witness. The same structural witness also records the equal finite-spine length by \autoref{thm:list-classifier-length-eq}.

In the nil-nil case, the two fold equations identify both fold endpoints with \(0_R\). The assumed zero self-classification \(0_R\sim_R0_R\) gives the fold comparison.

In the cons-cons case, write the two spines as \(\mathsf{cons}(a,xs')\) and \(\mathsf{cons}(b,ys')\). The constructor clause supplies the head comparison \(a\sim_R b\) and the tail classifier witness \(\mathsf{ListClassifierSpec}(\sim_R,xs',ys')\). The induction hypothesis gives \(\mathsf{fold}_{+}(xs')\sim_R\mathsf{fold}_{+}(ys')\). Applying the additive congruence field from \autoref{def:ring-stability-certificate} to these two comparisons yields
\[
(a+\mathsf{fold}_{+}(xs'))\sim_R(b+\mathsf{fold}_{+}(ys')).
\]
The cons fold equations identify these endpoints with \(\mathsf{fold}_{+}(\mathsf{cons}(a,xs'))\) and \(\mathsf{fold}_{+}(\mathsf{cons}(b,ys'))\), giving the displayed fold comparison.
\end{proof}

\begin{theorem}[Zero convolution summands fold to zero]
\label{thm:zero-convolution-summands-fold-zero}
Let \(R\) be a scalar carrier with classifier \(\sim_R\), zero \(0_R\), and addition \(+\), equipped with the additive fields retained in \autoref{def:ring-stability-certificate}: zero self-classification, classifier transitivity, additive congruence, and the additive left-zero law. For a commutative-ring scalar source, these are unchanged by \autoref{prop:commring-forgets-ring-certificate}.

Let \(\mathsf{fold}_{+}\) be the finite recursive coefficient fold from \autoref{thm:finite-additive-fold-congruence-coefficient-lists}. Let \(\mathsf{summ}_I:\mathsf{ListCarrier}(R)\) be the finite spine of scalar summands selected by a raw Cauchy convolution index spine \(I\), and let \(\mathsf{zero}_I:\mathsf{ListCarrier}(R)\) be the same finite spine with every entry replaced by \(0_R\). If the all-zero summand condition is represented by the structural witness
\[
\mathsf{ListClassifierSpec}(\sim_R,\mathsf{summ}_I,\mathsf{zero}_I),
\]
then
\[
\mathsf{fold}_{+}(\mathsf{summ}_I)\sim_R0_R.
\]
\end{theorem}
\begin{proof}
The displayed hypothesis is a finite-spine classifier witness as in \autoref{def:list-classifier-specification}. By \autoref{thm:list-classifier-case-exactness}, its only possible constructor cases are nil-nil and cons-cons. Induct on this structural witness.

In the nil-nil case, both spines are \(\mathsf{nil}\). The fold equation from \autoref{thm:finite-additive-fold-congruence-coefficient-lists} identifies the left endpoint with \(0_R\), and zero self-classification supplies \(0_R\sim_R0_R\).

In the cons-cons case, write the summand spine as \(\mathsf{cons}(a,xs')\) and the matching zero spine as \(\mathsf{cons}(0_R,zs')\). The constructor clause gives the head comparison \(a\sim_R0_R\) and the tail witness \(\mathsf{ListClassifierSpec}(\sim_R,xs',zs')\). The induction hypothesis gives
\[
\mathsf{fold}_{+}(xs')\sim_R0_R.
\]
Applying additive congruence from \autoref{def:ring-stability-certificate} to the head comparison and this tail comparison yields
\[
(a+\mathsf{fold}_{+}(xs'))\sim_R(0_R+0_R).
\]
The additive left-zero law identifies \(0_R+0_R\) with \(0_R\). Classifier transitivity composes these two comparisons. The cons fold equation then identifies \(a+\mathsf{fold}_{+}(xs')\) with \(\mathsf{fold}_{+}(\mathsf{cons}(a,xs'))\), giving the claimed fold comparison for the cons spine.
\end{proof}

\begin{definition}[Classified zero remainder spine]
\label{def:classified-zero-remainder-spine}
Let $R$ be a scalar carrier with classifier $\sim_R$ and zero endpoint $0_R$. For a finite coefficient spine $t:\mathsf{ListCarrier}(R)$, $\mathsf{ZeroRem}_R(t)$ means that every displayed coefficient in $t$ is scalar-classified as zero. It is the finite-spine predicate generated by the nil clause and the cons clause
$$
a\sim_R0_R
\quad\text{and}\quad
\mathsf{ZeroRem}_R(t')
\quad\Longrightarrow\quad
\mathsf{ZeroRem}_R(\mathsf{cons}(a,t')).
$$
\end{definition}

\begin{lemma}[Trim invariance under a common classified spine and zero remainders]
\label{lem:trim-invariance-common-classified-spine-zero-remainders}
Let $R$ be a scalar carrier with classifier $\sim_R$, zero endpoint $0_R$, and scalar certificate $\mathsf{cert}_R:\NameCert(R,\sim_R)$. Assume $0_R\sim_R0_R$. For a commutative-ring scalar source, \autoref{prop:commring-forgets-ring-certificate} keeps the underlying ring carrier, zero endpoint, and classifier unchanged. Let $\mathsf{trim}_R$ be the canonical polynomial trimming operation specified by \autoref{def:polynomial-pattern-specification} and \autoref{def:polynomial-stability-certificate}.

For finite coefficient spines $p,q,r,s:\mathsf{ListCarrier}(R)$, if
$$
\mathsf{ListClassifierSpec}(\sim_R,p,q),
\qquad
\mathsf{ZeroRem}_R(r),
\qquad
\mathsf{ZeroRem}_R(s)
$$
hold, then the normalized representatives are structurally list-same:
$$
\mathsf{ListClassifierSpec}\bigl(\sim_R,\mathsf{trim}_R(p{++}r),\mathsf{trim}_R(q{++}s)\bigr).
$$
\end{lemma}
\begin{proof}
By \autoref{thm:list-classifier-length-eq}, the classified common spines $p$ and $q$ have the same finite length. The proof is by induction on the displayed witness $\mathsf{ListClassifierSpec}(\sim_R,p,q)$ from \autoref{def:list-classifier-specification}.

First record the zero-remainder base fact. An induction on $\mathsf{ZeroRem}_R(t)$, using the trailing-zero removal and empty zero-polynomial clauses in \autoref{def:polynomial-stability-certificate}, identifies $\mathsf{trim}_R(t)$ with $\mathsf{nil}$. Hence two zero-remainder spines trim to endpoints classified by the nil clause of $\mathsf{ListClassifierSpec}$.

In the nil-nil case for the common spine, $p$ and $q$ are both $\mathsf{nil}$. The two original lists are exactly the remainders $r$ and $s$, so the zero-remainder base fact gives the nil-nil classifier witness for their trims.

In the cons-cons case, write
$$
p=\mathsf{cons}(a,p'),
\qquad
q=\mathsf{cons}(b,q').
$$
The classifier constructor supplies $a\sim_R b$ and a tail witness $\mathsf{ListClassifierSpec}(\sim_R,p',q')$. Applying the induction hypothesis to $p',q'$ with the same zero remainders gives
$$
\mathsf{ListClassifierSpec}\bigl(\sim_R,\mathsf{trim}_R(p'{++}r),\mathsf{trim}_R(q'{++}s)\bigr).
$$
By \autoref{thm:list-classifier-case-exactness}, the two trimmed tails have matching nil or cons shape; the mixed shapes are impossible.

If the trimmed tails are cons spines, canonical trimming keeps the displayed heads because a nonempty normalized tail contains a nonzero highest entry. The cons clause of $\mathsf{ListClassifierSpec}$ then combines the head witness $a\sim_R b$ with the classified trimmed tails.

If the trimmed tails are both nil, the canonical cons-trim clause tests only whether the displayed head is scalar-classified as zero. The head witness $a\sim_R b$, together with the symmetry and transitivity fields of $\mathsf{cert}_R$, gives
$$
a\sim_R0_R
\quad\Longleftrightarrow\quad
b\sim_R0_R.
$$
Thus the two trim computations take the same branch. In the dropped-head branch, both normalized representatives are $\mathsf{nil}$ and the nil clause classifies them. In the retained-head branch, both normalized representatives are singleton spines, and the cons clause classifies them using $a\sim_R b$ and the nil-tail classifier.

These cases exhaust the structural classifier witness by \autoref{thm:list-classifier-case-exactness}. Finally, \autoref{def:polynomial-classifier-specification} reads the resulting finite-spine classifier as structural sameness of the two normalized polynomial representatives.
\end{proof}
