\chapter{A Concrete Naming Certificate for $\TuringMachineUp$}
\label{ch:concrete-instances-turingmachine-namecert}

The Turing-machine interface $\TuringMachineUp$ packages a deterministic transition function on a finite alphabet together with a $\mathsf{BHist}$ tape carrier and a finite head-position witness. It depends on $\NameCert_{\NatUp}$ (\autoref{ch:concrete-instances-nat-namecert}), $\NameCert_{\SeqUp}$ (\autoref{ch:concrete-instances-seq-namecert}), and $\NameCert_{\ComputableUp}$ (\autoref{ch:concrete-instances-computable-namecert}).

\section{Carrier definition}
\label{sec:turingmachine-carrier}

A $\TuringMachineUp$ token carries: a finite state alphabet, a finite tape alphabet with a designated blank, a deterministic transition function, an initial-state name, and a halting-state predicate. The carrier accepts a configuration history $h$ when there is a $\SeqUp$ trace of $(\text{state}, \text{tape}, \text{head})$ rows whose zero entry is the initial configuration on a given input, every one-step extension matches the transition function, and halted rows repeat. The classifier is $\hsame$ on the configuration trace; the ledger keeps the deterministic transition table, head movement, and tape readback visible; the source covers finite alphabets, configurations, and traces; the pattern records initial-row, transition-step, halted-repetition, and tape-readback rows.

\begin{theorem}[TuringMachine configuration trace carrier]
\label{thm:turingmachine-configuration-trace-carrier}
A configuration trace accepted by the $\TuringMachineUp$ carrier is a
$\SeqUp$ row of $(\mathsf{state},\mathsf{tape},\mathsf{head})$ histories over
$\mathsf{BHist}$ with a unary time index, an initial configuration row, and the
displayed finite state and tape alphabets. The source rows consumed by the
carrier are exactly the $\NameCert_{\NatUp}$ unary time and head-position rows,
the $\NameCert_{\SeqUp}$ configuration trace row, and the
$\NameCert_{\ComputableUp}$ bounded deterministic-trace row.
\end{theorem}
\begin{proof}
Unpack the carrier prose above. The accepted history is not a host-level run; it
is the displayed $\SeqUp$ trace whose entries are triples of BEDC histories, and
whose index row is supplied by $\NameCert_{\NatUp}$.

The initial row is one entry of the same trace. The finite alphabets and
configuration components are therefore visible source rows, while
$\NameCert_{\ComputableUp}$ supplies the bounded deterministic trace format
that keeps the program code, bound, and endpoint readback in the ledger.
\end{proof}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineConfigurationTraceCarrier\_configuration\_trace\_surface}

\begin{theorem}[TuringMachine deterministic step transport]
\label{thm:turingmachine-deterministic-step-transport}
Let two current configuration rows of a $\TuringMachineUp$ trace be related by
$\hsame$, and let their deterministic transition-table rows be transported by
the same classifier data. Then the next-step configuration rows produced by the
transition table are again related by $\hsame$. The transport uses the
$\Cont$ trace-extension row and the displayed $\NameCert_{\SeqUp}$ classifier
on configuration traces.
\end{theorem}
\begin{proof}
Read the current configuration comparison through the $\hsame$ classifier on the
configuration trace. The deterministic transition table is a visible ledger row,
so transporting it carries the state update, tape-cell write, and head move to
the transported current configuration.

Apply the $\Cont$ trace-extension row to append the transported one-step result
to the $\SeqUp$ trace. Since the transition relation is deterministic, there is
only one next configuration row over the transported current row, and the
$\NameCert_{\SeqUp}$ classifier records it as the same trace step up to
$\hsame$.
\end{proof}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineDeterministicStepTransport\_step\_stability}

\begin{theorem}[TuringMachine halted repetition ledger exactness]
\label{thm:turingmachine-halted-repetition-ledger-exactness}
Once the halting predicate is displayed for a configuration row in a
$\TuringMachineUp$ trace, every later accepted trace-extension ledger row records
only repetitions of that halted configuration. No transition-table branch,
oracle row, or fresh tape update is available after the halted row.
\end{theorem}
\begin{proof}
Use the carrier clause that halted rows repeat. The halting predicate is a
visible ledger entry, so a later trace extension must cite the halted
configuration as its source row rather than reopen the deterministic transition
table.

The $\Cont$ row then extends the trace by the same configuration history. The
classifier for the repeated suffix is the ambient $\hsame$ on configuration
traces, and the exactness ledger records only the halted configuration, its tape,
and its head-position witness.
\end{proof}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineHaltedTrace\_ledger\_exactness}

\begin{theorem}[TuringMachine finite tape readback carrier]
\label{thm:turingmachine-finite-tape-readback-carrier}
Every visible tape readback of a $\TuringMachineUp$ accepted trace is a finite
$\mathsf{BHist}$ row indexed by the $\NatUp$ head-position witness. The readback
surface is carried by the $\NameCert_{\NatUp}$ head row, the
$\NameCert_{\SeqUp}$ configuration trace row, and the visible tape component of
the current configuration; it does not expose an infinite tape object.
\end{theorem}
\begin{proof}
Project a carried configuration row to its tape and head components. The head is
classified by the consumed $\NameCert_{\NatUp}$ row, while the configuration is
one entry of the consumed $\NameCert_{\SeqUp}$ trace.

The tape readback therefore names only the finite BEDC row addressed by that
head-position witness. Transport along $\hsame$ preserves the same finite
readback row, and the trace ledger records the accessed cell without adding an
unbounded external tape carrier.
\end{proof}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineFiniteTapeReadbackCarrier\_finite\_readback\_surface}

\begin{theorem}[TuringMachine obligation surface]
\label{thm:turingmachine-obligation-surface}
The complete $\TuringMachineUp$ obligation surface over $\mathsf{BHist}$ is
formed by the configuration trace carrier, the $\hsame$ classifier on
configuration traces, the deterministic transition row, the halted-repetition
row, the finite tape readback row, and the bounded $\ComputableUp$ simulation
trace rows. These rows consume exactly the displayed $\NatUp$ unary time and
head-position witnesses, the $\SeqUp$ configuration trace, $\Cont$
trace-extension data, and the ledger rows for initial configurations,
transition steps, halted repetitions, and bounded readback.
\end{theorem}
\begin{proof}
Collect the carrier rows from
\autoref{thm:turingmachine-configuration-trace-carrier} and the finite readback
rows from \autoref{thm:turingmachine-finite-tape-readback-carrier}. These
identify the accepted histories as $\mathsf{BHist}$ configuration rows indexed
by the consumed $\NatUp$ and $\SeqUp$ sources.

Next add the deterministic and halted parts. The step transport theorem
supplies the deterministic transition row and its $\Cont/\hsame$ stability,
while the halted-repetition theorem supplies the exact repeated suffix.

Finally include the bounded $\ComputableUp$ trace row. Since the carrier exposes
only the displayed initial row, transition step, halted repetition, finite
readback, and bounded-simulation ledger entries, the listed rows exhaust the
obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineObligationSurface\_bounded\_trace\_ledger}

\begin{theorem}[TuringMachine source-classifier obligation]
\label{thm:turingmachine-source-classifier-obligation}
The $\TuringMachineUp$ source reads exactly the finite state alphabet, finite
tape alphabet with blank row, unary time rows, unary head-position rows,
$\SeqUp$ configuration trace, deterministic transition table, and
$\ComputableUp$ bounded trace. Classifier transport is $\hsame$ on
configuration trace rows, with the deterministic transition table and finite
readback rows transported only through the displayed $\Cont$ trace-extension
surface.
\end{theorem}
\begin{proof}
Project a token to its source rows. The alphabets, transition table, time
indices, head positions, configuration trace, and bounded trace are explicit
coordinates of the accepted package.

The classifier has no separate host-machine equality. It compares configuration
trace rows by $\hsame$, then transports transition and readback rows along the
same displayed $\Cont$ extension data.

Because no other source coordinate is available in the package, every admitted
classifier transport is obtained from those rows and no oracle, universal
machine, or external computation predicate can enter the source.
\end{proof}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineSourceClassifierObligation\_cont\_transport}

\begin{theorem}[TuringMachine ledger exactness obligation]
\label{thm:turingmachine-ledger-exactness-obligation}
The $\TuringMachineUp$ ledger is exhausted by initial-row, transition-step,
halted-repetition, finite tape readback, and bounded-simulation rows. It
contains no oracle transcript, nondeterministic branch row, universal-machine
row, or halting-decision data.
\end{theorem}
\begin{proof}
Read the ledger fields of an accepted $\TuringMachineUp$ token. The initial row
starts the $\SeqUp$ trace, transition-step rows append deterministic successors,
and halted-repetition rows append the fixed halted configuration.

Finite tape readback is the projection of a displayed configuration row through
the head-position witness, and bounded simulation is the consumed
$\ComputableUp$ trace prefix.

These are all ledger constructors named by the carrier. Since the package has
no field for oracles, branch choice, universal-machine coding, or halting
decision, those data are excluded from ledger exactness.
\end{proof}

\section{The certificate}
\label{sec:turingmachine-certificate}

\begin{theorem}[TuringMachine trace source obligation]
\label{thm:turingmachine-trace-source-obligation}
The $\TuringMachineUp$ trace source is a $\SeqUp$ configuration carrier over
$\mathsf{BHist}$ whose rows are finite triples
$(\mathsf{state},\mathsf{tape},\mathsf{head})$. Its public source surface is
the $\NatUp$ unary time row, the $\NatUp$ head-position row, the $\SeqUp$
configuration trace row, the finite state and tape alphabets, and the
$\ComputableUp$ bounded deterministic-trace row.
\end{theorem}
\begin{proof}
Project the accepted machine token to its trace coordinate. The trace coordinate
is already a $\SeqUp$ row, and each entry is a triple of BEDC histories, so the
carrier is a finite $\mathsf{BHist}$ configuration sequence rather than a
host-level execution.

The visible indices are supplied by the consumed $\NatUp$ rows. The finite
alphabets and the bounded deterministic-trace row are ledger coordinates of the
same token, so every source row in the theorem is obtained by projection from
the displayed carrier package.
\end{proof}

\begin{theorem}[TuringMachine deterministic step stability]
\label{thm:turingmachine-deterministic-step-stability}
For a $\TuringMachineUp$ trace, one-step transition rows are stable under the
displayed $\Cont$ and $\hsame$ transport. If current configurations, transition
table rows, and head-position witnesses are transported by the public
classifier, then the next configurations produced by the deterministic step row
are again $\hsame$.
\end{theorem}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineStepRow\_hsame\_transport}
\begin{proof}
Read the current configurations through the $\hsame$ classifier on the
$\SeqUp$ trace. The transition table is a visible ledger row, so its transported
copy determines the same state update, tape write, and head movement over the
transported current configuration.

Apply the $\Cont$ row for trace extension. Determinism gives a single next row
for the transported data, and the $\SeqUp$ classifier records the two extended
traces as $\hsame$ at the next time index.
\end{proof}

\begin{theorem}[TuringMachine halted repeat obligation]
\label{thm:turingmachine-halted-repeat-obligation}
If a $\TuringMachineUp$ configuration row is marked halted, every accepted
later trace row repeats that halted configuration up to $\hsame$. The repeated
suffix exposes only the halted configuration, its tape row, its head-position
witness, and the halted ledger entry.
\end{theorem}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineHaltedTrace\_repeat\_obligation}
\begin{proof}
Use the halted-row clause of the carrier. Once the halted predicate is visible,
the accepted trace-extension field cites the halted configuration as its source
instead of reopening the transition table.

The repeated suffix is then built by the same $\Cont$ extension row. Since each
later entry is classified with the halted configuration by $\hsame$, the ledger
contains no additional branch, oracle query, or tape update beyond the repeated
halted row.
\end{proof}

\begin{theorem}[TuringMachine bounded readback soundness]
\label{thm:turingmachine-bounded-readback-soundness}
Every $\ComputableUp$ bounded readback consumed by $\TuringMachineUp$ is read
from the displayed finite trace prefix. The readback endpoint is the tape value
addressed by the $\NatUp$ head-position witness inside the current
configuration row, and no infinite tape carrier or halting-decision row is
exported.
\end{theorem}
\begin{proof}
Project the bounded readback row from the consumed $\ComputableUp$ surface. Its
bound is a finite trace prefix, and each trace entry is a $\SeqUp$
configuration row with a visible tape component and head-position witness.

The endpoint readback therefore evaluates the displayed tape row at the
displayed finite head witness. Transport by $\hsame$ preserves that bounded
endpoint, while the absence of an infinite tape coordinate prevents the
readback from exporting any stronger host computation claim.
\end{proof}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineBoundedReadbackSoundness\_endpoint\_transport}
\leanchecked{BEDC.Derived.TuringMachineUp.TuringMachineBoundedReadback\_soundness}

\begin{theorem}[TuringMachine NameCert surface obligation]
\label{thm:turingmachine-namecert-surface-obligation}
The public $\NameCert_{\TuringMachineUp}$ surface is obtained by repacking the
configuration trace carrier, deterministic transition classifier, $\Cont$ and
$\hsame$ stability rows, halted-repeat exactness, bounded readback exactness,
and deterministic transition ledger. This surface binds only the listed
$\mathsf{BHist}$, $\SeqUp$, $\NatUp$, $\ComputableUp$, $\Cont$, $\hsame$, and
ledger rows.
\end{theorem}
\begin{proof}
First collect the carrier rows from
\autoref{thm:turingmachine-trace-source-obligation}. These provide the finite
configuration trace, time index, head-position witness, alphabets, and bounded
deterministic-trace source.

Next add the stability and exactness rows. The deterministic-step row is stable
by \autoref{thm:turingmachine-deterministic-step-stability}, halted suffixes
are exact by \autoref{thm:turingmachine-halted-repeat-obligation}, and bounded
readback is exact by \autoref{thm:turingmachine-bounded-readback-soundness}.

Finally repack those rows as the naming certificate ledger. The package has no
field for nondeterminism, oracle queries, parallel execution, a universal
machine theorem, or a halting-decision classifier, so the public surface is
exactly the listed finite-row obligation surface.
\end{proof}

\begin{closurestatus}{\TuringMachineUp}
  \constructivestory{A $\TuringMachineUp$ token names a deterministic finite-state transition table over a finite tape alphabet with a designated blank symbol. A configuration history is built from a $\SeqUp$ trace of (state, tape, head-position) rows whose initial row is the boot configuration on a $\NatUp$-encoded input, whose one-step rows follow the transition function, and whose halted rows repeat the halted configuration. The classifier is $\hsame$ on the configuration trace, transport repacks the trace through the deterministic transition table, and the source binds finite-alphabet, finite-state, finite-trace, and finite-head-displacement rows. The pattern records the initial-row, transition-step, halted-repetition, and finite-tape-readback rows; the ledger keeps the deterministic transition table, head movement, and tape values visible. The five name-certificate obligations follow: the inhabited identity certificate is the boot trace at length zero; classifier stability is reflexive, symmetric, and transitive $\hsame$ on traces; transport repacks configurations through the transition function; ledger exactness identifies the accepted history with the bounded simulation row in the sense of \autoref{ch:concrete-instances-computable-namecert}; the extension boundary fixes the halted-repetition rule. A history $h$ lies in the signature gap of a $\TuringMachineUp$ token $p$ when the source-domain accepts a configuration trace with the right transition table, the signature relation pairs it with the halted output, and token introduction names that output as $p$. The chapter registers this finite-trace machine surface under the name $\TuringMachineUp$; it is a deterministic-transition-table object with no oracle, nondeterminism, parallelism, halting decision, or universal-machine claim.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The obligation scope is the surface in \autoref{thm:turingmachine-obligation-surface}, \autoref{thm:turingmachine-source-classifier-obligation}, and \autoref{thm:turingmachine-ledger-exactness-obligation}, grounded by \autoref{thm:turingmachine-configuration-trace-carrier}, \autoref{thm:turingmachine-deterministic-step-transport}, \autoref{thm:turingmachine-halted-repetition-ledger-exactness}, and \autoref{thm:turingmachine-finite-tape-readback-carrier}.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{The chapter does not close halting decidability, universal-machine theorems, oracle Turing machines, parallel/nondeterministic machines, or a standard-model bridge to classical computability.}
  \upgradepath{Public closure requires a checked public TuringMachineUp certificate theorem tying this finite trace surface to a Lean target.}
\end{closurestatus}
