\chapter{AspectChain NameCert Construction}
\label{ch:concrete-instances-aspectchain-namecert}
\origin{ai-composite}

The $\AspectChainUp$ interface packages the mind-matter double-aspect reading of \autoref{prin:hard-problems-mind-matter-two-aspects} as one finite certificate. The records-side rows expose the public material record surface of the chain, while the inscription-event-side rows expose the accepted event surface by which the same chain point is written, checked, and handed to local consumers. The inscription-event coordinate is the concrete sibling surface of \autoref{ch:concrete-instances-inscriptionevent-namecert}, while the locality rows are consumer boundaries only and do not collapse $\AspectChainUp$ into a global observer frame. The packet does not identify private mental states with host physical objects, and it does not add a metaphysical identity relation outside the displayed $\BHist$ data.

\begin{definition}[AspectChain carrier]
\label{def:aspect-chain-carrier}
An $\AspectChainUp$ carrier is a finite $\BHist$ packet
$$
A=(R,I,G,L,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the records-side $\BHist$ row read as the material record surface of the chain point;
\item $I$ is the inscription-event-side $\InscriptionEventUp$ row for the same accepted chain point;
\item $G$ is the public $\mathsf{GAP}$ provenance row recording the open commitment carried by the double-aspect reading;
\item $L$ is the local $\LocalityCellUp$ or $\ObserverLocalityCellUp$ row through which nearby observers may read the public record without receiving an all-observer frame;
\item $O$ is the optional $\OtherMindsCommitmentUp$ row by which a consumer may treat another inscription event as another conscious observational system;
\item $H$ stores componentwise $\hsame$ transports for the records row, inscription-event row, $\mathsf{GAP}$ provenance, locality row, other-minds row, package row, and local name;
\item $C$ stores the displayed $\Cont$ routes by which a consumer reads $R,I,G,L,O$ without leaving the finite packet;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\mathsf{GAP}$ provenance, $\InscriptionEventUp$, $\LocalityCellUp$, $\ObserverLocalityCellUp$, $\OtherMindsCommitmentUp$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\AspectChainUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows and their stored transports. It has no coordinate for a host mental substance, a host physical substance, a private phenomenal object, or an external identity predicate between mind and matter.
\end{definition}
\leanchecked{BEDC.Derived.AspectChainUp.AspectChainTasteGate\_single\_carrier\_alignment}

\begin{theorem}[AspectChain NameCert obligations]
\label{thm:aspect-chain-namecert-obligations}
The local $\NameCert_{\AspectChainUp}$ surface for the carrier of \autoref{def:aspect-chain-carrier} consists of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $A=(R,I,G,L,O,H,C,P,N)$;
\item records-side exactness: the material reading is exactly the $\BHist$ row $R$ together with its displayed transports and consumer routes;
\item inscription-event exactness: the phenomenological-first-person reading is exactly the $\InscriptionEventUp$ row $I$ together with its public checker, consumer, and $\mathsf{GAP}$ ledger surface;
\item locality and other-minds accountability: every cross-observer read factors through $L$ and, when present, through $O$;
\item non-collapse: the packet records two readings of one accepted chain point, but it exports neither a host mental state, nor a host physical object, nor a metaphysical identity relation between them.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.AspectChainUp.AspectChainNameCertObligations}
\begin{proof}
Carrier admission is projection from \autoref{def:aspect-chain-carrier}. The rows $R,I,G,L,O,H,C,P,N$ are all displayed coordinates of one finite $\BHist$ packet.

The records-side obligation reads only $R$ and the attached rows in $H$ and $C$. Thus the material reading is a public record surface rather than an additional host object.

The inscription-event obligation reads $I$ by applying the public carrier and downstream-handoff surface of $\InscriptionEventUp$. Its checker, consumer, and $\mathsf{GAP}$ ledger data remain rows inside the same packet.

For locality and other-minds accountability, a consumer must route through $L$ before treating the record as a shared local cell, and through $O$ before treating another inscription event as another conscious observational system. The remaining rows $H,C,P,N$ only transport, route, record provenance, and name this finite packet.
\end{proof}

\begin{theorem}[AspectChain consumer boundary]
\label{thm:aspect-chain-consumer-boundary}
Every consumer of an accepted $\AspectChainUp$ carrier may read only the records-side $\BHist$ row, the $\InscriptionEventUp$ row, the $\mathsf{GAP}$ provenance row, the locality-cell row, the other-minds commitment row, the componentwise $\hsame$ transports, the displayed $\Cont$ routes, the $\Pkg$ provenance, and the local $\NameCert$ row.

In particular, a consumer may use the packet to compare the records-side and inscription-event-side readings of one chain point, but it receives no hidden mental state, no host physical substrate object, no all-observer locality frame, and no unrecorded cross-aspect bridge.
\end{theorem}
\begin{proof}
Start with a consumer route into $A$. By the carrier definition, the only visible rows are $R,I,G,L,O,H,C,P,N$.

The records read is routed through $R$. The inscription-event read is routed through $I$, and \autoref{thm:inscription-event-downstream-handoff} bounds that read by the public source, name, route, check, consumer, ledger, transport, continuation, package, and naming rows of the inscription event.

The locality and other-minds reads are bounded by their displayed rows. The locality row prevents the consumer from importing a global observer frame, while the other-minds row records a commitment surface rather than direct access to another private state.

Consequently the consumer boundary is exactly the finite packet surface. The comparison of the two aspects is an internal two-reading relation over $A$, not an exported host-level identity or bridge object.
\end{proof}

\begin{theorem}[AspectChain non-collapse]
\label{thm:aspect-chain-non-collapse}
An accepted $\AspectChainUp$ carrier realizes the mind-matter double-aspect reading as one finite $\BHist$ packet with records-side and inscription-event-side rows. This realization does not collapse the records-side row into the inscription-event row, does not collapse the inscription-event row into the records-side row, and does not export host mental-state identity, host physical-object identity, private phenomenal access, or ambient metaphysical identity.
\end{theorem}
\leanchecked{BEDC.Derived.AspectChainUp.AspectChainCarrier\_non\_collapse}
\begin{proof}
Project the carrier $A=(R,I,G,L,O,H,C,P,N)$. The records-side coordinate $R$ and the inscription-event coordinate $I$ are distinct displayed rows of the same finite packet.

\autoref{thm:aspect-chain-namecert-obligations} fixes the two exactness obligations separately. The records-side reading is exhausted by $R$ and its routes, while the inscription-event reading is exhausted by $I$ and its public inscription-event surface.

\autoref{thm:aspect-chain-consumer-boundary} then bounds every public consumer by the same finite rows. Since the packet contains no coordinate for private phenomenal access, host physical-object identity, or an external identity predicate, no consumer can collapse either aspect into the other or export a metaphysical identity claim.
\end{proof}

\closureat{AspectChainUp}{seedStr}
\closureat{AspectChainUp}{obligationStr}[BEDC.Derived.AspectChainUp.AspectChainTasteGate\_single\_carrier\_alignment]
\closureat{AspectChainUp}{scopedStr}[BEDC.Derived.AspectChainUp.taste\_gate]

\begin{closurestatus}{\AspectChainUp}
  \constructivestory{An $\AspectChainUp$ packet is generated from one records-side $\BHist$ row, one $\InscriptionEventUp$ row, public GAP provenance, a locality-cell row, an optional other-minds commitment row, componentwise hsame transports, displayed Cont routes, Pkg provenance, and a local NameCert row.}
  \leanchecked{BEDC.Derived.AspectChainUp.taste\_gate}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:aspect-chain-carrier}, \autoref{thm:aspect-chain-namecert-obligations}, \autoref{thm:aspect-chain-consumer-boundary}, and \autoref{thm:aspect-chain-non-collapse} bind the scoped records-side row, inscription-event row, GAP provenance, locality and other-minds rows, hsame transport, Cont routes, Pkg provenance, and local NameCert rows already listed by the packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai-composite}
  \notclaimed{This chapter does not close a Lean implementation, bridge checking, private phenomenal access, host mental-state identity, host physical-object identity, global observer frame, or ambient metaphysical identity.}
  \upgradepath{Scoped closure requires a checked records-side, inscription-event-side, locality, other-minds, and non-collapse surface over the already listed packet rows.}
\end{closurestatus}
