\chapter{A Concrete Naming Certificate for $\KolmogorovUp$}
\label{ch:concrete-instances-kolmogorov-namecert}

The Kolmogorov-complexity interface $\KolmogorovUp$ packages a description-length predicate over a deterministic prefix-free decoder, parametrised by a displayed unary length budget. It depends on $\NameCert_{\NatUp}$ (\autoref{ch:concrete-instances-nat-namecert}), $\NameCert_{\TuringMachineUp}$ (\autoref{ch:concrete-instances-turingmachine-namecert}), and $\NameCert_{\ComputableUp}$ (\autoref{ch:concrete-instances-computable-namecert}).

\section{Carrier definition}
\label{sec:kolmogorov-carrier}

A $\KolmogorovUp$ token carries a deterministic prefix-free decoder $\TuringMachineUp$, a unary length budget $\ell$, and a target output history $h$. The carrier accepts a witness when there is a prefix-free description $d$ of unary length at most $\ell$ that, decoded by the decoder, halts and reads back $h$. The classifier is $\hsame$ on output histories at fixed budget $\ell$; the ledger keeps the description $d$, the unary budget, the decoded trace, and the readback row visible; the pattern records prefix-freeness, budget admissibility, decoded-readback exactness, and budget monotonicity.

\begin{theorem}[Kolmogorov prefix-free carrier obligation]
\label{thm:kolmogorov-prefix-free-carrier-obligation}
The $\KolmogorovUp$ carrier obligation is the finite $\mathsf{BHist}$ surface
whose accepted row consists of a prefix-free description history, a displayed
$\mathsf{UnaryHistory}$ length row, a fixed-budget $\hsame$ classifier on
decoded output histories, and the dependency rows supplied by
$\NameCert_{\NatUp}$, $\NameCert_{\TuringMachineUp}$, and
$\NameCert_{\ComputableUp}$. At a fixed unary budget $\ell$, the carrier accepts
exactly those description rows whose decoder trace is a displayed halted
$\TuringMachineUp$ trace consumed by the bounded $\ComputableUp$ readback.

This obligation records prefix-freeness and budget admissibility only as
visible finite rows. It does not assert universal-decoder optimality,
randomness extraction, the invariance theorem, or any standard
information-theoretic bridge.
\end{theorem}
\leanchecked{BEDC.Derived.KolmogorovUp.KolmogorovPrefixFreeCarrier\_obligation\_surface}
\leanchecked{BEDC.Derived.KolmogorovUp.KolmogorovPrefixFreeCarrierObligation\_finite\_surface}
\begin{proof}
Inspect the displayed witness row. Its $\mathsf{BHist}$ component supplies the
description history, its $\mathsf{UnaryHistory}$ component supplies the length
budget, and the fixed-budget $\hsame$ row supplies the classifier on decoded
output histories.

The $\NameCert_{\NatUp}$ dependency reads the unary length and budget rows, the
$\NameCert_{\TuringMachineUp}$ dependency reads the deterministic decoder
trace, and the $\NameCert_{\ComputableUp}$ dependency reads the bounded halted
output. Since each component is carried in the same finite ledger, the carrier
contains exactly the displayed prefix-free and budget rows and no external
optimality or information-theoretic structure.
\end{proof}

\begin{theorem}[Kolmogorov budget monotonicity obligation]
\label{thm:kolmogorov-budget-monotonicity-obligation}
Let a $\KolmogorovUp$ witness over $\mathsf{BHist}$ accept a description under
a unary budget $\ell$ with fixed-budget $\hsame$ decoded output classifier. If
$\ell'$ is obtained from $\ell$ by a displayed $\mathsf{UnaryHistory}$ budget
extension, then the same description, the same $\NameCert_{\NatUp}$ length
row, the same $\NameCert_{\TuringMachineUp}$ halted trace, and the same
$\NameCert_{\ComputableUp}$ bounded readback row form an accepted
$\KolmogorovUp$ witness at budget $\ell'$.

The transported row preserves the decoded readback and enlarges only the
visible unary admissibility bound. It does not introduce universal-decoder
optimality, randomness extraction, or a standard information-theoretic bridge.
\end{theorem}
\leanchecked{BEDC.Derived.KolmogorovUp.KolmogorovBudgetMonotonicity\_budget\_transport}
\begin{proof}
Start with the accepted witness at budget $\ell$. The description history,
decoder trace, halted readback, and output classifier are already visible in
the $\mathsf{BHist}$ ledger.

Apply constructor inspection to the displayed $\mathsf{UnaryHistory}$ extension
from $\ell$ to $\ell'$. The length-admissibility row for the old budget embeds
into the larger unary budget, while the fixed-budget $\hsame$ classifier on the
decoded output is reused unchanged at the new displayed budget.

The $\NameCert_{\NatUp}$ row witnesses the unary bound, and the
$\NameCert_{\TuringMachineUp}$ and $\NameCert_{\ComputableUp}$ rows are not
rerun. Therefore the accepted readback is preserved exactly, with only the
budget-admissibility coordinate enlarged.
\end{proof}
\leanchecked{BEDC.Derived.KolmogorovUp.KolmogorovBudgetMonotonicity\_budget\_extension}

\begin{theorem}[Kolmogorov decoded readback exactness]
\label{thm:kolmogorov-decoded-readback-exactness}
For every accepted $\KolmogorovUp$ witness over $\mathsf{BHist}$, the ledger
identifies the accepted output row with the displayed
$\NameCert_{\TuringMachineUp}$ halted decoder trace as read through the bounded
$\NameCert_{\ComputableUp}$ verdict, while the unary description and budget are
the rows certified by $\NameCert_{\NatUp}$ and $\mathsf{UnaryHistory}$. The
$\hsame$ classifier therefore compares only the decoded output histories at
the fixed displayed budget.

The exactness statement closes only the finite decoded-readback ledger. It
does not close universal-decoder optimality, randomness extraction, the
invariance theorem, or any standard information-theoretic bridge.
\end{theorem}
\leanchecked{BEDC.Derived.KolmogorovUp.KolmogorovDecodedReadback\_exactness}
\begin{proof}
Read the accepted witness as a finite ledger. The description and budget rows
are the $\NameCert_{\NatUp}$ and $\mathsf{UnaryHistory}$ coordinates, and the
decoder run is the displayed deterministic $\NameCert_{\TuringMachineUp}$
trace.

The bounded $\NameCert_{\ComputableUp}$ verdict consumes that halted trace and
exports a single readback row. Ledger exactness then identifies the accepted
$\KolmogorovUp$ output with that readback row, so the fixed-budget $\hsame$
classifier has no additional coordinate to compare.

The proof never replaces the displayed decoder by an optimal universal
decoder, never samples a randomness row, and never invokes an
information-theoretic bridge; all equalities are inside the finite decoded
trace ledger.
\end{proof}

\begin{theorem}[Kolmogorov public NameCert export]
\label{thm:kolmogorov-public-namecert-export}
The prefix-free carrier obligation, budget monotonicity obligation, and
decoded readback exactness assemble the public
$\NameCert_{\KolmogorovUp}$ export over $\mathsf{BHist}$,
$\mathsf{UnaryHistory}$, $\NatUp$, $\TuringMachineUp$, $\ComputableUp$, the
fixed-budget $\hsame$ classification, and the visible prefix-free decoder
ledger.

The exported public surface consists exactly of the carrier row for accepted
prefix-free descriptions, the fixed-budget output classifier, the stability
rows for transporting the same decoded output across displayed unary budget
extensions, the budget transport row, and the decoded-readback exactness row.
It does not assert universal-decoder optimality, randomness extraction, an
invariance theorem, resource-bounded complexity, or an information-theoretic
standard bridge.
\end{theorem}
\begin{proof}
First project
\autoref{thm:kolmogorov-prefix-free-carrier-obligation}. This supplies the
finite carrier: description histories in $\mathsf{BHist}$, displayed
$\mathsf{UnaryHistory}$ budgets, $\NameCert_{\NatUp}$ length rows,
$\NameCert_{\TuringMachineUp}$ halted decoder traces, and
$\NameCert_{\ComputableUp}$ bounded readback rows.

Next use \autoref{thm:kolmogorov-budget-monotonicity-obligation}. The budget
transport keeps the description, decoder trace, readback row, and
fixed-budget $\hsame$ classifier stable while only enlarging the visible unary
admissibility bound.

Finally apply \autoref{thm:kolmogorov-decoded-readback-exactness}. The
accepted output row is the decoded readback from the displayed halted trace,
so the public certificate repacks the carrier, classifier, stability, budget
transport, and exactness rows listed in the statement. No optimal universal
decoder, randomness row, or standard information-theoretic bridge is added.
\end{proof}

\closureat{KolmogorovUp}{scopedStr}[BEDC.Derived.KolmogorovUp.KolmogorovPrefixFreeCarrier\_obligation\_surface]
\closureat{KolmogorovUp}{publicStr}[BEDC.Derived.KolmogorovUp.KolmogorovPrefixFreeCarrier\_obligation\_surface]

\begin{closurestatus}{\KolmogorovUp}
  \constructivestory{A $\KolmogorovUp$ token names a deterministic prefix-free decoder $\TuringMachineUp$ together with a displayed unary length budget $\ell$ and a target output history $h$. The carrier accepts a witness when there is a prefix-free description history $d$ of unary length at most $\ell$ such that running the decoder on $d$, in the sense of $\NameCert_{\ComputableUp}$, halts and reads back $h$. The classifier is $\hsame$ on output histories at fixed unary budget; the source covers unary description lengths, budget values, decoder configurations, prefix-freeness rows, and decoded readback histories; the pattern records prefix-freeness admissibility, budget admissibility, decoded-readback exactness, budget monotonicity, and decoder-determinism rows; the ledger keeps the description $d$, the budget $\ell$, the decoded trace, and the readback row visible. The five name-certificate obligations are supplied by the bounded-simulation certificate plus the prefix-free description structure: the inhabited identity certificate is the empty-description trivial decoder; classifier stability is reflexive, symmetric, and transitive $\hsame$ at fixed budget; transport repacks descriptions through prefix-extension; ledger exactness identifies the accepted row with the decoded readback at the displayed budget; the extension boundary fixes budget monotonicity. A history $h$ lies in the signature gap of a $\KolmogorovUp$ token $p$ when the source-domain accepts the prefix-free decoded readback, the signature relation pairs it with the decoded output, and token introduction names that output as $p$. The chapter registers this prefix-free description-budget surface under the name $\KolmogorovUp$; it is a description-length object with no universal-decoder optimality, no resource-bounded variant ($K^{t}$, $K^{s}$), no randomness extraction, and no information-theoretic standard bridge.}
  \theoryclosure{\publicClosure}
  \scopeclosed{The public surface binds $\mathsf{BHist}$, $\mathsf{UnaryHistory}$, $\NatUp$, $\TuringMachineUp$, $\ComputableUp$, prefix-free description rows, bounded decoder traces, budget monotonicity, fixed-budget $\hsame$ output classification, and the exported $\NameCert_{\KolmogorovUp}$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{The chapter does not close universal-decoder optimality, resource-bounded Kolmogorov complexity ($K^{t}$, $K^{s}$), randomness extraction, the invariance theorem, or a standard information-theoretic bridge.}
  \upgradepath{Bridged closure requires a standard information-theoretic bridge theorem for the exported prefix-free decoder, budget, readback, classifier, and ledger surface.}
\end{closurestatus}
