\chapter{A Concrete Naming Certificate for $\CauchyNetUp$}
\label{ch:concrete-instances-cauchynet-namecert}
\origin{human}

The $\CauchyNetUp$ surface records directed convergence data as finite observation packets. Kelley-style Cauchy nets and uniform-space convergence provide the mathematical precedent, but the BEDC packet below is not a quotient net, a selected limit, or an ambient completeness theorem. It is a finite $\BHist$ boundary that exposes the directed windows actually inspected by downstream $\RegSeqRatUp$ and $\RealUp$ consumers.

The directed-window packet is a downstream consumer of \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}: those sibling chapters supply the schedule, regular rational readback, dyadic tolerance ledger, and real-name handoff rows used in the carrier below.

\begin{definition}[CauchyNet carrier]
\label{def:cauchy-net-carrier}
A $\CauchyNetUp$ carrier is a finite directed-window $\BHist$ packet
$$
K=(D,S,R,W,T,L,H,C,P,N)
$$
over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ with the following displayed rows:
\begin{enumerate}
\item $D$ is the finite directed index-window ledger, naming the inspected vertices and the common upper-window witnesses used by the packet;
\item $S$ is the $\StreamNameUp$ schedule that turns each requested directed window into displayed observation names;
\item $R$ is the $\RegSeqRatUp$ row read from the scheduled rational observations on those windows;
\item $W$ is the $\DyadicRatCoreUp$ observation row for the dyadic tolerances and rational comparisons used inside the finite windows;
\item $T$ is the eventual common-window classifier row, asserting that each displayed tolerance request is witnessed by one finite directed window in $D$;
\item $L$ is the $\RealUp$ handoff row through which downstream real consumers read the regular rational data;
\item $H$ stores componentwise $\hsame$ transports for $D,S,R,W,T,L$ and the local naming rows;
\item $C$ stores the finite $\Cont$ routes that expose directed windows, observations, common-window witnesses, classifier reads, and real handoffs;
\item $P$ is the $\Pkg$ provenance over the listed BEDC dependencies;
\item $N$ is the local $\NameCert_{\CauchyNetUp}$ row.
\end{enumerate}
The carrier exports only this finite directed-window packet. It contains no quotient of nets, no selected limit point, no ambient uniform-space completeness theorem, and no choice operator selecting cofinal windows.
\end{definition}
\leanchecked{BEDC.Derived.CauchyNetUp.CauchyNetCarrier\_transport\_semanticNameCert}
\leanchecked{BEDC.Derived.CauchyNetUp.CauchyNetCarrier\_commonWindow\_semanticNameCert}

\begin{theorem}[CauchyNet NameCert obligation surface]
\label{thm:cauchy-net-namecert-obligation-surface}
The local $\NameCert_{\CauchyNetUp}$ surface for \autoref{def:cauchy-net-carrier} consists of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed directed-window packet $K$;
\item eventual common-window classification through $T$, stating that each exposed tolerance request is routed to a common upper window recorded in $D$;
\item directed-window transport along $H$ and $C$, preserving the scheduled $\StreamNameUp$ observations, $\DyadicRatCoreUp$ comparisons, and $\RegSeqRatUp$ handoff rows;
\item ledger non-escape, stating that a consumer read without a displayed common-window witness is recorded as outside the packet rather than exported as convergence data;
\item $\RealUp$ handoff through $L$, so real-facing consumers see only the regular rational data certified by the same finite directed-window rows.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.CauchyNetUp.CauchyNetNameCert\_obligation\_surface}
\leanvariant{BEDC.Derived.CauchyNetUp.CauchyNetCarrier\_namecert\_obligation\_surface}
\begin{proof}
Carrier admission is projection from the finite tuple in \autoref{def:cauchy-net-carrier}. The directed index-window ledger, stream schedule, dyadic observations, regular rational handoff, classifier row, real handoff, transports, routes, package provenance, and local naming row are all visible coordinates of one $\BHist$ packet.

The eventual common-window classifier reads $T$ only after the finite directed ledger $D$ has supplied a displayed upper-window witness. The schedule $S$ and observation row $W$ then provide the rational data consumed by $R$.

Directed-window transport is componentwise through $H$ and replayed through $C$. These rows preserve the same windows, observations, classifier reads, and handoff rows; they do not add a cofinal choice function or a quotient relation on nets.

If a consumer asks for convergence data without a displayed common-window witness, no coordinate of $K$ can supply it. The package provenance records the request as outside the finite packet boundary. The only real-facing route is therefore the handoff $L$ through the same $\RegSeqRatUp$ row, which gives the stated $\RealUp$ boundary.
\end{proof}

\closureat{CauchyNetUp}{seedStr}
\closureat{CauchyNetUp}{publicStr}
\closureat{CauchyNetUp}{bridgedStr}

\begin{closurestatus}{\CauchyNetUp}
  \constructivestory{A $\CauchyNetUp$ packet is generated from a finite directed index-window ledger, a $\StreamNameUp$ schedule, $\DyadicRatCoreUp$ observation rows, a $\RegSeqRatUp$ handoff, an eventual common-window classifier, a $\RealUp$ handoff, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{\autoref{thm:cauchy-net-directed-window-localization} is the bridge-facing directed-window public export over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the quotient-free packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient nets, selected limits, ambient completeness, cofinal choice, or a uniform-space standard bridge.}
  \upgradepath{Bridged closure requires a standard bridge for the same quotient-free directed-window packet.}
\end{closurestatus}

\begin{definition}[CauchyNet witness-complete finite subwindow]
\label{def:cauchy-net-witness-complete-finite-subwindow}
Let
$$
K=(D,S,R,W,T,L,H,C,P,N)
$$
be an accepted $\CauchyNetUp$ carrier, and let $\Omega$ be a finite directed subwindow of the displayed index-window ledger $D$. The subwindow $\Omega$ is witness-complete for a displayed finite tolerance family $E$ when the retained rows
$$
D_{\Omega},S_{\Omega},R_{\Omega},W_{\Omega},T_{\Omega},L_{\Omega},H_{\Omega},C_{\Omega},P_{\Omega},N_{\Omega}
$$
satisfy the following conditions:
\begin{enumerate}
\item $D_{\Omega}$ is the finite directed subledger of $D$ on $\Omega$, and for every tolerance request in $E$ the common upper-window witness named by the original classifier row $T$ lies in $D_{\Omega}$;
\item $S_{\Omega}$ contains exactly the scheduled $\StreamNameUp$ observation names from $S$ whose directed addresses are in $D_{\Omega}$ and are used by those retained common-window witnesses;
\item $W_{\Omega}$ contains exactly the $\DyadicRatCoreUp$ observation and comparison rows from $W$ read by the retained scheduled observations;
\item $T_{\Omega}$ is the common-window classifier row restricted to the requests in $E$, with each classifier entry using its displayed witness from $D_{\Omega}$;
\item $R_{\Omega}$ is the $\RegSeqRatUp$ row obtained by restricting the original row $R$ to the retained schedule, observation, comparison, and classifier entries;
\item $L_{\Omega}$ is the $\RealUp$ handoff row whose source is the retained row $R_{\Omega}$;
\item $H_{\Omega}$ and $C_{\Omega}$ are the componentwise restrictions of the displayed $\hsame$ transports and $\Cont$ routes whose endpoints are among the retained rows;
\item $P_{\Omega}$ and $N_{\Omega}$ are the provenance and local $\NameCert_{\CauchyNetUp}$ rows restricted to the same retained coordinates.
\end{enumerate}
\end{definition}
\leandef{BEDC.Derived.CauchyNetUp.CauchyNetWitnessCompleteSubwindow}

\begin{theorem}[CauchyNet finite subwindow restriction]
\label{thm:cauchy-net-finite-subwindow-restriction}
Let
$$
K=(D,S,R,W,T,L,H,C,P,N)
$$
be an accepted $\CauchyNetUp$ carrier in the sense of \autoref{def:cauchy-net-carrier}. If $\Omega$ is witness-complete for a displayed finite tolerance family $E$ in the sense of \autoref{def:cauchy-net-witness-complete-finite-subwindow}, then
$$
K_{\Omega}=(D_{\Omega},S_{\Omega},R_{\Omega},W_{\Omega},T_{\Omega},L_{\Omega},H_{\Omega},C_{\Omega},P_{\Omega},N_{\Omega})
$$
is an accepted $\CauchyNetUp$ carrier. Moreover, every $\RealUp$ read exported by $L_{\Omega}$ factors through the retained $\RegSeqRatUp$ row $R_{\Omega}$, and $R_{\Omega}$ is the restriction of the same $\RegSeqRatUp$ row $R$ used by the original packet.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyNetUp.CauchyNetWitnessCompleteSubwindow\_carrier\_restriction}
\begin{proof}
Unfold the carrier of \autoref{def:cauchy-net-carrier}. A $\CauchyNetUp$ carrier has exactly the displayed rows
$$
D,S,R,W,T,L,H,C,P,N.
$$
The witness-complete subwindow supplies one retained row for each of these coordinates. Thus $K_{\Omega}$ has the required directed index-window ledger, schedule, regular rational row, dyadic observation row, common-window classifier, real handoff, componentwise transports, continuation routes, provenance, and local naming row.

The common-window obligation remains internal to the retained packet. For every tolerance request in $E$, witness-completeness keeps the common upper-window witness selected by $T$ inside $D_{\Omega}$. It also keeps the scheduled observation names in $S_{\Omega}$ and the dyadic comparison rows in $W_{\Omega}$ that are read at that witness. Hence the restricted classifier row $T_{\Omega}$ does not appeal to any vertex, observation, or comparison outside the finite subwindow.

The regular rational row is not recomputed from an external net. By definition of witness-completeness, $R_{\Omega}$ is the restriction of the original $\RegSeqRatUp$ row $R$ to the retained schedule, observation, comparison, and classifier entries. Therefore each retained regular rational read is attached to the same finite directed-window evidence that justified it in $K$.

The transport and continuation rows also remain closed under restriction. The rows $H_{\Omega}$ and $C_{\Omega}$ retain only componentwise $\hsame$ transports and $\Cont$ routes whose endpoints are among $D_{\Omega},S_{\Omega},R_{\Omega},W_{\Omega},T_{\Omega}$, and $L_{\Omega}$. The package and local naming rows $P_{\Omega}$ and $N_{\Omega}$ name precisely those retained coordinates, so no hidden cofinal choice function, quotient of nets, selected limit point, or ambient completeness theorem is introduced.

Apply the obligation surface of \autoref{thm:cauchy-net-namecert-obligation-surface}. Carrier admission is the displayed restricted tuple. Eventual common-window classification is supplied by $T_{\Omega}$ because all requested witnesses remain in $D_{\Omega}$. Directed-window transport is supplied by $H_{\Omega}$ and $C_{\Omega}$. Ledger non-escape holds because a request outside $E$ or outside the retained witness ledger has no coordinate in $K_{\Omega}$ from which convergence data can be exported. Finally, the only real-facing row is $L_{\Omega}$, and its source is exactly $R_{\Omega}$. Thus every $\RealUp$ handoff factors through the same restricted $\RegSeqRatUp$ row, with $R_{\Omega}$ inherited from $R$.
\end{proof}

\begin{theorem}[CauchyNet directed-window localization]\label{thm:cauchy-net-directed-window-localization}
Let
$$
K=(D,S,R,W,T,L,H,C,P,N)
$$
be an accepted $\CauchyNetUp$ carrier, and let $\Omega$ be witness-complete for a displayed finite tolerance family $E$ in the sense of \autoref{def:cauchy-net-witness-complete-finite-subwindow}. Then every $\RealUp$ handoff exported by the restricted row $L_{\Omega}$ is determined by the retained directed-window rows
$$
D_{\Omega},S_{\Omega},R_{\Omega},W_{\Omega},T_{\Omega},H_{\Omega},C_{\Omega},P_{\Omega},N_{\Omega}.
$$
No omitted directed vertex, cofinal choice function, quotient net, selected limit point, or ambient completeness row can change that handoff.
\end{theorem}
\begin{proof}
Unfold the witness-complete subwindow definition. The retained ledger $D_{\Omega}$ contains every common upper-window witness used by the displayed tolerance family $E$, while $S_{\Omega}$ and $W_{\Omega}$ contain exactly the scheduled observation names and dyadic comparison rows read at those witnesses. The classifier row $T_{\Omega}$ therefore has no address outside the retained directed window from which to read convergence evidence.

Apply \autoref{thm:cauchy-net-finite-subwindow-restriction}. The restricted tuple
$$
K_{\Omega}=(D_{\Omega},S_{\Omega},R_{\Omega},W_{\Omega},T_{\Omega},L_{\Omega},H_{\Omega},C_{\Omega},P_{\Omega},N_{\Omega})
$$
is itself an accepted $\CauchyNetUp$ carrier, and every real-facing read exported by $L_{\Omega}$ factors through the retained $\RegSeqRatUp$ row $R_{\Omega}$.

Apply the obligation surface of \autoref{thm:cauchy-net-namecert-obligation-surface} to the accepted carrier $K_{\Omega}$. Carrier admission is the displayed restricted tuple; eventual common-window classification is $T_{\Omega}$; directed-window transport is supplied by $H_{\Omega}$ and $C_{\Omega}$; ledger non-escape is enforced by the absence of any coordinate outside the retained rows; and the real-facing boundary is precisely the handoff through $L_{\Omega}$ from $R_{\Omega}$.

It remains only to exclude external data. The subwindow definition gives no coordinate for an omitted directed vertex, a cofinal selector, a quotient of nets, a selected limit point, or an ambient completeness theorem. Since the only exported real-facing route is the projection through $R_{\Omega}$ and $L_{\Omega}$ inside $K_{\Omega}$, changing any such omitted datum cannot affect the $\RealUp$ handoff.
\end{proof}
\leanchecked{BEDC.Derived.CauchyNetUp.CauchyNetDirectedWindow\_localization}
