\chapter{A Concrete Naming Certificate for $\AbelRuffiniUp$}
\label{ch:concrete-instances-abelruffini-namecert}

The Abel-Ruffini interface $\AbelRuffiniUp$ packages a non-solvability-by-radicals certificate for a degree-five polynomial over a $\NumFieldUp$ base. It depends on $\NameCert_{\PolynomialUp}$ (\autoref{ch:concrete-instances-polynomial-namecert}), $\NameCert_{\GaloisGroupUp}$ (\autoref{ch:concrete-instances-galoisgroup-namecert}), $\NameCert_{\SymGroupUp}$ (\autoref{ch:concrete-instances-symgroup-namecert}), and $\NameCert_{\NumFieldUp}$ (\autoref{ch:concrete-instances-numfield-namecert}).

\section{Carrier definition}
\label{sec:abelruffini-carrier}

An $\AbelRuffiniUp$ token carries: a separable monic polynomial $P$ of degree five over a $\NumFieldUp$ base $K$ together with three irreducibility, non-trivial-rational-root, and Galois-group-isomorphic-to-$S_5$ rows. The carrier accepts a non-solvability witness when $\Gal(P/K)$ is isomorphic to $S_5$ and the derived series of $S_5$ does not reach the trivial subgroup. The classifier is $\hsame$ on the Galois group rows; the ledger keeps the irreducibility witness, the $S_5$ identification, and the derived-series ledger visible.

\begin{theorem}[AbelRuffini polynomial Galois obligation]
\label{thm:abelruffini-polynomial-galois-obligation}
The $\AbelRuffiniUp$ source rows are the $\PolynomialUp$, $\NumFieldUp$,
$\GaloisGroupUp$, and $\SymGroupUp$ $\mathsf{BHist}$ packages for a displayed
degree-five polynomial, its base field row, its splitting-field row, and its
$S_5$ identification. The carrier reads the polynomial coefficient history,
separability and irreducibility rows, the non-trivial-rational-root row, the
Galois group package over the splitting field, and the symmetric-group
identification row.
\end{theorem}
\begin{proof}
Project the accepted token to its polynomial and base-field coordinates. The
coefficient history is supplied by $\PolynomialUp$, while the base and splitting
field data are supplied by $\NumFieldUp$ rows.

Next project the group coordinates. The Galois action row is a
$\GaloisGroupUp$ package, and the displayed comparison with $S_5$ is the
consumed $\SymGroupUp$ identification.

The carrier has no additional source coordinate for a host field extension or an
external classification theorem, so these four package families are exactly the
polynomial Galois source surface.
\end{proof}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniPolynomialGaloisObligation\_source\_surface}

\begin{theorem}[AbelRuffini derived-series ledger obligation]
\label{thm:abelruffini-derived-series-ledger-obligation}
The $\AbelRuffiniUp$ derived-series ledger is a finite $\mathsf{BHist}$ ledger.
Each step exposes the current subgroup row, the next commutator subgroup row,
and the $\hsame$ transport relating the displayed $S_5$ identification to the
Galois-group package. The ledger does not import a host solvable-group theorem.
\end{theorem}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniDerivedSeriesLedger\_obstruction\_endpoint\_boundary}
\begin{proof}
Read the derived-series field of the accepted package as a finite list of
displayed subgroup rows. Each row is a BEDC history, and each successor row is
recorded by the displayed commutator-step ledger.

Transport is internal to the same list. The $\hsame$ classifier relates the
Galois identification row to the corresponding $S_5$ subgroup row, then carries
the step witness to the next displayed subgroup.

Since every step is recorded as an explicit finite ledger row, non-solvability is
read from this ledger rather than from an imported abstract solvability theorem.
\end{proof}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniDerivedSeriesLedger\_assoc\_surface}

\begin{theorem}[AbelRuffini derived-series finite transport]
\label{thm:abelruffini-derived-series-finite-transport}
A displayed Galois row, $S_5$ row, subgroup row, commutator row,
obstruction row, and continuation chain repack into a finite
$\AbelRuffiniUp$ BEDC transport ledger. The ledger has a unary next row for
each displayed commutator step and an endpoint row for the obstruction, with
$\hsame$ comparisons for the subgroup row, the unary next row, and the
endpoint row.
\end{theorem}
\begin{proof}
Start with the finite derived-series ledger from
\autoref{thm:abelruffini-derived-series-ledger-obligation}. It supplies the
displayed subgroup rows, the commutator successor rows, and the obstruction row
as finite $\mathsf{BHist}$ data.

Project unary closure through the three continuation rows: first from the
Galois row to the displayed $S_5$ row, then from the current subgroup row to
the unary next commutator row, and finally from the obstruction row to the
endpoint row.

The three $\hsame$ comparisons are read from these same projections. Repacking
the subgroup comparison, next-row comparison, and endpoint comparison gives the
finite transport ledger without importing a separate radical-tower or
solvable-group theorem.
\end{proof}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniDerivedSeriesLedger\_finite\_transport}

\begin{theorem}[AbelRuffini non-radical boundary obligation]
\label{thm:abelruffini-nonradical-boundary-obligation}
The $\AbelRuffiniUp$ non-solvability-by-radicals boundary is read only from the
polynomial and Galois identification rows together with the finite
derived-series ledger. It excludes general degree-$n$ classification, an
$A_5$ simplicity proof, and radical-tower bridge data.
\end{theorem}
\begin{proof}
Start with the polynomial Galois obligation. It supplies the displayed
degree-five polynomial, the splitting-field row, the Galois-group row, and the
$S_5$ identification.

Then apply the derived-series ledger obligation. The finite subgroup ledger
records the obstruction row that prevents the displayed series from reaching the
trivial subgroup.

The boundary statement is therefore only a readback from these rows. No field of
the package names a degree-$n$ classification, an independent $A_5$ simplicity
argument, or a standard radical-tower bridge, so those data remain outside the
chapter scope.
\end{proof}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniNonradicalBoundary\_obstruction\_surface}
\leanvariant{BEDC.Derived.AbelRuffiniUp.AbelRuffiniNonradicalBoundary\_obligation}

\begin{theorem}[AbelRuffini public certificate export]
\label{thm:abelruffini-public-certificate-export}
The polynomial Galois obligation, derived-series ledger obligation, and
non-radical boundary obligation repack into the public
$\NameCert_{\AbelRuffiniUp}$ certificate over the displayed $\PolynomialUp$,
$\NumFieldUp$, $\GaloisGroupUp$, $\SymGroupUp$, $\hsame$, and finite
derived-series rows. The exported certificate exposes the degree-five
polynomial source, base-field row, Galois-group row, $S_5$ identification,
derived-series ledger, and non-solvability-by-radicals boundary, while keeping
general degree-$n$ Galois solvability, an $A_5$ simplicity proof,
transcendental methods, abstract solvable-group theory, and a standard
radical-tower bridge outside its scope.
\end{theorem}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniPublicCertificate\_export}
\begin{proof}
First apply
\autoref{thm:abelruffini-polynomial-galois-obligation}. This supplies the
displayed polynomial, number-field base, splitting-field and Galois-group rows,
and the consumed $\SymGroupUp$ comparison with $S_5$.

Next apply
\autoref{thm:abelruffini-derived-series-ledger-obligation}. The derived series
is a finite BEDC ledger whose rows are transported through the same $\hsame$
comparison, so the public certificate reads only the displayed subgroup steps.

Finally apply
\autoref{thm:abelruffini-nonradical-boundary-obligation}. It identifies the
non-solvability boundary as a readback from the polynomial, Galois
identification, and finite derived-series rows. Repacking these three
obligations yields the public $\NameCert_{\AbelRuffiniUp}$ export and preserves
all stated non-claims.
\end{proof}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniPublicCertificateExport\_namecert\_surface}

\begin{theorem}[AbelRuffini standard radical-tower bridge boundary]
\label{thm:abelruffini-standard-radical-tower-bridge-boundary}
The standard radical-tower bridge for the displayed degree-five
$\AbelRuffiniUp$ certificate may read only the $\PolynomialUp$ coefficient
rows, the $\NumFieldUp$ base row, the $\GaloisGroupUp$ and $\SymGroupUp$ $S_5$
identification rows, the finite derived-series obstruction ledger, the
displayed $\hsame$ transports, the $\Cont$ routes, the $\mathsf{Pkg}$
provenance, and the $\NameCert$ rows already exported by
\autoref{thm:abelruffini-public-certificate-export}. It adds no general
degree-$n$ solvability theorem, no $A_5$ simplicity proof, no resolvent
reduction, and no transcendental method.
\end{theorem}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniStandardRadicalTower\_bridge\_boundary}
\leanvariant{BEDC.Derived.AbelRuffiniUp.AbelRuffiniPublicCertificate\_radical\_tower\_bridge\_boundary}
\begin{proof}
Project the public certificate export through
\autoref{thm:abelruffini-public-certificate-export}. This exposes the
coefficient rows, base-field row, Galois-group row, $S_5$ comparison,
derived-series ledger, transport routes, package provenance, and local naming
rows as the whole visible packet.

Use \autoref{thm:abelruffini-polynomial-galois-obligation} for the
polynomial-Galois coordinates and
\autoref{thm:abelruffini-derived-series-ledger-obligation} for the finite
derived-series obstruction. These obligations account for every row the
radical-tower bridge is allowed to consume.

Finally repack the same finite rows as the bridge boundary. Since the packet
has no coordinate for a general degree-$n$ theorem, an $A_5$ simplicity proof,
a resolvent reduction, or a transcendental method, none of those objects can be
exported by the bridge.
\end{proof}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniRadicalTowerBridge\_standard\_boundary}

\begin{theorem}[AbelRuffini degree-five consumer examples]
\label{thm:abelruffini-degree-five-consumer-examples}
Finite downstream consumers for polynomial coefficient readback,
Galois-group identification, derived-series obstruction, and radical-tower
exclusion all read the same displayed degree-five packet exported by the
public certificate and the standard radical-tower bridge boundary. The shared
packet consists of the $\PolynomialUp$ coefficient rows, $\NumFieldUp$ base
row, $\GaloisGroupUp$ row, $\SymGroupUp$ $S_5$ identification row, finite
derived-series ledger, displayed $\hsame$ transports, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ rows.

These consumers do not assert a general degree-$n$ solvability theorem, an
$A_5$ simplicity proof, a resolvent reduction, transcendental methods, or
machine-checked radical-tower bridge evidence.
\end{theorem}
\begin{proof}
Apply \autoref{thm:abelruffini-public-certificate-export}. It exposes the
degree-five polynomial source, base-field row, Galois-group row, $S_5$
identification, derived-series ledger, non-radical boundary, transports,
continuations, package provenance, and local naming rows as one public packet.

The polynomial coefficient and Galois-identification consumers read the
polynomial-Galois rows supplied by
\autoref{thm:abelruffini-polynomial-galois-obligation}. The obstruction
consumer reads the finite derived-series rows supplied by
\autoref{thm:abelruffini-derived-series-ledger-obligation}.

Finally apply
\autoref{thm:abelruffini-standard-radical-tower-bridge-boundary}. It identifies
the radical-tower exclusion consumer as a read of the same public packet rather
than as a new general solvability surface. Since the packet has no coordinate
for the excluded objects, the four consumers add none of them.
\end{proof}

\begin{theorem}[AbelRuffini finite consumer completeness]\label{thm:abelruffini-finite-consumer-completeness}
Every finite downstream consumer of the displayed degree-five non-radical
boundary reads only the $\PolynomialUp$ coefficient rows, $\NumFieldUp$ base
row, $\GaloisGroupUp$ and $\SymGroupUp$ $S_5$ rows, finite derived-series
obstruction ledger, displayed $\hsame$ transport, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and $\NameCert_{\AbelRuffiniUp}$ provenance.
Conversely, those displayed rows repack as the same finite consumer surface.

The consumer surface contains no general degree-$n$ solvability theorem,
$A_5$ simplicity proof, resolvent reduction, transcendental method, or hidden
radical-tower assumption.
\end{theorem}
\leanchecked{BEDC.Derived.AbelRuffiniUp.AbelRuffiniFiniteConsumer\_completeness}
\begin{proof}
Project the polynomial and Galois rows through
\autoref{thm:abelruffini-polynomial-galois-obligation}. This supplies the
degree-five coefficient rows, the number-field base row, the Galois-group row,
and the displayed $S_5$ comparison through $\SymGroupUp$.

Next apply \autoref{thm:abelruffini-derived-series-ledger-obligation}. The
finite obstruction is read as the displayed derived-series ledger, transported
through the same $\hsame$ rows and package provenance.

Use \autoref{thm:abelruffini-public-certificate-export} to package these
polynomial, base-field, group, obstruction, transport, continuation, package,
and naming rows as the public $\NameCert_{\AbelRuffiniUp}$ surface.

For the converse direction, start from exactly those displayed rows and repack
them by the same public export. Then apply
\autoref{thm:abelruffini-standard-radical-tower-bridge-boundary}; it identifies
the finite downstream radical-tower consumer as a read of that surface and not
as an additional algebraic assumption.

Since no cited row names a general degree-$n$ theorem, an $A_5$ simplicity
proof, a resolvent reduction, a transcendental method, or a hidden
radical-tower assumption, every finite consumer is exhausted by the displayed
surface and the displayed surface repacks every such consumer.
\end{proof}

\closureat{AbelRuffiniUp}{bridgedStr}
\closureat{AbelRuffiniUp}{matureStr}

\begin{closurestatus}{\AbelRuffiniUp}
  \constructivestory{An $\AbelRuffiniUp$ token names a separable monic polynomial $P$ of degree five over a $\NumFieldUp$ base $K$ together with three witnesses: an irreducibility row, a non-trivial-rational-root row, and a Galois-group identification row $\Gal(P/K)\cong S_5$. The carrier accepts a non-solvability-by-radicals certificate when $\Gal(P/K)$ is isomorphic to $S_5$ in the sense of $\NameCert_{\GaloisGroupUp}$ and $\NameCert_{\SymGroupUp}$, and the derived series of $S_5$ stops at $A_5$ without reaching the trivial subgroup. The classifier is $\hsame$ on the Galois group identification rows; the source covers polynomial coefficient histories, splitting field carrier rows, Galois group elements, derived-series subgroups, and rational-root exclusion rows; the pattern records irreducibility admissibility, $S_5$ identification, derived-series exactness, non-radical-tower exclusion, and degree-five admissibility rows; the ledger keeps the polynomial coefficients, the irreducibility witness, the $S_5$ identification, and the derived-series ledger visible. The five name-certificate obligations are supplied by the $\GaloisGroupUp$ chain plus solvable-group structure: the inhabited identity certificate is a fixed polynomial $x^5-x-1$ over $\mathbb{Q}$; classifier stability is reflexive, symmetric, and transitive $\hsame$ on Galois group identifications; transport repacks Galois actions through polynomial transport; ledger exactness identifies the carrier row with the $S_5$ derived-series ledger; the extension boundary fixes the non-radical-tower row. A history $h$ lies in the signature gap of an $\AbelRuffiniUp$ token $p$ when the source-domain accepts the polynomial-coefficient history, the signature relation pairs it with the non-solvable Galois identification, and token introduction names that identification as $p$. The chapter registers this finite Galois-group-based non-solvability surface under the name $\AbelRuffiniUp$; it is a degree-five $S_5$-Galois object whose standard radical-tower bridge boundary reads only the displayed finite rows and does not add general degree-$n$ classification, an $A_5$ simplicity proof, resolvent reduction, or transcendental method.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The bridged surface binds the displayed $\PolynomialUp$, $\NumFieldUp$, $\GaloisGroupUp$, $\SymGroupUp$, $\hsame$, and finite derived-series ledger rows through \autoref{thm:abelruffini-public-certificate-export}, the standard radical-tower bridge boundary of \autoref{thm:abelruffini-standard-radical-tower-bridge-boundary}, the degree-five consumer examples of \autoref{thm:abelruffini-degree-five-consumer-examples}, and the finite consumer completeness theorem of \autoref{thm:abelruffini-finite-consumer-completeness}.}
  \formalstatus{\unformalizedV}
  \bridgestatus{paperBridge}
  \notclaimed{The chapter does not close general degree-$n$ Galois solvability, the $A_5$ simplicity proof, transcendental methods, abstract solvable-group theory, or machine-checked radical-tower bridge evidence.}
  \upgradepath{No paper-side theory grade remains for this chapter; formal bridge verification remains on the separate verification axis.}
\end{closurestatus}
