\chapter{A Concrete Naming Certificate for \(\FormalPowerSeriesUp\)}
\label{ch:concrete-instances-fps-namecert}

The formal power series interface \(\FormalPowerSeriesUp\) has certificate obligations over a scalar ring from \autoref{ch:concrete-instances-ring-namecert} as functions \(\mathbb{N} \to R\), interpreted as coefficient sequences without termination. The classifier is pointwise sameness on every index. Formal series addition and Cauchy product are derived operations governed by the ring's certificate fields. Convergence is not asserted: this is the formal carrier, not analytic series.

\section{Carrier definition}

\begin{definition}[FormalPowerSeries carrier]
\label{def:fps-carrier}
Use coefficient functions \(\NatUp\to R\) over a certified scalar ring \(R\).
\end{definition}

\section{Concrete singleton zero formal power series instance}
\label{sec:fps-concrete-singleton-zero-series-instance}
\label{sec:fps-concrete-singleton-instance}

\begin{definition}[Singleton zero formal power series instance]
\label{def:singleton-zero-fps-instance}
\label{def:singleton-empty-history-fps-instance}
Let $A_{\emp}$ be the singleton history source of
Definition~\ref{def:list-singleton-history-source} at $a_0=\emp$. Use the
singleton empty-history scalar ring of
Definition~\ref{def:singleton-empty-history-ring-instance}. Define the series
classifier
$$
\rho_{\emp}(h,k):=
A_{\emp}(h)\land A_{\emp}(k)\land\hsame(h,k).
$$
Set the formal-power-series code carrier to $A_{\emp}$ on
$\mathsf{BHist}$ endpoints. Represent the zero formal power series by
$Z_{\emp}:=\emp$, and set the unit formal power series to
$U_{\emp}:=\emp$. Define the coefficient readout and displayed operations by
$$
\mathsf{coeff}_{\emp}(F,n):=\emp,\qquad
F\oplus_{\mathrm{fps}}G:=\emp,\qquad
F\odot_{\mathrm{fps}}G:=\emp.
$$
Thus every coefficient, zero endpoint, unit endpoint, addition endpoint, and
Cauchy-product endpoint is the singleton scalar endpoint $\emp$.
\end{definition}
\leandef{BEDC.Derived.FpsUp.FpsSingletonEmptyHistoryCarrier}
\leandef{BEDC.Derived.FpsUp.FpsSingletonEmptyHistoryClassifier}

\begin{theorem}[Singleton zero formal power series laws]
\label{thm:singleton-zero-fps-laws}
\label{thm:singleton-empty-history-fps-laws}
The tuple of Definition~\ref{def:singleton-zero-fps-instance} satisfies the
$\FormalPowerSeriesUp$ law package over the concrete $\mathsf{BHist}$ carrier:
\begin{enumerate}
  \item $Z_{\emp}$ and $U_{\emp}$ are carried by $A_{\emp}$.
  \item Every coefficient query $\mathsf{coeff}_{\emp}(F,n)$ is carried by the
  singleton empty-history scalar ring.
  \item If $A_{\emp}(F)$ and $A_{\emp}(G)$, then
  $A_{\emp}(F\oplus_{\mathrm{fps}}G)$ and
  $A_{\emp}(F\odot_{\mathrm{fps}}G)$.
  \item $\rho_{\emp}$ is reflexive, symmetric, and transitive on carried series
  codes.
  \item Addition is congruent under $\rho_{\emp}$ and has $Z_{\emp}$ as left
  and right zero under $\rho_{\emp}$.
  \item Cauchy product is congruent under $\rho_{\emp}$ and has $U_{\emp}$ as
  left and right unit under $\rho_{\emp}$.
  \item The coefficient ledger of every displayed endpoint is the constant
  singleton scalar endpoint $\emp$, and the scalar clauses are those of
  Theorem~\ref{thm:singleton-empty-history-ring-laws}.
\end{enumerate}
No convergence field is required.
\end{theorem}
\begin{proof}
The carrier endpoint is supplied by Definition~\ref{def:list-singleton-history-source}
at $a_0=\emp$. In particular, $Z_{\emp}$, $U_{\emp}$, and every displayed
operation endpoint reduce to the same carried endpoint $\emp$.

For coefficient queries, every value of $\mathsf{coeff}_{\emp}(F,n)$ is
definitionally $\emp$. The scalar side is the singleton empty-history ring of
Definition~\ref{def:singleton-empty-history-ring-instance}, and
Theorem~\ref{thm:singleton-empty-history-ring-laws} supplies its scalar zero,
scalar one, addition, and multiplication clauses.

For addition and Cauchy-product closure, the displayed operations return
$\emp$ for every pair of inputs. The singleton carrier witness therefore
discharges both closure obligations without inspecting the input series or the
index used in a coefficient view.

Classifier reflexivity, symmetry, and transitivity are inherited from the
$\hsame$ reflexivity, symmetry, and transitivity laws in the FKernel, together
with the two singleton endpoint witnesses required by $\rho_{\emp}$. Operation
congruence reduces both addition results and both Cauchy-product results to
$\emp$, so the relation component is again $\hsame(\emp,\emp)$.

The zero laws and unit laws reduce to comparisons of $\emp$ with $\emp$.
The same $\rho_{\emp}$ package gives the left and right zero laws for addition
and the left and right unit laws for Cauchy product.

Finally, every coefficient query returns $\emp$. Hence the coefficient ledger
for the zero series, unit series, sum, and Cauchy product is constant, with no
convergence claim involved.
\end{proof}
\leanchecked{BEDC.Derived.FpsUp.fps\_singleton\_empty\_schema\_laws}

\begin{theorem}[Singleton coefficient endpoint has empty ledger]
\label{thm:fps-singleton-coeff-empty-ledger}
For every displayed singleton formal power series endpoint $F$ and coefficient
index $n$, if $F$ is carried by the singleton source, then
$$
\HSame(\mathsf{coeff}_{\emp}(F,n),\emp)
$$
and the coefficient endpoint is classified with the empty scalar endpoint by
$\rho_{\emp}$.
\end{theorem}
\begin{proof}
The coefficient operation of the singleton formal-power-series instance is
definitionally constant at $\emp$. The history-sameness part is therefore
$\HSame(\emp,\emp)$, and the classifier clause is the triple consisting of the
two singleton carrier witnesses for $\emp$ and the same reflexive
history-sameness witness.
\end{proof}
\leanchecked{BEDC.Derived.FpsUp.FpsSingletonCoeff\_empty\_ledger}

The $\FormalPowerSeriesUp$ schema is instantiated by this concrete
$\mathsf{BHist}$ carrier and constant coefficient operations, so future Lean
targets can be anchored directly in $\mathsf{BHist}$.

\begin{theorem}[Singleton empty-history FPS semantic name certificate]
\label{thm:fps-singleton-empty-history-semantic-namecert}
The singleton empty-history formal-power-series carrier
$A_{\emp}(h):=h\hsame\emp$ with classifier
$$
\rho_{\emp}(h,k):=A_{\emp}(h)\land A_{\emp}(k)\land h\hsame k
$$
forms a
$\mathsf{SemanticNameCert}(A_{\emp},A_{\emp},A_{\emp},\rho_{\emp})$.
\end{theorem}
\begin{proof}
The carrier is inhabited by $\emp$ with $\hsame$ reflexivity. Reflexivity,
symmetry, and transitivity of the classifier use the corresponding $\hsame$
laws, while the two carrier components are part of the classifier witness.
Carrier transport across the classifier reads out the right carrier component.
Pattern and ledger soundness are identity maps because the source, pattern, and
ledger predicates are the same singleton carrier.
\end{proof}
\leanchecked{BEDC.Derived.FpsUp.FpsSingletonEmptyHistory\_semanticNameCert}

\begin{theorem}[Singleton FPS classifier append split empty]
\label{thm:fps-singleton-classifier-append-split-empty}
For $p,q,h:\mathsf{BHist}$,
$$
\rho_{\emp}(\mathsf{append}(p,q),h)
\quad\Longleftrightarrow\quad
p\hsame\emp\land q\hsame\emp\land A_{\emp}(h).
$$
\end{theorem}
\begin{proof}
In the forward direction, the left carrier component of
$\rho_{\emp}(\mathsf{append}(p,q),h)$ says
$\mathsf{append}(p,q)\hsame\emp$. The append-empty inversion theorem splits
this into $p\hsame\emp$ and $q\hsame\emp$, while the right carrier component
already gives $A_{\emp}(h)$.

Conversely, append-empty introduction turns $p\hsame\emp$ and $q\hsame\emp$
into $A_{\emp}(\mathsf{append}(p,q))$. Together with $A_{\emp}(h)$, transitivity
through $\emp$ supplies the classifier comparison.
\end{proof}
\leanchecked{BEDC.Derived.FpsUp.FpsSingletonEmptyHistoryClassifier\_append\_split\_empty\_iff}

\section{The certificate}

\begin{definition}[FormalPowerSeries source specification]
\label{def:fps-source-specification}
The source is the natural index source and scalar ring source.
\end{definition}

\begin{definition}[FormalPowerSeries pattern specification]
\label{def:fps-pattern-specification}
The pattern is infinite coefficient assignment indexed by unary natural histories.
\end{definition}

\begin{definition}[FormalPowerSeries classifier specification]
\label{def:fps-classifier-specification}
The classifier relates two series when all corresponding coefficients are scalar-classified the same.
\end{definition}

\begin{definition}[FormalPowerSeries stability certificate]
\label{def:fps-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item pointwise reflexivity
  \item pointwise transitivity
  \item addition closure pointwise
  \item Cauchy product closure by finite sums at each coefficient index
  \item no convergence field is required
\end{enumerate}
\end{definition}

\begin{definition}[FormalPowerSeries ledger policy]
\label{def:fps-ledger-policy}
Record the coefficient rule and scalar ledgers at queried indices.
\end{definition}

\begin{definition}[\(\FormalPowerSeriesUp\) certificate obligations]
\label{def:fps-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\FormalPowerSeriesUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\FormalPowerSeriesUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:fps-zero-axiom-note}
Avoids funext by using pointwise classifier sameness.
\end{remark}
