\chapter{A Concrete Naming Certificate for $\ControlControllabilityUp$}
\label{ch:concrete-instances-controlcontrollability-namecert}

The $\ControlControllabilityUp$ interface records the finite reachability surface of a linear control system. Its textbook source is the Kalman controllability rank-style data of Kalman, \emph{On the General Theory of Control Systems} (1960), but the BEDC chapter states only the finite reachability ledger and $\NameCert$ surface. The dependency anchors are $\NameCert_{\DynSystemUp}$, $\NameCert_{\MatrixUp}$, $\NameCert_{\VecSpaceUp}$, $\NameCert_{\LinMapUp}$, $\NameCert_{\ControlObservabilityUp}$, $\NameCert_{\KalmanFilterUp}$, and $\NameCert_{\LQRUp}$.

\section{Carrier definition}
\label{sec:controlcontrollability-carrier}

\begin{definition}[ControlControllability finite reachability carrier]
\label{def:controlcontrollability-carrier}
A $\ControlControllabilityUp$ carrier is a finite $\mathsf{BHist}$ packet whose rows are a state-carrier row, an input-carrier row, a transition-matrix row $A$, a control-matrix row $B$, a finite horizon unary row $n$, the displayed reachability columns $B,AB,\ldots,A^{n-1}B$, a reachability-matrix row collecting those columns, $\hsame$ comparisons between corresponding finite rows, $\Cont$ provenance for each displayed multiplication and column append, and $\mathsf{Pkg}$ rows naming $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\ControlObservabilityUp$, $\KalmanFilterUp$, and $\LQRUp$.
\end{definition}
\leandef{BEDC.Derived.ControlControllabilityUp.ControlControllabilityCarrier}

\begin{definition}[ControlControllability classifier]
\label{def:controlcontrollability-classifier}
Two $\ControlControllabilityUp$ carriers are classified as the same finite reachability certificate exactly when their state rows, input rows, $A$ rows, $B$ rows, horizon rows, reachability-column rows, reachability-matrix rows, $\Cont$ routes, and $\mathsf{Pkg}$ rows agree under displayed $\hsame$ transports and the $\MatrixUp$ column-transport ledger. The classifier does not quotient by a host reachable subspace and does not identify packets by an ambient controllability predicate.
\end{definition}

\section{The certificate}
\label{sec:controlcontrollability-certificate}

\begin{theorem}[ControlControllability reachability ledger]
\label{thm:controlcontrollability-reachability-ledger}
Every accepted $\ControlControllabilityUp$ packet exposes exactly the state-carrier row, input-carrier row, transition row $A$, control row $B$, finite horizon row $n$, displayed reachability columns $B,AB,\ldots,A^{n-1}B$, reachability-matrix row, $\hsame$ transports, $\Cont$ provenance, and $\mathsf{Pkg}$ dependency rows of \autoref{def:controlcontrollability-carrier}. It exports no host reachable subspace, rank theorem, Kalman decomposition, analytic trajectory semantics, or infinite-horizon object.
\end{theorem}
\leanchecked{BEDC.Derived.ControlControllabilityUp.ControlControllabilityReachabilityPacket\_reachability\_ledger}
\begin{proof}
Project the accepted carrier to the rows listed in \autoref{def:controlcontrollability-carrier}. The state, input, transition, control, horizon, column, reachability-matrix, transport, continuation, and provenance rows are visible as finite $\mathsf{BHist}$ coordinates.

Conversely, every consumer-visible reachability read enters through one of those coordinates. Matrix multiplication and column append are recorded as $\MatrixUp$ and $\LinMapUp$ ledger rows, while the state and input endpoints are recorded through $\VecSpaceUp$ and $\DynSystemUp$ rows.

The carrier has no coordinate for a host reachable subspace, rank theorem, Kalman decomposition, analytic trajectory, or infinite horizon. Therefore those objects cannot be exported by the certificate.
\end{proof}

\begin{theorem}[ControlControllability reachability-column transport obligation]
\label{thm:controlcontrollability-column-transport-obligation}
Every displayed reachability column $B,AB,\ldots,A^{n-1}B$ in a $\ControlControllabilityUp$ packet is generated by finite $\MatrixUp$, $\LinMapUp$, $\Cont$, and $\mathsf{BHist}$ rows. Transport along the displayed $\hsame$ comparisons preserves the reachability-matrix packet by transporting each carrier column and the recorded column-append route, without invoking a host rank predicate or a host reachable subspace.
\end{theorem}
\begin{proof}
Project the accepted packet to its $B,AB,\ldots,A^{n-1}B$ rows. Each projected column is attached to a finite multiplication route, and the reachability-matrix row is the ordered append of those displayed columns.

Now transport the source rows along $\hsame$. The multiplication rows remain the same finite $\MatrixUp$ and $\LinMapUp$ routes after transport, and the append route remains a $\Cont$ coordinate of the same packet shape.

The preserved object is therefore the displayed reachability-matrix packet itself. No coordinate in the construction names a rank predicate or host reachable subspace, so no such predicate is used by the transport obligation.
\end{proof}

\begin{theorem}[ControlControllability classifier stability obligation]
\label{thm:controlcontrollability-classifier-stability-obligation}
The $\ControlControllabilityUp$ classifier is reflexive, symmetric, and transitive componentwise over the state row, input row, $A$ row, $B$ row, horizon row, reachability-column rows, reachability-matrix row, $\Cont$ rows, and $\mathsf{Pkg}$ rows of the carrier packet.
\end{theorem}
\begin{proof}
For reflexivity, apply the rowwise reflexivity of $\hsame$ to the state, input, matrix, horizon, reachability, continuation, and package coordinates, then repack the resulting finite row comparisons as a classifier witness.

For symmetry, reverse each displayed row comparison. The carrier has only finitely many named coordinates, so the reversed state, input, $A$, $B$, horizon, column, reachability-matrix, $\Cont$, and $\mathsf{Pkg}$ comparisons assemble into the symmetric classifier witness.

For transitivity, compose the corresponding row comparisons coordinate by coordinate. The composed rows have the same packet shape as the original classifier data, and repacking them gives the transitive classifier witness.
\end{proof}

\begin{theorem}[ControlControllability dependency scope obligation]
\label{thm:controlcontrollability-dependency-scope-obligation}
All public reachability reads from a $\ControlControllabilityUp$ packet factor through $\NameCert_{\DynSystemUp}$, $\NameCert_{\MatrixUp}$, $\NameCert_{\VecSpaceUp}$, $\NameCert_{\LinMapUp}$, $\NameCert_{\ControlObservabilityUp}$, $\NameCert_{\KalmanFilterUp}$, and $\NameCert_{\LQRUp}$ rows together with the displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ coordinates. They do not factor through host reachable subspaces, Kalman decomposition objects, or analytic trajectories.
\end{theorem}
\begin{proof}
Inspect the package provenance row of the carrier. Its named dependencies are exactly the displayed $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\ControlObservabilityUp$, $\KalmanFilterUp$, and $\LQRUp$ certificate rows, together with the kernel rows that record history, transport, continuation, and packaging.

Every public reachability read is a projection from that finite provenance packet or from the reachability rows transported by it. The dependency factorization is therefore exhausted by the named $\NameCert$ rows and the displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ coordinates.

The packet contains no coordinate for a host reachable subspace, no Kalman decomposition object, and no analytic trajectory semantics. Those objects are outside the dependency scope of the public surface.
\end{proof}

\begin{theorem}[ControlControllability NameCert obligation surface]
\label{thm:controlcontrollability-namecert-obligation-surface}
The local $\NameCert_{\ControlControllabilityUp}$ seed surface consists of the carrier and classifier rows of \autoref{def:controlcontrollability-carrier} and \autoref{def:controlcontrollability-classifier}, the finite reachability-ledger row of \autoref{thm:controlcontrollability-reachability-ledger}, the reachability-column transport obligation of \autoref{thm:controlcontrollability-column-transport-obligation}, the classifier stability obligation of \autoref{thm:controlcontrollability-classifier-stability-obligation}, and the dependency scope obligation of \autoref{thm:controlcontrollability-dependency-scope-obligation}.
\end{theorem}
\leanchecked{BEDC.Derived.ControlControllabilityUp.ControlControllabilityCarrier\_namecert\_obligation\_surface}
\begin{proof}
Start with the finite carrier and classifier. They determine the visible packet shape and the rowwise comparison relation for all state, input, transition, control, horizon, column, reachability-matrix, continuation, and provenance coordinates.

The reachability-ledger theorem identifies the exact exported rows. The matrix column-transport row is then a finite componentwise transport of the displayed $B,AB,\ldots,A^{n-1}B$ columns, not an appeal to a host reachable-space quotient.

The remaining dependency rows are package provenance. They allow consumers to compare the controllability packet with observability, Kalman-filter, and regulator packets only through named finite rows, so the resulting surface is a seed $\NameCert$ obligation rather than a standard control-theory bridge.
\end{proof}

\begin{theorem}[ControlControllability consumer boundary]
\label{thm:controlcontrollability-consumer-boundary}
Every downstream consumer of $\ControlControllabilityUp$ can read controllability data only through the displayed $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\ControlObservabilityUp$, $\KalmanFilterUp$, $\LQRUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows of \autoref{def:controlcontrollability-carrier}. No consumer can require analytic trajectory semantics, a host reachable subspace, Kalman decomposition, stochastic optimality, or a standard bridge from this chapter.
\end{theorem}
\begin{proof}
Take a consumer-visible readback from an accepted packet. By the classifier, the readback is invariant only under the displayed $\hsame$ transports and the $\MatrixUp$ column-transport ledger.

Apply the reachability-ledger theorem to exhaust the visible rows. The readback is therefore a finite route through state, input, transition, control, horizon, reachability-column, reachability-matrix, continuation, and package coordinates.

Since none of the excluded host objects appears as a carrier coordinate, a consumer cannot project one from the packet. The boundary is exactly the finite BEDC reachability surface.
\end{proof}

\closureat{ControlControllabilityUp}{seedStr}
\begin{closurestatus}{\ControlControllabilityUp}
  \constructivestory{}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed surface records the finite reachability carrier, classifier, reachability ledger, NameCert obligation surface, and consumer boundary for $\ControlControllabilityUp$ over displayed $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\ControlObservabilityUp$, $\KalmanFilterUp$, $\LQRUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close analytic trajectory semantics, Kalman decomposition, stochastic optimality, host reachable subspace quotients, rank-completeness, or a standard bridge.}
  \upgradepath{The scoped paper-axis step is a checked finite reachability $\NameCert_{\ControlControllabilityUp}$ theorem over the displayed carrier and classifier rows.}
\end{closurestatus}
