\chapter{A Concrete Naming Certificate for $\KKTUp$}
\label{ch:concrete-instances-kkt-namecert}

The $\KKTUp$ interface records the finite certificate surface of Karush--Kuhn--Tucker optimality data for a displayed constrained convex program. Its standard optimization source is Boyd and Vandenberghe, \emph{Convex Optimization} (2004). The BEDC dependencies are $\NameCert_{\ConvexSetUp}$ for the feasible-region row, $\NameCert_{\LPDualityUp}$ for primal-dual comparison rows, $\NameCert_{\MatrixUp}$ and $\NameCert_{\VecSpaceUp}$ for stationarity and residual rows, and $\NameCert_{\RealUp}$ for scalar slack and objective rows.

\section{Carrier definition}
\label{sec:kkt-carrier}

\begin{definition}[KKTUp BHist carrier]
\label{def:kkt-bhist-carrier}
A $\KKTUp$ carrier is a finite $\mathsf{BHist}$ packet whose visible rows are a primal variable row, a dual multiplier row, a constraint residual row, a stationarity row, feasibility rows, a complementary-slackness ledger, $\hsame$ comparison rows between corresponding displayed entries, $\Cont$ provenance rows for the stationarity and ledger readbacks, $\mathsf{Pkg}$ rows naming $\ConvexSetUp$, $\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$, and a $\NameCert$ provenance row for the accepted packet.

The classifier accepts exactly those packets whose primal, dual, residual, stationarity, feasibility, slackness, comparison, continuation, and package rows are read through the displayed dependency certificates. It exports no nonlinear optimizer, differentiability oracle, Slater witness, analytic duality theorem, or host real-valued minimization semantics.
\end{definition}
\leandef{BEDC.Derived.KKTUp.KKTCarrierPacket}

\section{The certificate}
\label{sec:kkt-certificate}

\begin{theorem}[KKTUp primal-dual row obligations]
\label{thm:kkt-primal-dual-row-obligations}
Every accepted $\KKTUp$ packet exposes a finite primal row, dual multiplier row, constraint residual row, stationarity row, and feasibility row. The primal and feasibility rows are read through $\ConvexSetUp$ and $\VecSpaceUp$; the dual and residual rows are read through $\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$; and every row carries its displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.KKTUp.KKTPrimalDualCarrier\_primal\_dual\_row\_obligations}
\begin{proof}
Project the carrier of \autoref{def:kkt-bhist-carrier}. Its accepted packet lists exactly the primal, multiplier, residual, stationarity, feasibility, comparison, continuation, package, and naming rows.

Read each row through its named dependency certificate. The feasible-region row supplies the convex-set face, the linear and vector rows supply the displayed stationarity and residual endpoints, the real rows supply scalar slack and objective endpoints, and the duality row supplies the primal-dual comparison.

No other row is present in the packet. The accepted primal-dual surface is therefore exhausted by the finite $\mathsf{BHist}$ rows and their visible provenance.
\end{proof}
\leanchecked{BEDC.Derived.KKTUp.KKTPrimalDualPacket\_row\_obligations}

\begin{theorem}[KKTUp stationarity and feasibility hsame transport]
\label{thm:kkt-stationarity-feasibility-hsame-transport}
Let $K$ and $K'$ be finite $\KKTUp$ packets whose primal variable, dual
multiplier, residual, stationarity, feasibility, and slackness rows are related
componentwise by the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ rows of the $\KKTUp$ classifier. Suppose the same transport also
respects the dependency rows over $\ConvexSetUp$, $\LPDualityUp$, $\MatrixUp$,
$\VecSpaceUp$, and $\RealUp$. If $K$ is accepted, then $K'$ is accepted on the
same stationarity and feasibility surface, and the complementary-slackness
ledger remains confined to the finite boundary of
\autoref{thm:kkt-complementarity-ledger-exactness}.

The transported packet introduces no analytic differentiability row, Slater
data, host minimization predicate, or solver semantics beyond the displayed
BEDC rows.
\end{theorem}
\leanchecked{BEDC.Derived.KKTUp.KKTPrimalDualCarrier\_stationarity\_feasibility\_hsame\_transport}
\leanchecked{BEDC.Derived.KKTUp.KKTCarrierPacket\_stationarity\_feasibility\_hsame\_transport}
\begin{proof}
Unfold \autoref{def:kkt-bhist-carrier}. The carrier names exactly the primal,
dual multiplier, residual, stationarity, feasibility, slackness, comparison,
continuation, package, and naming rows that can participate in the classifier.

Apply \autoref{thm:kkt-primal-dual-row-obligations}. The primal and feasibility
rows are read through $\ConvexSetUp$ and $\VecSpaceUp$, while the multiplier,
residual, stationarity, slackness, and scalar rows are read through
$\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$.

Transport each displayed row through the given componentwise $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and $\NameCert$ data, then repack the resulting finite
rows in the same carrier positions. Since the dependency rows are transported
with the visible packet, the stationarity and feasibility surface of $K'$ is
accepted by the same classifier shape.

Finally apply \autoref{thm:kkt-complementarity-ledger-exactness}. The slackness
ledger remains only the displayed residual, multiplier, scalar slack,
comparison, continuation, and package rows, so the transport cannot add
analytic differentiability, Slater data, host minimization semantics, or solver
evidence.
\end{proof}
\leanchecked{BEDC.Derived.KKTUp.KKTPrimalDualPacket\_stationarity\_feasibility\_hsame\_transport}

\begin{theorem}[KKTUp stationarity and feasibility stability]
\label{thm:kkt-stationarity-feasibility-stability}
Let $K$ and $K'$ be accepted $\KKTUp$ packets whose displayed primal variable, dual multiplier, residual, matrix and vector stationarity rows, real scalar rows, finite $\Cont$ routes, and $\mathsf{Pkg}$ provenance compare componentwise by the $\hsame$ rows of the $\KKTUp$ classifier. Transporting along those rows preserves the accepted stationarity and feasibility rows of the packet. The transport introduces no analytic differentiability oracle, Slater witness, nonlinear optimizer, or host minimization semantics.
\end{theorem}
\leanchecked{BEDC.Derived.KKTUp.KKTCarrierPacket\_stationarity\_feasibility\_stability}
\begin{proof}
Unpack the carrier of \autoref{def:kkt-bhist-carrier}. The stationarity and feasibility coordinates are displayed rows in the same finite $\mathsf{BHist}$ packet as the primal variable, multiplier, residual, scalar, continuation, package, and naming rows.

Apply \autoref{thm:kkt-primal-dual-row-obligations} to read the dependency provenance of those coordinates. The primal and feasibility rows are routed through the convex-set and vector-space certificates, while the dual, residual, stationarity, and scalar rows are routed through the displayed linear, vector, real, and duality certificates.

Componentwise $\hsame$ transport replaces each displayed row by its classified partner and keeps the finite $\Cont$ routes and $\mathsf{Pkg}$ provenance fixed at the readback boundary. Therefore the stationarity and feasibility rows remain accepted rows of $K'$.

The carrier has no field for a differentiability oracle, Slater witness, nonlinear optimizer, or host real minimization semantics. The stability claim is therefore confined to the displayed BEDC packet rows.
\end{proof}

\begin{theorem}[KKTUp complementarity ledger exactness]
\label{thm:kkt-complementarity-ledger-exactness}
In an accepted $\KKTUp$ packet, the complementary-slackness ledger is exactly the finite list of displayed residual, multiplier, scalar slack, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows carried by \autoref{def:kkt-bhist-carrier}. A downstream read of complementarity cannot use an unrecorded inequality family, host multiplication law, analytic limit, or external optimality predicate.
\end{theorem}
\leanchecked{BEDC.Derived.KKTUp.KKTComplementarityLedger\_exactness}
\begin{proof}
Inspect the complementary-slackness coordinate of the carrier. It is a finite ledger, and each entry points to the displayed residual row, multiplier row, scalar row, comparison row, continuation row, and package row.

The ledger readback is obtained by following those entries and no ambient arithmetic table is introduced. The real-valued component is the named $\RealUp$ endpoint already present in the packet.

Since the carrier has no coordinate for an external inequality family, analytic limit, or host optimality predicate, complementarity is exact at the displayed ledger boundary.
\end{proof}

\begin{theorem}[KKTUp NameCert obligation surface]
\label{thm:kkt-namecert-obligation-surface}
The local $\NameCert_{\KKTUp}$ obligation surface consists of five finite rows: the carrier and classifier row of \autoref{def:kkt-bhist-carrier}; the primal-dual dependency row over $\ConvexSetUp$, $\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$; the stationarity and feasibility stability row under componentwise $\hsame$ transport; the complementary-slackness ledger exactness row; and the downstream consumer boundary that restricts all reads to the displayed $\mathsf{BHist}$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.KKTUp.KKTPrimalDualCarrier\_namecert\_obligation\_surface}
\leanchecked{BEDC.Derived.KKTUp.KKTPrimalDualPacket\_namecert\_obligation\_surface}
\begin{proof}
Start from the finite carrier and classifier. These give the packet inventory and the accepted readback relation for every visible row.

Apply \autoref{thm:kkt-primal-dual-row-obligations} to bind the primal, dual, residual, stationarity, and feasibility rows to their dependency certificates. Componentwise $\hsame$ transport preserves the same row inventory because the classifier reads only those displayed comparisons and the same provenance rows.

Apply \autoref{thm:kkt-complementarity-ledger-exactness} for the slackness face. Repacking the dependency rows, transport rows, ledger row, and consumer restriction gives exactly the five local $\NameCert_{\KKTUp}$ obligations.
\end{proof}

\begin{theorem}[KKTUp downstream consumer boundary]
\label{thm:kkt-downstream-consumer-boundary}
Any optimization, algebraic, or control consumer of $\NameCert_{\KKTUp}$ may read only the finite primal, multiplier, residual, stationarity, feasibility, slackness, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows of the carrier. It cannot infer full nonlinear optimization semantics, Slater existence, analytic differentiability, host real minimization, or a solver certificate from the $\KKTUp$ packet alone.
\end{theorem}
\leanchecked{BEDC.Derived.KKTUp.KKTCarrierPacket\_downstream\_consumer\_boundary}
\begin{proof}
Take an arbitrary downstream read of the certificate. By the local obligation surface, the read must factor through the displayed carrier and its finite provenance rows.

The only optimization-facing rows in that carrier are the primal, multiplier, residual, stationarity, feasibility, and complementary-slackness entries. Each is already tied to a dependency certificate and to a visible continuation route.

All excluded analytic objects require rows absent from the carrier. The downstream boundary therefore stops at the finite BEDC packet and cannot project host optimization semantics or solver evidence.
\end{proof}

\begin{theorem}[KKTUp public finite-packet export]
\label{thm:kkt-public-finite-packet-export}
The public export for $\KKTUp$ is exactly the finite primal, multiplier,
residual, stationarity, feasibility, complementary-slackness, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows of
\autoref{def:kkt-bhist-carrier}. Its dependency reads pass only through
$\ConvexSetUp$, $\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$ rows
already recorded in the carrier and its local certificate surface.

The export contains no full nonlinear optimization semantics, Slater
existence, analytic differentiability, host minimization predicate, or solver
certificate.
\end{theorem}
\begin{proof}
Start with \autoref{thm:kkt-primal-dual-row-obligations}. It binds the primal,
multiplier, residual, stationarity, and feasibility rows to the displayed
$\ConvexSetUp$, $\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$
dependency reads.

Use \autoref{thm:kkt-stationarity-feasibility-hsame-transport} for the
componentwise $\hsame$ routes. These routes preserve the public row inventory
because they transport only the displayed stationarity and feasibility
certificates.

Apply \autoref{thm:kkt-complementarity-ledger-exactness} for the
complementary-slackness ledger. Then use
\autoref{thm:kkt-downstream-consumer-boundary} to restrict every downstream
read to the finite carrier rows, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
local $\NameCert_{\KKTUp}$ surface.

The carrier has no coordinate for nonlinear optimization semantics, Slater
existence, analytic differentiability, host minimization, or solver evidence.
The listed finite rows are therefore the whole public packet export.
\end{proof}

\closureat{KKTUp}{seedStr}
\closureat{KKTUp}{obligationStr}
\closureat{KKTUp}{scopedStr}[BEDC.Derived.KKTUp.KKTCarrierPacket\_downstream\_consumer\_boundary]
\closureat{KKTUp}{publicStr}[BEDC.Derived.KKTUp.KKTCarrierPacket\_downstream\_consumer\_boundary]
\closureat{KKTUp}{bridgedStr}[BEDC.Derived.KKTUp.KKTCarrierPacket\_downstream\_consumer\_boundary]
\begin{closurestatus}{\KKTUp}
  \constructivestory{The construction starts from a finite constrained-convex-program packet, records primal, dual, residual, stationarity, feasibility, and complementary-slackness rows, and routes every read through displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{By \autoref{thm:kkt-downstream-consumer-boundary}, \autoref{thm:kkt-public-finite-packet-export}, \autoref{def:kkt-standard-finite-packet-presentation}, and \autoref{thm:kkt-finite-packet-standard-bridge}, the scoped boundary binds the primal, dual, residual, stationarity, feasibility, slackness, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows of the finite KKT packet and its standard finite-packet bridge.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.KKTUp.KKTCarrierPacket\_downstream\_consumer\_boundary}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close full nonlinear optimization, Slater existence, analytic differentiability, host real optimization semantics, or checked bridge status.}
  \upgradepath{The next obligation is Lean bridge checking for the finite KKT packet without adding analytic solver semantics.}
\end{closurestatus}

\begin{definition}[Standard finite KKT packet presentation]
\label{def:kkt-standard-finite-packet-presentation}
A standard finite KKT packet presentation for $\KKTUp$ is a displayed finite table whose entries are exactly a primal variable row, a dual multiplier row, a constraint residual row, a stationarity row, feasibility rows, a complementary-slackness row, componentwise $\hsame$ rows between the displayed entries, $\Cont$ rows for stationarity and slackness readback, $\Pkg$ rows naming $\ConvexSetUp$, $\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$, a $\NameCert_{\KKTUp}$ row, and the dependency rows through those five named certificates. Its standard reading is only this finite KKT table: primal data, multipliers, residuals, stationarity, feasibility, and complementary slackness as displayed rows.
\end{definition}

\begin{theorem}[KKTUp finite-packet standard bridge]
\label{thm:kkt-finite-packet-standard-bridge}
Let $S$ be a standard finite KKT packet presentation in the sense of \autoref{def:kkt-standard-finite-packet-presentation}. If $S$ is admitted solely through the primal, multiplier, residual, stationarity, feasibility, complementary-slackness, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and dependency rows exported by $\KKTUp$, then $S$ has a conservative standard bridge through the public $\KKTUp$ finite packet. The forward read sends $S$ to the public export of \autoref{thm:kkt-public-finite-packet-export}. The reverse read sends that public export back to the same displayed finite KKT presentation, up to the componentwise $\hsame$ rows already present in $S$. Both composites preserve the primal, multiplier, residual, stationarity, feasibility, complementary-slackness, continuation, package, naming, and dependency rows.

The bridge adds no Slater condition, differentiability oracle, solver certificate, analytic duality theorem, nonlinear optimizer, host minimization predicate, or host real-valued optimization semantics.
\end{theorem}
\begin{proof}
Read $S$ through \autoref{def:kkt-standard-finite-packet-presentation}. Its entries are exactly the finite KKT rows listed there, together with the dependency rows over $\ConvexSetUp$, $\LPDualityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\RealUp$.

By \autoref{def:kkt-bhist-carrier}, these are precisely the visible carrier rows accepted by $\KKTUp$. The classifier therefore admits $S$ only by placing its primal, multiplier, residual, stationarity, feasibility, slackness, comparison, continuation, package, naming, and dependency entries in the corresponding finite $\BHist$ packet positions.

Apply \autoref{thm:kkt-primal-dual-row-obligations}. The primal, multiplier, residual, stationarity, and feasibility entries of $S$ are read through the displayed dependency certificates, and every such entry carries its visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. Apply \autoref{thm:kkt-complementarity-ledger-exactness} to the slackness entry. The complementary-slackness row is exactly the finite ledger over the displayed residual, multiplier, scalar slack, comparison, continuation, and package rows.

The forward standard read is now forced: it forgets no row and adds no row, but regards this accepted finite packet as the standard finite KKT table consisting of the displayed primal data, multipliers, residuals, stationarity, feasibility, and complementary slackness. This is the public export described in \autoref{thm:kkt-public-finite-packet-export}, because that theorem identifies the whole public $\KKTUp$ surface with exactly these finite rows and their five dependency reads.

For the reverse read, start from the public export just obtained. \autoref{thm:kkt-public-finite-packet-export} says that the export contains only the listed finite rows of \autoref{def:kkt-bhist-carrier}. Reinsert those rows into the table positions of \autoref{def:kkt-standard-finite-packet-presentation}. The stationarity and feasibility entries are stable under the componentwise comparisons by \autoref{thm:kkt-stationarity-feasibility-hsame-transport}, and the slackness entry is fixed at the ledger boundary by \autoref{thm:kkt-complementarity-ledger-exactness}. Hence the returned table is the same displayed finite KKT presentation, with equality understood through the $\hsame$ rows already carried by $S$.

The two composites therefore preserve every visible row of the presentation: primal, multiplier, residual, stationarity, feasibility, complementary slackness, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and the named dependency rows. Finally, \autoref{thm:kkt-downstream-consumer-boundary} rules out every downstream read not present in that finite carrier. Since there is no carrier coordinate for Slater data, differentiability, solver evidence, analytic duality, nonlinear optimization, host minimization, or host real-valued optimizer semantics, the bridge is conservative at exactly the finite packet boundary.
\end{proof}
