\chapter{A Concrete Naming Certificate for $\AxisUnarySpineNormalizerUp$}
\label{ch:concrete-instances-axisunaryspinenormalizer-namecert}
\origin{ai}

The $\AxisUnarySpineNormalizerUp$ packet gives the unary-direction bridge a concrete finite standard-boundary object. It records how a displayed $\NatUp$ unary spine is read beside a displayed $\AxisNatUp$ zero-spine packet, with the normalizing boundary carried by $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows rather than by an identification of the two carriers.

\begin{definition}[AxisUnarySpineNormalizer carrier]
\label{def:axis-unary-spine-normalizer-carrier}
An $\AxisUnarySpineNormalizerUp$ carrier is a finite $\BHist$ packet
$$
U=(N,A,L,Z,H,C,P,R)
$$
with the following visible coordinates:
\begin{enumerate}
\item $N$ is the source $\NatUp$ unary-spine row, read as a finite $\Eone$ history together with its local naming certificate;
\item $A$ is the target $\AxisNatUp$ zero-spine row, read as a finite $\Ezero$ history together with its local naming certificate;
\item $L$ is the displayed length ledger comparing the two histories by their finite step counts;
\item $Z$ is the standard-boundary row asserting that the unary read and the zero-spine read have the same displayed length while remaining different BEDC carrier predicates;
\item $H$ stores componentwise $\hsame$ transports for the unary row, zero-spine row, length ledger, standard-boundary row, and local name;
\item $C$ stores the displayed $\Cont$ routes that read the unary spine, read the zero spine, expose the length ledger, and hand the boundary row to downstream bridge consumers;
\item $P$ records $\Pkg$ provenance over $\NatUp$, $\AxisNatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $R$ is the local $\NameCert_{\AxisUnarySpineNormalizerUp}$ row.
\end{enumerate}
The carrier has no coordinate that identifies $\NatUp$ with $\AxisNatUp$, rewrites $\Eone$ constructors into $\Ezero$ constructors inside the kernel, or imports a host arithmetic normalizer.
\end{definition}

\begin{theorem}[AxisUnarySpineNormalizer NameCert obligations]
\label{thm:axis-unary-spine-normalizer-namecert-obligations}
The local $\NameCert_{\AxisUnarySpineNormalizerUp}$ surface for \autoref{def:axis-unary-spine-normalizer-carrier} consists exactly of source unary-spine admission, target zero-spine admission, displayed length-ledger readback, standard-boundary exposure, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and the local naming row. These obligations assemble a finite bridge-facing packet over $\NatUp$, $\AxisNatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ without equating the unary and axis carriers.
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed packet $U$. The rows $N$ and $A$ give the two named source surfaces, while $L$ and $Z$ give the finite comparison and the standard-boundary read.

The classifier is componentwise. The stored $\hsame$ row $H$ transports the unary read, zero-spine read, length ledger, boundary row, package row, and local name without replacing either carrier by the other.

The continuation and provenance clauses are the remaining finite obligations. The routes in $C$ expose the two spine reads and then pass the length ledger into $Z$, while $P$ records that every row belongs to the listed BEDC dependencies. No host normalizer or carrier identity has a coordinate in the packet.
\end{proof}

\begin{theorem}[AxisUnarySpineNormalizer standard boundary]
\label{thm:axis-unary-spine-normalizer-standard-boundary}
Every accepted $\AxisUnarySpineNormalizerUp$ carrier exposes a length-preserving standard-boundary row from its $\NatUp$ unary spine to its $\AxisNatUp$ zero spine. Downstream uses of the unary-direction bridge may read this row through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates, but they may not treat the source and target carrier predicates as equal inside the BEDC kernel.
\end{theorem}
\leanchecked{BEDC.Derived.AxisUnarySpineNormalizerUp.AxisUnarySpineNormalizerTasteGate\_single\_carrier\_alignment}
\begin{proof}
Start with an accepted carrier $U=(N,A,L,Z,H,C,P,R)$. By \autoref{thm:axis-unary-spine-normalizer-namecert-obligations}, every consumer-facing read of $U$ factors through the displayed rows of \autoref{def:axis-unary-spine-normalizer-carrier}.

The standard-boundary coordinate is $Z$. Its input data are the unary row $N$, the zero-spine row $A$, and the length ledger $L$, and its public route is one of the continuation rows in $C$.

The non-identification boundary is part of the same finite packet. Since neither $N$ nor $A$ is replaced by a shared carrier coordinate, the bridge exports a length-preserving standard boundary while preserving the kernel distinction between the two spine predicates.
\end{proof}

\closureat{AxisUnarySpineNormalizerUp}{seedStr}

\begin{closurestatus}{\AxisUnarySpineNormalizerUp}
  \constructivestory{An $\AxisUnarySpineNormalizerUp$ packet is generated from a $\NatUp$ unary-spine row, an $\AxisNatUp$ zero-spine row, a displayed length ledger, a standard-boundary row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:axis-unary-spine-normalizer-carrier}, \autoref{thm:axis-unary-spine-normalizer-namecert-obligations}, and \autoref{thm:axis-unary-spine-normalizer-standard-boundary} bind the finite unary-to-zero-spine normalizer boundary without identifying the source and target carriers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean formalization, bridge checking, kernel equality between $\NatUp$ and $\AxisNatUp$, host arithmetic normalization, or a public additive isomorphism.}
  \upgradepath{Obligation closure requires checked carrier admission, length-ledger readback, transport stability, and standard-boundary export for the same finite packet.}
\end{closurestatus}
