\chapter{A Concrete Naming Certificate for $\FullAxisRealRefusalUp$}
\label{ch:concrete-instances-fullaxisrealrefusal-namecert}
\origin{ai}

The $\FullAxisRealRefusalUp$ surface packages the AxisZeckendorf refusal that a $\FullAxisUp$ structural seal may be read as $\RealUp$. It is a finite certificate over already visible seal, refusal, transport, continuation, provenance, and naming rows. It exports no $\RealUp$ algebraic operation, no Cauchy completion, and no host limit.

\begin{definition}[FullAxis-to-Real refusal carrier]
\label{def:fullaxis-real-refusal-carrier}
A $\FullAxisRealRefusalUp$ carrier is a finite $\BHist$ packet
$$
Q=(F,R,C,H,T,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $F$ is the $\FullAxisUp$ structural-seal inventory, namely the prefix-thread carrier, source, pattern, classifier, stability, ledger, finite boundary marker, and public seal-name rows of \autoref{ch:concrete-instances-full-axis-seal-namecert};
\item $R$ is the Real-facing refusal row, citing the fact that $\FullAxisUp$ does not entail the Cauchy, limit-uniqueness, field, compactness, metric-completion, or selected-limit operations of $\RealUp$;
\item $C$ is the AxisZeckendorf cannot-claim row for the $\FullAxisUp$ as $\RealUp$ horizon, including the boundary refusal of \autoref{thm:cannot-claim-fullAxis-is-real-horizon};
\item $H$ records the displayed $\hsame$ transports for the structural seal row, the Real-facing refusal row, the cannot-claim row, the package row, and the local naming row;
\item $T$ records the displayed $\Cont$ routes by which consumers may read the seal inventory and replay the refusal without producing a positive $\RealUp$ bridge;
\item $P$ is the $\Pkg$ provenance over $\FullAxisUp$, $\AxisZeckendorfCannotClaimUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and the source $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\FullAxisRealRefusalUp}$ row.
\end{enumerate}
The carrier has no coordinate for addition, multiplication, order, Cauchy convergence, limit uniqueness, completeness, compactness, a quotient of histories, or host equality.
\end{definition}
\leanchecked{BEDC.Derived.FullAxisRealRefusalUp.FullAxisRealRefusalTasteGate\_single\_carrier\_alignment}

\begin{theorem}[FullAxis-to-Real refusal NameCert obligations]
\label{thm:fullaxis-real-refusal-namecert-obligations}
The local $\NameCert_{\FullAxisRealRefusalUp}$ surface for \autoref{def:fullaxis-real-refusal-carrier} consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the packet $Q=(F,R,C,H,T,P,N)$;
\item structural-seal coverage for the prefix-thread, boundary-finite, source-exhaustion, Real-route-separation, and seal-name rows collected in $F$;
\item refusal coverage for the Real-facing row $R$ and the AxisZeckendorf cannot-claim row $C$;
\item transport and continuation exactness for the displayed $\hsame$ rows $H$ and $\Cont$ routes $T$;
\item ledger non-escape through the $\Pkg$ provenance row $P$ and local $\NameCert$ row $N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:fullaxis-real-refusal-carrier}. The admitted packet has exactly seven visible rows, so every later read starts from $F,R,C,H,T,P,N$.

Structural-seal coverage is supplied by the first row. The row $F$ names the prefix-thread carrier, finite boundary marker, source-exhaustion statement, Real-route separation statement, and public seal-name alignment from the $\FullAxisUp$ chapter.

Refusal coverage is supplied by $R$ and $C$. The row $R$ records the missing $\RealUp$ operations, while $C$ points to the AxisZeckendorf cannot-claim horizon for the same boundary.

Transport and continuation exactness are the rows $H$ and $T$. They move only displayed refusal and seal rows, and therefore cannot turn the refusal into an algebraic or completion operation.

Finally, $P$ and $N$ record package provenance and the local naming ledger. Since none of the excluded $\RealUp$ operations is a coordinate of the packet, the NameCert surface is exhausted by the five displayed obligations.
\end{proof}

\begin{theorem}[FullAxis-to-Real refusal non-escape]
\label{thm:fullaxis-real-refusal-non-escape}
Every public read exported by an accepted $\FullAxisRealRefusalUp$ packet factors through the rows $F,R,C,H,T,P,N$. In particular, no consumer can extract a $\RealUp$ addition, multiplication, order, Cauchy convergence proof, limit-uniqueness proof, completeness row, compactness row, selected host limit, quotient stream, or host equality from the packet.
\end{theorem}
\begin{proof}
Inspect the packet coordinates. The structural-seal row $F$ exposes only the $\FullAxisUp$ prefix-thread and finite-boundary surface, while the rows $R$ and $C$ expose refusal data.

The transport and continuation rows $H$ and $T$ preserve those displayed rows componentwise. A transported refusal remains a refusal row, and a transported structural-seal read remains a read of the same prefix-thread inventory.

The provenance and naming rows $P$ and $N$ do not add mathematical operations. Because no coordinate contains a $\RealUp$ algebraic operation, completion operation, quotient stream, selected limit, or host equality, no public read can export one.
\end{proof}

\begin{theorem}[FullAxis-to-Real refusal vision concretization]
\label{thm:fullaxis-real-refusal-vision-concretization}
The AxisZeckendorf cannot-claim boundary for $\FullAxisUp$ as $\RealUp$ is realized by the finite $\FullAxisRealRefusalUp$ packet of \autoref{def:fullaxis-real-refusal-carrier}. The realization cites $\FullAxisUp$ structural-seal rows, Real-facing refusal rows, AxisZeckendorf cannot-claim rows, displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row, while exporting no $\RealUp$ operation.
\end{theorem}
\begin{proof}
Start from the cannot-claim theorem \autoref{thm:cannot-claim-fullAxis-is-real-horizon}. It supplies the boundary statement that the AxisZeckendorf cluster does not assert $\RealUp$ field operations on $\FullAxisUp$.

The carrier of \autoref{def:fullaxis-real-refusal-carrier} turns that boundary into finite rows. The row $F$ records the $\FullAxisUp$ seal surface, $R$ records the Real-facing refusal, and $C$ records the AxisZeckendorf horizon row.

Rows $H,T,P,N$ provide the admissible transport, continuation, package, and local naming surface. By \autoref{thm:fullaxis-real-refusal-non-escape}, this realization cannot be read as a positive $\RealUp$ bridge, so it concretizes the vision boundary as a finite refusal certificate.
\end{proof}

\closureat{FullAxisRealRefusalUp}{seedStr}

\begin{closurestatus}{\FullAxisRealRefusalUp}
  \constructivestory{A $\FullAxisRealRefusalUp$ packet is generated from FullAxis structural-seal rows, Real-facing refusal rows, the AxisZeckendorf cannot-claim horizon, displayed hsame transports, continuation routes, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the carrier, NameCert obligations, non-escape boundary, and AxisZeckendorf vision concretization for finite FullAxis-to-Real refusal packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close a RealUp bridge, RealUp algebraic operations for FullAxisUp, Cauchy completion, compactness, quotient streams, selected host limits, or host equality.}
  \upgradepath{Obligation closure requires checked carrier coverage, refusal-row coverage, transport exactness, continuation exactness, and ledger non-escape for the displayed packet.}
\end{closurestatus}
