\chapter{A Finite Value-Preservation Certificate for $\ZeckendorfCarryValueUp$}
\label{ch:concrete-instances-zeckendorf-carry-value-namecert}
\origin{ai}

The $\ZeckendorfCarryValueUp$ surface packages the Fibonacci value reading of the displayed Zeckendorf carry as a finite $\NameCert$ packet. It keeps the carry classifier separate from history sameness: the packet records the source and target windows, the carry row, the two Fibonacci value rows, the equality-of-value check, and the visible provenance needed by consumers.

The dependency anchors are $\ZCarryUp$, $\ZeckendorfNormalUp$, $\BHist$, $\HSame$, $\Cont$, $\Pkg$, $\NameCert$, and the displayed words of \autoref{def:axiszeckendorf-display-words}.

\begin{definition}[Zeckendorf carry-value carrier]
\label{def:zeckendorf-carry-value-carrier}
A $\ZeckendorfCarryValueUp$ carrier is a finite $\BHist$ packet
$$
V=(h,k,G,N_h,N_k,F,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $h=\mathtt{word\_011}$ is the displayed source carry window;
\item $k=\mathtt{word\_100}$ is the displayed target carry window;
\item $G$ is the local carry row $\mathsf{ZCarry}(h,k)$ inherited from $\ZCarryUp$;
\item $N_h$ records the source normality boundary, namely that $h$ is rejected by the $\ZeckendorfNormalUp$ normal-form classifier;
\item $N_k$ records the target normality boundary, namely that $k$ is accepted by the $\ZeckendorfNormalUp$ normal-form classifier;
\item $F$ records the finite Fibonacci value calculation for the two displayed windows and the equality of those two values;
\item $H$ records the negative history-sameness boundary $\neg\HSame(h,k)$ together with the displayed same-side transports allowed for consumers;
\item $C$ records the $\Cont$ routes from the carry row to the value calculation and from the value calculation to the public read;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\ZCarryUp$, $\ZeckendorfNormalUp$, $\HSame$, and the finite Fibonacci value rows;
\item $N$ is the local $\NameCert_{\ZeckendorfCarryValueUp}$ row.
\end{enumerate}
The classifier compares accepted packets through the carry row, the two value rows, and the listed provenance. It does not identify $h$ and $k$ by $\HSame$, install a kernel rewrite, or export a host-level quotient of histories.
\end{definition}
\leanchecked{BEDC.Derived.ZeckendorfCarryValueUp.ZeckendorfCarryValueTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Zeckendorf carry-value non-$\HSame$ boundary]
\label{thm:zeckendorf-carry-value-non-hsame-boundary}
For every accepted $\ZeckendorfCarryValueUp$ packet $V=(h,k,G,N_h,N_k,F,H,C,P,N)$, the value-preservation row and the history-sameness boundary occupy distinct coordinates. The row $F$ states that the displayed Fibonacci value of $h$ equals the displayed Fibonacci value of $k$, while $H$ records $\neg\HSame(h,k)$. Thus value preservation is a finite classifier-facing calculation, not a kernel identification of the two histories.
\end{theorem}
\leanchecked{BEDC.Derived.ZeckendorfCarryValueUp.ZeckendorfCarryValueNonHsameBoundary}
\begin{proof}
Project the carry row $G$ and the normality rows $N_h,N_k$. They fix the displayed source as $\mathtt{word\_011}$ and the displayed target as $\mathtt{word\_100}$ with the same orientation as the $\ZCarryUp$ packet.

Next project the value row $F$. It reads the finite Fibonacci value calculation for exactly those two displayed words and records equality of the computed values.

Finally project the boundary row $H$. Since $H$ records the negative $\HSame$ fact for the same source and target, the equality in $F$ cannot be read as a history-sameness witness. The public read therefore separates value preservation from kernel history identification.
\end{proof}

\begin{theorem}[Zeckendorf carry-value NameCert package]
\label{thm:zeckendorf-carry-value-namecert-package}
The rows of \autoref{def:zeckendorf-carry-value-carrier} form a finite $\NameCert_{\ZeckendorfCarryValueUp}$ package. Its obligations are carrier habitation, carry-generator orientation, source and target normality boundaries, finite Fibonacci value calculation, non-$\HSame$ separation, continuation routing, package provenance, and the local naming row. Every consumer-visible value-preservation read factors through
$$
h,k,G,N_h,N_k,F,H,C,P,N.
$$
No quotient stream, host arithmetic oracle, global normalization procedure, kernel rewrite, or source-target $\HSame$ proof is exported.
\end{theorem}
\leanchecked{BEDC.Derived.ZeckendorfCarryValueUp.ZeckendorfCarryValueCarrier\_namecert\_package}
\begin{proof}
Carrier habitation is the displayed packet of \autoref{def:zeckendorf-carry-value-carrier}. The packet stores the two windows, the carry row, the normality boundary rows, the value calculation, and the provenance rows in a single finite history surface.

The carry-generator orientation is read from $G$, while $N_h$ and $N_k$ supply the source rejection and target admission rows. These coordinates determine which finite words are sent to the value calculation.

The value-preservation read is then routed through $F$ and $C$. The row $F$ stores the two displayed Fibonacci value computations and their equality check, and $C$ records that consumers reach the public value row only along the carrier route.

The non-escape clauses are the remaining projections. The row $H$ prevents the value equality from becoming $\HSame(h,k)$, while $P$ and $N$ account for provenance and naming. Since none of the excluded objects is a coordinate of the packet, no consumer can extract it from the package.
\end{proof}

\begin{theorem}[Zeckendorf carry-value vision realization]
\label{thm:zeckendorf-carry-value-vision-realization}
The finite packet $V=(h,k,G,N_h,N_k,F,H,C,P,N)$ realizes the Fibonacci value-preservation reading of the displayed carry row as a concrete $\ZeckendorfCarryValueUp$ NameCert surface. It extends the carry classifier by adding the value row $F$ and its consumer route, while preserving the boundary that carry-relatedness and history sameness are different judgments.
\end{theorem}
\leanchecked{BEDC.Derived.ZeckendorfCarryValueUp.ZeckendorfCarryValueCarrier\_value\_public\_read}
\leanchecked{BEDC.Derived.ZeckendorfCarryValueUp.ZeckendorfCarryValueVisionRealization}
\begin{proof}
Start from the displayed $\ZCarryUp$ carrier. Its source, target, carry row, source rejection, target admission, and non-$\HSame$ boundary provide the rows $h,k,G,N_h,N_k,H$.

Add the finite value row $F$ for the two displayed words and route it through $C$. This supplies a consumer-facing value-preservation check without changing the carry generator or the normal-form classifier.

Package the resulting rows with $P$ and $N$. The package exposes value preservation only through the finite NameCert surface, so the existing separation between carry-relatedness and history sameness remains part of the public contract.
\end{proof}

\begin{theorem}[Zeckendorf carry-value classifier dependency]
\label{thm:zeckendorf-carry-value-classifier-dependency}
Every accepted $\ZeckendorfCarryValueUp$ packet consumes the carry row, source and target windows, normality boundary rows, and non-$\HSame$ separation supplied by the carry classifier of \autoref{ch:concrete-instances-zeckendorf-carry-classifier-namecert} before it adds the Fibonacci value row. The value-preservation surface is therefore a finite row over the $\ZCarryUp$ classifier, not a replacement for that classifier.
\end{theorem}
\begin{proof}
Project the carrier $V=(h,k,G,N_h,N_k,F,H,C,P,N)$ from \autoref{def:zeckendorf-carry-value-carrier}. The rows $h,k,G,N_h,N_k,H$ are the carry-side data: the two displayed windows, the carry row, the source and target normality boundaries, and the public separation from $\HSame$.

Use the local non-$\HSame$ boundary and NameCert package, \autoref{thm:zeckendorf-carry-value-non-hsame-boundary} and \autoref{thm:zeckendorf-carry-value-namecert-package}. They keep the value surface tied to the carry classifier while preventing the finite value equality from becoming a source-target history-sameness proof.

The additional row is $F$, routed through $C$ and recorded with $P$ and $N$. Thus the accepted packet first cites the sibling carry classifier of \autoref{ch:concrete-instances-zeckendorf-carry-classifier-namecert} and then appends the finite Fibonacci value-preservation row over that cited carrier.
\end{proof}
\leanchecked{BEDC.Derived.ZeckendorfCarryValueUp.ZeckendorfCarryValueUp\_classifier\_dependency\_rows}

\closureat{ZeckendorfCarryValueUp}{seedStr}

\begin{closurestatus}{\ZeckendorfCarryValueUp}
  \constructivestory{A $\ZeckendorfCarryValueUp$ packet records the displayed carry from $\mathtt{word\_011}$ to $\mathtt{word\_100}$, the finite Fibonacci value equality for those two words, the normality boundary rows, and the non-$\HSame$ separation row in one finite $\BHist$ certificate.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:zeckendorf-carry-value-carrier}, \autoref{thm:zeckendorf-carry-value-non-hsame-boundary}, \autoref{thm:zeckendorf-carry-value-namecert-package}, and \autoref{thm:zeckendorf-carry-value-vision-realization} bind the seed finite value-preservation packet over $\ZCarryUp$, $\ZeckendorfNormalUp$, $\BHist$, $\HSame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.ZeckendorfCarryValueUp.ZeckendorfCarryValueTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close a Lean implementation, a bridge certificate, a global Zeckendorf normalizer, uniqueness of numerical interpretation, a kernel rewrite, or source-target $\HSame$.}
  \upgradepath{Obligation closure requires checked carrier admission, finite value-row exactness, non-$\HSame$ preservation, continuation routing, and public non-escape for the displayed carry-value packet.}
\end{closurestatus}
