\begin{definition}[Opposite POSet certificate data]
\label{def:opposite-poset-certificate-data}
Let a $\POSetUp$ certificate be presented by a carrier predicate $\mathcal C$, classifier $\sim_C$, and relation $\le_C$. Define the opposite relation by
$$
a\le_C^{\mathrm{op}} b:=b\le_C a.
$$
The opposite POSet data $C^{\mathrm{op}}$ have the same carrier predicate $\mathcal C$, the same classifier $\sim_C$, and relation $\le_C^{\mathrm{op}}$. An antisymmetry ledger for $a\le_C^{\mathrm{op}} b$ and $b\le_C^{\mathrm{op}} a$ is the same pair of original comparison derivations, read as $b\le_C a$ and $a\le_C b$.
\end{definition}

\begin{theorem}[Opposite POSet certificate]
\label{thm:opposite-poset-certificate}
If $(\mathcal C,\sim_C,\le_C)$ satisfies the $\POSetUp$ certificate obligations of \autoref{def:poset-certificate-obligations}, then the data of \autoref{def:opposite-poset-certificate-data} also satisfy the $\POSetUp$ certificate obligations. Thus the same carrier and classifier carry a POSet certificate with relation $\le_C^{\mathrm{op}}$.
\end{theorem}
\begin{proof}
Unpack the given package through \autoref{def:poset-certificate-obligations}. By \autoref{prop:poset-forgets-preorder-certificate}, it has a $\PreorderUp$ reduct with the same carrier predicate $\mathcal C$, classifier $\sim_C$, and relation $\le_C$. Applying \autoref{thm:opposite-preorder-certificate} to that reduct supplies the carrier, source, preorder pattern, classifier, preorder stability rows, and preorder ledger for the relation $\le_C^{\mathrm{op}}$ of \autoref{def:opposite-poset-certificate-data}.

It remains to supply the partial-order rows of \autoref{def:poset-stability-certificate}. Let $a$ and $b$ be carried endpoints and suppose
$$
a\le_C^{\mathrm{op}} b
\qquad\text{and}\qquad
b\le_C^{\mathrm{op}} a.
$$
Unfolding the opposite relation gives $b\le_C a$ and $a\le_C b$. Applying the original antisymmetry field to the ordered pair $a\le_C b$ and $b\le_C a$ yields $a\sim_C b$, which is exactly the antisymmetry conclusion required for $\le_C^{\mathrm{op}}$.

The compatibility of antisymmetry with relation congruence is inherited in the same exchange of endpoints. Given classifier replacements $a\sim_C a'$ and $b\sim_C b'$, the opposite preorder relation-congruence row transports the two opposite comparisons to $a'\le_C^{\mathrm{op}} b'$ and $b'\le_C^{\mathrm{op}} a'$. Unfolding gives $b'\le_C a'$ and $a'\le_C b'$, and the original antisymmetry compatibility row applies to these transported original comparisons to produce $a'\sim_C b'$.

The source row of \autoref{def:poset-source-specification} is therefore a certified preorder carrier plus the antisymmetry field just proved. The pattern row of \autoref{def:poset-pattern-specification} is still preorder relation formation with classifier collapse from bidirectional comparison: a displayed pair of opposite comparisons is read as the same original pair with the two comparison derivations exchanged. The classifier row of \autoref{def:poset-classifier-specification} is unchanged because endpoint classification remains $\sim_C$.

Finally, the ledger row is \autoref{def:poset-ledger-policy}. It records both comparison derivations used by antisymmetry; under \autoref{def:opposite-poset-certificate-data}, those are exactly the original derivations $b\le_C a$ and $a\le_C b$ with the displayed slots exchanged. Hence the carrier, source, pattern, classifier, stability, and ledger rows satisfy \autoref{def:poset-certificate-obligations}, so $C^{\mathrm{op}}$ carries a $\POSetUp$ certificate.
\end{proof}

\begin{theorem}[Double opposite POSet certificate data identity]
\label{thm:double-opposite-poset-certificate-data-identity}
Let $D$ be a $\POSetUp$ certificate satisfying the obligations of
\autoref{def:poset-certificate-obligations}. Present its POSet data by a
carrier predicate $\mathcal C$, classifier $\sim_C$, order relation $\le_C$,
and antisymmetry ledger row $\mathcal L_C$ as in
\autoref{def:poset-ledger-policy}. Let
$D^{\mathrm{opop}}=(D^{\mathrm{op}})^{\mathrm{op}}$ be obtained by applying
\autoref{def:opposite-poset-certificate-data} twice. Then
$D^{\mathrm{opop}}$ is a $\POSetUp$ certificate, and its carrier predicate,
classifier, order relation, and antisymmetry ledger row are componentwise
identical to those of $D$: for carried endpoints $a,b$ and comparison
witnesses $p:a\le_C b$ and $q:b\le_C a$,
$$
\begin{aligned}
\mathcal C^{\mathrm{opop}}(a)&=\mathcal C(a),&
a\sim_C^{\mathrm{opop}}b&=a\sim_C b,\\
a\le_C^{\mathrm{opop}}b&=a\le_C b,&
\mathcal L_C^{\mathrm{opop}}(a,b;p,q)&=\mathcal L_C(a,b;p,q).
\end{aligned}
$$
Here $\mathcal L_C(a,b;p,q)$ denotes the ledger entry that records the
ordered antisymmetry pair $p,q$.
\end{theorem}
\begin{proof}
Because $D$ satisfies the $\POSetUp$ obligations,
\autoref{thm:opposite-poset-certificate} makes $D^{\mathrm{op}}$ a certified
$\POSetUp$ instance. Applying the same theorem to that certified opposite data
makes $D^{\mathrm{opop}}$ a certified $\POSetUp$ instance.

It remains to compare the displayed data. For the carrier predicate and
classifier, two unfoldings of \autoref{def:opposite-poset-certificate-data}
give
$$
\mathcal C^{\mathrm{opop}}(a)=\mathcal C^{\mathrm{op}}(a)=\mathcal C(a)
$$
and
$$
a\sim_C^{\mathrm{opop}}b=a\sim_C^{\mathrm{op}}b=a\sim_C b.
$$

For the order relation, the two reversals cancel:
$$
a\le_C^{\mathrm{opop}}b
=b\le_C^{\mathrm{op}}a
=a\le_C b.
$$
Thus the double opposite order field is exactly the original order field.

For the ledger row, \autoref{def:opposite-poset-certificate-data} says one
opposite keeps the same two antisymmetry derivations and exchanges their
displayed source and target slots. Hence the first opposite reads the ordered
ledger entry for $(a,b;p,q)$ in the exchanged slots, and the second opposite
performs the same exchange again. The endpoints and the two comparison slots
are restored to $(a,b;p,q)$, so
$\mathcal L_C^{\mathrm{opop}}(a,b;p,q)=\mathcal L_C(a,b;p,q)$.

The certified status and the four displayed component identities therefore
identify the double opposite POSet data with the original POSet data.
\end{proof}

\begin{theorem}[POSet finite-chain carrier closure]
\label{thm:poset-finite-chain-carrier-closure}
Let
$$
h=h_0,\ h_1,\ldots,h_n=k
$$
be a finite chain of carried unary-prefix histories in the concrete
$\POSetUp$ source of \autoref{def:concrete-unary-prefix-poset-instance}. If
each adjacent comparison $h_i\leq h_{i+1}$ is recorded by
$\mathsf{PreorderPrefixLE}$ in the finite $\Cont$ ledger, then every endpoint
$h_i$ in the chain remains inside
$\mathsf{PreorderCarrier}=\mathsf{UnaryHistory}$, and the composite comparison
from $h$ to $k$ is again a carried unary-prefix comparison recorded by that
finite ledger.
\end{theorem}
\begin{proof}
Argue by induction on the finite chain. The base chain has only the carried
endpoint $h$, so carrier closure is immediate from the displayed source row.

For the step, assume the prefix subchain from $h$ to $h_i$ has already stayed
inside $\mathsf{UnaryHistory}$ and has produced a carried composite comparison.
The adjacent row $h_i\leq h_{i+1}$ is a displayed
$\mathsf{PreorderPrefixLE}$ comparison between carried histories, so the
prefix transitivity row cited in
\autoref{thm:concrete-unary-prefix-poset-namecert} composes it with the
subchain comparison.

The same finite $\Cont$ ledger records the old subchain, the new adjacent
comparison, and their composite. Thus the next endpoint remains in
$\mathsf{PreorderCarrier}$ and the chain closes inside the concrete unary
prefix carrier.
\end{proof}

\begin{theorem}[POSet finite-chain antisymmetry collapse]
\label{thm:poset-finite-chain-antisymmetry-collapse}
Let $h$ and $k$ be carried unary-prefix histories. If the finite $\Cont$ ledger
records a finite $\mathsf{PreorderPrefixLE}$ chain from $h$ to $k$ and another
finite $\mathsf{PreorderPrefixLE}$ chain from $k$ to $h$, then the two endpoints
collapse to the carrier classifier:
$$
\mathsf{PreorderCarrier}(h)\wedge\mathsf{PreorderCarrier}(k)
\wedge h\leq k\wedge k\leq h
\Longrightarrow \hsame(h,k).
$$
\end{theorem}
\begin{proof}
First apply \autoref{thm:poset-finite-chain-carrier-closure} to the chain from
$h$ to $k$. It gives a carried composite comparison $h\leq k$ recorded by the
finite ledger.

Apply the same closure theorem to the reverse chain from $k$ to $h$. This
gives the carried composite comparison $k\leq h$ over the same unary-prefix
carrier.

Now apply \autoref{thm:poset-prefix-antisymmetry} to the opposing composite
prefix comparisons. The result is $\hsame(h,k)$, and
\autoref{thm:poset-prefix-classifier-exactness} identifies this history
sameness with the carrier classifier on the displayed unary-prefix endpoints.
\end{proof}

\begin{theorem}[POSet finite-chain NameCert surface]
\label{thm:poset-finite-chain-namecert-surface}
The finite-chain carrier closure of
\autoref{thm:poset-finite-chain-carrier-closure} and the finite-chain
antisymmetry collapse of
\autoref{thm:poset-finite-chain-antisymmetry-collapse} package as a
$\POSetUp$ $\NameCert$ obligation surface. Its rows are exactly the concrete
unary-prefix carrier, the $\hsame$ classifier, the
$\mathsf{PreorderPrefixLE}$ relation, prefix stability under finite
composition, the finite $\Cont$ ledger for adjacent and composite comparisons,
and the exactness row of
\autoref{thm:poset-prefix-classifier-exactness}. It adds no quotient carrier,
opposite presentation, totality field, lattice operation, or standard bridge.
\end{theorem}
\begin{proof}
Project the concrete unary-prefix certificate of
\autoref{thm:concrete-unary-prefix-poset-namecert}. It supplies the carrier,
classifier, relation, stability, ledger, and exactness rows for the
$\POSetUp$ surface.

The finite-chain carrier row is supplied by
\autoref{thm:poset-finite-chain-carrier-closure}. Its induction uses only
prefix transitivity and finite $\Cont$ composition already present in the
certificate ledger.

The finite-chain antisymmetry row is supplied by
\autoref{thm:poset-finite-chain-antisymmetry-collapse}. It reduces two finite
chains to opposing composite prefix comparisons, applies
\autoref{thm:poset-prefix-antisymmetry}, and then reads the result through
\autoref{thm:poset-prefix-classifier-exactness}.

Repacking these rows with the source certificate gives a single
$\POSetUp$ NameCert obligation surface. Since every row is drawn from the
concrete unary-prefix packet and its finite ledger, no additional order
structure or bridge datum is exported.
\end{proof}
