\begin{proposition}[$\POSetUp$ forgets to $\PreorderUp$ certificate]
\label{prop:poset-forgets-preorder-certificate}
Let $C$ carry a $\POSetUp(C)$ certificate with classifier $\sim_C$ and relation $\le_C$. If the antisymmetry field and the compatibility data whose only role is to transport that antisymmetry field across relation congruence are omitted, the retained carrier, source, pattern, classifier, preorder stability fields, and ledger form a $\PreorderUp(C)$ certificate. The carrier $C$, classifier $\sim_C$, and relation $\le_C$ are unchanged.
\end{proposition}
\begin{proof}
By \autoref{def:poset-certificate-obligations}, the given certificate supplies carrier, source, pattern, classifier, stability, and ledger data for $\POSetUp$. The construction keeps exactly the coordinates that do not require the partial-order antisymmetry clause.

By \autoref{def:poset-carrier}, a $\POSetUp$ carrier is a preorder setup together with antisymmetry under the carrier classifier. Removing the antisymmetry coordinate leaves the carrier, classifier, and relation data required by \autoref{def:preorder-carrier}. Hence $C$, $\sim_C$, and $\le_C$ are copied without replacement.

By \autoref{def:poset-source-specification}, the source is a certified preorder carrier plus an antisymmetry field. Omitting only the antisymmetry field leaves the source described in \autoref{def:preorder-source-specification}. By \autoref{def:poset-classifier-specification}, the classifier is the preorder carrier classifier, so it is exactly the classifier specified in \autoref{def:preorder-classifier-specification}.

By \autoref{def:poset-pattern-specification}, the pattern is preorder relation formation together with classifier collapse from bidirectional comparison. Retaining the one-direction judgment formation $a\le_C b$ and suppressing only the bidirectional-collapse rule leaves the relational judgment formation of \autoref{def:preorder-pattern-specification}.

By \autoref{def:poset-stability-certificate}, the first stability component is all preorder stability fields. These are precisely the classifier reflexivity, classifier transitivity, preorder reflexivity, preorder transitivity, and relation-congruence rows listed in \autoref{def:preorder-stability-certificate}. The remaining $\POSetUp$ rows, namely antisymmetry and compatibility of antisymmetry with relation congruence, are not obligations for $\PreorderUp$. Relation congruence itself is retained because it belongs to the preorder stability component.

Finally, \autoref{def:preorder-ledger-policy} asks for the compared carrier witnesses and the relation derivation. The $\POSetUp$ ledger of \autoref{def:poset-ledger-policy} adds the paired comparison record only when antisymmetry is used. With that antisymmetry use omitted, the remaining comparison provenance is the preorder ledger for the same relation $\le_C$.

The retained carrier, source, pattern, classifier, stability, and ledger fields are therefore exactly the obligations named in \autoref{def:preorder-certificate-obligations}, giving a $\PreorderUp(C)$ certificate with unchanged carrier, classifier, and relation.
\end{proof}

\begin{definition}[Preorder quotient presentation]
\label{def:preorder-quotient-presentation}
Let $(C,\sim_C,\le_C)$ be a $\PreorderUp$ package satisfying the carrier and stability fields of \autoref{def:preorder-carrier} and \autoref{def:preorder-stability-certificate}. On carried representatives define
$$
x\approx_C y :\Longleftrightarrow x\le_C y\land y\le_C x.
$$
Let $q:C\to C_{\!\approx}$ be the class map for $\approx_C$, and write $\overline{x}:=q(x)$. The quotient carrier is $C_{\!\approx}$. Its induced order and quotient classifier are
$$
\overline{x}\le_Q\overline{y} :\Longleftrightarrow x\le_C y,
\qquad
\overline{x}\sim_Q\overline{y} :\Longleftrightarrow x\approx_C y.
$$
\end{definition}

\begin{theorem}[Preorder quotient yields $\PosetUp$]
\label{thm:preorder-quotient-yields-poset}
Let $(C,\sim_C,\le_C)$ supply the carrier, classifier, relation, stability, and ledger fields of a $\PreorderUp$ certificate as in \autoref{def:preorder-certificate-obligations}. For the quotient presentation of \autoref{def:preorder-quotient-presentation}, $\approx_C$ is an equivalence relation on carried representatives, the induced order $\le_Q$ is independent of representatives, and $(C_{\!\approx},\sim_Q,\le_Q)$ supplies the $\POSetUp$ certificate obligations for the quotient partial order. Its classifier is exact on classes:
$$
\overline{x}\sim_Q\overline{y}
\Longleftrightarrow
x\approx_C y
\Longleftrightarrow
(x\le_C y\land y\le_C x).
$$
\end{theorem}
\begin{proof}
The preorder stability fields in \autoref{def:preorder-stability-certificate} give reflexivity and transitivity of $\le_C$ on carried representatives. Reflexivity of $\approx_C$ follows by pairing two copies of $x\le_C x$. Symmetry follows by exchanging the two comparison witnesses. For transitivity, assume $x\approx_C y$ and $y\approx_C z$. The forward comparison $x\le_C z$ is obtained by composing $x\le_C y$ with $y\le_C z$, and the reverse comparison $z\le_C x$ is obtained by composing $z\le_C y$ with $y\le_C x$. Hence $\approx_C$ is an equivalence relation.

The induced order is representative-independent. Suppose $x\approx_C x'$, $y\approx_C y'$, and $x\le_C y$. The reverse half of $x\approx_C x'$ gives $x'\le_C x$, so transitivity gives $x'\le_C y$. The forward half of $y\approx_C y'$ gives $y\le_C y'$, so another use of transitivity gives $x'\le_C y'$. Thus $\overline{x}\le_Q\overline{y}$ implies $\overline{x'}\le_Q\overline{y'}$ under replacement of representatives. Taking one representative fixed gives the two one-sided relation-congruence rows.

The quotient classifier is also representative-independent because $\approx_C$ is an equivalence relation: from $x\approx_C x'$ and $y\approx_C y'$, transitivity and symmetry give $x\approx_C y$ exactly when $x'\approx_C y'$. Therefore $\sim_Q$ is a well-defined classifier on $C_{\!\approx}$, and unfolding its definition gives the displayed exactness equivalence.

The $\POSetUp$ laws follow directly. Reflexivity of $\le_Q$ is the reflexivity of $\le_C$ on any representative. Transitivity of $\le_Q$ is the transitivity of $\le_C$ after unfolding the two induced comparisons. For antisymmetry, if $\overline{x}\le_Q\overline{y}$ and $\overline{y}\le_Q\overline{x}$, then $x\le_C y$ and $y\le_C x$, hence $x\approx_C y$, and therefore $\overline{x}\sim_Q\overline{y}$ by the quotient classifier.

The source row is the quotient carrier $C_{\!\approx}$, the pattern row is $\le_Q$ as in \autoref{def:poset-pattern-specification}, and the classifier row is $\sim_Q$ as in \autoref{def:poset-classifier-specification}. The stability rows required by \autoref{def:poset-stability-certificate} are the quotient reflexivity, transitivity, relation congruence, and antisymmetry just proved. The ledger of \autoref{def:poset-ledger-policy} records the two representatives and, when antisymmetry is invoked, the two induced comparisons. These are exactly the fields listed in \autoref{def:poset-certificate-obligations}, so the quotient presentation supplies the stated $\POSetUp$ certificate and hence the $\PosetUp$ quotient presentation.
\end{proof}

\begin{definition}[Opposite POSet certificate data]
\label{def:opposite-poset-certificate-data}
Let a $\POSetUp$ certificate be presented by a carrier predicate $\mathcal C$, classifier $\sim_C$, and relation $\le_C$. Define the opposite relation by
$$
a\le_C^{\mathrm{op}} b:=b\le_C a.
$$
The opposite POSet data $C^{\mathrm{op}}$ have the same carrier predicate $\mathcal C$, the same classifier $\sim_C$, and relation $\le_C^{\mathrm{op}}$. An antisymmetry ledger for $a\le_C^{\mathrm{op}} b$ and $b\le_C^{\mathrm{op}} a$ is the same pair of original comparison derivations, read as $b\le_C a$ and $a\le_C b$.
\end{definition}

\begin{theorem}[Opposite POSet certificate]
\label{thm:opposite-poset-certificate}
If $(\mathcal C,\sim_C,\le_C)$ satisfies the $\POSetUp$ certificate obligations of \autoref{def:poset-certificate-obligations}, then the data of \autoref{def:opposite-poset-certificate-data} also satisfy the $\POSetUp$ certificate obligations. Thus the same carrier and classifier carry a POSet certificate with relation $\le_C^{\mathrm{op}}$.
\end{theorem}
\begin{proof}
Unpack the given package through \autoref{def:poset-certificate-obligations}. By \autoref{prop:poset-forgets-preorder-certificate}, it has a $\PreorderUp$ reduct with the same carrier predicate $\mathcal C$, classifier $\sim_C$, and relation $\le_C$. Applying \autoref{thm:opposite-preorder-certificate} to that reduct supplies the carrier, source, preorder pattern, classifier, preorder stability rows, and preorder ledger for the relation $\le_C^{\mathrm{op}}$ of \autoref{def:opposite-poset-certificate-data}.

It remains to supply the partial-order rows of \autoref{def:poset-stability-certificate}. Let $a$ and $b$ be carried endpoints and suppose
$$
a\le_C^{\mathrm{op}} b
\qquad\text{and}\qquad
b\le_C^{\mathrm{op}} a.
$$
Unfolding the opposite relation gives $b\le_C a$ and $a\le_C b$. Applying the original antisymmetry field to the ordered pair $a\le_C b$ and $b\le_C a$ yields $a\sim_C b$, which is exactly the antisymmetry conclusion required for $\le_C^{\mathrm{op}}$.

The compatibility of antisymmetry with relation congruence is inherited in the same exchange of endpoints. Given classifier replacements $a\sim_C a'$ and $b\sim_C b'$, the opposite preorder relation-congruence row transports the two opposite comparisons to $a'\le_C^{\mathrm{op}} b'$ and $b'\le_C^{\mathrm{op}} a'$. Unfolding gives $b'\le_C a'$ and $a'\le_C b'$, and the original antisymmetry compatibility row applies to these transported original comparisons to produce $a'\sim_C b'$.

The source row of \autoref{def:poset-source-specification} is therefore a certified preorder carrier plus the antisymmetry field just proved. The pattern row of \autoref{def:poset-pattern-specification} is still preorder relation formation with classifier collapse from bidirectional comparison: a displayed pair of opposite comparisons is read as the same original pair with the two comparison derivations exchanged. The classifier row of \autoref{def:poset-classifier-specification} is unchanged because endpoint classification remains $\sim_C$.

Finally, the ledger row is \autoref{def:poset-ledger-policy}. It records both comparison derivations used by antisymmetry; under \autoref{def:opposite-poset-certificate-data}, those are exactly the original derivations $b\le_C a$ and $a\le_C b$ with the displayed slots exchanged. Hence the carrier, source, pattern, classifier, stability, and ledger rows satisfy \autoref{def:poset-certificate-obligations}, so $C^{\mathrm{op}}$ carries a $\POSetUp$ certificate.
\end{proof}

\begin{theorem}[Double opposite POSet certificate data identity]
\label{thm:double-opposite-poset-certificate-data-identity}
Let $D$ be a $\POSetUp$ certificate satisfying the obligations of
\autoref{def:poset-certificate-obligations}. Present its POSet data by a
carrier predicate $\mathcal C$, classifier $\sim_C$, order relation $\le_C$,
and antisymmetry ledger row $\mathcal L_C$ as in
\autoref{def:poset-ledger-policy}. Let
$D^{\mathrm{opop}}=(D^{\mathrm{op}})^{\mathrm{op}}$ be obtained by applying
\autoref{def:opposite-poset-certificate-data} twice. Then
$D^{\mathrm{opop}}$ is a $\POSetUp$ certificate, and its carrier predicate,
classifier, order relation, and antisymmetry ledger row are componentwise
identical to those of $D$: for carried endpoints $a,b$ and comparison
witnesses $p:a\le_C b$ and $q:b\le_C a$,
$$
\begin{aligned}
\mathcal C^{\mathrm{opop}}(a)&=\mathcal C(a),&
a\sim_C^{\mathrm{opop}}b&=a\sim_C b,\\
a\le_C^{\mathrm{opop}}b&=a\le_C b,&
\mathcal L_C^{\mathrm{opop}}(a,b;p,q)&=\mathcal L_C(a,b;p,q).
\end{aligned}
$$
Here $\mathcal L_C(a,b;p,q)$ denotes the ledger entry that records the
ordered antisymmetry pair $p,q$.
\end{theorem}
\begin{proof}
Because $D$ satisfies the $\POSetUp$ obligations,
\autoref{thm:opposite-poset-certificate} makes $D^{\mathrm{op}}$ a certified
$\POSetUp$ instance. Applying the same theorem to that certified opposite data
makes $D^{\mathrm{opop}}$ a certified $\POSetUp$ instance.

It remains to compare the displayed data. For the carrier predicate and
classifier, two unfoldings of \autoref{def:opposite-poset-certificate-data}
give
$$
\mathcal C^{\mathrm{opop}}(a)=\mathcal C^{\mathrm{op}}(a)=\mathcal C(a)
$$
and
$$
a\sim_C^{\mathrm{opop}}b=a\sim_C^{\mathrm{op}}b=a\sim_C b.
$$

For the order relation, the two reversals cancel:
$$
a\le_C^{\mathrm{opop}}b
=b\le_C^{\mathrm{op}}a
=a\le_C b.
$$
Thus the double opposite order field is exactly the original order field.

For the ledger row, \autoref{def:opposite-poset-certificate-data} says one
opposite keeps the same two antisymmetry derivations and exchanges their
displayed source and target slots. Hence the first opposite reads the ordered
ledger entry for $(a,b;p,q)$ in the exchanged slots, and the second opposite
performs the same exchange again. The endpoints and the two comparison slots
are restored to $(a,b;p,q)$, so
$\mathcal L_C^{\mathrm{opop}}(a,b;p,q)=\mathcal L_C(a,b;p,q)$.

The certified status and the four displayed component identities therefore
identify the double opposite POSet data with the original POSet data.
\end{proof}

\begin{theorem}[POSet finite-chain carrier closure]
\label{thm:poset-finite-chain-carrier-closure}
Let
$$
h=h_0,\ h_1,\ldots,h_n=k
$$
be a finite chain of carried unary-prefix histories in the concrete
$\POSetUp$ source of \autoref{def:concrete-unary-prefix-poset-instance}. If
each adjacent comparison $h_i\leq h_{i+1}$ is recorded by
$\mathsf{PreorderPrefixLE}$ in the finite $\Cont$ ledger, then every endpoint
$h_i$ in the chain remains inside
$\mathsf{PreorderCarrier}=\mathsf{UnaryHistory}$, and the composite comparison
from $h$ to $k$ is again a carried unary-prefix comparison recorded by that
finite ledger.
\end{theorem}
\begin{proof}
Argue by induction on the finite chain. The base chain has only the carried
endpoint $h$, so carrier closure is immediate from the displayed source row.

For the step, assume the prefix subchain from $h$ to $h_i$ has already stayed
inside $\mathsf{UnaryHistory}$ and has produced a carried composite comparison.
The adjacent row $h_i\leq h_{i+1}$ is a displayed
$\mathsf{PreorderPrefixLE}$ comparison between carried histories, so the
prefix transitivity row cited in
\autoref{thm:concrete-unary-prefix-poset-namecert} composes it with the
subchain comparison.

The same finite $\Cont$ ledger records the old subchain, the new adjacent
comparison, and their composite. Thus the next endpoint remains in
$\mathsf{PreorderCarrier}$ and the chain closes inside the concrete unary
prefix carrier.
\end{proof}

\begin{theorem}[POSet finite-chain antisymmetry collapse]
\label{thm:poset-finite-chain-antisymmetry-collapse}
Let $h$ and $k$ be carried unary-prefix histories. If the finite $\Cont$ ledger
records a finite $\mathsf{PreorderPrefixLE}$ chain from $h$ to $k$ and another
finite $\mathsf{PreorderPrefixLE}$ chain from $k$ to $h$, then the two endpoints
collapse to the carrier classifier:
$$
\mathsf{PreorderCarrier}(h)\wedge\mathsf{PreorderCarrier}(k)
\wedge h\leq k\wedge k\leq h
\Longrightarrow \hsame(h,k).
$$
\end{theorem}
\begin{proof}
First apply \autoref{thm:poset-finite-chain-carrier-closure} to the chain from
$h$ to $k$. It gives a carried composite comparison $h\leq k$ recorded by the
finite ledger.

Apply the same closure theorem to the reverse chain from $k$ to $h$. This
gives the carried composite comparison $k\leq h$ over the same unary-prefix
carrier.

Now apply \autoref{thm:poset-prefix-antisymmetry} to the opposing composite
prefix comparisons. The result is $\hsame(h,k)$, and
\autoref{thm:poset-prefix-classifier-exactness} identifies this history
sameness with the carrier classifier on the displayed unary-prefix endpoints.
\end{proof}

\begin{theorem}[POSet finite-chain NameCert surface]
\label{thm:poset-finite-chain-namecert-surface}
The finite-chain carrier closure of
\autoref{thm:poset-finite-chain-carrier-closure} and the finite-chain
antisymmetry collapse of
\autoref{thm:poset-finite-chain-antisymmetry-collapse} package as a
$\POSetUp$ $\NameCert$ obligation surface. Its rows are exactly the concrete
unary-prefix carrier, the $\hsame$ classifier, the
$\mathsf{PreorderPrefixLE}$ relation, prefix stability under finite
composition, the finite $\Cont$ ledger for adjacent and composite comparisons,
and the exactness row of
\autoref{thm:poset-prefix-classifier-exactness}. It adds no quotient carrier,
opposite presentation, totality field, lattice operation, or standard bridge.
\end{theorem}
\begin{proof}
Project the concrete unary-prefix certificate of
\autoref{thm:concrete-unary-prefix-poset-namecert}. It supplies the carrier,
classifier, relation, stability, ledger, and exactness rows for the
$\POSetUp$ surface.

The finite-chain carrier row is supplied by
\autoref{thm:poset-finite-chain-carrier-closure}. Its induction uses only
prefix transitivity and finite $\Cont$ composition already present in the
certificate ledger.

The finite-chain antisymmetry row is supplied by
\autoref{thm:poset-finite-chain-antisymmetry-collapse}. It reduces two finite
chains to opposing composite prefix comparisons, applies
\autoref{thm:poset-prefix-antisymmetry}, and then reads the result through
\autoref{thm:poset-prefix-classifier-exactness}.

Repacking these rows with the source certificate gives a single
$\POSetUp$ NameCert obligation surface. Since every row is drawn from the
concrete unary-prefix packet and its finite ledger, no additional order
structure or bridge datum is exported.
\end{proof}
