\chapter{A Concrete Naming Certificate for $\CauchyDiagonalFusionUp$}
\label{ch:concrete-instances-cauchydiagonalfusion-namecert}
\origin{ai}

The $\CauchyDiagonalFusionUp$ packet is the finite naming certificate that joins the observation-budget route, the regular Cauchy witness schedule, and the schedule-fusion row before the $\RealUp$ diagonal seal is read. It presents one completion-facing handoff over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealObservationBudgetUp$, $\RegularCauchyWitnessScheduleUp$, $\RealScheduleFusionUp$, and $\RealUp$, while withholding quotient streams, host real equality, selected limits, and ambient completeness.

This fusion packet consumes the modulus-indexed witness-window route of \autoref{ch:concrete-instances-regularcauchywitnessschedule-namecert}: the row $W$ is not an independent schedule oracle, but the sibling witness-schedule carrier transported into the diagonal fusion route before the dyadic readback and $\RealUp$ seal are available.

\begin{definition}[Cauchy diagonal fusion carrier]
\label{def:cauchy-diagonal-fusion-carrier}
A $\CauchyDiagonalFusionUp$ carrier is a finite $\BHist$ packet
$$
F=(E,B,W,S,D,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the precision request row whose tolerance selects the diagonal observation;
\item $B$ is the $\RealObservationBudgetUp$ row exposing the finite stream windows, dyadic readbacks, regular-sequence handoffs, and real-seal boundary for $E$;
\item $W$ is the $\RegularCauchyWitnessScheduleUp$ row exposing the modulus-indexed witness window used by the diagonal read;
\item $S$ is the $\RealScheduleFusionUp$ row that locks the schedule, window ledger, regular-rational readback, and seal handoff into one route;
\item $D$ is the $\DyadicRatCoreUp$ readback row consumed by both the observation budget and the witness schedule;
\item $R$ is the $\RegSeqRatUp$ handoff row reached after the dyadic readback and before the real seal;
\item $L$ is the $\RealUp$ diagonal seal row exported to completion-facing consumers;
\item $H$ records componentwise $\hsame$ transports for $E,B,W,S,D,R,L$ and the structural rows;
\item $C$ records the displayed $\Cont$ routes from precision request to observation budget, witness schedule, schedule fusion, dyadic readback, regular-rational handoff, and diagonal seal;
\item $P$ is the $\Pkg$ provenance over the listed rows, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CauchyDiagonalFusionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient stream equality, host real equality, a selected completed limit, an unbounded schedule, or an ambient completeness principle.
\end{definition}
\leandef{BEDC.Derived.CauchyDiagonalFusionUp.CauchyDiagonalFusionUp}

\begin{theorem}[Cauchy diagonal fusion NameCert obligations]
\label{thm:cauchy-diagonal-fusion-namecert-obligations}
The local $\NameCert_{\CauchyDiagonalFusionUp}$ surface consists exactly of carrier admission for $F=(E,B,W,S,D,R,L,H,C,P,N)$, precision request exposure, $\RealObservationBudgetUp$ observation routing, $\RegularCauchyWitnessScheduleUp$ witness-window routing, $\RealScheduleFusionUp$ schedule locking, $\DyadicRatCoreUp$ readback exposure, $\RegSeqRatUp$ handoff routing, $\RealUp$ diagonal seal exposure, componentwise $\hsame$ transport, displayed $\Cont$ route replay, $\Pkg$ provenance, and the local naming row.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-diagonal-fusion-carrier}. The rows $E,B,W,S,D,R,L$ are the only mathematical coordinates, and $H,C,P,N$ are the only transport, route, package, and naming coordinates.

The observation row $B$, witness row $W$, and schedule-fusion row $S$ are read before any seal consumer reaches $L$. Thus the local certificate is assembled from the same finite route rather than from a host completion object.

Since quotient streams, host equality, selected limits, unbounded schedules, and ambient completeness have no row in $F$, no local $\NameCert$ projection can export them.
\end{proof}

\begin{theorem}[Cauchy diagonal fusion schedule lock]
\label{thm:cauchy-diagonal-fusion-schedule-lock}
For an accepted $\CauchyDiagonalFusionUp$ carrier, every precision request routed through $E$ reaches the same $\RealObservationBudgetUp$ row $B$, $\RegularCauchyWitnessScheduleUp$ row $W$, and $\RealScheduleFusionUp$ row $S$ before reading the dyadic row $D$. The schedule fusion therefore fixes the finite window ledger and regular-rational readback used by the diagonal route.
\end{theorem}
\begin{proof}
Start with the precision request row $E$. The displayed continuations in $C$ send this request to $B,W,S$ before $D$ is available.

The transport row $H$ carries the same observation budget, witness schedule, and schedule-fusion rows componentwise. Therefore a transported precision request cannot select a second window family or a second schedule after the diagonal route has begun.
\end{proof}

\begin{theorem}[Cauchy diagonal fusion RealUp seal handoff]
\label{thm:cauchy-diagonal-fusion-real-seal-handoff}
Every $\RealUp$ diagonal seal read exported by an accepted $\CauchyDiagonalFusionUp$ packet factors through the finite route
$$
E \longmapsto B \longmapsto W \longmapsto S \longmapsto D \longmapsto R \longmapsto L.
$$
The seal receives only the precision request, observation-budget row, witness-schedule row, schedule-fusion row, dyadic readback, regular-rational handoff, transports, routes, provenance, and local naming data.
\end{theorem}
\begin{proof}
Apply the schedule-lock theorem to place every seal-facing request after $E,B,W,S,D$. The dyadic readback is therefore already tied to the displayed observation budget and witness schedule.

The regular-rational handoff row $R$ is the only source-facing row between the dyadic readback and the seal. The continuation route then reaches $L$ with $H,C,P,N$ as visible structural data.

No further analytic object is present in the carrier, so the seal handoff cannot bypass the finite diagonal route.
\end{proof}

\begin{theorem}[Cauchy diagonal fusion non-escape]
\label{thm:cauchy-diagonal-fusion-nonescape}
An accepted $\CauchyDiagonalFusionUp$ packet exports only the rows $E,B,W,S,D,R,L,H,C,P,N$ of \autoref{def:cauchy-diagonal-fusion-carrier}. It exports no quotient stream, no host real equality, no selected completed limit, no unbounded schedule, and no ambient completeness principle.
\end{theorem}
\begin{proof}
Inspect the carrier rows. The route-visible data are the precision request, observation budget, witness schedule, schedule fusion, dyadic readback, regular-rational handoff, and diagonal seal, together with the structural rows $H,C,P,N$.

The NameCert obligation theorem identifies this list as the local naming surface. The schedule-lock theorem and seal-handoff theorem then force every downstream read to pass through that surface.

Because the excluded objects are not coordinates and are not produced by the displayed continuations, no consumer can recover them from the packet.
\end{proof}
