\closureat{TotalOrderUp}{publicStr}[BEDC.Derived.PreorderUp.preorder\_prefix\_stability\_certificate\_fields]
\begin{closurestatus}{\TotalOrderUp}
  \constructivestory{The total-order surface keeps the unary-prefix carrier from $\PosetUp$ and adds only public selector rows saying that, on the exposed finite unary endpoints, a comparison phase can choose the relevant directed prefix evidence. The accepted objects are still unary histories over $\mathsf{BHist}$, with b0-headed histories excluded, and the classifier is still the carrier-aware $\hsame$ row that antisymmetry reads back from opposing comparisons. The source is the public unary-prefix order packet, the pattern records finite extrema, interval collapse, phase-exit, root-obligation, and certificate-boundary rows over the same prefix relation, and the ledger keeps each selector decision tied to explicit continuation witnesses rather than to a classical trichotomy oracle. The five name-certificate obligations are inherited from the preorder and poset layers: $\emp$ inhabits the carrier, $\hsame$ remains reflexive, symmetric, and transitive, and any classified endpoint stays inside the unary carrier. A history $h$ lies in the signature gap of a $\TotalOrderUp$ token $p$ when the source-domain accepts $h$, the signature relation pairs it with an answer endpoint and audit ledger, and token introduction names that answer as $p$; unfolded, $h$ is a unary endpoint whose comparison evidence, extrema row, and phase-exit data match the public token. There is no checked standard bridge here; the public audit boundary exports the finite unary-prefix selector surface only, leaving arbitrary total orders and classical trichotomy outside the closure. The chapter registers this selector-refined prefix package under the name $\TotalOrderUp$; totality is presented as public finite unary comparison data, not as an imported order type, quotient completion, or lattice structure.}
  \theoryclosure{\publicClosure}
  \scopeclosed{The public $\TotalOrderUp$ certificate surface is exported through the unary-prefix carrier, classifier, finite-extrema, phase-exit, certificate-boundary, public-audit, and root-obligation rows.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.PreorderUp.preorder\_prefix\_stability\_certificate\_fields}
  \bridgestatus{none}
  \notclaimed{It does not close the full TotalOrder bridge, arbitrary total orders, classical trichotomy, quotient completion, or lattice structure.}
  \upgradepath{Bridged closure requires the standard bridge theorem for the public unary-prefix $\TotalOrderUp$ certificate surface.}
\end{closurestatus}
