\begin{definition}[RegSeqRat constant dyadic source]
\label{def:regseqrat-constant-dyadic-source}
A $\RegSeqRatUp$ constant dyadic source packet for a displayed dyadic endpoint
$d$ is the finite packet obtained by reading one $\DyadicRatCoreUp$ endpoint
row for $d$, the constant $\StreamNameUp$ schedule that returns that same row
at every requested unary window, and the $\RegSeqRatUp$ regularity ledger that
compares any two displayed positions by the same endpoint row. Its visible
rows are the dyadic endpoint row, the dyadic radius row requested by each
window, the zero dyadic-distance row for equal endpoints, the regularity bound
row, componentwise $\hsame$ rows, displayed $\Cont$ routes, $\mathsf{Pkg}$
provenance, and local $\NameCert$ provenance.

The packet is only a finite BEDC source description. It is not a quotient
stream, host real equality, selected limit, metric completion object, Real
completeness row, or ambient embedding principle.
\end{definition}

\begin{theorem}[RegSeqRat constant dyadic regularity]
\label{thm:regseqrat-constant-dyadic-regularity}
Every finite window of a $\RegSeqRatUp$ constant dyadic source is regular. For
requested precisions $n$ and $m$, both displayed endpoints are the same
$\DyadicRatCoreUp$ row $d$, the dyadic-distance row is the equal-endpoint row,
and the regularity ledger is the displayed bound
$$
0 \leq 2^{-n}+2^{-m}.
$$
Thus the window supplies exactly the RegSeqRat regularity row over the constant
StreamName schedule, together with its $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
local $\NameCert$ rows.
\end{theorem}
\begin{proof}
Project the constant dyadic source of
\autoref{def:regseqrat-constant-dyadic-source}. The two endpoint projections
in any finite window are the same $\DyadicRatCoreUp$ endpoint row, because the
$\StreamNameUp$ schedule is constant.

Read the equal-endpoint dyadic-distance row from
\autoref{ch:concrete-instances-dyadicratcore-namecert}. The radius ledger for
the same window supplies the two displayed radii $2^{-n}$ and $2^{-m}$, so the
regularity comparison is bounded by the displayed sum.

Finally apply the RegSeqRat regularity obligation surface of
\autoref{thm:regseqrat-regularity-obligation-surface} and the finite-window
transport closure of
\autoref{thm:regseqrat-finite-window-transport-obligation}. They repack the
constant StreamName schedule of
\autoref{ch:concrete-instances-streamname-namecert} and the dyadic endpoint
rows as the required RegSeqRat regularity ledger, without adding quotient or
completion data.
\end{proof}

\begin{theorem}[RegSeqRat constant RealUp seal handoff]
\label{thm:regseqrat-constant-real-seal-handoff}
A $\RegSeqRatUp$ constant dyadic source reaches the $\RealUp$ seal only through
the four visible faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp.
$$
The source first reads the constant StreamName schedule, then the shared
DyadicRatCore endpoint and radius rows, then the RegSeqRat regularity and
classifier ledger of \autoref{thm:regseqrat-constant-dyadic-regularity}, and
then the RealUp seal row of
\autoref{ch:concrete-instances-real-namecert}. The handoff exports no quotient
stream equality, host real equality, completion object, selected limit, ambient
embedding theorem, or RealUp completeness row.
\end{theorem}
\begin{proof}
Start with the constant schedule and endpoint packet of
\autoref{def:regseqrat-constant-dyadic-source}. Its source rows are already the
StreamName and DyadicRatCore rows named by
\autoref{ch:concrete-instances-streamname-namecert} and
\autoref{ch:concrete-instances-dyadicratcore-namecert}.

Use \autoref{thm:regseqrat-constant-dyadic-regularity} to place every finite
window on the RegSeqRat regularity surface. The cited theorem supplies the
same endpoint, radius, distance, transport, route, package, and naming rows in
each requested window.

Finally apply the existing RegSeqRat seal route:
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness},
\autoref{thm:regseqrat-tail-budget-meet-handoff}, and
\autoref{thm:regseqrat-real-seal-handoff}. These route the finite
regular-rational packet to the RealUp seal through the four visible faces.
Since none of those faces contains a coordinate for quotient stream equality,
host real equality, completion objects, selected limits, embedding theorems, or
RealUp completeness, the constant packet exports no such row.
\end{proof}

\begin{theorem}[RegSeqRat constant dyadic classifier reflection]
\label{thm:regseqrat-constant-dyadic-classifier-reflection}
For two $\RegSeqRatUp$ constant dyadic source packets over displayed
$\DyadicRatCoreUp$ endpoints $d$ and $e$, the $\RegSeqRatUp$
dyadic-tolerance classifier read between their constant schedules is exactly
the finite $\DyadicRatCoreUp$ equality-and-tolerance row consumed by the
$\RealUp$ seal classifier. Thus agreement of the two constant sources at the
$\RealUp$ seal factors through the constant $\StreamNameUp$ schedules, the
$\DyadicRatCoreUp$ endpoint-distance ledger, the $\RegSeqRatUp$ regularity and
classifier ledger, and the $\RealUp$ seal, with no quotient stream equality,
host real equality, selected limit, completion datum, or RealUp completeness
row.
\end{theorem}
\begin{proof}
Project both constant source packets using
\autoref{def:regseqrat-constant-dyadic-source}. Their visible schedules are
constant $\StreamNameUp$ schedules, and every finite comparison therefore
reads the same displayed endpoint rows $d$ and $e$ at the requested windows.

Apply \autoref{thm:regseqrat-constant-dyadic-regularity} to both constant
sources. The resulting finite windows carry the endpoint rows, radius rows,
endpoint-distance row, $\hsame$ transport rows, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ provenance needed by the
RegSeqRat classifier ledger.

Now use the general seal classifier route:
\autoref{thm:regseqrat-real-seal-classifier-factorization} identifies the
classifier seen by the RealUp seal with the RegSeqRat dyadic-tolerance
classifier, and
\autoref{thm:regseqrat-real-seal-classifier-exhaustion} says that this
classifier consumes only the displayed finite rows just listed. In the
constant-source case those rows are precisely the DyadicRatCore
equality-and-tolerance row for $d$ and $e$.

Finally close with the handoff of
\autoref{thm:regseqrat-constant-real-seal-handoff}. That theorem supplies the
four-face route from the two constant source descriptions to the RealUp seal,
so the classifier reflection contains no additional coordinate for quotient
stream equality, host real equality, selected limits, completion data, or
RealUp completeness.
\end{proof}

\begin{theorem}[RegSeqRat constant tail seal invariance]
\label{thm:regseqrat-constant-tail-seal-invariance}
Let $C$ be a $\RegSeqRatUp$ constant dyadic source packet over a displayed
$\DyadicRatCoreUp$ endpoint $d$. For every certified unary tail shift of the
$\StreamNameUp$ schedule of $C$, the shifted source presents the same constant
$\StreamNameUp$ schedule, the same endpoint-distance ledger at $d$, and the
same $\RegSeqRatUp$ classifier surface to the $\RealUp$ seal.

Consequently any two certified unary tail shifts of the constant source have
the same $\RealUp$ seal source read after restriction to their common cofinal
finite window. This invariance is only a statement about the displayed
constant dyadic source rows, the RegSeqRat regularity and classifier surface,
and the RealUp seal-facing finite packet. It exports no quotient stream
equality, host real equality, selected limit, completion datum, or RealUp
completeness row.
\end{theorem}
\begin{proof}
Project the source by
\autoref{def:regseqrat-constant-dyadic-source}. A certified unary tail shift
changes only which schedule rows are requested; every requested row still
returns the same displayed $\DyadicRatCoreUp$ endpoint $d$ and the same
constant $\StreamNameUp$ schedule entry.

Apply \autoref{thm:regseqrat-constant-dyadic-regularity}. The endpoint rows on
the shifted windows are equal to $d$, so the endpoint-distance ledger is the
same equal-endpoint row and the dyadic-radius rows are read from the same
constant packet.

Use \autoref{thm:regseqrat-shifted-tail-regularity-closure} to repack each
shifted finite window as an accepted $\RegSeqRatUp$ window. Since the source is
constant, the repacked window carries the same regularity ledger and the same
dyadic-tolerance classifier surface as the unshifted constant source.

Now apply \autoref{thm:regseqrat-tail-cofinal-real-seal-invariance} to two
certified tail reads of the constant source. Their common cofinal finite
window identifies the displayed schedule rows, endpoint rows, endpoint-distance
ledger, classifier witness, $\hsame$ comparisons, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ provenance.

Finally close with
\autoref{thm:regseqrat-constant-real-seal-handoff}. The handoff says that the
constant source reaches the $\RealUp$ seal only through the visible
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces, so
the tail comparison has no coordinate for quotient stream equality, host real
equality, selected limits, completion data, or RealUp completeness.
\end{proof}
