\chapter{A Concrete Naming Certificate for $\RegSeqRatUp$}
\label{ch:concrete-instances-regseqrat-namecert}

The $\RegSeqRatUp$ interface names Bishop-style regular rational streams over the dyadic observation layer. It sits between $\DyadicRatCoreUp$, which supplies finite dyadic endpoints and radius ledgers, and $\RealUp$, which consumes accepted regular-sequence packets as the finite source surface of a real-name seal.

\section{Carrier and classifier}
\label{sec:regseqrat-carrier-classifier}

\begin{definition}[RegSeqRat stream carrier]
\label{def:regseqrat-stream-carrier}
A $\RegSeqRatUp$ stream carrier is a finite $\mathsf{BHist}$ packet naming a stream $x:\mathbb{N}\to\mathsf{BHist}$ together with the visible observation schedule supplied by $\StreamNameUp$. For every finite window requested by the schedule, the packet carries:
\begin{enumerate}
\item a unary index row naming the requested stream position;
\item a dyadic endpoint row accepted by $\DyadicRatCoreUp$;
\item the dyadic radius row $2^{-n}$ attached to the requested precision;
\item a regularity ledger comparing any two displayed endpoints $x_n$ and $x_m$ by the bound $2^{-n}+2^{-m}$;
\item the $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance rows for the $\StreamNameUp$ and $\DyadicRatCoreUp$ reads.
\end{enumerate}
The carrier stores only these scheduled finite observations. It contains no quotient carrier of Cauchy sequences, no ambient metric completion, and no host real endpoint.
\end{definition}
\leandef{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier}

\begin{definition}[RegSeqRat dyadic-tolerance classifier]
\label{def:regseqrat-classifier}
For accepted $\RegSeqRatUp$ carriers $x$ and $y$, the predicate $\mathsf{RegSeqRatClassifier}(x,y)$ records dyadic tolerance agreement on scheduled finite windows. A classifier witness supplies, for each requested unary precision window, dyadic observation rows for $x_n$ and $y_m$, a common finite refinement requested through $\StreamNameUp$, and a $\DyadicRatCoreUp$ tolerance ledger proving that the displayed dyadic distance is bounded by the requested dyadic radius.

The classifier is a predicate over finite dyadic ledgers and visible stream-name rows. It does not identify streams by a quotient relation and does not import any external real equality.
\end{definition}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatClassifier\_window\_pairing}

\section{Certificate obligations}
\label{sec:regseqrat-certificate-obligations}

\begin{theorem}[RegSeqRat regularity obligation surface]
\label{thm:regseqrat-regularity-obligation-surface}
The local $\NameCert_{\RegSeqRatUp}$ obligation surface consists of five finite rows:
\begin{enumerate}
\item carrier: the scheduled stream carrier of \autoref{def:regseqrat-stream-carrier};
\item classifier: the dyadic-tolerance classifier of \autoref{def:regseqrat-classifier};
\item regularity ledger: every displayed pair of endpoints $x_n,x_m$ is accompanied by a $\DyadicRatCoreUp$ bound row for $2^{-n}+2^{-m}$;
\item dyadic-radius observation: each precision request exposes the radius row, endpoint row, and finite dyadic distance row consumed by the classifier;
\item finite-window transport: restricting, refining, or transporting a window through $\hsame$ and $\Cont$ repacks the same $\StreamNameUp$ and $\DyadicRatCoreUp$ rows without adding a quotient or completion object.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_regularity\_obligation\_surface}
\begin{proof}
Project the carrier definition. Its accepted packet already lists the scheduled unary index rows, dyadic endpoint rows, radius rows, regularity comparisons, continuation routes, package provenance, and naming rows.

The classifier definition supplies the second face: every comparison between two accepted packets is a finite dyadic-tolerance ledger over the same scheduled observation rows. The regularity and dyadic-radius faces are the two distinguished projections from that ledger.

For finite-window transport, follow the displayed $\hsame$ and $\Cont$ rows attached to the schedule. A restriction or refinement only changes which finite indices are read; each selected endpoint and radius remains a $\DyadicRatCoreUp$ row with the same visible provenance. Repacking these projections gives exactly the five obligation rows and no additional carrier.
\end{proof}

\begin{theorem}[RegSeqRat window regularity ledger]
\label{thm:regseqrat-window-regularity-ledger}
Every scheduled finite window in an accepted $\RegSeqRatUp$ stream carrier carries the unary index rows requested by $\StreamNameUp$, two $\DyadicRatCoreUp$ endpoint rows for the displayed endpoints $x_n$ and $x_m$, the two dyadic radius rows $2^{-n}$ and $2^{-m}$, and the regularity ledger row displaying the bound
$$
2^{-n}+2^{-m}.
$$
The window carries these rows together with their $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance, and it carries no quotient sequence, metric-completion object, or host real endpoint.
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_window\_regularity\_ledger}
\begin{proof}
Project the stream carrier of \autoref{def:regseqrat-stream-carrier}. A scheduled window is generated by the visible $\StreamNameUp$ request, so its finite rows include the unary indices selected by that request and the dyadic endpoint rows accepted by $\DyadicRatCoreUp$.

The regularity row in \autoref{thm:regseqrat-regularity-obligation-surface} is the distinguished comparison row for any displayed endpoint pair. Reading it at the selected indices gives the two radius rows and the displayed ledger bound $2^{-n}+2^{-m}$.

The same carrier projection lists the $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance rows attached to those observations. Since the carrier has no coordinate for quotient sequences, completions, or host real endpoints, the window ledger is exhausted by the displayed finite rows.
\end{proof}

\begin{theorem}[RegSeqRat dyadic-radius observation]
\label{thm:regseqrat-dyadic-radius-observation}
Every classifier precision request in $\mathsf{RegSeqRatClassifier}(x,y)$ exposes only the $\StreamNameUp$ schedule rows, $\DyadicRatCoreUp$ endpoint rows, dyadic radius rows, finite dyadic distance rows, componentwise $\hsame$ rows, displayed $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ rows of the accepted $\RegSeqRatUp$ packets.
\end{theorem}
\begin{proof}
Unpack the classifier of \autoref{def:regseqrat-classifier}. A precision request first selects a finite stream-name window and then reads dyadic endpoints for the two accepted packets through $\DyadicRatCoreUp$.

The tolerance witness is a finite dyadic ledger. It records the requested radius and the displayed dyadic distance, together with the common refinement supplied by the same $\StreamNameUp$ schedule.

All comparison and routing data are the componentwise $\hsame$ rows, displayed $\Cont$ routes, package provenance, and naming rows already present in the packets. No external real equality, quotient carrier, or completion datum can be projected from the classifier definition.
\end{proof}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatClassifier\_dyadic\_radius\_observation}

\begin{theorem}[RegSeqRat finite-window transport obligation]
\label{thm:regseqrat-finite-window-transport-obligation}
Restricting, refining, or transporting a finite $\RegSeqRatUp$ window preserves the carrier and classifier rows through componentwise $\hsame$ comparisons and the displayed $\Cont$ routes. The transported window retains the $\StreamNameUp$ schedule, $\DyadicRatCoreUp$ endpoint rows, dyadic radius rows, finite dyadic distance rows, regularity ledgers, $\mathsf{Pkg}$ provenance, and $\NameCert$ rows, and introduces no additional carrier.
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_finite\_window\_transport\_obligation}
\begin{proof}
Start with the window ledger of \autoref{thm:regseqrat-window-regularity-ledger}. It identifies the unary index rows, endpoint rows, radius rows, and regularity bound carried by the source window.

Use \autoref{thm:regseqrat-dyadic-radius-observation} for the classifier side. Every precision request reads the same schedule, endpoint, radius, distance, comparison, continuation, package, and naming rows.

Now apply the transport statement of \autoref{thm:regseqrat-classifier-transport}. Its hypotheses are exactly componentwise $\hsame$ rows and displayed $\Cont$ routes preserving the schedule, endpoints, radius rows, and regularity ledgers. Repacking the transported rows gives the target finite window with the same carrier and classifier surface, and there is no coordinate from which an additional carrier could be introduced.
\end{proof}

\begin{theorem}[RegSeqRat classifier transport]
\label{thm:regseqrat-classifier-transport}
Let $x,y,x',y'$ be accepted $\RegSeqRatUp$ stream carriers. Suppose $x$ is transported to $x'$ and $y$ is transported to $y'$ by componentwise $\hsame$ rows and displayed $\Cont$ routes that preserve the $\StreamNameUp$ schedule, the $\DyadicRatCoreUp$ endpoint rows, the dyadic-radius rows, and the finite regularity ledgers. If $\mathsf{RegSeqRatClassifier}(x,y)$ holds, then $\mathsf{RegSeqRatClassifier}(x',y')$ holds on the transported finite windows.

The transported classifier reads only the carried stream-name, dyadic endpoint, radius, distance, regularity, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_classifier\_transport}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatClassifier\_transport}
\begin{proof}
Start with a finite classifier witness for $x$ and $y$. It consists of scheduled observation indices, endpoint rows, radius rows, common finite refinements, and dyadic distance ledgers.

Transport the two endpoint families along the supplied componentwise $\hsame$ rows. The $\Cont$ routes preserve the schedule, so every requested finite window for $x'$ and $y'$ has the same shape as the source window and reads the corresponding transported $\DyadicRatCoreUp$ endpoint rows.

Transport the dyadic-radius and distance ledgers through the same provenance. Since the regularity rows are carried with the endpoints, the transported witness satisfies the dyadic-tolerance classifier for $x'$ and $y'$ on the selected windows. No quotient sequence or ambient real equality is introduced.
\end{proof}

\begin{theorem}[RegSeqRat classifier symmetric finite-window]
\label{thm:regseqrat-classifier-symmetric-finite-window}
Let $x$ and $y$ be accepted $\RegSeqRatUp$ stream carriers. Suppose a finite $\StreamNameUp$ scheduled window witnesses $\mathsf{RegSeqRatClassifier}(x,y)$ by displayed $\DyadicRatCoreUp$ endpoint rows, dyadic-radius rows, finite dyadic distance ledgers, regularity ledgers, componentwise $\hsame$ comparisons, displayed $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ rows. Then the reversed scheduled window witnesses $\mathsf{RegSeqRatClassifier}(y,x)$ using the same finite rows with the endpoint-pair order swapped.
\end{theorem}
\begin{proof}
Project the witness through the classifier definition of \autoref{def:regseqrat-classifier}. The only visible coordinates are the scheduled endpoint rows, radius rows, dyadic distance ledgers, regularity rows, comparison rows, continuation routes, package provenance, and naming rows.

Reverse the scheduled window by swapping the two endpoint rows in every displayed pair. The dyadic distance ledger is read symmetrically by \autoref{thm:regseqrat-dyadic-radius-ledger-readback}, so the same tolerance rows certify the reversed endpoint comparison.

Transport the swapped rows through the finite-window transport obligation of \autoref{thm:regseqrat-finite-window-transport-obligation}. The componentwise $\hsame$ comparisons and displayed $\Cont$ routes preserve the schedule, endpoint rows, radii, distance rows, and regularity ledgers.

Apply classifier transport from \autoref{thm:regseqrat-classifier-transport} to the repacked reversed window. The resulting finite packet has exactly the rows required for $\mathsf{RegSeqRatClassifier}(y,x)$, and no quotient stream equality or host real equality is introduced.
\end{proof}

\begin{theorem}[RegSeqRat common-refinement classifier determinacy]
\label{thm:regseqrat-common-refinement-classifier-determinacy}
Let $x$ and $y$ be accepted $\RegSeqRatUp$ stream carriers. Suppose two finite $\StreamNameUp$ schedules both refine to a common window and carry the same transported $\DyadicRatCoreUp$ endpoint rows, dyadic-radius rows, regularity ledgers, classifier ledgers, $\hsame$ comparisons, $\Cont$ routes, and $\mathsf{Pkg}$ provenance. Then the two schedules determine the same $\mathsf{RegSeqRatClassifier}(x,y)$ read on that common window.

The common read is the one exposed by the $\RealUp$ seal handoff through the refined finite rows. It contains no quotient stream equality, host real equality, or metric-completion comparison.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regseqrat-stream-carrier} and the classifier of \autoref{def:regseqrat-classifier}. Each schedule reads only unary index rows, dyadic endpoints, radius rows, regularity ledgers, dyadic distance ledgers, and the displayed provenance attached to those rows.

Move both schedules to the stated common window. The finite-window transport obligation of \autoref{thm:regseqrat-finite-window-transport-obligation} carries the endpoints, radii, regularity rows, and provenance to the same refined rows on that window.

Apply classifier transport from \autoref{thm:regseqrat-classifier-transport} to both transported reads. Since the hypotheses identify the transported endpoint, radius, regularity, classifier, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows, the two classifier witnesses have the same finite ledger on the common window.

Finally read the $\RealUp$ seal boundary through \autoref{thm:regseqrat-real-seal-handoff}. That handoff consumes only the refined finite rows just identified, so it cannot distinguish the two source schedules and yields the same $\mathsf{RegSeqRatClassifier}$ read.
\end{proof}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_common\_refinement\_classifier\_determinacy}

\begin{theorem}[RegSeqRat classifier common-refinement transitivity]
\label{thm:regseqrat-classifier-common-refinement-transitivity}
Let $x$, $y$, and $z$ be accepted $\RegSeqRatUp$ packets. Suppose one finite $\StreamNameUp$ schedule witnesses $\mathsf{RegSeqRatClassifier}(x,y)$ and another finite $\StreamNameUp$ schedule witnesses $\mathsf{RegSeqRatClassifier}(y,z)$. If the two witnesses admit a common refinement on which the middle $y$ endpoint rows, dyadic-radius rows, regularity ledgers, classifier ledgers, $\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ provenance agree, then the common refinement witnesses $\mathsf{RegSeqRatClassifier}(x,z)$ using only the displayed finite rows.
\end{theorem}
\begin{proof}
Project both classifier witnesses to their finite scheduled windows. The finite-window transport obligation of \autoref{thm:regseqrat-finite-window-transport-obligation} moves the $x$--$y$ and $y$--$z$ endpoint families, radius rows, regularity ledgers, classifier ledgers, $\hsame$ rows, $\Cont$ routes, package rows, and naming rows to the stated common refinement.

On that common refinement, apply \autoref{thm:regseqrat-common-refinement-classifier-determinacy} to the two transported reads of the middle $y$ side. The agreement hypotheses identify the displayed $y$ endpoint rows and all provenance rows that the classifier can inspect, so the two source schedules have one middle finite surface.

Read the two dyadic tolerance ledgers through \autoref{thm:regseqrat-dyadic-radius-ledger-readback}. Since the radius and distance data are displayed on the same refined finite window, the $x$ endpoint rows and the $z$ endpoint rows compose across the common $y$ rows inside the dyadic ledger surface.

Finally use classifier transport from \autoref{thm:regseqrat-classifier-transport} to repack the composed finite surface as a witness for $\mathsf{RegSeqRatClassifier}(x,z)$. The construction introduces no quotient stream equality, host real equality, metric-completion object, or $\RealUp$ completeness datum.
\end{proof}

\begin{theorem}[RegSeqRat diagonal window extraction]
\label{thm:regseqrat-diagonal-window-extraction}
Let $P$ be an accepted $\RegSeqRatUp$ packet, and let $S$ be a finite $\StreamNameUp$ schedule whose two classifier witnesses for displayed reads of $P$ admit a common refinement. At the shared unary index of that refinement, the diagonal observation is a displayed finite window consisting only of $\mathsf{BHist}$ rows, the $\UnaryHistory$ witness for the index, the $\DyadicRatCoreUp$ endpoint and radius rows, regularity ledgers, $\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ provenance.

The same diagonal row is exactly the finite source row consumed by the $\RealUp$ seal handoff. Thus the extraction exports no quotient stream, host real equality, metric-completion point, $\RealUp$ completeness datum, or additional bridge coordinate.
\end{theorem}
\begin{proof}
Project the two scheduled reads through \autoref{thm:regseqrat-scheduled-window-projection}. This exposes the common-refinement schedule together with the displayed unary index, endpoint rows, radius rows, regularity ledgers, comparison rows, continuation routes, package provenance, and naming provenance.

Read the radius and distance components by \autoref{thm:regseqrat-dyadic-radius-ledger-readback}. The diagonal row at the shared unary index is therefore a finite $\DyadicRatCoreUp$ endpoint-and-radius observation inside the same displayed $\mathsf{BHist}$ packet.

Use \autoref{thm:regseqrat-common-refinement-classifier-determinacy} to identify the two transported classifier reads on the common refinement. Since the classifier can inspect only the displayed rows already projected, both witnesses present the same diagonal finite-window row.

Finally apply \autoref{thm:regseqrat-real-seal-handoff}. The $\RealUp$ seal consumes exactly the finite regular-rational source surface exposed by that diagonal row, so the handoff reads the extracted finite window itself and not any quotient, host-real, completion, or bridge datum.
\end{proof}

\begin{theorem}[RegSeqRat scheduled-window projection]
\label{thm:regseqrat-scheduled-window-projection}
For every accepted finite scheduled window of a $\RegSeqRatUp$ stream carrier, projection exposes only the unary index row, the $\DyadicRatCoreUp$ endpoint row, the dyadic-radius row, the regularity ledger rows, and the associated $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows. No projected window contains a quotient sequence coordinate, a host real coordinate, or a completion object.
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_scheduled\_window\_projection}
\begin{proof}
Project \autoref{def:regseqrat-stream-carrier}. Each scheduled window is stored as a finite $\mathsf{BHist}$ packet, and the carrier list contains precisely the unary index, dyadic endpoint, radius, regularity, continuation, package, and naming rows.

Apply \autoref{thm:regseqrat-regularity-obligation-surface} to read the same packet as a local obligation surface. The theorem identifies the carrier, regularity ledger, dyadic-radius observation, and finite-window transport faces as projections of those displayed rows.

Finally use \autoref{def:regseqrat-classifier} and \autoref{thm:regseqrat-classifier-transport} to check that classifier reads do not add further coordinates. They consume the projected dyadic ledgers and transport them along the displayed $\hsame$ and $\Cont$ rows.
\end{proof}

\begin{theorem}[RegSeqRat dyadic-radius ledger readback]
\label{thm:regseqrat-dyadic-radius-ledger-readback}
Every radius or distance comparison used by $\mathsf{RegSeqRatClassifier}$ is read back from displayed $\DyadicRatCoreUp$ radius and distance ledgers in the accepted finite window. The classifier never appeals to quotient equality of streams, host real equality, or an ambient metric-completion comparison.
\end{theorem}
\begin{proof}
Unfold the classifier of \autoref{def:regseqrat-classifier}. A witness is a finite list of scheduled dyadic observations, a common refinement row, and a $\DyadicRatCoreUp$ tolerance ledger for the displayed distance against the requested radius.

The available radius and regularity rows are exactly the dyadic-radius observation and regularity faces of \autoref{thm:regseqrat-regularity-obligation-surface}. Thus every comparison used in a classifier witness has a displayed ledger source inside the finite packet.

Transport stability follows from \autoref{thm:regseqrat-classifier-transport}. When the window is carried through $\hsame$ and $\Cont$, the radius and distance ledgers are carried as the same $\DyadicRatCoreUp$ rows, so no quotient or host-real equality can enter the readback.
\end{proof}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_dyadic\_radius\_ledger\_readback}

\begin{theorem}[RegSeqRat finite-window transport closure]
\label{thm:regseqrat-finite-window-transport-closure}
Restriction, refinement, and componentwise $\hsame$ or $\Cont$ transport of an accepted finite $\RegSeqRatUp$ window repack the same $\StreamNameUp$ schedule rows and $\DyadicRatCoreUp$ endpoint, radius, distance, and regularity rows. The repacked window remains within the displayed carrier and classifier surface of the same stream-name certificate.
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_finite\_window\_transport\_closure}
\begin{proof}
Begin with the finite-window transport row singled out by \autoref{thm:regseqrat-regularity-obligation-surface}. Restriction selects fewer scheduled unary indices, while refinement requests a larger finite schedule through $\StreamNameUp$ and keeps each selected endpoint and radius as a displayed $\DyadicRatCoreUp$ row.

For componentwise transport, apply \autoref{thm:regseqrat-classifier-transport}. Its hypotheses preserve the stream schedule, endpoint rows, radius rows, and regularity ledgers, and its conclusion rebuilds the dyadic-tolerance classifier on the transported finite windows.

The carrier of \autoref{def:regseqrat-stream-carrier} and the classifier of \autoref{def:regseqrat-classifier} therefore close under these finite operations by repacking existing rows. The resulting packet is still a $\RegSeqRatUp$ source surface, not a quotient or completion object.
\end{proof}

\begin{theorem}[RegSeqRat refined-window gluing]
\label{thm:regseqrat-refined-window-gluing}
Let $W_0$ and $W_1$ be accepted finite scheduled windows of the same $\RegSeqRatUp$ stream carrier. Suppose $\StreamNameUp$ supplies a finite common refinement schedule $W_\cup$ whose source rows restrict to the two input schedules, and suppose the overlapping unary index rows, $\DyadicRatCoreUp$ endpoint rows, dyadic radius rows, regularity ledgers, and classifier ledgers of $W_0$ and $W_1$ agree along the displayed $\hsame$ comparisons and $\Cont$ routes. Then the refined union repacks as an accepted finite $\RegSeqRatUp$ window over $W_\cup$.

The restrictions of this refined window back to $W_0$ and $W_1$ recover the original classifier witnesses on the two input windows. The gluing operation introduces no quotient sequence, host real equality, metric-completion row, or additional $\RealUp$ seal datum.
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_refined\_window\_gluing}
\begin{proof}
Project the two accepted windows by \autoref{thm:regseqrat-scheduled-window-projection}. This exposes the two finite lists of unary indices, dyadic endpoints, radius rows, regularity ledgers, classifier ledgers, and their displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance rows.

Use the common-refinement schedule supplied by $\StreamNameUp$ to choose the joint finite source window. On rows that come from only one input window, keep the corresponding projected row. On overlapping rows, use the stated $\hsame$ comparisons and $\Cont$ routes to identify the unary index, endpoint, radius, regularity, and classifier ledger entries as the same displayed BEDC data.

The overlap classifier is stable by \autoref{thm:regseqrat-classifier-transport}. Thus the two classifier witnesses restrict to the same transported witness wherever the schedules meet, and the non-overlap rows remain the witnesses already accepted in the two input windows.

Apply \autoref{thm:regseqrat-finite-window-transport-closure} to repack the joint schedule, transported overlap rows, and retained non-overlap rows as one finite $\RegSeqRatUp$ carrier and classifier surface. Restricting the repacked window back along either source schedule discards only the other side's rows, so it recovers the original classifier witness for that input window. Since every row used in the construction came from the two projected finite packets and their displayed refinement routes, no quotient sequence, host real equality, completion object, or $\RealUp$ seal row is created.
\end{proof}

\begin{theorem}[RegSeqRat prefix-window monotonicity]
\label{thm:regseqrat-prefix-window-monotonicity}
Let $W$ be an accepted finite scheduled $\RegSeqRatUp$ window over the dyadic-tolerance classifier of \autoref{def:regseqrat-classifier}. Suppose $W'$ is a finite certified $\StreamNameUp$ prefix subwindow of $W$, obtained by restricting the displayed schedule to an initial certified prefix. Then $W'$ repacks as an accepted finite $\RegSeqRatUp$ window over the same dyadic-tolerance classifier.

The endpoint, radius, regularity, classifier, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows of the repacked prefix are exactly the projections of the corresponding rows of $W$. The prefix restriction introduces no quotient sequence, host real equality, completion object, or $\RealUp$ seal row.
\end{theorem}
\begin{proof}
Project $W$ by \autoref{thm:regseqrat-scheduled-window-projection}. This exposes the visible finite schedule, endpoint rows, radius rows, regularity ledgers, classifier ledgers, $\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ rows.

Use the certified $\StreamNameUp$ prefix to select the initial sublist of scheduled rows. Since the subwindow is a prefix restriction, every endpoint, radius, regularity, classifier, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ row visible in $W'$ is the corresponding projected row already visible in $W$.

Apply \autoref{thm:regseqrat-finite-window-transport-closure} to repack those selected rows as a finite accepted $\RegSeqRatUp$ carrier and classifier surface over the original dyadic-tolerance classifier. No new coordinate is available in this restriction step, so quotient sequences, host real equality, completion objects, and $\RealUp$ seal rows cannot enter the prefix packet.

Finally, when the prefix is compared back with the larger window, use \autoref{thm:regseqrat-refined-window-gluing} on the overlap consisting of the prefix rows. The gluing restriction recovers the same classifier witness on that overlap, because both sides read the same projected endpoint, radius, regularity, classifier, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows.
\end{proof}

\begin{theorem}[RegSeqRat shifted-tail regularity closure]
\label{thm:regseqrat-shifted-tail-regularity-closure}
Let $P$ be an accepted $\RegSeqRatUp$ packet whose stream carrier, dyadic-tolerance classifier, regularity ledger, scheduled windows, and dyadic-radius rows are those of \autoref{def:regseqrat-stream-carrier} and \autoref{def:regseqrat-classifier}. For every certified unary tail index $k$, shifting the schedule of $P$ by $k$ and then reading any finite $\StreamNameUp$ window produces another accepted regular-rational packet over the same dyadic-tolerance classifier.

The shifted packet exposes only the transported $\mathsf{BHist}$ rows, componentwise $\hsame$ comparisons, visible $\Cont$ routes, the retained $\mathsf{Pkg}$ row, and the local $\NameCert$ provenance. It exports no quotient sequence, host real equality, ambient metric-completion object, or $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Use \autoref{thm:regseqrat-scheduled-window-projection} on the shifted finite tail window. The projection exposes exactly the unary tail indices, dyadic endpoint rows, regularity ledgers, radius rows, classifier ledgers, and the visible provenance already carried by $P$.

Read the transported radius and distance comparisons through \autoref{thm:regseqrat-dyadic-radius-ledger-readback}. Since the tail shift only selects later scheduled rows, each tolerance comparison is still a displayed $\DyadicRatCoreUp$ ledger row in the same source packet.

Apply \autoref{thm:regseqrat-finite-window-transport-closure} to repack the selected tail rows as a finite $\RegSeqRatUp$ window over the original dyadic-tolerance classifier. When two shifted finite windows overlap, use \autoref{thm:regseqrat-refined-window-gluing} to identify the common tail rows and retain the same classifier witness on the common refinement.

All consumed coordinates are therefore finite BEDC rows of the original accepted packet. The tail construction has no coordinate from which to read quotient sequences, host real equality, metric completion, or a $\RealUp$ completeness row.
\end{proof}

\begin{theorem}[RegSeqRat shifted-tail seal determinacy]
\label{thm:regseqrat-shifted-tail-seal-determinacy}
Let $P$ be an accepted $\RegSeqRatUp$ packet, and let $k$ be a certified unary tail index for its $\StreamNameUp$ schedule. For any finite $\StreamNameUp$ window read after shifting $P$ by $k$, the $\RealUp$ seal source read from that window is determined by the shifted scheduled window, the $\DyadicRatCoreUp$ endpoint rows, dyadic-radius rows, regularity ledgers, classifier ledgers, componentwise $\hsame$ rows, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ rows already present in $P$.

If two selected shifted windows admit a common finite refinement and agree there on those displayed rows, then the shifted $\RealUp$ seal source read is invariant under restriction to that refinement. The invariant source surface exports no quotient sequence, host real equality, metric-completion object, $\RealUp$ completeness row, or seal datum beyond those finite rows.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-shifted-tail-regularity-closure} to the certified tail shift and selected finite window. This repacks the shifted read as an accepted finite $\RegSeqRatUp$ window whose visible coordinates are precisely the scheduled tail rows, dyadic endpoints, dyadic-radius rows, regularity ledgers, classifier ledgers, $\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ rows inherited from $P$.

For two selected windows with a common finite refinement, use \autoref{thm:regseqrat-refined-window-gluing} to repack the refinement as one accepted finite window. The classifier witnesses on the overlap are fixed by \autoref{thm:regseqrat-common-refinement-classifier-determinacy}, so restriction back to either shifted window reads the same displayed classifier and regularity surface.

Finally apply \autoref{thm:regseqrat-real-seal-handoff}. The $\RealUp$ seal boundary consumes exactly the finite regular-rational source rows exposed above, so common refinement cannot create a new seal coordinate. The result is a determinacy statement for finite BEDC rows only, with no quotient sequence, host real equality, metric-completion object, completeness row, or further seal datum in the export surface.
\end{proof}

\begin{theorem}[RegSeqRat tail-cofinal RealUp seal invariance]
\label{thm:regseqrat-tail-cofinal-real-seal-invariance}
Let $P$ be an accepted $\RegSeqRatUp$ packet. Suppose $T_0$ and $T_1$ are two certified unary tail shifts of $P$ whose finite $\StreamNameUp$ windows admit a common cofinal refinement. Assume that, on the displayed refinement, the two shifted windows agree on the $\DyadicRatCoreUp$ endpoint rows, dyadic radius rows, regularity ledgers, classifier witnesses, $\hsame$ comparisons, $\Cont$ routes, and $\mathsf{Pkg}$ provenance rows.

Then the two tail reads determine the same $\RealUp$ seal source surface: every row consumed by the $\RealUp$ seal from $T_0$ is the corresponding displayed row consumed from $T_1$, after restriction to the common cofinal refinement. This invariance is only a statement about finite BEDC source rows. It does not identify quotient streams, host real values, metric-completion points, or any $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-shifted-tail-regularity-closure} separately to the two certified tail shifts. Each shifted finite window is repacked as an accepted $\RegSeqRatUp$ window over the original dyadic-tolerance classifier, and each exposes only transported $\mathsf{BHist}$ rows, displayed $\hsame$ comparisons, visible $\Cont$ routes, the retained $\mathsf{Pkg}$ row, and local $\NameCert$ provenance.

Use the common cofinal refinement as the joint schedule. The hypotheses identify the endpoint, radius, regularity, classifier, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows on the overlap, so \autoref{thm:regseqrat-refined-window-gluing} repacks the two tail windows into one accepted finite refinement whose restrictions recover the two original tail classifier witnesses.

Finally apply \autoref{thm:regseqrat-real-seal-handoff}. A $\RealUp$ seal read of a regular rational stream consumes exactly the scheduled stream-carrier rows, dyadic-tolerance classifier rows, regularity ledger rows, dyadic-radius rows, finite-window transport rows, and their displayed $\StreamNameUp$, $\DyadicRatCoreUp$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance. Since both tail reads restrict to the same refined finite packet, their seal source surfaces are the same displayed BEDC surface, with no quotient stream, host real equality, completion object, or completeness row available.
\end{proof}

\begin{theorem}[RegSeqRat RealUp seal handoff]
\label{thm:regseqrat-real-seal-handoff}
An accepted $\RegSeqRatUp$ packet is exactly the finite source surface consumed by the existing $\RealUp$ seal rows. The handoff surface consists of the scheduled stream carrier, the dyadic-tolerance classifier, the regularity ledger, the dyadic-radius observation rows, the finite-window transport rows, and their $\StreamNameUp$, $\DyadicRatCoreUp$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.

Thus a $\RealUp$ seal may read a regular rational stream only through those finite source rows. The handoff does not provide RealUp completeness, quotient carriers, metric completeness, or standard bridge data.
\end{theorem}
\begin{proof}
Read the accepted packet through \autoref{thm:regseqrat-regularity-obligation-surface}. The projection exposes precisely the carrier, classifier, regularity, dyadic-radius, and finite-window transport rows.

The existing $\RealUp$ seal rows consume regular rational-stream data by finite windows: a stream-name schedule selects dyadic endpoint observations, the classifier supplies dyadic tolerance agreement, and the regularity ledger supplies the source bounds needed at the seal boundary.

Conversely, any source read used by the seal is one of those finite rows, because the $\RegSeqRatUp$ carrier has no coordinate for quotient sequences, ambient metric completion, host real equality, or standard bridge data. The accepted packet and the seal source surface therefore coincide at the displayed finite boundary.
\end{proof}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_real\_seal\_handoff}

\begin{theorem}[RegSeqRat public source export]
\label{thm:regseqrat-public-source-export}
Any consumer of $\NameCert_{\RegSeqRatUp}$ may read exactly the scheduled stream carrier, the dyadic-tolerance classifier, the regularity ledger, dyadic-radius observations, finite-window transport and gluing rows, the $\RealUp$ seal handoff row, and their displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.

The exported surface contains no quotient sequences, host real equality, ambient metric completion, or extra seal data beyond those finite BEDC rows.
\end{theorem}
\begin{proof}
The regularity obligation surface of \autoref{thm:regseqrat-regularity-obligation-surface} exposes the scheduled carrier, classifier, regularity ledger, dyadic-radius rows, and their displayed provenance. The finite-window transport theorem \autoref{thm:regseqrat-finite-window-transport-closure} keeps reads inside the same finite source rows under restriction and refinement.

The refined-window gluing theorem \autoref{thm:regseqrat-refined-window-gluing} adds only common-refinement rows and transported overlap witnesses, again using the visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance already present in the two windows.

Finally, \autoref{thm:regseqrat-real-seal-handoff} identifies the $\RealUp$ seal boundary with that same regular-rational source surface. Since each cited theorem exposes only finite BEDC rows, their composition exhausts the public export surface and leaves no coordinate through which a consumer could read quotient sequences, host real equality, ambient metric completion, or additional seal data.
\end{proof}

\begin{theorem}[RegSeqRat standard bridge boundary]
\label{thm:regseqrat-standard-bridge-boundary}
An accepted $\RegSeqRatUp$ packet determines the finite standard-bridge boundary consumed by the $\RealUp$-facing regular rational stream interface. The boundary consists exactly of the scheduled stream carrier, the dyadic-tolerance classifier, the regularity ledger, dyadic-radius observation rows, finite-window transport and gluing rows, the $\RealUp$ seal handoff, and the visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.

The bridge boundary exports no quotient sequence, host real equality, ambient metric completion, or $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Start with the public source export of \autoref{thm:regseqrat-public-source-export}. It names the scheduled carrier, classifier, regularity ledger, radius observations, finite-window operations, seal handoff, and provenance as the consumer-visible rows of an accepted packet.

The seal-facing part is supplied by \autoref{thm:regseqrat-real-seal-handoff}. The finite-window part is supplied by \autoref{thm:regseqrat-finite-window-transport-closure}, \autoref{thm:regseqrat-refined-window-gluing}, and \autoref{thm:regseqrat-scheduled-window-projection}; the dyadic-radius readback is supplied by \autoref{thm:regseqrat-dyadic-radius-ledger-readback}.

Composing these rows gives the finite boundary read by the regular rational stream interface. Since the cited statements expose only the carrier, classifier, ledger, window, seal, and provenance coordinates just listed, there is no extra coordinate from which a quotient sequence, host real equality, ambient metric completion, or $\RealUp$ completeness datum could be exported.
\end{proof}

\begin{theorem}[RegSeqRat StreamName Dyadic finite-window lock]
\label{thm:regseqrat-streamname-dyadic-window-lock}
Let $P$ be an accepted finite $\RegSeqRatUp$ scheduled window. The same finite packet simultaneously exposes the $\StreamNameUp$ schedule row, the $\DyadicRatCoreUp$ endpoint and radius ledger extracted by the dyadic-radius window theorem, and the exact $\RealUp$ seal source surface consumed by \autoref{thm:regseqrat-real-seal-handoff}.

If two refinements of $P$ agree on the displayed $\StreamNameUp$ schedule rows, $\DyadicRatCoreUp$ endpoint rows, dyadic-radius rows, regularity ledgers, classifier rows, $\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$ rows, then they induce the same $\RealUp$ seal source surface. The lock exports no quotient stream, host real equality, ambient completion point, $\RealUp$ completeness datum, or additional standard-bridge coordinate.
\end{theorem}
\begin{proof}
Project $P$ by \autoref{thm:regseqrat-scheduled-window-projection}. This exposes the finite $\StreamNameUp$ schedule row together with the endpoint, regularity, classifier, transport, provenance, and local naming rows carried by the same accepted packet.

Next read the regularity and radius data through \autoref{thm:regseqrat-window-regularity-ledger} and \autoref{thm:regseqrat-dyadic-radius-ledger-readback}. These two facts identify the displayed $\DyadicRatCoreUp$ endpoint rows and radius ledger as rows of the same finite scheduled window.

For two refinements, apply \autoref{thm:regseqrat-refined-window-gluing}. Agreement on the displayed schedule, endpoint, radius, regularity, classifier, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows repacks the overlap as one accepted finite $\RegSeqRatUp$ window whose restrictions recover both refinements.

Finally use \autoref{thm:regseqrat-real-seal-handoff}. Since the seal reads only the finite regular-rational source rows just locked together, the two agreeing refinements present the same $\RealUp$ seal source surface and no hidden quotient, completion, equality, or bridge coordinate is available.
\end{proof}

\begin{theorem}[RegSeqRat StreamName Dyadic seal refinement lock]
\label{thm:regseqrat-streamname-dyadic-seal-refinement-lock}
Let $W_0$ and $W_1$ be accepted finite $\RegSeqRatUp$ windows that refine to a
common $\StreamNameUp$ schedule. Suppose the two windows agree on the displayed
$\StreamNameUp$ schedule rows, $\DyadicRatCoreUp$ endpoint and radius rows,
regularity ledgers, classifier witnesses, $\hsame$ comparisons, $\Cont$ routes,
$\Pkg$ provenance, and $\NameCert$ rows. Then their $\RealUp$ seal source reads
are the same displayed finite BEDC surface.

The refinement lock exports no quotient stream equality, host real equality,
ambient completion point, $\RealUp$ completeness row, or extra bridge
coordinate.
\end{theorem}
\begin{proof}
First glue the two windows along the common schedule using
\autoref{thm:regseqrat-refined-window-gluing}. The hypotheses identify exactly
the schedule, endpoint, radius, regularity, classifier, transport, provenance,
and naming rows needed to repack the common refinement as one accepted finite
$\RegSeqRatUp$ window.

Next apply \autoref{thm:regseqrat-tail-cofinal-real-seal-invariance}. It says
that cofinal refinement does not change the finite source surface read by the
$\RealUp$ seal, provided the displayed carrier, classifier, ledger, and
provenance rows agree on the refinement.

Finally combine \autoref{thm:regseqrat-real-seal-handoff} with
\autoref{thm:regseqrat-streamname-dyadic-window-lock}. These theorems identify
the seal-facing read with the same StreamName schedule and DyadicRatCore ledger
rows already locked by the common refinement, so the result is a finite BEDC
surface equality and not a host-level equality or completion claim.
\end{proof}

\begin{theorem}[RegSeqRat tail seal diagonal-window coherence]
\label{thm:regseqrat-tail-seal-diagonal-window-coherence}
Let $P$ be an accepted $\RegSeqRatUp$ packet, and let $T_0$ and $T_1$ be
certified unary tail shifts of $P$. Suppose the selected finite
$\StreamNameUp$ windows for $T_0$ and $T_1$ admit a common refinement. Then the
diagonal finite window supplied by
\autoref{thm:regseqrat-streamname-dyadic-window-lock} is exactly the finite
$\mathsf{BHist}$ surface consumed by
\autoref{thm:regseqrat-real-seal-handoff} for both shifted reads.

Consequently the two $\RealUp$ seal source surfaces agree on the displayed
$\StreamNameUp$ schedule rows, $\DyadicRatCoreUp$ endpoint and radius ledgers,
regularity rows, classifier rows, $\hsame$ comparisons, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and $\NameCert$ provenance. The coherence exports no
quotient stream equality, host real equality, completion object, or
completeness datum.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-shifted-tail-regularity-closure} to each
certified tail shift. Each shifted read is thereby presented as an accepted
finite regular-rational window carrying only the displayed schedule, dyadic,
regularity, classifier, transport, package, and naming rows of $P$.

Use \autoref{thm:regseqrat-refined-window-gluing} to glue the two selected
windows along the common refinement. The overlap classifier is determined by
\autoref{thm:regseqrat-common-refinement-classifier-determinacy}, so both
restrictions read the same classifier and regularity rows on the refined
window.

Now apply \autoref{thm:regseqrat-streamname-dyadic-window-lock}. The lock
identifies the shared $\StreamNameUp$ schedule rows with the same
$\DyadicRatCoreUp$ endpoint and radius ledgers inside the diagonal finite
packet.

Finally use \autoref{thm:regseqrat-real-seal-handoff}. The seal consumes
exactly that finite $\mathsf{BHist}$ surface, so the two shifted reads present
the same displayed source rows to $\RealUp$ and still expose no quotient
stream, host equality, completion object, or completeness datum.
\end{proof}

\begin{theorem}[RegSeqRat cofinal tail seal selected-window uniqueness]
\label{thm:regseqrat-cofinal-tail-seal-selected-window-uniqueness}
Let $P$ be an accepted $\RegSeqRatUp$ packet, and let $T_0$ and $T_1$ be two
certified cofinal tail shifts of $P$. Suppose the finite $\StreamNameUp$
windows selected by $T_0$ and $T_1$ have a common cofinal refinement on which
their selected endpoints, dyadic radii, regularity ledgers, classifier
ledgers, $\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
$\NameCert$ provenance agree. Then the two selected windows determine the
same finite $\RealUp$ seal source surface.

The conclusion is only a uniqueness statement for the displayed finite
$\mathsf{BHist}$ rows: it exports no quotient stream, host real equality,
metric-completion point, completeness row, or standard bridge coordinate.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:regseqrat-tail-cofinal-real-seal-invariance}. The common cofinal
refinement identifies the two tail surfaces on exactly the selected endpoint,
dyadic-radius, regularity, classifier, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ rows named in the hypotheses.

Next use \autoref{thm:regseqrat-tail-seal-diagonal-window-coherence}. The
diagonal selected window is the finite $\mathsf{BHist}$ surface through which
both cofinal tail reads pass, so the two selected windows cannot supply
separate seal-facing source data.

Finally apply \autoref{thm:regseqrat-real-seal-handoff}. The $\RealUp$ seal
reads precisely that diagonal finite regular-rational source surface. Since
the handoff consumes no quotient stream, host-real equality,
metric-completion point, completeness row, or standard bridge coordinate, the
two selected windows have the same finite seal source surface and nothing
stronger is exported.
\end{proof}

\begin{theorem}[RegSeqRat finite-window bridge source exhaustion]
\label{thm:regseqrat-window-bridge-source-exhaustion}
For every accepted finite $\RegSeqRatUp$ packet, the standard-bridge source
rows of \autoref{thm:regseqrat-standard-bridge-boundary} are exactly the
finite-window rows locked by
\autoref{thm:regseqrat-streamname-dyadic-window-lock}, refined by
\autoref{thm:regseqrat-streamname-dyadic-seal-refinement-lock}, and stabilized
by \autoref{thm:regseqrat-tail-seal-diagonal-window-coherence}. Equivalently,
the bridge-facing rows and the finite-window rows are the same displayed BEDC
surface over $\StreamNameUp$, $\DyadicRatCoreUp$, $\mathsf{BHist}$, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and $\NameCert$.

This exhaustion statement does not identify quotient streams, host real
equality, ambient completion points, metric completeness, $\RealUp$
completeness rows, or bridge coordinates beyond the displayed finite source
surface.
\end{theorem}
\begin{proof}
Project the accepted packet through
\autoref{thm:regseqrat-standard-bridge-boundary}. The bridge boundary exposes
only the scheduled stream carrier, dyadic-tolerance classifier, regularity
ledger, radius observations, finite transport and gluing rows, the $\RealUp$
seal handoff, and the displayed provenance rows.

Next apply \autoref{thm:regseqrat-streamname-dyadic-window-lock}. The same
packet projects the $\StreamNameUp$ schedule rows together with the
$\DyadicRatCoreUp$ endpoint and radius ledgers, and the lock identifies those
rows with the finite $\RealUp$ seal source surface read by
\autoref{thm:regseqrat-real-seal-handoff}.

For overlapping finite windows, use
\autoref{thm:regseqrat-streamname-dyadic-seal-refinement-lock}. It glues
agreement on the displayed schedule, endpoint, radius, regularity, classifier,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows into one finite
surface, so the bridge read cannot split from the window read on a common
refinement.

Finally use \autoref{thm:regseqrat-tail-seal-diagonal-window-coherence} and
\autoref{thm:regseqrat-real-seal-handoff}. The diagonal window is exactly the
finite $\mathsf{BHist}$ surface consumed by the $\RealUp$ seal, so every seal
row named by the standard bridge boundary is already one of the displayed
finite-window source rows. The carrier has no coordinate for quotient streams,
host real equality, ambient completion, metric completeness, or any further
bridge datum, which gives equality of the two displayed source surfaces.
\end{proof}

\begin{theorem}[RegSeqRat refined-window gluing RealUp seal factorization]
\label{thm:regseqrat-refined-window-gluing-real-seal-factorization}
Let $W_0$ and $W_1$ be accepted finite $\RegSeqRatUp$ windows whose displayed
$\StreamNameUp$ schedules admit a common refined window $W_\cup$ as in
\autoref{thm:regseqrat-refined-window-gluing}. Suppose the overlap hypotheses
identify the shared unary index rows, $\DyadicRatCoreUp$ endpoint rows,
dyadic-radius rows, regularity ledgers, classifier ledgers, $\hsame$
comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert$
provenance on $W_\cup$. Then the common refined window $W_\cup$ is exactly the
finite $\mathsf{BHist}$ source surface consumed by the $\RealUp$ seal handoff
of \autoref{thm:regseqrat-real-seal-handoff}.

Equivalently, composing refined-window gluing with the $\RealUp$ seal handoff
factors through the displayed finite BEDC packet $W_\cup$. The composition
introduces no quotient stream, host real equality, metric completeness,
completion point, or seal datum beyond the finite rows already present in
$W_\cup$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-refined-window-gluing} to the two accepted
windows. The result is one accepted finite $\RegSeqRatUp$ window over
$W_\cup$ whose union schedule, unary indices, endpoint rows, dyadic-radius
rows, regularity ledgers, provenance rows, and classifier readback restrict to
the two source windows.

Use the classifier window-pairing row of
\autoref{thm:regseqrat-classifier-window-pairing} on the refined window. It
identifies the shared endpoint observations and radius observations as the
same displayed $\DyadicRatCoreUp$ rows inside the common finite packet, so the
two source reads cannot supply separate seal-facing data.

Finally apply \autoref{thm:regseqrat-real-seal-handoff}. The handoff consumes
exactly the accepted finite regular-rational source surface just produced by
the gluing theorem, and therefore reads $W_\cup$ itself as the $\RealUp$ finite
seal source. Since every consumed coordinate is already a displayed
$\mathsf{BHist}$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, or $\NameCert$ row of $W_\cup$, the composition has no route to
a quotient stream, host real equality, metric-completion object, completion
point, or extra seal datum.
\end{proof}

\begin{theorem}[RegSeqRat common-window RealUp seal transitivity]
\label{thm:regseqrat-common-window-real-seal-transitivity}
Let $W_0$, $W_1$, and $W_2$ be accepted finite $\RegSeqRatUp$ windows. Suppose
the $W_0/W_1$ and $W_1/W_2$ refined-window gluing surfaces identify the middle
unary index rows, $\DyadicRatCoreUp$ endpoint rows, dyadic-radius rows,
regularity ledgers, classifier ledgers, $\hsame$ comparisons, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and $\NameCert$ provenance on a shared common
refinement. Then the composed $W_0/W_2$ handoff factors through the same
finite $\mathsf{BHist}$ source surface consumed by the $\RealUp$ seal.

Equivalently, the two common-window legs determine one seal-facing finite
packet: its source rows are exactly the shared unary observations,
DyadicRatCore endpoints, radius rows, regularity and classifier ledgers,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance read on the
common refinement. The composed handoff exports no quotient stream, host real
equality, metric completeness, completion point, or seal datum beyond that
finite source surface.
\end{theorem}
\begin{proof}
Project both legs with \autoref{thm:regseqrat-refined-window-gluing}. The
$W_0/W_1$ leg gives one accepted refined packet whose restrictions recover
$W_0$ and $W_1$, and the $W_1/W_2$ leg gives one accepted refined packet whose
restrictions recover $W_1$ and $W_2$.

Use \autoref{thm:regseqrat-common-refinement-classifier-determinacy} on the
middle window. The middle unary observations, endpoint rows, radius rows,
regularity ledgers, classifier ledgers, and provenance rows are the same
finite read, so the two legs share one common packet rather than two
seal-facing sources.

Apply \autoref{thm:regseqrat-tail-seal-diagonal-window-coherence} and
\autoref{thm:regseqrat-real-seal-handoff}. The diagonal finite read is the
$\mathsf{BHist}$ source surface consumed by the $\RealUp$ seal, and the seal
handoff reads only that finite regular-rational packet.

Finally invoke
\autoref{thm:regseqrat-refined-window-gluing-real-seal-factorization} on the
composed common packet. The $W_0/W_2$ handoff therefore factors through the
same finite source surface, with no coordinate for quotient streams, host real
equality, metric completeness, completion points, or additional seal data.
\end{proof}

\begin{theorem}[RegSeqRat refined-window chain exhaustion]
\label{thm:regseqrat-refined-window-chain-exhaustion}
Let $W_0,W_1,\ldots,W_n$ be a finite chain of accepted $\RegSeqRatUp$
scheduled windows. Suppose every consecutive overlap agrees on the
$\StreamNameUp$ schedule rows, $\DyadicRatCoreUp$ endpoint and radius rows,
regularity ledgers, classifier ledgers, $\hsame$ comparisons, $\Cont$ routes,
$\Pkg$ provenance, and $\NameCert$ provenance. Then the chain repacks into one
accepted common finite window, and every terminal $\RealUp$ seal read from the
chain factors through that common packet.

The common packet exposes only the displayed regular-rational source rows just
listed. It does not introduce quotient sequence equality, host real equality,
metric completion, or completeness data.
\end{theorem}
\begin{proof}
Induct on the finite chain of scheduled windows. The first adjacent link is
handled by \autoref{thm:regseqrat-refined-window-gluing}, which repacks two
accepted windows into one accepted finite refinement over the shared schedule,
endpoint, radius, ledger, transport, and provenance rows.

In the step, the induction hypothesis supplies one accepted common packet for
the initial segment. Apply
\autoref{thm:regseqrat-common-refinement-classifier-determinacy} on the overlap
with the next scheduled window. The determinacy row identifies the shared
$\StreamNameUp$ schedule, $\DyadicRatCoreUp$ endpoint and radius data,
regularity ledger, classifier ledger, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows as one finite read.

Use \autoref{thm:regseqrat-refined-window-gluing} again to glue the next window
to the common packet. This preserves acceptedness and produces the next common
finite window without adding any off-surface sequence, host-real, completion,
or completeness coordinate.

Finally apply \autoref{thm:regseqrat-real-seal-handoff}. Since the $\RealUp$
terminal seal consumes only the accepted finite regular-rational packet, every
seal read from the original chain factors through the repacked common window.
\end{proof}

\begin{theorem}[RegSeqRat StreamName cover-refinement seal handoff]
\label{thm:regseqrat-streamname-cover-refinement-seal-handoff}
Let $\mathcal W$ be a finite cover family of public $\StreamNameUp$ windows
over one observation map, and let $P$ be an accepted $\RegSeqRatUp$ packet
whose scheduled reads consume every member of $\mathcal W$. If a finite-window
$\RealUp$ seal handoff is read from the same packet, then that seal-facing
read factors through exactly the public $\StreamNameUp$ finite-window
interface together with the displayed $\mathsf{InBundle}$ rows, pointwise
$\RatUp$ classifier rows, the $\DyadicRatCoreUp$ denominator ledger, $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ provenance exposed by $P$.

Thus the cover-refinement handoff supplies no quotient stream, host real
equality, hidden limit selector, metric-completeness datum, or $\RealUp$
completeness row beyond the finite public window interface and its displayed
regular-rational ledgers.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-cover-refinement-exhaustion}. The finite
cover family over the common observation map is exhausted by public
$\StreamNameUp$ finite-window rows, so every covered read is already visible
through the public window interface and its $\mathsf{InBundle}$ membership
rows.

Next use \autoref{thm:regseqrat-streamname-dyadic-seal-refinement-lock}. For
each covered window consumed by $P$, the public schedule rows lock to the
same pointwise $\RatUp$ classifier rows and to the
$\DyadicRatCoreUp$ denominator ledger carried by the accepted regular-rational
packet.

Now apply \autoref{thm:regseqrat-tail-seal-diagonal-window-coherence}. The
finite cover refinements and the shifted diagonal reads present one coherent
finite $\mathsf{BHist}$ surface, with the same $\hsame$, $\Cont$, and
$\mathsf{Pkg}$ rows wherever the cover windows overlap.

Finally invoke \autoref{thm:regseqrat-real-seal-handoff}. The $\RealUp$ seal
consumes only that finite regular-rational source surface, so the handoff
factors through the public $\StreamNameUp$ finite-window interface and cannot
read a quotient stream, host real equality, hidden limit selector, metric
completion, or $\RealUp$ completeness coordinate.
\end{proof}

\begin{theorem}[RegSeqRat tail-stable window cover exhaustion]
\label{thm:regseqrat-tail-stable-window-cover-exhaustion}
Let $\mathcal W$ be a finite cover family of public $\StreamNameUp$ windows
over one accepted $\RegSeqRatUp$ packet. If every member of $\mathcal W$ is
stable under shifted-tail regularity closure and the overlaps of
$\mathcal W$ glue by refined-window gluing, then every finite-window
$\RealUp$ seal read over that packet factors through exactly the public
$\StreamNameUp$ windows, the pointwise $\RatUp$ classifier rows, the
$\DyadicRatCoreUp$ denominator and radius ledgers, and the displayed
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.

The factorization exports no quotient stream, host real equality, hidden
limit selector, metric-completeness datum, completion point, or additional
$\RealUp$ seal coordinate beyond the finite tail-stable cover surface.
\end{theorem}
\begin{proof}
Start with the cover-refinement handoff of
\autoref{thm:regseqrat-streamname-cover-refinement-seal-handoff}. It reads the
$\RealUp$ seal only through the public $\StreamNameUp$ finite-window
interface, the displayed $\mathsf{InBundle}$ rows, pointwise $\RatUp$
classifier rows, dyadic denominator ledger, and the stated provenance rows.

Apply \autoref{thm:regseqrat-shifted-tail-regularity-closure} to each window
in the cover. Tail stability keeps the scheduled regularity rows inside the
same accepted $\RegSeqRatUp$ packet after the shifted-tail read, so the seal
cannot leave the finite public cover.

Use \autoref{thm:regseqrat-refined-window-gluing} on every overlap. The
overlap rows glue the public windows into one finite source surface while
preserving the pointwise classifier rows, the dyadic denominator and radius
ledgers, and the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
provenance.

Finally invoke \autoref{thm:regseqrat-real-seal-handoff}. The $\RealUp$ seal
handoff consumes only the finite regular-rational packet just assembled, so
the tail-stable cover exhausts the whole seal-facing source surface and
leaves no off-table quotient, host-equality, completion, or extra seal row to
read.
\end{proof}

