\begin{theorem}[RegSeqRat StreamName Real scope triad]
\label{thm:regseqrat-streamname-real-scope-triad}
For every accepted $\RegSeqRatUp$ carrier $P$, every public $\RealUp$ seal read
of $P$ is exposed through the three visible scope gates
\begin{enumerate}
\item the $\StreamNameUp$ finite observation schedule selecting the requested
windows;
\item the $\DyadicRatCoreUp$ endpoint, radius, distance, and tail-budget rows
read from those windows;
\item the $\RealUp$ seal row that consumes the resulting $\RegSeqRatUp$
regular-Cauchy classifier surface.
\end{enumerate}
The triad preserves the displayed $\hsame$ comparisons, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ rows. It contains no quotient
stream equality, host real equality, selected limit, completion object,
ambient completeness datum, or second seal coordinate.
\end{theorem}
\begin{proof}
Start with the exact handoff of
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. It routes
public seal reads through StreamName schedules, DyadicRatCore ledgers,
RegSeqRat classifier rows, and the public RealUp seal.

Next apply the source lock of
\autoref{thm:regseqrat-streamname-dyadic-source-lock}. The StreamName schedule
and the dyadic endpoint, radius, and distance rows are one finite source
surface attached to the accepted carrier $P$.

Finally use \autoref{thm:regseqrat-real-seal-consumer-factorization}. It
identifies the downstream consumer as the same finite regular-Cauchy route
with its displayed transports, continuations, package provenance, and local
name row. Since those cited surfaces expose only the listed rows, the excluded
quotient, host, completion, and second-seal data cannot enter the triad.
\end{proof}

\begin{theorem}[RegSeqRat finite-request StreamName Real pullback]
\label{thm:regseqrat-finite-request-streamname-real-pullback}
Let $P$ be an accepted $\RegSeqRatUp$ carrier, and let a finite-request
consumer ask for a public $\RealUp$ seal read of $P$. If the consumer's
$\StreamNameUp$ finite section reaches a $\DyadicRatCoreUp$ endpoint, radius,
distance, and tail-budget surface, and if that surface reaches the public
$\RealUp$ seal, then the whole consumer factors through one finite $\BHist$
route:
\begin{enumerate}
\item the $\StreamNameUp$ request section selecting the finite windows;
\item the $\DyadicRatCoreUp$ endpoint, radius, distance, regularity, and
tail-budget rows over those windows;
\item the $\RegSeqRatUp$ classifier and readback rows consuming the dyadic
budget;
\item the $\RealUp$ seal row;
\item the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows carried by
the same packet.
\end{enumerate}
No factor of the route is a quotient stream, selected limit, ambient
completion object, host real equality, ambient completeness theorem, or
standard bridge row.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:regseqrat-streamname-real-scope-triad}. It places any
public seal read behind the StreamName finite observation schedule, the
DyadicRatCore budget rows, and the RealUp seal, while keeping the displayed
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows in view.

Next apply \autoref{thm:regseqrat-dyadic-tail-budget-totality}. The finite
request cannot bypass the endpoint, radius, distance, regularity, classifier,
tail-budget, transport, continuation, package, and local naming rows. Thus the
consumer's dyadic surface is already a finite $\BHist$ route rather than a
host or completion-side comparison.

Finally use \autoref{thm:regseqrat-consumer-seal-unblock-surface}. The scope
triad and the total tail budget are exactly the rows that unblock the public
RealUp handoff. Repacking those rows gives the stated pullback through the
same finite route, and the exclusions follow because none of the cited
surfaces exports quotient streams, selected limits, ambient completion data,
host real equality, ambient completeness, or bridge rows.
\end{proof}

\begin{theorem}[RegSeqRat dyadic tail-budget totality]
\label{thm:regseqrat-dyadic-tail-budget-totality}
Let $P$ be an accepted $\RegSeqRatUp$ carrier, and let a tail-budget consumer
request any completion-facing comparison of $P$. The comparison is total over
the displayed dyadic budget rows: it reads a $\StreamNameUp$ schedule row, the
matching $\DyadicRatCoreUp$ endpoint rows, the requested dyadic radius rows,
the dyadic distance rows, the regularity bound rows, the $\RegSeqRatUp$
classifier rows, componentwise $\hsame$ rows, displayed $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ provenance. No comparison
step has a separate source outside those rows.

Consequently every tail comparison that can feed the $\RealUp$ seal is a read
of the same finite dyadic budget surface, not a quotient-stream comparison,
host real comparison, selected-limit comparison, completion comparison, or
ambient completeness comparison.
\end{theorem}
\begin{proof}
Project the common dyadic tail ledger from
\autoref{thm:regseqrat-common-dyadic-tail-ledger}. It lists the schedule,
endpoint, radius, distance, classifier, regularity, transport, continuation,
package, and naming rows available to tail reads.

Use \autoref{thm:regseqrat-tail-budget-meet-handoff} to order a
completion-facing request through that ledger before any RealUp-facing surface
is visible. The request therefore has no earlier coordinate from which a
completion or host comparison could be read.

Now apply \autoref{thm:regseqrat-tail-budget-terminal-real-seal}. The terminal
surface preserves exactly the same finite dyadic budget rows all the way to
the RealUp seal. Thus the comparison is total over the displayed budget
surface and nowhere else.
\end{proof}

\begin{theorem}[RegSeqRat consumer seal unblock surface]
\label{thm:regseqrat-consumer-seal-unblock-surface}
For an accepted $\RegSeqRatUp$ carrier $P$, the downstream $\RealUp$ handoff
surface is unblocked precisely by the two rows supplied by
\autoref{thm:regseqrat-streamname-real-scope-triad} and
\autoref{thm:regseqrat-dyadic-tail-budget-totality}: the StreamName--RegSeqRat--RealUp
scope triad and the total dyadic tail-budget surface. Once these rows are
present, every public RealUp consumer reads the finite regular-Cauchy packet
through the visible $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$ faces, preserving $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ provenance.

The unblock surface is only this downstream handoff. It does not provide a
quotient stream, host real equality, selected limit, metric-completion object,
ambient completeness theorem, or bridge-checked RealUp consumer.
\end{theorem}
\begin{proof}
First assemble the scope row using
\autoref{thm:regseqrat-streamname-real-scope-triad}. This places every public
seal read behind the StreamName schedule, the dyadic observation budget, and
the RealUp seal.

Next assemble the budget row using
\autoref{thm:regseqrat-dyadic-tail-budget-totality}. It says that every
tail-budget comparison available to a completion-facing consumer is already a
read of the displayed dyadic ledger.

Finally combine the public consumer factorization of
\autoref{thm:regseqrat-real-seal-consumer-factorization} with the terminal
seal surface of \autoref{thm:regseqrat-tail-budget-terminal-real-seal}. These
facts package the scope row and the budget row as the downstream RealUp
handoff. Since the package exposes no quotient, host, selected-limit,
completion, completeness, or bridge-checked coordinate, the consumer is
unblocked exactly at the stated finite surface.
\end{proof}
