\begin{theorem}[RegSeqRat StreamName Dyadic Real handoff exactness]
\label{thm:regseqrat-streamname-dyadic-real-handoff-exactness}
For every accepted $\RegSeqRatUp$ carrier, any public $\RealUp$ seal consumer
of that carrier factors exactly through the finite route
\begin{enumerate}
\item the $\StreamNameUp$ schedule rows selecting the visible finite windows;
\item the $\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance rows read
from those windows;
\item the $\RegSeqRatUp$ classifier rows over the same scheduled dyadic
observations;
\item the $\RealUp$ seal rows consuming that finite classifier surface.
\end{enumerate}
The factorization preserves the displayed $\hsame$ comparisons, $\Cont$
routes, $\mathsf{Pkg}$ provenance, and local $\NameCert$ rows at every stage.
No quotient stream, host real equality, selected limit, metric-completion
object, ambient completeness datum, or extra seal coordinate can enter the
handoff.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regseqrat-stream-carrier} and the
classifier of \autoref{def:regseqrat-classifier}. Their visible rows are the
scheduled $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ endpoint and radius
reads, the finite dyadic-distance rows, regularity rows, classifier rows,
and the attached $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$
provenance.

Apply \autoref{thm:regseqrat-window-regularity-ledger} to the schedule side
and \autoref{thm:regseqrat-dyadic-radius-observation} to the classifier side.
Together they identify the endpoint, radius, distance, and regularity rows as
rows of the same finite scheduled observation package.

Transport that package through
\autoref{thm:regseqrat-finite-window-transport-obligation}. The transport
keeps the schedule, endpoint, radius, distance, regularity, classifier,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows componentwise, so the
consumer has no alternative finite source surface available.

Finally use \autoref{thm:regseqrat-real-seal-handoff},
\autoref{thm:regseqrat-real-seal-classifier-factorization}, and
\autoref{thm:regseqrat-real-seal-public-handoff-determinacy}. The first
theorem routes the accepted regular-rational source to the $\RealUp$ seal,
the second makes the classifier factorization explicit, and the third locks
the public consumer to the same finite schedule and replay ledger. Since the
cited surfaces expose only the displayed finite rows, there is no coordinate
for quotient streams, host real equality, selected limits, completion
objects, ambient completeness data, or an additional seal route.
\end{proof}

\begin{theorem}[RegSeqRat StreamName Dyadic Real handoff single-source lock]
\label{thm:regseqrat-streamname-dyadic-real-handoff-single-source-lock}
Let two public $\RealUp$ seal consumers read the same accepted
$\RegSeqRatUp$ carrier through displayed $\StreamNameUp$ schedules and
$\DyadicRatCoreUp$ endpoint and radius ledgers. Then both seal reads factor
through one finite source route: the schedule rows, dyadic endpoint rows,
dyadic radius rows, $\RegSeqRatUp$ classifier rows, regularity rows,
$\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and local
$\NameCert$ rows attached to that carrier.

The lock exposes no quotient stream, host real equality, selected limit,
metric-completeness datum, or extra $\RealUp$ seal coordinate. A consumer that
requests any of those objects has left the displayed source route rather than
reading a second seal source.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}.
It routes each public $\RealUp$ seal read through the same four-stage
StreamName, DyadicRatCore, RegSeqRat, and Real seal path, preserving the
displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows.

Next apply \autoref{thm:regseqrat-l10-source-lattice-pointer}. The L10 source
lattice records the finite schedule rows, dyadic endpoint and radius rows,
classifier rows, regularity rows, transports, routes, provenance, and naming
rows as one visible source packet. Since both consumers start from the same
accepted carrier, their displayed schedules and dyadic ledgers point into that
same packet.

Finally use \autoref{thm:regseqrat-real-seal-handoff},
\autoref{thm:regseqrat-real-seal-classifier-factorization}, and
\autoref{thm:regseqrat-real-seal-public-handoff-determinacy}. These seal
handoff results identify the public read with the regular-rational classifier
surface and rule out a second public seal source. The excluded quotient,
host-equality, selected-limit, completeness, and extra-coordinate data have no
row in the route just assembled, so the two seal consumers are locked to one
finite source route.
\end{proof}

\begin{theorem}[RegSeqRat StreamName Dyadic Real source-seal correspondence]
\label{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence}
For an accepted $\RegSeqRatUp$ carrier read through displayed
$\StreamNameUp$ schedules and $\DyadicRatCoreUp$ endpoint and radius ledgers,
the public $\RealUp$ seal route is equivalent, as a finite BEDC route, to the
four-stage route
\begin{enumerate}
\item $\StreamNameUp$ finite-window rows selecting the scheduled observations;
\item $\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance rows read from
those windows;
\item $\RegSeqRatUp$ classifier and regularity rows over the same finite
dyadic observations;
\item the $\RealUp$ seal row that consumes that classifier surface.
\end{enumerate}
The correspondence is bidirectional at the level of displayed rows: every
public seal read factors through the four-stage route, and every such
four-stage route determines the same public seal read for the accepted
carrier. It introduces no quotient stream, host real equality, selected limit,
ambient completeness datum, or hidden seal coordinate.
\end{theorem}
\begin{proof}
For the forward direction, apply
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. A public
$\RealUp$ seal read is routed through StreamName schedules, DyadicRatCore
endpoint and radius ledgers, RegSeqRat classifier rows, and the public seal,
while preserving the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ rows.

Next lock the source by
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-single-source-lock}. The
same accepted carrier supplies one finite source packet for all public seal
reads, so the route cannot branch into a second completion object or an
unstated equality of streams.

For the reverse direction, read the four displayed stages through the
Lean-facing anchors
\texttt{RatStreamNameFiniteWindowClassifier\_singleton\_diagonal\_handoff},
\texttt{DyadicRatCoreCarrier\_regseqrat\_bridge\_handoff\_exactness}, and
\texttt{RegSeqRatStreamCarrier\_real\_seal\_handoff}. These anchors match the
paper route from finite window rows to dyadic radius rows, from dyadic ledgers
to the RegSeqRat classifier, and from that classifier to the public Real seal.

The two directions have the same displayed coordinates. Since neither the
paper handoff theorems nor the Lean-facing handoff anchors expose quotient
streams, host real equality, selected limits, ambient completeness, or hidden
seal data, the correspondence is exactly the finite source-seal route stated
above.
\end{proof}

\begin{theorem}[RegSeqRat StreamName Dyadic Real triple exactness]
\label{thm:regseqrat-streamname-dyadic-real-triple-exactness}
For an accepted $\RegSeqRatUp$ carrier, the public $\RealUp$ seal route is
exactly the common finite triple surface consisting of the $\StreamNameUp$
schedule rows, the $\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance
rows, and the $\RegSeqRatUp$ classifier and regularity rows, with the $\RealUp$
seal as the consumer of that surface. The certificate preserves precisely the
displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows.

The triple surface contains no quotient stream, host real equality, selected
limit, metric-completion object, ambient completeness datum, choice datum, or
second $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. It gives
the four-stage public seal route and identifies the StreamName, DyadicRatCore,
RegSeqRat, and RealUp rows read by the consumer.

Next apply
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-single-source-lock}. The
schedule, dyadic ledger, classifier, regularity, transport, continuation,
package, and naming rows all come from one finite source route attached to the
accepted carrier.

Use \autoref{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence} to
read the public Real seal route and the displayed finite source-seal route in
both directions. Finally apply \autoref{thm:regseqrat-common-dyadic-tail-ledger}
to place cofinal tail reads on the same dyadic ledger whenever a tail
refinement is presented.

These four inputs leave exactly the triple surface named in the statement, with
the $\RealUp$ seal as its consumer. Their exclusion clauses remove quotient
streams, host real equality, selected limits, metric-completion objects,
ambient completeness data, choice data, and second seal coordinates.
\end{proof}

\begin{theorem}[RegSeqRat common dyadic tail ledger]
\label{thm:regseqrat-common-dyadic-tail-ledger}
Let $P$ be an accepted $\RegSeqRatUp$ carrier. Suppose two finite
$\StreamNameUp$ tail-window reads of $P$ feed public $\RealUp$ seal consumers,
and suppose the two reads admit a common cofinal dyadic refinement. Then the
two seal routes factor through one common finite ledger. This ledger consists
exactly of the $\StreamNameUp$ schedule rows, the $\DyadicRatCoreUp$ endpoint,
radius, and distance rows on the common refinement, the $\RegSeqRatUp$
classifier and regularity rows, componentwise $\hsame$ rows, displayed $\Cont$
routes, $\mathsf{Pkg}$ provenance, and local $\NameCert$ rows attached to $P$.

The common ledger is a displayed finite $\mathsf{BHist}$ route. It is not a
quotient stream equality, host real equality, selected limit, choice datum,
ambient completeness witness, or second $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness} to each
of the two tail-window reads. Each public seal consumer is thereby routed
through the same four surfaces: the $\StreamNameUp$ schedule rows,
$\DyadicRatCoreUp$ endpoint, radius, and distance rows, $\RegSeqRatUp$
classifier and regularity rows, and the $\RealUp$ seal rows consuming that
finite source surface.

Next apply
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-single-source-lock}. Since
both reads start from the same accepted carrier $P$, the two public seal
consumers have one displayed source route, with the same componentwise
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows.

It remains to identify the shared cofinal refinement as finite ledger data.
Use \autoref{thm:regseqrat-l10-source-lattice-pointer} to place the schedule,
endpoint, radius, classifier, regularity, transport, route, provenance, and
naming rows inside one visible L10 source packet.

Finally apply \autoref{thm:regseqrat-window-regularity-ledger},
\autoref{thm:regseqrat-dyadic-radius-observation}, and
\autoref{thm:regseqrat-dyadic-radius-ledger-readback}. These facts read the
cofinal dyadic refinement as displayed endpoint, radius, distance, and
regularity rows of the same finite packet. No step creates a host completion
object, selected limit, choice datum, quotient stream equality, host real
equality, or second seal coordinate, so the common tail route is exactly the
finite ledger stated above.
\end{proof}

\begin{theorem}[RegSeqRat Real seal window triple correspondence]
\label{thm:regseqrat-real-seal-window-triple-correspondence}
Let $P$ be an accepted $\RegSeqRatUp$ carrier read through a finite
$\StreamNameUp$ schedule. Suppose the displayed $\DyadicRatCoreUp$ endpoint,
radius, and dyadic-distance rows for that schedule feed the public $\RealUp$
seal consumer of $P$. Then the following four finite BEDC surfaces mutually
determine one another:
\begin{enumerate}
\item the $\StreamNameUp$ schedule rows and membership rows;
\item the $\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance rows;
\item the $\RegSeqRatUp$ classifier, regularity, and transport rows;
\item the public $\RealUp$ seal consumer row.
\end{enumerate}
Equivalently, any one of these displayed finite-window surfaces determines the
same $\mathsf{BHist}$ route through the other three, with the same
componentwise $\hsame$ rows, displayed $\Cont$ routes, $\mathsf{Pkg}$
provenance, and local $\NameCert$ rows. The correspondence contains no
quotient stream, host real equality, selected limit, ambient completeness
witness, choice datum, or hidden seal coordinate.
\end{theorem}
\begin{proof}
Start with
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. It gives the
finite route from the accepted carrier through the $\StreamNameUp$ schedule,
the $\DyadicRatCoreUp$ endpoint, radius, and distance rows, the
$\RegSeqRatUp$ classifier surface, and the public $\RealUp$ seal consumer.

Apply
\autoref{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence} to
read the route in both directions. The public seal read determines the
finite source surface, and the finite source surface determines the same
public seal read, without adding completion data or external equality.

Next use \autoref{thm:regseqrat-streamname-dyadic-real-triple-exactness}. It
identifies the schedule, dyadic ledger, and RegSeqRat classifier/regularity
surfaces as one exact triple surface whose consumer is the public $\RealUp$
seal row.

Finally apply \autoref{thm:regseqrat-common-dyadic-tail-ledger}. Whenever the
finite schedule is viewed through a common cofinal dyadic refinement, the same
schedule rows, endpoint rows, radius rows, distance rows, classifier rows,
regularity rows, transports, continuations, package provenance, and naming
rows are read back as one common $\mathsf{BHist}$ ledger. Thus each of the
four displayed surfaces recovers the same route through the other three.

All cited inputs expose only finite rows of the BEDC route. They provide no
coordinate for quotient streams, host real equality, selected limits, ambient
completeness, choice data, or hidden seal data, so the correspondence is
exactly the finite Real seal route stated above.
\end{proof}

\begin{theorem}[RegSeqRat L10 four-face necessity]
\label{thm:regseqrat-l10-four-face-necessity}
A current Phase Real and Completion exit read for an accepted $\RegSeqRatUp$
carrier requires all four displayed faces:
\begin{enumerate}
\item the $\StreamNameUp$ finite schedule and membership rows;
\item the $\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance ledgers;
\item the $\RegSeqRatUp$ classifier, regularity, and transport rows;
\item the public $\RealUp$ seal row.
\end{enumerate}
Removing any one of these faces breaks the finite BEDC route from the L10
source lattice to the completion-facing seal. Conversely, the four faces
together suffice for the exit read by the handoff exactness, source-seal
correspondence, triple exactness, window triple correspondence, and L10 source
lattice pointer results.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-l10-source-lattice-pointer}. It places the
accepted $\RegSeqRatUp$ carrier on the finite source lattice whose public
route must pass through scheduled windows, dyadic ledger rows, regular
sequence classifier rows, and the completion-facing seal.

Use \autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. The
handoff theorem displays the same route as an ordered finite passage through
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$. If the
schedule face is removed, the window route has no finite source index. If the
dyadic face is removed, the endpoint, radius, and distance ledgers cannot be
read. If the RegSeqRat face is removed, the classifier and regularity rows are
not available. If the Real face is removed, the public seal consumer has no
finite target row.

Now apply
\autoref{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence} and
\autoref{thm:regseqrat-streamname-dyadic-real-triple-exactness}. The first
identifies the source and seal reads as the same finite public route, while
the second binds the schedule, dyadic ledger, and RegSeqRat classifier faces
as one exact triple before the seal is consumed.

Finally use
\autoref{thm:regseqrat-real-seal-window-triple-correspondence}. It states that
each of the four displayed faces recovers the same $\mathsf{BHist}$ route
through the other three. Thus each face is necessary for the finite exit
route, and all four together are sufficient without adding quotient streams,
host real equality, selected limits, ambient completeness, choice data, or
hidden seal coordinates.
\end{proof}

\begin{theorem}[RegSeqRat Real seal finite-window saturation]
\label{thm:regseqrat-real-seal-finite-window-saturation}
Every accepted public $\RegSeqRatUp$ read that exits as a $\RealUp$ seal for
Phase Real and Completion is saturated by exactly four finite faces:
\begin{enumerate}
\item the $\StreamNameUp$ schedule and membership rows;
\item the $\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance ledgers;
\item the $\RegSeqRatUp$ classifier, regularity, and transport rows;
\item the public $\RealUp$ seal row.
\end{enumerate}
No fifth face is available to the exit read. In particular, the saturated
route contains no quotient stream, host real equality, selected limit,
ambient completeness witness, choice datum, or hidden seal coordinate beyond
the displayed $\mathsf{BHist}$, componentwise $\hsame$, $\Cont$, $\Pkg$, and
local $\NameCert$ rows.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:regseqrat-l10-four-face-necessity}. It shows that a
Phase Real and Completion exit read requires the schedule, dyadic ledger,
RegSeqRat classifier, and public seal faces, and that those four faces
suffice for the L10 exit route.

Use
\autoref{thm:regseqrat-real-seal-window-triple-correspondence}. It identifies
each displayed face with the same finite $\mathsf{BHist}$ route through the
other three, so any accepted public seal read already recovers the schedule,
dyadic, classifier, transport, and seal rows without an extra coordinate.

Next apply \autoref{thm:regseqrat-common-dyadic-tail-ledger}. It keeps common
cofinal dyadic refinements on the same endpoint, radius, distance,
classifier, regularity, transport, continuation, provenance, and local naming
ledger. Thus refinements do not create an additional face.

Finally use
\autoref{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence}. It
ties the finite source read to the public seal read in both directions. The
only surfaces exported to the seal are the four listed faces, and the
excluded quotient, host equality, selected-limit, completeness, choice, and
hidden-coordinate data have no row in the accepted route.
\end{proof}

\begin{theorem}[RegSeqRat StreamName Dyadic Real Lean anchor audit surface]
\label{thm:regseqrat-streamname-dyadic-real-lean-anchor-audit-surface}
For an accepted $\RegSeqRatUp$ carrier whose public seal route is saturated by
the four faces $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$, the Lean-facing anchors
\texttt{RatStreamNameFiniteWindowClassifier\_singleton\_diagonal\_handoff},
\texttt{DyadicRatCoreCarrier\_regseqrat\_bridge\_handoff\_exactness}, and
\texttt{RegSeqRatStreamCarrier\_real\_seal\_handoff} expose exactly the same
finite audit surface. Concretely, they expose the StreamName finite-window
membership surface, the DyadicRatCore endpoint, radius, and distance handoff
surface, and the RegSeqRat-to-Real public seal handoff surface. No additional
audit coordinate is supplied by a quotient stream, host real equality, selected
limit, ambient completeness witness, choice datum, or hidden seal coordinate.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence}. It
identifies the accepted carrier's finite source route with the public seal
route and already names the three Lean-facing anchors as the route from
finite-window rows to dyadic rows, from dyadic rows to the RegSeqRat
classifier, and from that classifier to the public Real seal.

Next use \autoref{thm:regseqrat-l10-four-face-necessity}. It shows that a
Phase Real and Completion exit read requires exactly the StreamName schedule,
DyadicRatCore ledger, RegSeqRat classifier, and Real seal faces for the L10
route. Thus the first two anchors cover the first-three-face passage through
StreamName, DyadicRatCore, and RegSeqRat, while the third anchor covers the
terminal seal passage into $\RealUp$.

Finally apply
\autoref{thm:regseqrat-real-seal-finite-window-saturation}. The saturated
route has no fifth face, and the excluded quotient stream, host real equality,
selected limit, ambient completeness, choice datum, and hidden seal coordinate
have no displayed row. Therefore the three named anchors are exactly the
finite audit surface that remains to be formalized for the four-face route.
\end{proof}

\begin{theorem}[RegSeqRat Real seal finite-cover gluing]
\label{thm:regseqrat-real-seal-finite-cover-gluing}
Let $\{\mathcal{S}_i\}_{i\in I}$ be a finite family of accepted public
$\RegSeqRatUp$ reads whose members exit as $\RealUp$ seals. Suppose each
$\mathcal{S}_i$ is saturated by exactly the four displayed faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp.
$$
Suppose also that every displayed pairwise overlap agrees on the shared
$\mathsf{BHist}$, componentwise $\hsame$, $\Cont$, $\Pkg$, $\NameCert$,
dyadic-ledger, classifier, regularity, and seal rows. Then the finite family
glues to one finite four-face L10 packet over the finite union of the
requests, with the same four faces and only the displayed
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.
The glued packet contains no quotient stream equality, no host real equality,
no selected limit, no ambient or metric-completeness datum, no choice data,
and no second $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
For each family member, apply
\autoref{thm:regseqrat-real-seal-finite-window-saturation}. This places the
member on one finite L10 exit route whose only faces are the StreamName
schedule, DyadicRatCore ledger, RegSeqRat classifier and regularity surface,
and Real seal row.

Glue the StreamName windows first. The overlap hypotheses identify the
displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, dyadic,
RegSeqRat, and Real rows seen from adjacent members, so
\autoref{thm:streamname-finite-request-cover-gluing} gives one finite
StreamName-side request packet over the finite union.

Next keep the Real consumer on that same finite section. Use
\autoref{thm:real-regseqrat-finite-request-fusion} to repack each seal request
through the displayed finite $\mathsf{BHist}$ packet, and use
\autoref{thm:real-regseqrat-completion-consumer-section-exactness} to force
every completion-facing or $\RealUp$-facing consumer to factor through that
section.

It remains to identify the dyadic and RegSeqRat faces on overlaps. Apply
\autoref{thm:regseqrat-common-dyadic-tail-ledger} to keep common cofinal
dyadic refinements on the same endpoint, radius, distance, classifier,
regularity, transport, continuation, provenance, and local naming ledger.
Then apply
\autoref{thm:regseqrat-real-seal-window-triple-correspondence} to recover each
of the four faces from the other three inside the same finite route.

Finish by finite induction over the request family. The empty cover gives the
empty displayed packet, and adjoining one saturated member uses the pairwise
overlap agreement above to attach it to the packet already built. At each
step the cited saturation, StreamName gluing, Real fusion, and consumer
section theorems export only the four displayed faces and their support rows,
so quotient stream equality, host real equality, selected limits, ambient or
metric completeness, choice data, and a second seal coordinate remain absent.
\end{proof}

\begin{theorem}[RegSeqRat Real seal finite-cover associativity]
\label{thm:regseqrat-real-seal-finite-cover-associativity}
Let $\mathcal{A}$, $\mathcal{B}$, and $\mathcal{C}$ be finite families of
accepted public $\RegSeqRatUp$ reads whose members exit as $\RealUp$ seals.
Assume that every member is saturated by the same four displayed faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp,
$$
and that every pairwise overlap among the three families satisfies the
four-face agreement used in
\autoref{thm:regseqrat-real-seal-finite-cover-gluing}. Then gluing
$\mathcal{A}\cup\mathcal{B}$ first and then gluing with $\mathcal{C}$ displays
the same finite four-face L10 packet as gluing $\mathcal{B}\cup\mathcal{C}$
first and then gluing with $\mathcal{A}$.

The common packet has exactly the StreamName schedule and membership face, the
DyadicRatCore endpoint, radius, and distance face, the RegSeqRat classifier,
regularity, and transport face, and the RealUp seal face, with the same
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. It
contains no quotient stream equality, no host real equality, no selected limit,
no ambient or metric-completeness datum, no choice data, and no second
$\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:regseqrat-real-seal-finite-cover-gluing} to
$\mathcal{A}\cup\mathcal{B}$ and then to
$(\mathcal{A}\cup\mathcal{B})\cup\mathcal{C}$. Apply the same theorem to
$\mathcal{B}\cup\mathcal{C}$ and then to
$\mathcal{A}\cup(\mathcal{B}\cup\mathcal{C})$. The overlap hypotheses are
exactly the hypotheses of the binary gluing theorem for each of these steps.

For every member used in either parenthesization, apply
\autoref{thm:regseqrat-real-seal-finite-window-saturation}. This identifies
the member with the same StreamName schedule and membership row, DyadicRatCore
endpoint, radius, and distance row, RegSeqRat classifier, regularity, and
transport row, and Real seal row.

The only remaining issue is overlap agreement after the intermediate gluing
step. Use
\autoref{thm:regseqrat-real-seal-window-triple-correspondence} to read any
three of the four faces as the same fourth face inside the finite route, and
use \autoref{thm:regseqrat-common-dyadic-tail-ledger} to keep the dyadic and
RegSeqRat ledger fixed on common cofinal tails. Thus both intermediate packets
present the same finite $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$,
$\NameCert$, endpoint, radius, distance, classifier, regularity, transport,
and seal rows on every overlap.

Conclude by finite induction over the members of $\mathcal{C}$ after the first
parenthesization, and symmetrically over the members of $\mathcal{A}$ after
the second parenthesization. The base case is the already glued binary packet.
The adjoining step attaches one saturated member along the overlap rows just
identified, so it cannot introduce a new face or a different support row. Hence
both parenthesizations expose the same finite BEDC rows and no extra route.
\end{proof}

\begin{theorem}[RegSeqRat StreamName Dyadic Real audit-clean exit readiness]
\label{thm:regseqrat-streamname-dyadic-real-audit-clean-exit-readiness}
For any accepted public L10 exit read of a $\RegSeqRatUp$ carrier, audit-clean
readiness for the Phase Real and Completion quartet is exactly the finite
four-face route through the $\StreamNameUp$ finite schedules, the
$\DyadicRatCoreUp$ dyadic endpoint, radius, and distance ledgers, the
$\RegSeqRatUp$ classifier, regularity, and transport rows, and the public
$\RealUp$ seal row.

The readiness surface contains only the displayed $\mathsf{BHist}$,
componentwise $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ support
rows for those four faces. It contains no Real completeness theorem, no quotient
representative, no host sequence equality, no trichotomy principle, no
open-cover compactness object, and no second $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
Start with
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. It routes the
accepted public seal read through the StreamName schedule face, the DyadicRatCore
ledger face, the RegSeqRat classifier and regularity face, and the public Real
seal face while preserving the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ rows.

Next apply
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-single-source-lock} and
\autoref{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence}. The
single-source lock prevents a second completion source, and the correspondence
identifies the finite source read with the public seal read in both directions.
Thus the exit criterion can read only the same finite rows from either side.

Use \autoref{thm:regseqrat-l10-four-face-necessity} together with
\autoref{thm:regseqrat-real-seal-finite-window-saturation}. These results say
that all four faces are required and that no fifth face is available to an
accepted Phase Real and Completion exit read.

Finally apply \autoref{thm:regseqrat-real-seal-finite-cover-gluing} and
\autoref{thm:regseqrat-real-seal-finite-cover-associativity}. Finite families of
accepted reads glue and reassociate without changing the StreamName,
DyadicRatCore, RegSeqRat, or Real seal rows, so audit-clean Lean work should
target this finite route. Stronger off-table claims about Real completeness,
quotient representatives, host sequence equality, trichotomy, open-cover
compactness, or a second Real seal coordinate are not part of the exit-readiness
surface.
\end{proof}

\begin{theorem}[RegSeqRat Real seal terminal-section exhaustion]
\label{thm:regseqrat-real-seal-terminal-section-exhaustion}
Every terminal public $\RealUp$ seal section of an accepted
$\RegSeqRatUp$ carrier is exhausted by the same finite L10 route through the
four displayed faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp.
$$
The exhausted section consists exactly of the displayed $\mathsf{BHist}$,
componentwise $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows,
together with the StreamName finite-window schedules, the DyadicRatCore
endpoint, radius, and distance ledgers, the RegSeqRat classifier, regularity,
and transport rows, and the public Real seal row.

No terminal section produced by this route contains a Real completeness
theorem, quotient representative, host equality, trichotomy principle,
open-cover compactness datum, choice datum, or second seal coordinate.
\end{theorem}
\begin{proof}
Begin with
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. It presents
the accepted carrier's public seal read as a finite passage from StreamName
finite-window schedules through DyadicRatCore ledgers and RegSeqRat classifier
data to the public Real seal row.

Next use
\autoref{thm:regseqrat-streamname-dyadic-real-source-seal-correspondence}. The
source side and the terminal seal side expose the same displayed section, so a
terminal $\RealUp$ seal section cannot carry rows absent from the finite source
route.

Apply \autoref{thm:regseqrat-l10-four-face-necessity} and
\autoref{thm:regseqrat-real-seal-finite-window-saturation}. Necessity gives the
four required faces, and saturation says the accepted exit read has no fifth
face beyond $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$.

For finite terminal sections, apply
\autoref{thm:regseqrat-real-seal-finite-cover-gluing} and
\autoref{thm:regseqrat-real-seal-finite-cover-associativity}. Gluing turns
overlapping accepted seal reads into one finite packet over the displayed
support rows, and associativity shows that the packet is independent of the
order in which those finite pieces are attached.

Finally apply
\autoref{thm:regseqrat-streamname-dyadic-real-audit-clean-exit-readiness}. Its
negative boundary is exactly the asserted terminal boundary: no Real
completeness theorem, quotient representative, host equality, trichotomy
principle, open-cover compactness datum, choice datum, or second seal
coordinate is part of the terminal public section. Hence every terminal section
is exhausted by the finite four-face route and by no additional BEDC row.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real observation interface]
\label{thm:streamname-regseqrat-real-observation-interface}
For any accepted public L10 exit read of a $\RegSeqRatUp$ carrier, the
$\StreamNameUp$--$\RealUp$ finite-window seal boundary of
\autoref{thm:streamname-realup-finite-window-seal-boundary} is exactly the
input face of the four-face route through $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and $\RealUp$ recorded by
\autoref{thm:regseqrat-real-seal-finite-window-saturation} and
\autoref{thm:regseqrat-streamname-dyadic-real-audit-clean-exit-readiness}.
Thus the public observation interface consumed by the RegSeqRat-to-Real exit is
the finite StreamName window package: the $\mathsf{RatStreamNameCarrier}$ and
$\mathsf{RatStreamNameClassifier}$ rows, finite-window classifier rows,
endpoint readbacks in $\RatUp$, empty-window boundary, and constant/reindexing
stability rows.

This identification introduces no quotient stream, host real equality, selected
limit, ambient completeness witness, choice datum, or second $\RealUp$ seal
coordinate.
\end{theorem}
\begin{proof}
Begin with the StreamName boundary theorem,
\autoref{thm:streamname-realup-finite-window-seal-boundary}. It names exactly
the finite observation rows exposed by the $\StreamNameUp$ public interface and
states that those rows are available to later $\RealUp$ and $\RegSeqRat$ seal
sites without carrying regularity or completion data.

Next apply the RegSeqRat handoff exactness theorem,
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. The handoff
uses the same finite StreamName schedules as its first face before it reads the
DyadicRatCore ledger, the RegSeqRat classifier and regularity rows, and the
public Real seal row.

The four-face necessity and saturation results,
\autoref{thm:regseqrat-l10-four-face-necessity} and
\autoref{thm:regseqrat-real-seal-finite-window-saturation}, then force that
first face to be precisely the public finite-window observation interface. A
different StreamName input would either omit a required face or add a fifth
face, both excluded by the saturated finite route.

Finally use the Real sibling lattice summary,
\autoref{thm:real-regseqrat-streamname-lattice-route}, together with the
audit-clean exit readiness theorem
\autoref{thm:regseqrat-streamname-dyadic-real-audit-clean-exit-readiness}. They
place the Real-facing exit on the same horizontal lattice edge and preserve the
negative boundary: no quotient stream, host real equality, selected limit,
ambient completeness witness, choice datum, or second $\RealUp$ seal coordinate
is introduced.
\end{proof}
