\begin{definition}[RegSeqRat tail-budget packet]
\label{def:regseqrat-tail-budget-packet}
The RegSeqRat tail-budget packet is the finite packet displayed to a $\RealUp$ seal consumer of an accepted $\RegSeqRatUp$ carrier. Its rows are the dyadic observation rows from $\DyadicRatCoreUp$, the StreamName window rows naming the finite request, the regularity-budget rows of the accepted $\RegSeqRatUp$ carrier, the tail-selector rows used by the request, the componentwise transport rows, displayed $\Cont$ continuations, $\Pkg$ provenance, and the local $\NameCert_{\RegSeqRatUp}$ naming row.

The packet has no hidden completion carrier. Its visible data are exactly the tail-budget source rows that feed the public $\RealUp$ seal.
\end{definition}

\begin{theorem}[RegSeqRat tail-budget non-escape]
\label{thm:regseqrat-tail-budget-nonescape}
A $\RealUp$ seal consumer of a RegSeqRat tail-budget packet can read only the displayed dyadic observation rows, StreamName window rows, regularity-budget rows, tail-selector rows, transport, continuation, provenance, and local naming rows of \autoref{def:regseqrat-tail-budget-packet}. It cannot obtain quotient sequence equality, a selected limit, countable choice, or ambient completeness from that packet.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:regseqrat-tail-budget-terminal-real-seal}. It places every completion-facing tail-budget consumer on the finite route through the StreamName schedule, DyadicRatCore ledger, RegSeqRat classifier and regularity rows, displayed support rows, and the public RealUp seal.

Next apply \autoref{thm:regseqrat-shared-window-selector-determinacy}. The shared-window selector is determined by the displayed finite source rows and by the local transport, continuation, provenance, and naming data; hidden selectors and selected limits do not distinguish a second route.

Use \autoref{thm:regseqrat-real-seal-selector-nonescape} to remove the excluded coordinates at the Real-facing boundary. It prevents quotient streams, selected limits, detached completion rows, and second seal data from being exported by the selector surface.

The rows remaining after these references are precisely the packet rows of \autoref{def:regseqrat-tail-budget-packet}. Since no cited boundary supplies quotient sequence equality, a selected limit, countable choice, or ambient completeness, a RealUp seal consumer cannot obtain them from the tail-budget packet.
\end{proof}
