\chapter{A Concrete Naming Certificate for $\CauchyModulusExtractionUp$}
\label{ch:concrete-instances-cauchymodulusextraction-namecert}
\origin{human}

The $\CauchyModulusExtractionUp$ packet records the finite observation-budget surface that a Real-completeness consumer uses before applying the diagonal route of \autoref{ch:visions-real-completeness}. It turns a regular Cauchy input over $\RegSeqRatUp$ into explicit witness schedules, selected stream windows, and dyadic tolerance rows, while keeping the resulting modulus read inside displayed $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\NameCert$ data.

It consumes the finite modulus-indexed schedule exposed by \autoref{ch:concrete-instances-regularcauchywitnessschedule-namecert}: $\RegularCauchyWitnessScheduleUp$ supplies the scheduled $\StreamNameUp$ window, $\RegSeqRatUp$ family row, $\DyadicRatCoreUp$ ledger, and $\RealUp$ seal handoff that this chapter repackages as an extracted modulus.

\begin{definition}[Cauchy modulus-extraction carrier]
\label{def:cauchy-modulus-extraction-carrier}
A $\CauchyModulusExtractionUp$ carrier is a finite $\BHist$ packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the positive tolerance request read through the $\RatUp$ and $\DyadicRatCoreUp$ precision ledgers;
\item $B$ is the finite observation budget selected for the requested tolerance and diagonal scale;
\item $W$ is the $\StreamNameUp$ window family inspected under that budget;
\item $S$ is the $\RegSeqRatUp$ schedule row naming the regular Cauchy witnesses consumed by the diagonal route;
\item $\mathsf{Mu}$ is the extracted modulus row, recording the natural threshold produced from $E,B,W,S$;
\item $Q$ is the $\DyadicRatCoreUp$ comparison and half-radius ledger used to justify the threshold;
\item $H$ records componentwise $\hsame$ transports for the tolerance request, budget, window family, schedule row, modulus row, dyadic ledger, package provenance, and local name;
\item $C$ records the displayed $\Cont$ routes from tolerance to budget, from budget to windows, from windows to schedule reads, from schedule reads to $\mathsf{Mu}$, and from $\mathsf{Mu}$ to the $\RealUp$ diagonal consumer;
\item $P$ is the $\Pkg$ provenance over $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CauchyModulusExtractionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only after transporting the same tolerance request, finite budget, inspected windows, schedule row, extracted modulus, and dyadic ledger to a common Real-completion surface. The carrier contains no host-level limit, no quotient stream equality, no ambient completeness theorem, and no modulus chosen outside the displayed finite budget.
\end{definition}

\begin{theorem}[Cauchy modulus-extraction NameCert obligations]
\label{thm:cauchy-modulus-extraction-namecert-obligations}
The local $\NameCert_{\CauchyModulusExtractionUp}$ surface for \autoref{def:cauchy-modulus-extraction-carrier} consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N)$;
\item budget exposure stating that $B$ is the only finite observation budget available for the tolerance request $E$;
\item schedule extraction stating that $W$ and $S$ are read through $\StreamNameUp$ and $\RegSeqRatUp$ rows before the modulus row $\mathsf{Mu}$ is exported;
\item dyadic soundness stating that $Q$ supplies the positive half-radius and comparison ledgers needed by the extracted threshold;
\item ledger exactness stating that all transport, continuation, package, and naming reads factor through $H,C,P,N$ and no external modulus selector is present.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.CauchyModulusExtractionUp.CauchyModulusExtractionCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-modulus-extraction-carrier}. The tuple lists the tolerance request, finite budget, inspected windows, regular Cauchy schedule, extracted modulus, dyadic ledger, transports, continuations, provenance, and local name.

Budget exposure uses the row $B$. A consumer may inspect only the finite windows listed by that budget, so the modulus row is tied to displayed observation data rather than to an ambient convergence choice.

Schedule extraction uses $W$ and $S$. The $\StreamNameUp$ windows identify the inspected rational observations, while the $\RegSeqRatUp$ schedule row records the regular Cauchy witnesses consumed by the diagonal Real-completion route.

Dyadic soundness is the role of $Q$. It stores the half-radius split and comparison ledger that justify the threshold recorded in $\mathsf{Mu}$ for the requested tolerance.

Finally, $H,C,P,N$ repack the same rows under componentwise transport, route replay, package provenance, and local naming. Since no remaining coordinate contains an external modulus selector, these five obligations exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction budget-window coverage]
\label{thm:cauchy-modulus-extraction-budget-window-coverage}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
every tolerance request $E$ that is accepted by the packet is routed through the finite budget row $B$ before any $\StreamNameUp$ window in $W$ is inspected and before any $\RegSeqRatUp$ schedule row $S$ is used to export $\mathsf{Mu}$. Thus the budget-window surface covers the whole route from requested tolerance to inspected stream data.
\end{theorem}
\begin{proof}
Project the accepted carrier to the displayed tuple. The rows available between the tolerance request and the modulus export are exactly the finite budget $B$, the window family $W$, and the schedule row $S$, together with the dyadic and certificate rows used later in the packet.

Use the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. Budget exposure identifies $B$ as the only finite observation budget available for $E$, and schedule extraction states that $W$ and $S$ are read before $\mathsf{Mu}$ is exported.

It follows that a consumer cannot inspect a StreamName window or use a RegSeqRat schedule directly from the tolerance request. The accepted route first passes through $B$, then through $W$ and $S$, so the finite budget-window surface covers the route to the extracted modulus.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction dyadic ledger positivity]
\label{thm:cauchy-modulus-extraction-dyadic-ledger-positivity}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the dyadic ledger row $Q$ supplies the positive half-radius and comparison rows used by the extracted modulus row $\mathsf{Mu}$. No threshold can be exported from the packet unless that export is justified through the displayed $\DyadicRatCoreUp$ ledger $Q$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyModulusExtractionUp.CauchyModulusExtractionCarrier\_dyadic\_ledger\_positivity}
\begin{proof}
Project the carrier. The displayed row $Q$ is the packet coordinate assigned to the $\DyadicRatCoreUp$ comparison and half-radius ledger, and $\mathsf{Mu}$ is the only extracted modulus row.

Apply dyadic soundness from \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. That obligation binds the positive half-radius split and comparison data needed by the threshold to $Q$.

Since the carrier contains no second dyadic ledger and no external threshold selector, any exported threshold must use the same $Q$ row. Therefore the positivity and comparison data required by $\mathsf{Mu}$ are supplied by the displayed ledger and cannot be bypassed inside the packet.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction RealUp seal boundary]
\label{thm:cauchy-modulus-extraction-real-seal-boundary}
Every $\RealUp$-facing consumer of an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N)
$$
reaches the RealUp seal only after the finite budget $B$, StreamName windows $W$, RegSeqRat schedule $S$, dyadic ledger $Q$, and extracted modulus row $\mathsf{Mu}$ have been displayed by the same packet. The seal-facing route imports no quotient stream equality, host real equality, trichotomy, selected limits, ambient completeness, or threshold chosen outside the displayed rows.
\end{theorem}
\begin{proof}
Project the carrier and read the continuation row $C$. The displayed routes go from tolerance to budget, from budget to windows, from windows to schedule reads, from schedule reads to $\mathsf{Mu}$, and from $\mathsf{Mu}$ to the $\RealUp$ diagonal consumer.

Use budget-window coverage to place $B,W,S$ before the extracted modulus, and use dyadic ledger positivity to place $Q$ before the threshold export. These rows account for the data consumed by the RealUp-facing route before the seal is reached.

Finally apply ledger exactness from \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. The carrier has no coordinate for quotient stream equality, host real equality, trichotomy, selected limits, ambient completeness, or an outside threshold selector, so the RealUp seal boundary is exactly the displayed finite packet boundary.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction budget soundness]
\label{thm:cauchy-modulus-extraction-budget-soundness}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the extracted modulus row $\mathsf{Mu}$ is sound for every diagonal Real-completion consumer that reads the same finite budget $B$, $\StreamNameUp$ windows $W$, $\RegSeqRatUp$ witness schedule $S$, and dyadic comparison ledger $Q$. The consumer receives a natural threshold justified by the displayed observation budget and receives no host-selected convergence modulus, quotient stream representative, or ambient completeness witness.
\end{theorem}
\begin{proof}
Read the tolerance request $E$ and the budget row $B$. The budget determines the finite observation family available to the extraction packet.

Read the window and schedule rows $W,S$. They identify the StreamName observations and RegSeqRat witnesses that the real-completeness diagonal route may consume for the requested scale.

Use the dyadic ledger $Q$ to justify the half-radius comparisons attached to those reads. The extracted row $\mathsf{Mu}$ records the resulting natural threshold and is transported by $H$ along the continuation routes in $C$.

The package and naming rows $P,N$ expose exactly that finite packet. Because the carrier has no coordinate for an external modulus, a host-selected limit, or quotient equality, the handoff to the $\RealUp$ diagonal consumer is precisely the displayed budget-sound modulus row.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction budget threshold uniqueness]
\label{thm:cauchy-modulus-extraction-budget-threshold-uniqueness}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the displayed rows $E,B,W,S,Q$ determine the exported threshold row $\mathsf{Mu}$ for every consumer that reads the same finite budget. No second modulus row, host-selected convergence modulus, quotient stream representative, or ambient completeness witness can determine a different threshold inside the packet.
\end{theorem}
\begin{proof}
Project the displayed packet. The only tolerance request is $E$, the only observation budget is $B$, the only window family is $W$, the only regular schedule is $S$, and the only dyadic comparison ledger is $Q$.

Use the NameCert obligations. Budget exposure fixes $B$ as the source of the observations, schedule extraction fixes $W,S$ before the modulus is exported, and dyadic soundness fixes $Q$ as the ledger attached to the threshold.

Apply budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness}. Since the consumer receives $\mathsf{Mu}$ only as the threshold justified by those finite rows and the carrier has no second selector coordinate, the threshold exported inside the packet is unique for that budget route.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction StreamName RegSeqRat factorization]
\label{thm:cauchy-modulus-extraction-streamname-regseqrat-factorization}
Every consumer route from the tolerance request $E$ to the extracted modulus row $\mathsf{Mu}$ factors through the finite $\StreamNameUp$ window row $W$ and the $\RegSeqRatUp$ schedule row $S$ of the same packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N).
$$
The factorization reads the budget row $B$ first, then the window and schedule rows, then the dyadic ledger $Q$, and only then exports $\mathsf{Mu}$.
\end{theorem}
\begin{proof}
Begin with carrier admission. The tuple presents $B,W,S,Q$ as the only finite observation, window, schedule, and dyadic comparison rows available before $\mathsf{Mu}$.

Use budget exposure and schedule extraction from \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. These clauses force the route from $E$ to the modulus to pass through the finite budget and then through the StreamName and RegSeqRat rows.

Finally use budget soundness. The Real-completion consumer receives the modulus only after the dyadic ledger has justified the threshold for those rows, so the StreamName and RegSeqRat factorization is part of every accepted route to $\mathsf{Mu}$.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction RealUp seal non-escape]
\label{thm:cauchy-modulus-extraction-realup-seal-nonescape}
Every $\RealUp$ seal-facing consumer of an accepted $\CauchyModulusExtractionUp$ packet reads the same finite budget, window, schedule, dyadic, and modulus rows
$$
B,W,S,Q,\mathsf{Mu}
$$
before reaching the RealUp handoff. The packet exports no seal-facing route through quotient stream equality, selected limits, host real equality, trichotomy, ambient completeness, or an external modulus selector.
\end{theorem}
\begin{proof}
Project the carrier and the continuation row $C$. The displayed continuation routes include the path from tolerance to budget, from budget to windows, from windows to schedule reads, from schedule reads to $\mathsf{Mu}$, and from $\mathsf{Mu}$ to the $\RealUp$ diagonal consumer.

Apply the StreamName-RegSeqRat factorization and budget-threshold uniqueness established above. They show that the consumer reaches the same exported modulus only through $B,W,S,Q$.

Finish with ledger exactness from the NameCert obligations and budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness}. Since the finite packet has no coordinate for quotient equality, selected limits, host real equality, trichotomy, ambient completeness, or an outside selector, no RealUp seal-facing consumer can escape that route.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction budget monotonicity]
\label{thm:cauchy-modulus-extraction-budget-monotonicity}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
let $B^{+}$ be a displayed finite budget row containing the same tolerance request $E$, the same $\StreamNameUp$ windows needed by $W$, the same $\RegSeqRatUp$ schedule row $S$, and the same $\DyadicRatCoreUp$ comparison ledger $Q$. Then the extracted modulus row $\mathsf{Mu}$ remains sound for every $\RealUp$ diagonal consumer that reads through $B^{+}$. The larger displayed budget may contain additional visible observations, but it cannot change the extracted threshold, introduce a second modulus selector, or supply quotient stream equality, a host limit, or ambient completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier to the tuple $E,B,W,S,\mathsf{Mu},Q,H,C,P,N$. The local rows identify the tolerance request, the original finite budget, the inspected windows, the regular Cauchy schedule, the extracted threshold, and the dyadic comparison ledger.

Apply the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. Budget exposure fixes the displayed observation source for $E$, schedule extraction fixes $W,S$ before $\mathsf{Mu}$ is exported, and dyadic soundness fixes $Q$ as the comparison ledger attached to the threshold.

Now read the consumer through $B^{+}$. By assumption, the rows of $B^{+}$ contain exactly the tolerance request, window reads, schedule row, and dyadic ledger already used by $B,W,S,Q$ for the extracted threshold.

Use budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness} on those common rows. The row $\mathsf{Mu}$ is therefore still the threshold justified by the displayed budget data, and the consumer receives it without any host-selected convergence modulus or quotient stream representative.

The extra rows of $B^{+}$ are exhausted by coordinate inspection. They are not read by $\mathsf{Mu}$, have no selector coordinate in the carrier, and do not add a host limit or ambient completeness witness. Hence enlarging the finite observation budget preserves the same budget-sound modulus handoff.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction transport stability]
\label{thm:cauchy-modulus-extraction-transport-stability}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
any componentwise $\hsame$ transport of $E,B,W,S,\mathsf{Mu},Q,H,C,P,N$ preserves the extracted modulus row $\mathsf{Mu}$ and preserves the finite budget source $B$ from which that row is read. The transported packet exports the same tolerance request, finite observation budget, StreamName windows, RegSeqRat schedule, dyadic comparison ledger, continuation routes, package provenance, and local naming row, and it exports no host-selected convergence modulus.
\end{theorem}
\begin{proof}
Project the accepted carrier to its displayed tuple. The row $H$ records componentwise transport for the tolerance request, budget, windows, schedule row, modulus row, dyadic ledger, provenance, and local name.

Apply the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. Carrier admission fixes the tuple, budget exposure fixes $B$ as the finite source for the tolerance request, schedule extraction fixes $W,S$ before $\mathsf{Mu}$ is exported, and ledger exactness routes all transport through $H,C,P,N$.

Finally use budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness}. The Real-completion handoff receives $\mathsf{Mu}$ only as the threshold justified by the displayed budget and schedule rows, so componentwise transport preserves both the modulus row and its finite budget source.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction selector stability]
\label{thm:cauchy-modulus-extraction-selector-stability}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
componentwise $\hsame$ transport of the tolerance request $E$, finite budget $B$, $\StreamNameUp$ windows $W$, $\RegSeqRatUp$ schedule $S$, $\DyadicRatCoreUp$ ledger $Q$, and modulus row $\mathsf{Mu}$ preserves the same selected modulus for any $\RealUp$ diagonal consumer. The transported consumer reads the same finite selector surface and receives no external modulus selector, quotient stream representative, selected limit, host real equality, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start with the carrier definition. The selector data visible before the $\RealUp$ handoff are exactly $E,B,W,S,Q,\mathsf{Mu}$, and the transport row $H$ is componentwise over those coordinates.

Apply the NameCert obligations and budget soundness. Carrier admission fixes the tuple, budget exposure fixes the finite source $B$, schedule extraction fixes $W,S$, dyadic soundness fixes $Q$, and budget soundness identifies $\mathsf{Mu}$ as the threshold justified by those displayed rows.

Use transport stability from \autoref{thm:cauchy-modulus-extraction-transport-stability}. Since the transported packet preserves both the modulus row and the finite budget source, the selected modulus seen by a diagonal consumer is the same selected row $\mathsf{Mu}$.

Finally apply the StreamName--RegSeqRat factorization and the $\RealUp$ seal non-escape theorem. The consumer reaches the handoff only through the finite budget, stream windows, regular schedule, dyadic ledger, and exported modulus, so no outside selector or completion object can alter the selected threshold.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction finite-budget handoff]
\label{thm:cauchy-modulus-extraction-budget-handoff}
Every $\RealUp$ completion-facing handoff from an accepted $\CauchyModulusExtractionUp$ packet factors through the finite budget row $B$ before reading the $\StreamNameUp$ windows $W$, the $\RegSeqRatUp$ schedule $S$, the $\DyadicRatCoreUp$ comparison ledger $Q$, and the exported modulus row $\mathsf{Mu}$. Thus the completion-facing route is a finite-budget handoff rather than a direct appeal to host convergence, quotient stream equality, selected limits, trichotomy, or ambient completeness.
\end{theorem}
\begin{proof}
Read the accepted packet through \autoref{def:cauchy-modulus-extraction-carrier}. The continuation row $C$ lists the route from tolerance to budget, from budget to windows, from windows to schedule reads, from schedule reads to $\mathsf{Mu}$, and from $\mathsf{Mu}$ to the $\RealUp$ diagonal consumer.

Apply the NameCert obligations and budget soundness. Budget exposure makes $B$ the only finite observation source for $E$, while budget soundness ties the exported modulus to the displayed budget, windows, schedule, and dyadic ledger.

Next use the StreamName--RegSeqRat factorization. It places $W$ and $S$ after the budget row and before the modulus export, and it places $Q$ as the dyadic ledger required by the extracted threshold.

Finish with the $\RealUp$ seal non-escape theorem. Since every seal-facing route reads through $B,W,S,Q,\mathsf{Mu}$ and the carrier has no coordinate for host convergence or quotient stream equality, every completion-facing handoff factors through the finite budget before the remaining rows are consumed.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction real diagonal handoff]
\label{thm:cauchy-modulus-extraction-real-diagonal-handoff}
Any $\RealUp$ diagonal or completion consumer of an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N)
$$
may read the extracted modulus row $\mathsf{Mu}$ only after the $\StreamNameUp$ windows $W$, the $\RegSeqRatUp$ schedule $S$, the $\DyadicRatCoreUp$ comparison ledger $Q$, and the finite budget row $B$ have been displayed through the same local packet.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows available before the modulus handoff are the tolerance request $E$, finite budget $B$, window family $W$, schedule row $S$, and dyadic ledger $Q$.

Apply the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. Budget exposure places $B$ before any window read, schedule extraction places $W,S$ before the export of $\mathsf{Mu}$, and dyadic soundness places $Q$ as the comparison ledger attached to the threshold.

Use budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness}. Since the handoff to the diagonal consumer is precisely the displayed budget-sound modulus row, any $\RealUp$ completion route reads $\mathsf{Mu}$ only after the windows, schedule, dyadic comparison ledger, and finite budget rows have appeared.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction ledger exactness]
\label{thm:cauchy-modulus-extraction-ledger-exactness}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the ledger is exact for the route from tolerance request to finite budget, StreamName windows, RegSeqRat schedule, extracted modulus, dyadic comparison ledger, and local NameCert:
$$
E,B,W,S,\mathsf{Mu},Q,H,C,P,N.
$$
It excludes quotient stream equality, host real equality, selected limits, trichotomy, ambient completeness, and any modulus selector not displayed by the finite packet.
\end{theorem}
\begin{proof}
Project the accepted carrier to the ten displayed rows. The route begins at the tolerance request $E$ and reaches the finite budget $B$, windows $W$, schedule $S$, extracted modulus $\mathsf{Mu}$, dyadic ledger $Q$, transports $H$, routes $C$, provenance $P$, and local name $N$.

Apply the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. They bind carrier admission, budget exposure, schedule extraction, dyadic soundness, and transport, continuation, package, and naming reads to the same finite tuple.

Finally use budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness}. The exported modulus is justified by the displayed observation budget and carries no coordinate for quotient stream equality, host real equality, selected limits, trichotomy, ambient completeness, or an outside selector, so the ledger is exact.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction route exactness]
\label{thm:cauchy-modulus-extraction-route-exactness}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
every accepted consumer route from the tolerance request $E$ to the extracted modulus row $\mathsf{Mu}$ factors through exactly the displayed rows
$$
E,B,W,S,\mathsf{Mu},Q,H,C,P,N.
$$
Thus the route passes through the finite budget, StreamName window family, RegSeqRat schedule row, dyadic comparison ledger, componentwise transports, continuation routes, package provenance, and local naming row, and it has no additional Real-completion coordinate.
\end{theorem}
\begin{proof}
Project the accepted carrier to its displayed tuple. The carrier presentation supplies the tolerance request, budget row, inspected windows, schedule row, extracted modulus, dyadic ledger, transports, continuations, provenance, and local name.

Apply the local NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. Carrier admission identifies the tuple, budget exposure fixes $B$, schedule extraction fixes $W,S$, dyadic soundness fixes $Q$, and ledger exactness fixes $H,C,P,N$ as the only remaining certificate rows.

Finally use budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness}. Since the handoff to the diagonal consumer is the displayed budget-sound modulus row and the carrier contains no extra selector, any accepted route from $E$ to $\mathsf{Mu}$ is exactly the route through those ten rows.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction window schedule exhaustion]
\label{thm:cauchy-modulus-extraction-window-schedule-exhaustion}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the inspected $\StreamNameUp$ window family $W$ and the $\RegSeqRatUp$ schedule row $S$ exhaust all schedule data available to a Real-completion diagonal consumer. The consumer may use the StreamName surface of \autoref{ch:concrete-instances-streamname-namecert}, the RegSeqRat schedule surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the Real carrier surface of \autoref{ch:concrete-instances-real-namecert}, but within this extraction packet those surfaces are reached only through $W$ and $S$.
\end{theorem}
\begin{proof}
The carrier first exposes the finite budget $B$ attached to the tolerance request $E$. This budget bounds which StreamName observations and regular Cauchy witnesses are visible to the diagonal consumer.

The window row $W$ is the only StreamName row in the packet. By the StreamName naming surface cited in \autoref{ch:concrete-instances-streamname-namecert}, window reads available to the consumer are therefore the reads displayed in $W$.

The schedule row $S$ is the only RegSeqRat schedule row in the packet. By the RegSeqRat naming surface cited in \autoref{ch:concrete-instances-regseqrat-namecert}, regular Cauchy witness reads available to the consumer are therefore the reads displayed in $S$.

The Real carrier surface cited in \autoref{ch:concrete-instances-real-namecert} receives the diagonal handoff through the continuation rows in $C$. Because those continuations start from the displayed budget, windows, and schedule row, no further schedule data can be introduced at the Real-completion boundary.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction dyadic ledger non-escape]
\label{thm:cauchy-modulus-extraction-dyadic-ledger-nonescape}
For an accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the dyadic comparison row $Q$ is the only positive half-radius and comparison ledger exported to the modulus row $\mathsf{Mu}$. The extraction packet exports no quotient stream, host-selected convergence modulus, selected limit, host real equality, or ambient completeness witness.
\end{theorem}
\begin{proof}
Read the dyadic row $Q$ from the carrier. It is the coordinate assigned to the positive half-radius split and to the comparisons used by the extracted threshold.

Apply dyadic soundness from \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. That obligation identifies $Q$ as the ledger needed by $\mathsf{Mu}$ and ties it to the displayed budget, windows, and schedule row.

Use budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness} to inspect the exported handoff. The consumer receives the natural threshold justified by $Q$ and by the finite rows $B,W,S$.

The carrier has no coordinate for a quotient stream, host-selected convergence modulus, selected limit, host real equality, or ambient completeness witness. Hence none of those objects can escape through the modulus row.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction budget fiber exhaustion]
\label{thm:cauchy-modulus-extraction-budget-fiber-exhaustion}
For an accepted $\CauchyModulusExtractionUp$ packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
a $\RealUp$ diagonal or completion consumer lies in the budget fiber over the displayed tolerance request $E$ and finite budget $B$ exactly when its route first reads $B$, then the $\StreamNameUp$ windows $W$ and $\RegSeqRatUp$ schedule $S$, then the $\DyadicRatCoreUp$ comparison ledger $Q$, and exports $\mathsf{Mu}$ only through $H,C,P,N$. No quotient stream equality, host real equality, selected limit, trichotomy, ambient completeness, or external modulus selector supplies another element of that budget fiber.
\end{theorem}
\begin{proof}
Start with a consumer lying in the displayed budget fiber. Apply the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations} to identify the accepted carrier rows, the exposed budget, the schedule extraction surface, the dyadic soundness row, and the transport, continuation, package, and naming rows.

The finite route is then forced by budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness} and route exactness from \autoref{thm:cauchy-modulus-extraction-route-exactness}. The consumer first reads $B$, then uses the StreamName--RegSeqRat factorization through $W$ and $S$, then reads the dyadic ledger $Q$ before exporting $\mathsf{Mu}$ through $H,C,P,N$.

Conversely, any route with exactly that read order is accepted by the same packet because each row is one of the displayed NameCert rows and the handoff to the Real diagonal surface uses the continuation rows already present in $C$.

It remains to exclude other fiber elements. Apply window-schedule exhaustion from \autoref{thm:cauchy-modulus-extraction-window-schedule-exhaustion} and dyadic-ledger non-escape from \autoref{thm:cauchy-modulus-extraction-dyadic-ledger-nonescape}. These results leave no coordinate through which quotient stream equality, host real equality, selected limits, trichotomy, ambient completeness, or an external modulus selector can enter the budget fiber.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction obligation closure package]
\label{thm:cauchy-modulus-extraction-obligation-closure-package}
For an accepted $\CauchyModulusExtractionUp$ packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the $\NameCert_{\CauchyModulusExtractionUp}$ obligation package consumed by the $\RealUp$ completion route is exactly the carrier row $E$, the finite budget row $B$, the $\StreamNameUp$ window row $W$, the $\RegSeqRatUp$ schedule row $S$, the $\DyadicRatCoreUp$ ledger $Q$, the extracted modulus row $\mathsf{Mu}$, and the structural rows $H,C,P,N$. Every $\RealUp$ diagonal consumer must pass through those rows before reading the modulus handoff. No such consumer obtains quotient stream equality, selected limits, trichotomy, host real equality, ambient completeness, or an external modulus selector from the package.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. Carrier admission fixes the displayed packet, budget exposure fixes $B$, schedule extraction fixes $W,S$, dyadic soundness fixes $Q$, and ledger exactness fixes $H,C,P,N$ as the structural route.

Budget soundness from \autoref{thm:cauchy-modulus-extraction-budget-soundness} then identifies $\mathsf{Mu}$ as the threshold justified by $B,W,S,Q$. The StreamName--RegSeqRat factorization of \autoref{thm:cauchy-modulus-extraction-streamname-regseqrat-factorization} forces every route from $E$ to $\mathsf{Mu}$ through the window and schedule rows.

Apply the Real diagonal handoff of \autoref{thm:cauchy-modulus-extraction-real-diagonal-handoff} and ledger exactness from \autoref{thm:cauchy-modulus-extraction-ledger-exactness}. These two results place the Real-facing read after the displayed budget, window, schedule, dyadic, modulus, transport, continuation, package, and naming rows.

Finally use budget-fiber exhaustion from \autoref{thm:cauchy-modulus-extraction-budget-fiber-exhaustion}. It rules out every remaining route through quotient stream equality, selected limits, trichotomy, host real equality, ambient completeness, or an external modulus selector, so the listed rows are the whole obligation package for the Real-completion route.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction public export]
\label{thm:cauchy-modulus-extraction-public-export}
For every accepted $\CauchyModulusExtractionUp$ carrier
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the public $\NameCert_{\CauchyModulusExtractionUp}$ export is exactly the carrier admission, finite budget exposure, $\StreamNameUp$--$\RegSeqRatUp$ factorization, $\DyadicRatCoreUp$ positivity and non-escape ledger, $\RealUp$ seal boundary, route exactness, window schedule exhaustion, budget fiber exhaustion, and obligation closure package already displayed by this chapter.

Thus downstream $\RealUp$ and Completion consumers may cite one public export instead of rebuilding the finite budget, dyadic, stream, schedule, seal, transport, continuation, provenance, and naming rows separately. The export contains no quotient stream equality, host real equality, selected limit, trichotomy, ambient completeness, or external modulus selector.
\end{theorem}
\begin{proof}
First read the accepted carrier through \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. This fixes $E,B,W,S,\mathsf{Mu},Q,H,C,P,N$ as the only rows available to the local naming certificate and identifies the carrier admission and finite budget exposure.

Next assemble the stream and dyadic surfaces. Apply \autoref{thm:cauchy-modulus-extraction-streamname-regseqrat-factorization}, \autoref{thm:cauchy-modulus-extraction-dyadic-ledger-positivity}, and \autoref{thm:cauchy-modulus-extraction-dyadic-ledger-nonescape}. These results put the window row, regular schedule, positive dyadic ledger, and dyadic non-escape boundary in the same displayed packet.

Now attach the Real-facing route. Use \autoref{thm:cauchy-modulus-extraction-realup-seal-nonescape}, \autoref{thm:cauchy-modulus-extraction-route-exactness}, and \autoref{thm:cauchy-modulus-extraction-window-schedule-exhaustion}. They force every seal-facing consumer through the exact finite route and exhaust the window schedule before any modulus handoff is readable.

Finally combine \autoref{thm:cauchy-modulus-extraction-budget-fiber-exhaustion} with \autoref{thm:cauchy-modulus-extraction-obligation-closure-package}. The first theorem exhausts the budget fiber over the displayed tolerance request, and the second repacks all named rows as the local obligation package. Therefore the public export is precisely the listed finite surface, with all excluded completion objects absent from the carrier.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction Real-completion consumer bridge]
\label{thm:cauchy-modulus-extraction-real-completion-consumer-bridge}
For every accepted $\CauchyModulusExtractionUp$ packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
every Real-completion consumer route that reads the extracted modulus row $\mathsf{Mu}$ factors through exactly the displayed rows $B,W,S,Q,\mathsf{Mu},H,C,P,N$ after carrier admission through $E$. The $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ surfaces reached by the route are precisely the sibling surfaces cited by \autoref{thm:cauchy-modulus-extraction-public-export}; no route obtains a host convergence modulus, quotient stream, selected limit, host real equality, ambient completeness, or choice-selected witness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyModulusExtractionUp.CauchyModulusExtractionUp\_StdBridge}
\begin{proof}
Start with the budget-window coverage theorem, \autoref{thm:cauchy-modulus-extraction-budget-window-coverage}. It places every accepted tolerance request $E$ behind the finite budget $B$ before any window or schedule row can contribute to $\mathsf{Mu}$.

Next use dyadic ledger positivity, \autoref{thm:cauchy-modulus-extraction-dyadic-ledger-positivity}. The extracted modulus is justified by the displayed $\DyadicRatCoreUp$ ledger $Q$, so the consumer receives a ledgered threshold rather than an external selector.

Now apply the StreamName--RegSeqRat factorization of \autoref{thm:cauchy-modulus-extraction-streamname-regseqrat-factorization}. The sibling surfaces \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-regseqrat-namecert} are reached only through the local $W$ and $S$ rows in this packet.

Finally cite RealUp seal non-escape, \autoref{thm:cauchy-modulus-extraction-realup-seal-nonescape}, together with the public export of \autoref{thm:cauchy-modulus-extraction-public-export}. These results identify the local Real-facing surface with the sibling surface \autoref{ch:concrete-instances-real-namecert}, keep the completion-facing read inside $B,W,S,Q,\mathsf{Mu},H,C,P,N$, and rule out host convergence moduli, quotient streams, selected limits, host real equality, ambient completeness, and choice-selected witnesses.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction dyadic Real consumer factorization]
\label{thm:cauchy-modulus-extraction-dyadic-real-consumer-factorization}
For every accepted $\CauchyModulusExtractionUp$ packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
every $\RealUp$-completion consumer that reads the extracted modulus row $\mathsf{Mu}$ factors first through the finite budget row $B$, the $\StreamNameUp$ window row $W$, the $\RegSeqRatUp$ schedule row $S$, and the $\DyadicRatCoreUp$ ledger row $Q$. The handoff to the Real-facing consumer exports only this displayed dyadic ledger route with $H,C,P,N$ attached; it exports no host modulus, quotient stream equality, selected limit, trichotomy, ambient completeness, or external real-completion witness.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:cauchy-modulus-extraction-namecert-obligations}. They identify the accepted packet with the rows $E,B,W,S,\mathsf{Mu},Q,H,C,P,N$ and leave no additional carrier coordinate for a Real consumer.

Use budget-window coverage from \autoref{thm:cauchy-modulus-extraction-budget-window-coverage}. Any consumer read of $\mathsf{Mu}$ must first pass through the finite budget $B$ and the displayed window row $W$, so the request is already inside the local ledger route.

Next apply dyadic ledger positivity and StreamName--RegSeqRat factorization, \autoref{thm:cauchy-modulus-extraction-dyadic-ledger-positivity} and \autoref{thm:cauchy-modulus-extraction-streamname-regseqrat-factorization}. These force the route through the regular schedule row $S$ and the dyadic ledger row $Q$ before the extracted modulus can be exposed.

Finally use the Real-completion consumer bridge, \autoref{thm:cauchy-modulus-extraction-real-completion-consumer-bridge}, and carrier non-escape from \autoref{thm:cauchy-modulus-extraction-realup-seal-nonescape}. The bridge supplies the Real-facing handoff, while non-escape excludes host moduli, quotient stream equality, selected limits, trichotomy, ambient completeness, and external completion witnesses from the exported packet.
\end{proof}

\begin{theorem}[Cauchy modulus-extraction mature package summary]
\label{thm:cauchy-modulus-extraction-mature-package-summary}
For every accepted $\CauchyModulusExtractionUp$ packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N),
$$
the finite Real-completion consumer surface is the public export, the Real-completion consumer bridge, the dyadic Real consumer factorization, route exactness, budget-fiber exhaustion, and the no-ambient-completeness boundary of this chapter assembled as one package. A downstream $\RealUp$ or completion consumer reads $E,B,W,S,\mathsf{Mu},Q,H,C,P,N$ in that finite order, obtains the extracted modulus only through the displayed budget-window-dyadic route, and obtains no quotient stream equality, host real equality, selected limit, trichotomy, ambient completeness, or external modulus selector.
\end{theorem}
\begin{proof}
Start with \autoref{thm:cauchy-modulus-extraction-public-export}. It collects carrier admission, budget exposure, window and schedule rows, dyadic ledger, Real seal boundary, route exactness, window exhaustion, budget-fiber exhaustion, and obligation closure into the public surface of $M$.

Use \autoref{thm:cauchy-modulus-extraction-real-completion-consumer-bridge}. The bridge sends Real-completion consumers through $B,W,S,Q,\mathsf{Mu},H,C,P,N$ after admission through $E$, so the extracted modulus is not read from an external host selector.

Apply \autoref{thm:cauchy-modulus-extraction-dyadic-real-consumer-factorization}. It records the reusable factorization through $B,W,S,Q$ before the Real-facing consumer can read $\mathsf{Mu}$.

Finally apply \autoref{thm:cauchy-modulus-extraction-route-exactness}, \autoref{thm:cauchy-modulus-extraction-budget-fiber-exhaustion}, and \autoref{thm:cauchy-modulus-extraction-realup-seal-nonescape}. Route exactness fixes the order of the finite rows, budget-fiber exhaustion leaves no second budget source, and the RealUp boundary excludes quotient stream equality, host real equality, selected limits, trichotomy, ambient completeness, and external modulus data.
\end{proof}

\closureat{CauchyModulusExtractionUp}{obligationStr}
\closureat{CauchyModulusExtractionUp}{scopedStr}
\closureat{CauchyModulusExtractionUp}{publicStr}
\closureat{CauchyModulusExtractionUp}{bridgedStr}
\closureat{CauchyModulusExtractionUp}{matureStr}

\begin{closurestatus}{\CauchyModulusExtractionUp}
  \constructivestory{A $\CauchyModulusExtractionUp$ packet is generated from a positive tolerance request, finite observation budget, StreamNameUp windows, RegSeqRatUp witness schedule, extracted modulus row, dyadic comparison ledger, componentwise transports, continuation routes, package provenance, and a local naming row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:cauchy-modulus-extraction-carrier}, \autoref{thm:cauchy-modulus-extraction-namecert-obligations}, \autoref{thm:cauchy-modulus-extraction-budget-soundness}, \autoref{thm:cauchy-modulus-extraction-streamname-regseqrat-factorization}, \autoref{thm:cauchy-modulus-extraction-dyadic-ledger-nonescape}, \autoref{thm:cauchy-modulus-extraction-real-diagonal-handoff}, \autoref{thm:cauchy-modulus-extraction-obligation-closure-package}, \autoref{thm:cauchy-modulus-extraction-public-export}, \autoref{thm:cauchy-modulus-extraction-real-completion-consumer-bridge}, \autoref{thm:cauchy-modulus-extraction-dyadic-real-consumer-factorization}, and \autoref{thm:cauchy-modulus-extraction-mature-package-summary} bind the mature finite Real-completion consumer surface for the modulus-extraction packet.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.CauchyModulusExtractionUp.CauchyModulusExtractionCarrier\_namecert\_obligations}
  \bridgestatus{bridgeChecked}
  \origin{human}
  \notclaimed{This chapter does not close RealUp completeness, uniqueness of completed limits, quotient equality of streams, host real equality, a public standard bridge, or Lean verification.}
  \upgradepath{No further upgrade: the chapter is at the top of the formal bridge axis.}
\end{closurestatus}
