\chapter{A Concrete Naming Certificate for $\ProductRegularCauchyLimitUp$}
\label{ch:concrete-instances-productregularcauchylimit-namecert}
\origin{ai}

The $\ProductRegularCauchyLimitUp$ packet names the finite Real-and-Completion handoff where a product of regular Cauchy names is read as a regular Cauchy limit classifier. It consumes the product-observation surface of $\CauchyProductUp$ from \autoref{ch:concrete-instances-cauchyproduct-namecert} and the classifier handoff of $\RegularCauchyLimitClassifierUp$ from \autoref{ch:concrete-instances-regularcauchylimitclassifier-namecert}, while keeping every consumer route inside displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows. The packet does not supply ambient completeness, quotient stream equality, a selected host limit, or host real multiplication.

\begin{definition}[Product regular-Cauchy limit carrier]
\label{def:product-regular-cauchy-limit-carrier}
A $\ProductRegularCauchyLimitUp$ carrier is a finite $\BHist$ packet
$$
U=(P,Q,W,R,D,E,H,C,L,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the accepted $\CauchyProductUp$ product packet for the two regular Cauchy source names;
\item $Q$ is the accepted $\RegularCauchyLimitClassifierUp$ packet that classifies the diagonal limit handoff for the product read;
\item $W$ is the joint $\StreamNameUp$ window ledger, combining the paired product windows with the selected diagonal-limit windows;
\item $R$ is the $\RegSeqRatUp$ readback row produced by the product-radius ledger and then consumed by the limit classifier;
\item $D$ is the $\DyadicRatCoreUp$ endpoint, radius, comparison, and precision ledger shared by the product observation and the limit handoff;
\item $E$ is the $\RealUp$ seal row through which a completion consumer sees the product-limit candidate;
\item $H$ stores componentwise $\hsame$ transports for $P,Q,W,R,D,E,L,N$ and the local packet shape;
\item $C$ stores finite $\Cont$ routes for every public read of the product row, diagonal-window classifier, dyadic ledger, regular readback, Real seal, package provenance, and local naming row;
\item $L$ is the $\Pkg$ provenance over $\CauchyProductUp$, $\RegularCauchyLimitClassifierUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ProductRegularCauchyLimitUp}$ row.
\end{enumerate}
The carrier contains no host multiplication primitive, no ambient completeness theorem, no quotient stream representative, and no independent selected limit.
\end{definition}

\begin{theorem}[Product regular-Cauchy limit NameCert obligations]
\label{thm:product-regular-cauchy-limit-namecert-obligations}
The local $\NameCert_{\ProductRegularCauchyLimitUp}$ surface for \autoref{def:product-regular-cauchy-limit-carrier} consists of six finite obligation rows:
\begin{enumerate}
\item carrier admission for the packet $U=(P,Q,W,R,D,E,H,C,L,N)$;
\item product-source admission stating that the only product observation is the accepted $\CauchyProductUp$ row $P$;
\item limit-classifier admission stating that the only completion-facing limit handoff is the accepted $\RegularCauchyLimitClassifierUp$ row $Q$;
\item shared-window exactness stating that $W,R,D,E$ are read in the order product windows, dyadic product observation, regular readback, diagonal-limit windows, and $\RealUp$ seal;
\item componentwise stability stating that $H$ and $C$ preserve the same product row, classifier row, shared ledger, package provenance, and local naming row under $\hsame$ and $\Cont$ transport;
\item ledger exactness stating that every public read factors through $P,Q,W,R,D,E,H,C,L,N$ and no ambient completeness or host real multiplication is exported.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.ProductRegularCauchyLimitUp.ProductRegularCauchyLimitTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:product-regular-cauchy-limit-carrier}. The tuple lists the product packet, limit classifier, windows, regular readback, dyadic ledger, Real seal, transports, routes, package provenance, and local naming row.

Product-source admission uses the $\CauchyProductUp$ row $P$. A consumer cannot read a product observation except through the paired product windows and dyadic product ledger already displayed by that packet.

Limit-classifier admission uses the $\RegularCauchyLimitClassifierUp$ row $Q$. Its diagonal-window classifier consumes the regular readback and Real seal data as displayed rows, not as a host-level selected limit.

The shared-window and stability clauses are the roles of $W,R,D,E,H,C$. They keep the product observation, regular readback, diagonal limit window, and seal handoff in one finite route under componentwise transport.

Finally, $L$ and $N$ repack those rows as the local certificate surface. Since the carrier has no coordinate for host multiplication, quotient stream equality, ambient completeness, or an independent selected limit, the public ledger exports only the displayed product-limit packet.
\end{proof}

\begin{theorem}[Product regular-Cauchy limit product-source admission]
\label{thm:product-regular-cauchy-limit-product-source-admission}
In a $\ProductRegularCauchyLimitUp$ carrier $U=(P,Q,W,R,D,E,H,C,L,N)$, the row $P$ is the only product-observation source. Every public product read of $U$ is consumed through the $\CauchyProductUp$ sibling surface of \autoref{ch:concrete-instances-cauchyproduct-namecert}, specifically through the paired-window source admission of \autoref{thm:cauchy-product-paired-window-source-admission} and the budget-route exactness of \autoref{thm:cauchy-product-budget-route-exactness}.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:product-regular-cauchy-limit-carrier}. The only coordinate named as a product observation is $P$, and it is explicitly an accepted $\CauchyProductUp$ packet.

The sibling certificate supplies the product read. By \autoref{thm:cauchy-product-paired-window-source-admission}, the source windows for the product read are the paired windows inside the $\CauchyProductUp$ packet. By \autoref{thm:cauchy-product-budget-route-exactness}, the dyadic product observation and regular readback route are consumed through that same sibling budget surface.

Since $U$ contains no second product-observation coordinate, every public product read factors through $P$ and its displayed $\CauchyProductUp$ surface.
\end{proof}

\begin{theorem}[Product regular-Cauchy limit classifier admission]
\label{thm:product-regular-cauchy-limit-limit-classifier-admission}
In a $\ProductRegularCauchyLimitUp$ carrier $U=(P,Q,W,R,D,E,H,C,L,N)$, the row $Q$ is the only completion-facing diagonal-limit classifier. A consumer reads the product-limit handoff through the $\RegularCauchyLimitClassifierUp$ sibling surface of \autoref{ch:concrete-instances-regularcauchylimitclassifier-namecert}, not through an ambient selected limit.
\end{theorem}
\begin{proof}
Inspect the displayed rows of the carrier. The only coordinate whose role is a completion-facing diagonal-limit handoff is $Q$, and its declared source is the accepted $\RegularCauchyLimitClassifierUp$ packet.

The classifier is therefore read through the sibling chapter named in the statement. The surrounding rows $R,D,E$ are inputs and seals for that classifier route; they do not create an independent completion theorem or selected host limit.

Thus every completion-facing product-limit read uses $Q$ as its classifier row and remains inside the finite diagonal-window handoff.
\end{proof}

\begin{theorem}[Product regular-Cauchy limit shared-window exactness]
\label{thm:product-regular-cauchy-limit-shared-window-exactness}
For a $\ProductRegularCauchyLimitUp$ carrier $U=(P,Q,W,R,D,E,H,C,L,N)$, the shared route through $W,R,D,E$ is ordered through the displayed sibling surfaces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp .
$$
The relevant dependency chapters are \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.
\end{theorem}
\begin{proof}
Begin with the shared window row. The carrier states that $W$ is the joint $\StreamNameUp$ window ledger combining the product windows with the selected diagonal-limit windows, so the first read is the StreamName sibling surface.

Next the dyadic and regular readback rows are fixed. The row $D$ supplies the $\DyadicRatCoreUp$ endpoint, radius, comparison, and precision ledger, while $R$ is the $\RegSeqRatUp$ readback row produced by the product-radius ledger and consumed by the limit classifier.

Finally the row $E$ is the $\RealUp$ seal through which the completion consumer sees the product-limit candidate. The route therefore has the displayed order $W,D,R,E$ across the four sibling surfaces, with no extra route outside those finite rows.
\end{proof}

\begin{theorem}[Product regular-Cauchy limit transport stability]
\label{thm:product-regular-cauchy-limit-transport-stability}
Componentwise $\hsame$ transport and the displayed $\Cont$ replay of a $\ProductRegularCauchyLimitUp$ carrier preserve the same product row $P$, classifier row $Q$, shared rows $W,R,D,E$, provenance row $L$, and local naming row $N$. The transported carrier has the same finite public rows and the same product-limit read surface.
\end{theorem}
\begin{proof}
The row $H$ stores componentwise $\hsame$ transports for $P,Q,W,R,D,E,L,N$ and for the local packet shape. Hence transport cannot replace the product source, classifier source, shared ledger, provenance, or name row with a row outside the displayed tuple.

The row $C$ stores the finite $\Cont$ routes for the public reads of the product row, diagonal-window classifier, dyadic ledger, regular readback, Real seal, package provenance, and local naming row. Replaying these routes after componentwise transport therefore reads the same named coordinates in the transported packet.

Thus the transported packet preserves the public product-limit surface exactly at the level of displayed rows.
\end{proof}

\begin{theorem}[Product regular-Cauchy limit ledger exactness]
\label{thm:product-regular-cauchy-limit-ledger-exactness}
For a $\ProductRegularCauchyLimitUp$ carrier $U=(P,Q,W,R,D,E,H,C,L,N)$, the ledger row $L$ and local naming row $N$ exhaust the public reads. The packet exports no host multiplication primitive, no quotient stream equality, no selected limit, and no ambient completeness theorem.
\end{theorem}
\begin{proof}
The provenance row $L$ names exactly the dependency surfaces listed in the carrier: $\CauchyProductUp$, $\RegularCauchyLimitClassifierUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.

The local row $N$ is the $\NameCert_{\ProductRegularCauchyLimitUp}$ row for this finite tuple. Together with $L$, it gives the public naming ledger for every accepted read of the packet.

The carrier has no coordinate for host multiplication, quotient streams, selected limits, or ambient completeness. Any read requiring one of those objects has no source row in $U$, so the public surface is exhausted by $P,Q,W,R,D,E,H,C,L,N$.
\end{proof}

\closureat{ProductRegularCauchyLimitUp}{seedStr}
\closureat{ProductRegularCauchyLimitUp}{obligationStr}[BEDC.Derived.ProductRegularCauchyLimitUp.ProductRegularCauchyLimitTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\ProductRegularCauchyLimitUp}
  \constructivestory{A $\ProductRegularCauchyLimitUp$ packet is generated from a $\CauchyProductUp$ product row, a $\RegularCauchyLimitClassifierUp$ diagonal-window classifier, shared $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal, transport routes, package provenance, and a local naming row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:product-regular-cauchy-limit-carrier}, \autoref{thm:product-regular-cauchy-limit-namecert-obligations}, \autoref{thm:product-regular-cauchy-limit-product-source-admission}, \autoref{thm:product-regular-cauchy-limit-limit-classifier-admission}, \autoref{thm:product-regular-cauchy-limit-shared-window-exactness}, \autoref{thm:product-regular-cauchy-limit-transport-stability}, and \autoref{thm:product-regular-cauchy-limit-ledger-exactness} bind the product-to-limit handoff as a finite Real-and-Completion NameCert packet.}
  \leanchecked{BEDC.Derived.ProductRegularCauchyLimitUp.taste\_gate}
  \leantarget{BEDC.Derived.ProductRegularCauchyLimitUp.ProductRegularCauchyLimitTasteGate\_single\_carrier\_alignment}
  \formalstatus{\axiomCleanV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close RealUp completeness, quotient stream equality, selected host limits, host real multiplication, or a public standard bridge.}
  \upgradepath{Public closure requires a single public export assembling the product-source admission, limit-classifier admission, shared-window exactness, transport stability, and ledger exactness rows.}
\end{closurestatus}
