\chapter{A Concrete Naming Certificate for $\CrossPerspectiveAlignmentUp$}
\label{ch:concrete-instances-crossperspectivealignment-namecert}
\origin{ai}

The $\CrossPerspectiveAlignmentUp$ surface turns the other-minds locality-cell commitment of \autoref{prin:hard-problems-other-minds-as-locality-cell} into a finite coordination packet. It aligns public observer commitments, locality-cell evidence, and inter-history coherence rows without exposing private $\mathsf{Self}$ coordinates or treating observer agreement as host-level identity.

The row $M$ is consumed from \autoref{ch:concrete-instances-multihistconfig-namecert} as the finite inter-Hist configuration surface. $\CrossPerspectiveAlignmentUp$ adds only locality-cell and public commitment routing on top of that sibling surface, not private observer-state access.

\begin{definition}[CrossPerspectiveAlignment carrier]
\label{def:cross-perspective-alignment-carrier}
A $\CrossPerspectiveAlignmentUp$ carrier is a finite $\BHist$ packet
$$
B=(A,B,L,O,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the source-observer row issuing the alignment request;
\item $B$ is the target-observer public row, read only as an other-minds commitment surface;
\item $L$ is the locality-cell evidence row, recording the public $\LocalityCellUp$ evidence that makes the target row available for coordination;
\item $O$ is the public $\OtherMindsCommitmentUp$ row tying $A$'s commitment to $B$ without direct target $\mathsf{Self}$ access;
\item $M$ is the accepted $\MultiHistConfigUp$ row displaying the finite inter-Hist configuration in which the two observer histories are compared;
\item $H$ records the componentwise $\hsame$ transports for the observer rows, locality-cell evidence, other-minds commitment, multi-Hist configuration, package row, and local naming row;
\item $C$ records the $\Cont$ routes that let public consumers read the commitment row, locality-cell row, and inter-Hist coherence rows without entering private observer state;
\item $P$ is the $\Pkg$ provenance over $\OtherMindsCommitmentUp$, $\LocalityCellUp$, $\MultiHistConfigUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\CrossPerspectiveAlignmentUp}$ row.
\end{enumerate}
The classifier compares carriers only through these displayed rows and their $\hsame$ and $\Cont$ transports.
\end{definition}
\leanchecked{BEDC.Derived.CrossPerspectiveAlignmentUp.CrossPerspectiveAlignmentTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CrossPerspectiveAlignment NameCert obligations]
\label{thm:cross-perspective-alignment-namecert-obligations}
The local $\NameCert_{\CrossPerspectiveAlignmentUp}$ surface has five finite obligations: carrier exposure by \autoref{def:cross-perspective-alignment-carrier}; public other-minds commitment through $O$; locality-cell evidence soundness through $L$; inter-Hist coherence through the $\MultiHistConfigUp$ row $M$ and the displayed $\hsame$ and $\Cont$ rows; and non-escape from private $\mathsf{Self}$ access, hidden observer histories, host observer equality, and unrecorded cross-perspective synchronization.
\end{theorem}
\begin{proof}
Carrier exposure is projection from the finite packet $B=(A,B,L,O,M,H,C,P,N)$.

The public commitment obligation is read from $O$. It uses $\OtherMindsCommitmentUp$ as a public certificate surface, so the target observer row is available only through visible commitment data.

The locality and inter-Hist obligations are read next. The locality-cell evidence is the row $L$, while finite inter-Hist coherence is the row $M$ transported by $H$ and consumed through $C$.

Finally inspect the coordinate list. There is no field for private target $\mathsf{Self}$ access, hidden observer history, host observer equality, or unrecorded synchronization, so none of those data can be exported by the packet.
\end{proof}

\begin{theorem}[CrossPerspectiveAlignment locality-cell soundness]
\label{thm:cross-perspective-alignment-locality-cell-soundness}
Every accepted $\CrossPerspectiveAlignmentUp$ packet aligns perspectives only after the public locality-cell evidence row $L$, the $\OtherMindsCommitmentUp$ row $O$, and the $\MultiHistConfigUp$ row $M$ are displayed in the same finite packet. A consumer may read $A,B,L,O,M,H,C,P,N$, but it cannot replace $L$ by private target-state access, a global observer frame, or an unlisted synchronization coordinate.
\end{theorem}
\begin{proof}
Project the accepted packet as $B=(A,B,L,O,M,H,C,P,N)$. The locality-cell evidence available to the consumer is exactly the displayed coordinate $L$.

The target public row is tied to the other-minds surface by $O$, and the inter-Hist comparison is tied to the finite configuration by $M$. The displayed transports $H$ and routes $C$ preserve those attachments as public certificate data.

No coordinate names private target-state access, a global observer frame, or an unlisted synchronization row. Thus locality-cell soundness is a finite public-evidence condition, not an ambient identification of observer states.
\end{proof}

\begin{theorem}[CrossPerspectiveAlignment non-escape boundary]
\label{thm:cross-perspective-alignment-nonescape}
An accepted $\CrossPerspectiveAlignmentUp$ carrier exports only the source-observer row, target-observer public row, locality-cell evidence row, public other-minds commitment row, finite multi-Hist configuration row, displayed $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row. It exports no private $\mathsf{Self}$ access for the target observer, no hidden observer history, no host observer equality, no global frame, and no unrecorded cross-perspective synchronization.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:cross-perspective-alignment-carrier}. Every exported row is one of $A$, $B$, $L$, $O$, $M$, $H$, $C$, $P$, or $N$.

The rows $L$, $O$, and $M$ are public certificate rows: locality-cell evidence, other-minds commitment, and finite multi-Hist configuration. The rows $H$ and $C$ only transport and route those displayed public rows.

There is no remaining coordinate for target private $\mathsf{Self}$ access, hidden observer history, host observer equality, a global frame, or unrecorded synchronization. Hence the alignment packet cannot export any of those objects.
\end{proof}

\begin{theorem}[CrossPerspectiveAlignment observer-identity handoff]
\label{thm:cross-perspective-alignment-observer-identity-handoff}
Every accepted $\CrossPerspectiveAlignmentUp$ alignment packet reads the target public identity only through the displayed observer-history identity and other-minds commitment rows. The target row $B$ may be consumed as a public $\ObserverHistIdentityUp/\OtherMindsCommitmentUp$ handoff carried by $O,H,C,P,N$, but no read may pass through a private target $\mathsf{Self}$ coordinate or identify the two observers by host equality.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cross-perspective-alignment-carrier}. The target row is the public coordinate $B$, and its commitment route is the row $O$ together with the displayed transports and continuations $H$ and $C$.

Use the NameCert obligations of \autoref{thm:cross-perspective-alignment-namecert-obligations}. They require public other-minds commitment through $O$ and make carrier exposure a finite packet read rather than a private observer-state read.

Finally apply the non-escape boundary of \autoref{thm:cross-perspective-alignment-nonescape}. Since the packet has no coordinate for private target $\mathsf{Self}$ access or host observer equality, every accepted target-identity handoff is exhausted by the public observer-history and other-minds rows already displayed.
\end{proof}

\begin{theorem}[CrossPerspectiveAlignment finite multi-Hist coherence]
\label{thm:cross-perspective-alignment-finite-multihist-coherence}
Every inter-history comparison accepted by $\CrossPerspectiveAlignmentUp$ factors through the finite $\MultiHistConfigUp$ row $M$, the componentwise $\hsame$ transports recorded in $H$, and the $\Cont$ routes recorded in $C$. No comparison may appeal to an ambient global history, an unlisted synchronization row, or a hidden equality between observer histories.
\end{theorem}
\begin{proof}
Read the carrier coordinates. The only inter-history configuration coordinate is $M$, and the only transport and consumer routes attached to it are the displayed rows $H$ and $C$.

The locality-cell soundness theorem \autoref{thm:cross-perspective-alignment-locality-cell-soundness} requires $L,O,M,H,C,P,N$ to appear in the same finite packet before the alignment is consumed. Thus comparison across histories is a replay of the finite multi-Hist row through the stored transport and continuation data.

The non-escape theorem \autoref{thm:cross-perspective-alignment-nonescape} excludes hidden observer histories, host observer equality, global frames, and unrecorded synchronization. Hence finite multi-Hist coherence is exactly the route through $M,H,C$, not an ambient comparison outside the packet.
\end{proof}

\begin{theorem}[CrossPerspectiveAlignment public consumer package]
\label{thm:cross-perspective-alignment-public-consumer-package}
The carrier exposure of \autoref{def:cross-perspective-alignment-carrier}, locality-cell soundness, observer-identity handoff, finite multi-Hist coherence, non-escape, and the displayed TasteGate marker assemble the public obligation package for $\CrossPerspectiveAlignmentUp$. A public consumer receives only the finite rows $A,B,L,O,M,H,C,P,N$ with their $\NameCert$ obligations, and receives no private target $\mathsf{Self}$, hidden observer history, host observer equality, global frame, or unrecorded synchronization.
\end{theorem}
\begin{proof}
Begin with the carrier definition. It displays exactly the source observer, target public observer, locality-cell evidence, other-minds commitment, multi-Hist configuration, componentwise transport, continuation, package provenance, and local naming rows.

Apply the existing NameCert obligation and locality-cell soundness theorems. They bind carrier exposure, public other-minds commitment through $O$, locality-cell evidence through $L$, and finite inter-Hist coherence through $M,H,C$.

The observer-identity handoff and finite multi-Hist coherence theorems above isolate the two consumer routes that would otherwise be ambiguous. The first keeps target public identity behind the observer-history and other-minds rows; the second keeps inter-history comparison behind the finite $M,H,C$ route.

Finally use the non-escape theorem and the checked TasteGate alignment marker. Non-escape removes private and ambient coordinates from the package, while the marker records that the displayed carrier is the single TasteGate-aligned carrier surface. Thus the public obligation package is finite and contains only the listed rows.
\end{proof}

\closureat{CrossPerspectiveAlignmentUp}{seedStr}
\closureat{CrossPerspectiveAlignmentUp}{obligationStr}

\begin{closurestatus}{\CrossPerspectiveAlignmentUp}
  \constructivestory{A $\CrossPerspectiveAlignmentUp$ packet is generated from a source observer row, a target public observer row, locality-cell evidence, a public $\OtherMindsCommitmentUp$ row, a finite $\MultiHistConfigUp$ row, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \leanchecked{BEDC.Derived.CrossPerspectiveAlignmentUp.taste\_gate}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:cross-perspective-alignment-carrier}, \autoref{thm:cross-perspective-alignment-namecert-obligations}, \autoref{thm:cross-perspective-alignment-locality-cell-soundness}, \autoref{thm:cross-perspective-alignment-nonescape}, \autoref{thm:cross-perspective-alignment-observer-identity-handoff}, \autoref{thm:cross-perspective-alignment-finite-multihist-coherence}, and \autoref{thm:cross-perspective-alignment-public-consumer-package} bind the finite public alignment surface over ObserverHistIdentity, OtherMindsCommitment, LocalityCell, MultiHistConfig, hsame, Cont, Pkg, NameCert, and the checked TasteGate carrier marker.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close a Lean implementation, bridge status, private access to another observer's $\mathsf{Self}$, hidden observer histories, host observer equality, a global frame, or unrecorded synchronization.}
  \upgradepath{Scoped closure requires checked carrier admission, observer-identity handoff, finite multi-Hist coherence, locality-cell soundness, non-escape, and TasteGate nontriviality with field faithfulness.}
\end{closurestatus}
