\chapter{A Concrete Naming Certificate for \(\IntervalUp\)}
\label{ch:concrete-instances-interval-namecert}

The unit interval interface \(\IntervalUp\) is licensed over Bishop reals from \autoref{ch:concrete-instances-real-namecert} as the predicate "\(0 \le x\) and \(x \le 1\)" interpreted constructively (with explicit moduli for the inequalities). The classifier is real sameness restricted to interval witnesses. It is not a primitive geometric object; it is licensed only as a derived sub-carrier of \(\RealUp\).

\begin{remark}[Interval certificate scope]
\label{rem:concrete-instances-interval-namecert-roadmap}
This chapter records the interval licensing target as a bounded subcarrier
with classifier transport inherited from internal history sameness.
\end{remark}

\section{Carrier definition}

\begin{definition}[Interval carrier]
\label{def:interval-carrier}
Use real witnesses \(x:\RealUp\) paired with constructive proofs \(0\le x\) and \(x\le1\).
\end{definition}

\begin{theorem}[Interval empty boundary]
\label{thm:interval-empty-boundary-of-hsame}
If a history \(h\) is internally the same as \(\emp\), then \(h\) inhabits the interval carrier whose lower boundary is \(\hsame(\emp,-)\) and whose upper boundary is \(\hsame(-,\emp)\).
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalCarrier\_empty\_boundary\_of\_hsame}
\begin{proof}
Transport the unary empty history across the symmetry of the given \(\hsame(h,\emp)\) witness. The lower boundary uses the symmetric witness, and the upper boundary uses the original witness.
\end{proof}

\begin{theorem}[Interval empty-boundary carrier iff endpoint]
\label{thm:interval-empty-boundary-carrier-iff-endpoint}
For the interval carrier whose lower boundary is \(\hsame(\emp,-)\) and whose
upper boundary is \(\hsame(-,\emp)\), carrier membership of \(h\) is equivalent
to the endpoint witness \(\hsame(h,\emp)\).
\end{theorem}
\begin{proof}
In the forward direction, eliminate the concrete interval-carrier conjunction
and project the upper-boundary witness. In the reverse direction, apply the
empty-boundary carrier constructor to the endpoint witness.
\end{proof}
\leanchecked{BEDC.Derived.IntervalUp.IntervalCarrier\_empty\_boundary\_iff\_hsame\_empty}

\begin{theorem}[Interval empty boundary hsame transport]
\label{thm:interval-empty-boundary-hsame-transport}
For the interval carrier whose lower boundary is \(\hsame(\emp,-)\) and whose upper boundary is \(\hsame(-,\emp)\), internal sameness transports carrier membership.
\end{theorem}
\begin{proof}
Unpack the interval carrier into unary membership and the two boundary witnesses. Unary membership transports along the given \(\hsame\) witness. The lower boundary composes \(\hsame(\emp,h)\) with \(\hsame(h,k)\), and the upper boundary composes the symmetric witness \(\hsame(k,h)\) with \(\hsame(h,\emp)\).
\end{proof}
\leanchecked{BEDC.Derived.IntervalUp.IntervalCarrier\_empty\_boundary\_hsame\_transport}

\begin{definition}[Interval empty-boundary ledger policy]
\label{def:interval-empty-boundary-ledger-policy}
The empty-boundary interval ledger records a raw endpoint in the concrete
carrier whose lower boundary is \(\hsame(\emp,-)\) and whose upper boundary is
\(\hsame(-,\emp)\), together with an internal history-sameness link from the
raw endpoint to the visible endpoint.
\end{definition}
\leandef{BEDC.Derived.IntervalUp.IntervalEmptyBoundaryLedgerPolicy}

\begin{theorem}[Interval empty-boundary ledger visible carrier]
\label{thm:interval-empty-boundary-ledger-visible-carrier}
If an empty-boundary interval ledger relates a raw endpoint to a visible
endpoint, then the visible endpoint remains in the same concrete
empty-boundary interval carrier.
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalEmptyBoundaryLedgerPolicy\_visible\_carrier}
\begin{proof}
Unpack the ledger into raw carrier evidence and the raw-visible
\(\hsame\) link. The empty-boundary carrier transport theorem carries the raw
carrier evidence across that link to the visible endpoint.
\end{proof}

\begin{theorem}[Interval empty-boundary ledger visible no zero endpoint]
\label{thm:interval-empty-boundary-ledger-visible-no-e0}
No visible endpoint of an empty-boundary interval ledger can have the form
$\mathsf{e0}(t)$.
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalEmptyBoundaryLedgerPolicy\_visible\_no\_e0}
\begin{proof}
The visible-carrier theorem exposes the transported empty-boundary carrier at
$\mathsf{e0}(t)$. Its upper boundary is an $\hsame(\mathsf{e0}(t),\emp)$
witness, contradicting BEDC history no-confusion.
\end{proof}

\begin{theorem}[Interval empty-boundary ledger raw-visible classifier]
\label{thm:interval-empty-boundary-ledger-raw-visible-classifier}
If an empty-boundary interval ledger relates a raw endpoint to a visible
endpoint, then those endpoints satisfy the restricted empty-boundary interval
classifier.
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalEmptyBoundaryLedgerPolicy\_raw\_visible\_classifier}
\begin{proof}
Unpack the ledger into raw carrier evidence and the raw-visible \(\hsame\)
link. The visible carrier theorem supplies the visible endpoint carrier, and
the two carrier witnesses with the stored link rebuild the interval classifier.
\end{proof}

\begin{theorem}[Interval empty-boundary ledger classifier endpoint equivalence]
\label{thm:interval-empty-boundary-ledger-classifier-endpoint-equivalence}
If $\mathsf{IntervalEmptyBoundaryLedgerPolicy}(\rho,v)$ holds, then every
target history $w$ is classified from $\rho$ exactly when it is classified from
$v$ by the empty-boundary interval classifier:
$$
\mathsf{IntervalClassifierSpec}_{\emp}(\rho,w)\leftrightarrow
\mathsf{IntervalClassifierSpec}_{\emp}(v,w).
$$
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalEmptyBoundaryLedgerPolicy\_classifier\_endpoint\_equivalence}
\begin{proof}
The ledger supplies the raw-visible empty-boundary interval classifier. For the
raw-to-visible direction, reverse that classifier by symmetry and compose it
with the raw-target classifier by transitivity. For the visible-to-raw
direction, compose the raw-visible classifier with the visible-target
classifier.
\end{proof}

\begin{theorem}[Interval empty boundary carrier uniqueness]
\label{thm:interval-empty-boundary-carrier-uniqueness}
For the interval carrier whose lower boundary is \(\hsame(\emp,-)\) and whose
upper boundary is \(\hsame(-,\emp)\), any two carrier inhabitants are
internally the same history.
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalCarrier\_empty\_boundary\_unique}
\begin{proof}
Unpack the two carrier witnesses and read their upper-bound witnesses
\(\hsame(h,\emp)\) and \(\hsame(k,\emp)\). Compose the first with the symmetry
of the second to obtain \(\hsame(h,k)\).
\end{proof}

\begin{theorem}[Interval empty-boundary classifier]
\label{thm:interval-empty-boundary-classifier}
If \(h\) and \(k\) are both internally the same as \(\emp\), then they satisfy the interval classifier whose lower boundary is \(\hsame(\emp,-)\) and whose upper boundary is \(\hsame(-,\emp)\).
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_empty\_boundary\_of\_hsame}
\begin{proof}
Apply the empty-boundary carrier theorem to \(h\) and to \(k\). The classifier relation is \(\HSame(h,k)\), obtained by composing \(\HSame(h,\emp)\) with the symmetry of \(\HSame(k,\emp)\).
\end{proof}

\begin{theorem}[Interval empty-boundary classifier characterization]
\label{thm:interval-empty-boundary-classifier-characterization}
For the interval classifier whose lower boundary is \(\hsame(\emp,-)\) and
whose upper boundary is \(\hsame(-,\emp)\), a pair \(h,k\) is classified
exactly when both endpoint histories are internally the same as \(\emp\).
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_empty\_boundary\_iff}
\begin{proof}
In the forward direction, eliminate the restricted classifier witness and read
the two upper-bound witnesses from the carrier data. In the reverse direction,
apply the empty-boundary classifier theorem to the two endpoint witnesses.
\end{proof}

\begin{theorem}[Interval empty-boundary classifier iff endpoints]
\label{thm:interval-empty-boundary-classifier-iff-endpoints}
For the interval classifier whose lower boundary is $\hsame(\emp,-)$ and whose upper boundary is $\hsame(-,\emp)$, a classifier witness between $h$ and $k$ is equivalent to endpoint witnesses $\hsame(h,\emp)$ and $\hsame(k,\emp)$.
\end{theorem}
\begin{proof}
In one direction, eliminate the restricted classifier witness and project the upper-boundary fields from the two interval carriers. In the other direction, apply the empty-boundary classifier constructor to the two endpoint witnesses.
\end{proof}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_empty\_boundary\_iff\_endpoints}

\begin{theorem}[Interval empty boundary excludes left zero-extension]
\label{thm:interval-empty-boundary-e0-left-absurd}
For the interval classifier whose lower boundary is \(\hsame(\emp,-)\) and
whose upper boundary is \(\hsame(-,\emp)\), no classifier witness can have
left endpoint \(\Ezero(t)\).
\end{theorem}
\begin{proof}
Eliminate the classifier witness and read the upper-boundary field of the left
carrier. It gives \(\hsame(\Ezero(t),\emp)\), contradicting BEDC history
no-confusion for zero-extension versus the empty history.
\end{proof}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_empty\_boundary\_no\_e0\_left}

\section{The certificate}

\begin{definition}[Interval source specification]
\label{def:interval-source-specification}
The source is the Bishop real source restricted to the closed unit interval predicate.
\end{definition}

\begin{definition}[Interval pattern specification]
\label{def:interval-pattern-specification}
The pattern is subcarrier formation by attaching lower and upper bound witnesses to a real.
\end{definition}

\begin{definition}[Interval classifier specification]
\label{def:interval-classifier-specification}
The classifier is \(\RealUp\) sameness restricted to interval witnesses.
\end{definition}

\begin{theorem}[Interval classifier transitivity]
\label{thm:interval-classifier-transitivity}
If interval classifier witnesses relate \(h\) to \(k\) and \(k\) to \(r\), then
they determine an interval classifier witness from \(h\) to \(r\).
\end{theorem}
\begin{proof}
Eliminate both restricted classifier witnesses. The first left carrier and the
second right carrier become the endpoint data for the composite classifier, and
the underlying history link is the transitive composite of the two \(\HSame\)
witnesses.
\end{proof}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_trans}

\begin{theorem}[Interval classifier symmetry]
\label{thm:interval-classifier-symmetry}
If interval classifier witnesses relate \(h\) to \(k\), then they determine an
interval classifier witness from \(k\) to \(h\).
\end{theorem}
\begin{proof}
Eliminate the restricted classifier witness. The endpoint interval-carrier
witnesses are exchanged, and the stored history-sameness link is reversed by
symmetry of \(\hsame\).
\end{proof}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_symm}

\begin{definition}[Interval stability certificate]
\label{def:interval-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item real classifier reflexivity and transitivity
  \item lower-bound preservation under real sameness
  \item upper-bound preservation under real sameness
  \item closure of endpoints \(0\) and \(1\)
  \item closure of interval operations explicitly proved to preserve bounds
\end{enumerate}
\end{definition}

\begin{definition}[Interval ledger policy]
\label{def:interval-ledger-policy}
Record the real ledger and both inequality moduli.
\end{definition}

\begin{definition}[\(\IntervalUp\) certificate obligations]
\label{def:interval-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\IntervalUp\).
\end{definition}

\begin{theorem}[Concrete \(\IntervalUp\) naming certificate]
\label{thm:concrete-interval-namecert}
The bounded-real subcarrier tuple forms a valid NameCert for \(\IntervalUp\).
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.interval\_name\_certificate}

\paragraph{Primitive boundary.}
\(\IntervalUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:interval-zero-axiom-note}
Uses constructive inequality witnesses with moduli rather than classical order trichotomy.
\end{remark}

\begin{closurestatus}{\IntervalUp}
  \constructivestory{}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The scoped interval certificate binds the bounded-real subcarrier, lower and upper boundary predicates, restricted interval classifier, empty-boundary ledger policy, boundary weakening maps, $\mathsf{BHist}$, and $\hsame$ transport.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.IntervalUp.interval\_name\_certificate}
  \bridgestatus{none}
  \notclaimed{General interval arithmetic, compactness of $[0,1]$, metric completeness, Heine-Borel, and any standard bridge to external real intervals are not closed here.}
  \upgradepath{A stronger closure grade requires public interval operations, compactness or metric bridge theorems, and standard-reference interval comparison certificates.}
\end{closurestatus}

\begin{theorem}[Interval carrier boundary weakening]
\label{thm:interval-carrier-boundary-weakening}
Let \(\ell_1,\ell_2,u_1,u_2:\mathsf{BHist}\to\mathsf{Prop}\) be interval boundary predicates. Suppose that for every history \(h:\mathsf{BHist}\) there are pointwise boundary maps
$$
\lambda_h:\ell_2(h)\to\ell_1(h),
\qquad
\upsilon_h:u_2(h)\to u_1(h).
$$
Then every inhabitant of the inner interval carrier is an inhabitant of the outer interval carrier:
$$
\mathsf{IntervalCarrier}_{\ell_2,u_2}(h)\to
\mathsf{IntervalCarrier}_{\ell_1,u_1}(h).
$$
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalCarrier\_boundary\_weakening}
\begin{proof}
By \autoref{def:interval-carrier}, an inner carrier witness consists of unary membership for \(h\), a lower-bound witness in \(\ell_2(h)\), and an upper-bound witness in \(u_2(h)\). Keep the unary membership witness unchanged. Apply the pointwise lower-bound map \(\lambda_h\) to the lower witness, and apply the pointwise upper-bound map \(\upsilon_h\) to the upper witness. These three witnesses reconstruct \(\mathsf{IntervalCarrier}_{\ell_1,u_1}(h)\) by \autoref{def:interval-carrier}.
\end{proof}

\begin{theorem}[Interval classifier boundary weakening]
\label{thm:interval-classifier-boundary-weakening}
Let \(\ell_1,\ell_2,u_1,u_2:\mathsf{BHist}\to\mathsf{Prop}\) be interval boundary predicates. Suppose that for every history \(x:\mathsf{BHist}\) there are pointwise boundary maps
$$
\lambda_x:\ell_2(x)\to\ell_1(x),
\qquad
\upsilon_x:u_2(x)\to u_1(x).
$$
Then for all histories \(h,k:\mathsf{BHist}\),
$$
\mathsf{IntervalClassifierSpec}_{\ell_2,u_2}(h,k)\to
\mathsf{IntervalClassifierSpec}_{\ell_1,u_1}(h,k).
$$
\end{theorem}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_boundary\_weakening}
\begin{proof}
Eliminate the inner classifier witness using \autoref{def:interval-classifier-specification}. It consists of an \(\mathsf{IntervalCarrier}_{\ell_2,u_2}(h)\) witness, an \(\mathsf{IntervalCarrier}_{\ell_2,u_2}(k)\) witness, and the stored \(\hsame(h,k)\) link. Apply \autoref{thm:interval-carrier-boundary-weakening} at \(h\) to obtain \(\mathsf{IntervalCarrier}_{\ell_1,u_1}(h)\), and apply the same theorem at \(k\) to obtain \(\mathsf{IntervalCarrier}_{\ell_1,u_1}(k)\). Rebuild the restricted classifier from these two carrier witnesses and the unchanged stored \(\hsame(h,k)\) witness by \autoref{def:interval-classifier-specification}.
\end{proof}

\begin{proposition}[Interval nesting requires boundary eliminators]
\label{prop:interval-nesting-requires-boundary-eliminators}
There is a finite one-history interpretation of the interval carrier and classifier clauses in which bare symbolic lower- and upper-nesting assumptions hold, the inner interval classifier holds at the unique endpoint, and the outer interval classifier fails at the pair of unique endpoints. Hence the classifier weakening
$$
\mathsf{IntervalClassifierSpec}_{\ell_{\mathrm{in}},u_{\mathrm{in}}}(h,k)\to
\mathsf{IntervalClassifierSpec}_{\ell_{\mathrm{out}},u_{\mathrm{out}}}(h,k)
$$
is not forced by symbolic nesting data unless that data eliminates to pointwise boundary maps
$$
\forall x:\mathsf{BHist},\ \ell_{\mathrm{in}}(x)\to\ell_{\mathrm{out}}(x)
\qquad\text{and}\qquad
\forall x:\mathsf{BHist},\ u_{\mathrm{in}}(x)\to u_{\mathrm{out}}(x),
$$
as required by \autoref{thm:interval-classifier-boundary-weakening}. In the naming-certificate template of \autoref{def:typed-naming-certificate}, a classifier-facing nesting field must therefore supply those maps, or data from which those maps are obtained.
\end{proposition}
\leanchecked{BEDC.Derived.IntervalUp.IntervalClassifierSpec\_boundary\_eliminator\_counterexample}
\begin{proof}
Interpret $\mathsf{BHist}$ by the singleton set $H=\{\star\}$. Let the unary-history predicate hold at $\star$, and let $\hsame(\star,\star)$ hold. Define the inner and outer boundaries by
$$
\ell_{\mathrm{in}}(\star)=\top,\qquad
u_{\mathrm{in}}(\star)=\top,\qquad
\ell_{\mathrm{out}}(\star)=\bot,\qquad
u_{\mathrm{out}}(\star)=\bot.
$$
Let the bare symbolic lower-nesting and upper-nesting assumptions be two atomic propositions $\sigma_{\ell}$ and $\sigma_{u}$, both interpreted by $\top$.

By \autoref{def:interval-carrier}, $\mathsf{IntervalCarrier}_{\ell_{\mathrm{in}},u_{\mathrm{in}}}(\star)$ holds: its witnesses are the unary-history witness, the true inner lower-bound witness, and the true inner upper-bound witness. Together with $\hsame(\star,\star)$, \autoref{def:interval-classifier-specification} gives
$$
\mathsf{IntervalClassifierSpec}_{\ell_{\mathrm{in}},u_{\mathrm{in}}}(\star,\star).
$$

If the outer classifier held, \autoref{def:interval-classifier-specification} would expose an outer carrier witness at the left endpoint. Eliminating that carrier by \autoref{def:interval-carrier} would give a witness of $\ell_{\mathrm{out}}(\star)$ and a witness of $u_{\mathrm{out}}(\star)$. These are witnesses of $\bot$, so the outer classifier fails.

A lower-bound eliminator in this interpretation is exactly a map $\top\to\bot$, obtained by evaluating $\forall x:H,\ \ell_{\mathrm{in}}(x)\to\ell_{\mathrm{out}}(x)$ at $\star$. Applying such a map to the true inner lower-bound witness would produce a contradiction. The upper-bound eliminator has the same form after evaluating $\forall x:H,\ u_{\mathrm{in}}(x)\to u_{\mathrm{out}}(x)$ at $\star$. Thus the true symbolic tokens $\sigma_{\ell}$ and $\sigma_{u}$ do not determine carrier inclusion; only boundary eliminators, or structure that yields them, can support interval classifier weakening.
\end{proof}
