\chapter{A Concrete Naming Certificate for $\ObserverPerspectiveClassifierUp$}
\label{ch:concrete-instances-observerperspectiveclassifier-namecert}
\origin{human}

The $\ObserverPerspectiveClassifierUp$ surface packages comparison between two observers as a finite public certificate. Each observer keeps its own universe-for-observer row; the classifier compares only the displayed rows that pass through locality cells, $\mathsf{GAP}$ commitments, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and the local naming row. It is not a global view over both worlds.

The packet consumes \autoref{ch:concrete-instances-consciousobserverstate-namecert} for the two observer-state rows $O_0,O_1$. Its locality evidence is read from the public cell surfaces of \autoref{ch:concrete-instances-localitycell-namecert} or \autoref{ch:concrete-instances-observer-locality-cell-namecert}, and the comparison is checked against the public alignment surface of \autoref{ch:concrete-instances-crossperspectivealignment-namecert} rather than against an ambient shared world.

\begin{definition}[Observer-perspective-classifier carrier]
\label{def:observer-perspective-classifier-carrier}
An $\ObserverPerspectiveClassifierUp$ carrier is a finite $\BHist$ packet
$$
Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O_0$ and $O_1$ are accepted $\ConsciousObserverStateUp$ rows naming the two conscious-observer state surfaces being compared;
\item $U_0$ and $U_1$ are the two universe-for-observer record surfaces, each read only as the records and closure rules accumulated by the corresponding observer row;
\item $L$ is the locality-cell evidence row, displayed as a $\LocalityCellUp$ or $\ObserverLocalityCellUp$ public coordination surface for the two observer rows;
\item $G$ is the paired $\mathsf{GAP}$ commitment ledger recording the two-sided coherence commitments by which $U_0$ and $U_1$ can be compared without identifying them as one host world;
\item $H$ records componentwise $\hsame$ transports for $O_0,O_1,U_0,U_1,L,G$ and for the package and local naming rows;
\item $C$ records the displayed $\Cont$ routes that let a consumer read each observer row, its universe-for-observer surface, the locality-cell evidence, and the paired $\mathsf{GAP}$ commitments in that order;
\item $P$ is the $\Pkg$ provenance over $\ConsciousObserverStateUp$, universe-for-observer record surfaces, $\LocalityCellUp$, $\ObserverLocalityCellUp$, $\mathsf{GAP}$ ledgers, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ObserverPerspectiveClassifierUp}$ row.
\end{enumerate}
The classifier compares two accepted carriers only through the displayed rows $O_0,O_1,U_0,U_1,L,G,H,C,P,N$ and their recorded transports and routes.
\end{definition}
\leandef{BEDC.Derived.ObserverperspectiveclassifierUp.ObserverPerspectiveClassifierCarrier}

\begin{theorem}[ObserverPerspectiveClassifier NameCert obligations]
\label{thm:observer-perspective-classifier-namecert-obligations}
For the carrier of \autoref{def:observer-perspective-classifier-carrier}, the local $\NameCert_{\ObserverPerspectiveClassifierUp}$ surface has exactly five obligation rows: carrier exposure for $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$; observer anchoring through $O_0,O_1$; universe-for-observer exposure through $U_0,U_1$; locality and coherence comparison through $L,G,H,C$; and non-escape from a god's-eye observer, host equality of worlds, private $\mathsf{Self}$ access, global spacetime carriers, hidden synchronization maps, and unrecorded cross-perspective evidence.
\end{theorem}
\begin{proof}
Carrier exposure is projection from the finite packet $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$.

Observer anchoring is read from $O_0$ and $O_1$. Universe-for-observer exposure is read from $U_0$ and $U_1$, with each universe surface attached to its own observer row.

The comparison obligation is then read from $L,G,H,C$. The locality-cell row $L$ supplies the public coordination surface, the paired $\mathsf{GAP}$ ledger $G$ records the coherence commitments, the transport row $H$ moves only displayed coordinates, and the continuation row $C$ replays only the displayed reading order.

Finally inspect the carrier list. No coordinate names a god's-eye observer, host equality of the two worlds, private $\mathsf{Self}$ access, global spacetime carrier, hidden synchronization map, or unrecorded evidence row, so none of those objects is exported by the local naming surface.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier locality-cell comparison]
\label{thm:observer-perspective-classifier-locality-cell-comparison}
Every accepted $\ObserverPerspectiveClassifierUp$ packet compares $U_0$ and $U_1$ only after the observer rows $O_0,O_1$, the locality-cell evidence $L$, and the paired $\mathsf{GAP}$ commitments $G$ have been displayed in the same finite carrier. A consumer may classify the two perspectives through $H$ and $C$, but it cannot replace the locality-cell comparison by a single ambient world, a shared external spacetime, or direct access to either observer's private $\mathsf{Self}$ row.
\end{theorem}
\begin{proof}
Project the accepted packet and read the two observer rows $O_0,O_1$ together with their universe-for-observer surfaces $U_0,U_1$.

The classifier is not applied to those universe surfaces in isolation. It first uses the locality-cell evidence $L$ and the paired $\mathsf{GAP}$ ledger $G$, then replays those rows through the displayed transports $H$ and continuations $C$.

Since the packet contains no ambient world coordinate, shared external spacetime row, or private $\mathsf{Self}$ coordinate, the comparison remains a finite locality-cell comparison between displayed observer perspectives.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier ledger exactness]
\label{thm:observer-perspective-classifier-ledger-exactness}
Every public read exported by an accepted $\ObserverPerspectiveClassifierUp$ carrier factors through the finite ledger
$$
O_0,O_1,U_0,U_1,L,G,H,C,P,N.
$$
The ledger is exact: observer rows, universe-for-observer surfaces, locality-cell evidence, paired $\mathsf{GAP}$ commitments, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ row are available, and no other comparison primitive is available.
\end{theorem}
\begin{proof}
The carrier definition displays all rows of the packet. The mathematical comparison data are $O_0,O_1,U_0,U_1,L,G$, and the structural data are $H,C,P,N$.

Any consumer read must pass through the displayed continuation routes in $C$. Those routes expose the two observer rows, their universe surfaces, the locality evidence, and the paired commitments before the package and naming rows are read.

There is no remaining coordinate for a second comparison primitive. Thus every exported read factors through the listed ledger and the ledger is exact for public consumers.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier non-escape boundary]
\label{thm:observer-perspective-classifier-nonescape}
An accepted $\ObserverPerspectiveClassifierUp$ carrier exports only the two conscious-observer state rows, the two universe-for-observer record surfaces, the locality-cell evidence row, the paired $\mathsf{GAP}$ commitment ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ row. It exports no god's-eye observer, no host equality of worlds, no private $\mathsf{Self}$ access, and no global spacetime carrier.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:observer-perspective-classifier-carrier}. Every exported row is one of $O_0,O_1,U_0,U_1,L,G,H,C,P,N$.

The positive comparison data remain public and finite: observer rows, universe-for-observer surfaces, locality-cell evidence, and paired $\mathsf{GAP}$ commitments. The rows $H,C,P,N$ transport, route, package, and name those same displayed coordinates.

No listed coordinate is a god's-eye observer, a host equality witness between worlds, a private $\mathsf{Self}$ row, or a global spacetime carrier. Therefore an accepted classifier cannot export any of those objects.
\end{proof}
\leanchecked{BEDC.Derived.ObserverperspectiveclassifierUp.ObserverPerspectiveClassifierNonescape}

\begin{theorem}[ObserverPerspectiveClassifier anchor-change stability]
\label{thm:observer-perspective-classifier-anchor-change-stability}
In an accepted $\ObserverPerspectiveClassifierUp$ carrier, changing the observer anchor from the $O_0$ side to the $O_1$ side, or from the $O_1$ side to the $O_0$ side, preserves a comparison verdict only through the displayed rows
$$
O_0,O_1,U_0,U_1,L,G,H,C,P,N.
$$
The stability route may use the two observer rows, the two universe-for-observer surfaces, locality evidence, paired $\mathsf{GAP}$ commitments, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ row, but it cannot pass through a privileged observer or any unlisted observer-neutral witness.
\end{theorem}
\begin{proof}
Apply the carrier description in \autoref{def:observer-perspective-classifier-carrier}. The only named anchors are $O_0$ and $O_1$, and each universe-for-observer surface is attached to one of those rows.

Apply the obligation theorem \autoref{thm:observer-perspective-classifier-namecert-obligations}. Anchor comparison is part of the finite local naming surface, so an anchor change must be replayed through the displayed locality, commitment, transport, continuation, package, and naming rows.

The locality comparison theorem \autoref{thm:observer-perspective-classifier-locality-cell-comparison} supplies the admissible comparison route, while \autoref{thm:observer-perspective-classifier-ledger-exactness} says that the ledger has no further comparison coordinate. Finally \autoref{thm:observer-perspective-classifier-nonescape} rules out a god's-eye observer and any unlisted observer-neutral witness, so the comparison is stable only through the displayed packet rows.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier GAP commitment readback]
\label{thm:observer-perspective-classifier-gap-commitment-readback}
Every cross-perspective comparison exported by an accepted $\ObserverPerspectiveClassifierUp$ carrier reads the paired $\mathsf{GAP}$ row $G$ before it exports a comparison verdict. A verdict based only on $O_0,O_1,U_0,U_1$ or only on the locality row $L$ is not a public classifier verdict for this carrier.
\end{theorem}
\begin{proof}
The carrier in \autoref{def:observer-perspective-classifier-carrier} displays $G$ as the paired commitment ledger by which $U_0$ and $U_1$ can be compared without identifying them as one host world.

By \autoref{thm:observer-perspective-classifier-namecert-obligations}, the comparison obligation is not just observer exposure or universe exposure; it is the locality and coherence comparison through $L,G,H,C$. The locality-cell comparison theorem \autoref{thm:observer-perspective-classifier-locality-cell-comparison} makes the same ordering explicit: the classifier compares after the observer rows, the locality-cell evidence, and the paired $\mathsf{GAP}$ commitments have been displayed in the same finite carrier.

The exactness theorem \autoref{thm:observer-perspective-classifier-ledger-exactness} then prevents a consumer from dropping $G$ while still claiming the public verdict. The non-escape theorem \autoref{thm:observer-perspective-classifier-nonescape} prevents replacing $G$ by hidden synchronization or host equality, so the paired commitment row must be read before the verdict is exported.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier comparison-route totality]
\label{thm:observer-perspective-classifier-comparison-route-totality}
Every accepted comparison route for an $\ObserverPerspectiveClassifierUp$ carrier factors through all of the public classifier layers: observer rows $O_0,O_1$, universe-for-observer surfaces $U_0,U_1$, locality evidence $L$, paired $\mathsf{GAP}$ commitments $G$, componentwise $\hsame$ transports $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$.
\end{theorem}
\begin{proof}
Start with the finite packet in \autoref{def:observer-perspective-classifier-carrier}. Its displayed rows already enumerate the observer, universe, locality, commitment, transport, continuation, provenance, and naming layers.

Apply \autoref{thm:observer-perspective-classifier-namecert-obligations} to read those layers as the local naming obligations. Apply \autoref{thm:observer-perspective-classifier-locality-cell-comparison} to place the comparison after the observer rows, universe surfaces, locality evidence, and paired commitment ledger.

It remains to account for transport, routing, provenance, and local naming. The exactness theorem \autoref{thm:observer-perspective-classifier-ledger-exactness} says that public reads factor through $H,C,P,N$ after the mathematical comparison rows, and \autoref{thm:observer-perspective-classifier-nonescape} says that no hidden comparison route remains outside this finite list. Hence every accepted comparison route factors through the stated public classifier layers.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier state totality]
\label{thm:observer-perspective-classifier-state-totality}
Every accepted public verdict for an $\ObserverPerspectiveClassifierUp$ carrier exposes both $\ConsciousObserverStateUp$ rows $O_0,O_1$ and their universe-for-observer surfaces $U_0,U_1$ before the verdict is public. In particular, a row that exports a comparison verdict without first displaying the two observer-state rows and the two attached universe surfaces is not an accepted classifier verdict for the carrier $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$.
\end{theorem}
\begin{proof}
Unpack the carrier tuple of \autoref{def:observer-perspective-classifier-carrier}. Its first four displayed comparison rows are exactly $O_0,O_1,U_0,U_1$, with $O_0,O_1$ naming the two conscious-observer state surfaces and $U_0,U_1$ naming the corresponding universe-for-observer surfaces.

The exactness theorem \autoref{thm:observer-perspective-classifier-ledger-exactness} says that every public read exported by an accepted carrier factors through the finite ledger. The comparison-route totality theorem \autoref{thm:observer-perspective-classifier-comparison-route-totality} then orders any accepted comparison route through observer rows, universe surfaces, locality evidence, paired commitments, transports, routes, provenance, and local naming.

Finally \autoref{thm:observer-perspective-classifier-nonescape} rules out replacing those displayed rows by a god's-eye observer, host equality, private $\mathsf{Self}$ access, or a global spacetime carrier. Hence a public verdict must expose both observer-state rows and both universe-for-observer surfaces before it exports the classifier verdict.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier locality refinement]
\label{thm:observer-perspective-classifier-locality-refinement}
Let $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$ be an accepted $\ObserverPerspectiveClassifierUp$ carrier. If a locality-cell row $L'$ refines the displayed locality evidence $L$ and the same paired $\mathsf{GAP}$ row $G$ is transported with $L'$ through the recorded $\hsame$ row, the displayed $\Cont$ routes, and the $\Pkg$ provenance, then the public comparison route is the same accepted route with $L'$ in the locality coordinate. No public consumer gains an additional comparison primitive by refining $L$ in this way.
\end{theorem}
\begin{proof}
Begin with the carrier definition. The locality coordinate and the paired commitment coordinate occur as the adjacent public comparison rows $L,G$, while $H,C,P$ record the componentwise transports, displayed reading routes, and provenance for those same rows.

The ledger exactness theorem \autoref{thm:observer-perspective-classifier-ledger-exactness} makes the route exact: a public read may use the observer rows, universe surfaces, locality row, paired commitment row, transports, continuations, provenance, and the local naming row, and no further comparison coordinate is available.

Transporting the refined row $L'$ together with the same $G$ through $H,C,P$ therefore changes only the displayed locality coordinate. The route still passes through the same ordered classifier layers by \autoref{thm:observer-perspective-classifier-comparison-route-totality}.

The non-escape theorem \autoref{thm:observer-perspective-classifier-nonescape} prevents the refinement from introducing a hidden synchronization map, host equality, or observer-neutral witness. Thus the public comparison route is preserved with $L'$ in the locality coordinate.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier perspective stability]
\label{thm:observer-perspective-classifier-perspective-stability}
For an accepted $\ObserverPerspectiveClassifierUp$ carrier $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$, swapping the two observer perspectives preserves acceptedness exactly for the carrier whose observer rows, universe-for-observer surfaces, locality row, paired $\mathsf{GAP}$ row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, comparison route, and local $\NameCert$ row are swapped together. Swapping only one face of the carrier is not an accepted public perspective swap.
\end{theorem}
\begin{proof}
First unpack the finite carrier tuple. The observer faces are not isolated parameters: $O_0,O_1$ are paired with $U_0,U_1$, and the comparison is witnessed through the locality row $L$, the paired commitment row $G$, the transport row $H$, the continuation row $C$, the provenance row $P$, and the local naming row $N$.

For the forward direction, assume the public perspective swap is accepted. By \autoref{thm:observer-perspective-classifier-state-totality}, both observer-state rows and both universe-for-observer surfaces must be exposed before the verdict. By \autoref{thm:observer-perspective-classifier-comparison-route-totality}, the accepted route also carries the locality, commitment, transport, continuation, provenance, and naming layers, so those layers must travel with the swapped perspectives.

For the reverse direction, swap the two observer rows together with their universe surfaces and carry the locality row, paired $\mathsf{GAP}$ row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, comparison route, and local $\NameCert$ row through the same finite ledger positions. The carrier definition still displays a tuple of the required form, and \autoref{thm:observer-perspective-classifier-ledger-exactness} supplies the same public readback surface.

It remains to exclude partial swaps. The non-escape theorem \autoref{thm:observer-perspective-classifier-nonescape} rules out any unlisted observer-neutral witness that could repair a swap of only one face. Hence acceptedness is preserved exactly when the paired observer rows, universe surfaces, locality evidence, paired commitment row, transports, routes, provenance, comparison route, and local naming row are swapped together.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier dependency scope]
\label{thm:observer-perspective-classifier-dependency-scope}
The accepted dependency scope of an $\ObserverPerspectiveClassifierUp$ carrier is exactly the finite public row family supplied by $\ConsciousObserverStateUp$, $\LocalityCellUp$ or $\ObserverLocalityCellUp$, $\CrossPerspectiveAlignmentUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The classifier has no dependency on an ambient world row, host equality between worlds, private $\mathsf{Self}$ access, global spacetime carrier, hidden synchronization map, or unrecorded cross-perspective evidence.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:observer-perspective-classifier-carrier}. Its comparison rows are the two conscious-observer state rows, the two universe-for-observer surfaces, the locality-cell row, and the paired $\mathsf{GAP}$ row; its structural rows are the $\BHist$ packet, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.

Apply \autoref{thm:observer-perspective-classifier-locality-cell-comparison} and \autoref{thm:observer-perspective-classifier-gap-commitment-readback}. They force any comparison to pass through the displayed locality evidence, paired commitment ledger, and recorded alignment surface rather than through a shared ambient world.

Finally apply \autoref{thm:observer-perspective-classifier-ledger-exactness} and \autoref{thm:observer-perspective-classifier-nonescape}. Exactness says no other comparison primitive is available, and non-escape excludes ambient world rows, host equality, private $\mathsf{Self}$ access, global spacetime carriers, hidden synchronization maps, and unrecorded evidence.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier alignment consumer]
\label{thm:observer-perspective-classifier-alignment-consumer}
Every downstream cross-perspective consumer of an accepted $\ObserverPerspectiveClassifierUp$ verdict must read the comparison through the displayed locality row, paired $\mathsf{GAP}$ commitment row, transport row, continuation row, provenance row, and local $\NameCert$ row. A consumer that bypasses one of those displayed rows is not reading the public classifier verdict.
\end{theorem}
\begin{proof}
Start from an accepted public verdict. By \autoref{thm:observer-perspective-classifier-comparison-route-totality}, the verdict route factors through $O_0,O_1,U_0,U_1,L,G,H,C,P,N$ in the public classifier layers.

The consumer side only needs the comparison layers after the observer-state and universe surfaces have been exposed. Those layers are precisely the locality row $L$, paired commitment row $G$, transport row $H$, continuation row $C$, provenance row $P$, and local naming row $N$.

If a consumer bypasses one of these rows, \autoref{thm:observer-perspective-classifier-ledger-exactness} says the read no longer factors through the exact public ledger. The non-escape boundary of \autoref{thm:observer-perspective-classifier-nonescape} prevents replacing the missing row by hidden synchronization, host equality, or a private observer witness, so the bypassed read is not the public classifier verdict.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier observer-state GAP route]
\label{thm:observer-perspective-classifier-observer-state-gap-route}
For an accepted $\ObserverPerspectiveClassifierUp$ carrier $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$, a public verdict may consume the paired $\mathsf{GAP}$ row $G$ only after the two conscious-observer state rows $O_0,O_1$ have exposed their GAP acknowledgement rows through the recorded state surface. A verdict that reads $G$ without both acknowledgements is not an accepted observer-perspective classifier verdict.
\end{theorem}
\begin{proof}
Project the carrier tuple from \autoref{def:observer-perspective-classifier-carrier}. The observer rows $O_0,O_1$ precede the universe surfaces, locality row, and paired commitment row, so the public carrier fixes the state coordinates before the comparison row $G$ can be read.

The state-totality theorem \autoref{thm:observer-perspective-classifier-state-totality} forces both conscious-observer state rows to be exposed before any public classifier verdict. The paired commitment readback theorem \autoref{thm:observer-perspective-classifier-gap-commitment-readback} then routes the displayed $\mathsf{GAP}$ row through the same finite comparison ledger.

Finally apply the ConsciousObserverState exactness anchor $\mathsf{ConsciousObserverStateCarrier\_gap\_acknowledgement\_exactness}$ to the two state rows. It identifies the required acknowledgement rows as the exact state-side witnesses consumed by $G$. The ledger exactness and non-escape theorems \autoref{thm:observer-perspective-classifier-ledger-exactness} and \autoref{thm:observer-perspective-classifier-nonescape} rule out replacing either acknowledgement by host equality, hidden synchronization, or private observer access.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier cross-alignment locality soundness]
\label{thm:observer-perspective-classifier-cross-alignment-locality-soundness}
A $\CrossPerspectiveAlignmentUp$ consumer may use an accepted $\ObserverPerspectiveClassifierUp$ verdict only when the displayed locality row $L$ and paired $\mathsf{GAP}$ row $G$ pass through the alignment locality-cell soundness route. If the consumer supplies a different locality cell, an unpaired commitment row, or an unrecorded alignment witness, it is not using the public classifier surface.
\end{theorem}
\begin{proof}
Start with the comparison route of \autoref{thm:observer-perspective-classifier-comparison-route-totality}. It orders the public read through the two observer rows, two universe surfaces, displayed locality row $L$, paired commitment row $G$, transports $H$, continuations $C$, provenance $P$, and local naming row $N$.

The alignment-consumer theorem \autoref{thm:observer-perspective-classifier-alignment-consumer} restricts downstream cross-perspective consumers to precisely the displayed comparison rows. Thus the consumer cannot detach $L$ from $G$ or replace either row before reading the classifier verdict.

Apply \autoref{thm:observer-perspective-classifier-locality-cell-comparison} to compare the locality cell against the classifier ledger, and then apply the CrossPerspectiveAlignment soundness anchor $\mathsf{CrossPerspectiveAlignmentCarrier\_locality\_cell\_soundness}$. These two routes identify the accepted locality-cell soundness witness with the displayed pair $L,G$.

The non-escape theorem \autoref{thm:observer-perspective-classifier-nonescape} excludes hidden synchronization, ambient world equality, and unrecorded cross-perspective evidence. Hence a consumer outside the $L,G$ soundness route is outside the public classifier surface.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier locality-cell exhaustion]
\label{thm:observer-perspective-classifier-locality-cell-exhaustion}
In an accepted $\ObserverPerspectiveClassifierUp$ carrier $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$, the locality coordinate $L$ is exhausted by the public $\LocalityCellUp$ or $\ObserverLocalityCellUp$ packet together with the rows $H,C,P,N$. No ambient world row, hidden synchronization map, host equality, or unrecorded locality witness can replace that public locality-cell data.
\end{theorem}
\begin{proof}
Read the carrier as a finite ledger. The locality row $L$ is not an abstract parameter: it is tied to the componentwise $\hsame$ transports $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$.

The locality-cell comparison theorem \autoref{thm:observer-perspective-classifier-locality-cell-comparison} and ledger exactness theorem \autoref{thm:observer-perspective-classifier-ledger-exactness} say that every public read of $L$ factors through those displayed rows. Apply the LocalityCell readback anchor $\mathsf{LocalityCellPacket\_interobserver\_readback}$ when $L$ is supplied by a $\LocalityCellUp$ packet, and apply the ObserverLocalityCell boundary anchor $\mathsf{ObserverLocalityCellPacket\_consumer\_boundary}$ when $L$ is supplied by an $\ObserverLocalityCellUp$ packet.

It remains to rule out replacements. The dependency-scope theorem \autoref{thm:observer-perspective-classifier-dependency-scope} limits the accepted row family to the displayed public packets, and the non-escape theorem \autoref{thm:observer-perspective-classifier-nonescape} rejects ambient world rows, hidden synchronization maps, host equality, private observer access, and unrecorded cross-perspective evidence. Therefore $L$ is exhausted exactly by the public locality-cell packet and the rows $H,C,P,N$.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier locality-commitment inversion]
\label{thm:observer-perspective-classifier-locality-commitment-inversion}
Let $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$ be an accepted $\ObserverPerspectiveClassifierUp$ carrier read inside the public $\BHist$ packet. Any accepted public comparison verdict determines the displayed locality row $L$ and paired $\mathsf{GAP}$ commitment row $G$ through the finite rows $Q$, with $H$ the componentwise $\hsame$ transport row, $C$ the displayed $\Cont$ route row, $P$ the $\Pkg$ provenance row, and $N$ the local $\NameCert$ row. A verdict that omits either $L$ or $G$ is outside the public classifier.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:observer-perspective-classifier-carrier}. The public read has only the finite coordinates $O_0,O_1,U_0,U_1,L,G,H,C,P,N$, so the comparison verdict cannot choose an unlisted locality or commitment coordinate.

Apply \autoref{thm:observer-perspective-classifier-locality-cell-comparison}. It identifies the displayed $L$ row as the locality-cell comparison surface tied to the transport, continuation, provenance, and naming rows. Apply \autoref{thm:observer-perspective-classifier-gap-commitment-readback} to identify $G$ as the paired commitment ledger for the same public comparison route.

It remains to exclude partial verdicts. Ledger exactness \autoref{thm:observer-perspective-classifier-ledger-exactness} says the public classifier has no comparison route outside the displayed rows, and non-escape \autoref{thm:observer-perspective-classifier-nonescape} rejects ambient locality, hidden synchronization, host equality, private observer access, and unrecorded alignment evidence. Hence a verdict missing either $L$ or $G$ is not an accepted public classifier verdict.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier two-state no-confusion]
\label{thm:observer-perspective-classifier-two-state-no-confusion}
For accepted $\ObserverPerspectiveClassifierUp$ carrier reads $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$ and $Q'=(O'_0,O'_1,U'_0,U'_1,L',G',H',C',P',N')$, equality of the public classifier verdict forces agreement on both conscious-observer state rows and both universe-for-observer rows before locality and alignment rows are compared. If any one of $O_0,O_1,U_0,U_1$ differs from the corresponding displayed row in $Q'$, the two reads are different public carrier reads rather than the same classifier verdict.
\end{theorem}
\begin{proof}
Start with the carrier definition. It presents each accepted read as a finite ordered $\BHist$ packet, so the state and universe-for-observer rows are public coordinates of the verdict rather than hidden parameters.

Apply state totality \autoref{thm:observer-perspective-classifier-state-totality}. Both observer-state rows and both attached universe surfaces must be exposed before the verdict may continue to locality, commitment, transport, continuation, provenance, and naming rows.

Next apply comparison-route totality \autoref{thm:observer-perspective-classifier-comparison-route-totality} and perspective stability \autoref{thm:observer-perspective-classifier-perspective-stability}. These identify the downstream comparison route only after the displayed state and universe rows have been fixed.

Finally use non-escape \autoref{thm:observer-perspective-classifier-nonescape}. It forbids repairing a disagreement in $O_0,O_1,U_0,U_1$ by host equality, private observer access, hidden synchronization, or an unrecorded cross-perspective witness. Therefore such a disagreement changes the public carrier read itself.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier alignment ledger coverage]
\label{thm:observer-perspective-classifier-alignment-ledger-coverage}
Every $\CrossPerspectiveAlignmentUp$ consumer of an accepted $\ObserverPerspectiveClassifierUp$ verdict is covered by the displayed ledger $L,G,H,C,P,N$. The locality row $L$ is supplied either by a public $\LocalityCellUp$ packet or by a public $\ObserverLocalityCellUp$ packet, and there is no third ambient locality, hidden synchronization route, or unrecorded alignment channel available to the consumer.
\end{theorem}
\begin{proof}
Begin with dependency scope \autoref{thm:observer-perspective-classifier-dependency-scope}. It confines the accepted classifier to the displayed observer-state, universe-for-observer, locality, alignment, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Apply the alignment-consumer theorem \autoref{thm:observer-perspective-classifier-alignment-consumer}. A downstream $\CrossPerspectiveAlignmentUp$ consumer must read the verdict through $L,G,H,C,P,N$ rather than through an independent alignment surface.

The cross-alignment locality soundness theorem \autoref{thm:observer-perspective-classifier-cross-alignment-locality-soundness} binds the consumer to the same displayed $L,G$ pair. Locality-cell exhaustion \autoref{thm:observer-perspective-classifier-locality-cell-exhaustion} restricts $L$ to the public $\LocalityCellUp$ or $\ObserverLocalityCellUp$ packet, and locality-commitment inversion \autoref{thm:observer-perspective-classifier-locality-commitment-inversion} keeps $L$ and $G$ jointly determined by the accepted carrier.

Thus every alignment consumer is covered by the displayed ledger. Any purported consumer using a third locality surface, hidden synchronization, or unrecorded alignment witness leaves the public classifier route.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier two-observer source admission]
\label{thm:observer-perspective-classifier-two-observer-source-admission}
An accepted public verdict for an $\ObserverPerspectiveClassifierUp$ carrier must first expose both accepted $\ConsciousObserverStateUp$ rows $O_0,O_1$ and their attached universe-for-observer surfaces $U_0,U_1$. The verdict may then read locality and alignment data, but it cannot read $L$, $G$, or a $\CrossPerspectiveAlignmentUp$ consumer route before the two observer-state rows and the two universe surfaces have appeared in the finite carrier.
\end{theorem}
\begin{proof}
Project the carrier $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$ from \autoref{def:observer-perspective-classifier-carrier}. The first displayed rows are the two observer-state sources and their two universe-for-observer surfaces, so the classifier has no earlier public comparison coordinate.

Apply the state-totality theorem \autoref{thm:observer-perspective-classifier-state-totality}. It turns this projection order into a public verdict condition: both observer-state rows and both attached universe surfaces must be exposed before the verdict is exported.

Finally apply the comparison-route totality and non-escape theorems, \autoref{thm:observer-perspective-classifier-comparison-route-totality} and \autoref{thm:observer-perspective-classifier-nonescape}. They force the later locality, commitment, transport, continuation, provenance, and alignment-facing reads to remain downstream of the displayed state rows, and they rule out a hidden observer-neutral source that could bypass the two source rows.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier alignment-locality cycle]
\label{thm:observer-perspective-classifier-alignment-locality-cycle}
For an accepted $\ObserverPerspectiveClassifierUp$ carrier, the locality coordinate $L$ must be a public $\LocalityCellUp$ or $\ObserverLocalityCellUp$ packet paired with the same displayed $\mathsf{GAP}$ row $G$. Every $\CrossPerspectiveAlignmentUp$ consumer of the verdict must consume that $L,G$ pair through the recorded rows $H,C,P,N$; it cannot bypass the pair by supplying an ambient locality row, an unpaired commitment row, or an unrecorded alignment witness.
\end{theorem}
\begin{proof}
Read $L$ from the carrier definition. Its declared role is the public locality-cell evidence row, and the next comparison coordinate $G$ is the paired $\mathsf{GAP}$ commitment ledger for comparing $U_0$ and $U_1$ without identifying them as one host world.

Apply locality-cell exhaustion \autoref{thm:observer-perspective-classifier-locality-cell-exhaustion}. It restricts $L$ to the public $\LocalityCellUp$ or $\ObserverLocalityCellUp$ packet together with the recorded transport, route, provenance, and naming rows.

Next apply cross-alignment locality soundness \autoref{thm:observer-perspective-classifier-cross-alignment-locality-soundness}. That theorem binds the alignment-facing consumer to the same displayed pair $L,G$.

The ledger exactness and non-escape boundary, \autoref{thm:observer-perspective-classifier-ledger-exactness} and \autoref{thm:observer-perspective-classifier-nonescape}, then exclude ambient locality rows, unpaired commitment rows, hidden synchronization, and unrecorded alignment witnesses. Thus the locality and alignment reads form the stated cycle around the public $L,G$ pair.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier obligation-closure witness]
\label{thm:observer-perspective-classifier-obligation-closure-witness}
The carrier row, the five local $\NameCert_{\ObserverPerspectiveClassifierUp}$ obligation rows, the two observer-state source rows, the locality-cell row, the paired $\mathsf{GAP}$ row, the $\CrossPerspectiveAlignmentUp$ consumer route, the componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and the local naming row form one finite obligation-closure witness for $\ObserverPerspectiveClassifierUp$.
\end{theorem}
\begin{proof}
Begin with the carrier and local obligation theorems, \autoref{def:observer-perspective-classifier-carrier} and \autoref{thm:observer-perspective-classifier-namecert-obligations}. They display the finite packet and identify the five local naming obligations carried by it.

The source admission theorem \autoref{thm:observer-perspective-classifier-two-observer-source-admission} binds both conscious-observer state rows and both universe-for-observer surfaces before any public verdict. The alignment-locality cycle theorem \autoref{thm:observer-perspective-classifier-alignment-locality-cycle} binds the public locality row, paired commitment row, and alignment-facing consumer to the same displayed route.

It remains to gather the already established public boundaries. Apply ledger exactness, non-escape, comparison-route totality, dependency scope, observer-state GAP route, cross-alignment locality soundness, and locality-cell exhaustion. These theorems account for $H,C,P,N$, exclude every unlisted observer-neutral or ambient replacement, and leave exactly the finite row family named in the statement.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier obligation unblock package]
\label{thm:observer-perspective-classifier-obligation-unblock-package}
The carrier exposure, local $\NameCert$ obligations, locality-cell comparison, ledger exactness, non-escape boundary, paired $\mathsf{GAP}$ readback, comparison-route totality, state totality, locality refinement, perspective stability, dependency scope, alignment-consumer discipline, observer-state GAP route, cross-alignment locality soundness, locality-cell exhaustion, two-observer source admission, alignment-locality cycle, and obligation-closure witness together form the finite $\ObserverPerspectiveClassifierUp$ obligation package for obligation-level closure.
\end{theorem}
\begin{proof}
First project the finite carrier from \autoref{def:observer-perspective-classifier-carrier}. This supplies the rows $O_0,O_1,U_0,U_1,L,G,H,C,P,N$ and fixes the only coordinates available to the package.

The local obligation surface is given by \autoref{thm:observer-perspective-classifier-namecert-obligations}. The comparison surface is then constrained by \autoref{thm:observer-perspective-classifier-locality-cell-comparison}, \autoref{thm:observer-perspective-classifier-ledger-exactness}, \autoref{thm:observer-perspective-classifier-nonescape}, and \autoref{thm:observer-perspective-classifier-gap-commitment-readback}.

The route and state coverage are supplied by \autoref{thm:observer-perspective-classifier-comparison-route-totality} and \autoref{thm:observer-perspective-classifier-state-totality}. Stability under admissible local changes is supplied by \autoref{thm:observer-perspective-classifier-locality-refinement} and \autoref{thm:observer-perspective-classifier-perspective-stability}.

It remains only to bind the consumer-facing dependency boundary. Apply \autoref{thm:observer-perspective-classifier-dependency-scope} to identify the accepted row family, and apply \autoref{thm:observer-perspective-classifier-alignment-consumer} to force downstream consumers through the displayed locality, commitment, transport, continuation, provenance, and naming rows.

The three concrete rows above close the exposed obligation route. The observer-state GAP route \autoref{thm:observer-perspective-classifier-observer-state-gap-route} ties $G$ to both state acknowledgements, the cross-alignment locality soundness route \autoref{thm:observer-perspective-classifier-cross-alignment-locality-soundness} ties $L,G$ to the alignment consumer, and locality-cell exhaustion \autoref{thm:observer-perspective-classifier-locality-cell-exhaustion} rules out ambient or hidden replacements for $L$. These finite components assemble exactly the obligation package claimed.

The dependency witness is explicit in the same finite packet. Apply \autoref{thm:observer-perspective-classifier-two-observer-source-admission} for the two source-state rows, \autoref{thm:observer-perspective-classifier-alignment-locality-cycle} for the $L,G$ locality and alignment cycle, and \autoref{thm:observer-perspective-classifier-obligation-closure-witness} to package these rows with the earlier carrier, obligation, exactness, and non-escape boundaries.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier BHist scope]
\label{thm:observer-perspective-classifier-bhist-scope}
Every accepted carrier read for $\ObserverPerspectiveClassifierUp$ is confined to the displayed finite $\BHist$ packet $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$. No observer-neutral row, host-world equality row, private $\mathsf{Self}$ row, global spacetime row, hidden synchronization row, or unrecorded cross-perspective row can enter the classifier scope.
\end{theorem}
\begin{proof}
Start with the carrier definition \autoref{def:observer-perspective-classifier-carrier}. It presents the accepted classifier as the finite $\BHist$ packet $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$, so every public read has one of these displayed coordinates as its source.

Ledger exactness \autoref{thm:observer-perspective-classifier-ledger-exactness} identifies the rows available inside that packet. The non-escape theorem \autoref{thm:observer-perspective-classifier-nonescape} excludes observer-neutral rows, host-world equality, private $\mathsf{Self}$ access, global spacetime carriers, hidden synchronization maps, and unrecorded cross-perspective evidence.

Finally apply dependency scope \autoref{thm:observer-perspective-classifier-dependency-scope}. It says the accepted row family is exactly the public family generated by the displayed observer-state, locality, alignment, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Hence no row outside $Q$ can enter the scope.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier alignment transport scope]
\label{thm:observer-perspective-classifier-alignment-transport-scope}
Every $\CrossPerspectiveAlignmentUp$ consumer of an accepted $\ObserverPerspectiveClassifierUp$ verdict may use only the displayed route through $L,G,H,C,P,N$. Its transport scope is the componentwise $\hsame$ row $H$ together with the displayed $\Cont$ routes $C$; it cannot import an ambient alignment map, an unpaired commitment row, or an unrecorded continuation.
\end{theorem}
\begin{proof}
The comparison-route totality theorem \autoref{thm:observer-perspective-classifier-comparison-route-totality} first exposes the available route: observer rows, universe-for-observer surfaces, locality evidence, paired $\mathsf{GAP}$ commitments, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local naming.

Next use the alignment-consumer theorem \autoref{thm:observer-perspective-classifier-alignment-consumer}. It forces any downstream consumer to read the verdict through $L,G,H,C,P,N$ rather than through a separate alignment channel.

The cross-alignment locality soundness theorem \autoref{thm:observer-perspective-classifier-cross-alignment-locality-soundness} binds the consumer to the same displayed $L,G$ pair. The alignment-locality cycle theorem \autoref{thm:observer-perspective-classifier-alignment-locality-cycle} then returns the read to $H,C,P,N$, with $\hsame$ and $\Cont$ supplying the transport scope. Thus ambient alignment maps, unpaired commitments, and unrecorded continuations are outside the accepted consumer scope.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier NameCert ledger scope]
\label{thm:observer-perspective-classifier-namecert-ledger-scope}
The local $\NameCert_{\ObserverPerspectiveClassifierUp}$ row closes only the finite observer-state, locality-cell, $\mathsf{GAP}$, transport, continuation, package, and naming ledger displayed by $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$. It does not close global spacetime, private $\mathsf{Self}$ access, host equality between worlds, hidden synchronization, or unrecorded cross-perspective evidence.
\end{theorem}
\begin{proof}
The local naming obligations are exactly the five rows listed in \autoref{thm:observer-perspective-classifier-namecert-obligations}. They cover carrier exposure, observer anchoring, universe-for-observer exposure, locality and coherence comparison, and the non-escape boundary.

Apply the obligation-closure witness \autoref{thm:observer-perspective-classifier-obligation-closure-witness}. It packages the carrier row, the local naming obligations, both observer-state rows, the locality-cell row, the paired $\mathsf{GAP}$ row, the alignment consumer route, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and the local naming row as one finite obligation witness.

The obligation unblock package \autoref{thm:observer-perspective-classifier-obligation-unblock-package} assembles the same rows as the chapter's obligation surface. The non-escape theorem \autoref{thm:observer-perspective-classifier-nonescape} keeps global spacetime, private $\mathsf{Self}$ access, host equality, hidden synchronization, and unrecorded cross-perspective evidence outside that surface. Therefore the $\NameCert$ row closes only the displayed finite ledger.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier carrier transport]
\label{thm:observerperspectiveclassifier-carrier-transport}
For an accepted $\ObserverPerspectiveClassifierUp$ carrier $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$, carrier transport preserves acceptedness exactly when the rows $O_0,O_1,U_0,U_1,L,G,H,C,P,N$ are transported componentwise through the displayed $\hsame$ rows in $H$ and then replayed through the displayed $\Cont$ routes in $C$. No transport that omits an observer-state row, a universe-for-observer row, the locality row, the paired $\mathsf{GAP}$ row, package provenance, or the local naming row is an accepted carrier transport.
\end{theorem}
\begin{proof}
Start from the finite carrier definition \autoref{def:observer-perspective-classifier-carrier}. It presents $Q$ as a $\BHist$ packet with exactly the displayed observer-state, universe-for-observer, locality, commitment, transport, continuation, package, and naming rows.

The forward direction uses the transport data already present in the accepted packet. Locality refinement \autoref{thm:observer-perspective-classifier-locality-refinement} and perspective stability \autoref{thm:observer-perspective-classifier-perspective-stability} keep the comparison attached to the same public locality and observer-perspective rows. The $\BHist$ scope theorem \autoref{thm:observer-perspective-classifier-bhist-scope} confines the read to $Q$, and the alignment transport scope theorem \autoref{thm:observer-perspective-classifier-alignment-transport-scope} forces the consumer route through the displayed $H$ and $C$ rows.

For the reverse direction, suppose every listed coordinate is transported through its displayed $\hsame$ row and replayed through its displayed $\Cont$ route. The same carrier rows are then available in the same finite order, with the package and local naming rows transported along with the data rows. Ledger exactness \autoref{thm:observer-perspective-classifier-ledger-exactness} and NameCert ledger scope \autoref{thm:observer-perspective-classifier-namecert-ledger-scope} therefore reconstruct the accepted carrier surface and exclude any transport using an omitted or hidden coordinate.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier classifier determinacy]
\label{thm:observerperspectiveclassifier-classifier-determinacy}
Let $Q$ and $Q'$ be accepted public $\ObserverPerspectiveClassifierUp$ carriers with public verdicts read through their local $\NameCert$ rows. The two verdicts are the same classifier verdict exactly when they agree on both observer-state rows, both universe-for-observer surfaces, the locality row, the paired $\mathsf{GAP}$ row, the componentwise $\hsame$ transports, the displayed $\Cont$ routes, the $\Pkg$ provenance, and the local $\NameCert$ row.
\end{theorem}
\begin{proof}
First compare the observer-state coordinates. The two-state no-confusion theorem \autoref{thm:observer-perspective-classifier-two-state-no-confusion} says that the accepted classifier keeps $O_0$ and $O_1$ as the two displayed state rows, so a public verdict cannot identify distinct state rows by passing to an ambient observer.

Next compare the locality and commitment coordinates. Locality-commitment inversion \autoref{thm:observer-perspective-classifier-locality-commitment-inversion} recovers the displayed locality row and paired $\mathsf{GAP}$ row from an accepted comparison verdict. Alignment-ledger coverage \autoref{thm:observer-perspective-classifier-alignment-ledger-coverage} then accounts for the alignment-facing route through the same finite ledger.

It remains to compare the structural coordinates. Ledger exactness \autoref{thm:observer-perspective-classifier-ledger-exactness} makes $H,C,P,N$ the only public transport, continuation, provenance, and naming rows available to the verdict. Non-escape \autoref{thm:observer-perspective-classifier-nonescape} excludes a private observer row, host equality, global spacetime carrier, hidden synchronization map, or unrecorded comparison witness that could distinguish two otherwise equal displayed verdicts.

Thus equality of all displayed rows determines equality of the classifier verdict. Conversely, equality of classifier verdicts forces equality of those rows by applying the same no-confusion, inversion, ledger-coverage, exactness, and non-escape boundaries to the public readback of the verdicts.
\end{proof}

\begin{theorem}[ObserverPerspectiveClassifier ledger exhaustion]
\label{thm:observerperspectiveclassifier-ledger-exhaustion}
Every accepted downstream consumer route for an $\ObserverPerspectiveClassifierUp$ verdict is exhausted by the displayed ledger $Q=(O_0,O_1,U_0,U_1,L,G,H,C,P,N)$. Such a route cannot add a god's-eye observer, host world equality, private $\mathsf{Self}$ row, global spacetime carrier, hidden synchronization map, or unrecorded cross-perspective evidence.
\end{theorem}
\begin{proof}
Project the accepted carrier and its public read route. Ledger exactness \autoref{thm:observer-perspective-classifier-ledger-exactness} supplies the complete row family $O_0,O_1,U_0,U_1,L,G,H,C,P,N$, and comparison-route totality \autoref{thm:observer-perspective-classifier-comparison-route-totality} sends every consumer through that displayed route.

The obligation unblock package \autoref{thm:observer-perspective-classifier-obligation-unblock-package} gathers the carrier exposure, local obligations, locality comparison, paired commitment readback, route coverage, state coverage, stability, and alignment-facing consumer discipline into the same finite package. Dependency scope \autoref{thm:observer-perspective-classifier-dependency-scope} then prevents a downstream consumer from importing rows outside the accepted public dependency family.

Finally apply NameCert ledger scope \autoref{thm:observer-perspective-classifier-namecert-ledger-scope}. The local naming row closes only the displayed observer-state, universe-for-observer, locality-cell, $\mathsf{GAP}$, transport, continuation, package, and naming ledger. The excluded god's-eye observer, host world equality, private $\mathsf{Self}$ row, global spacetime carrier, hidden synchronization map, and unrecorded cross-perspective evidence have no displayed coordinate and no accepted consumer route.
\end{proof}

\closureat{ObserverPerspectiveClassifierUp}{obligationStr}

\begin{closurestatus}{\ObserverPerspectiveClassifierUp}
  \constructivestory{An $\ObserverPerspectiveClassifierUp$ packet is generated from two conscious-observer state rows, two universe-for-observer record surfaces, locality-cell evidence, paired GAP commitments, componentwise transports, displayed continuation routes, package provenance, and a local naming row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:observer-perspective-classifier-carrier}, \autoref{thm:observer-perspective-classifier-namecert-obligations}, \autoref{thm:observer-perspective-classifier-locality-cell-comparison}, \autoref{thm:observer-perspective-classifier-ledger-exactness}, \autoref{thm:observer-perspective-classifier-nonescape}, \autoref{thm:observer-perspective-classifier-anchor-change-stability}, \autoref{thm:observer-perspective-classifier-gap-commitment-readback}, \autoref{thm:observer-perspective-classifier-comparison-route-totality}, \autoref{thm:observer-perspective-classifier-state-totality}, \autoref{thm:observer-perspective-classifier-locality-refinement}, \autoref{thm:observer-perspective-classifier-perspective-stability}, \autoref{thm:observer-perspective-classifier-observer-state-gap-route}, \autoref{thm:observer-perspective-classifier-cross-alignment-locality-soundness}, \autoref{thm:observer-perspective-classifier-locality-cell-exhaustion}, \autoref{thm:observer-perspective-classifier-locality-commitment-inversion}, \autoref{thm:observer-perspective-classifier-two-state-no-confusion}, \autoref{thm:observer-perspective-classifier-alignment-ledger-coverage}, \autoref{thm:observer-perspective-classifier-two-observer-source-admission}, \autoref{thm:observer-perspective-classifier-alignment-locality-cycle}, \autoref{thm:observer-perspective-classifier-obligation-closure-witness}, \autoref{thm:observer-perspective-classifier-bhist-scope}, \autoref{thm:observer-perspective-classifier-alignment-transport-scope}, \autoref{thm:observer-perspective-classifier-namecert-ledger-scope}, \autoref{thm:observerperspectiveclassifier-carrier-transport}, \autoref{thm:observerperspectiveclassifier-classifier-determinacy}, and \autoref{thm:observerperspectiveclassifier-ledger-exhaustion} bind the finite public classifier obligation surface for universe-for-observer comparison.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean verification, bridge status, god's-eye observation, host equality between worlds, private Self access, global spacetime, hidden synchronization, or unrecorded cross-perspective evidence.}
  \upgradepath{Scoped closure next requires Lean-side and formal scope witnesses for the same finite observer-state, locality-cell, paired GAP, and alignment-consumer packet.}
\end{closurestatus}
