\chapter{A Concrete Naming Certificate for $\MultiHistSuperpositionUp$}
\label{ch:concrete-instances-multihistsuperposition-namecert}
\origin{ai}

The $\MultiHistSuperpositionUp$ interface records the finite packet in which the inter-Hist locality chain reads quantum-state style content through displayed $\Eone$ and $\Ezero$ refinement rows rather than through metric geometry. It consumes the already named multi-Hist configuration, cross-Hist causal witnesses, and maximum-rate bound rows, then adds a phase-coherence ledger and local NameCert surface over the same finite histories.

\begin{definition}[MultiHistSuperposition carrier]
\label{def:multi-hist-superposition-carrier}
A $\MultiHistSuperpositionUp$ carrier is a finite $\BHist$ packet
$$
S=(M,E,Z,X,R,\Phi,H,Q,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $M$ is an accepted $\MultiHistConfigUp$ row displaying the finite family of observer-history rows, local ledgers, no-global-sync boundary, componentwise $\hsame$ transports, visible $\Cont$ routes, $\Pkg$ provenance, and local naming row;
\item $E$ is the finite $\Eone$ refinement family over the displayed histories of $M$, recording observation-sensitive rows only where the packet has a visible continuation route;
\item $Z$ is the finite $\Ezero$ refinement family over the same histories, recording name-sensitive rows only where the local naming ledger displays them;
\item $X$ is the finite family of $\CrossHistCausalUp$ witness rows over selected pairs of histories from $M$ and selected refinement slots from $E$ and $Z$;
\item $R$ is the accepted $\MaxCausalRateUp$ bound row for the displayed causal witness family $X$ over the same configuration row $M$;
\item $\Phi$ is the phase-coherence ledger, a finite row comparing the selected $\Eone$ and $\Ezero$ refinements along the displayed cross-Hist witnesses without quotienting histories or selecting a global phase;
\item $H$ records componentwise $\hsame$ transport for $M,E,Z,X,R,\Phi$, the probe-stability row, continuation routes, package row, and local naming row;
\item $Q$ records $\psame$ stability for the displayed probe reads used by the refinement rows and their phase-coherence ledger;
\item $C$ records the visible $\Cont$ routes from the configuration, refinement, causal, rate, and phase rows into the local certificate;
\item $P$ is the $\Pkg$ provenance over $\MultiHistSuperpositionUp$, $\MultiHistConfigUp$, $\CrossHistCausalUp$, $\MaxCausalRateUp$, $\BHist$, $\Eone$, $\Ezero$, $\hsame$, $\psame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\MultiHistSuperpositionUp}$ row.
\end{enumerate}
The carrier exports only finite observer-history rows, displayed refinement ledgers, selected cross-Hist causal witnesses, the inherited maximum-rate bound, phase-coherence rows, transport rows, continuation routes, provenance, and local naming data. It contains no Hilbert space, amplitude field, global phase, completed state vector, quotient of histories, or ambient probabilistic measure.
\end{definition}

\begin{theorem}[MultiHistSuperposition NameCert obligations]
\label{thm:multi-hist-superposition-namecert-obligations}
For the carrier of \autoref{def:multi-hist-superposition-carrier}, the local $\NameCert_{\MultiHistSuperpositionUp}$ surface consists exactly of carrier admission for $S=(M,E,Z,X,R,\Phi,H,Q,C,P,N)$, refinement locality for the displayed $\Eone$ and $\Ezero$ rows over $M$, cross-Hist causal inheritance through $X$, maximum-rate inheritance through $R$, phase-coherence exactness through $\Phi$, componentwise $\hsame$ and displayed $\psame$ stability through $H,Q$, visible $\Cont$ locality through $C$, $\Pkg$ provenance through $P$, local naming through $N$, and non-escape from global phases, completed state vectors, Hilbert spaces, quotient histories, and ambient probability measures.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:multi-hist-superposition-carrier}. The displayed packet supplies every row named by the local certificate.

Refinement locality reads $M$ before $E$ and $Z$. Each refinement row is attached to a displayed history and a visible continuation or naming route, so the refinement cannot introduce an unlisted observer history.

The causal and bound obligations are inherited in order. The witness family $X$ consumes selected histories and refinement slots from $M,E,Z$, while $R$ supplies only the finite maximum-rate row for that same witness family.

Phase-coherence exactness is the ledger condition on $\Phi$. It compares selected refinement rows along displayed witnesses, not representatives in a quotient of histories or amplitudes in a host state space.

Finally route all reads through $H,Q,C,P,N$. Since the carrier has no coordinate for global phase, Hilbert space, completed vector state, quotient history, or ambient measure, the non-escape clause is the displayed inventory boundary.
\end{proof}

\begin{theorem}[MultiHistSuperposition phase coherence]
\label{thm:multi-hist-superposition-phase-coherence}
For an accepted $\MultiHistSuperpositionUp$ carrier
$$
S=(M,E,Z,X,R,\Phi,H,Q,C,P,N),
$$
the phase-coherence ledger $\Phi$ is read only as a finite comparison of displayed $\Eone$ and $\Ezero$ refinement rows along the selected cross-Hist witness family $X$. Componentwise $\hsame$ transport in $H$, displayed $\psame$ stability in $Q$, and visible routes in $C$ preserve the same finite phase ledger; they do not identify histories by quotient, choose a global phase, or complete the packet into a host quantum state.
\end{theorem}
\begin{proof}
Project the accepted carrier and read $E,Z,X,\Phi$. The refinement families and witness family are finite rows over the displayed multi-Hist configuration.

Transport through $H$ preserves the histories, refinement rows, witness family, inherited rate row, and phase ledger componentwise. The probe row $Q$ preserves the probe reads used by the same refinement comparisons.

The continuation routes in $C$ keep every phase read on the displayed path from $M$ to $E,Z,X,R,\Phi$. Therefore the transported phase-coherence row remains the same finite BEDC ledger and cannot become a quotient, selected global phase, or completed state vector.
\end{proof}

\begin{theorem}[MultiHistSuperposition non-escape]
\label{thm:multi-hist-superposition-nonescape}
Every consumer of an accepted $\MultiHistSuperpositionUp$ carrier factors through the finite rows
$$
M,E,Z,X,R,\Phi,H,Q,C,P,N.
$$
In particular, the consumer may read the multi-Hist configuration row, $\Eone$ refinement rows, $\Ezero$ refinement rows, selected cross-Hist causal witnesses, maximum-rate bound row, phase-coherence ledger, componentwise $\hsame$ transports, displayed $\psame$ stability, visible $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\MultiHistSuperpositionUp}$ row, and nothing outside those rows.
\end{theorem}
\begin{proof}
Start with the carrier inventory. The listed coordinates are the only public rows of \autoref{def:multi-hist-superposition-carrier}.

Use the inherited non-escape boundaries of $\MultiHistConfigUp$, $\CrossHistCausalUp$, and $\MaxCausalRateUp$. They exclude global synchronization, unlisted causal witnesses, metric geometry, and ambient real-valued rate data from the upstream rows.

The refinement and phase rows add only $E,Z,\Phi$. By \autoref{thm:multi-hist-superposition-phase-coherence}, these rows are finite ledgers transported through $H,Q,C$ and do not export Hilbert spaces, amplitude fields, global phases, completed state vectors, quotient histories, or ambient probability measures.

Thus every consumer route is exhausted by $M,E,Z,X,R,\Phi,H,Q,C,P,N$.
\end{proof}

\begin{theorem}[MultiHistSuperposition obligation surface]
\label{thm:multi-hist-superposition-obligation-surface}
The $\MultiHistSuperpositionUp$ obligation surface is the finite package assembled from \autoref{def:multi-hist-superposition-carrier}, \autoref{thm:multi-hist-superposition-namecert-obligations}, \autoref{thm:multi-hist-superposition-phase-coherence}, and \autoref{thm:multi-hist-superposition-nonescape}. It is the concrete realization of the $\Eone$/$\Ezero$ refinement step of the inter-Hist locality chain: a local $\NameCert$ over finite $\BHist$, $\hsame$, $\psame$, $\Cont$, $\Pkg$, and refinement rows, not a host quantum-state construction.
\end{theorem}
\begin{proof}
The carrier definition supplies the finite packet rows and their dependency order. The NameCert obligation theorem binds those rows to carrier admission, refinement locality, causal and rate inheritance, phase exactness, transport stability, provenance, naming, and non-escape.

The phase-coherence theorem isolates the only quantum-state style row as the finite ledger $\Phi$ over displayed $\Eone$ and $\Ezero$ refinements. The non-escape theorem then exhausts every consumer route by the same packet.

Repack these rows under the local $\NameCert_{\MultiHistSuperpositionUp}$ entry. Since each component is one of $M,E,Z,X,R,\Phi,H,Q,C,P,N$, the obligation surface stays within the finite BEDC kernel rows named in the statement.
\end{proof}

\closureat{MultiHistSuperpositionUp}{seedStr}

\begin{closurestatus}{\MultiHistSuperpositionUp}
  \constructivestory{A $\MultiHistSuperpositionUp$ packet is generated from a $\MultiHistConfigUp$ row, finite $\Eone$ and $\Ezero$ refinement rows, selected $\CrossHistCausalUp$ witnesses, an inherited $\MaxCausalRateUp$ bound row, a phase-coherence ledger, componentwise $\hsame$ and displayed $\psame$ stability, visible $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite multi-Hist superposition packet over displayed BHist, refinement, causal, rate, phase-coherence, hsame, psame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Hilbert spaces, amplitudes, global phases, probability measures, completed quantum states, quotient histories, Lorentz geometry, curved spacetime, or Lean-side verification.}
  \upgradepath{Obligation closure requires carrier admission, refinement locality, causal and rate inheritance, phase-coherence exactness, transport stability, provenance, and non-escape obligations for the displayed finite packet.}
\end{closurestatus}
