\chapter{A Concrete Naming Certificate for $\RegularCauchySwapBisimulationUp$}
\label{ch:concrete-instances-regularcauchyswapbisimulation-namecert}
\origin{ai}

The $\RegularCauchySwapBisimulationUp$ packet names the finite symmetry surface between an alternating regular-Cauchy interleaving and the same interleaving read with the two source sides exchanged. It is a Real-and-Completion certificate over displayed $\RegSeqRatUp$, $\StreamNameUp$, $\RegularCauchyInterleavingUp$, and $\RealUp$ rows; it is not an equality of quotient reals, a host-level limit comparison, or an appeal to ambient completeness.

\begin{definition}[Regular Cauchy swap bisimulation carrier]
\label{def:regular-cauchy-swap-bisimulation-carrier}
A $\RegularCauchySwapBisimulationUp$ carrier is a finite $\BHist$ packet
$$
W=(A,B,S_A,S_B,\sigma,\sigma^{\mathrm{op}},M,E,E',H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two $\RegSeqRatUp$ source names whose finite rational observations may be interleaved;
\item $S_A$ and $S_B$ are the two $\StreamNameUp$ schedules that expose the selected finite windows for $A$ and $B$;
\item $\sigma$ is the alternating selector row that reads $A$ on its even side and $B$ on its odd side;
\item $\sigma^{\mathrm{op}}$ is the opposite selector row that reads the same schedules after exchanging the two source sides;
\item $M$ is the combined modulus ledger shared by the two selector presentations;
\item $E$ is the $\RealUp$ seal row reached through the $A,B,\sigma$ interleaving route;
\item $E'$ is the $\RealUp$ seal row reached through the $B,A,\sigma^{\mathrm{op}}$ interleaving route;
\item $H$ stores componentwise $\hsame$ transports for $A,B,S_A,S_B,\sigma,\sigma^{\mathrm{op}},M,E,E'$ and for the local packet shape;
\item $C$ stores the displayed $\Cont$ routes from each selector read through the selected schedule, the matching component of $M$, the corresponding $\RegularCauchyInterleavingUp$ row, and the real-facing seal boundary;
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\RegularCauchyInterleavingUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RegularCauchySwapBisimulationUp}$ row.
\end{enumerate}
The carrier contains no quotient-real equality row, no selected host limit, no ambient completeness coordinate, and no third schedule.
\end{definition}
\leandef{BEDC.Derived.RegularCauchySwapBisimulationUp.RegularCauchySwapBisimulationUp}

\begin{theorem}[Regular Cauchy swap bisimulation NameCert obligations]
\label{thm:regular-cauchy-swap-bisimulation-namecert-obligations}
The local $\NameCert_{\RegularCauchySwapBisimulationUp}$ surface for \autoref{def:regular-cauchy-swap-bisimulation-carrier} consists of six finite obligation rows:
\begin{enumerate}
\item carrier admission for the packet $W=(A,B,S_A,S_B,\sigma,\sigma^{\mathrm{op}},M,E,E',H,C,P,N)$;
\item forward interleaving admission through $A,B,S_A,S_B,\sigma,M,E$;
\item opposite interleaving admission through $B,A,S_B,S_A,\sigma^{\mathrm{op}},M,E'$;
\item selector-symmetry exactness stating that the opposite selector exchanges the same two schedule windows and the same two ledger components;
\item componentwise stability under the displayed $\hsame$ transports and replay through the displayed $\Cont$ routes;
\item real-seal non-escape stating that both real-facing rows are consumed only after the selected source name, selected schedule, shared ledger, interleaving row, package provenance, and local naming row have been displayed.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed tuple in \autoref{def:regular-cauchy-swap-bisimulation-carrier}. The packet lists exactly the two source names, two schedules, two selector rows, common ledger, two seal rows, transports, continuations, provenance, and local name.

The forward admission row is the ordinary $\RegularCauchyInterleavingUp$ route through $A,B,S_A,S_B,\sigma,M,E$. The opposite admission row uses the same data after exchanging the source and schedule coordinates and reading $\sigma^{\mathrm{op}}$.

Selector-symmetry exactness and stability are then local rows of the same packet. The $\hsame$ transports preserve each displayed coordinate componentwise, and the $\Cont$ routes replay only the chosen schedule and matching ledger component.

Finally, $P$ and $N$ repack those rows as the local certificate surface. Since the carrier has no coordinate for quotient real equality, selected host limits, ambient completeness, or a third schedule, the six rows exhaust the available certificate.
\end{proof}

\begin{theorem}[Regular Cauchy swap bisimulation selector symmetry]
\label{thm:regular-cauchy-swap-bisimulation-selector-symmetry}
For an accepted $\RegularCauchySwapBisimulationUp$ carrier $W$, every even read of $\sigma$ through $A,S_A$ and the first component of $M$ is matched by an odd read of $\sigma^{\mathrm{op}}$ through the same $A,S_A$ route and the same ledger component. Every odd read of $\sigma$ through $B,S_B$ and the second component of $M$ is matched by an even read of $\sigma^{\mathrm{op}}$ through the same $B,S_B$ route and the same ledger component. The matching is preserved by the displayed $\hsame$ transports and $\Cont$ routes.
\end{theorem}
\begin{proof}
Unpack the carrier. The only source rows are $A$ and $B$, the only schedule rows are $S_A$ and $S_B$, and the only selector rows are $\sigma$ and $\sigma^{\mathrm{op}}$.

Apply the selector parity exactness of $\RegularCauchyInterleavingUp$ to the forward route. It identifies the even reads with $A,S_A$ and the first component of $M$, and the odd reads with $B,S_B$ and the second component.

Apply the same exactness to the opposite route. Because $\sigma^{\mathrm{op}}$ is stored as the selector after exchanging the two source sides, its odd reads recover the forward even route and its even reads recover the forward odd route.

The stored $H$ and $C$ rows preserve this pairing componentwise. No third schedule or unlisted ledger component is present in the carrier, so the selector symmetry is confined to the displayed two-sided packet.
\end{proof}

\begin{theorem}[Regular Cauchy swap bisimulation Real seal non-escape]
\label{thm:regular-cauchy-swap-bisimulation-real-seal-nonescape}
Every $\RealUp$ consumer of the seal rows $E$ or $E'$ in an accepted $\RegularCauchySwapBisimulationUp$ carrier factors through one of the two displayed interleaving routes, the selected $\RegSeqRatUp$ source name, the selected $\StreamNameUp$ schedule, the shared modulus ledger $M$, the displayed $\hsame$ transport, the displayed $\Cont$ route, the package provenance $P$, and the local naming row $N$. The packet exports no quotient real equality, selected host limit, ambient completeness proof, or third schedule.
\end{theorem}
\begin{proof}
Start from the two seal coordinates. The row $E$ is downstream of the forward interleaving route, while $E'$ is downstream of the opposite interleaving route.

Use selector symmetry to identify which source side and schedule are read before each seal. The two routes differ only by the stored exchange of source sides and selector parity; both consume the same shared ledger $M$ through a displayed component.

The rows $H$ and $C$ attach the required transport and replay data to those finite reads. The provenance row $P$ and local name $N$ then close the packet without adding any real object beyond the two seal boundaries.

Since the carrier definition has no field for quotient real equality, selected limits, ambient completeness, or an unlisted schedule, a real-facing consumer cannot leave the displayed packet.
\end{proof}

\begin{theorem}[Regular Cauchy swap bisimulation public handoff]
\label{thm:regular-cauchy-swap-bisimulation-public-handoff}
The public handoff of an accepted $\RegularCauchySwapBisimulationUp$ carrier is exactly the finite packet
$$
A,B,S_A,S_B,\sigma,\sigma^{\mathrm{op}},M,E,E',H,C,P,N.
$$
It presents two selector-swapped $\RegularCauchyInterleavingUp$ routes with the same $\RegSeqRatUp$ source names, $\StreamNameUp$ schedules, combined modulus ledger, displayed transports, displayed continuations, package provenance, and local $\NameCert$ row. A downstream Real-and-Completion consumer receives this finite boundary and receives no quotient real equality, selected host limit, ambient completeness principle, or bridge-checked schema.
\end{theorem}
\begin{proof}
Carrier admission gives the listed tuple as the whole accepted object. The NameCert obligations identify the forward and opposite interleaving admissions, selector-symmetry row, stability rows, and seal-boundary row as local obligations of that same tuple.

The selector-symmetry theorem binds the two interleaving presentations to the same pair of source schedules and the same ledger components. Thus the public route does not introduce a fresh interleaving carrier; it exposes the two stored presentations of one finite packet.

The Real seal non-escape theorem confines every consumer of $E$ or $E'$ to those displayed rows. Repacking the carrier, obligations, selector symmetry, and non-escape boundary yields the announced public handoff.
\end{proof}

\closureat{RegularCauchySwapBisimulationUp}{seedStr}

\begin{closurestatus}{\RegularCauchySwapBisimulationUp}
  \constructivestory{A $\RegularCauchySwapBisimulationUp$ packet is generated from two $\RegSeqRatUp$ source names, two $\StreamNameUp$ schedules, an alternating selector, its opposite selector, a shared modulus ledger, two $\RealUp$ seal rows, displayed $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-swap-bisimulation-carrier}, \autoref{thm:regular-cauchy-swap-bisimulation-namecert-obligations}, \autoref{thm:regular-cauchy-swap-bisimulation-selector-symmetry}, \autoref{thm:regular-cauchy-swap-bisimulation-real-seal-nonescape}, and \autoref{thm:regular-cauchy-swap-bisimulation-public-handoff} bind the finite selector-swapped interleaving packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close quotient real equality, selected host limits, ambient completeness, bridge checking, or any route through a third schedule.}
  \upgradepath{Obligation closure requires checked carrier admission, forward and opposite interleaving admission, selector-symmetry exactness, componentwise stability, and RealUp seal non-escape for the displayed packet.}
\end{closurestatus}
