\chapter{A Concrete Naming Certificate for \(\MetricSpaceUp\)}
\label{ch:concrete-instances-metric-namecert}

The metric space interface \(\MetricSpaceUp\) has certificate obligations over a carrier together with a distance function \(d : C \times C \to \RealUp\) satisfying non-negativity, identity-of-indiscernibles (with apartness in place of decidable equality), symmetry, and the triangle inequality, all expressed in Bishop-style with explicit real moduli. It depends on \autoref{ch:concrete-instances-real-namecert}.

\section{Carrier definition}

\begin{definition}[MetricSpace carrier]
\label{def:metric-carrier}
Use an abstract carrier \(C\), classifier, apartness, and distance \(d:C\times C\to\RealUp\).
\end{definition}

\section{The certificate}

\begin{definition}[MetricSpace source specification]
\label{def:metric-source-specification}
The source is \(C\) together with the Bishop real distance codomain.
\end{definition}

\begin{definition}[MetricSpace pattern specification]
\label{def:metric-pattern-specification}
The pattern is metric judgment formation from carrier pairs to real distance witnesses.
\end{definition}

\begin{definition}[MetricSpace classifier specification]
\label{def:metric-classifier-specification}
The classifier is the supplied carrier sameness, with distance stable under classifier replacement.
\end{definition}

\begin{definition}[MetricSpace stability certificate]
\label{def:metric-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item distance non-negativity
  \item identity of indiscernibles using classifier and apartness
  \item symmetry
  \item triangle inequality
  \item distance congruence in both arguments
  \item explicit real moduli for all inequality fields
\end{enumerate}
\end{definition}

\begin{theorem}[Metric distance witness symmetric classifier]
\label{thm:metric-distance-witness-symmetric-classifier}
For unary endpoint histories $x,y$, if $d_{xy}$ is witnessed by the
continuation ledger from $x$ to $y$ and $d_{yx}$ is witnessed by the reversed
ledger from $y$ to $x$, then the two distance histories classify together by
$\hsame$:
$$
\mathsf{MetricDistanceWitness}(x,y,d_{xy})
\Longrightarrow
\mathsf{MetricDistanceWitness}(y,x,d_{yx})
\Longrightarrow
\hsame(d_{xy},d_{yx}).
$$
\end{theorem}
\begin{proof}
Unpack the two concrete distance witnesses. The endpoint histories are unary in
both directions, and the two displayed continuations are precisely the forward
and reversed unary continuation ledgers. Unary continuation commutativity gives
$\hsame(d_{xy},d_{yx})$.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricDistanceWitness\_symmetric\_classifier}

\begin{theorem}[Metric distance witness prefix closure]
\label{thm:metric-distance-witness-prefix-closed}
For unary histories $p,x,y,d$, a unary visible prefix on the first endpoint
and the distance ledger preserves the concrete metric distance witness:
$$
\mathsf{UnaryHistory}(p)
\Longrightarrow
\mathsf{MetricDistanceWitness}(x,y,d)
\Longrightarrow
\mathsf{MetricDistanceWitness}(p\cdot x,y,p\cdot d).
$$
\end{theorem}
\begin{proof}
Unpack the witness into unary endpoint and distance histories together with the
continuation ledger $d=x\cdot y$. Unary append closure gives unary histories
for $p\cdot x$ and $p\cdot d$. The prefixed continuation ledger is exactly the
associativity equality $(p\cdot x)\cdot y=p\cdot(x\cdot y)$.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricDistanceWitness\_prefix\_closed}

\begin{definition}[MetricSpace ledger policy]
\label{def:metric-ledger-policy}
Record carrier witnesses and the real ledger of each distance value.
\end{definition}

\begin{definition}[\(\MetricSpaceUp\) certificate obligations]
\label{def:metric-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\MetricSpaceUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\MetricSpaceUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:metric-zero-axiom-note}
Replaces decidable equality with apartness and explicit real-modulus inequalities.
\end{remark}
