\chapter{A Concrete Naming Certificate for $\RegularCauchyTailFusionUp$}
\label{ch:concrete-instances-regularcauchytailfusion-namecert}
\origin{ai}

The $\RegularCauchyTailFusionUp$ packet records the finite cofinal tail-fusion step used by Real completeness consumers before a diagonal $\RealUp$ seal is read. It joins regular-sequence tail witnesses, selected finite stream windows, dyadic tolerance ledgers, a shared tail-meet row, a diagonal seal route, and the local naming certificate into one displayed $\BHist$ surface. It exports no quotient stream, host real equality, selected completed limit, unbounded diagonal object, or ambient completeness theorem.

\falsifiablePrediction{Deleting the shared-threshold row $M$ permits a $\RealUp$ seal route to bypass the displayed $\RegularCauchyTailMeetUp$ handoff, while deleting the finite window row $W$ breaks the $\StreamNameUp$ and $\DyadicRatCoreUp$ route to the $\RegSeqRatUp$ readback.}

\independenceWitness{Nearest siblings: regular-cauchy-tail-meet, regularcauchylimittransport, streamname, dyadicratcore, and real. The $\RegularCauchyTailFusionUp$ packet is not bijective to any one of them because it stores the fused route $Q,X,W,D,T,M,R,L,H,C,P,N$ linking all five surfaces before the $\RealUp$ seal.}

\begin{definition}[Regular Cauchy tail fusion carrier]
\label{def:regular-cauchy-tail-fusion-carrier}
A $\RegularCauchyTailFusionUp$ carrier is a finite $\BHist$ packet
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $Q$ is the rational or dyadic precision request routed to the tail-fusion consumer;
\item $X$ is the $\RegSeqRatUp$ regular rational family row whose tail witnesses are being fused;
\item $W$ is the finite $\StreamNameUp$ window family selected for the precision request;
\item $D$ is the $\DyadicRatCoreUp$ tolerance and observation ledger for the selected windows;
\item $T$ is the finite tail-witness row exposing the cofinal tail data read from $X$ through $W$ and $D$;
\item $M$ is the $\RegularCauchyTailMeetUp$ shared-threshold row that makes the displayed tail witnesses use one cofinal tail bound;
\item $R$ is the $\RegSeqRatUp$ diagonal readback row reached after the shared tail bound and dyadic ledger are fixed;
\item $L$ is the $\RealUp$ seal row reached only after $Q,X,W,D,T,M,R$ have been exposed;
\item $H$ stores componentwise $\hsame$ transports for the precision request, regular family, windows, dyadic ledger, tail witnesses, tail-meet row, readback row, seal row, provenance, and local name;
\item $C$ stores the displayed $\Cont$ routes from precision request to window selection, dyadic observation, tail witness, shared tail meet, diagonal readback, and Real seal;
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyTailMeetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RegularCauchyTailFusionUp}$ row.
\end{enumerate}
The carrier is only the finite cofinal tail-fusion packet. It has no coordinate for quotient stream equality, host real equality, an externally selected limit, an unbounded diagonal stream, or an ambient completeness principle.
\end{definition}

\begin{definition}[Regular Cauchy tail fusion classifier]
\label{def:regular-cauchy-tail-fusion-classifier}
Two accepted $\RegularCauchyTailFusionUp$ carriers classify together when their displayed precision requests, regular-family rows, finite windows, dyadic ledgers, tail witnesses, shared tail-meet rows, diagonal readbacks, and Real seal rows are related componentwise by the stored $\hsame$ transports and replay the same $\Cont$ route from $Q$ through $M$ to $L$.

The classifier compares only the rows listed in \autoref{def:regular-cauchy-tail-fusion-carrier}; it does not compare quotient streams, host real values, selected external limits, or ambient completeness witnesses.
\end{definition}

\begin{theorem}[Regular Cauchy tail fusion NameCert obligations]
\label{thm:regular-cauchy-tail-fusion-namecert-obligations}
The local $\NameCert_{\RegularCauchyTailFusionUp}$ surface for the carrier of \autoref{def:regular-cauchy-tail-fusion-carrier} consists exactly of carrier admission, precision-request exposure, $\RegSeqRatUp$ family admission, finite $\StreamNameUp$ window coverage, $\DyadicRatCoreUp$ tolerance-ledger readback, finite tail-witness exposure, $\RegularCauchyTailMeetUp$ shared-threshold routing, diagonal $\RegSeqRatUp$ readback, $\RealUp$ seal handoff, componentwise $\hsame$ transport, displayed $\Cont$ route replay, $\Pkg$ provenance, and the local naming row.
\end{theorem}
\begin{proof}
Project the carrier $F$. Its coordinates list the precision request, regular family, selected windows, dyadic ledger, tail witnesses, shared tail meet, diagonal readback, Real seal, transports, routes, provenance, and local name.

The cofinal tail route is finite. A consumer first reads $Q$, then the selected windows $W$ and dyadic ledger $D$, then the tail witness row $T$, and only then the shared-threshold row $M$ used by the diagonal readback $R$.

The remaining rows $H,C,P,N$ transport, route, record provenance, and name the same packet. Since no carrier coordinate contains quotient streams, host real equality, selected limits, unbounded diagonal data, or ambient completeness, the listed obligations exhaust the local naming surface.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion tail-meet handoff]
\label{thm:regular-cauchy-tail-fusion-tail-meet-handoff}
For an accepted $\RegularCauchyTailFusionUp$ carrier, every cofinal tail witness read reaches the diagonal readback row $R$ through the finite route
$$
Q,X,W,D,T,M,H,C,P,N.
$$
The $\RegularCauchyTailMeetUp$ row $M$ is the only shared-threshold surface available to the packet, so the handoff cannot replace it by a hidden tail oracle, quotient-stream comparison, selected limit, host real equality, or ambient completeness row.
\end{theorem}
\begin{proof}
Read the carrier coordinates from \autoref{def:regular-cauchy-tail-fusion-carrier}. The only row that can merge tail witnesses into a common bound is $M$, and it appears after the precision request, regular-family row, finite windows, dyadic ledger, and tail-witness row.

Apply the NameCert obligation theorem. It binds the tail-witness exposure to $T$ and the shared-threshold routing to $M$, with all movement recorded by $H$ and $C$ and all provenance recorded by $P$ and $N$.

Because the classifier of \autoref{def:regular-cauchy-tail-fusion-classifier} compares only the displayed rows, no transported carrier can introduce a second tail source or an external comparison. The diagonal readback therefore receives the tail-meet handoff through exactly the finite route shown above.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion monotone window handoff]
\label{thm:regular-cauchy-tail-fusion-window-monotone-handoff}
Every accepted $\RegularCauchyTailFusionUp$ packet reads its selected $\StreamNameUp$ finite windows $W$ and dyadic ledger $D$ before the tail witnesses $T$ and shared threshold $M$ are consumed. Later $\RealUp$ seal reads through $L$ cannot skip $W,D$ or replace them by an unwindowed tail oracle, quotient stream comparison, selected limit, or ambient completeness row.
\end{theorem}
\begin{proof}
Project
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N).
$$
The carrier orders the finite windows and dyadic ledger before tail witnesses and before the shared threshold row.

Use \autoref{thm:regular-cauchy-tail-fusion-tail-meet-handoff}. It routes every cofinal tail witness through $Q,X,W,D,T,M,H,C,P,N$ before the diagonal readback $R$ is reached.

Now apply the limit-transport link to the later seal row. Since the $\RealUp$ handoff reads $L$ only after the displayed diagonal readback route, coordinate exhaustion leaves no route that bypasses $W,D$.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion shared-threshold exhaustion]
\label{thm:regular-cauchy-tail-fusion-shared-threshold-exhaustion}
Every $\RegularCauchyTailFusionUp$ route that reaches the diagonal readback $R$ or the $\RealUp$ seal $L$ uses the single displayed shared-threshold row $M$ supplied by the $\RegularCauchyTailMeetUp$ sibling. The packet has no second tail oracle, quotient stream comparison, selected limit, ambient completeness row, or independent threshold coordinate.
\end{theorem}
\begin{proof}
Project
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N).
$$
The only shared-threshold coordinate in the carrier is $M$.

Apply \autoref{thm:regular-cauchy-tail-fusion-tail-meet-handoff}. It sends each cofinal tail witness to $R$ through $M$, with all movement recorded by the displayed transport, continuation, provenance, and local naming rows.

Use the sibling link to \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert} to identify $M$ as the shared finite threshold surface. Use the link to \autoref{ch:concrete-instances-regularcauchylimittransport-namecert} for the subsequent route from $R$ to $L$.

Coordinate exhaustion closes the claim. Since no other carrier coordinate has the role of a threshold, tail oracle, quotient comparison, selected limit, or completeness witness, every route to $R$ or $L$ uses the displayed $M$ row.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion Real limit handoff]
\label{thm:regular-cauchy-tail-fusion-real-limit-handoff}
Every $\RealUp$ diagonal-limit consumer of an accepted $\RegularCauchyTailFusionUp$ packet reads the seal row $L$ only after the precision request, regular rational family, selected finite windows, dyadic tolerance ledger, finite tail witnesses, shared tail-meet row, diagonal readback, componentwise transports, continuation routes, package provenance, and local name have been displayed.

Equivalently, the completion-facing route factors through
$$
Q,X,W,D,T,M,R,H,C,P,N
$$
before the seal row $L$ is consumed, and it exports no quotient stream, host real equality, selected completed limit, unbounded diagonal object, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$ consumer of the seal row $L$. In the carrier, $L$ is downstream of the diagonal readback row $R$, so the consumer cannot inspect a seal before the finite readback route has been displayed.

Use \autoref{thm:regular-cauchy-tail-fusion-tail-meet-handoff}. It places every cofinal tail read through $Q,X,W,D,T,M,H,C,P,N$ before $R$ is reached.

Now append the seal route from $R$ to $L$ using the continuation rows in $C$ and the componentwise transports in $H$. The package provenance and local name record the same finite route. Since the carrier and classifier omit quotient streams, host equality, selected limits, unbounded diagonal objects, and ambient completeness, no completion-facing read can escape the displayed packet.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion limit-transport link]
\label{thm:regular-cauchy-tail-fusion-limit-transport-link}
Every accepted $\RegularCauchyTailFusionUp$ packet factors its $\RealUp$ seal handoff through the shared-threshold row of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert} and the displayed seal transport surface of \autoref{ch:concrete-instances-regularcauchylimittransport-namecert} before any $\RealUp$ consumer can read the diagonal limit row.

In particular, for
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N),
$$
the rows $Q,X,W,D,T$ expose the finite precision, regular rational family, selected windows, dyadic ledger, and tail witnesses; $M$ supplies the shared cofinal threshold; $R,L$ supply the diagonal readback and seal handoff; and $H,C,P,N$ record transport, continuation, provenance, and the local name.
\end{theorem}
\begin{proof}
Project the existing packet rows $Q,X,W,D,T,M,R,L,H,C,P,N$. The carrier gives no direct route from the finite tail witnesses to the Real seal; the route must first pass through the displayed shared-threshold row $M$ and the diagonal readback row $R$.

Use the tail-meet sibling \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}. Its shared cofinal threshold is exactly the row consumed at $M$, so the tail-fusion packet cannot read its finite witnesses as independent unmerged tails.

Now use the limit-transport sibling \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}. Its displayed seal transport surface is the finite route that carries the diagonal readback toward the Real-facing seal row, so $L$ is reached only after $M$ and $R$ have been exposed.

Finally apply the Real limit handoff theorem above. Since the carrier omits quotient streams, host real equality, selected limits, unbounded diagonal data, and ambient completeness, the sibling-linked route has no non-displayed escape before the $\RealUp$ consumer reads the diagonal limit row.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion public obligation handoff]
\label{thm:regular-cauchy-tail-fusion-public-obligation-handoff}
For every accepted $\RegularCauchyTailFusionUp$ packet
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N),
$$
the carrier rows, classifier comparison, tail-meet handoff, monotone window handoff, shared-threshold exhaustion, $\RealUp$ limit handoff, and limit-transport link jointly form the public obligation surface for downstream Real and Completion consumers. Every such consumer receives those rows as one finite handoff and receives no additional source beyond the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route.
\end{theorem}
\begin{proof}
Project the carrier and classifier. The public surface begins with the displayed coordinates $Q,X,W,D,T,M,R,L,H,C,P,N$, and classifier stability compares only those coordinates.

Use the tail-meet handoff, monotone window handoff, and shared-threshold exhaustion. These rows place every cofinal tail read behind the selected windows, dyadic ledger, finite witnesses, and the shared threshold $M$ supplied by \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}.

Use the Real limit handoff and the limit-transport link. They carry the diagonal readback through $R$ and the seal row $L$ along the displayed transport surface of \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}.

Repack the cited rows as the public obligation handoff. Since no other coordinate is available in the packet, every Real or Completion consumer receives exactly that finite surface.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion window budget coverage]
\label{thm:regular-cauchy-tail-fusion-window-budget-coverage}
Every accepted window read of a $\RegularCauchyTailFusionUp$ packet factors through the finite window and budget route
$$
W,D,T,M
$$
before the diagonal readback and Real seal rows $R,L$ are consumed. The row $W$ is read as the finite-window surface of \autoref{ch:concrete-instances-streamname-namecert}, $D$ is read as the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, $T$ records the displayed tail witnesses, and $M$ is the shared-threshold row.
\end{theorem}
\begin{proof}
Start from an accepted window read. Projection from the carrier shows that the only window coordinate is $W$, and the only budget coordinate attached to it is $D$.

Apply the StreamName finite-window rows, represented here by the $W$ coordinate, and then apply the dyadic ledger rows represented by $D$. These two rows supply the bounded window and tolerance information before any tail witness can be used.

Use the monotone window handoff and shared-threshold exhaustion. They force the read through $T$ and then through $M$ before the diagonal readback row $R$ and the seal row $L$ can be consumed.

Thus every accepted window read factors through $W,D,T,M$ first, and the downstream rows $R,L$ receive only the finite route already covered by those rows.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion Real seal non-escape]
\label{thm:regular-cauchy-tail-fusion-real-seal-nonescape}
Every $\RealUp$ or Completion consumer of a $\RegularCauchyTailFusionUp$ packet receives only the displayed route
$$
Q,X,W,D,T,M,R,L,H,C,P,N.
$$
The handoff exposes no quotient stream, host real equality, selected limit, unbounded diagonal object, hidden tail oracle, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with the public obligation handoff above. It places every downstream read on the displayed carrier, classifier, tail-meet, window, threshold, Real handoff, and limit-transport rows.

Apply window budget coverage. The consumer reaches $R$ and $L$ only after the route through $W,D,T,M$ has been exposed.

Finally use coordinate exhaustion. The carrier has no quotient stream coordinate, no host real equality coordinate, no selected-limit coordinate, no unbounded diagonal object, no hidden tail oracle, and no ambient completeness row. Therefore a Real or Completion consumer cannot escape the displayed finite route.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion scoped window exhaustion]
\label{thm:regular-cauchy-tail-fusion-scoped-window-exhaustion}
Every scoped completion-facing read of an accepted $\RegularCauchyTailFusionUp$ packet factors through the finite route
$$
Q,X,W,D,T,M,R,H,C,P,N
$$
before the seal row $L$ is consumed. Here $W,D$ are the $\StreamNameUp$ window row and $\DyadicRatCoreUp$ ledger row, $M$ is the $\RegularCauchyTailMeetUp$ shared-threshold row, and $R$ is the $\RegularCauchyLimitTransportUp$-facing readback. The read exports no quotient stream, host real equality, selected completed limit, unbounded diagonal data, or ambient completeness principle.
\end{theorem}
\begin{proof}
Project the carrier
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N).
$$
The completion-facing seal coordinate $L$ is downstream of the displayed diagonal readback row $R$, and the readback row is downstream of the selected finite windows, dyadic ledger, tail witnesses, and shared threshold.

Apply the tail-meet handoff and shared-threshold exhaustion. These results force the cofinal tail data through $Q,X,W,D,T,M,H,C,P,N$ and identify $M$ with the displayed $\RegularCauchyTailMeetUp$ sibling row rather than with an external tail oracle.

Apply the limit-transport link and the Real limit handoff. The transport sibling consumes the diagonal readback surface at $R$, and the Real handoff permits the seal read only after the finite route has been displayed.

Coordinate exhaustion closes the scoped claim. Since the carrier and classifier contain no quotient stream, host real equality, selected limit, unbounded diagonal coordinate, or ambient completeness row, the completion-facing read has no route outside the displayed finite window path before $L$.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion obligation surface]
\label{thm:regular-cauchy-tail-fusion-obligation-surface}
The carrier, classifier, local $\NameCert$ obligations, tail-meet handoff, window monotonicity, shared-threshold exhaustion, Real limit handoff, and limit-transport link of this chapter form the five obligation rows for $\RegularCauchyTailFusionUp$. The rows are carrier admission, classifier stability, cofinal-tail routing, downstream Real seal handoff, and ledger non-escape, and every route is confined to $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyTailMeetUp$, and $\RealUp$.
\end{theorem}
\begin{proof}
Carrier admission and classifier stability are exactly the surfaces of \autoref{def:regular-cauchy-tail-fusion-carrier} and \autoref{def:regular-cauchy-tail-fusion-classifier}. The local naming row is supplied by \autoref{thm:regular-cauchy-tail-fusion-namecert-obligations}.

The cofinal-tail route is assembled from \autoref{thm:regular-cauchy-tail-fusion-tail-meet-handoff}, \autoref{thm:regular-cauchy-tail-fusion-window-monotone-handoff}, and \autoref{thm:regular-cauchy-tail-fusion-shared-threshold-exhaustion}. These results force every tail witness through the displayed windows, dyadic ledger, and the sibling shared-threshold packet of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}.

The downstream Real seal handoff is supplied by \autoref{thm:regular-cauchy-tail-fusion-real-limit-handoff} and \autoref{thm:regular-cauchy-tail-fusion-limit-transport-link}. The latter also routes the diagonal readback through the seal-transport sibling \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}.

Ledger non-escape follows by collecting the exclusions in those displayed results. The carrier and classifier expose only the listed BEDC rows, so no route can introduce a quotient stream, host real equality, selected completed limit, unbounded diagonal object, independent tail oracle, or ambient completeness theorem.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion carrier-classifier synchronization]
\label{thm:regular-cauchy-tail-fusion-carrier-classifier-synchronization}
Every classifier comparison between accepted $\RegularCauchyTailFusionUp$ packets exposes the same carrier rows
$$
Q,X,W,D,T,M,R,L,H,C,P,N.
$$
The comparison is therefore synchronized with the displayed precision request, regular-family row, finite window, dyadic ledger, tail witnesses, shared-threshold row, diagonal readback, Real seal, componentwise transports, continuation routes, provenance, and local name. It cannot compare quotient streams, host real values, selected completed limits, unbounded diagonal objects, or ambient completeness witnesses.
\end{theorem}
\begin{proof}
Project the two accepted packets through \autoref{def:regular-cauchy-tail-fusion-carrier}. Each accepted carrier has exactly the rows $Q,X,W,D,T,M,R,L,H,C,P,N$, with no additional completion-facing coordinate.

Apply the classifier definition of \autoref{def:regular-cauchy-tail-fusion-classifier}. It compares the listed rows componentwise and replays the same displayed route from $Q$ through $M$ to $L$.

Use the tail-meet handoff, shared-threshold exhaustion, and limit-transport link. These results force the compared route through the $\RegularCauchyTailMeetUp$ sibling at $M$ and the $\RegularCauchyLimitTransportUp$ sibling before the seal row $L$ can be read.

Coordinate exhaustion gives synchronization. Since neither the carrier nor the classifier has a quotient-stream, host-real, selected-limit, unbounded-diagonal, or ambient-completeness coordinate, the comparison cannot leave the displayed rows.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion window transport lock]
\label{thm:regular-cauchy-tail-fusion-window-transport-lock}
For every accepted $\RegularCauchyTailFusionUp$ transport, the $\hsame$ rows preserve the selected $\StreamNameUp$ window $W$, the $\DyadicRatCoreUp$ ledger $D$, and the $\RegularCauchyTailMeetUp$ shared-threshold row $M$ before the $\RealUp$ seal row $L$ is consumed. A transported seal read cannot change the window, budget ledger, or shared threshold on the way to $L$.
\end{theorem}
\begin{proof}
Start from the carrier inventory $F=(Q,X,W,D,T,M,R,L,H,C,P,N)$. The rows $W,D,M$ are displayed before the diagonal readback $R$ and the seal row $L$.

Apply the monotone window handoff and shared-threshold exhaustion. They place $W$ and $D$ before the tail witnesses and identify $M$ as the single sibling threshold supplied by \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}.

Now apply the carrier-classifier synchronization theorem above. Its componentwise comparison uses $H$ only to transport the displayed rows, so $W,D,M$ remain the same selected window, ledger, and threshold rows along the accepted route.

Finally use the limit-transport link to \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}. The seal-facing transport begins after the diagonal readback has consumed $W,D,M$, so changing any of them before $L$ exits the accepted packet.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion ledger exactness]
\label{thm:regular-cauchy-tail-fusion-ledger-exactness}
Every $\RealUp$-facing consumer route of an accepted $\RegularCauchyTailFusionUp$ packet is exhausted by the finite window, shared-threshold, diagonal readback, transport, continuation, package, and local NameCert rows
$$
W,D,T,M,R,L,H,C,P,N.
$$
The route has no remaining ledger entry for a quotient stream, selected completed limit, host real equality, hidden tail oracle, independent transport, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$-facing read. By the Real limit handoff, the seal row $L$ is read only after the precision request, regular-family row, finite window, dyadic ledger, tail witnesses, shared threshold, and diagonal readback have already been displayed.

Use the tail-meet handoff and shared-threshold exhaustion. They route the finite tail witnesses through $T$ and the sibling threshold $M$, leaving no hidden tail oracle or independent threshold source.

Apply the window transport lock. It preserves $W,D,M$ through the componentwise $\hsame$ rows and keeps the route aligned with the displayed continuation and provenance rows before $L$.

Finally collect the public export packet and limit-transport link. These assemble the Real-facing route from the finite ledger rows $W,D,T,M,R,L,H,C,P,N$, so quotient streams, selected limits, host equality, independent transport, and ambient completeness are outside the local certificate.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion public export packet]
\label{thm:regular-cauchy-tail-fusion-public-export-packet}
The carrier, classifier, obligation surface, shared-threshold exhaustion, $\RealUp$ limit handoff, and limit-transport link for $\RegularCauchyTailFusionUp$ assemble one public export packet over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyTailMeetUp$, $\RegularCauchyLimitTransportUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. A public consumer may read exactly the finite route
$$
Q,X,W,D,T,M,R,L,H,C,P,N
$$
with $M$ as the shared-threshold row, $R$ as the diagonal readback row, and $L$ as the $\RealUp$ seal handoff.

The packet exports no quotient streams, host real equality, selected completed limits, unbounded diagonal data, hidden tail oracle, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Carrier admission and classifier stability are supplied by \autoref{def:regular-cauchy-tail-fusion-carrier} and \autoref{def:regular-cauchy-tail-fusion-classifier}. The local obligation surface is \autoref{thm:regular-cauchy-tail-fusion-obligation-surface}, so the public object starts from the same finite rows rather than from a host completion object.

The tail side is controlled by \autoref{thm:regular-cauchy-tail-fusion-tail-meet-handoff}, \autoref{thm:regular-cauchy-tail-fusion-window-monotone-handoff}, and \autoref{thm:regular-cauchy-tail-fusion-shared-threshold-exhaustion}. These theorems force every tail witness through the selected windows, dyadic ledger, finite witness row, and the displayed $\RegularCauchyTailMeetUp$ threshold row $M$.

The completion-facing side is controlled by \autoref{thm:regular-cauchy-tail-fusion-real-limit-handoff} and \autoref{thm:regular-cauchy-tail-fusion-limit-transport-link}. They route the diagonal readback $R$ and the seal row $L$ through the same $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ boundary, with the checked TasteGate marker recorded in the closure block below identifying the same carrier surface.

Repack these rows as the public export packet. Since each cited theorem excludes quotient streams, host real equality, selected limits, unbounded diagonal data, hidden tail oracles, and ambient completeness, the public export exposes only the displayed finite route.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion selector-budget window lock]
\label{thm:regular-cauchy-tail-fusion-selector-budget-window-lock}
Every selector-budget read through an accepted $\RegularCauchyTailFusionUp$ public export packet must pass through the displayed $\StreamNameUp$ window row $W$ and $\DyadicRatCoreUp$ ledger row $D$ before it reaches the shared $\RegularCauchyTailMeetUp$ row $M$. The accepted read has no route to an unbounded selector, hidden budget oracle, independent tail threshold, quotient stream, selected limit, host convergence row, or ambient completeness row outside the finite packet
$$
Q,X,W,D,T,M,R,L,H,C,P,N.
$$
\end{theorem}
\begin{proof}
Start with the public export packet of \autoref{thm:regular-cauchy-tail-fusion-public-export-packet}. It exposes exactly the finite rows $Q,X,W,D,T,M,R,L,H,C,P,N$, with $W$ and $D$ displayed before the tail-meet row $M$.

Apply \autoref{thm:regular-cauchy-tail-fusion-window-monotone-handoff} and \autoref{thm:regular-cauchy-tail-fusion-shared-threshold-exhaustion}. These rows force any selector-budget request to read the scheduled $\StreamNameUp$ window and $\DyadicRatCoreUp$ ledger before the $\RegularCauchyTailMeetUp$ sibling named in \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}.

Finally use \autoref{thm:regular-cauchy-tail-fusion-limit-transport-link} and the limit-transport sibling \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}. Since the transport begins after the same window, ledger, and shared-threshold rows have been displayed, no selector or budget read can bypass $W,D,M$ on the way to the Real-facing rows.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion cofinal route totality]
\label{thm:regular-cauchy-tail-fusion-cofinal-route-totality}
Every cofinal route to the diagonal readback of an accepted $\RegularCauchyTailFusionUp$ packet is exhausted by the displayed rows
$$
Q,X,W,D,T,M,R,H,C,P,N.
$$
The route reaches $R$ only through the precision request, regular source, finite window, dyadic ledger, tail witnesses, shared tail-meet row, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and local $\NameCert$ row; it has no further cofinal selector, hidden threshold, quotient stream, host limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier through the public export packet. Before the seal row is read, the available diagonal route is the finite predecessor $Q,X,W,D,T,M,R,H,C,P,N$.

Use \autoref{thm:regular-cauchy-tail-fusion-tail-meet-handoff} and \autoref{thm:regular-cauchy-tail-fusion-shared-threshold-exhaustion}. They place every cofinal witness behind the selected window, dyadic ledger, finite tail row, and the shared $\RegularCauchyTailMeetUp$ sibling row $M$.

Apply \autoref{thm:regular-cauchy-tail-fusion-limit-transport-link} and the sibling rows for \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}, and \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}. These rows account for the diagonal readback and its transports, so the listed route exhausts every cofinal path to $R$.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion Real seal factorization]
\label{thm:regular-cauchy-tail-fusion-real-seal-factorization}
Every $\RealUp$ seal consumer of an accepted $\RegularCauchyTailFusionUp$ packet factors through the same shared-threshold row $M$ and the same $\RegularCauchyLimitTransportUp$ sibling before it reads the seal row $L$. The consumer receives the seal only through
$$
Q,X,W,D,T,M,R,L,H,C,P,N,
$$
with $M$ supplied by \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert} and the transport surface supplied by \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:regular-cauchy-tail-fusion-real-limit-handoff} and \autoref{thm:regular-cauchy-tail-fusion-public-export-packet}. Together they place the seal row $L$ after the diagonal readback row $R$ and keep both rows inside the displayed finite packet.

Next apply \autoref{thm:regular-cauchy-tail-fusion-shared-threshold-exhaustion}. The route to $R$ must already have passed through the $\RegularCauchyTailMeetUp$ row $M$, so the seal consumer cannot read a separate threshold or hidden tail source.

Finally use \autoref{thm:regular-cauchy-tail-fusion-limit-transport-link}. It identifies the seal-facing transport as the displayed $\RegularCauchyLimitTransportUp$ sibling route, after which the public export exclusions rule out quotient streams, selected limits, host convergence, ambient completeness, and independent Real-seal paths.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion shared-source readback]
\label{thm:regular-cauchy-tail-fusion-shared-source-readback}
Every accepted $\RegularCauchyTailFusionUp$ packet
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N)
$$
reads its source rows $Q,X,W,D,T,M,R$ through one shared finite route before the $\RealUp$ seal row $L$ is consumed. The route starts with the $\StreamNameUp$ window row $W$, the $\DyadicRatCoreUp$ ledger row $D$, and the regular-family source row $X$, then passes through the $\RegularCauchyTailMeetUp$ shared threshold $M$ and the diagonal readback row $R$. No downstream consumer may split this read into an independent stream name, dyadic ledger, tail threshold, or diagonal readback source.
\end{theorem}
\begin{proof}
Project the displayed carrier. Its only source-side coordinates before the seal row are $Q,X,W,D,T,M,R$, with $H,C,P,N$ recording transport, continuation, provenance, and local naming data rather than separate source objects.

Use the tail-meet handoff and shared-threshold exhaustion. They identify $M$ as the sibling $\RegularCauchyTailMeetUp$ threshold row reached from the same $X,W,D,T$ source route, so the tail evidence cannot be read as a hidden or independently selected cofinal tail.

Apply window monotonicity and the limit-transport link. The window and dyadic rows remain the finite predecessor of the diagonal readback row $R$, and the transport row carries that readback toward the seal without introducing another source coordinate.

Finally use the public export packet. Since the public packet exposes exactly $Q,X,W,D,T,M,R,L,H,C,P,N$, every accepted consumer reads the source rows through the same finite route before $L$.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion Real seal consumer boundary]
\label{thm:regular-cauchy-tail-fusion-real-seal-consumer-boundary}
Every $\RealUp$ or completion-facing consumer of the seal row $L$ in an accepted $\RegularCauchyTailFusionUp$ packet factors through the shared-source readback of \autoref{thm:regular-cauchy-tail-fusion-shared-source-readback} and then through the displayed rows $H,C,P,N$. The boundary exposes no quotient stream, host equality, selected limit, hidden tail oracle, ambient completeness principle, or independent route around $Q,X,W,D,T,M,R$.
\end{theorem}
\begin{proof}
Start with a consumer request for the seal row $L$. By shared-source readback, the request first reaches the rows $Q,X,W,D,T,M,R$ through one $\StreamNameUp$--$\DyadicRatCoreUp$--$\RegularCauchyTailMeetUp$ route.

Apply the Real limit handoff. The handoff reads $L$ only after the diagonal readback row $R$ has been exposed, and it treats $L$ as a seal row rather than as a selected completed limit or ambient completeness witness.

Use the limit-transport link to move from $R$ to the seal-facing surface. The transport is recorded by the displayed $H$ and $C$ rows, with $P$ and $N$ carrying provenance and local naming for the same finite packet.

Finally apply the bridged consumer packet. It leaves every $\RealUp$ or completion-facing consumer behind the public export surface and the displayed rows $H,C,P,N$, so no quotient stream, host equality, selected limit, hidden tail oracle, ambient completeness principle, or independent route remains available.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion bridged consumer packet]
\label{thm:regular-cauchy-tail-fusion-bridged-consumer-packet}
Every completion-facing consumer of an accepted $\RegularCauchyTailFusionUp$ packet
$$
F=(Q,X,W,D,T,M,R,L,H,C,P,N)
$$
factors through the shared-threshold row of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}, the displayed seal-transport surface of \autoref{ch:concrete-instances-regularcauchylimittransport-namecert}, and the $\RealUp$ seal row before any public completion read. The packet supplies no quotient stream, host real equality, selected completed limit, unbounded diagonal object, ambient completeness theorem, hidden tail oracle, or independent transport route.
\end{theorem}
\begin{proof}
Begin with the displayed carrier and public export packet. The carrier lists the finite route $Q,X,W,D,T,M,R,L,H,C,P,N$, and \autoref{thm:regular-cauchy-tail-fusion-public-export-packet} permits a public consumer to read only that route.

Use \autoref{thm:regular-cauchy-tail-fusion-tail-meet-handoff} and \autoref{thm:regular-cauchy-tail-fusion-shared-threshold-exhaustion}. They force the tail witnesses through $T$ and then through the single shared-threshold row $M$ supplied by the tail-meet sibling.

Use \autoref{thm:regular-cauchy-tail-fusion-limit-transport-link}. It carries the diagonal readback surface from $R$ toward the displayed seal-transport sibling before the seal row $L$ can be read.

Apply \autoref{thm:regular-cauchy-tail-fusion-scoped-window-exhaustion} and the Real limit handoff. These keep the completion-facing read behind the selected windows, dyadic ledger, shared threshold, diagonal readback, and seal row.

Thus any completion-facing consumer factors through the tail-meet row, the limit-transport surface, and the Real seal before becoming public. The exclusions in the carrier, classifier, scoped window exhaustion, and public export packet rule out quotient streams, host real equality, selected limits, unbounded diagonal objects, ambient completeness, hidden tail oracles, and independent transport routes.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion mature consumer surface]
\label{thm:regular-cauchy-tail-fusion-mature-consumer-surface}
Every mature completion-facing consumer of an accepted $\RegularCauchyTailFusionUp$ packet factors through the same public export packet of \autoref{thm:regular-cauchy-tail-fusion-public-export-packet}, the bridged consumer packet of \autoref{thm:regular-cauchy-tail-fusion-bridged-consumer-packet}, the $\RegularCauchyTailMeetUp$ sibling, the $\RegularCauchyLimitTransportUp$ sibling, and the $\RealUp$ seal rows. The mature surface exports no quotient stream, selected limit, ambient completeness row, hidden tail oracle, or independent transport route.
\end{theorem}
\begin{proof}
Start with the public export packet. It exposes only the finite route $Q,X,W,D,T,M,R,L,H,C,P,N$ and denies quotient streams, host real equality, selected completed limits, unbounded diagonal data, hidden tail oracles, and ambient completeness.

Apply the bridged consumer packet. A completion-facing consumer must pass through the shared-threshold row supplied by the tail-meet sibling and the seal-transport surface supplied by the limit-transport sibling before it can read the $\RealUp$ seal row.

Finally collect the sibling and seal exclusions. Since the tail meet supplies only the shared finite threshold, the transport sibling supplies only the displayed seal route, and the Real row is read as a seal rather than as an ambient completeness theorem, every mature consumer factors through the same finite consumer surface.
\end{proof}

The Lean TasteGate namespace $\mathsf{BEDC.Derived.RegularCauchyTailFusionUp.TasteGate}$ must provide $\mathsf{Nontrivial}\ \mathsf{RegularCauchyTailFusionUp}$ and $\mathsf{FieldFaithful}\ \mathsf{RegularCauchyTailFusionUp}$ instances for the displayed carrier.

\begin{theorem}[Regular Cauchy tail fusion paired agreement source]
\label{thm:regular-cauchy-tail-fusion-paired-agreement-source}
Every accepted $\RegularCauchyTailFusionUp$ packet exposing
$$
Q,X,W,D,T,M,R,L,H,C,P,N
$$
supplies the single-source cofinal-tail input that a paired $\RealTailAgreementSealUp$ consumer may duplicate into its left and right source rows. This source is the finite route certified by the public export packet and the mature consumer surface, and it does not by itself export paired source equality, quotient stream equality, selected limit equality, host convergence, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the public export packet of \autoref{thm:regular-cauchy-tail-fusion-public-export-packet}. It exposes the finite route $Q,X,W,D,T,M,R,L,H,C,P,N$, with $X$ as the regular-family source row and $M$ as the shared cofinal-tail row.

Apply the bridged consumer packet of \autoref{thm:regular-cauchy-tail-fusion-bridged-consumer-packet} and the mature consumer surface of \autoref{thm:regular-cauchy-tail-fusion-mature-consumer-surface}. Together they force any Real-facing consumer to read this route through the public export boundary before reaching the seal-facing rows.

The paired seal of \autoref{ch:concrete-instances-realtailagreementseal-namecert} may use that single cofinal-tail source as the source of its left and right rows. The duplication is a consumer-side paired read, not an equality exported by the fusion packet, so the exclusions of the public export packet remain in force.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion paired window budget]
\label{thm:regular-cauchy-tail-fusion-paired-window-budget}
The $\RegularCauchyTailFusionUp$ window and budget route
$$
Q,X,W,D,T,M
$$
is the finite predecessor of the paired-window budget row consumed by the $\RealTailAgreementSealUp$ chapter \autoref{ch:concrete-instances-realtailagreementseal-namecert}. A paired agreement consumer may read this predecessor before forming its paired window row, but it receives no unbounded stream selector, independent budget oracle, quotient stream, selected limit, host convergence proof, or ambient completeness row from the fusion packet.
\end{theorem}
\begin{proof}
Read the public export packet. Its window and budget side is the finite route from the precision request $Q$ through the source row $X$, selected windows $W$, dyadic ledger $D$, tail witnesses $T$, and shared threshold $M$.

Use the bridged consumer packet to place this finite route before any completion-facing read. The consumer cannot reach the later diagonal readback or seal row without first passing through the selected windows, dyadic ledger, tail witnesses, and shared threshold.

The paired agreement seal consumes paired windows as its own local row. Therefore the fusion route is only the predecessor budget surface for that row: it supplies the finite window and threshold discipline that the seal duplicates into a paired-window read, while all non-escape clauses of the fusion packet remain available.
\end{proof}

\begin{theorem}[Regular Cauchy tail fusion real tail-agreement handoff]
\label{thm:regular-cauchy-tail-fusion-real-tail-agreement-handoff}
Any $\RealUp$ or $\CompletionUp$ consumer passing from $\RegularCauchyTailFusionUp$ to $\RealTailAgreementSealUp$ factors first through the fusion public export packet of \autoref{thm:regular-cauchy-tail-fusion-public-export-packet}, then through the bridged and mature consumer surfaces of \autoref{thm:regular-cauchy-tail-fusion-bridged-consumer-packet} and \autoref{thm:regular-cauchy-tail-fusion-mature-consumer-surface}, and only then through the paired agreement seal of \autoref{ch:concrete-instances-realtailagreementseal-namecert}. This handoff introduces no quotient stream, selected limit, host convergence row, ambient completeness row, hidden tail oracle, or independent equality route.
\end{theorem}
\begin{proof}
First expose the fusion packet publicly. By \autoref{thm:regular-cauchy-tail-fusion-public-export-packet}, the consumer can read only the finite rows $Q,X,W,D,T,M,R,L,H,C,P,N$ at the fusion boundary.

Next apply the bridged consumer packet and the mature consumer surface. These results force the completion-facing read through the shared-threshold row, the diagonal readback, and the $\RealUp$ seal route before it can be treated as a mature consumer surface.

Finally pass to the paired agreement seal named in \autoref{ch:concrete-instances-realtailagreementseal-namecert}. That chapter receives the cofinal-tail route as its predecessor and packages the paired agreement rows locally, so the transition remains a factorization through displayed packets rather than an appeal to quotient streams, selected limits, host convergence, ambient completeness, hidden tail oracles, or an independent equality route.
\end{proof}

\closureat{RegularCauchyTailFusionUp}{seedStr}
\closureat{RegularCauchyTailFusionUp}{obligationStr}
\closureat{RegularCauchyTailFusionUp}{scopedStr}
\closureat{RegularCauchyTailFusionUp}{publicStr}
\closureat{RegularCauchyTailFusionUp}{bridgedStr}[BEDC.Derived.RegularCauchyTailFusionUp.taste\_gate]
\closureat{RegularCauchyTailFusionUp}{matureStr}[BEDC.Derived.RegularCauchyTailFusionUp.taste\_gate]

\begin{closurestatus}{\RegularCauchyTailFusionUp}
  \constructivestory{A $\RegularCauchyTailFusionUp$ packet is generated from a precision request, $\RegSeqRatUp$ regular-family row, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerance ledger, finite tail witnesses, a $\RegularCauchyTailMeetUp$ shared-threshold row, diagonal readback, $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \leanchecked{BEDC.Derived.RegularCauchyTailFusionUp.taste\_gate}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:regular-cauchy-tail-fusion-obligation-surface}, \autoref{thm:regular-cauchy-tail-fusion-public-export-packet}, \autoref{thm:regular-cauchy-tail-fusion-bridged-consumer-packet}, \autoref{thm:regular-cauchy-tail-fusion-mature-consumer-surface}, \autoref{thm:regular-cauchy-tail-fusion-paired-agreement-source}, \autoref{thm:regular-cauchy-tail-fusion-paired-window-budget}, and \autoref{thm:regular-cauchy-tail-fusion-real-tail-agreement-handoff} bind the carrier, classifier, local naming row, cofinal-tail routing, downstream Real seal handoff, ledger non-escape, public export boundary, bridge-shaped consumer packet, mature consumer surface, paired agreement source, paired-window budget predecessor, and Real tail-agreement handoff for the finite cofinal tail-fusion packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close quotient stream equality, host real equality, external limit selection, unbounded diagonal streams, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{The paper closure axis is complete for this packet; Lean verification and bridge checking remain independent.}
\end{closurestatus}
