\chapter{A Concrete Naming Certificate for $\RealCompletionWitnessExtractorUp$}
\label{ch:concrete-instances-realcompletionwitnessextractor-namecert}
\origin{human}

The $\RealCompletionWitnessExtractorUp$ interface packages the diagonal-limit
witness surface used by the Real Completeness route. It starts from the
finite dyadic tolerance ledger, selected stream windows, regular-rational
readback rows, and RealUp seal rows already exposed by the Real and Completion
pipeline, then records the witness packet that a downstream completion
consumer may inspect. It is a finite NameCert packet; it is not a selected
host limit, quotient stream equality, or ambient completeness principle.

This extractor is the finite witness-facing consumer of
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-dyadicratcore-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert},
\autoref{ch:concrete-instances-real-namecert}, and
\autoref{ch:concrete-instances-cauchylimitseal-namecert}. Its substantive
dependency is the route from selected finite StreamName windows through
dyadic tolerance readback and regular-rational rows into the RealUp seal and
completion-facing handoff; it does not introduce a second completion
operator.

\begin{definition}[Real completion witness-extractor carrier]
\label{def:real-completion-witness-extractor-carrier}
A $\RealCompletionWitnessExtractorUp$ carrier is a finite $\BHist$ packet
$$
X=(D,W,M,Q,L,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the shared $\DyadicRatCoreUp$ tolerance ledger for the diagonal
regular-Cauchy route;
\item $W$ is the selected $\StreamNameUp$ window family used to read the
finite diagonal observations;
\item $M$ is the modulus schedule that chooses the displayed diagonal windows
and records the finite comparison budget for each requested precision;
\item $Q$ is the $\RegSeqRatUp$ readback row assembled from the selected
windows and dyadic tolerance rows;
\item $L$ is the $\RealUp$ seal row reached after the regular-rational
readback has passed through the displayed diagonal schedule;
\item $S$ is the completion-facing seal or handoff row consumed by Real
Completeness and Cauchy-limit consumers;
\item $H$ records componentwise $\hsame$ transports for $D,W,M,Q,L,S$ and the
local structural rows;
\item $C$ records the displayed $\Cont$ routes from tolerance requests through
the selected windows, modulus schedule, regular-rational readback, RealUp
seal, and completion-facing handoff;
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$, $\StreamNameUp$,
$\RegSeqRatUp$, $\RealUp$, $\CauchyLimitSealUp$, $\BHist$, $\hsame$, $\Cont$,
and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\RealCompletionWitnessExtractorUp}$ row.
\end{enumerate}
The carrier accepts exactly those packets whose completion-facing handoff is
read through the same finite dyadic ledger, selected windows, modulus schedule,
regular-rational witness, RealUp seal, transport rows, continuation rows, and
local certificate.
\end{definition}
\leandef{BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier}

\begin{theorem}[Real completion witness-extractor NameCert obligations]
\label{thm:real-completion-witness-extractor-namecert-obligations}
The local $\NameCert_{\RealCompletionWitnessExtractorUp}$ surface consists of
carrier admission for the packet $X=(D,W,M,Q,L,S,H,C,P,N)$, selected-window
admission through $D,W,M$, regular-rational readback through $Q$, RealUp seal
handoff through $L$, completion-facing handoff through $S$, componentwise
transport through $H$, displayed route replay through $C$, package provenance
through $P$, local naming through $N$, and non-escape for quotient streams,
selected host limits, host real equality, choice data, and ambient
completeness.
\end{theorem}
\begin{proof}
Project the carrier. The displayed packet lists the dyadic tolerance ledger,
selected window family, modulus schedule, regular-rational readback, RealUp
seal, completion-facing handoff, transports, routes, provenance, and local
certificate.

The selected-window obligation is read first. The route from $D$ through
$W$ and $M$ fixes the finite observations and the precision schedule before
any regular-rational witness can be exported.

The readback and seal obligations then factor through $Q,L,S$ in that order.
The rows $H$ and $C$ preserve this order componentwise, while $P$ and $N$
record the same finite packet as the local NameCert surface.

No coordinate of the carrier names quotient stream equality, a selected host
limit, host real equality, choice data, or ambient completeness. Those
conclusions therefore cannot be read from the witness extractor.
\end{proof}

\begin{theorem}[Real completion witness-extractor diagonal handoff]
\label{thm:real-completion-witness-extractor-diagonal-handoff}
Every Real Completeness diagonal-limit consumer of an accepted
$\RealCompletionWitnessExtractorUp$ packet receives exactly the finite handoff
$$
D,W,M,Q,L,S,H,C,P,N.
$$
The handoff presents the dyadic tolerance ledger, selected stream windows,
modulus schedule, regular-rational witness row, RealUp seal, completion-facing
seal, displayed $\hsame$ transports, displayed $\Cont$ routes, package
provenance, and local naming row. It supplies no independent completion
operator and no equality of quotient real names.
\end{theorem}
\begin{proof}
Start with the selected-window side of the carrier. The diagonal route can
inspect $D,W,M$ only as the displayed finite schedule for the requested
precision.

Next read the regular-rational witness $Q$. It is attached to the same
selected windows and dyadic ledger, so the consumer cannot choose a second
window family or a second modulus schedule.

Finally pass through the RealUp seal $L$ and the completion-facing handoff
$S$. The transport, continuation, provenance, and local naming rows keep the
handoff inside the same finite packet, and the carrier has no quotient-real
or ambient-completion coordinate.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_diagonal\_handoff}

\begin{theorem}[Real completion witness-extractor non-escape]
\label{thm:real-completion-witness-extractor-nonescape}
Every $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, or completion-facing
consumer of an accepted $\RealCompletionWitnessExtractorUp$ packet factors
through $D,W,M,Q,L,S,H,C,P,N$. The packet exports no quotient stream equality,
no selected host limit, no host real equality, no arbitrary choice of a
diagonal subsequence, and no ambient completeness theorem.
\end{theorem}
\begin{proof}
Use the NameCert obligations. They place every consumer-visible read on the
same carrier coordinates: dyadic tolerance ledger, selected windows, modulus
schedule, regular-rational witness, RealUp seal, completion-facing handoff,
transport rows, route rows, provenance, and local name.

For a stream or regular-rational consumer, the route stops at $W,M,Q$. For a
RealUp or completion-facing consumer, the route continues through $L$ and
$S$ after the same window and tolerance rows have already been fixed.

The excluded conclusions require rows not present in
\autoref{def:real-completion-witness-extractor-carrier}. Since $H,C,P,N$
only transport, replay, package, and name the displayed coordinates, no
consumer can escape the finite witness packet.
\end{proof}

\begin{theorem}[Real completion witness-extractor selected-window admission]
\label{thm:real-completion-witness-extractor-selected-window-admission}
For every accepted $\RealCompletionWitnessExtractorUp$ packet, the first
consumer-visible admission route exposes $D,W,M$ as the finite selected-window
route. The dyadic tolerance ledger $D$, the selected $\StreamNameUp$ windows
$W$, and the modulus schedule $M$ are fixed before any regular-rational
readback $Q$, RealUp seal $L$, or completion-facing handoff $S$ can be read.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-completion-witness-extractor-carrier}.
The rows $D,W,M$ are listed before the readback, seal, and handoff rows, and
they form the finite schedule on which the later reads are indexed.

Apply the local NameCert obligations. They bind carrier admission, selected
window exposure, and modulus exposure to the same displayed packet. Thus a
consumer cannot read $Q,L,S$ without first passing through the selected-window
route determined by $D,W,M$.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_selected\_window\_admission}

\begin{theorem}[Real completion witness-extractor regular readback route]
\label{thm:real-completion-witness-extractor-regular-readback-route}
Every $\RegSeqRatUp$ readback row $Q$ in an accepted
$\RealCompletionWitnessExtractorUp$ packet factors through the same
$D,W,M,H,C,P,N$ route. The readback may inspect the regular-rational witness
attached to the selected windows, but it cannot choose a second window family,
a second modulus schedule, or a second provenance and local naming route.
\end{theorem}
\begin{proof}
Start with the diagonal handoff theorem. It attaches $Q$ to the selected
window and modulus coordinates already fixed by $D,W,M$.

Next use componentwise transport, displayed continuation replay, package
provenance, and the local naming row. These are the rows $H,C,P,N$, so every
readback route for $Q$ remains inside the same transported and named packet.

The carrier contains no second copy of $W$ or $M$ and no alternate provenance
or naming coordinate. Therefore the $\RegSeqRatUp$ readback cannot select a
different window family or modulus schedule.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_regular\_readback\_route}

\begin{theorem}[Real completion witness-extractor seal handoff totality]
\label{thm:real-completion-witness-extractor-seal-handoff-totality}
Every RealUp read through $L$ and every completion-facing read through $S$ in
an accepted $\RealCompletionWitnessExtractorUp$ packet passes through the same
$D,W,M,Q,H,C,P,N$ route before the seal or handoff is consumed. These reads
export no quotient stream equality, host limit, choice datum, or ambient
completeness theorem.
\end{theorem}
\begin{proof}
Read the packet in carrier order. The selected tolerance, window, modulus, and
regular-rational rows $D,W,M,Q$ are fixed before the RealUp seal and the
completion-facing handoff are available to a consumer.

Transport and replay then keep $L$ and $S$ attached to the same packet through
$H$ and $C$, while $P$ and $N$ record the package provenance and local name.
Thus every seal or handoff read is routed through $D,W,M,Q,H,C,P,N$.

The forbidden outputs would require additional coordinates not present in the
carrier. Since the packet has no quotient equality row, no host-limit row, no
choice row, and no ambient-completeness row, the seal and handoff are total
only for the displayed finite route.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_seal\_handoff\_totality}

\begin{theorem}[Real completion witness-extractor transport totality]
\label{thm:real-completion-witness-extractor-transport-totality}
For every accepted $\RealCompletionWitnessExtractorUp$ carrier
$$
X=(D,W,M,Q,L,S,H,C,P,N),
$$
the transport and route rows $H,C$ are total for the selected-window, regular-readback, nonescape, and seal-handoff obligations. In particular, every read of $D,W,M,Q,L,S$ that is accepted by the local certificate replays through $H,C$ before it reaches package provenance $P$ and local naming $N$.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:real-completion-witness-extractor-selected-window-admission}. It fixes the selected-window route $D,W,M$ before any later witness coordinate is visible.

Apply \autoref{thm:real-completion-witness-extractor-regular-readback-route}. The readback row $Q$ remains attached to the same selected windows, modulus schedule, transport, route, provenance, and naming rows.

Now use \autoref{thm:real-completion-witness-extractor-seal-handoff-totality}. The RealUp seal $L$ and completion-facing handoff $S$ are consumed only after the selected-window and readback rows have passed through $H,C,P,N$.

Finally, \autoref{thm:real-completion-witness-extractor-nonescape} excludes quotient stream equality, selected host limits, host real equality, arbitrary diagonal choice, and ambient completeness. Thus the displayed $H,C$ rows exhaust transport and route replay for the accepted carrier.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_transport\_totality}

\begin{theorem}[Real completion witness-extractor provenance exhaustion]
\label{thm:real-completion-witness-extractor-provenance-exhaustion}
For every accepted $\RealCompletionWitnessExtractorUp$ carrier
$$
X=(D,W,M,Q,L,S,H,C,P,N),
$$
the provenance and naming rows $P,N$ account for all source chapters needed by the selected-window, regular-readback, nonescape, and seal-handoff route: $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyLimitSealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
Read the carrier definition. Its package row $P$ explicitly names the dyadic tolerance ledger, selected StreamName windows, regular-rational readback, RealUp seal, CauchyLimitSeal handoff, history, transport, route, package, and naming dependencies.

Use \autoref{thm:real-completion-witness-extractor-selected-window-admission} and \autoref{thm:real-completion-witness-extractor-regular-readback-route}. These theorems place $D,W,M,Q$ under the same $H,C,P,N$ packet.

Use \autoref{thm:real-completion-witness-extractor-seal-handoff-totality} together with \autoref{thm:real-completion-witness-extractor-nonescape}. The seal and handoff rows add no second provenance source and export none of the excluded completion or choice principles.

Therefore $P,N$ exhaust the provenance and local naming obligations for the displayed witness-extractor carrier.
\end{proof}

\begin{theorem}[Real completion witness-extractor obligation closure package]
\label{thm:real-completion-witness-extractor-obligation-closure-package}
The accepted carrier
$$
X=(D,W,M,Q,L,S,H,C,P,N)
$$
is an obligation-closed $\RealCompletionWitnessExtractorUp$ package for the present chapter: the selected-window route is fixed by $D,W,M$, the regular-readback route is fixed by $Q$, the Real and completion handoff route is fixed by $L,S$, transport and route replay are exhausted by $H,C$, and provenance plus local naming are exhausted by $P,N$.
\end{theorem}
\begin{proof}
Assemble the obligation rows from the preceding theorems. The selected-window theorem supplies the $D,W,M$ admission route, the regular-readback theorem supplies the $Q$ route, and the seal-handoff theorem supplies the $L,S$ route.

Apply \autoref{thm:real-completion-witness-extractor-transport-totality}. It accounts for componentwise transport and continuation replay across every displayed consumer read.

Apply \autoref{thm:real-completion-witness-extractor-provenance-exhaustion}. It accounts for package provenance and local naming over the Real and Completion dependency surface.

The nonescape theorem then removes the remaining forbidden exits: quotient stream equality, selected host limits, host real equality, arbitrary diagonal choice, ambient completeness, and un displayed completion operators. Hence the displayed carrier closes the chapter's transport, route replay, provenance, and naming obligations.
\end{proof}

\begin{theorem}[Real completion witness-extractor scoped route]
\label{thm:real-completion-witness-extractor-scoped-route}
Every accepted $\RealCompletionWitnessExtractorUp$ packet
$$
X=(D,W,M,Q,L,S,H,C,P,N)
$$
is scoped by the displayed finite witness route: the DyadicRatCore tolerance ledger $D$, StreamName windows $W$, RegSeqRat readback row $Q$, RealUp seal $L$, CauchyLimitSeal handoff $S$, componentwise $\hsame$ transport row $H$, displayed $\Cont$ route row $C$, package row $P$, and local $\NameCert$ row $N$. The route exports no quotient stream equality, host real equality, selected host limit, arbitrary diagonal choice, or ambient completeness principle.
\end{theorem}
\begin{proof}
First build the finite witness route. Apply \autoref{thm:real-completion-witness-extractor-selected-window-admission} to fix the dyadic tolerance ledger, selected StreamName windows, and modulus schedule. Apply \autoref{thm:real-completion-witness-extractor-regular-readback-route} to attach the RegSeqRat readback row to the same packet.

Next attach the completion-facing rows. Use \autoref{thm:real-completion-witness-extractor-seal-handoff-totality} for the RealUp seal and CauchyLimitSeal handoff, then use \autoref{thm:real-completion-witness-extractor-transport-totality} to route all displayed reads through componentwise $\hsame$ transport and displayed $\Cont$ continuation.

Finally, apply \autoref{thm:real-completion-witness-extractor-provenance-exhaustion} to account for $\Pkg$ provenance and local $\NameCert$ naming. The nonescape theorem, \autoref{thm:real-completion-witness-extractor-nonescape}, excludes quotient stream equality, host real equality, selected host limits, arbitrary diagonal choice, and ambient completeness. Therefore the accepted packet is scoped exactly by the displayed finite witness route.
\end{proof}

\begin{theorem}[Real completion witness-extractor kernel support scope]
\label{thm:real-completion-witness-extractor-kernel-support-scope}
The scoped route of \autoref{thm:real-completion-witness-extractor-scoped-route} depends only on the named sibling chapters $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\CauchyLimitSealUp$, together with the BEDC kernel rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. No further completion carrier, quotient principle, host equality row, selected-limit operator, diagonal-choice operator, or ambient-completeness row is part of the support.
\end{theorem}
\begin{proof}
Project the carrier

$$
X=(D,W,M,Q,L,S,H,C,P,N).
$$

The first five witness rows are the displayed sibling-chapter rows, while $H,C,P,N$ are the displayed kernel transport, route, package, and naming rows attached to the same packet.

Apply \autoref{thm:real-completion-witness-extractor-scoped-route}. It already factors every accepted read through the selected-window route, regular-readback route, seal-handoff route, componentwise transport, displayed continuation, provenance, and local naming rows.

The support list is exhausted by \autoref{thm:real-completion-witness-extractor-provenance-exhaustion}. The excluded carriers and principles are absent by \autoref{thm:real-completion-witness-extractor-nonescape}, so the scoped route has exactly the stated kernel support.
\end{proof}

\begin{theorem}[Real completion witness-extractor standard bridge surface]
\label{thm:real-completion-witness-extractor-standard-bridge-surface}
For every accepted $\RealCompletionWitnessExtractorUp$ packet
$$
X=(D,W,M,Q,L,S,H,C,P,N),
$$
the finite rows $D,W,M,Q,L,S,H,C,P,N$ form the paper bridge surface from the BEDC witness extractor to the standard diagonal-witness reading. Every standard consumer read factors through the checked diagonal handoff, the selected-window admission route, the regular-readback route, the seal-handoff totality row, and the transport totality rows. No quotient stream equality, host limit, choice datum, or ambient completeness row is exported by this bridge surface.
\end{theorem}
\begin{proof}
Start with \autoref{thm:real-completion-witness-extractor-diagonal-handoff}. It supplies the checked handoff from the displayed BEDC packet to the diagonal-witness reading while keeping the same carrier coordinates $D,W,M,Q,L,S,H,C,P,N$.

Next compose the route witnesses. Apply \autoref{thm:real-completion-witness-extractor-selected-window-admission} for $D,W,M$, then apply \autoref{thm:real-completion-witness-extractor-regular-readback-route} for $Q$. These two rows place each standard read over the selected dyadic windows and the displayed regular readback coordinate.

Now attach the completion-facing handoff. Apply \autoref{thm:real-completion-witness-extractor-seal-handoff-totality} for $L,S$, and apply \autoref{thm:real-completion-witness-extractor-transport-totality} for $H,C$. Thus the consumer route is carried only by the displayed seal, handoff, transport, and continuation rows.

Finally, the nonescape and support theorems exclude the remaining exits. Quotient stream equality, host limits, choice data, and ambient completeness do not occur among the exported rows, so the displayed finite packet is exactly the paper bridge surface for the standard diagonal-witness reading.
\end{proof}

\begin{theorem}[Real completion witness-extractor finite-prefix stability handoff]
\label{thm:real-completion-witness-extractor-prefix-stability-handoff}
Every accepted $\RealCompletionWitnessExtractorUp$ packet whose selected-window route is supplied by an accepted $\FinitePrefixLimitStabilityUp$ packet must read the finite prefix budget, $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance row, terminal $\RealUp$ seal, and extractor rows through one ordered finite route before any Completion-facing handoff is visible. Thus the extractor can consume finite-prefix stability only as the displayed handoff
$$
B \to W \to R \to D \to E \to X
$$
where $X=(D',W',M,Q,L,S,H,C,P,N)$ is the accepted extractor carrier, with $D',W',M$ reading the selected extractor window, $Q$ reading the regular-rational extractor row, and $L,S,H,C,P,N$ reading only the displayed seal, handoff, transport, continuation, provenance, and naming rows.
\end{theorem}
\begin{proof}
First read the supplying stability packet. Apply \autoref{thm:finite-prefix-limit-stability-real-handoff} to identify the finite handoff from the displayed prefix observation to the terminal $\RealUp$ seal, and apply \autoref{thm:finite-prefix-limit-stability-route-determinacy} to make that seal the unique consumer-facing end of the route.

Next pass the displayed route into the extractor. Apply \autoref{thm:real-completion-witness-extractor-selected-window-admission} to attach the extractor's selected window rows $D',W',M$ to the same finite route. Apply \autoref{thm:real-completion-witness-extractor-regular-readback-route} to read $Q$ only after that selected window has been admitted.

Finally attach the Completion-facing rows. Use \autoref{thm:real-completion-witness-extractor-seal-handoff-totality} to read $L,S$ as the visible Real and Completion handoff rows of the accepted extractor packet. Since the supplying stability packet has already fixed the order $B \to W \to R \to D \to E$, and the extractor theorems expose only $D',W',M,Q,L,S,H,C,P,N$, no Completion-facing handoff is visible before the finite-prefix stability route and the extractor rows have both been displayed.
\end{proof}

\closureat{RealCompletionWitnessExtractorUp}{seedStr}
\closureat{RealCompletionWitnessExtractorUp}{obligationStr}
\closureat{RealCompletionWitnessExtractorUp}{scopedStr}
\closureat{RealCompletionWitnessExtractorUp}{publicStr}[BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_diagonal\_handoff]
\closureat{RealCompletionWitnessExtractorUp}{bridgedStr}[BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_diagonal\_handoff]
\closureat{RealCompletionWitnessExtractorUp}{matureStr}[BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_diagonal\_handoff]

\begin{closurestatus}{\RealCompletionWitnessExtractorUp}
  \constructivestory{A $\RealCompletionWitnessExtractorUp$ packet is generated from a dyadic tolerance ledger, selected StreamNameUp windows, a modulus schedule, a RegSeqRat readback row, a RealUp seal row, a completion-facing handoff row, displayed hsame transports, Cont routes, package provenance, and a local NameCert row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:real-completion-witness-extractor-carrier}, \autoref{thm:real-completion-witness-extractor-standard-bridge-surface}, and \autoref{thm:real-completion-witness-extractor-prefix-stability-handoff} bind the finite diagonal witness-extractor packet, its standard bridge surface, and its finite-prefix stability handoff for Real and Completion consumers.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.RealCompletionWitnessExtractorUp.RealCompletionWitnessExtractorCarrier\_diagonal\_handoff}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close quotient stream equality, selected host limits, host real equality, arbitrary diagonal choice, ambient completeness, or bridge checking.}
  \upgradepath{The theory axis is mature; the remaining work is verification-axis bridge checking only.}
\end{closurestatus}
