\chapter{A Concrete Naming Certificate for $\DefiniteDescriptionBoundaryUp$}
\label{ch:concrete-instances-definite-description-boundary-namecert}
\origin{ai}

The $\DefiniteDescriptionBoundaryUp$ packet realizes the description-expansion boundary as a finite naming certificate. It treats a definite description as a row that may be consumed only after the packet exposes existence, uniqueness boundary, stability, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows. No description row becomes a denoting term by grammar alone.

The description row is consumed as a contextual class-like read of the kind isolated in \autoref{ch:concrete-instances-contextualclassreading-namecert}: the packet licenses inspection through displayed rows rather than turning syntax into an object. When existence or uniqueness fails, the failed read remains an externalized socket in the sense of \autoref{ch:concrete-instances-apophaticname-namecert}, so the boundary exports refusal data rather than a denoting term.

The description row is also read through the negative naming boundary of \autoref{ch:concrete-instances-negative-name-boundary-namecert} before any existence or uniqueness row is consumed. Definite descriptions refine that refusal surface by adding the displayed $D,E,U,S,H,C,P,N$ rows; they do not select a host denotation.

\begin{definition}[Definite-description boundary carrier]
\label{def:definite-description-boundary-carrier}
A $\DefiniteDescriptionBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(D,E,U,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the description row whose apparent denotation is being tested;
\item $E$ is the existence-witness row for a candidate history satisfying the description;
\item $U$ is the uniqueness-boundary row, recording either a displayed singleton boundary for the candidate or the explicit refusal to collapse multiple candidates;
\item $S$ is the stability row showing that permitted reads of the description survive the stated $\hsame$ and continuation routes;
\item $H$ is the componentwise $\hsame$ transport row for descriptions, witnesses, uniqueness boundaries, stability witnesses, replay routes, provenance, and local names;
\item $C$ is the $\Cont$ row that replays the finite route from the description row to the admitted witness and through the boundary check;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\BMark$, description rows, witness rows, uniqueness boundaries, stability rows, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\DefiniteDescriptionBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for a host-selected object, a choice function, a quotient class, proof-irrelevance, or an unrecorded semantic denotation.
\end{definition}
\leanchecked{BEDC.Derived.DefiniteDescriptionBoundaryUp.DefiniteDescriptionBoundaryTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Definite-description NameCert obligations]
\label{thm:definite-description-boundary-namecert-obligations}
The local $\NameCert_{\DefiniteDescriptionBoundaryUp}$ surface for \autoref{def:definite-description-boundary-carrier} consists exactly of carrier admission for $B=(D,E,U,S,H,C,P,N)$, existence exposure through $E$, uniqueness-boundary exposure through $U$, stability exposure through $S$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from the finite tuple in \autoref{def:definite-description-boundary-carrier}. The description row, witness row, boundary row, stability row, transport row, replay row, provenance row, and local name are all displayed coordinates of the same packet.

The naming obligations are exactly the rows a consumer can inspect before reading the description. Existence is read from $E$, the boundary between singleton and refusal is read from $U$, stability is read from $S$, and all transport, replay, provenance, and naming data are read through $H,C,P,N$.

No additional coordinate remains from which to select a host object or import an ambient denotation. The local $\NameCert$ surface is therefore exhausted by the listed rows.
\end{proof}

\begin{theorem}[Definite-description existence route]
\label{thm:definite-description-boundary-existence-route}
Let $B=(D,E,U,S,H,C,P,N)$ be an accepted $\DefiniteDescriptionBoundaryUp$ packet. Any public use of the description row $D$ as having a witness must factor through the displayed existence row $E$, replayed by $C$ and recorded by $P,N$.
\end{theorem}
\begin{proof}
Project the accepted packet to its description row $D$ and existence row $E$. The carrier contains no second existence coordinate and no host-level selection function.

The replay route $C$ is the only displayed path from the description row to the witness row, and $P,N$ bind that path to the packet provenance and local name. Thus a public existence read factors through $E,C,P,N$ rather than through an unstated denotation.
\end{proof}

\begin{theorem}[Definite-description uniqueness route]
\label{thm:definite-description-boundary-uniqueness-route}
Let $B=(D,E,U,S,H,C,P,N)$ be an accepted $\DefiniteDescriptionBoundaryUp$ packet. Any public use of $D$ as selecting at most one witness must factor through the uniqueness-boundary row $U$. If $U$ records refusal rather than singleton boundary, the packet exports only the refusal and does not export a denoting term.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. The only row that can certify uniqueness, or refuse it, is $U$.

When $U$ records a singleton boundary, the consumer reads that boundary through the same displayed replay and provenance rows $C,P,N$. When $U$ records refusal, the packet has no alternate coordinate from which a selected witness can be recovered.

Therefore uniqueness is not supplied by the grammar of the description. It is supplied only by the displayed boundary row, and failure of that row blocks denotation.
\end{proof}

\begin{theorem}[Definite-description stability route]
\label{thm:definite-description-boundary-stability-route}
Let $B=(D,E,U,S,H,C,P,N)$ be an accepted $\DefiniteDescriptionBoundaryUp$ packet. Any downstream read that transports the description across equivalent histories must use the stability row $S$ together with the componentwise $\hsame$ row $H$ and the replay row $C$.
\end{theorem}
\begin{proof}
The stability coordinate $S$ records the permitted movement of the description read under the packet's own transport discipline. The transport coordinate $H$ records the componentwise $\hsame$ data for the description, witness, boundary, stability, replay, provenance, and naming rows.

A downstream transport therefore has to pass through $S,H,C$. Package provenance and local naming remain the rows $P,N$, so the transported read is still the same finite certificate surface.

Since the carrier has no proof-irrelevance principle, quotient equality, or external equivalence oracle, no other stability route is available.
\end{proof}

\begin{theorem}[Definite-description ledger exhaustion]
\label{thm:definite-description-boundary-ledger-exhaustion}
Every accepted $\DefiniteDescriptionBoundaryUp$ packet exports description-expansion information only through the finite rows
$$
D,E,U,S,H,C,P,N.
$$
It exports no host-selected witness, no choice principle, no quotient representative, no proof-irrelevance shortcut, and no denoting term outside the displayed NameCert ledger.
\end{theorem}
\begin{proof}
Read the carrier as the tuple $B=(D,E,U,S,H,C,P,N)$. The definition lists every row available to a downstream consumer.

Existence, uniqueness boundary, and stability are exhausted by $E,U,S$. Transport, replay, provenance, and local naming are exhausted by $H,C,P,N$.

Thus the apparent denoting expression is expanded into its certificate rows. With no remaining coordinate for choice, quotient representative selection, proof irrelevance, or host denotation, the ledger boundary is exact.
\end{proof}

\closureat{DefiniteDescriptionBoundaryUp}{seedStr}

\begin{closurestatus}{\DefiniteDescriptionBoundaryUp}
  \constructivestory{A $\DefiniteDescriptionBoundaryUp$ packet is generated from a description row, an existence witness row, a uniqueness-boundary row, a stability row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:definite-description-boundary-carrier}, \autoref{thm:definite-description-boundary-namecert-obligations}, \autoref{thm:definite-description-boundary-existence-route}, \autoref{thm:definite-description-boundary-uniqueness-route}, \autoref{thm:definite-description-boundary-stability-route}, and \autoref{thm:definite-description-boundary-ledger-exhaustion} specify the finite description-expansion carrier and its ledger boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove Lean-side formal verification, a public definite-description operator, host choice, quotient representative selection, proof irrelevance, or a bridge to any external description calculus.}
  \upgradepath{Obligation closure requires checked carrier admission, existence-route exactness, uniqueness-boundary determinacy, stability transport, replay provenance, and ledger non-escape for the displayed packet.}
\end{closurestatus}
