\chapter{A Concrete Naming Certificate for $\RegularCauchyCofinalLimitUp$}
\label{ch:concrete-instances-regularcauchycofinallimit-namecert}
\origin{ai}

The cofinal-limit packet consumes \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert} through its finite window, regular-rational readback, and $\RealUp$ seal rows. Thus this chapter is not an isolated limit surface: it is the finite handoff across those sibling certificates that keeps the Real-and-Completion route visible inside one displayed carrier.

The $\RegularCauchyCofinalLimitUp$ surface records the finite cofinal-window route by which regular Cauchy data reaches a $\RealUp$ seal. It packages dyadic tolerance rows, StreamName windows, regular rational sequence rows, seal rows, transports, continuations, provenance, and local naming in one visible packet. The packet is a limit-facing certificate; it is not a quotient of streams, not host equality of completed reals, and not an invocation of ambient completeness.

\begin{definition}[RegularCauchyCofinalLimit carrier]
\label{def:regular-cauchy-cofinal-limit-carrier}
A $\RegularCauchyCofinalLimitUp$ carrier is a finite $\BHist$ packet
$$
K=(F,S,W,E,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite family row of $\RegSeqRatUp$ regular Cauchy names being compared by cofinal windows;
\item $S$ is the $\StreamNameUp$ schedule row naming the finite observations read from $F$;
\item $W$ is the cofinal-window ledger assigning each displayed precision request to a finite schedule window in $S$;
\item $E$ is the $\DyadicRatCoreUp$ tolerance and error ledger attached to those windows;
\item $R$ is the $\RegSeqRatUp$ readback row reached after the dyadic tolerance ledger has been fixed;
\item $L$ is the $\RealUp$ seal row reached from the displayed regular Cauchy readback;
\item $H$ records componentwise $\hsame$ transports for $F,S,W,E,R,L$ and the structural rows;
\item $C$ records the displayed $\Cont$ routes from $F$ through $S,W,E,R$ and then into $L$;
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and local certificate rows;
\item $N$ is the local $\NameCert_{\RegularCauchyCofinalLimitUp}$ row.
\end{enumerate}
The classifier for accepted carriers compares only the displayed rows $F,S,W,E,R,L,H,C,P,N$. It has no coordinate for quotient stream equality, host real equality, hidden limit selection, countable choice, or an ambient $\RealUp$ completeness principle.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyCofinalLimitUp.RegularCauchyCofinalLimitTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RegularCauchyCofinalLimit NameCert obligations]
\label{thm:regular-cauchy-cofinal-limit-namecert-obligations}
The local $\NameCert_{\RegularCauchyCofinalLimitUp}$ surface for \autoref{def:regular-cauchy-cofinal-limit-carrier} consists of five finite obligations:
\begin{enumerate}
\item carrier exposure, requiring every accepted object to display the packet $K=(F,S,W,E,R,L,H,C,P,N)$;
\item cofinal-window exactness, requiring every precision demand consumed by the limit route to pass through the displayed window ledger $W$ over the schedule row $S$;
\item dyadic tolerance readback, requiring the $\DyadicRatCoreUp$ ledger $E$ to be read only from the windows named by $W$ and the regular Cauchy family $F$;
\item seal factorization, requiring the $\RegSeqRatUp$ readback row $R$ and the $\RealUp$ seal row $L$ to be reached only through $F,S,W,E,H,C,P,N$;
\item non-escape, requiring the packet to export no quotient stream equality, host real equality, hidden limit selector, countable-choice row, or ambient $\RealUp$ completeness theorem.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is projection from the displayed tuple in \autoref{def:regular-cauchy-cofinal-limit-carrier}. The family, schedule, window, tolerance, readback, seal, transport, continuation, provenance, and local naming rows are all coordinates of one finite $\BHist$ packet.

Cofinal-window exactness reads the route $S,W$ before any tolerance row is consumed. Since $W$ is the only cofinal-window ledger in the carrier, a precision demand cannot be redirected to an unnamed tail or to a completed stream object.

Dyadic tolerance readback then uses $E$ together with $F,S,W$. The tolerance ledger is attached to the displayed windows and regular Cauchy rows, so it cannot be replaced by host real equality or a hidden completeness argument.

Finally, seal factorization and non-escape inspect the remaining rows $R,L,H,C,P,N$. They provide the only route into the $\RegSeqRatUp$ readback and $\RealUp$ seal, and none of the carrier coordinates names quotient stream equality, hidden limit selection, countable choice, or ambient $\RealUp$ completeness.
\end{proof}

\begin{theorem}[RegularCauchyCofinalLimit seal factorization]
\label{thm:regular-cauchy-cofinal-limit-seal-factorization}
Every $\RealUp$ seal read exported by an accepted $\RegularCauchyCofinalLimitUp$ packet factors through the finite route
$$
F,S,W,E,R,L,H,C,P,N.
$$
The seal consumer first reads the regular Cauchy family row, the StreamName schedule, the cofinal-window ledger, the dyadic tolerance ledger, and the regular rational readback row. Only then may it reach the displayed $\RealUp$ seal row $L$ through the componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\begin{proof}
Start with an accepted packet $K=(F,S,W,E,R,L,H,C,P,N)$. The carrier exposes no seal route except the displayed continuation chain through $C$.

The consumer first fixes the finite observation surface. It reads $F$ through $S$, then restricts the request to the cofinal windows named by $W$, and then reads the dyadic tolerance evidence in $E$ from those same windows.

The route to the seal is then forced through $R$ and $L$. The transports in $H$, continuations in $C$, provenance in $P$, and local certificate $N$ repack the same rows, so the seal read has no independent coordinate for a selected host limit or completed-stream equality.
\end{proof}

\begin{theorem}[RegularCauchyCofinalLimit non-escape]
\label{thm:regular-cauchy-cofinal-limit-nonescape}
An accepted $\RegularCauchyCofinalLimitUp$ packet can export only the displayed rows $F,S,W,E,R,L,H,C,P,N$ and their local classifier transports. A completion-facing consumer may use the cofinal-window ledger, dyadic tolerance ledger, regular rational readback, and $\RealUp$ seal exactly as named by the packet; it receives no quotient stream equality, no host real equality, no hidden limit selector, no choice-like tail, and no ambient $\RealUp$ completeness proof.
\end{theorem}
\begin{proof}
Project the finite carrier. The coordinate list contains rows for the regular Cauchy family, schedule, cofinal windows, dyadic tolerance ledger, readback, seal, transports, continuations, provenance, and local naming.

Apply the NameCert obligations from \autoref{thm:regular-cauchy-cofinal-limit-namecert-obligations}. They force every precision, tolerance, readback, and seal request through those coordinates and require non-escape for the excluded analytic objects.

Since quotient stream equality, host real equality, hidden limit selection, countable choice, and ambient completeness are not coordinates of $K$, neither $\hsame$ transport nor $\Cont$ replay can manufacture them as public exports.
\end{proof}

\begin{theorem}[RegularCauchyCofinalLimit public export]
\label{thm:regular-cauchy-cofinal-limit-public-export}
The carrier of \autoref{def:regular-cauchy-cofinal-limit-carrier}, the NameCert obligations of \autoref{thm:regular-cauchy-cofinal-limit-namecert-obligations}, the seal factorization of \autoref{thm:regular-cauchy-cofinal-limit-seal-factorization}, and the non-escape result of \autoref{thm:regular-cauchy-cofinal-limit-nonescape} assemble the public $\RegularCauchyCofinalLimitUp$ export consumed by $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ seal rows.

The export is exactly the finite cofinal-window packet $K=(F,S,W,E,R,L,H,C,P,N)$. It does not identify streams by quotient equality, does not compare host completed reals, does not select a hidden limit, and does not claim $\RealUp$ completeness outside the displayed seal route.
\end{theorem}
\begin{proof}
The carrier theorem fixes the public packet and the NameCert theorem lists its finite obligations. Together they expose the cofinal-window route, dyadic tolerance readback, regular rational handoff, seal row, transport, continuation, provenance, and local naming rows.

Seal factorization supplies the consumer route into $\RealUp$. It shows that any seal read must pass through $F,S,W,E,R,L,H,C,P,N$ in the displayed order.

Non-escape supplies the boundary condition for public use. Because the excluded quotient, host, selector, choice, and ambient-completeness objects are absent from the carrier, the public export is exactly the finite packet and no larger completion principle.
\end{proof}

\closureat{RegularCauchyCofinalLimitUp}{seedStr}

\begin{closurestatus}{\RegularCauchyCofinalLimitUp}
  \constructivestory{A $\RegularCauchyCofinalLimitUp$ packet is generated from regular Cauchy family rows, StreamName schedule rows, cofinal-window ledgers, DyadicRatCore tolerance rows, RegSeqRat readback rows, RealUp seal rows, componentwise transports, continuation routes, package provenance, and a local naming row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-cofinal-limit-carrier}, \autoref{thm:regular-cauchy-cofinal-limit-namecert-obligations}, \autoref{thm:regular-cauchy-cofinal-limit-seal-factorization}, \autoref{thm:regular-cauchy-cofinal-limit-nonescape}, and \autoref{thm:regular-cauchy-cofinal-limit-public-export} bind the finite cofinal-window route from regular Cauchy data to RealUp seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, quotient equality of streams, host real equality, hidden limit selection, countable choice, ambient RealUp completeness, or a public standard bridge.}
  \upgradepath{Scoped closure requires Lean encoding of the displayed carrier and checked theorems for cofinal-window exactness, dyadic tolerance readback, RegSeqRat handoff, RealUp seal factorization, and non-escape.}
\end{closurestatus}
