\chapter{A Concrete Naming Certificate for $\AxisNatReplacementRefusalUp$}
\label{ch:concrete-instances-axisnat-replacement-refusal-namecert}
\origin{ai}

The $\AxisNatReplacementRefusalUp$ surface packages the AxisZeckendorf boundary that $\AxisNatUp$ and $\NatUp$ remain distinct public interfaces. It records the AxisNat rows, the Nat rows, the unary-direction bridge rows, the checked cannot-claim rows, and the refusal ledger as finite data; it exports no kernel replacement of $\NatUp$ by $\AxisNatUp$.

Its composite dependencies are the $\AxisNatUp$ interface of \autoref{ch:concrete-instances-axisnat-namecert}, the $\NatUp$ interface of \autoref{ch:concrete-instances-nat-namecert}, the $\UnaryDirectionBridgeUp$ boundary of \autoref{ch:concrete-instances-unarydirectionbridge-namecert}, and the $\AxisZeckendorfCannotClaimUp$ refusal row of \autoref{ch:concrete-instances-axiszeckendorfcannotclaim-namecert}, joined into one finite non-replacement packet.

The refusal packet reads the AxisNat row from \autoref{ch:concrete-instances-axisnat-namecert}, the Nat row from \autoref{ch:concrete-instances-nat-namecert}, the bridge row from \autoref{ch:concrete-instances-unarydirectionbridge-namecert}, and the cannot-claim refusal row from \autoref{ch:concrete-instances-axiszeckendorfcannotclaim-namecert}. The local row $B$ permits only the unary-direction comparison, and $K$ records refusal of replacement rather than an isomorphism, kernel rewrite, or host equality between the two interfaces.

\begin{definition}[AxisNat replacement-refusal carrier]
\label{def:axisnat-replacement-refusal-carrier}
An $\AxisNatReplacementRefusalUp$ carrier is a finite $\BHist$ packet
$$
Q=(A,N,B,K,H,C,P,L)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $A$ is the $\AxisNatUp$ interface row, including the finite axis-origin, successor-spine, and AxisZeckendorf-facing readback rows;
\item $N$ is the $\NatUp$ interface row, including the finite zero, successor, induction, and standard Nat naming rows;
\item $B$ is the $\UnaryDirectionBridgeUp$ row through which an admitted consumer may compare unary direction data without collapsing either interface into the other;
\item $K$ is the checked cannot-claim row for the statement that $\AxisNatUp$ does not replace $\NatUp$, together with the kernel-distinctness and bridge-dependence rows cited by the AxisZeckendorf registry;
\item $H$ records displayed $\hsame$ transports for the AxisNat row, Nat row, bridge row, cannot-claim row, continuation row, provenance row, and local naming row;
\item $C$ records the displayed $\Cont$ routes by which consumers may replay the AxisNat read, the Nat read, the bridge read, and the refusal read;
\item $P$ is the $\Pkg$ provenance over $\AxisNatUp$, $\NatUp$, $\UnaryDirectionBridgeUp$, $\AxisZeckendorfCannotClaimUp$, $\BHist$, $\hsame$, $\Cont$, and the source $\NameCert$ rows;
\item $L$ is the local $\NameCert_{\AxisNatReplacementRefusalUp}$ row.
\end{enumerate}
The carrier has no coordinate for an isomorphism, a kernel rewrite, a definitional equality, a Nat induction transfer into AxisNat, an AxisNat successor transfer into Nat, or a global replacement principle.
\end{definition}
\leanchecked{BEDC.Derived.AxisNatReplacementRefusalUp.AxisNatReplacementRefusalTasteGate\_single\_carrier\_alignment}

\begin{theorem}[AxisNat replacement-refusal NameCert obligations]
\label{thm:axisnat-replacement-refusal-namecert-obligations}
The local $\NameCert_{\AxisNatReplacementRefusalUp}$ surface for \autoref{def:axisnat-replacement-refusal-carrier} consists exactly of six finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $Q=(A,N,B,K,H,C,P,L)$;
\item AxisNat interface exposure through the row $A$;
\item Nat interface exposure through the row $N$;
\item bridge-bounded comparison through the $\UnaryDirectionBridgeUp$ row $B$;
\item checked refusal coverage through the cannot-claim row $K$;
\item transport, continuation, provenance, and local naming exactness through $H,C,P,L$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:axisnat-replacement-refusal-carrier}. The packet has exactly the displayed AxisNat, Nat, bridge, refusal, transport, continuation, provenance, and naming rows.

The interface obligations are read separately from $A$ and $N$. The AxisNat row supplies AxisZeckendorf-facing unary data, while the Nat row supplies the standard Nat naming surface; neither row is consumed as the other.

Bridge-bounded comparison is the row $B$. It permits only the displayed unary-direction comparison and does not create an isomorphism, definitional equality, or kernel rewrite between the two interfaces.

The refusal row is $K$, backed by the cannot-claim registry and the kernel-distinctness boundary. The remaining rows $H,C,P,L$ preserve and replay this separation componentwise, so the NameCert surface is exhausted by the six obligations.
\end{proof}

\begin{theorem}[AxisNat replacement-refusal non-replacement boundary]
\label{thm:axisnat-replacement-refusal-nonreplacement-boundary}
Every public read exported by an accepted $\AxisNatReplacementRefusalUp$ packet factors through $A,N,B,K,H,C,P,L$. In particular, no consumer can extract a kernel replacement of $\NatUp$ by $\AxisNatUp$, a replacement of $\AxisNatUp$ by $\NatUp$, an unbounded bridge, a transferred induction principle, a transferred successor rule, or a host equality between the two interfaces.
\end{theorem}
\begin{proof}
Inspect the packet coordinates. The public AxisNat data are confined to $A$, and the public Nat data are confined to $N$.

The bridge coordinate $B$ is the only comparison route. Since it is a $\UnaryDirectionBridgeUp$ row, its output is a bounded direction read, not a replacement principle for either interface.

The refusal coordinate $K$ records the cannot-claim boundary. Transport, continuation, provenance, and naming rows $H,C,P,L$ replay that same boundary and add no interface operation. Because the excluded replacement objects are absent from the carrier, no public read can export them.
\end{proof}

\begin{theorem}[AxisNat replacement-refusal vision realization]
\label{thm:axisnat-replacement-refusal-vision-realization}
The AxisZeckendorf cannot-claim boundary for the statement that $\AxisNatUp$ replaces $\NatUp$ is realized by the finite $\AxisNatReplacementRefusalUp$ packet of \autoref{def:axisnat-replacement-refusal-carrier}. The realization cites AxisNat rows, Nat rows, UnaryDirectionBridge rows, checked cannot-claim rows, displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row, while exporting no replacement of either interface by the other.
\end{theorem}
\begin{proof}
Start from the registry statement \autoref{thm:cannot-claim-axisNat-replaces-natUp-horizon}. It records that the AxisZeckendorf cluster does not assert replacement of $\NatUp$ by $\AxisNatUp$.

The carrier of \autoref{def:axisnat-replacement-refusal-carrier} turns that boundary into finite rows. The rows $A$ and $N$ keep the two interfaces separate, $B$ records the bounded unary-direction bridge, and $K$ records the checked refusal ledger.

Rows $H,C,P,L$ provide the admissible transport, continuation, package, and local naming surface. By \autoref{thm:axisnat-replacement-refusal-nonreplacement-boundary}, this realization cannot be read as a positive replacement bridge, so it concretizes the vision boundary as a finite refusal certificate.
\end{proof}

\closureat{AxisNatReplacementRefusalUp}{seedStr}

\begin{closurestatus}{\AxisNatReplacementRefusalUp}
  \constructivestory{An $\AxisNatReplacementRefusalUp$ packet is generated from AxisNat interface rows, Nat interface rows, UnaryDirectionBridge rows, checked cannot-claim rows, displayed hsame transports, continuation routes, package provenance, and a local NameCert row. It is composite over the $\AxisNatUp$, $\NatUp$, $\UnaryDirectionBridgeUp$, and cannot-claim ledger surfaces, bundling those existing boundaries into one refusal surface.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the carrier, NameCert obligations, non-replacement boundary, and AxisZeckendorf vision realization for finite AxisNat-to-Nat refusal packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close a replacement of NatUp by AxisNatUp, a replacement of AxisNatUp by NatUp, an interface isomorphism, kernel rewriting, transferred induction, transferred successor structure, or host equality.}
  \upgradepath{Obligation closure requires checked carrier coverage, bridge-bounded comparison, cannot-claim coverage, transport exactness, continuation exactness, and ledger non-escape for the displayed packet.}
\end{closurestatus}
