\begin{theorem}[Continuous function carrier parallel composite determinacy]
\label{thm:continuous-function-carrier-parallel-composite-determinacy}
For BHist histories $source,middle,target,f,g,fg,fg',mod_F,mod_G,mod_{FG},
mod_{FG}',cert_F,cert_G,cert,cert'$, suppose
$$
\begin{array}{l}
\mathsf{ContinuousFunctionCarrier}(source,f,middle,mod_F,cert_F),\\
\mathsf{ContinuousFunctionCarrier}(middle,g,target,mod_G,cert_G),\\
\mathsf{Cont}(f,g,fg),\quad \mathsf{Cont}(f,g,fg'),\\
\mathsf{Cont}(mod_F,mod_G,mod_{FG}),\quad
\mathsf{Cont}(mod_F,mod_G,mod_{FG}'),\\
\mathsf{Cont}(target,mod_{FG},cert),\quad
\mathsf{Cont}(target,mod_{FG}',cert')
\end{array}
$$
hold. Then the two exposed composites are both continuous function carriers
and their graph, modulus, and certificate histories are determined:
$$
\begin{array}{l}
\mathsf{ContinuousFunctionCarrier}(source,fg,target,mod_{FG},cert)\land\\
\mathsf{ContinuousFunctionCarrier}(source,fg',target,mod_{FG}',cert')\land\\
\hsame(fg,fg')\land\hsame(mod_{FG},mod_{FG}')\land\hsame(cert,cert').
\end{array}
$$
\end{theorem}
\begin{proof}
First compose through the first visible ledger. The two given base carriers,
together with $\mathsf{Cont}(f,g,fg)$, $\mathsf{Cont}(mod_F,mod_G,mod_{FG})$,
and $\mathsf{Cont}(target,mod_{FG},cert)$, satisfy the hypotheses of
Theorem~\ref{thm:continuous-function-carrier-comp-closed}. This gives
$\mathsf{ContinuousFunctionCarrier}(source,fg,target,mod_{FG},cert)$.

The second displayed ledger has the same two base carriers. Applying the same
composition theorem to $\mathsf{Cont}(f,g,fg')$,
$\mathsf{Cont}(mod_F,mod_G,mod_{FG}')$, and
$\mathsf{Cont}(target,mod_{FG}',cert')$ gives
$\mathsf{ContinuousFunctionCarrier}(source,fg',target,mod_{FG}',cert')$.

Map determinacy is local to the shared graph rows. Continuation determinacy
for the two rows $\mathsf{Cont}(f,g,fg)$ and $\mathsf{Cont}(f,g,fg')$ gives
$\hsame(fg,fg')$; the same kernel determinacy applied to the two modulus rows
gives $\hsame(mod_{FG},mod_{FG}')$.

Finally compare the terminal certificate rows. They share the target history,
and the recovered modulus sameness transports the row
$\mathsf{Cont}(target,mod_{FG}',cert')$ back across
$\mathsf{Cont}(target,mod_{FG},cert)$, yielding $\hsame(cert,cert')$. These
five outputs are exactly the two composite carriers plus the three exposed
history-sameness conclusions.
\end{proof}
\leanchecked{BEDC.Derived.ContinuousUp.ContinuousFunctionCarrier\_parallel\_composite\_determinacy}

\begin{closurestatus}{\ContinuousFunctionCarrierUp}
  \constructivestory{The local continuous-function carrier is generated from two already carried graph-modulus rows by composing their map histories, their modulus histories, and the terminal certificate history through displayed continuation ledgers. The carrier accepts the two base continuous-function packages and a proposed composite only when the graph composite, modulus composite, and target-to-certificate continuation rows are present; a parallel composite without those ledgers has no admitted carrier row. The classifier for this seed is history-equality on the exposed composite graph, composite modulus, and composite certificate histories, so two parallel displays with the same inputs are recognized when continuation determinacy identifies those three outputs. The source is the pair of continuous-function carriers with their shared middle endpoint, the pattern is composition closure plus parallel determinacy, and the ledger records the two graph continuations, two modulus continuations, and two terminal certificate continuations. The five name-certificate obligations are local to this seed: the displayed composition theorem supplies inhabited composite rows, $\hsame$ supplies reflexive, symmetric, and transitive comparison of the exposed histories, and endpoint transport keeps transported composites inside the carrier. A package $h$ lies in the signature gap of a $\ContinuousFunctionCarrierUp$ token $p$ when the source-domain accepts the two base carriers and parallel continuation ledgers, the signature relation pairs the chosen composite with an answer carrier and evidence ledger, and the token-introduction relation names that answer as $p$; unfolded, both graph composites, both modulus composites, and both terminal certificates are history-same. The chapter registers this parallel-determinacy seed under $\ContinuousFunctionCarrierUp$; it contributes a local ledger for later $\ContinuousMapUp$ coherence, with no host function extensionality, public continuous-map bridge, or higher coherence package introduced here.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The chapter records the continuous function carrier ledger and its local composition-determinacy seed.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.ContinuousUp.ContinuousFunctionCarrier\_comp\_closed}
  \bridgestatus{none}
  \notclaimed{The chapter does not close the public continuous-map bridge or the full higher coherence package.}
  \upgradepath{Formalize the parallel composite determinacy theorem and bind the carrier ledger into the public ContinuousMapUp interface.}
\end{closurestatus}
