\chapter{A Concrete Naming Certificate for $\RegularCauchyProductBudgetUp$}
\label{ch:concrete-instances-regularcauchyproductbudget-namecert}
\origin{ai}

The $\RegularCauchyProductBudgetUp$ packet records the finite product-window ledger needed by Real-and-Completion multiplication consumers. It starts with two $\RegSeqRatUp$ source names, opens only displayed $\StreamNameUp$ windows, reads the product row through $\DyadicRatCoreUp$, accounts for the finite error split through $\FiniteErrorBudgetUp$, hands the result back as a $\RegSeqRatUp$ row, and seals the completion-facing read through $\RealUp$. The packet is a local product-budget certificate; it is not quotient stream equality, host real multiplication, an ambient completeness theorem, or a selected host limit.

\begin{definition}[RegularCauchyProductBudget carrier]
\label{def:regular-cauchy-product-budget-carrier}
A $\RegularCauchyProductBudgetUp$ carrier is a finite $\BHist$ packet
$$
B=(A,B,W_A,W_B,D_A,D_B,D,E,R,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two accepted $\RegSeqRatUp$ source packets whose product is being read;
\item $W_A$ and $W_B$ are the paired finite $\StreamNameUp$ windows opened from the two sources at the precision requested by the product route;
\item $D_A$ and $D_B$ are the dyadic endpoint and radius rows read from those two windows;
\item $D$ is the $\DyadicRatCoreUp$ product row computing the finite dyadic product observation from $D_A$ and $D_B$;
\item $E$ is the $\FiniteErrorBudgetUp$ product ledger assigning the source-window radii, product rounding allowance, and remaining readback budget;
\item $R$ is the $\RegSeqRatUp$ readback row produced from the dyadic product row and the finite budget ledger;
\item $S$ is the $\RealUp$ seal row through which a completion or real-algebra consumer reads the product candidate;
\item $H$ stores componentwise $\hsame$ transports for the source rows, windows, dyadic rows, budget ledger, readback, seal, package provenance, and local naming row;
\item $C$ stores the displayed $\Cont$ routes for source inspection, paired-window admission, dyadic product read, finite-budget exactness, regular readback, and RealUp seal handoff;
\item $P$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\FiniteErrorBudgetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RegularCauchyProductBudgetUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through the visible rows $A,B,W_A,W_B,D_A,D_B,D,E,R,S,H,C,P,N$.
\end{definition}

\begin{theorem}[RegularCauchyProductBudget window admission]
\label{thm:regular-cauchy-product-budget-window-admission}
Every accepted $\RegularCauchyProductBudgetUp$ carrier admits the paired source windows only through the two displayed $\RegSeqRatUp$ source rows and their $\StreamNameUp$ windows. More precisely, for
$$
B=(A,B,W_A,W_B,D_A,D_B,D,E,R,S,H,C,P,N),
$$
any product-window read first exposes the source packets $A$ and $B$, then the finite windows $W_A$ and $W_B$, and only then the dyadic source rows $D_A$ and $D_B$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-product-budget-carrier}. The source packets and paired windows are explicit coordinates, so the first available product-window data are $A,B,W_A,W_B$.

The dyadic source rows $D_A$ and $D_B$ are listed after the paired windows and are read through the same continuation route. Thus a consumer cannot obtain a dyadic product observation before the two finite windows have been admitted.

The remaining rows $D,E,R,S,H,C,P,N$ consume that displayed window data. Since the carrier has no coordinate for an unbounded stream observation or a quotient representative, all product-window admission is confined to the finite rows already named.
\end{proof}

\begin{theorem}[RegularCauchyProductBudget ledger exactness]
\label{thm:regular-cauchy-product-budget-ledger-exactness}
The finite product-budget ledger of an accepted $\RegularCauchyProductBudgetUp$ carrier is exactly the row $E$ applied to the dyadic source rows $D_A,D_B$ and the product row $D$. It accounts for the two source-window radii, the dyadic product rounding row, and the remaining readback allowance before any $\RegSeqRatUp$ product readback is exported.
\end{theorem}
\begin{proof}
Begin with the admitted windows from \autoref{thm:regular-cauchy-product-budget-window-admission}. They supply the two dyadic source rows $D_A$ and $D_B$ and therefore fix the inputs of the dyadic product row $D$.

Read the budget coordinate $E$. Its role in the carrier is the finite product ledger, so it binds the two source-window radii, the product rounding allowance, and the remaining readback budget to the same dyadic product observation.

The readback row $R$ is listed after $E$ and is routed through the same package provenance and continuation data. Hence no product readback can be exported without first passing through the displayed finite ledger.
\end{proof}

\begin{theorem}[RegularCauchyProductBudget RegSeqRat handoff]
\label{thm:regular-cauchy-product-budget-regseqrat-handoff}
Every $\RegSeqRatUp$ product readback exported by an accepted $\RegularCauchyProductBudgetUp$ carrier factors through the finite route
$$
A,B,W_A,W_B,D_A,D_B,D,E,R,H,C,P,N.
$$
The handoff preserves the same source rows, paired windows, dyadic product observation, product-budget ledger, $\hsame$ transports, $\Cont$ routes, package provenance, and local naming row.
\end{theorem}
\begin{proof}
Use window admission to identify the two source rows and their finite windows. This fixes $A,B,W_A,W_B,D_A,D_B$ as the only source data available to the product route.

Use ledger exactness to identify the dyadic product row and the finite budget ledger. The product readback must consume $D$ and $E$ before the row $R$ is available.

Finally inspect the structural rows $H,C,P,N$. They preserve the route componentwise under $\hsame$ and $\Cont$ transport and repack it as the local naming surface, so the exported $\RegSeqRatUp$ handoff is exactly the displayed finite route.
\end{proof}

\begin{theorem}[RegularCauchyProductBudget Real seal boundary]
\label{thm:regular-cauchy-product-budget-real-seal-boundary}
Every completion-facing or real-algebra read of an accepted $\RegularCauchyProductBudgetUp$ carrier reaches $\RealUp$ only through the seal row $S$ after the $\RegSeqRatUp$ handoff $R$ has been produced from the finite product-budget ledger. The carrier exports no host real multiplication, quotient stream equality, ambient completeness principle, hidden rounding oracle, or selected host limit.
\end{theorem}
\begin{proof}
Project the seal row $S$ from the carrier. It appears after the readback row $R$, so the real-facing route reaches the seal only after the finite product handoff has been assembled.

Apply \autoref{thm:regular-cauchy-product-budget-regseqrat-handoff}. The readback $R$ is already bound to the source rows, paired windows, dyadic product row, budget ledger, transports, routes, package provenance, and local naming row.

The carrier contains no coordinate for host multiplication, quotient stream equality, ambient completeness, hidden rounding, or selected host limits. Therefore the $\RealUp$ seal is a boundary around the displayed finite packet and exports no additional real object.
\end{proof}

\begin{theorem}[RegularCauchyProductBudget NameCert obligations]
\label{thm:regular-cauchy-product-budget-namecert-obligations}
The local $\NameCert_{\RegularCauchyProductBudgetUp}$ surface for \autoref{def:regular-cauchy-product-budget-carrier} consists of carrier admission, paired-window admission, dyadic product-row exactness, finite product-ledger exactness, $\RegSeqRatUp$ handoff exactness, $\RealUp$ seal boundary, componentwise $\hsame$ stability, displayed $\Cont$ route stability, $\Pkg$ provenance, and non-escape from host multiplication, quotient streams, ambient completeness, hidden rounding, and selected host limits.
\end{theorem}
\begin{proof}
Carrier admission is the tuple in \autoref{def:regular-cauchy-product-budget-carrier}. It lists the two sources, paired windows, dyadic source rows, dyadic product row, product ledger, readback, seal, transports, routes, provenance, and local naming row.

Paired-window admission is \autoref{thm:regular-cauchy-product-budget-window-admission}, and dyadic product-row exactness is the displayed use of $D_A,D_B,D$ inside the same carrier.

Finite product-ledger exactness is \autoref{thm:regular-cauchy-product-budget-ledger-exactness}. The $\RegSeqRatUp$ handoff exactness is \autoref{thm:regular-cauchy-product-budget-regseqrat-handoff}, and the $\RealUp$ seal boundary is \autoref{thm:regular-cauchy-product-budget-real-seal-boundary}.

The structural obligations are the roles of $H,C,P,N$. They keep transport, continuation, package provenance, and the local certificate on the same displayed packet. Since no forbidden external coordinate is present, non-escape follows by inspection of the carrier.
\end{proof}

\begin{theorem}[RegularCauchyProductBudget checked-obligation readiness]
\label{thm:regular-cauchy-product-budget-checked-obligation-readiness}
For the accepted $\RegularCauchyProductBudgetUp$ carrier
$$
B=(A,B,W_A,W_B,D_A,D_B,D,E,R,S,H,C,P,N),
$$
the carrier row, paired-window admission, finite product-ledger exactness, $\RegSeqRatUp$ handoff, $\RealUp$ seal boundary, componentwise $\hsame$ transport, displayed $\Cont$ route, $\Pkg$ provenance, and non-escape clauses form the single Lean-facing obligation surface for the product-budget packet.
\end{theorem}
\begin{proof}
First assemble the finite product route. Apply \autoref{thm:regular-cauchy-product-budget-window-admission} to expose the paired source windows, and apply \autoref{thm:regular-cauchy-product-budget-ledger-exactness} to bind the dyadic product row to the finite ledger $E$.

Next attach the consumer handoff boundary. Apply \autoref{thm:regular-cauchy-product-budget-regseqrat-handoff} for the $\RegSeqRatUp$ readback route, and apply \autoref{thm:regular-cauchy-product-budget-real-seal-boundary} for the $\RealUp$ seal boundary.

Finally repack the structural obligations. Apply \autoref{thm:regular-cauchy-product-budget-namecert-obligations}; its transport, route, provenance, local naming, and non-escape clauses name exactly the same packet. Hence the listed clauses form one obligation surface for downstream Lean formalization.
\end{proof}

\closureat{RegularCauchyProductBudgetUp}{seedStr}

\begin{closurestatus}{\RegularCauchyProductBudgetUp}
  \constructivestory{A $\RegularCauchyProductBudgetUp$ packet is generated from two $\RegSeqRatUp$ source rows, paired $\StreamNameUp$ windows, dyadic source rows, a $\DyadicRatCoreUp$ product row, a $\FiniteErrorBudgetUp$ ledger, a $\RegSeqRatUp$ readback, a $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-product-budget-carrier}, \autoref{thm:regular-cauchy-product-budget-window-admission}, \autoref{thm:regular-cauchy-product-budget-ledger-exactness}, \autoref{thm:regular-cauchy-product-budget-regseqrat-handoff}, \autoref{thm:regular-cauchy-product-budget-real-seal-boundary}, \autoref{thm:regular-cauchy-product-budget-namecert-obligations}, and \autoref{thm:regular-cauchy-product-budget-checked-obligation-readiness} bind the finite product-budget carrier and its local NameCert obligation surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, RealUp completeness, host real multiplication, quotient stream equality, a hidden rounding oracle, selected host limits, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, paired-window admission, dyadic product exactness, finite-ledger exactness, RegSeqRat handoff, RealUp seal boundary, transport stability, route stability, provenance, and non-escape for the same finite packet.}
\end{closurestatus}
