\chapter{A Concrete Naming Certificate for $\FableClockOrderUp$}
\label{ch:concrete-instances-fableclockorder-namecert}
\origin{human}

The $\FableClockOrderUp$ packet realizes the Empty-fable machine's local clock-order surface as finite certificate data. It records selector-ledger rows, local fable-clock ticks, adjacent step-order witnesses, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row. The packet is local to the displayed fable trace and has no coordinate for a synchronized clock shared across unrelated histories.

\begin{definition}[FableClockOrder carrier]
\label{def:fable-clock-order-carrier}
A $\FableClockOrderUp$ carrier is a finite $\BHist$ packet
$$
F=(H,S,T,E,W,L,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $H$ is the source $\Hist$ row whose Empty-fable trace is being read;
\item $S$ is the finite selector-ledger row beginning at $\emp$ and recording the enacted marks in order;
\item $T$ is the finite local fable-clock tick row, one tick for each displayed selector step;
\item $E$ records the adjacent $\Ext$ rows that move the ledger from one displayed history to the next;
\item $W$ records adjacent step-order witnesses connecting successive ledger positions and ticks;
\item $L$ records componentwise $\hsame$ transport for $H,S,T,E,W$ and the local naming row;
\item $C$ records the visible $\Cont$ routes by which consumers read the source history, selector ledger, local ticks, adjacent extensions, step-order witnesses, and local name;
\item $P$ is the $\Pkg$ provenance over $\Hist$, $\BHist$, $\Ext$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, selector-ledger rows, and local fable-clock ticks;
\item $N$ is the local $\NameCert_{\FableClockOrderUp}$ row.
\end{enumerate}
The carrier contains exactly these rows. It has no slot for an ambient host time, a clock shared by distinct histories, a comparison of unrelated fable traces, or a hidden chooser for missing selector steps.
\end{definition}

\begin{definition}[FableClockOrder classifier]
\label{def:fable-clock-order-classifier}
The $\FableClockOrderUp$ classifier compares two accepted packets only by the displayed tuple
$$
H,S,T,E,W,L,C,P,N.
$$
Two packet presentations agree when their source history rows, selector ledgers, local tick rows, adjacent extension rows, step-order witness rows, componentwise $\hsame$ transports, continuation routes, provenance rows, and local naming rows agree componentwise. The classifier does not compare ambient times, synchronize unrelated histories, or choose a missing branch outside the displayed selector ledger.
\end{definition}

\begin{theorem}[FableClockOrder NameCert obligations]
\label{thm:fable-clock-order-namecert-obligations}
The local $\NameCert_{\FableClockOrderUp}$ surface for \autoref{def:fable-clock-order-carrier} consists exactly of carrier admission for
$$
F=(H,S,T,E,W,L,C,P,N),
$$
classifier exactness for the rows of \autoref{def:fable-clock-order-classifier}, selector-ledger exposure, local tick exposure, adjacent step-order witness exposure, componentwise $\hsame$ stability, displayed $\Cont$ replay, $\Pkg$ provenance, and no-global-clock non-escape.
\end{theorem}
\begin{proof}
Carrier admission is projection from the finite tuple in \autoref{def:fable-clock-order-carrier}. The source history, selector ledger, local tick row, adjacent extension row, witness row, transport row, continuation row, provenance row, and local naming row are all displayed coordinates.

Classifier exactness is projection from \autoref{def:fable-clock-order-classifier}. Agreement is componentwise on the same rows, so the certificate has no second comparison surface.

The remaining obligations are carried by $L,C,P,N$. Componentwise transport preserves the displayed rows, continuation routes expose them to consumers, provenance names the package boundary, and the local naming row binds the packet without exporting an ambient clock.
\end{proof}

\begin{theorem}[FableClockOrder local step-order]
\label{thm:fable-clock-order-local-step-order}
For an accepted $\FableClockOrderUp$ packet
$$
F=(H,S,T,E,W,L,C,P,N),
$$
each displayed selector step in $S$ has a corresponding local tick in $T$ and an adjacent step-order witness in $W$. Consumer reads of this order factor through the same componentwise transport row $L$, continuation row $C$, provenance row $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The selector ledger $S$, local tick row $T$, adjacent extension row $E$, and witness row $W$ are coordinates of the same finite packet.

Read adjacent order through $E$ and $W$. The extension row records each displayed move between neighboring history positions, while the witness row attaches the corresponding local tick from $T$ to that move.

Transport and replay are then fixed by $L$ and $C$. Componentwise $\hsame$ movement preserves the rows being ordered, and the continuation route exposes only this local step-order surface.

Finally $P$ and $N$ bind the handoff to the named packet. Since the carrier has no coordinate for unrelated histories or ambient time, the order is local to the displayed selector ledger.
\end{proof}

\begin{theorem}[FableClockOrder no-global-clock non-escape]
\label{thm:fable-clock-order-no-global-clock}
Every accepted $\FableClockOrderUp$ packet exports only the finite local order carried by
$$
H,S,T,E,W,L,C,P,N.
$$
It does not export a synchronized clock across distinct histories, an ambient host-time parameter, a global ordering of all fable traces, or a hidden chooser for selector steps not recorded in $S$.
\end{theorem}
\begin{proof}
Inspect the carrier inventory. The only time-like row is the local tick row $T$, and it is paired with the selector ledger $S$ and adjacent witnesses $W$.

Use the local step-order theorem to delimit consumer access. Any read of order passes through the displayed transport, continuation, provenance, and naming rows attached to the same packet.

The excluded clock objects have no coordinate in the carrier and no clause in the classifier. Therefore no projection from an accepted packet can produce a synchronized clock, host-time parameter, global trace order, or hidden selector for steps outside $S$.
\end{proof}

\closureat{FableClockOrderUp}{seedStr}

\begin{closurestatus}{\FableClockOrderUp}
  \constructivestory{A $\FableClockOrderUp$ packet is generated from a source $\Hist$ row, a finite selector ledger, local fable-clock ticks, adjacent $\Ext$ and step-order witness rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:fable-clock-order-carrier}, \autoref{def:fable-clock-order-classifier}, \autoref{thm:fable-clock-order-namecert-obligations}, \autoref{thm:fable-clock-order-local-step-order}, and \autoref{thm:fable-clock-order-no-global-clock} bind local fable-clock order as a finite NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean verification, synchronized clocks across distinct histories, ambient host time, global ordering of all fable traces, or hidden selector choice.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier exactness, local step-order replay, no-global-clock non-escape, and NameCert row coverage for the same finite packet.}
\end{closurestatus}
