\chapter{A Concrete Naming Certificate for $\InscriptionAuditTraceUp$}
\label{ch:concrete-instances-inscriptionaudittrace-namecert}
\origin{ai}

The $\InscriptionAuditTraceUp$ surface realizes the audit trace of an inscription event as a finite NameCert packet. It combines the inscription-event source and named-record rows, the GAP-ledger residue rows, and the accepted-check consumer-budget rows into one public audit object. The packet records only the rows that a certificate, citation, theorem site, or $\ChapterTasteGate$ consumer may inspect.

The audit trace consumes \autoref{ch:concrete-instances-inscriptionevent-namecert} for the source, name, route, and check rows, \autoref{ch:concrete-instances-inscription-gap-ledger-namecert} for the residue row, and \autoref{ch:concrete-instances-inscription-acceptance-budget-namecert} for the accepted-check and downstream consumer-budget surface before it exposes its local public trace. The packet $S,M,R,K,U,Q,H,C,P,N$ is the finite join of those sibling surfaces: $S,M,R,K,U$ carry the event route and consumer boundary, $Q$ carries the GAP residue, and $H,C,P,N$ carry the transports, displayed continuations, provenance, and local certificate row. These sibling packets are the horizontal lattice route used by the carrier below, and no private agency predicate or host trace is exported by this join.

\begin{definition}[Inscription audit trace carrier]
\label{def:inscription-audit-trace-carrier}
An $\InscriptionAuditTraceUp$ carrier is a finite $\BHist$ packet
$$
A=(S,M,R,K,U,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the finite source-state row at which the inscription route begins;
\item $M$ is the named record, theorem site, citation row, or public interface admitted by the route;
\item $R$ is the displayed route witness from $S$ to $M$;
\item $K$ is the accepted-check row that admits $R$ as public record data for $M$;
\item $U$ is the downstream audit consumer row, naming the certificate, citation, theorem site, or $\ChapterTasteGate$ surface that may read the trace;
\item $Q$ is the GAP residue row left after the accepted route and consumer boundary are exposed;
\item $H$ records componentwise $\hsame$ transports for $S,M,R,K,U,Q$ together with package and local naming rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read the source, name, route, accepted check, consumer, and residue rows;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\InscriptionEventUp$, $\InscriptionGapLedgerUp$, $\InscriptionAcceptanceBudgetUp$, and $\ChapterTasteGate$ surfaces;
\item $N$ is the local $\NameCert_{\InscriptionAuditTraceUp}$ row.
\end{enumerate}
The carrier contains no private agency predicate, host process trace, unrecorded mutation, unchecked route, unbudgeted consumer right, or completed ontology of inscription beyond the displayed audit rows.
\end{definition}

\begin{theorem}[Inscription audit trace NameCert obligations]
\label{thm:inscription-audit-trace-namecert-obligations}
The local $\NameCert_{\InscriptionAuditTraceUp}$ surface for \autoref{def:inscription-audit-trace-carrier} consists of six finite obligations:
\begin{enumerate}
\item carrier exposure for $A=(S,M,R,K,U,Q,H,C,P,N)$;
\item source and named-record locality inherited from the $\InscriptionEventUp$ rows $S,M,R,K,U$;
\item accepted-check exactness inherited from the $\InscriptionAcceptanceBudgetUp$ row $K$;
\item GAP-residue exactness inherited from the $\InscriptionGapLedgerUp$ row $Q$;
\item consumer accountability through $U$ and the displayed $\Cont$ routes in $C$;
\item package and local naming stability through $H,P,N$ over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and $\ChapterTasteGate$ surfaces.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is projection from the displayed packet. The rows $S,M,R,K,U,Q,H,C,P,N$ are the complete inventory available to the audit trace.

The inscription-event rows supply the source, name, route, accepted-check, and consumer boundary. The acceptance-budget rows identify $K$ as the public check row and keep downstream use inside the consumer surface named by $U$.

The GAP-ledger rows identify $Q$ as the residue left at the accepted route boundary. The transport, continuation, package, and local naming rows then record how a $\ChapterTasteGate$ or certificate consumer reads the same finite packet without importing private agency or host process data.
\end{proof}

\begin{theorem}[Inscription audit trace route-check residue exhaustion]
\label{thm:inscription-audit-trace-route-check-residue-exhaustion}
For every accepted $\InscriptionAuditTraceUp$ carrier $A=(S,M,R,K,U,Q,H,C,P,N)$, the route-check-residue surface is exhausted by the rows $S,M,R,K,Q,H,C,P,N$. A public audit read first reaches the named record $M$ from the source row $S$ through the route witness $R$, then admits the route through the check row $K$, and then records the remaining GAP residue through $Q$.

No audit read may replace these rows by a host checker, hidden proof replay, private agency predicate, raw byte-change identity, or unrecorded route.
\end{theorem}
\begin{proof}
Project the carrier and isolate the route-facing rows $S,M,R,K,Q$. These are the only coordinates that connect source state, named record, accepted check, and residue.

Apply the inscription-event surface for the route from $S$ through $R$ to $M$. Apply the acceptance-budget surface to read $K$ as the accepted check, and apply the GAP-ledger surface to read $Q$ as the displayed residue.

The remaining rows $H,C,P,N$ preserve this same route under componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming. Since the carrier has no host checker, hidden replay, agency predicate, byte-change classifier, or unrecorded route coordinate, the route-check-residue surface is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[Inscription audit trace consumer non-escape]
\label{thm:inscription-audit-trace-consumer-nonescape}
Every downstream consumer of an accepted $\InscriptionAuditTraceUp$ carrier factors through the finite rows
$$
S,M,R,K,U,Q,H,C,P,N.
$$
The consumer may read the source state, named record, route witness, accepted check, intended consumer, GAP residue, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row. It cannot read private motives, host process traces, unchecked route data, unbudgeted consumer authority, or inscription data outside the finite audit trace.
\end{theorem}
\begin{proof}
Begin with the consumer row $U$ and the continuation row $C$. Together they name the public audit reader and the displayed route by which that reader enters the packet.

Use \autoref{thm:inscription-audit-trace-namecert-obligations}. The local NameCert surface binds the consumer to the inscription-event, GAP-ledger, and acceptance-budget rows visible in the same packet.

Use \autoref{thm:inscription-audit-trace-route-check-residue-exhaustion}. The consumer's route-check-residue read is already exhausted by $S,M,R,K,Q,H,C,P,N$. No additional carrier coordinate remains, so the consumer cannot escape to private motives, host traces, unchecked routes, unbudgeted authority, or outside inscription data.
\end{proof}

\begin{theorem}[Inscription audit trace TasteGate visible surface]
\label{thm:inscription-audit-trace-tastegate-visible-surface}
The $\ChapterTasteGate$-visible surface of an accepted $\InscriptionAuditTraceUp$ carrier is exactly the finite audit packet $A=(S,M,R,K,U,Q,H,C,P,N)$ together with its local $\NameCert_{\InscriptionAuditTraceUp}$ obligations. A gate may inspect the source, named record, route witness, accepted check, consumer row, GAP residue, transports, continuations, package provenance, and local naming row; it receives no hidden approval channel, private agency predicate, host trace, or row not named by the packet.
\end{theorem}
\leanchecked{BEDC.Derived.InscriptionAuditTraceUp.InscriptionAuditTraceTasteGate\_single\_carrier\_alignment}
\begin{proof}
The gate-facing input is the same carrier from \autoref{def:inscription-audit-trace-carrier}. The carrier lists the rows a $\ChapterTasteGate$ consumer may inspect and supplies no separate admission channel.

Apply \autoref{thm:inscription-audit-trace-namecert-obligations} to expose the local NameCert surface. It ties the inscription-event, GAP-ledger, and acceptance-budget readings to one finite audit packet.

Apply \autoref{thm:inscription-audit-trace-consumer-nonescape}. Since every downstream consumer, including a $\ChapterTasteGate$ consumer, factors through $S,M,R,K,U,Q,H,C,P,N$, the visible gate surface is exactly the displayed audit trace.
\end{proof}

\begin{theorem}[Inscription audit trace budget-ledger sibling route]
\label{thm:inscription-audit-trace-budget-ledger-sibling-route}
Every accepted $\InscriptionAuditTraceUp$ carrier first reads the inscription-event source and route rows through \autoref{ch:concrete-instances-inscriptionevent-namecert}, then reads the GAP residue row through \autoref{ch:concrete-instances-inscription-gap-ledger-namecert}, then reads the accepted-check budget row through \autoref{ch:concrete-instances-inscription-acceptance-budget-namecert}, and only then exposes the $\ChapterTasteGate$-visible row of \autoref{thm:inscription-audit-trace-tastegate-visible-surface}. The visible gate surface is therefore bound to the source, ledger, and budget siblings before any audit consumer may inspect it.
\end{theorem}
\begin{proof}
Project the accepted carrier $A=(S,M,R,K,U,Q,H,C,P,N)$ from \autoref{def:inscription-audit-trace-carrier}. The rows $S,M,R$ are the source, named-record, and route rows inherited from the inscription-event surface, and $U$ names the public audit consumer that eventually reaches the gate-facing read.

The row $Q$ is the GAP residue coordinate, so the route must pass through the sibling ledger surface before the audit trace can describe what remains at the accepted route boundary. The row $K$ is the accepted-check budget coordinate, so the same packet must also pass through the acceptance-budget sibling before exposing a consumer right.

The transport, continuation, provenance, and naming rows $H,C,P,N$ preserve this same route and do not add another inspection coordinate. Because the carrier has no hidden approval channel, private agency predicate, host trace, unchecked route, or unbudgeted consumer row, the $\ChapterTasteGate$ surface is reached only after the inscription-event, GAP-ledger, and acceptance-budget rows have been read.
\end{proof}

\closureat{InscriptionAuditTraceUp}{seedStr}
\closureat{InscriptionAuditTraceUp}{obligationStr}[BEDC.Derived.InscriptionAuditTraceUp.InscriptionAuditTraceTasteGate\_single\_carrier\_alignment]
\closureat{InscriptionAuditTraceUp}{scopedStr}[BEDC.Derived.InscriptionAuditTraceUp.InscriptionAuditTraceTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\InscriptionAuditTraceUp}
  \constructivestory{An $\InscriptionAuditTraceUp$ packet is generated from a source state, named record, route witness, accepted check, downstream audit consumer, GAP residue, componentwise hsame transports, displayed Cont routes, Pkg provenance, and a local NameCert row.}
  \leanchecked{BEDC.Derived.InscriptionAuditTraceUp.taste\_gate}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{def:inscription-audit-trace-carrier}, \autoref{thm:inscription-audit-trace-namecert-obligations}, \autoref{thm:inscription-audit-trace-route-check-residue-exhaustion}, \autoref{thm:inscription-audit-trace-consumer-nonescape}, \autoref{thm:inscription-audit-trace-tastegate-visible-surface}, and \autoref{thm:inscription-audit-trace-budget-ledger-sibling-route} bind the inscription audit trace as a finite public NameCert packet over inscription-event, GAP-ledger, acceptance-budget, and TasteGate-visible rows.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.InscriptionAuditTraceUp.InscriptionAuditTraceTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, private agency, host process traces, raw byte-change identity, unchecked route semantics, unbudgeted downstream consumption, or completed inscription ontology.}
  \upgradepath{Bridged closure requires a bridge row above the public audit-trace certificate surface, while preserving the carrier, route-check residue, consumer non-escape, sibling route, and TasteGate-visible packet.}
\end{closurestatus}
