\chapter{A Concrete Naming Certificate for $\AuditGateCompositionUp$}
\label{ch:concrete-instances-auditgatecomposition-namecert}
\origin{ai}

The $\AuditGateCompositionUp$ packet names a finite composition surface for
two audit gates that share a boundary row. It records the two gate rows, the
boundary-content rows seen by each gate, the two refusal-result rows, and the
composed refusal trace as one local $\NameCert$ packet. The packet is a
composition certificate: it does not create a new audit policy, weaken either
gate, or turn refusal into host-side permission.
The shared-boundary comparison and refusal rows are consumed from
\autoref{ch:concrete-instances-auditgateboundary-namecert} before the composed
trace is packaged.

\begin{definition}[Audit-gate composition carrier]
\label{def:audit-gate-composition-carrier}
An $\AuditGateCompositionUp$ carrier is a finite $\BHist$ packet
$$
C=(G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G_0$ and $G_1$ are the two audit-gate rows being composed;
\item $B_0$ and $B_1$ are the boundary-content rows read by the two gates,
with a displayed shared-boundary comparison between the exit surface of
$G_0$ and the entry surface of $G_1$;
\item $R_0$ and $R_1$ are the refusal-result rows produced by the two gates;
\item $Q$ is the composed refusal trace, recording that the downstream
consumer sees $R_0$ followed by $R_1$ through the shared boundary;
\item $H$ stores componentwise $\hsame$ transports for gate rows,
boundary-content rows, refusal-result rows, composed traces, provenance, and
the local name;
\item $K$ stores the $\Cont$ replay routes for reading $G_0$, reading
$G_1$, transporting the shared boundary, replaying both refusal rows, and
projecting the composed refusal trace;
\item $P$ stores $\Pkg$ provenance naming $\AuditGateBoundaryUp$,
$\OperationalMembraneUp$, $\AuditMembraneUp$, forbidden-ancestry audit rows,
paper-Lean drift rows, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
source packets;
\item $N$ is the local $\NameCert_{\AuditGateCompositionUp}$ row.
\end{enumerate}
The carrier exports only the displayed gate rows, boundary rows, refusal rows,
composed trace, transport, replay, provenance, and local naming rows.
\end{definition}

\begin{theorem}[Audit-gate composition NameCert obligations]
\label{thm:audit-gate-composition-namecert-obligations}
The local $\NameCert_{\AuditGateCompositionUp}$ surface for the carrier of
\autoref{def:audit-gate-composition-carrier} consists of six finite
obligations:
\begin{enumerate}
\item carrier admission for
$C=(G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N)$;
\item first-gate exposure for $G_0$, $B_0$, and $R_0$;
\item second-gate exposure for $G_1$, $B_1$, and $R_1$;
\item shared-boundary transport, requiring the exit content of the first gate
and the entry content of the second gate to be compared only through the
displayed $\hsame$ rows in $H$;
\item composed refusal replay, requiring $Q$ to be read through the displayed
$\Cont$ routes in $K$;
\item consumer non-escape, requiring the composed packet to export no hidden
permission row, no skipped gate, no host repair of a refused boundary, and no
audit result outside the displayed finite trace.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.BHistHendecaTupleNameCertUp.BHistHendecaTupleNameCertCarrierAdmission}
\begin{proof}
Carrier admission is projection from
\autoref{def:audit-gate-composition-carrier}. The two gate rows, two boundary
rows, two refusal rows, composed trace, transport, replay, provenance, and
local naming row are all displayed coordinates of the same finite packet.

The first and second gate obligations are read separately from the tuple.
Each gate keeps its own boundary-content row and refusal-result row, so
composition cannot identify the two gates or erase one of the two refusal
surfaces.

Shared-boundary transport is confined to $H$. The only comparison between
$B_0$ and $B_1$ is the displayed componentwise $\hsame$ comparison, and the
only public replay of the composed trace passes through $K$.

Finally $P$ and $N$ package the displayed rows as local NameCert data. Since
the carrier has no coordinate for a hidden permission row, skipped gate, host
repair, or unlisted audit result, the six obligations exhaust the public
surface of the composition packet.
\end{proof}

\begin{theorem}[Audit-gate composition boundary obligation]
\label{thm:audit-gate-composition-boundary-obligation}
For an accepted $\AuditGateCompositionUp$ carrier
$$
C=(G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N),
$$
the shared boundary rows $B_0$ and $B_1$ are the only boundary comparison surface. Every comparison between the exit content of $G_0$ and the entry content of $G_1$ must be read through the componentwise $\hsame$ transports in $H$ and the displayed $\Cont$ replay routes in $K$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:audit-gate-composition-carrier}. The only boundary-content coordinates are $B_0$ and $B_1$, and the only displayed comparison rows attached to them are the transports in $H$ and replay routes in $K$.

Now apply \autoref{thm:audit-gate-composition-namecert-obligations}. Its shared-boundary transport obligation reads the exit content of the first gate and the entry content of the second gate only through the displayed $\hsame$ rows.

Finally use \autoref{thm:audit-gate-composition-sibling-dependency-route}. The sibling route consumes the audit-gate boundary and membrane rows before $Q$ is public, so no ambient boundary object or host endpoint comparison can replace $B_0,B_1,H,K$.
\end{proof}

\begin{theorem}[Audit-gate composition membrane obligation]
\label{thm:audit-gate-composition-membrane-obligation}
For an accepted $\AuditGateCompositionUp$ carrier, the audit-membrane and operational-membrane provenance rows enter only through the provenance coordinate $P$. They cannot create a bypass row, host permission row, detached membrane policy, or second route around the displayed refusal and boundary packet.
\end{theorem}
\begin{proof}
Project the provenance coordinate in \autoref{def:audit-gate-composition-carrier}. The row $P$ names the $\AuditMembraneUp$ and $\OperationalMembraneUp$ sources together with the local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packets; no separate membrane carrier is exported.

Apply \autoref{thm:audit-gate-composition-namecert-obligations}. Its consumer non-escape obligation rules out hidden permission rows, skipped gates, host repair of refused boundaries, and unlisted audit results.

Then use \autoref{thm:audit-gate-composition-sibling-dependency-route}. Since sibling membrane rows are consumed only as named provenance before the composed refusal trace is packaged, they cannot generate a bypass or host-side permission surface.
\end{proof}

\begin{theorem}[Audit-gate composition operational obligation]
\label{thm:audit-gate-composition-operational-obligation}
For an accepted $\AuditGateCompositionUp$ carrier, the composed refusal trace $Q$ is replayed only after the gate rows $G_0,G_1$, boundary rows $B_0,B_1$, and refusal rows $R_0,R_1$ have been consumed. No consumer can read $Q$ as an operational result before those six source rows have entered the displayed route.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:audit-gate-composition-carrier}. The trace coordinate $Q$ is displayed only after the two gate rows, two boundary rows, and two refusal-result rows in the tuple.

Use \autoref{thm:audit-gate-composition-namecert-obligations}. Its first-gate, second-gate, shared-boundary transport, and composed-refusal replay obligations order the read through $G_0,G_1,B_0,B_1,R_0,R_1$ before $Q$ is projected.

Finally apply \autoref{thm:audit-gate-composition-sibling-dependency-route}. The dependency route consumes the sibling gate and membrane rows before the local packet exports the composed trace, so $Q$ has no premature operational read outside the displayed finite carrier.
\end{proof}

\begin{theorem}[Audit-gate composition sibling dependency route]
\label{thm:audit-gate-composition-sibling-dependency-route}
Every composed refusal route of an accepted $\AuditGateCompositionUp$ packet first consumes the gate rows of \autoref{ch:concrete-instances-auditgateboundary-namecert} and the membrane boundary surface of \autoref{ch:concrete-instances-operationalmembrane-namecert} before the local packet
$$
G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N
$$
can export the composed refusal trace. The exported trace is therefore a routed composition of sibling gate and membrane rows, not a standalone refusal oracle or a host-side repair of a refused boundary.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:audit-gate-composition-carrier}. The rows $G_0,G_1$ are the two gate rows, $B_0,B_1$ are the boundary-content rows, and $R_0,R_1,Q,H,K,P,N$ are the displayed refusal, transport, replay, provenance, and local naming rows.

Use \autoref{thm:audit-gate-composition-namecert-obligations}. Its first-gate and second-gate obligations expose the two gate rows before the composed trace is public, while its shared-boundary transport obligation forces the boundary comparison through the displayed rows in $H$ and $K$.

The provenance row $P$ names the sibling audit-gate boundary and operational membrane surfaces, and the local $\NameCert$ row $N$ packages them with the route. Thus the composed trace $Q$ can be exported only after those sibling gate and membrane rows have been consumed.
\end{proof}

\begin{theorem}[Audit-gate composition refusal transitivity]
\label{thm:audit-gate-composition-refusal-transitivity}
Let $C=(G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N)$ be an accepted
$\AuditGateCompositionUp$ carrier. If the first gate refuses the boundary
content recorded in $R_0$ and the second gate refuses the transported
boundary content recorded in $R_1$, then every public read of the composed
surface factors through the ordered refusal trace $Q$. The read cannot
replace either refusal by acceptance and cannot bypass the shared-boundary
transport.
\end{theorem}
\begin{proof}
Project the accepted packet to the two gate surfaces. The first refusal is
the row $R_0$ attached to $G_0$ and $B_0$, and the second refusal is the row
$R_1$ attached to $G_1$ and $B_1$.

Use the shared-boundary rows in $H$ to transport the exit content of the
first gate to the entry content of the second gate. This is the only bridge
between the two refusal reads, so the second refusal remains tied to the
transported boundary rather than to a new host-side boundary object.

Replay the ordered route through $K$. The route reads $R_0$, crosses the
displayed boundary comparison, reads $R_1$, and then exposes $Q$ as the
composed refusal trace.

Because $Q$ is built only from those displayed rows, a consumer has no
coordinate for replacing either refusal by acceptance or for bypassing the
shared-boundary transport.
\end{proof}

\begin{theorem}[Audit-gate composition consumer non-escape]
\label{thm:audit-gate-composition-consumer-nonescape}
Every consumer read of an accepted $\AuditGateCompositionUp$ packet factors
through
$$
G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N.
$$
The consumer receives a finite NameCert packet for composed gate surfaces,
shared boundary rows, refusal transitivity, and consumer non-escape. It
receives no general audit bypass, no external axiom-ancestry oracle, no
paper-Lean marker repair, no operational-membrane override, and no host
permission to treat a refused boundary as accepted.
\end{theorem}
\begin{proof}
Start from the carrier inventory. A consumer can project the two gate rows,
two boundary-content rows, two refusal-result rows, composed trace,
componentwise transport, replay route, provenance, and local name.

The composed read is then determined by
\autoref{thm:audit-gate-composition-namecert-obligations} and
\autoref{thm:audit-gate-composition-refusal-transitivity}. The first theorem
identifies the finite obligation surface, and the second theorem identifies
the ordered refusal route through the shared boundary.

The provenance row records the neighboring audit packets that the composition
may cite, but it does not import their host-side policy space. Since the
carrier has no bypass, marker-repair, membrane-override, or acceptance-after-
refusal coordinate, none of those objects can escape to the consumer.
\end{proof}

\begin{theorem}[Audit-gate composition root-source boundary]
\label{thm:audit-gate-composition-root-source-boundary}
Every root read of an accepted $\AuditGateCompositionUp$ packet exposes the
two audit-gate rows $G_0,G_1$, the two shared boundary rows $B_0,B_1$, and
the transport rows in $H$ before it may read the composed trace $Q$. The
root surface therefore has no direct route from either gate row to $Q$ that
bypasses the displayed shared-boundary packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:audit-gate-composition-carrier}. The
only rows preceding the composed trace are $G_0,G_1,B_0,B_1,R_0,R_1$ and
the componentwise transport data in $H$; no second source row is present.

The NameCert surface of
\autoref{thm:audit-gate-composition-namecert-obligations} binds those rows
as the displayed root source for the composition. Refusal transitivity then
reads the trace through the shared boundary, so any consumer that reaches
$Q$ has already exposed $G_0,G_1,B_0,B_1$ through the same finite packet.
\end{proof}

\begin{theorem}[Audit-gate composition composed-refusal inheritance]
\label{thm:audit-gate-composition-composed-refusal-inheritance}
Every composed trace of an accepted $\AuditGateCompositionUp$ packet inherits
both refusal rows $R_0$ and $R_1$ through the shared boundary. The trace $Q$
is not a new refusal object; it is the replay of $R_0$, the transported
boundary read, and $R_1$ inside the displayed carrier.
\end{theorem}
\begin{proof}
Start with the refusal rows in the carrier and the boundary rows named by
\autoref{thm:audit-gate-composition-root-source-boundary}. These are the
only displayed sources from which $Q$ can be read.

Use \autoref{thm:audit-gate-composition-refusal-transitivity}. It orders the
composition by the first refusal row, the shared-boundary transport, and the
second refusal row. Since consumer non-escape adds no host refusal channel,
the composed trace can inherit only $R_0$ and $R_1$ through that boundary.
\end{proof}

\begin{theorem}[Audit-gate composition downstream root package]
\label{thm:audit-gate-composition-downstream-unblock-package}
The downstream root package for $\AuditGateCompositionUp$ consists of
carrier exposure, shared-boundary transport, composed refusal replay, and
consumer non-escape. Concretely, every accepted packet exposes
$$
G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N
$$
as a finite NameCert surface for downstream audit-gate consumers, and exports
no bypass row, skipped-gate row, external ancestry oracle, or host acceptance
coordinate.
\end{theorem}
\begin{proof}
Carrier exposure is \autoref{def:audit-gate-composition-carrier}, and the
NameCert obligations are
\autoref{thm:audit-gate-composition-namecert-obligations}. Together they
display the two gate rows, two boundary rows, two refusal rows, trace row,
transports, replay route, provenance, and local name.

Shared-boundary transport is supplied by
\autoref{thm:audit-gate-composition-root-source-boundary}. Composed refusal
replay is supplied by
\autoref{thm:audit-gate-composition-composed-refusal-inheritance} and
\autoref{thm:audit-gate-composition-refusal-transitivity}.

Finally apply
\autoref{thm:audit-gate-composition-consumer-nonescape}. It removes every
consumer route to bypass rows, skipped-gate rows, external ancestry oracles,
and host acceptance coordinates, leaving exactly the displayed downstream
root package.
\end{proof}

\begin{theorem}[Audit-gate composition shared-boundary source]
\label{thm:audit-gate-composition-shared-boundary-source}
In every accepted $\AuditGateCompositionUp$ carrier
$$
C=(G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N),
$$
the shared boundary between $G_0$ and $G_1$ is read only through the displayed
$\BHist$ rows $B_0,B_1$, the componentwise $\hsame$ transports in $H$, and
the $\Cont$ replay route in $K$. No gate may substitute an ambient boundary
row, host boundary object, or unstated endpoint comparison for this displayed
source.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:audit-gate-composition-carrier}. The
only boundary-content rows in the packet are the displayed $\BHist$ rows
$B_0$ and $B_1$, and the only named rows surrounding them are the gate rows,
refusal rows, trace row, transports, continuations, provenance, and local
certificate.

Apply the NameCert obligations of
\autoref{thm:audit-gate-composition-namecert-obligations}. They bind the
shared-boundary comparison to the componentwise $\hsame$ data in $H$ and the
displayed $\Cont$ route in $K$, while $P$ and $N$ record the same finite
$\Pkg$ and $\NameCert$ provenance.

Finally use refusal transitivity and consumer non-escape,
\autoref{thm:audit-gate-composition-refusal-transitivity} and
\autoref{thm:audit-gate-composition-consumer-nonescape}. Since every composed
read passes through the ordered displayed trace and no ambient boundary
coordinate is exported, neither gate can replace $B_0,B_1,H,K$ by an external
source.
\end{proof}

\begin{theorem}[Audit-gate composition refusal-replay totality]
\label{thm:audit-gate-composition-refusal-replay-totality}
Every public composed-refusal read of an accepted $\AuditGateCompositionUp$
packet factors through $R_0$, the transported boundary row, $R_1$, and $Q$.
The rows $P$ and $N$ only package and name that same finite $\BHist$ route by
$\Pkg$ provenance and a local $\NameCert$ certificate; they do not add a
second refusal path.
\end{theorem}
\begin{proof}
Begin with the refusal-result rows $R_0$ and $R_1$ in the carrier. By
\autoref{thm:audit-gate-composition-namecert-obligations}, the first gate
exposes $R_0$, the second gate exposes $R_1$, and the shared boundary is
transported componentwise through $\hsame$ rows in $H$.

The replay theorem \autoref{thm:audit-gate-composition-refusal-transitivity}
then orders the public read. The route in $K$ reads $R_0$, crosses the
transported boundary row, reads $R_1$, and exposes $Q$ as the composed
refusal trace.

It remains to account for the packaging rows. The provenance row $P$ is a
$\Pkg$ record for the displayed audit, $\BHist$, $\hsame$, $\Cont$, and
$\NameCert$ sources, and $N$ is the local name for the same packet. By
consumer non-escape, these rows cannot be reread as a separate refusal
channel or as host permission.
\end{proof}

\begin{theorem}[Audit-gate composition consumer-permission exclusion]
\label{thm:audit-gate-composition-consumer-permission-exclusion}
After the ordered refusal trace of an accepted $\AuditGateCompositionUp$
carrier is consumed, the composed packet exports no permission row,
skipped-gate witness, policy weakening, or host acceptance coordinate. The
consumer remains inside the displayed $\BHist$ carrier, componentwise
$\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$
row.
\end{theorem}
\begin{proof}
Use the carrier inventory and the NameCert obligations first. They expose
only the two gate rows, boundary rows, refusal rows, composed trace,
componentwise transports, continuation routes, provenance, and local name.

Next apply refusal-replay totality together with
\autoref{thm:audit-gate-composition-refusal-transitivity}. A consumer reaches
the public result by reading $R_0$, the transported boundary row, $R_1$, and
$Q$ through the displayed $\Cont$ route in $K$.

Finally cite consumer non-escape,
\autoref{thm:audit-gate-composition-consumer-nonescape}. Because no
coordinate of $C$ is a permission row, skipped-gate witness, policy
weakening, or host acceptance coordinate, the $\Pkg$ row $P$ and
$\NameCert$ row $N$ can only package the refusal trace already displayed by
the packet.
\end{proof}

\begin{theorem}[Audit-gate composition root-boundary totality]
\label{thm:audit-gate-composition-root-boundary-totality}
Every root read of an accepted $\AuditGateCompositionUp$ packet exposes the
two audit-gate rows, both boundary-content rows, both refusal rows, the
shared-boundary transport, the replay row, the package row, and the local
NameCert row. The root packet has no public coordinate outside
$G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N$ for reinterpreting the composed refusal
trace as a host permission or as an external boundary oracle.
\end{theorem}
\begin{proof}
Project the accepted carrier of
\autoref{def:audit-gate-composition-carrier}. Its displayed coordinates are
exactly the two gate rows, two boundary rows, two refusal rows, composed
trace, transport row, replay row, package provenance, and local NameCert
row.

Apply the NameCert obligations of
\autoref{thm:audit-gate-composition-namecert-obligations}. They expose the
first gate, second gate, shared boundary, composed refusal replay, and
consumer non-escape obligations over the same tuple.

The refusal-replay totality theorem and the consumer-permission exclusion
theorem then exhaust the root read. Since the carrier contains no further
coordinate, the root boundary cannot export a permission row, host repair
row, or external boundary oracle.
\end{proof}

\begin{theorem}[Audit-gate composition operational membrane route]
\label{thm:audit-gate-composition-operational-membrane-route}
Every operational-membrane consumption route for an accepted
$\AuditGateCompositionUp$ packet is consumed only through the
$\AuditGateBoundaryUp$, $\OperationalMembraneUp$, and $\AuditMembraneUp$
surfaces named by the carrier provenance. The composed route cannot bypass
these named surfaces by reading an ambient membrane, a detached host policy,
or an unlisted audit row.
\end{theorem}
\begin{proof}
Read the provenance row $P$ in the carrier. It names
$\AuditGateBoundaryUp$, $\OperationalMembraneUp$, $\AuditMembraneUp$, the
forbidden-ancestry audit rows, paper-Lean drift rows, and the local
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ sources.

Use the sibling dependency route theorem
\autoref{thm:audit-gate-composition-sibling-dependency-route}. It forces the
composed refusal trace to consume the audit-gate boundary and operational
membrane rows before the local packet exports $Q$.

Finally apply consumer non-escape and consumer-permission exclusion. These
two boundaries leave no coordinate for an ambient membrane read, detached
host policy, or unlisted audit row, so the operational route remains inside
the three named membrane surfaces.
\end{proof}

\begin{theorem}[Audit-gate composition downstream ledger exhaustion]
\label{thm:audit-gate-composition-downstream-ledger-exhaustion}
Every downstream ledger read of an accepted $\AuditGateCompositionUp$ packet
exhausts the composed refusal trace $R_0 \longmapsto R_1 \longmapsto Q$.
The exported ledger contains no bypass, host repair, external ancestry
oracle, permission row, skipped-gate witness, or policy-weakening coordinate.
\end{theorem}
\begin{proof}
Start from refusal transitivity. It orders the two refusal rows through the
shared-boundary transport and states that every public read of the composed
surface factors through $Q$.

Refusal-replay totality then identifies the downstream ledger as the route
through $R_0$, the transported boundary row, $R_1$, and $Q$. The package and
local name rows only record that displayed route.

Consumer-permission exclusion supplies the final exhaustion step. A bypass,
host repair, external ancestry oracle, permission row, skipped-gate witness,
or policy-weakening coordinate would require an additional public row, but
the accepted carrier exports only the displayed finite ledger.
\end{proof}

\begin{theorem}[Audit-gate composition shared-boundary transitivity]
\label{thm:audit-gate-composition-shared-boundary-transitivity}
For an accepted $\AuditGateCompositionUp$ packet, comparison from the first
boundary-content row $B_0$ to the second boundary-content row $B_1$ composes
only through the displayed $\hsame$ row $H$, the displayed replay row $K$, and
the sibling $\AuditGateBoundaryUp$ and $\OperationalMembraneUp$ route named by
the provenance row $P$. No public comparison route may replace this boundary
movement by a host repair, detached membrane policy, or skipped audit-gate row.
\end{theorem}
\begin{proof}
Start with the carrier of
\autoref{def:audit-gate-composition-carrier}. Its only boundary-content
coordinates are $B_0$ and $B_1$, and the only public rows available for moving
between them are the componentwise transport row $H$, replay row $K$, package
row $P$, and local naming row $N$.

Apply the local obligations of
\autoref{thm:audit-gate-composition-namecert-obligations}. The shared-boundary
obligation ties the two boundary rows to the same accepted packet, while the
replay and provenance obligations keep that comparison inside the displayed
finite rows.

Use the sibling dependency route and the operational membrane route. They force
the comparison to pass through the named $\AuditGateBoundaryUp$ and
$\OperationalMembraneUp$ surfaces before the composition exports the trace
$Q$.

Finally apply consumer non-escape and downstream ledger exhaustion. Since the
public ledger has no host repair, detached policy, or skipped-gate coordinate,
the boundary comparison can only be the displayed $H,K,P,N$ route between
$B_0$ and $B_1$.
\end{proof}

\begin{theorem}[Audit-gate composition refusal-order determinacy]
\label{thm:audit-gate-composition-refusal-order-determinacy}
For accepted $\AuditGateCompositionUp$ packets preserving
$G_0,G_1,B_0,B_1,R_0,R_1,H,K,P,N$, the ordered refusal trace is the same row
$Q$. In particular, the exported trace cannot be reordered through host repair,
policy weakening, a skipped gate, or an alternate public ledger row.
\end{theorem}
\begin{proof}
Project the shared rows from the two accepted carriers. The two gate rows,
boundary rows, refusal rows, transport, replay, provenance, and local naming
rows agree by hypothesis.

Apply refusal transitivity. The composed refusal trace is read by first applying
$G_0$ to $B_0$, then transporting the boundary comparison, then applying $G_1$
to $B_1$. This fixes the order $R_0 \longmapsto R_1 \longmapsto Q$.

The shared-boundary transitivity row supplies the only route between $B_0$ and
$B_1$. Thus the second packet has no different comparison path from which a
second trace could be assembled.

Consumer-permission exclusion and downstream ledger exhaustion remove the last
alternatives. A reordered trace would require a host repair, policy weakening,
skipped-gate, or alternate ledger coordinate, and none is exported by the
accepted packet.
\end{proof}

\begin{theorem}[Audit-gate composition support-row exhaustion]
\label{thm:audit-gate-composition-support-row-exhaustion}
Every public support read of an accepted $\AuditGateCompositionUp$ packet is
exhausted by the transport and replay rows $H,K$, the provenance and local
naming rows $P,N$, the two gate rows $G_0,G_1$, the two boundary rows
$B_0,B_1$, and the two refusal rows $R_0,R_1$ together with their composed
trace $Q$. No support read exposes a host audit policy, parameter transport,
external boundary oracle, skipped-gate witness, or ledger row outside this
finite package.
\end{theorem}
\begin{proof}
Begin with the carrier inventory. The public support surface consists exactly
of $G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N$.

The NameCert obligations expose these rows in their required roles: the two
gate obligations, the shared boundary obligation, refusal replay, transport,
continuation, provenance, and local naming.

Next combine refusal transitivity, shared-boundary transitivity, and
refusal-order determinacy. These three rows account for the only boundary
movement and the only ordered refusal trace available to a public consumer.

Finally use consumer non-escape, consumer-permission exclusion, and downstream
ledger exhaustion. They rule out host audit policy, parameter transport,
external boundary oracles, skipped gates, and off-packet ledger rows, leaving
only the displayed support package.
\end{proof}

\begin{theorem}[Audit-gate composition public export]
\label{thm:audit-gate-composition-public-export}
The carrier, NameCert obligations, refusal transitivity, consumer nonescape,
consumer-permission exclusion, root-boundary totality, operational membrane
route, downstream ledger exhaustion, shared-boundary transitivity,
refusal-order determinacy, support-row exhaustion, and checked TasteGate row
form the public export surface for $\AuditGateCompositionUp$. A public consumer
of the accepted packet reads exactly the two audit-gate rows, two boundary rows,
two refusal rows, composed trace, transport and replay rows, provenance, local
name, and TasteGate witness; it receives no host audit policy, skipped gate,
external boundary oracle, permission override, or alternate downstream ledger.
\end{theorem}
\begin{proof}
First assemble the finite carrier and naming surface from
\autoref{def:audit-gate-composition-carrier} and
\autoref{thm:audit-gate-composition-namecert-obligations}. These rows expose
the packet coordinates and the local certificate consumed by any public read.

Next combine the route theorems: refusal transitivity, root-boundary totality,
the operational membrane route, downstream ledger exhaustion, shared-boundary
transitivity, refusal-order determinacy, and support-row exhaustion. Together
they give the only ordered path through $G_0,G_1,B_0,B_1,R_0,R_1,Q,H,K,P,N$.

Finally apply consumer nonescape, consumer-permission exclusion, and the checked
TasteGate row. These remove host policy, permission override, skipped gate, and
alternate-ledger exits, so the displayed packet is already the public export
surface.
\end{proof}

\closureat{AuditGateCompositionUp}{seedStr}
\closureat{AuditGateCompositionUp}{obligationStr}[BEDC.Derived.AuditGateCompositionUp.AuditGateCompositionTasteGate\_single\_carrier\_alignment]
\closureat{AuditGateCompositionUp}{scopedStr}[BEDC.Derived.AuditGateCompositionUp.AuditGateCompositionTasteGate\_single\_carrier\_alignment]
\closureat{AuditGateCompositionUp}{bridgedStr}[BEDC.Derived.AuditGateCompositionUp.AuditGateCompositionTasteGate\_single\_carrier\_alignment]
\closureat{AuditGateCompositionUp}{matureStr}[BEDC.Derived.AuditGateCompositionUp.AuditGateCompositionTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\AuditGateCompositionUp}
  \constructivestory{An $\AuditGateCompositionUp$ packet is generated from two audit-gate rows, two boundary-content rows, two refusal-result rows, a composed refusal trace, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:audit-gate-composition-carrier}, \autoref{thm:audit-gate-composition-namecert-obligations}, \autoref{thm:audit-gate-composition-refusal-transitivity}, \autoref{thm:audit-gate-composition-consumer-nonescape}, \autoref{thm:audit-gate-composition-consumer-permission-exclusion}, \autoref{thm:audit-gate-composition-root-boundary-totality}, \autoref{thm:audit-gate-composition-operational-membrane-route}, \autoref{thm:audit-gate-composition-downstream-ledger-exhaustion}, \autoref{thm:audit-gate-composition-shared-boundary-transitivity}, \autoref{thm:audit-gate-composition-refusal-order-determinacy}, \autoref{thm:audit-gate-composition-support-row-exhaustion}, \autoref{thm:audit-gate-composition-public-export}, and \leanchecked{BEDC.Derived.AuditGateCompositionUp.taste\_gate} bind the root boundary, membrane route, downstream refusal ledger, shared-boundary support rows, refusal-order determinacy, checked TasteGate instance, and public export surface of the finite audit-gate composition packet.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.AuditGateCompositionUp.AuditGateCompositionTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai-composite}
  \notclaimed{This chapter does not close audit-policy completeness, external ancestry search, marker repair, operational-membrane override, or a public standard bridge.}
  \upgradepath{No further paper-side closure upgrade is claimed; remaining work is formal bridge verification if a StdBridge theorem is later supplied.}
\end{closurestatus}
