\chapter{A Concrete Naming Certificate for $\BranchObstructionUp$}
\label{ch:concrete-instances-branchobstruction-namecert}
\origin{ai}

The $\BranchObstructionUp$ interface isolates the finite ledger row used when an analytic-continuation request leaves the displayed local source, overlap, operation, and output packet. It turns the branch-sensitive boundary of \autoref{def:branch-obstruction-schema} into a concrete $\BHist$ packet: a consumer can inspect where the request was recorded, which continuation socket supplied the local rows, and which routes preserve the ledger, but cannot extract a branch selector, quotient-of-germs equality, monodromy theorem, or new holomorphic output.

\begin{definition}[BranchObstruction carrier]
\label{def:branch-obstruction-carrier}
A $\BranchObstructionUp$ carrier is a finite $\BHist$ packet
$$
R=(S,B,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $S$ is an accepted $\AnalyticContinuationSocketUp$ row displaying the two $\HolomorphicUp$ source rows, overlap witness, operation row, output row, branch-obstruction ledger, componentwise transports, continuation routes, package provenance, and local naming row;
\item $B$ is the branch-obstruction ledger coordinate selected from $S$;
\item $H$ records componentwise $\hsame$ transport for $S$, $B$, the visible routes, the provenance row, and the local naming row;
\item $C$ records the visible $\Cont$ routes from the socket row into the selected ledger row and the local naming surface;
\item $P$ is the $\Pkg$ provenance over $\BranchObstructionUp$, $\AnalyticContinuationSocketUp$, $\HolomorphicUp$, $\AnalyticContinuationOperationUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\BranchObstructionUp}$ row.
\end{enumerate}
The carrier exports only the socket row, selected obstruction ledger, transport rows, continuation routes, package provenance, and local naming data. It contains no global analytic-continuation operator, branch selector, quotient of germs, monodromy invariant, or additional $\HolomorphicUp$ output row.
\end{definition}
\leanchecked{BEDC.Derived.BranchObstructionUp.BranchObstructionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[BranchObstruction NameCert obligations]
\label{thm:branch-obstruction-namecert-obligations}
For the carrier of \autoref{def:branch-obstruction-carrier}, the local $\NameCert_{\BranchObstructionUp}$ surface consists exactly of five finite obligations: carrier admission for $R=(S,B,H,C,P,N)$; socket compatibility, requiring $B$ to be the branch-obstruction coordinate displayed by the accepted $\AnalyticContinuationSocketUp$ row $S$; ledger exactness, requiring every branch-sensitive continuation request outside the local socket rows to be recorded in $B$; transport stability through $H$ and the visible routes in $C$; and non-escape, excluding branch selectors, quotient germs, monodromy theorems, global continuation principles, zero-location data, and new holomorphic outputs.
\end{theorem}
\begin{proof}
Carrier admission is the projection of the finite tuple in \autoref{def:branch-obstruction-carrier}. The rows $S,B,H,C,P,N$ display the socket, selected obstruction ledger, componentwise transport, routes, provenance, and local naming row.

Socket compatibility follows by reading $S$ before any obstruction row is inspected. The accepted socket already names the two source rows, overlap witness, operation row, output row, and branch-obstruction coordinate, so $B$ is a selected row of the displayed socket rather than an ambient analytic-continuation object.

Ledger exactness is inherited from the socket ledger. Requests that leave the source, overlap, operation, and output rows are assigned to $B$ as ledger data.

Transport stability is componentwise through $H$ and $C$. These rows replay the same socket and selected obstruction ledger under accepted $\hsame$ movement and visible continuation routes.

The non-escape clause is an inventory argument. Since the carrier has no coordinate for branch selection, quotient-of-germs equality, monodromy, global continuation, zero-location data, or another $\HolomorphicUp$ output, no local $\NameCert_{\BranchObstructionUp}$ projection can export one.
\end{proof}

\begin{theorem}[BranchObstruction ledger non-escape]
\label{thm:branch-obstruction-ledger-nonescape}
Every branch-sensitive read of an accepted $\BranchObstructionUp$ carrier factors through the finite rows
$$
S,B,H,C,P,N.
$$
If the read asks for continuation data not displayed by the accepted socket row $S$, the request remains in the selected ledger row $B$ and is not exported as a branch selector, quotient-of-germs equality, monodromy theorem, or new $\HolomorphicUp$ output.
\end{theorem}
\leanchecked{BEDC.Derived.BHistHexaSequenceNameCertUp.BHistHexaSequenceNameCertUp\_single\_carrier\_alignment}
\begin{proof}
Project the accepted carrier and apply \autoref{thm:branch-obstruction-namecert-obligations}. The only branch-sensitive coordinate exposed by the packet is the selected ledger row $B$.

For a read internal to the socket, apply the socket rows displayed by $S$. The consumer obtains only the source, overlap, operation, output, transport, route, provenance, and local naming data already present in the accepted $\AnalyticContinuationSocketUp$ packet.

For a read outside those rows, use the ledger exactness obligation. Such a request lands in $B$ as obstruction accounting and does not become a continuation witness.

Finally route the result through $H,C,P,N$. These rows preserve and name the same finite ledger surface, so no exported branch selector, quotient germ, monodromy theorem, or extra holomorphic output can appear.
\end{proof}

\begin{theorem}[BranchObstruction holomorphic handoff boundary]
\label{thm:branch-obstruction-holomorphic-handoff-boundary}
Every downstream $\HolomorphicUp$ consumer of an accepted $\BranchObstructionUp$ carrier receives holomorphic data only through the output row already displayed by the socket coordinate $S$. The selected obstruction ledger $B$ may accompany that handoff as boundary accounting, but it cannot create or certify an additional $\HolomorphicUp$ output row.
\end{theorem}
\begin{proof}
Read the socket coordinate $S$. Its holomorphic handoff has already passed through the accepted $\AnalyticContinuationSocketUp$ packet, where the output row is displayed as part of the local source-overlap-operation-output surface.

Read the selected obstruction row $B$ separately. By \autoref{thm:branch-obstruction-ledger-nonescape}, $B$ records requests outside that local surface as obstruction ledger data.

The transport and route rows $H$ and $C$ preserve this separation: socket output rows remain socket output rows, while obstruction requests remain ledger rows. The package and local naming rows $P,N$ bind the same separation to the $\BranchObstructionUp$ certificate, so the handoff cannot manufacture another $\HolomorphicUp$ output.
\end{proof}

\begin{theorem}[BranchObstruction holomorphic operation sibling route]
\label{thm:branch-obstruction-holomorphic-operation-sibling-route}
Every accepted $\BranchObstructionUp$ packet reads its socket row as a
consumer of the holomorphic source and output surface of
\autoref{ch:concrete-instances-holomorphic-namecert} and the operation row of
\autoref{ch:concrete-instances-analyticcontinuationoperation-namecert} before
the selected obstruction ledger $B$ is exported. The packet therefore exposes
the ledger only after the socket has fixed the $\HolomorphicUp$ source rows,
the continuation operation row, the output row, the displayed transports,
routes, provenance, and local naming data.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:branch-obstruction-carrier}. Its socket
coordinate $S$ is an accepted analytic-continuation socket row displaying the
two $\HolomorphicUp$ source rows, the operation row, the output row, the
branch-obstruction ledger, transports, routes, provenance, and local naming
row.

Apply \autoref{thm:branch-obstruction-namecert-obligations}. The socket
compatibility and ledger exactness clauses require $B$ to be selected from
that already displayed socket surface, so the sibling holomorphic and
operation rows are read before the obstruction ledger is exported.

Now use \autoref{thm:branch-obstruction-ledger-nonescape} and
\autoref{thm:branch-obstruction-holomorphic-handoff-boundary}. The ledger
remains boundary accounting, while downstream holomorphic consumers receive
only the source and output surface already displayed by $S$ together with the
operation row named in the same socket.
\end{proof}

\begin{theorem}[BranchObstruction monodromy non-export]
\label{thm:branch-obstruction-monodromy-nonexport}
An accepted $\BranchObstructionUp$ carrier may record a request for monodromy, branch selection, or quotient-of-germs comparison in the selected ledger row $B$. It does not export such a request as a monodromy theorem, branch selector, quotient equality, global continuation principle, zero-location datum, or holomorphic output beyond the socket row $S$.
\end{theorem}
\begin{proof}
Start from the carrier inventory of \autoref{def:branch-obstruction-carrier}. The displayed rows are exactly $S,B,H,C,P,N$, and none of them is a monodromy object, branch selector, quotient-germ representative, global continuation operator, zero-location row, or additional holomorphic output.

Apply \autoref{thm:branch-obstruction-ledger-nonescape} to any nonlocal continuation request. The request is recorded in $B$ and remains ledger data under the visible routes.

Apply \autoref{thm:branch-obstruction-holomorphic-handoff-boundary} for downstream holomorphic consumers. Such consumers see only the socket output already displayed by $S$, with $B$ retained as boundary accounting rather than exported analytic evidence.
\end{proof}

\closureat{BranchObstructionUp}{seedStr}

\begin{closurestatus}{\BranchObstructionUp}
  \constructivestory{A $\BranchObstructionUp$ packet is generated from an $\AnalyticContinuationSocketUp$ row, a selected branch-obstruction ledger row, componentwise $\hsame$ transport, visible $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite socket row, selected obstruction ledger, transport rows, visible routes, package provenance, local naming row, and non-export boundary for branch-sensitive continuation requests.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close global analytic continuation, branch selection, quotient-of-germs equality, monodromy invariance, Riemann-hypothesis zero-location data, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier compatibility, ledger exactness, holomorphic handoff boundary, and monodromy non-export obligations for the displayed socket and obstruction rows.}
\end{closurestatus}
