\chapter{A Concrete Naming Certificate for $\CofinalTailBudgetUp$}
\label{ch:concrete-instances-cofinal-tail-budget-namecert}
\origin{ai}

The $\CofinalTailBudgetUp$ packet records the finite shared-tail threshold used when a Real and Completion diagonal-limit argument must move from a cofinal family of tail windows to the displayed $\RealUp$ seal. It does not choose an infinite subsequence or identify a real number by quotienting. It names the finite budget row, the selected tail-window rows, the RegSeqRat handoff, and the RealUp seal route that later consumers may replay. It consumes the cofinal-subsequence window handoff surface of \autoref{ch:concrete-instances-cofinalsubsequence-namecert} but restricts it to the finite shared-tail budget rows $M,T,R,S,H,C,P,N$.

\begin{definition}[Cofinal tail budget carrier]
\label{def:cofinal-tail-budget-carrier}
A $\CofinalTailBudgetUp$ carrier is a finite $\BHist$ packet
$$
B=(M,T,R,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the finite modulus-budget row naming the requested precision level and the bound from which tail windows are read;
\item $T$ is the cofinal tail-window row, listing the finitely many windows whose anchors are at or beyond the bound recorded by $M$;
\item $R$ is the $\RegSeqRat$ handoff row that reads each selected tail window as a regular rational observation;
\item $S$ is the $\RealUp$ seal row consumed by the diagonal-limit handoff;
\item $H$ records componentwise $\hsame$ transport for $M,T,R,S,P,N$ and the local packet shape;
\item $C$ records the $\Cont$ routes by which a consumer reads the budget, selected windows, RegSeqRat handoff, RealUp seal, package provenance, and local naming row;
\item $P$ is the $\Pkg$ provenance over $\BHist$, finite modulus budgets, cofinal tail windows, $\RegSeqRat$ handoff rows, $\RealUp$ seal rows, $\hsame$, $\Cont$, and non-escape ledgers;
\item $N$ is the local $\NameCert_{\CofinalTailBudgetUp}$ row.
\end{enumerate}
The carrier contains no global completeness theorem, no choice of an infinite tail selector, and no quotient-level real equality. It exports only the finite shared-tail threshold packet displayed by $M,T,R,S,H,C,P,N$.
\end{definition}

\begin{theorem}[Cofinal tail budget NameCert obligations]
\label{thm:cofinal-tail-budget-namecert-obligations}
The local $\NameCert_{\CofinalTailBudgetUp}$ surface for \autoref{def:cofinal-tail-budget-carrier} consists of five finite obligation rows:
\begin{enumerate}
\item carrier admission for the packet $B=(M,T,R,S,H,C,P,N)$;
\item budget stability stating that componentwise $\hsame$ transport preserving $M,T,R,S,C,P,N$ preserves the same shared-tail threshold;
\item window exactness stating that every selected tail window in $T$ is read at or beyond the budget bound recorded by $M$;
\item seal handoff stating that the $\RegSeqRat$ row $R$ is the only route by which the selected windows feed the $\RealUp$ seal row $S$;
\item ledger exactness stating that every public read factors through $M,T,R,S,H,C,P,N$ and no unrecorded cofinal selector or completeness principle is exported.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed packet. The tuple lists the modulus budget, selected tail windows, RegSeqRat handoff, RealUp seal, transports, routes, provenance, and local naming row.

Budget stability is read through $H$ and $C$. Since the budget and window rows are transported together, the shared-tail threshold named by $M$ remains attached to the same selected windows in $T$.

Window exactness is the displayed role of $T$. Each public window read passes through $C$, and the package provenance $P$ records that the anchor lies at or beyond the finite bound supplied by $M$.

The seal handoff and ledger exactness are the remaining package clauses. A consumer reaches $S$ only through the RegSeqRat handoff row $R$, and every exported read remains a projection of $M,T,R,S,H,C,P,N$.
\end{proof}

\begin{theorem}[Cofinal tail budget window coverage]
\label{thm:cofinal-tail-budget-window-coverage}
For an accepted $\CofinalTailBudgetUp$ packet $B=(M,T,R,S,H,C,P,N)$, every public tail-window read covered by the packet is one of the finite windows listed in $T$, and each such read carries the shared-tail threshold recorded by $M$. A proposed window whose anchor is below the budget bound is not covered by this packet.
\end{theorem}
\begin{proof}
Project the carrier to obtain the budget row $M$ and the finite window row $T$. These two rows are paired in the same packet, so a covered read cannot detach the selected window from the displayed threshold.

Read the requested window through the continuation row $C$. If the request names a listed window, the route returns the corresponding $T$ coordinate together with the budget row $M$ and the RegSeqRat handoff $R$.

If the proposed anchor lies below the bound named by $M$, no coordinate of $T$ records it as covered. The package provenance $P$ therefore keeps the request outside the packet's coverage surface.
\end{proof}

\begin{theorem}[Cofinal tail budget Real seal handoff]
\label{thm:cofinal-tail-budget-real-seal-handoff}
Every $\RealUp$ seal read exported by an accepted $\CofinalTailBudgetUp$ packet factors through the selected tail windows $T$ and the $\RegSeqRat$ handoff row $R$. The seal row $S$ is therefore consumed as a finite diagonal-limit handoff from the displayed shared-tail threshold, not as an independent completeness claim.
\end{theorem}
\begin{proof}
Start from the carrier inventory. The only route to the RealUp seal coordinate is the continuation row $C$ reading the displayed seal row $S$ in the same packet as $M,T,R,H,P,N$.

The RegSeqRat handoff is the intermediate row. A seal consumer first reads the selected windows in $T$, then reads those windows through $R$, and only then reaches $S$.

Thus the exported seal is bound to the finite threshold and finite window ledger. Since the packet contains no global completeness theorem or quotient-level equality, the seal read is exactly the displayed handoff route.
\end{proof}

\begin{theorem}[Cofinal tail budget non-escape]
\label{thm:cofinal-tail-budget-nonescape}
An attempted Real and Completion tail read that omits the budget row $M$, a listed window from $T$, or the $\RegSeqRat$ handoff row $R$ is outside the $\CofinalTailBudgetUp$ packet. It cannot export the $\RealUp$ seal row $S$ and cannot be repacked as a cofinal shared-tail certificate.
\end{theorem}
\begin{proof}
Read the attempted route through the finite carrier. The packet exposes only $M,T,R,S,H,C,P,N$, so any route omitting the budget, selected-window, or handoff coordinate lacks a required source row.

Apply the window coverage row for omissions of $M$ or $T$. The request then has no covered tail-window coordinate at or beyond the shared threshold.

Apply the seal handoff row for omissions of $R$. A consumer cannot reach $S$ before the selected windows have been read as RegSeqRat handoff data.

The package provenance $P$ records the remaining attempt as outside the local naming surface. Hence the route cannot export $S$ or appear as a cofinal shared-tail certificate.
\end{proof}

\begin{theorem}[Cofinal tail budget stability]
\label{thm:cofinal-tail-budget-budget-stability}
Let $B=(M,T,R,S,H,C,P,N)$ be an accepted $\CofinalTailBudgetUp$ packet. Componentwise $\hsame$ transport recorded by $H$, and read through the displayed continuation routes $C$, preserves the same finite budget packet $M,T,R,S,P,N$. In particular, the shared-tail threshold named by $M$, the selected windows in $T$, the $\RegSeqRat$ handoff $R$, the $\RealUp$ seal row $S$, the package provenance $P$, and the local naming row $N$ remain attached to one another after transport.
\end{theorem}
\begin{proof}
Project the carrier to the transport row $H$. Its role in the packet is componentwise: it relates the displayed budget, window, handoff, seal, provenance, and naming coordinates without adding a second budget source.

Read the transported data through $C$. Each public route still lands in the same coordinates $M,T,R,S,P,N$, so the threshold in $M$ cannot detach from the finite window list $T$ or from the handoff and seal rows $R,S$.

The package row $P$ records this as provenance for the same local packet, and $N$ names that packet. Hence $\hsame$ transport preserves the displayed shared-tail budget packet rather than producing a new tail selector or a quotient witness.
\end{proof}

\begin{theorem}[Cofinal tail budget ledger exactness]
\label{thm:cofinal-tail-budget-ledger-exactness}
For an accepted $\CofinalTailBudgetUp$ packet $B=(M,T,R,S,H,C,P,N)$, every public read factors through the rows $M,T,R,S,H,C,P,N$. The exported ledger therefore excludes hidden cofinal selectors, quotient equality witnesses, ambient completeness rows, and any public read not routed through the displayed finite budget packet.
\end{theorem}
\begin{proof}
Start with a public read of the packet. The carrier definition exposes only the eight displayed rows, and the continuation row $C$ gives the public routes by which those rows are read.

If the read asks for budget, selected-window, handoff, seal, transport, provenance, or naming data, it is a projection through the corresponding coordinate. These projections are exactly the ledger entries named by $M,T,R,S,H,C,P,N$.

If the read asks for a hidden cofinal selector, a quotient equality witness, or an ambient completeness row, no displayed coordinate supplies it. The ledger therefore rejects that request as outside the local $\CofinalTailBudgetUp$ surface.
\end{proof}

\begin{theorem}[Cofinal tail budget obligation closure]
\label{thm:cofinal-tail-budget-obligation-closure}
The accepted $\CofinalTailBudgetUp$ packet closes its local obligation surface: carrier admission, budget stability, window coverage, $\RealUp$ seal handoff, ledger exactness, and non-escape are all witnessed by the same finite packet $B=(M,T,R,S,H,C,P,N)$.
\end{theorem}
\begin{proof}
Carrier admission is the tuple displayed in \autoref{def:cofinal-tail-budget-carrier}, and the NameCert surface of \autoref{thm:cofinal-tail-budget-namecert-obligations} lists the five obligation rows that must be read from it.

Budget stability is supplied by \autoref{thm:cofinal-tail-budget-budget-stability}. Window coverage is supplied by \autoref{thm:cofinal-tail-budget-window-coverage}, and the $\RealUp$ handoff is supplied by \autoref{thm:cofinal-tail-budget-real-seal-handoff}.

Ledger exactness is supplied by \autoref{thm:cofinal-tail-budget-ledger-exactness}. Non-escape is supplied by \autoref{thm:cofinal-tail-budget-nonescape}. These clauses all mention the same rows $M,T,R,S,H,C,P,N$, so the obligation surface is assembled without adding a hidden selector, quotient equality, or ambient completeness principle.
\end{proof}

\begin{theorem}[Cofinal tail budget primitive-scope binding]
\label{thm:cofinal-tail-budget-primitive-scope-binding}
For every accepted $\CofinalTailBudgetUp$ packet $B=(M,T,R,S,H,C,P,N)$, the budget row, selected tail windows, $\RegSeqRatUp$ handoff, $\RealUp$ seal, componentwise $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row are bound entirely through the displayed BEDC primitives $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\RegSeqRatUp$, and $\RealUp$, together with the cited cofinal-subsequence sibling surface of \autoref{ch:concrete-instances-cofinalsubsequence-namecert}. The binding exports no hidden cofinal selector, quotient equality witness, ambient completeness row, or nonlocal naming route.
\end{theorem}
\begin{proof}
Start with the carrier definition. The packet exposes only the displayed rows $M,T,R,S,H,C,P,N$, and \autoref{thm:cofinal-tail-budget-namecert-obligations} assigns the local naming obligations to those rows.

The budget and window clauses are fixed by \autoref{thm:cofinal-tail-budget-budget-stability} and \autoref{thm:cofinal-tail-budget-window-coverage}. They keep the finite budget row, selected tail windows, and componentwise transports inside the same $\BHist$ packet.

The Real-facing route is fixed by \autoref{thm:cofinal-tail-budget-real-seal-handoff}. It sends selected windows through the $\RegSeqRatUp$ handoff before the $\RealUp$ seal is read, so the seal cannot detach from the displayed tail-budget packet.

Ledger exactness and non-escape are supplied by \autoref{thm:cofinal-tail-budget-ledger-exactness} and \autoref{thm:cofinal-tail-budget-nonescape}. Together with the existing TasteGate marker, these clauses say that every accepted read remains a projection of the same carrier surface and every nonlisted selector, quotient witness, completeness row, or nonlocal naming route is outside the chapter scope.
\end{proof}

\closureat{CofinalTailBudgetUp}{seedStr}
\closureat{CofinalTailBudgetUp}{obligationStr}[BEDC.Derived.CofinalTailBudgetUp.CofinalTailBudgetTasteGate\_single\_carrier\_alignment]
\closureat{CofinalTailBudgetUp}{scopedStr}[BEDC.Derived.CofinalTailBudgetUp.CofinalTailBudgetTasteGate\_single\_carrier\_alignment]
\closureat{CofinalTailBudgetUp}{publicStr}[BEDC.Derived.CofinalTailBudgetUp.CofinalTailBudgetTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\CofinalTailBudgetUp}
  \constructivestory{A $\CofinalTailBudgetUp$ packet is generated from a finite modulus-budget row, cofinal tail-window row, RegSeqRat handoff row, RealUp seal row, componentwise hsame transports, displayed Cont routes, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{def:cofinal-tail-budget-carrier}, \autoref{thm:cofinal-tail-budget-namecert-obligations}, \autoref{thm:cofinal-tail-budget-budget-stability}, \autoref{thm:cofinal-tail-budget-window-coverage}, \autoref{thm:cofinal-tail-budget-real-seal-handoff}, \autoref{thm:cofinal-tail-budget-ledger-exactness}, \autoref{thm:cofinal-tail-budget-nonescape}, \autoref{thm:cofinal-tail-budget-obligation-closure}, \autoref{thm:cofinal-tail-budget-primitive-scope-binding}, and the local TasteGate target bind the local finite shared-tail threshold primitive scope.}
  \formalstatus{\auditCleanV}
  \leanchecked{BEDC.Derived.CofinalTailBudgetUp.taste\_gate}
  \leantarget{BEDC.Derived.CofinalTailBudgetUp.CofinalTailBudgetTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean implementation, bridge checking, Real completeness, infinite tail selection, quotient-level real equality, or a public RealUp object surface.}
  \upgradepath{Bridged closure requires a bridge for the finite shared-tail budget packet.}
\end{closurestatus}
