\chapter{RegularCauchyTelescopingBudget NameCert Construction}
\label{ch:concrete-instances-regular-cauchy-telescoping-budget-namecert}
\origin{ai}

The $\RegularCauchyTelescopingBudgetUp$ packet records the finite chained-window error ledger used by Real-completion diagonal handoffs. It starts with one precision request, opens a finite chain of selected $\StreamNameUp$ windows, reads their dyadic error rows, transports the result through $\RegSeqRatUp$, seals the terminal row through $\RealUp$, and records the telescoping composition that makes the intermediate errors visible. The packet is a NameCert surface for finite budget composition; it is not a quotient of streams, a selected host limit, countable choice, or an ambient completeness principle.

\begin{definition}[RegularCauchyTelescopingBudget carrier]
\label{def:regular-cauchy-telescoping-budget-carrier}
A $\RegularCauchyTelescopingBudgetUp$ carrier is a finite $\BHist$ packet
$$
B=(E,W,D,R,S,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the precision request whose requested Real-completion tolerance is being budgeted;
\item $W$ is a finite chain of selected $\StreamNameUp$ windows opened from the displayed regular Cauchy sources;
\item $D$ is the $\DyadicRatCoreUp$ error ledger read from the successive windows in $W$;
\item $R$ is the $\RegSeqRatUp$ handoff row obtained after the selected dyadic errors have been composed;
\item $S$ is the $\RealUp$ seal row reached from the handoff $R$ at the requested precision;
\item $T$ is the telescoping composition ledger, recording the finite sum of adjacent-window errors and the remaining budget after each handoff;
\item $H$ records componentwise $\hsame$ transports for $E,W,D,R,S,T$ and for the structural rows of the packet;
\item $C$ records the displayed $\Cont$ routes for precision exposure, window-chain admission, dyadic-ledger reads, telescoping composition, $\RegSeqRatUp$ handoff, and $\RealUp$ seal delivery;
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RegularCauchySequenceUp$, $\RegularCauchyWindowFusionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\RegularCauchyTelescopingBudgetUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through the visible rows $E,W,D,R,S,T,H,C,P,N$.
\end{definition}

\begin{theorem}[RegularCauchyTelescopingBudget NameCert obligations]
\label{thm:regular-cauchy-telescoping-budget-namecert-obligations}
The local $\NameCert_{\RegularCauchyTelescopingBudgetUp}$ surface for \autoref{def:regular-cauchy-telescoping-budget-carrier} consists of carrier admission for
$$
B=(E,W,D,R,S,T,H,C,P,N),
$$
precision exposure through $E$, finite window-chain admission through $W$, dyadic error-ledger exposure through $D$, telescoping composition through $T$, $\RegSeqRatUp$ handoff through $R$, $\RealUp$ seal delivery through $S$, componentwise $\hsame$ stability, displayed $\Cont$ route replay, $\Pkg$ provenance, local naming, and non-escape from quotient streams, selected host limits, countable choice, ambient completeness, hidden comparison rows, and unrecorded error budgets.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyTelescopingBudgetUp.RegularCauchyTelescopingBudgetTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:regular-cauchy-telescoping-budget-carrier}. The packet contains exactly the rows $E,W,D,R,S,T,H,C,P,N$.

The analytic-facing obligations are read in order. The precision request $E$ determines which finite chain of selected $\StreamNameUp$ windows $W$ is opened. The dyadic ledger $D$ records the error rows read from those windows, and the telescoping ledger $T$ records their finite composition before the $\RegSeqRatUp$ handoff $R$ is exposed.

The real-facing obligation is the seal row $S$. It is reached only after $R$ has consumed the displayed window chain and the telescoping ledger.

Finally $H,C,P,N$ preserve, route, package, and name the same finite packet. Because no coordinate names quotient streams, selected host limits, countable choice, ambient completeness, hidden comparison rows, or unrecorded budgets, the local NameCert exports none of that data.
\end{proof}

\begin{theorem}[RegularCauchyTelescopingBudget dyadic ledger exposure]
\label{thm:regular-cauchy-telescoping-budget-dyadic-ledger-exposure}
For every accepted $\RegularCauchyTelescopingBudgetUp$ carrier
$$
B=(E,W,D,R,S,T,H,C,P,N),
$$
the dyadic ledger row $D$ is readable only after the precision row $E$ and the finite $\StreamNameUp$ window chain $W$ have been exposed. The row $D$ supplies adjacent-window $\DyadicRatCoreUp$ error entries for the displayed finite route, and it supplies no quotient-stream equality, selected host limit, choice selector, ambient completeness row, hidden comparison row, or independent Real carrier.
\end{theorem}
\begin{proof}
Read the carrier in \autoref{def:regular-cauchy-telescoping-budget-carrier}. Its ordered packet has one precision request $E$, one finite selected-window chain $W$, and one dyadic error ledger $D$.

Apply the NameCert obligations of \autoref{thm:regular-cauchy-telescoping-budget-namecert-obligations}. Precision exposure through $E$ opens the finite $\StreamNameUp$ chain $W$, and $D$ is then the displayed $\DyadicRatCoreUp$ ledger read from those windows. The surrounding $\RegularCauchySequenceUp$ and $\RegularCauchyWindowFusionUp$ surfaces provide the selected-window sources and shared-window handoff route, not an ambient completion object.

Finally inspect the packet boundary. Quotient-stream equality, selected host limits, choice selectors, ambient completeness rows, hidden comparison rows, and independent Real carriers are absent from the coordinates $E,W,D,R,S,T,H,C,P,N$. The dyadic ledger therefore exposes only the finite adjacent-window error rows named by $D$.
\end{proof}

\begin{theorem}[RegularCauchyTelescopingBudget telescoping composition]
\label{thm:regular-cauchy-telescoping-budget-telescoping-composition}
For every accepted $\RegularCauchyTelescopingBudgetUp$ carrier
$$
B=(E,W,D,R,S,T,H,C,P,N),
$$
the telescoping composition row $T$ consumes exactly the finite adjacent-window error rows exposed by $D$, records the remaining budget at each finite handoff, and is stable only under the displayed componentwise $\hsame$ transports in $H$.
\end{theorem}
\begin{proof}
Use \autoref{def:regular-cauchy-telescoping-budget-carrier} to project the finite rows $D,T,H$. The ledger $D$ is the only coordinate containing adjacent-window dyadic error entries, and $T$ is the only coordinate recording their finite telescoping composition.

Apply \autoref{thm:regular-cauchy-telescoping-budget-namecert-obligations} and \autoref{thm:regular-cauchy-telescoping-budget-dyadic-ledger-exposure}. The $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchySequenceUp$, and $\RegularCauchyWindowFusionUp$ surfaces expose a finite list of adjacent-window error rows. The composition row $T$ consumes that displayed list and records the remaining budget passed at each handoff.

Stability is then confined to $H$. Since $H$ records componentwise $\hsame$ transports for $E,W,D,R,S,T$ and the structural rows, a transported packet preserves the same finite telescoping ledger exactly along those displayed transports and along no unrecorded comparison row.
\end{proof}

\begin{theorem}[RegularCauchyTelescopingBudget RegSeqRat handoff order]
\label{thm:regular-cauchy-telescoping-budget-regseqrat-handoff-order}
For every accepted $\RegularCauchyTelescopingBudgetUp$ carrier
$$
B=(E,W,D,R,S,T,H,C,P,N),
$$
the $\RegSeqRatUp$ handoff row $R$ is exposed only after $E,W,D,T$, and the $\RealUp$ seal row $S$ is exposed only after $R$.
\end{theorem}
\begin{proof}
First read the carrier and NameCert surface. By \autoref{def:regular-cauchy-telescoping-budget-carrier} and \autoref{thm:regular-cauchy-telescoping-budget-namecert-obligations}, the finite route exposes precision, selected windows, dyadic ledger rows, and telescoping composition as $E,W,D,T$ before the handoff row $R$.

The dyadic and telescoping obligations make this order explicit. Apply \autoref{thm:regular-cauchy-telescoping-budget-dyadic-ledger-exposure} to obtain the $E,W,D$ prefix, then apply \autoref{thm:regular-cauchy-telescoping-budget-telescoping-composition} to consume the adjacent-window $\DyadicRatCoreUp$ rows through $T$. The handoff row $R$ is therefore the first $\RegSeqRatUp$ row downstream of the finite $\StreamNameUp$, $\RegularCauchySequenceUp$, and $\RegularCauchyWindowFusionUp$ route.

Finally apply \autoref{thm:regular-cauchy-telescoping-budget-real-seal-handoff}. The seal row $S$ is the only $\RealUp$ seal row in the carrier, and that theorem places it after the route through $E,W,D,T,R$. Thus the Real-facing seal cannot be read before the $\RegSeqRatUp$ handoff has been exposed.
\end{proof}

\begin{theorem}[RegularCauchyTelescopingBudget window chain]
\label{thm:regular-cauchy-telescoping-budget-window-chain}
For every accepted $\RegularCauchyTelescopingBudgetUp$ carrier
$$
B=(E,W,D,R,S,T,H,C,P,N),
$$
the selected windows form a finite chain read through $\RegularCauchySequenceUp$ and $\RegularCauchyWindowFusionUp$ surfaces. Each adjacent-window error consumed by the chain is recorded in $D$, and each transfer of remaining precision is recorded in $T$ before the handoff row $R$ is available.
\end{theorem}
\begin{proof}
Project $E,W,D,T$ from the carrier. The precision row $E$ fixes the requested tolerance, and the window row $W$ is the only coordinate that opens selected $\StreamNameUp$ windows.

Use the existing $\RegularCauchySequenceUp$ and $\RegularCauchyWindowFusionUp$ surfaces as the displayed sources of the chain. They expose finite selected windows and shared-window Real-facing routes without selecting a host limit or quotient representative.

Now read the dyadic and telescoping rows. The ledger $D$ stores the adjacent-window error rows, while $T$ composes them and records the remaining budget passed to the next window. Since $R$ appears only after $D$ and $T$, the $\RegSeqRatUp$ handoff is downstream of the finite chain.
\end{proof}

\begin{theorem}[RegularCauchyTelescopingBudget Real seal handoff]
\label{thm:regular-cauchy-telescoping-budget-real-seal-handoff}
Every $\RealUp$ seal read exported by an accepted $\RegularCauchyTelescopingBudgetUp$ carrier factors through the route
$$
E,W,D,T,R,S,H,C,P,N.
$$
The route first consumes the requested precision, then the selected window chain, then the dyadic error ledger, then the telescoping composition ledger, then the $\RegSeqRatUp$ handoff, and only then the $\RealUp$ seal row.
\end{theorem}
\begin{proof}
Begin with the window-chain theorem. It places the selected windows, dyadic error rows, telescoping composition, and $\RegSeqRatUp$ handoff in the displayed order $E,W,D,T,R$.

Read the seal coordinate. The row $S$ is the only $\RealUp$ seal row in the carrier, and the continuation row $C$ exposes it only after the route through $E,W,D,T,R$ has been replayed.

The rows $H,P,N$ transport, package, and name the same route. Therefore every Real-facing consumer receives the seal through $E,W,D,T,R,S,H,C,P,N$ and through no independent completion object.
\end{proof}

\begin{theorem}[RegularCauchyTelescopingBudget non-escape]
\label{thm:regular-cauchy-telescoping-budget-nonescape}
For an accepted $\RegularCauchyTelescopingBudgetUp$ carrier, the finite telescoping budget exports no quotient stream equality, selected host limit, countable-choice selector, ambient completeness principle, hidden comparison row, unrecorded error budget, or independent RealUp carrier. All exported data are confined to
$$
E,W,D,R,S,T,H,C,P,N.
$$
\end{theorem}
\begin{proof}
Use the NameCert obligations to identify the complete carrier surface. The only admitted rows are $E,W,D,R,S,T,H,C,P,N$.

Use the window-chain theorem and the Real seal handoff theorem. They force every path to the $\RegSeqRatUp$ handoff and the $\RealUp$ seal to consume the finite selected windows, dyadic ledger, and telescoping composition ledger.

Inspect the packet boundary. No coordinate stores quotient stream equality, selected host limits, countable choice, ambient completeness, hidden comparisons, unrecorded budgets, or an independent real carrier. The exported surface is exactly the displayed finite packet.
\end{proof}

\closureat{RegularCauchyTelescopingBudgetUp}{seedStr}
\closureat{RegularCauchyTelescopingBudgetUp}{obligationStr}[BEDC.Derived.RegularCauchyTelescopingBudgetUp.RegularCauchyTelescopingBudgetTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\RegularCauchyTelescopingBudgetUp}
  \constructivestory{A $\RegularCauchyTelescopingBudgetUp$ packet is generated from a precision request, a finite chain of selected $\StreamNameUp$ windows, a $\DyadicRatCoreUp$ error ledger, a $\RegSeqRatUp$ handoff, a $\RealUp$ seal row, a telescoping composition ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:regular-cauchy-telescoping-budget-carrier}, \autoref{thm:regular-cauchy-telescoping-budget-namecert-obligations}, \autoref{thm:regular-cauchy-telescoping-budget-dyadic-ledger-exposure}, \autoref{thm:regular-cauchy-telescoping-budget-telescoping-composition}, \autoref{thm:regular-cauchy-telescoping-budget-regseqrat-handoff-order}, \autoref{thm:regular-cauchy-telescoping-budget-window-chain}, \autoref{thm:regular-cauchy-telescoping-budget-real-seal-handoff}, and \autoref{thm:regular-cauchy-telescoping-budget-nonescape} with the TasteGate instance \texttt{BEDC.Derived.RegularCauchyTelescopingBudgetUp.taste\_gate} bind the finite chained-window telescoping budget for Real-completion diagonal handoffs.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, RealUp completeness, quotient stream equality, selected host limits, countable choice, ambient completeness, hidden comparison rows, unrecorded error budgets, or a public standard bridge.}
  \upgradepath{Scoped closure requires binding the dyadic ledger exposure, telescoping composition, RegSeqRat handoff, RealUp seal delivery, transport stability, route replay, provenance, local naming, and non-escape obligations to explicit BEDC primitive scope rows for the same finite packet.}
\end{closurestatus}
