\chapter{A Concrete Naming Certificate for \(\FunctorUp\)}
\label{ch:concrete-instances-functor-namecert}

The functor interface \(\FunctorUp\) has certificate obligations between two categories from \autoref{ch:concrete-instances-category-namecert} as a pair of mappings (one on objects, one on morphisms) preserving identity and composition under the morphism classifier of the codomain. It is not a primitive function space between categories; it is admitted only as a structure-preserving pair of carrier mappings.

\section{Carrier definition}

\begin{definition}[Functor carrier]
\label{def:functor-carrier}
Use a structure with object mapping, morphism mapping, and proofs preserving identity and composition.
\end{definition}

\begin{theorem}[Prefix functor preserves hom carriers]
\label{thm:functor-prefix-hom-carrier-preserves}
For the unary-continuation category, if \(p\) is unary and \(f\) is a hom-carrier from \(a\) to \(b\), then the same morphism \(f\) is a hom-carrier from \(\mathsf{append}(p,a)\) to \(\mathsf{append}(p,b)\).
\end{theorem}
\begin{proof}
Unpack the hom-carrier witness into unary source, unary target, unary morphism, and a continuation from \(a\) through \(f\) to \(b\). Unary append closure gives the prefixed source and target carriers. Continuation associativity identifies appending \(f\) after \(\mathsf{append}(p,a)\) with \(\mathsf{append}(p,b)\).
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.FunctorPrefixHomCarrier\_preserves}

\begin{theorem}[Prefix functor preserves hom composition]
\label{thm:functor-prefix-hom-carrier-comp-preserves}
For the unary-continuation category, if \(p\) is unary, \(f\) is a hom-carrier from \(a\) to \(b\), \(g\) is a hom-carrier from \(b\) to \(c\), and \(\ContR(f,g,fg)\), then \(fg\) is a hom-carrier from \(\mathsf{append}(p,a)\) to \(\mathsf{append}(p,c)\).
\end{theorem}
\begin{proof}
First use category hom-carrier composition closure to place \(fg\) from \(a\) to \(c\). Then apply prefix preservation to that composite hom-carrier with the unary witness for \(p\).
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.FunctorPrefixHomCarrier\_comp\_preserves}

\begin{theorem}[Prefix functor preserves associative hom composition]
\label{thm:functor-prefix-hom-carrier-comp-assoc-preserves}
For the unary-continuation category, if \(p\) is unary and \(f,g,h\) are
composable hom-carriers with composites \(fg\), \(gh\), \(left\), and
\(right\), then \(left\) and \(right\) are hom-carriers from
\(\mathsf{append}(p,a)\) to \(\mathsf{append}(p,d)\), and
\(\HSame(left,right)\).
\end{theorem}
\begin{proof}
Use category-level associative composition closure to obtain the two
unprefixed composite hom-carriers and their classifier sameness. Prefix
preservation transports each composite hom-carrier across the unary prefix
\(p\), while the classifier sameness is the same continuation associativity
witness.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.FunctorPrefixHomCarrier\_comp\_assoc\_preserves}

\section{The certificate}

\begin{definition}[Functor source specification]
\label{def:functor-source-specification}
The source is a pair of certified categories.
\end{definition}

\begin{definition}[Functor pattern specification]
\label{def:functor-pattern-specification}
The pattern is structure-preserving mapping formation over object and morphism carriers.
\end{definition}

\begin{definition}[Functor classifier specification]
\label{def:functor-classifier-specification}
The classifier relates functors pointwise on object images and morphism images using the codomain category classifiers.
\end{definition}

\begin{definition}[Functor stability certificate]
\label{def:functor-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item pointwise object-map classifier reflexivity
  \item pointwise morphism-map classifier reflexivity
  \item pointwise transitivity
  \item identity preservation
  \item composition preservation
  \item stability under source and target classifier replacement
\end{enumerate}
\end{definition}

\begin{definition}[Functor ledger policy]
\label{def:functor-ledger-policy}
Record the two category ledgers and the preservation witnesses.
\end{definition}

\begin{definition}[\(\FunctorUp\) certificate obligations]
\label{def:functor-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\FunctorUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\FunctorUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:functor-zero-axiom-note}
Avoids funext by pointwise classifier sameness for object and morphism mappings.
\end{remark}
