\chapter{A Concrete Naming Certificate for $\ClosedGeneratorAuditUp$}
\label{ch:concrete-instances-closedgeneratoraudit-namecert}
\origin{human}

The $\ClosedGeneratorAuditUp$ packet names the finite audit surface shared by kernel acceptance, recursor authorization, and closed-term substitution. It packages MetaCIC generator-closure rows, closed-substitution rows, accepted kernel rows, audit-refusal rows, and local $\NameCert$ naming as one BEDC-readable object rather than as three unrelated host-side facts.

\begin{definition}[Closed generator audit carrier]
\label{def:closed-generator-audit-carrier}
A $\ClosedGeneratorAuditUp$ carrier is a finite $\BHist$ packet
$$
G=(T,K,R,S,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ records the generated MetaCIC term or proof row, including the local syntax object whose closure and acceptance are audited;
\item $K$ records the kernel acceptance row for the generated object and the accepted declaration or proof stamp exposed by $\KernelAcceptanceAuditWitnessUp$ or $\KernelAcceptanceTraceUp$;
\item $R$ records the authorized recursor row, including the emitted eliminator, checked motive, branch package, structural descent ledger, and generated output row supplied by $\RecursionAuthorizationLedgerUp$;
\item $S$ records the closed substitution and shift row, including the \texttt{GeneratorClosureClassifier}, \texttt{closed\_under\_substitute\_classifier}, \texttt{shift\_closed}, and \texttt{substitute\_closed} audit entries used to replay non-escape of closed terms;
\item $A$ records the axiom-purity audit row, with refusal entries for \texttt{Classical.choice}, \texttt{Quot.sound}, \texttt{propext}, host conversion, and any unrecorded proof oracle;
\item $H$ records componentwise $\hsame$ transport for the generated object, kernel row, recursor row, closed-substitution row, audit row, replay route, provenance, and local name;
\item $C$ records the displayed $\Cont$ routes replaying kernel acceptance, recursor authorization, closed-substitution preservation, audit refusal, and consumer access;
\item $P$ records the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\KernelAcceptanceAuditWitnessUp$, $\KernelAcceptanceTraceUp$, $\RecursionAuthorizationLedgerUp$, and $\GeneratorAuditClosureUp$;
\item $N$ is the local $\NameCert_{\ClosedGeneratorAuditUp}$ row.
\end{enumerate}
The carrier has no coordinate for a host proof kernel, quotient transport, classical selection, proposition extensionality, hidden conversion, or an accepted proof oracle outside the displayed rows.
\end{definition}

\begin{theorem}[Closed generator audit NameCert obligations]
\label{thm:closed-generator-audit-namecert-obligations}
For every accepted $\ClosedGeneratorAuditUp$ carrier
$$
G=(T,K,R,S,A,H,C,P,N),
$$
the local $\NameCert_{\ClosedGeneratorAuditUp}$ surface consists exactly of the following five obligations:
\begin{enumerate}
\item carrier admission exposes the generated object, kernel row, authorized recursor row, closed-substitution row, axiom-purity audit row, transport, replay, provenance, and local name as the packet $T,K,R,S,A,H,C,P,N$;
\item generator-closure replay reads the \texttt{GeneratorClosureClassifier} data in $S$ and routes it through the accepted generator-audit packet;
\item closed-substitution non-escape reads \texttt{closed\_under\_substitute\_classifier}, \texttt{shift\_closed}, and \texttt{substitute\_closed} only as the displayed closed-term rows in $S$;
\item kernel-acceptance replay reads $K$ through the displayed kernel-acceptance witness or trace and connects authorized recursor output $R$ to the generated row $T$;
\item audit-refusal exactness reads $A$ as the complete refusal row for \texttt{Classical.choice}, \texttt{Quot.sound}, \texttt{propext}, host conversion, and any unrecorded proof oracle.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the finite packet of \autoref{def:closed-generator-audit-carrier}. Its carrier coordinates are precisely $T,K,R,S,A,H,C,P,N$, so carrier admission and local naming have no row outside the displayed tuple.

The generator side is supplied by the existing generator-audit closure surface. It reads the \texttt{GeneratorClosureClassifier} row and the accepted substitute or shift closure witness before exposing the closure claim to a consumer.

The substitution side is the closed-term boundary. The entries \texttt{closed\_under\_substitute\_classifier}, \texttt{shift\_closed}, and \texttt{substitute\_closed} are recorded in $S$, and the replay route $C$ keeps them attached to the same generated row $T$.

The kernel and recursor side is read through $K$ and $R$. Kernel acceptance supplies the accepted declaration or proof stamp, while the recursion authorization ledger supplies the emitted recursor output and its structural authorization before it is identified with the generated row.

Finally use the audit row $A$. Since the forbidden dependencies and unrecorded proof-oracle requests are refused there, and since $H,C,P,N$ only transport and replay the displayed rows, the five obligations exhaust the local $\NameCert$ surface.
\end{proof}

\begin{theorem}[Closed generator audit non-escape]
\label{thm:closed-generator-audit-nonescape}
Every consumer of an accepted $\ClosedGeneratorAuditUp$ carrier
$$
G=(T,K,R,S,A,H,C,P,N)
$$
can read only the displayed MetaCIC and BEDC rows
$$
T,K,R,S,A,H,C,P,N.
$$
In particular, the consumer may read generated syntax, kernel acceptance, authorized recursor output, closed substitution and shift preservation, axiom-purity refusal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ naming. It cannot read \texttt{Classical.choice}, \texttt{Quot.sound}, \texttt{propext}, host conversion, or an unrecorded proof oracle.
\end{theorem}
\begin{proof}
Start from the carrier definition. The packet lists generated MetaCIC data, kernel acceptance, recursor authorization, closed-substitution audit data, audit refusal, transport, replay, provenance, and local naming as the full exported inventory.

Apply \autoref{thm:closed-generator-audit-namecert-obligations}. The NameCert surface routes every consumer read through one of the five displayed obligations, and each obligation returns to the same tuple $T,K,R,S,A,H,C,P,N$.

The refusal part is exact. Since the audit row $A$ names the forbidden dependencies and unrecorded proof-oracle requests only as refused rows, no consumer route can reinterpret them as accepted kernel evidence or closed-term evidence.

Thus every readable row is a displayed MetaCIC or BEDC row in the packet. The excluded host, quotient, classical, extensional, conversion, and oracle coordinates are absent from the carrier and cannot be exported by transport or replay.
\end{proof}

\closureat{ClosedGeneratorAuditUp}{seedStr}

\begin{closurestatus}{\ClosedGeneratorAuditUp}
  \constructivestory{A $\ClosedGeneratorAuditUp$ packet is generated from a MetaCIC term or proof row, kernel acceptance row, authorized recursor row, closed-substitution and shift row, axiom-purity audit row, componentwise $\hsame$ transports, displayed $\Cont$ replay routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:closed-generator-audit-carrier}, \autoref{thm:closed-generator-audit-namecert-obligations}, and \autoref{thm:closed-generator-audit-nonescape} specify the finite NameCert carrier, obligation surface, and non-escape boundary joining kernel acceptance, recursor authorization, and closed-term substitution audit rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not prove new MetaCIC closure lemmas, Lean kernel soundness, global recursor soundness, host conversion, quotient transport, classical choice, proposition extensionality, Lean-side verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, generator-closure replay, closed-substitution non-escape, kernel-acceptance replay, and audit-refusal exactness for the displayed packet.}
\end{closurestatus}
