\chapter{A Concrete Naming Certificate for \(\NatTransUp\)}
\label{ch:concrete-instances-nattrans-namecert}

The natural transformation interface \(\NatTransUp\) has certificate obligations between two functors from \autoref{ch:concrete-instances-functor-namecert} sharing source and target categories. The carrier is, for each object \(X\) of the source category, a morphism in the target category from the first functor's image of \(X\) to the second functor's image of \(X\), satisfying the naturality square under the codomain category's morphism classifier. It is not a primitive 2-cell; it is admitted only as an object-indexed family of morphisms with the naturality field.

\section{Carrier definition}

\begin{definition}[NatTrans carrier]
\label{def:nattrans-carrier}
Use an object-indexed family of codomain morphisms \(\eta_X:F(X)\to G(X)\) plus naturality witnesses for every source morphism.
\end{definition}
\leandef{BEDC.Derived.NatTransUp.NatTransPrefixComponentCarrier}

\begin{theorem}[NatTrans prefix component vertical composition closure]
\label{thm:nattrans-prefix-component-carrier-vert-comp-closed}
For prefix components over unary histories, if \(\eta\) is a component from
\(\mathsf{append}(p,a)\) to \(\mathsf{append}(q,a)\), \(\theta\) is a component
from \(\mathsf{append}(q,a)\) to \(\mathsf{append}(r,a)\), and
\(\ContR(\eta,\theta,\theta\eta)\), then the composite component is a component
from \(\mathsf{append}(p,a)\) to \(\mathsf{append}(r,a)\).
\end{theorem}
\begin{proof}
Unpack the two prefix-component carrier witnesses. The outer prefix and object
unary witnesses come from the first component and the target prefix witness
comes from the second component. Category hom-carrier composition closure
composes the two component morphisms across the shared middle object
\(\mathsf{append}(q,a)\).
\end{proof}
\leanchecked{BEDC.Derived.NatTransUp.NatTransPrefixComponentCarrier\_vert\_comp\_closed}

\begin{theorem}[NatTrans prefix component target-prefix determinacy]
\label{thm:nattrans-prefix-component-carrier-target-prefix-deterministic}
For prefix components over unary histories, if a fixed component history
$\eta$ is a component from $\mathsf{append}(p,a)$ to
$\mathsf{append}(q,a)$ and also from $\mathsf{append}(p,a)$ to
$\mathsf{append}(r,a)$, then $\HSame(q,r)$.
\end{theorem}
\begin{proof}
Unpack both prefix-component carrier witnesses to their underlying category
hom-carrier witnesses. Category target determinacy identifies
$\mathsf{append}(q,a)$ and $\mathsf{append}(r,a)$, and cancellation of the
shared suffix $a$ identifies the prefixes $q$ and $r$.
\end{proof}
\leanchecked{BEDC.Derived.NatTransUp.NatTransPrefixComponentCarrier\_target\_prefix\_deterministic}

\begin{theorem}[NatTrans prefix component source-prefix determinacy]
\label{thm:nattrans-prefix-component-carrier-source-prefix-deterministic}
For prefix components over unary histories, if a fixed component history
$\eta$ is a component from $\mathsf{append}(p,a)$ to
$\mathsf{append}(q,a)$ and also from $\mathsf{append}(r,a)$ to
$\mathsf{append}(q,a)$, then $\HSame(p,r)$.
\end{theorem}
\begin{proof}
Unpack both prefix-component carrier witnesses to their underlying category
hom-carrier witnesses. Category source determinacy identifies
$\mathsf{append}(p,a)$ and $\mathsf{append}(r,a)$, and cancellation of the
shared suffix $a$ identifies the prefixes $p$ and $r$.
\end{proof}
\leanchecked{BEDC.Derived.NatTransUp.NatTransPrefixComponentCarrier\_source\_prefix\_deterministic}

\begin{theorem}[NatTrans prefix component tail commutativity]
\label{thm:nattrans-prefix-component-carrier-tail-comm-hsame}
For prefix components over unary histories, if \(\eta\) is a component from
\(\mathsf{append}(p,a)\) to \(\mathsf{append}(q,a)\), \(\theta\) is a component
from \(\mathsf{append}(q,a)\) to \(\mathsf{append}(r,a)\),
\(\ContR(\eta,\theta,\eta\theta)\), and
\(\ContR(\theta,\eta,\theta\eta)\), then
\(\HSame(\eta\theta,\theta\eta)\).
\end{theorem}
\begin{proof}
Each prefix-component carrier exposes an underlying category hom-carrier. The
two hom-carriers expose unary membership for \(\eta\) and \(\theta\), and unary
continuation commutativity identifies the forward and reversed component
composites.
\end{proof}
\leanchecked{BEDC.Derived.NatTransUp.NatTransPrefixComponentCarrier\_tail\_comm\_hsame}

\begin{theorem}[Prefix identity naturality square]
\label{thm:nattrans-prefix-identity-naturality-square}
For the unary-continuation category, let \(p\) be unary and let \(f\) be a
hom-carrier from \(a\) to \(b\). If the two square composites are obtained by
composing \(f\) with the empty continuation on the left and on the right, then
both composites are hom-carriers from \(\mathsf{append}(p,a)\) to
\(\mathsf{append}(p,b)\), and the two composites are history-same.
\end{theorem}
\begin{proof}
The left empty continuation identifies the left composite with \(f\), and
the right empty continuation identifies the right composite with \(f\). The
given hom-carrier therefore supplies both unprefixed sides of the square.
Prefix hom-carrier preservation sends both sides across \(p\), and
transitivity of history sameness identifies the composites.
\end{proof}
\leanchecked{BEDC.Derived.NatTransUp.NatTransPrefixIdentity\_naturality\_square}

\begin{theorem}[Prefix identity component square closure]
\label{thm:nattrans-prefix-identity-component-square-closed}
For the unary-continuation category, if \(p\) and \(a\) are unary,
\(\ContR(\emp,\emp,id)\), \(\ContR(id,\emp,left)\), and
\(\ContR(\emp,id,right)\), then \(left\) and \(right\) are hom-carriers from
\(\mathsf{append}(p,a)\) to \(\mathsf{append}(p,a)\), and
\(\HSame(left,right)\).
\end{theorem}
\begin{proof}
The prefix identity hom-carrier theorem gives the carrier witness for \(id\)
at the prefixed object. The right unit continuation identifies \(left\) with
\(id\), and the left unit continuation identifies \(right\) with \(id\).
Transporting the identity carrier witness across these equalities gives both
legs of the component square, and transitivity of \(\HSame\) closes the
square.
\end{proof}
\leanchecked{BEDC.Derived.NatTransUp.NatTransPrefixIdentity\_identity\_component\_square\_closed}

\section{The certificate}

\begin{definition}[NatTrans source specification]
\label{def:nattrans-source-specification}
The source is two certified functors sharing the same certified source and target categories.
\end{definition}

\begin{definition}[NatTrans pattern specification]
\label{def:nattrans-pattern-specification}
The pattern is component-family formation with one codomain morphism per source object.
\end{definition}

\begin{definition}[NatTrans classifier specification]
\label{def:nattrans-classifier-specification}
The classifier relates natural transformations componentwise by the target category morphism classifier.
\end{definition}

\begin{definition}[NatTrans stability certificate]
\label{def:nattrans-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item componentwise reflexivity
  \item componentwise transitivity
  \item naturality square validity for every source morphism
  \item stability of naturality under component classifier replacement
  \item vertical composition closure
  \item identity natural transformation closure
\end{enumerate}
\end{definition}

\begin{definition}[NatTrans ledger policy]
\label{def:nattrans-ledger-policy}
Record the functor ledgers, component morphism ledgers, and naturality derivations.
\end{definition}

\begin{definition}[\(\NatTransUp\) certificate obligations]
\label{def:nattrans-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\NatTransUp\).
\end{definition}

\paragraph{Primitive boundary.}
\(\NatTransUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:nattrans-zero-axiom-note}
Avoids funext by componentwise classifier sameness.
\end{remark}
