\chapter{A Concrete Naming Certificate for $\MetaCICDischargeObligationUp$}
\label{ch:concrete-instances-metacic-discharge-obligation-namecert}
\origin{human}

The $\MetaCICDischargeObligationUp$ packet turns the four discharge obligations isolated in \autoref{ch:metacic-subject-reduction-obstruction} into a finite NameCert carrier. It is a sibling of \autoref{ch:concrete-instances-subjectreduction-namecert}: the latter records the accepted subject-reduction closure surface, while this packet records the four local inputs that must be supplied before the MetaCIC subject-reduction theorem can be consumed without hiding a closed theorem.

\begin{definition}[MetaCIC discharge-obligation carrier]
\label{def:metacic-discharge-obligation-carrier}
A $\MetaCICDischargeObligationUp$ carrier is a finite $\BHist$ packet
$$
D=(B,A,L,P,H,C,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the beta-substitution discharge row $\mathrm{BetaSubstitutionPreservation}$;
\item $A$ is the application-argument discharge row $\mathrm{AppArgTypeStable}$;
\item $L$ is the lambda-domain discharge row $\mathrm{LamDomainSubjectReduction}$;
\item $P$ is the Pi-domain discharge row $\mathrm{PiDomainSubjectReduction}$;
\item $H$ records componentwise $\hsame$ transport for the four discharge rows, the continuation routes, package provenance, and local naming;
\item $C$ records the displayed $\Cont$ routes by which a consumer reads the four discharge rows and the support rows;
\item $G$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and the MetaCIC subject-reduction discharge interface;
\item $N$ is the local $\NameCert_{\MetaCICDischargeObligationUp}$ row.
\end{enumerate}
The carrier contains no unparameterized closed subject-reduction theorem, no hidden proof of any discharge row, no host conversion rule, no erased derivation semantics, and no semantic equality of MetaCIC terms.
\end{definition}

\begin{definition}[MetaCIC discharge-obligation classifier]
\label{def:metacic-discharge-obligation-classifier}
The $\MetaCICDischargeObligationUp$ classifier accepts exactly those carrier reads that factor through
$$
B,A,L,P,H,C,G,N.
$$
The positive reads are the four discharge rows, their componentwise $\hsame$ transports, the displayed $\Cont$ routes, the $\Pkg$ provenance row, and the local $\NameCert$ row. A request for closed subject reduction, host conversion, hidden substitution preservation, quotient transport, or an undisplayed MetaCIC premise is classified as outside the packet.
\end{definition}

\begin{theorem}[MetaCIC discharge-obligation certificate surface]
\label{thm:metacic-discharge-obligation-certificate-surface}
For the carrier of \autoref{def:metacic-discharge-obligation-carrier}, the local $\NameCert_{\MetaCICDischargeObligationUp}$ surface consists exactly of carrier admission for
$$
D=(B,A,L,P,H,C,G,N),
$$
the four discharge rows $B,A,L,P$, componentwise $\hsame$ transport through $H$, displayed continuation reads through $C$, package provenance through $G$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite carrier. Its only discharge coordinates are $B,A,L,P$, and its only support coordinates are $H,C,G,N$.

Use the classifier of \autoref{def:metacic-discharge-obligation-classifier}. It accepts precisely reads through those rows, so the local certificate surface cannot introduce another MetaCIC premise.

Finally read the local $\NameCert$ row $N$. It names the same finite packet and therefore binds the certificate surface to the displayed carrier rather than to a hidden subject-reduction theorem.
\end{proof}

\begin{theorem}[MetaCIC discharge-obligation parameterized interface]
\label{thm:metacic-discharge-obligation-parameterized-interface}
Every consumer that uses $\MetaCICDischargeObligationUp$ as input to the MetaCIC subject-reduction interface must consume all four rows $B,A,L,P$ as the beta-substitution, application-argument, lambda-domain, and Pi-domain discharge rows. The support rows $H,C,G,N$ transport, replay, package, and name those four rows, but they do not add a fifth discharge row and do not produce a closed subject-reduction theorem.
\end{theorem}
\begin{proof}
Begin with the four-row inventory in \autoref{def:metacic-discharge-obligation-carrier}. It names exactly the four hypotheses isolated by \autoref{ch:metacic-subject-reduction-obstruction}.

Apply the certificate-surface theorem. Any subject-reduction-facing read sees $B,A,L,P$ together with transport, route, provenance, and naming support.

The sibling package in \autoref{ch:concrete-instances-subjectreduction-namecert} records the accepted subject-reduction closure surface. This packet instead supplies the finite obligation interface that a consumer must discharge before invoking that surface, so no closed theorem is exported from $H,C,G,N$.
\end{proof}

\begin{theorem}[MetaCIC discharge-obligation non-escape]
\label{thm:metacic-discharge-obligation-non-escape}
Every downstream read of an accepted $\MetaCICDischargeObligationUp$ carrier factors through
$$
B,A,L,P,H,C,G,N.
$$
It cannot inspect a hidden proof of beta substitution, application-argument stability, lambda-domain preservation, Pi-domain preservation, closed subject reduction, host conversion, erased derivation semantics, quotient equality, or an unrecorded MetaCIC reduction principle.
\end{theorem}
\begin{proof}
Read the request through the classifier. Positive reads factor through the four discharge rows or through the displayed support rows.

If the request asks for a closed theorem or for an undisplayed host principle, no coordinate of $D$ can answer it. The request is therefore outside the accepted carrier rather than a hidden route through the certificate.

The transport, continuation, provenance, and naming rows preserve the same inventory. They make the four obligations reusable as finite BEDC data, but they do not create another proof-producing coordinate.
\end{proof}

\closureat{MetaCICDischargeObligationUp}{seedStr}

\begin{closurestatus}{\MetaCICDischargeObligationUp}
  \constructivestory{A $\MetaCICDischargeObligationUp$ packet is generated from the four MetaCIC subject-reduction discharge rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-discharge-obligation-carrier}, \autoref{def:metacic-discharge-obligation-classifier}, \autoref{thm:metacic-discharge-obligation-certificate-surface}, \autoref{thm:metacic-discharge-obligation-parameterized-interface}, and \autoref{thm:metacic-discharge-obligation-non-escape} specify the finite four-obligation carrier, classifier, certificate surface, consumer interface, and non-escape boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not prove beta substitution, application-argument stability, lambda-domain preservation, Pi-domain preservation, closed subject reduction, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier exactness, four-row consumption, transport stability, route replay, provenance, local naming, and non-escape for the same finite packet.}
\end{closurestatus}
