\chapter{A Concrete Naming Certificate for $\MetaCICConfluenceNormalFragmentUp$}
\label{ch:concrete-instances-metacicconfluencenormalfragment-namecert}
\origin{human}

This chapter turns the closed-normal and atom part of
\autoref{ch:metacic-confluence-audit-map} into a finite certificate packet. It
sits next to
\autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert}:
the present packet records the checked confluence fragment already available
for closed normal and atom-shaped sources, while the sibling obstruction packet
keeps substitution-sensitive and subject-reduction boundaries visible.

\begin{definition}[MetaCIC confluence normal-fragment carrier]
\label{def:metacic-confluence-normal-fragment-carrier}
A $\MetaCICConfluenceNormalFragmentUp$ carrier is a finite $\BHist$ packet
$$
J=(T,B,S,A,G,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $T$ is the closed source term row at the empty context;
\item $B$ is the beta-normality row consumed by the closed-normal confluence
fragment;
\item $S$ is the checked $\mathrm{BetaStarStep}$ closed-normal confluence row;
\item $A$ is the atom-shape join row for sort and impossible closed-variable
sources;
\item $G$ is the conditional confluence-boundary row naming the remaining
closed parallel-diamond and substitution-compatibility interfaces;
\item $H$ records componentwise $\hsame$ transports for the source, normality,
star-confluence, atom, boundary, package, and local naming rows;
\item $C$ records the displayed $\Cont$ routes by which confluence consumers
read those rows;
\item $P$ is the $\Pkg$ provenance over MetaCIC beta reduction, closedness,
normality, atom joins, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\MetaCICConfluenceNormalFragmentUp}$ row.
\end{enumerate}
The carrier contains no coordinate for arbitrary closed-term Church--Rosser,
no proof of $\mathrm{BetaParallelDiamondClosed}$, and no proof of
$\mathrm{BetaParallelSubstitutionCompatibility}$.
\end{definition}

\begin{theorem}[MetaCIC confluence normal-fragment NameCert obligations]
\label{thm:metacic-confluence-normal-fragment-namecert-obligations}
The local $\NameCert_{\MetaCICConfluenceNormalFragmentUp}$ surface for
\autoref{def:metacic-confluence-normal-fragment-carrier} consists exactly of
carrier admission, closed-source row readback, beta-normality readback,
checked closed-normal star-confluence readback, atom-shape join readback,
conditional-boundary exposure, componentwise $\hsame$ transport, displayed
$\Cont$ route replay, $\Pkg$ provenance, and non-escape from arbitrary
closed-term Church--Rosser.
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed tuple $J$. The confluence
rows are $S$ for the closed-normal star fragment and $A$ for the atom-shaped
source fragment, with $T$ and $B$ supplying the closed source and beta-normality
inputs.

The row $G$ is part of the obligation surface because it names what remains
conditional: a closed parallel diamond and the substitution compatibility input
that would supply such a diamond. It is read as a boundary row, not as a proof
of the endpoint.

The structural rows $H,C,P,N$ carry exactly this finite packet under transport,
route replay, provenance, and local naming. Since the carrier has no coordinate
for an arbitrary closed-source Church--Rosser theorem, the NameCert surface
cannot export one.
\end{proof}
\leanchecked{BEDC.MetaCIC.betaParallel\_diamond\_closed\_normal}

\begin{theorem}[MetaCIC confluence closed-normal scope]
\label{thm:metacic-confluence-normal-fragment-closed-normal-scope}
Every accepted $\MetaCICConfluenceNormalFragmentUp$ packet exposes closed
multi-step confluence only for sources whose displayed closed row $T$ is paired
with the beta-normality row $B$. A consumer may read the checked row $S$ through
$H,C,P,N$, but it cannot replace $B$ by an arbitrary closed reduction source or
infer full closed-source Church--Rosser for $\mathrm{BetaStarStep}$.
\end{theorem}
\begin{proof}
Read the carrier rows $T,B,S$. The theorem row $S$ is attached to the
closed-normal input surface, so its source is not merely a closed term; it is a
closed term together with the beta-normality evidence recorded by $B$.

Transport and route replay through $H,C,P,N$ preserve the same dependency
shape. They do not add a reduction-to-normal row, a subject-reduction row, or a
closed parallel-diamond row.

Thus the consumer obtains the closed-normal confluence fragment and no stronger
closed-source confluence theorem. The missing arbitrary-source step remains the
boundary row $G$.
\end{proof}
\leanchecked{BEDC.MetaCIC.betaStarStep\_confluence\_closed\_normal}

\begin{theorem}[MetaCIC confluence atom-join scope]
\label{thm:metacic-confluence-normal-fragment-atom-join-scope}
The atom component $A$ of an accepted
$\MetaCICConfluenceNormalFragmentUp$ packet exposes only the sort and
impossible closed-variable joins already present in the confluence substrate.
It may be consumed together with $T,S,H,C,P,N$ as an atom-shaped supplement to
the closed-normal fragment, but it does not provide a beta-redex join for
arbitrary applications, lambdas, or Pi terms.
\end{theorem}
\begin{proof}
Project the atom row $A$. Its role is to record the atom-shaped joins listed in
\autoref{ch:metacic-confluence-audit-map}, where sort sources join directly and
closed variable sources are blocked by the closedness premise.

The row is consumed beside the normal-fragment row $S$, not above it. This keeps
atom geometry and closed-normal confluence inside the same finite packet while
leaving beta-redex and componentwise application branches outside the atom row.

Since no carrier coordinate names a substitution-compatible parallel diamond,
the atom row cannot be repacked as arbitrary closed confluence. It remains a
shape-limited join surface.
\end{proof}

\begin{theorem}[MetaCIC confluence ledger boundary]
\label{thm:metacic-confluence-normal-fragment-ledger-boundary}
Every confluence read exported by an accepted
$\MetaCICConfluenceNormalFragmentUp$ packet factors through
$$
T,B,S,A,G,H,C,P,N.
$$
The packet exposes closed-normal star confluence, atom-shaped joins, and the
conditional-boundary ledger, but it has no row for full parallel diamond,
substitution compatibility, arbitrary closed-term Church--Rosser, host
normalization, or a hidden subject-reduction theorem.
\end{theorem}
\begin{proof}
Start from \autoref{def:metacic-confluence-normal-fragment-carrier}. The only
consumer-visible confluence rows are $S$ and $A$, and the only row naming a
larger confluence endpoint is the conditional boundary row $G$.

Apply \autoref{thm:metacic-confluence-normal-fragment-namecert-obligations}.
It accounts for carrier admission, fragment readback, boundary exposure, and
the structural rows that route the packet.

No listed coordinate contains the full parallel diamond, the substitution
compatibility input, a host normalization principle, or subject reduction. The
ledger is therefore exhausted by the displayed rows.
\end{proof}

\begin{theorem}[MetaCIC confluence normal-fragment public certificate]
\label{thm:metacic-confluence-normal-fragment-public-certificate}
The public certificate exported by
$\MetaCICConfluenceNormalFragmentUp$ is the finite packet
$J=(T,B,S,A,G,H,C,P,N)$ together with the four surfaces of
\autoref{thm:metacic-confluence-normal-fragment-namecert-obligations},
\autoref{thm:metacic-confluence-normal-fragment-closed-normal-scope},
\autoref{thm:metacic-confluence-normal-fragment-atom-join-scope}, and
\autoref{thm:metacic-confluence-normal-fragment-ledger-boundary}. A downstream
consumer may cite the checked closed-normal and atom fragments through this
packet while the full arbitrary closed-source confluence claim remains outside
the certificate.
\end{theorem}
\begin{proof}
The NameCert obligations identify the carrier and its local structural rows.
The closed-normal theorem fixes the positive $\mathrm{BetaStarStep}$ scope, and
the atom theorem fixes the available shape-limited joins.

The ledger theorem then exhausts the exported rows. It lists the conditional
boundary row $G$ as a boundary, so the public certificate does not erase the
remaining closed parallel-diamond and substitution-compatibility inputs.

Together these rows form a finite BEDC certificate: positive where the Lean
fragment is checked, and explicitly bounded where arbitrary closed confluence is
not part of the packet.
\end{proof}

\closureat{MetaCICConfluenceNormalFragmentUp}{seedStr}
\closureat{MetaCICConfluenceNormalFragmentUp}{obligationStr}[BEDC.MetaCIC.betaParallel\_diamond\_closed\_normal]
\closureat{MetaCICConfluenceNormalFragmentUp}{scopedStr}[BEDC.MetaCIC.betaStarStep\_confluence\_closed\_normal]

\begin{closurestatus}{\MetaCICConfluenceNormalFragmentUp}
  \constructivestory{A $\MetaCICConfluenceNormalFragmentUp$ packet is generated from a closed source row, beta-normality row, checked closed-normal confluence row, atom-join row, conditional-boundary row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:metacic-confluence-normal-fragment-carrier}, \autoref{thm:metacic-confluence-normal-fragment-namecert-obligations}, \autoref{thm:metacic-confluence-normal-fragment-closed-normal-scope}, \autoref{thm:metacic-confluence-normal-fragment-atom-join-scope}, \autoref{thm:metacic-confluence-normal-fragment-ledger-boundary}, and \autoref{thm:metacic-confluence-normal-fragment-public-certificate} bind the closed-normal and atom confluence fragment as a finite NameCert packet.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.MetaCIC.betaStarStep\_confluence\_closed\_normal}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close arbitrary closed-term Church--Rosser, $\mathrm{BetaParallelDiamondClosed}$, $\mathrm{BetaParallelSubstitutionCompatibility}$, host normalization, or a public standard bridge.}
  \upgradepath{The next formal step is a checked certificate wrapper over the same carrier and a bridge once the remaining closed confluence boundary is discharged.}
\end{closurestatus}
