\chapter{A Concrete Naming Certificate for $\NormalFormConsistencySealUp$}
\label{ch:concrete-instances-normal-form-consistency-seal-namecert}
\origin{human}

The $\NormalFormConsistencySealUp$ packet gives the closed-normal branch of
\autoref{ch:closed-metacic-consistency-assembly} a finite NameCert object. It
sits between the closed-context carrier of
\autoref{ch:concrete-instances-closedtermcontextseal-namecert} and the
subject-reduction socket of
\autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}:
the seal records what the normal-form consistency theorem consumes, and it
keeps the missing subject-reduction discharge outside the packet.

\begin{definition}[Normal-form consistency seal carrier]
\label{def:normal-form-consistency-seal-carrier}
A $\NormalFormConsistencySealUp$ carrier is a finite $\BHist$ packet
$$
S=(T,F,N,K,X,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the empty-context MetaCIC typing row for the inspected closed
proof candidate;
\item $F$ is the internal false-type row named by that typing certificate;
\item $N$ is the beta-strong normality row for the same inspected candidate;
\item $K$ is the checked closed-normal consistency row naming
$\mathsf{BEDC.MetaCIC.closed\_normal\_consistency\_assembly}$;
\item $X$ is the subject-reduction boundary row, read only through
\autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert};
\item $H$ records componentwise $\hsame$ transports for the typing, false,
normality, theorem, boundary, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ routes by which a consumer reads those
finite rows;
\item $P$ is the $\Pkg$ provenance over MetaCIC typing, closed contexts,
beta-strong normality, $\BHist$, $\hsame$, $\Cont$, and sibling $\NameCert$
rows;
\item $L$ is the local $\NameCert_{\NormalFormConsistencySealUp}$ row.
\end{enumerate}
The carrier has no coordinate for arbitrary closed reduction, no closed
subject-reduction theorem, no hidden normalization transport, and no host-level
consistency principle.
\end{definition}
\leanchecked{BEDC.Derived.NormalFormConsistencySealUp.NormalFormConsistencySealTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Normal-form consistency seal obligations]
\label{thm:normal-form-consistency-seal-obligations}
Every accepted $\NormalFormConsistencySealUp$ packet binds a local NameCert
surface whose obligations are exactly carrier admission, classifier exactness
for $S=(T,F,N,K,X,H,C,P,L)$, readback of the checked closed-normal theorem row
$K$, componentwise $\hsame$ transport, displayed $\Cont$ route replay, package
provenance, and non-escape from the subject-reduction boundary row $X$.
\end{theorem}
\begin{proof}
Carrier admission is the displayed finite packet of
\autoref{def:normal-form-consistency-seal-carrier}. Classifier exactness is
componentwise: two seal packets compare only through the rows
$T,F,N,K,X,H,C,P,L$ and the displayed $\hsame$ transports.

The theorem row $K$ is read together with $T,F,N$, so the consumer obtains only
the normal-form contradiction already assembled in
$\mathsf{BEDC.MetaCIC.closed\_normal\_consistency\_assembly}$. The structural
rows $H,C,P,L$ preserve that same read under transport, route replay,
provenance, and local naming.

The boundary row $X$ is named but not discharged. Therefore the NameCert surface
records the subject-reduction frontier without turning it into a closed
subject-reduction theorem.
\end{proof}

\begin{theorem}[Normal-form consistency seal subject-reduction boundary]
\label{thm:normal-form-consistency-seal-subject-reduction-boundary}
The $\NormalFormConsistencySealUp$ packet factors every preservation-facing read
through \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}
and every closed-context read through
\autoref{ch:concrete-instances-closedtermcontextseal-namecert}. Hence the seal
may eliminate a closed beta-strong proof candidate of the internal false row,
but it does not provide a route from an arbitrary closed proof candidate to such
a normal endpoint.
\end{theorem}
\begin{proof}
For closed-context data, project the rows $T,F,N$ together with the provenance
row $P$. These rows are interpreted through the closed-term context seal, which
keeps the empty-context typing and closedness information as finite BEDC data.

For preservation-facing data, project the boundary row $X$. Its only named
consumer is the subject-reduction discharge socket, so the seal can cite the
frontier while leaving the beta, application-argument, lambda-domain, and
Pi-domain discharge rows outside the present carrier.

Combining these projections gives the normal-form use of $K$ without a
reduction-to-normal-form bridge for arbitrary closed proof candidates.
\end{proof}

\begin{theorem}[Normal-form consistency seal closed-normal frontier]
\label{thm:normal-form-consistency-seal-closed-normal-frontier}
Let $S=(T,F,N,K,X,H,C,P,L)$ be an accepted $\NormalFormConsistencySealUp$
packet. The packet may export the closed-normal contradiction route exactly
through the rows $T,F,N,K,H,C,P,L$: the typing row $T$, internal false row
$F$, beta-strong normality row $N$, checked closed-normal theorem row $K$,
componentwise transports, displayed continuation replay, provenance, and local
naming. The row $X$ remains only the visible subject-reduction boundary
citation and cannot discharge arbitrary subject reduction or turn an arbitrary
closed proof candidate into the closed-normal endpoint consumed by $K$.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:normal-form-consistency-seal-carrier}. The positive
closed-normal route is carried by $T,F,N,K$ and by the structural rows
$H,C,P,L$ that transport, replay, source, and name the same finite packet.

Apply \autoref{thm:normal-form-consistency-seal-obligations}. Its readback
clause exposes the checked theorem row $K$ only together with the displayed
typing, false, and beta-strong normality rows, while its non-escape clause
keeps the subject-reduction boundary row separate.

Finally use
\autoref{thm:normal-form-consistency-seal-subject-reduction-boundary}. That
boundary permits the seal to cite $X$ as the open preservation-facing socket,
but it does not supply a closed subject-reduction theorem. Hence consumers may
use the closed-normal contradiction route through $T,F,N,K,H,C,P,L$ and no
stronger subject-reduction route.
\end{proof}

\begin{theorem}[Normal-form consistency seal non-escape]
\label{thm:normal-form-consistency-seal-nonescape}
No consumer of an accepted $\NormalFormConsistencySealUp$ packet can read a
claim stronger than the displayed normal-form consistency surface. In
particular, the packet exports neither full closed consistency, nor closed
subject reduction, nor hidden normalization transport, nor a host equality
principle beyond the displayed $\hsame$ rows.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates in
\autoref{def:normal-form-consistency-seal-carrier}. The only theorem coordinate
is $K$, and $K$ is explicitly the closed-normal consistency row. The row $X$
records the subject-reduction boundary rather than a discharge of that
boundary.

The remaining coordinates $H,C,P,L$ are structural rows for transport, routing,
provenance, and local naming. They preserve the finite packet but do not add
new MetaCIC reduction, typing, or normalization facts.

Thus every public read stays inside the visible normal-form seal. Anything
requiring arbitrary closed reduction or full consistency must pass through a
separate subject-reduction discharge packet.
\end{proof}

\begin{theorem}[Normal-form consistency seal vision handoff]
\label{thm:normal-form-consistency-seal-vision-handoff}
The concrete $\NormalFormConsistencySealUp$ packet realizes the assembled node
of \autoref{ch:closed-metacic-consistency-assembly} as a finite BEDC object:
the closed-normal theorem row is public inside the seal, while the lift to full
closed consistency remains blocked until the subject-reduction socket is
filled by its own discharge data.
\end{theorem}
\begin{proof}
The vision chapter separates three items: the available closed-normal
consistency theorem, the missing subject-reduction route, and the blocked full
closed-consistency conclusion. The carrier of
\autoref{def:normal-form-consistency-seal-carrier} mirrors that separation by
placing $K$ and $X$ in different rows.

The obligation theorem and boundary theorem show how consumers may use $K$
with the closed-context rows while routing every preservation-facing request to
the sibling socket. The non-escape theorem then prevents the packet from being
read as a stronger consistency claim.

Therefore the handoff is a concrete finite packet rather than a promise of a
larger MetaCIC theorem.
\end{proof}

\begin{theorem}[Normal-form consistency seal continuation replay]
\label{thm:normal-form-consistency-seal-continuation-replay}
Let $S=(T,F,N,K,X,H,C,P,L)$ be an accepted
$\NormalFormConsistencySealUp$ packet. Every continuation replay read first
projects the MetaCIC typing row $T$, the false-type row $F$, the
beta-strong normality row $N$, the closed-normal consistency row $K$, and the
subject-reduction boundary row $X$, and only then reads through the displayed
$\Cont$ row $C$. No continuation consumer may bypass these rows to obtain a
closed subject-reduction discharge.
\end{theorem}
\begin{proof}
Read the carrier in
\autoref{def:normal-form-consistency-seal-carrier}. The packet lists
$T,F,N,K,X$ before the structural rows, so any replay route has a displayed
typing, false-type, normality, closed-normal consistency, and boundary source.

Apply the obligation surface of
\autoref{thm:normal-form-consistency-seal-obligations}. It makes the
continuation row part of the finite NameCert obligations for the same carrier.

The subject-reduction boundary theorem
\autoref{thm:normal-form-consistency-seal-subject-reduction-boundary} and the
non-escape theorem
\autoref{thm:normal-form-consistency-seal-nonescape} keep the read from
becoming a closed subject-reduction theorem. Thus continuation replay is a
route through $C$ after the displayed rows $T,F,N,K,X$ have been projected.
\end{proof}

\begin{theorem}[Normal-form consistency seal provenance exactness]
\label{thm:normal-form-consistency-seal-provenance-exactness}
For an accepted packet $S=(T,F,N,K,X,H,C,P,L)$, every dependency claim made by
the $\NormalFormConsistencySealUp$ surface is confined to the provenance row
$P$ over MetaCIC typing, closed contexts, beta-strong normality, $\BHist$,
$\hsame$, $\Cont$, and sibling $\NameCert$ rows. The packet contains no
additional provenance route for full closed consistency or closed subject
reduction.
\end{theorem}
\begin{proof}
Carrier admission in
\autoref{def:normal-form-consistency-seal-carrier} displays $P$ as the only
package provenance coordinate. The remaining structural rows $H,C,L$ transport
and name the packet but do not create dependency claims.

Use \autoref{thm:normal-form-consistency-seal-obligations} to identify the
obligation rows governed by that provenance: MetaCIC typing, closed-context
data, beta-strong normality, history transport, continuation routing, and the
local naming surface.

The boundary result
\autoref{thm:normal-form-consistency-seal-subject-reduction-boundary} and
\autoref{thm:normal-form-consistency-seal-nonescape} exclude a hidden
dependency on full closed consistency or a closed subject-reduction theorem.
Therefore every dependency claim remains exactly in the displayed row $P$.
\end{proof}

\begin{theorem}[Normal-form consistency seal local naming boundary]
\label{thm:normal-form-consistency-seal-local-naming-boundary}
For an accepted packet $S=(T,F,N,K,X,H,C,P,L)$, the local naming row $L$ names
only this finite normal-form consistency seal. It identifies the displayed
carrier, obligations, subject-reduction boundary, continuation replay, and
provenance rows, but it does not discharge closed subject reduction.
\end{theorem}
\begin{proof}
The carrier of \autoref{def:normal-form-consistency-seal-carrier} makes $L$
the local naming coordinate for the finite seal. It names the same packet rows
$T,F,N,K,X,H,C,P$ and no row outside the packet.

The obligation theorem
\autoref{thm:normal-form-consistency-seal-obligations} supplies the local
NameCert surface, while
\autoref{thm:normal-form-consistency-seal-subject-reduction-boundary} marks
$X$ as a boundary row rather than a discharge row.

The non-escape theorem
\autoref{thm:normal-form-consistency-seal-nonescape} prevents the local name
from being read as full closed consistency, closed subject reduction, hidden
normalization transport, or host equality. Hence $L$ names the finite seal and
nothing stronger.
\end{proof}

\closureat{NormalFormConsistencySealUp}{seedStr}

\begin{closurestatus}{\NormalFormConsistencySealUp}
  \constructivestory{A $\NormalFormConsistencySealUp$ packet is generated from closed-context typing, false-type, beta-strong normality, closed-normal consistency, subject-reduction boundary, transport, continuation, provenance, and local naming rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:normal-form-consistency-seal-carrier}, \autoref{thm:normal-form-consistency-seal-obligations}, \autoref{thm:normal-form-consistency-seal-subject-reduction-boundary}, \autoref{thm:normal-form-consistency-seal-nonescape}, \autoref{thm:normal-form-consistency-seal-vision-handoff}, \autoref{thm:normal-form-consistency-seal-continuation-replay}, \autoref{thm:normal-form-consistency-seal-provenance-exactness}, and \autoref{thm:normal-form-consistency-seal-local-naming-boundary} bind the finite normal-form consistency seal, its visible subject-reduction boundary, continuation replay, provenance exactness, and local naming boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter keeps full closed consistency, closed subject reduction, hidden normalization transport, and host equality outside the finite seal.}
  \upgradepath{Obligation closure is the next paper-side step: carrier admission, boundary routing, normal-form non-escape, continuation replay, provenance, and local naming must be bound as checked obligations for the same packet.}
\end{closurestatus}
