\chapter{A Concrete Naming Certificate for $\ClosedNormalConsistencyBoundaryUp$}
\label{ch:concrete-instances-closed-normal-consistency-boundary-namecert}
\origin{ai}

The $\ClosedNormalConsistencyBoundaryUp$ packet realizes the closed-normal MetaCIC consistency assembly of \autoref{ch:closed-metacic-consistency-assembly} as finite BEDC data. It sits beside the obstruction ledger of \autoref{ch:concrete-instances-metacic-reduction-obstruction-ledger-namecert} and the subject-reduction frontier of \autoref{ch:concrete-instances-metacic-subject-reduction-frontier-namecert}: those packets display the blocked lift, while this one records the positive normal-form consistency node and the exact boundary that prevents it from becoming full closed consistency.

\begin{definition}[Closed-normal consistency boundary carrier]
\label{def:closed-normal-consistency-boundary-carrier}
A $\ClosedNormalConsistencyBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(T,C,N,F,O,R,H,Q,P,M)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the empty-context MetaCIC typing row for the closed proof candidate;
\item $C$ is the closedness row for the same term;
\item $N$ is the beta-strong normality row consumed by the closed-normal consistency theorem;
\item $F$ is the displayed internal false-type row;
\item $O$ is the checked no-closed-normal-false row and the closed-normal consistency assembly row read as positive obstruction-to-false data;
\item $R$ is the subject-reduction refusal row inherited from the closed reduction obstruction;
\item $H$ records componentwise $\hsame$ transport for the typing, closedness, normality, false-type, positive theorem, refusal, route, provenance, and naming rows;
\item $Q$ records the displayed $\Cont$ routes by which a consumer reads the positive closed-normal node before it reaches the refusal boundary;
\item $P$ is the $\Pkg$ provenance over the MetaCIC consistency assembly, the reduction obstruction ledger, the subject-reduction frontier, $\BHist$, $\hsame$, $\Cont$, and local certificate rows;
\item $M$ is the local $\NameCert_{\ClosedNormalConsistencyBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for an unparameterized closed subject-reduction theorem, no route from arbitrary closed proofs to beta-strong normal proofs, no hidden discharge of beta substitution or dependent-codomain stability, and no host consistency theorem outside the displayed rows.
\end{definition}

\begin{theorem}[Closed-normal consistency boundary NameCert obligations]
\label{thm:closed-normal-consistency-boundary-namecert-obligations}
For an accepted $\ClosedNormalConsistencyBoundaryUp$ carrier $B=(T,C,N,F,O,R,H,Q,P,M)$, the local $\NameCert$ surface exposes exactly the empty-context typing row $T$, closedness row $C$, beta-strong normality row $N$, false-type row $F$, positive closed-normal consistency row $O$, subject-reduction refusal row $R$, componentwise transport $H$, displayed replay routes $Q$, package provenance $P$, and local naming $M$. A consumer may eliminate only the closed normal false-proof configuration displayed by $T,C,N,F,O$; it may not use the packet as a full closed consistency theorem.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedNormalConsistencyBoundaryUp.ClosedNormalConsistencyBoundaryUp\_taste\_gate\_boundary}
\begin{proof}
Project the carrier of \autoref{def:closed-normal-consistency-boundary-carrier}. The rows $T,C,N,F$ display the precise closed normal false-proof input consumed by the positive theorem row $O$.

Use the assembly chapter \autoref{ch:closed-metacic-consistency-assembly}. Its positive node is closed-normal consistency, so the elimination route requires beta-strong normality as an input row rather than deriving it from an arbitrary closed proof.

Use the sibling obstruction ledger \autoref{ch:concrete-instances-metacic-reduction-obstruction-ledger-namecert} and the subject-reduction frontier \autoref{ch:concrete-instances-metacic-subject-reduction-frontier-namecert}. They account for the missing lift through the displayed refusal and frontier rows, which this packet records as $R$ instead of erasing.

The support rows $H,Q,P,M$ transport, replay, package, and name the same inventory. Since no further coordinate is present, the local certificate exposes the closed-normal boundary and does not export closed subject reduction or full closed consistency.
\end{proof}

\begin{theorem}[Closed-normal consistency boundary non-discharge]
\label{thm:closed-normal-consistency-boundary-non-discharge}
The $\ClosedNormalConsistencyBoundaryUp$ packet does not discharge the MetaCIC subject-reduction frontier. Every request to turn an arbitrary closed false proof into the beta-strong input required by $O$ must pass through the refusal row $R$ and the sibling frontier packets of \autoref{ch:concrete-instances-metacic-reduction-obstruction-ledger-namecert} and \autoref{ch:concrete-instances-metacic-subject-reduction-frontier-namecert}; no compiler semantics, host normalization theorem, quotient conversion, hidden discharge proof, or ambient consistency principle can replace those rows.
\end{theorem}
\begin{proof}
Begin with the positive route. The carrier exposes $O$ only together with $T,C,N,F$, so the theorem it packages is the closed-normal node described in \autoref{ch:closed-metacic-consistency-assembly}.

Now consider a request for full closed consistency. Such a request needs a route from arbitrary closed typing to the beta-strong row $N$ while preserving the false-type row $F$.

The only row addressing that route is $R$. By the construction of the packet, $R$ points outward to the obstruction ledger and subject-reduction frontier rather than supplying the missing preservation theorem internally.

Finally inspect the remaining support rows. Transport, replay, provenance, and local naming preserve the displayed packet, but none of them adds compiler semantics, quotient conversion, a hidden discharge proof, or an ambient consistency principle. Thus the boundary is recorded without discharging it.
\end{proof}

\closureat{ClosedNormalConsistencyBoundaryUp}{seedStr}

\begin{closurestatus}{\ClosedNormalConsistencyBoundaryUp}
  \constructivestory{A $\ClosedNormalConsistencyBoundaryUp$ packet is generated from empty-context typing, closedness, beta-strong normality, internal false typing, the positive closed-normal consistency row, the subject-reduction refusal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:closed-normal-consistency-boundary-carrier}, \autoref{thm:closed-normal-consistency-boundary-namecert-obligations}, and \autoref{thm:closed-normal-consistency-boundary-non-discharge} bind the finite positive-normal node and its blocked closed-consistency lift.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove closed subject reduction, beta-substitution preservation, dependent-codomain stability, full closed consistency, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, exact positive-theorem consumption, refusal replay, provenance accounting, transport stability, and non-escape for the same finite packet.}
\end{closurestatus}
