\chapter{A Concrete Naming Certificate for $\SemidefiniteConeUp$}
\label{ch:concrete-instances-semidefinitecone-namecert}

The $\SemidefiniteConeUp$ interface names the finite certificate surface used by semidefinite programming over symmetric matrix data. In the external optimization presentation of Boyd--Vandenberghe 2004, the semidefinite cone is read through symmetric matrices whose quadratic form is nonnegative on every vector. The BEDC packet below keeps only the displayed finite rows required to name that surface: matrix rows, vector-space rows, convex-combination ledgers, bilinear-form pairings, order witnesses, and package provenance.

\section{Carrier packet}
\label{sec:semidefinitecone-carrier-packet}

\begin{definition}[SemidefiniteCone carrier packet]
\label{def:semidefinitecone-bhist-carrier}
A $\SemidefiniteConeUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
(M,V,C,B,N,P)
$$
with the following rows:
\begin{enumerate}
\item $M$ is a symmetric-matrix row read through $\MatrixUp$;
\item $V$ is a vector-space row read through $\VecSpaceUp$ over the same scalar boundary as $M$;
\item $C$ is a convex-combination ledger from $\ConvexSetUp$ for displayed matrix rows;
\item $B$ is a bilinear-form pairing row from $\BilinFormUp$ that reads $v^{T}Mv$ as a scalar row for displayed vectors $v$;
\item $N$ is an order and nonnegativity witness row saying that every vector row explicitly carried by the packet has nonnegative paired scalar value through $\OrderUp$;
\item $P$ is the $\Pkg$ provenance tying these rows to the cited $\MatrixUp$, $\VecSpaceUp$, $\ConvexSetUp$, $\BilinFormUp$, and $\OrderUp$ certificate boundaries.
\end{enumerate}
The carrier predicate is $\mathsf{SDConePacket}(M,V,C,B,N,P)$. Two accepted packets classify together only when their matrix, vector-space, convex-ledger, bilinear-pairing, nonnegativity, and provenance rows transport by displayed $\hsame$ and by the same $\Cont$ routes named in $P$.
\end{definition}

\begin{theorem}[SemidefiniteCone carrier stability]
\label{thm:semidefinitecone-carrier-stability}
Let $D=(M,V,C,B,N,P)$ be an accepted $\SemidefiniteConeUp$ carrier and let $D'=(M',V',C',B',N',P')$ be obtained by displayed $\hsame$ transport of all six rows, with the same $\Cont$ routes through the cited certificate boundaries. Then $D'$ is again an accepted carrier, and its classifier reads exactly the transported matrix, vector, convex, bilinear, nonnegativity, and provenance rows.
\end{theorem}
\leanchecked{BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_carrier\_stability}
\begin{proof}
Project the six coordinates of \autoref{def:semidefinitecone-bhist-carrier}. The matrix and vector-space coordinates are ordinary displayed rows, so $\hsame$ transport gives the rows $M'$ and $V'$ with the same scalar boundary.

Next transport the convex-combination ledger and the bilinear-form row. The stated $\Cont$ routes identify the same matrix and vector slots on the transported packet, so the pairing row remains readable as the displayed scalar value attached to $M'$ and $V'$.

Finally transport the order/nonnegativity witness and the package row. Repacking these transported rows gives $\mathsf{SDConePacket}(M',V',C',B',N',P')$, and the classifier has no coordinate other than the transported finite rows.
\end{proof}

\begin{theorem}[SemidefiniteCone cone-operation ledger]
\label{thm:semidefinitecone-cone-operation-ledger}
For accepted $\SemidefiniteConeUp$ carriers $D_0$ and $D_1$ over a common transported vector-space and scalar boundary, the cone-operation surface consists of finite rows for displayed matrix addition, displayed nonnegative scalar multiplication, the convex-combination ledger inherited from $\ConvexSetUp$, the bilinear pairing rows inherited from $\BilinFormUp$, the order witness rows inherited from $\OrderUp$, and $\Pkg$ provenance tying the operation packet to $D_0$ and $D_1$.

The operation ledger exports no spectral decomposition, no eigenvalue existence claim, no analytic closure of the cone, and no positivity predicate from a host matrix library.
\end{theorem}
\leanchecked{BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_cone\_operation\_ledger}
\begin{proof}
Read the two input carriers through \autoref{def:semidefinitecone-bhist-carrier}. Their matrix rows and common vector-space row supply the finite endpoints of the operation packet.

For addition, use the displayed $\MatrixUp$ addition row and the $\ConvexSetUp$ ledger that records the resulting matrix row as a convex or conic combination with visible coefficients. For nonnegative scalar multiplication, use the scalar row together with the $\OrderUp$ witness that the coefficient is nonnegative.

The bilinear-form row then reads each displayed vector test against the resulting matrix row. Because each nonnegativity assertion is an explicit order row and all dependencies are named in $\Pkg$, the ledger is exhausted by finite BEDC rows and does not appeal to spectral or analytic facts.
\end{proof}

\begin{theorem}[SemidefiniteCone dual-pairing boundary]
\label{thm:semidefinitecone-dual-pairing-boundary}
Every accepted $\SemidefiniteConeUp$ packet exposes its dual-facing read only through the displayed $\BilinFormUp$ pairing row and the transported $\OrderUp$ nonnegativity witness. A consumer may compare a matrix row with a displayed vector or test row through the finite scalar value named by the packet, $\hsame$ transport, $\Cont$ routes, and $\Pkg$ provenance.

The packet does not assert self-duality of the cone, closedness under analytic limits, or equality with any host-space positive-semidefinite predicate.
\end{theorem}
\leanchecked{BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_dual\_pairing\_empty\_boundary}
\begin{proof}
Project the bilinear-form row $B$ and the nonnegativity row $N$ from the carrier. These are the only coordinates that connect a matrix row to scalar comparison data.

A dual-facing consumer therefore receives a scalar pairing value only after following the displayed $\BilinFormUp$ row and the package routes named by $P$. The comparison of that scalar value with zero is an $\OrderUp$ row, transported by $\hsame$ when the underlying matrix or vector row is replaced.

No coordinate in the carrier contains a host dual cone, a topological closure assertion, or a spectral certificate. Thus the boundary is exactly the finite pairing-and-order surface stated in the theorem.
\end{proof}

\begin{theorem}[SemidefiniteCone NameCert obligation surface]
\label{thm:semidefinitecone-namecert-obligation-surface}
The local $\NameCert_{\SemidefiniteConeUp}$ obligation surface consists of five finite rows:
\begin{enumerate}
\item carrier: the $\mathsf{BHist}$ packet of \autoref{def:semidefinitecone-bhist-carrier};
\item classifier and stability: the displayed transport statement of \autoref{thm:semidefinitecone-carrier-stability};
\item cone-operation ledger: the addition and nonnegative scalar-multiplication rows of \autoref{thm:semidefinitecone-cone-operation-ledger};
\item dual-pairing boundary: the bilinear pairing and order rows of \autoref{thm:semidefinitecone-dual-pairing-boundary};
\item provenance: the $\Pkg$ row tying the packet to $\MatrixUp$, $\VecSpaceUp$, $\ConvexSetUp$, $\BilinFormUp$, and $\OrderUp$.
\end{enumerate}
These rows are the full public seed surface for the semidefinite-cone name.
\end{theorem}
\begin{proof}
The carrier row supplies the displayed matrix, vector-space, convex-ledger, bilinear-pairing, order, and provenance coordinates. This fixes the source domain of the name.

The stability row supplies the classifier behavior under $\hsame$ and $\Cont$ transport. The cone-operation row records the only operation reads available to downstream optimization packets, and the dual-pairing boundary records the only scalar comparison reads.

The provenance row names every dependency certificate used by the packet. Since the construction withholds spectral decomposition, eigenvalue existence, analytic closure, and host matrix positivity, the listed rows exhaust the $\NameCert_{\SemidefiniteConeUp}$ obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_namecert\_obligation\_surface}

\begin{theorem}[SemidefiniteCone scoped provenance package]
\label{thm:semidefinitecone-scoped-provenance-package}
Every accepted $\SemidefiniteConeUp$ packet exposes its public scope only
through $\MatrixUp$ symmetric-matrix rows, $\VecSpaceUp$ vector rows,
$\ConvexSetUp$ cone-combination rows, $\BilinFormUp$ pairing rows, $\OrderUp$
nonnegativity rows, and $\mathsf{Pkg}$ provenance, transported by displayed
$\hsame$ and $\Cont$ routes. The scoped package exports no spectral
decomposition, eigenvalue existence theorem, analytic closure of the cone,
self-duality assertion, host matrix positivity predicate, or standard bridge
data.
\end{theorem}
\leanchecked{BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_scoped\_provenance\_package}
\begin{proof}
Project the carrier of \autoref{def:semidefinitecone-bhist-carrier}. Its six
coordinates are the symmetric-matrix row, vector-space row, convex-combination
ledger, bilinear-pairing row, order/nonnegativity witness, and package
provenance, so the carrier has no dependency outside the displayed BEDC rows.

Use \autoref{thm:semidefinitecone-carrier-stability} for classifier transport.
The only permitted motion of an accepted packet is componentwise $\hsame$
transport along the same $\Cont$ routes named by the package row.

Use \autoref{thm:semidefinitecone-cone-operation-ledger} for the operation
surface and \autoref{thm:semidefinitecone-dual-pairing-boundary} for the
scalar-facing boundary. These two rows consume precisely the displayed
cone-operation, pairing, and order dependencies, then return to the same finite
packet surface.

Finally apply \autoref{thm:semidefinitecone-namecert-obligation-surface}. The
NameCert surface has no remaining coordinate from which a consumer could read
spectral decomposition, eigenvalue existence, analytic closure, self-duality,
host matrix positivity, or standard bridge data, so the scoped package is
exactly the listed BEDC provenance boundary.
\end{proof}

\begin{theorem}[SemidefiniteCone public packet certificate]
\label{thm:semidefinitecone-public-packet-certificate}
Whenever the carrier stability, cone-operation ledger, dual-pairing boundary,
$\NameCert_{\SemidefiniteConeUp}$ obligation surface, and scoped provenance
package rows of
\autoref{thm:semidefinitecone-carrier-stability},
\autoref{thm:semidefinitecone-cone-operation-ledger},
\autoref{thm:semidefinitecone-dual-pairing-boundary},
\autoref{thm:semidefinitecone-namecert-obligation-surface}, and
\autoref{thm:semidefinitecone-scoped-provenance-package} hold, the displayed
$\mathsf{BHist}$ matrix row, vector-space row, convex-ledger row,
bilinear-pairing row, order row, provenance row, and package row form the
exported public $\SemidefiniteConeUp$ packet. This public packet is the
consumer-facing certificate surface for the semidefinite-cone name, and it
exports no row beyond the ten-field roadmap entries already supplied by those
finite BEDC dependencies.
\end{theorem}
\begin{proof}
Use \autoref{thm:semidefinitecone-carrier-stability} to fix the transported
matrix, vector-space, convex-ledger, bilinear-pairing, order, and provenance
coordinates of the accepted packet.

Use \autoref{thm:semidefinitecone-cone-operation-ledger} and
\autoref{thm:semidefinitecone-dual-pairing-boundary} to expose the only
operation and scalar-comparison rows available to a consumer. These two rows
are the cone-operation and dual-facing entries of the public packet.

Finally apply \autoref{thm:semidefinitecone-namecert-obligation-surface} and
\autoref{thm:semidefinitecone-scoped-provenance-package}. Together they identify
the carrier, classifier, stability, ledger, exactness, provenance, scope,
absence, package, and bridge-boundary slots of the ten-field roadmap template,
so the public packet is exactly their conjunction over the displayed BEDC rows.
\end{proof}

\begin{theorem}[SemidefiniteCone standard bridge boundary]
\label{thm:semidefinitecone-standard-bridge-boundary}
Any standard bridge for the public $\SemidefiniteConeUp$ packet must read and
write exactly the displayed symmetric $\MatrixUp$ row, $\VecSpaceUp$ row,
$\ConvexSetUp$ cone-operation ledger, $\BilinFormUp$ pairing row, $\OrderUp$
nonnegativity witnesses, $\hsame$ and $\Cont$ transport rows, and $\mathsf{Pkg}$
provenance of \autoref{thm:semidefinitecone-public-packet-certificate}. The
bridge boundary exports no spectral decomposition, eigenvalue existence,
analytic closure, self-duality theorem, or host matrix positivity predicate.
\end{theorem}
\begin{proof}
Project the public packet theorem. Its carrier coordinates are the symmetric
matrix row, compatible vector-space row, convex cone-operation ledger,
bilinear-pairing row, order nonnegativity witnesses, transport rows, and
provenance rows.

The standard-facing bridge may therefore read those coordinates and may write
back only the same rows after $\hsame$ and $\Cont$ transport. This is the full
boundary because the public packet certificate has no additional output slot.

Spectral decomposition, eigenvalue existence, analytic closure, self-duality,
and host matrix positivity are not among the projected rows. They cannot be
exported by a bridge whose domain and codomain are restricted to the displayed
public packet.
\end{proof}

\closureat{SemidefiniteConeUp}{seedStr}
\closureat{SemidefiniteConeUp}{obligationStr}
\closureat{SemidefiniteConeUp}{scopedStr}[BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_dual\_pairing\_empty\_boundary]
\closureat{SemidefiniteConeUp}{publicStr}[BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_dual\_pairing\_empty\_boundary]
\closureat{SemidefiniteConeUp}{bridgedStr}
\closureat{SemidefiniteConeUp}{matureStr}

\begin{closurestatus}{\SemidefiniteConeUp}
  \constructivestory{A semidefinite-cone packet is generated by a symmetric $\MatrixUp$ row, a compatible $\VecSpaceUp$ row, a $\ConvexSetUp$ cone-operation ledger, a $\BilinFormUp$ pairing row, displayed $\OrderUp$ nonnegativity witnesses, and $\Pkg$ provenance for those finite rows.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:semidefinitecone-public-packet-certificate}, \autoref{thm:semidefinitecone-standard-bridge-boundary}, \autoref{thm:semidefinitecone-cone-operation-ledger}, and \autoref{thm:semidefinitecone-dual-pairing-boundary} bind the public packet certificate, standard bridge boundary, cone-operation ledger, and dual-pairing boundary as the mature packet surface over the displayed $\MatrixUp$, $\VecSpaceUp$, $\ConvexSetUp$, $\BilinFormUp$, $\OrderUp$, $\hsame$, $\Cont$, and $\Pkg$ rows visible to $\SemidefiniteConeUp$.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.SemidefiniteConeUp.SemidefiniteConePacket\_dual\_pairing\_empty\_boundary}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close spectral decomposition, eigenvalue existence, analytic closure, self-duality, host matrix positivity, or a machine-checked standard bridge.}
  \upgradepath{No further paper-side theory grade remains; formal bridge verification remains on the verification axis.}
\end{closurestatus}
