\chapter{A Concrete Naming Certificate for $\MetaCICAuditSynthesisPacketUp$}
\label{ch:concrete-instances-metacicauditsynthesispacket-namecert}
\origin{human}

The $\MetaCICAuditSynthesisPacketUp$ surface turns the synthesis overview of \autoref{ch:metacic-audit-synthesis} into one finite naming certificate. It sits beside the closed-normal packet of \autoref{ch:concrete-instances-closednormalconsistencypacket-namecert}, the normal-false exclusion packet of \autoref{ch:concrete-instances-normalfalseexclusion-namecert}, and the discharge-obligation ledger of \autoref{ch:concrete-instances-metacic-discharge-obligation-ledger-namecert}: those siblings separate the positive closed-normal branch from the subject-reduction obstruction, while the present packet records the combined audit surface without closing the missing transport edge.

\begin{definition}[MetaCIC audit synthesis packet carrier]
\label{def:metacic-audit-synthesis-packet-carrier}
A $\MetaCICAuditSynthesisPacketUp$ carrier is a finite $\BHist$ packet
$$
M=(S,C,N,U,D,A,B,H,R,P,L)
$$
with the following visible rows:
\begin{enumerate}
\item $S$ is the subject-reduction obstruction row, including the dependent-codomain boundary and the four named discharge slots;
\item $C$ is the confluence map row, recording the conditional diamond route, closed-normal fragment, and confluence-audit packet references;
\item $N$ is the normalization row, recording the candidate-mediated closed strong-normalization routes used by the closed-normal branch;
\item $U$ is the substitution row, recording closed shift, closed substitution, and closed composition routes needed by the discharge surface;
\item $D$ is the decidable-checking row, recording checked term equality, typing inference, gallery witnesses, and bounded normal comparison with its boundary;
\item $A$ is the closed-normal assembly row, tying closed strong normalization, normal-false exclusion, and the closed-normal consistency packet into the positive branch;
\item $B$ is the blocker row, recording that the synthesis does not supply closed subject reduction, arbitrary closed Church--Rosser, candidate-free normalization, global beta-conversion decidability, or full closed consistency;
\item $H$ records componentwise $\hsame$ transports for $S,C,N,U,D,A,B$ and the local structural rows;
\item $R$ records the displayed $\Cont$ routes by which consumers read the audit rows in synthesis order;
\item $P$ is the $\Pkg$ provenance over the MetaCIC audit maps, \autoref{ch:concrete-instances-closednormalconsistencypacket-namecert}, \autoref{ch:concrete-instances-normalfalseexclusion-namecert}, and \autoref{ch:concrete-instances-metacic-discharge-obligation-ledger-namecert};
\item $L$ is the local $\NameCert_{\MetaCICAuditSynthesisPacketUp}$ row.
\end{enumerate}
The classifier compares accepted synthesis packets only through the displayed rows $S,C,N,U,D,A,B,H,R,P,L$. The carrier has no coordinate for a hidden proof of subject reduction, an ambient consistency theorem, quotient equality of MetaCIC terms, or an external normalization oracle.
\end{definition}

\begin{theorem}[MetaCIC audit synthesis certificate surface]
\label{thm:metacic-audit-synthesis-certificate-surface}
The local $\NameCert_{\MetaCICAuditSynthesisPacketUp}$ surface for \autoref{def:metacic-audit-synthesis-packet-carrier} consists exactly of carrier admission for $M=(S,C,N,U,D,A,B,H,R,P,L)$, audit-row exposure for the subject-reduction, confluence, normalization, substitution, decidable-checking, closed-normal assembly, and blocker rows, componentwise $\hsame$ transport through $H$, displayed $\Cont$ route replay through $R$, package provenance through $P$, and local naming through $L$.
\end{theorem}
\begin{proof}
Project the finite packet of \autoref{def:metacic-audit-synthesis-packet-carrier}. The rows $S,C,N,U,D,A,B,H,R,P,L$ are the complete certificate surface, so carrier admission and classifier exactness are componentwise projections.

Read the positive audit rows next. The confluence row, normalization row, substitution row, decidable-checking row, and closed-normal assembly row cite the same audit-map separation stated in \autoref{ch:metacic-audit-synthesis}. The closed-normal side is routed through the packet of \autoref{ch:concrete-instances-closednormalconsistencypacket-namecert} and the normal-false exclusion surface of \autoref{ch:concrete-instances-normalfalseexclusion-namecert}.

Finally read $B,H,R,P,L$. The blocker row keeps the subject-reduction gap explicit, while the transport, continuation, provenance, and naming rows only replay the displayed finite packet. Thus the local certificate cannot export an unlisted MetaCIC theorem.
\end{proof}

\begin{theorem}[MetaCIC audit synthesis critical-path non-escape]
\label{thm:metacic-audit-synthesis-critical-path-nonescape}
Every consumer of an accepted $\MetaCICAuditSynthesisPacketUp$ carrier reads the critical path through
$$
S,C,N,U,D,A,B,H,R,P,L.
$$
It may inspect the audit synthesis rows and their finite transports, routes, provenance, and local name. It cannot read a second closed-consistency route, a hidden subject-reduction proof, an unrestricted Church--Rosser theorem, candidate-free normalization, global beta-conversion decidability, quotient equality of terms, or host-level completeness.
\end{theorem}
\begin{proof}
Start with carrier admission. Since the classifier of \autoref{def:metacic-audit-synthesis-packet-carrier} compares only the displayed rows, every consumer read is a projection from $S,C,N,U,D,A,B,H,R,P,L$ or a route recorded by $R$.

Use the sibling audit packets to identify the positive branch. \autoref{ch:concrete-instances-closednormalconsistencypacket-namecert} and \autoref{ch:concrete-instances-normalfalseexclusion-namecert} expose the closed-normal endpoint, while the confluence, normalization, substitution, and decidable rows keep their local audit boundaries visible.

The blocker row is then read as a boundary, not as a solved theorem. Because the carrier has no additional coordinate for full closed consistency or closed subject reduction, no consumer can escape the displayed critical path.
\end{proof}

\begin{theorem}[MetaCIC audit synthesis consistency blocker ledger]
\label{thm:metacic-audit-synthesis-consistency-blocker-ledger}
The consistency blocker of a $\MetaCICAuditSynthesisPacketUp$ packet is exactly the displayed row $B$ together with the subject-reduction row $S$. Agreement on $C,N,U,D,A,H,R,P,L$ cannot be repacked as closed subject reduction, closed reduction consistency, or a transport from arbitrary closed proof terms into the closed-normal exclusion branch.
\end{theorem}
\begin{proof}
Inspect $S$ first. It names the dependent-codomain obstruction and the four discharge slots, matching the finite ledger of \autoref{ch:concrete-instances-metacic-discharge-obligation-ledger-namecert}.

Inspect $B$ next. The blocker row records the unavailable closed transport edge as part of the packet, so the remaining positive rows cannot erase it.

The closed-normal assembly row $A$ can be consumed only with its stated boundary. It supports the positive branch named by the closed-normal and normal-false sibling chapters, but it does not create a reduction route from arbitrary closed proofs. Therefore agreement on the other rows leaves the blocker ledger intact.
\end{proof}

\begin{theorem}[MetaCIC audit synthesis closed-normal boundary]
\label{thm:metacic-audit-synthesis-closed-normal-boundary}
The closed-normal branch of an accepted $\MetaCICAuditSynthesisPacketUp$ packet is exhausted by the normalization row $N$, the closed-normal assembly row $A$, the normal-false exclusion boundary, and the structural rows $H,R,P,L$. The packet may certify the closed-normal consistency branch as named finite audit data, but it does not certify full closed MetaCIC consistency.
\end{theorem}
\begin{proof}
Project the normalization and assembly rows from \autoref{def:metacic-audit-synthesis-packet-carrier}. These rows are the only coordinates that feed the closed-normal branch.

Use the sibling boundaries. The closed-normal packet of \autoref{ch:concrete-instances-closednormalconsistencypacket-namecert} and the normal-false exclusion packet of \autoref{ch:concrete-instances-normalfalseexclusion-namecert} identify the branch reached after normality is already displayed.

It remains to compare this branch with the blocker row. The subject-reduction ledger of \autoref{ch:concrete-instances-metacic-discharge-obligation-ledger-namecert} keeps the missing transport edge outside the closed-normal rows, so the packet stops at the finite closed-normal boundary.
\end{proof}

\begin{theorem}[MetaCIC audit synthesis route-union exactness]
\label{thm:metacic-audit-synthesis-route-union-exactness}
For every accepted $\MetaCICAuditSynthesisPacketUp$ carrier
$$
M=(S,C,N,U,D,A,B,H,R,P,L),
$$
any packet consumer that reads confluence, normalization, substitution, decidable-checking, or closed-normal assembly must also carry the blocker row $B$ and the subject-reduction row $S$ through the same transport, route, provenance, and naming rows $H,R,P,L$. Thus the positive rows $C,N,U,D,A$ and the blocker row $B$ form one exact audit-route union over $S,H,R,P,L$. The packet supplies no hidden subject reduction, unrestricted Church--Rosser theorem, candidate-free normalization, global beta-conversion decidability, or quotient equality.
\end{theorem}
\begin{proof}
Use the certificate surface of \autoref{thm:metacic-audit-synthesis-certificate-surface}. It identifies $S,C,N,U,D,A,B,H,R,P,L$ as the complete finite carrier and local naming surface, so the positive audit rows and blocker row are read from one packet.

Next apply \autoref{thm:metacic-audit-synthesis-critical-path-nonescape}. Every consumer route stays inside the displayed critical path, and the only transport, route, provenance, and naming rows available to that route are $H,R,P,L$.

The blocker side is fixed by \autoref{thm:metacic-audit-synthesis-consistency-blocker-ledger}. The row $B$ is carried together with the subject-reduction row $S$, so agreement on confluence, normalization, substitution, decidable-checking, or assembly cannot erase the obstruction.

Finally use \autoref{thm:metacic-audit-synthesis-closed-normal-boundary}. It places the closed-normal branch inside the named finite boundary rather than inside full closed consistency. Therefore the route union is exact: reading any positive row also carries $S$ and $B$ through $H,R,P,L$, while hidden subject reduction, unrestricted Church--Rosser, candidate-free normalization, global beta-conversion decidability, and quotient equality remain outside the packet.
\end{proof}

\closureat{MetaCICAuditSynthesisPacketUp}{seedStr}

\begin{closurestatus}{\MetaCICAuditSynthesisPacketUp}
  \constructivestory{A $\MetaCICAuditSynthesisPacketUp$ packet is generated from subject-reduction obstruction, confluence, normalization, substitution, decidable-checking, closed-normal assembly, blocker, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-audit-synthesis-packet-carrier}, \autoref{thm:metacic-audit-synthesis-certificate-surface}, \autoref{thm:metacic-audit-synthesis-critical-path-nonescape}, \autoref{thm:metacic-audit-synthesis-consistency-blocker-ledger}, \autoref{thm:metacic-audit-synthesis-closed-normal-boundary}, and \autoref{thm:metacic-audit-synthesis-route-union-exactness} bind the finite MetaCIC audit synthesis packet and its blocker ledger.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close subject reduction, arbitrary closed Church--Rosser, candidate-free normalization, global beta-conversion decidability, full closed consistency, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, audit-row exactness, blocker non-escape, closed-normal boundary routing, transport, route replay, provenance, and local naming for the same finite packet.}
\end{closurestatus}
