\chapter{A Concrete Naming Certificate for $\BetaStepBoundaryUp$}
\label{ch:concrete-instances-betastepboundary-namecert}
\origin{ai}

The $\BetaStepBoundaryUp$ packet realizes the beta audit map of
\autoref{ch:metacic-beta-audit-map} as a finite BEDC naming surface. It sits
beside the subject-reduction carrier of
\autoref{ch:concrete-instances-subjectreduction-namecert}: the present packet
names the $\mathsf{BetaStep}$ and $\mathsf{BetaConv}$ boundary rows, while the
sibling packet records the preservation-facing route that must not be inferred
from beta reduction alone.

\begin{definition}[BetaStepBoundary carrier]
\label{def:beta-step-boundary-carrier}
A $\BetaStepBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(R,C,O,H,K,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $R$ records the $\mathsf{BetaStep}$ rule surface, including the direct
redex row and the congruence rows for application, lambda-domain, lambda-body,
Pi-domain, and Pi-codomain positions;
\item $C$ records the $\mathsf{BetaConv}$ common-reduct rows, including
reflexivity, symmetry, the beta-star injections, beta-step injections, and the
normal-middle conversion rows named by the audit map;
\item $O$ records the subject-reduction obstruction triggers: beta
substitution, application-argument stability, lambda-domain preservation, and
Pi-domain preservation;
\item $H$ stores componentwise $\hsame$ transports for the beta-rule rows,
conversion rows, obstruction-trigger rows, provenance row, and local naming row;
\item $K$ stores the displayed $\Cont$ routes by which consumers read beta
steps, common-reduct conversions, and obstruction triggers without crossing
from reduction into typed preservation;
\item $P$ is the $\Pkg$ provenance over the MetaCIC beta audit map,
\autoref{ch:concrete-instances-subjectreduction-namecert}, $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\BetaStepBoundaryUp}$ row.
\end{enumerate}
The packet contains no host conversion oracle, hidden typing-preservation
theorem, closed subject-reduction theorem, quotient equality, or erased
semantic equality coordinate.
\end{definition}

\begin{theorem}[BetaStepBoundary NameCert obligations]
\label{thm:beta-step-boundary-namecert-obligations}
The carrier of \autoref{def:beta-step-boundary-carrier} satisfies the local
$\NameCert_{\BetaStepBoundaryUp}$ obligation surface. Its five obligation rows
are:
\begin{enumerate}
\item carrier admission for the finite packet $B=(R,C,O,H,K,P,N)$;
\item beta-rule exactness, saying that $R$ exposes exactly the displayed
$\mathsf{BetaStep}$ constructor surface;
\item conversion-boundary readback, saying that $C$ exposes only the
$\mathsf{BetaConv}$ common-reduct and normal-middle rows listed by the audit
map;
\item subject-reduction non-escalation, saying that the obstruction triggers
in $O$ remain obligation rows and do not become a closed preservation theorem;
\item ledger non-escape, saying that $H,K,P,N$ supply only transport,
continuation, provenance, and naming for the displayed rows, never host
conversion or hidden typing preservation.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.BetaStepBoundaryUp.BetaStepBoundaryTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is the displayed $\BHist$ packet. Each coordinate is a finite
row for beta rules, conversion readback, obstruction triggers, transport,
continuation, provenance, or local naming.

Beta-rule exactness follows by projecting $R$. The row lists the direct beta
redex and the congruence positions, so a consumer cannot read an additional
reduction rule from the carrier.

Conversion-boundary readback follows by projecting $C$. Common-reduct
conversion, beta-star injection, beta-step injection, and normal-middle
conversion rows are available only as the listed conversion surface.

Subject-reduction non-escalation follows by projecting $O$ and comparing it
with \autoref{ch:concrete-instances-subjectreduction-namecert}. The beta packet
records the triggers that a preservation consumer must discharge, but it has no
coordinate carrying a closed subject-reduction theorem.

Finally inspect $H,K,P,N$. These rows move and replay the same finite packet,
record its provenance, and give it a local name. None of them contains host
conversion or hidden typing preservation, so every consumer remains inside the
displayed ledger.
\end{proof}

\closureat{BetaStepBoundaryUp}{seedStr}

\begin{closurestatus}{\BetaStepBoundaryUp}
  \constructivestory{A $\BetaStepBoundaryUp$ packet is generated from beta-step rule rows, beta-conversion common-reduct rows, subject-reduction obstruction triggers, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:beta-step-boundary-carrier} and \autoref{thm:beta-step-boundary-namecert-obligations} bind the finite beta-step, beta-conversion, obstruction-trigger, transport, route, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close subject reduction, beta-substitution preservation, application-argument stability, lambda-domain preservation, Pi-domain preservation, host conversion, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, beta-rule exactness, conversion-boundary readback, subject-reduction non-escalation, transport, route replay, provenance, and ledger non-escape for the same finite packet.}
\end{closurestatus}

\begin{lemma}[BetaStepBoundary obstruction-trigger enumeration]
\label{lem:beta-step-boundary-obstruction-trigger-enumeration}
Let $B=(R,C,O,H,K,P,N)$ be an accepted $\BetaStepBoundaryUp$ carrier. If a consumer reads a subject-reduction obstruction trigger from $B$ through the displayed obstruction slot, then the read trigger is one of exactly four rows:
$$
\mathrm{BetaSubstitutionPreservation},\quad
\mathrm{AppArgTypeStable},\quad
\mathrm{LamDomainSubjectReduction},\quad
\mathrm{PiDomainSubjectReduction}.
$$
Conversely, each of these four rows is a displayed obstruction-trigger row of the same obstruction slot $O$.
\end{lemma}
\begin{proof}
Project the accepted carrier through \autoref{def:beta-step-boundary-carrier}. The obstruction coordinate is the single row $O$, and that coordinate is displayed as the list of subject-reduction obstruction triggers: beta substitution, application-argument stability, lambda-domain preservation, and Pi-domain preservation.

The NameCert obligation surface of \autoref{thm:beta-step-boundary-namecert-obligations} keeps this projection exact. Its subject-reduction non-escalation clause says that the entries in $O$ remain obligation rows, while its ledger non-escape clause says that $H,K,P,N$ supply only transport, continuation, provenance, and naming for the displayed rows. Thus a continuation read through $K$ can select an entry of $O$, and an $\hsame$ transport through $H$ can replay that selected entry, but neither operation creates another obstruction trigger.

The four labels are also the four discharge obligations named in \autoref{sec:metacic-subject-reduction-four-obligations}, and \autoref{sec:metacic-beta-audit-map-sr-connection} identifies them as the beta-redex, application-argument, lambda-domain, and Pi-domain triggers born at the beta boundary. Since $R$ records beta-step constructors, $C$ records beta-conversion readback, and $P,N$ only record provenance and local naming, no subject-reduction obstruction trigger can be read from any coordinate other than $O$.

Therefore every admissible obstruction-trigger read from an accepted $\BetaStepBoundaryUp$ packet is one of the four displayed rows, and the carrier definition supplies the reverse inclusion by listing all four rows inside $O$.
\end{proof}
