\chapter{A Concrete Naming Certificate for \(\ConvergenceRadiusUp\)}
\label{ch:concrete-instances-convergence-radius-namecert}

This chapter gives a concrete naming-certificate construction for the convergence radius of a complex power series $\sum a_n z^n$ at the paper-proof level. The certificate sits above $\ComplexLimitUp$ (\autoref{ch:concrete-instances-complex-limit-namecert}) and the formal power series chapter (\autoref{ch:concrete-instances-fps-namecert}), and gives an explicit unary-history witness for the radius rather than a real-number supremum. Absolute convergence inside displayed strict subradii is proved by geometric majorant; Cauchy--Hadamard limsup exactness is recorded only as a separate analytic ledger row outside the checked-row reduct. The construction is fully constructive and uses no $\mathsf{Classical.choice}$, no $\mathsf{Quot.sound}$, and no $\mathsf{propext}$, so the certificate's Lean targets fall under the project's axiom-purity gate.

\input{parts/concrete_instances/convergence_radius/certificate_body}
\input{parts/concrete_instances/convergence_radius/cauchy_hadamard_boundary}

\begin{theorem}[Convergence radius coefficient-ring inclusion geometric-bound transport]
\label{thm:convrad-coefficient-ring-inclusion-geom-bound-transport}
Let
$$
\iota:R\hookrightarrow R'
$$
be a convergence-radius compatible coefficient-ring inclusion in the sense of
\autoref{def:conv-rad-coefficient-ring-inclusion}. For a source coefficient
family $a$ and its transported family $a'$ defined pointwise by the complex
realization rows of $\iota$, if
$$
\mathsf{GeomBound}(a,r,K),
$$
then
$$
\mathsf{GeomBound}(a',r,K).
$$
The radius history $r$ and constant history $K$ are unchanged.
\end{theorem}
\begin{proof}
Unfold the geometric-bound rows of \autoref{def:geom-bound}. The source bound
supplies the coefficient carrier rows, the radius carrier row, the constant
carrier row, and the pointwise comparison ledger for every unary index.

Use \autoref{def:conv-rad-coefficient-ring-inclusion} on each coefficient
row. Its complex-realization clause identifies $a_n$ with $a'_n$ through the
transported complex-history classifier, and its pointwise classifier transport
keeps the displayed coefficient read in the target source.

Therefore the comparison row for $a_n$ at radius $r$ and constant $K$ reads
as the corresponding comparison row for $a'_n$. The radius and constant
histories are not transported, so their carrier rows and ledger entries are
copied unchanged. Repacking these rows by \autoref{def:geom-bound} gives
$\mathsf{GeomBound}(a',r,K)$.
\end{proof}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadCoefficientRingInclusion\_geomBound\_transport}

\begin{theorem}[ConvergenceRadius checked-row reduct readback]
\label{thm:convergence-radius-checked-row-reduct-readback}
For any coefficient family $a$, center $z_0$, and unary radius $R$, a
$\mathsf{ConvRadSourceSpec}(a,z_0,R)$ row determines the checked-row reduct
of \autoref{def:convrad-checked-row-reduct}. The reduct consists of the source
row together with the geometric-bound readback rows supplied by the source
specification, and it contains no Cauchy--Hadamard exactness row.
\end{theorem}
\begin{proof}
Unfold the source specification of \autoref{def:conv-rad-source-spec}. Its
displayed data give the coefficient family, center, unary radius, and the
geometric-bound readback rows associated to the same source packet.

Now apply \autoref{def:convrad-checked-row-reduct}. The reduct keeps exactly
the checked rows read from that packet: the source row and the geometric-bound
rows already exposed by the source specification.

There is no constructor in the reduct for Cauchy--Hadamard exactness. Repacking
the displayed source and geometric-bound rows therefore gives precisely the
checked-row reduct claimed above.
\end{proof}

\begin{theorem}[ConvergenceRadius finite-prefix window stability]
\label{thm:convergence-radius-prefix-window-stability}
Let $\mathsf{ConvRadSourceSpec}(a,z_0,R)$ be a displayed convergence-radius
source packet. Restrict the packet to a certified finite unary prefix window
of coefficient indices and consumer reads. Then the checked-row reduct visible
to downstream consumers preserves the same radius witness, the
geometric-bound rows on the displayed prefix, the endpoint packages,
$\mathsf{BHist}$ histories, $\hsame$ transport rows, $\Cont$ routes, and
$\mathsf{Pkg}$ provenance.

The restricted reduct introduces no Cauchy--Hadamard exactness row, no
real-supremum row, and no host complex-analysis boundary beyond the rows
already visible in the finite prefix.
\end{theorem}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadCheckedRowReduct\_prefix\_window\_stability}
\begin{proof}
Unfold \autoref{def:conv-rad-source-spec} and
\autoref{def:convrad-checked-row-reduct}. The source packet already displays
the coefficient family, center, unary radius witness, geometric-bound rows,
endpoint packages, transport rows, continuation routes, and provenance.

Project the rows whose coefficient indices lie in the certified finite prefix.
The radius witness and endpoint packages are shared coordinates of the source
packet, while the geometric-bound rows are retained only where the prefix
contains the corresponding unary index.

Transport the retained entries componentwise by $\hsame$. Continuation
determinacy for the displayed $\Cont$ routes keeps the read paths attached to
the same packet, and the $\mathsf{Pkg}$ row records the unchanged provenance.

Finally use \autoref{thm:convergence-radius-public-boundary-exactness} only
to identify which retained rows are consumer-visible. That boundary has no
constructor for Cauchy--Hadamard exactness or real supremum, so the finite
prefix reduct exposes exactly the listed checked rows.
\end{proof}

\begin{theorem}[ConvergenceRadius public export]
\label{thm:convergence-radius-public-export}
\autoref{thm:conv-rad-semantic-namecert} exports the public
$\ConvergenceRadiusUp$ boundary over the power-series carrier,
geometric-bound rows, convergence-radius witness, radius classifier transport,
endpoint packages, and checked semantic certificate rows. Consumers may cite
this public boundary without treating Cauchy--Hadamard exactness or standard
complex-analysis bridge rows as checked consequences.
\end{theorem}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadCheckedRowReduct\_public\_export}
\leanvariant{BEDC.Derived.ConvergenceRadiusUp.ConvergenceRadiusCheckedRowReduct\_public\_export}
\leanvariant{BEDC.Derived.ConvergenceRadiusUp.ConvRad\_public\_export}
\begin{proof}
Cite the semantic naming certificate of
\autoref{thm:conv-rad-semantic-namecert}. It repacks the checked carrier,
classifier, transport, witness, and append-unary closure rows into the
$\NameCert$ schema for $\ConvergenceRadiusUp$.

Read the same packet through the checked-row reduct of
\autoref{def:convrad-checked-row-reduct}. This identifies the rows available
to consumers: the power-series carrier, geometric-bound data,
convergence-radius witness, radius classifier transport, endpoint packages,
and semantic certificate rows.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. The public
export therefore does not treat Cauchy--Hadamard exactness or standard
complex-analysis bridge rows as checked consequences.
\end{proof}

\begin{theorem}[ConvergenceRadius public boundary exactness]
\label{thm:convergence-radius-public-boundary-exactness}
The public $\ConvergenceRadiusUp$ boundary consists exactly of the
power-series carrier, geometric-bound rows, convergence-radius witness, radius
classifier transport, endpoint packages, checked-row reduct, and semantic
certificate rows. Every consumer read of the public export factors through
one of these rows.

Conversely, each listed row is visible through
\autoref{thm:convergence-radius-public-export}. The boundary does not imply
real-number supremum completeness, Cauchy--Hadamard exactness, or standard
complex-analysis bridge rows.
\end{theorem}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRad\_public\_boundary\_exactness}
\leanvariant{BEDC.Derived.ConvergenceRadiusUp.ConvRadSourceSpec\_public\_boundary\_exactness}
\begin{proof}
Start from \autoref{thm:convergence-radius-public-export}. Its public export
names the available carrier, geometric-bound, witness, classifier-transport,
endpoint-package, and semantic-certificate rows.

Refine this list through \autoref{thm:conv-rad-semantic-namecert} and
\autoref{def:convrad-checked-row-reduct}. The semantic certificate supplies
the naming packet, while the checked-row reduct gives the exact consumer
boundary through which every public read must factor.

For the converse, read each displayed component through the same public export.
Each listed row is one of the rows repacked by the certificate and retained by
the checked-row reduct.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. Since the
checked rows do not force Cauchy--Hadamard exactness, the boundary also does
not provide real-number supremum completeness or the standard
complex-analysis bridge rows.
\end{proof}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadCheckedRowReduct\_public\_boundary\_exactness}

\begin{theorem}[ConvergenceRadius geometric-bound common tail window]
\label{thm:convergence-radius-geometric-bound-common-tail-window}
For two accepted $\ConvergenceRadiusUp$ public packets over the same
power-series carrier, suppose their geometric-bound rows classify to the same
radius witness and their endpoint packages agree under the displayed radius
classifier. Then there is a single finite tail window through which both
public consumer reads factor. The common window exposes only the power-series
carrier, geometric-bound rows, convergence-radius witness, endpoint package,
checked-row reduct, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance.

The common window still exports no real supremum, Cauchy--Hadamard exactness,
or standard complex-analysis bridge row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:convergence-radius-public-export} to the two accepted
packets. Each public consumer read is therefore presented through the
power-series carrier, geometric-bound data, convergence-radius witness,
radius-classifier transport, endpoint package, checked-row reduct, and
semantic certificate rows.

Next use \autoref{thm:convergence-radius-public-boundary-exactness} for both
packets. The boundary exactness theorem forces each read to factor through
the displayed rows and does not leave a separate analytic coordinate outside
that finite surface.

The hypotheses identify the shared radius-classifier row and the endpoint
package rows. Refine the two directed tail ledgers to the finite common tail
where those rows are both displayed, and transport the two reads through the
same $\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. Since the
checked rows do not force Cauchy--Hadamard exactness, the shared tail window
cannot export a real supremum row or a standard complex-analysis bridge row.
\end{proof}

\begin{theorem}[ConvergenceRadius checked-row readback public factorization]
\label{thm:convergence-radius-checked-row-readback-public-factorization}
Every $\mathsf{ConvRadSourceSpec}$ consumer read factors first through
\autoref{def:convrad-checked-row-reduct} and only then reaches the public
export rows of \autoref{thm:convergence-radius-public-export} and
\autoref{thm:convergence-radius-public-boundary-exactness}. The factorization
exports no Cauchy--Hadamard exactness row and no real supremum completeness
principle.
\end{theorem}
\begin{proof}
Unpack the $\mathsf{ConvRadSourceSpec}$ row. Its source, geometric-bound, and
radius-witness data are the checked rows retained by
\autoref{def:convrad-checked-row-reduct}.

Apply the checked-row reduct readback of
\autoref{thm:convergence-radius-checked-row-reduct-readback}. This gives the
factor through which every source-specification consumer read is routed before
any public export row is inspected.

Now use \autoref{thm:convergence-radius-public-export} and
\autoref{thm:convergence-radius-public-boundary-exactness}. They expose the
same public carrier, geometric-bound, convergence-radius witness,
classifier-transport, endpoint-package, checked-reduct, and semantic
certificate rows, and they expose no additional analytic coordinate.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. Since the
checked rows do not force Cauchy--Hadamard exactness, the public readback
factorization also cannot export real supremum completeness.
\end{proof}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadSourceSpec\_checkedRowReduct\_readback}

\begin{theorem}[ConvergenceRadius bridged boundary]
\label{thm:convergence-radius-bridged-boundary}
\autoref{thm:convergence-radius-public-export} and
\autoref{thm:convergence-radius-public-boundary-exactness} determine the
bridge-consumable $\ConvergenceRadiusUp$ surface: the power-series carrier,
geometric-bound rows, convergence-radius witness, radius classifier transport,
endpoint packages, checked-row reduct, and semantic certificate rows.

Real-number supremum completeness, Cauchy--Hadamard exactness, and standard
complex-analysis bridge rows are not consequences of this boundary.
\end{theorem}
\begin{proof}
First compose the public export with the public boundary exactness theorem.
The export gives the consumer-facing packet, and exactness says that every
consumer read factors through the displayed power-series carrier,
geometric-bound, witness, classifier-transport, endpoint, checked-reduct, and
semantic-certificate rows.

Next read the same packet through
\autoref{def:convrad-checked-row-reduct}. This keeps precisely the checked
rows available to the bridge-facing consumer and adds no hidden supremum,
Cauchy--Hadamard, or standard complex-analysis row.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. Since the
checked rows do not force Cauchy--Hadamard exactness, the bridged boundary
cannot export real-number supremum completeness or any standard
complex-analysis bridge row as a consequence.
\end{proof}

\begin{theorem}[ConvergenceRadius coefficient-tail public boundary]
\label{thm:convergence-radius-tail-shift-public-boundary}
\autoref{thm:conv-rad-coefficient-tail-closed} factors through
\autoref{thm:convergence-radius-public-export} and
\autoref{thm:convergence-radius-public-boundary-exactness}: shifting a
certified coefficient stream to its tail preserves the displayed
$\mathsf{ConvRad}$ witness inside the same public carrier,
geometric-bound, witness, classifier-transport, endpoint, checked-reduct, and
semantic-certificate rows.

The tail-shift boundary adds no real-number supremum completeness,
Cauchy--Hadamard exactness, or standard complex-analysis bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRad\_tail\_shift\_public\_boundary}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRad\_tail\_shift\_checked\_row\_reduct\_semantic\_boundary}
\begin{proof}
First apply \autoref{thm:conv-rad-coefficient-tail-closed}. The checked
tail-closure theorem preserves the convergence-radius witness after replacing
the certified coefficient stream by its tail, with the displayed radius and
geometric-bound witness read through the same certificate body.

Next use \autoref{thm:convergence-radius-public-export} and
\autoref{thm:convergence-radius-public-boundary-exactness}. Public export gives
the consumer-facing packet, and exactness restricts every consumer read to the
named carrier, geometric-bound, witness, classifier-transport, endpoint,
checked-reduct, and semantic-certificate rows.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. Since the
checked rows do not force Cauchy--Hadamard exactness, the coefficient-tail
public boundary exports no real supremum, Cauchy--Hadamard, or standard
complex-analysis bridge consequence.
\end{proof}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadCheckedRowReduct\_coefficient\_tail\_public\_boundary}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadCheckedRowReduct\_tail\_shift\_public\_boundary}

\begin{theorem}[ConvergenceRadius checked-row two-sided ledger boundary]
\label{thm:convergence-radius-checked-row-two-sided-ledger-boundary}
For any checked-row reduct of a $\ConvergenceRadiusUp$ source and any unary
history $q$, the public checked rows determine a two-sided coefficient ledger:
the families $n \mapsto \mathsf{append}(a_n,q)$ and
$n \mapsto \mathsf{append}(q,a_n)$ carry $\mathsf{ConvRad}$ witnesses at the
same radius. This ledger remains inside the carrier, geometric-bound,
convergence-radius witness, endpoint, checked-reduct, and semantic certificate
rows.

The ledger adds no Cauchy--Hadamard exactness, real supremum row, or standard
complex-analysis bridge row.
\end{theorem}
\begin{proof}
Read the source through \autoref{def:convrad-checked-row-reduct}. The reduct
exposes the checked convergence-radius row, so the same radius is available to
both coefficient-family transports.

Apply \autoref{thm:conv-rad-append-unary-coeff-closed} to the unary history
$q$ for the family $n \mapsto \mathsf{append}(a_n,q)$. Apply
\autoref{thm:conv-rad-prepend-unary-coeff-closed} to the same unary history
for the family $n \mapsto \mathsf{append}(q,a_n)$. These two applications
produce the two sides of the public ledger at the original radius.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. Since the
checked reduct does not force Cauchy--Hadamard exactness, the two-sided ledger
does not introduce a real supremum row or a standard complex-analysis bridge
row.
\end{proof}
\leanchecked{BEDC.Derived.ConvergenceRadiusUp.ConvRadCheckedRowReduct\_append\_prepend\_ledger}

\begin{theorem}[ConvergenceRadius mature package boundary]
\label{thm:convergence-radius-mature-package-boundary}
\autoref{thm:convergence-radius-public-export},
\autoref{thm:convergence-radius-public-boundary-exactness}, and
\autoref{thm:convergence-radius-bridged-boundary} exhaust the mature paper
package for the $\ConvergenceRadiusUp$ power-series carrier,
geometric-bound rows, convergence-radius witness, radius-classifier
transport, endpoint packages, checked-row reduct, and semantic certificate
rows. Every consumer of the package factors through one of those rows.

The package exports no real-number supremum completeness,
Cauchy--Hadamard exactness, or standard complex-analysis bridge row.
\end{theorem}
\begin{proof}
First use \autoref{thm:convergence-radius-public-export} to identify the
consumer-facing packet. Its visible rows are the power-series carrier,
geometric-bound data, convergence-radius witness, radius-classifier
transport, endpoint packages, and semantic certificate rows.

Next apply \autoref{thm:convergence-radius-public-boundary-exactness}. This
turns the public export into an exact factorization statement: every public
consumer read passes through the displayed rows, and each displayed row is
available through the same export.

Now compose with \autoref{thm:convergence-radius-bridged-boundary}. The
bridge-consumable surface is therefore the same finite row package, with no
extra analytic coordinate added by the bridge-facing presentation.

Finally apply
\autoref{thm:convrad-checked-rows-do-not-force-cauchy-hadamard}. Since the
checked rows do not force Cauchy--Hadamard exactness, the mature paper
package cannot export real-number supremum completeness or any standard
complex-analysis bridge row.
\end{proof}

\closureat{ConvergenceRadiusUp}{obligationStr}[BEDC.Derived.ConvergenceRadiusUp.ConvRad\_semanticNameCert]
\closureat{ConvergenceRadiusUp}{scopedStr}[BEDC.Derived.ConvergenceRadiusUp.ConvRad\_semanticNameCert]
\closureat{ConvergenceRadiusUp}{publicStr}[BEDC.Derived.ConvergenceRadiusUp.ConvRad\_semanticNameCert]
\closureat{ConvergenceRadiusUp}{bridgedStr}[BEDC.Derived.ConvergenceRadiusUp.ConvRad\_semanticNameCert]
\closureat{ConvergenceRadiusUp}{matureStr}[BEDC.Derived.ConvergenceRadiusUp.ConvRad\_semanticNameCert]

\begin{closurestatus}{\ConvergenceRadiusUp}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:convergence-radius-public-export} binds the consumer-facing convergence-radius boundary over the power-series carrier, geometric-bound rows, convergence-radius witness, classifier transport, endpoint packages, checked-row reduct, and semantic certificate rows.}
  \constructivestory{A $\ConvergenceRadiusUp$ seed packet is generated from the displayed formal power-series carrier, finite geometric-majorant rows, a unary convergence-radius witness, classifier transport, stability rows, and the checked semantic certificate; consumers may read only those rows and their recorded package provenance.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.ConvergenceRadiusUp.ConvRad\_semanticNameCert}
  \bridgestatus{none}
  \notclaimed{This chapter does not close real-number supremum completeness or standard complex-analysis bridge rows.}
  \upgradepath{No further paper-side theory grade remains for the finite power-series radius surface; bridgeChecked verification remains on the separate formal axis.}
\end{closurestatus}
