\chapter{A Concrete Naming Certificate for $\MetacicOpenFrontierLedgerUp$}
\label{ch:concrete-instances-metacic-open-frontier-ledger-namecert}
\origin{human}

The $\MetacicOpenFrontierLedgerUp$ packet realizes the open-problem inventory of \autoref{ch:metacic-open-problems} as a finite NameCert frontier ledger. It sits beside the subject-reduction carrier of \autoref{ch:concrete-instances-subjectreduction-namecert}, the normal false exclusion packet of \autoref{ch:concrete-instances-normalfalseexclusion-namecert}, the normalization audit packet of \autoref{ch:concrete-instances-metacicnormalizationaudit-namecert}, and the decidability boundary packet of \autoref{ch:concrete-instances-metacicdecidableboundary-namecert}. Its purpose is to name the open rows that downstream consumers must keep visible before reading MetaCIC consistency, normalization, confluence, decidability, or typed-example evidence.

\begin{definition}[MetaCIC open frontier ledger carrier]
\label{def:metacic-open-frontier-ledger-carrier}
A $\MetacicOpenFrontierLedgerUp$ carrier is a finite $\BHist$ packet
$$
L=(S,E,F,N,D,T,K,H,C,P,Q)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the subject-reduction frontier row, naming the $\mathrm{SubjectReductionDischargeBundle}$ interface and its four obligation coordinates;
\item $E$ is the closed-normal exclusion row, naming the closed-normal false exclusion and closed-normal consistency boundary;
\item $F$ is the confluence frontier row, naming the residual-substitution and arbitrary closed-source Church--Rosser endpoints that remain outside the closed-normal fragment;
\item $N$ is the normalization frontier row, naming the candidate-mediated strong-normalization interface and its evidence boundary;
\item $D$ is the decidability frontier row, naming typing-checker exactness, bounded normal comparison, finished-normal side conditions, and the refusal of an unrestricted closed beta-conversion oracle;
\item $T$ is the typed-example boundary row, naming the gallery witnesses and the absence of exhaustive dependent-program coverage;
\item $K$ is the closed-consistency boundary row, naming the handoff from closed-normal consistency to any stronger closed consistency claim;
\item $H$ records componentwise $\hsame$ transport across $S,E,F,N,D,T,K,P,Q$;
\item $C$ records displayed $\Cont$ replay routes for the subject-reduction, confluence, normalization, decidability, typed-example, and consistency-boundary rows;
\item $P$ is the $\Pkg$ provenance over the MetaCIC open-problem inventory and the sibling concrete NameCert packets cited above;
\item $Q$ is the local $\NameCert_{\MetacicOpenFrontierLedgerUp}$ row.
\end{enumerate}
The carrier has no row for closed subject reduction, no arbitrary closed Church--Rosser theorem, no evidence-free global strong normalization theorem, no unrestricted closed beta-conversion decider, no exhaustive typed-example coverage theorem, and no full closed consistency claim.
\end{definition}

\begin{theorem}[MetaCIC open frontier ledger obligations]
\label{thm:metacic-open-frontier-ledger-namecert-obligations}
Every accepted $\MetacicOpenFrontierLedgerUp$ packet binds exactly the finite obligation surface displayed in \autoref{def:metacic-open-frontier-ledger-carrier}: carrier admission for $L=(S,E,F,N,D,T,K,H,C,P,Q)$, subject-reduction frontier visibility through $S$, closed-normal exclusion visibility through $E$, confluence-frontier visibility through $F$, normalization-frontier visibility through $N$, decidability-frontier visibility through $D$, typed-example boundary visibility through $T$, consistency-boundary visibility through $K$, componentwise $\hsame$ transport through $H$, finite $\Cont$ replay through $C$, package provenance through $P$, and local naming through $Q$.
\end{theorem}
\begin{proof}
Project the displayed carrier. The frontier rows are $S,E,F,N,D,T,K$, and each row corresponds to one boundary named in \autoref{ch:metacic-open-problems}.

Read the positive closed-normal row $E$ separately from the open rows $S,F,N,D,T,K$. This separation lets the ledger record the existing closed-normal exclusion surface without promoting it into a stronger endpoint.

The structural rows $H,C,P,Q$ only transport, replay, package, and name those displayed rows. Since no further coordinate is present, the listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[MetaCIC open frontier ledger subject-reduction boundary]
\label{thm:metacic-open-frontier-ledger-subject-reduction-boundary}
Every accepted $\MetacicOpenFrontierLedgerUp$ packet exposes subject reduction only through the frontier row $S$ and the sibling packet of \autoref{ch:concrete-instances-subjectreduction-namecert}. The row may name the $\mathrm{SubjectReductionDischargeBundle}$ interface and its beta-substitution, application-argument, lambda-domain, and Pi-domain coordinates, but it does not inhabit that bundle, prove the four coordinates, or export closed subject reduction.
\end{theorem}
\begin{proof}
Begin with the carrier row $S$. It is the only coordinate in the packet whose role is to name the subject-reduction frontier.

The sibling reference to \autoref{ch:concrete-instances-subjectreduction-namecert} supplies the accepted preservation-facing surface, while $S$ records the discharge interface that must still be supplied before the closed MetaCIC path can consume it as an unconditional theorem.

Transport through $H$ and replay through $C$ preserve this row as displayed. The package and local name rows $P,Q$ account for provenance and naming, so no hidden inhabitant of the discharge bundle or closed subject-reduction theorem can enter the ledger.
\end{proof}

\begin{theorem}[MetaCIC open frontier ledger normalization boundary]
\label{thm:metacic-open-frontier-ledger-normalization-boundary}
Agreement on an accepted $\MetacicOpenFrontierLedgerUp$ packet preserves the closed-normal exclusion row $E$ and the normalization frontier row $N$ as distinct coordinates. The packet may feed closed-normal consistency consumers through the closed-normal exclusion surface of \autoref{ch:concrete-instances-normalfalseexclusion-namecert} and the candidate-mediated audit surface of \autoref{ch:concrete-instances-metacicnormalizationaudit-namecert}, but it cannot erase candidate evidence, finished-normal evidence, or subject-reduction transport into a global closed consistency theorem.
\end{theorem}
\begin{proof}
Read $E$ as the closed-normal exclusion coordinate. It records the finite boundary at which a closed beta-normal proof of the internal false type is excluded.

Read $N$ as the normalization-frontier coordinate. It names the candidate-mediated route and its evidence boundary, matching the sibling audit surface rather than a blanket strong-normalization theorem.

The consistency row $K$ is downstream of both coordinates and remains a boundary row. Thus $H,C,P,Q$ can replay and name the closed-normal route, but they cannot identify $E$ with global normalization, erase the candidate evidence in $N$, or convert the ledger into full closed consistency.
\end{proof}

\begin{theorem}[MetaCIC open frontier ledger downstream handoff]
\label{thm:metacic-open-frontier-ledger-downstream-handoff}
Every downstream read of an accepted $\MetacicOpenFrontierLedgerUp$ carrier factors through
$$
S,E,F,N,D,T,K,H,C,P,Q.
$$
The handoff may cite subject-reduction obligations, closed-normal exclusion, confluence boundaries, candidate-mediated normalization, bounded decidability, typed-example gallery scope, and closed-consistency boundaries, but it may not replace those rows by vision prose, host metatheory, quotient equality over represented terms, or an unrecorded global MetaCIC theorem.
\end{theorem}
\begin{proof}
Project the carrier and apply the obligation theorem. The downstream consumer receives the seven frontier rows together with transport, replay, provenance, and local naming rows.

The confluence row $F$, decidability row $D$, typed-example row $T$, and consistency row $K$ are boundary coordinates rather than theorem endpoints. They keep residual substitution, bounded normal comparison, gallery scope, and full consistency separate from the positive closed-normal and checker-side data.

Since the carrier contains no host evaluator, quotient equality, erased normalizer, unrestricted conversion oracle, or global consistency endpoint, every accepted handoff remains inside the displayed ledger.
\end{proof}

\closureat{MetacicOpenFrontierLedgerUp}{seedStr}

\begin{closurestatus}{\MetacicOpenFrontierLedgerUp}
  \constructivestory{A $\MetacicOpenFrontierLedgerUp$ packet is generated from finite subject-reduction, closed-normal exclusion, confluence, normalization, decidability, typed-example, consistency-boundary, transport, continuation, provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-open-frontier-ledger-carrier}, \autoref{thm:metacic-open-frontier-ledger-namecert-obligations}, \autoref{thm:metacic-open-frontier-ledger-subject-reduction-boundary}, \autoref{thm:metacic-open-frontier-ledger-normalization-boundary}, and \autoref{thm:metacic-open-frontier-ledger-downstream-handoff} bind the finite open-frontier ledger and its downstream handoff discipline.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not prove closed subject reduction, arbitrary closed Church--Rosser, evidence-free global strong normalization, unrestricted closed beta-conversion decidability, exhaustive typed-example coverage, full closed consistency, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, exact row coverage for the seven frontier coordinates, sibling provenance, continuation replay, and non-escape for every downstream handoff.}
\end{closurestatus}
