\chapter{RealModulusFusion NameCert construction}
\label{ch:concrete-instances-realmodulusfusion-namecert}
\origin{human}

The $\RealModulusFusionUp$ packet realizes the finite shared-modulus face of the Real completeness route described in \autoref{ch:visions-real-completeness}. It sits between the diagonal-limit carrier of \autoref{ch:concrete-instances-realcompleteness-namecert}, the shared-tail packet of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}, the $\ChoiceFreeLimitScheduleUp$ selector route, the $\StreamNameUp$ window rows, the $\RegSeqRatUp$ handoff rows, and the terminal $\RealUp$ seal rows. The finite window family $W$ is consumed through the $\StreamNameUp$ window interface of \autoref{ch:concrete-instances-streamname-namecert} before the $\RegSeqRatUp$ handoff and $\RealUp$ seal are read. The chapter records only a seed NameCert surface; it does not claim full RealUp completeness.

\begin{definition}[RealModulusFusion carrier]
\label{def:real-modulus-fusion-carrier}
A $\RealModulusFusionUp$ carrier is a finite $\BHist$ packet
$$
F=(X,M,T,W,R,S,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the finite family of Cauchy modulus source rows consumed by the Real completeness diagonal route;
\item $M$ is the shared modulus row obtained before any tail comparison is exposed;
\item $T$ is the $\RegularCauchyTailMeetUp$ threshold row that records the common tail-meet comparison for the source rows;
\item $W$ is the finite $\StreamNameUp$ window family through which the scheduled rational tails are inspected;
\item $R$ is the $\RegSeqRatUp$ handoff row that reads the scheduled windows as regular rational data;
\item $S$ is the $\ChoiceFreeLimitScheduleUp$ or diagonal-selector route that names the inspected finite precision requests without a choice function;
\item $E$ is the $\RealUp$ seal row reached after the shared modulus, tail meet, stream-window, and regular-rational handoff rows have been displayed;
\item $H$ stores componentwise $\hsame$ transports for $X,M,T,W,R,S,E$;
\item $C$ stores the displayed $\Cont$ routes for reading modulus rows, tail-meet thresholds, stream windows, handoff rows, selector routes, and the seal boundary;
\item $P$ is the $\Pkg$ provenance row over $\RealCompletenessUp$, $\RegularCauchyTailMeetUp$, $\ChoiceFreeLimitScheduleUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RealModulusFusionUp}$ row.
\end{enumerate}
The carrier contains no quotient stream, selected limit, host real equality row, countable choice principle, trichotomy coordinate, or ambient completeness theorem.
\end{definition}

\begin{theorem}[RealModulusFusion NameCert obligations]
\label{thm:real-modulus-fusion-namecert-obligations}
The local $\NameCert_{\RealModulusFusionUp}$ surface for the carrier of \autoref{def:real-modulus-fusion-carrier} consists exactly of carrier admission, Cauchy modulus source admission, shared modulus exposure, $\RegularCauchyTailMeetUp$ threshold readback, $\StreamNameUp$ finite-window scheduling, $\RegSeqRatUp$ handoff routing, $\ChoiceFreeLimitScheduleUp$ selector routing, $\RealUp$ seal exposure, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row.
\end{theorem}
\begin{proof}
Carrier admission is projection from the finite packet $F$. The displayed rows list the Cauchy modulus sources, shared modulus, tail-meet threshold, stream windows, regular-rational handoff, choice-free schedule, seal row, transport, continuation, provenance, and local name.

The shared modulus route is finite. A consumer first reads the source modulus rows, then the shared row $M$, and only then reads the tail-meet threshold $T$ and the scheduled windows $W$.

The remaining obligations are routing and provenance obligations. The rows $H,C,P,N$ transport the displayed rows, replay the permitted reads, record package provenance, and name the packet. Since no quotient stream, selected limit, host real equality, countable choice, trichotomy, or ambient completeness coordinate appears in the carrier, no NameCert obligation can project one.
\end{proof}

\begin{theorem}[RealModulusFusion non-escape]
\label{thm:real-modulus-fusion-nonescape}
Every downstream consumer of an accepted $\RealModulusFusionUp$ packet can read only the finite rows
$$
X,M,T,W,R,S,E,H,C,P,N.
$$
In particular, no consumer route exports quotient streams, selected limits, host real equality, countable choice, trichotomy, or ambient completeness.
\end{theorem}
\begin{proof}
Start with a consumer route out of an accepted packet. By \autoref{def:real-modulus-fusion-carrier}, the only public coordinates are the eleven displayed rows of $F$.

Apply \autoref{thm:real-modulus-fusion-namecert-obligations}. Carrier admission and shared modulus exposure keep the read inside $X,M,T,W,R,S,E$, while transport and replay pass only through $H$ and $C$.

The package rows $P,N$ name the provenance and local certificate for the same finite surface. The excluded objects are not coordinates of $F$ and are not introduced by $\hsame$, $\Cont$, $\Pkg$, or $\NameCert$ routing, so the consumer has no exported path to them.
\end{proof}

\begin{theorem}[RealModulusFusion RegSeq handoff]
\label{thm:real-modulus-fusion-regseq-handoff}
For an accepted $\RealModulusFusionUp$ packet
$$
F=(X,M,T,W,R,S,E,H,C,P,N),
$$
every $\RegSeqRatUp$ read factors through the shared modulus row $M$, the tail-meet threshold $T$, and the scheduled $\StreamNameUp$ window family $W$ before it reaches the handoff row $R$. The handoff uses only the displayed $\hsame$ transports, $\Cont$ replay routes, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\begin{proof}
Project the accepted carrier. The regular-rational handoff row $R$ is displayed only after the shared modulus, tail-meet threshold, and stream-window rows.

Use the NameCert obligation surface. Source admission exposes $X$, shared modulus exposure fixes $M$, tail-meet readback fixes $T$, and finite-window scheduling fixes $W$ before a $\RegSeqRatUp$ consumer can read $R$.

Finally route the handoff through $H,C,P,N$. These rows transport, replay, package, and name the same finite route; they do not add quotient streams, selected limits, countable choice, trichotomy, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[RealModulusFusion Real seal boundary]
\label{thm:real-modulus-fusion-real-seal-boundary}
Every $\RealUp$ seal read exported by an accepted $\RealModulusFusionUp$ packet factors through the finite route
$$
X \longrightarrow M \longrightarrow T \longrightarrow W \longrightarrow R \longrightarrow S \longrightarrow E
$$
with transport, replay, provenance, and naming supplied by $H,C,P,N$. The seal boundary is therefore a finite shared-modulus NameCert over Cauchy modulus rows, tail-meet thresholds, $\StreamNameUp$ windows, $\RegSeqRatUp$ handoff, and $\RealUp$ seal rows, not a proof of host real completeness.
\end{theorem}
\begin{proof}
Begin with the accepted carrier and the displayed route to the seal. The row $E$ is the only $\RealUp$ seal coordinate, and it is downstream of the shared modulus, tail-meet, window, handoff, and selector rows.

Apply \autoref{thm:real-modulus-fusion-regseq-handoff} to force every regular-rational read through $M,T,W,R$. Then apply the NameCert obligations to pass from the choice-free schedule row $S$ to the seal row $E$ using the displayed continuation routes.

The non-escape theorem closes the boundary. Since the packet exports no quotient stream, selected limit, host real equality, countable choice, trichotomy, or ambient completeness coordinate, the seal read is only the displayed $\RealUp$ boundary of the finite shared-modulus route.
\end{proof}

\closureat{RealModulusFusionUp}{seedStr}

\begin{closurestatus}{\RealModulusFusionUp}
  \constructivestory{A $\RealModulusFusionUp$ packet is generated from finite Cauchy modulus source rows, one shared modulus row, a $\RegularCauchyTailMeetUp$ threshold row, $\StreamNameUp$ windows, a $\RegSeqRatUp$ handoff row, a $\ChoiceFreeLimitScheduleUp$ selector route, a $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ replay routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-modulus-fusion-carrier}, \autoref{thm:real-modulus-fusion-namecert-obligations}, \autoref{thm:real-modulus-fusion-nonescape}, \autoref{thm:real-modulus-fusion-regseq-handoff}, and \autoref{thm:real-modulus-fusion-real-seal-boundary} specify the finite shared-modulus carrier, local naming obligations, non-escape boundary, regular-rational handoff, and real-seal boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close full $\RealUp$ completeness, quotient-stream semantics, selected limits, host real equality, countable choice, trichotomy, ambient completeness, or Lean-side formal verification for $\RealModulusFusionUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability under $\hsame$ and $\Cont$, shared-modulus exactness, tail-meet readback, regular-rational handoff, real-seal boundary, and non-escape for the same packet rows.}
\end{closurestatus}
