\chapter{A Concrete Naming Certificate for $\MetaCICSubstitutionAuditPacketUp$}
\label{ch:concrete-instances-metacic-substitution-audit-packet-namecert}
\origin{human}

The $\MetaCICSubstitutionAuditPacketUp$ packet realizes the substitution audit map of \autoref{ch:metacic-substitution-audit-map} as a finite NameCert carrier. It sits between the closed substitution seal of \autoref{ch:concrete-instances-closedsubstitutionseal-namecert}, the closed syntax boundary of \autoref{ch:concrete-instances-closed-substitution-boundary-namecert}, and the subject-reduction obstruction packet of \autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert}: the present packet records closed movement and audit handoff rows, while the sibling obstruction packet records why those rows do not close unrestricted subject reduction.

\begin{definition}[MetaCIC substitution audit packet carrier]
\label{def:metacic-substitution-audit-packet-carrier}
A $\MetaCICSubstitutionAuditPacketUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,D,L,M,C,G,B,H,K,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $T$ records the MetaCIC \texttt{Term} row inspected by the substitution audit;
\item $D$ records the \texttt{ClosedAt} boundary row at which public reads of the term are admitted;
\item $L$ records the \texttt{shift\_closed} row, namely the closed shift route visible at boundary $D$;
\item $M$ records the \texttt{substitute\_closed} row, namely the closed substitution route visible at boundary $D$;
\item $C$ records the closed composition rows for the closed-at-zero and closed-at-depth substitution compositions named by the audit map;
\item $G$ records the generator-closure classifier rows for closed-under-shift, closed-under-substitution, and closed-composition reads;
\item $B$ records the boundary handoff to beta substitution preservation and to the four subject-reduction obstruction rows;
\item $H$ records componentwise $\hsame$ transports for term, boundary, movement, generator, composition, handoff, provenance, and local naming rows;
\item $K$ records the displayed $\Cont$ routes by which consumers inspect the rows without crossing from closed syntax movement into typed preservation;
\item $P$ is the $\Pkg$ provenance over the MetaCIC substitution audit map, the closed-substitution boundary packet, the subject-reduction obstruction packet, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\MetaCICSubstitutionAuditPacketUp}$ row.
\end{enumerate}
The carrier contains no unrestricted substitution calculus, no beta-substitution preservation theorem, no closed subject-reduction theorem, no quotient equality, and no erased semantic equality coordinate.
\end{definition}

\begin{theorem}[MetaCIC substitution audit packet NameCert obligations]
\label{thm:metacic-substitution-audit-packet-namecert-obligations}
The carrier of \autoref{def:metacic-substitution-audit-packet-carrier} satisfies the local $\NameCert_{\MetaCICSubstitutionAuditPacketUp}$ obligation surface. Its obligation rows are carrier admission for $Q=(T,D,L,M,C,G,B,H,K,P,N)$, classifier stability for the closed movement and generator rows, closed-boundary exactness through $D,L,M,C$, generator-closure handoff through $G,B$, and the non-escape ledger carried by $H,K,P,N$.
\end{theorem}
\begin{proof}
Carrier admission is the displayed finite $\BHist$ packet. The coordinates name the term, closed boundary, closed movement, closed composition, generator, subject-reduction handoff, transport, continuation, provenance, and local naming rows.

Project $D,L,M,C,G$. These rows expose exactly the closed syntax movement and generator-closure surface described in \autoref{ch:metacic-substitution-audit-map}; they do not contain a typed preservation conclusion.

Project $B$ next. The row is a handoff into the obstruction surface of \autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert}, not a discharge of beta substitution preservation or of the remaining subject-reduction obligations.

Finally inspect $H,K,P,N$. These rows transport, replay, locate, and name the same finite packet. Since none of them carries a hidden typed-preservation coordinate, the local NameCert obligations are exhausted by the displayed rows.
\end{proof}

\begin{theorem}[MetaCIC substitution audit closed boundary]
\label{thm:metacic-substitution-audit-packet-boundary}
For an accepted $\MetaCICSubstitutionAuditPacketUp$ carrier $Q=(T,D,L,M,C,G,B,H,K,P,N)$, every public read factors through the \texttt{ClosedAt} boundary row $D$ and then through the closed shift and closed substitution rows $L,M$ before it can consume the subject-reduction handoff row $B$.
\end{theorem}
\begin{proof}
Read the packet by projection. The term row $T$ is public only through the displayed boundary row $D$, and the movement rows $L,M$ are the only closed shift and closed substitution coordinates tied to that boundary.

The closed composition row $C$ and generator classifier row $G$ still sit on the same closed boundary. They can refine the audit read, but they do not bypass $D,L,M$.

The subject-reduction handoff row $B$ appears after the closed movement rows in the carrier inventory. Thus a consumer reaches any handoff only after the closed boundary and movement coordinates have already been selected.
\end{proof}

\begin{theorem}[MetaCIC substitution audit packet non-escape]
\label{thm:metacic-substitution-audit-packet-nonescape}
An accepted $\MetaCICSubstitutionAuditPacketUp$ carrier exports no unrestricted substitution commutation theorem, no open-term semantic equality, no full subject-reduction theorem, and no host equality principle. Its public surface is limited to the displayed closed boundary, closed movement, closed composition, generator-closure, handoff, transport, continuation, provenance, and local naming rows.
\end{theorem}
\begin{proof}
The carrier definition lists only $T,D,L,M,C,G,B,H,K,P,N$. Among these rows, the substitution-facing coordinates are the closed boundary and movement rows $D,L,M,C,G$.

The handoff row $B$ points to the subject-reduction obstruction surface, so it records where the missing typed-preservation work begins. It is not itself a proof of unrestricted substitution commutation, open-term semantic equality, or full subject reduction.

Rows $H,K,P,N$ only transport, replay, package, and name the finite packet. Since no host equality coordinate is present, those rows cannot export a host equality principle.
\end{proof}

\begin{theorem}[MetaCIC substitution audit boundary non-escape]
\label{thm:metacic-substitution-audit-packet-boundary-nonescape}
For an accepted $\MetaCICSubstitutionAuditPacketUp$ carrier $Q=(T,D,L,M,C,G,B,H,K,P,N)$, every consumer read remains inside the term row, closed boundary row, closed syntax movement rows, generator-closure rows, closed composition rows, and explicit subject-reduction handoff row. In particular, agreement on $H,K,P,N$ does not export an unrestricted substitution calculus, beta-substitution preservation, or closed subject reduction.
\end{theorem}
\begin{proof}
Read the carrier by projection. The rows $T,D,L,M,C,G$ provide the term, closed boundary, closed syntax movement, generator closure, and closed composition data, all under the displayed hypotheses.

The only row touching subject reduction is $B$. Its role is to point at the obstruction boundary, so a consumer can cite the missing discharge surface without obtaining the discharge itself.

The transport, continuation, provenance, and naming rows $H,K,P,N$ preserve the packet as a packet. They do not add a new row and therefore cannot export the unrestricted calculus or typed-preservation endpoints excluded by the carrier definition.
\end{proof}

\closureat{MetaCICSubstitutionAuditPacketUp}{seedStr}

\begin{closurestatus}{\MetaCICSubstitutionAuditPacketUp}
  \constructivestory{A $\MetaCICSubstitutionAuditPacketUp$ packet is generated from a MetaCIC term row, a ClosedAt boundary row, closed movement rows, generator-closure rows, closed composition rows, a subject-reduction handoff boundary, componentwise transports, displayed continuation routes, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-substitution-audit-packet-carrier}, \autoref{thm:metacic-substitution-audit-packet-namecert-obligations}, \autoref{thm:metacic-substitution-audit-packet-boundary}, \autoref{thm:metacic-substitution-audit-packet-nonescape}, and \autoref{thm:metacic-substitution-audit-packet-boundary-nonescape} bind the finite closed-substitution audit packet and its non-escape boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close unrestricted substitution, beta-substitution preservation, closed subject reduction, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, closed movement readback, generator-closure readback, closed composition readback, statement-shape routing, handoff routing, transport, continuation, provenance, naming, and boundary non-escape for the same finite packet.}
\end{closurestatus}
