\chapter{A Concrete Naming Certificate for $\SubjectReductionDischargeRouteCertUp$}
\label{ch:concrete-instances-subjectreductiondischargeroutecert-namecert}
\origin{human}

The $\SubjectReductionDischargeRouteCertUp$ packet turns the explicit discharge route of \autoref{ch:sr-discharge-routes} into a finite NameCert carrier. It sits between the socket packet of \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert} and the subject-reduction packet of \autoref{ch:concrete-instances-subjectreduction-namecert}: the socket names the four discharge obligations, the subject-reduction packet names the consumed typing-preservation read, and this route certificate records how bundle access exposes exactly that same four-row payload.

\begin{definition}[SubjectReductionDischargeRouteCert carrier]
\label{def:subject-reduction-discharge-route-cert-carrier}
A $\SubjectReductionDischargeRouteCertUp$ carrier is a finite $\BHist$ packet
$$
R=(B,V,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the explicit bundle row, naming the four-field $\mathrm{SubjectReductionDischargeBundle}$ packet;
\item $V$ is the bundle-consumption row for the subject-reduction theorem obtained from the explicit packet;
\item $O$ is the checked no-bundle obstruction row for the present raw relation;
\item $H$ records componentwise $\hsame$ transports for the bundle, bundle-consumption, obstruction, socket, provenance, and naming rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read the explicit bundle route, the obstruction ledger, the discharge socket, and the subject-reduction packet;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:sr-discharge-routes}, \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}, and \autoref{ch:concrete-instances-subjectreduction-namecert};
\item $N$ is the local $\NameCert_{\SubjectReductionDischargeRouteCertUp}$ row.
\end{enumerate}
The carrier contains no inhabitant of the four discharge hypotheses for the closed-CIC substrate, no closed subject-reduction theorem, no host conversion rule, and no alternate subject-reduction route outside the displayed bundle row.
\end{definition}
\leandef{BEDC.MetaCIC.SubjectReductionDischargeBundle}

\begin{theorem}[SubjectReductionDischargeRouteCert NameCert obligations]
\label{thm:subject-reduction-discharge-route-cert-obligations}
For the carrier of \autoref{def:subject-reduction-discharge-route-cert-carrier}, the local $\NameCert_{\SubjectReductionDischargeRouteCertUp}$ surface consists exactly of carrier admission for
$$
R=(B,V,O,H,C,P,N),
$$
route visibility for the explicit bundle row $B$, bundle-consumption row $V$, and obstruction row $O$, componentwise transport through $H$, displayed continuation reads through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.MetaCIC.subject\_reduction\_from\_bundle}
\begin{proof}
Project the displayed packet $R$. The explicit route is the bundle row $B$ consumed by $V$, and the obstruction row $O$ records why the raw relation does not inhabit the bundle.

Read $H$ and $C$ next. Transport preserves the named route rows componentwise, while continuation replay exposes only the displayed bundle, obstruction, socket, and subject-reduction reads.

Finally inspect $P$ and $N$. Provenance ties the route certificate to the vision chapter, the discharge socket, and the subject-reduction packet. Since no carrier coordinate supplies a closed-CIC inhabitant of the four hypotheses, the listed rows exhaust the NameCert obligations without closing the obstruction boundary.
\end{proof}

\begin{theorem}[SubjectReductionDischargeRouteCert socket consumption]
\label{thm:subject-reduction-discharge-route-cert-socket-consumption}
Every downstream consumer of an accepted $\SubjectReductionDischargeRouteCertUp$ packet that reads a $\SubjectReductionDischargeSocketUp$ row must consume the socket through the displayed route rows $B,V,O$, transported by $H$, replayed through $C$, and accounted for by $P,N$. The consumer may use the explicit bundle route only after the four discharge rows are supplied, and that route does not export a closed subject-reduction theorem for the present closed-CIC substrate.
\end{theorem}
\begin{proof}
Start with the accepted route certificate. Its only subject-reduction route coordinates are the explicit bundle row and the corresponding consumption row.

Apply the socket chapter through provenance. The socket supplies the four discharge rows as a finite obligation surface, and the route certificate records that those rows are carried explicitly by $B$.

The subject-reduction packet is reached only after the displayed route has been replayed through $C$. Because the carrier has no coordinate for a closed-CIC inhabitant of the four hypotheses, socket consumption remains a route-certificate read and cannot become an unparameterised closed theorem.
\end{proof}

\closureat{SubjectReductionDischargeRouteCertUp}{seedStr}

\begin{closurestatus}{\SubjectReductionDischargeRouteCertUp}
  \constructivestory{A $\SubjectReductionDischargeRouteCertUp$ packet is generated from an explicit bundle route, a subject-reduction consumption row, an obstruction row, componentwise $\hsame$ transports, displayed $\Cont$ routes, provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:subject-reduction-discharge-route-cert-carrier}, \autoref{thm:subject-reduction-discharge-route-cert-obligations}, and \autoref{thm:subject-reduction-discharge-route-cert-socket-consumption} bind the finite bundle route certificate and its socket-consumption boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close the four MetaCIC discharge obligations, construct an inhabited discharge bundle for the closed-CIC substrate, prove closed subject reduction, give Lean verification of the route certificate, or bridge check it.}
  \upgradepath{Obligation closure requires checked carrier admission, bundle route exactness, socket consumption, route replay, provenance, local naming, and non-escape for the same finite packet.}
\end{closurestatus}
