\chapter{A Concrete Naming Certificate for $\ClosedBetaPathUp$}
\label{ch:concrete-instances-closedbetapath-namecert}
\origin{human}

The $\ClosedBetaPathUp$ packet realizes the closure-preservation audit map of
\autoref{ch:metacic-closure-preservation-audit-map} as a finite NameCert route
object. It sits between the beta inventory of
\autoref{ch:concrete-instances-metacicbetaaudit-namecert}, the normal-form
seal of \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert},
and the closed-normal main-result packet of
\autoref{ch:concrete-instances-closednormalconsistencymain-namecert}: it names
the route by which closedness travels along finite beta movement before those
downstream packets read any closed-normal or beta-audit rows.

\begin{definition}[Closed beta path carrier]
\label{def:closed-beta-path-carrier}
A $\ClosedBetaPathUp$ carrier is a finite $\BHist$ packet
$$
Q=(s,t,n,B,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $s$ is the source MetaCIC term row;
\item $t$ is the target MetaCIC term row;
\item $n$ is the closedness-depth row for the displayed $\mathrm{ClosedAt}$
boundary;
\item $B$ is the finite $\mathrm{BetaStarStep}(s,t)$ route row, whose
one-step edges are $\mathrm{BetaStep}$ constructors;
\item $K$ is the closure-preservation witness row naming the
$\mathsf{BEDC.MetaCIC.betaStarStep\_preserves\_closed}$ route from
$\mathrm{ClosedAt}(n,s)$ to $\mathrm{ClosedAt}(n,t)$;
\item $H$ records componentwise $\hsame$ transport for the source, target,
depth, beta-route, closure-witness, provenance, and naming rows;
\item $C$ records the displayed $\Cont$ replay routes by which a consumer reads
$B$ and then $K$;
\item $P$ is the $\Pkg$ provenance over $\mathrm{ClosedAt}$,
$\mathrm{BetaStep}$, $\mathrm{BetaStarStep}$, $\mathsf{shift}$,
$\mathsf{substitute}$, componentwise transport, and sibling NameCert packets;
\item $N$ is the local $\NameCert_{\ClosedBetaPathUp}$ row.
\end{enumerate}
The carrier has no coordinate for typing preservation, normalization,
confluence, beta conversion, or closed consistency.
\end{definition}

\begin{theorem}[Closed beta path NameCert obligations]
\label{thm:closed-beta-path-namecert-obligations}
For an accepted $\ClosedBetaPathUp$ carrier
$$
Q=(s,t,n,B,K,H,C,P,N),
$$
the local $\NameCert_{\ClosedBetaPathUp}$ surface consists exactly of five
obligations:
\begin{enumerate}
\item carrier admission for the displayed finite packet;
\item preservation of $\mathrm{ClosedAt}(n,\cdot)$ along the finite beta route
$B$ through the witness row $K$;
\item exact replay of the route order by first reading $B$ and then reading
$K$ through the displayed continuation rows;
\item non-escape from typing, normalization, confluence, beta-conversion, and
closed-consistency claims not present in the carrier;
\item ledger exactness for $s,t,n,B,K,H,C,P,N$ and no hidden route coordinate.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is the packet of
\autoref{def:closed-beta-path-carrier}. The admitted route row $B$ supplies the
finite beta chain, and the witness row $K$ supplies the closedness transport
for exactly that chain.

Continuation replay is ordered by the carrier itself: a consumer first reads
the beta-star route and then reads the closure witness. Componentwise
transport through $H$ preserves the same source, target, depth, route, witness,
provenance, and naming rows.

The remaining coordinates are structural provenance and naming rows. Since no
coordinate carries typing preservation, normalization, confluence, beta
conversion, or closed consistency, the five displayed obligations exhaust the
local NameCert surface.
\end{proof}

\begin{theorem}[Closed beta path closure-preservation factorization]
\label{thm:closed-beta-path-closure-preservation-factorization}
Every consumer of an accepted $\ClosedBetaPathUp$ packet that later reads a
closed-normal packet, a normal-form consistency seal, a closed-normal main
packet, or a beta-audit packet must first factor its closedness read through
the $\mathsf{BEDC.MetaCIC.betaStarStep\_preserves\_closed}$ route named by
$K$. The consumer may then pass the transported closed endpoint to the sibling
packet it cites, but it cannot use $\ClosedBetaPathUp$ as a typing,
normalization, confluence, beta-conversion, or consistency certificate.
\end{theorem}
\begin{proof}
Project the accepted packet $Q$. The only row that exports closedness at the
target endpoint is $K$, and $K$ is tied to the displayed beta-star route $B$.
Thus every closedness read from $s$ to $t$ passes through the same
closure-preservation route.

The sibling packets cited by the consumer have their own carriers and local
NameCert rows. The present packet can hand them the transported closed endpoint
only after $B$ and $K$ have been replayed through $C$ and accounted for by
$P,N$.

Because the carrier lacks rows for typing preservation, normalization,
confluence, beta conversion, and consistency, the factorization cannot be
strengthened into any of those claims.
\end{proof}
\leanvariant{BEDC.MetaCIC.betaStarStep\_preserves\_closed}

\closureat{ClosedBetaPathUp}{seedStr}
\closureat{ClosedBetaPathUp}{obligationStr}

\begin{closurestatus}{\ClosedBetaPathUp}
  \constructivestory{A $\ClosedBetaPathUp$ packet is generated from a source term, target term, closedness depth, finite BetaStarStep route, beta-star closedness-preservation witness, componentwise $\hsame$ transports, displayed $\Cont$ replay routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:closed-beta-path-carrier}, \autoref{thm:closed-beta-path-namecert-obligations}, and \autoref{thm:closed-beta-path-closure-preservation-factorization} bind the finite closed-beta-route carrier, its five local NameCert obligations, and its closure-preservation factorization boundary.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.MetaCIC.betaStarStep\_preserves\_closed}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close MetaCIC subject reduction, normalization, confluence, beta conversion, full closed consistency, or a public standard bridge.}
  \upgradepath{Scoped closure requires checked carrier admission, route replay exactness, ledger exactness, and non-escape for the same finite closed beta path packet.}
\end{closurestatus}
