\chapter{A Concrete Naming Certificate for $\AuditMapFamilyPacketUp$}
\label{ch:concrete-instances-auditmapfamilypacket-namecert}
\origin{human}

The $\AuditMapFamilyPacketUp$ carrier realizes the audit-map family methodology of \autoref{ch:audit-map-family-methodology} as concrete finite NameCert data. It sits beside the subject-reduction certificate of \autoref{ch:concrete-instances-subjectreduction-namecert}, the MetaCIC audit synthesis packet of \autoref{ch:concrete-instances-metacicauditsynthesispacket-namecert}, and the substitution audit map of \autoref{ch:concrete-instances-substitutionauditmap-namecert}. Those sibling chapters supply local audit surfaces; this packet records the family-level rows that let a consumer read positive content, conditional content, obstructions, frontier claims, cross-module use, and boundary data without treating partial audit maps as closed MetaCIC.

\begin{definition}[Audit-map family packet carrier]
\label{def:audit-map-family-packet-carrier}
An $\AuditMapFamilyPacketUp$ carrier is a finite $\BHist$ packet
$$
A=(P,C,O,F,X,H,R,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the finite family of positive-content rows already licensed by local audit maps, including checked inventory and concrete packet rows supplied by sibling chapters;
\item $C$ is the family of conditional rows, each paired with the displayed discharge route or setup field needed before its conclusion can be consumed;
\item $O$ is the obstruction family naming blocked routes, missing inhabitants, shape restrictions, and no-go rows that must remain visible;
\item $F$ is the frontier family naming the strongest nearby claims offered to downstream readers without proof by the packet;
\item $X$ is the cross-module-use family naming which audit maps, synthesis chapters, and boundary packets may consume or supply each displayed row;
\item $H$ records componentwise $\hsame$ transports for positive, conditional, obstruction, frontier, cross-module-use, continuation, provenance, and local naming rows;
\item $R$ records the displayed $\Cont$ read routes by which a consumer inspects the audit rows without adding hidden coordinates;
\item $Q$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, the audit-map methodology, and the concrete sibling packets cited above;
\item $N$ is the local $\NameCert_{\AuditMapFamilyPacketUp}$ row.
\end{enumerate}
The classifier accepts exactly packets whose visible coordinates are $P,C,O,F,X,H,R,Q,N$. It exports no closed subject-reduction theorem, no full closed-MetaCIC consistency theorem, no erased obstruction, no proof of a frontier row, and no host semantic equality coordinate.
\end{definition}

\begin{theorem}[Audit-map family packet NameCert obligations]
\label{thm:audit-map-family-packet-namecert-obligations}
For the carrier of \autoref{def:audit-map-family-packet-carrier}, the local $\NameCert_{\AuditMapFamilyPacketUp}$ surface consists exactly of five obligations:
\begin{enumerate}
\item carrier admission for the finite packet $A=(P,C,O,F,X,H,R,Q,N)$;
\item classifier transport for the positive, conditional, obstruction, frontier, and cross-module-use rows through the componentwise $\hsame$ transports in $H$ and the displayed $\Cont$ routes in $R$;
\item obstruction and frontier exactness, requiring $O$ and $F$ to remain visible as boundary rows rather than as discharged theorem content;
\item cross-map dependency exposure, requiring every use by \autoref{ch:concrete-instances-subjectreduction-namecert}, \autoref{ch:concrete-instances-metacicauditsynthesispacket-namecert}, \autoref{ch:concrete-instances-substitutionauditmap-namecert}, or any sibling audit packet to be recorded in $X$ and sourced by $Q$;
\item non-escape from hidden closure, excluding closed MetaCIC, host semantics, unlisted discharge routes, and implicit proof of any obstruction or frontier row.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier $A$. Carrier admission supplies only the displayed rows $P,C,O,F,X,H,R,Q,N$, so every audit-map family read begins with the finite packet itself.

Transport is componentwise. The row $H$ moves the positive, conditional, obstruction, frontier, and cross-module-use rows together, while $R$ replays only the displayed continuation routes. Hence classifier movement cannot add a new row class.

The obstruction and frontier coordinates are then fixed. Rows $O$ and $F$ are part of the visible packet, but neither is a discharge witness or theorem constructor. They name where the audit family stops.

Finally inspect $X,Q,N$. Cross-module use is listed before it is consumed, provenance cites only displayed sibling packets, and the local name binds the same carrier. Therefore hidden closure, unlisted routes, host semantics, and implicit frontier proofs are outside the NameCert surface.
\end{proof}

\begin{theorem}[Audit-map family packet frontier exhaustion]
\label{thm:audit-map-family-packet-frontier-exhaustion}
For every accepted $\AuditMapFamilyPacketUp$ carrier $A=(P,C,O,F,X,H,R,Q,N)$, every consumer read of the audit-map family factors through the displayed rows $P,C,O,F,X,H,R,Q,N$. In particular, a downstream consumer cannot treat a partial audit map as closed MetaCIC, cannot bypass the conditional rows in $C$, cannot erase the obstruction rows in $O$, and cannot turn a frontier row in $F$ into a closed theorem.
\end{theorem}
\begin{proof}
Start from the carrier projection. The only family rows are positive content $P$, conditional content $C$, obstructions $O$, frontier rows $F$, and cross-module-use rows $X$.

Use the obligation theorem. Classifier transport and continuation replay preserve those same rows through $H$ and $R$, while $Q$ and $N$ record provenance and local naming without adding another consumer route.

It remains to exclude hidden closure. Since every consumer read has already been routed through the displayed audit rows, no downstream chapter can read a closed MetaCIC theorem, a discharged conditional row, an erased obstruction, or a proof of a frontier row unless that object appears as a displayed coordinate of the packet.
\end{proof}

\closureat{AuditMapFamilyPacketUp}{seedStr}

\begin{closurestatus}{\AuditMapFamilyPacketUp}
  \constructivestory{An $\AuditMapFamilyPacketUp$ packet is generated from positive-content rows, conditional rows, obstruction rows, frontier rows, cross-module-use rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:audit-map-family-packet-carrier}, \autoref{thm:audit-map-family-packet-namecert-obligations}, and \autoref{thm:audit-map-family-packet-frontier-exhaustion} bind the finite audit-map family carrier, row classifier, dependency exposure, and hidden-closure boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close subject reduction, full closed MetaCIC, host semantics, proof of frontier rows, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, obstruction and frontier exactness, cross-map dependency exposure, provenance, local naming, and non-escape for the same finite packet.}
\end{closurestatus}
