\chapter{A Concrete Naming Certificate for $\AuditMapMethodologyUp$}
\label{ch:concrete-instances-auditmapmethodology-namecert}
\origin{ai}

The $\AuditMapMethodologyUp$ packet realizes the audit-map family methodology
of \autoref{ch:audit-map-family-methodology} as a finite NameCert carrier. It
sits between the family-level method and the substitution audit map of
\autoref{ch:concrete-instances-substitutionauditmap-namecert}: the methodology
packet names the template, admissible row classes, boundary rule, and sibling
handoff through which concrete audit maps become readable without claiming
their neighbouring proof obligations.

\begin{definition}[Audit-map methodology carrier]
\label{def:audit-map-methodology-carrier}
An $\AuditMapMethodologyUp$ carrier is a finite $\BHist$ packet
$$
M=(T,A,C,O,F,B,S,H,R,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $T$ is the audit-map template row, recording the setup, established,
conditional, obstruction, frontier, cross-reference, and boundary slots of
\autoref{prin:audit-map-family-template};
\item $A$ is the admitted audit-map row family, whose entries include concrete
local maps such as $\SubstitutionAuditMapUp$;
\item $C$ is the classifier row separating established, conditional,
obstruction, frontier, and handoff content;
\item $O$ is the obligation-surface row listing the finite NameCert checks
needed before a local audit map can be consumed;
\item $F$ is the frontier row that records named open sockets without turning
them into theorem rows;
\item $B$ is the boundary row excluding hidden closure, ambient equality, and
unstated discharge routes;
\item $S$ is the sibling handoff row pointing from the methodology packet to
the concrete substitution audit map and to later audit-map family ledgers;
\item $H$ records componentwise $\hsame$ transports for the template, audit-map
family, classifier, obligation, frontier, boundary, handoff, route,
provenance, and naming rows;
\item $R$ records the displayed $\Cont$ routes through which consumers inspect
the methodology packet;
\item $P$ is the $\Pkg$ provenance over the audit-map family method,
$\SubstitutionAuditMapUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows;
\item $N$ is the local $\NameCert_{\AuditMapMethodologyUp}$ row.
\end{enumerate}
The classifier accepts exactly packets whose visible rows are the displayed
template, admitted audit-map family, classifier, obligation surface, frontier,
boundary, sibling handoff, transport, continuation, provenance, and naming
rows. It exports no proof of subject reduction, no confluence theorem, no
normalisation theorem, no closed-consistency theorem, no unlisted audit map,
and no host semantic equality coordinate.
\end{definition}
\leanchecked{BEDC.Derived.AuditMapMethodologyUp.AuditMapMethodologyTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Audit-map methodology obligation surface]
\label{thm:audit-map-methodology-obligation-surface}
For the carrier of \autoref{def:audit-map-methodology-carrier}, the local
$\NameCert_{\AuditMapMethodologyUp}$ surface consists exactly of carrier
admission for
$$
M=(T,A,C,O,F,B,S,H,R,P,N),
$$
template readback through $T$, admitted-map readback through $A$, classifier
readback through $C$, obligation-surface readback through $O$, frontier
readback through $F$, boundary readback through $B$, sibling handoff through
$S$, componentwise transport through $H$, displayed continuation through $R$,
package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite packet $M$. The row $T$ displays the audit-map template
before any local audit content is read, while $A$ supplies only the admitted
family of concrete map rows.

Read $C,O,F,B$ next. The classifier separates the row classes, the obligation
surface lists the NameCert checks, the frontier keeps open sockets visible,
and the boundary records the exclusions attached to the methodology.

Finally inspect $S,H,R,P,N$. The handoff row names the concrete sibling
surface, the transport and continuation rows replay the same displayed data,
the provenance row cites only visible sources, and the local naming row binds
the packet. No further obligation remains outside the listed coordinates.
\end{proof}

\begin{theorem}[Audit-map methodology template soundness]
\label{thm:audit-map-methodology-template-soundness}
Every accepted $\AuditMapMethodologyUp$ carrier
$M=(T,A,C,O,F,B,S,H,R,P,N)$ presents the template of
\autoref{prin:audit-map-family-template} as finite NameCert data: positive
content is read through the classifier, conditional content is routed through
the obligation surface, obstruction and frontier content remain named rows,
and cross-module use is available only through displayed handoff and
continuation rows.
\end{theorem}
\begin{proof}
Use the carrier definition to read $T$ as the finite template row. Its slots
are setup, established, conditional, obstruction, frontier, cross-reference,
and boundary, matching the method described in
\autoref{ch:audit-map-family-methodology}.

The classifier row $C$ and obligation row $O$ then sort the template entries.
Established entries may be cited as displayed rows, conditional entries retain
their named routes, and obstruction or frontier entries remain visible without
being promoted to solved theorem content.

The rows $S$ and $R$ account for cross-module use. A consumer can follow only
the displayed sibling handoff and continuation routes, so the template is
sound as NameCert data rather than as an ambient claim about neighbouring
modules.
\end{proof}

\begin{theorem}[Audit-map methodology boundary non-escape]
\label{thm:audit-map-methodology-boundary-nonescape}
For every accepted $\AuditMapMethodologyUp$ carrier
$M=(T,A,C,O,F,B,S,H,R,P,N)$, every consumer read remains inside the displayed
template, admitted audit-map family, classifier, obligation surface, frontier,
boundary, sibling handoff, $\hsame$ transport, $\Cont$ route, $\Pkg$
provenance, and local $\NameCert$ rows. In particular, the packet cannot
export a hidden proof obligation discharge, an unlisted audit map, subject
reduction, confluence, normalisation, closed consistency, or host semantic
equality.
\end{theorem}
\begin{proof}
Begin with carrier projection. The only consumer-facing data are the rows
$T,A,C,O,F,B,S,H,R,P,N$, so every read of the methodology packet enters
through the displayed audit-map family surface.

Apply the obligation surface of
\autoref{thm:audit-map-methodology-obligation-surface}. It binds each row
class, frontier socket, boundary exclusion, and sibling handoff to a visible
coordinate and routes transport or continuation through $H$ and $R$.

The provenance and naming rows rule out escape. Since $P$ records only the
methodology source and named concrete audit-map rows, and $N$ names only this
finite carrier, no consumer can extract a theorem or discharge route absent
from the packet.
\end{proof}

\begin{theorem}[Audit-map methodology substitution handoff]
\label{thm:audit-map-methodology-substitution-handoff}
The $\AuditMapMethodologyUp$ carrier admits $\SubstitutionAuditMapUp$ as a
concrete sibling handoff exactly at the row $S$: the methodology packet may
point to the substitution audit-map carrier of
\autoref{ch:concrete-instances-substitutionauditmap-namecert}, read its
closed-substitution audit rows as an admitted local map through $A$, and keep
all substitution-specific non-escape exclusions inside that sibling chapter.
\end{theorem}
\begin{proof}
Read $S$ as the sibling handoff row and $A$ as the admitted audit-map family
row. The handoff therefore points to $\SubstitutionAuditMapUp$ only as a
concrete local audit map, not as a replacement for the methodology packet.

The classifier $C$ and obligation row $O$ preserve the distinction between the
methodology slots and the substitution-specific rows. Closed shift,
substitution, and closed-composition data are read in the sibling chapter,
while this carrier records the fact that such a map is admitted by the method.

Finally use $B,H,R,P,N$. The boundary row keeps unrestricted substitution,
beta-substitution preservation, and closed subject reduction outside the
methodology handoff; transport, continuation, provenance, and naming replay
only the displayed finite rows. Thus the handoff is available without
absorbing the sibling's exclusions into a stronger methodology claim.
\end{proof}

\closureat{AuditMapMethodologyUp}{seedStr}

\begin{closurestatus}{\AuditMapMethodologyUp}
  \constructivestory{An $\AuditMapMethodologyUp$ packet is generated from an audit-map template row, admitted audit-map family rows, classifier rows, obligation-surface rows, frontier and boundary rows, a sibling handoff row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:audit-map-methodology-carrier}, \autoref{thm:audit-map-methodology-obligation-surface}, \autoref{thm:audit-map-methodology-template-soundness}, \autoref{thm:audit-map-methodology-boundary-nonescape}, and \autoref{thm:audit-map-methodology-substitution-handoff} bind the finite audit-map methodology carrier, template soundness, boundary, and substitution handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close subject reduction, confluence, normalisation, closed consistency, hidden discharge routes, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, template readback, admitted-map readback, classifier and obligation-surface exactness, boundary non-escape, substitution handoff, transport, continuation, provenance, and naming for the same finite packet.}
\end{closurestatus}
