\chapter{A Concrete Naming Certificate for $\FiniteTraceEvaluatorUp$}
\label{ch:concrete-instances-finitetraceevaluator-namecert}
\origin{ai}

The $\FiniteTraceEvaluatorUp$ packet realizes the runtime-candidate surface of \autoref{def:reflection-runtime-candidate} inside the reflection-limit boundary of \autoref{ch:visions-reflection-and-limits}. It sits beside the runtime-candidate boundary packet of \autoref{ch:concrete-instances-runtimecandidateboundary-namecert}, the diagonal finite-trace packet of \autoref{ch:concrete-instances-haltingdistinctiontrace-namecert}, and the finite-trace GAP socket of \autoref{ch:concrete-instances-finite-trace-gap-socket-namecert}. Those chapters expose, respectively, object-level runtime rows, a certificate-level diagonal trace, and the finite-window boundary; the present packet records a bounded evaluator trace whose accepted result is visible while host validation of the evaluator remains outside the packet.

\begin{definition}[Finite trace evaluator carrier]
\label{def:finite-trace-evaluator-carrier}
A $\FiniteTraceEvaluatorUp$ carrier is a finite $\BHist$ packet
$$
E=(I,T,A,V,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the input row of coded $\mathrm{CIC}^{*}$ expressions, proof objects, and states admitted to the bounded evaluator;
\item $T$ is the finite trace-step row, listing the displayed evaluator steps from the input row $I$ without adding an unbounded runtime;
\item $A$ is the accepted-result classifier row, grouping exactly the results reached by the displayed trace-step row $T$;
\item $V$ is the validation-boundary row, recording that host validation of the evaluator is not a packet coordinate;
\item $H$ records componentwise $\hsame$ transports for the input, trace-step, accepted-result, validation-boundary, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ routes by which a consumer reads $I$, replays $T$, reaches $A$, checks the boundary row $V$, and returns through provenance and local naming;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, the structural $\mathrm{CIC}^{*}$ coding interface, and \autoref{ch:concrete-instances-runtimecandidateboundary-namecert};
\item $N$ is the local $\NameCert_{\FiniteTraceEvaluatorUp}$ row.
\end{enumerate}
The classifier accepts exactly packets whose visible coordinates are $I,T,A,V,H,C,P,N$. The carrier has no coordinate for a host evaluator, a total truth predicate, an unbounded execution stream, or the judgment that the bounded evaluator validates itself.
\end{definition}

\begin{theorem}[FiniteTraceEvaluator NameCert obligations]
\label{thm:finite-trace-evaluator-namecert-obligations}
For the carrier of \autoref{def:finite-trace-evaluator-carrier}, the local $\NameCert_{\FiniteTraceEvaluatorUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission: every accepted object exposes the displayed packet $E=(I,T,A,V,H,C,P,N)$;
\item finite trace-step exposure: every evaluator step readable by a consumer is a row of the finite trace-step coordinate $T$ reached from the input coordinate $I$;
\item accepted-result classifier: every accepted result is classified by $A$ only after the corresponding trace-step row in $T$ has been displayed;
\item runtime-validation non-escape: the boundary row $V$ keeps host validation outside $I,T,A,H,C,P,N$ and prevents a packet row from serving as its own validator;
\item ledger exhaustion: the provenance and local naming rows $P,N$ exhaust the available dependencies and expose no unlisted evaluator, truth predicate, total halting predicate, or infinite trace.
\end{enumerate}
Consequently the certificate names a bounded object-level evaluator trace and its accepted-result ledger, but it does not internalize the host judgment that licenses the evaluator.
\end{theorem}
\begin{proof}
Carrier admission is tuple projection. The packet $E=(I,T,A,V,H,C,P,N)$ is finite, and every visible object-level coordinate is one of the displayed rows.

Trace-step exposure begins with $I$ and then reads $T$. Since $T$ is the only trace coordinate, a consumer can inspect only the finitely displayed evaluator steps and cannot replace them by an ambient runtime.

The accepted-result classifier is reached only after that trace read. A result belongs to $A$ because the packet displays the corresponding step in $T$; no accepted result is supplied by a hidden classifier or by host execution.

Runtime validation is separated by $V$. The argument of \autoref{thm:reflection-structure-existence-boundary} and the sibling packet \autoref{ch:concrete-instances-runtimecandidateboundary-namecert} place validation of a runtime candidate outside its source, pattern, classifier, stability, and ledger fields. Thus the finite trace evaluator records a boundary row rather than a self-validating checker.

Finally, $P$ and $N$ bind provenance and local naming without adding new evaluator content. Ledger exhaustion follows because every available consumer route has already passed through $I,T,A,V,H,C,P,N$, so an unlisted evaluator, truth predicate, total halting predicate, or infinite trace would require an extra coordinate absent from the carrier.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator bounded trace coverage]
\label{thm:finite-trace-evaluator-bounded-trace-coverage}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, every accepted evaluator result factors through
$$
I \longmapsto T \longmapsto A.
$$
No accepted result can bypass the bounded trace row $T$ or be supplied by a host evaluator, a total truth predicate, or an unbounded execution stream.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-trace-evaluator-carrier}. The only input-facing coordinate is $I$, the only trace-step coordinate is the finite row $T$, and the only accepted-result classifier is $A$.

Apply \autoref{thm:finite-trace-evaluator-namecert-obligations}. Its trace-step exposure and accepted-result classifier clauses force a consumer to read from $I$ into $T$ before any accepted result is visible at $A$.

The sibling runtime boundary of \autoref{ch:concrete-instances-runtimecandidateboundary-namecert}, the finite diagonal trace of \autoref{ch:concrete-instances-haltingdistinctiontrace-namecert}, and the finite-trace GAP socket of \autoref{ch:concrete-instances-finite-trace-gap-socket-namecert} supply only bounded object-level routes. They do not add a host evaluator, total truth predicate, or unbounded execution stream to the packet.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator host-validation refusal ledger]
\label{thm:finite-trace-evaluator-host-validation-refusal-ledger}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, the row $V$ is only a refusal and validation-boundary row. It does not supply host validation, total truth for $\mathrm{CIC}^{*}$ sentences, or a self-validating evaluator.
\end{theorem}
\begin{proof}
Read $V$ through \autoref{def:finite-trace-evaluator-carrier}. The definition names it as the validation-boundary coordinate and explicitly keeps host validation outside the displayed evaluator rows.

Use the runtime-validation non-escape clause of \autoref{thm:finite-trace-evaluator-namecert-obligations}. It prevents any packet row from becoming the validating host judgment for the same evaluator.

The cited sibling packets \autoref{ch:concrete-instances-runtimecandidateboundary-namecert}, \autoref{ch:concrete-instances-haltingdistinctiontrace-namecert}, and \autoref{ch:concrete-instances-finite-trace-gap-socket-namecert} expose runtime candidates, trace rows, and finite windows as object-level evidence. None of them turns $V$ into host validation, total truth, or self-validation.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator result-validation separation]
\label{thm:finite-trace-evaluator-result-validation-separation}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, result classification is visible only after bounded trace exposure through $I \longmapsto T \longmapsto A$, while validation remains outside the packet at the boundary row $V$. Thus the packet can display a bounded accepted result without claiming host validation of the evaluator that produced it.
\end{theorem}
\begin{proof}
First apply \autoref{thm:finite-trace-evaluator-bounded-trace-coverage}. It places every accepted result on the bounded route from $I$ through $T$ to $A$.

Next apply \autoref{thm:finite-trace-evaluator-host-validation-refusal-ledger}. It keeps host validation, total truth, and self-validation outside the same packet and records the refusal at $V$.

Together with \autoref{thm:finite-trace-evaluator-namecert-obligations}, these two readings exhaust the accepted packet. The runtime-candidate boundary, halting-distinction trace, and finite-trace GAP socket chapters supply finite object-level anchors, but the validation judgment is not a coordinate of $E$.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator object-level boundary]
\label{thm:finite-trace-evaluator-object-level-boundary}
Every consumer read of an accepted $\FiniteTraceEvaluatorUp$ packet factors through the finite route
$$
I \to T \to A \to V \to H \to C \to P \to N.
$$
The consumer may inspect the coded input, replay the displayed finite trace, and read the accepted-result classifier, but it cannot extract host validation, total halting information, truth for $\mathrm{CIC}^{*}$ sentences, or an unbounded evaluator from the packet.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:finite-trace-evaluator-carrier}. The input, trace-step, accepted-result, and validation-boundary information is exhausted by $I,T,A,V$.

Apply \autoref{thm:finite-trace-evaluator-namecert-obligations}. Its trace-step exposure and accepted-result classifier clauses force every evaluator read through $T$ and then through $A$, while its runtime-validation non-escape clause keeps the host validating judgment outside the packet.

The remaining rows $H,C,P,N$ transport, route, cite, and name the same finite packet. Hence every consumer read factors through the displayed route, and no unbounded evaluator or internal truth classifier is available from the finite trace evaluator.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator trace-result route]
\label{thm:finite-trace-evaluator-trace-result-route}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, every accepted result row classified by $A$ is reached
only through the bounded trace route
$$
I \to T \to A.
$$
The result row cannot be supplied by a host evaluator, a truth predicate for
$\mathrm{CIC}^{*}$ sentences, or an unbounded execution stream.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-trace-evaluator-carrier}. Its only
input-facing row is $I$, its only evaluator-step row is the finite trace row
$T$, and its only accepted-result classifier is $A$.

Apply \autoref{thm:finite-trace-evaluator-namecert-obligations}. The finite
trace-step exposure clause sends every evaluator step from $I$ into $T$, and
the accepted-result classifier clause permits $A$ to classify a result only
after the corresponding displayed trace-step row has been read.

The missing host evaluator, truth, and unbounded execution coordinates give the
non-escape conclusion. Since none of those objects is a row of
$E=(I,T,A,V,H,C,P,N)$, no accepted result can bypass the route
$I \to T \to A$.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator validation-row non-escape]
\label{thm:finite-trace-evaluator-validation-row-nonescape}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, the validation-boundary row $V$ refuses host validation,
total truth, self-validation of the evaluator, and unbounded execution as packet
coordinates. A consumer may read that refusal through $V,H,C,P,N$, but cannot
turn $V$ into any of the refused objects.
\end{theorem}
\begin{proof}
Start from \autoref{def:finite-trace-evaluator-carrier}. The row $V$ is named
only as the validation-boundary row, while host validation, total truth,
self-validation, and unbounded execution are explicitly absent from the carrier.

Use the runtime-validation non-escape clause of
\autoref{thm:finite-trace-evaluator-namecert-obligations}. It keeps host
validation outside $I,T,A,H,C,P,N$ and prevents a packet row from serving as its
own validator.

The transport, continuation, provenance, and naming rows preserve the same
finite packet. Thus $V$ records a boundary refusal, and the missing
host/evaluator/truth coordinates cannot be reconstructed by reading
$V,H,C,P,N$.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator provenance exhaustion]
\label{thm:finite-trace-evaluator-provenance-exhaustion}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, the rows $H,C,P,N$ exhaust componentwise transport,
consumer continuation, provenance, and local naming for the same finite packet.
They do not add host validation, a host evaluator, total truth, total halting,
or an unbounded trace.
\end{theorem}
\begin{proof}
Project the displayed packet in \autoref{def:finite-trace-evaluator-carrier}.
After $I,T,A,V$ are fixed, the only remaining rows are the componentwise
$\hsame$ transports $H$, the displayed $\Cont$ routes $C$, provenance $P$, and
the local $\NameCert_{\FiniteTraceEvaluatorUp}$ row $N$.

Apply the ledger-exhaustion clause of
\autoref{thm:finite-trace-evaluator-namecert-obligations}. It states that
$P,N$ exhaust the available dependencies and expose no unlisted evaluator,
truth predicate, total halting predicate, or infinite trace.

The rows $H$ and $C$ only transport and replay the same finite coordinates
already displayed by the carrier. Therefore $H,C,P,N$ close the local transport,
continuation, provenance, and naming surface without importing any missing
host/evaluator/truth coordinate.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator result classifier exactness]
\label{thm:finite-trace-evaluator-result-classifier-exactness}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, a result is classified by the accepted-result row $A$
if and only if the consumer has first read the displayed finite trace-step row
$T$ from the input row $I$. The classifier has no independent host execution
channel, no truth predicate for $\mathrm{CIC}^{*}$ sentences, and no
unbounded trace coordinate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-trace-evaluator-carrier}. The row
$A$ is displayed only as the accepted-result classifier of the same finite
packet whose trace-step coordinate is $T$.

Apply the finite trace-step exposure and accepted-result classifier clauses of
\autoref{thm:finite-trace-evaluator-namecert-obligations}. They force every
accepted result to be read after the corresponding displayed trace-step row,
and they provide no second classifier outside $I,T,A,V,H,C,P,N$.

Conversely, once the consumer reads $I$ and the corresponding finite step in
$T$, the displayed classifier row $A$ is the only accepted-result row available
in the packet. Thus result classification is exact at $A$ and cannot be
replaced by host execution, a truth predicate, or an unbounded trace.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator ledger non-escape]
\label{thm:finite-trace-evaluator-ledger-nonescape}
The finite ledger $I,T,A,V,H,C,P,N$ of an accepted
$\FiniteTraceEvaluatorUp$ packet exports no host validator, truth predicate,
total halting predicate, or infinite trace. Every readable evaluator result is
exhausted by the input row, the displayed finite trace-step row, the
accepted-result classifier, the validation-boundary row, the componentwise
transport and continuation rows, provenance, and the local name.
\end{theorem}
\begin{proof}
Start with the object-level boundary of
\autoref{thm:finite-trace-evaluator-object-level-boundary}. It sends every
consumer read through
$$
I \to T \to A \to V \to H \to C \to P \to N.
$$

Use the runtime-validation non-escape and ledger exhaustion clauses of
\autoref{thm:finite-trace-evaluator-namecert-obligations}. The row $V$ records
that host validation is outside the packet, while $P$ and $N$ close the
visible provenance and naming ledger without adding evaluator content.

Therefore an exported host validator, truth predicate, total halting
predicate, or infinite trace would require an additional coordinate not
present in the carrier. The displayed finite rows exhaust the packet's
consumer-facing ledger.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator obligation upgrade package]
\label{thm:finite-trace-evaluator-obligation-upgrade-package}
The $\FiniteTraceEvaluatorUp$ obligation surface needed for
obligationClosure is the package consisting of carrier admission, result
classifier exactness, runtime-validation non-escape, ledger exhaustion, and
consumer-route factorization for the same finite packet $E=(I,T,A,V,H,C,P,N)$.
This package is object-level only: it does not assert host validation of the
evaluator, total halting, truth for $\mathrm{CIC}^{*}$ sentences, or an
infinite execution trace.
\end{theorem}
\begin{proof}
Carrier admission is supplied by
\autoref{def:finite-trace-evaluator-carrier} and the first clause of
\autoref{thm:finite-trace-evaluator-namecert-obligations}. They fix the
available rows as $I,T,A,V,H,C,P,N$.

Result classifier exactness is exactly
\autoref{thm:finite-trace-evaluator-result-classifier-exactness}. It ties
accepted results to the displayed finite trace-step row before $A$ is read.

Runtime-validation non-escape and ledger exhaustion are supplied by the
corresponding clauses of \autoref{thm:finite-trace-evaluator-namecert-obligations}
and by \autoref{thm:finite-trace-evaluator-ledger-nonescape}. These keep host
validation, truth, total halting, and infinite traces outside the packet.

Finally apply \autoref{thm:finite-trace-evaluator-object-level-boundary}. The
consumer route factors through the displayed finite route, so the listed rows
form the whole obligation surface for the bounded evaluator packet.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator evaluation determinacy]
\label{thm:finite-trace-evaluator-evaluation-determinacy}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, an accepted result row is exposed only through the
displayed bounded trace rows $T,R,V,H,C,P,N$, where $R$ is the result row read
at $A$. The packet has no second result channel, host evaluator coordinate,
truth predicate, or unbounded execution stream from which a consumer could read
an accepted result.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-trace-evaluator-carrier}. The only
input-to-result route available to a consumer begins at $I$, proceeds through
the finite trace row $T$, and reaches the accepted-result classifier row $A$.
Reading $A$ exposes the result row $R$ as part of that same displayed route.

Apply \autoref{thm:finite-trace-evaluator-namecert-obligations}. Its finite
trace-step exposure and accepted-result classifier clauses say that accepted
results are classified only after the corresponding bounded trace rows have
been displayed.

Finally use \autoref{thm:finite-trace-evaluator-object-level-boundary}. The
remaining rows $V,H,C,P,N$ keep validation, transport, continuation,
provenance, and local naming on the same finite path, so no hidden evaluator or
ambient truth predicate can determine an additional result.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator boundary exhaustion]
\label{thm:finite-trace-evaluator-boundary-exhaustion}
Every runtime-validation read of an accepted $\FiniteTraceEvaluatorUp$ packet
remains a boundary read through $V,H,C,P,N$. No row exported by the packet is a
self-validating runtime coordinate, and no accepted result row can be promoted
to a host validator for the same evaluator.
\end{theorem}
\begin{proof}
Start with the validation-boundary coordinate in
\autoref{def:finite-trace-evaluator-carrier}. The carrier lists $V$ as the
place where host validation is recorded as outside the packet, not as a
runtime-coordinate constructor.

Apply the runtime-validation non-escape clause of
\autoref{thm:finite-trace-evaluator-namecert-obligations}. It keeps host
validation outside $I,T,A,H,C,P,N$ and prevents any packet row from serving as
its own validator.

Replay \autoref{thm:finite-trace-evaluator-object-level-boundary}. Every
consumer route passes from $A$ to $V$ and then through $H,C,P,N$, so runtime
evidence remains boundary evidence throughout the displayed finite ledger.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator runtime nonimport]
\label{thm:finite-trace-evaluator-runtime-nonimport}
The object-level runtime evidence read by an accepted
$\FiniteTraceEvaluatorUp$ packet is routed through
\autoref{ch:concrete-instances-runtimecandidateboundary-namecert},
\autoref{ch:concrete-instances-haltingdistinctiontrace-namecert}, and
\autoref{ch:concrete-instances-finite-trace-gap-socket-namecert}. The packet
does not import those rows as a host validator for its own evaluator; it only
records their finite boundary, diagonal trace, and finite-window socket as
displayed object-level dependencies.
\end{theorem}
\begin{proof}
Project the provenance and local naming rows $P,N$ of the carrier. Their
listed dependencies include the runtime-candidate boundary, the diagonal
finite-trace packet, and the finite-trace GAP socket as object-level sources
for the finite evaluator trace.

Apply \autoref{thm:finite-trace-evaluator-namecert-obligations}. Carrier
admission and ledger exhaustion restrict the dependency read to the displayed
rows $I,T,A,V,H,C,P,N$, while runtime-validation non-escape keeps a host
validator outside the packet.

Finally replay \autoref{thm:finite-trace-evaluator-object-level-boundary}. The
consumer may inspect the bounded trace and accepted-result classifier through
those dependency routes, but the route never exports total halting, host
validation, truth for $\mathrm{CIC}^{*}$ sentences, or an unbounded evaluator.
\end{proof}

\closureat{FiniteTraceEvaluatorUp}{seedStr}

\begin{closurestatus}{\FiniteTraceEvaluatorUp}
  \constructivestory{A $\FiniteTraceEvaluatorUp$ packet is generated from coded input rows, finite trace-step rows, accepted-result classifier rows, a validation-boundary row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-trace-evaluator-carrier}, \autoref{thm:finite-trace-evaluator-namecert-obligations}, and \autoref{thm:finite-trace-evaluator-object-level-boundary} bind the finite evaluator trace carrier, accepted-result classifier, validation boundary, and ledger exhaustion surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close host validation, total halting, truth for $\mathrm{CIC}^{*}$ sentences, unbounded evaluation, infinite traces, or a checked Lean certificate.}
  \upgradepath{Obligation closure requires checked carrier admission, finite trace-step exposure, accepted-result classifier exactness, runtime-validation non-escape, ledger exhaustion, and consumer-route factorization for the same packet.}
\end{closurestatus}
