\chapter{A Concrete Naming Certificate for $\GroundCompilerEventFlowAuditUp$}
\label{ch:concrete-instances-groundcompilereventflowaudit-namecert}
\origin{human}

The $\GroundCompilerEventFlowAuditUp$ packet realizes the compiler-layer audit map of \autoref{ch:bedc-groundcompiler-audit-map} as a finite NameCert carrier over event flows, channel encodings, decoder readback, generated recognizers, audit verdicts, provenance, and a local name. It sits beside the reusable audit-map packet surfaces of \autoref{ch:concrete-instances-auditmaptemplatepacket-namecert} and \autoref{ch:concrete-instances-auditmapfrontierpacket-namecert}: those sibling chapters describe family-level row templates and frontier packets, while this chapter binds the GroundCompiler event-flow channel as one concrete certificate object.

\begin{definition}[GroundCompiler event-flow audit carrier]
\label{def:ground-compiler-event-flow-audit-carrier}
A $\GroundCompilerEventFlowAuditUp$ carrier is a finite $\BHist$ packet
$$
G=(E,C,D,R,A,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the EventFlow source row naming the finite compiler-facing event stream being audited;
\item $C$ is the FlowEncoding channel row recording the legal channel encoding of $E$;
\item $D$ is the Decode round-trip row recording that decoding the channel returns the displayed event flow;
\item $R$ is the recognizer certificate row recording the generated recognizer routes that may inspect the decoded flow;
\item $A$ is the audit verdict row recording the accepted, conditional, obstruction, and boundary outcomes exposed by the GroundCompiler audit map;
\item $P$ is the package provenance row over \autoref{ch:bedc-groundcompiler-audit-map}, the sibling audit-map packet chapters, EventFlow, FlowEncoding, Decode, recognizer flows, $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\GroundCompilerEventFlowAuditUp}$ row.
\end{enumerate}
The classifier accepts exactly packets carrying these seven rows. It exports no hidden source channel, no unencoded event flow, no decoder result other than the displayed round-trip row, no recognizer route outside $R$, no audit verdict outside $A$, and no external provenance coordinate.
\end{definition}

\begin{theorem}[GroundCompiler event-flow obligation surface]
\label{thm:ground-compiler-event-flow-audit-obligation-surface}
For the carrier of \autoref{def:ground-compiler-event-flow-audit-carrier}, the local $\NameCert_{\GroundCompilerEventFlowAuditUp}$ surface consists exactly of carrier admission for
$$
G=(E,C,D,R,A,P,N),
$$
source readback through $E$, channel readback through $C$, decoder readback through $D$, recognizer certificate readback through $R$, audit verdict readback through $A$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite packet. The rows $E,C,D$ expose the EventFlow source, the FlowEncoding channel, and the Decode round-trip record before any recognizer or verdict row is available.

Read $R$ and $A$ next. The recognizer row records which generated routes may inspect the decoded flow, and the verdict row records the audit outcome classes as displayed rows.

Finally inspect $P$ and $N$. Provenance locates the packet in the GroundCompiler audit map and its sibling audit-map packet surfaces, while the local name binds the same seven-row object. Since every obligation is one of these displayed rows, the NameCert surface is exactly the carrier inventory.
\end{proof}

\begin{theorem}[GroundCompiler event-flow channel losslessness]
\label{thm:ground-compiler-event-flow-audit-channel-losslessness}
For every accepted $\GroundCompilerEventFlowAuditUp$ carrier $G=(E,C,D,R,A,P,N)$, a consumer may read the encoded channel only through the FlowEncoding row $C$ and may read the event flow recovered from that channel only through the Decode round-trip row $D$. The channel therefore exposes the same EventFlow row $E$ to recognizer and audit consumers and provides no second source stream, erased channel coordinate, host parser, or alternate decoder route.
\end{theorem}
\begin{proof}
Start from the carrier projection. The only source-facing rows are the displayed EventFlow row $E$, FlowEncoding row $C$, and Decode round-trip row $D$.

Use the obligation surface of \autoref{thm:ground-compiler-event-flow-audit-obligation-surface}. It separates channel readback from decoder readback, so the route from encoded channel to recognizer input must pass through $C$ and then $D$.

The remaining rows $R,A,P,N$ consume the decoded flow, source the packet, and name it. None of them contains a second source stream, parser, erased channel, or alternate decoder coordinate, so channel losslessness is exactly the displayed round-trip route from $E$ through $C$ and $D$.
\end{proof}

\begin{theorem}[GroundCompiler event-flow recognizer boundary]
\label{thm:ground-compiler-event-flow-audit-recognizer-boundary}
For every accepted $\GroundCompilerEventFlowAuditUp$ carrier $G=(E,C,D,R,A,P,N)$, every generated recognizer read of the event-flow channel factors through the rows $E,C,D,R$. A recognizer may inspect the decoded event flow certified by $D$ and may contribute to the audit verdict row $A$, but it cannot replace the source row, bypass the FlowEncoding channel, assert a decoder fact outside $D$, or turn motif, metric, theorem-code, or chapter-code reports into proof evidence.
\end{theorem}
\begin{proof}
Project $E,C,D,R$ from the accepted carrier. The recognizer certificate row is downstream of the event-flow source, the channel encoding, and the decoder round-trip row.

Apply \autoref{thm:ground-compiler-event-flow-audit-channel-losslessness}. Since the recognizer input is the decoded event flow certified by $D$, no recognizer route can supply a second source row or bypass the channel.

Now read the audit verdict row $A$. It may record the recognizer contribution as an audit outcome, but the carrier has no coordinate that promotes motif, metric, theorem-code, or chapter-code reports to proof evidence. Thus the recognizer boundary is the displayed route through $E,C,D,R,A$.
\end{proof}

\begin{theorem}[GroundCompiler event-flow audit non-escape]
\label{thm:ground-compiler-event-flow-audit-nonescape}
Every downstream consumer of an accepted $\GroundCompilerEventFlowAuditUp$ packet remains inside the finite route
$$
E,C,D,R,A,P,N.
$$
In particular, the packet exports no hidden input stream, no unencoded EventFlow source, no decoder route outside the round-trip row, no generated recognizer outside $R$, no audit verdict outside $A$, no external package source, and no host equality over compiler events.
\end{theorem}
\begin{proof}
Begin with the obligation surface. It lists exactly the source, channel, decode, recognizer, verdict, provenance, and local naming rows available to a consumer.

Use the channel losslessness theorem to confine source and channel reads to $E,C,D$. Then use the recognizer boundary theorem to confine recognizer-mediated inspection to $R$ and verdict production to $A$.

It remains to inspect provenance and naming. The rows $P$ and $N$ locate and name the same finite packet, but they do not add hidden input, an alternate decoder, an unlisted recognizer, an extra verdict, an external source, or host equality. Hence every consumer remains inside the displayed route.
\end{proof}

\closureat{GroundCompilerEventFlowAuditUp}{seedStr}

\begin{closurestatus}{\GroundCompilerEventFlowAuditUp}
  \constructivestory{A $\GroundCompilerEventFlowAuditUp$ packet is generated from an EventFlow source row, FlowEncoding channel row, Decode round-trip row, recognizer certificate row, audit verdict row, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:ground-compiler-event-flow-audit-carrier}, \autoref{thm:ground-compiler-event-flow-audit-obligation-surface}, \autoref{thm:ground-compiler-event-flow-audit-channel-losslessness}, \autoref{thm:ground-compiler-event-flow-audit-recognizer-boundary}, and \autoref{thm:ground-compiler-event-flow-audit-nonescape} bind the GroundCompiler event-flow audit channel as a finite source, encoding, decode, recognizer, verdict, provenance, and NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean verification, self-hosting of every compiler candidate, proof status for motif or metric reports, theorem-code evidence, chapter-code evidence, host event equality, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, event-flow readback, channel round-trip readback, recognizer routing, audit verdict routing, provenance, naming, and non-escape for the same finite packet.}
\end{closurestatus}
