\chapter{A Concrete Naming Certificate for $\GroundCompilerRecognitionUp$}
\label{ch:concrete-instances-groundcompilerrecognition-namecert}
\origin{ai}

The $\GroundCompilerRecognitionUp$ packet realizes the generated-recognition surface of \autoref{ch:bedc-groundcompiler-audit-map} as a finite NameCert carrier. It sits beside the finite evaluator packet of \autoref{ch:concrete-instances-finitetraceevaluator-namecert}: the evaluator records bounded trace rows and accepted-result readback, while this packet records generated recognizer rows, accepted-export rows, finite evaluator handoff rows, report non-evidence rows, and cannot-claim ledger rows before a downstream compiler consumer treats recognition as evidence.

\begin{definition}[GroundCompiler recognition carrier]
\label{def:groundcompiler-recognition-carrier}
A $\GroundCompilerRecognitionUp$ carrier is a finite $\BHist$ packet
$$
R=(I,G,A,T,V,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the GroundCompiler event-flow and source-channel input row under recognition;
\item $G$ is the generated recognizer row for packages, name certificates, derivation certificates, theorem identifiers, chapter records, or manifest records;
\item $A$ is the accepted-export row through which a recognized artifact may be consumed by a theorem-facing or NameCert-facing route;
\item $T$ is the finite trace evaluator handoff row, read through the bounded trace and accepted-result rows of \autoref{ch:concrete-instances-finitetraceevaluator-namecert};
\item $V$ is the report non-evidence row separating metric reports, motif reports, theorem code, chapter code, and readable source from proof or certificate evidence;
\item $L$ is the cannot-claim ledger row for hidden compiler input, raw event-flow equality, report-as-proof, code-as-proof, and unrecorded self-hosting claims;
\item $H$ records componentwise $\hsame$ transports for the input, recognizer, export, evaluator handoff, non-evidence, cannot-claim, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ routes for recognizer readback, accepted-export readback, finite evaluator handoff, non-evidence inspection, and ledger replay;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, \autoref{ch:bedc-groundcompiler-audit-map}, and \autoref{ch:concrete-instances-finitetraceevaluator-namecert};
\item $N$ is the local $\NameCert_{\GroundCompilerRecognitionUp}$ row.
\end{enumerate}
The classifier accepts exactly packets whose visible rows are $I,G,A,T,V,L,H,C,P,N$. It contains no host recognizer, no accepted export outside $A$, no evaluator validation outside $T$, no proof from reports or code, and no unlisted compiler input.
\end{definition}
\leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[GroundCompiler recognition NameCert obligations]
\label{thm:groundcompiler-recognition-namecert-obligations}
For the carrier of \autoref{def:groundcompiler-recognition-carrier}, the local $\NameCert_{\GroundCompilerRecognitionUp}$ surface consists of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $R=(I,G,A,T,V,L,H,C,P,N)$;
\item generated-recognizer exposure through $G$ after the event-flow and source-channel input row $I$ has been displayed;
\item accepted-export routing through $A$, with no consumer route bypassing the accepted-export row;
\item finite trace evaluator handoff through $T$, tied to the bounded trace and accepted-result rows of \autoref{ch:concrete-instances-finitetraceevaluator-namecert};
\item report and cannot-claim exhaustion through $V,L,H,C,P,N$, so reports, code, raw classifier quotients, and unrecorded self-hosting claims remain outside proof and certificate evidence.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionNameCert\_obligations}
\begin{proof}
Carrier admission is tuple projection. The finite packet displays exactly $I,G,A,T,V,L,H,C,P,N$.

Read recognition through $I$ and $G$. The source-like event row is visible before the generated recognizer row is consumed, so recognizer evidence cannot replace the input coordinate.

Accepted export is then confined to $A$. Since the carrier has no second export coordinate, every theorem-facing or NameCert-facing route must pass through the displayed accepted-export row.

The finite evaluator handoff is confined to $T$. By citing the sibling finite evaluator packet, the handoff exposes bounded trace and accepted-result rows without adding host evaluator validation or an unbounded execution stream.

Finally inspect $V,L,H,C,P,N$. The report non-evidence and cannot-claim rows state the excluded readings, while the transport, route, provenance, and naming rows replay only the displayed packet. Thus the five obligations exhaust the local certificate surface.
\end{proof}

\begin{theorem}[GroundCompiler recognition ledger non-escape]
\label{thm:groundcompiler-recognition-ledger-nonescape}
Every accepted $\GroundCompilerRecognitionUp$ packet exports recognition evidence only through the finite rows
$$
I,G,A,T,V,L,H,C,P,N.
$$
It exports no hidden compiler input, no host recognizer, no accepted export outside the certificate gate row, no proof from theorem code or chapter code, no proof from metric or motif reports, no raw event-flow equality from classifier membership, and no self-hosting tower outside the displayed ledger.
\end{theorem}
\leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionCarrier\_ledger\_nonescape}
\begin{proof}
Project the accepted carrier of \autoref{def:groundcompiler-recognition-carrier}. The listed rows are the whole exported $\BHist$ surface.

Apply \autoref{thm:groundcompiler-recognition-namecert-obligations}. Generated recognition is read through $G$, accepted exports through $A$, and evaluator handoff through $T$.

The non-evidence and cannot-claim rows then block hidden strengthening. Since $V$ separates reports and code from proof or certificate evidence, and $L$ lists the forbidden compiler readings, no public consumer can extract an unlisted recognizer, export, proof, raw equality, or compiler tower from the packet.
\end{proof}

\begin{theorem}[GroundCompiler recognition finite-trace handoff]
\label{thm:groundcompiler-recognition-finitetrace-handoff}
For every accepted $\GroundCompilerRecognitionUp$ carrier $R=(I,G,A,T,V,L,H,C,P,N)$, the evaluator-facing read factors through the finite trace evaluator rows cited by $T$. A downstream consumer may inspect the bounded trace and accepted-result handoff, then return to the generated recognizer and accepted-export rows $G,A$; it cannot turn the handoff into host evaluator validation, a total truth predicate, an infinite trace, or a proof object.
\end{theorem}
\leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionCarrier\_finite\_trace\_handoff\_boundary}
\begin{proof}
Start with the handoff coordinate $T$. It is the only evaluator-facing row in the recognition carrier.

Use the finite trace evaluator packet of \autoref{ch:concrete-instances-finitetraceevaluator-namecert}. That sibling exposes coded input, finite trace-step rows, accepted-result classification, and a validation boundary, while excluding host validation, total halting, truth, and unbounded execution.

Return through $H,C,P,N$ to the recognition rows. The route records only the displayed bounded handoff and then resumes at $G$ and $A$, so it supplies recognition and accepted export evidence without adding an evaluator, proof object, infinite trace, or truth predicate.
\end{proof}

\begin{theorem}[GroundCompiler recognition flow carrier exposure]
\label{thm:groundcompiler-recognition-flow-carrier-exposure}
For every accepted $\GroundCompilerRecognitionUp$ carrier $R=(I,G,A,T,V,L,H,C,P,N)$, the event-flow input, generated recognizer, accepted-export gate, finite-trace handoff, report non-evidence row, cannot-claim ledger, componentwise $\hsame$ rows, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row are all visible before recognition is consumed. No accepted consumer may read generated recognition while omitting $I$, $G$, or $A$.
\end{theorem}
\leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionCarrier\_flow\_carrier\_exposure}
\begin{proof}
Project the carrier of \autoref{def:groundcompiler-recognition-carrier}. The visible packet is exactly $I,G,A,T,V,L,H,C,P,N$.

Use \autoref{thm:groundcompiler-recognition-finitetrace-handoff} for the evaluator-facing coordinate. It places the bounded trace and accepted-result handoff inside $T$ and returns the read to $G$ and $A$ without adding host validation.

The remaining rows $V,L,H,C,P,N$ expose the report boundary, cannot-claim ledger, transports, replay routes, provenance, and local name. Thus recognition consumption cannot skip the event-flow, recognizer, or accepted-export coordinates.
\end{proof}

\begin{theorem}[GroundCompiler recognition certificate gate stability]
\label{thm:groundcompiler-recognition-certificate-gate-stability}
Every theorem-facing or NameCert-facing read of an accepted $\GroundCompilerRecognitionUp$ carrier factors through the accepted-export row $A$. The generated recognizer row $G$, finite-trace handoff row $T$, report non-evidence row $V$, and cannot-claim ledger row $L$ may constrain that read, but none of them creates a second certificate gate.
\end{theorem}
\leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionCarrier\_certificate\_gate\_stability}
\begin{proof}
Start from the accepted-export coordinate $A$. It is the only row in the carrier whose role is theorem-facing or NameCert-facing export.

Apply the finite-trace handoff theorem. The handoff through $T$ supplies bounded evaluator data and then returns to the recognizer and export rows; it does not create another accepted-export channel.

Finally inspect $V$ and $L$. Reports, code, raw event-flow equality, and unrecorded self-hosting claims are listed as non-evidence or cannot-claim data. They therefore restrict the certificate gate rather than replacing $A$.
\end{proof}

\begin{theorem}[GroundCompiler recognition NameCert non-escape]
\label{thm:groundcompiler-recognition-namecert-nonescape}
The local $\NameCert_{\GroundCompilerRecognitionUp}$ obligations for $I,G,A,T,V,L,H,C,P,N$ prevent accepted-export routing from bypassing $A$ and prevent reports, chapter code, theorem code, metric reports, or motif reports from becoming proof evidence. Every accepted read remains inside the displayed recognition carrier and its finite-trace handoff.
\end{theorem}
\begin{proof}
Use the NameCert obligation theorem. It lists carrier admission, generated-recognizer exposure, accepted-export routing, finite-trace handoff, and report-plus-ledger exhaustion over the same finite carrier.

The certificate gate stability theorem confines theorem-facing and NameCert-facing export to $A$. The finite-trace handoff theorem confines evaluator-facing data to $T$ and returns it to $G,A$.

It remains to inspect the report and code rows. The row $V$ separates reports and code from proof or certificate evidence, while $L$ records the cannot-claim readings. Hence no accepted route can turn reports or code into proof evidence, and no route can bypass $A$.
\end{proof}

\begin{theorem}[GroundCompiler recognition accepted-export totality]
\label{thm:groundcompiler-recognition-accepted-export-totality}
For every accepted $\GroundCompilerRecognitionUp$ carrier $R=(I,G,A,T,V,L,H,C,P,N)$, every theorem-facing export and every NameCert-facing export passes through the accepted-export row $A$. The carrier of \autoref{def:groundcompiler-recognition-carrier} and the obligations of \autoref{thm:groundcompiler-recognition-namecert-obligations} leave no second export row outside $A$.
\end{theorem}
\begin{proof}
Project the carrier. The theorem-facing and NameCert-facing export coordinate in the displayed packet is $A$.

Apply \autoref{thm:groundcompiler-recognition-namecert-obligations}. Its accepted-export obligation states that no consumer route bypasses the accepted-export row.

Use certificate gate stability, \autoref{thm:groundcompiler-recognition-certificate-gate-stability}. The generated recognizer row $G$, finite-trace handoff row $T$, report boundary row $V$, and ledger row $L$ constrain the read, but none supplies a second certificate gate. Hence every such export factors through $A$.
\end{proof}

\begin{theorem}[GroundCompiler recognition report boundary exhaustion]
\label{thm:groundcompiler-recognition-report-boundary-exhaustion}
For every accepted $\GroundCompilerRecognitionUp$ carrier $R=(I,G,A,T,V,L,H,C,P,N)$, every report read, chapter-code read, theorem-code read, metric-report read, or motif-report read passes through the report non-evidence row $V$ before evidence use is refused. The carrier and NameCert obligations therefore exhaust the report boundary before any downstream consumer can treat those reads as proof or certificate evidence.
\end{theorem}
\begin{proof}
Start from \autoref{def:groundcompiler-recognition-carrier}. The row $V$ is the displayed report non-evidence row separating metric reports, motif reports, theorem code, chapter code, and readable source from proof or certificate evidence.

Apply \autoref{thm:groundcompiler-recognition-namecert-obligations}. Its report and cannot-claim exhaustion obligation routes the listed report and code reads through $V,L,H,C,P,N$ before a consumer may inspect the packet as evidence.

Now use \autoref{thm:groundcompiler-recognition-namecert-nonescape}. It prevents reports and code from becoming proof evidence and keeps every accepted read inside the displayed carrier and finite-trace handoff. Thus $V$ is the report boundary, and evidence use is refused after that boundary is displayed.
\end{proof}
\leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionReportBoundary\_exhaustion}

\begin{theorem}[GroundCompiler recognition cannot-claim ledger coverage]
\label{thm:groundcompiler-recognition-cannot-claim-ledger-coverage}
For every accepted $\GroundCompilerRecognitionUp$ carrier $R=(I,G,A,T,V,L,H,C,P,N)$, every forbidden compiler reading is covered by the cannot-claim ledger row $L$, componentwise $\hsame$ transports $H$, displayed replay routes $C$, package provenance $P$, and the local $\NameCert$ row $N$. In particular hidden compiler input, raw event-flow equality, report-as-proof, code-as-proof, and unrecorded self-hosting claims cannot escape the ledger surface.
\end{theorem}
\begin{proof}
Project the packet of \autoref{def:groundcompiler-recognition-carrier}. The forbidden compiler readings are listed in the cannot-claim row $L$, and the structural rows $H,C,P,N$ are the only transport, route, provenance, and naming rows available to replay them.

Apply \autoref{thm:groundcompiler-recognition-namecert-obligations}. Its final obligation covers report and cannot-claim exhaustion through $V,L,H,C,P,N$ over the same finite carrier.

Use ledger non-escape, \autoref{thm:groundcompiler-recognition-ledger-nonescape}. It already excludes hidden compiler input, host recognizers, proof from code or reports, raw event-flow equality, and self-hosting outside the displayed ledger. Therefore each forbidden reading is covered by $L,H,C,P,N$ and no compiler reading escapes the packet.
\end{proof}

\closureat{GroundCompilerRecognitionUp}{seedStr}
\closureat{GroundCompilerRecognitionUp}{obligationStr}[BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionNameCert\_obligations]
\closureat{GroundCompilerRecognitionUp}{scopedStr}[BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionNameCert\_obligations]

\begin{closurestatus}{\GroundCompilerRecognitionUp}
  \constructivestory{A $\GroundCompilerRecognitionUp$ packet is generated from event-flow and source-channel input rows, generated recognizer rows, accepted-export rows, finite trace evaluator handoff rows, report non-evidence rows, cannot-claim ledger rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:groundcompiler-recognition-carrier}, \autoref{thm:groundcompiler-recognition-namecert-obligations}, \autoref{thm:groundcompiler-recognition-ledger-nonescape}, \autoref{thm:groundcompiler-recognition-finitetrace-handoff}, \autoref{thm:groundcompiler-recognition-flow-carrier-exposure}, \autoref{thm:groundcompiler-recognition-certificate-gate-stability}, \autoref{thm:groundcompiler-recognition-report-boundary-exhaustion}, and \autoref{thm:groundcompiler-recognition-cannot-claim-ledger-coverage} bind the carrier, NameCert obligations, ledger non-escape, finite-trace handoff, flow carrier exposure, certificate-gate stability, report-boundary exhaustion, and cannot-claim ledger coverage to the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ primitives.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.GroundCompilerRecognitionUp.GroundCompilerRecognitionNameCert\_obligations}
  \bridgestatus{none}
  \origin{ai}
  \leanchecked{BEDC.Derived.GroundCompilerRecognitionUp.taste\_gate}
  \notclaimed{This chapter does not prove self-hosting for every compiler candidate, validate the evaluator from inside the packet, turn reports or code into proof, identify recognizer classes with raw event-flow equality, or provide bridge checking.}
  \upgradepath{Public closure next requires a public export theorem for the same recognition carrier and accepted-export gate.}
\end{closurestatus}
