\chapter{A Concrete Naming Certificate for $\RealBallUp$}
\label{ch:concrete-instances-realball-namecert}

The $\RealBallUp$ interface names the finite dyadic-radius neighborhood surface around a $\RealUp$ center. In Bishop-style constructive analysis, a real neighborhood is read through finite rational approximations and explicit positive radii; the BEDC packet below keeps that reading at the visible $\mathsf{BHist}$ level, with no host real topology or open-cover compactness datum.

\section{Finite dyadic-window carrier}
\label{sec:realball-finite-dyadic-window-carrier}

\begin{definition}[RealBall finite-window carrier]
\label{def:realball-window-carrier}
A $\RealBallUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
B=(c,r,W,P,L)
$$
with the following visible rows:
\begin{enumerate}
\item $c$ is a $\RealUp$ center name read through a scheduled $\RegSeqRat$ stream and its $\StreamNameUp$ finite-window requests;
\item $r$ is a positive dyadic-radius row from $\DyadicRatCoreUp$;
\item $W$ is a finite dyadic-window witness listing the displayed center approximants, the displayed radius row, and the $\DyadicIntervalUp$ interval rows that cover the visible portion of the ball;
\item $P$ is the $\Pkg$ provenance tying the carrier to $\RealUp$, $\RegSeqRat$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\DyadicIntervalUp$ source certificates;
\item $L$ is the ledger that hides only the unobserved tail beyond the displayed window and records that every public read is made through $W$ and $P$.
\end{enumerate}
The carrier predicate is $\mathsf{RealBallWindow}(c,r,W,P,L)$. Two accepted carriers classify together only when their center names, positive dyadic radii, visible interval rows, provenance rows, and tail ledgers transport by displayed $\hsame$ and by the same $\Cont$ routes named in $P$.
\end{definition}
\leandef{BEDC.Derived.RealBallUp.RealBallWindowPacket}

\begin{theorem}[RealBall radius transport]
\label{thm:realball-radius-transport}
Let $B=(c,r,W,P,L)$ be an accepted $\RealBallUp$ carrier, and let $B'=(c',r',W',P',L')$ be obtained by displayed $\hsame$ transport of the $\RealUp$ center row, the positive $\DyadicRatCoreUp$ radius row, the visible $\DyadicIntervalUp$ window rows, and the provenance and ledger rows. If the same $\Cont$ routes named by $P$ and $P'$ preserve the $\RegSeqRat$ and $\StreamNameUp$ reads of the center, then $B'$ is again an accepted $\RealBallUp$ carrier.

The transported classifier reads the same finite dyadic-radius neighborhood surface: it changes only the displayed representatives of $c$, $r$, $W$, $P$, and $L$, and it introduces no Dedekind cut, trichotomy row, completeness datum, host real ball, or open-cover topology.
\end{theorem}
\leanchecked{BEDC.Derived.RealBallUp.RealBallWindowPacket\_radius\_transport}
\begin{proof}
Project the five coordinates of \autoref{def:realball-window-carrier}. The center coordinate is read through $\RealUp$, $\RegSeqRat$, and $\StreamNameUp$, so the stated $\hsame$ and $\Cont$ routes transport each displayed center approximant in the finite window.

Transport the positive dyadic-radius row through $\DyadicRatCoreUp$ and transport the displayed interval rows through $\DyadicIntervalUp$. The visible window witness $W'$ is obtained by repacking exactly these transported rows.

Finally transport the provenance row and the tail ledger. The ledger still hides only the unobserved tail beyond the displayed window, so the accepted packet has the same classifier surface and no additional topological or completeness coordinate.
\end{proof}

\begin{theorem}[RealBall finite-window NameCert surface]
\label{thm:realball-finite-window-namecert}
The local $\NameCert_{\RealBallUp}$ obligation surface consists of five finite rows:
\begin{enumerate}
\item carrier: the $\mathsf{BHist}$ packet $(c,r,W,P,L)$ of \autoref{def:realball-window-carrier};
\item classifier and stability: the transported-center and transported-radius statement of \autoref{thm:realball-radius-transport};
\item finite window: the witness $W$ listing the displayed $\RegSeqRat$ center approximants, the positive $\DyadicRatCoreUp$ radius row, and the $\DyadicIntervalUp$ interval rows visible at the requested precision;
\item provenance: the $\Pkg$ row naming the consumed $\RealUp$, $\RegSeqRat$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\DyadicIntervalUp$ certificate boundaries;
\item ledger boundary: the row $L$ recording that only the unobserved tail beyond the displayed window is hidden.
\end{enumerate}
These five rows are the full public seed surface for the finite dyadic-radius neighborhood name.
\end{theorem}
\leanchecked{BEDC.Derived.RealBallUp.RealBallWindowPacket\_finite\_window\_namecert}
\begin{proof}
The carrier row supplies the center, radius, finite window, provenance, and tail-ledger coordinates. This fixes the source domain of the name.

The classifier and stability row is \autoref{thm:realball-radius-transport}. It says that the only permitted motion is componentwise $\hsame$ transport along the displayed $\Cont$ routes named by the provenance row.

The remaining rows are direct projections from the carrier. Since the construction records no host real topology, open-cover family, completeness principle, or hidden equality quotient, the five listed rows exhaust the $\NameCert_{\RealBallUp}$ obligation surface.
\end{proof}

\begin{theorem}[RealBall metric-neighborhood handoff]
\label{thm:realball-metric-neighborhood-handoff}
A downstream $\MetricSpaceUp$ consumer may read an accepted $\RealBallUp$ carrier only as a finite real-neighborhood surface: a $\RealUp$ center name, a positive dyadic radius, a visible dyadic interval window, and the provenance and tail ledger of \autoref{def:realball-window-carrier}. The handoff supports metric-local arguments that consume displayed dyadic tolerances around a real name.

The handoff is not an open-cover topology and does not assert a basis theorem, Heine--Borel compactness, completeness of $\RealUp$, or choice of a global covering family.
\end{theorem}
\leanchecked{BEDC.Derived.RealBallUp.RealBallWindowCarrier\_metric\_neighborhood\_handoff}
\begin{proof}
Read the carrier through \autoref{def:realball-window-carrier}. The only metric-facing coordinates are the center name, the positive dyadic radius, and the displayed dyadic interval window around the center approximants.

The transport theorem \autoref{thm:realball-radius-transport} supplies the stability needed by a metric consumer: replacing the center name or radius by displayed $\hsame$ representatives repacks the same finite neighborhood surface.

No coordinate of the carrier contains an open cover, a covering selection principle, a completed metric object, or a host topology. A $\MetricSpaceUp$ consumer therefore receives exactly the finite dyadic-radius read described in the statement.
\end{proof}

\begin{theorem}[RealBall standard obligation boundary]
\label{thm:realball-standard-obligation-boundary}
The $\RealBallUp$ chapter claims only finite dyadic-window balls around $\RealUp$ names. Its dependency list is exactly the displayed $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRat$, $\RealUp$, and $\DyadicIntervalUp$ certificate surface named by the provenance row.

This places the chapter inside the same concrete-instance lattice as \autoref{ch:concrete-instances-real-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, and \autoref{ch:concrete-instances-regseqrat-namecert}: the $\RealBallUp$ carrier consumes $\RealUp$ names through $\StreamNameUp$ finite windows and $\RegSeqRat$ readback before exposing dyadic-window balls.

It does not claim real-number completeness, order trichotomy, locatedness outside the displayed window, Heine--Borel compactness, equivalence with host real open balls, a host topological bridge, or any open-cover compactness principle.
\end{theorem}
\leanchecked{BEDC.Derived.RealBallUp.RealBallWindowPacket\_standard\_obligation\_boundary}
\begin{proof}
The positive-radius datum is a $\DyadicRatCoreUp$ row, the center datum is a $\RealUp$ name read through $\RegSeqRat$ and $\StreamNameUp$, and the visible ball surface is a finite collection of $\DyadicIntervalUp$ rows. These are exactly the dependencies listed in the carrier provenance.

Apply \autoref{thm:realball-finite-window-namecert} to exhaust the public obligation surface. Every accepted read is one of the five finite rows listed there.

The excluded principles would require coordinates not present in the packet: global real order data, completed metric limits, open-cover families, compactness witnesses, or a host topological bridge. Since the carrier has no such coordinate, the boundary is precisely the finite dyadic-window claim.
\end{proof}

\begin{theorem}[RealBall scoped dependency packet]
\label{thm:realball-scoped-dependency-packet}
Every accepted $\RealBallUp$ finite-window packet is scoped by the center $\RealUp$ stream read, a positive $\DyadicRatCoreUp$ radius, visible $\DyadicIntervalUp$ window rows, $\mathsf{Pkg}$ provenance, and the local ledger boundary. All transport used by the packet factors through $\mathsf{BHist}$ carrier rows, displayed $\hsame$ identifications, $\Cont$ routes, and $\NameCert$ rows.

Consequently the accepted real-ball surface is a finite dyadic-neighborhood packet over the L10 primitives named in the carrier. It does not add a host topological ball, Heine--Borel compactness data, a global open-cover family, or completeness of the real-name carrier.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:realball-window-carrier}. The center coordinate is read as a $\RealUp$ name through the displayed $\RegSeqRat$ and $\StreamNameUp$ rows, while the radius coordinate is the positive $\DyadicRatCoreUp$ row stored in the same packet.

Next compose \autoref{thm:realball-radius-transport} with the visible $\DyadicIntervalUp$ window rows. This identifies the permitted $\hsame$ and $\Cont$ movement of the finite dyadic neighborhood without adding any coordinate outside the carrier.

The consumer face is the metric-neighborhood handoff of \autoref{thm:realball-metric-neighborhood-handoff}. The local $\NameCert_{\RealBallUp}$ surface of \autoref{thm:realball-finite-window-namecert} supplies the provenance and ledger rows used by that handoff.

Finally apply \autoref{thm:realball-standard-obligation-boundary}. It rules out host topology, compactness, and completeness coordinates, so the scoped dependency packet is exactly the finite center, radius, window, provenance, and ledger surface stated above.
\end{proof}
\leanchecked{BEDC.Derived.RealBallUp.RealBallWindowPacket\_scoped\_dependency\_packet}

\begin{theorem}[RealBall public NameCert export]
\label{thm:realball-public-namecert-export}
The finite-window carrier of \autoref{def:realball-window-carrier}, the radius transport of \autoref{thm:realball-radius-transport}, the finite-window $\NameCert_{\RealBallUp}$ surface of \autoref{thm:realball-finite-window-namecert}, the metric-neighborhood handoff of \autoref{thm:realball-metric-neighborhood-handoff}, the standard obligation boundary of \autoref{thm:realball-standard-obligation-boundary}, and the scoped dependency packet of \autoref{thm:realball-scoped-dependency-packet} assemble a public $\NameCert_{\RealBallUp}$ export for downstream $\MetricSpaceUp$ and $\RealUp$ consumers.

The exported boundary is exactly the finite dyadic-window neighborhood surface: a $\RealUp$ center read through $\RegSeqRat$ and $\StreamNameUp$, a positive $\DyadicRatCoreUp$ radius, visible $\DyadicIntervalUp$ rows, $\mathsf{Pkg}$ provenance, and the tail ledger. It exports no host topology, open-cover compactness, trichotomy, completeness datum, or host real ball.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:realball-window-carrier}. Its rows give the center name, positive dyadic radius, finite visible window, provenance packet, and ledger boundary that a public consumer can inspect.

Apply \autoref{thm:realball-radius-transport} to fix the stability row, and apply \autoref{thm:realball-finite-window-namecert} to package the carrier, classifier, finite window, provenance, and ledger as the local $\NameCert_{\RealBallUp}$ surface.

Next use the metric-neighborhood handoff of \autoref{thm:realball-metric-neighborhood-handoff}. This is the consumer-facing read for $\MetricSpaceUp$ and $\RealUp$: it exposes the finite dyadic-radius neighborhood without changing the underlying BEDC packet.

Finally combine the standard obligation boundary of \autoref{thm:realball-standard-obligation-boundary} with the scoped dependency packet of \autoref{thm:realball-scoped-dependency-packet}. These two rows state exactly which dependencies are public and which coordinates are absent, so repacking the listed rows gives the claimed $\NameCert_{\RealBallUp}$ export and nothing beyond it.
\end{proof}

\begin{theorem}[RealBall standard finite-window bridge]
\label{thm:realball-standard-bridge}
The public export of \autoref{thm:realball-public-namecert-export} determines
the standard finite-window bridge schema for $\RealBallUp$. The source row is
the $\RealUp$ center read through $\RegSeqRatUp$ and $\StreamNameUp$, the radius
row is the positive $\DyadicRatCoreUp$ datum, and the window row is the visible
$\DyadicIntervalUp$ packet. The only bridge routes are the displayed
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and ledger rows.

This bridge exports no host topology, open-cover compactness, trichotomy,
completeness datum, or host real ball.
\end{theorem}
\begin{proof}
Begin with the public export of
\autoref{thm:realball-public-namecert-export}. It exposes exactly the center,
positive radius, finite window, provenance, and ledger rows of the
$\NameCert_{\RealBallUp}$ packet.

Apply \autoref{thm:realball-scoped-dependency-packet} to identify the permitted
routes. The center row factors through $\RealUp$, $\RegSeqRatUp$, and
$\StreamNameUp$; the radius row factors through $\DyadicRatCoreUp$; and the
visible window factors through $\DyadicIntervalUp$.

Finally use \autoref{thm:realball-standard-obligation-boundary}. It excludes
host topology, compactness, trichotomy, completeness, and host-ball
coordinates. Projecting the displayed rows and repacking them gives exactly the
finite bridge schema stated above.
\end{proof}

\begin{theorem}[RealBall finite-window consumer coverage]
\label{thm:realball-finite-window-consumer-coverage}
Let $B=(c,r,W,P,L)$ be an accepted $\RealBallUp$ packet. Every public read of
$B$ by a $\MetricSpaceUp$ consumer, by a $\RegSeqRatUp$ read of the center, or
by a $\RealUp$ neighborhood consumer factors through exactly the center row
$c$, the positive dyadic radius row $r$, the visible $\DyadicIntervalUp$ window
rows $W$, the $\mathsf{Pkg}$ provenance row $P$, the ledger $L$, and the
$\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$ rows isolated by
\autoref{thm:realball-scoped-dependency-packet},
\autoref{thm:realball-public-namecert-export}, and
\autoref{thm:realball-standard-bridge}.

The consumer surface contains no coordinate for host topology, open-cover
compactness, Heine--Borel data, trichotomy, completeness, or host real balls.
\end{theorem}
\begin{proof}
Project the accepted packet through the carrier of
\autoref{def:realball-window-carrier}. The projection exposes only the center
name, positive dyadic radius, finite visible dyadic window, provenance packet,
and tail ledger, so these rows form the whole candidate packet seen by a
consumer.

Use the radius transport of \autoref{thm:realball-radius-transport} and the
finite-window $\NameCert_{\RealBallUp}$ surface of
\autoref{thm:realball-finite-window-namecert}. They keep the positive radius
row and the visible window stable under the displayed $\hsame$ and $\Cont$
classifiers, so replacing the packet by a classified equal one does not reveal a
new read coordinate.

Next apply the metric-neighborhood handoff and the public export of
\autoref{thm:realball-metric-neighborhood-handoff} and
\autoref{thm:realball-public-namecert-export}. These are exactly the public
routes used by $\MetricSpaceUp$, $\RegSeqRatUp$, and $\RealUp$ neighborhood
consumers: each route reads one of the displayed rows and then repacks it as
the same finite-window $\NameCert$ boundary.

Finally use the standard bridge of \autoref{thm:realball-standard-bridge}. The
bridge has no extra source, pattern, or ledger coordinate beyond the center,
radius, visible-window, provenance, $\mathsf{BHist}$, $\hsame$, $\Cont$, and
$\NameCert$ rows already listed. Since the bridge also excludes host topology,
open-cover compactness, Heine--Borel data, trichotomy, completeness, and host
real balls, every public consumer read is exhausted by the same visible packet.
\end{proof}

\closureat{RealBallUp}{seedStr}
\closureat{RealBallUp}{obligationStr}
\closureat{RealBallUp}{scopedStr}
\closureat{RealBallUp}{publicStr}
\closureat{RealBallUp}{bridgedStr}
\closureat{RealBallUp}{matureStr}

\begin{closurestatus}{\RealBallUp}
  \constructivestory{A real-ball packet is generated by a $\RealUp$ center name read through $\RegSeqRat$ and $\StreamNameUp$, a positive $\DyadicRatCoreUp$ radius row, visible $\DyadicIntervalUp$ window rows, $\Pkg$ provenance, and a ledger hiding only the unobserved tail.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The finite-window carrier of \autoref{def:realball-window-carrier}, radius transport of \autoref{thm:realball-radius-transport}, finite-window NameCert surface of \autoref{thm:realball-finite-window-namecert}, metric handoff of \autoref{thm:realball-metric-neighborhood-handoff}, boundary row of \autoref{thm:realball-standard-obligation-boundary}, scoped dependency packet of \autoref{thm:realball-scoped-dependency-packet}, public export of \autoref{thm:realball-public-namecert-export}, standard bridge of \autoref{thm:realball-standard-bridge}, and consumer coverage of \autoref{thm:realball-finite-window-consumer-coverage} are bound to $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, $\NameCert$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\DyadicIntervalUp$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.RealBallUp.RealBallWindowPacket\_finite\_window\_namecert}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close completeness, trichotomy, Heine--Borel compactness, host real topology, or host real balls.}
  \upgradepath{Further Lean work concerns the public export, standard bridge, and consumer-coverage targets beyond the cited finite-window NameCert surface.}
\end{closurestatus}
