\chapter{A Concrete Naming Certificate for $\TwinSubstrateRoundtripUp$}
\label{ch:concrete-instances-twinsubstrateroundtrip-namecert}
\origin{human}

The $\TwinSubstrateRoundtripUp$ packet turns the twin-substrate architecture of \autoref{ch:twin-substrate-synthesis} into a finite roundtrip boundary. It sits beside the MetaCIC synthesis certificate of \autoref{ch:concrete-instances-metacicauditsynthesis-namecert}, the GroundCompiler audit-map packet of \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, the synthesis packet of \autoref{ch:concrete-instances-twinsubstratesynthesis-namecert}, and the audit-coupling packet of \autoref{ch:concrete-instances-twinsubstrateauditcoupling-namecert}. Those siblings expose substrate-local audit rows and paired-read rows; this chapter packages the roundtrip read without making either substrate certify the other by hidden equality.

\begin{definition}[TwinSubstrateRoundtrip packet]
\label{def:twin-substrate-roundtrip-packet}
A $\TwinSubstrateRoundtripUp$ carrier is a finite $\BHist$ packet
$$
Q=(M,G,A,R,F,E,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $M$ is the MetaCIC synthesis row read through \autoref{ch:concrete-instances-metacicauditsynthesis-namecert};
\item $G$ is the GroundCompiler audit-map row read through \autoref{ch:concrete-instances-groundcompilerauditmap-namecert};
\item $A$ is the architecture row naming the substrate separation of \autoref{ch:twin-substrate-synthesis};
\item $R$ is the roundtrip route row, recording the finite order in which a consumer reads the MetaCIC surface, the compiler-facing surface, and the return-to-audit boundary;
\item $F$ is the frontier row recording which MetaCIC obligations and which GroundCompiler obligations remain substrate-local after the roundtrip read;
\item $E$ is the export row naming the downstream packet handed to self-compilation or audit-map consumers;
\item $H$ records componentwise $\hsame$ transport for the substrate rows, architecture row, route row, frontier row, export row, provenance row, and local name row;
\item $C$ records displayed $\Cont$ routes by which a consumer reads $M,G,A,R,F,E$ in finite order;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:twin-substrate-synthesis}, \autoref{ch:concrete-instances-metacicauditsynthesis-namecert}, \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, \autoref{ch:concrete-instances-twinsubstratesynthesis-namecert}, \autoref{ch:concrete-instances-twinsubstrateauditcoupling-namecert}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\TwinSubstrateRoundtripUp}$ row.
\end{enumerate}
The carrier has no coordinate for identifying $M$ with $G$, converting a compiler report into proof evidence, reading a closed-CIC theorem as a compiler input channel, or discharging either substrate frontier by an unrecorded host assertion.
\end{definition}

\begin{theorem}[TwinSubstrateRoundtrip obligation surface]
\label{thm:twin-substrate-roundtrip-obligation-surface}
For every accepted $\TwinSubstrateRoundtripUp$ carrier
$$
Q=(M,G,A,R,F,E,H,C,P,N),
$$
the local $\NameCert_{\TwinSubstrateRoundtripUp}$ surface consists exactly of MetaCIC synthesis readback through $M$, GroundCompiler audit-map readback through $G$, architecture separation through $A$, roundtrip route replay through $R$, frontier preservation through $F$, export readback through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite packet. The substrate rows $M$ and $G$ are separate coordinates, and $A$ records the architecture boundary that keeps their audit questions distinct.

Read the route and frontier rows next. The row $R$ gives the finite roundtrip order, while $F$ records which obligations remain MetaCIC-local or GroundCompiler-local after the read.

The export row $E$ is then a packaged public surface, not a hidden conversion between substrates. Rows $H,C,P,N$ transport, replay, package, and name the same displayed coordinates.

Since the packet contains no additional coordinate, the listed rows exhaust the local obligation surface. In particular, no compiler report, closed-CIC theorem row, hidden equality, or host assertion can enter the certificate outside $M,G,A,R,F,E,H,C,P,N$.
\end{proof}

\begin{theorem}[TwinSubstrateRoundtrip noncollapse]
\label{thm:twin-substrate-roundtrip-noncollapse}
Every public roundtrip read from an accepted $\TwinSubstrateRoundtripUp$ carrier factors through the displayed rows $M,G,A,R,F,E,H,C,P,N$ of \autoref{def:twin-substrate-roundtrip-packet}. Such a read may package MetaCIC and GroundCompiler audit surfaces together, but it cannot collapse the substrates, identify their classifiers, convert reports into proof evidence, or use closed-CIC rows as compiler input channels.
\end{theorem}
\begin{proof}
Start from the obligation surface of \autoref{thm:twin-substrate-roundtrip-obligation-surface}. It forces every public read to expose the MetaCIC row $M$ and the GroundCompiler row $G$ as separate coordinates before consulting the route or export rows.

The architecture row $A$ and frontier row $F$ preserve the substrate distinction. They record that MetaCIC proof-theoretic boundaries and GroundCompiler pipeline boundaries remain attached to their own rows even when a roundtrip consumer reads both.

The route row $R$ and export row $E$ supply a finite package for downstream consumers. Transport and continuation through $H$ and $C$, with provenance and naming through $P,N$, replay that package without adding a common equality or host-level audit oracle.

Therefore a public roundtrip read can carry both audit surfaces, but it cannot identify them or move evidence across the boundary except through the displayed packet rows.
\end{proof}

\closureat{TwinSubstrateRoundtripUp}{seedStr}

\begin{closurestatus}{\TwinSubstrateRoundtripUp}
  \constructivestory{A $\TwinSubstrateRoundtripUp$ packet is generated from a MetaCIC synthesis row, a GroundCompiler audit-map row, an architecture row, a roundtrip route row, a frontier row, an export row, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:twin-substrate-roundtrip-packet}, \autoref{thm:twin-substrate-roundtrip-obligation-surface}, and \autoref{thm:twin-substrate-roundtrip-noncollapse} bind the finite roundtrip package and its substrate noncollapse boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close MetaCIC subject reduction, GroundCompiler host trust, self-hosting correctness, Lean verification, audit cleanliness, axiom cleanliness, or bridge checking.}
  \upgradepath{Obligation closure requires checked substrate-row readback, route replay, frontier preservation, export exactness, transport, continuation, provenance, naming, and noncollapse for the same finite roundtrip packet.}
\end{closurestatus}
