\chapter{TwinSubstrateAuditSynthesis NameCert construction}
\label{ch:concrete-instances-twin-substrate-audit-synthesis-namecert}
\origin{ai}

The $\TwinSubstrateAuditSynthesisUp$ packet realizes the twin-substrate synthesis of \autoref{ch:twin-substrate-synthesis} as a finite NameCert object whose audit rows remain substrate-specific. It sits beside the MetaCIC audit synthesis of \autoref{ch:concrete-instances-metacicauditsynthesis-namecert}, the GroundCompiler audit map of \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, and the audit-map frontier packet of \autoref{ch:concrete-instances-auditmapfrontierpacket-namecert}: those siblings provide the two audit sources and the shared frontier discipline, while this chapter names their paired finite synthesis row.

\begin{definition}[Twin-substrate audit-synthesis carrier]
\label{def:twin-substrate-audit-synthesis-carrier}
A $\TwinSubstrateAuditSynthesisUp$ carrier is a finite $\BHist$ packet
$$
S=(M,G,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is a MetaCIC audit-synthesis row, read through \autoref{ch:concrete-instances-metacicauditsynthesis-namecert};
\item $G$ is a GroundCompiler audit-map row, read through \autoref{ch:concrete-instances-groundcompilerauditmap-namecert};
\item $A$ is an audit-frontier alignment row, read through \autoref{ch:concrete-instances-auditmapfrontierpacket-namecert}, that records which MetaCIC boundary and which GroundCompiler boundary are being paired;
\item $H$ records componentwise $\hsame$ transports for the MetaCIC row, GroundCompiler row, frontier alignment row, continuation row, package row, and local naming row;
\item $C$ records displayed $\Cont$ routes by which consumers read $M$, $G$, and $A$ without identifying their evidence kinds;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:twin-substrate-synthesis}, \autoref{ch:concrete-instances-metacicauditsynthesis-namecert}, \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, \autoref{ch:concrete-instances-auditmapfrontierpacket-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\TwinSubstrateAuditSynthesisUp}$ row.
\end{enumerate}
The classifier accepts exactly the packets whose public reads factor through $S=(M,G,A,H,C,P,N)$ and whose frontier alignment keeps MetaCIC proof-theoretic residue separate from GroundCompiler report, recognizer, channel, and hidden-input boundaries.
\end{definition}

\begin{theorem}[TwinSubstrateAuditSynthesis NameCert obligations]
\label{thm:twin-substrate-audit-synthesis-namecert-obligations}
For every accepted $\TwinSubstrateAuditSynthesisUp$ carrier
$$
S=(M,G,A,H,C,P,N),
$$
the local $\NameCert_{\TwinSubstrateAuditSynthesisUp}$ surface consists exactly of MetaCIC audit-synthesis readback through $M$, GroundCompiler audit-map readback through $G$, audit-frontier alignment through $A$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:twin-substrate-audit-synthesis-carrier}. Its coordinates are precisely the two audit rows, the frontier alignment row, the transport row, the continuation row, the provenance row, and the local naming row.

Read the substrate rows separately. The MetaCIC row $M$ carries the audit-synthesis surface, while the GroundCompiler row $G$ carries the compiler-facing audit-map surface. The alignment row $A$ names a shared frontier position, but it does not convert one row into the other.

Finally, $H,C,P,N$ transport, replay, package, and name only those displayed coordinates. Since the carrier has no hidden equality, report-to-proof conversion, or compiler-input oracle, the listed rows exhaust the NameCert obligation surface.
\end{proof}

\begin{theorem}[TwinSubstrateAuditSynthesis cross-map non-escape]
\label{thm:twin-substrate-audit-synthesis-cross-map-nonescape}
Every public cross-map read from an accepted $\TwinSubstrateAuditSynthesisUp$ carrier factors through the displayed rows $M,G,A,H,C,P,N$ of \autoref{def:twin-substrate-audit-synthesis-carrier}. Such a read cannot turn a GroundCompiler report, recognizer, channel row, or hidden-input refusal into MetaCIC proof evidence, and it cannot turn a MetaCIC obstruction, closed-calculus theorem row, or subject-reduction residue into GroundCompiler input or compiler-side evidence.
\end{theorem}
\begin{proof}
Start with the obligation surface of \autoref{thm:twin-substrate-audit-synthesis-namecert-obligations}. Every public read must first choose the MetaCIC row, the GroundCompiler row, or the frontier alignment row and then pass through the displayed continuation and transport rows.

For a MetaCIC-facing read, the consumer receives $M$ with $A,H,C,P,N$ as finite routing data. The GroundCompiler row $G$ may be present as paired audit context, but the packet contains no coordinate that reclassifies report, recognizer, channel, or hidden-input data as proof evidence.

For a GroundCompiler-facing read, the consumer receives $G$ with the same finite routing discipline. The MetaCIC row $M$ may be cited as the paired audit-synthesis boundary, but the packet contains no coordinate that reclassifies closed-calculus theorem data, obstruction data, or subject-reduction residue as compiler input.

Thus the ledger cannot escape the displayed packet. Coordinate exhaustion over $M,G,A,H,C,P,N$ preserves both refusal boundaries while allowing a finite paired audit read.
\end{proof}

\closureat{TwinSubstrateAuditSynthesisUp}{seedStr}

\begin{closurestatus}{\TwinSubstrateAuditSynthesisUp}
  \constructivestory{A $\TwinSubstrateAuditSynthesisUp$ packet is generated from a MetaCIC audit-synthesis row, a GroundCompiler audit-map row, an audit-frontier alignment row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:twin-substrate-audit-synthesis-carrier}, \autoref{thm:twin-substrate-audit-synthesis-namecert-obligations}, and \autoref{thm:twin-substrate-audit-synthesis-cross-map-nonescape} bind the finite paired audit-synthesis packet and its cross-map non-escape boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close MetaCIC subject reduction, GroundCompiler host trust, compiler self-reference, Lean verification, audit cleanliness, axiom cleanliness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, MetaCIC audit-synthesis readback, GroundCompiler audit-map readback, frontier-alignment exactness, transport, continuation, provenance, naming, and cross-map non-escape for the same finite packet.}
\end{closurestatus}
