\chapter{A Concrete Naming Certificate for $\AxiomDependencyTupleUp$}
\label{ch:concrete-instances-axiom-dependency-tuple-namecert}
\origin{human}

The $\AxiomDependencyTupleUp$ packet realizes the dependency-map reading of
\autoref{ch:bedc-axiom-dependency-map} as finite NameCert data. It follows
the audit-map family discipline of \autoref{ch:audit-map-family-methodology}
and sits beside the discharge-socket boundary of
\autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}:
the former gives the row family shape, while the latter is a concrete sibling
where missing MetaCIC supply is named rather than hidden.

\begin{definition}[AxiomDependencyTuple carrier]
\label{def:axiom-dependency-tuple-carrier}
An $\AxiomDependencyTupleUp$ carrier is a finite $\BHist$ packet
$$
A=(M,W,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is one of the three mode rows, Mode A for zero-supply internal
proof, Mode B for restricted-proof discharge under displayed supply, and
Mode C for counterexample or socket witness against an unstated supply;
\item $W$ is the witness row, recording a proof, restricted proof,
counterexample, or socket witness according to $M$;
\item $S$ is the required-supply ledger, listing exactly the host conversion,
quotient equality, $\mathsf{Classical.choice}$, $\mathsf{propext}$, ambient
classical theorem, or other named supply row that the entry requires;
\item $H$ records componentwise $\hsame$ transport for the mode, witness,
required-supply, route, provenance, and naming rows;
\item $C$ records the displayed $\Cont$ routes by which a consumer reads the
mode, witness, and required-supply ledger;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:bedc-axiom-dependency-map},
\autoref{ch:audit-map-family-methodology},
\autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert},
$\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\AxiomDependencyTupleUp}$ row.
\end{enumerate}
The classifier accepts exactly packets whose mode, witness, required-supply
ledger, transport, continuation, provenance, and naming rows are displayed in
this finite carrier.
\end{definition}

\begin{theorem}[AxiomDependencyTuple NameCert obligations]
\label{thm:axiom-dependency-tuple-namecert-obligations}
For the carrier of \autoref{def:axiom-dependency-tuple-carrier}, the local
$\NameCert_{\AxiomDependencyTupleUp}$ surface consists of carrier admission
for
$$
A=(M,W,S,H,C,P,N),
$$
mode classification, witness transport, required-supply ledger exactness,
displayed $\Cont$ route readback, $\Pkg$ provenance, and local naming. The
packet may name host conversion, quotient equality,
$\mathsf{Classical.choice}$, $\mathsf{propext}$, or an ambient classical CIC
theorem as supply in $S$, but it cannot export any of them as BEDC data.
\end{theorem}
\begin{proof}
Project the finite packet $A$. The rows $M,W,S$ provide the mathematical
payload: a mode, a witness appropriate to that mode, and the ledger of supply
required by that witness.

Read $H$ and $C$ next. Componentwise $\hsame$ transport preserves the same
mode and witness row, and every consumer route must replay the displayed
ledger before it reads the tuple.

Finally inspect $P$ and $N$. Provenance cites only the dependency-map chapter,
the audit-map methodology, the discharge-socket sibling, and the BEDC kernel
rows. Since no carrier coordinate contains host conversion, quotient equality,
choice, propositional extensionality, or an ambient classical theorem as an
exported BEDC proof, the named supply remains a ledger entry rather than a
hidden rule.
\end{proof}

\begin{theorem}[AxiomDependencyTuple mode exhaustion]
\label{thm:axiom-dependency-tuple-mode-exhaustion}
Every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$ is exhausted by the three displayed modes: Mode A carries
a zero-supply proof witness, Mode B carries a restricted-proof witness
together with the required-supply ledger $S$, and Mode C carries a
counterexample or socket witness naming the refused supply. Componentwise
$\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and the local
$\NameCert$ row preserve this trichotomy and do not add a fourth mode.
\end{theorem}
\begin{proof}
Inspect the mode row $M$ in the carrier of
\autoref{def:axiom-dependency-tuple-carrier}. Its visible constructors are
exactly the zero-supply, restricted-proof, and counterexample-or-socket
alternatives.

In Mode A, the witness row $W$ is read as an internal proof and the ledger
$S$ is empty of external supply. In Mode B, the witness row is read only
together with the named required supply. In Mode C, the witness row is a
counterexample or socket naming the missing supply rather than discharging it.

Transport and routing do not change the case split. The rows $H,C,P,N$ replay
the same mode, witness, and ledger coordinates, so no consumer can introduce
host conversion, quotient equality, $\mathsf{Classical.choice}$,
$\mathsf{propext}$, an ambient classical CIC theorem, or any fourth mode
outside the displayed packet.
\end{proof}

\begin{theorem}[AxiomDependencyTuple supply-ledger readback]
\label{thm:axiom-dependency-tuple-supply-ledger-readback}
Every accepted $\AxiomDependencyTupleUp$ packet exposes the required-supply row
$S$ before the witness row $W$ can be consumed. If the tuple names host
conversion, quotient equality, $\mathsf{Classical.choice}$,
$\mathsf{propext}$, an ambient theorem, or any other external supply, that name
remains a ledger row in $S$ and never becomes an exported BEDC rule.
\end{theorem}
\begin{proof}
Begin with the carrier projection
$$
A=(M,W,S,H,C,P,N).
$$
By \autoref{def:axiom-dependency-tuple-carrier}, the consumer-facing data
contains both the witness coordinate $W$ and the required-supply ledger $S$.

Apply \autoref{thm:axiom-dependency-tuple-namecert-obligations}. The local
$\NameCert_{\AxiomDependencyTupleUp}$ surface includes witness transport and
required-supply ledger exactness, so any route that reads $W$ must also read the
displayed supply row attached to that witness.

Finally use \autoref{thm:axiom-dependency-tuple-mode-exhaustion}. Mode A has no
external supply to export, Mode B consumes $W$ only under the displayed ledger,
and Mode C records a counterexample or socket rather than a discharge. Thus the
named host or classical material remains visible audit supply in $S$.
\end{proof}

\begin{theorem}[AxiomDependencyTuple zero-supply mode exactness]
\label{thm:axiom-dependency-tuple-zero-supply-mode-exactness}
For every accepted $\AxiomDependencyTupleUp$ packet
$A=(M,W,S,H,C,P,N)$ in Mode A, the required-supply ledger $S$ is exposed as
empty before the zero-supply witness row $W$ is read. Consequently the packet
consumes only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert_{\AxiomDependencyTupleUp}$ rows, with no host conversion, quotient
equality, $\mathsf{Classical.choice}$, $\mathsf{propext}$, or ambient theorem
available as BEDC proof data.
\end{theorem}
\begin{proof}
Project the tuple through
\autoref{def:axiom-dependency-tuple-carrier}. The public carrier has exactly
the rows $M,W,S,H,C,P,N$, so the Mode A claim can only mention the displayed
mode, witness, ledger, transport, route, provenance, and naming coordinates.

Apply \autoref{thm:axiom-dependency-tuple-namecert-obligations} and
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}. The local NameCert row
binds witness transport and required-supply ledger exactness, while mode
exhaustion identifies Mode A as the zero-supply case.

Now use \autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. The ledger
$S$ is read before $W$, and in Mode A that ledger contains no named external
supply. Finally,
\autoref{thm:axiom-dependency-tuple-route-nonexport} keeps every $\Cont$ route
from converting an absent ledger entry into a BEDC proof rule.
\end{proof}

\begin{theorem}[AxiomDependencyTuple restricted-supply ledger exactness]
\label{thm:axiom-dependency-tuple-restricted-supply-ledger-exactness}
For every accepted $\AxiomDependencyTupleUp$ packet
$A=(M,W,S,H,C,P,N)$ in Mode B, each host conversion, quotient equality,
$\mathsf{Classical.choice}$ use, $\mathsf{propext}$ use, or ambient theorem
required by the restricted witness appears as a visible row of $S$ before
$W$ is read. None of these named rows is converted into an internal BEDC rule.
\end{theorem}
\begin{proof}
Begin with the carrier and NameCert surfaces. By
\autoref{def:axiom-dependency-tuple-carrier} and
\autoref{thm:axiom-dependency-tuple-namecert-obligations}, a restricted packet
records the witness row and its required-supply ledger as separate public
coordinates, checked by local naming obligations.

The mode split is exhaustive by
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}. In Mode B, the witness is
the restricted-proof witness, and the supply required by that witness is not
part of the BEDC kernel surface.

Apply \autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. Every named
host conversion, quotient equality, choice, propositional extensionality, or
ambient theorem must be read from $S$ before $W$ is consumed.

Finally use \autoref{thm:axiom-dependency-tuple-route-nonexport}. A displayed
route may replay the ledger and witness coordinates, but it has no constructor
that turns a required-supply ledger row into an exported BEDC proof principle.
\end{proof}

\begin{theorem}[AxiomDependencyTuple downstream consumer supply boundary]
\label{thm:axiom-dependency-tuple-downstream-consumer-supply-boundary}
Every downstream consumer of an accepted $\AxiomDependencyTupleUp$ packet
factors its read through the displayed coordinates $M,W,S,H,C,P,N$. Hence
counterexample, socket, and restricted-proof supply remains an audit row in
the tuple rather than a hidden proof principle available to the consumer.
\end{theorem}
\begin{proof}
Use \autoref{def:axiom-dependency-tuple-carrier} to identify the only public
coordinates of the accepted packet. The downstream consumer has no carrier
component beyond $M,W,S,H,C,P,N$ from which to read additional supply.

The local NameCert and mode rows determine how those coordinates are consumed.
By \autoref{thm:axiom-dependency-tuple-namecert-obligations} and
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}, the consumer first
selects one of the three modes and then reads the corresponding witness and
ledger rows under the displayed transport, route, provenance, and naming data.

The ledger boundary is fixed by
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. Restricted supply,
host supply, quotient supply, choice, propositional extensionality, ambient
theorems, counterexamples, and sockets are visible only as rows attached to the
accepted tuple.

Finally apply \autoref{thm:axiom-dependency-tuple-route-nonexport}. Since every
consumer route merely replays the displayed coordinates, no downstream audit
or dependency-map consumer can promote those audit rows into hidden BEDC proof
data.
\end{proof}

\begin{theorem}[AxiomDependencyTuple route nonexport]
\label{thm:axiom-dependency-tuple-route-nonexport}
Every displayed $\Cont$ route in the coordinate $C$ replays the
$M,W,S,H,P,N$ components of an accepted $\AxiomDependencyTupleUp$ packet
componentwise. The route cannot introduce a fourth mode and cannot convert the
required-supply row $S$ into an internal proof principle.
\end{theorem}
\begin{proof}
Project the route coordinate $C$ from
\autoref{def:axiom-dependency-tuple-carrier}. Its declared role is readback for
the mode, witness, and required-supply ledger, with the remaining rows supplying
transport, provenance, and naming.

Apply \autoref{thm:axiom-dependency-tuple-namecert-obligations} to the same
carrier. The NameCert obligations include displayed $\Cont$ route readback and
componentwise transport, so a route is checked against the rows already present
in $A$.

The mode alternatives are exhausted by
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}. Since $C$ only replays the
displayed coordinates, it has no constructor by which to create another mode or
turn a required-supply ledger entry into a BEDC proof rule.
\end{proof}

\begin{theorem}[AxiomDependencyTuple consumer exhaustion]
\label{thm:axiom-dependency-tuple-consumer-exhaustion}
Every downstream consumer of an accepted $\AxiomDependencyTupleUp$ tuple is
exhausted by the mode row $M$, witness row $W$, required-supply ledger $S$,
displayed route row $C$, provenance row $P$, and local
$\NameCert_{\AxiomDependencyTupleUp}$ row $N$, together with their
componentwise transport $H$. There is no hidden consumer authority outside this
finite packet.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:axiom-dependency-tuple-carrier}. The packet
lists the only coordinates available to a consumer:
$$
M,\ W,\ S,\ H,\ C,\ P,\ N.
$$

The obligation theorem
\autoref{thm:axiom-dependency-tuple-namecert-obligations} assigns each
consumer-facing role to one of these coordinates: carrier admission, mode
classification, witness transport, ledger exactness, route readback,
provenance, and local naming.

Mode exhaustion then removes the only remaining possibility for extra consumer
authority. By \autoref{thm:axiom-dependency-tuple-mode-exhaustion}, every
accepted packet lies in Mode A, Mode B, or Mode C, and transport or route
readback preserves that case split. Hence any downstream consumer is confined to
the finite displayed rows.
\end{proof}

\begin{theorem}[AxiomDependencyTuple zero-supply mode soundness]
\label{thm:axiom-dependency-tuple-zero-supply-mode-soundness}
In Mode A, an accepted $\AxiomDependencyTupleUp$ packet consumes the witness
row $W$ only when the required-supply ledger $S$ records no external supply.
The zero-supply branch cannot smuggle host conversion, quotient equality,
$\mathsf{Classical.choice}$, $\mathsf{propext}$, or any ambient classical
theorem through the route row $C$, provenance row $P$, local
$\NameCert_{\AxiomDependencyTupleUp}$ row $N$, or componentwise transport row
$H$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:axiom-dependency-tuple-carrier}. The
coordinates $M,W,S,H,C,P,N$ are displayed separately, so the witness row and
the required-supply row are not identified by the packet shape.

Apply \autoref{thm:axiom-dependency-tuple-mode-exhaustion}. In the Mode A
branch, $W$ is the zero-supply proof witness and $S$ has no external host or
classical supply to replay.

The ledger boundary is then fixed by
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. A consumer can
read $W$ only through the visible ledger row, and in this branch that ledger
contains no host conversion, quotient equality, choice, propositional
extensionality, or ambient classical theorem.

Finally use \autoref{thm:axiom-dependency-tuple-route-nonexport} and
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion}. Routes and consumers
are exhausted by the displayed rows, so no hidden coordinate remains from which
the Mode A branch could import external supply.
\end{proof}

\begin{theorem}[AxiomDependencyTuple restricted-supply ledger nonpromotion]
\label{thm:axiom-dependency-tuple-restricted-supply-ledger-nonpromotion}
In Mode B, an accepted $\AxiomDependencyTupleUp$ packet reads the witness row
$W$ only together with the displayed required-supply row $S$. Every named host
conversion, quotient equality, $\mathsf{Classical.choice}$,
$\mathsf{propext}$, ambient classical theorem, or other supply entry in $S$
remains audit supply for the restricted witness and is not promoted to an
internal BEDC proof rule.
\end{theorem}
\begin{proof}
Start from the carrier
$$
A=(M,W,S,H,C,P,N).
$$
The carrier separates the restricted witness coordinate from the supply ledger
coordinate, so the witness cannot be read as though the ledger were absent.

By \autoref{thm:axiom-dependency-tuple-mode-exhaustion}, the Mode B branch is
the restricted-proof branch: $W$ is consumed under the named supply row $S$,
and it is neither a zero-supply proof nor a counterexample socket.

Apply \autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. The full
row $S$ is exposed whenever $W$ is consumed, including every named external
supply entry used by the restricted witness.

\autoref{thm:axiom-dependency-tuple-route-nonexport} prevents the displayed
route from turning $S$ into a rule. Together with
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion}, this confines every
consumer to audit readback of the ledger rather than promotion of the ledger
into BEDC supply.
\end{proof}

\begin{theorem}[AxiomDependencyTuple counterexample socket boundary]
\label{thm:axiom-dependency-tuple-counterexample-socket-boundary}
In Mode C, an accepted $\AxiomDependencyTupleUp$ packet records a
counterexample or socket witness against missing supply through $W$ and $S$.
The packet names the absent host conversion, quotient equality,
$\mathsf{Classical.choice}$, $\mathsf{propext}$, ambient classical theorem, or
other supply row, but it never discharges that supply and never exports it as
a BEDC rule.
\end{theorem}
\begin{proof}
Read the carrier in \autoref{def:axiom-dependency-tuple-carrier}. The witness
row $W$ and required-supply ledger $S$ are visible packet coordinates, and the
route, provenance, naming, and transport rows are separate from them.

Use \autoref{thm:axiom-dependency-tuple-mode-exhaustion}. The Mode C branch is
the counterexample-or-socket branch, so $W$ witnesses refusal or boundary data
against missing supply instead of providing a discharge.

The ledger remains visible by
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. Any named host or
classical material attached to the socket is read as a required-supply row in
$S$, not as a proof principle.

Finally apply \autoref{thm:axiom-dependency-tuple-route-nonexport} and
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion}. The continuation can
only replay the displayed packet rows, and every consumer is exhausted by those
rows, so the counterexample socket cannot discharge the missing supply it
records.
\end{proof}

\begin{theorem}[AxiomDependencyTuple zero-supply row separation]
\label{thm:axiom-dependency-tuple-zero-supply-row-separation}
In Mode A, an accepted $\AxiomDependencyTupleUp$ packet exposes an internal
zero-supply witness in $W$ and an empty external-supply ledger in $S$ before any
consumer route can read the witness. The displayed $\Cont$ row $C$ may replay
that separation, but it cannot insert host conversion, quotient equality,
$\mathsf{Classical.choice}$, $\mathsf{propext}$, or ambient classical supply into
the Mode A branch.
\end{theorem}
\begin{proof}
Begin with the carrier
$$
A=(M,W,S,H,C,P,N).
$$
By \autoref{def:axiom-dependency-tuple-carrier}, the witness row and the
required-supply ledger are separate displayed coordinates.

Apply \autoref{thm:axiom-dependency-tuple-mode-exhaustion}. In the Mode A case,
$W$ is the internal proof witness and $S$ is empty of external supply.

Now use \autoref{thm:axiom-dependency-tuple-supply-ledger-readback} and
\autoref{thm:axiom-dependency-tuple-route-nonexport}. A consumer route must read
the displayed ledger before consuming $W$, and the route has no constructor that
turns an empty ledger into host or classical supply.

Finally, \autoref{thm:axiom-dependency-tuple-consumer-exhaustion} confines every
consumer to the finite rows $M,W,S,H,C,P,N$. Hence Mode A exposes zero supply as
a row property of the packet rather than as a hidden external assumption.
\end{proof}

\begin{theorem}[AxiomDependencyTuple restricted-supply ledger totality]
\label{thm:axiom-dependency-tuple-restricted-supply-ledger-totality}
In Mode B, every restricted-proof witness in an accepted
$\AxiomDependencyTupleUp$ packet is consumed only together with the full
displayed required-supply row $S$. No consumer may read a proper subledger,
erase a named supply entry, or replace $S$ by an implicit host rule.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:axiom-dependency-tuple-carrier}. The Mode B
branch stores the restricted-proof witness in $W$ and its required supply in the
single ledger coordinate $S$.

The mode split is fixed by
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}. In that branch, the witness
is not a zero-supply proof and not a counterexample or socket; it is read as a
restricted proof under the displayed supply row.

Apply \autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. Any route that
consumes $W$ must first expose the same row $S$, including every host conversion,
quotient equality, choice, propositional extensionality, ambient theorem, or
other named supply entry recorded there.

The route and consumer boundaries then close the case. By
\autoref{thm:axiom-dependency-tuple-route-nonexport} and
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion}, the consumer has access
only to the displayed tuple rows, so it cannot silently shrink $S$ or promote a
ledger entry into a BEDC proof rule.
\end{proof}

\begin{theorem}[AxiomDependencyTuple counterexample socket nonexport]
\label{thm:axiom-dependency-tuple-counterexample-socket-nonexport}
In Mode C, every accepted counterexample or socket witness names refused supply
through the witness row $W$ and required-supply ledger $S$, while the route row
$C$, provenance row $P$, and local $\NameCert_{\AxiomDependencyTupleUp}$ row $N$
prevent that named supply from becoming an exported BEDC proof rule.
\end{theorem}
\begin{proof}
Read the carrier definition first. The witness row $W$ and the ledger row $S$
are displayed separately from route, provenance, and naming data.

Apply \autoref{thm:axiom-dependency-tuple-mode-exhaustion}. In Mode C, the
witness coordinate is a counterexample or socket, so the packet records refused
supply rather than a proof discharge.

Next use \autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. Any named
host conversion, quotient equality, $\mathsf{Classical.choice}$,
$\mathsf{propext}$, ambient theorem, or other external supply remains visible in
$S$ when a consumer reads the witness.

Finally combine \autoref{thm:axiom-dependency-tuple-route-nonexport} with
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion}. The route can only
replay the displayed rows, and every consumer is exhausted by those rows, so the
counterexample or socket cannot export the refused supply as a BEDC rule.
\end{proof}

\begin{theorem}[AxiomDependencyTuple BHist row scope]
\label{thm:axiom-dependency-tuple-bhist-row-scope}
For every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$, the seven displayed coordinates are finite
$\BHist$-readable rows. The packet reads mode, witness, required-supply,
transport, continuation, provenance, and naming data from those rows only, and
none of the rows exports host conversion, quotient equality,
$\mathsf{Classical.choice}$, $\mathsf{propext}$, or an ambient classical CIC
theorem as BEDC supply.
\end{theorem}
\begin{proof}
Start with \autoref{def:axiom-dependency-tuple-carrier}. The carrier is a
finite $\BHist$ packet, and the displayed packet coordinates are exactly
$M,W,S,H,C,P,N$.

The earlier obligation rows already describe what each coordinate can expose.
Use \autoref{thm:axiom-dependency-tuple-namecert-obligations} for carrier
admission and local naming, \autoref{thm:axiom-dependency-tuple-mode-exhaustion}
for the three mode rows, and
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback} for the required
supply row.

It remains to exclude hidden export. By
\autoref{thm:axiom-dependency-tuple-route-nonexport} and
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion}, a consumer can only
replay the displayed finite coordinates. Thus every named host or classical
dependency remains a ledger entry in $S$, never a BEDC proof rule exported by a
row of $A$.
\end{proof}

\begin{theorem}[AxiomDependencyTuple hsame and Cont scope]
\label{thm:axiom-dependency-tuple-hsame-cont-scope}
In an accepted $\AxiomDependencyTupleUp$ carrier $A=(M,W,S,H,C,P,N)$, the
transport row $H$ and continuation row $C$ preserve the separation between the
mode row $M$, witness row $W$, and required-supply ledger $S$. Componentwise
$\hsame$ transport and displayed $\Cont$ replay may carry the same tuple to a
consumer, but they do not identify a witness with its supply ledger, erase a
mode distinction, or create an implicit host rule.
\end{theorem}
\begin{proof}
Read $H$ from \autoref{def:axiom-dependency-tuple-carrier}. Its role is
componentwise $\hsame$ transport for the mode, witness, required-supply, route,
provenance, and naming rows, so transport is indexed by the displayed
coordinates rather than by an ambient equality principle.

Read $C$ next. The continuation row records the displayed routes by which a
consumer reads the mode, witness, and required-supply ledger. Apply
\autoref{thm:axiom-dependency-tuple-route-nonexport}: a route replays the
existing coordinates and has no constructor for another mode or an internal
host discharge.

The separation is stable in all three cases. Mode A keeps the empty supply row
separate by \autoref{thm:axiom-dependency-tuple-zero-supply-row-separation};
Mode B keeps the full ledger visible by
\autoref{thm:axiom-dependency-tuple-restricted-supply-ledger-totality}; Mode C
keeps the refused supply nonexported by
\autoref{thm:axiom-dependency-tuple-counterexample-socket-nonexport}. Hence
$H$ and $C$ transport and replay the separation instead of collapsing it.
\end{proof}

\begin{theorem}[AxiomDependencyTuple Pkg and NameCert scope]
\label{thm:axiom-dependency-tuple-pkg-namecert-scope}
For every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$, the provenance row $P$ and local naming row $N$ package
the same finite tuple as the $\NameCert_{\AxiomDependencyTupleUp}$ surface.
They cite the dependency-map, audit-map, discharge-socket, $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows without internalizing host conversion,
$\mathsf{Quot.sound}$, $\mathsf{Classical.choice}$, $\mathsf{propext}$, or
ambient classical theorems.
\end{theorem}
\begin{proof}
Project $P$ and $N$ from the carrier definition. The provenance row is a
$\Pkg$ row over the named chapters and BEDC kernel rows, while $N$ is the local
$\NameCert_{\AxiomDependencyTupleUp}$ row for the same finite packet.

The NameCert surface is fixed by
\autoref{thm:axiom-dependency-tuple-namecert-obligations}. It admits exactly
the carrier, mode classifier, witness transport, required-supply ledger,
displayed route readback, provenance, and local naming obligations already
present in $A$.

Finally combine \autoref{thm:axiom-dependency-tuple-bhist-row-scope} with
\autoref{thm:axiom-dependency-tuple-hsame-cont-scope}. The tuple rows are
finite and $\BHist$-readable, while transport and continuation preserve the
mode, ledger, and witness separation. Therefore $P$ and $N$ package the tuple
as a NameCert surface and do not turn any named host or classical dependency
into internal BEDC supply.
\end{proof}

\begin{theorem}[AxiomDependencyTuple root-unblock spine]
\label{thm:axiom-dependency-tuple-root-unblock-spine}
For every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$, the public dependency-tuple surface is exactly the joint
reading of the following rows over the displayed coordinates: mode exhaustion
for $M$, supply-ledger readback for $S$, route nonexport for $C$, consumer
exhaustion for the whole tuple, and primitive scope for the $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows. No additional root-unblock datum is
available outside these rows.
\end{theorem}
\begin{proof}
Start with \autoref{def:axiom-dependency-tuple-carrier}. The only carrier
coordinates are
$$
M,\ W,\ S,\ H,\ C,\ P,\ N.
$$

The root-unblock spine is read coordinate by coordinate. Use
\autoref{thm:axiom-dependency-tuple-mode-exhaustion} for $M$,
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback} for $S$,
\autoref{thm:axiom-dependency-tuple-route-nonexport} for $C$, and
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion} for the consumer
boundary of the full tuple.

It remains to account for primitive scope. This is exactly the content of
\autoref{thm:axiom-dependency-tuple-bhist-row-scope},
\autoref{thm:axiom-dependency-tuple-hsame-cont-scope}, and
\autoref{thm:axiom-dependency-tuple-pkg-namecert-scope}. These rows exhaust the
available $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ interfaces, so the
public dependency tuple is the conjunction of the displayed rows and nothing
external to the carrier.
\end{proof}

\begin{theorem}[AxiomDependencyTuple mode-ledger priority]
\label{thm:axiom-dependency-tuple-mode-ledger-priority}
Every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$ is consumed in mode-ledger order. In Mode A the consumer
reads the empty required-supply row before using the zero-supply witness. In
Mode B the consumer reads the displayed supply ledger before witness
consumption. In Mode C the consumer reads the counterexample or socket row as a
refusal of discharge before any attempted internal proof use.
\end{theorem}
\begin{proof}
Project the carrier and split by the mode row $M$. By
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}, the split has exactly the
three displayed cases.

In Mode A, apply
\autoref{thm:axiom-dependency-tuple-zero-supply-row-separation}. The ledger row
is empty as external supply and remains separate from the zero-supply witness,
so readback sees the empty ledger first.

In Mode B, apply
\autoref{thm:axiom-dependency-tuple-restricted-supply-ledger-totality}. The
restricted witness is not consumed until the required-supply ledger has been
displayed as the exact supply row for that witness.

In Mode C, apply
\autoref{thm:axiom-dependency-tuple-counterexample-socket-nonexport}. The
counterexample or socket row is read as a boundary witness, so the route records
refusal before any attempted discharge.
\end{proof}

\begin{theorem}[AxiomDependencyTuple consumer readiness]
\label{thm:axiom-dependency-tuple-consumer-readiness}
Downstream audit-map consumers may cite
\autoref{thm:axiom-dependency-tuple-root-unblock-spine},
\autoref{thm:axiom-dependency-tuple-mode-ledger-priority}, and the existing
scope rows of this chapter as the complete $\AxiomDependencyTupleUp$
root-unblock package. The package exports no host conversion,
$\mathsf{Quot.sound}$, $\mathsf{Classical.choice}$, $\mathsf{propext}$, or
ambient classical theorem as BEDC supply.
\end{theorem}
\begin{proof}
The spine theorem identifies the whole public surface with the displayed
carrier rows. The mode-ledger theorem fixes the order in which those rows are
read by any consumer.

The remaining cited scope rows are
\autoref{thm:axiom-dependency-tuple-bhist-row-scope},
\autoref{thm:axiom-dependency-tuple-hsame-cont-scope}, and
\autoref{thm:axiom-dependency-tuple-pkg-namecert-scope}. Together they show that
the primitive interfaces remain finite, componentwise, routed, packaged, and
locally named.

Finally use \autoref{thm:axiom-dependency-tuple-route-nonexport} and
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion}. A downstream
audit-map consumer can replay the tuple and its order of use, but cannot turn a
ledger entry naming host conversion, quotient equality, choice, propositional
extensionality, or an ambient classical theorem into exported BEDC proof
supply.
\end{proof}

\begin{theorem}[AxiomDependencyTuple audit-map row coverage]
\label{thm:axiom-dependency-tuple-audit-map-row-coverage}
For every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$, every downstream audit-map read of $A$ is covered by
exactly the displayed mode row, witness row, supply ledger row, componentwise
transport row, continuation route row, provenance row, and local
$\NameCert_{\AxiomDependencyTupleUp}$ row. No audit-map row outside
$M,W,S,H,C,P,N$ is required to replay the tuple.
\end{theorem}
\begin{proof}
Start with the carrier definition and the local NameCert obligations. By
\autoref{def:axiom-dependency-tuple-carrier} and
\autoref{thm:axiom-dependency-tuple-namecert-obligations}, the admitted packet
has exactly the displayed carrier, classifier, witness-transport,
required-supply, route-readback, provenance, and naming obligations.

The mode and ledger coverage are then fixed by
\autoref{thm:axiom-dependency-tuple-mode-exhaustion} and
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback}. These results
force every consumer read to begin with the three mode cases and the visible
required-supply row $S$.

The remaining public rows are stable under the routing discipline. Apply
\autoref{thm:axiom-dependency-tuple-route-nonexport},
\autoref{thm:axiom-dependency-tuple-root-unblock-spine}, and
\autoref{thm:axiom-dependency-tuple-consumer-readiness}: continuation reads
only replay displayed coordinates, the root-unblock spine names no extra row,
and the consumer package exports no host or classical supply.

Finally, the primitive row scope is exhausted by
\autoref{thm:axiom-dependency-tuple-bhist-row-scope},
\autoref{thm:axiom-dependency-tuple-hsame-cont-scope}, and
\autoref{thm:axiom-dependency-tuple-pkg-namecert-scope}. Thus every
downstream audit-map read is covered by the seven listed rows and by no
ambient interface.
\end{proof}

\begin{theorem}[AxiomDependencyTuple dependency-map soundness]
\label{thm:axiom-dependency-tuple-dependency-map-soundness}
Every downstream dependency-map read of an accepted
$\AxiomDependencyTupleUp$ carrier $A=(M,W,S,H,C,P,N)$ preserves the displayed
mode discipline. Mode A reads an empty $S$ before the zero-supply witness,
Mode B exposes $S$ before the restricted witness $W$, and Mode C reads the
counterexample or socket as refusal rather than as promoted host supply.
\end{theorem}
\begin{proof}
Split by the mode coordinate. The split is exhaustive by
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}, and its consumer order is
fixed by \autoref{thm:axiom-dependency-tuple-mode-ledger-priority}.

In Mode A, use
\autoref{thm:axiom-dependency-tuple-zero-supply-row-separation}. The ledger
$S$ is empty of external supply and is read separately before the internal
zero-supply witness in $W$.

In Mode B, use
\autoref{thm:axiom-dependency-tuple-restricted-supply-ledger-totality}. The
restricted witness cannot be consumed until the full displayed supply ledger
$S$ has been exposed, so no subledger or implicit host rule replaces it.

In Mode C, use
\autoref{thm:axiom-dependency-tuple-counterexample-socket-nonexport}. The
counterexample or socket names refused supply through $W$ and $S$, while
$C,P,N$ prevent that named supply from becoming an exported BEDC proof rule.

The consumer boundary closes the dependency-map claim. By
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback},
\autoref{thm:axiom-dependency-tuple-route-nonexport}, and
\autoref{thm:axiom-dependency-tuple-consumer-readiness}, all three reads keep
ledger exposure ahead of witness consumption and refuse every promotion of
host conversion, quotient equality, choice, propositional extensionality, or
ambient classical supply.
\end{proof}

\begin{theorem}[AxiomDependencyTuple public interface exactness]
\label{thm:axiom-dependency-tuple-public-interface-exactness}
The public interface exported by $\AxiomDependencyTupleUp$ to audit-map
consumers is exactly the carrier of
\autoref{def:axiom-dependency-tuple-carrier} together with the row coverage of
\autoref{thm:axiom-dependency-tuple-audit-map-row-coverage} and the
dependency-map soundness of
\autoref{thm:axiom-dependency-tuple-dependency-map-soundness}. It exports no
$\mathsf{Quot.sound}$, $\mathsf{Classical.choice}$, $\mathsf{propext}$, host
conversion, or ambient classical theorem.
\end{theorem}
\begin{proof}
The carrier supplies the public data. Its coordinates are precisely
$M,W,S,H,C,P,N$, and \autoref{thm:axiom-dependency-tuple-namecert-obligations}
identifies the local NameCert obligations attached to those coordinates.

The two consumer-facing surfaces are the row coverage and soundness results.
The first says that audit-map consumers read only the displayed seven rows;
the second says that dependency-map consumers preserve the mode-ledger
discipline in Modes A, B, and C.

It remains to exclude extra public exports. Apply
\autoref{thm:axiom-dependency-tuple-route-nonexport},
\autoref{thm:axiom-dependency-tuple-root-unblock-spine}, and
\autoref{thm:axiom-dependency-tuple-consumer-readiness}. Routes replay the
carrier, the spine has no additional root-unblock datum, and the consumer
package refuses every host conversion or classical theorem as BEDC supply.

Thus the public interface is the carrier plus these two audit surfaces, with
no quotient equality, choice, propositional extensionality, host conversion,
or ambient classical theorem exported alongside it.
\end{proof}

\closureat{AxiomDependencyTupleUp}{seedStr}
\closureat{AxiomDependencyTupleUp}{obligationStr}

\begin{closurestatus}{\AxiomDependencyTupleUp}
  \constructivestory{An $\AxiomDependencyTupleUp$ packet is generated from a three-mode row, a proof, restricted-proof, counterexample, or socket witness row, a required-supply ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:axiom-dependency-tuple-carrier}, \autoref{thm:axiom-dependency-tuple-namecert-obligations}, \autoref{thm:axiom-dependency-tuple-mode-exhaustion}, \autoref{thm:axiom-dependency-tuple-supply-ledger-readback}, \autoref{thm:axiom-dependency-tuple-route-nonexport}, \autoref{thm:axiom-dependency-tuple-consumer-exhaustion}, \autoref{thm:axiom-dependency-tuple-zero-supply-mode-soundness}, \autoref{thm:axiom-dependency-tuple-restricted-supply-ledger-nonpromotion}, \autoref{thm:axiom-dependency-tuple-counterexample-socket-boundary}, \autoref{thm:axiom-dependency-tuple-zero-supply-row-separation}, \autoref{thm:axiom-dependency-tuple-restricted-supply-ledger-totality}, \autoref{thm:axiom-dependency-tuple-counterexample-socket-nonexport}, \autoref{thm:axiom-dependency-tuple-bhist-row-scope}, \autoref{thm:axiom-dependency-tuple-hsame-cont-scope}, \autoref{thm:axiom-dependency-tuple-pkg-namecert-scope}, \autoref{thm:axiom-dependency-tuple-root-unblock-spine}, \autoref{thm:axiom-dependency-tuple-mode-ledger-priority}, \autoref{thm:axiom-dependency-tuple-consumer-readiness}, \autoref{thm:axiom-dependency-tuple-audit-map-row-coverage}, \autoref{thm:axiom-dependency-tuple-dependency-map-soundness}, and \autoref{thm:axiom-dependency-tuple-public-interface-exactness} bind the finite dependency-tuple carrier, mode exhaustion, ledger exactness, route non-export, consumer exhaustion, the three per-mode obligation rows, the three row-level separation rows, the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ primitive scope, the root-unblock spine, the consumer read order, and the exact public audit-map interface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not enumerate all classical CIC claims, internalize host conversion, quotient equality, choice, propositional extensionality, or ambient classical CIC theorem supply, give Lean verification, or bridge check the tuple.}
  \upgradepath{Public closure next requires Lean verification of the public consumer interface and a bridge check for the scoped tuple.}
\end{closurestatus}
