\chapter{A Concrete Naming Certificate for $\MetaCICIdentityUp$}
\label{ch:concrete-instances-metacicidentity-namecert}
\origin{ai}

The $\MetaCICIdentityUp$ packet realizes the framing principle of \autoref{ch:bedc-is-its-own-theory} as a finite NameCert surface. It sits beside the audit-map family certificate of \autoref{ch:concrete-instances-auditmapfamily-namecert} and the GroundCompiler audit-map packet of \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}: those siblings classify audit rows and compiler-facing evidence, while this chapter names the identity packet that lets a consumer read BEDC.MetaCIC through its own substrate commitments without treating classical CIC as a defining parent theory.

\begin{definition}[MetaCIC identity carrier]
\label{def:metacic-identity-carrier}
A $\MetaCICIdentityUp$ carrier is a finite $\BHist$ packet
$$
I=(G,E,R,A,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the closed-generator inventory row, listing the internal finite constructors for the term-level and certificate-level carriers used by BEDC.MetaCIC;
\item $E$ is the literal AST equality row, recording that internal type identity is read as displayed syntactic equality rather than as conversion through an external reduction theory;
\item $R$ is the structural recursor authorization row, naming only the eliminators supplied by the closed generators in $G$;
\item $A$ is the strict axiom-purity witness row, recording zero dependency on choice, quotient soundness, propositional extensionality, or any other undisplayed axiom route;
\item $B$ is the apophatic boundary socket, recording every request beyond $G,E,R,A$ as external supply rather than as a hidden internal theorem;
\item $H$ stores componentwise $\hsame$ transports for $G,E,R,A,B$ and the local naming rows;
\item $C$ stores finite $\Cont$ routes by which consumers read the five commitment rows, the transports, package provenance, and local naming row;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:bedc-is-its-own-theory}, \autoref{ch:concrete-instances-auditmapfamily-namecert}, \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\MetaCICIdentityUp}$ row.
\end{enumerate}
The carrier is an identity certificate for BEDC.MetaCIC's own displayed substrate. It is not a comparison theorem against classical CIC and does not import any conversion, quotient, extensionality, or choice principle from a neighbouring calculus.
\end{definition}
\leanchecked{BEDC.Derived.MetaCICIdentityUp.MetaCICIdentityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[MetaCIC identity NameCert obligations]
\label{thm:metacic-identity-namecert-obligations}
The local $\NameCert_{\MetaCICIdentityUp}$ surface for \autoref{def:metacic-identity-carrier} consists of five finite rows: carrier admission for $I$; classifier stability for the closed-generator inventory, literal AST equality, structural recursor authorization, strict axiom-purity witness, and apophatic boundary socket; boundary exactness for every read outside those five commitment rows; $\Pkg$ provenance over $G,E,R,A,B,H,C$; and local naming exactness for $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection of the finite tuple $I$. The generator, equality, recursor, purity, boundary, transport, continuation, provenance, and naming coordinates are all displayed rows of the same $\BHist$ packet.

Classifier stability is componentwise. Transport through $H$ preserves the closed-generator inventory, keeps literal equality attached to the same AST row, keeps recursor authorization local to the displayed constructors, and keeps the strict-purity witness attached to the same audit boundary.

The boundary row handles the remaining reads. If a consumer asks for conversion equality, quotient-of-germs equality, extensionality, choice, or a host theorem outside the displayed substrate commitments, the route lands in $B$ rather than in a new internal theorem row.

The package and naming rows then repack exactly those finite coordinates. Thus the obligation surface is the five-row NameCert surface for the identity packet itself.
\end{proof}

\begin{theorem}[MetaCIC identity boundary non-escape]
\label{thm:metacic-identity-boundary-nonescape}
For an accepted $\MetaCICIdentityUp$ carrier $I=(G,E,R,A,B,H,C,P,N)$, every consumer read of BEDC.MetaCIC's identity factors through the closed-generator inventory $G$, literal AST equality row $E$, structural recursor authorization $R$, strict axiom-purity witness $A$, apophatic boundary socket $B$, and structural rows $H,C,P,N$. A read outside those rows remains boundary data in $B$ and is not exported as conversion equality, quotient soundness, propositional extensionality, choice, or a parent-theory relation to classical CIC.
\end{theorem}
\begin{proof}
Read the consumer request through the finite routes in $C$. The positive routes land in the generator, equality, recursor, purity, transport, provenance, and naming rows displayed by the carrier.

For a request outside those coordinates, no row of $I$ supplies the requested principle. The apophatic boundary socket $B$ is the only classifier-visible destination for that request.

Boundary exactness then prevents a boundary entry from being reclassified as a theorem of the substrate. The identity packet therefore exports only the displayed BEDC.MetaCIC commitments and keeps comparison-facing or host-theoretic supply outside the internal carrier.
\end{proof}

\begin{theorem}[MetaCIC identity comparison is secondary]
\label{thm:metacic-identity-comparison-secondary}
Let $I=(G,E,R,A,B,H,C,P,N)$ be an accepted $\MetaCICIdentityUp$ carrier. Any comparison with classical CIC, audit-map methodology, or GroundCompiler audit evidence may read $I$ only after the five identity rows $G,E,R,A,B$ have already been fixed. Such a comparison can diagnose shared syntax, differing equality principles, differing axiom dependencies, or external sockets, but it cannot define the identity of BEDC.MetaCIC or add a new substrate commitment to $I$.
\end{theorem}
\begin{proof}
Project the carrier. The identity rows $G,E,R,A,B$ are displayed before the transport, route, package, and naming rows that expose the packet to downstream consumers.

Use the audit-map family and GroundCompiler audit-map chapters only as consumer contexts. They may inspect finite rows through $C,P,N$, but their own audit surfaces do not supply another generator, equality rule, recursor principle, purity witness, or internal theorem row for $I$.

Finally apply boundary non-escape. If a comparison requests a classical conversion rule, extensionality principle, quotient principle, choice principle, or parent-theory relation, the request is recorded in $B$. Therefore comparison remains diagnostic and secondary to the displayed identity packet.
\end{proof}

\closureat{MetaCICIdentityUp}{seedStr}

\begin{closurestatus}{\MetaCICIdentityUp}
  \constructivestory{A $\MetaCICIdentityUp$ packet is generated from closed-generator inventory, literal AST equality, structural recursor authorization, strict axiom-purity witness, apophatic boundary socket, componentwise $\hsame$ transports, finite $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-identity-carrier}, \autoref{thm:metacic-identity-namecert-obligations}, \autoref{thm:metacic-identity-boundary-nonescape}, and \autoref{thm:metacic-identity-comparison-secondary} define the finite identity packet, its NameCert obligations, its non-escape boundary, and its secondary comparison discipline.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close a Lean implementation, a public bridge, a classical CIC embedding, a conversion rule, quotient soundness, propositional extensionality, or choice.}
  \upgradepath{Obligation closure requires binding the identity packet obligations to concrete generator, AST equality, recursor, strict-purity, apophatic boundary, transport, route, provenance, and local naming rows.}
\end{closurestatus}
