\chapter{A Concrete Naming Certificate for $\BedcSelfTheoryUp$}
\label{ch:concrete-instances-bedcselftheory-namecert}
\origin{human}

The $\BedcSelfTheoryUp$ packet realizes the identity principle of \autoref{ch:bedc-is-its-own-theory} as a finite NameCert surface. It is not a new metatheory above BEDC.MetaCIC. It records the finite rows by which the five defining commitments of that chapter are made available to downstream audit consumers: closed generators, literal AST equality, structural recursor locality, strict axiom-purity reporting, and apophatic external boundaries. Horizontally, it reads the accepted-theorem audit face of \autoref{ch:concrete-instances-kernel-audit-witness-namecert}, the legal eliminator-call discipline of \autoref{ch:concrete-instances-authorizedrecursor-namecert}, the audit-gate boundary of \autoref{ch:concrete-instances-auditgateboundary-namecert}, and the external-socket naming discipline of \autoref{ch:concrete-instances-apophaticname-namecert}.

\begin{definition}[BEDC self-theory commitment carrier]
\label{def:bedc-self-theory-commitment-carrier}
A $\BedcSelfTheoryUp$ carrier is a finite $\BHist$ packet
$$
S=(G,E,R,A,X,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the closed-generator row, naming the finite inductive carrier inventory read as BEDC.MetaCIC substrate data;
\item $E$ is the literal AST equality row, recording that type comparison for the packet is the displayed syntactic equality route and not an external conversion principle;
\item $R$ is the structural recursor row, exposing the generator-local eliminators and their constructor-indexed branch discipline;
\item $A$ is the strict axiom-purity row, reading the source-token and proof-ancestry audit boundary through the finite audit gates;
\item $X$ is the apophatic external-boundary row, recording named sockets, setup fields, and GAP positions as visible external supply rather than hidden substrate content;
\item $L$ is the self-theory ledger row, aligning the five commitments with the chapter identity of \autoref{ch:bedc-is-its-own-theory};
\item $H$ records componentwise $\hsame$ transports for generator, equality, recursor, audit, apophatic, ledger, route, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read each commitment without replacing it by an ambient host principle;
\item $P$ is the $\Pkg$ provenance over $\BHist$, closed generators, literal equality, authorized recursors, audit gates, apophatic names, $\hsame$, $\Cont$, and local NameCert rows;
\item $N$ is the local $\NameCert_{\BedcSelfTheoryUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through the displayed tuple $G,E,R,A,X,L,H,C,P,N$.
\end{definition}

\begin{theorem}[BEDC self-theory NameCert obligations]
\label{thm:bedc-self-theory-namecert-obligations}
For the carrier of \autoref{def:bedc-self-theory-commitment-carrier}, the local $\NameCert_{\BedcSelfTheoryUp}$ surface consists of five finite commitments: closed-generator admission for $G$, literal-equality exactness for $E$, generator-local recursor authorization for $R$, strict audit visibility for $A$, and apophatic external-boundary visibility for $X$. The ledger, transport, continuation, provenance, and local naming rows $L,H,C,P,N$ bind these commitments as one finite packet and add no additional substrate principle.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:bedc-self-theory-commitment-carrier}. The tuple exposes the generator, equality, recursor, audit, apophatic, ledger, transport, route, provenance, and naming rows as finite coordinates.

The first three commitments are internal substrate commitments. The closed-generator row $G$ lists only displayed inductive carriers, the equality row $E$ records literal AST comparison, and the recursor row $R$ cites only generator-local eliminators whose branch discipline is already visible in the authorized-recursion surface of \autoref{ch:concrete-instances-authorizedrecursor-namecert}.

The audit and apophatic commitments are boundary commitments. The row $A$ is read through the audit-gate packet of \autoref{ch:concrete-instances-auditgateboundary-namecert}, while $X$ is read through the external-name discipline of \autoref{ch:concrete-instances-apophaticname-namecert}. Thus purity reports and external supplies remain visible rows, not hidden assumptions.

Finally $L,H,C,P,N$ package the same five commitments. They align the packet with \autoref{ch:bedc-is-its-own-theory}, transport and replay the displayed rows, record provenance through the neighboring NameCert surfaces, and expose local naming without adding a sixth commitment.
\end{proof}

\begin{theorem}[BEDC self-theory closed generator boundary]
\label{thm:bedc-self-theory-closed-generator-boundary}
Every accepted $\BedcSelfTheoryUp$ carrier reads BEDC.MetaCIC objects through the closed-generator row $G$ and the literal-equality row $E$. A downstream consumer cannot use the packet to import an unlisted constructor, a quotient representative, a host semantic equivalence, or a conversion rule not displayed by the carrier.
\end{theorem}
\begin{proof}
Let an accepted carrier be $S=(G,E,R,A,X,L,H,C,P,N)$. The object-facing rows are $G$ and $E$: $G$ names the finite constructor inventory, and $E$ names the syntactic equality route used when the packet compares type-level data.

The remaining rows cannot enlarge this inventory. Recursor access in $R$ consumes the same generator row, audit access in $A$ reports proof and source boundaries, and apophatic access in $X$ records external supply as external.

Transport, continuation, provenance, ledger, and naming rows preserve the displayed packet. Since none of $H,C,P,L,N$ supplies a constructor, quotient representative, host semantic equivalence, or extra conversion rule, the closed-generator boundary is exactly the displayed one.
\end{proof}

\begin{theorem}[BEDC self-theory structural recursor locality]
\label{thm:bedc-self-theory-structural-recursor-locality}
Every recursor read exported by an accepted $\BedcSelfTheoryUp$ carrier is local to the closed generator named by $G$ and the recursor row $R$. It exports no induction principle over an arbitrary semantic domain, no unchecked motive, no omitted branch, and no recursive route outside the displayed structural eliminator.
\end{theorem}
\begin{proof}
The row $R$ is interpreted together with $G$. Thus any exported eliminator is tied to the constructor inventory named by the same carrier.

Motive and branch discipline is inherited through the authorized-recursion surface cited in the provenance row $P$. A consumer may inspect the recursor only through the displayed route $C$, so the motive, branch package, and structural descent ledger remain part of the same finite read.

No other row contains an induction principle. The audit row reports boundaries, the apophatic row names external supply as external, and $H,L,N$ transport, align, and name the same packet. Hence recursor access remains generator-local.
\end{proof}

\begin{theorem}[BEDC self-theory non-escape]
\label{thm:bedc-self-theory-nonescape}
Every public read of an accepted $\BedcSelfTheoryUp$ packet factors through
$$
G,E,R,A,X,L,H,C,P,N.
$$
It exports no hidden classical-CIC parent theory, no ambient conversion rule, no undisplayed axiom dependency, no unrestricted recursion principle, and no external socket promoted to internal theorem content.
\end{theorem}
\begin{proof}
The packet inventory is finite and displayed in \autoref{def:bedc-self-theory-commitment-carrier}. A public read can project one of the five commitment rows or one of the rows that transports, routes, packages, aligns, or names them.

Classical-CIC parentage and ambient conversion are blocked by $G$ and $E$. The carrier names BEDC.MetaCIC by its own generator and equality rows rather than by a subtractive comparison with another calculus.

Undisplayed axioms and unrestricted recursion are blocked by $A$ and $R$. The audit row exposes source and proof-ancestry boundaries, and the recursor row remains tied to its closed generator and branch discipline.

External supply is blocked from becoming internal content by $X$. Since the apophatic row keeps sockets, setup fields, and GAP positions visible as boundary rows, no consumer can recover an internal theorem from them without a separate displayed route.

Therefore the self-theory packet is a finite naming certificate for the five commitments and not an escape route to unlisted principles.
\end{proof}

\closureat{BedcSelfTheoryUp}{seedStr}

\begin{closurestatus}{\BedcSelfTheoryUp}
  \constructivestory{A $\BedcSelfTheoryUp$ packet is generated from closed-generator inventory, literal AST equality, structural recursor locality, strict audit-purity rows, apophatic boundary rows, a self-theory ledger, displayed transports, continuation routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bedc-self-theory-commitment-carrier}, \autoref{thm:bedc-self-theory-namecert-obligations}, \autoref{thm:bedc-self-theory-closed-generator-boundary}, \autoref{thm:bedc-self-theory-structural-recursor-locality}, and \autoref{thm:bedc-self-theory-nonescape} bind BEDC.MetaCIC self-theory identity as a finite NameCert packet over five displayed commitments.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not prove a Lean-side carrier, a bridge theorem, a global completeness theorem for BEDC.MetaCIC, a semantic comparison theorem with classical CIC, or any external principle.}
  \upgradepath{Obligation closure requires checked carrier admission, five-commitment NameCert obligations, closed-generator boundary, structural recursor locality, and non-escape for the same finite packet.}
\end{closurestatus}
