\chapter{A Concrete Naming Certificate for $\AxiomDependencyMapUp$}
\label{ch:concrete-instances-axiomdependencymap-namecert}
\origin{human}

The $\AxiomDependencyMapUp$ packet turns the dependency-map reading of \autoref{ch:bedc-axiom-dependency-map} into a concrete finite certificate. It sits beside the axiom-query ledger $\AxiomQueryLedgerUp$ of \autoref{ch:concrete-instances-axiomqueryledger-namecert}, the family carrier $\AuditMapFamilyUp$ of \autoref{ch:concrete-instances-auditmapfamily-namecert}, the compiler-facing map $\GroundCompilerAuditMapUp$ of \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, and the cross-map weave $\AuditMapDependencyWeaveUp$ of \autoref{ch:concrete-instances-auditmapdependencyweave-namecert}. Those sibling chapters expose ledger, family, compiler, and dependency-weave rows; this chapter packages the claim-level dependency tuple that a downstream audit-map consumer reads before deciding whether the claim is internal, restricted, or blocked by named supply.

\begin{definition}[Axiom-dependency-map packet]
\label{def:axiom-dependency-map-certificate}
An $\AxiomDependencyMapUp$ packet is a finite $\BHist$ tuple
$$
X=(\Phi,M,W,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $\Phi$ is the claim row naming the classical-looking assertion being inspected against the BEDC substrate;
\item $M$ is the mode row, with one of the three displayed readings internal proof, restricted internal proof, or obstruction with named supply;
\item $W$ is the witness row, carrying the proof term, restricted proof surface, counterexample, refusal, or named socket that justifies the mode;
\item $A$ is the required-axiom-set row, listing the empty supply, restricted-surface condition, or named external supply rows required by the mode;
\item $H$ records componentwise $\hsame$ transport for the claim, mode, witness, required-axiom-set, continuation, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ replay routes by which a consumer replays the claim read, mode classification, witness readback, and required-supply readback;
\item $P$ is the $\Pkg$ provenance over the dependency-map vision, $\AxiomQueryLedgerUp$, $\AuditMapFamilyUp$, $\GroundCompilerAuditMapUp$, $\AuditMapDependencyWeaveUp$, $\hsame$, $\Cont$, and $\NameCert$ source packets;
\item $N$ is the local $\NameCert_{\AxiomDependencyMapUp}$ row.
\end{enumerate}
The packet exports no ambient theorem count, no host proof oracle, no hidden axiom supply, and no permission to treat a blocked or restricted row as an unconditional BEDC theorem.
\end{definition}

\begin{theorem}[Axiom-dependency-map obligations]
\label{thm:axiom-dependency-map-ledger-obligations}
For every $\AxiomDependencyMapUp$ packet
$$
X=(\Phi,M,W,A,H,C,P,N),
$$
the local $\NameCert_{\AxiomDependencyMapUp}$ surface consists exactly of claim exposure, mode exposure, witness exposure, required-axiom-set exposure, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row. Any consumer of $N$ must read the dependency tuple through these eight rows and cannot replace them by prose comparison with classical CIC.
\end{theorem}
\begin{proof}
Project the finite packet of \autoref{def:axiom-dependency-map-certificate}. The rows $\Phi,M,W,A$ expose the claim, the mode assigned to it, the displayed witness for that mode, and the required-supply row.

The rows $H$ and $C$ bind transport and replay. A consumer may move the packet componentwise and replay its reads, but the transport and replay endpoints remain the displayed claim, mode, witness, and required-axiom-set rows.

The provenance and naming rows $P,N$ package the same data as the local $\NameCert$ surface. Since the carrier has no further coordinate, there is no route from $N$ to an ambient theorem count, a host proof oracle, or a hidden supply row.
\end{proof}

\begin{theorem}[Axiom-dependency-map mode exhaustion]
\label{thm:axiom-dependency-map-mode-soundness}
For every accepted $\AxiomDependencyMapUp$ packet
$$
X=(\Phi,M,W,A,H,C,P,N),
$$
the mode row $M$ is exhausted by the three displayed cases: internal proof, restricted internal proof, and obstruction with named supply. In the first case $A$ records empty supply and $W$ records the internal witness; in the second case $A$ records the restricted surface and $W$ records the restricted witness; in the third case $A$ records the named supply and $W$ records the obstruction, refusal, counterexample, or socket row.
\end{theorem}
\begin{proof}
Read the mode row $M$ of the packet. By definition the carrier admits only the three displayed readings, so the case split has exactly those branches.

In the internal-proof branch, the claim row $\Phi$ is paired with a witness row $W$ that supplies the substrate proof and a required-axiom-set row $A$ that records empty supply.

In the restricted-proof branch, the same projection reads $W$ as the restricted witness and $A$ as the restricted-surface condition. The carrier contains no row that erases the restriction.

In the obstruction branch, the witness row records the counterexample, refusal, or socket and $A$ records the named supply. The packet therefore classifies blocked content as visible dependency data rather than as an unconditional theorem.
\end{proof}
\leanchecked{BEDC.Derived.AxiomDependencyMapUp.AxiomDependencyMapModeSoundness}

\begin{theorem}[Axiom-dependency-map query-ledger factorization]
\label{thm:axiom-dependency-map-query-ledger-factorization}
Every downstream audit read that treats an $\AxiomDependencyMapUp$ packet as proof-ancestry data factors through $\AxiomQueryLedgerUp$, $\AuditMapFamilyUp$, $\GroundCompilerAuditMapUp$, or $\AuditMapDependencyWeaveUp$ as named in $P$. In particular, a consumer cannot read the required-axiom-set row $A$ as a strict ancestry verdict unless the replay route in $C$ reaches the corresponding finite ledger, family, compiler, or weave row cited by the provenance package.
\end{theorem}
\begin{proof}
Start with the provenance row $P$. It cites the dependency-map vision, $\AxiomQueryLedgerUp$, $\AuditMapFamilyUp$, $\GroundCompilerAuditMapUp$, and $\AuditMapDependencyWeaveUp$ as the only package sources for query, family, compiler, and dependency-weave reads.

Next read the continuation row $C$. A proof-ancestry consumer must replay from $\Phi$ through the mode and witness rows to the required-axiom-set row $A$, then through the ledger, family, compiler, or weave row named by $P$.

If such a ledger or gate route is absent, the packet still records a claim-level dependency tuple, but not a strict ancestry verdict. The factorization therefore separates dependency-map classification from the finite query ledger that certifies a particular accepted declaration.
\end{proof}

\begin{theorem}[Axiom-dependency-map non-escape]
\label{thm:axiom-dependency-map-boundary}
For every accepted $\AxiomDependencyMapUp$ packet
$$
X=(\Phi,M,W,A,H,C,P,N),
$$
every public read remains inside the displayed claim, mode, witness, required-axiom-set, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The packet cannot turn a restricted row into an unrestricted theorem, a named supply row into internal BEDC content, an obstruction row into a proof, or a claim-level dependency tuple into a hidden host axiom.
\end{theorem}
\begin{proof}
Project the accepted packet as $X=(\Phi,M,W,A,H,C,P,N)$. These are the only rows exported by the carrier.

Mode soundness from \autoref{thm:axiom-dependency-map-mode-soundness} fixes how $M,W,A$ may be read. The internal, restricted, and obstruction branches each keep their own witness and required-supply interpretation.

The factorization result of \autoref{thm:axiom-dependency-map-query-ledger-factorization} binds proof-ancestry reads to the cited ledger, family, compiler, or weave packet. Thus query meaning cannot appear from the local name alone.

Since no further coordinate exists, a consumer has no place from which to obtain unrestricted closure, hidden supply, obstruction discharge, or host-axiom admission. All public reads remain inside the finite packet.
\end{proof}

\begin{theorem}[Axiom-dependency-map required-supply separation]
\label{thm:axiom-dependency-map-required-supply-separation}
For every accepted $\AxiomDependencyMapUp$ packet
$$
X=(\Phi,M,W,A,H,C,P,N),
$$
the required-axiom-set row $A$ separates the three displayed supply modes: empty supply for internal proof, restricted-surface conditions for restricted internal proof, and named external supply for obstruction or socket rows. No downstream consumer may read one supply mode as another through $H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.AxiomDependencyMapUp.AxiomDependencyMapRequiredSupplySeparation}
\begin{proof}
Apply mode soundness from \autoref{thm:axiom-dependency-map-mode-soundness}. The three cases for $M$ pair $W$ and $A$ with empty supply, restricted surface, or named supply respectively.

Next apply the query-ledger factorization theorem \autoref{thm:axiom-dependency-map-query-ledger-factorization}. Any consumer that treats $A$ as proof-ancestry data must replay the corresponding ledger, family, compiler, or weave route named in $P$ and routed by $C$.

Finally use the boundary theorem \autoref{thm:axiom-dependency-map-boundary}. The transport, continuation, provenance, and naming rows preserve the displayed tuple only. Since the packet contains no row that converts one supply mode into another, no consumer can read empty supply, restricted surface, and named external supply interchangeably.
\end{proof}

\begin{theorem}[Axiom-dependency-map restricted-row non-escape]
\label{thm:axiom-dependency-map-restricted-row-nonescape}
For every accepted $\AxiomDependencyMapUp$ packet
$$
X=(\Phi,M,W,A,H,C,P,N),
$$
if the mode row $M$ reads as restricted internal proof, then the witness row $W$ and required-supply row $A$ remain restricted under $H,C,P,N$. They cannot be exported as unconditional BEDC theorems, and the local $\NameCert_{\AxiomDependencyMapUp}$ row exposes only the restricted dependency tuple.
\end{theorem}
\begin{proof}
Start with mode soundness. In the restricted branch, $W$ is a restricted witness and $A$ is the restricted-surface condition; the carrier records no row that erases that condition.

Use query-ledger factorization to inspect any downstream replay. A consumer must pass through the finite ledger, family, compiler, or dependency-weave route named by $P$, so the restricted branch remains tied to the ledger that justifies the restricted reading.

Apply the non-escape boundary. The rows $H,C,P,N$ transport, replay, package, and name the same displayed tuple, and the carrier has no coordinate for unrestricted theorem export. Therefore a restricted proof row remains restricted and cannot be read as an unconditional BEDC theorem.
\end{proof}

\closureat{AxiomDependencyMapUp}{seedStr}

\begin{closurestatus}{\AxiomDependencyMapUp}
  \constructivestory{An $\AxiomDependencyMapUp$ packet is generated from a claim row, a mode row, a witness row, a required-axiom-set row, componentwise $\hsame$ transports, displayed $\Cont$ replay routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:axiom-dependency-map-certificate}, \autoref{thm:axiom-dependency-map-ledger-obligations}, \autoref{thm:axiom-dependency-map-mode-soundness}, \autoref{thm:axiom-dependency-map-query-ledger-factorization}, \autoref{thm:axiom-dependency-map-boundary}, \autoref{thm:axiom-dependency-map-required-supply-separation}, and \autoref{thm:axiom-dependency-map-restricted-row-nonescape} specify the finite claim-level dependency-map packet, mode soundness, ledger factorization, supply separation, restricted-row non-escape, and public boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not enumerate all classical CIC claims, prove global completeness of the dependency map, certify any hidden host proof oracle, close Lean verification, or bridge the packet to an external schema.}
  \upgradepath{Obligation closure requires checked carrier admission, mode classification, witness and required-supply exactness, query-ledger factorization, and non-escape for the displayed packet.}
\end{closurestatus}
