\chapter{A Concrete Naming Certificate for $\AxiomDependencyAuditMapUp$}
\label{ch:concrete-instances-axiom-dependency-audit-map-namecert}
\origin{human}

The $\AxiomDependencyAuditMapUp$ packet realizes the dependency-map vision of \autoref{ch:bedc-axiom-dependency-map} as a finite audit carrier. It sits beside the paper-marker resolution witness of \autoref{ch:concrete-instances-paper-lean-drift-witness-namecert} and the forbidden-host-axiom boundary of \autoref{ch:concrete-instances-forbidden-axiom-ancestry-namecert}: those chapters certify marker resolution and forbidden ancestry refusal, while this chapter packages the mode, witness, and required-axiom rows that make a dependency-map entry readable by a $\NameCert$ consumer.

\begin{definition}[AxiomDependencyAuditMap carrier]
\label{def:axiom-dependency-audit-map-carrier}
An $\AxiomDependencyAuditMapUp$ carrier is a finite $\BHist$ packet
$$
D=(K,M,W,A,L,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $K$ is the audited claim or declaration row whose dependency status is being read;
\item $M$ is the mode row, with one of the displayed readings internal, restricted, or externally supplied;
\item $W$ is the witness row for the selected mode, carrying the internal proof witness, restricted witness, refusal witness, counterexample row, or named socket;
\item $A$ is the required-axiom row, recording empty supply, a restricted-surface condition, or the finite named supply required by the mode;
\item $L$ is the finite audit ledger linking the claim row to the marker-resolution and forbidden-ancestry packets named by provenance;
\item $H$ records componentwise $\hsame$ transport for the claim, mode, witness, required-axiom, ledger, continuation, package, and local naming rows;
\item $C$ records the visible $\Cont$ routes by which a consumer replays the mode read, witness read, required-axiom read, and ledger read;
\item $P$ is the $\Pkg$ provenance over the dependency-map vision, $\PaperLeanDriftWitnessUp$, $\ForbiddenAxiomAncestryUp$, $\AxiomDependencyMapUp$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\AxiomDependencyAuditMapUp}$ row.
\end{enumerate}
The carrier exports no hidden proof oracle, no global theorem census, no host axiom permission, and no conversion from a restricted or supplied row into an unconditional BEDC theorem.
\end{definition}

\begin{theorem}[AxiomDependencyAuditMap mode totality]
\label{thm:axiom-dependency-audit-map-mode-totality}
For every accepted $\AxiomDependencyAuditMapUp$ packet
$$
D=(K,M,W,A,L,H,C,P,N),
$$
the mode row $M$ is exhausted by the three displayed readings internal, restricted, and externally supplied. The internal reading pairs $W$ with an internal witness and $A$ with empty supply; the restricted reading pairs $W$ with a restricted witness and $A$ with the restricted surface; the externally supplied reading pairs $W$ with the refusal, counterexample, or socket row and $A$ with the named finite supply.
\end{theorem}
\begin{proof}
Project the accepted packet and inspect its mode coordinate $M$. The carrier definition lists only the internal, restricted, and externally supplied readings, so the case split has exactly those branches.

In the internal branch, the witness row and required-axiom row are read together: $W$ records the displayed internal witness and $A$ records empty supply.

In the restricted branch, the same projection keeps the restriction visible by pairing $W$ with the restricted witness and $A$ with the restricted surface. No carrier coordinate erases that restriction.

In the externally supplied branch, $W$ records the refusal, counterexample, or socket row, while $A$ records the named finite supply. The packet therefore reports supply as audit data rather than as a BEDC proof.
\end{proof}
\leanchecked{BEDC.Derived.AxiomDependencyAuditMapUp.AxiomDependencyAuditMap\_mode\_totality}

\begin{theorem}[AxiomDependencyAuditMap NameCert obligations]
\label{thm:axiom-dependency-audit-map-namecert-obligations}
For the carrier of \autoref{def:axiom-dependency-audit-map-carrier}, the local $\NameCert_{\AxiomDependencyAuditMapUp}$ surface consists exactly of carrier exposure for $D$, mode totality for $M$, witness exposure for $W$, required-axiom exposure for $A$, finite ledger exposure for $L$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row $N$. Every consumer of $N$ must read the dependency lattice through these rows and cannot replace them by an unrecorded host-kernel comparison.
\end{theorem}
\begin{proof}
Carrier exposure is projection of \autoref{def:axiom-dependency-audit-map-carrier}. The claim, mode, witness, required-axiom, ledger, transport, replay, package, and local naming rows are all visible coordinates of the same finite packet.

Mode totality is supplied by \autoref{thm:axiom-dependency-audit-map-mode-totality}. It fixes how $M,W,A$ may be consumed in the internal, restricted, and externally supplied branches.

The ledger row $L$ links the claim to the paper-marker and forbidden-ancestry packets named by $P$. The transport and continuation rows $H,C$ preserve that link componentwise.

Since the carrier has no coordinate for a host proof oracle or an unrecorded axiom comparison, the local $\NameCert$ surface is exhausted by the displayed dependency rows.
\end{proof}

\begin{theorem}[AxiomDependencyAuditMap non-escape]
\label{thm:axiom-dependency-audit-map-nonescape}
Every public read from an accepted $\AxiomDependencyAuditMapUp$ packet remains inside the displayed claim, mode, witness, required-axiom, ledger, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The packet cannot turn a restricted row into an unrestricted theorem, a required-supply row into internal BEDC content, a refusal row into a proof, or a dependency-map entry into a hidden host axiom.
\end{theorem}
\begin{proof}
Project the packet as $D=(K,M,W,A,L,H,C,P,N)$. These rows are the complete carrier surface.

Apply \autoref{thm:axiom-dependency-audit-map-namecert-obligations}. It requires every consumer to pass through the displayed mode, witness, required-axiom, and ledger rows before reading the local naming certificate.

The mode-totality theorem fixes the interpretation of $M,W,A$ in each branch. The internal, restricted, and externally supplied branches remain disjoint audit readings, and no branch exports the excluded host objects.

Finally replay the packet through $H,C,P,N$. Componentwise transport and package provenance preserve the same finite rows, so there is no route to an unrestricted theorem, hidden supply, proof oracle, or host axiom outside the carrier.
\end{proof}

\closureat{AxiomDependencyAuditMapUp}{seedStr}

\begin{closurestatus}{\AxiomDependencyAuditMapUp}
  \constructivestory{An $\AxiomDependencyAuditMapUp$ packet is generated from an audited claim row, a mode row, a witness row, a required-axiom row, a finite audit ledger, displayed $\hsame$ and $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:axiom-dependency-audit-map-carrier}, \autoref{thm:axiom-dependency-audit-map-mode-totality}, \autoref{thm:axiom-dependency-audit-map-namecert-obligations}, and \autoref{thm:axiom-dependency-audit-map-nonescape} specify the finite dependency-map packet for mode, witness, required-axiom, ledger, and non-escape reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not enumerate all declarations, prove global dependency-map completeness, certify host-kernel proof ancestry, discharge named external supply, or bridge the packet to an external schema.}
  \upgradepath{Obligation closure requires checked carrier admission, mode totality, witness and required-axiom exactness, ledger exposure, and non-escape for the displayed packet.}
\end{closurestatus}
