\chapter{A Concrete Naming Certificate for $\MetaCICIdentityBoundaryUp$}
\label{ch:concrete-instances-metacicidentityboundary-namecert}
\origin{ai}

The $\MetaCICIdentityBoundaryUp$ packet realizes the identity reading of \autoref{ch:bedc-is-its-own-theory} as a finite NameCert boundary for BEDC.MetaCIC. It is placed beside the dependency map of \autoref{ch:concrete-instances-axiomdependencymap-namecert}, the normal-form false exclusion packet of \autoref{ch:concrete-instances-normalfalseexclusion-namecert}, the subject-reduction boundary of \autoref{ch:concrete-instances-metacic-subject-reduction-boundary-namecert}, the closed-normal consistency packet of \autoref{ch:concrete-instances-closed-normal-consistency-namecert}, and the discharge socket of \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}. Those siblings expose dependency, normal endpoint, subject-reduction boundary, consistency endpoint, and discharge-socket rows; this chapter names the identity boundary that keeps those rows visible without importing a classical CIC parent theory.

\begin{definition}[MetaCIC identity-boundary carrier]
\label{def:metacic-identity-boundary-carrier}
A $\MetaCICIdentityBoundaryUp$ carrier is a finite $\BHist$ packet
$$
M=(G,E,R,P,B,L,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the closed-generator row for BEDC.MetaCIC constructors, formation rows, and finite introduction routes;
\item $E$ is the literal AST equality row, reading identity by displayed syntax rather than by quotienting through an external calculus;
\item $R$ is the structural recursor row, exposing the induction and eliminator routes available on the closed generators;
\item $P$ is the strict-purity row, recording that accepted reads cite only displayed generator, equality, recursor, ledger, transport, route, provenance, and naming rows;
\item $B$ is the external-boundary row, recording exactly where a request asks for a classical CIC comparison, a closed subject-reduction theorem, or another nonlocal parent-theory commitment;
\item $L$ is the identity ledger, linking $G,E,R,P,B$ to the five sibling surfaces named above;
\item $H$ records componentwise $\hsame$ transport for all displayed rows;
\item $C$ records the finite $\Cont$ routes by which consumers read the generator, equality, recursor, purity, boundary, ledger, provenance, and local naming rows;
\item $Q$ is the $\Pkg$ provenance over \autoref{ch:bedc-is-its-own-theory}, \autoref{ch:concrete-instances-axiomdependencymap-namecert}, \autoref{ch:concrete-instances-normalfalseexclusion-namecert}, \autoref{ch:concrete-instances-metacic-subject-reduction-boundary-namecert}, \autoref{ch:concrete-instances-closed-normal-consistency-namecert}, \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\MetaCICIdentityBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for a closed subject-reduction theorem, no map from classical CIC into BEDC.MetaCIC, and no hidden axiom supply.
\end{definition}

\begin{definition}[MetaCIC identity-boundary classifier]
\label{def:metacic-identity-boundary-classifier}
Two $\MetaCICIdentityBoundaryUp$ carriers
$$
M=(G,E,R,P,B,L,H,C,Q,N)
$$
and
$$
M'=(G',E',R',P',B',L',H',C',Q',N')
$$
are classifier-equivalent exactly when the closed-generator rows, literal AST equality rows, structural recursor rows, strict-purity rows, external-boundary rows, identity-ledger rows, componentwise transports, continuation routes, provenance rows, and local naming rows agree through the displayed $\hsame$ and $\Cont$ data. The classifier does not compare carriers by semantic equivalence with classical CIC or by any theorem absent from the displayed sibling packets.
\end{definition}

\begin{theorem}[MetaCIC identity-boundary NameCert obligations]
\label{thm:metacic-identity-boundary-namecert-obligations}
For every $\MetaCICIdentityBoundaryUp$ carrier
$$
M=(G,E,R,P,B,L,H,C,Q,N),
$$
the local $\NameCert_{\MetaCICIdentityBoundaryUp}$ surface consists of five finite commitment rows:
\begin{enumerate}
\item closed-generator exposure through $G$;
\item literal AST equality exposure through $E$;
\item structural recursor exposure through $R$;
\item strict-purity exposure through $P$;
\item external-boundary exposure through $B$, with ledger accountability through $L,H,C,Q,N$.
\end{enumerate}
These rows certify the positive identity of BEDC.MetaCIC as its own substrate boundary. They do not certify a closed subject-reduction theorem, a comparison theorem with classical CIC, or any external proof supply.
\end{theorem}
\begin{proof}
Project the finite carrier of \autoref{def:metacic-identity-boundary-carrier}. The rows $G,E,R,P,B$ are the five commitment rows, and $L,H,C,Q,N$ make those commitments inspectable by ledger, transport, replay, provenance, and local naming.

Classifier exactness follows from \autoref{def:metacic-identity-boundary-classifier}. Agreement is checked on the displayed rows only, so an external comparison theorem or missing subject-reduction theorem cannot become part of the classifier.

The NameCert surface is therefore exactly the five displayed commitments plus their structural accountability rows. Since the carrier has no further coordinate, no sixth commitment or hidden parent-theory supply is exported.
\end{proof}

\begin{theorem}[MetaCIC identity-boundary ledger non-escape]
\label{thm:metacic-identity-boundary-ledger-nonescape}
Every consumer read of an accepted $\MetaCICIdentityBoundaryUp$ carrier factors through
$$
G,E,R,P,B,L,H,C,Q,N.
$$
If a route asks for a closed subject-reduction theorem, a semantic embedding into classical CIC, a host equality oracle, or an external axiom dependency not recorded by the sibling dependency-map packet, the request lands in the external-boundary row $B$ and cannot be exported as a theorem row.
\end{theorem}
\begin{proof}
Read the consumer route through $C$. If the route reaches $G,E,R,P,L,H,Q,N$, it remains inside the positive identity packet and its structural accountability rows.

If the route asks for material outside those rows, the carrier offers only $B$ as a boundary coordinate. The ledger row $L$ ties that boundary to the axiom-dependency map, normal false exclusion, subject-reduction boundary, closed-normal consistency, and discharge-socket siblings.

Thus a boundary read remains a boundary read. It cannot be reclassified as closed subject reduction, semantic parenthood, host equality, or an undisplayed axiom dependency.
\end{proof}

\begin{theorem}[MetaCIC identity-boundary sibling independence]
\label{thm:metacic-identity-boundary-sibling-independence}
\independenceWitness{The axiom-dependency-map packet, normal-false-exclusion packet, MetaCIC subject-reduction-boundary packet, closed-normal-consistency packet, and subject-reduction-discharge-socket packet are not bijective to the $\MetaCICIdentityBoundaryUp$ carrier. The dependency map has claim, mode, witness, and supply rows; normal false exclusion has a beta-strong false endpoint row; the subject-reduction boundary has obstruction rows for typed reduction preservation; closed-normal consistency has a positive normal endpoint; and the discharge socket has four discharge-commitment rows. None has exactly the five identity commitments $G,E,R,P,B$ with the identity ledger $L$ and local boundary classifier of \autoref{def:metacic-identity-boundary-classifier}.}
\end{theorem}
\begin{proof}
Compare row inventories. The sibling chapters named in the witness each expose a specialized consumer surface: dependency accounting, normal-endpoint exclusion, subject-reduction obstruction, closed-normal consistency, or four-row discharge sockets.

The identity-boundary carrier instead exposes closed generators, literal AST equality, structural recursors, strict purity, and external-boundary rows as one packet. Its ledger cites the siblings, but citation is not a bijection of carriers.

Therefore a consumer may use the siblings as provenance and boundary context, yet cannot replace this five-commitment identity packet by any one of them or by a product of their visible theorem rows.
\end{proof}

\begin{theorem}[MetaCIC identity-boundary TasteGate follow-up]
\label{thm:metacic-identity-boundary-tastegate-followup}
The Lean-side follow-up for $\MetaCICIdentityBoundaryUp$ must provide a $\ChapterTasteGate$ route whose carrier is nontrivial and field-faithful. In particular, the future `TasteGate.lean' development must supply $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances for the identity-boundary carrier before a checked gate can claim that the packet has more than a vacuous event-flow encoding and that its encoding preserves the five displayed commitment fields.
\end{theorem}
\begin{proof}
The carrier has five named commitment fields and structural rows that must remain distinguishable. A gate that recognizes only an event-flow round trip would not by itself show that the fields $G,E,R,P,B$ are preserved as distinct BEDC commitments.

Nontriviality rules out the empty or singleton reading of the carrier, and field faithfulness records that the encoding reflects the displayed field structure. These are exactly the extra gate rows needed before the identity-boundary packet can be read as a checked TasteGate object.
\end{proof}

\falsifiablePrediction{If a MetaCIC identity-boundary packet is accepted, no consumer route may turn its external-boundary row into a closed subject-reduction theorem without citing a subject-reduction discharge sibling.}

\closureat{MetaCICIdentityBoundaryUp}{seedStr}

\begin{closurestatus}{\MetaCICIdentityBoundaryUp}
  \constructivestory{A $\MetaCICIdentityBoundaryUp$ packet is generated from closed-generator rows, literal AST equality rows, structural recursor rows, strict-purity rows, external-boundary rows, an identity ledger, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-identity-boundary-carrier}, \autoref{def:metacic-identity-boundary-classifier}, \autoref{thm:metacic-identity-boundary-namecert-obligations}, \autoref{thm:metacic-identity-boundary-ledger-nonescape}, \autoref{thm:metacic-identity-boundary-sibling-independence}, and \autoref{thm:metacic-identity-boundary-tastegate-followup} specify the seed carrier, classifier, five-row NameCert surface, non-escape ledger, sibling independence witness, and gate-facing follow-up.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove closed subject reduction, construct a semantic embedding into classical CIC, close the sibling packets, provide Lean-side formal verification, or bridge the packet to an external schema.}
  \upgradepath{Obligation closure requires Lean encoding of the carrier and classifier, checked five-row obligation exposure, ledger non-escape, sibling independence, and a TasteGate route with Nontrivial and FieldFaithful instances.}
\end{closurestatus}
