\chapter{A Concrete Naming Certificate for $\RegularCauchyFiniteObservationRouteUp$}
\label{ch:concrete-instances-regular-cauchy-finite-observation-route-namecert}
\origin{ai}

The $\RegularCauchyFiniteObservationRouteUp$ packet names the concrete route from regular-Cauchy finite windows to the observation budget and the $\RealUp$ seal used by \autoref{ch:visions-real-completeness}. It reads its finite window side through \autoref{ch:concrete-instances-streamname-namecert}, its diagonal schedule through \autoref{ch:concrete-instances-stationarypartitiondiagonal-namecert}, and its budget side through \autoref{ch:concrete-instances-real-observation-budget-namecert}. The packet keeps these sibling surfaces in one route rather than replacing any of them.

\begin{definition}[Regular-Cauchy finite observation route carrier]
\label{def:regular-cauchy-finite-observation-route-carrier}
A $\RegularCauchyFiniteObservationRouteUp$ carrier is a finite $\BHist$ packet
$$
Z=(Q,W,D,R,B,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the finite regular-Cauchy request row, including the requested precision and the selected diagonal index;
\item $W$ is the finite $\StreamNameUp$ window row read by the route;
\item $D$ is the $\DyadicRatCoreUp$ observation ledger for the window;
\item $R$ is the $\RegSeqRatUp$ handoff row obtained from the finite observations;
\item $B$ is the $\RealObservationBudgetUp$ row admitting the same window, dyadic ledger, handoff, and seal request;
\item $S$ is the $\RealUp$ seal row reached only after the budget row has been displayed;
\item $H$ stores componentwise $\hsame$ transports for $Q,W,D,R,B,S,C,P,N$;
\item $C$ stores the $\Cont$ routes reading the request, window, dyadic ledger, regular-rational handoff, observation budget, seal row, provenance, and local name;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealObservationBudgetUp$, $\RealUp$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RegularCauchyFiniteObservationRouteUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient streams, host real equality, hidden limit selection, unbounded observation schedules, or a $\RealUp$ seal read outside the displayed budget.
\end{definition}

\begin{theorem}[Regular-Cauchy finite observation route obligations]
\label{thm:regular-cauchy-finite-observation-route-obligations}
For the carrier of \autoref{def:regular-cauchy-finite-observation-route-carrier}, the local $\NameCert_{\RegularCauchyFiniteObservationRouteUp}$ surface consists exactly of carrier admission, finite $\StreamNameUp$ window admission, $\DyadicRatCoreUp$ observation readback, $\RegSeqRatUp$ handoff, $\RealObservationBudgetUp$ budget admission, $\RealUp$ seal handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row.
\end{theorem}
\begin{proof}
Carrier admission is projection from the tuple $Z=(Q,W,D,R,B,S,H,C,P,N)$. The first six rows expose the finite request, selected window, dyadic ledger, regular-rational handoff, observation budget, and seal row.

The sibling surfaces supply the route checks. The $\StreamNameUp$ row gives the finite observation window, the $\DyadicRatCoreUp$ row gives the finite arithmetic readback, and the $\RegSeqRatUp$ row is the handoff consumed by the observation budget.

The budget and seal obligations are bound by $B,S,H,C,P,N$. Since the seal row is downstream of $B$ in the carrier and in the displayed continuation routes, the local certificate has no source from which to read a $\RealUp$ seal before the finite observation budget is present.
\end{proof}

\begin{theorem}[Regular-Cauchy finite observation route non-escape]
\label{thm:regular-cauchy-finite-observation-route-nonescape}
An accepted $\RegularCauchyFiniteObservationRouteUp$ carrier exports no quotient stream, host real equality proof, hidden limit selector, unbounded observation schedule, or direct $\RealUp$ seal read. Every completion-facing request remains inside the displayed rows $Q,W,D,R,B,S,H,C,P,N$.
\end{theorem}
\begin{proof}
Inspect the carrier inventory in \autoref{def:regular-cauchy-finite-observation-route-carrier}. The tuple lists the request, window, dyadic ledger, regular-rational handoff, observation budget, seal row, transports, continuations, provenance, and local naming data, and it lists none of the excluded objects.

Apply the obligation theorem. It makes the displayed rows the whole local $\NameCert$ surface, so a consumer cannot add quotient-stream equality, host real equality, hidden limit selection, an unbounded schedule, or an early seal coordinate while remaining in the accepted carrier.
\end{proof}

\begin{theorem}[Regular-Cauchy finite observation route Real seal handoff]
\label{thm:regular-cauchy-finite-observation-route-realseal-handoff}
Every $\RealUp$ seal read of an accepted $\RegularCauchyFiniteObservationRouteUp$ carrier factors through the finite route
$$
Q \to W \to D \to R \to B \to S
$$
with transport, continuation, provenance, and local naming rows $H,C,P,N$. Thus the seal is reached only after the $\RealObservationBudgetUp$ row has accepted the same $\StreamNameUp$ window, $\DyadicRatCoreUp$ readback, and $\RegSeqRatUp$ handoff.
\end{theorem}
\begin{proof}
Begin with the carrier. The seal coordinate $S$ appears after the window, dyadic ledger, handoff, and observation-budget rows in the displayed packet.

Read the observation-budget side through \autoref{ch:concrete-instances-real-observation-budget-namecert}. That sibling surface admits seal consumption only through finite windows, dyadic readbacks, regular-rational handoff rows, and its own budget row.

The rows $H,C,P,N$ record the componentwise transport, route replay, package provenance, and local name for the same packet. Therefore every $\RealUp$ seal read follows the displayed route through $B$ and cannot bypass the finite observation budget.
\end{proof}

\begin{theorem}[Regular-Cauchy finite observation route vision concretization]
\label{thm:regular-cauchy-finite-observation-route-vision-concretization}
The diagonal-limit route named in \autoref{ch:visions-real-completeness} is realized by accepted $\RegularCauchyFiniteObservationRouteUp$ packets as finite $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealObservationBudgetUp$, and $\RealUp$ seal data. The stationary diagonal side is read through \autoref{ch:concrete-instances-stationarypartitiondiagonal-namecert}, while product-facing consumers can share the finite window and handoff rows with \autoref{ch:concrete-instances-cauchyproduct-namecert} without importing quotient streams, hidden limits, or host real equality.
\end{theorem}
\begin{proof}
The diagonal-limit consumer in \autoref{ch:visions-real-completeness} needs a finite observation route before a $\RealUp$ seal is inspected. The carrier supplies exactly that route: request, window, dyadic readback, regular-rational handoff, observation budget, and seal.

The stationary diagonal sibling fixes the diagonal-window shape, and the CauchyProduct sibling can reuse the same kind of finite window and regular-rational handoff rows. These links do not add coordinates to $Z$; they only identify which sibling surfaces read the displayed rows.

Finally apply the Real seal handoff and non-escape theorems. Together they show that the vision-facing route reaches the $\RealUp$ seal through the finite observation budget and excludes quotient streams, hidden limit selection, and host real equality.
\end{proof}

\begin{theorem}[Regular-Cauchy finite observation route budget-selector pullback]
\label{thm:regular-cauchy-finite-observation-route-budget-selector-pullback}
Let
$$
Z=(Q,W,D,R,B,S,H,C,P,N)
$$
be an accepted $\RegularCauchyFiniteObservationRouteUp$ packet, and let
$$
F=(B_0,S_0,W_0,D_0,R_0,E_0,H_0,C_0,P_0,N_0)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. If the displayed $\hsame$ transports identify $W$ with $W_0$, $D$ with $D_0$, $R$ with $R_0$, and the route seal $S$ with $E_0$, then every $\RealUp$ or $\CauchyLimitSealUp$ consumer factors through both finite routes
$$
Q \to W \to D \to R \to B \to S
$$
and
$$
B_0 \to S_0 \to W_0 \to D_0 \to R_0 \to E_0 .
$$
The common consumer exports no quotient stream, hidden limit selector, host real equality, countable choice, or ambient completeness row.
\end{theorem}
\begin{proof}
Start on the regular-Cauchy route. By \autoref{thm:regular-cauchy-finite-observation-route-realseal-handoff}, every $\RealUp$ seal read of $Z$ passes through the displayed finite path $Q \to W \to D \to R \to B \to S$.

Move to the selector route. Apply \autoref{thm:finite-observation-budget-selector-budget-route-determinacy} to the packet $F$, obtaining the finite path $B_0 \to S_0 \to W_0 \to D_0 \to R_0 \to E_0$. The assumed componentwise $\hsame$ transports identify the shared window, dyadic ledger, $\RegSeqRatUp$ handoff, and seal endpoint.

Finally apply \autoref{thm:finite-observation-budget-selector-public-export} together with the non-escape theorem of this chapter. These two boundaries remove quotient streams, hidden limit selectors, host real equality, countable choice, and ambient completeness data, so the shared $\RealUp$ or $\CauchyLimitSealUp$ consumer can read only the two displayed finite routes and their visible transport, continuation, provenance, and naming rows.
\end{proof}

\falsifiablePrediction{Every accepted route factors through the displayed finite observation budget before any RealUp seal read; a seal read bypassing the budget refutes this chapter.}
\independenceWitness{real-observation-budget, finiteobservationbudgetselector, stationarypartitiondiagonal, cauchyproduct, streamname: none is bijective because this carrier simultaneously records the route from regular-Cauchy finite windows to the observation budget and RealUp seal, while each sibling lacks at least one of the route, budget, diagonal, product, or stream-only rows.}

\closureat{RegularCauchyFiniteObservationRouteUp}{seedStr}

\begin{closurestatus}{\RegularCauchyFiniteObservationRouteUp}
  \constructivestory{A $\RegularCauchyFiniteObservationRouteUp$ packet is generated from a finite regular-Cauchy request, selected $\StreamNameUp$ window, $\DyadicRatCoreUp$ observation ledger, $\RegSeqRatUp$ handoff, $\RealObservationBudgetUp$ budget row, $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-finite-observation-route-carrier}, \autoref{thm:regular-cauchy-finite-observation-route-obligations}, \autoref{thm:regular-cauchy-finite-observation-route-nonescape}, \autoref{thm:regular-cauchy-finite-observation-route-realseal-handoff}, \autoref{thm:regular-cauchy-finite-observation-route-vision-concretization}, and \autoref{thm:regular-cauchy-finite-observation-route-budget-selector-pullback} define the route carrier, obligation surface, non-escape boundary, Real seal handoff, vision-facing concretization, and budget-selector pullback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, quotient-stream equality, hidden limit selection, unbounded observation schedules, host real equality, RealUp completeness, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-window admission, dyadic readback, RegSeqRat handoff, observation-budget exactness, seal-handoff exactness, and non-escape for the same route packet.}
\end{closurestatus}
