\chapter{A Concrete Naming Certificate for $\LiteralASTEqualityBoundaryUp$}
\label{ch:concrete-instances-literal-ast-equality-boundary-namecert}
\origin{ai}

The $\LiteralASTEqualityBoundaryUp$ packet isolates the literal AST equality commitment of \autoref{ch:bedc-is-its-own-theory} as its own finite NameCert boundary. It sits beside the five-row own-theory packet of \autoref{ch:concrete-instances-internaltheoryboundary-namecert}, the broader theory-identity packet of \autoref{ch:concrete-instances-metacic-theory-identity-namecert}, and the dependency audit surface of \autoref{ch:concrete-instances-axiom-dependency-audit-map-namecert}. Those siblings package multiple identity or dependency commitments; this chapter names the single row that says equality is displayed AST equality and not beta equality, conversion equality, quotient equality, or host semantic equivalence.

\begin{definition}[Literal AST equality-boundary carrier]
\label{def:literal-ast-equality-boundary-carrier}
A $\LiteralASTEqualityBoundaryUp$ carrier is a finite $\BHist$ packet
$$
L=(A,T,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the displayed AST row, naming constructor tags, binder positions, variable rows, and immediate subterm rows exposed by the BEDC.MetaCIC syntax surface;
\item $T$ is the literal comparison row, recording equality only by identical displayed constructor tags and componentwise equality of displayed subrows;
\item $B$ is the boundary-refusal row for beta equality, conversion equality, quotient equality, proof irrelevance, proposition extensionality, host semantic equivalence, and parent-theory identity transport;
\item $H$ records componentwise $\hsame$ transport for the AST row, literal comparison row, boundary-refusal row, continuation routes, provenance row, and local naming row;
\item $C$ records displayed $\Cont$ routes by which a consumer reads literal equality and boundary refusal without adding a conversion oracle;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:bedc-is-its-own-theory}, \autoref{ch:concrete-instances-internaltheoryboundary-namecert}, \autoref{ch:concrete-instances-metacic-theory-identity-namecert}, \autoref{ch:concrete-instances-axiom-dependency-audit-map-namecert}, BEDC.MetaCIC AST rows, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\LiteralASTEqualityBoundaryUp}$ row.
\end{enumerate}
The carrier contains no beta-step evaluator, no conversion closure, no quotient of syntax, no external equality oracle, and no theorem identifying displayed AST equality with a semantic equality from another calculus.
\end{definition}

\begin{definition}[Literal AST equality-boundary classifier]
\label{def:literal-ast-equality-boundary-classifier}
Two $\LiteralASTEqualityBoundaryUp$ carriers
$$
L=(A,T,B,H,C,P,N)
$$
and
$$
L'=(A',T',B',H',C',P',N')
$$
are classifier-equivalent exactly when the displayed AST rows, literal comparison rows, boundary-refusal rows, componentwise transports, continuation routes, provenance rows, and local naming rows agree through the displayed $\hsame$ and $\Cont$ data. The classifier does not compare carriers by beta-normal form, definitional conversion, quotient representative, proof irrelevance, proposition extensionality, or host semantic equality.
\end{definition}

\begin{theorem}[Literal AST equality-boundary NameCert obligations]
\label{thm:literal-ast-equality-boundary-namecert-obligations}
For every $\LiteralASTEqualityBoundaryUp$ carrier
$$
L=(A,T,B,H,C,P,N),
$$
the local $\NameCert_{\LiteralASTEqualityBoundaryUp}$ surface consists exactly of the following finite rows:
\begin{enumerate}
\item carrier admission for the displayed packet of \autoref{def:literal-ast-equality-boundary-carrier};
\item classifier stability under the literal classifier of \autoref{def:literal-ast-equality-boundary-classifier};
\item literal equality exactness through $A$ and $T$;
\item boundary refusal through $B$ for every beta, conversion, quotient, proof-irrelevance, proposition-extensionality, host-semantic, or parent-theory equality request;
\item ledger exactness through $H,C,P,N$ for the same displayed rows.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the finite carrier. The rows $A,T,B$ are the only equality-facing coordinates before transport, route replay, provenance, or local naming is read.

Classifier stability is componentwise by \autoref{def:literal-ast-equality-boundary-classifier}. A transported packet may preserve literal AST equality, but it cannot replace that comparison by beta equality, conversion equality, quotient equality, or host semantic equality.

The rows $H,C,P,N$ make the same equality boundary readable by downstream consumers. Since the carrier has no evaluator, conversion closure, quotient, proof-irrelevance row, proposition-extensionality row, or parent-theory equality row, the listed NameCert obligations exhaust the packet surface.
\end{proof}

\begin{theorem}[Literal AST equality exactness]
\label{thm:literal-ast-equality-boundary-exactness}
Every equality read from an accepted $\LiteralASTEqualityBoundaryUp$ carrier
$$
L=(A,T,B,H,C,P,N)
$$
factors through the displayed AST row $A$, the literal comparison row $T$, and the componentwise transport and replay rows $H,C$. The read exports only constructor-tag equality and componentwise displayed subrow equality, and it exports no beta equality, conversion equality, quotient equality, proof irrelevance, proposition extensionality, host semantic equivalence, or parent-theory identity transport.
\end{theorem}
\begin{proof}
Begin with the carrier definition. The equality coordinate is $T$, and it is attached to the displayed AST row $A$.

Transport and replay are componentwise. The rows $H$ and $C$ can move or read $A$ and $T$, but they do not add a computation relation or quotient relation.

The boundary-refusal row $B$ accounts for every stronger equality request. Therefore any accepted equality read remains literal and displayed, with no route to the excluded equality principles.
\end{proof}

\begin{theorem}[Literal AST equality sibling independence]
\label{thm:literal-ast-equality-boundary-sibling-independence}
\independenceWitness{internaltheoryboundary, metacic-theory-identity, axiom-dependency-audit-map, bedcselftheory: the new carrier isolates one literal-equality boundary row rather than packaging all theory-identity commitments or all axiom-dependency routes.}
\end{theorem}
\begin{proof}
Compare row inventories. The internal-theory and MetaCIC theory-identity packets package closed generators, literal AST equality, structural recursors, purity, and apophatic boundary data together.

The axiom-dependency audit map packages claim, dependency, route, and audit rows. The BEDC self-theory packet packages the five positive own-theory commitments as one substrate-facing certificate.

The $\LiteralASTEqualityBoundaryUp$ carrier keeps only the displayed AST row, literal comparison row, boundary-refusal row, and structural ledger rows. It can be cited by those broader siblings, but none of them is bijective to this single equality-boundary packet.
\end{proof}

\begin{theorem}[Literal AST equality TasteGate obligation]
\label{thm:literal-ast-equality-boundary-tastegate-obligation}
The Lean-side `TasteGate.lean' development for $\LiteralASTEqualityBoundaryUp$ includes explicit $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances. These instances are the gate-facing rows that separate a real literal-equality boundary carrier from a vacuous event-flow encoding and record that the encoding preserves the displayed AST row, literal comparison row, boundary-refusal row, transport rows, route rows, provenance row, and local naming row.
\end{theorem}
\leanchecked{BEDC.Derived.LiteralASTEqualityBoundaryUp.LiteralASTEqualityBoundaryTasteGate\_single\_carrier\_alignment}
\begin{proof}
The carrier has distinct equality-facing fields. A gate that recognizes only an event-flow round trip would not show that $A$, $T$, and $B$ remain separate rows.

Nontriviality rules out the empty reading of the packet. Field faithfulness records preservation of the displayed field structure, so the literal equality boundary remains a finite carrier with inspectable rows rather than an unstructured event name.
\end{proof}

\falsifiablePrediction{No accepted packet may replace literal AST equality by beta/conversion equality without leaving the carrier rows.}

\closureat{LiteralASTEqualityBoundaryUp}{seedStr}

\begin{closurestatus}{\LiteralASTEqualityBoundaryUp}
  \constructivestory{A $\LiteralASTEqualityBoundaryUp$ packet is generated from displayed AST rows, literal comparison rows, boundary-refusal rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:literal-ast-equality-boundary-carrier}, \autoref{def:literal-ast-equality-boundary-classifier}, \autoref{thm:literal-ast-equality-boundary-namecert-obligations}, \autoref{thm:literal-ast-equality-boundary-exactness}, \autoref{thm:literal-ast-equality-boundary-sibling-independence}, and \autoref{thm:literal-ast-equality-boundary-tastegate-obligation} specify the literal AST equality boundary packet and its gate-facing obligation surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove beta soundness, conversion decidability, quotient soundness, proof irrelevance, proposition extensionality, host semantic equality, Lean verification, or bridge checking for $\LiteralASTEqualityBoundaryUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, literal equality exactness, boundary refusal, ledger exactness, and TasteGate nontriviality with field faithfulness.}
\end{closurestatus}
