\chapter{A Concrete Naming Certificate for $\TheorySelfClassifierUp$}
\label{ch:concrete-instances-theoryselfclassifier-namecert}
\origin{ai}

The $\TheorySelfClassifierUp$ packet realizes the own-theory reading of \autoref{ch:bedc-is-its-own-theory} as a finite classifier surface. It sits beside \autoref{ch:concrete-instances-internaltheoryboundary-namecert}, \autoref{ch:concrete-instances-metacic-theory-identity-namecert}, \autoref{ch:concrete-instances-axiom-dependency-audit-map-namecert}, and \autoref{ch:concrete-instances-bedcselftheory-namecert}: those siblings expose boundary, identity, dependency-audit, and self-theory rows, while this chapter packages the row comparison that lets a consumer read the five commitments as one self-theory classifier.

\begin{definition}[Theory self-classifier carrier]
\label{def:theory-self-classifier-carrier}
A $\TheorySelfClassifierUp$ carrier is a finite $\BHist$ packet
$$
T=(G,E,R,P,A,L,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the closed-generator row, naming the finite constructor and declaration inventory used by the theory surface;
\item $E$ is the literal equality row, recording that comparison is syntactic equality of the displayed object rows rather than semantic equality in a host calculus;
\item $R$ is the structural recursor row, exposing the eliminators attached to the closed generators named by $G$;
\item $P$ is the purity row, recording zero hidden axiom supply and strict proof-ancestry accountability for internal reads;
\item $A$ is the apophatic boundary row, recording visible sockets and setup fields for requests outside the internal substrate;
\item $L$ is the classifier ledger that compares $G,E,R,P,A$ as one self-theory surface;
\item $H$ records componentwise $\hsame$ transports for generator, equality, recursor, purity, boundary, ledger, route, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read each commitment and then return to the classifier ledger;
\item $Q$ is the $\Pkg$ provenance over \autoref{ch:bedc-is-its-own-theory}, \autoref{ch:concrete-instances-internaltheoryboundary-namecert}, \autoref{ch:concrete-instances-metacic-theory-identity-namecert}, \autoref{ch:concrete-instances-axiom-dependency-audit-map-namecert}, \autoref{ch:concrete-instances-bedcselftheory-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\TheorySelfClassifierUp}$ row.
\end{enumerate}
The carrier has no coordinate for a classical-CIC parent theory, semantic equality oracle, hidden recursor supply, unrecorded axiom dependency, or boundary row promoted to internal theorem content.
\end{definition}

\begin{theorem}[Theory self-classifier NameCert obligations]
\label{thm:theory-self-classifier-namecert-obligations}
For every $\TheorySelfClassifierUp$ carrier
$$
T=(G,E,R,P,A,L,H,C,Q,N),
$$
the local $\NameCert_{\TheorySelfClassifierUp}$ surface consists exactly of carrier admission, closed-generator exposure, literal-equality exposure, structural-recursor exposure, purity exposure, apophatic-boundary exposure, classifier-ledger comparison, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. The ledger row $L$ is required to compare the five commitment rows as one self-theory surface before a consumer may export a self-theory reading.
\end{theorem}
\begin{proof}
Project the finite carrier of \autoref{def:theory-self-classifier-carrier}. The rows $G,E,R,P,A$ are the five commitment coordinates, while $L,H,C,Q,N$ provide comparison, transport, replay, provenance, and local naming.

The NameCert obligations for the five commitments are read componentwise. The generator row supplies the closed inventory, the equality row supplies literal comparison, the recursor row supplies only generator-local eliminators, the purity row supplies strict audit visibility, and the apophatic row keeps external supply visible as boundary data.

The classifier obligation is the additional row $L$. It compares those five rows as one surface, so a consumer cannot cite a self-theory reading by projecting only one commitment or by replacing the row comparison with a sibling chapter.

Since the carrier contains no further coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Theory self-classifier non-escape]
\label{thm:theory-self-classifier-nonescape}
Every public read from an accepted $\TheorySelfClassifierUp$ carrier factors through
$$
G,E,R,P,A,L,H,C,Q,N.
$$
A consumer may read the five commitment rows, their classifier ledger, componentwise transports, displayed routes, provenance, and local name. It cannot read a classical-CIC parent theory, a host semantic equality oracle, a hidden recursor, an unrecorded axiom dependency, or an apophatic boundary promoted to internal theorem content.
\end{theorem}
\begin{proof}
Start from the displayed carrier. The only self-theory commitments are $G,E,R,P,A$, and the only row that compares them as one surface is $L$.

Routes through $C$ and transports through $H$ preserve those rows componentwise. They can replay a commitment read or move the packet, but they cannot create a new substrate principle.

The provenance and naming rows $Q,N$ cite the sibling surfaces and bind the local certificate. Citation gives a consumer context for the five rows; it does not add a parent theory, host equality, hidden recursor, axiom supply, or internal theorem extracted from a boundary row.

Thus every public read remains inside $T=(G,E,R,P,A,L,H,C,Q,N)$, and the excluded objects have no route through the accepted packet.
\end{proof}

\begin{theorem}[Theory self-classifier sibling independence]
\label{thm:theory-self-classifier-sibling-independence}
\independenceWitness{Nearest siblings: internaltheoryboundary, metacic-theory-identity, axiomdependencyauditmap, and bedcselftheory. No one of these is bijective to the $\TheorySelfClassifierUp$ carrier because each lacks the classifier row $L$ that compares closed generators, literal equality, structural recursors, purity, and apophatic boundary rows as one self-theory surface.}
\end{theorem}
\begin{proof}
Compare row inventories. The internal-theory-boundary packet exposes the five commitments as a boundary, the MetaCIC theory-identity packet records identity rows, the axiom-dependency-audit-map packet records mode and supply rows, and the BEDC self-theory packet packages the commitments as a self-theory certificate.

The $\TheorySelfClassifierUp$ carrier requires the same five commitment rows together with the classifier ledger $L$ that compares them as one surface. None of the sibling carriers has that row with the displayed comparison role.

Therefore a consumer may cite those siblings as provenance, but no cited sibling is a bijective replacement for this classifier packet.
\end{proof}

\begin{theorem}[Theory self-classifier TasteGate target]
\label{thm:theory-self-classifier-tastegate-target}
The later Lean `TasteGate.lean' development for $\TheorySelfClassifierUp$ must provide a $\mathsf{Nontrivial}$ witness with two explicit carrier values and a $\mathsf{FieldFaithful}$ witness by field projection, match analysis, and injection over the displayed rows $G,E,R,P,A,L,H,C,Q,N$.
\end{theorem}
\begin{proof}
The carrier has distinguishable commitment and classifier fields, so a singleton event-flow encoding would not show that the self-theory surface is genuinely classified.

Nontriviality supplies two explicit packets. Field faithfulness then checks the event-flow encoding by projecting each displayed row, matching on the carrier constructor, and using injection to recover equality of all fields from equality of encodings.

These two gate obligations are the Lean-side conditions needed before the classifier can be treated as a checked TasteGate object.
\end{proof}

\falsifiablePrediction{A TheorySelfClassifierUp packet cannot export a self-theory reading unless the five commitment rows are all present as displayed BHist coordinates.}

\closureat{TheorySelfClassifierUp}{seedStr}

\begin{closurestatus}{\TheorySelfClassifierUp}
  \constructivestory{A $\TheorySelfClassifierUp$ packet is generated from closed-generator, literal-equality, structural-recursor, purity, apophatic-boundary, classifier-ledger, transport, route, provenance, and local naming rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:theory-self-classifier-carrier}, \autoref{thm:theory-self-classifier-namecert-obligations}, \autoref{thm:theory-self-classifier-nonescape}, \autoref{thm:theory-self-classifier-sibling-independence}, and \autoref{thm:theory-self-classifier-tastegate-target} specify the seed carrier, finite NameCert surface, non-escape boundary, sibling independence witness, and gate-facing target.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not provide Lean-side verification, bridge checking, a classical-CIC embedding, a semantic equality oracle, a hidden axiom route, or a completed TasteGate instance.}
  \upgradepath{Obligation closure requires Lean encoding of the carrier, checked five-row classifier obligations, non-escape, sibling independence, and a TasteGate route with Nontrivial and FieldFaithful instances.}
\end{closurestatus}
