\chapter{A Concrete Naming Certificate for $\TypedExampleAuditBudgetUp$}
\label{ch:concrete-instances-typedexampleauditbudget-namecert}
\origin{ai}

The $\TypedExampleAuditBudgetUp$ packet realizes the TypedExamples audit-map vision of \autoref{ch:metacic-typedexamples-audit-map} as a finite regression-spend certificate. It sits beside the MetaCIC gallery of \autoref{ch:concrete-instances-metacictypedexamplesgallery-namecert}, the typed-example gallery of \autoref{ch:concrete-instances-typedexamplegallery-namecert}, the worked-example seal of \autoref{ch:concrete-instances-metacic-typedexamples-seal-namecert}, and the beta-step boundary of \autoref{ch:concrete-instances-betastepboundary-namecert}: those siblings expose gallery rows, checker rows, seal rows, and reduction-boundary rows, while this chapter records which accepted rows have regression budget and which consumer spends may read that budget.

\begin{definition}[TypedExampleAuditBudget carrier]
\label{def:typed-example-audit-budget-carrier}
A $\TypedExampleAuditBudgetUp$ carrier is a finite $\BHist$ packet
$$
A=(G,C,B,Z,R,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the finite gallery-row inventory inherited from the accepted TypedExamples and MetaCIC gallery packets;
\item $C$ is the checker-row inventory recording the accepted local type-checker reads for the same gallery rows;
\item $B$ is the beta-row inventory recording the selected beta computations and boundary steps that the gallery spends;
\item $Z$ is the closedness-row inventory recording the closed term, context, and well-scoped inputs required by the checker rows;
\item $R$ is the regression-budget row, naming the accepted gallery rows that count as covered and the consumer-spend boundary attached to each row;
\item $H$ records componentwise $\hsame$ transports for gallery, checker, beta, closedness, regression-budget, provenance, and local naming rows;
\item $K$ records the displayed $\Cont$ routes by which downstream checker-audit consumers reach exactly the rows $G,C,B,Z,R$;
\item $P$ is the $\Pkg$ provenance over the sibling gallery, seal, beta-boundary, transport, continuation, and regression-budget rows;
\item $N$ is the local $\NameCert_{\TypedExampleAuditBudgetUp}$ row.
\end{enumerate}
The carrier has no coordinate for a global checker-completeness theorem, a subject-reduction theorem, a normalization theorem, an arbitrary beta closure, or an unbudgeted consumer spend.
\end{definition}

\begin{theorem}[TypedExampleAuditBudget NameCert obligations]
\label{thm:typed-example-audit-budget-namecert-obligations}
For the carrier of \autoref{def:typed-example-audit-budget-carrier}, the local $\NameCert_{\TypedExampleAuditBudgetUp}$ surface consists of five finite rows:
\begin{enumerate}
\item carrier admission for $A=(G,C,B,Z,R,H,K,P,N)$;
\item gallery-row exactness through $G$ against the sibling gallery packets of \autoref{ch:concrete-instances-metacictypedexamplesgallery-namecert} and \autoref{ch:concrete-instances-typedexamplegallery-namecert};
\item checker, beta, and closedness exposure through $C$, $B$, and $Z$;
\item regression-budget non-escape through $R$, including the consumer-spend boundary attached to accepted rows;
\item transport and provenance through $H$, $K$, $P$, and the local name row $N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection of the displayed finite packet. Every public row that a checker-audit consumer may inspect is present before the local $\NameCert$ row is read.

Gallery exactness is sibling-bounded. The row $G$ names the gallery entries, while $C$, $B$, and $Z$ expose the checker, beta, and closedness evidence that the gallery and seal packets already make visible.

The regression-budget row $R$ is separate from gallery acceptance. A consumer that reads an accepted gallery row must still pass through $R$ to learn whether that row is counted as covered and which spend boundary it carries.

Finally $H$, $K$, $P$, and $N$ bind the row reads to displayed transport, continuation, provenance, and local naming. Since no coordinate names a global checker theorem, subject reduction, normalization, arbitrary beta closure, or unbudgeted spend, the certificate cannot export one.
\end{proof}

\begin{theorem}[TypedExampleAuditBudget regression non-escape]
\label{thm:typed-example-audit-budget-regression-nonescape}
Every checker-audit consumer of an accepted $\TypedExampleAuditBudgetUp$ packet can read gallery acceptance only together with the displayed checker, beta, closedness, regression-budget, transport, continuation, provenance, and local naming rows. Removing the regression-budget row $R$ destroys the consumer's ability to distinguish accepted gallery entries from entries counted as regression coverage, and no sibling gallery, seal, or beta-boundary packet can reconstruct that distinction.
\end{theorem}
\begin{proof}
Project an accepted carrier $A=(G,C,B,Z,R,H,K,P,N)$. The rows $G,C,B,Z$ expose gallery acceptance, checker reads, selected beta computations, and closedness inputs, but only $R$ records regression coverage and consumer-spend boundaries.

Use the transport and continuation rows $H$ and $K$ for downstream checker-audit reads. They route the consumer through the displayed coordinates and therefore preserve the separation between gallery admission and regression coverage.

The sibling packets do not identify these two readings. The MetaCIC and typed-example galleries name accepted rows, the seal names worked-example closure of the gallery surface, and the beta-step boundary names reduction-boundary rows; none of them carries the regression-budget coordinate $R$ together with its spend boundary. Thus removing $R$ erases precisely the coverage distinction claimed by the packet.
\end{proof}

\falsifiablePrediction{If the regression-budget row is removed from an accepted TypedExampleAuditBudget packet, a downstream checker-audit consumer can no longer distinguish gallery acceptance from regression coverage.}

\independenceWitness{Nearest siblings: metacictypedexamplesgallery, typedexamplegallery, metacic-typedexamples-seal, betastepboundary. The budget packet is not bijective with any sibling because it carries a regression-budget row and a consumer-spend boundary that gallery and seal packets do not expose, while BetaStepBoundary carries reduction-boundary rows rather than typed-example gallery spend rows.}

The proposed Lean follow-up for namespace $\mathsf{BEDC.Derived.TypedExampleAuditBudgetUp}$ places the taste-gate surface in $\mathsf{BEDC.Derived.TypedExampleAuditBudgetUp.TasteGate}$. Its file $\mathsf{lean4/BEDC/Derived/TypedExampleAuditBudgetUp/TasteGate.lean}$ includes both $\mathsf{Nontrivial}\ \TypedExampleAuditBudgetUp$ with an explicit witness pair and $\mathsf{FieldFaithful}\ \TypedExampleAuditBudgetUp$ with mk-field projections and an injection proof.

\closureat{TypedExampleAuditBudgetUp}{seedStr}

\begin{closurestatus}{\TypedExampleAuditBudgetUp}
  \constructivestory{A $\TypedExampleAuditBudgetUp$ packet is generated from finite gallery rows, checker rows, beta rows, closedness rows, regression-budget rows, componentwise transports, continuation routes, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:typed-example-audit-budget-carrier}, \autoref{thm:typed-example-audit-budget-namecert-obligations}, and \autoref{thm:typed-example-audit-budget-regression-nonescape} bind the finite gallery, checker, beta, closedness, regression-budget, consumer-spend, transport, provenance, and local naming surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close checker completeness, subject reduction, normalization, global beta closure, arbitrary gallery soundness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, gallery-row exactness, checker exposure, beta exposure, closedness exposure, regression-budget non-escape, consumer-spend boundary visibility, componentwise transport, displayed continuation, provenance, and local naming rows.}
\end{closurestatus}
