\chapter{A Concrete Naming Certificate for $\RealSealComparisonUp$}
\label{ch:concrete-instances-realsealcomparison-namecert}
\origin{ai}

The $\RealSealComparisonUp$ packet is the equality-facing comparison surface for two sealed $\RealUp$ routes in the Real completeness target of \autoref{ch:visions-real-completeness}. It consumes two Cauchy-limit seal packets from \autoref{ch:concrete-instances-cauchylimitseal-namecert}, the separated uniqueness row of \autoref{ch:concrete-instances-regular-limit-uniqueness-namecert}, and the diagonal stability route of \autoref{ch:concrete-instances-diagonal-limit-stability-namecert}. The packet records a finite comparison between the two sealed routes; it is not a quotient stream, a host real equality, a selected limit, or an ambient completeness principle.

\falsifiablePrediction{If a $\RealSealComparisonUp$ route is accepted, it factors through two displayed $\CauchyLimitSealUp$ public route packets and one separated comparison row. A route requiring quotient streams, host real equality, selected limits, or ambient completeness is outside the carrier.}

\independenceWitness{cauchylimitseal, regularlimituniqueness, diagonallimitstability, realobservationbudget, regularcauchycomparison: none is bijective to $\RealSealComparisonUp$ because this carrier contains two seal routes and one equality-facing separated comparison between them. CauchyLimitSeal, RealObservationBudget, and DiagonalLimitStability are single-route or representative-to-seal packets; RegularLimitUniqueness supplies the separated row without the two public seal routes; RegularCauchyComparison compares regular sources before the paired seal-comparison package is assembled.}

\begin{definition}[Real seal comparison carrier]
\label{def:real-seal-comparison-carrier}
A $\RealSealComparisonUp$ carrier is a finite $\BHist$ packet
$$
Q=(S_0,S_1,U,D_0,D_1,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S_0$ and $S_1$ are two public $\CauchyLimitSealUp$ route packets, each already exposing its regular source, finite windows, $\RegSeqRatUp$ readback, $\RealUp$ seal, transport, continuation, provenance, and local naming rows;
\item $U$ is the separated $\RegularLimitUniquenessUp$ comparison row between the two $\RealUp$ seal outputs;
\item $D_0$ and $D_1$ are the $\DiagonalLimitStabilityUp$ rows that attach the two seal routes to their displayed diagonal representatives;
\item $K$ is the equality-facing comparison verdict read only after $S_0$, $S_1$, and $U$ have been displayed;
\item $H$ records componentwise $\hsame$ transport for the two seal packets, the separated comparison row, the diagonal-stability rows, the verdict, route replay, provenance, and local naming;
\item $C$ records the displayed $\Cont$ routes that replay the two seal packets, the separated comparison, the diagonal-stability handoffs, and the verdict;
\item $P$ is the $\Pkg$ provenance over $\CauchyLimitSealUp$, $\RegularLimitUniquenessUp$, $\DiagonalLimitStabilityUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RealSealComparisonUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient stream equality, host real equality, a selected host limit, countable choice, trichotomy, or an ambient Real completeness theorem.
\end{definition}
\leanchecked{BEDC.Derived.RealSealComparisonUp.RealSealComparisonTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RealSealComparison NameCert obligations]
\label{thm:real-seal-comparison-namecert-obligations}
For every $\RealSealComparisonUp$ carrier
$$
Q=(S_0,S_1,U,D_0,D_1,K,H,C,P,N),
$$
the local $\NameCert_{\RealSealComparisonUp}$ surface consists of carrier exposure for the two $\CauchyLimitSealUp$ route packets, exposure of the separated $\RegularLimitUniquenessUp$ comparison row, exposure of the two $\DiagonalLimitStabilityUp$ handoff rows, equality-facing verdict exposure through $K$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-seal-comparison-carrier}. The two seal packets, separated comparison row, diagonal-stability rows, verdict row, transports, continuations, provenance, and local name are explicit coordinates of one finite $\BHist$ packet.

Read the two seal routes through the Cauchy-limit seal public boundary. Each side must already present its regular source, finite windows, readback, and $\RealUp$ seal before the comparison route can inspect it.

Then read $U$ through the separated uniqueness surface and $D_0,D_1$ through diagonal-limit stability. These rows make the equality-facing verdict a finite comparison between displayed seal routes, not a host equality between completed reals.

The structural rows $H,C,P,N$ transport, replay, authenticate, and name exactly those displayed rows. Since the carrier contains no quotient, host equality, selected limit, choice, trichotomy, or ambient-completeness coordinate, the local NameCert obligations are exhausted by the listed packet.
\end{proof}
\leanchecked{BEDC.Derived.RealSealComparisonUp.RealSealComparisonCarrier\_namecert\_obligations}

\begin{theorem}[RealSealComparison uniqueness handoff]
\label{thm:real-seal-comparison-uniqueness-handoff}
Any accepted $\RealSealComparisonUp$ packet that exports equality of the two sealed $\RealUp$ routes must factor the export through the two displayed $\CauchyLimitSealUp$ packets $S_0,S_1$ and the separated comparison row $U$. The verdict $K$ is determined only after those three rows and the diagonal-stability handoffs $D_0,D_1$ have been replayed through the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Start with the two seal packets. The Cauchy-limit seal boundary forces each $\RealUp$ route to expose its public route packet before a downstream consumer reads the seal.

Next apply the separated uniqueness row. The comparison between the two seal outputs is the row $U$, so the equality-facing verdict cannot be read before both $S_0$ and $S_1$ have reached their displayed seals.

The diagonal-stability rows attach the seal routes to their representatives, while $H,C,P,N$ replay and authenticate the same finite route. Thus the handoff to equality is the displayed two-seal and one-separated-row route, with no independent host equality or selected limit available.
\end{proof}

\begin{theorem}[RealSealComparison non-escape]
\label{thm:real-seal-comparison-nonescape}
Downstream consumers of an accepted $\RealSealComparisonUp$ packet receive only the finite comparison surface
$$
S_0,S_1,U,D_0,D_1,K,H,C,P,N.
$$
They receive no quotient stream, host real equality, selected limit, countable-choice selector, trichotomy row, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Project the accepted carrier. The public comparison surface contains exactly the two seal route packets, separated comparison row, diagonal-stability handoffs, verdict, transports, continuations, provenance, and local naming row.

Use the uniqueness handoff to route any equality-facing consumer through $S_0,S_1,U,D_0,D_1$ before it reaches $K$. This makes the displayed finite comparison the only consumer-visible equality boundary.

Finally inspect the excluded data. No coordinate in the carrier stores quotient stream equality, host real equality, a selected limit, countable choice, trichotomy, or ambient completeness. The downstream export therefore cannot escape the finite two-seal comparison surface.
\end{proof}

\closureat{RealSealComparisonUp}{seedStr}

\begin{closurestatus}{\RealSealComparisonUp}
  \constructivestory{A $\RealSealComparisonUp$ packet is generated from two $\CauchyLimitSealUp$ public route packets, a separated $\RegularLimitUniquenessUp$ comparison row, two $\DiagonalLimitStabilityUp$ handoff rows, an equality-facing verdict, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-seal-comparison-carrier}, \autoref{thm:real-seal-comparison-namecert-obligations}, \autoref{thm:real-seal-comparison-uniqueness-handoff}, and \autoref{thm:real-seal-comparison-nonescape} specify the finite two-seal comparison carrier, local NameCert rows, separated uniqueness handoff, and non-escape boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove host real equality, quotient-stream equality, selected-limit existence, ambient Real completeness, Lean verification, or bridge checking for $\RealSealComparisonUp$.}
  \upgradepath{Obligation closure requires checked two-seal carrier admission, separated comparison exactness, diagonal-stability replay, equality-verdict determinacy, transport preservation, and consumer non-escape for the same finite packet.}
\end{closurestatus}
