\chapter{A Concrete Naming Certificate for $\ObserverLocalityTransportUp$}
\label{ch:concrete-instances-observer-locality-transport-namecert}
\origin{ai}

The $\ObserverLocalityTransportUp$ packet realizes the transport boundary in the Inter-Hist Locality chain of \autoref{ch:visions-inter-hist-locality}. It sits after the observer-locality cell surface of \autoref{ch:concrete-instances-observer-locality-cell-namecert}, the causal-route surface of \autoref{ch:concrete-instances-crosshistcausal-namecert}, and the unary-bound surface of \autoref{ch:concrete-instances-maxcausalrate-namecert}; it is the route-level sibling read by the cross-Hist causal-rate packet of \autoref{ch:concrete-instances-crosshistcausalrate-namecert}. The packet records the finite path by which a consumer transports locality-cell data through causal rows and maximum-rate rows without entering a global observer frame.

\begin{definition}[Observer-locality transport carrier]
\label{def:observer-locality-transport-carrier}
An $\ObserverLocalityTransportUp$ carrier is a finite $\BHist$ packet
$$
T=(O,D,R,L,H,Q,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the $\ObserverLocalityCellUp$ row that supplies the two-observer locality cell being transported;
\item $D$ is the finite family of $\CrossHistCausalUp$ rows that records the causal route through which the locality-cell read is moved between the two displayed histories;
\item $R$ is the $\MaxCausalRateUp$ row whose unary bound is read only after the causal routes in $D$ have been exposed;
\item $L$ is the no-global-frame ledger, recording that the transport route contains no privileged observer frame, synchronized clock, metric tensor, Lorentz-geometry coordinate, or host real-valued speed row;
\item $H$ records componentwise $\hsame$ transport for the locality cell, causal rows, maximum-rate row, no-global-frame ledger, probe-stability row, continuation routes, provenance row, and local naming row;
\item $Q$ records $\psame$ stability for the probe reads used by the locality-cell row, causal rows, and maximum-rate row;
\item $C$ records displayed $\Cont$ routes by which a consumer reads $O$, replays each row of $D$, reads $R$, checks $L$, and transports the same packet through $H$ and $Q$;
\item $P$ is the $\Pkg$ provenance over $\ObserverLocalityTransportUp$, $\ObserverLocalityCellUp$, $\CrossHistCausalUp$, $\MaxCausalRateUp$, $\CrossHistCausalRateUp$, $\BHist$, $\hsame$, $\psame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ObserverLocalityTransportUp}$ row.
\end{enumerate}
The carrier exports only the displayed locality cell, causal rows, maximum-rate row, no-global-frame ledger, transport rows, continuation routes, provenance, and local naming data.
\end{definition}

\begin{theorem}[Observer-locality transport NameCert obligations]
\label{thm:observer-locality-transport-namecert-obligations}
For the carrier of \autoref{def:observer-locality-transport-carrier}, the local $\NameCert_{\ObserverLocalityTransportUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $T=(O,D,R,L,H,Q,C,P,N)$;
\item locality-cell source exactness, requiring the transported row to be the $\ObserverLocalityCellUp$ row $O$ and not a detached observer-frame coordinate;
\item causal-route handoff, requiring every transport route to pass through the displayed $\CrossHistCausalUp$ family $D$ before the maximum-rate row $R$ is read;
\item transport stability through componentwise $\hsame$ in $H$, probe stability in $Q$, and displayed $\Cont$ replay in $C$;
\item non-escape, excluding global frames, synchronized clocks, metric tensors, Lorentz geometry, host real-valued speed, and any locality read not routed through $O,D,R,L,H,Q,C,P,N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:observer-locality-transport-carrier}. The rows $O,D,R,L,H,Q,C,P,N$ display the locality cell, causal family, maximum-rate row, no-global-frame ledger, transports, routes, provenance, and local name.

Locality-cell source exactness reads $O$ first. The packet has no separate observer-frame coordinate, so the transported locality surface is the finite cell row rather than an ambient frame.

Causal-route handoff then reads $D$ before $R$. Each maximum-rate read is attached to the displayed causal family, so a consumer cannot replace the route witness by a bare unary bound.

Transport stability is componentwise through $H,Q,C$, and the non-escape claim is the carrier inventory. Since no excluded structure is a coordinate of $T$, no local certificate projection can export one.
\end{proof}

\begin{theorem}[Observer-locality transport boundary]
\label{thm:observer-locality-transport-boundary}
Every public consumer of an accepted $\ObserverLocalityTransportUp$ packet reads the locality-cell row only through
$$
O,D,R,L,H,Q,C,P,N.
$$
In particular, the consumer must pass from the $\ObserverLocalityCellUp$ row $O$ through the $\CrossHistCausalUp$ rows $D$ before it reads the $\MaxCausalRateUp$ row $R$ or the cross-Hist causal-rate surface of \autoref{ch:concrete-instances-crosshistcausalrate-namecert}.
\end{theorem}
\begin{proof}
Project the accepted carrier. The locality-cell source is the row $O$, and the only displayed route family connecting it to rate data is $D$.

Use the causal-route handoff in \autoref{thm:observer-locality-transport-namecert-obligations}. It places the $\CrossHistCausalUp$ rows before the maximum-rate row $R$, so the rate read is not a substitute for the transport route.

Finally route through $H,Q,C,P,N$ and check the no-global-frame ledger $L$. The consumer remains inside the finite packet and cannot read a global frame, metric tensor, Lorentz geometry, synchronized clock, or host real-valued speed.
\end{proof}

\begin{theorem}[Observer-locality transport rate pullback]
\label{thm:observer-locality-transport-rate-pullback}
Every rate-facing consumer of an accepted $\ObserverLocalityTransportUp$ packet factors through the same finite tuple
$$
O,D,R,L,H,Q,C,P,N.
$$
In particular, the consumer must read the $\ObserverLocalityCellUp$ row $O$, the $\CrossHistCausalUp$ route family $D$, the $\MaxCausalRateUp$ row $R$, and the $\CrossHistCausalRateUp$ consumer surface through one transport packet. The packet exports no global frame, synchronized clock, metric tensor, Lorentz geometry, host real-valued speed, or detached rate row.
\end{theorem}
\begin{proof}
Project the accepted carrier from \autoref{def:observer-locality-transport-carrier}. The tuple $O,D,R,L,H,Q,C,P,N$ lists the locality cell, causal family, maximum-rate row, no-global-frame ledger, structural rows, provenance, and local naming row available to a rate-facing consumer.

Apply \autoref{thm:observer-locality-transport-namecert-obligations}. The NameCert surface places locality-cell exactness before causal-route handoff, and it requires every maximum-rate read to pass through the displayed causal family.

Now use \autoref{thm:observer-locality-transport-boundary}. It keeps the public consumer inside the same tuple and routes any cross-Hist causal-rate read through the locality cell, causal routes, maximum-rate row, and transport rows.

The non-escape clause follows from the ledger $L$ and carrier inventory. Since no listed coordinate is a global frame, synchronized clock, metric tensor, Lorentz geometry, host real-valued speed, or detached rate row, the accepted transport packet cannot export one.
\end{proof}

\begin{theorem}[Observer-locality transport TasteGate obligation]
\label{thm:observer-locality-transport-tastegate-obligation}
The later Lean \texttt{TasteGate.lean} development for $\ObserverLocalityTransportUp$ must include explicit $\mathsf{Nontrivial}\ \ObserverLocalityTransportUp$ and $\mathsf{FieldFaithful}\ \ObserverLocalityTransportUp$ instances. These instances must preserve the locality-cell row, causal-route family, maximum-rate row, no-global-frame ledger, $\hsame$ transport, $\psame$ stability, $\Cont$ routes, package provenance, and local naming row.
\end{theorem}
\begin{proof}
The packet is not determined by a single locality cell or a single rate row. It carries a route-level transport witness between the cell and the maximum-rate surface.

Nontriviality rules out a collapsed carrier in which the route witness is indistinguishable from the cell or rate rows. Field faithfulness records preservation of all displayed coordinates $O,D,R,L,H,Q,C,P,N$, so a TasteGate consumer can distinguish the route-level transport row from the sibling surfaces it connects.
\end{proof}
\leanchecked{BEDC.Derived.ObserverLocalityTransportUp.ObserverLocalityTransportTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Observer-locality transport obligation carrier admission]
\label{thm:observer-locality-transport-obligation-carrier-admission}
For every accepted $\ObserverLocalityTransportUp$ carrier
$$
T=(O,D,R,L,H,Q,C,P,N),
$$
the finite local $\NameCert_{\ObserverLocalityTransportUp}$ surface admits exactly the displayed transport packet. The admitted rows are the $\ObserverLocalityCellUp$ source row $O$, the $\CrossHistCausalUp$ route family $D$, the $\MaxCausalRateUp$ rate row $R$, the no-global-frame ledger $L$, componentwise transport $H$, probe stability $Q$, continuation replay $C$, package provenance $P$, and the local naming row $N$.
\end{theorem}
\begin{proof}
Project the carrier displayed in \autoref{def:observer-locality-transport-carrier}. Its coordinates are precisely $O,D,R,L,H,Q,C,P,N$, and each coordinate already has the named transport role used by the local certificate.

Apply the boundary theorem, \autoref{thm:observer-locality-transport-boundary}. It says every public consumer reads the locality-cell row only through the same tuple, so carrier admission cannot add an external frame, clock, metric, or detached rate coordinate.

Finally apply the rate pullback theorem, \autoref{thm:observer-locality-transport-rate-pullback}. The rate-facing surface also factors through the same packet, which makes the admitted carrier the complete finite NameCert row for later promotion.
\end{proof}

\begin{theorem}[Observer-locality transport obligation causal-route handoff]
\label{thm:observer-locality-transport-obligation-causal-route-handoff}
For every accepted $\ObserverLocalityTransportUp$ carrier $T=(O,D,R,L,H,Q,C,P,N)$, any consumer that reads the maximum-rate row $R$ or the cross-Hist causal-rate surface must first pass through the displayed route family $D$ from the locality-cell row $O$. The handoff is transported only by $H$, stabilized only by $Q$, replayed only by $C$, packaged only by $P$, and locally named only by $N$.
\end{theorem}
\begin{proof}
Begin with the local NameCert obligations of \autoref{thm:observer-locality-transport-namecert-obligations}. Their handoff row places every maximum-rate read after the displayed $\CrossHistCausalUp$ family $D$.

Use \autoref{thm:observer-locality-transport-boundary} to identify the public route. The consumer starts at the locality-cell row $O$, moves through $D$, and only then reaches $R$ or a cross-Hist causal-rate read.

The rate pullback theorem, \autoref{thm:observer-locality-transport-rate-pullback}, keeps this handoff inside $T$. Thus $H,Q,C,P,N$ preserve and replay the same finite route instead of manufacturing a second causal path or detached rate row.
\end{proof}

\begin{theorem}[Observer-locality transport route composition determinacy]
\label{thm:observer-locality-transport-route-composition-determinacy}
For every accepted $\ObserverLocalityTransportUp$ carrier
$$
T=(O,D,R,L,H,Q,C,P,N),
$$
any two public consumers that read the same $\ObserverLocalityCellUp$ row $O$ and the same $\CrossHistCausalUp$ family $D$ before reading the $\MaxCausalRateUp$ row $R$ have the same displayed transport route through $H,Q,C,P,N$. No such consumer can splice in a detached causal row, detached rate row, global frame, synchronized clock, metric tensor, Lorentz coordinate, or host real-valued speed.
\end{theorem}
\begin{proof}
Project the accepted carrier from \autoref{def:observer-locality-transport-carrier}. The only displayed route from the locality cell to the rate row is the finite packet $O,D,R,L,H,Q,C,P,N$.

Apply causal-route handoff, \autoref{thm:observer-locality-transport-obligation-causal-route-handoff}. It forces both consumers to read $O$, then the same family $D$, and only then the rate row $R$.

Use rate pullback, \autoref{thm:observer-locality-transport-rate-pullback}. Since every rate-facing consumer remains inside the same tuple, the continuation, transport, stability, provenance, and naming rows are exactly $H,Q,C,P,N$ for both reads.

Finally apply non-global-frame exhaustion, \autoref{thm:observer-locality-transport-obligation-nonglobal-frame-exhaustion}. The excluded coordinates have no carrier row in $T$, so they cannot be spliced into the displayed route.
\end{proof}

\begin{theorem}[Observer-locality transport obligation non-global-frame exhaustion]
\label{thm:observer-locality-transport-obligation-nonglobal-frame-exhaustion}
For every accepted $\ObserverLocalityTransportUp$ carrier $T=(O,D,R,L,H,Q,C,P,N)$, the no-global-frame ledger $L$ exhausts every request for a privileged observer frame, synchronized clock, metric tensor, Lorentz-geometry coordinate, host real-valued speed, or locality read not routed through $O,D,R,L,H,Q,C,P,N$. Later promotion reads the existing \texttt{BEDC.Derived.ObserverLocalityTransportUp.ObserverLocalityTransportTasteGate\_single\_carrier\_alignment} marker together with the $\mathsf{Nontrivial}\ \ObserverLocalityTransportUp$ and $\mathsf{FieldFaithful}\ \ObserverLocalityTransportUp$ instances, so the AI-origin TasteGate discipline is attached to this same finite carrier rather than to a global frame.
\end{theorem}
\begin{proof}
Read the ledger coordinate $L$ in the carrier definition. It records exactly the exclusions for global frame, synchronized clock, metric tensor, Lorentz geometry, host real-valued speed, and off-route locality access.

Apply \autoref{thm:observer-locality-transport-boundary}. Since every public locality read stays inside $T$, any request for a global frame has no coordinate except the refusal recorded by $L$.

Apply \autoref{thm:observer-locality-transport-rate-pullback} for rate-facing consumers. The rate row is available only after the causal route and never as a host real-valued speed or Lorentz coordinate, so the exhaustion covers both locality and rate interfaces.

The TasteGate marker already checked in this chapter is then read as a single-carrier alignment condition. Nontriviality separates the transport packet from its sibling rows, and field faithfulness preserves all coordinates $O,D,R,L,H,Q,C,P,N$ during promotion.
\end{proof}

\falsifiablePrediction{If the transport packet is atomic, a consumer cannot replace the displayed locality-cell row by a MaxCausalRate row without passing through CrossHistCausal transport.}

\independenceWitness{Nearest siblings: observerlocalitycell, crosshistcausal, maxcausalrate, crosshistcausalrate. The transport packet is not bijective to any of them because it carries a route-level transport row between sibling surfaces, while those siblings carry cell, causal, bound, or rate rows without this route witness.}

\closureat{ObserverLocalityTransportUp}{seedStr}
\closureat{ObserverLocalityTransportUp}{obligationStr}[BEDC.Derived.ObserverLocalityTransportUp.ObserverLocalityTransportTasteGate\_single\_carrier\_alignment]
\closureat{ObserverLocalityTransportUp}{scopedStr}[BEDC.Derived.ObserverLocalityTransportUp.ObserverLocalityTransportTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\ObserverLocalityTransportUp}
  \constructivestory{An $\ObserverLocalityTransportUp$ packet is generated from an observer-locality cell, finite cross-Hist causal route rows, a maximum-rate row, a no-global-frame ledger, componentwise $\hsame$ transport, $\psame$ stability, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:observer-locality-transport-carrier}, \autoref{thm:observer-locality-transport-namecert-obligations}, \autoref{thm:observer-locality-transport-boundary}, \autoref{thm:observer-locality-transport-tastegate-obligation}, \leanchecked{BEDC.Derived.ObserverLocalityTransportUp.taste\_gate}, and the checked single-carrier marker \texttt{BEDC.Derived.ObserverLocalityTransportUp.ObserverLocalityTransportTasteGate\_single\_carrier\_alignment} bind the finite carrier rows $O,D,R,L,H,Q,C,P,N$ with the kernel rows $\BHist$, $\hsame$, $\psame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not derive Lorentz geometry, metric tensors, synchronized clocks, global frames, host real-valued speed, Lean verification, or bridge checking for $\ObserverLocalityTransportUp$.}
  \upgradepath{Public closure next requires a public transport export theorem over the same finite route.}
\end{closurestatus}
