\chapter{A Concrete Naming Certificate for $\StateSpaceModelUp$}
\label{ch:concrete-instances-statespacemodel-namecert}

The $\StateSpaceModelUp$ interface records the finite state-transition packet shared by the control-facing certificates. Its BEDC surface consumes $\NameCert_{\DynSystemUp}$ for transition rows, $\NameCert_{\MatrixUp}$ for displayed matrices, $\NameCert_{\VecSpaceUp}$ for state, input, and output rows, and $\NameCert_{\LinMapUp}$ for the linear maps. The textbook reference point is Kailath, \emph{Linear Systems} (1980).

The dependency anchors are $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\ControlObservabilityUp$, $\ControlControllabilityUp$, $\KalmanFilterUp$, $\LQRUp$, and $\RiccatiUp$. The chapter names only the finite carrier consumed by those certificates, not a host trajectory space or an analytic realization theorem.

\section{Finite state-transition carrier}
\label{sec:statespacemodel-carrier}

\begin{definition}[StateSpaceModel finite BHist carrier]
\label{def:statespacemodel-carrier}
A $\StateSpaceModelUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
(X,U,Y,A,B,C,P,L)
$$
whose displayed rows are:
\begin{enumerate}
\item a state row $X$, an input row $U$, and an output row $Y$ read through $\VecSpaceUp$;
\item a transition matrix row $A$, an input-map matrix row $B$, and an observation-map matrix row $C$ read through $\MatrixUp$;
\item linear-map rows for $A:X\to X$, $B:U\to X$, and $C:X\to Y$ read through $\LinMapUp$;
\item a displayed finite transition ledger $x,u\mapsto Ax+Bu$ and observation ledger $x\mapsto Cx$ read through $\DynSystemUp$;
\item $\Cont$ routes for the transition, input, observation, and readback rows;
\item $\hsame$ transports for the state, input, output, matrix, linear-map, transition, observation, $\Cont$, and provenance rows;
\item $\mathsf{Pkg}$ provenance row $P$ naming the consumed $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, and $\LinMapUp$ certificates;
\item a hidden-data ledger $L$ recording that only the displayed rows are exported.
\end{enumerate}
No host trajectory space, analytic semigroup, probability measure, infinite-horizon limit, external realization object, or unlogged state stream is a coordinate of the carrier.
\end{definition}

\begin{definition}[StateSpaceModel component classifier]
\label{def:statespacemodel-classifier}
The $\StateSpaceModelUp$ classifier compares two accepted packets componentwise. It compares the displayed state, input, and output traces through $\VecSpaceUp$; the transition, input-map, and observation-map rows through $\MatrixUp$ and $\LinMapUp$; the finite transition and observation ledgers through $\DynSystemUp$; and the provenance through the named $\Cont$, $\hsame$, and $\mathsf{Pkg}$ rows.

Two packets are classified together exactly when all displayed trace rows and all displayed provenance rows are $\hsame$-matched in this componentwise sense. The classifier has no coordinate for comparing hidden trajectories, host probability spaces, analytic flow objects, or limiting behavior.
\end{definition}

\section{Control handoff surface}
\label{sec:statespacemodel-control-handoff}

\begin{theorem}[StateSpaceModel NameCert obligation surface]
\label{thm:statespacemodel-namecert-obligation-surface}
The local $\NameCert_{\StateSpaceModelUp}$ obligation surface consists of five finite rows:
\begin{enumerate}
\item carrier: the finite packet of \autoref{def:statespacemodel-carrier};
\item classifier: the componentwise comparison of \autoref{def:statespacemodel-classifier};
\item transport: $\hsame$ transport of state, input, output, matrix, linear-map, transition, observation, $\Cont$, and $\mathsf{Pkg}$ rows preserves accepted packets;
\item finite trace ledger: every visible transition or observation read is one of the displayed $Ax+Bu$ or $Cx$ ledger rows;
\item hidden-data ledger: the packet records that host trajectories, analytic realizations, stochastic data, and infinite-horizon objects are outside the exported carrier.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.StateSpaceModelUp.StateSpaceModelPacket\_semantic\_name\_certificate}
\begin{proof}
Start with the carrier rows. They enumerate exactly the finite state, input, output, matrix, linear-map, transition, observation, continuation, transport, provenance, and hidden-ledger coordinates.

The classifier row is the componentwise comparison of those coordinates. Transport replaces each displayed coordinate by its $\hsame$ match and then repacks the same finite tuple, so accepted packets remain accepted.

The trace ledger rows are projections from the displayed transition and observation entries. Since the hidden-data ledger is also a coordinate of the packet, every consumer can see the boundary saying that the excluded host and limiting objects are not part of the exported surface.
\end{proof}
\leanchecked{BEDC.Derived.StateSpaceModelUp.StateSpaceModelPacket\_namecert\_obligation\_surface}

\begin{theorem}[StateSpaceModel control handoff]
\label{thm:statespacemodel-control-handoff}
The control-facing certificates $\KalmanFilterUp$, $\LQRUp$, $\ControlObservabilityUp$, $\ControlControllabilityUp$, and $\RiccatiUp$ may consume a $\StateSpaceModelUp$ packet only through the displayed finite state, input, output, transition, input-map, observation-map, trace-ledger, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows of \autoref{def:statespacemodel-carrier}. A downstream control certificate cannot demand an unlogged trajectory space, analytic flow, stochastic model, or limiting algebraic object from this handoff.
\end{theorem}
\leanchecked{BEDC.Derived.StateSpaceModelUp.StateSpaceModelPacket\_control\_handoff\_transport}
\begin{proof}
Read a downstream control request as a projection from the accepted carrier. The Kalman and Riccati consumers can project matrix, vector, covariance-facing, transition, and observation rows; the LQR consumer can project state, input, cost-adjacent transition, and horizon-facing rows; and the observability and controllability consumers can project the displayed $C$ and $B$ faces together with the transition row $A$.

All of these projections are among the finite rows named in \autoref{def:statespacemodel-carrier}. The classifier of \autoref{def:statespacemodel-classifier} transports the same rows componentwise, so the handoff remains stable under representative change.

The excluded objects are not packet coordinates. Therefore no listed control-facing certificate can recover them from the $\StateSpaceModelUp$ handoff alone.
\end{proof}

\begin{theorem}[StateSpaceModel ledger boundary]
\label{thm:statespacemodel-ledger-boundary}
The $\StateSpaceModelUp$ ledger excludes host trajectory spaces, analytic semigroup objects, probability measures, and infinite-horizon limits. Every consumer-visible read factors through the displayed finite $\mathsf{BHist}$ rows for $X$, $U$, $Y$, $A$, $B$, $C$, finite transition and observation traces, $\hsame$ transport, $\Cont$ routing, and $\mathsf{Pkg}$ provenance.
\end{theorem}
\begin{proof}
Project the accepted packet to its visible rows. The carrier lists state, input, output, matrix, linear-map, transition, observation, transport, continuation, provenance, and hidden-ledger entries, and no additional coordinate is available.

The hidden-data ledger states the exclusion boundary. A host trajectory space, analytic semigroup, probability measure, or infinite-horizon limit would require an additional coordinate or a separate certificate, so it cannot be read from this packet.

Thus every consumer-visible read is a finite $\mathsf{BHist}$ projection from the displayed state-space rows.
\end{proof}

\begin{theorem}[StateSpaceModel obligation closure]
\label{thm:statespacemodel-obligation-closure}
\autoref{def:statespacemodel-carrier},
\autoref{def:statespacemodel-classifier},
\autoref{thm:statespacemodel-namecert-obligation-surface},
\autoref{thm:statespacemodel-control-handoff}, and
\autoref{thm:statespacemodel-ledger-boundary} exhaust the finite
$\NameCert_{\StateSpaceModelUp}$ obligation surface over $\DynSystemUp$,
$\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\Cont$, $\hsame$, and $\Pkg$ rows.

Every downstream control certificate reads only these finite rows and their
displayed handoff boundaries.
\end{theorem}
\begin{proof}
Project the carrier coordinates. The visible tuple contains the state, input,
output, matrix, linear-map, transition, observation, continuation, transport,
package, and hidden-data ledger rows, and the classifier compares exactly those
coordinates componentwise.

The NameCert obligation theorem records the same rows as the local certificate
surface. The control handoff theorem then restricts Kalman, LQR,
controllability, observability, and Riccati consumers to the displayed finite
coordinates and trace ledgers.

The ledger-boundary theorem accounts for the excluded host trajectory,
analytic-flow, stochastic, and infinite-horizon objects. Since no downstream
control certificate can read outside the listed rows, the finite obligation
surface is exhausted.
\end{proof}

\begin{theorem}[StateSpaceModel public finite-transition export]
\label{thm:statespacemodel-public-finite-transition-export}
\autoref{def:statespacemodel-carrier},
\autoref{def:statespacemodel-classifier},
\autoref{thm:statespacemodel-namecert-obligation-surface},
\autoref{thm:statespacemodel-control-handoff},
\autoref{thm:statespacemodel-ledger-boundary}, and
\autoref{thm:statespacemodel-obligation-closure} jointly export the public
finite $\StateSpaceModelUp$ interface over $\DynSystemUp$, $\MatrixUp$,
$\VecSpaceUp$, $\LinMapUp$, $\Cont$, $\hsame$, and $\Pkg$ rows.

Kalman, LQR, controllability, observability, and Riccati consumers read only
the displayed finite state, input, output, transition, input-map,
observation-map, trace-ledger, transport, continuation, provenance, and local
name rows.
\end{theorem}
\begin{proof}
Project the carrier rows. They display the state, input, output, matrix,
linear-map, transition, observation, trace, continuation, transport, package,
hidden-data ledger, and local naming coordinates used by the public
$\StateSpaceModelUp$ packet.

Invoke the classifier and the $\NameCert$ obligation surface. Together they
make the componentwise comparison and the local certificate boundary depend
only on the displayed $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$,
$\Cont$, $\hsame$, and $\Pkg$ rows.

Use the control handoff, ledger boundary, and obligation closure to restrict
downstream Kalman, LQR, controllability, observability, and Riccati reads to
those finite rows. The same boundary excludes host trajectories, analytic
semigroups, stochastic data, and infinite-horizon limits from the exported
interface.
\end{proof}

\begin{theorem}[StateSpaceModel public interface boundary]
\label{thm:statespacemodel-public-interface-boundary}
The public $\StateSpaceModelUp$ interface exports exactly the finite state, input, output, transition, input-map, observation-map, trace-ledger, classifier-transport, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows isolated by \autoref{def:statespacemodel-carrier}, \autoref{def:statespacemodel-classifier}, \autoref{thm:statespacemodel-control-handoff}, \autoref{thm:statespacemodel-ledger-boundary}, and \autoref{thm:statespacemodel-obligation-closure}. No further public coordinate is part of the certificate boundary.
\end{theorem}
\begin{proof}
Project the carrier and classifier definitions. They expose the finite state, input, output, transition, input-map, observation-map, trace-ledger, classifier-transport, continuation, sameness, package, and naming rows carried by a $\StateSpaceModelUp$ packet.

Compose those projections with \autoref{thm:statespacemodel-control-handoff}. The handoff routes every control-facing read through the same displayed rows, so no consumer-facing state-space coordinate can be read outside the finite certificate surface.

Apply \autoref{thm:statespacemodel-ledger-boundary} and \autoref{thm:statespacemodel-obligation-closure} to close the projection under the visible ledger and obligation rows. These two results repack the projected rows as the public interface boundary and show that the exported surface is exhausted by the listed data.

The boundary therefore excludes host trajectory spaces, analytic semigroups, stochastic models, infinite-horizon limits, controllability tests, observability tests, filtering optimality, regulator optimality, and standard bridge data.
\end{proof}

\closureat{StateSpaceModelUp}{seedStr}
\closureat{StateSpaceModelUp}{obligationStr}
\closureat{StateSpaceModelUp}{scopedStr}

\begin{closurestatus}{\StateSpaceModelUp}
  \constructivestory{A state-space-model packet is seeded by finite $\mathsf{BHist}$ rows for state, input, output, transition, input-map, observation-map, transition and observation traces, $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and a hidden-data ledger.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The scoped surface binds the finite state, input, output, matrix, linear-map, transition, observation, trace-ledger, transport, continuation, provenance, and name rows to $\DynSystemUp$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\Cont$, $\hsame$, and $\Pkg$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host trajectory spaces, analytic semigroups, probability measures, infinite-horizon limits, controllability tests, observability tests, filtering optimality, regulator optimality, or a standard bridge.}
  \upgradepath{Public closure requires a standard finite-transition bridge and a consumer-facing $\StateSpaceModelUp$ export theorem over the scoped finite state-transition packet and its control handoff boundary.}
\end{closurestatus}
