\chapter{A Conditional Certificate Boundary for $\RealAnalyticUp$}
\label{ch:concrete-instances-real-analytic-namecert}

This chapter records the proof obligations for the constructive transcendental package $\RealAnalyticUp$ over $\RatUp$, $\StreamNameUp$, $\RegSeqRat$, and $\RealUp$ without asserting a completed $\NameCert(\RealAnalyticUp)$. The package is organized around five interrelated objects on $\RealUp$-history representations: the constant $\pi$, the exponential $\exp$, the logarithm $\log$ on positive arguments, and the trigonometric pair $\sin / \cos$. The construction boundary sits above $\RatUp$ (\autoref{ch:concrete-instances-rat-namecert}) for the rational base, $\StreamNameUp$ for explicit unary streams, $\RegSeqRat$ for regular Cauchy data, and $\RealUp$ (\autoref{ch:concrete-instances-real-namecert}) for the eventual real-history carrier. Every series below is given by an explicit unary-history term, every modulus is a total function on the unary index domain, and every passage from regular rational data to a real-history value requires a supplied limit witness from the Phase Real and Completion obligations.

\section{Constructive \(\pi\) via Leibniz acceleration}
\label{sec:real-analytic-pi}

\begin{definition}[Leibniz partial sum]
\label{def:real-analytic-leibniz-partial-sum}
For unary index \(n\), the Leibniz partial sum predicate \(\mathsf{LeibPart}(n, S_n)\) holds when \(S_n\) is the explicit \(\RatUp\)-history obtained by summing the first \(n\) terms of \(\sum_{k \geq 0} (-1)^k / (2k+1)\) via unary recursion using \(\RatUp\) addition and signed-fraction subtraction.
\end{definition}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticLeibnizPartialSum}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticLeibnizPartSum}

\begin{lemma}[Leibniz alternating-series Cauchy modulus]
\label{lem:real-analytic-leibniz-cauchy}
The sequence of partial sums \(S_n\) is a \(\RegSeqRat\)-Cauchy sequence with explicit modulus \(N(k) := 2^{k+1}\): for all unary \(m, n \geq N(k)\), \(|4 S_m - 4 S_n| < 2^{-k}\).
\end{lemma}
\begin{proof}
Pair adjacent terms after index \(N(k)\); each pair has magnitude bounded by the next omitted term \(1/(2N(k)+1)\). The alternating bound gives \(|4 S_m - 4 S_n| \leq 4/(2N(k)+1) < 2^{-k}\) for the chosen \(N(k)\).
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticLeibnizPartSum\_index\_result\_unary}

\begin{definition}[Constructive \(\pi\)]
\label{def:real-analytic-pi}
$\mathsf{Pi}$ is a $\RealUp$-history candidate only together with a supplied limit witness from the Phase Real and Completion obligations, applied to the $\RegSeqRat$ Cauchy data of \autoref{lem:real-analytic-leibniz-cauchy} for the rescaled sequence $(4 S_n)_n$. The local data of this chapter is the $\RegSeqRat$ name and its explicit modulus inherited from the alternating-series bound.
\end{definition}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticPiBoundary}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticPiBoundary\_leibniz\_index\_result\_unary}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticPiLocalData}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticPiCandidate}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticPi}

\begin{theorem}[Series variant equivalence boundary]
\label{thm:real-analytic-series-variant-equivalence-boundary}
Let $p_1$ and $p_2$ be two explicit $\pi$ stream presentations, such as the
Leibniz rescaling and a faster Machin or Chudnovsky presentation. A conclusion
$\mathsf{RealClassifier}(r_1,r_2)$ is available for their $\RealUp$ histories
only under supplied rows: both $p_1$ and $p_2$ satisfy the relevant
$\RegSeqRat$ carrier obligations, a $\RegSeqRat$ classifier witness relates the
two stream names, both streams have supplied $\RealUp$ limit witnesses with
targets $r_1$ and $r_2$, and the supplied $\RealUp$ limit-uniqueness row
transports the stream classifier to the real-history classifier.
\end{theorem}
\begin{proof}
Use the supplied $\RegSeqRat$ classifier witness first. The two
carrier-obligation rows make this witness a relation between legitimate regular
rational stream names, so it is eligible for transport by the real-completion
interface.

Apply the two supplied $\RealUp$ limit witnesses next. They place $p_1$ and
$p_2$ in the real-history carrier as $r_1$ and $r_2$, without adding any
independent equality claim between the analytic presentations.

Finally invoke the supplied limit-uniqueness row. Its transport clause takes the
$\RegSeqRat$ classifier witness between the source streams and the two limit
witnesses, and returns the displayed conclusion
$\mathsf{RealClassifier}(r_1,r_2)$.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticLeibnizPartSum\_pointwise\_hsame\_deterministic}

\begin{theorem}[Real-analytic supplied limit consumption boundary]
\label{thm:real-analytic-supplied-limit-consumption-boundary}
Let $P$ be any local analytic stream package used in this chapter: the Leibniz
$\mathsf{Pi}$ stream, an exponential partial-sum stream, a logarithm bisection
stream, or a sine or cosine partial-sum stream. A displayed $\RealUp$ output
$r$ for $P$ is consumable only through the following supplied rows:
\begin{enumerate}
\item a $\RegSeqRat$ carrier witness for the underlying $\mathsf{BHist}$ stream
name and its unary modulus;
\item a $\RealUp$ limit witness naming $r$ as the target history of that stream;
\item the Phase Real and Completion limit-transport or limit-uniqueness row that
connects the supplied stream witness to the public $\RealUp$ carrier and
classifier surface.
\end{enumerate}
If two such packages $P$ and $Q$ are related by a supplied $\RegSeqRat$
classifier witness and their supplied targets are $r$ and $s$, then the only
conclusion licensed by those rows is $\mathsf{RealClassifier}(r,s)$. The rows do
not supply $\RealUp$ completeness, $\RealUp$ arithmetic, $\RealUp$ order, metric
completeness, or a standard bridge.
\end{theorem}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticSuppliedLimitConsumption\_boundary}
\begin{proof}
The transport pattern is the one isolated in
\autoref{thm:real-analytic-series-variant-equivalence-boundary}. The
$\RegSeqRat$ classifier is applied at the stream-name level, the two supplied
limit witnesses name the target histories, and the supplied Phase Real and
Completion uniqueness row returns only the displayed real-history classifier.

For the stream-side inputs, use the local obligation package of
\autoref{thm:real-analytic-local-stream-obligations-only}. Its unary and
pointwise transport clauses cover the finite partial-sum witnesses used by the
Leibniz, exponential, logarithm-bisection, sine, and cosine packages, but they do
not create a $\RegSeqRat$ carrier row or a $\RealUp$ limit row.

The public rows available after a limit witness are exactly the rows exposed by
\autoref{thm:realup-public-certificate-export}: carrier, classifier, stability,
transport, finite observation, ledger, and seal data for the scoped $\RealUp$
surface. That public boundary explicitly excludes completion theorems,
arithmetic and order closure, metric completeness, and standard-bridge data, so
the stated classifier is the maximal conclusion licensed by the supplied rows.
\end{proof}

\section{Constructive exponential}
\label{sec:real-analytic-exp}

\begin{definition}[Exponential partial sum]
\label{def:real-analytic-exp-part}
For \(\RealUp\)-history \(x\) and unary index \(n\), the predicate \(\mathsf{ExpPart}(x, n, S_n)\) holds when \(S_n\) is the partial sum \(\sum_{k=0}^{n} x^k / k!\) computed by unary recursion: powers \(x^k\) via iterated \(\RealUp\) multiplication, factorials \(k!\) via the unary factorial of \(\PrimeUp\) (\autoref{ch:concrete-instances-prime-namecert}), and division as \(\RealUp\)-multiplicative inverse against the positive unary denominator.
\end{definition}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticExpPart}

\begin{lemma}[Real-analytic complex partial-sum indices are unary]
\label{lem:real-analytic-complex-part-sum-index-unary}
For the real-analytic series interface, every closed complex partial-sum
witness has unary index.
\end{lemma}
\begin{proof}
Induct on the closed complex partial-sum witness. The zero constructor has the
empty index, and the successor constructor applies the unary successor closure
to the predecessor index.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticComplexPartSum\_index\_unary}

\begin{theorem}[Real-analytic complex partial-sum results are unary]
\label{thm:real-analytic-complex-part-sum-result-unary}
For the real-analytic series interface, if the chosen zero history is unary and
each term history is unary on unary indices, then every closed complex
partial-sum witness has unary result.
\end{theorem}
\begin{proof}
Induct on the closed complex partial-sum witness. The base is the supplied
unary zero history. In the successor case, an inner induction on the
predecessor partial-sum witness supplies unaryness of the predecessor index,
the term hypothesis supplies unaryness of the next term, and unary continuation
closure gives the successor result.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticLeibnizPartSum\_successor\_result\_deterministic}

\begin{theorem}[Real-analytic complex partial-sum indices and results are unary]
\label{thm:real-analytic-complex-part-sum-index-result-unary}
For the real-analytic series interface, if the chosen zero history is unary and
each term history is unary on unary indices, then every closed complex
partial-sum witness has both unary index and unary result.
\end{theorem}
\begin{proof}
Induct on the closed complex partial-sum witness. The base has empty unary
index and the supplied unary zero result. In the successor case, the induction
hypothesis gives unaryness of the predecessor index and result; closure under
\(\Eone\) gives the successor index, the term hypothesis gives the next unary
term, and unary continuation closure gives the successor result.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticComplexPartSum\_index\_result\_unary}

\begin{theorem}[Real-analytic complex absolute partial-sum indices and results are unary]
\label{thm:real-analytic-complex-abs-part-sum-index-result-unary}
For the real-analytic absolute-series interface, if the chosen zero history is
unary and each modulus history is unary on unary indices, then every closed
absolute complex partial-sum witness has both unary index and unary result.
\end{theorem}
\begin{proof}
Induct on the closed absolute partial-sum witness. The zero case is the empty
unary index with the supplied unary zero result. In the successor case, the
induction hypothesis supplies the predecessor index and result; unary
\(\Eone\)-closure supplies the successor index, the modulus hypothesis supplies
the unary summand, and unary continuation closure supplies the successor
result.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticComplexAbsPartSum\_index\_result\_unary}

\begin{theorem}[Real-analytic pointwise complex partial-sum target unaryness]
\label{thm:real-analytic-complex-part-sum-pointwise-result-unary-transport}
For two complex term families $c,d:\mathsf{BHist}\to\mathsf{BHist}$, suppose
the chosen zero histories are $\hsame$, the source zero history is unary, each
$c(m)$ is unary on unary indices, and $c(m)\hsame d(m)$ at every unary index.
If $n$ is unary and closed partial-sum witnesses compute results $S$ for
$(zero,c)$ and $T$ for $(zero',d)$ at $n$, then $T$ is unary.
\end{theorem}
\begin{proof}
The source partial-sum unary theorem gives unaryness of $S$. Pointwise
$\hsame$ determinacy for complex partial sums identifies $S$ and $T$ under
$\hsame$, using the zero comparison, the pointwise term comparison, and the
unary index witness. Unary history closure under $\hsame$ gives unaryness of
$T$.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticComplexPartSum\_pointwise\_result\_unary\_transport}

\begin{theorem}[Closed pointwise complex partial-sum unary transport]
\label{thm:real-analytic-complex-part-sum-closed-pointwise-index-result-unary-transport}
For two complex term families $c,d:\mathsf{BHist}\to\mathsf{BHist}$, suppose
the chosen zero histories $zero$ and $zero'$ are $\hsame$, the source zero
history $zero$ is unary, each $c(m)$ is unary whenever $m$ is unary, and
$c(m)\hsame d(m)$ for every unary index $m$. If closed partial-sum witnesses
compute $S$ for $(zero,c)$ and $T$ for $(zero',d)$ at the same index $n$, then
$\mathsf{UnaryHistory}(n)$ and $\mathsf{UnaryHistory}(T)$.
\end{theorem}
\begin{proof}
Apply the complex partial-sum index unary theorem to the source witness. This
turns the closed source computation into the unary index witness
$\mathsf{UnaryHistory}(n)$.

With this derived index witness, apply the complex partial-sum index/result
unary theorem to the same source witness. The hypotheses on $zero$ and $c$
give $\mathsf{UnaryHistory}(S)$.

Pointwise $\hsame$ determinacy for complex partial sums identifies $S$ and
$T$ under $\hsame$, using the comparison of the zero histories and the
pointwise comparison $c(m)\hsame d(m)$ at unary indices. Unary history
transport along $\hsame$ carries $\mathsf{UnaryHistory}(S)$ to
$\mathsf{UnaryHistory}(T)$.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticComplexPartSum\_closed\_pointwise\_index\_result\_unary\_transport}

\begin{theorem}[Real-analytic pointwise absolute partial-sum target unaryness]
\label{thm:real-analytic-complex-abs-part-sum-pointwise-result-unary-transport}
For two modulus families $\mathsf{modulus},\mathsf{modulus}':
\mathsf{BHist}\to\mathsf{BHist}$, suppose the chosen zero histories are
$\hsame$, the source zero history is unary, each source modulus value is unary
on unary indices, and the two modulus families are pointwise $\hsame$ on unary
indices. If $n$ is unary and closed absolute partial-sum witnesses compute
results $M$ and $T$ at $n$, then $T$ is unary.
\end{theorem}
\begin{proof}
The source absolute partial-sum unary theorem gives unaryness of $M$.
Pointwise $\hsame$ determinacy for absolute partial sums identifies $M$ and
$T$ under $\hsame$, using the zero comparison, the pointwise modulus
comparison, and the unary index witness. Unary history closure under $\hsame$
gives unaryness of $T$.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticComplexAbsPartSum\_pointwise\_result\_unary\_transport}

\begin{theorem}[Closed pointwise absolute partial-sum unary transport]
\label{thm:real-analytic-complex-abs-part-sum-closed-pointwise-index-result-unary-transport}
For two modulus families $m,m':\mathsf{BHist}\to\mathsf{BHist}$, suppose
the chosen zero histories $zero$ and $zero'$ are $\hsame$, the source zero
history $zero$ is unary, each $m(i)$ is unary whenever $i$ is unary, and
$m(i)\hsame m'(i)$ for every unary index $i$. If closed absolute partial-sum
witnesses compute $M$ for $(zero,m)$ and $T$ for $(zero',m')$ at the same
index $n$, then $\mathsf{UnaryHistory}(n)$ and $\mathsf{UnaryHistory}(T)$.
\end{theorem}
\begin{proof}
Apply the absolute partial-sum index/result unary theorem to the source
witness. The source zero unaryness and the unaryness of $m(i)$ on unary
indices give both $\mathsf{UnaryHistory}(n)$ and $\mathsf{UnaryHistory}(M)$.

Using the derived unary index witness, apply the pointwise absolute partial-sum
target unary transport theorem to the two closed computations. The zero
comparison, source modulus unaryness, and pointwise comparison
$m(i)\hsame m'(i)$ at unary indices give $\mathsf{UnaryHistory}(T)$.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticComplexAbsPartSum\_closed\_pointwise\_index\_result\_unary\_transport}

\begin{theorem}[Real-analytic local stream unary package]
\label{thm:real-analytic-local-stream-obligations-only}
Let $zero,zero':\mathsf{BHist}$ be chosen zero histories. Let
$c,d:\mathsf{BHist}\to\mathsf{BHist}$ be complex term families, and let
$m,m':\mathsf{BHist}\to\mathsf{BHist}$ be absolute-modulus families. Assume
$\mathsf{UnaryHistory}(zero)$, $zero\hsame zero'$, each $c(i)$ is unary at
unary $i$, each $m(i)$ is unary at unary $i$, and the pointwise comparisons
$c(i)\hsame d(i)$ and $m(i)\hsame m'(i)$ hold at every unary index $i$. Then
the local stream side supplies exactly the following four obligations:
\begin{enumerate}
\item every closed witness $\mathsf{ComplexPartSum}(zero,c,n,S)$ gives
$\mathsf{UnaryHistory}(n)$ and $\mathsf{UnaryHistory}(S)$;
\item if $n$ is unary and closed pointwise witnesses
$\mathsf{ComplexPartSum}(zero,c,n,S)$ and
$\mathsf{ComplexPartSum}(zero',d,n,T)$ are given, then
$\mathsf{UnaryHistory}(T)$;
\item every closed witness $\mathsf{ComplexAbsPartSum}(zero,m,n,M)$ gives
$\mathsf{UnaryHistory}(n)$ and $\mathsf{UnaryHistory}(M)$;
\item if $n$ is unary and closed pointwise witnesses
$\mathsf{ComplexAbsPartSum}(zero,m,n,M)$ and
$\mathsf{ComplexAbsPartSum}(zero',m',n,T)$ are given, then
$\mathsf{UnaryHistory}(T)$.
\end{enumerate}
This package contains only finite stream-side data; the $\RegSeqRat$ carrier
row, the $\RealUp$ limit witness row, and the limit-uniqueness classifier row
remain the separate supplied hypotheses of
\autoref{thm:real-analytic-certificate-boundary}.
\end{theorem}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticLocalStream\_obligations\_package}
\begin{proof}
For the complex closed-source clause, apply
\autoref{thm:real-analytic-complex-part-sum-index-result-unary}. Its hypotheses
are exactly the unary zero history and unaryness of $c(i)$ on unary indices.

For the complex pointwise target clause, apply
\autoref{thm:real-analytic-complex-part-sum-pointwise-result-unary-transport}.
The hypotheses provide the comparison $zero\hsame zero'$, the source unary
zero history, unaryness of the source term family, the pointwise comparisons
$c(i)\hsame d(i)$, and the displayed unary index.

For the absolute closed-source clause, apply
\autoref{thm:real-analytic-complex-abs-part-sum-index-result-unary}. Its
hypotheses are the same unary zero history and unaryness of $m(i)$ on unary
indices.

For the absolute pointwise target clause, apply
\autoref{thm:real-analytic-complex-abs-part-sum-pointwise-result-unary-transport}.
The hypotheses provide the zero comparison, the source unary zero history, the
source modulus unaryness, the pointwise comparisons $m(i)\hsame m'(i)$, and the
displayed unary index. These four applications do not create a
$\RegSeqRat$ name, a $\RealUp$ limit, or a real-history classifier; those rows
remain external to the finite stream package.
\end{proof}

\begin{lemma}[Exponential Cauchy modulus on bounded inputs]
\label{lem:real-analytic-exp-cauchy}
For every \(\RealUp\)-history \(x\) with \(|x| \leq B\) (explicit unary upper bound \(B\)), the partial sums \(\mathsf{ExpPart}(x, n, S_n)\) form a \(\RegSeqRat\)-Cauchy sequence with explicit modulus \(N(k) := 2 B + k\): for all \(m, n \geq N(k)\), \(|S_m - S_n| < 2^{-k}\).
\end{lemma}
\begin{proof}
For \(n \geq 2B\), the ratio of successive terms \(|x|/(n+1)\) is bounded by \(1/2\), so the tail majorizes a geometric series with ratio \(1/2\). The geometric-series modulus \(2^{-(n - 2B)}\) gives the explicit \(N(k)\) above.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticExp\_local\_witness\_unary}

\begin{definition}[Constructive \(\exp\)]
\label{def:real-analytic-exp}
For a $\RealUp$-history $x$, $\mathsf{Exp}(x, y)$ holds in this chapter only relative to a supplied $\RealUp$ limit witness from the Phase Real and Completion obligations for the partial sums $\mathsf{ExpPart}(x, \cdot, \cdot)$ and the Cauchy modulus of \autoref{lem:real-analytic-exp-cauchy}. The local witness includes the explicit input bound $B$ and the modulus $N$.
\end{definition}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticExp}

\begin{theorem}[Exponential additivity]
\label{thm:real-analytic-exp-add}
For $\RealUp$-histories $x$ and $y$, assume supplied $\RealAlgOrder$ rows for $x+y$, products in $\RealUp$, powers $x^k$, $y^k$, and $(x+y)^k$, the unary factorial-denominator inverses, and the Cauchy-product comparison between the partial sums of $\mathsf{ExpPart}(x+y,\cdot,\cdot)$ and the product of the partial sums for $x$ and $y$. Assume also supplied $\RealUp$ limit witnesses and their limit-uniqueness classifier rows for $\mathsf{Exp}(x,e_x)$, $\mathsf{Exp}(y,e_y)$, and $\mathsf{Exp}(x+y,e_{x+y})$. Under exactly these rows, $\mathsf{RealClassifier}(e_{x+y}, e_x \cdot e_y)$ holds.
\end{theorem}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticExp\_product\_witness\_unary}
\begin{proof}
The $\RealAlgOrder$ rows make the finite algebraic comparison meaningful: addition supplies $x+y$, multiplication supplies the product side, powers and factorial-denominator inverses supply the displayed exponential terms, and the Cauchy-product row compares the two regular rational partial-sum families.

The three supplied $\RealUp$ limit witnesses place those regular rational families in the real-history carrier. Their supplied classifier uniqueness rows identify the common limit, giving $\mathsf{RealClassifier}(e_{x+y}, e_x \cdot e_y)$.
\end{proof}

\section{Constructive logarithm on positives}
\label{sec:real-analytic-log}

\begin{definition}[Logarithm via inverse-of-\(\exp\) bisection]
\label{def:real-analytic-log}
For a positive $\RealUp$-history $x$ (i.e.\ apartness witness $x \neq 0$ with positive sign), $\mathsf{Log}(x, y)$ holds in this chapter only relative to a supplied $\RealUp$ limit witness for the dyadic bisection sequence on unary precision $k$: at each precision, locate the dyadic-rational interval $[y_k, y_k + 2^{-k}]$ such that $\exp(y_k) \leq x < \exp(y_k + 2^{-k})$ (decidable on rational representations using \autoref{def:real-analytic-exp}), and assemble the local $\RegSeqRat$ data with modulus $N(k) = k + \lceil \log_2(1/x) \rceil$.
\end{definition}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticLog}

\begin{theorem}[Logarithm is the inverse of \(\exp\) on positives]
\label{thm:real-analytic-log-exp-inverse}
For a $\RealUp$-history $x$, assume supplied positivity and apartness rows for $x$, supplied dyadic bisection rows locating rational intervals $[y_k,y_k+2^{-k}]$ with $\exp(y_k) \leq x < \exp(y_k+2^{-k})$, supplied rational-embedding rows for the dyadic endpoints and exponential comparisons, and supplied $\RealUp$ limit witnesses with limit-uniqueness classifier rows for $\mathsf{Log}(x,y)$ and $\mathsf{Exp}(y,e_y)$. Under these rows, $\mathsf{RealClassifier}(e_y,x)$ holds. Conversely, for a $\RealUp$-history $z$, assume the supplied $\mathsf{Exp}(z,w)$ limit witness, the supplied positivity row for $w$, the same bisection and rational-embedding rows applied to $w$, and the supplied uniqueness rows for $\mathsf{Log}(w,z')$; then $\mathsf{RealClassifier}(z',z)$ holds.
\end{theorem}
\begin{proof}
For the forward direction, the supplied positivity row permits the bisection search, and the dyadic and rational-embedding rows provide the rational comparisons used at every precision. The supplied limit witness for $\mathsf{Log}(x,y)$ records the bisection limit, while the supplied witness for $\mathsf{Exp}(y,e_y)$ records the exponential value of that limit.

The supplied uniqueness rows then identify the real-history value of $\exp(y)$ with the original positive input $x$. The reverse direction uses the supplied $\mathsf{Exp}(z,w)$ row as the positive input for the same bisection package, and the uniqueness row for $\mathsf{Log}(w,z')$ identifies the recovered logarithm with $z$.
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticLogExpInverse\_supplied\_boundary\_unary}

\begin{theorem}[Logarithm of a unary natural]
\label{thm:real-analytic-log-unary}
For positive unary natural $n$, assume supplied rational-embedding rows sending the unary numeral $\Eone^n(\emp)$ into the positive $\RealUp$ carrier, supplied positivity and apartness rows for that embedded value, supplied dyadic bisection rows with the modulus determined by the unary length of $n$, and supplied $\RealUp$ limit uniqueness rows for the resulting $\mathsf{Log}(\Eone^n(\emp),y_n)$ witness. Under these rows, $y_n$ is the constructive $\log n$ input used by the Dirichlet term construction (\autoref{ch:concrete-instances-dirichlet-series-namecert}).
\end{theorem}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticLog\_hsame\_transport\_value\_unary}
\begin{proof}
The rational-embedding rows place the unary numeral inside $\RealUp$ with the required positive sign data. The bisection rows then specialize \autoref{def:real-analytic-log} to this embedded value and supply the precision modulus determined by the unary length of $n$.

The supplied limit witness and uniqueness rows turn the bisection stream into the real-history value $y_n$. No logarithm classifier conclusion is available before these rows are present.
\end{proof}

\section{Constructive sine and cosine}
\label{sec:real-analytic-trig}

\begin{definition}[Sine and cosine partial sums]
\label{def:real-analytic-trig-part}
For \(\RealUp\)-history \(x\) and unary index \(n\), \(\mathsf{SinPart}(x, n, S_n)\) and \(\mathsf{CosPart}(x, n, C_n)\) are the partial sums \(\sum_{k=0}^{n} (-1)^k x^{2k+1}/(2k+1)!\) and \(\sum_{k=0}^{n} (-1)^k x^{2k}/(2k)!\) respectively, computed by unary recursion as in \autoref{def:real-analytic-exp-part}.
\end{definition}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticTrigPart}

\begin{lemma}[Trigonometric Cauchy modulus]
\label{lem:real-analytic-trig-cauchy}
For every \(\RealUp\)-history \(x\) with \(|x| \leq B\), the partial sums \(\mathsf{SinPart}\) and \(\mathsf{CosPart}\) form \(\RegSeqRat\)-Cauchy sequences with explicit modulus \(N(k) := B^2 + k\). The bound is the alternating-series majorant: each term has magnitude bounded by the previous one once \(2k(2k+1) > B^2\).
\end{lemma}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticTrigPart\_pair\_index\_result\_unary}

\begin{definition}[Constructive \(\sin\) and \(\cos\)]
\label{def:real-analytic-sin-cos}
$\mathsf{Sin}(x, s)$ and $\mathsf{Cos}(x, c)$ hold in this chapter only relative to supplied $\RealUp$ limit witnesses from the Phase Real and Completion obligations for $\mathsf{SinPart}(x, \cdot, \cdot)$ and $\mathsf{CosPart}(x, \cdot, \cdot)$ respectively, using the explicit Cauchy moduli of \autoref{lem:real-analytic-trig-cauchy}.
\end{definition}
\leandef{BEDC.Derived.RealAnalyticUp.RealAnalyticSinCosCandidate}

\begin{theorem}[Pythagorean identity]
\label{thm:real-analytic-pythagorean}
For a $\RealUp$-history $x$, assume supplied $\RealAlgOrder$ rows for products, squares, addition, and the constant $\Eone(\emp)$, supplied product-stability rows for multiplying supplied sine and cosine limits, supplied trigonometric limit witnesses for $\mathsf{Sin}(x,s)$ and $\mathsf{Cos}(x,c)$, and supplied limit-uniqueness classifier rows comparing the regular rational partial sums for $s^2+c^2$ with the constant-one witness. Under these rows, $\mathsf{RealClassifier}(s^2 + c^2, \Eone(\emp))$ holds.
\end{theorem}
\begin{proof}
The supplied algebraic rows make $s^2+c^2$ and the constant-one comparison available in $\RealUp$. Product stability transports the supplied sine and cosine limit witnesses through the finite products needed to form the square terms.

The regular rational comparison is the usual cancellation between the odd-power and even-power partial sums, bounded by the trigonometric Cauchy modulus of \autoref{lem:real-analytic-trig-cauchy}. The supplied uniqueness classifier rows then identify the resulting value with $\Eone(\emp)$.
\end{proof}

\begin{theorem}[Sine vanishes at integer multiples of \(\pi\)]
\label{thm:real-analytic-sin-pi-multiples}
For every signed unary integer $n$, assume supplied $\RealAlgOrder$ rows for integer scalar multiplication $n \cdot \mathsf{Pi}$, addition of consecutive multiples of $\mathsf{Pi}$, products in the sine addition formula, and the zero constant $\emp$. Assume also a supplied constant $\mathsf{Pi}$ limit witness, supplied trigonometric limit witnesses for the required sine and cosine terms, supplied addition-formula rows for $\sin(a+b)$ and $\cos(a+b)$ at these arguments, supplied product-stability rows for the formula terms, and supplied limit-uniqueness classifier rows for the base values $\sin(0)$ and $\sin(\mathsf{Pi})$. Under these rows, $\mathsf{Sin}(n \cdot \mathsf{Pi},s)$ gives $\mathsf{RealClassifier}(s,\emp)$. In particular, the negative signed multiples supply the zero witness used in \autoref{ch:concrete-instances-zeta-zeros-namecert}.
\end{theorem}
\begin{proof}
The supplied $\mathsf{Pi}$ limit witness and scalar-multiplication rows make each integer multiple $n \cdot \mathsf{Pi}$ a legitimate $\RealUp$ argument. The trigonometric witnesses and classifier rows supply the base values $\sin(0)$ and $\sin(\mathsf{Pi})$ as zero.

For the induction step, the supplied addition-formula row rewrites $\sin((n+1)\mathsf{Pi})$ through $\sin(n\mathsf{Pi})\cos(\mathsf{Pi})+\cos(n\mathsf{Pi})\sin(\mathsf{Pi})$. Product stability transports the induction hypothesis and the base zero classifier through the product terms, and the supplied uniqueness row returns the classifier $\mathsf{RealClassifier}(s,\emp)$.
\end{proof}

\section{Certificate target}
\label{sec:real-analytic-cert-target}

\begin{theorem}[Real-analytic Real-completion dependency surface]
\label{thm:real-analytic-real-completion-dependency-surface}
Any admissible use of the local endpoint rows for $\mathsf{Pi}$, $\mathsf{Exp}$, $\mathsf{Log}$, $\mathsf{Sin}$, or $\mathsf{Cos}$ must factor through the following supplied Phase Real and Completion faces: the $\DyadicRatCore$ arithmetic and modulus rows for the relevant partial sums, the $\StreamNameUp$ observation-carrier and classifier rows, the $\RegSeqRat$ regularity and stream-classifier rows, the $\RealUp$ seal or limit-witness rows, and $\mathsf{RealClassifier}$ limit-uniqueness transport. The local partial-sum, Cauchy-modulus, parity-split, and addition-formula rows do not by themselves provide a $\RealUp$ endpoint classifier or a completed $\NameCert(\RealAnalyticUp)$.
\end{theorem}
\begin{proof}
For $\mathsf{Pi}$, \autoref{sec:real-analytic-pi} supplies the Leibniz partial-sum family and its explicit Cauchy modulus. Those rows are rational stream data only: the endpoint becomes a real-history object only after the supplied $\DyadicRatCore$ arithmetic, $\StreamNameUp$ observation, $\RegSeqRat$ regularity, $\RealUp$ limit witness, and $\mathsf{RealClassifier}$ uniqueness rows are present.

For $\mathsf{Exp}$, \autoref{sec:real-analytic-exp} supplies the power-series partial sums, the bounded-input modulus, and the local additivity row. The additivity statement uses supplied $\RealUp$ witnesses and classifier uniqueness for the three exponential endpoints; without those faces, the Cauchy-product comparison remains a regular-rational stream comparison and does not name a completed endpoint.

For $\mathsf{Log}$, \autoref{sec:real-analytic-log} supplies the inverse-of-exponential bisection scheme and the inverse relation under positivity, apartness, rational-embedding, and bisection hypotheses. The bisection rows produce a candidate stream, while the $\RealUp$ seal or limit witness and uniqueness transport are the supplied Completion faces that turn that stream into a usable logarithm endpoint.

For $\mathsf{Sin}$ and $\mathsf{Cos}$, \autoref{sec:real-analytic-trig} supplies the trigonometric partial sums, their shared modulus, the parity splits, and the addition-formula rows. The parity and addition formulas compare coefficient streams and transported product streams; they still require the supplied $\StreamNameUp$, $\RegSeqRat$, $\RealUp$, and uniqueness rows before either trigonometric endpoint has a real-history classifier.

Repacking these five cases gives exactly the dependency surface consumed by \autoref{thm:real-analytic-certificate-boundary}: every analytic endpoint enters through the displayed Phase Real and Completion faces, and every local calculation remains a proof obligation until those faces are supplied.
\end{proof}

\begin{closurestatus}{\RealAnalyticUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{thm:real-analytic-real-completion-dependency-surface} binds the paper-side seed scope to the supplied DyadicRatCore, StreamNameUp, RegSeqRat, RealUp, and RealClassifier dependency faces for the five displayed analytic endpoints.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RealAnalyticUp.real\_analytic\_certificate\_boundary}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a completed $\NameCert(\RealAnalyticUp)$, $\RealUp$ completeness, or standard bridges for the analytic endpoints.}
  \upgradepath{A higher closure grade requires checked carrier, classifier, exactness, ledger, and bridge rows for the analytic endpoint package over the completed RealUp surface.}
\end{closurestatus}

\begin{theorem}[$\RealAnalyticUp$ certificate boundary]
\label{thm:real-analytic-certificate-boundary}
Suppose the following machine-checked rows are supplied for the analytic construction over $\RatUp$, $\StreamNameUp$, $\RegSeqRat$, and $\RealUp$:
\begin{enumerate}
  \item \textbf{Dyadic rational core}: $\DyadicRatCore$ arithmetic, signed fractions, factorial denominators, powers, and positivity comparisons for the displayed series and bisection predicates.
  \item \textbf{Stream carrier}: $\StreamNameUp$ and $\RegSeqRat$ data for every displayed partial-sum family, including the explicit unary moduli of \autoref{lem:real-analytic-leibniz-cauchy}, \autoref{lem:real-analytic-exp-cauchy}, and \autoref{lem:real-analytic-trig-cauchy}.
  \item \textbf{Real carrier}: $\RealUp$ limit witnesses for $\mathsf{Pi}$, $\mathsf{Exp}$, $\mathsf{Log}$, $\mathsf{Sin}$, and $\mathsf{Cos}$, supplied from the Phase Real and Completion obligations.
  \item \textbf{Classifier}: limit uniqueness for the supplied $\RealUp$ witnesses, stated up to $\mathsf{RealClassifier}$.
  \item \textbf{Stability}: supplied conditional rows for additivity of $\exp$ (\autoref{thm:real-analytic-exp-add}), inverse relation $\log = \exp^{-1}$ (\autoref{thm:real-analytic-log-exp-inverse}), Pythagorean identity (\autoref{thm:real-analytic-pythagorean}), and $\pi$-multiple zeros of $\sin$ (\autoref{thm:real-analytic-sin-pi-multiples}), each with its theorem-site hypotheses for algebraic operations, bisection or Cauchy-product comparison, limit witnesses, classifiers, addition formulas, and product stability.
\end{enumerate}
Under these supplied rows, the tuple $(\mathsf{Pi}, \mathsf{Exp}, \mathsf{Log}, \mathsf{Sin}, \mathsf{Cos})$, with sources, classifiers, stability obligations, ledgers, and standard bridges, is a $\NameCert(\RealAnalyticUp)$ candidate over $\RealUp$. Without those supplied rows, this chapter exports only the displayed proof obligations and explicit-modulus scaffolds.
\end{theorem}
\leanchecked{BEDC.Derived.RealAnalyticUp.real\_analytic\_certificate\_boundary}
\begin{proof}
The local constructions provide regular rational stream data: the Leibniz rescaling for $\pi$, the exponential power-series family, the bisection presentation of $\log$, and the sine and cosine power-series families. Their moduli are explicit unary functions, so they can be passed to the $\StreamNameUp$ and $\RegSeqRat$ rows once those rows are available.

The supplied $\RealUp$ limit witnesses then assign real-history candidates to the five analytic objects. Limit uniqueness supplies the classifier row, and the four stability obligations listed in the statement provide the algebraic and trigonometric preservation clauses required by the $\NameCert$ template.

Thus the tuple has the shape of a naming-certificate candidate exactly when the rows in the statement are present. In their absence, the chapter has not produced the carrier, classifier, or stability package needed for a completed $\NameCert(\RealAnalyticUp)$.
\end{proof}

\begin{corollary}[$\RealAnalyticUp$ primitive boundary]
\label{cor:real-analytic-primitive-boundary}
$\RealAnalyticUp$ is not a BEDC primitive, and this chapter alone does not license it as an available naming certificate. Its admissible use requires the supplied Real and Completion rows named in \autoref{thm:real-analytic-certificate-boundary}.
\end{corollary}

\begin{lemma}[Odd trigonometric Cauchy-product coefficient split]
\label{lem:real-analytic-odd-trig-cauchy-product-split}
For $\RealUp$-histories $x$ and $y$ and unary degree $n$, assume supplied $\RealAlgOrder$ rows for addition, products, powers, factorial-denominator inverses, signs, and the binomial expansion of $(x+y)^{2n+1}$. Then the degree-$2n+1$ coefficient of the regular rational Cauchy product
$$
\mathsf{SinPart}(x,\cdot,\cdot)\mathsf{CosPart}(y,\cdot,\cdot)
+
\mathsf{CosPart}(x,\cdot,\cdot)\mathsf{SinPart}(y,\cdot,\cdot)
$$
is classified with the degree-$2n+1$ coefficient of $\mathsf{SinPart}(x+y,\cdot,\cdot)$.
\end{lemma}
\begin{proof}
Expand the first product into the odd-in-$x$, even-in-$y$ terms
$$
(-1)^{i+j}\frac{x^{2i+1}y^{2j}}{(2i+1)!(2j)!},
$$
and expand the second product into the even-in-$x$, odd-in-$y$ terms
$$
(-1)^{i+j}\frac{x^{2i}y^{2j+1}}{(2i)!(2j+1)!}.
$$
On the degree-$2n+1$ slice, both products have $i+j=n$, so all signs are $(-1)^n$. The supplied factorial-denominator rows move every term to the common denominator $(2n+1)!$. The first family contributes the binomial terms in which the exponent of $x$ is odd, and the second family contributes the binomial terms in which the exponent of $x$ is even. These two disjoint parity classes exhaust the binomial expansion of $(x+y)^{2n+1}$. After multiplication by the common sign $(-1)^n$ and the common denominator inverse, the displayed coefficient is classified with the corresponding coefficient of $\mathsf{SinPart}(x+y,\cdot,\cdot)$.
\end{proof}

\begin{theorem}[Sine addition formula row]
\label{thm:real-analytic-sin-add}
For $\RealUp$-histories $x$ and $y$, let $z$ be the endpoint supplied by the $\RealAlgOrder$ addition row for $x+y$. Assume supplied trigonometric limit witnesses for $\mathsf{Sin}(x,s_x)$, $\mathsf{Cos}(x,c_x)$, $\mathsf{Sin}(y,s_y)$, $\mathsf{Cos}(y,c_y)$, and $\mathsf{Sin}(z,s_z)$. Assume supplied $\RealAlgOrder$ rows naming the product endpoints $s_x\cdot c_y$ and $c_x\cdot s_y$ and their sum, product-stability rows saying that these endpoints are the $\RealUp$ limits of the corresponding Cauchy-product streams, and a regular-rational Cauchy-product comparison whose coefficient part is \autoref{lem:real-analytic-odd-trig-cauchy-product-split} and whose tail estimates use the modulus of \autoref{lem:real-analytic-trig-cauchy}. If the supplied limit-uniqueness classifier rows compare that product-sum stream with $\mathsf{SinPart}(z,\cdot,\cdot)$ at their real-history limits, then
$$
\RealClassifier(s_z, s_x\cdot c_y + c_x\cdot s_y).
$$
\end{theorem}
\begin{proof}
By \autoref{def:real-analytic-sin-cos}, the five trigonometric witnesses expose regular rational stream names for the sine and cosine partial sums of $x$, $y$, and $z$. The addition row identifies $z$ as the $\RealUp$ endpoint for $x+y$, while the product and sum rows make the right-hand endpoint $s_x\cdot c_y+c_x\cdot s_y$ meaningful inside the same $\RealAlgOrder$ interface.

Product stability transports the four input trigonometric limits through the two displayed products and then through the final sum. Thus the right-hand endpoint is the $\RealUp$ limit of the regular rational stream obtained from
$$
\mathsf{SinPart}(x,\cdot,\cdot)\mathsf{CosPart}(y,\cdot,\cdot)
+
\mathsf{CosPart}(x,\cdot,\cdot)\mathsf{SinPart}(y,\cdot,\cdot).
$$
The supplied Cauchy-product comparison identifies this stream with the $\mathsf{SinPart}(z,\cdot,\cdot)$ stream: its finite coefficient calculation is the odd-parity split of \autoref{lem:real-analytic-odd-trig-cauchy-product-split}, and its tails are bounded by the trigonometric Cauchy modulus of \autoref{lem:real-analytic-trig-cauchy} after passing to a common unary precision.

The two real-history endpoints are therefore limits of classified regular rational stream names. Applying the supplied limit-uniqueness classifier row gives
$$
\RealClassifier(s_z, s_x\cdot c_y + c_x\cdot s_y).
$$
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticSinAdd\_local\_product\_sum\_unary}

\begin{lemma}[Even trigonometric Cauchy-product coefficient split]
\label{lem:real-analytic-even-trig-cauchy-product-split}
For $\RealUp$-histories $x$ and $y$ and unary degree $n$, assume supplied $\RealAlgOrder$ rows for addition, products, differences, powers, factorial-denominator inverses, signs, and the binomial expansion of $(x+y)^{2n}$. Then the degree-$2n$ coefficient of the regular rational Cauchy-product difference
$$
\mathsf{CosPart}(x,\cdot,\cdot)\mathsf{CosPart}(y,\cdot,\cdot)
-
\mathsf{SinPart}(x,\cdot,\cdot)\mathsf{SinPart}(y,\cdot,\cdot)
$$
is classified with the degree-$2n$ coefficient of $\mathsf{CosPart}(x+y,\cdot,\cdot)$. The odd total-degree slices on both sides are empty by parity.
\end{lemma}
\begin{proof}
Expand the cosine-cosine product into the even-in-$x$, even-in-$y$ terms
$$
(-1)^{i+j}\frac{x^{2i}y^{2j}}{(2i)!(2j)!},
$$
and expand the sine-sine product into the odd-in-$x$, odd-in-$y$ terms
$$
(-1)^{i+j}\frac{x^{2i+1}y^{2j+1}}{(2i+1)!(2j+1)!}.
$$
On the degree-$2n$ slice, the cosine-cosine product has $i+j=n$, so every sign is $(-1)^n$. The sine-sine product has $i+j=n-1$ when $n>0$, so its sign is $(-1)^{n-1}$; the displayed subtraction changes this to $(-1)^n$. For $n=0$, the sine-sine contribution is empty.

The supplied factorial-denominator rows move every nonempty term to the common denominator $(2n)!$. The cosine-cosine family contributes the binomial terms in which the exponent of $x$ is even, and the subtracted sine-sine family contributes the binomial terms in which the exponent of $x$ is odd. These two parity classes partition the binomial expansion of $(x+y)^{2n}$. After multiplication by the common sign $(-1)^n$ and the common denominator inverse, the displayed coefficient is classified with the corresponding coefficient of $\mathsf{CosPart}(x+y,\cdot,\cdot)$.

No odd total degree can arise from an even-even product or an odd-odd product, and $\mathsf{CosPart}(x+y,\cdot,\cdot)$ has only even powers. Hence the odd slices are empty on both sides.
\end{proof}

\begin{theorem}[Cosine addition formula row]
\label{thm:real-analytic-cos-add}
For $\RealUp$-histories $x$ and $y$, let $z$ be the endpoint supplied by the $\RealAlgOrder$ addition row for $x+y$. Assume supplied trigonometric limit witnesses for $\mathsf{Cos}(z,c_z)$, $\mathsf{Cos}(x,c_x)$, $\mathsf{Cos}(y,c_y)$, $\mathsf{Sin}(x,s_x)$, and $\mathsf{Sin}(y,s_y)$. Assume supplied $\RealAlgOrder$ rows naming the product endpoints $c_x\cdot c_y$ and $s_x\cdot s_y$ and the displayed difference $c_x\cdot c_y-s_x\cdot s_y$, product-stability rows saying that the two product endpoints are the $\RealUp$ limits of the corresponding Cauchy-product streams, and the supplied difference row saying that $c_x\cdot c_y-s_x\cdot s_y$ is the $\RealUp$ limit of their pointwise difference. Assume also a regular-rational Cauchy-product comparison whose coefficient part is \autoref{lem:real-analytic-even-trig-cauchy-product-split} and whose tail estimates use the modulus of \autoref{lem:real-analytic-trig-cauchy}. If the supplied limit-uniqueness classifier rows compare that product-difference stream with $\mathsf{CosPart}(z,\cdot,\cdot)$ at their real-history limits, then
$$
\RealClassifier(c_z, c_x\cdot c_y - s_x\cdot s_y).
$$
\end{theorem}
\begin{proof}
By \autoref{def:real-analytic-sin-cos}, the five trigonometric witnesses expose regular rational stream names for the cosine partial sums of $z$, $x$, and $y$, and for the sine partial sums of $x$ and $y$. The addition row identifies $z$ as the $\RealUp$ endpoint for $x+y$. The operation rows are the addition, negation, and multiplication rows exposed by the $\RealAlgOrder$ interface of \autoref{def:realalgorder-concrete-interface}; they make the right-hand endpoint $c_x\cdot c_y-s_x\cdot s_y$ meaningful in the same real-history interface.

Product stability transports the input trigonometric limits through the two products $c_x\cdot c_y$ and $s_x\cdot s_y$. The supplied difference row then transports those product limits through the displayed subtraction. Thus the right-hand endpoint is the $\RealUp$ limit of the regular rational stream obtained from
$$
\mathsf{CosPart}(x,\cdot,\cdot)\mathsf{CosPart}(y,\cdot,\cdot)
-
\mathsf{SinPart}(x,\cdot,\cdot)\mathsf{SinPart}(y,\cdot,\cdot).
$$
The supplied Cauchy-product comparison identifies this stream with the $\mathsf{CosPart}(z,\cdot,\cdot)$ stream: its finite coefficient calculation is the even-parity split of \autoref{lem:real-analytic-even-trig-cauchy-product-split}, and its tails are bounded by the trigonometric Cauchy modulus of \autoref{lem:real-analytic-trig-cauchy} after passing to a common unary precision.

The two real-history endpoints are therefore limits of classified regular rational stream names. Applying the supplied limit-uniqueness classifier row gives
$$
\RealClassifier(c_z, c_x\cdot c_y - s_x\cdot s_y).
$$
\end{proof}
\leanchecked{BEDC.Derived.RealAnalyticUp.RealAnalyticCosAdd\_local\_product\_difference\_unary}
