\chapter{A Concrete Naming Certificate for $\CauchyTailWitnessEnvelopeUp$}
\label{ch:concrete-instances-cauchy-tail-witness-envelope-namecert}
\origin{ai-composite}

The $\CauchyTailWitnessEnvelopeUp$ packet is the composite finite witness envelope for the Real-completeness diagonal tail route of \autoref{ch:visions-real-completeness}. It consumes the stream window surface of \autoref{ch:concrete-instances-streamname-namecert}, the finite-window envelope of \autoref{ch:concrete-instances-finitewindowenvelope-namecert}, and the common-tail comparison packet of \autoref{ch:concrete-instances-cauchy-tail-comparison-namecert}. The packet keeps the witness route finite by storing the selected StreamName window, the finite-window endpoint ledger, the Cauchy tail-comparison row, the RealTailAgreementSeal row, the RealUp readback row, and the structural provenance needed to replay the same route.

\begin{definition}[CauchyTailWitnessEnvelope carrier]
\label{def:cauchy-tail-witness-envelope-carrier}
A $\CauchyTailWitnessEnvelopeUp$ carrier is a finite $\BHist$ packet
$$
E=(S,F,Q,A,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the finite $\StreamNameUp$ window selected for the diagonal tail request;
\item $F$ is the $\FiniteWindowEnvelopeUp$ row that binds the selected window to its dyadic endpoint ledger, regular-rational readback, and RealUp endpoint surface;
\item $Q$ is the $\CauchyTailComparisonUp$ row that compares the relevant late regular-name windows through the same selected window and endpoint ledger;
\item $A$ is the $\RealTailAgreementSealUp$ row reached after the finite-window and comparison rows have both been displayed;
\item $R$ is the $\RealUp$ readback row exported to the diagonal Real-completeness route;
\item $H$ records componentwise $\hsame$ transports for $S,F,Q,A,R,C,P,N$;
\item $C$ records the displayed $\Cont$ routes that replay the selected window, finite-window envelope, tail comparison, tail-agreement seal, RealUp readback, provenance, and local naming row;
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\FiniteWindowEnvelopeUp$, $\CauchyTailComparisonUp$, $\RealTailAgreementSealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CauchyTailWitnessEnvelopeUp}$ row.
\end{enumerate}
The carrier contains no quotient stream equality, no host real equality, no selected host limit, no countable-choice selector, and no ambient completeness principle.
\end{definition}
\leanchecked{BEDC.Derived.CauchyTailWitnessEnvelopeUp.CauchyTailWitnessEnvelopeTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyTailWitnessEnvelope NameCert obligations]
\label{thm:cauchy-tail-witness-envelope-namecert-obligations}
For the carrier of \autoref{def:cauchy-tail-witness-envelope-carrier}, the local $\NameCert_{\CauchyTailWitnessEnvelopeUp}$ surface consists exactly of carrier admission for
$$
E=(S,F,Q,A,R,H,C,P,N),
$$
selected $\StreamNameUp$ window exposure through $S$, finite-window envelope exposure through $F$, common-tail comparison exposure through $Q$, RealTailAgreementSeal exposure through $A$, RealUp readback exposure through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the displayed carrier. The rows $S,F,Q,A,R,H,C,P,N$ are the only coordinates of the finite packet.

Read the analytic rows in order. The selected stream window $S$ is first bound into the finite-window envelope $F$, and the tail comparison $Q$ reads its common window and dyadic endpoint ledger through that same envelope surface.

The tail-agreement seal $A$ and RealUp readback $R$ are then reached only after $S,F,Q$ have been displayed. The structural rows $H,C,P,N$ transport, replay, authenticate, and name the same packet, so the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope selector handoff]
\label{thm:cauchy-tail-witness-envelope-selector-handoff}
Every diagonal-tail selector read exported by an accepted $\CauchyTailWitnessEnvelopeUp$ carrier factors through the selected window $S$, the finite-window envelope $F$, and the Cauchy tail-comparison row $Q$ before the RealTailAgreementSeal row $A$ or the RealUp readback row $R$ can be consumed. The handoff supplies the finite witness route used by \autoref{ch:visions-real-completeness}, not an isolated RealUp seal or a host limit.
\end{theorem}
\begin{proof}
Start with the selected window. The carrier has exactly one StreamName window coordinate $S$, and that coordinate is the source read by the envelope row $F$.

Use the finite-window dependency next. The row $F$ supplies the selected window and endpoint ledger consumed by the comparison row $Q$, so the comparison is not a host-level comparison detached from the envelope.

Finally read $A$ and $R$. These rows are reached after the selector, envelope, and comparison rows have been replayed through $C$ and transported through $H$. Thus the diagonal-tail handoff remains a finite witness envelope rather than a selected limit or isolated RealUp object.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope non-escape]
\label{thm:cauchy-tail-witness-envelope-nonescape}
Every downstream consumer of an accepted $\CauchyTailWitnessEnvelopeUp$ packet receives only the finite surface
$$
S,F,Q,A,R,H,C,P,N.
$$
It receives no quotient stream equality, host real equality, selected host limit, countable-choice selector, or ambient completeness theorem. A later Lean TasteGate module for this carrier must therefore expose nontriviality and field-faithfulness over the displayed packet fields rather than over a collapsed RealUp output.
\end{theorem}
\begin{proof}
Project the carrier and apply the NameCert obligation theorem. The public surface is exhausted by the selected window, finite-window envelope, common-tail comparison, tail-agreement seal, RealUp readback, transport, replay, provenance, and local naming rows.

The selector handoff theorem keeps every diagonal-tail read on those rows. In particular, the comparison row $Q$ consumes the finite-window endpoint ledger from $F$, and the seal row $A$ is unavailable before that route is displayed.

The excluded objects have no coordinate in the packet. Since the carrier has no quotient stream, host real equality, host-selected limit, choice selector, or ambient completeness row, no downstream consumer can recover one from an accepted envelope.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope finite-window exactness]
\label{thm:cauchy-tail-witness-envelope-finite-window-exactness}
For every accepted $\CauchyTailWitnessEnvelopeUp$ carrier
$$
E=(S,F,Q,A,R,H,C,P,N),
$$
the selected $\StreamNameUp$ window $S$ is consumed through the $\FiniteWindowEnvelopeUp$ row $F$ before any tail-comparison, seal, or RealUp read is exported. The endpoint ledger, regular-rational readback, and RealUp endpoint surface used by the envelope are therefore the ones displayed by $F$.
\end{theorem}
\begin{proof}
Project the carrier and use the NameCert obligation theorem. The only selected-window coordinate is $S$, and the only finite-window envelope coordinate is $F$.

Apply the selector handoff theorem. It places $S$ before $F$ and $F$ before $Q,A,R$, so no later row can read the selected window except through the envelope.

Finally use non-escape. Since the packet has no hidden endpoint ledger or host equality coordinate, the endpoint data consumed downstream are exactly the ledger rows displayed by $F$.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope tail-comparison exactness]
\label{thm:cauchy-tail-witness-envelope-tail-comparison-exactness}
For every accepted $\CauchyTailWitnessEnvelopeUp$ carrier $E=(S,F,Q,A,R,H,C,P,N)$, the tail-comparison row $Q$ reads the same finite-window endpoint ledger exposed by $F$ before any RealTailAgreementSeal row $A$ is consumed. No comparison row may bypass the selected window $S$ or replace the endpoint ledger by quotient stream equality or host real equality.
\end{theorem}
\begin{proof}
Start from finite-window exactness. By \autoref{thm:cauchy-tail-witness-envelope-finite-window-exactness}, the selected window $S$ and endpoint ledger are already bound through $F$.

Use the NameCert obligation theorem to locate $Q$. The comparison row is a displayed carrier coordinate and its consumer route follows the selected window and finite-window envelope rows.

Apply the selector handoff theorem. It places $Q$ before $A$ and $R$, so the seal cannot be reached until the comparison has read the same $S,F$ ledger.

The non-escape theorem removes the remaining alternatives. Quotient streams, host real equality, selected host limits, countable choice, and ambient completeness are not packet coordinates, so they cannot replace the finite comparison ledger.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope Real tail seal boundary]
\label{thm:cauchy-tail-witness-envelope-real-tail-seal-boundary}
For every accepted $\CauchyTailWitnessEnvelopeUp$ carrier $E=(S,F,Q,A,R,H,C,P,N)$, the RealTailAgreementSeal row $A$ and the RealUp readback row $R$ are reached only after the selected window $S$, finite-window envelope $F$, tail-comparison row $Q$, transport rows $H$, continuation rows $C$, provenance row $P$, and local naming row $N$ have been displayed.

The boundary is a finite witness-envelope route. It does not export quotient stream equality, host real equality, a selected host limit, a countable-choice selector, or ambient completeness.
\end{theorem}
\begin{proof}
Project the accepted packet. The carrier has exactly the rows $S,F,Q,A,R,H,C,P,N$, with $H,C,P,N$ carrying transport, replay, provenance, and local naming for the same packet.

Apply finite-window exactness and tail-comparison exactness. These theorems route the seal-facing read through $S,F,Q$ before $A$ is available.

Use the selector handoff theorem for the final order of consumption. It places $A$ and then $R$ after the selected window, envelope, and comparison rows, while the structural rows replay and authenticate the same route.

Finally apply non-escape. Since no excluded object is present in the carrier, the seal boundary is exactly the displayed finite witness-envelope route.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope obligation closure]
\label{thm:cauchy-tail-witness-envelope-obligation-closure}
For every accepted $\CauchyTailWitnessEnvelopeUp$ packet $E=(S,F,Q,A,R,H,C,P,N)$, the carrier definition, local $\NameCert$ obligations, selector handoff, finite-window exactness, tail-comparison exactness, Real-tail seal boundary, and non-escape theorem jointly form the $\obligationClosure$ surface over $\StreamNameUp$, $\FiniteWindowEnvelopeUp$, $\CauchyTailComparisonUp$, $\RealTailAgreementSealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The package exports exactly the selected stream-name window, finite endpoint envelope, Cauchy tail-comparison ledger, RealTailAgreementSeal boundary, RealUp readback row, transport rows, continuation routes, package provenance, and local naming row displayed by $E$.
\end{theorem}
\begin{proof}
Project the tuple $E=(S,F,Q,A,R,H,C,P,N)$. The carrier definition supplies the row names, and the local NameCert obligations certify that each downstream consumer reads those rows as a single finite witness-envelope packet.

Follow the route order. The selector handoff places $S$ before $F,Q,A,R$, finite-window exactness binds the endpoint ledger through $S,F$, tail-comparison exactness makes $Q$ read that same ledger before $A$, and the Real-tail seal boundary places $A$ and $R$ after the selected window, envelope, comparison, transport, continuation, provenance, and local naming rows.

Finally apply non-escape. Quotient stream equality, host equality, a host-selected limit, a choice selector, and ambient completeness are not coordinates of $E$, so no hidden row remains outside the displayed obligation surface.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope scoped route binding]
\label{thm:cauchy-tail-witness-envelope-scoped-route-binding}
Every accepted $\CauchyTailWitnessEnvelopeUp$ packet
$$
E=(S,F,Q,A,R,H,C,P,N)
$$
exposes the selected $\StreamNameUp$ window $S$, the $\FiniteWindowEnvelopeUp$ row $F$, the $\CauchyTailComparisonUp$ row $Q$, the $\RealTailAgreementSealUp$ row $A$, the $\RealUp$ readback row $R$, componentwise $\hsame$ transports $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$ as one finite L10 witness-envelope route over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The route exposes no quotient stream equality, host real equality, selected host limit, countable-choice selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Start from the local NameCert obligations. They identify the displayed coordinates $S,F,Q,A,R,H,C,P,N$ as the entire accepted packet surface, and the TasteGate marker for $\CauchyTailWitnessEnvelopeUp$ aligns this single carrier with its named field-faithful carrier route.

Use the selector handoff to place the route on the selected window. The row $S$ is consumed by the finite-window envelope $F$, and $F$ supplies the endpoint ledger that the tail-comparison row $Q$ reads.

Apply finite-window exactness and tail-comparison exactness. These results make the selected window, endpoint envelope, and Cauchy tail-comparison ledger the same finite route before the RealTailAgreementSeal row is available.

Finally use the Real-tail seal boundary and non-escape theorem. The seal row $A$, RealUp readback row $R$, transports $H$, continuations $C$, provenance $P$, and naming row $N$ remain inside the same finite packet, while quotient stream equality, host real equality, selected host limits, countable choice, and ambient completeness have no carrier coordinate.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope consumer interface exactness]
\label{thm:cauchy-tail-witness-envelope-consumer-interface-exactness}
For every accepted $\CauchyTailWitnessEnvelopeUp$ packet
$$
E=(S,F,Q,A,R,H,C,P,N)
$$
a public consumer of $\CauchyTailWitnessEnvelopeUp$ has exactly the finite interface consisting of the selected $\StreamNameUp$ window $S$, the $\FiniteWindowEnvelopeUp$ endpoint row $F$, the $\CauchyTailComparisonUp$ row $Q$, the $\RealTailAgreementSealUp$ boundary row $A$, the $\RealUp$ readback row $R$, and the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows carried by $H,C,P,N$.

Conversely, the displayed rows $S,F,Q,A,R,H,C,P,N$ suffice for the public consumer interface. They export no quotient stream equality, host real equality, host-selected limit, countable-choice selector, or ambient completeness principle.
\end{theorem}
\begin{proof}
For exactness, project the carrier $E=(S,F,Q,A,R,H,C,P,N)$. By the NameCert obligation theorem, these are exactly the rows admitted for the local $\NameCert_{\CauchyTailWitnessEnvelopeUp}$ surface, so a public consumer has no off-packet coordinate before the route is inspected.

Use the selector handoff and finite-window exactness. The selected window $S$ is first read through the envelope $F$, and the endpoint ledger exported to the consumer is the one displayed by that same finite-window row.

Next apply tail-comparison exactness. The row $Q$ reads the same $S,F$ ledger before the Real-tail seal can be consumed, so the comparison branch cannot replace the finite ledger by quotient stream equality or host real equality.

Now use the Real-tail seal boundary, obligation closure, and scoped route binding. The rows $A$ and $R$ are reached only after $S,F,Q,H,C,P,N$ have been displayed, and the structural rows transport, replay, package, and name that same finite route.

For sufficiency, start with the displayed rows $S,F,Q,A,R,H,C,P,N$. The NameCert obligations admit them as one local naming surface, the selector handoff places the analytic rows in the required order, and the finite-window, tail-comparison, and seal-boundary theorems provide the endpoint, comparison, boundary, and readback components of the consumer route.

Finally apply non-escape and scoped route binding. Since the accepted packet has no coordinate for a quotient stream, host real equality, host-selected limit, countable-choice selector, or ambient completeness principle, the displayed rows provide the whole public interface and no stronger object is exported.
\end{proof}

\begin{theorem}[CauchyTailWitnessEnvelope standard bridge surface]
\label{thm:cauchy-tail-witness-envelope-standard-bridge-surface}
Every standard-facing read of an accepted $\CauchyTailWitnessEnvelopeUp$ packet $E=(S,F,Q,A,R,H,C,P,N)$ factors through the selected $\StreamNameUp$ window $S$, the $\FiniteWindowEnvelopeUp$ endpoint row $F$, the $\CauchyTailComparisonUp$ row $Q$, the $\RealTailAgreementSealUp$ boundary row $A$, the $\RealUp$ readback row $R$, and the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows carried by $H,C,P,N$.

The bridge surface exports no quotient stream equality, host real equality, host-selected limit, countable-choice selector, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with the local NameCert obligations of \autoref{thm:cauchy-tail-witness-envelope-namecert-obligations}. They identify $S,F,Q,A,R,H,C,P,N$ as the complete accepted carrier surface for the local $\NameCert_{\CauchyTailWitnessEnvelopeUp}$ row.

Use the selector handoff theorem \autoref{thm:cauchy-tail-witness-envelope-selector-handoff}. It places every diagonal-tail read first on the selected $\StreamNameUp$ window and then on the finite-window envelope before the comparison, seal, or readback rows are consumed.

Apply finite-window exactness and tail-comparison exactness from \autoref{thm:cauchy-tail-witness-envelope-finite-window-exactness} and \autoref{thm:cauchy-tail-witness-envelope-tail-comparison-exactness}. These results bind the endpoint ledger and comparison row to the same finite $S,F$ surface.

Next use the Real-tail seal boundary of \autoref{thm:cauchy-tail-witness-envelope-real-tail-seal-boundary}. The rows $A$ and $R$ are reached only after the selected window, finite-window envelope, comparison row, transports, continuations, provenance, and local name have been displayed.

Now combine non-escape, scoped route binding, and consumer interface exactness from \autoref{thm:cauchy-tail-witness-envelope-nonescape}, \autoref{thm:cauchy-tail-witness-envelope-scoped-route-binding}, and \autoref{thm:cauchy-tail-witness-envelope-consumer-interface-exactness}. Together they state that a public or standard-facing consumer has exactly the listed finite interface and no off-packet coordinate.

Therefore the standard bridge surface is precisely the displayed $S,F,Q,A,R,H,C,P,N$ route, with no quotient stream equality, host real equality, host-selected limit, countable-choice selector, or ambient completeness coordinate.
\end{proof}

\closureat{CauchyTailWitnessEnvelopeUp}{seedStr}
\closureat{CauchyTailWitnessEnvelopeUp}{obligationStr}
\closureat{CauchyTailWitnessEnvelopeUp}{scopedStr}
\closureat{CauchyTailWitnessEnvelopeUp}{publicStr}
\closureat{CauchyTailWitnessEnvelopeUp}{bridgedStr}[BEDC.Derived.CauchyTailWitnessEnvelopeUp.CauchyTailWitnessEnvelopeTasteGate\_single\_carrier\_alignment]
\closureat{CauchyTailWitnessEnvelopeUp}{matureStr}

\begin{closurestatus}{\CauchyTailWitnessEnvelopeUp}
  \constructivestory{A $\CauchyTailWitnessEnvelopeUp$ packet is generated from a selected $\StreamNameUp$ window, a finite-window envelope row, a Cauchy tail-comparison row, a $\RealTailAgreementSealUp$ row, a $\RealUp$ readback row, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:cauchy-tail-witness-envelope-carrier}, \autoref{thm:cauchy-tail-witness-envelope-namecert-obligations}, \autoref{thm:cauchy-tail-witness-envelope-selector-handoff}, \autoref{thm:cauchy-tail-witness-envelope-finite-window-exactness}, \autoref{thm:cauchy-tail-witness-envelope-tail-comparison-exactness}, \autoref{thm:cauchy-tail-witness-envelope-real-tail-seal-boundary}, \autoref{thm:cauchy-tail-witness-envelope-nonescape}, \autoref{thm:cauchy-tail-witness-envelope-scoped-route-binding}, the bridge-facing public consumer surface \autoref{thm:cauchy-tail-witness-envelope-consumer-interface-exactness}, and the standard bridge surface \autoref{thm:cauchy-tail-witness-envelope-standard-bridge-surface} bind the selected StreamName window, finite-window envelope, tail-comparison row, RealTailAgreementSeal row, RealUp readback row, BHist carrier surface, hsame transports, Cont routes, Pkg provenance, NameCert row, public consumer interface, and standard-facing read as one finite bridge-facing surface.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.CauchyTailWitnessEnvelopeUp.CauchyTailWitnessEnvelopeTasteGate\_single\_carrier\_alignment}
  \bridgestatus{paperBridge}
  \origin{ai}
  \leanchecked{BEDC.Derived.CauchyTailWitnessEnvelopeUp.taste\_gate}
  \notclaimed{This chapter does not close quotient streams, host real equality, selected host limits, countable choice, ambient completeness, or machine bridge checking.}
  \upgradepath{No further paper-side closure upgrade remains; machine bridge checking stays on the formal axis.}
\end{closurestatus}
