\chapter{A Concrete Naming Certificate for $\RealCompletionSealClassifierUp$}
\label{ch:concrete-instances-real-completion-seal-classifier-namecert}
\origin{ai}

The $\RealCompletionSealClassifierUp$ packet realizes the Real completeness vision of \autoref{ch:visions-real-completeness} as a finite classifier boundary for completion-seal reads. It joins the tail-agreement seal of $\RealTailAgreementSealUp$, the sealed Cauchy-limit route of $\CauchyLimitSealUp$, and the synchronized budget route of \autoref{ch:concrete-instances-cauchy-seal-budget-synchronizer-namecert} before a $\RealUp$ consumer reads equivalence of completion-facing seals. The packet has no coordinate for quotient streams, host real equality, selected external limits, countable choice, or ambient completeness.

\begin{definition}[Real completion-seal classifier carrier]
\label{def:real-completion-seal-classifier-carrier}
A $\RealCompletionSealClassifierUp$ carrier is a finite $\BHist$ packet
$$
K=(A,L,S,B,R,W,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the $\RealTailAgreementSealUp$ row naming the tail-agreement comparison used by the completion read;
\item $L$ is the $\CauchyLimitSealUp$ row whose public route exposes the sealed Cauchy-limit endpoint;
\item $S$ is the $\CauchySealBudgetSynchronizerUp$ row tying the seal read to the displayed selector, observation-budget, shared-threshold, and compatibility rows;
\item $B$ is the finite budget row read from the synchronizer, including the displayed precision request and selected observation window;
\item $R$ is the $\RegSeqRatUp$ handoff row assembled from the displayed regular rational source data;
\item $W$ is the $\StreamNameUp$ finite window row inspected before the regular handoff is consumed;
\item $D$ is the $\DyadicRatCoreUp$ tolerance and observation ledger used by the same completion-seal read;
\item $H$ records componentwise $\hsame$ transports for $A,L,S,B,R,W,D,C,P,N$;
\item $C$ stores the displayed $\Cont$ routes by which consumers read the agreement seal, limit seal, synchronizer, budget, regular handoff, stream window, dyadic ledger, provenance, and local naming row;
\item $P$ is the $\Pkg$ provenance over $\RealTailAgreementSealUp$, $\CauchyLimitSealUp$, $\CauchySealBudgetSynchronizerUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RealCompletionSealClassifierUp}$ row.
\end{enumerate}
The carrier classifies completion-seal equivalence only through these displayed rows. It does not identify real names by quotient streams, host equality, selected external limits, countable choice, or an ambient completeness theorem.
\end{definition}
\leandef{BEDC.Derived.RealCompletionSealClassifierUp.RealCompletionSealClassifierUp}
\leanchecked{BEDC.Derived.RealCompletionSealClassifierUp.RealCompletionSealClassifierTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Real completion-seal classifier NameCert obligations]
\label{thm:real-completion-seal-classifier-obligations}
For the carrier of \autoref{def:real-completion-seal-classifier-carrier}, the local $\NameCert_{\RealCompletionSealClassifierUp}$ surface consists of five rows:
\begin{enumerate}
\item carrier admission for the finite packet $K=(A,L,S,B,R,W,D,H,C,P,N)$;
\item completion-seal classifier stability under the componentwise $\hsame$ transports in $H$;
\item displayed seal equivalence through the $\RealTailAgreementSealUp$ and $\CauchyLimitSealUp$ rows $A,L$;
\item budget and synchronizer exactness through $S,B,W,R,D$ before any $\RealUp$ seal read is exported;
\item provenance and naming exactness through the displayed $\Cont$, $\Pkg$, and $\NameCert$ rows $C,P,N$.
\end{enumerate}
Later Lean work in \texttt{TasteGate.lean} must provide \texttt{Nontrivial RealCompletionSealClassifierUp} and \texttt{FieldFaithful RealCompletionSealClassifierUp} instances for this same carrier surface.
\end{theorem}
\begin{proof}
Carrier admission is projection from the tuple in \autoref{def:real-completion-seal-classifier-carrier}. The agreement seal, limit seal, synchronizer, budget, regular handoff, stream window, dyadic ledger, transport, route, provenance, and local naming rows are all explicit coordinates.

Classifier stability is componentwise. The row $H$ transports the agreement, seal, synchronizer, budget, regular handoff, stream window, and dyadic observation rows without creating a quotient stream or host equality comparison.

Displayed seal equivalence is read through $A$ and $L$. The tail-agreement row supplies the finite comparison surface, and the Cauchy-limit seal row supplies the completion-facing endpoint route.

Budget exactness is read through $S,B,W,R,D$. The synchronizer forces the seal read to pass through a displayed budget row, a finite stream window, the regular rational handoff, and the dyadic tolerance ledger before a $\RealUp$ consumer may inspect the completion seal.

Finally, the routes in $C$ and the provenance and naming rows $P,N$ authenticate exactly that finite surface. Thus the five obligations are the whole classifier interface.
\end{proof}

\begin{theorem}[Real completion-seal classifier non-escape]
\label{thm:real-completion-seal-classifier-nonescape}
Every accepted $\RealCompletionSealClassifierUp$ read factors through the displayed agreement, seal, synchronizer, budget, regular handoff, stream-window, dyadic, transport, route, provenance, and naming rows
$$
A,L,S,B,R,W,D,H,C,P,N.
$$
No accepted read may bypass both a displayed seal row and a displayed budget or synchronizer row while still exporting a completion-seal classifier to a $\RealUp$ consumer.
\end{theorem}
\begin{proof}
Project the accepted carrier to $K=(A,L,S,B,R,W,D,H,C,P,N)$. The only seal-facing rows are $A$ and $L$, and the only budget-facing synchronization rows are $S,B,W,R,D$.

Apply the NameCert obligation surface. It requires displayed seal equivalence through $A,L$ and budget-synchronizer exactness through $S,B,W,R,D$ before the route can be authenticated by $C,P,N$.

The componentwise transports in $H$ preserve those rows and do not create a second completion channel. Since the carrier contains no quotient stream, host real equality, selected external limit, countable-choice row, or ambient completeness theorem, a read that bypasses both the seal rows and the budget or synchronizer rows has no remaining coordinate from which to export a classifier.
\end{proof}

\begin{theorem}[Real completion-seal classifier stability]
\label{thm:real-completion-seal-classifier-stability}
Let $K=(A,L,S,B,R,W,D,H,C,P,N)$ be an accepted $\RealCompletionSealClassifierUp$ carrier. Componentwise $\hsame$ transport along the rows recorded in $H$ preserves the classifier read on the agreement seal, limit seal, synchronizer, budget, regular handoff, stream-window, dyadic ledger, displayed routes, provenance, and local naming coordinates of $K$. In particular, a transported accepted read still classifies completion-seal equivalence only through those displayed coordinates.
\end{theorem}
\begin{proof}
Project the accepted carrier to its tuple $K$. The transport row $H$ is a coordinate of the same carrier, so its componentwise $\hsame$ data is read only against the displayed rows $A,L,S,B,R,W,D,C,P,N$.

Use the obligation surface of \autoref{thm:real-completion-seal-classifier-obligations}. Its stability row is exactly the requirement that the classifier surface remains the same classifier after those componentwise transports.

Finally use the non-escape boundary of \autoref{thm:real-completion-seal-classifier-nonescape}. Since no quotient stream, host equality, selected external limit, countable-choice row, or ambient completeness theorem is present in $K$, the transported read has no second completion channel.
\end{proof}

\begin{theorem}[Real completion-seal classifier seal equivalence]
\label{thm:real-completion-seal-classifier-seal-equivalence}
Let $K=(A,L,S,B,R,W,D,H,C,P,N)$ be an accepted $\RealCompletionSealClassifierUp$ carrier. Before any $\RealUp$ consumer receives a seal classifier, completion-seal equivalence is read only through the $\RealTailAgreementSealUp$ row $A$ and the $\CauchyLimitSealUp$ row $L$, together with the displayed route row $C$ that exposes those two rows to the consumer.
\end{theorem}
\begin{proof}
Project the carrier to $K$. The only agreement-facing coordinate is $A$, and the only completion-limit-facing coordinate is $L$.

Invoke the NameCert obligations of \autoref{thm:real-completion-seal-classifier-obligations}. The displayed seal-equivalence row requires the classifier to pass through $A$ and $L$ before the route data in $C$ can authenticate a $\RealUp$ consumer read.

The non-escape theorem then rules out every bypass. A read that does not use $A$ and $L$ has no displayed seal row left in the carrier from which to export a completion-seal classifier.
\end{proof}

\begin{theorem}[Real completion-seal classifier budget exactness]
\label{thm:real-completion-seal-classifier-budget-exactness}
Let $K=(A,L,S,B,R,W,D,H,C,P,N)$ be an accepted $\RealCompletionSealClassifierUp$ carrier. The synchronizer and budget rows $S,B,W,R,D$ are exact prerequisites for the seal read: the classifier must pass through the synchronizer, finite budget, finite stream window, regular rational handoff, and dyadic tolerance ledger before any completion-seal classifier is exported. This prerequisite surface excludes quotient streams, host real equality, selected external limits, countable choice, and ambient completeness.
\end{theorem}
\begin{proof}
Project the accepted read to the carrier tuple. The synchronizer, budget, stream-window, regular handoff, and dyadic rows are precisely $S,B,W,R,D$.

Apply the obligation surface. Its budget and synchronizer exactness row says that these five coordinates are prerequisites for the seal read before the routes, provenance, and local naming rows can authenticate an exported classifier.

Apply the non-escape boundary. If a read bypasses the displayed budget or synchronizer surface, then the carrier has no quotient stream, host equality, selected external limit, countable-choice row, or ambient completeness theorem that could replace it.
\end{proof}

\begin{theorem}[Real completion-seal classifier window factorization]
\label{thm:real-completion-seal-classifier-window-factorization}
Every exported $\RealCompletionSealClassifierUp$ classifier window factors through the synchronizer row $S$, budget row $B$, finite stream-window row $W$, regular rational handoff row $R$, and dyadic tolerance row $D$ before the exported completion-seal read $E$ is available to a $\RealUp$ consumer. The factorization is read inside the same carrier $K=(A,L,S,B,R,W,D,H,C,P,N)$ and is authenticated only by the displayed route, provenance, and local naming rows $C,P,N$.
\end{theorem}
\begin{proof}
Project the accepted carrier to $K$. The NameCert obligations of \autoref{thm:real-completion-seal-classifier-obligations} expose $S,B,W,R,D$ as the budget and synchronizer exactness rows for the classifier window.

Use budget exactness from \autoref{thm:real-completion-seal-classifier-budget-exactness}. It forces the exported read to pass through the synchronizer, finite budget, stream window, regular handoff, and dyadic tolerance ledger before $C,P,N$ can authenticate the consumer-facing read.

Finally apply non-escape from \autoref{thm:real-completion-seal-classifier-nonescape}. Since no quotient stream, host equality, selected external limit, countable-choice row, or ambient completeness theorem is present, there is no second path from the window to $E$.
\end{proof}

\begin{theorem}[Real completion-seal classifier tail-agreement stability]
\label{thm:real-completion-seal-classifier-tail-agreement-stability}
Let $K=(A,L,S,B,R,W,D,H,C,P,N)$ and $K'=(A',L',S',B',R',W',D',H',C',P',N')$ be accepted $\RealCompletionSealClassifierUp$ carriers related by the displayed componentwise $\hsame$ transports. Transport preserves the joint seal-equivalence read through $A,L$ and its transported counterpart through $A',L'$ as presented to consumers by $H,C,P,N$ and $H',C',P',N'$.
\end{theorem}
\begin{proof}
Start with componentwise stability, \autoref{thm:real-completion-seal-classifier-stability}. The transport rows record exactly the agreement, limit-seal, synchronizer, budget, window, handoff, dyadic, route, provenance, and local naming coordinates.

Apply seal equivalence from \autoref{thm:real-completion-seal-classifier-seal-equivalence}. The classifier reads completion-seal equivalence only through $A,L$ before the $\RealUp$ consumer sees the exported seal classifier.

The transported read is therefore the same joint $A,L$ seal-equivalence read through the transported support rows. Non-escape from \autoref{thm:real-completion-seal-classifier-nonescape} rules out any quotient-stream or host-equality comparison appearing during transport.
\end{proof}

\begin{theorem}[Real completion-seal classifier RealUp non-escape]
\label{thm:real-completion-seal-classifier-realup-nonescape}
A $\RealUp$ consumer of an accepted $\RealCompletionSealClassifierUp$ packet cannot read the completion-seal classifier from quotient streams, host equality, selected external limits, countable choice, or ambient completeness. The consumer receives only the displayed seal rows $A,L$, synchronizer and budget rows $S,B,W,R,D$, componentwise transport row $H$, route row $C$, provenance row $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the consumer read to the accepted carrier $K=(A,L,S,B,R,W,D,H,C,P,N)$. The obligation theorem, \autoref{thm:real-completion-seal-classifier-obligations}, lists all rows available to the local $\NameCert$ surface.

Use \autoref{thm:real-completion-seal-classifier-window-factorization} for the exported classifier window and \autoref{thm:real-completion-seal-classifier-tail-agreement-stability} for the transported seal-equivalence read. Together they place the consumer-facing classifier behind the displayed rows $A,L,S,B,W,R,D,H,C,P,N$.

Finally apply \autoref{thm:real-completion-seal-classifier-nonescape}. The carrier contains no quotient-stream coordinate, host equality, selected external limit, countable-choice row, or ambient completeness theorem, so a $\RealUp$ consumer has no route to such data.
\end{proof}

\begin{theorem}[Real completion-seal classifier public scope]
\label{thm:real-completion-seal-classifier-public-scope}
Every accepted $\RealCompletionSealClassifierUp$ packet exposes one public classifier scope over the finite carrier rows
$$
A,L,S,B,R,W,D,H,C,P,N
$$
of \autoref{def:real-completion-seal-classifier-carrier}. Any $\RealUp$ or completion-seal consumer must factor through the seal-equivalence theorem, budget exactness, window factorization, tail-agreement stability, and the $\RealUp$ non-escape theorem. No quotient stream, host equality, selected external limit, countable choice, or ambient completeness row is exported.
\end{theorem}
\begin{proof}
Project the accepted packet to the carrier tuple of \autoref{def:real-completion-seal-classifier-carrier}. This fixes the only available public rows as $A,L,S,B,R,W,D,H,C,P,N$.

Use the NameCert obligations of \autoref{thm:real-completion-seal-classifier-obligations}. They make seal equivalence through $A,L$, budget and synchronizer exactness through $S,B,W,R,D$, and route authentication through $C,P,N$ the whole classifier interface.

Compose \autoref{thm:real-completion-seal-classifier-window-factorization} with \autoref{thm:real-completion-seal-classifier-tail-agreement-stability}. The exported classifier window and the transported agreement read therefore remain on the same finite route through $A,L,S,B,R,W,D,H,C,P,N$.

Finally apply \autoref{thm:real-completion-seal-classifier-realup-nonescape}. It excludes quotient streams, host real equality, selected external limits, countable choice, and ambient completeness from the consumer surface, so the public scope is exactly the displayed finite classifier route.
\end{proof}

\begin{theorem}[Real completion-seal classifier public export]
\label{thm:real-completion-seal-classifier-public-export}
Every public $\RealCompletionSealClassifierUp$ export to a $\RealUp$ consumer or to a completion-seal consumer factors through the finite route
$$
A,L,S,B,W,R,D,H,C,P,N.
$$
The exported boundary is exactly the displayed seal-equivalence, budget-exactness, window-factorization, tail-agreement-stability, $\RealUp$ non-escape, and public-scope surface of the accepted carrier. It exports no quotient stream, host real equality, selected external limit, countable-choice row, or ambient completeness principle.
\end{theorem}
\begin{proof}
Project the accepted public packet to the carrier of \autoref{def:real-completion-seal-classifier-carrier}. This fixes the public export route as $A,L,S,B,W,R,D,H,C,P,N$, with the same displayed route, provenance, and local naming surface.

Use seal equivalence from \autoref{thm:real-completion-seal-classifier-seal-equivalence} and budget exactness from \autoref{thm:real-completion-seal-classifier-budget-exactness}. These two rows force any exported classifier to read the agreement seal, completion-limit seal, synchronizer, finite budget, StreamName window, regular handoff, and dyadic tolerance ledger before the consumer sees the classifier.

Next apply the window factorization of \autoref{thm:real-completion-seal-classifier-window-factorization} and the tail-agreement stability of \autoref{thm:real-completion-seal-classifier-tail-agreement-stability}. They keep the exported window and transported agreement read on the same finite route through $A,L,S,B,W,R,D,H,C,P,N$.

Finally invoke $\RealUp$ non-escape from \autoref{thm:real-completion-seal-classifier-realup-nonescape} and public scope from \autoref{thm:real-completion-seal-classifier-public-scope}. Since quotient streams, host real equality, selected external limits, countable choice, and ambient completeness are absent from the carrier and from the public scope, no downstream export can recover them.
\end{proof}

\falsifiablePrediction{If a Real completion-seal classifier read bypasses both a displayed seal row and a displayed budget/synchronizer row, the classifier packet is refuted.}

\independenceWitness{realtailagreementseal, cauchylimitseal, cauchysealbudgetsynchronizer, real, regseqrat: no sibling is bijective because the classifier packet has a joint completion-seal classifier row tying agreement, seal, synchronizer, and Real handoff rows; each sibling lacks at least one of these coordinates.}

\closureat{RealCompletionSealClassifierUp}{seedStr}
\closureat{RealCompletionSealClassifierUp}{obligationStr}[BEDC.Derived.RealCompletionSealClassifierUp.RealCompletionSealClassifierTasteGate\_single\_carrier\_alignment]
\closureat{RealCompletionSealClassifierUp}{scopedStr}

\begin{closurestatus}{\RealCompletionSealClassifierUp}
  \constructivestory{A $\RealCompletionSealClassifierUp$ packet is generated from tail-agreement seal rows, Cauchy-limit seal rows, Cauchy seal-budget synchronizer rows, finite budget rows, regular rational handoff rows, StreamName windows, DyadicRatCore ledgers, componentwise transports, displayed routes, provenance, and local naming.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:real-completion-seal-classifier-carrier}, \autoref{thm:real-completion-seal-classifier-obligations}, \autoref{thm:real-completion-seal-classifier-nonescape}, \autoref{thm:real-completion-seal-classifier-stability}, \autoref{thm:real-completion-seal-classifier-seal-equivalence}, \autoref{thm:real-completion-seal-classifier-budget-exactness}, \autoref{thm:real-completion-seal-classifier-window-factorization}, \autoref{thm:real-completion-seal-classifier-tail-agreement-stability}, \autoref{thm:real-completion-seal-classifier-realup-nonescape}, \autoref{thm:real-completion-seal-classifier-public-scope}, and \autoref{thm:real-completion-seal-classifier-public-export} bind the carrier, NameCert obligation surface, non-escape boundary, componentwise stability, seal-equivalence read, budget exactness, window factorization, tail-agreement stability, RealUp non-escape, public classifier scope, and public consumer export for the finite completion-seal classifier packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, host real equality, selected external limits, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Public closure next requires Lean formalization for the same finite carrier and public consumer theorem.}
\end{closurestatus}
