\chapter{A Concrete Naming Certificate for $\CompactNetModulusSelectorUp$}
\label{ch:concrete-instances-compactnetmodulusselector-namecert}
\origin{ai}

The $\CompactNetModulusSelectorUp$ interface is the concrete finite selector behind the compact-uniform-continuity construction of \autoref{ch:visions-compact-uniform-continuity}. It consumes the compact finite-net rows of \autoref{ch:concrete-instances-compact-namecert}, the pointwise-modulus rows of \autoref{ch:concrete-instances-continuous-namecert}, the metric-distance rows of \autoref{ch:concrete-instances-metric-namecert}, the positive rational order rows of \autoref{ch:concrete-instances-rat-namecert}, and the finite lower-bound fold surface of \autoref{ch:concrete-instances-finitenetminimumfold-namecert}. Its output is the single finite packet a uniform-modulus consumer reads when a tolerance history is converted into a precision history by a compact net.

The selected precision row is assembled from sibling concrete packets: the finite cover and budget surface of \autoref{ch:concrete-instances-compactmoduluscover-namecert}, the fold output of \autoref{ch:concrete-instances-finitenetminimumfold-namecert}, and the downstream precision packet read by \autoref{ch:concrete-instances-uniformmodulus-namecert}. The selector therefore records a horizontal dependency route from compact cover data through a finite lower-bound fold to the uniform-modulus consumer boundary.

\begin{definition}[Compact net modulus selector carrier]
\label{def:compact-net-modulus-selector-carrier}
A $\CompactNetModulusSelectorUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the displayed compact metric source row, including the located finite-net coverage data for the requested tolerance history;
\item $Y$ is the displayed target metric row whose distance comparisons are consumed after the pointwise-modulus reads;
\item $E$ is the positive $\RatUp$ tolerance history requested by the uniform-modulus consumer;
\item $\mathcal{P}$ is the nonempty finite $\mathsf{ProbeBundle}$ spine of compact-net centers;
\item $C$ records bundled center histories and half-radius coverage rows for the source metric;
\item $R$ records the positive $\RatUp$ subordinate radius rows attached to the bundled centers;
\item $M$ records the $\ContinuousFunctionUp$ pointwise-modulus rows at the centers of $\mathcal{P}$ for the tolerance history $E$;
\item $F$ is the accepted $\FiniteNetMinimumFoldUp$ lower-bound row over $\mathcal{P}$ and $R$;
\item $D$ is the selected positive precision history exported by the fold row $F$;
\item $H$ records componentwise $\hsame$ transport for the metric, compact-net, tolerance, radius, pointwise-modulus, fold, precision, route, provenance, and naming rows;
\item $Q$ records the displayed $\Cont$ routes through which compact, continuous, metric, rational, fold, and uniform-modulus consumers read the packet;
\item $P$ is the $\Pkg$ provenance over $\CompactUp$, $\ContinuousFunctionUp$, $\MetricSpaceUp$, $\RatUp$, $\FiniteNetMinimumFoldUp$, $\mathsf{ProbeBundle}$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and local naming rows;
\item $N$ is the local $\NameCert_{\CompactNetModulusSelectorUp}$ row.
\end{enumerate}
The carrier exports only the compact-net input, pointwise-modulus radii, selected lower-bound fold row, tolerance-to-precision handoff, transport rows, continuation routes, package provenance, and local naming row. It has no coordinate for open-cover compactness, a host minimum, a choice-selected center, a quotient of point histories, or an external modulus function.
\end{definition}

\begin{theorem}[Compact net modulus selector NameCert obligations]
\label{thm:compact-net-modulus-selector-namecert-obligations}
The local $\NameCert_{\CompactNetModulusSelectorUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the packet of \autoref{def:compact-net-modulus-selector-carrier};
\item compact-net exactness, requiring $X,\mathcal{P},C,R$ to display the located finite $\varepsilon$-net rows read from the compact source certificate;
\item pointwise-modulus exactness, requiring every row of $M$ to be attached to a bundled center and to the displayed tolerance history $E$;
\item lower-bound fold exactness, requiring $F$ to be the $\FiniteNetMinimumFoldUp$ row over the same $\mathcal{P}$ and $R$ and requiring $D$ to be its exported positive lower-bound history;
\item non-escape, requiring every consumer read of $D$ to pass through $X,Y,E,\mathcal{P},C,R,M,F,H,Q,P,N$ and forbidding open-cover compactness, host minima, choice-selected centers, quotient point equality, and external modulus functions.
\end{enumerate}
\end{theorem}

\begin{proof}
Carrier admission is projection from \autoref{def:compact-net-modulus-selector-carrier}. The packet displays the source and target metric rows, tolerance history, finite probe spine, compact coverage rows, subordinate radius rows, pointwise-modulus rows, fold row, selected precision, transports, routes, provenance, and local name.

Compact-net exactness reads the finite coverage surface from $X,\mathcal{P},C,R$. The center and radius rows are not reconstructed by the selector; they are the displayed input rows supplied by the compact naming certificate.

Pointwise-modulus exactness then reads $M$ only at bundled centers. Each local row is tied to the same tolerance history $E$ and to the source and target metric rows already displayed in the carrier.

Lower-bound fold exactness reads $F$ over the same probe spine and radius ledger. The selected precision $D$ is accepted only as the positive lower-bound output of that finite fold.

The non-escape obligation is the carrier inventory together with the displayed routes. Since no excluded object is a coordinate of $S$, no local naming projection or continuation route can export one.
\end{proof}
\leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorNameCertObligations}

\begin{theorem}[Compact net modulus selector fold soundness]
\label{thm:compact-net-modulus-selector-fold-soundness}
Let
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
be an accepted $\CompactNetModulusSelectorUp$ carrier. If a source-distance read is certified below the selected precision history $D$, then the compact-continuous handoff for tolerance $E$ factors through one bundled center of $\mathcal{P}$, the corresponding pointwise-modulus row in $M$, and the same lower-bound fold certificate $F$.

The handoff uses the selected row only as a finite $\RatUp$ lower bound below every displayed subordinate radius row in $R$.
\end{theorem}
\leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorCarrier\_fold\_soundness}

\begin{proof}
Begin with the compact-net coordinate. The accepted carrier exposes $\mathcal{P}$ as a nonempty finite probe spine and $C$ as the coverage row assigning each source-point history to a bundled center with a displayed half-radius comparison.

Read the selected precision through $F$. By the lower-bound fold exactness obligation, $D$ is below every radius ledger in $R$ through the $\RatUp$ classifier and the stored transport rows in $H$.

Use the metric rows of $X$ to route a source-distance read below $D$ through the bundled center supplied by $C$. The comparison $D \le R_p$ keeps the second point inside the local ball named by the same probe.

Finally apply the corresponding pointwise-modulus row of $M$ and the target metric row $Y$. The output distance estimate is therefore read from $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$, not from an external modulus selector.
\end{proof}

\begin{theorem}[Compact net modulus selector non-escape]
\label{thm:compact-net-modulus-selector-nonescape}
Every consumer read of an accepted $\CompactNetModulusSelectorUp$ packet factors through the displayed compact-net input, pointwise-modulus radii, selected lower-bound fold row, transport rows, continuation routes, provenance, and local naming row of \autoref{def:compact-net-modulus-selector-carrier}. The packet exports no open-cover compactness principle, no host minimum over rationals, no choice-selected center, no quotient point equality, no sequential compactness argument, and no external modulus function.
\end{theorem}

\begin{proof}
Project the accepted carrier. Its coordinates are exactly $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$.

The NameCert obligations force compact reads through $X,\mathcal{P},C,R$, pointwise-modulus reads through $M$, and selected-precision reads through $F,D$. The transport and continuation rows $H,Q$ replay those same routes componentwise.

No coordinate remains from which a consumer could read open-cover compactness, host minima, choice-selected centers, quotient point equality, sequential compactness, or an external modulus function. Thus every public read stays within the finite selector packet.
\end{proof}
\leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorCarrier\_nonescape}

\begin{theorem}[Compact net modulus selector independence boundary]
\label{thm:compact-net-modulus-selector-independence-boundary}
The $\CompactNetModulusSelectorUp$ carrier is not bijective, as a NameCert obligation surface, to any one of its compact, continuous, metric, rational, finite-net-minimum-fold, or uniform-modulus siblings. It is the joint packet that stores the compact-net input, pointwise-modulus radii, selected lower-bound fold row, and tolerance-only handoff together.
\end{theorem}

\begin{proof}
The compact sibling supplies finite-net coverage but has no pointwise-modulus row, no selected lower-bound fold output, and no target-metric handoff.

The continuous sibling supplies pointwise-modulus rows but has no compact probe spine and no finite lower-bound fold over a bundled radius ledger.

The metric and rational siblings supply distance and order readbacks only. They do not carry the compact coverage row, the bundled center ledger, or the tolerance-to-precision handoff.

The finite-net-minimum-fold sibling supplies the lower-bound fold but not the compact coverage input, pointwise-modulus rows, or target-metric consumer route. The uniform-modulus sibling reads the resulting precision packet, while this selector records the compact-net and pointwise-modulus source rows that justify that precision. Hence no bijection preserves the listed NameCert obligations.
\end{proof}

\begin{theorem}[Compact net modulus selector TasteGate obligation]
\label{thm:compact-net-modulus-selector-tastegate-obligation}
The later Lean TasteGate file for namespace $\mathsf{BEDC.Derived.CompactNetModulusSelectorUp}$ must provide $\mathsf{Nontrivial}\ \CompactNetModulusSelectorUp$ and $\mathsf{FieldFaithful}\ \CompactNetModulusSelectorUp$ instances for the same finite carrier. These instances must preserve the compact-net input, pointwise-modulus radius rows, selected lower-bound fold row, tolerance-to-precision handoff, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorTasteGate\_single\_carrier\_alignment}

\begin{proof}
Nontriviality is witnessed by the dependency mix of the carrier. Removing the compact-net rows leaves no bundled source for the fold; removing the pointwise-modulus rows leaves no local continuity handoff; removing the fold row leaves no selected tolerance-only precision.

Field faithfulness records that these rows are preserved as one packet. A TasteGate consumer must therefore distinguish $\CompactNetModulusSelectorUp$ from its compact, continuous, metric, rational, finite-fold, and uniform-modulus siblings by the full coordinate surface $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$.
\end{proof}

\begin{theorem}[Compact net modulus selector root obligation triad]
\label{thm:compact-net-modulus-selector-root-obligation-triad}
Every accepted $\CompactNetModulusSelectorUp$ packet exposes exactly the compact finite-net row $X,\mathcal{P},C$, the pointwise-modulus radius rows $R,M$, the lower-bound fold row $F$, the selected precision $D$, and the structural rows $H,Q,P,N$ of \autoref{def:compact-net-modulus-selector-carrier}. The root obligation surface is therefore the triad consisting of finite-net input, pointwise-radius input, and metric-selector output. It exports no open-cover compactness, host minimum, quotient point equality, choice-selected center, or external modulus function.
\end{theorem}
\begin{proof}
Read the carrier definition. The finite-net part is visible in $X,\mathcal{P},C$, the radius and pointwise-modulus part is visible in $R,M$, and the selected metric precision is visible through $F,D$.

Use \autoref{thm:compact-net-modulus-selector-namecert-obligations}. Its compact-net exactness, pointwise-modulus exactness, lower-bound fold exactness, and non-escape clauses bind those rows to the same local naming surface.

The fold, non-escape, and TasteGate rows then exhaust the public consumer route. By \autoref{thm:compact-net-modulus-selector-fold-soundness}, \autoref{thm:compact-net-modulus-selector-nonescape}, and \autoref{thm:compact-net-modulus-selector-tastegate-obligation}, the output precision is read as one finite packet and not as any excluded compactness, minimum, quotient, center-selection, or external-modulus object.
\end{proof}

\begin{theorem}[Compact net modulus selector pointwise radius route]
\label{thm:compact-net-modulus-selector-pointwise-radius-route}
For an accepted $\CompactNetModulusSelectorUp$ carrier $S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)$, each center radius is read through the $\ContinuousFunctionUp$ pointwise-modulus row $M$, the positive $\RatUp$ radius row $R$, and the $\MetricSpaceUp$ source and target rows $X,Y$ before the finite lower-bound fold row $F$ can select the precision history $D$. No center radius is consumed as a free scalar, a host metric fact, or a hidden modulus choice.
\end{theorem}
\leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorCarrier\_pointwise\_radius\_route}
\begin{proof}
Begin with the displayed center ledger. The probe spine $\mathcal{P}$ and coverage row $C$ identify the bundled centers, while the radius row $R$ records positive rational histories attached to those centers.

Next read the pointwise route. The row $M$ supplies the $\ContinuousFunctionUp$ pointwise-modulus data at the bundled centers, and the rows $X,Y$ supply the source and target $\MetricSpaceUp$ distance reads through the continuation routes in $Q$.

Only after those rows are visible does the fold row $F$ select $D$. The NameCert obligations and fold soundness force $F$ to fold over the same $\mathcal{P}$ and $R$, so the selected precision cannot be read before the pointwise-radius and metric boundaries are in place.
\end{proof}

\begin{theorem}[Compact net modulus selector metric consumer boundary]
\label{thm:compact-net-modulus-selector-metric-consumer-boundary}
Downstream compact-uniform-continuity consumers of an accepted $\CompactNetModulusSelectorUp$ carrier receive a finite metric selector packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
and nothing outside that packet. The delivered boundary consists of compact finite-net input, pointwise-modulus radius rows, the finite lower-bound fold, selected precision, transport rows, continuation routes, provenance, and the local $\NameCert$ row; it does not deliver open-cover compactness, a host minimum, quotient point equality, a choice-selected center, or an external modulus function.
\end{theorem}
\leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorCarrier\_metric\_consumer\_boundary}
\begin{proof}
Project the consumer-facing packet from \autoref{def:compact-net-modulus-selector-carrier}. Its metric content is displayed by $X,Y,R,D$ together with the finite center and fold rows $\mathcal{P},C,M,F$.

Apply the NameCert and non-escape theorems. They require every consumer read to pass through the listed carrier rows, transports, routes, provenance, and local name.

The sibling inputs cited in the chapter introduction supply the compact, continuous, metric, rational, and fold readings, but this selector exports only their assembled finite packet. Thus the compact-uniform-continuity consumer receives a selector boundary rather than an open-cover compactness principle, host minimum, quotient equality, selected center, or external modulus.
\end{proof}

\begin{theorem}[Compact net modulus selector consumer factorization]
\label{thm:compact-net-modulus-selector-consumer-factorization}
Every downstream $\UniformModulusUp$ consumer of an accepted $\CompactNetModulusSelectorUp$ carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
factors through compact finite-net input $X,\mathcal{P},C$, pointwise continuous radius rows $R,M$, metric rows $X,Y$, the positive rational tolerance row $E$, finite lower-bound fold $F$, selected precision $D$, and structural rows $H,Q,P,N$. No such consumer may replace this route by open-cover compactness, a host minimum, quotient point equality, a choice-selected center, sequential compactness, or an external modulus function.
\end{theorem}
\begin{proof}
Begin with the local NameCert obligations. They attach the accepted selector to the displayed compact, continuous, metric, rational, fold, selected-precision, transport, route, provenance, and naming rows of $S$.

Use fold soundness and the pointwise radius route. The fold row $F$ reads the finite probe spine and radius ledger, while each radius row reaches $D$ only through the pointwise continuous row $M$, metric rows $X,Y$, and positive rational tolerance row $E$.

Now apply the metric consumer boundary. A downstream $\UniformModulusUp$ consumer receives the assembled selector packet, not a detached compactness theorem or detached modulus function.

Finally invoke non-escape. Since the carrier has no row for open-cover compactness, host minima, quotient point equality, choice-selected centers, sequential compactness, or external modulus functions, every consumer factors through the displayed rows $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$.
\end{proof}
\leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorCarrier\_consumer\_factorization}

\begin{theorem}[Compact net modulus selector request obligation surface]
\label{thm:compact-net-modulus-selector-request-obligation-surface}
For an accepted carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the request obligation surface distinguishes precision requests by visible tolerance and finite-net rows. If two requests have tolerance rows $E_0$ and $E_1$ or finite-net rows $(\mathcal{P}_0,C_0,R_0)$ and $(\mathcal{P}_1,C_1,R_1)$ that are not identified by the displayed $\hsame$ rows $H$, then their selected precision histories must be read as distinct request packets through $Q,P,N$. This obligation is part of the TasteGate surface of \autoref{thm:compact-net-modulus-selector-tastegate-obligation}.
\end{theorem}
\begin{proof}
Project the carrier. The tolerance row $E$, finite probe spine $\mathcal{P}$, coverage row $C$, subordinate radius row $R$, selected precision row $D$, transports $H$, routes $Q$, provenance $P$, and local name $N$ are visible coordinates of $S$.

Use the NameCert obligations and fold soundness. They require selected precision to be read through the same tolerance, compact-net, pointwise-modulus, and fold rows that produced it.

Apply the TasteGate obligation surface. Because TasteGate preservation must keep the displayed carrier rows, a change in visible tolerance or finite-net data that is not transported by $H$ cannot be collapsed into the same request packet by $Q,P,N$.
\end{proof}

\begin{theorem}[Compact net modulus selector TasteGate nontriviality boundary]
\label{thm:compact-net-modulus-selector-tastegate-nontriviality-boundary}
The TasteGate obligation for $\CompactNetModulusSelectorUp$ is nontrivial on the displayed carrier $S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)$. At least the request with tolerance row $E_0$ and finite-net row $(\mathcal{P}_0,C_0,R_0)$ and the request with tolerance row $E_1$ or finite-net row $(\mathcal{P}_1,C_1,R_1)$ must remain distinguishable whenever their visible rows are not connected by the displayed $\hsame$ transport $H$.

Thus the carrier cannot be replaced by a one-element surface while preserving the compact-net input, pointwise-modulus rows, lower-bound fold row, selected precision history, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row named in \autoref{thm:compact-net-modulus-selector-tastegate-obligation}.
\end{theorem}
\begin{proof}
Start from the request obligation surface. It ties a selected precision history to the tolerance row and finite-net rows that generated the request.

If two requests differ in visible tolerance or finite-net data and $H$ does not identify those rows, the local classifier has no displayed transport that can merge them. The routes $Q$ and provenance row $P$ must therefore preserve the difference when the local name $N$ exports the packet.

The TasteGate obligation requires preservation of the full coordinate surface. A one-element carrier would erase the displayed distinction between the two request packets, so it cannot satisfy the nontriviality boundary for this NameCert surface.
\end{proof}

\begin{theorem}[Compact net modulus selector field-faithful row]
\label{thm:compact-net-modulus-selector-field-faithful-row}
Any consumer preserving all displayed rows of an accepted $\CompactNetModulusSelectorUp$ carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
preserves the exported precision history $D$ together with its compact-net, pointwise-modulus, lower-bound fold, transport, route, provenance, and naming evidence. This field-faithful row is the paper-side obligation that allows future Lean instances for $\mathsf{Nontrivial}\ \CompactNetModulusSelectorUp$ and $\mathsf{FieldFaithful}\ \CompactNetModulusSelectorUp$ to use the displayed request packets rather than a one-element carrier.
\end{theorem}
\begin{proof}
Read $D$ through the carrier and the fold soundness theorem. The selected precision is not a free output; it is the lower-bound fold result tied to $E,\mathcal{P},C,R,M,F$.

Use non-escape and the TasteGate obligation. Every public consumer of the selected precision must preserve the transport rows $H$, continuation routes $Q$, package provenance $P$, and local name $N$ along with the compact, continuous, metric, rational, and fold inputs.

Therefore a row-preserving consumer preserves the exported precision history as a field of the same packet. This is exactly the field-faithful surface needed for later Lean instances, without collapsing the NameCert carrier to one element.
\end{proof}

\begin{theorem}[Compact net modulus selector source coverage]
\label{thm:compact-net-modulus-selector-source-coverage}
Let
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
be an accepted $\CompactNetModulusSelectorUp$ carrier. Every accepted selector packet reads the compact cover rows, finite-net fold row, continuous pointwise-modulus rows, source and target metric distance rows, positive $\RatUp$ precision row, and $\UniformModulusUp$ output handoff through the displayed carrier coordinates of \autoref{def:compact-net-modulus-selector-carrier}. No source row is supplied by an ambient compactness principle, host minimum, quotient point equality, choice-selected center, or external modulus function.
\end{theorem}
\begin{proof}
Start with the carrier inventory of \autoref{def:compact-net-modulus-selector-carrier}. The compact source is visible in $X,\mathcal{P},C,R$, the continuous pointwise rows are visible in $M$, the metric rows are visible in $X,Y$, and the positive precision row is visible in $D$.

Apply \autoref{thm:compact-net-modulus-selector-fold-soundness} and \autoref{thm:compact-net-modulus-selector-pointwise-radius-route}. The fold reads only the displayed probe spine and radius ledger, while each center radius reaches the selected precision only through the pointwise-modulus and metric rows already stored in $S$.

Finally use \autoref{thm:compact-net-modulus-selector-metric-consumer-boundary} and \autoref{thm:compact-net-modulus-selector-field-faithful-row}. A downstream $\UniformModulusUp$ consumer receives the same field-preserving selector packet, so every public source read remains inside the listed carrier coordinates.
\end{proof}

\begin{theorem}[Compact net modulus selector center ledger exposure]
\label{thm:compact-net-modulus-selector-center-ledger-exposure}
Let
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
be an accepted $\CompactNetModulusSelectorUp$ carrier. Every accepted selector packet exposes the finite probe spine $\mathcal{P}$, center coverage row $C$, subordinate radius row $R$, and pointwise-modulus row $M$ before the selected precision row $D$ can be read. Thus the precision handoff is never read from a hidden center selector, a quotient point equality, an ambient compactness principle, or an external modulus function.
\end{theorem}
\begin{proof}
Project $S$ through \autoref{def:compact-net-modulus-selector-carrier}. The finite probe spine, center coverage row, subordinate radius row, and pointwise-modulus row are displayed coordinates of the same accepted packet as the selected precision row.

Apply \autoref{thm:compact-net-modulus-selector-namecert-obligations}. Its compact-net exactness and pointwise-modulus exactness rows force $C,R,M$ to be public before a consumer can reach the lower-bound fold or the selected precision.

Finally use \autoref{thm:compact-net-modulus-selector-pointwise-radius-route}. Each center radius reaches the precision threshold only through the displayed pointwise-modulus and metric rows, so no hidden center choice, quotient equality, ambient compactness principle, or external modulus function can supply $D$.
\end{proof}

\begin{theorem}[Compact net modulus selector fold radius exhaustion]
\label{thm:compact-net-modulus-selector-fold-radius-exhaustion}
For an accepted carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the fold row $F$ consumes exactly the displayed finite probe spine $\mathcal{P}$ and subordinate radius ledger $R$ before it exports the selected precision row $D$. The fold cannot read a host minimum, a choice-selected center, quotient point equality, or an external modulus as a second source for the selected radius budget.
\end{theorem}
\begin{proof}
Start with \autoref{thm:compact-net-modulus-selector-fold-soundness}. It identifies the lower-bound fold as a read over the displayed probe spine and radius ledger.

Use \autoref{thm:compact-net-modulus-selector-finite-fold-budget-exactness}. The selected precision is exact only as the fold output over $\mathcal{P}$ and $R$, so a second host minimum or external rational infimum has no carrier coordinate.

Apply non-escape and field faithfulness, \autoref{thm:compact-net-modulus-selector-nonescape} and \autoref{thm:compact-net-modulus-selector-field-faithful-row}. Public consumers preserve the displayed fold route and cannot replace it by choice-selected center data, quotient point equality, or an external modulus.
\end{proof}

\begin{theorem}[Compact net modulus selector UniformModulus handoff]
\label{thm:compact-net-modulus-selector-uniformmodulus-handoff}
Any downstream $\UniformModulusUp$ read of the selected precision row $D$ from an accepted $\CompactNetModulusSelectorUp$ packet passes through the already exposed compact row $X,\mathcal{P},C,R$, continuous pointwise row $M$, metric rows $X,Y$, rational tolerance row $E$, fold row $F$, transport row $H$, continuation row $Q$, provenance row $P$, and local $\NameCert$ row $N$. The handoff therefore consumes the selector obligation surface rather than a parameter-only modulus promise.
\end{theorem}
\begin{proof}
Begin with source coverage, \autoref{thm:compact-net-modulus-selector-source-coverage}. It places every public source read for the uniform-modulus output inside the displayed selector coordinates.

Next use the metric consumer boundary, \autoref{thm:compact-net-modulus-selector-metric-consumer-boundary}. A metric-facing consumer must keep the compact, continuous, rational, and fold inputs attached to the selected threshold rather than reading the threshold as a detached number.

Finally apply the request obligation surface and public handoff rows, \autoref{thm:compact-net-modulus-selector-tastegate-obligation} and \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}. They carry the same transport, continuation, provenance, and local naming rows into $\UniformModulusUp$, so the downstream read of $D$ is exactly the exposed selector route.
\end{proof}

\begin{theorem}[Compact net modulus selector metric threshold stability]
\label{thm:compact-net-modulus-selector-metric-threshold-stability}
For accepted $\CompactNetModulusSelectorUp$ carriers
$$
S_0=(X_0,Y_0,E_0,\mathcal{P}_0,C_0,R_0,M_0,F_0,D_0,H_0,Q_0,P_0,N_0)
$$
and
$$
S_1=(X_1,Y_1,E_1,\mathcal{P}_1,C_1,R_1,M_1,F_1,D_1,H_1,Q_1,P_1,N_1),
$$
componentwise $\hsame$ transport along the displayed carrier rows and replay through the displayed $\Cont$ routes preserves the chosen precision threshold. Thus any metric consumer that reads $D_0$ below the pointwise-radius fold route of $S_0$ reads the transported threshold $D_1$ through the corresponding fold, radius, pointwise-modulus, metric, provenance, and naming rows of $S_1$.
\end{theorem}
\begin{proof}
Project both packets with \autoref{def:compact-net-modulus-selector-carrier}. The transport rows $H_0,H_1$ name the componentwise $\hsame$ identifications for compact-net data, tolerance histories, radius ledgers, pointwise-modulus rows, folds, selected precision histories, routes, provenance, and local names.

Use \autoref{thm:compact-net-modulus-selector-pointwise-radius-route} to identify the threshold route before the fold is read. The selected precision is available only after the corresponding radius and pointwise-modulus rows have been transported through the displayed metric rows.

Apply \autoref{thm:compact-net-modulus-selector-fold-soundness}. Since the fold row is over the transported probe spine and radius ledger, the selected threshold is preserved as the same finite lower-bound read rather than as a host minimum.

The consumer-facing statement follows from \autoref{thm:compact-net-modulus-selector-metric-consumer-boundary} and \autoref{thm:compact-net-modulus-selector-field-faithful-row}. Field-preserving consumers must keep the selected precision together with its compact, continuous, metric, rational, fold, route, provenance, and naming evidence.
\end{proof}

\begin{theorem}[Compact net modulus selector ledger route exactness]
\label{thm:compact-net-modulus-selector-ledger-route-exactness}
Every public read of an accepted $\CompactNetModulusSelectorUp$ selector packet factors through the finite ledger rows
$$
X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N
$$
named by \autoref{def:compact-net-modulus-selector-carrier}. In particular, compact-cover reads, pointwise-modulus reads, metric-threshold reads, rational-precision reads, finite-fold reads, and $\UniformModulusUp$ handoff reads use the same displayed ledger route, with no host minimum and no ambient compactness principle.
\end{theorem}
\begin{proof}
First read the ledger from \autoref{def:compact-net-modulus-selector-carrier}. The listed coordinates are the only rows exported by the selector packet.

Next apply \autoref{thm:compact-net-modulus-selector-fold-soundness} and \autoref{thm:compact-net-modulus-selector-pointwise-radius-route}. They force the selected precision to pass through the displayed compact-net, radius, pointwise-modulus, metric, and fold rows before any consumer can use it.

Finally apply \autoref{thm:compact-net-modulus-selector-metric-consumer-boundary} and \autoref{thm:compact-net-modulus-selector-field-faithful-row}. Public consumers preserve exactly the carrier fields they receive, so the route cannot be replaced by a host minimum, ambient compactness principle, quotient equality, selected-center choice, or external modulus.
\end{proof}

\begin{theorem}[Compact net modulus selector compact-cover consumer lock]
\label{thm:compact-net-modulus-selector-compact-cover-consumer-lock}
Let
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
be an accepted $\CompactNetModulusSelectorUp$ carrier. Every compact-cover consumer of $S$ reads the source metric row $X$, finite probe spine $\mathcal{P}$, coverage ledger $C$, and subordinate radius row $R$ before it can read the pointwise-modulus row $M$, the fold row $F$, or the selected precision row $D$. The consumer imports no open-cover compactness principle and no choice-selected center.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-net-modulus-selector-carrier}. The compact-cover portion is displayed by $X,\mathcal{P},C,R$, while $M,F,D$ are later rows in the same finite selector packet.

Use the NameCert obligations and fold soundness. Compact-net exactness binds cover reads to $X,\mathcal{P},C,R$, and lower-bound fold exactness can only use the already displayed probe spine and radius ledger.

Finally apply non-escape and the TasteGate obligation row. Since neither open-cover compactness nor a choice-selected center is a carrier coordinate, no compact-cover consumer can import either object before the selector reaches $M,F,D$.
\end{proof}

\begin{theorem}[Compact net modulus selector finite-fold budget exactness]
\label{thm:compact-net-modulus-selector-finite-fold-budget-exactness}
For an accepted carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the selected precision history $D$ is exact only as the $\FiniteNetMinimumFoldUp$ output $F$ over the displayed probe spine $\mathcal{P}$ and radius ledger $R$. No host minimum, external rational infimum, hidden compactness choice, or quotient of center histories can serve as a second budget source for $D$.
\end{theorem}
\begin{proof}
Read $D$ through the carrier. The only row that exports a selected lower-bound history is $F$, and $F$ is named as the fold over $\mathcal{P}$ and $R$.

Apply the NameCert lower-bound fold obligation together with \autoref{thm:compact-net-modulus-selector-fold-soundness}. These rows force the budget comparison to remain inside the displayed finite probe spine and radius ledger.

Use non-escape and TasteGate preservation to exclude alternate sources. A host minimum, external infimum, hidden center choice, or quotient center history is not preserved as a field of $S$, so it cannot be the exactness witness for $D$.
\end{proof}

\begin{theorem}[Compact net modulus selector uniform-modulus public handoff]
\label{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}
Every $\UniformModulusUp$ consumer downstream of an accepted $\CompactNetModulusSelectorUp$ packet receives exactly the assembled finite packet
$$
X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N.
$$
It receives the tolerance row, compact finite-net rows, pointwise-modulus rows, selected fold budget, transports, continuation routes, provenance, and local naming row, and it receives no open-cover compactness, host minimum, choice-selected center, quotient point equality, or external modulus function.
\end{theorem}
\begin{proof}
Start with the carrier and the NameCert obligations. They expose $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$ as the full selector packet and bind cover, pointwise, fold, and route reads to those rows.

Use fold soundness to identify $D$ as the precision handed to the uniform-modulus consumer. The selected precision is produced over the displayed probe spine and radius ledger, not by an external selector.

Finally apply non-escape and the TasteGate obligation row. Every downstream public handoff preserves the same finite fields, so excluded compactness, minimum, choice, quotient, and external-modulus objects are not delivered to $\UniformModulusUp$.
\end{proof}

\begin{theorem}[Compact net modulus selector carrier admission scope]
\label{thm:compact-net-modulus-selector-carrier-admission-scope}
For an accepted $\CompactNetModulusSelectorUp$ carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
carrier admission exposes the compact source metric row $X$, target metric row $Y$, tolerance row $E$, finite probe bundle $\mathcal{P}$, coverage ledger $C$, subordinate radius row $R$, pointwise-modulus row $M$, lower-bound fold row $F$, selected precision row $D$, transport rows $H$, continuation routes $Q$, provenance $P$, and local naming row $N$ as one finite surface. A consumer entering $\UniformModulusUp$ through this carrier must keep all public reads on those rows and cannot replace them by open-cover compactness, a host minimum, a choice-selected center, quotient point equality, or an external modulus function.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{thm:compact-net-modulus-selector-namecert-obligations}. Carrier admission and the local NameCert clauses expose exactly the displayed tuple $S$ and bind the compact-net, pointwise-modulus, lower-bound, transport, route, provenance, and naming rows to the same packet.

Use \autoref{thm:compact-net-modulus-selector-tastegate-nontriviality-boundary}. The finite probe surface is admitted only as the displayed bundle with its local rows, so the carrier cannot be read as a hidden open-cover compactness principle or as a selected-center choice.

Finally apply \autoref{thm:compact-net-modulus-selector-field-faithful-row} and \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}. Field faithfulness preserves the tuple coordinates, and the public handoff delivers the same finite selector surface to $\UniformModulusUp$.
\end{proof}

\begin{theorem}[Compact net modulus selector lower-bound route totality]
\label{thm:compact-net-modulus-selector-lower-bound-route-totality}
For an accepted carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
every public read of the selected precision row $D$ is total only through the finite lower-bound fold row $F$ over $\mathcal{P}$ and $R$, followed by the route rows $H,Q,P,N$ that deliver the selector into $\UniformModulusUp$. No consumer may read $D$ as a host infimum, host minimum, ambient compactness witness, quotient of centers, or external modulus.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:compact-net-modulus-selector-finite-fold-budget-exactness}. It identifies $D$ as the exact output of the displayed lower-bound fold $F$ over the finite probe spine and subordinate radius ledger.

Apply \autoref{thm:compact-net-modulus-selector-namecert-obligations}. The lower-bound clause is part of the same carrier admission surface, so the route from $F$ to $D$ must keep $X,Y,E,\mathcal{P},C,R,M,H,Q,P,N$ attached.

The public handoff of \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}, together with the TasteGate boundary and field-faithful row of \autoref{thm:compact-net-modulus-selector-tastegate-nontriviality-boundary} and \autoref{thm:compact-net-modulus-selector-field-faithful-row}, then sends precisely that finite lower-bound route to $\UniformModulusUp$ and excludes every host or quotient substitute for $D$.
\end{proof}

\begin{theorem}[Compact net modulus selector obligation envelope]
\label{thm:compact-net-modulus-selector-obligation-envelope}
The obligation envelope of an accepted $\CompactNetModulusSelectorUp$ carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
is the finite carrier-admission row, the TasteGate nontriviality surface for $\mathcal{P}$, the field-faithful row, the lower-bound fold route $F$, the selected precision row $D$, and the public consumer route into $\UniformModulusUp$. This envelope is exactly the surface available to downstream consumers, and it contains no open-cover compactness, sequential compactness, host minimum, choice-selected center, quotient point equality, or external modulus function.
\end{theorem}
\begin{proof}
First read the NameCert obligations through \autoref{thm:compact-net-modulus-selector-namecert-obligations}. They collect carrier admission, compact-net exactness, pointwise-modulus exactness, lower-bound fold exactness, transport stability, and non-escape into one local packet.

Next use \autoref{thm:compact-net-modulus-selector-finite-fold-budget-exactness}. This pins the selected precision row $D$ to the finite fold row $F$ over $\mathcal{P}$ and $R$ rather than to any ambient minimum principle.

Finally combine \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}, \autoref{thm:compact-net-modulus-selector-tastegate-nontriviality-boundary}, and \autoref{thm:compact-net-modulus-selector-field-faithful-row}. The handoff exports the same tuple to $\UniformModulusUp$, TasteGate keeps the probe surface finite and nontrivial, and field faithfulness prevents a consumer from replacing the displayed rows by hidden compactness, choice, quotient, or external-modulus data.
\end{proof}

\begin{theorem}[Compact net modulus selector route primitive scope]
\label{thm:compact-net-modulus-selector-route-primitive-scope}
Every accepted $\CompactNetModulusSelectorUp$ packet binds the $\CompactUp$ finite-net rows, $\ContinuousFunctionUp$ pointwise-modulus rows, $\MetricSpaceUp$ distance rows, $\RatUp$ positive precision rows, $\FiniteNetMinimumFoldUp$ lower-bound rows, $\mathsf{ProbeBundle}$ rows, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ as its complete primitive scope. The selector supplies no open-cover compactness, sequential compactness, host minima, choice-selected centers, quotient point equality, or external modulus functions.
\end{theorem}
\begin{proof}
First project the carrier and NameCert obligations, \autoref{def:compact-net-modulus-selector-carrier} and \autoref{thm:compact-net-modulus-selector-namecert-obligations}. They display exactly the compact-net, metric, positive rational, probe, pointwise-modulus, lower-bound fold, transport, continuation, provenance, and local naming rows.

Next use the pointwise-radius route and finite-fold budget exactness, \autoref{thm:compact-net-modulus-selector-pointwise-radius-route} and \autoref{thm:compact-net-modulus-selector-finite-fold-budget-exactness}. These routes force every radius and selected precision read through $X,Y,E,\mathcal{P},C,R,M,F,D$ before a public handoff can occur.

Finally apply the uniform-modulus public handoff and obligation envelope, \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff} and \autoref{thm:compact-net-modulus-selector-obligation-envelope}. The downstream consumer receives the same finite selector packet, so any open-cover, sequential compactness, host-minimum, choice, quotient, or external-modulus object would require a primitive coordinate absent from the accepted carrier.
\end{proof}

\begin{theorem}[Compact net modulus selector request route determinacy]
\label{thm:compact-net-modulus-selector-request-route-determinacy}
For an accepted $\CompactNetModulusSelectorUp$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the visible tolerance row $E$ and finite-net rows $X,\mathcal{P},C,R$
determine the request packet read by the selector. A public request consumer
may continue through $M,F,D,H,Q,P,N$, but it cannot replace the request by
open-cover compactness, selected centers, host metric data, quotient point
equality, or an external modulus function.
\end{theorem}
\begin{proof}
Begin with the request obligation surface,
\autoref{thm:compact-net-modulus-selector-request-obligation-surface}. It binds
the tolerance, finite-net, metric, and pointwise-radius rows to the same
selector request before the selected precision can be read.

Next apply \autoref{thm:compact-net-modulus-selector-namecert-obligations}.
The carrier admission and local naming clauses keep $E$ and
$X,\mathcal{P},C,R$ inside one accepted packet with the pointwise-modulus and
fold rows.

Finally use \autoref{thm:compact-net-modulus-selector-field-faithful-row} and
\autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}. Field
faithfulness preserves the displayed rows, and the handoff sends exactly that
request packet to $\UniformModulusUp$ without adding host compactness, selected
centers, quotient equality, or an external modulus.
\end{proof}

\begin{theorem}[Compact net modulus selector fold consumer exhaustion]
\label{thm:compact-net-modulus-selector-fold-consumer-exhaustion}
Every public read of the selected precision row $D$ is exhausted by the finite
fold row $F$ over the same $\mathsf{ProbeBundle}$ $\mathcal{P}$ and radius
ledger $R$. The read retains the compact, continuous, metric, rational,
transport, route, provenance, and local naming rows of $S$, and it exports no
host minimum, selected-center choice, quotient point equality, or open-cover
compactness witness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:compact-net-modulus-selector-finite-fold-budget-exactness}.
It identifies $D$ as the output of the displayed fold $F$ over
$\mathcal{P}$ and $R$, not as a host minimum or external rational infimum.

Use \autoref{thm:compact-net-modulus-selector-fold-soundness} together with
\autoref{thm:compact-net-modulus-selector-pointwise-radius-route}. The fold
reads only the bundled probes and subordinate radii supplied by the same metric
and pointwise-modulus rows.

Apply \autoref{thm:compact-net-modulus-selector-namecert-obligations} and
\autoref{thm:compact-net-modulus-selector-field-faithful-row}. These keep the
fold, selected precision, transports, routes, provenance, and local naming rows
attached to the carrier, so no unlisted center, quotient equality, or host
minimum can supply $D$.
\end{proof}

\begin{theorem}[Compact net modulus selector uniform request factorization]
\label{thm:compact-net-modulus-selector-uniform-request-factorization}
Every $\UniformModulusUp$ consumer of an accepted
$\CompactNetModulusSelectorUp$ packet factors through the compact, continuous,
metric, $\RatUp$, $\FiniteNetMinimumFoldUp$, $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ rows displayed by
\autoref{thm:compact-net-modulus-selector-route-primitive-scope}. The
factorization exports the selected request and precision boundary only through
those rows.
\end{theorem}
\begin{proof}
First combine
\autoref{thm:compact-net-modulus-selector-request-route-determinacy} with
\autoref{thm:compact-net-modulus-selector-fold-consumer-exhaustion}. The
request is fixed by the tolerance and finite-net rows, and the selected
precision is fixed by the finite fold over the same probe bundle and radius
ledger.

Next apply \autoref{thm:compact-net-modulus-selector-namecert-obligations}. The
carrier, compact-net, pointwise-modulus, lower-bound, transport, route,
provenance, and local naming clauses keep these request rows in one finite
packet.

Finally use \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}
and \autoref{thm:compact-net-modulus-selector-route-primitive-scope}. They pass
the same packet to $\UniformModulusUp$ and identify all public primitive rows,
so no open-cover compactness, host metric primitive, selected center, quotient
point equality, or external modulus remains available.
\end{proof}

\begin{theorem}[Compact net modulus selector selected precision exactness]
\label{thm:compact-net-modulus-selector-selected-precision-exactness}
For an accepted $\CompactNetModulusSelectorUp$ carrier
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
a downstream $\UniformModulusUp$ consumer reads the selected precision row $D$
if and only if the same visible tolerance row $E$, finite probe spine
$\mathcal{P}$, coverage row $C$, subordinate radius rows $R$,
pointwise-modulus rows $M$, fold row $F$, transports $H$, routes $Q$,
provenance $P$, and local $\NameCert$ row $N$ are displayed. The read is
therefore completely determined by those visible rows and exports no
open-cover compactness, host minimum, quotient point equality,
choice-selected center, or external modulus function.
\end{theorem}
\begin{proof}
For necessity, start with
\autoref{thm:compact-net-modulus-selector-uniform-request-factorization}. Any
downstream $\UniformModulusUp$ consumer must factor through the displayed
selector route before it can read $D$.

Apply \autoref{thm:compact-net-modulus-selector-namecert-obligations}. The
carrier, compact-net, pointwise-modulus, lower-bound fold, transport, route,
provenance, and local naming clauses keep
$E,\mathcal{P},C,R,M,F,H,Q,P,N$ attached to the same accepted packet.

For sufficiency, use \autoref{thm:compact-net-modulus-selector-fold-soundness}.
Once the finite probe spine, radius ledger, pointwise-modulus rows, and fold
row are displayed inside the same packet, $D$ is the selected finite lower-bound
read rather than a host minimum.

Finally apply \autoref{thm:compact-net-modulus-selector-ledger-route-exactness}
and \autoref{thm:compact-net-modulus-selector-uniform-request-factorization}.
The ledger route and uniform request factorization carry exactly that visible
packet to the downstream consumer, so open-cover compactness, host minima,
quotient point equality, choice-selected centers, and external modulus
functions have no coordinate from which to determine $D$.
\end{proof}

\begin{theorem}[CompactNetModulusSelector finite-net budget route]
\label{thm:compact-net-modulus-selector-finite-net-budget-route}
For an accepted $\CompactNetModulusSelectorUp$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
every modulus read factors through the $\CompactUp$ finite-net rows $X,\mathcal{P},C,R$, the $\MetricSpaceUp$ distance rows $X,Y$, the $\RatUp$ tolerance row $E$, and the $\UniformModulusUp$ request rows before exposing the selected net budget $D$. The route exports no open-cover compactness, choice-selected point, host real metric, quotient center equality, or external modulus function.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{thm:compact-net-modulus-selector-carrier-admission-scope}. It exposes the compact finite-net rows, metric rows, rational tolerance, pointwise-modulus row, lower-bound fold, selected precision, transport, route, provenance, and local naming rows as one finite surface.

Use the pointwise-radius and lower-bound routes, \autoref{thm:compact-net-modulus-selector-pointwise-radius-route} and \autoref{thm:compact-net-modulus-selector-lower-bound-route-totality}. They force the selected budget to pass through the displayed finite probe spine, subordinate radii, and lower-bound fold before $D$ is readable.

Apply the uniform-modulus public handoff and route primitive scope, \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff} and \autoref{thm:compact-net-modulus-selector-route-primitive-scope}. These rows deliver the same finite selector packet into $\UniformModulusUp$ and exclude open-cover compactness, host metric supply, selected centers, quotient point equality, and external modulus functions.
\end{proof}

\begin{theorem}[CompactNetModulusSelector primitive-scope closure]
\label{thm:compact-net-modulus-selector-primitive-scope-closure}
For every accepted $\CompactNetModulusSelectorUp$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the public selector route is scoped exactly by the $\CompactUp$, $\ContinuousFunctionUp$, $\MetricSpaceUp$, $\RatUp$, $\FiniteNetMinimumFoldUp$, $\mathsf{ProbeBundle}$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed in \autoref{def:compact-net-modulus-selector-carrier}. Every $\UniformModulusUp$ read of $D$ factors through those rows, and the exported surface contains no open-cover compactness, sequential compactness, host minimum, selected center, quotient point equality, or external modulus function.
\end{theorem}
\begin{proof}
Project the accepted packet through \autoref{def:compact-net-modulus-selector-carrier}. This reads $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$ as the whole finite selector carrier and leaves no additional compactness or modulus coordinate.

Apply \autoref{thm:compact-net-modulus-selector-route-primitive-scope}. It identifies the primitive public route as the displayed compact, continuous, metric, rational, finite-fold, probe-bundle, history, transport, continuation, provenance, and local naming rows.

Use \autoref{thm:compact-net-modulus-selector-finite-net-budget-route} to bind the selected budget $D$ to the compact finite-net rows, pointwise-radius route, and finite lower-bound fold before any uniform-modulus consumer can read it.

Finally combine \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff} with \autoref{thm:compact-net-modulus-selector-obligation-envelope}. The downstream $\UniformModulusUp$ handoff therefore sees only the finite selector route and not open-cover compactness, sequential compactness, a host minimum, a selected center, quotient point equality, or an external modulus function.
\end{proof}

\begin{theorem}[CompactNetModulusSelector center-radius monotonicity]
\label{thm:compact-net-modulus-selector-center-radius-monotonicity}
For every accepted $\CompactNetModulusSelectorUp$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the selected precision row $D$ stays below every displayed center radius in the finite radius ledger $R$ as read through the finite fold row $F$. The comparison is a finite selector comparison inside the same packet and not an open-cover compactness argument, host minimum, quotient point equality, choice-selected center, or external modulus computation.
\end{theorem}
\begin{proof}
Start with fold soundness and lower-bound route totality, \autoref{thm:compact-net-modulus-selector-fold-soundness} and \autoref{thm:compact-net-modulus-selector-lower-bound-route-totality}. They identify $D$ as the lower-bound fold output read from the same nonempty probe spine and displayed radius ledger.

Next apply finite-fold budget exactness, \autoref{thm:compact-net-modulus-selector-finite-fold-budget-exactness}. The comparison of $D$ with each displayed center radius is made through $F$ over $\mathcal{P}$ and $R$, so no ambient minimum or quotient equality can supply a different bound.

Finally use primitive-scope closure from \autoref{thm:compact-net-modulus-selector-primitive-scope-closure}. The public selector route contains only $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$, which keeps the center-radius monotonicity inside the finite packet.
\end{proof}

\begin{theorem}[CompactNetModulusSelector fold-output positive]
\label{thm:compact-net-modulus-selector-fold-output-positive}
For every accepted $\CompactNetModulusSelectorUp$ packet $S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)$, the fold output $D$ remains a positive $\RatUp$ precision history. Its positivity is read through the same nonempty finite probe spine $\mathcal{P}$ and radius ledger $R$ that feed the fold row $F$, and not through a host minimum, open-cover compactness principle, selected center, quotient point equality, or external modulus.
\end{theorem}
\begin{proof}
Begin with the accepted carrier and fold soundness, \autoref{def:compact-net-modulus-selector-carrier} and \autoref{thm:compact-net-modulus-selector-fold-soundness}. The carrier stores a positive tolerance history and positive subordinate radius rows, while fold soundness reads the output through the displayed finite fold.

Use lower-bound route totality and finite-fold budget exactness, \autoref{thm:compact-net-modulus-selector-lower-bound-route-totality} and \autoref{thm:compact-net-modulus-selector-finite-fold-budget-exactness}. These results keep $D$ on the same nonempty probe spine and radius ledger, so the fold output is a $\RatUp$ precision history rather than a host-selected real number.

Finally apply center-radius monotonicity from \autoref{thm:compact-net-modulus-selector-center-radius-monotonicity}. Since $D$ is read below the displayed positive radii through $F$, positivity remains part of the finite selector packet and cannot be replaced by an external compactness or modulus object.
\end{proof}

\begin{theorem}[CompactNetModulusSelector uniform-consumer precision lock]
\label{thm:compact-net-modulus-selector-uniform-consumer-precision-lock}
Every downstream compact-uniform-continuity consumer of an accepted $\CompactNetModulusSelectorUp$ packet receives only the finite selector route
$$
X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N.
$$
The consumer cannot replace the selected precision row by open-cover compactness, a host minimum, quotient point equality, a choice-selected center, or an external modulus function.
\end{theorem}
\begin{proof}
Start with the uniform-modulus public handoff, \autoref{thm:compact-net-modulus-selector-uniform-modulus-public-handoff}. It sends the downstream $\UniformModulusUp$ consumer the same finite selector packet rather than an ambient compactness or modulus object.

Next combine finite-net budget routing with fold-output positivity, \autoref{thm:compact-net-modulus-selector-finite-net-budget-route} and \autoref{thm:compact-net-modulus-selector-fold-output-positive}. The selected precision row is a positive $\RatUp$ fold output tied to $X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N$.

Finally apply primitive-scope closure from \autoref{thm:compact-net-modulus-selector-primitive-scope-closure}. The primitive route exposes no open-cover compactness, host minimum, quotient point equality, selected-center oracle, or external modulus coordinate, so the uniform consumer is locked to the displayed precision row $D$.
\end{proof}

\begin{definition}[Compact net modulus selector root readiness]
\label{def:compact-net-modulus-selector-root-readiness}
The root-readiness packet for $\CompactNetModulusSelectorUp$ is the finite tuple
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N)
$$
read with the following public roles:
\begin{enumerate}
\item $X,\mathcal{P},C$ are the compact-net source rows from $\CompactUp$, including the finite center spine and its coverage rows;
\item $R,M$ are the subordinate positive $\RatUp$ radius rows and the $\ContinuousFunctionUp$ pointwise-modulus rows attached to the same centers and tolerance row $E$;
\item $F,D$ are the $\FiniteNetMinimumFoldUp$ fold output and the selected positive precision row exported from that fold;
\item $H,Q$ are the displayed $\hsame$ transport rows and $\Cont$ consumer routes through the metric, compact, continuous, rational, fold, and uniform-modulus interfaces;
\item $P,N$ are the package provenance and the local $\NameCert_{\CompactNetModulusSelectorUp}$ row.
\end{enumerate}
Root readiness means that these rows are sufficient for downstream uniform-modulus consumers to read the selector as a finite compact-net handoff: compact coverage is exposed through $X,\mathcal{P},C$, pointwise-radius control through $R,M$, finite lower-bound selection through $F,D$, and all public transport through $H,Q,P,N$.
\end{definition}

\begin{theorem}[Compact net modulus selector finite-net exposure]
\label{thm:compact-net-modulus-selector-finite-net-exposure}
For every accepted root-ready $\CompactNetModulusSelectorUp$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
each selected precision row exposes a nonempty finite $\mathsf{ProbeBundle}$ spine $\mathcal{P}$, the compact coverage rows $C$ over the source row $X$, and the subordinate positive $\RatUp$ radius rows $R$ used by the finite fold. The exposure is public only through the compact-net source rows, the pointwise-modulus rows $M$, and the selected fold rows $F,D$ of \autoref{def:compact-net-modulus-selector-root-readiness}.
\end{theorem}
\begin{proof}
Read the root-ready tuple through \autoref{def:compact-net-modulus-selector-carrier} and \autoref{def:compact-net-modulus-selector-root-readiness}. The compact part of the packet is exactly $X,\mathcal{P},C,R$, with $\mathcal{P}$ named as the nonempty finite probe spine and $C$ naming the coverage rows over the source metric.

Use \autoref{thm:compact-net-modulus-selector-namecert-obligations}. Its compact-net exactness clause keeps $X,\mathcal{P},C,R$ attached to the local $\NameCert$ row, while its pointwise-modulus clause ties each row of $M$ to the same centers and tolerance history $E$.

Finally apply \autoref{thm:compact-net-modulus-selector-fold-soundness}. The selected precision row $D$ is read through the finite fold $F$ over the same probe spine and radius ledger, so the downstream consumer sees finite compact-net exposure rather than an ambient compactness principle.
\end{proof}

\begin{theorem}[Compact net modulus selector totally bounded handoff]
\label{thm:compact-net-modulus-selector-totallybounded-handoff}
Every downstream $\TotallyBoundedUp$ or $\UniformModulusUp$ consumer of a root-ready $\CompactNetModulusSelectorUp$ packet receives the compact finite-net rows only through the displayed fold row $F$ and selected precision row $D$. The handoff preserves the source rows $X,\mathcal{P},C$, the subordinate radius rows $R$, the pointwise-modulus rows $M$, and the routes $H,Q,P,N$, but it does not supply any separate compactness witness or external modulus function.
\end{theorem}
\begin{proof}
Start with the root obligation triad, \autoref{thm:compact-net-modulus-selector-root-obligation-triad}. It identifies the public surface as finite-net input, pointwise-radius input, and metric-selector output on the same carrier.

Next use \autoref{thm:compact-net-modulus-selector-finite-net-budget-route} and \autoref{thm:compact-net-modulus-selector-primitive-scope-closure}. These theorems route every modulus read through the compact, continuous, metric, rational, finite-fold, transport, continuation, provenance, and local naming rows displayed by the selector.

The sibling chapters supply the source interfaces: \autoref{ch:concrete-instances-compact-namecert} supplies compact finite-net rows, \autoref{ch:concrete-instances-continuous-namecert} supplies pointwise-modulus rows, \autoref{ch:concrete-instances-metric-namecert} supplies metric reads, \autoref{ch:concrete-instances-rat-namecert} supplies positive rational order rows, \autoref{ch:concrete-instances-finitenetminimumfold-namecert} supplies the finite fold, and \autoref{ch:concrete-instances-uniformmodulus-namecert} reads the selected precision boundary. The selector hands them forward only as $F,D$ together with the displayed route rows.
\end{proof}

\begin{theorem}[Compact net modulus selector consumer non-escape]
\label{thm:compact-net-modulus-selector-consumer-nonescape}
No downstream consumer of a root-ready $\CompactNetModulusSelectorUp$ packet can read open-cover compactness, a host minimum, a choice-selected center, quotient point equality, sequential compactness, or an external modulus function. Every consumer read factors through
$$
X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N
$$
as displayed in \autoref{def:compact-net-modulus-selector-root-readiness}.
\end{theorem}
\begin{proof}
Project the packet through \autoref{def:compact-net-modulus-selector-root-readiness}. Its public coordinates are the compact-net rows, pointwise-radius rows, finite fold, selected precision, transport rows, continuation routes, provenance, and local name.

Apply \autoref{thm:compact-net-modulus-selector-nonescape} and \autoref{thm:compact-net-modulus-selector-metric-consumer-boundary}. They already forbid consumer reads outside the displayed selector packet and identify the delivered boundary as a finite metric selector packet.

Finally use \autoref{thm:compact-net-modulus-selector-selected-precision-exactness} and \autoref{thm:compact-net-modulus-selector-primitive-scope-closure}. The selected precision is determined by the visible finite-net, radius, pointwise-modulus, fold, transport, route, provenance, and naming rows, leaving no coordinate for open-cover compactness, host minima, choice-selected centers, quotient point equality, sequential compactness, or external modulus functions.
\end{proof}

\begin{theorem}[Compact net modulus selector cover-radius synchronization]
\label{thm:compact-net-modulus-selector-cover-radius-synchronization}
For every accepted root-ready $\CompactNetModulusSelectorUp$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the compact cover rows $C$ and the positive $\RatUp$ radius rows $R$ are synchronized over the same finite probe spine $\mathcal{P}$. A cover read through $C$ cannot be consumed without the corresponding positive radius ledger $R$, and a radius read through $R$ cannot be consumed without the compact-net cover rows $C$ over the source metric row $X$.
\end{theorem}
\begin{proof}
Project $S$ through \autoref{def:compact-net-modulus-selector-root-readiness}. The displayed carrier stores $X,\mathcal{P},C,R$ as the compact finite-net input and makes $R$ the subordinate positive-radius ledger attached to that same probe spine.

Use \autoref{thm:compact-net-modulus-selector-finite-net-exposure}. It exposes the compact coverage rows and the positive radius rows together, with no separate coordinate for a detached cover row or a detached radius row.

Finally apply \autoref{thm:compact-net-modulus-selector-consumer-nonescape}. Since every downstream read factors through the displayed tuple, a consumer cannot separate $C$ from $R$ while remaining inside the accepted selector surface.
\end{proof}

\begin{theorem}[Compact net modulus selector fold-output positivity]
\label{thm:compact-net-modulus-selector-fold-output-positivity}
For every accepted root-ready $\CompactNetModulusSelectorUp$ packet
$$
S=(X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N),
$$
the fold output row $D$ is a positive precision row only through the positive $\RatUp$ radius ledger $R$, the pointwise-modulus rows $M$, and the finite lower-bound fold row $F$. No consumer may treat $D$ as a host minimum, a nonpositive bound, or a choice-selected external modulus value.
\end{theorem}
\begin{proof}
Read $D$ through \autoref{thm:compact-net-modulus-selector-fold-soundness}. The finite fold row $F$ computes the selected lower-bound precision from the positive radius and pointwise-modulus rows already present in the carrier.

Use \autoref{thm:compact-net-modulus-selector-selected-precision-exactness}. It fixes the precision row by the visible compact-net, radius, pointwise-modulus, fold, transport, route, provenance, and naming rows, so positivity is inherited from the $\RatUp$ radius ledger and the admitted fold route.

\autoref{thm:compact-net-modulus-selector-consumer-nonescape} excludes host minima, choice-selected centers, quotient point equality, and external modulus functions. Thus the only public interpretation of $D$ is the positive fold output carried by $R,M,F$ inside the displayed packet.
\end{proof}

\begin{theorem}[Compact net modulus selector request-to-precision factorization]
\label{thm:compact-net-modulus-selector-request-to-precision-factorization}
Every tolerance request $E$ accepted by a root-ready $\CompactNetModulusSelectorUp$ packet factors to the selected precision row $D$ through
$$
X,Y,E,\mathcal{P},C,R,M,F,D,H,Q,P,N.
$$
The handoff first reads compact coverage through $X,\mathcal{P},C$, then positive subordinate radii through $R$, then pointwise-modulus rows through $M$, then the finite fold output through $F,D$, and finally the transport, route, provenance, and local certificate rows $H,Q,P,N$.
\end{theorem}
\begin{proof}
Begin with \autoref{def:compact-net-modulus-selector-root-readiness}. The tolerance row $E$ is displayed with the source and target metric rows, the compact finite-net input, the pointwise-modulus rows, and the selected fold output.

Apply \autoref{thm:compact-net-modulus-selector-cover-radius-synchronization}. It forces every compact cover read to carry the matching positive radius ledger, so the request cannot bypass $X,\mathcal{P},C,R$.

Next apply \autoref{thm:compact-net-modulus-selector-fold-output-positivity}. The fold output $D$ is admitted only through $R,M,F$, and therefore the tolerance request reaches a precision row only through the finite selector fold.

Finally use \autoref{thm:compact-net-modulus-selector-consumer-nonescape}. The displayed transport, route, provenance, and local naming rows $H,Q,P,N$ are the only remaining public coordinates, so the request-to-precision handoff factors through exactly the root-ready carrier.
\end{proof}

\begin{theorem}[Compact net modulus selector fold-consumer coherence]
\label{thm:compact-net-modulus-selector-fold-consumer-coherence}
Every fold consumer of a root-ready $\CompactNetModulusSelectorUp$ packet that preserves the selected precision row $D$ also preserves the same $\mathsf{ProbeBundle}$ spine $\mathcal{P}$ and positive radius ledger $R$. Consequently the fold handoff cannot be reinterpreted as a host minimum, quotient center equality, or external modulus function.
\end{theorem}
\begin{proof}
Project the consumer read through \autoref{def:compact-net-modulus-selector-carrier}. The only fold data in the carrier are the finite fold row $F$, the selected precision row $D$, the bundled centers $\mathcal{P}$, and the radius ledger $R$.

Now use \autoref{def:compact-net-modulus-selector-root-readiness} and \autoref{thm:compact-net-modulus-selector-finite-net-exposure}. They identify $D$ as the fold-selected precision attached to the same finite probe spine and subordinate positive radius rows.

Apply \autoref{thm:compact-net-modulus-selector-totallybounded-handoff}. Any consumer preserving $D$ along the finite fold route receives the compact finite-net rows through $F,D$ and therefore keeps $\mathcal{P}$ and $R$ in the same public ledger.

\autoref{thm:compact-net-modulus-selector-consumer-nonescape} excludes every alternate read of a host minimum, quotient center equality, and external modulus function. The preserved selected precision is therefore coherent only with the original probe bundle and radius ledger.
\end{proof}

\input{parts/concrete_instances/5703a_compactnetmodulusselector_uniform_modulus_entry_exhaustion}

\falsifiablePrediction{Removing the selected lower-bound row breaks the uniform-modulus handoff while leaving compact-net coverage and pointwise-modulus rows readable.}

\independenceWitness{Compare compact, continuous, metric, finite-net-minimum-fold, and uniform-modulus siblings: none is bijective because this carrier alone stores the compact-net input, pointwise-modulus radii, selected lower-bound fold row, and tolerance-only handoff together.}

\closureat{CompactNetModulusSelectorUp}{seedStr}
\closureat{CompactNetModulusSelectorUp}{obligationStr}[BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorTasteGate\_single\_carrier\_alignment]
\closureat{CompactNetModulusSelectorUp}{scopedStr}[BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\CompactNetModulusSelectorUp}
  \constructivestory{A $\CompactNetModulusSelectorUp$ packet is generated from a compact metric finite-net row, a target metric row, a positive tolerance history, a nonempty $\mathsf{ProbeBundle}$ of centers, positive subordinate radius rows, pointwise-modulus rows at the bundled centers, a finite lower-bound fold, selected precision, displayed $\hsame$ and $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \leanchecked{BEDC.Derived.CompactNetModulusSelectorUp.taste\_gate}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:compact-net-modulus-selector-carrier}, \autoref{thm:compact-net-modulus-selector-namecert-obligations}, \autoref{thm:compact-net-modulus-selector-cover-radius-synchronization}, \autoref{thm:compact-net-modulus-selector-fold-output-positivity}, \autoref{thm:compact-net-modulus-selector-request-to-precision-factorization}, \autoref{thm:compact-net-modulus-selector-fold-soundness}, \autoref{thm:compact-net-modulus-selector-nonescape}, and \autoref{thm:compact-net-modulus-selector-independence-boundary} bind the finite compact-net selector packet, its local NameCert obligations, cover-radius synchronization, fold-output positivity, request-to-precision factorization, fold soundness, non-escape boundary, and sibling independence boundary.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.CompactNetModulusSelectorUp.CompactNetModulusSelectorTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close bridge checking, open-cover compactness, sequential compactness, a host minimum, a choice-selected center, quotient point equality, or an external modulus function for $\CompactNetModulusSelectorUp$.}
  \upgradepath{Public closure requires a public-object surface for the compact-net selector beyond the scoped finite selector carrier.}
\end{closurestatus}
