\chapter{A Concrete Naming Certificate for $\TailBudgetCoherenceUp$}
\label{ch:concrete-instances-tail-budget-coherence-namecert}
\origin{ai-composite}

The $\TailBudgetCoherenceUp$ packet is the composite Real and Completion surface joining the finite tail-budget route of \autoref{ch:concrete-instances-regular-cauchy-tail-budget-namecert}, the shared threshold route of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}, the agreement-seal route of \autoref{ch:concrete-instances-realtailagreementseal-namecert}, and the diagonal-completion route named in \autoref{ch:visions-real-completeness}. It is not an atomic carrier: its atomicity witness is intentionally replaced by a composite-dependency explanation over existing sibling packets. The later Lean TasteGate work must still provide $\mathsf{Nontrivial}\ \TailBudgetCoherenceUp$ and $\mathsf{FieldFaithful}\ \TailBudgetCoherenceUp$ instances for the displayed composite carrier.

\begin{definition}[Tail budget coherence carrier]
\label{def:tail-budget-coherence-carrier}
A $\TailBudgetCoherenceUp$ carrier is a finite $\BHist$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\RegularCauchyTailMeetUp$ shared-threshold row used by the diagonal tail route;
\item $O$ is the $\RealObservationBudgetUp$ observation-budget row that bounds the Real-facing finite reads;
\item $S$ is the $\RegularCauchySelectorBudgetUp$ selector-budget row that supplies the diagonal member requests;
\item $A$ is the $\RealTailAgreementSealUp$ agreement-seal row tying the tail route to the Real-facing agreement surface;
\item $L$ is the $\CauchyLimitSealUp$ limit-seal row reached only after the threshold, observation budget, selector budget, and agreement seal have been displayed;
\item $W$ is the finite $\StreamNameUp$ window ledger served by the observation and selector budgets;
\item $R$ is the $\RegSeqRatUp$ readback row attached to those windows;
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger read before the regular-rational handoff and seal rows;
\item $H$ records componentwise $\hsame$ transports for the threshold, observation budget, selector budget, agreement seal, limit seal, windows, readback, tolerance ledger, route, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ routes from the tail threshold to the budget rows, from budgets to finite windows, from windows to dyadic tolerance and regular readback rows, and from the readback to the agreement and limit seals;
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyTailMeetUp$, $\RealObservationBudgetUp$, $\RegularCauchySelectorBudgetUp$, $\RealTailAgreementSealUp$, $\CauchyLimitSealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\TailBudgetCoherenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. The carrier contains no quotient stream equality, no selected host limit, no host real equality, and no ambient completeness principle.
\end{definition}
\leandef{BEDC.Derived.TailBudgetCoherenceUp.TailBudgetCoherenceUp}

\begin{theorem}[Tail budget coherence NameCert obligations]
\label{thm:tail-budget-coherence-namecert-obligations}
For the carrier of \autoref{def:tail-budget-coherence-carrier}, the local $\NameCert_{\TailBudgetCoherenceUp}$ surface consists exactly of carrier admission for $T=(M,O,S,A,L,W,R,D,H,C,P,N)$, TailMeet threshold exposure through $M$, observation-budget exposure through $O$, selector-budget exposure through $S$, agreement-seal exposure through $A$, limit-seal exposure through $L$, finite window service through $W$, regular readback through $R$, dyadic tolerance accounting through $D$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.TailBudgetCoherenceUp.TailBudgetCoherenceCarrier\_namecert\_obligations}
\leanchecked{BEDC.Derived.TailBudgetCoherenceUp.TailBudgetCoherenceTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the displayed packet. Its coordinates are exactly $M,O,S,A,L,W,R,D,H,C,P,N$, so carrier admission and local naming cannot introduce a second tail threshold, budget, readback, agreement seal, or limit seal.

Read the route rows in dependency order. The threshold row $M$ fixes the shared tail boundary; $O$ and $S$ bound the observation and selector requests; $W,D,R$ display the finite windows, tolerance ledger, and regular-rational readback available after those budget rows.

The seal rows are then read through the same route. The agreement row $A$ and limit row $L$ are attached to the displayed readback surface, while $H,C,P,N$ transport, replay, package, and name only that finite packet.

Thus the NameCert surface is composite rather than atomic. It packages the displayed sibling rows from the tail-meet, observation-budget, selector-budget, agreement-seal, limit-seal, stream-window, readback, and dyadic-ledger chapters, and it exports no quotient streams, host real equality, selected limits, or ambient completeness.
\end{proof}

\begin{theorem}[Tail budget coherence real-completion handoff]
\label{thm:tail-budget-coherence-real-completion-handoff}
Every Real and Completion consumer that cites an accepted $\TailBudgetCoherenceUp$ packet must read the completion-facing $\RealUp$ or $\CauchyLimitSealUp$ surface through the displayed route
$$
M,O,S,W,D,R,A,L,H,C,P,N.
$$
In particular, the route realizes the Real completeness handoff of \autoref{ch:visions-real-completeness} as one finite threshold, observation-budget, selector-budget, agreement-seal, and limit-seal surface over the sibling packets of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}, \autoref{ch:concrete-instances-realtailagreementseal-namecert}, and \autoref{ch:concrete-instances-regular-cauchy-tail-budget-namecert}.
\end{theorem}
\begin{proof}
Start from the accepted carrier and project the threshold, budget, window, readback, and seal rows. The TailMeet row $M$ supplies the shared tail boundary, while $O$ and $S$ supply the two finite budget gates that service observation and selector requests.

Use the displayed window route next. The $\StreamNameUp$ row $W$, $\DyadicRatCoreUp$ tolerance ledger $D$, and $\RegSeqRatUp$ readback row $R$ are the only finite readback coordinates available before a seal-facing consumer reaches $A$ or $L$.

Now apply the sibling routes. The tail-budget packet of \autoref{ch:concrete-instances-regular-cauchy-tail-budget-namecert} supplies the budget-row source, the TailMeet sibling supplies the threshold source, and the RealTailAgreementSeal sibling supplies the agreement-seal source. The $\CauchyLimitSealUp$ row is read only after those rows have been displayed.

The structural rows $H,C,P,N$ carry the same composite packet to downstream Real and Completion consumers. Since the packet has no coordinate for quotient stream equality, selected host limits, host real equality, or ambient completeness, the handoff is exactly the finite BEDC-visible route stated above.
\end{proof}

\begin{theorem}[Tail budget coherence threshold-budget exposure]
\label{thm:tail-budget-coherence-threshold-budget-exposure}
For any accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
the TailMeet threshold row $M$, observation-budget row $O$, and selector-budget row $S$ are exposed before any finite window row $W$, dyadic tolerance row $D$, regular readback row $R$, agreement-seal row $A$, or limit-seal row $L$ is consumed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:tail-budget-coherence-carrier}. The first three budget-facing coordinates of the accepted packet are $M,O,S$, and the displayed carrier order places $W,R,D,A,L$ only after those rows have been named.

Apply \autoref{thm:tail-budget-coherence-namecert-obligations}. Its NameCert surface exposes TailMeet threshold, observation budget, and selector budget as separate rows before the finite window service, regular readback, dyadic tolerance accounting, agreement-seal exposure, and limit-seal exposure rows are read.

The structural rows $H,C,P,N$ transport, replay, package, and name the same packet. They do not supply an alternate window, tolerance ledger, readback route, agreement seal, or limit seal outside the exposed threshold and budget rows.
\end{proof}

\begin{theorem}[Tail budget coherence window-readback exactness]
\label{thm:tail-budget-coherence-window-readback-exactness}
For any accepted $\TailBudgetCoherenceUp$ packet $T=(M,O,S,A,L,W,R,D,H,C,P,N)$, the rows $W,D,R$ form the unique finite window, dyadic tolerance, and $\RegSeqRatUp$ readback route available under the displayed threshold and budget rows $M,O,S$.
\end{theorem}
\begin{proof}
Use \autoref{thm:tail-budget-coherence-threshold-budget-exposure} to fix $M,O,S$ as the exposed threshold and budget rows before any readback-facing coordinate is consumed.

Now apply \autoref{thm:tail-budget-coherence-namecert-obligations}. The accepted NameCert surface lists exactly one finite window service row $W$, one dyadic tolerance accounting row $D$, and one regular readback row $R$ in the displayed packet.

Because the classifier compares accepted packets only through the displayed rows of \autoref{def:tail-budget-coherence-carrier}, there is no second finite window, tolerance ledger, or readback coordinate for a Real or Completion consumer to select. Thus $W,D,R$ are the exact readback route under $M,O,S$.
\end{proof}

\begin{theorem}[Tail budget coherence seal non-escape]
\label{thm:tail-budget-coherence-seal-nonescape}
Every Real or Completion consumer of an accepted $\TailBudgetCoherenceUp$ packet reaches the agreement-seal row $A$ and limit-seal row $L$ only after the rows $M,O,S,W,D,R$ have been displayed, and receives no quotient stream equality, host real equality, selected host limit, countable-choice selector, or ambient completeness principle from the packet.
\end{theorem}
\begin{proof}
Start with \autoref{thm:tail-budget-coherence-window-readback-exactness}. It identifies $W,D,R$ as the exact finite readback route available under the already exposed threshold and budget rows $M,O,S$.

Apply \autoref{thm:tail-budget-coherence-real-completion-handoff}. Any Real or Completion consumer must read the handoff through the displayed route $M,O,S,W,D,R,A,L,H,C,P,N$, so the agreement seal $A$ and limit seal $L$ are reached only after the finite threshold, budget, window, tolerance, and readback rows.

Finally inspect the carrier definition. It contains no coordinate for quotient stream equality, host real equality, selected host limit, countable-choice selector, or ambient completeness, and the NameCert obligations package only the displayed finite rows.
\end{proof}

\begin{theorem}[Tail budget coherence Real-completion budget route refinement]
\label{thm:tail-budget-coherence-real-completion-budget-route-refinement}
Every Real or Completion consumer of an accepted $\TailBudgetCoherenceUp$ packet factors through the ordered finite route
$$
M,O,S,W,D,R,A,L,H,C,P,N.
$$
The threshold row $M$, observation-budget row $O$, and selector-budget row $S$ are exposed before any finite window, readback, or seal row is consumed; $W,D,R$ are the unique finite $\StreamNameUp$--$\DyadicRatCoreUp$--$\RegSeqRatUp$ readback route; and $A,L$ are reachable only after that readback route has been displayed.

The refinement exports no quotient stream equality, host real equality, selected host limit, countable-choice selector, or ambient completeness principle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:tail-budget-coherence-threshold-budget-exposure}. It fixes $M,O,S$ as the exposed threshold, observation-budget, and selector-budget surface before a consumer reaches any window, readback, tolerance, agreement-seal, or limit-seal row.

Next apply \autoref{thm:tail-budget-coherence-window-readback-exactness}. Under those budget rows, the only readback route is the finite $W,D,R$ surface, read as the $\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance ledger, and $\RegSeqRatUp$ regular-rational readback.

Then use \autoref{thm:tail-budget-coherence-seal-nonescape}. It places $A,L$ after the displayed readback route and blocks every quotient stream equality, host real equality, selected host limit, countable-choice selector, and ambient completeness coordinate.

Finally apply \autoref{thm:tail-budget-coherence-real-completion-handoff}. The Real and Completion consumer therefore sees a single finite route $M,O,S,W,D,R,A,L,H,C,P,N$, with $H,C,P,N$ transporting, replaying, packaging, and naming the same packet rather than opening a second analytic surface.
\end{proof}

\begin{theorem}[Tail budget coherence obligation-closure package]
\label{thm:tail-budget-coherence-obligation-closure-package}
For an accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
the carrier of \autoref{def:tail-budget-coherence-carrier}, the NameCert obligations of \autoref{thm:tail-budget-coherence-namecert-obligations}, the Real-completion handoff of \autoref{thm:tail-budget-coherence-real-completion-handoff}, the threshold-budget exposure of \autoref{thm:tail-budget-coherence-threshold-budget-exposure}, the window-readback exactness of \autoref{thm:tail-budget-coherence-window-readback-exactness}, and the seal non-escape boundary of \autoref{thm:tail-budget-coherence-seal-nonescape} assemble the fieldwise $\obligationClosure$ surface for $\TailBudgetCoherenceUp$.

The rows remain separate carrier, NameCert, handoff, threshold-budget, finite-window, readback, tolerance-ledger, agreement-seal, and limit-seal obligations. The package exports no quotient stream, host real equality, selected limit, countable-choice selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the carrier definition to fix the displayed packet $T=(M,O,S,A,L,W,R,D,H,C,P,N)$ and its ambient BEDC rows. The classifier has access only to the listed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates and to the named sibling rows.

Invoke \autoref{thm:tail-budget-coherence-namecert-obligations} to bind the carrier admission, local naming row, componentwise transports, continuation replay, package provenance, threshold row, budget rows, window row, tolerance ledger, readback row, agreement seal, and limit seal.

Chain \autoref{thm:tail-budget-coherence-real-completion-handoff}, \autoref{thm:tail-budget-coherence-threshold-budget-exposure}, and \autoref{thm:tail-budget-coherence-window-readback-exactness}. These theorems route every Real or Completion consumer through the finite sequence $M,O,S,W,D,R,A,L,H,C,P,N$, expose $M,O,S$ before any readback-facing row, and identify $W,D,R$ as the exact finite readback route under those exposed threshold and budget rows.

Finally apply \autoref{thm:tail-budget-coherence-seal-nonescape}. The agreement seal and limit seal are reachable only through the displayed finite packet, and no quotient stream, host real equality, selected host limit, countable-choice selector, or ambient completeness coordinate is exported. The composite-dependency explanation therefore keeps the result as a finite Real-completion handoff package, not an atomic analytic object.
\end{proof}

\begin{theorem}[Tail budget coherence primitive scope]
\label{thm:tail-budget-coherence-primitive-scope}
For an accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
the primitive scope is exactly the sibling rows $\RegularCauchyTailMeetUp$, $\RealObservationBudgetUp$, $\RegularCauchySelectorBudgetUp$, $\RealTailAgreementSealUp$, $\CauchyLimitSealUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ together with the kernel rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ displayed in the packet.

Every Real-completion consumer route through $T$ first passes through those rows and cannot use quotient stream equality, host real equality, selected limits, countable-choice selectors, or ambient completeness outside the displayed finite packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:tail-budget-coherence-carrier}. This fixes the accepted packet as the displayed tuple $T=(M,O,S,A,L,W,R,D,H,C,P,N)$, with $M,O,S,A,L,W,R,D$ supplied by the eight named sibling rows and $H,C,P,N$ supplied by the local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface.

Use \autoref{thm:tail-budget-coherence-namecert-obligations} to bind carrier admission, componentwise transport, continuation replay, package provenance, and local naming to those displayed coordinates. Then apply \autoref{thm:tail-budget-coherence-real-completion-handoff} to force every Real-completion consumer route through the same packet rather than through a host equality or ambient limit object.

Now use \autoref{thm:tail-budget-coherence-threshold-budget-exposure} and \autoref{thm:tail-budget-coherence-window-readback-exactness}. They expose $M,O,S$ before any readback-facing coordinate and identify $W,D,R$ as the exact finite window, tolerance, and readback route available under that exposure.

Finally apply \autoref{thm:tail-budget-coherence-seal-nonescape}. The agreement seal $A$ and limit seal $L$ are reachable only after the displayed finite route, and no coordinate remains for quotient stream equality, host real equality, selected limits, countable-choice selectors, or ambient completeness. Hence the primitive scope is exhausted by the finite packet named in the theorem.
\end{proof}

\begin{theorem}[Tail budget coherence sibling-scope lock]
\label{thm:tail-budget-coherence-sibling-scope-lock}
For an accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
each displayed row is read only through the named sibling packets and BEDC kernel rows: $M$ through $\RegularCauchyTailMeetUp$, $O$ through $\RealObservationBudgetUp$, $S$ through $\RegularCauchySelectorBudgetUp$, $A$ through $\RealTailAgreementSealUp$, $L$ through $\CauchyLimitSealUp$, $W$ through $\StreamNameUp$, $R$ through $\RegSeqRatUp$, $D$ through $\DyadicRatCoreUp$, and $H,C,P,N$ through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:tail-budget-coherence-carrier}. The accepted tuple displays $M,O,S,A,L,W,R,D,H,C,P,N$ as separate coordinates, and the classifier compares accepted packets only through those coordinates.

Apply \autoref{thm:tail-budget-coherence-namecert-obligations} to bind each coordinate to its local obligation row. The threshold, observation-budget, selector-budget, agreement-seal, limit-seal, window, readback, and dyadic-tolerance rows are supplied by their named sibling packets, while $H,C,P,N$ supply only componentwise transport, continuation replay, provenance, and local naming.

Finally use \autoref{thm:tail-budget-coherence-primitive-scope}. It identifies the primitive surface as the eight sibling rows together with $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. There is no remaining coordinate from which a consumer could read an unlisted sibling packet or a host-level analytic primitive.
\end{proof}

\begin{theorem}[Tail budget coherence Real route scope]
\label{thm:tail-budget-coherence-real-route-scope}
Every $\RealUp$ or Completion consumer of an accepted $\TailBudgetCoherenceUp$ packet factors through
$$
M,O,S,W,D,R,A,L,H,C,P,N
$$
before reading an agreement seal or a limit seal. In particular, no Real-facing or Completion-facing consumer reaches $A$ or $L$ without first passing through the TailMeet threshold, observation budget, selector budget, finite window, dyadic tolerance ledger, and regular readback rows.
\end{theorem}
\begin{proof}
Start with \autoref{thm:tail-budget-coherence-real-completion-handoff}. It states the handoff route for every Real and Completion consumer as the displayed sequence $M,O,S,W,D,R,A,L,H,C,P,N$.

Use \autoref{thm:tail-budget-coherence-threshold-budget-exposure} to place $M,O,S$ before any readback-facing row is consumed. Then use \autoref{thm:tail-budget-coherence-window-readback-exactness} to identify $W,D,R$ as the exact finite window, tolerance, and readback route under that exposed threshold and budget surface.

The seal rows are now forced by \autoref{thm:tail-budget-coherence-seal-nonescape}. The agreement seal $A$ and limit seal $L$ are reachable only after $M,O,S,W,D,R$, and the structural rows $H,C,P,N$ transport and name the same finite packet rather than opening a second Real or Completion path.
\end{proof}

\begin{theorem}[Tail budget coherence no ambient completeness scope]
\label{thm:tail-budget-coherence-no-ambient-completeness-scope}
The scoped $\TailBudgetCoherenceUp$ route exports no quotient stream equality, no host real equality, no selected limit, no countable-choice selector, and no ambient completeness principle. Its public output is only the finite coherence route through $M,O,S,W,D,R,A,L,H,C,P,N$ and the sibling packets named in \autoref{thm:tail-budget-coherence-sibling-scope-lock}.
\end{theorem}
\begin{proof}
Inspect the carrier of \autoref{def:tail-budget-coherence-carrier}. The accepted packet contains rows for the threshold, budgets, finite windows, dyadic tolerance ledger, regular readback, agreement seal, limit seal, componentwise transport, continuation replay, provenance, and local naming, but it contains no coordinate for quotient equality, host equality, selected limits, choice selectors, or completeness.

Apply \autoref{thm:tail-budget-coherence-obligation-closure-package}. The obligation surface assembled there is fieldwise over the same finite rows and explicitly keeps the seal route separate from quotient stream equality, host real equality, selected limits, countable-choice selectors, and ambient completeness.

Combine this with \autoref{thm:tail-budget-coherence-sibling-scope-lock} and \autoref{thm:tail-budget-coherence-real-route-scope}. The first locks every row to the named sibling and kernel packets, and the second forces Real and Completion consumers through the finite route before any seal read. Therefore the scoped route exports no ambient completeness object beyond the displayed coherence packet.
\end{proof}

\begin{theorem}[Tail budget coherence public export boundary]
\label{thm:tail-budget-coherence-public-export-boundary}
The public export of an accepted $\TailBudgetCoherenceUp$ packet is exactly the finite route
$$
M,O,S,W,D,R,A,L,H,C,P,N
$$
through the sibling rows named by \autoref{thm:tail-budget-coherence-sibling-scope-lock}. Every $\RealUp$ or Completion consumer must pass through threshold-budget exposure, window-readback exactness, Real route scope, and no-ambient-completeness scope before it reads the agreement seal $A$ or limit seal $L$.

Consequently the public export contains no quotient stream, selected host limit, host real equality, countable-choice selector, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with the sibling-scope lock of \autoref{thm:tail-budget-coherence-sibling-scope-lock}. It ties $M,O,S,A,L,W,R,D$ to the named TailMeet, observation-budget, selector-budget, agreement-seal, limit-seal, StreamName, RegSeqRat, and DyadicRatCore sibling packets, and ties $H,C,P,N$ to the BEDC kernel rows.

Apply threshold-budget exposure from \autoref{thm:tail-budget-coherence-threshold-budget-exposure}. It places $M,O,S$ before any finite window, dyadic tolerance, regular readback, agreement-seal, or limit-seal coordinate can be consumed.

Next apply window-readback exactness from \autoref{thm:tail-budget-coherence-window-readback-exactness} and Real route scope from \autoref{thm:tail-budget-coherence-real-route-scope}. These identify $W,D,R$ as the exact readback route under $M,O,S$ and force every Real or Completion consumer through $M,O,S,W,D,R,A,L,H,C,P,N$ before seal access.

Finally use no-ambient-completeness scope from \autoref{thm:tail-budget-coherence-no-ambient-completeness-scope}. Since the accepted route exports no quotient stream equality, host real equality, selected limit, countable-choice selector, or ambient completeness principle, the finite route written above is the complete public boundary.
\end{proof}

\begin{theorem}[Tail budget coherence Real-seal window stability]
\label{thm:tail-budget-coherence-real-seal-window-stability}
For an accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
any $\RealUp$ or Completion consumer that reaches the agreement seal $A$ or the limit seal $L$ must preserve the same finite $\StreamNameUp$ window $W$, $\DyadicRatCoreUp$ tolerance ledger $D$, and $\RegSeqRatUp$ readback $R$ fixed under the threshold-budget rows $M,O,S$.

Componentwise $\hsame$ transport may rename these rows, but it may not replace them by a second window, a host limit, a quotient stream equality, or an ambient completeness route.
\end{theorem}
\begin{proof}
First expose the budget spine. By \autoref{thm:tail-budget-coherence-threshold-budget-exposure}, every readback-facing route through $T$ presents $M,O,S$ before the finite window, dyadic tolerance, regular readback, agreement seal, or limit seal is consumed.

Next fix the finite readback rows. Apply \autoref{thm:tail-budget-coherence-window-readback-exactness}; it identifies $W,D,R$ as the exact $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ route under the displayed threshold and budget rows, so a seal consumer cannot substitute a second readback surface.

Now place the seal consumer on the public route. The Real route scope of \autoref{thm:tail-budget-coherence-real-route-scope} and the public export boundary of \autoref{thm:tail-budget-coherence-public-export-boundary} force any $\RealUp$ or Completion read of $A$ or $L$ through $M,O,S,W,D,R,A,L,H,C,P,N$.

Finally use seal non-escape from \autoref{thm:tail-budget-coherence-seal-nonescape}. Since the accepted packet exports neither host limits, quotient stream equality, nor ambient completeness, componentwise $\hsame$ transport can only rename the displayed rows and cannot replace the finite window-readback triple.
\end{proof}

\begin{theorem}[Tail budget coherence bridge interface]
\label{thm:tail-budget-coherence-bridge-interface}
For an accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
the composite sibling route from $\RegularCauchyTailMeetUp$, $\RealObservationBudgetUp$, $\RegularCauchySelectorBudgetUp$, $\RealTailAgreementSealUp$, $\CauchyLimitSealUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ bridges to the public Real-and-Completion consumer interface exactly through the finite surface
$$
M,O,S,W,D,R,A,L,H,C,P,N.
$$
The forward direction is the public export boundary of \autoref{thm:tail-budget-coherence-public-export-boundary}. The reverse projection is the sibling-scope lock of \autoref{thm:tail-budget-coherence-sibling-scope-lock} together with the primitive scope of \autoref{thm:tail-budget-coherence-primitive-scope}.

Thus the bridge carries only the displayed threshold, observation-budget, selector-budget, agreement-seal, limit-seal, window, readback, dyadic-tolerance, transport, continuation, provenance, and local naming rows. It carries no quotient stream equality, no host real equality, no selected limit, no countable-choice selector, and no ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.TailBudgetCoherenceUp.TailBudgetCoherenceUp\_StdBridge}
\begin{proof}
For the forward direction, apply \autoref{thm:tail-budget-coherence-public-export-boundary}. It identifies the public Real-and-Completion export as the finite route $M,O,S,W,D,R,A,L,H,C,P,N$ through the sibling rows already locked by the accepted packet.

For the reverse projection, start with \autoref{thm:tail-budget-coherence-sibling-scope-lock}. It reads each coordinate of $T$ only through the named sibling packets and through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Then apply \autoref{thm:tail-budget-coherence-primitive-scope} to exhaust the primitive surface by those same sibling and kernel rows.

The consumer side is controlled by \autoref{thm:tail-budget-coherence-real-route-scope}. Every Real or Completion consumer factors through $M,O,S,W,D,R,A,L,H,C,P,N$ before reading an agreement seal or a limit seal.

Finally apply \autoref{thm:tail-budget-coherence-no-ambient-completeness-scope}. Since the route exports no quotient stream equality, host real equality, selected limit, countable-choice selector, or ambient completeness principle, the two projections describe a bridge only for the finite public surface and not for any stronger analytic equality or completeness object.
\end{proof}

\begin{theorem}[Tail budget coherence finite-route determinacy]
\label{thm:tail-budget-coherence-finite-route-determinacy}
For an accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
any two $\RealUp$ or $\CompletionUp$ consumers that read the same TailMeet threshold, observation budget, selector budget, finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, agreement seal, limit seal, and structural rows determine the same public finite route
$$
M,O,S,W,D,R,A,L,H,C,P,N.
$$
No second window, quotient stream equality, selected limit, host real equality, countable-choice selector, or ambient completeness row can distinguish the two routes.
\end{theorem}
\begin{proof}
Begin with threshold-budget exposure from \autoref{thm:tail-budget-coherence-threshold-budget-exposure}. It fixes the TailMeet threshold, observation-budget, and selector-budget rows before any consumer can read the finite window or either seal.

Next apply window-readback exactness from \autoref{thm:tail-budget-coherence-window-readback-exactness}. The shared window, dyadic ledger, and regular readback are exactly $W,D,R$, so two consumers with the same displayed readback data cannot separate into two finite-window routes.

The Real route scope and public export boundary, \autoref{thm:tail-budget-coherence-real-route-scope} and \autoref{thm:tail-budget-coherence-public-export-boundary}, place both consumers on $M,O,S,W,D,R,A,L,H,C,P,N$ before either Real or Completion endpoint sees the agreement or limit seal.

Finally use the sibling-scope lock, bridge interface, and no-ambient-completeness scope of \autoref{thm:tail-budget-coherence-sibling-scope-lock}, \autoref{thm:tail-budget-coherence-bridge-interface}, and \autoref{thm:tail-budget-coherence-no-ambient-completeness-scope}. These exhaust the structural rows and exclude quotient stream equality, selected limits, host real equality, choice selectors, and ambient completeness rows, so the two reads are the same public finite route.
\end{proof}

\begin{theorem}[Tail budget coherence synchronizer comparison]
\label{thm:tail-budget-coherence-synchronizer-comparison}
For an accepted $\TailBudgetCoherenceUp$ packet
$$
T=(M,O,S,A,L,W,R,D,H,C,P,N),
$$
the $\RealWindowSynchronizerUp$ packet on the same consumer route is the window-to-seal projection of $T$: it reads the shared StreamName window $W$, RegSeqRat readback $R$, threshold-budget spine $M,O,S$, CauchyLimitSeal row $L$, transport, continuation, provenance, and local naming rows, and then exposes only the corresponding Real-window seal surface. The projection discards no hidden completion coordinate because $T$ carries none.
\end{theorem}
\begin{proof}
Begin with the TailBudgetCoherence bridge interface of \autoref{thm:tail-budget-coherence-bridge-interface}. It presents the public consumer route as $M,O,S,W,D,R,A,L,H,C,P,N$.

Compare this route with the RealWindowSynchronizer carrier and obligation package from \autoref{def:real-window-synchronizer-carrier} and \autoref{thm:real-window-synchronizer-obligation-closure-package}. The synchronizer reads the same window $W$, readback $R$, threshold spine, limit seal $L$, transport, continuation, provenance, and naming rows when it exposes its Real-window seal.

The TailBudgetCoherence no-ambient-completeness scope ensures that the larger packet has no quotient stream, selected limit, host real equality, or ambient completeness coordinate to hide from the projection. Hence the synchronizer packet is exactly the window-to-seal projection of the public tail-budget packet.
\end{proof}

\begin{theorem}[Tail budget coherence shared-window refinement]
\label{thm:tail-budget-coherence-shared-window-refinement}
In an accepted $\TailBudgetCoherenceUp$ packet $T=(M,O,S,A,L,W,R,D,H,C,P,N)$, the shared window and refinement rows $W,D,R$ agree under the threshold-budget rows $M,O,S$. Any RealWindowSynchronizer consumer that reads $W$ and $R$ through this packet also reads the dyadic tolerance ledger $D$ as the displayed refinement witness for the same shared threshold-budget spine.
\end{theorem}
\begin{proof}
Apply threshold-budget exposure from \autoref{thm:tail-budget-coherence-threshold-budget-exposure}. It places the TailMeet threshold, observation budget, and selector budget rows $M,O,S$ before the finite window, dyadic tolerance ledger, and regular readback are consumed.

Then use window-readback exactness from \autoref{thm:tail-budget-coherence-window-readback-exactness}. It identifies $W,D,R$ as the exact StreamName, DyadicRatCore, and RegSeqRat route under those same threshold-budget rows.

A RealWindowSynchronizer consumer reading through the TailBudgetCoherence packet therefore cannot choose a second window or readback row. It receives $W$ and $R$ together with $D$ as the refinement witness for the shared $M,O,S$ spine.
\end{proof}

\begin{theorem}[Tail budget coherence Real-window consumer route]
\label{thm:tail-budget-coherence-real-window-consumer-route}
Any $\RealWindowSynchronizerUp$ consumer that uses an accepted $\TailBudgetCoherenceUp$ packet follows the public route
$$
M,O,S,W,D,R,A,L,H,C,P,N.
$$
The route carries the TailMeet threshold, observation budget, selector budget, shared StreamName window, DyadicRatCore tolerance ledger, RegSeqRat readback, agreement seal, CauchyLimitSeal row, transport, continuation, provenance, and local naming rows, and it exports no quotient stream or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Use the synchronizer comparison of \autoref{thm:tail-budget-coherence-synchronizer-comparison} to place the RealWindowSynchronizer consumer as a projection of the TailBudgetCoherence public packet.

Apply shared-window refinement from \autoref{thm:tail-budget-coherence-shared-window-refinement}. The window, dyadic ledger, and readback rows are the displayed $W,D,R$ rows under the same threshold-budget spine $M,O,S$.

Finally use the public export boundary and no-ambient-completeness scope of \autoref{thm:tail-budget-coherence-public-export-boundary} and \autoref{thm:tail-budget-coherence-no-ambient-completeness-scope}. The consumer route is exactly $M,O,S,W,D,R,A,L,H,C,P,N$, with no quotient stream or ambient completeness coordinate.
\end{proof}

\falsifiablePrediction{If a completion-facing consumer reads the limit seal without a displayed TailMeet threshold, observation budget, selector budget, finite window ledger, dyadic tolerance ledger, regular readback, and agreement-seal row, that read is not accepted by $\TailBudgetCoherenceUp$.}

The composite-dependency explanation is the replacement for an atomic independence witness. The carrier is deliberately assembled from existing $\RegularCauchyTailMeetUp$, $\RealObservationBudgetUp$, $\RegularCauchySelectorBudgetUp$, $\RealTailAgreementSealUp$, $\CauchyLimitSealUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ rows; its content is the coherence of those rows at the Real-completion handoff, not a new primitive analytic object.

\closureat{TailBudgetCoherenceUp}{scopedStr}
\closureat{TailBudgetCoherenceUp}{publicStr}
\closureat{TailBudgetCoherenceUp}{bridgedStr}
\closureat{TailBudgetCoherenceUp}{matureStr}

\begin{closurestatus}{\TailBudgetCoherenceUp}
  \constructivestory{A $\TailBudgetCoherenceUp$ packet is generated from TailMeet threshold, Real observation-budget, regular Cauchy selector-budget, RealTailAgreementSeal, CauchyLimitSeal, finite StreamName window, RegSeqRat readback, DyadicRatCore tolerance, componentwise transport, displayed continuation, provenance, and local NameCert rows.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:tail-budget-coherence-carrier}, \autoref{thm:tail-budget-coherence-namecert-obligations}, \autoref{thm:tail-budget-coherence-real-completion-handoff}, \autoref{thm:tail-budget-coherence-threshold-budget-exposure}, \autoref{thm:tail-budget-coherence-window-readback-exactness}, \autoref{thm:tail-budget-coherence-seal-nonescape}, \autoref{thm:tail-budget-coherence-obligation-closure-package}, \autoref{thm:tail-budget-coherence-primitive-scope}, \autoref{thm:tail-budget-coherence-public-export-boundary}, \autoref{thm:tail-budget-coherence-real-seal-window-stability}, \autoref{thm:tail-budget-coherence-sibling-scope-lock}, \autoref{thm:tail-budget-coherence-real-route-scope}, \autoref{thm:tail-budget-coherence-no-ambient-completeness-scope}, and \autoref{thm:tail-budget-coherence-bridge-interface} give the mature treatment of the public export boundary, Real-seal window stability, bridge interface, sibling-scope lock, Real route scope, and no-ambient-completeness scope for the finite Real-completion tail-budget handoff.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.TailBudgetCoherenceUp.TailBudgetCoherenceTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not prove Real completeness, quotient equality of regular streams, selected-limit existence, host real equality, or bridge checking for $\TailBudgetCoherenceUp$.}
  \upgradepath{The theory axis is mature for the finite Real-completion tail-budget handoff; independent Lean verification or bridge checking remains on the verification axis.}
\end{closurestatus}
