\chapter{A Concrete Naming Certificate for $\FiniteTailFiberScheduleUp$}
\label{ch:concrete-instances-finite-tail-fiber-schedule-namecert}
\origin{ai}

The $\FiniteTailFiberScheduleUp$ packet realizes the finite tail route behind the Real-completeness target of \autoref{ch:visions-real-completeness}. It sits after the stream-name surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic readback core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the RealUp seal of \autoref{ch:concrete-instances-real-namecert}, and the shared tail-meet route of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}. The packet records one finite tail fiber, its schedule row, and its seal handoff without claiming quotient reals, ambient completeness, or an unrestricted diagonal theorem.

\begin{definition}[Finite tail-fiber schedule carrier]
\label{def:finite-tail-fiber-schedule-carrier}
A $\FiniteTailFiberScheduleUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,F,S,D,R,E,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $T$ is the displayed tail index at which the finite Real-completeness route is read;
\item $F$ is the finite fiber row over that tail index, recording the stream observations available at the selected tail;
\item $S$ is the schedule row that binds the tail index and finite fiber to the selected RealUp seal route;
\item $D$ is the dyadic radius ledger consumed by the finite tail readback;
\item $R$ is the $\RegSeqRatUp$ readback row used to interpret the scheduled fiber as regular rational data;
\item $E$ is the $\RealUp$ seal row reached by the scheduled tail-fiber route;
\item $H$ records componentwise $\hsame$ transport for the tail index, fiber row, schedule row, dyadic radius ledger, $\RegSeqRatUp$ readback, and $\RealUp$ seal;
\item $C$ records the displayed $\Cont$ routes for stream-name readback, dyadic-radius use, regular-rational readback, tail-meet comparison, and seal consumption;
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RegularCauchyTailMeetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and local naming rows;
\item $N$ is the local $\NameCert_{\FiniteTailFiberScheduleUp}$ row.
\end{enumerate}
The classifier compares two carriers only by the displayed rows $T,F,S,D,R,E,H,C,P,N$. It has no coordinate for quotient stream equality, an infinite tail oracle, a selected host limit, countable choice, or an ambient real-completeness theorem.
\end{definition}
\leanchecked{BEDC.Derived.FiniteTailFiberScheduleUp.FiniteTailFiberScheduleTasteGate\_single\_carrier\_alignment}

\begin{theorem}[FiniteTailFiberSchedule NameCert obligations]
\label{thm:finite-tail-fiber-schedule-namecert-obligations}
Every accepted $\FiniteTailFiberScheduleUp$ packet with carrier \autoref{def:finite-tail-fiber-schedule-carrier} carries the standard five local naming obligations:
\begin{enumerate}
\item carrier habitation: the tuple $Q=(T,F,S,D,R,E,H,C,P,N)$ is admitted as one finite $\BHist$ packet;
\item classifier transport: the componentwise $\hsame$ rows in $H$ and the displayed $\Cont$ routes in $C$ preserve the tail index, finite fiber, schedule, dyadic ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, package, and naming rows;
\item schedule-to-fiber exactness: every accepted schedule read passes through the displayed tail index $T$ and finite fiber row $F$ before it can cite a RealUp seal;
\item dyadic and regular readback exactness: every seal-facing radius and regular-rational read passes through the dyadic ledger $D$ and the $\RegSeqRatUp$ readback row $R$;
\item non-escape: accepted carriers export no quotient real, selected host limit, infinite tail oracle, countable-choice row, or ambient Real-completeness theorem.
\end{enumerate}
Thus the local $\NameCert_{\FiniteTailFiberScheduleUp}$ surface is exactly the finite schedule from a displayed tail fiber to a displayed $\RealUp$ seal.
\end{theorem}
\begin{proof}
Carrier habitation is the displayed finite tuple $Q=(T,F,S,D,R,E,H,C,P,N)$. Each coordinate is a visible history row or a finite route between such rows, so admission does not require an external stream space or a host real carrier.

For classifier transport, read the structural rows componentwise. The $\hsame$ data in $H$ preserve each displayed coordinate, and the $\Cont$ routes in $C$ replay the stream-name, dyadic-radius, regular-rational, tail-meet, and seal-consumption reads without introducing another tail object.

Schedule-to-fiber exactness follows from the shape of $S$. A schedule row is accepted only when it binds the displayed tail index $T$ to the finite fiber row $F$, and the seal row $E$ is reachable only along that same route.

Dyadic and regular readback exactness then projects $D$ and $R$. The radius information used at the scheduled tail is precisely the finite dyadic ledger, and the regular-rational data are precisely the displayed $\RegSeqRatUp$ readback for that fiber.

Non-escape is carrier inspection. Since no coordinate stores quotient equality, a host-selected limit, an infinite tail oracle, countable choice, or an ambient completeness theorem, every consumer of the packet must remain inside the displayed tail-fiber schedule and RealUp seal rows.
\end{proof}

\falsifiablePrediction{Any accepted finite tail-fiber schedule consumer reaches the RealUp seal only after the displayed tail index, finite fiber, dyadic radius, RegSeqRat readback, hsame, Cont, Pkg, and local NameCert rows are present.}

\independenceWitness{Compare StreamName, RegSeqRat, DyadicRatCore, RealUp, and RegularCauchyTailMeet: this packet is not bijective with any of them because it carries a schedule row binding one finite tail fiber to a RealUp seal; each sibling lacks at least the schedule-to-seal obligation or the tail-fiber ledger.}

The later Lean \texttt{TasteGate.lean} boundary for this carrier must provide \texttt{Nontrivial FiniteTailFiberScheduleUp} and \texttt{FieldFaithful FiniteTailFiberScheduleUp} instances with explicit witness pairs and field projections. The nontrivial witness separates a scheduled tail-fiber packet from a carrier with no seal route, while field faithfulness preserves the tail index, finite fiber, schedule row, dyadic ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, $\hsame$ transport, $\Cont$ routes, package provenance, and local naming row.

\closureat{FiniteTailFiberScheduleUp}{seedStr}

\begin{closurestatus}{\FiniteTailFiberScheduleUp}
  \constructivestory{A $\FiniteTailFiberScheduleUp$ packet is generated from a displayed tail index, finite fiber row, schedule row, dyadic radius ledger, RegSeqRat readback, RealUp seal, componentwise hsame transports, displayed Cont routes, Pkg provenance, and local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-tail-fiber-schedule-carrier} and \autoref{thm:finite-tail-fiber-schedule-namecert-obligations} bind the finite tail-fiber schedule and RealUp seal handoff route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, quotient reals, host real completeness, selected limits, countable choice, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, schedule-to-fiber exactness, dyadic and regular readback exactness, RealUp seal handoff, transport closure, and TasteGate nontriviality with field faithfulness.}
\end{closurestatus}

\begin{lemma}[FiniteTailFiberSchedule seal-route determinacy]
\label{lem:finite-tail-fiber-schedule-seal-route-determinacy}
Let
$$
Q=(T,F,S,D,R,E,H,C,P,N)
$$
and
$$
Q'=(T',F',S',D',R',E',H',C',P',N')
$$
be accepted $\FiniteTailFiberScheduleUp$ packets. Suppose the displayed non-seal rows agree componentwise through the packet classifier:
$$
T=T',\quad F=F',\quad S=S',\quad D=D',\quad R=R',\quad H=H',\quad C=C',\quad P=P',\quad N=N'.
$$
Then the $\RealUp$ seal rows $E$ and $E'$ are classified along the same finite tail-fiber route. More explicitly, any accepted read of $E$ and any accepted read of $E'$ both factor through the common route
$$
T,F,S,D,R,H,C,P,N,
$$
so the seal comparison has no independent coordinate from which to distinguish two RealUp seal routes under the same displayed tail index, finite fiber, schedule, dyadic ledger, RegSeqRat readback, transport, continuation, provenance, and local naming rows.
\end{lemma}
\begin{proof}
Project both packets to the carrier of \autoref{def:finite-tail-fiber-schedule-carrier}. The only row that can expose a RealUp seal is the seal coordinate attached to the same tuple as the displayed tail index, finite fiber, schedule row, dyadic ledger, RegSeqRat readback, componentwise transports, continuation routes, package provenance, and local name.

Apply the schedule-to-fiber obligation from \autoref{thm:finite-tail-fiber-schedule-namecert-obligations}. In each accepted packet, a seal-facing schedule read must first pass through the displayed tail index and finite fiber row. Since $T=T'$, $F=F'$, and $S=S'$, the two packets present one scheduled tail-fiber route before either seal row can be cited.

Apply the dyadic and regular readback obligation from the same theorem. A seal-facing radius read is the displayed dyadic ledger $D$, and the regular-rational read is the displayed $\RegSeqRatUp$ row $R$. Since $D=D'$ and $R=R'$, the readback portion of the two seal routes is the same finite ledger rather than two separate regular-rational sources.

The transport and continuation rows now identify the remaining route data. The common rows $H=H'$ and $C=C'$ replay the same componentwise $\hsame$ transport and the same displayed $\Cont$ route through the stream-name readback, dyadic-radius use, regular-rational readback, tail-meet comparison, and seal consumption. The common rows $P=P'$ and $N=N'$ attach the same package provenance and local naming surface to that replay.

Finally use non-escape from \autoref{thm:finite-tail-fiber-schedule-namecert-obligations}. The packet has no coordinate for a quotient real, selected host limit, infinite tail oracle, countable-choice row, ambient completeness theorem, or second seal selector. Therefore an alleged distinct seal route would need an unlisted coordinate, while every accepted seal read is already forced through the common finite route $T,F,S,D,R,H,C,P,N$. Hence $E$ and $E'$ classify together along that route.
\end{proof}
