\chapter{A Concrete Naming Certificate for $\SemigroupUp$}
\label{ch:concrete-instances-semigroup-namecert}

The semigroup interface $\SemigroupUp$ adds associativity to $\MagmaUp$ (\autoref{ch:concrete-instances-magma-namecert}). It sits between the magma layer and $\NameCert_{\MonoidUp}$ (\autoref{ch:concrete-instances-monoid-namecert}), exposing the closure law that distinguishes free semigroups from arbitrary binary structures.

\section{Carrier definition}
\label{sec:semigroup-carrier}

\begin{definition}[Concrete unary-history semigroup instance]
\label{def:concrete-unary-history-semigroup-instance}
The concrete unary-history semigroup instance reuses the magma carrier,
operation, and classifier from
\autoref{def:concrete-unary-history-magma-instance}. Thus the carrier is
$\mathsf{UnaryHistory}$, multiplication is
$\mathsf{mul}_U(h,k):=\mathsf{append}(h,k)$, the continuation witness is
$\Cont(h,k,\mathsf{append}(h,k))$, and endpoint comparison is the
carrier-aware relation
$$
R_U(h,k):=\mathsf{UnaryHistory}(h)\land\mathsf{UnaryHistory}(k)\land\hsame(h,k).
$$
\end{definition}

\begin{theorem}[Concrete unary-history semigroup laws]
\label{thm:concrete-unary-history-semigroup-laws}
The instance of \autoref{def:concrete-unary-history-semigroup-instance}
satisfies the magma closure and multiplication congruence laws of
\autoref{thm:concrete-unary-history-magma-laws}. In addition, for unary
histories $h,k,l:\mathsf{BHist}$,
$$
R_U(\mathsf{mul}_U(\mathsf{mul}_U(h,k),l),
\mathsf{mul}_U(h,\mathsf{mul}_U(k,l))).
$$
\end{theorem}
\begin{proof}
The closure and multiplication congruence clauses are the magma laws from
\autoref{thm:concrete-unary-history-magma-laws}, applied to the same carrier
$\mathsf{UnaryHistory}$, operation $\mathsf{append}$, and classifier $R_U$.

For associativity, first apply unary append closure to $h$ and $k$, and again
to $k$ and $l$. These witnesses place the intermediate products
$\mathsf{append}(h,k)$ and $\mathsf{append}(k,l)$ in the carrier, so the two
outer products are also unary by the same closure theorem.

The four continuation witnesses
$\Cont(h,k,\mathsf{append}(h,k))$,
$\Cont(\mathsf{append}(h,k),l,\mathsf{append}(\mathsf{append}(h,k),l))$,
$\Cont(k,l,\mathsf{append}(k,l))$, and
$\Cont(h,\mathsf{append}(k,l),\mathsf{append}(h,\mathsf{append}(k,l)))$
are then fed to \texttt{BEDC.FKernel.Cont.cont\_assoc\_hsame}. The result is
the endpoint $\hsame$ proof between the two parenthesizations, and the carrier
witnesses already built above package it as $R_U$.
\end{proof}
\leanchecked{BEDC.Derived.SemigroupUp.concrete\_unary\_history\_semigroup\_cont\_assoc\_classifier}

\begin{theorem}[Concrete unary-history semigroup fourfold coherence]
\label{thm:concrete-unary-history-semigroup-fourfold-coherence}
For unary histories $h,k,l,m:\mathsf{BHist}$, the left-nested and
right-nested fourfold products are classified by $R_U$:
$$
R_U(\mathsf{mul}_U(\mathsf{mul}_U(\mathsf{mul}_U(h,k),l),m),
\mathsf{mul}_U(h,\mathsf{mul}_U(k,\mathsf{mul}_U(l,m)))).
$$
The ten-field per-object fit is: traditional target fourfold semigroup
associativity coherence; BEDC source $\mathsf{BHist}$ restricted to
$\mathsf{UnaryHistory}$; carrier $\mathsf{UnaryHistory}$; classifier
carrier-aware $\hsame$; stability from unary append closure, the checked ternary
semigroup law, and classifier transitivity; ledger the two fourfold append
trees; core theorem
\autoref{thm:concrete-unary-history-semigroup-fourfold-coherence}; exactness
endpoint classification by $R_U$; standard bridge free unary append semigroup;
status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
First use unary append closure to keep all intermediate products in the carrier.
In particular, $\mathsf{mul}_U(l,m)$, $\mathsf{mul}_U(h,k)$,
$\mathsf{mul}_U(\mathsf{mul}_U(h,k),l)$, and the outer products on both sides
are again unary histories.

Apply \autoref{thm:concrete-unary-history-semigroup-laws} to
$(\mathsf{mul}_U(h,k),l,m)$. This classifies the left-nested product with the
middle bracketing
$$
\mathsf{mul}_U(\mathsf{mul}_U(h,k),\mathsf{mul}_U(l,m)).
$$

Apply \autoref{thm:concrete-unary-history-semigroup-laws} again to
$(h,k,\mathsf{mul}_U(l,m))$. This classifies the same middle bracketing with
the right-nested product.

Finally compose the two classifier witnesses using
\autoref{lem:concrete-unary-history-magma-classifier-stability}. Its
transitivity component gives the displayed $R_U$ classification between the two
fourfold append trees.
\end{proof}

The ten-field per-object fit is: traditional target semigroup; BEDC source
$\mathsf{BHist}$ restricted to unary histories; carrier $\mathsf{UnaryHistory}$;
classifier carrier-aware $\hsame$ on unary endpoints; stability closure,
congruence, and associativity for unary append; ledger append provenance
through $\Cont$; core theorem
\autoref{thm:concrete-unary-history-semigroup-laws}; exactness endpoint
classification by $R_U$; standard bridge free unary append semigroup; status
$\mathsf{ProofTarget}$.

\section{The certificate}
\label{sec:semigroup-certificate}

\begin{theorem}[Concrete unary-history SemigroupUp semantic certificate]
\label{thm:concrete-unary-history-semigroup-semantic-certificate}
Let $U(h)$ abbreviate $\mathsf{UnaryHistory}(h)$, let
$\mathsf{mul}_U(h,k):=\mathsf{append}(h,k)$, and let
$$
R_U(h,k):=U(h)\land U(k)\land\hsame(h,k).
$$
The tuple with source, pattern, and ledger all equal to $U$, classifier
$R_U$, and multiplication $\mathsf{mul}_U$ is the concrete $\SemigroupUp$
semantic naming certificate over $\mathsf{BHist}$. Its certificate fields are:
carrier inhabitation by $\emp$; classifier reflexivity, symmetry,
transitivity, and carrier transport; multiplication closure; multiplication
congruence; associativity; ledger append provenance through $\Cont$; and
exactness
$$
R_U(h,k)\Longleftrightarrow U(h)\land U(k)\land\hsame(h,k).
$$
\end{theorem}
\begin{proof}
The carrier field is supplied by $\emp$, which is a unary history. The
classifier fields are the four stability components of
\autoref{lem:concrete-unary-history-magma-classifier-stability}: reflexivity on
carrier points, symmetry, transitivity, and the two endpoint carrier
projections stored in each $R_U(h,k)$ witness.

The multiplication closure and multiplication congruence fields are inherited
from \autoref{thm:concrete-unary-history-magma-laws}, applied to the same
carrier $U$, multiplication $\mathsf{append}$, and classifier $R_U$. The ledger
row is the canonical append provenance
$\Cont(h,k,\mathsf{append}(h,k))$ for the displayed multiplication.

Associativity is the additional semigroup law in
\autoref{thm:concrete-unary-history-semigroup-laws}. Its checked Lean source,
\texttt{BEDC.Derived.SemigroupUp.concrete\_unary\_history\_semigroup\_cont\_assoc\_classifier},
packages the two parenthesized append products as carrier-aware $R_U$-equivalent
endpoints.

Finally, exactness is definitional: the public classifier $R_U$ is precisely the
triple consisting of the two unary carrier witnesses and the endpoint
$\hsame$ proof. Thus the displayed biconditional is the certificate's endpoint
criterion, with no extra cases beyond the concrete unary-history carrier.
\end{proof}
\leanchecked{BEDC.Derived.SemigroupUp.ConcreteUnaryHistorySemigroup\_semanticNameCert}

\begin{definition}[Semigroup certificate fields]
\label{def:semigroup-certificate-fields}
Let $C$ be a carrier with classifier $\sim_C$ and multiplication $\cdot$. A $\SemigroupUp(C)$ certificate consists of the carrier, source, pattern, classifier, stability, exactness, and ledger rows whose operation language is generated by carried endpoints and binary multiplication. The classifier rows are carrier inhabitation, reflexivity, symmetry, transitivity, and carrier transport for $\sim_C$. The algebraic rows are multiplication closure, multiplication congruence in both arguments, and associativity under $\sim_C$. The exactness row is the public endpoint criterion attached to the same classifier, and the ledger records carrier witnesses and the multiplication operation tree behind each product expression. This abstracts the field list realized in \autoref{thm:concrete-unary-history-semigroup-semantic-certificate}. No distinguished identity element, left identity row, or right identity row belongs to the $\SemigroupUp$ row set.
\end{definition}

\begin{proposition}[Monoid forgets to Semigroup certificate]
\label{prop:monoid-forgets-semigroup-certificate}
Let $C$ carry a $\MonoidUp(C)$ certificate with multiplication $\cdot$, identity $e$, and classifier $\sim_C$. If the identity element is not exported, the left and right identity stability rows are omitted, and every ledger entry whose expression provenance uses the distinguished identity symbol is omitted, then the retained carrier, source, semigroup pattern, classifier, semigroup stability fields, exactness row, and multiplication ledger form a $\SemigroupUp(C)$ certificate. The carrier $C$, multiplication $\cdot$, and classifier $\sim_C$ are unchanged.
\end{proposition}
\begin{proof}
By \autoref{def:monoid-certificate-obligations}, the given certificate supplies carrier, source, pattern, classifier, stability, and ledger data for $\MonoidUp(C)$. The construction keeps exactly the rows whose endpoint claims and expression provenance use only the carrier classifier and binary multiplication.

By \autoref{def:monoid-carrier}, a monoid carrier is a carrier $C$ with classifier $\sim_C$, operation $\cdot:C\times C\to C$, identity $e$, and law fields. Suppressing the identity coordinate leaves the same carrier, classifier, and binary operation. The operation type already gives the multiplication closure row required by \autoref{def:semigroup-certificate-fields}.

By \autoref{def:monoid-source-specification}, the source is the carrier $C$ with its classifier and operation data, so the retained source is still over the same $C$, $\sim_C$, and $\cdot$. By \autoref{def:monoid-pattern-specification}, the monoid pattern forms expressions from $e$, carrier witnesses, and binary multiplication. Restricting that pattern to expressions containing no identity symbol leaves precisely the product-expression language of \autoref{def:semigroup-certificate-fields}. By \autoref{def:monoid-classifier-specification}, the classifier is the supplied carrier sameness relation, so the classifier and its endpoint exactness row are copied without changing endpoints.

For stability, \autoref{def:monoid-stability-certificate} lists classifier reflexivity, classifier transitivity, associativity under the classifier, left identity, right identity, and multiplication congruence. Retaining the first, second, third, and sixth rows gives the semigroup algebraic stability rows: classifier reflexivity and transitivity, associativity, and multiplication congruence. The classifier symmetry and carrier-transport rows belong to the underlying NameCert core exhibited for monoids in \autoref{thm:concrete-monoid-namecert}; they mention only $C$ and $\sim_C$, so they are retained verbatim. The two discarded identity rows mention $e$ and are not semigroup obligations.

Finally, \autoref{def:monoid-ledger-policy} records carrier witnesses and operation trees behind monoid expressions. Removing the entries whose operation tree uses the identity symbol leaves the carrier witnesses and binary multiplication provenance for product expressions. These are exactly the ledger rows required by \autoref{def:semigroup-certificate-fields}. Hence the retained rows satisfy the $\SemigroupUp(C)$ certificate fields with the original carrier, multiplication, and classifier.
\end{proof}

\begin{proposition}[Semigroup forgets to Magma certificate]
\label{prop:semigroup-forgets-magma-certificate}
Let $C$ be a carrier with classifier $\sim_C$ and multiplication $\cdot$. If
$C$ carries a $\SemigroupUp(C)$ certificate with these data, then the retained
carrier, source, binary-operation pattern, classifier, exactness row, operation
closure row, operation congruence row, and binary-operation ledger form a
$\MagmaUp(C)$ certificate after the associativity stability row is omitted. The
carrier $C$, multiplication $\cdot$, and classifier $\sim_C$ are unchanged.
\end{proposition}
\begin{proof}
By \autoref{def:semigroup-certificate-fields}, a $\SemigroupUp(C)$ certificate
contains carrier, source, pattern, classifier, stability, exactness, and ledger
rows whose operation language is generated by carried endpoints and binary
multiplication. Its classifier rows are carrier inhabitation, reflexivity,
symmetry, transitivity, and carrier transport for $\sim_C$. Its algebraic rows
are multiplication closure, multiplication congruence in both arguments, and
associativity under $\sim_C$.

The magma interface in \autoref{ch:concrete-instances-magma-namecert} requires
a carrier with one binary operation and no associativity, identity, or inverse
demands. The concrete field realization in
\autoref{thm:concrete-unary-history-magma-semantic-certificate} records exactly
the rows needed by that interface: carrier inhabitation; classifier
reflexivity, symmetry, transitivity, and carrier transport; operation closure;
operation congruence; binary-operation ledger provenance; and exactness for the
same public classifier.

Retain the carrier $C$, the source over $C$, the classifier $\sim_C$, and the
exactness row attached to that classifier. Interpret the semigroup
multiplication $\cdot$ as the magma operation. The pattern and ledger remain
well formed because both interfaces use the same single binary operation
language; associativity is a stability law, not an additional operation symbol
or carrier coordinate.

The closure row and the congruence row of the semigroup certificate are copied
as the operation closure and operation congruence rows of the magma
certificate. The classifier rows are copied without changing endpoints. The
associativity row has no corresponding $\MagmaUp$ obligation, so omitting it
leaves every magma row supplied. Hence the retained rows satisfy the
$\MagmaUp(C)$ certificate fields over the original carrier, multiplication, and
classifier.
\end{proof}

\begin{definition}[Opposite semigroup operation]
\label{def:opposite-semigroup-operation}
Let $C$ be a carrier with binary multiplication $\cdot$. The opposite multiplication on the same carrier is the binary operation $\star$ defined by
$$
x\star y:=y\cdot x.
$$
It introduces no additional carrier element and no additional classifier relation.
\end{definition}
\leandef{BEDC.Derived.SemigroupUp.ConcreteUnaryHistorySemigroupOppositeMul}
\leandef{BEDC.Derived.SemigroupUp.ConcreteUnaryHistorySemigroup\_oppMul}

\begin{proposition}[Opposite semigroup certificate]
\label{prop:opposite-semigroup-certificate}
Let $C$ be a carrier with classifier $\sim_C$ and multiplication $\cdot$. If $C$ carries a $\SemigroupUp(C)$ certificate for $\cdot$, then the same carrier and classifier carry a $\SemigroupUp(C)$ certificate for the opposite multiplication $\star$ of \autoref{def:opposite-semigroup-operation}.
\end{proposition}
\leanchecked{BEDC.Derived.SemigroupUp.ConcreteUnaryHistorySemigroup\_opposite\_semanticNameCert}
\leanchecked{BEDC.Derived.SemigroupUp.concrete\_unary\_history\_semigroup\_opposite\_cont\_assoc\_classifier}
\begin{proof}
By \autoref{def:semigroup-certificate-fields}, the semigroup certificate consists of the carrier, source, pattern, classifier, stability, exactness, and ledger rows for carried endpoints and one binary multiplication. The carrier rows and the classifier rows are retained unchanged, since the carrier is still $C$ and the classifier is still $\sim_C$. The exactness row is also retained unchanged, because it is attached to this same public classifier.

The operation source for $\star$ is the displayed definition $x\star y:=y\cdot x$. Closure follows immediately from the original multiplication closure row: if $x,y\in C$, then $y\cdot x\in C$, hence $x\star y\in C$.

For congruence, assume $x\sim_C x'$ and $y\sim_C y'$. The original multiplication congruence applied to the ordered pair of witnesses $y\sim_C y'$ and $x\sim_C x'$ gives
$$
y\cdot x\sim_C y'\cdot x'.
$$
By the definition of $\star$, this is exactly
$$
x\star y\sim_C x'\star y'.
$$
Thus the opposite operation satisfies the semigroup multiplication-congruence row.

For associativity, let $x,y,z\in C$. The two opposite products unfold as
$$
(x\star y)\star z=z\cdot (y\cdot x)
$$
and
$$
x\star (y\star z)=(z\cdot y)\cdot x.
$$
The original associativity row for $\cdot$, applied to the triple $(z,y,x)$, gives a classifier witness
$$
(z\cdot y)\cdot x\sim_C z\cdot (y\cdot x).
$$
The classifier symmetry row from the same certificate reverses this witness, yielding
$$
z\cdot (y\cdot x)\sim_C (z\cdot y)\cdot x,
$$
which is precisely the associativity row for $\star$ in the displayed orientation.

It remains only to account for the pattern and ledger rows. A $\star$-expression tree is read as a $\cdot$-expression tree by exchanging the two children at each binary node. Leaves remain carried endpoints, and each binary node is licensed by the original multiplication source. The same tree reading transports the operation-tree provenance in the ledger. Since \autoref{def:semigroup-certificate-fields} includes no identity, inverse, left-unit, or right-unit row, there is no further handed obligation to check. These rows together form the required $\SemigroupUp(C)$ certificate for the opposite multiplication.
\end{proof}

\closureat{SemigroupUp}{matureStr}[BEDC.Derived.SemigroupUp.ConcreteUnaryHistorySemigroup\_semanticNameCert]
\begin{closurestatus}{\SemigroupUp}
  \constructivestory{}
  \theoryclosure{\matureClosure}
  \scopeclosed{The mature paper-side package consists of the concrete unary-history $\SemigroupUp$ semantic certificate over $\UnaryHistory$, append, carrier-aware $\hsame$, $\Cont$ provenance, associativity, congruence, and exactness; the forgetful bridge from $\MonoidUp$ in \autoref{prop:monoid-forgets-semigroup-certificate}; the forgetful bridge to $\MagmaUp$ in \autoref{prop:semigroup-forgets-magma-certificate}; and the opposite semigroup certificate in \autoref{prop:opposite-semigroup-certificate}.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.SemigroupUp.ConcreteUnaryHistorySemigroup\_semanticNameCert}
  \bridgestatus{paperBridge}
  \notclaimed{Checked bridge verification, identity, inverse, commutativity, ring or field structure remain outside this claim.}
  \upgradepath{Bridge verification can promote the paper bridge rows to checked bridge status without changing the mature semigroup package recorded here.}
\end{closurestatus}
