\chapter{A Concrete Naming Certificate for $\CauchyFilterUp$}
\label{ch:concrete-instances-cauchyfilter-namecert}

The $\CauchyFilterUp$ interface names the finite filterbase surface used by
the real-completion boundary. The external mathematical idiom is the
Kelley--Bourbaki language of filters and directed bases, but the BEDC object
below keeps only explicit finite rows: base packets over $\mathsf{BHist}$,
refinement ledgers, Cauchy-modulus rows, and handoff rows for
$\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealBallUp$, and
$\RealUp$.

\begin{definition}[CauchyFilter finite-filterbase carrier]
\label{def:cauchyfilter-finite-filterbase-carrier}
A $\CauchyFilterUp$ finite-filterbase carrier is a finite $\mathsf{BHist}$
packet
$$
F=(B,R,M,L,P)
$$
with the following visible rows:
\begin{enumerate}
\item $B$ is a finite list of base packets, each base packet carrying a
  $\StreamNameUp$ scheduled window and a nonempty finite family of
  $\DyadicRatCoreUp$ observation rows;
\item $R$ is a refinement ledger whose row for two displayed base packets
  names a third displayed base packet refining both requested packets;
\item $M$ is a $\CauchyModulusUp$ row assigning to each requested precision a
  finite base packet after which all displayed dyadic observations are within
  the requested radius;
\item $L$ is the ledger exposing the base-packet rows, the refinement rows,
  the modulus rows, the componentwise $\hsame$ comparisons, and the displayed
  $\Cont$ routes used by refinements and precision reads;
\item $P$ is the $\Pkg$ provenance row naming the $\RegSeqRatUp$,
  $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealBallUp$, and $\RealUp$ certificate
  boundaries consumed by the packet.
\end{enumerate}
The carrier accepts only these finite rows. Classification is componentwise
transport of $B$, $R$, $M$, $L$, and $P$ through the displayed $\hsame$ and
$\Cont$ data.
\end{definition}

\begin{theorem}[CauchyFilter directed refinement obligation]
\label{thm:cauchyfilter-directed-refinement-obligation}
For every accepted $\CauchyFilterUp$ carrier $F=(B,R,M,L,P)$ and every two
base packets displayed in $B$, the refinement row in $R$ is a displayed
$\Cont$ and $\hsame$ obligation: it names a finite base packet in the same
carrier whose observation rows refine both inputs through the continuation
routes recorded by $L$.
\end{theorem}
\begin{proof}
Project the accepted carrier through
\autoref{def:cauchyfilter-finite-filterbase-carrier}. The row $R$ is stored
with the base packets it refines, so the two input packets and the refined
packet are all visible finite $\mathsf{BHist}$ rows.

Read the continuation routes from $L$. Each route records how the refined
packet restricts to the requested input packet, and the accompanying $\hsame$
rows compare the displayed dyadic observations componentwise.

Thus directedness is not a global existence assertion. It is exactly the
finite refinement row already stored in the carrier, together with its
displayed $\Cont$ and $\hsame$ witnesses.
\end{proof}

\begin{theorem}[CauchyFilter Cauchy modulus obligation]
\label{thm:cauchyfilter-cauchy-modulus-obligation}
Let $F=(B,R,M,L,P)$ be an accepted $\CauchyFilterUp$ carrier. The modulus row
$M$ makes $F$ a constructive Cauchy object: for each displayed precision
request, $M$ selects a finite base packet, and every later refinement row in
$R$ carries dyadic observations whose $\DyadicRatCoreUp$ distance ledger is
bounded by the requested radius.
\end{theorem}
\begin{proof}
Fix a precision request and project the selected row of $M$. It names a base
packet in $B$ and records the requested dyadic radius through the
$\CauchyModulusUp$ boundary.

Now take any later refinement row displayed by $R$. By
\autoref{thm:cauchyfilter-directed-refinement-obligation}, the later packet
refines the selected packet through explicit $\Cont$ routes and componentwise
$\hsame$ comparisons.

The dyadic distance bound is read from the same finite ledger $L$. Since the
bound is attached to the selected precision and transported along the displayed
refinement rows, the carrier supplies a constructive Cauchy witness using only
its finite base, modulus, and dyadic observation rows.
\end{proof}

\begin{theorem}[CauchyFilter NameCert obligation surface]
\label{thm:cauchyfilter-namecert-obligation-surface}
The local $\NameCert_{\CauchyFilterUp}$ obligation surface consists of five
finite rows:
\begin{enumerate}
\item carrier: the finite-filterbase carrier of
\autoref{def:cauchyfilter-finite-filterbase-carrier};
\item classifier transport: accepted carriers compare by componentwise
$\hsame$ transport of the base packets, refinement ledgers, modulus rows,
evidence ledgers, and provenance rows, with reads routed through displayed
$\Cont$ data;
\item directedness: the displayed refinement row of
\autoref{thm:cauchyfilter-directed-refinement-obligation};
\item Cauchy modulus: the precision-to-base selection and dyadic-radius
readback of \autoref{thm:cauchyfilter-cauchy-modulus-obligation};
\item downstream handoff: $\RealUp$ and $\RegSeqRatUp$ consumers read only the
base packets, stream schedules, dyadic observations, real-ball bounds,
refinement rows, modulus rows, ledger rows, and provenance rows of the same
finite packet.
\end{enumerate}
These five rows form the seed obligation for naming completion-facing Cauchy
filterbase data over displayed histories.
\end{theorem}
\begin{proof}
The carrier row is
\autoref{def:cauchyfilter-finite-filterbase-carrier}. It supplies the finite
base packets, refinement ledger, Cauchy-modulus row, evidence ledger, and
provenance row.

Classifier transport is componentwise. Transporting the five carrier
coordinates through their displayed $\hsame$ rows and following the recorded
$\Cont$ routes repacks the same finite-filterbase shape.

Directedness and the Cauchy property are the two distinguished projections of
the carrier. The first projection is
\autoref{thm:cauchyfilter-directed-refinement-obligation}; the second is
\autoref{thm:cauchyfilter-cauchy-modulus-obligation}.

For downstream readback, a $\RealUp$ or $\RegSeqRatUp$ consumer can cite only
the rows named by $P$ and exposed by $L$. Those rows are exactly the base
packets, stream schedules, dyadic observations, real-ball bounds, refinement
rows, modulus rows, ledger rows, and provenance rows of the carrier, so the
surface is exhausted by the five listed obligations.
\end{proof}

\begin{theorem}[CauchyFilter carrier transport obligation]
\label{thm:cauchyfilter-carrier-transport-obligation}
Let $F=(B,R,M,L,P)$ and $F'=(B',R',M',L',P')$ be displayed
$\CauchyFilterUp$ finite-filterbase carriers. Suppose the evidence ledger
exhibits componentwise $\hsame$ rows for $B$ with $B'$, $R$ with $R'$, $M$
with $M'$, $L$ with $L'$, and $P$ with $P'$, and suppose every read used by a
refinement or precision request is routed through the displayed $\Cont$ rows.
Then classifier transport preserves the accepted carrier tuple: $F$ is
accepted exactly when the transported tuple $F'$ is accepted, and all accepted
reads remain inside the displayed finite rows $(B',R',M',L',P')$.
\end{theorem}
\begin{proof}
Unpack the finite carrier of
\autoref{def:cauchyfilter-finite-filterbase-carrier}. Acceptance is expressed
only through the five displayed coordinates $B$, $R$, $M$, $L$, and $P$.

Transport is componentwise. The base packets, refinement ledger, modulus row,
evidence ledger, and provenance row are compared by the named $\hsame$
witnesses, while each refinement or precision read follows a displayed
$\Cont$ route recorded in the ledger.

Apply \autoref{thm:cauchyfilter-namecert-obligation-surface} to identify the
classifier row as the transport row of the local $\NameCert$ surface. The
transported carrier therefore has exactly the same finite-filterbase shape,
with rows read from $(B',R',M',L',P')$.

No host filter, selected limit, quotient real, or ambient completeness object
is introduced by this transport. The construction moves only the displayed
finite rows and their recorded $\hsame$ and $\Cont$ witnesses.
\end{proof}

\begin{theorem}[CauchyFilter refinement directedness package]
\label{thm:cauchyfilter-refinement-directedness-package}
For an accepted $\CauchyFilterUp$ carrier $F=(B,R,M,L,P)$, the directedness
obligation is the finite package consisting of the two input base packets in
$B$, the selected third base packet named by the row of $R$, the two displayed
$\Cont$ routes from that selected packet to the inputs, the componentwise
$\hsame$ witnesses for the transported dyadic observations, and the modulus
row of $M$ that reads the selected packet at every requested precision.
\end{theorem}
\begin{proof}
Choose two displayed base packets in $B$. By
\autoref{thm:cauchyfilter-directed-refinement-obligation}, the corresponding
row of $R$ names a third displayed base packet together with the continuation
routes and componentwise comparison rows needed to refine both inputs.

The selected packet is still a base packet of the same finite carrier, so the
modulus row can be read without leaving the displayed surface. Apply
\autoref{thm:cauchyfilter-cauchy-modulus-obligation} to attach the requested
precision row and its dyadic-radius ledger to the same refinement package.

The resulting object is a directedness package, not an ambient filter
principle. Every component is one of the rows already listed in
\autoref{def:cauchyfilter-finite-filterbase-carrier} and exposed by
\autoref{thm:cauchyfilter-namecert-obligation-surface}.
\end{proof}

\begin{theorem}[CauchyFilter Real and RegSeqRat handoff non-escape]
\label{thm:cauchyfilter-real-regseq-handoff-nonescape}
Every $\RealUp$ or $\RegSeqRatUp$ consumer of an accepted $\CauchyFilterUp$
carrier $F=(B,R,M,L,P)$ reads only the displayed base packets, the
$\StreamNameUp$ schedules, the $\DyadicRatCoreUp$ observation rows, the
$\RealBallUp$ bounds, the refinement rows, the Cauchy-modulus rows, the ledger
rows, and the $\Pkg$ provenance rows named by $L$ and $P$. The handoff does
not read a host filter, a selected limit, a quotient real, or an ambient
completeness principle.
\end{theorem}
\begin{proof}
Project the downstream handoff row from
\autoref{thm:cauchyfilter-namecert-obligation-surface}. It lists the rows
available to $\RealUp$ and $\RegSeqRatUp$ consumers: base packets, stream
schedules, dyadic observations, real-ball bounds, refinement rows, modulus
rows, ledger rows, and provenance rows.

The carrier definition fixes where these rows live. By
\autoref{def:cauchyfilter-finite-filterbase-carrier}, the base packets are in
$B$, refinement data is in $R$, precision data is in $M$, read evidence is in
$L$, and downstream provenance is in $P$.

Directed refinement and precision readback do not add further carrier data.
They are the displayed rows supplied by
\autoref{thm:cauchyfilter-directed-refinement-obligation} and
\autoref{thm:cauchyfilter-cauchy-modulus-obligation}.

Thus the Real and regular rational sequence handoff is closed under the named
finite rows. Since no step constructs or selects an external filter limit, the
handoff cannot escape through host filters, selected limits, quotient reals,
or ambient completeness.
\end{proof}

\begin{theorem}[CauchyFilter L10 dependency handoff lattice]
\label{thm:cauchyfilter-l10-dependency-handoff-lattice}
Every accepted $\CauchyFilterUp$ handoff is a horizontal L10 dependency
lattice for the real-completion surface. Its base packets are read through
\autoref{ch:concrete-instances-streamname-namecert}, its dyadic observations
through \autoref{ch:concrete-instances-dyadicratcore-namecert}, its regular
readbacks through \autoref{ch:concrete-instances-regseqrat-namecert}, and its
final seal through \autoref{ch:concrete-instances-real-namecert}. The lattice
is exhausted by the finite carrier rows, directed refinement rows,
Cauchy-modulus rows, ledger evidence, and provenance rows of the accepted
carrier; it contains no host filter, selected limit, quotient real, or ambient
completeness datum.
\end{theorem}
\begin{proof}
Start with an accepted carrier $F=(B,R,M,L,P)$. The carrier definition
\autoref{def:cauchyfilter-finite-filterbase-carrier} places every base packet
in the displayed finite row $B$, and each such packet carries its
$\BHist$ evidence, $\StreamNameUp$ schedule, dyadic observation rows,
real-ball bounds, ledger reads, and downstream provenance. Hence the
horizontal base layer of the handoff is read through the StreamName and
DyadicRatCore concrete-instance chapters cited in the statement.

The middle layer is forced by the two obligations of the accepted carrier.
Apply \autoref{thm:cauchyfilter-directed-refinement-obligation} to read a
displayed refinement row of $R$ whenever two base packets are compared, and
apply \autoref{thm:cauchyfilter-cauchy-modulus-obligation} to read the
displayed precision row of $M$ together with its retained dyadic-radius ledger.
These rows are still entries of $B$, $R$, $M$, and $L$, so they add refinement
and Cauchy control without introducing a new completion object.

Finally apply
\autoref{thm:cauchyfilter-real-regseq-handoff-nonescape}. It identifies the
regular-sequence and real handoff boundary as exactly the displayed base,
stream, dyadic, real-ball, refinement, modulus, ledger, and $\Pkg$ provenance
rows. Therefore the RegSeqRat readback layer and the Real sealing layer are
the cited sibling concrete-instance dependencies, and the whole L10 handoff is
closed before any host filter, selected limit, quotient real, or ambient
completeness principle can be read.
\end{proof}

\begin{theorem}[CauchyFilter uniform-space completion handoff]
\label{thm:cauchyfilter-uniformspace-completion-handoff}
Let $F=(B,R,M,L,P)$ be an accepted $\CauchyFilterUp$ finite-filterbase
carrier whose provenance row exposes the same finite entourage and
filterbase surface consumed by $\UniformSpaceUp$. Every $\CompletionUp$ or
$\RealUp$ read admitted from $F$ factors first through the displayed
$\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, $\RegSeqRatUp$
readback rows, $\RealBallUp$ bounds, and the finite $\UniformSpaceUp$
entourage rows before any completion-facing seal is available. Consequently
the handoff described in \autoref{ch:concrete-instances-uniformspace-namecert}
and consumed by \autoref{ch:concrete-instances-completion-namecert} and
\autoref{ch:concrete-instances-metric-namecert} receives only the finite
ledger displayed by the Cauchy filterbase carrier, not a selected limit,
quotient stream, host filter, or ambient completeness object.
\end{theorem}
\begin{proof}
Project the carrier $F=(B,R,M,L,P)$. The base row $B$ supplies the displayed
filterbase packets, $R$ supplies directed refinement, $M$ supplies Cauchy
precision, $L$ supplies ledger reads, and $P$ supplies provenance. By
\autoref{thm:cauchyfilter-l10-dependency-handoff-lattice}, these rows already
identify the StreamName windows, DyadicRatCore observations, RegSeqRat
readback rows, RealBall bounds, ledger evidence, and real-facing provenance.

Next route the finite filterbase as uniform entourage data. Apply
\autoref{thm:uniformspace-cauchy-completion-handoff}: the UniformSpaceUp
interface exposes only finite entourage rows, diagonal rows, refinement rows,
symmetry rows, composition rows, endpoint $\hsame$ transport, and $\Pkg$
provenance. Since the provenance row of $F$ exposes precisely this surface,
the CauchyFilterUp read may be consumed by the UniformSpaceUp handoff without
adding a further carrier coordinate.

The completion-facing consumer therefore receives the displayed finite
ledger in the stated order: stream windows, dyadic observations, regular
readback, real-ball bounds, and uniform entourage rows. None of the preceding
projections constructs a chosen limit, quotient stream equality, host filter,
or ambient completeness witness, so no such object can be read before the
completion-facing seal.
\end{proof}

\begin{closurestatus}{\CauchyFilterUp}
  \constructivestory{A $\CauchyFilterUp$ packet is generated by finite base packets over $\mathsf{BHist}$, a displayed refinement ledger, a $\CauchyModulusUp$ precision row, visible dyadic observation rows, stream schedules, real-ball bounds, componentwise $\hsame$ transports, displayed $\Cont$ routes, and $\Pkg$ provenance for the real-completion handoff.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope registers the finite-filterbase carrier, carrier transport row, directed-refinement package, Cauchy-modulus obligation, and downstream $\RealUp/\RegSeqRatUp$ non-escape handoff surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{The chapter does not close real completeness, uniqueness of real endpoints, analytic filters, or a checked bridge to an external filter schema.}
  \upgradepath{Scoped closure requires Lean targets for carrier transport, refinement directedness, modulus readback, and the finite $\RealUp/\RegSeqRatUp$ handoff surface.}
\end{closurestatus}

\begin{definition}[CauchyFilter finite subfilterbase restriction datum]
\label{def:cauchyfilter-finite-subfilterbase-restriction-datum}
Let $F=(B,R,M,L,P)$ be an accepted $\CauchyFilterUp$ finite-filterbase
carrier in the sense of \autoref{def:cauchyfilter-finite-filterbase-carrier}.
A finite subfilterbase restriction datum for $F$ is a displayed finite sublist
$B'\subseteq B$ together with two preservation rows:
\begin{enumerate}
\item refinement preservation: whenever $b_0$ and $b_1$ are displayed in $B'$
and the row of $R$ for $(b_0,b_1)$ names a refined base packet $b_2$, the
packet $b_2$ is displayed in $B'$ and the corresponding $\Cont$ and $\hsame$
witnesses in $L$ are retained in the restricted ledger;
\item modulus preservation: for every precision request admitted by the
carrier, the base packet selected by the row $M$ is displayed in $B'$, and the
associated dyadic-radius readback row of $L$ is retained in the restricted
ledger.
\end{enumerate}
The restricted packet is
$$
F|_{B'}=(B',R|_{B'},M|_{B'},L|_{B'},P),
$$
where $R|_{B'}$ keeps exactly the refinement rows whose two inputs lie in
$B'$, $M|_{B'}$ keeps the same precision-to-base selections, $L|_{B'}$ keeps
only the ledger rows used by those base, refinement, modulus, $\Cont$, and
$\hsame$ reads, and $P$ is the unchanged downstream provenance row.
\end{definition}

\begin{theorem}[CauchyFilter finite subfilterbase restriction]
\label{thm:cauchyfilter-finite-subfilterbase-restriction}
Let $F=(B,R,M,L,P)$ be an accepted $\CauchyFilterUp$ finite-filterbase carrier.
If $B'\subseteq B$ is a finite subfilterbase restriction datum for $F$ in the
sense of \autoref{def:cauchyfilter-finite-subfilterbase-restriction-datum},
then the restricted packet
$$
F|_{B'}=(B',R|_{B'},M|_{B'},L|_{B'},P)
$$
is an accepted $\CauchyFilterUp$ finite-filterbase carrier. Its downstream
handoff boundary is the same finite $\RegSeqRatUp$, $\StreamNameUp$,
$\DyadicRatCoreUp$, $\RealBallUp$, and $\RealUp$ provenance boundary carried by
$F$.
\end{theorem}
\begin{proof}
The carrier rows are finite because $B'$ is a displayed finite sublist of the
finite base row $B$, while $R|_{B'}$, $M|_{B'}$, and $L|_{B'}$ are obtained by
retaining displayed rows from the finite ledgers $R$, $M$, and $L$ of
\autoref{def:cauchyfilter-finite-filterbase-carrier}. Each base packet in
$B'$ is already a base packet of $B$, hence it carries the same $\BHist$ row,
$\StreamNameUp$ scheduled window, and nonempty finite family of
$\DyadicRatCoreUp$ observation rows that it carried in $F$.

Directedness is inherited row by row. Take two base packets displayed in
$B'$. In the accepted carrier $F$, \autoref{thm:cauchyfilter-directed-refinement-obligation}
reads the corresponding row of $R$ as a displayed refinement packet together
with its $\Cont$ routes and componentwise $\hsame$ witnesses. Refinement
preservation in the restriction datum says that this refined packet is again
displayed in $B'$ and that the required continuation and comparison witnesses
remain in $L|_{B'}$. Therefore $R|_{B'}$ supplies exactly the directed
refinement obligation required of the restricted carrier.

The Cauchy modulus row is also inherited without changing the selected bases.
For a displayed precision request, \autoref{thm:cauchyfilter-cauchy-modulus-obligation}
reads the row of $M$ in $F$ as a selected base packet together with the dyadic
radius ledger controlling every later displayed refinement. Modulus
preservation says that the selected packet lies in $B'$ and that the associated
radius readback row remains in $L|_{B'}$. If a later refinement is read inside
$R|_{B'}$, it is one of the refinement rows of $R$, so the same dyadic bound
from $L$ applies to it, and the retained row in $L|_{B'}$ records that bound.
Thus $M|_{B'}$ is a constructive Cauchy modulus for the restricted packet.

It remains to identify the handoff boundary. The restriction does not replace
$P$; it only removes base, refinement, modulus, and ledger rows not used by
$B'$. Hence a downstream $\RealUp$ or $\RegSeqRatUp$ consumer can still read
exactly the provenance categories listed in
\autoref{thm:cauchyfilter-namecert-obligation-surface}: base packets, stream
schedules, dyadic observations, real-ball bounds, refinement rows, modulus
rows, ledger rows, and the same $\Pkg$ provenance boundary. Since every
retained row is a displayed row of the accepted carrier and the two preservation
conditions keep all refinement and modulus rows needed for the CauchyFilter
obligations, $F|_{B'}$ repacks as an accepted $\CauchyFilterUp$ carrier with
the same finite downstream handoff boundary.
\end{proof}
