\chapter{A Concrete Naming Certificate for $\BaireSpaceUp$}
\label{ch:concrete-instances-bairespace-namecert}
\origin{human}

The $\BaireSpaceUp$ interface names Brouwer-style Baire space as a certificate
for natural-number-indexed streams whose observations are displayed finite
unary histories. The BEDC surface does not treat infinite sequences as
primitive histories. It records finite prefix windows, a prefix-cylinder
classifier, stream-name scheduling rows, and package provenance that can be
read by $\RegSeqRatUp$ and $\RealUp$ consumers.
The schedule row $s$ is consumed from
\autoref{ch:concrete-instances-streamname-namecert}; $\NatUp$ supplies the
unary index rows, and the $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$
boundaries are the downstream consumer surfaces for the displayed finite
prefix windows.

\begin{definition}[BaireSpace stream carrier]
\label{def:baire-space-stream-carrier}
A $\BaireSpaceUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
B=(s,w,c,l,p)
$$
with the following visible rows:
\begin{enumerate}
\item $s$ is a $\StreamNameUp$ schedule row whose $n$th displayed request
returns a finite $\mathsf{UnaryHistory}$ answer row;
\item $w$ is a finite prefix-window ledger listing the requested natural
indices and the unary answer rows displayed for those indices;
\item $c$ is the prefix-cylinder classifier row: two packets classify together
over a displayed window exactly when their listed unary answer rows are paired
componentwise by $\hsame$ through the same scheduled indices;
\item $l$ is the local ledger exposing the $\mathsf{BHist}$ packet, the
$\mathsf{UnaryHistory}$ answer rows, the finite index window, the
componentwise $\hsame$ comparisons, and the $\Cont$ routes used by prefix
restriction;
\item $p$ is the $\Pkg$ provenance row naming the $\NatUp$, $\StreamNameUp$,
$\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ certificate boundaries
available to consumers.
\end{enumerate}
The carrier predicate is $\mathsf{BairePrefix}(s,w,c,l,p)$. It accepts only
finite prefix displays of a natural-number-indexed stream; every public read
is routed through the selected window and the displayed classifier row.
\end{definition}
\leanchecked{BEDC.Derived.BaireSpaceUp.TasteGate.BaireSpaceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[BaireSpace prefix-cylinder stability]
\label{thm:baire-space-prefix-cylinder-stability}
Let $B=(s,w,c,l,p)$ be an accepted $\BaireSpaceUp$ carrier. If $B'$ is obtained
from $B$ by transporting the stream schedule, every displayed unary answer in a
finite prefix window, the classifier row, the local ledger, and the provenance
row by the $\hsame$ and $\Cont$ data recorded in $l$, then $B'$ is again an
accepted carrier. The prefix-cylinder classifier for the transported window
reads exactly the transported unary rows and no tail beyond that window.
\end{theorem}
\leanchecked{BEDC.Derived.BaireSpaceUp.BaireSpacePrefixPacket\_prefix\_cylinder\_stability}
\begin{proof}
Project the carrier of \autoref{def:baire-space-stream-carrier}. The only
data visible to the classifier are the stream schedule, the finite index
window, and the unary answer rows listed by that window.

Transport each listed row through the displayed $\hsame$ comparisons in the
ledger. The $\Cont$ routes in the same ledger restrict the stream readback to
the transported prefix, so the repacked tuple has the same carrier shape.

The classifier row is a cylinder classifier. It compares exactly the displayed
prefix entries, and no coordinate in the carrier stores an infinite tail as a
history object. Thus the transported packet is accepted with the transported
prefix-cylinder read.
\end{proof}

\begin{theorem}[BaireSpace prefix-restriction composition]
\label{thm:baire-space-prefix-restriction-composition}
Let $B=(s,w,c,l,p)$ be an accepted $\BaireSpaceUp$ carrier. Suppose the ledger
$l$ displays a prefix restriction from $B$ to $B_1$ and then a second prefix
restriction from $B_1$ to $B_2$, each recorded by the corresponding $\hsame$
comparisons and $\Cont$ routes on the stream schedule, finite index window,
unary answer rows, classifier row, and provenance row. Then the composite
restriction is again an accepted $\BaireSpaceUp$ prefix packet.

Its visible unary rows are exactly the twice-restricted subwindow of $w$, its
classifier is the componentwise $\hsame$ restriction of the original
prefix-cylinder classifier $c$ to that subwindow, and its provenance is still
the same $\Pkg$ row $p$. The composite packet introduces no hidden infinite
tail and no host sequence equality.
\end{theorem}
\begin{proof}
Project the accepted packet $B$ through
\autoref{def:baire-space-stream-carrier}. The first displayed restriction is a
transport of the schedule, window, unary rows, classifier, ledger, and
provenance along rows already recorded in $l$.

Use \autoref{thm:baire-space-prefix-cylinder-stability} on this first
restriction. The result is an accepted prefix packet $B_1$ whose classifier
reads only the first restricted finite subwindow.

Apply the same stability theorem to the second displayed restriction out of
$B_1$. The $\Cont$ routes compose inside the displayed ledger, so the resulting
packet reads precisely the subwindow obtained by restricting the original
prefix window twice.

It remains to identify the classifier and provenance. The classifier at each
listed coordinate is obtained by the componentwise $\hsame$ restriction of the
original cylinder row $c$, and the $\Pkg$ coordinate is transported as the same
provenance row $p$.

Finally, the ledger coverage statement of
\autoref{thm:baire-space-ledger-coverage} rules out every consumer read not
listed in the finite window. Hence the composite construction cannot expose an
infinite tail or an equality of host sequences.
\end{proof}
\leanchecked{BEDC.Derived.BaireSpaceUp.BaireSpacePrefixPacket\_prefix\_restriction\_composition}

\begin{theorem}[BaireSpace NameCert obligations]
\label{thm:baire-space-namecert-obligations}
The local $\NameCert_{\BaireSpaceUp}$ obligation surface consists of five
finite rows:
\begin{enumerate}
\item carrier: the stream carrier of
\autoref{def:baire-space-stream-carrier};
\item classifier: the prefix-cylinder row comparing displayed unary answers
componentwise over a finite index window;
\item stability: prefix-window transport as in
\autoref{thm:baire-space-prefix-cylinder-stability};
\item exactness: a public observation is readable from the certificate iff it
is one of the finite unary rows listed by the selected prefix window;
\item provenance: downstream reads factor through the displayed $\NatUp$,
$\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ package
rows carried by $p$.
\end{enumerate}
These rows are the complete seed obligation for naming countable stream space
data over BEDC histories.
\end{theorem}
\begin{proof}
The carrier and classifier rows are the first two projections of
\autoref{def:baire-space-stream-carrier}. They expose the scheduled stream
read, the finite index window, and the unary answer rows over that window.

Stability is supplied by
\autoref{thm:baire-space-prefix-cylinder-stability}. Transporting the
schedule, window, answer rows, ledger, and provenance repacks the same finite
prefix surface.

For exactness, inspect the coordinates of the packet. A public observation can
only be read from the prefix ledger $w$ through the classifier row $c$ and the
routes in $l$. The provenance row $p$ names the available consumers but does
not add a second observation channel.
\end{proof}

\begin{theorem}[BaireSpace real-name handoff]
\label{thm:baire-space-real-name-handoff}
Every $\RegSeqRatUp$ or $\RealUp$ consumer of an accepted $\BaireSpaceUp$
packet reads the stream only through finite prefix windows. A regular rational
sequence consumer may read a requested unary index and its scheduled answer
row, and a real-name consumer may combine that finite read with the
$\DyadicRatCoreUp$ provenance named by $p$. Neither consumer receives a
primitive infinite history, a completed real, or an unlogged tail equality.
\end{theorem}
\leanchecked{BEDC.Derived.BaireSpaceUp.BaireSpacePrefixPacket\_real\_name\_handoff\_transport}
\begin{proof}
Project the accepted packet through
\autoref{def:baire-space-stream-carrier}. The stream schedule is present only
through finite request rows, and the answers are the unary histories displayed
in $w$.

A $\RegSeqRatUp$ consumer therefore obtains a finite index request and the
corresponding unary answer row. Transport of that read is controlled by the
prefix-cylinder classifier and the ledger routes.

A $\RealUp$ consumer can additionally use the $\DyadicRatCoreUp$ provenance
named by $p$ when interpreting the finite answer as a dyadic or regular
sequence component. The packet still exposes only the selected prefix rows, so
no completed infinite object is exported.
\end{proof}

\begin{theorem}[BaireSpace Real stream prefix determinacy]
\label{thm:bairespace-real-stream-prefix-determinacy}
Let $B=(s,w,c,l,p)$ and $B'=(s',w',c',l',p')$ be accepted $\BaireSpaceUp$
packets. Suppose their scheduled finite prefix indices agree and the unary
answer rows at each displayed index are paired componentwise by $\hsame$.
Then every $\RegSeqRatUp$ or $\RealUp$ consumer reads the same finite
stream-prefix boundary from $B$ and $B'$.

The determinacy is only for logged finite prefix rows. It does not identify
primitive infinite histories, host sequences, completed reals, or unlogged
tails.
\end{theorem}
\begin{proof}
Apply \autoref{thm:baire-space-prefix-cylinder-stability} to transport the
componentwise unary answer rows through the common scheduled prefix indices.
The transported classifier still reads only the displayed finite window.

Use \autoref{thm:baire-space-prefix-restriction-composition} to compare any
consumer-requested subwindow of the two packets inside the same restricted
prefix. The composed restriction preserves the schedule, answer rows,
classifier, ledger, and provenance rows needed by the consumer.

For $\RegSeqRatUp$ and $\RealUp$ consumers, invoke
\autoref{thm:baire-space-real-name-handoff}. Those consumers receive only the
finite prefix requests and unary answer rows, with the $\DyadicRatCoreUp$
provenance available to the real-name interpretation.

Finally apply \autoref{thm:baire-space-ledger-coverage}. Since the ledger
covers exactly the displayed stream packet, unary answer rows, prefix window,
classifier, $\hsame$ comparisons, $\Cont$ routes, and provenance, there is no
row from which an infinite history, host sequence equality, completed real, or
unlogged tail could distinguish the two reads.
\end{proof}

\begin{theorem}[BaireSpace ledger coverage]
\label{thm:baire-space-ledger-coverage}
For an accepted carrier $B=(s,w,c,l,p)$, the ledger $l$ covers every public
row of the $\BaireSpaceUp$ packet: the $\mathsf{BHist}$ stream packet, the
$\mathsf{UnaryHistory}$ answer rows, the finite prefix window, the
prefix-cylinder classifier, the componentwise $\hsame$ comparisons, the
prefix-restriction $\Cont$ routes, and the package provenance. The ledger
exports no apartness principle, choice functional, host sequence equality, or
real-completeness assertion.
\end{theorem}
\begin{proof}
Read the packet coordinates one by one. The stream schedule $s$, prefix window
$w$, classifier $c$, and provenance $p$ are all named fields of the carrier,
and the ledger $l$ records the comparison and restriction routes among them.

Any public row must be read from one of those fields. Prefix restriction uses
the displayed $\Cont$ route, while equality of observations uses the displayed
componentwise $\hsame$ rows in the cylinder classifier.

The omitted objects would require extra coordinates: an apartness principle,
a choice functional, a host equality on full sequences, or a completeness
theorem for real names. No such coordinate occurs in the carrier, so the
ledger coverage is exactly the listed finite surface.
\end{proof}

\begin{theorem}[BaireSpace cylinder-tail coverage]
\label{thm:baire-space-cylinder-tail-coverage}
Every finite prefix-cylinder consumer read from an accepted $\BaireSpaceUp$
packet factors through the displayed $\StreamNameUp$ schedule, the
prefix-restriction ledger, $\hsame$ transport, $\Cont$ routes, $\mathsf{Pkg}$
provenance, and the $\RealUp$ handoff boundary. The read exposes no completed
infinite sequence, no classical topology, and no choice-selected branch.
\end{theorem}
\begin{proof}
Read the stream carrier of \autoref{def:baire-space-stream-carrier}. Its public
coordinates are the schedule, finite prefix window, prefix-cylinder classifier,
ledger, and provenance rows, so a cylinder-tail consumer begins with a finite
window named by that carrier.

Use \autoref{thm:baire-space-prefix-cylinder-stability} to keep the cylinder
answer stable under displayed prefix reads, and
\autoref{thm:baire-space-prefix-restriction-composition} to compose the
restriction ledger. These steps route the consumer through the same $\hsame$
transport and $\Cont$ paths already recorded in the packet.

The real-facing boundary is exactly the finite handoff of
\autoref{thm:baire-space-real-name-handoff}, and
\autoref{thm:baire-space-ledger-coverage} exhausts the remaining public rows.
No carrier coordinate stores a completed sequence, a topological completion, or
a choice-selected branch, so such data cannot be exported by a prefix-cylinder
read.
\end{proof}

\begin{theorem}[BaireSpace obligation window classifier]
\label{thm:bairespace-obligation-window-classifier}
Every accepted $\BaireSpaceUp$ prefix packet supplies the obligation surface
consisting of the finite $\StreamNameUp$ schedule, $\NatUp$ index rows,
displayed $\UnaryHistory$ answers, prefix-cylinder classifier, componentwise
$\hsame$, prefix-restriction $\Cont$, $\mathsf{Pkg}$ provenance, and consumer
handoff rows for $\RegSeqRatUp$ and $\RealUp$.

The classifier is exhausted by finite windows. It excludes host sequence
equality, choice-selected branches, and classical topology.
\end{theorem}
\begin{proof}
Project the accepted prefix packet through
\autoref{def:baire-space-stream-carrier}. The carrier provides the finite
schedule, index window, displayed unary answers, classifier row, ledger, and
package provenance.

Use \autoref{thm:baire-space-prefix-cylinder-stability} and
\autoref{thm:baire-space-prefix-restriction-composition} to keep every
classifier read inside finite prefix windows under the displayed $\hsame$ and
$\Cont$ rows.

Apply \autoref{thm:baire-space-namecert-obligations} for the local naming
surface, \autoref{thm:baire-space-real-name-handoff} for the
$\RegSeqRatUp/\RealUp$ consumer rows, and \autoref{thm:baire-space-ledger-coverage}
for exhaustion of the public ledger.

Finally, \autoref{thm:baire-space-cylinder-tail-coverage} rules out any tail
read not already listed in the finite cylinder packet. Thus the obligation
surface is exactly the finite window classifier, with no host sequence equality,
choice-selected branch, or classical topology.
\end{proof}

\begin{theorem}[BaireSpace finite cylinder stream boundary]
\label{thm:baire-space-finite-cylinder-stream-boundary}
Every accepted $\BaireSpaceUp$ packet consumed by $\StreamNameUp$,
$\RegSeqRatUp$, or $\RealUp$ is exhausted by the finite schedule, $\NatUp$
index rows, displayed $\UnaryHistory$ answers, prefix-cylinder classifier,
componentwise $\hsame$ rows, $\Cont$ restriction routes, $\mathsf{Pkg}$
provenance, and local $\NameCert_{\BaireSpaceUp}$ ledger. These rows are the
exact finite-cylinder boundary for stream-name, regular-sequence, and
real-facing consumers.

The boundary excludes host sequence equality, infinite tails, classical
topology, choice-selected branches, and completed reals.
\end{theorem}
\begin{proof}
Project the accepted packet through
\autoref{def:baire-space-stream-carrier}. The carrier exposes the finite
$\StreamNameUp$ schedule, $\NatUp$ index rows, displayed unary answers,
prefix-cylinder classifier, transport routes, package provenance, and local
certificate ledger.

Apply \autoref{thm:baire-space-real-name-handoff} to identify the
$\RegSeqRatUp$ and $\RealUp$ consumer rows reached from that schedule. The
handoff uses the same finite prefix-cylinder coordinates and introduces no
completed real or host stream equality.

Use \autoref{thm:baire-space-ledger-coverage} for the remaining package and
certificate rows, and use
\autoref{thm:baire-space-cylinder-tail-coverage} to rule out any read from an
undisplayed infinite tail. The obligation window classifier of
\autoref{thm:bairespace-obligation-window-classifier} then pins the classifier
surface to the same finite window.

Thus every $\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ consumer read is one
of the projected finite-cylinder rows. Since those rows contain no host
sequence equality, infinite tail object, classical topological principle,
choice-selected branch, or completed real, none can appear at the boundary.
\end{proof}

\begin{theorem}[BaireSpace scoped finite-consumer boundary]
\label{thm:bairespace-scoped-finite-consumer-boundary}
Every $\BaireSpaceUp$ consumer read factors through the finite $\StreamNameUp$
schedule, the $\NatUp$ index rows, displayed $\UnaryHistory$ answers, the
prefix-cylinder classifier, componentwise $\hsame$, prefix-restriction $\Cont$,
$\mathsf{Pkg}$ provenance, and the $\RegSeqRatUp$, $\RealUp$, and
$\DyadicRatCoreUp$ handoff rows.

This finite boundary exhausts the scoped public surface. It exposes no host
sequence equality, no choice-selected branch, no completed infinite sequence,
and no classical topology.
\end{theorem}
\begin{proof}
Project the consumer read through the stream carrier of
\autoref{def:baire-space-stream-carrier}. The only displayed coordinates are
the schedule, finite index window, unary answer rows, classifier, transport
ledger, package provenance, and downstream handoff rows.

Apply \autoref{thm:baire-space-prefix-cylinder-stability} to keep the
prefix-cylinder answer stable under displayed finite reads. Then use
\autoref{thm:baire-space-prefix-restriction-composition} to compose the
prefix-restriction $\Cont$ rows along the same componentwise $\hsame$ route.

The real-facing and rational-facing consumer rows are supplied by
\autoref{thm:baire-space-real-name-handoff}. The remaining public coordinates
are exhausted by \autoref{thm:baire-space-ledger-coverage} and by the obligation
window classifier of \autoref{thm:bairespace-obligation-window-classifier}.

Therefore any scoped consumer read is already one of the finite prefix-cylinder
packet reads listed above. Since none of the cited rows constructs a host
sequence equality, a choice branch, a completed infinite sequence, or a
classical topological object, none is available at the scoped boundary.
\end{proof}

\begin{theorem}[BaireSpace public prefix-cylinder certificate]
\label{thm:bairespace-public-prefix-cylinder-certificate}
The stream carrier of \autoref{def:baire-space-stream-carrier}, the obligation
window classifier of \autoref{thm:bairespace-obligation-window-classifier}, and
the finite-consumer boundary of
\autoref{thm:bairespace-scoped-finite-consumer-boundary} export the public
$\NameCert_{\BaireSpaceUp}$ surface for the same prefix-cylinder packet.

That surface consists exactly of the finite $\StreamNameUp$ schedule, the
$\NatUp$ index rows, displayed $\UnaryHistory$ answers, the prefix-cylinder
classifier, componentwise $\hsame$, prefix-restriction $\Cont$,
$\mathsf{Pkg}$ provenance, and the $\RegSeqRatUp$, $\RealUp$, and
$\DyadicRatCoreUp$ handoff rows. It excludes host sequence equality,
choice-selected branches, completed infinite sequences, classical topology,
apartness on Baire space, and real completeness.
\end{theorem}
\begin{proof}
Start with an accepted prefix-cylinder packet and project it through
\autoref{def:baire-space-stream-carrier}. This gives the finite schedule,
index rows, displayed unary answers, classifier coordinate, transport routes,
and package provenance that are available to the public name certificate.

The classifier row is the one identified by
\autoref{thm:bairespace-obligation-window-classifier}. Its finite-window
description is stable under the componentwise $\hsame$ and prefix-restriction
$\Cont$ rows already used by the scoped boundary.

The downstream rows are exactly the rows supplied by
\autoref{thm:baire-space-real-name-handoff}. The remaining ledger coordinates
are exhausted by \autoref{thm:baire-space-ledger-coverage}, while
\autoref{thm:baire-space-cylinder-tail-coverage} prevents a hidden tail read
from entering the packet.

Finally apply \autoref{thm:bairespace-scoped-finite-consumer-boundary}. It
states that every consumer read has already factored through this finite
prefix-cylinder list, so repackaging the same rows as the public
$\NameCert_{\BaireSpaceUp}$ surface adds no host equality, branch selector,
completed sequence, topological principle, Baire-space apartness, or real
completeness field.
\end{proof}

\begin{theorem}[BaireSpace prefix-stream bridge]\label{thm:bairespace-prefix-stream-bridge}
The public prefix-cylinder certificate of
\autoref{thm:bairespace-public-prefix-cylinder-certificate} has a conservative
stream-name reading: every accepted prefix-cylinder read factors through the
displayed $\StreamNameUp$ schedule, $\NatUp$ index rows, unary answer rows,
componentwise $\hsame$, prefix-restriction $\Cont$, $\Pkg$ provenance, and the
$\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ handoff rows. Reading the
stream-name packet back recovers exactly those rows.

The bridge adds no host sequence equality, choice-selected branch, completed
infinite sequence, classical topology, apartness on Baire space, or real
completeness.
\end{theorem}
\leanchecked{BEDC.Derived.BaireSpaceUp.BaireSpaceUp\_StdBridge}
\begin{proof}
Project the public certificate through
\autoref{thm:bairespace-public-prefix-cylinder-certificate}. Its visible rows
are already the finite schedule, finite index window, unary answers,
classifier, componentwise transport, prefix-restriction route, package
provenance, and downstream handoff rows.

Use \autoref{thm:bairespace-scoped-finite-consumer-boundary} to identify every
standard finite-prefix read with one of these displayed packet rows. This
prevents a read of an infinite host sequence or a choice-selected branch from
being inserted into the prefix-cylinder interface.

Apply \autoref{thm:baire-space-cylinder-tail-coverage}. The finite cylinder
tail is already accounted for by the displayed prefix window, so no completed
infinite sequence or hidden tail coordinate enters the readback.

For downstream consumers, apply
\autoref{thm:baire-space-real-name-handoff}. The rational and real-facing
handoffs remain finite prefix reads and do not require real completeness,
classical topology, or a Baire-space apartness principle.

Finally use \autoref{thm:baire-space-ledger-coverage} to exhaust the remaining
ledger rows. Reading the standard finite prefix-cylinder packet back into
$\BaireSpaceUp$ therefore recovers exactly the displayed carrier and handoff
surface, with no additional host equality, branch selector, completed
sequence, topological object, apartness row, or real-completeness row.
\end{proof}

\begin{theorem}[BaireSpace finite prefix-cylinder coverage]
\label{thm:bairespace-finite-prefix-cylinder-coverage}
Every finite stream-name consumer read of a certified $\BaireSpaceUp$ packet
factors through a displayed prefix-cylinder row.

Compatible nested prefix cylinders share a common finite prefix transport
through the same $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local
$\NameCert_{\BaireSpaceUp}$ rows.
\end{theorem}
\begin{proof}
Start with \autoref{thm:baire-space-prefix-cylinder-stability}. It keeps each
accepted finite read inside the displayed prefix-cylinder classifier, finite
$\NatUp$ index rows, unary answer rows, and stream schedule.

For nested cylinders, apply
\autoref{thm:baire-space-prefix-restriction-composition}. The composed
restriction route supplies the common finite prefix transport through the same
$\hsame$, $\Cont$, package, and local certificate rows.

Use \autoref{thm:baire-space-real-name-handoff} for rational and real-facing
consumers. Those reads remain finite stream-name handoffs rather than
completed sequences or real-completeness assumptions.

Finally combine \autoref{thm:bairespace-scoped-finite-consumer-boundary} with
\autoref{thm:bairespace-prefix-stream-bridge}. The scoped boundary exhausts
the finite consumer rows, and the bridge identifies the same rows with the
stream-name presentation, yielding the stated finite prefix-cylinder
coverage.
\end{proof}

\begin{theorem}[BaireSpace StreamName prefix sieve]
\label{thm:bairespace-streamname-prefix-sieve}
Every finite prefix-cylinder read consumed by $\StreamNameUp$, $\RegSeqRatUp$,
or $\RealUp$ factors through the displayed $\StreamNameUp$ schedule, $\NatUp$
index rows, $\mathsf{UnaryHistory}$ answer rows, prefix-cylinder classifier,
componentwise $\hsame$ rows, $\Cont$ restriction routes, $\mathsf{Pkg}$
provenance, and local $\NameCert_{\BaireSpaceUp}$ ledger.

The sieve exports no choice-selected branch, host sequence equality, completed
sequence, or real-completeness row.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:baire-space-prefix-cylinder-stability}. It keeps each
finite observation inside the displayed prefix-cylinder classifier and the
finite $\NatUp$ index and unary answer rows.

Use \autoref{thm:baire-space-prefix-restriction-composition} to compose the
restriction routes. The resulting read still travels through the same
$\StreamNameUp$ schedule, componentwise $\hsame$ rows, $\Cont$ routes, package
provenance, and local naming ledger.

For rational and real consumers, apply
\autoref{thm:baire-space-real-name-handoff}. The $\RegSeqRatUp$ and $\RealUp$
rows are therefore finite prefix reads of the displayed stream schedule rather
than completed host sequences.

Finally invoke \autoref{thm:baire-space-ledger-coverage}. It exhausts the
remaining certificate rows, so no choice-selected branch, host sequence
equality, completed sequence, or real-completeness row is exported.
\end{proof}

\begin{theorem}[BaireSpace finite-prefix consumer completeness]
\label{thm:bairespace-finite-prefix-consumer-completeness}
Every accepted finite consumer of the public prefix-cylinder bridge factors
through one displayed finite prefix window. The window consists exactly of the
$\StreamNameUp$ schedule, $\NatUp$ index rows, unary answer rows, the
prefix-cylinder classifier, componentwise $\hsame$ rows, prefix-restriction
$\Cont$ routes, $\mathsf{Pkg}$ provenance, and the $\RegSeqRatUp$, $\RealUp$,
and $\DyadicRatCoreUp$ handoff rows.

This factorization exports no host sequence equality, choice branch, completed
infinite sequence, apartness row, external topology, or real completeness row.
\end{theorem}
\begin{proof}
Start with the public prefix-cylinder certificate of
\autoref{thm:bairespace-public-prefix-cylinder-certificate}. Its exposed rows
are already the finite schedule, prefix index window, displayed unary answers,
classifier coordinate, componentwise transport, prefix-restriction route,
package provenance, and downstream handoff surface.

Read the same packet through \autoref{thm:bairespace-prefix-stream-bridge}. This
identifies every bridge consumer with the stream-name presentation over the
same finite prefix window, so the consumer has no separate access to a host
sequence or a choice-selected branch.

The remaining coverage is ledger-local. Apply
\autoref{thm:baire-space-ledger-coverage} to exhaust the certificate rows and
\autoref{thm:baire-space-cylinder-tail-coverage} to keep tail information inside
the displayed finite cylinder. No completed infinite sequence or external
topological row is produced.

Finally apply \autoref{thm:baire-space-real-name-handoff}. The
$\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ consumers therefore receive
only the listed handoff rows, not real completeness, apartness on Baire space,
or any additional host equality principle. Hence every accepted finite consumer
factors through the displayed finite prefix window.
\end{proof}

\begin{theorem}[BaireSpace prefix intersection normal form]
\label{thm:bairespace-prefix-intersection-normal-form}
Two compatible finite prefix-cylinder consumers of an accepted
$\BaireSpaceUp$ packet, whose requested $\NatUp$ prefix windows overlap through
displayed $\hsame$ and $\Cont$ routes, factor through one displayed finite
prefix window. The normal-form window carries the $\StreamNameUp$ schedule,
$\NatUp$ index rows, $\mathsf{UnaryHistory}$ answer rows, the prefix-cylinder
classifier, componentwise $\hsame$ rows, $\Cont$ restrictions, $\mathsf{Pkg}$
provenance, and the $\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ handoff
rows.

The intersection read exports no host sequence equality, choice branch,
completed infinite sequence, apartness row, external topology, or
real-completeness row.
\end{theorem}
\begin{proof}
Use \autoref{thm:baire-space-prefix-cylinder-stability} on each consumer. Both
reads remain inside finite prefix-cylinder rows whose schedule, requested
$\NatUp$ indices, unary answers, and prefix classifier are displayed in the
accepted packet.

Apply \autoref{thm:baire-space-prefix-restriction-composition} to the overlap
routes. Compatibility through $\hsame$ and $\Cont$ lets the two requested
windows compose to one finite window carrying the common componentwise
transport, restriction provenance, and $\mathsf{Pkg}$ row.

Read the resulting window through
\autoref{thm:bairespace-prefix-stream-bridge} and
\autoref{thm:bairespace-streamname-prefix-sieve}. These identify the
intersection as a $\StreamNameUp$ schedule read and exhaust the finite prefix
coordinates before any completed host sequence or choice-selected branch can be
formed.

Finally invoke
\autoref{thm:bairespace-finite-prefix-consumer-completeness}. The
$\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ consumers receive only the
listed handoff rows, so the compatible intersection has the stated finite
normal form and exports none of the excluded topology, apartness, or
real-completeness data.
\end{proof}

\begin{theorem}[BaireSpace prefix-cylinder separation]
\label{thm:bairespace-prefix-cylinder-separation}
Let two accepted $\BaireSpaceUp$ prefix packets have a displayed common finite
prefix window. If, at the first listed mismatch in that window, one displayed
$\mathsf{UnaryHistory}$ answer row is not related by the packet classifier to
the corresponding row of the other packet, then the two packets do not classify
together through that prefix-cylinder surface.

Later tail rows, host sequence equality, completed infinite sequences,
external topology, apartness data, and choice-selected branches are irrelevant
to this separation claim.
\end{theorem}
\begin{proof}
Project both packets to their finite prefix-cylinder carriers. The projected
rows are the $\StreamNameUp$ schedule, the $\NatUp$ prefix indices, displayed
$\mathsf{UnaryHistory}$ answers, the prefix classifier, componentwise
$\hsame$ transport, prefix-restriction $\Cont$ routes, package provenance, and
the downstream handoff rows.

Use \autoref{thm:baire-space-prefix-cylinder-stability} on both packets. Every
classifier read that can affect the prefix-cylinder comparison is restricted
to the displayed unary answer rows inside the common finite window.

Apply \autoref{thm:baire-space-prefix-restriction-composition} and
\autoref{thm:bairespace-prefix-intersection-normal-form}. These put the two
packets on one displayed prefix window, with the same visible transport and
restriction provenance, before any later tail coordinate is consulted.

At the first listed mismatch, the classifier row required for joint
classification is absent by hypothesis. The packet carrier has no hidden host
sequence equality, classical topology datum, or tail row that can replace this
displayed classifier coordinate. Hence the two packets cannot classify
together through the prefix-cylinder surface.
\end{proof}

\closureat{BaireSpaceUp}{obligationStr}
\closureat{BaireSpaceUp}{scopedStr}
\closureat{BaireSpaceUp}{publicStr}
\closureat{BaireSpaceUp}{bridgedStr}
\closureat{BaireSpaceUp}{matureStr}

\begin{closurestatus}{\BaireSpaceUp}
  \constructivestory{A $\BaireSpaceUp$ packet is generated by a $\StreamNameUp$ schedule, finite $\NatUp$ prefix-window requests, displayed $\mathsf{UnaryHistory}$ answer rows, a prefix-cylinder classifier, componentwise $\hsame$ comparisons, prefix-restriction $\Cont$ routes, and $\Pkg$ provenance for $\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ consumers.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:bairespace-public-prefix-cylinder-certificate}, \autoref{thm:bairespace-prefix-stream-bridge}, and \autoref{thm:bairespace-streamname-prefix-sieve} close the public prefix-cylinder certificate, stream-name readback, and finite prefix-cylinder consumer completeness surface through the $\StreamNameUp$ schedule, $\NatUp$ index rows, displayed unary answers, prefix-cylinder classifier, componentwise $\hsame$, prefix-restriction $\Cont$, $\mathsf{Pkg}$ provenance, and $\RegSeqRatUp$, $\RealUp$, and $\DyadicRatCoreUp$ handoff rows.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.BaireSpaceUp.BaireSpacePrefixPacket\_real\_name\_handoff\_transport}
  \bridgestatus{bridgeChecked}
  \origin{human}
  \notclaimed{This chapter does not close choice sequences as completed host functions, apartness on Baire space, continuity theorems, real completeness, or an external topology of Baire space.}
  \upgradepath{No further upgrade -- chapter at top of formal axis.}
\end{closurestatus}
