\chapter{A Concrete Naming Certificate for $\MaxRateReadGateUp$}
\label{ch:concrete-instances-maxratereadgate-namecert}
\origin{ai}

The $\MaxRateReadGateUp$ packet is the finite gate between the inter-Hist locality vision of \autoref{ch:visions-inter-hist-locality} and downstream maximum-rate consumers such as $\LorentzFrameRateUp$ and $\InterHistLocalityLedgerUp$. It consumes the unary-bound surface of \autoref{ch:concrete-instances-maxcausalrate-namecert}, but makes the read public only when the same packet also displays observer-symmetry and no-global-frame refusal rows. The gate is therefore not a new rate value, metric geometry, or global reference frame; it is a NameCert boundary that prevents detached maximum-rate reads.

\falsifiablePrediction{An accepted $\MaxRateReadGateUp$ consumer that reads a $\MaxCausalRateUp$ row while omitting either observer-symmetry or no-global-frame refusal refutes the packet.}

\independenceWitness{Nearest siblings: multihistconfig, crosshistcausal, maxcausalrate, observerlocalitycell, interhistinvariant. None is bijective to $\MaxRateReadGateUp$ because each omits either the paired gate requiring both symmetry and no-global-frame refusal or the maximum-rate consumer lock.}

\begin{definition}[MaxRateReadGate carrier]
\label{def:max-rate-read-gate-carrier}
A $\MaxRateReadGateUp$ carrier is a finite $\BHist$ packet
$$
G=(M,R,S,F,L,H,Q,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $M$ is an accepted $\MultiHistConfigUp$ row supplying the finite observer-history configuration and its no-global-sync surface;
\item $R$ is an accepted $\MaxCausalRateUp$ row whose unary-bound surface is being read;
\item $S$ is the observer-symmetry row, recording that the rate read is invariant under swapping the displayed observer-history presentations after componentwise transport;
\item $F$ is the no-global-frame refusal row, recording that the read does not import a privileged observer, synchronized clock, metric tensor, Lorentz frame, or ambient real-valued speed;
\item $L$ is the maximum-rate consumer lock, requiring every public consumer of $R$ to pass through both $S$ and $F$ before it may read the unary-bound row;
\item $H$ records componentwise $\hsame$ transport for $M,R,S,F,L,Q,C,P,N$;
\item $Q$ records $\psame$ stability for the probe reads used by the rate row, symmetry row, refusal row, and consumer lock;
\item $C$ records the displayed $\Cont$ routes from the configuration and rate rows into $S,F,L,H,Q,P,N$;
\item $P$ is the $\Pkg$ provenance over $\MaxRateReadGateUp$, $\MaxCausalRateUp$, $\MultiHistConfigUp$, $\CrossHistCausalUp$, $\ObserverLocalityCellUp$, $\InterHistInvariantUp$, $\BHist$, $\hsame$, $\psame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\MaxRateReadGateUp}$ row.
\end{enumerate}
The carrier exports a finite public read gate for a maximum-rate row. It does not export a detached rate, a host-side numeric speed, a metric structure, a synchronized frame, or an all-observer reference coordinate.
\end{definition}
\leanchecked{BEDC.Derived.MaxRateReadGateUp.MaxRateReadGateTasteGate\_single\_carrier\_alignment}

\begin{theorem}[MaxRateReadGate NameCert obligations]
\label{thm:max-rate-read-gate-namecert-obligations}
For the carrier of \autoref{def:max-rate-read-gate-carrier}, the local $\NameCert_{\MaxRateReadGateUp}$ surface consists exactly of six finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $G=(M,R,S,F,L,H,Q,C,P,N)$;
\item rate-source locality, requiring $R$ to be read as the $\MaxCausalRateUp$ row attached to the same displayed configuration $M$;
\item observer-symmetry exactness, requiring every public rate read to pass through $S$ after componentwise transport;
\item no-global-frame refusal, requiring every public rate read to pass through $F$ before any consumer sees the unary-bound surface;
\item consumer-lock exactness, requiring $L$ to bind the reads of $R,S,F$ into one public gate rather than three independent rows;
\item transport stability and non-escape through $H,Q,C,P,N$, excluding global frames, synchronized clocks, metric tensors, Lorentz frames, host real speeds, and detached maximum-rate reads.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is the projection of the finite tuple in \autoref{def:max-rate-read-gate-carrier}. The rows $M,R,S,F,L,H,Q,C,P,N$ display the configuration, rate row, symmetry row, refusal row, lock, transport, probe stability, route, provenance, and local naming data.

Rate-source locality follows by reading $M$ before $R$. The rate row is not a free-standing numeric surface; it is the $\MaxCausalRateUp$ row already tied to the finite witness-family packet described in \autoref{ch:concrete-instances-maxcausalrate-namecert}.

The public gate is then formed by $S,F,L$. The symmetry row supplies the observer-symmetric read, the refusal row blocks global-frame imports, and the lock row requires both gates before any consumer reads the unary-bound surface.

Transport stability is componentwise through $H,Q,C$. These rows replay the same configuration, rate, symmetry, refusal, and lock data under accepted $\hsame$ and $\psame$ movement.

The non-escape clause is an inventory argument. Since the carrier has no coordinate for a global frame, synchronized clock, metric tensor, Lorentz frame, host real speed, or detached rate row, no local $\NameCert_{\MaxRateReadGateUp}$ projection can export one.
\end{proof}

\begin{theorem}[MaxRateReadGate symmetry and non-escape]
\label{thm:max-rate-read-gate-symmetry-nonescape}
Every public consumer of an accepted $\MaxRateReadGateUp$ carrier
$$
G=(M,R,S,F,L,H,Q,C,P,N)
$$
may read the $\MaxCausalRateUp$ row $R$ only through the observer-symmetry row $S$, the no-global-frame refusal row $F$, and the maximum-rate consumer lock $L$. Swapping the displayed observer-history presentations preserves the public read after transport through $H,Q,C$, and no consumer receives a global frame, synchronized clock, metric tensor, Lorentz frame, host real-valued speed, or detached rate row.
\end{theorem}
\leanchecked{BEDC.Derived.MaxRateReadGateUp.MaxRateReadGateCarrier\_symmetry\_nonescape}
\begin{proof}
Start with the accepted carrier and project $M$ and $R$. The configuration row $M$ supplies the finite observer-history surface, while $R$ supplies the maximum causal-rate row already bounded inside that surface.

Apply the observer-symmetry row $S$. It records that the public rate read is invariant under swapping the displayed observer-history presentations after replaying the componentwise transport data.

Next apply the no-global-frame refusal row $F$. This blocks any attempt to interpret the rate read as a privileged observer frame, synchronized clock, metric tensor, Lorentz frame, or ambient numeric speed.

Finally apply the consumer lock $L$ and route the read through $H,Q,C,P,N$. The lock binds $R,S,F$ into one public gate, so a consumer that omits either symmetry or refusal leaves the $\MaxRateReadGateUp$ surface.
\end{proof}

\begin{theorem}[MaxRateReadGate downstream consumer boundary]
\label{thm:max-rate-read-gate-downstream-consumer-boundary}
A $\LorentzFrameRateUp$, $\InterHistLocalityLedgerUp$, or other maximum-rate consumer may use an accepted $\MaxRateReadGateUp$ packet only as the finite gated surface
$$
M,R,S,F,L,H,Q,C,P,N.
$$
The consumer may inspect the multi-Hist configuration row, the $\MaxCausalRateUp$ row, the observer-symmetry row, the no-global-frame refusal row, the consumer lock, componentwise transport, probe stability, displayed continuation routes, provenance, and local naming data. It may not bypass the gate to obtain a free rate value or a global reference frame.
\end{theorem}
\begin{proof}
Read the carrier rows listed in \autoref{def:max-rate-read-gate-carrier}. The only maximum-rate input is $R$, and the only public path to $R$ goes through $S,F,L$.

Use \autoref{thm:max-rate-read-gate-namecert-obligations} to bind those rows as the local NameCert surface. The obligations make rate-source locality, symmetry, refusal, and lock exactness part of one packet.

Then use \autoref{thm:max-rate-read-gate-symmetry-nonescape}. It preserves the read under observer swap and excludes every detached global-frame or numeric-rate export.

Thus downstream consumers receive a finite gate rather than a rate primitive. Any consumer that asks for a read of $R$ without $S$ and $F$ is outside the displayed packet.
\end{proof}

\begin{theorem}[MaxRateReadGate CrossHistCausalRate handoff]
\label{thm:max-rate-read-gate-cross-hist-causal-rate-handoff}
Every $\CrossHistCausalRateUp$ consumer of an accepted $\MaxRateReadGateUp$ packet reads the maximum-rate row only through
$$
M,R,S,F,L,H,Q,C,P,N.
$$
The row $R$ is tied to the $\MaxCausalRateUp$ surface of \autoref{ch:concrete-instances-maxcausalrate-namecert}, $S$ is the observer-symmetry row, $F$ is the no-global-frame refusal row, and $L$ is the consumer lock. The handoff to \autoref{ch:concrete-instances-crosshistcausalrate-namecert} therefore exports a gated maximum-rate boundary rather than a detached rate value, host speed, metric row, clock, or global observer frame.
\end{theorem}
\begin{proof}
Apply \autoref{thm:max-rate-read-gate-namecert-obligations}. It binds the carrier rows $M,R,S,F,L,H,Q,C,P,N$ into one local NameCert surface and makes rate-source locality part of the packet.

Next apply \autoref{thm:max-rate-read-gate-symmetry-nonescape}. This forces every public read of $R$ to pass through the observer-symmetry row $S$, the no-global-frame refusal row $F$, and the lock row $L$.

Finally apply \autoref{thm:max-rate-read-gate-downstream-consumer-boundary}. A $\CrossHistCausalRateUp$ consumer is one of the maximum-rate consumers that receives the finite gate, so its handoff reads the same ten rows and no detached global-frame or numeric-rate surface.
\end{proof}

\begin{theorem}[MaxRateReadGate NameCert package]
\label{thm:max-rate-read-gate-namecert-package}
The carrier, local NameCert obligations, symmetry-and-non-escape theorem, and downstream consumer boundary assemble the concrete $\NameCert_{\MaxRateReadGateUp}$ package over $\MultiHistConfigUp$, $\MaxCausalRateUp$, $\CrossHistCausalUp$, $\ObserverLocalityCellUp$, $\InterHistInvariantUp$, $\BHist$, $\hsame$, $\psame$, $\Cont$, $\Pkg$, and $\NameCert$. The package is ready for a Lean realization whose gate file provides \texttt{Nontrivial MaxRateReadGateUp} and \texttt{FieldFaithful MaxRateReadGateUp} instances in \texttt{lean4/BEDC/Derived/MaxRateReadGateUp/TasteGate.lean}, with the canonical declaration surface expected at \texttt{BEDC.Derived.MaxRateReadGateUp.taste\_gate}.
\end{theorem}
\begin{proof}
Begin with the carrier definition. It fixes the ten visible rows and names the $\MaxCausalRateUp$ source of the rate read.

Add the NameCert obligations. They require locality against $M$, observer symmetry through $S$, no-global-frame refusal through $F$, consumer locking through $L$, and transport through $H,Q,C,P,N$.

The symmetry-and-non-escape theorem and downstream boundary then exhaust the public consumer surface. Together they make the package finite, falsifiable, and separated from the sibling packets that supply only configuration, causal witnesses, raw maximum-rate bounds, locality cells, or invariant readback rows.
\end{proof}

\closureat{MaxRateReadGateUp}{seedStr}

\begin{closurestatus}{\MaxRateReadGateUp}
  \constructivestory{A $\MaxRateReadGateUp$ packet is generated from a $\MultiHistConfigUp$ row, a $\MaxCausalRateUp$ row, an observer-symmetry row, a no-global-frame refusal row, a maximum-rate consumer lock, componentwise $\hsame$ transports, $\psame$ probe stability, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:max-rate-read-gate-carrier}, \autoref{thm:max-rate-read-gate-namecert-obligations}, \autoref{thm:max-rate-read-gate-symmetry-nonescape}, and \autoref{thm:max-rate-read-gate-namecert-package} bind the finite maximum-rate read gate with observer symmetry, no-global-frame refusal, consumer locking, and local NameCert packaging.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, global frames, metric tensors, Lorentz frames, host real speeds, detached maximum-rate values, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, rate-source locality, observer-symmetry exactness, no-global-frame refusal, consumer-lock exactness, transport stability, and non-escape for the same finite packet.}
\end{closurestatus}
