\chapter{A Trust Manifest Surface for $\CellularTrustSubstrateUp$}
\label{ch:concrete-instances-cellular-trust-substrate-namecert}
\origin{ai}

The $\CellularTrustSubstrateUp$ surface realizes the cellular trust substrate of \autoref{def:cellular-trust-substrate} as a finite NameCert packet. It is not merely a cellular-rule carrier: it binds the local transition table, the orbit window, the classifier, the manifest row, and the audit route into one closed observation surface. The resulting packet gives later Rule 110 and no-induction arguments a concrete certificate object to cite instead of a narrative-only substrate.

The trust substrate consumes the local rule and finite orbit discipline of \autoref{ch:concrete-instances-cellularautomaton-namecert} and the bounded trace boundary of \autoref{ch:concrete-instances-bounded-universal-trace-namecert} before its manifest and audit rows are public. Those sibling surfaces supply the displayed cellular evolution and step-indexed trace limit, while this packet records the additional trust manifest and replay route.

The packet consumes the local substrate carrier of \autoref{ch:concrete-instances-cellularsubstrate-namecert} and the finite local read boundary of \autoref{ch:concrete-instances-localitycell-namecert}. Its trust rows add manifest and audit-route accountability on top of those sibling surfaces, so an accepted read must first expose the cellular carrier and local boundary before the manifest and replay rows can certify the trusted substrate packet.

\falsifiablePrediction{Removing the local-rule row permits two orbit windows with different update tables to classify as the same substrate packet; removing the manifest row prevents a finite audit replay from reconstructing the displayed observation boundary.}

\independenceWitness{Nearest siblings: localitycell, continuationautomaton, haltingdistinction, continuationbigstep, and groundcompilereventflowauditroute. None is bijective to the cellular trust substrate because those siblings omit either the fixed local transition table, the orbit-window manifest row, or the closed substrate observation boundary.}

\begin{definition}[Cellular trust substrate carrier]
\label{def:cellular-trust-substrate-carrier}
A $\CellularTrustSubstrateUp$ carrier is a finite $\BHist$ packet
$$
S=(R,W,K,M,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the local cellular rule row, including the finite alphabet, neighbourhood arity, boundary convention, and complete transition table;
\item $W$ is the orbit-window row, consisting of the initial configuration, the finite time interval, and the displayed cell coordinates accepted for observation;
\item $K$ is the classifier row assigning finite substrate tags to windows generated by $R$ on $W$;
\item $M$ is the manifest row recording the text-format schema, expected read fields, replay bounds, and admitted observation boundary;
\item $A$ is the audit-route row replaying the finite generation of each displayed orbit window and each classifier decision;
\item $H$ records componentwise $\hsame$ transports for $R,W,K,M,A,P,N$;
\item $C$ records displayed $\Cont$ routes through the local rule, orbit window, classifier, manifest, and audit route;
\item $P$ is the $\Pkg$ provenance over $\CellularTrustSubstrateUp$, \autoref{def:cellular-trust-substrate}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\CellularTrustSubstrateUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only by the displayed rule table, orbit window, substrate classifier, manifest, audit route, transport rows, continuation routes, provenance, and naming row. It has no coordinate for an unbounded orbit, host evaluator identity, hidden update table, detached manifest schema, quotient stream equality, or external induction principle.
\end{definition}
\leandef{BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrateUp}

\begin{theorem}[Cellular trust substrate obligation surface]
\label{thm:cellular-trust-substrate-obligation-surface}
For the carrier of \autoref{def:cellular-trust-substrate-carrier}, the local $\NameCert_{\CellularTrustSubstrateUp}$ surface consists exactly of carrier exposure for $S=(R,W,K,M,A,H,C,P,N)$, local-rule accountability through $R$, orbit-window exposure through $W$, classifier accountability through $K$, manifest replay through $M$, finite audit routing through $A$, componentwise stability through $H$, displayed continuation through $C$, package provenance through $P$, and local naming through $N$. No consumer can read a cellular trust substrate, a Rule 110 substrate, a closed observation boundary, or a no-induction substrate premise as $\CellularTrustSubstrateUp$ evidence without passing through these rows.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:cellular-trust-substrate-carrier}. The packet displays the rule table, orbit window, classifier, manifest, audit route, transports, continuation routes, provenance, and local naming row as its only coordinates.

Local-rule, orbit-window, classifier, manifest, and audit accountability are read from $R,W,K,M,A$. The rule row decides the next state locally; the orbit-window row states the finite observation domain; the classifier row names only windows generated inside that domain; the manifest row states the replay schema; and the audit row records the finite route by which each accepted read is recovered.

The remaining rows close the NameCert surface. The $H,C,P,N$ rows transport, replay, record, and name exactly the displayed packet. Since the carrier lacks coordinates for unbounded orbit access, hidden update tables, detached manifests, quotient streams, host evaluator identity, and external induction, the listed rows exhaust the public obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrate\_obligation\_surface}

\begin{theorem}[Local-rule nonescape]
\label{thm:cellular-trust-substrate-local-rule-nonescape}
Every accepted classifier read exported by a $\CellularTrustSubstrateUp$ carrier factors through the displayed local rule row $R$ and the finite orbit-window row $W$. In particular, two packets whose accepted evidence differs only by a hidden update table, a host evaluator, or an unstated boundary convention cannot be classified as the same cellular trust substrate packet.
\end{theorem}
\begin{proof}
Begin with the accepted-read route. By \autoref{thm:cellular-trust-substrate-obligation-surface}, a classifier read reaches the local NameCert row only through $R,W,K,M,A,H,C,P,N$.

The row $R$ supplies the complete local update table and boundary convention, while $W$ supplies the initial configuration and finite observation domain. The classifier row $K$ has no independent transition semantics; it can only tag windows admitted by the route from $R$ through $W$.

Thus changing the update table, host evaluator, or boundary convention without changing the displayed $R$ row is not a move inside the carrier. Since the packet has no hidden coordinate from which such a change can be recovered, the accepted classifier cannot identify the two displays as the same substrate evidence.
\end{proof}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrate\_local\_rule\_window\_classifier\_reflect\_display}

\begin{theorem}[Orbit observation boundary]
\label{thm:cellular-trust-substrate-orbit-observation-boundary}
Every closed observation exported by a $\CellularTrustSubstrateUp$ carrier is bounded by the manifest row $M$ and replayed by the audit-route row $A$. Consequently, a consumer obtains a finite observation boundary for the displayed orbit window, not an unbounded orbit, a stream quotient, or an internal induction rule over all cellular times.
\end{theorem}
\begin{proof}
The manifest row $M$ states the accepted text-format schema, replay bounds, and observation boundary. The audit-route row $A$ then replays each displayed orbit-window and classifier read against that schema.

Apply \autoref{thm:cellular-trust-substrate-obligation-surface}. A closed observation is accepted as $\CellularTrustSubstrateUp$ evidence only when the route through $M$ and $A$ reaches the local naming row $N$.

It follows that the exported boundary is finite and displayed. The carrier has no coordinate for an all-time orbit, quotient stream representative, or induction rule over cellular time, so no such object is obtained by consuming the packet.
\end{proof}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrate\_orbit\_observation\_boundary}

\begin{theorem}[Cellular trust substrate obligation closure]
\label{thm:cellular-trust-substrate-obligation-closure}
The carrier of \autoref{def:cellular-trust-substrate-carrier}, the local-rule nonescape theorem \autoref{thm:cellular-trust-substrate-local-rule-nonescape}, the orbit observation boundary theorem \autoref{thm:cellular-trust-substrate-orbit-observation-boundary}, the falsifiable prediction, the independence witness, and the Lean TasteGate single-carrier alignment together supply the obligation-closure surface for $\CellularTrustSubstrateUp$. The closed surface is the finite route through $R,W,K,M,A,H,C,P,N$, with no claim of Rule 110 universality, host evaluator correctness, quotient stream equality, cellular completeness, or internal induction.
\end{theorem}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrateTasteGate\_single\_carrier\_alignment}
\begin{proof}
The carrier displays the complete local-rule, orbit-window, classifier, manifest, audit-route, transport, continuation, provenance, and naming rows. The local-rule nonescape theorem forces classifier reads through $R$ and $W$, and the orbit observation boundary theorem forces closed observations through $M$ and $A$.

The falsifiable prediction identifies the two row removals that would break the route, while the independence witness separates this carrier from nearby cellular and continuation packets. The Lean TasteGate alignment supplies the checked single-carrier evidence that the displayed packet has the intended TasteGate carrier shape.

Together these ingredients exhaust the obligation surface named by \autoref{thm:cellular-trust-substrate-obligation-surface}. Since the packet still lacks coordinates for universality, host evaluator semantics, quotient streams, cellular completeness, and induction over all times, obligation closure stops at the displayed BEDC rows.
\end{proof}

\begin{theorem}[Cellular trust substrate primitive scope binding]
\label{thm:cellular-trust-substrate-primitive-scope-binding}
For every accepted $\CellularTrustSubstrateUp$ carrier $S=(R,W,K,M,A,H,C,P,N)$, the rows $R,W,K,M,A,H,C,P,N$ bind only to the BEDC primitive surface $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. In particular, $R,W,K,M,A$ are finite $\BHist$ rows, $H$ is their componentwise $\hsame$ transport, $C$ is their displayed $\Cont$ route, $P$ is their $\Pkg$ provenance, and $N$ is the local $\NameCert_{\CellularTrustSubstrateUp}$ row.
\end{theorem}
\begin{proof}
Start from the obligation surface of \autoref{thm:cellular-trust-substrate-obligation-surface}. It lists the complete carrier admission route for $S=(R,W,K,M,A,H,C,P,N)$ and names no primitive outside $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Local-rule nonescape forces every classifier read through the displayed $R$ and $W$ rows. Orbit observation boundary forces every closed observation through the finite manifest and audit rows $M$ and $A$.

The checked TasteGate single-carrier alignment cited at \autoref{thm:cellular-trust-substrate-obligation-closure} confirms that the displayed carrier shape is the aligned cellular trust substrate shape. Hence the primitive bindings are exactly the listed BEDC rows, with no host evaluator, quotient stream, or induction principle added by the packet.
\end{proof}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.CellularTrustSubstrate\_primitive\_scope\_binding}

\begin{theorem}[Cellular trust substrate sibling scope binding]
\label{thm:cellular-trust-substrate-sibling-scope-binding}
For every accepted $\CellularTrustSubstrateUp$ carrier $S=(R,W,K,M,A,H,C,P,N)$, the same rows bind the packet to the sibling surfaces $\CellularAutomatonUp$, $\BoundedUniversalTraceUp$, $\CellularSubstrateUp$, and $\LocalityCellUp$. The rule and orbit rows consume the cellular automaton and bounded trace surfaces, while the classifier, manifest, audit, transport, route, provenance, and naming rows expose only the local substrate and locality-cell boundaries needed by downstream cellular trust consumers.
\end{theorem}
\begin{proof}
The opening dependency paragraphs place $\CellularTrustSubstrateUp$ after the local rule and finite orbit discipline of $\CellularAutomatonUp$ and $\BoundedUniversalTraceUp$, and after the local substrate and local read boundaries of $\CellularSubstrateUp$ and $\LocalityCellUp$.

Apply local-rule nonescape. The accepted classifier route cannot pass around $R$ and $W$, so the cellular automaton and bounded trace rows are sibling inputs rather than optional explanatory context.

Apply orbit observation boundary. The manifest row $M$ and audit row $A$ bound every closed observation before it is exported, and $H,C,P,N$ keep the same route transported, replayed, packaged, and named.

Finally use the obligation closure theorem together with the checked TasteGate single-carrier alignment cited at \autoref{thm:cellular-trust-substrate-obligation-closure}. They identify the accepted sibling scope as the displayed finite route and exclude Rule 110 universality, host evaluator correctness, quotient stream equality, cellular completeness, and all-time induction from the binding.
\end{proof}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.CellularTrustSubstrate\_sibling\_scope\_binding}

The Lean TasteGate namespace $\mathsf{BEDC.Derived.CellularTrustSubstrateUp.TasteGate}$ must provide $\mathsf{Nontrivial}\ \mathsf{CellularTrustSubstrateUp}$ and $\mathsf{FieldFaithful}\ \mathsf{CellularTrustSubstrateUp}$ instances for the displayed carrier, while $\mathsf{BEDC.Derived.CellularTrustSubstrateUp.taste\_gate}$ records the chapter-level TasteGate instance.

\begin{theorem}[Cellular trust substrate public export package]
\label{thm:cellular-trust-substrate-public-export-package}
Every public consumer of an accepted $\CellularTrustSubstrateUp$ packet $S=(R,W,K,M,A,H,C,P,N)$ receives exactly the local-rule row, finite orbit-window row, classifier row, manifest row, audit route, componentwise transport, continuation route, provenance, and local \NameCert{} row. This public package is routed through $\CellularAutomatonUp$, $\BoundedUniversalTraceUp$, $\CellularSubstrateUp$, and $\LocalityCellUp$, and it carries no Rule 110 universality, host evaluator correctness, quotient stream equality, cellular completeness, or all-time induction.
\end{theorem}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.CellularTrustSubstrate\_public\_export\_package}
\begin{proof}
Start from the obligation surface. It exposes the local rule, orbit window, classifier, manifest, audit route, transport, continuation, provenance, and local naming rows as the complete accepted packet.

Use local-rule nonescape and orbit observation boundary. They force classifier reads through $R,W$ and closed observation reads through $M,A$, excluding hidden update tables, host evaluators, unbounded orbits, quotient streams, and induction over all cellular times.

Apply primitive scope binding and sibling scope binding. The primitive route is confined to $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, while the sibling route passes through $\CellularAutomatonUp$, $\BoundedUniversalTraceUp$, $\CellularSubstrateUp$, and $\LocalityCellUp$.

Finally use the obligation closure theorem and its TasteGate alignment marker. They identify the displayed carrier shape as the aligned single-carrier surface, so a public consumer receives exactly the listed packet and no Rule 110 universality, host evaluator correctness, quotient stream equality, cellular completeness, or all-time induction.
\end{proof}

\begin{theorem}[Cellular trust substrate bridge-scope package]
\label{thm:cellular-trust-substrate-bridge-scope-package}
Any bridge-scope consumer of an accepted $\CellularTrustSubstrateUp$ packet must preserve the local-rule row, orbit-window row, classifier row, manifest row, audit route, componentwise $\hsame$ transport, displayed $\Cont$ route, $\Pkg$ provenance, local $\NameCert$ row, falsifiable prediction, independence witness, and TasteGate alignment marker. The bridge-scope package carries no Rule 110 universality, host evaluator correctness, quotient stream equality, cellular completeness, hidden global orbit, or all-time induction principle.
\end{theorem}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.CellularTrustSubstrate\_bridge\_scope\_package}
\begin{proof}
Start from the public export theorem. It gives every public consumer exactly the local rule, orbit window, classifier, manifest, audit route, transport, continuation, provenance, and local naming rows.

Apply primitive scope binding. The public rows are bound to $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, so the bridge-scope consumer cannot add a host evaluator, quotient stream representative, or induction principle.

Next apply sibling scope binding. It keeps the route attached to $\CellularAutomatonUp$, $\BoundedUniversalTraceUp$, $\CellularSubstrateUp$, and $\LocalityCellUp$, which supplies the local-rule, finite-orbit, classifier, manifest, audit, prediction, and independence surface used by the bridge.

Finally use obligation closure and the TasteGate alignment marker. They identify the displayed carrier as the accepted cellular trust substrate packet, so the bridge-scope consumer preserves the stated rows without importing Rule 110 universality, cellular completeness, or hidden all-time behavior.
\end{proof}

\begin{theorem}[Cellular trust substrate mature route completeness]
\label{thm:cellular-trust-substrate-mature-route-completeness}
For every accepted $\CellularTrustSubstrateUp$ packet $S=(R,W,K,M,A,H,C,P,N)$,
the local-rule row, orbit-window row, classifier row, manifest row, audit
route, primitive scope, sibling scope, public export package, and bridge-scope
package exhaust all mature public reads of the packet. A mature consumer can
only preserve the finite route through $R,W,K,M,A,H,C,P,N$, together with the
TasteGate single-carrier alignment marker; it receives no Rule 110
universality, host evaluator correctness, quotient stream equality, cellular
completeness, hidden global orbit, or all-time induction principle.
\end{theorem}
\begin{proof}
Start from the obligation surface and the obligation closure theorem. They
display exactly the carrier rows $R,W,K,M,A,H,C,P,N$ and identify the
TasteGate single-carrier alignment as the checked carrier-shape evidence for
the packet.

The route constraints are then supplied in layers. Local-rule nonescape forces
classifier reads through $R$ and $W$, while orbit observation boundary forces
closed observations through the manifest row $M$ and audit route $A$.

Next apply primitive scope binding and sibling scope binding. These results
bind the same route to $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and to
the sibling surfaces $\CellularAutomatonUp$, $\BoundedUniversalTraceUp$,
$\CellularSubstrateUp$, and $\LocalityCellUp$, without adding a host evaluator
or an all-time cellular principle.

Finally use the public export package and bridge-scope package. The public
package exposes exactly the listed rows, and the bridge-scope package
preserves the same rows across bridge-facing reads. Therefore the mature
public surface has no remaining paper-side coordinate beyond the displayed
finite route and the TasteGate alignment marker.
\end{proof}
\leanchecked{BEDC.Derived.CellularTrustSubstrateUp.CellularTrustSubstrate\_mature\_route\_completeness}

\closureat{CellularTrustSubstrateUp}{seedStr}
\closureat{CellularTrustSubstrateUp}{scopedStr}[BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrateTasteGate\_single\_carrier\_alignment]
\closureat{CellularTrustSubstrateUp}{publicStr}[BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrateTasteGate\_single\_carrier\_alignment]
\closureat{CellularTrustSubstrateUp}{bridgedStr}[BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrateTasteGate\_single\_carrier\_alignment]
\closureat{CellularTrustSubstrateUp}{matureStr}[BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrateTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\CellularTrustSubstrateUp}
  \constructivestory{A $\CellularTrustSubstrateUp$ packet is generated from the displayed local rule, finite orbit window, classifier, manifest, audit route, componentwise transport, continuation route, package provenance, and local naming rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The carrier, obligation surface, falsifiable prediction, independence witness, and TasteGate alignment marker bind the finite $R,W,K,M,A,H,C,P,N$ cellular trust route.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.CellularTrustSubstrateUp.TasteGate.CellularTrustSubstrateTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Rule 110 universality, host evaluator correctness, quotient streams, cellular completeness, or all-time induction.}
  \upgradepath{Obligation and public closure require only the displayed carrier rows, local-rule route, orbit boundary, manifest, audit route, transport, replay, provenance, and naming data.}
\end{closurestatus}
