\chapter{A Concrete Naming Certificate for $\ClosureUniversalityQuadrantUp$}
\label{ch:concrete-instances-closureuniversalityquadrant-namecert}
\origin{ai}

The $\ClosureUniversalityQuadrantUp$ packet realizes the two-axis map of \autoref{ch:visions-closure-universality-quadrant} as an atomic finite $\NameCert$ carrier whose first public read is the closure coordinate and whose second public read is the universality coordinate. It sits beside the cellular rule-table surface of \autoref{ch:concrete-instances-cellularautomaton-namecert}, the closed cellular-carrier surface of \autoref{ch:concrete-instances-cellularsubstrate-namecert}, the finite diagonal trace of \autoref{ch:concrete-instances-haltingdistinctiontrace-namecert}, and the fixed-point frontier of \autoref{ch:concrete-instances-haltingdiagonal-namecert}. The packet is not a duplicate of any one sibling: it records the quadrant row and the exclusion-ledger row through which consumers keep closure evidence and universality evidence distinct.

\falsifiablePrediction{Any accepted quadrant consumer that reads a closed-substrate consequence without the displayed closure-axis row is outside the certificate.}

\independenceWitness{cellularautomaton, cellularsubstrate, haltingdistinctiontrace, haltingdiagonal: none is bijective because $\ClosureUniversalityQuadrantUp$ carries a dedicated two-axis quadrant row and an exclusion-ledger row. The cellularautomaton packet has a rule table and orbit ledger but no quadrant ledger, the cellularsubstrate packet has a closed carrier route but no universality coordinate, the haltingdistinctiontrace packet has a finite diagonal distinction trace but no closure-axis certificate, and the haltingdiagonal packet has fixed-point obstruction rows rather than a closure-universality classifier.}

\begin{definition}[Closure-universality quadrant carrier]
\label{def:closure-universality-quadrant-carrier}
A $\ClosureUniversalityQuadrantUp$ carrier is a finite $\BHist$ packet
$$
Q=(S,K,U,G,X,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the substrate-name row, drawn from a finite BEDC substrate surface such as $\CellularAutomatonUp$, $\CellularSubstrateUp$, $\HaltingDistinctionTraceUp$, or $\HaltingDiagonalUp$;
\item $K$ is the closure-axis row, recording whether the consumer is reading a closed substrate consequence, an open observation channel, or an explicit refusal of closure;
\item $U$ is the universality-axis row, recording whether the same substrate row is read as universal, subuniversal, diagonal-only, or explicitly outside the universality claim;
\item $G$ is the quadrant row determined by the displayed ordered pair $(K,U)$;
\item $X$ is the exclusion-ledger row, recording the forbidden conversions between closed substrate evidence, universality evidence, diagonal trace evidence, halting obstruction evidence, and host-level semantic claims;
\item $H$ records componentwise $\hsame$ transports for $S,K,U,G,X,P,N$;
\item $C$ records displayed $\Cont$ routes that replay the closure-axis read, the universality-axis read, the quadrant read, and the exclusion-ledger read;
\item $P$ is the $\Pkg$ provenance over $\ClosureUniversalityQuadrantUp$, \autoref{ch:visions-closure-universality-quadrant}, the four sibling concrete instances, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ClosureUniversalityQuadrantUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,K,U,G,X,H,C,P,N$. It has no coordinate that derives universality from closure, derives closure from universality, upgrades a finite diagonal trace to a universal substrate, or reads a halting diagonal obstruction as a closed cellular carrier.
\end{definition}

\begin{definition}[Closure-universality quadrant classifier]
\label{def:closure-universality-quadrant-classifier}
For the carrier of \autoref{def:closure-universality-quadrant-carrier}, the local quadrant classifier is the finite read
$$
\mathsf{Quad}(Q)=(K,U,G,X).
$$
It accepts a packet only when $G$ is the displayed quadrant row for the ordered pair $(K,U)$ and $X$ records the forbidden cross-axis conversions. A consumer that sees $G$ without $K$, without $U$, or without $X$ has not read a $\ClosureUniversalityQuadrantUp$ certificate.
\end{definition}

\begin{theorem}[Closure-universality quadrant certificate surface]
\label{thm:closure-universality-quadrant-certificate-surface}
For an accepted $\ClosureUniversalityQuadrantUp$ carrier $Q=(S,K,U,G,X,H,C,P,N)$, the local $\NameCert_{\ClosureUniversalityQuadrantUp}$ surface consists exactly of carrier exposure, closure-axis accountability through $K$, universality-axis accountability through $U$, quadrant accountability through $G$, exclusion-ledger accountability through $X$, componentwise transport through $H$, displayed replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier by \autoref{def:closure-universality-quadrant-carrier}. The rows $S,K,U,G,X,H,C,P,N$ are the whole displayed $\BHist$ packet.

Apply the classifier of \autoref{def:closure-universality-quadrant-classifier}. It reads the closure row, universality row, quadrant row, and exclusion ledger as one finite surface, so a consumer cannot cite the quadrant while omitting the closure-axis or exclusion rows.

The sibling anchors supply only their own rows. $\CellularAutomatonUp$ supplies cellular rule and orbit data, $\CellularSubstrateUp$ supplies a closed substrate route, $\HaltingDistinctionTraceUp$ supplies a finite distinction trace, and $\HaltingDiagonalUp$ supplies a fixed-point obstruction frontier. The packet packages those possible sources through $P$ and $N$ without identifying their classifiers.
\end{proof}

\begin{theorem}[Closure-universality axis-independence boundary]
\label{thm:closure-universality-quadrant-axis-independence-boundary}
In an accepted $\ClosureUniversalityQuadrantUp$ packet, neither the closure-axis row $K$ nor the universality-axis row $U$ determines the other. The quadrant row $G$ is accepted only as the displayed ordered-pair read $(K,U)$, and the exclusion ledger $X$ records that closure evidence, universality evidence, finite halting-distinction evidence, and halting-diagonal obstruction evidence are not interchangeable.
\end{theorem}
\begin{proof}
Read $K$ and $U$ as distinct carrier coordinates. The closure-axis row records closed-substrate eligibility or its refusal, while the universality-axis row records universality eligibility or its refusal.

Use the classifier surface from \autoref{def:closure-universality-quadrant-classifier}. The quadrant row is a read of the ordered pair $(K,U)$ together with $X$, not a projection from one axis alone.

The exclusion ledger gives the boundary cases. Cellular closed-substrate rows may support $K$ without supplying $U$, cellular universality rows may support $U$ without closing every observation channel, finite distinction traces remain trace evidence rather than universality evidence, and halting-diagonal rows remain obstruction evidence rather than closed-substrate evidence. Hence the axes stay independent at the NameCert surface.
\end{proof}

\begin{theorem}[Closure-universality closed-substrate nonescape]
\label{thm:closure-universality-quadrant-closed-substrate-nonescape}
Every closed-substrate consequence exported by an accepted $\ClosureUniversalityQuadrantUp$ packet factors through
$$
S,K,U,G,X,H,C,P,N .
$$
It cannot escape through a bare cellular rule table, a cellular carrier row without $K$, a finite halting-distinction trace, a halting-diagonal obstruction, a host semantic equality, a quotient substrate equality, or a hidden theorem outside the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:closure-universality-quadrant-certificate-surface}. Any public read of the packet must project the displayed carrier rows and then pass through the local naming surface.

For a closed-substrate consequence, the route must include the closure-axis row $K$. The route also includes $U,G,X$ because the packet certifies a quadrant location, not merely a closed carrier row.

Finally apply the axis boundary of \autoref{thm:closure-universality-quadrant-axis-independence-boundary}. The exclusion ledger blocks the escape routes through bare cellular automation, closed cellular substrate, finite halting distinction, halting diagonal obstruction, host equality, quotient equality, and hidden theorem rows. The remaining route is exactly the displayed finite packet.
\end{proof}

The Lean file \texttt{BEDC/Derived/ClosureUniversalityQuadrantUp/TasteGate.lean} must provide \texttt{Nontrivial ClosureUniversalityQuadrantUp} and \texttt{FieldFaithful ClosureUniversalityQuadrantUp} instances for this carrier, with fields preserving the closure-axis row, universality-axis row, quadrant row, exclusion-ledger row, transport row, continuation row, package provenance, and local naming row.

\closureat{ClosureUniversalityQuadrantUp}{seedStr}

\begin{closurestatus}{\ClosureUniversalityQuadrantUp}
  \constructivestory{A $\ClosureUniversalityQuadrantUp$ packet is generated from a finite substrate row, closure-axis row, universality-axis row, quadrant row, exclusion-ledger row, componentwise hsame transports, displayed continuation routes, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:closure-universality-quadrant-carrier}, \autoref{def:closure-universality-quadrant-classifier}, \autoref{thm:closure-universality-quadrant-certificate-surface}, \autoref{thm:closure-universality-quadrant-axis-independence-boundary}, and \autoref{thm:closure-universality-quadrant-closed-substrate-nonescape} specify the finite closure-first quadrant certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove Lean verification, bridge checking, Rule 110 universality, global halting decidability, oracle computation, host semantic equality, quotient substrate equality, or derivability between the two axes.}
  \upgradepath{Obligation closure requires checked carrier, classifier, certificate-surface, axis-boundary, closed-substrate nonescape, nontriviality, and field-faithfulness targets for the same finite packet.}
\end{closurestatus}
