\chapter{A Concrete Naming Certificate for $\HaltedTmRoundTripUp$}
\label{ch:concrete-instances-halted-tm-round-trip-namecert}
\origin{ai}

The $\HaltedTmRoundTripUp$ packet is the finite certificate target for the Cook compile-frontier engineering path of \autoref{ch:visions-cook-compile-frontier-engineering-path}. It joins a staged Turing-machine compilation row, a Rule 110 orbit row, an inverse decode row, a halted readback row, and a scale-threshold row in one NameCert carrier. The packet sits beside the cellular trust substrate of \autoref{ch:concrete-instances-cellular-trust-substrate-namecert}, the bounded universal trace of \autoref{ch:concrete-instances-bounded-universal-trace-namecert}, the compiler optimization endomorphism of \autoref{ch:concrete-instances-compiler-optimization-endomorphism-namecert}, and the universal closed substrate of \autoref{ch:concrete-instances-universal-closed-substrate-namecert}; it is not reducible to any one of those siblings because it records the complete round trip from machine input to halted readback at a finite frontier coordinate.

\falsifiablePrediction{Deleting the decode row permits an orbit witness without a halted-TM readback; deleting the scale-threshold row permits a frontier claim without the finite Cook-stage budget.}

\independenceWitness{cellulartrustsubstrate, cellularautomaton, boundeduniversaltrace, compiler-optimization-endomorphism, universalclosedsubstrate; none is bijective because none preserves all staged compile, orbit, decode, halt, and frontier-scale rows.}

\begin{definition}[HaltedTmRoundTrip carrier]
\label{def:halted-tm-round-trip-carrier}
A $\HaltedTmRoundTripUp$ carrier is a finite $\BHist$ packet
$$
T=(M,G,Y,R,D,Q,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the halted Turing-machine source row, naming the finite state set, tape alphabet, transition table, initial configuration, and halted output row selected for the target machine;
\item $G$ is the staged Cook compilation row, recording the TM-to-tag, tag-to-cyclic, and cyclic-to-Rule-110 stages as finite compiler rows;
\item $Y$ is the cyclic-tag schedule row, including the production count, tape-symbol count, initial cyclic word, and finite schedule bound used by the compiled run;
\item $R$ is the Rule 110 initial row and local-rule orbit row, with the finite cell window, step budget, and accepted observation coordinates;
\item $D$ is the inverse decode row from the observed Rule 110 window back through cyclic-tag and tag-system readback;
\item $Q$ is the halted readback row, stating that the decoded machine row matches the halted output named by $M$;
\item $F$ is the frontier-scale row, recording the finite production, tape-symbol, row-width, and step-budget thresholds used by the compile-frontier read;
\item $H$ records componentwise $\hsame$ transports for $M,G,Y,R,D,Q,F,P,N$;
\item $C$ records displayed $\Cont$ routes through the staged compile, Rule 110 orbit, inverse decode, halted readback, and frontier-scale rows;
\item $P$ is the $\Pkg$ provenance over $\HaltedTmRoundTripUp$, \autoref{ch:visions-cook-compile-frontier-engineering-path}, \autoref{ch:concrete-instances-cellular-trust-substrate-namecert}, \autoref{ch:concrete-instances-bounded-universal-trace-namecert}, \autoref{ch:concrete-instances-compiler-optimization-endomorphism-namecert}, \autoref{ch:concrete-instances-universal-closed-substrate-namecert}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\HaltedTmRoundTripUp}$ row.
\end{enumerate}
The local classifier compares accepted packets only through $M,G,Y,R,D,Q,F,H,C,P,N$. It has no coordinate for an unbounded halting predicate, host evaluator equality, a detached Rule 110 orbit, a decode-free universality claim, or a scale-free frontier assertion.
\end{definition}
\leandef{BEDC.Derived.HaltedTmRoundTripUp.TasteGate.HaltedTmRoundTripUp}

\begin{theorem}[HaltedTmRoundTrip NameCert obligations]
\label{thm:halted-tm-round-trip-namecert-obligations}
For the carrier of \autoref{def:halted-tm-round-trip-carrier}, the local $\NameCert_{\HaltedTmRoundTripUp}$ surface consists exactly of carrier admission for $T=(M,G,Y,R,D,Q,F,H,C,P,N)$, staged compile accountability through $G$, cyclic-tag schedule accountability through $Y$, Rule 110 orbit accountability through $R$, inverse decode exactness through $D$, halted readback exactness through $Q$, frontier-scale accountability through $F$, and componentwise transport, replay, provenance, and local naming through $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:halted-tm-round-trip-carrier}. The source machine, staged compiler, cyclic schedule, Rule 110 orbit, inverse decode, halt readback, scale row, transport, route, provenance, and naming rows are the only coordinates available to a consumer.

The compile side is read through $M,G,Y,R$. The source row names the halted machine, the staged compiler row records the three Cook stages, the schedule row fixes the finite cyclic-tag budget, and the Rule 110 row records the finite orbit window accepted for observation.

The readback side is read through $D,Q,F$. The decode row returns from the observed orbit to the machine-facing row, the halt row checks that decoded row against the displayed halted output, and the scale row records the finite frontier budget under which the route is being claimed.

Finally $H,C,P,N$ bind the NameCert surface. Since the carrier has no coordinate for unbounded halting, host evaluator equality, a detached orbit witness, a decode-free readback, or a scale-free frontier claim, the listed rows exhaust the local obligations.
\end{proof}

\begin{theorem}[HaltedTmRoundTrip scale-threshold route]
\label{thm:halted-tm-round-trip-scale-threshold-route}
Every compile-frontier read exported by an accepted $\HaltedTmRoundTripUp$ packet factors through the staged finite route
$$
M,G,Y,R,D,Q,F,H,C,P,N .
$$
The route may state that the displayed halted machine has been compiled through the Cook stages, evaluated on a finite Rule 110 orbit, decoded back to the halted row, and checked at the thresholds recorded by $F$. It may not state the frontier claim without the scale row, the halted readback without the decode row, or the Rule 110 orbit without the staged compile row.
\end{theorem}
\begin{proof}
Begin with the route row $C$. Its admitted paths replay the staged compiler rows, then the cyclic-tag schedule, then the Rule 110 orbit, then the inverse decode and halted readback.

The scale-threshold row $F$ is read on the same route. It records the finite production count, tape-symbol count, row-width budget, and step-budget threshold used by the frontier claim, so the exported read is a bounded certificate rather than an ambient universality assertion.

The dependency on $D$ and $Q$ is essential. Without $D$, the packet contains an orbit observation but no machine-facing readback; without $Q$, it contains a decode but no halted-row match; without $F$, it contains a round trip but no Cook-frontier coordinate.
\end{proof}

\begin{theorem}[HaltedTmRoundTrip nonescape]
\label{thm:halted-tm-round-trip-nonescape}
An accepted $\HaltedTmRoundTripUp$ packet exports no unbounded halting predicate, no host evaluator equality, no detached Rule 110 orbit certificate, no decode-free halted readback, no scale-free frontier claim, and no semantic proof that every Turing machine is handled by the displayed route. Its public content is exactly the finite packet $M,G,Y,R,D,Q,F,H,C,P,N$ of \autoref{def:halted-tm-round-trip-carrier}.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. The source row names one finite halted-machine target, the compile rows name one staged Cook route, and the orbit row names one finite Rule 110 observation window.

The readback and scale rows restrict the export. The decoded row $D$ and halt row $Q$ bind the orbit to the named halted output, while $F$ binds the read to a finite frontier coordinate.

The excluded objects require rows absent from the carrier. Unbounded halting needs a global decision predicate, host evaluator equality needs a semantic equality row, a detached orbit certificate would omit $G$, a decode-free halt read would omit $D$, and a scale-free frontier claim would omit $F$. None of these coordinates is present, so the packet exports only the displayed finite NameCert surface.
\end{proof}

The Lean \texttt{TasteGate.lean} development for $\HaltedTmRoundTripUp$ will need $\mathsf{Nontrivial}\ \HaltedTmRoundTripUp$ and $\mathsf{FieldFaithful}\ \HaltedTmRoundTripUp$ instances. These instances must preserve the halted-machine source row, staged compile row, cyclic-tag schedule, Rule 110 orbit, inverse decode, halted readback, frontier-scale row, componentwise transport, replay route, package provenance, and local naming row.

\closureat{HaltedTmRoundTripUp}{seedStr}

\begin{closurestatus}{\HaltedTmRoundTripUp}
  \constructivestory{A $\HaltedTmRoundTripUp$ packet is generated from a halted Turing-machine source row, staged Cook compile row, cyclic-tag schedule, Rule 110 orbit row, inverse decode row, halted readback row, frontier-scale row, componentwise transports, displayed routes, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:halted-tm-round-trip-carrier}, \autoref{thm:halted-tm-round-trip-namecert-obligations}, \autoref{thm:halted-tm-round-trip-scale-threshold-route}, and \autoref{thm:halted-tm-round-trip-nonescape} specify the finite Cook compile-frontier round-trip certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove Lean verification, bridge checking, unbounded halting, host evaluator equality, global Rule 110 correctness, all-machine universality, or a detached decode-free frontier result.}
  \upgradepath{Obligation closure requires checked carrier admission, staged compile accountability, Rule 110 orbit accountability, inverse decode exactness, halted readback exactness, frontier-scale accountability, nontriviality, and field faithfulness for the same packet.}
\end{closurestatus}
