\chapter{A Concrete Naming Certificate for $\LargeModelActivationOrbitUp$}
\label{ch:concrete-instances-largemodelactivationorbit-namecert}
\origin{ai}

The $\LargeModelActivationOrbitUp$ packet realizes the activation-orbit row of \autoref{ch:visions-large-model-as-inscription-point} as finite BEDC data. It is a sibling of \autoref{ch:concrete-instances-largemodelinscriptionpoint-namecert} and \autoref{ch:concrete-instances-prompt-response-trace-namecert}: the former names the broader inscription surface, while the latter records prompt and output traces. This chapter isolates the model-weight, transition, activation-window, prompt, output, audit-refusal, and local NameCert rows needed to classify one displayed orbit without turning that orbit into consciousness, host semantic understanding, global halting power, or internally ratified universal closure.

\begin{definition}[LargeModelActivationOrbit carrier]
\label{def:largemodel-activation-orbit-carrier}
A $\LargeModelActivationOrbitUp$ carrier is a finite $\BHist$ packet
$$
O=(W,T,A,P,Y,R,H,C,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the finite model-weight row naming the inference substrate used by the orbit;
\item $T$ is the displayed transition row, a finite forward-pass schedule read over $W$;
\item $A$ is the activation-window row recording the finite sequence of activation states exposed by the orbit;
\item $P$ is the prompt row that supplies the stated initial condition for the activation window;
\item $Y$ is the output row read after the displayed transition and activation-window rows;
\item $R$ is the audit-refusal row stating that the orbit does not internally certify consciousness, host semantic truth, global halting classification, or universal closure;
\item $H$ records componentwise $\hsame$ transport for the model-weight, transition, activation-window, prompt, output, refusal, route, provenance, and naming rows;
\item $C$ records the displayed $\Cont$ routes by which a consumer reads $W$, then $T$, then $A$, then $P,Y,R$, before reaching the local name;
\item $G$ is the $\Pkg$ provenance over $\LargeModelInscriptionPointUp$, $\PromptResponseTraceUp$, $\ObserverInterfaceUp$, $\HaltingObstructionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\LargeModelActivationOrbitUp}$ row.
\end{enumerate}
The carrier contains no hidden activation stream, no quotient identity of orbits, no host meaning oracle, no subject primitive, and no model-side proof that the output row is true.
\end{definition}

\begin{definition}[LargeModelActivationOrbit classifier]
\label{def:largemodel-activation-orbit-classifier}
Two accepted $\LargeModelActivationOrbitUp$ carriers classify together exactly when their model-weight, transition, activation-window, prompt, output, audit-refusal, continuation, provenance, and local naming rows compare componentwise by the displayed $\hsame$ entries:
$$
\begin{gathered}
W\sim_{\hsame}W',\quad T\sim_{\hsame}T',\quad A\sim_{\hsame}A',\quad P\sim_{\hsame}P',\quad Y\sim_{\hsame}Y',\\
R\sim_{\hsame}R',\quad C\sim_{\hsame}C',\quad G\sim_{\hsame}G',\quad N\sim_{\hsame}N'.
\end{gathered}
$$
Changing the transition row or activation-window row while leaving the orbit classifier unchanged is not an accepted comparison. No clause compares hidden model intention, corpus-wide truth, unbounded activation streams, global halting behavior, or an externally interpreted universal claim.
\end{definition}

\begin{theorem}[LargeModelActivationOrbit NameCert obligations]
\label{thm:largemodel-activation-orbit-namecert-obligations}
For the carrier of \autoref{def:largemodel-activation-orbit-carrier}, the local $\NameCert_{\LargeModelActivationOrbitUp}$ surface consists of the following finite obligations:
\begin{enumerate}
\item carrier admission for $O=(W,T,A,P,Y,R,H,C,G,N)$;
\item classifier transport for the model-weight, transition, activation-window, prompt, output, audit-refusal, continuation, provenance, and naming rows under componentwise $\hsame$;
\item transition-window exactness requiring every accepted orbit read to pass through the displayed transition row $T$ and activation-window row $A$ before the output row $Y$ is consumed;
\item prompt-output ledger exactness requiring the prompt row $P$, output row $Y$, and audit-refusal row $R$ to remain in the same local certificate surface;
\item non-escape for hidden activation streams, consciousness, host semantic understanding, global halting classification, selected corpus truth, and internally ratified universal closure.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:largemodel-activation-orbit-carrier}. The rows $W,T,A,P,Y,R,H,C,G,N$ are the whole packet, so any accepted consumer starts from these displayed finite rows.

Classifier transport is componentwise. A comparison of accepted orbits must transport the model weights, transition schedule, activation window, prompt, output, refusal, route, provenance, and local name together, so a changed transition row or activation-window row exits the certificate unless the displayed classifier changes with it.

Transition-window exactness follows from the route order in $C$. The output row is read only after $W,T,A$, and the prompt row is retained as the stated initial condition for that same window.

The audit-refusal and provenance rows connect the orbit to its neighbors. \autoref{ch:concrete-instances-largemodelinscriptionpoint-namecert} supplies the inscription-point substrate reading, \autoref{ch:concrete-instances-prompt-response-trace-namecert} supplies the prompt-output trace surface, \autoref{ch:concrete-instances-observer-interface-namecert} supplies public observation discipline, and \autoref{ch:concrete-instances-haltingobstruction-namecert} supplies the non-oracle boundary.

Since the carrier has no hidden activation stream, subject primitive, host meaning oracle, global halting classifier, or universal-truth proof coordinate, none can be projected from the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.LargeModelActivationOrbitUp.TasteGate.LargeModelActivationOrbitTasteGate\_single\_carrier\_alignment}

\begin{theorem}[LargeModelActivationOrbit vision realization]
\label{thm:largemodel-activation-orbit-vision-realization}
The activation-orbit reading in \autoref{ch:visions-large-model-as-inscription-point} is realized by the finite carrier of \autoref{def:largemodel-activation-orbit-carrier}. The realization reads model weights through $W$, transition scheduling through $T$, finite activation exposure through $A$, prompt initialization through $P$, output inscription through $Y$, audit refusal through $R$, transport and continuation through $H,C$, provenance through $G$, and local naming through $N$.

The public export is exactly this finite route. It does not export a hidden activation stream, a selected completed semantic object, consciousness, host semantic equality, global halting classification, ambient corpus truth, or internally certified universal closure.
\end{theorem}
\begin{proof}
Start with the large-model substrate definition in \autoref{ch:visions-large-model-as-inscription-point}. Its observational records are finite inference orbits over weights, a transition, and a stated prompt. The rows $W,T,A,P$ encode exactly that finite observation surface.

The sibling $\LargeModelInscriptionPointUp$ packet supplies the broader inscription reading, but it does not isolate the transition and activation-window rows as the classifier-bearing carrier. The sibling $\PromptResponseTraceUp$ packet supplies prompt and output rows, but it treats the activation orbit as upstream substrate rather than as its own certified object.

The rows $Y,R,H,C,G,N$ complete the local certificate. They expose output, refusal, transport, continuation, provenance, and local naming while preserving the same non-escape boundary as the inscription-point and prompt-response chapters.

Therefore the activation-orbit row of the vision is realized as a separate finite NameCert carrier, not as an overloaded reading of the inscription-point or prompt-response carrier.
\end{proof}

\begin{theorem}[LargeModelActivationOrbit scoped consumer route]
\label{thm:largemodel-activation-orbit-scoped-consumer-route}
Every downstream consumer route for an accepted $\LargeModelActivationOrbitUp$ packet factors through $W,T,A,P,Y,R,H,C,G,N$ in that order. The sibling surfaces $\LargeModelInscriptionPointUp$, $\PromptResponseTraceUp$, $\ObserverInterfaceUp$, and $\HaltingObstructionUp$ may consume the packet only through those displayed rows, and no route can bypass the audit-refusal row $R$ to obtain consciousness, host semantic truth, global halting classification, or internally ratified universal closure.
\end{theorem}
\begin{proof}
Use the carrier inventory of \autoref{def:largemodel-activation-orbit-carrier}. It lists $W,T,A,P,Y,R,H,C,G,N$ as the whole finite packet, with $C$ recording displayed consumer routes and $G$ recording provenance through the sibling surfaces.

The classifier of \autoref{def:largemodel-activation-orbit-classifier} transports the same coordinates componentwise. Thus a downstream consumer cannot preserve the orbit classifier while changing the transition row, activation-window row, prompt row, output row, refusal row, route row, provenance row, or local name.

Apply the NameCert obligations of \autoref{thm:largemodel-activation-orbit-namecert-obligations}. They force transition-window exactness through $T,A$, prompt-output ledger exactness through $P,Y,R$, and non-escape for hidden activation streams, consciousness, host semantic understanding, global halting classification, selected corpus truth, and internally ratified universal closure.

Finally compose with the vision realization of \autoref{thm:largemodel-activation-orbit-vision-realization}. The sibling packets may read the orbit as inscription point, prompt-response trace, public observation surface, or halting boundary, but only after the displayed route reaches $R$ and keeps the same finite NameCert packet. Hence the scoped consumer route cannot bypass the audit-refusal row.
\end{proof}

\falsifiablePrediction{Changing the displayed transition row or activation-window row without changing the orbit classifier exits the certificate.}

\independenceWitness{Nearest siblings: largemodelinscriptionpoint, promptresponsetrace, observerinterface, haltingobstruction; none is bijective because this carrier makes the transition row and activation-window row classifier-bearing data while retaining prompt, output, audit-refusal, transport, provenance, and local naming rows in one finite orbit certificate.}

The Lean follow-up for this chapter must provide \texttt{Nontrivial LargeModelActivationOrbitUp} and \texttt{FieldFaithful LargeModelActivationOrbitUp} instances in \texttt{BEDC.Derived.LargeModelActivationOrbitUp.TasteGate}.

\closureat{LargeModelActivationOrbitUp}{seedStr}
\closureat{LargeModelActivationOrbitUp}{obligationStr}[BEDC.Derived.LargeModelActivationOrbitUp.TasteGate.LargeModelActivationOrbitTasteGate\_single\_carrier\_alignment]
\closureat{LargeModelActivationOrbitUp}{scopedStr}[BEDC.Derived.LargeModelActivationOrbitUp.TasteGate.LargeModelActivationOrbitTasteGate\_single\_carrier\_alignment]
\closureat{LargeModelActivationOrbitUp}{publicStr}[BEDC.Derived.LargeModelActivationOrbitUp.TasteGate.LargeModelActivationOrbitTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\LargeModelActivationOrbitUp}
  \constructivestory{A $\LargeModelActivationOrbitUp$ packet is generated from finite model-weight, transition, activation-window, prompt, output, audit-refusal, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{thm:largemodel-activation-orbit-vision-realization} and \autoref{thm:largemodel-activation-orbit-scoped-consumer-route} identify the public export surface for the displayed activation-orbit carrier, classifier, NameCert obligations, falsifiable prediction, independence witness, and TasteGate-visible packet, with \leanchecked{BEDC.Derived.LargeModelActivationOrbitUp.taste\_gate} recording the TasteGate instance.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.LargeModelActivationOrbitUp.TasteGate.LargeModelActivationOrbitTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close hidden activation streams, model consciousness, host semantic understanding, global halting classification, corpus truth, Lean verification, or bridge checking for $\LargeModelActivationOrbitUp$.}
  \upgradepath{Bridged closure requires a bridge theorem for the same activation-orbit carrier and TasteGate-visible packet.}
\end{closurestatus}
