\chapter{A Concrete Naming Certificate for $\PolePlacementUp$}
\label{ch:concrete-instances-poleplacement-namecert}

The $\PolePlacementUp$ interface records the finite closed-loop ledger used by
control certificates that choose a displayed feedback row and target a
displayed characteristic-polynomial row. In the standard finite-dimensional
control setting of Chen, \emph{Linear System Theory and Design} (1999), pole
placement relates the state matrix, input matrix, feedback gain, and requested
closed-loop characteristic polynomial. The BEDC surface below names only the
finite rows of that relation. It exports no analytic spectrum, no host
trajectory space, and no stabilizing feedback existence theorem.

\begin{definition}[PolePlacement finite BHist carrier]
\label{def:poleplacement-carrier}
A $\PolePlacementUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
\Pi=(X,U,A,B,K,C,T,H,R,P,L)
$$
whose visible rows are:
\begin{enumerate}
\item a state row $X$ and an input row $U$ read through $\VecSpaceUp$ and the
state/input face of $\StateSpaceModelUp$;
\item a transition matrix row $A$ and input matrix row $B$ read through
$\MatrixUp$ and $\LinMapUp$;
\item a feedback gain row $K$ read as a finite matrix and linear-map row from
$X$ to $U$;
\item a closed-loop row $C$ whose displayed matrix ledger records
$C=A+BK$ over the same state carrier;
\item a target characteristic row $T$ and characteristic-comparison ledger $H$
recording the requested finite polynomial row and its displayed comparison
with the characteristic row of $C$;
\item $\hsame$ comparisons for the state, input, $A$, $B$, $K$, $C$, target,
characteristic, continuation, and provenance rows;
\item $\Cont$ routes $R$ for reading multiplication $BK$, addition $A+BK$,
closed-loop readback, and characteristic-row comparison;
\item a $\mathsf{Pkg}$ provenance row $P$ naming $\StateSpaceModelUp$,
$\ControlControllabilityUp$, $\MatrixUp$, $\VecSpaceUp$, and $\LinMapUp$;
\item a ledger boundary row $L$ saying that no host trajectory space, analytic
spectrum, eigenvalue multiplicity theorem, or stabilizing feedback theorem is
part of the carrier.
\end{enumerate}
Two accepted packets classify together only when every displayed row in this
inventory is transported componentwise by the recorded $\hsame$ comparisons
and every matrix, linear-map, closed-loop, and target-polynomial read follows
one of the recorded $\Cont$ routes.
\end{definition}
\leandef{BEDC.Derived.PolePlacementUp.PolePlacementSourcePacket}

\begin{theorem}[PolePlacement closed-loop ledger]
\label{thm:poleplacement-closed-loop-ledger}
Every accepted $\PolePlacementUp$ packet exposes exactly the finite state row
$X$, input row $U$, transition row $A$, input row $B$, gain row $K$,
closed-loop row $C$, target characteristic row $T$, characteristic-comparison
ledger $H$, $\hsame$ rows, $\Cont$ routes, and $\mathsf{Pkg}$ provenance rows
listed in \autoref{def:poleplacement-carrier}. The closed-loop readback is the
displayed ledger $C=A+BK$ and no additional host closed-loop system is
exported.
\end{theorem}
\leanchecked{BEDC.Derived.PolePlacementUp.PolePlacementSourcePacket\_closed\_loop\_ledger}
\leanchecked{BEDC.Derived.PolePlacementUp.PolePlacementCarrier\_closed\_loop\_ledger}
\begin{proof}
Project the accepted carrier of \autoref{def:poleplacement-carrier}. The
projection exposes the finite state, input, matrix, gain, closed-loop, target,
comparison, transport, continuation, provenance, and boundary rows.

The closed-loop row is read through the displayed matrix multiplication and
addition routes. The multiplication route supplies the $BK$ ledger, the
addition route supplies the $A+BK$ ledger, and the closed-loop row $C$ is the
recorded endpoint of that finite calculation.

Transporting the packet replaces each coordinate by its displayed $\hsame$
match and follows the same $\Cont$ routes. Since the carrier has no coordinate
for a host trajectory space or analytic closed-loop object, every
consumer-visible closed-loop read is exhausted by the finite ledger.
\end{proof}

\begin{theorem}[PolePlacement NameCert obligations]
\label{thm:poleplacement-namecert-obligations}
The local $\NameCert_{\PolePlacementUp}$ obligation surface consists of five
finite rows:
\begin{enumerate}
\item carrier habitation: an accepted packet is inhabited by choosing displayed
$\StateSpaceModelUp$, $\MatrixUp$, $\VecSpaceUp$, and $\LinMapUp$ source rows
and recording the gain, closed-loop, target, comparison, transport,
continuation, and provenance rows of \autoref{def:poleplacement-carrier};
\item classifier transport: accepted packets compare by componentwise $\hsame$
transport of $X$, $U$, $A$, $B$, $K$, $C$, $T$, $H$, $R$, $P$, and $L$;
\item closed-loop ledger exactness: the only closed-loop row exported by the
packet is the displayed $C=A+BK$ ledger of
\autoref{thm:poleplacement-closed-loop-ledger};
\item target-polynomial ledger: every target read is the finite row $T$
together with the comparison ledger $H$ against the characteristic row of $C$;
\item downstream consumer boundary: $\RiccatiUp$, $\LQRUp$,
$\KalmanFilterUp$, and $\StateSpaceModelUp$ consumers may read only the finite
state, input, matrix, gain, closed-loop, target, comparison, transport,
continuation, and provenance rows of the same packet.
\end{enumerate}
\end{theorem}
\begin{proof}
The habitation row is a finite packet assembly. Each required coordinate is a
displayed $\mathsf{BHist}$ row, and the provenance row names the consumed
state-space, controllability, matrix, vector-space, and linear-map
certificates.

Classifier transport is componentwise. Transporting $X$, $U$, $A$, $B$, $K$,
$C$, $T$, $H$, $R$, $P$, and $L$ along the displayed $\hsame$ rows preserves
the same carrier inventory and the same matrix and characteristic-read routes.

The closed-loop obligation is exactly
\autoref{thm:poleplacement-closed-loop-ledger}. The target-polynomial
obligation is the corresponding projection of $T$ and $H$, so it records a
finite comparison row rather than an analytic spectral theorem.

Finally, the downstream boundary is the package projection. Since the package
row names only the displayed control and algebra certificates, the listed
consumers cannot recover host trajectories, unlogged spectra, or feedback
existence principles from the $\PolePlacementUp$ surface.
\end{proof}

\begin{theorem}[PolePlacement consumer boundary]
\label{thm:poleplacement-consumer-boundary}
Every downstream read from an accepted $\PolePlacementUp$ packet factors
through the finite rows of \autoref{def:poleplacement-carrier}. Riccati, LQR,
KalmanFilter, and StateSpaceModel consumers may use the displayed
$\StateSpaceModelUp$, $\ControlControllabilityUp$, $\MatrixUp$, $\VecSpaceUp$,
$\LinMapUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows, but
they cannot demand an analytic spectrum, a host trajectory space, a
stabilizing controller theorem, a controllability-rank proof, or an external
feedback solver from this certificate.
\end{theorem}
\begin{proof}
Take a consumer-visible readback from an accepted packet. By
\autoref{def:poleplacement-carrier}, the readback is a projection from the
finite carrier rows or from the provenance row naming the consumed
certificates.

Apply \autoref{thm:poleplacement-closed-loop-ledger} to the closed-loop part.
This identifies the only available feedback read as the displayed $A+BK$ row
and its target characteristic comparison.

The listed consumers therefore receive only finite BEDC rows and their
transport and continuation data. Any analytic spectrum, host trajectory,
stabilizing-controller theorem, rank proof, or external solver would require a
coordinate absent from the packet.
\end{proof}

\begin{theorem}[PolePlacement standard finite bridge]
\label{thm:poleplacement-standard-finite-bridge}
The finite $\PolePlacementUp$ packet of
\autoref{def:poleplacement-carrier}, together with the closed-loop ledger,
NameCert obligation surface, and consumer boundary, interprets as the standard
finite pole-placement schema: a state row, input row, transition matrix row
$A$, input matrix row $B$, gain row $K$, closed-loop row $A+BK$, and requested
target characteristic row are all displayed as finite $\mathsf{BHist}$ rows
with explicit transport, continuation, and provenance. This bridge exports no
analytic spectral assumption, pole-existence theorem, host trajectory
semantics, or feedback optimality claim.
\end{theorem}
\begin{proof}
Begin with the carrier. It gives the state and input rows, the matrix and
linear-map rows for $A$, $B$, and $K$, the displayed closed-loop endpoint, and
the target characteristic ledger.

Use \autoref{thm:poleplacement-closed-loop-ledger} to identify the closed-loop
schema field with the finite $A+BK$ calculation. Use
\autoref{thm:poleplacement-namecert-obligations} to package the carrier,
classifier transport, ledger exactness, target-polynomial ledger, and
downstream boundary as the local name-certificate surface.

Apply \autoref{thm:poleplacement-consumer-boundary} to restrict every public
read to the same finite rows. The resulting interpretation is exactly the
standard finite pole-placement data shape, while the excluded analytic and
optimality claims remain outside the certificate.
\end{proof}

\begin{theorem}[PolePlacement scoped dependency packet]\label{thm:poleplacement-scoped-dependency-packet}
The closed-loop ledger of \autoref{thm:poleplacement-closed-loop-ledger},
target-polynomial ledger and certificate surface of
\autoref{thm:poleplacement-namecert-obligations}, consumer boundary of
\autoref{thm:poleplacement-consumer-boundary}, and standard finite bridge of
\autoref{thm:poleplacement-standard-finite-bridge} form one scoped dependency
packet. Its only source rows are the displayed $\mathsf{BHist}$ state, input,
matrix, gain, closed-loop, target, characteristic-comparison, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$,
$\StateSpaceModelUp$, and $\ControlControllabilityUp$ rows.
\end{theorem}
\begin{proof}
Project the packet through \autoref{def:poleplacement-carrier}. The available
coordinates are exactly the finite state and input rows, matrix rows, gain row,
closed-loop row, target row, characteristic-comparison row, transports,
continuations, and package provenance named in the statement.

Apply \autoref{thm:poleplacement-closed-loop-ledger} to identify the closed-loop
projection, and apply \autoref{thm:poleplacement-namecert-obligations} to bind
the target-polynomial ledger and certificate obligations to the same carrier
rows.

For every consumer projection, use
\autoref{thm:poleplacement-consumer-boundary}; for the standard finite data
shape, use \autoref{thm:poleplacement-standard-finite-bridge}. Both results
factor through the displayed $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$,
$\StateSpaceModelUp$, $\ControlControllabilityUp$, $\mathsf{BHist}$, $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ rows.

Repacking these projections gives a single scoped dependency packet. No
analytic spectrum, host trajectory space, unlogged rank proof, or external
feedback solver is introduced, because no such coordinate occurs in the
projected rows.
\end{proof}

\begin{theorem}[PolePlacement public consumer export]\label{thm:poleplacement-public-consumer-export}
The scoped dependency packet of
\autoref{thm:poleplacement-scoped-dependency-packet} exports a public
finite-control interface to $\RiccatiUp$, $\LQRUp$, $\KalmanFilterUp$, and
$\StateSpaceModelUp$ consumers. The exported interface consists exactly of the
state row, input row, transition matrix row, input matrix row, gain row,
closed-loop row $A+BK$, target characteristic row,
characteristic-comparison ledger, displayed $\hsame$ rows, $\Cont$ routes, and
$\mathsf{Pkg}$ provenance over $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$,
$\StateSpaceModelUp$, and $\ControlControllabilityUp$.

It exports no analytic spectrum, host trajectory space, stabilizing feedback
theorem, controllability-rank completeness, feedback optimality, or external
solver.
\end{theorem}
\begin{proof}
Start with the closed-loop ledger of
\autoref{thm:poleplacement-closed-loop-ledger}. It identifies the displayed
transition, input, gain, and $A+BK$ rows as finite ledger coordinates.

Apply \autoref{thm:poleplacement-namecert-obligations} to attach the target
characteristic row, characteristic-comparison ledger, displayed $\hsame$ rows,
$\Cont$ routes, and package provenance to the same accepted carrier.

Use \autoref{thm:poleplacement-consumer-boundary} for the downstream read
boundary, and use \autoref{thm:poleplacement-standard-finite-bridge} for the
standard finite-control packet shape. These two results identify exactly the
$\RiccatiUp$, $\LQRUp$, $\KalmanFilterUp$, and $\StateSpaceModelUp$ consumer
surface named in the statement.

Finally apply \autoref{thm:poleplacement-scoped-dependency-packet}. Since that
packet has no coordinate for analytic spectra, host trajectory spaces,
stabilizing feedback existence, rank-completeness, optimality, or solver data,
none of those objects can be exported by the public interface.
\end{proof}

\closureat{PolePlacementUp}{obligationStr}
\closureat{PolePlacementUp}{scopedStr}
\closureat{PolePlacementUp}{publicStr}

\begin{closurestatus}{\PolePlacementUp}
  \constructivestory{A $\PolePlacementUp$ packet is seeded by finite $\mathsf{BHist}$ rows for state, input, transition matrix, input matrix, gain, closed-loop matrix $A+BK$, target characteristic row, characteristic-comparison ledger, $\hsame$ transports, $\Cont$ routes, and $\mathsf{Pkg}$ provenance over the state-space, controllability, matrix, vector-space, and linear-map certificates.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{thm:poleplacement-scoped-dependency-packet} binds the finite pole-placement carrier, closed-loop ledger, target-polynomial ledger, NameCert obligation rows, consumer boundary, standard finite data shape, and displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, $\MatrixUp$, $\VecSpaceUp$, $\LinMapUp$, $\StateSpaceModelUp$, and $\ControlControllabilityUp$ dependencies, while \autoref{thm:poleplacement-public-consumer-export} exposes the downstream finite-control public export.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close analytic spectral theory, pole-existence theorems, stabilizing feedback existence, controllability-rank completeness, host trajectory semantics, feedback optimality, or a machine-checked standard bridge.}
  \upgradepath{Bridged closure requires a standard finite-control bridge over the same displayed state, input, matrix, feedback, target-polynomial, transport, continuation, package, and consumer rows.}
\end{closurestatus}
