\chapter{A Concrete Naming Certificate for $\ContextWindowCommitmentUp$}
\label{ch:concrete-instances-contextwindowcommitment-namecert}
\origin{ai}

The $\ContextWindowCommitmentUp$ packet realizes bounded prompt context as finite BEDC data. It is a large-model inscription sibling of \autoref{ch:concrete-instances-prompt-response-trace-namecert}, \autoref{ch:concrete-instances-largemodelinscriptionpoint-namecert}, \autoref{ch:concrete-instances-attention-ledger-namecert}, \autoref{ch:concrete-instances-observer-interface-namecert}, and \autoref{ch:concrete-instances-inscriptionevent-namecert}. Its distinguishing datum is the committed window scope: prompt, response boundary, audit refusal, downstream consumer ledger, transport, route, provenance, and local naming rows are displayed before any consumer may treat the packet as context for a model response.

\begin{definition}[ContextWindowCommitment carrier]
\label{def:context-window-commitment-carrier}
A $\ContextWindowCommitmentUp$ carrier is a finite $\BHist$ packet
$$
C=(S,P,B,R,U,H,K,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the committed window-scope row, recording the finite prompt context made available to the model-side inscription route;
\item $P$ is the prompt row admitted inside the displayed window;
\item $B$ is the prompt-response boundary row, separating the consumed prompt context from the emitted response row;
\item $R$ is the audit-refusal row, recording unsupported universal closure, hidden model-state access, ambient corpus truth, and unverified semantic claims as refused reads;
\item $U$ is the downstream consumer ledger, naming the public consumer route that may read the bounded window and response boundary;
\item $H$ records componentwise $\hsame$ transport for window scope, prompt, boundary, refusal, consumer, route, provenance, and local naming rows;
\item $K$ records the displayed $\Cont$ route from window scope through prompt, boundary, refusal, consumer ledger, provenance, and local name;
\item $G$ is the $\Pkg$ provenance over $\PromptResponseTraceUp$, $\LargeModelInscriptionPointUp$, $\AttentionLedgerUp$, $\ObserverInterfaceUp$, $\InscriptionEventUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ContextWindowCommitmentUp}$ row.
\end{enumerate}
The carrier has no coordinate for an unbounded context store, hidden model state, ambient corpus oracle, private semantic evaluator, or post-response mutation of the committed window.
\end{definition}
\leanchecked{BEDC.Derived.ContextWindowCommitmentUp.ContextWindowCommitmentTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ContextWindowCommitment NameCert obligations]
\label{thm:context-window-commitment-namecert-obligations}
For the carrier of \autoref{def:context-window-commitment-carrier}, the local $\NameCert_{\ContextWindowCommitmentUp}$ surface consists exactly of carrier admission for $C=(S,P,B,R,U,H,K,G,N)$, bounded window exposure through $S$, prompt admission through $P$, response-boundary exposure through $B$, audit-refusal exposure through $R$, downstream consumer routing through $U$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $K$, package provenance through $G$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the displayed carrier. The rows $S,P,B,R,U,H,K,G,N$ list the entire packet before any consumer can read a prompt context or response boundary.

The window row $S$ is read before the prompt row $P$, and the boundary row $B$ is read before the downstream consumer row $U$. This forces the response-facing route to be consumed as a bounded prompt-response packet rather than as an ambient model-state query.

The audit-refusal row $R$ blocks unsupported universal closure, hidden context extension, ambient corpus truth, and unverified semantic claims. The transport, route, provenance, and local naming rows then package exactly this finite surface.

Since no coordinate stores an unbounded context store, hidden model state, ambient corpus oracle, private evaluator, or post-response mutation channel, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[ContextWindowCommitment prompt-response boundary]
\label{thm:context-window-commitment-prompt-response-boundary}
Every accepted $\ContextWindowCommitmentUp$ consumer route factors through the displayed finite window scope $S$, prompt row $P$, prompt-response boundary $B$, audit-refusal row $R$, downstream consumer ledger $U$, $\hsame$ transport row $H$, displayed $\Cont$ route $K$, $\Pkg$ provenance $G$, and local $\NameCert_{\ContextWindowCommitmentUp}$ row $N$.

If $B$ is absent, the packet cannot distinguish a committed prompt window from a response read that has silently consumed additional context.
\end{theorem}
\begin{proof}
Begin with \autoref{def:context-window-commitment-carrier}. Its route row $K$ orders the committed window, prompt, boundary, refusal, and downstream consumer rows before the local name is reached.

Apply \autoref{thm:context-window-commitment-namecert-obligations}. Any accepted consumer must expose $S,P,B,R,U,H,K,G,N$ together, so the response-facing read is tied to the same finite window that admitted the prompt.

If $B$ is removed, the remaining packet still contains a window and a prompt, but it no longer records the response boundary that separates consumed context from emitted output. The consumer then has no finite row excluding additional context reads.

With $B$ present, the route has a visible boundary between prompt context and response consumption. The proof uses only displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{proof}

\begin{theorem}[ContextWindowCommitment nonescape]
\label{thm:context-window-commitment-nonescape}
No public consumer of an accepted $\ContextWindowCommitmentUp$ packet can read an ambient model-state oracle, an unbounded context store, a hidden corpus-truth predicate, a private evaluator, or a response-side context mutation. Public reads are limited to the committed window scope, prompt, response boundary, audit refusal, downstream consumer ledger, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed in \autoref{def:context-window-commitment-carrier}.
\end{theorem}
\begin{proof}
Inspect the carrier inventory. The public coordinates are exactly $S,P,B,R,U,H,K,G,N$, so every projection from an accepted packet factors through the bounded window and its recorded response boundary.

The prompt-response trace and large-model inscription siblings supply model-side provenance, while the attention, observer-interface, and inscription-event siblings supply public observation and inscription discipline. None supplies a hidden model-state row to this packet.

The audit-refusal and downstream consumer rows close the route. They record which reads are refused and which consumer may inspect the finite window, without adding a separate oracle or mutable response-side context.

Therefore a consumer can recover the displayed finite packet and its certified route, but no ambient model state, unbounded context, hidden corpus truth, private evaluator, or post-response mutation channel is available for projection.
\end{proof}

\falsifiablePrediction{Any accepted ContextWindowCommitmentUp consumer factors through a displayed finite prompt-response window and cannot read an ambient model-state oracle.}

\independenceWitness{Nearest siblings: promptresponsetrace, largemodelinscriptionpoint, attentionledger, observerinterface, and inscriptionevent; none is bijective because none simultaneously carries committed window scope, prompt-response boundary, audit-refusal route, and downstream consumer ledger.}

The Lean TasteGate namespace $\mathsf{BEDC.Derived.ContextWindowCommitmentUp}$ exposes $\mathsf{Nontrivial}\ \ContextWindowCommitmentUp$ and $\mathsf{FieldFaithful}\ \ContextWindowCommitmentUp$ for the same finite carrier.

\closureat{ContextWindowCommitmentUp}{seedStr}

\begin{closurestatus}{\ContextWindowCommitmentUp}
  \constructivestory{A $\ContextWindowCommitmentUp$ packet is generated from a committed finite window scope, prompt row, prompt-response boundary, audit-refusal row, downstream consumer ledger, componentwise $\hsame$ transport, displayed $\Cont$ route, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:context-window-commitment-carrier}, \autoref{thm:context-window-commitment-namecert-obligations}, \autoref{thm:context-window-commitment-prompt-response-boundary}, and \autoref{thm:context-window-commitment-nonescape} specify the finite bounded-context commitment and its consumer-facing non-escape surface.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.ContextWindowCommitmentUp.ContextWindowCommitmentTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close model consciousness, corpus truth, host semantic understanding, hidden model-state access, unbounded context stores, or bridge checking for $\ContextWindowCommitmentUp$.}
  \upgradepath{Obligation closure requires checked boundary exactness, refusal exactness, downstream consumer coverage, and bridge status over the same committed window, prompt, response boundary, audit refusal, hsame, Cont, Pkg, and NameCert rows.}
\end{closurestatus}
