\chapter{A Concrete Naming Certificate for $\ContinuedFractionUp$}
\label{ch:concrete-instances-continuedfraction-namecert}
\origin{human}

The $\ContinuedFractionUp$ interface names finite continued-fraction
observation packets as constructive real-name neighbors. Following Khinchin's
continued-fraction treatment, the BEDC surface records partial quotients,
convergent rows, certified dyadic error radii, stream observations, regular
rational handoff rows, and a real-name boundary without completing an infinite
expansion or quotienting tails.

The partial-quotient spine consumes the $\NatUp$ carrier of
\autoref{ch:concrete-instances-nat-namecert}. The convergent numerator and
denominator rows consume the rational arithmetic surface of
\autoref{ch:concrete-instances-rat-namecert}, and the certified error-radius
row consumes \autoref{ch:concrete-instances-dyadicratcore-namecert}. The
scheduled handoff and seal route then consume
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert}, and
\autoref{ch:concrete-instances-real-namecert}, locating the finite
continued-fraction carrier in the Real-completion dependency lattice.

\begin{definition}[ContinuedFraction carrier packet]
\label{def:continuedfraction-carrier}
A $\ContinuedFractionUp$ carrier packet is a finite $\mathsf{BHist}$ record
$$
C=(a,p,q,e,s,r,b,\ell,P)
$$
with the following visible rows:
\begin{enumerate}
\item $a$ is the finite partial-quotient spine over $\NatUp$;
\item $p$ and $q$ are the convergent numerator and denominator rows read over
$\RatUp$, including the displayed recurrence ledger for each finite index;
\item $e$ is the $\DyadicRatCoreUp$ error-radius row attached to the displayed
convergent window;
\item $s$ is the $\StreamNameUp$ observation schedule through which finite
convergent windows are exposed;
\item $r$ is the $\RegSeqRatUp$ handoff row built from the scheduled rational
convergents and their dyadic radius rows;
\item $b$ is the $\RealUp$ seal boundary row that consumes the regular
sequence surface without selecting a completed real value;
\item $\ell$ is the finite ledger naming the recurrence rows, endpoint rows,
transport windows, and dependency anchors;
\item $P$ is the $\mathsf{Pkg}$ provenance row for the carrier and the local
$\NameCert_{\ContinuedFractionUp}$ registration.
\end{enumerate}
The carrier accepts exactly those packets whose rows occur in one finite
history and whose recurrence, endpoint, schedule, handoff, boundary, and
provenance entries are connected by displayed $\hsame$ and $\Cont$ routes.
\end{definition}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionTasteGate\_single\_carrier\_alignment}
\leandef{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket}

\begin{definition}[ContinuedFraction classifier]
\label{def:continuedfraction-classifier}
Two accepted $\ContinuedFractionUp$ packets classify together when every shared
finite convergent window has classifier-equal numerator, denominator, and
dyadic radius endpoint rows through the $\RatUp$ and $\DyadicRatCoreUp$
classifiers, and when the transported $\StreamNameUp$, $\RegSeqRatUp$,
$\RealUp$, recurrence-ledger, and $\mathsf{Pkg}$ rows agree through the same
displayed $\hsame$ and $\Cont$ routes.
\end{definition}

\begin{theorem}[ContinuedFraction NameCert obligations]
\label{thm:continuedfraction-namecert-obligations}
The local $\NameCert_{\ContinuedFractionUp}$ obligation surface consists of
five rows:
\begin{enumerate}
\item carrier inhabitation by the empty partial-quotient spine or by a
singleton convergent with visible $\NatUp$, $\RatUp$, $\DyadicRatCoreUp$,
$\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\mathsf{Pkg}$ rows;
\item classifier transport along the componentwise $\hsame$ and $\Cont$ routes
named in \autoref{def:continuedfraction-classifier};
\item recurrence-ledger stability for the finite convergent numerator and
denominator rows;
\item finite-window $\RegSeqRatUp$ handoff for scheduled convergent windows
and dyadic radius rows;
\item $\RealUp$ boundary exactness through the displayed seal row and no other
real-facing coordinate.
\end{enumerate}
\end{theorem}
\begin{proof}
For habitation, use either the empty spine with an empty scheduled window or a
singleton spine whose first convergent is carried by the displayed rational
endpoint rows. The dyadic radius, stream schedule, handoff row, boundary row,
ledger, and package provenance are then the corresponding finite rows in the
same $\mathsf{BHist}$ packet.

For transport, project the carrier coordinates of
\autoref{def:continuedfraction-carrier}. The classifier of
\autoref{def:continuedfraction-classifier} compares only shared finite
windows, so every transported row is one of the named numerator, denominator,
radius, schedule, handoff, boundary, ledger, or provenance coordinates.

For stability and exactness, read the recurrence ledger before the handoff
rows. The ledger records the finite recurrence steps for convergents, the
handoff consumes only scheduled finite windows, and the real-facing boundary
is the single seal row $b$.
\end{proof}

\begin{theorem}[ContinuedFraction RegSeqRat handoff]
\label{thm:continuedfraction-regseqrat-handoff}
Every accepted $\ContinuedFractionUp$ packet exports a $\RegSeqRatUp$ handoff
only through scheduled finite convergent windows, their $\RatUp$ numerator and
denominator rows, their $\DyadicRatCoreUp$ radius rows, the displayed
recurrence ledger, and the accompanying $\hsame$, $\Cont$, and $\mathsf{Pkg}$
provenance.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_regseqrat\_handoff}
\begin{proof}
Project an accepted packet to the rows $a$, $p$, $q$, $e$, $s$, $r$, $\ell$,
and $P$. The schedule $s$ selects the finite convergent windows, while $p$ and
$q$ provide the rational endpoint rows and $e$ provides the dyadic radius rows
for those windows.

The handoff row $r$ is indexed by exactly that scheduled data. Transport of a
handoff comparison therefore factors through the componentwise $\hsame$ rows,
the displayed $\Cont$ routes, and the package provenance already present in
the carrier packet.

No coordinate of the carrier stores an infinite tail, a quotient class of
tails, or a completed real. The handoff is consequently a finite
regular-sequence surface over the visible convergent ledger.
\end{proof}

\begin{theorem}[ContinuedFraction L10 sibling dependency route]
\label{thm:continuedfraction-l10-sibling-dependency-route}
Every $\RegSeqRatUp$ or $\RealUp$ boundary read of an accepted
$\ContinuedFractionUp$ packet first factors through the existing L10 sibling
route
\autoref{ch:concrete-instances-dyadicratcore-namecert},
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert}, and
\autoref{ch:concrete-instances-real-namecert}. Only after those
$\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows have
been read through the displayed carrier route may the finite continued-fraction
seal be consumed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:continuedfraction-carrier}. The rows
$e,s,r,b$ are exactly the dyadic-radius row, stream observation schedule,
regular-rational handoff, and real seal boundary; there is no second coordinate
for a real-facing read outside these rows.

Apply \autoref{thm:continuedfraction-regseqrat-handoff}. It forces the
$\RegSeqRatUp$ boundary through the scheduled finite convergent windows, their
$\RatUp$ numerator and denominator rows, the $\DyadicRatCoreUp$ radius row, and
the displayed $\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance.

The $\RealUp$ read then consumes the same handoff row before it reaches the
seal coordinate $b$. Thus the boundary route is the concrete-instance sibling
lattice route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and
$\RealUp$, followed by the finite continued-fraction seal and no kernel-only
island remains.
\end{proof}

\begin{theorem}[ContinuedFraction RealUp boundary]
\label{thm:continuedfraction-real-boundary}
Every $\RealUp$ read of an accepted $\ContinuedFractionUp$ packet factors
through the $\RegSeqRatUp$ handoff row and the seal boundary row carried by
\autoref{def:continuedfraction-carrier}. It exposes the same finite
convergent, radius, schedule, recurrence, transport, and provenance ledger,
and it does not assert total continued-fraction expansion for every real,
uniqueness of infinite expansions, measure-theoretic typicality, or quotient
equality of infinite tails.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_real\_boundary}
\leanvariant{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_real\_boundary\_scope}
\begin{proof}
Read the boundary coordinate $b$ of the carrier. Its source is the regular
sequence handoff row $r$, so any real-facing consumer first passes through the
scheduled convergent windows and their rational and dyadic endpoint rows.

The classifier has no separate real-equality clause. Boundary comparisons are
therefore inherited from the finite-window $\RegSeqRatUp$ handoff and from the
transport, continuation, ledger, and provenance rows already visible in the
packet.

Since the carrier stores only a finite partial-quotient spine and finite
window data, it cannot provide a total expansion theorem, an infinite-tail
uniqueness theorem, a typicality theorem, or a quotient equality principle.
The $\RealUp$ boundary is exactly the displayed seal surface.
\end{proof}

\begin{theorem}[ContinuedFraction digit-tail stability]
\label{thm:continuedfraction-digit-tail-stability}
Restrict an accepted $\ContinuedFractionUp$ packet to a displayed finite digit
tail. The restricted packet preserves the same $\RatUp$ convergent rows,
$\StreamNameUp$ schedule, $\RegSeqRatUp$ handoff, and $\RealUp$ boundary ledger
visible in the original packet, with no host infinite expansion and no selected
real endpoint.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_digit\_tail\_stability}
\begin{proof}
Project the carrier of \autoref{def:continuedfraction-carrier} to its finite
partial-quotient spine, convergent rows, schedule, handoff, boundary row,
recurrence ledger, and provenance. The classifier of
\autoref{def:continuedfraction-classifier} compares only the displayed digit
and window rows.

Apply \autoref{thm:continuedfraction-namecert-obligations} to keep the carrier
and classifier obligations inside the finite ledger. The restriction to a digit
tail is therefore a projection of the same recorded rows, not a passage to an
infinite expansion object.

The projected schedule feeds the same finite convergent windows into
\autoref{thm:continuedfraction-regseqrat-handoff}. The real-facing read is then
the boundary of \autoref{thm:continuedfraction-real-boundary}, so the restricted
tail inherits the displayed $\RegSeqRatUp$ handoff and $\RealUp$ ledger without
selecting an endpoint.
\end{proof}

\begin{theorem}[ContinuedFraction recurrence ledger obligation]
\label{thm:continuedfraction-obligation-recurrence-ledger}
For every accepted $\ContinuedFractionUp$ carrier packet, the partial-quotient
spine, the numerator and denominator recurrence rows, and the dyadic radius rows
are finite $\mathsf{BHist}$ rows. Their comparisons are stable exactly along the
displayed $\hsame$ and $\Cont$ routes named by the carrier ledger, and no
recurrence datum is read outside those finite rows.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_recurrence\_ledger\_transport}
\begin{proof}
Project the packet of \autoref{def:continuedfraction-carrier} to the rows
$a$, $p$, $q$, $e$, and $\ell$. These are coordinates of one finite
$\mathsf{BHist}$ record, so the partial quotient, recurrence, and radius data
are already finite rows.

The accepted-carrier clause requires the coordinates to be connected by
displayed $\hsame$ and $\Cont$ routes. Hence transport of a recurrence row or a
radius row is componentwise transport along the ledger routes, with no extra
tail coordinate available.
\end{proof}

\begin{theorem}[ContinuedFraction finite handoff obligation]
\label{thm:continuedfraction-obligation-finite-handoff}
The $\RegSeqRatUp$ handoff of an accepted $\ContinuedFractionUp$ packet is
exhausted by scheduled finite convergent windows, their $\mathsf{Pkg}$
provenance, and the local $\NameCert_{\ContinuedFractionUp}$ row. Every handoff
read factors through those rows together with the displayed recurrence and
dyadic-radius ledger.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_finite\_handoff\_obligation}
\begin{proof}
Project the carrier to the schedule $s$, handoff row $r$, ledger $\ell$, package
row $P$, and local name-certificate registration. By
\autoref{def:continuedfraction-carrier}, the schedule selects the visible
finite convergent windows and the handoff consumes precisely that scheduled
surface.

The package row supplies provenance for the same carrier packet, and the local
$\NameCert_{\ContinuedFractionUp}$ row registers the displayed classifier
discipline. Thus a handoff read can be reconstructed from the scheduled finite
windows, the recurrence and radius rows, $P$, and the local certificate row.
\end{proof}

\begin{theorem}[ContinuedFraction real-boundary obligation]
\label{thm:continuedfraction-obligation-real-boundary}
Every $\RealUp$ boundary read of an accepted $\ContinuedFractionUp$ packet
factors through the same finite $\RegSeqRatUp$ handoff used by the carrier. The
boundary exposes no completed real, no quotient tail, and no host equality
beyond the finite handoff, boundary row, $\mathsf{Pkg}$ provenance, and local
$\NameCert_{\ContinuedFractionUp}$ dependency rows.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_real\_boundary\_transport}
\begin{proof}
Project the packet to the handoff row $r$, boundary row $b$, ledger $\ell$, and
package row $P$. The boundary coordinate in
\autoref{def:continuedfraction-carrier} is explicitly the $\RealUp$ seal row
fed by the regular-sequence handoff.

Since the carrier has no coordinate for a completed real, an infinite quotient
tail, or host equality, no boundary read can expose such an object. Its data are
the finite handoff rows, the seal boundary, the package provenance, and the
local name-certificate dependency rows already present in the packet.
\end{proof}

\begin{theorem}[ContinuedFraction convergent-window standard bridge]
\label{thm:continued-fraction-convergent-window-standard-bridge}
A finite $\ContinuedFractionUp$ packet determines a conservative standard
finite convergent window. Its BEDC readback recovers exactly the $\NatUp$
partial quotient spine, $\RatUp$ convergent rows, $\DyadicRatCoreUp$ radius
row, $\StreamNameUp$ schedule, $\RegSeqRatUp$ handoff, $\RealUp$ seal boundary,
finite ledger, $\mathsf{Pkg}$ provenance, and local
$\NameCert_{\ContinuedFractionUp}$ row.

This bridge excludes total expansion, uniqueness of infinite expansions,
measure-typicality, quotient tails, and completed real equality.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_convergent\_window\_standard\_bridge}
\begin{proof}
Project the finite continued-fraction carrier and classifier. The carrier
coordinates supply the partial quotient spine, rational convergent rows, dyadic
radius row, observation schedule, handoff row, seal boundary, finite ledger,
package provenance, and local name-certificate evidence.

Restrict the digit spine to the displayed finite window. The recurrence
stability and finite handoff obligation identify the same $\RatUp$ convergent
rows and $\DyadicRatCoreUp$ radius row at every displayed position, so the
standard window has no additional convergent coordinate.

Compose \autoref{thm:continuedfraction-obligation-finite-handoff} with
\autoref{thm:continuedfraction-obligation-real-boundary}. The handoff sends the
finite convergent window through $\RegSeqRatUp$, and the real-boundary
obligation seals the resulting $\RealUp$ row without adding quotient-tail or
completed-real equality data.

Reading the conservative standard window back componentwise therefore recovers
the original BEDC finite ledger, package provenance, and local name-certificate
row. Since every step stays inside the finite carrier and classifier rows, the
bridge contains no total expansion theorem, no uniqueness statement for
infinite expansions, no measure-typicality claim, no quotient tail, and no
completed real equality.
\end{proof}

\begin{theorem}[ContinuedFraction scoped boundary]
\label{thm:continuedfraction-scoped-boundary}
The carrier of \autoref{def:continuedfraction-carrier}, classifier of
\autoref{def:continuedfraction-classifier}, NameCert obligations of
\autoref{thm:continuedfraction-namecert-obligations}, $\RegSeqRatUp$ handoff of
\autoref{thm:continuedfraction-regseqrat-handoff}, recurrence ledger of
\autoref{thm:continuedfraction-obligation-recurrence-ledger}, finite handoff of
\autoref{thm:continuedfraction-obligation-finite-handoff}, and $\RealUp$
boundary of \autoref{thm:continuedfraction-obligation-real-boundary} assemble
one scoped $\ContinuedFractionUp$ packet.

The packet is over finite partial quotient windows, rational convergent rows,
dyadic radius rows, scheduled $\StreamNameUp$ observations, $\RegSeqRatUp$
handoff rows, $\RealUp$ seal rows, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$.
\end{theorem}
\begin{proof}
Use \autoref{def:continuedfraction-carrier} and
\autoref{def:continuedfraction-classifier} to identify the visible carrier and
classifier rows. The obligation surface is recorded by
\autoref{thm:continuedfraction-namecert-obligations}.

The recurrence and finite handoff rows are supplied by
\autoref{thm:continuedfraction-obligation-recurrence-ledger} and
\autoref{thm:continuedfraction-obligation-finite-handoff}. The external
handoff and boundary are supplied by
\autoref{thm:continuedfraction-regseqrat-handoff},
\autoref{thm:continuedfraction-real-boundary}, and
\autoref{thm:continuedfraction-obligation-real-boundary}.

Repack these finite rows as the consumer boundary for the accepted
$\ContinuedFractionUp$ packet. The displayed history, equality, continuation,
package, and local certificate dependencies account for every row used by the
packet, so no convergence theorem for arbitrary continued fractions is claimed.
\end{proof}

\begin{theorem}[ContinuedFraction finite-packet standard bridge]
\label{thm:continuedfraction-finite-packet-standard-bridge}
The finite partial-quotient spine, rational convergent rows, dyadic radius
rows, scheduled observation windows, $\RegSeqRatUp$ handoff, $\RealUp$
boundary, displayed $\hsame$ rows, $\Cont$ read routes, $\mathsf{Pkg}$
provenance, and local $\NameCert_{\ContinuedFractionUp}$ row of an accepted
$\ContinuedFractionUp$ packet assemble the standard finite continued-fraction
packet boundary for $\ContinuedFractionUp$. The assembled boundary is exactly
the finite packet surface; it excludes total expansion of every real,
uniqueness of infinite tails, quotient equality, and measure-theoretic claims.
\end{theorem}
\begin{proof}
First build the finite handoff surface. Apply
\autoref{thm:continuedfraction-regseqrat-handoff} to the scheduled convergent
windows, rational numerator and denominator rows, dyadic radius rows,
recurrence ledger, $\hsame$ transport, $\Cont$ routes, and $\mathsf{Pkg}$
provenance.

Next attach the real-facing seal. Apply
\autoref{thm:continuedfraction-real-boundary} and
\autoref{thm:continuedfraction-obligation-real-boundary}; both read the same
$\RegSeqRatUp$ handoff and boundary coordinate, so the real row contributes no
separate completed real, quotient-tail equality, or host equality principle.

Finally repack the displayed rows through
\autoref{thm:continuedfraction-scoped-boundary}. The scoped packet already
contains the finite spine, convergent rows, radius rows, schedule, handoff,
boundary, transport, continuation, package, and local name-certificate rows,
so it is the standard finite continued-fraction packet boundary and nothing
stronger.
\end{proof}

\begin{theorem}[ContinuedFraction prefix convergent window]
\label{thm:continuedfraction-prefix-convergent-window}
Every finite prefix of a certified $\ContinuedFractionUp$ packet determines a
convergent numerator and denominator window whose $\RegSeqRatUp$ handoff reads
only the displayed digit, recurrence, tail, $\hsame$, $\Cont$, package, and
local $\NameCert_{\ContinuedFractionUp}$ rows.

The window contributes no completed real, quotient tail equality, total
expansion theorem, or host equality principle.
\end{theorem}
\begin{proof}
Begin with the scheduled convergent read of
\autoref{thm:continuedfraction-regseqrat-handoff}. It identifies the finite
partial-quotient prefix, numerator and denominator rows, dyadic radius row,
observation schedule, $\hsame$ transport, $\Cont$ routes, and package
provenance available to the regular-sequence consumer.

Next use \autoref{thm:continuedfraction-digit-tail-stability}. The digit and
tail rows remain within the same finite prefix surface, so extending or
restricting a prefix does not add an external host equality or quotient-tail
coordinate.

Apply \autoref{thm:continuedfraction-obligation-recurrence-ledger} to bind the
convergent numerator and denominator rows to the displayed recurrence ledger.
Then repack the same rows through
\autoref{thm:continuedfraction-finite-packet-standard-bridge}. The resulting
consumer window is exactly the finite continued-fraction packet surface named
in the statement.
\end{proof}

\begin{theorem}[ContinuedFraction rational-interval window handoff]
\label{thm:continuedfraction-rational-interval-window-handoff}
Every accepted $\ContinuedFractionUp$ packet whose convergent window is read as
a $\RationalIntervalUp$ endpoint window exposes exactly the finite
partial-quotient spine, the $\RatUp$ numerator and denominator rows, the
$\DyadicRatCoreUp$ radius row, the $\StreamNameUp$ schedule, the
$\RegSeqRatUp$ handoff, the $\RealUp$ seal boundary, displayed $\hsame$
transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and the local
$\NameCert_{\ContinuedFractionUp}$ row.

The handoff exports no completed real, quotient tail, total expansion theorem,
or interval arithmetic law.
\end{theorem}
\begin{proof}
First read the scheduled convergent rows through
\autoref{thm:continuedfraction-regseqrat-handoff}. This identifies the finite
partial-quotient spine, rational numerator and denominator rows, dyadic radius
row, stream schedule, $\hsame$ transports, $\Cont$ routes, and package
provenance as the regular rational source seen by the consumer.

Next apply \autoref{thm:continuedfraction-obligation-finite-handoff}. The
finite handoff exhaustion accounts for the displayed recurrence and endpoint
window rows, so the $\RationalIntervalUp$ consumer can only read the finite
endpoint shape already present in the packet.

Finally use \autoref{thm:continuedfraction-real-boundary}. The real-facing seal
is the boundary row of the same finite handoff, while the rational-interval
endpoint and containment rows are only its finite consumer shape. Thus no
completed real, quotient tail, total expansion theorem, or interval arithmetic
law is exported.
\end{proof}
\leanchecked{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_rational\_interval\_window\_handoff\_certificate}

\begin{theorem}[ContinuedFraction nested cylinder boundary]
\label{thm:continuedfraction-nested-cylinder-boundary}
Let an accepted $\ContinuedFractionUp$ packet display two finite prefix windows
whose smaller prefix is obtained by restricting the larger finite
partial-quotient spine. Then the smaller $\RegSeqRatUp$ handoff and
$\RationalIntervalUp$ endpoint window are exactly the restriction of the larger
packet's finite partial-quotient spine, recurrence ledger, dyadic radius row,
$\StreamNameUp$ schedule, $\hsame$ transport, $\Cont$ routes, $\mathsf{Pkg}$
provenance, and local $\NameCert_{\ContinuedFractionUp}$ rows.

The boundary exports no completed real, quotient tail, total expansion theorem,
or interval arithmetic law.
\end{theorem}
\begin{proof}
First compare the two displayed prefix windows. Apply
\autoref{thm:continuedfraction-digit-tail-stability} to see that restricting
the larger finite prefix preserves exactly the digit, tail, scheduled
observation, $\hsame$, $\Cont$, package, and local name-certificate rows already
visible in the smaller prefix.

Next read both prefixes through
\autoref{thm:continuedfraction-prefix-convergent-window}. The convergent
numerator and denominator rows, recurrence ledger, dyadic radius row, and
$\RegSeqRatUp$ handoff for the smaller window are therefore the restricted rows
of the larger packet, with no extra host equality or quotient-tail coordinate.

Finally apply
\autoref{thm:continuedfraction-rational-interval-window-handoff} and
\autoref{thm:continuedfraction-obligation-real-boundary}. These identify the
rational-interval endpoint window and real-facing boundary as consumer views of
the same finite handoff, so the nested cylinder boundary is precisely the
finite restriction stated above and exports nothing beyond that surface.
\end{proof}

\begin{theorem}[ContinuedFraction common-refinement cylinder exhaustion]
\label{thm:continuedfraction-common-refinement-cylinder-exhaustion}
Let $P$ and $Q$ be accepted $\ContinuedFractionUp$ packets whose finite prefix
cylinders overlap, and let a finite consumer compare the two packets only
through that overlap. Then the comparison refines to a displayed common prefix
cylinder, and the common consumer surface is exactly the $\RegSeqRatUp$
handoff, the $\RationalIntervalUp$ endpoint window, the $\DyadicRatCoreUp$
radius row, the $\StreamNameUp$ schedule, the $\RealUp$ boundary row, the
displayed $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
the local $\NameCert_{\ContinuedFractionUp}$ row.

The common prefix cylinder exports no completed real equality, quotient tail,
total expansion, or interval arithmetic law.
\end{theorem}
\begin{proof}
First apply \autoref{thm:continuedfraction-nested-cylinder-boundary} to the
overlapping finite prefix cylinders. It restricts both accepted packets to the
same displayed prefix rows: finite partial quotients, recurrence ledger,
scheduled observations, dyadic radius row, transports, routes, provenance, and
local name-certificate data.

Next apply
\autoref{thm:continuedfraction-rational-interval-window-handoff}. The
restricted prefix is read as the rational-interval endpoint window together
with the regular rational handoff, so the consumer sees the interval endpoint
surface only through the displayed finite rows.

Now use \autoref{thm:continuedfraction-obligation-finite-handoff}. The finite
handoff repacks the convergent and recurrence rows into the packet obligation
surface without adding a completed real, quotient tail, or total expansion
coordinate.

Finally apply \autoref{thm:continuedfraction-obligation-real-boundary}. The
real-facing boundary row is the boundary of the same finite cylinder handoff,
and the cited handoff theorems provide exactly the $\RegSeqRatUp$,
$\RationalIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealUp$,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows named in the
statement.
\end{proof}

\begin{theorem}[ContinuedFraction convergent prefix window normal form]
\label{thm:continuedfraction-convergent-prefix-window-normal-form}
Every finite $\RealUp$ or $\RegSeqRatUp$ consumer read of an accepted
$\ContinuedFractionUp$ packet restricted to a certified prefix factors through
one displayed prefix normal form. The normal form consists exactly of the
finite partial-quotient spine, numerator and denominator convergent rows, the
$\DyadicRatCoreUp$ radius row, the $\StreamNameUp$ schedule, the
$\RegSeqRatUp$ handoff, the $\RealUp$ boundary row, visible $\hsame$
transports, visible $\Cont$ routes, $\mathsf{Pkg}$ provenance, and the local
$\NameCert_{\ContinuedFractionUp}$ row.

The factorization is unchanged by restricting to a smaller certified prefix
or by passing to a common overlapping prefix cylinder. It exports no completed
real equality, quotient tail, total expansion theorem, interval arithmetic
law, or host equality principle.
\end{theorem}
\begin{proof}
First apply \autoref{thm:continuedfraction-prefix-convergent-window}. It reads
the certified prefix through the finite partial-quotient spine, numerator and
denominator convergent rows, dyadic radius row, schedule, regular rational
handoff, visible transports, continuation routes, package provenance, and
local name-certificate row.

Next apply
\autoref{thm:continuedfraction-rational-interval-window-handoff}. The
rational-interval view is only the endpoint boundary of the same finite
convergent window, so it does not add an interval arithmetic law or a host
equality principle.

Use \autoref{thm:continuedfraction-nested-cylinder-boundary} for prefix
restriction. The smaller certified prefix inherits exactly the restricted
spine, recurrence, radius, schedule, handoff, boundary, transport,
continuation, package, and local certificate rows from the larger packet.

Finally apply
\autoref{thm:continuedfraction-common-refinement-cylinder-exhaustion}. Any
consumer comparison over overlapping certified prefixes refines to the same
common prefix cylinder, and that cylinder contains precisely the rows listed
in the normal form. Completed real equality, quotient tail, total expansion,
interval arithmetic, and host equality are absent from those finite rows.
\end{proof}

\begin{theorem}[ContinuedFraction dyadic approximation extraction]
\label{thm:continuedfraction-dyadic-approximation-extraction}
Let $P$ be an accepted $\ContinuedFractionUp$ packet whose displayed rows include
a finite convergent window, a $\DyadicRatCoreUp$ radius row, a
$\StreamNameUp$ schedule, a $\RegSeqRatUp$ handoff, and a $\RealUp$ boundary
row. Then the same visible rows determine an accepted
$\DyadicApproximationUp$ packet.

The precision row of the $\DyadicApproximationUp$ packet is the displayed
window precision of $P$, its endpoint row is the transported
$\DyadicRatCoreUp$ convergent/radius endpoint, its window is the scheduled
regular-rational readback, and its ledger is the existing real-boundary
handoff. The extraction introduces no quotient real, infinite-tail equality,
selected endpoint, or completeness principle.
\end{theorem}
\begin{proof}
Start with \autoref{thm:continuedfraction-regseqrat-handoff}. It reads the
accepted continued-fraction prefix as the displayed regular-rational source
window, with the schedule, recurrence ledger, transport rows, continuation
routes, package provenance, and local name-certificate row still visible.

Next apply
\autoref{thm:continuedfraction-rational-interval-window-handoff}. The same
prefix window supplies the finite rational endpoint row, and the
$\DyadicRatCoreUp$ radius row transports that endpoint into the dyadic endpoint
coordinate required by the approximation packet.

Use \autoref{thm:continuedfraction-common-refinement-cylinder-exhaustion} to
identify the finite consumer surface when the packet is restricted or compared
inside a common prefix cylinder. The precision, endpoint, scheduled readback,
ledger, transport, route, provenance, and local certificate rows remain exactly
the displayed rows named in the statement.

Finally apply \autoref{thm:dyadic-approximation-window-obligations} and
\autoref{thm:dyadic-approximation-real-seal-handoff}. These repack the
transported precision, endpoint, window, and ledger rows as an accepted
$\DyadicApproximationUp$ packet and seal its $\RealUp$ boundary through the
existing handoff. Since every coordinate came from a displayed finite row, no
quotient real, infinite-tail equality, selected endpoint, or completeness
principle is added.
\end{proof}

\closureat{ContinuedFractionUp}{seedStr}
\closureat{ContinuedFractionUp}{obligationStr}
\closureat{ContinuedFractionUp}{scopedStr}
\closureat{ContinuedFractionUp}{publicStr}
\closureat{ContinuedFractionUp}{bridgedStr}
\closureat{ContinuedFractionUp}{matureStr}

\begin{closurestatus}{\ContinuedFractionUp}
  \constructivestory{A $\ContinuedFractionUp$ packet is generated by a finite partial-quotient spine, rational convergent rows, dyadic radius rows, scheduled observation windows, a regular-sequence handoff, a real-name seal boundary, and a finite provenance ledger.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:continuedfraction-regseqrat-handoff}, \autoref{thm:continuedfraction-real-boundary}, \autoref{thm:continuedfraction-scoped-boundary}, and \autoref{thm:continuedfraction-finite-packet-standard-bridge} form the bridged public export surface by binding the finite carrier, classifier, recurrence-ledger obligation, regular-sequence handoff obligation, real-boundary obligation, standard finite-packet boundary, and displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ dependencies for continued-fraction packets over existing BEDC kernels.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.ContinuedFractionUp.ContinuedFractionPacket\_convergent\_window\_standard\_bridge}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close total expansion for every real, uniqueness of infinite expansions, measure-theoretic typicality, quotient equality of infinite tails, or machine-checked standard bridges.}
  \upgradepath{No further paper-side theory grade remains for the finite continued-fraction packet; formal verification and bridge checking remain separate.}
\end{closurestatus}
