\chapter{A Concrete Naming Certificate for $\BishopRealUp$}
\label{ch:concrete-instances-bishopreal-namecert}

The $\BishopRealUp$ interface records the Bishop--Bridges 1985 constructive-analysis
reading of real names inside the BEDC certificate layer. Its carrier is not a
Dedekind cut, a quotient real, or a completed host number. It is a finite
certificate surface over regular rational names, locatedness evidence,
apartness evidence, explicit modulus rows, and the visible $\RealUp$ seal.

\begin{definition}[BishopReal regular located carrier]
\label{def:bishopreal-regular-located-carrier}
A $\BishopRealUp$ packet is a finite $\mathsf{BHist}$ row
$$
B=(S,Q,D,M,L,A,E,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $S$ is a $\StreamNameUp$ schedule naming the finite windows through which
the rational approximation stream is inspected;
\item $Q$ is a certified $\RegSeqRatUp$ name read on those scheduled windows;
\item $D$ is the $\DyadicRatCoreUp$ endpoint packet used for finite tolerance
and interval observations;
\item $M$ is the explicit $\ModulusOfConvergenceUp$ row controlling the regular
sequence windows;
\item $L$ is the displayed $\LocatedRealUp$ evidence row;
\item $A$ is the displayed $\ApartnessRealUp$ evidence row;
\item $E$ is the $\RealUp$ seal consumed by downstream real-facing interfaces;
\item $H$ records componentwise $\hsame$ transport for $S,Q,D,M,L,A$, and $E$;
\item $C$ records the visible $\Cont$ routes through which a consumer reaches the
finite stream windows, dyadic endpoint packets, modulus rows, locatedness rows,
apartness rows, and seal row;
\item $P$ is the $\Pkg$ provenance row naming $\DyadicRatCoreUp$,
$\StreamNameUp$, $\RegSeqRatUp$, $\LocatedRealUp$, $\ApartnessRealUp$,
$\ModulusOfConvergenceUp$, and $\RealUp$ as the dependency anchors;
\item $N$ is the local $\NameCert_{\BishopRealUp}$ ledger row.
\end{enumerate}
The carrier predicate is
$\mathsf{BishopRealPacket}(S,Q,D,M,L,A,E,H,C,P,N)$. Its classifier compares two
accepted packets only by passing through common finite stream windows, the same
dyadic endpoint packet family, the displayed modulus rows, the locatedness and
apartness evidence rows, and the visible $\RealUp$ seal. No coordinate stores a
Dedekind cut, quotient real, trichotomy principle, selected limit, or classical
completeness witness.
\end{definition}

\begin{theorem}[BishopReal located-apartness transport]
\label{thm:bishopreal-located-apartness-transport}
For any two accepted $\BishopRealUp$ packets
$B=(S,Q,D,M,L,A,E,H,C,P,N)$ and $B'=(S',Q',D',M',L',A',E',H',C',P',N')$, a
componentwise $\hsame$ comparison of their stream schedules, regular rational
names, dyadic endpoint packets, modulus rows, locatedness rows, apartness rows,
and $\RealUp$ seals transports the local classifier from $B$ to $B'$.
Downstream reads of locatedness or apartness therefore factor through the same
finite stream-window and dyadic-endpoint surface, never through trichotomy or
host real equality.
\end{theorem}
\begin{proof}
Project the two carrier rows through
\autoref{def:bishopreal-regular-located-carrier}. The schedule coordinates give
the only stream windows a consumer may inspect, and the dyadic endpoint
coordinates give the only finite tolerance packets available at those windows.

Transport the regular rational, modulus, locatedness, apartness, and seal rows
componentwise along the displayed $\hsame$ witnesses. Each read is reached
through one of the visible $\Cont$ routes in the carrier, so the transported
packet has the same finite observation shape as the source packet.

The forbidden host data are absent from the carrier. Since no coordinate stores
trichotomy, quotient equality, a cut, or a selected limit, the classifier cannot
export any such principle after transport.
\end{proof}
\leanchecked{BEDC.Derived.BishopRealUp.BishopRealPacket\_located\_apartness\_transport}

\begin{theorem}[BishopReal RegSeqRat readback]
\label{thm:bishopreal-regseqrat-readback}
Every $\RealUp$ seal read exported by an accepted $\BishopRealUp$ packet factors
through the certified $\RegSeqRatUp$ name $Q$, the scheduled finite windows $S$,
the $\DyadicRatCoreUp$ endpoint packets $D$, and the explicit
$\ModulusOfConvergenceUp$ row $M$. The readback exposes only the regular
rational name, its dyadic finite observations, and the displayed real seal.
\end{theorem}
\leanchecked{BEDC.Derived.BishopRealUp.BishopRealPacket\_regseqrat\_readback}
\begin{proof}
Let a downstream consumer read the seal coordinate $E$ of a packet $B$. By the
carrier definition, $E$ is stored together with the schedule $S$, regular name
$Q$, dyadic packet family $D$, and modulus row $M$.

The continuation coordinate $C$ gives the finite routes by which $E$ is reached.
Each such route also names the stream window, dyadic endpoint packet, and
modulus row used for the observation. Thus the seal read has the advertised
regular-sequence handoff as part of its visible packet.

Nothing else remains to read. The packet has no coordinate for a quotient class,
cut membership predicate, choice-selected endpoint, or classical completeness
argument, so the readback is exhausted by $S,Q,D,M$, and $E$.
\end{proof}

\begin{theorem}[BishopReal ledger obligation surface]
\label{thm:bishopreal-ledger-obligation-surface}
The local $\NameCert_{\BishopRealUp}$ ledger surface consists exactly of the
carrier, classifier, stability, readback, and dependency rows displayed by
\autoref{def:bishopreal-regular-located-carrier},
\autoref{thm:bishopreal-located-apartness-transport}, and
\autoref{thm:bishopreal-regseqrat-readback}. Its dependency anchors are
$\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\LocatedRealUp$,
$\ApartnessRealUp$, $\ModulusOfConvergenceUp$, and $\RealUp$.
\end{theorem}
\begin{proof}
The carrier row is the packet of
\autoref{def:bishopreal-regular-located-carrier}. It lists the stream schedule,
regular rational name, dyadic endpoint packet, modulus, locatedness, apartness,
seal, transport, continuation, provenance, and local ledger coordinates.

The classifier and stability rows are supplied by
\autoref{thm:bishopreal-located-apartness-transport}. They compare packets only
through common finite stream windows and componentwise transport of the visible
rows.

The exactness and readback row is
\autoref{thm:bishopreal-regseqrat-readback}. The provenance coordinate $P$ and
ledger coordinate $N$ list precisely the seven dependency anchors named in the
statement, so the ledger surface has no further exported row.
\end{proof}

\begin{theorem}[BishopReal carrier construction obligation]
\label{thm:bishopreal-carrier-construction-obligation}
The carrier obligation for $\BishopRealUp$ is to construct the finite packet
of \autoref{def:bishopreal-regular-located-carrier} from a certified
$\RegSeqRatUp$ name, scheduled $\StreamNameUp$ windows, $\DyadicRatCoreUp$
endpoint packets, a displayed $\ModulusOfConvergenceUp$ row, displayed
$\LocatedRealUp$ and $\ApartnessRealUp$ evidence rows, the visible $\RealUp$
seal, componentwise $\hsame$ transport, finite $\Cont$ routes, $\mathsf{Pkg}$
provenance, and the local $\NameCert_{\BishopRealUp}$ ledger.
\end{theorem}
\begin{proof}
Read the coordinates of \autoref{def:bishopreal-regular-located-carrier}.
They list exactly the regular rational name, finite observation windows,
dyadic endpoint packets, convergence modulus, locatedness and apartness rows,
real seal, transport, continuation, provenance, and local ledger.

The construction obligation is therefore finite: provide those displayed rows
and repack them as the carrier predicate. No Dedekind cut, quotient real,
trichotomy principle, selected limit, or classical completeness coordinate is
available to the constructor.
\end{proof}

\begin{theorem}[BishopReal classifier stability obligation]
\label{thm:bishopreal-classifier-stability-obligation}
The classifier stability obligation for $\BishopRealUp$ is componentwise
transport under $\hsame$ for the $\RegSeqRatUp$, $\LocatedRealUp$,
$\ApartnessRealUp$, $\ModulusOfConvergenceUp$, and $\RealUp$ rows along the
finite $\Cont$ routes displayed in the carrier. Accepted packets may classify
together only through those finite routes and their shared BEDC dependency
surface.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bishopreal-located-apartness-transport}. It transports the
stream schedule, regular rational name, dyadic endpoint packet, modulus row,
locatedness row, apartness row, and $\RealUp$ seal componentwise along the
displayed $\hsame$ witnesses.

The same theorem records that every transported read is reached through one of
the finite $\Cont$ routes in the carrier. Thus the classifier is stable exactly
on the displayed packet surface and does not acquire host real equality,
trichotomy, or a quotient comparison.
\end{proof}

\begin{theorem}[BishopReal readback ledger exhaustion obligation]
\label{thm:bishopreal-readback-ledger-exhaustion-obligation}
The readback-ledger exhaustion obligation for $\BishopRealUp$ is that every
exported $\RealUp$ seal read factors through the certified $\RegSeqRatUp$ name,
the scheduled finite windows, the $\DyadicRatCoreUp$ endpoint packets, the
displayed $\ModulusOfConvergenceUp$ row, and the dependency anchors
$\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\LocatedRealUp$,
$\ApartnessRealUp$, $\ModulusOfConvergenceUp$, and $\RealUp$. The exhausted
ledger excludes Dedekind cuts, quotient reals, trichotomy, selected limits, and
classical completeness.
\end{theorem}
\begin{proof}
First apply \autoref{thm:bishopreal-regseqrat-readback}. It says each
$\RealUp$ seal read passes through the regular rational name, scheduled
windows, dyadic endpoint packets, and explicit convergence modulus.

Then apply \autoref{thm:bishopreal-ledger-obligation-surface}. Its provenance
and local ledger rows list exactly the seven dependency anchors in the
statement, so the readback has no further exported row.

The non-constructive real principles are absent twice: they are not carrier
coordinates, and they are not ledger anchors. The readback surface is therefore
exhausted by the finite BEDC rows already displayed.
\end{proof}

\begin{theorem}[BishopReal public NameCert export]
\label{thm:bishopreal-public-namecert-export}
The carrier construction, classifier stability, $\RegSeqRatUp$ readback,
located-apartness transport, readback-ledger exhaustion, explicit modulus rows,
and $\RealUp$ seal assemble the public $\NameCert_{\BishopRealUp}$ export over
regular rational names. Every public read factors through exactly the displayed
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, $\NameCert$,
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows.

The public export contains no Dedekind cut, quotient real, trichotomy, selected
limit, or classical completeness row.
\end{theorem}
\begin{proof}
First read the carrier from
\autoref{def:bishopreal-regular-located-carrier}. It lists the regular
rational name, finite stream windows, dyadic endpoint packets, convergence
modulus, locatedness and apartness rows, visible real seal, transport,
continuation, provenance, and local naming ledger.

Next apply \autoref{thm:bishopreal-located-apartness-transport} and
\autoref{thm:bishopreal-regseqrat-readback}. These identify the componentwise
transport rows and the $\RealUp$ seal readback as finite reads of the same
constructive-real packet.

Then use \autoref{thm:bishopreal-ledger-obligation-surface},
\autoref{thm:bishopreal-carrier-construction-obligation},
\autoref{thm:bishopreal-classifier-stability-obligation}, and
\autoref{thm:bishopreal-readback-ledger-exhaustion-obligation}. Together they
exhaust the carrier, classifier, ledger, construction, and readback rows named
in the statement.

Project the visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$,
$\NameCert$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows from that
surface. Repacking those rows gives the public $\NameCert_{\BishopRealUp}$
export.

Dedekind cuts, quotient reals, trichotomy, selected limits, and classical
completeness remain outside the export because none is present in the carrier
or ledger surface.
\end{proof}

\begin{theorem}[BishopReal standard finite-packet bridge]
\label{thm:bishopreal-standard-finite-packet-bridge}
\autoref{thm:bishopreal-public-namecert-export},
\autoref{thm:bishopreal-regseqrat-readback}, and
\autoref{thm:bishopreal-readback-ledger-exhaustion-obligation} determine the
standard Bishop-style finite packet bridge for $\BishopRealUp$ over
$\RegSeqRatUp$, $\LocatedRealUp$, $\ApartnessRealUp$,
$\ModulusOfConvergenceUp$, and $\RealUp$. The bridge packet consists only of
the regular rational name, locatedness row, apartness row, modulus row,
$\RealUp$ seal, $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance,
and $\NameCert$ ledger rows displayed by the BEDC carrier.

Consequently the standard constructive-real packet exported by
$\BishopRealUp$ has no Dedekind cut, quotient real, trichotomy, selected limit,
or classical completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.BishopRealUp.BishopRealPacket\_standard\_finite\_packet\_bridge}
\begin{proof}
First project the public export from
\autoref{thm:bishopreal-public-namecert-export}. It supplies the finite
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, $\NameCert$,
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows of the accepted
constructive-real packet.

Next identify the regular rational name and the visible $\RealUp$ seal through
\autoref{thm:bishopreal-regseqrat-readback}. The readback passes only through
the certified $\RegSeqRatUp$ name, scheduled finite windows, dyadic endpoint
packets, and explicit modulus row.

Finally apply \autoref{thm:bishopreal-readback-ledger-exhaustion-obligation}.
It says every standard field of the readback is one of the displayed finite
BEDC rows over $\RegSeqRatUp$, $\LocatedRealUp$, $\ApartnessRealUp$,
$\ModulusOfConvergenceUp$, and $\RealUp$.

The excluded real principles are not present in the public export, not present
in the readback, and not present in the exhausted ledger. The resulting packet
is therefore exactly the standard finite-packet bridge claimed in the
statement.
\end{proof}

\begin{theorem}[BishopReal regular-Cauchy located Real seal]
\label{thm:bishopreal-regular-cauchy-located-real-seal}
Let $B=(S,Q,D,M,L,A,E,H,C,P,N)$ be an accepted $\BishopRealUp$ packet. Suppose
its $\RegSeqRatUp$ name, locatedness row, apartness row, modulus row, and
$\RealUp$ seal are transported along the displayed $\hsame$ witnesses and read
only through the displayed $\Cont$ routes of
\autoref{def:bishopreal-regular-located-carrier}. Then $B$ exports one finite
constructive-real seal surface.

The surface consists exactly of the regular rational name $Q$, the scheduled
finite windows $S$, the dyadic endpoint packets $D$, the locatedness row $L$,
the apartness row $A$, the modulus row $M$, the $\RealUp$ seal $E$, the
visible $\hsame$ transports, the visible $\Cont$ routes, the $\mathsf{Pkg}$
provenance row, and the local $\NameCert_{\BishopRealUp}$ ledger. Every public
read of the accepted packet factors through those rows and through no
Dedekind cut, quotient real, trichotomy principle, selected limit, or
classical completeness witness.
\end{theorem}
\begin{proof}
First read the regular rational and seal coordinates. Apply
\autoref{thm:bishopreal-regseqrat-readback} to identify every $\RealUp$ seal
read with the certified $\RegSeqRatUp$ name, scheduled finite windows,
dyadic endpoint packets, explicit modulus row, and displayed seal.

Next transport the constructive-real evidence rows. Apply
\autoref{thm:bishopreal-located-apartness-transport} to carry the regular
rational name, locatedness row, apartness row, modulus row, and seal row along
the displayed $\hsame$ witnesses and through the same finite $\Cont$ routes.

Now exhaust the public ledger. Apply
\autoref{thm:bishopreal-readback-ledger-exhaustion-obligation} to show that
every exported read is accounted for by the listed dependency anchors and
finite BEDC rows.

Finally apply \autoref{thm:bishopreal-standard-finite-packet-bridge}. It
repackages those rows as the standard Bishop-style finite packet over
$\RegSeqRatUp$, $\LocatedRealUp$, $\ApartnessRealUp$,
$\ModulusOfConvergenceUp$, and $\RealUp$. Since the bridge has no coordinate
for cuts, quotient reals, trichotomy, selected limits, or classical
completeness, the same exclusions hold for the seal surface.
\end{proof}

\begin{theorem}[BishopReal finite constructive-real consumer completeness]
\label{thm:bishopreal-finite-constructive-real-consumer-completeness}
Every finite consumer read of an accepted $\BishopRealUp$ packet factors through
exactly the regular rational name, scheduled finite windows, dyadic endpoint
packets, locatedness row, apartness row, modulus row, visible $\RealUp$ seal,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert_{\BishopRealUp}$ rows
of \autoref{thm:bishopreal-regular-cauchy-located-real-seal}. Conversely those
rows repack as the finite constructive-real consumer surface of the accepted
packet.

Thus the mature consumer surface for $\BishopRealUp$ is precisely the displayed
regular-Cauchy located real packet. It contains no Dedekind cut, quotient real,
trichotomy principle, selected limit, or classical completeness witness.
\end{theorem}
\begin{proof}
Project the accepted carrier through
\autoref{def:bishopreal-regular-located-carrier}. The carrier lists the
regular rational name, scheduled finite windows, dyadic endpoint packets,
locatedness row, apartness row, modulus row, visible seal, transport routes,
package row, and local certificate ledger as the available public coordinates.

Next transport the real evidence through
\autoref{thm:bishopreal-located-apartness-transport} and read back the regular
name through \autoref{thm:bishopreal-regseqrat-readback}. These two results
identify every constructive-real read with the displayed regular rational name,
its finite windows, its dyadic endpoint packets, and its explicit modulus and
locatedness-apartness rows.

Now exhaust the ledger. Apply
\autoref{thm:bishopreal-readback-ledger-exhaustion-obligation} and
\autoref{thm:bishopreal-public-namecert-export}. The first theorem says that no
finite read leaves the displayed ledger, while the second exports that ledger as
the public $\NameCert$ surface of the accepted packet.

Finally apply \autoref{thm:bishopreal-standard-finite-packet-bridge} and
\autoref{thm:bishopreal-regular-cauchy-located-real-seal}. They repack the same
rows as the standard finite constructive-real packet and the regular-Cauchy
located $\RealUp$ seal. Since the carrier and both repackings have no coordinate
for cuts, quotient reals, trichotomy, selected limits, or classical
completeness, those structures cannot be consumed from the finite packet.
\end{proof}

\closureat{BishopRealUp}{seedStr}
\closureat{BishopRealUp}{obligationStr}
\closureat{BishopRealUp}{scopedStr}
\closureat{BishopRealUp}{publicStr}
\closureat{BishopRealUp}{bridgedStr}
\closureat{BishopRealUp}{matureStr}

\begin{closurestatus}{\BishopRealUp}
  \constructivestory{A $\BishopRealUp$ packet is generated from a certified $\RegSeqRatUp$ name, finite stream windows, dyadic endpoint packets, an explicit convergence modulus, locatedness evidence, apartness evidence, componentwise transport rows, continuation routes, package provenance, and the visible $\RealUp$ seal.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:bishopreal-regular-located-carrier}, \autoref{thm:bishopreal-located-apartness-transport}, \autoref{thm:bishopreal-regseqrat-readback}, \autoref{thm:bishopreal-ledger-obligation-surface}, \autoref{thm:bishopreal-carrier-construction-obligation}, \autoref{thm:bishopreal-classifier-stability-obligation}, \autoref{thm:bishopreal-readback-ledger-exhaustion-obligation}, \autoref{thm:bishopreal-public-namecert-export}, \autoref{thm:bishopreal-standard-finite-packet-bridge}, \autoref{thm:bishopreal-regular-cauchy-located-real-seal}, and \autoref{thm:bishopreal-finite-constructive-real-consumer-completeness} name the finite constructive real-neighbor certificate surface, standard bridge, regular-Cauchy located $\RealUp$ seal, and finite constructive-real consumer surface over regular rational names, locatedness, apartness, explicit modulus rows, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Dedekind-cut reals, quotient reals, trichotomy, selected limits, classical completeness, or formal verification of the finite consumer theorem.}
  \upgradepath{No further paper-axis theory grade remains; Lean verification remains on the formal axis.}
\end{closurestatus}
