\chapter{A Concrete Naming Certificate for $\HilbertUp$}
\label{ch:concrete-instances-hilbert-namecert}

The Hilbert-space interface $\HilbertUp$ packages a Banach space whose norm is induced by an inner product. It depends on $\NameCert_{\InnerProductUp}$ (\autoref{ch:concrete-instances-innerproduct-namecert}) and $\NameCert_{\BanachUp}$ (\autoref{ch:concrete-instances-banach-namecert}), and is the substrate for the spectral and orthogonal-decomposition certificates of functional analysis.

\section{Carrier definition}
\label{sec:hilbert-carrier}

\begin{definition}[Compatible inner-product Banach carrier]
\label{def:hilbert-compatible-inner-product-banach-carrier}
A compatible inner-product Banach carrier for $\HilbertUp$ is a history
predicate $X:\mathsf{BHist}\to\mathsf{Prop}$ with point classifier
$\sim_X$ together with three displayed rows over the same carried histories.
The first row is a concrete $\BanachUp$ candidate of
\autoref{def:banach-concrete-carrier}. The second row is an
$\InnerProductUp$ carrier on $X$, including the vector-space structure,
sesquilinear form, conjugate symmetry, linearity, positivity, and
inner-product classifier transport. The third row is a norm-induction ledger
recording that the Banach norm and Banach metric rows are exactly the rows
displayed by the inner-product norm:
$$
\|x\|_{\BanachUp}=\sqrt{\langle x,x\rangle_{\InnerProductUp}}
$$
and
$$
d_{\BanachUp}(x,y)=\|x-y\|_{\BanachUp}
$$
for carried histories $x,y:X$.

The compatibility requirement is literal row sharing, not an isomorphism
postulate: the Banach carrier, the inner-product carrier, and the
norm-induced metric ledger expose the same point carrier $X$ and the same
classifier $\sim_X$. Every accepted Hilbert row therefore carries a visible
Banach surface, a visible inner-product surface, and a ledger explaining why
the Banach metric is the metric induced by the inner-product norm.
\end{definition}

\begin{definition}[Hilbert singleton empty-history carrier]
\label{def:hilbert-singleton-empty-history-carrier}
The concrete $\HilbertUp$ carrier is the singleton empty-history Banach
carrier of \autoref{def:banach-singleton-empty-history-instance}, read over
the singleton empty-history vector space of
\autoref{def:singleton-empty-history-vecspace-instance}. Thus the vector
carrier is $A_{\emp}$, the vector classifier is $\rho_{\emp}$, the normed
carrier is the singleton $\BanachUp$ carrier, and the norm is
$\nu_{\emp}$.

The inner-product row is the constant-zero RealUp endpoint
$$
\langle m,n\rangle_{\emp}:=0_{\mathsf{Real}}^{c}
$$
for all displayed vector histories $m,n:\mathsf{BHist}$. Its scalar-side
classifier is $\mathsf{RealConstantHistoryClassifier}$. The induced norm row
is read by the same constant endpoint:
$$
\|\!m\!\|_{\langle,\rangle_{\emp}}:=0_{\mathsf{Real}}^{c}.
$$
Hence the induced norm is the singleton $\NormUp$ norm $\nu_{\emp}$ from
\autoref{def:singleton-empty-history-norm-instance}. The ledger records the
singleton vector-space source, the Banach singleton carrier, and the RatUp zero
witness sealed as the RealUp constant endpoint.
\end{definition}

\section{The certificate}
\label{sec:hilbert-certificate}

\begin{theorem}[Hilbert induced norm Banach compatibility]
\label{thm:hilbert-induced-norm-banach-compatibility}
Every accepted compatible inner-product Banach carrier exposes the same point
carrier and classifier to its $\BanachUp$ and $\InnerProductUp$ surfaces.
Moreover, $\hsame$ transport preserves the norm-induced Banach metric witness:
if $x\sim_X x'$ and $y\sim_X y'$, then a displayed
$\mathsf{BanachMetricWitness}_X(x,y,d)$ row transports to the corresponding
$\mathsf{BanachMetricWitness}_X(x',y',d')$ row classified by the same
inner-product norm ledger.
\end{theorem}
\begin{proof}
Unpack the compatible carrier of
\autoref{def:hilbert-compatible-inner-product-banach-carrier}. The Banach row
and inner-product row have the same endpoint predicate $X$ and classifier
$\sim_X$ by definition, so no change of carrier or classifier is introduced.

Apply \autoref{thm:banach-norm-induced-metric-compatibility} to read the
Banach metric through the displayed norm row. The Hilbert ledger identifies
that norm row with the inner-product norm row, so the metric witness remains
the norm-induced Banach witness after this reading.

Finally use the componentwise $\hsame$ transport rows supplied by the Banach
surface and the inner-product surface. They move the vector representative,
difference row, inner-product norm row, and RealUp distance endpoint together,
and repack the transported rows as
$\mathsf{BanachMetricWitness}_X(x',y',d')$ over the same classifier
$\sim_X$.
\end{proof}

\begin{theorem}[Hilbert complete inner-product limit stability]
\label{thm:hilbert-complete-inner-product-limit-stability}
Let $H$ be a compatible inner-product Banach carrier. For any regular Cauchy
stream $s$ over the Banach metric, any displayed
$\mathsf{CompleteMetricLimitWitness}(X,s,\mu,\ell,L)$ supplied by the Banach
row, and any proof that the stream observations remain in the inner-product
carrier, there is a Hilbert limit witness with the same selected limit
$\ell$, the same limit name $L$, and the same classifier $\sim_X$.
\end{theorem}
\begin{proof}
Start from the Banach row contained in $H$. Its completeness field supplies
the displayed $\mathsf{CompleteMetricLimitWitness}(X,s,\mu,\ell,L)$ and its
carrier endpoint data through \autoref{def:banach-concrete-carrier}.

The observation-stability hypothesis says that the same stream is carried by
the inner-product surface of $H$. Use the inner-product carrier stability row
to transport all observation representatives through $\sim_X$ while retaining
the displayed inner-product norm rows named by the Hilbert ledger.

Apply \autoref{thm:hilbert-induced-norm-banach-compatibility} to identify the
transported Banach distance witnesses with the inner-product norm-induced
ones. The selected limit endpoint $\ell$ and limit name $L$ are therefore not
changed; they are merely read as Hilbert rows over the same carrier,
classifier, and visible metric ledger.
\end{proof}

\begin{theorem}[Hilbert NameCert obligation surface]
\label{thm:hilbert-namecert-obligation-surface}
The compatible carrier of
\autoref{def:hilbert-compatible-inner-product-banach-carrier}, its induced
classifier $\sim_X$, the norm-metric compatibility of
\autoref{thm:hilbert-induced-norm-banach-compatibility}, the complete-limit
stability of \autoref{thm:hilbert-complete-inner-product-limit-stability}, and
the visible ledger joining the Banach and inner-product rows assemble the
paper-side $\NameCert_{\HilbertUp}$ obligation surface. This surface records
the Hilbert carrier, classifier, norm-induced Banach metric, complete-limit
stability, and ledger provenance; it does not assert a standard
Hilbert-space bridge.
\end{theorem}
\begin{proof}
Use the compatible carrier definition for the public carrier field. It
already contains the Banach row, the inner-product row, and the row-sharing
ledger binding both surfaces to the same $X$ and $\sim_X$.

Use \autoref{thm:hilbert-induced-norm-banach-compatibility} for the
norm-metric field. It identifies the Banach metric witness as the metric
induced by the inner-product norm and records that $\hsame$ transport
preserves that witness componentwise.

Use \autoref{thm:hilbert-complete-inner-product-limit-stability} for the
limit-stability field. It consumes the Banach
$\mathsf{CompleteMetricLimitWitness}$ row together with the inner-product
observation-stability row and returns the same selected limit as a Hilbert
limit witness.

The remaining fields are inherited from the source rows: the Banach surface
provides the complete normed metric obligations, the inner-product surface
provides the sesquilinear, symmetry, positivity, and classifier-stability
obligations, and the ledger records exactly which displayed rows are shared.
Thus the paper-side $\NameCert_{\HilbertUp}$ obligation surface is assembled
without adding any standard bridge claim.
\end{proof}

\begin{theorem}[Hilbert singleton inner-product norm compatibility]
\label{thm:hilbert-singleton-inner-product-norm-compatibility}
For the carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}, the norm induced by
$\langle-,-\rangle_{\emp}$ agrees with the singleton norm $\nu_{\emp}$:
$$
\mathsf{RealConstantHistoryClassifier}
  (\|\!m\!\|_{\langle,\rangle_{\emp}},\nu_{\emp}(m))
$$
for every carried $m:\mathsf{BHist}$. Moreover positive definiteness of the
inner-product row collapses to the singleton vector classifier:
$$
\mathsf{RealConstantHistoryClassifier}
  (\langle m,m\rangle_{\emp},0_{\mathsf{Real}}^{c})
\Longleftrightarrow
\rho_{\emp}(m,\emp).
$$
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_inner\_product\_norm\_compatibility}
\begin{proof}
The induced norm and $\nu_{\emp}$ are both the constant endpoint
$0_{\mathsf{Real}}^{c}$. The carrier and classifier rows of
\autoref{thm:singleton-empty-history-norm-carrier-classifier} give the RealUp
constant-history classifier for this endpoint, so the two norm presentations
are classified together.

For positive definiteness in the forward direction, the inner-product value
$\langle m,m\rangle_{\emp}$ is again $0_{\mathsf{Real}}^{c}$. Apply
\autoref{thm:singleton-empty-history-vecspace-endpoint-collapse} to the
carried vector endpoint. It identifies $m$ with $\emp$ under $\rho_{\emp}$.

For the reverse direction, assume $\rho_{\emp}(m,\emp)$. The inner-product row
does not inspect the representative; it returns $0_{\mathsf{Real}}^{c}$ for
every pair. The zero-exactness boundary of
\autoref{thm:singleton-empty-history-norm-zero-exactness}, together with the
constant-real classifier already supplied by the singleton norm carrier,
repackages the row as
$\mathsf{RealConstantHistoryClassifier}
(\langle m,m\rangle_{\emp},0_{\mathsf{Real}}^{c})$.
\end{proof}

\begin{theorem}[Hilbert singleton complete normed certificate]
\label{thm:hilbert-singleton-complete-normed-certificate}
The normed part of
\autoref{def:hilbert-singleton-empty-history-carrier} is complete. Every
regular Cauchy stream carried by $A_{\emp}$ has selected limit $\emp$, every
late distance-to-limit row is classified with $0_{\mathsf{Real}}^{c}$, and any
two selected Banach limit witnesses are classified by $\rho_{\emp}$.
\end{theorem}
\begin{proof}
Use the singleton Banach carrier of
\autoref{def:banach-singleton-empty-history-instance}. Its metric is the
constant RealUp zero endpoint and its limit-selection rule sends every
certified regular Cauchy stream to $\emp$.

The complete-metric laws are supplied by
\autoref{thm:singleton-complete-metric-laws}. They give the carried singleton
limit, the empty modulus, and the late-observation ledgers for the constant
zero metric.

Finally apply
\autoref{thm:banach-singleton-limit-namecert-uniqueness} to compare any two
Banach limit witnesses for the same stream. In the singleton vector carrier,
\autoref{thm:singleton-empty-history-vecspace-endpoint-collapse} reads that
comparison as the classifier row $\rho_{\emp}$, so the complete normed
certificate is the Banach singleton certificate read through the Hilbert
carrier.
\end{proof}

\begin{theorem}[Hilbert singleton classifier source boundary]
\label{thm:hilbert-singleton-classifier-source-boundary}
The carrier of
\autoref{def:hilbert-singleton-empty-history-carrier} exposes exactly the
singleton vector-space carrier $A_{\emp}$ and classifier $\rho_{\emp}$. The
Banach row, the singleton $\NormUp$ row, the inner-product row, and the
Hilbert row all read their vector endpoints from the same
$\mathsf{BHist}$ source; no carrier endpoint and no vector classifier outside
the singleton empty-history source is used.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_classifier\_source\_boundary}
\begin{proof}
Unfold the Hilbert singleton carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}. Its first displayed
source is the singleton vector-space instance of
\autoref{def:singleton-empty-history-vecspace-instance}, so the visible vector
carrier is $A_{\emp}$ and the visible classifier is $\rho_{\emp}$.

The normed row is the singleton norm instance of
\autoref{def:singleton-empty-history-norm-instance}, and the Banach row is the
singleton Banach instance of
\autoref{def:banach-singleton-empty-history-instance}. Both rows are stated
over the same singleton vector carrier and therefore project the same
$A_{\emp}$ and $\rho_{\emp}$ fields.

The Hilbert row adds only the constant inner-product display over those
carried histories. Since that display takes arguments
$m,n:\mathsf{BHist}$ from the already fixed singleton carrier, the Hilbert
surface has the same endpoint source as the vector-space, norm, and Banach
surfaces.
\end{proof}

\begin{theorem}[Hilbert singleton constant inner-product transport]
\label{thm:hilbert-singleton-constant-inner-product-transport}
For the carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}, if
$\rho_{\emp}(m,m')$ and $\rho_{\emp}(n,n')$, then the corresponding
inner-product endpoints are related by the constant-real classifier:
$$
\mathsf{RealConstantHistoryClassifier}
  (\langle m,n\rangle_{\emp},\langle m',n'\rangle_{\emp}).
$$
The induced norm endpoints are transported along the same scalar classifier,
so
$$
\mathsf{RealConstantHistoryClassifier}
  (\|\!m\!\|_{\langle,\rangle_{\emp}},\|\!m'\!\|_{\langle,\rangle_{\emp}})
$$
holds over the singleton vector classifier.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_constant\_inner\_product\_transport}
\begin{proof}
The inner-product operation in
\autoref{def:hilbert-singleton-empty-history-carrier} is constant: every
ordered pair of carried histories is sent to the endpoint
$0_{\mathsf{Real}}^{c}$. Thus the two endpoints
$\langle m,n\rangle_{\emp}$ and $\langle m',n'\rangle_{\emp}$ are the same
constant RealUp zero endpoint.

The singleton norm carrier supplies the scalar-side classifier
$\mathsf{RealConstantHistoryClassifier}$ for this constant endpoint. Applying
that classifier to the two constant zero presentations gives the displayed
inner-product transport row.

For the induced norm, use
\autoref{thm:hilbert-singleton-inner-product-norm-compatibility}. It reads
the induced norm as the singleton norm $\nu_{\emp}$, whose endpoint is again
the same constant RealUp zero row. The norm transport conclusion is therefore
the same constant-real classifier row read through the induced norm display.
\end{proof}

\begin{theorem}[Hilbert singleton ledger exhaustion]
\label{thm:hilbert-singleton-ledger-exhaustion}
Every row consumed by the singleton $\HilbertUp$ package is one of the
singleton vector-space source row, the singleton $\NormUp$ row, the singleton
Banach completion row, or the constant RealUp zero inner-product row. The
package introduces no $\StdBridge$ row, no second vector carrier, and no
carrier source beyond the $\mathsf{BHist}$ singleton ledger recorded in
\autoref{def:hilbert-singleton-empty-history-carrier}.
\end{theorem}
\begin{proof}
The carrier and classifier accounting is fixed by
\autoref{thm:hilbert-singleton-classifier-source-boundary}. It leaves only
the singleton vector-space source $A_{\emp}$, $\rho_{\emp}$, and the
$\mathsf{BHist}$ endpoint source available to the Hilbert package.

The scalar stability accounting is fixed by
\autoref{thm:hilbert-singleton-constant-inner-product-transport}. It says
that both the inner-product endpoint and the induced norm endpoint are
transported by $\mathsf{RealConstantHistoryClassifier}$ at the constant
RealUp zero row.

The completeness accounting is exactly
\autoref{thm:hilbert-singleton-complete-normed-certificate}, which reads the
singleton Banach completion row through the Hilbert carrier. Together with
the ledger sentence in
\autoref{def:hilbert-singleton-empty-history-carrier}, these rows exhaust the
package: vector source, norm source, Banach completion source, and constant
inner-product zero source are all named, and no standard bridge or outside
carrier source remains.
\end{proof}

\begin{theorem}[Hilbert NameCert obligation package]
\label{thm:hilbert-namecert-obligation-package}
The carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}, together with the
classifier-source boundary
\autoref{thm:hilbert-singleton-classifier-source-boundary}, the
constant-inner-product transport row
\autoref{thm:hilbert-singleton-constant-inner-product-transport}, the ledger
exhaustion row \autoref{thm:hilbert-singleton-ledger-exhaustion}, and the
certificate rows
\autoref{thm:hilbert-singleton-inner-product-norm-compatibility} and
\autoref{thm:hilbert-singleton-complete-normed-certificate}, assembles the
paper-side $\NameCert_{\HilbertUp}$ obligation package. Its carrier is
$A_{\emp}$, its classifier is $\rho_{\emp}$, its inner-product row is
$\langle-,-\rangle_{\emp}$, its induced norm is $\nu_{\emp}$, its completeness
field is the singleton Banach limit rule, its ledger is the union of the
singleton vector-space, norm, inner-product zero-row, and Banach-completion
ledgers, and its bridge status is none.
\end{theorem}
\begin{proof}
The carrier and classifier fields are supplied by
\autoref{thm:hilbert-singleton-classifier-source-boundary}. The Banach source
is exactly \autoref{def:banach-singleton-empty-history-instance}, so the
normed carrier and metric rows are already present before the Hilbert row is
attached.

The inner-product compatibility field is
\autoref{thm:hilbert-singleton-inner-product-norm-compatibility}. It identifies
the induced norm with $\nu_{\emp}$ and reflects positive definiteness back to
the singleton classifier against $\emp$.

The transport field is
\autoref{thm:hilbert-singleton-constant-inner-product-transport}. It records
that replacing either input by a $\rho_{\emp}$-classified endpoint leaves the
inner-product endpoint and the induced norm endpoint inside the same
$\mathsf{RealConstantHistoryClassifier}$ row.

The completeness field is
\autoref{thm:hilbert-singleton-complete-normed-certificate}. It supplies the
selected limit, the convergence ledgers, and classifier uniqueness for
regular Cauchy streams in the norm induced by the inner product.

\autoref{thm:hilbert-singleton-ledger-exhaustion} supplies the ledger field.
Combining these rows gives the local $\HilbertUp$ naming certificate: the
traditional target is the one-point Hilbert space, the BEDC source is
$\mathsf{BHist}$, the carrier and classifier are $A_{\emp}$ and
$\rho_{\emp}$, the stability rows are constant-zero classifier transport, the
exactness row is positive definiteness against $\emp$, the ledger records the
shared singleton provenance, and no standard bridge is claimed here.
\end{proof}

\begin{theorem}[Hilbert singleton source compatibility]
\label{thm:hilbert-singleton-source-compatibility}
For the carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}, the singleton
$\VecSpaceUp$, $\NormUp$, and $\BanachUp$ sources read one carried predicate
and one classifier:
$$
A_{\mathsf{Hilbert},\emp}=A_{\emp}
\quad\text{and}\quad
\rho_{\mathsf{Hilbert},\emp}=\rho_{\emp}.
$$
The norm row is the singleton norm endpoint $\nu_{\emp}$, the Banach metric
row is the norm-induced constant RealUp zero distance, and the inner-product
row returns $0_{\mathsf{Real}}^{c}$ under
$\mathsf{RealConstantHistoryClassifier}$ for every displayed pair
$m,n:\mathsf{BHist}$.
\end{theorem}
\begin{proof}
Unfold the Hilbert carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}. Its vector source is
the singleton empty-history vector space, so the displayed carrier and
classifier are $A_{\emp}$ and $\rho_{\emp}$ before the norm or inner-product
rows are attached.

For the norm source, apply
\autoref{thm:singleton-empty-history-norm-carrier-classifier}. It reads every
carried norm endpoint as $\nu_{\emp}$ and classifies all displayed singleton
norm values through $\mathsf{RealConstantHistoryClassifier}$ at
$0_{\mathsf{Real}}^{c}$.

For the Banach source, the carrier is
\autoref{def:banach-singleton-empty-history-instance}. Its metric is induced
from the same singleton norm and therefore exposes the same carried predicate,
the same classifier, and the same constant RealUp zero endpoint surface.

The inner-product row is defined separately but uses no additional carrier
data. It returns $0_{\mathsf{Real}}^{c}$ for every pair
$m,n:\mathsf{BHist}$, and
\autoref{thm:singleton-empty-history-vecspace-endpoint-collapse} supplies the
underlying vector endpoint collapse used by all three sources.
\end{proof}

\begin{theorem}[Hilbert singleton endpoint readback]
\label{thm:hilbert-singleton-endpoint-readback}
Every norm endpoint, inner-product self-value, and Banach distance endpoint
exposed by the Hilbert singleton package is classified with
$0_{\mathsf{Real}}^{c}$ by
$\mathsf{RealConstantHistoryClassifier}$. Concretely, for carried histories
$m,n:\mathsf{BHist}$,
$$
\mathsf{RealConstantHistoryClassifier}(\nu_{\emp}(m),0_{\mathsf{Real}}^{c}),
\quad
\mathsf{RealConstantHistoryClassifier}
  (\langle m,m\rangle_{\emp},0_{\mathsf{Real}}^{c}),
\quad
\mathsf{RealConstantHistoryClassifier}(d_{\emp}(m,n),0_{\mathsf{Real}}^{c})
$$
are the public endpoint rows of the package.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_endpoint\_readback}
\begin{proof}
The norm endpoint row is the zero-exactness surface of
\autoref{thm:singleton-empty-history-norm-zero-exactness}. On the singleton
carrier, the only accepted vector endpoint is classified with $\emp$, so the
norm value is read as $0_{\mathsf{Real}}^{c}$ by the constant-real
classifier.

The inner-product self-value is handled by
\autoref{thm:hilbert-singleton-inner-product-norm-compatibility}. It identifies
the induced norm with $\nu_{\emp}$ and states that the diagonal
inner-product row is classified with the constant RealUp zero endpoint
exactly at the singleton vector classifier boundary.

The Banach distance endpoint comes from
\autoref{def:banach-singleton-empty-history-instance}. Its metric row is the
norm-induced singleton distance, and
\autoref{thm:banach-singleton-empty-history-carrier-classifier} reads every
displayed distance as the same constant RealUp zero endpoint.
\end{proof}

\begin{definition}[Hilbert singleton projection witness]
\label{def:hilbert-singleton-projection-witness}
For the carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}, a Hilbert singleton
projection witness from a carried endpoint $m$ to a projected endpoint $p$ is
the concrete tuple
$$
\bigl(A_{\emp}(m),A_{\emp}(p),\rho_{\emp}(p,\emp),
  \mathsf{RealConstantHistoryClassifier}
    (\|\!m-p\!\|_{\langle,\rangle_{\emp}},0_{\mathsf{Real}}^{c}),
  \mathsf{RealConstantHistoryClassifier}
    (\langle m-p,p\rangle_{\emp},0_{\mathsf{Real}}^{c})\bigr).
$$
The first two entries record that both endpoints are carried by the
singleton empty-history carrier, the third entry fixes the concrete projected
endpoint ledger, the fourth entry is the constant RealUp zero readback for
the induced norm, and the fifth entry is the constant inner-product row
against the projected endpoint.
\end{definition}
\leandef{BEDC.Derived.HilbertUp.HilbertSingletonProjectionWitness}

\begin{theorem}[Hilbert singleton projection existence]
\label{thm:hilbert-singleton-projection-existence}
Every carried endpoint $m$ of
\autoref{def:hilbert-singleton-empty-history-carrier} admits a Hilbert
singleton projection witness with projected endpoint $\emp$.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingletonProjection\_existence}
\begin{proof}
First read the Hilbert carrier through
\autoref{thm:hilbert-singleton-source-compatibility}. The endpoint $m$ is
carried by $A_{\emp}$, and the projected endpoint $\emp$ is carried by the
same singleton source and classified with itself by $\rho_{\emp}$.

Next use \autoref{thm:hilbert-singleton-endpoint-readback}. It identifies
the induced norm endpoint exposed by the Hilbert singleton package with the
constant RealUp zero endpoint under
$\mathsf{RealConstantHistoryClassifier}$.

Finally apply
\autoref{thm:hilbert-singleton-constant-inner-product-transport}. The
inner-product row is constant at $0_{\mathsf{Real}}^{c}$, so
$\langle m-\emp,\emp\rangle_{\emp}$ is classified with the same constant
RealUp zero endpoint. These rows are exactly the tuple required by
\autoref{def:hilbert-singleton-projection-witness}.
\end{proof}

\begin{theorem}[Hilbert singleton projection idempotence]
\label{thm:hilbert-singleton-projection-idempotent}
If $p$ is the projected endpoint in a Hilbert singleton projection witness
for $m$, then the Hilbert singleton projection witness for $p$ has projected
endpoint $\emp$, and this endpoint is classified with $p$ by $\rho_{\emp}$.
\end{theorem}
\begin{proof}
Unpack the witness of
\autoref{def:hilbert-singleton-projection-witness}. One of its displayed
rows is $\rho_{\emp}(p,\emp)$, so the projected endpoint is already fixed at
the singleton empty-history representative.

Apply
\autoref{thm:singleton-empty-history-vecspace-endpoint-collapse} to the
carried endpoint $p$. The singleton carrier has no second vector endpoint, so
the endpoint used by the projection witness of $p$ is again $\emp$.

Combining the displayed row $\rho_{\emp}(p,\emp)$ with this singleton
collapse gives the idempotence claim: projecting the projected endpoint does
not leave the $\rho_{\emp}$-class of $p$.
\end{proof}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingletonProjection\_witness\_idempotent}

\begin{theorem}[Hilbert singleton projection orthogonal zero]
\label{thm:hilbert-singleton-projection-orthogonal-zero}
Let $p$ be the projected endpoint in a Hilbert singleton projection witness
for $m$. For every carried endpoint $n$ of
\autoref{def:hilbert-singleton-empty-history-carrier}, the residual
inner-product row is classified with $0_{\mathsf{Real}}^{c}$:
$$
\mathsf{RealConstantHistoryClassifier}
  (\langle m-p,n\rangle_{\emp},0_{\mathsf{Real}}^{c}).
$$
\end{theorem}
\begin{proof}
The inner-product operation in
\autoref{def:hilbert-singleton-empty-history-carrier} is constant at
$0_{\mathsf{Real}}^{c}$ for every displayed pair of carried histories. Thus
the residual row $\langle m-p,n\rangle_{\emp}$ does not depend on the
representatives $m$, $p$, or $n$.

Use \autoref{thm:hilbert-singleton-endpoint-readback} to read this displayed
inner-product endpoint through the Hilbert singleton package. The scalar
classifier is $\mathsf{RealConstantHistoryClassifier}$, and its endpoint is
the constant RealUp zero endpoint.

The witness assumption supplies the carried projected endpoint and the
$\rho_{\emp}(p,\emp)$ row from
\autoref{def:hilbert-singleton-projection-witness}. Hence the residual
inner-product row is the same constant-zero row after the projection ledger is
unpacked.
\end{proof}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingletonProjection\_orthogonal\_zero}

\begin{theorem}[Hilbert singleton projection uniqueness]
\label{thm:hilbert-singleton-projection-uniqueness}
Let $s$ be an accepted regular Cauchy stream in the Hilbert singleton carrier.
Any two Hilbert singleton limit or projection witnesses for $s$ are identified
by $\rho_{\emp}$. Consequently they project to the same Banach limit, the same
singleton $\NormUp$ zero endpoint, and the same inner-product zero row.
\end{theorem}
\begin{proof}
First read each Hilbert limit witness through the complete normed field of
\autoref{thm:hilbert-singleton-complete-normed-certificate}. This places the
limit witnesses on the Banach singleton surface for the same accepted regular
Cauchy stream.

Apply \autoref{thm:banach-singleton-limit-namecert-uniqueness} to the two
Banach-surface rows. It identifies their displayed limits first by $\hsame$
and then by the singleton vector classifier $\rho_{\emp}$.

For a projection witness, use
\autoref{def:hilbert-singleton-projection-witness} to read the projected
endpoint as a carried singleton endpoint with displayed row
$\rho_{\emp}(p,\emp)$. Then apply
\autoref{thm:hilbert-singleton-projection-idempotent}. It says that the
projection branch remains in the same $\rho_{\emp}$-class after projecting
again.

Finally use \autoref{thm:hilbert-singleton-source-compatibility}. The
Hilbert carrier, the normed carrier, and the Banach carrier all expose the
same classifier surface, so the $\rho_{\emp}$ comparison just obtained is
simultaneously the Banach limit comparison, the NormUp zero-endpoint
comparison, and the inner-product row comparison. The endpoint readback is the
constant RealUp zero row supplied by
\autoref{thm:hilbert-singleton-endpoint-readback}.
\end{proof}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingletonProjection\_uniqueness}

\begin{theorem}[Hilbert singleton limit inner-product carrier]
\label{thm:hilbert-singleton-limit-inner-product-carrier}
Let $s$ be an accepted regular Cauchy stream in the Hilbert singleton carrier,
and let $\ell:\mathsf{BHist}$ be the selected complete-limit witness exposed by
the Hilbert singleton package. Then $\ell$ is carried by $A_{\emp}$, the
classifier $\rho_{\emp}$ classifies $\ell$ with $\emp$, and the inner-product
row of the limit is the constant RealUp zero endpoint:
$$
\mathsf{RealConstantHistoryClassifier}
  (\langle \ell,\ell\rangle_{\emp},0_{\mathsf{Real}}^{c}).
$$
\end{theorem}
\begin{proof}
First use the complete normed field of
\autoref{thm:hilbert-singleton-complete-normed-certificate}. It reads the
accepted Hilbert Cauchy stream as the Banach singleton completion problem and
places its selected limit witness on the Banach limit row.

Apply \autoref{thm:banach-singleton-limit-namecert-uniqueness} to the selected
Banach limit row. Since the Banach singleton carrier and classifier are
$A_{\emp}$ and $\rho_{\emp}$, the selected witness is classified with $\emp$
by $\rho_{\emp}$.

Finally transport the same witness back through
\autoref{thm:hilbert-singleton-source-compatibility}. The Hilbert and Banach
surfaces share the carrier and classifier, while
\autoref{thm:hilbert-singleton-endpoint-readback} reads the diagonal
inner-product value as the constant RealUp zero endpoint.
\end{proof}

\begin{theorem}[Hilbert singleton norm-induced metric classifier]
\label{thm:hilbert-singleton-norm-induced-metric-classifier}
For carried histories $m,n:\mathsf{BHist}$ on the Hilbert singleton carrier,
the Banach metric endpoint $d_{\emp}(m,n)$, the induced-norm endpoint
$\|m-n\|_{\langle,\rangle_{\emp}}$, and the constant endpoint
$0_{\mathsf{Real}}^{c}$ are classified by
$\mathsf{RealConstantHistoryClassifier}$. Consequently the metric classifier
on the singleton Hilbert carrier is exactly the norm-induced classifier
obtained from the constant inner product.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_norm\_induced\_metric\_classifier}
\begin{proof}
Begin with
\autoref{thm:hilbert-singleton-inner-product-norm-compatibility}. It identifies
the norm induced by the constant inner product with the singleton norm
$\nu_{\emp}$ on every carried history.

Next apply
\autoref{thm:hilbert-induced-norm-banach-compatibility}. The Banach distance
row attached to the singleton Hilbert package is the distance induced by that
same norm, so $d_{\emp}(m,n)$ and
$\|m-n\|_{\langle,\rangle_{\emp}}$ name the same endpoint surface for the
classifier.

It remains to read the endpoint. By
\autoref{thm:hilbert-singleton-endpoint-readback}, the norm endpoint, the
inner-product endpoint, and the Banach metric endpoint are all classified by
$\mathsf{RealConstantHistoryClassifier}$ at $0_{\mathsf{Real}}^{c}$.
\end{proof}

\begin{theorem}[Hilbert singleton semantic NameCert surface]
\label{thm:hilbert-singleton-semantic-namecert-surface}
The singleton carrier $A_{\emp}$, classifier $\rho_{\emp}$, constant
inner-product row, induced norm row, complete-limit row, norm-induced metric
classifier, projection uniqueness row, and ledger exhaustion row together form
the concrete paper-side SemanticNameCert surface for $\HilbertUp$. This surface
does not assert a standard bridge; it records the singleton Hilbert certificate
inside the BEDC BHist and NameCert interfaces.
\end{theorem}
\begin{proof}
Start from \autoref{thm:hilbert-namecert-obligation-package}. It assembles the
carrier, classifier, vector source, scalar source, norm source, Banach source,
and Hilbert inner-product source into the Hilbert singleton obligation package.

The complete-limit carrier row is supplied by
\autoref{thm:hilbert-singleton-limit-inner-product-carrier}. The metric row is
the norm-induced classifier of
\autoref{thm:hilbert-singleton-norm-induced-metric-classifier}.

Projection determinacy is exactly
\autoref{thm:hilbert-singleton-projection-uniqueness}, and the remaining
certificate ledger is exhausted by
\autoref{thm:hilbert-singleton-ledger-exhaustion}. These rows give the
paper-side SemanticNameCert surface for $\HilbertUp$ while leaving any
standard bridge claim outside the singleton certificate.
\end{proof}

\begin{theorem}[Hilbert singleton universal orthogonality]
\label{thm:hilbert-singleton-universal-orthogonality}
For any carried histories $m,n:\mathsf{BHist}$ in the singleton Hilbert
carrier, the inner-product endpoint is the constant RealUp zero row:
$$
\mathsf{RealConstantHistoryClassifier}
  (\langle m,n\rangle_{\emp},0_{\mathsf{Real}}^{c}).
$$
Thus every carried pair is orthogonal under the singleton Hilbert classifier.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_universal\_orthogonality}
\begin{proof}
By \autoref{def:hilbert-singleton-empty-history-carrier}, every carried
history is the public singleton endpoint. Hence the displayed pair has no
separate source data beyond the unique $\emp$ endpoint.

Apply
\autoref{thm:hilbert-singleton-constant-inner-product-transport}. The
constant inner-product row transports every accepted pair to the same
$\mathsf{RealConstantHistoryClassifier}$ value at $0_{\mathsf{Real}}^{c}$.

Finally,
\autoref{thm:hilbert-singleton-endpoint-readback} identifies that endpoint
with the public Hilbert readback row. This is precisely the singleton
orthogonality classifier for the carried pair.
\end{proof}

\begin{theorem}[Hilbert singleton parallelogram collapse]
\label{thm:hilbert-singleton-parallelogram-collapse}
For carried histories $m,n:\mathsf{BHist}$ in the singleton Hilbert carrier,
the parallelogram law surface over the singleton vector-space operations
collapses to the constant RealUp zero endpoint. The four norm rows
$$
\nu_{\emp}(m+n),\quad
\nu_{\emp}(m-n),\quad
\nu_{\emp}(m),\quad
\nu_{\emp}(n)
$$
are all classified with $0_{\mathsf{Real}}^{c}$ by
$\mathsf{RealConstantHistoryClassifier}$, so both sides of the Hilbert
parallelogram identity are read through the same constant-real row.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_parallelogram\_collapse}
\begin{proof}
First use \autoref{thm:hilbert-singleton-source-compatibility}. It places the
Hilbert carrier, the singleton vector carrier, and the singleton norm carrier
on one shared $\rho_{\emp}$ source surface.

The vector operations are collapsed by
\autoref{thm:singleton-empty-history-vecspace-endpoint-collapse}. Therefore
$m+n$, $m-n$, $m$, and $n$ all expose the unique carried endpoint of the
singleton vector space.

Apply \autoref{thm:singleton-empty-history-norm-laws} to those four carried
endpoints. Each displayed norm is classified with the constant RealUp zero
endpoint, and \autoref{thm:hilbert-singleton-endpoint-readback} reads these
norm rows inside the Hilbert package. The two parallelogram sides therefore
have the same classifier row.
\end{proof}

\begin{theorem}[Hilbert singleton projection boundary]
\label{thm:hilbert-singleton-projection-boundary}
The public projection boundary of the singleton Hilbert package selects
$\emp$ for every carried input pair. The selected endpoint is classified by
$\rho_{\emp}$, and the projection readback agrees simultaneously with the
Banach limit row, the singleton $\NormUp$ row, and the constant
inner-product zero row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:hilbert-singleton-projection-uniqueness} to the public
projection witnesses for the carried inputs. Since the Hilbert carrier has
only the singleton endpoint, uniqueness identifies every selected endpoint by
$\rho_{\emp}$.

The complete normed certificate in
\autoref{thm:hilbert-singleton-complete-normed-certificate} places that
selection on the Banach singleton surface. Through
\autoref{thm:hilbert-singleton-source-compatibility}, the same source
comparison is also the singleton $\NormUp$ comparison.

It remains to read the Hilbert geometry row. By
\autoref{thm:hilbert-singleton-universal-orthogonality}, the inner-product
component of the selected pair is the constant RealUp zero row. Hence the
projection boundary agrees with the Banach limit row, the NormUp zero row,
and the orthogonality row at the same selected endpoint.
\end{proof}

\input{parts/concrete_instances/hilbert_orthogonal_projection_row.tex}

\input{parts/concrete_instances/hilbert_orthogonal_residual_decomposition.tex}
