\chapter{A Concrete Naming Certificate for $\DyadicWindowSealUp$}
\label{ch:concrete-instances-dyadic-window-seal-namecert}
\origin{ai}

The $\DyadicWindowSealUp$ packet realizes the Real and Completion route of \autoref{ch:visions-real-completeness} as a finite service boundary before a $\RealUp$ seal consumer is allowed to read completion-facing data. It sits between the dyadic precision surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the observation-budget surface of \autoref{ch:concrete-instances-real-observation-budget-namecert}, the seal synchronizer of \autoref{ch:concrete-instances-cauchy-seal-budget-synchronizer-namecert}, and the completion-seal classifier of \autoref{ch:concrete-instances-real-completion-seal-classifier-namecert}. The packet is a finite Real-and-Completion seal service, not a quotient stream, selected host limit, host real equality, hidden selector, unbounded schedule, or ambient completeness principle.

\begin{definition}[Dyadic window seal carrier]
\label{def:dyadic-window-seal-carrier}
A $\DyadicWindowSealUp$ carrier is a finite $\BHist$ packet
$$
W=(q,w,r,b,z,s,h,c,p,n)
$$
with the following displayed rows:
\begin{enumerate}
\item $q$ is the dyadic precision and request row read from the $\DyadicRatCoreUp$ ledger;
\item $w$ is the finite $\StreamNameUp$ window served for that request;
\item $r$ is the $\RegSeqRatUp$ readback row obtained through the window;
\item $b$ is the $\RealObservationBudgetUp$ row that admits the finite observation service;
\item $z$ is the $\CauchySealBudgetSynchronizerUp$ row tying the request, budget, shared threshold, and seal service together;
\item $s$ is the $\RealUp$ seal row that may be consumed only after $q,w,r,b,z$ are displayed;
\item $h$ records componentwise $\hsame$ transport for the request, window, readback, budget, synchronizer, and seal rows;
\item $c$ records the displayed $\Cont$ routes by which every consumer reaches those rows;
\item $p$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealObservationBudgetUp$, $\CauchySealBudgetSynchronizerUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $n$ is the local $\NameCert_{\DyadicWindowSealUp}$ row.
\end{enumerate}
The carrier has no coordinate for a quotient stream representative, host real equality, selected host limit, hidden selector, unbounded observation schedule, or ambient completeness theorem.
\end{definition}
\leandef{BEDC.Derived.DyadicWindowSealUp.DyadicWindowSealUp}

\begin{theorem}[Dyadic window seal NameCert obligations]
\label{thm:dyadic-window-seal-namecert-obligations}
For the carrier of \autoref{def:dyadic-window-seal-carrier}, the local $\NameCert_{\DyadicWindowSealUp}$ surface consists of six finite rows:
\begin{enumerate}
\item carrier admission for $W=(q,w,r,b,z,s,h,c,p,n)$ as one displayed $\BHist$ packet;
\item dyadic request exactness identifying $q$ with the precision and request ledger row served by $\DyadicRatCoreUp$;
\item finite-window readback exactness identifying $w$ and $r$ as the $\StreamNameUp$ window and $\RegSeqRatUp$ readback for the same request;
\item observation-budget admission through $b$ before any $\RealUp$ seal row is exposed;
\item synchronizer agreement through $z$, forcing the request, budget, shared-threshold, and seal rows to be read as one finite route;
\item transport, route, provenance, and local naming exactness through $h,c,p,n$.
\end{enumerate}
Lean \texttt{BEDC.Derived.DyadicWindowSealUp.TasteGate} must provide explicit \texttt{Nontrivial DyadicWindowSealUp} and \texttt{FieldFaithful DyadicWindowSealUp} instances for this same carrier surface.
\end{theorem}
\begin{proof}
Project the carrier tuple in \autoref{def:dyadic-window-seal-carrier}. The request, window, readback, budget, synchronizer, seal, transport, route, provenance, and naming rows are all displayed coordinates of the packet.

The dyadic request row fixes the precision service, and the window and readback rows fix the finite observation through $\StreamNameUp$ and $\RegSeqRatUp$. The budget row admits the service only as a finite observation, while the synchronizer row ties that budget to the same seal route.

Finally the transport and continuation rows authenticate componentwise movement of the displayed service. Repacking those rows with $p$ and $n$ gives the local NameCert surface and leaves no carrier coordinate through which a hidden selector, quotient stream, host real equality, selected limit, unbounded schedule, or ambient completeness premise can enter.
\end{proof}

\begin{theorem}[Dyadic window seal budget pullback]
\label{thm:dyadic-window-seal-budget-pullback}
Let $W=(q,w,r,b,z,s,h,c,p,n)$ be an accepted $\DyadicWindowSealUp$ packet. Every observation-budget consumer that reaches the $\RealUp$ seal row $s$ factors through the finite pullback route
$$
q \longmapsto w \longmapsto r \longmapsto b \longmapsto z \longmapsto s.
$$
The route is exhausted by the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the same packet, and exports no quotient stream equality, host real equality, selected host limit, hidden selector, unbounded schedule, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the obligation surface of \autoref{thm:dyadic-window-seal-namecert-obligations}. It requires the dyadic request row, stream window, regular readback, observation budget, synchronizer, and seal row to belong to one accepted packet.

Read the consumer through the observation-budget row. Since $b$ is displayed as a coordinate of the same carrier, the admitted service can inspect only the request, window, readback, and budget rows already named by $q,w,r,b$.

Now apply synchronizer agreement. The row $z$ binds that budget route to the shared seal route ending at $s$, while $h,c,p,n$ record the componentwise transport, continuation replay, provenance, and local naming. Carrier inspection supplies the stated exclusions.
\end{proof}

\begin{theorem}[Dyadic window seal non-escape]
\label{thm:dyadic-window-seal-nonescape}
No accepted $\DyadicWindowSealUp$ read can export a $\RealUp$ seal consumer without first displaying the dyadic request row, finite $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\RealObservationBudgetUp$ row, and $\CauchySealBudgetSynchronizerUp$ row of the same packet. Any read that bypasses one of those rows has no remaining coordinate from which to export a completion-facing seal service.
\end{theorem}
\begin{proof}
Project the accepted packet to $W=(q,w,r,b,z,s,h,c,p,n)$. The only seal-facing coordinate is $s$, and the only service route into it is the displayed finite chain through $q,w,r,b,z$.

Use \autoref{thm:dyadic-window-seal-budget-pullback}. It places every observation-budget consumer of $s$ on the same pullback route and authenticates the route through $h,c,p,n$.

The carrier definition then rules out all bypasses. There is no quotient-stream coordinate, host equality test, selected host limit, hidden selector, unbounded schedule, or ambient completeness field that could replace a missing request, window, readback, budget, or synchronizer row.
\end{proof}

\begin{theorem}[Dyadic window seal Real handoff]
\label{thm:dyadic-window-seal-real-handoff}
Every accepted $\DyadicWindowSealUp$ consumer that hands data to $\RealUp$ hands only the finite packet rows
$$
q,w,r,b,z,s,h,c,p,n.
$$
In particular, a $\RealUp$ seal read factors through the displayed dyadic precision request, finite $\StreamNameUp$ window, $\RegSeqRatUp$ readback, observation budget, and synchronizer row before the seal is consumed.
\end{theorem}
\begin{proof}
Apply \autoref{thm:dyadic-window-seal-namecert-obligations} to identify the displayed Real-and-Completion service surface. The only rows available to a consumer are the request, window, readback, budget, synchronizer, seal, transport, route, provenance, and local naming rows.

Apply \autoref{thm:dyadic-window-seal-budget-pullback}. It orders every seal read through $q,w,r,b,z$ before the consumer reaches $s$.

Finally apply \autoref{thm:dyadic-window-seal-nonescape}. Since no alternate analytic or quotient coordinate is present, the handoff to $\RealUp$ is exactly the finite packet route.
\end{proof}

\falsifiablePrediction{Every accepted DyadicWindowSealUp RealUp consumer factors through the displayed dyadic window and synchronizer rows before any seal read.}

\independenceWitness{Nearest siblings: real-observation-budget, cauchy-seal-budget-synchronizer, finite-tail-diagonal-seal, regular-cauchy-limit-classifier, and real-completion-seal-classifier; none is bijective because DyadicWindowSealUp uniquely carries the dyadic request, finite StreamName window, RegSeqRat readback, observation budget, synchronizer row, and RealUp seal in one carrier.}

\closureat{DyadicWindowSealUp}{seedStr}

\begin{closurestatus}{\DyadicWindowSealUp}
  \constructivestory{A $\DyadicWindowSealUp$ packet is generated from a dyadic precision request, finite StreamName window, RegSeqRat readback, observation-budget row, seal synchronizer row, RealUp seal, componentwise transports, displayed continuations, provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-window-seal-carrier}, \autoref{thm:dyadic-window-seal-namecert-obligations}, \autoref{thm:dyadic-window-seal-budget-pullback}, \autoref{thm:dyadic-window-seal-nonescape}, and \autoref{thm:dyadic-window-seal-real-handoff} bind the finite Real-and-Completion service packet to the displayed dyadic request, window, readback, budget, synchronizer, seal, transport, route, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close RealUp completeness, quotient stream equality, host real equality, selected host limits, hidden selectors, unbounded schedules, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Scoped closure requires checked carrier, obligation, pullback, non-escape, and Real handoff targets for the same finite packet surface.}
\end{closurestatus}
