\chapter{A Concrete Naming Certificate for $\CauchyFilterUp$}

The $\CauchyFilterUp$ surface names the finite observation filter used by the
Real and Completion phase when a consumer needs explicit Cauchy data without
host filters or choice-selected subsequences. It sits between
$\StreamNameUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$ as a visible packet of late-window evidence.

\begin{definition}[CauchyFilter carrier]\label{def:cauchyfilter-carrier}
A $\CauchyFilterUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
F=(s,d,m,e,r,t,c,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $s$ is the $\StreamNameUp$ observation family whose entries are visible
in the packet;
\item $d$ is a directed finite-window index ledger ordering the finite tails
through which observations are read;
\item $m$ is the $\CauchyModulusUp$ threshold row assigning a displayed
precision request to a finite tail bound;
\item $e$ is the dyadic endpoint row package supplied by $\DyadicRatCoreUp$;
\item $r$ is the compatibility row against $\RegSeqRatUp$, recording the same
late-window comparisons as regular rational sequence evidence;
\item $t$ contains the $\hsame$ and $\Cont$ transport rows used to compare and
extend finite windows;
\item $c$ is the consumer-facing ledger naming $\RealUp$ as the sealed reader
of the finite filter packet;
\item $P$ is the $\mathsf{Pkg}$ provenance for the dependency anchors
$\StreamNameUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$;
\item $N$ is the local $\NameCert_{\CauchyFilterUp}$ row.
\end{enumerate}
The carrier accepts exactly those packets whose listed rows occur in one
finite history and whose transport routes are displayed in that history. It
does not contain a host filter, ultrafilter, chosen subsequence, metric
completion point, or quotient stream.
\end{definition}

\begin{theorem}[CauchyFilter finite-window coverage]\label{thm:cauchyfilter-finite-window-coverage}
Every accepted $\CauchyFilterUp$ carrier covers its public observations by a
directed finite window. More precisely, each visible $\StreamNameUp$ read in
the packet factors through the index ledger $d$, the $\CauchyModulusUp$
threshold row $m$, the dyadic endpoint rows $e$, the $\hsame$ and $\Cont$
transport rows $t$, and the $\mathsf{Pkg}$ provenance $P$.
\end{theorem}
\begin{proof}
Start from the carrier decomposition in
\autoref{def:cauchyfilter-carrier}. The observation family, directed window
ledger, threshold row, endpoint rows, transport rows, and provenance row are
all coordinates of the same finite $\mathsf{BHist}$ packet.

For a displayed observation read, choose the finite tail window named by the
ledger. The threshold row supplies the bound for the requested precision, and
the dyadic endpoint rows give the finite values inspected inside that tail.

The remaining comparison is routed through the displayed $\hsame$ and $\Cont$
transport rows. Since the packet contains no constructor for an external
filter object, the public read is exhausted by the finite window and its
package provenance.
\end{proof}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterPacket\_finite\_window\_coverage}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterCarrier\_finite\_window\_coverage}

\begin{theorem}[CauchyFilter RegSeqRat handoff]\label{thm:cauchyfilter-regseqrat-handoff}
An accepted $\CauchyFilterUp$ packet hands off to $\RegSeqRatUp$ exactly
through its compatibility row $r$. The handoff preserves the
$\StreamNameUp$ observation family, the $\CauchyModulusUp$ threshold row, the
$\DyadicRatCoreUp$ endpoint rows, the directed finite-window ledger, and the
displayed $\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterCarrier\_regseqrat\_handoff}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterPacket\_regseqrat\_handoff}
\begin{proof}
Project the packet to the compatibility row $r$ and the rows named in
\autoref{def:cauchyfilter-carrier}. The row $r$ is already the displayed
regular-sequence comparison against the same late-window observations.

Transport along the listed $\hsame$ rows and restrict along the displayed
$\Cont$ windows. These operations do not change the stream observations,
threshold row, dyadic endpoints, or directed window ledger; they only re-read
the same finite rows through the $\RegSeqRatUp$ certificate.

Thus the handoff has no additional carrier beyond the visible compatibility
row and the package provenance. A $\RegSeqRatUp$ consumer receives finite
late-window evidence, not a quotient stream or a completed real.
\end{proof}

\begin{theorem}[CauchyFilter Real seal consumer boundary]\label{thm:cauchyfilter-real-seal-consumer-boundary}
Every $\RealUp$ consumer of an accepted $\CauchyFilterUp$ packet factors
through the displayed finite filter surface: the $\StreamNameUp$ observations,
directed finite-window ledger, $\CauchyModulusUp$ threshold row,
$\DyadicRatCoreUp$ endpoints, $\RegSeqRatUp$ compatibility row, $\hsame$ and
$\Cont$ transport, and $\mathsf{Pkg}$ provenance. The boundary exports no
metric-completion point, host real equality, or choice-selected tail.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterFiniteWindowSurface\_real\_seal\_consumer\_boundary}
\begin{proof}
Read the consumer ledger coordinate $c$ of the carrier. It names $\RealUp$ as
a sealed reader of the same finite filter rows rather than as a source of
extra completion data.

Apply the finite-window coverage theorem to the underlying observations, then
apply the $\RegSeqRatUp$ handoff theorem to the compatibility row. Together
they identify every available consumer read with a displayed tail window,
endpoint package, threshold row, transport route, and provenance row.

There is no remaining coordinate from which a metric-completion point, host
real equality, or selected infinite subsequence could be read. The real-facing
boundary is therefore the finite filter surface itself.
\end{proof}

\begin{theorem}[CauchyFilter public obligation catalogue]\label{thm:cauchyfilter-public-obligation-catalogue}
The public $\NameCert_{\CauchyFilterUp}$ obligation catalogue has exactly five
rows:
\begin{enumerate}
\item the carrier row of \autoref{def:cauchyfilter-carrier};
\item the classifier row identifying two packets when they admit a common
finite filter refinement with the same threshold, endpoint, and compatibility
rows;
\item stability under $\hsame$ transport of the observation, threshold,
endpoint, compatibility, and provenance rows;
\item exactness of visible filter-window reads through the directed finite
ledger and displayed $\Cont$ routes;
\item a ledger-exclusion row forbidding host filters, ultrafilters,
choice-selected subsequences, metric-completion points, and quotient streams.
\end{enumerate}
These rows are the entire public surface used by $\StreamNameUp$,
$\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$
consumers.
\end{theorem}
\begin{proof}
The carrier row is the finite packet specified in
\autoref{def:cauchyfilter-carrier}. Its coordinates already list the
observation family, finite-window ledger, threshold, endpoints,
regular-sequence compatibility, transport, provenance, and local naming row.

The classifier compares two packets by refining their directed ledgers to a
common finite window and then comparing the threshold, endpoint, compatibility,
transport, and provenance rows through $\hsame$. This gives the stability row
at the same time, because transported packets retain the rows used by the
classifier.

Exactness follows by re-reading each public observation through the same
finite ledger and $\Cont$ route. The ledger-exclusion row is forced by the
carrier shape: none of the listed external filter, completion, choice, or
quotient objects is a coordinate of the packet.
\end{proof}

\begin{theorem}[CauchyFilter common-refinement classifier]\label{thm:cauchyfilter-common-refinement-classifier}
Two accepted $\CauchyFilterUp$ packets classify together exactly when their
directed finite-window ledgers admit a displayed common finite refinement
carrying the same $\StreamNameUp$ observations, $\CauchyModulusUp$ threshold
rows, $\DyadicRatCoreUp$ endpoint rows, $\RegSeqRatUp$ compatibility row,
$\hsame$ and $\Cont$ transport rows, and $\mathsf{Pkg}$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterPacket\_common\_refinement\_classifier}
\begin{proof}
Project both accepted packets through the carrier decomposition of
\autoref{def:cauchyfilter-carrier}. The visible coordinates are finite
$\mathsf{BHist}$ rows, so the two directed ledgers can be compared by passing
to the displayed common window named by the classifier row.

On that common window, compare the threshold, endpoint, regular-sequence
compatibility, transport, and provenance coordinates through the recorded
$\hsame$ rows. The displayed $\Cont$ routes re-read the same observations
without adding a host filter or a selected subsequence.

Repack the matched rows as one $\NameCert_{\CauchyFilterUp}$ classifier
judgement. Conversely, reading such a classifier judgement exposes precisely
the common finite refinement and the listed coordinate equalities, so it
returns the same condition.
\end{proof}

\begin{theorem}[CauchyFilter refinement transport]\label{thm:cauchyfilter-filter-refinement-transport}
Refining the directed finite window of an accepted $\CauchyFilterUp$ packet
preserves acceptance and preserves every visible observation through the
displayed $\hsame$ and $\Cont$ transport rows.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterPacket\_refinement\_transport}
\begin{proof}
Begin with the finite-window coverage theorem. The public observations already
factor through the directed ledger, threshold row, endpoint rows, transport
rows, and provenance row of the accepted packet.

Apply \autoref{thm:cauchyfilter-common-refinement-classifier} to the original
window and the refined window. The common-refinement classifier identifies the
same $\StreamNameUp$ observations, $\CauchyModulusUp$ thresholds,
$\DyadicRatCoreUp$ endpoints, $\RegSeqRatUp$ compatibility row, and package
provenance on the refined ledger.

The refined packet is therefore accepted by the same finite carrier rows. No
host filter, ultrafilter, or choice-selected subsequence is introduced, because
the transport uses only the displayed $\hsame$ comparisons and $\Cont$ routes.
\end{proof}
\leanchecked{BEDC.Derived.CauchyFilterUp.CauchyFilterPacket\_window\_refinement\_transport}

\begin{theorem}[CauchyFilter Real-seal refinement exhaustion]\label{thm:cauchyfilter-real-seal-refinement-exhaustion}
After any common finite refinement, every $\RealUp$ consumer read from an
accepted $\CauchyFilterUp$ packet factors through the same finite filter rows
and exports no metric-completion point, host real equality, quotient stream, or
choice-selected tail.
\end{theorem}
\begin{proof}
Use \autoref{thm:cauchyfilter-common-refinement-classifier} to replace the
consumer-facing packet by its common refined finite window. The classifier
keeps the visible observations, thresholds, endpoints, compatibility,
transport, and provenance rows fixed on that window.

Apply \autoref{thm:cauchyfilter-regseqrat-handoff} to the compatibility row.
The handoff shows that the regular-rational read is the same finite late-window
evidence, not an external quotient stream.

Finally apply \autoref{thm:cauchyfilter-real-seal-consumer-boundary}. The
$\RealUp$ ledger reads only the finite filter surface and therefore has no
coordinate from which a metric-completion point, host real equality, or
choice-selected tail could be exported.
\end{proof}

\begin{theorem}[CauchyFilter scoped dependency packet]\label{thm:cauchyfilter-scoped-dependency-packet}
The carrier of \autoref{def:cauchyfilter-carrier}, finite-window coverage of
\autoref{thm:cauchyfilter-finite-window-coverage}, $\RegSeqRatUp$ handoff of
\autoref{thm:cauchyfilter-regseqrat-handoff}, $\RealUp$ seal boundary of
\autoref{thm:cauchyfilter-real-seal-consumer-boundary}, common-refinement
classifier of \autoref{thm:cauchyfilter-common-refinement-classifier},
refinement transport of \autoref{thm:cauchyfilter-filter-refinement-transport},
and Real-seal refinement exhaustion of
\autoref{thm:cauchyfilter-real-seal-refinement-exhaustion} form one scoped
BEDC packet over $\mathsf{BHist}$.

Observation reads in this packet pass through $\StreamNameUp$, precision rows
through $\CauchyModulusUp$, endpoints through $\DyadicRatCoreUp$, compatibility
through $\RegSeqRatUp$, and every public transport through the displayed
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Project an accepted packet to the carrier rows of
\autoref{def:cauchyfilter-carrier}. Apply
\autoref{thm:cauchyfilter-finite-window-coverage} to identify the finite
$\mathsf{BHist}$ window and its $\StreamNameUp$ observations,
$\CauchyModulusUp$ precision rows, and $\DyadicRatCoreUp$ endpoint rows.

The compatibility and consumer boundaries are the next projections. Use
\autoref{thm:cauchyfilter-regseqrat-handoff} for the $\RegSeqRatUp$ handoff and
\autoref{thm:cauchyfilter-real-seal-consumer-boundary} for the $\RealUp$ seal.
Both cite only displayed finite rows and package provenance.

It remains to bind refinement. Apply
\autoref{thm:cauchyfilter-common-refinement-classifier} and
\autoref{thm:cauchyfilter-filter-refinement-transport} to move between finite
windows through the recorded $\hsame$ and $\Cont$ data, then use
\autoref{thm:cauchyfilter-real-seal-refinement-exhaustion} to close the
consumer readback under common refinement.

Repacking these projections gives the single scoped packet. Since every cited
projection is a coordinate of the displayed $\mathsf{BHist}$,
$\StreamNameUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, or $\NameCert$ surface, there is no channel
for a host filter, ultrafilter, quotient stream, or choice-selected
subsequence.
\end{proof}

\begin{theorem}[CauchyFilter finite-filter standard bridge]
\label{thm:cauchyfilter-finite-filter-standard-bridge}
An accepted $\CauchyFilterUp$ packet determines the standard finite
Cauchy-filter schema exactly through the displayed $\StreamNameUp$ observation
rows, directed finite-window ledger, $\CauchyModulusUp$ threshold row,
$\DyadicRatCoreUp$ endpoint rows, $\RegSeqRatUp$ compatibility row, displayed
$\hsame$ routes, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and the local
$\NameCert$ row.

Conversely, any standard finite-filter package whose rows are exactly those
displayed BEDC rows repacks as the same public $\CauchyFilterUp$ packet. The
bridge has no coordinate for host filters, ultrafilters, quotient streams,
metric-completion points, or choice-selected subsequences.
\end{theorem}
\begin{proof}
Project the accepted packet through the carrier of
\autoref{def:cauchyfilter-carrier}. Apply
\autoref{thm:cauchyfilter-finite-window-coverage} to expose the finite
observation windows, directed ledger, $\StreamNameUp$ rows,
$\CauchyModulusUp$ threshold row, and $\DyadicRatCoreUp$ endpoints as the
visible finite-filter data.

Next use \autoref{thm:cauchyfilter-regseqrat-handoff} to read the
$\RegSeqRatUp$ compatibility row and
\autoref{thm:cauchyfilter-real-seal-consumer-boundary} to keep the $\RealUp$
consumer boundary on the same finite surface. These projections add no carrier
beyond the displayed finite rows.

Apply \autoref{thm:cauchyfilter-scoped-dependency-packet} to gather the
displayed $\hsame$ routes, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and local
$\NameCert$ row into the scoped dependency packet. This is exactly the standard
finite Cauchy-filter schema because the cited packet has no additional
coordinate.

For the converse direction, start with a standard finite-filter package whose
coordinates are exactly the displayed rows. Repack those rows in the carrier,
handoff, refinement, seal, transport, provenance, and local naming positions
just projected. The result is the same public $\CauchyFilterUp$ packet because
no further coordinate remains to choose.

The excluded objects are not hidden cases of the construction. Host filters,
ultrafilters, quotient streams, metric-completion points, and choice-selected
subsequences are absent from every cited projection, so the bridge cannot read
or export them.
\end{proof}

\begin{theorem}[CauchyFilter RegSeqRat Real seal exhaustion]
\label{thm:cauchyfilter-regseqrat-real-seal-exhaustion}
Every $\RegSeqRatUp$ handoff and every $\RealUp$ seal consumer read from an
accepted $\CauchyFilterUp$ packet factors through one finite surface: stream
observations, the directed finite-window ledger, the modulus threshold,
dyadic endpoints, the compatibility row, $\hsame$ transport, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ evidence.

No consumer read from this export contains a host filter, ultrafilter,
quotient stream, metric-completion point, or choice-selected subsequence.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchyfilter-finite-window-coverage}. It gives the
stream observations, directed finite-window ledger, modulus threshold, and
dyadic endpoints as displayed finite rows of the accepted packet.

Next apply \autoref{thm:cauchyfilter-regseqrat-handoff}. The
$\RegSeqRatUp$ consumer receives exactly the compatibility row over those
finite observations and endpoints.

Apply \autoref{thm:cauchyfilter-real-seal-consumer-boundary}. The $\RealUp$
seal consumes the same finite filter surface, with no additional host filter
or completion coordinate.

It remains to bind refinement. Use
\autoref{thm:cauchyfilter-common-refinement-classifier} and
\autoref{thm:cauchyfilter-filter-refinement-transport} for the common
finite-window classifier and its $\hsame$ and $\Cont$ transport, then apply
\autoref{thm:cauchyfilter-scoped-dependency-packet} to repack the package and
local naming rows.

The cited projections exhaust the consumer coordinates. Therefore each
$\RegSeqRatUp$ handoff and each $\RealUp$ seal read factors through the single
finite surface stated above, and the excluded host objects have no displayed
row from which they could be read.
\end{proof}

\begin{theorem}[CauchyFilter finite-filter mature coverage]
\label{thm:cauchyfilter-finite-filter-mature-coverage}
Every public or standard finite-filter consumer read of an accepted
$\CauchyFilterUp$ packet is exhausted by the displayed $\StreamNameUp$
observations, directed finite-window ledger, $\CauchyModulusUp$ threshold,
$\DyadicRatCoreUp$ endpoints, $\RegSeqRatUp$ compatibility, $\RealUp$ seal,
common-refinement classifier, $\hsame$ and $\Cont$ transport,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ row.

The covered surface preserves the exclusions of host filters, ultrafilters,
quotient streams, metric-completion points, and choice-selected subsequences.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchyfilter-finite-window-coverage}. It supplies the
displayed stream observations, directed finite-window ledger, threshold row,
and dyadic endpoint rows as the finite carrier available to consumers.

Next use \autoref{thm:cauchyfilter-regseqrat-handoff} and
\autoref{thm:cauchyfilter-real-seal-consumer-boundary}. These identify the
$\RegSeqRatUp$ compatibility read and the $\RealUp$ seal as reads of the same
finite carrier, with no completion or host-filter coordinate added.

Refinement is controlled by
\autoref{thm:cauchyfilter-common-refinement-classifier} and
\autoref{thm:cauchyfilter-filter-refinement-transport}. The first theorem
classifies common finite-window refinements, and the second transports that
classifier through the displayed $\hsame$ and $\Cont$ routes.

Finally apply \autoref{thm:cauchyfilter-finite-filter-standard-bridge} and
\autoref{thm:cauchyfilter-regseqrat-real-seal-exhaustion}. The standard
finite-filter packet and the $\RegSeqRatUp$/$\RealUp$ consumer boundary read
exactly the listed rows, while host filters, ultrafilters, quotient streams,
metric-completion points, and choice-selected subsequences remain outside the
packet.
\end{proof}

\begin{theorem}[CauchyFilter mature Real consumer example]
\label{thm:cauchyfilter-mature-real-consumer-example}
A $\RealUp$ seal consumer supplied with an accepted $\CauchyFilterUp$ packet
and a $\RegSeqRatUp$ compatibility row obtains a finite late-window package
consisting only of $\StreamNameUp$ observations, $\CauchyModulusUp$ thresholds,
$\DyadicRatCoreUp$ endpoints, the compatibility row, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and local $\NameCert$ evidence.

The package contains no host filter, ultrafilter, quotient stream,
metric-completion point, or choice-selected subsequence.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchyfilter-finite-window-coverage}. It supplies the
visible stream observations, finite-window ledger, modulus threshold, and
dyadic endpoint rows of the accepted packet.

Next use \autoref{thm:cauchyfilter-regseqrat-handoff}. The
$\RegSeqRatUp$ compatibility row is a read of the same finite late-window
surface, so it adds no host filter or quotient-stream coordinate.

Apply \autoref{thm:cauchyfilter-real-seal-consumer-boundary}. This identifies
the $\RealUp$ seal consumer as a reader of the finite filter package rather than
of a selected completion object.

Finally use \autoref{thm:cauchyfilter-regseqrat-real-seal-exhaustion}. It
exhausts the combined $\RegSeqRatUp$ and $\RealUp$ readback surface by the
listed rows, leaving the excluded host objects outside the package.
\end{proof}

\closureat{CauchyFilterUp}{seedStr}
\closureat{CauchyFilterUp}{obligationStr}
\closureat{CauchyFilterUp}{scopedStr}
\closureat{CauchyFilterUp}{publicStr}
\closureat{CauchyFilterUp}{bridgedStr}
\closureat{CauchyFilterUp}{matureStr}

\begin{closurestatus}{\CauchyFilterUp}
  \constructivestory{A $\CauchyFilterUp$ packet is generated by visible $\StreamNameUp$ observations, a directed finite-window ledger, a $\CauchyModulusUp$ threshold row, $\DyadicRatCoreUp$ endpoint rows, $\RegSeqRatUp$ compatibility, displayed transport, package provenance, and a local naming row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:cauchyfilter-finite-filter-mature-coverage} combines the finite-window coverage, $\RegSeqRatUp$ handoff, $\RealUp$ seal boundary, refinement transport, and finite-filter standard bridge over $\StreamNameUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.CauchyFilterUp.CauchyFilterPacket\_window\_refinement\_transport}
  \leantarget{BEDC.Derived.CauchyFilterUp.CauchyFilterCarrier\_finite\_window\_coverage}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close host filter theory, ultrafilter selection, quotient-stream equality, metric completion, or Lean bridge checking.}
  \upgradepath{No further paper-axis theory upgrade remains; only bridgeChecked verification remains on the formal bridge axis.}
\end{closurestatus}
