\chapter{A Concrete Naming Certificate for $\CauchySharedTailModulusUp$}
\label{ch:concrete-instances-cauchy-shared-tail-modulus-namecert}
\origin{ai}

The $\CauchySharedTailModulusUp$ packet realizes the Real and Completion route of \autoref{ch:visions-real-completeness} as a finite shared-tail threshold certificate. It consumes the explicit modulus extraction surface of \autoref{ch:concrete-instances-cauchymodulusextraction-namecert}, the dyadic tail-radius ledger of \autoref{ch:concrete-instances-dyadictailradiusledger-namecert}, the finite window service of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the Real seal boundary of \autoref{ch:concrete-instances-real-namecert}. Its purpose is to synchronize two regular-Cauchy tail requests through one displayed dyadic threshold before any $\RealUp$ completion-facing seal is exposed.

\begin{definition}[Cauchy shared-tail modulus carrier]
\label{def:cauchy-shared-tail-modulus-carrier}
A $\CauchySharedTailModulusUp$ carrier is a finite $\BHist$ packet
$$
S=(R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R_0$ and $R_1$ are the two accepted $\RegSeqRatUp$ sources whose tails are being synchronized for a Real-completion consumer;
\item $M_0$ and $M_1$ are the displayed $\CauchyModulusExtractionUp$ rows supplying the two finite tail requests;
\item $\tau$ is the single shared dyadic tail-threshold row, read through the $\DyadicTailRadiusLedgerUp$ service;
\item $D$ is the dyadic tolerance ledger witnessing that both requests are served at the same threshold $\tau$;
\item $W_0$ and $W_1$ are the $\StreamNameUp$ finite-window rows opened by $\tau$ for the two sources;
\item $Q_0$ and $Q_1$ are the $\RegSeqRatUp$ readback rows obtained from the two windows and the shared dyadic ledger;
\item $E$ is the $\RealUp$ seal row exposed only after the two readbacks have passed through the same shared threshold;
\item $H$ records componentwise $\hsame$ transport for the sources, extracted moduli, shared threshold, dyadic ledger, windows, readbacks, Real seal, provenance, and local name;
\item $C$ records the displayed $\Cont$ routes from each extracted modulus to $\tau$, from $\tau$ to the two windows, from the windows to the readbacks, and from the readbacks to the Real seal;
\item $P$ is the $\Pkg$ provenance over $\CauchyModulusExtractionUp$, $\DyadicTailRadiusLedgerUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RegularCauchyTailMeetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CauchySharedTailModulusUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient stream equality, host real equality, selected limits, independent per-source seal exposure, hidden threshold replacement, or an ambient completeness principle.
\end{definition}
\leanchecked{BEDC.Derived.CauchySharedTailModulusUp.CauchySharedTailModulusTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cauchy shared-tail modulus NameCert obligations]
\label{thm:cauchy-shared-tail-modulus-namecert-obligations}
For the carrier of \autoref{def:cauchy-shared-tail-modulus-carrier}, the local $\NameCert_{\CauchySharedTailModulusUp}$ surface consists exactly of carrier admission for $S$, paired request exposure through $M_0,M_1$, shared-threshold exposure through $\tau,D$, window service through $W_0,W_1$, regular readback through $Q_0,Q_1$, Real seal ordering through $E$, componentwise stability through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$. A completion-facing consumer obtains no $\RealUp$ seal read until both requests have been routed through the shared dyadic threshold.
\end{theorem}
\begin{proof}
Project the displayed carrier. The rows $R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N$ are all of the public packet, so every tail request, threshold, window, readback, seal, transport, route, provenance, and local name is visible before the certificate is consumed.

The sibling modulus and dyadic rows supply the request boundary. The extracted modulus rows come from \autoref{ch:concrete-instances-cauchymodulusextraction-namecert}, while the shared dyadic tolerance row comes from \autoref{ch:concrete-instances-dyadictailradiusledger-namecert}; together they force both tail requests to meet at the same finite threshold $\tau$.

The window and readback rows then route through \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-regseqrat-namecert}. The Real seal row is exposed only after those finite rows have been replayed through $C$ and transported by $H$.

Since the carrier contains no quotient stream, host real equality, selected limit, hidden threshold replacement, or ambient completeness coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus tail synchronization]
\label{thm:cauchy-shared-tail-modulus-tail-synchronization}
Every accepted $\CauchySharedTailModulusUp$ packet synchronizes the two tail requests through the same row $\tau$. In particular, any $\RegularCauchyTailMeetUp$, $\RegSeqRatUp$, or $\StreamNameUp$ consumer of the packet reads $M_0$ and $M_1$ before $\tau$, reads both windows $W_0,W_1$ only through $\tau$, and reads the two regular outputs $Q_0,Q_1$ only after the shared dyadic ledger $D$ has been displayed.
\end{theorem}
\begin{proof}
Start with the carrier definition. The two request rows $M_0,M_1$ and the single threshold row $\tau$ are separate displayed coordinates, but there is no second threshold coordinate.

Use the local obligations of \autoref{thm:cauchy-shared-tail-modulus-namecert-obligations}. Paired request exposure forces both requests to be visible before the threshold is consumed, and shared-threshold exposure forces both window services through the same $\tau,D$ rows.

The sibling $\RegularCauchyTailMeetUp$ route reads the same threshold as its shared-tail row. Thus every tail-meet, StreamName, or RegSeqRat consumer remains on the finite route through $M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1$.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus Real seal handoff]
\label{thm:cauchy-shared-tail-modulus-real-seal-handoff}
Every $\RealUp$ completion-facing read of an accepted $\CauchySharedTailModulusUp$ packet factors through the displayed route
$$
M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N.
$$
The Real seal $E$ is therefore a handoff from one shared dyadic tail threshold, not from two independent tail witnesses or an ambient completeness oracle.
\end{theorem}
\leanchecked{BEDC.Derived.CauchySharedTailModulusUp.CauchySharedTailModulusCarrier\_real\_seal\_handoff}
\begin{proof}
Read the Real seal coordinate in the carrier. The only $\RealUp$ seal row is $E$, and it appears after the paired request, threshold, dyadic, window, and readback rows.

Apply \autoref{thm:cauchy-shared-tail-modulus-tail-synchronization}. It places both regular-Cauchy tails on the same threshold $\tau$ before either readback can reach the seal.

Finally use the displayed transport, route, provenance, and naming rows $H,C,P,N$. They authenticate the same finite route and do not add an independent seal coordinate, so the completion-facing read is exactly the listed handoff.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus carrier admission exactness]
\label{thm:cauchy-shared-tail-modulus-carrier-admission-exactness}
An accepted $\CauchySharedTailModulusUp$ packet exposes exactly the carrier rows
$$
R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N.
$$
The local $\NameCert_{\CauchySharedTailModulusUp}$ admission read has no additional coordinate for quotient stream equality, host real equality, selected limits, independent per-source seal exposure, hidden threshold replacement, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-shared-tail-modulus-carrier}. The accepted packet is the displayed finite tuple, so carrier admission can expose precisely its two source rows, two extracted modulus rows, one shared threshold row, the dyadic ledger, two windows, two readbacks, the Real seal, transport, route, provenance, and local name.

Apply the local NameCert obligations of \autoref{thm:cauchy-shared-tail-modulus-namecert-obligations}. They match the admission surface field by field and assign each row to one visible obligation: paired request exposure, shared-threshold exposure, paired window service, regular readback, Real seal ordering, componentwise stability, displayed replay, provenance, and local naming.

Finally use the Real seal handoff of \autoref{thm:cauchy-shared-tail-modulus-real-seal-handoff}. Any completion-facing read still factors through the same displayed rows, so a purported extra coordinate would not be read from the accepted carrier.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus paired-window readback service]
\label{thm:cauchy-shared-tail-modulus-paired-window-readback-service}
For every accepted $\CauchySharedTailModulusUp$ packet, both finite windows $W_0,W_1$ and both regular readbacks $Q_0,Q_1$ are served from the one shared threshold row $\tau$ together with its dyadic ledger row $D$. No consumer reads either window or readback through a private threshold row.
\end{theorem}
\begin{proof}
Start from carrier admission exactness, \autoref{thm:cauchy-shared-tail-modulus-carrier-admission-exactness}. The only threshold row available to the accepted packet is $\tau$, and the only dyadic threshold ledger row is $D$.

Apply the synchronization theorem \autoref{thm:cauchy-shared-tail-modulus-tail-synchronization}. It orders the paired request rows $M_0,M_1$ before $\tau,D$, then routes both windows $W_0,W_1$ and both readbacks $Q_0,Q_1$ through that shared threshold service.

The paired-window obligation and Real seal handoff keep the downstream read on the same row. Thus every window and readback consumer is served from $\tau,D$, and a private-threshold window is not a read of the displayed packet.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus route replay provenance]
\label{thm:cauchy-shared-tail-modulus-route-replay-provenance}
For an accepted $\CauchySharedTailModulusUp$ packet, the rows $H,C,P,N$ transport, replay, package, and name only the displayed route
$$
R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E.
$$
They do not certify an alternate route with hidden thresholds, independent Real seals, quotient stream equality, host real equality, selected limits, or ambient completeness.
\end{theorem}
\begin{proof}
Use carrier admission exactness to identify the public route inventory. The non-structural rows before $H,C,P,N$ are exactly $R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E$, so transport and replay have no hidden source outside this list.

Next apply the local NameCert obligations. The transport row $H$ is componentwise, the replay row $C$ follows the displayed continuation routes, the provenance row $P$ packages the cited concrete BEDC surfaces, and $N$ names the local certificate.

Finally compose with paired-window readback service and the Real seal handoff. Those two theorems force the middle route and the completion-facing seal to use the same $\tau,D,W_0,W_1,Q_0,Q_1,E$ path, so $H,C,P,N$ certify only the displayed route.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus paired-window obligation]
\label{thm:cauchy-shared-tail-modulus-paired-window-obligation}
For every accepted $\CauchySharedTailModulusUp$ packet, the two $\StreamNameUp$ window rows $W_0,W_1$ are exposed only after the paired request rows $M_0,M_1$ and the single dyadic threshold package $\tau,D$ have been displayed. Thus no consumer of the packet may read either window as a unilateral source window or as a window opened by a private threshold.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-shared-tail-modulus-carrier}. The rows $M_0,M_1,\tau,D,W_0,W_1$ are displayed in the finite packet, with a single threshold coordinate $\tau$ and a single dyadic tolerance ledger $D$ serving both requests.

Apply \autoref{thm:cauchy-shared-tail-modulus-tail-synchronization}. It places $M_0$ and $M_1$ before the shared threshold read, and it routes both StreamName windows through the same $\tau,D$ rows.

The public route row $C$ and transport row $H$ replay that ordering componentwise. Since the carrier has no hidden threshold or unilateral window coordinate, the only accepted window read is the paired read through $M_0,M_1,\tau,D$.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus threshold uniqueness obligation]
\label{thm:cauchy-shared-tail-modulus-threshold-uniqueness-obligation}
Let a consumer route claim to read an accepted $\CauchySharedTailModulusUp$ packet while replacing the shared threshold row $\tau$ by two independent threshold rows. Then the route is not a read of the carrier in \autoref{def:cauchy-shared-tail-modulus-carrier}. Any completion-facing route that reaches the Real seal must use the unique public threshold coordinate $\tau$ and its dyadic ledger row $D$.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. The packet contains one threshold row $\tau$ and one dyadic ledger row $D$; it contains no coordinates for separate left and right thresholds.

Apply carrier-coordinate uniqueness in the displayed tuple. A route that supplies two independent threshold rows asks for two carrier coordinates where the carrier presents only one, so it leaves the packet surface before any Real seal read is considered.

Now apply \autoref{thm:cauchy-shared-tail-modulus-real-seal-handoff}. Every completion-facing Real seal read factors through the displayed route containing the same $\tau,D$ rows. Therefore a route that replaces $\tau$ cannot be a read of the accepted carrier.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus paired-source readback]
\label{thm:cauchy-shared-tail-modulus-paired-source-readback}
Every accepted $\CauchySharedTailModulusUp$ packet reads both $\RegSeqRatUp$ source rows $R_0,R_1$ before the shared threshold row $\tau$ is consumed. A downstream regular-Cauchy, StreamName, RealUp, or completion-facing consumer may inspect $Q_0,Q_1$ only as readbacks of the paired source rows through $M_0,M_1,\tau,D,W_0,W_1$.
\end{theorem}
\begin{proof}
Start with the carrier definition. The source rows $R_0,R_1$ are displayed before the extracted modulus rows, the single threshold row, the dyadic ledger, the window rows, and the readback rows.

Apply the tail synchronization theorem. It orders the two modulus requests before $\tau$ and routes both windows and both readbacks through the shared threshold service.

Finally use threshold uniqueness. Since the accepted packet has no private threshold coordinate, a consumer that reaches $Q_0,Q_1$ without reading both source rows through the common route is not reading the displayed shared-tail packet.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus dyadic ledger exactness]
\label{thm:cauchy-shared-tail-modulus-dyadic-ledger-exactness}
For every accepted $\CauchySharedTailModulusUp$ packet, the dyadic ledger row $D$ is the exact common tolerance witness for both finite windows $W_0,W_1$ and both regular readbacks $Q_0,Q_1$. No consumer may replace $D$ by two private dyadic ledgers, omit it from one side, or read the Real seal row $E$ as if the two windows had independent tolerance witnesses.
\end{theorem}
\begin{proof}
Project the displayed packet. It contains one dyadic ledger row $D$ paired with the single threshold row $\tau$.

Use paired-window readback service. Both windows and both readbacks are served from the same $\tau,D$ pair, so $D$ is not an optional annotation on one side of the route.

The Real seal handoff then carries the same dyadic ledger into the completion-facing read. Since the seal factors through $M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N$, omitting or duplicating $D$ leaves the accepted carrier surface.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus completion-consumer non-escape]
\label{thm:cauchy-shared-tail-modulus-completion-consumer-nonescape}
Any $\RealUp$ or completion-facing consumer of an accepted $\CauchySharedTailModulusUp$ packet factors through
$$
M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N.
$$
The consumer cannot obtain selected limits, quotient real equality, host real equality, ambient completeness, two private thresholds, or a Real seal detached from the paired source readback and dyadic ledger rows.
\end{theorem}
\begin{proof}
First apply the Real seal handoff. It identifies the completion-facing route as the displayed finite path through the two modulus rows, the shared threshold, the dyadic ledger, paired windows, paired readbacks, Real seal, transport, route, provenance, and local name.

Next use paired-source readback and dyadic ledger exactness. These rows ensure that $Q_0,Q_1$ remain readbacks of the two displayed sources through one common $\tau,D$ route.

Finally apply threshold uniqueness. The accepted carrier has no selected-limit coordinate, quotient-real coordinate, host-equality coordinate, ambient-completeness coordinate, or pair of private threshold coordinates, so a consumer that extracts any of those objects is outside the packet.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus field-faithfulness obligation]
\label{thm:cauchy-shared-tail-modulus-field-faithfulness-obligation}
For the carrier
$$
S=(R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N),
$$
the public fields $R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N$ determine the local $\NameCert_{\CauchySharedTailModulusUp}$ read. No proper subtuple of these fields exposes the same completion-facing $\RealUp$ seal, because omitting any paired source, request, threshold, dyadic ledger, window, readback, seal, transport, route, provenance, or local name removes a row used by the displayed handoff.
\end{theorem}
\begin{proof}
Start from \autoref{thm:cauchy-shared-tail-modulus-namecert-obligations}. It lists the carrier admission row, paired requests, shared threshold, dyadic ledger, paired windows, paired readbacks, Real seal, componentwise stability, route replay, provenance, and local name as the public NameCert surface.

Use \autoref{thm:cauchy-shared-tail-modulus-tail-synchronization} for the middle of the read. It forces the two request rows, the single threshold row, the dyadic ledger, both windows, and both regular readbacks to appear in the same finite route.

Finally apply \autoref{thm:cauchy-shared-tail-modulus-real-seal-handoff}. The Real seal is exposed only through the complete displayed route
$$
M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N.
$$

Dropping any listed field breaks either carrier admission, the synchronized finite route, or the authenticated Real seal handoff. Hence the full public tuple determines the NameCert read, while no proper subtuple exposes the same seal.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus public obligation package]
\label{thm:cauchy-shared-tail-modulus-public-obligation-package}
For the carrier
$$
S=(R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N),
$$
carrier admission, paired request exposure, the shared threshold, the dyadic ledger, paired $\StreamNameUp$ windows, paired $\RegSeqRatUp$ readbacks, $\RealUp$ seal ordering, componentwise transport, route replay, package provenance, and local $\NameCert_{\CauchySharedTailModulusUp}$ naming form one public obligation package. A consumer cannot detach any of these rows from the package while still claiming to read the shared-tail Real-completion surface.
\end{theorem}
\begin{proof}
Project the displayed packet $S$. The carrier definition exposes exactly the two sources, two modulus rows, one threshold row, one dyadic ledger, two windows, two readbacks, one Real seal, transport, route, provenance, and local name.

Use the local NameCert obligations and the tail synchronization theorem. They bind carrier admission, paired request exposure, shared-threshold exposure, window service, regular readback, and Real seal ordering to the same finite route.

Now apply the paired-window obligation, threshold uniqueness obligation, and field-faithfulness obligation. These rows prevent a consumer from replacing the shared threshold, splitting the paired windows into private routes, or dropping a public field while preserving the completion-facing Real seal read.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus Real-completion obligation closure]
\label{thm:cauchy-shared-tail-modulus-real-completion-obligation-closure}
Every Real-completion-facing consumer route for an accepted $\CauchySharedTailModulusUp$ packet must pass through the public obligation package of \autoref{thm:cauchy-shared-tail-modulus-public-obligation-package} before reading the $\RealUp$ seal. In particular, no such route may replace the shared threshold row $\tau$ and its dyadic ledger row $D$ by private per-source thresholds.
\end{theorem}
\begin{proof}
First apply the public obligation package theorem. It places carrier admission, paired request exposure, shared-threshold exposure, paired windows, paired readbacks, Real seal ordering, transport, replay, provenance, and local naming on one public surface.

Then use the Real seal handoff theorem. Any completion-facing read of the Real seal factors through the displayed route containing $M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N$.

Finally apply the threshold uniqueness obligation. Since the accepted carrier has only the shared threshold coordinate $\tau$ and ledger coordinate $D$, a route with private per-source thresholds is not a read of the packet.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus threshold transport stability]
\label{thm:cauchy-shared-tail-modulus-threshold-transport-stability}
For an accepted $\CauchySharedTailModulusUp$ packet, componentwise $\hsame$ transport along $H$ preserves the shared threshold row $\tau$ and the dyadic ledger row $D$ as one paired service for both source requests. Any transported consumer route that introduces a private left threshold, a private right threshold, or a second dyadic ledger is outside the local $\NameCert_{\CauchySharedTailModulusUp}$ package.
\end{theorem}
\begin{proof}
Read the carrier rows for $H$. The transport row is componentwise for the sources, extracted moduli, shared threshold, dyadic ledger, windows, readbacks, Real seal, provenance, and local name; it is not a constructor for new threshold coordinates.

Apply threshold uniqueness and dyadic ledger exactness. These two rows identify $\tau$ and $D$ as the only threshold service available to the accepted packet, and they keep both finite windows and both regular readbacks attached to that same service.

Now transport the displayed route by $H$. Since every transported component is a component of
$$
R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,P,N,
$$
the transported packet still has one threshold row and one ledger row. A route with private thresholds or a second ledger therefore asks for rows not carried by the packet.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus window readback transport]
\label{thm:cauchy-shared-tail-modulus-window-readback-transport}
For an accepted $\CauchySharedTailModulusUp$ packet, the paired windows $W_0,W_1$, paired readbacks $Q_0,Q_1$, and Real seal $E$ are transported only along the shared route recorded by $H$ and $C$. No transported read may detach $W_0$ or $W_1$ from $\tau,D$, detach $Q_0$ or $Q_1$ from the paired windows, or expose $E$ without the displayed shared-tail route.
\end{theorem}
\begin{proof}
Start with paired-window readback service. It serves $W_0,W_1,Q_0,Q_1$ from the same $\tau,D$ rows, so the window and readback transport has a single threshold source.

Use route replay provenance. The rows $H$ and $C$ transport and replay only the displayed route through the two sources, two extracted moduli, the shared threshold, the dyadic ledger, the paired windows, the paired readbacks, and the Real seal.

Finally apply the Real seal handoff. The seal row $E$ is downstream of the paired readbacks and the same shared threshold route, so a transported consumer that detaches a window, readback, or seal from $H,C$ is not reading the accepted package.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus obligation closure package]
\label{thm:cauchy-shared-tail-modulus-obligation-closure-package}
For the carrier
$$
S=(R_0,R_1,M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N),
$$
carrier admission, local $\NameCert$ obligations, tail synchronization, threshold uniqueness, threshold transport stability, paired window and readback transport, Real seal handoff, field-faithfulness, and the checked TasteGate carrier alignment form one $\obligationClosure$ surface for $\CauchySharedTailModulusUp$. The package has no coordinate for private thresholds, independent Real seals, quotient stream equality, host real equality, selected limits, or ambient completeness.
\end{theorem}
\begin{proof}
First collect carrier admission and the local NameCert obligations. They expose exactly the displayed rows of $S$ and assign them to paired source requests, one shared threshold, one dyadic ledger, paired windows, paired readbacks, one Real seal, componentwise transport, replay, provenance, and local naming.

Next use synchronization, threshold uniqueness, and threshold transport stability. These rows bind $M_0,M_1,\tau,D$ into one shared finite threshold service and exclude private thresholds under both direct reads and componentwise $\hsame$ transport.

Then apply window readback transport and Real seal handoff. They keep $W_0,W_1,Q_0,Q_1,E$ on the same $H,C$ route, so the completion-facing read cannot detach the seal from the paired finite route.

Finally combine field-faithfulness with the checked TasteGate carrier alignment. The public tuple is the whole local package surface, and the TasteGate marker records that the carrier alignment is a single visible packet. Thus the listed rows assemble the obligation surface without adding any hidden completion or quotient coordinate.
\end{proof}

\begin{theorem}[Cauchy shared-tail modulus falsifiable prediction]
\label{thm:cauchy-shared-tail-modulus-falsifiable-prediction}
If a consumer accepts a $\CauchySharedTailModulusUp$ packet while reading a $\RealUp$ seal before the shared threshold row $\tau$ or while replacing $\tau$ by two independent threshold rows, then that consumer is not reading the packet of \autoref{def:cauchy-shared-tail-modulus-carrier}. The accepted packet exposes one shared dyadic threshold before any Real seal route.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. There is exactly one shared threshold row $\tau$ and exactly one Real seal row $E$.

Use the NameCert obligations to order the public read. The paired request rows, the shared dyadic threshold, the dyadic ledger, both StreamName windows, and both RegSeqRat readbacks are displayed before the Real seal row can be consumed.

Replacing $\tau$ by two independent thresholds asks for carrier coordinates that are not present. Reading $E$ before $\tau$ violates the displayed route order, so either behavior leaves the accepted packet surface.
\end{proof}

\falsifiablePrediction{If a CauchySharedTailModulusUp packet is accepted, every RealUp completion-facing read factors through the displayed shared threshold before any Real seal is exposed.}

\independenceWitness{cauchymodulusextraction, dyadictailradiusledger, regularcauchytailmeet, realcompletionsealclassifier: none is bijective because each lacks either the paired request rows, the shared threshold row, or the combined Real seal handoff carried by $\CauchySharedTailModulusUp$.}

The Lean follow-up must create \texttt{lean4/BEDC/Derived/CauchySharedTailModulusUp/TasteGate.lean} with $\mathsf{Nontrivial}\ \CauchySharedTailModulusUp$ and $\mathsf{FieldFaithful}\ \CauchySharedTailModulusUp$ instances for the displayed carrier.

\closureat{CauchySharedTailModulusUp}{seedStr}
\closureat{CauchySharedTailModulusUp}{obligationStr}

\begin{closurestatus}{\CauchySharedTailModulusUp}
  \constructivestory{A $\CauchySharedTailModulusUp$ packet is generated from two regular-Cauchy source rows, extracted modulus rows, one shared dyadic threshold, a dyadic tolerance ledger, paired finite windows, paired regular readbacks, a Real seal handoff row, componentwise transports, displayed replay, provenance, and local naming.}
  \leanchecked{BEDC.Derived.CauchySharedTailModulusUp.taste\_gate}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:cauchy-shared-tail-modulus-carrier}, \autoref{thm:cauchy-shared-tail-modulus-namecert-obligations}, \autoref{thm:cauchy-shared-tail-modulus-tail-synchronization}, \autoref{thm:cauchy-shared-tail-modulus-real-seal-handoff}, \autoref{thm:cauchy-shared-tail-modulus-carrier-admission-exactness}, \autoref{thm:cauchy-shared-tail-modulus-paired-window-readback-service}, \autoref{thm:cauchy-shared-tail-modulus-route-replay-provenance}, \autoref{thm:cauchy-shared-tail-modulus-threshold-transport-stability}, \autoref{thm:cauchy-shared-tail-modulus-window-readback-transport}, \autoref{thm:cauchy-shared-tail-modulus-obligation-closure-package}, \autoref{thm:cauchy-shared-tail-modulus-falsifiable-prediction}, the checked TasteGate marker following \autoref{def:cauchy-shared-tail-modulus-carrier}, and the independence witness bind the obligation surface for shared-tail synchronization before Real seal exposure.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close quotient stream equality, host real equality, selected limits, independent per-source seal exposure, hidden threshold replacement, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Scoped closure requires binding the same carrier admission, shared threshold, paired window and readback rows, Real seal route, componentwise transport, replay, provenance, and TasteGate alignment to explicit primitive scope.}
\end{closurestatus}
