\chapter{A Concrete Naming Certificate for $\ManifoldUp$}
\label{ch:concrete-instances-manifold-namecert}

The manifold interface $\ManifoldUp$ packages a topological carrier with a finite atlas of charts into $(\RealUp)^n$ whose transition maps are constructively smooth. It depends on $\NameCert_{\TopologyUp}$ (\autoref{ch:concrete-instances-topology-namecert}) and the real-analytic certificate (\autoref{ch:concrete-instances-real-analytic-namecert}), and supplies the substrate for the bundle and de~Rham certificates.

\section{Carrier definition}
\label{sec:manifold-carrier}

\begin{definition}[Charted manifold carrier]
\label{def:manifold-charted-carrier}
A charted $\ManifoldUp$ carrier package over a $\TopologyUp$ source is a tuple
$$
\mathcal{M}=(X,\mathcal{T},A,\mathsf{Dom},\mathsf{domIx},\mathsf{chart},\mathsf{coord},\mathsf{Trans})
$$
with the following displayed data. The point carrier is a predicate
$X:\mathsf{BHist}\to\mathsf{Prop}$ on BEDC histories, and
$\mathcal{T}$ is an indexed open topology carrier for $X$ in the sense of
\autoref{def:topology-indexed-open-carrier}. The atlas index family $A$ is
finite. For every $a:A$, the chart-domain predicate
$\mathsf{Dom}_a:X\to\mathsf{Prop}$ is carried by a witnessed open
$\mathsf{domIx}(a):\mathsf{OpenIx}$:
$$
\mathsf{CarriesOpen}_{\mathcal{T}}(\mathsf{domIx}(a),\mathsf{Dom}_a).
$$
The chart map $\mathsf{chart}_a$ sends a point $x$ with
$\mathsf{Dom}_a(x)$ to a finite list of coordinate histories
$$
\mathsf{coord}_a(x)=(r_1,\ldots,r_{n(a)})
$$
whose entries satisfy the $\RealUp$ carrier and are classified by the
$\RealUp$ classifier under replacement of $x$ along the topology carrier
classifier.

For every overlap row $a,b:A$ and every point $x$ lying in
$\mathsf{Dom}_a\cap\mathsf{Dom}_b$, the ledger includes a transition entry
$$
\mathsf{Trans}_{a,b}(x):
\mathsf{coord}_a(x)\longmapsto \mathsf{coord}_b(x)
$$
whose source and target coordinate lists are finite $\RealUp$ histories and
whose local transport row is certified by the $\RealAnalyticUp$ boundary of
\autoref{thm:real-analytic-certificate-boundary}. Thus the manifold carrier
does not add a new equality principle: point sameness is the topology carrier
classifier, coordinate sameness is the $\RealUp$ classifier, and overlap
smoothness is ledgered by supplied real-analytic rows.
\end{definition}

\begin{definition}[Chart-atlas manifold carrier]
\label{def:manifold-chart-atlas-carrier}
A chart-atlas manifold carrier for $\ManifoldUp$ is a predicate
$\mathsf{ManAtlasPkg}(P)$ on $\mathsf{BHist}$ packages $P$ whose fields are the
following rows.
\begin{enumerate}
\item The traditional target is a finite-atlas topological manifold.
\item The BEDC source is $\TopologyUp$ together with $\RealUp$ coordinate
histories and real-analytic transition rows from
\autoref{ch:concrete-instances-real-analytic-namecert}.
\item The carrier row contains a topological carrier history $M$ with its
$\TopologyUp$ certificate, a finite chart-index history $I$, chart-domain
predicates $\mathsf{Dom}_i$ on $M$, chart maps
$\varphi_i:\mathsf{Dom}_i\to(\RealUp)^{n_i}$, and overlap transition ledgers
$\mathsf{Trans}_{ij}$ for each chart pair $i,j$.
\item The classifier row is componentwise $\hsame$ on $M$, on $I$, on every
chart-domain row, on every chart-map row, and on every transition ledger.
\item The stability row says that componentwise $\hsame$ transport of those
fields carries $\mathsf{ManAtlasPkg}$ packages to
$\mathsf{ManAtlasPkg}$ packages.
\item The ledger records topology rows, real-coordinate rows, overlap rows, and
constructively smooth transition certificates for each nonempty chart overlap.
\item The standard bridge row is absent: this carrier names the BEDC
obligation surface and does not assert an external manifold equivalence.
\end{enumerate}
Equivalently, $\mathsf{ManAtlasPkg}(P)$ is the ten-field
$\NameCert_{\ManifoldUp}$ source object whose public carrier is the finite
chart atlas over $M$, whose classifier is the displayed componentwise
$\hsame$ classifier, and whose visible ledger is the topology-coordinate-overlap
ledger just listed.
\end{definition}

\begin{definition}[Singleton empty-chart manifold package]
\label{def:manifold-singleton-empty-chart-package}
Let the BEDC manifold carrier be the singleton history predicate
$$
C_{\emp}(h)\quad\Longleftrightarrow\quad \hsame(h,\emp)
$$
on $\mathsf{BHist}$. Its carrier classifier is $\hsame$ restricted to
$C_{\emp}$: two carried histories classify when they are internally the same,
and the carrier side conditions are transported along $\hsame$.

The topology surface is the inherited indexed $\TopologyUp$ boundary surface on
this carrier. The distinguished top index carries $C_{\emp}$ itself, and the
distinguished bottom index carries the empty predicate. The membership ledger
records the chosen history, its $C_{\emp}$ witness, the classifier row, and the
boundary open witness supplied by $\TopologyUp$.

The atlas has one chart $\chi_{\emp}$. Its domain is the top open of the
displayed topology surface. Its target is the constant zero endpoint of
$\RealUp$, read through the real-analytic local constant stream boundary. For
every carried $h$, the chart value is the same constant endpoint, and the chart
ledger records $\mathsf{BHist}$, $\mathsf{UnaryHistory}$, $\hsame$, $\Cont$,
$\TopologyUp$, $\RealUp$, and the $\RealAnalyticUp$ constant-map boundary.

Thus the singleton package supplies the following ten certificate rows:
\begin{enumerate}
\item the traditional target is a one-point smooth manifold;
\item the BEDC source is $\mathsf{BHist}$ with $\emp$ as the displayed point;
\item the carrier choice is $C_{\emp}$;
\item the classifier choice is $\hsame$ restricted to $C_{\emp}$;
\item the stability obligations are carrier transport, top-domain transport,
bottom-domain exclusion, chart-value transport, and transition transport;
\item the ledger is the history, unary-history row, classifier row,
continuation row, topology boundary row, real constant endpoint row, and
real-analytic constant-map row;
\item the core theorem list is carrier topology scope, chart coverage,
transition smoothness, and the assembled $\ManifoldUp$ obligation package;
\item the exactness predicate says every chart-domain witness is exactly a
$C_{\emp}$ witness and every transition witness is the sole self-overlap row;
\item the standard bridge is absent;
\item the status is paper-side obligation target.
\end{enumerate}
\end{definition}

\section{The certificate}
\label{sec:manifold-certificate}

\begin{theorem}[Manifold chart endpoint coverage]
\label{thm:manifold-chart-endpoint-coverage}
For a charted carrier package $\mathcal{M}$ as in
\autoref{def:manifold-charted-carrier}, every displayed chart row exposes the
following endpoint data:
\begin{enumerate}
\item the underlying $\TopologyUp$ carrier row $X(x)$ and the classifier
$\mathsf{same}_X$ supplied by $\mathcal{T}$;
\item the witnessed open row
$\mathsf{CarriesOpen}_{\mathcal{T}}(\mathsf{domIx}(a),\mathsf{Dom}_a)$ for the
chart domain;
\item the finite $\RealUp$ coordinate output
$\mathsf{coord}_a(x)=(r_1,\ldots,r_{n(a)})$;
\item the visible atlas ledger entry recording $a$, $\mathsf{domIx}(a)$,
$x$, and the coordinate list.
\end{enumerate}
\end{theorem}
\begin{proof}
Unfold the charted carrier package of
\autoref{def:manifold-charted-carrier}. The first fields are exactly the
predicate $X$ on $\mathsf{BHist}$ and the indexed open topology carrier
$\mathcal{T}$, so the $\TopologyUp$ carrier and classifier are obtained by
projection.

For a fixed atlas index $a$, the same unfolding exposes the domain predicate
$\mathsf{Dom}_a$, the chosen open index $\mathsf{domIx}(a)$, and the carrying
equation for that open. This is the chart-domain open witness required by the
certificate.

Finally project the chart map field. Its output is already a finite list of
$\RealUp$ coordinate histories, and the atlas index plus open index are
retained in the package ledger. No quotient or hidden atlas representative is
introduced, so the displayed tuple is the visible readback of the chart row.
\end{proof}

\begin{theorem}[Manifold transition classifier stability]
\label{thm:manifold-transition-classifier-stability}
Let $\mathcal{M}$ be a charted carrier package. Suppose $x,y:\mathsf{BHist}$
are carried points with $\mathsf{same}_X(x,y)$, and suppose the atlas domains
$\mathsf{Dom}_a$ and $\mathsf{Dom}_b$ carry $x$ through their witnessed open
indices. Then the overlap transition row
$\mathsf{Trans}_{a,b}(x)$ transports to the corresponding row at $y$ using:
\begin{enumerate}
\item the topology carrier classifier and membership-stability field of
\autoref{def:topology-indexed-open-carrier};
\item the two carrying equations for
$\mathsf{CarriesOpen}_{\mathcal{T}}(\mathsf{domIx}(a),\mathsf{Dom}_a)$ and
$\mathsf{CarriesOpen}_{\mathcal{T}}(\mathsf{domIx}(b),\mathsf{Dom}_b)$;
\item the $\RealUp$ classifier on each coordinate of
$\mathsf{coord}_a(-)$ and $\mathsf{coord}_b(-)$;
\item the supplied $\RealAnalyticUp$ local transport rows from
\autoref{thm:real-analytic-certificate-boundary}.
\end{enumerate}
Consequently the transported source and target coordinate lists represent the
same overlap transition in the atlas ledger.
\end{theorem}
\begin{proof}
Begin with the topology side. The carrying equation for
$\mathsf{domIx}(a)$ converts $\mathsf{Dom}_a(x)$ into
$\mathsf{OpenAt}(\mathsf{domIx}(a),x)$. The membership-stability field of
\autoref{def:topology-indexed-open-carrier}, applied to
$\mathsf{same}_X(x,y)$, transports this open membership to $y$, and the same
carrying equation converts it back to $\mathsf{Dom}_a(y)$.

Repeat the identical argument for $b$. This supplies the transported overlap
witness $\mathsf{Dom}_a(y)\wedge\mathsf{Dom}_b(y)$, so the transition ledger
has the same atlas indices at the transported point.

Project the coordinate fields from
\autoref{def:manifold-charted-carrier}. Their stability clauses give
coordinatewise $\RealUp$ classifier witnesses from
$\mathsf{coord}_a(x)$ to $\mathsf{coord}_a(y)$ and from
$\mathsf{coord}_b(x)$ to $\mathsf{coord}_b(y)$.

The transition row itself is one of the real-analytic rows supplied at the
boundary of \autoref{thm:real-analytic-certificate-boundary}. Apply that row
to the transported overlap witness and the coordinatewise $\RealUp$ classifier
witnesses. The result is the transition row at $y$, classified by the same
visible atlas ledger entry.
\end{proof}

\begin{theorem}[Manifold charted NameCert surface]
\label{thm:manifold-charted-namecert-surface}
A charted carrier package $\mathcal{M}$ as in
\autoref{def:manifold-charted-carrier}, together with
\autoref{thm:manifold-chart-endpoint-coverage} and
\autoref{thm:manifold-transition-classifier-stability}, assembles the
paper-side $\NameCert_{\ManifoldUp}$ obligation surface. Its fields are the
$\mathsf{BHist}$ point carrier $X$, the $\TopologyUp$ classifier
$\mathsf{same}_X$, the finite atlas ledger, chart-domain open witnesses,
finite $\RealUp$ coordinate outputs, overlap-transition stability rows, and an
explicit statement that no standard bridge is claimed.
\end{theorem}
\begin{proof}
Unfold the NameCert template fields against
\autoref{def:manifold-charted-carrier}. The traditional target is a charted
manifold, the BEDC source is $\mathsf{BHist}$ equipped with the topology
carrier $\mathcal{T}$ and the finite atlas data, the carrier is $X$, and the
classifier is $\mathsf{same}_X$.

Endpoint coverage supplies the public readback rows: each chart exposes its
carried point, witnessed open domain, finite coordinate output, and atlas
ledger entry. These are exactly the carrier, source, and ledger fields needed
by the certificate surface.

Transition classifier stability supplies the stability field. It transports
overlap rows along the topology classifier, uses the two chart-domain carrying
equations to keep the point inside both domains, and then invokes the
$\RealUp$ and $\RealAnalyticUp$ rows for coordinate and smooth-transition
transport.

The exactness policy is visible-ledger exactness: a manifold chart row is
accepted only through the displayed atlas index, open witness, coordinate
output, and transition row. The standard bridge field is absent, so the
assembled surface is a BEDC paper-side NameCert obligation package rather than
a bridge to an external manifold library.
\end{proof}

\begin{theorem}[Manifold chart-transition classifier stability]
\label{thm:manifold-chart-transition-classifier-stability}
Let $P$ and $Q$ be $\mathsf{BHist}$ packages. Suppose
$\mathsf{ManAtlasPkg}(P)$ holds and the data of $P$ and $Q$ are related
componentwise by $\hsame$: the topological carrier histories are $\hsame$, the
finite chart-index histories are $\hsame$, corresponding chart-domain rows are
$\hsame$, corresponding chart-map rows are $\hsame$, and corresponding
real-analytic transition ledgers are $\hsame$. Then
$\mathsf{ManAtlasPkg}(Q)$ holds.
\end{theorem}
\begin{proof}
Unpack $\mathsf{ManAtlasPkg}(P)$ using
\autoref{def:manifold-chart-atlas-carrier}. The package supplies the
$\TopologyUp$ carrier row for $M$, the finite chart-index row, all chart-domain
and chart-map rows, and the overlap transition ledgers.

Transport the topological carrier by the supplied $\hsame$ comparison of the
carrier histories. Transport the finite chart-index row in the same way. For
each chart index, transport the domain predicate and the chart-map row by the
componentwise $\hsame$ hypotheses.

For each chart pair, transport the real-coordinate transition ledger and the
constructively smooth transition certificate by the corresponding
real-analytic $\hsame$ row. Repack the transported topology, chart, map,
overlap, and smoothness rows. These are exactly the fields required by
\autoref{def:manifold-chart-atlas-carrier} for
$\mathsf{ManAtlasPkg}(Q)$.
\end{proof}

\begin{theorem}[Manifold atlas overlap coverage]
\label{thm:manifold-atlas-overlap-coverage}
Every carried atlas package $P$ with $\mathsf{ManAtlasPkg}(P)$ exposes, for
each chart pair $i,j$ in its finite chart-index history, a domain-overlap row
$$
\mathsf{Overlap}_{ij}(x)
:\Longleftrightarrow
\mathsf{Dom}_i(x)\wedge\mathsf{Dom}_j(x)
$$
on the topological carrier and the corresponding constructively smooth
$\RealUp$ transition ledger from $\varphi_i$-coordinates to
$\varphi_j$-coordinates on that overlap.
\end{theorem}
\begin{proof}
Unpack the carried atlas package by
\autoref{def:manifold-chart-atlas-carrier}. The finite chart-index row gives
the admissible chart pairs, while the chart-domain rows give the two predicates
$\mathsf{Dom}_i$ and $\mathsf{Dom}_j$ over the same topological carrier.

For a fixed pair $i,j$, form the overlap row by conjunction of the two domain
memberships. The topology ledger records the carrier support of both domains,
so the overlap row is a predicate on the same topological carrier $M$.

The package ledger contains, for this same pair, the transition row
$\mathsf{Trans}_{ij}$. Its real-coordinate part records the source and target
$\RealUp$ coordinate histories, and its real-analytic part records the
constructively smooth transition certificate on the displayed overlap. Project
these two ledger components to obtain the claimed coverage row.
\end{proof}

\begin{theorem}[Manifold name-certificate obligation surface]
\label{thm:manifold-namecert-obligation-surface}
The carrier definition of
\autoref{def:manifold-chart-atlas-carrier}, together with
\autoref{thm:manifold-chart-transition-classifier-stability} and
\autoref{thm:manifold-atlas-overlap-coverage}, assembles the paper-side
$\ManifoldUp$ obligation surface. The surface consists of a topological carrier,
a finite chart atlas, chart classifier stability, overlap coverage, the
transition-smoothness ledger, and no standard bridge row.
\end{theorem}
\begin{proof}
The carrier definition supplies the named source object:
$\TopologyUp$ rows for the base carrier, $\RealUp$ coordinate rows for chart
targets, finite chart-index data, chart domains, chart maps, and transition
ledgers.

\autoref{thm:manifold-chart-transition-classifier-stability} supplies the
classifier-stability obligation for the whole package, because every public
field is transported by the componentwise $\hsame$ classifier specified in the
carrier definition.

\autoref{thm:manifold-atlas-overlap-coverage} supplies the overlap and
transition-smoothness obligations. The absence of a standard bridge is already
part of the carrier definition, so the assembled object is exactly the
$\ManifoldUp$ paper obligation surface listed in the theorem statement.
\end{proof}

\begin{theorem}[Singleton manifold carrier topology scope]
\label{thm:manifold-singleton-carrier-topology-scope}
For histories $h,k:\mathsf{BHist}$, if $C_{\emp}(h)$ and $\hsame(h,k)$ hold,
then $C_{\emp}(k)$ holds. Moreover the inherited indexed $\TopologyUp$ boundary
surface has the exact scope:
$$
\mathsf{OpenAt}(\top_{\TopologyUp},h)\Longleftrightarrow C_{\emp}(h)
$$
and
$$
\mathsf{OpenAt}(\bot_{\TopologyUp},h)\Longleftrightarrow \bot.
$$
Consequently the top open transports along the restricted $\hsame$ classifier,
and the bottom open contributes no carried point.
\end{theorem}
\begin{proof}
Unfold $C_{\emp}$ from
\autoref{def:manifold-singleton-empty-chart-package}. A witness
$C_{\emp}(h)$ is exactly $\hsame(h,\emp)$. Compose it with the supplied
$\hsame(h,k)$ using symmetry and transitivity of $\hsame$, with orientation
chosen so that the endpoint is $\hsame(k,\emp)$. This is the carrier witness
$C_{\emp}(k)$.

For the topology scope, use the indexed boundary open witnesses of
\autoref{def:topology-indexed-boundary-open-witnesses} and the boundary closure
of \autoref{thm:topology-indexed-open-boundary-closure}. The top index carries
the whole displayed carrier predicate, which in this instance is $C_{\emp}$,
while the bottom index carries the empty predicate.

The transport statement is then the same membership-stability field from
\autoref{def:topology-indexed-open-carrier}, specialized to the top boundary
index. The bottom clause has no point to transport because its carried
predicate is $\bot$.
\end{proof}

\begin{theorem}[Singleton manifold chart coverage]
\label{thm:manifold-singleton-chart-coverage}
The one-chart atlas $\{\chi_{\emp}\}$ of
\autoref{def:manifold-singleton-empty-chart-package} covers exactly the
carried histories:
$$
h\in\mathsf{dom}(\chi_{\emp})
\Longleftrightarrow
C_{\emp}(h).
$$
For every such $h$, the chart exposes the same constant zero endpoint of
$\RealUp$:
$$
\chi_{\emp}(h)=0_{\RealUp}.
$$
The chart-domain ledger is therefore the top-open witness together with the
$C_{\emp}$ witness, and the chart-value ledger is the real constant endpoint
row.
\end{theorem}
\begin{proof}
By definition of the atlas in
\autoref{def:manifold-singleton-empty-chart-package}, the domain of
$\chi_{\emp}$ is the distinguished top open of the inherited indexed topology
surface. Apply
\autoref{thm:manifold-singleton-carrier-topology-scope} to identify this
membership with $C_{\emp}(h)$.

For the value statement, unfold the chart map. It is the constant map whose
target is the displayed zero endpoint of $\RealUp$. No property of $h$ is used
except membership in the top domain, so the same endpoint is exposed for every
carried history.

The ledger statement is just the pairing of these two witnesses. Domain
coverage records the top-open row and its $C_{\emp}$ readback; value coverage
records the real endpoint row supplied by the local constant stream boundary.
\end{proof}

\begin{theorem}[Singleton manifold transition smoothness]
\label{thm:manifold-singleton-transition-smoothness}
Every nonempty chart overlap in the singleton atlas is the self-overlap of
$\chi_{\emp}$. On that overlap the transition map is simultaneously the
identity transition on the displayed singleton domain and the constant
$0_{\RealUp}$ transition on the target endpoint. This transition is accepted by
the real-analytic local constant stream boundary.
\end{theorem}
\begin{proof}
There is only one chart in the atlas, so any overlap whose two chart names are
present must be the pair $(\chi_{\emp},\chi_{\emp})$. The domain side is the
top open, hence \autoref{thm:manifold-singleton-chart-coverage} identifies the
overlap points exactly with $C_{\emp}$.

On the carrier side, two points in the overlap are classified by the restricted
$\hsame$ relation. Since every carried point is $\hsame$ to $\emp$, transitivity
identifies all visible overlap histories with the same singleton point.

On the target side, both charts expose $0_{\RealUp}$. The transition therefore
has no varying real argument: it is the identity when read on the singleton
domain and the constant zero map when read on the real endpoint. The
$\RealAnalyticUp$ local constant stream boundary accepts exactly this constant
map, so the overlap transition supplies the required smoothness row.
\end{proof}

\begin{theorem}[Singleton manifold NameCert obligation package]
\label{thm:manifold-singleton-namecert-obligation-package}
The rows of
\autoref{def:manifold-singleton-empty-chart-package},
\autoref{thm:manifold-singleton-carrier-topology-scope},
\autoref{thm:manifold-singleton-chart-coverage}, and
\autoref{thm:manifold-singleton-transition-smoothness} assemble the
paper-side $\NameCert_{\ManifoldUp}$ obligation package for the singleton
empty-chart construction.
\end{theorem}
\begin{proof}
The traditional target row is the one-point smooth manifold. The BEDC source
row is $\mathsf{BHist}$ with the displayed empty history, and the carrier row
is the predicate $C_{\emp}$. The classifier row is $\hsame$ restricted to that
carrier.

The stability rows are supplied by the carrier transport in
\autoref{thm:manifold-singleton-carrier-topology-scope}, the top and bottom
boundary rows inherited from $\TopologyUp$, the chart coverage statement of
\autoref{thm:manifold-singleton-chart-coverage}, and the transition statement
of \autoref{thm:manifold-singleton-transition-smoothness}.

The ledger records $\mathsf{BHist}$, $\mathsf{UnaryHistory}$, $\hsame$,
$\Cont$, the indexed $\TopologyUp$ boundary rows, the $\RealUp$ constant
endpoint, and the $\RealAnalyticUp$ constant-map boundary. These are precisely
the rows named in the construction package, with no hidden atlas component.

The core theorem list is the four displayed rows of this section. Exactness is
the pair of readbacks: the chart domain is exactly $C_{\emp}$, and the only
transition is the self-overlap constant transition. The standard bridge row is
absent, and the resulting status is a paper-side obligation target for the
Lean declaration
$\mathsf{BEDC.Derived.ManifoldUp.SingletonEmptyChart\_name\_certificate}$.
\end{proof}

\begin{definition}[Singleton manifold atlas ledger]
\label{def:manifold-singleton-atlas-ledger}
The singleton manifold atlas ledger is the $\mathsf{BHist}$ package determined
by the carrier $C_{\emp}$ of
\autoref{def:manifold-singleton-empty-chart-package}, the single chart index
$\chi_{\emp}$, the top-open chart domain supplied by $\TopologyUp$, the constant
$0_{\RealUp}$ endpoint supplied by $\RealUp$, and the
$\RealAnalyticUp$ local constant transition row. Its ten-field template is:
\begin{description}
\item[Traditional target.] The one-point smooth manifold.
\item[BEDC source.] $\mathsf{BHist}$ with distinguished history $\emp$.
\item[Carrier.] The predicate $C_{\emp}(h)$, equivalently $\hsame(h,\emp)$.
\item[Classifier.] The relation $\hsame$ restricted to $C_{\emp}$.
\item[Stability obligations.] Carrier transport, top-open membership transport,
chart-domain readback, chart-value constancy, and transition-row constancy.
\item[Ledger.] The rows
$\mathsf{BHist}$, $\mathsf{UnaryHistory}$, $\hsame$, $\Cont$, the indexed
$\TopologyUp$ boundary rows, the $\RealUp$ zero endpoint, and the
$\RealAnalyticUp$ constant-map row.
\item[Core theorem list.]
\autoref{thm:manifold-singleton-carrier-topology-scope},
\autoref{thm:manifold-singleton-chart-coverage},
\autoref{thm:manifold-singleton-transition-smoothness}, and
\autoref{thm:manifold-singleton-namecert-obligation-package}.
\item[Exactness.] The only accepted domain witness is the top-open
$C_{\emp}$ witness, and the only accepted overlap transition is the
self-overlap constant transition.
\item[No standard bridge.] The ledger contains no $\StdBridge$ row.
\item[Status.] A paper-side $\NameCert_{\ManifoldUp}$ obligation target for
later formalization under $\mathsf{BEDC.Derived.ManifoldUp}$.
\end{description}
\end{definition}

\begin{theorem}[Singleton manifold atlas index exhaustion]
\label{thm:manifold-singleton-atlas-index-exhaustion}
In the singleton manifold atlas ledger of
\autoref{def:manifold-singleton-atlas-ledger}, every visible chart-index row is
the sole index $\chi_{\emp}$. Every nonempty overlap row is the pair
$(\chi_{\emp},\chi_{\emp})$, and every accepted chart-domain witness is exactly
the top-open $C_{\emp}$ witness.
\end{theorem}
\begin{proof}
Unfold the atlas ledger of
\autoref{def:manifold-singleton-atlas-ledger} and the construction package of
\autoref{def:manifold-singleton-empty-chart-package}. The chart-index field is
the displayed singleton list, so any visible chart row has the unique name
$\chi_{\emp}$.

With only one chart name available, a nonempty overlap can have no index pair
other than $(\chi_{\emp},\chi_{\emp})$. The overlap is nonempty exactly when its
domain side admits a carried history, and the only domain side exposed by the
construction is the inherited top open.

Apply
\autoref{thm:manifold-singleton-carrier-topology-scope} to identify that
top-open membership with $C_{\emp}$. Then apply
\autoref{thm:manifold-singleton-chart-coverage} to read the same witness as
the chart-domain ledger row, proving that no second chart-domain witness is
present.
\end{proof}

\begin{theorem}[Singleton manifold chart-value transport]
\label{thm:manifold-singleton-chart-value-transport}
Let $h,k:\mathsf{BHist}$. If $C_{\emp}(h)$, $C_{\emp}(k)$, and $\hsame(h,k)$
hold, then the chart-value ledger transports the value
$\chi_{\emp}(h)=0_{\RealUp}$ to the value $\chi_{\emp}(k)=0_{\RealUp}$. Under
the same transport, the transition ledger remains the
$\RealAnalyticUp$ constant-map row for the self-overlap
$(\chi_{\emp},\chi_{\emp})$.
\end{theorem}
\begin{proof}
Use the carrier witnesses to read both $h$ and $k$ as histories in
$C_{\emp}$. The relation $\hsame(h,k)$ supplies the classifier transport
between them, and symmetry and transitivity of $\hsame$ keep the transport
inside the singleton carrier.

Apply \autoref{thm:manifold-singleton-chart-coverage} to the carried history
$h$. The chart value is the constant endpoint $0_{\RealUp}$. Apply the same
coverage theorem to the carried history $k$; the target endpoint is again
$0_{\RealUp}$, so the chart-value ledger has transported the displayed value
without changing the real row.

Finally apply
\autoref{thm:manifold-singleton-transition-smoothness}. Since the atlas has
only the self-overlap $(\chi_{\emp},\chi_{\emp})$ and both chart readings are
the same constant endpoint, the transition ledger is still the
$\RealAnalyticUp$ local constant map row.
\end{proof}
