\chapter{A Concrete Naming Certificate for $\LargeModelContextAuditUp$}
\label{ch:concrete-instances-largemodelcontextaudit-namecert}
\origin{ai}

The $\LargeModelContextAuditUp$ packet realizes the context-and-audit side of \autoref{ch:visions-large-model-as-inscription-point} as finite BEDC data. It consumes the context-window commitment of \autoref{ch:concrete-instances-contextwindowcommitment-namecert}, the prompt-response trace of \autoref{ch:concrete-instances-prompt-response-trace-namecert}, the model-trace surface of \autoref{ch:concrete-instances-modeltrace-namecert}, the audit channel of \autoref{ch:concrete-instances-largemodelauditchannel-namecert}, and the checked-output harness of \autoref{ch:concrete-instances-verifiedoutputharness-namecert}. Its distinguishing role is a finite context-audit packet: a model output is accepted only after the displayed context, prompt-response, model trace, audit channel, verified harness, refusal, transport, continuation, provenance, and local naming rows have been read together.

\begin{definition}[LargeModelContextAudit carrier]
\label{def:large-model-context-audit-carrier}
A $\LargeModelContextAuditUp$ carrier is a finite $\BHist$ packet
$$
X=(C,T,M,A,V,R,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $C$ is the $\ContextWindowCommitmentUp$ row naming the bounded prompt context, response boundary, admitted source rows, and downstream consumer surface;
\item $T$ is the $\PromptResponseTraceUp$ row recording the prompt, response, source-channel route, observer-interface handoff, and obstruction boundary;
\item $M$ is the $\ModelTraceUp$ row recording the finite model-state trace, output trace, corpus-supply row, refusal row, and accepted readback;
\item $A$ is the $\LargeModelAuditChannelUp$ row carrying prompt, output, checker, refusal, audit membrane, route, provenance, and local name;
\item $V$ is the $\VerifiedOutputHarnessUp$ row carrying the checker-facing acceptance harness for the same output record;
\item $R$ is the refusal row, recording unsupported, out-of-context, unverifiable, policy-refused, or route-incomplete claims before acceptance is exposed;
\item $H$ records componentwise $\hsame$ transport for context, prompt-response, model-trace, audit-channel, harness, refusal, route, provenance, and naming rows;
\item $K$ records the displayed $\Cont$ route by which a consumer reads $C$, then $T$, then $M$, then $A$ and $V$, before reaching $R,P,N$;
\item $P$ is the $\Pkg$ provenance over $\ContextWindowCommitmentUp$, $\PromptResponseTraceUp$, $\ModelTraceUp$, $\LargeModelAuditChannelUp$, $\VerifiedOutputHarnessUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\LargeModelContextAuditUp}$ row.
\end{enumerate}
The carrier has no coordinate for hidden context recovery, unchecked model output acceptance, unrecorded checker state, host semantic understanding, corpus-wide truth, or a private route bypassing the displayed context-audit ledger.
\end{definition}
\leanchecked{BEDC.Derived.LargeModelContextAuditUp.LargeModelContextAuditTasteGate\_single\_carrier\_alignment}

\begin{theorem}[LargeModelContextAudit NameCert obligations]
\label{thm:large-model-context-audit-namecert-obligations}
For the carrier of \autoref{def:large-model-context-audit-carrier}, the local $\NameCert_{\LargeModelContextAuditUp}$ surface consists of carrier admission for
$$
X=(C,T,M,A,V,R,H,K,P,N),
$$
classifier transport for the same rows under componentwise $\hsame$, route exactness through the displayed $\Cont$ row $K$, refusal exactness through $R$, audit-channel and verified-harness exposure through $A$ and $V$, provenance through $P$, and local naming through $N$. Every accepted consumer read of a model output factors through the displayed $\ContextWindowCommitmentUp$, $\PromptResponseTraceUp$, $\ModelTraceUp$, $\LargeModelAuditChannelUp$, and $\VerifiedOutputHarnessUp$ rows before the output can be accepted.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:large-model-context-audit-carrier}. The packet displays context, prompt-response trace, model trace, audit channel, verified harness, refusal, transport, route, provenance, and local naming rows as its entire public surface.

Classifier transport is componentwise. A transported packet must carry $C,T,M,A,V,R,H,K,P,N$ together, so a changed context window, trace row, checker row, refusal row, or verified harness cannot be silently retained by the same local name.

Route exactness follows from $K$. A consumer first reads the bounded context row $C$, then the prompt-response row $T$, then the model-trace row $M$, and only then reaches the audit channel $A$ and verified harness $V$ before refusal, provenance, and naming are exposed.

The non-escape clauses follow from the carrier inventory. No row stores hidden context recovery, unchecked acceptance, unrecorded checker state, host semantic understanding, corpus-wide truth, or a private acceptance route.
\end{proof}
\leanchecked{BEDC.Derived.LargeModelContextAuditUp.TasteGate.LargeModelContextAuditTasteGate\_single\_carrier\_alignment}

\begin{theorem}[LargeModelContextAudit refusal factorization]
\label{thm:large-model-context-audit-refusal-factorization}
Every refusal or accepted-output decision exposed by an accepted $\LargeModelContextAuditUp$ carrier
$$
X=(C,T,M,A,V,R,H,K,P,N)
$$
factors through the displayed context-window commitment, prompt-response trace, model trace, audit channel, verified output harness, componentwise transport, continuation route, provenance, and local naming rows. In particular, a consumer cannot accept a model output by reading $V$ alone; the read must also pass through $C,T,M,A,R,H,K,P,N$.
\end{theorem}
\begin{proof}
Start with a refusal or accepted-output read. The entry row is the bounded context commitment $C$, because the packet has no separate coordinate for hidden context recovery or a bare output acceptance.

The prompt-response row $T$ and model-trace row $M$ then identify the finite emitted record being audited. These rows bind the output to its prompt, source-channel route, trace, corpus-supply handoff, and refusal boundary before any checker-facing surface is consumed.

The audit-channel row $A$ and verified-harness row $V$ provide the checker and acceptance surfaces. The refusal row $R$ records unsupported or out-of-context outcomes before the local name can expose acceptance.

Finally route the read through $H,K,P,N$. Those rows supply transport, continuation, provenance, and local naming data, so the consumer receives a displayed context-audit packet rather than a private evaluator route or an unchecked model emission.
\end{proof}

\falsifiablePrediction{Any accepted LargeModelContextAuditUp consumer factors through displayed ContextWindowCommitmentUp, PromptResponseTraceUp, ModelTraceUp, LargeModelAuditChannelUp, and VerifiedOutputHarnessUp rows before accepting a model output.}

\independenceWitness{contextwindowcommitment, promptresponsetrace, modeltrace, largemodelauditchannel, verifiedoutputharness: the context-audit packet is not bijective with these siblings because it binds their rows into one consumer route and adds a shared refusal, transport, continuation, provenance, and local NameCert surface that no single sibling carries alone.}

The Lean follow-up must provide $\mathsf{Nontrivial}\ \LargeModelContextAuditUp$ and $\mathsf{FieldFaithful}\ \LargeModelContextAuditUp$ instances in $\mathsf{BEDC.Derived.LargeModelContextAuditUp/TasteGate.lean}$ for the same finite carrier.

\closureat{LargeModelContextAuditUp}{seedStr}

\begin{closurestatus}{\LargeModelContextAuditUp}
  \constructivestory{A $\LargeModelContextAuditUp$ packet is generated from context-window commitment, prompt-response trace, model trace, audit channel, verified output harness, refusal, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:large-model-context-audit-carrier}, \autoref{thm:large-model-context-audit-namecert-obligations}, and \autoref{thm:large-model-context-audit-refusal-factorization} specify the finite context-audit packet and its consumer route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close model consciousness, corpus truth, host semantic understanding, global checker correctness, hidden context recovery, Lean verification, or bridge checking for $\LargeModelContextAuditUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, context-route exactness, refusal factorization, nontriviality, and field faithfulness for the same context-audit carrier.}
\end{closurestatus}
