\chapter{A Concrete Naming Certificate for $\BundleUp$}
\label{ch:concrete-instances-bundle-namecert}

The bundle interface $\BundleUp$ packages a fibred carrier $E \to B$ with locally trivial fibres of a fixed model type. It depends on $\NameCert_{\ManifoldUp}$ (\autoref{ch:concrete-instances-manifold-namecert}) for the base and total-space topology, and supplies the substrate for the tangent, cotangent, and frame bundles.

\section{Carrier definition}
\label{sec:bundle-carrier}

\begin{definition}[Bundle local-trivialization obligation surface]
\label{def:bundle-local-trivialization-obligation-surface}
The local-trivialization obligation surface for $\BundleUp$ is the ten-field
$\NameCert_{\BundleUp}$ template whose rows are fixed as follows.
\begin{enumerate}
\item The traditional target is a fibred carrier $\pi:E\to B$ whose fibres are
locally trivial over a fixed fibre model $F$.
\item The BEDC source is $\NameCert_{\ManifoldUp}$ together with visible
$\mathsf{BHist}$ histories for the base space, the total space, the projection,
local trivializations, transition data, and the source ledger.
\item The carrier is a $\mathsf{BHist}$ package
$\mathsf{BundleLocalTrivPkg}(P)$ exposing a base manifold row $B$, a total
manifold row $E$, a projection row $\pi$, a fibre-model row $F$, finite
chart-trivialization $\mathsf{ProbeBundle}$ rows, transition rows on overlaps,
and a ledger row recording the source of each displayed field.
\item The retained manifold classifier from $\NameCert_{\ManifoldUp}$ classifies
the base and total manifold rows.
\item The remaining classifier is componentwise $\hsame$ on projection
histories, fibre-model histories, trivialization $\mathsf{ProbeBundle}$ rows,
transition rows, and source-ledger rows.
\item Carrier stability transports $\mathsf{BundleLocalTrivPkg}$ packages along
the retained manifold classifier on $B$ and $E$ and along componentwise
$\hsame$ on every displayed bundle row.
\item Projection compatibility says that transport of $\pi$ along the base and
total classifiers remains the displayed projection row between the transported
manifold rows.
\item Transition congruence says that if two overlapping trivialization rows
are transported by componentwise $\hsame$, then the corresponding transition
row is transported to the displayed transition row over the transported
overlap.
\item Ledger descent says that every transported carrier, projection,
trivialization, fibre-model, and transition row keeps the same source entry
after replacing its fields by classified histories.
\item Exactness is visible local-trivialization readback: every accepted
$\NameCert_{\BundleUp}$ field is one of the carrier, classifier, stability,
projection, transition, ledger, and readback rows above. The standard bridge
row is absent.
\end{enumerate}
\end{definition}

\section{The certificate}
\label{sec:bundle-certificate}

\begin{theorem}[Bundle carrier projection obligation]
\label{thm:bundle-carrier-projection-obligation}
Every carried row of $\mathsf{BundleLocalTrivPkg}(P)$ exposes exactly the
base manifold row, total manifold row, projection row, fibre-model row,
trivialization $\mathsf{ProbeBundle}$ row, transition row, and source-ledger
row displayed in
\autoref{def:bundle-local-trivialization-obligation-surface}. There is no
other carrier case in the $\BundleUp$ obligation surface.
\end{theorem}
\begin{proof}
Unpack $\mathsf{BundleLocalTrivPkg}(P)$ by
\autoref{def:bundle-local-trivialization-obligation-surface}. The carrier
slot is a $\mathsf{BHist}$ package whose displayed fields are the base row,
total row, projection row, fibre-model row, trivialization
$\mathsf{ProbeBundle}$ rows, transition rows, and source ledger.

Projecting a carried bundle row therefore reads one of those listed fields.
The base and total projections are manifold rows classified by the upstream
$\NameCert_{\ManifoldUp}$ row, while the projection, fibre, trivialization,
transition, and ledger projections are the componentwise $\hsame$ fields of
the same package.

No additional branch is available: the carrier predicate is the displayed
package predicate itself, and its final readback row accepts only the listed
fields. Thus every carried row is one of the named rows, and the carrier has no
second case.
\end{proof}

\begin{theorem}[Bundle trivialization transition stability]
\label{thm:bundle-trivialization-transition-stability}
For packages satisfying $\mathsf{BundleLocalTrivPkg}$, componentwise $\hsame$
transport preserves local trivialization rows and transition compatibility
through the retained $\NameCert_{\ManifoldUp}$ classifier on the base and total
manifold rows.
\end{theorem}
\begin{proof}
Start with a carried package and a componentwise transport witness. The base
and total manifold rows are transported by the classifier retained from
$\NameCert_{\ManifoldUp}$, so their chart and overlap histories remain accepted
manifold histories.

The trivialization row is a finite $\mathsf{ProbeBundle}$ of local witnesses.
Induct on that closed probe bundle. The empty probe row is preserved by the
carrier-stability clause, and each bundled probe is transported by the
componentwise $\hsame$ classifier on its trivialization history.

For an overlap row, the transition congruence field of
\autoref{def:bundle-local-trivialization-obligation-surface} compares the two
transported trivialization rows and the displayed transition row. Projection
compatibility supplies the same base and total rows after transport, so the
transition still relates fibres over the transported base overlap.

Ledger descent then transports the provenance row for the trivialization and
transition witnesses. Hence local trivialization rows and transition
compatibility are preserved by the displayed $\hsame$ transport.
\end{proof}

\begin{theorem}[Bundle NameCert exactness obligation]
\label{thm:bundle-namecert-exactness-obligation}
The public fields of $\NameCert_{\BundleUp}$ are exactly the carrier,
classifier, stability, transition ledger, visible exactness readback, and
absent bridge row specified by
\autoref{def:bundle-local-trivialization-obligation-surface}.
\end{theorem}
\begin{proof}
First project the carrier by
\autoref{thm:bundle-carrier-projection-obligation}. This accounts for the base
manifold row, total manifold row, projection row, fibre-model row,
trivialization $\mathsf{ProbeBundle}$ row, transition row, and source-ledger
row.

Next read the classifier and stability fields from the definition. The
classifier is the retained $\NameCert_{\ManifoldUp}$ classifier on base and
total rows together with componentwise $\hsame$ on all bundle-specific
histories. The stability fields are carrier transport, projection
compatibility, transition congruence, and ledger descent.

Finally apply the visible local-trivialization readback row. It accepts only
the displayed carrier fields, the displayed classifier and stability fields,
the transition ledger, and the explicit statement that the standard bridge row
is absent. Therefore the public $\NameCert_{\BundleUp}$ surface is exhausted
by exactly those fields.
\end{proof}

\begin{theorem}[Bundle projection and fibre source scope]
\label{thm:bundle-projection-fibre-source-scope}
In every carried $\mathsf{BundleLocalTrivPkg}(P)$ row, the base row, total row,
projection row, fibre-model row, and source row are scoped entirely by
$\mathsf{BHist}$. The base and total rows use the retained
$\NameCert_{\ManifoldUp}$ classifier, while projection, fibre, and source rows
are compared by componentwise $\hsame$ rather than by host-level functions.
\end{theorem}
\begin{proof}
Apply \autoref{def:bundle-local-trivialization-obligation-surface} to read the
displayed bundle surface. Its source row is a visible $\mathsf{BHist}$ ledger,
and its base, total, projection, and fibre-model entries are also displayed as
histories inside $\mathsf{BundleLocalTrivPkg}(P)$.

Apply \autoref{thm:bundle-carrier-projection-obligation} to project those rows
from the carried package. The base and total rows are classified by the retained
$\NameCert_{\ManifoldUp}$ row, and every bundle-specific row is transported only
by the componentwise $\hsame$ clauses of the surface.

Thus no host function is part of the scoped comparison. The fibre and
projection data remain named histories, and the ledger records their sources in
the same $\mathsf{BHist}$ vocabulary.
\end{proof}

\begin{theorem}[Bundle trivialization ProbeBundle scope]
\label{thm:bundle-trivialization-probebundle-scope}
The finite trivialization rows in $\mathsf{BundleLocalTrivPkg}(P)$ are exactly
$\mathsf{ProbeBundle}$ witnesses. Componentwise $\hsame$ transport preserves
their scope by induction on the closed constructors $\mathsf{Bnil}$ and
$\mathsf{Bcons}$.
\end{theorem}
\begin{proof}
Read the trivialization row from
\autoref{def:bundle-local-trivialization-obligation-surface}. The row is not an
external family of functions: it is the finite $\mathsf{ProbeBundle}$ field
listed in the carried bundle package.

Induct on the displayed probe bundle. In the $\mathsf{Bnil}$ case, the empty
witness has no chart row to transport, so the carrier-stability field preserves
the row directly.

In the $\mathsf{Bcons}$ case, the head witness is transported by the
componentwise $\hsame$ classifier on its trivialization history. The induction
hypothesis preserves the remaining witnesses, and the closed constructor
reassembles the transported $\mathsf{ProbeBundle}$ row.

This is precisely the stability mechanism used in
\autoref{thm:bundle-trivialization-transition-stability}, so finite
trivialization scope is preserved without leaving the BEDC history language.
\end{proof}

\begin{theorem}[Bundle transition and ledger scope]
\label{thm:bundle-transition-ledger-scope}
Transition rows and source-ledger rows in $\mathsf{BundleLocalTrivPkg}(P)$
descend under componentwise $\hsame$. The descent uses the retained
$\NameCert_{\ManifoldUp}$ classifier only for the base and total manifold rows;
overlap transitions and ledger entries remain bundle-specific
$\mathsf{BHist}$ rows.
\end{theorem}
\begin{proof}
Start with two transported trivialization rows. By
\autoref{thm:bundle-trivialization-transition-stability}, their overlap row is
still compared after transport through the displayed transition congruence
field.

The manifold part of the comparison is exactly the retained
$\NameCert_{\ManifoldUp}$ classifier on base and total rows. The transition row
itself is not reinterpreted as a host map; it is the transported
bundle-specific history named by the componentwise $\hsame$ field.

Finally apply the ledger-descent row of
\autoref{def:bundle-local-trivialization-obligation-surface}. It sends the
source entry for each carrier, projection, trivialization, fibre-model, and
transition row to the corresponding transported source entry. Hence both the
transition row and the ledger row descend in the same scoped vocabulary.
\end{proof}

\begin{theorem}[Bundle scoped obligation package]
\label{thm:bundle-namecert-scoped-obligation-package}
The carrier projection, projection--fibre source scope, finite
$\mathsf{ProbeBundle}$ trivialization scope, transition--ledger descent, and
visible exactness rows together form the scoped
$\NameCert_{\BundleUp}$ obligation package. Its public surface is kernel-facing:
all bundle-specific data are $\mathsf{BHist}$ rows compared by componentwise
$\hsame$, and the only retained external classifier is
$\NameCert_{\ManifoldUp}$ on the base and total manifold rows.
\end{theorem}
\begin{proof}
First assemble the carrier rows using
\autoref{thm:bundle-carrier-projection-obligation}. This supplies the base,
total, projection, fibre-model, trivialization, transition, and source-ledger
rows named by $\mathsf{BundleLocalTrivPkg}(P)$.

Next add the scoped comparisons. The projection and fibre source claim is
\autoref{thm:bundle-projection-fibre-source-scope}; finite trivialization scope
is \autoref{thm:bundle-trivialization-probebundle-scope}; transition and ledger
descent is \autoref{thm:bundle-transition-ledger-scope}.

It remains to identify the public certificate surface. Apply
\autoref{thm:bundle-namecert-exactness-obligation}: the accepted
$\NameCert_{\BundleUp}$ fields are exactly the displayed carrier, classifier,
stability, transition ledger, readback, and absent-bridge rows. Therefore the
scoped rows above repack into the stated kernel-facing obligation package.
\end{proof}
