\chapter{A Concrete Naming Certificate for $\ApophaticKernelBoundaryUp$}
\label{ch:concrete-instances-apophatic-kernel-boundary-namecert}
\origin{ai}

The $\ApophaticKernelBoundaryUp$ packet realizes the proof discipline of \autoref{ch:visions-apophatic-naming-as-discipline} at the kernel boundary. It sits beside the named externality packet of \autoref{ch:concrete-instances-apophaticname-namecert}, the socket ledger of \autoref{ch:concrete-instances-apophaticsocket-namecert}, the audit readback gate of \autoref{ch:concrete-instances-externalitygate-namecert}, and the refusal packet of \autoref{ch:concrete-instances-negativecertificateboundary-namecert}. Those siblings expose names, socket rows, gate readback, or negative certificates; this chapter packages the finite row where a kernel-facing request is refused unless its supply is displayed at type or ledger level.

\begin{definition}[Apophatic kernel boundary carrier]
\label{def:apophatic-kernel-boundary-carrier}
An $\ApophaticKernelBoundaryUp$ carrier is a finite $\BHist$ packet
$$
K=(A,S,Q,R,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the accepted $\ApophaticNameUp$ row naming the external dependency position;
\item $S$ is the accepted $\ApophaticSocketUp$ row recording the requested supply shape and socket ledger;
\item $Q$ is the kernel-boundary question that asks whether the request is exposed at type or ledger level;
\item $R$ is the refusal ledger for any request that would enter as an axiom, hidden setup field, host quotient, selected representative, or unrecorded supply;
\item $G$ is the audit gate row that reads back the question, refusal outcome, and visible route;
\item $H$ records componentwise $\hsame$ transports for the name, socket, question, refusal, gate, route, provenance, and local certificate rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read the name, socket, kernel-boundary question, refusal ledger, and audit gate;
\item $P$ is the $\Pkg$ provenance over $\ApophaticNameUp$, $\ApophaticSocketUp$, $\ExternalityGateUp$, $\NegativeCertificateBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ApophaticKernelBoundaryUp}$ row.
\end{enumerate}
The carrier contains no coordinate for an axiom, hidden setup field, host quotient, selected representative, primitive kernel supply, or unrecorded dependency.
\end{definition}
\leanchecked{BEDC.Derived.ApophaticKernelBoundaryUp.ApophaticKernelBoundaryTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Apophatic kernel boundary NameCert obligations]
\label{thm:apophatic-kernel-boundary-namecert-obligations}
The local $\NameCert_{\ApophaticKernelBoundaryUp}$ surface for \autoref{def:apophatic-kernel-boundary-carrier} consists exactly of carrier admission for $K=(A,S,Q,R,G,H,C,P,N)$, name-to-socket routing from $A$ to $S$, kernel-boundary refusal exactness through $Q$ and $R$, audit-readback stability through $G$, componentwise transport through $H$, displayed route replay through $C$, package provenance through $P$, local naming through $N$, and non-internalization of the refused kernel-facing supply.
\end{theorem}
\begin{proof}
Project the carrier. Its displayed rows are exactly the apophatic name, apophatic socket, kernel-boundary question, refusal ledger, audit gate, transport, route, provenance, and local naming rows.

Use the sibling packets cited above. The $\ApophaticNameUp$ row supplies the named externality, the $\ApophaticSocketUp$ row supplies the socket ledger, the $\ExternalityGateUp$ row supplies visible gate readback, and the $\NegativeCertificateBoundaryUp$ row supplies the refusal discipline for attempted internalizers.

The local NameCert surface is therefore exhausted by the displayed packet. Since the carrier has no coordinate for an axiom, hidden setup field, host quotient, selected representative, primitive kernel supply, or unrecorded dependency, no such object can be produced by the certificate.
\end{proof}

\begin{theorem}[Apophatic kernel boundary noninternalization]
\label{thm:apophatic-kernel-boundary-noninternalization}
Every accepted $\ApophaticKernelBoundaryUp$ packet keeps kernel-facing supply requests outside the generated substrate unless they are displayed as type-level or ledger-level rows. A consumer may cite the name row $A$, socket row $S$, boundary question $Q$, refusal ledger $R$, audit gate $G$, transport row $H$, route row $C$, provenance row $P$, and local naming row $N$, but it cannot extract an axiom, hidden setup field, host quotient, selected representative, primitive kernel supply, or unrecorded dependency from the packet.
\end{theorem}
\begin{proof}
Begin with the carrier inventory of \autoref{def:apophatic-kernel-boundary-carrier}. The packet displays the request, the gate question, the refusal ledger, and the readback route, but it does not display the requested kernel-facing supply as an internal coordinate.

Apply \autoref{thm:apophatic-kernel-boundary-namecert-obligations}. A consumer route must pass through the name-to-socket route, the kernel-boundary question, the refusal ledger, and the audit gate before it can cite the packet.

Thus any route asking for an axiom, hidden setup field, host quotient, selected representative, primitive kernel supply, or unrecorded dependency asks for data absent from the carrier and refused by the ledger.
\end{proof}

\begin{theorem}[Apophatic kernel boundary public route]
\label{thm:apophatic-kernel-boundary-public-route}
Every public consumer of an accepted $\ApophaticKernelBoundaryUp$ packet factors through the displayed route
$$
A \to S \to Q \to R \to G \to (H,C,P,N).
$$
The route first names the externality, then records the socket, then asks the kernel-boundary question, then reads the refusal ledger, then exposes the audit gate, and only then replays transport, continuation, provenance, and local NameCert rows. No public route bypasses $R$ or $G$ to reach an axiom, hidden setup field, host quotient, selected representative, primitive kernel supply, or unrecorded dependency.
\end{theorem}
\begin{proof}
Read the displayed order in \autoref{def:apophatic-kernel-boundary-carrier}. The rows $A,S,Q,R,G$ appear before the transport, continuation, provenance, and local naming rows.

The NameCert obligations of \autoref{thm:apophatic-kernel-boundary-namecert-obligations} bind the name-to-socket route, refusal exactness, and audit-readback stability to that same carrier order. Hence a public citation of the packet must retain the refusal ledger and gate readback.

The noninternalization theorem then excludes every requested supply that is not a displayed row. The public route is therefore exactly the finite route through $A,S,Q,R,G,H,C,P,N$.
\end{proof}

\falsifiablePrediction{Every accepted ApophaticKernelBoundaryUp consumer reaches a refusal-ledger row before it may cite a kernel-boundary request, and no consumer extracts an axiom, hidden setup field, host quotient, or unrecorded supply from the packet.}

\independenceWitness{apophaticname, apophaticsocket, externalitygate, negativecertificateboundary: ApophaticNameUp lacks a kernel-boundary refusal ledger, ApophaticSocketUp lacks the gate-readback row, ExternalityGateUp lacks the primitive-kernel refusal boundary, and NegativeCertificateBoundaryUp lacks the name-to-socket route; no bijection preserves all rows A,S,Q,R,G,H,C,P,N.}

The proposed Lean \texttt{TasteGate.lean} boundary is \texttt{lean4/BEDC/Derived/ApophaticKernelBoundaryUp/TasteGate.lean}. It must provide \texttt{Nontrivial ApophaticKernelBoundaryUp} and \texttt{FieldFaithful ApophaticKernelBoundaryUp} instances for the same displayed carrier.

\closureat{ApophaticKernelBoundaryUp}{seedStr}

\begin{closurestatus}{\ApophaticKernelBoundaryUp}
  \constructivestory{An $\ApophaticKernelBoundaryUp$ packet is generated from an apophatic-name row, an apophatic-socket row, a kernel-boundary question, a refusal ledger, an audit gate, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:apophatic-kernel-boundary-carrier}, \autoref{thm:apophatic-kernel-boundary-namecert-obligations}, \autoref{thm:apophatic-kernel-boundary-noninternalization}, and \autoref{thm:apophatic-kernel-boundary-public-route} bind the finite kernel-boundary refusal carrier, public route, and non-internalization surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not supply a kernel axiom, hidden setup field, host quotient, selected representative, primitive kernel supply, Lean verification, or bridge checking for $\ApophaticKernelBoundaryUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, name-to-socket routing, kernel-boundary refusal exactness, audit-readback stability, non-internalization, nontriviality, and field faithfulness for the same finite packet.}
\end{closurestatus}
