\chapter{A Concrete Naming Certificate for $\InscriptionRouteAuditUp$}
\label{ch:concrete-instances-inscription-route-audit-namecert}
\origin{ai}

The $\InscriptionRouteAuditUp$ packet gives the inscription-event vision of
\autoref{ch:visions-inscription-event-as-concrete-instance} a public route
audit from visible gap to accepted checker row and downstream consumer. It
sits beside the local inscription point of
\autoref{ch:concrete-instances-inscriptionpoint-namecert}, the full audit
trace of \autoref{ch:concrete-instances-inscriptionaudittrace-namecert}, and
the finite witness route of
\autoref{ch:concrete-instances-finitewitnessroute-namecert}. Those siblings
respectively expose the supply socket, the broad inscription trace, and a
finite consumer route; the present packet isolates the route by which a
visible gap becomes a named accepted checker row before a public consumer may
read it.

\begin{definition}[Inscription route-audit carrier]
\label{def:inscription-route-audit-carrier}
An $\InscriptionRouteAuditUp$ carrier is a finite $\BHist$ packet
$$
Q=(S,G,R,A,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the prior source-scope row containing the records visible before the route is accepted;
\item $G$ is the visible gap row whose public residue asks for a route;
\item $R$ is the named route row proposed to connect the visible gap to a reusable checker surface;
\item $A$ is the accepted checker row, recording the finite check by which $R$ is admitted as public record data;
\item $D$ is the downstream consumer row that may read the accepted route only after $A$ is visible;
\item $H$ records componentwise $\hsame$ transports for $S,G,R,A,D$ together with continuation, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ routes by which a consumer reads source scope, visible gap, named route, accepted checker, and downstream consumer rows;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\InscriptionPointUp$, $\InscriptionAuditTraceUp$, $\InscriptionCommitmentSealUp$, $\FiniteWitnessRouteUp$, and $\ProofTermErasureAuditRouteUp$ rows;
\item $N$ is the local $\NameCert_{\InscriptionRouteAuditUp}$ row.
\end{enumerate}
The classifier accepts exactly packets with these nine displayed rows. It has
no coordinate for a private motive, hidden checker, unchecked route, downstream
right outside $D$, host process trace, or consumer path that bypasses the
accepted checker row.
\end{definition}
\leanchecked{BEDC.Derived.InscriptionRouteAuditUp.TasteGate.InscriptionRouteAuditTasteGate\_single\_carrier\_alignment}

\begin{theorem}[InscriptionRouteAudit NameCert obligations]
\label{thm:inscription-route-audit-namecert-obligations}
For the carrier of \autoref{def:inscription-route-audit-carrier}, the local
$\NameCert_{\InscriptionRouteAuditUp}$ surface consists exactly of five finite
obligations:
\begin{enumerate}
\item carrier exposure for $Q=(S,G,R,A,D,H,C,P,N)$;
\item visible-gap locality: every route read begins at the prior source scope $S$ and the displayed gap row $G$;
\item accepted-route exactness: the named route $R$ becomes public only through the accepted checker row $A$;
\item downstream consumer accountability: every public consumer row $D$ factors through $A$ before the consumer read is visible;
\item provenance and local naming exhaustion through $H,C,P,N$, with no private motive, hidden checker, unchecked route, or off-packet consumer right.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is projection from the displayed packet. The rows
$S,G,R,A,D,H,C,P,N$ are the full inventory available to an audit reader.

The gap-facing route begins with $S$ and $G$. These rows identify the prior
records and the public gap residue; without them the named route has no
visible socket to answer.

The checker-facing route then reads $R$ through $A$. The accepted checker row
is the only place where the proposed route is admitted as public record data,
so no hidden checker or unchecked replay can replace it.

Finally, $D,H,C,P,N$ bind downstream consumption, transport, continuation,
provenance, and local naming to the same finite packet. Since the carrier has
no private motive, host trace, or off-packet consumer coordinate, the five
obligations exhaust the local certificate surface.
\end{proof}

\falsifiablePrediction{If the route-audit carrier is atomic, every public downstream use must factor through the accepted checker row before the consumer row is visible.}

\begin{theorem}[InscriptionRouteAudit falsifiable prediction]
\label{thm:inscription-route-audit-falsifiable-prediction}
Every public downstream read of an accepted $\InscriptionRouteAuditUp$ carrier
$Q=(S,G,R,A,D,H,C,P,N)$ factors through the accepted checker row $A$ before the
consumer row $D$ is visible. A purported public use that reaches $D$ while
bypassing $A$ is outside the carrier.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:inscription-route-audit-carrier}. The only
consumer-facing row is $D$, and the definition places it after the named route
and accepted checker rows $R,A$.

Apply the accepted-route exactness and downstream consumer accountability
clauses of \autoref{thm:inscription-route-audit-namecert-obligations}. They
make $A$ the public admission point for $R$ and require every downstream read
through $D$ to factor through that checker row.

The transport, continuation, provenance, and local naming rows preserve this
same route. Hence a consumer path that reaches $D$ without first exposing $A$
would require an additional carrier coordinate, which the packet does not
contain.
\end{proof}

\independenceWitness{inscriptionaudittrace, inscriptioncommitmentseal, inscriptionpoint, finitewitnessroute, prooftermerasureauditroute: the route-audit carrier has both accepted-checker and downstream-gap rows, while these siblings respectively lack the full route from visible gap to public consumer; hence no carrier bijection preserves all NameCert rows.}

\begin{theorem}[InscriptionRouteAudit independence witness]
\label{thm:inscription-route-audit-independence-witness}
The $\InscriptionRouteAuditUp$ carrier is not bijective, under NameCert-row
preservation, with $\InscriptionAuditTraceUp$, $\InscriptionCommitmentSealUp$,
$\InscriptionPointUp$, $\FiniteWitnessRouteUp$, or
$\ProofTermErasureAuditRouteUp$. It uniquely binds the visible gap row $G$,
the named route row $R$, the accepted checker row $A$, and the public consumer
row $D$ as one route-audit packet.
\end{theorem}
\begin{proof}
Compare the displayed coordinates. The present carrier has the paired
gap-to-checker and checker-to-consumer route
$$
G \to R \to A \to D.
$$

The inscription audit trace supplies a broader trace packet, while the
commitment seal isolates a commitment row rather than the visible
gap-to-checker route. The inscription point supplies the local socket and
actuality rows, not the public consumer route from $G$ through $A$.

The finite witness route supplies a Real-and-Completion consumer path, and the
proof-term erasure audit route supplies erasure-facing audit rows. Neither
contains this chapter's simultaneous visible gap, named route, accepted
checker, and downstream public consumer rows. Thus no carrier bijection can
preserve all local NameCert obligations.
\end{proof}

The Lean target family $BEDC.Derived.InscriptionRouteAuditUp$ should provide a
$\mathsf{Nontrivial}$ instance by exhibiting two distinct finite packets with
different accepted checker rows, and a $\mathsf{FieldFaithful}$ instance whose
projections recover $S,G,R,A,D,H,C,P,N$ from the carrier.

\closureat{InscriptionRouteAuditUp}{seedStr}

\begin{closurestatus}{\InscriptionRouteAuditUp}
  \constructivestory{An $\InscriptionRouteAuditUp$ packet is generated from prior source scope, a visible gap, a named route, an accepted checker row, a downstream consumer row, componentwise hsame transports, displayed Cont routes, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:inscription-route-audit-carrier}, \autoref{thm:inscription-route-audit-namecert-obligations}, \autoref{thm:inscription-route-audit-falsifiable-prediction}, and \autoref{thm:inscription-route-audit-independence-witness} bind the visible gap-to-accepted-route audit packet and its downstream consumer boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, private agency, host process traces, unchecked routes, downstream rights outside the displayed consumer row, or a completed ontology of inscription events.}
  \upgradepath{Obligation closure requires Lean encoding of the carrier, explicit nontrivial witnesses, field-faithful projections, accepted-checker factorization, consumer non-escape, and independence from the named sibling packets.}
\end{closurestatus}
