\chapter{A Concrete Naming Certificate for $\FiniteObservationInterfaceUp$}
\label{ch:concrete-instances-finite-observation-interface-namecert}
\origin{ai}

The $\FiniteObservationInterfaceUp$ packet realizes the Real and Completion target of \autoref{ch:visions-real-completeness} as a finite read surface. It consumes the StreamName observation boundary of \autoref{ch:concrete-instances-streamname-namecert}, the RegSeqRat regularity surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the DyadicRatCore tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the RealUp handoff surface of \autoref{ch:concrete-instances-real-namecert}. It is narrower than a completion theorem: the packet exposes a selected finite observation window, records the omitted tail as a ledger, and then routes every real-facing read through the displayed sibling rows.

\begin{definition}[Finite observation interface carrier]
\label{def:finite-observation-interface-carrier}
A $\FiniteObservationInterfaceUp$ carrier is a finite $\BHist$ packet
$$
O=(S,R,D,T,E,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ observation row whose finite read entries are visible before any real-facing handoff;
\item $R$ is the $\RegSeqRatUp$ regularity row that reads the same observation entries as regular rational data;
\item $D$ is the $\DyadicRatCoreUp$ tolerance row accounting for every displayed precision request and dyadic error bound used by the read;
\item $T$ is the selected finite-window row, listing the exact bounded observation window exposed to the consumer;
\item $E$ is the omitted-tail ledger, recording precisely which StreamName and RegSeqRat entries lie outside $T$ and are not exported as selected rows;
\item $H$ stores componentwise $\hsame$ transports for the observation row, regularity row, tolerance row, selected window, omitted-tail ledger, provenance, and local naming row;
\item $C$ stores the displayed $\Cont$ replay routes that read $S$, then $R$, then $D$, expose $T$, record $E$, and only then hand off to the RealUp row consumed by the downstream route;
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, selected finite-window rows, omitted-tail ledgers, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\FiniteObservationInterfaceUp}$ row naming exactly this finite observation interface packet.
\end{enumerate}
The carrier has no coordinate for a full Real completeness proof, quotient stream equality, host real equality, selected limit, or export of the omitted tail as a selected stream row.
\end{definition}
\leanchecked{BEDC.Derived.FiniteObservationInterfaceUp.FiniteObservationInterfaceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Finite observation interface NameCert obligations]
\label{thm:finite-observation-interface-namecert-obligations}
For every accepted $\FiniteObservationInterfaceUp$ carrier $O=(S,R,D,T,E,H,C,P,N)$, the local $\NameCert_{\FiniteObservationInterfaceUp}$ surface consists of five obligations:
\begin{enumerate}
\item carrier admission: the accepted packet displays exactly the rows $S,R,D,T,E,H,C,P,N$ of \autoref{def:finite-observation-interface-carrier};
\item selected-window exposure: the finite window $T$ is exposed before any RealUp handoff is made available to a consumer;
\item omitted-tail ledger exactness: the ledger $E$ records the entries outside $T$ and cannot be read as a selected stream row;
\item dyadic tolerance accountability: every precision request used by the read is accounted for by the dyadic row $D$ before the route reaches the RealUp surface;
\item StreamName/RegSeqRat/Real handoff non-escape: every handoff to RealUp factors through $S$, $R$, $D$, $T$, $E$, $H$, $C$, $P$, and $N$, and no quotient stream equality, host real equality, full Real completeness, or selected limit is exported.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationInterfaceUp.FiniteObservationInterfaceNameCert\_obligation\_surface}
\begin{proof}
Carrier admission is projection from \autoref{def:finite-observation-interface-carrier}. The StreamName observation row, RegSeqRat regularity row, DyadicRatCore tolerance row, selected window, omitted-tail ledger, transport, continuation, provenance, and naming coordinates are all displayed in the same finite packet.

The selected-window and omitted-tail obligations are separated by the two rows $T$ and $E$. A consumer may inspect the selected finite window $T$; it may also inspect the ledger $E$ as the exact record of entries outside that window. The ledger row is not a second selected stream row, because the carrier gives it only the omitted-tail role.

Dyadic accountability is read through $D$ before the Real-facing route is exposed. The replay rows $H,C,P,N$ keep the StreamName, RegSeqRat, dyadic, selected-window, and tail-ledger reads in one local NameCert packet, so the Real handoff has no coordinate from which to obtain completeness, quotient equality, host equality, or a selected limit.
\end{proof}

\begin{theorem}[Finite observation interface selected-stream handoff]
\label{thm:finite-observation-interface-selected-stream-handoff}
Every Real-facing finite observation read of an accepted $\FiniteObservationInterfaceUp$ packet routes through the displayed StreamName row $S$, RegSeqRat row $R$, DyadicRatCore row $D$, selected finite-window row $T$, omitted-tail ledger $E$, transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$. The route cannot assert full Real completeness, quotient stream equality, host real equality, or the existence of a selected limit.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationInterfaceUp.FiniteObservationInterfaceSelectedStream\_handoff}
\begin{proof}
Start with a Real-facing consumer read. By the NameCert obligations, the read reaches the RealUp side only after the StreamName observation row $S$, the RegSeqRat regularity row $R$, and the DyadicRatCore tolerance row $D$ have been displayed.

The selected stream information is then exactly the finite window $T$. The omitted-tail ledger $E$ is read as a boundary record for what the packet withholds from the selected window; it is not exported through the same classifier role as $T$.

Finally replay the route through $H,C,P,N$. These rows transport and package the displayed finite packet, and they do not add a coordinate for ambient Real completeness, quotient stream equality, host real equality, or limit selection. Thus every Real-facing finite observation read remains inside the displayed interface route.
\end{proof}

\begin{theorem}[Finite observation interface scoped closure]
\label{thm:finite-observation-interface-scoped-closure}
Every accepted $\FiniteObservationInterfaceUp$ read is scoped exactly by the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of \autoref{def:finite-observation-interface-carrier}, together with the sibling $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ surfaces. Selected-window exposure, omitted-tail exactness, dyadic accountability, and Real-facing non-escape are all read through the same finite packet
$$
O=(S,R,D,T,E,H,C,P,N).
$$
No coordinate of the scoped read supplies full Real completeness, quotient stream equality, host real equality, or a selected-limit coordinate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-observation-interface-carrier}. This gives the finite packet $O=(S,R,D,T,E,H,C,P,N)$ and fixes the displayed $\BHist$, transport, continuation, package, and naming rows as the only rows available to the interface read.

Apply \autoref{thm:finite-observation-interface-namecert-obligations}. Carrier admission binds the packet to those displayed rows, selected-window exposure is read through $T$, omitted-tail exactness is read through $E$, dyadic accountability is read through $D$, and the StreamName/RegSeqRat/Real handoff condition forces every Real-facing route through the same local packet.

Apply \autoref{thm:finite-observation-interface-selected-stream-handoff}. The sibling $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ surfaces are therefore used only along the displayed finite route. Since the carrier has no coordinate for full Real completeness, quotient stream equality, host real equality, or a selected limit, none of those claims can escape the scoped packet.
\end{proof}

\begin{theorem}[Finite observation interface public certificate route]
\label{thm:finite-observation-interface-public-certificate-route}
Every accepted $\FiniteObservationInterfaceUp$ packet
$$
O=(S,R,D,T,E,H,C,P,N)
$$
exports a public reusable certificate only through the displayed StreamName row $S$, RegSeqRat row $R$, DyadicRatCore row $D$, selected finite-window row $T$, omitted-tail ledger $E$, transport row $H$, replay row $C$, provenance row $P$, and local $\NameCert$ row $N$. The public route does not export Real completeness, a selected limit, quotient stream equality, host real equality, or an omitted-tail-as-selected-stream row.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:finite-observation-interface-carrier}. The accepted packet has exactly the rows $S,R,D,T,E,H,C,P,N$, and the carrier explicitly withholds Real completeness, quotient stream equality, host real equality, selected limits, and any selected-stream role for the omitted tail.

Apply \autoref{thm:finite-observation-interface-namecert-obligations}. The local NameCert obligations force carrier admission, selected-window exposure, omitted-tail exactness, dyadic tolerance accountability, and StreamName/RegSeqRat/Real handoff non-escape to be read from those rows.

Apply \autoref{thm:finite-observation-interface-selected-stream-handoff} and \autoref{thm:finite-observation-interface-scoped-closure}. The reusable surface is therefore public only as the displayed finite certificate route, and no hidden Real-facing coordinate is available outside that route.
\end{proof}

\begin{theorem}[Finite observation interface consumer reuse]
\label{thm:finite-observation-interface-consumer-reuse}
Any downstream L10 consumer that reuses an accepted $\FiniteObservationInterfaceUp$ packet must reuse the public certificate route of \autoref{thm:finite-observation-interface-public-certificate-route}. Such a consumer may read the StreamName, RegSeqRat, DyadicRatCore, selected-window, omitted-tail, transport, replay, provenance, and NameCert rows, but it cannot bypass those rows to obtain an independent RealUp handoff.
\end{theorem}
\begin{proof}
Begin with a downstream L10 consumer of the accepted packet. By \autoref{thm:finite-observation-interface-public-certificate-route}, the only reusable certificate exported by the packet is the displayed route through $S,R,D,T,E,H,C,P,N$.

The route itself is constrained by \autoref{thm:finite-observation-interface-namecert-obligations}. In particular, the selected window is exposed before any RealUp handoff, the omitted tail remains a ledger rather than a selected stream, and dyadic accountability is supplied before the Real-facing read.

Use \autoref{thm:finite-observation-interface-selected-stream-handoff} together with \autoref{thm:finite-observation-interface-scoped-closure}. Every Real-facing read is already scoped by the finite packet and its sibling surfaces, so a downstream consumer has no bypass row from which to form an independent handoff.
\end{proof}

\begin{theorem}[Finite observation interface L10 no-escape public boundary]
\label{thm:finite-observation-interface-l10-noescape-public-boundary}
The public $\FiniteObservationInterfaceUp$ route for an accepted packet $O=(S,R,D,T,E,H,C,P,N)$ is an L10 boundary: it exports the displayed finite certificate rows and nothing beyond them. In particular, no downstream L10 reuse of the route exports Real completeness, a selected limit, quotient stream equality, host real equality, or an omitted-tail-as-selected-stream row.
\end{theorem}
\begin{proof}
The carrier description in \autoref{def:finite-observation-interface-carrier} fixes the packet inventory. It names the selected finite window $T$ and the omitted-tail ledger $E$ as distinct rows, and it gives no coordinate for completeness, quotient equality, host equality, or limit selection.

Apply \autoref{thm:finite-observation-interface-namecert-obligations} to bind those rows to the local NameCert surface. The non-escape obligation says that every handoff to RealUp factors through $S,R,D,T,E,H,C,P,N$ and through no extra Real-facing row.

Finally combine \autoref{thm:finite-observation-interface-selected-stream-handoff}, \autoref{thm:finite-observation-interface-scoped-closure}, and \autoref{thm:finite-observation-interface-public-certificate-route}. The public route is reusable by L10 consumers, but its reuse is still the same finite boundary, so the listed non-export claims remain unavailable.
\end{proof}

\begin{theorem}[Finite observation interface L10 bridge]
\label{thm:finite-observation-interface-l10-bridge}
For every accepted packet $O=(S,R,D,T,E,H,C,P,N)$, the public certificate route of \autoref{thm:finite-observation-interface-public-certificate-route} is exactly the L10 bridge surface consumed by $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ readers. Every bridge read factors through $S,R,D,T,E,H,C,P,N$, and no bridge read exports Real completeness, selected limits, quotient stream equality, host real equality, or omitted-tail-as-selected-stream data.
\end{theorem}
\begin{proof}
Start from the public reusable certificate route. By \autoref{thm:finite-observation-interface-public-certificate-route}, the exported surface is the displayed finite route through $S,R,D,T,E,H,C,P,N$, with no additional Real-facing coordinate.

The selected-stream handoff of \autoref{thm:finite-observation-interface-selected-stream-handoff} identifies the only route by which a Real-facing finite observation read can reach the sibling $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ surfaces. The scoped closure theorem \autoref{thm:finite-observation-interface-scoped-closure} keeps that route inside the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Now apply consumer reuse from \autoref{thm:finite-observation-interface-consumer-reuse}. Any L10 reader using the packet must reuse the public certificate route, so its bridge read has no bypass around $S,R,D,T,E,H,C,P,N$.

Finally use the L10 no-escape boundary of \autoref{thm:finite-observation-interface-l10-noescape-public-boundary}. Since the public route exports only the displayed finite certificate rows, the bridge surface consumed by the four downstream readers cannot export Real completeness, selected limits, quotient stream equality, host real equality, or omitted-tail-as-selected-stream data.
\end{proof}

\falsifiablePrediction{Every accepted FiniteObservationInterfaceUp packet exposes a selected finite observation window before any RealUp handoff and cannot export an omitted tail as a selected stream row.}

\independenceWitness{streamname, regseqrat, dyadicratcore, real, finitewindowenvelope: the interface packet combines selected-window, omitted-tail, dyadic tolerance, regularity, and Real handoff rows; each sibling lacks at least one of these carrier rows, so no bijection preserves the full field inventory.}

The Lean file \texttt{Derived/FiniteObservationInterfaceUp/TasteGate.lean} must provide $\mathsf{Nontrivial}\ \FiniteObservationInterfaceUp$ and $\mathsf{FieldFaithful}\ \FiniteObservationInterfaceUp$ instances for the displayed coordinates $S,R,D,T,E,H,C,P,N$.

\closureat{FiniteObservationInterfaceUp}{scopedStr}
\closureat{FiniteObservationInterfaceUp}{publicStr}
\closureat{FiniteObservationInterfaceUp}{bridgedStr}
\closureat{FiniteObservationInterfaceUp}{matureStr}

\begin{closurestatus}{\FiniteObservationInterfaceUp}
  \constructivestory{A $\FiniteObservationInterfaceUp$ packet is generated from a StreamName observation row, RegSeqRat regularity row, DyadicRatCore tolerance row, selected finite-window row, omitted-tail ledger, componentwise $\hsame$ transports, displayed $\Cont$ replay, package provenance, and a local $\NameCert$ row.}
  \leanchecked{BEDC.Derived.FiniteObservationInterfaceUp.taste\_gate}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:finite-observation-interface-carrier}, \autoref{thm:finite-observation-interface-namecert-obligations}, \autoref{thm:finite-observation-interface-selected-stream-handoff}, \autoref{thm:finite-observation-interface-scoped-closure}, \autoref{thm:finite-observation-interface-public-certificate-route}, and \autoref{thm:finite-observation-interface-l10-bridge} bind the finite observation carrier, local NameCert obligation surface, selected-window route, omitted-tail boundary, dyadic accountability, Real-facing non-escape scope, reusable public certificate route, and L10 bridge surface.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.FiniteObservationInterfaceUp.taste\_gate}
  \bridgestatus{paperBridge}
  \origin{ai}
  \notclaimed{This chapter does not close Real completeness, selected-limit existence, quotient stream equality, host real equality, Lean verification, or bridge checking.}
  \upgradepath{No further theory-axis closure is claimed here; remaining verification-axis work is auditCleanV or bridgeCheckedV for the displayed finite observation interface.}
\end{closurestatus}
