\chapter{A Concrete Naming Certificate for $\UniformSpaceUp$}
\label{ch:concrete-instances-uniformspace-namecert}

The $\UniformSpaceUp$ surface names the finite entourage interface between
$\MetricUp$, $\TopologyUp$, $\FilterUp$, $\CauchyFilterUp$, and
$\CompletionUp$. Bourbaki--Kelley uniform-space practice treats entourages as
the common language behind topology, filters, Cauchy data, and completion; the
BEDC certificate keeps only finite $\mathsf{BHist}$ rows, visible classifier
transport, and explicit refinement ledgers.

\begin{definition}[UniformSpaceUp BHist entourage carrier]
\label{def:uniformspace-bhist-carrier}
A $\UniformSpaceUp$ carrier is a finite packet
$$
U=(X,E,D,R,S,C,P,N)
$$
where $X$ is the carried point-history source, $E$ is a finite list of
entourage rows over $X\times X$, $D$ records the diagonal row for each listed
entourage, $R$ records finite refinement witnesses, $S$ records symmetry
readback, $C$ records composition readback, $P$ is the $\mathsf{Pkg}$
provenance ledger, and $N$ is the local $\NameCert_{\UniformSpaceUp}$ row.
The point classifier is inherited from the $X$ row and is stable under
$\hsame$ transport on both coordinates of every entourage row.
\end{definition}

\begin{theorem}[UniformSpaceUp finite filterbase diagonal obligation]
\label{thm:uniformspace-filterbase-diagonal-obligation}
Every accepted $\UniformSpaceUp$ carrier exposes a finite filterbase of
entourage rows. For each displayed entourage $V\in E$, the diagonal row
records that every accepted point history $x$ has $(x,x)$ in $V$, and the
finite filterbase ledger records a displayed refinement row for every pair of
entourages named by downstream $\FilterUp$ or $\CauchyFilterUp$ consumers.
\end{theorem}
\leanchecked{BEDC.Derived.UniformSpaceUp.UniformSpacePacket\_filterbase\_diagonal\_obligation}
\begin{proof}
Unpack the carrier of \autoref{def:uniformspace-bhist-carrier}. The diagonal
component $D$ is indexed by the same finite entourage list $E$, so each
consumer-visible entourage carries its own diagonal witness.

For a pair of displayed entourages, the refinement component $R$ supplies a
third displayed entourage and the two inclusion reads needed by a filterbase
consumer. Repacking those rows gives the finite filterbase obligation without
forming an external filter object.
\end{proof}

\begin{theorem}[UniformSpaceUp diagonal refinement obligation]
\label{thm:uniformspace-diagonal-refinement-obligation}
If a $\UniformSpaceUp$ consumer requests a diagonal neighbourhood from a
$\MetricUp$ ball row or a $\TopologyUp$ neighbourhood row, the carrier factors
the request through one of its finite entourage rows and a displayed
refinement ledger. The request sees only the point source, the chosen
entourage, its diagonal row, $\hsame$ transport on endpoints, and the
$\mathsf{Pkg}$ provenance row.
\end{theorem}
\leanchecked{BEDC.Derived.UniformSpaceUp.UniformSpaceEntouragePacket\_diagonal\_refinement\_obligation}
\begin{proof}
Read the request as a finite row over the same point-history source $X$. The
$\MetricUp$ and $\TopologyUp$ anchors supply only neighbourhood data, not a
host uniformity.

The carrier supplies a named entourage row whose diagonal witness covers the
requested point and whose refinement ledger records the inclusion into the
requested neighbourhood. Endpoint changes are transported by the inherited
$\hsame$ classifier, and the visible provenance remains the single package
row $P$.
\end{proof}

\begin{theorem}[UniformSpaceUp symmetry and composition obligation]
\label{thm:uniformspace-symmetry-composition-obligation}
For every displayed entourage $V$ in an accepted $\UniformSpaceUp$ carrier,
the symmetry row $S$ gives a displayed entourage $V^{\mathrm{op}}$ with the
endpoints exchanged. For every displayed entourage $V$, the composition row
$C$ gives a displayed refinement $W$ such that two successive $W$-steps read
as one $V$-step. Both rows are finite $\mathsf{BHist}$ ledgers stable under
the inherited point classifier.
\end{theorem}
\begin{proof}
The symmetry component is a row-by-row endpoint exchange in the finite
entourage list. Applying $\hsame$ on the first and second coordinates carries
the exchanged row to classified representatives.

The composition component names a finite witness $W$ and a ledger read from
$W\circ W$ into $V$. Because both $W$-steps and the target $V$-step are rows of
the same carrier, the composition readback is stable under the same endpoint
transport and package provenance.
\end{proof}

\begin{theorem}[UniformSpaceUp Cauchy and completion handoff]
\label{thm:uniformspace-cauchy-completion-handoff}
Every $\CauchyFilterUp$ or $\CompletionUp$ consumer of a
$\UniformSpaceUp$ packet factors through the finite entourage filterbase,
diagonal rows, refinement rows, symmetry rows, composition rows, $\hsame$
endpoint transport, and $\mathsf{Pkg}$ provenance of
\autoref{def:uniformspace-bhist-carrier}. The handoff introduces no
choice-selected completion point, quotient stream equality, open-cover
compactness, or host-space uniformity.
\end{theorem}
\begin{proof}
Project the accepted packet to its finite filterbase rows. A Cauchy consumer
reads finite entourage obligations exactly as in the $\CauchyFilterUp$ surface:
each demanded precision row is matched by a displayed entourage and a
refinement witness.

A completion consumer may retain the same finite Cauchy ledger and provenance
rows, but there is no coordinate in the carrier for a selected limit point or
a quotient class of streams. Therefore the handoff is only the visible
entourage data listed in the theorem.
\end{proof}

\begin{theorem}[UniformSpaceUp classifier transport obligation]
\label{thm:uniformspace-classifier-transport-obligation}
Let $U=(X,E,D,R,S,C,P,N)$ be an accepted $\UniformSpaceUp$ carrier as in
\autoref{def:uniformspace-bhist-carrier}. Endpoint $\hsame$ transport of the
point source $X$ and of every displayed entourage row repacks another accepted
$\UniformSpaceUp$ carrier with the same finite entourage list, diagonal
ledger, refinement ledger, symmetry ledger, composition ledger,
$\mathsf{Pkg}$ provenance, and $\NameCert_{\UniformSpaceUp}$ row.
\end{theorem}
\leanchecked{BEDC.Derived.UniformSpaceUp.UniformSpacePacket\_classifier\_transport\_obligation}
\begin{proof}
Unpack the carrier definition. The point classifier is the one inherited from
the $X$ row, and every entourage row is explicitly declared stable under
$\hsame$ on both coordinates.

Transport the endpoint histories first, then apply the same transport to the
diagonal, refinement, symmetry, and composition rows. The carrier has no
coordinate outside these finite ledgers, so the transported rows repack with
the unchanged package provenance and naming certificate.
\end{proof}

\begin{theorem}[UniformSpaceUp entourage ledger exactness]
\label{thm:uniformspace-entourage-ledger-exactness}
Every consumer-visible entourage read from an accepted $\UniformSpaceUp$
carrier is exhausted by the finite list $E$, the diagonal row $D$, the
refinement row $R$, the symmetry row $S$, the composition row $C$, and the
$\mathsf{Pkg}$ provenance row. No consumer can read an additional host
uniformity, open-cover compactness principle, quotient stream equality, or
choice-selected completion datum from the carrier.
\end{theorem}
\begin{proof}
Project the accepted packet to the coordinates of
\autoref{def:uniformspace-bhist-carrier}. The only entourage-bearing
coordinate is the finite list $E$, and the only certified reads from this list
are the rows named by $D$, $R$, $S$, and $C$.

Apply the diagonal obligation of
\autoref{thm:uniformspace-filterbase-diagonal-obligation}, the neighbourhood
refinement obligation of
\autoref{thm:uniformspace-diagonal-refinement-obligation}, and the symmetry
and composition obligation of
\autoref{thm:uniformspace-symmetry-composition-obligation}. These rows account
for every displayed consumer read while the package row $P$ accounts for
provenance.
\end{proof}

\begin{theorem}[UniformSpaceUp common refinement Cauchy handoff]
\label{thm:uniformspace-common-refinement-cauchy-handoff}
Any $\CauchyFilterUp$ or $\CompletionUp$ request through two compatible
entourage demands of an accepted $\UniformSpaceUp$ carrier factors through a
displayed common refinement row. The exported handoff contains only the point
source, the two demanded entourage rows, the common refinement witness,
endpoint $\hsame$ transport, the relevant $\Cont$ observation windows, and
$\mathsf{Pkg}$ provenance; it exports no choice-selected limit, quotient
stream, open-cover compactness, or host uniformity.
\end{theorem}
\begin{proof}
Start with the two compatible demands as finite reads from the entourage list
$E$. The filterbase diagonal obligation provides the common refinement row
from $R$ and the inclusions back into the two demanded rows.

Transport endpoint representatives by
\autoref{thm:uniformspace-classifier-transport-obligation}. The refinement,
diagonal, symmetry, and composition rows remain rows of the same finite
carrier after this transport.

Finally apply the handoff theorem
\autoref{thm:uniformspace-cauchy-completion-handoff}. A Cauchy or completion
consumer receives the finite refinement ledger and provenance, but the carrier
contains no coordinate for a selected limit, quotient stream, open-cover
compactness datum, or ambient host uniformity.
\end{proof}

\begin{theorem}[UniformSpaceUp common refinement functoriality]
\label{thm:uniformspace-cauchy-completion-common-refinement-functoriality}
Let $U_0$, $U_1$, and $U_2$ be accepted $\UniformSpaceUp$ packets. Suppose the
displayed finite entourage ledger contains a compatible common-refinement row
from $U_0$ to $U_1$ and a compatible common-refinement row from $U_1$ to $U_2$.
Then every $\CauchyFilterUp$ or $\CompletionUp$ request routed through $U_2$
also routes through $U_0$ by the composed finite entourage ledger.

The composed handoff contains only the point-history source, the two displayed
common-refinement rows, diagonal witnesses, endpoint $\hsame$ transport,
the relevant $\Cont$ observation windows, $\mathsf{Pkg}$ provenance, and local
$\NameCert_{\UniformSpaceUp}$ rows. It introduces no quotient equality of
Cauchy streams, no selected completion point, no choice-based completion data,
and no ambient host uniformity.
\end{theorem}
\begin{proof}
First compose the two displayed common-refinement rows. The filterbase
diagonal, neighbourhood refinement, symmetry, and composition obligations keep
the composite as a finite entourage ledger row of the same BEDC form.

Next apply \autoref{thm:uniformspace-classifier-transport-obligation} to each
handoff. Endpoint representatives move along the displayed $\hsame$ rows, and
the $\Cont$ observation windows remain rows of the accepted packets.

Now invoke
\autoref{thm:uniformspace-common-refinement-cauchy-handoff} for the route from
$U_2$ to $U_1$, and invoke it again for the route from $U_1$ to $U_0$. The first
application supplies the finite ledger consumed by the second, so the
$\CauchyFilterUp$ or $\CompletionUp$ request is read at $U_0$ through the
composed common refinement.

Finally repack the resulting ledger with the same $\mathsf{BHist}$, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance. Since the construction
only concatenates displayed finite rows, it never forms a quotient of Cauchy
streams and never selects a completion point.
\end{proof}

\begin{theorem}[UniformSpaceUp scoped entourage package]
\label{thm:uniformspace-scoped-entourage-package}
The carrier of \autoref{def:uniformspace-bhist-carrier}, together with
\autoref{thm:uniformspace-filterbase-diagonal-obligation},
\autoref{thm:uniformspace-diagonal-refinement-obligation},
\autoref{thm:uniformspace-symmetry-composition-obligation},
\autoref{thm:uniformspace-cauchy-completion-handoff},
\autoref{thm:uniformspace-classifier-transport-obligation},
\autoref{thm:uniformspace-entourage-ledger-exactness}, and
\autoref{thm:uniformspace-common-refinement-cauchy-handoff}, and
\autoref{thm:uniformspace-cauchy-completion-common-refinement-functoriality},
forms one scoped BEDC packet over $\mathsf{BHist}$, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$.

Every $\CauchyFilterUp$ and $\CompletionUp$ consumer of this packet receives
only finite entourage rows, displayed endpoint transports, continuation
routes, package provenance, and the local naming row.
\end{theorem}
\begin{proof}
Unpack the carrier of \autoref{def:uniformspace-bhist-carrier}. Its displayed
coordinates are the point-history source, the finite entourage list, the
diagonal row, the refinement row, the symmetry row, the composition row,
transport and continuation data, package provenance, and local naming evidence.

The diagonal and filterbase projections are exactly
\autoref{thm:uniformspace-filterbase-diagonal-obligation} and
\autoref{thm:uniformspace-diagonal-refinement-obligation}. The symmetry and
composition projections are supplied by
\autoref{thm:uniformspace-symmetry-composition-obligation}.

Classifier transport is supplied by
\autoref{thm:uniformspace-classifier-transport-obligation}, and carrier
exhaustion is supplied by
\autoref{thm:uniformspace-entourage-ledger-exactness}. These projections keep
all consumer reads on the same $\mathsf{BHist}$, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$ surface.

Finally apply \autoref{thm:uniformspace-cauchy-completion-handoff} and
\autoref{thm:uniformspace-common-refinement-cauchy-handoff}. The
$\CauchyFilterUp$ and $\CompletionUp$ consumers receive the finite entourage
rows and their common refinement data, with no selected completion point,
quotient stream, open-cover compactness datum, or ambient host uniformity.
\end{proof}

\begin{theorem}[UniformSpaceUp entourage public export]
\label{thm:uniformspace-entourage-public-export}
The finite filterbase diagonal row, diagonal refinement row, symmetry and
composition rows, classifier transport row, entourage ledger, and
common-refinement Cauchy handoff rows of the scoped $\UniformSpaceUp$ packet
assemble into the public downstream packet for $\CauchyFilterUp$ and
$\CompletionUp$ consumers.

The public packet exports only finite entourage data over $\mathsf{BHist}$,
displayed $\hsame$ endpoint transport, $\Cont$ observation routes,
$\mathsf{Pkg}$ provenance, and local $\NameCert$ evidence.
\end{theorem}
\begin{proof}
Start with the scoped package of
\autoref{thm:uniformspace-scoped-entourage-package}. It binds the carrier of
\autoref{def:uniformspace-bhist-carrier} to the finite entourage rows,
transport rows, continuation routes, package provenance, and local naming
evidence.

The finite filterbase and diagonal parts are supplied by
\autoref{thm:uniformspace-filterbase-diagonal-obligation} and
\autoref{thm:uniformspace-diagonal-refinement-obligation}. Symmetry and
composition are supplied by
\autoref{thm:uniformspace-symmetry-composition-obligation}.

Classifier transport and ledger exhaustion are supplied by
\autoref{thm:uniformspace-classifier-transport-obligation} and
\autoref{thm:uniformspace-entourage-ledger-exactness}. These rows ensure
that public consumers read the same finite entourage surface after endpoint
transport.

Finally use \autoref{thm:uniformspace-cauchy-completion-handoff} and
\autoref{thm:uniformspace-common-refinement-cauchy-handoff}. They identify
the downstream $\CauchyFilterUp$ and $\CompletionUp$ requests with the common
finite-refinement packet, leaving selected limits, quotient streams,
open-cover compactness data, and host uniformities outside the export.
\end{proof}

\begin{theorem}[UniformSpace finite-entourage standard bridge]
\label{thm:uniformspace-standard-bridge}
The finite filterbase diagonal row, diagonal refinement row, symmetry and
composition rows, classifier transport row, entourage ledger,
common-refinement Cauchy handoff rows, displayed $\mathsf{BHist}$, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows assemble the standard
finite-entourage bridge for $\UniformSpaceUp$.

The bridge exposes exactly the public finite-entourage packet of
\autoref{thm:uniformspace-entourage-public-export}. It does not add
choice-based completion, quotient equality of Cauchy streams, open-cover
compactness, host uniformity, or selected limits.
\end{theorem}
\begin{proof}
Begin with the scoped finite-entourage package of
\autoref{thm:uniformspace-scoped-entourage-package}. Its carrier is the
displayed $\mathsf{BHist}$ of \autoref{def:uniformspace-bhist-carrier},
equipped with the finite diagonal, refinement, symmetry, composition,
classifier, ledger, handoff, continuation, package, and naming rows.

Apply \autoref{thm:uniformspace-entourage-public-export}. The public export
repackages the same rows for $\CauchyFilterUp$ and $\CompletionUp$ consumers,
so the standard bridge has a fixed source packet and a fixed public target
packet over the same $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
coordinates.

The Cauchy side is supplied by
\autoref{thm:uniformspace-cauchy-completion-handoff} and
\autoref{thm:uniformspace-common-refinement-cauchy-handoff}. These theorems
carry common finite-refinement data across the downstream Cauchy requests
without choosing a completion point or identifying streams by quotient
equality.

It remains only to record the boundary of the bridge. Since the cited package,
public export, and Cauchy handoff theorems contain no rows for choice-based
completion, open-cover compactness, host uniformity, or selected limits, the
assembled bridge is exactly the finite-entourage standard bridge stated here.
\end{proof}

\begin{theorem}[UniformSpace finite Cauchy and completion consumer examples]
\label{thm:uniformspace-finite-cauchy-completion-consumer-examples}
The finite-entourage bridge for $\UniformSpaceUp$ yields two concrete
downstream consumer examples.

First, a $\CauchyFilterUp$ request reads the common refinement row of the
finite entourage packet as its finite Cauchy witness ledger. Second, a
$\CompletionUp$ request reads the same finite Cauchy ledger as completion input
without selecting a limit and without quotienting streams.

Both consumers use only the finite entourage list, diagonal witnesses, common
refinement rows, symmetry rows, composition rows, endpoint $\hsame$ transport,
$\Cont$ observation windows, $\mathsf{Pkg}$ provenance, and local
$\NameCert_{\UniformSpaceUp}$ row exported by the bridge.
\end{theorem}
\begin{proof}
Use \autoref{thm:uniformspace-entourage-public-export}. It fixes the public
finite-entourage packet containing the finite entourage list, diagonal
witnesses, symmetry and composition rows, classifier transport, endpoint
$\hsame$ rows, $\Cont$ windows, package provenance, and local naming row.

Apply \autoref{thm:uniformspace-standard-bridge}. The standard bridge exposes
that packet as the public $\UniformSpaceUp$ source for downstream consumers and
adds no selected completion point, quotient stream equality, open-cover
compactness, host uniformity, or selected limit.

Next use \autoref{thm:uniformspace-cauchy-completion-handoff}. It routes the
finite $\CauchyFilterUp$ and $\CompletionUp$ requests through the same displayed
finite-entourage packet.

Finally apply \autoref{thm:uniformspace-common-refinement-cauchy-handoff}. The
common refinement row supplies the finite Cauchy witness ledger for the
$\CauchyFilterUp$ read, and the same ledger is retained by the $\CompletionUp$
read without selecting a limit or quotienting streams.
\end{proof}

\begin{theorem}[UniformSpace entourage-filter-metric comparison]
\label{thm:uniformspace-entourage-filter-metric-comparison}
An accepted $\UniformSpaceUp$ packet compares two point histories only through
the displayed entourage rows, filter-neighbourhood rows, $\MetricUp$ distance
witness rows when those witnesses are present, componentwise $\hsame$
transports on the two endpoints, $\Cont$ routes, and $\mathsf{Pkg}$
provenance.

The comparison exports no host uniformity, open-cover compactness principle,
quotient topology equality, choice-selected completion datum, or ambient
metric space equality. A downstream $\MetricUp$, $\TopologyUp$, $\FilterUp$,
or $\CauchyFilterUp$ consumer therefore receives exactly the finite comparison
surface carried by the $\UniformSpaceUp$ packet.
\end{theorem}
\begin{proof}
Project the accepted packet by
\autoref{thm:uniformspace-scoped-entourage-package}. This supplies the point
source, finite entourage list, diagonal, refinement, symmetry, composition,
transport, continuation, package, and local naming rows over the same
$\mathsf{BHist}$ surface.

Next replay the filter-neighbourhood witnesses. The finite filterbase
diagonal obligation and the diagonal refinement obligation identify each
requested neighbourhood with a displayed entourage row and a displayed
refinement route, while componentwise $\hsame$ carries the two endpoint
histories through the same classifier surface.

When a $\MetricUp$ distance witness row is present, it is read as one of the
neighbourhood anchors already routed through the displayed entourage ledger.
The classifier transport obligation preserves that row under endpoint
transport, and the common-refinement handoff keeps the filter and Cauchy reads
on the same finite continuation routes.

Finally apply
\autoref{thm:uniformspace-entourage-ledger-exactness}. Since the exactness
boundary has no coordinate for host uniformity, open-cover compactness,
quotient topology equality, or ambient metric equality, the comparison is
exhausted by the displayed entourage, filter, metric-witness, $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ rows.
\end{proof}

\closureat{UniformSpaceUp}{seedStr}
\closureat{UniformSpaceUp}{obligationStr}
\closureat{UniformSpaceUp}{publicStr}
\closureat{UniformSpaceUp}{bridgedStr}
\closureat{UniformSpaceUp}{matureStr}

\begin{closurestatus}{\UniformSpaceUp}
  \constructivestory{A uniform-space packet is generated by a carried point-history source, a finite list of entourage rows, diagonal witnesses, finite filterbase refinements, symmetry rows, composition rows, endpoint $\hsame$ transport, package provenance, and a local naming row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:uniformspace-entourage-public-export}, \autoref{thm:uniformspace-standard-bridge}, and \autoref{thm:uniformspace-finite-cauchy-completion-consumer-examples} export the finite filterbase diagonal, diagonal refinement, symmetry and composition, classifier transport, entourage ledger, common-refinement Cauchy handoff rows, common-refinement functoriality, standard finite-entourage bridge, and finite Cauchy and completion consumer examples as the public $\UniformSpaceUp$ downstream packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{The chapter does not close choice-based completion, quotient equality of Cauchy streams, open-cover compactness, host uniformity, or selected limits.}
  \upgradepath{The paper-side finite-entourage consumer treatment is mature; formal verification remains on the Lean axis.}
\end{closurestatus}
