\chapter{A Concrete Naming Certificate for $\TrieUp$}
\label{ch:concrete-instances-trie-namecert}

The $\TrieUp$ interface names finite prefix-indexed data without importing host
strings, host maps, or a host trie primitive. The reference point is Okasaki,
\emph{Purely Functional Data Structures} (1998), where tries are finite
prefix trees for keyed lookup; the BEDC surface below reads that structure as
finite $\BoolUp$, $\ListUp$, $\OptionUp$, $\NatUp$, and $\BitVectorUp$ rows.

\begin{definition}[Trie BHist source]\label{def:trie-bhist-source}
A $\TrieUp$ source packet is a finite $\mathsf{BHist}$ record
$$
T=(k,v,l,b,p)
$$
with the following visible coordinates:
\begin{enumerate}
\item $k$ is a finite key-path row, read either as a $\BitVectorUp$ path or as
a $\ListUp$ spine of branch histories;
\item $v$ is an $\OptionUp$ terminal payload row, recording whether the
current prefix carries a value and, when present, exposing only the displayed
value row;
\item $l$ is a $\NatUp$ length and depth ledger recording the finite prefix
length, the depth of each inspected node, and the fact that every public read
is below that depth;
\item $b$ is the branch ledger whose branch tags are $\BoolUp$ rows and whose
left and right subprefix reads are routed only through displayed finite list
or bit-vector positions;
\item $p$ is the $\Pkg$ provenance naming the consumed $\BoolUp$, $\ListUp$,
$\OptionUp$, $\NatUp$, $\BitVectorUp$, $\hsame$, and $\Cont$ certificate rows.
\end{enumerate}
The carrier predicate is $\mathsf{TrieSource}(k,v,l,b,p)$. Its classifier
compares accepted packets by componentwise key-path comparison, optional
payload comparison, branch-tag comparison, length-ledger comparison, and the
same displayed $\hsame$, $\Cont$, and $\Pkg$ routes. The packet contains no
host string equality, host finite map, function extensionality, hidden
ordering on keys, or unbounded tree object.
\end{definition}

\begin{theorem}[Trie carrier stability]\label{thm:trie-carrier-stability}
Let $T=(k,v,l,b,p)$ be an accepted $\TrieUp$ source packet. If the key path,
optional payload, depth ledger, branch ledger, and provenance row are
transported by displayed $\hsame$ along the $\Cont$ routes named by $p$, then
the transported packet $T'=(k',v',l',b',p')$ is again an accepted $\TrieUp$
source packet.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_carrier\_stability}
\leanvariant{BEDC.Derived.TrieUp.TriePacket\_carrier\_stability}
\begin{proof}
Project the five coordinates of \autoref{def:trie-bhist-source}. The
$\NatUp$ ledger transports first, so every later prefix and branch read is
bounded by the transported finite depth row.

Transport the key row through its displayed $\BitVectorUp$ or $\ListUp$
presentation. Each branch tag is a $\BoolUp$ row, so the branch ledger
transports componentwise along the same key-path positions.

Finally transport the optional payload and provenance rows. The $\OptionUp$
row preserves the absent case and transports the present payload only when the
present tag is displayed, while the $\Pkg$ row keeps the same finite
certificate dependencies. Thus the transported record is another accepted
trie source packet.
\end{proof}

\begin{theorem}[Trie classifier laws]\label{thm:trie-classifier-laws}
The $\TrieUp$ classifier is reflexive, symmetric, and transitive on accepted
packets by componentwise use of the $\BitVectorUp$ or $\ListUp$ key-path
classifier, the $\OptionUp$ payload classifier, the $\BoolUp$ branch
classifier, and the $\NatUp$ ledger classifier.
\end{theorem}
\begin{proof}
For reflexivity, take the reflexive classifier row for the key path, the
optional payload, each boolean branch tag, and the finite depth ledger. The
provenance and continuation rows are read unchanged.

For symmetry, reverse each displayed component comparison. The absent and
present cases of the optional payload reverse by the $\OptionUp$ classifier,
and every branch tag reverses by the $\BoolUp$ classifier.

For transitivity, compose the two key-path comparisons, the two optional
payload comparisons, the two branch-ledger comparisons, and the two depth
ledger comparisons. The depth ledger fixes the finite set of visible prefix
positions, so no hidden branch can enter the composite classifier.
\end{proof}

\begin{theorem}[Trie ledger coverage]\label{thm:trie-ledger-coverage}
Every public read of an accepted $\TrieUp$ packet factors through the finite
ledger $(k,v,l,b,p)$. Consumers see exactly finite prefix rows, boolean branch
rows, optional terminal payload rows, depth and length rows, $\hsame$
transports, $\Cont$ routes, and $\Pkg$ provenance.

Consequently the packet exports no host string type, host map lookup, ambient
function space, infinite tree, or implicit key ordering.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_ledger\_coverage}
\begin{proof}
Start from the carrier definition. Its tuple lists exactly the key, terminal
payload, depth ledger, branch ledger, and provenance coordinates.

A prefix-facing consumer reads $k$ through the displayed $\BitVectorUp$ or
$\ListUp$ path. A branch-facing consumer reads $b$ only through the boolean
tags admitted by the finite depth ledger $l$. A value-facing consumer reads
$v$ only through the $\OptionUp$ absent-or-present row.

The remaining public reads are the displayed $\hsame$ comparisons, $\Cont$
routes, and $\Pkg$ provenance named in $p$. Since no further coordinate is
present, every consumer projection is one of these finite rows.
\end{proof}

\begin{theorem}[Trie prefix-branch exactness]
\label{thm:trie-obligation-prefix-branch-exactness}
Every public branch read at a displayed finite prefix of an accepted $\TrieUp$
packet is determined by the key path row, the $\NatUp$ depth ledger, the
$\BoolUp$ branch tag at that prefix, the optional payload row, visible
$\hsame$ transport, $\Cont$ routes, and $\mathsf{Pkg}$ provenance from
\autoref{def:trie-bhist-source}.

No host string equality, host map lookup, hidden branch coordinate, or infinite
tree can change the read.
\end{theorem}
\begin{proof}
Project the tuple $(k,v,l,b,p)$ from \autoref{def:trie-bhist-source}. The key
path row $k$, optional payload row $v$, depth ledger $l$, branch ledger $b$,
and provenance row $p$ are the only coordinates admitted by the accepted
packet.

Use \autoref{thm:trie-ledger-coverage} to bound public branch reads by the
finite prefix rows displayed below the depth ledger. A consumer at such a
prefix can inspect only the recorded branch tag, the corresponding key-path
coordinate, the optional terminal payload row, and the visible transport and
provenance rows.

Finally apply \autoref{thm:trie-classifier-laws} componentwise. Transport of
the key, branch, payload, and depth rows preserves exactly the displayed finite
coordinates, so the $\NameCert$ surface of
\autoref{thm:trie-namecert-obligation-surface} receives a branch read whose
value is fixed by the recorded rows and by no host-side tree structure.
\end{proof}

\begin{theorem}[Trie prefix branch consumer exhaustion]
\label{thm:trie-prefix-branch-consumer-exhaustion}
Any accepted $\TrieUp$ prefix-branch consumer read factors through the displayed
finite $\mathsf{BHist}$ prefix row, the $\BoolUp$ branch tag, the $\ListUp$ path
spine, the $\NatUp$ depth counter, the $\OptionUp$ terminal payload row,
displayed $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
the local $\NameCert_{\TrieUp}$ ledger.

The consumer surface is exactly this finite BEDC row surface. It exports no
host map, external tree equality, unbounded lookup function, hidden node object,
or host key ordering.
\end{theorem}
\begin{proof}
Project the source tuple $(k,v,l,b,p)$ of
\autoref{def:trie-bhist-source}. The key coordinate supplies the displayed
finite prefix row as a $\ListUp$ spine, the branch ledger supplies the
$\BoolUp$ branch tag, the depth coordinate supplies the $\NatUp$ counter, and
the terminal coordinate supplies the $\OptionUp$ payload row.

Use \autoref{thm:trie-obligation-prefix-branch-exactness} to bind a public
prefix-branch read to those coordinates. Its route records the same displayed
$\hsame$ transports, $\Cont$ routes, and $\mathsf{Pkg}$ provenance named by the
source packet.

Repack the resulting finite read through
\autoref{thm:trie-namecert-obligation-surface}. The local $\NameCert_{\TrieUp}$
ledger accepts exactly the carrier rows, classifier rows, prefix-branch
determinacy rows, transport rows, and ledger-exactness rows already displayed
in the packet.

Apply \autoref{thm:trie-ledger-coverage} for the exclusion claim. Since every
consumer projection is a row of $(k,v,l,b,p)$ or the named local certificate
ledger, no host map, external tree equality, unbounded lookup function, hidden
node object, or host key ordering is exported.
\end{proof}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_prefix\_branch\_consumer\_exhaustion}

\begin{theorem}[Trie key-path exhaustion]\label{thm:trie-key-path-exhaustion}
Every public key-path read of an accepted $\TrieUp$ packet is exhausted by
the displayed $\BitVectorUp$ or $\ListUp$ key row, the $\NatUp$ depth ledger,
the $\hsame$ transports and $\Cont$ routes named by the packet, and the
$\Pkg$ provenance row. No host string, host ordering, ambient finite map, or
hidden key predicate contributes an additional public key-path coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_key\_path\_route\_exhaustion}
\begin{proof}
Project the key coordinate $k$ and depth ledger $l$ from
\autoref{def:trie-bhist-source}. The definition gives $k$ only as a displayed
$\BitVectorUp$ path or as a $\ListUp$ spine of branch histories, and it gives
$l$ as the bound for every public prefix read.

Use \autoref{thm:trie-carrier-stability} to see that transport preserves this
same finite key presentation along the displayed $\hsame$ and $\Cont$ routes.
Then apply \autoref{thm:trie-classifier-laws} componentwise to the accepted
key rows.

Finally apply \autoref{thm:trie-ledger-coverage}. Since every public read is
a projection from $(k,v,l,b,p)$, the only remaining key-path data is the
provenance named in $p$, and no host key structure is exported.
\end{proof}

\begin{theorem}[Trie prefix-branch determinacy]\label{thm:trie-prefix-branch-determinacy}
At each displayed finite prefix below the $\NatUp$ depth row of an accepted
$\TrieUp$ packet, the $\BoolUp$ branch tag selects exactly the recorded left
or right subprefix. No unrecorded branch at that prefix is public.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_prefix\_branch\_determinacy}
\begin{proof}
Project the branch ledger $b$ and the depth ledger $l$ from
\autoref{def:trie-bhist-source}. The ledger $l$ bounds the finite prefix
positions that a consumer may inspect, and $b$ records branch tags only at
those displayed positions.

For any such prefix, read the branch tag through its $\BoolUp$ row. The two
displayed boolean cases select the recorded left or right subprefix row, and
\autoref{thm:trie-classifier-laws} transports equality of branch reads
componentwise through the same finite coordinates.

The stability theorem \autoref{thm:trie-carrier-stability} preserves the
branch ledger under $\hsame$ and $\Cont$. Applying
\autoref{thm:trie-ledger-coverage} then excludes any branch coordinate not
recorded in $(k,v,l,b,p)$, so no extra branch is public.
\end{proof}

\begin{theorem}[Trie lookup payload projection]\label{thm:trie-lookup-payload-projection}
Every lookup payload read of an accepted $\TrieUp$ packet factors through the
$\OptionUp$ absent-or-present terminal row at the displayed key path. The
read never factors through a host finite map, host lookup function, or ambient
function space.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_lookup\_payload\_projection}
\begin{proof}
Project the terminal payload coordinate $v$ from
\autoref{def:trie-bhist-source}. The coordinate is an $\OptionUp$ row at the
displayed key path, so a consumer can observe only the absent tag or the
present tag together with the displayed payload row.

The key path used by the lookup is fixed by
\autoref{thm:trie-key-path-exhaustion}. The payload row transports along the
same displayed $\hsame$ and $\Cont$ routes by
\autoref{thm:trie-carrier-stability}, and the accepted-row comparison is
componentwise by \autoref{thm:trie-classifier-laws}.

Apply \autoref{thm:trie-ledger-coverage} to close the projection. Since the
finite tuple exports no host map or function coordinate, lookup payload reads
can only pass through the displayed $\OptionUp$ terminal row.
\end{proof}

\begin{theorem}[Trie NameCert obligation surface]\label{thm:trie-namecert-obligation-surface}
The local $\NameCert_{\TrieUp}$ obligation surface consists of five finite
rows:
\begin{enumerate}
\item carrier habitation: the empty trie is carried by the empty key path, an
absent $\OptionUp$ payload, the zero $\NatUp$ depth ledger, the empty branch
ledger, and the corresponding $\Pkg$ provenance;
\item classifier laws: reflexivity, symmetry, and transitivity are inherited
componentwise from \autoref{thm:trie-classifier-laws};
\item prefix-branch determinacy: at each displayed finite prefix, a $\BoolUp$
branch tag selects exactly the recorded left or right subprefix row, and no
unrecorded branch is public, as witnessed by
\autoref{thm:trie-key-path-exhaustion} and
\autoref{thm:trie-obligation-prefix-branch-exactness};
\item transport under $\hsame$ and $\Cont$: the stability theorem
\autoref{thm:trie-carrier-stability} repacks transported key, payload, branch,
ledger, and provenance rows as another accepted packet, with lookup payload
projection fixed by \autoref{thm:trie-lookup-payload-projection};
\item ledger exactness: downstream consumers may read only finite prefix
rows, branch rows, optional terminal payload rows, length and depth rows, and
the displayed provenance rows of \autoref{thm:trie-ledger-coverage}, with the
key-path, branch, and payload projections separated by
\autoref{thm:trie-key-path-exhaustion},
\autoref{thm:trie-prefix-branch-determinacy}, and
\autoref{thm:trie-lookup-payload-projection}.
\end{enumerate}
These rows are the complete seed obligation surface for prefix-tree
NameCert data over finite BEDC rows.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_namecert\_obligation\_surface}
\begin{proof}
For carrier habitation, choose the empty $\BitVectorUp$ or empty $\ListUp$
path, the absent $\OptionUp$ payload, the zero $\NatUp$ depth row, and the
empty branch ledger. The provenance row records only the finite data
certificates consumed by the packet.

For the classifier laws, apply \autoref{thm:trie-classifier-laws}. Because the
classifier is componentwise, the three equivalence laws are inherited from the
key, option, boolean branch, and natural ledger classifiers.

For prefix-branch determinacy, apply
\autoref{thm:trie-key-path-exhaustion} and
\autoref{thm:trie-prefix-branch-determinacy}. The key-path theorem fixes the
finite prefix positions, and the branch theorem fixes the recorded left or
right subprefix at each displayed position.

For transport, apply \autoref{thm:trie-carrier-stability}. The same $\hsame$
and $\Cont$ routes move the visible rows without adding host string equality,
host maps, or unbounded trees. Lookup payload reads are then projected through
\autoref{thm:trie-lookup-payload-projection}.

For ledger exactness, apply \autoref{thm:trie-ledger-coverage}. Every
downstream read is a projection from the finite tuple $(k,v,l,b,p)$, so the
NameCert obligation surface is exhausted by the listed rows.
\end{proof}

\begin{definition}[Trie terminal value packet]\label{def:trie-terminal-value-packet}
For a finite Boolean-key path, the visible terminal-value row is the
$\mathsf{BHist}$ packet
$$
\mathsf{TrieTerminal}(q,t,r,c,e,g,n)
$$
whose coordinates are as follows:
\begin{enumerate}
\item $q$ is the finite key spine, presented as a $\ListUp$ row of $\BoolUp$
branch histories;
\item $t$ is the terminal $\OptionUp$ value row, with the absent case carrying
no payload and the present case exposing only the displayed value packet;
\item $r$ is the displayed $\hsame$ transport row for the key spine and the
terminal option row;
\item $c$ is the $\Cont$ route taking each accepted prefix row to its extended
prefix row and taking the terminal option row to the lookup-facing read;
\item $e$ is the $\mathsf{BHist}$ branch ledger recording the visible
left-or-right decision at each position of $q$;
\item $g$ is the $\Pkg$ provenance naming the consumed $\BoolUp$, $\ListUp$,
$\OptionUp$, $\hsame$, and $\Cont$ rows;
\item $n$ is the local $\NameCert$ row certifying that these displayed rows are
the public terminal packet for the Boolean-key lookup.
\end{enumerate}
The packet contains no host map entry, host string key, ambient lookup
function, or hidden node object.
\end{definition}

\begin{theorem}[Trie prefix-extension classifier stability]\label{thm:trie-prefix-extension-classifier-stability}
Let $p$ and $p'$ be displayed Boolean-key prefixes classified by the
$\TrieUp$ classifier, and let $b$ be a visible $\BoolUp$ branch row. If $p$ is
extended by $b$ along the $\ListUp$ key spine and the extension is transported
through the displayed $\hsame$ row and $\Cont$ route of the packet, then the
transported extension of $p'$ is classified under the same branch label $b$.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TriePrefixExtensionClassifier\_stability}
\begin{proof}
Induct on the displayed $\ListUp$ key spine. In the empty-spine case, the
extension exposes only the first $\BoolUp$ branch row, and classifier
reflexivity for that branch row supplies the transported label.

For the cons-spine step, apply the induction hypothesis to the tail prefix.
The head branch row is transported by the same $\hsame$ route, and
\autoref{thm:trie-classifier-laws} composes the head comparison with the
classified tail comparison.

The $\Cont$ route then repacks the extended prefix as a public trie row.
\autoref{thm:trie-carrier-stability} keeps the transported record accepted,
so the resulting extension remains classified under the same visible branch
label and no hidden host key coordinate is introduced.
\end{proof}

\begin{theorem}[Trie Boolean-key path ledger coverage]\label{thm:trie-boolean-key-path-ledger-coverage}
Every admitted finite Boolean-key lookup path in a $\TrieUp$ packet carries a
ledger entry for each displayed branch decision and one terminal
$\OptionUp$ value packet at the final prefix. These entries are precisely the
visible $\BoolUp$ branch rows, the $\ListUp$ key-spine rows, the transported
$\hsame$ and $\Cont$ rows, the $\Pkg$ provenance, and the terminal packet of
\autoref{def:trie-terminal-value-packet}.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieTerminalPacket\_boolean\_key\_path\_ledger\_coverage}
\begin{proof}
Induct on the displayed $\ListUp$ key spine. For the empty spine, the lookup
path is already at the terminal prefix, so the ledger contains the single
$\OptionUp$ terminal packet and the provenance rows named by
\autoref{def:trie-terminal-value-packet}.

For a cons spine, the head is a visible $\BoolUp$ branch decision. Record that
branch row in the ledger and apply the induction hypothesis to the remaining
spine, transporting the tail ledger by the displayed $\hsame$ row.

Finally compose the $\Cont$ routes along the finite spine. The composed route
preserves the branch entries and delivers the terminal $\OptionUp$ packet at
the final prefix, while \autoref{thm:trie-ledger-coverage} excludes any
additional host lookup, hidden key ordering, or infinite-tree coordinate.
\end{proof}

\begin{theorem}[Trie branch read exactness]\label{thm:trie-branch-read-exactness}
Let $T=(k,v,l,b,p)$ be an accepted $\TrieUp$ source packet. Every public
branch read of $T$ factors through a displayed finite prefix position bounded
by the $\NatUp$ depth ledger, a $\BoolUp$ branch tag, the corresponding
$\ListUp$ or $\BitVectorUp$ key-path row, the displayed $\hsame$ and $\Cont$
route, and the $\Pkg$ provenance named by $p$.

Conversely, every displayed branch row of that form is an accepted public
branch read of $T$. No host string, host finite map, ambient lookup function,
or hidden key-order coordinate contributes an additional public branch read.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieBranchRead\_exactness}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_branch\_read\_exactness}
\begin{proof}
Project the five coordinates of \autoref{def:trie-bhist-source}. The branch
ledger $b$ records only boolean branch tags at finite prefix positions, and the
depth ledger $l$ bounds the positions visible to public reads.

Apply \autoref{thm:trie-ledger-coverage} to obtain the available coordinates.
The key row is read through the displayed $\ListUp$ or $\BitVectorUp$ path, and
the branch selector is read through its $\BoolUp$ row.

Use \autoref{thm:trie-classifier-laws} to transport the key-path, branch, and
ledger coordinates componentwise along the named $\hsame$ and $\Cont$ routes.
The provenance coordinate $p$ supplies exactly the consumed certificate rows.

For the converse direction, start from a displayed prefix position, branch tag,
key-path row, transport route, and provenance row named in the packet. These
are precisely coordinates of $(k,v,l,b,p)$, so they assemble to a public branch
read accepted by the carrier.

The exclusions follow from absence of coordinates in
\autoref{def:trie-bhist-source}: host strings, host maps, ambient lookup
functions, and key-order data cannot be projected from the packet.
\end{proof}

\begin{theorem}[Trie key-prefix transport]\label{thm:trie-key-prefix-transport}
For accepted $\TrieUp$ packets transported along the displayed $\hsame$ and
$\Cont$ routes, key-path rows preserve finite prefix positions, $\NatUp$ depth
bounds, and $\BoolUp$ branch selectors. Thus a transported branch read remains
on the same displayed finite prefix surface, with only the corresponding
$\ListUp$ or $\BitVectorUp$ key row, branch tag, ledger row, and $\Pkg$
provenance transported.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_key\_prefix\_transport}
\begin{proof}
Begin with \autoref{thm:trie-carrier-stability}. Transporting the accepted
packet repacks the key, payload, branch, ledger, and provenance coordinates as
another accepted $\TrieUp$ packet.

The component laws in \autoref{thm:trie-classifier-laws} transport the key row
through its displayed $\ListUp$ or $\BitVectorUp$ presentation and transport
each branch selector through its $\BoolUp$ classifier row. The $\NatUp$ ledger
travels componentwise with those same finite positions.

Finally, return to the source packet of \autoref{def:trie-bhist-source}. The
only key-path coordinates present there are the displayed key row, finite depth
bound, branch selector, named $\hsame$ and $\Cont$ route, and $\Pkg$
provenance. Hence transport preserves exactly those prefix coordinates and no
additional key structure.
\end{proof}

\begin{theorem}[Trie lookup ledger exhaustion]\label{thm:trie-lookup-ledger-exhaustion}
Every lookup-facing consumer of an accepted $\TrieUp$ packet is exhausted by
the displayed key path, $\OptionUp$ terminal payload, $\BoolUp$ branch rows,
$\NatUp$ depth ledger, $\hsame$ rows, $\Cont$ routes, and $\Pkg$ provenance
already present in the packet. The packet exports no host finite-map lookup,
string equality, function extensionality, infinite tree, or key ordering.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieBHistSource\_lookup\_ledger\_exhaustion}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_lookup\_ledger\_exhaustion}
\begin{proof}
Use \autoref{thm:trie-branch-read-exactness} for branch-facing reads. Each such
read is a displayed finite prefix position, boolean selector, key-path row,
transport route, and provenance row from the packet.

Use \autoref{thm:trie-key-prefix-transport} for transported key-facing reads.
It preserves the finite prefix positions, ledger bounds, and branch selectors
under the displayed $\hsame$ and $\Cont$ routes.

The remaining lookup payload coordinate is the $\OptionUp$ row already recorded
in \autoref{def:trie-bhist-source}. Apply \autoref{thm:trie-ledger-coverage}
and \autoref{thm:trie-namecert-obligation-surface} to collect the full packet
surface.

Since the collected surface is exactly $(k,v,l,b,p)$, every lookup-facing
consumer projection is one of the displayed rows. Host finite maps, string
equality, function extensionality, infinite trees, and key orderings are not
coordinates of that packet, so they are not exported.
\end{proof}

\begin{theorem}[Trie lookup prefix ledger factorization]\label{thm:trie-lookup-prefix-ledger-factorization}
Let $T=(k,v,l,b,p)$ be an accepted $\TrieUp$ source packet and let $q$ be a
finite key prefix displayed by the $\ListUp$ or $\BitVectorUp$ key-path row.
A lookup read at $q$ factors through exactly one of two visible sources: the
optional terminal payload row at $q$, or a branch ledger row extending $q$
below the unary depth ledger. An absent terminal payload row alone is not
evidence for absence below $q$ unless the branch ledger below $q$ is also
exhausted.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_lookup\_prefix\_ledger\_factorization}
\begin{proof}
Project the source packet of \autoref{def:trie-bhist-source}. The prefix $q$
is read from the displayed key-path coordinate, while the optional terminal
payload and branch rows are separate coordinates of the same packet.

Use \autoref{thm:trie-branch-read-exactness} to identify every branch read
below $q$ with a displayed finite prefix position, boolean selector, key-path
row, transport route, and provenance row. Then use
\autoref{thm:trie-lookup-ledger-exhaustion} to see that no other lookup-facing
source is available.

Split the optional payload row at $q$. In the present case, the lookup read
uses the terminal $\OptionUp$ payload projection. In the absent case, the
absence of that terminal coordinate only removes the terminal source at $q$.

It remains to account for reads below the prefix. Those reads must pass
through branch ledger rows extending $q$; only when that branch ledger is also
exhausted does the packet provide finite evidence for absence below the
prefix. No host map lookup, string equality, or ambient trie semantics is
imported.
\end{proof}

\begin{theorem}[Trie finite branch consumer boundary]\label{thm:trie-finite-branch-consumer-boundary}
Let $T=(k,v,l,b,p)$ be a concrete $\TrieUp$ $\mathsf{BHist}$ source packet
from \autoref{def:trie-bhist-source}, with displayed key path $k$, optional
terminal payload $v$, unary depth ledger $l$, boolean branch rows $b$, and
$\Pkg$ provenance $p$ over $\BoolUp$, $\ListUp$, $\OptionUp$, $\NatUp$, and
$\BitVectorUp$ certificates. Every finite branch consumer read of $T$ factors
through exactly one of two visible projections: either the terminal payload
projection of \autoref{thm:trie-lookup-payload-projection}, or the branch
route determined by \autoref{thm:trie-prefix-branch-determinacy}.

These two projections exhaust the public consumer surface. No host string,
host finite map, infinite tree, ambient lookup function, or key-order
semantics is introduced by a finite branch read.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_finite\_branch\_consumer\_boundary}
\begin{proof}
Unfold the source packet of \autoref{def:trie-bhist-source}. Its public
coordinates are the key path, optional payload, depth ledger, branch ledger,
and provenance rows named in the theorem.

Split on the displayed optional terminal branch. In the absent case, there is
no terminal payload coordinate to read, so the consumer must remain on the
finite branch route. In the present case, the only terminal read is the
$\OptionUp$ payload row, and
\autoref{thm:trie-lookup-payload-projection} supplies that projection.

For the branch route, use \autoref{thm:trie-key-path-exhaustion} to cover the
finite key positions. At each covered prefix,
\autoref{thm:trie-prefix-branch-determinacy} fixes the unique displayed
$\BoolUp$ branch row selected by the packet.

Finally apply \autoref{thm:trie-ledger-coverage} to account for provenance.
The ledger contains only the displayed $\BoolUp$, $\ListUp$, $\OptionUp$,
$\NatUp$, $\BitVectorUp$, $\hsame$, $\Cont$, and $\Pkg$ rows, so no host
string, host map, infinite-tree coordinate, ambient lookup function, or
key-order semantics can be projected by the consumer.
\end{proof}
\leanchecked{BEDC.Derived.TrieUp.TrieFiniteBranchConsumer\_boundary}

\begin{theorem}[Trie public NameCert export]\label{thm:trie-public-namecert-export}
The source packet of \autoref{def:trie-bhist-source}, the obligation surface
of \autoref{thm:trie-namecert-obligation-surface}, the branch read exactness
of \autoref{thm:trie-branch-read-exactness}, the lookup ledger exhaustion of
\autoref{thm:trie-lookup-ledger-exhaustion}, the prefix ledger factorization
of \autoref{thm:trie-lookup-prefix-ledger-factorization}, and the finite branch
consumer boundary of \autoref{thm:trie-finite-branch-consumer-boundary}
assemble the
public $\NameCert_{\TrieUp}$ surface for the finite key path, optional payload,
unary depth ledger, branch rows, displayed $\hsame$ and $\Cont$ routes,
$\Pkg$ provenance, and $\BoolUp$, $\ListUp$, $\OptionUp$, $\NatUp$, and
$\BitVectorUp$ certificates.

This public export contains no host strings, host finite maps, infinite trees,
key ordering, or ambient lookup function.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_public\_namecert\_export}
\begin{proof}
Project the scoped packet rows from \autoref{def:trie-bhist-source}. They are
exactly the finite key path, optional terminal payload, unary depth ledger,
branch ledger, transport routes, continuation routes, and provenance rows.

Apply \autoref{thm:trie-namecert-obligation-surface} to package these rows as
the local $\NameCert_{\TrieUp}$ obligation surface. The branch rows are
identified by \autoref{thm:trie-branch-read-exactness}, and the lookup-facing
payload and ledger reads are exhausted by
\autoref{thm:trie-lookup-ledger-exhaustion}.

The prefix boundary is
\autoref{thm:trie-lookup-prefix-ledger-factorization}: a missing terminal row
at a prefix is separated from exhaustion of branch rows below that prefix, so
the public export records finite failed-lookup evidence only when both visible
sources have been accounted for.

Finally use \autoref{thm:trie-finite-branch-consumer-boundary}. It states that
every finite branch consumer read factors through the displayed terminal
payload or branch route, so the assembled packet is a public consumer surface
over precisely the named rows.

The excluded objects are not coordinates of the source packet and are not
introduced by any of the cited projections. Hence host strings, host finite
maps, infinite trees, key ordering, and ambient lookup functions are absent
from the public $\NameCert_{\TrieUp}$ export.
\end{proof}

\begin{theorem}[Trie public export route decomposition]\label{thm:trie-public-export-route-decomposition}
The public $\NameCert_{\TrieUp}$ export decomposes every finite consumer route
into exactly one of two displayed routes: the optional terminal payload
projection or the Boolean branch route below the unary depth ledger. In both
routes the key path, payload row when present, branch row, depth row, displayed
$\hsame$ transport, $\Cont$ routes, and $\mathsf{Pkg}$ provenance are preserved
as rows of the same finite packet.

No host string, host finite map, infinite tree, ambient lookup function, or
key-order semantics is introduced by this decomposition.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_public\_export\_route\_decomposition}
\begin{proof}
Project the public packet through
\autoref{thm:trie-public-namecert-export}. This exposes the finite key path,
optional payload, unary depth ledger, branch rows, displayed transport,
continuation routes, and package provenance.

For the terminal route, apply
\autoref{thm:trie-lookup-payload-projection}. If the terminal payload is
present, the consumer read is exactly the displayed $\OptionUp$ payload row at
the selected key path. If it is absent, there is no terminal payload coordinate
to read.

For the branch route, apply \autoref{thm:trie-branch-read-exactness}. It
identifies every branch-facing read below the unary depth ledger with the
corresponding displayed $\BoolUp$ branch row.

Finally use \autoref{thm:trie-lookup-ledger-exhaustion}. The ledger has no
third consumer route beyond the optional terminal payload projection and the
finite branch route, and all named key, payload, branch, depth, transport,
continuation, and provenance rows remain inside the same public
$\NameCert_{\TrieUp}$ export.
\end{proof}

\begin{theorem}[Trie standard finite packet bridge]\label{thm:trie-standard-finite-packet-bridge}
The finite $\TrieUp$ packet of \autoref{def:trie-bhist-source} and the public
export of \autoref{thm:trie-public-namecert-export} bridge to the standard
finite prefix-tree reading. The visible key path, optional payload, unary
depth ledger, $\BoolUp$ branch rows, $\mathsf{BHist}$ packet rows, $\hsame$
transport, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and $\NameCert_{\TrieUp}$
rows are exactly the public bridge surface.

The bridge exports no host string, host finite map, hidden infinite tree, key
ordering, or ambient lookup function.
\end{theorem}
\begin{proof}
Project the finite packet as $(k,v,l,b,p)$ from
\autoref{def:trie-bhist-source}. The coordinates are the displayed key path,
optional terminal payload, unary depth ledger, branch rows, and provenance
rows, with the $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ surfaces already named by the source and public export.

Use \autoref{thm:trie-key-path-exhaustion} to identify the standard
prefix-tree path with the displayed finite key row. Use
\autoref{thm:trie-prefix-branch-determinacy} to identify each finite branch
decision with its recorded $\BoolUp$ row below the depth ledger.

Apply \autoref{thm:trie-lookup-payload-projection} for the optional terminal
payload. Then apply \autoref{thm:trie-public-namecert-export} to package the
path, payload, branch, transport, continuation, provenance, and local naming
rows as the public $\NameCert_{\TrieUp}$ surface.

Finally, exhaust the remaining reads through the unary ledger. Every standard
finite prefix-tree read is below the displayed depth row and therefore lands
in one of the projected rows. Since the packet has no coordinate for host
strings, host maps, hidden infinite trees, key orderings, or ambient lookup
functions, none is exported by the bridge.
\end{proof}

\begin{theorem}[Trie terminal-prefix readback coverage]\label{thm:trie-terminal-prefix-readback-coverage}
Every terminal read of a finite $\TrieUp$ packet factors through the displayed
finite key prefix, optional terminal payload row, $\BoolUp$ branch row, unary
depth ledger, $\hsame$ transport, $\Cont$ route, $\mathsf{Pkg}$ provenance,
and local $\NameCert_{\TrieUp}$ row.

Conversely, any finite read assembled from exactly those rows repacks as a
terminal-prefix read of the same finite packet. The readback surface contains
no host string, host map, infinite tree, key-order semantics, ambient lookup
function, or balancing invariant.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieTerminalPacket\_prefix\_readback\_coverage}
\leanchecked{BEDC.Derived.TrieUp.TerminalPrefixReadback.TrieSourcePacket\_terminal\_prefix\_readback\_coverage}
\begin{proof}
For a prefix-facing read, apply
\autoref{thm:trie-prefix-branch-consumer-exhaustion}. It keeps the consumer
inside the displayed key prefix, unary depth ledger, branch rows, transport
routes, continuation routes, provenance, and local naming evidence.

For a terminal key-path read, apply
\autoref{thm:trie-boolean-key-path-ledger-coverage}. The terminal payload is
read at the displayed prefix endpoint, and every branch decision is one of the
recorded $\BoolUp$ rows below the unary depth ledger.

Use \autoref{thm:trie-branch-read-exactness} to identify the branch route
used by the terminal read. Then apply
\autoref{thm:trie-standard-finite-packet-bridge} to repack the same rows as a
finite prefix-tree reading.

The converse direction reverses this packaging: a read built from the key
prefix, optional payload, branch, depth, transport, continuation, provenance,
and local certificate rows is exactly a terminal-prefix read of the displayed
finite packet. Since no cited row names host strings, host maps, infinite
trees, key-order semantics, lookup functions, or balancing invariants, none is
available to the readback.
\end{proof}
\leanchecked{BEDC.Derived.TrieUp.TrieTerminalPacket\_terminal\_prefix\_readback\_coverage}

\begin{theorem}[Trie finite consumer completeness]\label{thm:trie-finite-consumer-completeness}
Every finite consumer of the $\TrieUp$ bridge factors through the key-path
row, the optional terminal payload row, the unary length and depth ledger, the
$\BoolUp$ branch rows, displayed $\hsame$ transport, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and the $\BoolUp$, $\ListUp$, $\OptionUp$,
$\NatUp$, and $\BitVectorUp$ certificates already named by
\autoref{thm:trie-public-namecert-export} and
\autoref{thm:trie-standard-finite-packet-bridge}.

Conversely, any finite read assembled from exactly those rows repacks as a
valid finite trie consumer read of the bridged packet. The completeness
surface exports no host strings, host finite maps, infinite trees,
key-order semantics, ambient lookup function, or balancing invariant.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_finite\_consumer\_completeness}
\begin{proof}
Project the source packet of \autoref{def:trie-bhist-source}. Its carrier
coordinates are the key path, optional terminal payload, unary ledger, branch
rows, and provenance row, together with the displayed $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and local certificate data.

For the forward direction, read branch-facing coordinates through
\autoref{thm:trie-branch-read-exactness}. Transported key prefixes are carried
by \autoref{thm:trie-key-prefix-transport}, while lookup-facing rows are
exhausted by \autoref{thm:trie-lookup-ledger-exhaustion}. The boundary theorem
\autoref{thm:trie-finite-branch-consumer-boundary} then leaves only the
terminal payload projection or the displayed branch route.

Apply \autoref{thm:trie-public-namecert-export} to collect these coordinates
as the public $\NameCert_{\TrieUp}$ surface. Then apply
\autoref{thm:trie-standard-finite-packet-bridge} to identify the same surface
with the standard finite prefix-tree reading.

For the converse direction, start with a finite read using only the listed
rows. The public export supplies the local certificate package, and the
standard bridge repacks the key path, payload, ledger, branch, transport,
continuation, provenance, and certificate rows into the accepted finite trie
consumer surface.

No cited theorem introduces a coordinate outside the source packet. Hence
host strings, host finite maps, infinite trees, key-order semantics, ambient
lookup functions, and balancing invariants remain outside the exported
consumer interface.
\end{proof}

\closureat{TrieUp}{seedStr}
\closureat{TrieUp}{obligationStr}
\closureat{TrieUp}{scopedStr}
\closureat{TrieUp}{publicStr}
\closureat{TrieUp}{bridgedStr}
\closureat{TrieUp}{matureStr}

\begin{closurestatus}{\TrieUp}
  \constructivestory{A trie packet is generated by a finite key-path row, an optional terminal payload row, a unary length and depth ledger, boolean branch rows, displayed transport routes, and package provenance over Bool, List, Option, Nat, and BitVector certificates.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:trie-bhist-source}, \autoref{thm:trie-namecert-obligation-surface}, \autoref{thm:trie-branch-read-exactness}, \autoref{thm:trie-lookup-ledger-exhaustion}, \autoref{thm:trie-lookup-prefix-ledger-factorization}, \autoref{thm:trie-finite-branch-consumer-boundary}, \autoref{thm:trie-public-namecert-export}, \autoref{thm:trie-standard-finite-packet-bridge}, and \autoref{thm:trie-finite-consumer-completeness} assemble the public finite trie $\NameCert$ export, bridge it to the standard finite prefix-tree reading, and exhaust finite consumer reads over the key path, optional payload, unary depth ledger, branch rows, displayed transport and continuation routes, package provenance, and Bool, List, Option, Nat, and BitVector certificates.}
  \formalstatus{\unformalizedV}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close host strings, host finite maps, function extensionality, infinite trees, key-order semantics, balancing invariants, or host lookup behavior.}
  \upgradepath{No further paper-side theory grade remains for the finite trie packet surface; formal bridge verification remains on the separate verification axis.}
\end{closurestatus}

\begin{definition}[Displayed Trie prefix subledger]\label{def:trie-displayed-prefix-subledger}
Let $T=(k,v,l,b,p)$ be an accepted $\TrieUp$ source packet. A displayed prefix subledger of $T$ is a finite packet
$$
U=(k_U,v_U,l_U,b_U,p_U;\iota)
$$
with a displayed inclusion row $\iota$ into the visible prefix positions of $T$ such that:
\begin{enumerate}
\item $k_U$ is a finite $\BitVectorUp$ path or $\ListUp$ spine whose entries are exactly the key-path entries of $k$ at the positions selected by $\iota$;
\item the selected positions are prefix-closed: whenever a displayed position is selected, every displayed predecessor prefix of that position in the key-path ledger is also selected;
\item $v_U$ is the $\OptionUp$ payload row of $T$ restricted to selected terminal positions, so the absent tag stays absent and a present tag exposes only the same displayed payload row already exposed by $v$;
\item $l_U$ is the $\NatUp$ depth ledger obtained by restricting $l$ to the selected positions, with each selected read still below the corresponding depth bound;
\item $b_U$ is the branch ledger obtained by retaining exactly the $\BoolUp$ branch tags and left or right subprefix reads of $b$ whose source and target prefixes are selected by $\iota$;
\item $p_U$ is the projected $\Pkg$ provenance row naming only the consumed $\BoolUp$, $\ListUp$, $\OptionUp$, $\NatUp$, $\BitVectorUp$, $\hsame$, and $\Cont$ rows that occur in the retained coordinates.
\end{enumerate}
The associated restricted packet is $T|_U=(k_U,v_U,l_U,b_U,p_U)$.
\end{definition}

\begin{theorem}[Trie prefix subledger restriction carrier]\label{thm:trie-prefix-subledger-restriction-carrier}
Let $T=(k,v,l,b,p)$ be an accepted $\TrieUp$ source packet, and let $U$ be a displayed prefix subledger of $T$ in the sense of \autoref{def:trie-displayed-prefix-subledger}. Then the restricted packet
$$
T|_U=(k_U,v_U,l_U,b_U,p_U)
$$
is again an accepted $\TrieUp$ source packet under the same $\BoolUp$, $\ListUp$, $\OptionUp$, $\NatUp$, and $\BitVectorUp$ dependency certificates.
\end{theorem}
\begin{proof}
Unpack the accepted source packet by \autoref{def:trie-bhist-source}. The original carrier consists only of the key-path row, optional terminal payload row, finite depth ledger, boolean branch ledger, and package provenance row. The displayed subledger definition selects rows from exactly those five coordinates and records the inclusion row $\iota$.

First consider the key coordinate. Since $k_U$ is obtained by selecting displayed positions of the finite $\BitVectorUp$ path or $\ListUp$ branch-history spine of $k$, it is again a finite key-path row of the same kind. Prefix-closedness of the selected positions ensures that every selected non-root prefix has its predecessor prefix in the same restricted packet, so no branch read in $k_U$ points outside the restricted carrier.

Next consider the $\NatUp$ ledger. The row $l_U$ is the restriction of $l$ to selected positions. Every public read admitted by $l_U$ was already a public read admitted by $l$, and the depth inequality for that read is the same displayed $\NatUp$ row. Thus the restricted depth ledger is finite and still bounds all selected key and branch reads.

For the branch coordinate, each retained entry of $b_U$ is a $\BoolUp$ tag already present in $b$. The definition of displayed prefix subledger keeps a branch entry only when its source prefix and the selected left or right subprefix row are both selected by $\iota$. Therefore the branch ledger of the restricted packet has no public unrecorded branch, and every visible branch selection remains routed through displayed finite list or bit-vector positions.

For the optional payload coordinate, the absent case is inherited unchanged from $v$. In the present case, $v_U$ exposes only a payload row already exposed by the original $\OptionUp$ row $v$ at a selected terminal prefix. Thus no payload comparison, hidden value equality, or terminal read is introduced by the restriction.

Finally, $p_U$ is the projection of the original provenance row $p$ to the dependency rows actually used by $k_U$, $v_U$, $l_U$, and $b_U$. It names the same kinds of certificates as $p$: $\BoolUp$, $\ListUp$, $\OptionUp$, $\NatUp$, $\BitVectorUp$, $\hsame$, and $\Cont$. Since \autoref{thm:trie-ledger-coverage} says every public read of an accepted trie packet factors through the finite ledger coordinates, deleting unselected rows cannot create a host string equality, a host finite map lookup, an ambient function space, an infinite tree, or an implicit ordering on keys.

The five projected coordinates therefore satisfy the same carrier clauses as \autoref{def:trie-bhist-source}. Hence $T|_U=(k_U,v_U,l_U,b_U,p_U)$ is an accepted $\TrieUp$ source packet under the same finite dependency certificates.
\end{proof}
