\chapter{A Concrete Naming Certificate for $\OracleResponseLedgerUp$}
\label{ch:concrete-instances-oracleresponseledger-namecert}
\origin{ai}

The $\OracleResponseLedgerUp$ packet realizes the oracle-response row of
\autoref{def:quadrant-oracle-substrate} as a finite $\NameCert$ surface. It
sits between the oracle-call transcript of
\autoref{ch:concrete-instances-oracleaugmentedsubstrate-namecert} and the
external-channel boundary of
\autoref{ch:concrete-instances-oracle-substrate-boundary-namecert}. Its
distinguishing datum is a response ledger: a query can be paired with a finite
reply and boundary row without becoming a closed-substrate observation.

\falsifiablePrediction{No accepted response ledger can certify a closed-substrate observation unless the same packet also displays the boundary row separating the response from substrate-internal orbit data.}

\independenceWitness{closureuniversalityquadrant, oracleaugmentedsubstrate, oraclesubstrateboundary, universalclosedsubstrate, presburger-subuniversal; the response ledger carries a query/response row that the quadrant map and closed-substrate witnesses lack, while boundary chapters do not classify response equality.}

\begin{definition}[Oracle-response ledger carrier]
\label{def:oracle-response-ledger-carrier}
An $\OracleResponseLedgerUp$ carrier is a finite $\BHist$ packet
$$
L=(S,Q,R,B,F,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the substrate row whose oracle-facing request is being inspected;
\item $Q$ is the finite oracle-query row, recording the query name, request
site, and local input slice;
\item $R$ is the response row, recording the finite reply token, response
name, and point of consumption;
\item $B$ is the boundary row, separating the response from closed
substrate-internal orbit observations;
\item $F$ is the refusal row, excluding closed-substrate certification,
quotient-response equality, hidden oracle correctness, and host-semantic
conversion of the response;
\item $E$ is the route-exactness row, recording that any public response read
must pass through $Q,R,B,F$ before it reaches a quadrant or boundary consumer;
\item $H$ records componentwise $\hsame$ transports for $S,Q,R,B,F,E,P,N$;
\item $C$ records displayed $\Cont$ routes through the query, response,
boundary, refusal, and response-ledger reads;
\item $P$ is the $\Pkg$ provenance over $\OracleResponseLedgerUp$,
$\OracleAugmentedSubstrateUp$, $\OracleSubstrateBoundaryUp$,
$\ClosureUniversalityQuadrantUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows;
\item $N$ is the local $\NameCert_{\OracleResponseLedgerUp}$ row.
\end{enumerate}
The local classifier compares accepted ledgers only through these rows. It has
no coordinate for treating the response as a closed orbit record, no hidden
oracle-correctness proof, and no quotient equality of response behaviours.
\end{definition}
\leanchecked{BEDC.Derived.OracleResponseLedgerUp.OracleResponseLedgerTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Oracle-response ledger NameCert obligations]
\label{thm:oracle-response-ledger-namecert-obligations}
For the carrier of \autoref{def:oracle-response-ledger-carrier}, the local
$\NameCert_{\OracleResponseLedgerUp}$ surface consists exactly of seven finite
obligation rows:
\begin{enumerate}
\item carrier exposure for $L=(S,Q,R,B,F,E,H,C,P,N)$;
\item query accountability through the displayed oracle-query row $Q$;
\item response accountability through the displayed reply row $R$;
\item boundary accountability through $B$, separating the response from
closed-substrate observations;
\item refusal accountability through $F$, excluding closed replay, hidden
oracle correctness, quotient response equality, and host semantic conversion;
\item route exactness through $E,C$, requiring public response consumers to
read the query, response, boundary, and refusal rows in the same packet;
\item componentwise stability, provenance, and local naming through $H,P,N$.
\end{enumerate}
Thus an oracle response is accepted only as a finite BEDC ledger over query,
response, boundary, refusal, route, provenance, and naming rows.
\end{theorem}
\begin{proof}
Carrier exposure is projection from
\autoref{def:oracle-response-ledger-carrier}. The accepted packet displays
the substrate row, query row, response row, boundary row, refusal row,
route-exactness row, transports, routes, provenance, and local name as its only
public coordinates.

Query and response accountability are separate finite reads. The row $Q$
records the request site and local input slice, while $R$ records the reply
token and point of consumption. Neither row reconstructs the other from the
substrate row alone.

Boundary and refusal accountability keep the response outside the closed
observation channel. The boundary chapter supplies the external-channel
separation, and the oracle-augmented substrate chapter supplies the call and
transcript surface. The refusal row records that closed replay, hidden oracle
correctness, quotient response equality, and host semantic conversion are not
available inside the ledger.

Finally $E,C,H,P,N$ route, transport, package, and name the same finite packet.
Any public response consumer must therefore pass through the displayed query,
response, boundary, and refusal rows before using the ledger, and no unlisted
closed-substrate or oracle-correctness coordinate remains.
\end{proof}

\begin{theorem}[Oracle-response ledger boundary non-escape]
\label{thm:oracle-response-ledger-boundary-nonescape}
Every public response read exported by an accepted
$\OracleResponseLedgerUp$ packet factors through the finite route
$$
S,Q,R,B,F,E,H,C,P,N .
$$
The route can certify a finite query/response ledger at an oracle boundary,
but it exports no closed-substrate observation for the response, no hidden
oracle-correctness theorem, no quotient equality of response streams, no host
semantic equality, and no closed universal substrate witness.
\end{theorem}
\begin{proof}
Begin with the carrier projection. The only response-facing coordinates are
the substrate row $S$, query row $Q$, response row $R$, boundary row $B$,
refusal row $F$, route-exactness row $E$, transports $H$, continuations $C$,
provenance $P$, and local name $N$.

The boundary row must be displayed before a response can be read as an oracle
response. By \autoref{ch:concrete-instances-oracle-substrate-boundary-namecert},
the oracle-facing edge is separated from closed substrate observations, and by
\autoref{ch:concrete-instances-oracleaugmentedsubstrate-namecert} the call and
transcript remain explicit oracle rows rather than substrate-internal orbit
data.

The refusal row then blocks the remaining escape modes. A closed universal
substrate witness, quotient response equality, hidden oracle-correctness
theorem, or host semantic equality would require a coordinate not present in
$L$.

Thus the public response ledger is exactly the displayed finite route. It may
serve quadrant and boundary consumers as oracle-response evidence, but only as
finite BEDC data with the boundary and refusal rows still visible.
\end{proof}

The later Lean \texttt{TasteGate.lean} development for
$\OracleResponseLedgerUp$ must provide explicit
$\mathsf{Nontrivial}\ \OracleResponseLedgerUp$ and
$\mathsf{FieldFaithful}\ \OracleResponseLedgerUp$ instances for the displayed
carrier. These instances must preserve the query row, response row, boundary
row, refusal row, route-exactness row, transport rows, continuation routes,
package provenance, and local naming row.

\closureat{OracleResponseLedgerUp}{seedStr}

\begin{closurestatus}{\OracleResponseLedgerUp}
  \constructivestory{An $\OracleResponseLedgerUp$ packet is generated from a substrate row, oracle-query row, response row, boundary row, refusal row, route-exactness row, componentwise hsame transports, displayed continuation routes, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:oracle-response-ledger-carrier}, \autoref{thm:oracle-response-ledger-namecert-obligations}, and \autoref{thm:oracle-response-ledger-boundary-nonescape} specify the finite oracle-response ledger certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove Lean verification, bridge checking, oracle correctness, closed replay of oracle responses, quotient response equality, host semantic equality, or physical realizability of oracle channels.}
  \upgradepath{Obligation closure requires checked carrier admission, query accountability, response accountability, boundary accountability, refusal exactness, route exactness, nontriviality, and field faithfulness for the same response ledger.}
\end{closurestatus}
