\chapter{A Concrete Naming Certificate for $\LocatedCauchyUp$}
\label{ch:concrete-instances-locatedcauchy-namecert}

The $\LocatedCauchyUp$ interface records the finite located-Cauchy packet that
sits between explicit Cauchy-rate names and the $\RealUp$ seal. Following
Bishop and Bridges, Constructive Analysis, the packet treats located rational
ball data as constructive evidence attached to a Cauchy name. It does not form
Dedekind cuts, quotient streams, selected real limits, trichotomy witnesses,
choice data, or open-cover compactness objects.

\begin{definition}[LocatedCauchy finite carrier]
\label{def:locatedcauchy-bhist-carrier}
A $\LocatedCauchyUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
L=(S,D,M,W,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ schedule naming the requested precision windows;
\item $D$ is the displayed family of $\DyadicRatCoreUp$ endpoint rows read on
those windows;
\item $M$ is the $\CauchyModulusUp$ precision row that assigns each requested
precision to a finite observation threshold;
\item $W$ is the family of located dyadic-ball witnesses for each displayed
precision request, with center and radius read from the dyadic endpoint rows;
\item $H$ records componentwise $\hsame$ transport for schedules, endpoint rows,
modulus rows, and located-ball witnesses;
\item $C$ records the $\Cont$ readback routes through which a consumer reaches
finite precision windows, dyadic endpoint rows, modulus rows, and located-ball
witnesses;
\item $P$ is the $\Pkg$ provenance row naming $\DyadicRatCoreUp$,
$\StreamNameUp$, $\CauchyModulusUp$, $\RegSeqRatUp$, and $\RealUp$ as the
dependency anchors;
\item $N$ is the local $\NameCert_{\LocatedCauchyUp}$ provenance row.
\end{enumerate}
The carrier predicate is
$\mathsf{LocatedCauchyPacket}(S,D,M,W,H,C,P,N)$. A constant dyadic stream
inhabits the carrier by taking $S$ to repeat one scheduled dyadic endpoint, $M$
to return the same threshold for every requested precision, and $W$ to display
the corresponding degenerate located dyadic ball at each requested window.
\end{definition}

\begin{definition}[LocatedCauchy classifier]
\label{def:locatedcauchy-classifier}
Two accepted $\LocatedCauchyUp$ packets
$L=(S,D,M,W,H,C,P,N)$ and $L'=(S',D',M',W',H',C',P',N')$ are classified alike
when the displayed schedules agree componentwise, the dyadic endpoint rows
agree componentwise, the modulus rows agree on every requested precision
window, the located-ball witnesses agree through their displayed endpoint and
radius rows, the $\hsame$ rows transport those components, the $\Cont$ routes
expose the same finite readback surface, and the $\Pkg$ provenance rows name the
same dependency anchors.

The classifier has no coordinate for host real equality, completed quotient
streams, Dedekind-cut membership, trichotomy, choice-selected representatives,
or open-cover compactness. It compares only the finite located windows and the
provenance rows displayed in
\autoref{def:locatedcauchy-bhist-carrier}.
\end{definition}

\begin{theorem}[LocatedCauchy window stability]
\label{thm:locatedcauchy-window-stability}
Let $L$ be an accepted $\LocatedCauchyUp$ packet. If a requested precision
window is refined through the displayed $\CauchyModulusUp$ row, then the refined
readback still factors through the same $\StreamNameUp$ schedule, the same
family of $\DyadicRatCoreUp$ endpoint rows, and the transported located
dyadic-ball witness family. Thus precision refinement changes only which finite
window is read; it does not expose a completed real value or an unbounded stream
object.
\end{theorem}
\leanchecked{BEDC.Derived.LocatedCauchyUp.LocatedCauchyCarrier\_window\_stability}
\begin{proof}
Project $L$ through \autoref{def:locatedcauchy-bhist-carrier}. The modulus
coordinate $M$ is the only row that answers a precision request, and it answers
by naming a finite observation threshold inside the schedule $S$.

At the refined threshold, the endpoint data are read from $D$ and the located
ball data are read from $W$. The transport coordinate $H$ supplies the
componentwise $\hsame$ rows needed to move these visible rows along an accepted
classifier comparison.

The continuation coordinate $C$ exhausts the readback routes. Since no carrier
coordinate stores a quotient stream, host real, or selected limit, refinement
cannot reveal data outside the displayed finite located window.
\end{proof}

\begin{theorem}[LocatedCauchy NameCert obligation surface]
\label{thm:locatedcauchy-namecert-obligation-surface}
The local $\NameCert_{\LocatedCauchyUp}$ seed surface consists of the following
five rows:
\begin{enumerate}
\item carrier inhabitation by the constant dyadic stream described in
\autoref{def:locatedcauchy-bhist-carrier};
\item classifier reflexivity, symmetry, and transitivity obtained from
componentwise $\hsame$ over schedules, endpoints, modulus rows, located balls,
continuation routes, and package provenance;
\item carrier transport along the classifier rows of
\autoref{def:locatedcauchy-classifier};
\item precision-window stability under modulus refinement as in
\autoref{thm:locatedcauchy-window-stability};
\item $\RealUp$ seal boundary, where consumers see only finite located windows
and the dependency provenance needed to pass toward $\RegSeqRatUp$ and
$\RealUp$.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.LocatedCauchyUp.LocatedCauchyCarrier\_semantic\_name\_certificate}
\begin{proof}
The carrier row is the finite packet displayed in
\autoref{def:locatedcauchy-bhist-carrier}. The constant dyadic stream gives an
inhabited packet because each requested precision reads the same dyadic endpoint
and the same degenerate located ball.

The classifier laws are inherited component by component from the displayed
$\hsame$ rows. Reflexivity uses the identity rows, symmetry reverses each
componentwise comparison, and transitivity composes the visible comparisons on
schedules, endpoints, modulus data, located-ball witnesses, continuation
routes, and provenance.

Transport repacks the carrier coordinates after those classifier comparisons.
Window stability is exactly
\autoref{thm:locatedcauchy-window-stability}, and the final row is the seal
boundary isolated in
\autoref{thm:locatedcauchy-real-seal-boundary}.
\end{proof}

\begin{theorem}[LocatedCauchy real seal boundary]
\label{thm:locatedcauchy-real-seal-boundary}
Every $\RealUp$-facing read exported by an accepted $\LocatedCauchyUp$ packet
factors through a finite requested precision window, its $\CauchyModulusUp$
threshold, the scheduled $\DyadicRatCoreUp$ endpoint rows, and the displayed
located dyadic-ball witness. The packet supplies a constructive real-name
neighbor for $\RegSeqRatUp$ and $\RealUp$ consumers, but it claims no Dedekind
cut, quotient stream, trichotomy principle, choice-selected representative, or
open-cover compactness principle.
\end{theorem}
\leanchecked{BEDC.Derived.LocatedCauchyUp.LocatedCauchyCarrier\_real\_seal\_boundary}
\begin{proof}
Take any consumer route from the packet toward the real seal. By the carrier
definition, every such route is one of the displayed $\Cont$ rows in $C$, and
each route names the precision window it reads.

The precision window is resolved by the modulus row $M$, then by the scheduled
endpoint rows in $D$ and the located-ball witnesses in $W$. These are precisely
the finite rows exposed to $\RegSeqRatUp$ and $\RealUp$ consumers.

The exclusions follow from absence of coordinates. The packet stores no cut
predicate, no quotient-stream equality, no trichotomy witness, no selected
representative, and no open-cover compactness datum, so none of those objects
can be exported through the real-facing readback.
\end{proof}

\begin{theorem}[LocatedCauchy scoped dependency package]
\label{thm:locatedcauchy-scoped-dependency-package}
Any accepted $\LocatedCauchyUp$ packet whose displayed rows satisfy
\autoref{def:locatedcauchy-bhist-carrier},
\autoref{def:locatedcauchy-classifier},
\autoref{thm:locatedcauchy-window-stability},
\autoref{thm:locatedcauchy-namecert-obligation-surface}, and
\autoref{thm:locatedcauchy-real-seal-boundary} determines a scoped dependency
package over $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$,
$\NameCert$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\CauchyModulusUp$,
$\RegSeqRatUp$, and $\RealUp$.

Every $\RealUp$-facing consumer read from that package is exhausted by those
displayed rows. The package cannot export a Dedekind cut, quotient stream,
host real equality, trichotomy, choice data, or open-cover compactness.
\end{theorem}
\leanchecked{BEDC.Derived.LocatedCauchyUp.LocatedCauchyCarrier\_scoped\_dependency\_package}
\begin{proof}
Project the accepted packet through
\autoref{def:locatedcauchy-bhist-carrier}. This exposes the schedule,
dyadic-endpoint rows, modulus row, located-ball witnesses, transport rows,
continuation routes, package provenance, and local name certificate as one
finite $\mathsf{BHist}$ surface.

Use \autoref{def:locatedcauchy-classifier} to transport the exposed rows
componentwise. The classifier compares only the displayed schedules, endpoint
rows, modulus data, located-ball witnesses, continuation routes, and package
provenance, so no external real-equality or quotient coordinate is introduced.

For precision refinement, apply
\autoref{thm:locatedcauchy-window-stability}. It keeps every refined read on
the same scheduled finite window surface and preserves the visible
$\DyadicRatCoreUp$, $\CauchyModulusUp$, and located-ball rows.

The five local certificate rows are exactly the surface named by
\autoref{thm:locatedcauchy-namecert-obligation-surface}. Finally,
\autoref{thm:locatedcauchy-real-seal-boundary} exhausts every $\RealUp$-facing
consumer read by the displayed finite rows, which proves the stated exclusions.
\end{proof}

\begin{theorem}[LocatedCauchy public Real consumer export]
\label{thm:locatedcauchy-public-real-consumer-export}
The public $\LocatedCauchyUp$ export to $\RealUp$ consumers is exactly the finite packet surface consisting of the $\StreamNameUp$ schedule, $\DyadicRatCoreUp$ endpoint rows, $\CauchyModulusUp$ precision row, located dyadic-ball witnesses, componentwise $\hsame$, displayed $\Cont$ routes, $\mathsf{Pkg}$ provenance, and the local $\NameCert$ row.

Every $\RealUp$-facing consumer read is exhausted by that finite packet surface. The export does not supply Dedekind cuts, quotient streams, host real equality, trichotomy, choice data, selected representatives, or open-cover compactness.
\end{theorem}
\begin{proof}
Expose the public surface using \autoref{thm:locatedcauchy-scoped-dependency-package}. It projects an accepted packet to the displayed schedule, dyadic endpoint rows, modulus data, located-ball witnesses, transport rows, continuation routes, package provenance, and local name certificate over the named BEDC components.

For refined consumer reads, apply \autoref{thm:locatedcauchy-window-stability}. Refinement changes only which finite threshold and endpoint rows are read from the same packet; it does not add a quotient stream or completed real object.

Finally use \autoref{thm:locatedcauchy-real-seal-boundary}. That boundary exhausts the $\RealUp$-facing routes by the finite located windows and records the exclusions for Dedekind cuts, quotient streams, host real equality, trichotomy, choice data, selected representatives, and open-cover compactness.
\end{proof}

\begin{theorem}[LocatedCauchy finite-window bridge boundary]
\label{thm:locatedcauchy-finite-window-bridge-boundary}
Every $\RealUp$-facing read of an accepted $\LocatedCauchyUp$ packet factors through exactly the finite $\StreamNameUp$ schedule, $\CauchyModulusUp$ threshold, $\DyadicRatCoreUp$ endpoint rows, located dyadic-ball witnesses, componentwise $\hsame$, displayed $\Cont$ routes, $\mathsf{Pkg}$ provenance, and local $\NameCert$ rows of the packet.

Conversely, every displayed finite window accepted by the carrier is exported by \autoref{thm:locatedcauchy-public-real-consumer-export}. The boundary exports no Dedekind cut, quotient stream, host real equality, trichotomy, choice datum, selected representative, or open-cover compactness witness.
\end{theorem}
\leanchecked{BEDC.Derived.LocatedCauchyUp.LocatedCauchyCarrier\_finite\_window\_bridge\_boundary}
\begin{proof}
Project the accepted packet through
\autoref{def:locatedcauchy-bhist-carrier}. This gives the finite schedule,
modulus threshold, endpoint rows, located-ball witnesses, transport routes,
package provenance, and local name-certificate rows.

Use \autoref{def:locatedcauchy-classifier} to identify consumer reads only
componentwise through the displayed rows. Then apply
\autoref{thm:locatedcauchy-window-stability}; a refined read stays on a finite
scheduled window and changes neither the carrier nor the visible dependency
surface.

Next apply \autoref{thm:locatedcauchy-real-seal-boundary} and
\autoref{thm:locatedcauchy-scoped-dependency-package}. These results bind the
finite located-Cauchy window to the scoped dependency package over
$\DyadicRatCoreUp$, $\StreamNameUp$, $\CauchyModulusUp$, $\RegSeqRatUp$, and
$\RealUp$.

For the reverse direction, an accepted displayed finite window is already one
of the public packet windows. Therefore
\autoref{thm:locatedcauchy-public-real-consumer-export} exports exactly that
window to $\RealUp$ consumers and supplies no additional row.
\end{proof}

\closureat{LocatedCauchyUp}{seedStr}
\closureat{LocatedCauchyUp}{obligationStr}
\closureat{LocatedCauchyUp}{scopedStr}
\closureat{LocatedCauchyUp}{publicStr}

\begin{closurestatus}{\LocatedCauchyUp}
  \constructivestory{A $\LocatedCauchyUp$ packet is generated from a finite StreamName schedule, DyadicRatCore endpoint rows, a CauchyModulus precision row, located dyadic-ball witnesses, componentwise transport rows, continuation readback routes, package provenance for DyadicRatCoreUp, StreamNameUp, CauchyModulusUp, RegSeqRatUp, and RealUp, and a local NameCert provenance row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{thm:locatedcauchy-scoped-dependency-package} and \autoref{thm:locatedcauchy-public-real-consumer-export} bind the scoped package and public $\RealUp$ consumer export over $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, $\NameCert$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\CauchyModulusUp$, $\RegSeqRatUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Dedekind cuts, quotient streams, host real equality, trichotomy, choice, open-cover compactness, or a standard bridge.}
  \upgradepath{Bridged closure requires a standard located-Cauchy finite-packet bridge for the public $\RealUp$ consumer export.}
\end{closurestatus}

\begin{theorem}[LocatedCauchy constant window degeneracy]
\label{thm:locatedcauchy-constant-window-degeneracy}
Let $L=(S,D,M,W,H,C,P,N)$ be the constant dyadic-stream $\LocatedCauchyUp$ carrier described in \autoref{def:locatedcauchy-bhist-carrier}. Thus there is one displayed dyadic endpoint row $d$ such that $S$ repeats the scheduled endpoint $d$, the modulus row $M$ returns the same observation threshold for every requested precision, and $W$ displays the degenerate located dyadic ball attached to $d$ at each requested window.

Then every consumer-visible precision request for $L$ reads the same degenerate dyadic endpoint. More precisely, for any requested precision window $q$, the $\Cont$ readback route selected by $C$ factors through the $\StreamNameUp$ row that schedules $d$, the $\CauchyModulusUp$ row that returns the constant threshold, the $\DyadicRatCoreUp$ endpoint row $d$, and the located-ball witness in $W$ whose left endpoint, center endpoint, and right endpoint are all the displayed row $d$. Hence the classifier of \autoref{def:locatedcauchy-classifier} sees no window-dependent endpoint variation in the constant packet: changing $q$ changes only the name of the finite request, not the dyadic endpoint or the degenerate located ball read at that request.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{def:locatedcauchy-bhist-carrier}. The constant-stream clause fixes the visible coordinates: the schedule $S$ repeats one scheduled dyadic endpoint row $d$, the modulus row $M$ returns the same threshold for each requested precision, and the witness family $W$ assigns to each requested window the degenerate located dyadic ball corresponding to that same endpoint.

Let $q$ be a requested precision window. The only route from a consumer request to packet data is one of the continuation rows recorded in $C$. By the carrier definition, such a route first reads the requested window through $S$ and $M$, then reads the endpoint data from $D$, and then reads the located-ball witness from $W$. Since $S$ is constant and $M$ returns the fixed threshold, this route reaches the same scheduled endpoint row $d$ for the request $q$ as for any other request.

At that row, $D$ is the displayed $\DyadicRatCoreUp$ endpoint family of the packet, and the constant-stream clause says that the located witness attached by $W$ is degenerate at $d$. Thus the left endpoint, center endpoint, and right endpoint exposed by the located dyadic ball are all the same displayed dyadic row $d$.

Finally, \autoref{def:locatedcauchy-classifier} compares only the displayed schedules, endpoint rows, modulus rows, located-ball witnesses, transport rows, continuation routes, and provenance. None of those coordinates contains a second endpoint for the constant packet, so a change of requested precision window cannot introduce endpoint variation. It only selects another finite request whose readback again reaches the same degenerate dyadic ball at $d$.
\end{proof}
