\chapter{A Concrete Naming Certificate for $\GroundCompilerRecognizerFlowUp$}
\label{ch:concrete-instances-groundcompilerrecognizerflow-namecert}
\origin{ai}

The $\GroundCompilerRecognizerFlowUp$ packet realizes the generated-recognizer route of \autoref{ch:bedc-groundcompiler-audit-map} as a finite NameCert carrier. It sits beside the event-flow route of \autoref{ch:concrete-instances-groundcompilereventflowauditroute-namecert}, the audit-map packet of \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, and the recognizer audit packet of \autoref{ch:concrete-instances-groundcompilerrecognizerauditpacket-namecert}: those siblings display event-flow routing, compiler audit inventory, and recognizer-facing audit rows, while this chapter binds the source channel, generated recognizer, certificate gate, and non-evidence refusal as one consumer packet.

\begin{definition}[GroundCompiler recognizer-flow carrier]
\label{def:groundcompiler-recognizer-flow-carrier}
A $\GroundCompilerRecognizerFlowUp$ carrier is a finite $\BHist$ packet
$$
G=(E,S,R,Q,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the event-flow row naming the formal GroundCompiler event packet under inspection;
\item $S$ is the source-channel row recording the legal channel encoding, decoder address, and lossless readback route for $E$;
\item $R$ is the generated-recognizer row recording package recognition, local certificate recognition, derivation-certificate recognition, theorem-identifier recognition, chapter-flow recognition, and accepted-export recognition;
\item $Q$ is the certificate-gate row through which an accepted generated recognizer result may be read as GroundCompiler evidence;
\item $B$ is the non-evidence row separating source text, carried metadata, metric reports, motif reports, compiler reports, proof text, host compiler state, and raw classifier quotients from certificate evidence;
\item $H$ records componentwise $\hsame$ transports for event-flow, source-channel, generated-recognizer, certificate-gate, non-evidence, continuation, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ routes from event flow to source channel, from source-channel readback to generated recognition, from generated recognition to certificate gate, from excluded report-like objects to non-evidence, and from the accepted packet to downstream consumers;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:bedc-groundcompiler-audit-map}, \autoref{ch:concrete-instances-groundcompilereventflowauditroute-namecert}, \autoref{ch:concrete-instances-groundcompilerauditmap-namecert}, \autoref{ch:concrete-instances-groundcompilerrecognizerauditpacket-namecert}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\GroundCompilerRecognizerFlowUp}$ row.
\end{enumerate}
The classifier for accepted carriers compares exactly the displayed coordinates $E,S,R,Q,B,H,C,P,N$. It has no coordinate for hidden compiler input, proof reconstructed from source text, metric evidence, motif identity, report evidence, raw classifier equality, or an unmediated generated export.
\end{definition}
\leanchecked{BEDC.Derived.GroundCompilerRecognizerFlowUp.GroundCompilerRecognizerFlowTasteGate\_single\_carrier\_alignment}

\begin{theorem}[GroundCompiler recognizer-flow NameCert obligations]
\label{thm:groundcompiler-recognizer-flow-namecert-obligations}
For every accepted $\GroundCompilerRecognizerFlowUp$ carrier
$$
G=(E,S,R,Q,B,H,C,P,N),
$$
the local $\NameCert_{\GroundCompilerRecognizerFlowUp}$ surface consists exactly of event-flow readback through $E$, source-channel lossless routing through $S$, generated-recognizer mediation through $R$, certificate-gate acceptance through $Q$, non-evidence refusal through $B$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $E,S,R,Q,B$ are the public data coordinates, and $H,C,P,N$ transport, route, locate, and name those same coordinates.

Read the route in order. The event-flow row supplies the formal input, the source-channel row supplies legal encoding and lossless readback, the generated-recognizer row mediates recognition of packages and certificate-like compiler exports, and the certificate-gate row is the only positive acceptance point.

The non-evidence row records every excluded channel: source text, carried metadata, metric reports, motif reports, compiler reports, proof text, host state, and raw classifier quotients. Since no carrier coordinate converts $B$ into $E$, $S$, $R$, $Q$, or proof evidence, the displayed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[GroundCompiler recognizer-flow certificate-gate exactness]
\label{thm:groundcompiler-recognizer-flow-certificate-gate-exactness}
Every accepted $\GroundCompilerRecognizerFlowUp$ export that reaches the certificate gate $Q$ first passes through the displayed event-flow row $E$, source-channel row $S$, and generated-recognizer row $R$. An export that omits the generated recognizer row cannot be read as accepted GroundCompiler evidence by $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, or the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Start with the carrier classifier of \autoref{def:groundcompiler-recognizer-flow-carrier}. A certificate-facing read is accepted only when it compares the displayed coordinates $E,S,R,Q,B,H,C,P,N$.

Apply the NameCert obligation surface of \autoref{thm:groundcompiler-recognizer-flow-namecert-obligations}. It orders the positive route through event flow, source channel, generated recognizer, and certificate gate, so $Q$ is not reachable as a standalone export coordinate.

Finally inspect the structural rows. Transport, continuation, provenance, and local naming preserve the same packet, but none supplies a replacement for $R$. Therefore a compiler export without the generated-recognizer row is outside the accepted GroundCompiler evidence route.
\end{proof}

\begin{theorem}[GroundCompiler recognizer-flow non-evidence refusal]
\label{thm:groundcompiler-recognizer-flow-non-evidence-refusal}
For every accepted $\GroundCompilerRecognizerFlowUp$ carrier, source text, carried metadata, metric reports, motif reports, compiler reports, proof text, host compiler state, and raw classifier quotients can be read only through the non-evidence row $B$. They cannot become event-flow input, source-channel readback, generated-recognizer evidence, certificate-gate evidence, or BEDC proof evidence inside the packet.
\end{theorem}
\begin{proof}
Project the packet and isolate $B$. It is the only coordinate assigned to report-like, host-like, text-like, metric, motif, and quotient objects.

Use certificate-gate exactness. Any route to accepted GroundCompiler evidence has already passed through $E,S,R,Q$, so it cannot start from an object classified only by $B$.

The remaining rows $H,C,P,N$ preserve and replay displayed coordinates. They do not add a constructor from non-evidence to event flow, channel readback, generated recognition, certificate evidence, or proof evidence, so the refusal row is stable under every public consumer read.
\end{proof}

\begin{theorem}[GroundCompiler recognizer-flow TasteGate carrier readback]
\label{thm:groundcompiler-recognizer-flow-tastegate-carrier-readback}
For every displayed $\GroundCompilerRecognizerFlowUp$ packet
$$
G=(E,S,R,Q,B,H,C,P,N),
$$
the TasteGate row for $\mathsf{BEDC.Derived.GroundCompilerRecognizerFlowUp}$ reads the single carrier through exactly the same event-flow, source-channel, generated-recognizer, certificate-gate, non-evidence, transport, continuation, provenance, and local naming coordinates. A TasteGate consumer cannot replace $G$ by a hidden compiler input, raw recognizer quotient, proof text, metric report, motif report, or unmediated generated export.
\end{theorem}
\leanchecked{BEDC.Derived.GroundCompilerRecognizerFlowUp.taste\_gate}
\begin{proof}
Start from the carrier definition. The packet has exactly the displayed rows $E,S,R,Q,B,H,C,P,N$, and the classifier compares only those rows.

Apply the existing single-carrier TasteGate alignment named by the Lean surface. It makes the TasteGate entry a readback of the same finite carrier rather than a second carrier with extra compiler-facing coordinates.

Finally use the non-evidence refusal row. Objects such as proof text, reports, motifs, raw quotients, and unmediated exports are recorded only at $B$, so the TasteGate read cannot promote them into the positive carrier route.
\end{proof}

\begin{theorem}[GroundCompiler recognizer-flow field-faithful row projection]
\label{thm:groundcompiler-recognizer-flow-field-faithful-readback}
For every accepted $\GroundCompilerRecognizerFlowUp$ packet $G=(E,S,R,Q,B,H,C,P,N)$, the field-faithful projection of the TasteGate surface is componentwise: $E$ remains the event-flow row, $S$ the source-channel row, $R$ the generated-recognizer row, $Q$ the certificate-gate row, $B$ the non-evidence row, $H$ the $\hsame$ transport row, $C$ the $\Cont$ replay row, $P$ the $\Pkg$ provenance row, and $N$ the local $\NameCert_{\GroundCompilerRecognizerFlowUp}$ row.
\end{theorem}
\begin{proof}
Project the accepted packet and keep the row order fixed. Field faithfulness can only report the fields already exposed by the carrier and by the NameCert obligation surface.

The positive route rows $E,S,R,Q$ are separated from the refusal row $B$, while $H,C,P,N$ are structural rows attached to the same carrier. No projection step has a coordinate from which to synthesize a compiler proof, hidden recognizer state, or report-like witness.

Thus the TasteGate field readback is exactly componentwise over $E,S,R,Q,B,H,C,P,N$.
\end{proof}

\begin{theorem}[GroundCompiler recognizer-flow nontrivial witness boundary]
\label{thm:groundcompiler-recognizer-flow-nontrivial-witness-boundary}
The nontrivial witness for $\GroundCompilerRecognizerFlowUp$ separates an accepted recognizer-flow packet from every packet that omits one of $E,S,R,Q,B,H,C,P,N$ or tries to identify the non-evidence row $B$ with event-flow, source-channel, generated-recognizer, certificate-gate, or proof-evidence data. The separation is witnessed inside the finite carrier rows and does not assert compiler correctness, self-hosting, or proof reconstruction.
\end{theorem}
\begin{proof}
Use the carrier inventory to compare two candidate packets. A packet missing any one of the displayed coordinates cannot satisfy the same row-by-row classifier as $G$.

For the positive evidence route, apply certificate-gate exactness. Accepted evidence must pass through $E,S,R,Q$, and none of the structural rows replaces a missing generated-recognizer or certificate-gate coordinate.

For the boundary side, apply non-evidence refusal. The row $B$ is stable under transport, continuation, provenance, and local naming, so it remains separated from evidence and proof rows. This gives a finite nontrivial witness boundary without importing compiler correctness or proof reconstruction.
\end{proof}

\falsifiablePrediction{A compiler export that omits the generated recognizer row cannot pass the certificate gate as accepted GroundCompiler evidence.}

\independenceWitness{groundcompilereventflowaudit, groundcompilerauditmap, auditmapfamily, auditmapcoverageledger, namecertgenerated: event-flow audit lacks generated-recognizer mediation, audit-map packets lack the certificate-gate row, audit families lack source-channel lossless routing, coverage ledgers lack the non-evidence refusal row, and NameCert-generated surfaces do not carry the compiler recognizer flow as a single packet.}

The Lean TasteGate follow-up for $\mathsf{BEDC.Derived.GroundCompilerRecognizerFlowUp}$ must provide $\mathsf{Nontrivial}\ \GroundCompilerRecognizerFlowUp$ and $\mathsf{FieldFaithful}\ \GroundCompilerRecognizerFlowUp$ instances for the displayed carrier $E,S,R,Q,B,H,C,P,N$.

\closureat{GroundCompilerRecognizerFlowUp}{seedStr}
\closureat{GroundCompilerRecognizerFlowUp}{obligationStr}
\closureat{GroundCompilerRecognizerFlowUp}{scopedStr}[BEDC.Derived.GroundCompilerRecognizerFlowUp.GroundCompilerRecognizerFlowTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\GroundCompilerRecognizerFlowUp}
  \constructivestory{A $\GroundCompilerRecognizerFlowUp$ packet is generated from event-flow, source-channel, generated-recognizer, certificate-gate, non-evidence, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows; the TasteGate row is recorded at BEDC.Derived.GroundCompilerRecognizerFlowUp.taste\_gate.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:groundcompiler-recognizer-flow-carrier}, \autoref{thm:groundcompiler-recognizer-flow-namecert-obligations}, \autoref{thm:groundcompiler-recognizer-flow-certificate-gate-exactness}, \autoref{thm:groundcompiler-recognizer-flow-non-evidence-refusal}, \autoref{thm:groundcompiler-recognizer-flow-tastegate-carrier-readback}, \autoref{thm:groundcompiler-recognizer-flow-field-faithful-readback}, and \autoref{thm:groundcompiler-recognizer-flow-nontrivial-witness-boundary} bind the finite GroundCompiler recognizer-flow carrier, TasteGate carrier readback, field-faithful projection, nontrivial witness boundary, certificate-gate exactness, and non-evidence refusal.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.GroundCompilerRecognizerFlowUp.GroundCompilerRecognizerFlowTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close compiler correctness, self-hosting coverage, proof reconstruction from source text, metric evidence, motif evidence, report evidence, audit cleanliness, or bridge checking.}
  \upgradepath{The next paper-axis step is a public export statement over the same event-flow, source-channel, generated-recognizer, certificate-gate, non-evidence, transport, route, provenance, and NameCert rows.}
\end{closurestatus}
