\chapter{A Concrete Naming Certificate for $\ObserverFilterBudgetSelectorUp$}
\label{ch:concrete-instances-observer-filter-budget-selector-namecert}
\origin{ai}

The $\ObserverFilterBudgetSelectorUp$ packet realizes observer-history identity as a finite selected-row budget feeding the StreamName and Real-completion observation routes. It consumes the selected and omitted rows of \autoref{ch:concrete-instances-observer-filter-namecert}, the observer-history source of \autoref{ch:concrete-instances-observerhistoryidentity-namecert}, the finite StreamName window route of \autoref{ch:concrete-instances-streamname-namecert}, and the L10 budget selector of \autoref{ch:concrete-instances-finiteobservationbudgetselector-namecert}. Its role is to bind those routes into one local NameCert packet, not to create a quotient stream, host real equality, selected host limit, or hidden observation selector.

\falsifiablePrediction{A packet with a finite observation budget but no selected ObserverFilter row is rejected by the local classifier.}

\independenceWitness{observerfilter, finiteobservationbudgetselector, observerhistoryidentity, streamname, real: no sibling is bijective because none carries selected and omitted observer rows together with a finite L10 observation budget and Real-seal handoff.}

\begin{definition}[Observer-filter budget-selector carrier]
\label{def:observer-filter-budget-selector-carrier}
An $\ObserverFilterBudgetSelectorUp$ carrier is a finite $\BHist$ packet
$$
G=(F,I,S,O,B,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is an accepted $\ObserverFilterUp$ packet with selected subhistory row $S$ and omitted-row ledger $O$;
\item $I$ is the $\ObserverHistoryIdentityUp$ source row factored by the observer filter;
\item $B$ is an accepted $\FiniteObservationBudgetSelectorUp$ row whose selected schedule reads only from $S$;
\item $W$ is the finite $\StreamNameUp$ window family selected from that schedule;
\item $D$ is the $\DyadicRatCoreUp$ ledger read from the finite windows in $W$;
\item $R$ is the $\RegSeqRatUp$ handoff row reached after the dyadic ledger;
\item $E$ is the $\RealUp$ seal row exposed only after the displayed budget route;
\item $H$ records componentwise $\hsame$ transports for the observer-filter, identity, selected row, omitted ledger, budget, window, dyadic, handoff, seal, provenance, and local name rows;
\item $C$ records the displayed $\Cont$ routes from $I$ to $F$, from $S$ to $B$, from $B$ to $W$, from $W$ to $D$, from $D$ to $R$, and from $R$ to $E$;
\item $P$ is the $\Pkg$ provenance over $\ObserverHistoryIdentityUp$, $\ObserverFilterUp$, $\StreamNameUp$, $\FiniteObservationBudgetSelectorUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ObserverFilterBudgetSelectorUp}$ row.
\end{enumerate}
The classifier accepts $G$ only when the budget row $B$ reads from the selected row $S$ of $F$ and the omitted ledger $O$ remains a boundary row. The carrier has no coordinate for a finite budget without an observer-filter selection, an omitted-row observation window, quotient streams, host real equality, countable choice, hidden limit selectors, or ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Observer-filter budget-selector NameCert surface]
\label{thm:observer-filter-budget-selector-namecert-surface}
For the carrier of \autoref{def:observer-filter-budget-selector-carrier}, the local $\NameCert_{\ObserverFilterBudgetSelectorUp}$ surface consists exactly of carrier admission for $G=(F,I,S,O,B,W,D,R,E,H,C,P,N)$, observer-history factorization through $I$ and $F$, selected-row budget admission through $S$ and $B$, StreamName window exposure through $W$, dyadic ledger exposure through $D$, $\RegSeqRatUp$ handoff through $R$, $\RealUp$ seal exposure through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, local naming through $N$, and non-escape for omitted rows in $O$.
\end{theorem}
\begin{proof}
Project the carrier. The displayed packet contains the observer-history row, observer filter, selected and omitted rows, budget selector, finite windows, dyadic ledger, regular handoff, Real seal, and the four structural rows $H,C,P,N$.

Read the positive route in order. The observer-history row $I$ is first consumed by the observer filter $F$; the selected subhistory $S$ then supplies the only schedule source for $B$; the budget selector exposes the finite windows $W$ before the dyadic ledger $D$, handoff row $R$, and seal row $E$ are available.

The omitted ledger is checked by coordinate exhaustion. It appears as $O$ and nowhere as $B$, $W$, $D$, $R$, or $E$. Since the carrier also omits quotient streams, host real equality, countable choice, hidden selectors, and ambient completeness, the listed rows exhaust the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorNameCertSurface\_omitted\_field\_empty\_reflects}

\begin{theorem}[Observer-filter budget-selector StreamName handoff]
\label{thm:observer-filter-budget-selector-streamname-handoff}
Every accepted $\ObserverFilterBudgetSelectorUp$ packet routes its finite observation budget through the selected ObserverFilter row before any $\StreamNameUp$ window is available:
$$
I \to F \to S \to B \to W \to D \to R \to E.
$$
The omitted ledger $O$ may be read only as boundary data through $H,C,P,N$; it cannot supply StreamName windows, dyadic observations, $\RegSeqRatUp$ handoff rows, $\RealUp$ seals, quotient streams, host real equality rows, or hidden limit selectors.
\end{theorem}
\begin{proof}
Start with the NameCert surface theorem. It identifies the accepted packet with $G=(F,I,S,O,B,W,D,R,E,H,C,P,N)$ and places the budget selector after the selected row $S$.

Apply the ObserverFilter L10 handoff of \autoref{thm:observer-filter-budget-selector-l10-handoff}. That handoff forces every budget-selector route whose schedule reads from $S$ through the chain from observer-history identity to observer filter, StreamName, and the finite observation-budget selector.

The remaining coordinates are the budget-selector continuation. The route from $B$ to $W,D,R,E$ is the finite observation route, while $H,C,P,N$ only transport, replay, package, and name the same packet.

Thus the public handoff is exactly the displayed finite route. Because $O$ is not a selected row or budget coordinate, no omitted row can become any of the named observation, completion, equality, or selector objects.
\end{proof}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorStreamNameHandoff\_omitted\_boundary\_not\_erased}

\begin{theorem}[Observer-filter budget-selector omitted-row exclusion]
\label{thm:observer-filter-budget-selector-omitted-row-exclusion}
For every accepted $\ObserverFilterBudgetSelectorUp$ packet
$$
G=(F,I,S,O,B,W,D,R,E,H,C,P,N),
$$
any consumer that reaches one of $B,W,D,R,E$ factors through the selected row $S$. The omitted ledger $O$ may be read only through the boundary rows $H,C,P,N$ and cannot be repacked as an observation window, dyadic ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, quotient stream, host equality row, hidden limit selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the carrier definition for $G$. The positive observation coordinates are $I,F,S,B,W,D,R,E$, while the omitted ledger occurs only as the displayed row $O$ together with the structural rows $H,C,P,N$.

Apply \autoref{thm:observer-filter-budget-selector-namecert-surface}. It identifies $O$ as boundary-only data and places carrier admission, continuation replay, provenance, and local naming in the rows $H,C,P,N$ rather than in the observation route.

Apply \autoref{thm:observer-filter-budget-selector-streamname-handoff}. The handoff forces every consumer reaching the budget, window, dyadic, regular-sequence, or Real-seal coordinates through
$$
I \to F \to S \to B \to W \to D \to R \to E.
$$

It remains to exhaust the packet coordinates. There is no carrier slot in which $O$ can appear as $B$, $W$, $D$, $R$, $E$, a quotient stream, host equality row, hidden limit selector, or ambient completeness row, so the omitted ledger cannot be repacked as any such consumer-facing object.
\end{proof}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorOmittedRowExclusion\_omitted\_boundary\_not\_repacked}

\begin{theorem}[Observer-filter budget selector selected-row gate]
\label{thm:observer-filter-budget-selector-selected-row-gate}
Every accepted $\ObserverFilterBudgetSelectorUp$ packet
$$
G=(F,I,S,O,B,W,D,R,E,H,C,P,N)
$$
must expose the selected $\ObserverFilterUp$ row $S$ before any finite budget row $B$, $\StreamNameUp$ window family $W$, dyadic ledger $D$, $\RegSeqRatUp$ handoff $R$, or $\RealUp$ seal row $E$ can be consumed. The omitted rows $O$ remain ledger data through $H,C,P,N$ and cannot feed the selected schedule, quotient streams, host real equality, or hidden observation selectors.
\end{theorem}
\begin{proof}
Project the carrier $G$. The positive route records $I,F,S,B,W,D,R,E$ in that order, while $O$ is a separate omitted-row ledger and $H,C,P,N$ are the transport, continuation, provenance, and local naming rows.

Apply the local NameCert surface. It admits the budget row only as the row whose selected schedule reads from $S$, and it places the StreamName, dyadic, regular-sequence, and Real-seal rows after that budget row.

Now use omitted-row exclusion from \autoref{thm:observer-filter-budget-selector-omitted-row-exclusion}. Since every consumer of $B,W,D,R,E$ factors through the selected row and since $O$ cannot be repacked as one of those consumer-facing coordinates, the selected-row gate is the only entry to the finite observation route.

The remaining excluded objects follow by coordinate exhaustion. The carrier has no row for quotient streams, host real equality, or hidden observation selectors, so none of them can bypass $S$ or make the omitted ledger into a schedule source.
\end{proof}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorSelectedRowGate\_selected\_field\_not\_erased}

\begin{theorem}[Observer-filter budget-selector budget refinement nonescape]
\label{thm:observer-filter-budget-selector-budget-refinement-nonescape}
Let
$$
G=(F,I,S,O,B,W,D,R,E,H,C,P,N)
$$
be an accepted $\ObserverFilterBudgetSelectorUp$ packet. Any finite-budget refinement that replaces $B$ by a row $B^\sharp$ while preserving the selected $\ObserverFilterUp$ row $S$ and the $\StreamNameUp$ window family $W$ preserves the downstream route
$$
I \to F \to S \to B^\sharp \to W \to D \to R \to E.
$$
Such a refinement cannot turn omitted ledger data $O$ into a window, dyadic ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, quotient stream, host real equality row, hidden limit selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the carrier definition for $G$. Its positive observation coordinates are the displayed rows $I,F,S,B,W,D,R,E$, while $O$ appears as an omitted ledger and $H,C,P,N$ provide boundary transport, continuation, provenance, and local naming.

Apply \autoref{thm:observer-filter-budget-selector-selected-row-gate}. The gate forces any consumer of the finite budget row, window family, dyadic ledger, regular-sequence handoff, or Real seal to enter through $S$; replacing $B$ by a refinement that preserves $S$ and $W$ therefore leaves the consumer route through the selected row.

Apply \autoref{thm:observer-filter-budget-selector-omitted-row-exclusion}. The omitted ledger remains boundary-only data, so the refinement has no source from which to manufacture a consumer-facing row out of $O$.

It remains to exhaust the coordinates before dyadic readback consumes $D$. The packet has no slot in which $O$ can become $W,D,R,E$, a quotient stream, a host real equality row, a hidden limit selector, or an ambient completeness row; hence the refined budget still feeds exactly the displayed route.
\end{proof}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorBudgetRefinementNonescape\_budget\_field\_not\_erased}

\begin{theorem}[Observer-filter budget-selector dyadic readback exactness]
\label{thm:observer-filter-budget-selector-dyadic-readback-exactness}
Every accepted $\ObserverFilterBudgetSelectorUp$ packet reads the $\DyadicRatCoreUp$ row $D$ only after the selected $\ObserverFilterUp$ row $S$, finite budget row $B$, and $\StreamNameUp$ window family $W$ have been exposed in the displayed route
$$
I \to F \to S \to B \to W \to D.
$$
The readback cannot replace $D$ by omitted-row data from $O$, quotient streams, host real equality, or hidden limit selectors.
\end{theorem}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorDyadicReadbackExactness\_dyadic\_field\_not\_erased}
\begin{proof}
Start with the accepted carrier $G=(F,I,S,O,B,W,D,R,E,H,C,P,N)$. The carrier definition places $D$ after $W$, and the StreamName handoff theorem places $W$ after the selected-row budget route through $S$ and $B$.

Apply \autoref{thm:observer-filter-budget-selector-namecert-surface}. It identifies the $\DyadicRatCoreUp$ exposure as the named row $D$ and keeps the omitted ledger $O$ outside the positive observation route.

Finally use coordinate exhaustion. The carrier has no coordinate for quotient streams, host real equality, or hidden limit selectors, so the only dyadic readback available to the packet is the displayed row reached through $I,F,S,B,W$.
\end{proof}

\begin{theorem}[Observer-filter budget-selector Real-seal terminality]
\label{thm:observer-filter-budget-selector-real-seal-terminality}
Every terminal $\RealUp$ seal read of an accepted $\ObserverFilterBudgetSelectorUp$ packet factors through
$$
I \to F \to S \to B \to W \to D \to R \to E,
$$
with the omitted row $O$ serving only as a boundary ledger. No terminal read may bypass the selected observer-filter budget route or use $O$ as a Real-seal source.
\end{theorem}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorRealSealTerminality\_terminal\_field\_not\_erased}
\begin{proof}
The StreamName handoff theorem gives the positive route from $I$ through $F,S,B,W,D,R,E$. This already places the terminal Real seal after the finite budget windows and the dyadic and regular-sequence rows.

The dyadic readback exactness theorem pins the $D$ row to the selected observer-filter budget route. Therefore the following $R$ and $E$ reads inherit the same selected-row dependency rather than a separate omitted-row or host-real source.

The omitted ledger remains boundary data because it is listed only as $O$ and transported by $H,C,P,N$. Since the carrier excludes quotient streams, host real equality, selected host limits, and hidden limit selectors, every terminal Real-seal read factors through the displayed route.
\end{proof}

\begin{theorem}[Observer-filter budget-selector bridge-ready route]
\label{thm:observer-filter-budget-selector-bridge-ready-route}
Every accepted $\ObserverFilterBudgetSelectorUp$ packet exposes the exact bridge-ready selected-row chain
$$
I \to F \to S \to B \to W \to D \to R \to E.
$$
The rows $O,H,C,P,N$ are retained only as omitted-row boundary data, componentwise transport, displayed route replay, provenance, and local naming. In particular, the L10 budget route from \autoref{ch:concrete-instances-observerhistoryidentity-namecert}, \autoref{ch:concrete-instances-observer-filter-namecert}, \autoref{ch:concrete-instances-finiteobservationbudgetselector-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, and the dyadic-to-Real chapters is presented as one public route rather than as separable packet facts.
\end{theorem}
\leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorBridgeReadyRoute\_support\_fields\_faithful}
\begin{proof}
Begin with \autoref{thm:observer-filter-budget-selector-namecert-surface}. It identifies the accepted packet as $G=(F,I,S,O,B,W,D,R,E,H,C,P,N)$ and fixes the NameCert surface over the selected-row budget carrier.

Next use \autoref{thm:observer-filter-budget-selector-streamname-handoff}. This supplies the L10 route through $I,F,S,B,W$ and keeps $O$ outside the StreamName window source.

The dyadic and terminal components are then forced by \autoref{thm:observer-filter-budget-selector-dyadic-readback-exactness} and \autoref{thm:observer-filter-budget-selector-real-seal-terminality}. The first pins $D$ to the selected-row finite-window readback, and the second makes $E$ terminal only after $R$.

It remains to account for the remaining coordinates. The carrier definition assigns $H$ to $\hsame$ transport, $C$ to $\Cont$ replay, $P$ to $\Pkg$ provenance, and $N$ to the local $\NameCert$ row, so none of them can become an additional observation or completion source. The displayed chain is therefore the bridge-ready route exported by the packet.
\end{proof}

\begin{theorem}[Observer-filter budget-selector bridge boundary locality]
\label{thm:observer-filter-budget-selector-locality-bridge-boundary}
The bridge-ready route of \autoref{thm:observer-filter-budget-selector-bridge-ready-route} is local to $\ObserverHistoryIdentityUp$, $\ObserverFilterUp$, $\FiniteObservationBudgetSelectorUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It exports no quotient stream, host real equality, countable choice selector, hidden limit selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the carrier coordinates. The positive rows are exactly $I,F,S,B,W,D,R,E$, and each one belongs to one of the named source chapters or kernel rows.

Now project the structural coordinates. The rows $H,C,P,N$ provide only transport, route replay, provenance, and local naming for the same packet. The omitted ledger $O$ is held as boundary data and is not a source for $B,W,D,R$, or $E$.

Coordinate exhaustion gives the exclusion claim. The carrier definition contains no coordinate for quotient streams, host real equality, countable choice selectors, hidden limit selectors, or ambient completeness; hence the public bridge boundary cannot export any such row.
\end{proof}

\begin{theorem}[Observer-filter budget-selector Real-completion consumer]
\label{thm:observer-filter-budget-selector-real-completion-consumer}
Any Real and Completion consumer reading an accepted $\ObserverFilterBudgetSelectorUp$ packet must pass through the selected observer row $S$, finite budget row $B$, $\StreamNameUp$ window row $W$, $\DyadicRatCoreUp$ ledger row $D$, $\RegSeqRatUp$ handoff row $R$, and $\RealUp$ seal row $E$ before the read can be used by a $\CauchyLimitSealUp$ or $\RealCompletionSelectorSealUp$ packet. The structural rows $O,H,C,P,N$ remain omitted-row boundary data, componentwise transport, displayed replay, provenance, and local naming for the same route.
\end{theorem}
\begin{proof}
Begin with the bridge-ready route of \autoref{thm:observer-filter-budget-selector-bridge-ready-route}. It exposes the selected-row chain
$$
I \to F \to S \to B \to W \to D \to R \to E
$$
as the public route available to a Real and Completion consumer.

The terminality theorem \autoref{thm:observer-filter-budget-selector-real-seal-terminality} makes the final $\RealUp$ read depend on the preceding selected row, budget, window, dyadic ledger, and regular-sequence handoff. Thus a downstream $\CauchyLimitSealUp$ or $\RealCompletionSelectorSealUp$ consumer cannot start at $E$ alone.

The sibling L10 handoff rows already cited in the chapter provide the source side of the same route: observer-history identity feeds the selected observer row, the finite observation-budget selector supplies $B$, and the StreamName chapter supplies $W$. Since the carrier has no coordinate for quotient streams, host real equality, selected host limits, hidden limit selectors, or ambient completeness, the listed chain is the only Real-completion consumer route exported by the packet.
\end{proof}

The Lean file \texttt{Derived/ObserverFilterBudgetSelectorUp/TasteGate.lean} will provide $\mathsf{Nontrivial}\ \ObserverFilterBudgetSelectorUp$ and $\mathsf{FieldFaithful}\ \ObserverFilterBudgetSelectorUp$ instances over the displayed rows.

\closureat{ObserverFilterBudgetSelectorUp}{seedStr}
\closureat{ObserverFilterBudgetSelectorUp}{obligationStr}[BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorTasteGate\_single\_carrier\_alignment]
\closureat{ObserverFilterBudgetSelectorUp}{bridgedStr}[BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorTasteGate\_single\_carrier\_alignment]
\closureat{ObserverFilterBudgetSelectorUp}{matureStr}[BEDC.Derived.ObserverFilterBudgetSelectorUp.ObserverFilterBudgetSelectorTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\ObserverFilterBudgetSelectorUp}
  \constructivestory{An $\ObserverFilterBudgetSelectorUp$ packet is generated from observer-history identity, observer-filter selected and omitted rows, a finite observation-budget selector, StreamName windows, DyadicRatCore observations, RegSeqRat handoff, Real seal, componentwise hsame transports, displayed Cont routes, Pkg provenance, and a local NameCert row.}
  \leanchecked{BEDC.Derived.ObserverFilterBudgetSelectorUp.taste\_gate}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:observer-filter-budget-selector-carrier}, \autoref{thm:observer-filter-budget-selector-namecert-surface}, \autoref{thm:observer-filter-budget-selector-streamname-handoff}, \autoref{thm:observer-filter-budget-selector-dyadic-readback-exactness}, and the public export \autoref{thm:observer-filter-budget-selector-real-seal-terminality} bind the finite selected-row budget route, dyadic readback exactness, and terminal Real-seal factorization over ObserverHistoryIdentityUp, ObserverFilterUp, StreamNameUp, FiniteObservationBudgetSelectorUp, DyadicRatCoreUp, RegSeqRatUp, RealUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close quotient streams, host real equality, selected host limits, countable choice, hidden limit selectors, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{No further paper-side closure grade remains for the selected-row Real-seal route; verification and bridge checking remain separate axes.}
\end{closurestatus}
