\chapter{A Concrete Naming Certificate for $\BetaCongruenceDomainAuditUp$}
\label{ch:concrete-instances-beta-congruence-domain-audit-namecert}
\origin{ai}

The $\BetaCongruenceDomainAuditUp$ packet realizes the binder-domain trigger surface identified in \autoref{ch:metacic-beta-audit-map}. It sits beside the beta-step boundary of \autoref{ch:concrete-instances-betastepboundary-namecert} and the beta-substitution preservation packet of \autoref{ch:concrete-instances-betasubstitutionpreservation-namecert}: those siblings expose the raw beta relation and the redex-substitution preservation row, while this packet binds the $\texttt{congLamDom}$ and $\texttt{congPiDom}$ domain-trigger rows as finite subject-reduction audit data.

\falsifiablePrediction{A packet omitting the displayed binder-domain trigger row is not an accepted $\BetaCongruenceDomainAuditUp$ carrier.}

\independenceWitness{betastepboundary, betasubstitutionpreservation, metacic-subject-reduction-obstruction, subjectreductiondischarge: no sibling is bijective because the new packet stores the binder-domain beta-congruence trigger, displayed domain readback, subject-reduction handoff row, transport, route, provenance, and local naming together.}

\begin{definition}[BetaCongruenceDomainAudit carrier]
\label{def:beta-congruence-domain-audit-carrier}
A $\BetaCongruenceDomainAuditUp$ carrier is a finite $\BHist$ packet
$$
D=(T,M,\Pi,R,S,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the binder-domain trigger row, tagged by the local $\texttt{congLamDom}$ or $\texttt{congPiDom}$ beta constructor;
\item $M$ is the lambda-domain readback row for the displayed old and new lambda annotations, when the trigger is the lambda-domain constructor;
\item $\Pi$ is the Pi-domain readback row for the displayed old and new Pi annotations, when the trigger is the Pi-domain constructor;
\item $R$ is the subject-reduction handoff row naming the binder-domain discharge surface consumed by $\SubjectReductionDischargeUp$;
\item $S$ is the finite subject-reduction trigger ledger tying $T,M,\Pi,R$ to the same domain-congruence beta step;
\item $H$ stores componentwise $\hsame$ transports for the trigger, readback, handoff, ledger, route, provenance, and naming rows;
\item $K$ stores the displayed $\Cont$ routes for reading the trigger, replaying the domain readback, and handing the row to the subject-reduction discharge interface;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:metacic-beta-audit-map}, \autoref{ch:concrete-instances-betastepboundary-namecert}, \autoref{ch:concrete-instances-betasubstitutionpreservation-namecert}, \autoref{ch:concrete-instances-subjectreductiondischarge-namecert}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\BetaCongruenceDomainAuditUp}$ row.
\end{enumerate}
The carrier is exactly this finite packet. It contains no beta-redex substitution semantics, no typed preservation theorem, no unrestricted conversion, and no closed subject-reduction theorem.
\end{definition}

\begin{theorem}[BetaCongruenceDomainAudit NameCert obligations]
\label{thm:beta-congruence-domain-audit-namecert-obligations}
For the carrier of \autoref{def:beta-congruence-domain-audit-carrier}, the local $\NameCert_{\BetaCongruenceDomainAuditUp}$ surface consists of carrier admission for
$$
D=(T,M,\Pi,R,S,H,K,P,N),
$$
binder-domain trigger readback, lambda-domain readback, Pi-domain readback, subject-reduction handoff replay, finite trigger-ledger exactness, componentwise $\hsame$ transport, displayed $\Cont$ route replay, $\Pkg$ provenance, and non-escape from beta-redex substitution semantics, typed preservation, unrestricted conversion, and closed subject reduction.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:beta-congruence-domain-audit-carrier}. The packet exposes exactly $T,M,\Pi,R,S,H,K,P,N$.

The trigger row $T$ records whether the beta step is the lambda-domain constructor or the Pi-domain constructor named in \autoref{ch:metacic-beta-audit-map}. The readback rows $M$ and $\Pi$ keep the displayed old and new domain annotations separate from any redex-substitution row.

The handoff row $R$ and ledger row $S$ place the trigger beside the subject-reduction discharge surface without discharging it. The transports $H$, routes $K$, provenance $P$, and local name $N$ bind the read into one finite NameCert packet.

Since no coordinate supplies beta-redex substitution semantics, typed preservation, unrestricted conversion, or closed subject reduction, no consumer of the local certificate can export those objects from the binder-domain trigger packet.
\end{proof}

\begin{theorem}[BetaCongruenceDomainAudit trigger handoff]
\label{thm:beta-congruence-domain-audit-trigger-handoff}
An accepted $\BetaCongruenceDomainAuditUp$ packet presents the $\texttt{congLamDom}$ and $\texttt{congPiDom}$ beta constructors as finite subject-reduction trigger rows. The handoff to $\SubjectReductionDischargeUp$ reads only
$$
D=(T,M,\Pi,R,S,H,K,P,N),
$$
where $T$ is the binder-domain trigger, $M$ and $\Pi$ are the displayed domain readbacks, $R$ is the discharge-facing row, $S$ is the finite trigger ledger, and $H,K,P,N$ are the local transport, route, provenance, and naming rows.
\end{theorem}
\begin{proof}
First read the trigger from $T$. The beta-step boundary sibling records that $\texttt{congLamDom}$ and $\texttt{congPiDom}$ are beta constructors, while this carrier stores which binder-domain constructor is being audited.

Next read the displayed domain annotations. The lambda-domain case uses $M$, and the Pi-domain case uses $\Pi$; each route is replayed through $H$ and $K$ before the handoff row $R$ is visible.

Finally apply the provenance row $P$. It links the trigger to the beta audit map, beta-step boundary, beta-substitution preservation sibling, and subject-reduction discharge surface, but it does not identify the binder-domain trigger with redex substitution or typed preservation.
\end{proof}

\begin{theorem}[BetaCongruenceDomainAudit non-escape]
\label{thm:beta-congruence-domain-audit-nonescape}
Every accepted $\BetaCongruenceDomainAuditUp$ packet exposes binder-domain beta-congruence only through the rows
$$
T,M,\Pi,R,S,H,K,P,N.
$$
A downstream consumer may read the binder-domain trigger, displayed lambda-domain readback, displayed Pi-domain readback, discharge-facing handoff, finite trigger ledger, transports, routes, provenance, and local naming row. It cannot replace those rows by beta-redex substitution semantics, typed preservation, unrestricted conversion, or closed subject reduction.
\end{theorem}
\begin{proof}
Project the carrier. The only beta-facing row is $T$, and the only binder annotation readbacks are $M$ and $\Pi$.

Use the NameCert obligations of \autoref{thm:beta-congruence-domain-audit-namecert-obligations}. They require the handoff and ledger rows to remain tied to the same trigger packet through $H,K,P,N$.

The exclusions follow from absence of coordinates. Redex substitution, typed preservation, unrestricted conversion, and closed subject reduction would each require a separate row or external route, and none is present in $D$.
\end{proof}

\begin{theorem}[BetaCongruenceDomainAudit TasteGate target]
\label{thm:beta-congruence-domain-audit-tastegate-target}
The Lean-facing taste gate for $\BetaCongruenceDomainAuditUp$ is the finite carrier discipline of \autoref{def:beta-congruence-domain-audit-carrier} together with the obligation, handoff, and non-escape theorems of this chapter. The downstream taste-gate module \texttt{Derived/BetaCongruenceDomainAuditUp/TasteGate.lean} must provide \texttt{Nontrivial BetaCongruenceDomainAuditUp} and \texttt{FieldFaithful BetaCongruenceDomainAuditUp} instances for the rows $T,M,\Pi,R,S,H,K,P,N$.
\end{theorem}
\begin{proof}
The carrier theorem fixes the finite row inventory. The NameCert obligations identify the admission, readback, handoff, ledger, transport, route, provenance, and naming fields.

The handoff theorem shows the packet is not merely a beta-step boundary: it has a discharge-facing route for binder-domain triggers. The non-escape theorem shows it is not a typed preservation theorem or unrestricted conversion rule.

These three facts are exactly the paper-side target for a nontrivial instance and a field-faithful instance: an accepted carrier has the displayed rows, and each row is recoverable without adding hidden host semantics.
\end{proof}

\begin{closurestatus}{\BetaCongruenceDomainAuditUp}
  \constructivestory{A $\BetaCongruenceDomainAuditUp$ packet is generated from beta-domain admission rows, readback rows, a discharge-facing handoff, a binder-domain trigger ledger, componentwise $\hsame$ transport, displayed $\Cont$ routes, provenance, and local naming. The $\BHist$ carrier records where beta congruence is allowed to be consumed and where the domain audit must refuse an unrestricted conversion read. Its classifier first exposes the admission surface, then the handoff and trigger ledger, and only then lets downstream consumers read the audit row. The route is finite and syntactic, not a host conversion theorem.}
  \theoryclosure{\seedClosure}
  \scopeclosed{This chapter binds the beta congruence domain audit carrier, handoff theorem, non-escape theorem, and paper-side TasteGate target.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{It does not claim unrestricted conversion, typed preservation, subject reduction, or host beta-equivalence semantics.}
  \upgradepath{To reach obligationClosure, formalize the beta-domain admission and discharge-trigger rows as nontrivial and field-faithful carrier data.}
\end{closurestatus}
