\chapter{A Concrete Naming Certificate for $\ObserverTraceSealUp$}
\label{ch:concrete-instances-observertraceseal-namecert}
\origin{ai}

The $\ObserverTraceSealUp$ packet realizes the observer-history identity vision of \autoref{ch:visions-observer-hist-identity} as a finite sealed trace certificate. It reads the no-subject identity surface of \autoref{ch:concrete-instances-observerhistidentity-namecert} together with the observer trace, distinction trace, bounded trace, and finite evaluator siblings. The finite evaluator sibling of \autoref{ch:concrete-instances-finitetraceevaluator-namecert} supplies bounded checkpoint and runtime readback, while $\ObserverTraceSealUp$ adds the seal and no-subject refusal row. Its novelty is the seal row: a visible refusal ledger that binds each accepted trace to the same observer row, observation row, route, provenance, and local name before any consumer may read the trace.

\begin{definition}[ObserverTraceSeal carrier]
\label{def:observer-trace-seal-carrier}
An $\ObserverTraceSealUp$ carrier is a finite $\BHist$ packet
$$
S=(O,T,A,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the observer row, read as a finite $\Hist$ or $\BHist$ observer-history surface;
\item $T$ is the accepted trace row over the same observer-history surface;
\item $A$ is the observation row, recording the displayed $\Cont$-mediated read of the trace;
\item $R$ is the seal and no-subject refusal ledger, recording that the trace has no owner, subject carrier, hidden observer equality, or off-packet identity row;
\item $H$ records componentwise $\hsame$ transport for $O,T,A,R,P,N$;
\item $C$ records the displayed $\Cont$ routes from the observer row through the trace, observation, seal, provenance, and naming rows;
\item $P$ is the $\Pkg$ provenance over $\ObserverHistIdentityUp$, $\ObserverKernelTraceUp$, $\ObserverDistinctionTraceUp$, $\BoundedUniversalTraceUp$, $\FiniteTraceEvaluatorUp$, $\BHist$, $\Hist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ObserverTraceSealUp}$ row.
\end{enumerate}
The carrier has no coordinate for observer-substance, host equality of observers, quotient observer identity, detached trace ownership, or an evaluator graph outside the displayed trace packet.
\end{definition}

\begin{theorem}[ObserverTraceSeal NameCert obligations]
\label{thm:observer-trace-seal-namecert-obligations}
For the carrier of \autoref{def:observer-trace-seal-carrier}, the local $\NameCert_{\ObserverTraceSealUp}$ surface consists exactly of five finite obligation rows:
\begin{enumerate}
\item carrier admission for $S=(O,T,A,R,H,C,P,N)$;
\item observer and trace exposure through the displayed $O,T,A$ rows;
\item seal and no-subject refusal through $R$;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, and $\Pkg$ provenance through $H,C,P$;
\item local naming exactness through $N$.
\end{enumerate}
No accepted consumer can read the trace without passing through all five rows.
\end{theorem}
\leanchecked{BEDC.Derived.ObserverTraceSealUp.ObserverTraceSealUp\_taste\_gate\_boundary}
\begin{proof}
Carrier admission is projection from \autoref{def:observer-trace-seal-carrier}. The packet displays the observer row, trace row, observation row, seal row, transport, route, provenance, and local name.

The observer and trace exposure rows are read through $O,T,A$. The trace is therefore attached to the same observer-history surface and the same displayed observation route before the seal is inspected.

The refusal row $R$ records the no-subject boundary. Componentwise transport and replay are then supplied only by $H$ and $C$, while $P$ and $N$ record provenance and local naming. Since no further coordinate is present, the five rows exhaust the local certificate.
\end{proof}

\begin{theorem}[ObserverTraceSeal no-subject nonescape]
\label{thm:observer-trace-seal-non-subject-nonescape}
Every accepted $\ObserverTraceSealUp$ packet exposes a trace only through the displayed observer row, trace row, observation row, seal row, componentwise $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row $O,T,A,R,H,C,P,N$. It cannot export an observer-substance carrier, hidden subject row, host equality of observers, quotient observer identity, detached trace owner, or evaluator graph outside those rows.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:observer-trace-seal-namecert-obligations}. They force every accepted read through $O,T,A,R,H,C,P,N$ before the local name is available.

Use the observer-history identity sibling \autoref{ch:concrete-instances-observerhistidentity-namecert}. It reads observer identity as a finite history and observation surface rather than as a separate subject carrier.

Now attach the seal row $R$. The refusal ledger is part of the same accepted packet as the trace, so a consumer cannot expose $T$ while omitting the no-subject refusal. The absent observer-substance, hidden subject, host equality, quotient identity, detached owner, and evaluator graph each require a coordinate outside the carrier.
\end{proof}

\falsifiablePrediction{If an accepted ObserverTraceSeal packet exposes a trace without the no-subject refusal row, then thm:observer-trace-seal-non-subject-nonescape is refuted by that packet.}

\independenceWitness{observerhistidentity, observerkerneltrace, observerdistinctiontrace, boundeduniversaltrace, finitetraceevaluator: the packet records an observer row, trace row, observation row, seal row, no-subject refusal, transport, route, provenance, and local name in one finite carrier.}

The seal row plus the no-subject refusal ledger prevents a bijection to any sibling carrier. $\ObserverHistIdentityUp$ supplies identity comparison without a sealed trace row, $\ObserverKernelTraceUp$ supplies trace exposure without the extra seal obligation, $\ObserverDistinctionTraceUp$ orders distinction steps without bounded trace readback, $\BoundedUniversalTraceUp$ supplies a fuel-indexed trace without observer-history identity, and $\FiniteTraceEvaluatorUp$ supplies finite evaluation without the no-subject seal.

\begin{theorem}[ObserverTraceSeal public export]
\label{thm:observer-trace-seal-public-export}
Every public export of an accepted $\ObserverTraceSealUp$ packet is exactly the displayed observer row, trace row, observation row, no-subject seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row
$$
O,T,A,R,H,C,P,N .
$$
The export contains no observer-substance carrier, detached trace owner, host equality of observers, quotient observer identity, hidden subject row, or evaluator graph outside the sealed packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:observer-trace-seal-carrier}. Its rows are exactly the observer row $O$, trace row $T$, observation row $A$, seal and no-subject refusal row $R$, transport $H$, replay $C$, provenance $P$, and local naming row $N$.

Apply the NameCert obligations of \autoref{thm:observer-trace-seal-namecert-obligations}. They force every accepted public read through carrier admission, observer and trace exposure, no-subject refusal, transport, replay, provenance, and local naming before the trace can be exported.

Finally use \autoref{thm:observer-trace-seal-non-subject-nonescape}. The absent observer-substance, detached owner, host equality, quotient identity, hidden subject, and external evaluator graph have no coordinate in the carrier, so the public export is exactly the displayed finite surface.
\end{proof}

\closureat{ObserverTraceSealUp}{seedStr}
\closureat{ObserverTraceSealUp}{obligationStr}[BEDC.Derived.ObserverTraceSealUp.ObserverTraceSealUp\_taste\_gate\_boundary]
\closureat{ObserverTraceSealUp}{publicStr}[BEDC.Derived.ObserverTraceSealUp.ObserverTraceSealUp\_taste\_gate\_boundary]

\begin{closurestatus}{\ObserverTraceSealUp}
  \constructivestory{An $\ObserverTraceSealUp$ packet is generated from an observer row, trace row, observation row, seal and no-subject refusal ledger, componentwise hsame transport, displayed Cont routes, package provenance, and a local NameCert row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{def:observer-trace-seal-carrier}, \autoref{thm:observer-trace-seal-namecert-obligations}, \autoref{thm:observer-trace-seal-non-subject-nonescape}, and \autoref{thm:observer-trace-seal-public-export} specify the finite sealed trace packet, its no-subject boundary, and its public export surface.}
  \formalstatus{\axiomCleanV}
  \leanchecked{BEDC.Derived.ObserverTraceSealUp.taste\_gate}
  \leantarget{BEDC.Derived.ObserverTraceSealUp.ObserverTraceSealUp\_taste\_gate\_boundary}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, a host observer model, quotient observer identity, detached trace ownership, or evaluator graph semantics.}
  \upgradepath{Bridge closure requires a bridge-facing consumer surface for the same displayed observer, trace, seal, transport, replay, provenance, and local naming rows.}
\end{closurestatus}
