\chapter{A Concrete Naming Certificate for $\MetaCICDischargeObstructionLatticeUp$}
\label{ch:concrete-instances-metacicdischargeobstructionlattice-namecert}
\origin{ai}

The $\MetaCICDischargeObstructionLatticeUp$ packet realizes the critical path of \autoref{ch:metacic-audit-synthesis} as a finite discharge-obstruction lattice. It sits beside the audit-synthesis packet of \autoref{ch:concrete-instances-metacicauditsynthesis-namecert}, the discharge-obligation packet of \autoref{ch:concrete-instances-metacic-discharge-obligation-namecert}, the subject-reduction obstruction packet of \autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert}, the decidable audit packet of \autoref{ch:concrete-instances-metacicdecidableauditpacket-namecert}, and the confluence audit packet of \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}. Those siblings expose available, blocked, and required MetaCIC audit rows; the present packet records their finite lattice order without turning the blocked subject-reduction edge into a closed consistency theorem.

\begin{definition}[MetaCIC discharge-obstruction lattice carrier]
\label{def:metacic-discharge-obstruction-lattice-carrier}
A $\MetaCICDischargeObstructionLatticeUp$ carrier is a finite $\BHist$ packet
$$
L=(N,D,C,O,Q,T,R,P,K)
$$
with the following displayed rows:
\begin{enumerate}
\item $N$ is the closed-normal consistency row, reading the available normal endpoint through \autoref{ch:concrete-instances-metacicauditsynthesis-namecert};
\item $D$ is the decidable checker row, reading local typing and bounded-normal comparison through \autoref{ch:concrete-instances-metacicdecidableauditpacket-namecert};
\item $C$ is the confluence-status row, reading conditional bridges and closed-normal fragments through \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert};
\item $O$ is the subject-reduction obstruction row, reading the checked blocked edge through \autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert};
\item $Q$ is the discharge-obligation row, reading the four required subject-reduction inputs through \autoref{ch:concrete-instances-metacic-discharge-obligation-namecert};
\item $T$ records componentwise $\hsame$ transports for the closed-normal, checker, confluence, obstruction, obligation, package, and naming rows;
\item $R$ records displayed $\Cont$ routes by which a consumer reads available rows before blocked rows and required rows before any attempted closed-consistency export;
\item $P$ is the $\Pkg$ provenance over the MetaCIC audit synthesis, discharge-obligation, subject-reduction obstruction, decidable checker, confluence audit, $\BHist$, $\hsame$, $\Cont$, and \NameCert{} rows;
\item $K$ is the local $\NameCert_{\MetaCICDischargeObstructionLatticeUp}$ row.
\end{enumerate}
The carrier contains no coordinate for unconditional closed consistency, no coordinate erasing the discharge-obligation row, and no coordinate replacing the obstruction row by a closed subject-reduction theorem.
\end{definition}

\begin{theorem}[MetaCIC discharge-obstruction lattice NameCert obligations]
\label{thm:metacic-discharge-obstruction-lattice-namecert-obligations}
For the carrier of \autoref{def:metacic-discharge-obstruction-lattice-carrier}, the local $\NameCert_{\MetaCICDischargeObstructionLatticeUp}$ surface consists exactly of carrier admission for $L=(N,D,C,O,Q,T,R,P,K)$, closed-normal consistency exposure, decidable-checker exposure, confluence-status exposure, subject-reduction obstruction exposure, discharge-obligation exposure, componentwise $\hsame$ transport, displayed $\Cont$ route replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $N,D,C,O,Q,T,R,P,K$ are the complete finite packet, so carrier admission and local naming are direct projections.

Read the available branch through $N,D,C$. These rows expose closed-normal consistency, local checker evidence, and confluence status as separate sibling reads, matching the available entries of \autoref{ch:metacic-audit-synthesis}.

Read the blocked and required branch through $O$ and $Q$. The obstruction row keeps the subject-reduction edge unavailable, while the discharge-obligation row lists the required inputs that a later consumer must supply before that edge can be used.

Finally read $T,R,P,K$. Transport, route replay, provenance, and local naming preserve the same row order, and the carrier has no additional coordinate from which a hidden closed-consistency theorem could be exported.
\end{proof}

\begin{theorem}[MetaCIC discharge-obstruction lattice falsifiable nonescape]
\label{thm:metacic-discharge-obstruction-lattice-falsifiable-nonescape}
Any accepted consumer of a $\MetaCICDischargeObstructionLatticeUp$ carrier cannot export unconditional closed consistency unless the discharge-obligation row $Q$ is filled and the obstruction row $O$ is discharged. A consumer that reads only $N,D,C,T,R,P,K$, or reads $O$ merely as an obstruction, remains confined to closed-normal consistency, local checker evidence, confluence status, and the recorded blocked edge.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:metacic-discharge-obstruction-lattice-namecert-obligations}. It places the closed-normal, decidable, and confluence rows on the available side, and it keeps the obstruction and obligation rows visible as separate coordinates.

The falsifiable test is row-local. If a claimed consumer exports unconditional closed consistency, its route must show where $Q$ supplies the required subject-reduction inputs and where $O$ ceases to be the blocked subject-reduction edge.

When either row is absent in that role, route replay through $R$ stops at the closed-normal branch and the recorded blocked edge. Provenance through $P$ and naming through $K$ preserve the same boundary, so the claimed export has no accepted carrier coordinate.
\end{proof}

\begin{theorem}[MetaCIC discharge-obstruction lattice independence witness]
\label{thm:metacic-discharge-obstruction-lattice-independence-witness}
The siblings \autoref{ch:concrete-instances-metacicauditsynthesis-namecert}, \autoref{ch:concrete-instances-metacic-discharge-obligation-namecert}, \autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert}, \autoref{ch:concrete-instances-metacicdecidableauditpacket-namecert}, and \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert} are independent witnesses for the $\MetaCICDischargeObstructionLatticeUp$ lattice. None is bijective with the lattice carrier, because each lacks at least one of the available, blocked, or required edge rows displayed by $N,D,C,O,Q,T,R,P,K$.
\end{theorem}
\begin{proof}
Compare the audit-synthesis sibling first. It names the combined critical path, but it does not by itself separate every available, blocked, and required edge row as the lattice carrier does.

Compare the discharge-obligation and subject-reduction obstruction siblings next. The former displays the required inputs, while the latter displays the blocked edge; neither alone carries the closed-normal, decidable, confluence, obstruction, and obligation rows as one ordered packet.

Finally compare the decidable and confluence audit siblings. They provide available checker and confluence rows, but they do not contain the discharge-obligation row and the subject-reduction obstruction row together. Hence none of the five siblings is bijective with $L$, and together they witness the lattice as a genuine finite assembly rather than a renamed copy of one sibling.
\end{proof}

The Lean-side handoff for this packet is the finite object $\mathrm{Nontrivial}\ \MetaCICDischargeObstructionLatticeUp$, witnessed by an explicit pair separating an available-row projection from a blocked-row projection, together with $\mathrm{FieldFaithful}\ \MetaCICDischargeObstructionLatticeUp$ by constructor-field projection and injection over $N,D,C,O,Q,T,R,P,K$.

\closureat{MetaCICDischargeObstructionLatticeUp}{seedStr}

\begin{closurestatus}{\MetaCICDischargeObstructionLatticeUp}
  \constructivestory{A $\MetaCICDischargeObstructionLatticeUp$ packet is generated from closed-normal consistency, decidable-checker, confluence-status, subject-reduction obstruction, discharge-obligation, transport, route, provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-discharge-obstruction-lattice-carrier}, \autoref{thm:metacic-discharge-obstruction-lattice-namecert-obligations}, \autoref{thm:metacic-discharge-obstruction-lattice-falsifiable-nonescape}, and \autoref{thm:metacic-discharge-obstruction-lattice-independence-witness} bind the MetaCIC audit critical path as a finite discharge-obstruction lattice.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove closed subject reduction, unconditional closed consistency, arbitrary closed Church--Rosser, global decidability, checked Lean certificate coverage, or a public standard bridge.}
  \upgradepath{Formal closure requires checked carrier admission, field-faithful projections, nontrivial available-blocked witnesses, route replay, provenance, and non-escape for the same finite lattice rows.}
\end{closurestatus}
