\chapter{A Concrete Naming Certificate for $\AxiomRefusalLedgerUp$}
\label{ch:concrete-instances-axiom-refusal-ledger-namecert}
\origin{ai}

The $\AxiomRefusalLedgerUp$ packet makes an axiom-use attempt visible as a finite NameCert refusal row. It sits under the apophatic-name discipline of \autoref{ch:visions-apophatic-naming-as-discipline} and consumes the named externality surface of \autoref{ch:concrete-instances-apophaticname-namecert} together with the socket surface of \autoref{ch:concrete-instances-apophaticsocket-namecert}. Its role is narrower than those siblings: it records that an attempted kernel-facing assumption is refused as an axiom and redirected either to a displayed setup-field obligation or to an audit-visible unmet boundary.

\begin{definition}[AxiomRefusalLedger carrier]
\label{def:axiom-refusal-ledger-carrier}
An $\AxiomRefusalLedgerUp$ carrier is a finite $\BHist$ packet
$$
L=(A,S,Q,F,R,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the accepted $\ApophaticNameUp$ row naming the unsupported dependency position;
\item $S$ is the accepted $\ApophaticSocketUp$ row recording the requested supply shape and its visible site;
\item $Q$ is the axiom-use question, asking whether the request would be consumed as a Lean axiom, hidden theorem, host assumption, or unrecorded primitive;
\item $F$ is the setup-field alternative row, recording the exposed carrier field or implementation obligation that would have to supply the requested data without expanding the substrate;
\item $R$ is the refusal ledger for the attempted axiom channel;
\item $G$ is the audit-readback row that displays the question, the setup-field alternative, and the refusal outcome;
\item $H$ records componentwise $\hsame$ transports for $A,S,Q,F,R,G$ together with continuation, provenance, and naming rows;
\item $C$ records the displayed $\Cont$ routes by which consumers read the name, socket, axiom-use question, setup-field alternative, refusal ledger, and audit readback;
\item $P$ is the $\Pkg$ provenance over $\ApophaticNameUp$, $\ApophaticSocketUp$, $\ApophaticGateQuestionUp$, $\ExternalityGateUp$, $\TypeLevelSocketExposureUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\AxiomRefusalLedgerUp}$ row.
\end{enumerate}
The carrier contains no coordinate that can be consumed as a Lean axiom, hidden theorem, host assumption, quotient representative, selected witness, or unrecorded primitive.
\end{definition}

\begin{theorem}[AxiomRefusalLedger NameCert obligations]
\label{thm:axiom-refusal-ledger-namecert-obligations}
For the carrier of \autoref{def:axiom-refusal-ledger-carrier}, the local $\NameCert_{\AxiomRefusalLedgerUp}$ surface consists exactly of carrier admission for $L=(A,S,Q,F,R,G,H,C,P,N)$, apophatic-name exposure through $A$, socket exposure through $S$, axiom-use question exactness through $Q$, setup-field alternative exposure through $F$, refusal-ledger coverage through $R$, audit-readback stability through $G$, componentwise transport through $H$, displayed route replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the displayed carrier. Its rows are exactly the apophatic name, socket, axiom-use question, setup-field alternative, refusal ledger, audit readback, transport, route, provenance, and local naming rows.

Read the name and socket rows through the sibling surfaces. The $\ApophaticNameUp$ row names the unsupported dependency, and the $\ApophaticSocketUp$ row records the requested supply shape without producing that supply.

The question, alternative, and refusal rows are then read through $Q,F,R,G$. The question identifies the attempted axiom channel, $F$ records the setup-field route that would make the dependency explicit, $R$ refuses the internalization, and $G$ makes the refusal available to audit consumers.

Finally $H,C,P,N$ only transport, replay, package, and name the same visible packet. Since no row is an axiom, hidden theorem, host assumption, quotient representative, selected witness, or unrecorded primitive, the local NameCert obligations are exhausted by the displayed packet.
\end{proof}

\begin{theorem}[AxiomRefusalLedger noninternalization]
\label{thm:axiom-refusal-ledger-noninternalization}
Every accepted $\AxiomRefusalLedgerUp$ packet refuses an axiom-use attempt as internal substrate content. A consumer may cite the rows $A,S,Q,F,R,G,H,C,P,N$, including the setup-field alternative and audit readback, but no coordinate of the accepted packet can be consumed as a Lean axiom, hidden theorem, host assumption, quotient representative, selected witness, or unrecorded primitive.
\end{theorem}
\begin{proof}
Begin with the carrier inventory of \autoref{def:axiom-refusal-ledger-carrier}. The packet displays the requested dependency position and the attempted axiom channel, but the only response rows are the setup-field alternative, refusal ledger, and audit readback.

Apply the NameCert obligations of \autoref{thm:axiom-refusal-ledger-namecert-obligations}. Every consumer route must pass through $Q,F,R,G$ before it can cite the packet, so the request is classified and refused before it reaches downstream use.

The sibling boundaries of \autoref{ch:concrete-instances-apophaticname-namecert} and \autoref{ch:concrete-instances-apophaticsocket-namecert} keep the named dependency and socket shape outside generated content. Thus the accepted packet exports only visible refusal and setup-field exposure, never an internal axiom channel.
\end{proof}

\begin{theorem}[AxiomRefusalLedger gate readback]
\label{thm:axiom-refusal-ledger-gate-readback}
Every audit read of an accepted $\AxiomRefusalLedgerUp$ packet factors through the route
$$
A \to S \to Q \to F \to R \to G \to (H,C,P,N).
$$
The readback row $G$ reports the axiom-use question, the setup-field alternative, and the refusal ledger before any downstream consumer may cite the packet. No audit read can bypass $G$ to recover a Lean axiom, hidden theorem, host assumption, quotient representative, selected witness, or unrecorded primitive.
\end{theorem}
\begin{proof}
Read the displayed order in \autoref{def:axiom-refusal-ledger-carrier}. The rows $A,S,Q,F,R,G$ precede the structural rows and make the name, socket, question, alternative, refusal, and readback visible in that order.

Use \autoref{thm:axiom-refusal-ledger-namecert-obligations}. Audit-readback stability is one of the local certificate rows, so any audit consumer that cites the packet must preserve $G$ together with $Q,F,R$.

Finally apply noninternalization, \autoref{thm:axiom-refusal-ledger-noninternalization}. Since the packet has no consumable axiom or hidden theorem coordinate, bypassing $G$ cannot produce a stronger read; the only available audit route is the displayed one.
\end{proof}

\begin{theorem}[AxiomRefusalLedger sibling independence]
\label{thm:axiom-refusal-ledger-sibling-independence}
$\AxiomRefusalLedgerUp$ is not a renaming of $\ApophaticNameUp$, $\ApophaticSocketUp$, $\ApophaticGateQuestionUp$, $\ExternalityGateUp$, or $\TypeLevelSocketExposureUp$. The axiom-refusal packet simultaneously carries an axiom-use question $Q$, a setup-field alternative $F$, a refusal ledger $R$, and an audit-readback row $G$ over the same named socket. Each listed sibling lacks at least one of these coordinates, so no bijection of displayed rows preserves the local NameCert surface.
\end{theorem}
\begin{proof}
Compare first with $\ApophaticNameUp$ and $\ApophaticSocketUp$. Those siblings name the externality and requested supply shape, but they do not carry the paired axiom-use question and setup-field alternative rows $Q,F$.

Compare next with $\ApophaticGateQuestionUp$ and $\ExternalityGateUp$. Those siblings expose gate questions or readback gates, but they do not bind the question to a setup-field alternative and an axiom-channel refusal ledger in one packet.

Finally compare with $\TypeLevelSocketExposureUp$. It exposes type-level socket data, but it is not the audit ledger for refusing a Lean axiom or hidden theorem channel. Hence no row-preserving bijection can identify the carrier $A,S,Q,F,R,G,H,C,P,N$ with any of the listed sibling packets.
\end{proof}

\falsifiablePrediction{Every accepted AxiomRefusalLedgerUp packet exposes $A,S,Q,F,R,G,H,C,P,N$ before citation, and no accepted packet has any coordinate that can be consumed as a Lean axiom or hidden theorem.}

\independenceWitness{apophaticname, apophaticsocket, apophaticgatequestion, externalitygate, typelevelsocketexposure: AxiomRefusalLedgerUp alone carries the paired axiom-use question, setup-field alternative, refusal ledger, and audit-readback rows for one named socket; no sibling preserves all rows A,S,Q,F,R,G,H,C,P,N.}

The proposed Lean \texttt{TasteGate.lean} boundary is \texttt{lean4/BEDC/Derived/AxiomRefusalLedgerUp/TasteGate.lean}. It must provide \texttt{Nontrivial AxiomRefusalLedgerUp} and \texttt{FieldFaithful AxiomRefusalLedgerUp} instances for the same displayed carrier.

\closureat{AxiomRefusalLedgerUp}{seedStr}

\begin{closurestatus}{\AxiomRefusalLedgerUp}
  \constructivestory{An $\AxiomRefusalLedgerUp$ packet is generated from an apophatic-name row, apophatic-socket row, axiom-use question, setup-field alternative, refusal ledger, audit readback, componentwise transports, displayed continuations, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:axiom-refusal-ledger-carrier}, \autoref{thm:axiom-refusal-ledger-namecert-obligations}, \autoref{thm:axiom-refusal-ledger-noninternalization}, \autoref{thm:axiom-refusal-ledger-gate-readback}, and \autoref{thm:axiom-refusal-ledger-sibling-independence} bind the finite axiom-refusal carrier, setup-field alternative, audit readback, noninternalization surface, and sibling separation.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not supply the refused axiom, hidden theorem, host assumption, quotient representative, selected witness, Lean verification, or bridge checking for $\AxiomRefusalLedgerUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, axiom-use question exactness, setup-field alternative exposure, refusal-ledger coverage, audit-readback stability, noninternalization, nontriviality, and field faithfulness for the same finite packet.}
\end{closurestatus}
