\begin{theorem}[RationalInterval midpoint bisection window]
\label{thm:rationalinterval-midpoint-bisection-window}
Let $I$ be an accepted $\RationalIntervalUp$ packet with displayed lower
endpoint, upper endpoint, dyadic-width witness, containment ledger, visible
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local
$\NameCert_{\RationalIntervalUp}$ rows. Suppose a midpoint row $m$ is displayed
on the same $\RatUp$ and $\DyadicRatCoreUp$ endpoint surface, and suppose two
containment subledgers display the left window from the lower endpoint to $m$
and the right window from $m$ to the upper endpoint.

Then the two half-windows are accepted $\RationalIntervalUp$ finite packets.
They share the midpoint boundary row, their endpoint and dyadic-width rows are
read from the same displayed surface, and every $\RegSeqRatUp$ or finite-window
$\RealUp$ consumer read of either half-window is one of the original endpoint,
width, containment, refinement, $\mathsf{BHist}$, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, or local $\NameCert$ rows. Conversely, every original finite
consumer read whose endpoint and containment rows lie in one half factors
through the corresponding half-window packet.

The bisection window exports no completed $\RealUp$ equality, located subset
datum, open cover, quotient Cauchy class, apartness row, interval arithmetic
operation, or standard bridge datum.
\end{theorem}
\begin{proof}
Use \autoref{thm:rationalinterval-endpoint-width-ledger} to read the lower
endpoint, upper endpoint, midpoint row, and dyadic-width witnesses from the
same $\RatUp$ and $\DyadicRatCoreUp$ surface. Apply
\autoref{thm:rational-interval-endpoint-order-witness} to obtain the displayed
endpoint order for the left and right half-windows.

Next construct the two finite packets. Apply
\autoref{thm:rational-interval-common-refinement-window} to the parent window
and the midpoint row, and compose the resulting refinement routes with
\autoref{thm:rational-interval-refinement-composition}. This gives accepted
left and right $\RationalIntervalUp$ packets whose common endpoint is exactly
the displayed midpoint boundary.

The order in which the parent containment ledger, midpoint row, and two
subledgers are grouped does not affect the consumer-visible packet. This is
\autoref{thm:rationalinterval-common-refinement-associativity}, applied to the
two ways of parenthesizing the same finite refinement data.

Finally apply \autoref{thm:rationalinterval-finite-consumer-completeness}.
Every $\RegSeqRatUp$ or finite-window $\RealUp$ read of a half-window is
exhausted by the listed endpoint, width, containment, refinement,
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$
rows, and the same exhaustion gives the converse factorization for parent
consumer reads restricted to either half.
\end{proof}

\begin{theorem}[RationalInterval refinement choice neutrality]
\label{thm:rationalinterval-refinement-choice-neutrality}
Fix a $\RationalIntervalUp$ endpoint packet over $\mathsf{BHist}$. For any
two common-refinement windows whose endpoint, containment, dyadic-transport,
$\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows satisfy the
directed-refinement and associativity hypotheses, the resulting finite consumer
packages for $\RegSeqRatUp$ and $\RealUp$ are $\hsame$-equivalent.

Thus a finite $\RegSeqRatUp$ or $\RealUp$ consumer may use any displayed
common-refinement witness for the fixed endpoint packet without selecting
completed real equality, quotient Cauchy classes, located subsets, apartness,
interval arithmetic, or host standard interval data.
\end{theorem}
\begin{proof}
Use \autoref{thm:rational-interval-common-refinement-window} to put both
refinement choices over explicit finite endpoint and containment windows, and
use \autoref{thm:rational-interval-directed-refinement-basis} to compare their
directed basis rows inside one displayed finite $\mathsf{BHist}$ packet.

Compose the comparison routes with
\autoref{thm:rational-interval-refinement-composition}. Then
\autoref{thm:rational-interval-endpoint-transport-classifier} identifies the
endpoint, containment, dyadic-width, $\Cont$, $\mathsf{Pkg}$, and local
$\NameCert$ rows seen after the displayed $\hsame$ transport.

Finally apply \autoref{thm:rationalinterval-common-refinement-associativity}.
It identifies the two readings at the finite $\RegSeqRatUp$ and $\RealUp$
consumer surface exposed by the fixed endpoint packet.
\end{proof}

\begin{theorem}[RationalInterval bisection refinement nesting]
\label{thm:rationalinterval-bisection-refinement-nesting}
Let $I$ be an accepted $\RationalIntervalUp$ endpoint packet with displayed
lower endpoint, midpoint row, upper endpoint, containment ledger, dyadic-width
rows, visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local
$\NameCert_{\RationalIntervalUp}$ rows. Suppose the midpoint bisection of
\autoref{thm:rationalinterval-midpoint-bisection-window} displays the left and
right half-windows, and suppose either half-window is refined once more by a
finite rational-window packet over the same endpoint surface.

Then the two-step choice factors through one finite rational-window packet over
the original endpoint, midpoint, containment, dyadic-width, $\mathsf{BHist}$,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows. Every
$\RegSeqRatUp$ or finite-window $\RealUp$ consumer of the nested half-window
reads this packet, and changing the displayed common-refinement witness changes
only the $\hsame$ representative of the same finite consumer package.

The nesting claim does not assert completed $\RealUp$ equality, quotient Cauchy
classes, located subsets, apartness, interval arithmetic, or host interval
data.
\end{theorem}
\begin{proof}
First apply \autoref{thm:rationalinterval-midpoint-bisection-window}. It
constructs the accepted left and right half-window packets from the parent
endpoint, midpoint, containment, dyadic-width, $\mathsf{BHist}$, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows.

Next compose the chosen half-window refinement with the parent bisection route.
The finite parenthesization of that two-step route is exactly the content of
\autoref{thm:rationalinterval-common-refinement-associativity}; it repacks the
displayed endpoint and containment rows as one rational-window packet over the
original endpoint surface.

Finally use \autoref{thm:rationalinterval-refinement-choice-neutrality}. Any
alternate displayed common-refinement witness for the same nested half-window
has the same finite $\RegSeqRatUp$ and $\RealUp$ consumer package up to
$\hsame$. Since all rows used by the construction are the listed finite BEDC
rows, no completed-real equality, quotient class, located-subset datum,
apartness row, interval operation, or host interval structure is exported.
\end{proof}
