\chapter{A Concrete Naming Certificate for $\ExternalSupplyBoundaryUp$}
\label{ch:concrete-instances-external-supply-boundary-namecert}
\origin{ai}

The $\ExternalSupplyBoundaryUp$ packet realizes the boundary discipline of \autoref{ch:visions-external-supply-without-axioms} as a finite NameCert object. It sits beside the socket ledger of \autoref{ch:concrete-instances-supplysocketledger-namecert}, the apophatic socket surface of \autoref{ch:concrete-instances-apophaticsocket-namecert}, the audit gate boundary of \autoref{ch:concrete-instances-auditgateboundary-namecert}, and the gate-question packet of \autoref{ch:concrete-instances-apophaticgatequestion-namecert}. Those siblings expose socket use, requested externality, gate rows, or audit questions; this packet binds the complete boundary record that keeps external supply visible without making the requested supply internal.

\begin{definition}[ExternalSupplyBoundary carrier]
\label{def:external-supply-boundary-carrier}
An $\ExternalSupplyBoundaryUp$ carrier is a finite $\BHist$ packet
$$
E=(B,R,I,A,G,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the boundary-name row naming the exact external supply site;
\item $R$ is the requested-supply-shape row, recording what the site asks to consume;
\item $I$ is the non-internalization row, recording that the requested supply is not available as substrate truth;
\item $A$ is the accepted-boundary-form row, one of setup field, NameCert row, GAP ledger, bridge slot, or apophatic socket;
\item $G$ is the associated $\mathsf{GAP}$ ledger row preserving the residue or socket pressure generated by the request;
\item $Q$ is the gate-question row naming the finite audit question that must be asked before any consumer reads the boundary;
\item $H$ records componentwise $\hsame$ transport for $B,R,I,A,G,Q$;
\item $C$ records displayed $\Cont$ replay routes through the same boundary rows;
\item $P$ is the $\Pkg$ provenance over $\SupplySocketLedgerUp$, $\ApophaticSocketUp$, $\AuditGateBoundaryUp$, $\ApophaticGateQuestionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ExternalSupplyBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for an internal witness of the requested supply, no hidden selector, no host quotient, and no theorem asserting that the requested supply exists.
\end{definition}
\leanchecked{BEDC.Derived.ExternalSupplyBoundaryUp.ExternalSupplyBoundaryTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ExternalSupplyBoundary NameCert obligations]
\label{thm:external-supply-boundary-namecert-obligations}
For the carrier of \autoref{def:external-supply-boundary-carrier}, the local $\NameCert_{\ExternalSupplyBoundaryUp}$ surface consists exactly of carrier admission for $E=(B,R,I,A,G,Q,H,C,P,N)$, boundary-name exposure through $B$, requested-supply exactness through $R$, non-internalization exactness through $I$, accepted-form exposure through $A$, $\mathsf{GAP}$-ledger readback through $G$, gate-question readback through $Q$, componentwise $\hsame$ stability through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.

Equivalently, a consumer may read the boundary name, requested supply shape, non-internalization status, accepted boundary form, associated $\mathsf{GAP}$ ledger, and gate question, but no requested supply content outside those rows.
\end{theorem}
\begin{proof}
Project the displayed carrier. The accepted packet lists $B,R,I,A,G,Q,H,C,P,N$, so the local certificate cannot introduce a second boundary name, requested-supply shape, non-internalization row, accepted boundary form, $\mathsf{GAP}$ ledger, gate question, transport row, replay route, provenance row, or local name.

Read the obligation rows in order. The boundary name $B$ identifies the site, the requested-supply row $R$ names the demanded shape, and the non-internalization row $I$ prevents that request from becoming substrate truth.

Next read $A,G,Q$. The accepted-boundary-form row states how the request remains visible, the $\mathsf{GAP}$ row records the residue or socket pressure, and the gate-question row states the audit question a consumer must ask.

Finally inspect $H,C,P,N$. These rows only transport, replay, package, and name the same finite packet. Therefore the NameCert obligations are exhausted by the displayed rows.
\end{proof}

\begin{theorem}[ExternalSupplyBoundary non-internalization]
\label{thm:external-supply-boundary-non-internalization}
Every accepted $\ExternalSupplyBoundaryUp$ packet refuses internalization of its requested supply. A downstream consumer may cite $B,R,I,A,G,Q,H,C,P,N$ as boundary evidence, but it may not read from the packet an internal witness, selector, quotient representative, proposition equality token, or theorem that supplies the requested content.
\end{theorem}
\begin{proof}
Begin with the non-internalization row $I$. By the carrier definition, $I$ is displayed as a row of the packet rather than derived from a hidden consumer convention.

Use the accepted-boundary-form row $A$ together with the $\mathsf{GAP}$ ledger $G$. The row $A$ records the visible form in which the request is held, and $G$ records the residue or socket pressure that would otherwise be erased.

Use the gate-question row $Q$ to bind the consumer read to an audit question. A consumer can ask whether the boundary remains visible, but the packet contains no coordinate that answers by supplying the requested content.

The remaining rows $H,C,P,N$ preserve and name only the displayed boundary rows. Since no coordinate stores an internal witness, selector, quotient representative, proposition equality token, or supplied-content theorem, every accepted packet keeps the requested supply external.
\end{proof}

\begin{theorem}[ExternalSupplyBoundary accepted form exhaustion]
\label{thm:external-supply-boundary-accepted-form-exhaustion}
For every accepted $\ExternalSupplyBoundaryUp$ packet
$$
E=(B,R,I,A,G,Q,H,C,P,N),
$$
the accepted boundary form row $A$ is exhausted by exactly one of the displayed
boundary forms: setup field, NameCert row, $\mathsf{GAP}$ ledger, bridge slot,
or apophatic socket. The packet exposes no accepted form outside those rows
and no internal witness of the requested supply.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:external-supply-boundary-carrier}. The
accepted-form coordinate is the row $A$, and it is read beside
$B,R,I,G,Q,H,C,P,N$.

Use \autoref{thm:external-supply-boundary-namecert-obligations}. The local
NameCert surface binds accepted-form exposure to carrier admission,
requested-supply exactness, non-internalization, GAP-ledger readback,
gate-question readback, transport, replay, provenance, and local naming.

Finally apply \autoref{thm:external-supply-boundary-non-internalization}. Since
the requested supply is not internalized, the accepted form cannot be replaced
by a hidden witness, selector, quotient representative, proposition equality
token, or supplied-content theorem.
\end{proof}

\begin{theorem}[ExternalSupplyBoundary gate question determinacy]
\label{thm:external-supply-boundary-gate-question-determinacy}
For every accepted $\ExternalSupplyBoundaryUp$ packet
$$
E=(B,R,I,A,G,Q,H,C,P,N),
$$
the gate-question row $Q$ is deterministic for downstream reads. Once the
boundary name $B$, requested-supply shape $R$, non-internalization row $I$,
accepted form $A$, and $\mathsf{GAP}$ ledger $G$ are fixed, every consumer
reads the same finite question $Q$ through $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the displayed carrier. The row $Q$ is a coordinate of the same finite
packet as $B,R,I,A,G,H,C,P,N$, so there is no second question row available to
a consumer.

Use \autoref{thm:external-supply-boundary-namecert-obligations}. Gate-question
readback is one of the local obligations, and the structural rows $H,C,P,N$
only transport, replay, package, and name that row.

Apply \autoref{thm:external-supply-boundary-non-internalization}. The
determinacy of $Q$ cannot be bypassed by reading an internal witness,
selector, quotient representative, proposition equality token, or theorem
that supplies the requested content.
\end{proof}

\begin{theorem}[ExternalSupplyBoundary sibling compatibility]
\label{thm:external-supply-boundary-sibling-compatibility}
Every accepted $\ExternalSupplyBoundaryUp$ packet
$$
E=(B,R,I,A,G,Q,H,C,P,N)
$$
is compatible with the sibling surfaces $\SupplySocketLedgerUp$,
$\ApophaticSocketUp$, $\AuditGateBoundaryUp$, and $\ApophaticGateQuestionUp$.
The row $P$ records those sibling provenances, while $A,G,Q$ expose the
accepted boundary form, socket or residue ledger, and gate question needed by
the sibling reads. The compatibility does not internalize the requested
supply.
\end{theorem}
\begin{proof}
Project the carrier. The provenance row $P$ explicitly ranges over the socket
ledger, apophatic socket, audit gate boundary, and apophatic gate question
sibling surfaces, while $A,G,Q$ display the accepted form, residue ledger, and
question rows they consume.

Use \autoref{thm:external-supply-boundary-namecert-obligations}. It binds
sibling-facing provenance to the same carrier admission, non-internalization,
accepted-form readback, GAP-ledger exposure, gate-question readback,
transport, replay, and local naming rows.

Finally use \autoref{thm:external-supply-boundary-non-internalization}. The
sibling compatibility route can expose socket use, apophatic refusal, audit
boundary pressure, and gate-question reads, but it has no coordinate for an
internal witness, selector, quotient representative, proposition equality
token, or supplied-content theorem.
\end{proof}

\begin{theorem}[ExternalSupplyBoundary carrier admission]
\label{thm:external-supply-boundary-carrier-admission}
Every accepted $\ExternalSupplyBoundaryUp$ boundary read is admitted only by the
finite $\BHist$ carrier
$$
E=(B,R,I,A,G,Q,H,C,P,N).
$$
The local $\NameCert_{\ExternalSupplyBoundaryUp}$ row $N$ projects exactly this
tuple: boundary name $B$, requested-supply shape $R$, non-internalization row
$I$, accepted-boundary-form row $A$, $\mathsf{GAP}$ ledger $G$, gate question
$Q$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$,
package provenance $P$, and local naming $N$.
\end{theorem}
\begin{proof}
Start from the carrier definition. The packet is displayed as the ten-coordinate
finite history $E=(B,R,I,A,G,Q,H,C,P,N)$, and every coordinate is named before
the local certificate row is read.

Use \autoref{thm:external-supply-boundary-namecert-obligations}. Carrier
admission is the first obligation of the local NameCert surface, and the later
obligations are all projections from the same displayed packet.

Thus an accepted boundary read has no second carrier and no unlisted coordinate.
It is admitted exactly through the finite $\BHist$ tuple named by $N$.
\end{proof}

\begin{theorem}[ExternalSupplyBoundary GAP ledger exposure]
\label{thm:external-supply-boundary-gap-ledger-exposure}
Every accepted $\ExternalSupplyBoundaryUp$ read exposes requested-supply
pressure factors only through the $\mathsf{GAP}$ ledger row $G$, while the
non-internalization row $I$ records that the same request is not available as
internal substrate content. The exposure is therefore a ledger read of boundary
pressure, not a supply witness.
\end{theorem}
\begin{proof}
Read the packet through \autoref{thm:external-supply-boundary-carrier-admission}.
The rows $I$ and $G$ are coordinates of the same finite carrier, so a consumer
cannot separate ledger pressure from the non-internalization status that names
the request as external.

Apply \autoref{thm:external-supply-boundary-namecert-obligations}. The local
surface lists non-internalization exactness through $I$ and
$\mathsf{GAP}$-ledger readback through $G$ as distinct obligations over the same
boundary packet.

Finally use \autoref{thm:external-supply-boundary-non-internalization}. Since no
coordinate supplies the requested content, the $G$ read exposes only residue or
socket pressure for the request named by $R$ and refused by $I$.
\end{proof}

\begin{theorem}[ExternalSupplyBoundary socket readback]
\label{thm:external-supply-boundary-socket-readback}
Every sibling boundary read through $\SupplySocketLedgerUp$,
$\ApophaticSocketUp$, $\AuditGateBoundaryUp$, and
$\ApophaticGateQuestionUp$ must pass through the displayed rows
$A,G,Q,H,C,P,N$ of the same accepted $\ExternalSupplyBoundaryUp$ packet. The
readback may expose accepted boundary form, socket or residue ledger, gate
question, transport, replay, provenance, and local naming, but it may not bypass
those rows to obtain requested supply content.
\end{theorem}
\begin{proof}
Use \autoref{thm:external-supply-boundary-sibling-compatibility}. The sibling
surfaces named there consume the provenance row $P$ together with the accepted
form $A$, ledger $G$, and gate question $Q$.

Use \autoref{thm:external-supply-boundary-carrier-admission} to place those rows
inside the single finite carrier. The transport row $H$, replay row $C$,
provenance row $P$, and naming row $N$ keep the sibling read attached to that
carrier rather than to an external socket convention.

Apply \autoref{thm:external-supply-boundary-gap-ledger-exposure} and
\autoref{thm:external-supply-boundary-non-internalization}. The readback can
carry socket pressure and the audit question, but the requested supply remains
external to the packet.
\end{proof}

\falsifiablePrediction{A boundary packet that omits either the non-internalization row or the GAP-ledger row cannot satisfy the non-internalization theorem.}

\independenceWitness{Compare SupplySocketLedger, ApophaticSocket, AuditGateBoundary, and ApophaticGateQuestion: none is bijective to ExternalSupplyBoundary, because each lacks at least one of the requested-supply shape, accepted boundary form, GAP ledger, or gate-question rows required by the packet.}

The Lean follow-up must provide explicit $\mathsf{Nontrivial}\ \ExternalSupplyBoundaryUp$ and $\mathsf{FieldFaithful}\ \ExternalSupplyBoundaryUp$ instances in $\mathsf{lean4/BEDC/Derived/ExternalSupplyBoundaryUp/TasteGate.lean}$ before the chapter can claim a checked taste-gate target.

\closureat{ExternalSupplyBoundaryUp}{seedStr}
\closureat{ExternalSupplyBoundaryUp}{obligationStr}
\closureat{ExternalSupplyBoundaryUp}{scopedStr}
\closureat{ExternalSupplyBoundaryUp}{scopedStr}[BEDC.Derived.ExternalSupplyBoundaryUp.ExternalSupplyBoundaryTasteGate\_single\_carrier\_alignment]
\closureat{ExternalSupplyBoundaryUp}{publicStr}[BEDC.Derived.ExternalSupplyBoundaryUp.ExternalSupplyBoundaryTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\ExternalSupplyBoundaryUp}
  \constructivestory{An $\ExternalSupplyBoundaryUp$ packet is generated from a boundary-name row, requested-supply-shape row, non-internalization row, accepted-boundary-form row, $\mathsf{GAP}$ ledger row, gate-question row, componentwise $\hsame$ transports, displayed $\Cont$ replay, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{def:external-supply-boundary-carrier}, \autoref{thm:external-supply-boundary-namecert-obligations}, \autoref{thm:external-supply-boundary-non-internalization}, \autoref{thm:external-supply-boundary-accepted-form-exhaustion}, \autoref{thm:external-supply-boundary-gate-question-determinacy}, \autoref{thm:external-supply-boundary-sibling-compatibility}, \autoref{thm:external-supply-boundary-carrier-admission}, \autoref{thm:external-supply-boundary-gap-ledger-exposure}, and \autoref{thm:external-supply-boundary-socket-readback} bind the finite boundary packet, its NameCert obligations, non-internalization row, accepted-form exhaustion, gate-question determinacy, sibling compatibility, carrier admission, GAP-ledger exposure, and socket readback.}
  \leanchecked{BEDC.Derived.ExternalSupplyBoundaryUp.taste\_gate}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.ExternalSupplyBoundaryUp.ExternalSupplyBoundaryTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close internal witnesses, selectors, quotient representatives, supplied-content theorems, Lean TasteGate verification, or bridge checking.}
  \upgradepath{Bridge closure requires a bridge theorem for the same finite external-supply boundary packet.}
\end{closurestatus}
