\chapter{A Concrete Naming Certificate for $\ApophaticFixedPointUp$}
\label{ch:concrete-instances-apophaticfixedpoint-namecert}
\origin{ai}

The $\ApophaticFixedPointUp$ packet realizes the vision of \autoref{ch:visions-apophatic-fixed-point-and-inscription} as a finite NameCert carrier. It consumes the apophatic name discipline of \autoref{ch:concrete-instances-apophaticname-namecert}, the local inscription surface of \autoref{ch:concrete-instances-inscriptionpoint-namecert}, the visible socket-use ledger of \autoref{ch:concrete-instances-socket-use-ledger-namecert}, and the fixed witness discipline of \autoref{ch:concrete-instances-generatorfixedpoint-namecert}. The packet keeps far-end unification, local inscription readback, boundary noninternalization, and fixed-point ledger rows together without turning the far end into a kernel object.

\begin{definition}[ApophaticFixedPoint carrier]
\label{def:apophatic-fixed-point-carrier}
An $\ApophaticFixedPointUp$ carrier is a finite $\BHist$ packet
$$
F=(S,T,I,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the forward-socket family row, recording the finite socket names, their requested supply shapes, visible use sites, and socket-use ledger links;
\item $T$ is the apophatic far-end boundary row, naming the unique far end common to the displayed socket family without representing it as a kernel object;
\item $I$ is the local inscription point row, recording where the common far-end boundary is read back on the local observation chain;
\item $L$ is the boundary ledger row, recording the fixed-point ledger entries, refused internalizations, and accepted local readback events for the same socket family;
\item $H$ records componentwise $\hsame$ transports for $S,T,I,L$, the continuation row, the package row, and the local naming row;
\item $C$ records the displayed $\Cont$ routes by which consumers read the socket family, far-end boundary, local inscription point, ledger rows, provenance, and local certificate;
\item $P$ is the $\Pkg$ provenance over $\ApophaticNameUp$, $\InscriptionPointUp$, $\SocketUseLedgerUp$, $\GeneratorFixedPointUp$, $\BHist$, $\mathsf{GAP}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ApophaticFixedPointUp}$ row.
\end{enumerate}
The carrier contains exactly these rows. It has no coordinate for an internal object $\mathsf{T}$, no equality between the far-end boundary and a local state, no detached self-center object, no hidden socket selector, and no host fixed-point principle outside the displayed ledger.
\end{definition}

\begin{theorem}[ApophaticFixedPoint NameCert obligations]
\label{thm:apophatic-fixed-point-namecert-obligations}
For the carrier of \autoref{def:apophatic-fixed-point-carrier}, the local $\NameCert_{\ApophaticFixedPointUp}$ surface consists exactly of carrier admission for
$$
F=(S,T,I,L,H,C,P,N),
$$
forward-socket family exposure through $S$, unique apophatic far-end naming through $T$, local inscription readback through $I$, boundary-ledger coverage through $L$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:apophatic-fixed-point-carrier}. The tuple lists the socket family, far-end boundary, local inscription point, ledger, transport, continuation, provenance, and local naming rows.

Read the four nearest concrete sources through their displayed roles. The $\ApophaticNameUp$ row supplies boundary naming, $\InscriptionPointUp$ supplies the local inscription readback surface, $\SocketUseLedgerUp$ supplies visible socket-use rows, and $\GeneratorFixedPointUp$ supplies fixed-witness ledger discipline.

The NameCert obligations are exhausted by $S,T,I,L,H,C,P,N$. Since the carrier has no coordinate for an internal $\mathsf{T}$ object, detached self-center, hidden selector, or host fixed-point principle, every accepted read remains a finite certificate route.
\end{proof}

\begin{theorem}[ApophaticFixedPoint boundary noninternalization]
\label{thm:apophatic-fixed-point-boundary-noninternalization}
For an accepted $\ApophaticFixedPointUp$ packet, the far-end row $T$ is readable only as the common apophatic boundary of the displayed forward-socket family $S$. A consumer may transport or replay this row through $H,C,P,N$, but it cannot read $T$ as a kernel object, local state, $\BHist$ constructor, selected supply witness, object-level equality, or host fixed-point theorem.
\end{theorem}
\begin{proof}
Start with the carrier inventory in \autoref{def:apophatic-fixed-point-carrier}. The far-end coordinate is the boundary row $T$, and its socket domain is the displayed family $S$.

The ledger row $L$ records which attempted internalizations are refused, while $H,C,P,N$ only transport, replay, package, and name the same finite rows. None of these rows adds a kernel carrier for the far end.

Apply the NameCert obligations of \autoref{thm:apophatic-fixed-point-namecert-obligations}. They bind every read of $T$ to $S,T,I,L,H,C,P,N$, so a far-end read that treats $T$ as an object, state, constructor, selected witness, equality, or host theorem has no accepted route in the packet.
\end{proof}

\begin{theorem}[ApophaticFixedPoint local inscription readback]
\label{thm:apophatic-fixed-point-local-inscription-readback}
Every accepted local readback of an $\ApophaticFixedPointUp$ packet factors through the route
$$
S \longmapsto T \longmapsto I \longmapsto L \longmapsto H,C,P,N .
$$
The read first exposes the socket family, then names the unique apophatic far-end boundary, then records the local inscription point, and finally checks the boundary ledger, transport, continuation, provenance, and local $\NameCert$ rows. It exports no local inscription read that bypasses the socket family or internalizes the far end.
\end{theorem}
\begin{proof}
Project an accepted packet $F=(S,T,I,L,H,C,P,N)$. The local inscription row is $I$, but it is part of the same finite carrier as the socket family $S$ and far-end boundary $T$.

Use \autoref{thm:apophatic-fixed-point-boundary-noninternalization}. It blocks any read that turns $T$ into an internal object before $I$ is consumed as a local inscription point.

The remaining rows give the public readback surface. The ledger row $L$ records accepted local readback and refused internalization attempts, while $H,C,P,N$ preserve and expose only the displayed route. Thus every local inscription readback factors through the stated finite chain.
\end{proof}

\falsifiablePrediction{Any accepted ApophaticFixedPointUp packet whose far-end row is read as a kernel object violates the boundary-noninternalization theorem.}

\independenceWitness{apophaticname, inscriptionpoint, socketuseledger, generatorfixedpoint: none combines forward-socket unification, local inscription readback, boundary noninternalization, and fixed-point ledger rows in one packet.}

The proposed Lean \texttt{TasteGate.lean} boundary is \texttt{lean4/BEDC/Derived/ApophaticFixedPointUp/TasteGate.lean}. It must provide \texttt{Nontrivial ApophaticFixedPointUp} and \texttt{FieldFaithful ApophaticFixedPointUp} instances for the same displayed carrier.

\closureat{ApophaticFixedPointUp}{seedStr}

\begin{closurestatus}{\ApophaticFixedPointUp}
  \constructivestory{An $\ApophaticFixedPointUp$ packet is generated from a forward-socket family row, apophatic far-end boundary row, local inscription point row, boundary ledger row, componentwise transports, displayed continuations, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:apophatic-fixed-point-carrier}, \autoref{thm:apophatic-fixed-point-namecert-obligations}, \autoref{thm:apophatic-fixed-point-boundary-noninternalization}, and \autoref{thm:apophatic-fixed-point-local-inscription-readback} bind the seed finite carrier over $S,T,I,L,H,C,P,N$ without claiming a checked TasteGate.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close an internal far-end object, host fixed-point theorem, Lean verification, nontriviality, field faithfulness, or bridge checking.}
  \upgradepath{Obligation closure requires the displayed $S,T,I,L,H,C,P,N$ carrier, its NameCert obligations, noninternalization and readback rows, and future TasteGate instances for the same packet.}
\end{closurestatus}
