\chapter{A Concrete Naming Certificate for $\InscriptionHashTraceUp$}
\label{ch:concrete-instances-inscription-hash-trace-namecert}
\origin{ai}

The $\InscriptionHashTraceUp$ packet realizes the hash-like apophatic fixed-point digest of \autoref{ch:visions-hash-like-apophatic-fixed-point} as a finite inscription trace. It sits beside the hash certificate of \autoref{ch:concrete-instances-hash-namecert}, the inscription event packet of \autoref{ch:concrete-instances-inscriptionevent-namecert}, the trace classifier of \autoref{ch:concrete-instances-inscription-trace-classifier-namecert}, the apophatic fixed-point packet of \autoref{ch:concrete-instances-apophaticfixedpoint-namecert}, and the hash-apophatic seal of \autoref{ch:concrete-instances-hashapophaticseal-namecert}. Its distinguishing role is that the visible digest, inscription event, trace classifier, refusal ledger, route audit, transport, continuation, package, and local name are one finite consumer-facing row.

\begin{definition}[InscriptionHashTrace carrier]
\label{def:inscription-hash-trace-carrier}
An $\InscriptionHashTraceUp$ carrier is a finite $\BHist$ packet
$$
T=(D,I,K,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the visible digest row read through the $\HashUp$ certificate surface;
\item $I$ is the finite inscription-event row that records where the digest is written into the observer-facing trace;
\item $K$ is the inscription trace-classifier row that keeps digest sameness distinct from trace-source equality;
\item $R$ is the refusal-ledger row blocking hidden preimage, global digest, and object-level $\mathsf{T}$ reads;
\item $A$ is the route-audit row showing that the digest read passes through inscription and classifier surfaces before the apophatic fixed-point seal is cited;
\item $H$ records componentwise $\hsame$ transports for $D,I,K,R,A,C,P,N$;
\item $C$ records the displayed $\Cont$ route through the digest, inscription event, classifier, refusal, audit, provenance, and naming rows;
\item $P$ is the $\Pkg$ provenance over $\HashUp$, $\InscriptionEventUp$, $\InscriptionTraceClassifierUp$, $\ApophaticFixedPointUp$, $\HashApophaticSealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\InscriptionHashTraceUp}$ row.
\end{enumerate}
The carrier contains no coordinate for a selected digest preimage, a global universe hash, source equality from digest sameness, an uninscribed trace read, an unaudited route, or an internal object named $\mathsf{T}$.
\end{definition}

\begin{theorem}[InscriptionHashTrace NameCert obligations]
\label{thm:inscription-hash-trace-namecert-obligations}
For the carrier of \autoref{def:inscription-hash-trace-carrier}, the local $\NameCert_{\InscriptionHashTraceUp}$ surface consists exactly of carrier admission for
$$
T=(D,I,K,R,A,H,C,P,N),
$$
visible digest exposure through $D$, inscription-event exposure through $I$, trace-classifier exposure through $K$, refusal-ledger exposure through $R$, route-audit exposure through $A$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.

Every accepted consumer preserves these rows together. In particular, the hash-like digest can be cited toward the apophatic fixed-point seal only after the inscription event, trace classifier, refusal ledger, and route audit have been displayed.
\end{theorem}
\begin{proof}
Project the accepted carrier in \autoref{def:inscription-hash-trace-carrier}. Its displayed rows are exactly $D,I,K,R,A,H,C,P,N$.

Read the sibling surfaces in order. The hash certificate supplies the visible digest row, the inscription-event packet supplies the finite writing site, the trace-classifier packet supplies the trace-facing classifier, and the hash-apophatic seal supplies the apophatic fixed-point endpoint only through a displayed refusal-aware route.

The rows $R$ and $A$ are part of the same carrier, so refusal and route audit are not optional side conditions. Since the carrier has no further coordinate, these rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[InscriptionHashTrace refusal nonescape]
\label{thm:inscription-hash-trace-refusal-nonescape}
Every accepted $\InscriptionHashTraceUp$ consumer that reads $D$ must also read $I,K,R,A,H,C,P,N$. Consequently the packet exports no selected preimage, no global universe digest, no source equality obtained from digest sameness, no uninscribed trace, no unaudited route to the seal, and no internal $\mathsf{T}$ object.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:inscription-hash-trace-namecert-obligations}. They place every public digest read inside the finite carrier $T=(D,I,K,R,A,H,C,P,N)$.

The inscription event and trace classifier are read before the refusal and audit rows. Thus a consumer cannot detach the digest from the trace site or replace classifier sameness by source equality.

Finally inspect the carrier inventory. It contains no preimage selector, global digest, uninscribed trace coordinate, unaudited route coordinate, or internal $\mathsf{T}$ object, so none of those readings can escape the displayed packet.
\end{proof}

\begin{theorem}[InscriptionHashTrace audit route]
\label{thm:inscription-hash-trace-audit-route}
Any accepted route from an $\InscriptionHashTraceUp$ digest row to the $\HashApophaticSealUp$ endpoint factors through the displayed chain
$$
\HashUp \to \InscriptionEventUp \to \InscriptionTraceClassifierUp \to R \to A \to H,C,P,N.
$$
The route cannot cite the apophatic fixed-point seal before the digest evidence, inscription event, classifier row, refusal ledger, route audit, componentwise $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows have all been exposed.
\end{theorem}
\leanchecked{BEDC.Derived.InscriptionHashTraceUp.TasteGate.InscriptionHashTrace\_audit\_route}
\begin{proof}
Use \autoref{thm:inscription-hash-trace-namecert-obligations} to put the route inside the accepted carrier. The only digest-facing row is $D$, and it is packaged with the inscription event $I$ and classifier row $K$.

Next read $R$ and $A$. The refusal row records the blocked preimage, global digest, and object-level $\mathsf{T}$ readings, while the audit row records the permitted route toward the hash-apophatic seal.

The remaining rows $H,C,P,N$ transport, replay, cite, and name only that finite route. Hence any seal-facing consumer sees the displayed chain and no shortcut around it.
\end{proof}

\begin{theorem}[InscriptionHashTrace field-faithful prediction]
\label{thm:inscription-hash-trace-fieldfaithful-prediction}
A Lean TasteGate carrier for $\InscriptionHashTraceUp$ is field-faithful only when equality of the projected rows $D,I,K,R,A,H,C,P,N$ determines equality of the whole packet, and it is nontrivial only when at least one displayed digest row can vary while the remaining rows stay fixed. Dropping $I$, $K$, $R$, or $A$ makes the carrier unable to witness the inscription hash trace route.
\end{theorem}
\leanchecked{BEDC.Derived.InscriptionHashTraceUp.TasteGate.InscriptionHashTraceTasteGate\_single\_carrier\_alignment}
\begin{proof}
The carrier of \autoref{def:inscription-hash-trace-carrier} is a constructor over the nine displayed rows. Equality of the projected rows therefore gives equality of the constructor instance, while changing the digest row gives a nontrivial witness pair.

The route theorem above supplies the semantic boundary for this encoding. Without the inscription event, the digest is not trace-local; without the classifier, digest sameness can be mistaken for trace-source equality; without the refusal ledger, hidden preimage and object-level $\mathsf{T}$ readings are not blocked; and without the audit row, the route to the hash-apophatic seal is not displayed.
\end{proof}

\falsifiablePrediction{Any accepted $\InscriptionHashTraceUp$ consumer factors through the displayed hash digest, inscription event, trace classifier, refusal ledger, route-audit, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows before it can cite the apophatic fixed-point seal.}

\independenceWitness{hash, inscriptionevent, inscriptiontraceclassifier, apophaticfixedpoint, and hashapophaticseal: no bijection preserves the displayed rows because $\InscriptionHashTraceUp$ alone binds the digest row, inscription event, trace classifier, refusal ledger, route audit, transport, continuation, provenance, and local NameCert row in one carrier.}

The Lean TasteGate boundary is \texttt{lean4/BEDC/Derived/InscriptionHashTraceUp/TasteGate.lean}. It includes explicit \texttt{Nontrivial InscriptionHashTraceUp} and \texttt{FieldFaithful InscriptionHashTraceUp} instances for the displayed finite carrier.

\closureat{InscriptionHashTraceUp}{seedStr}

\begin{closurestatus}{\InscriptionHashTraceUp}
  \constructivestory{An $\InscriptionHashTraceUp$ packet is generated from a visible digest row, inscription-event row, trace-classifier row, refusal-ledger row, route-audit row, componentwise hsame transports, displayed Cont routes, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:inscription-hash-trace-carrier}, \autoref{thm:inscription-hash-trace-namecert-obligations}, \autoref{thm:inscription-hash-trace-refusal-nonescape}, \autoref{thm:inscription-hash-trace-audit-route}, and \autoref{thm:inscription-hash-trace-fieldfaithful-prediction} bind the carrier, NameCert obligations, refusal nonescape, audit route, and field-faithful prediction rows for the finite inscription hash trace packet.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.InscriptionHashTraceUp.TasteGate.InscriptionHashTraceTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close hidden preimages, global universe digests, source equality from digest sameness, unaudited routes, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier, classifier, refusal, audit-route, nontriviality, and field-faithfulness rows.}
\end{closurestatus}
