\providecommand{\ChurchEliminatorRegressionMatrixUp}{\mathsf{ChurchEliminatorRegressionMatrix}^{\uparrow}}

\chapter{A Concrete Naming Certificate for $\ChurchEliminatorRegressionMatrixUp$}
\label{ch:concrete-instances-church-eliminator-regression-matrix-namecert}
\origin{ai}

The $\ChurchEliminatorRegressionMatrixUp$ packet realizes the Church eliminator rows of \autoref{ch:metacic-typedexamples-audit-map} as a finite checker and beta-regression matrix. It sits beside the MetaCIC gallery of \autoref{ch:concrete-instances-metacictypedexamplesgallery-namecert}, the coverage matrix of \autoref{ch:concrete-instances-typedexamplecoveragematrix-namecert}, the audit budget of \autoref{ch:concrete-instances-typedexampleauditbudget-namecert}, the application route of \autoref{ch:concrete-instances-metacictypedexamplesapplicationroute-namecert}, and the beta-step boundary of \autoref{ch:concrete-instances-betastepboundary-namecert}. Those siblings expose gallery, coverage, budget, application, and beta-boundary rows; this chapter binds the Church boolean, natural-number, list, and sum eliminators as one row-indexed regression object.

\begin{definition}[Church eliminator regression matrix carrier]
\label{def:church-eliminator-regression-matrix-carrier}
A $\ChurchEliminatorRegressionMatrixUp$ carrier is a finite $\BHist$ packet
$$
E=(F,G,L,C,B,S,X,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite family row with exactly the Church boolean, natural-number, list, and sum eliminator families;
\item $G$ records the gallery entry for the same family row, including the displayed type former, constructors, and eliminator term;
\item $L$ records the local eliminator shape, respectively boolean branch selection, natural-number recursor, list fold, and sum case analysis;
\item $C$ records the checker acceptance row for the displayed eliminator;
\item $B$ records the selected beta-regression row for the same eliminator family;
\item $S$ records the regression-spend row licensed for that family;
\item $X$ is the exactness row asserting that every accepted family in $F$ has exactly the displayed $G,L,C,B,S$ cells and no extra eliminator family;
\item $H$ records componentwise $\hsame$ transports for family, gallery, eliminator, checker, beta, spend, exactness, continuation, provenance, and naming rows;
\item $K$ records the displayed $\Cont$ routes by which eliminator-regression consumers read the same row;
\item $P$ is the $\Pkg$ provenance over the TypedExamples gallery, coverage matrix, audit budget, application route, beta-step boundary, transport, continuation, and exactness rows;
\item $N$ is the local $\NameCert_{\ChurchEliminatorRegressionMatrixUp}$ row.
\end{enumerate}
The carrier has no coordinate for arbitrary eliminator soundness, global normalization, subject reduction, confluence, unbounded beta closure, or a regression spend not indexed by one of the four displayed Church families.
\end{definition}

\begin{theorem}[Church eliminator regression matrix NameCert obligations]
\label{thm:church-eliminator-regression-matrix-namecert-obligations}
For the carrier of \autoref{def:church-eliminator-regression-matrix-carrier}, the local $\NameCert_{\ChurchEliminatorRegressionMatrixUp}$ surface consists exactly of carrier admission for
$$
E=(F,G,L,C,B,S,X,H,K,P,N),
$$
family exposure through the four displayed Church eliminator rows, gallery exposure through $G$, eliminator-shape exposure through $L$, checker exposure through $C$, beta-regression exposure through $B$, spend exposure through $S$, row exactness through $X$, and transport, continuation, provenance, and local naming through $H,K,P,N$.
\end{theorem}
\begin{proof}
Project the displayed carrier. The family row $F$ is read before any eliminator cell is available, and it lists only the boolean, natural-number, list, and sum eliminator families.

For each displayed family, the rows $G,L,C,B,S$ are paired by the same row index. Thus a consumer reaches the gallery entry, eliminator shape, checker acceptance, beta-regression cell, and spend cell only as cells of the same Church eliminator row.

The exactness row $X$ exhausts the local NameCert surface. The rows $H,K,P,N$ preserve, route, package, and name the same finite packet, while no carrier coordinate supplies arbitrary eliminator metatheory or an unindexed spend.
\end{proof}

\begin{theorem}[Church eliminator regression matrix family exactness]
\label{thm:church-eliminator-regression-matrix-family-exactness}
Every accepted $\ChurchEliminatorRegressionMatrixUp$ packet has exactly four eliminator families: Church booleans, Church natural numbers, Church lists, and Church sums. Each family row carries its displayed gallery, eliminator-shape, checker, beta-regression, and spend cells, and every displayed checker or beta-regression cell belongs to one of those four family rows.
\end{theorem}
\begin{proof}
Read the family row $F$ and the exactness row $X$. By construction, $F$ has the four displayed Church eliminator families and no fifth family coordinate.

The exactness row $X$ pairs each family with its $G,L,C,B,S$ cells. Hence a checker cell or beta-regression cell cannot be read before choosing one of the displayed Church eliminator families.

Conversely, each listed family receives the paired gallery, eliminator-shape, checker, beta-regression, and spend cells from $X$. This gives both inclusion directions for the finite family inventory.
\end{proof}

\begin{theorem}[Church eliminator regression matrix non-escape]
\label{thm:church-eliminator-regression-matrix-nonescape}
Every eliminator-regression consumer of an accepted $\ChurchEliminatorRegressionMatrixUp$ carrier reads the Church boolean, natural-number, list, and sum eliminator rows only through
$$
F,G,L,C,B,S,X,H,K,P,N.
$$
The consumer cannot replace a missing family, checker, beta-regression, or spend cell by the general coverage matrix alone, by an ambient checker theorem, by an application-route cell, or by an unindexed beta-boundary row.
\end{theorem}
\begin{proof}
Let an eliminator-regression consumer be given. Its public read passes through the continuation row $K$, so it reaches only the displayed family, gallery, eliminator, checker, beta, spend, exactness, transport, provenance, and local naming rows.

The sibling packets provide provenance for the cells, but the row-indexed eliminator pairing is carried by $F$ and $X$. A general coverage matrix, application route, audit budget, or beta-step boundary does not by itself name the combined Church eliminator regression row.

No coordinate in the carrier names an ambient checker theorem, an arbitrary beta-boundary cell, or an unindexed spend. Therefore the accepted consumer surface is exactly the finite Church eliminator regression matrix.
\end{proof}

\falsifiablePrediction{An eliminator regression consumer that accepts a Church family without the displayed family, checker, beta-regression, and spend rows refutes the packet.}

\independenceWitness{Nearest siblings: metacictypedexamplesgallery, typedexamplecoveragematrix, typedexampleauditbudget, metacictypedexamplesapplicationroute, betastepboundary. None is bijective to ChurchEliminatorRegressionMatrixUp because each sibling omits at least one row among the four-family eliminator index, checker cells, beta-regression cells, spend cells, and local exactness row.}

The Lean follow-up for namespace $\mathsf{BEDC.Derived.ChurchEliminatorRegressionMatrixUp.TasteGate}$ must include $\mathsf{Nontrivial}\ \ChurchEliminatorRegressionMatrixUp$ and $\mathsf{FieldFaithful}\ \ChurchEliminatorRegressionMatrixUp$ instances with an explicit witness pair and mk-field projections.

\closureat{ChurchEliminatorRegressionMatrixUp}{seedStr}

\begin{closurestatus}{\ChurchEliminatorRegressionMatrixUp}
  \constructivestory{A $\ChurchEliminatorRegressionMatrixUp$ packet is generated from four Church eliminator family rows, paired gallery cells, eliminator-shape cells, checker cells, beta-regression cells, spend cells, exactness rows, componentwise transports, continuation routes, provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:church-eliminator-regression-matrix-carrier}, \autoref{thm:church-eliminator-regression-matrix-namecert-obligations}, \autoref{thm:church-eliminator-regression-matrix-family-exactness}, and \autoref{thm:church-eliminator-regression-matrix-nonescape} bind the four-family Church eliminator regression matrix.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close arbitrary eliminator soundness, subject reduction, confluence, global normalization, unrestricted beta closure, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, four-family exactness, paired checker and beta-regression exposure, spend confinement, componentwise transport, displayed continuation, provenance, and local naming rows.}
\end{closurestatus}
