\chapter{A Concrete Naming Certificate for $\LayeredRelationSiteUp$}
\label{ch:concrete-instances-layeredrelationsite-namecert}
\origin{ai}

The $\LayeredRelationSiteUp$ packet realizes the layered relation certificate of \autoref{ch:visions-layered-relation-certificate} as finite $\BHist$ data. It sits beside the frame-refusal audit of \autoref{ch:concrete-instances-relationalframeaudit-namecert}, the observer classifier of \autoref{ch:concrete-instances-observerhsameclassifier-namecert}, the local gluing surface of \autoref{ch:concrete-instances-sheaf-namecert}, and the compiler route of \autoref{ch:concrete-instances-certificatecompiler-namecert}. Those siblings supply frame refusal, observer comparison, cover-local transport, and certificate movement; this packet binds relation rows, refinement chains, locality gates, and refusal ledgers as one NameCert site.

\falsifiablePrediction{If the LayeredRelationSiteUp carrier is atomic, then any reduction to RelationalFrameAuditUp loses either the refinement-chain row or the locality-gate refusal row.}

\independenceWitness{relationalframeaudit, observerhsameclassifier, sheaf, certificatecompiler: none is bijective to $\LayeredRelationSiteUp$ because the site carrier carries source-site rows, relation rows, refinement-chain rows, locality-gate refusals, transport, replay, provenance, and local NameCert rows in one packet. RelationalFrameAuditUp carries frame refusal without the refinement chain, ObserverHsameClassifierUp carries observer comparison without the source-site ledger, SheafUp carries locality and gluing without the relation-refusal ledger, and CertificateCompilerUp carries certificate movement without the layered relation site.}

\begin{definition}[LayeredRelationSite carrier]
\label{def:layered-relation-site-carrier}
A $\LayeredRelationSiteUp$ carrier is a finite $\BHist$ packet
$$
L=(S_A,S_B,R_A,R_B,J,G,T,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S_A$ and $S_B$ are the two source-site rows whose relation is being certified;
\item $R_A$ and $R_B$ are the relation rows read from the two sites, including the displayed classifier surfaces consumed by the comparison;
\item $J$ is the refinement-chain row recording the finite layer correspondence and the obstruction rows that force each classifier split;
\item $G$ is the locality-gate row deciding which relation reads are admitted locally and which requests are refused;
\item $T$ records the relation transport row that moves accepted source-site comparisons componentwise through $\hsame$;
\item $E$ records replay rows for relation reads, refinement-chain steps, locality-gate decisions, and refusal ledger entries;
\item $H$ records componentwise $\hsame$ transport for $S_A,S_B,R_A,R_B,J,G,T,E,P,N$;
\item $C$ records the displayed $\Cont$ routes through which downstream consumers replay relation rows, refinement rows, locality decisions, and refusal rows;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\RelationalFrameAuditUp$, $\ObserverHsameClassifierUp$, $\SheafUp$, $\CertificateCompilerUp$, and local relation-site dependencies;
\item $N$ is the local $\NameCert_{\LayeredRelationSiteUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through these rows. It has no coordinate for object identity between the two sites, global-frame synchronization, host powerset equality, unrecorded compiler semantics, empirical physical force, or subject-substance.
\end{definition}
\leandef{BEDC.Derived.LayeredRelationSiteUp.LayeredRelationSiteUp}

\begin{theorem}[LayeredRelationSite NameCert obligations]
\label{thm:layered-relation-site-namecert-obligations}
For the carrier of \autoref{def:layered-relation-site-carrier}, the local $\NameCert_{\LayeredRelationSiteUp}$ surface consists of five obligations:
\begin{enumerate}
\item carrier exposure: every accepted packet exposes exactly $L=(S_A,S_B,R_A,R_B,J,G,T,E,H,C,P,N)$;
\item relation-row admission: each comparison is read through the displayed source-site and relation rows $S_A,S_B,R_A,R_B$;
\item refinement-chain exactness: the layer map and obstruction-to-classifier-split data are exactly the row $J$;
\item locality-gate refusal: every nonlocal or over-reading request is routed to the displayed gate and refusal row $G$;
\item componentwise transport and replay: relation rows, refinement-chain rows, gate decisions, refusal ledgers, package provenance, and local naming are transported only by $T,H$ and replayed only by $E,C$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is projection from the finite tuple in \autoref{def:layered-relation-site-carrier}. The accepted packet has no fields outside $S_A,S_B,R_A,R_B,J,G,T,E,H,C,P,N$.

Relation-row admission is the projection to the two source-site rows and their relation rows. The packet can compare only the displayed $R_A$ and $R_B$ surfaces over $S_A$ and $S_B$, so it cannot identify the source sites as objects.

Refinement-chain exactness is the projection to $J$. The chain row carries the layer map and the obstruction rows that force classifier splits, matching the certificate discipline of \autoref{ch:visions-layered-relation-certificate}.

Locality-gate refusal is the projection to $G$. A request outside the displayed relation read or locality site has no accepted output row except the gate refusal.

Finally, transport and replay are componentwise. The row $T$ records relation transport, $H$ records $\hsame$ transport over all carrier coordinates, and $E,C$ replay the same route with the package and local naming rows $P,N$.
\end{proof}

\begin{theorem}[LayeredRelationSite independence boundary]
\label{thm:layered-relation-site-independence-boundary}
The siblings $\RelationalFrameAuditUp$, $\ObserverHsameClassifierUp$, $\SheafUp$, and $\CertificateCompilerUp$ are independence witnesses for $\LayeredRelationSiteUp$. No bijection from any one sibling carrier to the carrier of \autoref{def:layered-relation-site-carrier} preserves all carrier rows and all five obligations of \autoref{thm:layered-relation-site-namecert-obligations}.
\end{theorem}
\begin{proof}
Compare $\RelationalFrameAuditUp$ first. It supplies the no-global-frame and refusal discipline of \autoref{ch:concrete-instances-relationalframeaudit-namecert}, but it has no row that simultaneously records the layered refinement chain $J$ and the relation-site locality gate $G$.

Compare $\ObserverHsameClassifierUp$ next. It supplies an observer-history classifier and transport route, but it does not carry the two source-site rows, the paired relation rows, or the obstruction-driven refinement chain required by the relation site.

The $\SheafUp$ sibling supplies local gluing and cover-sensitive transport, while $\CertificateCompilerUp$ supplies finite certificate movement. Neither sibling carries the paired relation rows together with the gate-refusal ledger and the layered relation provenance row.

Thus any attempted bijection loses at least one carrier coordinate or one NameCert obligation: relation admission, refinement-chain exactness, locality-gate refusal, or componentwise relation replay. The $\LayeredRelationSiteUp$ carrier is therefore not a renamed copy of any listed sibling.
\end{proof}

\begin{theorem}[LayeredRelationSite downstream gate target]
\label{thm:layered-relation-site-downstream-gate-target}
The Lean-facing downstream surface for $\LayeredRelationSiteUp$ is the packet family recorded under $\mathsf{Derived/LayeredRelationSiteUp/TasteGate.lean}$ with explicit $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances. The gate checks that the source-site rows, relation rows, refinement-chain row, locality-gate refusal row, transport, replay, provenance, and local naming row remain recoverable from the admitted packet.
\end{theorem}
\begin{proof}
The carrier and NameCert obligations already name the row inventory the gate must inspect. Nontriviality is witnessed by two packets differing in a visible source-site row. Field faithfulness is witnessed by projection of all carrier rows from the constructor.

The downstream gate therefore does not add a new relation semantics. It records that the finite site packet has a real display, that every displayed field can be recovered from that display, and that the relation-site carrier is not a singleton placeholder.
\end{proof}
\leanchecked{BEDC.Derived.LayeredRelationSiteUp.taste\_gate}

\closureat{LayeredRelationSiteUp}{seedStr}

\begin{closurestatus}{\LayeredRelationSiteUp}
  \constructivestory{A $\LayeredRelationSiteUp$ packet is generated from two source-site rows, paired relation rows, a refinement-chain row, a locality-gate refusal row, relation transport, replay, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:layered-relation-site-carrier}, \autoref{thm:layered-relation-site-namecert-obligations}, and \autoref{thm:layered-relation-site-independence-boundary} bind the layered relation certificate as a finite relation-site NameCert packet over source-site rows, relation rows, refinement chains, locality gates, refusal ledgers, transport, replay, provenance, and local naming.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.LayeredRelationSiteUp.taste\_gate}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close object identity between related sites, empirical physics, subject-substance, global-frame synchronization, host powerset equality, compiler semantics, or bridge checking.}
  \upgradepath{Scoped closure requires checked paper-side exactness for relation admission, refinement-chain replay, locality-gate refusal, dependency provenance, and downstream consumer boundaries over the same finite rows.}
\end{closurestatus}
