\chapter{A Concrete Naming Certificate for $\LayeredRelationCertUp$}
\label{ch:concrete-instances-layered-relation-cert-namecert}
\origin{ai}

The $\LayeredRelationCertUp$ packet realizes the relation-certificate discipline of \autoref{ch:visions-layered-relation-certificate} as a finite $\NameCert$ surface. It consumes the local inscription row discipline of \autoref{ch:concrete-instances-inscriptionevent-namecert}, the gap ledger surface of \autoref{ch:concrete-instances-inscription-gap-ledger-namecert}, the quotient-soundness refusal boundary of \autoref{ch:concrete-instances-quotient-soundness-boundary-namecert}, and the audited generator route of \autoref{ch:concrete-instances-authorizedgeneratorrecursor-namecert}. The packet does not assert that two objects are identical; it names the exact rows through which a same-schema relation may be consumed.

\begin{definition}[Layered relation NameCert row carrier]
\label{def:layered-relation-namecert-row-carrier}
A $\LayeredRelationCertUp$ carrier is a finite packet
$$
R=(A,B,L,U,V,W,F,H,C,P,G,N),
$$
where $A$ and $B$ are the two displayed source-chain rows, $L$ is the finite two-chain layer map, $U$ is the same-schema exactness row, $V$ is the preserved-structure row, $W$ is the not-preserved row, $F$ is the failure-boundary row, $H$ is componentwise $\hsame$ transport, $C$ is displayed continuation replay, $P$ is package provenance, $G$ is the gap and quotient-soundness boundary row, and $N$ is the local $\NameCert_{\LayeredRelationCertUp}$ row.

The carrier has no coordinate for object identity between the two source domains, empirical law transfer, quotient-stream equality, subject-substance transfer, global-frame transfer, or an unbounded analogy principle.
\end{definition}

\begin{theorem}[Layered relation NameCert row obligations]
\label{thm:layered-relation-namecert-row-obligations}
For an accepted $\LayeredRelationCertUp$ packet, the local $\NameCert$ surface consists exactly of source-chain admission through $A,B$, finite layer-map exposure through $L$, same-schema exactness through $U$, preserved-structure exposure through $V$, explicit non-preservation through $W$, failure-boundary exposure through $F$, componentwise transport through $H$, replay through $C$, provenance through $P$, gap and quotient-soundness refusal through $G$, and the local naming row $N$.
\end{theorem}
\begin{proof}
Start with the row carrier of \autoref{def:layered-relation-namecert-row-carrier}. It lists the only coordinates available to a consumer, so same-schema evidence must read the two source chains, the finite layer map, the exactness row, the preserved row, and the not-preserved row from the same packet.

The inscription-side rows are anchored by \autoref{ch:concrete-instances-inscriptionevent-namecert} and \autoref{ch:concrete-instances-inscription-gap-ledger-namecert}. They keep the two source-chain displays and the gap ledger visible rather than allowing a bare analogy token to stand in for evidence.

The refusal side is anchored by \autoref{ch:concrete-instances-quotient-soundness-boundary-namecert} and the audited generator route of \autoref{ch:concrete-instances-authorizedgeneratorrecursor-namecert}. These boundaries keep quotient soundness, generator authority, and downstream consumption attached to the displayed rows $F,G,H,C,P,N$.
\end{proof}
\leanchecked{BEDC.Derived.LayeredRelationCertUp.LayeredRelationCert\_namecert\_row\_obligations}

\begin{theorem}[Layered relation NameCert refusal]
\label{thm:layered-relation-namecert-row-refusal}
No accepted $\LayeredRelationCertUp$ packet exports object identity between its two source domains, empirical transfer, quotient equality, subject-substance transfer, global-frame transfer, or a hidden bridge beyond the rows
$$
(A,B,L,U,V,W,F,H,C,P,G,N).
$$
In particular, a consumer that omits either the not-preserved row $W$ or the failure-boundary row $F$ cannot read the packet as same-schema evidence.
\end{theorem}
\begin{proof}
Apply \autoref{thm:layered-relation-namecert-row-obligations}. The row obligations place not-preserved content and the failure boundary inside the same local naming surface as the preserved and exactness rows.

The quotient-soundness boundary prevents the same-schema row $U$ from becoming quotient equality, while the inscription-gap ledger prevents missing source rows from being filled by a hidden bridge. Hence object identity, empirical transfer, subject-substance transfer, and global-frame transfer have no carrier coordinate.

If $W$ or $F$ is absent, the consumer has either no explicit refusal of non-preserved content or no boundary at which the relation weakens. Such a packet is therefore not an accepted same-schema certificate.
\end{proof}

\begin{theorem}[Layered relation NameCert nontriviality]
\label{thm:layered-relation-namecert-row-nontriviality}
The $\LayeredRelationCertUp$ carrier is not reducible to the source-chain packet of inscriptionevent, the gap packet of inscriptiongapledger, the quotient-refusal packet of quotientsoundnessboundary, the generator-audit packet of authorizedgeneratorrecursor, or the audit-map packet of auditmapfamily. Its nontrivial surface is the simultaneous presence of a two-chain layer map together with preserved, not-preserved, and failure-boundary rows.
\end{theorem}
\begin{proof}
Compare the displayed row sets. The inscriptionevent sibling supplies source inscription rows but not the two-chain layer map with preserved and not-preserved relation rows. The inscriptiongapledger sibling supplies the gap ledger but not same-schema exactness or the preserved-structure row.

The quotientsoundnessboundary sibling supplies a refusal boundary for quotient over-readings, while authorizedgeneratorrecursor supplies an audited generator route. Neither sibling contains both source chains together with $L,U,V,W,F$ as one relation certificate.

The auditmapfamily sibling supplies audit-map methodology, not a local relation packet with the two-chain layer map plus preserved, not-preserved, and failure-boundary surface. Therefore the carrier is nontrivial relative to all named siblings.
\end{proof}

\begin{theorem}[Layered relation NameCert field faithfulness]
\label{thm:layered-relation-namecert-row-field-faithful}
Every downstream consumer that reads a $\LayeredRelationCertUp$ packet as same-schema evidence must preserve the field roles of $A,B,L,U,V,W,F,H,C,P,G,N$. A transported read may rename the packet only through $H,C,P,N$; it may not collapse $A$ with $B$, read $V$ without $W$, read $U$ without $F$, or move the boundary row $G$ into a source-chain coordinate.
\end{theorem}
\begin{proof}
Use the NameCert obligations of \autoref{thm:layered-relation-namecert-row-obligations}. They assign each public field its role before the local certificate can be consumed.

Next apply the refusal theorem \autoref{thm:layered-relation-namecert-row-refusal}. It blocks the only collapses that would turn same-schema evidence into identity, empirical transfer, quotient equality, or hidden bridge content.

The remaining transport rows $H,C,P,N$ only preserve, replay, package, and name the displayed packet. Since none of those rows adds a new source-chain, exactness, preserved, not-preserved, or boundary coordinate, the field roles are faithful under downstream consumption.
\end{proof}

\falsifiablePrediction{A relation certificate that omits either the not-preserved row or the failure-boundary row cannot be consumed as same-schema evidence by any downstream bridge chapter.}

\independenceWitness{Nearest siblings: inscriptionevent, inscriptiongapledger, quotientsoundnessboundary, authorizedgeneratorrecursor, and auditmapfamily. None is bijective to $\LayeredRelationCertUp$ because none has the two-chain layer map plus preserved, not-preserved, and failure-boundary surface in one finite NameCert packet.}

Later Lean work must provide $\mathsf{Nontrivial}\ \LayeredRelationCertUp$ and $\mathsf{FieldFaithful}\ \LayeredRelationCertUp$ instances in \texttt{TasteGate.lean}.
