\chapter{A Concrete Naming Certificate for $\KernelInductiveEliminatorUp$}
\label{ch:concrete-instances-kernelinductiveeliminator-namecert}
\origin{ai}

The $\KernelInductiveEliminatorUp$ packet realizes the eliminator side of the kernel-acceptance witness of \autoref{ch:visions-kernel-acceptance-as-audit-witness} as finite $\NameCert$ data. It sits beside the inductive-declaration packet of \autoref{ch:concrete-instances-kernelinductiveacceptance-namecert}, the accepted-declaration witness of \autoref{ch:concrete-instances-kernelacceptancewitness-namecert}, the generator-closure surface of \autoref{ch:concrete-instances-generatorclosure-namecert}, the type-classifier membership surface of \autoref{ch:concrete-instances-typeclassifiermembership-namecert}, and the subject-reduction boundary of \autoref{ch:concrete-instances-subjectreduction-namecert}. Those siblings record declaration acceptance, generator closure, type membership, and preservation-facing rows; this packet records the emitted case-analysis rule rows that must be displayed before any eliminator consumer reads them.

\begin{definition}[KernelInductiveEliminator carrier]
\label{def:kernel-inductive-eliminator-carrier}
A $\KernelInductiveEliminatorUp$ carrier is a finite $\BHist$ packet
$$
E=(D,S,L,M,R,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the accepted inductive declaration row already named by $\KernelInductiveAcceptanceUp$;
\item $S$ is the constructor-signature row whose finite constructor inventory determines the available case branches;
\item $L$ is the emitted eliminator-name row, including the recursor, induction-principle, motive, minor-premise, and computation-rule names emitted for $D$;
\item $M$ is the motive-and-branch arity row, recording the finite arity match between constructor signatures and eliminator minor premises;
\item $R$ is the emitted-rule ledger, listing exactly the case-analysis and computation rows that may be read by downstream consumers;
\item $B$ is the boundary row that refuses a consumer asking for a host eliminator primitive not displayed in $R$;
\item $H$ records componentwise $\hsame$ transports for $D,S,L,M,R,B,P,N$;
\item $C$ records the displayed $\Cont$ routes from accepted declaration to constructor signatures, from signatures to emitted eliminator rows, from eliminator rows to motive-and-branch arity, and from emitted rules to consumers;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:visions-kernel-acceptance-as-audit-witness}, \autoref{ch:concrete-instances-kernelinductiveacceptance-namecert}, \autoref{ch:concrete-instances-kernelacceptancewitness-namecert}, \autoref{ch:concrete-instances-generatorclosure-namecert}, \autoref{ch:concrete-instances-typeclassifiermembership-namecert}, \autoref{ch:concrete-instances-subjectreduction-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\KernelInductiveEliminatorUp}$ row.
\end{enumerate}
The carrier contains no hidden host recursor, no unlisted computation rule, no ambient induction theorem, and no subject-reduction proof beyond the displayed emitted-rule surface.
\end{definition}

\begin{theorem}[KernelInductiveEliminator NameCert obligations]
\label{thm:kernel-inductive-eliminator-namecert-obligations}
For the carrier of \autoref{def:kernel-inductive-eliminator-carrier}, the local $\NameCert_{\KernelInductiveEliminatorUp}$ surface consists of five finite obligations:
\begin{enumerate}
\item carrier exposure for the packet $E=(D,S,L,M,R,B,H,C,P,N)$;
\item declaration handoff, requiring the row $D$ to be consumed from the accepted inductive declaration surface of $\KernelInductiveAcceptanceUp$;
\item branch arity exactness, requiring the eliminator motive and minor-premise rows in $L,M$ to match the constructor-signature row $S$;
\item emitted-rule ledger exactness, requiring every case-analysis or computation read to be one of the displayed entries of $R$;
\item primitive non-escape, requiring any attempted host eliminator primitive outside $R$ to land in the refusal boundary $B$ rather than in a consumer route.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is projection from the displayed $\BHist$ packet. The accepted declaration, constructor signature, eliminator names, motive-and-branch arities, emitted-rule ledger, refusal boundary, transport, route, provenance, and local name are coordinates of one finite object.

The declaration handoff reads $D$ through \autoref{ch:concrete-instances-kernelinductiveacceptance-namecert}. That chapter records the accepted inductive declaration and constructor-signature ledger, while the present packet starts only after those rows are available.

Branch arity exactness is the local comparison between $S$ and $M$. Each constructor listed in $S$ has exactly the minor-premise row recorded in $M$, and the eliminator names in $L$ are public only through that finite comparison.

Finally, emitted-rule exactness and primitive non-escape are read from $R$ and $B$. A downstream generator, type-classifier, or subject-reduction consumer may consume a displayed emitted rule, but a request for an unrecorded host primitive has no coordinate in $E$ and is routed to the refusal boundary.
\end{proof}

\begin{theorem}[KernelInductiveEliminator nontrivial boundary]
\label{thm:kernel-inductive-eliminator-nontrivial-boundary}
The $\KernelInductiveEliminatorUp$ packet has a nontrivial boundary for TasteGate: an accepted packet displays at least one emitted-rule row through $D,S,L,M,R,H,C,P,N$, while a consumer asking for an eliminator primitive absent from $R$ lands in $B$ and is not accepted as a displayed eliminator read. The Lean file \texttt{lean4/BEDC/Derived/KernelInductiveEliminatorUp/TasteGate.lean} must provide $\mathsf{Nontrivial}\ \KernelInductiveEliminatorUp$ for this finite carrier.
\end{theorem}
\begin{proof}
The accepted side is visible because the carrier exposes an emitted-rule ledger $R$ after the declaration, constructor-signature, eliminator-name, and arity rows have been displayed.

The refused side is visible because $B$ is a separate row. A request for an eliminator primitive not listed in $R$ cannot be reclassified as an emitted-rule read without adding a coordinate absent from the carrier.

Thus the boundary has two distinguishable finite outcomes: displayed emitted-rule consumption and refusal of an unrecorded primitive.
\end{proof}

\begin{theorem}[KernelInductiveEliminator field-faithful boundary]
\label{thm:kernel-inductive-eliminator-field-faithful-boundary}
The $\KernelInductiveEliminatorUp$ packet is field-faithful for TasteGate: any accepted read that preserves $D,S,L,M,R,B,H,C,P,N$ componentwise preserves the emitted eliminator surface, and any read that drops $L$, $M$, or $R$ is not a faithful read of this carrier. The Lean file \texttt{lean4/BEDC/Derived/KernelInductiveEliminatorUp/TasteGate.lean} must provide $\mathsf{FieldFaithful}\ \KernelInductiveEliminatorUp$ for this finite carrier.
\end{theorem}
\begin{proof}
Start with two accepted reads related by the displayed $\hsame$ rows. Componentwise transport preserves the accepted declaration, constructor signature, eliminator names, arity ledger, emitted-rule ledger, refusal boundary, route, provenance, and local name together.

The fields $L$, $M$, and $R$ distinguish this carrier from the surrounding acceptance packets. $\KernelInductiveAcceptanceUp$ can expose accepted declarations and constructor signatures, but it does not by itself expose the full emitted-rule consumer surface isolated here.

If any of $L$, $M$, or $R$ is absent, the read may still be a declaration-acceptance read, a generator-closure read, a type-membership read, or a subject-reduction boundary read. It is not a faithful read of $\KernelInductiveEliminatorUp$.
\end{proof}

\falsifiablePrediction{An accepted $\KernelInductiveEliminatorUp$ packet cannot export a host eliminator primitive unless the requested primitive appears as a displayed emitted-rule row in $R$.}

\independenceWitness{KernelInductiveAcceptance, KernelAcceptanceWitness, GeneratorClosure, TypeClassifierMembership, SubjectReduction: declaration acceptance, accepted-declaration witnessing, generator closure, type membership, and preservation rows are not bijective to emitted eliminator discharge because none of the five sibling surfaces simultaneously records eliminator names, motive-and-branch arity, emitted computation rows, and refusal of host primitives as the packet $E=(D,S,L,M,R,B,H,C,P,N)$ does.}

\closureat{KernelInductiveEliminatorUp}{seedStr}

\begin{closurestatus}{\KernelInductiveEliminatorUp}
  \constructivestory{A $\KernelInductiveEliminatorUp$ packet is generated from an accepted inductive declaration row, constructor-signature row, emitted eliminator-name row, motive-and-branch arity row, emitted-rule ledger, host-primitive refusal boundary, componentwise $\hsame$ transport, displayed $\Cont$ routes, provenance, and local naming. The carrier first consumes the accepted declaration, then compares constructor signatures with eliminator minor premises, and finally exposes only the emitted rules listed in the ledger. The classifier admits eliminator use as finite emitted-rule data and routes any absent primitive to the refusal boundary.}
  \theoryclosure{\seedClosure}
  \scopeclosed{This chapter binds the kernel inductive eliminator carrier, NameCert obligations, nontrivial boundary, field-faithful boundary, prediction, and independence witness.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{It does not claim hidden host recursors, unlisted computation rules, ambient induction theorems, or subject-reduction proofs beyond the emitted-rule surface.}
  \upgradepath{To reach obligationClosure, check the declaration handoff, arity exactness, emitted-rule ledger, and primitive-refusal boundary.}
\end{closurestatus}
