\chapter{A Concrete Naming Certificate for $\LayeredRelationFailureBoundaryUp$}
\label{ch:concrete-instances-layered-relation-failure-boundary-namecert}
\origin{ai}

The $\LayeredRelationFailureBoundaryUp$ packet realizes the failure-boundary row of \autoref{ch:visions-layered-relation-certificate} as a finite $\NameCert$ surface for cross-domain relation certificates. It sits beside the full relation packet of \autoref{ch:concrete-instances-layeredrelationcert-namecert}, the audit-frame packet of \autoref{ch:concrete-instances-relationalframeaudit-namecert}, the force-like inter-history relation packet of \autoref{ch:concrete-instances-forceinterhistrelation-namecert}, and the failed gate witness of \autoref{ch:concrete-instances-auditgatefailurewitness-namecert}. Those siblings expose a complete relation certificate, an audit frame, a force-like carrier, or a failed audit item; this packet isolates the coordinate that says exactly where same-schema export weakens or is refused before any public consumer may read relation language.

\falsifiablePrediction{Any public same-schema export that lacks a displayed failure-boundary row cannot cite this NameCert; a verified export without such a row refutes the packet.}

\independenceWitness{layeredrelationcert, relationalframeaudit, forceinterhistrelation, auditgatefailurewitness, apophaticname: the packet is not bijective with any sibling because it isolates the weakening/failure coordinate, whereas the siblings respectively package the full relation certificate, audit frame, force-like carrier, failed audit witness, or named apophatic boundary.}

\begin{definition}[Layered relation failure-boundary carrier]
\label{def:layered-relation-failure-boundary-carrier}
A $\LayeredRelationFailureBoundaryUp$ carrier is a finite $\BHist$ packet
$$
F=(R,E,B,W,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the relation-certificate row being tested for public same-schema export;
\item $E$ is the exactness row that records what the relation may export before identity, empirical transfer, proof transfer, or bridge strength is read;
\item $B$ is the failure-boundary row naming the condition under which the relation weakens, fails, or must be withheld from public export;
\item $W$ is the weakening and refusal row attached to $B$, listing the non-preserved structure, refused object content, refused empirical content, and refused bridge content;
\item $G$ is the gate report row recording no identity collapse, hidden axiom, global-frame leak, subject-substance leak, or empirical overclaim for the displayed relation read;
\item $H$ records componentwise $\hsame$ transport for relation-certificate, exactness, failure-boundary, weakening, gate-report, route, provenance, and local-name rows;
\item $C$ records displayed $\Cont$ routes from $R$ to $E$, from $E$ to $B$, from $B$ to $W$, from $W$ to $G$, and from the accepted gate report to any public same-schema consumer;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:visions-layered-relation-certificate}, \autoref{ch:concrete-instances-layeredrelationcert-namecert}, \autoref{ch:concrete-instances-relationalframeaudit-namecert}, \autoref{ch:concrete-instances-forceinterhistrelation-namecert}, \autoref{ch:concrete-instances-auditgatefailurewitness-namecert}, \autoref{ch:concrete-instances-apophaticname-namecert}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\LayeredRelationFailureBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for exporting a same-schema relation without a displayed weakening and failure boundary, and it has no coordinate for turning the boundary into object identity, empirical law, hidden axiom, global frame, subject substance, or checked bridge strength.
\end{definition}
\leandef{BEDC.Derived.LayeredRelationFailureBoundaryUp.LayeredRelationFailureBoundaryUp}
\leanchecked{BEDC.Derived.LayeredRelationFailureBoundaryUp.LayeredRelationFailureBoundaryTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Layered relation failure-boundary non-escape]
\label{thm:layered-relation-failure-boundary-nonescape}
For every accepted $\LayeredRelationFailureBoundaryUp$ carrier
$$
F=(R,E,B,W,G,H,C,P,N),
$$
all public relation export reads pass through $R,E,B,W,G,H,C,P,N$. The consumer may read exactness only together with the displayed failure-boundary row $B$ and the weakening/refusal row $W$; it receives no route that bypasses $B$, detaches $W$, hides the gate report $G$, or promotes same-schema language to object identity, empirical transfer, proof transfer, global-frame transfer, subject-substance transfer, or bridge checking.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:layered-relation-failure-boundary-carrier}. The exactness row $E$, failure-boundary row $B$, weakening/refusal row $W$, and gate report row $G$ are displayed as separate coordinates of the same finite packet.

Read the continuation routes in $C$. A public same-schema consumer reaches $E$ from $R$, then reaches $B$, then reaches $W$, and then reads $G$ before export. Thus exactness cannot be consumed as a detached object-identity or bridge-strength claim.

The structural rows $H,P,N$ transport, cite, and name the same packet. Since none of those rows supplies a new relation source, hidden axiom, empirical law, global frame, subject-substance carrier, or bridge checker, the displayed boundary cannot escape through transport, provenance, or local naming.
\end{proof}
\leanchecked{BEDC.Derived.LayeredRelationFailureBoundaryUp.LayeredRelationFailureBoundary\_failure\_boundary\_row\_determinacy}

\begin{theorem}[Layered relation failure-boundary gate exactness]
\label{thm:layered-relation-failure-boundary-gate-exactness}
An accepted $\LayeredRelationFailureBoundaryUp$ packet permits public same-schema export exactly when the relation-certificate row $R$, exactness row $E$, failure-boundary row $B$, weakening/refusal row $W$, and gate report row $G$ are displayed in the same carrier and the consumer route preserves them through $H,C,P,N$. If any of $B,W,G$ is absent, then the packet supplies no public exactness export.
\end{theorem}
\begin{proof}
For the forward direction, read the carrier. The public exactness route is the displayed route from $R$ through $E,B,W,G$ and then through the structural rows $H,C,P,N$. These rows give the relation certificate, the exactness claim, the boundary where it weakens, the refused content attached to that boundary, and the gate report that prevents over-reading.

For the reverse direction, suppose a displayed route presents $R,E,B,W,G,H,C,P,N$ in one carrier. The route has the exactness row, the failure boundary, the weakening/refusal row, and the gate report needed by \autoref{ch:visions-layered-relation-certificate} before public export, so it determines the same same-schema consumer surface.

If $B$ is absent, the export has no row naming where the relation weakens or fails. If $W$ is absent, the export has no refusal row separating exactness from preserved content. If $G$ is absent, the export has no gate report blocking identity collapse, hidden axiom use, global-frame leakage, subject-substance leakage, or empirical overclaim. In each case the carrier lacks a public exactness export route.
\end{proof}

\closureat{LayeredRelationFailureBoundaryUp}{seedStr}

\begin{closurestatus}{\LayeredRelationFailureBoundaryUp}
  \constructivestory{A $\LayeredRelationFailureBoundaryUp$ packet is generated from a relation-certificate row, exactness row, failure-boundary row, weakening/refusal row, gate report, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:layered-relation-failure-boundary-carrier}, \autoref{thm:layered-relation-failure-boundary-nonescape}, and \autoref{thm:layered-relation-failure-boundary-gate-exactness} bind the finite failure-boundary packet for same-schema relation export.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close the full layered relation certificate, a relational frame audit, a force-like relation, a failed audit witness, object identity, empirical transfer, global-frame transfer, subject-substance transfer, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, exactness gating, weakening/refusal attachment, gate-report preservation, transport, continuation, provenance, naming, and TasteGate nontriviality with field faithfulness for the same failure-boundary packet.}
\end{closurestatus}
