\chapter{A Concrete Naming Certificate for $\SubstitutionBoundaryAuditUp$}
\label{ch:concrete-instances-substitutionboundaryaudit-namecert}
\origin{ai}

The $\SubstitutionBoundaryAuditUp$ packet realizes the substitution audit map of \autoref{ch:metacic-substitution-audit-map} as finite NameCert data. It consumes the closed shift and substitution boundary of \autoref{ch:concrete-instances-closedtermsubstitutionboundary-namecert}, the authorized generator surface of \autoref{ch:concrete-instances-authorizedgeneratorrecursor-namecert}, and the gap-closure boundary of \autoref{ch:concrete-instances-gapclosureboundary-namecert}. Its role is to expose exactly the rows by which a closed shift or closed substitution route may be audited before a consumer reads the operation result.

\begin{definition}[SubstitutionBoundaryAudit carrier]
\label{def:substitution-boundary-audit-carrier}
A $\SubstitutionBoundaryAuditUp$ carrier is a finite $\BHist$ packet
$$
A=(T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the closed source-term row whose boundary is being audited;
\item $V$ is the closed value row used by a substitution route, or the inert value row for a shift-only route;
\item $d$ is the displayed depth row at which shift or substitution is read;
\item $C_{\mathsf{src}}$ is the closedness witness for the source term at depth $d$;
\item $C_{\mathsf{val}}$ is the closedness witness for the value row at the same audit boundary;
\item $Q$ is the shift-boundary row recording the closed shift operation and its classifier read;
\item $R$ is the substitute-boundary row recording the closed substitution operation and its classifier read;
\item $L$ is the audit ledger for operation order, closed composition, and generator-closure classification;
\item $E$ is the audit-exposure row that must be read before either $Q$ or $R$ is exported to a downstream consumer;
\item $H$ records componentwise $\hsame$ transport for the term, value, depth, closedness, operation, ledger, exposure, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ routes for closedness reads, shift reads, substitution reads, ledger reads, and audit exposure;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:metacic-substitution-audit-map}, $\ClosedTermSubstitutionBoundaryUp$, $\AuthorizedGeneratorRecursorUp$, $\GapClosureBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\SubstitutionBoundaryAuditUp}$ row.
\end{enumerate}
The carrier has no coordinate for an open source term, host substitution semantics, subject reduction, unrestricted generator recursion, hidden evaluator state, or a gap discharge outside the displayed packet.
\end{definition}
\leanchecked{BEDC.Derived.SubstitutionBoundaryAuditUp.SubstitutionBoundaryAuditTasteGate\_single\_carrier\_alignment}

\begin{theorem}[SubstitutionBoundaryAudit NameCert obligations]
\label{thm:substitution-boundary-audit-namecert-obligations}
For the carrier of \autoref{def:substitution-boundary-audit-carrier}, the local $\NameCert_{\SubstitutionBoundaryAuditUp}$ surface consists exactly of carrier admission, classifier stability, closedness-read order, audit non-escape, and consumer exactness for
$$
A=(T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,E,H,C,P,N).
$$
Carrier admission exposes all displayed rows; classifier stability keeps the shift row $Q$ and substitute row $R$ attached to the same term, value, and depth rows; closedness-read order places $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$ before either operation row; audit non-escape forces $L,E,H,C,P,N$ to travel with the operation reads; consumer exactness says that every accepted consumer of $Q$ or $R$ reads only this packet.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:substitution-boundary-audit-carrier}. The displayed tuple lists the source, value, depth, closedness, operation, ledger, exposure, transport, continuation, provenance, and local naming rows.

Classifier stability follows from the closed shift and substitution boundary of \autoref{ch:concrete-instances-closedtermsubstitutionboundary-namecert}. Both operation rows are read at the same displayed term, value, and depth boundary, so no second classifier source is available.

Closedness-read order is the route through $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$. The authorized generator surface of \autoref{ch:concrete-instances-authorizedgeneratorrecursor-namecert} contributes only the permitted generator-closure classifier rows recorded in $L$ and does not supply a replacement closedness witness.

Audit non-escape is the row $E$ together with the ledger, transport, continuation, provenance, and local name rows $L,H,C,P,N$. The gap-closure boundary of \autoref{ch:concrete-instances-gapclosureboundary-namecert} remains a sibling refusal surface: it can be cited as a boundary, but it is not discharged by this packet.

Finally, consumer exactness follows because $Q$ and $R$ are the only operation rows and $E$ is their shared audit-exposure gate. Any accepted consumer route for a closed shift or substitution result therefore factors through the displayed packet and nowhere else.
\end{proof}

\begin{theorem}[SubstitutionBoundaryAudit falsifiable route]
\label{thm:substitution-boundary-audit-falsifiable-route}
Any accepted $\SubstitutionBoundaryAuditUp$ consumer route that reaches $Q$ or $R$ must expose both the relevant closedness rows $C_{\mathsf{src}},C_{\mathsf{val}}$ and the audit ledger $L$ before the operation row. A route that reaches $Q$ or $R$ while bypassing those rows is not an accepted carrier route.
\end{theorem}
\begin{proof}
Start with \autoref{thm:substitution-boundary-audit-namecert-obligations}. It places closedness-read order and audit non-escape among the local certificate obligations.

If a route reaches the shift row $Q$, the classifier stability clause ties $Q$ to $T,d,C_{\mathsf{src}},L,E$ and to the displayed transport and continuation rows. The shift read therefore cannot be consumed before the source closedness and ledger rows are visible.

If a route reaches the substitute row $R$, the same obligation surface ties $R$ to $T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},L,E$. The value closedness row is part of the substitution boundary, so a consumer that bypasses it is outside the carrier.

Thus the prediction is refuted exactly by a counter-route that accepts $Q$ or $R$ without the relevant closedness and ledger rows. Such a route would contradict the displayed NameCert surface rather than extend it.
\end{proof}

\begin{theorem}[SubstitutionBoundaryAudit independence witness]
\label{thm:substitution-boundary-audit-independence-witness}
The carrier of \autoref{def:substitution-boundary-audit-carrier} is not bijective, row for row, to any of $\ClosedTermSubstitutionBoundaryUp$, $\AuthorizedGeneratorRecursorUp$, $\GapClosureBoundaryUp$, or $\MetaCICNormalizationFrontierUp$. A bijection preserving local NameCert obligations would have to preserve the dedicated audit-exposure row $E$ coupled to both the shift boundary row $Q$ and the substitute boundary row $R$, and no listed sibling carries exactly that joint exposure surface.
\end{theorem}
\begin{proof}
Compare first with $\ClosedTermSubstitutionBoundaryUp$. That sibling supplies the closed shift and substitution boundary rows, but it does not isolate a separate audit-exposure row $E$ whose only role is to gate both operation rows before downstream use.

Compare next with $\AuthorizedGeneratorRecursorUp$ and $\GapClosureBoundaryUp$. The generator sibling supplies permitted generator-recursion rows, while the gap sibling records a closure boundary. Neither carries the paired shift and substitute operation rows together with the closedness, ledger, and exposure order required here.

Finally compare with $\MetaCICNormalizationFrontierUp$. It records candidate and endpoint normalization routes with obstruction retention, not the term/value/depth substitution audit packet. Since each sibling omits at least one of $Q,R,L,E$ or carries a different endpoint surface, no carrier bijection can preserve all NameCert obligations.
\end{proof}

\falsifiablePrediction{Any accepted SubstitutionBoundaryAuditUp consumer route that reaches $Q$ or $R$ must expose both the relevant ClosedAt rows and the audit ledger before the operation row; a counter-route bypassing those rows refutes the chapter.}

\independenceWitness{closedtermsubstitutionboundary, authorizedgeneratorrecursor, gapclosureboundary, metacicnormalizationfrontier: the audit carrier is not bijective to any sibling because it has a dedicated audit-exposure row $E$ coupled to both shift and substitute boundary reads.}

The later Lean TasteGate file will provide $\mathsf{Nontrivial}\ \SubstitutionBoundaryAuditUp$ with two explicit witness packets, one for a shift audit route and one for a substitute audit route, and $\mathsf{FieldFaithful}\ \SubstitutionBoundaryAuditUp$ by matching and injection over the displayed fields $T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,E,H,C,P,N$.

\closureat{SubstitutionBoundaryAuditUp}{seedStr}

\begin{closurestatus}{\SubstitutionBoundaryAuditUp}
  \constructivestory{A $\SubstitutionBoundaryAuditUp$ packet is generated from a source term, value row, depth row, closedness witnesses, shift and substitute boundary rows, audit ledger, audit-exposure row, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:substitution-boundary-audit-carrier}, \autoref{thm:substitution-boundary-audit-namecert-obligations}, \autoref{thm:substitution-boundary-audit-falsifiable-route}, and \autoref{thm:substitution-boundary-audit-independence-witness} display the finite NameCert surface for closed shift and substitution audit routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close subject reduction, unrestricted substitution commutation, open-term substitution semantics, generator recursion, gap discharge, or bridge checking for $\SubstitutionBoundaryAuditUp$.}
  \upgradepath{Obligation closure requires a Lean carrier encoding, checked NameCert obligation theorem, checked route theorem, independence theorem, and TasteGate nontriviality with field faithfulness for the same audit packet.}
\end{closurestatus}
