\chapter{A Concrete Naming Certificate for $\CauchyLimitFunctorUp$}
\label{ch:concrete-instances-cauchy-limit-functor-namecert}
\origin{human}

The $\CauchyLimitFunctorUp$ packet names the functorial transport surface for Cauchy limit seals in the Real and Completion route of \autoref{ch:visions-real-completeness}. It sits after the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. It also consumes the existing limit-seal boundary of \autoref{ch:concrete-instances-cauchylimitseal-namecert} and the completion-seal classifier of \autoref{ch:concrete-instances-real-completion-seal-classifier-namecert}. The packet is a routed transport object: it carries a finite source seal, a finite target seal, and the displayed map between their regular Cauchy data without adding a host-level completion theorem.

\falsifiablePrediction{If a completion consumer accepts a transported Cauchy limit seal while changing the source stream window, target stream window, regular-rational readback, dyadic tolerance ledger, or RealUp endpoint row outside the displayed transport packet, it refutes the $\CauchyLimitFunctorUp$ classifier.}

\independenceWitness{cauchylimitseal, realcompletionsealclassifier, streamname, regseqrat, dyadicratcore, real: no listed sibling is bijective to $\CauchyLimitFunctorUp$ because the functor packet carries source and target limit-seal rows together with the finite transport map, classifier row, dyadic tolerance ledger, regular-rational readback, RealUp endpoint, componentwise transports, continuation replay, provenance, and local NameCert row.}

\begin{definition}[Cauchy limit functor carrier]
\label{def:cauchy-limit-functor-carrier}
A $\CauchyLimitFunctorUp$ carrier is a finite $\BHist$ packet
$$
F=(S,T,M,W_0,W_1,R,D,K,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\CauchyLimitSealUp$ row whose limit-seal route is being transported;
\item $T$ is the target $\CauchyLimitSealUp$ row reached after transport;
\item $M$ is the finite transport-map row from the source window and readback data to the target window and readback data;
\item $W_0$ is the source $\StreamNameUp$ window row read by $S$;
\item $W_1$ is the target $\StreamNameUp$ window row read by $T$;
\item $R$ is the $\RegSeqRatUp$ readback row preserved by the displayed transport;
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger controlling the transported precision request;
\item $K$ is the $\RealCompletionSealClassifierUp$ row that recognizes the transported seal boundary;
\item $E$ is the terminal $\RealUp$ endpoint row consumed after the target seal is displayed;
\item $H$ records componentwise $\hsame$ transports for the two limit seals, map row, stream windows, regular-rational readback, dyadic ledger, classifier, endpoint, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ replay route from $S$ through $M,W_0,W_1,R,D,K$ to $T$ and then to $E$;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:concrete-instances-cauchylimitseal-namecert}, \autoref{ch:concrete-instances-real-completion-seal-classifier-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-real-namecert}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\CauchyLimitFunctorUp}$ row.
\end{enumerate}
The carrier exports no quotient stream equality, selected host limit, ambient completeness principle, countable-choice selector, detached Real value, or second transport route beyond the displayed packet.
\end{definition}

\begin{definition}[Cauchy limit functor classifier]
\label{def:cauchy-limit-functor-classifier}
The $\CauchyLimitFunctorUp$ classifier compares two carriers only by the displayed rows
$$
S,T,M,W_0,W_1,R,D,K,E,H,C,P,N.
$$
Two packets are classifier-equal exactly when the source and target limit-seal rows agree, the transport-map row agrees, the source and target $\StreamNameUp$ windows agree, the $\RegSeqRatUp$ readback and $\DyadicRatCoreUp$ tolerance ledger agree, and the classifier, endpoint, transport, continuation, provenance, and local naming rows agree componentwise. The classifier has no coordinate for quotient equality of Cauchy names, host real equality, an untracked selector, a detached limit object, or an ambient completeness theorem.
\end{definition}

\begin{theorem}[Cauchy limit functor NameCert obligations]
\label{thm:cauchy-limit-functor-namecert-obligations}
For the carrier of \autoref{def:cauchy-limit-functor-carrier}, the local $\NameCert_{\CauchyLimitFunctorUp}$ surface consists exactly of the following five obligation rows:
\begin{enumerate}
\item carrier exposure for $F=(S,T,M,W_0,W_1,R,D,K,E,H,C,P,N)$;
\item source-to-target seal exposure through the ordered route $S \to M \to T$;
\item finite observation exposure through $W_0,W_1,R,D$;
\item completion-consumer exposure through $K$ and $E$;
\item structural exposure through componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local naming $N$.
\end{enumerate}
No $\CauchyLimitFunctorUp$ consumer can read the transported limit seal without preserving all five rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-limit-functor-carrier}. Its displayed packet is exactly $F=(S,T,M,W_0,W_1,R,D,K,E,H,C,P,N)$, so the carrier row supplies the finite object being named.

Read the seal route next. The source seal $S$ is transported only through the finite map row $M$, and the target seal $T$ is reached only after that row is displayed. Thus the seal exposure is the ordered route $S \to M \to T$.

Now inspect the observation rows. The source and target windows $W_0,W_1$, the regular-rational readback $R$, and the dyadic tolerance ledger $D$ are the finite data over which the transport map is read. The completion-facing rows $K,E$ then recognize the transported seal boundary and deliver the terminal $\RealUp$ endpoint.

Finally the rows $H,C,P,N$ transport, replay, record provenance for, and name the same packet. Since the carrier and classifier contain no further coordinates, a consumer that bypasses any one of the five obligation rows leaves the $\CauchyLimitFunctorUp$ surface.
\end{proof}

\begin{theorem}[Cauchy limit functor Real-completion consumer boundary]
\label{thm:cauchy-limit-functor-real-completion-consumer}
Every Real and Completion consumer that cites an accepted $\CauchyLimitFunctorUp$ packet factors through the finite route
$$
S \longmapsto M \longmapsto W_0,W_1,R,D \longmapsto K \longmapsto T \longmapsto E \longmapsto H,C,P,N.
$$
The consumer may use the source and target $\CauchyLimitSealUp$ rows, the transport map, the two $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback, the $\DyadicRatCoreUp$ tolerance ledger, the $\RealCompletionSealClassifierUp$ row, the terminal $\RealUp$ endpoint, and the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It receives no quotient stream equality, host real equality, selected limit, detached completion object, ambient completeness principle, countable-choice selector, or second transport route.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:cauchy-limit-functor-namecert-obligations}. They force every accepted read through the carrier row, the source-to-target seal route, the finite observation rows, the completion-consumer rows, and the structural rows.

Use the classifier of \autoref{def:cauchy-limit-functor-classifier}. It compares only $S,T,M,W_0,W_1,R,D,K,E,H,C,P,N$, so a Real and Completion consumer cannot distinguish two reads by adding quotient stream equality, host real equality, a selected limit, or an ambient completion proof.

Finally follow the route displayed in the carrier. The source seal $S$ is transported by $M$ over the windows $W_0,W_1$, readback $R$, and tolerance ledger $D$; the classifier row $K$ recognizes the transported boundary before the target seal $T$ and endpoint row $E$ are consumed. The structural rows $H,C,P,N$ package that same finite route, so no detached completion object, choice-selected witness, or second route remains available.
\end{proof}

\closureat{CauchyLimitFunctorUp}{seedStr}

\begin{closurestatus}{\CauchyLimitFunctorUp}
  \constructivestory{A $\CauchyLimitFunctorUp$ packet is generated from source and target CauchyLimitSeal rows, a finite transport-map row, source and target StreamName windows, a RegSeqRat readback, a DyadicRatCore tolerance ledger, a RealCompletionSealClassifier row, a terminal RealUp endpoint, componentwise transports, displayed replay, provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-limit-functor-carrier}, \autoref{def:cauchy-limit-functor-classifier}, \autoref{thm:cauchy-limit-functor-namecert-obligations}, and \autoref{thm:cauchy-limit-functor-real-completion-consumer} bind the finite transport carrier, classifier, five NameCert obligation rows, and Real-completion consumer boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean verification, bridge checking, quotient stream equality, host real equality, selected limits, ambient completeness, countable choice, or a universal completion functor.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier exactness, source-to-target seal exposure, finite observation exposure, completion-consumer exposure, and structural transport for the same finite packet.}
\end{closurestatus}
