\chapter{A Concrete Naming Certificate for $\AxisCarryDiamondRouteUp$}
\label{ch:concrete-instances-axis-carry-diamond-route-namecert}
\origin{ai}

The $\AxisCarryDiamondRouteUp$ packet names the two-route diamond that compares displayed Zeckendorf carry-normalization paths. It is adjacent to the finite confluence surface of \autoref{ch:concrete-instances-axis-carry-confluence-namecert}, but its local role is the route certificate itself: two source carry windows, two route rows, one shared normal target row, value ledgers, non-$\hsame$ boundary rows, componentwise transports, continuation replay, provenance, and a local naming row are carried together as a finite packet.

It is an ai over the $\ZCarryUp$, $\ZeckendorfCarryNormalizationUp$, $\ZeckendorfCarryValueUp$, and $\AxisZeckendorfCarryBudgetUp$ sibling surfaces, with the diamond row acting only as the finite shared-target route bundle.

\falsifiablePrediction{Two accepted diamond packets with the same two displayed source carry windows and same shared target row cannot expose two different target-normality ledgers.}

\independenceWitness{zeckendorfcarryclassifier, zeckendorfcarrynormalization, zcarry, zeckendorfcarryvalue, axiszeckendorfcarrybudget: the diamond carrier has two route rows and a shared-target ledger absent from each sibling, while each sibling lacks at least one of the paired-route or shared-normal-target coordinates.}

The packet consumes $\ZCarryUp$ edges from \autoref{ch:concrete-instances-zcarry-namecert}, the normalization handoff of \autoref{ch:concrete-instances-zeckendorf-carry-normalization-namecert}, the value row of \autoref{ch:concrete-instances-zeckendorf-carry-value-namecert}, and the finite budget surface of \autoref{ch:concrete-instances-axiszeckendorfcarrybudget-namecert}. It does not identify the carry sources by $\hsame$ and does not promote the diamond to a kernel rewrite.

\begin{definition}[Axis carry diamond-route carrier]
\label{def:axis-carry-diamond-route-carrier}
An $\AxisCarryDiamondRouteUp$ carrier is a finite $\BHist$ packet
$$
D=(a,b,c,n,\rho_0,\rho_1,\nu_0,\nu_1,\eta,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $a$ is the displayed overlap source row for the diamond;
\item $b$ and $c$ are the two displayed carry-successor source windows;
\item $n$ is the shared normal target row admitted by $\ZeckendorfCarryNormalizationUp$;
\item $\rho_0$ is the first route row, consisting of a $\ZCarryUp$ edge from $a$ to $b$ and a $\ZeckendorfCarryNormalizationUp$ handoff from $b$ to $n$;
\item $\rho_1$ is the second route row, consisting of a $\ZCarryUp$ edge from $a$ to $c$ and a $\ZeckendorfCarryNormalizationUp$ handoff from $c$ to $n$;
\item $\nu_0$ and $\nu_1$ are the displayed finite value ledgers for the two routes;
\item $\eta$ is the shared target-normality ledger for $n$;
\item $H$ records the non-$\hsame$ carry boundaries together with componentwise transports for all displayed route, value, target, continuation, provenance, and naming rows;
\item $C$ records displayed $\Cont$ routes for replaying the two route rows, both value ledgers, the shared target-normality row, and the local naming row;
\item $P$ records $\Pkg$ provenance over $\ZCarryUp$, $\ZeckendorfCarryNormalizationUp$, $\ZeckendorfCarryValueUp$, $\AxisZeckendorfCarryBudgetUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\AxisCarryDiamondRouteUp}$ row.
\end{enumerate}
The carrier exports only this finite two-route packet. It contains no source-target $\hsame$ proof, no host arithmetic quotient, no global confluence theorem, no hidden normalizer, and no kernel rewrite rule.
\end{definition}
\leandef{BEDC.Derived.AxisCarryDiamondRouteUp.AxisCarryDiamondRouteUp}
\leanchecked{BEDC.Derived.AxisCarryDiamondRouteUp.AxisCarryDiamondRouteTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Axis carry diamond routes name two-step confluence]
\label{thm:axis-carry-diamond-route-names-two-step-confluence}
For an accepted $\AxisCarryDiamondRouteUp$ carrier $D=(a,b,c,n,\rho_0,\rho_1,\nu_0,\nu_1,\eta,H,C,P,N)$, the route rows $\rho_0$ and $\rho_1$ name two displayed carry-normalization paths from the same overlap source row $a$ to the same normal target row $n$. The shared target-normality ledger $\eta$ is read only after both route rows and both value ledgers have been exposed, so any diamond consumer receives a finite two-step confluence packet rather than two unrelated carry edges.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $\rho_0$ and $\rho_1$ are the only route coordinates, and their endpoints are fixed by the displayed rows $a,b,c,n$.

Read the normal target and value rows next. The target coordinate $n$ is shared, while $\nu_0$ and $\nu_1$ record the finite value ledgers along the two displayed paths.

Finally replay the support rows. The continuation and provenance rows expose the two routes and the shared target ledger as one packet, and the local $\NameCert$ row names that packet before a consumer may cite the diamond.
\end{proof}
\leanchecked{BEDC.Derived.AxisCarryDiamondRouteUp.AxisCarryDiamondRouteCarrier\_names\_two\_step\_confluence}

\begin{theorem}[Axis carry diamond-route non-escape]
\label{thm:axis-carry-diamond-route-nonescape}
Every accepted $\AxisCarryDiamondRouteUp$ read factors through the displayed packet
$$
D=(a,b,c,n,\rho_0,\rho_1,\nu_0,\nu_1,\eta,H,C,P,N).
$$
It can expose the two carry-normalization route rows, the shared normal target row, the two value ledgers, the shared target-normality ledger, non-$\hsame$ carry boundaries, componentwise transports, route replay, provenance, and local naming. It cannot expose source-target $\hsame$, host arithmetic equality, a quotient normal form, an unbounded normalizer, a global confluence theorem, or a kernel rewrite.
\end{theorem}
\begin{proof}
Begin with \autoref{def:axis-carry-diamond-route-carrier}. The displayed tuple lists every coordinate available to an accepted read, and none of the excluded objects is a coordinate.

The route coordinates are finite. Each route row is assembled from the $\ZCarryUp$ and $\ZeckendorfCarryNormalizationUp$ sibling surfaces, while the value and target ledgers are displayed as $\nu_0,\nu_1,\eta$ rather than as host arithmetic or quotient data.

The support rows $H,C,P,N$ preserve and replay only those displayed coordinates. Since the carrier contains no hidden normalizer, global confluence row, source-target $\hsame$ proof, or kernel rewrite rule, no accepted projection can escape the finite diamond-route packet.
\end{proof}
\leanchecked{BEDC.Derived.AxisCarryDiamondRouteUp.AxisCarryDiamondRouteNonescape}

The Lean taste-gate file for this carrier should provide explicit \texttt{Nontrivial AxisCarryDiamondRouteUp} and \texttt{FieldFaithful AxisCarryDiamondRouteUp} instances for the displayed row inventory.

\closureat{AxisCarryDiamondRouteUp}{seedStr}

\begin{closurestatus}{\AxisCarryDiamondRouteUp}
  \constructivestory{An $\AxisCarryDiamondRouteUp$ packet is generated from an overlap source row, two carry-successor rows, a shared normal target, two carry-normalization route rows, two value ledgers, a shared target-normality ledger, non-$\hsame$ boundary rows, componentwise transports, continuation routes, provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:axis-carry-diamond-route-carrier}, \autoref{thm:axis-carry-diamond-route-names-two-step-confluence}, and \autoref{thm:axis-carry-diamond-route-nonescape} specify the finite two-route diamond carrier, shared target ledger, and non-escape boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, arbitrary carry confluence, host arithmetic quotienting, global normalization, source-target $\hsame$, or kernel rewriting.}
  \upgradepath{Obligation closure requires checked carrier admission, paired route rows, shared target-normality, value-ledger exactness, non-$\hsame$ preservation, route replay, provenance, and local naming for the same finite packet.}
\end{closurestatus}
