\begin{theorem}[Hilbert singleton orthogonal complement collapse]
\label{thm:hilbert-singleton-orthogonal-complement-collapse}
For the carrier of
\autoref{def:hilbert-singleton-empty-history-carrier}, any displayed vector
endpoint orthogonal to the singleton carried surface is classified by
$\rho_{\emp}$ with $\emp$. Conversely, every carried endpoint has the
zero inner-product row against every carried endpoint:
$$
\mathsf{RealConstantHistoryClassifier}
  (\langle m,n\rangle_{\emp},0_{\mathsf{Real}}^{c})
$$
for carried histories $m,n:\mathsf{BHist}$. Thus the displayed orthogonal
complement of the singleton carrier collapses to the singleton endpoint.
\end{theorem}
\begin{proof}
First identify the source surface. By
\autoref{thm:hilbert-singleton-source-compatibility}, the Hilbert carrier,
the singleton vector-space carrier, and the Banach carrier all expose the
same predicate $A_{\emp}$ and classifier $\rho_{\emp}$.

Now apply
\autoref{thm:singleton-empty-history-vecspace-endpoint-collapse}. Any
displayed vector endpoint on this singleton vector-space surface is therefore
classified by $\rho_{\emp}$ with $\emp$; there is no separate vector endpoint
available for an orthogonal-complement row.

For the converse direction, take carried endpoints $m,n:\mathsf{BHist}$.
\autoref{thm:hilbert-singleton-universal-orthogonality} reads their
inner-product endpoint as $0_{\mathsf{Real}}^{c}$ under
$\mathsf{RealConstantHistoryClassifier}$, so every carried endpoint is
orthogonal to every other carried endpoint in the singleton Hilbert display.
\end{proof}

\begin{theorem}[Hilbert singleton projection-residual decomposition]
\label{thm:hilbert-singleton-projection-residual-decomposition}
Let $s$ be an accepted regular Cauchy stream in the Hilbert singleton carrier,
and let $p$ be a Hilbert singleton projection witness for its carried
endpoint. Then $p$ decomposes the endpoint into its unique
$\rho_{\emp}$-classified projection plus a residual whose inner-product row is
orthogonal to the singleton carrier and whose norm endpoint is
$0_{\mathsf{Real}}^{c}$.
\end{theorem}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingletonProjection\_residual\_decomposition}
\leanchecked{BEDC.Derived.HilbertUp.HilbertSingleton\_projection\_residual\_decomposition}
\begin{proof}
Use \autoref{thm:hilbert-singleton-projection-uniqueness} to read the
projection witness against the complete singleton Hilbert surface. Any other
limit or projection witness for the same accepted stream is identified with
$p$ by $\rho_{\emp}$.

The projection component is therefore the singleton endpoint classified by
$\rho_{\emp}$ with $\emp$. The complete normed certificate
\autoref{thm:hilbert-singleton-complete-normed-certificate} supplies the
matching Banach limit row and the norm-induced constant RealUp zero endpoint.

It remains to identify the residual row. Since both the carried endpoint and
the projection component lie on the singleton carrier,
\autoref{thm:hilbert-singleton-universal-orthogonality} classifies the
inner-product row of the residual comparison with $0_{\mathsf{Real}}^{c}$.

\autoref{thm:hilbert-singleton-orthogonal-complement-collapse} then collapses
the residual endpoint itself to the singleton classifier. Its norm endpoint is
read back as $0_{\mathsf{Real}}^{c}$ by the complete normed certificate, so
the projection plus residual display is the unique singleton decomposition
with zero orthogonal residual.
\end{proof}
