\begin{definition}[Measure event row coverage]
\label{def:measure-event-row-coverage}
For the $\MeasureUp$ sigma-algebra carrier surface of
\autoref{def:measure-sigma-algebra-carrier-surface}, the event row coverage
predicate is the assertion that every row consumed by a downstream certificate
is attached to a visible $\mathsf{BHist}$ ledger row of that carrier surface.
Concretely, the covered rows are:
\begin{enumerate}
  \item every measurable event read by the measurable-family predicate
  $\mathcal{A}$;
  \item the empty-event row;
  \item every binary-union row, including its disjointness witness when the
  union is read as a disjoint union;
  \item every countable-union row for a StreamName-style measurable family,
  together with its pairwise-disjointness witness when sigma-additivity is
  invoked;
  \item every $\RealUp$ endpoint row $\mu(E)$ classified by the measure-value
  classifier;
  \item every countable-sum endpoint $\Sigma_\mu(E_\bullet)$ and every
  head-tail readback row attached to that endpoint.
\end{enumerate}
Coverage requires the attachment to be exact: the downstream consumer reads the
displayed $\mathsf{BHist}$ row, its $\hsame$ transport row, and the associated
$\RealUp$ endpoint classifier row, and it reads no additional event carrier,
choice object, quotient object, or analytic completion object from the
$\MeasureUp$ package.
\end{definition}

\begin{theorem}[Measure measurable family exactness]
\label{thm:measure-measurable-family-exactness}
For the $\MeasureUp$ sigma-algebra carrier surface, the event row coverage
predicate of \autoref{def:measure-event-row-coverage} gives coverage,
soundness, and completeness for the measurable-family classifier. Coverage
means that every measurable event, closure event, disjointness witness,
$\RealUp$ endpoint, and countable-sum endpoint used by the classifier is read
from a displayed ledger row. Soundness means that transporting a covered row
along the classifier gives the corresponding covered row in the target
presentation. Completeness means that every row available to the
measurable-family classifier is one of the rows listed in the coverage
predicate.
\end{theorem}
\begin{proof}
Unpack \autoref{def:measure-sigma-algebra-carrier-surface}. Its carrier,
stability, ledger, and exactness fields list exactly the measurable-event,
empty-event, binary-union, countable-union, disjointness, endpoint, and
countable-sum rows named in \autoref{def:measure-event-row-coverage}.

Coverage is therefore projection from the displayed carrier and ledger fields.
Each consumed event or endpoint row is attached to one of those fields by the
exactness clause of the surface.

Soundness is the transport statement of
\autoref{thm:measure-carrier-classifier-obligation}. Componentwise $\hsame$
moves the event rows, and the $\RealUp$ classifier moves the endpoint rows.
The ledger witness attached to a visible row is repacked after that visible row
has been transported.

Completeness is the exhaustion statement of
\autoref{thm:measure-ledger-exactness-obligation}. Since the ledger contains
only the listed rows and every hidden measurable-set or countable-sum witness
is attached to one of them, the measurable-family classifier has no further
row to read.
\end{proof}

\begin{theorem}[Measure probability normalization row]
\label{thm:measure-probability-normalization-row}
Let a covered $\MeasureUp$ package carry a total event row $\Omega$ whose
endpoint is classified as the probability unit:
$$
\mu(\Omega)\sim_R 1_R.
$$
Together with the empty-zero theorem
\autoref{thm:measure-empty-set-zero-from-sigma-additivity} and the finite
disjoint-union theorem
\autoref{thm:measure-finite-disjoint-union-additivity}, this row supplies the
normalization and finite-additivity rows consumed by $\ProbSpaceUp$. The claim
is only the projection of the total-event endpoint and the repacking of the
two named $\MeasureUp$ consequence theorems into the probability-space
certificate surface.
\end{theorem}
\begin{proof}
Project the total-event ledger row from the covered measure package. Its
endpoint comparison is already the normalization row required by
$\ProbSpaceUp$, namely $\mu(\Omega)\sim_R1_R$.

Next project the empty event, binary disjoint-union, endpoint, and additive
$\AbGroupUp$ rows exposed by \autoref{def:measure-event-row-coverage}. With
those rows in hand, \autoref{thm:measure-empty-set-zero-from-sigma-additivity}
gives the zero endpoint for the empty event.

Finally apply \autoref{thm:measure-finite-disjoint-union-additivity} to a
covered disjoint measurable pair. The result is exactly the finite-additivity
comparison used by the probability-space carrier; no sigma-additivity theorem
beyond the named $\MeasureUp$ package rows is imported into $\ProbSpaceUp$.
\end{proof}

\begin{theorem}[Measure integral premeasure consumption]
\label{thm:measure-integral-premeasure-consumption}
The $\IntegralUp$ premeasure interface may consume exactly the following rows
from the $\MeasureUp$ package: covered measurable-event rows, $\RealUp$
endpoint classifier rows, countable-sum endpoint rows, classifier-stable
head-tail readback rows, and the finite disjoint-union theorem
\autoref{thm:measure-finite-disjoint-union-additivity}. The same exposed
endpoint classifier and additive compatibility rows are the MeasureUp rows
available to $\FunctionalAnalysisUp$. These rows are precisely the public
surface supplied by \autoref{def:measure-certificate-surface},
\autoref{thm:measureup-sigma-additive-certificate-obligations}, and
\autoref{thm:measure-namecert-obligation-package}.
\end{theorem}
\begin{proof}
Begin with the public certificate surface of
\autoref{def:measure-certificate-surface}. Its projections provide the
measurable-family predicate, endpoint map, countable-sum endpoint, head-tail
readback row, and countable-sum classifier row.

The certificate obligation theorem
\autoref{thm:measureup-sigma-additive-certificate-obligations} identifies the
sigma-algebra rows and the sigma-additivity rows that make those projections
available to premeasure constructions. In particular it names the empty,
binary disjoint-union, countable disjoint-union, sigma-additivity, and
head-tail rows as the complete certificate rows used by the measure
consequences.

The NameCert package theorem
\autoref{thm:measure-namecert-obligation-package} repacks those rows as the
surface consumed by downstream analysis chapters. Reading that package through
\autoref{def:measure-event-row-coverage} leaves exactly the measurable-event,
endpoint, countable-sum, head-tail, and finite disjoint-union rows named in
the statement, with no additional carrier row available for $\IntegralUp$ or
$\FunctionalAnalysisUp$.
\end{proof}
