\begin{theorem}[RatUp reflexive NumField scoped NameCert certificate]
\label{thm:numfield-rat-reflexive-scoped-namecert-certificate}
The RatUp reflexive $\NumFieldUp$ construction carries a scoped
$\NameCert_{\NumFieldUp}$ certificate with the following ten fields.
\begin{enumerate}
\item The traditional target is the finite field extension of RatUp presented
by the reflexive identity extension and the singleton rational basis.
\item The BEDC source is RatUp together with the reflexive $\FieldExtUp$
extension over $\mathsf{BHist}$.
\item The public carrier is
\autoref{def:numfield-rat-reflexive-carrier}.
\item The classifier is $\mathsf{RatHistoryClassifier}$ on the RatUp endpoint
histories.
\item The classifier-stability field is supplied by
\autoref{thm:numfield-rat-reflexive-classifier-transport}.
\item The exactness field is supplied by
\autoref{thm:numfield-rat-reflexive-ledger-exactness}.
\item The ledger field is the RatUp operation-table ledger together with the
singleton basis row, as exhausted by
\autoref{thm:numfield-rat-reflexive-ledger-exactness}.
\item The core witness list is
\autoref{thm:numfield-reflexive-rational-finite-extension-witness} together
with \autoref{thm:numfield-reflexive-namecert-obligation-surface}.
\item The standard-bridge field is absent.
\item The formalization target is the
$\mathsf{BEDC.Derived.NumFieldUp}$ RatUp reflexive certificate surface.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_scoped\_namecert\_certificate}
\begin{proof}
The carrier and classifier fields are projections of
\autoref{def:numfield-rat-reflexive-carrier}. That carrier is already a
package over $\mathsf{BHist}$ whose visible endpoint classifier is
$\mathsf{RatHistoryClassifier}$.

The stability field is
\autoref{thm:numfield-rat-reflexive-classifier-transport}. The exactness and
ledger fields are the two projections of
\autoref{thm:numfield-rat-reflexive-ledger-exactness}: one projection says
that accepted rows are exactly the displayed RatUp reflexive FieldExt rows,
and the other isolates the singleton basis row.

The finite-extension witness is
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}, and the
assembled NameCert obligations are
\autoref{thm:numfield-reflexive-namecert-obligation-surface}. Repacking these
named fields gives the scoped certificate. No additional bridge row is
constructed, so the standard-bridge field remains absent.
\end{proof}

\begin{theorem}[RatUp reflexive NumField public NameCert interface]
\label{thm:numfield-rat-reflexive-public-namecert-interface}
The scoped certificate of
\autoref{thm:numfield-rat-reflexive-scoped-namecert-certificate} exports the
public $\NameCert_{\NumFieldUp}$ surface whose data are the RatUp carrier,
$\mathsf{RatHistoryClassifier}$, the identity embedding, the singleton finite
basis, scalar action by RatUp multiplication, exact endpoint classification,
and the RatUp operation-table ledger.
\end{theorem}
\begin{proof}
Project the scoped certificate along its carrier and classifier fields. These
are the RatUp history carrier and $\mathsf{RatHistoryClassifier}$ because
\autoref{def:numfield-rat-reflexive-carrier} is built from the RatUp reflexive
FieldExt carrier.

Project the extension fields from
\autoref{thm:fieldext-reflexive-public-namecert-interface}. They give the
identity embedding, the self-vector-space row, and scalar action by RatUp
multiplication.

Project the finite-basis field from
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}. Its basis
has exactly the rational unit vector, and its coordinate classifier is the
RatUp endpoint classifier.

Finally project exactness and ledger provenance from
\autoref{thm:numfield-rat-reflexive-ledger-exactness}. Repacking these
projections yields the displayed public $\NameCert_{\NumFieldUp}$ interface.
\end{proof}

\begin{theorem}[RatUp reflexive NumField standard-bridge boundary]
\label{thm:numfield-rat-reflexive-standard-bridge-boundary}
The certificate of
\autoref{thm:numfield-rat-reflexive-scoped-namecert-certificate} claims no
host number-field bridge. Any standard bridge for this surface must separately
interpret the RatUp identity field extension and singleton basis. The public
BEDC surface established here remains entirely within RatUp, $\FieldExtUp$,
$\hsame$, and the displayed $\mathsf{BHist}$ rows.
\end{theorem}
\begin{proof}
Read the bridge field of the scoped certificate. It is explicitly absent, so
the certificate exports only BEDC package data and no host interpretation.

The exported BEDC data are still concrete: the RatUp source certificate, the
reflexive FieldExt carrier, identity embedding, singleton basis, classifier
transport, exact endpoint classification, and operation-table ledger. These
are precisely the fields cited in
\autoref{thm:numfield-rat-reflexive-public-namecert-interface}.

Therefore any host number-field bridge has to add an interpretation of the
RatUp identity extension and its singleton basis as a separate construction.
The present certificate stops at the public BEDC interface and does not claim a
standard bridge.
\end{proof}

\begin{theorem}[NumFieldUp reflexive rational FieldExt scope]
\label{thm:numfield-reflexive-rational-fieldext-scope}
The NumFieldUp source over \autoref{def:numfield-rat-reflexive-carrier}
consumes exactly the RatUp reflexive $\FieldExtUp$ public interface. Its base
field and ambient field are both $\FieldUp(\RatUp)$, its embedding is the
identity row, its vector carrier is $\mathsf{RatHistoryCarrier}$, its scalar
action is RatUp multiplication, and it introduces no additional
$\mathsf{BHist}$ endpoint or classifier beyond the RatUp reflexive source.
\end{theorem}
\begin{proof}
Read the public extension surface from
\autoref{thm:fieldext-reflexive-public-namecert-interface}. The interface
lists the two $\FieldUp(\RatUp)$ endpoint certificates, the identity embedding,
and the self-vector-space carrier over $\mathsf{RatHistoryCarrier}$.

Apply
\autoref{thm:fieldext-ratup-reflexive-operation-table-coverage} to the vector
and scalar rows. It identifies vector addition, vector zero, vector negation,
and scalar action with rows of the RatUp operation table, so the scalar action
is RatUp multiplication.

The carrier of \autoref{def:numfield-rat-reflexive-carrier} only repacks this
public $\FieldExtUp$ surface with the singleton basis field. Therefore the
NumFieldUp source has no separate endpoint, classifier, or operation row
outside the RatUp reflexive FieldExt scope.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_fieldext\_scope}

\begin{theorem}[NumFieldUp reflexive rational singleton-basis exhaustion]
\label{thm:numfield-reflexive-rational-singleton-basis-exhaustion}
Every finite-basis row admitted by the carrier of
\autoref{def:numfield-rat-reflexive-carrier} is the singleton rational unit
basis row. Its only basis endpoint is the RatUp unit history, and every
coordinate comparison is classified by $\mathsf{RatHistoryClassifier}$.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_singleton\_basis\_transport}
\begin{proof}
Use
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}. The
finite-extension witness has basis list $[\mathbf{1}_{\mathsf{Rat}}]$ and
represents each carried ambient endpoint by the coordinate row
$m\cdot\mathbf{1}_{\mathsf{Rat}}$.

Apply
\autoref{thm:numfield-rat-reflexive-ledger-exactness}. It exhausts every
accepted NumField row by the RatUp reflexive FieldExt rows together with the
displayed singleton basis row.

Since there is no second basis field in
\autoref{def:numfield-rat-reflexive-carrier}, any admitted finite-basis row is
that singleton row. The coordinate classifier is the RatUp classifier already
named by the finite-extension witness, namely
$\mathsf{RatHistoryClassifier}$.
\end{proof}

\begin{theorem}[NumFieldUp reflexive rational exactness package]
\label{thm:numfield-reflexive-rational-exactness-package}
The carrier, classifier, FieldExt scope, singleton basis, stability, endpoint
exactness, and ledger rows of \autoref{def:numfield-rat-reflexive-carrier}
assemble a concrete paper-side exactness package for
$\NameCert_{\NumFieldUp}$ over $\mathsf{BHist}$.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_exactness\_package}
\begin{proof}
Start with the carrier and classifier fields from
\autoref{thm:numfield-rat-reflexive-classifier-transport}. They place the
RatUp reflexive package rows in $\mathsf{BHist}$ and transport accepted
packages componentwise by $\hsame$.

Use
\autoref{thm:numfield-reflexive-rational-fieldext-scope} for the extension
surface. It fixes the base and ambient fields to $\FieldUp(\RatUp)$, the
embedding to the identity row, the vector carrier to
$\mathsf{RatHistoryCarrier}$, and scalar action to RatUp multiplication.

Use
\autoref{thm:numfield-reflexive-rational-singleton-basis-exhaustion} for the
finite-basis clause. It shows that the only basis row is the rational unit row
and that coordinate comparisons are read by
$\mathsf{RatHistoryClassifier}$.

Finally combine
\autoref{thm:numfield-rat-reflexive-ledger-exactness} with
\autoref{thm:rat-history-semantic-name-certificate}. The former exhausts the
ledger and exactness rows by the RatUp FieldExt table plus the singleton
basis, while the latter supplies the RatUp endpoint certificate. These rows
are exactly the carrier, classifier, stability, endpoint exactness, and ledger
fields required for the paper-side $\NameCert_{\NumFieldUp}$ exactness
package.
\end{proof}
