\begin{theorem}[RatUp reflexive NumField classifier transport]
\label{thm:numfield-rat-reflexive-classifier-transport}
For accepted package histories $P,Q:\mathsf{BHist}$ in the carrier of
\autoref{def:numfield-rat-reflexive-carrier}, if the displayed package rows of
$P$ and $Q$ are componentwise related by $\hsame$, then the $\NumFieldUp$
classifier transports the carrier of $P$ to the carrier of $Q$. The transported
rows are exactly the RatUp carrier row, the RatUp FieldUp base row, the RatUp
FieldUp ambient row, the identity embedding row, the singleton basis row, and
the scalar-action row.
\end{theorem}
\begin{proof}
Unfold \autoref{def:numfield-rat-reflexive-carrier}. The source pattern is the
RatUp reflexive $\FieldExtUp$ pattern with a singleton basis field, so the
carrier rows of $P$ and $Q$ have the same visible components.

Apply
\autoref{thm:fieldext-ratup-reflexive-source-pattern-lock}. It fixes the base
carrier, ambient carrier, vector carrier, classifiers, identity embedding, and
scalar action to the concrete RatUp data already certified by the
$\FieldUp(\RatUp)$ source.

The RatUp classifier component is read from
\autoref{thm:rat-history-semantic-name-certificate}. Thus componentwise
$\hsame$ transports the rational endpoint rows, and the identity embedding
does not alter either endpoint.

It remains to transport the singleton basis row. The row has one displayed
unit vector and one coordinate classifier, both over the same
$\mathsf{RatHistoryCarrier}$ and $\mathsf{RatHistoryClassifier}$. Projection
from the componentwise $\hsame$ hypothesis therefore gives the transported
basis row, and repacking the transported FieldExt rows with this basis row
gives the claimed $\NumFieldUp$ carrier transport.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexiveSingletonBasis\_scalar\_transport}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_classifier\_transport}

\begin{theorem}[RatUp reflexive NumField ledger exactness]
\label{thm:numfield-rat-reflexive-ledger-exactness}
Every accepted $\NumFieldUp$ carrier row, embedding row, basis row,
scalar-action row, operation row, exactness row, and ledger row in
\autoref{def:numfield-rat-reflexive-carrier} is one of the displayed rows of
the RatUp reflexive $\FieldExtUp$ certificate, together with the singleton
basis row. In particular, the FieldExt rows are exhausted by
\autoref{thm:fieldext-ratup-reflexive-certificate-row-exhaustion}, and the
basis row adds only the unit vector over $\mathsf{RatHistoryCarrier}$ with
coordinate classifier $\mathsf{RatHistoryClassifier}$.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_ledger\_exactness}
\begin{proof}
Begin with an accepted $\NumFieldUp$ row and unfold
\autoref{def:numfield-rat-reflexive-carrier}. The definition admits only rows
belonging to the RatUp reflexive $\FieldExtUp$ source pattern and the singleton
basis field.

For carrier, classifier, embedding, scalar-action, operation, exactness, and
ledger rows, apply
\autoref{thm:fieldext-ratup-reflexive-certificate-row-exhaustion}. It says
that the FieldExt part is covered by the two reads of the
$\FieldUp(\RatUp)$ endpoint certificate, the identity embedding row, and the
self-vector-space row whose scalar action is RatUp multiplication.

The remaining row is the singleton basis field. Its support has one basis
entry, the rational unit history, and its coordinate comparison is the same
RatUp classifier. The basis ledger therefore records no operation endpoint
beyond the unit row already present in the RatUp FieldUp table and no
classifier beyond $\mathsf{RatHistoryClassifier}$.

Combining these projections gives row exactness for the complete
$\NumFieldUp$ carrier: every accepted row is either one of the exhausted
FieldExt rows or the displayed singleton basis row.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexiveSingletonBasis\_ledger\_exactness}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_ledger\_exactness}

\begin{theorem}[RatUp reflexive NumField NameCert obligations]
\label{thm:numfield-rat-reflexive-namecert-obligations}
The carrier of \autoref{def:numfield-rat-reflexive-carrier} satisfies the
paper-side $\NameCert_{\NumFieldUp}$ obligations. Its carrier, classifier,
stability, exactness, ledger, finite-basis, embedding, and scalar-action
clauses are assembled from
\autoref{thm:numfield-rat-reflexive-classifier-transport},
\autoref{thm:numfield-rat-reflexive-ledger-exactness},
\autoref{thm:fieldext-reflexive-public-namecert-interface}, and
\autoref{thm:rat-history-semantic-name-certificate}.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_namecert\_obligations}
\begin{proof}
The carrier clause is
\autoref{def:numfield-rat-reflexive-carrier}. It exposes a concrete package
history over $\mathsf{BHist}$ whose fields are the RatUp reflexive FieldExt
package and the singleton rational basis.

The classifier and stability clauses are supplied by
\autoref{thm:numfield-rat-reflexive-classifier-transport}. This transports the
package componentwise by $\hsame$ and uses the RatUp classifier fields from
\autoref{thm:rat-history-semantic-name-certificate}.

The FieldExt certificate surface is
\autoref{thm:fieldext-reflexive-public-namecert-interface}. It supplies the
base and ambient $\FieldUp(\RatUp)$ certificates, the identity embedding, the
self-vector-space rows, exact endpoint classification, and ledger provenance
over the RatUp operation table.

Finally use
\autoref{thm:numfield-rat-reflexive-ledger-exactness}. It shows that the
NumField ledger contains no row outside the exhausted FieldExt table and the
singleton basis row. Repacking these carrier, classifier, stability,
exactness, finite-basis, embedding, scalar-action, and ledger fields gives the
paper-side $\NameCert_{\NumFieldUp}$ obligation package.
\end{proof}
