\begin{theorem}[AuthorizedGeneratorRecursor acceptance totality]
\label{thm:authorized-generator-recursor-acceptance-totality}
Every accepted $\AuthorizedGeneratorRecursorUp$ carrier exposes its branch, descent, audit, output, and local $\NameCert$ rows through the finite route
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The branch row $B$, descent row $D$, audit row $A$, output row $O$, displayed $\BHist$ carrier, componentwise $\hsame$ transport $H$, displayed $\Cont$ route $C$, $\Pkg$ provenance $P$, ground boundary row $G$, and local $\NameCert$ row $N$ are all available from the accepted packet and no consumer may read a detached recursor surface before these rows have been displayed.
\end{theorem}
\begin{proof}
Start from the carrier of \autoref{def:authorized-generator-recursor-carrier}. Its accepted packet lists exactly the signature, emitted recursor, motive, branch, descent, output, audit, transport, continuation, provenance, boundary, and naming rows.

Apply \autoref{thm:authorized-generator-recursor-root-carrier-route}. It places every closed-substitution-facing read inside the same finite route and makes the branch, descent, audit, and output rows visible only as packet coordinates.

The naming and replay coordinates are supplied by \autoref{thm:authorized-generator-recursor-root-namecert-consumer-readiness} and \autoref{thm:authorized-generator-recursor-ground-compiler-handoff}. These identify $H,C,P,G,N$ as the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support for the same accepted carrier.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorCarrier\_acceptance\_totality}

\begin{theorem}[AuthorizedGeneratorRecursor output stability]
\label{thm:authorized-generator-recursor-output-stability}
For two accepted $\AuthorizedGeneratorRecursorUp$ packets whose displayed branch, descent, audit, transport, continuation, provenance, boundary, and local naming rows are related by the shown $\hsame$ and $\Cont$ routes, every output read of $O$ is stable along those routes. The output cannot be separated from the branch package $B$, descent row $D$, audit row $A$, $\Pkg$ provenance $P$, ground boundary $G$, and local $\NameCert$ row $N$ that present it.
\end{theorem}
\begin{proof}
First expose the output through \autoref{thm:authorized-generator-recursor-acceptance-totality}. The read of $O$ begins only after the branch, descent, audit, transport, continuation, provenance, boundary, and naming rows have been displayed in the same finite packet.

Next apply \autoref{thm:authorized-generator-recursor-output-audit-nonescape}. It prevents an output consumer from detaching $O$ from $A,G,N$ or from replacing the accepted audit route with a host-side read.

The displayed $\hsame$ and $\Cont$ rows then transport the same packet surface componentwise. Since no off-packet generator coordinate is exported, any output read along those routes is the same accepted output read carried by $B,D,A,P,G,N$.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorCarrier\_output\_stability}

\begin{theorem}[AuthorizedGeneratorRecursor ledger separation]
\label{thm:authorized-generator-recursor-ledger-separation}
Audit-ledger reads of an accepted $\AuthorizedGeneratorRecursorUp$ packet do not import host recursion, hidden generators, or closed-substitution facts not already present in
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
Every audit read factors through the displayed branch, descent, output, transport, continuation, provenance, ground-boundary, and local $\NameCert$ rows of the packet.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorCarrier\_ledger\_separation}
\begin{proof}
Begin with \autoref{thm:authorized-generator-recursor-audit-ledger-nonescape}. The audit ledger has no independent source for hidden generators, host induction, external axioms, unaudited dependencies, or off-packet substitution channels.

Use \autoref{thm:authorized-generator-recursor-closed-substitution-gate}. Closed-substitution-facing reads reach the output only after the accepted signature, branch, descent, audit, transport, continuation, provenance, boundary, and naming rows have been carried together.

Finally apply \autoref{thm:authorized-generator-recursor-ground-compiler-authorization}. The ground-compiler consumer reads the same finite packet, so the audit ledger cannot import a recursion principle or substitution fact absent from $I,E,M,B,D,O,A,H,C,P,G,N$.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor acceptance obstruction locality]
\label{cor:authorized-generator-recursor-acceptance-obstruction-locality}
Let an accepted $\AuthorizedGeneratorRecursorUp$ packet be read through the acceptance-totality surface. Any displayed failure, refusal, separation, or countermodel row cited from the route
$$
I,E,M,B,D,O,A,H,C,P,G,N
$$
blocks only the named converse or reuse route whose read would detach $O$ from the displayed branch, descent, audit, transport, continuation, provenance, boundary, or local naming rows. The same row cannot be reinterpreted as a global impossibility result, a host theorem, or hidden external validation for a coordinate absent from the displayed packet.
\end{corollary}
\begin{proof}
By \autoref{thm:authorized-generator-recursor-acceptance-totality}, every accepted read begins from the finite packet $I,E,M,B,D,O,A,H,C,P,G,N$. Thus a consumer-facing obstruction has access only to the listed signature, emitted recursor, motive, branch, descent, output, audit, transport, continuation, provenance, boundary, and local $\NameCert$ coordinates.

Apply \autoref{thm:authorized-generator-recursor-ledger-separation}. It says that audit-ledger reads of the same packet do not import host recursion, hidden generators, external axioms, unaudited dependencies, or closed-substitution facts beyond the displayed rows, and that every audit read factors through the branch, descent, output, transport, continuation, provenance, ground-boundary, and local $\NameCert$ rows. Therefore a cited separation or refusal row can obstruct only a read that asks for one of the excluded off-packet coordinates. Reading it as a global impossibility theorem, a host theorem, or an external validation certificate would require exactly the kind of unlisted coordinate that ledger separation rejects.

It remains to check that the obstruction is strict for output reuse. By \autoref{thm:authorized-generator-recursor-output-stability}, every accepted output read of $O$ is stable only along the displayed $\hsame$ and $\Cont$ routes and cannot be separated from $B,D,A,P,G,N$. Hence a converse or reuse route that omits or replaces those rows is not another interpretation of the accepted output; it is the named failed route blocked at the displayed packet boundary. The obstruction therefore stays local to that coordinate and exports no additional impossibility, host-side theorem, or hidden validation principle.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorAcceptanceObstructionLocality}
