\begin{theorem}[AuthorizedGeneratorRecursor RegSeqRat route factorization]
\label{thm:authorized-generator-recursor-regseqrat-route-factorization}
Let
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N)
$$
be an accepted $\AuthorizedGeneratorRecursorUp$ packet. Every $\RegSeqRatUp$ consumer of the recursor output factors through the displayed signature, eliminator, motive, branch, descent, output, audit, transport, continuation, provenance, boundary, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ rows. In particular, the consumer may read $O$ only after the route retains $I,E,M,B,D,A,H,C,P,G,N$ in the same finite packet, and it obtains no regular-rational source outside that route.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRegSeqRatRouteFactorization}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorCarrier\_regseqrat\_route\_factorization}
\begin{proof}
Start from the L10 source triad, \autoref{thm:authorized-generator-recursor-l10-open-phase-source-triad}. It already identifies the $\RegSeqRatUp$ consumer as a finite-source reader of $I,E,M,B,D,O,A,H,C,P,G,N$ rather than as a separate source producer.

Use the open-phase consumer handoff, \autoref{thm:authorized-generator-recursor-open-phase-consumer-handoff}. The handoff keeps $O$ attached to $A,H,C,P,G,N$, so a regular-rational consumer cannot detach the output from audit, transport, continuation, provenance, boundary, and local naming rows.

Finally apply the ground-compiler authorization row, \autoref{thm:authorized-generator-recursor-ground-compiler-authorization}. The ground-facing read of $O$ is admitted only after the same finite packet has been retained, which is exactly the required factorization route for $\RegSeqRatUp$ consumption.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor Real seal non-escape]
\label{thm:authorized-generator-recursor-real-seal-route-nonescape}
For an accepted $\AuthorizedGeneratorRecursorUp$ packet
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N),
$$
every $\RealUp$ consumer of the recursor output preserves the same finite route through $I,E,M,B,D,O,A,H,C,P,G,N$. The route supplies only displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, audit, and local $\NameCert$ data; it supplies no selected real witness, quotient stream, host equality, detached induction rule, or external proof producer.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRealSealRouteNonescape}
\begin{proof}
Read the output route through \autoref{thm:authorized-generator-recursor-l10-open-phase-source-triad}. The theorem places $\RealUp$ use on the same displayed packet as $\StreamNameUp$ and $\RegSeqRatUp$, with no coordinate for a selected limit or quotient stream.

The consumer side is controlled by \autoref{thm:authorized-generator-recursor-open-phase-consumer-handoff}. It allows specialization to a real-source route while keeping $O$ with $A,H,C,P,G,N$ and excluding host choice, hidden induction, selected-limit, quotient-stream, and proof-producing interpretations.

The ledger side is closed by \autoref{thm:authorized-generator-recursor-open-phase-ledger-nonescape}. Since the audit and boundary rows exhaust what can be exported to the real-facing consumer, the real seal does not escape the AuthorizedGeneratorRecursor packet.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor completion boundary exhaustion]
\label{thm:authorized-generator-recursor-completion-boundary-exhaustion}
Let $R=(I,E,M,B,D,O,A,H,C,P,G,N)$ be an accepted $\AuthorizedGeneratorRecursorUp$ packet. A completion-facing consumer of the recursor output has exactly two admissible boundary shapes: it either displays a separate completion-seal row before using completion data, or it remains bounded by the AuthorizedGeneratorRecursor packet through $I,E,M,B,D,O,A,H,C,P,G,N$. Without the separate completion-seal row, the consumer cannot read a completion object, quotient completion equality, selected limit, host completeness proof, or off-packet proof producer.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:authorized-generator-recursor-open-phase-consumer-handoff}. Completion-facing use is treated as a downstream specialization of the same finite output route, so $O$ remains attached to $A,H,C,P,G,N$.

Apply \autoref{thm:authorized-generator-recursor-open-phase-ledger-nonescape}. The ledger exported by the packet is finite and local to $I,E,M,B,D,O,A,H,C,P,G,N$, and it does not export completion objects, real-completeness data, quotient completion equality, selected limits, or host completeness proofs.

If the consumer displays a separate completion-seal row, that row is outside the AuthorizedGeneratorRecursor packet and must carry its own boundary obligation. If it does not, the ground-compiler authorization theorem \autoref{thm:authorized-generator-recursor-ground-compiler-authorization} keeps the consumer on the accepted packet surface, exhausting the completion boundary at $G,N$ and the retained audit route.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor RegSeqRat route strict obstruction]
\label{cor:authorized-generator-recursor-regseqrat-route-strict-obstruction}
Let
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N)
$$
be an accepted $\AuthorizedGeneratorRecursorUp$ packet. Suppose a displayed failure, refusal, separation, or countermodel row is used against a named converse, reuse, or readback route for the $\RegSeqRatUp$ factorization of $R$. Then the row is a strict local obstruction: it blocks only that named route at the finite packet surface
$$
I,E,M,B,D,O,A,H,C,P,G,N,
$$
with readback through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, audit, transport, provenance, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ rows. It cannot be reinterpreted as a global impossibility theorem, a host theorem about recursors or real completion, hidden external validation of the failed route, a selected real witness, a quotient stream equality, a detached induction rule, a completion object, or an external proof producer.
\end{corollary}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRegSeqRatRouteStrictObstruction}
\begin{proof}
Apply the $\RegSeqRatUp$ route factorization theorem, \autoref{thm:authorized-generator-recursor-regseqrat-route-factorization}. It states that every $\RegSeqRatUp$ consumer of the recursor output factors through the displayed signature, eliminator, motive, branch, descent, output, audit, transport, continuation, provenance, boundary, and local naming rows. In particular, the consumer may read $O$ only while retaining $I,E,M,B,D,A,H,C,P,G,N$ in the same finite packet, and it obtains no regular-rational source outside that route.

Now apply the Real seal non-escape theorem, \autoref{thm:authorized-generator-recursor-real-seal-route-nonescape}. The real-facing endpoint preserves the same finite route through $I,E,M,B,D,O,A,H,C,P,G,N$ and supplies only displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, audit, and local $\NameCert$ data. It supplies no selected real witness, quotient stream, host equality, detached induction rule, or external proof producer.

Consider the displayed failure, refusal, separation, or countermodel row. If it is cited against a named converse, reuse, or readback route, the first theorem forces that citation to live on the $\RegSeqRatUp$ factorization surface, and the second theorem prevents the same citation from being lifted through a real-facing escape coordinate. Thus the row can obstruct only the advertised route at the coordinate where that route asks to read, reuse, detach, or bypass one of the displayed packet rows.

Any stronger interpretation asks for data that neither theorem exports. A global impossibility theorem would require a theorem surface beyond the accepted finite packet; a host theorem would require host equality, detached induction, or host completeness data; hidden external validation would require a proof-producing channel outside the packet; a selected real witness, quotient stream equality, or completion object would require one of the objects explicitly absent from the real seal. Since the accepted packet exports none of these coordinates, the obstruction remains strict and local to the named $\RegSeqRatUp$ route.
\end{proof}
