\begin{definition}[AuthorizedGeneratorRecursor readiness route obligation packet]
\label{def:authorized-generator-recursor-readiness-route}
An $\AuthorizedGeneratorRecursorUp$ readiness route is the finite $\BHist$
packet
$$
Q=(U,J,K,O,L,H,C,P,N)
$$
read from the admitted carrier of
\autoref{def:authorized-generator-recursor-carrier}. The authorization row
$U$ records the accepted constructor signature, emitted eliminator, checked
motive, complete branch package, and structural descent rows
$I,E,M,B,D$; the generator row $J$ records the authorized recursor call; the
ground-compiler recognition row $K$ records that the route reaches the
compiler boundary only through $G$; the output row $O$ is the displayed public
name; the refusal ledger $L$ records the audit row $A$ together with the
refusal of unlisted branches, non-structural recursion, external axioms, hidden
generators, and unaudited dependency channels; $H$ is componentwise $\hsame$
transport; $C$ is the displayed $\Cont$ replay route; $P$ is the $\Pkg$
provenance row; and $N$ is the local
$\NameCert_{\AuthorizedGeneratorRecursorUp}$ row.
\end{definition}
\leandef{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorReadinessRoute}

\begin{theorem}[AuthorizedGeneratorRecursor ground compiler admission]
\label{thm:authorized-generator-recursor-ground-compiler-admission}
Every accepted $\AuthorizedGeneratorRecursorUp$ readiness route factors its
generator output through the authorization row $U$ and the ground-compiler
recognition row $K$. Equivalently, no route may expose $O$ to a
ground-compiler consumer unless the same finite packet retains the accepted
signature, emitted eliminator, motive, branch package, structural descent,
audit provenance, boundary row, transports, continuation replay, package
provenance, and local NameCert row.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursor\_ground\_compiler\_admission}
\leanvariant{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorGroundCompilerAdmission}
\begin{proof}
Start with root carrier admission. By
\autoref{thm:authorized-generator-recursor-root-carrier-admission}, the
accepted packet exposes only $I,E,M,B,D,O,A,H,C,P,G,N$ before a
ground-compiler or output-facing consumer may read it.

The authorization row $U$ is obtained by grouping the signature, eliminator,
motive, branch, and descent rows. Theorems
\ref{thm:authorized-generator-recursor-branch-exhaustion} and
\ref{thm:authorized-generator-recursor-structural-descent-locality} keep the
authorized generator call on those rows, so $J$ cannot be read as a detached
proof-producing source.

Now attach compiler recognition. The ground-compiler authorization theorem and
the handoff theorem, \autoref{thm:authorized-generator-recursor-ground-compiler-authorization}
and \autoref{thm:authorized-generator-recursor-ground-compiler-handoff}, force
any compiler-facing read of $O$ to retain $G,H,C,P,N$ with the audit row. Thus
the output reaches the compiler only through $U$ and $K$ inside the displayed
readiness packet.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor output refusal route]
\label{thm:authorized-generator-recursor-output-refusal}
Any request against an $\AuthorizedGeneratorRecursorUp$ readiness route that
omits either the authorization row $U$ or the refusal ledger $L$ remains
$\mathsf{GAP}$-ledger content. Such a request is not exported as the public
output row $O$ and is not consumed as a ground-compiler route.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursor\_output\_refusal}
\begin{proof}
First read the refusal side of the carrier. The $\mathsf{GAP}$ boundary
refusal theorem, \autoref{thm:authorized-generator-recursor-gap-boundary-refusal},
places external axioms, hidden generators, non-structural recursion, and
unlisted branches behind the boundary row $G$ and the audit row $A$.

If $U$ is absent, the request has no accepted signature, eliminator, motive,
branch package, or structural descent row from which a recursor output can be
formed. Root authorization obligations and root ground-compiler authorization
therefore leave the request at the boundary rather than at $O$.

If $L$ is absent, the request has no source-refusal, dependency-refusal, or
hidden-generator ledger attached to the output route. The audit dependency
refusal theorem and the root output boundary package keep such a request in
the $\mathsf{GAP}$ ledger until the refusal rows are restored.

Finally apply root output saturation. Since
\autoref{thm:authorized-generator-recursor-root-output-route-saturation}
exports $O$ only through the saturated carrier route, a request missing $U$ or
$L$ cannot be the exported output and cannot be read as a compiler-recognized
route.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor NameCert obligation exhaustion]
\label{thm:authorized-generator-recursor-namecert-obligation-exhaustion}
The rows of the readiness route obligation packet exhaust the local carrier,
classifier, stability, ledger, and non-escape obligations for
$\AuthorizedGeneratorRecursorUp$. Carrier admission is supplied by $U,J,K,O$;
classifier visibility is supplied by $C,N$; stability is supplied by $H$ and
$P$; the refusal ledger is supplied by $L$; and non-escape is supplied by the
joint retention of $U,K,L,H,C,P,N$ around $O$.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorNameCertObligationExhaustion}
\begin{proof}
Carrier exhaustion is already finite. The carrier admission packet supplies
$I,E,M,B,D,O,A,H,C,P,G,N$, and the readiness route only repackages these rows
as authorization, generator, ground-compiler recognition, output, refusal,
transport, replay, provenance, and local naming rows.

Classifier and stability obligations are retained by the public surface. The
NameCert surface of \autoref{thm:authorized-generator-recursor-namecert-surface}
classifies the route through the same packet, while output-name stability keeps
$O$ attached to $H,C,P,G,N$ and to the authorization rows.

The ledger obligations are exhausted by refusal and audit rows. Use
\autoref{thm:authorized-generator-recursor-audit-dependency-refusal},
\autoref{thm:authorized-generator-recursor-root-audit-membrane-source-refusal},
and \autoref{thm:authorized-generator-recursor-gap-boundary-refusal}; together
they place source refusal, dependency refusal, and hidden-generator refusal in
$L$ before output exposure.

It remains to rule out escape. Root carrier admission, root output route
saturation, and ground-compiler admission above keep every consumer-facing read
inside the same finite packet. Therefore the readiness rows exhaust the local
carrier, classifier, stability, ledger, and non-escape obligations without
adding an off-packet route.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor readiness-route public-admission strict obstruction]
\label{cor:authorized-generator-recursor-readiness-route-public-admission-strict-obstruction}
Let
$$
Q=(U,J,K,O,L,H,C,P,N)
$$
be an $\AuthorizedGeneratorRecursorUp$ readiness route. Suppose a displayed
failure, refusal, separation, or countermodel row is cited against a named
public-admission converse or reuse route for the output row $O$. Then the cited
row is a strict local obstruction: it blocks only the named route whose
consumer-facing read omits, replaces, or bypasses one of the displayed
readiness coordinates
$$
U,J,K,O,L,H,C,P,N.
$$
In particular, its force is confined to the authorization row $U$, the
generator-call row $J$, the ground-compiler recognition row $K$, the output row
$O$, the refusal ledger $L$, componentwise $\hsame$ transport $H$, the
$\Cont$ replay route $C$, the $\Pkg$ provenance row $P$, and the local
$\NameCert_{\AuthorizedGeneratorRecursorUp}$ row $N$. It cannot be
reinterpreted as a global impossibility theorem, a host theorem, hidden
external validation, or an off-packet certificate for any coordinate not
displayed by $Q$.
\end{corollary}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorReadinessRoutePublicAdmissionStrictObstruction}
\begin{proof}
Read the packet from \autoref{def:authorized-generator-recursor-readiness-route}.
The readiness route has exactly the displayed finite coordinates
$U,J,K,O,L,H,C,P,N$. The row $U$ is the only authorization package for the
accepted signature, eliminator, motive, branch package, and structural descent
rows; $J$ is only the authorized recursor call; $K$ reaches the compiler
boundary only through the displayed boundary row; $L$ is the refusal ledger for
unlisted branches, non-structural recursion, external axioms, hidden
generators, and unaudited dependency channels; and $H,C,P,N$ are respectively
the displayed transport, replay, provenance, and local naming rows. Thus a
consumer-facing use of the public output has no coordinate from which to read a
detached converse route, a second generator route, a host theorem, or an
external validation certificate.

Now apply \autoref{thm:authorized-generator-recursor-output-refusal}. Any
request against the readiness route that omits $U$ or $L$ remains
$\mathsf{GAP}$-ledger content. It is not exported as $O$ and is not consumed as
a ground-compiler route. Hence a displayed refusal, failure, separation, or
countermodel row can affect a public-admission converse or reuse attempt only
at the precise coordinate where that attempt omits, replaces, or bypasses the
authorization package or the refusal ledger.

It remains to exclude stronger readings. Interpreting the same row as a global
impossibility theorem would require a theorem surface not indexed by the named
failed route. Interpreting it as a host theorem would require a host-facing
recursion, induction, equality, or completion coordinate outside the packet.
Interpreting it as hidden external validation would require a certificate
channel not carried by $H,C,P,N$ and not audited by $L$. None of these
coordinates appears in $Q$, and the output-refusal route leaves every request
missing $U$ or $L$ at the local $\mathsf{GAP}$ boundary. Therefore the
obstruction is strict and local to the named public-admission converse or reuse
route.
\end{proof}
