\begin{theorem}[AuthorizedGeneratorRecursor root branch-package coverage]
\label{thm:authorized-generator-recursor-root-branch-package-coverage}
For every accepted $\AuthorizedGeneratorRecursorUp$ root packet with displayed carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N),
$$
the branch-package surface exposes every constructor branch only through the accepted signature, emitted eliminator, checked motive, branch package, and structural-descent rows $I,E,M,B,D$. Any branch not listed by $I$ and not carried by $B$ is rejected before a downstream generator-audit or closed-normal consumer can read the output row $O$.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootBranchPackageCoverage}
\begin{proof}
Project the carrier of \autoref{def:authorized-generator-recursor-carrier}. The rows $I,E,M,B,D$ are displayed before $O$, and the carrier has no coordinate for an extra constructor, missing branch, or detached branch table.

Use the local NameCert surface and the root row exposure results. By \autoref{thm:authorized-generator-recursor-namecert-surface}, \autoref{thm:authorized-generator-recursor-root-branch-row-exposure}, and \autoref{thm:authorized-generator-recursor-root-signature-row-totality}, the branch package is read as part of the same finite packet rather than through a hidden generator route.

Finally apply \autoref{thm:authorized-generator-recursor-branch-exhaustion}, \autoref{thm:authorized-generator-recursor-branch-budget-exhaustion}, and \autoref{thm:authorized-generator-recursor-obligation-triad}. They force branch coverage to stay on the constructor list displayed by $I$, the recursor row $E$, the checked motive $M$, the branch package $B$, and the descent row $D$. Thus an unlisted branch has no public route to $O$.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor root motive descent stability]
\label{thm:authorized-generator-recursor-root-motive-descent-stability}
For every accepted $\AuthorizedGeneratorRecursorUp$ root packet, structural descent through $D$ preserves the checked motive row $M$ before the output row $O$ is exposed. A public recursive read cannot retain the descent row while replacing the motive, cannot read $O$ from a motive-free descent surface, and cannot route the recursor through a branch package detached from $M$.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootMotiveDescentStability}
\begin{proof}
Start with the carrier and root descent exposure. The packet of \autoref{def:authorized-generator-recursor-carrier} places $M$ and $D$ in the same displayed tuple, while \autoref{thm:authorized-generator-recursor-root-descent-row-exposure} exposes the descent row on every root-facing recursive read.

The stability step is supplied by structural locality. Apply \autoref{thm:authorized-generator-recursor-structural-descent-locality}, \autoref{thm:authorized-generator-recursor-branch-descent-totality}, and \autoref{thm:authorized-generator-recursor-root-descent-audit-coupling}. These results keep the recursive read on the accepted signature, emitted eliminator, checked motive, branch package, descent row, and audit row together.

It remains to reach the output boundary. By \autoref{thm:authorized-generator-recursor-root-output-audit-totality} and \autoref{thm:authorized-generator-recursor-root-output-namecert-saturation}, public exposure of $O$ consumes the same packet. The TasteGate target named \texttt{BEDC.Derived.AuthorizedGeneratorRecursorUp.taste\_gate} is used only as the aligned-carrier marker from \autoref{thm:authorized-generator-recursor-ground-compiler-handoff}; the paper-side motive and descent obligations are carried by the cited root theorems.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor root audit ledger exactness]
\label{thm:authorized-generator-recursor-root-audit-ledger-exactness}
For every accepted $\AuthorizedGeneratorRecursorUp$ root packet, public output reads factor through exactly the output, audit, transport, continuation, package, boundary, and local-name rows $O,A,H,C,P,G,N$ after branch and descent admission. The packet exports no hidden generator, unaudited dependency route, external axiom channel, or naming certificate outside the displayed audit ledger.
\end{theorem}
\begin{proof}
Read the audit ledger from the carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N).
$$
The rows $O,A,H,C,P,G,N$ are public only as coordinates of this packet, and \autoref{thm:authorized-generator-recursor-audit-boundary} places output exposure behind the accepted signature, motive, branch package, structural descent, and audit provenance.

Use factorization through the sibling root surfaces. \autoref{thm:authorized-generator-recursor-audit-provenance-factorization}, \autoref{thm:authorized-generator-recursor-root-audit-boundary-exposure}, \autoref{thm:authorized-generator-recursor-root-consumer-factorization}, and \autoref{thm:authorized-generator-recursor-consumer-ledger-cover} attach $O$ to $A,H,C,P,G,N$ before any downstream consumer can cite the recursor output.

Finally apply the refusal and readiness results. \autoref{thm:authorized-generator-recursor-root-boundary-nonescape}, \autoref{thm:authorized-generator-recursor-root-audit-handoff-lock}, and \autoref{thm:authorized-generator-recursor-root-readiness-exhaustion} exclude hidden generators, unaudited dependency routes, and off-packet naming. Therefore the public ledger is exact for the displayed audit route and exports nothing beyond it.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursor\_root\_audit\_ledger\_exactness}
