\begin{theorem}[AuthorizedGeneratorRecursor root carrier route]
\label{thm:authorized-generator-recursor-root-carrier-route}
Every closed-substitution-facing route from an accepted $\AuthorizedGeneratorRecursorUp$ packet factors through the displayed packet rows
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The route may expose the accepted signature, emitted recursor, motive, branch package, descent row, output row, audit row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, ground-compiler boundary, and local $\NameCert$ row, but it has no route coordinate outside that finite carrier.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootCarrierRoute}
\begin{proof}
Start from the carrier of \autoref{def:authorized-generator-recursor-carrier}. It lists exactly the packet rows $I,E,M,B,D,O,A,H,C,P,G,N$, so a closed-substitution-facing consumer begins from the same finite route used by the root recursor surface.

Apply \autoref{thm:authorized-generator-recursor-root-normalization-boundary}. The normalization and closed-substitution consumers receive $O$ only after signature admission, branch coverage, structural descent, audit provenance, and the ground-compiler boundary have been displayed.

Finally use \autoref{thm:authorized-generator-recursor-root-namecert-consumer-readiness} and \autoref{thm:authorized-generator-recursor-ground-compiler-handoff}. These identify the consumer route with the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, and $\NameCert$ rows, leaving no additional carrier for an off-packet substitution read.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor closed substitution gate]
\label{thm:authorized-generator-recursor-closed-substitution-gate}
For a sibling $\ClosedTermSubstitutionBoundaryUp$ consumer, the output row $O$ of an accepted $\AuthorizedGeneratorRecursorUp$ packet is reachable only after the signature rows $I,E,M$, branch row $B$, descent row $D$, audit row $A$, componentwise transport row $H$, displayed continuation row $C$, package row $P$, ground-compiler boundary row $G$, and local naming row $N$ have all been carried in the same finite packet. In particular, the consumer reaches $O$ through $\Cont$, $\Pkg$, and $\NameCert$ rows rather than through a detached substitution principle.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorClosedSubstitutionGate}
\begin{proof}
First invoke \autoref{thm:authorized-generator-recursor-root-carrier-route}. It places every closed-substitution-facing route inside the displayed packet before any consumer reads the output row.

Next apply \autoref{thm:authorized-generator-recursor-root-normalization-boundary}. This forces the output read behind accepted signatures, branch coverage, structural descent, audit provenance, and the sibling closed-substitution boundary rows.

The remaining rows are the transport and naming rows. By \autoref{thm:authorized-generator-recursor-root-namecert-consumer-readiness}, the route exposes $H,C,P,G,N$ as componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, ground-compiler boundary, and local $\NameCert$ data. Thus the sibling consumer reaches $O$ only after the stated route has been displayed.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor audit ledger nonescape]
\label{thm:authorized-generator-recursor-audit-ledger-nonescape}
The audit ledger exported by an accepted $\AuthorizedGeneratorRecursorUp$ packet carries no hidden generator, host induction principle, external axiom, unaudited dependency route, or off-packet substitution channel. Every audit-facing closed-substitution read remains inside the route
$$
I,E,M,B,D,O,A,H,C,P,G,N
$$
and inside the local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed by that packet.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorAuditLedgerNonescape}
\begin{proof}
Begin with the carrier route of \autoref{thm:authorized-generator-recursor-root-carrier-route}. Since every closed-substitution-facing route factors through the finite packet, the audit ledger has no independent source row from which to export a hidden generator or host induction principle.

Next use the closed substitution gate of \autoref{thm:authorized-generator-recursor-closed-substitution-gate}. The output row is reachable only after the signature, branch, descent, audit, transport, continuation, package, boundary, and local naming rows have been displayed.

Finally apply \autoref{thm:authorized-generator-recursor-ground-compiler-handoff}. The handoff consumes the same finite carrier and supplies no external axiom, unaudited dependency route, or off-packet substitution channel. Therefore the audit ledger remains nonescaping for the displayed authorized-generator packet.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor root route strict obstruction]
\label{cor:authorized-generator-recursor-root-route-strict-obstruction}
Let an accepted $\AuthorizedGeneratorRecursorUp$ packet be read by a $\ClosedTermSubstitutionBoundaryUp$ consumer through the root route of \autoref{thm:authorized-generator-recursor-root-carrier-route}. Any consumer-facing use of the obstruction recorded by \autoref{thm:authorized-generator-recursor-audit-ledger-nonescape} is strict and local: it can block only the named converse or reuse route that tries to read the output row $O$ without the displayed packet rows
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
Equivalently, the obstruction is confined to the failure of an off-packet closed-substitution, hidden-generator, host-induction, unaudited-dependency, or detached-output route. It cannot be reinterpreted as a global impossibility theorem, a host theorem, or hidden external validation of any coordinate outside the accepted $\AuthorizedGeneratorRecursorUp$ packet.
\end{corollary}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootRouteStrictObstruction}
\begin{proof}
Read the root carrier route first. By \autoref{thm:authorized-generator-recursor-root-carrier-route}, every closed-substitution-facing route from the accepted packet factors through exactly the finite carrier
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The same statement identifies the exposed data as the accepted signature, emitted recursor, motive, branch package, descent row, output row, audit row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, ground-compiler boundary, and local $\NameCert$ row. Hence a consumer-facing route has no independent coordinate from which to read a second generator, a detached substitution principle, a host induction principle, or an external theorem.

Now apply \autoref{thm:authorized-generator-recursor-audit-ledger-nonescape}. The audit ledger carries no hidden generator, host induction principle, external axiom, unaudited dependency route, or off-packet substitution channel, and every audit-facing closed-substitution read remains inside the displayed carrier and inside the local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Thus a displayed failure, refusal, separation, or countermodel row can only deny the attempted converse or reuse route at the packet coordinate where that route asks to leave the carrier.

The remaining interpretations are outside the finite route. A global impossibility theorem would quantify beyond the accepted packet; a host theorem would add semantic strength not carried by $I,E,M,B,D,O,A,H,C,P,G,N$; hidden external validation would require an extra validating row not present among $A,H,C,P,G,N$. Since the cited carrier and ledger theorems give no such coordinate, the obstruction has exactly its local blocking force against the named converse or reuse route and no wider export surface.
\end{proof}
