\begin{definition}[AuthorizedGeneratorRecursor root output boundary package]
\label{def:authorized-generator-recursor-root-output-boundary-package}
The root output boundary package for an accepted $\AuthorizedGeneratorRecursorUp$ packet is the finite $\BHist$ carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N)
$$
of \autoref{def:authorized-generator-recursor-carrier}, read with the following boundary roles. The rows $I,E,M,B,D$ form the signature, eliminator, motive, branch, and structural-descent admission surface. The row $O$ is the public output name. The rows $A,H,C,P,G,N$ form the audit provenance, componentwise transport, continuation, package provenance, host-boundary, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ surface. The package admits $O$ only as a row of this displayed packet, after the branch package, descent locality, audit provenance, operational-membrane handoff, kernel-boundary exhaustion, and TasteGate carrier handoff have all been retained.
\end{definition}
\leandef{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootOutputBoundaryPackage}

\begin{theorem}[AuthorizedGeneratorRecursor root branch output closed boundary]
\label{thm:authorized-generator-recursor-root-branch-output-closed-boundary}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet, public output reads from the root output boundary package of \autoref{def:authorized-generator-recursor-root-output-boundary-package} occur only after the accepted signature row $I$, emitted eliminator row $E$, checked motive row $M$, branch-package row $B$, and structural-descent row $D$ have been retained. No public read of $O$ can detach the output from the constructor signature, eliminator, motive, branch package, or structural descent rows.
\end{theorem}
\begin{proof}
Project the carrier named by \autoref{def:authorized-generator-recursor-carrier}. The package of \autoref{def:authorized-generator-recursor-root-output-boundary-package} uses the same displayed tuple
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N).
$$

Branch coverage is forced before any output read. Apply \autoref{thm:authorized-generator-recursor-branch-exhaustion}; the row $B$ contains exactly the branches associated with the accepted constructors displayed by $I$ and the eliminator named by $E$.

Descent locality then binds the recursive read to the motive and descent rows. By \autoref{thm:authorized-generator-recursor-structural-descent-locality}, a public recursive read cannot pass through a generator route detached from $M$ and $D$.

Finally use \autoref{thm:authorized-generator-recursor-ground-compiler-handoff}. The TasteGate handoff consumes only the same finite carrier, so it cannot supply an output route that bypasses $I,E,M,B,D$. Therefore public access to $O$ is closed under the displayed branch and descent boundary.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursor\_root\_branch\_output\_closed\_boundary}

\begin{theorem}[AuthorizedGeneratorRecursor root audit membrane source refusal]
\label{thm:authorized-generator-recursor-root-audit-membrane-source-refusal}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet, the audit row $A$ of the root output boundary package consumes $\OperationalMembraneUp$ provenance, source-axiom refusal, and dependency refusal before the output row $O$ is public. Thus $O$ cannot be read as a public output through an audit route that omits operational provenance, source refusal, or transitive dependency refusal.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootAuditMembraneSourceRefusal}
\begin{proof}
Begin with the audit side of \autoref{def:authorized-generator-recursor-root-output-boundary-package}. The rows $O,A,H,C,P,G,N$ are retained together, and $A$ is the row that records the build check, source-axiom refusal, dependency refusal, and operational-membrane provenance.

Apply \autoref{thm:authorized-generator-recursor-audit-provenance-factorization}. It prevents $O$ from becoming public apart from $A,H,C,P,G,N$, so the output row cannot be read as an unaudited recursor result.

Now apply \autoref{thm:authorized-generator-recursor-operational-membrane-audit-handoff}. The audit row must consume the $\OperationalMembraneUp$ provenance before public exposure of $O$, and the same row carries source-axiom and dependency refusal for the packet.

The carrier alignment of \autoref{thm:authorized-generator-recursor-ground-compiler-handoff} supplies no substitute audit channel. Hence a public output read must pass through operational provenance, source refusal, and dependency refusal before $O$ leaves the package boundary.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor root host-boundary NameCert exhaustion]
\label{thm:authorized-generator-recursor-root-host-boundary-namecert-exhaustion}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet, the host-boundary row $G$ of the root output boundary package is exhausted by the displayed $\NameCert_{\AuthorizedGeneratorRecursorUp}$ packet. At $G$ the packet cannot export a free induction principle, hidden branch source, external axiom, or proof generator outside
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootHostBoundaryNameCertExhaustion}
\begin{proof}
Read the host-boundary row from \autoref{def:authorized-generator-recursor-root-output-boundary-package}. The row $G$ is not a second generator surface; it is one coordinate of the same finite carrier displayed in \autoref{def:authorized-generator-recursor-carrier}.

Branch and descent escape are already excluded inside the packet. Use \autoref{thm:authorized-generator-recursor-branch-exhaustion} and \autoref{thm:authorized-generator-recursor-structural-descent-locality} to keep every branch source and recursive call on $I,E,M,B,D$.

Audit escape is excluded before the boundary row becomes useful to a consumer. By \autoref{thm:authorized-generator-recursor-audit-provenance-factorization} and \autoref{thm:authorized-generator-recursor-operational-membrane-audit-handoff}, public output remains attached to the audit provenance, operational membrane, source refusal, dependency refusal, transport, continuation, package, and local name rows.

Finally apply \autoref{thm:authorized-generator-recursor-kernel-boundary-exhaustion} together with \autoref{thm:authorized-generator-recursor-ground-compiler-handoff}. The boundary row is exhausted by the displayed NameCert packet and the TasteGate carrier handoff adds no free induction principle, hidden branch source, external axiom, or proof generator.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor root output boundary strict obstruction]
\label{cor:authorized-generator-recursor-root-output-boundary-strict-obstruction}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet, any displayed failure, refusal, separation, or countermodel row attached to the root output boundary package of \autoref{def:authorized-generator-recursor-root-output-boundary-package} is a strict local obstruction. It blocks only the named converse or reuse route that would read $O$ without the displayed audit and boundary rows. It does not state a global impossibility for recursors, does not become a host theorem about all generators, and does not supply hidden external validation. Equivalently, every consumer-facing use of the obstruction factors through the finite rows
$$
I,E,M,B,D,O,A,H,C,P,G,N,
$$
and every unlisted coordinate is rejected as outside the local $\AuthorizedGeneratorRecursorUp$ packet.
\end{corollary}
\begin{proof}
Start from the package definition. By \autoref{def:authorized-generator-recursor-root-output-boundary-package}, the root output boundary is the single finite $\BHist$ carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N).
$$
The row $O$ is public only as the output row of this carrier. The rows $I,E,M,B,D$ supply the accepted signature, emitted eliminator, checked motive, branch package, and structural descent surface, while $A,H,C,P,G,N$ supply audit provenance, componentwise transport, continuation, package provenance, host boundary, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ data. Thus a consumer-facing use cannot begin from an isolated output token; it must enter through one of the displayed rows.

Apply \autoref{thm:authorized-generator-recursor-root-audit-membrane-source-refusal}. The only obstruction supplied by the audit side is the refusal of an output read whose audit route omits $\OperationalMembraneUp$ provenance, source-axiom refusal, or transitive dependency refusal. This is a local refusal at $A$ and its attached output ledger $O,A,H,C,P,G,N$. It blocks the converse route that tries to reuse $O$ as unaudited output, but it does not assert that no accepted recursor output exists and does not certify any fact outside the displayed packet.

Apply \autoref{thm:authorized-generator-recursor-root-host-boundary-namecert-exhaustion}. At the host-boundary row $G$, the packet exports no free induction principle, hidden branch source, external axiom, or proof generator outside
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
Therefore the boundary obstruction blocks only the attempted reuse of $G$ as a host-side generator or external validation channel. It cannot be reinterpreted as a host theorem about all generator mechanisms, because the cited theorem exhausts $G$ by the same local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ carrier.

It remains to exclude unlisted consumer coordinates. If a consumer-facing use were global, host-theoretic, or externally validated, it would need a coordinate not among the admission rows $I,E,M,B,D$, the output and audit rows $O,A,H,C,P$, or the boundary and name rows $G,N$. The package definition supplies no such coordinate; the audit refusal eliminates unaudited output reuse; and the host-boundary exhaustion eliminates free host proof production at $G$. Hence each displayed failure, refusal, separation, or countermodel row is strict in exactly the local sense: it obstructs the named converse or reuse route inside the root output boundary package, while every broader reading remains outside the BEDC packet.
\end{proof}
