\begin{theorem}[AuthorizedGeneratorRecursor root output consumer triad]
\label{thm:authorized-generator-recursor-root-output-consumer-triad}
Every root output consumer of an accepted $\AuthorizedGeneratorRecursorUp$
packet receives the output row only through the finite $\BHist$ route
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The route displays the accepted authorization surface $I,E,M,B,D$, the
generator state witnessed by the output row $O$, the audit row $A$, the
componentwise $\hsame$ row $H$, the displayed $\Cont$ route $C$, the $\Pkg$
provenance row $P$, the ground-boundary row $G$, and the local
$\NameCert_{\AuthorizedGeneratorRecursorUp}$ row $N$.

Thus a root consumer has no hidden generator authority, host recursion oracle,
off-packet output row, detached readiness row, private continuation, external
package source, or outside naming certificate.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursor\_root\_output\_consumer\_triad}
\begin{proof}
Begin with route-pack exactness,
\autoref{thm:authorized-generator-recursor-route-pack-exactness}. It makes
$I,E,M,B,D,O,A,H,C,P,G,N$ the complete packet available to a recursor route.

Use the downstream consumer ledger cover,
\autoref{thm:authorized-generator-recursor-consumer-ledger-cover}. It states
that generator, substitution-boundary, and TasteGate consumers receive only
the carrier, branch, descent, audit, transport, continuation, package,
boundary, and local naming rows displayed by the packet.

Finally apply output route readiness,
\autoref{thm:authorized-generator-recursor-output-route-readiness}. The output
row $O$ is route-ready only inside the same finite packet, so a root consumer
cannot replace the displayed authorization, readiness, continuation, package,
ground-boundary, or local naming rows by hidden generator authority or host
recursion.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor readiness route totality]
\label{thm:authorized-generator-recursor-readiness-route-totality}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet, the readiness route
from authorization to output is total exactly on the displayed rows
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The accepted constructor signature, emitted eliminator, motive, branch
package, and structural descent rows provide authorization; the output row and
audit row provide generator-state exposure and refusal evidence; the
$\hsame$, $\Cont$, $\Pkg$, ground-boundary, and local $\NameCert$ rows provide
the only admissible route support.

No consumer may complete the readiness route by importing an unlisted branch,
non-structural recursive call, hidden generator state, host recursion rule,
private output channel, or off-packet naming witness.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorReadinessRouteTotality}
\begin{proof}
Start from the readiness route obligation packet of
\autoref{def:authorized-generator-recursor-readiness-route}. It repackages the
accepted carrier rows as authorization, generator, ground-recognition, output,
refusal, transport, replay, provenance, and local naming data.

Apply ground compiler admission,
\autoref{thm:authorized-generator-recursor-ground-compiler-admission}. The
generator output reaches any ground-compiler or output-facing consumer only
through the authorization row and ground-boundary recognition carried by the
same finite packet.

Use NameCert obligation exhaustion,
\autoref{thm:authorized-generator-recursor-namecert-obligation-exhaustion}.
The carrier, classifier, stability, ledger, and non-escape obligations are
exhausted by these readiness rows. Therefore the route is total on the
displayed packet and cannot be completed by hidden generator state, host
recursion, private output exposure, or an external naming row.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor output route naming exhaustion]
\label{thm:authorized-generator-recursor-output-route-naming-exhaustion}
Every accepted output route naming surface for
$\AuthorizedGeneratorRecursorUp$ is exhausted by the same finite route
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The public name of $O$ must retain the authorization rows, generator-state
row, readiness and audit rows, displayed $\Cont$ route, $\Pkg$ source, and
local $\NameCert$ row already present in the packet.

Consequently the output route cannot be named through a hidden generator, a
host-recursive eliminator, an external continuation, an unaudited package
source, a missing readiness row, or a naming certificate outside the displayed
$\BHist$ carrier.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorCarrier\_output\_route\_naming\_exhaustion}
\begin{proof}
Project the root output consumer triad above. Any root consumer reaches $O$
only after the authorization, generator-state, audit, transport,
continuation, package, boundary, and local naming rows are displayed.

Apply readiness route totality. Since the readiness route is total only on
$I,E,M,B,D,O,A,H,C,P,G,N$, an output name cannot be certified by a partial
route missing authorization, audit, continuation, package, boundary, or local
NameCert support.

Finally use downstream readback exhaustion,
\autoref{thm:authorized-generator-recursor-downstream-readback-exhaustion}.
It removes detached generator routes, host recursion oracles, hidden
substitution channels, unlicensed output rows, and external naming witnesses
from downstream reads. Hence the displayed finite carrier exhausts the output
route naming surface.
\end{proof}

\begin{lemma}[AuthorizedGeneratorRecursor root output consumer downstream coverage]
\label{lem:authorized-generator-recursor-root-output-consumer-downstream-coverage}
For every accepted $\AuthorizedGeneratorRecursorUp$ root output packet with displayed route
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N),
$$
every accepted local consumer-facing use of the root output row $O$ is exhausted by the finite downstream surfaces already displayed in $R$. More precisely, the use must factor through the authorization and branch alternatives $I,E,M,B,D$, the output and audit ledger rows $O,A$, the transport, continuation, package, boundary, and local naming rows $H,C,P,G,N$, or the coverage row obtained by reading readiness and output-route naming through the same carrier.

Consequently a request for an unlisted branch, non-structural recursive call, hidden generator state, host recursion rule, private output channel, external continuation, unaudited package source, missing readiness row, or naming certificate outside the displayed $\BHist$ packet is not an accepted local consumer of the $\AuthorizedGeneratorRecursorUp$ root output.
\end{lemma}
\begin{proof}
Start with readiness route totality, \autoref{thm:authorized-generator-recursor-readiness-route-totality}. It states that the route from authorization to output is total exactly on
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
Thus a consumer-facing use of $O$ cannot begin from a free generator surface. Its admission side is forced through the accepted constructor signature, emitted eliminator, motive, branch package, and structural descent rows $I,E,M,B,D$, and its output side is forced to retain $O,A,H,C,P,G,N$ as route support in the same packet.

Next use output route naming exhaustion, \autoref{thm:authorized-generator-recursor-output-route-naming-exhaustion}. Any public name of the output route must keep the authorization rows, generator-state row, readiness and audit rows, displayed $\Cont$ route, $\Pkg$ source, and local $\NameCert$ row already present in $R$. Hence naming $O$ supplies no fourth downstream surface: it only records the same finite carrier as a named route and keeps the local consumer inside the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, and $\NameCert$ coordinates.

Combine these two constraints. If a proposed local consumer is accepted, readiness totality places the read on the displayed authorization-to-output route, while naming exhaustion keeps the public name of that read on the same carrier. The consumer therefore lands on one of the finite alternatives, ledger rows, or carrier-coverage rows listed in the statement.

It remains to exclude the apparent alternatives. An unlisted branch or non-structural recursive call would bypass $I,E,M,B,D$; hidden generator state or a host recursion rule would add a generator coordinate not present in the readiness route; a private output channel would detach $O$ from $A,H,C,P,G,N$; an external continuation or unaudited package source would replace $C$ or $P$; a missing readiness row would contradict route totality; and an outside naming certificate would contradict output route naming exhaustion. None of these requests has a coordinate in $R$, so each remains outside the accepted $\AuthorizedGeneratorRecursorUp$ packet.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootOutputConsumerDownstreamCoverage}
