\begin{theorem}[AuthorizedGeneratorRecursor root output route saturation]
\label{thm:authorized-generator-recursor-root-output-route-saturation}
Every public output route of an accepted $\AuthorizedGeneratorRecursorUp$ packet factors through the accepted signature row $I$, emitted eliminator row $E$, checked motive row $M$, branch package $B$, structural descent row $D$, output row $O$, audit row $A$, componentwise transport row $H$, displayed continuation row $C$, provenance row $P$, ground-compiler boundary row $G$, and local $\NameCert$ row $N$. Thus the output is public only as the saturated finite carrier route
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootOutputRouteSaturation}
\leanvariant{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursor\_root\_output\_route\_saturation}
\begin{proof}
Begin with the carrier and root output audit rows. \autoref{def:authorized-generator-recursor-carrier} displays the accepted signature, eliminator, motive, branch, descent, output, audit, transport, continuation, provenance, boundary, and naming rows, while \autoref{thm:authorized-generator-recursor-root-output-audit-totality} places every public read of $O$ behind the same packet.

Next attach boundary and compiler visibility. \autoref{thm:authorized-generator-recursor-root-boundary-nonescape} prevents the boundary row from exporting a hidden generator or host induction principle, and \autoref{thm:authorized-generator-recursor-ground-compiler-handoff} reads the ground-compiler boundary only through the accepted carrier.

Finally use consumer readiness. \autoref{thm:authorized-generator-recursor-root-namecert-consumer-readiness} packages the output route for downstream consumers without dropping branch, descent, audit, boundary, provenance, or local naming rows. Hence every public output route factors through the displayed saturated route.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor root boundary nonescape saturation]
\label{thm:authorized-generator-recursor-root-boundary-nonescape-saturation}
The saturated public output route of \autoref{thm:authorized-generator-recursor-root-output-route-saturation} exports no hidden generator, host induction principle, external axiom, unaudited dependency route, or off-packet substitution channel. Any consumer that reaches $O$ must keep the accepted signature, eliminator, motive, branch, descent, audit, transport, continuation, provenance, ground-compiler boundary, and local NameCert rows inside the same $\BHist$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootBoundaryNonescapeSaturation}
\begin{proof}
Project the saturated route
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The route already contains the only output, audit, ground-boundary, provenance, and local naming rows supplied by the accepted carrier.

Apply root boundary nonescape and the ground-compiler handoff. \autoref{thm:authorized-generator-recursor-root-boundary-nonescape} excludes hidden generator, host induction, external axiom, and unaudited dependency exports at the boundary, while \autoref{thm:authorized-generator-recursor-ground-compiler-handoff} keeps the compiler-facing read on the same finite packet.

It remains to rule out substitution escape. \autoref{thm:authorized-generator-recursor-root-namecert-consumer-readiness} and \autoref{thm:authorized-generator-recursor-root-output-audit-totality} force closed-normal and generator-audit consumers to retain the output audit route before using $O$. Since no off-packet substitution coordinate appears in the carrier, the saturated route has no channel through which such a substitution can be exported.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor root output-route strict obstruction]
\label{cor:authorized-generator-recursor-root-output-route-strict-obstruction}
Suppose a displayed failure, refusal, separation, or countermodel row is cited against a named converse or reuse route in the root output-route surface of an accepted $\AuthorizedGeneratorRecursorUp$ packet. Then that row is a strict local obstruction: it blocks only the named route whose consumer-facing read omits, replaces, detaches, or bypasses one of the displayed finite carrier coordinates
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
The route coordinates are $I,E,M,B,D,O,A$, the transport coordinate is $H$, the readback and provenance coordinates are $C,P$, and the boundary-certificate coordinates are $G,N$. The same displayed row cannot be reinterpreted as a global impossibility theorem for authorized generator recursors, a host theorem, hidden external validation of the failed route, or evidence for any unlisted consumer coordinate.
\end{corollary}
\begin{proof}
Start with output-route saturation. By \autoref{thm:authorized-generator-recursor-root-output-route-saturation}, every public output route of an accepted packet factors through the finite carrier
$$
I,E,M,B,D,O,A,H,C,P,G,N.
$$
Thus a consumer-facing read of $O$ has only the listed packet coordinates available. Its route side must pass through the accepted signature, emitted eliminator, checked motive, branch package, structural descent row, output row, and audit row $I,E,M,B,D,O,A$. Its transport side is the componentwise row $H$, its continuation and provenance readback is $C,P$, and its boundary and local certificate side is $G,N$.

Apply boundary nonescape saturation. \autoref{thm:authorized-generator-recursor-root-boundary-nonescape-saturation} says that the same saturated route exports no hidden generator, host induction principle, external axiom, unaudited dependency route, or off-packet substitution channel, and that any consumer reaching $O$ must keep the accepted signature, eliminator, motive, branch, descent, audit, transport, continuation, provenance, ground-compiler boundary, and local $\NameCert$ rows inside the same $\BHist$ packet. Therefore a negative row can act only at one of those displayed coordinates: it may deny the named converse or reuse route when that route tries to detach $O$ from its branch, descent, audit, transport, readback, boundary, or local naming support.

No stronger reading has a carrier. A global impossibility theorem would require a theorem coordinate not indexed by the named route and not confined to the accepted packet. A host theorem would require a host-facing induction or proof row outside $I,E,M,B,D,O,A,H,C,P,G,N$. Hidden external validation would require an additional validating certificate, dependency route, or substitution channel outside $A,H,C,P,G,N$. The two cited saturation theorems provide no such coordinate and explicitly keep every public read of $O$ on the displayed finite route. Hence the obstruction is strict and local: it blocks the named converse or reuse route at the displayed packet coordinate that the row denies, and it rejects every unlisted interpretation as outside the accepted $\AuthorizedGeneratorRecursorUp$ output-route surface.
\end{proof}
