\begin{theorem}[AuthorizedGeneratorRecursor root authorization downstream surface]
\label{thm:authorized-generator-recursor-root-authorization-downstream-surface}
Every downstream read of an accepted $\AuthorizedGeneratorRecursorUp$ root packet is authorized only through the finite carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N).
$$
The authorization row, output audit row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, host-boundary row, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ row must remain in the same $\BHist$ packet before a consumer may read the emitted recursor, branch package, structural descent, or output row.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootAuthorizationDownstreamSurface}
\begin{proof}
Begin with \autoref{thm:authorized-generator-recursor-carrier-admission}. It admits the root object only as the displayed finite carrier and leaves no separate authorization channel.

Apply \autoref{thm:authorized-generator-recursor-ledger-descent} and \autoref{thm:authorized-generator-recursor-consumer-nonescape}. Together they force downstream consumers to traverse the accepted signature, emitted recursor, motive, branch package, descent row, output row, audit row, transport, continuation, provenance, boundary, and local naming rows in one packet.

Finally use the root obligation surfaces in \autoref{def:authorized-generator-recursor-root-output-boundary-package} and \autoref{thm:authorized-generator-recursor-branch-output-closure-row}. The output audit and authorization ledgers therefore reach downstream consumers only through finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{proof}

\begin{theorem}[AuthorizedGeneratorRecursor Real stream handoff row]
\label{thm:authorized-generator-recursor-real-stream-handoff-row}
If an accepted $\AuthorizedGeneratorRecursorUp$ packet is used by an L10 $\RealUp$, $\StreamNameUp$, or $\RegSeqRatUp$ consumer, then the handoff is the same authorized route $I,E,M,B,D,O,A,H,C,P,G,N$. The Real, stream-name, and regular-rational data may enter only as finite source rows carried by the displayed $\BHist$, transported by $\hsame$, replayed by $\Cont$, packaged by $\Pkg$, and named by the local $\NameCert$ row; no selected Real limit, quotient stream equality, host evaluation, or detached generator state is exported.
\end{theorem}
\begin{proof}
Start with \autoref{thm:authorized-generator-recursor-real-stream-route}. It already places every L10 Real, stream-name, and regular-rational read on the displayed packet.

Use \autoref{thm:authorized-generator-recursor-closed-substitution-handoff} to keep the output row behind the same authorized carrier before any downstream consumer receives it.

Finally apply \autoref{thm:authorized-generator-recursor-root-authorization-downstream-surface}. The handoff row is therefore a finite authorized route with audit, transport, continuation, package, boundary, and local naming data, not a host-side stream or Real interface.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRealStreamHandoffRow}

\begin{theorem}[AuthorizedGeneratorRecursor closed substitution gate row]
\label{thm:authorized-generator-recursor-closed-substitution-gate-row}
The closed-substitution gate for an accepted $\AuthorizedGeneratorRecursorUp$ packet opens only after authorization, branch coverage, structural descent, output audit, Real/StreamName/RegSeqRat handoff, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, host-boundary exposure, and local $\NameCert$ certification are all present in the finite route $I,E,M,B,D,O,A,H,C,P,G,N$. It cannot be opened by unrestricted substitution, unchecked recursion, external proof generation, host equality, or a private audit channel.
\end{theorem}
\begin{proof}
First read the closed-substitution handoff of \autoref{thm:authorized-generator-recursor-closed-substitution-handoff}. It keeps closed-substitution consumers on the displayed route and excludes unrestricted substitution and external proof generation.

Next attach the L10 handoff row from \autoref{thm:authorized-generator-recursor-real-stream-handoff-row}. This supplies the Real, stream-name, and regular-rational source rows without leaving the finite carrier.

The gate is then closed by \autoref{thm:authorized-generator-recursor-root-authorization-downstream-surface} together with \autoref{thm:authorized-generator-recursor-substitution-membrane-lock}. Authorization, audit, transport, continuation, provenance, boundary, and naming all remain packet-local, so there is no coordinate for unchecked recursion, host equality, or a private audit channel.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorClosedSubstitutionGateRow}

\begin{lemma}[AuthorizedGeneratorRecursor root authorization bridge determinacy]
\label{lem:authorized-generator-recursor-root-authorization-bridge-determinacy}
Let an accepted $\AuthorizedGeneratorRecursorUp$ root packet be consumed through any downstream route, componentwise transport, readback, or L10 handoff. Then that consumer-facing bridge is determined by the finite carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N).
$$
The route part factors through $I,E,M,B,D,O,A$, the transport and readback part factors through $H,C,P$, and the boundary-certificate part factors through $G,N$. For an L10 $\RealUp$, $\StreamNameUp$, or $\RegSeqRatUp$ consumer, the source rows may enter only as packet-local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ data. No unlisted bridge coordinate is available for a selected Real limit, quotient stream equality, host evaluation, detached generator state, private audit row, off-packet readback, second transport, or second local naming certificate.
\end{lemma}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorRootAuthorizationBridgeDeterminacy}
\begin{proof}
Start with the root authorization downstream surface, \autoref{thm:authorized-generator-recursor-root-authorization-downstream-surface}. It authorizes every downstream read of an accepted root packet only through the finite carrier $R=(I,E,M,B,D,O,A,H,C,P,G,N)$. The same theorem requires the authorization row, output audit row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, host-boundary row, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ row to remain in one $\BHist$ packet before the emitted recursor, branch package, structural descent, or output row can be read. Thus any consumer-facing bridge already has its route side confined to $I,E,M,B,D,O,A$ and its audit-facing continuation confined to the displayed packet.

Apply the Real stream handoff row, \autoref{thm:authorized-generator-recursor-real-stream-handoff-row}. It says that every L10 $\RealUp$, $\StreamNameUp$, or $\RegSeqRatUp$ use of the accepted packet is the same authorized route $I,E,M,B,D,O,A,H,C,P,G,N$. Its source data enter only as finite rows carried by $\BHist$, transported by $\hsame$, replayed by $\Cont$, packaged by $\Pkg$, and named by the local $\NameCert$ row. Hence a Real, stream-name, or regular-rational reading is not an additional bridge coordinate; it is the same route with the source rows read through $H,C,P,G,N$.

The two cited surfaces cover all bridge forms named in the statement. A displayed route is covered by the carrier rows and authorization ledger of \autoref{thm:authorized-generator-recursor-root-authorization-downstream-surface}. A componentwise transport is exactly the retained $\hsame$ row $H$, a readback is exactly the displayed $\Cont$ replay and $\Pkg$ provenance rows $C,P$, and an L10 handoff is exactly the specialization supplied by \autoref{thm:authorized-generator-recursor-real-stream-handoff-row}. The host boundary and local naming side is exhausted by $G,N$ in the same packet.

It remains to exclude alternate bridges. Any selected Real limit, quotient stream equality, host evaluation, detached generator state, private audit row, off-packet readback, second transport, or second local naming certificate would have to be either a row of $R$ or an exported interface allowed by the L10 handoff. The carrier displays no such row, and \autoref{thm:authorized-generator-recursor-real-stream-handoff-row} explicitly keeps the L10 data inside finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, and local $\NameCert$ rows. Therefore every consumer-facing route, transport, readback, or handoff factors through the cited local rows, while unlisted bridge coordinates remain unavailable.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor root authorization determinacy]
\label{cor:authorized-generator-recursor-root-authorization-determinacy}
Let
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N)
$$
be the fixed finite carrier of an accepted $\AuthorizedGeneratorRecursorUp$ root packet. Once the authorization row, output audit row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, host-boundary row, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ row of $R$ are fixed, every accepted consumer-facing use of root authorization must use the same chapter-named finite route, packet-local normal-form reading, or exactness decision. The route side is fixed by $I,E,M,B,D,O,A$, the transport and readback side is fixed by $H,C,P$, and the boundary-certificate side is fixed by $G,N$. Hence two accepted consumers over the fixed rows cannot choose different authorization coordinates, a detached normal-form source, an off-packet readback, a private audit channel, a second transport, a second local naming certificate, or a duplicate classifier source.
\end{corollary}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorCarrier\_root\_authorization\_determinacy}
\begin{proof}
First apply \autoref{thm:authorized-generator-recursor-root-authorization-downstream-surface}. It authorizes every downstream read of an accepted root packet only through the displayed finite carrier $R=(I,E,M,B,D,O,A,H,C,P,G,N)$, and it requires the authorization row, output audit row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, host-boundary row, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ row to remain in the same $\BHist$ packet before a consumer may read the emitted recursor, branch package, structural descent, or output row. Thus an accepted consumer-facing route, normal-form reading, or exactness decision has no starting point outside those packet rows: it must read the recursor, descent, output, audit, transport, continuation, provenance, boundary, and local certificate as one finite surface.

Now use \autoref{lem:authorized-generator-recursor-root-authorization-bridge-determinacy}. That lemma separates the fixed packet into the relevant roles. The route part factors through $I,E,M,B,D,O,A$, the transport and readback part factors through $H,C,P$, and the boundary-certificate part factors through $G,N$. It also covers the L10 $\RealUp$, $\StreamNameUp$, and $\RegSeqRatUp$ handoff by forcing those source rows to enter only as packet-local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, boundary, and local $\NameCert_{\AuthorizedGeneratorRecursorUp}$ data. Therefore a consumer-facing normal-form reading or exactness decision is not an independent classifier; it is the same fixed route read through the displayed transport, readback, provenance, boundary, and certificate rows.

It remains to rule out competing choices. Any alternate authorization coordinate, detached normal-form source, off-packet readback, private audit channel, second transport, second local naming certificate, or duplicate classifier source would have to supply either an additional row of $R$ or an exported consumer interface not mediated by the rows named above. The downstream surface supplies no such row, and the bridge-determinacy lemma explicitly excludes unlisted bridge coordinates for selected Real limits, quotient stream equality, host evaluation, detached generator state, private audit rows, off-packet readbacks, second transports, and second local naming certificates. A duplicate classifier source would enter only through one of those excluded interfaces or through a carrier coordinate outside $R$. Since the rows of $R$ are fixed and every accepted consumer use factors through them, all accepted consumers determine the same finite route and the same packet-local normal-form or exactness decision named by the chapter.
\end{proof}
