\begin{theorem}[AuthorizedGeneratorRecursor terminal consumer readiness]
\label{thm:authorized-generator-recursor-terminal-consumer-readiness}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet with displayed carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N),
$$
every terminal normalization or closed-substitution consumer may read the recursor output only after the finite packet of \autoref{def:authorized-generator-recursor-carrier}, the route authorization of \autoref{thm:authorized-generator-recursor-route-authorization}, the output ledger exactness of \autoref{thm:authorized-generator-recursor-output-ledger-exactness}, and the substitution handoff nonescape of \autoref{thm:authorized-generator-recursor-substitution-handoff-nonescape} have all been displayed. Such a consumer receives $O$ as a row of $R$, with branch, descent, audit, boundary, and local naming data still attached, and not as a detached recursor theorem.
\end{theorem}
\begin{proof}
Project the finite $\BHist$ packet from \autoref{def:authorized-generator-recursor-carrier}. The rows $I,E,M,B,D,O,A,H,C,P,G,N$ are the only displayed coordinates, so the terminal consumer starts from the packet rather than from an ambient generator principle.

Apply \autoref{thm:authorized-generator-recursor-route-authorization} to route the public output through accepted signature, emitted recursor, motive, branch package, structural descent, audit, transport, continuation, provenance, boundary, and local $\NameCert$ rows. Then apply \autoref{thm:authorized-generator-recursor-output-ledger-exactness} to keep $O$ in the same ledger.

Finally use \autoref{thm:authorized-generator-recursor-substitution-handoff-nonescape}. The handoff to the sibling boundaries of \autoref{ch:concrete-instances-closedtermsubstitutionboundary-namecert} and \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert} is therefore a displayed BEDC row read, not a hidden induction source, unchecked generator, detached normalization proof, or external proof-producing channel.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorTerminalConsumerReadiness}

\begin{theorem}[AuthorizedGeneratorRecursor boundary factorization]
\label{thm:authorized-generator-recursor-boundary-factorization}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet with carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N),
$$
any public route from the recursor output $O$ into a $\ClosedTermSubstitutionBoundaryUp$ consumer or a $\MetaCICNormalizationFrontierUp$ consumer factors through the displayed rows $B,D,A,H,C,P,G,N$ after $I,E,M$ have admitted the generator surface. In particular, the boundary route is the carrier route certified by \autoref{def:authorized-generator-recursor-carrier}, \autoref{thm:authorized-generator-recursor-route-authorization}, \autoref{thm:authorized-generator-recursor-output-ledger-exactness}, and \autoref{thm:authorized-generator-recursor-substitution-handoff-nonescape}.
\end{theorem}
\begin{proof}
Begin with the route authorization theorem. It fixes the public recursor route at the rows of $R$, so a consumer path to $O$ must pass through the branch row $B$, the descent row $D$, and the audit row $A$ before any boundary read is available.

Use output ledger exactness to attach $H,C,P,G,N$ to the same route. The componentwise transport, continuation replay, package provenance, boundary row, and local certificate are not auxiliary witnesses outside the packet; they are the boundary-facing coordinates of the packet itself.

The closed-term and normalization-frontier sibling chapters can therefore consume only this factored carrier route. A route that skipped $B,D,A,H,C,P,G,N$ would need a boundary coordinate outside $R$, but \autoref{def:authorized-generator-recursor-carrier} displays no such coordinate.
\end{proof}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorBoundaryFactorization}

\begin{theorem}[AuthorizedGeneratorRecursor normalization consumer nonescape]
\label{thm:authorized-generator-recursor-normalization-consumer-nonescape}
For every accepted $\AuthorizedGeneratorRecursorUp$ packet with carrier
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N),
$$
a $\MetaCICNormalizationFrontierUp$ consumer receives the recursor-generated output only as the authorized finite route already consumable by $\ClosedTermSubstitutionBoundaryUp$. The normalization consumer cannot reinterpret $O$ as hidden induction, an unchecked generator, a detached normalization theorem, a subject-reduction source, a host equality principle, or an external proof-producing source.
\end{theorem}
\leanchecked{BEDC.Derived.AuthorizedGeneratorRecursorUp.AuthorizedGeneratorRecursorNormalizationConsumerNonescape}
\begin{proof}
First read the route through \autoref{thm:authorized-generator-recursor-terminal-consumer-readiness}. Terminal readiness keeps the normalization consumer behind the same displayed finite packet as the closed-substitution consumer.

Next apply \autoref{thm:authorized-generator-recursor-boundary-factorization}. The route into \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert} must factor through the branch, descent, audit, transport, continuation, provenance, boundary, and local naming rows already exposed to \autoref{ch:concrete-instances-closedtermsubstitutionboundary-namecert}.

It remains to exclude non-displayed sources. Since \autoref{thm:authorized-generator-recursor-substitution-handoff-nonescape} exports no hidden recursor, unrestricted substitution calculus, proof generator, external axiom channel, host equality, or off-packet certificate, the normalization consumer has no coordinate from which to acquire hidden induction, an unchecked generator, detached normalization, subject reduction, or an external proof-producing source.
\end{proof}

\begin{corollary}[AuthorizedGeneratorRecursor terminal consumer strict obstruction]
\label{cor:authorized-generator-recursor-terminal-consumer-strict-obstruction}
Let
$$
R=(I,E,M,B,D,O,A,H,C,P,G,N)
$$
be an accepted $\AuthorizedGeneratorRecursorUp$ packet. Suppose a displayed failure, refusal, separation, or countermodel row is cited against a named converse, reuse, separation, or readback route for the terminal consumer surface of $R$. Then the cited row is a strict local obstruction. It blocks only the named route whose consumer-facing use tries to read the terminal output $O$, normalization readiness, or closed-substitution handoff away from the displayed packet rows $I,E,M,B,D,O,A,H,C,P,G,N$. Every admitted consumer-facing use factors through the packet carrier, route authorization, output-ledger exactness, substitution handoff, boundary factorization, and normalization-consumer nonescape rows already displayed for $R$. The same cited row cannot be reinterpreted as a global impossibility theorem for recursors, a host theorem about normalization or substitution, hidden external validation of the failed route, or an obstruction to any consumer route that still factors through the displayed rows of $R$.
\end{corollary}
\begin{proof}
Start with terminal consumer readiness, \autoref{thm:authorized-generator-recursor-terminal-consumer-readiness}. A terminal normalization or closed-substitution consumer may read the recursor output only after the finite carrier of \autoref{def:authorized-generator-recursor-carrier}, route authorization, output ledger exactness, and substitution handoff nonescape have all been displayed. Thus the consumer receives $O$ as a row of $R$, with branch, descent, audit, boundary, and local naming data still attached, and not as a detached recursor theorem.

Apply normalization consumer nonescape, \autoref{thm:authorized-generator-recursor-normalization-consumer-nonescape}. It says that a $\MetaCICNormalizationFrontierUp$ consumer receives the recursor-generated output only as the authorized finite route already consumable by $\ClosedTermSubstitutionBoundaryUp$. The listed failed readings are hidden induction, an unchecked generator, a detached normalization theorem, a subject-reduction source, a host equality principle, and an external proof-producing source.

The required factorization is therefore finite and rowwise. By readiness, the consumer-facing read begins at the displayed carrier $R$ and cannot start from an ambient generator principle. By boundary factorization, the route from $O$ into the closed-substitution or normalization-frontier consumer passes through $B,D,A,H,C,P,G,N$ after $I,E,M$ have admitted the generator surface. By normalization nonescape, no further coordinate is exported for hidden induction, unchecked generation, detached normalization, subject reduction, host equality, or external proof production.

Now take the cited failure, refusal, separation, or countermodel row. If it is used against the named converse, reuse, separation, or readback route, the preceding paragraph forces that use to land at the exact displayed coordinate where the named route tries to omit, replace, detach, or bypass one of the packet rows. That is the strict local obstruction.

Any stronger reading would require data not supplied by the terminal consumer surface. A global impossibility theorem would require a recursor-wide theorem row outside the accepted packet. A host theorem about normalization or substitution would require host normalization, host equality, or host substitution data outside $R$. Hidden external validation would require an external certificate or proof-producing channel not carried by $P$, $G$, or $N$. These are exactly the readings excluded by terminal readiness and normalization consumer nonescape. Hence the obstruction blocks only the named local route and does not obstruct any consumer route that continues to factor through the displayed packet rows of $R$.
\end{proof}
