\begin{theorem}[Closed-term substitution boundary closed-source budget surface]
\label{thm:closed-term-substitution-boundary-closed-source-budget-surface}
Every accepted $\ClosedTermSubstitutionBoundaryUp$ packet exposes the finite rows
$$
T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,A,H,C,P,N.
$$
The source closedness row $C_{\mathsf{src}}$ and the value closedness row $C_{\mathsf{val}}$ are read before any closed shift budget $Q$ or closed substitution budget $R$ is consumed. Thus the operation budget is a closed-source and closed-value surface over the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, not a host substitution semantics or hidden evaluator route.
\end{theorem}
\begin{proof}
Project the accepted carrier from \autoref{def:closed-term-substitution-boundary-carrier} and the classifier from \autoref{def:closed-term-substitution-boundary-classifier}. The displayed packet already separates the term row $T$, value row $V$, depth row $d$, source closedness row $C_{\mathsf{src}}$, value closedness row $C_{\mathsf{val}}$, shift row $Q$, substitution row $R$, ledger row $L$, audit row $A$, transport row $H$, route row $C$, provenance row $P$, and local naming row $N$.

Apply \autoref{thm:closed-term-substitution-boundary-namecert-obligations}. Its carrier exposure and classifier obligations force every public read to begin from the same finite packet, so no consumer can acquire $Q$ or $R$ from an unlisted operation source.

Finally use \autoref{thm:closed-term-substitution-boundary-shift-substitution-ledger-lock}. The ledger lock places $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$ before the shift and substitution rows in the public operation budget, and \autoref{thm:closed-term-substitution-boundary-ledger-non-escape} rules out a hidden source for closedness or operation state.
\end{proof}
\leanchecked{BEDC.Derived.ClosedtermsubstitutionboundaryUp.ClosedTermSubstitutionBoundaryClosedSourceBudgetSurface}

\begin{theorem}[Closed-term substitution boundary substitution budget totality]
\label{thm:closed-term-substitution-boundary-substitution-budget-totality}
Every substitution consumer of an accepted $\ClosedTermSubstitutionBoundaryUp$ packet factors through source closedness, value closedness, the closed shift row, the closed substitution row, the finite ledger, the audit row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ row. Equivalently, the consumer route is exhausted by
$$
C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,A,H,C,P,N
$$
inside the carrier over $T,V,d$, and it receives no subject reduction theorem, host syntax quotient, hidden compiler state, or host substitution semantics.
\end{theorem}
\begin{proof}
Start with the closed-source budget surface of \autoref{thm:closed-term-substitution-boundary-closed-source-budget-surface}. It provides the entry condition: $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$ are exposed before the operation rows $Q$ and $R$ can be spent.

Next apply \autoref{thm:closed-term-substitution-boundary-consumer-boundary}. It forces downstream consumers to read the closed shift and substitution boundary through the displayed carrier, transports, routes, provenance, and local naming row.

The audit and ledger rows close the remaining path. By \autoref{thm:closed-term-substitution-boundary-ledger-non-escape} and \autoref{thm:closed-term-substitution-boundary-shift-substitution-ledger-lock}, the finite ledger and audit row exhaust the operation budget; by \autoref{thm:closed-term-substitution-boundary-namecert-export-totality}, the exported surface is exactly $T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,A,H,C,P,N$.
\end{proof}

\begin{theorem}[Closed-term substitution boundary consumer audit triad]
\label{thm:closed-term-substitution-boundary-consumer-audit-triad}
For $\ClosedTermSubstitutionBoundaryUp$, the closed-source budget surface of \autoref{thm:closed-term-substitution-boundary-closed-source-budget-surface}, the substitution budget totality row of \autoref{thm:closed-term-substitution-boundary-substitution-budget-totality}, and the non-escape audit rows of the chapter assemble the consumer-facing triad. The triad says that every substitution-facing consumer first reads closedness, then spends only the displayed operation boundary, and finally remains audit-visible through $L,A,H,C,P,N$.
\end{theorem}
\begin{proof}
First take closedness as the entry surface. The closed-source budget theorem exposes $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$ before any operation row is consumed.

Second take operation totality as the consumer boundary. The substitution budget theorem factors every consumer through $Q,R,L,A,H,C,P,N$ over the same $T,V,d$ carrier rows.

Third attach the audit witness. Apply \autoref{thm:closed-term-substitution-boundary-audit-route-coverage}, \autoref{thm:closed-term-substitution-boundary-audit-boundary-factorization}, and \autoref{thm:closed-term-substitution-boundary-root-audit-totality}. These rows keep the consumer inside the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet and prevent escape to host substitution semantics, hidden compiler state, or an untracked audit route.
\end{proof}
