\begin{theorem}[Closed-term substitution boundary root value visibility]
\label{thm:closed-term-substitution-boundary-root-value-visibility}
Every root consumer of an accepted $\ClosedTermSubstitutionBoundaryUp$ packet must expose
$$
T,V,d,C_{\mathsf{src}},C_{\mathsf{val}}
$$
before either the closed-shift row $Q$ or the substitute-closed row $R$ is used. The exposed rows are the displayed source term, substituting value, inspected depth, source closedness witness, and value closedness witness of the same finite $\BHist$ packet.
\end{theorem}
\begin{proof}
Read the root consumer through the carrier and local certificate rows of \autoref{def:closed-term-substitution-boundary-carrier} and \autoref{thm:closed-term-substitution-boundary-namecert-obligations}. They make $T,V,d,C_{\mathsf{src}},C_{\mathsf{val}}$ packet coordinates rather than hidden preconditions.

Use source and value admission from \autoref{thm:closed-term-substitution-boundary-source-closedness-admission} and \autoref{thm:closed-term-substitution-boundary-value-closedness-admission}. These rows place the closedness witnesses on the visible route before the shift or substitution boundary can be read.

Finally apply \autoref{thm:closed-term-substitution-boundary-ledger-non-escape} and \autoref{thm:closed-term-substitution-boundary-consumer-boundary}. The ledger and consumer boundary prevent a root consumer from obtaining $Q$ or $R$ from host substitution semantics, a hidden evaluator, or an ambient compiler theorem.
\end{proof}

\begin{theorem}[Closed-term substitution boundary root operation dependency]
\label{thm:closed-term-substitution-boundary-root-operation-dependency}
In every root read of an accepted $\ClosedTermSubstitutionBoundaryUp$ packet, the rows $Q$ and $R$ are dependent operation rows over the displayed witnesses $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$. They may be consumed only as the packet's certified closed-shift and substitute-closed boundary rows, not as host shift semantics, host substitution semantics, subject reduction, or an evaluator equation.
\end{theorem}
\begin{proof}
Start from the operation inventory of \autoref{thm:closed-term-substitution-boundary-operation-row-determinacy}. It identifies $Q$ and $R$ as the only operation rows of the finite packet.

Use \autoref{thm:closed-term-substitution-boundary-closedness-ledger-coverage} and \autoref{thm:closed-term-substitution-boundary-shift-substitution-ledger-lock}. These rows force the operation read through the displayed closedness witnesses and ledger before any downstream citation can mention $Q$ or $R$.

The exclusion of host semantics follows from \autoref{thm:closed-term-substitution-boundary-ledger-route-separation} and \autoref{thm:closed-term-substitution-boundary-audit-boundary-factorization}. Hence the operation dependency is a packet dependency over the displayed closedness witnesses, not an imported shift or substitution semantics.
\end{proof}

\begin{theorem}[Closed-term substitution boundary root consumer exhaustion]
\label{thm:closed-term-substitution-boundary-root-consumer-exhaustion}
Downstream self-compilation and normalization consumers exhaust their closed-substitution read through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet of $\ClosedTermSubstitutionBoundaryUp$. No remaining consumer route may add an unregistered free-variable coordinate, host equality, hidden evaluator, hidden compiler state, subject-reduction theorem, or host substitution semantics.
\end{theorem}
\begin{proof}
First package the root-visible rows by \autoref{thm:closed-term-substitution-boundary-root-value-visibility} and \autoref{thm:closed-term-substitution-boundary-root-operation-dependency}. Together they expose the source, value, depth, closedness, and operation surface before any root read continues.

Next use the existing consumer rows. The self-compilation route of \autoref{thm:closed-term-substitution-boundary-consumer-factorization} and the normalization-frontier handoff of \autoref{thm:closed-term-substitution-boundary-normalization-frontier-handoff} both factor through the same finite boundary packet.

Finally apply \autoref{thm:closed-term-substitution-boundary-namecert-export-totality} and \autoref{thm:closed-term-substitution-boundary-audit-boundary-factorization}. The displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows therefore exhaust the downstream read, with no route to hidden substitution or compiler data.
\end{proof}

\begin{theorem}[Closed-term substitution boundary root value downstream coverage]
\label{thm:closed-term-substitution-boundary-root-value-downstream-coverage}
Every accepted local consumer of the root value row $V$ in a $\ClosedTermSubstitutionBoundaryUp$ packet is exhausted by the displayed finite coverage alternatives
$$
(T,V,d,C_{\mathsf{src}},C_{\mathsf{val}}),\qquad (Q,R),\qquad (\BHist,\hsame,\Cont,\Pkg,\NameCert).
$$
The first alternative covers the visible value and closedness read, the second covers the certified closed-shift and substitute-closed operation rows, and the third covers downstream self-compilation or normalization consumption through the packet ledger. No excluded route through an unregistered free-variable coordinate, host equality, hidden evaluator, hidden compiler state, subject-reduction theorem, or host substitution semantics belongs to the accepted BEDC packet.
\end{theorem}
\begin{proof}
Let an accepted local consumer ask for the root value row $V$. By \autoref{thm:closed-term-substitution-boundary-root-value-visibility}, the consumer must first expose
$$
T,V,d,C_{\mathsf{src}},C_{\mathsf{val}}
$$
inside the same finite $\BHist$ packet before either operation row can be used. Any consumer whose read stops at the value, inspected depth, or closedness witnesses is therefore covered by the first displayed alternative.

If the consumer continues to an operation read, \autoref{thm:closed-term-substitution-boundary-root-operation-dependency} identifies $Q$ and $R$ as dependent operation rows over the displayed witnesses $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$. Thus the operation continuation is covered by the certified closed-shift and substitute-closed rows, not by a host shift rule, host substitution rule, evaluator equation, or subject-reduction theorem.

It remains to cover consumers that pass the operation rows downstream. This is exactly the exhaustion statement of \autoref{thm:closed-term-substitution-boundary-root-consumer-exhaustion}: downstream self-compilation and normalization consumers factor through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet, with no route to an unregistered free-variable coordinate, host equality, hidden evaluator, hidden compiler state, subject reduction, or host substitution semantics. The three displayed alternatives therefore cover every accepted local root-value consumer, and all excluded alternatives remain outside the accepted BEDC packet.
\end{proof}
