\begin{theorem}[Closed-term substitution boundary source triad]
\label{thm:closed-term-substitution-boundary-source-triad}
For every accepted $\ClosedTermSubstitutionBoundaryUp$ packet
$$
S=(T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,A,H,C,P,N),
$$
the displayed rows $T,V,d,C_{\mathsf{src}},C_{\mathsf{val}}$ form the complete source, value, and depth admission triad before any shift row $Q$ or substitution row $R$ is consumed. The triad is read through the carrier, classifier, local $\NameCert$ obligations, and closedness ledger, and it exposes no operation row before the source and value closedness witnesses are fixed.
\end{theorem}
\leanchecked{BEDC.Derived.ClosedtermsubstitutionboundaryUp.ClosedTermSubstitutionBoundarySourceTriad}
\begin{proof}
Read the carrier of \autoref{def:closed-term-substitution-boundary-carrier}. It displays the source term row $T$, value row $V$, inspected depth row $d$, source closedness row $C_{\mathsf{src}}$, value closedness row $C_{\mathsf{val}}$, operation rows, ledger, audit row, transports, routes, provenance, and local name as one finite packet.

Use the classifier and local $\NameCert$ obligations of \autoref{def:closed-term-substitution-boundary-classifier} and \autoref{thm:closed-term-substitution-boundary-namecert-obligations}. They make the source/value closedness rows the admission surface for closed shift and closed substitution.

Finally apply source/value closedness admission through \autoref{thm:closed-term-substitution-boundary-closedness-ledger-coverage}. The ledger records the closedness reads before $Q$ or $R$ is consumed, so the source, value, and depth rows form the complete admission triad for the operation boundary.
\end{proof}

\begin{theorem}[Closed-term substitution boundary operation route]
\label{thm:closed-term-substitution-boundary-operation-route}
Every accepted operation read of a $\ClosedTermSubstitutionBoundaryUp$ packet factors through
$$
Q,R,L,H,C,P,N
$$
after the closedness witnesses $C_{\mathsf{src}}$ and $C_{\mathsf{val}}$ have been displayed. The route is the finite operation surface of the packet, not host substitution semantics, unchecked compiler state, subject reduction, or a hidden evaluator.
\end{theorem}
\begin{proof}
Start from the source triad of \autoref{thm:closed-term-substitution-boundary-source-triad}. It supplies the displayed term rows, depth row, and closedness witnesses that must be fixed before any operation read.

Apply the substitution-row exactness and shift-substitution ledger lock theorems, \autoref{thm:closed-term-substitution-boundary-substitution-row-exactness} and \autoref{thm:closed-term-substitution-boundary-shift-substitution-ledger-lock}. These results force reads of $Q$ and $R$ through the closedness ledger $L$ and the audit-visible packet boundary.

The remaining operation route is componentwise transport, continuation consumption, package provenance, and local naming. Thus $H,C,P,N$ are the only admissible transport and consumer rows after $Q,R,L$, and no host substitution semantics, unchecked compiler state, subject reduction, or hidden evaluator is exported.
\end{proof}

\begin{theorem}[Closed-term substitution boundary audit non-escape]
\label{thm:closed-term-substitution-boundary-audit-nonescape}
The audit row $A$ of an accepted $\ClosedTermSubstitutionBoundaryUp$ packet excludes free-variable leaks, host equality, unchecked compiler state, subject reduction, and host substitution semantics from the source/value/depth admission surface and from the operation route
$$
T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,H,C,P,N.
$$
Every audit-visible consumer must replay the displayed finite packet rather than importing an external substitution theorem or compiler fact.
\end{theorem}
\begin{proof}
Project the audit row from the carrier and route it through the classifier. The rows $A,H,C,P,N$ belong to the same finite packet as the source triad and operation rows, so audit visibility cannot be detached from the displayed boundary.

Apply the local $\NameCert$ obligations and ledger non-escape theorem, \autoref{thm:closed-term-substitution-boundary-namecert-obligations} and \autoref{thm:closed-term-substitution-boundary-ledger-non-escape}. They rule out unregistered free variables, hidden host equality, unchecked compiler state, ambient subject reduction, and host substitution semantics.

Finally combine the source triad with the operation route from \autoref{thm:closed-term-substitution-boundary-source-triad} and \autoref{thm:closed-term-substitution-boundary-operation-route}. Every operation read already passes through the closedness witnesses, ledger, transports, continuation route, provenance, and local name, so the audit row covers the complete finite route and no external substitution or compiler fact is available.
\end{proof}

\begin{corollary}[Closed-term substitution boundary source triad strict obstruction]
\label{cor:closed-term-substitution-boundary-source-triad-strict-obstruction}
Let
$$
S=(T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,A,H,C,P,N)
$$
be an accepted $\ClosedTermSubstitutionBoundaryUp$ packet, and let $O$ be a displayed failure, refusal, separation, or countermodel row attached in the root-unblock source surface to a named consumer-facing converse or reuse attempt. If the named attempt asks to read the closed-term substitution boundary through the source, value, and depth admission triad, then $O$ is a strict local obstruction: it blocks only that named attempt at one of the displayed rows
$$
T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,A,H,C,P,N
$$
or at the corresponding refusal to supply an unlisted coordinate. It does not imply a global impossibility statement, a host theorem, hidden external validation, host substitution semantics, subject reduction, unchecked compiler state, host equality, or a free-variable leak outside the accepted packet.
\end{corollary}
\begin{proof}
By \autoref{thm:closed-term-substitution-boundary-source-triad}, the rows $T,V,d,C_{\mathsf{src}},C_{\mathsf{val}}$ form the complete admission triad before any shift row $Q$ or substitution row $R$ is consumed. Thus a consumer-facing converse or reuse attempt has no access to an operation row until the source term, value term, inspected depth, and both closedness witnesses have already been fixed.

By \autoref{thm:closed-term-substitution-boundary-audit-nonescape}, every audit-visible consumer must replay the finite packet route
$$
T,V,d,C_{\mathsf{src}},C_{\mathsf{val}},Q,R,L,H,C,P,N,
$$
with the audit row $A$ excluding free-variable leaks, host equality, unchecked compiler state, subject reduction, and host substitution semantics from both the admission surface and the operation route. Hence any consumer-facing use of $O$ either factors through one of the displayed packet rows or asks for a coordinate that the packet does not export.

If the named attempt factors through a displayed row, then the displayed row $O$ can obstruct only that requested converse or reuse read: the packet still exposes the remaining listed rows only through the same finite route. If the named attempt asks for an unlisted coordinate, then the obstruction is the local refusal of that coordinate, since the source triad and audit non-escape surface provide no projection to a host theorem, hidden external validation, global impossibility claim, unchecked compiler state, subject reduction theorem, host substitution semantics, host equality, or free-variable leak. Therefore $O$ has exactly strict local force against the named converse or reuse route and cannot be reinterpreted as any stronger external or global claim.
\end{proof}
