\chapter{A Concrete Naming Certificate for $\CompletelyRegularSpaceUp$}
\label{ch:concrete-instances-completely-regular-space-namecert}
\origin{human}

Following Kelley and Engelking, the $\CompletelyRegularSpaceUp$ packet records the classical point-versus-closed-set real-valued separation surface as finite BEDC naming data. It sits between the topology source of \autoref{ch:concrete-instances-topology-namecert}, the point-versus-closed-set neighbourhood route of \autoref{ch:concrete-instances-regular-topological-space-namecert}, the real-number carrier of \autoref{ch:concrete-instances-real-namecert}, and the Urysohn-style function consumer of \autoref{ch:concrete-instances-urysohn-lemma-namecert}. The packet names only the displayed continuous real-valued separator route; it does not import host powersets, arbitrary function spaces, selected complements, normality, metrization, or ambient completeness.

\begin{definition}[Completely regular space carrier]
\label{def:completely-regular-space-carrier}
A $\CompletelyRegularSpaceUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,R,C,F,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\TopologyUp$ source row, carrying the open-index classifier, displayed neighbourhood reads, and closed-row vocabulary available to the packet.
\item $R$ is the $\RegularTopologicalSpaceUp$ source row, tying the point-versus-closed-set request to the regular neighbourhood-separation route already named over $T$.
\item $C$ is the closed-set and point request row, displaying the inspected point, the closed row avoided by that point, and the membership and nonmembership reads over the same topology source.
\item $F$ is the $\RealUp$-valued $\ContinuousMapUp$ separator row. It records a displayed map row, a zero read on the closed-set row, a unit read at the point, and a continuity replay over $T$.
\item $H$ records componentwise $\hsame$ transport for $T,R,C,F,K,P,N$ and for the displayed real-valued separation reads.
\item $K$ records displayed $\Cont$ replay from a completely-regular request through the topology source, regular-space source, request row, separator row, transport, provenance, and local naming.
\item $P$ is the $\Pkg$ provenance over $\CompletelyRegularSpaceUp$, $\TopologyUp$, $\RegularTopologicalSpaceUp$, $\RealUp$, $\ContinuousMapUp$, $\UrysohnLemmaUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompletelyRegularSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,R,C,F,H,K,P,N$. It has no coordinate for a host powerset, an external function space, a chosen complement, normal-space Urysohn data, metrization, host real completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Completely regular space NameCert obligations]
\label{thm:completely-regular-space-namecert-obligations}
For every accepted $\CompletelyRegularSpaceUp$ carrier
$$
Q=(T,R,C,F,H,K,P,N),
$$
the local $\NameCert_{\CompletelyRegularSpaceUp}$ surface consists exactly of topology-source admission through $T$; regular-space source admission through $R$; closed-set and point request admission through $C$; $\RealUp$-valued $\ContinuousMapUp$ separator exactness through $F$; componentwise $\hsame$ transport through $H$; displayed $\Cont$ replay through $K$; provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:completely-regular-space-carrier}. The accepted packet displays the topology source, the regular-space source, the point-versus-closed-set request, the real-valued separator row, and the structural rows.

The request row is read before any function row. The row $C$ binds the inspected point and the closed row to the same $\TopologyUp$ source, while $R$ supplies only the regular neighbourhood route named by \autoref{ch:concrete-instances-regular-topological-space-namecert}.

The separator obligation is exactly $F$. It records the $\RealUp$ codomain, the $\ContinuousMapUp$ continuity replay, the zero read on the closed row, and the unit read at the displayed point, so the certificate has no coordinate for a host function space or a selected complement.

Finally $H,K,P,N$ transport, replay, package, and name the same finite route. Since no further coordinate is present, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Real-valued separation window]
\label{thm:completely-regular-space-real-valued-separation-window}
Every real-valued separation read exported by an accepted $\CompletelyRegularSpaceUp$ packet must pass through $\TopologyUp$, $\RegularTopologicalSpaceUp$, $\RealUp$, and $\ContinuousMapUp$ before any $\UrysohnLemmaUp$, $\UrysohnMetrizationUp$, or metrization consumer reads it. The consumer receives only the finite row sequence $T,R,C,F,H,K,P,N$ and cannot read a host powerset, a selected complement, an ambient function-space object, host real completeness, or an untracked Urysohn separator from the packet.
\end{theorem}
\begin{proof}
Begin with the source rows. The topology row $T$ supplies the displayed open and closed vocabulary, and the regular-space row $R$ ties the request to the point-versus-closed-set route already named over that topology.

The closed-set and point request row $C$ is the only entry point for the separation problem. It must be visible before the real-valued separator is read, so no later consumer can replace the request by an ambient complement or by a host powerset argument.

The separator row $F$ then displays both codomain and continuity: it is a $\RealUp$-valued $\ContinuousMapUp$ row with the required zero and unit reads. The transport row $H$ and replay row $K$ preserve the same sequence before provenance and naming are inspected.

Thus an Urysohn-style or metrization-facing consumer reads the named finite route through $\TopologyUp$, $\RegularTopologicalSpaceUp$, $\RealUp$, and $\ContinuousMapUp$. It receives no stronger normality theorem, no selected separating function outside $F$, and no ambient completeness principle from the completely regular packet.
\end{proof}

\falsifiablePrediction{Every accepted $\CompletelyRegularSpaceUp$ read exposes a $\TopologyUp$ source row, a $\RegularTopologicalSpaceUp$ source row, a closed-set and point request row, a $\RealUp$-valued $\ContinuousMapUp$ separator row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{topology, regular-topological-space, real, continuous-map, urysohn-lemma: $\CompletelyRegularSpaceUp$ is not bijective to any listed sibling because it binds real-valued point-versus-closed-set separation as a finite NameCert route between topology and Urysohn-style consumers.}

\closureat{CompletelyRegularSpaceUp}{seedStr}

\begin{closurestatus}{\CompletelyRegularSpaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:completely-regular-space-carrier}, \autoref{thm:completely-regular-space-namecert-obligations}, and \autoref{thm:completely-regular-space-real-valued-separation-window} seed the finite real-valued point-versus-closed-set separation route over topology, regular-space, real, continuous-map, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close normality, Urysohn function construction, metrization, host powersets, arbitrary function spaces, selected complements, host real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, request-row exactness, real-valued continuous separator exactness, transport, replay, provenance, and local naming for BEDC.Derived.CompletelyRegularSpaceUp.}
  \constructivestory{A $\CompletelyRegularSpaceUp$ packet is generated from a Topology source row, a RegularTopologicalSpace source row, a closed-set and point request row, a Real-valued ContinuousMap separator row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
