\section{Public closure record}
\label{sec:abgroup-public-closure-record}

\begin{theorem}[AbGroup public operation surface]
\label{thm:abgroup-public-operation-surface}
The public $\AbGroupUp$ surface consists of the singleton empty-history carrier,
classifier, and operation tuple from
\autoref{def:singleton-empty-history-abgroup-instance}; the checked singleton
laws from \autoref{thm:singleton-empty-history-abgroup-laws}; the forgetful
group reduct from \autoref{prop:abgroup-forgets-group-certificate}; the
abelian normalizer-orbit collapse package from
\autoref{thm:abgroup-total-centralizer-normalizer-orbit-collapse}; and the
middle-four and double-cancellation normal-form rows represented by
\autoref{thm:abgroup-middle-four-interchange},
\autoref{thm:abgroup-middle-four-double-cancel}, and
\autoref{thm:abgroup-middle-four-transported-double-cancel}. No host equality,
quotient carrier, subgroup primitive, or module equivalence is part of this
surface.
\end{theorem}
\begin{proof}
The carrier, classifier, multiplication, identity, inverse, and commutativity
data are the singleton empty-history data of
\autoref{def:singleton-empty-history-abgroup-instance}. The checked laws in
\autoref{thm:singleton-empty-history-abgroup-laws} make those operations the
displayed $\AbGroupUp$ singleton package.

The group-facing part is obtained by applying
\autoref{prop:abgroup-forgets-group-certificate}; it keeps the same carrier,
classifier, multiplication, identity, and inverse while only dropping the
commutativity field as an extra obligation. The abelian operation consequences
then remain visible through
\autoref{thm:abgroup-total-centralizer-normalizer-orbit-collapse} and the
normal-form rows
\autoref{thm:abgroup-middle-four-interchange},
\autoref{thm:abgroup-middle-four-double-cancel}, and
\autoref{thm:abgroup-middle-four-transported-double-cancel}.

These cited rows exhaust the public operation surface asserted here: they
expose the singleton carrier and laws, the group reduct, the centralizer and
normalizer collapse, and the middle-four cancellation forms. Since none of the
cited rows constructs host equality, a quotient carrier, a subgroup primitive,
or a module equivalence, the public surface adds none of those structures.
\end{proof}

\begin{lemma}[AbGroup forgetful bridge determinacy]
\label{lem:abgroup-forgets-group-bridge-determinacy}
For the public singleton empty-history $\AbGroupUp$ surface, the bridge-facing
$\GroupUp$ consumer obtained by applying
\autoref{prop:abgroup-forgets-group-certificate} to
\autoref{thm:abgroup-singleton-terminal-standard-bridge} is determined by the
following finite local rows: the retained carrier, source, pattern, classifier,
stability, and ledger fields of the forgetful reduct; the unchanged
multiplication, unit, inverse, and classifier; the constant encode row to
$\emp$; the terminal decode row; the terminal decode-encode row; the
encode-decode readback row $\rho_{\emp}(h,\emp)$ for each carried endpoint
$h:A_{\emp}$; the operation-translation row reading the same displayed
operation as the group multiplication, $\emp$ as the unit, and the constant
operation as inverse; the theorem-preservation rows for carrier, closure, unit,
inverse, and associativity; and the no-host-leak surface $\BHist$, $A_{\emp}$,
$\rho_{\emp}$, $\emp$, and the displayed operations. Hence every displayed
route, transport, readback, or handoff available to such a consumer factors
through these rows, and no unlisted bridge coordinate, host equality, quotient
carrier, subgroup primitive, module equivalence, or commutativity obligation is
available as part of the $\GroupUp$ handoff.
\end{lemma}
\begin{proof}
Apply \autoref{prop:abgroup-forgets-group-certificate}. It says exactly that
the $\GroupUp$ certificate retained from an $\AbGroupUp$ certificate consists
of the carrier, source, pattern, classifier, stability, and ledger fields, with
the carrier, multiplication, identity, inverse operation, and classifier copied
unchanged. Thus any consumer-facing route or transport that asks only for a
group certificate must enter through one of these retained rows.

Now read \autoref{thm:abgroup-singleton-terminal-standard-bridge} through this
reduct. Its encode row is the constant map from the unique terminal host point
to $\emp$, and its decode row sends every carried endpoint of $A_{\emp}$ to the
unique host point. The two round-trip rows are therefore fixed: decode-encode is
terminal equality, while encode-decode is precisely the displayed classifier
witness $\rho_{\emp}(h,\emp)$. Consequently every readback available to the
consumer factors through this single carrier-and-classifier surface.

The same theorem fixes the operation handoff. After forgetting commutativity,
the group-facing operation translation is the unchanged displayed operation,
with $\emp$ as unit and the constant operation as inverse. The theorem-
preservation rows needed by a $\GroupUp$ consumer are exactly the carrier,
closure, unit, inverse, and associativity rows, all of which are retained by the
forgetful certificate. The abelian commutativity and double-negation rows remain
rows of the abelian bridge, but they are not additional coordinates of the
$\GroupUp$ handoff.

Finally, the no-host-leak clause of
\autoref{thm:abgroup-singleton-terminal-standard-bridge} restricts the exported
BEDC-facing surface to $\BHist$, $A_{\emp}$, $\rho_{\emp}$, $\emp$, and the
displayed operations. Since \autoref{prop:abgroup-forgets-group-certificate}
adds no field while forming the reduct, a consumer has no route to any bridge
coordinate outside the listed rows. The omitted commutativity obligation,
commutativity-compatibility data, host equality, quotient carrier, subgroup
primitive, and module equivalence are therefore unavailable as $\GroupUp$ bridge
handoff data.
\end{proof}
