\begin{theorem}[Reality-constrained methodology-ledger observation row]
\label{thm:reality-constrained-methodology-ledger-observation-row}
Let $L=(X,A,O,T,I,S,D,U,F,H,C,Q,N)$ be an accepted
$\RealityConstrainedMethodologyLedgerUp$ packet. Every observation-facing
methodology read must expose the sibling rows for $\RealityConstrainedTruthCert$
and $\SignatureFit$ together with the displayed scope row $S$, refusal row $D$,
failure row $F$, transport row $H$, consumer route $C$, provenance row $Q$,
and local $\NameCert_{\RealityConstrainedMethodologyLedgerUp}$ row $N$. The
observation row is therefore finite $\BHist$ ledger data, not final model
truth, hidden observer privilege, or an off-ledger domain oracle.
\end{theorem}
\begin{proof}
Start with the carrier and NameCert obligations of the chapter. They expose
$X,A,O,T,I,S,D,U,F,H,C,Q,N$ as the finite packet and make sibling
accountability, scope exactness, refusal routing, failure exposure, and ledger
non-escape duties of that packet.

Next use the root methodology triad and root audit source lock. These rows
keep observation, audit, objectivity, tower-compression, and open-fit evidence
inside the same transport, consumer, provenance, and naming surface.

Finally apply the root open-fit model-audit obligation. It prevents an
observation read from becoming a closed empirical fit or host model-truth
certificate outside the displayed local ledger.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger method-fit row]
\label{thm:reality-constrained-methodology-ledger-method-fit-row}
For every accepted $\RealityConstrainedMethodologyLedgerUp$ packet
$L=(X,A,O,T,I,S,D,U,F,H,C,Q,N)$, every method-fit read through the
$\SignatureFit$ surface is accepted only with the $\RealityConstrainedTruthCert$
observation rows, the scope/refusal/upgrade rows $S,D,U$, and the
failure/consumer/provenance/name rows $F,C,Q,N$ visible in the same packet.
The read cannot be replaced by unbounded explanation, final truth, closed
empirical fit, hidden observer privilege, endpoint identity, or off-ledger
methodology authority.
\end{theorem}
\begin{proof}
Begin with scope-export exactness and domain-leakage refusal. These results
require $S$ before methodology export and route beyond-scope attempts through
the displayed refusal surface.

Now apply upgrade-route determinacy and failure-surface exhaustion. Any
admitted movement beyond the current scope stays in $U$, and defeating tests
from sibling surfaces must be collected in $F$ before $C$ is accepted.

Finally use consumer-route exactness and the root route packet. They identify
method-fit consumption with a read of $L$ itself, carried by $H,C,Q,N$, rather
than with a second authority outside the ledger.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger nonescape]
\label{thm:reality-constrained-methodology-ledger-nonescape}
Every root consumer of an accepted $\RealityConstrainedMethodologyLedgerUp$
packet is exhausted by the observation row, method-fit row, scope row, refusal
row, upgrade row, failure row, transport row, consumer route, provenance row,
and local $\NameCert$ row displayed in
$L=(X,A,O,T,I,S,D,U,F,H,C,Q,N)$. No hidden domain leakage, private classifier
choice, final model-truth oracle, unledgered compression channel, endpoint
identity, or off-ledger methodology authority is available to that consumer.
\end{theorem}
\begin{proof}
First combine the observation row and method-fit row above. Together they
place truth-certificate and signature-fit consumption inside the displayed
methodology ledger with $S,D,U,F,H,C,Q,N$ visible.

Next apply the chapter's root route totality and root route non-escape
theorems. They admit consumer reads only through displayed BEDC rows and
exclude hidden model identity, unbounded truth, host semantic oracles,
unledgered compression, and private classifier choice.

Finally use the NameCert unblock surface and root authority carrier totality.
Since the authority read stays on $L$ itself and the local certificate names no
additional coordinate, the root consumer cannot escape the finite methodology
ledger.
\end{proof}
