\begin{definition}[Reality-constrained methodology-ledger root route packet]
\label{def:reality-constrained-methodology-ledger-root-route-packet}
The root route packet for $\RealityConstrainedMethodologyLedgerUp$ is the finite $\BHist$ display
$$
R=(O,M,J,E,T,K,C,P,N)
$$
whose rows record, in order, open-fit evidence from $\OpenFitPacketUp$, model-audit evidence from $\RealityConstrainedModelAuditUp$, objectivity evidence from $\RealityConstrainedObjectivityUp$, explanation evidence from $\RealityConstrainedExplanationUp$, tower-compression evidence from $\RealityConstrainedTowerCompressionUp$, transport rows for the displayed methodology constraints, continuation rows for root consumers, provenance rows for the sibling certificates, and the local $\NameCert_{\RealityConstrainedMethodologyLedgerUp}$ row.

The packet has no coordinate for hidden model identity, unbounded truth, a host semantic oracle, unledgered compression, or private classifier choice.
\end{definition}

\begin{theorem}[Reality-constrained methodology-ledger root route totality]
\label{thm:reality-constrained-methodology-ledger-root-route-totality}
Every root methodology-ledger consumer factors through the rows of \autoref{def:reality-constrained-methodology-ledger-root-route-packet}. In particular, the consumer must read the open-fit, model-audit, objectivity, explanation, tower-compression, transport, continuation, provenance, and local $\NameCert$ rows before using the methodology ledger as a root dependency.
\end{theorem}
\begin{proof}
Project the local carrier and certificate from \autoref{def:reality-constrained-methodology-ledger-carrier} and \autoref{def:reality-constrained-methodology-ledger-certificate}. They already expose the sibling, transport, consumer, provenance, and local naming rows as a finite ledger.

Use the sibling chapters as the only admitted sources. The open-fit packet, model-audit packet, objectivity packet, explanation packet, and tower-compression packet supply the five root methodology constraints named in the packet definition.

Finally apply the local NameCert obligations, root carrier obligation, and consumer-route exactness. These results force the consumer route to stay on the displayed finite rows and prevent a hidden methodology source from replacing the local ledger.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger root route nonescape]
\label{thm:reality-constrained-methodology-ledger-root-route-nonescape}
The root route packet of \autoref{def:reality-constrained-methodology-ledger-root-route-packet} exports no hidden model identity, unbounded truth coordinate, host semantic oracle, unledgered compression channel, or private classifier choice. Every accepted root read remains a finite BEDC route through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Start from root route totality. Any accepted root consumer has already been routed through $O,M,J,E,T,K,C,P,N$.

Apply the carrier non-escape clauses from the local NameCert obligations and the root authority carrier totality theorem. They leave no field in the methodology ledger for a model identity hidden from the packet, unbounded truth, or a host semantic oracle.

Use the tower-compression and consumer-route rows for the remaining exclusions. Compression is ledgered through the displayed tower row, while classifier choice and consumer replay remain public $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$ data rather than private host coordinates.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger root source invariant triad]
\label{thm:reality-constrained-methodology-ledger-root-source-invariant-triad}
For the root route packet
$$
R=(O,M,J,E,T,K,C,P,N)
$$
of \autoref{def:reality-constrained-methodology-ledger-root-route-packet}, the source invariants read by downstream methodology-ledger consumers are exactly the sibling rows $O,M,J,E,T$ together with the transport, continuation, provenance, and local naming rows $K,C,P,N$. The packet exposes those invariants only as finite $\BHist$ data transported by $\hsame$, replayed by $\Cont$, packaged by $\Pkg$, and bound by the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Begin with the packet definition. It names the five sibling source rows for open fit, model audit, objectivity, explanation, and tower compression, and it records the four support rows $K,C,P,N$ in the same finite display.

Apply root route totality. Any root methodology-ledger consumer must first read the displayed rows $O,M,J,E,T,K,C,P,N$, so the sibling sources cannot be replaced by a hidden methodology source.

Finally apply root route nonescape. The only kernel support exported with those sibling rows is $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert$ row, which makes the displayed triad of source, transport, and provenance the whole root surface.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger root failure ledger surface]
\label{thm:reality-constrained-methodology-ledger-root-failure-ledger-surface}
Every failure or refusal read available at the methodology-ledger root is ledgered through the displayed packet rows
$$
O,M,J,E,T,K,C,P,N.
$$
The sibling source rows supply the visible open-fit, model-audit, objectivity, explanation, and tower-compression tests, while $K,C,P,N$ keep the failure ledger inside $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert$ surface. No off-ledger failure waiver, hidden model identity, or unbounded truth coordinate is exported.
\end{theorem}
\begin{proof}
Project the finite packet from \autoref{def:reality-constrained-methodology-ledger-root-route-packet}. Its source rows are precisely the sibling rows $O,M,J,E,T$, and its support rows are $K,C,P,N$.

Use root route totality to force every accepted root consumer through those rows before the methodology ledger can be used as a dependency. Thus any failure or refusal test seen at the root is read from the same finite packet.

Root route nonescape supplies the exclusions. Since the packet exports only $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ support, an off-ledger waiver, hidden identity, or unbounded truth coordinate has no row from which it could be read.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger root export nonescape]
\label{thm:reality-constrained-methodology-ledger-root-export-nonescape}
The public root export of $\RealityConstrainedMethodologyLedgerUp$ is exhausted by the packet rows $O,M,J,E,T,K,C,P,N$, with the sibling source rows carried through the displayed BEDC support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. A downstream consumer may export the finite methodology-ledger route, but it may not export hidden model identity, unbounded truth, a host semantic oracle, unledgered compression, private classifier choice, or a source row outside the sibling packet.
\end{theorem}
\begin{proof}
First read the packet definition, which fixes the export surface as $O,M,J,E,T,K,C,P,N$ and gives no coordinate for any additional source row.

Root route totality then identifies every accepted downstream read with that same packet. The source rows are the listed siblings, and the continuation and provenance rows carry them without introducing a second route.

Apply root route nonescape for the export boundary. It restricts the consumer-visible support to $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert$ row, so none of the excluded host, truth, compression, classifier, or extra-source coordinates can leave the root packet.
\end{proof}
