\begin{theorem}[Reality-constrained methodology-ledger root carrier obligation]
\label{thm:reality-constrained-methodology-ledger-root-carrier-obligation}
Let $L=(X,A,O,T,I,S,D,U,F,H,C,Q,N)$ be an accepted $\RealityConstrainedMethodologyLedgerUp$ packet. Every root methodology-ledger read must expose the sibling failure, open-fit, and objectivity dependency rows through the same finite $\BHist$ carrier, the same componentwise $\hsame$ transport, the same displayed consumer route, the same package provenance row, and the same local $\NameCert_{\RealityConstrainedMethodologyLedgerUp}$ row. The read cannot replace $L$ by an off-ledger methodology carrier, hidden observer privilege, final model truth, or closed empirical oracle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:reality-constrained-methodology-ledger-carrier}. It displays the explanation, audit, objectivity, tower-compression, open-fit, scope, refusal, upgrade, failure, transport, consumer, provenance, and local naming rows in one packet.

Apply \autoref{thm:reality-constrained-methodology-ledger-root-dependency-totality}. The sibling failure, open-fit, and objectivity dependencies remain rows of the same finite methodology ledger rather than external carriers.

Finally use \autoref{thm:reality-constrained-methodology-ledger-route-normal-form}. Since every consumer route factors through $L$, there is no route for an off-ledger methodology carrier, hidden observer privilege, final model truth, or closed empirical oracle.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger root classifier stability]
\label{thm:reality-constrained-methodology-ledger-root-classifier-stability}
For an accepted $\RealityConstrainedMethodologyLedgerUp$ packet $L=(X,A,O,T,I,S,D,U,F,H,C,Q,N)$, the root classifier is stable exactly along the displayed $\hsame$ transport and $\Cont$ route. Any classifier read comparing sibling failure, open-fit, objectivity, refusal, upgrade, or failure rows must compare the same local NameCert packet, and it cannot introduce a hidden fit selector, detached domain-truth predicate, or external adequacy theorem.
\end{theorem}
\begin{proof}
Start from \autoref{thm:reality-constrained-methodology-ledger-root-carrier-obligation}. The root read has already exposed the displayed finite carrier and the local NameCert row.

Use \autoref{thm:reality-constrained-methodology-ledger-namecert-obligations}. Its classifier and ledger clauses bind sibling accountability, scope exactness, domain-leakage refusal, failure exposure, and non-escape to the same packet.

Then apply \autoref{thm:reality-constrained-methodology-ledger-consumer-route-exactness}. The classifier travels only along the displayed $\hsame$ and $\Cont$ rows, so hidden fit selectors, detached domain-truth predicates, and external adequacy theorems have no accepted comparison route.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger root ledger exactness]
\label{thm:reality-constrained-methodology-ledger-root-ledger-exactness}
Every root ledger export of an accepted $\RealityConstrainedMethodologyLedgerUp$ packet is exactly the finite packet $X,A,O,T,I,S,D,U,F,H,C,Q,N$ read through $\BHist$, $\hsame$, $\Cont$, package provenance, and local NameCert data. The ledger records sibling failure, open-fit, objectivity, refusal, upgrade, and failure rows without exporting unbounded methodology authority, hidden empirical fit, endpoint identity, or off-ledger proof evidence.
\end{theorem}
\begin{proof}
First retain the carrier and classifier by \autoref{thm:reality-constrained-methodology-ledger-root-carrier-obligation} and \autoref{thm:reality-constrained-methodology-ledger-root-classifier-stability}. The ledger export is already tied to the displayed finite packet and its componentwise transport route.

Next read the failure and refusal rows through \autoref{thm:reality-constrained-methodology-ledger-failure-route-locality} and \autoref{thm:reality-constrained-methodology-ledger-root-refusal-upgrade-coverage}. These theorems keep defeating tests, refusal records, and allowed extensions local to $L$.

Finally use \autoref{thm:reality-constrained-methodology-ledger-public-export-readiness}. A public methodology readback may export only the local methodology-ledger interface, so unbounded methodology authority, hidden empirical fit, endpoint identity, and off-ledger proof evidence are excluded.
\end{proof}
