\begin{theorem}[Reality-constrained methodology-ledger TasteGate readback surface]
\label{thm:reality-constrained-methodology-ledger-tastegate-readback-surface}
For every displayed $\RealityConstrainedMethodologyLedgerUp$ packet
$L=(X,A,O,T,I,S,D,U,F,H,C,Q,N)$, the rows shown in the paper carrier are the
same rows decoded by the checked TasteGate readback theorem
\texttt{RealityConstrainedMethodologyLedgerTasteGate\_single\_carrier\_alignment}.
The encoding route reads each $\BHist$ row as a finite $\BMark$ event, decodes
it back to the same $\BHist$ row, and reconstructs the single
$\RealityConstrainedMethodologyLedgerUp$ carrier rather than a second
methodology object.
\end{theorem}
\leanchecked{BEDC.Derived.RealityConstrainedMethodologyLedgerUp.RealityConstrainedMethodologyLedgerTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project $L$ into its thirteen displayed rows. The TasteGate readback theorem
proves the $\BHist$ encode-decode identity for each row and the round-trip law
from the event-flow presentation back to the same ledger packet.

Apply the injectivity component of the same checked theorem. If two event-flow
readbacks agree, the underlying $\RealityConstrainedMethodologyLedgerUp$
packets agree, so the paper rows and the decoded rows are not parallel
carriers. They are the same finite carrier read through the TasteGate surface.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger nontrivial field-faithful readback]
\label{thm:reality-constrained-methodology-ledger-nontrivial-field-faithful-readback}
The paper-side falsifiable-prediction row and independence witness are
witnessed on the same $\RealityConstrainedMethodologyLedgerUp$ carrier by the
Lean \texttt{Nontrivial} and \texttt{FieldFaithful} instances. The
\texttt{Nontrivial} instance separates the all-empty packet from the packet
whose $X$ row is $e0(\emptyset)$, and the \texttt{FieldFaithful} instance
says equality of the displayed row list
$[X,A,O,T,I,S,D,U,F,H,C,Q,N]$ determines equality of the packet.
\end{theorem}
\begin{proof}
Use the \texttt{Nontrivial} instance for the falsifiable-prediction witness.
It supplies two packets in the same carrier and proves they are distinct by
constructor separation at the $X$ row.

Use the \texttt{FieldFaithful} instance for row independence. Its field map is
exactly the displayed row list, and its faithfulness clause says that no hidden
coordinate remains after those rows agree. Thus the prediction witness and the
field-faithfulness readback live on the carrier already named by the paper
certificate.
\end{proof}

\begin{theorem}[Reality-constrained methodology-ledger formal-target closure route]
\label{thm:reality-constrained-methodology-ledger-formal-target-closure-route}
The refusal-upgrade surface, failure-consumer surface, prediction row, and
TasteGate readback surface together give a formal-target route for later
closure promotion of $\RealityConstrainedMethodologyLedgerUp$. The route is
confined to the displayed finite carrier, its $\BHist/\hsame/\Cont/\Pkg$
support, its local $\NameCert$ obligations, and the checked TasteGate readback;
it does not claim public closure, bridge closure, physical-model adequacy, or a
domain-truth oracle.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:reality-constrained-methodology-ledger-refusal-upgrade-totality}
and
\autoref{thm:reality-constrained-methodology-ledger-failure-consumer-coverage}.
These surfaces route refusal, upgrade, failure exposure, and consumer access
through the displayed methodology-ledger rows.

Apply
\autoref{thm:reality-constrained-methodology-ledger-prediction-row-nonescape}
and
\autoref{thm:reality-constrained-methodology-ledger-tastegate-readback-surface}.
The prediction read remains inside the same finite ledger, and the TasteGate
readback identifies the event-flow decoding with the displayed carrier. This
is a formal-target route for a later closurestatus decision, not itself a
claim of public or bridge closure.
\end{proof}
