\begin{theorem}[CompactUniformContinuity four-source handoff correspondence]
\label{thm:compact-uniform-continuity-four-source-handoff-correspondence}
For every accepted $\CompactUniformContinuityUp$ root packet, the finite $\mathsf{ProbeBundle}$ compact-net rows, the pointwise $\ContinuousMapUp$ modulus rows, the source and target $\mathsf{MetricDistanceWitness}$ rows, the positive $\RatUp$ fold rows, and the $\RealUp$ seal row form one finite handoff correspondence. A consumer may enter the handoff through any displayed compact, continuous, metric, rational, or real row, but every such entry reads the same carrier packet with the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CompactUniformContinuityUp}$ provenance.

The correspondence has no coordinate for open-cover compactness, sequence compactness, host minimum selection, or an external modulus. It is the root handoff of the displayed finite rows.
\end{theorem}
\leanchecked{BEDC.Derived.CompactUniformContinuityUp.CompactUniformContinuityPacket\_four\_source\_handoff\_correspondence}
\begin{proof}
Start with the compact-net side. Apply \autoref{thm:compact-uniform-continuity-finite-net-handoff} to bind the finite $\mathsf{ProbeBundle}$ net to the centerwise $\ContinuousMapUp$ modulus rows.

Next read the metric and rational rows. Metric-distance routing supplies the only source and target distance observations, while radius-fold exactness identifies the positive $\RatUp$ fold as the precision row consumed by the handoff.

Finally attach the real-facing boundary. Use the real seal boundary together with the rational fold export theorem to repack the compact, continuous, metric, rational, and real rows as one carrier correspondence. Since each step is a projection from the accepted packet followed by displayed transport, no outside compactness or modulus coordinate is introduced.
\end{proof}
