\begin{theorem}[CompactUniformContinuity four-source handoff correspondence]
\label{thm:compact-uniform-continuity-four-source-handoff-correspondence}
For every accepted $\CompactUniformContinuityUp$ root packet, the finite $\mathsf{ProbeBundle}$ compact-net rows, the pointwise $\ContinuousMapUp$ modulus rows, the source and target $\mathsf{MetricDistanceWitness}$ rows, the positive $\RatUp$ fold rows, and the $\RealUp$ seal row form one finite handoff correspondence. A consumer may enter the handoff through any displayed compact, continuous, metric, rational, or real row, but every such entry reads the same carrier packet with the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CompactUniformContinuityUp}$ provenance.

The correspondence has no coordinate for open-cover compactness, sequence compactness, host minimum selection, or an external modulus. It is the root handoff of the displayed finite rows.
\end{theorem}
\begin{proof}
Start with the compact-net side. Apply \autoref{thm:compact-uniform-continuity-finite-net-handoff} to bind the finite $\mathsf{ProbeBundle}$ net to the centerwise $\ContinuousMapUp$ modulus rows.

Next read the metric and rational rows. Metric-distance routing supplies the only source and target distance observations, while radius-fold exactness identifies the positive $\RatUp$ fold as the precision row consumed by the handoff.

Finally attach the real-facing boundary. Use the real seal boundary together with the rational fold export theorem to repack the compact, continuous, metric, rational, and real rows as one carrier correspondence. Since each step is a projection from the accepted packet followed by displayed transport, no outside compactness or modulus coordinate is introduced.
\end{proof}
\leanchecked{BEDC.Derived.CompactUniformContinuityUp.CompactUniformContinuityPacket\_four\_source\_handoff\_correspondence}

\begin{theorem}[CompactUniformContinuity rational fold metric compatibility]
\label{thm:compact-uniform-continuity-rational-fold-metric-compatibility}
In an accepted $\CompactUniformContinuityUp$ packet, the rational-fold precision row is compatible with every source-center and target-output metric read consumed by the handoff of \autoref{thm:compact-uniform-continuity-four-source-handoff-correspondence}. Each $\mathsf{MetricDistanceWitness}$ read is routed through the displayed compact-net center, then compared only against the precision exported by the positive $\RatUp$ lower-bound fold and its recorded $\hsame$ and $\Cont$ transports.

Thus no metric consumer can replace the rational fold by a host minimum, an unrecorded real radius, or an external modulus choice.
\end{theorem}
\begin{proof}
Project the displayed metric witnesses from the carrier. By metric-distance routing, every source-center or target-output distance read is one of these witnesses and not a host metric call.

Apply finite-net handoff to place those metric witnesses on the same route as the centerwise $\ContinuousMapUp$ modulus rows. Radius-fold exactness then identifies the precision read by that route with the positive $\RatUp$ lower-bound fold.

The rational fold export theorem says that all downstream precision consumers factor through this fold. Therefore every metric read consumed by the handoff is compatible with the same rational precision row, and no hidden radius selector is available.
\end{proof}
\leanchecked{BEDC.Derived.CompactUniformContinuityUp.CompactUniformContinuityPacket\_rational\_fold\_metric\_compatibility}

\begin{theorem}[CompactUniformContinuity compact-continuous NameCert export]
\label{thm:compact-uniform-continuity-compact-continuous-namecert-export}
The compact-net rows, pointwise $\ContinuousMapUp$ modulus rows, $\mathsf{MetricDistanceWitness}$ rows, positive $\RatUp$ fold rows, and $\RealUp$ seal row of an accepted $\CompactUniformContinuityUp$ packet export a finite $\NameCert_{\CompactUniformContinuityUp}$ package. The exported package is exactly the displayed carrier, classifier, transport, continuation, package, and naming ledger over those rows.

It exports no open-cover compactness, sequence compactness, host minimum, host modulus, or additional real-coordinate selector.
\end{theorem}
\begin{proof}
First assemble the finite handoff correspondence from \autoref{thm:compact-uniform-continuity-four-source-handoff-correspondence}. This supplies the compact, continuous, metric, rational, and real rows as one accepted packet with fixed provenance.

Next apply \autoref{thm:compact-uniform-continuity-rational-fold-metric-compatibility}. The metric observations and rational precision row agree along the displayed finite-net route, so the exported package has a single precision ledger.

Finally use the real seal boundary and rational fold export theorem. The real-facing row can only read the sealed finite packet, while the rational fold remains the only exported precision. Repacking these rows gives the finite $\NameCert_{\CompactUniformContinuityUp}$ package and leaves no coordinate for open covers, sequence compactness, host minima, or external modulus data.
\end{proof}
\leanchecked{BEDC.Derived.CompactUniformContinuityUp.CompactUniformContinuityPacket\_compact\_continuous\_namecert\_export}

\begin{theorem}[CompactUniformContinuity four-source bridge determinacy]
\label{thm:compact-uniform-continuity-four-source-bridge-determinacy}
For every accepted $\CompactUniformContinuityUp$ root packet, the consumer-facing bridge determined by \autoref{thm:compact-uniform-continuity-four-source-handoff-correspondence} and \autoref{thm:compact-uniform-continuity-compact-continuous-namecert-export} has a unique displayed finite source. Any route, transport, readback, or handoff through the compact, continuous, metric, rational, or real side factors through the finite $\ProbeBundle$ compact-net rows, the centerwise $\ContinuousMapUp$ modulus rows, the source and target $\mathsf{MetricDistanceWitness}$ rows, the positive $\RatUp$ fold rows, the $\RealUp$ seal row, and the common $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CompactUniformContinuityUp}$ provenance.

Consequently an unlisted bridge coordinate, including open-cover compactness, sequence compactness, host minimum selection, a hidden real-radius selector, or an external modulus, is unavailable to every such consumer.
\end{theorem}
\begin{proof}
Apply \autoref{thm:compact-uniform-continuity-four-source-handoff-correspondence}. It states that a consumer may enter through any displayed compact, continuous, metric, rational, or real row, but every such entry reads the same accepted carrier packet and the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CompactUniformContinuityUp}$ provenance. Thus the compact entry is the finite $\ProbeBundle$ net row, the continuous entry is the centerwise $\ContinuousMapUp$ modulus row, the metric entry is one of the displayed source or target $\mathsf{MetricDistanceWitness}$ rows, the rational entry is the positive $\RatUp$ fold row, and the real entry is the $\RealUp$ seal row.

Apply \autoref{thm:compact-uniform-continuity-compact-continuous-namecert-export}. The export packages exactly the displayed carrier, classifier, transport, continuation, package, and naming ledger over those rows. Therefore a route is read through the displayed $\Cont$ continuation rows, a transport is read through the displayed $\hsame$ and classifier rows, a readback is a projection to one of the listed compact, continuous, metric, rational, or real rows, and a handoff is the finite correspondence obtained by repacking those projections with the same $\Pkg$ and $\NameCert_{\CompactUniformContinuityUp}$ provenance.

These four consumer actions have the same source because the correspondence fixes the carrier packet before the export repacks it, and the export exposes no second carrier, classifier, transport, continuation, package, or naming ledger. Hence two displayed consumer entries cannot determine different bridge data: after projection they land in the same finite row list and after export they carry the same provenance.

The nonlisted cases are excluded by the same two rows. The correspondence explicitly has no coordinate for open-cover compactness, sequence compactness, host minimum selection, or an external modulus, and the export adds no open-cover, sequence, host-minimum, host-modulus, or additional real-coordinate selector. Since an unavailable coordinate is neither a projection from the carrier nor a transported component of the exported $\NameCert_{\CompactUniformContinuityUp}$ package, no consumer-facing route, transport, readback, or handoff can factor through it.
\end{proof}

\begin{corollary}[CompactUniformContinuity four-source handoff consumer determinacy]
\label{cor:compact-uniform-continuity-four-source-handoff-consumer-determinacy}
For every accepted $\CompactUniformContinuityUp$ root packet, fix the finite $\ProbeBundle$ compact-net rows, the centerwise $\ContinuousMapUp$ modulus rows, the source and target $\mathsf{MetricDistanceWitness}$ rows, the positive $\RatUp$ fold rows, the $\RealUp$ seal row, and the common $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CompactUniformContinuityUp}$ provenance named by \autoref{thm:compact-uniform-continuity-four-source-handoff-correspondence}. Then every accepted consumer-facing use that reports a route selection, a normal-form readback, or an exactness decision for the four-source handoff reports the one determined by those fixed rows.

The finite route is the displayed handoff through compact-net coverage, centerwise continuity, source and target metric witnesses, rational fold precision, and the real seal. The normal-form readback is the ordered projection to those same rows with the displayed transport, continuation, package, and local naming provenance. The exactness decision accepts precisely the consumer uses that factor through that fixed finite route. No open-cover compactness coordinate, sequence compactness coordinate, host minimum selector, hidden real-radius selector, external modulus, alternate hidden coordinate, or duplicate classifier source can supply a different accepted route, normal form, or exactness decision.
\end{corollary}
\begin{proof}
Fix the accepted root packet and the listed local rows. By \autoref{thm:compact-uniform-continuity-four-source-handoff-correspondence}, a consumer may enter through any displayed compact, continuous, metric, rational, or real row, but every such entry reads the same carrier packet with the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CompactUniformContinuityUp}$ provenance. Thus the five source families are not competing sources; they are five entry faces of one finite handoff correspondence.

Apply \autoref{thm:compact-uniform-continuity-four-source-bridge-determinacy}. It identifies the consumer-facing bridge as having a unique displayed finite source and forces every route, transport, readback, or handoff through the compact, continuous, metric, rational, or real side to factor through exactly the fixed row list. Since the rows have been fixed, two accepted consumer uses cannot choose distinct finite sources: after factorization, both land in the same compact-net rows, the same centerwise modulus rows, the same source and target metric-witness rows, the same rational fold rows, the same real seal row, and the same structural provenance.

A reported route selection is therefore the displayed factorization route through those rows. A reported normal-form readback is the same ordered projection of the fixed carrier: first the finite $\ProbeBundle$ compact-net and coverage rows, then the centerwise $\ContinuousMapUp$ modulus rows, then the source and target $\mathsf{MetricDistanceWitness}$ rows, then the positive $\RatUp$ fold, and finally the $\RealUp$ seal, all transported and repacked by $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert$ row. A reported exactness decision is consequently the decision that a consumer use is accepted exactly when it factors through this fixed route and its structural provenance.

It remains to exclude alternate sources for the same public decision. If a purported duplicate classifier source is one of the displayed classifier, transport, continuation, package, or naming rows, then it is already part of the fixed provenance and determines the same route. If it is not one of those rows, then \autoref{thm:compact-uniform-continuity-four-source-bridge-determinacy} and \autoref{thm:compact-uniform-continuity-four-source-handoff-correspondence} leave it no projection, transport, readback, or handoff coordinate. The excluded open-cover, sequence, host-minimum, hidden real-radius, and external-modulus cases are therefore rejected before they can become accepted consumer-facing data.
\end{proof}
