\section{The L1-L4 Stratification}\label{sec:self-comp-stratification}

The phrase ``BEDC compiles itself'' has several inequivalent readings. The
paper uses a stratified reading rather than a single slogan. Each layer states
which object is visible, which checker acts on it, and which ceiling prevents a
stronger reading.

L1 is static paper-Lean alignment. A paper site names a Lean target through
`\verb|\leanchecked|', `\verb|\leanvariant|', `\verb|\leanstmt|',
`\verb|\leandef|', or a closure-status `\verb|\leantarget|'. The external audit
script `\verb|lean4/scripts/bedc_ci.py audit|' reads those names and checks that
the referenced Lean declarations exist under `\verb|lean4/BEDC|'. L1 therefore
does not ask BEDC to prove its own metatheory. It asks the repository to expose a
typed correspondence between paper claims and Lean declarations, with failed
name resolution treated as a build-time fault.

L1 has three important limits. First, it is syntactic at the boundary between
paper and Lean: a marker can name a declaration, but it does not itself explain
the declaration's proof. Second, the audit is a Python-side repository check,
not a Lean theorem about LaTeX. Third, the closure axis and the verification axis
remain distinct: a Lean target can be checked while the paper-side theory claim
is only scoped, and a paper claim can be theoretically delimited while its
formal marker is only a target.

L2 is internal base reflection. At this layer BEDC represents selected parts of
its own kernel vocabulary as Lean data and proves internal self-consistency
facts about them. The base reflection surface covers package reflection,
signature-object reflection, domain reflection, token uniqueness replacements,
and witness-chain descriptions of generated sameness. Its job is not to certify
the whole Lean kernel. Its job is to show that BEDC can place its own finite
kernel objects under typed constructors and prove the advertised local
coherence facts inside CIC.

In symbols, the intended shape of L2 is:

$$
\begin{aligned}
\text{finite BEDC object}
&\longmapsto \text{Lean-coded reflection datum},\\
\text{reflection datum}
&\longmapsto \text{local coherence theorem}.
\end{aligned}
$$

The arrow is intentionally local. It does not assert that every paper sentence,
every Lean declaration, or every semantic reading of BEDC is reflected. It
asserts that the finite kernel interfaces identified by the base-reflection
surface admit typed internal witnesses.

L3 is the NameCert obligation surface. Here BEDC records that concrete
mathematical interfaces expose obligation packets rather than finished external
mathematics. Holonomy, KKT, and SpectralMeasure are representative cases:
their Lean declarations register the shape of the name-certificate obligation,
not a public closure theorem for the surrounding domain. The L3 surface is
therefore a disciplined boundary between a typed internal packet and the
mathematical work required to discharge a domain-specific certificate.

L3 matters for self-compilation because it prevents reflection from becoming a
claim-laundering device. A reflected name-certificate packet can say, in Lean,
which obligations belong to the interface. It cannot, merely by being named,
turn those obligations into domain theorems. The packet is a typed surface for
inspection and later discharge; it is not a bridge from syntax to truth.

L4 is not a single level. It splits into four readings, only one of which is
claimed here.

L4a is an axiom-free completeness theorem for BEDC inside CIC. This would say
that BEDC internally proves the complete soundness or completeness of the host
logic sufficient to certify all of its own proof checking. BEDC does not claim
L4a. Since BEDC is formalized inside the host Calculus of Inductive
Constructions, Tarski undefinability and Godel's second incompleteness theorem
block the relevant global truth and consistency assertions from being obtained
as axiom-free internal theorems of the same strength.

L4-mid is the finite type-checked Manifest of paper-anchored theorems. This is
the achieved self-compilation surface. BEDC contains a Lean-side manifest whose
entries pair paper labels, Lean names, propositions, and proof terms. The
dependent field `\verb|proof : prop|' makes type correctness a kernel obligation
when the manifest elaborates. The observable theorem
`\verb|BEDC.Manifest.manifest_wellformed|' then exposes, for every manifest
entry, a witness of the registered proposition.

L4b is an elaboration-time Lean audit that replaces the external Python name
audit. Such a layer would move more of L1 from repository tooling into Lean's
own elaboration and reflection facilities. The present chapter does not claim
L4b. It isolates the target shape: Lean-visible declarations, Lean-visible
paper anchors or generated manifest entries, and an elaboration-time failure
mode when the surface does not match.

L4c is a bijection between the theory-closure axis and the verification-status
axis. BEDC rejects L4c as a matter of governance. Paper-side closure and
Lean-side verification are intentionally independent coordinates. Their joint
reporting is a product condition, not a fixed point:

$$
\begin{aligned}
\mathrm{VerifiedGate}(N,c,v)
  &:= \mathrm{TheoryGate}(N,c) \wedge \mathrm{FormalStatus}(N,v).
\end{aligned}
$$

This product form is part of the self-compilation surface. It lets BEDC say
exactly which fragment is internally checked, which fragment is theoretically
closed, and which bridge remains absent, without collapsing those statements
into a single certification number.
