\section{Internal Manifest}\label{sec:self-comp-manifest}

The internal Manifest is the L4-mid surface in its most concrete form. It is a
finite Lean object that records selected paper-anchored theorem claims as
kernel-checked entries. Each entry carries a paper label, a fully qualified Lean
name, the proposition being recorded, and a proof of that proposition.

The core shape is the Lean structure `\verb|BEDC.Manifest.ClaimEntry|':

$$
\begin{aligned}
\mathrm{ClaimEntry}
  &= \{\,\mathrm{paper\_label} : \mathrm{String},\\
  &\qquad \mathrm{lean\_name} : \mathrm{String},\\
  &\qquad \mathrm{prop} : \mathrm{Prop},\\
  &\qquad \mathrm{proof} : \mathrm{prop}\,\}.
\end{aligned}
$$

The last field is the essential one. The manifest does not store an untyped
string saying that a proof exists. It stores a proof term whose type is the
entry's own proposition. When Lean elaborates the list of entries, the kernel
checks that each proof term inhabits the proposition supplied by that same
entry. A malformed pair cannot be silently accepted as a well-typed entry.

This makes Manifest wellformedness kernel-decidable in the practical sense used
by this paper: the Lean kernel either accepts the manifest term or rejects it
during checking. The paper does not claim that BEDC internally decides arbitrary
truth. It claims the finite manifest has a type-checking boundary. For each
entry already present in the finite list, Lean checks the displayed proof
against the displayed proposition.

The Manifest therefore separates three surfaces that are easy to confuse. The
paper label is a human-facing anchor into the LaTeX document. The Lean name is a
string that records the declaration intended by the entry. The proposition and
proof field are the kernel-facing content. The manifest theorem below speaks
about the kernel-facing content; repository audits continue to police paper
marker names and file-level correspondence.

\leanchecked{BEDC.Manifest.manifest\_wellformed}

The theorem `\verb|BEDC.Manifest.manifest_wellformed|' is an observable
corollary of this dependent representation. It says that every entry in
`\verb|BEDC.Manifest.manifest|' has a nonempty proposition:

$$
\begin{aligned}
\forall e,\ e \in \mathrm{manifest}
  \longrightarrow \mathrm{Nonempty}(e.\mathrm{prop}).
\end{aligned}
$$

Its proof is direct: the entry already contains `\verb|e.proof|', so the
witness is `\verb|\langle e.proof\rangle|'. The content is not hidden in that
short proof term. The work is performed by the typing of `\verb|ClaimEntry|'
and by the kernel's acceptance of each manifest entry.

This is why the Manifest is L4-mid rather than L4a. It is internal, finite, and
type checked. It does not define Lean truth for Lean inside Lean. It does not
prove that every possible BEDC paper claim has a corresponding proof. It does
not certify arbitrary external mathematics. It certifies that the listed
paper-anchored theorem entries have proof terms accepted by the host kernel.

The Manifest also clarifies the relation between paper governance and Lean
verification. A Manifest entry can support a paper marker and can make the
corresponding proof term visible as data. It does not erase the need for the
paper-side closure fields: `\verb|\theoryclosure|', `\verb|\scopeclosed|',
`\verb|\formalstatus|', `\verb|\bridgestatus|', `\verb|\notclaimed|', and
`\verb|\upgradepath|'. Those fields state the theoretical scope around the
claim. The Manifest states that selected Lean propositions have typed proof
terms.

Consequently, the self-compilation claim at this layer is precise. BEDC can
carry a finite manifest of its own paper-anchored Lean theorems as Lean data,
and the kernel can reject ill-typed entries. That is a real internal reflection
surface, but it is deliberately not a global self-certification theorem.
