\subsection{Evolution Trajectory}\label{subsec:reconstruction-evolution-trajectory}

The MetaCIC surface admits several coherent directions while retaining its
inside-host reconstruction role. One direction is a richer conversion relation:
eta-conversion can be added to \texttt{BetaStep} and
\texttt{BetaParallel}, with eta-reduction for functions represented beside
beta contraction. Another direction is a universe hierarchy, replacing the
single sort by indexed $\mathrm{Type}\ i$ levels and typing rules that track
universe movement. A third direction is syntax for inductive families beyond
Pi and Sort, so that families with constructors and eliminators become
represented objects.

Deeper metatheory would strengthen the current shape-local surface. A full
substitution-preservation theorem would transport arbitrary binder domains
through shift and substitution, rather than relying only on closed-domain
cases. Strong normalization for closed sort-typed terms would naturally follow
a Tait reducibility route, with reducibility predicates indexed by represented
types. A complete Church--Rosser theorem would turn the local parallel
diamond components into confluence for the full represented reduction system.

A host bridge would add reflection in the other direction: selected
\texttt{Lean.Expr} values could be translated into BEDC \texttt{Term} values
under an explicit reconstruction certificate. On that basis, a command such
as \texttt{\#metacic\_decide} could ask the host to quote a term, reconstruct
the corresponding MetaCIC object, and discharge represented typing or
conversion goals against the internal BEDC surface.
