\subsection{Lean Module Topology}\label{subsec:reconstruction-module-topology}

The Lean dependency topology for \texttt{BEDC.MetaCIC} is a directed acyclic
graph. \texttt{BEDC.MetaCIC.Syntax} is the foundation: it imports
\texttt{BEDC.FKernel.Mark} and defines $\mathrm{Term}$, $\mathrm{Ctx}$,
$\mathrm{shift}$, and $\mathrm{substitute}$. On that base,
\texttt{BEDC.MetaCIC.ClosedTerm} and \texttt{BEDC.MetaCIC.Beta} depend only
on syntax. The substitution family
\texttt{BEDC.MetaCIC.Substitution.NatShift},
\texttt{BEDC.MetaCIC.Substitution.Basic},
\texttt{BEDC.MetaCIC.Substitution.Core}, and
\texttt{BEDC.MetaCIC.Substitution.Statements} depends on syntax and closed
terms, while \texttt{BEDC.MetaCIC.Substitution} re-exports that surface.
\texttt{BEDC.MetaCIC.Typing.Core},
\texttt{BEDC.MetaCIC.Typing.SubstitutionSurface}, and
\texttt{BEDC.MetaCIC.Typing.ClosedBinderDomains} depend on syntax and the
substitution surface. \texttt{BEDC.MetaCIC.SubjectReduction} depends on
typing and beta reduction; \texttt{BEDC.MetaCIC.Confluence} depends on beta
reduction; \texttt{BEDC.MetaCIC.Normalization} depends on beta reduction and
closed terms; and \texttt{BEDC.MetaCIC.AtomInfer} and
\texttt{BEDC.MetaCIC.TypedExamples} depend on typing. No module in this
topology imports back into one of its prerequisites.

\subsection{Tactic Discipline}\label{subsec:reconstruction-tactic-discipline}

The MetaCIC Lean modules are kept under a restricted proof discipline. Tactics
such as \texttt{simp}, \texttt{decide}, and \texttt{omega} are not used in
this layer, because they can introduce transitive dependencies on
\texttt{propext}, decision procedures, or classical reasoning.

The permitted proof surface is the structural fragment needed by the
reconstruction: \texttt{match}, \texttt{cases}, \texttt{rfl},
\texttt{exact}, \texttt{apply}, \texttt{intro}, \texttt{contradiction},
\texttt{rw}, \texttt{unfold}, \texttt{induction}, and \texttt{change}.
These commands keep proofs close to the generated inductive structure of the
syntax, typing, reduction, and substrate definitions.

This discipline is a necessary condition for preserving the axiom-free status
of the MetaCIC reconstruction. The strict purity audit
\texttt{python3 lean4/scripts/bedc\_ci.py axiom-purity --strict} checks each
theorem's transitive dependencies against the forbidden constants
\texttt{Classical.choice}, \texttt{Quot.sound}, and \texttt{propext}; the gate
passes only when the forbidden set is empty for every audited theorem.

\subsection{Build and Audit Process}\label{subsec:reconstruction-build-audit-process}

The complete local verification gate for \texttt{BEDC.MetaCIC} is the Lean
build followed by the paper and axiom audits:

\begin{verbatim}
cd lean4 && lake build
python3 tools/check-axioms.py
python3 lean4/scripts/bedc_ci.py audit
python3 lean4/scripts/bedc_ci.py axiom-purity --strict
python3 lean4/scripts/bedc_ci.py conservativity-audit
\end{verbatim}

The first command checks that the Lean modules build with no accepted
\texttt{sorry} terms and no project axioms. The axiom audit enforces the
source-level ban on \texttt{axiom}. The drift audit resolves the paper's Lean
markers against the actual \texttt{lean4/BEDC/} namespace. The strict
axiom-purity audit checks transitive theorem dependencies, excluding
\texttt{propext}, \texttt{Classical.choice}, and \texttt{Quot.sound}. The
conservativity audit is the metalogical gate for the reconstruction surface.
Each command must exit with status $0$. The chain passes only when the paper
invariant and the mechanized state agree, and that agreement is the local
shipping condition for the MetaCIC reconstruction.

\subsection{Axiom-Free Claim}\label{subsec:reconstruction-axiom-free-claim}

The axiom-free claim for \texttt{BEDC.MetaCIC} has two distinct parts. First,
no \texttt{BEDC.MetaCIC} module declares a host axiom. This is a project-wide
hard invariant: \texttt{tools/check-axioms.py} exits with failure if an axiom
declaration appears in the BEDC Lean sources.

Second, the checked \texttt{BEDC.MetaCIC} theorems do not depend on Lean
stdlib axioms such as \texttt{Classical.choice}, \texttt{Quot.sound}, or
\texttt{propext}. This dependency claim is audited by
\texttt{bedc\_ci.py axiom-purity --strict}, which queries Lean through
\texttt{\#print axioms} and rejects those extra axiom dependencies.

Thus the commitment is stronger than the absence of local axiom declarations:
the reconstructed MetaCIC layer is a pure constructive fragment inside CIC,
with no reliance on Lean's additional axioms beyond CIC. The audit currently
covers more than 9,000 checked theorems, and the exact count is allowed to
change with the theorem set.
