\section*{Shift-Aware Metatheory: Case-Level Closure}\label{sec:self-comp-shift-aware-metatheory}

The shift-aware MetaCIC layer isolates subject reduction into local closure contracts for
substitution, beta contraction, and congruence. The scope is deliberately
case-level: each theorem states a structurally checkable condition on the
represented syntax and typing derivation, and the final assembly records the
remaining interface hypotheses.

\paragraph{Atom-shaped binder substitution.}
Substitution preserves typing for the Pi and lambda constructors under
closedness and atom-shape hypotheses. For Pi terms, the domain and codomain
premises reduce to the sort-or-variable fragment after binder-head transport.
\leanchecked{BEDC.MetaCIC.substitute\_preserves\_typing\_pi}
For lambda terms, the same pattern applies to the body under the shifted binder
context, yielding a typed substituted lambda against the substituted Pi type.
\leanchecked{BEDC.MetaCIC.substitute\_preserves\_typing\_lam}

The shared binder transport step is represented explicitly as the equality
which turns substitution under a shifted closed head into the shifted
substituted head.
\leanchecked{BEDC.MetaCIC.substitute\_preserves\_typing\_binder\_head\_shape}
The lower-level constructor assemblers expose the same decomposition without
the atom-shape discharge:
\leanchecked{BEDC.MetaCIC.substitute\_preserves\_typing\_pi\_if\_subderivations}
\leanchecked{BEDC.MetaCIC.substitute\_preserves\_typing\_lam\_if\_subderivations}

The closed binder-domain surface removes the atom-shape restriction when every
binder domain in the source derivation is closed at its local depth. In that
surface, removing the substituted hypothesis preserves the represented
derivation, and closedness makes substitution definitionally inert on both the
term and its type. This gives a direct closed-domain substitution-preservation
theorem for the represented typing judgment.
\leandef{BEDC.MetaCIC.ClosedBinderDomainTyping}
\leandef{BEDC.MetaCIC.ClosedBinderDomainsSubstitutionSurface}
\leanchecked{BEDC.MetaCIC.substitute\_preserves\_typing\_closed\_binder\_domains}

\paragraph{Beta-substitution cases.}
The clean beta-substitution contract is
$\mathrm{BetaSubstitutionPreservation}$: a typed body under the shifted
domain context remains typed after substituting a typed argument into both body
and codomain. The sort and variable cases are fully closed by direct inversion
on the body derivation.
\leanchecked{BEDC.MetaCIC.betaSubstitutionPreservation\_sort\_var}
The depth-one form supplies the same atom-shaped argument inside an additional
binder frame, which is the common recursive premise used by binder bodies.
\leanchecked{BEDC.MetaCIC.betaSubstitutionPreservation\_depth\_one\_sort\_var}

Pi bodies, lambda bodies, and application bodies are then separated into
constructor-specific clean lemmas. The Pi case reconstructs a typed Pi after
cleaning the substituted domain and proving the codomain in the shifted
context.
\leanchecked{BEDC.MetaCIC.betaSubstitutionPreservation\_pi\_body}
The lambda case follows the same domain-cleaning pattern and reconstructs the
lambda rule with the body under the shifted substituted domain.
\leanchecked{BEDC.MetaCIC.betaSubstitutionPreservation\_lam\_body}
The application case factors through typed substituted function and argument
premises, then closes the result type by a shape-bounded substitute composition
equation for the application codomain.
\leanchecked{BEDC.MetaCIC.betaSubstitutionPreservation\_app\_body}

\paragraph{Parallel-reduction confluence frame.}
The confluence layer separates ordinary beta steps from a parallel reduction
relation. One-step beta embeds into the parallel relation, while reflexivity is
available for every represented term. The diamond goal is recorded as the
closed proposition $\mathrm{BetaParallelDiamond}$, and the constructor-level
join assemblers close the variable, sort, application, lambda, and Pi
component cases.
\leandef{BEDC.MetaCIC.BetaStarStep}
\leandef{BEDC.MetaCIC.BetaStarConfluent}
\leandef{BEDC.MetaCIC.BetaParallel}
\leandef{BEDC.MetaCIC.BetaParallelDiamond}
\leanvariant{BEDC.MetaCIC.betaParallel\_refl}
\leanvariant{BEDC.MetaCIC.betaStep\_to\_parallel}
\leanchecked{BEDC.MetaCIC.betaParallel\_var\_diamond}
\leanchecked{BEDC.MetaCIC.betaParallel\_sort\_diamond}
\leanchecked{BEDC.MetaCIC.betaParallel\_app\_diamond\_of\_components}
\leanchecked{BEDC.MetaCIC.betaParallel\_lam\_diamond\_of\_components}
\leanchecked{BEDC.MetaCIC.betaParallel\_pi\_diamond\_of\_components}

\paragraph{Subject-reduction assembly.}
Subject reduction is split across beta contraction and congruence rules. The
beta contraction step is the abstract interface from
$\mathrm{BetaSubstitutionPreservation}$ to the application redex typing
judgment. The congruence steps preserve typing when reduction happens in the
function, argument, lambda body, or Pi codomain position:
\leanchecked{BEDC.MetaCIC.subject\_reduction\_congApp1}
\leanchecked{BEDC.MetaCIC.subject\_reduction\_congApp2}
\leanchecked{BEDC.MetaCIC.subject\_reduction\_congLam}
\leanchecked{BEDC.MetaCIC.subject\_reduction\_congPi}

The main theorem assembles these cases by induction on the represented beta
step. It takes beta-substitution preservation and application-argument type
stability as explicit hypotheses, then returns preservation of the same
represented type across a single beta step.
\leanchecked{BEDC.MetaCIC.subject\_reduction}

The closed-term boundary is also represented explicitly. A closed lambda can
contain a beta redex whose local argument is the bound variable of the enclosing
lambda; the whole term is closed, the inner beta contraction steps under the
binder, but the contracted argument is not closed at depth zero. This records
the precise local obstruction that a closed-term subject-reduction theorem must
discharge: closedness of the outer term alone does not provide zero-depth
closedness for every local redex argument.
\leandef{BEDC.MetaCIC.closedBinderRedexTerm}
\leanchecked{BEDC.MetaCIC.closedBinderRedexTerm\_closed}
\leanchecked{BEDC.MetaCIC.closedBinderRedexTerm\_steps}
\leanchecked{BEDC.MetaCIC.closedBinderRedexTerm\_argument\_not\_closed}
\leanchecked{BEDC.MetaCIC.closed\_term\_step\_has\_unclosed\_local\_argument}
