\section*{V7 Metatheory: Case-Level Closure}\label{sec:self-comp-v7-metatheory}

The V7 MetaCIC layer isolates subject reduction into local closure contracts for
substitution, beta contraction, and congruence. The scope is deliberately
case-level: each theorem states a structurally checkable condition on the
represented syntax and typing derivation, and the final assembly records the
remaining interface hypotheses.

\paragraph{Atom-shaped binder substitution.}
Substitution preserves typing for the Pi and lambda constructors under
closedness and atom-shape hypotheses. For Pi terms, the domain and codomain
premises reduce to the sort-or-variable fragment after binder-head transport.
\leanchecked{BEDC.MetaCIC.V2.substitute\_preserves\_typing\_V2\_pi}
For lambda terms, the same pattern applies to the body under the shifted binder
context, yielding a typed substituted lambda against the substituted Pi type.
\leanchecked{BEDC.MetaCIC.V2.substitute\_preserves\_typing\_V2\_lam}

The shared binder transport step is represented explicitly as the equality
which turns substitution under a shifted closed head into the shifted
substituted head.
\leanchecked{BEDC.MetaCIC.V2.substitute\_preserves\_typing\_V2\_binder\_head\_shape}
The lower-level constructor assemblers expose the same decomposition without
the atom-shape discharge:
\leanchecked{BEDC.MetaCIC.V2.substitute\_preserves\_typing\_V2\_pi\_if\_subderivations}
\leanchecked{BEDC.MetaCIC.V2.substitute\_preserves\_typing\_V2\_lam\_if\_subderivations}

\paragraph{Beta-substitution cases.}
The clean beta-substitution contract is
$\mathrm{BetaSubstitutionPreservationV2}$: a typed body under the shifted
domain context remains typed after substituting a typed argument into both body
and codomain. The sort and variable cases are fully closed by direct inversion
on the body derivation.
\leanchecked{BEDC.MetaCIC.V2.betaSubstitutionPreservationV2\_sort\_var}
The one-deep version supplies the same atom-shaped argument inside an additional
binder frame, which is the common recursive premise used by binder bodies.
\leanchecked{BEDC.MetaCIC.V2.betaSubstitutionPreservationV2\_depth\_one\_sort\_var}

Pi bodies, lambda bodies, and application bodies are then separated into
constructor-specific clean lemmas. The Pi case reconstructs a typed Pi after
cleaning the substituted domain and proving the codomain in the shifted
context.
\leanchecked{BEDC.MetaCIC.V2.betaSubstitutionPreservationV2\_pi\_body}
The lambda case follows the same domain-cleaning pattern and reconstructs the
lambda rule with the body under the shifted substituted domain.
\leanchecked{BEDC.MetaCIC.V2.betaSubstitutionPreservationV2\_lam\_body}
The application case factors through typed substituted function and argument
premises, then closes the result type by a shape-bounded substitute composition
equation for the application codomain.
\leanchecked{BEDC.MetaCIC.V2.betaSubstitutionPreservationV2\_app\_body}

\paragraph{Subject-reduction assembly.}
Subject reduction is split across beta contraction and congruence rules. The
beta contraction step is the abstract interface from
$\mathrm{BetaSubstitutionPreservationV2}$ to the application redex typing
judgment. The congruence steps preserve typing when reduction happens in the
function, argument, lambda body, or Pi codomain position:
\leanchecked{BEDC.MetaCIC.V2.subject\_reduction\_V2\_congApp1}
\leanchecked{BEDC.MetaCIC.V2.subject\_reduction\_V2\_congApp2}
\leanchecked{BEDC.MetaCIC.V2.subject\_reduction\_V2\_congLam}
\leanchecked{BEDC.MetaCIC.V2.subject\_reduction\_V2\_congPi}

The main theorem assembles these cases by induction on the represented beta
step. It takes beta-substitution preservation and application-argument type
stability as explicit hypotheses, then returns preservation of the same
represented type across a single beta step.
\leanchecked{BEDC.MetaCIC.V2.subject\_reduction\_V2}
