\section{Bounds: What This Surface Does Not Claim}\label{sec:self-comp-not-claimed}

The self-compilation surface is bounded by explicit negative claims. These
bounds are part of the theory, because without them a reflection result can be
misread as a stronger foundational theorem.

First, BEDC does not claim L4a. Since the formalization sits inside the host
Calculus of Inductive Constructions, an internal axiom-free theorem asserting
the relevant complete truth, soundness, or consistency of that same host-scale
calculus is blocked by the Godel-Tarski boundary. Tarski undefinability blocks
an internal truth predicate with the required global behavior. Godel's second
incompleteness theorem blocks a sufficiently strong, consistent system from
proving its own consistency in the corresponding internal form.

Second, BEDC rejects L4c. The paper's governance discipline keeps theory
closure and verification status as independent axes. The policy is recorded in
\autoref{ch:theory-amendment-policy}. A scoped paper theorem can be paired with
a Lean target, a checked Lean theorem can sit inside a deliberately narrow
paper scope, and a bridge can be absent even when both coordinates are clear.
This is not a defect in the surface. It is the mechanism that prevents a proof
marker from becoming a claim of public mathematical closure.

Third, TM simulation does not subsume CIC reconstruction. A simulator can make
behavioral statements about execution traces. Such statements have the shape of
finite runs, accept states, and observed outputs. CIC reconstruction gives
structural statements about syntax, contexts, typing, and reduction. These
objects can occur under universal quantifiers and induction principles:

$$
\begin{aligned}
\forall d,\ \mathrm{TypingDerivation}(d)
  \longrightarrow \mathrm{Property}(d).
\end{aligned}
$$

That judgmental form is not the same as predicting that a machine accepts a
file. Both surfaces are useful, but they support different theorems.

Fourth, the reflection bridge between MetaCIC and the host kernel is outside
the present scope. A bridge would have to relate represented judgments to actual
host elaboration or kernel checking with enough precision to transfer
meaningful proof obligations. That is a V2-and-beyond metatheoretic program.
The present surface records the construction and boundary of represented
syntax, represented typing, finite checked manifest entries, and external
paper-Lean audits.

These bounds fix the intended reading. BEDC can internally carry finite checked
theorem entries, represent parts of its own kernel vocabulary, and expose
obligation packets for concrete name certificates. It cannot, from inside the
same host logic and without additional axioms, certify the global truth or
consistency of the host that checks it.
