\section{Typed Examples Gallery}\label{sec:typed-examples-gallery}

The typed examples gallery is the reader-facing index for closed-term witnesses
inside `\verb|BEDC.MetaCIC.TypedExamples|'.  It complements the representational
adequacy argument in \autoref{sec:metatheory-representational-adequacy}: the
adequacy claim explains why the first-principles substrate is the right target,
while this gallery lists the concrete closed terms whose typing or reduction
facts have been mechanized on that substrate.

\subsection{Why a gallery}\label{subsec:typed-examples-gallery-why}

`\verb|BEDC.MetaCIC|' is a first-principles substrate.  It does not inherit a
host-kernel reflection API, a built-in quotation mechanism, or a host-level
`\verb|decide|' path for typing judgments.  Each displayed typing fact is built
by an explicit chain of constructors for the object syntax, object typing
relation, and object reduction relation.  The gallery is therefore not a
convenience catalogue alone: it is the compact map of the mechanized closed-term
witnesses that exercise the representational layer.

\subsection{Sibling index}\label{subsec:typed-examples-gallery-siblings}

\begin{longtable}{p{0.23\textwidth}p{0.68\textwidth}}
\textbf{Lean sibling} & \textbf{Role} \\
\hline
`\verb|Sorts.lean|' & Sort-level and variable lookup typing examples over
small contexts. \\
`\verb|Identity.lean|' & Identity-shaped $\lambda x:T.\ x$ witnesses, dependent
identity forms, and simple projections. \\
`\verb|ConstForms.lean|' & Constant-function forms and their staged
applications. \\
`\verb|AppForms.lean|' & Application-shaped witnesses, including reduced and
unreduced forms over empty and small contexts. \\
`\verb|PiForms.lean|' & Pi-type formation and lambda terms whose types are Pi
forms. \\
`\verb|BetaRedex.lean|' & Beta-redex witnesses and corresponding `\verb|BetaStep|'
or `\verb|BetaStarStep|' instances. \\
`\verb|ChurchGallery.lean|' & Church encodings for Booleans, naturals, pairs,
and options. \\
`\verb|Polymorphic.lean|' & Pi-polymorphic identity, constant, apply, flip, and
compose forms. \\
\end{longtable}

\subsection{Mechanized witnesses}\label{subsec:typed-examples-gallery-witnesses}

\begin{longtable}{p{0.24\textwidth}p{0.36\textwidth}p{0.31\textwidth}}
\textbf{Example} & \textbf{Lean witness} & \textbf{Description} \\
\hline
Sorts & \leanvariant{BEDC.MetaCIC.var\_zero\_in\_sort\_ctx} & Variable zero in a one-sort context. \\
Sorts & \leanvariant{BEDC.MetaCIC.var\_one\_in\_double\_sort\_ctx} & Variable one in a two-sort context. \\
Sorts & \leanvariant{BEDC.MetaCIC.middle\_var\_in\_triple\_sort} & Middle variable lookup in a three-sort context. \\
Sorts & \leanvariant{BEDC.MetaCIC.deep\_var\_in\_quad\_sort} & Deep variable lookup in a four-sort context. \\
Sorts & \leanvariant{BEDC.MetaCIC.mixed\_ctx\_vars} & Variable lookup in a mixed sort-and-Pi context. \\
Sorts & \leanvariant{BEDC.MetaCIC.mixed\_ctx\_var\_zero} & Front variable lookup in a mixed context. \\
Sorts & \leanvariant{BEDC.MetaCIC.mixed\_var\_in\_three\_ctx} & Interior variable lookup in a mixed three-entry context. \\
Sorts & \leanvariant{BEDC.MetaCIC.var\_in\_quint\_sort} & Deep variable lookup in a five-sort context. \\
Identity & \leanvariant{BEDC.MetaCIC.lam\_dependent\_identity} & Dependent identity lambda. \\
Identity & \leanvariant{BEDC.MetaCIC.carrier\_identity\_in\_sort\_ctx} & Identity over a carrier variable in a sort context. \\
Identity & \leanvariant{BEDC.MetaCIC.lam\_inner\_to\_outer\_in\_double\_sort} & Lambda returning an outer variable. \\
Identity & \leanvariant{BEDC.MetaCIC.triple\_sort\_lam} & Three-level sort lambda witness. \\
Identity & \leanvariant{BEDC.MetaCIC.polymorphic\_identity} & Pi-polymorphic identity witness. \\
Identity & \leanvariant{BEDC.MetaCIC.nested\_poly\_id} & Nested polymorphic identity witness. \\
Identity & \leanvariant{BEDC.MetaCIC.lam\_constructs\_dependent\_pi} & Lambda forming a dependent Pi target. \\
Identity & \leanvariant{BEDC.MetaCIC.double\_lam\_pi\_construct} & Two-lambda Pi construction. \\
Identity & \leanvariant{BEDC.MetaCIC.first\_of\_two} & First projection over two arguments. \\
Identity & \leanvariant{BEDC.MetaCIC.second\_of\_two} & Second projection over two arguments. \\
Identity & \leanvariant{BEDC.MetaCIC.ignore\_arg} & Lambda that ignores an argument. \\
Identity & \leanvariant{BEDC.MetaCIC.double\_poly\_first} & Polymorphic first projection. \\
Identity & \leanvariant{BEDC.MetaCIC.second\_proj} & Second projection witness. \\
ConstForms & \leanvariant{BEDC.MetaCIC.app\_const\_sort\_in\_empty\_ctx} & Constant sort function applied in the empty context. \\
ConstForms & \leanvariant{BEDC.MetaCIC.const\_sort\_app} & Application of a constant sort function. \\
ConstForms & \leanvariant{BEDC.MetaCIC.double\_lam\_const} & Two-argument constant lambda. \\
ConstForms & \leanvariant{BEDC.MetaCIC.double\_lam\_const\_first\_app} & First application of a two-argument constant lambda. \\
ConstForms & \leanvariant{BEDC.MetaCIC.double\_lam\_const\_repeated\_app} & Repeated application of a two-argument constant lambda. \\
ConstForms & \leanvariant{BEDC.MetaCIC.twice\_applied\_const} & Fully applied constant function witness. \\
ConstForms & \leanvariant{BEDC.MetaCIC.first\_arg\_proj} & First-argument projection as a constant form. \\
ConstForms & \leanvariant{BEDC.MetaCIC.second\_arg\_proj} & Second-argument projection as a constant form. \\
ConstForms & \leanvariant{BEDC.MetaCIC.const\_sort\_1\_applied} & One-step application of a sort constant. \\
ConstForms & \leanvariant{BEDC.MetaCIC.applied\_const\_sort} & Applied constant-sort witness. \\
AppForms & \leanvariant{BEDC.MetaCIC.id\_applied\_to\_sort\_type} & Type of identity applied to sort. \\
AppForms & \leanvariant{BEDC.MetaCIC.poly\_id\_at\_sort\_full} & Fully instantiated polymorphic identity at sort. \\
AppForms & \leanvariant{BEDC.MetaCIC.poly\_id\_double\_app} & Polymorphic identity with two applications. \\
AppForms & \leanvariant{BEDC.MetaCIC.poly\_id\_to\_pi\_type} & Polymorphic identity applied to a Pi type. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_id\_sort\_in\_empty\_ctx} & Identity application in the empty context. \\
AppForms & \leanvariant{BEDC.MetaCIC.id\_to\_id\_in\_empty} & Identity function applied to identity in the empty context. \\
AppForms & \leanvariant{BEDC.MetaCIC.applied\_pi\_constructor\_in\_empty} & Applied Pi constructor in the empty context. \\
AppForms & \leanvariant{BEDC.MetaCIC.applied\_pi\_constructor\_in\_empty\_result\_eq} & Result equality for the applied Pi constructor. \\
AppForms & \leanvariant{BEDC.MetaCIC.id\_applied\_to\_pi} & Identity applied to a Pi expression. \\
AppForms & \leanvariant{BEDC.MetaCIC.id\_applied\_pi\_value} & Value witness for identity applied to Pi. \\
AppForms & \leanvariant{BEDC.MetaCIC.id\_applied\_to\_pi\_result\_eq} & Result equality for identity applied to Pi. \\
AppForms & \leanvariant{BEDC.MetaCIC.id\_on\_pi\_sort\_sort} & Identity on the sort-to-sort Pi type. \\
AppForms & \leanvariant{BEDC.MetaCIC.pi\_value\_id} & Identity value for a Pi-shaped term. \\
AppForms & \leanvariant{BEDC.MetaCIC.proj\_for\_pi\_arg} & Projection with a Pi argument. \\
AppForms & \leanvariant{BEDC.MetaCIC.identity\_on\_pi\_type} & Identity over a Pi type. \\
AppForms & \leanvariant{BEDC.MetaCIC.id\_for\_pi\_applied} & Applied identity for a Pi argument. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_id\_var\_in\_sort\_ctx} & Identity applied to a variable in a sort context. \\
AppForms & \leanvariant{BEDC.MetaCIC.dep\_id\_applied\_to\_arg\_in\_sort\_ctx} & Dependent identity applied to a parameter in a sort context. \\
AppForms & \leanvariant{BEDC.MetaCIC.dep\_id\_applied\_to\_arg\_result\_in\_sort\_ctx} & Result typing for dependent identity application. \\
AppForms & \leanvariant{BEDC.MetaCIC.applied\_dep\_id\_in\_double\_sort\_ctx} & Applied dependent identity in a two-sort context. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_with\_pi\_context} & Application in a context containing a Pi type. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_pi\_var\_to\_sort} & Pi variable applied to sort. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_pi\_function} & Application of a Pi-typed function. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_pi\_ctx\_to\_sort} & Pi-context application targeting sort. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_two\_pi\_vars} & Application between two Pi-context variables. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_pi\_deep\_var} & Application involving a deeper Pi variable. \\
AppForms & \leanvariant{BEDC.MetaCIC.apply\_function\_arg\_in\_empty} & Function-argument application in the empty context. \\
AppForms & \leanvariant{BEDC.MetaCIC.app\_id\_pi\_var\_sort\_in\_sort\_ctx} & Identity application over a Pi variable in a sort context. \\
AppForms & \leanvariant{BEDC.MetaCIC.pi\_var\_sort\_then\_sort\_id\_app\_in\_sort\_ctx} & Pi variable followed by sort identity application. \\
AppForms & \leanvariant{BEDC.MetaCIC.apply\_function\_arg\_in\_value\_ctx} & Function-argument application in a value context. \\
AppForms & \leanvariant{BEDC.MetaCIC.dep\_pi\_app} & Dependent Pi application. \\
AppForms & \leanvariant{BEDC.MetaCIC.apply\_function\_arg} & Function-argument application witness. \\
AppForms & \leanvariant{BEDC.MetaCIC.applied\_poly\_id} & Applied polymorphic identity witness. \\
PiForms & \leanvariant{BEDC.MetaCIC.two\_sort\_vars} & Pair of sort variables in context. \\
PiForms & \leanvariant{BEDC.MetaCIC.lam\_pi\_var0\_var1} & Lambda whose type is a Pi over variables zero and one. \\
PiForms & \leanvariant{BEDC.MetaCIC.lam\_pi\_var\_var} & Lambda over variable-shaped Pi data. \\
PiForms & \leanvariant{BEDC.MetaCIC.pi\_var\_sort\_in\_sort\_ctx} & Pi formation from a variable to sort. \\
PiForms & \leanvariant{BEDC.MetaCIC.pi\_using\_arrow\_in\_ctx} & Arrow-like Pi formation in context. \\
PiForms & \leanvariant{BEDC.MetaCIC.pi\_sort\_sort\_in\_empty\_ctx} & Sort-to-sort Pi in the empty context. \\
PiForms & \leanvariant{BEDC.MetaCIC.pi\_sort\_dependent} & Dependent Pi over sort. \\
PiForms & \leanvariant{BEDC.MetaCIC.nested\_pi\_sort\_sort} & Nested sort-to-sort Pi. \\
PiForms & \leanvariant{BEDC.MetaCIC.triple\_pi\_sort} & Three-level Pi over sort. \\
PiForms & \leanvariant{BEDC.MetaCIC.nested\_pi\_dep\_in\_empty} & Nested dependent Pi in the empty context. \\
PiForms & \leanvariant{BEDC.MetaCIC.nested\_pi\_var\_sort} & Nested Pi using a variable and sort. \\
PiForms & \leanvariant{BEDC.MetaCIC.map\_pi\_in\_sort\_ctx} & Map-like Pi in a sort context. \\
PiForms & \leanvariant{BEDC.MetaCIC.triple\_lam\_pi\_construction} & Three-lambda Pi construction. \\
PiForms & \leanvariant{BEDC.MetaCIC.double\_poly\_pi} & Double-polymorphic Pi witness. \\
PiForms & \leanvariant{BEDC.MetaCIC.double\_arrow\_in\_sort} & Double-arrow Pi in sort. \\
PiForms & \leanvariant{BEDC.MetaCIC.pi\_var\_var\_in\_quad\_sort} & Pi over variables in a four-sort context. \\
PiForms & \leanvariant{BEDC.MetaCIC.nested\_pi\_chain} & Chain of nested Pi forms. \\
PiForms & \leanvariant{BEDC.MetaCIC.pi\_function\_to\_sort\_in\_empty} & Function-to-sort Pi in the empty context. \\
PiForms & \leanvariant{BEDC.MetaCIC.function\_of\_function} & Function-of-function Pi witness. \\
PiForms & \leanvariant{BEDC.MetaCIC.nested\_shifted\_pi\_in\_sort} & Nested shifted Pi in sort. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.id\_sort\_redex} & Beta step for identity at sort. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.id\_sort\_redex\_typed} & Typing fact for identity-at-sort redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.fn\_sort\_to\_sort\_redex} & Beta step for a sort-to-sort function. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.fn\_sort\_to\_sort\_redex\_typed} & Typing fact for the sort-to-sort redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.const\_sort\_redex} & Beta step for a constant sort function. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.const\_sort\_redex\_typed} & Typing fact for the constant sort redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.inner\_id\_redex} & Beta step inside an identity-shaped term. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.inner\_sort\_id\_redex} & Inner sort identity beta step. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.inner\_sort\_id\_redex\_typed} & Typing fact for the inner sort identity redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.app\_right\_id\_sort\_redex} & Beta step in the right side of an application. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.app\_right\_id\_sort\_redex\_typed} & Typing fact for the right-application redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.pi\_domain\_redex} & Beta step in a Pi domain. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.pi\_domain\_redex\_typed} & Typing fact for the Pi-domain redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.pi\_cod\_redex} & Beta step in a Pi codomain. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.pi\_cod\_redex\_typed} & Typing fact for the Pi-codomain redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.poly\_id\_two\_step\_redex} & Two-step beta reduction for polymorphic identity. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.poly\_id\_two\_step\_redex\_typed} & Typing fact for the two-step polymorphic redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.k\_sort\_partial\_redex} & Partial beta step for a sort-level K combinator. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.k\_sort\_partial\_redex\_typed} & Typing fact for the partial K redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.k\_sort\_two\_step\_redex} & Two-step beta reduction for the sort-level K combinator. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.k\_sort\_two\_step\_redex\_typed} & Typing fact for the two-step K redex. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.app\_left\_projection\_redex} & Beta step for a left projection application. \\
BetaRedex & \leanvariant{BEDC.MetaCIC.app\_left\_projection\_redex\_typed} & Typing fact for the left projection redex. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_bool\_type} & Church Boolean type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_true} & Church true term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_false} & Church false term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_nat\_type} & Church natural-number type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_zero} & Church zero term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_one} & Church one term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_nat\_type\_in\_ctx} & Church natural-number type in context. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_succ\_type} & Church successor type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_succ} & Church successor term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_identity\_type} & Church identity type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_identity} & Church identity term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_const\_type} & Church constant-function type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_const} & Church constant-function term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_bool\_elim\_sort} & Boolean eliminator over sort. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_pair\_type} & Church pair type former. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_pair\_ab\_type} & Church pair type at two arguments. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_mk\_pair\_type} & Pair constructor type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_mk\_pair} & Pair constructor term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_fst\_type} & First projection type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_fst} & First projection term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_snd\_type} & Second projection type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_snc\_type} & Constant-style helper type for the second projection. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_snd} & Second projection term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_pair\_former} & Pair type former witness. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_pair\_bool\_nat\_type} & Boolean-natural Church pair type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_option\_at\_type} & Church option type at an argument. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_option\_type} & Church option type former. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_none\_type} & None constructor type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_none} & None constructor term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_some\_type} & Some constructor type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_some} & Some constructor term. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_option\_in\_case\_ctx\_type} & Option type in a case-analysis context. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_case\_option\_type} & Option case-analysis type. \\
ChurchGallery & \leanvariant{BEDC.MetaCIC.church\_case\_option} & Option case-analysis term. \\
Polymorphic & \leanvariant{BEDC.MetaCIC.poly\_identity\_type} & Pi-polymorphic identity type. \\
Polymorphic & \leanvariant{BEDC.MetaCIC.poly\_const\_type} & Pi-polymorphic constant-function type. \\
Polymorphic & \leanvariant{BEDC.MetaCIC.poly\_apply\_type} & Pi-polymorphic apply type. \\
Polymorphic & \leanvariant{BEDC.MetaCIC.poly\_flip\_type} & Pi-polymorphic flip type. \\
Polymorphic & \leanvariant{BEDC.MetaCIC.poly\_compose\_type} & Pi-polymorphic compose type. \\
Polymorphic & \leanvariant{BEDC.MetaCIC.poly\_identity\_at\_sort\_type} & Polymorphic identity instantiated at sort. \\
\end{longtable}

\subsection{Boundary of the gallery}\label{subsec:typed-examples-gallery-boundary}

The gallery records closed-term witness patterns.  It does not claim a catalogue
of non-closed terms, although the object syntax and context machinery can state
such judgments.  It also does not present general typing in arbitrary non-empty
contexts: several witnesses use small explicit contexts, but the dominant path
for the self-compilation metatheory is the closed-term path.  Finally, it does
not claim reduction over open terms; the displayed reduction witnesses are
closed or are paired with closed typing facts where the file states them.

\subsection{Contributor discipline}\label{subsec:typed-examples-gallery-contributor}

A witness belongs in this gallery when it is a concrete `\verb|theorem|' inside
`\verb|lean4/BEDC/MetaCIC/TypedExamples/|' and its target name is stable under
`\verb|BEDC.MetaCIC|'.  Choose the sibling by term shape rather than by proof
technique: sort and variable facts go in `\verb|Sorts.lean|', identity-like
lambda terms in `\verb|Identity.lean|', constant functions in
`\verb|ConstForms.lean|', applications in `\verb|AppForms.lean|', Pi formation
in `\verb|PiForms.lean|', beta witnesses in `\verb|BetaRedex.lean|', Church
encodings in `\verb|ChurchGallery.lean|', and Pi-polymorphic combinators in
`\verb|Polymorphic.lean|'.  The paper row should use `\verb|\leanvariant|',
not `\verb|\leanchecked|', because the gallery is an index of sibling witnesses
rather than the canonical primary site for a single paper theorem.
