\section{Metatheory Milestone Consolidation}
\label{sec:metatheory-milestone-consolidation}

This section gives a single reader-facing account of the metatheory now
available around \texttt{BEDC.MetaCIC}.  The account is deliberately two-sided.
On one side it records the checked Lean surface: represented syntax, closure,
substitution, reduction, confluence components, subject reduction interfaces,
typed examples, host-gallery transport, and the $\mathsf{BHist}$ embedding.
On the other side it places that surface next to the standard textbook routes
for the Calculus of Inductive Constructions and related pure type systems.

The point of the comparison is scope control.  BEDC is not a replacement
kernel and not a full formalization of CIC.  It is a mathlib-free,
zero-axiom, zero-sorry represented calculus inside Lean 4, with enough
first-principles metatheory to support the self-compilation surface used in
this paper.  The checked pieces are meaningful because they are proved over
the represented object language itself, not imported from host conversion,
host normalization, or a library theorem about lambda calculus.

\subsection{What \texttt{BEDC.MetaCIC} Achieves}
\label{subsec:metatheory-achieves}

The represented substrate is a single-sort dependent-function core.  Its term
syntax has five constructors: sort, de Bruijn variable, application, lambda,
and Pi.  Context lookup is a first-principles list lookup.  Shift and
substitution are native recursive operations on the represented syntax, and
the closure predicate \texttt{ClosedAt} records exactly which de Bruijn
variables are in scope at a given boundary.

The substrate is shift-aware in the strict de Bruijn sense.  Descent under a
binder changes the relevant cutoff, and substitution below a binder shifts the
inserted term.  This is why closure preservation is a theorem rather than a
notation convention.  The checked closure layer says that closed terms remain
closed under shift and substitution at the relevant boundary, and that beta
reduction preserves the same closure predicate.

\leanvariant{BEDC.MetaCIC.shift\_closed}
\leanvariant{BEDC.MetaCIC.substitute\_closed}
\leanvariant{BEDC.MetaCIC.substitute\_preserves\_closed\_at}
\leanvariant{BEDC.MetaCIC.betaStep\_preserves\_closed}
\leanvariant{BEDC.MetaCIC.betaStarStep\_preserves\_closed}

These facts are not cosmetic.  They are the algebraic guardrail that keeps the
MetaCIC reduction relation inside the intended closed fragment.  In particular,
the one-step theorem covers beta contraction and all congruence constructors;
the finite-chain theorem lifts it along the represented reflexive-transitive
closure \texttt{BetaStarStep}.  Hence every finite represented beta trace
starting from a closed term remains closed at every displayed point of the
trace.

The confluence surface is split into atom results and compound-shape
assemblers.  For atoms, sort and variable sources cannot produce a genuine
fork.  Their beta-star and parallel-beta forks join at the source itself.  The
checked atom diamonds record the fully closed part of the confluence story:

\leanvariant{BEDC.MetaCIC.betaStarStep\_diamond\_sort}
\leanvariant{BEDC.MetaCIC.betaStarStep\_diamond\_var}
\leanvariant{BEDC.MetaCIC.betaParallel\_sort\_diamond}
\leanvariant{BEDC.MetaCIC.betaParallel\_var\_diamond}

For compound terms, the checked layer supplies the structural components
needed by the standard parallel-reduction path.  Application, lambda, and Pi
diamonds can be assembled from diamonds of their components.  Lambda and Pi
shape forks reduce to domain-body and domain-codomain obligations.  Application
forks are exposed by a full inversion theorem, because an application branch
may either remain an application or contract after the function side exposes a
lambda.

\leanvariant{BEDC.MetaCIC.betaParallel\_app\_diamond\_of\_components}
\leanvariant{BEDC.MetaCIC.betaParallel\_lam\_diamond\_of\_components}
\leanvariant{BEDC.MetaCIC.betaParallel\_pi\_diamond\_of\_components}
\leanvariant{BEDC.MetaCIC.betaParallel\_lam\_shape\_diamond}
\leanvariant{BEDC.MetaCIC.betaParallel\_pi\_shape\_diamond}
\leanvariant{BEDC.MetaCIC.betaParallel\_app\_full\_inv}
\leanvariant{BEDC.MetaCIC.betaParallel\_app\_shape\_diamond\_from\_substitution}
\leanvariant{BEDC.MetaCIC.betaParallel\_diamond\_from\_substitution}

The last two targets make the boundary explicit.  A full parallel diamond is
available from a substitution-compatibility hypothesis.  The Lean theorem does
not hide that hypothesis; it states exactly where the remaining algebraic
content must enter.  In textbook prose the missing law is often described as
``substitution commutes with residual reduction.''  In this substrate it must
be a concrete law about \texttt{substitute 0} with the same shifts and cutoffs
used by \texttt{BEDC.MetaCIC.substitute}.

Subject reduction has a similarly explicit shape.  The central theorem is a
hypothesis-based theorem over the represented typing and beta-step relations.
Its beta case uses the beta-substitution-preservation interface; its
congruence cases use the application-argument and binder-domain stability
interfaces.  This is stronger than a mere statement of intent, because the
ordinary beta, app, lambda, and Pi cases are checked as Lean theorems over the
object calculus.

\leanvariant{BEDC.MetaCIC.subject\_reduction\_beta}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congApp1}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congApp2}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congLam}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congPi}
\leanvariant{BEDC.MetaCIC.subject\_reduction}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_retype}
\leanstmt{BEDC.MetaCIC.BetaSubstitutionPreservation}
\leanstmt{BEDC.MetaCIC.AppArgTypeStable}
\leanstmt{BEDC.MetaCIC.LamDomainSubjectReduction}
\leanstmt{BEDC.MetaCIC.PiDomainSubjectReduction}

The subject-reduction theorem should be read as a precise local theorem, not
as a disguised claim that all standard preservation obligations have been
discharged.  The three interfaces identify the required stability facts.  The
closed-term path is also constrained by the checked obstruction showing that a
closed outer term may contain a locally open redex argument when the redex is
examined under binders.

\leanvariant{BEDC.MetaCIC.closedBinderRedexTerm\_closed}
\leanvariant{BEDC.MetaCIC.closedBinderRedexTerm\_steps}
\leanvariant{BEDC.MetaCIC.closedBinderRedexTerm\_argument\_not\_closed}
\leanvariant{BEDC.MetaCIC.closed\_term\_step\_has\_unclosed\_local\_argument}

The normalization surface is intentionally modest.  Operationally, the paper
uses a bounded normalizer reading: a fuel-indexed host computation follows a
chosen finite beta path, and closure preservation is carried by the checked
finite-trace theorems.  The checked atom-level termination content is the
normal-form behavior of sort and closed variable atoms: no beta successor can
start from such a source, and a typed closed atom is therefore beta-inert.

\leanvariant{BEDC.MetaCIC.sort\_no\_beta}
\leanvariant{BEDC.MetaCIC.closed\_var\_no\_beta}
\leanvariant{BEDC.MetaCIC.closed\_atom\_normal\_form}

This is the atom-level strong-normalization reading used here: for atom
sources there is no first step, so every beta path is already finished.  It is
not a global strong-normalization theorem for all well-typed represented terms.
The reducibility-candidates route is therefore a frontier for the represented
calculus, not a completed adequacy theorem in the Lean surface.

The typed examples gallery gives concrete pressure on the syntax, typing, and
reduction definitions.  It contains Church-encoded Booleans, naturals, pairs,
and options; polymorphic identity, constant, flip, and compose forms; and a
family of beta-redex witnesses.  The examples are not produced by quotation
from Lean expressions.  They are represented terms whose typing and reduction
evidence is constructed inside \texttt{BEDC.MetaCIC}.

\leanvariant{BEDC.MetaCIC.church\_bool\_type}
\leanvariant{BEDC.MetaCIC.church\_true}
\leanvariant{BEDC.MetaCIC.church\_false}
\leanvariant{BEDC.MetaCIC.church\_nat\_type}
\leanvariant{BEDC.MetaCIC.church\_zero}
\leanvariant{BEDC.MetaCIC.church\_one}
\leanvariant{BEDC.MetaCIC.church\_pair\_type}
\leanvariant{BEDC.MetaCIC.church\_mk\_pair}
\leanvariant{BEDC.MetaCIC.church\_option\_type}
\leanvariant{BEDC.MetaCIC.church\_none}
\leanvariant{BEDC.MetaCIC.church\_some}
\leanvariant{BEDC.MetaCIC.poly\_identity\_type}
\leanvariant{BEDC.MetaCIC.poly\_const\_type}
\leanvariant{BEDC.MetaCIC.poly\_flip\_type}
\leanvariant{BEDC.MetaCIC.poly\_compose\_type}
\leanvariant{BEDC.MetaCIC.id\_sort\_redex}
\leanvariant{BEDC.MetaCIC.id\_sort\_redex\_typed}
\leanvariant{BEDC.MetaCIC.poly\_id\_two\_step\_redex}
\leanvariant{BEDC.MetaCIC.poly\_id\_two\_step\_redex\_typed}
\leanvariant{BEDC.MetaCIC.k\_sort\_two\_step\_redex}
\leanvariant{BEDC.MetaCIC.k\_sort\_two\_step\_redex\_typed}

The host bridge gives a second view of the same gallery.  Host-side Lean
definitions record the familiar computational behavior of identity, constant,
flip, compose, Church constructors, and selected redexes by reflexive
equalities.  The transport side then points to the represented MetaCIC
witnesses for corresponding typing and reduction facts.  This is not a kernel
soundness theorem from host elaboration to MetaCIC.  It is a checked alignment
gallery: named host examples and named represented examples are paired at the
level of concrete witnesses.

\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_identity\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_const\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_flip\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_compose\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_identity\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_const\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_flip\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_compose\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_true\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_false\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_zero\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_one\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_id\_sort\_redex\_step}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_id\_sort\_redex\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_poly\_id\_two\_step\_redex\_star}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_poly\_id\_two\_step\_redex\_well\_typed}

The $\mathsf{BHist}$ bridge connects the self-compilation substrate back to the
finite-history world of BEDC.  The embedding \texttt{bhistToTerm} turns a
\texttt{BHistIdx} into a represented MetaCIC term, and the closure theorem says
that the result is closed at boundary $0$.  This is exactly the kind of bridge
needed by a closed-atom self-compilation surface: histories can be represented
as terms without opening a de Bruijn variable.

\leanvariant{BEDC.MetaCIC.BHistSubstrate.bhistToTerm\_closed}
\leanvariant{BEDC.MetaCIC.BHistSubstrate.bhistToTerm\_injective}

\subsection{Comparison with Textbook CIC Metatheory}
\label{subsec:metatheory-textbook-comparison}

The textbook metatheory of CIC is usually organized around a rich kernel with
universes, products, conversion, inductive objects, and a semantic or syntactic
normalization argument.  Coquand--Werner style presentations are commonly read
through normalization by evaluation or closely related semantic normalization
methods.  Those routes exploit a carefully chosen semantic model of terms,
types, and conversion.  BEDC takes a more direct first-principles path: it
defines the object syntax, object typing, object beta relation, and object
metatheory inside Lean 4, then proves local facts about those inductive
objects.

The difference is not merely aesthetic.  Normalization by evaluation is a
semantic proof architecture; the evaluator and reifier are part of the proof
that well-typed terms normalize.  BEDC's bounded normalizer is not such a
semantic normalization proof.  It is an operational finite approximation whose
termination comes from host fuel.  The checked theorem around it is closure
preservation along represented beta traces, not a theorem that all well-typed
represented terms normalize.

Pure type systems give another useful comparison point.  In the Barendregt
style, a calculus is presented by a set of sorts, axioms, and product rules.
The BEDC fragment can be read as a single-sort sub-PTS: it has one represented
sort, Pi formation, lambda introduction, application elimination, and explicit
beta reduction, but it does not carry a universe hierarchy, cumulativity, or
the full set of conversion principles used by CIC kernels.  The single-sort
choice keeps the object calculus small enough for mathlib-free proof from
first principles.

Reducibility candidates provide the standard Girard/Tait route to strong
normalization.  That route interprets types as sets of strongly normalizing
terms stable under reduction, then proves adequacy by induction on typing
derivations.  BEDC has the syntactic substrate needed to state this route:
represented typing, represented beta, closure, finite reduction chains, and
atom-level normal-form facts.  What is not present is the full adequacy proof:
an interpretation of every admissible represented type as a candidate and an
induction showing that every typing derivation lands in the corresponding
candidate.

The comparison therefore has a precise shape:

\begin{center}
\begin{tabular}{p{0.26\linewidth}p{0.29\linewidth}p{0.36\linewidth}}
\hline
Textbook route & Standard role & BEDC reading \\
\hline
Coquand--Werner CIC &
semantic normalization and kernel-scale conversion metatheory &
direct object-language proofs over a narrower represented calculus \\
Pure type systems &
sorts, axioms, and product rules as a parametric calculus schema &
single-sort dependent-function sub-PTS with explicit beta only \\
Tait--Martin-Lof parallel reduction &
diamond proof route for beta confluence &
atom diamonds and compound-shape assemblers, with application residuals
still isolated as substitution compatibility \\
Girard/Tait reducibility candidates &
strong-normalization adequacy by semantic interpretation of types &
frontier over the represented calculus, with atom-level normal-form facts
already checked \\
\hline
\end{tabular}
\end{center}

This reading keeps the standard references conceptually visible without
pretending that their full theorems have been imported.  The BEDC theorem names
are theorem names about the represented calculus.  They do not mention the host
kernel's own conversion relation, and they do not rely on host metatheory as a
black box.

\subsection{Frontier}
\label{subsec:metatheory-frontier}

The first frontier is the full \texttt{BetaParallel} diamond without a
closed-term precondition.  The checked theorem
\texttt{betaParallel\_diamond\_from\_substitution} identifies the exact
remaining input: parallel substitution compatibility.  Proving that input in
the present de Bruijn substrate requires a binder-aware commutation theorem for
parallel residuals and substitution.

The second frontier is the complete discharge of the three subject-reduction
hypotheses in the general form.  The theorem
\texttt{subject\_reduction} already packages the main induction once beta
substitution preservation, application-argument stability, lambda-domain
stability, and Pi-domain stability are available.  The closed-term path is
natural, but the local-redex obstruction shows why closedness alone does not
erase all binder bookkeeping.

The third frontier is a strong-normalization theorem for the represented
calculus.  The current checked facts prove that atoms are beta-inert and that
finite traces preserve closedness.  A full theorem would require an admissible
type grammar, reducibility candidates for that grammar, and an adequacy proof
over represented typing derivations.

The fourth frontier is the weak closed-term form of substitution composition.
The unrestricted zero-depth equation is refuted by a checked counterexample.
Positive shape-local facts already exist for closed sort, variable,
application, lambda-anchor, and Pi-anchor cases, but the theorem needed by the
application residual proof must be stated in the exact closed form that the
shift-aware substitution operation satisfies.

\leanvariant{BEDC.MetaCIC.substitute\_substitute\_zero\_zero\_unclosed\_counterexample}
\leanvariant{BEDC.MetaCIC.substitute\_substitute\_zero\_zero\_closed\_sort}
\leanvariant{BEDC.MetaCIC.substitute\_substitute\_zero\_zero\_closed\_var}
\leanvariant{BEDC.MetaCIC.substitute\_substitute\_zero\_zero\_closed\_app}
\leanvariant{BEDC.MetaCIC.substitute\_substitute\_zero\_zero\_lam\_closed\_anchor}
\leanvariant{BEDC.MetaCIC.substitute\_substitute\_zero\_zero\_pi\_closed\_anchor}

\subsection{Boundary Statement}
\label{subsec:metatheory-boundary-statement}

BEDC does not pursue a universe hierarchy or cumulativity in
\texttt{BEDC.MetaCIC}.  The represented calculus has a single sort and the
paper reads it as a universe-zero dependent-function core.  This excludes the
kernel-scale universe constraints and cumulativity rules that a full CIC
formalization would need.

BEDC does not pursue inductive families inside the MetaCIC substrate.  The
object language has no represented inductive declarations, constructors,
recursors, motive elaboration, or large eliminators.  Church encodings in the
typed gallery are represented terms in the dependent-function fragment, not
host inductive datatypes transported into the object calculus.

BEDC does not pursue propositional irrelevance.  The object calculus has no
separate proof-irrelevant proposition sort and no quotient by proof identity.
All checked theorems are Lean theorems about the represented syntax and
relations.

BEDC does not pursue eta-conversion.  The reduction relation is beta-only:
lambda eta and Pi eta are not reduction constructors, and the confluence and
subject-reduction surfaces are stated for the beta relation that is actually
encoded.

BEDC does not pursue pattern matching from inductive types beyond the closed
atoms and Church-encoded examples displayed in the gallery.  The object
language has no case tree language and no pattern compiler.  This keeps the
self-compilation surface tied to the finite closed-term and closed-history
bridge it needs.

\subsection{Why This Boundary}
\label{subsec:metatheory-boundary-rationale}

The first reason is axiom purity.  The development is mathlib-free and audited
against extra axioms.  In particular, the project excludes reliance on
\texttt{Classical.choice}, \texttt{Quot.sound}, and \texttt{propext} in the
checked theorem dependency chain.  That restriction rules out many convenient
shortcuts for quotienting syntax, using classical well-founded arguments, or
collapsing propositions by extensionality.  The substrate must be built from
inductive syntax, recursive functions, and explicit constructors.

The second reason is methodological.  The self-compilation chapter values
substrate coherence over maximal expressivity.  A small represented calculus
with explicit closure, substitution, beta, typing, and finite examples gives a
clear audit trail.  A larger calculus with universes, inductives, conversion,
and pattern matching would be closer to a production kernel, but it would also
move the paper away from the first-principles invariant that makes every claim
traceable to a named Lean object.

The third reason is sufficiency for the BEDC goal.  The self-compilation
surface needs closed-atom and finite-history meta-reasoning, not a full
mechanization of CIC.  Histories must embed as closed represented terms.
Gallery witnesses must exercise the dependent-function core.  Reduction traces
must preserve closedness.  Atom sources must be beta-inert.  These are exactly
the checked components listed above.  The larger textbook theorems remain the
right comparison class, but the paper's claim is intentionally narrower.

The resulting boundary is neither a defect nor a hidden theorem.  It is the
chosen contract for this represented calculus: first-principles syntax and
local metatheory, checked without additional axioms, supporting the
self-compilation layer while leaving full CIC metatheory outside the claimed
surface.
