\section{Session Closing Summary}
\label{sec:session-closing-summary}

This closing section gathers the self-compilation surface as a single
reader-facing account.  The chapter has reached a point where the
closed-term metatheory is represented inside Lean, the Church-encoded gallery
is broad enough to exercise the object calculus, and the host bridge carries
both directions of the intended comparison: ordinary Lean examples on one
side, represented MetaCIC terms and beta traces on the other.  The result is
not a full kernel story.  It is a closed, first-principles story about the
fragment that BEDC uses when it treats its finite self-description as object
language data.

The self-compilation chapter began from the L1/L4 distinction and the
Godel--Tarski boundary.  It then built the MetaCIC reconstruction as an
explicit object calculus: syntax, contexts, closure, substitution, typing,
beta reduction, finite beta chains, typed examples, bounded normalization, and
bridges from finite BEDC histories.  The present position is sharper than a
catalogue of definitions.  The calculus has closed-term preservation facts,
subject-reduction interfaces with checked positive and negative resolutions,
atom and closed-normal confluence results, candidate-based strong-normalization
witnesses for the represented gallery, a decidable checker with soundness and
completeness facts, Church-encoded data with beta laws, and HostBridge
transport facts aligning represented examples with host computation.

The common invariant behind these pieces is that BEDC does not outsource the
mathematics to a quotation facility or to mathlib.  The represented syntax is
an inductive datatype.  De Bruijn shifting and substitution are recursive
functions.  Closure, typing, beta steps, beta-star chains, parallel beta, and
conversion are object-language relations.  Every Lean target cited below lives
in this first-principles surface.  The paper therefore reads the
self-compilation chapter as a closed-term metatheory for the represented
fragment, not as a statement about Lean's host kernel.

\subsection{Mechanized Theorems Table}
\label{subsec:session-closing-mechanized-theorems}

The table records the principal theorem families used by the chapter.  Each
entry uses \verb|\leanvariant| because this section is an index of already
documented targets rather than the primary site for a single canonical paper
theorem.

\begin{longtable}{p{0.18\textwidth}p{0.31\textwidth}p{0.42\textwidth}}
\toprule
Layer & Mechanized content & Lean targets \\
\midrule
\endfirsthead
\toprule
Layer & Mechanized content & Lean targets \\
\midrule
\endhead
Substrate &
Closed terms, native substitution, shift-aware closure, and closure
preservation across beta traces. &
\leanvariant{BEDC.MetaCIC.shift\_closed}
\leanvariant{BEDC.MetaCIC.substitute\_closed}
\leanvariant{BEDC.MetaCIC.closedAt\_shift}
\leanvariant{BEDC.MetaCIC.closedAt\_substitute}
\leanvariant{BEDC.MetaCIC.substitute\_preserves\_closed\_at}
\leanvariant{BEDC.MetaCIC.betaStep\_preserves\_closed}
\leanvariant{BEDC.MetaCIC.betaStarStep\_preserves\_closed}
\\
Typing rules &
The object typing judgment, the beta-substitution interface, and shape-wise
substitution preservation for Pi, lambda, and application. &
\leanvariant{BEDC.MetaCIC.HasType}
\leanvariant{BEDC.MetaCIC.BetaSubstitutionPreservation}
\leanvariant{BEDC.MetaCIC.substitute\_preserves\_typing\_pi}
\leanvariant{BEDC.MetaCIC.substitute\_preserves\_typing\_lam}
\leanvariant{BEDC.MetaCIC.substitute\_preserves\_typing\_app\_cod\_sort\_var\_commutes}
\leanvariant{BEDC.MetaCIC.substitute\_preserves\_typing\_via\_term\_induction}
\\
Subject reduction &
The hypothesis-explicit subject-reduction theorem, its constructor cases, the
closed independent-codomain application discharge, and the checked closed
binder-domain obstructions. &
\leanvariant{BEDC.MetaCIC.subject\_reduction\_beta}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congApp1}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congApp2}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congLam}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_congPi}
\leanvariant{BEDC.MetaCIC.subject\_reduction}
\leanvariant{BEDC.MetaCIC.appArgTypeStable\_closed}
\leanvariant{BEDC.MetaCIC.subject\_reduction\_closed\_app\_independent\_codomain}
\leanvariant{BEDC.MetaCIC.not\_subject\_reduction\_closed}
\\
Confluence &
Atom diamonds, shape assemblers for compound terms, the conditional full
parallel diamond, and the unconditional closed-normal surface. &
\leanvariant{BEDC.MetaCIC.betaStarStep\_diamond\_sort}
\leanvariant{BEDC.MetaCIC.betaStarStep\_diamond\_var}
\leanvariant{BEDC.MetaCIC.betaParallel\_diamond\_sort}
\leanvariant{BEDC.MetaCIC.betaParallel\_diamond\_var}
\leanvariant{BEDC.MetaCIC.betaParallel\_app\_diamond\_of\_components}
\leanvariant{BEDC.MetaCIC.betaParallel\_lam\_diamond\_of\_components}
\leanvariant{BEDC.MetaCIC.betaParallel\_pi\_diamond\_of\_components}
\leanvariant{BEDC.MetaCIC.betaParallel\_app\_shape\_diamond\_from\_substitution}
\leanvariant{BEDC.MetaCIC.betaParallel\_diamond\_from\_substitution}
\leanvariant{BEDC.MetaCIC.betaParallel\_diamond\_closed\_normal}
\leanvariant{BEDC.MetaCIC.betaStarStep\_confluence\_closed\_normal}
\\
Strong normalization &
The reducibility vocabulary, Pi adequacy, closed candidate consequences, and
the gallery witnesses used by the closed self-compilation surface. &
\leanvariant{BEDC.MetaCIC.StrongNormalizable}
\leanvariant{BEDC.MetaCIC.Candidate}
\leanvariant{BEDC.MetaCIC.ClosedCandidate}
\leanvariant{BEDC.MetaCIC.PiCandidate}
\leanvariant{BEDC.MetaCIC.CandidateSet}
\leanvariant{BEDC.MetaCIC.candidate\_implies\_sn}
\leanvariant{BEDC.MetaCIC.closedCandidate\_implies\_sn}
\leanvariant{BEDC.MetaCIC.piCandidate\_implies\_sn}
\leanvariant{BEDC.MetaCIC.pi\_candidate\_app}
\leanvariant{BEDC.MetaCIC.PiAdequacy.piCandidate\_implies\_sn}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_candidate}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_closedCandidate}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_candidateSet}
\\
Decidable checker &
The context-sensitive executable type checker, its closed wrapper, and the
soundness and completeness theorems that connect it to the inductive typing
judgment. &
\leanvariant{BEDC.MetaCIC.inferTypeCtx}
\leanvariant{BEDC.MetaCIC.inferTypeCtxClosed}
\leanvariant{BEDC.MetaCIC.inferTypeCtx\_sound}
\leanvariant{BEDC.MetaCIC.inferTypeCtx\_complete}
\leanvariant{BEDC.MetaCIC.inferTypeCtxClosed\_sound}
\leanvariant{BEDC.MetaCIC.inferTypeCtxClosed\_complete}
\leanvariant{BEDC.MetaCIC.CheckCompleteness.inferTypeCtx\_complete\_raw}
\leanvariant{BEDC.MetaCIC.inferTypeCtx\_complete\_strict}
\\
Church gallery &
Closed represented encodings for Booleans, naturals, pairs, options, and
polymorphic combinators. &
\leanvariant{BEDC.MetaCIC.church\_bool\_type}
\leanvariant{BEDC.MetaCIC.church\_true}
\leanvariant{BEDC.MetaCIC.church\_false}
\leanvariant{BEDC.MetaCIC.church\_nat\_type}
\leanvariant{BEDC.MetaCIC.church\_zero}
\leanvariant{BEDC.MetaCIC.church\_one}
\leanvariant{BEDC.MetaCIC.church\_succ}
\leanvariant{BEDC.MetaCIC.church\_pair\_type}
\leanvariant{BEDC.MetaCIC.church\_mk\_pair}
\leanvariant{BEDC.MetaCIC.church\_fst}
\leanvariant{BEDC.MetaCIC.church\_snd}
\leanvariant{BEDC.MetaCIC.church\_option\_type}
\leanvariant{BEDC.MetaCIC.church\_none}
\leanvariant{BEDC.MetaCIC.church\_some}
\leanvariant{BEDC.MetaCIC.church\_case\_option}
\leanvariant{BEDC.MetaCIC.poly\_identity\_type}
\leanvariant{BEDC.MetaCIC.poly\_compose\_type}
\\
Algebraic laws &
Beta-star laws for Church Boolean projections, Church numeral application,
polymorphic identity, and pair selection. &
\leanvariant{BEDC.MetaCIC.church\_true\_proj}
\leanvariant{BEDC.MetaCIC.church\_false\_proj}
\leanvariant{BEDC.MetaCIC.church\_zero\_apply}
\leanvariant{BEDC.MetaCIC.church\_one\_apply}
\leanvariant{BEDC.MetaCIC.poly\_identity\_apply}
\leanvariant{BEDC.MetaCIC.church\_pair\_value\_to\_selector}
\\
Church natural recursion &
Closed successor and addition facts for represented Church naturals, including
successor application, zero-left addition, addition application, and the
successor-left addition law. &
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_succ\_closed}
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_add\_type}
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_succ\_iter}
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_succ\_zero\_conv}
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_succ\_zero\_to\_one}
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_add\_zero}
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_add\_apply}
\leanvariant{BEDC.MetaCIC.ChurchNatRec.church\_add\_succ\_left}
\\
HostBridge &
Host-side beta equalities, represented typing transport, represented beta
transport, and bounded-normalizer equations for the same finite examples. &
\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_identity\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_const\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_church\_true\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.Host.host\_church\_zero\_beta}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_identity\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_true\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_zero\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_pair\_type\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_church\_option\_type\_well\_typed}
\leanvariant{BEDC.HostBridge.MetaCICTransport.transport\_poly\_id\_two\_step\_redex\_star}
\leanvariant{BEDC.HostBridge.normalize\_church\_true\_apply}
\leanvariant{BEDC.HostBridge.normalize\_church\_zero\_apply}
\\
Beta conversion &
Symmetric join-based conversion, constructors from beta-star and beta-step,
conditional transitivity, closed-normal transitivity, equality of closed
normal forms, and a closed lambda-domain obstruction to a blanket typing
invariance statement. &
\leanvariant{BEDC.MetaCIC.BetaConv}
\leanvariant{BEDC.MetaCIC.BetaConv.refl}
\leanvariant{BEDC.MetaCIC.BetaConv.symm}
\leanvariant{BEDC.MetaCIC.BetaConv.of\_betaStar\_left}
\leanvariant{BEDC.MetaCIC.BetaConv.of\_betaStep\_left}
\leanvariant{BEDC.MetaCIC.BetaConv.trans\_of\_confluence}
\leanvariant{BEDC.MetaCIC.BetaConv.trans\_closed\_normal\_middle}
\leanvariant{BEDC.MetaCIC.BetaConv\_normal\_forms\_equal\_closed}
\leanvariant{BEDC.MetaCIC.BetaConv\_closed\_lam\_domain\_type\_obstruction}
\leanvariant{BEDC.MetaCIC.not\_HasType\_BetaConv\_invariant\_closed}
\\
\bottomrule
\end{longtable}

\subsection{How to Read the Table}
\label{subsec:session-closing-table-reading}

The table is deliberately organized by proof pressure rather than by file
path.  A reader who starts from the substrate rows sees the object calculus
as a small de Bruijn machine: terms are built by constructors, contexts are
lists, closure is a boundary predicate, and substitution is the operation that
must respect the boundary.  This is the layer that prevents later examples
from becoming informal syntax diagrams.  The object calculus has to preserve
its own scope before any self-compilation claim can use it.

The typing and subject-reduction rows then show how much of the ordinary
metatheory is available at the represented level.  The theorem named
\texttt{subject\_reduction} is intentionally hypothesis-explicit.  It is not
a paper promise that all conversion-sensitive facts hold automatically.  It
is a Lean theorem that lists the required stability interfaces and proves the
constructor cases once those interfaces are supplied.  The closed
independent-codomain theorem is the positive closed case used by the gallery.
The negative closed binder-domain targets explain why the paper does not
silently strengthen the theorem beyond what the represented calculus proves.

The confluence row has the same discipline.  The atom and closed-normal
targets are unconditional.  The application and full-diamond targets expose a
substitution-compatibility premise.  This matters because the self-compilation
chapter uses confluence where its sources are atom-shaped, closed-normal, or
part of the finite gallery.  It does not need to pretend that every
application residual of the represented calculus has been globally joined.
The row therefore records both usable theorem content and the exact algebraic
frontier.

The strong-normalization row should also be read as a scoped result.  The
project has a robust vocabulary of candidates, closed candidates, Pi
candidates, neutral normal forms, and closed typed candidate consequences.
That vocabulary is sufficient for the gallery witnesses and for the
closed-term termination claims made in the chapter.  It is not a semantic
normalization theorem for every well-typed represented term.  This distinction
keeps the paper aligned with its Lean surface: the file names and theorem
names show candidate adequacy where it is actually proved, not where a
textbook proof might eventually go.

The decidable-checker row is the executable counterpart to the inductive
typing relation.  It closes a practical loop: the chapter can present a
represented term, cite an inductive typing witness, and also cite a recursive
checker whose soundness and completeness connect computation back to
\texttt{HasType}.  This is one of the reasons the self-compilation surface is
not merely philosophical.  The represented fragment can be used as data, and
the project has a checked path for recognizing its closed typed examples.

The Church gallery and HostBridge rows give the computational content of the
chapter.  Church Booleans, naturals, pairs, options, and polymorphic
combinators are familiar enough to act as inspection points.  If the
represented calculus mishandled binders, substitution, application, or
closedness, these examples would be where the defect becomes visible.  The
host bridge then places those represented examples next to ordinary host Lean
functions.  The bridge does not collapse the two layers; it gives a finite
alignment of examples across them.

The BetaConv row is a useful final row because it shows how the chapter treats
conversion.  Conversion is represented as a common-join relation over
\texttt{BetaStarStep}.  Reflexivity and symmetry are immediate from that
definition.  Transitivity is available under named confluence conditions and
under the closed-normal middle case.  The closed lambda-domain obstruction
prevents the paper from claiming a blanket typing-invariance theorem for
closed conversion.  Thus even the conversion layer follows the same pattern:
state the relation, prove the stable facts, and name the obstruction where
the stronger reading fails.

\subsection{Closed Surface}
\label{subsec:session-closing-closed-surface}

The closed surface consists of the parts of the chapter that can be read
without an unproved paper-side metatheoretic promise.  The first closed part
is the de Bruijn substrate.  The calculus does not identify closedness with a
typographic convention about missing variable names.  It proves that the
recursive operations respect the boundary they are meant to respect.  This is
the algebra behind every later finite evaluator trace: once a term is closed
at boundary $0$, beta contraction and beta congruence cannot manufacture a
free represented variable.

The second closed part is the subject-reduction interface.  The central
theorem states the exact hypotheses needed for displayed-type preservation
along one beta step.  The beta case and congruence cases are checked directly.
Inside the closed empty-context surface, the application-argument stability
interface is discharged for independent codomains.  The two binder-domain
interfaces are not swept into prose: Lean supplies closed counterexamples
showing that lambda-domain and Pi-domain blanket readings are false as stated.
This gives the chapter a stronger boundary than an informal preservation
paragraph would give.  It says what works, what does not work, and which
object-language witnesses enforce the distinction.

The third closed part is confluence at the level needed by the current
self-compilation reading.  Atom sources have no genuine beta forks.  Closed
normal sources have immediate joins.  Compound terms have shape assemblers,
and the full parallel diamond is available from the named substitution
compatibility condition.  The confluence story is therefore not hidden behind
a universal Church--Rosser slogan.  It is a structured surface: atom results,
shape results, closed-normal results, and one explicit algebraic frontier for
application residuals.

The fourth closed part is normalization for the represented gallery.  The
chapter uses strong-normalization witnesses and candidate structures, not a
global theorem that every closed well-typed represented term normalizes.
Sorts, variables, neutral applications, lambdas, Pis, Church Booleans, Church
naturals, identity-shaped terms, and selected closed terms carry the witnesses
needed by the paper.  The main practical fact is enough for the BEDC surface:
the concrete represented programs used as examples come with closed typing,
finite beta traces, or candidate-style termination evidence at the exact
places where termination is cited.

The fifth closed part is the executable checker.  The checker is not an
oracle.  It is a recursive function whose result is connected back to
\texttt{HasType}.  Soundness says that a returned type is justified by the
inductive typing judgment.  Completeness says that a derivable term is
accepted by the checker at the displayed type.  The closed wrapper specializes
that story to the empty-context surface used by the chapter.  This makes the
gallery simultaneously human-readable and executable: a represented term can
be shown in the paper, typed by an inductive proof, and checked by the
decidable surface.

The sixth closed part is the Church gallery.  The gallery covers Boolean
choice, natural zero and one, successor, pairs, options, and polymorphic
combinators.  Its laws are beta-star laws over represented terms, not
host-level reductions pasted into prose.  The natural recursion surface closes
successor and addition, including the relation between successor of zero and
one, addition by zero on the left, application of addition, and the
successor-left law.  Multiplication and exponentiation are not cited here as
mechanized targets because no Lean target with those names is present in the
audited surface.

The seventh closed part is HostBridge.  The bridge has two readings.  On the
host side, ordinary Lean functions compute by reflexivity.  On the represented
side, the corresponding MetaCIC terms have typing witnesses and beta traces.
The bridge does not claim that host Lean elaboration is reflected into
MetaCIC.  It provides a checked finite transport gallery, large enough to say
that the same examples that compute in the host also exist as represented
object-language terms inside BEDC.

\subsection{Open Frontier}
\label{subsec:session-closing-open-frontier}

The open frontier is equally important to the chapter's meaning.  The first
frontier is open-term metatheory across binders.  The closed empty-context
surface is robust, but closedness at the outer boundary does not erase the
local obligations created below lambdas and Pis.  The checked binder-domain
counterexamples show exactly why.  A stronger theorem would need a transport
discipline for binder contexts and displayed codomains, not merely a stronger
wording of the closed theorem.

The second frontier is full confluence for \texttt{BetaStarStep} beyond the
atom and closed-normal shapes.  The atom diamonds are complete for atom
sources, and the compound machinery exposes the right structure, but a full
unconditional Church--Rosser result needs the remaining substitution
compatibility law for application residuals.  The chapter therefore treats
\texttt{betaParallel\_diamond\_from\_substitution} as a conditional theorem,
not as a completed global confluence theorem.

The third frontier is the rest of Church natural arithmetic.  Successor and
addition are represented and mechanized.  The present paper surface does not
cite multiplication or exponentiation targets because the audited Lean tree
does not contain them.  Those operations fit the same object-language style,
but the closing account reports only the checked targets that the audit can
find.

The fourth frontier is the full host-kernel feature set: universe hierarchy,
inductive families, propositional irrelevance, eta-conversion, cumulativity,
quotients, and proof-irrelevant conversion.  None of these is part of the
present \texttt{BEDC.MetaCIC} scope.  The calculus is a universe-$0$,
beta-only, single-sort dependent-function fragment.  This restriction is not
an omission to hide.  It is what keeps the formalization mathlib-free and
axiom-free while still covering the represented terms used by the
self-compilation story.

\subsection{Why This Surface Closes Here}
\label{subsec:session-closing-why-close}

This is the correct closing point because the closed-term metatheory now
covers the substance of BEDC's self-compilation surface.  The paper needs a
finite represented syntax, a checked closure discipline, a typing relation,
beta traces, a bounded evaluator, examples that exercise dependent functions,
Church-encoded data, and a bridge to ordinary host examples.  Those pieces are
present.  Their Lean targets are visible.  Their restrictions are visible as
well.

The zero-axiom invariant is central to the interpretation.  BEDC's MetaCIC
surface is not merely constructive in prose.  It avoids project axioms, mathlib
imports, sorry placeholders, and standard-library axiom dependencies in the
validated discipline of the project.  In that sense the represented
metatheory sits in the same strict constructive class that one expects from a
Brouwer or Bishop reading: theorems are derived from inductive definitions,
recursive functions, structures, and prior theorems, not from an external
logical extension.

The practical consequence is that the chapter can stop treating
self-compilation as a metaphor.  A finite BEDC history can be embedded as a
closed represented term.  A represented term can be typed.  Finite represented
beta traces can be checked.  Closedness is preserved along those traces.
Representative host computations have corresponding represented transport
witnesses.  The remaining task line is therefore not to argue again that
reflection is possible in principle.  It is to extend the $\mathsf{BHist}$
substrate bridge from closed atoms toward self-application while preserving
the same audit discipline.

\subsection{Forward-Looking Summary}
\label{subsec:session-closing-forward-looking}

The next self-compilation work line is not a broader claim about every CIC
feature.  It is a deeper bridge from BEDC's finite-history substrate into the
represented closed-term calculus.  The current \texttt{BHistSubstrate}
embedding already shows that a history index can be turned into a closed
MetaCIC term and that the embedding is injective.  The natural continuation
is to give that embedding more semantic load: histories should not only enter
the represented syntax as atoms, but should participate in typed represented
programs that describe their own admissible transformations.

That direction keeps the chapter's scale under control.  Instead of expanding
the object calculus toward all of Lean, the project can ask a narrower
question: which additional finite BEDC structures must be represented so that
self-application is no longer merely a host-side explanation?  The answer is
likely to involve typed encodings of package signatures, bridge certificates,
and closure-preserving transformations between history-shaped terms.  Each
candidate should enter by the same route used here: define the represented
object, prove closure, prove typing, give finite beta behavior where
computation is claimed, and expose every remaining hypothesis as a named Lean
target.

The closed-term metatheory is already enough to support that route.  It gives
the low-level guarantee that represented self-application does not lose the
boundary condition.  It gives a subject-reduction theorem whose hypotheses
tell the project which typing interfaces must be supplied.  It gives a
confluence surface for the atom and closed-normal cases likely to appear in
finite certificate encodings.  It gives candidate and strong-normalization
witnesses for the small functional programs used as examples.  It gives an
executable checker for recognizing the typed fragment.  Those are the
ingredients needed for a disciplined expansion of the $\mathsf{BHist}$ bridge,
provided each additional represented object remains inside the same audit
rules.

The Church gallery suggests a useful design style for that expansion.  The
gallery does not begin with a universal theorem about all data encodings.  It
starts with concrete encodings whose laws are inspectable.  Booleans choose,
naturals apply successors, pairs feed a selector, options choose between a
default and a branch, and polymorphic functions exercise Pi structure.  A
self-application bridge can follow the same method: begin with finite,
closed, typed objects whose behavior can be stated as beta-star or BetaConv
laws, then use the resulting library as the surface that higher-level BEDC
claims cite.

HostBridge also points to the right discipline.  The host layer is valuable
because it gives ordinary Lean computations that readers can recognize.  The
represented layer is valuable because it proves that corresponding examples
exist inside the object calculus.  Future bridge work should preserve that
separation.  A host computation can guide the example, but the represented
term must carry its own typing and reduction evidence.  A host theorem can
explain the expected behavior, but the paper-side claim should cite the
MetaCIC target that realizes the behavior in the represented language.

The open-term frontier should be approached only when the closed bridge
requires it.  The binder-domain counterexamples show that open contexts are
not a matter of adding a quantifier to closed theorems.  They require a
context-transport account that respects shifted domains and displayed
codomains.  If self-application can be expressed through closed certificate
objects and closed transformations, the project should keep using that route.
If a later certificate necessarily crosses binders, the theorem statement
should expose the transport structure directly rather than hiding it behind a
closedness hypothesis.

The same caution applies to full confluence.  A complete Church--Rosser
theorem would be valuable, but the chapter already identifies the exact
missing algebraic law.  The correct next theorem would be the substitution
compatibility needed by application residuals, stated over the actual
\texttt{substitute} and \texttt{shift} functions of the represented calculus.
Once that law is available, the existing conditional diamond target provides
the route to the stronger result.  Until then, the paper should continue to
cite atom, shape, closed-normal, and conditional confluence targets with their
actual scopes.

The arithmetic frontier is similarly concrete.  Successor and addition are
mechanized for Church naturals.  Multiplication and exponentiation should be
added only when their represented terms, closure facts, typing facts, and
beta laws exist in Lean.  The present closing section therefore treats them
as mathematical next objects, not as paper facts.  This is not a weakness of
the self-compilation chapter; it is the rule that keeps the chapter
audit-clean.

In short, the forward path is to make self-application less metaphorical while
keeping the calculus small.  Extend the finite-history bridge.  Add
represented certificate programs only when their closed typing and beta
behavior are checked.  Preserve the distinction between host computation and
represented computation.  Treat open binders, full confluence, richer
arithmetic, universes, and inductive families as separate theorem projects.
The closing surface is strong because it is narrow, visible, and mechanically
audited.

\subsection{What BEDC Does Not Claim}
\label{subsec:session-closing-not-claimed}

BEDC does not claim to replace the Lean 4 kernel.  The represented calculus is
an object-language fragment inside Lean, not an implementation of Lean's
elaborator, environment, universe constraints, inductive compiler, recursor
generation, quotient layer, or kernel conversion checker.  Host Lean remains
the metalanguage in which BEDC proves facts about the represented object
calculus.

BEDC also does not claim a universal mechanization of CIC.  The present scope
is deliberately constrained by three commitments: first-principles definitions,
mathlib-free Lean, and zero project axioms.  Those commitments make the proofs
auditable, but they also keep the object calculus narrow.  The correct reading
is a closed-term sub-fragment with a rich gallery and explicit bridges, not a
general theorem about all terms and all type formers of CIC.

Finally, BEDC does not claim that every frontier has been discharged by naming
it.  Conditional theorems remain conditional.  Counterexamples remain
counterexamples.  Open-term binder transport, full application-residual
confluence, universe hierarchy, inductive families, propositional
irrelevance, eta-conversion, multiplication, and exponentiation stay outside
the closed surface reported here unless corresponding Lean targets enter the
audited tree.  This is the discipline that makes the closing meaningful: the
chapter closes exactly the surface it can verify, and no larger one.
