\begin{theorem}[FinSet enumeration carrier boundary]
\label{thm:finset-enumeration-carrier-boundary}
Fix a $\SetUp$ carrier $A:\mathsf{BHist}\to\mathsf{Prop}$ with classifier $\sim_A$, and let $xs:\mathsf{HistSpine}$ be the finite spine supplied by the $\ListUp$ enumeration witness. The public $\FinSetUp$ carrier exported by \autoref{def:finset-enumeration-carrier} consists exactly of a carried query history, a $\mathsf{SpineMember}$ witness in the displayed finite spine, and a classifier witness against one displayed spine entry. It exports no host set, no duplicate-normalized quotient, and no hidden enumeration order.
\end{theorem}
\begin{proof}
Unfold the carrier in \autoref{def:finset-enumeration-carrier}. A public membership row is a pair consisting of $A(a)$ and a displayed witness
$$
\exists x:\mathsf{BHist}.\;\mathsf{SpineMember}(x,xs)\land a\sim_A x.
$$
Thus the only exported data are the carried query history, the finite-spine occurrence, and the classifier comparison to the displayed entry.

The occurrence entry is source-carried by \autoref{lem:finset-enumeration-spine-entries-source-carried}, so the witness really lives in the fixed $\SetUp$ source rather than in a host set. The equivalence of \autoref{thm:finset-enumeration-membership-exactness} says that this displayed occurrence-and-classifier surface is not merely sufficient but exact for the carrier.

No further public field remains. Duplicate handling is mediated by the classifier and by later enumeration theorems, while enumeration order remains the visible $\ListUp$ spine data rather than a hidden quotient. Hence the public carrier boundary is exactly the stated finite-data surface.
\end{proof}
