\begin{theorem}[Reality-constrained TruthCert L10 source readiness]
\label{thm:reality-constrained-truth-cert-l10-source-readiness}
For every accepted $\RealityConstrainedTruthCertUp$ packet
$$
(S,\Sigma,K,T,U,D,I,L,F,N),
$$
the L10 consumers $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ may read the
TruthCert surface only through the finite source row $S$, signature row
$\Sigma$, classifier row $K$, tower row $T$, stability row $U$, descent row
$D$, observer-invariant row $I$, ledger row $L$, failure row $F$, and local
$\NameCert_{\RealityConstrainedTruthCertUp}$ row $N$. No L10 consumer receives
an unlisted source, ambient truth predicate, global reality oracle, or
off-packet continuation.
\end{theorem}
\begin{proof}
Read the carrier and field-coverage rows from
\autoref{def:reality-constrained-truth-cert-carrier} and
\autoref{thm:reality-constrained-truth-cert-field-coverage}. They make the
displayed tuple the full finite packet, with $S,\Sigma,K,T,U,D,I,L,F,N$ as the
available rows.

Next apply sibling dependency and sibling handoff totality,
\autoref{thm:reality-constrained-truth-cert-sibling-dependency} and
\autoref{thm:reality-constrained-truth-cert-sibling-handoff-totality}. These
place $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ behind the displayed
TruthCert handoff rather than behind an independent source supply.

Finally use export readiness,
\autoref{thm:reality-constrained-truth-cert-export-readiness}. The export row
is root-ready only after the finite source, classifier, ledger, failure, and
local naming rows are consumed, so every L10 read is confined to the accepted
packet.
\end{proof}
\leanchecked{BEDC.Derived.RealityConstrainedTruthCertUp.RealityConstrainedTruthCertL10SourceReadiness}

\begin{theorem}[Reality-constrained TruthCert L10 failure ledger lock]
\label{thm:reality-constrained-truth-cert-l10-failure-ledger-lock}
For every accepted $\RealityConstrainedTruthCertUp$ packet
$(S,\Sigma,K,T,U,D,I,L,F,N)$, each L10 read by $\StreamNameUp$,
$\RegSeqRatUp$, or $\RealUp$ that reaches the classifier row $K$ must also keep
the ledger row $L$ and the failure row $F$ in the same packet. The read cannot
drop finite defeat, domain exit, classifier mismatch, hidden residue, later
observation, or compression provenance while retaining the local name $N$.
\end{theorem}
\begin{proof}
Start with ledger exactness and failure-surface exactness,
\autoref{thm:reality-constrained-truth-cert-ledger-exactness} and
\autoref{thm:reality-constrained-truth-cert-failure-surface-exactness}. They
identify $L$ and $F$ as displayed rows of the accepted packet, not optional
annotations.

Use field coverage to keep $K,L,F,N$ in the same finite carrier. A consumer
that exposes $K$ through the local name must therefore remain inside
$S,\Sigma,K,T,U,D,I,L,F,N$.

Apply export readiness to the L10-facing handoff. Since the export cannot
expose $N$ before ledger and failure rows have been consumed, any read that
drops $L$ or $F$ is outside the $\RealityConstrainedTruthCertUp$ route.
\end{proof}
\leanchecked{BEDC.Derived.RealityConstrainedTruthCertUp.RealityConstrainedTruthCert\_l10\_failure\_ledger\_lock}

\begin{theorem}[Reality-constrained TruthCert L10 export totality]
\label{thm:reality-constrained-truth-cert-l10-export-totality}
The L10 export of an accepted $\RealityConstrainedTruthCertUp$ packet
$(S,\Sigma,K,T,U,D,I,L,F,N)$ is total for $\StreamNameUp$, $\RegSeqRatUp$, and
$\RealUp$: every accepted downstream read is accounted for by the finite source
row $S$, the classifier row $K$, the ledger row $L$, the failure row $F$, and
the local $\NameCert$ row $N$, together with the intervening signature, tower,
stability, descent, and observer-invariant rows. There is no second L10 export
through hidden source material, hidden failure repair, host equality, or an
ambient truth object.
\end{theorem}
\begin{proof}
Assemble the packet from carrier coverage and sibling dependency. These rows
state that the TruthCert object and its downstream consumers are expressed by
the displayed finite carrier and its listed sibling routes.

The ledger and failure lock fixes the classifier-facing part of the export.
By \autoref{thm:reality-constrained-truth-cert-l10-failure-ledger-lock}, any
L10 read that keeps the local name also keeps the classifier, ledger, and
failure rows inside the same packet.

Finally apply export readiness and sibling handoff totality. Together they
make the displayed packet the only source-readiness route for
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, so the L10 export is total over
the listed rows and has no hidden branch.
\end{proof}
\leanchecked{BEDC.Derived.RealityConstrainedTruthCertUp.RealityConstrainedTruthCertL10ExportTotality}

\begin{theorem}[Reality-constrained TruthCert L10 readiness obligation surface]
\label{thm:reality-constrained-truth-cert-l10-readiness-obligation-surface}
For every accepted $\RealityConstrainedTruthCertUp$ packet
$(S,\Sigma,K,T,U,D,I,L,F,N)$, the three L10 rows
\autoref{thm:reality-constrained-truth-cert-l10-source-readiness},
\autoref{thm:reality-constrained-truth-cert-l10-failure-ledger-lock}, and
\autoref{thm:reality-constrained-truth-cert-l10-export-totality} form the
complete readiness obligation surface for routing the packet through
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The surface consists exactly of
source confinement to the displayed packet, classifier-ledger-failure
co-residence inside that packet, and total export through the finite packet
rows $S,\Sigma,K,T,U,D,I,L,F,N$. It exposes no ambient truth predicate, quotient
real equality, selected limit, global reality oracle, or off-packet
continuation.
\end{theorem}
\begin{proof}
First use
\autoref{thm:reality-constrained-truth-cert-l10-source-readiness}. It confines
every L10 read by $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ to the finite
rows $S,\Sigma,K,T,U,D,I,L,F,N$, so no consumer can begin from an unlisted
source, ambient truth predicate, global reality oracle, or off-packet
continuation.

Next use
\autoref{thm:reality-constrained-truth-cert-l10-failure-ledger-lock}. This
keeps the classifier row $K$, the ledger row $L$, the failure row $F$, and the
local name row $N$ co-resident whenever a downstream L10 read reaches the
classifier. Hence the readiness surface cannot retain classifier evidence while
dropping defeat, domain exit, mismatch, hidden residue, observation, or
compression provenance.

Finally apply
\autoref{thm:reality-constrained-truth-cert-l10-export-totality}. The export
row accounts for every accepted downstream read by the displayed finite packet,
so there is no alternate route through quotient real equality, selected limits,
host equality, hidden repair, or an ambient truth object. The three rows
therefore give the complete L10 obligation surface needed by the downstream
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route.
\end{proof}

\begin{theorem}[Reality-constrained TruthCert L10 terminal source boundary]
\label{thm:reality-constrained-truth-cert-l10-terminal-source-boundary}
For every accepted $\RealityConstrainedTruthCertUp$ packet
$(S,\Sigma,K,T,U,D,I,L,F,N)$, any terminal L10 consumer read by
$\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ that is licensed by the TruthCert
route must pass through the same displayed source row $S$, classifier row $K$,
ledger row $L$, failure row $F$, export row, and local
$\NameCert_{\RealityConstrainedTruthCertUp}$ row $N$. The terminal read cannot
substitute quotient real equality, host equality, model--reality identity,
selected limits, hidden repair, or off-packet truth export for those packet
rows.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:reality-constrained-truth-cert-l10-source-readiness}. It confines
each $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ read to the displayed packet
$S,\Sigma,K,T,U,D,I,L,F,N$, so the terminal consumer has no source outside the
accepted TruthCert carrier.

Next use
\autoref{thm:reality-constrained-truth-cert-l10-failure-ledger-lock}. This keeps
the classifier row $K$, the ledger row $L$, the failure row $F$, and the local
name row $N$ co-resident whenever the terminal route reaches classifier
evidence.

The export side is exhausted by
\autoref{thm:reality-constrained-truth-cert-l10-export-totality} and
\autoref{thm:reality-constrained-truth-cert-l10-readiness-obligation-surface}.
Together they say that every accepted L10 read is already accounted for by the
finite source, classifier, ledger, failure, export, and naming rows of the same
packet.

Finally identify the downstream Real and Completion consumers through
\autoref{thm:reality-constrained-truth-cert-l10-source-exposure},
\autoref{thm:reality-constrained-truth-cert-physical-fit-nonescape}, and
\autoref{thm:reality-constrained-truth-cert-open-fit-refusal-surface}. These
root L10 obligations place physical fit, open-fit refusal, and terminal
$\RealUp$ access on the same source boundary, blocking quotient real equality,
host equality, model--reality identity, selected limits, hidden repair, and
off-packet truth export.
\end{proof}

\begin{theorem}[Reality-constrained TruthCert L10 terminal source determinacy]
\label{thm:reality-constrained-truth-cert-l10-terminal-source-determinacy}
Let $(S,\Sigma,K,T,U,D,I,L,F,N)$ and
$(S',\Sigma',K',T',U',D',I',L',F',N')$ be accepted
$\RealityConstrainedTruthCertUp$ packets. Suppose their displayed finite source,
signature, classifier, tower, stability, descent, observer-invariant, ledger,
failure, and local $\NameCert_{\RealityConstrainedTruthCertUp}$ rows agree
componentwise under the recorded $\hsame$ transport, displayed $\Cont$ replay,
and $\Pkg$ support. Then any two accepted terminal L10 reads by
$\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ determine the same BEDC-visible
terminal source boundary. The determinacy uses only the displayed packet rows:
it exports no quotient real equality, host equality, model--reality identity,
selected limit, hidden repair, global reality oracle, off-packet truth export,
or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:reality-constrained-truth-cert-l10-source-readiness}. Each terminal
read is confined to the displayed packet, so agreement on
$S,\Sigma,K,T,U,D,I,L,F,N$ and
$S',\Sigma',K',T',U',D',I',L',F',N'$ leaves no unlisted source row available to
separate the two reads.

Next use
\autoref{thm:reality-constrained-truth-cert-l10-failure-ledger-lock}. The
classifier, ledger, failure, and local-name rows stay co-resident with the same
accepted packet under the recorded $\hsame$, $\Cont$, and $\Pkg$ support. Thus a
terminal read cannot agree on the visible rows while changing the defeat,
domain-exit, mismatch, hidden-residue, later-observation, or compression
provenance boundary.

The export route is exhausted by
\autoref{thm:reality-constrained-truth-cert-l10-export-totality} and
\autoref{thm:reality-constrained-truth-cert-l10-readiness-obligation-surface}.
Together they make every accepted $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$
read a read of the same finite source, classifier, ledger, failure, export, and
local $\NameCert$ rows rather than a read of an external truth object.

Finally apply
\autoref{thm:reality-constrained-truth-cert-l10-terminal-source-boundary},
\autoref{thm:reality-constrained-truth-cert-l10-source-exposure},
\autoref{thm:reality-constrained-truth-cert-physical-fit-nonescape}, and
\autoref{thm:reality-constrained-truth-cert-open-fit-refusal-surface}. These
root rows place physical fit, open-fit refusal, and terminal $\RealUp$ access on
the same displayed source boundary. Since the two packets agree on every row
that those routes may inspect, the BEDC-visible terminal source boundary is the
same, with no quotient, host, model--reality, limit-selection, repair, oracle,
off-packet export, or ambient-completeness branch left over.
\end{proof}
