\begin{theorem}[Reality-constrained TruthCert L10 source exposure]
\label{thm:reality-constrained-truth-cert-l10-source-exposure}
For every accepted $\RealityConstrainedTruthCertUp$ packet
$$
(S,\Sigma,K,T,U,D,I,L,F,N),
$$
the source exposed to the L10 chain $\StreamNameUp$, $\RegSeqRatUp$, and
$\RealUp$ is exactly the displayed TruthCert surface. The chain reads the
source row $S$, signature row $\Sigma$, classifier row $K$, approximation tower
row $T$, continuation-stability row $U$, descent row $D$,
observer-invariant row $I$, methodology-ledger row $L$, open-fit failure row
$F$, and local $\NameCert_{\RealityConstrainedTruthCertUp}$ row $N$ through the
same finite packet, not through model--reality identity, unbounded
confirmation, observer privilege, host equality, quotient real equality, or a
direct truth export.
\end{theorem}
\begin{proof}
Start from field coverage and sibling dependency,
\autoref{thm:reality-constrained-truth-cert-field-coverage} and
\autoref{thm:reality-constrained-truth-cert-sibling-dependency}. They project
the accepted carrier to the nine displayed TruthCert rows and place the
open-fit, objectivity, explanation, physical-induction, and tower-compression
dependencies on that same carrier.

Next use L10 source readiness,
\autoref{thm:reality-constrained-truth-cert-l10-source-readiness}. It routes
the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ reads through
$S,\Sigma,K,T,U,D,I,L,F,N$ and leaves no unlisted source, ambient truth
predicate, global reality oracle, or off-packet continuation for the L10
consumer.

Finally apply the root TasteGate obligation
\autoref{thm:reality-constrained-truth-cert-root-tastegate-obligation}. The
root read consumes the same finite packet, so the L10 exposure cannot be
replaced by identity between the model and reality, unbounded confirmation,
observer privilege, host equality, quotient real equality, or direct truth
export.
\end{proof}

\begin{theorem}[Reality-constrained TruthCert physical-fit nonescape]
\label{thm:reality-constrained-truth-cert-physical-fit-nonescape}
Every physical-fit read of an accepted $\RealityConstrainedTruthCertUp$ packet
that reaches $\RealUp$ must also expose the $\RealityConstrainedOpenFitUp$ and
$\RealityConstrainedMethodologyLedgerUp$ sibling surfaces in the same nine-row
TruthCert boundary. In particular, finite fit, open continuation, finite
defeat, methodology scope, domain-leakage refusal, provenance, hidden residue,
and local naming remain recorded in $S,\Sigma,K,T,U,D,I,L,F,N$; no consumer may
export physical fit by quotient real equality, host equality, model--reality
identity, unbounded confirmation, observer privilege, or direct truth export.
\end{theorem}
\begin{proof}
Project the carrier by field coverage. The rows $S,\Sigma,K,T,U,D,I,L,F,N$ are
mandatory before the local name is readable, so a physical-fit read that drops
one of them is only a projection of the TruthCert packet.

Use sibling dependency to identify the two sibling surfaces. The
$\RealityConstrainedOpenFitUp$ route supplies finite fit, open continuation,
and finite defeat, while $\RealityConstrainedMethodologyLedgerUp$ supplies
methodology scope, refusal, provenance, hidden residue, and consumer
discipline.

Now apply L10 source readiness together with the root TasteGate obligation.
The $\RealUp$ read enters through the same L10 source boundary that serves
$\StreamNameUp$ and $\RegSeqRatUp$, and the root read has no hidden coordinate
beyond the displayed packet.

Thus physical fit cannot escape through quotient real equality, host equality,
model--reality identity, unbounded confirmation, observer privilege, or direct
truth export. It remains a finite TruthCert read with the open-fit and
methodology-ledger surfaces visible.
\end{proof}

\begin{theorem}[Reality-constrained TruthCert open-fit refusal surface]
\label{thm:reality-constrained-truth-cert-open-fit-refusal-surface}
For every accepted $\RealityConstrainedTruthCertUp$ packet
$(S,\Sigma,K,T,U,D,I,L,F,N)$, any downstream read that uses the
$\RealityConstrainedOpenFitUp$ surface must carry the refusal information
through the same L10 chain $\StreamNameUp \to \RegSeqRatUp \to \RealUp$ and
through the $\RealityConstrainedMethodologyLedgerUp$ row. The refusal surface
records finite defeat, domain exit, classifier mismatch, later observation,
compression residue, and local naming, and it refuses model--reality identity,
unbounded confirmation, observer privilege, host equality, quotient real
equality, and direct truth export.
\end{theorem}
\begin{proof}
Read the nine rows from field coverage. The failure row $F$, ledger row $L$,
classifier row $K$, tower row $T$, and local name $N$ are part of the same
accepted carrier, so the refusal information cannot be detached from the
TruthCert packet.

Apply sibling dependency to the open-fit and methodology-ledger routes. The
open-fit surface contributes finite defeat and later-observation exposure,
while the methodology-ledger surface records domain exit, refusal, compression
residue, consumer discipline, and provenance.

Use L10 source readiness to place the refusal surface on the
$\StreamNameUp \to \RegSeqRatUp \to \RealUp$ chain. The L10 read is therefore a
finite source read of $S,\Sigma,K,T,U,D,I,L,F,N$, not a separate physical-truth
channel.

Finally use the root TasteGate obligation. Since the root read consumes exactly
the displayed packet, the open-fit refusal surface blocks model--reality
identity, unbounded confirmation, observer privilege, host equality, quotient
real equality, and direct truth export.
\end{proof}
