\begin{theorem}[Real tail-agreement seal budget-source window service]
\label{thm:real-tail-agreement-seal-budget-source-window-service}
Every paired tail-window service exposed by an accepted $\RealTailAgreementSealUp$ packet reads the $\RegularCauchyTailBudgetUp$ row and the $\ObservationBudgetLimiterUp$ row before the paired finite-window row $W$ is public. The local packet may then expose
$$
R,S,W,D,A,H,C,P,N,
$$
but it cannot serve $W$ from an uncapped observation request, an unregistered tail source, a selected limit, or a host convergence witness.
\end{theorem}
\begin{proof}
Project the accepted carrier $Q=(R,S,W,D,A,H,C,P,N)$ and use the local $\NameCert_{\RealTailAgreementSealUp}$ obligations. They make the source rows, paired window row, dyadic readback row, agreement row, transport rows, continuation rows, package row, and local name the complete service surface.

Apply budget-window coherence. The finite tail request behind the paired service is the $\RegularCauchyTailBudgetUp$ row, and the observation row serving that request is capped by the $\ObservationBudgetLimiterUp$ route before the local $W$ row is available.

Finally use window-meet coverage and the non-escape theorems. The public service reads the finite StreamName meet and then the local route $W \to D \to A$, while quotient stream equality, selected limits, uncapped observations, and host convergence have no coordinate in the packet.
\end{proof}

\begin{theorem}[Real tail-agreement seal shared-threshold budget exactness]
\label{thm:real-tail-agreement-seal-shared-threshold-budget-exactness}
For an accepted $\RealTailAgreementSealUp$ packet, the shared $\RegularCauchyTailMeetUp$ threshold together with the $\RegularCauchyTailBudgetUp$ budget source determines the finite window route before any dyadic readback row $D$ or agreement row $A$ is public. Thus the only public agreement route is the budgeted shared-threshold route
$$
\RegularCauchyTailBudgetUp \longmapsto \RegularCauchyTailMeetUp \longmapsto W \longmapsto D \longmapsto A.
$$
\end{theorem}
\begin{proof}
Begin with the carrier and NameCert rows. The local seal has exactly one paired window row $W$, one dyadic readback row $D$, and one agreement row $A$, transported and served only through the displayed histories and continuations.

Use budget-window coherence to place the consumer on the budget source. Then apply the tail-meet factorization: the shared threshold is read before any completion-facing sibling route can consume the local agreement surface.

The window-meet coverage theorem identifies the finite StreamName route feeding $W$, and the window-route exact companion forces the subsequent read through $D$ and then $A$. Non-escape excludes quotient streams, selected tails, host limits, and hidden completion selectors, so the shared threshold and budget source jointly determine the finite route before $D$ and $A$ are exposed.
\end{proof}

\begin{theorem}[Real tail-agreement seal budgeted TailMeet window exhaustion]
\label{thm:real-tail-agreement-seal-budgeted-tailmeet-window-exhaustion}
For an accepted $\RealTailAgreementSealUp$ packet $Q=(R,S,W,D,A,H,C,P,N)$, every $\RealUp$ or $\CompletionUp$ consumer that reaches the agreement row $A$ passes, in order, through $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, $\RegularCauchyTailMeetUp$, the displayed paired window row $W$, the dyadic readback row $D$, and only then $A$. The route exports no quotient stream equality, host real equality, selected tail, ambient convergence predicate, or second agreement row.
\end{theorem}
\begin{proof}
Start with the budget-source window service. It places any public paired-window request behind the observation limiter and the regular Cauchy tail budget before the row $W$ can be read.

Next apply shared-threshold budget exactness. The shared $\RegularCauchyTailMeetUp$ threshold is the only threshold row feeding the displayed finite window route, so the consumer cannot bypass the budget through an unregistered tail source.

Use window-meet coverage to identify the paired window row and the dyadic readback row. The displayed service therefore proceeds through $W$ and then $D$ before the local agreement row $A$ is available.

Finally apply the Real-completion budgeted route and the non-escape clauses. They confine every $\RealUp$ and $\CompletionUp$ consumer to the same displayed packet rows and exclude quotient stream equality, host real equality, selected tails, ambient convergence predicates, and any second agreement coordinate.
\end{proof}

\begin{theorem}[Real tail-agreement seal Real-completion budgeted route]
\label{thm:real-tail-agreement-seal-real-completion-budgeted-route}
Every $\RealUp$ or $\CompletionUp$ consumer of an accepted $\RealTailAgreementSealUp$ packet factors through the budget source, shared threshold, finite windows, dyadic readback, and agreement row before the seal is public. Concretely, the consumer route is confined to
$$
\RegularCauchyTailBudgetUp,\ \ObservationBudgetLimiterUp,\ \RegularCauchyTailMeetUp,\ W,\ D,\ A,\ R,S,H,C,P,N,
$$
and cannot import quotient stream equality, host real equality, selected limits, ambient completeness, or a second agreement row.
\end{theorem}
\begin{proof}
Start with the RealUp consumer threshold factorization and the Completion consumer ledger. Together they place both Real and Completion consumers on the displayed carrier rows before any public seal read.

Next use the budget-source window service and shared-threshold budget exactness. The consumer first receives the budgeted observation route, then the shared TailMeet threshold, then the finite StreamName windows, dyadic readback row, and agreement row.

It remains to close the public boundary. Apply window-meet coverage, the completion route non-escape theorem, and the Real--Completion boundary theorem. These results keep the route inside the displayed $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so no external quotient, host limit, selected tail, ambient completeness proof, or second agreement coordinate can be read before the seal is public.
\end{proof}

\begin{theorem}[Real tail-agreement seal budget-threshold readback exhaustion]
\label{thm:real-tail-agreement-seal-budget-threshold-readback-exhaustion}
Every $\RealTailAgreementSealUp$ consumer route that exposes a public agreement row factors through $\RegularCauchyTailBudgetUp$, $\ObservationBudgetLimiterUp$, $\RegularCauchyTailMeetUp$, the finite StreamName window $W$, the dyadic readback row $D$, the agreement row $A$, and only then the $\RealUp$ or $\CompletionUp$ seal rows. No quotient-stream equality, selected limit, uncapped observation, host convergence witness, or second agreement coordinate is available along this public route.
\end{theorem}
\begin{proof}
Apply the budget-source window service to place any public paired-window request behind the $\RegularCauchyTailBudgetUp$ row and the $\ObservationBudgetLimiterUp$ cap before $W$ is served.

Next apply shared-threshold budget exactness. The only threshold available to the public agreement route is the $\RegularCauchyTailMeetUp$ row, and it feeds the finite StreamName window before the dyadic readback row $D$ and agreement row $A$ can be read.

Finally use the Real-completion budgeted route. Carrier projection identifies the remaining public rows as the displayed Real and Completion seal rows, and non-escape excludes quotient-stream equality, selected limits, uncapped observations, host convergence witnesses, and any second agreement coordinate.
\end{proof}

\begin{theorem}[Real tail-agreement seal terminal consumer route exhaustion]
\label{thm:real-tail-agreement-seal-terminal-consumer-route-exhaustion}
Every terminal $\RealUp$ or $\CompletionUp$ consumer that exposes the agreement row of an accepted $\RealTailAgreementSealUp$ packet is exhausted by the single displayed route
$$
\ObservationBudgetLimiterUp,\ \RegularCauchyTailBudgetUp,\ \RegularCauchyTailMeetUp,\ W,\ D,\ A,\ R,S,H,C,P,N.
$$
In particular, the terminal consumer must traverse the observation cap, the regular Cauchy tail budget, the shared TailMeet threshold, the finite StreamName window $W$, the dyadic readback row $D$, the agreement row $A$, and the displayed $R,S,H,C,P,N$ rows. It has no quotient stream equality, selected limit, uncapped observation, host convergence witness, or second agreement coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.RealTailAgreementSealUp.RealTailAgreementSealTerminalRoute\_exhaustion}
\begin{proof}
First apply the budget-source window service. It places the finite StreamName window behind the $\ObservationBudgetLimiterUp$ cap and the $\RegularCauchyTailBudgetUp$ source before any agreement-facing row can be read.

Next apply shared-threshold budget exactness and the budgeted TailMeet window exhaustion theorem. These force the route through $\RegularCauchyTailMeetUp$, then through the displayed window $W$, dyadic readback row $D$, and agreement row $A$.

Apply the Real-completion budgeted route and the budget-threshold readback exhaustion theorem to the terminal consumer. They identify the remaining public rows as $R,S,H,C,P,N$ and show that both $\RealUp$ and $\CompletionUp$ consumers use the same carrier route.

Carrier projection now leaves exactly the displayed packet coordinates, and non-escape removes every route not represented by those coordinates. Hence quotient stream equality, selected limits, uncapped observation requests, host convergence witnesses, and any second agreement coordinate are outside the terminal consumer surface.
\end{proof}

\begin{theorem}[Real tail-agreement seal budget route uniqueness]
\label{thm:real-tail-agreement-seal-budget-route-uniqueness}
Every accepted $\RealTailAgreementSealUp$ terminal consumer exposing the public agreement row has the unique public route
$$
\ObservationBudgetLimiterUp \to \RegularCauchyTailBudgetUp \to \RegularCauchyTailMeetUp \to W \to D \to A \to R,S,H,C,P,N.
$$
Any displayed consumer route that omits or reorders the observation cap, the tail budget, the shared $\RegularCauchyTailMeetUp$ threshold, the finite $\StreamNameUp$ window $W$, the dyadic readback row $D$, or the agreement row $A$ is outside the carrier. Thus the agreement seal has no alternate public route through quotient streams, selected limits, uncapped observations, host convergence, or a second agreement row.
\end{theorem}
\begin{proof}
The budget-source window service fixes the first public read. A consumer exposing the agreement row must first pass through the $\ObservationBudgetLimiterUp$ cap and the $\RegularCauchyTailBudgetUp$ source before the finite window $W$ is available.

Shared-threshold budget exactness then fixes the next boundary. The $\RegularCauchyTailMeetUp$ threshold is the only public threshold feeding the displayed finite window, and budgeted TailMeet exhaustion forces the route through $W$, then $D$, then $A$.

The Real-completion budgeted route identifies the remaining public rows as $R,S,H,C,P,N$. Terminal consumer route exhaustion shows that both $\RealUp$ and $\CompletionUp$ consumers read the same displayed carrier route after $A$.

Therefore any route that omits or reorders one of the named rows cannot be a route through the accepted carrier. The non-escape clauses exclude quotient stream equality, selected limits, uncapped observations, host convergence witnesses, and any second agreement row.
\end{proof}
\leanchecked{BEDC.Derived.RealTailAgreementSealUp.RealTailAgreementSeal\_budget\_route\_uniqueness}

\begin{theorem}[Real tail-agreement seal root budget-source totality]
\label{thm:real-tail-agreement-seal-root-budget-source-totality}
Every root-facing $\RealTailAgreementSealUp$ consumer that exposes the public agreement row must first read $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, $\RegularCauchyTailMeetUp$, the finite $\StreamNameUp$ window $W$, the dyadic readback row $D$, and the agreement row $A$, before any $\RealUp$ or $\CompletionUp$ seal row is public. Thus the root budget-source route is total for agreement-facing consumers and has no quotient stream equality, selected limit, uncapped observation, host convergence witness, or second agreement coordinate.
\end{theorem}
\begin{proof}
Start with the budget-source window service. It places every root-facing window read behind the $\ObservationBudgetLimiterUp$ cap and the $\RegularCauchyTailBudgetUp$ source before the finite window $W$ is available.

Next apply shared-threshold budget exactness and budgeted TailMeet window exhaustion. These force the public route through $\RegularCauchyTailMeetUp$, then through $W$, the dyadic readback row $D$, and the agreement row $A$.

Finally use terminal consumer route exhaustion. It identifies the only later public rows as the displayed $\RealUp$ and $\CompletionUp$ seal rows carried by $R,S,H,C,P,N$, so the earlier budget-source route is total for any consumer exposing $A$.

Coordinate exhaustion gives the exclusions. Quotient streams, selected limits, uncapped observations, host convergence witnesses, and second agreement coordinates have no carrier row in the displayed root route.
\end{proof}

\begin{theorem}[Real tail-agreement seal terminal budget-source lock]
\label{thm:real-tail-agreement-seal-terminal-budget-source-lock}
Every terminal $\RealUp$ or $\CompletionUp$ consumer exposing the $\RealTailAgreementSealUp$ agreement row must first lock onto the same $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, $\RegularCauchyTailMeetUp$, $\CauchySealBudgetSynchronizerUp$, finite $\StreamNameUp$ window $W$, $\DyadicRatCoreUp$ readback $D$, and agreement row $A$. Any terminal route that does not preserve this source lock is outside the carrier and cannot supply quotient-stream equality, selected limits, host convergence, ambient completeness, or a second agreement coordinate.
\end{theorem}
\begin{proof}
Start from the budget-source window service and root budget-source totality. They force every terminal agreement consumer to read the observation cap, tail budget, shared TailMeet threshold, finite window $W$, dyadic readback $D$, and agreement row $A$ before the Real or Completion seal rows are public.

Use shared-threshold budget exactness together with budgeted TailMeet window exhaustion. The shared $\RegularCauchyTailMeetUp$ threshold is the unique source boundary for the finite window and cannot be replaced by an uncapped observation or a selected-limit read.

Apply the budget synchronizer factorization theorem \autoref{thm:real-tail-agreement-seal-budget-synchronizer-factorization}. It inserts the $\CauchySealBudgetSynchronizerUp$ row between the shared threshold and the finite window, so the lock is the same route for both $\RealUp$ and $\CompletionUp$ consumers.

Finally use terminal consumer route exhaustion and downstream route no-branching. Any route that drops one of the locked rows has no displayed carrier coordinate, and the excluded quotient-stream, selected-limit, host-convergence, ambient-completeness, and second-agreement readings therefore cannot supply the terminal seal.
\end{proof}

\begin{theorem}[Real tail-agreement seal budget route canonical form]
\label{thm:real-tail-agreement-seal-budget-route-canonical-form}
Every accepted terminal agreement route of a $\RealTailAgreementSealUp$ packet has the canonical displayed order
$$
\ObservationBudgetLimiterUp \to \RegularCauchyTailBudgetUp \to \RegularCauchyTailMeetUp \to W \to D \to A \to R,S,H,C,P,N.
$$
Any public read of the agreement row $A$ is equivalent, as a $\BHist$ route through the packet, to traversing that order before $A$ is exposed.
\end{theorem}
\begin{proof}
First use the budget-source window service and shared-threshold budget exactness. They place every public window request behind the observation cap, the regular Cauchy tail budget, and the shared $\RegularCauchyTailMeetUp$ threshold before $W$ is available.

Next apply budgeted TailMeet window exhaustion. It forces the route from the shared threshold through the finite StreamName window $W$, then through the dyadic readback row $D$, and only then to the agreement row $A$.

The Real-completion budgeted route and terminal consumer route exhaustion identify the remaining public rows as $R,S,H,C,P,N$. Budget route uniqueness then rules out any accepted terminal route that omits or reorders one of the displayed rows.

Therefore a public read of $A$ is exactly a traversal of the canonical route shown in the statement.
\end{proof}

\begin{theorem}[Real tail-agreement seal budget synchronizer factorization]
\label{thm:real-tail-agreement-seal-budget-synchronizer-factorization}
Every accepted terminal agreement route of a $\RealTailAgreementSealUp$ packet factors through the budget synchronizer before any $\RealUp$ or $\CompletionUp$ seal consumer receives the classifier. The route has the ordered public surface
$$
\ObservationBudgetLimiterUp \to \RegularCauchyTailBudgetUp \to \RegularCauchyTailMeetUp \to \CauchySealBudgetSynchronizerUp \to W \to D \to A \to R,S,H,C,P,N.
$$
Here $W$ is the finite $\StreamNameUp$ window, $D$ is the $\DyadicRatCoreUp$ readback obtained from the $\RegSeqRatUp$ handoff, and $A$ is the unique agreement row exported to the Real and Completion consumers. No quotient stream equality, selected limit, uncapped observation request, host convergence witness, or second agreement row is available before those consumers read the classifier.
\end{theorem}
\begin{proof}
Start with the budget-source window service and shared-threshold exactness. They place any terminal agreement route behind $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, and the shared $\RegularCauchyTailMeetUp$ threshold before the finite window row can be public.

Next apply budgeted TailMeet exhaustion and the synchronizer row. The shared threshold is routed through $\CauchySealBudgetSynchronizerUp$ before the $\StreamNameUp$ window $W$ is read, and the $\RegSeqRatUp$ handoff supplies the finite regular-sequence data used by the $\DyadicRatCoreUp$ readback row $D$.

Use the canonical-form theorem \autoref{thm:real-tail-agreement-seal-budget-route-canonical-form}. It identifies the terminal agreement route with the displayed order through $W$, $D$, and the agreement row $A$ before the remaining seal rows $R,S,H,C,P,N$ are public.

Finally apply terminal consumer route exhaustion and downstream route no-branching. The exported classifier therefore reaches $\RealUp$ and $\CompletionUp$ only through the displayed synchronizer route, and the non-escape clauses exclude quotient streams, selected limits, uncapped observations, host convergence, and second agreement rows.
\end{proof}

\begin{theorem}[Real tail-agreement seal budget synchronizer route determinacy]
\label{thm:real-tail-agreement-seal-budget-synchronizer-route-determinacy}
Let two terminal $\RealUp$ or $\CompletionUp$ consumers of an accepted $\RealTailAgreementSealUp$ packet preserve the same observation cap, tail budget, shared $\RegularCauchyTailMeetUp$ threshold, $\CauchySealBudgetSynchronizerUp$ row, finite $\StreamNameUp$ window $W$, $\DyadicRatCoreUp$ readback $D$, and agreement row $A$. Then the two consumers expose the same displayed public route through $R,S,H,C,P,N$. No quotient stream, selected limit, uncapped observation, host convergence witness, ambient completeness datum, or second agreement row can distinguish the terminal routes.
\end{theorem}
\begin{proof}
Start with the terminal budget-source lock of \autoref{thm:real-tail-agreement-seal-terminal-budget-source-lock}. It fixes the observation cap, tail budget, shared TailMeet threshold, finite window, readback row, and agreement row before either terminal seal consumer can read the classifier.

Apply the canonical-form theorem \autoref{thm:real-tail-agreement-seal-budget-route-canonical-form}. Once those source rows are fixed, each public agreement read traverses the same ordered finite route before the displayed $R,S,H,C,P,N$ rows are exposed.

Next use the synchronizer factorization of \autoref{thm:real-tail-agreement-seal-budget-synchronizer-factorization}. The shared threshold passes through the same $\CauchySealBudgetSynchronizerUp$ row before the finite window $W$, the dyadic readback $D$, and the agreement row $A$ are consumed.

Finally apply downstream route no-branching, \autoref{thm:real-tail-agreement-seal-downstream-route-no-branching}. Since no carrier coordinate supplies quotient streams, selected limits, uncapped observations, host convergence, ambient completeness, or a second agreement row, the two terminal consumers cannot be distinguished after preserving the same synchronizer route.
\end{proof}

\begin{theorem}[Real tail-agreement seal downstream route no-branching]
\label{thm:real-tail-agreement-seal-downstream-route-no-branching}
No downstream $\RealUp$ or $\CompletionUp$ consumer of an accepted $\RealTailAgreementSealUp$ packet can branch around the budget route through quotient stream equality, selected limits, uncapped observations, host convergence, or a second agreement coordinate. Every such consumer remains on the canonical route through $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, $\RegularCauchyTailMeetUp$, $W$, $D$, $A$, and the displayed $R,S,H,C,P,N$ rows.
\end{theorem}
\begin{proof}
Begin with root budget-source totality. It places any root-facing agreement read behind the observation cap, tail budget, shared TailMeet threshold, finite window, dyadic readback, and agreement row.

Use the canonical-form theorem \autoref{thm:real-tail-agreement-seal-budget-route-canonical-form}. It identifies any public read of $A$ with the single displayed order through the finite carrier rows.

Finally apply terminal consumer route exhaustion and budget route uniqueness. These theorems leave no coordinate for quotient stream equality, selected limits, uncapped observations, host convergence witnesses, or a second agreement row, so no downstream $\RealUp$ or $\CompletionUp$ consumer can branch around the budget route.
\end{proof}

\begin{theorem}[Real tail-agreement seal regular TailMeet budget lock]
\label{thm:real-tail-agreement-seal-regular-tailmeet-budget-lock}
Every terminal $\RealTailAgreementSealUp$ agreement route accepted by $\RealUp$ or $\CompletionUp$ is locked to the ordered route
$$
\ObservationBudgetLimiterUp \to \RegularCauchyTailBudgetUp \to \RegularCauchyTailMeetUp \to \CauchySealBudgetSynchronizerUp \to W \to D \to A \to R,S,H,C,P,N.
$$
Here $W$ is the finite $\StreamNameUp$ window, $D$ is the $\DyadicRatCoreUp$ readback, $A$ is the unique agreement row, and $R,S,H,C,P,N$ are the local seal rows displayed by the accepted packet. Once this route is fixed, no quotient stream, selected limit, host equality, ambient completeness principle, or second agreement row can distinguish any downstream seal consumer.
\end{theorem}
\begin{proof}
First build the upstream budget source. The budget-source window service and shared-threshold exactness place any terminal agreement route behind $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, and the shared $\RegularCauchyTailMeetUp$ threshold before a finite agreement window can be read.

Next attach the synchronizer. Apply the budget synchronizer factorization of \autoref{thm:real-tail-agreement-seal-budget-synchronizer-factorization}: the shared threshold passes through $\CauchySealBudgetSynchronizerUp$ before the finite $\StreamNameUp$ window $W$, the $\DyadicRatCoreUp$ readback $D$, and the agreement row $A$ are consumed.

The local agreement surface is then fixed by downstream route no-branching, \autoref{thm:real-tail-agreement-seal-downstream-route-no-branching}. It keeps each $\RealUp$ and $\CompletionUp$ consumer on the same route through $R,S,H,C,P,N$ after the synchronizer route has been selected.

Finally use the CauchyLimitSeal finite-window lattice route, \autoref{thm:cauchy-limit-seal-finite-window-lattice-dependency}. The finite window is a lattice meet rather than a hidden selected limit, so the completed route has no coordinate for quotient stream equality, host equality, ambient completeness, or a second agreement row to separate the consumers.
\end{proof}

\begin{theorem}[Real tail-agreement seal budget route factorization]
\label{thm:real-tail-agreement-seal-budget-route-factorization}
Every accepted terminal agreement read of a $\RealTailAgreementSealUp$ packet factors through the canonical budget route, the synchronizer route, and the regular-tailmeet budget lock before it exports the terminal agreement row to a $\RealUp$ or $\CompletionUp$ consumer. Thus the exported terminal agreement has the single displayed route through $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, $\RegularCauchyTailMeetUp$, $\CauchySealBudgetSynchronizerUp$, the finite $\StreamNameUp$ window $W$, the $\DyadicRatCoreUp$ readback row $D$, the agreement row $A$, and the local seal rows $R,S,H,C,P,N$.
\end{theorem}
\begin{proof}
Apply budget route uniqueness from \autoref{thm:real-tail-agreement-seal-budget-route-uniqueness}. Any accepted terminal agreement read must use the displayed observation cap, regular Cauchy tail budget, shared TailMeet threshold, finite window, dyadic readback, agreement row, and local seal rows.

Next use the canonical-form theorem \autoref{thm:real-tail-agreement-seal-budget-route-canonical-form}. It identifies the public read of $A$ with that ordered route before the terminal seal rows can be exported.

Insert the synchronizer by \autoref{thm:real-tail-agreement-seal-budget-synchronizer-route-determinacy}. The terminal route preserves the same $\CauchySealBudgetSynchronizerUp$ row before the finite window, readback row, and agreement row are consumed.

Finally apply downstream route no-branching from \autoref{thm:real-tail-agreement-seal-downstream-route-no-branching} and the regular TailMeet budget lock of \autoref{thm:real-tail-agreement-seal-regular-tailmeet-budget-lock}. The terminal agreement row is therefore exported only after the displayed budget route, synchronizer route, and regular-tailmeet lock have all been traversed, with no quotient stream, selected limit, host equality, ambient completeness coordinate, or second agreement row available.
\end{proof}

\begin{theorem}[Real tail-agreement seal root budget-source canonicality]
\label{thm:real-tail-agreement-seal-root-budget-source-canonicality}
Every displayed $\RealTailAgreementSealUp$ packet exposing a terminal agreement row determines a unique root budget-source row. The canonical source is the initial $\BHist$ segment through $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, $\RegularCauchyTailMeetUp$, $\CauchySealBudgetSynchronizerUp$, $W$, $D$, and $A$ whose $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are consumed by the terminal route
$$
\ObservationBudgetLimiterUp \to \RegularCauchyTailBudgetUp \to \RegularCauchyTailMeetUp \to \CauchySealBudgetSynchronizerUp \to W \to D \to A \to R,S,H,C,P,N.
$$
No second source row, quotient stream equality, selected limit, uncapped observation request, host convergence witness, or ambient completeness datum can serve as a competing root budget source. The intended Lean home for this package is the namespace \texttt{BEDC.Derived.RealTailAgreementSealUp.RootBudget}.
\end{theorem}
\begin{proof}
Use root budget-source totality, \autoref{thm:real-tail-agreement-seal-root-budget-source-totality}. It forces any root-facing agreement consumer to read the observation cap, the regular tail budget, the shared TailMeet threshold, the finite window, the dyadic readback row, and the agreement row before the terminal seal rows are public.

Use budget route uniqueness, \autoref{thm:real-tail-agreement-seal-budget-route-uniqueness}. Once the displayed packet exposes the public agreement row, no accepted $\BHist$ route may omit or reorder the budget source, shared threshold, finite window, readback row, or agreement row.

Finally apply the regular TailMeet budget lock of \autoref{thm:real-tail-agreement-seal-regular-tailmeet-budget-lock}. The synchronizer and the local rows $R,S,H,C,P,N$ are consumed on the same route, so the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows name one canonical root budget-source row and exclude every competing source coordinate.
\end{proof}

\begin{theorem}[Real tail-agreement seal root budget threshold coverage]
\label{thm:real-tail-agreement-seal-root-budget-threshold-coverage}
For every accepted $\RealTailAgreementSealUp$ terminal agreement route, the shared-threshold budget row covers every $\RegularCauchyTailMeetUp$ window admitted by the regular TailMeet budget lock. Concretely, any TailMeet window consumed by $\RealUp$ or $\CompletionUp$ is first covered by the $\RegularCauchyTailBudgetUp$ source and the shared $\RegularCauchyTailMeetUp$ threshold, then read through $W$, $D$, $A$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the packet. No selected tail, uncapped observation, host convergence witness, quotient stream equality, or second agreement row lies outside this threshold coverage.
\end{theorem}
\begin{proof}
Begin with shared-threshold budget exactness, \autoref{thm:real-tail-agreement-seal-shared-threshold-budget-exactness}. It identifies the shared $\RegularCauchyTailMeetUp$ threshold and the regular tail budget as the unique public source for the finite route before $D$ or $A$ is visible.

Next use budgeted TailMeet window exhaustion and the regular TailMeet budget lock. They show that each terminal $\RealUp$ or $\CompletionUp$ consumer reaches the agreement row only through the shared threshold, the synchronizer, the finite window $W$, and the dyadic readback row $D$.

The terminal route exhaustion theorem then consumes the local rows $R,S,H,C,P,N$ on the same displayed packet. Thus every admitted TailMeet window is already covered by the shared-threshold budget row, and the excluded selected-tail, uncapped-observation, host-convergence, quotient, and second-agreement readings have no carrier coordinate.
\end{proof}

\begin{theorem}[Real tail-agreement seal root budget terminal consumption]
\label{thm:real-tail-agreement-seal-root-budget-terminal-consumption}
Every terminal $\RealUp$ or $\CompletionUp$ consumer of a displayed $\RealTailAgreementSealUp$ packet may consume only the canonical root budget route produced by root budget-source canonicality and root budget threshold coverage. The permitted consumption route is the finite $\BHist$ route through $\ObservationBudgetLimiterUp$, $\RegularCauchyTailBudgetUp$, $\RegularCauchyTailMeetUp$, $\CauchySealBudgetSynchronizerUp$, $W$, $D$, $A$, and $R,S,H,C,P,N$, together with the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Any terminal read requiring a second source row, a selected limit, quotient stream equality, uncapped observations, host convergence, ambient completeness, or a second agreement coordinate is outside the package.
\end{theorem}
\begin{proof}
First take the canonical source supplied by \autoref{thm:real-tail-agreement-seal-root-budget-source-canonicality}. It combines totality with budget route uniqueness, so the terminal consumer has only one root budget-source row to read.

Next use \autoref{thm:real-tail-agreement-seal-root-budget-threshold-coverage}. The shared threshold covers the TailMeet window consumed by the terminal route, and the window is read through $W$, $D$, and $A$ before any local seal row is exposed.

Finally apply terminal consumer route exhaustion and downstream route no-branching. They consume $R,S,H,C,P,N$ through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and rule out every terminal route that asks for a second source, selected limit, quotient stream equality, uncapped observation, host convergence, ambient completeness, or a second agreement coordinate.
\end{proof}
