\begin{theorem}[Real tail-agreement seal root source-window admission]
\label{thm:real-tail-agreement-seal-root-source-window-admission}
Every root read of an accepted $\RealTailAgreementSealUp$ packet $Q=(R,S,W,D,A,H,C,P,N)$ first admits the displayed $\RegSeqRatUp$ source rows $R,S$ and the paired $\StreamNameUp$ window row $W$ before any agreement row can be consumed. The admission route is the carrier route of \autoref{def:real-tail-agreement-seal-carrier} together with the NameCert source-separation and paired-window obligations, and it exposes no source object outside those finite rows.
\end{theorem}
\leanchecked{BEDC.Derived.RealTailAgreementSealUp.RealTailAgreementSealTerminalRoute\_root\_source\_window\_admission}
\begin{proof}
Project $Q$ by the carrier definition. The only source coordinates visible at the root are $R,S$, and the only window coordinate attached to them is the displayed paired row $W$.

Apply the source separation obligation and the paired-window source lock. These obligations force each root read to pass through the $\RegSeqRatUp$ source rows and then the $\StreamNameUp$ paired-window row before any local agreement data is available.

The root-window readback theorem then identifies this admitted window as the first leg of the public readback route. Since no additional source or window coordinate exists in the carrier, the root surface cannot expose an alternative source-window path.
\end{proof}

\begin{theorem}[Real tail-agreement seal root dyadic agreement exactness]
\label{thm:real-tail-agreement-seal-root-dyadic-agreement-exactness}
For every accepted $\RealTailAgreementSealUp$ packet $Q=(R,S,W,D,A,H,C,P,N)$, the agreement row $A$ is root-readable only after the displayed dyadic route $W \to D$ has been read. The exact route is the finite $\StreamNameUp$ window row $W$, the $\DyadicRatCoreUp$ readback row $D$, and then the local agreement row $A$; it is not a quotient stream equality, host convergence predicate, or selected tail.
\end{theorem}
\leanchecked{BEDC.Derived.RealTailAgreementSealUp.RealTailAgreementSealCarrier\_root\_dyadic\_agreement\_exactness}
\begin{proof}
Begin with the root source-window admission theorem. It places the root read on the displayed paired window row $W$ before the agreement row can be inspected.

Use the dyadic window exactness and dyadic terminal nonescape obligations. They make $D$ the only dyadic readback attached to $W$ and leave no second dyadic carrier for the consumer to choose.

Now apply root-window readback and tail-classifier transport. The public classifier is transported through the same $W \to D$ route, so the agreement row $A$ is reached exactly after that finite dyadic read and not through an ambient equality or convergence principle.
\end{proof}

\begin{theorem}[Real tail-agreement seal root Completion boundary]
\label{thm:real-tail-agreement-seal-root-completion-boundary}
Every root-facing $\RealUp$ or $\CompletionUp$ consumer of an accepted $\RealTailAgreementSealUp$ packet receives only the finite rows $R,S,W,D,A,H,C,P,N$ and the named sibling routes through $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, regular-tail meet and fusion, $\RealUp$, $\CompletionUp$, and Cauchy-limit-seal consumers. The boundary supplies no quotient stream equality, selected limit, host convergence, or choice-selected tail.
\end{theorem}
\begin{proof}
Read the consumer through the Completion consumer scope theorem. It lists the packet rows and the named sibling consumer routes available at the Real and Completion boundary.

Combine this with root source-window admission and root dyadic agreement exactness. The source, window, dyadic readback, and agreement rows have already been exposed in the order $R,S,W,D,A$ before any sibling consumer receives the packet.

The carrier supplies the remaining local transport, continuity, package, and NameCert rows $H,C,P,N$. Since neither the carrier nor the cited sibling routes contain a coordinate for quotient stream equality, selected limits, host convergence, or choice-selected tails, the root Completion boundary is exhausted by the displayed finite rows.
\end{proof}

\begin{theorem}[Real tail-agreement seal root Completion-window totality]
\label{thm:real-tail-agreement-seal-root-completion-window-totality}
Every root Completion-facing read of an accepted $\RealTailAgreementSealUp$ packet factors through the ordered route consisting of the $\RegSeqRatUp$ source rows $R,S$, the $\StreamNameUp$ paired window row $W$, the $\DyadicRatCoreUp$ readback row $D$, the local agreement row $A$, the regular-tail meet and fusion surfaces, and then the $\RealUp$, $\CompletionUp$, and $\CauchyLimitSealUp$ consumer rows. The route is total for such root reads and supplies no quotient stream equality, selected limit, host convergence, or choice-selected tail.
\end{theorem}
\begin{proof}
Start with root source-window admission. It places the root read first on the two displayed $\RegSeqRatUp$ source rows and then on the paired $\StreamNameUp$ window row, so the consumer has no source-window route outside $R,S,W$.

Next use root dyadic agreement exactness. The admitted window is read back through the displayed $\DyadicRatCoreUp$ row $D$, and the local agreement row $A$ is available only after that finite $W \to D$ leg.

Now apply the Completion handoff totality theorem. It sends every Completion-facing consumer from the local agreement surface through the regular-tail meet and fusion route and then to the named Completion-side consumer rows.

Finally combine the root Completion boundary with the Completion consumer scope theorem. These two boundary statements identify the remaining visible endpoints as the $\RealUp$, $\CompletionUp$, and $\CauchyLimitSealUp$ consumer rows already named by the chapter. Since each step consumes only displayed rows of the packet or named sibling surfaces, no quotient stream equality, selected limit, host convergence, or choice-selected tail can enter the root Completion-facing read.
\end{proof}
