\begin{theorem}[RegSeqRat carrier obligation]
\label{thm:regseqrat-carrier-obligation}
The carrier obligation for $\RegSeqRat$ is exactly the
$\mathsf{RatStreamNameCarrier}$ row together with the regularity witness over
$\mathsf{UnaryHistory}$ observations. Concretely, for a rational-observation
map $s:\Hist\to\Hist$, a $\RegSeqRat$ carrier consists of
$\mathsf{RatStreamNameCarrier}(s)$ and a ledger which, at each certified unary
observation index $n$, exposes the endpoint $\RatUp$ carrier row
$\mathsf{RatHistoryCarrier}(s(n))$ and the dyadic-tolerance witness demanded by
the stream regularity check.
\end{theorem}
\begin{proof}
Unfold the spine named in
Definition~\ref{def:regseqrat-stream-certificate-spine}. Its first component
is the $\mathsf{RatStreamNameCarrier}$ row, and its ledger is indexed only by
certified $\mathsf{UnaryHistory}$ observations.

The endpoint carrier rows are supplied by
\autoref{thm:regseqrat-stream-classifier-stability-spine}; the constant case is
supplied by \autoref{thm:regseqrat-constant-stream-spine}. The public package
\autoref{thm:regseqrat-stream-spine-scoped-package} records these rows as the
carrier face of the scoped spine.

The seal consumer
\autoref{thm:regseqrat-realup-seal-consumes-stream-spine} uses no carrier data
outside this spine. Thus the carrier obligation is precisely the named
stream-name carrier plus the unary-observation regularity ledger.
\end{proof}

\begin{theorem}[RegSeqRat classifier obligation]
\label{thm:regseqrat-classifier-obligation}
The classifier obligation for $\RegSeqRat$ is exactly
$\mathsf{RealUnaryStreamClassifier}$ read with
$\mathsf{RatStreamNameClassifier}$ endpoint recovery. For carried streams
$s,t:\Hist\to\Hist$, a classifier row records the pointwise $\RatUp$
comparison over every certified $\mathsf{UnaryHistory}$ observation and
recovers the two endpoint stream-name carrier rows used by
$\mathsf{RatStreamNameClassifier}(s,t)$.
\end{theorem}
\begin{proof}
Start from Definition~\ref{def:regseqrat-stream-certificate-spine}. The spine
does not introduce a separate classifier relation; it stores the RealUp unary
stream classifier over the same BEDC unary observations.

Apply \autoref{thm:regseqrat-stream-classifier-stability-spine}. It reads the
pointwise $\RatUp$ classifier rows from
$\mathsf{RealUnaryStreamClassifier}$, recovers the endpoint carrier rows, and
repackages the transported data as a
$\mathsf{RatStreamNameClassifier}$ row. The constant boundary is the reflexive
case supplied by \autoref{thm:regseqrat-constant-stream-spine}.

The scoped package
\autoref{thm:regseqrat-stream-spine-scoped-package} lists the reflexive,
symmetric, transitive, and transported classifier rows together. The seal
consumer \autoref{thm:regseqrat-realup-seal-consumes-stream-spine} confirms
that the same row is the classifier exported through the $\RealUp$ interface.
\end{proof}

\begin{theorem}[RegSeqRat carrier-classifier export package]
\label{thm:regseqrat-carrier-classifier-export-package}
For carried rational-observation streams $s,t:\Hist\to\Hist$, the
$\RegSeqRat$ spine exports exactly the
$\mathsf{RatStreamNameCarrier}(s)$ row, the
$\mathsf{RatStreamNameCarrier}(t)$ row, the
$\mathsf{RatStreamNameClassifier}(s,t)$ row, the
$\mathsf{RealUnaryStreamClassifier}(s,t)$ row, the endpoint
$\mathsf{RatHistoryCarrier}$ and $\mathsf{RatHistoryClassifier}$ rows over
certified $\mathsf{UnaryHistory}$ observations, and the finite
$\mathsf{DyadicRatCore}$ ledger rows later consumed by the $\RealUp$ seal.

This export package contains no quotient representatives, completion data,
metric completeness, $\RealUp$ completeness, Classical data, or standard
bridge data. Its public boundary is the carried stream-name surface, the
endpoint RatUp observation surface, the finite dyadic ledger, and the
downstream $\RealUp$ seal consumption row.
\end{theorem}
\begin{proof}
Read the carrier rows from Definition~\ref{def:regseqrat-stream-certificate-spine}.
Apply \autoref{thm:regseqrat-carrier-obligation} to the carried streams $s$
and $t$. This supplies the two $\mathsf{RatStreamNameCarrier}$ rows and the
endpoint $\mathsf{RatHistoryCarrier}$ rows indexed by certified
$\mathsf{UnaryHistory}$ observations.

Read the classifier rows from the same spine. Apply
\autoref{thm:regseqrat-classifier-obligation}. It exposes the recorded
$\mathsf{RealUnaryStreamClassifier}(s,t)$ row, recovers the pointwise endpoint
$\mathsf{RatHistoryClassifier}$ rows, and repackages them as the
$\mathsf{RatStreamNameClassifier}(s,t)$ row.

Next read the dyadic side. Apply
\autoref{thm:dyadic-rat-core-scoped-primitive-dependency-package} to identify
the finite $\mathsf{DyadicRatCore}$ ledger rows and their scoped primitive
source. Then apply
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation} to consume
those rows at the $\RealUp$ seal boundary.

The four cited obligations exhaust the displayed package. The carrier and
classifier faces are read from the same certificate spine, while the dyadic
ledger and the $\RealUp$ seal are consumed as already recorded rows. None of
these steps adds a quotient representative, a completion object, a metric
completeness principle, a $\RealUp$ completeness principle, Classical data, or
standard bridge data as a primitive input.
\end{proof}

\begin{theorem}[RegSeqRat export determines the RealUp seal source]
\label{thm:regseqrat-export-real-seal-source-determinacy}
For carried rational-observation streams $s,t:\Hist\to\Hist$, the export
package of
\autoref{thm:regseqrat-carrier-classifier-export-package} determines the exact
source face read by the downstream $\RealUp$ seal. That source face consists
precisely of the two $\mathsf{RatStreamNameCarrier}$ rows for $s$ and $t$, the
$\mathsf{RatStreamNameClassifier}(s,t)$ row, the pointwise
$\mathsf{RealUnaryStreamClassifier}(s,t)$ row, the endpoint
$\mathsf{RatHistoryCarrier}$ and $\mathsf{RatHistoryClassifier}$ rows over
certified $\mathsf{UnaryHistory}$ observations, and the finite
$\mathsf{DyadicRatCore}$ ledger rows.

No quotient representative, completion object, metric completeness principle,
or $\RealUp$ completeness datum is part of this seal source. Consequently, any
$\RealUp$ seal source read from the $\RegSeqRat$ package factors through the
same visible carrier, classifier, endpoint, and dyadic ledger rows.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:regseqrat-carrier-classifier-export-package}. It identifies the
two stream-name carrier rows, the stream-name classifier row, the pointwise
RealUnary classifier row, the endpoint RatUp carrier and classifier rows over
certified unary observations, and the finite dyadic ledger rows as the complete
exported surface.

Next apply
\autoref{thm:dyadic-rat-core-scoped-primitive-dependency-package}. This fixes
the dyadic primitive source of the ledger rows as the scoped
$\mathsf{DyadicRatCore}$ data, with no additional completion or quotient
object hidden behind the ledger.

Finally apply
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation}. The $\RealUp$
seal consumes the same dyadic ledger together with the same carried stream-name
and endpoint observation rows. Since the preceding export package already
lists all rows available at the $\RegSeqRat$ boundary, row exhaustion forces
every seal-source read to factor through exactly those visible rows and through
no separate $\RealUp$ completeness datum.
\end{proof}

\begin{theorem}[RegSeqRat export finite-window row exhaustion]
\label{thm:regseqrat-export-finite-window-row-exhaustion}
For carried rational-observation streams $s,t:\Hist\to\Hist$ and a certified
finite $\mathsf{ProbeBundle}$ window, every finite-window row consumed by the
downstream $\RealUp$ seal from the $\RegSeqRat$ export factors through exactly
the listed $\mathsf{RatStreamNameCarrier}(s)$ and
$\mathsf{RatStreamNameCarrier}(t)$ rows, the
$\mathsf{RatStreamNameClassifier}(s,t)$ row, the
$\mathsf{RealUnaryStreamClassifier}(s,t)$ row, the endpoint $\RatUp$ carrier
and classifier rows, the finite $\mathsf{DyadicRatCore}$ ledger, the displayed
$\mathsf{BHist}$ rows, the $\hsame$ transports, the $\Cont$ continuation
routes, the $\mathsf{Pkg}$ provenance, and the local $\NameCert$ rows.

Consequently two certified windows which agree on these rows present the same
finite-window consumer surface to $\RealUp$. The exhaustion statement exports
no quotient representative, completed $\RealUp$ equality, metric-completeness
datum, Classical datum, or standard bridge datum.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:regseqrat-carrier-classifier-export-package}. It identifies the
stream-name carrier rows, the stream-name classifier row, the pointwise
RealUnary classifier row, the endpoint $\RatUp$ rows, and the finite dyadic
ledger as the complete $\RegSeqRat$ export package.

Next apply
\autoref{thm:regseqrat-export-real-seal-source-determinacy}. The downstream
$\RealUp$ seal reads its source face from the same exported carrier,
classifier, endpoint, and dyadic ledger rows, so it has no independent source
coordinate outside the displayed package.

Finally apply \autoref{thm:realup-regseqrat-finite-window-projection} to the
certified finite $\mathsf{ProbeBundle}$ window. This restricts the seal read to
the displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local
$\NameCert$ rows attached to that window.

If two certified windows agree on all listed rows, the three preceding
identifications give the same projected consumer surface. Since no cited
boundary contains a field for quotient representatives, completed $\RealUp$
equality, metric completeness, Classical data, or standard bridge data, those
objects cannot be consumed by the finite-window seal.
\end{proof}
