\begin{definition}[DyadicRatCore observation row]
\label{def:dyadic-rat-core-observation-row}
A DyadicRatCore observation row for a BEDC history $d$ is the package consisting
of a $\mathsf{RatHistoryCarrier}(d)$ witness, a positive unary denominator row
$\mathsf{PositiveUnaryDenominator}(d)$, and the dyadic-radius token used by the
$\RegSeqRat$ regularity check. Its classifier face is inherited from
$\mathsf{RatHistoryClassifier}$, together with $\hsame$ transport of the
positive-denominator row.
\end{definition}
\leandef{BEDC.Derived.RealUp.DyadicRatCoreObservationRow}

\begin{theorem}[DyadicRatCore observation-row classifier transport]
\label{thm:dyadic-rat-core-observation-row-classifier-transport}
Let $d,e,d',e':\Hist$. Suppose $d$ and $e$ carry
$\mathsf{DyadicRatCoreObservationRow}$ packages, suppose
$\mathsf{RatHistoryClassifier}(d,e)$ holds, and suppose
$\hsame(d,d')$ and $\hsame(e,e')$ hold. If the dyadic-radius tokens for
$d'$ and $e'$ are the same certified unary-observation requests as the
tokens for $d$ and $e$, transported along those two $\hsame$ rows inside the
$\RegSeqRat$ ledger, then $d'$ and $e'$ carry
$\mathsf{DyadicRatCoreObservationRow}$ packages and
$\mathsf{RatHistoryClassifier}(d',e')$ holds.
\end{theorem}
\begin{proof}
Unpack Definition~\ref{def:dyadic-rat-core-observation-row}. The source rows
at $d$ and $e$ consist of rational-history carriers, positive unary
denominator rows, and dyadic-radius tokens attached to certified
$\RegSeqRat$ unary observations.

Apply the RatUp classifier transport to
$\mathsf{RatHistoryClassifier}(d,e)$ along $\hsame(d,d')$ and
$\hsame(e,e')$. This gives the transported classifier
$\mathsf{RatHistoryClassifier}(d',e')$, and the transported carrier rows are
read from the same rational-history endpoint spine.

The denominator component follows by positive-denominator transport. Applying
\autoref{thm:rat-positive-unary-denominator-hsame-transport} to the two
$\hsame$ rows carries the positive unary denominator rows from $d$ to $d'$
and from $e$ to $e'$.

Finally, the dyadic-radius component is ledger-attached to the same certified
unary-observation requests in the $\RegSeqRat$ spine. Transporting the
endpoint rows changes neither the request names nor the recorded
dyadic-tolerance tokens, so no completion or quotient datum is introduced.
Repacking the transported carrier, denominator, token, and classifier rows
gives the stated DyadicRatCore observation-row transport.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.DyadicRatCoreObservationRow\_classifier\_transport}

The fit is as follows: traditional target dyadic rational observation
transport; BEDC source RatUp plus RegSeqRat unary requests over
$\mathsf{BHist}$; carrier $\mathsf{DyadicRatCoreObservationRow}$; classifier
$\mathsf{RatHistoryClassifier}$; stability transported denominator rows;
ledger unchanged dyadic-radius request; core theorem
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport};
exactness transported row plus classifier; standard bridge finite RealUp
windows; status $\mathsf{ProofTarget}$.

\begin{theorem}[DyadicRatCore scoped source package]
\label{thm:dyadic-rat-core-scoped-source-package}
The DyadicRatCore source used by $\RegSeqRat$ is the concrete BEDC scoped
source package over $\Hist$ whose carrier, classifier, stability, and ledger
faces are all read from the rational-history endpoint spine. For each endpoint
history $d$, the carrier face is
$\mathsf{RatHistoryCarrier}(d)$ together with
$\mathsf{PositiveUnaryDenominator}(d)$ and the dyadic-radius token recorded by
the $\RegSeqRat$ regularity request. For endpoints $d,e$, the classifier face
is $\mathsf{RatHistoryClassifier}(d,e)$ together with $\hsame$ transport of the
positive-denominator rows. The stability face is inherited from the $\RatUp$
carrier and classifier transports and from the pointwise classifier obligation
of $\RegSeqRat$. The ledger face is exactly the finite family of
dyadic-tolerance requests already recorded in the $\RegSeqRat$ spine.
\end{theorem}
\begin{proof}
Start with the carrier face. Definition~\ref{def:dyadic-rat-core-observation-row}
names the three endpoint rows: the rational-history carrier, the positive
unary denominator, and the dyadic-radius token. The endpoint carrier and the
finite dyadic request are supplied by
\autoref{thm:regseqrat-carrier-obligation}, while
\autoref{thm:rat-history-carrier-positive-denominator-equivalence} converts
the carrier row into the positive-denominator row.

Next read the classifier and stability faces. The pointwise stream classifier
obligation in \autoref{thm:regseqrat-classifier-obligation} exposes the
$\mathsf{RatHistoryClassifier}(d,e)$ endpoint comparison used by the
DyadicRatCore source. RatUp carrier and classifier transport carries the
rational-history rows along the same $\hsame$ comparison, and
\autoref{thm:rat-positive-unary-denominator-hsame-transport} carries the
positive-denominator row.

It remains only to identify the ledger. No request outside the
$\RegSeqRat$ spine is used: the dyadic-radius token is attached to the same
certified unary observation entry that supplies the endpoint rational row.
Thus the source package has precisely the stated carrier, classifier,
stability, and finite ledger faces over $\Hist$.
\end{proof}

\begin{theorem}[Phase Real dyadic stream RegSeq scope]
\label{thm:real-phase-dyadic-stream-regseq-scope}
Every DyadicRatCore request consumed by the Phase Real $\RegSeqRat$ spine is
exactly a $\mathsf{DyadicRatCoreObservationRow}$ over $\mathsf{BHist}$. Its
carrier, positive-denominator, dyadic-radius, classifier, and ledger faces are
read from the $\RatUp$ carrier and classifier transports together with the
$\RegSeqRat$ unary observation request. No $\RealUp$ completeness row, quotient
row, completion object, metric-completeness row, Classical datum, or standard
bridge row is part of this DyadicRatCore source scope.
\end{theorem}
\begin{proof}
Unpack \autoref{def:dyadic-rat-core-observation-row}. A consumed endpoint row is
the rational-history carrier, positive unary denominator, and dyadic-radius
token attached to the certified unary observation entry of the $\RegSeqRat$
spine.

Apply \autoref{thm:dyadic-rat-core-scoped-source-package}. Its carrier face is
the endpoint $\RatUp$ row, its classifier face is the
$\mathsf{RatHistoryClassifier}$ comparison, and its stability face is the same
$\hsame$ transport used by the $\RegSeqRat$ pointwise classifier obligation.

The remaining ledger component is the finite dyadic-tolerance request already
named by the $\RegSeqRat$ carrier and classifier obligations. Repacking these
faces gives exactly the Phase Real DyadicRatCore request scope, and there is no
slot in that package for quotient, completion, metric, Classical, or $\RealUp$
completeness data.
\end{proof}

\begin{theorem}[DyadicRatCore observation row hsame transport]
\label{thm:dyadic-rat-core-observation-row-hsame-transport}
Let $d,e:\Hist$. If $d$ has a DyadicRatCore observation row in the sense of
\autoref{def:dyadic-rat-core-observation-row} and $\hsame(d,e)$ holds, then
$e$ has a DyadicRatCore observation row. Its $\mathsf{RatHistoryCarrier}(e)$
component is the $\RatUp$ carrier transport of the carrier component at $d$,
its $\mathsf{PositiveUnaryDenominator}(e)$ component is transported by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}, and its
dyadic-radius token is the same certified observation ledger entry of the
$\RegSeqRat$ spine.
\end{theorem}
\begin{proof}
Unpack the row named by
\autoref{def:dyadic-rat-core-observation-row}. It consists of a
$\mathsf{RatHistoryCarrier}(d)$ row, a
$\mathsf{PositiveUnaryDenominator}(d)$ row, and a dyadic-radius token attached
to a certified unary observation entry in the $\RegSeqRat$ regularity ledger.

Transport the carrier face along $\hsame(d,e)$ using the $\RatUp$ carrier
transport already used in
\autoref{thm:dyadic-rat-core-scoped-source-package}. The compatibility between
the rational-history carrier and the positive-denominator row is the one
identified by
\autoref{thm:rat-history-carrier-positive-denominator-equivalence}.

Now apply
\autoref{thm:rat-positive-unary-denominator-hsame-transport} to carry the
positive-denominator component from $d$ to $e$. The endpoint rational row and
the certified dyadic request are the rows recorded by
\autoref{thm:regseqrat-carrier-obligation} inside the scoped spine of
\autoref{thm:regseqrat-stream-spine-scoped-package}.

The dyadic-radius token is not recomputed during transport: it remains attached
to the same certified observation ledger entry used by the source package.
Thus the transported carrier row, the transported positive-denominator row,
and the unchanged ledger token repack as a DyadicRatCore observation row for
$e$.
\end{proof}

\begin{theorem}[DyadicRatCore observation source transport determinacy]
\label{thm:dyadic-observation-source-transport-determinacy}
Let $d,e:\Hist$, and suppose $\hsame(d,e)$ is displayed. Fix one certified
$\RegSeqRat$ unary observation request whose source surface at $d$ is a
DyadicRatCore observation row. If two transported source packages are obtained
at $e$ by carrying that row along the same $\hsame(d,e)$ display through that
same certified request, then the two packages expose the same
$\mathsf{RatHistoryCarrier}(e)$ face, the same
$\mathsf{PositiveUnaryDenominator}(e)$ face, the same dyadic-radius token, and
the same $\mathsf{RatHistoryClassifier}$ face. No quotient row, completion row,
metric-completeness row, Classical datum, or standard bridge row can separate
the two transported source surfaces.
\end{theorem}
\begin{proof}
Unpack Definition~\ref{def:dyadic-rat-core-observation-row}. The source row at
$d$ consists only of the rational-history carrier, the positive unary
denominator row, and the dyadic-radius token attached to the named certified
$\RegSeqRat$ unary observation request.

Apply \autoref{thm:dyadic-rat-core-observation-row-hsame-transport} to each
transport along the displayed $\hsame(d,e)$ row. Both transported packages
therefore read their $\mathsf{RatHistoryCarrier}(e)$ and
$\mathsf{PositiveUnaryDenominator}(e)$ components from the same carrier
transport and the same positive-denominator transport.

Next identify the public source faces by
\autoref{thm:dyadic-rat-core-scoped-source-package}. Its carrier,
classifier, stability, and ledger faces are exactly the RatUp endpoint spine,
the positive-denominator transport row, and the finite dyadic request ledger;
there is no further source face available for a second transported package to
choose.

For the classifier face, use
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport}. Since both
packages use the same displayed $\hsame(d,e)$ row and the same certified
$\RegSeqRat$ request, the transported $\mathsf{RatHistoryClassifier}$ face is
the same face in both packages.

The dyadic-radius token remains attached to the original certified unary
observation ledger entry throughout the transport. Repacking these common
carrier, denominator, token, and classifier faces gives determinacy of the
transported source surface, and the excluded quotient, completion, metric,
Classical, and bridge rows have no slot in the scoped source package.
\end{proof}

\begin{theorem}[DyadicRatCore common-exponent transport determinacy]
\label{thm:dyadic-observation-common-exponent-determinacy}
Let $d,e,d',e',r,s:\Hist$. Suppose $d$ and $e$ carry
$\mathsf{DyadicRatCoreObservationRow}$ packages for the same certified
$\RegSeqRat$ observation request, with $r$ and $s$ naming the unary-radius
histories of that request. Suppose
$\mathsf{RatHistoryClassifier}(d,e)$ holds, and suppose $\hsame(d,d')$ and
$\hsame(e,e')$ are displayed. If the packages at $d'$ and $e'$ are obtained by
transporting the source rows along those displayed $\hsame$ rows without
changing the certified request ledger, then the two transported packages
expose the same $\RatUp$ carrier faces, the same positive-unary-denominator
faces, the same unary radius/request token, and the same
$\mathsf{RatHistoryClassifier}(d',e')$ surface. No quotient row, completion
row, metric-completeness row, Classical datum, or standard bridge row
contributes an additional common-exponent choice.
\end{theorem}
\begin{proof}
First transport the classifier surface. Apply
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport} to the
source comparison $\mathsf{RatHistoryClassifier}(d,e)$ and to the displayed
rows $\hsame(d,d')$ and $\hsame(e,e')$. The transported endpoint comparison is
therefore the single surface $\mathsf{RatHistoryClassifier}(d',e')$ attached
to the same certified $\RegSeqRat$ request.

Next transport the two endpoint source rows. Apply
\autoref{thm:dyadic-rat-core-observation-row-hsame-transport} to the row at
$d$ and to the row at $e$. Because the request ledger is unchanged, the
transported rows inherit the same dyadic request token and the same
positive-unary-denominator transport rows used by the source package.

Finally compare the transported packages with
\autoref{thm:dyadic-observation-source-transport-determinacy}. The theorem
identifies the $\RatUp$ carrier face, the positive-denominator face, the
dyadic-radius token, and the classifier face for transports through a fixed
certified request. These identified faces are exactly the common-exponent
surface of the two presentations, and the scoped source package has no field
for quotient, completion, metric-completeness, Classical, or standard bridge
data.
\end{proof}

\begin{theorem}[Dyadic observation transport RealUp feed determinacy]
\label{thm:dyadic-observation-transport-realup-feed-determinacy}
Let $d,e:\Hist$, and suppose $\hsame(d,e)$ is displayed. Fix one certified
$\RegSeqRat$ unary observation request whose source surface at $d$ is a
$\mathsf{DyadicRatCoreObservationRow}$. If two RealUp finite-window feed
packages are obtained by first transporting that source to $e$ along the same
$\hsame(d,e)$ row and then applying the DyadicRatCore public observation feed,
then the two feed packages expose the same RatUp endpoint carrier, the same
positive-denominator row, the same dyadic-radius ledger token, the same RealUp
finite-window source face, and the same exclusion boundary. No quotient row,
completion row, Classical datum, external metric primitive, RealUp completeness
claim, or standard bridge row can distinguish the two feeds.
\end{theorem}
\begin{proof}
Project the transported sources with
\autoref{thm:dyadic-observation-source-transport-determinacy}. Both source
packages at $e$ therefore expose the same RatUp endpoint carrier, the same
positive-denominator row, the same dyadic-radius token, and the same
$\mathsf{RatHistoryClassifier}$ face.

Feed these common source rows through
\autoref{thm:dyadicratcore-public-observation-realup-window-feed}. The public
observation feed consumes exactly the transported DyadicRatCore source, the
finite dyadic request ledger, and the RealUp finite-window source face recorded
by that ledger.

It remains only to compare the visible fields of the two feeds. Since the
input source projections are common and the feed theorem has no slot for a
second quotient, completion, Classical, metric, completeness, or bridge datum,
field projection gives the same RatUp endpoint carrier, positive-denominator
row, dyadic-radius token, RealUp finite-window source face, and exclusion
boundary in both packages.
\end{proof}

The intended Lean target shape for this boundary is
\texttt{BEDC.Derived.RealUp.DyadicRatCore\_scoped\_source\_package}.
