\begin{theorem}[DyadicRatCore carrier and classifier obligations]
\label{thm:dyadic-rat-core-carrier-classifier-obligations}
The carrier and classifier obligations for DyadicRatCore are the certificate
boundary whose carrier row is
$\mathsf{DyadicRatCoreObservationRow}(d)$ from
\autoref{def:dyadic-rat-core-observation-row}, whose classifier row is
$\mathsf{RatHistoryClassifier}(d,e)$ transported through
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport}, and whose
source package is the scoped boundary of
\autoref{thm:dyadic-rat-core-scoped-source-package}. Concretely, for each
endpoint history $d:\Hist$, the carrier obligation reads exactly the
$\mathsf{RatHistoryCarrier}(d)$ row, the
$\mathsf{PositiveUnaryDenominator}(d)$ row, and the dyadic-radius token already
recorded by the $\RegSeqRat$ ledger. For each classifier comparison
$\mathsf{RatHistoryClassifier}(d,e)$, the classifier obligation transports
that three-field row along $\hsame(d,e)$ and repacks no additional completion,
quotient, or external metric datum.
\end{theorem}
\begin{proof}
Unpack the definition of the observation row. The carrier face is precisely the
triple named in \autoref{def:dyadic-rat-core-observation-row}: a RatUp endpoint
carrier, a positive unary denominator row, and the dyadic-radius token from the
regularity ledger.

Now use \autoref{thm:dyadic-rat-core-scoped-source-package}. It identifies the
source of every such row as the RatUp endpoint history together with the
$\RegSeqRat$ observation request, so the carrier obligation has no independent
object outside that scoped package.

For the classifier face, apply
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport}. The
$\mathsf{RatHistoryClassifier}$ comparison supplies the $\hsame$ transport of
the endpoint carrier, denominator row, and dyadic token, which is exactly the
DyadicRatCore classifier obligation.
\end{proof}

\begin{theorem}[RealUp-RegSeqRat finite-window projection]
\label{thm:realup-regseqrat-finite-window-projection}
A finite DyadicRatCore observation package over a certified unary request
projects to the exact $\RegSeqRat$ finite-window observation surface consumed by
$\RealUp$. The projected surface consists of the $\RatUp$ endpoint carrier, the
positive unary denominator row, the dyadic-radius token, the $\StreamNameUp$
request name, the $\RegSeqRat$ regularity ledger, $\hsame$ transport for the
endpoint and denominator rows, and finite ledger provenance for the displayed
window. It exports no quotient carrier, no completion object, no
metric-completeness row, no Classical representative, and no standard bridge
datum.
\end{theorem}
\begin{proof}
Project the finite package to its three visible faces. The package theorem
\autoref{thm:dyadic-rat-core-finite-observation-obligation-package} identifies
these faces as the carrier-classifier face, the finite arithmetic face, and the
radius-distance face over the same certified unary request.

The endpoint rows are read from
\autoref{thm:dyadic-rat-core-carrier-classifier-obligations}. They give exactly
the $\RatUp$ carrier, positive unary denominator row, dyadic-radius token, and
$\hsame$ transport required by the $\RegSeqRat$ finite window.

The radius and distance rows are read from
\autoref{thm:dyadic-rat-core-radius-distance-obligations}. They keep the
dyadic-radius refinement, dyadic distance, absolute-value row, request name,
and regularity ledger inside the same finite observation ledger.

Finally repack these shared rows as the $\RegSeqRat$ finite-window projection.
Since the source package has no coordinate for a quotient carrier, completion
object, metric-completeness witness, Classical representative, or standard
bridge, the projection passed to $\RealUp$ contains none of those data.
\end{proof}

\begin{theorem}[DyadicRatCore arithmetic-stability obligations]
\label{thm:dyadic-rat-core-arithmetic-stability-obligations}
The arithmetic-stability obligations for DyadicRatCore are the finite
certificate rows required to read dyadic rational endpoint arithmetic through
the BEDC source package. They consist of operation rows for dyadic addition,
negation, subtraction, multiplication, and positive-denominator division;
classifier congruence rows showing that $\mathsf{RatHistoryClassifier}$ and
$\hsame$ transport carry equivalent inputs to equivalent operation outputs;
denominator-preservation rows showing that the
$\mathsf{PositiveUnaryDenominator}$ face remains in the DyadicRatCore carrier
after each operation; and finite ledger provenance rows tying every requested
operation to the dyadic observation ledger consumed by the $\RegSeqRat$
regularity check. These are obligations for formal proof targets over the
existing RatUp, StreamNameUp, $\mathsf{BHist}$, $\hsame$, and dyadic ledger
interfaces; they do not assert arithmetic laws beyond that certificate
inventory.
\end{theorem}
\begin{proof}
Read every operation input as a DyadicRatCore observation row using
\autoref{thm:dyadic-rat-core-carrier-classifier-obligations}. This exposes the
RatUp carrier, the positive denominator row, and the dyadic-radius token at
each endpoint.

The operation row is then a finite BEDC request over the same endpoint
histories. RatUp supplies the rational endpoint operation, StreamNameUp keeps
the requested stream observation name stable, and the dyadic ledger records the
finite observation request consumed downstream by $\RegSeqRat$.

Classifier congruence is the same transport pattern used for the carrier and
classifier boundary. The $\mathsf{RatHistoryClassifier}$ comparison and
$\hsame$ denominator transport carry equivalent inputs to the corresponding
operation outputs, while denominator preservation keeps the result inside the
DyadicRatCore observation-row format.
\end{proof}

\begin{theorem}[DyadicRatCore radius, distance, and absolute-value obligations]
\label{thm:dyadic-rat-core-radius-distance-obligations}
The monotone dyadic-radius, distance, and absolute-value obligations for
DyadicRatCore are the certificate rows consumed by $\RegSeqRat$ regularity and
by the $\RealUp$ sealing boundary. The radius obligation states that
strengthening a finite dyadic-radius request preserves the same RatUp endpoint
carrier and transports only the ledger token. The distance obligation states
that dyadic endpoint distance is read from two
$\mathsf{DyadicRatCoreObservationRow}$ inputs, is stable under
$\mathsf{RatHistoryClassifier}$ and $\hsame$ transport, and records its output
in the same finite ledger. The absolute-value obligation is the unary instance
of the same pattern: it reads one endpoint row, preserves positive-denominator
and classifier compatibility, and exposes the output row required by the
$\RegSeqRat$ regularity spine before $\RealUp$ sealing.
\end{theorem}
\begin{proof}
Begin with the carrier and classifier package of
\autoref{thm:dyadic-rat-core-carrier-classifier-obligations}. It gives the
endpoint rows and their $\mathsf{RatHistoryClassifier}$ transport inside
$\mathsf{BHist}$ and $\hsame$.

For radius monotonicity, refine the finite dyadic request in the ledger. The
RatUp endpoint carrier and the positive-denominator face remain fixed, while
the dyadic-radius token is replaced by the stronger certified request used by
the $\RegSeqRat$ regularity spine.

For distance and absolute value, use the same operation-row shape as in
\autoref{thm:dyadic-rat-core-arithmetic-stability-obligations}. The binary
distance row and the unary absolute-value row read only DyadicRatCore carrier
data, preserve classifier compatibility under $\hsame$, and expose exactly the
finite output rows consumed by the RealUp sealing interface.
\end{proof}

\begin{theorem}[DyadicRatCore finite observation obligation package]
\label{thm:dyadic-rat-core-finite-observation-obligation-package}
A finite DyadicRatCore observation package over a certified unary request is
exactly the conjunction of the carrier and classifier face, the arithmetic
operation face, and the monotone-radius face already displayed in this
inventory. Its first component is the
$\mathsf{DyadicRatCoreObservationRow}$ carrier and classifier boundary of
\autoref{thm:dyadic-rat-core-carrier-classifier-obligations}. Its second
component is the finite dyadic addition, negation, subtraction,
multiplication, and positive-denominator division rows of
\autoref{thm:dyadic-rat-core-arithmetic-stability-obligations}. Its third
component is the monotone dyadic-radius, dyadic-distance, and absolute-value
surface of \autoref{thm:dyadic-rat-core-radius-distance-obligations}. All
three components are read over the same $\mathsf{BHist}$ endpoints, $\RatUp$
carrier rows, $\StreamNameUp$ request name, $\RegSeqRat$ regularity ledger,
$\hsame$ transport, and finite observation ledger data. The package has no
coordinate for quotient carriers, completion objects, metric completeness,
Classical data, or standard bridges.
\end{theorem}
\begin{proof}
Project a candidate finite observation package to its carrier/classifier
coordinate. By
\autoref{thm:dyadic-rat-core-carrier-classifier-obligations}, this coordinate
is precisely the $\mathsf{DyadicRatCoreObservationRow}$ face over the RatUp
endpoint, positive denominator, dyadic-radius token, $\mathsf{BHist}$ history,
and $\hsame$ comparison rows.

Project the same package to its operation coordinate. By
\autoref{thm:dyadic-rat-core-arithmetic-stability-obligations}, the only
operation rows present are the finite dyadic arithmetic rows whose endpoints,
classifier transports, denominator preservation, $\StreamNameUp$ request name,
and $\RegSeqRat$ ledger are the rows already exposed by the first coordinate.

Project the radius-distance coordinate. By
\autoref{thm:dyadic-rat-core-radius-distance-obligations}, this coordinate
contains only monotone-radius refinement, dyadic distance, and absolute-value
rows over the same finite ledger and the same endpoint classifier transport.

Conversely, given those three faces over the same histories, carriers, request
name, regularity ledger, $\hsame$ transport, and finite observation ledger,
repack them as the DyadicRatCore observation package. The repacking has no
constructor input for a host quotient carrier, completion object, metric
completeness witness, Classical datum, or standard bridge, so none of those
objects is exported to $\RegSeqRat$ or $\RealUp$.
\end{proof}
