\begin{theorem}[RegSeqRat dyadic observation coverage]
\label{thm:regseqrat-dyadic-observation-coverage}
Let $s:\Hist\to\Hist$ carry a $\RegSeqRat$ stream certificate spine, and let
$n$ be a certified $\mathsf{UnaryHistory}$ observation index of that spine. Then
the exposed endpoint $s(n)$ has a DyadicRatCore observation row in the sense of
\autoref{def:dyadic-rat-core-observation-row}. Moreover, if a stream classifier
is transported pointwise along $\hsame$ to a target endpoint $s'(n)$, then the
same pointwise transport carries this DyadicRatCore observation row to
$s'(n)$.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:regseqrat-stream-certificate-spine}. At the
certified observation index $n$, \autoref{thm:regseqrat-carrier-obligation}
supplies the endpoint $\mathsf{RatHistoryCarrier}(s(n))$ row and the
dyadic-tolerance witness recorded in the regularity ledger.

The positive-denominator component is read from the RatUp carrier interface:
\autoref{thm:rat-history-carrier-positive-denominator-equivalence} converts the
endpoint carrier row into $\mathsf{PositiveUnaryDenominator}(s(n))$. These
three pieces are exactly the DyadicRatCore observation row of
\autoref{def:dyadic-rat-core-observation-row}.

For the transported endpoint, apply
\autoref{thm:regseqrat-classifier-obligation} to recover the pointwise
$\mathsf{RatHistoryClassifier}$ row carried by the stream classifier. Its
$\hsame$ comparison transports the endpoint carrier/classifier face through the
existing $\mathsf{RatHistoryClassifier}$ transport, and
\autoref{thm:rat-positive-unary-denominator-hsame-transport} transports the
positive-denominator row to $s'(n)$.

The dyadic-radius token is attached to the same certified observation request
in the spine ledger, so no additional completion or quotient datum is needed.
Thus the transported package is again a DyadicRatCore observation row.
\end{proof}

\begin{theorem}[DyadicRatCore observation row finite-ledger extraction]
\label{thm:dyadic-rat-core-observation-row-finite-ledger-extraction}
Let $s:\Hist\to\Hist$ carry a $\RegSeqRat$ stream certificate spine. For every
finite BEDC ledger bundle $L$ of certified $\mathsf{UnaryHistory}$ observation
requests in that spine, there is a finite family indexed by the entries
$n\in L$ whose $n$-th member is a
$\mathsf{DyadicRatCoreObservationRow}(s(n))$ in the sense of
\autoref{def:dyadic-rat-core-observation-row}. This family is read from the
DyadicRatCore scoped source package of
\autoref{thm:dyadic-rat-core-scoped-source-package}; its carrier and classifier
faces are precisely the $\RegSeqRat$ carrier and classifier obligations of
\autoref{thm:regseqrat-carrier-obligation} and
\autoref{thm:regseqrat-classifier-obligation}.

Moreover, if a stream classifier transports the spine pointwise to a target
stream $s':\Hist\to\Hist$, then the same finite family transports endpointwise:
for each certified request $n\in L$, the transported endpoint row is a
$\mathsf{DyadicRatCoreObservationRow}(s'(n))$.
\end{theorem}
\begin{proof}
Induct on the finite ledger bundle $L$. The empty bundle has no certified
observation entry, so the indexed family and its transported endpoint family
are empty.

For a cons bundle, write the displayed head request as the certified
$\mathsf{UnaryHistory}$ observation index $n$ and write $L'$ for the remaining
finite bundle. Apply
\autoref{thm:regseqrat-dyadic-observation-coverage} to the head request in the
$\RegSeqRat$ spine. It supplies the row
$\mathsf{DyadicRatCoreObservationRow}(s(n))$ by unpacking
\autoref{def:dyadic-rat-core-observation-row}, with the carrier datum supplied
by \autoref{thm:regseqrat-carrier-obligation} and the classifier transport
datum supplied by \autoref{thm:regseqrat-classifier-obligation}.

The source package identification in
\autoref{thm:dyadic-rat-core-scoped-source-package} says that no additional
ledger face is used beyond these certified unary observation entries. Therefore
the tail induction hypothesis extracts the finite family over $L'$ from the
same spine and transports it along the same pointwise classifier.

Adjoin the head row to the tail family. The transported head row is provided by
the transported clause of
\autoref{thm:regseqrat-dyadic-observation-coverage}, and the transported tail is
the induction hypothesis. Hence the cons bundle extracts and transports the
claimed finite family endpointwise.
\end{proof}

\begin{theorem}[RegSeqRat observation ledger dyadic endpoint coverage]
\label{thm:regseqrat-observation-ledger-dyadic-endpoint-coverage}
Let $s:\Hist\to\Hist$ carry a $\RegSeqRat$ stream certificate spine, and let
$L$ be a finite BEDC ledger bundle of certified unary $\RegSeqRat$
observations. Every dyadic endpoint row visible to a downstream $\RealUp$
finite-window consumer is one of the rows extracted by
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction},
transported endpointwise along the same pointwise classifier.

Equivalently, the consumer-visible endpoint surface is exhausted by the finite
family of $\mathsf{DyadicRatCoreObservationRow}(s(n))$ rows indexed by
certified entries $n\in L$, together with their pointwise transported endpoint
rows. No hidden selector, quotient representative, completion object, or host
index can produce an additional dyadic endpoint row.
\end{theorem}
\begin{proof}
Induct on the finite ledger bundle $L$. The empty bundle has no certified unary
observation entry, so a downstream finite-window consumer has no dyadic endpoint
row to read from that ledger.

For a cons bundle, write the head request as $n$ and the tail as $L'$. Apply
\autoref{thm:regseqrat-dyadic-observation-coverage} to the head. It gives the
visible $\mathsf{DyadicRatCoreObservationRow}(s(n))$ and its pointwise
transported endpoint row.

Apply
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction} to the
tail ledger $L'$. The induction hypothesis says every endpoint row visible from
$L'$ is already in the extracted tail family and transported along the same
pointwise classifier.

Adjoin the head row to the extracted tail family. Carrier projection leaves no
projection for a hidden selector, quotient representative, completion object, or
host index, so the displayed finite family exhausts the downstream
consumer-visible dyadic endpoint rows.
\end{proof}

\begin{theorem}[RegSeqRat constant and transport obligation]
\label{thm:regseqrat-constant-and-transport-obligation}
The constant and transport obligations for $\RegSeqRat$ are the inhabitation of
the constant rational-observation stream and pointwise $\hsame$ transport of
stream classifiers. For every $d:\Hist$ with
$\mathsf{RatHistoryCarrier}(d)$, $\mathsf{RatConstStream}_d$ carries a
$\RegSeqRat$ spine. If $s,t$ are classified streams and $s',t'$ are pointwise
$\hsame$ transports over certified unary observations, then the transported
stream-name classifier $\mathsf{RatStreamNameClassifier}(s',t')$ is part of
the same obligation set.
\end{theorem}
\begin{proof}
Definition~\ref{def:regseqrat-stream-certificate-spine} identifies the
constant case as a spine over a stream-name carrier plus a regularity ledger.
Apply \autoref{thm:regseqrat-constant-stream-spine} to the supplied
$\mathsf{RatHistoryCarrier}(d)$; the resulting ledger is constant at every
certified unary observation.

For transport, apply
\autoref{thm:regseqrat-stream-classifier-stability-spine} to the two endpoint
$\hsame$ rows. It supplies the transported pointwise $\RatUp$ classifiers and
repackages them as $\mathsf{RatStreamNameClassifier}(s',t')$.

The scoped package
\autoref{thm:regseqrat-stream-spine-scoped-package} places the constant and
transport clauses in one certificate package, and
\autoref{thm:regseqrat-realup-seal-consumes-stream-spine} shows that these
clauses are sufficient for the downstream RealUp seal to consume the stream
classifier.
\end{proof}

\begin{theorem}[RegSeqRat public rational-stream interface]
\label{thm:regseqrat-public-rational-stream-interface}
A $\RegSeqRat$ public rational-stream interface is exactly the package formed
from \autoref{thm:regseqrat-dyadic-observation-coverage},
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction},
\autoref{thm:regseqrat-constant-and-transport-obligation},
\autoref{thm:regseqrat-streamname-scoped-interface}, and
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation}. Its public
template has the following ten fields:
\begin{enumerate}
  \item the traditional target is the regular rational Cauchy stream spine;
  \item the BEDC source is DyadicRatCore plus StreamNameUp plus RatUp over
  $\Hist$;
  \item the carrier is the $\RegSeqRat$ stream certificate spine;
  \item the classifier is the pointwise
  $\mathsf{RealUnaryStreamClassifier}$ and
  $\mathsf{RatStreamNameClassifier}$ row;
  \item stability is the family of pointwise $\hsame$ transport rows;
  \item the ledger consists of finite unary observation requests and
  dyadic-tolerance tokens;
  \item the core theorem list is the five cited blocks above;
  \item exactness says the RealUp seal consumes exactly those finite rows;
  \item no standard bridge datum is part of the interface;
  \item the status is a paper-side public interface target.
\end{enumerate}
\end{theorem}
\begin{proof}
Collect the five cited packages in the displayed order. The first package
supplies DyadicRatCore observation coverage at each certified unary request,
the second extracts finite ledger families from any selected observation
bundle, and the third supplies the constant stream and pointwise transport
obligations.

For every selected observation, use
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction}. It
turns the finite unary ledger entries and dyadic-tolerance tokens into endpoint
DyadicRatCore rows, and its transported clause carries the same rows along the
chosen pointwise $\hsame$ comparison.

Next use \autoref{thm:regseqrat-streamname-scoped-interface}. It supplies the
stream-name interface, the classifier transport row, and the endpoint carrier
rows needed to read the $\mathsf{RealUnaryStreamClassifier}$ and
$\mathsf{RatStreamNameClassifier}$ components pointwise.

Finally apply
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation}. The seal
obligation identifies the data consumed by RealUp with the same finite
observation rows already extracted from the $\RegSeqRat$ ledger. Therefore the
package exposes the stated public rational-stream interface without quotient,
completion, metric-completeness, arithmetic/order, Classical, or standard
bridge data.
\end{proof}

\begin{theorem}[RegSeqRat finite-window seal exactness]
\label{thm:regseqrat-finite-window-seal-exactness}
Let $s:\Hist\to\Hist$ carry a $\RegSeqRat$ rational-observation stream
certificate spine, and let $\mathcal{P}:\mathsf{ProbeBundle}$ be a certified
finite bundle of unary observation requests. The finite observation rows
accepted by the $\RegSeqRat$-to-$\RealUp$ seal over $\mathcal{P}$ are exactly
the union of the DyadicRatCore endpoint observation-row family extracted by
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction} and the
$\StreamNameUp$ finite-window rows exposed by
\autoref{thm:streamname-public-finite-window-interface}.

Equivalently, a finite window feeds the seal precisely when its carrier,
classifier, pointwise stability, dyadic-ledger, and stream-name finite-window
rows are present in the public rational-stream interface of
\autoref{thm:regseqrat-public-rational-stream-interface}. This exactness claim
does not introduce quotient carriers, completion objects, $\RealUp$
completeness, metric completeness, Classical data, or standard bridge status.
\end{theorem}
\begin{proof}
Expose the public rational-stream package by
\autoref{thm:regseqrat-public-rational-stream-interface}. Its carrier,
classifier, stability, ledger, and stream-name fields are the only rows made
available to the downstream seal.

For the forward direction, take a row accepted by the seal over
$\mathcal{P}$. Apply
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation} to read it as a
finite unary observation request with the recorded dyadic-tolerance token and
endpoint $\RatUp$ data. Then apply
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction}
endpointwise to place the endpoint datum in the DyadicRatCore observation-row
family, and use \autoref{thm:streamname-public-finite-window-interface} to read
the same request as a stream-name finite-window classifier row.

For the reverse direction, suppose the finite window carries the displayed
DyadicRatCore endpoint family together with the $\StreamNameUp$ finite-window
interface rows. The public package supplies the corresponding carrier,
classifier, pointwise stability, and dyadic-ledger fields, so
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation} gives the seal
consumer for those rows.

Finally apply \autoref{thm:regseqrat-seal-finite-window-source-coverage}. It
identifies the finite-window source package consumed by the seal with exactly
the same DyadicRatCore, dyadic-ledger, and $\StreamNameUp$ rows, so no further
quotient, completion, metric, Classical, $\RealUp$ completeness, or bridge data
can enter the seal interface.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RegseqratFiniteWindowSealExactness}

\begin{theorem}[RegSeqRat finite-window seal overlap compatibility]
\label{thm:regseqrat-finite-window-seal-overlap-compatibility}
Let $s,t:\Hist\to\Hist$ carry $\RegSeqRat$ rational-observation stream
certificate spines. Let $\mathcal P,\mathcal Q:\mathsf{ProbeBundle}$ be
certified finite observation windows, and let
$\mathcal R:\mathsf{ProbeBundle}$ be a certified common sub-bundle of both
$\mathcal P$ and $\mathcal Q$. Suppose the $\RegSeqRat$-to-$\RealUp$ seal
packages over $\mathcal P$ and $\mathcal Q$ agree after restriction to
$\mathcal R$ on the StreamName finite-window classifier, the DyadicRatCore
observation rows, the unary observation witnesses, and the dyadic ledger
tokens.

Then the two $\RealUp$ seal readbacks restrict to the same consumer-facing
package over $\mathcal R$. This common package contains only the finite-window
classifier, the pointwise $\mathsf{RatHistoryClassifier}$ rows, the dyadic
observation rows, the regularity ledger, and the $\RealUp$ observation
classifier; it contains no completion object, quotient carrier, or host-index
equality row.
\end{theorem}
\begin{proof}
First restrict the two finite windows to the common sub-bundle
$\mathcal R$. By
\autoref{thm:streamname-regseqrat-overlap-pullback-handoff}, the restricted
StreamName handoff rows classify the same consumer-facing finite-window tuple
over $\mathcal R$.

Now read each restricted seal with
\autoref{thm:regseqrat-finite-window-seal-exactness}. Each readback is
therefore exhausted by the StreamName finite-window rows and the DyadicRatCore
endpoint observation-row family over the same common bundle.

Identify the dyadic component through
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction}. The
assumed agreement of unary witnesses and dyadic ledger tokens gives the same
endpoint observation rows on the two restricted packages.

Finally repack the identified rows using
\autoref{thm:real-phase-seal-consumer-exactness}. The resulting
consumer-facing $\RealUp$ package over $\mathcal R$ is the same on both sides,
and the cited exactness boundaries expose no completion, quotient, or
host-index equality coordinate.
\end{proof}

\begin{theorem}[Phase Real seal consumer exactness]
\label{thm:real-phase-seal-consumer-exactness}
Let $s:\Hist\to\Hist$ carry a $\RegSeqRat$ rational-observation stream spine,
and let $\mathcal{P}:\mathsf{ProbeBundle}$ be a certified finite-window package.
Every consumer-facing row of the $\RealUp$ seal over $\mathcal{P}$ factors
through exactly four displayed surfaces: the DyadicRatCore endpoint observation
family of \autoref{def:dyadic-rat-core-observation-row}, the $\StreamNameUp$
finite-window classifier rows, the $\RegSeqRat$ regularity ledger, and the
$\Eone$-sealed $\RealUp$ observation row. Conversely, those four surfaces
assemble the consumer-facing seal package for the same finite window.

Thus the Phase Real seal consumer reads precisely the endpoint carrier,
positive-denominator, dyadic-radius, stream-name finite-window, regularity
ledger, and $\Eone$ seal rows exposed by the certified spine. It does not read a
quotient carrier, completion object, Classical choice row, metric-completeness
row, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
For a consumed seal row, first apply
\autoref{thm:regseqrat-finite-window-seal-exactness}. The row is therefore
drawn from the DyadicRatCore endpoint family and the $\StreamNameUp$
finite-window classifier rows in the same certified window.

The DyadicRatCore component is the observation family named by
\autoref{def:dyadic-rat-core-observation-row} and scoped by
\autoref{thm:dyadic-rat-core-scoped-source-package}. The stream-name component
is supplied by the public rational-stream interface of
\autoref{thm:regseqrat-public-rational-stream-interface}, which also carries the
$\RegSeqRat$ regularity ledger and the $\Eone$ seal row consumed by $\RealUp$.

For the converse direction, start with exactly those four surfaces over
$\mathcal{P}$. The public rational-stream interface packages the endpoint
carrier, classifier, stability, and regularity rows; the finite-window seal
exactness theorem then assembles them as the consumer-facing $\RealUp$ seal
package. Since every cited surface is part of this finite BEDC ledger, no
quotient, completion, Classical, metric-completeness, or ambient completeness
row can be consumed.
\end{proof}
