\begin{theorem}[RegSeqRat dyadic ledger and RealUp seal obligation]
\label{thm:regseqrat-dyadic-ledger-and-real-seal-obligation}
The dyadic-ledger and $\RealUp$ seal obligation for $\RegSeqRat$ consists of
finite unary observation indices, the endpoint $\RatUp$ rows read at those
indices, the dyadic-tolerance witnesses used by regularity, and the seal export
of the recorded $\mathsf{RealUnaryStreamClassifier}$ row. Whenever sealed
$\RealUp$ candidates expose streams satisfying the $\RegSeqRat$ spine and
record their stream comparison row, the seal exports the RealUp observation
classifier required by \autoref{def:real-classifier-specification}.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:regseqrat-stream-certificate-spine}. Its ledger is
finite at the level of requested unary observations and dyadic-tolerance
checks, and each ledger entry is backed by endpoint $\RatUp$ carrier and
classifier rows.

The constant ledger is supplied by
\autoref{thm:regseqrat-constant-stream-spine}. The general endpoint and
transport rows are supplied by
\autoref{thm:regseqrat-stream-classifier-stability-spine}, while
\autoref{thm:regseqrat-stream-spine-scoped-package} gathers the ledger,
classifier, constant, and transport faces as one scoped certificate package.

Finally apply \autoref{thm:regseqrat-realup-seal-consumes-stream-spine}. The
seal reads the already recorded
$\mathsf{RealUnaryStreamClassifier}$ row and exports exactly the observation
classifier required by the RealUp boundary, without adding quotient or
completion data.
\end{proof}

\begin{theorem}[DyadicRatCore obligation boundary package]
\label{thm:dyadic-rat-core-obligation-boundary-package}
The DyadicRatCore obligation boundary consists exactly of the carrier,
classifier, arithmetic-stability, monotone-radius, distance and absolute-value,
operation-stability, finite-ledger extraction, and $\RegSeqRat$ seal faces
listed in this section. Its carrier face is
\autoref{thm:dyadic-rat-core-carrier-obligation}; its classifier face is
\autoref{thm:dyadic-rat-core-classifier-obligation}; its dyadic arithmetic
face is \autoref{thm:dyadic-rat-core-arithmetic-stability-obligation}; its
monotone-radius face is
\autoref{thm:dyadic-rat-core-monotone-radius-obligation}; its distance and
absolute-value face is
\autoref{thm:dyadic-rat-core-distance-absolute-obligation}; its operation
stability face is
\autoref{thm:dyadic-rat-core-operation-stability-obligation}; its finite
ledger extraction face is
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction}; and
its downstream seal face is
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation}.

No face in this package reads a quotient, a completion object, Classical data,
or an external metric primitive. Every named face is read from $\mathsf{BHist}$,
$\hsame$, RatUp endpoint histories, StreamNameUp request names, the
DyadicRatCore observation row, and the finite dyadic ledger consumed by
$\RegSeqRat$ and $\RealUp$.
\end{theorem}
\begin{proof}
Read the carrier and classifier faces first. Apply
\autoref{thm:dyadic-rat-core-carrier-obligation} and
\autoref{thm:dyadic-rat-core-classifier-obligation}. These identify the
endpoint rows, their $\hsame$ transport, and the RatUp positive-denominator
source used by the observation row.

Next read the stability inventory. Apply
\autoref{thm:dyadic-rat-core-arithmetic-stability-obligation},
\autoref{thm:dyadic-rat-core-monotone-radius-obligation},
\autoref{thm:dyadic-rat-core-distance-absolute-obligation}, and
\autoref{thm:dyadic-rat-core-operation-stability-obligation}. Together they
cover the dyadic arithmetic, radius refinement, distance, absolute-value, and
operation rows without adding a separate metric carrier.

Finally read the ledger and seal faces. Apply
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction} for the
finite family of endpoint rows, and apply
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation} for the
$\RegSeqRat$ ledger consumed by the $\RealUp$ seal.

The cited theorem list exhausts the displayed boundary: each clause is one of
the named faces above, and the proofs of those faces read only $\mathsf{BHist}$,
$\hsame$, endpoint histories, request names, observation rows, and finite
ledger entries. Hence the package has no quotient, completion object,
Classical datum, or external metric primitive as an input.
\end{proof}

\begin{theorem}[DyadicRatCore scoped dependency package]
\label{thm:dyadic-rat-core-scoped-dependency-package}
Every obligation face named in
\autoref{thm:dyadic-rat-core-obligation-boundary-package} is grounded only in
$\mathsf{BHist}$, $\hsame$, the unary $\Cont$ context laws, RatUp endpoint
carrier and classifier rows, RatUp positive-denominator transport,
StreamNameUp request names, the DyadicRatCore observation row, finite dyadic
ledger entries, and the $\RegSeqRat$ and $\RealUp$ seal rows. Thus the
DyadicRatCore boundary has a scoped source package whose dependency chains are
exactly the listed primitive BEDC rows.
\end{theorem}
\begin{proof}
First read the carrier and classifier sources. Apply
\autoref{thm:dyadic-rat-core-carrier-obligation} and
\autoref{thm:dyadic-rat-core-classifier-obligation}. These two faces expose the
RatUp endpoint carrier rows, endpoint classifier rows, $\hsame$ transport, and
positive-denominator transport used by the DyadicRatCore observation row.

Next read the arithmetic and radius sources. Apply
\autoref{thm:dyadic-rat-core-arithmetic-stability-obligation} and
\autoref{thm:dyadic-rat-core-monotone-radius-obligation}. Their inputs are the
same endpoint rows, StreamNameUp requests, dyadic ledger entries, and unary
$\Cont$ context laws already displayed by the boundary package.

The metric-shaped faces add no separate metric carrier. Apply
\autoref{thm:dyadic-rat-core-distance-absolute-obligation} and
\autoref{thm:dyadic-rat-core-operation-stability-obligation}. They read the
distance, absolute-value, and operation rows through the DyadicRatCore
observation row and transport them along the same $\hsame$ and context data.

Finally read the finite ledger and seal sources. Apply
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction} for the
finite family of dyadic endpoint entries, and apply
\autoref{thm:regseqrat-dyadic-ledger-and-real-seal-obligation} for the
$\RegSeqRat$ ledger consumed by the $\RealUp$ seal. These are precisely the
remaining faces in
\autoref{thm:dyadic-rat-core-obligation-boundary-package}, so every scoped
dependency chain has been bound to the displayed primitive sources.
\end{proof}

\begin{closurestatus}{\DyadicRatCore}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The DyadicRatCore obligation faces are bound to $\mathsf{BHist}$, $\hsame$, unary $\Cont$ context laws, RatUp endpoint carrier and classifier rows, RatUp positive-denominator transport, StreamNameUp request names, the DyadicRatCore observation row, finite dyadic ledger entries, and the $\RegSeqRat$ and $\RealUp$ seal rows.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.RealUp.DyadicRatCore\_scoped\_source\_package}
  \bridgestatus{none}
  \notclaimed{This boundary does not claim RealUp completeness, quotient construction, or a standard bridge.}
  \upgradepath{The next grade requires a public-object surface or a checked bridge beyond the DyadicRatCore scoped source package.}
\end{closurestatus}
