\begin{theorem}[GaloisGroupUp composition associativity row]
\label{thm:galoisgroup-composition-associativity-row}
Let $x$, $y$, and $z$ be accepted fixed-base automorphism-action rows of an
automorphism-action packet
$(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. Suppose the target
endpoint of $x$ is $\hsame$-classified with the source endpoint of $y$, the
target endpoint of $y$ is $\hsame$-classified with the source endpoint of $z$,
and the two finite $\mathsf{Cont}$ parenthesizations
$(z\circ y)\circ x$ and $z\circ(y\circ x)$ are both displayed by the composition
row $m$. Then the two parenthesized rows are classified by the inherited
$\GroupUp$ associativity row, transported along the endpoint $\hsame$ rows from
the public $\NameCert_{\GaloisExtUp}$ boundary of $E$.
\end{theorem}
\begin{proof}
Project $x$, $y$, and $z$ through
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. The GaloisExtUp
public boundary of \autoref{thm:galoisext-public-obligation-boundary} supplies
the accepted source, middle, and target endpoints together with the classifier
rows that identify the two displayed middle endpoints.

Apply \autoref{thm:galoisgroup-composition-closure} first to $x$ and $y$, then
to the resulting row and $z$. This constructs the finite $\mathsf{Cont}$ row for
$(z\circ y)\circ x$ with the required fixed-base witness and provenance.

Apply \autoref{thm:galoisgroup-composition-closure} in the other order, first
to $y$ and $z$ and then to $x$ with the result. This constructs the finite
$\mathsf{Cont}$ row for $z\circ(y\circ x)$ over the same outer endpoints.

The $\NameCert_{\GroupUp}$ dependency $G$ supplies the operation, unit,
associativity, congruence, and two-sided inverse-law surface named in
\autoref{ch:concrete-instances-group-namecert}. Its associativity row
classifies the two operation parenthesizations in $G$, and the endpoint
$\hsame$ rows from $E$ transport that classification to the displayed
automorphism-action rows.

Repacking the transported classifier, the two composition ledgers, the
fixed-base witnesses, and the $\Pkg$ provenance gives the claimed
GaloisGroupUp classifier row.
\end{proof}

\begin{theorem}[GaloisGroupUp inverse cancellation rows]
\label{thm:galoisgroup-inverse-cancellation-rows}
For every accepted fixed-base automorphism-action row $x$ of an
automorphism-action packet
$(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, let $x^{-1}$ be the
inverse row supplied by \autoref{thm:galoisgroup-inverse-closure}. The composed
rows $x^{-1}\circ x$ and $x\circ x^{-1}$ are accepted by
\autoref{thm:galoisgroup-composition-closure} and are classified with the unit
automorphism row of \autoref{thm:galoisgroup-unit-automorphism-row} by the
inherited left and right inverse laws of the $\NameCert_{\GroupUp}$ dependency,
with endpoint transport through the public $\NameCert_{\GaloisExtUp}$ boundary.
\end{theorem}
\begin{proof}
Start with the accepted row $x$ and unpack it using
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. The endpoint rows,
fixed-base row, classifier row, inverse row, provenance row, and finite ledger
all live in the same packet, while
\autoref{thm:galoisext-public-obligation-boundary} supplies the public
GaloisExtUp classifier rows needed for endpoint transport.

Use \autoref{thm:galoisgroup-inverse-closure} to obtain the accepted inverse
row $x^{-1}$. Its source and target are the reversed endpoints of $x$, and its
fixed-base witness is transported by the same $\hsame$ comparisons on the base
endpoint.

Apply \autoref{thm:galoisgroup-composition-closure} to $x$ followed by
$x^{-1}$, and again to $x^{-1}$ followed by $x$. These applications produce the
two finite composition ledgers and preserve the fixed-base witness on both
sides.

The $\NameCert_{\GroupUp}$ packet $G$ supplies the operation, unit, congruence,
associativity, and two-sided inverse-law rows from the GroupUp surface named in
\autoref{ch:concrete-instances-group-namecert}. The right inverse law classifies
$x\circ x^{-1}$ with the unit row, and the left inverse law classifies
$x^{-1}\circ x$ with the unit row.

Finally, \autoref{thm:galoisgroup-unit-automorphism-row} identifies that unit
row with the fixed-base identity automorphism row over $E$. Repacking the two
inverse-law classifications with the endpoint $\hsame$ transports and the
ledger $\lambda$ gives the two claimed GaloisGroupUp cancellation rows.
\end{proof}

\begin{theorem}[GaloisGroupUp identity row closure]
\label{thm:galoisgroup-identity-row-closure}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the $\GroupUp$
unit row of $G$, read through the GaloisExtUp identity classifier of $E$ and
the fixed-base row $b$, is an accepted $\GaloisGroupUp$ automorphism-action row.
It fixes every displayed base endpoint by $\hsame$, carries only rows listed in
$\lambda$, and uses no equality of host fields or ambient automorphism sets.
\end{theorem}
\begin{proof}
Project the packet to its consumed rows $E$ and $G$. The Galois-extension
projection supplies the displayed extension endpoints, the identity classifier,
and the exactness rows on the public extension surface. The group projection
supplies the unit endpoint, the unit classifier rows, and the provenance needed
to read the unit as a finite $\mathsf{BHist}$ row.

Now combine those projections with the fixed-base row $b$. For each displayed
base endpoint, the identity classifier leaves the endpoint in its original
$\hsame$ class, and $b$ records that this comparison is part of the finite
automorphism ledger. Thus the unit action fixes every displayed base endpoint.

Finally, repack the base row, identity action row, classifier row $c$,
provenance row $\rho$, and the same finite ledger $\lambda$. The resulting row
has the packet shape required by
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, so it is accepted
by the public $\NameCert_{\GaloisGroupUp}$ carrier.
\end{proof}

\begin{theorem}[GaloisGroupUp composition classifier congruence]
\label{thm:galoisgroup-composition-classifier-congruence}
Let $x,x',y,y'$ be accepted fixed-base automorphism-action rows in an
automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}. Suppose $x$ is
classified with $x'$, $y$ is classified with $y'$, the target endpoint of $x$
is classified with the source endpoint of $y$, and the target endpoint of
$x'$ is classified with the source endpoint of $y'$. Then the composite of
$x$ with $y$ is classified with the composite of $x'$ with $y'$. The
classification uses only inherited GaloisExtUp classifier transport,
$\GroupUp$ operation congruence, $\hsame$, $\Cont$, and $\mathsf{Pkg}$
provenance from the packet.
\end{theorem}
\begin{proof}
First transport the extension faces. The GaloisExtUp classifier of $E$
transports source, middle, and target endpoints across the displayed
$\hsame$ rows, and the $\Cont$ rows in $\lambda$ record the two compatible
composition ledgers.

Next transport the fixed-base faces. Since $x$ is classified with $x'$ and
$y$ is classified with $y'$, their fixed-base witnesses compare by the
classifier row $c$. The middle endpoint comparisons align the two ways of
reading the shared extension endpoint, so the composed fixed-base witness is
again compared by $\hsame$.

Apply the $\GroupUp$ operation congruence from $G$ to the operation endpoints
underlying the two composites. The $\mathsf{Pkg}$ row $\rho$ identifies these
operation endpoints as dependency rows from $G$, while the acted-on extension
endpoints remain dependency rows from $E$.

Repack the transported source, middle, target, fixed-base, operation, and
ledger rows as the composed classifier row. This gives classifier-equivalent
composites without introducing any host automorphism equality.
\end{proof}
\leanchecked{BEDC.Derived.GaloisGroupUp.GaloisGroupAutomorphismActionCompositionPacket\_classifier\_congruence}

\begin{theorem}[GaloisGroupUp automorphism ledger exactness]
\label{thm:galoisgroup-automorphism-ledger-exactness}
For an automorphism-action packet $(E,G,b,a,m,i,c,\rho,\lambda)$ of
\autoref{def:galoisgroup-bhist-automorphism-action-packet}, the public ledger
$\lambda$ hides exactly the dependency rows, fixed-base rows, identity rows,
action rows, composition rows, inverse rows, classifier rows, provenance rows,
and exactness rows exposed by the $\GaloisGroupUp$ automorphism surface. Every
public consumer of the packet factors through those rows and does not require
host automorphism equality, equality of ambient function spaces, or equality of
uncarried quotient representatives.
\end{theorem}
\begin{proof}
Project the packet coordinates. The rows $E$ and $G$ give the dependency
surfaces, $b$ gives the fixed-base surface, the unit endpoint of $G$ with the
identity classifier of $E$ gives the identity surface, $m$ gives composition,
$i$ gives inverse, $c$ gives classifier comparison, and $\rho$ gives
provenance. The exactness rows are precisely the exactness rows already named
by the dependency packets and the automorphism-action surface.

These projected rows account for every public operation used by a
$\NameCert_{\GaloisGroupUp}$ consumer. Carrier acceptance uses the dependency
and fixed-base rows; identity uses the unit and identity-classifier rows;
composition and inverse use $m$ and $i$; classifier transport uses $c$ together
with $\hsame$ and $\Cont$; provenance uses $\rho$.

Conversely, start from exactly those finite rows and their $\mathsf{Pkg}$
assignments. Repacking them as $E$, $G$, $b$, $a$, $m$, $i$, $c$, $\rho$, and
$\lambda$ reconstructs the public automorphism-action packet. Since no
coordinate contains host automorphism equality, no consumer can depend on such
an equality through the public ledger.
\end{proof}
