\chapter{A Concrete Naming Certificate for $\CoveringDimensionUp$}
\label{ch:concrete-instances-coveringdimension-namecert}
\origin{human}

Following Hurewicz--Wallman and Engelking, the $\CoveringDimensionUp$ packet records finite-cover dimension as BEDC refinement data. The classical statement is read here through compact metric finite rows: a finite cover is displayed as $\BHist$ cover entries, a refinement is a finite map of rows, the order bound is a visible multiplicity ledger, and the Lebesgue-number evidence is the compact finite ledger already exposed by \autoref{ch:concrete-instances-compactmetric-namecert}, \autoref{ch:concrete-instances-finite-epsilon-net-namecert}, and \autoref{ch:concrete-instances-compact-cover-lebesgue-ledger-namecert}. Thus the packet speaks about a named finite cover-refinement surface, not about arbitrary open-cover compactness.

\begin{definition}[Covering dimension carrier]
\label{def:covering-dimension-carrier}
A $\CoveringDimensionUp$ carrier is a finite $\BHist$ packet
$$
D=(K,E,C,R,O,L,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row, including the compact metric classifier and the finite-net read route consumed by the packet;
\item $E$ is the $\FiniteEpsilonNetUp$ row, exposing the finite $\mathsf{ProbeBundle}$ of centers and tolerance-indexed coverage witnesses used to sample the cover;
\item $C$ is the finite cover row, a displayed list of $\BHist$ cover members together with membership witnesses readable through the compact metric source;
\item $R$ is the finite refinement map row, assigning each refined cover member to a displayed parent member of $C$ and recording the local containment witness;
\item $O$ is the order-bound witness row, recording that no inspected point-history is carried by more than the displayed bound of refined members;
\item $L$ is the $\CompactCoverLebesgueLedgerUp$ row, tying the cover and refinement to positive radius ledgers and finite Lebesgue-style readback;
\item $H$ records componentwise $\hsame$ transport for the compact metric source, finite epsilon-net row, cover row, refinement map, order-bound witness, Lebesgue ledger, replay row, provenance row, and local naming row;
\item $T$ records displayed $\Cont$ routes through which compact-metric, finite-net, cover, refinement, order-bound, and Lebesgue-ledger consumers inspect the packet;
\item $P$ is the $\Pkg$ provenance over $\CoveringDimensionUp$, $\CompactMetricUp$, $\FiniteEpsilonNetUp$, $\CompactCoverLebesgueLedgerUp$, $\mathsf{ProbeBundle}$, $\BHist$, $\hsame$, $\Cont$, and local naming rows;
\item $N$ is the local $\NameCert_{\CoveringDimensionUp}$ row.
\end{enumerate}
The carrier has no coordinate for an arbitrary open cover, a choice-selected refinement, a host finite-subcover theorem, a classical covering-dimension theorem, quotient real equality, or an external multiplicity oracle.
\end{definition}

\begin{theorem}[Covering dimension NameCert obligations]
\label{thm:covering-dimension-namecert-obligations}
For every accepted $\CoveringDimensionUp$ carrier
$$
D=(K,E,C,R,O,L,H,T,P,N),
$$
the local $\NameCert_{\CoveringDimensionUp}$ surface consists exactly of carrier admission for $D$, compact metric admission through $K$, finite epsilon-net admission through $E$, finite cover admission through $C$, refinement containment through $R$, order-bound verification through $O$, Lebesgue-ledger compatibility through $L$, componentwise $\hsame$ stability through $H$, displayed $\Cont$ replay through $T$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:covering-dimension-carrier}. The analytic rows are exactly the compact metric source $K$, finite epsilon-net row $E$, finite cover row $C$, refinement row $R$, order-bound row $O$, and Lebesgue-ledger row $L$.

Carrier admission and compact admission are rowwise. The finite-net row $E$ supplies the only center bundle and coverage witnesses read by the packet, so every cover and refinement check is anchored in displayed compact metric data.

The finite cover row $C$ is refined only through $R$. Each refined member carries its displayed parent and containment witness before the order row $O$ may count overlaps.

The Lebesgue-ledger row $L$ ties the same cover route to positive radius data. Its compatibility obligation forces the refinement and order rows to be read with the finite lower-radius ledger rather than with a detached open-cover argument.

Finally $H,T,P,N$ transport, replay, package, and name the same finite surface. Since the carrier contains no arbitrary open-cover coordinate, choice-selected refinement, host subcover theorem, classical dimension theorem, quotient equality, or external multiplicity oracle, none of those objects can enter the local NameCert obligations.
\end{proof}

\begin{theorem}[Covering dimension refinement order]
\label{thm:covering-dimension-refinement-order}
Every accepted $\CoveringDimensionUp$ refinement factors through the finite route
$$
K,E,C \longmapsto R,O,L \longmapsto H,T,P,N .
$$
Thus a downstream dimension consumer receives a displayed finite cover, a displayed refinement map into that cover, an order-bound witness over the refined rows, and the compact Lebesgue ledger before it may read the packet as a dimension bound.
\end{theorem}
\begin{proof}
Begin with a downstream consumer of an accepted carrier $D$. By \autoref{def:covering-dimension-carrier}, the consumer enters through the compact metric row $K$ and the finite epsilon-net row $E$ before it can inspect any cover data.

The cover row $C$ is then opened as a finite list of named cover members. The refinement row $R$ maps each refined member back to this list and records the containment evidence needed to read the refined cover as a refinement of $C$.

The order-bound row $O$ counts only refined members that are already visible through $R$. Hence the order claim is a finite overlap ledger over the displayed refinement, not a global theorem about all open covers.

The Lebesgue-ledger row $L$ supplies the positive radius readback compatible with the same finite cover route. Transport, replay, provenance, and naming through $H,T,P,N$ preserve that route for the dimension consumer.
\end{proof}

\begin{theorem}[Covering dimension ledger non-escape]
\label{thm:covering-dimension-ledger-non-escape}
No accepted $\CoveringDimensionUp$ packet can replace its finite rows $K,E,C,R,O,L,H,T,P,N$ by arbitrary open-cover compactness, choice-selected refinements, a host multiplicity oracle, or a classical dimension theorem. Any exported dimension-bound claim must be read through the displayed cover, refinement, order-bound, Lebesgue-ledger, transport, replay, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Inspect the carrier inventory of \autoref{def:covering-dimension-carrier}. The only compactness data are the compact metric row $K$, the finite epsilon-net row $E$, and the finite Lebesgue-ledger row $L$.

The only cover data are the finite cover row $C$ and the refinement map row $R$. The only multiplicity data are the order-bound witnesses in $O$.

The structural rows $H,T,P,N$ preserve and expose these displayed rows. They do not add an open-cover family, a choice operator, a host overlap counter, or an external theorem.

Therefore any consumer that exports a dimension-bound claim without reading $K,E,C,R,O,L,H,T,P,N$ leaves the carrier surface and is not reading a $\CoveringDimensionUp$ certificate.
\end{proof}

\falsifiablePrediction{A consumer that claims a $\CoveringDimensionUp$ bound while omitting the finite cover row, refinement map row, order-bound witness row, compact Lebesgue ledger, $\hsame$, $\Cont$, $\Pkg$, or $\NameCert$ rows refutes the carrier of \autoref{def:covering-dimension-carrier}.}

\independenceWitness{compactmetric, finite-epsilon-net, compact-cover-lebesgue-ledger: $\CoveringDimensionUp$ binds a finite cover row, a refinement map, an order-bound ledger, compact finite-net provenance, and Lebesgue-ledger compatibility in one NameCert packet; each named sibling lacks at least one of these rows as a local dimension-obligation coordinate.}

\closureat{CoveringDimensionUp}{seedStr}

\begin{closurestatus}{\CoveringDimensionUp}
  \constructivestory{A $\CoveringDimensionUp$ packet is generated from a CompactMetricUp source, a FiniteEpsilonNetUp center bundle, a finite BHist cover row, a finite refinement map, an order-bound witness ledger, a CompactCoverLebesgueLedgerUp row, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:covering-dimension-carrier}, \autoref{thm:covering-dimension-namecert-obligations}, \autoref{thm:covering-dimension-refinement-order}, and \autoref{thm:covering-dimension-ledger-non-escape} seed the finite cover-refinement dimension packet over compact metric finite-net and Lebesgue-ledger rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim arbitrary open-cover compactness, choice-selected refinements, classical covering-dimension theorems, Lean verification, bridge checking, quotient real equality, or host multiplicity oracles.}
  \upgradepath{Obligation closure requires checked carrier admission, refinement containment, order-bound verification, Lebesgue-ledger compatibility, and ledger nonescape for BEDC.Derived.CoveringDimensionUp.CoveringDimensionPacket\_namecert\_obligations.}
\end{closurestatus}
