\chapter{MetaCIC Confluence partial-closure audit map}
\label{ch:metacic-confluence-audit-map}
\origin{ai}

\section{The setup}
\label{sec:metacic-confluence-audit-map-setup}

The BEDC.MetaCIC confluence module is split across six sibling files:
\texttt{AtomJoin}, \texttt{AtomShape}, \texttt{ClosedGeneral},
\texttt{ClosedUnconditional}, \texttt{Core}, and \texttt{Diamond}. The split is
not cosmetic. The files separate raw reduction infrastructure, atom-shape
facts, componentwise diamond lemmas, substitution-sensitive diamond assembly,
closed-term bridge statements, and the unconditional fragments that are already
available for specific closed sources.

Confluence is therefore not presented as a single hidden theorem. The Lean side
exposes the exact state: a full parallel diamond follows from a substitution
compatibility input, closed multi-step confluence follows from a closed
parallel-diamond input, and a smaller set of closed source shapes is discharged
without that input.

The operative relations are the multi-step closure $\mathrm{BetaStarStep}$ and
the Tait--Martin-L\"of style parallel relation $\mathrm{BetaParallel}$. The
ordinary proof route is also visible in the file structure: prove a diamond for
parallel reduction, transport parallel steps into multi-step beta reduction,
derive a strip lemma, and then derive Church--Rosser for the star relation. The
current substrate has checked much of this route, but the point where parallel
beta redexes require residual substitution compatibility remains an explicit
input.

\section{What is established}
\label{sec:metacic-confluence-audit-map-established}

The checked inventory has six parts.

\begin{itemize}
\item \texttt{Diamond.lean} contains the substitution-sensitive assembly. The
  full parallel diamond is proved from the explicit substitution compatibility
  proposition, and the unclosed substitution commutation obstruction is named:
  \leanvariant{BEDC.MetaCIC.betaParallel\_diamond\_from\_substitution}
  \leanvariant{BEDC.MetaCIC.betaParallel\_app\_shape\_diamond\_from\_substitution}
  \leanvariant{BEDC.MetaCIC.substitute\_commutation\_unclosed\_obstruction}.
\item \texttt{ClosedGeneral.lean} turns a closed parallel diamond into closed
  strip and closed multi-step confluence. It also records the imported
  unclosed substitution counterexample next to the closed-substitution
  compatibility interface:
  \leanvariant{BEDC.MetaCIC.betaParallel\_closed\_strip\_from\_diamond}
  \leanvariant{BEDC.MetaCIC.betaStarStep\_confluence\_general\_of\_parallel\_diamond\_closed}
  \leanvariant{BEDC.MetaCIC.betaParallel\_closed\_substitution\_compatibility\_obstruction}.
\item \texttt{ClosedUnconditional.lean} proves unconditional closed confluence
  for normal sources and the atom cases that reduce to normality. The theorem
  family is shape-limited, not a blanket closed confluence theorem:
  \leanvariant{BEDC.MetaCIC.betaParallel\_diamond\_closed\_normal}
  \leanvariant{BEDC.MetaCIC.betaStarStep\_confluence\_closed\_normal}
  \leanvariant{BEDC.MetaCIC.betaStarStep\_confluence\_closed\_sort}
  \leanvariant{BEDC.MetaCIC.betaStarStep\_confluence\_closed\_var\_impossible}.
\item \texttt{Core.lean} supplies the reduction algebra: multi-step
  concatenation, parallel-to-star transport, atom diamonds, and componentwise
  diamonds for application, lambda, and Pi shapes:
  \leanvariant{BEDC.MetaCIC.betaParallel\_to\_betaStar}
  \leanvariant{BEDC.MetaCIC.betaParallel\_app\_diamond\_of\_components}
  \leanvariant{BEDC.MetaCIC.betaParallel\_lam\_shape\_diamond}
  \leanvariant{BEDC.MetaCIC.betaParallel\_pi\_shape\_diamond}.
\item \texttt{AtomShape.lean} proves the case analysis needed to keep atoms
  and non-lambda applications from silently entering the beta-redex branch:
  \leanvariant{BEDC.MetaCIC.betaStep\_app\_cases}
  \leanvariant{BEDC.MetaCIC.betaStarStep\_app\_non\_lam\_shape}
  \leanvariant{BEDC.MetaCIC.betaParallel\_betaStarStep\_atom\_coincide}
  \leanvariant{BEDC.MetaCIC.betaStar\_sort\_join}.
\item \texttt{AtomJoin.lean} exposes the small join and inversion wrappers used
  by the later confluence files. The atom joins are unconditional, while the
  application shape result separates congruence targets from beta-redex targets:
  \leanvariant{BEDC.MetaCIC.betaStarStep\_diamond\_sort}
  \leanvariant{BEDC.MetaCIC.betaStarStep\_diamond\_var}
  \leanvariant{BEDC.MetaCIC.betaParallel\_app\_target\_shape}
  \leanvariant{BEDC.MetaCIC.betaParallel\_app\_no\_beta}.
\end{itemize}

This is a genuine checked layer. The manuscript may cite componentwise
diamonds, atom joins, parallel-to-star transport, closed normal confluence, and
the conditional bridges from parallel diamond to closed star confluence.

The inventory also fixes what cannot be inferred by proximity. The presence of
\texttt{BetaParallelDiamondClosed} as a proposition does not itself discharge
that proposition. The theorem
\texttt{betaStarStep\_confluence\_general\_of\_parallel\_diamond\_closed}
consumes such a diamond as an input; it is not the diamond. Likewise, the
theorem \texttt{betaParallel\_diamond\_from\_substitution} consumes
$\mathrm{BetaParallelSubstitutionCompatibility}$; it does not prove that
compatibility proposition.

\section{What is conditional}
\label{sec:metacic-confluence-audit-map-conditional}

The boundary is the substitution input. \texttt{Diamond.lean} defines
$\mathrm{BetaParallelSubstitutionCompatibility}$ and proves full parallel
diamond from it. \texttt{ClosedGeneral.lean} defines
$\mathrm{BetaParallelDiamondClosed}$ and proves closed multi-step confluence
from that input. These are parameterised results, not closed-source
unconditional discharge.

The unconditional part is narrower. Closed normal sources are confluent; sort
sources are confluent; closed variable sources are handled through an
impossible closedness premise; atom and non-lambda application shape lemmas
prevent false beta-redex cases. None of these statements is the full closed
Church--Rosser theorem for arbitrary closed terms.

The sharp reading is therefore:
\begin{itemize}
\item full parallel diamond is conditional on
  $\mathrm{BetaParallelSubstitutionCompatibility}$;
\item full closed star confluence is conditional on
  $\mathrm{BetaParallelDiamondClosed}$;
\item closed normal, sort, and impossible closed-variable source cases are
  unconditional;
\item application, lambda, Pi, and atom shape lemmas are infrastructure, not
  final closed confluence claims.
\end{itemize}

This conditional shape is constructive and useful. If the substitution
compatibility input is later supplied inside the same first-principles
substrate, the existing bridge theorems already specify how the result flows
to the parallel diamond and then to closed star confluence. Until that input is
supplied, the bridge remains a bridge from a named premise, not a closure
certificate for the endpoint.

\section{Comparison with the SR obstruction}
\label{sec:metacic-confluence-audit-map-sr-comparison}

The subject-reduction map in
\autoref{ch:metacic-subject-reduction-obstruction} isolates a
dependent-codomain obstruction: typing preservation across beta and binder
congruence needs four named hypotheses. The confluence map has a different
shape. It is not blocked by a displayed codomain that must be retyped after a
reduction. It is blocked at the residual-substitution algebra needed to join
parallel beta branches.

That difference matters. The confluence side already proves a large amount of
syntax-directed reduction geometry without invoking typing. The remaining
boundary is the substitution compatibility interface that makes the
application beta branch commute with the componentwise join. Thus the
confluence obstruction is algebraic over terms, while the subject-reduction
obstruction is type-preservation across dependent codomains.

The two maps also differ in their positive fragments. Subject reduction already
has a parameterised theorem whose four inputs are typing-specific. Confluence
has a parameterised theorem whose central input is substitution compatibility,
plus unconditional results for closed normal sources and for atom cases. A
reader should therefore not merge the two boundaries into one generic
``MetaCIC gap''. They name different interfaces and would be discharged by
different proofs.

\section{Apophatic framing}
\label{sec:metacic-confluence-audit-map-apophatic}

This chapter applies the same apophatic discipline as
\autoref{ch:metacic-subject-reduction-obstruction}. BEDC names the open cell
instead of silently promoting a conditional theorem into an unconditional
claim. The audit map is not a confluence proof. It is a paper-side handle for
the exact proof state exported by the Lean substrate.

The positive content is still substantial: the module names the missing input,
proves the bridges that would consume it, and proves the available closed
normal and atom fragments. The negative content is equally binding: a full
closed Church--Rosser theorem for arbitrary closed terms is not claimed here.

This is why the chapter belongs in the visions layer rather than in a proof
obligations chapter. It does not introduce a new axiom, a new rule of the
calculus, or a new proof principle. It gives the paper a stable handle for
reading the checked confluence files without inflating a conditional theorem
into a public closure claim.

\section{Boundary}
\label{sec:metacic-confluence-audit-map-boundary}

This chapter does not solve MetaCIC confluence. It records the partial closure
state of the confluence files and forbids the manuscript from citing a theorem
stronger than the Lean interface supplies. The available claims are the
checked component lemmas, the substitution-conditional parallel diamond, the
closed-diamond-to-star-confluence bridge, and the unconditional closed normal
and atom cases.

In particular, this chapter does not claim
$\mathrm{BetaParallelSubstitutionCompatibility}$, does not claim
$\mathrm{BetaParallelDiamondClosed}$, and does not claim arbitrary closed-term
Church--Rosser for $\mathrm{BetaStarStep}$. Those are the boundary names that
must remain visible when the confluence module is cited elsewhere in the
manuscript.

\concretizedIn{ch:concrete-instances-metacicconfluencenormalfragment-namecert}{The checked closed-normal and atom confluence fragments are realized as a finite NameCert packet with conditional-boundary non-escape.}
\concretizedIn{ch:concrete-instances-closednormalconfluenceseal-namecert}{Closed-normal confluence is realized as a finite seal packet separating available normal-source joins from the substitution-compatibility boundary.}
\concretizedIn{ch:concrete-instances-metacic-confluence-audit-packet-namecert}{Finite NameCert packet for the confluence audit-map boundary.}
\concretizedIn{ch:concrete-instances-metacic-confluence-audit-namecert}{The conditional confluence audit map is realized as a finite NameCert packet separating checked fragments from named remaining inputs.}
\concretizedIn{ch:concrete-instances-parallelconfluenceaudit-namecert}{The conditional parallel-diamond bridge, closed-star handoff, atom fragments, and substitution-compatibility boundary are packaged as a finite NameCert carrier.}
\concretizedIn{ch:concrete-instances-metacicconfluenceauditwitness-namecert}{Finite audit-witness packet for the conditional MetaCIC confluence boundary.}
\concretizedIn{ch:concrete-instances-metacic-residual-substitution-boundary-namecert}{The residual-substitution compatibility boundary is realized as a finite NameCert packet for conditional confluence handoff.}
\concretizedIn{ch:concrete-instances-metacic-confluence-critical-pair-boundary-namecert}{The confluence critical-pair boundary is realized as finite MetaCIC redex-frontier and common-reduct NameCert data.}
\concretizedIn{ch:concrete-instances-closed-parallel-diamond-premise-ledger-namecert}{The closed parallel diamond premise is realized as a finite ledger boundary consumed by the conditional MetaCIC confluence bridge.}
