\chapter{MetaCIC Decidability partial-closure audit map}
\label{ch:metacic-decidable-audit-map}
\origin{ai}

\section{The setup}
\label{sec:metacic-decidable-audit-map-setup}

The BEDC.MetaCIC decidability submodule records the mechanical checking layer
for the internal CIC fragment. It is split across five sibling files:
\texttt{CheckClosed}, \texttt{CheckClosedAtom}, \texttt{CheckCompleteness},
\texttt{GalleryTests}, and \texttt{NormalEqDecide}. The split separates
syntax equality, type inference, completeness wrappers, gallery checks, and a
bounded normal-equality checker.

The central checker is \texttt{inferTypeCtx}. It maps a context and a term to
an optional inferred type. Its closed-term wrapper is
\texttt{inferTypeCtxClosed}. The equality atom is \texttt{Term.eq}, a Boolean
structural equality on represented terms, with \texttt{checkSameTerm} as the
option-valued interface used by the typing checker. The normal-equality side
uses \texttt{normalizeBounded} and \texttt{decideClosedBetaConv}; this is a
fuel-bounded normal-form comparison, not an unrestricted beta-conversion
oracle.

The audit question is therefore precise. The submodule does not assert a
single informal statement saying that MetaCIC is decidable. It provides
checked Boolean and option procedures, then proves the soundness and
completeness properties that are available for those procedures. This chapter
maps exactly which part is closed and which part remains conditional on
normalisation or on a particular term shape.

\section{What is established}
\label{sec:metacic-decidable-audit-map-established}

The checked inventory has five parts.

\begin{itemize}
\item \texttt{CheckClosedAtom.lean} gives structural equality for terms. The
  Boolean equality is reflexive, converts true results into propositional
  equality, converts propositional equality into true results, and exposes the
  full iff statement:
  \leanvariant{BEDC.MetaCIC.Term.eq\_refl}
  \leanvariant{BEDC.MetaCIC.Term.eq\_true\_to\_eq}
  \leanvariant{BEDC.MetaCIC.Term.eq\_eq\_to\_true}
  \leanvariant{BEDC.MetaCIC.Term.eq\_correct}.
\item The option-valued same-term checker is also bidirectional. A successful
  check gives equality, and equality gives a successful check:
  \leanvariant{BEDC.MetaCIC.checkSameTerm\_sound}
  \leanvariant{BEDC.MetaCIC.checkSameTerm\_complete}.
\item The first type-inference checker \texttt{inferType} is sound and
  complete for the inductive \texttt{HasType} relation, both in arbitrary
  contexts and in the empty context wrapper:
  \leanvariant{BEDC.MetaCIC.inferType\_sound}
  \leanvariant{BEDC.MetaCIC.inferType\_complete}
  \leanvariant{BEDC.MetaCIC.inferTypeClosed\_sound}
  \leanvariant{BEDC.MetaCIC.inferTypeClosed\_complete}.
\item \texttt{CheckClosed.lean} repeats the checker through
  \texttt{inferTypeCtx}, with explicit recognisers for sort and Pi types. The
  context-indexed and closed wrappers are again sound and complete through
  \texttt{inferTypeCtx\_sound}, \texttt{inferTypeCtx\_complete},
  \texttt{inferTypeCtxClosed\_sound}, and
  \texttt{inferTypeCtxClosed\_complete}.
\item \texttt{CheckCompleteness.lean} records a shape-organised completeness
  surface. Its raw, total-exists, and strict exported wrappers are checked,
  and the direct Pi, lambda, and application cases expose the main compound
  shapes:
  \leanvariant{BEDC.MetaCIC.CheckCompleteness.inferTypeCtx\_complete\_pi\_direct}
  \leanvariant{BEDC.MetaCIC.CheckCompleteness.inferTypeCtx\_complete\_lam\_direct}
  \leanvariant{BEDC.MetaCIC.CheckCompleteness.inferTypeCtx\_complete\_app\_direct}.
\end{itemize}

This is a strong positive layer. For represented syntax equality, the Boolean
procedure is correct. For typing, the option-valued inference procedure is
not merely a recogniser for gallery examples; it is proved sound and complete
against the inductive \texttt{HasType} relation exported by the substrate.

The gallery file supplies executable sanity rows for the closed example
surface. Boolean, natural-number, pair, option, list, sum, and polymorphic
witnesses all pass the \texttt{inferTypeCtx []} non-\texttt{none} test:
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_bool\_witnesses}
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_nat\_witnesses}
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_pair\_witnesses}
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_option\_witnesses}
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_list\_witnesses}
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_sum\_witnesses}
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_polymorphic\_witnesses}
\leanvariant{BEDC.MetaCIC.gallery\_sanity\_all\_typed\_witnesses}.

The gallery rows are not the source of the general typing theorem. Their
role is audit-facing: they show that the same checker surface used in the
soundness and completeness theorems also accepts the main Church-encoded
example families.

\section{Normal equality and bounded beta conversion}
\label{sec:metacic-decidable-audit-map-normal-equality}

\texttt{NormalEqDecide.lean} adds a separate equality surface. It defines a
bounded normalizer and compares the bounded normal forms with
\texttt{Term.eq}. The basic structural facts are checked:
\leanvariant{BEDC.MetaCIC.normalizeBounded\_zero}
\leanvariant{BEDC.MetaCIC.normalizeBounded\_sort}
\leanvariant{BEDC.MetaCIC.normalizeBounded\_var}
\leanvariant{BEDC.MetaCIC.normalizeBounded\_lam\_succ}
\leanvariant{BEDC.MetaCIC.normalizeBounded\_pi\_succ}
\leanvariant{BEDC.MetaCIC.normalizeBounded\_app\_succ}.

The decision procedure is reflexive at every fuel value, and a true Boolean
result implies equality of the two bounded normalizer outputs:
\leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_refl}
\leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_true\_eq\_normalized}.

It also yields beta-convertibility between the bounded normalizer outputs:
\leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_true\_betaConv\_normalized}.

The stronger finished-normalisation interface is explicitly conditional. If
both terms have closed finished normalisation witnesses at the same fuel, then
a true result from \texttt{decideClosedBetaConv} gives equality of the named
normal forms, beta-convertibility of those normal forms, and preservation of
the closed normal-form witnesses:
\leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_sound\_finished}
\leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_sound\_finished\_betaConv}
\leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_sound\_finished\_eq}.

This file is therefore a bounded normal-equality checker plus a conditional
soundness bridge for the case where the fuel is known to finish on closed
normal forms. It is not a theorem that arbitrary closed terms have a computed
finished normal form at some fuel, and it is not an unrestricted decision
procedure for beta conversion over all closed terms.

\section{What remains conditional}
\label{sec:metacic-decidable-audit-map-conditional}

Three boundaries must remain visible.

\begin{itemize}
\item Typing is closed at the checker interface. For the represented
  \texttt{HasType} relation, \texttt{inferTypeCtx} has soundness and
  completeness theorems. The paper may cite this as a checked typing
  decision surface for the encoded relation.
\item Closedness itself is represented by the inductive predicate
  \texttt{ClosedAt}. The decidability submodule consumes closedness in places
  such as \texttt{inferTypeCtxClosed\_sound} and
  \texttt{ClosedFinishedNormalizes}; it does not provide a separate theorem
  named \texttt{Decidable (ClosedAt n t)}.
\item Beta-conversion equality is conditional on bounded normalisation data.
  The Boolean checker is proved sound for equality of bounded normalizer
  outputs and for finished closed normal forms. It is not a global
  closed-term beta-conversion decider unless the missing normalisation
  endpoint data is supplied.
\end{itemize}

The first boundary is positive closure. The second is a naming boundary: the
closedness predicate is an inductive relation with many checked preservation
facts elsewhere in MetaCIC, but this submodule does not export a dedicated
closedness-decision theorem. The third boundary links directly to
normalisation: full conversion decidability would require a bridge from typed
closed terms to finished bounded normal forms at a specified fuel or to an
equivalent fuel-erased normalisation theorem.

\section{Comparison with other audit maps}
\label{sec:metacic-decidable-audit-map-comparison}

The subject-reduction audit map in
\autoref{ch:metacic-subject-reduction-obstruction} is blocked by
dependent-codomain preservation. It names four typing-preservation
obligations and records an obstruction to an unconditional closed
subject-reduction theorem. The decidability map has a different shape. Typing
inference itself is not the obstruction; it is already checked as sound and
complete for the encoded \texttt{HasType} relation.

The confluence audit map in \autoref{ch:metacic-confluence-audit-map} is
blocked at residual substitution compatibility for joining parallel beta
branches. The decidability map uses substitution through typing and normal
comparison, but its open edge is not the parallel diamond. Its open edge is
the endpoint data needed to promote bounded normal equality into global
closed-term conversion decidability.

The normalisation layer is the closest neighbour. The bounded normalizer in
\texttt{NormalEqDecide} supplies a computable comparison surface. Strong
normalisation supplies the kind of endpoint guarantee that would make such a
surface public for all typed closed terms. Without that connection, the
normal-equality checker remains a bounded and conditionally sound procedure.

\concretizedIn{ch:concrete-instances-metacicdecidableboundary-namecert}{MetaCIC decidability boundaries are realized as finite checker, bounded-normal comparison, refusal, provenance, and local NameCert rows.}
\concretizedIn{ch:concrete-instances-metacicdecidabilitywitness-namecert}{The concrete witness packages typing-checker exactness and bounded-conversion non-escape as finite NameCert rows.}
\concretizedIn{ch:concrete-instances-bounded-normal-equality-checker-namecert}{Bounded normal-equality checkers are realized as finite BHist packets over bounded normalizer output rows, structural Term.eq readback, finished-normalization witnesses, closedness rows, hsame transport, Cont replay, Pkg provenance, and local NameCert rows.}
\concretizedIn{ch:concrete-instances-finite-observation-fold-namecert}{Finite observation folds realize the bounded MetaCIC checker-output packet as finite NameCert data.}
\concretizedIn{ch:concrete-instances-metacic-decidable-typing-frontier-namecert}{The decidable typing frontier is realized as finite checker, structural equality, bounded-normal comparison, refusal, provenance, and local NameCert rows.}

Thus the three maps should not be read as one generic MetaCIC deficit. Subject
reduction needs preservation across dependent typing, confluence needs
substitution compatibility for joins, and decidability needs the exact bridge
from bounded computation to finished normal forms when beta conversion is the
target. The typing-checker part of decidability is already closed; the
conversion-checker part is intentionally narrower.

\section{Apophatic framing}
\label{sec:metacic-decidable-audit-map-apophatic}

The apophatic discipline is the same as in the subject-reduction and
confluence chapters. BEDC names what the checker proves and refuses to let a
Boolean procedure become a stronger theorem by prose. A successful
\texttt{inferTypeCtx} result carries a checked \texttt{HasType} witness by
soundness. A \texttt{HasType} witness is accepted by the checker by
completeness. A successful bounded beta-conversion result carries only the
bounded-normal equality and the finished-normalisation consequences stated by
the corresponding theorems.

This is why the word ``decidable'' has to be read at the level of the
exported theorem. For syntax equality and typing inference, the checked
theorems give a closed decision surface. For closedness and global beta
conversion, this chapter records the absence of a named theorem at that
strength in the decidability submodule. The absence is not repaired by
gallery success or by the existence of a bounded normalizer.

\section{Boundary}
\label{sec:metacic-decidable-audit-map-boundary}

This chapter records the partial closure state of the MetaCIC decidability
files. It may be cited for structural term equality, same-term checking,
typing-inference soundness and completeness, the shape-organised completeness
wrappers, gallery acceptance rows, and the bounded normal-equality soundness
facts listed above.

It does not claim a theorem named \texttt{Decidable (ClosedAt n t)}. It does
not claim an unrestricted closed-term beta-conversion decider. It does not
claim that \texttt{decideClosedBetaConv} is complete for beta conversion at
arbitrary fuel. Those stronger readings require explicit Lean targets before
they can enter the paper as closure claims.

\concretizedIn{ch:concrete-instances-metacicdecidableauditpacket-namecert}{MetaCIC decidability is realized as a finite audit packet separating checked typing inference from bounded conversion soundness.}
\concretizedIn{ch:concrete-instances-bounded-beta-comparison-namecert}{Bounded beta comparison is realized as a finite checker packet with an explicit finished-normalisation boundary.}
\concretizedIn{ch:concrete-instances-metacicdecidablecheckerseal-namecert}{The checker seal packages typing, same-term, and bounded normal-equality rows as a finite NameCert surface.}
