\chapter{MetaCIC Normalization partial-closure audit map}
\label{ch:metacic-normalization-audit-map}
\origin{ai}

\section{The setup}
\label{sec:metacic-normalization-audit-map-setup}

BEDC.MetaCIC's normalisation submodule is laid out across four sibling files:
\texttt{AppAdequacy}, \texttt{ClosedSN}, \texttt{PiAdequacy}, and
\texttt{Reducibility}. Together they aim at strong normalisation on closed terms
via the candidate-mediated reducibility path.

The operative endpoint is $\mathrm{StrongNormalizable}(t)$. The module does not
present that endpoint as a hidden global oracle. It exposes a reducibility
candidate layer, a closed-candidate layer, candidate-set wrappers, Pi and
application adequacy lemmas, and closed typed term projections from those
witnesses.

This chapter records the exact reading discipline for that interface. The
normalisation files contain many checked termination facts, but the public
closed-term route is candidate-mediated. A manuscript citation must therefore
name the supplied candidate evidence, closed candidate evidence, or candidate-set
membership evidence; it must not silently cite an unconditional theorem for every
closed typed term.

\section{What is established}
\label{sec:metacic-normalization-audit-map-established}

The checked inventory has six parts.

\begin{itemize}
\item Reducibility candidate predicate. \texttt{Reducibility.lean} defines the
  candidate surface and proves that candidates imply strong normalisation:
  \leanvariant{BEDC.MetaCIC.Candidate}
  \leanvariant{BEDC.MetaCIC.candidate\_implies\_sn}
  \leanvariant{BEDC.MetaCIC.candidate\_sn}
  \leanvariant{BEDC.MetaCIC.candidate\_closed\_under\_beta}.
\item Closed SN from candidate. \texttt{ClosedSN.lean} projects an empty-context
  typed closed term to strong normalisation when the corresponding candidate
  witness is supplied:
  \leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_candidate}.
\item Closed SN from closed candidate. The closed-candidate wrapper carries the
  closedness of the type and term together with the reducibility candidate, and
  the closed typed term projection consumes that wrapper:
  \leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_closedCandidate}
  \leanvariant{BEDC.MetaCIC.closedCandidate\_implies\_sn}.
\item Closed SN from candidate set. Candidate sets package membership,
  soundness, and beta-closure; closed typed terms inherit strong normalisation
  from membership in such a set:
  \leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_candidateSet}
  \leanvariant{BEDC.MetaCIC.candidateSet\_implies\_sn}
  \leanvariant{BEDC.MetaCIC.canonicalCandidateSet\_sound}.
\item App adequacy. Application cases are discharged when the function side
  supplies Pi-candidate or Pi-head candidate evidence and the argument supplies
  domain-candidate evidence. The step lemmas keep the result inside the same
  candidate-mediated path:
  \leanvariant{BEDC.MetaCIC.app\_case\_candidate}
  \leanvariant{BEDC.MetaCIC.app\_case\_sn\_from\_pi\_candidate}
  \leanvariant{BEDC.MetaCIC.app\_case\_sn\_from\_candidate}
  \leanvariant{BEDC.MetaCIC.app\_case\_step\_sn}.
\item Pi adequacy. Pi candidates and neutral normal forms supply the function
  and binder-side termination facts used by the application layer and the typed
  examples:
  \leanvariant{BEDC.MetaCIC.piCandidate\_implies\_sn}
  \leanvariant{BEDC.MetaCIC.PiAdequacy.piCandidate\_implies\_sn}
  \leanvariant{BEDC.MetaCIC.neutralNormal\_implies\_sn}
  \leanvariant{BEDC.MetaCIC.sn\_pi}.
\end{itemize}

The no-infinite-reduction reading is also present. Strong normalisation excludes
infinite beta chains, and the same candidate-mediated closed-term routes export
that exclusion:
\leanvariant{BEDC.MetaCIC.strongNormalizable\_no\_infinite\_reduction}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_no\_infinite\_reduction\_from\_candidate}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_no\_infinite\_reduction\_from\_closedCandidate}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_no\_infinite\_reduction\_from\_candidateSet}.

\section{File-by-file audit reading}
\label{sec:metacic-normalization-audit-map-file-reading}

\texttt{Reducibility.lean} is the base layer. It defines
$\mathrm{BetaStrong}$, $\mathrm{StrongNormalizable}$, candidate heads,
candidates, closed candidates, Pi candidates, and candidate sets. The file also
proves the core closure facts: candidates imply SN, candidates are stable under
one beta step, candidate sets export SN through their soundness field, and the
canonical candidate set is sound and beta-closed.

The important audit point is that a candidate is not merely a term-level SN
tag. It also carries the head-shape information needed by the Pi and application
routes. For Pi types this head information includes the ability to send
candidate arguments to strongly normalising applications. That is the beginning
of the candidate-mediated application story, and it is why the application layer
does not reduce to a simple componentwise SN claim.

\texttt{ClosedSN.lean} is the closed-term projection layer. It introduces
$\mathrm{ClosedTypedTerm}$, $\mathrm{ClosedTypedCandidate}$,
$\mathrm{ClosedTypedPiCandidate}$, and
$\mathrm{ClosedTypedCandidateSetMember}$. The three main closed typed term
theorems project SN from candidate, closed-candidate, and candidate-set evidence.
The same file then mirrors those projections into no-infinite-reduction
statements.

This file is the main public citation site for closed-term SN. Its statements
are strong enough for the closed-normal branch of the consistency assembly, but
their quantifier shape matters. Empty-context typing and closedness are present;
the candidate witness is still a separate input. A citation that drops that input
would cite a theorem that the file does not export.

\texttt{PiAdequacy.lean} supplies neutral and Pi-shaped adequacy. It contains a
namespace wrapper for Pi-candidate SN, defines neutral normal forms, proves that
neutral normality is stable under beta steps, and derives SN for neutral
applications and displayed Pi constructions. It also records typed-example SN
facts for the Church gallery. These example facts are useful witnesses that the
machinery runs on concrete closed terms, not a replacement for the general
candidate interface.

\texttt{AppAdequacy.lean} is the application-facing layer. It turns a
PiCandidate function and a candidate argument into a candidate application, then
projects SN and beta-step SN consequences. It also supplies closed application
wrappers and small example applications. The file ends with the negative
guardrail showing that componentwise SN of function and argument alone does not
entail SN of their application.

The four files therefore form a staged route:
\begin{itemize}
\item \texttt{Reducibility} defines the candidate objects and their SN
  consequences;
\item \texttt{ClosedSN} projects those consequences to closed typed term and
  no-infinite-reduction statements;
\item \texttt{PiAdequacy} supplies neutral and Pi-shaped adequacy facts;
\item \texttt{AppAdequacy} discharges application cases under candidate evidence
  and records the non-unconditional application boundary.
\end{itemize}

This route is partial closure in the precise BEDC sense. It closes the local
candidate-mediated path and the named closed-term projections from that path. It
does not erase the candidate layer or turn the examples into a theorem over all
closed typed terms.

\section{What remains conditional}
\label{sec:metacic-normalization-audit-map-conditional}

The normalisation files have no visible \texttt{sorry}, \texttt{admit}, or
\texttt{axiom} marker in this submodule. The conditionality is instead at the
interface: the closed typed term theorems consume candidate evidence,
closed-candidate evidence, or candidate-set membership evidence. They do not
construct such evidence for every empty-context typed closed term.

The sharp reading is therefore:
\begin{itemize}
\item candidate evidence implies strong normalisation;
\item closed typed terms are strongly normalising once they are placed inside the
  candidate, closed-candidate, or candidate-set interface;
\item Pi and application adequacy show how the candidate interface behaves over
  the displayed Pi and application fragments;
\item the module does not export a blanket theorem of the form every closed typed
  BEDC.MetaCIC term is strongly normalising without candidate-mediated evidence.
\end{itemize}

This boundary is checked negatively on the application side. The file
\texttt{AppAdequacy.lean} records a self-application counterexample to the claim
that strong normalisation of parts alone gives unconditional strong
normalisation of applications:
\leanvariant{BEDC.MetaCIC.selfApplyApp\_not\_sn}
\leanvariant{BEDC.MetaCIC.app\_sn\_from\_parts\_is\_not\_unconditional}.
Thus the word ``candidate-mediated'' is not stylistic caution. It names the
actual guardrail that prevents the paper from overreading componentwise
termination as global application termination.

\section{Comparison with SR obstruction and Confluence audit map}
\label{sec:metacic-normalization-audit-map-comparison}

The subject-reduction map in
\autoref{ch:metacic-subject-reduction-obstruction} isolates a
dependent-codomain obstruction: closed subject reduction is blocked unless four
named preservation obligations are supplied. The confluence map in
\autoref{ch:metacic-confluence-audit-map} isolates a residual-substitution
boundary for the full parallel diamond and arbitrary closed star confluence.

Normalisation has a different shape. It is not currently blocked by an explicit
proof-hole marker inside the normalisation submodule, and it is not the same as
the SR dependent-codomain obstruction or the confluence substitution boundary.
Its public frontier is the reducibility-candidate interface: the checked SN
projections are closed over the candidate evidence they consume, while the
manuscript must not erase that evidence from the statement being cited.

For full closed consistency, the three maps meet in
\autoref{ch:closed-metacic-consistency-assembly}. Strong normalisation supplies
the closed-normal branch through the candidate-mediated path. Subject reduction
would have to transport arbitrary closed proofs while preserving the displayed
false type. The no-closed-normal-proof-of-false theorem then rules out the
normal endpoint. The present chapter records the SN pillar; it does not close
the subject-reduction transport pillar.

\section{Apophatic framing and boundary}
\label{sec:metacic-normalization-audit-map-boundary}

This audit map applies the same apophatic discipline as the SR and confluence
maps. BEDC names the open cell instead of silently promoting a conditional
interface into an unconditional closure theorem. The map is not a new
normalisation proof. It is a paper-side handle for the exact proof state exposed
by the Lean normalisation files.

The available positive claims are the checked candidate-to-SN lemmas, the
closed typed term projections from candidate evidence, the candidate-set
projections, the Pi and application adequacy lemmas, the example-level SN facts,
and the no-infinite-reduction consequences. The explicit boundary is equally
binding: this chapter does not claim global strong normalisation for every
closed typed MetaCIC term without candidate-mediated evidence, does not turn
componentwise application SN into unconditional application SN, and does not
close the subject-reduction obligations needed by full closed consistency.

\concretizedIn{ch:concrete-instances-metacicnormalizationbudget-namecert}{Candidate-mediated normalization is represented as a finite budgeted NameCert surface, not as an unconditional closed-term theorem.}
\concretizedIn{ch:concrete-instances-metacicnormalizationaudit-namecert}{MetaCIC normalization audit packets realize the finite strong-normalization scope, confluence-boundary refusal, transport, route replay, provenance, and local NameCert rows.}
\concretizedIn{ch:concrete-instances-metacicnormalizationauditseal-namecert}{The normalization audit map is realized as the finite candidate-mediated MetaCICNormalizationAuditSeal packet.}
\concretizedIn{ch:concrete-instances-candidate-evidence-sn-route-namecert}{Candidate-mediated strong-normalization routes are realized as finite NameCert packets over candidate evidence, closed-candidate evidence, candidate-set membership, Pi/app adequacy rows, and no-infinite-reduction projections.}
\concretizedIn{ch:concrete-instances-pi-application-adequacy-route-namecert}{Pi-application adequacy routes are realized as finite candidate-mediated NameCert packets over Pi evidence, argument evidence, application candidate rows, closed typed projections, and no-infinite-reduction boundaries.}
\concretizedIn{ch:concrete-instances-metacicnormalizationcertificaterouter-namecert}{Candidate-mediated normalization routes are packaged as a finite NameCert router.}
\concretizedIn{ch:concrete-instances-metacic-normalization-confluence-bridge-namecert}{MetaCIC normalization and confluence audit routes are realized as a finite bridge packet over the subject-reduction and closed-consistency boundary.}
\concretizedIn{ch:concrete-instances-metacic-normal-audit-socket-namecert}{The normalization audit socket is realized as finite candidate, closed-candidate, obstruction, frontier, hsame, Cont, Pkg, and NameCert rows.}
\concretizedIn{ch:concrete-instances-metacic-typed-normalization-audit-namecert}{The candidate-mediated typed-normalization route is realized as a finite NameCert audit packet.}
\concretizedIn{ch:concrete-instances-metacic-candidate-set-normalization-namecert}{Candidate-set normalization is realized as finite candidate evidence, closed-term projection, application/Pi adequacy, no-infinite-reduction, obstruction, transport, continuation, provenance, and NameCert rows.}
\concretizedIn{ch:concrete-instances-metacic-normalization-window-confluence-namecert}{Finite NameCert landing for candidate-mediated normalization windows and confluence boundaries.}
\concretizedIn{ch:concrete-instances-metacicnormalizationfrontier-namecert}{The normalization frontier packet separates candidate evidence, closed-normal use, and subject-reduction obstruction rows as finite MetaCIC audit data.}
\concretizedIn{ch:concrete-instances-metacic-candidate-set-sn-handoff-namecert}{Candidate-set strong-normalization handoffs are realized as finite CandidateSet membership, closed-term, beta-closure, and SN export NameCert data.}
