\begin{theorem}[Real unary stream-name classifier exactness]
\label{thm:real-unary-streamname-classifier-exactness}
For observation maps $s,t:\Hist\to\Hist$, if
$$
\mathsf{RatStreamNameCarrier}(s)
\quad\text{and}\quad
\mathsf{RatStreamNameCarrier}(t),
$$
then the Real unary classifier and the StreamNameUp classifier identify the same
BEDC relation:
$$
\mathsf{RealUnaryStreamClassifier}(s,t)
\Longleftrightarrow
\mathsf{RatStreamNameClassifier}(s,t).
$$
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:rat-stream-name-carrier},
Definition~\ref{def:rat-stream-name-classifier}, and
Definition~\ref{def:real-unary-observation-stream-classifier}. Both classifier
names then expose the same pointwise assertion: for every certified unary
observation $n$, the histories $s(n)$ and $t(n)$ are related by
$\mathsf{RatHistoryClassifier}$.

For the forward direction, combine the two displayed carrier hypotheses with
the pointwise Real unary classifier row. Repack those rows under the
StreamNameUp classifier name.

For the reverse direction, project the pointwise classifier field from
$\mathsf{RatStreamNameClassifier}(s,t)$ at each certified unary observation.
The resulting pointwise RatUp classifier is exactly the Real unary classifier
row.
\end{proof}

\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamClassifier\_ratStreamName\_pointwise\_iff}

Fit. Traditional target: classifier exactness for certified countable rational
observations. BEDC source: $\StreamNameUp+\RealUp$ over $\mathsf{BHist}$.
Carrier: $\mathsf{RatStreamNameCarrier}$. Classifier pair:
$\mathsf{RealUnaryStreamClassifier}$ and
$\mathsf{RatStreamNameClassifier}$. Stability: the existing carrier rows in
\autoref{thm:real-unary-stream-classifier-stability-package}. Ledger: the unary
observation witness. Core theorem:
\autoref{thm:real-unary-streamname-classifier-exactness}. Exactness: the
displayed if-and-only-if. Standard bridge: pointwise rational stream equality.
Status: $\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp finite-window coverage]
\label{thm:real-unary-streamname-finite-window-coverage}
For observation maps $s,t:\Hist\to\Hist$ and histories $a,w:\Hist$, if
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),\quad
\mathsf{UnaryHistory}(a),\quad
\mathsf{UnaryHistory}(w),
$$
then the certified StreamNameUp classifier supplies the finite RealUp
observation window:
$$
\mathsf{RealUnaryStreamWindowClassifier}(s,t,a,w).
$$
\end{theorem}
\begin{proof}
Use the reverse direction of
\autoref{thm:real-unary-streamname-classifier-exactness} with the two carrier
rows. The StreamNameUp classifier hypothesis therefore gives
$\mathsf{RealUnaryStreamClassifier}(s,t)$.

The remaining hypotheses are exactly the unary anchor and unary bound required
by \autoref{thm:real-unary-stream-window-coverage}. Applying that coverage
theorem to $s$, $t$, $a$, and $w$ yields
$\mathsf{RealUnaryStreamWindowClassifier}(s,t,a,w)$.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RatStreamNameClassifier\_real\_unary\_window\_coverage}

Fit. Traditional target: finite windows for certified countable rational
observations. BEDC source: StreamNameUp plus RealUp unary stream classifier.
Carrier: observation maps over $\mathsf{BHist}$. Classifier:
$\mathsf{RealUnaryStreamWindowClassifier}$. Stability: inherited from
\autoref{thm:real-unary-streamname-classifier-exactness} and
\autoref{thm:real-unary-stream-window-coverage}. Ledger: anchor, bound, and
bounded offset. Core theorem:
\autoref{thm:real-unary-streamname-finite-window-coverage}. Exactness: bounded
pointwise RatUp classification. Standard bridge: finite rational observation
windows. Status: $\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp selected endpoint denominator package]
\label{thm:real-unary-streamname-selected-endpoint-denominator-package}
For observation maps $s,t:\Hist\to\Hist$, a certified observation $n:\Hist$,
and histories $z_s,z_t:\Hist$, assume
$$
\mathsf{RatStreamNameClassifier}(s,t),\quad \mathsf{UnaryHistory}(n).
$$
Then the selected observation carries the RatUp denominator package:
$$
\begin{array}{l}
\mathsf{RatHistoryClassifier}(s(n),t(n))\land
\mathsf{PositiveUnaryDenominator}(s(n))\land
\mathsf{PositiveUnaryDenominator}(t(n))\land\\
\mathsf{UnaryHistory}(s(n))\land
\mathsf{UnaryHistory}(t(n))\land
(\hsame(s(n),\emp)\to\mathsf{False})\land\\
(\hsame(t(n),\emp)\to\mathsf{False})\land
(\hsame(s(n),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t(n),\Ezero(z_t))\to\mathsf{False}).
\end{array}
$$
\end{theorem}
\begin{proof}
Project $\mathsf{RatStreamNameClassifier}(s,t)$ at the certified observation
$n$. The unary certificate for $n$ gives the point classifier
$\mathsf{RatHistoryClassifier}(s(n),t(n))$.

Apply \autoref{thm:rat-history-classifier-positive-denominators} to this point
classifier, and then apply
\autoref{thm:positive-unary-denominator-unary-and-nonempty} separately to the
two positive-denominator witnesses. This gives the two positive denominator
rows, the two unary endpoint rows, and the two nonempty exclusions.

For a zero-headed display on the left, transport
$\mathsf{PositiveUnaryDenominator}(s(n))$ along
$\hsame(s(n),\Ezero(z_s))$ by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}, contradicting
\autoref{thm:rat-positive-denominator-e0-absurd}. The right endpoint uses the
same argument with $t(n)$ and $z_t$, and the collected rows form the displayed
package.
\end{proof}

Fit. Traditional target: selected rational observation readback. BEDC source:
$\StreamNameUp+\RatUp$ over $\mathsf{BHist}$. Carrier: observation maps.
Classifier: $\mathsf{RatStreamNameClassifier}$. Stability: point projection and
RatUp denominator transport. Ledger: selected observation and zero-head tests.
Core theorem:
\autoref{thm:real-unary-streamname-selected-endpoint-denominator-package}.
Exactness: the displayed endpoint package. Standard bridge: finite rational
observation readback. Status: $\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp transported selected endpoint shape package]
\label{thm:real-unary-streamname-transported-selected-endpoint-shape-package}
For unary observation maps $s,t,s',t':\Hist\to\Hist$, a certified observation
$n:\Hist$, and histories $a,b,z_s,z_t:\Hist$, assume
$$
\mathsf{UnaryHistory}(n),\quad
\mathsf{RealUnaryStreamClassifier}(s,t),
$$
the pointwise transport rows
$$
\forall k,\ \mathsf{UnaryHistory}(k)\to\hsame(s(k),s'(k)),
\quad
\forall k,\ \mathsf{UnaryHistory}(k)\to\hsame(t(k),t'(k)),
$$
and the displayed selected endpoints
$$
\hsame(s'(n),\Eone(a)),\quad \hsame(t'(n),\Eone(b)).
$$
Then the transported selected endpoints carry the full RatUp denominator and
one-tail shape package:
$$
\begin{array}{l}
\mathsf{RatHistoryClassifier}(s'(n),t'(n))\land
\mathsf{PositiveUnaryDenominator}(s'(n))\land
\mathsf{PositiveUnaryDenominator}(t'(n))\land\\
\mathsf{UnaryHistory}(s'(n))\land
\mathsf{UnaryHistory}(t'(n))\land
(\hsame(s'(n),\emp)\to\mathsf{False})\land
(\hsame(t'(n),\emp)\to\mathsf{False})\land\\
(\hsame(s'(n),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t'(n),\Ezero(z_t))\to\mathsf{False})\land\\
\mathsf{UnaryHistory}(a)\land
\mathsf{UnaryHistory}(b)\land
\hsame(a,b).
\end{array}
$$
\end{theorem}
\begin{proof}
Evaluate $\mathsf{RealUnaryStreamClassifier}(s,t)$ at the certified observation
$n$. The assumption $\mathsf{UnaryHistory}(n)$ gives the point classifier
$\mathsf{RatHistoryClassifier}(s(n),t(n))$.

Apply \autoref{thm:rat-history-classifier-hsame-transport} to this point
classifier and to the two pointwise transport rows evaluated at $n$. This gives
the transported selected classifier
$\mathsf{RatHistoryClassifier}(s'(n),t'(n))$.

Apply \autoref{thm:rat-history-classifier-positive-denominators} to the
transported selected classifier, then apply
\autoref{thm:positive-unary-denominator-unary-and-nonempty} separately to the two
positive-denominator witnesses. These rows give the two positive denominators,
the two unary endpoint rows, and the two nonempty exclusions.

It remains to rule out zero-headed displays. If $\hsame(s'(n),\Ezero(z_s))$
holds, transport $\mathsf{PositiveUnaryDenominator}(s'(n))$ along that comparison
by \autoref{thm:rat-positive-unary-denominator-hsame-transport}, then contradict
\autoref{thm:rat-positive-denominator-e0-absurd}. The same argument for $t'(n)$
and $z_t$ gives the second zero-headed exclusion.

For the one-tail readback, transport
$\mathsf{RatHistoryClassifier}(s'(n),t'(n))$ along the two displayed
$\Eone$ endpoint comparisons, obtaining
$\mathsf{RatHistoryClassifier}(\Eone(a),\Eone(b))$. Apply
\autoref{thm:rat-history-classifier-e1-tail-unary-iff} in the forward direction
to read back $\mathsf{UnaryHistory}(a)$, $\mathsf{UnaryHistory}(b)$, and
$\hsame(a,b)$, then package all displayed rows.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamClassifier\_transported\_selected\_endpoint\_shape\_package}

Fit. Traditional target: selected unary stream observation readback. BEDC source:
RealUp unary streams plus RatUp classifier. Carrier: unary-indexed rational
observation maps. Classifier: $\mathsf{RealUnaryStreamClassifier}$. Stability:
pointwise $\hsame$ transport. Ledger: selected certified observation and endpoint
displays. Core theorem:
\autoref{thm:real-unary-streamname-transported-selected-endpoint-shape-package}.
Exactness: displayed endpoint package. Standard bridge: selected rational
observation readback for RealUp names. Status: $\mathsf{ProofTarget}$.
