\begin{theorem}[Rat StreamName unary-context full endpoint package]
\label{thm:rat-streamname-unary-context-full-endpoint-package}
For observation maps $s,t:\Hist\to\Hist$, a selected observation $n:\Hist$,
prefix and tail histories $p_s,p_t,q_s,q_t:\Hist$, middle histories
$m_s,m_t:\Hist$, output histories $o_s,o_t:\Hist$, displayed tails
$a,b:\Hist$, and zero-head tests $z_s,z_t:\Hist$, assume
$$
\begin{array}{l}
\mathsf{RatStreamNameClassifier}(s,t),\quad
\mathsf{UnaryHistory}(n),\quad
\mathsf{UnaryHistory}(p_s),\quad
\hsame(p_s,p_t),\\
\mathsf{UnaryHistory}(q_s),\quad
\hsame(q_s,q_t),\quad
\mathsf{Cont}(p_s,s(n),m_s),\quad
\mathsf{Cont}(m_s,q_s,o_s),\\
\mathsf{Cont}(p_t,t(n),m_t),\quad
\mathsf{Cont}(m_t,q_t,o_t),\quad
\hsame(o_s,\Eone(a)),\quad
\hsame(o_t,\Eone(b)).
\end{array}
$$
Then the two contextual outputs carry the full RatUp endpoint package:
$$
\begin{array}{l}
\mathsf{RatHistoryClassifier}(o_s,o_t)\land
\mathsf{PositiveUnaryDenominator}(o_s)\land
\mathsf{PositiveUnaryDenominator}(o_t)\land\\
\mathsf{UnaryHistory}(o_s)\land
\mathsf{UnaryHistory}(o_t)\land
(\hsame(o_s,\emp)\to\mathsf{False})\land
(\hsame(o_t,\emp)\to\mathsf{False})\land\\
(\hsame(o_s,\Ezero(z_s))\to\mathsf{False})\land
(\hsame(o_t,\Ezero(z_t))\to\mathsf{False})\land\\
\mathsf{UnaryHistory}(a)\land
\mathsf{UnaryHistory}(b)\land
\hsame(a,b).
\end{array}
$$
\end{theorem}
\begin{proof}
Project the point classifier from
$\mathsf{RatStreamNameClassifier}(s,t)$ at the certified observation $n$. This
gives $\mathsf{RatHistoryClassifier}(s(n),t(n))$.

Build the contextual output classifier by applying
\autoref{thm:rat-history-classifier-unary-denominator-context-closed} to the
point classifier and the matching unary prefix and tail contexts, then use the
four continuation displays and associativity of the continuation append to
transport the closed classifier to $o_s$ and $o_t$.

Apply
\autoref{thm:rat-history-classifier-cont-unary-context-positive-denominators}
to the same point classifier and the displayed continuation context. This
exposes positive unary denominator witnesses for $o_s$ and $o_t$. Applying
\autoref{thm:positive-unary-denominator-unary-and-nonempty} separately gives
the unary-history rows and the two exclusions against $\emp$.

For a zero-headed display on the left, transport
$\mathsf{PositiveUnaryDenominator}(o_s)$ along $\hsame(o_s,\Ezero(z_s))$ and
contradict \autoref{thm:rat-positive-denominator-e0-absurd}. The right endpoint
uses the same transport argument with $o_t$ and $z_t$.

Finally apply
\autoref{thm:rat-streamname-classifier-unary-context-e1-pair-readback} to the
original StreamNameUp classifier, the certified observation, the matching
contexts, the four continuation rows, and the two displayed $\Eone$ outputs.
This reads back $\mathsf{UnaryHistory}(a)$, $\mathsf{UnaryHistory}(b)$, and
$\hsame(a,b)$. Collecting the classifier, denominator, exclusion, and readback
rows gives the displayed endpoint package.
\end{proof}

Fit. Traditional target: unary-context endpoint readback for certified rational
stream names. BEDC source: $\StreamNameUp+\RatUp$ over $\mathsf{BHist}$.
Carrier: observation maps with unary BEDC observations. Classifier:
$\mathsf{RatStreamNameClassifier}$. Stability: point projection, RatUp unary
context closure, continuation readback, and positive-denominator transport.
Ledger: selected observation, matching prefix and tail contexts, continuation
rows, endpoint displays, and zero-head tests. Core theorem:
\autoref{thm:rat-streamname-unary-context-full-endpoint-package}. Exactness:
the displayed contextual endpoint package. Standard bridge: concrete
BHist-anchored rational observation contexts for RealUp names. Status:
$\mathsf{ProofTarget}$.
