\begin{theorem}[Rat StreamName unary-context e-one tail determinacy]
\label{thm:rat-streamname-unary-context-e1-tail-determinacy}
For observation maps $s,t:\Hist\to\Hist$, a selected observation $n:\Hist$,
prefix and tail histories $p_s,p_t,q_s,q_t:\Hist$, middle histories
$m_s,m_t:\Hist$, output histories $o_s,o_t:\Hist$, and displayed tails
$a,a',b,b':\Hist$, assume
$$
\begin{array}{l}
\mathsf{RatStreamNameClassifier}(s,t),\quad
\mathsf{UnaryHistory}(n),\quad
\mathsf{UnaryHistory}(p_s),\quad
\hsame(p_s,p_t),\\
\mathsf{UnaryHistory}(q_s),\quad
\hsame(q_s,q_t),\quad
\mathsf{Cont}(p_s,s(n),m_s),\quad
\mathsf{Cont}(m_s,q_s,o_s),\\
\mathsf{Cont}(p_t,t(n),m_t),\quad
\mathsf{Cont}(m_t,q_t,o_t),
\end{array}
$$
and the four e-one displays
$$
\hsame(o_s,\Eone(a)),\quad
\hsame(o_s,\Eone(a')),\quad
\hsame(o_t,\Eone(b)),\quad
\hsame(o_t,\Eone(b')).
$$
Then all of the following data hold:
\begin{enumerate}
\item $\mathsf{UnaryHistory}(a)$;
\item $\mathsf{UnaryHistory}(a')$;
\item $\mathsf{UnaryHistory}(b)$;
\item $\mathsf{UnaryHistory}(b')$;
\item $\hsame(a,a')$;
\item $\hsame(a,b)$;
\item $\hsame(a,b')$;
\item $\hsame(a',b)$;
\item $\hsame(a',b')$;
\item $\hsame(b,b')$.
\end{enumerate}
\end{theorem}
\begin{proof}
Apply
\autoref{thm:rat-streamname-unary-context-full-endpoint-package}
to the displays $\hsame(o_s,\Eone(a))$ and $\hsame(o_t,\Eone(b))$.
Its tail rows supply $\mathsf{UnaryHistory}(a)$,
$\mathsf{UnaryHistory}(b)$, and $\hsame(a,b)$.

Apply the same full endpoint package again to the displays
$\hsame(o_s,\Eone(a'))$ and $\hsame(o_t,\Eone(b'))$. This supplies
$\mathsf{UnaryHistory}(a')$, $\mathsf{UnaryHistory}(b')$, and
$\hsame(a',b')$.

For the left-output tail comparison, compose the first display of $o_s$ with
the symmetry of the second display. The resulting
$\hsame(\Eone(a),\Eone(a'))$ is inverted by
$\mathsf{BEDC.FKernel.Hist.hsame\_e1\_inversion\_iff}$, giving
$\hsame(a,a')$.

The same composition and e-one inversion applied to the two displays of $o_t$
gives $\hsame(b,b')$. Transitivity of $\hsame$, using $\hsame(a,b)$ together
with symmetry of $\hsame(a',b')$ and the two same-side comparisons, gives the
remaining mixed rows $\hsame(a,b')$ and $\hsame(a',b)$. Package the four
unary rows with the six displayed tail comparisons.
\end{proof}

Fit. Traditional target: selected contextual rational-stream tail determinacy.
BEDC source: $\StreamNameUp+\RatUp+\mathsf{BHist}$. Carrier: observation maps
over $\Hist$. Classifier: $\mathsf{RatStreamNameClassifier}$. Stability:
unary context closure, e-one no-confusion, and $\hsame$ transitivity. Ledger:
selected observation, context rows, continuation rows, and endpoint displays.
Core theorem:
\autoref{thm:rat-streamname-unary-context-e1-tail-determinacy}. Exactness:
uniqueness of displayed e-one tails. Standard bridge: RegSeqRat selected
observation canonicalization. Status: $\mathsf{ProofTarget}$.

\begin{theorem}[Rat StreamName unary-context bundled tail determinacy]
\label{thm:rat-streamname-unary-context-bundled-tail-determinacy}
Let $s,t:\Hist\to\Hist$ be public rational $\StreamNameUp$ rows with
$\mathsf{RatStreamNameClassifier}(s,t)$. Let
$\mathcal P:\mathsf{ProbeBundle}$ be a finite bundle of unary observation
requests. Suppose that every bundled request $n$ with
$\mathsf{InBundle}(n,\mathcal P)$ carries $\mathsf{UnaryHistory}(n)$, shared
prefix rows $p_s(n),p_t(n):\Hist$, shared tail-context rows
$q_s(n),q_t(n):\Hist$, middle rows $m_s(n),m_t(n):\Hist$, output rows
$o_s(n),o_t(n):\Hist$, and displayed tails
$a(n),a'(n),b(n),b'(n):\Hist$ satisfying
$$
\begin{aligned}
\mathsf{UnaryHistory}(p_s(n)),\quad \hsame(p_s(n),p_t(n)),\quad
\mathsf{UnaryHistory}(q_s(n)),\quad \hsame(q_s(n),q_t(n)),\\
\mathsf{Cont}(p_s(n),s(n),m_s(n)),\quad
\mathsf{Cont}(m_s(n),q_s(n),o_s(n)),\\
\mathsf{Cont}(p_t(n),t(n),m_t(n)),\quad
\mathsf{Cont}(m_t(n),q_t(n),o_t(n)).
\end{aligned}
$$
and the four e-one endpoint displays
$$
\hsame(o_s(n),\Eone(a(n))),\quad
\hsame(o_s(n),\Eone(a'(n))),\quad
\hsame(o_t(n),\Eone(b(n))),\quad
\hsame(o_t(n),\Eone(b'(n))).
$$
Then the bundled displayed tail rows are unary and pairwise $\hsame$ across
all source and target endpoint reads. More explicitly, for every bundled
$n$, the four rows $a(n),a'(n),b(n),b'(n)$ are unary, and the six comparisons
$$
\begin{gathered}
\hsame(a(n),a'(n)),\quad \hsame(a(n),b(n)),\quad
\hsame(a(n),b'(n)),\\
\hsame(a'(n),b(n)),\quad \hsame(a'(n),b'(n)),\quad
\hsame(b(n),b'(n))
\end{gathered}
$$
hold inside the same finite bundle surface. This surface is exactly the
finite source surface consumed by the $\RegSeqRatUp/\RealUp$ handoff: the
bundled unary rows, their $\mathsf{InBundle}$ witnesses, the shared
prefix--tail context, the continuation rows, the endpoint displays, the
pointwise rational-stream handoff rows, and the support rows
$\hsame,\Cont,\Pkg,\NameCert$. It contains no quotient stream equality,
selected limit, host real equality, metric-completion point, or $\RealUp$
completeness row.
\end{theorem}
\begin{proof}
Fix a bundled observation $n$ and its membership row
$\mathsf{InBundle}(n,\mathcal P)$. Apply
\autoref{thm:rat-streamname-unary-context-e1-tail-determinacy} to the
displayed prefix, tail-context, continuation, output, and e-one rows attached
to $n$. This gives the four unary tail rows and the six pairwise $\hsame$
comparisons for that bundled request.

Repeat this pointwise over the finite $\mathsf{ProbeBundle}$. The
$\mathsf{InBundle}$ membership witnesses keep each selected observation
inside $\mathcal P$, so the collected rows are one finite family rather than
a hidden choice of endpoint tails.

Finally apply
\autoref{thm:streamname-tail-compatible-window-cofinal-bundle-lock}. Its
cofinal packet identifies the collected unary observations, membership rows,
shared tail-compatible context, pointwise $\RegSeqRatUp$ handoff rows, and
support rows as the finite bundled handoff surface. The non-escape clauses in
that lock exclude quotient stream equality, selected limits, host real
equality, metric-completion data, and ambient $\RealUp$ completeness from the
surface just constructed.
\end{proof}

Fit. Traditional target: finite contextual rational-stream tail determinacy.
BEDC source: $\StreamNameUp+\RatUp+\mathsf{ProbeBundle}+\mathsf{BHist}$.
Carrier: public rational StreamName rows over $\Hist$ with bundled unary
requests. Classifier: $\mathsf{RatStreamNameClassifier}$ together with
$\mathsf{InBundle}$ membership. Stability: pointwise unary-context closure,
e-one no-confusion, finite-bundle collection, and tail-compatible cofinal
locking. Ledger: bundled observation rows, shared prefix and tail-context
rows, continuation rows, endpoint displays, pointwise rational handoff rows,
and $\Pkg/\NameCert$ support. Core theorem:
\autoref{thm:rat-streamname-unary-context-bundled-tail-determinacy}.
Exactness: all displayed source and target e-one tails in the bundle are
unary and pairwise $\hsame$. Standard bridge: finite $\RegSeqRatUp/\RealUp$
handoff surface. Status: $\mathsf{ProofTarget}$.
