\chapter{A Concrete Naming Certificate for $\BishopCompletionIdempotenceWitnessUp$}
\label{ch:concrete-instances-bishop-completion-idempotence-witness-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\BishopCompletionIdempotenceWitnessUp$ packet records the finite witness that applying regular-Cauchy completion to an already displayed regular-Cauchy completion route does not create a second ambient completion object. It sits after the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the idempotence boundary of \autoref{ch:concrete-instances-cauchy-completion-idempotence-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the Bishop-style flattening witness as BEDC rows, not as quotient representatives, selected limits, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop completion-idempotence witness carrier]
\label{def:bishop-completion-idempotence-witness-carrier}
A $\BishopCompletionIdempotenceWitnessUp$ carrier is a finite $\BHist$ packet
$$
W=(S,D,R,I,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ finite-window row exposing the source and repeated-completion requests.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used by the window comparison and regularity readback.
\item $R$ is the $\RegSeqRatUp$ row carrying the regular rational source readback visible to the completion route.
\item $I$ is the $\CauchyCompletionIdempotenceUp$ row flattening the repeated completion boundary to the displayed completion route.
\item $E$ is the terminal $\RealUp$ seal row reached only after $S,D,R,I$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the window, tolerance, readback, idempotence, seal, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay of the same finite route.
\item $P$ is the $\Pkg$ provenance over $\BishopCompletionIdempotenceWitnessUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyCompletionIdempotenceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopCompletionIdempotenceWitnessUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $S,D,R,I,E,H,C,P,N$. It has no coordinate for quotient regular sequences, selected representatives, a second completed object, countable choice, host equality of completions, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Bishop completion-idempotence witness obligations]
\label{thm:bishop-completion-idempotence-witness-obligations}
For every accepted $\BishopCompletionIdempotenceWitnessUp$ carrier
$$
W=(S,D,R,I,E,H,C,P,N),
$$
the local $\NameCert_{\BishopCompletionIdempotenceWitnessUp}$ surface consists exactly of finite stream-window exposure through $S$, dyadic tolerance exposure through $D$, regular rational readback through $R$, displayed completion-idempotence flattening through $I$, terminal real sealing through $E$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-completion-idempotence-witness-carrier}. The rows $S,D,R$ expose the regular-Cauchy source route, while $I$ supplies the displayed idempotence row consumed by the completion-facing read.

Use the sibling surfaces in order. The stream windows come from \autoref{ch:concrete-instances-streamname-namecert}, the tolerance ledger from \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the regular rational readback from \autoref{ch:concrete-instances-regseqrat-namecert}. The flattening row is exactly the finite idempotence boundary of \autoref{ch:concrete-instances-cauchy-completion-idempotence-namecert}.

Finally $E,H,C,P,N$ seal, transport, replay, source, and name the same finite route. Because the carrier contains no quotient, selector, second-completion, choice, host-equality, or ambient-completeness coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Bishop completion-idempotence witness route]
\label{thm:bishop-completion-idempotence-witness-route}
Every $\RealUp$ or Completion consumer of an accepted $\BishopCompletionIdempotenceWitnessUp$ packet factors through the finite route
$$
\StreamNameUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp,\ \CauchyCompletionIdempotenceUp,\ \RealUp .
$$
Thus repeated regular-Cauchy completion is flattened by displayed BEDC rows before the terminal real seal is consumed. The route exports no quotient representative, selected limit, second completion carrier, countable-choice schedule, host equality of completed objects, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with \autoref{thm:bishop-completion-idempotence-witness-obligations}. It forces every consumer read through the finite window, dyadic tolerance, regular readback, idempotence, and real-seal rows before the local certificate can be inspected.

The $\CauchyCompletionIdempotenceUp$ row then identifies the repeated-completion boundary with the displayed completion route. Since the row is downstream of $S,D,R$, the flattening is a finite regular-Cauchy read rather than a comparison of quotient representatives.

The terminal row $E$ is only the $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The absence of quotient, selector, choice, host-equality, second-completion, and ambient-completeness coordinates prevents any such object from entering the exported route.
\end{proof}

\falsifiablePrediction{Every accepted $\BishopCompletionIdempotenceWitnessUp$ read exposes StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, CauchyCompletionIdempotence flattening, RealUp seal, componentwise hsame, Cont replay, Pkg provenance, and local NameCert rows before any repeated-completion consumer is served.}

\independenceWitness{streamname, dyadicratcore, regseqrat, cauchy-completion-idempotence, real: none is bijective with $\BishopCompletionIdempotenceWitnessUp$ because this packet alone binds the regular-Cauchy observation route, displayed completion-idempotence flattening row, terminal RealUp seal, transport, replay, provenance, and local naming as one witness.}

\closureat{BishopCompletionIdempotenceWitnessUp}{seedStr}

\begin{closurestatus}{\BishopCompletionIdempotenceWitnessUp}
  \constructivestory{A $\BishopCompletionIdempotenceWitnessUp$ packet is generated from StreamName windows, DyadicRatCore tolerance rows, RegSeqRat readback, a CauchyCompletionIdempotence flattening row, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-completion-idempotence-witness-carrier}, \autoref{thm:bishop-completion-idempotence-witness-obligations}, and \autoref{thm:bishop-completion-idempotence-witness-route} seed the finite Bishop-style repeated-completion flattening witness.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, countable choice, host equality of completed objects, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-window coverage, dyadic tolerance exactness, RegSeqRat readback, idempotence flattening, RealUp seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BishopCompletionIdempotenceWitnessUp.}
\end{closurestatus}
