\chapter{Unary Commutativity Proof Obligations}
\label{ch:v151-unary-obligations}

The v1.5 additive boundary correctly states that \(\AddUp\) requires unary continuation commutativity. This chapter decomposes that commutativity proof into smaller obligations. These obligations are more suitable for machine verification than a single opaque paper proof.

\begin{definition}[Unary right-shift obligation]
The unary right-shift obligation is the statement that if
\[
  \Unary(k),
  \qquad
  \ContR(k,\Eone(h),r),
\]
then there exists a history \(v\) such that
\[
  \ContR(k,h,v)
  \quad\text{and}\quad
  \hsame(r,\Eone(v)).
\]
\end{definition}

\begin{definition}[\(\Eone\)-congruence obligation]
The \(\Eone\)-congruence obligation is the statement that
\[
  \hsame(u,v)
  \quad\Rightarrow\quad
  \hsame(\Eone(u),\Eone(v)).
\]
\end{definition}

\begin{definition}[Unary continuation commutativity obligation]
The unary continuation commutativity obligation is the statement that if
\[
  \Unary(h),\quad \Unary(k),\quad
  \ContR(h,k,r),\quad \ContR(k,h,r'),
\]
then
\[
  \hsame(r,r').
\]
\end{definition}

\begin{theorem}[Commutativity from right-shift and \(\Eone\)-congruence]
\label{thm:v151-comm-from-obligations}
Assume unary right-shift, \(\Eone\)-congruence, continuation unit laws, continuation associativity up to \(\hsame\), and unary closure of continuation. Then unary continuation commutativity holds.
\end{theorem}

\begin{proof}
Induct on the unary derivation of the left input \(h\). The empty case follows from the unit laws. In the step case, write \(h=\Eone(h_0)\). Invert \(\ContR(\Eone(h_0),k,r)\) to obtain \(u\) with \(\ContR(h_0,k,u)\) and \(\hsame(r,\Eone(u))\). Apply unary right-shift to \(\ContR(k,\Eone(h_0),r')\) to obtain \(v\) with \(\ContR(k,h_0,v)
\) and \(\hsame(r',\Eone(v))\). By the induction hypothesis, \(\hsame(u,v)\). By \(\Eone\)-congruence, \(\hsame(\Eone(u),\Eone(v))\). Transitivity of \(\hsame\) yields \(\hsame(r,r')\).
\end{proof}

\begin{corollary}[Additive naming boundary after v1.5.1]
The name \(\AddUp\) is licensed only after the unary right-shift and \(\Eone\)-congruence obligations have been supplied. Before that point, the frozen safe name is \(\UnaryContMonoidUp\).
\end{corollary}

\begin{proof}
The monoid-like name requires unit and associativity. The additive name requires the additional commutativity field. Theorem~\ref{thm:v151-comm-from-obligations} reduces that field to two smaller obligations plus the already known continuation laws.
\end{proof}
