\chapter{Summary of the v1.5.1 Proof-Obligation Patch}
\label{ch:v151-summary}

The v1.5.1 patch does not add a new derived object. It freezes only the corrections that are safe and turns the remaining risks into explicit proof obligations.

\begin{enumerate}
  \item \(\InDom(D,h)\) is frozen as the live replacement for \(h\in D\).
  \item \(\TokIntro(\Pi,s,p)\) is frozen as the live replacement for \(\Tok_{\Pi}(s)\).
  \item \(\DomainPolicy(D)\) is required before any concrete domain can participate in active gap theorems.
  \item \(\PkgTokPol(\Pi)\) is required before concrete package exactness can be used.
  \item Concrete Globalize exactness is policy-supported, not unconditional.
  \item The additive name \(\AddUp\) is conditional on unary commutativity; before that, the safe name is \(\UnaryContMonoidUp\).
\end{enumerate}

\begin{corollary}[Live state after v1.5.1]
After v1.5.1, the first concrete Globalize instance is correct as a policy-supported construction, and the first additive naming certificate is correct only as a conditional license pending unary commutativity obligations.
\end{corollary}

\begin{proof}
The Globalize statement follows from Chapters~\ref{ch:v151-domain-policy},~\ref{ch:v151-package-token-policy}, and~\ref{ch:v151-gap-policy}. The additive naming boundary follows from Chapter~\ref{ch:v151-unary-obligations}.
\end{proof}

\paragraph{Next proof target.}
The next proof work should be local, not expansive: establish \(\DomainPolicy\) for the unary source, implement \(\PkgTokPol\) for the concrete signature-token package, and prove unary right-shift plus \(\Eone\)-congruence.
