\begin{theorem}[Cauchy modulus refinement root-window selector uniqueness]
\label{thm:cauchy-modulus-refinement-root-window-selector-uniqueness}
Let
$$
R=(M_0,M_1,U,V,T,W,Q,E,H,C,P,N)
$$
and
$$
R'=(M_0',M_1',U',V',T',W',Q',E',H',C',P',N')
$$
be accepted $\CauchyModulusRefinementUp$ packets. Suppose the two packets expose the same source schedules, shared meet, selector budget, finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ readback, $\RegSeqRatUp$ handoff, and structural rows along the displayed root route. Then every $\RealUp$ or Completion-facing consumer classifies $E$ and $E'$ as the same consumer-visible Real seal under that route.

No Real completeness principle, quotient stream, selected host limit, countable-choice row, host real equality, hidden selector, or second meet row is used in the classification.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyModulusRefinementUp.CauchyModulusRefinementCarrier\_root\_window\_selector\_uniqueness}
\begin{proof}
First apply root route determinacy, \autoref{thm:cauchy-modulus-refinement-root-route-determinacy}. Agreement on the source schedules and shared meet places both accepted packets on the same displayed route through $U,V,T$ before a finite window or Real seal can be read.

Next use the Real-window budget pullback and terminal consumer theorems, \autoref{thm:cauchy-modulus-refinement-real-window-budget-pullback} and \autoref{thm:cauchy-modulus-refinement-real-window-terminal-consumer}. These force every $\RealUp$ or Completion-facing consumer to read the same finite request, window, dyadic readback, regular handoff, selector, disclosure, and support rows before it reaches the seal.

Finally invoke L10 row exactness, \autoref{thm:cauchy-modulus-refinement-l10-row-exactness}. The L10 consumer inventory is exactly the displayed route with $H,C,P,N$, so two accepted packets agreeing on those route rows expose one consumer-visible Real seal surface. Since none of the excluded rows is present in the carrier, the uniqueness claim does not use Real completeness.
\end{proof}

\begin{theorem}[Cauchy modulus refinement selector threshold exhaustion]
\label{thm:cauchy-modulus-refinement-window-selector-threshold-exhaustion}
Every accepted $\CauchyModulusRefinementUp$ route whose public consumer reaches a $\RealUp$ or Completion seal through the displayed root-window selector is exhausted by the finite rows
$$
M_0,M_1,U,V,T,W,Q,E,H,C,P,N.
$$
Deleting $U$, $T$, $W$, or $Q$ breaks the route before the seal can be consumed: $U$ supplies the selector budget, $T$ fixes the public threshold handoff, $W$ exposes the finite window, and $Q$ exposes the dyadic readback required by the public consumer.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyModulusRefinementUp.CauchyModulusRefinementPacket\_window\_selector\_threshold\_exhaustion}
\begin{proof}
First apply root route determinacy, \autoref{thm:cauchy-modulus-refinement-root-route-determinacy}. It places every accepted route to a Real or Completion seal on the displayed root route through $M_0,M_1,U,V,T,W,Q,E,H,C,P,N$.

Next use root budget consumer exhaustion, \autoref{thm:cauchy-modulus-refinement-root-budget-consumer-exhaustion}. The budget-facing consumer cannot reach the seal before reading the selector budget and its finite-window support, so deleting $U$ or $W$ interrupts the route before any public endpoint is available.

Then apply root threshold public exhaustion, \autoref{thm:cauchy-modulus-refinement-root-threshold-public-exhaustion}. The public threshold leg must pass through $T$ and the dyadic readback row $Q$ before it can expose the seal; removing either row leaves only a partial route.

Finally invoke the local selector uniqueness theorem, \autoref{thm:cauchy-modulus-refinement-root-window-selector-uniqueness}. Once the route rows are fixed, all Real or Completion-facing consumers read the same displayed seal surface. Thus the listed rows exhaust the accepted public route, and the four named deletions break it before seal consumption.
\end{proof}

\begin{theorem}[Cauchy modulus refinement Real-seal route nonescape]
\label{thm:cauchy-modulus-refinement-real-seal-route-nonescape}
Every accepted $\CauchyModulusRefinementUp$ route that reaches a $\RealUp$ or Completion seal through the root-window selector is confined to the rows
$$
M_0,M_1,U,V,T,W,Q,E,H,C,P,N.
$$
Preserving the seal preserves the selector budget $U$, the threshold handoff $T$, the finite window $W$, and the dyadic readback $Q$. Such a route cannot read a Real completeness principle, quotient stream, selected host limit, countable-choice row, host real equality, hidden selector, or second meet row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyModulusRefinementUp.CauchyModulusRefinementCarrier\_real\_seal\_route\_nonescape}
\begin{proof}
First apply root route determinacy, \autoref{thm:cauchy-modulus-refinement-root-route-determinacy}. It places every accepted route to a Real or Completion seal on the displayed root route before any terminal consumer can inspect the seal.

Next use real-window budget pullback and the real-window terminal consumer theorem, \autoref{thm:cauchy-modulus-refinement-real-window-budget-pullback} and \autoref{thm:cauchy-modulus-refinement-real-window-terminal-consumer}. These force the consumer-facing seal to retain the selector budget, finite window, dyadic readback, and public threshold handoff as displayed rows.

Now invoke L10 row exactness, \autoref{thm:cauchy-modulus-refinement-l10-row-exactness}. The L10 inventory is exactly the carrier rows $M_0,M_1,U,V,T,W,Q,E,H,C,P,N$, so no hidden completeness, quotient, host-limit, choice, equality, selector, or second-meet coordinate can be read.

Finally apply selector threshold exhaustion, \autoref{thm:cauchy-modulus-refinement-window-selector-threshold-exhaustion}. Deleting $U$, $T$, $W$, or $Q$ breaks the route before the seal can be consumed, hence preserving the seal preserves those four rows and the accepted route is nonescaping.
\end{proof}

\begin{corollary}[Cauchy modulus refinement root-window selector strict obstruction]
\label{cor:cauchy-modulus-refinement-root-window-selector-strict-obstruction}
Let an accepted $\CauchyModulusRefinementUp$ route reach a $\RealUp$ or Completion seal through the root-window selector, and let a displayed failure, refusal, separation, or countermodel row be read as blocking a named converse, reuse, transport, or readback attempt for that selector route. Then the obstruction is strict and local: it blocks only that named attempt at one of the displayed rows
$$
M_0,M_1,U,V,T,W,Q,E,H,C,P,N.
$$
Every consumer-facing use of the obstruction factors through the same finite route rows, and any coordinate not listed in this display is rejected as unavailable to the obstruction. In particular, the obstruction cannot be reinterpreted as a global impossibility theorem, a host theorem about all Cauchy presentations, a Real-completeness principle, a quotient-stream argument, a selected host limit, a countable-choice principle, host real equality, a hidden selector, a second meet row, or hidden external validation.
\end{corollary}
\begin{proof}
First apply the Real-seal route nonescape theorem, \autoref{thm:cauchy-modulus-refinement-real-seal-route-nonescape}. It confines every accepted root-window route reaching a $\RealUp$ or Completion seal to the displayed rows
$$
M_0,M_1,U,V,T,W,Q,E,H,C,P,N,
$$
and it states that preserving the seal preserves the selector budget $U$, threshold handoff $T$, finite window $W$, and dyadic readback $Q$. Thus any failure, refusal, separation, or countermodel row that is consumer-facing along this route can only be read through the named finite inventory; an unlisted coordinate has no place where it can be consumed.

Next apply root-window selector uniqueness, \autoref{thm:cauchy-modulus-refinement-root-window-selector-uniqueness}. Once the source schedules, shared meet, selector budget, finite window, dyadic readback, regular handoff, and structural rows agree along the displayed root route, every $\RealUp$ or Completion-facing consumer classifies the exposed seal by that same route surface. Hence an obstruction row cannot detach from its named converse, reuse, transport, or readback attempt and become a second classification principle for the seal.

Combining the two facts gives the strict local reading. Nonescape removes Real completeness, quotient streams, selected host limits, countable choice, host real equality, hidden selectors, and second meet rows from the available inventory, while uniqueness prevents the same finite obstruction row from being read as a different consumer-visible seal argument. Therefore the displayed obstruction blocks only the named route attempt inside the root-window selector packet and supplies no global impossibility theorem, host theorem, or hidden external validation.
\end{proof}
