\begin{theorem}[MulUp public semantic exit certificate]
\label{thm:mulup-public-semantic-exit-certificate}
The concrete unary multiplication surface obtained from
\autoref{thm:unary-multiplication-mulup-semantic-exit-package},
\autoref{thm:mulup-semantic-exit-audit-row-coverage}, the right and left
additive distribution surfaces
\autoref{thm:natmul-additive-right-distributivity-surface} and
\autoref{thm:natmul-additive-left-distributivity-surface}, and
\autoref{thm:natmul-unary-prefix-order-monotone} is the public
$\NameCert_{\MulUp}$ consumption package over $\mathsf{BHist}$ for the full
natural-arithmetic phase.

A consumer of this package may read only the carrier
$\mathsf{UnaryHistory}$, the classifier $\hsame$, the continuation ledger
$\Cont$, the multiplication relation $\mathsf{NatMul}$, the semantic result
$\NameCert$ row, and the displayed $\AddUp/\OrderUp$ interaction rows. The
certificate does not expose cancellation, semiring completeness, or
standard-bridge data.
\end{theorem}
\begin{proof}
Project the semantic exit package of
\autoref{thm:unary-multiplication-mulup-semantic-exit-package}. This gives the
unary carrier over $\mathsf{BHist}$, the classifier, the multiplication
relation, the unit, the finite multiplication law rows, and the semantic result
$\NameCert$ row.

Apply the audit coverage theorem
\autoref{thm:mulup-semantic-exit-audit-row-coverage}. Its coverage statement
identifies the same public rows with the two additive distribution surfaces and
the unary-prefix monotonicity row, all through $\mathsf{UnaryHistory}$,
$\hsame$, $\Cont$, and $\mathsf{NatMul}$.

Repack the two $\AddUp$ distribution rows and the $\OrderUp$ monotonicity row
as one public consumption boundary. Since every displayed row uses the same
carrier, classifier, continuation ledger, and multiplication relation, the
boundary is exactly the $\NameCert_{\MulUp}$ package consumed by the full
natural-arithmetic phase, while the excluded cancellation, semiring, and
standard-bridge data remain outside the theorem.
\end{proof}

\begin{definition}[MulUp Full Nat audit consumer surface]
\label{def:mulup-full-nat-audit-consumer-surface}
The Full Nat audit consumer surface for $\MulUp$ is the finite row family over
$\mathsf{BHist}$ consisting exactly of the carrier $\mathsf{UnaryHistory}$,
the classifier $\hsame$, the continuation ledger $\Cont$, the multiplication
relation $\mathsf{NatMul}$, the semantic result $\NameCert$ row, the right and
left $\AddUp$ distributivity rows, the unary-prefix $\OrderUp$ monotonicity
row, and the divisibility-order rows available in the phase-exit package.

Every row in the surface is read through the same unary endpoints, the same
history classifier, and the same finite continuation ledgers. The surface has
no coordinate for host multiplication, quotient equality, semiring structure,
or cancellation outside the displayed divisibility-order rows.
\end{definition}
\begin{proof}
This is the row list projected from
\autoref{thm:mulup-public-semantic-exit-certificate} and
\autoref{thm:mulup-full-nat-arithmetic-phase-exit-boundary}. The first theorem
fixes the carrier, classifier, continuation, multiplication, semantic result,
and $\AddUp/\OrderUp$ rows; the phase-exit boundary adds the divisibility-order
consumer rows over the same endpoints.
\end{proof}

\begin{theorem}[MulUp Full Nat Lean target boundary]
\label{thm:mulup-full-nat-lean-target-boundary}
A later Lean audit target for the L7 $\MulUp$ exit may consume exactly the rows
of \autoref{def:mulup-full-nat-audit-consumer-surface}: $\mathsf{UnaryHistory}$,
$\hsame$, $\Cont$, $\mathsf{NatMul}$, the semantic result $\NameCert$ row, the
two $\AddUp$ distributivity rows, the $\OrderUp$ monotonicity row, and the
divisibility-order rows. It may not consume host multiplication, quotient
formation, semiring primitives, a cancellation law, or a second carrier.
\end{theorem}
\begin{proof}
Start from the consumer normal form of
\autoref{thm:mulup-full-nat-arithmetic-consumer-normal-form}. It states that
the Full Nat Arithmetic consumer reads the phase-exit boundary only through
the listed $\mathsf{BHist}$ rows.

Next apply \autoref{thm:mulup-full-nat-arithmetic-phase-exit-boundary}. This
fixes the concrete source of the $\mathsf{NatMul}$ semantic exit, the additive
distribution rows, the order row, and the divisibility rows.

Therefore a Lean target whose purpose is audit consumption has no further input
slot. Any host multiplication, quotient, semiring, cancellation, or alternate
carrier would be outside the displayed row family and hence outside the
boundary.
\end{proof}

\begin{theorem}[MulUp L7 audit-clean exit surface]
\label{thm:mulup-l7-audit-clean-exit-surface}
The L7 Full Nat Arithmetic phase-exit surface for $\MulUp$ is assembled by the
checked $\mathsf{BEDC.Derived.PrimeUp.NatMul\_unary\_mulup\_certificate}$ row,
the checked
$\mathsf{BEDC.Derived.PrimeUp.NatMul\_result\_semanticNameCert}$ row, the
right and left $\AddUp$ distributivity rows, the unary-prefix $\OrderUp$
monotonicity row, and the divisibility-order rows of the phase-exit package.
All rows are over $\mathsf{UnaryHistory}$, $\hsame$, finite $\Cont$ ledgers,
and $\mathsf{NatMul}$.
\end{theorem}
\begin{proof}
Project \autoref{thm:mulup-public-semantic-exit-certificate}. It supplies the
public $\MulUp$ package and names the checked $\mathsf{NatMul}$ certificate and
semantic result certificate as the multiplication core.

Use \autoref{thm:mulup-full-nat-arithmetic-phase-exit-boundary} to attach the
surrounding arithmetic rows: the two $\AddUp$ distributivity rows, the
$\OrderUp$ monotonicity row, and the divisibility-order consumer rows. The
normal form theorem \autoref{thm:mulup-full-nat-arithmetic-consumer-normal-form}
identifies these as the rows available to a Full Nat Arithmetic consumer.

Finally repack the rows through
\autoref{def:mulup-full-nat-audit-consumer-surface}. The repacking changes no
carrier, classifier, continuation ledger, or multiplication relation, so the
result is a single L7 audit-clean exit surface rather than a host arithmetic
surface.
\end{proof}
