\begin{theorem}[Cauchy root filter-completion anchor]
\label{thm:cauchy-filter-completion-cauchy-anchor}
Every Cauchy root consumer that first reaches the $\CauchyFilterCompletionUp$ surface of \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert} must already have read the Cauchy core route, the finite $\StreamNameUp$ windows of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ tolerance ledger, and the terminal $\RealUp$ seal. The route remains inside componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert_{\CauchyUp}$ row.
\end{theorem}
\begin{proof}
Project the root hub through its Cauchy core child. The core route exposes the stream-window, tolerance, readback, transport, replay, provenance, and naming rows before any completion-facing consumer can inspect the root packet.

Now read the $\CauchyFilterCompletionUp$ chapter. Its completion handoff consumes the same finite windows and regular rational readback before the terminal Real seal is visible, so the root consumer cannot enter through a detached filter object.

The structural rows preserve the path. Componentwise $\hsame$ transport and displayed $\Cont$ replay keep the consumer inside the Cauchy root packet, while $\Pkg$ provenance and the local $\NameCert$ row record that no quotient filter, selected limit, countable-choice selector, host equality, or ambient $\RealUp$ completeness row is exported.
\end{proof}
