\chapter{A Concrete Naming Certificate for $\CauchyUp$}
\label{ch:concrete-instances-cauchy-namecert}
\origin{human}

Following Bishop and Bridges, the $\CauchyUp$ packet records the ordinary constructive Cauchy-real carrier as finite BEDC naming data. It sits above the stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular-rational sequence surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet is not a quotient construction of reals; it is a finite route by which a modulus, rational readback, transport, replay, provenance, and local naming row become visible before any $\RealUp$ consumer can read the Cauchy object.

\begin{definition}[Cauchy carrier]
\label{def:cauchy-carrier}
A $\CauchyUp$ carrier is a finite $\BHist$ packet
$$
X=(S,D,R,M,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ observation row, recording the finite windows of rational approximants inspected by the carrier.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row, carrying the positive dyadic scale, comparison cells, and slack conversions used to interpret each requested window.
\item $R$ is the $\RegSeqRatUp$ regular-sequence row, exposing the rational readback consumed downstream.
\item $M$ is the modulus row, recording the displayed threshold assignment used by Cauchy requests and refusing any hidden convergence theorem.
\item $Q$ is the modulus/readback compatibility row, requiring the stream window, dyadic tolerance, regular rational sequence, and modulus rows to agree at every displayed precision request.
\item $E$ is the terminal $\RealUp$ seal-facing row, exposed only after $S,D,R,M,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the stream, dyadic, regular-sequence, modulus, compatibility, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Cauchy request through $S,D,R,M,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through the displayed rows $S,D,R,M,Q,E,H,C,P,N$. It has no coordinate for quotient-stream equality, a selected limit, host real equality, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy NameCert obligations]
\label{thm:cauchy-namecert-obligations}
For every accepted $\CauchyUp$ carrier
$$
X=(S,D,R,M,Q,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyUp}$ surface consists exactly of carrier admission, stream-window stability, dyadic tolerance exactness, regular-rational readback, displayed modulus admission, modulus/readback compatibility, $\RealUp$ seal ordering, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming for the finite carrier of \autoref{def:cauchy-carrier}.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-carrier}. The accepted packet displays precisely the stream, dyadic, regular-sequence, modulus, compatibility, seal, transport, replay, provenance, and local naming rows.

The stability and exactness obligations are rowwise. The stream row supplies only finite windows, the dyadic row supplies only displayed tolerance cells, the regular-sequence row supplies only rational readback, and the modulus row supplies only the visible threshold assignment.

The compatibility row $Q$ binds these four data rows before any $\RealUp$ seal can be consumed. The structural rows $H,C,P,N$ then transport, replay, source, and name the same route without adding quotient equality, selected limits, host real equality, choice, trichotomy, compactness, or ambient completeness.
\end{proof}

\begin{theorem}[Cauchy modulus readback route]
\label{thm:cauchy-modulus-readback-route}
Every accepted $\CauchyUp$ consumer route factors through the displayed path
$$
S,D,M \longmapsto Q \longmapsto R \longmapsto E \longmapsto H,C,P,N .
$$
Thus a precision request reads finite $\StreamNameUp$ observations, $\DyadicRatCoreUp$ tolerances, the explicit modulus row, the compatibility row, the $\RegSeqRatUp$ readback, and only then the $\RealUp$ seal-facing boundary.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $X=(S,D,R,M,Q,E,H,C,P,N)$ and a displayed precision request. The only finite observations available to the request are the windows in $S$, and their tolerance scale is read through $D$.

The request next reads the explicit modulus row $M$. The compatibility row $Q$ is the only coordinate that relates the chosen window, tolerance, threshold, and regular-rational readback, so the route cannot bypass it.

After $Q$ is displayed, the consumer may read the $\RegSeqRatUp$ row $R$ and then the terminal $\RealUp$ seal-facing row $E$. The rows $H,C,P,N$ preserve this same route under transport, replay, provenance, and local naming.

Since the carrier has no quotient, selected-limit, host equality, countable-choice, trichotomy, open-cover, or ambient-completeness coordinate, the displayed route is the whole public Cauchy readback surface.
\end{proof}

\begin{theorem}[Cauchy StreamName RegSeqRat window]
\label{thm:cauchy-core-streamname-regseqrat-window}
Every accepted $\CauchyUp$ packet exposes its $\RegSeqRatUp$ row only through the displayed $\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance row, and modulus/readback compatibility row. Thus a regular rational read of $X=(S,D,R,M,Q,E,H,C,P,N)$ must factor through $S,D,M,Q$ before it can inspect $R$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-carrier}. The row $S$ is the only finite observation surface, $D$ is the only displayed tolerance surface, and $M$ is the only modulus row available to the packet.

Apply \autoref{thm:cauchy-namecert-obligations} to identify $Q$ as the compatibility row binding stream windows, dyadic tolerances, regular rational readback, and modulus data. Then apply \autoref{thm:cauchy-modulus-readback-route}: the displayed route reads $S,D,M$ and $Q$ before $R$.

The carrier has no quotient stream, selected limit, host real equality, countable choice, trichotomy, or ambient completeness coordinate. Hence the stated window and compatibility rows exhaust the public access path to $\RegSeqRatUp$.
\end{proof}

\begin{theorem}[Cauchy RegSeqRat Real seal]
\label{thm:cauchy-core-regseqrat-real-seal}
Every $\RealUp$-facing read of an accepted $\CauchyUp$ packet factors through the $\RegSeqRatUp$ readback row before the terminal real seal. In the notation of \autoref{def:cauchy-carrier}, the seal-facing route is
$$
S,D,M,Q \longmapsto R \longmapsto E \longmapsto H,C,P,N .
$$
It does not expose quotient streams, selected limits, host real equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project $X=(S,D,R,M,Q,E,H,C,P,N)$ from \autoref{def:cauchy-carrier}. The seal row $E$ is declared terminal and seal-facing; it is not an independent source of Cauchy data.

Use \autoref{thm:cauchy-modulus-readback-route} to order the displayed read. The route reaches $R$ after $S,D,M,Q$ and reaches $E$ only after $R$ has been displayed.

Finally apply \autoref{thm:cauchy-namecert-obligations}. The rows $H,C,P,N$ transport, replay, source, and name the same route, so they cannot insert quotient representatives, selected limits, host equality, countable choice, trichotomy, or ambient completeness between $\RegSeqRatUp$ and $\RealUp$.
\end{proof}

\begin{theorem}[Cauchy modulus transport stability]
\label{thm:cauchy-core-modulus-transport-stability}
Let
$$
X=(S,D,R,M,Q,E,H,C,P,N)
$$
and
$$
X'=(S',D',R',M',Q',E',H',C',P',N')
$$
be accepted $\CauchyUp$ packets. Suppose the stream row, dyadic tolerance row, modulus row, modulus/readback compatibility row, $\RegSeqRatUp$ readback row, $\RealUp$ seal row, replay row, provenance row, and local naming row are transported componentwise by the displayed $\hsame$ data in $H$ and $H'$, and suppose both packets are replayed through the same displayed $\Cont$ route. Then the public Cauchy readback route
$$
S,D,M \longmapsto Q \longmapsto R \longmapsto E \longmapsto H,C,P,N
$$
is the same BEDC route as
$$
S',D',M' \longmapsto Q' \longmapsto R' \longmapsto E' \longmapsto H',C',P',N' .
$$
In particular, componentwise transport of the modulus/readback surface cannot introduce quotient stream equality, a selected limit, host real equality, countable choice, trichotomy, or ambient completeness.
\end{theorem}
\begin{proof}
Project both accepted packets through \autoref{def:cauchy-carrier}. The only visible coordinates are the stream, dyadic tolerance, regular-rational readback, modulus, compatibility, seal, transport, replay, provenance, and local naming rows.

Apply \autoref{thm:cauchy-modulus-readback-route} to $X$ and to $X'$. The two projected routes must read their displayed stream, dyadic, and modulus rows before their compatibility rows, and the shared $\Cont$ replay identifies these reads through the componentwise $\hsame$ data.

Next use \autoref{thm:cauchy-core-streamname-regseqrat-window}. Access to $R$ and $R'$ is forced through the transported $S,D,M,Q$ and $S',D',M',Q'$ rows, so no other regular-rational readback path is available.

Finally apply \autoref{thm:cauchy-core-regseqrat-real-seal}. The $\RealUp$ seal remains downstream of the transported $\RegSeqRatUp$ rows, and the structural rows $H,C,P,N$ and $H',C',P',N'$ only transport, replay, source, and name that path. Since neither carrier contains quotient streams, selected limits, host equality, choice, trichotomy, or ambient completeness, the two displays name the same BEDC route.
\end{proof}
