\chapter{A Concrete Naming Certificate for $\CauchyCompleteOrderedFieldUp$}
\label{ch:concrete-instances-cauchy-complete-ordered-field-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, the $\CauchyCompleteOrderedFieldUp$ packet records the constructive complete ordered-field interface by finite regular-Cauchy and order-algebra rows rather than by an ambient completed real line. It sits beside the terminal Real naming seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational sequence packet of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic arithmetic substrate of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the constructive algebraic order packet of \autoref{ch:concrete-instances-real-alg-order-namecert}, and the Bishop real completion route of \autoref{ch:concrete-instances-bishop-real-completion-namecert}. The chapter exposes the common interface downstream completion and metric chapters can cite when they need Real scalars, regular Cauchy limit rows, and ordered-field compatibility in one NameCert packet.

\begin{definition}[Cauchy-complete ordered-field carrier]
\label{def:cauchy-complete-ordered-field-carrier}
A $\CauchyCompleteOrderedFieldUp$ carrier is a finite $\BHist$ packet
$$
K=(R,D,S,Q,B,A,L,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUp$ scalar row, read only through terminal Real name seals.
\item $D$ is the $\DyadicRatCoreUp$ positive-precision ledger used by the regular Cauchy and order rows.
\item $S$ is the $\StreamNameUp$ finite observation row for rational windows.
\item $Q$ is the $\RegSeqRatUp$ regular rational sequence row.
\item $B$ is the $\BishopRealCompletionUp$ completion route from $D,S,Q$ into the Real seal $R$.
\item $A$ is the $\RealAlgOrderUp$ algebra-order row, recording addition, multiplication, zero, one, positivity, and order compatibility only as displayed finite ledger entries.
\item $L$ is the regular-Cauchy limit ledger naming accepted Cauchy requests, precision windows, candidate limit rows, and convergence readbacks through $D,S,Q,B,R$.
\item $O$ is the order-algebra compatibility ledger, recording that limit rows preserve the displayed ordered-field operations through $A$ and not through host equality.
\item $H$ records componentwise $\hsame$ transport for scalar, dyadic, stream, regular-Cauchy, completion, algebra-order, limit, compatibility, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from precision requests through regular Cauchy readback, Bishop completion, Real sealing, algebra-order compatibility, and local naming.
\item $P$ is the $\Pkg$ provenance over $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealAlgOrderUp$, $\BishopRealCompletionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompleteOrderedFieldUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,D,S,Q,B,A,L,O,H,C,P,N$. It has no coordinate for ambient $\RealUp$ completeness, quotient equality of real names, trichotomy, open-cover compactness, selected representatives, or choice.
\end{definition}

\begin{theorem}[Cauchy-complete ordered-field NameCert obligations]
\label{thm:cauchy-complete-ordered-field-namecert-obligations}
For every accepted $\CauchyCompleteOrderedFieldUp$ carrier
$$
K=(R,D,S,Q,B,A,L,O,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompleteOrderedFieldUp}$ surface consists exactly of carrier admission for the displayed Real scalar row $R$, dyadic precision ledger $D$, stream-window row $S$, regular rational sequence row $Q$, Bishop completion route $B$, algebra-order row $A$, regular-Cauchy limit ledger $L$, order-algebra compatibility ledger $O$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-complete-ordered-field-carrier}. The projection exposes exactly the Real scalar, dyadic precision, stream-window, regular rational, Bishop completion, algebra-order, limit, compatibility, transport, replay, provenance, and naming rows.

The completion-facing rows are read only through $D,S,Q,B,R,L$. A consumer receives finite precision requests, finite rational windows, regular readbacks, the Bishop completion route, the terminal Real seal, and a displayed limit ledger.

The ordered-field rows are read only through $A$ and $O$. They record operation and order compatibility for the same displayed limit rows, without adding host equality, quotient representatives, trichotomy, open-cover compactness, selected limits, or choice.

Finally $H,C,P,N$ transport, replay, source, and name that finite surface. Since the carrier has no further coordinate, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Regular-Cauchy limit route]
\label{thm:cauchy-complete-ordered-field-regular-cauchy-limit-route}
Every limit read exported by an accepted $\CauchyCompleteOrderedFieldUp$ packet factors through the ordered route
$$
\DyadicRatCoreUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \BishopRealCompletionUp \longrightarrow \RealUp
$$
and then through the displayed limit ledger $L$ and structural rows $H,C,P,N$. Thus downstream completion and metric consumers may cite one finite interface for regular-Cauchy limit service, but they receive no ambient $\RealUp$ completeness theorem, quotient equality, selected representative, trichotomy, open-cover compactness, or choice principle.
\end{theorem}
\begin{proof}
Begin with the precision ledger $D$. It supplies only the positive dyadic rows inspected by the regular-Cauchy request.

The request then passes through $S$ and $Q$. The row $S$ names the finite rational windows, and $Q$ supplies the regular rational readback for those windows.

Only after that readback may the packet use $B$ and $R$. The Bishop completion row $B$ routes the same data to the terminal Real seal $R$, while $L$ records the candidate limit and convergence readbacks for the accepted request.

The rows $H,C,P,N$ preserve, replay, source, and name the route. No excluded ambient completeness or choice coordinate appears in the carrier, so every exported limit read is confined to the stated finite path.
\end{proof}

\begin{theorem}[Order-algebra compatibility route]
\label{thm:cauchy-complete-ordered-field-order-algebra-compatibility}
Every algebraic or order read exported by an accepted $\CauchyCompleteOrderedFieldUp$ packet factors through the $\RealAlgOrderUp$ row $A$ together with the regular-Cauchy limit ledger $L$ and the compatibility ledger $O$. Addition, multiplication, zero, one, positivity, and order comparison are available only as displayed rows compatible with the route through $D,S,Q,B,R$, and not as ambient host-field operations.
\end{theorem}
\begin{proof}
Read the algebra-order row $A$. It is the only coordinate naming field operations and order comparison, so a consumer cannot obtain algebraic structure from the host Real carrier.

Next read the limit ledger $L$. The ledger ties the operation and order requests to the same regular-Cauchy route through $D,S,Q,B,R$ used for limit service.

Use the compatibility ledger $O$ to bind the two surfaces. It records preservation of addition, multiplication, zero, one, positivity, and order comparison for the displayed limit rows.

Transport and replay are again confined to $H$ and $C$, with $P$ and $N$ supplying provenance and local naming. Thus the compatibility surface remains finite and supplies no quotient equality, trichotomy, open-cover compactness, selected representative, ambient completeness, or choice.
\end{proof}

\begin{theorem}[Cauchy-complete ordered-field regular-Cauchy existence]
\label{thm:cauchy-complete-ordered-field-regular-cauchy-existence}
For every accepted $\CauchyCompleteOrderedFieldUp$ carrier
$$
K=(R,D,S,Q,B,A,L,O,H,C,P,N),
$$
every regular-Cauchy limit request admitted by $K$ is presented only by a finite route through
$$
D \longrightarrow S \longrightarrow Q \longrightarrow B \longrightarrow R
$$
and by the limit ledger $L$. The existence surface therefore names limit service as displayed precision, stream-window, regular-sequence, Bishop-completion, Real-seal, and ledger rows, with no quotient equality, selected representative, choice, trichotomy, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Start with an admitted limit request. The carrier projection gives the dyadic precision row $D$, stream-window row $S$, regular rational sequence row $Q$, Bishop completion route $B$, Real seal $R$, and limit ledger $L$ as the only completion-facing coordinates.

The request is first read against $D$, then against the finite observation row $S$, then against the regular-sequence row $Q$. The route can enter the Real naming surface only through $B$ and then $R$.

The ledger $L$ records the accepted request, the precision windows, the candidate limit row, and the convergence readbacks for that same route. Since the carrier has no quotient, representative-selection, choice, trichotomy, or ambient-completeness coordinate, the displayed rows are the whole existence surface.
\end{proof}

\begin{theorem}[Cauchy-complete ordered-field order-limit transport]
\label{thm:cauchy-complete-ordered-field-order-limit-transport}
For every accepted $\CauchyCompleteOrderedFieldUp$ carrier
$$
K=(R,D,S,Q,B,A,L,O,H,C,P,N),
$$
every algebraic and order read on a limit row of $L$ factors through the algebra-order row $A$ and the compatibility ledger $O$. The transport rows $H$, replay rows $C$, provenance row $P$, and local naming row $N$ preserve that same finite route through $D,S,Q,B,R,L,A,O$ and add no host equality, selected representative, choice, trichotomy, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Read a limit row from $L$. Its completion data has already been confined to the route through $D,S,Q,B,R$.

Algebraic and order observations can then use only $A$ and $O$. The row $A$ names addition, multiplication, zero, one, positivity, and comparison, while $O$ records that those reads are compatible with the same displayed limit rows.

The structural rows do not create a second route. The transport row $H$ preserves the componentwise names, $C$ replays the displayed dependencies, $P$ records provenance, and $N$ supplies the local certificate name. Hence order-limit transport stays on the finite rows and does not expose host-field equality, representatives, choice, trichotomy, or ambient completeness.
\end{proof}

\begin{theorem}[CauchyCompleteOrderedField scoped kernel route]
\label{thm:cauchy-complete-ordered-field-scoped-kernel-route}
For every accepted $\CauchyCompleteOrderedFieldUp$ carrier
$$
K=(R,D,S,Q,B,A,L,O,H,C,P,N),
$$
the consumer-visible kernel route consists exactly of Real scalar exposure through $R$, dyadic precision through $D$, finite $\StreamNameUp$ windows through $S$, $\RegSeqRatUp$ readback through $Q$, Bishop completion handoff through $B$, $\RealAlgOrderUp$ operations through $A$, regular-Cauchy limit ledger reads through $L$, order-algebra compatibility through $O$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and the local $\NameCert_{\CauchyCompleteOrderedFieldUp}$ row $N$. No accepted carrier exports ambient Real completeness, quotient streams, host field operations, trichotomy, or selected limits beyond those displayed rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-complete-ordered-field-carrier}. The projection exposes precisely the rows $R,D,S,Q,B,A,L,O,H,C,P,N$, so any consumer route must begin inside the displayed finite packet.

Apply the NameCert obligations of \autoref{thm:cauchy-complete-ordered-field-namecert-obligations}. They identify the Real scalar, dyadic precision, stream-window, regular-rational, Bishop completion, algebra-order, limit, compatibility, transport, replay, provenance, and local naming rows as the full obligation surface.

The completion side is then fixed by \autoref{thm:cauchy-complete-ordered-field-regular-cauchy-limit-route}. The route to a Real-facing limit read passes through $D,S,Q,B,R,L$ and the structural rows, with no quotient stream or selected-limit coordinate.

The algebra and order side is fixed by \autoref{thm:cauchy-complete-ordered-field-order-algebra-compatibility}. Operations and order comparisons are read only through $A$ and $O$ against the same displayed limit ledger.

Since no carrier coordinate remains after $H,C,P,N$, the route refuses ambient $\RealUp$ completeness, quotient streams, host field operations, trichotomy, and selected limits. The scoped dependency surface is exactly the finite row list stated above.
\end{proof}

\closureat{CauchyCompleteOrderedFieldUp}{seedStr}
\closureat{CauchyCompleteOrderedFieldUp}{obligationStr}
\closureat{CauchyCompleteOrderedFieldUp}{scopedStr}

\begin{closurestatus}{\CauchyCompleteOrderedFieldUp}
  \constructivestory{A $\CauchyCompleteOrderedFieldUp$ packet is generated from Real scalar seals, dyadic precision rows, StreamName windows, RegSeqRat readbacks, a BishopRealCompletion route, RealAlgOrder operation and order rows, regular-Cauchy limit ledgers, compatibility ledgers, componentwise transport, replay, provenance, and local NameCert evidence.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:cauchy-complete-ordered-field-carrier}, \autoref{thm:cauchy-complete-ordered-field-namecert-obligations}, \autoref{thm:cauchy-complete-ordered-field-regular-cauchy-limit-route}, \autoref{thm:cauchy-complete-ordered-field-order-algebra-compatibility}, \autoref{thm:cauchy-complete-ordered-field-regular-cauchy-existence}, \autoref{thm:cauchy-complete-ordered-field-order-limit-transport}, and \autoref{thm:cauchy-complete-ordered-field-scoped-kernel-route} close the explicit finite scoped surface for Real, regular-Cauchy existence, order-limit transport, completion, and metric consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not assert ambient $\RealUp$ completeness, quotient equality of real names, trichotomy, open-cover compactness, selected representatives, choice, Lean verification, or bridge checking.}
  \upgradepath{Public closure requires checked consumer exports and downstream bridge rows for BEDC.Derived.CauchyCompleteOrderedFieldUp.}
\end{closurestatus}
