\chapter{A Concrete Naming Certificate for $\CauchyRealLocatorPointwiseInductionUp$}
\label{ch:concrete-instances-cauchy-real-locator-pointwise-induction-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the
$\CauchyRealLocatorPointwiseInductionUp$ packet records the finite-window
induction route used by Cauchy real locators. It is a sibling of the locator
surface of \autoref{ch:concrete-instances-cauchy-real-locator-namecert} and
the finite schedule discipline of
\autoref{ch:concrete-instances-streamname-namecert}: a pointwise induction
step opens one displayed stream window, reads its dyadic tolerance ledger,
passes through the regular rational readback, and returns to the same
Real-facing locator seal. The packet is not an induction principle over all
host streams, a quotient-real equality theorem, a countable-choice selector,
or an ambient completeness assertion.

\begin{definition}[Cauchy real locator pointwise induction carrier]
\label{def:cauchy-real-locator-pointwise-induction-carrier}
A $\CauchyRealLocatorPointwiseInductionUp$ carrier is a finite $\BHist$ packet
$$
I=(L,W,D,Q,R,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the source $\CauchyRealLocatorUp$ row, carrying the locator
modulus, finite-window, dyadic, regular-rational, and Real seal data.
\item $W$ is the $\StreamNameUp$ pointwise window row selected for the current
locator request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used to compare the pointwise
window with the requested side test.
\item $Q$ is the $\RegSeqRatUp$ readback row exposed after the window and
dyadic tolerance have been displayed.
\item $R$ is the terminal $\RealUp$ locator seal reached by the pointwise
readback.
\item $B$ is the finite induction-branch ledger, recording the base window and
successor-window handoff over the displayed rows $W,D,Q,R$.
\item $H$ records componentwise $\hsame$ transport for the locator source,
window, dyadic tolerance, regular readback, Real seal, branch ledger, replay,
provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay for each pointwise induction step.
\item $P$ is the $\Pkg$ provenance over $\CauchyRealLocatorUp$,
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local
$\NameCert_{\CauchyRealLocatorPointwiseInductionUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through these displayed rows. It
has no coordinate for host stream induction, quotient stream equality, selected
limits, countable choice, trichotomy, open-cover compactness, or ambient
$\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy real locator pointwise window induction]
\label{thm:cauchy-real-locator-pointwise-window-induction}
For every accepted $\CauchyRealLocatorPointwiseInductionUp$ carrier
$$
I=(L,W,D,Q,R,B,H,C,P,N),
$$
each pointwise locator step factors through the finite route
$$
L \longmapsto W,D \longmapsto Q \longmapsto R \longmapsto B,H,C,P,N .
$$
The base and successor cases of the induction ledger $B$ may inspect only the
displayed $\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance,
$\RegSeqRatUp$ readback, and $\RealUp$ locator seal supplied by the same
$\CauchyRealLocatorUp$ source row.
\end{theorem}
\begin{proof}
Project the accepted carrier. The source row $L$ is the only Cauchy real
locator coordinate, so every pointwise step begins by reading the displayed
locator packet of \autoref{ch:concrete-instances-cauchy-real-locator-namecert}.

The induction window is then opened through $W$. The dyadic tolerance row $D$
is the only comparison surface attached to that window, and the regular
rational readback $Q$ is available only after the window and dyadic rows have
been displayed.

The terminal read reaches $R$ and is then recorded by the branch ledger $B$.
The base branch and each successor branch therefore preserve the same finite
route rather than selecting a host stream representative.

Finally $H,C,P,N$ transport, replay, source, and name the same packet. Since
the carrier contains no row for host stream induction, quotient stream
equality, selected limits, countable choice, trichotomy, open-cover
compactness, or ambient completeness, the displayed route exhausts the
pointwise induction surface.
\end{proof}

\begin{theorem}[Cauchy real locator pointwise induction NameCert obligations]
\label{thm:cauchy-real-locator-pointwise-induction-namecert-obligations}
For every accepted $\CauchyRealLocatorPointwiseInductionUp$ carrier
$$
I=(L,W,D,Q,R,B,H,C,P,N),
$$
the local $\NameCert_{\CauchyRealLocatorPointwiseInductionUp}$ obligations are exactly carrier admission for the $\CauchyRealLocatorUp$ source row $L$, pointwise $\StreamNameUp$ window admission for $W$, $\DyadicRatCoreUp$ tolerance compatibility for $D$, $\RegSeqRatUp$ readback for $Q$, $\RealUp$ locator-seal ordering for $R$, finite base and successor branch admission for $B$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-real-locator-pointwise-induction-carrier}. The tuple displays the locator source, pointwise window, dyadic tolerance, regular-rational readback, real seal, branch ledger, and structural rows.

The source and window obligations are read from $L$ and $W$. The dyadic tolerance row $D$ is the only comparison surface attached to that pointwise window, and the readback row $Q$ can be inspected only after those rows are displayed.

The real-seal ordering obligation is the row $R$, downstream of $Q$. The branch ledger $B$ records the finite base and successor handoff over the same displayed rows rather than over a host stream representative.

The rows $H,C,P,N$ transport, replay, source, and name the packet. Since no other coordinate occurs in the carrier, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Cauchy real locator pointwise window stability]
\label{thm:cauchy-real-locator-pointwise-induction-window-stability}
Let
$$
I=(L,W,D,Q,R,B,H,C,P,N)
$$
be an accepted $\CauchyRealLocatorPointwiseInductionUp$ carrier. Replacing the locator source, $\StreamNameUp$ pointwise window, $\DyadicRatCoreUp$ tolerance row, $\RegSeqRatUp$ readback row, and $\RealUp$ seal by displayed componentwise $\hsame$ rows, and replaying the replacement through $C$, preserves the admissible pointwise induction route
$$
L\longmapsto W,D\longmapsto Q\longmapsto R\longmapsto B .
$$
Thus the base and successor branches of the finite induction ledger remain attached to the same locator source and cannot introduce host stream induction, quotient stream equality, selected limits, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier and use \autoref{thm:cauchy-real-locator-pointwise-window-induction}. Every pointwise step already factors through the displayed locator source, window, dyadic tolerance, regular-rational readback, real seal, and branch ledger.

The componentwise replacement is recorded by $H$. It transports the locator source, window, tolerance, readback, seal, branch ledger, replay, provenance, and local name without adding another induction coordinate.

The replay row $C$ then carries the transported rows through the same pointwise route. The branch ledger $B$ therefore continues to read the base window and successor-window handoff over $W,D,Q,R$.

The carrier has no row for any excluded host or quotient object, so row exhaustion shows that the transported packet preserves exactly the admissible pointwise induction route.
\end{proof}

\closureat{CauchyRealLocatorPointwiseInductionUp}{seedStr}

\begin{closurestatus}{\CauchyRealLocatorPointwiseInductionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-real-locator-pointwise-induction-carrier}, \autoref{thm:cauchy-real-locator-pointwise-window-induction}, \autoref{thm:cauchy-real-locator-pointwise-induction-namecert-obligations}, and \autoref{thm:cauchy-real-locator-pointwise-induction-window-stability} seed the finite pointwise induction route over CauchyRealLocator, StreamName, DyadicRatCore, RegSeqRat, RealUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host stream induction, quotient stream equality, selected limits, countable choice, trichotomy, open-cover compactness, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, window induction, dyadic tolerance compatibility, RegSeqRat readback, Real seal ordering, and local NameCert registration for BEDC.Derived.CauchyRealLocatorPointwiseInductionUp.}
  \constructivestory{A $\CauchyRealLocatorPointwiseInductionUp$ packet is generated from a CauchyRealLocator source row, one StreamName pointwise window, a DyadicRatCore tolerance ledger, a RegSeqRat readback row, a RealUp locator seal, a finite induction-branch ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
