\begin{definition}[Cauchy root stream carrier]
\label{def:cauchy-root-stream-carrier}
A $\CauchyUp$ root stream carrier is a finite $\BHist$ packet
$$
Q=(S,T,M,W,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $S$ is the certified finite observation stream. It records only the visible request windows that a Cauchy consumer may inspect.
\item $T$ is the tail-threshold row. It assigns each displayed precision request a later visible window of $S$.
\item $M$ is the modulus row. It records the finite evidence that two observations past the displayed threshold meet the requested tolerance.
\item $W$ is the witness ledger. It stores the accepted comparisons between observed entries, not a quotient class, selected limit, or ambient completeness theorem.
\item $H$ is componentwise $\hsame$ transport for the stream, threshold, modulus, witness, replay, provenance, and naming rows.
\item $C$ is displayed $\Cont$ replay from an admitted Cauchy request through $S,T,M,W,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyUp}$ row.
\end{enumerate}
The classifier compares accepted root stream packets only through the displayed tuple $S,T,M,W,H,C,P,N$.
\end{definition}

\begin{theorem}[Cauchy root tail stability]
\label{thm:cauchy-root-tail-stability}
Let $Q=(S,T,M,W,H,C,P,N)$ be an accepted $\CauchyUp$ root stream carrier. Every $\hsame$ transport of $Q$ and every displayed $\Cont$ replay of a Cauchy request preserves the tail-threshold row $T$, the modulus row $M$, and the witness ledger $W$ as componentwise rows over the same finite observation stream $S$. Consequently a tail read transported or replayed from $Q$ remains a Cauchy root stream read, and it does not acquire a quotient stream equality, a selected limit, a choice schedule, or a host completeness assertion.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-root-stream-carrier}. The only rows available to a Cauchy request are the displayed stream window, tail threshold, modulus, witness ledger, transport, replay, provenance, and naming rows.

The $\hsame$ row $H$ is componentwise by definition of the carrier surface. It transports $S,T,M,W,C,P,N$ as rows of the same packet, so it cannot introduce a second stream, an external representative, or an ambient equality oracle.

The $\Cont$ row $C$ replays an admitted request through the displayed packet. Since the replay reads $T,M,W$ after $S$ and before $P,N$, the transported request still witnesses the same finite tail-stability surface.
\end{proof}

\begin{theorem}[Cauchy root NameCert obligation surface]
\label{thm:cauchy-root-namecert-obligation-surface}
For every accepted $\CauchyUp$ root stream carrier $Q=(S,T,M,W,H,C,P,N)$, the local $\NameCert_{\CauchyUp}$ obligation surface consists exactly of the following rows:
\begin{enumerate}
\item carrier admission for the finite observation stream $S$;
\item classifier admission for the tail-threshold row $T$ and modulus row $M$;
\item stability under componentwise $\hsame$ transport $H$ and displayed $\Cont$ replay $C$;
\item comparison fidelity for the witness ledger $W$ against the displayed tolerance requests;
\item provenance and local naming through $P$ and $N$.
\end{enumerate}
No obligation row certifies quotient streams, selected limits, countable choice, host real equality, or an ambient completion theorem.
\end{theorem}
\begin{proof}
Read the eight rows of \autoref{def:cauchy-root-stream-carrier}. Carrier admission is the row $S$, while classifier admission is carried by the threshold and modulus rows $T,M$.

Stability is supplied by the structural rows $H$ and $C$. These rows keep the request inside the displayed packet and force every transported or replayed tail read to pass through the same finite stream surface.

The witness ledger $W$ supplies the comparison data for the displayed tolerance requests, and $P,N$ source and name the packet. Since no remaining coordinate exists, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy root completion consumer route]
\label{thm:cauchy-root-completion-consumer-route}
Every completion-facing consumer of an accepted $\CauchyUp$ root stream carrier first reads the finite stream row of \autoref{ch:concrete-instances-streamname-namecert}, then the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, then the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. Metric and uniform completion consumers may use the same displayed route only after those rows have exposed the tail threshold, modulus, and witness ledger of $Q$.
\end{theorem}
\begin{proof}
Start with a completion-facing read from $Q$. The carrier projection exposes the finite stream row before any threshold, modulus, witness, or structural row can be consumed.

The stream row is then read through the regular rational route. This is the point at which completion-facing consumers can inspect the finite rational data attached to the Cauchy window, while the Real seal remains downstream.

Finally the terminal Real seal is consumed after the tail-threshold, modulus, and witness rows are visible. The route therefore reaches completion consumers through StreamName, RegSeqRat, and RealUp data, not through quotient completions or selected representatives.
\end{proof}
