\chapter{A Concrete Naming Certificate for $\CauchyTailEnvelopeComparisonUp$}
\label{ch:concrete-instances-cauchy-tail-envelope-comparison-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CauchyTailEnvelopeComparisonUp$ packet records the finite comparison surface for two displayed Cauchy tail-envelope reads before either branch reaches the terminal real-name seal. It sits after the dyadic tail envelope of \autoref{ch:concrete-instances-dyadic-cauchy-tail-envelope-namecert}, the tail-diameter boundary of \autoref{ch:concrete-instances-cauchy-tail-diameter-namecert}, the finite stream schedules of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names a paired finite tail route; it is not quotient stream equality, a selected common limit, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy tail-envelope comparison carrier]
\label{def:cauchy-tail-envelope-comparison-carrier}
A $\CauchyTailEnvelopeComparisonUp$ carrier is a finite $\BHist$ packet
$$
Q=(E_0,E_1,W_0,W_1,D,J,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E_0$ and $E_1$ are accepted $\DyadicCauchyTailEnvelopeUp$ rows naming the two tail-envelope reads being compared.
\item $W_0$ and $W_1$ are the $\StreamNameUp$ tail windows opened by the two envelope reads.
\item $D$ is the shared $\DyadicRatCoreUp$ tolerance row used to compare the two displayed tails.
\item $J$ is the common-window row, recording the finite refinement through which $W_0$ and $W_1$ are read before either branch reaches a $\RealUp$ seal.
\item $T$ is the paired tail-diameter row, recording the displayed comparison with the $\CauchyTailDiameterUp$ boundary.
\item $H$ records componentwise $\hsame$ transport for the two envelope rows, stream windows, shared tolerance, common-window refinement, tail-diameter row, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a paired precision request through $E_0,E_1,J,D,T$.
\item $P$ is the $\Pkg$ provenance over $\CauchyTailEnvelopeComparisonUp$, $\DyadicCauchyTailEnvelopeUp$, $\CauchyTailDiameterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyTailEnvelopeComparisonUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. It has no coordinate for quotient stream equality, selected common limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, or bridge checking.
\end{definition}

\begin{theorem}[Cauchy tail-envelope comparison NameCert obligations]
\label{thm:cauchy-tail-envelope-comparison-namecert-obligations}
For every accepted $\CauchyTailEnvelopeComparisonUp$ carrier
$$
Q=(E_0,E_1,W_0,W_1,D,J,T,H,C,P,N),
$$
the local $\NameCert_{\CauchyTailEnvelopeComparisonUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the two dyadic tail-envelope rows, their stream windows, the shared dyadic tolerance, the common-window refinement, the paired tail-diameter row, transport, replay, provenance, and local naming rows;
\item envelope exposure, requiring both branches to display their $\DyadicCauchyTailEnvelopeUp$ rows before the paired comparison is consumed;
\item common-window admission, requiring $J$ to be fixed before either branch reads a $\RegSeqRatUp$ row toward $\RealUp$;
\item tolerance alignment, requiring both tail reads to use the same displayed $\DyadicRatCoreUp$ tolerance row $D$;
\item diameter comparison, requiring the paired tail-diameter row $T$ to be read through the same common window and tolerance data;
\item componentwise transport, displayed replay, provenance, and local naming through $H,C,P,N$;
\item refusal of quotient stream equality, selected common limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, and bridge checking as local certificate data.
\end{enumerate}
No comparison obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-tail-envelope-comparison-carrier}. The accepted packet exposes exactly the two dyadic tail-envelope rows $E_0,E_1$, their opened stream windows $W_0,W_1$, the shared tolerance row $D$, the common-window row $J$, the tail-diameter row $T$, and the structural rows $H,C,P,N$.

The envelope exposure clauses follow from the two displayed $\DyadicCauchyTailEnvelopeUp$ rows. Each branch must open its finite stream window before the paired comparison can read any regular rational data.

The common-window and tolerance clauses are the role of $J$ and $D$. They force the two branches to pass through one finite refinement and one dyadic budget before the paired tail-diameter row is consumed.

The remaining rows are structural. The $\hsame$ row transports each displayed coordinate componentwise, the $\Cont$ row replays the same paired route, and the $\Pkg$ and $\NameCert$ rows source and name only that finite surface.

Since none of the excluded principles occurs as a carrier coordinate, the local certificate cannot export quotient stream equality, a selected common limit, countable choice, trichotomy, host real equality, ambient Real completeness, or bridge checking.
\end{proof}

\begin{theorem}[Cauchy tail-envelope comparison common window]
\label{thm:cauchy-tail-envelope-comparison-common-window}
Every accepted $\CauchyTailEnvelopeComparisonUp$ carrier compares its two displayed tail-envelope reads through a single finite common-window route
$$
E_0,E_1 \longrightarrow J \longrightarrow W_0,W_1 \longrightarrow D \longrightarrow T .
$$
Consequently any $\RegSeqRatUp$, $\DyadicRatCoreUp$, or $\RealUp$ consumer of the paired comparison receives the same displayed common-window row before either branch can present a terminal real-name seal.
\end{theorem}
\begin{proof}
Begin with the two accepted envelope rows. By \autoref{thm:dyadic-cauchy-tail-envelope-common-refinement}, paired dyadic tail-envelope reads serving the same displayed precision request admit a finite common route before any $\RealUp$ seal is inspected.

The carrier row $J$ records that common route for the comparison packet. Once $J$ is fixed, both stream windows $W_0$ and $W_1$ are read as displayed rows over the same refinement rather than as completed streams.

The shared tolerance row $D$ and the tail-diameter row $T$ are then downstream from the common window. Thus every consumer of the paired comparison receives the displayed route through $E_0,E_1,J,W_0,W_1,D,T$ before any real-name seal is available.
\end{proof}

\begin{theorem}[Cauchy tail-envelope comparison nonescape]
\label{thm:cauchy-tail-envelope-comparison-nonescape}
Every $\RealUp$ or completion-facing consumer of an accepted $\CauchyTailEnvelopeComparisonUp$ packet receives only the two displayed $\DyadicCauchyTailEnvelopeUp$ rows, their finite $\StreamNameUp$ windows, the shared $\DyadicRatCoreUp$ tolerance, the common-window refinement, the $\CauchyTailDiameterUp$ comparison row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. It receives no quotient stream, selected common limit, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, or bridge-checking row.
\end{theorem}
\begin{proof}
Project the carrier rows listed in \autoref{def:cauchy-tail-envelope-comparison-carrier}. A consumer reaches the paired comparison only through $E_0,E_1,W_0,W_1,D,J,T,H,C,P,N$.

Apply \autoref{thm:cauchy-tail-envelope-comparison-common-window}. The common-window route places the two envelope rows, the finite refinement, the displayed windows, the shared tolerance, and the tail-diameter comparison before any terminal real-name seal can be read.

The excluded data are absent from the carrier and from the common-window route. Hence the comparison packet cannot export quotient streams, selected common limits, countable-choice schedules, trichotomy data, host real equality, ambient Real completeness, or a bridge-checking row to downstream Real or Completion consumers.
\end{proof}

\closureat{CauchyTailEnvelopeComparisonUp}{seedStr}

\begin{closurestatus}{\CauchyTailEnvelopeComparisonUp}
  \constructivestory{A $\CauchyTailEnvelopeComparisonUp$ packet is generated from two displayed DyadicCauchyTailEnvelope rows, their StreamName tail windows, a shared DyadicRatCore tolerance row, a common-window refinement, a CauchyTailDiameter comparison row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-tail-envelope-comparison-carrier}, \autoref{thm:cauchy-tail-envelope-comparison-namecert-obligations}, \autoref{thm:cauchy-tail-envelope-comparison-common-window}, and \autoref{thm:cauchy-tail-envelope-comparison-nonescape} seed the paired finite tail-envelope comparison route before either branch reaches Real or Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient stream equality, selected common limits, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, paired envelope exposure, common-window admission, tolerance alignment, tail-diameter comparison, transport, replay, provenance, and nonescape for BEDC.Derived.CauchyTailEnvelopeComparisonUp.}
\end{closurestatus}
