\begin{theorem}[MetricSpace LocatedReal distance source boundary]
\label{thm:metricspace-locatedreal-distance-source-boundary}
Let $L_x$ and $L_y$ be accepted $\LocatedRealUp$ packets whose
$\StreamNameUp$ schedules admit a common finite observation window. Suppose
their $\DyadicRatCore$ endpoint ledgers and radius ledgers are transported to
that window by the displayed $\hsame$ and $\Cont$ rows, and suppose a
contextual metric row
$\mathsf{MetricDistanceWitness}(p\cdot x,y\cdot q,(p\cdot d)\cdot q)$
is displayed for the two projected endpoints.

Then any $\MetricSpaceUp$ consumer reads the distance-source boundary exactly
through the finite rows named by
\autoref{thm:locatedreal-metric-consumer-handoff} together with the metric
visible-context rows: the $\RegSeqRatUp$ source windows, the $\DyadicRatCore$
endpoint and radius rows, the $\StreamNameUp$ schedule rows, the
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
provenance, and the $\hsame$ classifier on the central distance row $d$.

Conversely, any packet carrying precisely those rows repacks as the metric
distance-source row for the two located packets. No quotient real, host real
equality, trichotomy principle, open-cover compactness datum, or metric
completion object is part of this boundary.
\end{theorem}
\begin{proof}
Project $L_x$ and $L_y$ with
\autoref{thm:locatedreal-metric-consumer-handoff}. This leaves only the
displayed $\RegSeqRatUp$ source windows, the common $\StreamNameUp$ schedule,
the transported $\DyadicRatCore$ endpoint and radius ledgers, the enclosure
classifier rows, and the visible $\mathsf{BHist}$, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$ provenance.

Next apply \autoref{thm:metric-distance-witness-visible-context-iff} to the
contextual metric row. The visible prefix and suffix rows are peeled away,
leaving the central witness $\mathsf{MetricDistanceWitness}(x,y,d)$ over the
two projected located endpoints.

For uniqueness of the central distance read, apply
\autoref{thm:metric-distance-witness-visible-context-determinacy}. Any second
packet with the same displayed source windows, endpoint ledgers, schedule
rows, provenance rows, and contextual metric witness has a central distance
classifier $\hsame(d,e)$, so the metric consumer cannot distinguish a hidden
distance coordinate.

The converse direction repacks exactly the displayed rows: the located packets
come from the handoff surface, the contextual distance row supplies the metric
visible context, and the central $\hsame$ classifier is the only distance
classifier retained. Since each coordinate in this construction is one of the
listed finite rows, no excluded real-number, compactness, or completion
principle is introduced.
\end{proof}
