\begin{theorem}[Metric RealAlgOrder apartness distance scope]
\label{thm:metric-realalgorder-apartness-distance-scope}
For constant-rational $\RealUp$ endpoints carried by the $\RealAlgOrder$
constant boundary, the finite packet supplied by
\autoref{thm:realalgorder-constant-apartness-metric-handoff} and read by
\autoref{thm:apartnessreal-metric-handoff} and
\autoref{thm:apartnessreal-metric-consumer-separation-boundary} is exactly the
$\MetricSpaceUp$ positive-separation distance scope.

The scope consists of the two endpoint histories, the positive
$\DyadicRatCoreUp$ radius or apartness row, the $\hsame$ transports, the
$\Cont$ routes, the visible $\mathsf{Pkg}$ provenance, and the $\NameCert$
ledger tying the endpoints to their constant-rational source. Repacked as a
metric consumer row, these data form the positive-separation side of a
$\mathsf{MetricDistanceWitness}$ boundary and expose no trichotomy,
completion, quotient-real equality, open-cover compactness, or host real
equality.
\end{theorem}
\begin{proof}
Project the constant carrier, classifier, algebra, order, and apartness rows
from the $\RealAlgOrder$ constant boundary. By
\autoref{thm:realalgorder-constant-apartness-metric-handoff}, the consumer sees
only the two $\RealUp$ endpoint histories, their rational source witnesses, the
positive dyadic or apartness row, and the displayed $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$ provenance.

Apply the scoped certificate
\autoref{thm:realalgorder-constant-rational-scoped-certificate}. It keeps the
endpoint histories inside the constant-rational boundary and prevents any
additional real-order coordinate from being read by the downstream consumer.

Next apply \autoref{thm:apartnessreal-metric-handoff} and
\autoref{thm:apartnessreal-metric-consumer-separation-boundary}. These two
rows identify the same finite packet as apartness data consumable by metric
or order constructions, with the positive row and endpoint readbacks still
tied to the same $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ ledger.

Finally repack the resulting finite separation row as the positive-separation
side of the $\MetricSpaceUp$ distance consumer boundary. The metric
visible-context and boundary exactness rows are used only to keep the BEDC
ledger stable under contextual prefixes and empty-boundary readback; they do
not add a coordinate for trichotomy, completion, quotient-real equality,
open-cover compactness, or host real equality.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricRealalgorderApartnessDistanceScope}

\begin{theorem}[Metric RealAlgOrder apartness positive reflection]
\label{thm:metric-realalgorder-apartness-positive-reflection}
For constant-rational $\RealUp$ endpoints, any finite packet satisfying
\autoref{thm:metric-realalgorder-apartness-distance-scope} and the
$\ApartnessRealUp$ metric consumer boundary determines exactly the
positive-separation component of the $\MetricSpaceUp$ distance witness. Every
metric consumer may read the same positive dyadic or apartness row, endpoint
histories, $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
$\NameCert$ provenance supplied by the scoped packet. The reflection exports no
converse trichotomy, quotient-real equality, completion, or host equality.
\end{theorem}
\begin{proof}
Start with the constant-rational handoff
\autoref{thm:realalgorder-constant-apartness-metric-handoff}. Its packet gives
the endpoint histories, the rational source rows, and the positive dyadic or
apartness row that can be consumed without reading an additional real-order
coordinate.

Apply \autoref{thm:realalgorder-constant-rational-scoped-certificate}. The
certificate keeps those rows inside the constant-rational $\RealAlgOrder$
surface and records the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ provenance.

Use \autoref{thm:apartnessreal-metric-handoff} together with
\autoref{thm:apartnessreal-metric-consumer-separation-boundary}. These results
identify the same positive row as the separation data that an
$\ApartnessRealUp$ metric consumer may read.

Finally apply
\autoref{thm:metric-realalgorder-apartness-distance-scope} and project the
positive side of the resulting $\mathsf{MetricDistanceWitness}$ boundary. This
is only a repacking of the displayed finite rows, so the metric consumer gains
no coordinate for converse trichotomy, quotient-real equality, completion, or
host equality.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricRealalgorderApartnessPositiveReflection}

\begin{theorem}[Metric RealAlgOrder positive-radius distance boundary]
\label{thm:metric-realalgorder-positive-radius-distance-boundary}
For constant-rational $\RealUp$ endpoints carried by the scoped
$\RealAlgOrderUp$ boundary, the positive $\DyadicRatCoreUp$ radius or apartness
row, the two endpoint $\mathsf{BHist}$ rows, the displayed $\hsame$ transports,
the $\Cont$ routes, visible $\mathsf{Pkg}$ provenance, and the local
$\NameCert$ rows are exactly the positive-distance boundary of the
$\mathsf{MetricDistanceWitness}$ consumed by $\MetricSpaceUp$. Thus the concrete
dyadic-or-apartness row named by the $\RealAlgOrderUp$ packet is the
positive-distance component read by the metric witness, and every such metric
witness component recovers the same finite positive-radius row.

The boundary is local to the displayed BEDC rows. It contains no trichotomy,
quotient-real equality, completion, open-cover compactness, host metric-space
structure, or host real equality.
\end{theorem}
\begin{proof}
For the forward direction, start with the scoped constant-rational
$\RealAlgOrderUp$ packet. Apply
\autoref{thm:realalgorder-constant-apartness-metric-handoff} to expose exactly
the two endpoint histories, their rational source rows, the positive dyadic or
apartness row, the $\hsame$ transports, the $\Cont$ routes, visible
$\mathsf{Pkg}$ provenance, and the local $\NameCert$ ledger. Then apply
\autoref{thm:apartnessreal-metric-handoff} and
\autoref{thm:metric-realalgorder-apartness-positive-reflection}. These rows
identify the same finite packet as the positive component of the
$\mathsf{MetricDistanceWitness}$ boundary read by $\MetricSpaceUp$.

For the reverse direction, begin with a positive-distance boundary of the
$\mathsf{MetricDistanceWitness}$ whose endpoints are the same
constant-rational $\RealUp$ rows. Use
\autoref{thm:metricspace-realalgorder-positive-radius-budget-interface} to read
the positive-radius budget through the scoped $\RealAlgOrderUp$ certificate,
and then use
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}
to identify the public positive-distance component with the finite apartness
packet of the same endpoint histories, transports, routes, package provenance,
and name-certificate rows.

Both directions therefore name the same concrete positive row. The repacking
steps only move between the RealAlgOrder, ApartnessReal, and MetricSpace
consumer surfaces; they do not introduce a branch for trichotomy, a
quotient-real equality, a completion principle, an open-cover compactness
principle, a host metric-space structure, or a host real equality.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricRealalgorderPositiveRadiusDistanceBoundary}
\leanvariant{BEDC.Derived.MetricUp.MetricRealAlgOrder\_positive\_radius\_distance\_boundary}

\begin{theorem}[RealAlgOrder apartness metric symmetric separation]
\label{thm:realalgorder-apartness-metric-symmetric-separation}
For constant-rational $\RealUp$ endpoints carried by the $\RealAlgOrder$
constant boundary, the positive-separation packet identified by
\autoref{thm:metric-realalgorder-apartness-positive-reflection} remains a valid
positive-separation component of the $\MetricSpaceUp$ distance witness after
the two endpoint histories are swapped. The swapped orientation keeps the same
positive $\DyadicRatCoreUp$ radius or apartness row, the same finite separation
ledger, and the same displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ provenance; only the left and right endpoint histories are read in
the reverse order.

This is a metric-facing consequence of apartness symmetry. It gives the
symmetric endpoint orientation required by a distance witness, but it does not
add trichotomy, quotient-real equality, completion, or host real equality.
\end{theorem}
\begin{proof}
Start with the constant-rational handoff
\autoref{thm:realalgorder-constant-apartness-metric-handoff}. It supplies the
two endpoint histories, rational source rows, positive dyadic or apartness row,
and visible $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.

Apply the scoped certificate
\autoref{thm:realalgorder-constant-rational-scoped-certificate}. The certificate
keeps both endpoint histories inside the same constant-rational
$\RealAlgOrder$ boundary and does not introduce any additional real-order
coordinate.

Use \autoref{thm:apartnessreal-symmetry-stability} to exchange the two
endpoint histories and endpoint readbacks. The apartness row, positive radius
or separation ledger, and all displayed transport and provenance rows are
preserved componentwise.

Finally apply
\autoref{thm:metric-realalgorder-apartness-positive-reflection} to the swapped
packet. Since the positive-separation component is the same finite row read in
the opposite endpoint order, it is again a valid positive component of the
$\MetricSpaceUp$ distance witness, with no added equality, completion, or
trichotomy principle.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.RealAlgOrderApartnessMetricSymmetricSeparation}

\begin{theorem}[Metric RealAlgOrder apartness triangle budget]
\label{thm:metric-realalgorder-apartness-triangle-budget}
For constant-rational $\RealUp$ endpoints $x,y,z$ carried by the
$\RealAlgOrder$ constant boundary, two adjacent finite apartness packets for
$(x,y)$ and $(y,z)$ supply the exact visible rows required by the
$\MetricSpaceUp$ triangle-budget consumer for the outer pair $(x,z)$ after
endpoint orientation is normalized. The consumer may read only the three
endpoint histories, the two positive $\DyadicRatCoreUp$ radius or apartness
rows, the finite adjacent separation ledgers, the induced outer-pair
$\mathsf{BHist}$ row, the displayed $\hsame$ transports, the $\Cont$ routes,
the visible $\mathsf{Pkg}$ provenance, and the local $\NameCert$ rows attached
to the constant-rational sources.

The statement is a local RealAlgOrder-to-MetricSpace budget law. It exports no
trichotomy, quotient-real equality, completion, open-cover compactness, or
host metric-space structure.
\end{theorem}
\begin{proof}
Begin with the two adjacent apartness packets. Apply
\autoref{thm:metric-realalgorder-apartness-positive-reflection} to each packet;
this exposes exactly the positive-separation rows, endpoint histories,
$\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
$\NameCert$ rows already present in the constant-rational boundary.

If one adjacent packet is presented in the reverse endpoint order, use
\autoref{thm:realalgorder-apartness-metric-symmetric-separation} to swap only
the endpoint histories. The positive row and finite ledger are unchanged, so
the two adjacent packets now share the middle endpoint history $y$ in the
orientation read by the triangle consumer.

With the adjacent rows normalized, invoke the $\MetricSpaceUp$ visible-context
triangle boundary and the public law package. These rows concatenate the two
finite positive-separation ledgers into the outer-pair triangle budget while
preserving the displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$,
and $\NameCert$ provenance.

No excluded principle is used in the repacking step. Trichotomy, quotient-real
equality, completion, open-cover compactness, and a host metric-space structure
are not coordinates of the adjacent RealAlgOrder packets or of the visible
triangle-budget consumer surface.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricRealalgorderApartness\_triangle\_budget}

\begin{theorem}[RealAlgOrder apartness metric NameCert route]
\label{thm:realalgorder-apartness-metric-namecert-route}
For constant-rational $\RealUp$ endpoints carried by the scoped
$\RealAlgOrderUp$ boundary, the carrier and classifier rows of
\autoref{thm:realalgorder-constant-rational-scoped-certificate}, the finite
apartness-to-metric handoff of
\autoref{thm:realalgorder-constant-apartness-metric-handoff}, the
$\ApartnessRealUp$ metric handoff of \autoref{thm:apartnessreal-metric-handoff},
the positive-separation reflection of
\autoref{thm:metric-realalgorder-apartness-positive-reflection}, the symmetric
endpoint separation of
\autoref{thm:realalgorder-apartness-metric-symmetric-separation}, and the
triangle-budget rows of \autoref{thm:metric-realalgorder-apartness-triangle-budget}
assemble into the exact finite $\NameCert$ route consumable by
$\MetricSpaceUp$ and by the $\SOneUp$ boundary reader.

The route consists only of endpoint $\mathsf{BHist}$ rows, the positive
$\DyadicRatCoreUp$ radius or apartness rows, the displayed $\hsame$ transports,
the $\Cont$ routes, the $\mathsf{Pkg}$ provenance, and the local $\NameCert$
rows attached to the constant-rational sources and metric consumers. It exports
no trichotomy, quotient-real equality, completion, open-cover compactness, or
host equality.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealalgorderApartnessMetricNameCertRoute}
\begin{proof}
First read the two endpoint rows through
\autoref{thm:realalgorder-constant-rational-scoped-certificate}. This fixes the
scoped $\RealAlgOrderUp$ carrier and classifier surface and keeps the endpoint
histories tied to their constant-rational source rows.

Next apply \autoref{thm:realalgorder-constant-apartness-metric-handoff} and
\autoref{thm:apartnessreal-metric-handoff}. These two handoffs present the same
finite apartness row as metric-facing positive-separation data, with the
visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
provenance unchanged.

Now use \autoref{thm:metric-realalgorder-apartness-positive-reflection} to
package the positive row as the positive component of the $\MetricSpaceUp$
distance witness, and use
\autoref{thm:realalgorder-apartness-metric-symmetric-separation} when the
consumer requests the opposite endpoint orientation.

Finally apply \autoref{thm:metric-realalgorder-apartness-triangle-budget}. The
triangle route concatenates only the displayed adjacent separation ledgers and
therefore gives exactly the finite $\NameCert$ route needed by metric and
circle-boundary consumers, without adding any excluded host-order, quotient,
completion, compactness, or equality principle.
\end{proof}
