\begin{definition}[MetricSpace real-distance carrier]
\label{def:metricspace-real-distance-carrier}
The $\MetricSpaceUp$ real-distance carrier for the open Real Algebra and
Geometry phase is the finite unary endpoint packet
$$
(x,y,d,r;\ w,b,c,p,a)
$$
where $x$ and $y$ are unary $\mathsf{BHist}$ endpoint histories, $w$ is the
displayed row $\mathsf{MetricDistanceWitness}(x,y,d)$, $b$ is the closed
ball-budget row $\mathsf{MetricBallBudget}_d(x,y;r)$, $c$ is the classifier
row $\hsame$ on endpoint and result histories, $p$ is the visible $\Cont$
provenance for the distance witness, and $a$ is the $\RealAlgOrder$ budget
packet consisting of the constant-rational endpoint rows, positive
$\DyadicRatCoreUp$ or apartness row, ordered-real comparison, addition,
transitivity, and addition-monotonicity rows used by the budget predicate.

The carrier exposes exactly these rows. It does not contain an ambient host
metric space, a quotient-real equality, a completeness principle, an
open-cover compactness principle, or a topology generator separate from the
displayed distance packet.
\end{definition}
\leandef{BEDC.Derived.MetricUp.MetricspaceRealDistanceCarrier}

\begin{theorem}[MetricSpace RealAlgOrder positive-radius budget interface]
\label{thm:metricspace-realalgorder-positive-radius-budget-interface}
For constant-rational $\RealUp$ endpoints in the carrier of
\autoref{def:metricspace-real-distance-carrier}, the $a$-coordinate supplies
exactly the ordered-real fields required by
\autoref{def:metric-ball-budget-predicate} and consumed by
\autoref{thm:metric-ball-budget-composition}: ordered-real comparison,
addition, transitivity, and two-sided addition-monotonicity. The interface is
read through the scoped $\RealAlgOrderUp$ certificate and the apartness distance
scope of \autoref{thm:metric-realalgorder-apartness-distance-scope}, so the
positive-radius row is the same finite order-or-apartness row exposed to the
metric budget consumer.

This interface exports no trichotomy branch, quotient-real equality,
completeness principle, open-cover compactness, or host metric-space row.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealalgorderPositiveRadiusBudgetInterface}
\begin{proof}
Project the $a$-coordinate from
\autoref{def:metricspace-real-distance-carrier}. By construction this
coordinate is the $\RealAlgOrder$ budget packet attached to the same endpoint
histories, distance witness, classifier, continuation, and provenance rows as
the metric carrier.

Apply \autoref{thm:real-alg-order-namecert-obligations}. Its order stability
and ledger-exactness rows identify the comparison, addition, transitivity, and
addition-monotonicity data as finite displayed order rows, while
\autoref{thm:real-alg-order-apartness-nonescape} prevents any trichotomy,
quotient-real equality, host real carrier, or completeness coordinate from
being read through the order or apartness side.

Next use \autoref{thm:metric-realalgorder-apartness-distance-scope} together
with
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}.
These theorems identify the metric-facing positive row with the same endpoint
$\mathsf{BHist}$ histories, positive $\DyadicRatCoreUp$ radius or apartness
row, $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
$\NameCert$ ledger supplied by the scoped $\RealAlgOrderUp$ packet.

Finally compare this inventory with
\autoref{def:metric-ball-budget-predicate}. The predicate asks only for
ordered-real comparison, addition, budget transitivity, and two-sided
budget-addition monotonicity, and
\autoref{thm:metric-ball-budget-composition} consumes only those displayed
fields. Therefore the $a$-coordinate is precisely the positive-radius budget
interface used by the composition theorem, with none of the excluded host
principles added.
\end{proof}

\begin{theorem}[MetricSpace public law package]
\label{thm:metricspace-public-law-package}
The real-distance carrier of
\autoref{def:metricspace-real-distance-carrier} supports the public
$\MetricSpaceUp$ distance laws needed by the open phase:
\begin{enumerate}
  \item symmetry, by transporting the endpoint order through
  $\mathsf{MetricDistanceWitness}$ symmetry and the RealAlgOrder apartness
  symmetric-separation row;
  \item identity boundary, by the empty-distance row and the empty-boundary
  visible-context rows;
  \item triangle-budget composition, by the visible-context triangle boundary
  and the $\mathsf{MetricBallBudget}$ composition row;
  \item carrier transport, by $\hsame$ transport of endpoints and result
  histories together with the displayed $\Cont$ provenance.
\end{enumerate}

These laws are public laws of the finite BEDC packet only. They do not assert
an arbitrary host metric, completeness, compactness, or a hidden equality on
real distances.
\end{theorem}
\begin{proof}
For symmetry, read the distance row through
\autoref{thm:metric-distance-witness-symmetric-classifier}. The positive
real-distance side is kept in the same packet by
\autoref{thm:realalgorder-apartness-metric-symmetric-separation}, so swapping
the endpoints changes only the orientation of the unary endpoint histories.

For the identity boundary, apply
\autoref{thm:metric-distance-witness-empty-distance-iff}. The visible-context
empty-boundary rows then show that a zero public distance read is exactly the
empty endpoint boundary up to $\hsame$, with no quotient-real equality added.

For triangle-budget composition, use
\autoref{thm:metricspace-visible-context-triangle-boundary} to form the
composite witness over the same endpoint and continuation rows. Then apply
\autoref{thm:metric-ball-budget-composition} to compose the two displayed
budget rows.

For carrier transport, use the endpoint and result $\hsame$ rows already
contained in \autoref{def:metricspace-real-distance-carrier}. The visible
$\Cont$ provenance identifies the transported witness with the same public
distance packet, so every exported law remains inside the carrier.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealDistanceCarrier\_public\_law\_package}

\begin{theorem}[MetricSpace open-phase consumer interface]
\label{thm:metricspace-open-phase-consumer-interface}
Every $\SOneUp$ consumer and every later L10 consumer in the open Real
Algebra and Geometry phase reads $\MetricSpaceUp$ real-distance data only
through the carrier of \autoref{def:metricspace-real-distance-carrier} and the
law package of \autoref{thm:metricspace-public-law-package}. The consumer
surface is the RealAlgOrder apartness distance scope together with the existing
visible-context consumer surface; it exposes no additional host metric-space
coordinate, no completion row, and no open-cover compactness row.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceOpenPhaseConsumerInterface}
\begin{proof}
Start with
\autoref{thm:metric-realalgorder-apartness-distance-scope}. It identifies the
constant-rational endpoint histories, positive apartness or dyadic radius, and
visible $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance available
to a metric-facing real-distance consumer.

Next apply
\autoref{thm:metricspace-visible-context-distance-consumer-surface}. That
consumer theorem restricts $\SOneUp$ and the named downstream metric consumers
to the visible-context distance witness, ball-budget, classifier, and finite
provenance rows.

The L10 consumers in the open phase can only compose with the same
RealAlgOrder apartness scope and the same visible-context public surface.
Therefore their readable interface is exactly
\autoref{def:metricspace-real-distance-carrier} equipped with
\autoref{thm:metricspace-public-law-package}, and no host metric,
completion, or open-cover compactness coordinate is exported.
\end{proof}

\begin{theorem}[MetricSpace RealAlgOrder positive-distance public correspondence]
\label{thm:metricspace-realalgorder-positive-distance-public-correspondence}
For constant-rational $\RealUp$ endpoints, the positive component of the
$\MetricSpaceUp$ real-distance carrier of
\autoref{def:metricspace-real-distance-carrier} is equivalent to the finite
apartness packet isolated by
\autoref{thm:metric-realalgorder-apartness-distance-scope} and
\autoref{thm:metric-realalgorder-apartness-positive-reflection}. Concretely,
to read a positive public distance row is to read the two endpoint
$\mathsf{BHist}$ histories, the positive $\DyadicRatCoreUp$ radius or
apartness row, the displayed $\hsame$ transports, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and $\NameCert$ ledger supplied by the
$\RealAlgOrder$ constant-rational boundary; conversely, those same rows repack
as the positive component of the carrier.

Endpoint reversal is supplied by
\autoref{thm:realalgorder-apartness-metric-symmetric-separation}. The
correspondence introduces no trichotomy, completion, quotient-real equality,
open-cover compactness, or host equality.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealalgorderPositiveDistancePublicCorrespondence}
\begin{proof}
Project the carrier of \autoref{def:metricspace-real-distance-carrier}. Its
positive side is not a separate host metric object; it is the displayed
$\RealAlgOrder$ budget packet attached to the distance witness, classifier,
continuation, package, and name-certificate rows.

For the forward direction, read that budget packet through
\autoref{thm:metric-realalgorder-apartness-distance-scope}. Then apply
\autoref{thm:metric-realalgorder-apartness-positive-reflection} to identify
the positive public distance row with the finite apartness data available to a
metric-facing consumer.

For the reverse direction, start with the finite apartness packet named by the
same two theorems. The rows already match the carrier fields: endpoint
histories, positive dyadic or apartness data, $\hsame$ transports, $\Cont$
routes, $\mathsf{Pkg}$ provenance, and the $\NameCert$ ledger. Repacking these
rows with the carrier's displayed distance witness gives the positive
component of the public real-distance carrier.

Finally use
\autoref{thm:realalgorder-apartness-metric-symmetric-separation} for endpoint
reversal. Symmetry changes only the orientation of the two endpoint histories,
so the same finite packet remains the public positive-distance witness and no
trichotomy, completion, quotient-real equality, open-cover compactness, or host
equality is added.
\end{proof}

\begin{theorem}[MetricSpace apartness positive-distance triangle boundary]
\label{thm:metricspace-apartness-positive-distance-triangle-boundary}
Let $x$, $y$, and $z$ be constant-rational $\RealUp$ endpoints read through
the $\MetricUp$ real-distance public surface. Suppose the adjacent positive
distance reads for $(x,y)$ and $(y,z)$ are represented by the finite
$\RealAlgOrder$ apartness packets isolated in
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}.
Then the triangle-boundary consumer read for the outer pair $(x,z)$ factors
through exactly those endpoint $\mathsf{BHist}$ histories, the positive
$\DyadicRatCoreUp$ or apartness rows, the displayed $\hsame$ transports,
$\Cont$ routes, $\mathsf{Pkg}$ provenance, local $\NameCert$ rows, and the
metric triangle ledger of \autoref{thm:metricspace-public-law-package}.

The resulting consumer row exports only this visible finite boundary. It does
not export trichotomy, open-cover compactness, completed-real equality, or a
host metric-space structure.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceApartnessPositiveDistanceTriangleBoundary}
\begin{proof}
Apply
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}
to the adjacent packets $(x,y)$ and $(y,z)$. Each read gives the same kind of
finite public data: endpoint histories, positive dyadic or apartness rows,
displayed $\hsame$ transports, continuation routes, package provenance, and
local name-certificate rows.

Use
\autoref{thm:realalgorder-apartness-metric-symmetric-separation} whenever an
adjacent endpoint orientation must be read from the opposite side. This
changes only the order in which the two endpoint histories are presented; it
does not add trichotomy, completed-real equality, compactness, or host metric
structure.

Finally apply \autoref{thm:metricspace-public-law-package}. Its triangle row
is already a visible-context ledger over the public distance witness, so the
two adjacent positive packets repack as the outer triangle-boundary consumer
read for $(x,z)$. The repacking uses only the displayed $\mathsf{BHist}$,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, $\NameCert$, and metric-law rows listed in
the statement.
\end{proof}

\begin{theorem}[MetricSpace SOne RealAlgOrder consumer factorization]
\label{thm:metricspace-s1-realalgorder-consumer-factorization}
Every $\SOneUp$ metric consumer read whose two real coordinates are read
through the constant-rational $\RealAlgOrderUp$ boundary factors through the
finite rows of \autoref{def:metricspace-real-distance-carrier}. The only
readable rows are the endpoint $\mathsf{BHist}$ rows of the two coordinates,
the displayed $\mathsf{MetricDistanceWitness}$ row, the positive
$\DyadicRatCoreUp$ or apartness rows supplied by the $\RealAlgOrderUp$
boundary, the $\hsame$ transport rows, $\Cont$ routes, $\mathsf{Pkg}$
provenance, local $\NameCert$ rows, and the triangle ledger of
\autoref{thm:metricspace-public-law-package}.

Thus the $\MetricSpaceUp$ consumer surface seen from $\SOneUp$ and
$\RealAlgOrderUp$ is a finite BEDC packet. It does not include trichotomy,
completed-real equality, open-cover compactness, or a host metric-space
structure.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceSoneRealalgorderConsumerFactorization}
\leanvariant{BEDC.Derived.MetricUp.MetricspaceS1RealalgorderConsumerFactorization}
\begin{proof}
Project the admitted circle point through
\autoref{thm:sone-real-metric-bridge-boundary}. The public bridge exposes only
the two $\RealUp$ component rows, their product ledger, the unit-equation row,
and the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows.

Apply
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}
to each constant-rational component read. This replaces every positive
metric-distance demand by the visible $\RealAlgOrderUp$ apartness packet, with
endpoint histories, positive dyadic or apartness data, and the same transport
and package rows as in the carrier.

Next use
\autoref{thm:metricspace-apartness-positive-distance-triangle-boundary}. Its
triangle-boundary row is exactly the finite metric-law ledger over the
positive packets, so the $\SOneUp$ metric consumer has no additional distance
coordinate beyond the carrier and public-law rows.

Finally compare with
\autoref{thm:sone-regseqrat-metric-observation-boundary}. The observation
boundary already prevents quotient-circle, angle, compactness, connectedness,
and metric-completeness rows from entering the read. Since the
$\RealAlgOrderUp$ correspondence contributes no trichotomy or completed-real
equality and the $\MetricSpaceUp$ law package contributes no host metric
space, the resulting consumer factors through exactly the finite packet listed
in the statement.
\end{proof}

\begin{theorem}[MetricSpace real-distance scoped certificate]
\label{thm:metricspace-real-distance-scoped-certificate}
The finite $\MetricSpaceUp$ scoped certificate for the open real-algebra and
geometry phase consists exactly of the real-distance carrier of
\autoref{def:metricspace-real-distance-carrier}, the public law package of
\autoref{thm:metricspace-public-law-package}, the open-phase consumer
interface of \autoref{thm:metricspace-open-phase-consumer-interface}, the
$\RealAlgOrder$ positive-distance correspondence of
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence},
and the apartness triangle boundary of
\autoref{thm:metricspace-apartness-positive-distance-triangle-boundary}.

Its rows are only the displayed $\mathsf{BHist}$ endpoint histories, $\hsame$
transport rows, $\Cont$ routes, $\mathsf{Pkg}$ provenance, local $\NameCert$
registrations, the public metric-law rows, and the displayed $\RealAlgOrder$
positive-distance budget rows. The certificate exports no host metric-space
primitive, quotient-real equality, completion, open-cover compactness, or
trichotomy.
\end{theorem}
\begin{proof}
Begin with the carrier of
\autoref{def:metricspace-real-distance-carrier}. It supplies the endpoint
histories, the displayed distance witness, the transport and continuation
routes, package provenance, and the local name-certificate row.

Attach the public law package of
\autoref{thm:metricspace-public-law-package} and read it through
\autoref{thm:metricspace-open-phase-consumer-interface}. This gives the open
phase only the finite law rows for symmetry, separation, and triangle
composition over the same carrier fields.

Next insert the $\RealAlgOrder$ side by
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}.
That theorem identifies the positive-distance consumer row with the displayed
apartness budget packet, so no second positivity primitive or completed-real
coordinate is introduced.

Finally compose with
\autoref{thm:metricspace-apartness-positive-distance-triangle-boundary}. The
triangle-boundary read uses the same endpoint histories, positive-distance
budget rows, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ data already
listed above. Since none of the cited components contains a host metric,
quotient-real equality, completion, open-cover compactness, or trichotomy row,
the assembled scoped certificate has no coordinate from which such data could
be exported.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealDistanceScopedCertificate}

\begin{theorem}[MetricSpace RealAlgOrder triangle consumer exhaustion]
\label{thm:metricspace-realalgorder-triangle-consumer-exhaustion}
Every $\MetricSpaceUp$ triangle-consumer read whose endpoints are constant
rational $\RealAlgOrderUp$ endpoints and whose distance data are read through
the real-distance carrier of
\autoref{def:metricspace-real-distance-carrier} is exhausted by the finite
rows already displayed in that carrier, the public law package of
\autoref{thm:metricspace-public-law-package}, the positive-distance
correspondence of
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence},
and the apartness triangle boundary of
\autoref{thm:metricspace-apartness-positive-distance-triangle-boundary}.

Equivalently, a triangle consumer over endpoints $(x,y,z)$ can read only the
three endpoint $\mathsf{BHist}$ histories, the two adjacent positive
$\RealAlgOrderUp$ packets, the displayed $\hsame$ transports, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, local $\NameCert$ rows, and the finite metric-law
triangle ledger. It has no coordinate for trichotomy, quotient-real equality,
completion, open-cover compactness, or an ambient host metric-space
structure.
\end{theorem}
\begin{proof}
Project the adjacent positive-distance reads for $(x,y)$ and $(y,z)$ through
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}.
The projection exposes only endpoint histories, positive dyadic or apartness
rows, transport rows, continuation routes, package provenance, and local
name-certificate data.

Orient the two adjacent endpoint packets by
\autoref{thm:realalgorder-apartness-metric-symmetric-separation}. Endpoint
reversal changes only the order of the displayed unary histories, so it cannot
introduce trichotomy, quotient-real equality, completion, compactness, or a
host metric-space coordinate.

Compose the oriented packets through
\autoref{thm:metricspace-apartness-positive-distance-triangle-boundary}. That
boundary theorem is the public triangle read of
\autoref{thm:metricspace-public-law-package}, hence the outer consumer is
formed from the same two adjacent positive packets and the same finite
triangle ledger.

Finally compare the assembled read with
\autoref{thm:metricspace-real-distance-scoped-certificate}. The scoped
certificate lists every exported coordinate of the real-distance public
surface. Since the triangle construction above uses only those rows, no
additional coordinate remains for a mature metric-space primitive or completed
real equality.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealalgorderTriangleConsumerExhaustion}

\begin{theorem}[MetricSpace RealAlgOrder SOne distance route exhaustion]
\label{thm:metricspace-realalgorder-sone-distance-route-exhaustion}
For any accepted $\SOneUp$ metric consumer whose coordinates are read through
constant-rational $\RealAlgOrderUp$ endpoints and whose distance request uses
the carrier of \autoref{def:metricspace-real-distance-carrier}, the public
read is exhausted by the finite route consisting of the two $\SOneUp$
coordinate histories, the $\RealAlgOrderUp$ apartness or positive dyadic rows,
the $\mathsf{MetricDistanceWitness}$ rows, endpoint and result $\hsame$
transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, local $\NameCert$ rows,
and the $\MetricSpaceUp$ triangle ledger.

This route exports no angle parametrization, quotient-circle equality,
completed-real equality, open-cover compactness, trichotomy, or host
metric-space primitive.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealalgorderSoneDistanceRouteExhaustion}
\begin{proof}
First apply
\autoref{thm:metricspace-s1-realalgorder-consumer-factorization}. It reduces
the accepted $\SOneUp$ metric read to the real-distance carrier of
\autoref{def:metricspace-real-distance-carrier}, so the only available
coordinate histories are the two visible $\SOneUp$ histories and their
constant-rational endpoint rows.

Next use
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}
on the distance request. The positive component of the carrier is exactly the
visible $\RealAlgOrderUp$ apartness or positive dyadic packet, together with
the same $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows.

For triangle-facing consumers, compose with
\autoref{thm:metricspace-apartness-positive-distance-triangle-boundary} and
\autoref{thm:metricspace-realalgorder-triangle-consumer-exhaustion}. These
results identify the remaining public metric-law data with the finite
$\MetricSpaceUp$ triangle ledger over the displayed distance witnesses and
endpoint transports.

Finally compare with the $\SOneUp$ observation boundary used in
\autoref{thm:metricspace-s1-realalgorder-consumer-factorization}. That
boundary excludes angle parametrization, quotient-circle equality, completed
real equality, open-cover compactness, trichotomy, and host metric-space
primitives from the consumer surface, so the finite route listed in the
statement is exhaustive.
\end{proof}

\begin{theorem}[Metric RealAlgOrder SOne equation-distance factorization]
\label{thm:metric-realalgorder-sone-equation-distance-factorization}
Every accepted $\SOneUp$ equation-distance consumer whose component reads pass
through $\RealAlgOrderUp$ apartness or positive dyadic rows and whose metric
request uses \autoref{def:metricspace-real-distance-carrier} factors through
exactly the finite rows listed in
\autoref{thm:metricspace-realalgorder-sone-distance-route-exhaustion}. The same
route supplies the equation-consumer boundary and excludes angle
parametrization, quotient-circle equality, completed-real equality, trichotomy,
open-cover compactness, and host metric primitives.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricRealalgorderSoneEquationDistanceFactorization}
\begin{proof}
First apply \autoref{thm:metricspace-s1-realalgorder-consumer-factorization}.
It places the accepted $\SOneUp$ equation-distance read on the real-distance
carrier, so the visible component histories are the two displayed circle
coordinates and their constant-rational $\RealAlgOrderUp$ endpoint rows.

Next use
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}.
The positive-distance component is read only through apartness or positive
dyadic rows, the distance witness, endpoint transports, continuation routes,
package provenance, and local naming certificates.

For metric-law consumers, compose with
\autoref{thm:metricspace-realalgorder-triangle-consumer-exhaustion}. This keeps
the triangle-facing read on the same distance witnesses and the same finite
$\MetricSpaceUp$ ledger.

Finally compare the resulting packet with
\autoref{thm:metricspace-realalgorder-sone-distance-route-exhaustion}. Its
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows already
list every coordinate available to the equation consumer, leaving no coordinate
for angle parameters, quotient or completed equality, trichotomy, open-cover
compactness, or host metric primitives.
\end{proof}

\begin{theorem}[Metric RealAlgOrder SOne equation-distance symmetry]
\label{thm:metric-realalgorder-sone-equation-distance-symmetry}
Let an accepted $\SOneUp$ equation-distance consumer factor through
constant-rational $\RealAlgOrderUp$ coordinate endpoints and the
$\MetricSpaceUp$ real-distance carrier of
\autoref{def:metricspace-real-distance-carrier}. Then the coordinate-swapped
equation-distance read factors through the same finite route after
coordinate-pair determinacy, $\RealAlgOrderUp$ apartness metric symmetric
separation, and $\MetricSpaceUp$ route exhaustion. The swapped read introduces
no angle parametrization, quotient-circle equality, completed-real equality,
trichotomy, open-cover compactness, or host metric primitive.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricRealalgorderSoneEquationDistanceSymmetry}
\begin{proof}
Start with the original accepted equation-distance consumer and apply
\autoref{thm:metric-realalgorder-sone-equation-distance-factorization}. The
factorization exposes only the two $\SOneUp$ coordinate histories, their
constant-rational $\RealAlgOrderUp$ endpoint rows, the real-distance witness,
endpoint transports, continuation routes, package provenance, and local
name-certificate rows.

For the coordinate swap, use
\autoref{thm:sone-history-carrier-coordinate-pair-deterministic}. The
determinacy statement identifies the swapped pair as the same two circle
coordinate histories with their order reversed, so no angle parameter or
quotient-circle equality is added to the read.

Apply
\autoref{thm:realalgorder-apartness-metric-symmetric-separation} to the
endpoint rows. This reverses the apartness or positive dyadic separation
packet inside $\RealAlgOrderUp$ while preserving the same endpoint histories,
the same $\hsame$ transports, and the same finite package and certificate
data.

Finally compare the swapped packet with
\autoref{thm:metricspace-realalgorder-sone-distance-route-exhaustion}. That
exhaustion theorem already lists the complete $\MetricSpaceUp$ route available
to the equation-distance carrier. Hence the coordinate-swapped read stays on
the same finite route and leaves no coordinate for completed-real equality,
trichotomy, open-cover compactness, or host metric primitives.
\end{proof}

\begin{theorem}[MetricSpace RealAlgOrder SOne positive-boundary equivalence]
\label{thm:metricspace-realalgorder-sone-positive-boundary-equivalence}
Let constant-rational $\RealUp$ endpoints be accepted by the $\SOneUp$
component-and-equation consumer through the $\MetricSpaceUp$ real-distance
carrier of \autoref{def:metricspace-real-distance-carrier}. Then the
$\RealAlgOrderUp$ positive-boundary row, the $\MetricSpaceUp$
positive-distance row, and the $\SOneUp$ equation-separation row are
equivalent finite BEDC readings of the same packet. The shared packet consists
exactly of endpoint $\BHist$ rows, a positive $\DyadicRatCoreUp$ or apartness
row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, local
$\NameCert$ rows, the metric distance witness, and the $\SOneUp$ component
and unit-equation rows. It does not include trichotomy, quotient-real
equality, angle quotient, completed-real equality, open-cover compactness,
connectedness, or host metric primitives.
\end{theorem}
\leanchecked{BEDC.Derived.MetricUp.MetricspaceRealalgorderSonePositiveBoundaryEquivalence}
\begin{proof}
First apply
\autoref{thm:metricspace-realalgorder-positive-distance-public-correspondence}.
This identifies the $\RealAlgOrderUp$ positive-boundary read with the
$\MetricSpaceUp$ positive-distance row through the visible endpoint histories,
apartness or positive dyadic data, transport rows, continuation routes,
package provenance, local naming certificates, and the metric distance
witness.

Next apply
\autoref{thm:metricspace-s1-realalgorder-consumer-factorization}. The
$\SOneUp$ component-and-equation consumer can only enter through that
real-distance public interface, so its component rows and unit-equation rows
read the same endpoints and distance witness rather than a separate angle or
quotient-circle carrier.

The route is exhaustive by
\autoref{thm:metricspace-realalgorder-sone-distance-route-exhaustion}. Hence
any consumer claiming one of the three boundary views must use the displayed
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, distance, component, and
unit-equation rows.

Finally compare with
\autoref{thm:realalgorder-metric-sone-positive-boundary-correspondence} and
\autoref{thm:sone-realalgorder-equation-consumer-boundary}. These two
boundary theorems give the reverse readings from the
$\RealAlgOrderUp$--$\MetricSpaceUp$ side and from the $\SOneUp$ equation
consumer side. Together they show that the positive-boundary,
positive-distance, and equation-separation rows are three readings of one
finite certificate packet, with no remaining coordinate for trichotomy,
quotient-real equality, angle quotient, completed-real equality,
open-cover compactness, connectedness, or host metric primitives.
\end{proof}
