\begin{theorem}[Metric seed closure surface]
\label{thm:metric-seed-closure-surface}
The $\MetricUp$ seed closure surface is the finite public package assembled from the metric carrier of \autoref{def:metric-carrier}, the boundary exactness rows of \autoref{thm:metric-distance-witness-empty-source-e1-distance-target-exactness} and \autoref{thm:metric-distance-witness-empty-target-e1-distance-source-exactness}, the real-distance public interface of \autoref{def:metricspace-real-distance-carrier}, the triangle continuation rows of \autoref{thm:metric-distance-witness-triangle-append-closed}, and the transport surface of \autoref{thm:metric-distance-witness-hsame-fields-transport}. A seed consumer of $\MetricUp$ can read only these carrier, boundary, distance, triangle, and transport rows together with their $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ provenance.
\end{theorem}
\begin{proof}
Project the metric carrier first. The carrier fixes the endpoint histories, distance witness rows, classifier, continuation, provenance, and local naming coordinates available to any public metric read.

Boundary exactness then identifies the endpoint and empty-boundary cases already named by the carrier. The real-distance public interface supplies the displayed ordered-real budget rows used by downstream consumers.

The triangle surface is the visible continuation package: triangle append closure and the associated middle-continuation rows keep composite distance reads inside the same finite witness family. Transport then moves endpoints, witnesses, budgets, and provenance componentwise through the displayed $\hsame$ and $\Cont$ rows.

No additional host metric, topology generator, compactness principle, completeness row, or quotient real equality appears in these referenced surfaces. Hence the named carrier, boundary, distance, triangle, and transport files form the seed closure surface for $\MetricUp$.
\end{proof}
\leanchecked{BEDC.Derived.MetricUp.MetricSeedClosureSurface\_public\_package}
