\begin{theorem}[Sheaf carrier support obligation]
\label{thm:sheaf-carrier-support-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$. Then the carrier support exposed by $\mathcal{S}$ is only the indexed section presheaf carrier over the $\TopologyUp$ open-index surface, together with the sheaf locality and gluing fields. Concretely, every carrier row is one of the section carriers $\mathsf{Sec}(i)$, section classifiers $\sim_i$, equivalence fields, restriction maps $\rho_{i,j}$, identity and composition laws, indexed open-cover data, compatible local-family predicates, locality implications, or gluing witnesses described in \autoref{def:sheaf-indexed-section-presheaf-carrier} and \autoref{def:sheaf-indexed-cover-compatibility-locality}.
\end{theorem}
\begin{proof}
Project the indexed section presheaf component of $\mathcal{S}$. Its displayed rows are precisely the open-indexed section carriers, classifiers, equivalence witnesses, restriction maps, and restriction identity and composition laws of \autoref{def:sheaf-indexed-section-presheaf-carrier}.

Project the sheaf component of $\mathcal{S}$. By \autoref{def:sheaf-indexed-cover-compatibility-locality}, this contributes only indexed open covers, compatible local families, the locality field, and the gluing field. No additional carrier row is introduced beyond those two displayed interfaces, so the asserted carrier support is exhausted by their projections.
\end{proof}

\begin{theorem}[Sheaf classifier transport obligation]
\label{thm:sheaf-classifier-transport-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$, and suppose its indexed section presheaf carrier carries a stable sheaf restriction row in the sense of \autoref{def:sheaf-stable-restriction-row}. Then section classifiers transport through every restriction. Moreover, for every indexed open cover $\mathcal{U}=(A,\iota,h,\gamma)$ of $i$ and every pair $g,h':\mathsf{Sec}(i)$,
$$
\bigl(\forall a:A,\ \rho_{i,\iota(a)}(g)\sim_{\iota(a)}\rho_{i,\iota(a)}(h')\bigr)
\Longrightarrow
g\sim_i h'.
$$
Thus restriction stability gives classifier transport along the presheaf maps, and sheaf locality turns coverwise classifier equality back into classifier equality on the covered open.
\end{theorem}
\begin{proof}
For a single inclusion $j\le_{\mathcal{T}} i$, the transport claim is exactly the stable restriction row of \autoref{def:sheaf-stable-restriction-row}: a classifier equality $s\sim_i t$ restricts to $\rho_{i,j}(s)\sim_j\rho_{i,j}(t)$. The source and target classifiers are those supplied by the section presheaf carrier, and their reflexive, symmetric, and transitive behavior is supplied by the equivalence field of \autoref{def:sheaf-indexed-section-presheaf-carrier}.

For a cover $\mathcal{U}$, assume the displayed coverwise equality of the restrictions of $g$ and $h'$. This is exactly the antecedent required by the sheaf locality field in \autoref{def:sheaf-indexed-cover-compatibility-locality}. Applying that field over the same indexed cover gives $g\sim_i h'$, which is the global classifier equality claimed.
\end{proof}

\begin{theorem}[Sheaf cover ledger exactness obligation]
\label{thm:sheaf-cover-ledger-exactness-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$. An accepted cover and gluing ledger row for $\mathcal{S}$ consists exactly of indexed open-cover data $\mathcal{U}=(A,\iota,h,\gamma)$, the finite-intersection rows of the $\TopologyUp$ carrier, a compatible local section family $s_a:\mathsf{Sec}(\iota(a))$, and a global section $g:\mathsf{Sec}(i)$ with displayed restriction equalities
$$
\forall a:A,\quad \rho_{i,\iota(a)}(g)\sim_{\iota(a)}s_a.
$$
The ledger uses no host open-cover equality and no quotient primitive: all comparison data is expressed through indexed opens, restriction maps, and the section classifiers of \autoref{def:sheaf-indexed-section-presheaf-carrier}.
\end{theorem}
\begin{proof}
Unfold the indexed open cover and compatibility clauses in \autoref{def:sheaf-indexed-cover-compatibility-locality}. The cover ledger records only the indexing type $A$, the open-index map $\iota$, the inclusion witnesses $h_a:\iota(a)\le_{\mathcal{T}}i$, and the pointwise cover law $\gamma$. Compatibility is recorded by restricting local sections to the finite-intersection index supplied by the $\TopologyUp$ carrier and comparing them with the classifier on that intersection.

Unfold the gluing clause of the same definition. A gluing ledger row adds a section $g:\mathsf{Sec}(i)$ and the displayed restriction equalities against the compatible family. The theorem \autoref{thm:sheaf-global-restrictions-compatible-local-family} checks that restrictions of a global section produce a compatible local family, while \autoref{thm:sheaf-gluing-uniqueness-from-locality} checks that two displayed gluings of the same compatible family are classifier-equal.

The two definitions just unfolded contain no host-side equality of open covers and no quotient constructor. Their comparison mechanism is the indexed inclusion relation $j\le_{\mathcal{T}} i$, the finite-intersection row of the topology carrier, the restriction maps, and the section classifiers. Hence the listed rows are exact for the accepted cover and gluing ledger.
\end{proof}

\begin{definition}[Sheaf BHist cover nerve ledger]
\label{def:sheaf-bhist-cover-nerve-ledger}
Let $\mathcal{T}$ be an indexed open topology carrier for $\TopologyUp$ whose point carrier is $\mathsf{BHist}$, whose membership classifier is $\mathsf{OpenAt}$, and whose finite-intersection index is written $\wedge_{\TopologyUp}$. Let $\mathcal{S}$ be an indexed sheaf carrier over $\mathcal{T}$, and let $\mathcal{U}=(A,\iota,h,\gamma)$ be an indexed open cover of $i:\mathsf{OpenIx}$. The $\mathsf{BHist}$ cover nerve ledger of $\mathcal{U}$ is the finite-intersection ledger surface with the following rows.
\begin{enumerate}
\item For each $a:A$, the member row is the indexed open $\iota(a)$ with its inclusion witness $h_a:\iota(a)\le_{\mathcal{T}}i$ and its visible membership predicate $\mathsf{OpenAt}(\iota(a),b)$ for $b:\mathsf{BHist}$.
\item For each $a,b:A$, the pair-overlap row is $k_{a,b}:=\iota(a)\wedge_{\TopologyUp}\iota(b)$, together with the two finite-intersection projections $k_{a,b}\le_{\mathcal{T}}\iota(a)$ and $k_{a,b}\le_{\mathcal{T}}\iota(b)$ and the two restriction rows from $\mathsf{Sec}(\iota(a))$ and $\mathsf{Sec}(\iota(b))$ to $\mathsf{Sec}(k_{a,b})$.
\item For each $a,b,c:A$, the triple-overlap row is $\ell_{a,b,c}:=k_{a,b}\wedge_{\TopologyUp}\iota(c)$, together with the finite-intersection projections $\ell_{a,b,c}\le_{\mathcal{T}}k_{a,b}$ and $\ell_{a,b,c}\le_{\mathcal{T}}\iota(c)$ and the restriction rows obtained by composing through $k_{a,b}$ or directly from any member whose inclusion route is displayed.
\end{enumerate}
The ledger contains only $\mathsf{OpenAt}$ rows, finite-intersection projections, inclusion witnesses, presheaf restriction rows, section classifiers, and visible $\mathsf{BHist}$ provenance. It does not identify cover presentations by host equality and does not quotient overlap rows.
\end{definition}

\begin{theorem}[Sheaf BHist cover nerve overlap projections]
\label{thm:sheaf-bhist-cover-nerve-overlap-projections}
Let $\mathcal{T}$ be an indexed open topology carrier for $\TopologyUp$ on $\mathsf{BHist}$, let $\mathcal{S}$ be an indexed sheaf carrier over $\mathcal{T}$, and let $\mathcal{U}=(A,\iota,h,\gamma)$ be an indexed open cover of $i:\mathsf{OpenIx}$. For a local family $s_a:\mathsf{Sec}(\iota(a))$, compatibility over $\mathcal{U}$ is exactly the assertion that every pair-overlap row of the $\mathsf{BHist}$ cover nerve ledger carries classifier equality between the two projected restrictions:
$$
\forall a,b:A,\quad
\rho_{\iota(a),k_{a,b}}(s_a)
\sim_{k_{a,b}}
\rho_{\iota(b),k_{a,b}}(s_b),
$$
where $k_{a,b}:=\iota(a)\wedge_{\TopologyUp}\iota(b)$ and the inclusions are the finite-intersection projections of \autoref{def:topology-indexed-open-carrier}.
\end{theorem}
\begin{proof}
Unfold the compatibility predicate in \autoref{def:sheaf-indexed-cover-compatibility-locality}. Its only comparison clauses are indexed by pairs $a,b:A$, and each clause restricts $s_a$ and $s_b$ to the common intersection $\iota(a)\wedge_{\TopologyUp}\iota(b)$ before comparing them by the section classifier at that intersection.

Unfold the cover nerve ledger of \autoref{def:sheaf-bhist-cover-nerve-ledger}. Its pair-overlap rows are exactly the same indices $k_{a,b}$, with the same two finite-intersection projections supplied by \autoref{def:topology-indexed-open-carrier}. Therefore every compatibility clause is a classifier equality on one pair-overlap ledger row.

Conversely, assume every pair-overlap ledger row carries the displayed classifier equality. Reading those rows through the same two projections gives precisely the clauses required by \autoref{def:sheaf-indexed-cover-compatibility-locality}. Restriction composition is not extra data here; it only confirms that any displayed route to $k_{a,b}$ reads as the same section classifier row as the direct pair-overlap restriction.
\end{proof}

\begin{theorem}[Sheaf BHist cover nerve gluing readback]
\label{thm:sheaf-bhist-cover-nerve-gluing-readback}
Let $\mathcal{T}$ be an indexed open topology carrier for $\TopologyUp$ on $\mathsf{BHist}$, let $\mathcal{S}$ be an indexed sheaf carrier over $\mathcal{T}$, and let $\mathcal{U}=(A,\iota,h,\gamma)$ be an indexed open cover of $i:\mathsf{OpenIx}$. Suppose $s_a:\mathsf{Sec}(\iota(a))$ is compatible over $\mathcal{U}$ and $g:\mathsf{Sec}(i)$ is a gluing section with
$$
\forall a:A,\quad \rho_{i,\iota(a)}(g)\sim_{\iota(a)}s_a.
$$
Then the $\mathsf{BHist}$ cover nerve ledger reads $g$ back to the local family on every member row and to the induced compatible family on every pair-overlap row. Explicitly, for every $a:A$,
$$
\rho_{i,\iota(a)}(g)\sim_{\iota(a)}s_a,
$$
and for every $a,b:A$, writing $k_{a,b}:=\iota(a)\wedge_{\TopologyUp}\iota(b)$,
$$
\rho_{\iota(a),k_{a,b}}(\rho_{i,\iota(a)}(g))
\sim_{k_{a,b}}
\rho_{\iota(a),k_{a,b}}(s_a)
$$
and
$$
\rho_{\iota(b),k_{a,b}}(\rho_{i,\iota(b)}(g))
\sim_{k_{a,b}}
\rho_{\iota(b),k_{a,b}}(s_b).
$$
Consequently the two restrictions of $g$ to each pair-overlap ledger row recover the same classifier row as the compatible family there.
\end{theorem}
\begin{proof}
The member readback is the gluing equality displayed in the statement. It is exactly the gluing clause of \autoref{def:sheaf-indexed-cover-compatibility-locality} evaluated at the member row $\iota(a)$.

For a pair $a,b:A$, write $k=\iota(a)\wedge_{\TopologyUp}\iota(b)$. The finite-intersection field of \autoref{def:topology-indexed-open-carrier} supplies $k\le_{\mathcal{T}}\iota(a)$ and $k\le_{\mathcal{T}}\iota(b)$, which are the two pair-overlap projections recorded by \autoref{def:sheaf-bhist-cover-nerve-ledger}.

Transport the gluing equality $\rho_{i,\iota(a)}(g)\sim_{\iota(a)}s_a$ along $k\le_{\mathcal{T}}\iota(a)$ using the restriction classifier-stability field from \autoref{def:sheaf-indexed-section-presheaf-carrier}. This gives the first pair-overlap readback equality. The same transport along $k\le_{\mathcal{T}}\iota(b)$ gives the second one.

It remains to compare the two readings of $g$ on $k$. Restriction composition identifies the restriction of $\rho_{i,\iota(a)}(g)$ to $k$ and the restriction of $\rho_{i,\iota(b)}(g)$ to $k$ with the direct restriction $\rho_{i,k}(g)$, up to the classifier $\sim_k$. The compatibility of $s_a$ gives the corresponding equality between the two local-family restrictions. Transitivity and symmetry of $\sim_k$ combine these rows, so the pair-overlap ledger reads the gluing section back to the same classifier row as the compatible local family.
\end{proof}

\begin{theorem}[Sheaf NameCert carrier obligation]
\label{thm:sheaf-namecert-carrier-obligation}
Every indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$ determines the carrier-facing rows required by the $\NameCert_{\SheafUp}$ template. The rows are fixed as follows.
\begin{enumerate}
\item The traditional target is sheaf-theoretic section data over open covers.
\item The BEDC source is the presheaf restriction source of $\PreSheafUp$ together with the indexed-open source of $\TopologyUp$.
\item The carrier is the indexed section presheaf of \autoref{def:sheaf-indexed-section-presheaf-carrier}, equipped with the locality and gluing fields of \autoref{def:sheaf-indexed-cover-compatibility-locality}.
\item The classifier row is the family of section classifiers $\sim_i$.
\item The stability row is supplied by the restriction identity, restriction composition, restriction classifier-stability, and classifier-equivalence fields.
\item The ledger is the displayed data of covers, intersections, inclusion witnesses, and restriction maps.
\item The exactness row is visible cover-local readback: compatible local sections glue to a global section and locality identifies any two global readbacks with the same cover restrictions.
\item The standard bridge row is absent; this certificate surface records the BEDC sheaf interface without claiming an external set-theoretic sheaf bridge.
\end{enumerate}
\end{theorem}
\begin{proof}
Unpack the indexed sheaf carrier. Its presheaf part is exactly the tuple $\mathcal{P}=(\mathsf{Sec},\sim,\rho,\mathsf{Eqv},\mathsf{Id},\mathsf{Comp},\mathsf{Res})$ of \autoref{def:sheaf-indexed-section-presheaf-carrier}, so the carrier, classifier, and restriction-stability rows are not extra data: they are the displayed section carriers, displayed section classifiers, and the identity, composition, equivalence, and restriction classifier-stability fields.

Unpack the cover part. The topology side contributes open indices, inclusions, and finite-intersection witnesses by \autoref{def:topology-indexed-open-carrier}; the presheaf side contributes contravariant restriction scope by \autoref{ch:concrete-instances-presheaf-namecert}. The remaining sheaf fields in \autoref{def:sheaf-indexed-cover-compatibility-locality} are precisely locality and gluing over those covers, which give the visible cover-local readback row and leave no separate standard-bridge row to construct.
\end{proof}

\begin{theorem}[Sheaf restriction stability obligation]
\label{thm:sheaf-restriction-stability-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$. For inclusions $k\le_{\mathcal{T}}j\le_{\mathcal{T}}i$, restriction identity and restriction composition keep every section row inside the displayed classifier family. Explicitly, for $s:\mathsf{Sec}(i)$ one has
$$
\rho_{i,i}(s)\sim_i s
$$
and
$$
\rho_{j,k}(\rho_{i,j}(s))\sim_k\rho_{i,k}(s).
$$
When $k$ is an indexed intersection supplied by the finite-intersection field of \autoref{def:topology-indexed-open-carrier}, the same restriction-composition statement applies to the two induced inclusion chains, so cover restrictions remain stable under the topology intersection witnesses.
\end{theorem}
\begin{proof}
The first displayed relation is the identity field of the indexed section presheaf carrier in \autoref{def:sheaf-indexed-section-presheaf-carrier}. The second displayed relation is the composition field for the chain $k\le_{\mathcal{T}}j\le_{\mathcal{T}}i$. Both conclusions land in the classifier specified by the target open index, namely $\sim_i$ for identity and $\sim_k$ for composition.

For the intersection case, use \autoref{def:topology-indexed-open-carrier} to obtain the open-index intersection and its two projection inclusions. Combining either projection with a cover inclusion gives one of the admissible chains governed by the contravariant restriction interface of \autoref{ch:concrete-instances-presheaf-namecert}. Applying the same composition field to those chains gives stability on every displayed intersection row.
\end{proof}

\begin{theorem}[Sheaf locality and gluing NameCert obligation]
\label{thm:sheaf-locality-gluing-namecert-obligation}
For an indexed sheaf carrier $\mathcal{S}$ for $\SheafUp$, the locality and gluing fields supply the certificate rows consumed by \autoref{thm:sheaf-gluing-uniqueness-from-locality}, \autoref{thm:sheaf-global-restrictions-compatible-local-family}, and \autoref{cor:sheaf-gluing-global-restrictions-idempotent}. Namely, every compatible local family over an indexed open cover has a global readback section, and locality identifies any two global sections whose restrictions agree on every cover member.
\end{theorem}
\begin{proof}
Fix an indexed cover $\mathcal{U}=(A,\iota,h,\gamma)$ of $i$ and a compatible family $s_a:\mathsf{Sec}(\iota(a))$. The cover and compatibility predicates are those of \autoref{def:sheaf-indexed-cover-compatibility-locality}; their intersection clauses are meaningful because \autoref{def:topology-indexed-open-carrier} supplies finite-intersection witnesses, and their restriction clauses live in the contravariant presheaf scope of \autoref{ch:concrete-instances-presheaf-namecert}.

Apply the gluing field to obtain a section $g:\mathsf{Sec}(i)$ whose restrictions classify as the family $s_a$. Apply the locality field to any pair of such global sections whose memberwise restrictions agree; this is exactly the premise used by \autoref{thm:sheaf-gluing-uniqueness-from-locality}. The compatibility theorem uses the same restriction-composition row on intersections, and the idempotence corollary repacks gluing plus uniqueness for the local family obtained from one global section.
\end{proof}

\begin{theorem}[SheafUp BHist obligation surface]
\label{thm:sheaf-bhist-obligation-surface}
Let $\mathcal{T}$ be an indexed open topology carrier for $\TopologyUp$ whose point carrier is $\mathsf{BHist}$, with classifier $\hsame$, membership row $\mathsf{OpenAt}$, and finite-intersection index $\wedge_{\TopologyUp}$. Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over $\mathcal{T}$ in the sense of \autoref{def:sheaf-indexed-section-presheaf-carrier} and \autoref{def:sheaf-indexed-cover-compatibility-locality}. Then $\mathcal{S}$ supplies the $\SheafUp$ carrier, section classifiers, restriction maps, restriction identity, restriction composition, indexed-cover rows, compatibility predicate, locality field, gluing field, and visible $\mathsf{BHist}$ ledger rows required by the paper-side $\NameCert_{\SheafUp}$ obligation surface. The exposed data depend only on $\NameCert_{\PreSheafUp}$, $\NameCert_{\TopologyUp}$, the row $\mathsf{OpenAt}$, the finite-intersection rows of $\mathcal{T}$, and the classifier-equivalence fields on the section carriers.
\end{theorem}
\begin{proof}
Project the carrier and classifier rows from the indexed section presheaf carrier. For each open index $i$, the section carrier $\mathsf{Sec}(i)$ and classifier $\sim_i$ are visible, and the equivalence field supplies the reflexive, symmetric, and transitive classifier rules required by the certificate surface.

Project the restriction rows from the same tuple. The identity and composition fields are exactly the $\PreSheafUp$ restriction identity and restriction composition obligations, with inclusions interpreted through the indexed-open preorder $j\le_{\mathcal{T}}i$ defined by $\mathsf{OpenAt}$. The finite-intersection row of $\mathcal{T}$ supplies the common target index used in compatibility checks.

Finally project the cover, compatibility, locality, and gluing rows from \autoref{def:sheaf-indexed-cover-compatibility-locality}. The visible ledger is $\mathsf{BHist}$-scoped because every open membership and every inclusion witness is expressed by $\mathsf{OpenAt}$ on $\mathsf{BHist}$, and no host powerset equality is part of the exposed surface.
\end{proof}

\begin{theorem}[SheafUp restriction hsame transport obligation]
\label{thm:sheaf-restriction-hsame-transport-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over a $\mathsf{BHist}$-scoped indexed open topology carrier $\mathcal{T}$. Suppose a second displayed carrier is obtained by componentwise $\hsame$ transport of the topology row $\mathsf{OpenAt}$, the section carriers and classifiers, the restriction maps, and the indexed-cover rows. Then restriction compatibility, locality, and gluing for $\mathcal{S}$ transport to the displayed carrier. In particular, a compatible family remains compatible after transport, a locality hypothesis on transported restrictions yields transported classifier equality of global sections, and a gluing witness transports to a gluing witness for the transported local family.
\end{theorem}
\begin{proof}
Transport the topology row first. The $\TopologyUp$ membership-stability field moves each occurrence of $\mathsf{OpenAt}(i,h)$ across the displayed $\hsame$ witness, so the inclusion witnesses $j\le_{\mathcal{T}}i$ and the cover law for $\mathcal{U}=(A,\iota,\eta,\gamma)$ remain valid after transport.

Next transport the section rows. The componentwise transport hypothesis identifies each section carrier, classifier, and restriction map with its transported counterpart. Compatibility is a conjunction of classifier equalities after restricting to the finite-intersection index, so it follows by applying the transported restriction rows and then reading the section classifier equivalence fields in the transported carrier.

For locality, begin with transported agreement of two global sections on every cover member. Move that agreement back along the componentwise classifier transport, apply the locality field of $\mathcal{S}$, and transport the resulting global classifier equality forward. For gluing, transport the compatible family back, apply the gluing field of $\mathcal{S}$ to obtain a global section, and transport that witness and its restriction equalities forward.
\end{proof}

\begin{theorem}[SheafUp cover gluing NameCert export]
\label{thm:sheaf-cover-gluing-namecert-export}
The $\mathsf{BHist}$-scoped surface of \autoref{thm:sheaf-bhist-obligation-surface}, together with the transport obligation of \autoref{thm:sheaf-restriction-hsame-transport-obligation}, the uniqueness theorem \autoref{thm:sheaf-gluing-uniqueness-from-locality}, and the global-restriction compatibility theorem \autoref{thm:sheaf-global-restrictions-compatible-local-family}, assembles the paper-side $\NameCert_{\SheafUp}$ obligation surface consumed by $\RingedSpaceUp$ and $\SchemeUp$. The exported surface provides sheaf carrier data, restriction coherence, cover compatibility, locality, gluing, uniqueness up to section classifier equality, and compatibility of restrictions of global sections; it claims no standard bridge and no external powerset equality.
\end{theorem}
\begin{proof}
Start with the obligation surface of \autoref{thm:sheaf-bhist-obligation-surface}. It supplies the carrier, classifier, restriction, cover, compatibility, locality, gluing, and visible ledger rows over $\mathsf{BHist}$, all routed through $\NameCert_{\PreSheafUp}$ and $\NameCert_{\TopologyUp}$.

Use \autoref{thm:sheaf-restriction-hsame-transport-obligation} to make those rows stable under the componentwise $\hsame$ transports seen by downstream chapters. This gives $\RingedSpaceUp$ and $\SchemeUp$ a transport discipline for topology membership through $\mathsf{OpenAt}$ and for section equality through the displayed section classifiers.

The gluing consequences are then the two local theorems already present in the chapter. Apply \autoref{thm:sheaf-gluing-uniqueness-from-locality} for uniqueness of a glued global section up to the section classifier, and apply \autoref{thm:sheaf-global-restrictions-compatible-local-family} for compatibility of the local family obtained by restricting a global section.

Combining these rows gives exactly the paper-side $\NameCert_{\SheafUp}$ obligation surface needed by the dependent ringed-space and scheme certificates. Since every cited row stays inside indexed opens, $\mathsf{OpenAt}$, $\hsame$, and section classifiers, the package contains neither a standard sheaf bridge nor an equality of host powersets.
\end{proof}
