\begin{theorem}[Sheaf NameCert carrier obligation]
\label{thm:sheaf-namecert-carrier-obligation}
Every indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$ determines the carrier-facing rows required by the $\NameCert_{\SheafUp}$ template. The rows are fixed as follows.
\begin{enumerate}
\item The traditional target is sheaf-theoretic section data over open covers.
\item The BEDC source is the presheaf restriction source of $\PreSheafUp$ together with the indexed-open source of $\TopologyUp$.
\item The carrier is the indexed section presheaf of \autoref{def:sheaf-indexed-section-presheaf-carrier}, equipped with the locality and gluing fields of \autoref{def:sheaf-indexed-cover-compatibility-locality}.
\item The classifier row is the family of section classifiers $\sim_i$.
\item The stability row is supplied by the restriction identity, restriction composition, restriction classifier-stability, and classifier-equivalence fields.
\item The ledger is the displayed data of covers, intersections, inclusion witnesses, and restriction maps.
\item The exactness row is visible cover-local readback: compatible local sections glue to a global section and locality identifies any two global readbacks with the same cover restrictions.
\item The standard bridge row is absent; this certificate surface records the BEDC sheaf interface without claiming an external set-theoretic sheaf bridge.
\end{enumerate}
\end{theorem}
\begin{proof}
Unpack the indexed sheaf carrier. Its presheaf part is exactly the tuple $\mathcal{P}=(\mathsf{Sec},\sim,\rho,\mathsf{Eqv},\mathsf{Id},\mathsf{Comp},\mathsf{Res})$ of \autoref{def:sheaf-indexed-section-presheaf-carrier}, so the carrier, classifier, and restriction-stability rows are not extra data: they are the displayed section carriers, displayed section classifiers, and the identity, composition, equivalence, and restriction classifier-stability fields.

Unpack the cover part. The topology side contributes open indices, inclusions, and finite-intersection witnesses by \autoref{def:topology-indexed-open-carrier}; the presheaf side contributes contravariant restriction scope by \autoref{ch:concrete-instances-presheaf-namecert}. The remaining sheaf fields in \autoref{def:sheaf-indexed-cover-compatibility-locality} are precisely locality and gluing over those covers, which give the visible cover-local readback row and leave no separate standard-bridge row to construct.
\end{proof}

\begin{theorem}[Sheaf restriction stability obligation]
\label{thm:sheaf-restriction-stability-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$. For inclusions $k\le_{\mathcal{T}}j\le_{\mathcal{T}}i$, restriction identity and restriction composition keep every section row inside the displayed classifier family. Explicitly, for $s:\mathsf{Sec}(i)$ one has
$$
\rho_{i,i}(s)\sim_i s
$$
and
$$
\rho_{j,k}(\rho_{i,j}(s))\sim_k\rho_{i,k}(s).
$$
When $k$ is an indexed intersection supplied by the finite-intersection field of \autoref{def:topology-indexed-open-carrier}, the same restriction-composition statement applies to the two induced inclusion chains, so cover restrictions remain stable under the topology intersection witnesses.
\end{theorem}
\begin{proof}
The first displayed relation is the identity field of the indexed section presheaf carrier in \autoref{def:sheaf-indexed-section-presheaf-carrier}. The second displayed relation is the composition field for the chain $k\le_{\mathcal{T}}j\le_{\mathcal{T}}i$. Both conclusions land in the classifier specified by the target open index, namely $\sim_i$ for identity and $\sim_k$ for composition.

For the intersection case, use \autoref{def:topology-indexed-open-carrier} to obtain the open-index intersection and its two projection inclusions. Combining either projection with a cover inclusion gives one of the admissible chains governed by the contravariant restriction interface of \autoref{ch:concrete-instances-presheaf-namecert}. Applying the same composition field to those chains gives stability on every displayed intersection row.
\end{proof}

\begin{theorem}[Sheaf locality and gluing NameCert obligation]
\label{thm:sheaf-locality-gluing-namecert-obligation}
For an indexed sheaf carrier $\mathcal{S}$ for $\SheafUp$, the locality and gluing fields supply the certificate rows consumed by \autoref{thm:sheaf-gluing-uniqueness-from-locality}, \autoref{thm:sheaf-global-restrictions-compatible-local-family}, and \autoref{cor:sheaf-gluing-global-restrictions-idempotent}. Namely, every compatible local family over an indexed open cover has a global readback section, and locality identifies any two global sections whose restrictions agree on every cover member.
\end{theorem}
\begin{proof}
Fix an indexed cover $\mathcal{U}=(A,\iota,h,\gamma)$ of $i$ and a compatible family $s_a:\mathsf{Sec}(\iota(a))$. The cover and compatibility predicates are those of \autoref{def:sheaf-indexed-cover-compatibility-locality}; their intersection clauses are meaningful because \autoref{def:topology-indexed-open-carrier} supplies finite-intersection witnesses, and their restriction clauses live in the contravariant presheaf scope of \autoref{ch:concrete-instances-presheaf-namecert}.

Apply the gluing field to obtain a section $g:\mathsf{Sec}(i)$ whose restrictions classify as the family $s_a$. Apply the locality field to any pair of such global sections whose memberwise restrictions agree; this is exactly the premise used by \autoref{thm:sheaf-gluing-uniqueness-from-locality}. The compatibility theorem uses the same restriction-composition row on intersections, and the idempotence corollary repacks gluing plus uniqueness for the local family obtained from one global section.
\end{proof}

\begin{theorem}[SheafUp BHist obligation surface]
\label{thm:sheaf-bhist-obligation-surface}
Let $\mathcal{T}$ be an indexed open topology carrier for $\TopologyUp$ whose point carrier is $\mathsf{BHist}$, with classifier $\hsame$, membership row $\mathsf{OpenAt}$, and finite-intersection index $\wedge_{\TopologyUp}$. Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over $\mathcal{T}$ in the sense of \autoref{def:sheaf-indexed-section-presheaf-carrier} and \autoref{def:sheaf-indexed-cover-compatibility-locality}. Then $\mathcal{S}$ supplies the $\SheafUp$ carrier, section classifiers, restriction maps, restriction identity, restriction composition, indexed-cover rows, compatibility predicate, locality field, gluing field, and visible $\mathsf{BHist}$ ledger rows required by the paper-side $\NameCert_{\SheafUp}$ obligation surface. The exposed data depend only on $\NameCert_{\PreSheafUp}$, $\NameCert_{\TopologyUp}$, the row $\mathsf{OpenAt}$, the finite-intersection rows of $\mathcal{T}$, and the classifier-equivalence fields on the section carriers.
\end{theorem}
\begin{proof}
Project the carrier and classifier rows from the indexed section presheaf carrier. For each open index $i$, the section carrier $\mathsf{Sec}(i)$ and classifier $\sim_i$ are visible, and the equivalence field supplies the reflexive, symmetric, and transitive classifier rules required by the certificate surface.

Project the restriction rows from the same tuple. The identity and composition fields are exactly the $\PreSheafUp$ restriction identity and restriction composition obligations, with inclusions interpreted through the indexed-open preorder $j\le_{\mathcal{T}}i$ defined by $\mathsf{OpenAt}$. The finite-intersection row of $\mathcal{T}$ supplies the common target index used in compatibility checks.

Finally project the cover, compatibility, locality, and gluing rows from \autoref{def:sheaf-indexed-cover-compatibility-locality}. The visible ledger is $\mathsf{BHist}$-scoped because every open membership and every inclusion witness is expressed by $\mathsf{OpenAt}$ on $\mathsf{BHist}$, and no host powerset equality is part of the exposed surface.
\end{proof}

\begin{theorem}[SheafUp restriction hsame transport obligation]
\label{thm:sheaf-restriction-hsame-transport-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over a $\mathsf{BHist}$-scoped indexed open topology carrier $\mathcal{T}$. Suppose a second displayed carrier is obtained by componentwise $\hsame$ transport of the topology row $\mathsf{OpenAt}$, the section carriers and classifiers, the restriction maps, and the indexed-cover rows. Then restriction compatibility, locality, and gluing for $\mathcal{S}$ transport to the displayed carrier. In particular, a compatible family remains compatible after transport, a locality hypothesis on transported restrictions yields transported classifier equality of global sections, and a gluing witness transports to a gluing witness for the transported local family.
\end{theorem}
\begin{proof}
Transport the topology row first. The $\TopologyUp$ membership-stability field moves each occurrence of $\mathsf{OpenAt}(i,h)$ across the displayed $\hsame$ witness, so the inclusion witnesses $j\le_{\mathcal{T}}i$ and the cover law for $\mathcal{U}=(A,\iota,\eta,\gamma)$ remain valid after transport.

Next transport the section rows. The componentwise transport hypothesis identifies each section carrier, classifier, and restriction map with its transported counterpart. Compatibility is a conjunction of classifier equalities after restricting to the finite-intersection index, so it follows by applying the transported restriction rows and then reading the section classifier equivalence fields in the transported carrier.

For locality, begin with transported agreement of two global sections on every cover member. Move that agreement back along the componentwise classifier transport, apply the locality field of $\mathcal{S}$, and transport the resulting global classifier equality forward. For gluing, transport the compatible family back, apply the gluing field of $\mathcal{S}$ to obtain a global section, and transport that witness and its restriction equalities forward.
\end{proof}

\begin{theorem}[SheafUp cover gluing NameCert export]
\label{thm:sheaf-cover-gluing-namecert-export}
The $\mathsf{BHist}$-scoped surface of \autoref{thm:sheaf-bhist-obligation-surface}, together with the transport obligation of \autoref{thm:sheaf-restriction-hsame-transport-obligation}, the uniqueness theorem \autoref{thm:sheaf-gluing-uniqueness-from-locality}, and the global-restriction compatibility theorem \autoref{thm:sheaf-global-restrictions-compatible-local-family}, assembles the paper-side $\NameCert_{\SheafUp}$ obligation surface consumed by $\RingedSpaceUp$ and $\SchemeUp$. The exported surface provides sheaf carrier data, restriction coherence, cover compatibility, locality, gluing, uniqueness up to section classifier equality, and compatibility of restrictions of global sections; it claims no standard bridge and no external powerset equality.
\end{theorem}
\begin{proof}
Start with the obligation surface of \autoref{thm:sheaf-bhist-obligation-surface}. It supplies the carrier, classifier, restriction, cover, compatibility, locality, gluing, and visible ledger rows over $\mathsf{BHist}$, all routed through $\NameCert_{\PreSheafUp}$ and $\NameCert_{\TopologyUp}$.

Use \autoref{thm:sheaf-restriction-hsame-transport-obligation} to make those rows stable under the componentwise $\hsame$ transports seen by downstream chapters. This gives $\RingedSpaceUp$ and $\SchemeUp$ a transport discipline for topology membership through $\mathsf{OpenAt}$ and for section equality through the displayed section classifiers.

The gluing consequences are then the two local theorems already present in the chapter. Apply \autoref{thm:sheaf-gluing-uniqueness-from-locality} for uniqueness of a glued global section up to the section classifier, and apply \autoref{thm:sheaf-global-restrictions-compatible-local-family} for compatibility of the local family obtained by restricting a global section.

Combining these rows gives exactly the paper-side $\NameCert_{\SheafUp}$ obligation surface needed by the dependent ringed-space and scheme certificates. Since every cited row stays inside indexed opens, $\mathsf{OpenAt}$, $\hsame$, and section classifiers, the package contains neither a standard sheaf bridge nor an equality of host powersets.
\end{proof}
