\section{Root obligations for downstream certificates}
\label{sec:sheaf-root-obligations}

\begin{definition}[SheafUp root-unblock BEDC source]
\label{def:sheaf-root-unblock-bedc-source}
The root-unblock source for $\SheafUp$ is the ten-field certificate surface consumed by ringed-space, scheme, and restricted-open sheaf constructions.
\begin{enumerate}
\item The traditional target is sheaves of sections over indexed opens.
\item The BEDC source chapters are $\TopologyUp$, $\PreSheafUp$, and $\NameCert$.
\item The history ledger is the $\mathsf{BHist}$ cover-nerve ledger of \autoref{def:sheaf-bhist-cover-nerve-ledger}.
\item The carrier is the indexed section presheaf carrier of \autoref{def:sheaf-indexed-section-presheaf-carrier}, equipped with the locality and gluing fields of \autoref{def:sheaf-indexed-cover-compatibility-locality}.
\item The classifier family is the open-indexed relation $\sim_i$ on $\mathsf{Sec}(i)$.
\item The cover ledger records cover indices $A$, cover-member maps $\iota:A\to\mathsf{OpenIx}$, and pointwise cover rows over $\mathsf{BHist}$.
\item The overlap ledger records finite intersections $\iota(a)\wedge_{\TopologyUp}\iota(a')$ and their projection rows.
\item The restriction ledger records routes from a target open to cover members and overlaps, with identity, composition, and classifier-stability rows.
\item Optional route histories are recorded by $\Cont$ rows, and history-cell membership is transported only by $\hsame$.
\item The surface contains no quotient of cover presentations and no equality of host powersets of opens.
\end{enumerate}
\end{definition}

\begin{theorem}[Sheaf root-unblock cover membership obligation]
\label{thm:sheaf-root-unblock-cover-membership-obligation}
Let $\mathcal{U}=(A,\iota,h,\gamma)$ be an accepted cover row of an open index $i$ over a $\mathsf{BHist}$ topology ledger. Then every displayed history membership in the covered open has a displayed cover-member witness:
$$
\forall b:\mathsf{BHist},\
\mathsf{OpenAt}(i,b)
\Longrightarrow
\exists a:A,\ \mathsf{OpenAt}(\iota(a),b).
$$
All overlap information used downstream is recorded only through finite-intersection rows and $\hsame$-stable $\mathsf{BHist}$ membership, not through host powerset equality.
\end{theorem}
\begin{proof}
Unfold the accepted cover row. Its pointwise cover component is exactly the displayed implication from $\mathsf{OpenAt}(i,b)$ to a cover index $a:A$ with $\mathsf{OpenAt}(\iota(a),b)$.

For overlap rows, use the finite-intersection field of the indexed topology carrier as in \autoref{thm:sheaf-bhist-cover-nerve-overlap-projections}. It supplies the overlap index and the two projection rows back to the participating cover members.

History transport is then read from the $\mathsf{BHist}$ cover-nerve ledger of \autoref{def:sheaf-bhist-cover-nerve-ledger}. That ledger admits only $\hsame$-stable membership transport, so the exported cover-membership row stays internal to indexed opens and history cells.
\end{proof}

\begin{theorem}[Sheaf root-unblock restriction stability obligation]
\label{thm:sheaf-root-unblock-restriction-stability-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$. Restriction identity, restriction composition, stable restriction rows, and $\Cont$ associativity for route histories preserve the target section classifier along one-step and two-step restriction routes. Concretely, for $j\le_{\mathcal{T}}i$ and $k\le_{\mathcal{T}}j\le_{\mathcal{T}}i$, the rows
$$
\rho_{i,i}(s)\sim_i s,
\qquad
s\sim_i t\Longrightarrow \rho_{i,j}(s)\sim_j\rho_{i,j}(t),
\qquad
\rho_{j,k}(\rho_{i,j}(s))\sim_k\rho_{i,k}(s)
$$
are the classifier-preserving route rows exposed to downstream certificates.
\end{theorem}
\begin{proof}
The identity and composition rows are fields of the indexed section presheaf carrier in \autoref{def:sheaf-indexed-section-presheaf-carrier}. The one-step classifier preservation row is the stable restriction row of \autoref{def:sheaf-stable-restriction-row}, also cited as \autoref{thm:sheaf-restriction-classifier-transport}.

For a two-step route, first use restriction classifier transport along $j\le_{\mathcal{T}}i$, then compose with the route from $j$ to $k$. The displayed composition row identifies this two-step restriction with the direct restriction from $i$ to $k$ in the classifier $\sim_k$.

If the ledger also carries $\Cont$ histories for the same routes, their associativity only compares displayed route histories. It does not alter the open index $k$ or the classifier $\sim_k$, so it preserves the same target section classifier consumed by the certificate.
\end{proof}

\begin{theorem}[Sheaf root-unblock locality and gluing obligation]
\label{thm:sheaf-root-unblock-locality-gluing-obligation}
Let $\mathcal{S}$ be an indexed sheaf carrier for $\SheafUp$ over an indexed open topology carrier $\mathcal{T}$, and let $\mathcal{U}=(A,\iota,h,\gamma)$ be an indexed cover of $i$. Compatible local families with displayed gluings have a $\NameCert$-consumable exactness row: locality gives global classifier equality for any two global readbacks whose restrictions agree on the cover, and gluing supplies existence of a global readback without quotienting cover presentations.
\end{theorem}
\begin{proof}
The existence half is the gluing field in \autoref{def:sheaf-indexed-cover-compatibility-locality}. Given a compatible local family, it supplies a section $g:\mathsf{Sec}(i)$ together with displayed restriction rows to each $\iota(a)$.

The uniqueness half is locality. If two global readbacks restrict to classifier-equal sections on every cover member, the locality field returns equality in the global classifier $\sim_i$; \autoref{thm:sheaf-gluing-uniqueness-from-locality} packages the same argument for two displayed gluings of one compatible family.

Refinement and presentation changes are handled by the existing refinement rows \autoref{thm:sheaf-refinement-gluing-descent}, \autoref{thm:sheaf-refined-cover-exactness-obligation}, \autoref{thm:sheaf-common-refinement-gluing-invariance}, and \autoref{thm:sheaf-cover-presentation-exactness}. Each row uses displayed cover maps, common refinements, restriction stability, $\Cont$ route histories when present, and $\hsame$-stable membership; none introduces a quotient of cover presentations.
\end{proof}

\begin{definition}[Sheaf root cover-nerve export surface]
\label{def:sheaf-root-cover-nerve-export-surface}
The root cover-nerve export surface for $\SheafUp$ is the three-row $\mathsf{BHist}$-scoped certificate surface consumed by downstream chapters.
\begin{enumerate}
\item The traditional target is sheaves over indexed opens, read through section carriers on a cover nerve rather than through host open covers.
\item The BEDC source chapters are $\TopologyUp$, $\PreSheafUp$, and $\NameCert$.
\item The carrier is the family of indexed sections over $\mathsf{BHist}$ opens, using $\mathsf{Sec}(i)$ from \autoref{def:sheaf-indexed-section-presheaf-carrier} for each open index $i$.
\item The classifier family is the displayed section relation $\sim_i$ on $\mathsf{Sec}(i)$.
\item The stability rows are restriction identity, restriction composition, classifier transport, and optional $\Cont$ route-history transport.
\item The ledger rows are cover-member cells, pair-overlap cells, and route-history cells in the $\mathsf{BHist}$ cover nerve of \autoref{def:sheaf-bhist-cover-nerve-ledger}.
\item The exactness rows are cover membership, restriction route stability, and locality/gluing.
\item The cover-membership row sends every accepted $\mathsf{OpenAt}(i,b)$ cell to a displayed cover member and its pair-overlap ledger context.
\item The downstream export is exactly the rows listed here: $\RingedSpaceUp$, $\SchemeUp$, and topology pullback consumers receive no host cover equality, cover quotient, stalk quotient, or external sheafification operation.
\item There is no standard bridge in this surface.
\end{enumerate}
\end{definition}

\begin{theorem}[Sheaf root cover-nerve membership exhaustion]
\label{thm:sheaf-root-cover-nerve-membership-exhaustion}
Let $\mathcal{U}=(A,\iota,h,\gamma)$ be an accepted cover row of an indexed open $i$ over the $\mathsf{BHist}$ topology ledger. Every displayed cell $\mathsf{OpenAt}(i,b)$ in this accepted cover has a cover-member witness and a pair-overlap row inside the $\mathsf{BHist}$ cover nerve:
$$
\forall b:\mathsf{BHist},\
\mathsf{OpenAt}(i,b)
\Longrightarrow
\exists a:A,\ \mathsf{OpenAt}(\iota(a),b)
$$
and for every second member $a':A$ the ledger also contains the finite-intersection row for $\iota(a)\wedge_{\TopologyUp}\iota(a')$ with its two projections to the participating members.
\end{theorem}
\leanchecked{BEDC.Derived.SheafUp.SheafRootCoverNerve\_membership\_exhaustion}
\begin{proof}
Apply the cover-membership obligation of \autoref{thm:sheaf-root-unblock-cover-membership-obligation}. It reads the accepted cover row as a $\mathsf{BHist}$-indexed implication from an ambient displayed cell to a cover-member witness, so every $\mathsf{OpenAt}(i,b)$ cell is exhausted by a displayed member $\iota(a)$.

The pair-overlap row is then the overlap projection surface of \autoref{thm:sheaf-bhist-cover-nerve-overlap-projections}, unpacked inside the cover-nerve ledger of \autoref{def:sheaf-bhist-cover-nerve-ledger}. For each pair $a,a':A$, the finite-intersection row supplies the overlap index and the two projections back to $\iota(a)$ and $\iota(a')$.

Because the ledger transports membership only by $\hsame$, this exhaustion stays scoped to $\mathsf{BHist}$ cells and indexed opens. No host cover equality or quotient of cover presentations is introduced.
\end{proof}

\begin{theorem}[Sheaf root cover-nerve restriction route stability]
\label{thm:sheaf-root-cover-nerve-restriction-route-stability}
Let $\mathcal{S}$ be the indexed section carrier of \autoref{def:sheaf-indexed-section-presheaf-carrier} over an indexed open topology carrier. One-step and two-step restrictions preserve section classifiers:
$$
s\sim_i t
\Longrightarrow
\rho_{i,j}(s)\sim_j\rho_{i,j}(t),
\qquad
\rho_{j,k}(\rho_{i,j}(s))\sim_k\rho_{i,k}(s)
$$
for every displayed chain $k\le_{\mathcal{T}}j\le_{\mathcal{T}}i$. Optional $\Cont$ route histories compare route witnesses only and do not alter the target classifier $\sim_j$ or $\sim_k$.
\end{theorem}
\leanchecked{BEDC.Derived.SheafUp.SheafBHistCoverNerveLedger\_route\_hsame\_transport}
\begin{proof}
The first displayed row is the restriction classifier-transport field of \autoref{def:sheaf-indexed-section-presheaf-carrier}. It is also the one-step stability clause isolated by \autoref{thm:sheaf-root-unblock-restriction-stability-obligation}.

For the two-step row, apply the composition field of the same carrier to the chain $k\le_{\mathcal{T}}j\le_{\mathcal{T}}i$. The comparison lands in $\sim_k$, so the direct restriction and the composed restriction have the same target classifier.

If a $\Cont$ history is present, use the route-history part of \autoref{thm:sheaf-root-unblock-restriction-stability-obligation}. Those histories record associativity of displayed routes; they do not change the open index of the restricted section, hence cannot change the classifier family consumed downstream.
\end{proof}

\begin{theorem}[Sheaf root cover-nerve downstream coverage]
\label{thm:sheaf-root-cover-nerve-downstream-coverage}
The downstream consumers $\RingedSpaceUp$, $\SchemeUp$, and topology pullback constructions receive exactly the rows of \autoref{def:sheaf-root-cover-nerve-export-surface}: cover-member cells, pair-overlap cells, one-step and two-step restriction stability rows, optional $\Cont$ route histories, and locality/gluing exactness rows. They receive no host cover equality, cover quotient, stalk quotient, or external sheafification operation.
\end{theorem}
\begin{proof}
The carrier part is fixed by \autoref{def:sheaf-indexed-section-presheaf-carrier}: downstream chapters can read only indexed section carriers, section classifiers, restrictions, and the identity, composition, and classifier-transport rows attached to them.

The cover part is fixed by \autoref{def:sheaf-bhist-cover-nerve-ledger} and \autoref{thm:sheaf-root-cover-nerve-membership-exhaustion}. These provide cover-member cells and pair-overlap cells over $\mathsf{BHist}$, with overlap projections supplied by \autoref{thm:sheaf-bhist-cover-nerve-overlap-projections}.

The exactness part is the union of the three root obligations. Cover membership comes from \autoref{thm:sheaf-root-unblock-cover-membership-obligation}; restriction route stability comes from \autoref{thm:sheaf-root-unblock-restriction-stability-obligation}; locality and gluing come from \autoref{thm:sheaf-root-unblock-locality-gluing-obligation}.

Those cited rows are precisely the rows listed in \autoref{def:sheaf-root-cover-nerve-export-surface}. Since none of them introduces host cover equality, a cover quotient, a stalk quotient, or an external sheafification operation, no downstream consumer obtains such a row from this export surface.
\end{proof}
\leanchecked{BEDC.Derived.SheafUp.SheafRootCoverNerve\_downstream\_coverage}

\begin{theorem}[Sheaf root cover-nerve exact globalization package]
\label{thm:sheaf-root-cover-nerve-exact-globalize-package}
The root cover-nerve export surface of \autoref{def:sheaf-root-cover-nerve-export-surface} forms an $\ExactGlobalizeBase$-style package over the indexed-open $\mathsf{BHist}$ cover nerve. Its coverage face is \autoref{thm:sheaf-root-cover-nerve-membership-exhaustion}; its base soundness face is \autoref{thm:sheaf-root-cover-nerve-restriction-route-stability}; its base completeness and exactness face is the locality-gluing row of \autoref{thm:sheaf-root-unblock-locality-gluing-obligation}. Hence $\RingedSpaceUp$ and $\SchemeUp$ may consume one classifier-exact cover-nerve package, with no host cover equality, cover quotient, stalk quotient, or external sheafification operation.
\end{theorem}
\begin{proof}
Unpack \autoref{def:sheaf-root-cover-nerve-export-surface}. The carrier is the indexed family $\mathsf{Sec}(i)$ over $\mathsf{BHist}$ opens, the classifier is the displayed relation $\sim_i$, and the ledger is the cover nerve of \autoref{def:sheaf-bhist-cover-nerve-ledger}.

The coverage face is exactly \autoref{thm:sheaf-root-cover-nerve-membership-exhaustion}. It sends each displayed $\mathsf{OpenAt}(i,b)$ cell to a cover member and records the pair-overlap rows needed by downstream restriction routes.

The base soundness face is \autoref{thm:sheaf-root-cover-nerve-restriction-route-stability}. One-step restriction, two-step restriction, classifier transport, and optional $\Cont$ route histories preserve the section classifier on the target indexed open.

The base completeness and exactness face is \autoref{thm:sheaf-root-unblock-locality-gluing-obligation}. Gluing constructs the global readback from compatible local rows, and locality identifies any two global readbacks whose restrictions agree on the accepted cover.

These are precisely the coverage, soundness, and completeness fields required by the exact-globalization constructor of \autoref{thm:exact-globalize-base-target}, with the relation field constrained as in \autoref{def:exact-globalize-base}. Repacking the three displayed faces therefore gives the single classifier-exact cover-nerve package consumed by the downstream chapters, and \autoref{thm:sheaf-root-cover-nerve-downstream-coverage} fixes that no quotient or external sheafification row is exported.
\end{proof}
