\begin{definition}[MetaCIC normalization frontier carrier]
\label{def:metacic-normalization-frontier-carrier}
A $\MetaCICNormalizationFrontierUp$ carrier is a finite $\BHist$ packet
$$
F=(C,K,E,N,S,H,R,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $C$ is the candidate-evidence row for the inspected empty-context typed closed MetaCIC terms;
\item $K$ is the closed-candidate evidence row, recording where the closed term is actually placed into the candidate interface;
\item $E$ is the finished-normal evidence row available after bounded reduction or displayed normal-form inspection;
\item $N$ is the normal-endpoint use row consumed by closed-normal consistency routes;
\item $S$ is the subject-reduction obstruction row, kept visible whenever candidate evidence or finished-normal evidence does not erase the preservation boundary;
\item $H$ records componentwise $\hsame$ transport for $C,K,E,N,S,R,P,L$ and the local packet shape;
\item $R$ records the displayed $\Cont$ replay routes by which downstream consumers read candidate evidence, finished-normal evidence, normal endpoints, and obstruction rows;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:metacic-open-problems}, \autoref{ch:concrete-instances-metacic-open-frontier-ledger-namecert}, \autoref{ch:concrete-instances-metacicnormalizationaudit-namecert}, \autoref{ch:concrete-instances-metacicnormalizationauditseal-namecert}, and \autoref{ch:concrete-instances-closed-normal-route-certificate-namecert};
\item $L$ is the local $\NameCert_{\MetaCICNormalizationFrontierUp}$ row.
\end{enumerate}
The carrier is finite and obstruction-preserving. It records where a closed-normal consumer may read normalization evidence, but it does not turn the normalization frontier into a blanket closed strong-normalization theorem.
\end{definition}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.taste\_gate}

\begin{theorem}[MetaCIC normalization frontier NameCert obligations]
\label{thm:metacic-normalization-frontier-namecert-obligations}
Every accepted $\MetaCICNormalizationFrontierUp$ packet with carrier \autoref{def:metacic-normalization-frontier-carrier} carries exactly the following local NameCert obligations:
\begin{enumerate}
\item carrier admission for $F=(C,K,E,N,S,H,R,P,L)$ as one finite $\BHist$ packet;
\item candidate-evidence boundary: a read of candidate-mediated strong-normalization content must pass through $C$ and the closed-candidate row $K$;
\item finished-normal boundary: a read of finished-normal content must pass through $E$ before it can feed the normal-endpoint row $N$;
\item closed-normal consumer handoff: any consistency-facing read of $N$ must replay through $R$ with provenance $P$ and the local naming row $L$;
\item subject-reduction-obstruction separation: the obstruction row $S$ remains distinct from $C,K,E,N$ and is not discharged by the normalization packet.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.MetaCICNormalizationFrontierCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is projection from \autoref{def:metacic-normalization-frontier-carrier}. The nine rows $C,K,E,N,S,H,R,P,L$ are the complete finite packet.

For the candidate boundary, inspect $C$ and $K$. The candidate row records the available normalization evidence, while the closed-candidate row records the point at which an empty-context closed term is admitted to that interface.

For the finished-normal boundary, inspect $E$ and $N$. The endpoint row is available to a closed-normal consumer only after the finished-normal evidence row has been read through the displayed replay route.

The handoff and separation clauses use the structural rows. The replay row $R$, provenance row $P$, and local row $L$ expose only the displayed normalization frontier, and the obstruction coordinate $S$ remains a named coordinate rather than a hidden subject-reduction theorem.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier carrier rows]
\label{thm:metacic-normalization-frontier-carrier-rows}
For every accepted $\MetaCICNormalizationFrontierUp$ packet, carrier admission exposes the concrete finite packet
$$
F=(C,K,E,N,S,H,R,P,L)
$$
as a $\BHist$ carrier with candidate rows $C,K$, finished rows $E,N$, obstruction row $S$, componentwise $\hsame$ row $H$, displayed $\Cont$ replay row $R$, $\Pkg$ provenance row $P$, and local $\NameCert$ row $L$. No carrier read may replace these rows by an unnamed normalization source.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-normalization-frontier-carrier}. It lists $F=(C,K,E,N,S,H,R,P,L)$ as one finite $\BHist$ packet.

Apply the carrier-admission clause of \autoref{thm:metacic-normalization-frontier-namecert-obligations}. That clause routes every carrier read through the displayed rows before any downstream closed-normal consumer may use the frontier.

The row $S$ remains visible in the same projection. Since it is a named obstruction coordinate rather than an erased proof obligation, carrier admission cannot be read as a blanket normalization theorem.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier classifier stability]
\label{thm:metacic-normalization-frontier-classifier-stability}
In an accepted $\MetaCICNormalizationFrontierUp$ packet
$$
F=(C,K,E,N,S,H,R,P,L),
$$
the local classifier is stable under componentwise $\hsame$ transport only along the displayed $\BHist$ rows: candidate-mediated reads pass through $C,K$, finished-normal reads pass through $E,N$, and both routes replay through the $\Cont$ row $R$ with $\Pkg$ provenance $P$ and local $\NameCert$ row $L$. The obstruction row $S$ is transported as an obstruction row and is not discharged by classifier stability.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.MetaCICNormalizationFrontierCarrier\_classifier\_stability}
\begin{proof}
Use the NameCert obligations to separate the two positive evidence routes. Candidate reads are routed through $C,K$, while finished-normal reads are routed through $E,N$ before the normal endpoint is consumed.

Transport is componentwise through $H$. It can preserve the displayed candidate, finished, replay, provenance, and local naming rows, but it has no coordinate that turns a candidate row into a finished row or erases the obstruction row $S$.

The replay row $R$ and package row $P$ then expose the same classified frontier surface to downstream consumers. Thus classifier stability is stability of the displayed packet, with $S$ retained as an obstruction coordinate.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier ledger exhaustion]
\label{thm:metacic-normalization-frontier-ledger-exhaustion}
Every ledger read exported by an accepted $\MetaCICNormalizationFrontierUp$ packet
$$
F=(C,K,E,N,S,H,R,P,L)
$$
is exhausted by the candidate rows $C,K$ or the finished rows $E,N$, together with $\BHist$ carrier exposure, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $R$, $\Pkg$ provenance through $P$, the local $\NameCert$ row $L$, and the retained obstruction row $S$. A read bypassing both $C,K$ and $E,N$ is outside the packet.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.MetaCICNormalizationFrontierCarrier\_ledger\_exhaustion}
\begin{proof}
Start with the local obligation inventory. The candidate-evidence boundary names $C,K$, and the finished-normal boundary names $E,N$.

The ledger support rows do not supply a third positive evidence source. The row $H$ transports displayed fields, $R$ replays displayed consumer routes, $P$ records package provenance, and $L$ names the local certificate surface.

It remains to account for $S$. The obstruction row is carried alongside both positive routes, so exhaustion of the ledger does not solve or erase the subject-reduction boundary. Therefore any ledger read outside $C,K$ and $E,N$ has no accepted normalization-evidence coordinate in the packet.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier non-escape]
\label{thm:metacic-normalization-frontier-nonescape}
An accepted $\MetaCICNormalizationFrontierUp$ packet exports no blanket strong-normalization theorem for all empty-context typed closed MetaCIC terms, no full closed consistency theorem, and no erased subject-reduction transport. Any closed-normal consistency consumer route must factor through the candidate-evidence rows $C,K$ or through the finished-normal row $E$ before it reads $N$; a route that bypasses both is outside the carrier.
\end{theorem}
\begin{proof}
Project the carrier. The only normalization evidence rows are $C,K$ and $E$, and the only closed-normal endpoint row is $N$.

The replay and provenance rows $R$ and $P$ do not add new normalization evidence. They only expose the recorded candidate-evidence route, the finished-normal route, and the local endpoint route to a consumer.

The obstruction row $S$ is separate from those positive rows. Since the packet has no coordinate for global closed strong normalization, full closed consistency, or erased subject-reduction transport, none of those objects can be exported by its local certificate.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier redex boundary]
\label{thm:metacic-normalization-frontier-redex-boundary}
In every accepted $\MetaCICNormalizationFrontierUp$ packet
$$
F=(C,K,E,N,S,H,R,P,L),
$$
the candidate rows $C,K$ and the finished-normal rows $E,N$ determine a finite redex-boundary route for the inspected empty-context typed closed MetaCIC terms. Any read that turns candidate evidence into finished-normal endpoint use must pass through $C,K,E,N$ and retain the obstruction row $S$ as a displayed coordinate, with replay and provenance supplied only by $H,R,P,L$.

The route is a BEDC frontier route, not a blanket strong-normalization theorem, not a closed consistency theorem, and not an erased subject-reduction transport.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.MetaCICNormalizationFrontierCarrier\_redex\_boundary}
\begin{proof}
Project the carrier in \autoref{def:metacic-normalization-frontier-carrier}. The rows $C,K,E,N,S,H,R,P,L$ are the finite packet, and $S$ is listed separately from the positive candidate and finished-normal evidence rows.

Apply \autoref{thm:metacic-normalization-frontier-namecert-obligations}. Its candidate-evidence boundary forces candidate-mediated reads through $C,K$, while its finished-normal boundary places $E$ before $N$.

Now use \autoref{thm:metacic-normalization-frontier-nonescape}. Since the packet exports no blanket strong-normalization theorem, no full closed consistency theorem, and no erased subject-reduction transport, the redex boundary remains exactly the displayed finite route.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier fuel route]
\label{thm:metacic-normalization-frontier-fuel-route}
Every bounded replay of an accepted $\MetaCICNormalizationFrontierUp$ packet has a finite fuel route from candidate evidence $C,K$ to finished-normal evidence $E,N$, with the obstruction row $S$ carried alongside the replay rows $H,R,P,L$. The fuel route may be consumed by closed-normal downstream packets only through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates of
$$
F=(C,K,E,N,S,H,R,P,L).
$$

It exports no unbounded normalization schedule, no global subject-reduction proof, and no closed consistency theorem.
\end{theorem}
\begin{proof}
Start from \autoref{def:metacic-normalization-frontier-carrier}. The packet is finite, so a bounded replay reads only the named carrier rows and cannot synthesize an additional normalization schedule.

Apply the handoff clauses in \autoref{thm:metacic-normalization-frontier-namecert-obligations}. Candidate evidence enters through $C,K$, finished-normal endpoint use enters through $E,N$, and downstream closed-normal use must replay through $R$ with provenance $P$ and local naming row $L$.

Use \autoref{thm:metacic-normalization-frontier-obstruction-ledger} for the row $S$. The obstruction is transported as a separate coordinate and is not discharged by the positive evidence rows.

Finally apply \autoref{thm:metacic-normalization-frontier-nonescape}. The finite replay route therefore remains a fuel route inside the packet and does not export unbounded normalization, global subject reduction, or closed consistency.
\end{proof}
