\begin{theorem}[MetaCIC normalization frontier closed-candidate readback exhaustion]
\label{thm:metacic-normalization-frontier-closed-candidate-readback-exhaustion}
For every accepted $\MetaCICNormalizationFrontierUp$ packet
$$
F=(C,K,E,N,S,H,R,P,L),
$$
closed-candidate readback is exhausted by the candidate evidence row $C$, the closed-candidate row $K$, displayed replay $R$, provenance $P$, and the local $\NameCert_{\MetaCICNormalizationFrontierUp}$ row $L$. A root reader cannot obtain closed-candidate evidence from $E,N,S,H$ or from any host normalization, scheduler, quotient-equality, or closed-consistency surface outside the displayed packet.
\end{theorem}
\begin{proof}
Start with the NameCert obligation rows of \autoref{thm:metacic-normalization-frontier-namecert-obligations}. They attach candidate evidence to the displayed carrier and separate it from finished-normal evidence, obstruction transport, and external host normalization.

Next project the root candidate gate. Theorem~\ref{thm:metacic-normalization-frontier-root-candidate-gate-projection} identifies the candidate read with $C,K$ before any replay, provenance, or local naming support can be used.

Finally add the consumer support rows. Theorem~\ref{thm:metacic-normalization-frontier-root-normal-endpoint-route-exhaustion} keeps endpoint use on the distinct $E,N,R,P,L$ route, while Theorem~\ref{thm:metacic-normalization-frontier-root-obstruction-route-separation} leaves $S$ visible but unavailable as positive candidate evidence. Thus closed-candidate readback is exhausted by $C,K,R,P,L$ and by no unlisted source.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.MetaCICNormalizationFrontierCarrier\_closed\_candidate\_readback\_exhaustion}

\begin{theorem}[MetaCIC normalization frontier finished-endpoint use totality]
\label{thm:metacic-normalization-frontier-finished-endpoint-use-totality}
For every accepted $\MetaCICNormalizationFrontierUp$ packet
$$
F=(C,K,E,N,S,H,R,P,L),
$$
finished endpoint use is total exactly over the finished-normal evidence row $E$, the normal-endpoint row $N$, displayed replay $R$, provenance $P$, and the local $\NameCert_{\MetaCICNormalizationFrontierUp}$ row $L$. The endpoint route may consult the candidate gate only through the already displayed $C,K$ boundary, and it has no bypass through obstruction transport, host reachability, scheduler progress, or erased subject-reduction transport.
\end{theorem}
\begin{proof}
First read the endpoint-facing obligations. Theorem~\ref{thm:metacic-normalization-frontier-namecert-obligations} places finished-normal evidence before endpoint use and keeps both rows under the same local certificate surface.

Now follow the root endpoint route. Theorem~\ref{thm:metacic-normalization-frontier-root-normal-endpoint-route-exhaustion} exhausts endpoint access by $E,N,R,P,L$, so no finished endpoint can be consumed before those support rows are visible.

It remains to rule out hidden positive sources. Theorem~\ref{thm:metacic-normalization-frontier-root-candidate-gate-projection} confines candidate consultation to $C,K$, and Theorem~\ref{thm:metacic-normalization-frontier-root-obstruction-route-separation} keeps $S$ transported rather than consumed. Hence endpoint use is total over $E,N,R,P,L$ without importing host reachability, scheduler progress, or erased subject-reduction transport.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier obstruction-visible transport]
\label{thm:metacic-normalization-frontier-obstruction-visible-transport}
For every accepted $\MetaCICNormalizationFrontierUp$ packet
$$
F=(C,K,E,N,S,H,R,P,L),
$$
transport of the obstruction row keeps $S$ visible under componentwise $\hsame$ transport $H$, displayed replay $R$, provenance $P$, and the local naming row $L$. Such transport can accompany candidate readback through $C,K$ and finished-endpoint use through $E,N,R,P,L$, but it cannot turn $S$ into positive normalization evidence, closed consistency, quotient-level term equality, or erased subject-reduction transport.
\end{theorem}
\begin{proof}
Begin with the local obligation surface. Theorem~\ref{thm:metacic-normalization-frontier-namecert-obligations} records $S$ as an obstruction row of the same packet that carries $C,K,E,N,H,R,P,L$.

Transport then follows the root separation rows. Theorem~\ref{thm:metacic-normalization-frontier-root-obstruction-route-separation} keeps $S$ alongside the candidate route through $C,K$ and the endpoint route through $E,N,R,P,L$.

Finally use the two positive route projections. Theorem~\ref{thm:metacic-normalization-frontier-root-candidate-gate-projection} gives the only closed-candidate readback route, and Theorem~\ref{thm:metacic-normalization-frontier-root-normal-endpoint-route-exhaustion} gives the only finished-endpoint route. Since neither route consumes $S$, obstruction-visible transport under $H,R,P,L$ cannot become positive normalization evidence or any of the excluded global objects.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier route readback public export]
\label{thm:metacic-normalization-frontier-route-readback-public-export}
Every public readback export of an accepted $\MetaCICNormalizationFrontierUp$
packet
$$
F=(C,K,E,N,S,H,R,P,L)
$$
factors through the closed-candidate route $C,K,R,P,L$, the finished endpoint
route $E,N,R,P,L$, and obstruction-visible transport $S,H,R,P,L$. The exported
surface has no route through host normalization, scheduler progress, quotient
equality, a closed-consistency shortcut, or erased subject-reduction transport.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:metacic-normalization-frontier-closed-candidate-readback-exhaustion}.
It identifies the closed-candidate public readback route as $C,K,R,P,L$ and
rules out host normalization, scheduler, quotient-equality, and
closed-consistency sources for that face.

Next apply
\autoref{thm:metacic-normalization-frontier-finished-endpoint-use-totality}.
The finished endpoint face is total only over $E,N,R,P,L$, with candidate
consultation confined to the already displayed $C,K$ boundary.

Finally apply
\autoref{thm:metacic-normalization-frontier-obstruction-visible-transport}.
The obstruction row $S$ remains visible only under $H,R,P,L$ and cannot become
positive normalization evidence, quotient equality, closed consistency, or
erased subject-reduction transport. Combining the three route rows gives the
whole public export surface.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.MetaCICNormalizationFrontierCarrier\_route\_readback\_public\_export}
