\begin{theorem}[MetaCIC normalization frontier root carrier rows]
\label{thm:metacic-normalization-frontier-root-carrier-rows}
Every root consumer of an accepted $\MetaCICNormalizationFrontierUp$ packet first reads exactly the finite carrier rows
$$
C,K,E,N,S,H,R,P,L.
$$
The rows are the candidate-evidence surface, the closed-candidate surface, the finished-normal evidence surface, the normal-endpoint surface, the obstruction row, the transport row, the replay row, the provenance row, and the local naming row of the root packet.
\end{theorem}
\begin{proof}
Project the carrier definition in \autoref{def:metacic-normalization-frontier-carrier}. It lists $F=(C,K,E,N,S,H,R,P,L)$ as the complete packet and gives no additional root-facing coordinate.

Apply the NameCert obligations of \autoref{thm:metacic-normalization-frontier-namecert-obligations}. Candidate reads enter through $C,K$, finished-normal reads enter through $E,N$, obstruction transport keeps $S$ separate, and closed-normal downstream use replays through $H,R,P,L$.

Finally use the fuel route of \autoref{thm:metacic-normalization-frontier-fuel-route}. Any root consumer that asks for a bounded replay remains inside those carrier rows before it can be consumed by a downstream closed-normal packet.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier root consumer non-escape]
\label{thm:metacic-normalization-frontier-root-consumer-nonescape}
No root consumer of an accepted $\MetaCICNormalizationFrontierUp$ packet can extract a blanket strong-normalization theorem, a closed consistency theorem, or erased subject-reduction transport from the rows $C,K,E,N,S,H,R,P,L$.
\end{theorem}
\begin{proof}
Start with \autoref{thm:metacic-normalization-frontier-root-carrier-rows}. It exhausts the root packet by the displayed carrier rows and leaves no hidden normalization, consistency, or erased-transport coordinate.

Use \autoref{thm:metacic-normalization-frontier-nonescape}. The chapter already separates candidate and finished-normal evidence from blanket strong normalization, full closed consistency, and erased subject-reduction transport.

Now apply \autoref{thm:metacic-normalization-frontier-redex-boundary} together with \autoref{thm:metacic-normalization-frontier-fuel-route}. The root consumer receives only a bounded redex-boundary and fuel route, with $S$ still displayed as an obstruction row, so none of the excluded global objects can be read from the packet.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier root candidate-gate projection]
\label{thm:metacic-normalization-frontier-root-candidate-gate-projection}
Every root consumer that asks the candidate gate of an accepted $\MetaCICNormalizationFrontierUp$ packet must project the finite $\BHist$ packet
$$
F=(C,K,E,N,S,H,R,P,L)
$$
through the candidate rows $C,K$ before it can use replay, provenance, or local naming support. The projection exposes no candidate evidence outside the displayed packet and leaves the obstruction row $S$ present as a separate row.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:metacic-normalization-frontier-root-carrier-rows}. It identifies $F=(C,K,E,N,S,H,R,P,L)$ as the whole root-facing carrier, so a root read has no unnamed candidate coordinate.

Apply the candidate-evidence boundary from \autoref{thm:metacic-normalization-frontier-namecert-obligations}. That boundary places candidate access through $C,K$ and attaches the read to the same local $\NameCert$ surface.

Use \autoref{thm:metacic-normalization-frontier-candidate-route} for the downstream support rows. It routes candidate consumption through $C,K,R,P,L$, while \autoref{thm:metacic-normalization-frontier-root-consumer-nonescape} rules out an external candidate source.

The obstruction row is controlled by \autoref{thm:metacic-normalization-frontier-obstruction-ledger}. Since $S$ is a named row of the same finite packet, the candidate-gate projection does not discharge it.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier root normal-endpoint route exhaustion]
\label{thm:metacic-normalization-frontier-root-normal-endpoint-route-exhaustion}
Every root consumer that reaches the normal endpoint of an accepted $\MetaCICNormalizationFrontierUp$ packet must route through the finite $\BHist$ packet
$$
F=(C,K,E,N,S,H,R,P,L)
$$
by the finished-normal evidence row $E$, the normal-endpoint row $N$, the replay row $R$, the provenance row $P$, and the local naming row $L$. There is no root endpoint route that bypasses $E,N,R,P,L$ or erases the obstruction row $S$.
\end{theorem}
\begin{proof}
Project the root carrier rows. The finite packet names $E,N,R,P,L$ as the endpoint-facing and support rows and provides no additional normal-endpoint coordinate.

Use the finished-normal boundary in \autoref{thm:metacic-normalization-frontier-namecert-obligations}. It places the finished evidence row $E$ before endpoint use through $N$ and keeps both rows under the local certificate interface.

Next apply \autoref{thm:metacic-normalization-frontier-finished-route} and \autoref{thm:metacic-normalization-frontier-root-normal-endpoint-handoff}. Together they force endpoint consumption through $E,N,R,P,L$ rather than through a free-standing closed-normal witness.

Finally invoke \autoref{thm:metacic-normalization-frontier-root-consumer-nonescape} and \autoref{thm:metacic-normalization-frontier-obstruction-retention}. They exclude a bypassing endpoint object and keep $S$ visible throughout the route.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier root obstruction-preserving NameCert triad]
\label{thm:metacic-normalization-frontier-root-obstruction-preserving-namecert-triad}
For an accepted $\MetaCICNormalizationFrontierUp$ packet, the root-facing $\NameCert$ surface presents exactly the obstruction-preserving triad of the candidate-gate projection through $C,K$, the normal-endpoint route through $E,N,R,P,L$, and the retained obstruction row $S$ inside the finite $\BHist$ packet
$$
F=(C,K,E,N,S,H,R,P,L).
$$
The triad is transported only by the displayed $\hsame$, $\Cont$, $\Pkg$, and local naming coordinates of the packet.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICNormalizationFrontierUp.MetaCICNormalizationFrontierRootObstructionPreservingNamecertTriad}
\begin{proof}
Start with the root carrier rows and the NameCert obligations. They place the local certificate over the same finite packet $F=(C,K,E,N,S,H,R,P,L)$ and do not supply a second certificate target.

Apply \autoref{thm:metacic-normalization-frontier-root-candidate-gate-projection} for the candidate side. It isolates the candidate gate at $C,K$ and leaves replay, provenance, and local naming support inside the displayed packet.

Apply \autoref{thm:metacic-normalization-frontier-root-normal-endpoint-route-exhaustion} for the endpoint side. It exhausts normal-endpoint access by $E,N,R,P,L$ and keeps the endpoint route within the same $\BHist$ packet.

It remains to track the obstruction row. Use \autoref{thm:metacic-normalization-frontier-obstruction-ledger} and \autoref{thm:metacic-normalization-frontier-root-consumer-nonescape}; together they keep $S$ as a retained row and prevent the triad from exporting blanket normalization, closed consistency, or erased subject-reduction transport.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier root candidate-endpoint coherence]
\label{thm:metacic-normalization-frontier-root-candidate-endpoint-coherence}
Any root consumer of an accepted $\MetaCICNormalizationFrontierUp$ packet that moves from the candidate rows $C,K$ to the endpoint rows $E,N$ preserves the same finite packet
$$
F=(C,K,E,N,S,H,R,P,L).
$$
The route cannot switch candidate evidence sources between the candidate gate and the normal endpoint.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:metacic-normalization-frontier-root-carrier-rows}. It identifies $F=(C,K,E,N,S,H,R,P,L)$ as the complete root-facing packet.

Apply \autoref{thm:metacic-normalization-frontier-root-candidate-gate-projection}. The candidate side enters through $C,K$ and attaches replay, provenance, and local naming to the same carrier rows.

Apply \autoref{thm:metacic-normalization-frontier-root-normal-endpoint-route-exhaustion}. The endpoint side reaches $E,N$ only through $E,N,R,P,L$ and has no second endpoint coordinate.

Finally use \autoref{thm:metacic-normalization-frontier-root-obstruction-preserving-namecert-triad} together with \autoref{thm:metacic-normalization-frontier-root-consumer-nonescape}. The triad transports the candidate and endpoint routes through the same $\hsame$, $\Cont$, $\Pkg$, and naming rows, while non-escape rules out an external candidate source.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier root obstruction route separation]
\label{thm:metacic-normalization-frontier-root-obstruction-route-separation}
For every root consumer of an accepted $\MetaCICNormalizationFrontierUp$ packet, the obstruction row $S$ is transported alongside both the candidate route through $C,K$ and the endpoint route through $E,N,R,P,L$. It is never consumed as positive normalization evidence.
\end{theorem}
\begin{proof}
Project the root carrier rows. The row $S$ is a named coordinate of the same finite packet as $C,K,E,N,R,P,L$.

Use \autoref{thm:metacic-normalization-frontier-root-candidate-gate-projection}. The candidate route leaves $S$ present as a separate row rather than discharging it.

Use \autoref{thm:metacic-normalization-frontier-root-normal-endpoint-route-exhaustion}. The endpoint route cannot bypass or erase $S$, because endpoint access is exhausted by $E,N,R,P,L$ inside the same packet.

The separation claim is then exactly the obstruction part of \autoref{thm:metacic-normalization-frontier-root-obstruction-preserving-namecert-triad}. Together with \autoref{thm:metacic-normalization-frontier-root-consumer-nonescape}, it prevents $S$ from being read as a blanket strong-normalization witness.
\end{proof}

\begin{theorem}[MetaCIC normalization frontier root closed-normal route totality]
\label{thm:metacic-normalization-frontier-root-closed-normal-route-totality}
Every closed-normal consumer route of an accepted $\MetaCICNormalizationFrontierUp$ root packet is exhausted by the candidate route, endpoint route, replay row $R$, provenance row $P$, local naming row $L$, and obstruction row $S$ of
$$
F=(C,K,E,N,S,H,R,P,L).
$$
There is no closed-normal root route outside those displayed rows.
\end{theorem}
\begin{proof}
Start with \autoref{thm:metacic-normalization-frontier-root-carrier-rows}. The root packet exposes no row beyond $C,K,E,N,S,H,R,P,L$.

Apply \autoref{thm:metacic-normalization-frontier-root-candidate-endpoint-coherence}. It prevents a closed-normal consumer from changing candidate evidence sources when moving from $C,K$ to $E,N$.

Apply \autoref{thm:metacic-normalization-frontier-root-obstruction-route-separation}. The obstruction row remains transported beside the candidate and endpoint routes and cannot be converted into positive normalization evidence.

Finally use \autoref{thm:metacic-normalization-frontier-root-obstruction-preserving-namecert-triad} and \autoref{thm:metacic-normalization-frontier-root-consumer-nonescape}. They exhaust the route by the displayed certificate triad and exclude blanket normalization, closed consistency, erased subject-reduction transport, or any hidden closed-normal endpoint.
\end{proof}
