\chapter{A Concrete Naming Certificate for $\CauchyCompletionStabilityUp$}
\label{ch:concrete-instances-cauchycompletionstability-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\CauchyCompletionStabilityUp$ packet isolates the finite stability route by which a modulus-indexed regular rational Cauchy read remains attached to the same terminal Real seal under accepted transport. It depends on the finite-window naming surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal seal of \autoref{ch:concrete-instances-real-namecert}, the explicit modulus packet of \autoref{ch:concrete-instances-realcauchymodulus-namecert}, and the located comparison boundary of \autoref{ch:concrete-instances-locatedreal-namecert}. The chapter records only the constructive L10 completion-stability route over those siblings.

\begin{definition}[CauchyCompletionStability carrier]
\label{def:cauchy-completion-stability-carrier}
A $\CauchyCompletionStabilityUp$ carrier is a finite $\BHist$ packet
$$
T=(M,S,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the modulus schedule that assigns each requested completion tolerance a finite threshold and radius budget;
\item $S$ is the $\StreamNameUp$ window family selected by the thresholds in $M$;
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the finite dyadic comparisons read on those windows;
\item $Q$ is the $\RegSeqRatUp$ readback row whose regularity is witnessed only through $M,S,D$;
\item $E$ is the terminal $\RealUp$ seal row reached after the modulus, window, tolerance, and regular-readback rows have been consumed;
\item $H$ records componentwise $\hsame$ transport for $M,S,D,Q,E$ and for the structural rows of the packet;
\item $C$ records the displayed $\Cont$ replay that rereads the same modulus schedule, StreamName windows, dyadic tolerance rows, RegSeqRat readback, Real seal, and transport ledger;
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionStabilityUp$, $\RealCauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\LocatedRealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CauchyCompletionStabilityUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient stream equality, host real equality, countable choice, trichotomy, a selected limit, open-cover compactness, or a general $\RealUp$ completeness theorem.
\end{definition}

\begin{theorem}[CauchyCompletionStability NameCert obligations]
\label{thm:cauchy-completion-stability-namecert-obligations}
The local $\NameCert_{\CauchyCompletionStabilityUp}$ surface for \autoref{def:cauchy-completion-stability-carrier} consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure: the accepted object is the packet $T=(M,S,D,Q,E,H,C,P,N)$ with no hidden completion coordinate;
\item classifier: each stability request is classified only by the displayed modulus schedule $M$, finite $\StreamNameUp$ windows $S$, dyadic tolerance ledger $D$, and regular readback row $Q$;
\item stability: the terminal $\RealUp$ seal $E$ remains attached to the same finite route whenever $H$ transports the displayed rows and $C$ replays the corresponding consumer path;
\item provenance: $P$ records exactly the sibling route through $\RealCauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, and $\LocatedRealUp$, while $N$ names the local packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is projection from the tuple $T=(M,S,D,Q,E,H,C,P,N)$. Every accepted coordinate is displayed, and the final coordinate is the local naming row.

The classifier is finite because a stability request first reads the threshold data in $M$, then the finite windows in $S$, then the dyadic tolerance ledger in $D$, and then the regular rational readback in $Q$. No classifier row can inspect a quotient stream or a host real equality proof.

Transport stability uses $H$ componentwise and then replays the same path through $C$. The replay returns to the rows $M,S,D,Q,E$, so the terminal Real seal is stable only along the displayed route.

The provenance and naming clauses follow from $P$ and $N$. Since the carrier contains no coordinate for countable choice, trichotomy, selected limits, open-cover compactness, or general Real completeness, the four obligation rows exhaust the local certificate surface.
\end{proof}

\begin{theorem}[CauchyCompletionStability cross-chapter scope]
\label{thm:cauchy-completion-stability-cross-chapter-scope}
Every export of an accepted $\CauchyCompletionStabilityUp$ packet is confined to the finite L10 completion-stability route
$$
M\longmapsto S\longmapsto D\longmapsto Q\longmapsto E\longmapsto(H,C,P,N).
$$
It exports no quotient stream equality, no host real equality, no countable-choice schedule, no trichotomy principle, no selected limit, no open-cover compactness principle, and no general $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Read the packet through the obligations of \autoref{thm:cauchy-completion-stability-namecert-obligations}. The only analytic route is the displayed sequence from the modulus schedule to the terminal Real seal.

The structural coordinates do not widen that route. The transport row $H$ and replay row $C$ preserve the same rows, while $P$ and $N$ only record provenance and local naming.

Inspecting the carrier of \autoref{def:cauchy-completion-stability-carrier} shows that the excluded principles have no row from which they could be read. Therefore the packet exports exactly the finite completion-stability route and none of the listed ambient or classical principles.
\end{proof}

\begin{closurestatus}{\CauchyCompletionStabilityUp}
  \constructivestory{A $\CauchyCompletionStabilityUp$ packet is generated from a modulus schedule, finite $\StreamNameUp$ windows, a $\DyadicRatCoreUp$ tolerance ledger, a $\RegSeqRatUp$ readback row, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-stability-carrier}, \autoref{thm:cauchy-completion-stability-namecert-obligations}, and \autoref{thm:cauchy-completion-stability-cross-chapter-scope} seed the finite completion-stability route across StreamName, DyadicRatCore, RegSeqRat, Real, RealCauchyModulus, and LocatedReal siblings.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient stream equality, host real equality, countable choice, trichotomy, selected limits, open-cover compactness, general $\RealUp$ completeness, or a Lean theorem.}
  \upgradepath{A formal route can encode the nine-row carrier and prove the NameCert obligation and cross-chapter scope theorems under BEDC.Derived.CauchyCompletionStabilityUp.}
\end{closurestatus}
