\chapter{Window-Six Private/Shared Decoration NameCert Construction}
\label{ch:concrete-instances-window-six-private-shared-decoration-namecert}
\origin{ai}

The $\WindowSixPrivateSharedDecorationUp$ packet realizes the private/shared decoration enumeration of \autoref{thm:philosophy-private-shared-decoration-enumeration} inside the DNA window-six boundary-tile source of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}. It consumes the boundary-tile packet of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the six-boundary coverage packet of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the boundary-trigger closure packet of \autoref{ch:concrete-instances-dna-boundary-trigger-closure-namecert}, and the trigger-threshold packet of \autoref{ch:concrete-instances-dna-window-six-trigger-threshold-namecert}. The packet records private blocks, shared row sets, trigger coverage, decoration counts, transport, replay, provenance, and local naming as finite rows; it is not a biological mechanism, stochastic fitness model, hidden enumeration oracle, or quotient codon semantics.

\begin{definition}[Window-six private/shared decoration carrier]\label{def:window-six-private-shared-decoration-carrier}
A $\WindowSixPrivateSharedDecorationUp$ carrier is a finite $\BHist$ packet
$$
W=(B,S,T,E,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the private-block row, recording the nonempty private coordinate blocks attached to each accepted decorated support.
\item $S$ is the shared-row-set ledger, assigning every shared coordinate to a finite row set of size at least two.
\item $T$ is the trigger-coverage row, read through the carried DNA boundary-tile, six-boundary coverage, closure, and threshold packets.
\item $E$ is the decoration-count row, recording the finite enumeration factors from the source private/shared theorem.
\item $D$ is the defect ledger, recording row-set-size contribution to the defect-refined decoration polynomial.
\item $H$ records componentwise $\hsame$ transport for private blocks, shared row sets, trigger coverage, decoration count, defect ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a window-six decoration request through $B,S,T,E,D,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\WindowSixPrivateSharedDecorationUp$, $\DnaWindowSixBoundaryTileUp$, $\SixBoundaryTileCoverageUp$, $\DnaBoundaryTriggerClosureUp$, $\DNAWindowSixTriggerThresholdUp$, the source theorem of \autoref{thm:philosophy-private-shared-decoration-enumeration}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\WindowSixPrivateSharedDecorationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,S,T,E,D,H,C,P,N$. It has no coordinate for biological mechanism, stochastic evolutionary semantics, quotient codon equality, hidden global enumeration, or an unrecorded trigger oracle.
\end{definition}

\begin{theorem}[Window-six private/shared decoration obligations]\label{thm:window-six-private-shared-decoration-obligations}
For every accepted $\WindowSixPrivateSharedDecorationUp$ carrier
$$
W=(B,S,T,E,D,H,C,P,N),
$$
the local $\NameCert_{\WindowSixPrivateSharedDecorationUp}$ surface consists exactly of private-block admission through $B$, shared-row-set admission through $S$, trigger-coverage exposure through $T$, decoration-count exposure through $E$, defect-ledger exposure through $D$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:window-six-private-shared-decoration-carrier}. The private block, shared row set, trigger coverage, decoration count, defect ledger, transport, replay, provenance, and naming data are precisely $B,S,T,E,D,H,C,P,N$.

The rows $B,S$ enforce the private/shared split: each accepted support has a displayed private block, and each shared coordinate is assigned to a row set of size at least two. The trigger-coverage row $T$ then ties those rows to the existing window-six boundary, coverage, closure, and threshold packets.

The rows $E,D$ record the enumeration and defect data used by the source theorem. Finally $H,C,P,N$ preserve, replay, source, and name the same finite route. Since the carrier has no additional coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Window-six private/shared decoration enumeration handoff]\label{thm:window-six-private-shared-decoration-enumeration-handoff}
Every accepted $\WindowSixPrivateSharedDecorationUp$ consumer that reads a private/shared window-six decoration factors through
$$
\DnaWindowSixBoundaryTileUp,\ \SixBoundaryTileCoverageUp,\ \DnaBoundaryTriggerClosureUp,\ \DNAWindowSixTriggerThresholdUp
\longmapsto
B,S,T,E,D,H,C,P,N .
$$
The exported object is a finite private/shared row-set ledger with trigger-coverage and decoration-count rows. It is not a biological model, a quotient codon space, a hidden enumeration oracle, or an unrestricted trigger-search theorem.
\end{theorem}
\begin{proof}
Read the accepted carrier through \autoref{def:window-six-private-shared-decoration-carrier}. The private and shared ledgers $B,S$ supply the displayed row-set split before a decoration count is exposed.

Next use $T$ to route the split through the boundary-tile, six-boundary coverage, boundary-trigger closure, and trigger-threshold siblings. This prevents a decoration request from bypassing the window-six trigger-coverage surface.

The enumeration row $E$ and defect row $D$ then record the finite count and defect-polynomial data from the source theorem. The structural rows $H,C,P,N$ transport, replay, source, and locally name the same rows.

Therefore every accepted consumer receives the finite packet described in the theorem, rather than biological semantics, quotient codon equality, hidden enumeration, or unrestricted trigger search.
\end{proof}

\falsifiablePrediction{Every accepted $\WindowSixPrivateSharedDecorationUp$ packet must expose private-block, shared-row-set, trigger-coverage, decoration-count, hsame, Cont, Pkg, and NameCert rows before it can export a private/shared window-six decoration read.}

\independenceWitness{dna-window-six-boundary-tile, six-boundary-tile-coverage, dna-boundary-trigger-closure, dna-window-six-trigger-threshold: $\WindowSixPrivateSharedDecorationUp$ is not bijective to any listed sibling because the private/shared row-set ledger jointly carries private blocks, shared row sets, trigger coverage, decoration counts, defect rows, transport, replay, provenance, and local naming.}

The Lean TasteGate route for \texttt{BEDC.Derived.WindowSixPrivateSharedDecorationUp.TasteGate} must provide explicit $\Nontrivial\ \WindowSixPrivateSharedDecorationUp$ and $\FieldFaithful\ \WindowSixPrivateSharedDecorationUp$ instances preserving $B,S,T,E,D,H,C,P,N$ as separate displayed fields.

\closureat{WindowSixPrivateSharedDecorationUp}{seedStr}

\begin{closurestatus}{\WindowSixPrivateSharedDecorationUp}
  \constructivestory{A $\WindowSixPrivateSharedDecorationUp$ packet is generated from private-block rows, shared-row-set ledgers, trigger-coverage rows, decoration-count rows, defect ledgers, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:window-six-private-shared-decoration-carrier}, \autoref{thm:window-six-private-shared-decoration-obligations}, and \autoref{thm:window-six-private-shared-decoration-enumeration-handoff} seed the finite private/shared window-six decoration packet over displayed boundary, coverage, closure, threshold, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological mechanism, stochastic evolution, quotient codon equality, hidden global enumeration, unrestricted trigger search, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, private-block exposure, shared-row-set arity, trigger-coverage routing, decoration-count exposure, defect-ledger exposure, TasteGate nontriviality, field faithfulness, transport, replay, provenance, and local naming for BEDC.Derived.WindowSixPrivateSharedDecorationUp.}
\end{closurestatus}
