\begin{theorem}[Diagonal tail selector root cofinal admission]
\label{thm:diagonal-tail-selector-root-cofinal-admission}
Let
$$
G=(R,n,\mu,k,W,D,T,S,H,C,P,N)
$$
be an accepted $\DiagonalTailSelectorUp$ packet. Before any selector read is
performed, the root admission surface exposes the source regular row $R$, the
precision request $n$, the displayed modulus $\mu$, the selected threshold
index $k$, the finite stream window $W$, the dyadic readback row $D$, the
tail-selector handoff $T$, the Real seal row $S$, the componentwise $\hsame$
rows $H$, the displayed $\Cont$ routes $C$, the $\Pkg$ provenance row $P$,
and the local $\NameCert$ row $N$. No selector step may consult a row outside
this displayed packet.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonalTailSelectorUp.DiagonalTailSelectorCarrier\_root\_cofinal\_admission}
\begin{proof}
Project the accepted carrier of $\DiagonalTailSelectorUp$. Its root packet is
the tuple $G$, and the selector coordinate is read only after the visible
source, modulus, window, readback, tail, seal, transport, continuation,
provenance, and naming rows have been fixed.

Apply \autoref{thm:diagonal-tail-selector-window-admission} to the first
selector read. The theorem routes the read through $\mu$ at $n$ and then
through $W$ and $D$, so no hidden source row is available before the
cofinal index is selected.
\end{proof}

\begin{theorem}[Diagonal tail selector root budget handoff]
\label{thm:diagonal-tail-selector-root-budget-handoff}
For every accepted $\DiagonalTailSelectorUp$ packet $G$, the selected
cofinal row factors through the visible L10 route
$$
\LimitSelectorUp,\quad
\RegularCauchyTailSelectorUp,\quad
\StreamNameUp,\quad
\DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad
\RealUp.
$$
The factorization consumes only the rows exposed by
\autoref{thm:diagonal-tail-selector-root-cofinal-admission}: the cofinal
index comes from the displayed selector/modulus budget, the finite window and
dyadic readback supply the stream evidence, the regular Cauchy tail row
transports the shared threshold, and the Real row receives only the resulting
finite seal packet.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonalTailSelectorUp.DiagonalTailSelectorRootBudgetHandoff}
\begin{proof}
Start with the root admission surface of
\autoref{thm:diagonal-tail-selector-root-cofinal-admission}. The selector row
is already tied to $R,n,\mu,k,W,D,T,S,H,C,P,N$, so any downstream budget
handoff must reuse these rows.

Next apply \autoref{thm:diagonal-tail-selector-limit-handoff},
\autoref{thm:diagonal-tail-selector-source-modulus-route-exactness}, and
\autoref{thm:diagonal-tail-selector-tail-meet-consumption-scope}. Together
they route the cofinal selection through the displayed limit selector,
regular tail-selector, stream-name, dyadic readback, regular sequence, and
Real seal rows.

It remains to identify the budget boundary. The handoff contains no row
besides the root packet and the named L10 consumers, so the selected cofinal
row factors through exactly the displayed route.
\end{proof}

\begin{theorem}[Diagonal tail selector root seal non-escape]
\label{thm:diagonal-tail-selector-root-seal-nonescape}
The root budget route of an accepted $\DiagonalTailSelectorUp$ packet exports
no quotient stream, countable-choice selector, host-selected limit, host real
equality, hidden tail oracle, or ambient completeness row. Its public output
is only the finite cofinal-window, dyadic-readback, regular-tail, Real-seal,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface named by the root packet.
\end{theorem}
\begin{proof}
Use \autoref{thm:diagonal-tail-selector-root-budget-handoff} to place every
selected cofinal row on the displayed L10 route. Each consumer receives only
the rows exposed by the accepted root packet.

Now apply \autoref{thm:diagonal-tail-selector-real-seal-source-exhaustion}
and \autoref{thm:diagonal-tail-selector-tail-meet-consumption-scope}. These
results exhaust the Real seal and tail-meet consumption boundaries and list
the objects that cannot be exported through them.

The remaining rows $H,C,P,N$ are structural transport, continuation,
provenance, and naming rows. They record the visible finite route rather than
adding quotient streams, countable choice, host limits, host equality, hidden
tail oracles, or completeness data.
\end{proof}

\begin{theorem}[Diagonal tail selector cofinal budget replay]
\label{thm:diagonal-tail-selector-cofinal-budget-replay}
For every accepted $\DiagonalTailSelectorUp$ packet
$$
G=(R,n,\mu,k,W,D,T,S,H,C,P,N),
$$
the same cofinal budget is replayed through
$$
\LimitSelectorUp,\quad
\RegularCauchyTailSelectorUp,\quad
\StreamNameUp,\quad
\DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad
\RealUp.
$$
The replay first reads the root admission rows $R,n,\mu,k,W,D,T,S,H,C,P,N$,
then consumes the selected cofinal index and finite window through the
displayed L10 route, and finally checks compatibility with the tail budget of
\autoref{thm:diagonal-tail-selector-tail-budget-compatibility}. No consumer
may replace this replay by a fresh selector, quotient stream, hidden tail row,
or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonalTailSelectorUp.DiagonalTailSelectorCarrier\_cofinal\_budget\_replay}
\begin{proof}
Begin with \autoref{thm:diagonal-tail-selector-root-cofinal-admission}. It
projects the accepted packet $G$ and fixes the source regular row, precision
request, modulus, threshold, finite window, dyadic readback, tail handoff,
Real seal, transport, route, provenance, and naming rows before any selector
read is performed.

Apply \autoref{thm:diagonal-tail-selector-root-budget-handoff}. The selected
cofinal row is routed through the displayed L10 consumers
$\LimitSelectorUp$, $\RegularCauchyTailSelectorUp$, $\StreamNameUp$,
$\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ using only the rows named
by the root packet.

Now use
\autoref{thm:diagonal-tail-selector-tail-budget-compatibility}. The public
budget source and the tail budget consume the same rows
$R,n,\mu,k,W,D,H,C,P,N$ before $S$ is read, so the replay cannot fork into a
separate selector or hidden tail source.

Finally invoke \autoref{thm:diagonal-tail-selector-root-seal-nonescape}. The
root seal has no coordinate for quotient streams, countable choice,
host-selected limits, host real equality, hidden tail oracles, or ambient
completeness. Hence the replay is exactly the displayed cofinal budget route.
\end{proof}

\begin{theorem}[Diagonal tail selector public root replay package]
\label{thm:diagonal-tail-selector-public-root-replay-package}
Every accepted $\DiagonalTailSelectorUp$ packet
$$
G=(R,n,\mu,k,W,D,T,S,H,C,P,N)
$$
whose public budget source reads the root cofinal admission row of
\autoref{thm:diagonal-tail-selector-root-cofinal-admission}, the root budget
handoff row of \autoref{thm:diagonal-tail-selector-root-budget-handoff}, and
the cofinal budget replay row of
\autoref{thm:diagonal-tail-selector-cofinal-budget-replay} exports exactly the
finite route
$$
R,n,\mu,k,W,D,T,S,H,C,P,N
$$
through
$$
\LimitSelectorUp,\quad
\RegularCauchyTailSelectorUp,\quad
\StreamNameUp,\quad
\DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad
\CauchyLimitSealUp,\quad
\RealUp.
$$
The package exports no quotient stream, selected host limit, countable-choice
schedule, host real equality, ambient completeness principle, or hidden tail
oracle.
\end{theorem}
\begin{proof}
Project the root cofinal admission row. It fixes the accepted packet
$G=(R,n,\mu,k,W,D,T,S,H,C,P,N)$ as the full carrier inventory available to the
public budget source.

Apply the root budget handoff row next. The handoff places the selected cofinal
read on the displayed L10 factorization through $\LimitSelectorUp$,
$\RegularCauchyTailSelectorUp$, $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$.

Use the cofinal budget replay row to reuse the same finite budget through that
consumer chain. The replay does not allocate a second selector, stream, or host
limit row; it only replays the rows already named by the root packet.

Finally combine the public budget export and non-escape rows. They identify
the exported object as the finite route above and exclude quotient streams,
selected host limits, countable-choice schedules, host real equality, ambient
completeness, and hidden tail oracles from the public replay package.
\end{proof}

\begin{theorem}[Diagonal tail selector budget readback non-escape]
\label{thm:diagonal-tail-selector-budget-readback-nonescape}
The readback exported by the cofinal budget replay of
\autoref{thm:diagonal-tail-selector-cofinal-budget-replay} is only the finite
root packet
$$
R,n,\mu,k,W,D,T,S,H,C,P,N
$$
together with its displayed L10 consumer route. It exports no quotient stream,
choice selector, host-selected limit, host real equality, hidden tail oracle,
or ambient completeness row.
\end{theorem}
\begin{proof}
Use \autoref{thm:diagonal-tail-selector-cofinal-budget-replay} to put the
readback on the same cofinal budget route through $\LimitSelectorUp$,
$\RegularCauchyTailSelectorUp$, $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and $\RealUp$.

The root packet contributes exactly the rows listed in
\autoref{thm:diagonal-tail-selector-root-cofinal-admission}. The budget
handoff of \autoref{thm:diagonal-tail-selector-root-budget-handoff} then
consumes those rows without adding any external selector coordinate.

For the tail-facing part, apply
\autoref{thm:diagonal-tail-selector-tail-budget-compatibility}. It identifies
the shared finite budget consumed by the schedule and tail-meet routes before
the Real seal row is read.

The excluded objects are precisely the objects ruled out by
\autoref{thm:diagonal-tail-selector-root-seal-nonescape}. Since the readback
has no row beyond the accepted packet and its displayed L10 route, none of
them can be exported.
\end{proof}

\begin{theorem}[Diagonal tail selector terminal budget determinacy]
\label{thm:diagonal-tail-selector-terminal-budget-determinacy}
Let
$$
G=(R,n,\mu,k,W,D,T,S,H,C,P,N)
$$
be an accepted $\DiagonalTailSelectorUp$ packet. Any terminal $\RealUp$
consumer, and any completion-facing consumer that reads the selected cofinal
row, factors through the same displayed root budget route
$$
R,n,\mu,k,W,D,T,S,H,C,P,N
$$
and then through
$$
\LimitSelectorUp,\quad
\RegularCauchyTailSelectorUp,\quad
\StreamNameUp,\quad
\DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad
\RealUp.
$$
No such consumer may replace the terminal budget by a fresh selector,
quotient stream, host-selected limit, hidden tail row, or ambient
completeness witness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:diagonal-tail-selector-root-cofinal-admission}. It
fixes the accepted packet $G$ as the only root surface available before the
selected cofinal row is read.

Apply \autoref{thm:diagonal-tail-selector-root-budget-handoff}. The selected
cofinal row is handed to the terminal route through the displayed L10
consumer chain, so a Real or completion-facing read has no second budget
coordinate.

Replay the route with
\autoref{thm:diagonal-tail-selector-cofinal-budget-replay}. The replay uses
the same root rows and the same named consumers, and
\autoref{thm:diagonal-tail-selector-tail-budget-compatibility} identifies the
tail-facing threshold with that displayed budget.

Finally apply
\autoref{thm:diagonal-tail-selector-budget-readback-nonescape}. Since the
terminal readback exports only $R,n,\mu,k,W,D,T,S,H,C,P,N$ and its displayed
L10 route, it cannot substitute a fresh selector, quotient stream,
host-selected limit, hidden tail row, or ambient completeness witness.
\end{proof}

\begin{theorem}[Diagonal tail selector root formal target surface]
\label{thm:diagonal-tail-selector-root-formal-target-surface}
Let
$$
G=(R,n,\mu,k,W,D,T,S,H,C,P,N)
$$
be an accepted $\DiagonalTailSelectorUp$ packet. The Lean-facing formal target
surface for $\RealUp$ and completion-facing consumers is exactly the finite
packet
$$
R,n,\mu,k,W,D,T,S,H,C,P,N
$$
together with the displayed route through
$$
\LimitSelectorUp,\quad
\RegularCauchyTailSelectorUp,\quad
\StreamNameUp,\quad
\DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad
\CauchyLimitSealUp,\quad
\RealUp.
$$
It contains no quotient stream, countable choice operator, host-selected
limit, host real equality, hidden tail oracle, or ambient completeness
principle.
\end{theorem}
\begin{proof}
Begin with
\autoref{thm:diagonal-tail-selector-root-cofinal-admission}. It fixes the
accepted root surface to the coordinates of $G$ and the named cofinal route,
so every downstream consumer starts from the same finite packet.

Use \autoref{thm:diagonal-tail-selector-root-budget-handoff} to hand those
coordinates to the consumer route. Then apply
\autoref{thm:diagonal-tail-selector-cofinal-budget-replay} to replay the same
budget through $\LimitSelectorUp$, $\RegularCauchyTailSelectorUp$,
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$,
$\CauchyLimitSealUp$, and $\RealUp$.

The public packaging is supplied by
\autoref{thm:diagonal-tail-selector-public-root-replay-package}. The
readback boundary of
\autoref{thm:diagonal-tail-selector-budget-readback-nonescape} then rules out
quotient streams, countable choice, host-selected limits, host real equality,
hidden tail oracles, and ambient completeness as exported coordinates.

Finally, \autoref{thm:diagonal-tail-selector-terminal-budget-determinacy}
identifies every terminal Real or completion-facing read with that same
route. Carrier-coordinate exhaustion leaves exactly the listed packet and
route, with no remaining coordinate from which an excluded object could be
read.
\end{proof}

\begin{theorem}[Diagonal tail selector terminal cofinal route exhaustion]
\label{thm:diagonal-tail-selector-terminal-cofinal-route-exhaustion}
Let
$$
G=(R,n,\mu,k,W,D,T,S,H,C,P,N)
$$
be an accepted $\DiagonalTailSelectorUp$ packet. Every terminal $\RealUp$ or
$\CompletionUp$ consumer of the cofinal selector route is exhausted by the
displayed packet $G$ together with the L10 route through
$$
\LimitSelectorUp,\quad
\RegularCauchyTailSelectorUp,\quad
\StreamNameUp,\quad
\DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad
\CauchyLimitSealUp,\quad
\RealUp.
$$
No quotient stream, countable-choice selector, host-selected limit, host real
equality, hidden tail oracle, or ambient completeness row can be recovered from
such a terminal consumer.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:diagonal-tail-selector-root-cofinal-admission} and
\autoref{thm:diagonal-tail-selector-root-budget-handoff}. These identify the
accepted root surface with the displayed coordinates of $G$ and send that same
finite budget into the terminal route.

Next use
\autoref{thm:diagonal-tail-selector-cofinal-budget-replay}. The replay keeps
the cofinal route on the named L10 spine through $\LimitSelectorUp$,
$\RegularCauchyTailSelectorUp$, $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$.

The public surface is then the one supplied by
\autoref{thm:diagonal-tail-selector-public-root-replay-package}. By
\autoref{thm:diagonal-tail-selector-budget-readback-nonescape}, a terminal
readback from this surface cannot export a quotient stream, countable-choice
selector, host-selected limit, host real equality, hidden tail oracle, or
ambient completeness row.

Finally apply
\autoref{thm:diagonal-tail-selector-terminal-budget-determinacy} and
\autoref{thm:diagonal-tail-selector-root-formal-target-surface}. They identify
every terminal $\RealUp$ or $\CompletionUp$ consumer with the same packet and
route. Carrier-coordinate exhaustion therefore leaves exactly the displayed
coordinates and no remaining carrier from which one of the excluded objects
could be read.
\end{proof}
