\section{Singleton Cont History Instance for \texorpdfstring{$\CommRingUp$}{CommRingUp}}
\label{sec:commring-singleton-cont-history-instance}

\begin{definition}[CommRingUp singleton Cont history instance]
\label{def:commring-singleton-cont-history-instance}
Let $A_{\emp}$ be the singleton $\mathsf{BHist}$ carrier whose only accepted
endpoint is $\emp$, and let $R_{\emp}$ be the classifier that identifies two
accepted endpoints exactly when both are $\hsame$ to $\emp$. Define addition
and multiplication by the same concrete continuation endpoint:
$$
x+_{\emp}y:=\Cont(x,y,\emp),
\qquad
x\cdot_{\emp}y:=\Cont(x,y,\emp).
$$
The zero and one rows are both the displayed empty endpoint $\emp$. The
package ledger records the two input endpoints, the append read, the output
endpoint, and the singleton classifier witness returning the output to
$\emp$.
\end{definition}

\begin{theorem}[Singleton Cont commutative-ring laws]
\label{thm:commring-singleton-cont-commutative-laws}
The carrier $A_{\emp}$ with classifier $R_{\emp}$, operations
$+_{\emp}$ and $\cdot_{\emp}$, and constants $0_{\emp}=1_{\emp}=\emp$
satisfies the $\CommRingUp$ law surface. Additive group laws, multiplicative
monoid laws, distributivity, and multiplicative commutativity all read back to
the singleton endpoint under $\hsame$.
\end{theorem}
\begin{proof}
Every accepted input endpoint is classified with $\emp$ by $R_{\emp}$. The
continuation endpoint for either operation is therefore an accepted singleton
endpoint and is again classified with $\emp$.

For associativity, identity, and inverse rows on addition, both sides of each
law are continuation endpoints whose source and target histories classify to
$\emp$. The additive inverse operation is the constant empty endpoint, so the
left and right inverse rows also reduce to the same readback.

The multiplicative identity, associativity, and commutativity rows are
identical endpoint-readback arguments, because multiplication uses the same
concrete continuation endpoint and its unit is also $\emp$.

For distributivity, expand both sides as finite continuation endpoints over
accepted singleton histories. Each displayed endpoint returns to $\emp$ under
$R_{\emp}$, so the two sides classify together. Repacking these rows gives the
commutative-ring law surface without quantified abstract operators.
\end{proof}

\begin{theorem}[CommRingUp singleton Cont schema source]
\label{thm:commring-singleton-cont-schema-unlock}
The singleton Cont history instance of
\autoref{def:commring-singleton-cont-history-instance} is a concrete
$\mathsf{BHist}$-anchored source for $\CommRingUp$. Future formal targets may
use this carrier, classifier, operation table, constants, and endpoint ledger
as the ground source instead of proving the commutative-ring schema from
arbitrary carrier parameters and abstract binary operations.
\end{theorem}
\begin{proof}
The definition supplies all rows demanded by the commutative-ring source:
carrier, classifier, addition, multiplication, zero, one, and package
provenance. The preceding theorem supplies the finite law rows for the same
objects.

Thus a consumer can cite the singleton packet directly. No external carrier,
parameter family, host equality, or abstract operation table is needed to
obtain a concrete $\CommRingUp$ source.
\end{proof}
