\chapter{A Concrete Naming Certificate for $\CauchySubsequenceSelectorUp$}
\label{ch:concrete-instances-cauchy-subsequence-selector-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy sequences, the $\CauchySubsequenceSelectorUp$ packet records the finite selector schedule by which a regular rational Cauchy name may expose a monotone subsequence corridor before a Real or Completion consumer reads the terminal seal. It sits after the regular rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}, and the Cauchy hub of \autoref{ch:concrete-instances-cauchysequencespace-namecert}. The packet gives diagonal, tail, and completion-facing chapters a named L10 selector object; it is not a quotient of streams, a selected host limit, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy subsequence selector carrier]
\label{def:cauchy-subsequence-selector-carrier}
A $\CauchySubsequenceSelectorUp$ carrier is a finite $\BHist$ packet
$$
S=(R,W,M,G,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RegSeqRatUp$ source row whose rational reads are being sampled.
\item $W$ is the $\StreamNameUp$ finite-window row exposing the source observations consumed by the selector.
\item $M$ is the monotone selector row, recording a finite schedule of indices and the strict order checks between successive selected positions.
\item $G$ is the Cauchy-gap ledger, recording the tail comparison requests that make the selected windows compatible with the source Cauchy evidence.
\item $E$ is the terminal $\RealUp$ seal row, available only after $R,W,M,G$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source, window, monotone selector, Cauchy-gap, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a subsequence request through $R,W,M,G,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchySubsequenceSelectorUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchySubsequenceSelectorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,W,M,G,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, host real equality, countable choice, trichotomy, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Cauchy subsequence selector NameCert obligations]
\label{thm:cauchy-subsequence-selector-namecert-obligations}
For every accepted $\CauchySubsequenceSelectorUp$ carrier $S=(R,W,M,G,E,H,C,P,N)$, the local $\NameCert_{\CauchySubsequenceSelectorUp}$ surface consists exactly of carrier admission, selector monotonicity, $\StreamNameUp$ window coverage, Cauchy-gap compatibility, $\RegSeqRatUp$ handoff, $\RealUp$ seal non-escape, componentwise transport, displayed replay, package provenance, and local naming. Each obligation is read through the finite route
$$
R,W,M,G \longrightarrow E \longrightarrow H,C,P,N .
$$
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-subsequence-selector-carrier}. The packet first exposes the regular rational source $R$, the finite observation windows $W$, the monotone selector schedule $M$, and the Cauchy-gap ledger $G$.

Selector monotonicity is local to $M$. The window coverage obligation then reads $W$ at precisely the positions displayed by $M$, so every selected index has a finite $\StreamNameUp$ observation before any handoff is consumed.

The $\RegSeqRatUp$ handoff is the source row $R$ restricted along the displayed schedule and checked against the Cauchy-gap ledger $G$. The terminal seal $E$ is downstream of those rows, and it is only a $\RealUp$ seal for the displayed subsequence corridor.

Transport through $H$, replay through $C$, provenance $P$, and local naming $N$ preserve the same route. Since quotient stream equality, selected limits, host real equality, countable choice, trichotomy, and ambient Real completeness are absent from the carrier coordinates, no obligation can discharge outside the displayed finite packet.
\end{proof}

\begin{theorem}[Cauchy subsequence selector real handoff]
\label{thm:cauchy-subsequence-selector-real-handoff}
Every $\RealUp$ or Completion-facing consumer of an accepted $\CauchySubsequenceSelectorUp$ packet must first read the $\RegSeqRatUp$ source row, the $\StreamNameUp$ finite windows, the monotone selector schedule, and the Cauchy-gap ledger. The handoff to $E$ therefore supplies a finite subsequence corridor from regular rational data to Real-facing data, not a host subsequence theorem, not a selected limit, and not a quotient construction.
\end{theorem}
\begin{proof}
Project an accepted carrier $S=(R,W,M,G,E,H,C,P,N)$. The source row $R$ is the only regular rational input, and $W$ is the only finite observation surface available to a consumer.

The selector row $M$ records the monotone schedule. The Cauchy-gap ledger $G$ records the finite tail comparisons that let the scheduled windows be read as a subsequence corridor of the same source.

Only after $R,W,M,G$ are present may the consumer inspect $E$ as a Real-facing seal. The transport, replay, provenance, and naming rows keep that order visible to downstream chapters.

The carrier contains no coordinate for quotient stream equality, a chosen host subsequence, a selected limit, countable choice, trichotomy, or ambient $\RealUp$ completeness. Thus every Real or Completion handoff factors through the displayed selector rows.
\end{proof}

\closureat{CauchySubsequenceSelectorUp}{seedStr}

\begin{closurestatus}{\CauchySubsequenceSelectorUp}
  \constructivestory{A $\CauchySubsequenceSelectorUp$ packet is generated from a RegSeqRat source row, finite StreamName windows, monotone selector schedule, Cauchy-gap ledger, terminal Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-subsequence-selector-carrier}, \autoref{thm:cauchy-subsequence-selector-namecert-obligations}, and \autoref{thm:cauchy-subsequence-selector-real-handoff} seed the finite selector corridor from regular rational Cauchy data to a Real-facing seal.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.CauchySubsequenceSelectorUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient stream equality, selected limits, countable choice, trichotomy, host real equality, Lean verification, bridge checking, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, selector monotonicity, StreamName window coverage, Cauchy-gap compatibility, RegSeqRat handoff, Real seal non-escape, transport, replay, provenance, and local naming for BEDC.Derived.CauchySubsequenceSelectorUp.}
\end{closurestatus}
