\concretizedIn{ch:concrete-instances-regularcauchydiagonal-namecert}{Stationary regular Cauchy diagonal packets are represented as finite NameCert carriers over RatUp, StreamNameUp, RegSeqRatUp, and RealUp.}
\concretizedIn{ch:concrete-instances-finitewindowenvelope-namecert}{Finite observation windows are realized as a NameCert envelope linking DyadicRatCore, StreamNameUp, RegSeqRat, and RealUp seals.}
\concretizedIn{ch:concrete-instances-regular-cauchy-limit-modulus-namecert}{The diagonal-limit modulus is represented as a finite NameCert packet over RegSeqRatUp, StreamNameUp, DyadicRatCoreUp, and RealUp.}
\concretizedIn{ch:concrete-instances-regularcauchylimitclassifier-namecert}{Regular Cauchy limit classifiers are realized as finite NameCert packets linking RegSeqRatUp diagonal extraction, StreamNameUp windows, and RealUp seal handoff.}
\concretizedIn{ch:concrete-instances-transportedstationarywindowseal-namecert}{Transported stationary diagonal window-seal packets are realized as a finite NameCert carrier over RatUp, StreamNameUp, RegSeqRatUp, FiniteWindowEnvelopeUp, and RealUp.}
\concretizedIn{ch:concrete-instances-realcompleteness-namecert}{The Real completeness diagonal-limit target is represented as a finite NameCert seed over DyadicRatCore, StreamNameUp, RegSeqRatUp, and RealUp.}
\concretizedIn{ch:concrete-instances-regular-cauchy-triangle-bound-namecert}{The three-leg diagonal regularity estimate is realized as a finite NameCert packet over DyadicRatCore, StreamNameUp, RegSeqRatUp, and RealUp.}
\concretizedIn{ch:concrete-instances-finitetaildiagonalseal-namecert}{Finite-tail diagonal seals realize the selected regular-Cauchy tail window as a RealUp-facing NameCert packet without quotient streams or host real equality.}
\concretizedIn{ch:concrete-instances-regular-cauchy-tail-meet-namecert}{Regular Cauchy tail-meet packets realize the shared dyadic tail threshold needed by diagonal RealUp completion consumers.}
\concretizedIn{ch:concrete-instances-dyadicabsolutevalue-namecert}{Dyadic absolute-value rows are realized as finite DyadicRatCore BHist packets with sign-split, nonnegative-output, and tolerance-ledger surfaces.}
\concretizedIn{ch:concrete-instances-realdiagonalwindowcoverage-namecert}{Real diagonal-window coverage realizes the finite selected-window route from StreamName and RegSeqRat data through DyadicRatCore observations to the RealUp seal.}
\concretizedIn{ch:concrete-instances-realdiagonalmeshbudget-namecert}{Finite diagonal mesh-budget packets realize the precision-to-window-to-dyadic-readback route used by Real completeness consumers before the RealUp seal.}
\concretizedIn{ch:concrete-instances-regularcauchylimittransport-namecert}{Regular Cauchy limit transport packets realize classifier-stable diagonal-limit handoff across RegSeqRatUp, StreamNameUp, DyadicRatCoreUp, and RealUp rows.}
\concretizedIn{ch:concrete-instances-regularcauchywitnessschedule-namecert}{Regular Cauchy witness schedules realize the modulus-indexed finite observation route from RegSeqRat and StreamName data through DyadicRatCore readback to the RealUp seal.}
\concretizedIn{ch:concrete-instances-cauchydiagonalfusion-namecert}{Cauchy diagonal fusion realizes the finite route from observation budgets and witness schedules through schedule fusion to the RealUp diagonal seal.}
\concretizedIn{ch:concrete-instances-regularcauchyzero-namecert}{Regular Cauchy zero packets realize the zero-source identity surface for tail-meet, diagonal, and RealUp seal consumers.}
\concretizedIn{ch:concrete-instances-stationarydiagonalwindow-namecert}{Stationary diagonal finite-window classifier correspondence is realized as a concrete NameCert packet linking RatUp, StreamNameUp, RegSeqRatUp, DyadicRatCoreUp, and RealUp.}
\concretizedIn{ch:concrete-instances-modulus-indexed-tail-cover-namecert}{The modulus-indexed finite tail-window cover is realized as a concrete NameCert packet from unary precision requests through CauchyModulusUp, StreamNameUp, DyadicRatCoreUp, RegSeqRatUp, and RealUp seal rows.}
\concretizedIn{ch:concrete-instances-productregularcauchylimit-namecert}{Product regular-Cauchy limit packets realize the product-limit handoff across CauchyProductUp, RegularCauchyLimitClassifierUp, StreamNameUp, RegSeqRatUp, DyadicRatCoreUp, and RealUp.}
\concretizedIn{ch:concrete-instances-regularcauchytailfusion-namecert}{Regular Cauchy tail fusion realizes the cofinal tail-to-diagonal RealUp seal route as a finite NameCert packet.}
\concretizedIn{ch:concrete-instances-diagonal-tail-selector-namecert}{Diagonal tail selectors realize the finite cofinal-tail route from a regular Cauchy modulus through StreamName windows, dyadic readback, RegSeqRat rows, and the RealUp seal without quotient streams or host-selected limits.}
\concretizedIn{ch:concrete-instances-realtailagreementseal-namecert}{Real tail-agreement seals realize paired cofinal tail-window agreement as a finite NameCert packet over DyadicRatCoreUp, StreamNameUp, RegSeqRatUp, and RealUp.}
\concretizedIn{ch:concrete-instances-diagonal-limit-compatibility-namecert}{Diagonal-limit compatibility is realized as a finite NameCert packet tying RealCompleteness, RegularCauchyTriangleBound, CauchyLimitSeal, StreamName, RegSeqRat, DyadicRatCore, and RealUp seal rows.}
\concretizedIn{ch:concrete-instances-regularcauchysequence-namecert}{Regular Cauchy sequence packets realize the finite family, modulus, selected-window, dyadic readback, RegSeqRat, and RealUp seal surface used by the diagonal-limit handoff.}
\concretizedIn{ch:concrete-instances-regularcauchyswapbisimulation-namecert}{Regular Cauchy swap bisimulations realize selector-swapped interleavings as finite RegSeqRat, StreamName, RealUp, hsame, Cont, Pkg, and NameCert packets.}
\concretizedIn{ch:concrete-instances-real-budget-tail-meet-namecert}{Budgeted tail-meet packets realize finite observation budgets and shared-tail thresholds for the Real completeness seal route.}
\concretizedIn{ch:concrete-instances-realcompletionwitnessextractor-namecert}{Real completion witness extractors realize the diagonal regular-Cauchy limit route as a finite NameCert packet over modulus schedules, selected windows, RegSeqRat witnesses, RealUp seals, hsame transport, Cont replay, and non-escape ledgers.}
\concretizedIn{ch:concrete-instances-regularcauchycofinallimit-namecert}{Regular Cauchy cofinal limits are realized as finite cofinal-window NameCert packets over DyadicRatCore, StreamNameUp, RegSeqRat, and RealUp seal rows.}
\concretizedIn{ch:concrete-instances-cofinalregularlimitbudget-namecert}{Cofinal regular-limit budgets realize the Real completeness diagonal target as finite precision, cofinal-window, RegSeqRat handoff, RealUp seal, route, provenance, and NameCert rows.}
\concretizedIn{ch:concrete-instances-regularcauchyproductbudget-namecert}{Regular Cauchy product budgets realize the finite product-window ledger from RegSeqRatUp sources through StreamNameUp, DyadicRatCoreUp, FiniteErrorBudgetUp, and RealUp seal rows.}
\concretizedIn{ch:concrete-instances-regularcauchyselectorbudget-namecert}{Regular Cauchy selector budgets realize the modulus-selected finite window, RegSeqRat handoff, RealUp seal route, and non-escape ledger used by the Real completeness diagonal construction.}
\concretizedIn{ch:concrete-instances-choicefreediagonalselector-namecert}{Choice-free diagonal selectors realize the finite precision, cofinal-window, StreamName, RegSeqRat, RealUp seal, hsame, Cont, Pkg, and NameCert selector boundary used by the Real completeness handoff.}
\concretizedIn{ch:concrete-instances-dyadic-cofinal-tail-selector-namecert}{Dyadic cofinal tail selectors realize the finite cofinal-window route used by the Real and Completion diagonal-limit handoff.}
\concretizedIn{ch:concrete-instances-tail-cofinality-schedule-namecert}{Tail cofinality schedules realize the finite shared-threshold route from DyadicRatCore, StreamNameUp, RegSeqRatUp, and RealUp seal rows used by the diagonal-limit handoff.}
\concretizedIn{ch:concrete-instances-regularcauchymerge-namecert}{RegularCauchy merge packets realize the two-route cofinal selector agreement used by the Real completeness diagonal-limit handoff.}
\concretizedIn{ch:concrete-instances-cofinal-tail-budget-namecert}{Cofinal tail budgets realize finite shared-tail threshold packets for the Real and Completion diagonal-limit handoff.}
\concretizedIn{ch:concrete-instances-observablecauchyseal-namecert}{Observable Cauchy seals realize finite observation routes from StreamName windows and dyadic readbacks through RegSeqRat handoff rows into a RealUp seal.}
\concretizedIn{ch:concrete-instances-regular-cauchy-telescoping-budget-namecert}{Regular Cauchy telescoping budgets realize finite chained-window error-ledger composition for the Real completeness diagonal-limit handoff.}
\concretizedIn{ch:concrete-instances-realmodulusfusion-namecert}{Real modulus fusion realizes the real-completeness vision as a finite shared-modulus NameCert over Cauchy modulus rows, tail-meet thresholds, StreamName windows, RegSeqRat handoff, and RealUp seal rows.}
\concretizedIn{ch:concrete-instances-cauchy-tail-modulus-seal-namecert}{Cauchy tail-modulus seals realize the shared-tail modulus, fusion, witness-extractor, and RealUp seal route as one finite NameCert packet.}
\concretizedIn{ch:concrete-instances-regular-cauchy-modulus-normalizer-namecert}{Regular Cauchy modulus normalizers realize the shared finite modulus-window route used by the Real completeness diagonal-limit handoff.}
\concretizedIn{ch:concrete-instances-finiteobservationbudgetselector-namecert}{Finite observation-budget selector packets realize the finite diagonal observation budget used by the Real completeness route.}
\concretizedIn{ch:concrete-instances-regularcauchytailschedule-namecert}{Regular Cauchy tail schedules realize the finite precision-to-cofinal-tail route consumed by tail-meet, tail-fusion, diagonal-selector, and RealUp seal packets.}
\concretizedIn{ch:concrete-instances-cauchydiagonalbudget-namecert}{Cauchy diagonal budgets realize the Real completeness diagonal selector as finite precision, mesh-budget, comparison, seal-handoff, hsame, Cont, Pkg, and NameCert rows.}
\concretizedIn{ch:concrete-instances-cofinal-modulus-seal-namecert}{Cofinal modulus seals realize the Real-completeness cofinal-tail modulus route as a finite completion-seal NameCert surface.}
\concretizedIn{ch:concrete-instances-diagonal-limit-stability-namecert}{Diagonal-limit stability packets realize the finite stability comparison between a diagonal representative and the sealed RealUp limit route.}
\concretizedIn{ch:concrete-instances-regular-cauchy-finite-observation-route-namecert}{Regular-Cauchy finite observation routes are realized as finite StreamName, DyadicRatCore, RegSeqRat, RealObservationBudget, and RealUp seal packets.}
\concretizedIn{ch:concrete-instances-cauchy-modulus-refinement-namecert}{Cauchy modulus refinements realize the shared-meet and selector-budget route used by the Real completeness diagonal handoff.}
\concretizedIn{ch:concrete-instances-real-seal-congruence-namecert}{Real seal congruence packets realize classifier-preserving replacement of RegSeqRat and StreamName readbacks under the RealUp seal.}
\concretizedIn{ch:concrete-instances-realsealcomparison-namecert}{Real seal comparison packets realize equality-facing comparison of two sealed RealUp routes as finite CauchyLimitSeal, RegularLimitUniqueness, DiagonalLimitStability, hsame, Cont, Pkg, and NameCert rows.}
\concretizedIn{ch:concrete-instances-regular-cauchy-tail-fiber-namecert}{Regular Cauchy tail fibers realize the shared finite tail-fiber classifier consumed by RealUp diagonal completion and tail-agreement routes.}
\concretizedIn{ch:concrete-instances-diagonal-limit-budget-namecert}{Diagonal limit budget packets realize the finite modulus, window, dyadic-tolerance, and RealUp seal budget consumed by the Real completeness diagonal route.}
\concretizedIn{ch:concrete-instances-realcompletionselectorseal-namecert}{Real completion selector-seal packets realize the finite selector-budget, selected-window, RegSeqRat readback, CauchyLimitSeal, and RealUp seal route.}
\concretizedIn{ch:concrete-instances-finitecauchygluingbudget-namecert}{Finite Cauchy gluing budgets realize the Real-completeness witness route as one finite budget, synchronizer, completion-seal, StreamName, RegSeqRat, DyadicRatCore, and RealUp NameCert surface.}
