\chapter{A Concrete Naming Certificate for $\BHistArityThirteenSequenceNameCertUp$}
\label{ch:concrete-instances-b-hist-arity13-sequence-name-cert-namecert}
\origin{ai-composite}

The $\BHistArityThirteenSequenceNameCertUp$ packet is the ordered arity-thirteen sequence-window capstone for the carrier-isomorphism bucket. It is composite over the tuple capstone of \autoref{ch:concrete-instances-b-hist-arity13-tuple-namecert}, the sequence neighbors of \autoref{ch:concrete-instances-b-hist-nona-sequence-name-cert-namecert}, \autoref{ch:concrete-instances-b-hist-deca-sequence-name-cert-namecert}, and \autoref{ch:concrete-instances-b-hist-hendeca-sequence-name-cert-namecert}, and the bucket members \autoref{ch:concrete-instances-authoredrecordboundary-namecert}, \autoref{ch:concrete-instances-cauchy-witness-gluing-namecert}, \autoref{ch:concrete-instances-compactnetmodulusselector-namecert}, \autoref{ch:concrete-instances-compilerclassifierroute-namecert}, \autoref{ch:concrete-instances-dyadic-tolerance-triangle-ledger-namecert}, \autoref{ch:concrete-instances-layeredrelationdisplay-namecert}, \autoref{ch:concrete-instances-objectconstitutionledger-namecert}, and \autoref{ch:concrete-instances-observer-filter-budget-selector-namecert}. The chapter names the BEDC-native sequence surface that reads thirteen ordered $\BHist$ rows together with an index row, componentwise transport, continuation replay, provenance, and local naming, while leaving every bucket member as its own local certificate.

\begin{definition}[BHistArity13SequenceNameCert carrier]
\label{def:b-hist-arity13-sequence-name-cert-carrier}
A $\BHistArityThirteenSequenceNameCertUp$ carrier is a finite sequence-window packet
$$
S=(R_0,R_1,R_2,R_3,R_4,R_5,R_6,R_7,R_8,R_9,R_{10},R_{11},R_{12},I,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $R_0,\ldots,R_{12}$ are the thirteen ordered $\BHist$ rows admitted by the window. Each row is read as a displayed BEDC history component, and its tag records the local sequence role rather than a host-side position.
\item $I$ is the finite order and index row. It records the first and last admitted positions, the successor route through the thirteen entries, and the rule that every sequence read factors through one of $R_0,\ldots,R_{12}$.
\item $H$ records componentwise $\hsame$ transport for $R_0,\ldots,R_{12},I,C,P,L$ and no transport row outside the displayed packet.
\item $C$ records the displayed $\Cont$ replay from window admission through index preservation, componentwise comparison, transport, provenance readback, and local naming.
\item $P$ is the $\Pkg$ provenance over the thirteen-row window encoder, the tuple and sequence capstone anchors cited above, the bucket members named above, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $L$ is the local $\NameCert_{\BHistArityThirteenSequenceNameCertUp}$ row.
\end{enumerate}
The carrier has no coordinate for an untagged row, a fourteenth sequence component, a hidden permutation, a host equality test, unordered bucket membership alone, or a relocation of any tuple, sequence, or bucket-member chapter.
\end{definition}

\begin{definition}[BHistArity13SequenceNameCert classifier]
\label{def:b-hist-arity13-sequence-name-cert-classifier}
Two $\BHistArityThirteenSequenceNameCertUp$ packets
$$
S=(R_0,R_1,R_2,R_3,R_4,R_5,R_6,R_7,R_8,R_9,R_{10},R_{11},R_{12},I,H,C,P,L)
$$
and
$$
S'=(R'_0,R'_1,R'_2,R'_3,R'_4,R'_5,R'_6,R'_7,R'_8,R'_9,R'_{10},R'_{11},R'_{12},I',H',C',P',L')
$$
are classifier-equivalent exactly when each displayed window row compares componentwise,
$$
\begin{aligned}
&R_0 \sim R'_0,\quad R_1 \sim R'_1,\quad R_2 \sim R'_2,\quad R_3 \sim R'_3,\quad R_4 \sim R'_4,\quad R_5 \sim R'_5,\\
&R_6 \sim R'_6,\quad R_7 \sim R'_7,\quad R_8 \sim R'_8,\quad R_9 \sim R'_9,\quad R_{10} \sim R'_{10},\quad R_{11} \sim R'_{11},\\
&R_{12} \sim R'_{12},
\end{aligned}
$$
the index rows display the same finite order, the transport rows display the same $\hsame$ routes for those components and for $I,C,P,L$, and the replay rows display the same $\Cont$ route from window admission through local naming. No comparison is available through hidden permutation, untagged payload, host equality, bucket membership alone, omitted position, tuple-chapter relocation, sequence-chapter relocation, or bucket-member relocation.
\end{definition}

\begin{theorem}[BHistArity13SequenceNameCert carrier admission]
\label{thm:b-hist-arity13-sequence-name-cert-carrier-admission}
Every accepted $\BHistArityThirteenSequenceNameCertUp$ packet admits exactly the displayed window rows
$$
R_0,R_1,R_2,R_3,R_4,R_5,R_6,R_7,R_8,R_9,R_{10},R_{11},R_{12},I,H,C,P,L.
$$
The thirteen rows are ordered tag-encoded $\BHist$ components, $I$ is the only index and order row, and $H,C,P,L$ are the only structural rows by which a consumer may transport, replay, source, or locally name the sequence window.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:b-hist-arity13-sequence-name-cert-carrier}. The definition lists the thirteen ordered $\BHist$ rows, then lists the index, transport, continuation, provenance, and local naming rows.

There is no remaining coordinate in the packet. Thus any accepted window read lands in exactly the displayed rows, and any proposed fourteenth component, detached order table, hidden permutation, or off-packet structural row lies outside the accepted surface.
\end{proof}

\begin{theorem}[BHistArity13SequenceNameCert classifier exactness]
\label{thm:b-hist-arity13-sequence-name-cert-classifier-exactness}
For accepted $\BHistArityThirteenSequenceNameCertUp$ packets $S$ and $S'$, the classifier of \autoref{def:b-hist-arity13-sequence-name-cert-classifier} is exact for the arity-thirteen sequence window: it compares the thirteen $\BHist$ rows at matching indices, compares the displayed finite order through $I,I'$, compares the displayed $\hsame$ and $\Cont$ routes through $H,H',C,C'$, and preserves the provenance and local naming rows through $P,P',L,L'$. It does not compare by unordered tuple membership, by a hidden permutation, by a detached order table, by bucket membership alone, by any sibling-chapter relocation, or by a host equality test.
\end{theorem}
\begin{proof}
Start with the classifier definition. It requires one comparison for each matching pair $R_i,R'_i$, requires the index rows to display the same finite order, and requires the displayed transport and replay routes to preserve that same ordered list.

The provenance and local naming rows are part of the same sequence-window carrier, so their comparison is not an external bucket judgment. Since the classifier has no clause for unordered tuple membership, hidden permutation, detached order table, bucket membership alone, sibling-chapter relocation, or host equality, the displayed indexwise route is the exact comparison surface.
\end{proof}

\begin{theorem}[BHistArity13SequenceNameCert tag exhaustion]
\label{thm:b-hist-arity13-sequence-name-cert-tag-exhaustion}
For an accepted $\BHistArityThirteenSequenceNameCertUp$ packet, the tags carried by $R_0,\ldots,R_{12}$ exhaust the sequence rows available to the local $\NameCert$ interface. Any consumer may transport or replay these rows only through the displayed $I$, $H$, and $C$ rows, and cannot manufacture an unlisted tag, collapse two tags into one bucket witness, import a carrier row from a sibling capstone, alter the displayed order, or read a fourteenth sequence component.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:b-hist-arity13-sequence-name-cert-carrier}. The carrier has exactly the thirteen ordered $\BHist$ rows together with $I,H,C,P,L$, and \autoref{thm:b-hist-arity13-sequence-name-cert-carrier-admission} identifies this displayed list as the whole accepted row inventory.

The index, transport, and replay access paths are therefore already fixed by $I$, $H$, and $C$. No consumer can introduce another tag, change the displayed order, or merge two tags into a single bucket witness, because such a move would require an additional carrier row or a non-displayed structural clause.

Finally apply \autoref{thm:b-hist-arity13-sequence-name-cert-classifier-exactness}. Every public comparison remains indexwise over the same thirteen tags and the same displayed structural rows, so sibling capstones cannot contribute hidden carrier rows and no fourteenth component is readable through the local $\NameCert$ surface.
\end{proof}

\begin{theorem}[BHistArity13SequenceNameCert scoped support package]
\label{thm:b-hist-arity13-sequence-name-cert-scoped-support-package}
The carrier admission, classifier exactness, and tag-exhaustion clauses bind the $\BHistArityThirteenSequenceNameCertUp$ packet to the displayed BEDC support
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert,
$$
to the arity-thirteen tuple capstone, the neighboring sequence capstones, and to the bucket members \autoref{ch:concrete-instances-authoredrecordboundary-namecert}, \autoref{ch:concrete-instances-cauchy-witness-gluing-namecert}, \autoref{ch:concrete-instances-compactnetmodulusselector-namecert}, \autoref{ch:concrete-instances-compilerclassifierroute-namecert}, \autoref{ch:concrete-instances-dyadic-tolerance-triangle-ledger-namecert}, \autoref{ch:concrete-instances-layeredrelationdisplay-namecert}, \autoref{ch:concrete-instances-objectconstitutionledger-namecert}, and \autoref{ch:concrete-instances-observer-filter-budget-selector-namecert}. The resulting scope is the ordered arity-thirteen $\BHist$ sequence window with displayed index row, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row; it is not an unordered bucket tuple, a host-side equality classifier, a hidden permutation, or a hidden fourteenth position.
\end{theorem}
\begin{proof}
Apply \autoref{thm:b-hist-arity13-sequence-name-cert-carrier-admission} to identify the admitted rows and exclude any fourteenth coordinate. Apply \autoref{thm:b-hist-arity13-sequence-name-cert-classifier-exactness} to keep comparison on matching sequence indices, the displayed index row, and the structural rows.

Apply \autoref{thm:b-hist-arity13-sequence-name-cert-tag-exhaustion} to rule out unlisted tags, order changes, row fusion, sibling-carrier imports, and hidden components at the local $\NameCert$ interface.

The support package is therefore the named BEDC packet itself. Its provenance can source the cited tuple capstone, sequence capstones, and bucket members, but no carrier or classifier row relocates those sibling chapters or replaces their local certificates.
\end{proof}

\falsifiablePrediction{Any accepted consumer route that reads an unordered tuple coordinate, an untagged row, a fourteenth sequence row, a hidden permutation, bucket membership alone, an order table detached from $I$, or a sibling capstone relocation fails carrier admission, classifier exactness, or tag exhaustion for $\BHistArityThirteenSequenceNameCertUp$.}

\independenceWitness{b-hist-arity13-tuple-name-cert, b-hist-nona-sequence-name-cert, b-hist-deca-sequence-name-cert, b-hist-hendeca-sequence-name-cert, and the cited bucket members: none is bijective to $\BHistArityThirteenSequenceNameCertUp$ because this packet carries thirteen ordered payload rows plus an index row, componentwise transport, replay, provenance, and local $\NameCert$, while the cited siblings supply tuple, sequence, or member-local surfaces.}

\closureat{BHistArity13SequenceNameCertUp}{seedStr}

\begin{closurestatus}{\BHistArityThirteenSequenceNameCertUp}
  \constructivestory{A $\BHistArityThirteenSequenceNameCertUp$ packet is generated from thirteen ordered $\BHist$ sequence rows, a finite index row, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:b-hist-arity13-sequence-name-cert-carrier}, \autoref{def:b-hist-arity13-sequence-name-cert-classifier}, \autoref{thm:b-hist-arity13-sequence-name-cert-carrier-admission}, \autoref{thm:b-hist-arity13-sequence-name-cert-classifier-exactness}, \autoref{thm:b-hist-arity13-sequence-name-cert-tag-exhaustion}, and \autoref{thm:b-hist-arity13-sequence-name-cert-scoped-support-package} identify the arity-thirteen sequence-window carrier surface and its BEDC support package.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai-composite}
  \notclaimed{This chapter does not provide a Lean declaration, standard bridge, tuple-chapter replacement, sequence-chapter replacement, bucket-member replacement, or public acceptance interface.}
  \upgradepath{Formalization requires a Lean carrier for BEDC.Derived.BHistArity13SequenceNameCertUp and checked carrier-admission, classifier-exactness, tag-exhaustion, and scoped-support theorems.}
\end{closurestatus}
