\begin{theorem}[SeparatedCompletion filterbase admission]
\label{thm:separated-completion-filterbase-admission}
For every accepted $\SeparatedCompletionUp$ carrier
$$
S=(M,D,C,Z,U,H,R,T,P,N),
$$
any filterbase-facing admission read factors through the same finite source route as \autoref{thm:separated-completion-root-obligation-package}. The $\CauchyCompletionReflectorUp$ and $\MetricCompletionUp$ rows receive the source metric $M$, dense embedding $D$, completion handoff $C$, separated classifier $Z$, $\RegSeqRatUp$ and $\StreamNameUp$ windows, terminal $\RealUp$ seal, and structural rows $H,R,T,P,N$ before a filterbase consumer may inspect completion data. Thus filterbase admission is a $\BHist$ and $\NameCert$ route, not a quotient completion, selected representative, host equality, countable-choice selector, or ambient complete-space coordinate.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $M,D,C$ admit the source metric, dense embedding, and completion handoff before any filterbase-facing consumer can read completion data.

The separated classifier row $Z$ and uniqueness boundary $U$ keep the filterbase comparison inside the same displayed separated route. Apply \autoref{thm:separated-completion-classifier-stability-root-obligation} to see that transport and replay cannot add a host equality coordinate.

Finally read the completion-facing spine. The $\CauchyCompletionReflectorUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ rows are delivered through $H,R,T,P,N$, so the filterbase admission has no access to quotient completions, selected representatives, countable choice, or an ambient complete-space object.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy-equivalence routing]
\label{thm:separated-completion-cauchy-equivalence-routing}
For every accepted $\SeparatedCompletionUp$ carrier, each Cauchy-equivalence read sent to $\RegSeqRatUp$, $\StreamNameUp$, $\MetricCompletionUp$, or $\RealUp$ factors through the separated classifier and the Cauchy source rows before the terminal Real seal is exposed. In symbols, the public Cauchy-equivalence route is
$$
M,D,C,Z,U \longmapsto \RegSeqRatUp,\StreamNameUp,\MetricCompletionUp,\RealUp \longmapsto H,R,T,P,N .
$$
The route exports only displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and does not export quotient stream equality, host equality of completed points, selected limits, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:separatedcompletion-cauchy-equivalence-source}. It places every Cauchy-equivalence read behind the displayed Cauchy source and separated-completion rows, so the comparison is not a free-standing quotient relation.

Next apply \autoref{thm:separatedcompletion-zero-distance-factorization} and \autoref{thm:separatedcompletion-limit-uniqueness-export}. These theorems route zero-distance and uniqueness reads through $Z$ and $U$ before the regular-rational and stream windows can be consumed.

The Real-facing boundary is then supplied by \autoref{thm:separated-completion-real-seal-root-obligation}. The structural rows preserve and replay the same path through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, so no quotient stream equality, host equality, selected limit, choice principle, or ambient completeness coordinate is available.
\end{proof}

\begin{theorem}[SeparatedCompletion completion-reflector nonescape]
\label{thm:separated-completion-completion-reflector-nonescape}
Every $\CauchyCompletionReflectorUp$ or $\MetricCompletionUp$ consumer of an accepted $\SeparatedCompletionUp$ carrier remains inside the finite route
$$
M,D,C,Z,U,H,R,T,P,N
$$
together with the displayed $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ handoff rows. The reflector may read the source metric, dense embedding, separated classifier, uniqueness boundary, transport, replay, provenance, and local naming, but it may not import quotient completions, selected representatives, host equality, countable choice, hidden complete metric spaces, or an ambient real-completeness theorem.
\end{theorem}
\begin{proof}
Read the reflector handoff through \autoref{thm:separatedcompletion-completion-reflector-handoff}. It already places the completion-reflector consumer downstream of the source metric, dense embedding, completion handoff, separated classifier, and Real-facing L10 spine.

The root package of \autoref{thm:separated-completion-root-obligation-package} exhausts the carrier-admission, classifier-stability, and Real-seal obligations. Hence the reflector consumer can inspect only the rows listed there and the transport, replay, provenance, and naming rows $H,R,T,P,N$.

Nonescape follows from absence of coordinates. Quotient completions, selected representatives, host equality, countable choice, hidden complete metric spaces, and ambient real completeness are not fields of the carrier and cannot be produced by $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, or local $\NameCert$ naming.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy-reflector triangle]
\label{thm:separatedcompletion-cauchy-reflector-triangle}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier whose source route receives $\CauchyCompletionReflectorUp$, $\CompletionUniversalPropertyUp$, $\RegularCauchyCompletionSeparatedUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows. Every endpoint-uniqueness read sent toward a Real-facing completion seal factors through the separated classifier row $Z$ before it can be consumed by the reflector or universal-property rows. The triangle
$$
\CauchyCompletionReflectorUp
\longmapsto
\SeparatedCompletionUp
\longmapsto
\CompletionUniversalPropertyUp
$$
therefore commutes at the displayed $\NameCert$ surface through $M,D,C,Z,U,H,R,T,P,N$, and exports no quotient completion, selected representative, host equality of completed points, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The dense source rows $M,D,C$ are read first, so the reflector-facing route starts from the same finite metric, dense embedding, and completion handoff as the rest of the chapter.

Apply \autoref{thm:separated-completion-dense-factorization} and \autoref{thm:separated-completion-uniqueness-boundary}. They place endpoint uniqueness downstream of the dense factorization and force the uniqueness boundary to read the separated classifier row $Z$ rather than a host equality coordinate.

Now apply \autoref{thm:separatedcompletion-completion-reflector-handoff}. The CauchyCompletionReflector and CompletionUniversalProperty consumers receive the same route through $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyCompletionSeparatedUp$, and the terminal $\RealUp$ seal.

The transport, route-preservation, provenance, and local naming rows $H,R,T,P,N$ preserve this factorization. Because the carrier contains no quotient-completion, selected-representative, host-equality, choice, or ambient-completeness coordinate, the only available triangle is the displayed separated-classifier route.
\end{proof}

\begin{theorem}[SeparatedCompletion root-consumer unblock package]
\label{thm:separatedcompletion-root-consumer-unblock-package}
Every downstream Real or Completion consumer of an accepted $\SeparatedCompletionUp$ carrier must factor through the carrier-admission root obligation, classifier-stability root obligation, Real-seal root obligation, root obligation package, and Cauchy-reflector triangle before reading any completion-facing output. Equivalently, any consumer route over $S=(M,D,C,Z,U,H,R,T,P,N)$ must display the finite root surface
$$
M,D,C,Z,U,H,R,T,P,N
$$
together with the carrier-admission, classifier-stability, Real-seal, root-package, and reflector-triangle witnesses. The package exports no quotient completion, selected representative, host equality of completed points, countable choice, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Project the accepted carrier into the rows $M,D,C,Z,U,H,R,T,P,N$. The source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, route preservation, replay, provenance, and local naming rows are therefore the only displayed input surface available to downstream consumers.

Apply \autoref{thm:separated-completion-root-obligation-package}. It combines the carrier-admission root obligation, classifier-stability root obligation, and Real-seal root obligation, so the source, classifier, and seal sides of the accepted packet are exhausted before a completion-facing output can be read.

Next apply \autoref{thm:separatedcompletion-cauchy-reflector-triangle}. The reflector and universal-property routes commute only through the separated classifier row and the same finite L10 source spine, so endpoint-uniqueness reads cannot bypass the root package.

The remaining structural rows $H,R,T,P,N$ preserve, replay, source, and name that route. Since no quotient completion, selected representative, host equality, countable-choice schedule, or ambient Real-completeness coordinate appears among the carrier rows, the displayed package is the required unblock surface for all downstream Real and Completion consumers.
\end{proof}

\begin{theorem}[SeparatedCompletion dense limit route]
\label{thm:separatedcompletion-dense-limit-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every accepted limit-facing read must pass through the displayed $\MetricCompletionUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, $\HausdorffCompletionUp$, $\RegularCauchyCompletionSeparatedUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows before the uniqueness row $U$ is public. The route exposes dense source data, zero-distance classification, regular-Cauchy separated completion, and the Real-facing L10 spine, and it exports no quotient completion, selected limit representative, host equality of completed points, countable-choice schedule, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Read the dense source prefix first. Dense factorization, \autoref{thm:separated-completion-dense-factorization}, and dense replay scope, \autoref{thm:separatedcompletion-dense-replay-scope}, force every completion-facing read through $M,D,C$ before any separated classifier or uniqueness row is available.

Read the classifier and limit boundary next. Zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, makes $Z$ the separated equality route, and limit-uniqueness export, \autoref{thm:separatedcompletion-limit-uniqueness-export}, makes $U$ the public uniqueness row over $M,D,C,Z$.

Now attach source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, and nonescape, \autoref{thm:separated-completion-nonescape}. These results keep the source route inside the displayed MetricCompletion, CompletionEmbedding, CompletionUniversalProperty, SeparatedMetric, HausdorffCompletion, RegularCauchyCompletionSeparated, DyadicRatCore, StreamName, RegSeqRat, and Real rows. Since none of the excluded objects is a carrier coordinate, the dense limit route reaches uniqueness only through the displayed packet.
\end{proof}

\begin{theorem}[SeparatedCompletion choice-free limit transport]
\label{thm:separatedcompletion-choice-free-limit-transport}
For accepted $\SeparatedCompletionUp$ carriers whose source, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, route, provenance, and local naming rows are matched componentwise by $\hsame$ and replayed by $\Cont$, the transported packet preserves the same dense source, zero-distance classifier, and uniqueness boundary. This preservation uses no countable choice, quotient completion, selected representative, host equality of completed points, hidden complete metric space, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project the two carriers and read their transported rows componentwise. The $\hsame$ rows act only on $M,D,C,Z,U,H,R,T,P,N$, and the $\Cont$ rows replay the same displayed path.

Apply dense factorization, \autoref{thm:separated-completion-dense-factorization}, to both packets. The dense source remains the $M,D,C$ route after transport, because no additional source coordinate is present.

Apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, and limit-uniqueness export, \autoref{thm:separatedcompletion-limit-uniqueness-export}. They identify $Z$ as the classifier and $U$ as the uniqueness boundary before any downstream completion consumer can read the transported packet.

Finally use source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, together with nonescape, \autoref{thm:separated-completion-nonescape}. The structural rows preserve the dense source, zero-distance classifier, and uniqueness boundary, while the excluded choice, quotient, representative, host-equality, hidden-space, and ambient-completeness objects remain absent from the carrier.
\end{proof}

\begin{theorem}[SeparatedCompletion completion uniqueness package]
\label{thm:separatedcompletion-completion-uniqueness-package}
Every downstream $\MetricCompletionUp$ or $\HausdorffCompletionUp$ consumer of an accepted $\SeparatedCompletionUp$ carrier receives uniqueness only as the displayed row $U$ over $M,D,C,Z$ together with the structural rows $H,R,T,P,N$. The package may use the dense limit route of \autoref{thm:separatedcompletion-dense-limit-route} and the choice-free transport route of \autoref{thm:separatedcompletion-choice-free-limit-transport}, but it cannot export quotient completion equality, a selected representative, host equality of completed points, countable choice, a hidden complete metric space, or an ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with the dense route. By \autoref{thm:separatedcompletion-dense-limit-route}, a MetricCompletion or HausdorffCompletion consumer sees $M,D,C$ before the separated classifier $Z$ and uniqueness row $U$ are public.

Read uniqueness through the local row $U$. The limit-uniqueness export theorem, \autoref{thm:separatedcompletion-limit-uniqueness-export}, identifies that row as the whole uniqueness boundary over $M,D,C,Z$.

Transport and replay are then handled by \autoref{thm:separatedcompletion-choice-free-limit-transport}. The rows $H,R,T,P,N$ preserve, replay, source, and name the same boundary for downstream consumers.

Apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, and nonescape, \autoref{thm:separated-completion-nonescape}, to close the package. Since the carrier contains no quotient completion equality, selected representative, host equality, choice schedule, hidden complete metric space, or ambient completeness coordinate, the displayed $U$ row over $M,D,C,Z,H,R,T,P,N$ is the only uniqueness package available.
\end{proof}

\begin{theorem}[SeparatedCompletion density separated route]
\label{thm:separated-completion-density-separated-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every dense limit read exported before uniqueness must factor through the displayed $\CompletionEmbeddingUp$ row $D$, the $\SeparatedMetricUp$ zero-distance classifier $Z$, the $\RegularCauchyCompletionSeparatedUp$ route carried by $C$, the $\StreamNameUp$ and $\RegSeqRatUp$ readback rows in the completion handoff, and the terminal $\RealUp$ seal before $U$ may be consumed. Thus density and separation meet inside the finite route
$$
M,D,C,Z \longmapsto U,H,R,T,P,N ,
$$
not in a quotient completion, selected representative, host equality of completed points, countable-choice schedule, hidden complete metric space, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Project the carrier first. The source metric row $M$ and dense embedding row $D$ are the only displayed entrance into a dense limit read.

Read the completion handoff $C$ next. Its regular-Cauchy separated route carries the $\StreamNameUp$, $\RegSeqRatUp$, and terminal $\RealUp$ seal rows before a separated comparison can be public.

Apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The separated classifier $Z$ is the comparison boundary after $C$, so host equality of completed points and quotient equality are unavailable.

Only then may the uniqueness row $U$ be consumed. The structural rows $H,R,T,P,N$ transport, replay, source, and name the same dependency order, and the excluded completion objects have no coordinate in the carrier.
\end{proof}

\begin{theorem}[SeparatedCompletion filterbase reflector exhaustion]
\label{thm:separated-completion-filterbase-reflector-exhaustion}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every filterbase-facing reflector read exported by $S$ factors through the displayed $\MetricCompletionUp$ admission row, the $\CompletionEmbeddingUp$ dense row, the $\CompletionUniversalPropertyUp$ reflector boundary, the $\SeparatedMetricUp$ classifier, the $\HausdorffCompletionUp$ separated readback, the $\RegularCauchyCompletionSeparatedUp$ route, the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ L10 spine, and then through the structural $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The exported read contains no quotient completion equality, selected representative, countable-choice schedule, host equality of completed points, hidden complete metric space, or ambient $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Project the carrier. The only reflector-facing coordinates are the source metric row $M$, dense embedding row $D$, completion handoff row $C$, separated classifier row $Z$, uniqueness boundary $U$, and the structural rows $H,R,T,P,N$.

Read the filterbase entrance through the existing admission route of \autoref{thm:separated-completion-filterbase-admission}. That route already places filterbase data inside the displayed $\MetricCompletionUp$ and $\CompletionEmbeddingUp$ prefix before a reflector consumer may inspect completion data.

Attach the reflector boundary using \autoref{thm:separatedcompletion-completion-reflector-handoff} and \autoref{thm:separatedcompletion-cauchy-reflector-triangle}. The $\CompletionUniversalPropertyUp$, $\HausdorffCompletionUp$, and $\RegularCauchyCompletionSeparatedUp$ rows are consumed only after $M,D,C,Z,U$ have been displayed.

Finally read the L10 spine carried by $C$: $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ supply finite tolerance, window, readback, and seal data. Since the carrier has no coordinate for quotient completion equality, selected representatives, choice schedules, host equality, hidden complete spaces, or ambient completeness, the reflector read is exhausted by the named rows.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy-sequence equivalence lock]
\label{thm:separated-completion-cauchy-sequence-equivalence-lock}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every Cauchy-equivalence read exported by $S$ is locked to the displayed route through $\MetricCompletionUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, $\HausdorffCompletionUp$, $\RegularCauchyCompletionSeparatedUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row. No exported equivalence may be replaced by quotient completion equality, a selected representative, countable choice, host equality of completed points, a hidden complete metric space, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from the Cauchy-equivalence source theorem \autoref{thm:separatedcompletion-cauchy-equivalence-source}. It places every comparison inside the displayed source, dense embedding, and completion handoff rows $M,D,C$ before the separated classifier $Z$ can be read.

Use zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, to make $Z$ the separated comparison boundary. The equivalence read is therefore a displayed zero-distance route through the $\MetricCompletionUp$, $\SeparatedMetricUp$, $\RegSeqRatUp$, and $\RealUp$ rows carried by $M,D,C,Z$.

Read the uniqueness and Hausdorff boundary through \autoref{thm:separatedcompletion-limit-uniqueness-export} and \autoref{thm:separatedcompletion-hausdorff-uniqueness-route}. These routes attach the $\CompletionUniversalPropertyUp$, $\HausdorffCompletionUp$, and $\RegularCauchyCompletionSeparatedUp$ rows without adding any equality object outside the carrier.

The structural rows $H,R,T,P,N$ preserve, replay, source, and name the same route. Since quotient completions, selected representatives, choice schedules, host equality, hidden complete spaces, and ambient completeness are absent from the carrier, every exported Cauchy-equivalence read is locked to the displayed finite route.
\end{proof}

\begin{theorem}[SeparatedCompletion Hausdorff completion readback]
\label{thm:separated-completion-hausdorff-completion-readback}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every $\HausdorffCompletionUp$ readback consumed by a downstream completion chapter factors through the same displayed $\MetricCompletionUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, $\RegularCauchyCompletionSeparatedUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route. The readback is a finite separated-completion boundary over $S$, not a quotient completion equality, selected representative, countable-choice schedule, host equality of completed points, hidden complete metric space, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Project the accepted carrier and read $M,D,C$ as the dense completion prefix. By \autoref{thm:separated-completion-density-separated-route}, the downstream completion consumer must see the dense embedding, separated classifier, regular-Cauchy separated route, stream and rational readback rows, and terminal Real seal before uniqueness may be consumed.

Now read the Hausdorff boundary through \autoref{thm:separatedcompletion-hausdorff-uniqueness-route} and the reflector handoff through \autoref{thm:separatedcompletion-completion-reflector-handoff}. These theorems place $\HausdorffCompletionUp$ readback after $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, and $\RegularCauchyCompletionSeparatedUp$ have been displayed over the same source route.

Finally apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. The rows $H,R,T,P,N$ transport, replay, preserve, source, and name the displayed route, while quotient completion equality, selected representatives, choice schedules, host equality, hidden complete spaces, and ambient real completeness have no coordinate in the carrier.
\end{proof}

\begin{theorem}[SeparatedCompletion source triad obligation]
\label{thm:separatedcompletion-obligation-source-triad}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every accepted packet reads the source metric row $M$, dense embedding row $D$, and completion handoff row $C$ before any separated comparison through $Z$ is public. The triad is preserved through $\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$ provenance, and the local $\NameCert$ row, and no separated-comparison consumer can start from $Z,U,H,R,T,P,N$ alone.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. The source metric, dense embedding, and completion handoff rows are exactly the coordinates $M,D,C$, and the separated classifier is a later coordinate $Z$ over the same packet.

Apply dense factorization, \autoref{thm:separated-completion-dense-factorization}. It places every completion-facing read on the route $M,D\mapsto C$ before separated comparison or uniqueness data is available.

Now apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The row $Z$ reads equality as displayed zero-distance evidence over the already exposed dense completion handoff, not as an independent comparison source. The structural rows $H,R,T,P,N$ only preserve, replay, source, and name this order.
\end{proof}

\begin{theorem}[SeparatedCompletion quotient-exhaustion refusal]
\label{thm:separatedcompletion-no-quotient-exhaustion}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, and hidden complete spaces are absent from every public route exported by $S$. Any public completion-facing, equality-facing, uniqueness-facing, or reflector-facing read is exhausted by $M,D,C,Z,U,H,R,T,P,N$ through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
Start with universal route exhaustion, \autoref{thm:separatedcompletion-universal-route-exhaustion}. It identifies the public route with the displayed source, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, provenance, and local naming rows.

Attach the dense source and comparison constraints. Dense factorization, \autoref{thm:separated-completion-dense-factorization}, forces $M,D,C$ to be read first, and zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, forces equality reads through $Z$ rather than through host equality or quotient equality.

Finally apply the limit-uniqueness export, \autoref{thm:separatedcompletion-limit-uniqueness-export}. It makes $U$ the whole public uniqueness boundary over $M,D,C,Z$. Since the carrier has no coordinate for quotient completions, selected representatives, choice schedules, ambient Real completeness, or hidden complete spaces, those objects are absent from every public route.
\end{proof}

\begin{theorem}[SeparatedCompletion scoped route]
\label{thm:separatedcompletion-scoped-route}
For every accepted $\SeparatedCompletionUp$ carrier, the scoped route is exactly
$$
M,D,C,Z,U,H,R,T,P,N
$$
read through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The route admits the source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, route ledger, provenance, and local naming rows, and it admits no additional completion, equality, choice, Real-completeness, or hidden-space coordinate.
\end{theorem}
\begin{proof}
Project the accepted carrier using \autoref{def:separated-completion-carrier}. This gives the displayed row inventory $M,D,C,Z,U,H,R,T,P,N$ and no further public coordinate.

Use \autoref{thm:separatedcompletion-obligation-source-triad} to fix the source prefix. Every separated-completion read starts with $M,D,C$ before it can inspect $Z$ or $U$.

Use quotient-exhaustion refusal, \autoref{thm:separatedcompletion-no-quotient-exhaustion}, for the negative side. It excludes quotient completions, selected representatives, host equality, countable choice, ambient Real completeness, and hidden complete spaces from the route. The remaining rows are precisely the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface already displayed by the carrier.
\end{proof}

\begin{closurestatus}{\SeparatedCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:separated-completion-carrier}, \autoref{thm:separated-completion-namecert-obligations}, \autoref{thm:separated-completion-dense-factorization}, \autoref{thm:separated-completion-uniqueness-boundary}, \autoref{thm:separatedcompletion-cauchy-equivalence-source}, \autoref{thm:separatedcompletion-zero-distance-factorization}, \autoref{thm:separatedcompletion-limit-uniqueness-export}, \autoref{thm:separatedcompletion-dense-uniqueness-interface}, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, and \autoref{thm:separated-completion-nonescape} seed the general separated-completion interface over finite source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, hidden complete metric spaces, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-source compatibility, separated-classifier exactness, uniqueness-boundary exactness, transport replay, and non-escape for BEDC.Derived.SeparatedCompletionUp.}
  \constructivestory{A $\SeparatedCompletionUp$ packet is generated from a source metric row, a dense CompletionEmbedding row, a completion handoff through the DyadicRatCore-StreamName-RegSeqRat-Real L10 spine, a SeparatedMetric classifier, a CompletionUniversalProperty-HausdorffCompletion-RegularCauchyCompletionSeparated uniqueness boundary, componentwise hsame transport, Cont replay, route-preservation ledger, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
