\chapter{A Concrete Naming Certificate for $\SeparatedCompletionUp$}
\label{ch:concrete-instances-separatedcompletion-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, and Kelley-style separated uniform reasoning, the $\SeparatedCompletionUp$ packet records the finite NameCert boundary at which a metric-completion route becomes separated without becoming a quotient completion. It consumes the metric-completion surface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the dense embedding route of \autoref{ch:concrete-instances-completionembedding-namecert}, the extension-and-uniqueness surface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the zero-distance classifier of \autoref{ch:concrete-instances-separatedmetric-namecert}, the Hausdorff boundary of \autoref{ch:concrete-instances-hausdorffcompletion-namecert}, and the regular-Cauchy separated route of \autoref{ch:concrete-instances-regular-cauchy-completion-separated-namecert}. The L10 spine supplying finite names is the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route of \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

The packet is a general separated-completion interface. It exposes source metric rows, dense embedding rows, completion handoff rows, separated classifier rows, uniqueness-boundary rows, transport rows, continuation replay, package provenance, and local naming. It exports no quotient completion, no selected representative, no host equality of completed points, no countable-choice schedule, no ambient $\RealUp$ completeness theorem, and no hidden complete metric space.

\begin{definition}[SeparatedCompletion carrier]
\label{def:separated-completion-carrier}
A $\SeparatedCompletionUp$ carrier is a finite $\BHist$ packet
$$
S=(M,D,C,Z,U,H,R,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source metric row together with the $\MetricCompletionUp$ admission boundary for completion-facing reads.
\item $D$ is the dense $\CompletionEmbeddingUp$ row, recording how source observations enter the completion interface before any separated comparison is public.
\item $C$ is the completion handoff row, read through the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ L10 naming spine.
\item $Z$ is the $\SeparatedMetricUp$ classifier row that compares displayed completion readings by zero-distance evidence rather than by host equality.
\item $U$ is the uniqueness boundary, supplied by the $\CompletionUniversalPropertyUp$, $\HausdorffCompletionUp$, and $\RegularCauchyCompletionSeparatedUp$ rows over the same source, dense embedding, completion handoff, and separated classifier.
\item $H$ records componentwise $\hsame$ transport for $M,D,C,Z,U$ and for the local structural rows.
\item $R$ records displayed $\Cont$ replay from source metric observations through dense embedding, completion handoff, separated classification, and uniqueness boundary.
\item $T$ is the local transport ledger that states that hsame transport and Cont replay preserve the same ordered completion route.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, $\HausdorffCompletionUp$, $\RegularCauchyCompletionSeparatedUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SeparatedCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient Cauchy classes, selected completion representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or an external complete metric space.
\end{definition}
\leandef{BEDC.Derived.SeparatedCompletionUp.SeparatedCompletionCarrier}

\begin{theorem}[SeparatedCompletion NameCert obligations]
\label{thm:separated-completion-namecert-obligations}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, the local $\NameCert_{\SeparatedCompletionUp}$ surface consists exactly of these finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, hsame transport, Cont replay, package provenance, and local naming rows;
\item dense-source compatibility, requiring every completion-facing consumer to read $M$ and $D$ before the handoff row $C$;
\item separated-classifier exactness, requiring every comparison of completion readings to pass through $Z$ after $C$ has been displayed;
\item uniqueness-boundary exactness, requiring every asserted uniqueness read to be exhausted by $U$ over the same $M,D,C,Z$ route;
\item transport replay, requiring $H,R,T$ to preserve the ordered route under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item ledger non-escape, excluding quotient completions, selected representatives, host equality, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:separated-completion-carrier}. The tuple displays the source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, structural transport rows, provenance, and local naming.

Dense-source compatibility is the first dependency order. The rows $M$ and $D$ must be present before $C$ can expose any completion-facing read, so no consumer can replace the dense embedding by a selected representative or external completion point.

Separated-classifier exactness is isolated in $Z$. Once $C$ has been displayed, comparison of completion readings is admitted only through the zero-distance classifier row, not through host equality of completed points.

The uniqueness boundary is the row $U$. It is read over the same $M,D,C,Z$ route and is therefore a local ledger comparison, not a quotient-completion uniqueness theorem outside the packet.

Finally, $H,R,T,P,N$ record transport, replay, route preservation, provenance, and local naming for exactly those rows. Since the carrier has no quotient, representative, choice, ambient-completeness, host-equality, or external-complete-space coordinate, the listed obligations exhaust the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.SeparatedCompletionUp.SeparatedCompletionCarrier\_semantic\_name\_certificate}

\begin{theorem}[SeparatedCompletion source-metric obligation]
\label{thm:separated-completion-source-metric-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every $\BHist$ or $\NameCert_{\SeparatedCompletionUp}$ read that exposes completion-facing metric data must first enter through the source metric row $M$. The later rows $D,C,Z,U,H,R,T,P,N$ may transport, replay, source, and name that read, but none of them supplies an independent source metric, an external complete metric space, a quotient completion, or host equality of completed points.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. The coordinate $M$ is the displayed source metric row and is the only carrier coordinate with source-metric status.

Apply \autoref{thm:separated-completion-namecert-obligations}. Carrier admission and dense-source compatibility place $M$ before the dense row $D$ and the completion handoff $C$, while the remaining rows only compare, transport, replay, source, and locally name the same displayed route.

Since the carrier has no external complete-space, quotient-completion, host-equality, or second source-metric coordinate, every metric read is a read through $M$ preserved by $H,R,T,P,N$.
\end{proof}

\begin{theorem}[SeparatedCompletion dense-embedding obligation]
\label{thm:separated-completion-dense-embedding-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every dense source read consumed by a completion-facing row must pass through the dense embedding row $D$ before the completion handoff row $C$ is public. No row of the packet may treat $C$, $Z$, or $U$ as a dense embedding unless the preceding $M,D$ route has already been displayed in the same $\BHist$ packet.
\end{theorem}
\begin{proof}
Read the displayed tuple in \autoref{def:separated-completion-carrier}. The row $D$ is the dense $\CompletionEmbeddingUp$ row, and $C$ is the downstream completion handoff row.

Use the dense-source compatibility clause of \autoref{thm:separated-completion-namecert-obligations}. It requires every completion-facing consumer to read $M$ and $D$ before $C$, so the handoff cannot be used as a substitute dense embedding.

The separated classifier $Z$ and uniqueness row $U$ are later rows over the same route. Thus a dense source read reaches $C,Z,U$ only after the displayed $M,D$ entrance has been recorded in $\BHist$ and replayed by the local $\Cont$ data.
\end{proof}

\begin{theorem}[SeparatedCompletion zero-distance obligation]
\label{thm:separated-completion-zero-distance-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every separated comparison must read the zero-distance classifier row $Z$ before any uniqueness-boundary row $U$ is consumed. The comparison is therefore a finite classifier route through $M,D,C,Z,U$ with $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local naming, not host equality, selected representatives, quotient completion equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The row $Z$ is the only separated zero-distance classifier row, while $U$ records uniqueness over the same source, dense, completion, and classifier route.

Apply separated-classifier exactness from \autoref{thm:separated-completion-namecert-obligations}. A comparison of completion readings reaches $Z$ only after $C$ has been displayed, and uniqueness-boundary exactness reads $U$ over that same $M,D,C,Z$ route.

The structural rows $H,R,T,P,N$ preserve, replay, source, and name the route without adding a second comparison principle. Because the excluded host-equality, representative, quotient, and ambient-completeness objects are absent from the carrier, every separated comparison must pass through $Z$ before $U$.
\end{proof}

\begin{definition}[SeparatedCompletion kernel route]
\label{def:separated-completion-kernel-route}
The separated-completion kernel route of an accepted carrier $S=(M,D,C,Z,U,H,R,T,P,N)$ is the ordered readback
$$
M,D \longmapsto C \longmapsto Z,U \longmapsto H,R,T,P,N .
$$
Thus every completion-facing consumer first reads the source metric row $M$ and dense embedding row $D$, then the completion handoff row $C$, then the separated classifier and uniqueness rows $Z,U$, and only then the transport, replay, provenance, and local naming rows $H,R,T,P,N$.
\end{definition}

\begin{theorem}[SeparatedCompletion separated-limit handoff]
\label{thm:separated-completion-separated-limit-handoff}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every separated completion comparison reaches the separated classifier row $Z$ and uniqueness boundary row $U$ only after the source metric row $M$, dense embedding row $D$, and completion handoff row $C$ have been displayed.
\end{theorem}
\begin{proof}
Use the carrier projection of \autoref{def:separated-completion-carrier} and the obligation order of \autoref{thm:separated-completion-namecert-obligations}. The rows $M$ and $D$ are the source and dense-entry surface, while $C$ is the only completion handoff row.

The separated classifier $Z$ and uniqueness boundary $U$ are downstream rows in the same carrier. Since the carrier has no separate comparison coordinate, a separated-limit handoff cannot inspect $Z$ or $U$ before the $M,D,C$ route has been read.
\end{proof}
\leanchecked{BEDC.Derived.SeparatedCompletionUp.SeparatedCompletionCarrier\_separated\_limit\_handoff}

\begin{theorem}[SeparatedCompletion L10 readback exhaustion]
\label{thm:separated-completion-l10-readback-exhaustion}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, the handoff row $C$ is exhausted by the finite L10 readbacks through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. It exports no quotient completion, selected representative, host equality of completed points, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project $C$ from the carrier of \autoref{def:separated-completion-carrier}. The definition identifies $C$ as the completion handoff row read through the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ naming spine.

Apply \autoref{thm:separated-completion-namecert-obligations}. The ledger non-escape clause states that quotient completions, selected representatives, host equality, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces are absent from the local surface.

Therefore every L10 readback of $C$ is exhausted by the displayed dyadic, stream, regular-rational, and real-name route, and no additional completion principle is exported.
\end{proof}

\begin{theorem}[SeparatedCompletion obligation surface]
\label{thm:separated-completion-obligation-surface}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every local $\NameCert_{\SeparatedCompletionUp}$ read starts with the displayed source row $M$, dense row $D$, completion handoff $C$, separated classifier $Z$, and uniqueness row $U$, then preserves that route through $\BHist$, $\hsame$, $\Cont$, provenance, and local naming data in $H,R,T,P,N$. The surface exports no quotient completion, selected representative, host equality, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $M,D,C,Z,U$ are the only source, dense, completion, separated-classifier, and uniqueness rows available to the local certificate.

The structural rows $H,R,T$ then transport and replay the same ordered route through $\hsame$ and $\Cont$ inside $\BHist$. The provenance and local naming rows $P,N$ attach the route to $\NameCert_{\SeparatedCompletionUp}$ without adding another completion object.

Since the carrier has no quotient-completion, representative-selection, host-equality, countable-choice, or Real-completeness coordinate, every obligation read is exhausted by the displayed rows.
\end{proof}

\begin{theorem}[SeparatedCompletion source-density triad]
\label{thm:separatedcompletion-source-density-triad}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every separated-completion consumer must read the source metric row $M$, dense embedding row $D$, and completion handoff row $C$ before it can read the separated classifier $Z$, the uniqueness boundary $U$, or any Real-facing seal exported by the packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. Its first three analytic rows are exactly $M,D,C$, while $Z$ and $U$ are later rows over the same displayed packet.

Apply \autoref{thm:separated-completion-namecert-obligations}. Dense-source compatibility requires $M,D$ before $C$, separated-classifier exactness requires $C$ before $Z$, and uniqueness-boundary exactness reads $U$ over the same $M,D,C,Z$ route.

The Real-facing seal is part of the completion handoff read through $C$. Hence no separated classifier, uniqueness, or Real-facing consumer can bypass the source-density triad.
\end{proof}

\begin{theorem}[SeparatedCompletion source-density factorization]\label{thm:separatedcompletion-source-density-factorization}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every completion-facing read that claims source density factors through the ordered prefix $M,D,C$ before the separated classifier $Z$, uniqueness boundary $U$, transport row $H$, replay row $R$, route ledger $T$, provenance row $P$, or local naming row $N$ is consumed. The factorization is the dense-source compatibility clause of the local NameCert obligations, not a quotient-completion read, selected representative, host equality of completed points, countable-choice schedule, or ambient Real-completeness assertion.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. The source metric row is $M$, the dense embedding row is $D$, and the completion handoff row is $C$; the remaining rows $Z,U,H,R,T,P,N$ are downstream of that prefix.

Apply \autoref{thm:separated-completion-namecert-obligations}. Its dense-source compatibility clause requires every completion-facing consumer to read $M$ and $D$ before the handoff row $C$ is public.

The structural rows $H,R,T,P,N$ can only transport, replay, preserve, source, and name the same displayed route. Since the carrier has no quotient-completion, selected-representative, host-equality, choice, or ambient-completeness coordinate, source density can only be read through $M,D,C$.
\end{proof}

\begin{theorem}[SeparatedCompletion uniqueness boundary scope]\label{thm:separatedcompletion-uniqueness-boundary-scope}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. The uniqueness boundary row $U$ is scoped only over the already displayed route $M,D,C,Z$ and the structural rows $H,R,T,P,N$. A consumer may read $U$ as the local separated-completion uniqueness boundary, but cannot use it as a quotient completion, a selected representative comparison, a host equality of completed points, a countable-choice selector, or an ambient Real-completeness theorem.
\end{theorem}
\begin{proof}
First read the source-density factorization of \autoref{thm:separatedcompletion-source-density-factorization}. It places every completion-facing read on the prefix $M,D,C$.

Next apply the separated-classifier exactness and uniqueness-boundary exactness clauses of \autoref{thm:separated-completion-namecert-obligations}. They place $Z$ after the handoff row $C$ and read $U$ over the same $M,D,C,Z$ route.

Finally attach $H,R,T,P,N$. These rows keep the uniqueness comparison inside displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ data. No listed row supplies an external completion object, a selected representative, host equality, choice, or ambient completeness.
\end{proof}

\begin{theorem}[SeparatedCompletion Real-seal nonescape]\label{thm:separatedcompletion-realseal-nonescape}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Any Real-facing seal exported by the packet is read through the completion handoff row $C$ after $M,D$ and before the separated uniqueness surface $Z,U,H,R,T,P,N$ is consumed. The seal remains a finite route through the displayed $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows; it cannot escape into quotient completion, selected representatives, host equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the carrier row $C$. By \autoref{def:separated-completion-carrier}, $C$ is the completion handoff read through the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ L10 naming spine.

Use \autoref{thm:separatedcompletion-source-density-factorization}. The handoff row $C$ is reachable only after the source metric row $M$ and dense embedding row $D$ have been displayed.

Use \autoref{thm:separatedcompletion-uniqueness-boundary-scope}. The later separated rows $Z,U,H,R,T,P,N$ preserve and name the same handoff route rather than adding an external Real-completion principle. Therefore every Real-facing seal stays inside the displayed carrier and cannot introduce the excluded quotient, representative, host-equality, choice, or completeness objects.
\end{proof}

\begin{theorem}[SeparatedCompletion seal uniqueness]
\label{thm:separated-completion-seal-uniqueness}
For accepted packets $S=(M,D,C,Z,U,H,R,T,P,N)$ and $S'=(M,D,C,Z,U',H',R',T',P,N')$ with the same displayed source, dense, completion, separated-classifier, and provenance rows, any equality-of-export read between their completion seals is determined by the local uniqueness rows $U,U'$ together with the $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ data in $H,R,T,N$ and $H',R',T',N'$. It is not a quotient completion, selected representative comparison, host equality, countable-choice selection, or ambient Real-completeness conclusion.
\end{theorem}
\begin{proof}
The shared rows $M,D,C,Z,P$ fix the source metric, dense embedding, completion handoff, separated classifier, and provenance surface for both packets.

Any remaining comparison must therefore inspect $U,U'$ and the corresponding transport, replay, route-preservation, and local naming rows. These rows compare completion exports only over the already displayed route.

No carrier coordinate supplies quotient equality, selected representatives, host equality, choice, or Real completeness. Thus seal uniqueness is local to $U,U'$ and the displayed $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ data.
\end{proof}

\begin{theorem}[SeparatedCompletion diagonal classifier obligation]
\label{thm:separatedcompletion-diagonal-classifier-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every diagonal classifier read comparing a completion-facing row with itself is forced through the separated classifier row $Z$ after the dense route $M,D,C$ has been displayed. The read is a $\BHist$-visible zero-distance comparison preserved by $\hsame$ and $\Cont$ data, not a host equality, quotient-completion equality, selected representative, countable-choice schedule, or ambient $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. The only separated comparison coordinate is $Z$, and it appears downstream from the source metric row $M$, dense embedding row $D$, and completion handoff row $C$.

Apply the NameCert obligations of \autoref{thm:separated-completion-namecert-obligations}. They require dense-source compatibility before $C$ is consumed and separated-classifier exactness before any comparison is public.

The diagonal case does not add a new coordinate. Transport and replay are still the displayed rows $H,R,T$, so the comparison remains inside the local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface. Since the excluded objects have no carrier field, the diagonal classifier obligation is forced through $Z$.
\end{proof}

\begin{theorem}[SeparatedCompletion separated-limit handoff obligation]
\label{thm:separatedcompletion-separated-limit-handoff}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every separated-limit handoff read must pass through the source metric row $M$, dense embedding row $D$, completion handoff row $C$, separated classifier row $Z$, and uniqueness boundary row $U$ before the structural rows $H,R,T,P,N$ are consumed. No consumer can obtain that handoff from a quotient completion, a selected representative, host equality of completed points, countable choice, or an ambient Real-completeness coordinate.
\end{theorem}
\begin{proof}
Start with the dense route. The carrier exposes $M,D,C$ as the only entrance to completion-facing reads, and \autoref{thm:separated-completion-dense-factorization} makes every such read factor through that entrance.

Next read the separated boundary. The classifier row $Z$ and uniqueness row $U$ are later rows in the same accepted packet, so a separated-limit handoff can consume them only after the dense handoff is visible.

Finally attach $H,R,T,P,N$. These rows transport, replay, source, and name the same route rather than adding another completion object. The carrier therefore supplies no quotient, selected representative, host equality, choice, or ambient completeness coordinate from which a bypassing handoff could be read.
\end{proof}

\begin{theorem}[SeparatedCompletion nonescape obligation]
\label{thm:separatedcompletion-nonescape-obligation}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, the local $\NameCert_{\SeparatedCompletionUp}$ surface exports only the displayed rows $M,D,C,Z,U,H,R,T,P,N$. It exports no quotient completion, no selected representative, no countable-choice schedule, no host equality of completed points, and no ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Use the carrier admission and obligation surface of \autoref{def:separated-completion-carrier} and \autoref{thm:separated-completion-namecert-obligations}. They enumerate exactly the rows available to the accepted packet.

The dense route $M,D,C$, the separated classifier $Z$, and the uniqueness boundary $U$ account for the analytic part of the surface. The structural rows $H,R,T,P,N$ account for componentwise $\hsame$ transport, displayed $\Cont$ replay, route preservation, provenance, and local naming.

There is no remaining coordinate to project a quotient completion, representative selector, choice schedule, host equality, or ambient Real-completeness theorem. Hence every exported obligation remains inside the displayed finite carrier.
\end{proof}

\begin{theorem}[SeparatedCompletion window transport]
\label{thm:separated-completion-window-transport}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. If a completion-facing window read is transported componentwise by the displayed $\hsame$ row $H$, then the transported read remains on the same $M,D,C,Z,U$ route and is replayed by the displayed $\Cont$ row $R$ and transport ledger $T$ before the local $\NameCert_{\SeparatedCompletionUp}$ row $N$ is inspected. The transport introduces no quotient completion, selected representative, host equality, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start from the window read over $M,D,C$. These rows fix the source metric, dense source, and completion handoff before any separated comparison is available.

Apply the displayed $\hsame$ row $H$ componentwise. The transport is a movement of the already displayed $\BHist$ rows, not a selection of a new representative or a quotient completion class.

The $\Cont$ replay row $R$ and the transport ledger $T$ then replay the same route through $Z,U,P,N$. Since all excluded principles are absent from the carrier, transported windows remain inside the local NameCert surface.
\end{proof}

\begin{theorem}[SeparatedCompletion dense factorization]
\label{thm:separated-completion-dense-factorization}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every completion-facing consumer read factors through the finite dense route
$$
M,D\longmapsto C\longmapsto Z\longmapsto U\longmapsto H,R,T,P,N .
$$
Thus source metric data enter the separated-completion boundary only through the displayed metric-completion and dense-embedding rows before any separated classifier or uniqueness boundary can be consumed.
\end{theorem}
\leanchecked{BEDC.Derived.SeparatedCompletionUp.SeparatedCompletionDenseFactorization}
\begin{proof}
Begin with an accepted consumer read. Carrier admission gives the rows $M,D,C,Z,U,H,R,T,P,N$ and no other completion coordinate.

The source part is $M,D$. The metric-completion row admits the request, and the dense embedding row carries source observations into the completion-facing interface.

The handoff row $C$ is read only after that source part is fixed. Its L10 route is the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ naming spine, so the consumer cannot replace it by a quotient stream or selected host limit.

The separated classifier $Z$ and uniqueness boundary $U$ are downstream of the same handoff. Transport, replay, provenance, and local naming in $H,R,T,P,N$ preserve this route and add no external completion object.
\end{proof}

\begin{theorem}[SeparatedCompletion uniqueness boundary]
\label{thm:separated-completion-uniqueness-boundary}
For accepted packets
$$
S=(M,D,C,Z,U,H,R,T,P,N)
\quad\text{and}\quad
S'=(M,D,C,Z,U',H',R',T',P,N')
$$
over the same source metric row, dense embedding, completion handoff, separated classifier, and package provenance, every comparison between their completion-facing exports is exhausted by the uniqueness rows $U,U'$ together with the displayed transport and replay rows $H,R,T$ and $H',R',T'$.
\end{theorem}
\begin{proof}
The shared coordinates $M,D,C,Z,P$ fix the metric-completion source, the dense embedding route, the completion handoff, the separated classifier, and the provenance surface for both packets.

The remaining comparison data are $U,H,R,T,N$ and $U',H',R',T',N'$. The uniqueness rows compare completion-facing presentations over the same shared route, while the transport and replay rows display the permitted movements of that route.

No further field remains from which a consumer could read quotient-completion equality, a selected representative, host equality, countable choice, ambient $\RealUp$ completeness, or a hidden complete metric space. The uniqueness judgement is therefore exactly the displayed local boundary.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy-equivalence source]
\label{thm:separatedcompletion-cauchy-equivalence-source}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every comparison between separated-completion exports first reads the $\RegularCauchyCompletionSeparatedUp$ and $\CauchySequenceEquivalenceUp$ source rows carried by $M,D,C$ before the separated classifier row $Z$ is available. The comparison route is therefore sourced in displayed Cauchy-equivalence data over the same source metric and dense embedding, not in quotient completions, selected representatives, host equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a comparison read of an accepted packet. Carrier admission exposes $M,D,C,Z,U,H,R,T,P,N$ and no other completion coordinate.

The source of the read is the $M,D,C$ route. The metric row and dense embedding row fix the source side, while the completion handoff records the regular-Cauchy separated completion and Cauchy-sequence equivalence data consumed by the comparison.

Only after that source route is displayed may $Z$ classify separated completion readings. Since the carrier has no quotient-completion, selected-representative, host-equality, choice, Real-completeness, or hidden-complete-space coordinate, no comparison can bypass the displayed Cauchy-equivalence source.
\end{proof}

\begin{theorem}[SeparatedCompletion Cauchy reflector obligation]
\label{thm:separatedcompletion-cauchy-reflector-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every Cauchy-reflector read exposed by $S$ first displays the $\CauchyCompletionReflectorUp$ route and the dense embedding route inside the $M,D,C$ rows, then reads the separated comparison row $Z$. The obligation is a $\BHist$ and $\NameCert$ row route through $M,D,C,Z,H,R,T,P,N$, not parameter transport over an external completion object.
\end{theorem}
\begin{proof}
Start from \autoref{thm:separatedcompletion-cauchy-equivalence-source}. It places every comparison behind the displayed Cauchy-equivalence and regular separated-completion source rows carried by $M,D,C$.

The reflector read is therefore not a free-standing map. Its source side is the displayed CauchyCompletionReflector row, while the dense embedding row $D$ records the admission route into the completion handoff $C$.

Only after those rows are visible can $Z$ compare separated completion readings. The structural rows $H,R,T,P,N$ transport, replay, source, and locally name the same route, so the Cauchy reflector obligation is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[SeparatedCompletion source-density obligation]
\label{thm:separatedcompletion-source-density-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every completion-facing obligation first reads the source metric row $M$ and dense embedding row $D$, then passes through the completion handoff $C$ before the separated zero-distance classifier row $Z$ or the uniqueness row $U$ is public. The source-density route is recorded by $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and it admits no quotient completion, selected representative, host equality, countable choice, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Project the accepted packet of \autoref{def:separated-completion-carrier}. The source metric row $M$ and dense embedding row $D$ are the displayed entrance into every separated completion obligation.

Use dense factorization, \autoref{thm:separated-completion-dense-factorization}. It places the completion handoff $C$ downstream from the source metric and dense embedding route, so a consumer cannot start from separated comparison or uniqueness data alone.

The classifier and uniqueness rows are therefore later reads. The row $Z$ compares only after the source-density route has been displayed, and $U$ records uniqueness over that same route.

The structural rows $H,R,T,P,N$ preserve, replay, source, and name the route. Since the carrier has no coordinate for quotient completions, selected representatives, host equality, countable choice, or ambient Real completeness, those objects are refused by the obligation surface.
\end{proof}

\begin{theorem}[SeparatedCompletion zero-distance classifier obligation]
\label{thm:separatedcompletion-zero-distance-classifier-obligation}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. The separated zero-distance classifier row $Z$ is available only after the source metric route $M$, dense embedding route $D$, and completion handoff $C$ have been displayed. It classifies completion reads through the separated zero-distance row of the packet, not through quotient completion equality, selected representatives, host equality of completed points, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the Cauchy reflector obligation of \autoref{thm:separatedcompletion-cauchy-reflector-obligation}. It exposes the reflector route inside $M,D,C$ before separated comparison can be read.

Apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The theorem identifies $Z$ as the finite separated comparison boundary over the already displayed completion handoff.

The uniqueness and structural rows do not create a second classifier. The row $U$ reads uniqueness downstream from $Z$, while $H,R,T,P,N$ only transport, replay, source, and name the same comparison route.

Thus every zero-distance classifier obligation is carried by $M,D,C,Z,U,H,R,T,P,N$. The excluded quotient, representative, host-equality, choice, and ambient-completeness objects have no carrier coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion completion reflector route]
\label{thm:separatedcompletion-completion-reflector-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every completion reflector handoff exported by $S$ follows the route from the source metric and dense embedding rows $M,D$ through the completion handoff $C$, the separated zero-distance classifier $Z$, the uniqueness boundary $U$, and the structural rows $H,R,T,P,N$. A downstream reflector consumer receives that finite route only; it receives no quotient completion, selected representative, host equality, countable choice, hidden complete metric space, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Use the source-density obligation, \autoref{thm:separatedcompletion-source-density-obligation}, to fix the entrance of the reflector route at $M,D,C$. The completion reflector cannot be read before the source metric and dense embedding rows have been displayed.

Next use the zero-distance classifier obligation, \autoref{thm:separatedcompletion-zero-distance-classifier-obligation}. It makes $Z$ the separated comparison boundary for the same handoff route, rather than an equality imported from a quotient completion.

Attach the existing reflector handoff through \autoref{thm:separatedcompletion-completion-reflector-handoff}. The uniqueness row $U$ and the rows $H,R,T,P,N$ preserve, replay, source, and name the reflector route for downstream completion consumers.

No remaining coordinate names a selected representative, host equality, countable-choice schedule, hidden complete metric space, or ambient Real completeness theorem. The completion reflector handoff is therefore exactly the displayed finite packet route.
\end{proof}

\begin{theorem}[SeparatedCompletion Real seal nonescape]
\label{thm:separatedcompletion-real-seal-nonescape}
Every $\RealUp$ seal read accepted by a $\SeparatedCompletionUp$ carrier remains downstream of the displayed $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$ rows carried through $M,D,C$. The seal may be consumed by the separated classifier $Z$ and uniqueness boundary $U$, but it cannot expose host real equality, ambient $\RealUp$ completeness, quotient completion equality, selected representatives, or countable choice.
\end{theorem}
\begin{proof}
Read the source route $M,D,C$ first. These rows carry the metric-completion source, dense embedding, regular rational readback, finite stream windows, and dyadic tolerance evidence before any separated comparison is inspected.

The $\RealUp$ seal is reached only after that finite route. It records terminal readback data for the displayed completion route rather than an ambient completeness theorem.

Now apply the separated classifier and uniqueness rows $Z,U$. They consume the seal downstream of the same packet, while $H,R,T,P,N$ merely transport, replay, source, and name the route. Since no excluded real or completion principle is a carrier coordinate, the seal cannot escape the displayed rows.
\end{proof}

\begin{theorem}[SeparatedCompletion universal route exhaustion]
\label{thm:separatedcompletion-universal-route-exhaustion}
For every accepted $\SeparatedCompletionUp$ carrier, the universal completion route is exhausted by the displayed rows
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The route exports dense-source admission, Cauchy-equivalence sourcing, separated comparison, uniqueness boundary, transport, replay, provenance, and local naming, but it exports no quotient completion, selected representative, host equality, countable choice, ambient $\RealUp$ completeness, or additional universal completion principle outside the carrier.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. Its displayed rows are exactly the source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, transport, replay, provenance, and local naming rows.

Use dense factorization and the Cauchy-equivalence source theorem. They place the universal read behind $M,D,C$ before $Z$ or $U$ can be inspected.

The separated comparison and uniqueness rows then account for the completion-facing universal property available to consumers. No further coordinate remains for quotient completion, representative selection, host equality, choice, or ambient completeness.

Finally $H,R,T,P,N$ preserve the same row list. Thus the displayed carrier exhausts the universal route and exports no completion principle beyond the finite packet.
\end{proof}

\begin{theorem}[SeparatedCompletion universal separated factorization]
\label{thm:separatedcompletion-universal-separated-factorization}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every universal completion read accepted through $S$ passes through $M,D,C$ before the separated classifier $Z$ or the uniqueness row $U$ may be consumed. The separated equality read is zero-distance evidence over the same displayed route, not quotient equality, host equality of completed points, selected representative equality, or an ambient completion equality.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. The only universal completion route available to the packet is the displayed row list $M,D,C,Z,U,H,R,T,P,N$.

Use dense factorization, \autoref{thm:separated-completion-dense-factorization}, and universal route exhaustion, \autoref{thm:separatedcompletion-universal-route-exhaustion}. Together they place every universal read behind the source metric, dense embedding, and completion handoff rows $M,D,C$.

Now apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The separated classifier row $Z$ reads equality as displayed zero-distance evidence over that same handoff, while $U$ reads uniqueness only after the classifier route is exposed.

Finally use nonescape, \autoref{thm:separated-completion-nonescape}. Since quotient equality, host equality, selected representatives, and ambient completion equality have no field in the accepted carrier, they cannot replace the displayed zero-distance route.
\end{proof}

\begin{theorem}[SeparatedCompletion zero-distance factorization]
\label{thm:separatedcompletion-zero-distance-factorization}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. The separated classifier route factors through the $\MetricCompletionUp$, $\SeparatedMetricUp$, $\RegSeqRatUp$, and $\RealUp$ zero-distance evidence displayed by $M,C,Z$. Thus a separated-completion equality read is a finite zero-distance handoff through the local packet, not a quotient completion, a selected representative, host equality, countable choice, or an ambient $\RealUp$ completeness assertion.
\end{theorem}
\begin{proof}
Read the route in order. The row $M$ supplies the metric-completion admission boundary, and $C$ supplies the finite L10 handoff through regular rational readback toward the Real-facing seal.

The row $Z$ then reads that handoff as $\SeparatedMetricUp$ zero-distance evidence. Its classifier compares displayed completion readings by zero distance after the $\RegSeqRatUp$ and $\RealUp$ rows have been reached through $C$.

Transport, replay, provenance, and local naming in $H,R,T,P,N$ preserve the same factorization. No field remains for quotient completion equality, selected representatives, host equality, countable choice, or ambient Real completeness.
\end{proof}

\begin{theorem}[SeparatedCompletion limit-uniqueness export]
\label{thm:separatedcompletion-limit-uniqueness-export}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, the public limit-uniqueness export is exactly the local boundary $U$ over the already displayed $M,D,C,Z$ route. The export contains no separate uniqueness principle over quotient completions, selected representatives, host equality, countable choice, ambient $\RealUp$ completeness, or hidden complete metric spaces.
\end{theorem}
\begin{proof}
Carrier admission makes $U$ the only uniqueness-boundary row in the packet. Its hypotheses and conclusion are read over the same source metric, dense embedding, completion handoff, and separated classifier rows $M,D,C,Z$.

The transport and replay rows $H,R,T$ can move this boundary componentwise, but they do not create a second uniqueness coordinate. The package and local naming rows $P,N$ record the same source list.

Therefore every public uniqueness export is the local $U$ boundary over $M,D,C,Z$. The excluded quotient, representative, host-equality, choice, Real-completeness, and hidden-complete-space objects are absent from the carrier and cannot be exported.
\end{proof}

\begin{theorem}[SeparatedCompletion dense uniqueness interface]
\label{thm:separatedcompletion-dense-uniqueness-interface}
Let
$$
S=(M,D,C,Z,U,H,R,T,P,N)
\quad\text{and}\quad
S'=(M,D,C,Z,U',H',R',T',P,N')
$$
be accepted $\SeparatedCompletionUp$ carriers with the same dense-source route $M,D,C$ and the same zero-distance separated classifier $Z$. Then any completion-facing comparison between their exports exposes the same limit-uniqueness boundary through $U,U'$ together with the displayed transport and replay rows. It exports no quotient representative, no selected completion point, no host equality of completed points, no countable-choice schedule, and no ambient $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Use the dense factorization of \autoref{thm:separated-completion-dense-factorization}. Every completion-facing read of either packet first passes through the shared source metric, dense embedding, and completion handoff rows $M,D,C$.

Use the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}. Since the separated classifier row $Z$ is also shared, the comparison is read as zero-distance evidence over the same finite route rather than as host equality of completed points.

Apply the limit-uniqueness export of \autoref{thm:separatedcompletion-limit-uniqueness-export} to both packets. The only remaining uniqueness data are $U,U'$ and the displayed transport and replay rows $H,R,T$ and $H',R',T'$. The carrier has no quotient representative, selected completion point, choice schedule, or ambient completeness coordinate, so the dense uniqueness interface exports exactly that local boundary.
\end{proof}

\begin{theorem}[SeparatedCompletion source-comparison exhaustion]
\label{thm:separatedcompletion-source-comparison-exhaustion}
Let
$$
S=(M,D,C,Z,U,H,R,T,P,N)
\quad\text{and}\quad
S'=(M,D,C,Z,U',H',R',T',P,N')
$$
be accepted $\SeparatedCompletionUp$ carriers over the same source metric row, dense embedding, completion handoff, separated classifier, and provenance surface. Every accepted comparison between their separated-completion exports is exhausted by the shared $M,D,C,Z$ source route, by the uniqueness rows $U,U'$, and by the displayed transport and replay rows $H,R,T$ and $H',R',T'$. The comparison exports no quotient completion, selected representative, host equality of completed points, countable-choice schedule, ambient $\RealUp$ completeness theorem, or hidden complete metric space.
\end{theorem}
\begin{proof}
First use the dense factorization of \autoref{thm:separated-completion-dense-factorization}. It sends every completion-facing read through the shared source metric row $M$, dense embedding row $D$, and completion handoff row $C$ before any separated classifier or uniqueness boundary is consumed.

Next use the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}. The shared classifier $Z$ reads the comparison as zero-distance evidence over the same finite route, so the comparison cannot be replaced by host equality of completed points.

Now apply the limit-uniqueness export of \autoref{thm:separatedcompletion-limit-uniqueness-export} to both packets. The only remaining comparison rows are $U,U'$ together with the displayed transport and replay ledgers.

Finally attach the Cauchy-equivalence source theorem, \autoref{thm:separatedcompletion-cauchy-equivalence-source}. It keeps the comparison sourced in the displayed Cauchy-equivalence and dense-completion data carried by $M,D,C$. Since the carriers contain no excluded completion coordinate, the listed rows exhaust the accepted comparison surface.
\end{proof}

\begin{theorem}[SeparatedCompletion non-escape]
\label{thm:separated-completion-nonescape}
Every accepted $\SeparatedCompletionUp$ carrier exports only the rows
$$
M,D,C,Z,U,H,R,T,P,N
$$
of \autoref{def:separated-completion-carrier}. No consumer of the packet can obtain a quotient completion, selected representative, host equality of completed points, countable-choice schedule, ambient $\RealUp$ completeness theorem, or hidden complete metric space.
\end{theorem}
\begin{proof}
The NameCert obligations of \autoref{thm:separated-completion-namecert-obligations} enumerate the carrier, dense-source, separated-classifier, uniqueness-boundary, transport-replay, and refusal rows available to the packet.

The dense factorization of \autoref{thm:separated-completion-dense-factorization} covers every completion-facing consumer read. Such a read must traverse $M,D,C,Z,U,H,R,T,P,N$ and cannot bypass the finite route through a host completion object.

The uniqueness boundary of \autoref{thm:separated-completion-uniqueness-boundary} covers every comparison between completion-facing exports. Since the carrier has no additional coordinate beyond the displayed rows, none of the excluded quotient, representative, host-equality, choice, Real-completeness, or hidden-complete-space objects can be projected from an accepted packet.
\end{proof}

\begin{theorem}[SeparatedCompletion choice-free source route]
\label{thm:separatedcompletion-choice-free-source-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every accepted source-to-uniqueness read exposes the source metric row $M$, dense embedding row $D$, completion handoff row $C$, and separated classifier row $Z$ before any uniqueness row $U$ is available. The route is carried by displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and cannot expose choice data, quotient completion data, selected representatives, or host equality of completed points.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:separated-completion-carrier}. Its displayed rows are $M,D,C,Z,U,H,R,T,P,N$, so the source metric, dense embedding, completion handoff, and separated classifier are present before the uniqueness boundary can be projected.

Apply the dense factorization theorem, \autoref{thm:separated-completion-dense-factorization}. It fixes the order $M,D\mapsto C\mapsto Z\mapsto U$ for completion-facing reads.

Apply the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization} and the source-comparison exhaustion theorem, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. These results keep the comparison in displayed Cauchy and zero-distance data rather than in quotient or host equality data.

The structural support rows are exactly $H,R,T,P,N$: componentwise $\hsame$ transport, displayed $\Cont$ replay, route preservation, $\Pkg$ provenance, and local $\NameCert$ admission. Since the carrier contains no choice, quotient completion, selected-representative, or host-equality coordinate, the source route is choice-free.
\end{proof}

\begin{theorem}[SeparatedCompletion regular-Cauchy source route]
\label{thm:separatedcompletion-regular-cauchy-source-route}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every regular-Cauchy source read used by the separated-completion boundary factors through the displayed source metric row $M$, dense embedding row $D$, completion handoff row $C$, and separated classifier row $Z$ before the uniqueness row $U$ and the structural rows $H,R,T,P,N$ are consumed. The route may use the dense factorization of \autoref{thm:separated-completion-dense-factorization}, the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}, and the source-comparison exhaustion of \autoref{thm:separatedcompletion-source-comparison-exhaustion}, but it cannot add quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or hidden complete metric spaces.
\end{theorem}
\begin{proof}
Start with carrier admission. The visible rows are exactly $M,D,C,Z,U,H,R,T,P,N$, so any regular-Cauchy source read must begin inside the displayed carrier inventory.

Apply dense factorization, \autoref{thm:separated-completion-dense-factorization}. It fixes $M,D$ as the source prefix and $C$ as the completion handoff reached from that prefix.

Apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The separated classifier row $Z$ reads equality through zero-distance evidence over the same handoff, not through host equality of completed points.

Finally use source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It leaves only $U,H,R,T,P,N$ as the downstream uniqueness, transport, replay, route, provenance, and naming rows, and the excluded completion and choice objects have no coordinate in the carrier.
\end{proof}

\begin{theorem}[SeparatedCompletion Hausdorff uniqueness route]
\label{thm:separatedcompletion-hausdorff-uniqueness-route}
For accepted $\SeparatedCompletionUp$ carriers over displayed rows $M,D,C,Z,U,H,R,T,P,N$, every Hausdorff-style uniqueness read is exhausted by the dense source route $M,D,C$, the zero-distance separated classifier $Z$, the uniqueness boundary $U$, and the transport, replay, route, provenance, and local naming rows $H,R,T,P,N$. The read is a local separated-completion boundary over the theorems \autoref{thm:separated-completion-dense-factorization}, \autoref{thm:separatedcompletion-zero-distance-factorization}, and \autoref{thm:separatedcompletion-source-comparison-exhaustion}; it is not a quotient completion, a selected representative, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or a hidden complete metric space.
\end{theorem}
\begin{proof}
Read the dense source route first. By \autoref{thm:separated-completion-dense-factorization}, a uniqueness consumer must pass through $M,D,C$ before reaching any separated classifier or uniqueness row.

Read the separated classifier next. By \autoref{thm:separatedcompletion-zero-distance-factorization}, $Z$ supplies the zero-distance route that replaces host equality inside the accepted packet.

The Hausdorff-style uniqueness boundary is then the local row $U$ together with the structural rows $H,R,T,P,N$. These rows transport, replay, preserve, source, and name the same displayed route.

Source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}, closes the comparison surface. Since quotient completions, selected representatives, host equality, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces are absent from $M,D,C,Z,U,H,R,T,P,N$, they cannot enter the uniqueness read.
\end{proof}

\begin{theorem}[SeparatedCompletion metric-completion handoff]
\label{thm:separatedcompletion-metric-completion-handoff}
Every metric-completion handoff exported by an accepted $\SeparatedCompletionUp$ carrier factors through the displayed rows
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The handoff uses the dense route of \autoref{thm:separated-completion-dense-factorization}, the zero-distance route of \autoref{thm:separatedcompletion-zero-distance-factorization}, and the exhausted comparison surface of \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It exports no quotient completion, selected representative, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or hidden complete metric space.
\end{theorem}
\begin{proof}
Project the accepted carrier. The metric-completion source row $M$, dense embedding row $D$, and completion handoff row $C$ form the only displayed metric-completion prefix.

Use \autoref{thm:separated-completion-dense-factorization}. It sends every completion-facing handoff through $M,D,C$ before any separated or uniqueness boundary is available.

Use \autoref{thm:separatedcompletion-zero-distance-factorization}. The row $Z$ is the separated comparison route available after the completion handoff, and it is finite zero-distance evidence rather than host equality.

Use \autoref{thm:separatedcompletion-source-comparison-exhaustion}. The remaining rows $U,H,R,T,P,N$ exhaust the uniqueness, transport, replay, route, provenance, and naming surface. Because the carrier has no quotient-completion, selected-representative, host-equality, choice, Real-completeness, or hidden-complete-space coordinate, the metric-completion handoff exports only the displayed finite route.
\end{proof}

\begin{theorem}[SeparatedCompletion filtered limit boundary]
\label{thm:separatedcompletion-filtered-limit-boundary}
For an accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, every filtered limit-boundary read is exhausted by the Cauchy-equivalence source rows displayed by $M,D,C$, the zero-distance separated classifier row $Z$, the local uniqueness row $U$, and the transport and replay rows $H,R,T$. It exports no additional limit selector, quotient class, host equality, countable-choice schedule, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Read the source side first. The Cauchy-equivalence source theorem, \autoref{thm:separatedcompletion-cauchy-equivalence-source}, places every comparison over the displayed $M,D,C$ route.

Read the classifier next. The zero-distance factorization theorem, \autoref{thm:separatedcompletion-zero-distance-factorization}, makes $Z$ the only separated comparison row available after the completion handoff.

Read the boundary row. The limit-uniqueness export theorem, \autoref{thm:separatedcompletion-limit-uniqueness-export}, identifies $U$ as the public uniqueness boundary over the same $M,D,C,Z$ route.

Finally apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It includes the displayed $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows and excludes any extra selector, quotient class, host equality, choice schedule, or ambient Real-completeness coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion completion-reflector handoff]
\label{thm:separatedcompletion-completion-reflector-handoff}
Every handoff from an accepted $\SeparatedCompletionUp$ carrier to $\CauchyCompletionReflectorUp$ or $\CompletionUniversalPropertyUp$ factors through the same finite source route
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The handoff may use the source metric, dense factorization, zero-distance factorization, limit-uniqueness export, source-comparison exhaustion, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row, but it cannot add a quotient completion, selected representative, host equality, countable choice, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project the accepted carrier and apply dense factorization from \autoref{thm:separated-completion-dense-factorization}. The handoff begins with $M,D,C$, so both reflector-facing and universal-property-facing reads share the same source metric, dense embedding, and completion handoff.

Apply the zero-distance factorization of \autoref{thm:separatedcompletion-zero-distance-factorization}. The separated classifier $Z$ is the only comparison route available before any uniqueness boundary is read.

Apply the limit-uniqueness export of \autoref{thm:separatedcompletion-limit-uniqueness-export} and the source-comparison exhaustion theorem, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. Together they identify $U$ and the transport and replay rows $H,R,T$ as the complete handoff boundary.

The provenance and local naming rows $P,N$ attach the boundary to $\Pkg$ and $\NameCert$ data. Because the carrier contains no quotient-completion, selected-representative, host-equality, choice, or ambient-completeness coordinate, a $\CauchyCompletionReflectorUp$ or $\CompletionUniversalPropertyUp$ consumer receives only the displayed finite route.
\end{proof}

\begin{theorem}[SeparatedCompletion dense replay scope]
\label{thm:separatedcompletion-dense-replay-scope}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, every completion-facing read exposes the source metric row $M$, dense embedding row $D$, and completion handoff row $C$ before the separated classifier $Z$, uniqueness boundary $U$, transport row $H$, replay row $R$, route ledger $T$, provenance row $P$, or local naming row $N$ is consumed. Thus dense replay is a finite $M,D,C$ prefix over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data, not a selected representative or quotient-completion read.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:separated-completion-carrier}. The rows $M,D,C$ are the only source metric, dense embedding, and completion handoff coordinates.

Apply dense factorization, \autoref{thm:separated-completion-dense-factorization}. It places every completion-facing consumer read on the route $M,D\mapsto C$ before the separated classifier and uniqueness boundary are available.

Then use the choice-free source route, \autoref{thm:separatedcompletion-choice-free-source-route}. The structural rows $H,R,T,P,N$ preserve the same ordered route and do not introduce a choice coordinate, quotient completion, selected representative, or host equality of completed points.
\end{proof}

\begin{theorem}[SeparatedCompletion separated classifier scope]
\label{thm:separatedcompletion-separated-classifier-scope}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, zero-distance classification through $Z$ is the only separated equality route after the dense completion handoff $M,D,C$ has been displayed. Any completion-facing equality read that bypasses $Z$ leaves the $\NameCert_{\SeparatedCompletionUp}$ surface and cannot be recovered from $U,H,R,T,P,N$ alone.
\end{theorem}
\begin{proof}
Read the dense prefix first. By \autoref{thm:separatedcompletion-dense-replay-scope}, a completion-facing equality read has already exposed $M,D,C$ before it reaches any separated comparison row.

Now apply zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}. The classifier row $Z$ reads equality as displayed zero-distance evidence over the $\MetricCompletionUp$, $\SeparatedMetricUp$, $\RegSeqRatUp$, and $\RealUp$ route, rather than as host equality or quotient completion equality.

Finally apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. The uniqueness, transport, replay, provenance, and naming rows preserve a comparison once $Z$ is present, but none of them supplies an alternate separated equality route.
\end{proof}

\begin{theorem}[SeparatedCompletion obligation closure package]
\label{thm:separatedcompletion-obligation-closure-package}
The accepted $\SeparatedCompletionUp$ carrier
$$
S=(M,D,C,Z,U,H,R,T,P,N)
$$
supports an obligationClosure package whose finite boundary is exactly dense factorization, zero-distance factorization, source-comparison exhaustion, the choice-free source route, the filtered limit boundary, and the completion-reflector handoff. The package closes the paper-side obligation surface over the displayed rows and refuses quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces.
\end{theorem}
\begin{proof}
Build the source prefix from dense factorization, \autoref{thm:separated-completion-dense-factorization}, and dense replay scope, \autoref{thm:separatedcompletion-dense-replay-scope}. These results force every completion-facing read through $M,D,C$.

Build the classifier boundary from zero-distance factorization, \autoref{thm:separatedcompletion-zero-distance-factorization}, and separated classifier scope, \autoref{thm:separatedcompletion-separated-classifier-scope}. They make $Z$ the only separated equality route after the dense completion handoff.

Add the comparison and source routes from \autoref{thm:separatedcompletion-source-comparison-exhaustion} and \autoref{thm:separatedcompletion-choice-free-source-route}. These theorems keep all comparison data in displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally attach the filtered limit boundary, \autoref{thm:separatedcompletion-filtered-limit-boundary}, and the completion-reflector handoff, \autoref{thm:separatedcompletion-completion-reflector-handoff}. The resulting package contains no coordinate for quotient completions, selected representatives, host equality, countable choice, ambient Real completeness, or hidden complete metric spaces, so the obligation surface is closed at the paper level.
\end{proof}

\begin{theorem}[SeparatedCompletion choice-free endpoint package]
\label{thm:separatedcompletion-choice-free-endpoint-package}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, any endpoint comparison exported to $\MetricCompletionUp$, $\HausdorffCompletionUp$, $\RegularCauchyCompletionSeparatedUp$, $\RegSeqRatUp$, $\StreamNameUp$, or $\RealUp$ consumers factors through the displayed rows
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The exported comparison is the finite endpoint package obtained from dense-source admission, filtered limit boundary, choice-free source transport, completion uniqueness, and Cauchy-reflector handoff. It exports no quotient completion, selected representative, host equality of completed points, countable choice, hidden complete metric space, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with the dense route. Dense factorization, \autoref{thm:separated-completion-dense-factorization}, and dense replay scope, \autoref{thm:separatedcompletion-dense-replay-scope}, force every endpoint-facing read through $M,D,C$ before the separated classifier or uniqueness boundary is available.

Transport the limit boundary without a selector. The filtered limit boundary of \autoref{thm:separatedcompletion-filtered-limit-boundary} and the choice-free source route of \autoref{thm:separatedcompletion-choice-free-source-route} keep the read inside displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Thus the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ handoff remains a finite route through $C$ and cannot become a selected limit.

Attach the completion uniqueness package. The obligation closure package of \autoref{thm:separatedcompletion-obligation-closure-package} supplies the local uniqueness boundary over $Z,U,H,R,T,P,N$, while the Hausdorff uniqueness route of \autoref{thm:separatedcompletion-hausdorff-uniqueness-route} keeps the comparison separated rather than quotient-based.

Finally use the Cauchy-reflector handoff, \autoref{thm:separatedcompletion-completion-reflector-handoff}, together with the Cauchy reflector obligation of \autoref{thm:separatedcompletion-cauchy-reflector-obligation}. These results route $\MetricCompletionUp$, $\HausdorffCompletionUp$, and $\RegularCauchyCompletionSeparatedUp$ consumers through the same displayed endpoint rows. Since the carrier has no quotient, representative-selection, host-equality, choice, hidden-complete-space, or ambient-completeness coordinate, the endpoint package exports exactly the rows stated above.
\end{proof}

\begin{theorem}[SeparatedCompletion carrier admission root obligation]
\label{thm:separated-completion-carrier-admission-root-obligation}
Every accepted $\SeparatedCompletionUp$ carrier exposes only the displayed $\CauchySequenceEquivalenceUp$, $\CompletionEmbeddingUp$, $\CompletionUniversalPropertyUp$, $\HausdorffCompletionUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ rows before its local $\NameCert_{\SeparatedCompletionUp}$ row is read. The admission surface contains no additional completion point, quotient class, selected representative, host equality of completed points, countable-choice schedule, or hidden complete metric space.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-carrier}. The source, dense-embedding, completion handoff, separated classifier, and uniqueness rows are exactly $M,D,C,Z,U$.

Read these rows through the existing source route. The Cauchy-equivalence source theorem, \autoref{thm:separatedcompletion-cauchy-equivalence-source}, and the dense factorization theorem, \autoref{thm:separated-completion-dense-factorization}, place the admission boundary over $\CauchySequenceEquivalenceUp$, $\CompletionEmbeddingUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ data.

Then attach the uniqueness boundary from \autoref{thm:separated-completion-uniqueness-boundary}. It adds only the displayed $\CompletionUniversalPropertyUp$ and $\HausdorffCompletionUp$ rows over the same finite route. Since $H,R,T,P,N$ merely transport, replay, preserve, source, and name the displayed rows, the excluded completion objects have no carrier coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion classifier stability root obligation]
\label{thm:separated-completion-classifier-stability-root-obligation}
For any accepted $\SeparatedCompletionUp$ carriers over componentwise $\hsame$-transported $M,D,C,Z,U,H,R,T,P,N$ rows, the separated classifier exposed by $Z$ is preserved by the displayed transport and replay rows. This stability cannot introduce quotient-completion equality, selected representatives, host equality of completed points, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the transported carrier rows. Componentwise $\hsame$ transport acts on the displayed source metric, dense embedding, completion handoff, separated classifier, uniqueness boundary, replay, provenance, and local naming rows named by the carrier.

Apply separated classifier scope, \autoref{thm:separatedcompletion-separated-classifier-scope}. After the dense completion handoff, $Z$ is the only separated equality route available to a completion-facing read.

Finally apply source-comparison exhaustion, \autoref{thm:separatedcompletion-source-comparison-exhaustion}. It keeps transported comparisons inside $M,D,C,Z,U,H,R,T,P,N$. Because the transported packet has no quotient-completion or host-equality coordinate, classifier stability cannot create one.
\end{proof}

\begin{theorem}[SeparatedCompletion Real seal root obligation]
\label{thm:separated-completion-real-seal-root-obligation}
Any Real-facing seal read exported by an accepted $\SeparatedCompletionUp$ carrier factors through displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\MetricCompletionUp$ rows before the separated completion handoff is consumed. The seal read is therefore a finite BEDC route through $M,D,C,Z,U,H,R,T,P,N$, not an ambient $\RealUp$ completeness principle or a chosen completion representative.
\end{theorem}
\begin{proof}
Read the dense prefix first. By \autoref{thm:separatedcompletion-dense-replay-scope}, every completion-facing read exposes $M,D,C$ before any separated classifier, uniqueness boundary, or local naming row is available.

The opening carrier route identifies this prefix with the L10 spine through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, together with the $\MetricCompletionUp$ handoff. The Real-facing seal is therefore downstream from finite stream windows and regular rational readback.

Now apply the choice-free source route, \autoref{thm:separatedcompletion-choice-free-source-route}, and the completion-reflector handoff, \autoref{thm:separatedcompletion-completion-reflector-handoff}. They keep the separated completion handoff in displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and exclude ambient Real completeness, selected representatives, quotient completions, host equality, and countable choice.
\end{proof}

\begin{theorem}[SeparatedCompletion root obligation package]
\label{thm:separated-completion-root-obligation-package}
For every accepted $\SeparatedCompletionUp$ carrier, the carrier-admission, classifier-stability, and Real-seal root obligations of \autoref{thm:separated-completion-carrier-admission-root-obligation}, \autoref{thm:separated-completion-classifier-stability-root-obligation}, and \autoref{thm:separated-completion-real-seal-root-obligation} jointly exhaust the finite $\NameCert_{\SeparatedCompletionUp}$ surface over $\CauchyCompletionReflectorUp$, $\CompletionEmbeddingUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\RealUp$, and $\StreamNameUp$ rows. Thus every downstream completion consumer receives only displayed source admission, separated classifier stability, Real-seal readback, componentwise transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
The carrier-admission root obligation identifies the finite row inventory available to the accepted carrier. It confines every completion-facing read to the displayed source, dense embedding, completion handoff, separated classifier, uniqueness, transport, replay, provenance, and local naming rows.

The classifier-stability root obligation then fixes the separated equality surface. Transport and replay preserve the classifier row inside that same finite inventory, so no extra quotient representative or host equality coordinate appears after the carrier is admitted.

The Real-seal root obligation closes the remaining completion-to-Real route through the StreamName, RegSeqRat, DyadicRatCore, and MetricCompletion rows. Together the three obligations cover the root surface exposed to CauchyCompletionReflector, CompletionEmbedding, MetricCompletion, RegSeqRat, Real, and StreamName consumers, and none of them introduces quotient representatives, host equality, countable choice, or an ambient completeness coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion separated witness triad]
\label{thm:separated-completion-separated-witness-triad}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every separated-completion equality consumer must expose the dense source row $D$, the zero-distance classifier row $Z$, and the uniqueness boundary row $U$ in that order before any exported completion seal is read. The exposed triad is the root obligation witness over the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route; it is not a quotient completion, selected representative, host equality, countable-choice schedule, or completeness claim for $\RealUp$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $D,Z,U$ are already part of the finite inventory listed in \autoref{def:separated-completion-carrier}, with $D$ recording dense source admission, $Z$ recording separated zero-distance classification, and $U$ recording the uniqueness boundary over the same route.

Use the NameCert obligations of \autoref{thm:separated-completion-namecert-obligations}. Dense-source compatibility forces the consumer to read $D$ before the completion handoff can be inspected. Separated-classifier exactness then places $Z$ after the handoff, and uniqueness-boundary exactness places $U$ over the same $M,D,C,Z$ route.

The root obligation package, \autoref{thm:separated-completion-root-obligation-package}, binds these rows to the carrier-admission, classifier-stability, and Real-seal obligations. Thus an exported completion seal can be read only after the dense source row, zero-distance classifier, and uniqueness boundary have been displayed in the stated order.

The carrier has no coordinate for quotient completions, selected representatives, host equality, countable choice, or ambient $\RealUp$ completeness. The witness triad is therefore induction-ready because later consumers can recurse over the displayed rows $D,Z,U$ and their structural transport data, without selecting representatives or appealing to an external completion equality.
\end{proof}
