\begin{theorem}[SeparatedCompletion source-density scope]
\label{thm:separated-completion-source-density-scope}
Let $S=(M,D,C,Z,U,H,R,T,P,N)$ be an accepted $\SeparatedCompletionUp$ carrier. Every source-density read consumed by $S$ is scoped by the source metric row $M$, dense embedding row $D$, completion handoff row $C$, separated classifier row $Z$, uniqueness row $U$, componentwise transport $H$, displayed replay and route ledger $R,T$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$ through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The read may cite \autoref{def:separated-completion-carrier} and \autoref{thm:separated-completion-namecert-obligations}, but it exports no quotient completion, selected representative, host equality of completed points, countable-choice schedule, ambient $\RealUp$ completeness, or hidden complete metric space.
\end{theorem}
\begin{proof}
Project the accepted carrier. The source metric row, dense embedding row, completion handoff row, separated classifier row, uniqueness row, transport, replay, route ledger, provenance, and local name are exactly $M,D,C,Z,U,H,R,T,P,N$.

Apply the NameCert obligations of \autoref{thm:separated-completion-namecert-obligations}. They force dense-source compatibility through $M,D,C$ and keep every completion-facing read inside the same local packet.

Finally use the scoped route and quotient-exhaustion rows, \autoref{thm:separatedcompletion-scoped-route} and \autoref{thm:separatedcompletion-no-quotient-exhaustion}. These identify the public route as the displayed kernel surface through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, with the excluded completion objects absent from every coordinate.
\end{proof}

\begin{theorem}[SeparatedCompletion classifier scope]
\label{thm:separated-completion-classifier-scope}
For every accepted $\SeparatedCompletionUp$ carrier $S=(M,D,C,Z,U,H,R,T,P,N)$, a separated classifier read is scoped only after the source metric row $M$, dense embedding row $D$, and completion handoff row $C$ have been displayed. The classifier row $Z$, uniqueness row $U$, transport row $H$, replay and route rows $R,T$, provenance $P$, and local $\NameCert$ row $N$ bind the comparison to $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, citing the carrier and obligation surfaces of \autoref{def:separated-completion-carrier} and \autoref{thm:separated-completion-namecert-obligations}.
\end{theorem}
\begin{proof}
Read the source-density prefix first. By \autoref{thm:separated-completion-source-density-scope}, the rows $M,D,C$ are the only source, dense, and completion-handoff entrance for the accepted carrier.

Now inspect the classifier side. The separated classifier exactness clause of \autoref{thm:separated-completion-namecert-obligations} places $Z$ after $C$, and the uniqueness-boundary exactness clause reads $U$ over the same $M,D,C,Z$ route.

The structural rows $H,R,T,P,N$ preserve, replay, source, and name that route. Hence the classifier scope is a local BEDC kernel route through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, not a host equality or quotient-completion comparison.
\end{proof}

\begin{theorem}[SeparatedCompletion nonescape scope]
\label{thm:separated-completion-nonescape-scope}
Every public separated-completion read of an accepted $\SeparatedCompletionUp$ carrier is exhausted by the source metric row, dense embedding row, completion handoff row, separated classifier row, uniqueness row, transport, replay, route ledger, provenance, and local NameCert rows
$$
M,D,C,Z,U,H,R,T,P,N
$$
through the kernel rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Together with \autoref{thm:separated-completion-source-density-scope} and \autoref{thm:separated-completion-classifier-scope}, this excludes quotient completions, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, and hidden complete metric spaces from the scoped public surface.
\end{theorem}
\begin{proof}
Begin with the carrier and obligations. The carrier definition fixes $M,D,C,Z,U,H,R,T,P,N$ as the whole packet, and \autoref{thm:separated-completion-namecert-obligations} assigns source-density, separated-classifier, uniqueness, transport, replay, provenance, and naming roles to those rows.

Apply the source-density and classifier scope theorems. They place source reads through $M,D,C$ and separated comparisons through $Z,U$ after that prefix, with $H,R,T,P,N$ attached as structural BEDC rows.

Use quotient-exhaustion refusal, \autoref{thm:separatedcompletion-no-quotient-exhaustion}, for the negative side. Since none of the excluded objects is a carrier coordinate, every public read remains inside $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ over the displayed row inventory.
\end{proof}

\begin{theorem}[SeparatedCompletion scope-closure route]
\label{thm:separatedcompletion-scope-closure-route}
Every public $\SeparatedCompletionUp$ read of an accepted carrier factors through the ordered rows
$$
M,D,C,Z,U,H,R,T,P,N .
$$
The prefix $M,D,C$ supplies the source metric, dense embedding, and completion handoff scope of \autoref{thm:separated-completion-source-density-scope}; the rows $Z,U$ supply the separated classifier and uniqueness scope of \autoref{thm:separated-completion-classifier-scope}; and the rows $H,R,T,P,N$ preserve the same public route through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ as in \autoref{thm:separated-completion-nonescape-scope}. The route exports no quotient completion, selected representative, host equality of completed points, countable choice, ambient $\RealUp$ completeness, or hidden complete metric space.
\end{theorem}
\begin{proof}
Start with the source-density theorem. It identifies $M,D,C$ as the only entrance for source metric, dense embedding, and completion handoff data.

Next apply the classifier theorem. The separated classifier row $Z$ and uniqueness row $U$ are read only after that source-density prefix, so classifier comparison cannot detach from $M,D,C$.

Finally apply the nonescape theorem. It attaches $H,R,T,P,N$ to the same ordered carrier route and excludes quotient completions, selected representatives, host equality, countable choice, ambient real completeness, and hidden complete metric spaces from the public surface.
\end{proof}
