\chapter{A Concrete Naming Certificate for $\HeronSquareRootUp$}
\label{ch:concrete-instances-heron-square-root-namecert}
\origin{human}

From Heron's classical square-root iteration and Bishop-style constructive convergence, the $\HeronSquareRootUp$ packet records the finite dyadic evidence needed to run the Babylonian recurrence inside the L10 Real and Completion route. It refines the square-root service of \autoref{ch:concrete-instances-regular-cauchy-square-root-namecert} by exposing seed positivity, reciprocal accounting, contraction estimates, $\RegSeqRatUp$ readback, and the terminal $\RealUp$ seal as named rows. The packet sits beside $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, and $\NewtonIterationUp$; it is not a host square-root function, quotient-real equality, a selected completed limit, or an ambient completeness theorem.

\begin{definition}[Heron square-root carrier]
\label{def:heron-square-root-carrier}
A $\HeronSquareRootUp$ carrier is a finite $\BHist$ packet
$$
H=(A,S,R,L,W,D,K,Q,E,T,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the positive dyadic radicand row, including lower-bound and nonzero-denominator witnesses inside $\DyadicRatCoreUp$.
\item $S$ is the finite positive dyadic seed row from which the Heron recurrence starts.
\item $R$ is the reciprocal and division ledger row, recording the displayed divisions $A/x_i$ and every denominator witness used by the recurrence.
\item $L$ is the finite Heron ledger whose rows have the form $x_{i+1}=(x_i+A/x_i)/2$ and whose arithmetic is read only through $A,S,R$ and $\DyadicRatCoreUp$.
\item $W$ is the finite iteration-window row, exposing exactly the initial segment of $L$ requested by a precision consumer.
\item $D$ is the dyadic contraction-estimate row, recording the squared-error, halving, and tolerance comparisons that bound the visible window.
\item $K$ is the $\NewtonIterationUp$ provenance row showing that the displayed recurrence is the specialized Newton step for $x^2-A$ without importing a host root.
\item $Q$ is the $\RegSeqRatUp$ readback row produced from $A,S,R,L,W,D,K$.
\item $E$ is the $\RealUp$ seal row, available only after the regular readback row $Q$ has been displayed.
\item $T$ records componentwise $\hsame$ transport for the radicand, seed, reciprocal ledger, Heron ledger, window, contraction estimate, Newton provenance, readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of each precision request through $A,S,R,L,W,D,K,Q,E,T,P,N$.
\item $P$ is the $\Pkg$ provenance over $\HeronSquareRootUp$, $\DyadicRatCoreUp$, $\NewtonIterationUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HeronSquareRootUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a host square-root operation, quotient-real equality, selected limits, arbitrary real trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Heron square-root regular-Cauchy handoff]
\label{thm:heron-square-root-regular-cauchy-handoff}
Every accepted $\HeronSquareRootUp$ packet reaches $\RealUp$ only through the finite dyadic error ledger, $\RegSeqRatUp$ readback, and terminal Real seal displayed in
$$
A,S \longmapsto R,L,W,D,K \longmapsto Q \longmapsto E .
$$
Thus a Real or Completion consumer first sees the positive radicand and seed rows, then the reciprocal and division ledger, Heron recurrence window, dyadic contraction estimates, and $\NewtonIterationUp$ provenance, and only then may read the regular rational name and $\RealUp$ seal. The handoff exports no host square-root function, quotient-real equality, selected completed limit, arbitrary real trichotomy, or ambient completeness object.
\end{theorem}
\begin{proof}
Start with an accepted carrier $H=(A,S,R,L,W,D,K,Q,E,T,C,P,N)$. The carrier inventory exposes the positive dyadic radicand $A$ and seed $S$ before any recurrence row can be inspected.

The numerical ledger is finite. The reciprocal row $R$ stores the displayed divisions $A/x_i$, the Heron ledger $L$ stores the visible recurrence rows, the window row $W$ selects the requested finite segment, and the contraction row $D$ stores the dyadic error comparisons for that segment.

The route then records provenance through $K$. This row identifies the same displayed recurrence as the Newton step for $x^2-A$ through $\NewtonIterationUp$, but it contributes only finite ledger provenance and no external square-root value.

The consumer-facing read is downstream of those rows. The $\RegSeqRatUp$ row $Q$ is produced by replaying the finite dyadic ledger, and the $\RealUp$ seal $E$ is available only after $Q$ has been displayed.

The remaining rows $T,C,P,N$ transport, replay, record provenance, and name the same packet. Since the carrier contains no host square-root coordinate, quotient-real equality, selected limit, trichotomy classifier, or ambient completeness row, every accepted Real-facing read factors through the displayed route.
\end{proof}

\falsifiablePrediction{Every accepted HeronSquareRootUp Real-facing read factors through positive DyadicRatCoreUp radicand and seed rows, a reciprocal and division ledger, a finite Heron window, dyadic contraction estimates, NewtonIterationUp provenance, RegSeqRatUp readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{dyadicratcore, newtoniteration, regseqrat, real, regularcauchysquareroot: $\HeronSquareRootUp$ is not bijective to any listed sibling because it binds positive dyadic seed data, reciprocal/division rows, Heron recurrence windows, contraction estimates, Newton provenance, regular readback, Real seal handoff, transport, replay, provenance, and local naming as one finite certificate.}

\closureat{HeronSquareRootUp}{seedStr}

\begin{closurestatus}{\HeronSquareRootUp}
  \constructivestory{A $\HeronSquareRootUp$ packet is generated from positive DyadicRatCore radicand and seed rows, reciprocal and division ledger rows, finite Heron recurrence windows, dyadic contraction estimates, NewtonIteration provenance, RegSeqRat readback, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:heron-square-root-carrier} and \autoref{thm:heron-square-root-regular-cauchy-handoff} seed the finite Heron square-root carrier and its regular-Cauchy handoff route for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a host square-root function, quotient-real equality, selected completed limits, arbitrary real trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, positive dyadic seed exactness, reciprocal and division ledger exactness, Heron-window stability, dyadic contraction accounting, regular readback, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.HeronSquareRootUp.}
\end{closurestatus}
