\begin{theorem}[Heron square-root real reciprocal forward link]
\label{thm:heron-square-root-real-reciprocal-forward-link}
Every accepted $\HeronSquareRootUp$ packet reads its reciprocal row through \autoref{ch:concrete-instances-cauchyinversebudget-namecert}, \autoref{ch:concrete-instances-regular-cauchy-division-namecert}, and \autoref{ch:concrete-instances-real-reciprocal-namecert} before the $\RegSeqRatUp$ readback and terminal $\RealUp$ seal are public. For a carrier
$$
H=(A,S,R,L,W,D,K,Q,E,T,C,P,N),
$$
the reciprocal ledger $R$ is the displayed nonzero-apart route feeding the Heron recurrence, and the visible consumer path is
$$
R \longmapsto \CauchyInverseBudgetUp \longmapsto \RegularCauchyDivisionUp \longmapsto \RealReciprocalUp \longmapsto Q \longmapsto E .
$$
No Heron read exports a host reciprocal function, total division, quotient real equality, arbitrary trichotomy, selected completed limit, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted Heron carrier. The reciprocal ledger row $R$ is already a coordinate of the finite packet, and it appears before the Heron recurrence window, contraction estimate, regular readback, and Real seal.

Apply \autoref{thm:heron-square-root-regular-cauchy-handoff}. It forces every Real-facing Heron read to pass through the reciprocal and division ledger before $Q$ and $E$ can be inspected.

Use the sibling route from \autoref{thm:heron-square-root-regular-cauchy-sibling-route}. The row $R$ is therefore not a local host inverse; it is a displayed reciprocal ledger over the dyadic and regular-Cauchy route.

Finally read the reciprocal lattice through the named chapters. \autoref{ch:concrete-instances-cauchyinversebudget-namecert} supplies the finite inverse budget, \autoref{ch:concrete-instances-regular-cauchy-division-namecert} supplies the guarded division handoff, and \autoref{ch:concrete-instances-real-reciprocal-namecert} supplies the nonzero-apart Real reciprocal packet. Only after those rows are visible may the Heron readback $Q$ and terminal seal $E$ be public.
\end{proof}
