\chapter{A Concrete Naming Certificate for $\LawvereMetricCompletionUp$}
\label{ch:concrete-instances-lawvere-metric-completion-namecert}
\origin{human}

Following Lawvere on generalized metric spaces and enriched-category distance, the $\LawvereMetricCompletionUp$ packet records the finite directed-distance profile surface through which an enriched metric completion can be consumed inside BEDC. It sits beside the Yoneda profile route of \autoref{ch:concrete-instances-yoneda-completion-namecert}, the ordinary metric observation rows of \autoref{ch:concrete-instances-metric-namecert}, the formal-ball approximation surface of \autoref{ch:concrete-instances-formalball-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a one-sided enriched completion boundary; it does not select host limits, quotient directed Cauchy objects, symmetric metric completions, global colimits, or ambient $\RealUp$ completeness.

\begin{definition}[Lawvere metric completion carrier]
\label{def:lawvere-metric-completion-carrier}
A $\LawvereMetricCompletionUp$ carrier is a finite $\BHist$ packet
$$
L=(M,Y,F,D,A,T,R,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the directed $\MetricUp$ source row, carrying the visible point classifier and the finite one-sided distance comparisons accepted by the source packet.
\item $Y$ is the $\YonedaCompletionUp$ handoff row, exposing the covariant and contravariant distance profiles retained for the displayed source points.
\item $F$ is the finite probe-comparison row, listing the source probes against which two directed profiles are compared.
\item $D$ is the directed-distance profile row, recording the left and right distance readings that make the completion candidate visible as a Lawvere-enriched profile.
\item $A$ is the $\FormalBallUp$ approximation row, displaying finite ball inclusions and radius cuts used before any completion-facing consumer reads $D$.
\item $T$ is the $\DyadicRatCoreUp$ tolerance-accounting row for directed profile errors, ball radii, and probe budgets.
\item $R$ is the $\RegSeqRatUp$ readback row for the retained regular rational windows.
\item $S$ is the $\RealUp$ seal row for directed distance values and zero-distance comparison readback.
\item $H$ records componentwise $\hsame$ transport for source rows, profile rows, probe comparisons, formal-ball approximations, dyadic tolerances, regular readbacks, Real seals, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from source distances to Yoneda profiles, from profiles to formal-ball approximations, and from tolerance windows to Real readback.
\item $P$ is the $\Pkg$ provenance over $\LawvereMetricCompletionUp$, $\MetricUp$, $\YonedaCompletionUp$, $\FormalBallUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LawvereMetricCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,Y,F,D,A,T,R,S,H,C,P,N$. It has no coordinate for selected Cauchy weights, quotient profile equality, symmetric completion collapse, host enriched colimits, countable choice, or ambient real completeness.
\end{definition}

\begin{theorem}[Lawvere metric completion NameCert obligations]
\label{thm:lawvere-metric-completion-namecert-obligations}
For every accepted $\LawvereMetricCompletionUp$ carrier $L=(M,Y,F,D,A,T,R,S,H,C,P,N)$, the local $\NameCert_{\LawvereMetricCompletionUp}$ surface consists exactly of directed source admission, YonedaCompletion handoff, finite probe comparisons, directed distance-profile admission, FormalBall approximation, DyadicRatCore tolerance accounting, RegSeqRat readback, RealUp seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every enriched-metric completion consumer must inspect those rows before treating the packet as a completion neighbour.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:lawvere-metric-completion-carrier}. The source and Yoneda rows $M,Y$ are the only rows that introduce directed distance profiles from the displayed metric source.

The finite comparison route is $F,D,A,T$. Probe comparisons fix which source probes are being tested, the directed profile row records the left and right readings, the formal-ball row supplies finite approximation cuts, and the dyadic row records the tolerance accounting for those cuts.

Readback and transport are then forced through $R,S,H,C,P,N$. The regular rational windows and Real seal expose only the retained directed distance values, while componentwise transport, replay, provenance, and local naming preserve the same finite route.

Since the classifier has no additional coordinate, selected Cauchy weights, quotient profile equality, symmetric completion collapse, host enriched colimits, countable choice, and ambient real completeness cannot be read from the packet.
\end{proof}

\begin{theorem}[Lawvere metric completion finite profile nonescape]
\label{thm:lawvere-metric-completion-finite-profile-nonescape}
Every completion-facing read exported by an accepted $\LawvereMetricCompletionUp$ packet factors through
$$
\MetricUp,\ \YonedaCompletionUp,\ \FormalBallUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp,\ \RealUp .
$$
The read first fixes the directed source and Yoneda profile rows, then the finite probe comparisons and formal-ball approximations, then dyadic tolerance accounting, regular rational readback, Real sealing, transport, replay, provenance, and local naming. It exports no quotient directed Cauchy object, selected profile limit, symmetric metric completion collapse, host enriched colimit, or ambient completeness principle.
\end{theorem}
\begin{proof}
Let $L=(M,Y,F,D,A,T,R,S,H,C,P,N)$ be accepted. A completion-facing consumer first receives $M,Y,F,D$, so the directed profile is tied to displayed source distances, Yoneda handoff, and finite probe comparisons.

The approximation stage is $A,T$. Formal-ball inclusions and dyadic tolerance rows determine which finite directed-distance errors are visible before readback.

Finally $R,S,H,C,P,N$ expose only regular rational windows, Real seals, transport, replay, provenance, and local naming for that same route. The excluded quotient, choice, colimit, symmetric-collapse, and ambient-completeness objects are not carrier fields, so no completion consumer can bypass the finite profile surface.
\end{proof}

\begin{theorem}[Lawvere metric completion directed-profile composition]
\label{thm:lawvere-metric-completion-directed-profile-composition}
Every completion-facing read from an accepted $\LawvereMetricCompletionUp$ packet composes through the $\YonedaCompletionUp$ profile handoff, $\MetricUp$ directed source data, $\FormalBallUp$ approximation rows, $\DyadicRatCoreUp$ tolerance accounting, $\RegSeqRatUp$ readback, and $\RealUp$ seal rows before it is visible as a Lawvere-enriched completion profile. The composed read exports directed source distances, finite probe comparisons, formal-ball approximation cuts, dyadic error budgets, regular rational windows, Real sealing, transport, replay, provenance, and local naming, but it exports no symmetric metric completion, quotient directed Cauchy object, selected profile limit, global colimit, countable-choice schedule, or ambient completeness claim.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:lawvere-metric-completion-carrier}. The directed source and profile handoff are exactly the rows $M,Y,F,D$.

Apply \autoref{thm:lawvere-metric-completion-namecert-obligations}. It forces any completion-facing consumer to inspect directed source admission, YonedaCompletion handoff, finite probe comparison, directed profile admission, FormalBall approximation, DyadicRatCore tolerance accounting, RegSeqRat readback, Real sealing, transport, replay, provenance, and local naming.

Apply \autoref{thm:lawvere-metric-completion-finite-profile-nonescape}. The nonescape theorem identifies the public route through $\MetricUp$, $\YonedaCompletionUp$, $\FormalBallUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$.

The composed read is therefore the displayed directed-profile route itself. Since the carrier has no coordinate for a symmetric completion, quotient directed Cauchy object, selected profile limit, host colimit, choice schedule, or ambient completeness witness, none of those objects can be exported by the composition.
\end{proof}

\falsifiablePrediction{Removing any one of the $\YonedaCompletionUp$ handoff, finite probe-comparison row, $\FormalBallUp$ approximation row, $\DyadicRatCoreUp$ tolerance row, $\RegSeqRatUp$ readback row, $\RealUp$ seal, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, or local $\NameCert$ row makes \autoref{thm:lawvere-metric-completion-finite-profile-nonescape} false: a completion consumer could no longer verify the displayed directed-profile route.}

\independenceWitness{yonedacompletion, metriccompletion, formalball, dyadicratcore, regseqrat, real: $\LawvereMetricCompletionUp$ is not bijective to any listed sibling because it jointly carries directed source distances, Yoneda profile handoff, finite probe comparisons, formal-ball approximations, dyadic tolerance accounting, regular rational readback, Real sealing, transport, replay, provenance, and local naming rows.}

\closureat{LawvereMetricCompletionUp}{seedStr}

\begin{closurestatus}{\LawvereMetricCompletionUp}
  \constructivestory{A $\LawvereMetricCompletionUp$ packet is generated from directed MetricUp source data, YonedaCompletionUp profile handoff, finite probe comparisons, directed distance-profile rows, FormalBallUp approximations, DyadicRatCoreUp tolerance accounting, RegSeqRatUp readback windows, RealUp seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lawvere-metric-completion-carrier}, \autoref{thm:lawvere-metric-completion-namecert-obligations}, and \autoref{thm:lawvere-metric-completion-finite-profile-nonescape} seed the finite Lawvere-enriched completion route over directed profile, approximation, tolerance, readback, transport, replay, provenance, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected Cauchy weights, quotient profile equality, symmetric metric completion collapse, host enriched colimits, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, directed profile admission, probe comparison, FormalBall approximation, DyadicRatCore tolerance accounting, RegSeqRat readback, RealUp sealing, transport, replay, provenance, and local naming for BEDC.Derived.LawvereMetricCompletionUp.}
\end{closurestatus}
