\begin{definition}[Cyclotomic root obligation inventory]
\label{def:cyclotomic-root-obligation-inventory}
The root obligation inventory of $\NameCert_{\CyclotomicUp}$ is the finite
packet consisting of the $\NameCert_{\NumFieldUp}$ source row, the
$\NameCert_{\SplittingFieldUp}$ source row, the positive unary exponent row,
the primitive-root classifier row, the rational polynomial ledger for
$X^n-1$, the finite $\Cont$ readback, the $\hsame$ transport row, the $\Pkg$
provenance row, the exactness row identifying the displayed root surface, and
the downstream consumer rows for $\IwasawaUp$, $\ClassFieldUp$, and
$\RegulatorUp$. Each component is a displayed $\mathsf{BHist}$, $\Cont$,
$\hsame$, or $\Pkg$ row of the cyclotomic carrier and its source certificates.
\end{definition}

\begin{theorem}[Cyclotomic root carrier classifier obligations]
\label{thm:cyclotomic-root-carrier-classifier-obligations}
The carrier and classifier obligations of the cyclotomic root inventory are
exactly the displayed $\mathsf{BHist}$ rows of
\autoref{def:cyclotomic-root-obligation-inventory}: the NumFieldUp source, the
SplittingFieldUp source, the positive unary exponent, the primitive-root
classifier, and the rational polynomial ledger, together with their finite
$\Cont$, $\hsame$, and $\Pkg$ support rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cyclotomic-root-carrier}. Its visible
entries are the source field, exponent, polynomial, splitting-field, root,
acceptance, transport, and provenance rows.

Apply \autoref{def:cyclotomic-rational-polynomial-classifier} to identify the
polynomial ledger and primitive-root classifier rows. Apply
\autoref{thm:cyclotomic-root-carrier-classifier-scope} to see that the
classifier boundary is only the componentwise $\hsame$ transport on those
displayed rows, with $\Cont$ and $\Pkg$ kept as ledger support.

Thus every carrier and classifier obligation is one of the displayed rows of
the inventory, and no ambient cyclotomic-field carrier is required.
\end{proof}

\begin{theorem}[Cyclotomic root ledger exactness obligation]
\label{thm:cyclotomic-root-ledger-exactness-obligation}
The ledger of \autoref{def:cyclotomic-root-obligation-inventory} is exact:
after reading the polynomial, primitive endpoint, splitting-field, transport,
and provenance rows, the cyclotomic root packet contains no host cyclotomic
field, no quotient of roots, and no object beyond the displayed finite rows.
\end{theorem}
\begin{proof}
Use \autoref{thm:cyclotomic-polynomial-ledger-exactness} for the rational
polynomial ledger and
\autoref{thm:cyclotomic-primitive-root-readback-exactness} for the endpoint
readback. These two results identify the polynomial and primitive-root data as
finite projections of the accepted carrier.

Next apply \autoref{thm:cyclotomic-root-ledger-stability-package}. It carries
the splitting-field, factorization, endpoint, transport, and NumFieldUp
provenance rows through the same $\hsame$, $\Cont$, and $\Pkg$ support.

The resulting packet is precisely the inventory. Since each coordinate has
already been projected from the displayed carrier, there is no remaining
coordinate in which a host cyclotomic field or quotient root could be exported.
\end{proof}

\begin{theorem}[Cyclotomic root downstream consumer obligations]
\label{thm:cyclotomic-root-downstream-consumer-obligations}
Downstream $\IwasawaUp$, $\ClassFieldUp$, and $\RegulatorUp$ readers consume
only the packet boundary listed in
\autoref{def:cyclotomic-root-obligation-inventory}: source certificates,
positive exponent and primitive-root classifier rows, polynomial ledger,
finite $\Cont$ readback, $\hsame$ transport, $\Pkg$ provenance, and the
exactness row of the cyclotomic root surface.
\end{theorem}
\begin{proof}
For the Iwasawa and ClassField readers, apply
\autoref{thm:cyclotomic-root-iwasawa-classfield-consumer-boundary}. It factors
both consumers through the cyclotomic root downstream package and excludes
tower maps, reciprocity maps, class groups, local symbols, completion data,
quotient roots, and host-field equality.

For the Regulator reader, use the same packet boundary: the reader can address
the NumFieldUp source, the polynomial ledger, and the finite root readback
only through the displayed $\mathsf{BHist}$, $\Cont$, $\hsame$, and $\Pkg$
rows. These rows are exactly the rows named by the inventory.

Therefore every downstream consumer cited here reads the same finite packet
boundary, and none receives a host algebra primitive outside that packet.
\end{proof}
