\begin{theorem}[Cyclotomic root obligation threshold]
\label{thm:cyclotomic-root-obligation-threshold}
The accepted $\CyclotomicUp$ root boundary supplies the threshold obligation
surface consumed by $\IwasawaUp$, $\ClassFieldUp$, and $\RegulatorUp$: the root
carrier of \autoref{def:cyclotomic-root-carrier}, the rational-polynomial
classifier transport of
\autoref{thm:cyclotomic-root-layer-classifier-transport}, the polynomial ledger
of \autoref{thm:cyclotomic-polynomial-ledger-exactness}, the primitive-root
readback of \autoref{thm:cyclotomic-primitive-root-readback-exactness}, and the
finite $\Cont$, $\hsame$, and $\Pkg$ rows listed by
\autoref{def:cyclotomic-root-obligation-inventory}. It exports that finite root
surface without adding a host cyclotomic field, quotient root, class group,
tower map, or reciprocity map.
\end{theorem}
\begin{proof}
Start from \autoref{def:cyclotomic-root-obligation-inventory}. It names the
NumFieldUp and SplittingFieldUp source rows, the positive exponent, the
primitive-root classifier, the rational polynomial ledger for $X^n-1$, finite
readback, transport, provenance, and downstream consumer rows.

Apply \autoref{thm:cyclotomic-root-carrier-classifier-obligations}. The carrier
and classifier clauses are exactly those displayed $\mathsf{BHist}$ rows with
their $\Cont$, $\hsame$, and $\Pkg$ support.

Next use \autoref{thm:cyclotomic-root-ledger-exactness-obligation}. It identifies
the polynomial, primitive endpoint, splitting-field, transport, and provenance
rows as an exact finite ledger, so no host cyclotomic field or quotient-root
coordinate is available.

Finally apply \autoref{thm:cyclotomic-root-downstream-consumer-obligations}.
The three downstream fronts consume only the inventory boundary. Repacking these
three cited obligations gives the stated threshold surface.
\end{proof}

\begin{theorem}[Cyclotomic root classifier readback threshold]
\label{thm:cyclotomic-root-classifier-readback-threshold}
Every downstream read of the $\CyclotomicUp$ root classifier by $\IwasawaUp$,
$\ClassFieldUp$, or $\RegulatorUp$ factors through the same displayed
$\mathsf{BHist}$ root row, the rational-polynomial classifier row, primitive
readback, $\Cont$ acceptance, $\hsame$ transport, and $\Pkg$ provenance of
\autoref{def:cyclotomic-root-obligation-inventory}. Conversely, these rows
repack into the root classifier surface of
\autoref{thm:cyclotomic-root-obligation-threshold}.
\end{theorem}
\begin{proof}
For the forward projection, read a downstream classifier access through
\autoref{thm:cyclotomic-root-iwasawa-classfield-consumer-boundary} for
$\IwasawaUp$ and $\ClassFieldUp$, and through
\autoref{thm:cyclotomic-root-downstream-consumer-obligations} for the shared
Regulator-facing root surface.

The projected rows are then controlled by
\autoref{thm:cyclotomic-root-carrier-classifier-scope}. That theorem leaves only
componentwise $\hsame$ transport on the displayed root rows, with $\Cont$ and
$\Pkg$ kept as finite support.

For the converse direction, take exactly the displayed root carrier, classifier,
primitive readback, transport, acceptance, and provenance rows. The threshold
theorem repacks them as the accepted root obligation surface, so the downstream
readback closes without a host root quotient or ambient field equality.
\end{proof}

\begin{theorem}[Cyclotomic root ledger exactness threshold]
\label{thm:cyclotomic-root-ledger-exactness-threshold}
The $\CyclotomicUp$ root ledger exported at the threshold surface is exact: once
the root carrier, rational-polynomial classifier transport, polynomial ledger,
primitive-root readback, finite $\Cont$, componentwise $\hsame$, and $\Pkg$
rows are fixed, every accepted consumer row for $\IwasawaUp$, $\ClassFieldUp$,
or $\RegulatorUp$ reads the same finite root boundary and no additional host
algebra primitive.
\end{theorem}
\begin{proof}
Use \autoref{thm:cyclotomic-root-ledger-stability-package}. The polynomial
ledger, primitive endpoint readback, splitting-field root and factorization
rows, and NumFieldUp provenance remain stable under the same $\hsame$, $\Cont$,
and $\Pkg$ support.

Combine this with \autoref{thm:cyclotomic-root-ledger-exactness-obligation}.
The exactness obligation says that after those rows are read, the packet has no
remaining coordinate for a host cyclotomic field, root quotient, valuation row,
or class-field operation.

It remains to identify the consumers. Apply
\autoref{thm:cyclotomic-root-obligation-threshold} and
\autoref{thm:cyclotomic-root-classifier-readback-threshold}; together they show
that $\IwasawaUp$, $\ClassFieldUp$, and $\RegulatorUp$ all factor through the
same finite root boundary.
\end{proof}

\begin{theorem}[Cyclotomic source triad readback completeness]
\label{thm:cyclotomic-source-triad-readback-completeness}
For an accepted $\CyclotomicUp$ root packet, every downstream readback of the
source triad is complete from the displayed $\mathsf{BHist}$ rows: the
$\NameCert_{\NumFieldUp}$ row, the $\NameCert_{\SplittingFieldUp}$ row over the
rational polynomial ledger for $X^n-1$, and the primitive endpoint row. The
readback uses only the carried $\hsame$ comparisons, finite $\Cont$ acceptance,
$\mathsf{Pkg}$ provenance, and the $\NameCert_{\CyclotomicUp}$ classifier rows
listed by \autoref{thm:cyclotomic-source-triad-obligation}.
\end{theorem}
\begin{proof}
Start with the source triad of
\autoref{thm:cyclotomic-source-triad-obligation}. It names the NumFieldUp
source, SplittingFieldUp source, and primitive endpoint as the entire
cyclotomic source family over the carrier of
\autoref{def:cyclotomic-root-carrier}.

Use \autoref{thm:cyclotomic-downstream-source-exactness} to identify every
downstream source read with the same displayed $\mathsf{BHist}$, $\Cont$,
$\hsame$, and $\mathsf{Pkg}$ support. Then use
\autoref{thm:cyclotomic-polynomial-ledger-exactness} for the polynomial ledger
and \autoref{thm:cyclotomic-primitive-root-endpoint-transport} for the
primitive endpoint.

These projections repack the whole $\NameCert_{\CyclotomicUp}$ source triad.
There is no fourth source row, because the cited obligation surface has no
coordinate outside the displayed carrier, classifier, acceptance, and
provenance rows.
\end{proof}

\begin{theorem}[Cyclotomic downstream valuation exclusion]
\label{thm:cyclotomic-downstream-valuation-exclusion}
At the $\CyclotomicUp$ root threshold, a downstream $\PadicUp$,
$\IwasawaUp$, or $\ClassFieldUp$ consumer may cite the
$\NameCert_{\CyclotomicUp}$ source triad only through the displayed
$\mathsf{BHist}$ carrier, $\hsame$ transport, finite $\Cont$ acceptance,
$\mathsf{Pkg}$ provenance, and $\NameCert$ rows. The threshold exports no
valuation row, completion row, measure row, reciprocity map, local symbol, or
host field equality.
\end{theorem}
\begin{proof}
Read the downstream interface through
\autoref{thm:cyclotomic-padic-completion-input-boundary} and
\autoref{thm:cyclotomic-classfield-source-interface}. Both boundaries allow
the cyclotomic packet to serve only as source data for later certificates.

Apply \autoref{thm:cyclotomic-polynomial-ledger-exactness}. The polynomial
ledger is the $X^n-1$ row attached to the same SplittingFieldUp source, not a
valuation or completion datum. Apply
\autoref{thm:cyclotomic-primitive-root-endpoint-transport} to keep primitive
endpoint transport inside the carried $\hsame$ and $\Cont$ rows.

Finally use \autoref{thm:cyclotomic-downstream-source-exactness}. Since the
downstream source surface is exhausted by the displayed $\mathsf{BHist}$,
$\Cont$, $\hsame$, $\mathsf{Pkg}$, and $\NameCert$ rows, all valuation,
completion, measure, reciprocity, local-symbol, and host-equality data must
come from another certificate.
\end{proof}

\begin{theorem}[Cyclotomic root-layer consumer threshold]
\label{thm:cyclotomic-root-layer-consumer-threshold}
The root-layer consumer threshold for $\CyclotomicUp$ is exactly the source
triad readback, polynomial-ledger exactness, and primitive endpoint transport
surface over $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ rows. Once these rows are fixed, $\IwasawaUp$, $\PadicUp$, and
$\ClassFieldUp$ consumers have all cyclotomic source data they may read, and no
analytic, quotient, valuation, or host-equality row is supplied by the
cyclotomic certificate.
\end{theorem}
\begin{proof}
First collect the complete source triad from
\autoref{thm:cyclotomic-source-triad-readback-completeness}. This supplies the
NumFieldUp source, the SplittingFieldUp source, and the primitive endpoint over
the displayed carrier and classifier support.

Next attach the ledger and endpoint controls. The polynomial row is exact by
\autoref{thm:cyclotomic-polynomial-ledger-exactness}, and primitive endpoint
transport is exactly the transported endpoint surface of
\autoref{thm:cyclotomic-primitive-root-endpoint-transport}.

The consumer side is then bounded by
\autoref{thm:cyclotomic-root-obligation-threshold} and
\autoref{thm:cyclotomic-downstream-valuation-exclusion}. Together they show
that the listed source rows are sufficient for the root-layer consumers and
that the excluded analytic, quotient, valuation, and host-equality rows remain
outside the $\CyclotomicUp$ certificate.
\end{proof}
