\chapter{A Concrete Naming Certificate for $\LocatedApartnessRealBridgeUp$}
\label{ch:concrete-instances-located-apartness-real-bridge-namecert}
\origin{human}

Following Bishop and Bridges, the $\LocatedApartnessRealBridgeUp$ packet records the finite comparison route by which located-radius readback and positive apartness evidence can be consumed together without promoting the result to classical real order. It sits between the located-real surface of \autoref{ch:concrete-instances-locatedreal-namecert}, the Cauchy real apartness surface of \autoref{ch:concrete-instances-cauchy-real-apartness-namecert}, the real apartness order bridge of \autoref{ch:concrete-instances-real-apartness-order-bridge-namecert}, and the cotransitivity route of \autoref{ch:concrete-instances-apartness-cotransitivity-namecert}. The packet is a constructive comparison bridge for Real and Completion consumers; it is not a trichotomy theorem, quotient-real equality principle, host real equality test, selected-limit operator, or completeness claim.

\begin{definition}[Located apartness real bridge carrier]
\label{def:located-apartness-real-bridge-carrier}
A $\LocatedApartnessRealBridgeUp$ carrier is a finite $\BHist$ packet
$$
J=(L_0,L_1,R_0,R_1,A,O,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L_0$ and $L_1$ are accepted $\LocatedRealUp$ endpoint packets whose finite located-radius windows are being compared.
\item $R_0$ and $R_1$ are the located-radius readback rows, each exposing a $\StreamNameUp$ window, a $\RegSeqRatUp$ readback, and a $\DyadicRatCoreUp$ radius ledger before any terminal $\RealUp$ seal is inspected.
\item $A$ is the positive apartness witness row, read through the $\CauchyRealApartnessUp$ surface and tied to the same endpoint windows.
\item $O$ is the order-facing bridge row supplied by $\RealApartnessOrderBridgeUp$, used only after $A$ has exposed positive apartness.
\item $T$ is the cotransitivity route row, pointing to the existing $\ApartnessCotransitivityUp$ surface when a third displayed real name is inspected.
\item $H$ records componentwise $\hsame$ transport for the endpoint packets, readbacks, apartness witness, order bridge, cotransitivity route, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a located-apartness bridge request through $L_0,L_1,R_0,R_1,A,O,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedApartnessRealBridgeUp$, $\LocatedRealUp$, $\CauchyRealApartnessUp$, $\RealApartnessOrderBridgeUp$, $\ApartnessCotransitivityUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedApartnessRealBridgeUp}$ row.
\end{enumerate}
The classifier admits exactly the finite packet in which located-radius readback and apartness evidence share the displayed endpoint windows. It has no coordinate for real trichotomy, quotient equality, host real equality, selected limits, countable choice, ambient completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Located real apartness cotransitive bridge]
\label{thm:located-real-apartness-cotransitive-bridge}
For every accepted $\LocatedApartnessRealBridgeUp$ carrier
$$
J=(L_0,L_1,R_0,R_1,A,O,T,H,C,P,N),
$$
any comparison read that uses the located-radius readbacks $R_0,R_1$ together with the positive apartness witness $A$ reaches a Real-facing consumer only through the existing apartness-cotransitivity surface. More precisely, the read first opens the two $\LocatedRealUp$ endpoint packets, then the shared finite readback route
$$
\StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \DyadicRatCoreUp \longmapsto \RealUp,
$$
then the $\CauchyRealApartnessUp$ witness, then the $\RealApartnessOrderBridgeUp$ order-facing handoff, and finally the $\ApartnessCotransitivityUp$ row $T$ when a third real name is present. The export is finite constructive comparison evidence only. It exports no trichotomy, quotient real equality, host real equality, selected limit, countable-choice branch selection, ambient $\RealUp$ completeness, or completion principle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-apartness-real-bridge-carrier}. The endpoint information is exactly the two located real packets $L_0,L_1$ and the two finite located-radius readbacks $R_0,R_1$.

The apartness row is opened only after those finite readbacks are visible. Thus $A$ is tied to the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and terminal $\RealUp$ route as the endpoint data.

The order-facing handoff is downstream of apartness. The row $O$ may expose the order bridge supplied by $\RealApartnessOrderBridgeUp$, but it receives positive separation from $A$ and cannot introduce an equality test or a trichotomy branch.

When a third real name is inspected, the route must pass through $T$. That row is precisely the cotransitivity surface of $\ApartnessCotransitivityUp$, so the consumer receives a displayed cotransitive apartness route rather than a classical comparison principle.

The remaining rows $H,C,P,N$ transport, replay, package, and name the same finite route. Since the carrier lists no quotient equality, host equality, selected limit, choice, or completeness row, none can be exported by the local certificate.
\end{proof}

\begin{theorem}[Located apartness real bridge NameCert obligations]
\label{thm:located-apartness-real-bridge-namecert-obligations}
For every accepted $\LocatedApartnessRealBridgeUp$ carrier
$$
J=(L_0,L_1,R_0,R_1,A,O,T,H,C,P,N),
$$
the local $\NameCert_{\LocatedApartnessRealBridgeUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item endpoint admission for the two $\LocatedRealUp$ endpoint packets $L_0,L_1$;
\item located-radius readback for $R_0,R_1$, each displaying the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and terminal $\RealUp$ route attached to its endpoint;
\item positive apartness witness admission for the $\CauchyRealApartnessUp$ row $A$;
\item order-facing handoff for the $\RealApartnessOrderBridgeUp$ row $O$, read only after $A$ has exposed positive apartness;
\item cotransitivity routing for the $\ApartnessCotransitivityUp$ row $T$ when a third displayed real name is inspected;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$.
\end{enumerate}
These rows export only the displayed constructive comparison route. They do not assert real trichotomy, quotient real equality, host real equality, selected limits, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-apartness-real-bridge-carrier}. The endpoint and readback obligations are exactly the rows $L_0,L_1,R_0,R_1$, so the local certificate admits only displayed located endpoints and finite radius-readback data.

The apartness and order rows are $A$ and $O$. The carrier orders them so that the $\CauchyRealApartnessUp$ witness is exposed before the $\RealApartnessOrderBridgeUp$ handoff can be consumed.

Apply \autoref{thm:located-real-apartness-cotransitive-bridge}. It reads the same endpoint, readback, apartness, and order rows as the consumer-facing route, and it sends any third-name comparison through the cotransitivity row $T$.

The remaining rows $H,C,P,N$ transport, replay, package, and name that route. Since the carrier has no coordinate for trichotomy, quotient equality, host equality, selected limits, countable choice, ambient completeness, Lean verification, or bridge checking, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Located apartness real two-way separation]
\label{thm:located-apartness-real-two-way-separation}
An accepted $\LocatedApartnessRealBridgeUp$ carrier exposes $\RealUp$ separation reads only through the displayed located-apartness row $A$ and its endpoint readbacks $L_0,L_1,R_0,R_1$. Conversely, it exposes located-apartness reads only through the terminal $\RealUp$ seal route carried by $R_0,R_1$ together with the bridge transport, replay, provenance, and naming rows $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier $J=(L_0,L_1,R_0,R_1,A,O,T,H,C,P,N)$ from \autoref{def:located-apartness-real-bridge-carrier}. The Real-facing data are the two located endpoints and their radius-readback rows, while the positive separation data are confined to the apartness witness row $A$.

Apply the NameCert obligations of \autoref{thm:located-apartness-real-bridge-namecert-obligations}. They require endpoint admission, located-radius readback, positive apartness admission, order-facing handoff, cotransitivity routing, and structural replay to be read as the same finite packet.

In the Real-facing direction, a separation read reaches the endpoint seal only after the displayed apartness row has tied the endpoints to positive evidence. In the apartness-facing direction, a consumer of $A$ receives only the endpoint $\RealUp$ seal route plus $H,C,P,N$; the carrier exports no trichotomy, quotient equality, host equality, selected limit, countable-choice branch, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[Located apartness real nontrichotomy boundary]
\label{thm:located-apartness-real-nontrichotomy-boundary}
Every accepted $\LocatedApartnessRealBridgeUp$ read that exports an order-facing handoff still factors through the positive apartness row $A$ and the cotransitivity route $T$. Consequently the handoff cannot export a three-way comparison branch, quotient-real equality, host real equality, or a detached order comparison outside
$$
L_0,L_1,R_0,R_1,A,O,T,H,C,P,N .
$$
\end{theorem}
\begin{proof}
Project the carrier $J=(L_0,L_1,R_0,R_1,A,O,T,H,C,P,N)$ from \autoref{def:located-apartness-real-bridge-carrier}. The order-facing row is $O$, and it is listed downstream of the positive apartness witness $A$ rather than as an independent trichotomy or equality coordinate.

Apply \autoref{thm:located-real-apartness-cotransitive-bridge}. It forces any third-name comparison to pass through the cotransitivity row $T$ after the endpoint readbacks and the positive apartness row have been displayed.

Apply \autoref{thm:located-apartness-real-bridge-namecert-obligations} and \autoref{thm:located-apartness-real-two-way-separation}. These obligations keep $O$ downstream of $A$ and keep all Real-facing separation reads attached to the endpoint readbacks $R_0,R_1$.

The remaining rows $H,C,P,N$ transport, replay, source, and name the same finite packet. Since no carrier coordinate records a three-way comparison branch, quotient-real equality, host real equality, or detached order comparison, none can be exported by an accepted read.
\end{proof}

\begin{theorem}[Located apartness real bridge completion forward route]
\label{thm:located-apartness-real-bridge-completion-forward-route}
Any L10 completion consumer, in particular the $\BishopRegularCauchyCompletionUp$ consumer of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}, that reads located apartness from an accepted $\LocatedApartnessRealBridgeUp$ carrier
$$
J=(L_0,L_1,R_0,R_1,A,O,T,H,C,P,N)
$$
must pass through the located-radius readbacks $R_0,R_1$, the $\CauchyRealApartnessUp$ surface $A$, the $\RealApartnessOrderBridgeUp$ compatibility row $O$, and the $\ApartnessCotransitivityUp$ row $T$ before it consumes any completion-facing comparison. The route exports constructive comparison evidence only; it exports no trichotomy, quotient-real equality, selected limit, host equality, countable choice, ambient $\RealUp$ completeness, or completion principle outside the displayed rows.
\end{theorem}
\begin{proof}
Project the endpoint and readback rows from \autoref{def:located-apartness-real-bridge-carrier}. The completion-facing consumer first sees the two located endpoints and their finite radius readbacks, so the comparison begins with visible $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and terminal $\RealUp$ data.

Apply \autoref{thm:located-real-apartness-cotransitive-bridge}. It opens the Cauchy real apartness witness after the readbacks, then routes the positive evidence through the order-facing bridge and the cotransitivity surface whenever a third name is inspected.

Use \autoref{thm:located-apartness-real-bridge-namecert-obligations} and \autoref{thm:located-apartness-real-two-way-separation}. These keep located-apartness evidence and Real-facing separation tied to the same finite packet before any completion-facing comparison is consumed.

Since the carrier has no coordinate for trichotomy, quotient equality, selected limits, host equality, choice, completeness, or an independent completion principle, the forward route is exactly the displayed located-radius, apartness, order-bridge, and cotransitivity handoff.
\end{proof}

\closureat{LocatedApartnessRealBridgeUp}{seedStr}

\begin{closurestatus}{\LocatedApartnessRealBridgeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-apartness-real-bridge-carrier} and \autoref{thm:located-real-apartness-cotransitive-bridge} seed the finite constructive comparison route over located-real endpoints, located-radius readbacks, Cauchy apartness, the real-apartness order bridge, and apartness cotransitivity.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close real trichotomy, quotient real equality, host real equality, selected limits, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located-radius readback stability, Cauchy apartness handoff, order-bridge compatibility, cotransitivity routing, transport, replay, provenance, and local naming for BEDC.Derived.LocatedApartnessRealBridgeUp.}
  \constructivestory{A $\LocatedApartnessRealBridgeUp$ packet is generated from two located-real endpoints, two located-radius readbacks, a positive Cauchy real apartness witness, a real-apartness order bridge row, an apartness-cotransitivity route, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
