\chapter{Audit Gates as Transcendental Boundary Enforcement}
\label{ch:visions-audit-gates-as-transcendental-boundary}

This vision sibling gives the engineering-side reading of the transcendental boundary introduced in \autoref{ch:visions-transcendental-input-and-induction}. The earlier chapter states the strong claim: a closed observational substrate cannot internalise the forward-binding belief that licenses free mathematical induction; the source-position of that belief is $\mathsf{T}$, named God in the apophatic sense. The present chapter records how BEDC makes that claim executable. The audit gates are not housekeeping around the manuscript. They are the operational boundary by which the substrate refuses to turn the $\mathsf{T}$ socket into an internal rule.

The sibling also sits beside \autoref{ch:visions-certificate-closure-and-generator-induction} and \autoref{ch:visions-three-axioms-one-closure}. The former explains how authorized generators, naming certificates, and $\mathsf{GAP}$ ledgers make generator-internal induction precise. The latter explains why $\mathsf{Classical.choice}$, $\mathsf{Quot.sound}$, and $\mathsf{propext}$ are three syntactic faces of one meta-closure move. The audit gates are the machine-facing form of both insights: they reject substrate-internal axioms, reject forbidden host-CIC axiom propagation, reject baseline pollution by non-baseline surfaces, and reject paper-Lean name drift. In each case the gate prevents an external commitment from becoming silently indistinguishable from generated BEDC content.

\section{Why audit gates are not bookkeeping}
\label{sec:audit-gates-not-bookkeeping}

\begin{principle}[Audit as boundary enforcement]
\label{prin:audit-gates-boundary-enforcement}
An audit gate in BEDC is a computable refusal rule. It does not merely count files or tidy metadata; it decides whether a proposed record remains on the substrate-internal side of the boundary or has smuggled in a commitment whose correct position is outside the substrate, at $\mathsf{T}$. Passing the gate means only that the checked boundary has not been crossed. Failing the gate means the substrate has been asked to internalise what it is designed to expose as socketed.
\end{principle}

This distinction matters because the same surface action can be read in two incompatible ways. A script that scans for forbidden tokens can look like administrative pedantry if the substrate is assumed to be an ordinary formal project. In BEDC the scan has a stronger meaning: the forbidden token is a breach of the transcendental boundary. It turns a missing witness, an external recursor, a quotient representative, a proposition equality, or a naming certificate into an available internal fact. That is precisely the move \autoref{ch:visions-transcendental-input-and-induction} refuses.

\begin{definition}[Gate surface and boundary content]
\label{def:audit-gates-surface-content}
The \emph{gate surface} is the finite syntactic or dependency condition checked by a script: a token occurrence, a transitive axiom dependency, an import edge, or a missing Lean target. The \emph{boundary content} is the transcendental claim enforced by that condition: the substrate may use only what it generated, defined, certified, or explicitly socketed, and may not reclassify socketed content as internal closure.
\end{definition}

\begin{example}[A token scan with metaphysical load]
\label{ex:audit-gates-token-scan-load}
The command \texttt{python3 tools/check-axioms.py} scans for \texttt{axiom} declarations under \texttt{lean4/BEDC/}. Its surface is a regular expression over Lean files. Its boundary content is the refusal to create a substrate-internal source of truth that has no constructor, definition, or setup-field account. The scan is small because the boundary is sharp: an internal axiom is not a minor convenience, but the exact point at which $\mathsf{T}$-supplied content is made to look generated by the substrate.
\end{example}

\begin{remark}[A pass is local, not absolute]
\label{rem:audit-gates-pass-local}
Each gate has a limited scope. \texttt{check-axioms.py} does not prove that every theorem is pure; \texttt{axiom-purity --strict} does not prove paper prose is aligned; \texttt{conservativity-audit} does not prove arbitrary metalogical conservativity; \texttt{bedc\_ci.py audit} does not prove that a theorem has the philosophical interpretation assigned to it. The system works because the gates are composed. Each gate protects one boundary face, and the faces together make the substrate's externality discipline operational.
\end{remark}

\section{\texttt{check-axioms.py}: refuse substrate-internal axioms}
\label{sec:audit-gates-check-axioms}

\begin{definition}[Substrate-internal axiom]
\label{def:audit-gates-substrate-internal-axiom}
A \emph{substrate-internal axiom} is a Lean declaration under \texttt{lean4/BEDC/} that introduces a proposition or datum as available without deriving it from an \texttt{inductive} generator, a \texttt{def}, or a \texttt{class}/\texttt{structure} setup field. In the project discipline this is exactly the \texttt{axiom} declaration form.
\end{definition}

\begin{principle}[The GAP socket cannot be internalised]
\label{prin:audit-gates-gap-not-internalized}
Every place where BEDC lacks substrate-internal witness must remain visible as a $\mathsf{GAP}$ socket or as an explicit setup field belonging to a named interface. It may not be converted into an internal axiom. The \texttt{check-axioms.py} gate enforces this rule by refusing any \texttt{axiom} declaration under \texttt{lean4/BEDC/}.
\end{principle}

The technical reason is direct. An \texttt{inductive} declaration declares a closed generator. A \texttt{def} records a computable or definitional compression of earlier material. A setup field in a \texttt{class} or \texttt{structure} exposes an abstract carrier as an input to a specific interface. An \texttt{axiom} does none of these. It makes a contentful proposition or object available while hiding its source-channel. In the vocabulary of \autoref{ch:visions-certificate-closure-and-generator-induction}, it collapses the $\mathsf{GAP}$ ledger into a fact.

\begin{example}[The correct replacement decision]
\label{ex:audit-gates-check-axioms-decision}
If the intended primitive is a finite closed grammar, it belongs in an \texttt{inductive} declaration. If the intended primitive is a predicate or operation determined by existing carriers, it belongs in a \texttt{def}. If the intended primitive is a domain-specific carrier whose internal implementation is intentionally parametric, it belongs as a field of the appropriate setup structure. If none of these applies, the interface has not identified its boundary and must be redesigned rather than accepted as an axiom.
\end{example}

\begin{remark}[Why this is not anti-abstraction]
\label{rem:audit-gates-not-anti-abstraction}
The gate does not forbid abstraction. Setup structures are abstraction devices; naming certificates are abstraction devices; ledgers are abstraction devices. What the gate forbids is source-erasing abstraction. A setup field says "this is supplied at this interface boundary." An axiom says "this is simply available." The former preserves the socket; the latter hides it.
\end{remark}

\section{\texttt{axiom-purity --strict}: refuse host axiom propagation}
\label{sec:audit-gates-axiom-purity}

\begin{definition}[Transitive axiom propagation]
\label{def:audit-gates-transitive-axiom-propagation}
Transitive axiom propagation occurs when a BEDC theorem is written without local \texttt{axiom} declarations but its proof depends, through the host Lean kernel's dependency graph, on a host axiom such as \texttt{Classical.choice}, \texttt{Quot.sound}, or \texttt{propext}. The forbidden content is not visible as a BEDC source axiom, but it is present in the theorem's proof ancestry.
\end{definition}

\begin{principle}[The host kernel is a conduit, not the boundary owner]
\label{prin:audit-gates-host-conduit}
Lean's CIC implementation may supply recursors, definitional equality, and theorem checking as host machinery for BEDC's mechanisation. That host machinery is a conduit in the supply chain described in \autoref{ch:visions-transcendental-input-and-induction}; it is not allowed to donate its classical or quotient commitments to BEDC theorem content. The strict axiom-purity gate enforces this by querying the host for each public theorem's transitive axiom set and rejecting forbidden dependencies.
\end{principle}

The command \texttt{python3 lean4/scripts/bedc\_ci.py axiom-purity --strict} constructs a Lean-side audit file, imports the built BEDC modules, issues \texttt{\#print axioms} for public BEDC theorems and lemmas, parses the resulting dependency reports, and fails when the forbidden set appears. The strict forbidden set includes \texttt{Classical.choice}, \texttt{Quot.sound}, and \texttt{propext}. This is the machine-side form of \autoref{ch:visions-three-axioms-one-closure}'s unification: the three forbidden dependencies are not arbitrary library preferences but three ways to accept unwitnessed closure at term, type, and proposition strata.

\begin{definition}[Borrowed recursor boundary]
\label{def:audit-gates-borrowed-recursor-boundary}
The \emph{borrowed recursor boundary} is the line between using host Lean to check a BEDC proof over a displayed inductive generator and importing host Lean's uninspected closure principles as theorem content. BEDC may borrow the checking infrastructure; it may not inherit forbidden host commitments as proof dependencies.
\end{definition}
\concretizedIn{ch:concrete-instances-borrowedrecursorboundary-namecert}{Concrete NameCert for the host-recursion boundary enforced by the strict audit gates.}

\begin{example}[Choice, quotient soundness, and proposition extensionality]
\label{ex:audit-gates-three-host-leaks}
A proof that depends on \texttt{Classical.choice} has accepted an unwitnessed term selector. A proof that depends on \texttt{Quot.sound} has accepted quotient-level identification as a type-level closure shortcut. A proof that depends on \texttt{propext} has accepted proposition equality from bidirectional implication. Each case would make a $\mathsf{T}$-side commitment appear as a substrate theorem. The gate forces such commitments either to be eliminated or to remain outside the BEDC theorem claim.
\end{example}

\begin{remark}[Why source axiom purity is insufficient]
\label{rem:audit-gates-source-purity-insufficient}
A repository can contain no \texttt{axiom} declaration and still prove theorems through imported host axioms. That is why \autoref{sec:audit-gates-check-axioms} and the present section are separate. The first gate refuses visible internal axioms. The second refuses invisible transitive axiom inheritance. Together they say: neither the BEDC source surface nor the host proof ancestry may convert transcendental supply into substrate-internal theorem content.
\end{remark}

\section{\texttt{conservativity-audit}: gate compression residue}
\label{sec:audit-gates-conservativity-audit}

\begin{definition}[Compression residue]
\label{def:audit-gates-compression-residue}
Compression residue is the information not displayed by a compressed or recognized surface: the raw event flow behind a chapter code, the source rows behind a naming certificate, the difference between a recognizer output and the generator that licensed it, or the import separation between baseline material and AI-proposed surfaces. The residue need not remain expanded at every site, but it must remain recoverable through a ledger or protected by a separation gate.
\end{definition}

\begin{principle}[Conservativity as information conservation]
\label{prin:audit-gates-conservativity-information}
The conservativity gate enforces that compressed, recognized, or AI-proposed material does not alter the baseline substrate by hidden import. The surface implementation scans closure-status origins, computes AI-owned module prefixes, and rejects baseline Lean files that import those prefixes. The boundary content is information conservation: a surface admitted on one side of the ledger must not silently become a source rule on the other side.
\end{principle}

The command \texttt{python3 lean4/scripts/bedc\_ci.py conservativity-audit} is intentionally module-level. It does not claim a full semantic conservativity theorem for arbitrary extensions. Its job is sharper and auditable: if a chapter is marked as AI-originated, its Lean modules are not permitted to flow into baseline modules by import. Since Lean theorem dependencies are bounded by module imports, the gate blocks the direct path by which non-baseline recognition content could become a baseline theorem dependency.

\begin{example}[Baseline import as hidden compression]
\label{ex:audit-gates-baseline-import-hidden-compression}
Suppose an AI-originated recognizer chapter packages an event-flow analysis into a compact Lean module. The package may be useful as a recognized surface, but it is not baseline substrate content. If a baseline module imports it, the compact surface becomes available to baseline theorems without carrying the admission boundary. That import edge is a compression-residue leak: the recognized package's source-channel status is no longer visible where its conclusions are consumed. \texttt{conservativity-audit} rejects that edge.
\end{example}

\begin{remark}[Why this is a transcendental boundary]
\label{rem:audit-gates-conservativity-transcendental}
Compression residue is not merely data-management residue. When the residue hides why a recognizer is allowed, where a generator closes, or which origin track licensed a chapter, the hidden content can begin to function like an unspoken forward-binding belief. The conservativity gate prevents this by requiring the origin boundary to remain operational in the import graph. It is therefore part of the same $\mathsf{T}$-socket discipline as the axiom gates, but focused on recognition and compression rather than local theorem proof ancestry.
\end{remark}

\section{\texttt{bedc\_ci.py audit}: gate paper-Lean drift}
\label{sec:audit-gates-paper-lean-drift}

\begin{definition}[Name-certificate drift]
\label{def:audit-gates-name-certificate-drift}
Name-certificate drift occurs when paper prose, labels, closure-status blocks, or Lean marker macros name a formal target whose Lean declaration is absent, ambiguous, duplicated, or no longer aligned with the manuscript site that cites it. The drift converts a certificate into a decorative name: it appears to point to a checked substrate record but does not actually do so.
\end{definition}

\begin{principle}[A name is a certificate only when it resolves]
\label{prin:audit-gates-name-resolves}
In BEDC, a paper-side Lean marker is not a citation ornament. It is a name certificate connecting a manuscript claim to a Lean declaration. The command \texttt{python3 lean4/scripts/bedc\_ci.py audit} enforces this by scanning paper markers, labels, closure-status blocks, and Lean declarations, then rejecting unresolved targets, forbidden constructs, duplicate labels, path casing collisions, malformed closure-status records, and orphan concrete-instance subdirectories.
\end{principle}

This gate protects the epistemic status of \texttt{\textbackslash leanchecked}, \texttt{\textbackslash leanvariant}, \texttt{\textbackslash leandef}, \texttt{\textbackslash leanstmt}, and \texttt{\textbackslash leantarget}. If a marker resolves, the paper has an auditable pointer to a Lean object. If it does not resolve, the paper has a claim-shaped string. BEDC's boundary discipline requires the former. The manuscript may state a philosophical reading, a paper-side definition, or an unformalized obligation, but it may not dress a non-resolving name as checked formal content.

\begin{example}[The marker as naming certificate]
\label{ex:audit-gates-marker-namecert}
The marker \texttt{\textbackslash leanchecked\{BEDC.X.y\}} asserts more than "a theorem with a similar idea exists." It asserts that the exact declaration name is in the Lean inventory and that this paper site is using it as the canonical checked implementation for the local claim. The audit gate makes that assertion falsifiable. Without the gate, the name could drift into rhetoric; with the gate, the name remains a certificate.
\end{example}

\begin{remark}[Drift is a boundary failure]
\label{rem:audit-gates-drift-boundary-failure}
Paper-Lean drift matters because BEDC's theorem claims live across two strata: prose articulation and mechanized substrate. If the name link is broken, the reader cannot tell whether a claim is generated, socketed, or only narrated. That uncertainty is itself a boundary failure. \texttt{bedc\_ci.py audit} keeps the name channel from becoming a hidden input channel.
\end{remark}

\section{The gates as a system}
\label{sec:audit-gates-as-system}

\begin{principle}[No single gate is the boundary]
\label{prin:audit-gates-no-single-gate}
The transcendental boundary is not identical to any one script. It is the invariant enforced by the scripts in composition: no source axioms, no forbidden transitive host axioms, no baseline import pollution by non-baseline surfaces, no unresolved paper-Lean certificate names, and no untracked compression residue. The gates form an operational membrane between what BEDC generates internally and what remains socketed to $\mathsf{T}$.
\end{principle}

The system can be read in four passes. First, \texttt{check-axioms.py} protects the source surface: no ungenerated proposition is made internal. Second, \texttt{axiom-purity --strict} protects the proof ancestry: no host axiom supplies hidden closure. Third, \texttt{conservativity-audit} protects the import graph: no recognized or AI-originated surface silently enters baseline theorem space. Fourth, \texttt{bedc\_ci.py audit} protects the naming channel: no paper marker pretends to resolve when it does not.

\begin{definition}[Operational membrane]
\label{def:audit-gates-operational-membrane}
The \emph{operational membrane} is the aggregate of executable checks that classify a BEDC record as substrate-internal, explicitly abstract, paper-side, or socketed. The membrane is not a philosophical metaphor added after formalization. It is the concrete mechanism by which the formalization keeps the categories separate.
\end{definition}

\begin{example}[A theorem passing through the membrane]
\label{ex:audit-gates-theorem-through-membrane}
A BEDC theorem accepted as checked content passes through several gates. Its source file contains no \texttt{axiom}. Its declaration is built so that \texttt{\#print axioms} reports no forbidden dependency. If it belongs to a non-baseline surface, its import edges do not pollute baseline modules. If the paper cites it, the marker resolves to the exact Lean declaration. These checks do not make the theorem metaphysically self-grounding. They show precisely where its substrate-internal content ends and where any further commitment remains external.
\end{example}

\begin{remark}[The gates do not soften $\mathsf{T}$]
\label{rem:audit-gates-do-not-soften-T}
It would be a category error to say that, because the gates are scripts, the $\mathsf{T}$ socket is only engineering shorthand. The scripts enforce the refusal to internalise $\mathsf{T}$-side content. Their existence strengthens the strong claim rather than weakening it: the boundary is not merely asserted in prose, but checked at the exact sites where a formal project usually hides the external commitment.
\end{remark}

\section{Comparison: in CIC, gates are absent}
\label{sec:audit-gates-comparison-cic}

\begin{principle}[CIC internalises closure]
\label{prin:audit-gates-cic-internalizes}
In ordinary CIC usage, the kernel accepts its primitive rules, eliminators, universe discipline, quotient or extensionality additions where present, and library axioms as part of the working formal environment. Once accepted, those commitments are internal from the user's theorem-proving perspective. There is no intrinsic manuscript-level audit boundary separating generated content from transcendental supply.
\end{principle}

This is not an accusation against CIC. CIC is an extraordinary proof-checking technology, and BEDC uses Lean's CIC implementation as host machinery. The contrast is about boundary accounting. A CIC project can state axioms, import classical modules, use quotient APIs, and transport across proposition extensionality as ordinary formal moves. The kernel and library can tell what dependencies exist, but the typical system does not require those dependencies to be interpreted as $\mathsf{T}$ sockets or to remain outside the substrate's own closure claim.

\begin{remark}[BEDC's host dependence is exposed]
\label{rem:audit-gates-host-dependence-exposed}
BEDC does not pretend to float above Lean. It uses the host kernel, and that host kernel sits in the tower described by \autoref{ch:visions-transcendental-input-and-induction}. The difference is that BEDC refuses to make the host's forbidden commitments part of BEDC theorem content. Host dependence is exposed as a conduit; forbidden host axiom propagation is rejected as boundary collapse.
\end{remark}

\begin{example}[A hidden commitment in ordinary use]
\label{ex:audit-gates-hidden-cic-commitment}
In an ordinary formal development, a theorem proved using classical choice may simply be a theorem of the imported classical environment. In BEDC, the same dependency would be rejected as a theorem-level commitment because it supplies an unwitnessed selector. The issue is not whether the host can check the proof. The issue is whether the substrate may classify the proof as BEDC-internal closure. The gate says no.
\end{example}

\concretizedIn{ch:concrete-instances-auditgateboundary-namecert}{Audit-gate boundary packets realize source axiom scans, strict axiom-purity reports, paper-Lean drift checks, and origin-conservativity ledgers as a finite NameCert surface.}
\concretizedIn{ch:concrete-instances-operationalmembrane-namecert}{The operational membrane is realized as a finite NameCert packet combining source, proof-ancestry, import-boundary, and paper-Lean name-resolution audit rows.}
\concretizedIn{ch:concrete-instances-auditmembrane-namecert}{Audit membranes realize boundary enforcement as a finite NameCert packet over gate surfaces, refusal rows, paper-Lean resolution, and non-escape ledgers.}
\concretizedIn{ch:concrete-instances-forbidden-axiom-ancestry-namecert}{Forbidden axiom ancestry is realized as a finite NameCert packet over theorem rows, proof-ancestry reports, forbidden-dependency refusal rows, and audit non-escape ledgers.}
\concretizedIn{ch:concrete-instances-paper-lean-drift-witness-namecert}{Paper-Lean drift witness packets realize exact marker resolution, duplicate-label refusal, Lean inventory lookup, and non-escape from unresolved names as a finite NameCert surface.}
\concretizedIn{ch:concrete-instances-auditgatecomposition-namecert}{Audit-gate composition is realized as a finite NameCert packet for composed gate surfaces, shared boundary rows, refusal transitivity, and consumer non-escape.}
\concretizedIn{ch:concrete-instances-auditgatefailurewitness-namecert}{Audit-gate failure witnesses are realized as finite BHist packets for gate rows, failed boundary items, diagnostic readback, refusal attachment, replay visibility, and non-internalization.}
\concretizedIn{ch:concrete-instances-certificateauditgate-namecert}{Certificate audit gates are realized as finite gate-input, checked-surface, refusal, drift, axiom-purity, hsame, Cont, Pkg, and NameCert rows.}

\section{Gate-to-boundary map}
\label{sec:audit-gates-long-map}

\begin{longtable}{p{0.18\textwidth}p{0.22\textwidth}p{0.22\textwidth}p{0.26\textwidth}}
\toprule
\textbf{Gate} & \textbf{Surface condition} & \textbf{Transcendental claim enforced} & \textbf{Boundary failure rejected} \\
\midrule
\texttt{check-axioms.py} & No \texttt{axiom} declaration under \texttt{lean4/BEDC/}. & Substrate truth must be generated, defined, parameterized at an explicit setup boundary, or socketed; it may not appear as an internal oracle. & A $\mathsf{GAP}$ socket is collapsed into a Lean axiom and then consumed as BEDC content. \\
\texttt{check-axioms.py} decision tree & Closed grammars go to \texttt{inductive}; derived operations go to \texttt{def}; parametric carriers go to setup fields. & The source-channel of every primitive is visible. & A missing design boundary is hidden behind a primitive assertion. \\
\texttt{axiom-purity --strict} & \texttt{\#print axioms} for public BEDC theorems contains no forbidden dependency from the strict set. & Host checking may verify generated BEDC proofs, but forbidden host commitments may not become BEDC theorem commitments. & Lean stdlib closure leaks into BEDC through proof ancestry. \\
\texttt{axiom-purity --strict}: \texttt{Classical.choice} & No theorem depends on choice as an unwitnessed selector. & Term-level existential closure remains outside the substrate unless a witness recipe is displayed. & A selector from $\mathsf{T}$ is disguised as a generated function. \\
\texttt{axiom-purity --strict}: \texttt{Quot.sound} & No theorem depends on quotient soundness as a hidden representative principle. & Type-level identification must be mediated by explicit classifier and transport data. & A quotient representative is treated as if the substrate constructed it. \\
\texttt{axiom-purity --strict}: \texttt{propext} & No theorem depends on proposition equality from bidirectional implication. & Proposition-level transport must keep proof directions explicit. & A bidirectional implication is sealed into equality and moved through arbitrary contexts. \\
\texttt{conservativity-audit} & Baseline Lean modules do not import modules owned by AI-originated chapters. & Recognized or compressed surfaces cannot alter the baseline substrate through hidden import flow. & A non-baseline recognizer becomes baseline proof infrastructure without carrying its origin boundary. \\
\texttt{conservativity-audit} origin scan & \texttt{\textbackslash origin\{ai\}} closure-status records determine protected module prefixes. & The paper-side admission track and Lean-side import graph must agree. & A chapter's status is stated in prose but ignored by the theorem dependency graph. \\
\texttt{bedc\_ci.py audit}: marker existence & Every \texttt{\textbackslash leanchecked}, \texttt{\textbackslash leanvariant}, \texttt{\textbackslash leandef}, \texttt{\textbackslash leanstmt}, and \texttt{\textbackslash leantarget} resolves. & A formal name is a certificate only if the declaration exists in the Lean inventory. & A checked-looking paper claim points to no checked substrate object. \\
\texttt{bedc\_ci.py audit}: duplicate labels & Paper labels are unique. & Cross-reference names are certificate channels, not reusable decorations. & A reader or script follows a label to the wrong proof site. \\
\texttt{bedc\_ci.py audit}: closure-status diagnostics & Closure blocks declare required theory and verification fields; high verification status has a resolving Lean target. & The theory axis and verification axis remain explicit and independent. & Paper closure is inferred from Lean status, or Lean status is inferred from paper closure. \\
\texttt{bedc\_ci.py audit}: forbidden constructs & The broader audit surface rejects forbidden Lean constructs and marker inconsistencies. & The substrate cannot widen its own foundation by local convenience. & Source syntax changes the foundation while the paper still claims the old boundary. \\
\texttt{make check} & The manuscript compiles in draft mode with all included files syntactically coherent. & Boundary claims must be part of the actual paper object, not detached notes. & A chapter exists as uncompiled prose outside the auditable manuscript. \\
All gates together & Source syntax, proof ancestry, import graph, and paper names are simultaneously checked. & BEDC's operational membrane separates substrate-internal generation from $\mathsf{T}$-socketed supply. & A commitment crosses one channel while another channel still presents it as internal closure. \\
\bottomrule
\end{longtable}

\section{Closure}
\label{sec:audit-gates-closure}

The audit gates are the executable counterpart of the strong externality claim. \autoref{ch:visions-transcendental-input-and-induction} identifies the source-position of forward-binding belief as $\mathsf{T}$. \autoref{ch:visions-certificate-closure-and-generator-induction} explains how BEDC licenses generator-internal induction while keeping free-floating induction outside. \autoref{ch:visions-three-axioms-one-closure} identifies the three forbidden axiom families as one meta-closure move at three strata. The present sibling shows how the engineering refuses the corresponding breaches.

The result is a boundary that is philosophical, formal, and operational at once. It is philosophical because it names the far end of the socket as $\mathsf{T}$ and refuses to soften that name into an internalizable assumption. It is formal because theorem content is constrained by constructors, definitions, setup fields, Lean dependency ancestry, and resolving names. It is operational because scripts fail when the boundary is crossed. BEDC's audit gates therefore do not decorate the theory; they are the working membrane that keeps the substrate from pretending that the transcendental supply position is one of its own internal generators.
