\begin{theorem}[Diagonal-limit audit handoff]
\label{thm:diagonal-limit-compatibility-audit-handoff}
The root-unblock surface for $\DiagonalLimitCompatibilityUp$ is the package
formed by \autoref{thm:diagonal-limit-compatibility-root-dependency-triad},
\autoref{thm:diagonal-limit-compatibility-consumer-threshold}, and
\autoref{thm:diagonal-limit-compatibility-non-escape}. It exposes the triad
$D,W,Q$, the side rows $S,R,T$, and the local $\BHist/\hsame/\Cont/\Pkg/
\NameCert$ boundary without importing ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityAuditHandoff}
\begin{proof}
The root dependency triad names the required ledger, window, and readback rows
and records the Cauchy seal, Real completeness, and triangle-bound side rows.

The consumer-threshold theorem then places every downstream read of $Q,L$
behind the seven dependency rows and the local structural rows.

The non-escape theorem supplies the audit boundary. It removes quotient
streams, selected host limits, host real equality, choice data, and ambient
completeness from the handoff, so the three cited results form the complete
root-unblock surface.
\end{proof}

\begin{theorem}[Diagonal-limit obligation-closure package]
\label{thm:diagonal-limit-compatibility-obligation-closure-package}
An accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
forms an obligation-closure surface for the diagonal-limit handoff. The surface packages the triangle selector $T$, the $\CauchyLimitSealUp$ route $S$, the shared $\StreamNameUp$ window ledger $W$, the $\DyadicRatCoreUp$ tolerance ledger $D$, the $\RegSeqRatUp$ readback $Q$, the $\RealUp$ seal class $L$, componentwise $\hsame$ transport $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$ as the only rows available to downstream completion consumers.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityObligationClosurePackage}
\leanvariant{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier of \autoref{def:diagonal-limit-compatibility-carrier}. The displayed coordinates already list the diagonal source, triangle row, seal route, tolerance ledger, window ledger, readback row, real seal class, transports, continuations, provenance, and local certificate.

Apply \autoref{thm:diagonal-limit-compatibility-namecert-obligations}, \autoref{thm:diagonal-limit-compatibility-triangle-selector-alignment}, and \autoref{thm:diagonal-limit-compatibility-seal-route-compatibility}. These results identify the obligation rows, fix the triangle selector to $W,D$, and force the seal route to reach $Q,L$ only through $R,T,D,W$.

Finally use \autoref{thm:diagonal-limit-compatibility-classifier-transport} and \autoref{thm:diagonal-limit-compatibility-non-escape}. Transport preserves the same classifier rows, and non-escape excludes quotient streams, selected host limits, host real equality, choice data, and ambient completeness. Thus the listed packet is the complete obligation-closure surface.
\end{proof}

\begin{theorem}[Diagonal-limit shared window ledger]
\label{thm:diagonal-limit-compatibility-shared-window-ledger}
For an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
the $\StreamNameUp$ row $W$ is the shared finite window ledger for the diagonal selector, triangle-bound estimate, dyadic tolerance read, $\RegSeqRatUp$ readback, and downstream $\CauchyLimitSealUp$ consumer. No consumer may replace $W$ after entering the displayed compatibility packet.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilitySharedWindowLedger}
\begin{proof}
Start from the carrier projection. The window row $W$ is displayed together with the diagonal packet $R$, triangle row $T$, dyadic ledger $D$, seal route $S$, readback row $Q$, and real seal class $L$.

Use \autoref{thm:diagonal-limit-compatibility-triangle-selector-alignment}. It fixes the triangle row to the same selected windows named by $R,W,D$ and excludes a second selector surface.

Use \autoref{thm:diagonal-limit-compatibility-seal-route-compatibility} and \autoref{thm:diagonal-limit-compatibility-classifier-transport}. The seal route can reach $Q,L$ only after $W$ has been fixed, and transport preserves that same compatibility classifier.

The non-escape theorem, \autoref{thm:diagonal-limit-compatibility-non-escape}, supplies the boundary. Since no alternate window family is exported, $W$ remains the shared ledger for every downstream read.
\end{proof}

\begin{theorem}[Diagonal-limit seal consumer threshold]
\label{thm:diagonal-limit-compatibility-seal-consumer-threshold}
In an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
a downstream $\CauchyLimitSealUp$ or $\RealUp$ consumer may inspect the $\RegSeqRatUp$ readback $Q$ and the $\RealUp$ seal class $L$ only after the diagonal packet $R$, triangle selector row $T$, dyadic tolerance ledger $D$, shared window ledger $W$, componentwise $\hsame$ transport $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$ have been read.
\end{theorem}
\begin{proof}
Project the accepted carrier and isolate the consumer-facing rows $S,Q,L$. The seal route is part of the displayed packet and is not an independent completion principle.

Apply \autoref{thm:diagonal-limit-compatibility-namecert-obligations}. Its seal-compatibility and classifier-transport clauses place the read of $Q,L$ behind the diagonal route, triangle estimate, tolerance ledger, window family, transports, continuations, provenance, and local naming row.

Now apply \autoref{thm:diagonal-limit-compatibility-seal-route-compatibility}. The route $S$ cannot bypass $R,T,D,W$ when it reaches $Q$ and $L$.

Finally use \autoref{thm:diagonal-limit-compatibility-non-escape}. Because the packet exports no selected host limit, host real equality, choice datum, or ambient completeness principle, the displayed rows form the threshold for every downstream seal consumer.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_seal\_consumer\_threshold}

\begin{theorem}[Diagonal-limit source ledger]
\label{thm:diagonal-limit-compatibility-source-ledger}
For an accepted $\DiagonalLimitCompatibilityUp$ $\BHist$ carrier
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
the source ledger is exactly the displayed $\RealCompletenessUp$ row $R$,
triangle row $T$, seal route $S$, dyadic tolerance ledger $D$, stream-window
row $W$, regular-rational readback row $Q$, $\RealUp$ seal row $L$,
componentwise $\hsame$ transport $H$, displayed $\Cont$ routes $C$, $\Pkg$
provenance $P$, and local $\NameCert$ row $N$ of
\autoref{def:diagonal-limit-compatibility-carrier}. By
\autoref{thm:diagonal-limit-compatibility-non-escape}, no other source row is
available to the compatibility packet.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:diagonal-limit-compatibility-carrier}. The coordinates
$R,T,S,D,W,Q,L$ are the only source, estimate, seal, tolerance, window,
readback, and real-seal rows in the packet.

Read the structural rows $H,C,P,N$. They do not create further source data;
they transport, route, record provenance, and name the already displayed
coordinates.

Apply \autoref{thm:diagonal-limit-compatibility-non-escape}. Since the packet
exports no host limit, quotient stream, choice datum, host real equality, or
ambient completeness principle, the listed rows are the whole source ledger.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilitySourceLedger}

\begin{theorem}[Diagonal-limit consumer transport]
\label{thm:diagonal-limit-compatibility-consumer-transport}
For accepted $\DiagonalLimitCompatibilityUp$ $\BHist$ carriers
$K=(R,T,S,D,W,Q,L,H,C,P,N)$ and
$K'=(R',T',S',D',W',Q',L',H',C',P',N')$, every downstream seal or
$\RealUp$ consumer that reads through the carrier of
\autoref{def:diagonal-limit-compatibility-carrier} factors through the
displayed componentwise $\hsame$ rows in $H,H'$ and the displayed $\Cont$
routes in $C,C'$, with $\Pkg$ provenance $P,P'$ and local $\NameCert$ rows
$N,N'$ preserving the same compatibility surface. By
\autoref{thm:diagonal-limit-compatibility-non-escape}, no consumer may bypass
those rows.
\end{theorem}
\begin{proof}
Start with the two accepted carriers and isolate the consumer-facing rows
$S,Q,L$ and $S',Q',L'$. The carrier definition places both reads behind the
same diagonal, triangle, tolerance, and window coordinates.

Use the componentwise transport rows $H,H'$. They identify the source rows by
$\hsame$ before a consumer reaches the seal or $\RealUp$ rows, so the
classifier transported to the consumer is the displayed one.

Use the continuation rows $C,C'$ next. Every read of the seal route, regular
readback, or real-seal row is replayed through the displayed $\Cont$ routes,
and $P,P',N,N'$ record only that finite route surface.

Finally apply \autoref{thm:diagonal-limit-compatibility-non-escape}. Since no
alternate host-limit, quotient-stream, choice, or ambient-completeness route is
exported, downstream consumers factor through the displayed transport and
continuation rows.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityConsumerTransport}

\begin{theorem}[Diagonal-limit ambient completeness refusal]
\label{thm:diagonal-limit-compatibility-ambient-completeness-refusal}
An accepted $\DiagonalLimitCompatibilityUp$ $\BHist$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
from \autoref{def:diagonal-limit-compatibility-carrier} exports no host limit,
no quotient stream, no choice datum, and no ambient completeness principle.
Its only exported surface is the displayed source ledger, componentwise
$\hsame$ transport $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$,
and local $\NameCert$ row $N$; this is exactly the non-escape boundary of
\autoref{thm:diagonal-limit-compatibility-non-escape}.
\end{theorem}
\begin{proof}
Project the packet $K$. The visible coordinates are the diagonal packet,
triangle row, seal route, tolerance ledger, window row, readback row, real
seal row, transport, continuation, provenance, and naming row.

Inspect the omitted coordinates. There is no row for a selected host limit,
no row for quotienting streams, no row for a choice datum, and no row for an
ambient completeness principle.

Apply \autoref{thm:diagonal-limit-compatibility-non-escape}. The non-escape
boundary therefore turns the omission into a consumer rule: a downstream
chapter may read the displayed compatibility packet, but it may not treat that
read as host completeness or as a hidden quotient construction.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityAmbientCompletenessRefusal}

\begin{theorem}[Diagonal-limit source gate]
\label{thm:diagonallimitcompatibility-source-gate}
For an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
every accepted downstream read first fixes the $\RealCompletenessUp$ diagonal packet $R$, the $\StreamNameUp$ window family $W$, the $\DyadicRatCoreUp$ tolerance ledger $D$, and the $\RegSeqRatUp$ readback row $Q$ before any consumer treats the seal route $S$ or the $\RealUp$ seal row $L$ as available. The source gate is exactly the route displayed by \autoref{def:diagonal-limit-compatibility-carrier}; it is not a host limit selection and not an ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilitySourceGate}
\begin{proof}
Project the carrier $K$ from \autoref{def:diagonal-limit-compatibility-carrier}. The diagonal source $R$, windows $W$, dyadic ledger $D$, readback $Q$, seal route $S$, and seal row $L$ are all named coordinates of the same finite packet.

Apply \autoref{thm:diagonal-limit-compatibility-triangle-selector-alignment} and \autoref{thm:diagonal-limit-compatibility-seal-consumer-threshold}. The selector alignment fixes $W,D$ at the diagonal source, and the threshold theorem places every downstream seal read behind $R,T,D,W,H,C,P,N$.

Use \autoref{thm:diagonal-limit-compatibility-seal-route-compatibility} to route the read of $Q,L$ through the displayed rows. Then use \autoref{thm:diagonal-limit-compatibility-classifier-transport} to keep the same classifier under $H$ and $C$.

Finally apply \autoref{thm:diagonal-limit-compatibility-non-escape}. Since the packet exports no selected host limit, host real equality, choice datum, or ambient completeness principle, the displayed source gate is the only way a downstream consumer reaches the seal-facing rows.
\end{proof}

\begin{theorem}[Diagonal-limit triangle-seal interface]
\label{thm:diagonallimitcompatibility-triangle-seal-interface}
For an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
the $\RegularCauchyTriangleBoundUp$ row $T$ is the sole public interface between the diagonal selector carried by $R,W,D$ and the $\CauchyLimitSealUp$ route $S$. A consumer may pass from the diagonal source to the seal route only through the triangle row together with the displayed dyadic ledger, stream-window ledger, classifier transport, continuation routes, package provenance, and local naming row.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_triangle\_seal\_interface}
\begin{proof}
Start with the carrier. The only row naming the three-leg estimate between the diagonal source and the seal route is $T$, and the only ledgers available to it are $D$ and $W$.

Apply \autoref{thm:diagonal-limit-compatibility-triangle-selector-alignment}. It binds $T$ to the same selected windows and dyadic tolerance ledger named by $R,W,D$, so the selector side has no second interface row.

Next apply \autoref{thm:diagonal-limit-compatibility-seal-route-compatibility}. The route $S$ reaches $Q,L$ only through $R,T,D,W$, so the seal side also has no bypass around the triangle estimate.

Classifier transport and non-escape close the interface. By \autoref{thm:diagonal-limit-compatibility-classifier-transport} the same interface is preserved through $H,C$, and by \autoref{thm:diagonal-limit-compatibility-non-escape} no quotient stream, selected host limit, choice datum, or ambient completeness coordinate can supply another route.
\end{proof}

\begin{theorem}[Diagonal-limit downstream consumer gate]
\label{thm:diagonallimitcompatibility-downstream-consumer-gate}
Every $\RealUp$ or $\CauchyLimitSealUp$ consumer of an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
factors through the displayed rows $R,T,S,D,W,Q,L,H,C,P,N$. The consumer may use the diagonal packet, triangle interface, seal route, dyadic ledger, stream-window ledger, regular rational readback, real seal row, componentwise transport, continuation routes, package provenance, and local naming row, but it cannot introduce host limits, quotient streams, choice data, host real equality, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityDownstreamConsumerGate}
\begin{proof}
Read the consumer from the carrier. The displayed coordinates already list the only source, interface, route, ledger, readback, transport, continuation, provenance, and naming rows available to the packet.

Use \autoref{thm:diagonallimitcompatibility-source-gate} to force the source-side order. The diagonal packet, stream windows, dyadic ledger, and regular rational readback are fixed before the consumer treats the seal-facing rows as available.

Use \autoref{thm:diagonallimitcompatibility-triangle-seal-interface} together with \autoref{thm:diagonal-limit-compatibility-seal-route-compatibility}. These theorems force the route from the diagonal selector to the seal consumer through $T,D,W,S$ and then to $Q,L$.

Finally apply \autoref{thm:diagonal-limit-compatibility-classifier-transport} and \autoref{thm:diagonal-limit-compatibility-non-escape}. Transport preserves the displayed classifier, and non-escape excludes every host-limit, quotient-stream, choice, host-equality, or ambient-completeness coordinate not carried by $K$.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility window-budget triad lock]
\label{thm:diagonal-limit-compatibility-window-budget-triad-lock}
Every $\RealUp$ or $\CauchyLimitSealUp$ consumer of an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
must read the same triad $(D,W,Q)$ before the terminal seal row $L$ is available. Here $W$ is the $\StreamNameUp$ finite-window surface, $D$ is the $\DyadicRatCoreUp$ tolerance ledger, and $Q$ is the $\RegSeqRatUp$ readback row. The three rows form one shared route through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface; no quotient stream, selected host limit, host real equality, choice datum, or ambient completeness principle can supply a second triad.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_window\_budget\_triad\_lock}
\begin{proof}
Project the accepted packet from \autoref{def:diagonal-limit-compatibility-carrier}. The rows $D,W,Q$ occur as named coordinates of the same finite packet as the terminal seal row $L$.

Apply \autoref{thm:diagonal-limit-compatibility-triangle-selector-alignment}. It binds the selector side to the displayed $\StreamNameUp$ windows $W$ and $\DyadicRatCoreUp$ tolerance ledger $D$, so the window and tolerance coordinates are fixed before any seal-facing read.

Next apply \autoref{thm:diagonal-limit-compatibility-seal-route-compatibility}. The seal route reaches the $\RegSeqRatUp$ readback $Q$ and terminal row $L$ only through the same $R,T,D,W$ route, so $Q$ is not a separate host readback channel.

Use \autoref{thm:diagonal-limit-compatibility-classifier-transport} to carry this route through the displayed $H$ and $C$ rows. The transported consumer therefore sees the same $(D,W,Q)$ triad that the carrier exposes.

Finally apply \autoref{thm:diagonal-limit-compatibility-non-escape}. Since the packet exports no quotient stream, selected host limit, host real equality, choice datum, or ambient completeness coordinate, no downstream $\RealUp$ or $\CauchyLimitSealUp$ consumer can replace the displayed triad before reading $L$.
\end{proof}

\begin{theorem}[Diagonal-limit shared modulus terminal seal]
\label{thm:diagonal-limit-compatibility-shared-modulus-terminal-seal}
For an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
any terminal $\RealUp$ or $\CauchyLimitSealUp$ seal read that factors through a compatible $\CauchyModulusExtractionUp$ packet
$$
M=(E,B,W,S,\mathsf{Mu},Q,H,C,P,N)
$$
and through the finite-window budget envelope of $\CauchyLimitSealUp$ passes through one shared finite route. The route first reads $R,T,S,D,W,Q,L,H,C,P,N$ from the diagonal-limit packet and then reads the extraction rows $E,B,W,S,\mathsf{Mu},Q,H,C,P,N$ as the same budget-window-modulus surface. It exports no quotient stream, selected host limit, host real equality, trichotomy, choice datum, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the accepted diagonal packet. By \autoref{thm:diagonal-limit-compatibility-non-escape}, every seal-facing read of $K$ is confined to $R,T,S,D,W,Q,L,H,C,P,N$ and cannot import a quotient stream, selected host limit, host real equality, trichotomy, choice datum, or ambient completeness.

Next attach the compatible modulus-extraction packet. The public export of \autoref{thm:cauchy-modulus-extraction-public-export} exposes exactly $E,B,W,S,\mathsf{Mu},Q,H,C,P,N$, and the consumer bridge of \autoref{thm:cauchy-modulus-extraction-real-completion-consumer-bridge} forces Real-completion reads of $\mathsf{Mu}$ through those displayed rows.

Finally align the seal envelope. The finite-window budget equivalence of \autoref{thm:cauchy-limit-seal-finite-window-budget-equivalence} identifies the terminal seal read with the same finite budget-window route, and the verification handoff of \autoref{thm:cauchy-limit-seal-verification-handoff} repacks that route as the reusable $\CauchyLimitSealUp$ surface. Thus the Real-facing terminal read is the same finite budget-window-modulus route already displayed by the diagonal packet and the extraction packet, with no extra completion coordinate.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilitySharedModulusTerminalSeal}

\begin{theorem}[Diagonal-limit window synchronizer pullback]
\label{thm:diagonal-limit-window-synchronizer-pullback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let
$$
Z=(W_Z,Q_Z,S_Z,L_Z,D_Z,H_Z,C_Z,P_Z,N_Z)
$$
be an accepted $\RealWindowSynchronizerUp$ packet whose $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\CauchyLimitSealUp$ row, $\RealUp$ seal row, and shared threshold-budget rows agree componentwise with $W,Q,S,L,D$ through the displayed $\hsame$ and $\Cont$ routes. Then every terminal $\RealUp$ or $\CauchyLimitSealUp$ consumer of $K$ pulls back through the synchronizer finite window-to-seal packet $Z$.

The pullback uses only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the two accepted packets. It does not introduce quotient streams, selected host limits, host real equality, choice data, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityWindowSynchronizerPullback}
\begin{proof}
First lock the diagonal side. Apply \autoref{thm:diagonal-limit-compatibility-window-budget-triad-lock} to force every terminal read of $K$ through the common $(D,W,Q)$ triad before $L$ is available. Then apply \autoref{thm:diagonal-limit-compatibility-shared-modulus-terminal-seal} to make the terminal $\RealUp$ and $\CauchyLimitSealUp$ reads use the same finite budget-window-modulus route.

Next read the synchronizer side. The budget pullback of \autoref{thm:real-window-synchronizer-budget-pullback} places the synchronizer threshold and window rows over the same finite budget surface. The limit-seal compatibility of \autoref{thm:real-window-synchronizer-limit-seal-compatibility} carries the $\CauchyLimitSealUp$ row through that surface, and the Real-seal exposure of \autoref{thm:real-window-synchronizer-real-seal-exposure} exposes the terminal $\RealUp$ seal only after the same window-to-seal route.

It remains to identify the two finite routes. The hypotheses give componentwise $\hsame$ and $\Cont$ transport from the diagonal rows $W,Q,S,L,D$ to the synchronizer rows $W_Z,Q_Z,S_Z,L_Z,D_Z$. Transport through the displayed $\BHist$, $\Pkg$, and $\NameCert$ rows repacks the consumer as a read of $Z$ without changing the terminal object.

Finally use \autoref{thm:real-window-synchronizer-nonescape}. Since the synchronizer packet exports no quotient stream, selected host limit, host real equality, choice datum, or ambient completeness coordinate, the pulled-back consumer has no route outside the finite window-to-seal packet.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility window source exhaustion]
\label{thm:diagonal-limit-compatibility-window-source-exhaustion}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Every accepted diagonal-limit consumer route that reaches the $\RealUp$ seal row $L$ first factors through the displayed source ledger, the window-budget triad $(D,W,Q)$, the shared modulus route, the synchronizer pullback surface, and the seal route rows $S,L$.

The exhausted route exports no quotient stream, selected host limit, ambient completeness principle, or independent real-equality coordinate. Its only available coordinates are the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of $K$ together with the compatible finite-window packets through which the route is explicitly pulled back.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_window\_source\_exhaustion}
\begin{proof}
Begin with the source ledger. Apply \autoref{thm:diagonal-limit-compatibility-source-ledger} to identify the readable source rows as $R,T,S,D,W,Q,L,H,C,P,N$ and to exclude any hidden host-limit or quotient-stream source.

Next lock the finite window route. The shared window ledger and consumer transport of \autoref{thm:diagonal-limit-compatibility-window-budget-triad-lock} force the consumer through $(D,W,Q)$ before the seal row is available, while \autoref{thm:diagonal-limit-compatibility-shared-modulus-terminal-seal} identifies the terminal seal read with the same finite budget-window-modulus route.

The ambient-completeness refusal is supplied by \autoref{thm:diagonal-limit-compatibility-ambient-completeness-refusal}. It prevents the consumer from replacing the displayed finite route by a host completeness principle, selected limit, or host real-equality coordinate.

Finally apply \autoref{thm:diagonal-limit-window-synchronizer-pullback}. The terminal consumer is repacked through the synchronizer finite window-to-seal packet, and the carrier projection together with the non-escape clauses of the displayed packets leaves no coordinate outside the stated source, window, modulus, synchronizer, and seal rows.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility formal target packet]
\label{thm:diagonal-limit-compatibility-formal-target-packet}
Every Lean-facing formal target for an accepted $\DiagonalLimitCompatibilityUp$
packet exposes exactly the carrier rows
$$
R,T,S,D,W,Q,L,H,C,P,N
$$
together with the compatible finite-window packets cited by
\autoref{thm:diagonal-limit-compatibility-window-source-exhaustion}. The
target may consume $\RealCompletenessUp$,
$\RegularCauchyTriangleBoundUp$, $\CauchyLimitSealUp$, $\DyadicRatCoreUp$,
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ only through those displayed
rows and their finite-window pullbacks.

The formal target has no coordinate for quotient streams, selected host
limits, host real equality, choice data, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityFormalTargetPacket}
\begin{proof}
Project the carrier of the accepted diagonal-limit packet. The projection
displays exactly $R,T,S,D,W,Q,L,H,C,P,N$, and the local NameCert obligations
make the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows
the only routes available to a formal target.

Next apply the terminal Real route and the window-budget triad lock. The
terminal route keeps the Real-facing consumer on $R,T,S,D,W,Q,L,H,C,P,N$, while
\autoref{thm:diagonal-limit-compatibility-window-budget-triad-lock} forces any
seal-facing read through the displayed $(D,W,Q)$ finite-window triad.

Now attach the shared modulus terminal seal and the synchronizer pullback.
\autoref{thm:diagonal-limit-compatibility-shared-modulus-terminal-seal}
identifies the terminal $\RealUp$ and $\CauchyLimitSealUp$ reads with one
finite budget-window-modulus route, and
\autoref{thm:diagonal-limit-window-synchronizer-pullback} repacks that route
through the compatible $\RealWindowSynchronizerUp$ packet.

Finally use
\autoref{thm:diagonal-limit-compatibility-window-source-exhaustion}. It
exhausts the source, window, shared modulus, synchronizer, and seal rows
available to the Lean-facing packet. The named upstream chapters may be
consumed only through these rows, so quotient streams, selected host limits,
host real equality, choice data, and ambient completeness have no target
coordinate.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_formal\_target\_packet}

\begin{theorem}[Diagonal-limit finite-window-only consumer]
\label{thm:diagonal-limit-compatibility-finite-window-only-consumer}
Every accepted $\DiagonalLimitCompatibilityUp$ consumer of $\RealUp$ or
$\CauchyLimitSealUp$ is admitted only through the displayed finite rows
$$
R,T,S,D,W,Q,L,H,C,P,N
$$
of its accepted packet and through the compatible finite-window packets cited by
\autoref{thm:diagonal-limit-compatibility-window-source-exhaustion}. A route
that uses quotient streams, host real equality, selected host limits, choice
data, or ambient completeness is outside the carrier and is not an admitted
consumer route.
\end{theorem}
\begin{proof}
Start with the source ledger. By
\autoref{thm:diagonal-limit-compatibility-source-ledger}, the accepted packet
exposes only $R,T,S,D,W,Q,L,H,C,P,N$ together with its displayed $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Lock the finite route before the terminal read. The window-budget triad lock of
\autoref{thm:diagonal-limit-compatibility-window-budget-triad-lock} forces the
consumer through $(D,W,Q)$, and
\autoref{thm:diagonal-limit-compatibility-shared-modulus-terminal-seal} makes
the terminal $\RealUp$ and $\CauchyLimitSealUp$ reads share the same
finite-window seal route.

Next pull the route through the synchronizer. Apply
\autoref{thm:diagonal-limit-window-synchronizer-pullback} to repack the
terminal consumer through the compatible finite window-to-seal packet without
adding a host coordinate.

Finally use
\autoref{thm:diagonal-limit-compatibility-window-source-exhaustion}. It
exhausts the admissible source, triad, shared modulus, synchronizer, and seal
coordinates, while \autoref{thm:diagonal-limit-compatibility-non-escape}
removes quotient streams, host real equality, selected host limits, choice
data, and ambient completeness from the carrier. Therefore every accepted
$\RealUp$ or $\CauchyLimitSealUp$ consumer is finite-window-only.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_finite\_window\_only\_consumer}
