\begin{definition}[DiagonalLimitCompatibility root formal source]
\label{def:diagonal-limit-compatibility-root-formal-source}
A $\DiagonalLimitCompatibilityUp$ root formal source is a finite packet
$$
S=(B,T,W,R,L,H,C,P,N)
$$
where $B$ is the $\CauchyDiagonalBudgetUp$ source row, $T$ is the $\DiagonalTailSelectorUp$ selector row, $W$ is the $\StreamNameUp$ finite-window row, $R$ is the $\RegSeqRatUp$ regular handoff row, $L$ is the $\RealUp$ seal row, $H$ records componentwise $\hsame$ transports, $C$ records displayed $\Cont$ routes, $P$ records $\Pkg$ provenance, and $N$ is the local $\NameCert_{\DiagonalLimitCompatibilityUp}$ row.

The sibling sources are the budget packet of \autoref{ch:concrete-instances-cauchydiagonalbudget-namecert}, the selector packet of \autoref{ch:concrete-instances-diagonaltailselector-namecert}, the finite-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational sequence surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the seal surface of \autoref{ch:concrete-instances-real-namecert}. The tuple contains no quotient stream, host limit, countable-choice selector, or ambient completeness coordinate.
\end{definition}
\leandef{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityRootFormalSource}

\begin{theorem}[DiagonalLimitCompatibility root formal route]
\label{thm:diagonal-limit-compatibility-root-formal-route}
Every accepted $\DiagonalLimitCompatibilityUp$ route that is available to a root formal consumer factors through the finite source tuple of \autoref{def:diagonal-limit-compatibility-root-formal-source}. In particular, the consumer reads the budget row $B$, selector row $T$, finite window row $W$, regular handoff row $R$, and $\RealUp$ seal row $L$ before the local $\NameCert_{\DiagonalLimitCompatibilityUp}$ route is accepted.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityRootFormalRoute}
\begin{proof}
Project the source tuple $S=(B,T,W,R,L,H,C,P,N)$. The diagonal budget row $B$ supplies the precision and mesh budget, and the selector row $T$ supplies the cofinal tail selection used by the diagonal route.

The finite-window and regular handoff rows are then read in order. The $\StreamNameUp$ row $W$ displays the finite observation window, and the $\RegSeqRatUp$ row $R$ is the regular sequence handoff attached to that same window.

Only after those rows are visible does the route reach the $\RealUp$ seal row $L$. The transports in $H$, continuations in $C$, provenance in $P$, and local naming row $N$ replay that same order for the accepted $\DiagonalLimitCompatibilityUp$ consumer, so the route factors through the listed source tuple.
\end{proof}

\begin{theorem}[DiagonalLimitCompatibility root formal non-escape]
\label{thm:diagonal-limit-compatibility-root-formal-nonescape}
An accepted root formal route for $\DiagonalLimitCompatibilityUp$ cannot use quotient streams, host limits, countable choice, or ambient completeness to replace any row of the finite source tuple of \autoref{def:diagonal-limit-compatibility-root-formal-source}.
\end{theorem}
\begin{proof}
Read the carrier inventory of \autoref{def:diagonal-limit-compatibility-root-formal-source}. Its only source rows are $B,T,W,R,L,H,C,P,N$, and each row is tied to a displayed sibling chapter: Cauchy diagonal budget, diagonal tail selector, StreamName finite window, RegSeqRat regular handoff, and Real seal.

Quotient streams and host limits would require additional equality or limit coordinates, but none are present in the tuple. Countable choice would require an unbounded selector family beyond $T$, while ambient completeness would require a completion principle beyond the seal row $L$.

Thus every accepted route stays inside the finite handoff packet. Any consumer that asks for one of the excluded principles has asked for data not carried by the $\DiagonalLimitCompatibilityUp$ source tuple.
\end{proof}

\begin{theorem}[DiagonalLimitCompatibility root readback determinacy]
\label{thm:diagonal-limit-compatibility-root-readback-determinacy}
Let $S=(B,T,W,R,L,H,C,P,N)$ and $S'=(B',T',W',R',L',H',C',P',N')$ be accepted $\DiagonalLimitCompatibilityUp$ root formal routes. If the displayed $\CauchyDiagonalBudgetUp$ rows agree as $B=B'$, the displayed $\DiagonalTailSelectorUp$ rows agree as $T=T'$, the displayed $\StreamNameUp$ finite windows agree as $W=W'$, the displayed $\RegSeqRatUp$ handoff rows agree as $R=R'$, and the displayed $\RealUp$ seal rows agree as $L=L'$, then the two routes determine the same local $\DiagonalLimitCompatibilityUp$ readback through $H,C,P,N$. They cannot be separated by quotient streams, host limits, countable-choice selectors, or ambient completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:diagonal-limit-compatibility-root-formal-route} to both accepted routes. Each route is forced through the finite source tuple of \autoref{def:diagonal-limit-compatibility-root-formal-source}, so every readback begins with the same five displayed source rows $B,T,W,R,L$.

Compare those five source rows componentwise. The budget, selector, finite-window, regular handoff, and seal agreements identify the only external rows available before the local $\DiagonalLimitCompatibilityUp$ route reaches $H,C,P,N$.

It remains to exclude a later separating coordinate. By \autoref{thm:diagonal-limit-compatibility-root-formal-nonescape}, neither route can introduce quotient streams, host limits, countable-choice selectors, or ambient completeness in place of the finite tuple. Hence the remaining local readback through $H,C,P,N$ is determined by the same displayed source data.
\end{proof}

\begin{theorem}[DiagonalLimitCompatibility root formal seal factorization]
\label{thm:diagonal-limit-compatibility-root-formal-seal-factorization}
Every accepted root formal route $S=(B,T,W,R,L,H,C,P,N)$ for $\DiagonalLimitCompatibilityUp$ factors any $\RealUp$ or completion-facing seal read through the ordered rows $B,T,W,R,L$ before the local $\DiagonalLimitCompatibilityUp$ rows $H,C,P,N$ are consumed. No quotient stream, host limit, countable-choice selector, or ambient completeness row can replace the seal factor $L$.

Consequently, after the seal factor $L$ is reached through the displayed $\CauchyDiagonalBudgetUp$, $\DiagonalTailSelectorUp$, $\StreamNameUp$, and $\RegSeqRatUp$ rows, the remaining readback through $H,C,P,N$ is determined by those same source rows.
\end{theorem}
\begin{proof}
Start with the formal route. By \autoref{thm:diagonal-limit-compatibility-root-formal-route}, every accepted root formal consumer reads the ordered tuple $B,T,W,R,L$ before it accepts the local $\NameCert_{\DiagonalLimitCompatibilityUp}$ rows.

Next exclude off-packet seal sources. The non-escape theorem \autoref{thm:diagonal-limit-compatibility-root-formal-nonescape} says that quotient streams, host limits, countable-choice selectors, and ambient completeness rows are not coordinates of the source tuple, so none of them can stand in for the $\RealUp$ seal row $L$.

Finally apply readback determinacy. Once the displayed source rows $B,T,W,R,L$ have been fixed, \autoref{thm:diagonal-limit-compatibility-root-readback-determinacy} identifies the subsequent $H,C,P,N$ readback as the one determined by those rows. Thus every Real or completion-facing seal read factors through $B,T,W,R,L$ before the local diagonal-compatibility rows are consumed.
\end{proof}

\begin{theorem}[DiagonalLimitCompatibility root formal Lean-target boundary]
\label{thm:diagonal-limit-compatibility-root-formal-lean-target-boundary}
Every Lean target that formalizes the $\DiagonalLimitCompatibilityUp$ root formal handoff must expose exactly the finite rows
$$
B,T,W,R,L,H,C,P,N
$$
from \autoref{def:diagonal-limit-compatibility-root-formal-source}. The target may project these rows and prove route, non-escape, readback determinacy, or seal factorization over them, but it may not add a quotient stream row, host limit row, countable choice row, ambient completeness row, or any second source row outside the displayed tuple.
\end{theorem}
\begin{proof}
Project the source tuple. The route theorem \autoref{thm:diagonal-limit-compatibility-root-formal-route} already forces every accepted root formal consumer through $B,T,W,R,L,H,C,P,N$.

Next apply \autoref{thm:diagonal-limit-compatibility-root-formal-nonescape}. The excluded quotient, host-limit, choice, and completeness coordinates are not carried by the tuple, so they cannot become formal target rows.

Finally use \autoref{thm:diagonal-limit-compatibility-root-readback-determinacy} and \autoref{thm:diagonal-limit-compatibility-root-formal-seal-factorization}. They show that the displayed rows are sufficient for readback and seal-facing consumers, leaving no remaining source coordinate for the formal boundary.
\end{proof}

\begin{theorem}[DiagonalLimitCompatibility root formal kernel scope]
\label{thm:diagonal-limit-compatibility-root-formal-kernel-scope}
In the root formal handoff for $\DiagonalLimitCompatibilityUp$, the row $B$ is the $\CauchyDiagonalBudgetUp$ row, $T$ is the $\DiagonalTailSelectorUp$ row, $W$ is the $\StreamNameUp$ row, $R$ is the $\RegSeqRatUp$ row, $L$ is the $\RealUp$ seal row, $H$ is the displayed $\hsame$ transport row, $C$ is the displayed $\Cont$ route row, $P$ is the $\Pkg$ provenance row, and $N$ is the local $\NameCert$ row. Together these rows form the finite $\BHist$ kernel scope for the handoff, and no root formal target for this site may replace them by a host sequence, host real, external selector family, quotient stream, or ambient completeness principle.
\end{theorem}
\begin{proof}
Read \autoref{def:diagonal-limit-compatibility-root-formal-source} componentwise. It assigns the five source rows to $\CauchyDiagonalBudgetUp$, $\DiagonalTailSelectorUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, and assigns the support rows to $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The route theorem \autoref{thm:diagonal-limit-compatibility-root-formal-route} then places those rows inside the accepted root formal consumer route. The seal factorization theorem \autoref{thm:diagonal-limit-compatibility-root-formal-seal-factorization} identifies the same order before the local support rows are consumed.

Apply non-escape from \autoref{thm:diagonal-limit-compatibility-root-formal-nonescape}. Since host sequences, host reals, external selector families, quotient streams, and ambient completeness principles are absent from the $\BHist$ tuple, the kernel scope is exactly the displayed row list.
\end{proof}

\begin{theorem}[DiagonalLimitCompatibility root formal audit handoff]
\label{thm:diagonal-limit-compatibility-root-formal-audit-handoff}
An audit consumer for the $\DiagonalLimitCompatibilityUp$ root formal handoff may accept only the finite route
$$
B \longrightarrow T \longrightarrow W \longrightarrow R \longrightarrow L \longrightarrow H,C,P,N
$$
over the source tuple of \autoref{def:diagonal-limit-compatibility-root-formal-source}. The audit surface rejects quotient streams, host limits, countable choice, ambient completeness, and any consumer route whose seal or readback bypasses one of the displayed rows.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityRootFormalAuditHandoff}
\begin{proof}
Begin with the accepted route. By \autoref{thm:diagonal-limit-compatibility-root-formal-route}, an audit read that belongs to this root handoff must pass through the displayed tuple.

Seal-facing reads are handled by \autoref{thm:diagonal-limit-compatibility-root-formal-seal-factorization}. They pass through $B,T,W,R,L$ before the local $H,C,P,N$ rows are consumed, so a bypassing seal route is not an accepted route for this site.

Readback-facing reads are handled by \autoref{thm:diagonal-limit-compatibility-root-readback-determinacy}. Once the displayed rows are fixed, the local readback is fixed as well. The non-escape theorem \autoref{thm:diagonal-limit-compatibility-root-formal-nonescape} removes quotient streams, host limits, countable choice, and ambient completeness from the audit handoff.
\end{proof}
