\begin{theorem}[Diagonal-limit seal source synchronization]
\label{thm:diagonal-limit-compatibility-seal-source-synchronization}
For an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
any seal-facing read first fixes the diagonal packet $R$, the triangle row
$T$, the dyadic ledger $D$, the window ledger $W$, the regular readback row
$Q$, and the seal row $L$ through the displayed $\hsame$ transports $H$,
$\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$.
The read cannot inspect $Q$ or $L$ through a second source route, alternate
window ledger, host limit, or ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_seal\_source\_synchronization}
\begin{proof}
Project the carrier of
\autoref{def:diagonal-limit-compatibility-carrier}. The accepted packet
exposes exactly the source rows $R,T,S,D,W,Q,L$ together with $H,C,P,N$.

Use triangle selector alignment,
\autoref{thm:diagonal-limit-compatibility-triangle-selector-alignment}, to
bind the triangle row $T$ to the same dyadic ledger $D$ and window ledger $W$
already named by the diagonal packet $R$.

Now apply seal route compatibility,
\autoref{thm:diagonal-limit-compatibility-seal-route-compatibility}. The
seal route can read $Q$ and $L$ only after the displayed source, triangle,
tolerance, and window rows have been fixed.

Finally apply non-escape,
\autoref{thm:diagonal-limit-compatibility-non-escape}. Since no second source
route, alternate window ledger, host limit, host equality, choice datum, or
ambient completeness row is exported, the seal-facing read is synchronized to
the displayed packet rows.
\end{proof}

\begin{theorem}[Diagonal-limit triangle readback lock]
\label{thm:diagonal-limit-compatibility-triangle-readback-lock}
For an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N),
$$
the $\RegSeqRatUp$ readback row $Q$ is locked behind the same triangle row
$T$, dyadic ledger $D$, and window ledger $W$ that support the seal route.
After $T,D,W$ have been displayed, $Q$ cannot be selected from a second
regular readback route or from a tolerance row outside the packet.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_triangle\_readback\_lock}
\begin{proof}
Start with window ledger exactness,
\autoref{thm:diagonal-limit-compatibility-window-ledger-exactness}. The row
$W$ is the exact shared-window ledger read by the diagonal source, triangle
row, dyadic ledger, seal route, readback row, and real seal row.

Next use the triangle seal route,
\autoref{thm:diagonal-limit-compatibility-triangle-seal-route}. It places the
seal route to $Q$ behind the displayed $T,D,W$ rows.

Apply regular readback exactness,
\autoref{thm:diagonal-limit-compatibility-regular-readback-exactness}. That
theorem identifies $Q$ as the readback determined by the same $T,D,W$ route
and excludes another regular readback or dyadic witness.

The non-escape boundary then removes any remaining hidden source. The packet
has no coordinate from which a second readback route or alternate tolerance
surface could be selected.
\end{proof}

\begin{theorem}[Diagonal-limit real seal factorization]
\label{thm:diagonal-limit-compatibility-real-seal-factorization}
Every $\RealUp$ or $\CauchyLimitSealUp$ consumer of an accepted
$\DiagonalLimitCompatibilityUp$ packet factors through
$$
R,T,S,D,W,Q,L,H,C,P,N.
$$
The consumer receives the displayed diagonal source, triangle row, seal
route, dyadic ledger, window ledger, regular readback, real seal row,
componentwise transports, continuations, provenance, and local naming row. It
receives no quotient stream, selected host limit, host real equality, choice
datum, or ambient completeness theorem.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_real\_seal\_factorization}
\begin{proof}
First read the seal source synchronization theorem,
\autoref{thm:diagonal-limit-compatibility-seal-source-synchronization}. It
fixes the source, triangle, dyadic, window, readback, seal, transport, route,
provenance, and naming rows before a seal-facing consumer can proceed.

Then apply the triangle readback lock,
\autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}. The
regular readback row $Q$ is tied to the same $T,D,W$ route as the seal row,
so a $\CauchyLimitSealUp$ or $\RealUp$ consumer has no independent readback
surface.

Finally use completion consumer nonescape,
\autoref{thm:diagonal-limit-compatibility-completion-consumer-nonescape}.
Every completion-facing read remains inside the displayed packet rows and
exports none of the omitted quotient, host, choice, or completeness data.
\end{proof}

\begin{theorem}[Diagonal-limit Real seal consumer scope]
\label{thm:diagonal-limit-compatibility-real-seal-consumer-scope}
Every $\RealUp$ or $\CauchyLimitSealUp$ consumer of an accepted
$\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
first reads the synchronized source rows $R,T,D,W$, the $\RegSeqRatUp$
readback row $Q$, and the real seal row $L$ through $H,C,P,N$. Such a
consumer cannot obtain a host limit, quotient stream, choice datum, ambient
completeness row, or second source route.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_real\_seal\_consumer\_scope}
\begin{proof}
Apply \autoref{thm:diagonal-limit-compatibility-seal-source-synchronization}.
It fixes the displayed source rows $R,T,D,W$, the readback row $Q$, the seal
row $L$, and the structural rows $H,C,P,N$ before any seal-facing read can
continue.

Next use \autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}.
The readback row $Q$ is locked behind the same triangle, dyadic, and window
rows $T,D,W$, so the consumer has no independent readback or tolerance route.

Finally apply
\autoref{thm:diagonal-limit-compatibility-real-seal-factorization}. The
factorization routes every $\RealUp$ or $\CauchyLimitSealUp$ consumer through
the displayed packet rows and exports none of the host limit, quotient stream,
choice, ambient completeness, or second-source data excluded in the statement.
\end{proof}

\begin{theorem}[Diagonal-limit seal source scope row]
\label{thm:diagonal-limit-compatibility-seal-source-scope-row}
Every accepted $\DiagonalLimitCompatibilityUp$ packet
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
exposes a seal-facing $\RealUp$ or $\CauchyLimitSealUp$ consumer only after the finite budget-selector route, synchronized triangle row, dyadic ledger, stream window, $\RegSeqRatUp$ readback, Real seal, transports, continuations, provenance, and $\NameCert$ rows have been fixed. Thus the consumer reads only the displayed rows $R,T,S,D,W,Q,L,H,C,P,N$ and cannot obtain a second source route, quotient stream, host limit, choice datum, or ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_seal\_source\_scope\_row}
\begin{proof}
Project the carrier of \autoref{def:diagonal-limit-compatibility-carrier}. The accepted packet displays the finite route rows $R,T,S,D,W,Q,L$ and the structural rows $H,C,P,N$ before any seal-facing consumer can be addressed.

Apply seal source synchronization, \autoref{thm:diagonal-limit-compatibility-seal-source-synchronization}. It fixes the source route, triangle row, dyadic ledger, stream window, readback row, seal row, transport, continuation, provenance, and local naming rows as one packet.

Use the triangle readback lock, \autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}. The readback row $Q$ is tied to the same $T,D,W$ route as the seal row $L$, so a $\RealUp$ or $\CauchyLimitSealUp$ consumer has no separate tolerance or regular-sequence source.

Finally apply the Real seal consumer scope theorem, \autoref{thm:diagonal-limit-compatibility-real-seal-consumer-scope}. It routes the consumer through the displayed rows and excludes second source routes, quotient streams, host limits, choice data, and ambient completeness.
\end{proof}

\begin{theorem}[Diagonal-limit seal source determinacy]
\label{thm:diagonal-limit-compatibility-seal-source-determinacy}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
and
$$
K'=(R',T',S',D',W',Q',L',H',C',P',N')
$$
be accepted $\DiagonalLimitCompatibilityUp$ packets. Suppose their displayed
rows agree componentwise by $\hsame$:
$$
\begin{gathered}
\hsame{R}{R'},\quad \hsame{T}{T'},\quad \hsame{S}{S'},\quad
\hsame{D}{D'},\quad \hsame{W}{W'},\quad \hsame{Q}{Q'},\quad
\hsame{L}{L'},\\
\hsame{H}{H'},\quad \hsame{C}{C'},\quad \hsame{P}{P'},\quad
\hsame{N}{N'}.
\end{gathered}
$$
If two $\RealUp$ or $\CauchyLimitSealUp$ consumers both pass through
\autoref{thm:diagonal-limit-compatibility-seal-source-scope-row}, then they
determine the same seal-facing finite route. In particular, they cannot be
distinguished by a host limit, quotient stream, choice datum, ambient
completeness principle, or second source route.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_seal\_source\_determinacy}
\begin{proof}
Apply seal source synchronization,
\autoref{thm:diagonal-limit-compatibility-seal-source-synchronization}, to
both accepted packets. Each seal-facing read is first confined to the displayed
rows $R,T,S,D,W,Q,L,H,C,P,N$ and $R',T',S',D',W',Q',L',H',C',P',N'$.

Use the triangle readback lock,
\autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}. The
readback coordinate is tied to the same triangle, dyadic, and window rows as
the seal coordinate, so the componentwise $\hsame$ hypotheses identify the
finite route through $T,D,W,Q,L$ on both sides.

Next apply real seal factorization,
\autoref{thm:diagonal-limit-compatibility-real-seal-factorization}, and real
seal consumer scope,
\autoref{thm:diagonal-limit-compatibility-real-seal-consumer-scope}. The
consumer route factors through exactly the displayed coordinates and exports no
host limit, quotient stream, choice datum, ambient completeness row, or second
source route.

It remains only to exhaust the coordinates. The hypotheses identify every
displayed source, structural, provenance, and naming row by $\hsame$, while the
factorization and scope theorems leave no hidden coordinate outside those rows.
Thus the two consumers determine the same seal-facing finite route and admit no
remaining distinguishing datum of the kinds named in the statement.
\end{proof}

\begin{theorem}[Diagonal-limit four-face budget ownership]
\label{thm:diagonal-limit-compatibility-four-face-budget-ownership}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
and
$$
K'=(R',T',S',D',W',Q',L',H',C',P',N')
$$
be accepted $\DiagonalLimitCompatibilityUp$ packets whose displayed rows agree
componentwise by $\hsame$. Any $\RealUp$ or $\CauchyLimitSealUp$ consumer that
passes through the synchronized seal source of $K$ and $K'$ decomposes its
finite budget into exactly four owned faces. The $\StreamNameUp$ face owns the
finite window/source row $S$ and window ledger $W$; the $\DyadicRatCoreUp$ face
owns the dyadic tolerance ledger $D$; the $\RegSeqRatUp$ face owns the readback
row $Q$ behind the synchronized $T,D,W$ route; and the $\RealUp$ face owns the
seal row $L$. The support rows $H,C,P,N$ are shared BEDC support rows for
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, not a fifth mathematical face.

Consequently the finite budget carries no quotient stream equality, host
sequence equality, selected limit, ambient $\RealUp$ completeness theorem,
metric-completeness datum, countable-choice datum, or standard bridge row. The
same four faces are the Phase Real and Completion boundary faces named by
\autoref{thm:streamname-real-completion-four-object-exit-route}.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_four\_face\_budget\_ownership}
\begin{proof}
First apply seal source synchronization,
\autoref{thm:diagonal-limit-compatibility-seal-source-synchronization}. It
confines every seal-facing read to the displayed rows
$R,T,S,D,W,Q,L,H,C,P,N$ and their componentwise $\hsame$ partners in $K'$.

Next use the triangle readback lock,
\autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}. The
readback row $Q$ is available only behind the same synchronized $T,D,W$ route,
so it cannot supply an independent tolerance ledger, regular source, or host
sequence equality.

Apply real seal factorization and real seal consumer scope,
\autoref{thm:diagonal-limit-compatibility-real-seal-factorization} and
\autoref{thm:diagonal-limit-compatibility-real-seal-consumer-scope}. These
identify the seal consumer with the displayed finite packet and exclude
quotient stream equality, selected limits, ambient completeness, choice data,
and any second source route. Then apply seal source determinacy,
\autoref{thm:diagonal-limit-compatibility-seal-source-determinacy}, to see
that the componentwise $\hsame$ agreement leaves no additional coordinate on
which two consumers can differ.

It remains to name the ownership boundary. The row $S$ together with $W$ is
the StreamName finite window/source face, $D$ is the DyadicRatCore tolerance
ledger, $Q$ is the RegSeqRat readback face behind $T,D,W$, and $L$ is the Real
seal face. The rows $H,C,P,N$ only transport, continue, package, and certify
these four faces. Finally
\autoref{thm:streamname-real-completion-four-object-exit-route} identifies
exactly the same four faces with the current Phase Real and Completion exit
route, so the diagonal seal packet contributes no fifth mathematical face or
standard bridge row.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibility\_four\_face\_budget\_ownership}

\begin{theorem}[Diagonal-limit four-face budget determinacy]
\label{thm:diagonal-limit-compatibility-four-face-budget-determinacy}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
and
$$
K'=(R',T',S',D',W',Q',L',H',C',P',N')
$$
be accepted $\DiagonalLimitCompatibilityUp$ packets. Suppose the
$\StreamNameUp$ window/source face, the $\DyadicRatCoreUp$ tolerance face, the
$\RegSeqRatUp$ readback face, the $\RealUp$ seal face, and the support rows
$H,C,P,N$ agree by $\hsame$:
$$
\begin{gathered}
\hsame{S}{S'},\quad \hsame{W}{W'},\quad \hsame{D}{D'},\quad
\hsame{Q}{Q'},\quad \hsame{L}{L'},\\
\hsame{H}{H'},\quad \hsame{C}{C'},\quad \hsame{P}{P'},\quad
\hsame{N}{N'}.
\end{gathered}
$$
Then every $\RealUp$ or $\CauchyLimitSealUp$ consumer that passes through the
two accepted packets reads the same finite seal route. The route has exactly the
four faces owned by $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$, with $H,C,P,N$ as support rows, and it has no second source route,
quotient stream, host limit, choice datum, ambient completeness row, metric
completion row, or standard bridge row.
\end{theorem}
\begin{proof}
Start with seal source synchronization,
\autoref{thm:diagonal-limit-compatibility-seal-source-synchronization}. It
places each seal-facing read behind the displayed diagonal source, triangle,
dyadic, window, readback, seal, transport, continuation, provenance, and naming
rows.

Use the triangle readback lock,
\autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}. The readback
row $Q$ cannot move independently of the synchronized triangle, dyadic, and
window rows, so the $\hsame$ agreement on $D,W,Q$ fixes the tolerance and
readback part of the route seen by either consumer.

Next apply real seal factorization,
\autoref{thm:diagonal-limit-compatibility-real-seal-factorization}, and real
seal consumer scope,
\autoref{thm:diagonal-limit-compatibility-real-seal-consumer-scope}. These
results force the $\RealUp$ or $\CauchyLimitSealUp$ consumer to pass through the
displayed seal row $L$ and prevent any hidden host limit, quotient stream,
choice datum, ambient completeness row, or second source route from entering the
consumer route.

Now invoke seal source determinacy,
\autoref{thm:diagonal-limit-compatibility-seal-source-determinacy}. Together
with the stated $\hsame$ agreement on $S,W,D,Q,L,H,C,P,N$, it identifies all
coordinates that the consumer can read after synchronization and factorization.

Finally use four-face budget ownership,
\autoref{thm:diagonal-limit-compatibility-four-face-budget-ownership}. The only
owned mathematical faces are the $\StreamNameUp$ window/source face, the
$\DyadicRatCoreUp$ tolerance face, the $\RegSeqRatUp$ readback face, and the
$\RealUp$ seal face, while $H,C,P,N$ only support transport, continuation,
packaging, and naming. Hence both consumers read the same finite seal route and
no additional completion, bridge, choice, quotient, or host row remains.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityFourFaceBudgetDeterminacy}

\begin{theorem}[Diagonal-limit four-face pullback exactness]
\label{thm:diagonal-limit-compatibility-four-face-pullback-exactness}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
and
$$
K'=(R',T',S',D',W',Q',L',H',C',P',N')
$$
be accepted $\DiagonalLimitCompatibilityUp$ packets whose displayed rows agree
componentwise by $\hsame$. A $\RealUp$ or $\CauchyLimitSealUp$ consumer
classifies through the diagonal seal source of $K$ and $K'$ if and only if its
four projections classify componentwise on the $\StreamNameUp$ window/source
face $(S,W)$, the $\DyadicRatCoreUp$ tolerance face $D$, the $\RegSeqRatUp$
readback face $Q$ behind the synchronized $T,D,W$ route, and the $\RealUp$ seal
face $L$.

The only gluing data are the displayed support rows $H,C,P,N$ and
$H',C',P',N'$, read respectively as $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
support. The exact pullback exports no quotient stream, host equality, selected
limit, ambient completeness theorem, metric-completeness datum, countable-choice
row, or standard bridge row.
\end{theorem}
\begin{proof}
For the forward direction, start with a consumer that classifies through the
diagonal seal source. Apply seal source synchronization,
\autoref{thm:diagonal-limit-compatibility-seal-source-synchronization}, to
confine the read to the displayed rows of $K$ and $K'$.

Use the triangle readback lock,
\autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}, to keep the
readback coordinate $Q$ behind the same synchronized $T,D,W$ route. Then apply
real seal factorization,
\autoref{thm:diagonal-limit-compatibility-real-seal-factorization}, so the
$\RealUp$ or $\CauchyLimitSealUp$ consumer reads the seal row only after the
displayed source, tolerance, window, and readback rows have been fixed.

Now project the synchronized packet to its four faces. Four-face budget
ownership,
\autoref{thm:diagonal-limit-compatibility-four-face-budget-ownership}, names
exactly the $\StreamNameUp$ window/source face, the $\DyadicRatCoreUp$ tolerance
face, the $\RegSeqRatUp$ readback face, and the $\RealUp$ seal face. The
componentwise $\hsame$ hypotheses therefore give componentwise classification
of those four projections, with $H,C,P,N$ and $H',C',P',N'$ as the only support
rows.

For the reverse direction, assume the four projected faces classify
componentwise through the displayed support rows. Apply
\autoref{thm:regseqrat-four-face-terminal-pullback} to repack the
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces as one
finite terminal pullback surface.

Next apply \autoref{thm:realup-open-phase-four-face-pullback}. The compatible
open-phase faces determine a single consumer-visible seal-source handoff, and
the comparison uses only $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally use seal source determinacy,
\autoref{thm:diagonal-limit-compatibility-seal-source-determinacy}. The
componentwise agreement of the accepted packets leaves no hidden coordinate
outside the displayed finite route, so the repacked four-face surface is exactly
the diagonal seal source classification for $K$ and $K'$.

The exclusion clauses come from the same cited pullback and factorization
results together with four-face budget ownership. None of the accepted rows
contains quotient stream equality, host equality, selected limits, ambient
completeness, metric-completeness data, countable-choice rows, or standard
bridge rows, so none can be part of the exact pullback.
\end{proof}

\begin{theorem}[Diagonal-limit tail-seal source uniqueness]
\label{thm:diagonal-limit-compatibility-tail-seal-source-uniqueness}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
be an accepted $\DiagonalLimitCompatibilityUp$ packet. Any terminal
$\RealUp$ seal read using the displayed $\StreamNameUp$ window row $W$ and
source row $S$, the $\RegSeqRatUp$ readback row $Q$, the $\DyadicRatCoreUp$
tolerance ledger $D$, and the $\CauchyLimitSealUp$ route has a unique
displayed tail-seal source up to componentwise $\hsame$ through the support
rows $H,C,P,N$.

Equivalently, two terminal seal reads whose $\StreamNameUp$,
$\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\CauchyLimitSealUp$ faces are
accepted by the same packet determine the same consumer-visible source route
after transport through $H$, replay through $C$, packaging through $P$, and
local naming through $N$. The uniqueness statement exports no quotient stream,
host real equality, hidden selector, selected host limit, detached completion
object, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with two terminal $\RealUp$ seal reads of the accepted packet. Seal
source synchronization,
\autoref{thm:diagonal-limit-compatibility-seal-source-synchronization},
places both reads behind the displayed $R,T,S,D,W,Q,L,H,C,P,N$ rows.

The triangle readback lock,
\autoref{thm:diagonal-limit-compatibility-triangle-readback-lock}, fixes
$Q$ behind the same $T,D,W$ route. Hence neither read can choose a separate
regular readback, tolerance witness, or window source while still being a
read of $K$.

Next use real seal factorization,
\autoref{thm:diagonal-limit-compatibility-real-seal-factorization}. A
$\RealUp$ or $\CauchyLimitSealUp$ consumer reaches the terminal seal only
after the displayed source, window, tolerance, readback, and seal rows have
already been fixed.

Four-face budget determinacy,
\autoref{thm:diagonal-limit-compatibility-four-face-budget-determinacy},
identifies the consumer-visible mathematical faces as the
$\StreamNameUp$ window/source face, the $\DyadicRatCoreUp$ tolerance face,
the $\RegSeqRatUp$ readback face, and the $\RealUp$ seal face. The support
rows $H,C,P,N$ only transport, replay, package, and name those same faces.

Finally apply four-face pullback exactness,
\autoref{thm:diagonal-limit-compatibility-four-face-pullback-exactness}.
The four accepted faces repack as one terminal pullback surface, and seal
source determinacy identifies the resulting source route. Thus any two
terminal seal reads have the same displayed tail-seal source up to
componentwise $\hsame$ through $H,C,P,N$.

The refusal clauses are inherited from the cited synchronization,
factorization, budget, and pullback results. Since no accepted row contains a
quotient stream, host real equality, hidden selector, selected host limit,
detached completion object, or ambient completeness theorem, none can be used
to produce another terminal tail-seal source.
\end{proof}
