\begin{theorem}[Diagonal-limit compatibility seal-budget synchronizer handoff]
\label{thm:diagonal-limit-compatibility-seal-budget-synchronizer-handoff}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
be an accepted $\DiagonalLimitCompatibilityUp$ packet. If its seal route is read through an accepted $\CauchySealBudgetSynchronizerUp$ packet whose displayed request, seal, budget, tail schedule, selector, compatibility, transport, route, provenance, and local naming rows are transported into the same seal route, then the compatibility consumer reads the synchronizer rows before it reads the regular-rational row $Q$ and the $\RealUp$ seal row $L$.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_seal\_budget\_synchronizer\_handoff}
\begin{proof}
Start with the compatibility carrier and its seal-route compatibility theorem. The route to $Q$ and $L$ is already constrained by $R,T,S,D,W,H,C,P,N$, so a seal consumer has no entry point outside the displayed compatibility packet.

Now insert the accepted $\CauchySealBudgetSynchronizerUp$ packet at the seal route $S$. Apply \autoref{thm:cauchy-seal-budget-synchronizer-obligations}: its request, seal, budget, shared-tail schedule, diagonal selector, joint compatibility, transport, continuation, provenance, and naming rows must be exposed before its seal row is usable.

Finally use \autoref{thm:diagonal-limit-compatibility-window-ledger-exactness} and \autoref{thm:diagonal-limit-compatibility-real-seal-exactness}. They bind the compatibility ledger and final seal to the same finite window and dyadic surface, so the synchronizer rows are consumed before $Q,L$ rather than after the seal has escaped the packet.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility tail-schedule readback]
\label{thm:diagonal-limit-compatibility-tail-schedule-readback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet whose seal-budget synchronizer supplies the tail schedule row. Then the compatibility route reads the $\TailCofinalityScheduleUp$ packet before the $\RegSeqRatUp$ row $Q$ and the $\RealUp$ seal row $L$. The readback keeps the tail schedule, finite window row, dyadic ledger, regular-rational row, and real seal row on the same displayed route.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_tail\_schedule\_readback}
\begin{proof}
First apply \autoref{thm:diagonal-limit-compatibility-seal-budget-synchronizer-handoff}. The synchronizer rows are upstream of the compatibility readback through $Q,L$, so its tail schedule row is available before the final seal is consumed.

Next use \autoref{thm:tail-cofinality-schedule-diagonal-handoff}. The schedule route reads the precision request, finite-window schedule, dyadic ledger, regular-rational readback, and real seal in that order.

Transport this route back through the compatibility packet by \autoref{thm:diagonal-limit-compatibility-regular-readback-exactness}. The regular row $Q$ is fixed by the same triangle, dyadic, and window rows already displayed in $K$.

Finally apply \autoref{thm:diagonal-limit-compatibility-source-route-exactness}. It places the schedule-supported readback on the route from $R$ through $T,D,W,S,Q$ to $L$, so the tail schedule is read before the RegSeqRat and RealUp seal rows.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility real-seal budget nonescape]
\label{thm:diagonal-limit-compatibility-real-seal-budget-nonescape}
For an accepted $\DiagonalLimitCompatibilityUp$ packet whose seal route is read through an accepted $\CauchySealBudgetSynchronizerUp$ packet and whose tail schedule is supplied by $\TailCofinalityScheduleUp$, the combined route exports only the displayed compatibility rows, synchronizer rows, tail-schedule rows, regular-rational readback, and $\RealUp$ seal. It exports no quotient stream, host real equality, selected host limit, countable choice row, or ambient completeness theorem.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_real\_seal\_budget\_nonescape}
\begin{proof}
Use \autoref{thm:diagonal-limit-compatibility-completion-consumer-nonescape} for the compatibility packet. It removes quotient streams, selected host limits, host real equality, choice data, and ambient completeness from every completion-facing read of $K$.

Use \autoref{thm:cauchy-seal-budget-synchronizer-nonescape} for the inserted synchronizer route. A seal read must factor through both the displayed seal row and the displayed budget row, and any tail use must pass through the selector, shared threshold, and compatibility row.

Use \autoref{thm:tail-cofinality-schedule-real-seal-readback} for the schedule component. It forces the readback through the finite schedule, dyadic ledger, regular-rational row, and real seal, while excluding quotient streams, host-selected limits, ambient completeness, hidden tail oracles, and unbounded schedules.

Combining these three boundaries leaves only the displayed finite packets and their structural rows. There is no coordinate in the combined route from which a quotient stream, host real equality, selected host limit, countable choice row, or ambient completeness theorem can be exported.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility synchronizer-tail selector Real route]
\label{thm:diagonal-limit-compatibility-synchronizer-tail-selector-real-route}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose its seal route is read through an accepted $\CauchySealBudgetSynchronizerUp$ packet and its tail schedule is supplied by an accepted $\TailCofinalityScheduleUp$ packet on the same displayed route. Then every selector-facing Real consumer reaches the $\RegSeqRatUp$ row $Q$ and the $\RealUp$ seal row $L$ only through the finite route $K$ together with the synchronizer request, seal, budget, selector, compatibility, transport, route, provenance, local naming rows, and the tail-schedule precision, window, dyadic, regular-rational, and Real-seal rows.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_synchronizer\_tail\_selector\_real\_route}
\begin{proof}
First apply \autoref{thm:diagonal-limit-compatibility-seal-budget-synchronizer-handoff}. It places the synchronizer rows before the regular-rational row and the Real seal inside the displayed compatibility packet.

Next apply \autoref{thm:diagonal-limit-compatibility-tail-schedule-readback}. The tail schedule is read through the same finite window, dyadic ledger, regular-rational row, and Real seal route, so it cannot be consumed as an external cofinality object.

Finally use \autoref{thm:diagonal-limit-compatibility-window-ledger-exactness} and \autoref{thm:diagonal-limit-compatibility-real-seal-exactness}. These exactness rows identify $W,D,Q,L$ as the unique displayed route from the selector budget into the Real seal. The combined consumer therefore reaches $Q$ and $L$ only through $K$ plus the synchronizer and schedule rows.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility selector-budget shared-tail nonescape]
\label{thm:diagonal-limit-compatibility-selector-budget-shared-tail-nonescape}
For an accepted $\DiagonalLimitCompatibilityUp$ packet whose selector budget, seal-budget synchronizer, and tail schedule share the route of \autoref{thm:diagonal-limit-compatibility-synchronizer-tail-selector-real-route}, the combined route exports no quotient stream, selected limit, host real equality, countable-choice tail, or ambient completeness coordinate. The only public Real-facing surface is the displayed selector budget, synchronizer handoff, tail schedule, regular-rational row, and $\RealUp$ seal.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}. It fixes the source, triangle, seal, dyadic, finite-window, regular-rational, Real-seal, transport, route, provenance, and local naming rows before any selector-facing consumer can read the seal.

Insert the seal-synchronizer handoff using \autoref{thm:diagonal-limit-compatibility-seal-budget-synchronizer-handoff}. The synchronizer consumes only its displayed request, seal, budget, selector, compatibility, transport, route, provenance, and naming rows on the same finite route.

Now apply \autoref{thm:diagonal-limit-compatibility-real-seal-budget-nonescape}. That theorem excludes quotient streams, host real equality, selected host limits, countable-choice rows, and ambient completeness from the shared seal route. Since the tail schedule is supplied by \autoref{thm:diagonal-limit-compatibility-tail-schedule-readback}, there is no second tail coordinate from which a countable-choice tail or ambient completeness datum could be exported.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility tail-budget observation triple lock]
\label{thm:diagonal-limit-compatibility-tail-budget-observation-triple-lock}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the same displayed route consumes an accepted $\CauchySealBudgetSynchronizerUp$ packet, an accepted $\TailCofinalityScheduleUp$ packet, and an accepted $\RealObservationBudgetUp$ packet. Then every Real-facing or completion-facing read of this route passes through the compatibility rows of $K$, the synchronizer budget rows, the tail schedule rows, the observation-budget rows, the $\RegSeqRatUp$ row $Q$, and the $\RealUp$ seal row $L$.

The finite route exports no quotient stream, selected host limit, host equality, countable-choice tail, hidden observation budget, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_tail\_budget\_observation\_lock}
\begin{proof}
First apply \autoref{thm:diagonal-limit-compatibility-seal-budget-synchronizer-handoff}. It places the synchronizer request, seal, budget, selector, compatibility, transport, route, provenance, and local naming rows before the regular-rational row $Q$ and the Real seal row $L$.

Next apply \autoref{thm:diagonal-limit-compatibility-tail-schedule-readback}. The tail schedule is read back through the same finite window, dyadic ledger, regular-rational row, and Real seal, so it cannot contribute an external cofinal tail.

Now use \autoref{thm:diagonal-limit-compatibility-synchronizer-tail-selector-real-route}. The selector-facing Real route is already exhausted by $K$ together with the synchronizer and tail-schedule rows. Then \autoref{thm:diagonal-limit-compatibility-selector-budget-shared-tail-nonescape} removes quotient streams, selected limits, host equality, countable-choice tails, and ambient completeness from that shared route.

Finally attach the accepted $\RealObservationBudgetUp$ packet through the consumer surface of \autoref{ch:concrete-instances-real-observation-budget-namecert}. Its finite request rows determine only which displayed observations are read. Combined with \autoref{thm:diagonal-limit-compatibility-real-seal-budget-nonescape}, this leaves no coordinate for a hidden observation budget or for any completion-facing object outside the listed compatibility, synchronizer, schedule, observation-budget, RegSeqRat, and RealUp rows.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility triple-budget route exhaustion]
\label{thm:diagonal-limit-compatibility-triple-budget-route-exhaustion}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose its displayed finite route consumes accepted $\CauchySealBudgetSynchronizerUp$, $\TailCofinalityScheduleUp$, and $\RealObservationBudgetUp$ packets on the same route. Then every Real-facing completion read is exhausted by the compatibility rows of $K$, the synchronizer request, seal, and budget rows, the tail-schedule precision, window, and dyadic rows, the observation-budget request rows, the $\RegSeqRatUp$ row $Q$, and the $\RealUp$ seal row $L$.

This route exports no quotient stream, host real equality, hidden observation budget, selected host limit, countable-choice tail, or ambient completeness theorem.
\end{theorem}
\begin{proof}
First apply \autoref{thm:diagonal-limit-compatibility-seal-budget-synchronizer-handoff}. It places the accepted synchronizer request, seal, budget, selector, compatibility, transport, route, provenance, and local naming rows before any read reaches the regular-rational row $Q$ or the Real seal row $L$.

Next apply \autoref{thm:diagonal-limit-compatibility-tail-schedule-readback}. The accepted tail schedule is read back through the same finite precision, window, dyadic, regular-rational, and Real-seal route, so the completion consumer has no separate cofinal-tail coordinate.

Use \autoref{thm:diagonal-limit-compatibility-synchronizer-tail-selector-real-route} to identify the selector-facing Real route with the compatibility, synchronizer, and schedule rows already displayed. Then \autoref{thm:diagonal-limit-compatibility-selector-budget-shared-tail-nonescape} excludes quotient streams, host real equality, selected host limits, countable-choice tails, and ambient completeness from that shared selector-budget route.

Finally apply \autoref{thm:diagonal-limit-compatibility-tail-budget-observation-triple-lock}. The accepted observation-budget packet contributes only its displayed request rows to the same finite route. The carrier inventory therefore contains exactly the compatibility rows, synchronizer request/seal/budget rows, tail-schedule precision/window/dyadic rows, observation-budget request rows, $Q$, and $L$, with no additional coordinate from which a hidden observation budget or any other completion-facing object could be exported.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility synchronizer-observation cofinal pullback]
\label{thm:diagonal-limit-compatibility-synchronizer-observation-cofinal-pullback}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the same displayed finite route consumes accepted $\CauchySealBudgetSynchronizerUp$, $\TailCofinalityScheduleUp$, and $\RealObservationBudgetUp$ packets. Let $\rho$ and $\rho'$ be two Real-facing reads of this route. If $\rho$ and $\rho'$ agree on the synchronizer budget rows, the tail-schedule rows, the observation-budget request rows, the $\RegSeqRatUp$ row $Q$, the $\RealUp$ seal row $L$, and the displayed $hsame$, $Cont$, $Pkg$, and $NameCert$ rows of $K$, then $\rho$ and $\rho'$ determine the same finite cofinal observation route.

The pullback route contains no quotient stream, host real equality, hidden observation budget, selected host limit, countable-choice tail, or ambient completeness row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:diagonal-limit-compatibility-seal-budget-synchronizer-handoff}. The synchronizer request, seal, budget, selector, compatibility, transport, route, provenance, and local naming rows must be read before either $\rho$ or $\rho'$ can reach $Q$ or $L$.

Next apply \autoref{thm:diagonal-limit-compatibility-tail-schedule-readback} and \autoref{thm:diagonal-limit-compatibility-real-seal-budget-nonescape}. The tail schedule is read back through the displayed finite window, dyadic ledger, regular-rational row, and Real seal, while the seal-budget route excludes quotient streams, host real equality, selected host limits, countable-choice rows, and ambient completeness.

Now use \autoref{thm:diagonal-limit-compatibility-synchronizer-tail-selector-real-route} and \autoref{thm:diagonal-limit-compatibility-selector-budget-shared-tail-nonescape}. They identify the selector-facing Real route with the compatibility packet, synchronizer rows, tail schedule, $Q$, and $L$, and they leave no separate selector or shared-tail coordinate on which the two reads could differ.

Finally apply \autoref{thm:diagonal-limit-compatibility-tail-budget-observation-triple-lock} and \autoref{thm:diagonal-limit-compatibility-triple-budget-route-exhaustion}. The accepted observation-budget packet contributes only its displayed request rows, and the exhausted route has precisely the compatibility, synchronizer, schedule, observation-budget, RegSeqRat, and RealUp seal rows listed in the statement. Since $\rho$ and $\rho'$ agree on all of these rows and on the displayed $hsame$, $Cont$, $Pkg$, and $NameCert$ rows, finite row exhaustion leaves no fifth coordinate from which a distinct cofinal observation route could be read.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility synchronizer-observation route uniqueness]
\label{thm:diagonal-limit-compatibility-synchronizer-observation-route-uniqueness}
Let
$$
K=(R,T,S,D,W,Q,L,H,C,P,N)
$$
be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let $\rho$ and $\rho'$
be two Real-facing reads of the displayed synchronizer-observation surface. If
they agree on the displayed compatibility rows of $K$, the accepted
$\CauchySealBudgetSynchronizerUp$ rows, the accepted
$\TailCofinalityScheduleUp$ rows, the accepted $\RealObservationBudgetUp$
request rows, the $\RegSeqRatUp$ row $Q$, the $\RealUp$ seal row $L$, and the
displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, then they determine
the same synchronizer-observation route.

The two reads cannot differ by quotient stream, hidden observation budget,
selected host limit, host equality, countable-choice tail, or ambient
completeness.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:diagonal-limit-compatibility-synchronizer-tail-selector-real-route}.
It places every selector-facing Real read on the displayed compatibility
packet together with the synchronizer rows, the tail-schedule rows, $Q$, and
$L$.

Next use
\autoref{thm:diagonal-limit-compatibility-selector-budget-shared-tail-nonescape}.
This removes quotient streams, selected host limits, host equality,
countable-choice tails, and ambient completeness from the shared route, so
agreement cannot be broken by an external Real-facing coordinate.

Apply
\autoref{thm:diagonal-limit-compatibility-tail-budget-observation-triple-lock}.
The observation-budget packet contributes only its accepted request rows on the
same finite route; hence a hidden observation budget has no separate source.

Finally combine
\autoref{thm:diagonal-limit-compatibility-triple-budget-route-exhaustion} with
\autoref{thm:diagonal-limit-compatibility-synchronizer-observation-cofinal-pullback}.
The triple-budget route is exhausted by the listed compatibility,
synchronizer, schedule, observation-budget, RegSeqRat, RealUp, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows, and the cofinal pullback identifies any
two reads that agree on those rows. Thus $\rho$ and $\rho'$ determine one
synchronizer-observation route.
\end{proof}
