\begin{theorem}[Diagonal-limit compatibility selector-budget source lock]
\label{thm:diagonal-limit-compatibility-selector-budget-source-lock}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Every selector-budget read of $K$ is sourced only by the displayed diagonal source row, the $\StreamNameUp$ window row $W$, the $\DyadicRatCoreUp$ ledger row $D$, the $\RegSeqRatUp$ readback row $Q$, the $\RealUp$ seal row $L$, and the structural rows $H,C,P,N$. The read cannot use an unlisted budget source, hidden selector input, host real equality, selected limit, quotient stream, or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_source\_lock}
\begin{proof}
Start from \autoref{thm:diagonal-limit-compatibility-root-budget-source}. It identifies the budget source of an accepted compatibility packet with the displayed diagonal route, dyadic ledger, stream window, regular-rational handoff, Real seal, transport rows, continuation rows, provenance, and local name.

Apply \autoref{thm:diagonal-limit-compatibility-root-window-route} and \autoref{thm:diagonal-limit-compatibility-root-seal-boundary}. The window $W$ is read before the regular readback $Q$, and the Real-facing row $L$ is reached only through the displayed $D,W,Q$ route.

Finally apply \autoref{thm:diagonal-limit-compatibility-root-consumer-nonescape} and \autoref{thm:diagonal-limit-compatibility-completion-consumer-nonescape}. These boundaries remove the possible routes through hidden budget data, quotient streams, selected limits, host equality, choice data, and ambient completeness. Thus the selector budget is locked to the displayed finite source surface.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget RealLimitUniqueness pullback]
\label{thm:diagonal-limit-selector-budget-real-limit-uniqueness-pullback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet exposing the selector-budget rows $W,D,Q,L$. Let
$$
U=(L_0,L_1,Q_U,S_U,D_U,R_U,V_U,H_U,C_U,P_U,N_U)
$$
be an accepted $\RealLimitUniquenessSealUp$ packet whose two $\CauchyLimitSealUp$ rows and shared comparison-window route are read through the same $W,D,Q,L$ surface of $K$: $S_U$ is supplied by $W$, $D_U$ is supplied by $D$, $Q_U$ is supplied by $Q$, and $R_U$ is supplied by $L$. Suppose also that the terminal $\RealCompletionExactBoundaryUp$ packet reads the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces through that route.

Then every uniqueness consumer factors through the displayed diagonal selector-budget route of $K$ before reading $V_U$. No accepted pullback may insert quotient streams, selected limits, host real equality, countable choice, independent completion data, ambient completeness, or a second completion-facing source.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitSelectorBudgetRealLimitUniquenessPullback}
\begin{proof}
First lock the diagonal source. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. These force every selector-budget read of $K$ through the displayed diagonal source and the rows $W,D,Q,L,H,C,P,N$.

Next attach the uniqueness seal. The two-seal exposure theorem, \autoref{thm:real-limit-uniqueness-seal-two-seal-exposure}, places $L_0$ and $L_1$ before any uniqueness read. The shared comparison window, \autoref{thm:real-limit-uniqueness-seal-shared-comparison-window}, then routes the comparison through $Q_U,S_U,D_U,R_U,V_U$, which is the same surface as $Q,W,D,L$ under the hypothesis.

Now read the terminal completion boundary. By \autoref{thm:real-completion-exact-boundary-four-face-exactness}, the completion-facing faces are exactly the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and terminal $\RealUp$ rows exposed by the accepted boundary. Since those faces are the same $W,Q,D,L$ route, the uniqueness consumer has no independent completion-facing source.

Finally combine diagonal source lock with the RealLimitUniqueness nonescape and consumer handoff results implicit in the two-seal and shared-window route. The accepted route has no coordinate for quotient streams, selected limits, host real equality, countable choice, independent completion data, ambient completeness, or a second completion-facing source, so every uniqueness consumer factors through the displayed diagonal selector-budget route.
\end{proof}

\begin{theorem}[Diagonal-limit compatibility seal-synchronizer budget handoff]
\label{thm:diagonal-limit-compatibility-seal-synchronizer-budget-handoff}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet whose seal route is consumed through an accepted $\CauchySealBudgetSynchronizerUp$ packet. The synchronizer handoff is downstream of the same finite selector-budget prefix of \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}: the diagonal source, $W,D,Q,L$, and the structural rows $H,C,P,N$ are fixed before the synchronizer may export a seal-facing read.
\end{theorem}
\begin{proof}
First use \autoref{thm:diagonal-limit-compatibility-root-budget-source} and \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}. They fix the finite prefix that any selector-budget read must expose before the completion-facing route can inspect the readback and seal rows.

Next use the existing seal-budget synchronizer handoff. The synchronizer rows are inserted at the displayed seal route and must be consumed before the regular-rational row $Q$ and the Real seal row $L$ escape to a consumer.

Apply \autoref{thm:diagonal-limit-compatibility-root-window-route}, \autoref{thm:diagonal-limit-compatibility-root-seal-boundary}, \autoref{thm:diagonal-limit-compatibility-root-consumer-nonescape}, and \autoref{thm:diagonal-limit-compatibility-completion-consumer-nonescape}. These keep the synchronizer attached to the same $D,W,Q,L,H,C,P,N$ surface, so the handoff is downstream of the selector-budget prefix and has no separate source through host limits, quotient streams, host equality, choice data, or ambient completeness.
\end{proof}
\leanvariant{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_seal\_budget\_synchronizer\_handoff}

\begin{theorem}[Diagonal-limit compatibility completion-consumer budget non-escape]
\label{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape}
Every $\CompletionUp$-facing or $\RealUp$-facing consumer of an accepted $\DiagonalLimitCompatibilityUp$ packet that uses the selector-budget route receives only the finite route
$$
R,T,S,D,W,Q,L,H,C,P,N .
$$
The consumer cannot bypass that route by quotient streams, selected limits, host equality, choice data, independent completion data, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:diagonal-limit-compatibility-root-budget-source}, \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}, and \autoref{thm:diagonal-limit-compatibility-seal-synchronizer-budget-handoff}. Together they place the selector read, the seal synchronizer, the stream window, the dyadic ledger, the regular readback, and the Real seal on one finite prefix.

Now apply \autoref{thm:diagonal-limit-compatibility-root-window-route}, \autoref{thm:diagonal-limit-compatibility-root-seal-boundary}, and \autoref{thm:diagonal-limit-compatibility-root-consumer-nonescape}. They exhaust downstream $\RealUp$, $\CompletionUp$, and completion-seal consumers by the displayed budget, window, diagonal, seal, transport, route, provenance, and local-name rows.

Finally apply \autoref{thm:diagonal-limit-compatibility-completion-consumer-nonescape}. Since every completion-facing consumer already factors through the same listed packet coordinates, there is no remaining coordinate from which quotient streams, selected limits, host equality, choice data, independent completion data, or ambient completeness can be exported.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCompletionConsumerBudgetNonescape}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_completion\_consumer\_budget\_nonescape}

\begin{theorem}[Diagonal-limit selector-budget formal target lock]
\label{thm:diagonal-limit-selector-budget-formal-target-lock}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Any formal target for the selector-budget route of $K$ must keep the source locked to the displayed diagonal source, the $\StreamNameUp$ window row $W$, the $\DyadicRatCoreUp$ ledger row $D$, the $\RegSeqRatUp$ readback row $Q$, the $\RealUp$ seal row $L$, and the structural rows $H,C,P,N$. It may not replace that route by quotient streams, selected limits, host equality, choice data, independent completion data, ambient completeness, or a second completion-facing source.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_formal\_target\_lock}
\begin{proof}
First apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}. It fixes every selector-budget read to the displayed diagonal source together with the $W,D,Q,L,H,C,P,N$ rows.

Next apply \autoref{thm:diagonal-limit-compatibility-seal-synchronizer-budget-handoff}. The seal-facing synchronizer is downstream of that same finite selector-budget prefix, so the route cannot acquire a second seal source before readback.

Finally apply \autoref{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape}. Every completion-facing or $\RealUp$-facing consumer is exhausted by $R,T,S,D,W,Q,L,H,C,P,N$, which rules out quotient streams, selected limits, host equality, choice data, independent completion data, and ambient completeness for the formal target boundary.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget route determinacy]
\label{thm:diagonal-limit-selector-budget-route-determinacy}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Any selector-budget route of $K$ consumed by a downstream $\CompletionUp$ or $\RealUp$ reader is the displayed diagonal route: it is determined by the diagonal source, the $\StreamNameUp$ window row $W$, the $\DyadicRatCoreUp$ ledger row $D$, the $\RegSeqRatUp$ readback row $Q$, the $\RealUp$ seal row $L$, and the structural rows $H,C,P,N$. No second selector-budget route through quotient streams, selected limits, host equality, choice data, independent completion data, ambient completeness, or a hidden seal source can serve the same downstream reader.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_route\_determinacy}
\begin{proof}
Start with \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}. It confines every selector-budget read of $K$ to the displayed diagonal source and the finite rows $W,D,Q,L,H,C,P,N$.

Next apply \autoref{thm:diagonal-limit-compatibility-seal-synchronizer-budget-handoff}. The seal-facing handoff sits downstream of the same finite selector-budget prefix, so a downstream reader cannot insert an alternate seal route between the readback row $Q$ and the $\RealUp$ seal row $L$.

Finally apply \autoref{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape}. Every $\CompletionUp$-facing or $\RealUp$-facing consumer using the selector budget is exhausted by the displayed packet coordinates. Hence two such consumer routes with the same displayed diagonal source and the same rows $W,D,Q,L,H,C,P,N$ have no coordinate on which to differ, and the selector-budget route is determined by that finite surface.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget Real-seal nonescape]
\label{thm:diagonal-limit-selector-budget-real-seal-nonescape}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Every selector-budget $\RealUp$-seal consumer of $K$ reaches the seal row $L$ only through the displayed diagonal source together with the $\StreamNameUp$ window row $W$, the $\DyadicRatCoreUp$ ledger row $D$, the $\RegSeqRatUp$ readback row $Q$, and the structural rows $H,C,P,N$. The consumer has no route through quotient streams, selected limits, host equality, choice data, independent completion data, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_real\_seal\_nonescape}
\begin{proof}
Start with \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}. It fixes every selector-budget read of $K$ to the displayed diagonal source and the rows $W,D,Q,L,H,C,P,N$.

Apply \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. Any downstream $\RealUp$-facing consumer using that budget is therefore the same diagonal route, not a second route through hidden selector or completion data.

Finally use the Real-facing side of \autoref{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape}. Since the only route to $L$ is already the displayed finite route, quotient streams, selected limits, host equality, choice data, independent completion data, and ambient completeness have no remaining coordinate from which to enter the seal consumer.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget root public readback exhaustion]
\label{thm:diagonal-limit-selector-budget-root-public-readback-exhaustion}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. The root public readback route for the selector-budget surface is exhausted by the displayed diagonal source and the rows $W,D,Q,L,H,C,P,N$. In particular, every public readback of the selector budget factors through the selector-budget source lock, the selector-budget route determinacy boundary, and the selector-budget $\RealUp$-seal nonescape boundary before it can expose a root-facing Real or Completion consumer.
\end{theorem}
\begin{proof}
First apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}. This identifies the public readback source as the displayed diagonal source and the finite selector rows $W,D,Q,L,H,C,P,N$.

Next apply \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. The public readback cannot branch into a second selector-budget route after the source has been fixed.

Finally apply \autoref{thm:diagonal-limit-selector-budget-real-seal-nonescape}. The Real-seal endpoint of the public route reaches $L$ only through the same diagonal source and the same structural rows. Thus the root public readback is exhausted by the stated finite surface and cannot export quotient streams, selected limits, host equality, choice data, independent completion data, ambient completeness, or hidden seal data.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_root\_public\_readback\_exhaustion}

\begin{theorem}[Diagonal-limit selector-budget Cauchy limit functor pullback]
\label{thm:diagonal-limit-selector-budget-cauchy-limit-functor-pullback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let
$$
F=(S_F,T_F,M_F,W_0,W_1,R_F,D_F,K_F,E_F,H_F,C_F,P_F,N_F)
$$
be an accepted $\CauchyLimitFunctorUp$ packet whose source and target seal rows are read through the same selector-budget surface $D,W,Q,L$ of $K$: the functor windows $W_0,W_1$ are supplied by $W$, the readback $R_F$ is supplied by $Q$, the ledger $D_F$ is supplied by $D$, and the Real-facing endpoint row $E_F$ is supplied by $L$.

Then every $\RealUp$-facing or $\CompletionUp$-facing functor transport of $F$ factors through the displayed diagonal selector-budget route of $K$. Conversely, that selector-budget route supplies exactly the finite source, window, readback, dyadic ledger, classifier, endpoint, transport, replay, provenance, and local naming rows required by the public seal export of $F$:
$$
S,D,W,Q,L,H,C,P,N
\quad\hbox{and}\quad
S_F,W_0,W_1,R_F,D_F,K_F,E_F,H_F,C_F,P_F,N_F .
$$
No ambient limit object, hidden selector, quotient stream equality, host real equality, countable-choice selector, independent completion object, or second public transport route is available at the pullback boundary.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_cauchy\_limit\_functor\_pullback}
\begin{proof}
First lock the diagonal side. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-formal-target-lock}. These force the accepted $\DiagonalLimitCompatibilityUp$ packet to expose only the diagonal source together with $D,W,Q,L,H,C,P,N$, and they prevent a formal target from replacing that route by quotient streams, selected limits, host equality, choice data, independent completion data, ambient completeness, or a second source.

Next identify the downstream route. By \autoref{thm:diagonal-limit-selector-budget-route-determinacy}, any $\RealUp$-facing or $\CompletionUp$-facing consumer using the selector budget is the displayed diagonal route. Since the functor rows $W_0,W_1,R_F,D_F,E_F$ are read through $W,Q,D,L$, any functor transport that reaches a Real or Completion consumer has already entered that same route.

Now read the $\CauchyLimitFunctorUp$ public surface. The NameCert obligations of \autoref{thm:cauchy-limit-functor-namecert-obligations} provide exactly the functor carrier, source-to-target seal exposure, finite observations, completion-consumer rows, and structural rows. The Real-completion consumer boundary of \autoref{thm:cauchy-limit-functor-real-completion-consumer} keeps those rows inside the same finite transport route and removes detached completion data, ambient completeness, host real equality, quotient stream equality, selected limits, countable choice, and second routes.

Finally apply \autoref{thm:cauchy-limit-functor-public-seal-export}. Its reusable public surface is the finite route through source seal, transport map, stream windows, readback, dyadic ledger, classifier, target seal, endpoint, componentwise transport, replay, provenance, and local naming. Under the shared $D,W,Q,L$ read, those requirements are supplied by the displayed selector-budget rows of $K$ together with the functor rows of $F$, so the pullback gives exactly the stated public-seal transport boundary and no additional route.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget finite-tail-filter handoff]
\label{thm:diagonal-limit-selector-budget-finite-tail-filter-handoff}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let
$$
F=(S_F,D_F,R_F,B_F,Q_F,E_F,H_F,C_F,P_F,N_F)
$$
be an accepted $\FiniteTailFilterUp$ packet whose stream-window row, dyadic-ledger row, regular-readback row, tail-budget and common-tail rows, and $\RealUp$ seal row are read through the same displayed selector-budget surface $W,D,Q,L$ of $K$: $S_F$ is supplied by $W$, $D_F$ is supplied by $D$, $R_F$ is supplied by $Q$, the rows $B_F,Q_F$ are consumed through the same finite tail surface, and $E_F$ is supplied by $L$.

Then every $\RealUp$-facing or $\CompletionUp$-facing finite-tail-filter consumer of $F$ factors through the displayed diagonal selector-budget route of $K$. Conversely, the selector-budget route supplies exactly the finite cofinal-tail rows required by $\FiniteTailFilterUp$:
$$
S_F,D_F,R_F,B_F,Q_F,E_F,H_F,C_F,P_F,N_F
$$
read through
$$
S,D,R,W,Q,L,H,C,P,N .
$$
No accepted handoff may insert a hidden tail selector, detached dyadic ledger, quotient stream equality, selected limit, host real equality, countable-choice selector, independent completion object, or ambient completeness witness between the diagonal selector budget and the finite-tail-filter consumer.
\end{theorem}
\begin{proof}
First lock the diagonal route. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-formal-target-lock}. These force the accepted $\DiagonalLimitCompatibilityUp$ packet to expose the diagonal source together with $W,D,Q,L,H,C,P,N$, and they prevent a formal target from replacing that surface by hidden selector data or an independent completion-facing source.

Next identify the consumer route. By \autoref{thm:diagonal-limit-selector-budget-route-determinacy}, any $\RealUp$-facing or $\CompletionUp$-facing consumer using the selector budget is the displayed diagonal route. Apply \autoref{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape} and \autoref{thm:diagonal-limit-compatibility-completion-consumer-nonescape} to remove quotient streams, selected limits, host equality, choice data, independent completion data, and ambient completeness from that route.

Now read the finite-tail-filter surface. Tail-window exactness, \autoref{thm:finite-tail-filter-tail-window-exactness}, identifies the windows and dyadic tolerances used by the tail-budget row, the common-tail comparison row, and the seal-facing row. Since $S_F,D_F,R_F,E_F$ are read through $W,D,Q,L$, the finite-tail rows $B_F,Q_F$ have no separate selector or tolerance ledger from which to build another consumer path.

Finally use \autoref{thm:finite-tail-filter-real-seal-handoff} and \autoref{thm:finite-tail-filter-sibling-tail-handoff}. The Real and Completion seal reads of $F$ pass through the finite cofinal-tail packet $S_F,D_F,R_F,B_F,Q_F,E_F,H_F,C_F,P_F,N_F$, while sibling consumers cannot substitute their own tail selector, ledger, common-tail row, or seal row. Under the shared $W,D,Q,L$ read, those rows are exactly the displayed selector-budget rows of $K$ together with the structural rows $H,C,P,N$, so the handoff factors through the diagonal route and supplies precisely the finite-tail-filter packet.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitSelectorBudgetFiniteTailFilterHandoff}

\begin{theorem}[Diagonal-limit selector-budget regular-tail-meet handoff]
\label{thm:diagonal-limit-selector-budget-regular-tail-meet-handoff}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose its displayed selector-budget surface is consumed by an accepted $\RegularCauchyTailMeetUp$ shared-threshold packet and then by either an accepted $\FiniteTailFilterUp$ packet or a $\RealUp$ seal consumer. The resulting route factors through the displayed diagonal source, the rows $W,D,Q,L$, the shared tail-meet threshold, and the structural rows $H,C,P,N$.

No accepted handoff may insert a hidden tail selector, quotient stream, host equality, selected limit, countable-choice selector, independent completion object, or ambient completeness row between the diagonal selector budget, the shared threshold, and the finite-tail-filter or Real seal consumer.
\end{theorem}
\begin{proof}
First lock the diagonal source. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. They force every selector-budget consumer to read the displayed diagonal route through $W,D,Q,L,H,C,P,N$ and leave no second route through quotient streams, selected limits, host equality, choice data, independent completion data, ambient completeness, or hidden seal data.

Next read the shared-threshold surface of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}. The regular tail-meet packet supplies the common tail threshold as a displayed finite row, so the selector budget reaches downstream seal consumers only after that threshold has been named in the same finite route.

Finally compose with \autoref{thm:diagonal-limit-selector-budget-finite-tail-filter-handoff}. The finite-tail-filter handoff already routes Real-facing and Completion-facing consumers through the displayed selector-budget rows and the finite cofinal-tail packet. With the regular tail-meet threshold placed upstream of that handoff, the composite route has exactly the stated diagonal source, $W,D,Q,L$, shared threshold, and structural rows, and no hidden selector or ambient completion row remains available.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_regular\_tail\_meet\_handoff}

\begin{theorem}[Diagonal-limit selector-budget tail-meet pullback exhaustion]
\label{thm:diagonal-limit-selector-budget-tail-meet-pullback-exhaustion}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the displayed selector-budget surface of $K$ is consumed by an accepted $\RegularCauchyTailMeetUp$ packet with shared tail-meet threshold $\tau$, and that the same threshold-facing route is then consumed by an accepted $\FiniteTailFilterUp$ packet
$$
F=(S_F,D_F,R_F,B_F,Q_F,E_F,H_F,C_F,P_F,N_F).
$$
Every $\CompletionUp$-facing or $\RealUp$-facing consumer of this composite packet has exactly one route: the displayed diagonal source of $K$, the rows $W,D,Q,L$, the shared threshold $\tau$, the finite-tail-filter rows $S_F,D_F,R_F,B_F,Q_F,E_F,H_F,C_F,P_F,N_F$, and the structural rows $H,C,P,N$.

No accepted pullback along this route may add a hidden selector, quotient stream, host equality row, selected limit, countable-choice selector, independent completion datum, second completion source, or ambient completeness witness.
\end{theorem}
\begin{proof}
First lock the diagonal selector source. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. These identify the only downstream selector-budget route as the displayed diagonal source together with $W,D,Q,L,H,C,P,N$.

Next place the shared threshold on that route. The shared-threshold surface of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}, together with \autoref{thm:regular-cauchy-tail-meet-selector-budget-public-route} and \autoref{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy}, makes the threshold $\tau$ a displayed finite row reached through the same selector windows and readback rows. A second threshold route would require a hidden selector or an independent tail oracle, neither of which is carried by the accepted packet.

Now attach the finite-tail-filter consumer. By \autoref{thm:diagonal-limit-selector-budget-finite-tail-filter-handoff}, Real-facing and Completion-facing consumers of $F$ read the finite packet rows $S_F,D_F,R_F,B_F,Q_F,E_F,H_F,C_F,P_F,N_F$ only through the displayed selector-budget surface $W,D,Q,L$ of $K$.

Finally compose with \autoref{thm:diagonal-limit-selector-budget-regular-tail-meet-handoff}. The regular tail-meet handoff already places $\tau$ between the diagonal selector budget and the finite-tail-filter or Real seal consumer. Combining the two handoffs gives one composite route with the diagonal source, $W,D,Q,L$, the shared threshold, the finite-tail-filter packet rows, and $H,C,P,N$ as its complete coordinate list. Since the source lock and determinacy theorems have no remaining carrier coordinate for quotient streams, host equality, selected limits, countable-choice selectors, independent completion data, second completion sources, or ambient completeness, the pullback route is exhausted.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_tail\_meet\_pullback\_exhaustion}

\begin{theorem}[Diagonal-limit selector-budget TailCofinalitySchedule pullback]
\label{thm:diagonal-limit-selector-budget-pullback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet, and let $A=(E_A,W_A,D_A,R_A,L_A,H_A,C_A,P_A,N_A)$ be an accepted $\TailCofinalityScheduleUp$ packet. Suppose the schedule packet consumes the same $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ readback, and $\RealUp$ seal rows through the selector-budget surface of $K$: $W_A$ is supplied by $W$, $D_A$ by $D$, $R_A$ by $Q$, and $L_A$ by $L$.

Then every completion-facing or Real-facing consumer of the combined packet factors through the shared finite route
$$
W,D,Q,L,H,C,P,N
\quad\hbox{read as}\quad
W_A,D_A,R_A,L_A,H_A,C_A,P_A,N_A.
$$
No hidden selector, quotient stream, host equality, selected limit, independent completion datum, ambient completeness witness, or second schedule budget can intervene.
\end{theorem}
\begin{proof}
First lock the diagonal selector source. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. They identify the only selector-budget route as the displayed diagonal source together with $W,D,Q,L,H,C,P,N$.

Next use \autoref{thm:diagonal-limit-selector-budget-tail-meet-pullback-exhaustion}. It removes any alternate tail-facing route between the selector budget, shared threshold, finite-tail packet, and downstream Real or Completion consumer.

Now attach the schedule packet. By \autoref{thm:tail-cofinality-schedule-diagonal-handoff} and \autoref{thm:tail-cofinality-schedule-regular-cauchy-completion-route}, the accepted $\TailCofinalityScheduleUp$ consumer reads the window, ledger, regular-rational readback, and Real seal through the finite schedule route before the completion seal can be inspected.

The hypotheses identify those schedule rows with $W,D,Q,L$ from $K$. Hence every combined consumer has the single shared route listed in the statement, and the non-escape clauses from the diagonal selector and schedule boundaries leave no coordinate for a hidden selector, quotient stream, host equality, selected limit, independent completion datum, ambient completeness witness, or second schedule budget.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_tail\_cofinality\_schedule\_pullback}

\begin{theorem}[Diagonal-limit selector-budget UniformCauchyCriterion terminal pullback]
\label{thm:diagonal-limit-selector-budget-uniform-criterion-pullback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let
$$
U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)
$$
be an accepted finite-family $\UniformCauchyCriterionUp$ packet whose shared window, dyadic ledger, regular readback, and terminal $\RealUp$ seal rows are read through the same selector-budget surface $W,D,Q,L$ of $K$: the window family $W_U$ is supplied by $W$, the dyadic tolerance row $Q_U$ is supplied by $D$, the regular tail readback $T_U$ is supplied by $Q$, and the terminal seal row $E_U$ is supplied by $L$.

Then every terminal $\RealUp$-facing or $\CompletionUp$-facing consumer of $U$ factors through the displayed diagonal selector-budget route of $K$. Conversely, that route supplies the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealWindowBudgetUp$, and $\RealCompletionExactBoundaryUp$ faces needed by the $\UniformCauchyCriterionUp$ terminal envelope:
$$
W,D,Q,L,H,C,P,N
\quad\hbox{read as}\quad
W_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U .
$$
No accepted terminal route may insert quotient streams, host equality, selected limits, choice data, independent completion data, host metric data, ambient completeness, or a second terminal Real or Completion source.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_uniform\_criterion\_pullback}
\begin{proof}
First lock the diagonal side. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. These identify the only selector-budget route of $K$ as the displayed diagonal source together with $W,D,Q,L,H,C,P,N$.

Next exclude detached terminal data. By \autoref{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape}, any $\RealUp$-facing or $\CompletionUp$-facing consumer using that route is exhausted by the same finite packet rows and has no coordinate for quotient streams, selected limits, host equality, choice data, independent completion data, or ambient completeness.

Now attach the finite-family terminal envelope. The seal envelope of \autoref{thm:uniform-cauchy-criterion-terminal-seal-envelope}, the completion--Real correspondence of \autoref{thm:uniform-cauchy-criterion-completion-real-correspondence}, and finite-window coverage in \autoref{thm:uniform-cauchy-criterion-finite-window-coverage} require the $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledger, Real-window budget, and exact Real-completion boundary before a terminal consumer can read the seal.

Under the shared $W,D,Q,L$ surface, those UniformCauchyCriterion rows are precisely the selector-budget rows of $K$ together with the structural rows $H,C,P,N$. Hence every admitted terminal consumer factors through the displayed diagonal route, and reading the same route backward supplies exactly the terminal envelope faces without adding host metric data, an independent completion object, or an ambient completeness principle.
\end{proof}

\begin{theorem}[Diagonal-limit uniform-criterion terminal uniqueness pullback]
\label{thm:diagonal-limit-uniform-criterion-terminal-uniqueness-pullback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let
$$
U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)
$$
be an accepted finite-family $\UniformCauchyCriterionUp$ packet, and let
$$
V=(L_0,L_1,Q_V,S_V,D_V,R_V,V_V,H_V,C_V,P_V,N_V)
$$
be an accepted $\RealLimitUniquenessSealUp$ packet. Suppose the shared selector-budget surface $W,D,Q,L$ of $K$ supplies the UniformCauchyCriterion rows $W_U,Q_U,T_U,E_U$ and also supplies the RealLimitUniquenessSeal rows $S_V,D_V,Q_V,R_V$. Suppose further that the terminal $\RealUp$ or $\CompletionUp$ consumer of $U$ is the consumer handed to the uniqueness seal through the same displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces.

Then that terminal Real or Completion consumer has exactly one finite pullback route: the displayed diagonal selector-budget rows $W,D,Q,L,H,C,P,N$ of $K$, read as the UniformCauchyCriterion terminal rows and as the RealLimitUniquenessSeal comparison rows. No accepted terminal pullback through this route may add quotient streams, selected limits, host real equality, countable choice, independent completion data, ambient completeness, or a second completion-facing source.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitUniformCriterionTerminalUniquenessPullback}
\begin{proof}
First apply \autoref{thm:diagonal-limit-selector-budget-uniform-criterion-pullback}. It places every terminal $\RealUp$-facing or $\CompletionUp$-facing consumer of $U$ on the displayed diagonal selector-budget route of $K$ and reads $W,D,Q,L,H,C,P,N$ as the UniformCauchyCriterion terminal surface.

Next apply \autoref{thm:diagonal-limit-selector-budget-real-limit-uniqueness-pullback}. It places the RealLimitUniquenessSeal comparison route on the same displayed selector-budget rows and rules out quotient streams, selected limits, host real equality, countable choice, independent completion data, ambient completeness, and a second completion-facing source.

Finally compare the two consumers. By \autoref{thm:diagonal-limit-selector-budget-route-determinacy}, any consumer that uses the selector budget of $K$ is the displayed finite route rather than a parallel route through hidden selector or completion data. By \autoref{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape}, a terminal Real or Completion consumer using that route has no remaining coordinate from which an independent completion object, host equality, selected limit, quotient stream, countable-choice selector, ambient completeness witness, or second completion-facing source could be exported. Thus the UniformCauchyCriterion terminal consumer and the uniqueness-seal consumer collapse to the same finite pullback route.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget Real and Completion exit route]
\label{thm:diagonal-limit-selector-budget-uniform-real-exit}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let
$$
U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)
$$
be an accepted finite-family $\UniformCauchyCriterionUp$ packet whose window, dyadic tolerance, regular readback, and local $\RealUp$ seal rows consume the same $W,D,Q,L$ rows of $K$. Then every Phase Real and Completion exit read admitted by $U$ factors through the finite surface
$$
R,T,S,D,W,Q,L,H,C,P,N
\quad\hbox{and}\quad
I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U,
$$
where the displayed diagonal source supplies the selector-budget route, the $\DyadicRatCoreUp$ ledger supplies the tolerance row, the $\StreamNameUp$ family supplies the window row, the $\RegSeqRatUp$ readback supplies the regular tail row, the local $\RealUp$ seal supplies the terminal seal row, and the $\UniformCauchyCriterionUp$ envelope supplies the finite-family terminal boundary.

The same exit read preserves the structural $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It has no accepted coordinate for quotient streams, host real equality, selected limits, countable-choice selectors, independent completion data, host metric data, ambient completeness, or a second Real or Completion source.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_uniform\_real\_exit}
\begin{proof}
First lock the diagonal source. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. These force every Real-facing or Completion-facing read that touches the selector budget to use the displayed diagonal source of $K$ and the rows $W,D,Q,L,H,C,P,N$.

Next remove escape data from the completion side. Apply \autoref{thm:diagonal-limit-compatibility-completion-consumer-budget-nonescape} and \autoref{thm:diagonal-limit-selector-budget-uniform-criterion-pullback}. The first result leaves no coordinate for quotient streams, selected limits, host equality, countable-choice data, independent completion data, or ambient completeness. The second result identifies the UniformCauchyCriterion terminal pullback with the same $W,D,Q,L$ surface.

Now read the terminal envelope facts for $\UniformCauchyCriterionUp$. The seal envelope of \autoref{thm:uniform-cauchy-criterion-terminal-seal-envelope}, the completion--Real correspondence of \autoref{thm:uniform-cauchy-criterion-completion-real-correspondence}, and finite-window coverage in \autoref{thm:uniform-cauchy-criterion-finite-window-coverage} require the $\StreamNameUp$ window family, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ tail readback, local $\RealUp$ seal, and finite-family terminal boundary before an exit read can reach the public Real or Completion surface.

Finally compose the two boundaries. Under the shared consumption hypothesis, $W_U,Q_U,T_U,E_U$ are the reads of $W,D,Q,L$, while $H_U,C_U,P_U,N_U$ preserve the same $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows as $H,C,P,N$. Thus every Phase Real and Completion exit read factors through the displayed diagonal source and the finite UniformCauchyCriterion envelope, with no remaining public coordinate for host metric data, ambient completeness, independent completion data, or a second Real or Completion source.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget finite-observation coverage]
\label{thm:diagonal-limit-selector-budget-finite-observation-coverage}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet, and let the terminal Real-and-Completion exit route of $K$ be read through a displayed $\FiniteObservationBudgetSelectorUp$ selector budget
$$
F=(B_F,S_F,W_F,D_F,R_F,E_F,H_F,C_F,P_F,N_F).
$$
If the accepted exit route consumes the selector budget of $F$, then its finite observation surface is exactly the exported selector surface: the budget row $B_F$, selected schedule $S_F$, finite $\StreamNameUp$ windows $W_F$, $\DyadicRatCoreUp$ ledger $D_F$, $\RegSeqRatUp$ handoff $R_F$, terminal $\RealUp$ seal $E_F$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows $H_F,C_F,P_F,N_F$.

The same surface is the one consumed by the $\UniformCauchyCriterionUp$ pullback and the $\CauchyLimitSealUp$ route. No accepted reader along this terminal route may insert a quotient stream, host real equality, selected host limit, countable-choice selector, ambient completeness witness, metric-completeness row, arithmetic package, order package, or bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitCompatibilityCarrier\_selector\_budget\_finite\_observation\_coverage}
\begin{proof}
First lock the diagonal source. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock}. Any terminal Real-and-Completion read that reaches the selector budget of $K$ must pass through the displayed diagonal source and the rows $W,D,Q,L,H,C,P,N$.

Next identify the selector budget surface. The public export theorem \autoref{thm:finite-observation-budget-selector-public-export} exposes exactly the finite route $B_F,S_F,W_F,D_F,R_F,E_F$ together with $H_F,C_F,P_F,N_F$. The diagonal consumer boundary \autoref{thm:finite-observation-budget-selector-diagonal-consumer-boundary} makes that exported surface the one seen by diagonal-limit and Real-completion consumers, and terminal route endpoint exactness \autoref{thm:finite-observation-budget-selector-terminal-route-endpoint-exactness} fixes the terminal endpoint at the displayed seal $E_F$ through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Now compare the downstream readers. The UniformCauchyCriterion pullback \autoref{thm:diagonal-limit-selector-budget-uniform-criterion-pullback} reads the shared window, dyadic ledger, regular handoff, and Real seal rows through the same selector-budget surface. The CauchyLimitSeal route is a seal-facing reader of the same public selector packet, so the diagonal consumer boundary places it on the exported finite route rather than on an additional completion or bridge coordinate.

Finally apply the Real-and-Completion exit theorem \autoref{thm:diagonal-limit-selector-budget-uniform-real-exit}. Its exclusion list removes quotient streams, host real equality, selected limits, countable-choice selectors, host metric data, ambient completeness, independent completion data, and second Real or Completion sources. Since the public selector export also carries no metric-completeness row, arithmetic package, order package, or bridge row, the terminal route has exactly the finite observation surface listed in the statement.
\end{proof}

\begin{theorem}[Diagonal-limit selector-budget finite-prefix-budget pullback]
\label{thm:diagonal-limit-selector-budget-finite-prefix-budget-pullback}
Let $K=(R,T,S,D,W,Q,L,H,C,P,N)$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Let
$$
B=(Q_B,B_B,W_B,D_B,R_B,S_B,E_B,H_B,C_B,P_B,N_B)
$$
be an accepted $\FinitePrefixLimitBudgetUp$ packet whose window, dyadic ledger, regular readback, and terminal seal rows are read through the same selector-budget surface $W,D,Q,L$ of $K$. Then every Real-and-Completion terminal consumer that passes through $B$ factors through exactly the finite route
$$
W,D,Q,L,H,C,P,N
$$
read as
$$
W_B,D_B,R_B,S_B,E_B,H_B,C_B,P_B,N_B.
$$
No accepted route may insert a quotient stream, host real equality, selected limit, countable-choice selector, ambient $\RealUp$ completeness, metric-completeness row, arithmetic package, order package, or bridge row between the selector-budget surface and the terminal Real or Completion read.
\end{theorem}
\begin{proof}
First lock the diagonal source. Apply \autoref{thm:diagonal-limit-compatibility-selector-budget-source-lock} and \autoref{thm:diagonal-limit-selector-budget-route-determinacy}. These force every terminal read that touches the selector budget of $K$ to use the displayed rows $W,D,Q,L,H,C,P,N$ rather than a parallel route through hidden selector data.

Next read the finite-prefix budget side. The seal ordering theorem \autoref{thm:finite-prefix-limit-budget-seal-ordering} places every seal-facing read behind the ordered route $Q_B \to B_B \to W_B \to D_B \to R_B \to S_B$. The consumer boundary \autoref{thm:finite-prefix-limit-budget-consumer-boundary} and seal-consumer coverage \autoref{thm:finite-prefix-limit-budget-seal-consumer-coverage} say that a Real-facing or completion-facing consumer receives only the finite-prefix rows $Q_B,B_B,W_B,D_B,R_B,S_B,E_B,H_B,C_B,P_B,N_B$.

Under the shared-surface hypothesis, the rows $W_B,D_B,R_B,S_B$ are precisely the finite-prefix read of $W,D,Q,L$, while $E_B,H_B,C_B,P_B,N_B$ preserve the same exclusion, transport, continuation, provenance, and local naming boundary as the displayed support rows of $K$. Compose this identification with \autoref{thm:diagonal-limit-selector-budget-uniform-real-exit} and \autoref{thm:diagonal-limit-selector-budget-finite-observation-coverage} to obtain the terminal Real-and-Completion surface through the finite selector-budget route.

Finally apply the finite-prefix non-escape theorem \autoref{thm:finite-prefix-limit-budget-real-seal-nonescape-extension}. Its exclusion list matches the diagonal exit exclusions: quotient streams, host real equality, selected limits, countable-choice selectors, hidden terminal data, and ambient completeness are absent. Since neither the selector-budget route nor the finite-prefix budget carrier contains a metric-completeness row, arithmetic package, order package, or bridge row, the pullback is exactly the displayed finite route.
\end{proof}
\leanchecked{BEDC.Derived.DiagonallimitcompatibilityUp.DiagonalLimitSelectorBudgetFinitePrefixBudgetPullback}
