\begin{theorem}[UniformCauchyCriterion diagonal uniqueness exit]
\label{thm:uniform-cauchy-criterion-diagonal-uniqueness-exit}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Suppose its terminal rows are consumed through an accepted $\DiagonalLimitCompatibilityUp$ selector-budget route and through an accepted $\RealLimitUniquenessSealUp$ comparison route, with both routes reading the same displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces.

Then every Phase Real and Completion exit read of $U$ factors through that same finite route. The terminal read uses the stream windows carried by $W$, the regular rational readback carried by $T$, the dyadic tolerance ledger carried by $Q$, and the Real seal carried by $E$, together with the structural rows $H,C,P,N$. No exit read has access to quotient streams, host real equality, selected limits, choice data, ambient completeness, or a second completion source.
\end{theorem}
\begin{proof}
Start with the public export of $U$. By \autoref{thm:uniform-cauchy-criterion-public-non-escape-export}, every downstream consumer is already exhausted by the finite rows $I,W,M,Q,T,E,H,C,P,N$, so the exit read has no hidden analytic coordinate before the terminal rows are interpreted.

Next apply the terminal seal envelope, the completion--Real correspondence, and the finite-window extraction route. The envelope keeps the terminal seal downstream of the displayed rows, the correspondence identifies the Real-facing and Completion-facing endpoint reads on the same seal route, and \autoref{thm:uniform-cauchy-criterion-finite-window-real-seal-extraction} extracts the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces from $W,T,Q,E$.

Now attach the diagonal selector-budget route. The diagonal compatibility surface supplies the same finite faces to the UniformCauchyCriterion terminal rows, while the uniqueness-seal comparison consumes those faces through the same selector budget. By \autoref{thm:diagonal-limit-uniform-criterion-terminal-uniqueness-pullback}, the terminal consumer and the uniqueness-seal consumer collapse to one finite pullback route rather than two endpoint sources.

Finally combine this pullback with the non-escape clauses on both sides. Since the shared route has no coordinate for quotient streams, host equality, selected limits, choice data, ambient completeness, or an independent completion object, every Phase Real and Completion exit read of $U$ factors through the same finite $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_uniqueness\_exit}

\begin{theorem}[UniformCauchyCriterion diagonal exit classifier]
\label{thm:uniform-cauchy-criterion-diagonal-exit-classifier}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Suppose two terminal exit reads of $U$, one Phase Real-facing and one Completion-facing, consume the same displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces, the same accepted $\DiagonalLimitCompatibilityUp$ selector-budget route, and the same accepted $\RealLimitUniquenessSealUp$ comparison rows.

Then the two terminal Real-facing classifier rows are $hsame$-equivalent. In particular, no second completion source, quotient-stream equality, host real equality, selected limit, choice datum, ambient completeness coordinate, or independent endpoint witness can distinguish the two terminal classifier reads.
\end{theorem}
\begin{proof}
Apply \autoref{thm:uniform-cauchy-criterion-diagonal-uniqueness-exit} to the two exit reads. Both reads factor through the common finite route carried by $I,W,M,Q,T,E,H,C,P,N$, so neither route has an extra source from which a different terminal classifier could be read.

The public rows are exhausted by \autoref{thm:uniform-cauchy-criterion-public-non-escape-export}. The Real-seal part of the route is exhausted by \autoref{thm:uniform-cauchy-criterion-finite-window-real-seal-extraction}, which reads the displayed stream name, regular rational sequence, dyadic tolerance core, and Real seal from $W,T,Q,E$.

Now compare the selector and uniqueness consumers. The shared $\DiagonalLimitCompatibilityUp$ route and the shared $\RealLimitUniquenessSealUp$ comparison rows are collapsed by \autoref{thm:diagonal-limit-uniform-criterion-terminal-uniqueness-pullback}, so the Phase Real-facing and Completion-facing classifier consumers lie over the same finite pullback route.

The classifier conclusion is therefore forced at the level of $BHist$ rows. Since $hsame$ identifies terminal rows read from the same finite pullback route, the two terminal Real-facing classifier rows are $hsame$-equivalent, and the excluded coordinates have no remaining slot through which to separate them.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_exit\_classifier}

\begin{theorem}[UniformCauchyCriterion diagonal exit nonescape]
\label{thm:uniform-cauchy-criterion-diagonal-exit-nonescape}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal exit reads share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, and $\RealLimitUniquenessSealUp$ rows.

Then every classifier distinction visible at the diagonal exit is witnessed inside the finite rows $BHist$, $hsame$, $\Cont$, $\Pkg$, and $\NameCert$ carried by $H,C,P,N$ and the terminal route $I,W,M,Q,T,E$. Quotient streams, host real equality, selected limits, choice data, ambient completeness, metric-completeness data, and independent completion sources are outside the accepted diagonal exit classifier.
\end{theorem}
\begin{proof}
Apply \autoref{thm:uniform-cauchy-criterion-diagonal-uniqueness-exit}. The Phase Real-facing and Completion-facing terminal reads already factor through the same finite pullback route, whose displayed coordinates are the stream name, regular rational readback, dyadic tolerance ledger, Real seal, and structural rows $H,C,P,N$.

Next apply \autoref{thm:uniform-cauchy-criterion-diagonal-exit-classifier}. It identifies any two terminal classifier reads over that shared route at the level of $hsame$, so a visible distinction must be carried by the finite $BHist$ and classifier rows rather than by an external analytic separator.

The diagonal-limit pullback, \autoref{thm:diagonal-limit-uniform-criterion-terminal-uniqueness-pullback}, supplies no separate selector route, and the real-limit uniqueness side is bounded by the same non-escape surface used above for the $\RealUp$ seal. Hence quotient streams, host real equality, selected limits, choice data, ambient completeness, metric-completeness data, and independent completion sources have no route slot in the accepted diagonal exit classifier.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_exit\_nonescape}

\begin{theorem}[UniformCauchyCriterion diagonal budget extraction]
\label{thm:uniform-cauchy-criterion-diagonal-budget-extraction}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal exit is read through the same displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, and $\RealLimitUniquenessSealUp$ rows. Then the accepted terminal exit extracts exactly the finite budget route
$$
W,Q,T,E,H,C,P,N
$$
for its Phase Real and Completion-facing consumers. No quotient stream, selected limit, host equality, choice row, ambient completeness witness, or independent completion datum can replace that route.
\end{theorem}
\begin{proof}
First use \autoref{thm:uniform-cauchy-criterion-diagonal-uniqueness-exit}. It places every terminal exit read of $U$ on the shared finite route carried by the stream window, dyadic tolerance ledger, regular rational readback, Real seal, and structural rows.

Next apply \autoref{thm:uniform-cauchy-criterion-diagonal-exit-classifier} and \autoref{thm:uniform-cauchy-criterion-diagonal-exit-nonescape}. The classifier is forced inside the same $BHist$, $hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows, and the non-escape boundary removes the listed host or completion-side coordinates.

Now pull the selector budget back through \autoref{thm:diagonal-limit-selector-budget-uniform-criterion-pullback}. Under the shared $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ reads, the UniformCauchyCriterion terminal consumer receives precisely the displayed rows $W,Q,T,E,H,C,P,N$.

Finally use \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The Phase Real and Completion exit sees only the four completion-facing faces and their structural budget rows, so the extracted route is finite and no external stream quotient, host-selected endpoint, choice principle, ambient completeness row, or detached completion datum remains available.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_budget\_extraction}

\begin{theorem}[UniformCauchyCriterion exit route consumer coverage]
\label{thm:uniform-cauchy-criterion-exit-route-consumer-coverage}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal exit is read through the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, and $\RealLimitUniquenessSealUp$ rows. Every Phase Real and Completion consumer of that accepted terminal exit factors through $W,Q,T,E,H,C,P,N$ together with those shared sibling rows. No quotient stream, host real equality, selected limit, choice row, ambient completeness witness, or independent completion datum can replace that finite route.
\end{theorem}
\begin{proof}
First apply \autoref{thm:uniform-cauchy-criterion-diagonal-uniqueness-exit}. It places every Phase Real and Completion exit read over the same displayed terminal route rather than over separate endpoint sources.

Next use \autoref{thm:uniform-cauchy-criterion-diagonal-exit-classifier} and \autoref{thm:uniform-cauchy-criterion-diagonal-exit-nonescape}. The classifier is read inside the finite $BHist$, $hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ structure, and the nonescape theorem removes quotient streams, host equality, selected limits, choice data, ambient completeness, and independent completion sources from the accepted exit.

Now apply \autoref{thm:uniform-cauchy-criterion-diagonal-budget-extraction}. It identifies $W,Q,T,E,H,C,P,N$ as the exact budget route delivered to the terminal consumer.

Finally pull this route along \autoref{thm:diagonal-limit-selector-budget-uniform-criterion-pullback} and \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The selector-budget pullback supplies the shared $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces, while four-face exactness keeps the Phase Real and Completion consumers on the same boundary. Hence every terminal consumer is covered by the listed finite route and no excluded coordinate can serve as a replacement.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_exit\_route\_consumer\_coverage}

\begin{theorem}[UniformCauchyCriterion diagonal structural-face coverage]
\label{thm:uniform-cauchy-criterion-diagonal-structural-face-coverage}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal exit is read through shared $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, and $\RealLimitUniquenessSealUp$ rows. Then the four structural faces $W,Q,T,E$ together with $H,C,P,N$ are exhaustive for every diagonal-exit classifier and every Phase Real or Completion consumer route.

In particular, no accepted diagonal-exit read can replace that route by quotient streams, host equality, selected limits, choice rows, ambient completeness, metric-completeness witnesses, or independent completion sources.
\end{theorem}
\begin{proof}
First apply \autoref{thm:uniform-cauchy-criterion-diagonal-uniqueness-exit}. It places the terminal exit over the shared finite route rather than over a second endpoint source.

Next apply \autoref{thm:uniform-cauchy-criterion-diagonal-exit-classifier} and \autoref{thm:uniform-cauchy-criterion-diagonal-exit-nonescape}. The classifier is read through the same finite $BHist$, $hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows, and the nonescape boundary removes quotient streams, host equality, selected limits, choice data, ambient completeness, metric-completeness data, and independent completion sources.

Now use \autoref{thm:uniform-cauchy-criterion-diagonal-budget-extraction} and \autoref{thm:uniform-cauchy-criterion-exit-route-consumer-coverage}. These identify $W,Q,T,E,H,C,P,N$ as the exact route delivered to every Phase Real and Completion consumer.

Finally pull the route through \autoref{thm:diagonal-limit-selector-budget-uniform-criterion-pullback} and \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The selector-budget pullback supplies the shared stream, regular sequence, dyadic core, and Real faces, while four-face exactness keeps the Real-completion boundary on $W,Q,T,E$. Hence the listed structural faces and support rows cover every diagonal-exit classifier and consumer route.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_structural\_face\_coverage}

\begin{theorem}[UniformCauchyCriterion diagonal tail-budget exhaustion]
\label{thm:uniform-cauchycriterion-diagonal-tail-budget-exhaustion}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal exit shares the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, $\RealLimitUniquenessSealUp$, and $\TailCofinalityScheduleUp$ rows. Then every tail-budget read at that terminal exit factors through the already extracted route
$$
W,Q,T,E,H,C,P,N.
$$
No quotient stream, host equality, selected limit, choice row, ambient completeness, detached tail oracle, second completion source, or replacement tail schedule can serve in place of that route.
\end{theorem}
\begin{proof}
Start with diagonal budget extraction, \autoref{thm:uniform-cauchy-criterion-diagonal-budget-extraction}. It identifies $W,Q,T,E,H,C,P,N$ as the finite route delivered to Phase Real and Completion-facing consumers of the accepted terminal exit.

Next apply exit route consumer coverage and structural-face coverage, \autoref{thm:uniform-cauchy-criterion-exit-route-consumer-coverage} and \autoref{thm:uniform-cauchy-criterion-diagonal-structural-face-coverage}. These keep every terminal consumer on the same stream-window, dyadic-tolerance, regular-readback, Real-seal, transport, route, provenance, and local naming rows.

Now attach the tail-cofinality sibling route. By \autoref{thm:uniform-cauchy-criterion-tail-cofinality-schedule-handoff} and the TailCofinalitySchedule route theorem cited there, the cofinal tail schedule is consumed only as a sibling route on the same finite window, regular readback, and Real seal before the terminal exit is read.

The nonescape clause is inherited from the cited routes. None of the diagonal, consumer-coverage, structural-face, or tail-cofinality rows supplies quotient streams, host equality, selected limits, choice rows, ambient completeness, detached tail oracles, or independent completion sources, so every tail-budget read is exhausted by $W,Q,T,E,H,C,P,N$.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_tail\_budget\_exhaustion}

\begin{theorem}[UniformCauchyCriterion diagonal terminal route exhaustion]
\label{thm:uniform-cauchy-criterion-diagonal-terminal-route-exhaustion}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal Phase Real and Completion read is shared with the displayed $\DiagonalLimitCompatibilityUp$, $\RealLimitUniquenessSealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows. Then every terminal read of $U$ is exhausted by the finite route
$$
W,Q,T,E,H,C,P,N.
$$
No accepted terminal consumer can replace that route by quotient streams, host equality, selected limits, choice data, ambient completeness, metric-completeness data, or a detached completion source.
\end{theorem}
\begin{proof}
First use \autoref{thm:uniform-cauchy-criterion-diagonal-structural-face-coverage}. It says that the four structural faces $W,Q,T,E$ together with $H,C,P,N$ cover every diagonal-exit classifier and every Phase Real or Completion consumer route.

Next use \autoref{thm:uniform-cauchy-criterion-diagonal-budget-extraction}. It identifies the budget delivered to the terminal consumer as exactly $W,Q,T,E,H,C,P,N$, so the terminal read has no unaccounted row outside the displayed packet.

Now combine the classifier and non-escape surfaces. By \autoref{thm:uniform-cauchy-criterion-diagonal-exit-classifier} and \autoref{thm:uniform-cauchy-criterion-diagonal-exit-nonescape}, any visible distinction at the terminal diagonal exit is already carried by the displayed $BHist$, $hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally apply \autoref{thm:uniform-cauchy-criterion-exit-route-consumer-coverage}. Since every terminal consumer is already covered by the same finite route, the listed quotient, host-equality, choice, completeness, metric-completeness, and detached-completion coordinates have no accepted route slot from which they could replace $W,Q,T,E,H,C,P,N$.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_terminal\_route\_exhaustion}

\begin{theorem}[UniformCauchyCriterion terminal Real-completion lock]
\label{thm:uniform-cauchy-criterion-terminal-real-completion-lock}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal read shares the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, $\RealLimitUniquenessSealUp$, and $\TailCofinalityScheduleUp$ rows. Then every Real-and-Completion phase exit classifier is locked to the finite route
$$
W,Q,T,E,H,C,P,N.
$$
The locked route is the one whose packet supplies $\Cont(I,T,R_t)$, $\Cont(T,E,R_E)$, $\Cont(R_t,R_E,R_B)$, and $\Cont(R_B,P,R_C)$, whose package signs $R_t$, $R_E$, $R_B$, and $R_C$, and whose terminal completion read carries the local name row $N$ while refusing both host-tail return continuations out of $R_B$. No quotient stream, host real equality, choice row, ambient completeness, detached completion endpoint, selected representative, or replacement tail schedule can refine that terminal classifier.
\end{theorem}
\begin{proof}
Start with diagonal uniqueness exit and the diagonal exit classifier. They identify the accepted terminal read as a finite classifier route over the same stream name, regular rational readback, dyadic tolerance, Real seal, transport, continuation, provenance, and local naming rows.

Apply diagonal budget extraction along the concrete continuation chain. The accepted packet gives the index-to-tail read, the tail-to-seal read, the tail-read-to-seal-read budget read, and the budget-to-provenance completion read:
$$
\Cont(I,T,R_t),\quad
\Cont(T,E,R_E),\quad
\Cont(R_t,R_E,R_B),\quad
\Cont(R_B,P,R_C).
$$

The same extraction supplies the package signatures of $R_t$, $R_E$, $R_B$, and $R_C$. Together with the packet signature for $N$, this makes the completion read a unary finite read over the displayed route and keeps the terminal local name tied to the accepted bundle.

Now use the host-tail refusal supplied by the same budget read. Both possible host-tail return continuations from $R_B$ back to $R_t$ are absurd, so the route cannot be refined by returning through an external tail oracle, selected representative, host equality row, or detached completion endpoint.

Finally combine exit-route consumer coverage, structural-face coverage, tail-budget exhaustion, and terminal-route exhaustion. The $\TailCofinalityScheduleUp$ row is consumed as a sibling schedule on the same finite route, and \autoref{thm:uniform-cauchy-criterion-diagonal-terminal-route-exhaustion} leaves no route slot outside $W,Q,T,E,H,C,P,N$. Therefore every terminal Real-and-Completion exit classifier is locked to that finite route.
\end{proof}
\leanvariant{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_real\_completion\_budget\_lock}

\begin{theorem}[UniformCauchyCriterion Real-completion selector-route stability]
\label{thm:uniform-cauchy-criterion-real-completion-selector-route-stability}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal exit shares the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, $\RealLimitUniquenessSealUp$, and $\TailCofinalityScheduleUp$ rows. Suppose one Phase Real and Completion consumer route is replaced by another accepted route with the same extracted $W,Q,T,E,H,C,P,N$ faces and the same displayed sibling rows.

Then the replacement preserves the Phase Real and Completion selector boundary. Every admissible selector read remains exhausted by the same finite route $W,Q,T,E,H,C,P,N$, together with the displayed stream-name, regular-sequence, dyadic-core, Real, diagonal-compatibility, uniqueness-seal, and tail-cofinality faces. No quotient stream, host equality, selected limit, countable-choice row, ambient-completeness witness, or independent completion datum can refine or distinguish the replacement route.
\end{theorem}
\begin{proof}
First apply diagonal budget extraction, \autoref{thm:uniform-cauchy-criterion-diagonal-budget-extraction}. It identifies the finite route $W,Q,T,E,H,C,P,N$ delivered to Phase Real and Completion-facing consumers of the accepted terminal exit.

Next use exit route consumer coverage and structural-face coverage, \autoref{thm:uniform-cauchy-criterion-exit-route-consumer-coverage} and \autoref{thm:uniform-cauchy-criterion-diagonal-structural-face-coverage}. These theorems keep every consumer route on the same stream-window, dyadic-tolerance, regular-readback, Real-seal, transport, route, provenance, and local naming faces.

Now compare the original and replacement routes. By hypothesis they share the extracted $W,Q,T,E,H,C,P,N$ faces and the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, $\RealLimitUniquenessSealUp$, and $\TailCofinalityScheduleUp$ rows, so the replacement has no additional selector coordinate.

Finally apply diagonal terminal route exhaustion and the terminal Real-completion lock, \autoref{thm:uniform-cauchy-criterion-diagonal-terminal-route-exhaustion} and \autoref{thm:uniform-cauchy-criterion-terminal-real-completion-lock}. They exhaust all admissible Phase Real and Completion reads by the same finite route. Therefore quotient streams, host equality, selected limits, countable choice, ambient completeness, and independent completion data remain outside the preserved selector boundary.
\end{proof}

\begin{theorem}[UniformCauchyCriterion diagonal uniqueness four-face terminal]
\label{thm:uniform-cauchy-diagonal-uniqueness-four-face-terminal}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose terminal read shares the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, $\RealLimitUniquenessSealUp$, and $\TailCofinalityScheduleUp$ rows. Then every accepted UniformCauchyCriterion terminal read over those rows factors through the same four-face Phase Real and Completion packet with structural route
$$
W,Q,T,E,H,C,P,N.
$$
The four faces are exactly the stream-window, dyadic-tolerance, regular-readback, and Real-seal faces, and the route is preserved through the same diagonal-compatibility, uniqueness-seal, and tail-cofinality rows. No quotient stream, host real equality, selected limit, countable-choice row, ambient-completeness witness, detached tail oracle, or independent completion datum can distinguish a second terminal read.
\end{theorem}
\begin{proof}
First apply diagonal budget extraction, \autoref{thm:uniform-cauchy-criterion-diagonal-budget-extraction}. It identifies $W,Q,T,E,H,C,P,N$ as the finite budget route delivered to Phase Real and Completion-facing consumers of the accepted terminal exit.

Next use exit route consumer coverage, \autoref{thm:uniform-cauchy-criterion-exit-route-consumer-coverage}. Every accepted terminal consumer is already routed through the same extracted budget together with the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\DiagonalLimitCompatibilityUp$, and $\RealLimitUniquenessSealUp$ rows.

Now apply diagonal structural-face coverage, \autoref{thm:uniform-cauchy-criterion-diagonal-structural-face-coverage}. The route is forced to expose the four structural faces $W,Q,T,E$ and the support rows $H,C,P,N$ before the terminal classifier or any Phase Real and Completion consumer may be read.

Finally use selector-route stability, \autoref{thm:uniform-cauchy-criterion-real-completion-selector-route-stability}. Since the original and replacement terminal reads share the extracted budget and the same diagonal-compatibility, uniqueness-seal, and tail-cofinality rows, the replacement preserves the Phase Real and Completion selector boundary. The listed quotient, host-equality, choice, completeness, tail-oracle, and detached-completion coordinates therefore have no accepted route slot.
\end{proof}
