\begin{theorem}[Uniform Cauchy criterion finite-family budget seal composition]
\label{thm:uniform-cauchy-criterion-finite-family-budget-seal-composition}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted finite-family $\UniformCauchyCriterionUp$ packet. Any $\RealWindowBudgetUp$ consumer that preserves the endpoint route of $U$, the $\StreamNameUp$ four-object exit route, the $\RegSeqRatUp$ real-seal handoff, and the $\RealWindowBudgetUp$ completion handoff factors through the single budgeted seal path
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T \longmapsto E.
$$
It cannot introduce a second $\StreamNameUp$ family, quotient stream, host real equality, selected limit, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_finite\_family\_budget\_seal\_composition}
\begin{proof}
First apply the finite-family endpoint budget reflector and route lock, \autoref{thm:uniform-cauchy-criterion-finite-family-endpoint-budget-reflector} and \autoref{thm:uniform-cauchy-criterion-finite-family-route-lock}. They identify every endpoint-facing read of $U$ with the displayed budgeted route and prevent a second public seal path through an independent stream family or detached completion coordinate.

Next compose the three external handoff surfaces. The $\StreamNameUp$ side is the four-object exit route of \autoref{thm:streamname-real-completion-four-object-exit-route}; the regular-rational side is the seal handoff of \autoref{thm:regseqrat-real-seal-handoff}; and the Real-window side is the completion handoff of \autoref{thm:real-window-budget-real-completion-handoff}. These surfaces read the finite StreamName, RegSeqRat, DyadicRatCore, and Real faces as projections of one displayed BEDC route rather than as independently chosen completion data.

The local nonescape boundary then removes the absent coordinates. By \autoref{thm:uniform-cauchy-criterion-finite-family-nonescape-ledger}, selected limits, quotient streams, host real equality, ambient completeness, and detached tail data are not rows of the accepted packet.

Finally use the terminal Real-window route of \autoref{thm:uniform-cauchy-criterion-realwindowbudget-terminal-route}. Since the endpoint route, StreamName exit, RegSeqRat seal handoff, and RealWindowBudget completion handoff have all been identified with the same rows $I,W,M,Q,T,E,H,C,P,N$, the consumer has only the single factorization path displayed in the statement.
\end{proof}

\begin{theorem}[Uniform Cauchy criterion terminal seal envelope]
\label{thm:uniform-cauchy-criterion-terminal-seal-envelope}
Every terminal consumer of an accepted finite-family $\UniformCauchyCriterionUp$ packet factors through the displayed $\StreamNameUp$ window, the $\RegSeqRatUp$ readback, the $\DyadicRatCoreUp$ ledger, the $\RealUp$ seal, the $\RealWindowBudgetUp$ packet, and the four-face boundary of $\RealCompletionExactBoundaryUp$. The envelope has no coordinate for quotient streams, host equality, selected limits, choice, host metric data, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_terminal\_seal\_envelope}
\begin{proof}
First use the finite-family budget seal composition and the Real-window terminal route. They identify the terminal route of the criterion with the single displayed path through the finite window, tolerance ledger, regular readback, and Real seal rows.

Next attach the Real-window budget and exact-boundary surfaces. The Real-window handoff supplies the budget packet, while four-face exactness identifies the StreamName, RegSeqRat, DyadicRatCore, and Real faces as the only completion-facing boundary.

Finally use the terminal quotient-refusal and non-escape clauses already cited above. They remove quotient streams, host equality, selected limits, choice, host metric data, and ambient completeness from the consumer surface, so the listed rows form the terminal envelope.
\end{proof}

\begin{theorem}[Uniform Cauchy criterion completion Real correspondence]
\label{thm:uniform-cauchy-criterion-completion-real-correspondence}
For every accepted finite-family $\UniformCauchyCriterionUp$ packet, every completion-facing read of its terminal $\RealUp$ seal is the same read as the four-face $\RealCompletionExactBoundaryUp$ route over the displayed $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, $\RealWindowBudgetUp$ packet, and structural $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. No host equality, quotient stream, selected limit, choice, host metric datum, or ambient completeness proof may mediate this correspondence.
\end{theorem}
\begin{proof}
Start from \autoref{thm:uniform-cauchy-criterion-terminal-seal-envelope}. It gives the completion-facing consumer a single route through the StreamName, RegSeqRat, DyadicRatCore, Real, and budget rows before the exact boundary is read.

Apply the Real-completion boundary pullback and four-face exactness. These results say that the terminal Real face is the fourth face of the same boundary whose earlier faces are the StreamName window, regular readback, and dyadic ledger.

The non-escape clauses then rule out the absent mediators. Since the accepted packet carries only the displayed finite rows and structural support, the completion read and the Real seal read are the same BEDC route.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_completion\_real\_correspondence}

\begin{theorem}[Uniform Cauchy criterion terminal four-face window exactness]
\label{thm:uniform-cauchy-criterion-terminal-four-face-window-exactness}
For every accepted finite-family $\UniformCauchyCriterionUp$ packet, a terminal finite-window read is exact if and only if it factors through the displayed $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal, $\RealWindowBudgetUp$ packet, and $\RealCompletionExactBoundaryUp$ four-face boundary. No quotient stream, host equality, selected limit, choice row, host metric datum, ambient completeness proof, or second completion face may mediate the read.
\end{theorem}
\begin{proof}
The forward direction starts from the terminal seal envelope, \autoref{thm:uniform-cauchy-criterion-terminal-seal-envelope}. It supplies the single terminal route through the StreamName window, regular readback, dyadic ledger, Real seal, RealWindowBudget packet, and exact-boundary face.

Use the completion Real correspondence, \autoref{thm:uniform-cauchy-criterion-completion-real-correspondence}, to identify the Real seal with the fourth face of the same exact boundary. The first three faces are the StreamName window, RegSeqRat readback, and DyadicRatCore ledger already present in the envelope.

For the reverse direction, apply finite-window coverage, \autoref{thm:uniform-cauchy-criterion-finite-window-coverage}. Any read outside the displayed route would ask for one of the refused mediators or a second completion face, so every factorization through the listed four-face route is exactly the terminal finite-window read.
\end{proof}

\begin{theorem}[Uniform Cauchy criterion finite-window coverage]
\label{thm:uniform-cauchy-criterion-finite-window-coverage}
Every finite-window observation used by a terminal $\UniformCauchyCriterionUp$ consumer is covered by the same $\StreamNameUp$ window and $\RegSeqRatUp$ readback that feed the $\DyadicRatCoreUp$ ledger, the $\RealUp$ seal, the $\RealWindowBudgetUp$ packet, and the $\RealCompletionExactBoundaryUp$ four-face boundary. A consumer that asks for a quotient stream, host equality, selected limit, choice principle, host metric datum, or ambient completeness row has left the accepted terminal envelope.
\end{theorem}
\begin{proof}
Use the finite-observation terminal synchronization theorem to pull any finite observation back to the displayed selector route. The synchronization fixes the shared window, dyadic ledger, regular readback, and Real seal rows.

Then use the budget seal composition and terminal envelope theorem. They keep the pulled-back finite observation on the same window-to-seal route consumed by RealWindowBudgetUp and by the exact completion boundary.

The exclusion statement follows from the same quotient-refusal and non-escape boundaries. Those objects are not rows of the finite terminal envelope, so they cannot cover or refine an accepted finite-window observation.
\end{proof}

\begin{theorem}[Uniform Cauchy criterion finite-family Rat fold handoff]
\label{thm:uniform-cauchy-criterion-finite-family-rat-fold-handoff}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted finite-family $\UniformCauchyCriterionUp$ packet. A finite family of shared-threshold windows transported through $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\RatUp$ order readback admits a single $\BHist$ lower-bound fold row consumed by the finite-family seal of $U$. The fold row is read through the same $I,W,M,Q,T,E,H,C,P,N$ route and cannot introduce quotient streams, selected host limits, host real equality, detached tail oracles, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
First use the finite-family seal obligation package. It supplies the accepted rows $I,W,M,Q,T,E,H,C,P,N$ and identifies the shared-window seal route that every finite-family consumer must preserve.

Next read each threshold through the rational order surface. The $\StreamNameUp$ window provides the finite family of windows, the $\RegSeqRatUp$ readback supplies regular tail data, the $\RealUp$ seal keeps the terminal face on the displayed route, and the $\RatUp$ order readback exposes only rational lower-bound comparisons.

Now fold over the finite family. Using the same minimum-selector pattern employed by the compact-uniform-modulus chapters, each rational threshold comparison contributes one displayed lower-bound row, and finite iteration combines those rows into a single $\BHist$ lower-bound fold row.

Finally repack the fold row into the shared-window seal route. The route lock, nonescape ledger, and terminal seal envelope keep the fold on $I,W,M,Q,T,E,H,C,P,N$, so the finite-family seal consumes the lower-bound row without importing any absent completion or choice coordinate.
\end{proof}
