The late boundary and overlap routes consume the L10 sibling surfaces \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-real-namecert}, and the existing dyadic tail and tolerance rows already named in the parent packet. They read those dependencies through the same shared window, threshold, dyadic tolerance, tail-ledger, and seal handoff coordinates.

\begin{theorem}[UniformCauchyCriterion empty-family tail ledger]
\label{thm:uniform-cauchy-criterion-empty-family-tail-ledger}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Suppose that $I$ is the empty finite family index ledger and that $T$ is the empty finite tail-comparison ledger. Then the shared-threshold route is accepted as the vacuous finite-family route
$$
\mathsf{empty}_{I} \longmapsto W \longmapsto M \longmapsto Q \longmapsto \mathsf{empty}_{T} \longmapsto E.
$$
It has no family member at which a tail comparison can be requested, no completed family limit to export through the $\RealUp$ seal, and no indexwise schedule distinct from the single displayed $\CauchyModulusUp$ row $M$.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_empty\_family\_tail\_ledger}
\begin{proof}
Project the accepted packet through \autoref{def:uniform-cauchy-criterion-carrier}. Its only family-facing rows are the finite index ledger $I$, the shared window family $W$, the single modulus schedule $M$, the tolerance row $Q$, and the tail-comparison ledger $T$.

Because $I$ is empty, there is no displayed family index through which a consumer can select a component window or request an indexwise threshold. The window-stability row of \autoref{thm:uniform-cauchy-criterion-window-stability} therefore has no component case to check; the shared row $M$ remains the only threshold schedule visible in the packet.

Because $T$ is empty, \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness} leaves no accepted tail comparison after the route through $I,W,M,Q$. Thus the finite family criterion is satisfied only in the vacuous sense: every possible comparison for an index in $I$ is already exhausted by the absence of such an index and by the absence of a tail-ledger entry.

Now apply \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. Transport can rename the displayed rows through $\hsame$ and replay their reads through $\Cont$, but it cannot replace the single schedule $M$ by a family of independently selected schedules. With the family ledger empty, there is not even an index at which such a schedule could be named.

Finally use \autoref{thm:uniform-cauchy-criterion-real-seal-handoff} and \autoref{thm:uniform-cauchy-criterion-non-escape-boundary}. Every $\RealUp$ seal read still factors through $I,W,M,Q,T,E$, and in the present boundary this is precisely the displayed route through the empty family ledger and empty tail ledger. Since the packet has no coordinate for a completed family limit, quotient stream family, host real equality, selected limit, or ambient completeness principle, the seal handoff exports none of them.
\end{proof}

\begin{theorem}[UniformCauchyCriterion single-member restriction exactness]
\label{thm:uniform-cauchy-criterion-single-member-restriction-exactness}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet, and let $i$ be a displayed member of the finite family ledger $I$. The singleton restriction $U|_{\{i\}}$ reads the same shared rows $W,M,Q,T,E,H,C,P,N$ through the component selected by $i$. Its finite-family ledger is the one-member restriction of $I$, and it adds no pointwise limit, no indexwise modulus, and no endpoint read outside the original tail ledger.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_single\_member\_restriction\_exactness}
\begin{proof}
Project $U$ through \autoref{def:uniform-cauchy-criterion-carrier}. The family-facing rows are $I,W,M,Q,T$, and the singleton request supplies only a displayed member $i$ of $I$.

Apply \autoref{thm:uniform-cauchy-criterion-window-stability}. Restricting to the component named by $i$ keeps the read inside the same shared window family $W$ and transports only the selected component through the existing $\hsame$ rows.

Next use \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness} and \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. The tail comparison for the singleton still passes through the same $M,Q,T$ route, so the restricted packet has no coordinate for an independently chosen pointwise threshold.

Finally apply \autoref{thm:uniform-cauchy-criterion-regseqrat-consumer-package} and \autoref{thm:uniform-cauchy-criterion-real-seal-completion-boundary}. A downstream consumer sees the same regular-rational and seal handoff rows, specialized to the displayed singleton, and cannot extract a pointwise limit from the restriction.
\end{proof}

\begin{theorem}[UniformCauchyCriterion paired-family union ledger]
\label{thm:uniform-cauchy-criterion-paired-family-union-ledger}
Let $J$ and $K$ be two displayed subfamily ledgers of an accepted $\UniformCauchyCriterionUp$ packet
$$
U=(I,W,M,Q,T,E,H,C,P,N).
$$
Suppose both subfamily ledgers factor through the same $I,W,M,Q,T$ rows. Then the paired-family ledger $J\cup K$ is accepted over the same shared threshold route. Its tail comparisons are exactly the union of the two displayed subfamily tail reads inside $T$, transported by the same $H,C$ rows and sealed through the same $E,P,N$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_paired\_family\_union\_ledger}
\begin{proof}
Read the two subfamily ledgers as displayed restrictions of $I$. Since both factor through the same packet $U$, neither subfamily supplies an additional window family or modulus row.

Use \autoref{thm:uniform-cauchy-criterion-window-stability} to keep both subfamily reads on $W$. Use \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport} to keep both threshold requests on the single schedule $M$.

Apply \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. The only accepted tail-comparison entries are the displayed rows of $T$ after the route through $I,W,M,Q$, so the paired ledger is their finite union inside that same ledger.

It remains to package the paired read for consumers. Use \autoref{thm:uniform-cauchy-criterion-regseqrat-consumer-package} and \autoref{thm:uniform-cauchy-criterion-real-seal-completion-boundary}: the union ledger is replayed by the same $H,C$ rows and inherits the same $E,P,N$ seal and provenance surface.
\end{proof}

\begin{theorem}[UniformCauchyCriterion shared-schedule Real seal inheritance]
\label{thm:uniform-cauchy-criterion-shared-schedule-real-seal-inheritance}
Every $\RealUp$-facing consumer of a singleton restriction or paired-family ledger of an accepted $\UniformCauchyCriterionUp$ packet inherits the same shared schedule and seal handoff route
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T \longmapsto E.
$$
The inherited route may restrict or pair displayed family entries, but it cannot introduce a new Cauchy schedule, selected family limit, quotient stream family, host real equality, or ambient completeness object.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_shared\_schedule\_real\_seal\_inheritance}
\begin{proof}
Begin with the real-facing consumer read. By \autoref{thm:uniform-cauchy-criterion-real-seal-handoff}, every such read reaches $E$ only after passing through $I,W,M,Q,T$.

For a singleton restriction, apply \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness}. The selected component keeps the same shared schedule and specializes only the finite family ledger.

For a paired-family read, apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}. The paired ledger is assembled inside the same tail ledger and is replayed by the same transport and continuation rows.

Finally use \autoref{thm:uniform-cauchy-criterion-regseqrat-consumer-package}, \autoref{thm:uniform-cauchy-criterion-real-seal-completion-boundary}, and \autoref{thm:uniform-cauchy-criterion-non-escape-boundary}. These package the inherited seal route and rule out any new schedule, selected limit, quotient stream family, host equality, or completeness principle.
\end{proof}

\begin{theorem}[UniformCauchyCriterion shared-window threshold meet]
\label{thm:uniform-cauchy-criterion-shared-window-threshold-meet}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. The shared window family $W$ and the single modulus row $M$ determine one finite threshold meet before any $Q,T,E$ read is available. Every tolerance row, tail-comparison row, and $\RealUp$ seal row is therefore downstream of the same $W,M$ route and cannot select an indexwise modulus family.
\end{theorem}
\begin{proof}
First project the carrier of \autoref{def:uniform-cauchy-criterion-carrier}. The packet has one shared window family row $W$ and one modulus schedule row $M$.

Apply \autoref{thm:uniform-cauchy-criterion-window-stability}. Transport of a family request stays inside the same window family, so no later read can replace $W$ by a separately chosen component window.

Next apply \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. The threshold route is transported as the single row $M$, and the tolerance, tail, and seal coordinates are read only after that route has been fixed.

It remains to rule out later selection. Use \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness} and \autoref{thm:uniform-cauchy-criterion-real-seal-handoff}: $Q,T,E$ are consumer rows downstream of $I,W,M$, not sources for a second modulus family.
\end{proof}
\begin{theorem}[UniformCauchyCriterion family-tail intersection]
\label{thm:uniform-cauchy-criterion-family-tail-intersection}
For every accepted $\UniformCauchyCriterionUp$ packet and every nonempty subfamily request, the tail read is an intersection of the existing finite family ledger with the same $W,M,Q,T$ route. It is not an independently chosen family of moduli, and it cannot detach a subfamily from the displayed index ledger $I$ or the shared threshold route.
\end{theorem}
\begin{proof}
Begin with the finite index ledger $I$. A nonempty subfamily request is a read of displayed indices from $I$, so it has no source outside the accepted packet.

Use \autoref{thm:uniform-cauchy-criterion-window-stability} and \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. These keep the subfamily request on the same window family $W$ and the same modulus row $M$.

Now apply \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. A tail comparison is accepted only as a read through $Q$ and $T$ after the displayed family and threshold rows are fixed.

Thus the subfamily tail is the finite intersection of the already displayed family ledger with the same $W,M,Q,T$ route. The packet has no coordinate for an independently chosen family of moduli.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_family\_tail\_intersection}

\begin{theorem}[UniformCauchyCriterion RegSeqRat uniform consumer exhaustion]
\label{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}
Every $\RegSeqRatUp$-facing consumer of an accepted $\UniformCauchyCriterionUp$ packet is exhausted by the rows
$$
I,W,M,Q,T,E,H,C,P,N.
$$
Such a consumer reads the shared window family, single threshold row, dyadic tolerance row, finite tail ledger, seal handoff, transport rows, continuation routes, package provenance, and local naming row. It cannot export quotient streams, selected limits, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:uniform-cauchy-criterion-regseqrat-tail-equivalence}. The $\RegSeqRatUp$ read is the same finite evidence as the tail-ledger route, so it must pass through $I,W,M,Q,T$.

Apply \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet}. This fixes the shared window and threshold rows before the consumer can inspect the tolerance, tail, or seal coordinates.

Use \autoref{thm:uniform-cauchy-criterion-family-tail-intersection} for nonempty subfamily reads, and use \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger} for the empty-family boundary. Both cases keep the consumer inside the finite family ledger and the same $W,M,Q,T$ route.

Finally apply \autoref{thm:uniform-cauchy-criterion-non-escape-boundary}. The remaining rows $E,H,C,P,N$ package the seal, transport, continuation, provenance, and local name, but they add no quotient stream, selected limit, host real equality, or completeness principle.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_regseqrat\_uniform\_consumer\_exhaustion}

\begin{theorem}[UniformCauchyCriterion tail-overlap budget exhaustion]
\label{thm:uniform-cauchy-criterion-tail-overlap-budget-exhaustion}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every overlap of two finite subfamily tail requests in $U$ factors through the same finite rows $I,W,M,Q,T,E,H,C,P,N$. The overlap has no second tail budget, quotient stream family, selected family limit, host real equality, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_tail\_overlap\_budget\_exhaustion}
\begin{proof}
First combine the paired-family union ledger with the shared-window threshold meet. By \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}, two finite family requests are joined only inside the displayed index ledger $I$. By \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet}, their common window and threshold route is the same $W,M$ route, not a pair of separately chosen schedules.

Next pass from the joined family request to the tail read. Use \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}: the common tail is an intersection of the displayed family ledger with $W,M,Q,T$. Thus the dyadic tolerance row and tail ledger row are inherited from $U$ rather than rebuilt for the overlap.

Finally send the overlap to the consumers. Apply \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion} to exhaust the RegSeqRat side by $I,W,M,Q,T,E,H,C,P,N$, and apply \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization} to keep the Real seal side downstream of the same package. The non-escape boundary then rules out a second budget, quotient stream family, selected limit, host real equality, or ambient completeness row.
\end{proof}

\begin{theorem}[UniformCauchyCriterion RegSeqRat--Real seal overlap]
\label{thm:uniform-cauchy-criterion-regseqrat-real-seal-overlap}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Any overlap of two finite subfamily tail requests that reaches a $\RegSeqRatUp$-facing consumer and then a $\RealUp$ seal factors through the same route
$$
I,W,M,Q,T,E,H,C,P,N.
$$
The overlap cannot introduce a second RegSeqRat classifier, quotient stream family, selected family limit, host real equality, or ambient completeness witness.
\end{theorem}
\begin{proof}
First place the two subfamily requests on the common window. Apply \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet} to identify the shared window and threshold rows $W,M$ before either request reaches its tolerance or tail data.

Next pass to the finite family-tail overlap. Apply \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}. The common tail evidence is the displayed intersection inside the finite ledger $I$ and the same dyadic tolerance and tail rows $Q,T$.

Now read the RegSeqRat-facing consumer. By \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}, the consumer is exhausted by $I,W,M,Q,T,E,H,C,P,N$, so it has no coordinate for a second RegSeqRat classifier or quotient stream family.

Finally attach the Real seal. Use \autoref{thm:uniform-cauchy-criterion-shared-schedule-real-seal-inheritance} and \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization} to keep the seal read downstream of the same $E,H,C,P,N$ rows. The non-escape boundary then rules out selected family limits, host real equality, and ambient completeness.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_regseqrat\_real\_seal\_overlap}

\begin{theorem}[UniformCauchyCriterion RegSeqRat--Real seal pullback exactness]
\label{thm:uniform-cauchy-criterion-regseqrat-real-seal-pullback-exactness}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every displayed subfamily pullback that reaches both a $\RegSeqRatUp$-facing consumer and a $\RealUp$ seal is exact on the same route
$$
I,W,M,Q,T,E,H,C,P,N.
$$
It cannot introduce a second RegSeqRat classifier, quotient stream family, selected family limit, host real equality, or ambient completeness witness.
\end{theorem}
\begin{proof}
First put the pullback on the shared threshold route. Apply \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet}: the shared window row $W$ and the single modulus row $M$ are fixed before any tolerance, tail, or seal row is read.

Next restrict the subfamily tail. By \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}, the pullback is an intersection of the existing finite family ledger with the same $W,M,Q,T$ route. It therefore has no separate index carrier or independently selected modulus family.

Now exhaust the RegSeqRat-facing side. Use \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}; the consumer is exhausted by $I,W,M,Q,T,E,H,C,P,N$ and has no coordinate for a second RegSeqRat classifier or quotient stream family.

Finally attach the Real seal through \autoref{thm:uniform-cauchy-criterion-regseqrat-real-seal-overlap}. The overlap already reaches the $\RegSeqRatUp$ consumer and the $\RealUp$ seal through the same route. The non-escape boundary then rules out selected family limits, host real equality, and ambient completeness, so the displayed pullback is exact on the original packet rows.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_regseqrat\_real\_seal\_pullback\_exactness}

\begin{theorem}[UniformCauchyCriterion shared-tail subfamily pullback]
\label{thm:uniform-cauchy-criterion-shared-tail-subfamily-pullback}
For every accepted $\UniformCauchyCriterionUp$ packet $U=(I,W,M,Q,T,E,H,C,P,N)$, any downstream $\RegSeqRatUp$ or $\RealUp$ consumer of a displayed subfamily pullback reads the same shared tail route through the finite index ledger. Such a consumer cannot introduce an indexwise modulus family or detach the pullback from the rows $I,W,M,Q,T,E,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier rows of $U$. The only finite family ledger is $I$, the only shared window and threshold route is $W,M$, and the only tail and seal rows available to a consumer are $Q,T,E$ with their displayed transport, continuation, provenance, and naming rows.

For a one-component pullback, use singleton restriction exactness. The singleton request is a read of the existing family ledger and therefore follows the same $W,M,Q,T$ route. For two displayed components, use \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}; finite pairs are joined inside the displayed ledger before any tail read is exposed.

It remains to handle downstream consumers. Apply \autoref{thm:uniform-cauchy-criterion-tail-overlap-budget-exhaustion}. The pullback is already exhausted by the common finite route, so a $\RegSeqRatUp$ or $\RealUp$ consumer receives only the shared tail package and has no coordinate for an indexwise modulus family.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_shared\_tail\_subfamily\_pullback}

\begin{theorem}[UniformCauchyCriterion finite-index ledger transport]
\label{thm:uniform-cauchy-criterion-finite-index-ledger-transport}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every transported family request for $U$ factors through the displayed finite ledger $I$, componentwise $\hsame$ transport, and displayed $\Cont$ routes before any request can reach $W,M,Q,T,E$. Thus the transported request is a replay of the public finite package and cannot choose a new index carrier, a new family window, or an external modulus schedule.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_finite\_index\_ledger\_transport}
\begin{proof}
Project the carrier of \autoref{def:uniform-cauchy-criterion-carrier}. The only family ledger coordinate supplied by the packet is $I$, and the only transport and continuation coordinates supplied for family reads are $H$ and $C$.

Apply \autoref{thm:uniform-cauchy-criterion-window-stability}. Any transported family request that reaches $W$ is already a read of the displayed window family over $I$, so it has no independent carrier from which a second family can be selected.

Next apply \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. The same transported request reaches $M,Q,T$ only by following the shared threshold route, with componentwise $\hsame$ evidence and the displayed $\Cont$ routes supplied by $H$ and $C$.

Finally use \autoref{thm:uniform-cauchy-criterion-real-seal-handoff}. The seal row $E$ is downstream of the same finite ledger and transport route, so the transported request reaches $W,M,Q,T,E$ only as a replay of $I,H,C$ inside the public package.
\end{proof}

\begin{theorem}[UniformCauchyCriterion finite-ledger route coverage]
\label{thm:uniform-cauchy-criterion-finite-ledger-route-coverage}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every downstream $\RegSeqRatUp$-facing or $\RealUp$-facing consumer route for $U$ factors through the displayed finite index ledger $I$, shared window $W$, single modulus $M$, tolerance row $Q$, tail ledger $T$, seal handoff $E$, transport row $H$, continuation row $C$, provenance row $P$, and local name $N$.

Consequently the route ledger is exhausted by $I,W,M,Q,T,E,H,C,P,N$. It has no coordinate for a quotient stream family, selected family limit, host equality, or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_finite\_ledger\_route\_coverage}
\begin{proof}
First put transported family requests on the public ledger. By \autoref{thm:uniform-cauchy-criterion-finite-index-ledger-transport}, a transported request can reach $W,M,Q,T,E$ only after reading $I,H,C$.

Next fix the threshold and tail rows. Apply \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet} to identify the shared $W,M$ route, and apply \autoref{thm:uniform-cauchy-criterion-family-tail-intersection} to keep every nonempty subfamily tail inside the same $I,W,M,Q,T$ ledger.

Now read the two consumer sides. The $\RegSeqRatUp$ side is exhausted by \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}. The shared $\RegSeqRatUp$--$\RealUp$ pullback route is exact by \autoref{thm:uniform-cauchy-criterion-regseqrat-real-seal-pullback-exactness}.

Finally apply \autoref{thm:uniform-cauchy-criterion-non-escape-boundary}. Since the packet exports only the displayed seal, transport, continuation, provenance, and naming rows after the tail ledger is fixed, no quotient stream family, selected limit, host equality, or ambient completeness coordinate remains.
\end{proof}

\begin{theorem}[UniformCauchyCriterion shared-schedule cofinal pullback]
\label{thm:uniform-cauchy-criterion-shared-schedule-cofinal-pullback}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every cofinal subfamily pullback of $U$ that reaches a $\RegSeqRatUp$ consumer and a $\RealUp$ seal consumer factors through the same finite schedule
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T
$$
before either consumer reads $E,H,C,P,N$. The pullback therefore shares the displayed finite index ledger, window family, modulus schedule, dyadic tolerance row, and tail ledger, and it exports no quotient stream family, selected family limit, host real equality, or ambient completeness datum.
\end{theorem}
\begin{proof}
First place the cofinal pullback on the finite ledger. By \autoref{thm:uniform-cauchy-criterion-finite-index-ledger-transport}, every transported family request already passes through $I,H,C$ before it can reach $W,M,Q,T,E$.

Next identify the schedule read. Apply \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet}: the shared window row $W$ and the single modulus row $M$ are fixed before any tolerance, tail, or seal coordinate is available.

Now restrict to the cofinal subfamily tail. Use \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}; the pullback is a finite intersection inside the displayed ledger and keeps the same $W,M,Q,T$ route. Thus cofinality contributes no new index carrier and no independently selected modulus family.

Finally send the pullback to the two consumers. The $\RegSeqRatUp$ side is exhausted by \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}, and the shared $\RegSeqRatUp$--$\RealUp$ seal route is \autoref{thm:uniform-cauchy-criterion-regseqrat-real-seal-overlap}. The non-escape boundary then excludes quotient stream families, selected limits, host real equality, and ambient completeness, leaving the same finite schedule for both consumers.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_shared\_schedule\_cofinal\_pullback}

\begin{theorem}[UniformCauchyCriterion shared-tail ledger coverage]
\label{thm:uniform-cauchy-criterion-shared-tail-ledger-coverage}
For every accepted $\UniformCauchyCriterionUp$ packet, the empty-family tail read, singleton restriction, paired-family read, and nonempty subfamily tail read are all exhausted by one shared route
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T.
$$
No listed tail read supplies a second tail ledger, an indexwise modulus family, or a detached comparison route outside the accepted packet.
\end{theorem}
\begin{proof}
Consider the four displayed kinds of family-tail consumer. For the empty-family boundary, apply \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger}; the accepted tail evidence is the displayed empty read of the same $T$ row.

For singleton reads, apply \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness}. The selected component is a restriction of $I$ and keeps the same $W,M,Q,T$ route.

For paired reads, apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}. The pair is assembled as a finite union inside the existing tail ledger, not as a new schedule or comparison object.

For nonempty subfamily reads, apply \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}. The subfamily tail is the finite intersection of the displayed ledger with the same shared route.

These cases cover the available family-tail reads of the packet. Since each case enters $T$ only through $I,W,M,Q$, the packet has no remaining coordinate from which a second tail ledger or detached route could be exported.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_shared\_tail\_ledger\_coverage}

\begin{theorem}[UniformCauchyCriterion Real seal consumer factorization]
\label{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}
Every $\RegSeqRatUp$-, $\RealUp$-, or completion-facing consumer of an accepted $\UniformCauchyCriterionUp$ packet factors through the public finite package
$$
I,W,M,Q,T,E,H,C,P,N.
$$
The factorization exposes the shared window, single threshold row, dyadic tolerance row, finite tail ledger, Real seal handoff, transport rows, continuation routes, provenance row, and local name. It cannot export quotient streams, selected limits, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Start with a $\RegSeqRatUp$-facing consumer. By \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}, the consumer is exhausted by $I,W,M,Q,T,E,H,C,P,N$ and cannot leave that finite package.

For the shared threshold dependency, apply \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet}. This fixes $W$ and $M$ before any tolerance, tail, or seal read is available, so later consumers inherit the same route.

Now pass to the $\RealUp$ seal boundary. Use \autoref{thm:uniform-cauchy-criterion-real-seal-completion-boundary}: the completion-facing handoff is exposed only as the seal row $E$ over the already displayed family and tail ledger.

Finally apply \autoref{thm:uniform-cauchy-criterion-non-escape-boundary}. The rows $H,C,P,N$ package transport, continuation, provenance, and the local name, while the packet still exports no quotient stream, selected limit, host real equality, or ambient completeness principle.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_real\_seal\_consumer\_factorization}

\begin{theorem}[UniformCauchyCriterion shared tail gluing determinacy]
\label{thm:uniform-cauchy-criterion-shared-tail-gluing-determinacy}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Suppose two finite subfamily tail reads of $U$ have the same displayed family intersection inside $I$ and agree on the shared threshold route through $W,M,Q,T$. Then the glued shared-tail read induces the same $\RegSeqRatUp$-facing consumer row and the same $\RealUp$ seal route through $E,H,C,P,N$. No second tail budget, quotient stream family, selected limit, host real equality, or ambient completeness coordinate can split the glued read after those rows agree.
\end{theorem}
\begin{proof}
First build the common tail ledger. Apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}; the two finite subfamily reads are assembled as a displayed union inside $I$ and do not create a new schedule outside the packet.

Next identify the shared tail. By \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}, agreement of the displayed family intersection inside $I$ makes the tail read a finite intersection of the same ledger along the same $W,M,Q,T$ route.

Now exhaust the possible overlap budget. Use \autoref{thm:uniform-cauchy-criterion-tail-overlap-budget-exhaustion}; since the threshold route already agrees through $W,M,Q,T$, the glued read has no coordinate from which a second tail budget can be exported.

Pass to the seal-facing rows by \autoref{thm:uniform-cauchy-criterion-regseqrat-real-seal-overlap}. The $\RegSeqRatUp$ readback and the $\RealUp$ seal handoff therefore see the same shared tail rather than two independent quotient stream families.

Finally apply \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The downstream consumer rows are exhausted by $I,W,M,Q,T,E,H,C,P,N$, so the glued shared tail fixes both the $\RegSeqRatUp$ consumer row and the $\RealUp$ seal route through $E,H,C,P,N$ and leaves no selected limit, host real equality, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[UniformCauchyCriterion budgeted Real seal factorization]
\label{thm:uniform-cauchy-criterion-budgeted-real-seal-factorization}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every $\RealUp$-facing seal read of $U$ that consumes a uniform family tail factors through the displayed finite route
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T \longmapsto E
$$
together with the sibling budget surfaces of $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and the dyadic tail/tolerance ledger. The factorization exposes only the finite index ledger, shared stream-name window, single threshold row, dyadic tolerance row, shared tail ledger, and Real seal handoff. It exports no quotient stream family, selected family limit, host real equality, or ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_budgeted\_real\_seal\_factorization}
\begin{proof}
First exhaust the family-tail cases before any seal read is considered. Apply \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger} for the empty-family boundary and \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness} for singleton reads. Apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger} for paired-family reads and \autoref{thm:uniform-cauchy-criterion-family-tail-intersection} for nonempty subfamilies.

These four cases land in the shared tail ledger by \autoref{thm:uniform-cauchy-criterion-shared-tail-ledger-coverage}. Hence every uniform family tail reaches $T$ only through the displayed $I,W,M,Q$ route and carries no separate stream family, pointwise modulus family, or detached comparison row.

Next route the budget consumers. By \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}, the $\RegSeqRatUp$ read is exhausted by $I,W,M,Q,T,E,H,C,P,N$. By \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}, the $\RealUp$ seal read is downstream of the same finite package rather than a separate completion object.

The cited route is exactly the sibling chain through $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and the dyadic tail/tolerance ledger: $W$ supplies the stream-name family surface, $M,Q,T$ supply the RegSeqRat and dyadic budget rows, and $E$ is the Real seal handoff. Since the route has no coordinate outside those rows, quotient stream families, selected family limits, host real equality, and ambient completeness are refused at the seal boundary.
\end{proof}

\begin{theorem}[UniformCauchyCriterion terminal late-route exhaustion]
\label{thm:uniform-cauchy-criterion-terminal-late-route-exhaustion}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every terminal $\RegSeqRatUp$, $\RealUp$, or completion-facing late-boundary consumer of $U$ is exhausted by the shared finite route
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T \longmapsto E \longmapsto H,C,P,N.
$$
The exhaustion is obtained by splitting only along the displayed late cases: empty family, singleton restriction, paired-family ledger, and nonempty subfamily tail. After those cases are read, the $\RegSeqRatUp$ consumer is handled by \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}, and the $\RealUp$ or completion-facing seal consumer is handled by \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The terminal route exports no indexwise modulus family, quotient stream family, selected family limit, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the four late family cases. The empty-family boundary is \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger}; the singleton restriction is \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness}. Both enter the same displayed $I,W,M,Q,T$ route.

The remaining family cases are paired-family and nonempty-subfamily reads. Apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger} for the paired ledger and \autoref{thm:uniform-cauchy-criterion-family-tail-intersection} for the nonempty subfamily tail. These two cases still use the same finite family and tail rows, so no separate modulus family or quotient stream family is introduced.

Now pass from family-tail exhaustion to terminal consumers. Apply \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion} to the $\RegSeqRatUp$-facing route; it reads exactly $I,W,M,Q,T,E,H,C,P,N$.

Finally apply \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The $\RealUp$ and completion-facing seal reads factor through the same package, with $E$ as the displayed seal handoff and $H,C,P,N$ as transport, continuation, provenance, and local naming. Since every late case has already been placed on that route, the accepted packet has no coordinate for a selected family limit, host real equality, or ambient completeness principle.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_terminal\_late\_route\_exhaustion}

\begin{theorem}[UniformCauchyCriterion finite tail readback coverage]
\label{thm:uniform-cauchy-criterion-finite-tail-readback-coverage}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every finite tail readback request for $U$ is covered by exactly one of the displayed routes: the empty-family route, the singleton restriction route, the paired-family route, or the nonempty-subfamily route. After that route is selected, every $\RegSeqRatUp$-, $\RealUp$-, or completion-facing consumer factors through
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T \longmapsto E
$$
together with the transport, continuation, provenance, and local naming rows $H,C,P,N$.

Consequently no finite tail readback of $U$ can export a quotient stream family, a selected family limit, host real equality, or ambient completeness outside the displayed packet.
\end{theorem}
\begin{proof}
Split the finite family request before any $\RegSeqRatUp$ or $\RealUp$ seal is inspected. The empty request is handled by \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger}; a one-member request is handled by \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness}. A two-sided displayed family read is handled by \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}.

It remains to cover finite nonempty subfamily reads that are not already one of those boundary cases. Apply \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}. This places the read inside the displayed finite family ledger and the same $W,M,Q,T$ route, with no source for an independently selected modulus family or detached tail ledger.

The four cases are exhaustive for finite tail readbacks because every request is either empty, a singleton, a paired displayed family, or a nonempty subfamily read. Apply \autoref{thm:uniform-cauchy-criterion-shared-tail-ledger-coverage} to put all of them on the shared tail ledger, then apply \autoref{thm:uniform-cauchy-criterion-terminal-late-route-exhaustion} to pass from that ledger to terminal consumers.

The consumer handoff is therefore the displayed route through $I,W,M,Q,T,E$ and then through $H,C,P,N$. Since the accepted packet has no coordinate for quotient stream families, selected limits, host equality, or ambient completeness, none of those principles can escape through a finite tail readback.
\end{proof}

\begin{theorem}[UniformCauchyCriterion finite-tail window factorization]
\label{thm:uniform-cauchy-criterion-finite-tail-window-factorization}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every finite tail readback covered by the empty-family, singleton, paired-family, or nonempty-subfamily case of \autoref{thm:uniform-cauchy-criterion-finite-tail-readback-coverage} factors through one L10 handoff route:
$$
I,W,M,Q,T \longmapsto \FiniteTailFilterUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
together with the structural rows $E,H,C,P,N$. The $\FiniteTailFilterUp$ stage is the finite-tail window route supplied by the tail-window exactness and Real-seal handoff rows of \autoref{ch:concrete-instances-finite-tail-filter-namecert}; the $\StreamNameUp$ stage reads the finite-window classifier already displayed by $W$; the $\RegSeqRatUp$ stage consumes the tail readback carried by $T$; and the $\RealUp$ stage seals the same route through $E$.

Thus the finite readback coverage of $U$ exports no indexwise modulus family, quotient stream family, selected limit, host real equality, ambient completeness principle, or detached tail filter outside the displayed packet.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:uniform-cauchy-criterion-finite-tail-readback-coverage}. It reduces every finite tail readback to one of the empty, singleton, paired-family, or nonempty-subfamily routes before any terminal consumer is inspected.

Next apply \autoref{thm:uniform-cauchy-criterion-shared-tail-ledger-coverage}. The four routes share the same finite family ledger and the same tail ledger $T$, so their readback evidence is already on the displayed $I,W,M,Q,T$ surface.

Now pass through the finite-tail window route. By \autoref{thm:finite-tail-filter-tail-window-exactness}, the relevant stream window, dyadic tolerance row, regular readback, tail-budget row, common-tail comparison, and seal-facing row are coordinates of one $\FiniteTailFilterUp$ packet. By \autoref{thm:finite-tail-filter-real-seal-handoff}, that packet is the route seen by Real and Completion consumers.

Finally identify the two terminal consumers. The RegSeqRat-facing part is exhausted by \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}, and the Real-facing part is exhausted by \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. These two rows read the same $W,T,E,H,C,P,N$ surface, so the L10 handoff has no carrier coordinate for an indexwise modulus family, quotient stream family, selected limit, host real equality, ambient completeness principle, or detached tail filter.
\end{proof}

\begin{theorem}[UniformCauchyCriterion late-overlap exhaustion]
\label{thm:uniform-cauchy-criterion-late-overlap-exhaustion}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every empty-family, singleton, paired-family, nonempty subfamily, and transported-family request that reaches a $\RegSeqRatUp$ or $\RealUp$ consumer factors through the same public route
$$
I,W,M,Q,T,E,H,C,P,N .
$$
The route exposes the finite index ledger, shared window family, single threshold row, dyadic tolerance row, tail ledger, Real seal handoff, transport rows, continuation routes, provenance row, and local name. It cannot export indexwise moduli, selected family limits, quotient stream families, host real equality, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_late\_overlap\_exhaustion}
\begin{proof}
First exhaust the family-tail cases. Use \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger} for the empty boundary, \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness} for singleton reads, \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger} for paired-family reads, and \autoref{thm:uniform-cauchy-criterion-family-tail-intersection} for nonempty subfamilies.

These four rows place every family-tail request on the same $I,W,M,Q,T$ route. They leave no coordinate for a separate indexwise modulus or a detached family-tail ledger.

Next handle transported requests by \autoref{thm:uniform-cauchy-criterion-finite-index-ledger-transport}. Transport can replay the displayed finite ledger through $H$ and $C$, but it cannot choose a new index carrier, window family, or external threshold schedule.

Now apply \autoref{thm:uniform-cauchy-criterion-shared-tail-ledger-coverage}. The empty, singleton, paired, and nonempty family reads are all covered by the shared tail ledger, so the transported case also reaches consumers through the same public package after its $H,C$ replay.

Finally use \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. Every $\RegSeqRatUp$ or $\RealUp$ consumer is exhausted by $I,W,M,Q,T,E,H,C,P,N$, and the seal boundary exports no indexwise moduli, selected family limits, quotient stream families, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[UniformCauchyCriterion tail-budget Real route]
\label{thm:uniform-cauchy-criterion-tail-budget-real-route}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every Real-facing or completion-facing read of $U$ factors first through the public route
$$
I,W,M,Q,T,E,H,C,P,N
$$
and then through the $\TailBudgetCoherenceUp$ public boundary for finite tail-budget handoffs. The consumer receives the finite index ledger, shared window family, single threshold row, dyadic tolerance row, tail ledger, Real seal row, transports, continuation routes, provenance, and local name; it receives no direct Real equality, quotient completion object, selected family limit, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:uniform-cauchy-criterion-late-overlap-exhaustion}. It sends every empty-family, singleton, paired-family, nonempty subfamily, and transported-family request to the same finite route $I,W,M,Q,T,E,H,C,P,N$ before the request can reach a $\RegSeqRatUp$ or $\RealUp$ consumer.

Next apply \autoref{thm:uniform-cauchy-criterion-shared-tail-ledger-coverage}. The tail row used by those consumers is the shared $T$ ledger reached through $I,W,M,Q$, so the route already has the finite tail-budget shape expected by the tail-budget handoff.

Finally use \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization} together with \autoref{thm:tail-budget-coherence-public-export-boundary}. The Real seal row $E$ is therefore read as a finite public tail-budget export, and every stronger Real or completion object would require a coordinate outside the displayed packet.
\end{proof}

\begin{theorem}[UniformCauchyCriterion shared-window nonescape]
\label{thm:uniform-cauchy-criterion-shared-window-nonescape}
For an accepted $\UniformCauchyCriterionUp$ packet $U=(I,W,M,Q,T,E,H,C,P,N)$, the shared-window and tail-budget route rules out any consumer escape to indexwise moduli, quotient stream families, selected family limits, host real equality, or ambient completeness. Every such attempted read is refused unless it is represented by the displayed finite rows $I,W,M,Q,T,E,H,C,P,N$ and then by the $\TailBudgetCoherenceUp$ public route.
\end{theorem}
\begin{proof}
The shared window is fixed by \autoref{thm:uniform-cauchy-criterion-shared-window-threshold-meet}. All later tolerance and tail requests inherit the single $W,M$ route.

Use \autoref{thm:uniform-cauchy-criterion-shared-tail-ledger-coverage} to place the empty, singleton, paired, and nonempty family reads on the same $I,W,M,Q,T$ ledger. No separate indexwise modulus family or quotient stream family is introduced in any case.

Now apply \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The Real seal and completion-facing reads are exhausted by $E,H,C,P,N$ over the same finite route.

The remaining excluded reads are exactly the stronger analytic objects denied by \autoref{thm:tail-budget-coherence-no-ambient-completeness-scope}. Thus the packet has no escape path to selected family limits, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[UniformCauchyCriterion completion consumer package]
\label{thm:uniform-cauchy-criterion-completion-consumer-package}
Every completion-facing consumer of an accepted $\UniformCauchyCriterionUp$ packet is packaged by the finite chain of sibling surfaces
$$
\StreamNameUp,\RegSeqRatUp,\DyadicRatCoreUp,\CauchyLimitSealUp,\TailBudgetCoherenceUp,\RealUp .
$$
The package reads the shared window, rational regular-sequence readback, dyadic tolerance row, limit-seal handoff, finite tail-budget coherence row, and Real-facing seal only through $I,W,M,Q,T,E,H,C,P,N$. It exports no quotient completion carrier, countable-choice selector, selected family limit, host real equality, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with the late-overlap theorem. By \autoref{thm:uniform-cauchy-criterion-late-overlap-exhaustion}, every family-tail or transported-family request reaching a completion consumer has already passed through the finite package $I,W,M,Q,T,E,H,C,P,N$.

Read the sibling rows in order. The shared window supplies the $\StreamNameUp$-style finite window, the rational readback supplies the $\RegSeqRatUp$ surface, the tolerance row supplies the $\DyadicRatCoreUp$ datum, and the seal row supplies the $\CauchyLimitSealUp$ handoff.

The public export boundary of \autoref{thm:tail-budget-coherence-public-export-boundary} then repackages these rows as the $\TailBudgetCoherenceUp$ route consumed by $\RealUp$.

Finally apply \autoref{thm:uniform-cauchy-criterion-shared-window-nonescape}. Since every consumer-facing row stays inside the same finite package, the excluded quotient, selector, limit, equality, and completeness objects have no exported coordinate.
\end{proof}

\begin{theorem}[UniformCauchyCriterion index restriction]
\label{thm:uniform-cauchy-criterion-index-restriction}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet, and let $J$ be a displayed finite subledger of $I$. The restricted family request over $J$ is accepted through the same route
$$
J \subseteq I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T \longmapsto E.
$$
It preserves the same shared window family, threshold schedule, dyadic tolerance row, tail ledger, and real-seal handoff, and it exports no selected limit, host equality, quotient stream, or ambient completeness datum.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:uniform-cauchy-criterion-subfamily-restriction}. A displayed subledger $J$ is read as a restriction of the finite index ledger $I$, so it has no independent family carrier.

Use \autoref{thm:uniform-cauchy-criterion-window-stability} and \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. The restricted request remains on the same shared window family $W$ and the same threshold schedule $M$ before it reaches any tolerance or tail comparison row.

Apply \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. The tail evidence for $J$ is exactly the displayed subledger of $T$ reached through $I,W,M,Q$.

Finally use \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The seal read is downstream of the same finite package, so the restricted packet cannot export selected limits, host equality, quotient streams, or ambient completeness.
\end{proof}
\leanvariant{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_subfamily\_restriction}

\begin{theorem}[UniformCauchyCriterion window refinement]
\label{thm:uniform-cauchy-criterion-window-refinement}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Suppose $W'$ is a transported $\StreamNameUp$ window refinement of $W$ along the displayed $\hsame$ row $H$ and displayed $\Cont$ routes $C$. Then the refined request is accepted through the same shared-threshold and dyadic-tail route $I,W,M,Q,T,E$, with $W'$ serving only as the transported presentation of the original window family.
\end{theorem}
\leanvariant{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_window\_refinement\_seal\_route}
\begin{proof}
Project the accepted carrier and the transported refinement. The refinement data are read through $H$ and $C$, so $W'$ is not a second window family but a transported presentation of the displayed $W$ row.

Apply \autoref{thm:uniform-cauchy-criterion-window-stability}. This keeps the refined $\StreamNameUp$ request inside the same finite window family over the index ledger $I$.

Next use \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. The threshold schedule remains the single row $M$, and the dyadic tolerance row $Q$ is reached only after that shared threshold route.

Apply \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness} and then \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The refined window request consumes the same tail ledger and seal handoff, so it cannot detach a new modulus family, selected limit, host equality, quotient stream, or ambient completeness claim.
\end{proof}

\begin{theorem}[UniformCauchyCriterion finite family union]
\label{thm:uniform-cauchy-criterion-family-union}
Let $U_J$ and $U_K$ be accepted $\UniformCauchyCriterionUp$ packets whose displayed subfamily ledgers $J$ and $K$ use the same shared window family $W$, threshold schedule $M$, dyadic tolerance row $Q$, tail ledger $T$, real-seal handoff $E$, and compatible finite index ledgers inside a common $\BHist$ packet. Then the finite union ledger $J\cup K$ is accepted as a $\UniformCauchyCriterionUp$ family read through the same $W,M,Q,T,E,H,C,P,N$ route.

The union packet is assembled only by finite ledger union and componentwise transport. It does not select pointwise limits, compare host reals, quotient stream names, or appeal to ambient completeness.
\end{theorem}
\begin{proof}
Read the two packets through their common displayed schedule and compatible finite ledgers. Compatibility means both subfamily requests already sit inside the same $\BHist$ inventory and do not supply separate threshold or tolerance coordinates.

Apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}. The paired-family ledger assembles $J\cup K$ as a finite union inside the existing index and tail ledgers.

Use \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport} and \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. These keep the union request on the same $W,M,Q,T$ route and force every tail comparison to be a displayed row of the shared ledger.

Finally apply \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. The real-seal consumer reads the same finite package after the union ledger is assembled, so selected limits, host equality, quotient streams, and ambient completeness have no coordinate through which to enter.
\end{proof}

\begin{theorem}[UniformCauchyCriterion shared window pullback]
\label{thm:uniform-cauchy-criterion-realup-regseqrat-shared-window-pullback}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Suppose $\UniformCauchyCriterionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RealUp$ seal consumers all read the displayed rows $I,W,M,Q,T,E,H,C,P,N$ of $U$. Then their consumer-visible packets form one finite pullback surface over the shared window row $W$, shared threshold row $M$, dyadic tolerance row $Q$, tail ledger $T$, and seal row $E$.

Equivalently, any two such consumers that agree on the displayed $\BMark$ and $\BHist$ routes $H,C$ have the same finite-window projection and the same seal-facing tail packet. No consumer can add a second stream-name family, RegSeqRat ledger, dyadic tolerance route, Real seal handoff, selected limit, host equality, quotient stream, or ambient completeness datum.
\end{theorem}
\begin{proof}
First fix the window surface. Apply \autoref{thm:uniform-cauchy-criterion-window-stability}: every $\StreamNameUp$ read of the accepted packet is already a read of the displayed family $W$ over the finite index ledger $I$.

Next fix the threshold and tail coordinates. Apply \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport} and \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. The route through $M,Q,T$ is therefore the single transported route determined by $H,C$.

Now pass to the consumer boundary. By \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}, every $\RegSeqRatUp$-visible read is exhausted by the same finite package $I,W,M,Q,T,E,H,C,P,N$. By \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}, the $\RealUp$ seal read factors through that package rather than through a separate completion object.

Finally use \autoref{thm:uniform-cauchy-criterion-window-refinement} for transported presentations and \autoref{thm:uniform-cauchy-criterion-family-union} for finite unions of compatible subledgers. These two closure operations preserve the same $W,M,Q,T,E,H,C$ surface, so the consumer-visible packets are glued only along their common displayed rows. That is precisely the finite pullback surface claimed above.
\end{proof}

\begin{theorem}[UniformCauchyCriterion overlap refinement determinacy]
\label{thm:uniform-cauchy-criterion-overlap-refinement-determinacy}
Let $U$ be an accepted $\UniformCauchyCriterionUp$ packet with displayed rows $I,W,M,Q,T,E,H,C,P,N$. If two refined window reads $W_1$ and $W_2$ overlap on a displayed finite subledger of $I$ and both refinements are transported through compatible $H,C$ routes, then the overlap determines the same tail ledger row $T$ and the same seal route $E$ for both reads.

Thus an overlapping refinement cannot expose two tail ledgers, two Real seal routes, or a detached RegSeqRat tolerance route over the common finite-window surface.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_overlap\_refinement\_determinacy}
\begin{proof}
Apply \autoref{thm:uniform-cauchy-criterion-window-refinement} to both refined reads. Each refinement is only a transported presentation of the same displayed window family $W$, so their overlap still lies over the finite index ledger $I$.

Use \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. Compatibility of the displayed $H,C$ routes forces both refined reads to reach the same threshold row $M$ and dyadic tolerance row $Q$ before any tail comparison is read.

Now apply \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. On the common subledger, the tail evidence is exactly the displayed restriction of $T$.

For the seal boundary, use \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. Since the seal row is downstream of the same finite package, the overlap has no coordinate from which a second seal route or detached tolerance route can be produced.
\end{proof}

\begin{theorem}[UniformCauchyCriterion seal route uniqueness]
\label{thm:uniform-cauchy-criterion-seal-route-uniqueness}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. A $\RealUp$ seal consumer of $U$ cannot obtain a second seal route from the same accepted packet: every seal-facing read factors through the displayed route
$$
I \longmapsto W \longmapsto M \longmapsto Q \longmapsto T \longmapsto E.
$$
The packet therefore has one consumer-visible seal handoff and no alternate handoff through selected limits, host real equality, quotient stream names, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_seal\_route\_uniqueness}
\begin{proof}
Start with \autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}. Any $\RealUp$ seal-facing consumer is exhausted by the displayed finite package $I,W,M,Q,T,E,H,C,P,N$.

Apply \autoref{thm:uniform-cauchy-criterion-shared-threshold-transport} and \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. These identify the only path from the window family to the tail ledger as $W,M,Q,T$.

Finally use \autoref{thm:uniform-cauchy-criterion-regseqrat-uniform-consumer-exhaustion}. The RegSeqRat-facing side also has no route outside the same finite package, so a second seal handoff would require a second visible row not present in $U$. Hence every seal read is the displayed route through $E$.
\end{proof}

\begin{theorem}[UniformCauchyCriterion late-boundary formal target packet]
\label{thm:uniform-cauchy-criterion-late-boundary-formal-target-packet}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ late-boundary packet. Suppose the empty-family tail ledger, paired-family union ledger, family-tail intersection, overlap-refinement determinacy, and seal-route uniqueness rows of $U$ are displayed. Then these rows assemble one finite consumer surface over $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyModulusUp$, $\DyadicTailBoundUp$, $\TailBudgetCoherenceUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Equivalently, every late-boundary consumer reads the same displayed package $I,W,M,Q,T,E,H,C,P,N$ before it reaches a family-tail, overlap, or Real-seal conclusion. The packet exports no second family ledger, detached tail budget, alternate overlap route, selected limit, quotient stream family, host equality, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_late\_boundary\_formal\_target\_packet}
\begin{proof}
First read the family endpoints. Apply \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger} for the empty-family boundary and \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger} for paired family reads. Both rows remain inside the displayed index, window, modulus, dyadic tail, and tail-budget ledger $I,W,M,Q,T$.

Next read the common tail surface. Apply \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}. Nonempty subfamilies meet the same displayed tail ledger, so the empty, paired, and intersected reads share one finite family-tail package.

Now attach the boundary route. Use \autoref{thm:uniform-cauchy-criterion-overlap-refinement-determinacy} to make overlapping refinements read the same $T$ row and seal route, and use \autoref{thm:uniform-cauchy-criterion-seal-route-uniqueness} to identify the Real-facing handoff as the displayed route through $E$.

The remaining rows $H,C,P,N$ are exactly the transport, continuation, package, and local naming coordinates of the same packet. Since the preceding rows already exhaust the family-tail, overlap, and seal boundaries, there is no carrier coordinate from which an additional consumer surface can be exported.
\end{proof}

\begin{theorem}[UniformCauchyCriterion diagonal-budget pullback]
\label{thm:uniform-cauchy-criterion-diagonal-budget-pullback}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ family packet, and let
$$
B=(\epsilon,M_B,W_B,D_B,K_B,S_B,H_B,C_B,P_B,N_B)
$$
be an accepted $\CauchyDiagonalBudgetUp$ packet. Suppose the displayed $\StreamNameUp$ window of $U$ agrees with $W_B$, the $\DyadicRatCoreUp$ tolerance ledger of $U$ agrees with $D_B$, the $\RegSeqRatUp$ readback row of $U$ agrees with $K_B$, and the $\RealUp$ seal boundary of $U$ agrees with $S_B$, all after the displayed $\hsame$ transports and $\Cont$ routes are replayed. Then every family-tail or completion-facing read of $U$ factors through the shared finite route
$$
\epsilon,M_B,W_B,D_B,K_B,S_B,H_B,C_B,P_B,N_B.
$$
The pullback adds no separate family limit, quotient stream family, host real equality, countable-choice schedule, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_diagonal\_budget\_pullback}
\begin{proof}
First identify the UniformCauchyCriterion side. The shared-window pullback theorem, \autoref{thm:uniform-cauchy-criterion-realup-regseqrat-shared-window-pullback}, makes the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ consumers of $U$ read the same finite $W,M,Q,T,E,H,C,P,N$ surface.

Next close the seal route inside $U$. Apply seal-route uniqueness, \autoref{thm:uniform-cauchy-criterion-seal-route-uniqueness}, and the late-boundary formal target packet, \autoref{thm:uniform-cauchy-criterion-late-boundary-formal-target-packet}. They force every family-tail, overlap, or Real-seal consumer to pass through the displayed family packet before it reaches a completion-facing conclusion.

Now compare with the diagonal budget. The componentwise agreement hypotheses identify the shared window, tolerance ledger, RegSeqRat readback row, and Real seal boundary with $W_B,D_B,K_B,S_B$. The Cauchy diagonal budget route theorem, \autoref{thm:cauchy-diagonal-budget-uniform-criterion-budget-route}, and limit-seal eligibility, \autoref{thm:cauchy-diagonal-budget-limit-seal-eligibility}, then place the same consumer behind $\epsilon,M_B,W_B,D_B,K_B,S_B,H_B,C_B,P_B,N_B$.

Since both packets expose only displayed transport, continuation, provenance, and local naming rows, the common pullback leaves no coordinate for a separate family limit, quotient stream family, host real equality, countable-choice schedule, or ambient completeness principle.
\end{proof}

\begin{theorem}[UniformCauchyCriterion paired-overlap real seal determinacy]
\label{thm:uniform-cauchy-criterion-paired-overlap-real-seal-determinacy}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Suppose the paired-family union row, family-tail intersection row, overlap-refinement determinacy row, seal-route uniqueness row, and diagonal-budget pullback row are displayed for $U$. Then every paired-overlap $\RealUp$-facing consumer factors through one finite route over
$$
I,W,M,Q,T,E,H,C,P,N
$$
and through the shared $\CauchyDiagonalBudgetUp$ route determined by the diagonal-budget pullback.

Thus the consumer-visible handoff is the same finite family-tail, overlap, seal, and diagonal-budget surface. It exports no second family limit, quotient stream family, host real equality, countable-choice schedule, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_paired\_overlap\_real\_seal\_determinacy}
\begin{proof}
First assemble the finite paired-family surface. Apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger}; the two family requests are read as one finite union ledger inside the displayed index, window, modulus, dyadic tolerance, and tail rows.

Next force the overlap to remain on that surface. Apply \autoref{thm:uniform-cauchy-criterion-family-tail-intersection} and \autoref{thm:uniform-cauchy-criterion-overlap-refinement-determinacy}. The common tail evidence is the displayed restriction of $T$, and every overlapping refinement reads the same seal-facing route.

Now close the Real-facing boundary. Apply \autoref{thm:uniform-cauchy-criterion-seal-route-uniqueness}. Any $\RealUp$ consumer of the paired-overlap packet must pass through the displayed handoff $E$ after reading the same $I,W,M,Q,T,H,C,P,N$ rows.

Finally transport the result to the shared diagonal-budget route by \autoref{thm:uniform-cauchy-criterion-diagonal-budget-pullback}. The diagonal route identifies the compatible window, tolerance, readback, and seal coordinates, so the paired-overlap consumer has no coordinate from which to export a second family limit, quotient stream family, host equality, countable-choice schedule, or ambient completeness datum.
\end{proof}

\begin{theorem}[UniformCauchyCriterion late-boundary no-choice exhaustion]
\label{thm:uniform-cauchy-criterion-late-boundary-nochoice-exhaustion}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every empty-family, singleton, paired-family, nonempty subfamily, overlap-refinement, or diagonal-budget $\RealUp$-seal consumer of $U$ factors through the same finite rows
$$
I,W,M,Q,T,E,H,C,P,N
$$
and, when a $\CauchyDiagonalBudgetUp$ packet is displayed, through the corresponding diagonal route
$$
\epsilon,M_B,W_B,D_B,K_B,S_B,H_B,C_B,P_B,N_B.
$$

Thus the late boundary has one consumer-visible family-tail, overlap, seal, and diagonal-budget surface. It exports no countable-choice schedule, selected family limit, quotient stream family, host real equality, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_late\_boundary\_nochoice\_exhaustion}
\begin{proof}
First exhaust the family-tail cases inside the displayed packet. Apply \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger} for the empty-family boundary and \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness} for singleton reads. These cases use only the displayed index ledger, window row, threshold row, dyadic tolerance row, and tail ledger.

For finite family combinations, apply \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger} and \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}. Paired-family and nonempty subfamily consumers are assembled by finite ledger union or finite tail intersection inside $I,W,M,Q,T$, so they cannot supply an indexwise schedule or a separate family-limit coordinate.

Next close the overlap and seal boundary. Use \autoref{thm:uniform-cauchy-criterion-overlap-refinement-determinacy} to force overlapping refinements to read the same tail ledger row and Real-facing route, and use \autoref{thm:uniform-cauchy-criterion-seal-route-uniqueness} to identify every seal-facing read with the displayed handoff through $E$.

When a diagonal budget is present, apply \autoref{thm:uniform-cauchy-criterion-diagonal-budget-pullback}. The compatible window, tolerance, RegSeqRat readback, and Real seal coordinates are then read through $\epsilon,M_B,W_B,D_B,K_B,S_B,H_B,C_B,P_B,N_B$, not through a second completion-facing object.

Finally apply \autoref{thm:uniform-cauchy-criterion-paired-overlap-real-seal-determinacy}. The rows $H,C,P,N$ provide only transport, continuation, provenance, and local naming for the same finite route. The carrier inventory therefore contains no coordinate from which a countable-choice schedule, selected family limit, quotient stream family, host equality, or ambient completeness datum can escape.
\end{proof}

\begin{theorem}[UniformCauchyCriterion late-overlap route exhaustion]
\label{thm:uniform-cauchy-criterion-late-overlap-route-exhaustion}
Let
$$
U=(I,W,M,Q,T,E,H,C,P,N)
$$
be an accepted $\UniformCauchyCriterionUp$ packet. Every empty-family, singleton, paired-family, nonempty-subfamily, overlap-refinement, diagonal-budget, $\CauchyLimitSealUp$, or $\RealUp$-seal consumer of $U$ is routed through the same finite surface
$$
I,W,M,Q,T,E,H,C,P,N.
$$
When a diagonal budget is displayed, the same consumer also factors through the shared pullback route
$$
\epsilon,M_B,W_B,D_B,K_B,S_B,H_B,C_B,P_B,N_B.
$$
Thus paired-overlap, diagonal-budget, CauchyLimitSeal, and RealUp consumers have one late-boundary route and no separate family limit, quotient stream family, host real equality, countable-choice schedule, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
First exhaust the elementary family cases. Apply \autoref{thm:uniform-cauchy-criterion-empty-family-tail-ledger} and \autoref{thm:uniform-cauchy-criterion-single-member-restriction-exactness} for empty-family and singleton reads; both remain inside the displayed $I,W,M,Q,T$ rows.

Next assemble finite family consumers. Use \autoref{thm:uniform-cauchy-criterion-paired-family-union-ledger} and \autoref{thm:uniform-cauchy-criterion-family-tail-intersection}. Paired-family and nonempty-subfamily reads are finite union and intersection routes over the same index, window, modulus, tolerance, and tail surface.

Now close the overlap and seal route. Apply \autoref{thm:uniform-cauchy-criterion-overlap-refinement-determinacy} and \autoref{thm:uniform-cauchy-criterion-seal-route-uniqueness}. Overlap refinements, CauchyLimitSeal consumers, and RealUp-seal consumers must pass through the displayed handoff row $E$ with support from $H,C,P,N$.

When a diagonal budget is present, apply \autoref{thm:uniform-cauchy-criterion-diagonal-budget-pullback}. The compatible window, dyadic tolerance ledger, RegSeqRat readback, and Real seal are then read through $\epsilon,M_B,W_B,D_B,K_B,S_B,H_B,C_B,P_B,N_B$ rather than through an additional completion object.

Finally combine \autoref{thm:uniform-cauchy-criterion-paired-overlap-real-seal-determinacy} with \autoref{thm:uniform-cauchy-criterion-late-boundary-nochoice-exhaustion}. The first theorem identifies paired-overlap Real-seal consumers with the diagonal-budget pullback, and the second theorem exhausts all late-boundary no-choice consumers. Hence every listed consumer uses the same finite route and exports no separate family limit, quotient stream family, host real equality, countable-choice schedule, or ambient completeness coordinate.
\end{proof}
\leanchecked{BEDC.Derived.UniformCauchyCriterionUp.UniformCauchyCriterionPacket\_late\_overlap\_route\_exhaustion}
