\section{Terminal history field instance}
\label{sec:field-terminal-history-instance}

\begin{definition}[Terminal history FieldUp instance]
\label{def:field-terminal-history-field-instance}
The terminal history $\FieldUp$ instance is the concrete $\mathsf{BHist}$
tuple
$$
\mathcal F_{\emp}:=
(A_{\emp},R_{\emp},+_{\emp},-_{\emp},0_{\emp},\cdot_{\emp},1_{\emp},
N_{\emp},(\ )^{-1}_{\emp})
$$
with carrier
$$
A_{\emp}(h):= h\hsame\emp
$$
and classifier
$$
R_{\emp}(h,k):=A_{\emp}(h)\land A_{\emp}(k).
$$
The additive and multiplicative endpoints are the same terminal append rows:
$$
h+_{\emp}k:=\mathsf{append}(h,k),\qquad
h\cdot_{\emp}k:=\mathsf{append}(h,k),
$$
with $-_{\emp}h:=\emp$, $0_{\emp}:=\emp$, and $1_{\emp}:=\emp$. The inverse
operation is defined only on the displayed nonzero boundary row:
$$
h^{-1}_{\emp}:=\emp
$$
whenever the unit-boundary certificate $N_{\emp}(h)$ is present. The predicate
$N_{\emp}$ has no public rows except the certified unit endpoint over
$\emp$, and that endpoint is carried with its $\hsame$, $\Cont$, and $\Pkg$
provenance.
\end{definition}

\begin{theorem}[Terminal history FieldUp laws]
\label{thm:field-terminal-history-field-laws}
The tuple $\mathcal F_{\emp}$ of
\autoref{def:field-terminal-history-field-instance} satisfies the displayed
$\FieldUp$ laws: the $\RingUp$ laws, commutative multiplication, unit laws,
distributivity, and the inverse law on the stated unit-boundary nonzero row.
Every carried endpoint appearing in these laws reduces through $R_{\emp}$ to
the terminal history $\emp$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:ringup-public-singleton-operation-surface}. It supplies the
singleton carrier $A_{\emp}$, classifier $R_{\emp}$, displayed addition,
negation, zero, multiplication, one, distributivity, and operation ledger over
the same terminal $\mathsf{BHist}$ endpoint.

The commutative multiplication and unit rows are the singleton public rows of
\autoref{thm:commring-singleton-public-operation-surface}, read with the same
carrier and classifier. Since $1_{\emp}$ is $\emp$, both left and right unit
checks reduce to the terminal endpoint.

For the inverse row, project the displayed nonzero boundary certificate. Its
only public endpoint is the unit row over $\emp$, and the inverse endpoint is
defined as $\emp$. Therefore
$(h^{-1}_{\emp}\cdot_{\emp} h)$ and $(h\cdot_{\emp} h^{-1}_{\emp})$ are both
classified by $R_{\emp}$ against $1_{\emp}$.

No further case remains: every operation in the tuple either returns
$\emp$ directly or appends carried endpoints already classified with $\emp$,
and the singleton append rows read those append endpoints back to the same
terminal carrier.
\end{proof}

\begin{theorem}[Terminal history FieldUp schema laws]
\label{thm:field-terminal-history-schema-laws}
The terminal history instance $\mathcal F_{\emp}$ supplies the $\FieldUp$
schema surface: the carrier $A_{\emp}$ carries a semantic certificate, the
empty endpoint cannot be a displayed nonzero row, nonzero rows transport along
$R_{\emp}$, the inverse endpoint remains in the carrier, inverse endpoints are
congruent under $R_{\emp}$, and both products
$h^{-1}_{\emp}\cdot_{\emp}h$ and $h\cdot_{\emp}h^{-1}_{\emp}$ classify
against $1_{\emp}$ whenever the displayed nonzero boundary row for $h$ is
present.
\end{theorem}
\begin{proof}
Read the carrier and classifier from
\autoref{def:field-terminal-history-field-instance}. The carrier is the
terminal $\hsame$ row against $\emp$, so the singleton endpoint reduction used
in \autoref{thm:field-terminal-history-field-laws} gives the semantic
certificate and all classifier transports.

The displayed nonzero predicate has no row over the empty endpoint except the
certified unit-boundary endpoint, and that endpoint reduces to the same
terminal carrier. Hence the empty endpoint is not a separate nonzero object,
and transporting a nonzero row across $R_{\emp}$ keeps the same displayed
boundary data.

Finally, the inverse operation always returns $\emp$. By
\autoref{thm:field-terminal-history-field-laws}, both inverse-product rows
therefore reduce through the singleton classifier to $1_{\emp}=\emp$, and the
same terminal reduction proves inverse carrier closure and inverse classifier
congruence.
\end{proof}

\begin{theorem}[Terminal FieldUp nonzero boundary]
\label{thm:field-terminal-nonzero-boundary}
Any $\FieldUp$ inverse consumer of
\autoref{def:field-terminal-history-field-instance} may read only the singleton
unit/nonzero row, the carrier classifier $A_{\emp}$, the terminal classifier
$R_{\emp}$, the displayed $\hsame$ witnesses, finite $\Cont$ provenance, and
$\Pkg$ provenance. It receives no host field, quotient of nonzero elements, or
external inverse object.
\end{theorem}
\begin{proof}
Unpack the terminal tuple. The carrier and classifier expose only histories
classified with $\emp$, and the operation rows are the displayed empty endpoint
or append endpoints already governed by the singleton public operation
surface.

The inverse row is indexed by $N_{\emp}$, whose public boundary is the
certified unit endpoint. Projecting that boundary gives exactly the
$\hsame$, $\Cont$, and $\Pkg$ rows attached to the same terminal history.

Thus a consumer can form inverse statements only by using the displayed
unit-boundary certificate and the singleton classifier. There is no exported
row from which a host field, a quotient carrier of nonzero elements, or an
external inverse operation could be read.
\end{proof}

\begin{theorem}[Terminal FieldUp history scope package]
\label{thm:field-terminal-history-scope-package}
The terminal $\FieldUp$ carrier of
\autoref{def:field-terminal-history-field-instance} is a one-endpoint
$\mathsf{BHist}$ scope packet. Every admitted carrier row is classified by
$A_{\emp}$ against $\emp$, every classifier comparison factors through
$R_{\emp}$, and every visible dependency is one of the displayed $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows already attached to the terminal
endpoint.
\end{theorem}
\begin{proof}
Project the terminal tuple and use
\autoref{thm:field-terminal-history-field-laws}. The carrier is the singleton
history endpoint, and all additive, multiplicative, zero, unit, and inverse
rows reduce back to $\emp$ through the same classifier.

Apply \autoref{thm:field-terminal-history-schema-laws}. It identifies the
schema-facing rows with the displayed terminal carrier, classifier transport,
and nonzero boundary, so no second history endpoint can enter the scope.

The remaining route data are exactly the $\hsame$ witnesses, finite $\Cont$
provenance, $\Pkg$ provenance, and local naming certificate already listed in
\autoref{thm:field-terminal-nonzero-boundary}. Thus the terminal carrier is a
closed one-endpoint history scope packet.
\end{proof}

\begin{theorem}[Terminal FieldUp inverse ledger scope]
\label{thm:field-terminal-inverse-ledger-scope}
In the terminal $\FieldUp$ packet, every inverse row and every apart-zero row is
exhausted by the unit-boundary witness $N_{\emp}$ and its transport through
$R_{\emp}$. The inverse ledger exposes no nonterminal nonzero carrier, no
quotient of invertible elements, and no inverse operation outside the singleton
$\mathsf{BHist}$ endpoint.
\end{theorem}
\begin{proof}
Start with the nonzero boundary row of
\autoref{thm:field-terminal-nonzero-boundary}. It says that an inverse consumer
can read only the unit/nonzero row at $\emp$ together with the carrier and
classifier rows of the terminal tuple.

Use \autoref{thm:field-terminal-history-schema-laws} to transport that row
along $R_{\emp}$. The transported nonzero datum remains the same displayed
unit-boundary certificate, and the inverse endpoint is again $\emp$.

Finally apply \autoref{thm:field-terminal-history-field-laws}. The inverse
products classify against $1_{\emp}$ by the singleton law surface, so every
inverse and apart-zero ledger row has already been consumed by the terminal
witness.
\end{proof}

\begin{theorem}[Terminal FieldUp RatUp exit handoff]
\label{thm:field-terminal-ratup-fieldup-exit-handoff}
The terminal history packet hands off from the existing $\RatUp$ and
$\FieldUp$ exit surface by the same singleton $\mathsf{BHist}$ endpoint:
carrier admission, classifier transport, inverse use, apart-zero use, and
consumer exit all factor through $\emp$, $A_{\emp}$, $R_{\emp}$, the displayed
$\hsame$ and $\Cont$ rows, the $\Pkg$ row, and the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Read the exit-facing surface through the terminal carrier of
\autoref{def:field-terminal-history-field-instance}. The carrier and
classifier rows are the same singleton rows used by the terminal $\RatUp$ and
$\FieldUp$ public operation packets.

Apply \autoref{thm:field-terminal-history-scope-package} for carrier and
classifier scope, then apply
\autoref{thm:field-terminal-inverse-ledger-scope} for the inverse and
apart-zero ledger rows. These two scope statements cover the rows a consumer
can inspect before leaving the terminal field packet.

Thus the exit handoff is not an external field construction. It is the existing
singleton history endpoint with its recorded $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ transport data.
\end{proof}
