\section{Rat denominator external-unit envelope cancellation exactness}
\label{sec:field-rat-denominator-unit-envelope-cancellation-exactness}

\begin{theorem}[Rat denominator external-unit envelope cancellation exactness]
\label{thm:field-rat-denominator-unit-envelope-cancellation-exactness}
For the tuple $(C_D^\ast,R_D^\ast,\mu_D^\ast,e_D^\ast)$ of
\autoref{def:field-rat-denominator-unit-envelope} and the strict support
predicate $N_D^\ast$ of
\autoref{def:field-rat-denominator-unit-envelope-strict-support}, strict
common factors cancel exactly at the envelope classifier. For histories
$h,k,t:\mathsf{BHist}$, if $C_D^\ast(h)$, $C_D^\ast(k)$, $C_D^\ast(t)$, and
$N_D^\ast(t)$, then
$$
R_D^\ast(\mu_D^\ast(h,t),\mu_D^\ast(k,t))
\Longleftrightarrow R_D^\ast(h,k),
$$
and
$$
R_D^\ast(\mu_D^\ast(t,h),\mu_D^\ast(t,k))
\Longleftrightarrow R_D^\ast(h,k).
$$
\end{theorem}
\begin{proof}
Unfold the envelope tuple and the strict support predicate. The hypothesis
$N_D^\ast(t)$ identifies the common factor as a genuine
$\mathsf{RatHistoryCarrier}$ endpoint, so multiplication by $t$ remains in the
carried Rat denominator branch after applying the append continuation closure
used by the envelope laws.

For the forward right-cancellation direction, split the carrier witnesses for
$h$ and $k$ into carried denominator and external empty branches.

In the carried/carried branch, all three factors lie in
$\mathsf{RatDenomUnitCarrier}$, and the displayed envelope classifier is read
as the corresponding empty-unit classifier by
\autoref{thm:field-rat-denominator-unit-envelope-carried-classifier-exactness}.
Apply
\autoref{thm:field-rat-denominator-empty-unit-cancellative-commutative-monoid-package}
to cancel the strict common factor. The resulting carried denominator
classifier is then packed back into $R_D^\ast(h,k)$ through the carried branch
of the envelope classifier.

In a mixed branch, one of $h$ and $k$ is external while the other is carried.
Because $t$ has strict support, the product on the carried side has a
$\mathsf{RatHistoryCarrier}$ witness, while the product on the external side is
classified with the same carried continuation only through a mixed
external-carried alternative. The classifier normal form and
\autoref{thm:field-rat-denominator-unit-envelope-classifier-exactness}, together
with $\mathsf{RatHistoryCarrier\_not\_empty}$, rule out such a product
classifier. Hence the antecedent of the forward implication cannot hold in the
mixed cases.

In the external/external branch, both $h$ and $k$ are classified with
$e_D^\ast=\emp$. The two products are classified with the common carried
continuation of $t$ by the one-sided unit laws, and the conclusion
$R_D^\ast(h,k)$ is the empty branch of the envelope classifier.

The forward left-cancellation direction is the same case split with the common
strict factor placed on the left. The carried/carried case uses the left
cancellation field of
\autoref{thm:field-rat-denominator-empty-unit-cancellative-commutative-monoid-package};
the mixed cases are excluded by the same classifier exactness and
$\mathsf{RatHistoryCarrier\_not\_empty}$ argument; the external/external case
packs the empty branch directly.

For the reverse directions, assume $R_D^\ast(h,k)$. The carrier hypothesis on
$t$ gives reflexivity $R_D^\ast(t,t)$, and the multiplication congruence field
of
\autoref{thm:field-rat-denominator-unit-envelope-commutative-monoid-laws}
combines $R_D^\ast(h,k)$ with this reflexive common factor. Placing the
reflexive factor on the right gives
$R_D^\ast(\mu_D^\ast(h,t),\mu_D^\ast(k,t))$; placing it on the left gives
$R_D^\ast(\mu_D^\ast(t,h),\mu_D^\ast(t,k))$.
\end{proof}
\leanchecked{BEDC.Derived.FieldUp.field\_rat\_denominator\_unit\_envelope\_cancellation\_exactness}

\textbf{Traditional target}: cancellative denominator envelope for
$\FieldUp(\mathsf{RatUp})$; \textbf{BEDC source}: $\mathsf{BHist}$,
$\mathsf{RatHistoryCarrier}$, $\mathsf{RatDenomUnitCarrier}$,
$\mathsf{RatDenomUnitClassifier}$, $\Cont$, and $\mathsf{append}$;
\textbf{carrier}: $C_D^\ast$; \textbf{classifier}: $R_D^\ast$;
\textbf{multiplication}: $\mu_D^\ast$; \textbf{unit}: $e_D^\ast$;
\textbf{ledger}: external-unit bit plus common denominator continuation
witness; \textbf{core theorem}:
\autoref{thm:field-rat-denominator-unit-envelope-cancellation-exactness};
\textbf{exactness predicate}: strict-factor cancellation; \textbf{standard
bridge}: ordinary denominator cancellation; \textbf{status}:
$\mathsf{LeanChecked}$.
