\section{Field affine explicit inverse}
\label{sec:field-affine-explicit-inverse}

\begin{theorem}[Field two-sided affine expression has explicit inverse]
\label{thm:field-affine-two-sided-explicit-inverse}
For a BEDC history-level $\FieldUp$ candidate with the same operations,
additive laws, multiplication laws, congruence data, and indexed inverse laws
as in
\autoref{thm:field-affine-two-sided-equation-exact-from-apartness}, let
$p_a:\mathsf{NonZero}_F(a)$ and $p_b:\mathsf{NonZero}_F(b)$ be the two
nonzero witnesses for the left and right affine factors. For each
$c:\mathsf{BHist}$ define
$$
s(c)=
\mathsf{mul}(\mathsf{inv}(a,p_a),
\mathsf{mul}(\mathsf{add}(c,\mathsf{neg}(d)),\mathsf{inv}(b,p_b))).
$$
Then every $c,x,y:\mathsf{BHist}$ satisfies the following three clauses.
\begin{enumerate}
\item $\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,s(c)),b),d)\hsame c$.
\item If
$\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,x),b),d)\hsame c$, then
$x\hsame s(c)$.
\item If
$$
\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,x),b),d)\hsame
\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,y),b),d),
$$
then $x\hsame y$.
\end{enumerate}
\end{theorem}
\begin{proof}
For the displayed preimage, instantiate
\autoref{thm:field-affine-two-sided-equation-exact-from-apartness} at
$x=s(c)$. The reverse implication only needs the reflexive classifier
equality $s(c)\hsame s(c)$, so it produces
$\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,s(c)),b),d)\hsame c$.

For uniqueness of any solution, use the forward implication of the same
exactness theorem. An assumed classification of the affine expression at
$x$ with $c$ is transported directly to $x\hsame s(c)$.

For equality of two affine expressions, apply
\autoref{thm:field-affine-two-sided-map-classifier-exact-from-apartness} to the
assumed classifier equality. Its conclusion is exactly $x\hsame y$.
\end{proof}

\begin{theorem}[Field equal-squares signed factors cannot both be nonzero]
\label{thm:field-equal-squares-signed-factors-not-both-nonzero}
For a BEDC history-level $\FieldUp$ candidate with the hypotheses of
\autoref{thm:field-equal-squares-signed-factor-exclusion} and
\autoref{thm:field-nonzero-factors-exclude-zero-product}, every
$a,b:\mathsf{BHist}$ satisfies
$$
a\cdot a\hsame b\cdot b
\quad\Longrightarrow\quad
\mathsf{NonZero}_F(a+b)\to
\mathsf{NonZero}_F(a+(-b))\to\mathsf{False}.
$$
The traditional target is constructive signed-factor square reasoning; the
BEDC source is $\FieldUp$ together with $\CommRingUp$; the carrier is
$\mathsf{BHist}$; the classifier is $\hsame$; the ledger consists of the two
explicit signed-factor nonzero witnesses; the core theorem is this block; the
exactness predicate is impossibility of simultaneous nonzero signed factors
under equal squares; the status is $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Assume $a\cdot a\hsame b\cdot b$ and witnesses
$p_+:\mathsf{NonZero}_F(a+b)$ and
$p_-:\mathsf{NonZero}_F(a+(-b))$.

First apply \autoref{thm:commring-difference-of-squares-zero-exact} to the
square equality. The signed-factor product is classified as zero:
$$
(a+b)\cdot(a+(-b))\hsame0.
$$

Now apply \autoref{thm:field-nonzero-factors-exclude-zero-product} to the two
nonzero witnesses $p_+$ and $p_-$ together with this displayed zero product.
That theorem says that such a zero product is impossible when both factors are
explicitly nonzero, so the assumed pair of signed-factor witnesses yields
$\mathsf{False}$.
\end{proof}
\leanchecked{BEDC.Derived.FieldUp.field\_equal\_squares\_signed\_factors\_not\_both\_nonzero}

\begin{theorem}[Field affine two-sided equation solutions are unique from apartness]
\label{thm:field-affine-two-sided-equation-solution-unique-from-apartness}
For a BEDC history-level $\FieldUp$ candidate with operations
$\mathsf{add},\mathsf{mul},\mathsf{neg},\mathsf{zero},\mathsf{one}$ on
$\mathsf{BHist}$, additive group laws for
$\mathsf{add},\mathsf{neg},\mathsf{zero}$, addition congruence,
multiplication associativity, left and right multiplicative identity laws,
multiplication congruence, and indexed inverse laws for witnesses
$p_a:\mathsf{NonZero}_F(a)$ and $p_b:\mathsf{NonZero}_F(b)$, every
$x,y,d,c:\mathsf{BHist}$ satisfies
$$
\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,x),b),d)\hsame c
\quad\Longrightarrow\quad
\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,y),b),d)\hsame c
\quad\Longrightarrow\quad
x\hsame y.
$$
\end{theorem}
\begin{proof}
Assume the two displayed affine equations. Use symmetry of the second equation
and transitivity of $\hsame$ to compose the first equation with it. This gives
the classifier equality between the two affine outputs:
$$
\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,x),b),d)\hsame
\mathsf{add}(\mathsf{mul}(\mathsf{mul}(a,y),b),d).
$$

Apply \autoref{thm:field-affine-two-sided-map-classifier-exact-from-apartness}
with the same certified nonzero factors $p_a,p_b$ and offset $d$. The affine
classifier exactness theorem removes the shared affine map and yields
$x\hsame y$.
\end{proof}

Per-object certificate: Traditional target: affine equation uniqueness. BEDC
source: $\FieldUp$ over $\mathsf{BHist}$ plus additive group laws. Carrier
choice: $\mathsf{BHist}$. Classifier choice: $\hsame$. Stability obligations:
the operations and laws required by affine two-sided injectivity. Ledger: the
two certified factors and offset. Core theorem list entry:
Theorem~\ref{thm:field-affine-two-sided-equation-solution-unique-from-apartness}.
Exactness predicate: two certified solutions of the same affine equation are
classified equal. Standard bridge and downstream use: canonical solution
extraction for FieldUp equation solving. Status: $\mathsf{ProofTarget}$.
