\begin{theorem}[Rat denominator unit carrier zero-headed absurd]
\label{thm:rat-denom-unit-carrier-e0-absurd}
For every tail $t:\mathsf{BHist}$, the empty-unit denominator carrier cannot
hold on a zero-headed history:
$$
\mathsf{RatDenomUnitCarrier}(\Ezero(t))\Longrightarrow \bot.
$$
\end{theorem}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitCarrier\_e0\_absurd}
\begin{proof}
Unfold the empty-unit denominator carrier. Its empty-endpoint branch would make
$\Ezero(t)$ equal to $\emp$, contradicting constructor disjointness. Its Rat
branch is impossible because the Rat denominator carrier has no zero-headed
inhabitant.
\end{proof}

\begin{theorem}[Rat denominator unit classifier empty endpoint iff]
\label{thm:rat-denom-unit-classifier-empty-endpoint-iff}
For every history $h:\mathsf{BHist}$, the empty-unit denominator classifier
against the empty endpoint records exactly the displayed empty endpoint
comparison, on either side:
$$
\mathsf{RatDenomUnitClassifier}(\emp,h)\Longleftrightarrow h\hsame\emp,
\qquad
\mathsf{RatDenomUnitClassifier}(h,\emp)\Longleftrightarrow h\hsame\emp.
$$
\end{theorem}
\begin{proof}
Unfold the classifier into its two carrier fields and its endpoint sameness
field. In the forward directions, the endpoint field gives the desired
comparison, using symmetry for the left endpoint placement. In the reverse
directions, the displayed empty comparison supplies the nonempty endpoint
carrier by the empty branch, while the empty endpoint itself uses reflexivity.
\end{proof}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitClassifier\_empty\_endpoint\_iff}

\begin{theorem}[Rat denominator unit carrier append zero-headed absurd]
\label{thm:rat-denom-unit-carrier-append-e0-absurd}
For histories $h,k,tail:\mathsf{BHist}$, two empty-unit denominator carrier
witnesses cannot have a product classified with a zero-headed endpoint:
$$
\mathsf{RatDenomUnitCarrier}(h)\to
\mathsf{RatDenomUnitCarrier}(k)\to
\mathsf{append}(h,k)\hsame\Ezero(tail)\to\bot.
$$
\end{theorem}
\begin{proof}
Closure of $\mathsf{RatDenomUnitCarrier}$ under continuation gives a carrier
witness for $\mathsf{append}(h,k)$. Transport this carrier witness along the
displayed endpoint sameness to obtain
$\mathsf{RatDenomUnitCarrier}(\Ezero(tail))$, contradicting the zero-headed
absurdity theorem above.
\end{proof}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitCarrier\_append\_e0\_absurd}

\begin{theorem}[Rat denominator unit carrier append one-headed result cases]
\label{thm:rat-denom-unit-carrier-append-e1-result-cases}
For histories \(h,k,tail:\mathsf{BHist}\), if \(h\) and \(k\) are carried by
the empty-unit denominator carrier and their append is one-headed, then either
the right factor is empty and the left factor accounts for the one-headed
result, or the right factor itself is one-headed with a unary exposed tail:
$$
\begin{aligned}
&\mathsf{RatDenomUnitCarrier}(h)\to
\mathsf{RatDenomUnitCarrier}(k)\to
\mathsf{append}(h,k)\hsame\Eone(tail)\\
&\quad\to
\left(k\hsame\emp\land
  \mathsf{RatDenomUnitCarrier}(\Eone(tail))\land h\hsame\Eone(tail)\right)\\
&\qquad{}\lor
\exists k_0:\mathsf{BHist}.\;
  k=\Eone(k_0)\land\mathsf{UnaryHistory}(k_0)\land
  \mathsf{RatDenomUnitCarrier}(tail)\land\Cont(h,k_0,tail).
\end{aligned}
$$
\end{theorem}
\begin{proof}
Read the append comparison as a continuation into a one-headed result and
apply the continuation one-headed-result inversion. The empty-right branch
closes the displayed one-headed carrier by denominator-unit continuation
closure. In the headed-right branch, the carrier on \(k=\Eone(k_0)\) gives a
unary witness for \(k_0\); visible carrier cases make \(k_0\) carried, and
continuation closure then carries the exposed tail.
\end{proof}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitCarrier\_append\_e1\_result\_cases}

\begin{theorem}[Rat denominator unit carrier one-headed unary iff]
\label{thm:field-rat-denom-unit-carrier-one-headed-unary-iff}
For every tail $t:\mathsf{BHist}$, the empty-unit denominator carrier sees a
one-headed history exactly when the tail is unary:
$$
\mathsf{RatDenomUnitCarrier}(\Eone(t))
\Longleftrightarrow
\mathsf{UnaryHistory}(t).
$$
\end{theorem}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitCarrier\_e1\_tail\_unary\_iff}
\begin{proof}
Unfold the empty-unit denominator carrier. Its empty-endpoint branch would give
$\Eone(t)\hsame\emp$, contradicting constructor disjointness. The remaining
branch is $\mathsf{RatHistoryCarrier}(\Eone(t))$, which is equivalent to
$\mathsf{UnaryHistory}(t)$ by the one-headed Rat carrier characterization.
\end{proof}

\begin{theorem}[Rat denominator unit classifier one-headed tail iff]
\label{thm:rat-denom-unit-classifier-e1-tail-iff}
For histories $d,e:\mathsf{BHist}$, the empty-unit denominator classifier on
two one-headed histories is exactly the pair of unary tail witnesses together
with tail sameness:
$$
\mathsf{RatDenomUnitClassifier}(\Eone(d),\Eone(e))
\Longleftrightarrow
\mathsf{UnaryHistory}(d)\wedge
\mathsf{UnaryHistory}(e)\wedge d\hsame e.
$$
\end{theorem}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitClassifier\_e1\_tail\_iff}
\begin{proof}
Unfold the classifier into its two empty-unit carrier fields and the endpoint
sameness field. Each carrier field is converted by the one-headed carrier
characterization above, and the endpoint sameness field is converted by
constructor injectivity for $\Eone$.
\end{proof}

\begin{theorem}[Rat denominator unit classifier displayed context one-tail readback]
\label{thm:rat-denom-unit-classifier-cont-context-e1-pair-readback}
Let $d,e,p_d,p_e,t_d,t_e,m_d,m_e,out_d,out_e,a,b:\mathsf{BHist}$. If
$\mathsf{RatDenomUnitClassifier}(d,e)$,
$\mathsf{RatDenomUnitClassifier}(p_d,p_e)$, and
$\mathsf{RatDenomUnitClassifier}(t_d,t_e)$ hold, and the displayed
continuations
$\mathsf{Cont}(p_d,d,m_d)$, $\mathsf{Cont}(m_d,t_d,out_d)$,
$\mathsf{Cont}(p_e,e,m_e)$, and $\mathsf{Cont}(m_e,t_e,out_e)$ expose
contextual endpoints satisfying $\hsame(out_d,\Eone(a))$ and
$\hsame(out_e,\Eone(b))$, then
$$
\mathsf{UnaryHistory}(a)\land\mathsf{UnaryHistory}(b)\land\hsame(a,b).
$$
\end{theorem}
\begin{proof}
Compose the prefix classifier with the core denominator-unit classifier through
the first pair of continuations, then compose the resulting middle classifier
with the tail classifier through the second pair. This gives a
$\mathsf{RatDenomUnitClassifier}(out_d,out_e)$ witness.

Transport that classifier along the endpoint displays
$\hsame(out_d,\Eone(a))$ and $\hsame(out_e,\Eone(b))$. The result is a
classifier between $\Eone(a)$ and $\Eone(b)$. Apply
\autoref{thm:rat-denom-unit-classifier-e1-tail-iff} in the forward direction
to read back the two unary tail witnesses and their $\hsame$ link.
\end{proof}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitClassifier\_cont\_context\_e1\_pair\_readback}

\begin{theorem}[Rat denominator unit classifier visible cases iff]
\label{thm:rat-denom-unit-classifier-visible-cases-iff}
For histories $h,k:\mathsf{BHist}$, the empty-unit denominator classifier is
equivalent to either the empty--empty branch or a matched pair of one-headed
unary denominator tails:
$$
\begin{aligned}
&\mathsf{RatDenomUnitClassifier}(h,k)\\
&\Longleftrightarrow
\left(h\hsame\emp\land k\hsame\emp\right)\\
&\quad{}\lor
\exists h_t,k_t:\mathsf{BHist}.\;
h=\Eone(h_t)\land k=\Eone(k_t)\land \mathsf{UnaryHistory}(h_t)\\
&\qquad{}\land \mathsf{UnaryHistory}(k_t)\land h_t\hsame k_t.
\end{aligned}
$$
\end{theorem}
\begin{proof}
Unpack the classifier into two carrier witnesses and an endpoint comparison.
Each carrier is split by the visible carrier equivalence. Mixed empty and
one-headed endpoints contradict constructor disjointness. The one-headed pair
branch converts endpoint sameness through $\Eone$ injectivity, and the reverse
direction rebuilds the two carriers and the classifier comparison from the
displayed tail data.
\end{proof}
\leanchecked{BEDC.Derived.FieldUp.RatDenomUnitClassifier\_visible\_cases\_iff}
