\begin{definition}[Field ledger policy]
\label{def:field-ledger-policy}
Record the ring ledger and the $\mathsf{NonZero}_F$ witness used for each inverse.
\end{definition}

\begin{definition}[$\FieldUp$ certificate obligations]
\label{def:field-certificate-obligations}
For the concrete target $\FieldUp(\RatUp)$, a certificate must provide the
following rows as a single obligation record.
\begin{enumerate}
  \item Source and carrier: the rational-history source on
  $\mathsf{BHist}$ with carrier $\mathsf{RatHistoryCarrier}$.
  \item Classifier and pattern: $\mathsf{RatHistoryClassifier}$ and the
  continuation pattern $\Cont$ over $\mathsf{BHist}$.
  \item Ring base: the $\CommRingUp$ additive, multiplicative,
  commutativity, distributivity, operation-congruence, and ring-ledger rows.
  \item Apartness and inverse data: $\mathsf{NonZero}_F$ apartness from zero,
  transport of nonzero evidence, inverse closure, inverse classifier
  exactness, and left and right inverse laws indexed by nonzero witnesses.
  \item Product data: the two-sided zero-product rows and the certified
  nonzero-product contradiction rows.
  \item Denominator tuple:
  $(\mathsf{RatDenomUnitCarrier},\mathsf{RatDenomUnitClassifier},
  \mathsf{append},\emp,\mathsf{RatHistoryCarrier})$ with its multiplicative,
  unit, closure, classifier, and ledger rows.
  \item Contextual denominator data: the action $\Gamma$, its envelope and
  normalized-support rows, and the context-pair monoid rows for pair product,
  unit-pair action, composition, and strict-support readback.
  \item Affine source: $\mathsf{AffAut}_F$ with the packaged affine
  $\GroupUp$ rows used by the field certificate.
  \item Ledger and exactness data: ring expression ledger rows, inverse
  witness ledger rows, denominator ledger rows, contextual-pair ledger rows,
  affine coefficient ledger rows, coverage, soundness, completeness, exact
  zero classification, denominator exactness, contextual-action exactness,
  context-pair exactness, and affine classifier exactness.
  \item Status: the record status field, instantiated here as
  $\mathsf{ProofTarget}$.
\end{enumerate}
\end{definition}

\paragraph{Per-object certificate record.}
\begin{enumerate}
  \item Traditional target: constructive field.
  \item BEDC source: $\RatUp$ plus $\CommRingUp$ data.
  \item Carrier choice: the $\RatUp$ carrier with $\mathsf{NonZero}_F(a)$ derived from apartness from $0$.
  \item Classifier choice: the rational classifier plus $\mathsf{NonZero}_F$ transport.
  \item Stability obligations: commutative-ring laws, contradiction of $\mathsf{NonZero}_F(0)$, nonzero transport, inverse closure, and inverse laws indexed by nonzero witnesses.
  \item Ledger: ring expression tree plus the $\mathsf{NonZero}_F$ witness for each inverse.
  \item Core theorem list: inverse closure, left inverse, right inverse, nonzero
  stability, inverse congruence from apartness transport, inverse involution under
  explicit nonzero evidence, right-multiplication equation solving,
  right-multiplication equation exactness, left-multiplication equation solving,
  left-multiplication equation exactness, middle multiplication equation solving,
  middle multiplication equation exactness, two-sided multiplication exactness,
  two-sided zero-product exactness, zero-product exclusion from two nonzero
  witnesses, signed-factor apartness exclusivity, affine left equation exactness,
  affine right equation exactness, two-sided affine equation exactness,
  one-sided affine map classifier exactness, two-sided affine map classifier
  exactness, affine automorphism package, product-witness independence,
  denominator row laws, denominator contextual action certificate,
  \autoref{thm:ratup-fieldup-denominator-complete-contextual-row-package},
  \autoref{thm:field-rat-denominator-normalized-contextual-action-package},
  \autoref{thm:ratup-fieldup-denominator-contextual-action-unit-composition-laws},
  \autoref{thm:ratup-fieldup-denominator-total-normalization-support-collapse-row},
  \autoref{thm:ratup-fieldup-denominator-action-envelope-certificate-component},
  \autoref{thm:ratup-fieldup-denominator-context-pair-action-certificate},
  \autoref{thm:ratup-fieldup-denominator-context-pair-normalized-row-exhaustion},
  \autoref{thm:field-rat-denominator-context-pair-product-strict-support-commutes},
  \autoref{thm:ratup-fieldup-transported-strict-support-contextual-separation-package},
  \autoref{thm:field-affine-automorphism-group-certificate}, and distributivity
  inherited from $\CommRingUp$.
  \item Exactness predicate: coverage, soundness, completeness, exact zero
  classification, denominator row exactness, contextual denominator action
  exactness, normalized contextual denominator action exactness through
  \autoref{thm:field-rat-denominator-normalized-contextual-action-package},
  no-extra-support contextual-action support neutrality through
  \autoref{thm:ratup-fieldup-denominator-total-normalization-support-collapse-row},
  denominator-action envelope exactness through
  \autoref{thm:ratup-fieldup-denominator-action-envelope-certificate-component},
  contextual denominator unit-composition action laws, denominator context-pair
  action exactness through
  \autoref{thm:ratup-fieldup-denominator-context-pair-action-certificate},
  context-pair normalized row coverage through
  \autoref{thm:ratup-fieldup-denominator-context-pair-normalized-row-exhaustion},
  context-pair product strict-support commutation through
  \autoref{thm:field-rat-denominator-context-pair-product-strict-support-commutes},
  transported strict-support contextual separation through
  \autoref{thm:ratup-fieldup-transported-strict-support-contextual-separation-package},
  nonzero-product contradiction inside certified two-sided multiplication for
  admitted field packages, and the concrete affine automorphism $\GroupUp$
  certificate.
  \item Standard bridge: deferred conservative bridge.
  \item Status: ProofTarget.
\end{enumerate}

\paragraph{Primitive boundary.}
$\FieldUp$ is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:field-zero-axiom-note}
Explicit apartness witnesses support inverse formation without LEM-based
$a\ne0$ reasoning.
\end{remark}

\begin{theorem}[Field certificate forgets to CommRing certificate]
\label{thm:field-certificate-forgets-to-commring-certificate}
Let $\mathcal F$ be a BEDC history-level $\FieldUp(F)$ certificate with carrier
$C_F$, classifier $R_F$, operations
$\mathsf{add}_F$, $\mathsf{zero}_F$, $\mathsf{neg}_F$,
$\mathsf{mul}_F$, and $\mathsf{one}_F$, nonzero predicate
$\mathsf{NonZero}_F$, and proof-indexed inverse
$\mathsf{inv}_F(a,p)$ for $p:\mathsf{NonZero}_F(a)$. If $\mathcal F$
satisfies the field source, pattern, classifier, stability, ledger, and
obligation rows of \autoref{def:field-source-specification},
\autoref{def:field-pattern-specification},
\autoref{def:field-classifier-specification},
\autoref{def:field-stability-certificate},
\autoref{def:field-ledger-policy}, and
\autoref{def:field-certificate-obligations}, then
$$
\mathcal F_{\mathsf{CommRing}}:=
(C_F,R_F,\mathsf{add}_F,\mathsf{zero}_F,\mathsf{neg}_F,
\mathsf{mul}_F,\mathsf{one}_F)
$$
is a $\CommRingUp(F)$ source package in the sense of
\autoref{def:commring-source-specification},
\autoref{def:commring-pattern-specification},
\autoref{def:commring-classifier-specification}, and
\autoref{def:commring-stability-certificate}. It has the same carrier,
classifier, additive operation, zero, additive inverse, multiplication, and
unit as $\mathcal F$; the nonzero apartness row and all proof-indexed inverse
rows are not used by this reduct.
\end{theorem}
\begin{proof}
Unpack the field source row. By \autoref{def:field-source-specification}, a
field source is already a certified commutative-ring carrier together with the
additional constructive apartness predicate. Selecting the commutative-ring
coordinate gives the same carrier $C_F$ and does not change any BEDC history
endpoint.

Unpack the field pattern row. By \autoref{def:field-pattern-specification}, the
field pattern is commutative-ring expression formation with one added formation
rule for $\mathsf{inv}_F(a,p)$ when $p:\mathsf{NonZero}_F(a)$. Restricting to
expressions with no inverse node leaves exactly the commutative-ring pattern
from \autoref{def:commring-pattern-specification}, using the original
$\mathsf{add}_F$, $\mathsf{neg}_F$, $\mathsf{mul}_F$, $\mathsf{zero}_F$, and
$\mathsf{one}_F$ rows.

Unpack the classifier row. By \autoref{def:field-classifier-specification}, the
field classifier is ring sameness $R_F$ together with transport of
$\mathsf{NonZero}_F$ along that classifier. The $\CommRingUp(F)$ classifier
requires only the ring classifier, so the projected classifier is exactly the
same $R_F$.

Unpack the stability row. The first item of
\autoref{def:field-stability-certificate} is all commutative-ring stability
fields. These are precisely the closure, congruence, additive, multiplicative,
distributive, and multiplicative-commutativity rows listed in
\autoref{def:commring-stability-certificate}. The remaining field rows concern
$\mathsf{NonZero}_F(0)$, nonzero transport, inverse closure, and the left and
right inverse laws indexed by nonzero witnesses; none is required for the
commutative-ring certificate.

Finally, \autoref{def:field-ledger-policy} records the ring ledger together
with the nonzero witness used for each inverse. Selecting the ring ledger and
omitting inverse-witness entries gives the commutative-ring ledger for the same
operations and classifier. Thus every $\CommRingUp(F)$ row is a coordinate of
$\mathcal F$, and the displayed tuple is the required forgetful certificate.
\end{proof}
