\begin{definition}[LambdaCalc root constructor readback packet]
\label{def:lambdacalc-root-constructor-readback-packet}
A LambdaCalc root constructor readback packet is the finite $\mathsf{BHist}$
packet consisting of the visible $\TreeUp$ syntax row, the $\NatUp$ binder or
variable-index row when the root tag carries one, the constructor tag
$\mathsf{lamVar}$, $\mathsf{lamAbs}$, or $\mathsf{lamApp}$, the
constructor-preserving $\Cont$ provenance, the root $\hsame$ readback row, and
the $\Pkg$ provenance tying those rows to
$\mathsf{LambdaCalcBHistTermCarrier}$. No host syntax tree, ambient variable
set, or quotient alpha-class is part of the packet.
\end{definition}

\begin{theorem}[LambdaCalc root constructor readback exhaustion]
\label{thm:lambdacalc-root-constructor-readback-exhaustion}
Every accepted variable, abstraction, or application row of
$\mathsf{LambdaCalcBHistTermCarrier}$ projects to exactly one constructor case
of \autoref{def:lambdacalc-root-constructor-readback-packet}. The projection
uses only the displayed $\TreeUp$ row, the visible $\NatUp$ index rows,
$\Cont$, $\hsame$, and $\Pkg$ provenance.
\end{theorem}
\begin{proof}
For a variable row, apply
\autoref{thm:lambdacalc-variable-constructor-carrier}. The unary index is the
visible $\NatUp$ payload and the root readback row is the displayed
$\mathsf{lamVar}$ tag.

For abstraction and application rows, use
\autoref{thm:lambdacalc-abstraction-application-carrier-closure}. The theorem
keeps the binder row, body row, and two application subtrees inside the
visible $\TreeUp$ spine with constructor-preserving $\Cont$ transport.

The case split is exhausted by
\autoref{thm:lambdacalc-constructor-case-exhaustion}. Repacking each case with
the shared $\Pkg$ provenance gives exactly one readback packet and introduces
no extra equality relation.
\end{proof}

\begin{theorem}[LambdaCalc root beta-alpha consumer threshold]
\label{thm:lambdacalc-root-beta-alpha-consumer-threshold}
Every beta-redex, alpha-renaming, and substitution consumer for
$\LambdaCalcUp$ reads its root data from
\autoref{def:lambdacalc-root-constructor-readback-packet} together with the
finite substitution ledger of
\autoref{thm:lambdacalc-namecert-substitution-ledger}. Thus the consumer
surface uses only $\mathsf{BHist}$ constructor packets, $\Cont$, $\hsame$, and
$\Pkg$ provenance.
\end{theorem}
\begin{proof}
First project each consumed root through
\autoref{thm:lambdacalc-root-constructor-readback-exhaustion}. This supplies
the visible constructor tag, TreeUp syntax row, NatUp index row when present,
and the root readback provenance.

Next attach the free-variable and capture-avoidance ledgers. Apply
\autoref{thm:lambdacalc-free-variable-ledger-coverage} and
\autoref{thm:lambdacalc-capture-avoidance-cont-closure}; these keep the
substitution endpoint inside the displayed carrier and record the route as
$\Cont$ data.

Finally transport alpha and beta endpoints by
\autoref{thm:lambdacalc-alpha-beta-carrier-transport}. The finite ledger of
\autoref{thm:lambdacalc-namecert-substitution-ledger} supplies the remaining
substitution provenance, so beta, alpha, and substitution consumers cross the
root boundary only through the displayed packets.
\end{proof}

\begin{definition}[LambdaCalc root normal form packet]
\label{def:lambdacalc-root-normal-form-packet}
A LambdaCalc root normal form packet is the finite $\mathsf{BHist}$ packet
whose source is a root constructor readback packet of
\autoref{def:lambdacalc-root-constructor-readback-packet}, whose visible
syntax row lies in $\TreeUp$, whose binder and variable-index rows lie in
$\NatUp$ when present, and whose reduction frontier records that the root is
not a beta-redex visible through the displayed $\Cont$, $\hsame$, and $\Pkg$
provenance. The packet contains only constructor tags, finite subtree rows,
NatUp index rows, capture-avoidance continuation rows, root readback rows, and
the package provenance of $\mathsf{LambdaCalcBHistTermCarrier}$.
\end{definition}

\begin{theorem}[LambdaCalc root normal form readback]
\label{thm:lambdacalc-root-normal-form-readback}
Every accepted $\LambdaCalcUp$ root whose constructor readback packet has no
visible beta-redex exposure reads back to exactly one root normal form packet.
The readback uses the same $\TreeUp$ syntax row, the same $\NatUp$ binder or
variable-index payload when present, and the same $\Cont$, $\hsame$, and
$\Pkg$ provenance as the constructor readback packet.
\end{theorem}
\begin{proof}
First project the accepted root through
\autoref{thm:lambdacalc-root-constructor-readback-exhaustion}. This gives the
visible constructor tag and the finite TreeUp and NatUp rows, with no ambient
syntax object.

Next use the beta ledger scope theorem
\autoref{thm:lambdacalc-root-beta-ledger-scope}. The hypothesis that no
visible beta-redex exposure is present excludes exactly the application-over-
abstraction root case while leaving the variable, abstraction, and non-redex
application cases inside the displayed constructor carrier.

Finally repack the surviving constructor row with the original continuation,
root readback, and package provenance. The packet is unique because the
constructor case exhaustion theorem gives exactly one root constructor case.
\end{proof}

\begin{theorem}[LambdaCalc root substitution normal form consumer]
\label{thm:lambdacalc-root-substitution-normal-form-consumer}
Every substitution, alpha, or beta consumer that needs a LambdaCalc root normal
form may read only the packet of
\autoref{def:lambdacalc-root-normal-form-packet}, the finite substitution
ledger of \autoref{thm:lambdacalc-namecert-substitution-ledger}, and the alpha
transport of \autoref{thm:lambdacalc-alpha-beta-carrier-transport}. It may not
read a host substitution function, a quotient alpha-class, or a syntax tree
outside $\mathsf{LambdaCalcBHistTermCarrier}$.
\end{theorem}
\begin{proof}
Begin with the consumer threshold
\autoref{thm:lambdacalc-root-beta-alpha-consumer-threshold}. It already
restricts beta, alpha, and substitution consumers to constructor packets,
finite substitution ledgers, $\Cont$, $\hsame$, and $\Pkg$ provenance.

Apply \autoref{thm:lambdacalc-root-normal-form-readback} to the consumed root
when the consumer asks for a normal-form surface. This replaces the root
constructor packet by the corresponding normal form packet without changing
the TreeUp syntax row, NatUp payload, continuation, or package provenance.

The remaining consumer data is exactly the finite substitution ledger and
alpha transport already named by the threshold theorem. Since those rows live
inside the displayed $\mathsf{BHist}$ carrier, no host substitution or quotient
alpha object is available to the consumer.
\end{proof}
