\begin{theorem}[Finite observation-budget selector Real-seal window saturation]
\label{thm:finite-observation-budget-selector-real-seal-window-saturation}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Any Real-completion or diagonal consumer that reaches the same terminal row $E$ through the same budget, schedule, dyadic, regular, transport, continuation, provenance, and local naming rows $B,S,D,R,H,C,P,N$ must use the displayed finite $\StreamNameUp$ window family $W$. Adding or replacing a window without changing the budget or schedule is not a refinement of the same selector packet; it is a different accepted packet with a different window row.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_real\_seal\_window\_saturation}
\begin{proof}
Start with the route into the terminal Real seal. By \autoref{thm:finite-observation-budget-selector-real-seal-handoff}, every Real-facing read of $E$ is reached only after the finite budget, schedule, selected window family, dyadic ledger, and regular handoff have been exposed.

Use window exhaustion for the lower observation segment. By \autoref{thm:finite-observation-budget-selector-dyadic-window-exhaustion}, the dyadic observations in $D$ are already covered by the displayed finite windows $W$, so a diagonal or completion consumer has no independent dyadic source outside that family.

Now apply route determinacy. The theorem \autoref{thm:finite-observation-budget-selector-budget-route-determinacy} fixes the displayed route from $B$ through $S,W,D,R$ to $E$ whenever the structural rows $H,C,P,N$ are preserved.

Finally use the terminal theorems to exclude a hidden selector. By \autoref{thm:finite-observation-budget-selector-terminal-route-no-branching} and \autoref{thm:finite-observation-budget-selector-terminal-route-endpoint-exactness}, a consumer reaching the same endpoint through the same displayed rows cannot pass through a second window source. A changed window family therefore changes the accepted selector packet rather than refining the original one.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal window minimality]
\label{thm:finite-observation-budget-selector-terminal-window-minimality}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Every terminal $\RealUp$-facing read of $F$ factors through exactly the displayed finite budget row $B$, selected $\StreamNameUp$ window family $W$, $\DyadicRatCoreUp$ ledger $D$, $\RegSeqRatUp$ handoff $R$, componentwise $\hsame$ transports $H$, displayed $\Cont$ route $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$, with the selected schedule row $S$ mediating the route
$$
B \to S \to W \to D \to R \to E.
$$
If any one of the displayed budget, schedule, window, dyadic ledger, regular handoff, seal, transport, continuation, provenance, or local naming rows is dropped, the remaining rows no longer determine the terminal endpoint exactness of \autoref{thm:finite-observation-budget-selector-terminal-route-endpoint-exactness}.
\end{theorem}
\begin{proof}
First identify the only route available to a terminal consumer. The budget-route determinacy theorem \autoref{thm:finite-observation-budget-selector-budget-route-determinacy} fixes the path from $B$ through $S,W,D,R$ to $E$, and terminal selector synchronization \autoref{thm:finite-observation-budget-selector-terminal-selector-synchronization} keeps the selected schedule and window rows attached to that path.

Next remove terminal branching. By \autoref{thm:finite-observation-budget-selector-terminal-route-no-branching}, two consumers exposing the same displayed rows determine the same terminal route, so there is no alternate endpoint route through quotient streams, host real equality, countable choice, hidden selectors, side-channel completion, or ambient completeness.

It remains to record sufficiency and minimality. Sufficiency is exactly endpoint exactness from \autoref{thm:finite-observation-budget-selector-terminal-route-endpoint-exactness}: the displayed rows identify the terminal endpoint with $E$ by componentwise $\hsame$ transport. For minimality, each listed row is used by one segment of the displayed route or by its transport, continuation, provenance, and naming certificate. Dropping such a row removes the corresponding segment or certificate witness, so the endpoint can no longer be recovered by the cited exactness theorem.
\end{proof}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_window\_minimality}

\begin{theorem}[Finite observation-budget selector diagonal-tail coverage]
\label{thm:finite-observation-budget-selector-diagonal-tail-coverage}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. The terminal window inventory of \autoref{thm:finite-observation-budget-selector-terminal-window-minimality} covers every diagonal-tail consumer route used by $\RegularCauchyTailSelectorUp$, $\RealDiagonalCompletionUp$, and $\RealCompletionSelectorSealUp$: such a consumer reads its terminal $\RealUp$ handoff only through the finite route
$$
B \to S \to W \to D \to R \to E
$$
and through the displayed $H,C,P,N$ rows. The coverage imports no quotient stream, countable choice operation, host real equality, hidden selector, detached completion limit, or independent completeness oracle.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_diagonal\_tail\_coverage}
\begin{proof}
Begin with the tail-facing side. The tail-meet seal compatibility theorem \autoref{thm:finite-observation-budget-selector-tail-meet-seal-compatibility} places every selected-tail or seal consumer on the displayed finite chain, and the diagonal consumer boundary \autoref{thm:finite-observation-budget-selector-diagonal-consumer-boundary} keeps diagonal-limit and Real-completion consumers inside the same rows.

Now attach the selector-seal consumer. The RealCompletionSelectorSeal pullback \autoref{thm:finite-observation-budget-selector-realcompletionselectorseal-pullback} identifies the shared budget, selected window, regular readback, and terminal seal rows with the selector-seal route using only displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data.

Finally apply terminal window minimality, \autoref{thm:finite-observation-budget-selector-terminal-window-minimality}. Its inventory is sufficient for the terminal endpoint and loses exactness when a displayed row is removed. Therefore the diagonal-tail consumers named in the statement are covered by the same finite terminal window, while the excluded quotient, choice, host-equality, hidden-selector, detached-limit, and completeness coordinates remain absent.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal section exactness]
\label{thm:finite-observation-budget-selector-terminal-section-exactness}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Every terminal Real-completion or diagonal-tail section whose displayed rows agree with $B,S,W,D,R,E,H,C,P,N$ is exactly the finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$. The section exports no quotient stream, host real equality, countable choice, hidden selector, detached completion limit, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_section\_exactness}
\begin{proof}
First use terminal window minimality, \autoref{thm:finite-observation-budget-selector-terminal-window-minimality}. It supplies the full selector inventory $B,S,W,D,R,E,H,C,P,N$ and says that dropping any one of those rows loses terminal endpoint determination.

Next apply terminal route endpoint exactness, \autoref{thm:finite-observation-budget-selector-terminal-route-endpoint-exactness}. Since the displayed rows agree with the accepted packet, the terminal section reaches the same $\RealUp$ endpoint $E$ through the same componentwise $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

For diagonal-tail consumers, use \autoref{thm:finite-observation-budget-selector-diagonal-tail-coverage}. It keeps the $\RegularCauchyTailSelectorUp$, $\RealDiagonalCompletionUp$, and $\RealCompletionSelectorSealUp$ reads on the same finite route
$$
B \to S \to W \to D \to R \to E.
$$

Finally identify that route with the existing four-face finite-section pullback. By \autoref{thm:streamname-finite-section-pullback-exactness}, agreement of the finite $\StreamNameUp$ windows with the $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ readback, and current $\RealUp$ seal determines exactly the same terminal section and exports none of the excluded quotient, host-equality, choice, hidden-selector, detached-limit, metric-completeness, or ambient-completeness coordinates.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal section pullback uniqueness]
\label{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}
Let
$$
F_0=(B,S,W,D,R,E,H,C,P,N)
$$
and
$$
F_1=(B,S,W,D,R,E,H,C,P,N)
$$
be accepted $\FiniteObservationBudgetSelectorUp$ packets with the same displayed budget, schedule, window, dyadic ledger, regular handoff, Real seal, transport, continuation, provenance, and local naming rows. Suppose that the terminal sections of $F_0$ and $F_1$ both satisfy the finite-section pullback along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$. Then the two terminal sections determine the same budget-to-seal route
$$
B \to S \to W \to D \to R \to E
$$
and the same $\RealUp$ seal up to the recorded componentwise $\hsame$ transports. No quotient stream, host real equality, choice row, hidden selector, metric-completeness row, or ambient-completeness oracle can distinguish the two terminal sections.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_section\_pullback\_uniqueness}
\begin{proof}
First apply terminal section exactness, \autoref{thm:finite-observation-budget-selector-terminal-section-exactness}, to each accepted packet. Since both displayed rows are $B,S,W,D,R,E,H,C,P,N$, both terminal sections are the finite section pulled back through the same $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces.

Next identify the endpoint route. Terminal route endpoint exactness, \autoref{thm:finite-observation-budget-selector-terminal-route-endpoint-exactness}, fixes the endpoint at the displayed seal $E$, while terminal window minimality, \autoref{thm:finite-observation-budget-selector-terminal-window-minimality}, keeps every route segment attached to the same rows $B,S,W,D,R,E,H,C,P,N$.

Finally use the four-face pullback exactness \autoref{thm:streamname-finite-section-pullback-exactness}. The shared finite windows, dyadic ledger, regular readback, and Real seal determine one pulled-back section, so the two terminal sections induce the same displayed chain and the same $\RealUp$ seal under the componentwise $\hsame$ transports. The non-escape clauses in the cited exactness and minimality theorems exclude quotient streams, host equalities, choice rows, hidden selectors, metric-completeness rows, and ambient-completeness oracles as possible distinguishing data.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal cofinal-window coverage]
\label{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Every cofinal terminal consumer compatible with the displayed selector rows factors through the same finite window route
$$
B \to S \to W \to D \to R \to E.
$$
Compatibility with $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\RegularCauchyTailSelectorUp$, $\RealDiagonalCompletionUp$, and $\RealCompletionSelectorSealUp$ is therefore mediated only by the displayed budget, schedule, window, dyadic ledger, regular handoff, Real seal, componentwise $\hsame$ transports, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row. The exported terminal surface contains no quotient stream, countable choice operation, host real equality, hidden selector, detached completion limit, or ambient completeness oracle.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_cofinal\_window\_coverage}
\begin{proof}
First fix the finite terminal inventory. Terminal window minimality, \autoref{thm:finite-observation-budget-selector-terminal-window-minimality}, says that every terminal $\RealUp$-facing read of $F$ uses exactly the displayed rows $B,S,W,D,R,E,H,C,P,N$ with $S$ mediating the route through the finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ ledger, and $\RegSeqRatUp$ handoff.

Next attach the diagonal-tail consumers. By \autoref{thm:finite-observation-budget-selector-diagonal-tail-coverage}, the $\RegularCauchyTailSelectorUp$, $\RealDiagonalCompletionUp$, and $\RealCompletionSelectorSealUp$ reads of the packet all remain on the same finite route and import none of the excluded quotient, choice, host-equality, hidden-selector, detached-limit, or completeness coordinates.

Now pass from a compatible terminal section to the displayed section. Terminal section exactness, \autoref{thm:finite-observation-budget-selector-terminal-section-exactness}, identifies any section agreeing with the displayed rows as the finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$.

Finally use pullback uniqueness. The uniqueness theorem \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}, together with \autoref{thm:streamname-finite-section-pullback-exactness}, leaves only the chain $B \to S \to W \to D \to R \to E$ as the cofinal terminal route. Hence every compatible cofinal consumer factors through that route and exports only the displayed structural rows.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal cofinal-window transport invariance]
\label{thm:finite-observation-budget-selector-terminal-cofinal-window-transport-invariance}
Let
$$
F_0=(B,S,W,D,R,E,H,C,P,N)
$$
and
$$
F_1=(B,S,W,D,R,E,H,C,P,N)
$$
be accepted $\FiniteObservationBudgetSelectorUp$ packets whose terminal rows agree componentwise in the budget row $B$, schedule row $S$, finite $\StreamNameUp$ window family $W$, $\DyadicRatCoreUp$ ledger $D$, $\RegSeqRatUp$ handoff $R$, $\RealUp$ seal $E$, componentwise $\hsame$ transports $H$, displayed $\Cont$ route $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$. Then every cofinal terminal consumer compatible with $F_0$ is compatible with $F_1$, and conversely, and both compatibilities factor through the same displayed route
$$
B \to S \to W \to D \to R \to E.
$$
No quotient stream, host real equality, choice operation, hidden selector, detached completion limit, or ambient completeness oracle can distinguish the two packets at a cofinal terminal consumer.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_cofinal\_window\_transport\_invariance}
\begin{proof}
First apply terminal cofinal-window coverage, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}, to $F_0$ and to $F_1$. Since the two packets expose the same displayed rows $B,S,W,D,R,E,H,C,P,N$, every compatible cofinal terminal consumer on either side is already forced onto the same finite route through the selected $\StreamNameUp$ windows, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, and terminal $\RealUp$ seal.

Next identify the terminal sections. The terminal section exactness theorem \autoref{thm:finite-observation-budget-selector-terminal-section-exactness} turns compatibility with the displayed rows into the finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$.

Now use terminal section pullback uniqueness, \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}. The two sections have the same budget, schedule, window, dyadic, regular, seal, transport, continuation, provenance, and local naming rows, so they determine one route and one terminal seal under the recorded componentwise $\hsame$ transports.

Finally invoke \autoref{thm:streamname-finite-section-pullback-exactness}. The four-face pullback has no additional quotient, host-equality, choice, hidden-selector, detached-limit, or ambient-completeness coordinate. Thus transport along the shared rows carries cofinal terminal compatibility in either direction and leaves the route $B \to S \to W \to D \to R \to E$ invariant.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal cofinal-window section decomposition]
\label{thm:finite-observation-budget-selector-terminal-cofinal-window-section-decomposition}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Every cofinal terminal consumer compatible with $F$ decomposes into the four displayed section faces: the finite $\StreamNameUp$ window family $W$, the $\DyadicRatCoreUp$ ledger $D$, the $\RegSeqRatUp$ readback $R$, and the terminal $\RealUp$ seal $E$. The only transport data between these faces are the componentwise $\hsame$ rows $H$, displayed $\Cont$ route $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$.

Equivalently, the consumer route is the finite section
$$
W \to D \to R \to E
$$
inside the budget and schedule envelope $B,S$. It exports no quotient stream, host real equality, choice row, hidden selector, detached limit, metric-completeness row, or ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_cofinal\_window\_section\_decomposition}
\begin{proof}
First apply terminal cofinal-window coverage, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}. It places every compatible cofinal terminal consumer on the displayed route from the finite budget and selected schedule through $W,D,R$ to $E$.

Next use terminal section exactness, \autoref{thm:finite-observation-budget-selector-terminal-section-exactness}. This identifies the compatible terminal section with the finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$.

Now apply terminal section pullback uniqueness, \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}. The rows $B,S,W,D,R,E,H,C,P,N$ determine a single budget-to-seal route, so any compatible consumer has the same four-face section decomposition.

Finally use \autoref{thm:streamname-finite-section-pullback-exactness}. Its finite-section pullback gives the displayed $\StreamNameUp$ window face, $\DyadicRatCoreUp$ ledger face, $\RegSeqRatUp$ readback face, and $\RealUp$ seal face, while the non-escape clauses in the cited theorems exclude quotient streams, host real equality, choice rows, hidden selectors, detached limits, metric-completeness rows, and ambient completeness.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal route status readback]
\label{thm:finite-observation-budget-selector-terminal-route-status-readback}
Every terminal cofinal consumer of an accepted $\FiniteObservationBudgetSelectorUp$ packet reports its route status only through the displayed budget, schedule, finite window, dyadic ledger, regular-rational readback, Real seal, transport, continuation, provenance, and local naming rows
$$
B,S,W,D,R,E,H,C,P,N.
$$
No quotient stream, hidden selector, host real equality, metric-completeness row, countable choice row, or ambient completeness oracle is a status coordinate for the same terminal route.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_route\_status\_readback}
\begin{proof}
First apply terminal cofinal-window coverage. It places every compatible terminal consumer on the displayed route from budget and schedule through the window, dyadic, regular, and Real-seal faces.

Next use terminal cofinal-window transport invariance. The status readback is preserved by the componentwise $\hsame$ rows, the displayed continuation row, the package provenance row, and the local naming row, so transport cannot create a second terminal status.

Finally apply terminal cofinal-window section decomposition. The route decomposes into the four displayed faces $W,D,R,E$ inside the envelope $B,S,H,C,P,N$, and the four-face pullback exactness excludes quotient, hidden-selector, choice, host-equality, metric-completeness, and ambient-completeness coordinates.
\end{proof}

\begin{theorem}[Finite observation-budget selector cofinal window exhaustion]
\label{thm:finite-observation-budget-selector-cofinal-window-exhaustion}
For an accepted $\FiniteObservationBudgetSelectorUp$ packet, the cofinal terminal route is exhausted by the rows $B,S,W,D,R,E,H,C,P,N$. No quotient stream, hidden selector, countable choice row, host real equality, metric-completeness row, or ambient completeness oracle can refine the same route while preserving the displayed terminal window.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_cofinal\_window\_exhaustion}
\begin{proof}
Begin with terminal window minimality. Removing a displayed row loses terminal endpoint determination, so a refinement of the same route must preserve the visible budget, schedule, window, dyadic, regular, seal, transport, continuation, provenance, and naming rows.

Use terminal route status readback. Any compatible terminal consumer reports status through those rows alone, so a hidden selector, quotient stream, or choice row would be an extra status coordinate rather than a refinement of the same route.

Finally invoke terminal cofinal-window section decomposition and the four-face pullback exactness. The four faces $W,D,R,E$ already determine the terminal section over $B,S,H,C,P,N$, leaving no host real equality, metric-completeness row, or ambient completeness oracle to refine the cofinal window.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal-window nonescape]
\label{thm:finite-observation-budget-selector-terminal-window-nonescape}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Every terminal Real-completion consumer that preserves the displayed budget, schedule, finite $\StreamNameUp$ window, dyadic ledger, $\RegSeqRatUp$ handoff, Real seal, $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row has no additional status coordinate for quotient streams, hidden selectors, host real equality, metric-completeness data, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
First use terminal-window minimality, \autoref{thm:finite-observation-budget-selector-terminal-window-minimality}. It says that the displayed rows $B,S,W,D,R,E,H,C,P,N$ are sufficient for terminal endpoint determination and that dropping any displayed row loses that determination.

Next apply terminal route status readback, \autoref{thm:finite-observation-budget-selector-terminal-route-status-readback}. A compatible terminal consumer reports status only through the same rows, so any quotient stream, hidden selector, host equality, metric-completeness row, choice row, or ambient-completeness oracle would be an additional status coordinate.

Use cofinal-window exhaustion, \autoref{thm:finite-observation-budget-selector-cofinal-window-exhaustion}, to rule out refinements of the same terminal route. The route is already exhausted by the displayed packet.

Finally apply the four-face terminal correspondence, \autoref{thm:finite-observation-budget-selector-four-face-terminal-correspondence}. The section faces $W,D,R,E$ assemble the terminal consumer over $B,S,H,C,P,N$, leaving no further terminal-window escape coordinate.
\end{proof}

\begin{theorem}[Finite observation-budget selector four-face terminal correspondence]
\label{thm:finite-observation-budget-selector-four-face-terminal-correspondence}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. A terminal consumer is compatible with $F$ exactly when it is given by the four displayed terminal section faces $W,D,R,E$ together with the shared budget, schedule, transport, continuation, provenance, and local naming rows $B,S,H,C,P,N$. Thus the public terminal route is precisely the finite observation-budget passage
$$
B,S \to W \to D \to R \to E
$$
and the correspondence exports no quotient stream, host real equality, choice row, detached completion limit, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_four\_face\_terminal\_correspondence}
\begin{proof}
Start with terminal cofinal-window section decomposition, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-section-decomposition}. It sends every compatible terminal consumer to the four displayed faces $W,D,R,E$ inside the shared envelope $B,S,H,C,P,N$.

For the reverse direction, apply terminal section exactness, \autoref{thm:finite-observation-budget-selector-terminal-section-exactness}. A section assembled from $W,D,R,E$ and the shared rows is already a terminal section over the accepted packet, so it gives a compatible terminal consumer.

The two constructions are inverse on the displayed rows by terminal section pullback uniqueness, \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}. No second terminal section can have the same budget, schedule, window, dyadic, regular, seal, transport, continuation, provenance, and naming rows.

Finally use \autoref{thm:streamname-finite-section-pullback-exactness}. The underlying finite $\StreamNameUp$ section has no additional quotient, host-equality, choice, detached-limit, metric-completeness, or ambient-completeness coordinate, so the four faces are exactly the terminal route.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal budget exhaustion]
\label{thm:finite-observation-budget-selector-terminal-budget-exhaustion}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. No terminal consumer route reaching the displayed $\RealUp$ seal $E$ can read outside the budget row $B$, selected schedule row $S$, finite $\StreamNameUp$ window family $W$, $\DyadicRatCoreUp$ ledger $D$, $\RegSeqRatUp$ handoff $R$, componentwise $\hsame$ transports $H$, displayed $\Cont$ route $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$. Thus the terminal budget is exhausted exactly by the route
$$
B,S \to W \to D \to R \to E.
$$
The exhausted surface has no quotient stream, host real equality, countable choice row, hidden selector, detached completion limit, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_terminal\_budget\_exhaustion}
\begin{proof}
First apply terminal window minimality, \autoref{thm:finite-observation-budget-selector-terminal-window-minimality}. It identifies the complete terminal inventory of an accepted packet and says that dropping any displayed row removes the endpoint exactness supplied by the terminal route.

Next attach diagonal-tail coverage, \autoref{thm:finite-observation-budget-selector-diagonal-tail-coverage}. This keeps every Real-completion and diagonal consumer on the same finite chain through $B,S,W,D,R,E$ and the same transport, continuation, provenance, and local naming rows.

Now use terminal section exactness, \autoref{thm:finite-observation-budget-selector-terminal-section-exactness}. A consumer that reaches the terminal seal through the displayed rows is exactly the finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$.

Finally combine terminal section pullback uniqueness with the four-face terminal correspondence, \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness} and \autoref{thm:finite-observation-budget-selector-four-face-terminal-correspondence}. These results leave no second terminal route with the same rows and no additional quotient, host-equality, choice, hidden-selector, detached-limit, metric-completeness, or ambient-completeness coordinate.
\end{proof}

\begin{theorem}[Finite observation-budget selector cofinal route choice freeness]
\label{thm:finite-observation-budget-selector-cofinal-route-choice-freeness}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Every cofinal terminal route compatible with $F$ is determined by the displayed budget, schedule, finite window, dyadic ledger, regular handoff, Real seal, transport, continuation, provenance, and local naming rows. In particular, cofinal compatibility requires no independent choice of terminal route, no choice of a hidden tail selector, and no choice of an external completion witness beyond the four faces $W,D,R,E$ inside the envelope $B,S,H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteObservationBudgetSelectorUp.FiniteObservationBudgetSelectorCarrier\_cofinal\_route\_choice\_freeness}
\begin{proof}
Start from terminal cofinal-window coverage, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}. It forces any compatible cofinal consumer onto the displayed finite route from the selected budget and schedule through $W,D,R$ to $E$.

Next decompose the route by \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-section-decomposition}. The consumer is exactly the four-face section with $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces and with transport supplied only by $H,C,P,N$.

The forward and reverse readings of compatibility are supplied by the four-face terminal correspondence, \autoref{thm:finite-observation-budget-selector-four-face-terminal-correspondence}. A consumer compatible with $F$ gives the displayed four faces, and the displayed four faces with the shared rows give a compatible terminal consumer.

Finally use terminal section pullback uniqueness, \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}. Since no second section can carry the same displayed rows, there is no remaining route-choice parameter, hidden selector, external completion witness, quotient stream, host equality, or ambient completeness oracle.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal readiness correspondence]
\label{thm:finite-observation-budget-selector-terminal-readiness-correspondence}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. The following terminal-readiness data are equivalent as public Real-and-Completion handoff surfaces:
\begin{enumerate}
\item a terminal consumer route compatible with $F$;
\item the exhausted finite budget route $B,S \to W \to D \to R \to E$ together with the displayed $H,C,P,N$ rows;
\item the four-face terminal section $W,D,R,E$ inside the same budget, schedule, transport, continuation, provenance, and local $\NameCert$ envelope.
\end{enumerate}
Under this correspondence, later $\RealUp$, diagonal-completion, and selector-seal consumers receive exactly the displayed budget-readiness rows and no quotient stream, host real equality, countable choice operation, hidden selector, detached completion limit, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\begin{proof}
First pass from a compatible terminal consumer to the exhausted route. By \autoref{thm:finite-observation-budget-selector-terminal-budget-exhaustion}, any terminal route reaching $E$ is already confined to the displayed budget, schedule, window, dyadic, regular, seal, transport, continuation, provenance, and local naming rows.

Next pass from the exhausted route to the four-face section. The terminal cofinal-window section decomposition theorem, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-section-decomposition}, rewrites the route as the four faces $W,D,R,E$ inside the envelope $B,S,H,C,P,N$.

For the converse direction, use the four-face terminal correspondence, \autoref{thm:finite-observation-budget-selector-four-face-terminal-correspondence}. The four displayed faces together with the shared rows assemble exactly a compatible terminal consumer.

It remains to show that the correspondence is the handoff surface seen by downstream consumers. Terminal section exactness and pullback uniqueness, \autoref{thm:finite-observation-budget-selector-terminal-section-exactness} and \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}, identify all three descriptions with the same finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$.

Finally, cofinal route choice freeness, \autoref{thm:finite-observation-budget-selector-cofinal-route-choice-freeness}, removes any extra route parameter. Hence $\RealUp$, diagonal-completion, and selector-seal consumers inherit only the displayed budget-readiness rows and none of the excluded quotient, host-equality, choice, hidden-selector, detached-limit, metric-completeness, or ambient-completeness data.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal four-face pullback lock]
\label{thm:finite-observation-budget-selector-terminal-four-face-pullback-lock}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. The terminal Real-and-Completion consumer surface of $F$ is locked by the four displayed faces $W,D,R,E$ in the following sense:
\begin{enumerate}
\item the $\StreamNameUp$ finite-section pullback reads exactly the selected finite window family $W$;
\item the $\DyadicRatCoreUp$ ledger face reads exactly $D$;
\item the $\RegSeqRatUp$ readback face reads exactly $R$;
\item the $\RealUp$ terminal seal face reads exactly $E$.
\end{enumerate}
Every $\UniformCauchyCriterionUp$, $\RealUp$, diagonal-completion, or selector-seal consumer compatible with the selector must factor through exactly this route
$$
B,S \to W \to D \to R \to E
$$
with transport, continuation, provenance, and local naming supplied only by $H,C,P,N$. The locked surface contains no quotient stream, host real equality, countable choice operation, hidden tail selector, detached completion witness, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\begin{proof}
First identify the public readiness surface. The terminal readiness correspondence, \autoref{thm:finite-observation-budget-selector-terminal-readiness-correspondence}, equates a compatible terminal consumer, the exhausted route $B,S \to W \to D \to R \to E$, and the four-face section $W,D,R,E$ inside the shared $H,C,P,N$ envelope.

Now pin the four faces as a pullback rather than as a loose list. Terminal section exactness, \autoref{thm:finite-observation-budget-selector-terminal-section-exactness}, identifies any compatible terminal section with the finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$. Terminal section pullback uniqueness, \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}, leaves no second section with the same displayed rows.

Next read the StreamName-facing side through the ambient finite-section theorem. By \autoref{thm:streamname-finite-section-pullback-exactness}, the selected finite windows, dyadic ledger, regular readback, and Real seal determine one four-face pullback. Therefore the first face reads $W$, the second reads $D$, the third reads $R$, and the fourth reads $E$.

Finally attach the open Real-and-Completion consumers. The UniformCauchyCriterion pullback, \autoref{thm:finite-observation-budget-selector-uniform-cauchycriterion-pullback}, places any compatible uniform-Cauchy read on the same finite observation route, while the readiness correspondence already covers the $\RealUp$, diagonal-completion, and selector-seal handoff surfaces. Thus every such consumer factors through the displayed route and can export only $B,S,W,D,R,E,H,C,P,N$, with the quotient, host-equality, choice, hidden-selector, detached-witness, metric-completeness, and ambient-completeness coordinates absent.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal cofinal schedule lock]
\label{thm:finite-observation-budget-selector-terminal-cofinal-schedule-lock}
Let
$$
F_0=(B,S,W,D,R,E,H,C,P,N)
$$
and
$$
F_1=(B,S',W,D,R,E,H,C,P,N)
$$
be accepted $\FiniteObservationBudgetSelectorUp$ packets. Suppose both packets are compatible with the same terminal cofinal-window route and with the same four-face pullback through $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$. Then every terminal consumer reads the same budget-to-seal surface from $F_0$ and $F_1$:
$$
B \to W \to D \to R \to E
$$
with transport, continuation, provenance, and local naming supplied only by $H,C,P,N$. In particular, the terminal consumer can read no distinction between $S$ and $S'$. Any actual schedule separation must alter the displayed route before the terminal seal, not only a hidden scheduling coordinate behind the common four-face surface.

The locked surface contains no quotient stream, countable choice operation, hidden selector, detached completion limit, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\begin{proof}
First apply terminal cofinal-window coverage, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}, to $F_0$ and to $F_1$. Each compatible terminal consumer is forced onto the displayed finite route through the $\StreamNameUp$ window family $W$, $\DyadicRatCoreUp$ ledger $D$, $\RegSeqRatUp$ handoff $R$, and $\RealUp$ seal $E$.

Next use terminal cofinal-window transport invariance, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-transport-invariance}, on the rows shared by the two packets. The only row not literally shared is the schedule coordinate, and the hypothesis says that both schedules feed the same terminal cofinal-window route and the same four-face pullback. Transport therefore carries terminal compatibility from $F_0$ to $F_1$ and back without creating a second terminal read.

Now exhaust the terminal budget. By \autoref{thm:finite-observation-budget-selector-terminal-budget-exhaustion}, any terminal consumer that reaches $E$ is already confined to the displayed budget, finite window, dyadic ledger, regular handoff, seal, transport, continuation, provenance, and local naming rows. Cofinal route choice freeness, \autoref{thm:finite-observation-budget-selector-cofinal-route-choice-freeness}, removes any independent route choice or hidden selector that could record a separate schedule decision.

Finally apply the terminal four-face pullback lock, \autoref{thm:finite-observation-budget-selector-terminal-four-face-pullback-lock}. Since both packets present the same $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces, the terminal consumer sees the same locked surface. Thus a real schedule separation must appear before the terminal seal as a displayed route change; it cannot be stored only in a hidden scheduling coordinate.

The non-escape clauses in the cited theorems exclude quotient streams, countable choice, hidden selectors, detached completion limits, metric-completeness rows, and ambient completeness oracles from the terminal surface.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal tail-meet synchronization]
\label{thm:finite-observation-budget-selector-terminal-tail-meet-synchronization}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Any terminal consumer that is compatible both with the $\FiniteObservationBudgetSelectorUp$ cofinal-window route and with either a $\RegularCauchyTailMeetUp$ shared-tail route or a $\TailCofinalityScheduleUp$ cofinal schedule must read the same L10 terminal route
$$
B,S \to W \to D \to R \to E.
$$
Equivalently, the tail-meet consumer, the cofinal-schedule consumer, and the terminal selector consumer all factor through the same four displayed faces $W,D,R,E$, with transport, continuation, provenance, and local naming supplied only by $H,C,P,N$. The synchronized surface cannot introduce a second tail-meet threshold, hidden cofinal schedule, quotient stream, host real equality, choice row, detached limit, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\begin{proof}
First place the selector-side consumer on the terminal route. Terminal cofinal-window coverage, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}, forces every compatible terminal read through the displayed finite window, dyadic ledger, regular-rational readback, and Real seal faces. The terminal four-face pullback lock, \autoref{thm:finite-observation-budget-selector-terminal-four-face-pullback-lock}, then identifies those faces as exactly $W,D,R,E$ over the route $B,S \to W \to D \to R \to E$.

Next attach the schedule side. The terminal cofinal schedule lock, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-schedule-lock}, says that two accepted schedules with the same terminal cofinal-window route and the same four-face pullback give the terminal consumer no visible schedule distinction. Thus a $\TailCofinalityScheduleUp$ consumer compatible with $F$ reads the same schedule-facing route rather than a hidden cofinal schedule behind it.

Now attach the shared-tail side. The RegularCauchyTailMeet budget-selector handoff, \autoref{thm:regular-cauchy-tail-meet-budget-selector-handoff}, requires every $\FiniteObservationBudgetSelectorUp$ consumer of an accepted shared-tail packet to consume the displayed TailMeet route before selecting a downstream budget. The root budget route lock, \autoref{thm:regular-cauchy-tail-meet-root-budget-route-lock}, leaves no second downstream budget or independent tail oracle available to the same consumer.

Combining these route locks gives determinacy at the terminal selector surface. Both the TailMeet-compatible read and the cofinal-schedule-compatible read reach the same selector packet $F$, and $F$ has only the four terminal faces $W,D,R,E$ after $B,S$. Therefore the common consumer factors through the displayed route $B,S \to W \to D \to R \to E$.

The non-escape clauses in the cited selector and TailMeet results remove every unlisted resource. Hence no second tail-meet threshold, hidden cofinal schedule, quotient stream, host real equality, choice row, detached limit, metric-completeness row, or ambient completeness oracle can be added at the synchronized terminal surface.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal window seal inversion]
\label{thm:finite-observation-budget-selector-terminal-window-seal-inversion}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Any terminal consumer exposing the same four faces $W,D,R,E$ and the same budget, schedule, transport, continuation, provenance, and local naming rows $B,S,H,C,P,N$ determines the same Real seal route
$$
B,S \to W \to D \to R \to E.
$$
Conversely, any accepted terminal Real-seal route from $B,S$ to $E$ decomposes into those four displayed faces $W,D,R,E$ inside the same envelope. The correspondence exports no quotient stream, host real equality, countable choice operation, detached limit, metric-completeness row, or ambient completeness oracle.
\end{theorem}
\begin{proof}
For the forward direction, begin with terminal cofinal-window coverage. \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage} places every compatible terminal consumer on the displayed finite route through the window, dyadic, regular, and Real-seal faces.

Terminal section exactness and terminal section pullback uniqueness then remove any second route. By \autoref{thm:finite-observation-budget-selector-terminal-section-exactness}, the compatible consumer is the finite section pulled back along $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$; by \autoref{thm:finite-observation-budget-selector-terminal-section-pullback-uniqueness}, the shared rows $B,S,W,D,R,E,H,C,P,N$ determine a single terminal section.

For the reverse direction, read an accepted Real-seal route through the four-face surface. The terminal four-face pullback lock, \autoref{thm:finite-observation-budget-selector-terminal-four-face-pullback-lock}, pins the four displayed faces as $W,D,R,E$, and terminal tail-meet synchronization, \autoref{thm:finite-observation-budget-selector-terminal-tail-meet-synchronization}, keeps tail-meet and cofinal-schedule consumers on the same L10 route.

Thus terminal routes and compatible terminal windows determine one another over the displayed packet. The non-escape clauses in the cited theorems exclude quotient streams, host real equality, countable choice, detached limits, metric-completeness rows, and ambient completeness from either direction of the correspondence.
\end{proof}

\begin{theorem}[Finite observation-budget selector terminal window choice-free section]
\label{thm:finite-observation-budget-selector-terminal-window-choice-free-section}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Every terminal cofinal-window section accepted by $F$ is determined by the displayed finite selector row $S$, the shared tail-meet route, and the Real-seal route
$$
B,S \to W \to D \to R \to E.
$$
It is not determined by a hidden choice of subsequence, a host-selected limit, a quotient stream, host real equality, a detached completion point, a metric-completeness row, or an ambient completeness oracle.
\end{theorem}
\begin{proof}
Start with terminal cofinal-window coverage, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}. It places every compatible terminal consumer on the displayed finite route through the window, dyadic ledger, regular handoff, and Real seal.

Apply the pullback lock, \autoref{thm:finite-observation-budget-selector-terminal-four-face-pullback-lock}. The four terminal faces are exactly $W,D,R,E$, so the terminal section is already read through the packet rows $B,S,W,D,R,E,H,C,P,N$.

Next use the cofinal schedule lock and tail-meet synchronization, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-schedule-lock} and \autoref{thm:finite-observation-budget-selector-terminal-tail-meet-synchronization}. These results identify the schedule-facing consumer and the shared-tail consumer with the same route rather than with a hidden subsequence choice.

Finally invoke window seal inversion, \autoref{thm:finite-observation-budget-selector-terminal-window-seal-inversion}. The Real-seal route and the terminal cofinal window determine one another over the displayed packet. Therefore the terminal section is choice-free in the stated sense: it is fixed by $S$, the tail-meet route, and the Real-seal route, and it has no hidden subsequence, host limit, quotient, host equality, detached completion, metric-completeness, or ambient-completeness coordinate.
\end{proof}

\begin{theorem}[Finite observation-budget selector budget-prefix pullback inversion]
\label{thm:finite-observation-budget-selector-budget-prefix-pullback-inversion}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Suppose a terminal four-face section is compatible with $F$, its finite budget prefix and selected-schedule prefix agree with the displayed rows $B,S$, and its terminal seal agrees with $E$ through the displayed transport, continuation, provenance, and local naming rows $H,C,P,N$. Then that terminal section is forced to be the finite route
$$
B \to S \to W \to D \to R \to E.
$$
Conversely, a section that passes through the displayed rows $B,S,W,D,R,E,H,C,P,N$ is exactly a compatible terminal four-face section for $F$.

This inversion exports only the accepted budget prefix, selected schedule, window family, dyadic ledger, regular readback, Real seal, componentwise $\hsame$ transports, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row. It excludes quotient streams, host real equality, choice rows, hidden selectors, detached completion limits, metric-completeness rows, and ambient completeness.
\end{theorem}
\begin{proof}
For the forward direction, begin with the agreed budget and schedule prefix. Terminal budget exhaustion, \autoref{thm:finite-observation-budget-selector-terminal-budget-exhaustion}, confines any compatible terminal route reaching $E$ to the displayed packet rows, so the prefix inventory cannot be enlarged beyond $B,S$ and the rows they expose.

Next bind the four terminal faces. The terminal four-face pullback lock, \autoref{thm:finite-observation-budget-selector-terminal-four-face-pullback-lock}, identifies the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces as $W,D,R,E$ inside the same $H,C,P,N$ envelope.

Now recover the window from the seal-facing read. Terminal window seal inversion, \autoref{thm:finite-observation-budget-selector-terminal-window-seal-inversion}, says that the Real-seal route and the terminal cofinal window determine one another over the displayed packet. Since the seal agrees with $E$ through $H,C,P,N$, the window-facing section is the displayed $W$ rather than a detached completion-side choice.

Finally remove hidden selection. Terminal window choice-free section, \autoref{thm:finite-observation-budget-selector-terminal-window-choice-free-section}, fixes the terminal cofinal-window section from $S$, the shared tail-meet route, and the Real-seal route. The forward section is therefore the finite route $B \to S \to W \to D \to R \to E$, with no quotient stream, host real equality, choice row, hidden selector, detached completion limit, metric-completeness row, or ambient completeness coordinate.

For the converse direction, read the displayed route as a terminal consumer surface. The four-face terminal correspondence, \autoref{thm:finite-observation-budget-selector-four-face-terminal-correspondence}, assembles the four displayed faces $W,D,R,E$ together with the agreed rows $B,S,H,C,P,N$ into a compatible terminal consumer for $F$.

The same correspondence identifies that consumer with the terminal four-face section it exposes. Hence any route through the displayed rows is exactly the compatible terminal four-face section, and the excluded quotient, host-equality, choice, hidden-selector, detached-limit, metric-completeness, and ambient-completeness data have no coordinate in either direction.
\end{proof}

\begin{theorem}[Finite observation-budget selector bounded-monotone diagonal synchronization]
\label{thm:finite-observation-budget-selector-bounded-monotone-diagonal-synchronization}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Let $M$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet whose convergence-seal route is terminal-compatible with $F$, and let $L$ be an accepted $\DiagonalLimitCompatibilityUp$ packet reading the same terminal $\RealUp$ and $\CauchyLimitSealUp$ surface. Then every downstream $\RealUp$, $\CauchyLimitSealUp$, $\RegularCauchyTailSelectorUp$, or diagonal-completion consumer compatible with $F$, $M$, and $L$ factors through the single finite terminal route
$$
B,S \to W \to D \to R \to E
$$
together with the common $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

The synchronized surface exports no quotient stream, selected host limit, host real equality, trichotomy, countable choice, hidden selector, detached completion limit, metric-completeness row, open-cover compactness, or ambient completeness oracle.
\end{theorem}
\begin{proof}
First bind the terminal surface supplied by $F$. Terminal cofinal-window coverage, \autoref{thm:finite-observation-budget-selector-terminal-cofinal-window-coverage}, places every compatible terminal read on the displayed finite window route, and the terminal four-face pullback lock, \autoref{thm:finite-observation-budget-selector-terminal-four-face-pullback-lock}, identifies the four terminal faces as $W,D,R,E$ inside the same $H,C,P,N$ envelope.

Next apply the budget-prefix inversion above. Since the compatible reads agree on the budget prefix $B,S$ and the terminal seal $E$, \autoref{thm:finite-observation-budget-selector-budget-prefix-pullback-inversion} forces the section to be exactly the route $B \to S \to W \to D \to R \to E$ rather than a route selected from outside the accepted packet.

Now attach the bounded-monotone consumer. The bounded-monotone selector terminal pullback and Real-seal route exhaustion, \autoref{thm:bounded-monotone-cauchy-witness-selector-terminal-pullback} and \autoref{thm:bounded-monotone-cauchy-witness-real-seal-public-unblock}, route the convergence-seal and limit-seal consumers through the displayed witness rows and then through the same $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Finally read the diagonal packet as a compatibility consumer of that same surface. The diagonal-limit bounded-monotone handoff and the existing compatibility pullback allow $L$ to inspect only the terminal Real and limit-seal rows already exposed by $F$ and $M$. It therefore adds no second terminal route and no independent completion-side coordinate.

Combining these route locks, every named downstream consumer factors through the single displayed terminal surface. The non-escape clauses in the finite-selector and bounded-monotone theorems exclude quotient streams, selected host limits, host real equality, trichotomy, countable choice, hidden selectors, detached completion limits, metric-completeness rows, open-cover compactness, and ambient completeness from the synchronized route.
\end{proof}

\begin{theorem}[Finite observation-budget selector bounded-monotone diagonal Lean handoff]
\label{thm:finite-observation-budget-selector-bounded-monotone-diagonal-synchronization-lean-handoff}
Let
$$
F=(B,S,W,D,R,E,H,C,P,N)
$$
be an accepted $\FiniteObservationBudgetSelectorUp$ packet. Let $M$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet, and let $L$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose $F$, $M$, and $L$ satisfy the terminal compatibility hypotheses of \autoref{thm:finite-observation-budget-selector-bounded-monotone-diagonal-synchronization}: the bounded-monotone witness reads the terminal convergence-seal route of $F$, and the diagonal packet reads the same terminal $\RealUp$ and $\CauchyLimitSealUp$ surface.

Then the later Lean target may be stated as one BEDC route handoff over exactly the displayed finite-selector rows $B,S,W,D,R,E,H,C,P,N$, the bounded-monotone selector and real-seal rows, and the diagonal seal and readback rows. The handoff consumes no quotient stream, selected host limit, host real equality, countable choice, metric-completeness row, ambient completeness oracle, hidden selector, detached completion limit, or independent diagonal completion coordinate.
\end{theorem}
\begin{proof}
First read the selector side. Terminal route status readback and terminal budget exhaustion, \autoref{thm:finite-observation-budget-selector-terminal-route-status-readback} and \autoref{thm:finite-observation-budget-selector-terminal-budget-exhaustion}, force every compatible terminal read of $F$ onto the displayed rows $B,S,W,D,R,E,H,C,P,N$.

Next attach the bounded-monotone witness. The bounded-monotone selector terminal pullback and Real-seal public route exhaustion identify the convergence-seal consumer of $M$ with the same selector surface, so its selector and real-seal rows do not introduce a second host limit, quotient stream, or countable-choice coordinate.

Finally attach the diagonal packet. The diagonal-limit compatibility four-face terminal pullback and synchronized budget terminality theorems, \autoref{thm:diagonal-limit-compatibility-four-face-terminal-pullback} and \autoref{thm:diagonal-limit-compatibility-synchronized-budget-terminality}, make $L$ a reader of the same terminal seal and readback rows rather than a supplier of an independent completion oracle.

Combining the three route locks gives a single formalization-ready BEDC obligation: Lean must consume the finite-selector rows, the bounded-monotone seal rows, and the diagonal seal/readback rows as one route handoff, with every excluded host, quotient, choice, metric-completeness, ambient-completeness, and detached-limit coordinate absent from the statement.
\end{proof}
