\section{Poset root comparison surface}
\label{sec:poset-root-comparison-surface}

\begin{definition}[POSet root comparison surface]\label{def:poset-root-comparison-surface}
The root comparison surface for $\POSetUp$ is the carried $\mathsf{BHist}$
surface whose carrier row is the unary $\mathsf{BHist}$ carrier
$\mathsf{UnaryHistory}$ of \autoref{def:poset-carrier}, whose classifier row
is the carrier $\hsame$ row on carried unary histories, and whose relation row
is the inherited prefix comparison on $\mathsf{BHist}$. Its $\NameCert$
payload consists of the inherited carrier and classifier rows, the two
directed comparison rows, the antisymmetry collapse row, and the finite
$\Cont$ ledger governed by \autoref{def:poset-ledger-policy}.
\end{definition}

\begin{theorem}[POSet root hsame transport surface]\label{thm:poset-root-hsame-transport-surface}
For carried unary $\mathsf{BHist}$ endpoints $h$ and $k$ in
\autoref{def:poset-root-comparison-surface}, an $\hsame(h,k)$ classifier row
transports the root carrier, classifier, and prefix-comparison rows without
changing the $\mathsf{UnaryHistory}$ carrier or replacing the $\NameCert$
object by a quotient representative.
\end{theorem}
\begin{proof}
Read the carrier and classifier rows from \autoref{def:poset-carrier}. The
root endpoints are already carried $\mathsf{BHist}$ histories in
$\mathsf{UnaryHistory}$, so the transport target remains inside the same
displayed carrier.

Apply the prefix stability rows of
\autoref{thm:preorder-prefix-order-laws-hsame}. They transport comparison
endpoints along $\hsame$ while preserving the inherited prefix relation on
the carried histories.

Finally repack the transported carrier, classifier, and comparison rows into
the root surface of \autoref{def:poset-root-comparison-surface}. The
$\NameCert$ object still names the same $\mathsf{BHist}$ rows and the same
finite $\Cont$ ledger.
\end{proof}

\begin{theorem}[POSet root antisymmetry surface]\label{thm:poset-root-antisymmetry-surface}
For endpoints $h,k:\mathsf{BHist}$ carried by $\mathsf{UnaryHistory}$, the two
root comparison rows $h\le_{\mathsf{pref}}k$ and
$k\le_{\mathsf{pref}}h$ determine the root classifier row $\hsame(h,k)$, and
this classifier is the one recorded by the $\POSetUp$ $\NameCert$ surface.
\end{theorem}
\begin{proof}
Project the two directed relation rows from
\autoref{def:poset-root-comparison-surface}. They are precisely the inherited
prefix-comparison rows on carried unary $\mathsf{BHist}$ endpoints.

Apply \autoref{thm:poset-prefix-antisymmetry}. The theorem collapses the
opposite prefix witnesses to the classifier conclusion $\hsame(h,k)$.

Use \autoref{thm:poset-prefix-classifier-exactness} to identify this
classifier conclusion with the carrier classifier row recorded by the root
$\NameCert$ surface. Thus antisymmetry produces no host equality or quotient
object beyond the displayed $\hsame$ row.
\end{proof}

\begin{theorem}[POSet root ledger exhaustion surface]\label{thm:poset-root-ledger-exhaustion-surface}
Every root $\POSetUp$ ledger entry used by the comparison surface is one of
the finite $\Cont$ rows named by \autoref{def:poset-ledger-policy}: the
carried $\mathsf{BHist}$ endpoints, the two directed prefix witnesses, and
the resulting $\hsame$ classifier row. No additional comparison, endpoint, or
external equality row is part of the root $\NameCert$ ledger.
\end{theorem}
\begin{proof}
Start from the ledger policy of \autoref{def:poset-ledger-policy}. It names
the finite continuation data attached to a $\POSetUp$ comparison use: carried
endpoints, directed prefix witnesses, and classifier readback.

The root surface of \autoref{def:poset-root-comparison-surface} has no other
carrier or relation coordinate. Its only relation rows are the inherited
prefix comparisons on $\mathsf{UnaryHistory}$ endpoints.

Apply \autoref{thm:poset-root-antisymmetry-surface} to any opposing pair in
the ledger. The only possible collapse row is $\hsame$, so the displayed
$\Cont$ ledger exhausts the root $\NameCert$ comparison data.
\end{proof}

\begin{theorem}[POSet root threshold unblock surface]\label{thm:poset-root-threshold-unblock-surface}
The root $\POSetUp$ surface supplies the dependency-ready rows needed by
downstream order constructions: a $\mathsf{BHist}$ carrier restricted to
$\mathsf{UnaryHistory}$, an $\hsame$ classifier, inherited prefix comparison
rows, antisymmetry, classifier exactness, and the finite $\Cont$ ledger. Any
downstream $\TotalOrderUp$ or $\OrderUp$ construction may add selector or
public-order rows, but it inherits these root rows as fixed $\NameCert$
inputs.
\end{theorem}
\begin{proof}
Collect the carrier and classifier rows from
\autoref{def:poset-root-comparison-surface}. Collect the inherited prefix
comparison and transport behavior from
\autoref{thm:poset-root-hsame-transport-surface}.

Next add the antisymmetry collapse of
\autoref{thm:poset-root-antisymmetry-surface} and the classifier exactness
row of \autoref{thm:poset-prefix-classifier-exactness}. These rows give the
partial-order boundary over the same carried $\mathsf{BHist}$ endpoints.

Finally attach the finite ledger exhaustion statement of
\autoref{thm:poset-root-ledger-exhaustion-surface}. The resulting package is
exactly the root $\NameCert$ input available to downstream order surfaces;
later selector or public export rows extend this package without replacing
its carrier, classifier, comparison, antisymmetry, exactness, or ledger rows.
\end{proof}
