The Cauchy-space route for $\CauchyEquivalenceSetoidUp$ is a child dependency of the finite regular-rational comparison surface. A consumer in \autoref{ch:concrete-instances-cauchyspace-namecert} reads the setoid only after the regular rational windows of \autoref{ch:concrete-instances-regseqrat-namecert} have exposed the comparison rows, and before the completion-facing seals of \autoref{ch:concrete-instances-metriccompletion-namecert} or \autoref{ch:concrete-instances-real-namecert} may consume them.

\begin{theorem}[CauchySpace route for Cauchy-equivalence setoids]
\label{thm:cauchy-space-cauchy-equivalence-setoid-route}
Every $\CauchySpaceUp$ consumer that uses a $\CauchyEquivalenceSetoidUp$ comparison must read it through the finite $\RegSeqRatUp$ comparison route before any $\MetricCompletionUp$ or $\RealUp$ seal is available. Thus the setoid supplies a routed comparison row for Cauchy-space and metric-completion consumers, not a detached quotient equality or a host representative selector.
\end{theorem}
\begin{proof}
Read the setoid comparison as a regular-rational route. The sibling surface of \autoref{ch:concrete-instances-regseqrat-namecert} supplies the finite windows through which two Cauchy names become comparable.

The Cauchy-space consumer of \autoref{ch:concrete-instances-cauchyspace-namecert} can then import that comparison as one row in its finite filter-uniform route. It has not yet reached a metric-completion seal or a terminal real seal.

Only downstream of that route may \autoref{ch:concrete-instances-metriccompletion-namecert} and \autoref{ch:concrete-instances-real-namecert} consume the comparison. Because the route stores no quotient equality, selected representative, or host equality test, the setoid remains a finite dependency edge in the L10 completion lattice.
\end{proof}
