\begin{theorem}[Completion and real dependency readback]
\label{thm:cauchy-equivalence-setoid-completion-real-dependency-readback}
Every $\CauchyEquivalenceSetoidUp$ read consumed by $\RegSeqRatUp$, $\RealUp$, $\CauchySpaceUp$, $\UniformSpaceCompletionUp$, or $\RealSeparabilityUp$ is available only through the displayed classifier and readback rows of the accepted packet. More precisely, a consumer may inspect the two $\StreamNameUp$ windows, the two $\RegSeqRatUp$ readback rows of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ tolerance ledger, the setoid-test classifier, the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row. The completion-facing consumers of \autoref{ch:concrete-instances-uniform-space-completion-namecert} and the density-facing consumers of \autoref{ch:concrete-instances-real-separability-namecert} receive exactly that route, so the setoid remains a child dependency of the Real-completion lattice rather than a top-level quotient stream, selected representative, countable-choice selector, host real equality, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with an accepted $\CauchyEquivalenceSetoidUp$ carrier. Its public coordinates are the two stream windows, the two regular-rational readback rows, the dyadic tolerance ledger, the setoid-test classifier, the Real seal boundary, transport, replay, provenance, and local naming.

The $\RegSeqRatUp$ and $\RealUp$ consumers read these coordinates in the order already exposed by the classifier route. The $\CauchySpaceUp$ consumer of \autoref{ch:concrete-instances-cauchyspace-namecert} receives the same comparison row only after the regular-rational readback and Real seal have been displayed.

For completion and separability consumers, apply the uniform-completion and real-separability routes. They consume the displayed comparison after the same readback and classifier rows, and neither route adds a quotient equality, selected representative, countable-choice selector, host real equality, or ambient completeness coordinate. Hence every listed sibling reads the setoid only through the displayed dependency route.
\end{proof}
