\begin{theorem}[Open-tail Cauchy equivalence transitivity route]
\label{thm:cauchy-equivalence-setoid-open-tail-transitivity}
Every open-tail classifier route from an accepted $\CauchyEquivalenceSetoidUp$ packet composes Cauchy-equivalence transitivity with the $\RealUp$ completion readback as a finite NameCert route. If two displayed comparisons share the middle regular-Cauchy read, then the consumer first reads the two $\StreamNameUp$ window pairs, then the two $\RegSeqRatUp$ readback rows of \autoref{ch:concrete-instances-regseqrat-namecert}, then the $\DyadicRatCoreUp$ tolerance ledger and transitivity row, and only then reaches the $\RealUp$ completion seal of \autoref{ch:concrete-instances-real-namecert}. The route is available to completion consumers through \autoref{ch:concrete-instances-metriccompletion-namecert}, but it exports no quotient stream equality, selected representative, host real equality, or detached completion point.
\end{theorem}
\begin{proof}
Project the accepted $\CauchyEquivalenceSetoidUp$ carrier. The two open-tail comparisons expose their finite stream windows and regular rational readbacks before the setoid classifier can be consumed.

Use the open-tail classifier route of \autoref{thm:cauchy-equivalence-setoid-open-tail-classifier}. Each comparison is already constrained to the same StreamName, RegSeqRat, DyadicRatCore, and RealUp route, so the shared middle read is a displayed row rather than a quotient representative.

Now compose the two displayed tolerance ledgers by the transitivity row carried by the setoid packet. The resulting comparison remains in the same $\BHist$ surface and is transported by the packet $\hsame$ row and replayed by its $\Cont$ row.

Finally pass the composed classifier to the Real completion readback. Since the terminal seal is downstream from the displayed windows, readbacks, dyadic ledger, transitivity row, transport, replay, provenance, and local naming, no host equality or detached completion point is introduced.
\end{proof}
