The Real classifier route of \autoref{ch:concrete-instances-real-classifier-namecert} treats \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert} as a visible sibling dependency, not as a hidden quotient boundary. Its consumer first exposes the regular rational readback discipline of \autoref{ch:concrete-instances-regseqrat-namecert}, then opens the StreamName windows and DyadicRatCore tolerance rows that make the Cauchy setoid finite before the Real-facing classifier seal is read.

\begin{theorem}[Cauchy equivalence setoid Real classifier forward dependency]
\label{thm:cauchy-equivalence-setoid-real-classifier-forward-dependency}
Every $\RealClassifierUp$ consumer that reads an accepted $\CauchyEquivalenceSetoidUp$ packet must pass through the finite route
$$
\StreamNameUp,\RegSeqRatUp,\DyadicRatCoreUp\longmapsto\CauchyEquivalenceSetoidUp\longmapsto\RealUp .
$$
The route exposes StreamName windows, RegSeqRat readbacks, and DyadicRatCore tolerance rows before any Real equality-facing seal or classifier boundary is consumed; it supplies no selected representative, quotient equality oracle, countable-choice schedule, ambient Real completeness witness, Lean verification, or bridge check.
\end{theorem}
\begin{proof}
Start from the Cauchy setoid packet and the Real classifier consumer. The packet exposes equality only through finite StreamName windows and the regular rational rows that are read on those windows.

Read the RegSeqRat and DyadicRatCore data next. These rows fix the rational readback and tolerance ledger before the classifier can ask for a Real-facing boundary.

Finally pass the visible setoid route to the Real classifier. Since the classifier receives only the displayed finite route, no quotient oracle, selected representative, choice schedule, ambient completeness datum, Lean proof, or bridge coordinate is available.
\end{proof}
