\begin{theorem}[Cauchy equivalence setoid Real separability route]
\label{thm:cauchy-equivalence-setoid-real-separability-route}
Let $Q=(S_0,S_1,R_0,R_1,D,T,E,H,C,P,N)$ be an accepted $\CauchyEquivalenceSetoidUp$ carrier. Every $\RealSeparabilityUp$ consumer that exports a $\RealUp$ read from $Q$ factors through the displayed Cauchy equivalence row, the regular rational readback rows $R_0,R_1$, the terminal Real seal row $E$, and the finite density route of \autoref{ch:concrete-instances-real-separability-namecert}. In particular, the consumer may inspect only
$$
S_0,S_1 \longmapsto R_0,R_1 \longmapsto D,T \longmapsto E \longmapsto H,C,P,N
$$
before it reaches the Real-separability density read.
\end{theorem}
\begin{proof}
Start with an accepted consumer of $Q$ that exports a Real-separability read. By \autoref{def:cauchy-equivalence-setoid-carrier}, the only equality-facing rows available to that consumer are the two StreamName windows, the two RegSeqRat readback rows, the dyadic tolerance ledger, the setoid-test row, the Real seal boundary, and the structural rows.

Apply \autoref{thm:cauchy-equivalence-setoid-classifier-laws} and \autoref{thm:cauchy-equivalence-setoid-namecert-surface}. These force the Cauchy equivalence row to be read as finite classifier data over $S_0,S_1,R_0,R_1,D,T$, with no quotient-equality or host-equality coordinate.

Next use the sibling route through \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-real-namecert}, and \autoref{ch:concrete-instances-real-separability-namecert}. The regular rational readback is inspected before $E$, and the finite density route of $\RealSeparabilityUp$ is available only after that Real seal has been displayed.

This is the forward dependency that moves the density surface of \autoref{ch:concrete-instances-real-separability-namecert} through the $\CauchyEquivalenceSetoidUp$ classifier before $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ are consumed.

Finally, \autoref{thm:cauchy-equivalence-setoid-transport} keeps the route componentwise under $H$, while $C,P,N$ replay, source, and name the same rows. Thus every Real-separability consumer factors through the displayed Cauchy equivalence, RegSeqRat readback, Real seal, and density route.
\end{proof}

\begin{theorem}[Cauchy equivalence setoid Real-separability forward link]
\label{thm:cauchy-equivalence-setoid-real-separability-forward-link}
The $\CauchyEquivalenceSetoidUp$ classifier route is the forward source consumed by the $\RealSeparabilityUp$ RegSeqRat dependency lattice. Any consumer using \autoref{ch:concrete-instances-real-separability-namecert} together with the regular rational surface of \autoref{ch:concrete-instances-regseqrat-namecert} must first read the displayed Cauchy-equivalence classifier rows, the two RegSeqRat readback rows, the dyadic tolerance ledger, and the Real seal boundary supplied by the accepted $\CauchyEquivalenceSetoidUp$ packet.

Consequently the RealSeparability density surface receives a finite Cauchy/RegSeqRat comparison route rather than a quotient stream equality, selected representative, host real equality, countable-choice selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Begin with the accepted $\CauchyEquivalenceSetoidUp$ classifier route. Its visible source rows are the two StreamName windows, the two RegSeqRat readback rows, the dyadic tolerance ledger, the setoid-test row, the Real seal boundary, and the $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ support.

Apply \autoref{thm:cauchy-equivalence-setoid-real-separability-route}. That route places the RealSeparability consumer after the Cauchy-equivalence classifier, the RegSeqRat readback rows, and the Real seal boundary, so the density read cannot bypass the displayed setoid comparison.

Now read the RegSeqRat dependency through \autoref{ch:concrete-instances-regseqrat-namecert}. The same regular rational rows that feed the Cauchy-equivalence classifier are the rows consumed by the RealSeparability lattice, and \autoref{ch:concrete-instances-real-separability-namecert} receives them as finite classifier-facing data.

The route is consumed by \autoref{ch:concrete-instances-real-separability-namecert} because the Cauchy-equivalence setoid classifier rows provide the dense-read equality surface used by $\RealSeparabilityUp$.

The excluded objects have no source row in this route. Quotient stream equality, selected representatives, host real equality, countable-choice selectors, and ambient completeness data are not among the displayed classifier, readback, tolerance, seal, transport, continuation, package, or naming rows, so they cannot serve as a second forward dependency.
\end{proof}
