\section{Downstream Dependency Lattice}
\label{sec:hyperspace-downstream-dependency-lattice}

\begin{theorem}[Hyperspace Vietoris downstream dependency]
\label{thm:hyperspace-vietoris-downstream-dependency}
Every $\VietorisTopologyUp$ or $\HausdorffDistanceUp$ downstream read of an accepted $\HyperspaceUp$ packet consumes the compact source, finite subset-net schedules, and directed coverage ledgers of \autoref{thm:hyperspace-vietoris-handoff} before it may expose a topology row or distance row. In particular, the interfaces of \autoref{ch:concrete-instances-vietoris-topology-namecert} and \autoref{ch:concrete-instances-hausdorff-distance-namecert} both pass through the compact-metric boundary of \autoref{ch:concrete-instances-compactmetric-namecert}; neither consumer receives a host powerset topology, quotient compactum, selected compact limit, open-cover compactness proof, or untracked Hausdorff metric.
\end{theorem}
\leanchecked{BEDC.Derived.HyperspaceUp.HyperspaceVietorisDownstreamDependency}
\begin{proof}
Read the handoff theorem \autoref{thm:hyperspace-vietoris-handoff}. It forces any Vietoris-topology or Hausdorff-distance consumer to open the compact source row, finite subset-net schedules, directed coverage ledgers, and tolerance readback row before the structural transport, replay, provenance, and naming rows are public.

For a $\VietorisTopologyUp$ consumer, the topology row is therefore downstream from the finite hit, miss, and refinement data already supplied by the compact source and subset-net schedules. It cannot be exposed as a host powerset topology independent of those rows.

For a $\HausdorffDistanceUp$ consumer, the distance row is downstream from the two directed coverage ledgers and the same tolerance readback boundary. It cannot be exposed as an untracked metric, selected compact limit, quotient compactum, or open-cover compactness proof.

Thus the compact-metric dependency of \autoref{ch:concrete-instances-compactmetric-namecert} sits below both downstream consumers in the same lattice: compact source first, finite nets and directed coverage next, topology or distance rows only after that displayed dependency path.
\end{proof}
