\begin{theorem}[Hyperspace Vietoris handoff]
\label{thm:hyperspace-vietoris-handoff}
Every Vietoris-topology or Hausdorff-distance consumer of an accepted $\HyperspaceUp$ packet must first read the compact source row, the finite subset-net schedules, both directed coverage ledgers, and the tolerance readback row. In the notation of \autoref{def:hyperspace-carrier}, the route is
$$
X,K_0,K_1,N_0,N_1,D_0,D_1,R \longmapsto H_s,C,P,M .
$$
Thus the downstream interfaces of \autoref{ch:concrete-instances-vietoris-topology-namecert} and \autoref{ch:concrete-instances-hausdorff-distance-namecert} consume the same compact-source and finite-net boundary supplied by \autoref{ch:concrete-instances-compactmetric-namecert}. When hyperspace packets are read through metric distance-to-closed-set witnesses, the Vietoris finite-hit and finite-miss surface also consumes the distance-function embedding route of \autoref{ch:concrete-instances-kuratowski-embedding-namecert}; the consumers receive no host powerset topology, quotient compactum, selected compact limit, open-cover compactness proof, or untracked Hausdorff metric.
\end{theorem}
\begin{proof}
Project the accepted $\HyperspaceUp$ carrier. The source row $X$ is the only compact metric source, and the finite subset-net schedules are displayed by $K_0,K_1,N_0,N_1$ before any directed distance or topology read is public.

Use the Hausdorff-distance ledger stability and finite Hausdorff carrier theorems of \autoref{thm:hyperspace-hausdorff-distance-stability} and \autoref{thm:hyperspace-finite-hausdorff-carrier}. They force the two directed coverage ledgers $D_0,D_1$ and the tolerance readback row $R$ to be present before a symmetric Hausdorff consumer can read a distance value.

For Vietoris consumers, use the root Vietoris net basis and refinement factorization in \autoref{thm:hyperspace-root-vietoris-net-basis} and \autoref{thm:hyperspace-vietoris-refinement-factorization}. Those results route hit, miss, and refinement reads through the same compact source and finite subset-net schedules.

Both public reads therefore have the same source lock. The Vietoris-topology read cannot expose a hit or miss neighborhood until it has consumed the compact-metric source row $X$, the finite subset-net schedules $K_0,K_1,N_0,N_1$, and the directed coverage ledgers $D_0,D_1$ that witness how the scheduled finite subsets cover the compact source.

The Hausdorff-distance read is locked by the same rows. Before a symmetric distance value is public, the two directed coverage ledgers must already be visible over the displayed compact-metric source row and the finite subset-net schedules; otherwise the row would be an untracked host metric rather than the displayed Hausdorff-distance consumer of the hyperspace packet.

The structural rows $H_s,C,P,M$ only transport, replay, source, and name this displayed packet. Since no forbidden host powerset, quotient compactum, selected compact limit, open-cover compactness proof, or untracked Hausdorff metric appears in the carrier, every Vietoris or Hausdorff consumer must use the stated handoff.
\end{proof}
\leanchecked{BEDC.Derived.HyperspaceUp.Hyperspace\_vietoris\_handoff}

\begin{lemma}[Vietoris located-real tolerance dependency]
\label{thm:hyperspace-vietoris-located-real-dependency}
Every Vietoris-topology or Hausdorff-distance consumer of an accepted $\HyperspaceUp$ packet that reads tolerance comparisons must route the tolerance through $\LocatedRealUp$ or the RealUp located-tolerance ledger before reading the symmetric Hausdorff value. In the notation of \autoref{def:hyperspace-carrier}, the tolerance readback row $R$ is therefore downstream of the compact source, finite subset-net schedules, and directed coverage ledgers named by \autoref{thm:hyperspace-vietoris-handoff}, and upstream of the Hausdorff read consumed by \autoref{ch:concrete-instances-hausdorff-distance-namecert}.
\end{lemma}
\begin{proof}
Project the accepted $\HyperspaceUp$ carrier. The compact source and finite subset-net schedules are the rows $X,K_0,K_1,N_0,N_1$, while $D_0,D_1$ record the directed coverage ledgers.

Apply \autoref{thm:hyperspace-vietoris-handoff}. It forces both Vietoris and Hausdorff consumers to expose those rows before the tolerance readback row $R$ becomes available.

The tolerance comparison itself must then be read through the displayed $\LocatedRealUp$ surface of \autoref{ch:concrete-instances-located-real-namecert} or through the located-tolerance ledger sealed by \autoref{ch:concrete-instances-real-namecert}. Since the carrier has no separate coordinate for an untracked Hausdorff metric or a host real comparison, the symmetric Hausdorff value can only be consumed after that located tolerance route is visible.
\end{proof}
\leanchecked{BEDC.Derived.HyperspaceUp.HyperspaceVietorisLocatedRealDependency}
