\chapter{A Concrete Naming Certificate for $\InactiveLayerQuotientDynamicsUp$}
\label{ch:concrete-instances-inactive-layer-quotient-dynamics-namecert}
\origin{ai}

The $\InactiveLayerQuotientDynamicsUp$ packet realizes the zero-marker inactive-layer quotient dynamics of \autoref{thm:philosophy-weighted-quotient-path} and \autoref{thm:philosophy-inactive-median-layer} as finite orbit-state NameCert data. It sits beside the DNA boundary-tile packet of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the finite trace evaluator of \autoref{ch:concrete-instances-finitetraceevaluator-namecert}, the Hilbert--Alexander blocker surface of \autoref{ch:concrete-instances-hilbert-alexander-blocker-namecert}, and the arity-ten $\BHist$ tuple capstone of \autoref{ch:concrete-instances-b-hist-deca-tuple-name-cert-namecert}. Those siblings expose boundary, finite evaluation, blocker, or tuple-capacity rows separately; this packet binds the six active orbit states, weighted path, inactive median layer, and active-inactive trigger boundary into one carrier.

\begin{definition}[Inactive-layer quotient dynamics carrier]
\label{def:inactive-layer-quotient-dynamics-carrier}
An $\InactiveLayerQuotientDynamicsUp$ carrier is a finite $\BHist$ packet
$$
Q=(O,W,I,A,B,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the six orbit-state row containing $\mathrm{AGR}$, $\mathrm{Anchor}_{6}$, $\mathrm{StopStart}_{6}$, $\mathrm{UUR}$, $\mathrm{CUR}$, and $\mathrm{CUY}$;
\item $W$ is the weighted quotient-path row, recording exactly the cross-orbit Hamming weights displayed in \autoref{thm:philosophy-weighted-quotient-path};
\item $I$ is the inactive median-layer row, carrying $\mathrm{WYG}\cup\{\mathrm{AAG},\mathrm{ACA},\mathrm{UGG}\}$ and its square-with-leaves graph;
\item $A$ is the active-inactive interface row, exposing the two active gates and the inactive-square contact point;
\item $B$ is the boundary-tile provenance row read from the DNA six-window boundary surface;
\item $T$ is the trigger-boundary ledger, binding the weighted path and inactive layer before any zero-marker dynamics read is exported;
\item $H$ records componentwise $\hsame$ transport for $O,W,I,A,B,T,C,P,N$;
\item $C$ records displayed $\Cont$ replay for the orbit-state, inactive-layer, and trigger-boundary route;
\item $P$ is the $\Pkg$ provenance over $\InactiveLayerQuotientDynamicsUp$, the philosophy quotient-dynamics source, DNA boundary tiles, finite trace evaluation, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\InactiveLayerQuotientDynamicsUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these finite rows. It has no coordinate for an unlisted cross-orbit Hamming edge, stochastic biological semantics, quotient codon equality, hidden genome dynamics, or a host automaton oracle.
\end{definition}

\begin{theorem}[Inactive-layer quotient dynamics obligations]
\label{thm:inactive-layer-quotient-dynamics-obligations}
For the carrier of \autoref{def:inactive-layer-quotient-dynamics-carrier}, the local $\NameCert_{\InactiveLayerQuotientDynamicsUp}$ surface consists exactly of orbit-state admission through $O$, weighted-path admission through $W$, inactive-layer admission through $I$, active-inactive interface admission through $A$, boundary-tile provenance through $B$, trigger-boundary binding through $T$, and structural transport, replay, provenance, and local naming through $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier $Q=(O,W,I,A,B,T,H,C,P,N)$. The orbit row $O$ displays the six states, and the weighted row $W$ records the path and its cross-orbit weights.

Read the inactive and interface rows next. The row $I$ displays the zero-marker inactive layer, while $A$ identifies the active gates and contact point through which active and inactive reads meet.

The boundary and trigger rows bind the packet. The provenance row $B$ keeps the construction on the DNA boundary-tile surface, and $T$ requires the quotient path and inactive layer to be read together before dynamics are exported. Transport, replay, provenance, and naming then preserve the same finite inventory.
\end{proof}

\begin{theorem}[Inactive-layer quotient dynamics trigger boundary]
\label{thm:inactive-layer-quotient-dynamics-trigger-boundary}
Every accepted $\InactiveLayerQuotientDynamicsUp$ dynamics read factors through
$$
O,W,I,A,B,T,H,C,P,N .
$$
In particular, a zero-marker inactive-layer read must expose the weighted six-state quotient path, the inactive square-with-leaves layer, the active gates, and the contact point before any trigger-boundary conclusion is read.
\end{theorem}
\begin{proof}
Use \autoref{thm:inactive-layer-quotient-dynamics-obligations}. It makes $O,W,I,A$ the visible orbit, path, inactive-layer, and interface rows of the packet.

The trigger boundary is not independent of those rows. The row $T$ binds the active and inactive surfaces after $B$ has recorded the boundary-tile provenance, so a dynamics consumer cannot detach the inactive layer from the displayed quotient path.

Since the carrier has no unlisted cross-orbit edge, stochastic semantics, quotient codon equality, hidden dynamics row, or host automaton oracle, every accepted trigger-boundary read remains inside the displayed finite route.
\end{proof}

\falsifiablePrediction{The weighted inactive-layer quotient path fails if a nonlisted cross-orbit Hamming edge is exhibited between two orbit states outside the displayed path rows $O,W,I,A$.}

\independenceWitness{dna-window-six-boundary-tile, finite-trace-evaluator, hilbert-alexander-blocker, b-hist-deca-tuple-name-cert, metaciccriticalpath: none is bijective to $\InactiveLayerQuotientDynamicsUp$ because each lacks at least one of the six orbit-state row, weighted quotient path, inactive square-with-leaves layer, active gate interface, and trigger-boundary ledger bound in this packet.}

\closureat{InactiveLayerQuotientDynamicsUp}{seedStr}

\begin{closurestatus}{\InactiveLayerQuotientDynamicsUp}
  \constructivestory{An $\InactiveLayerQuotientDynamicsUp$ packet is generated from six orbit states, weighted quotient-path rows, inactive median-layer rows, active-inactive interface rows, boundary-tile provenance, a trigger-boundary ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert data.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:inactive-layer-quotient-dynamics-carrier}, \autoref{thm:inactive-layer-quotient-dynamics-obligations}, and \autoref{thm:inactive-layer-quotient-dynamics-trigger-boundary} seed the finite inactive-layer quotient dynamics packet and its trigger boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim stochastic biological semantics, quotient codon equality, hidden genome dynamics, an unlisted cross-orbit Hamming edge, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked orbit-state admission, weighted-path admission, inactive-layer admission, active-inactive interface admission, trigger-boundary binding, transport, replay, provenance, and local naming for BEDC.Derived.InactiveLayerQuotientDynamicsUp.}
\end{closurestatus}
